### 2020-02-12 writeup/setup.tex
edit

\section{Problem setup}

\begin{enumerate}
%    \item {\bf The distributed learning problem.}
%    \begin{align}
 %     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
 %   \end{align}
 %   A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spetrum.
 %   This is also known as covariate shift in the literature.
 %   Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.
  \item {\bf The multi-task learning problem.} \\
    {\it Different covariates:}
    If we follow the model setup of the first problem, but consider the following objective instead.
    \begin{align}
        f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
    \end{align}
    This is a slightly more complicated parameterization of the first problem, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

    {\it Different models:} The most general version is when the covariates are different between different tasks and the single-task models are also different.
    Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
\end{enumerate}

\section{General hypothesis}

Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}. \todo{Add some references to add spice on these takes.}

\subsection{Covariate shift}

In this setting, we assume that the covariates of task $i$ are drawn from $\Sigma_i \in \real^{d \times d}$, but the models are the same across all the tasks, i.e.
\begin{align}
  y_i = X_i \theta + \varepsilon_i, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
\end{align}

Since the models are same, the most natural objective is using Equation \eqref{eq_dist}.

\begin{proposition}
  Show that adding tasks always helps or reduces estimation error.
\end{proposition}

\paragraph{The case of two tasks: $k = 2$.} We would like to get insight on how the covariate shift results in slower rates of transfer. The key quantity is to look at:
\begin{align}
  \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}]
\end{align}

\subsection{Model shift}

We remove the assumption that the models are the same. The $i$-th task data can be viewed as generated by a separate model $\theta_i$. 
\begin{align}
  y_i = X_i \theta_i + \varepsilon_i.
\end{align}

%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}

### 2020-02-12 writeup/setup.tex
edit

@@
-\section{Problem setup}
+\section{Problem setup: The multi-task learning problem}\label{sec_setup}
 
-\begin{enumerate}
 %    \item {\bf The distributed learning problem.}
@@
  %   Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.
-  \item {\bf The multi-task learning problem.} \\
-    {\it Different covariates:}
+
+    \paragraph{Different covariates:}
     If we follow the model setup of the first problem, but consider the following objective instead.
@@
 
-    {\it Different models:} The most general version is when the covariates are different between different tasks and the single-task models are also different.
+    \paragraph{Different models:} The most general version is when the covariates are different between different tasks and the single-task models are also different.
     Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
-\end{enumerate}
 

### 2020-02-12 writeup/setup.tex
wip

@@
-\section{Problem setup: The multi-task learning problem}\label{sec_setup}
+\section{Problem Setup}\label{sec_setup}
 
-%    \item {\bf The distributed learning problem.}
+In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
+We use a shared module $B$ for all tasks and a separate module $\set{A_i}_{i=1}^k$ for each task.
+%    \paragraph{Different covariates:}
+This corresponds to minimizing the following optimization objective.
+\begin{align}
+	\label{eq_mtl}
+	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
+\end{align}
+
+When the models are the same for all tasks, we use a simplified objective as follows.
+\begin{align}
+	\label{eq_mtl_basic}
+	f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2.
+\end{align}
+%{\bf The distributed learning problem.}
 %    \begin{align}
@@
 %   \end{align}
- %   A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spetrum.
- %   This is also known as covariate shift in the literature.
- %   Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.
 
-    \paragraph{Different covariates:}
-    If we follow the model setup of the first problem, but consider the following objective instead.
-    \begin{align}
-        f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
-    \end{align}
-    This is a slightly more complicated parameterization of the first problem, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
+Equation \eqref{eq_mtl} is a slightly more complicated parametrization of equation \eqref{eq_mtl_basic}, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
 
-    \paragraph{Different models:} The most general version is when the covariates are different between different tasks and the single-task models are also different.
-    Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
-
-\section{General hypothesis}
+\subsection{Hypothesis}
 
@@
 
-\subsection{Covariate shift}
+\subsubsection{Covariate Shift}
+
+A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spectrum.
+This is also known as covariate shift in the literature.
+Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.
 
@@
 
-Since the models are same, the most natural objective is using Equation \eqref{eq_dist}.
+\subsubsection{Model Shift}
 
-\begin{proposition}
-  Show that adding tasks always helps or reduces estimation error.
-\end{proposition}
+The most general version is when the covariates are different between different tasks and the single-task models are also different.
+Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
 
-\paragraph{The case of two tasks: $k = 2$.} We would like to get insight on how the covariate shift results in slower rates of transfer. The key quantity is to look at:
-\begin{align}
-  \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}]
-\end{align}
-
-\subsection{Model shift}
-
-We remove the assumption that the models are the same. The $i$-th task data can be viewed as generated by a separate model $\theta_i$. 
+We remove the assumption that the models are the same.
+The $i$-th task data can be viewed as generated by a separate model $\theta_i$.
 \begin{align}

### 2020-02-24 writeup/setup.tex
edit
edits

@@
 Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
-\todo{Add some references to add spice on these takes.}
+%\todo{Add some references to add spice on these takes.}
 
@@
 This is also known as covariate shift in the literature.
-Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.
+Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.
 
@@
 \begin{align}
-	y_i = X_i \theta + \varepsilon_i, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
+	y_i = X_i \beta + \varepsilon_i, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
 \end{align}
@@
 We remove the assumption that the models are the same.
-The $i$-th task data can be viewed as generated by a separate model $\theta_i$.
+The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^d$.
 \begin{align}
-	y_i = X_i \theta_i + \varepsilon_i.
+	y_i = X_i \beta_i + \varepsilon_i.
 \end{align}
 
+\subsection{Objectives}
+
+We will designate the $k$-th task as the target.
+Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task.
+Concretely, we focus on two objectives.
+\begin{itemize}
+	\item Estimation error for the target model $\beta_t$: we consider their distance
+		\[ \exarg{\varepsilon}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
+	\item Test error for the target task:
+		\[ \exarg{x \sim \Sigma_k}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}. \]
+\end{itemize}
+%\todo{may also consider test error}
 %Several relevant directions on this setting.

### 2020-03-16 writeup/setup.tex
edit

@@
 
+One important case is the sparse case, where we assume that the $\beta_i$'s are sparse in the sense 
+that each $\beta_i$ is in a subspace of dimension $k_i\ll p$. In other words,
+$$\beta_i = \sum_{j=1}^{k_i} a^{(i)}_j v^{(i)}_j,$$
+where $\{v^{(i)}_j\}$ is a set of $k_i$ orthonormal vectors. For $X_i= Z_i \Sigma_i^{1/2}$, we have 
+$$ X_i \beta_i = Z_i \Sigma_i^{1/2}\beta_i=  Z_i \Sigma_i^{1/2}P_i\beta_i,\quad P_i:= \sum_{j=1}^{k_i}v_j^{(i)}(v_j^{(i)})^\top.$$
+Then we have 
+$$\frac{1}{n_i}\mathbb E\left[P_i \Sigma_i^{1/2} Z_i^T Z_i \Sigma_i^{1/2}P_i\right]=P_i \Sigma_i P_i.$$
+Hence our analysis will be valid with projected covariance matrices $P_i \Sigma_i P_i$. Moreover, due to the sparsity assumption, it is natural to have restricted isometry property: 
+$$\frac{1}{n_i} P_i \Sigma_i^{1/2} Z_i^T Z_i \Sigma_i^{1/2}P_i \approx P_i \Sigma_i P_i.$$
+Finally, for our analysis it is not necessary to assume that $\beta_T$ is sparse for the target.
+
 \subsection{Objectives}

### 2020-03-16 writeup/setup.tex
edit

@@
 
+\paragraph{Sparse models.}
 One important case is the sparse case, where we assume that the $\beta_i$'s are sparse in the sense 

### 2020-03-16 writeup/setup.tex
wip

@@
 In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
-We use a shared module $B$ for all tasks and a separate module $\set{A_i}_{i=1}^k$ for each task.
+We use a shared body (module) $B$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
 %    \paragraph{Different covariates:}
@@
 \end{align}
-
-When the models are the same for all tasks, we use a simplified objective as follows.
-\begin{align}
-	\label{eq_mtl_basic}
-	f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2.
-\end{align}
-%{\bf The distributed learning problem.}
-%    \begin{align}
-%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
-%   \end{align}
-
-Equation \eqref{eq_mtl} is a slightly more complicated parametrization of equation \eqref{eq_mtl_basic}, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
+Note that we consider the natural parameterization without reweighting the tasks above.
 
@@
 \begin{align}
-	y_i = X_i \beta + \varepsilon_i, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
+	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
 \end{align}
+
+When the models are the same for all tasks, we use a simplified objective as follows.
+\begin{align}
+	\label{eq_mtl_basic}
+	f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2.
+\end{align}
+%{\bf The distributed learning problem.}
+%    \begin{align}
+%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
+%   \end{align}
+
+Equation \eqref{eq_mtl} is a slightly more complicated parametrization of equation \eqref{eq_mtl_basic}, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
 

### 2020-03-16 writeup/setup.tex
wip

@@
 	\label{eq_mtl}
-	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
+	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \norm{X_i B A_i - Y_i}^2.
 \end{align}
 Note that we consider the natural parameterization without reweighting the tasks above.
+The shared body $B$ plays an important role because it allows information transfer between different task data.
 
@@
 %\todo{Add some references to add spice on these takes.}
+We consider two natural questions within each category.
+\begin{itemize}
+	\item How does covariate shift affect the rate of information transfer? For example, is it better to have the same covariance matrix or not?
+	\item Under model shift, when do we get positive vs. negative transfer? How does the type of transfer depend on the number of data points, the distance of the task models etc?
+\end{itemize}
 
@@
 	\label{eq_mtl_basic}
-	f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2.
+	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
 \end{align}

### 2020-03-16 writeup/setup.tex
wip

@@
 
-A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spectrum.
+A natural setting is when the covariance matrices $\frac{1}{n_i}\cdot X_i^{\top} X_i$ are different, i.e. having different spectrum or singular vectors.
 This is also known as covariate shift in the literature.
-Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.
+\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
 
@@
 %   \end{align}
-
-Equation \eqref{eq_mtl} is a slightly more complicated parametrization of equation \eqref{eq_mtl_basic}, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
+Equation \eqref{eq_mtl_basic} is simplified from Equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
 
@@
 
-The most general version is when the covariates are different between different tasks and the single-task models are also different.
-Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
-
-We remove the assumption that the models are the same.
-The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^d$.
+In addition to covariate shift, in general the single-task models can also be different across different tasks.
+\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.}
+%We remove the assumption that the models are the same.
+The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
 \begin{align}
-	y_i = X_i \beta_i + \varepsilon_i.
+	Y_i = X_i \beta_i + \varepsilon_i.
 \end{align}
@@
 We will designate the $k$-th task as the target.
-Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task.
+Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
 Concretely, we focus on two objectives.
@@
 	\item Estimation error for the target model $\beta_t$: we consider their distance
-		\[ \exarg{\varepsilon}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
+		\[ \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
 	\item Test error for the target task:
-		\[ \exarg{x \sim \Sigma_k}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}. \]
+		\[ \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}}. \]
 \end{itemize}

### 2020-03-16 writeup/setup.tex
wip

@@
 In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
-We use a shared body (module) $B$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
+We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
 %    \paragraph{Different covariates:}
@@
 The shared body $B$ plays an important role because it allows information transfer between different task data.
+There are two ways to ensure the sharing of information between tasks.
+\begin{itemize}
+	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
+	\item Controlling the capacity $r$ of $B$.
+\end{itemize}
 

### 2020-03-16 writeup/setup.tex
wip

@@
 In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
-We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
+We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{A_i \in \real^{r}}_{i=1}^k$ for each task.
 %    \paragraph{Different covariates:}
@@
 
+\begin{proposition}\label{prop_monotone}
+  When there is no model shift, adding the source task data always reduces the estimation error, i.e.
+	\[ e(\hat{\beta}_{s,t}) \le e(\hat{\beta}_t). \]
+\end{proposition}
+
+\begin{proof}
+	This is simply because $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}}$.
+\end{proof}
+
 \subsubsection{Model Shift}

### 2020-03-16 writeup/setup.tex
wip

@@
 
+\paragraph{Objectives.}
+We will designate the $k$-th task as the target.
+Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
+Concretely, we focus on two objectives.
+\begin{itemize}
+	\item Estimation error for the target model $\beta_t$: we consider their distance
+		\[ e(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
+	\item Test error for the target task:
+		\begin{align*}
+			te(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
+			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
+		\end{align*}
+\end{itemize}
+%\todo{may also consider test error}
+%Several relevant directions on this setting.
+%\begin{itemize}
+%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
+%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
+%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
+%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
+%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
+%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
+%\end{itemize}
+
 \subsubsection{Covariate Shift}
@@
 \begin{proposition}\label{prop_monotone}
+	Suppose that $n > p$.
   When there is no model shift, adding the source task data always reduces the estimation error, i.e.
@@
 Finally, for our analysis it is not necessary to assume that $\beta_T$ is sparse for the target.
-
-\subsection{Objectives}
-
-We will designate the $k$-th task as the target.
-Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
-Concretely, we focus on two objectives.
-\begin{itemize}
-	\item Estimation error for the target model $\beta_t$: we consider their distance
-		\[ \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
-	\item Test error for the target task:
-		\[ \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}}. \]
-\end{itemize}
-%\todo{may also consider test error}
-%Several relevant directions on this setting.
-%\begin{itemize}
-%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
-%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
-%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
-%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
-%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
-%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
-%\end{itemize}

### 2020-03-16 writeup/setup.tex
wip

@@
 
-\subsection{Hypothesis}
-
-Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
-%\todo{Add some references to add spice on these takes.}
-We consider two natural questions within each category.
-\begin{itemize}
-	\item How does covariate shift affect the rate of information transfer? For example, is it better to have the same covariance matrix or not?
-	\item Under model shift, when do we get positive vs. negative transfer? How does the type of transfer depend on the number of data points, the distance of the task models etc?
-\end{itemize}
+\paragraph{Data generation.} We shall assume that each task data follows a linear model.
+For every $1\le i\le k$, we assume that
+\[ Y_i = X_i \beta_i + \varepsilon_i, \]
+where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
+Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
 
@@
 
+\subsection{Hypothesis}
+
+Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
+%\todo{Add some references to add spice on these takes.}
+We consider two natural questions within each category.
+\begin{itemize}
+	\item How does covariate shift affect the rate of information transfer? For example, is it better to have the same covariance matrix or not?
+	\item Under model shift, when do we get positive vs. negative transfer? How does the type of transfer depend on the number of data points, the distance of the task models etc?
+\end{itemize}
+
 \subsubsection{Covariate Shift}
 
-A natural setting is when the covariance matrices $\frac{1}{n_i}\cdot X_i^{\top} X_i$ are different, i.e. having different spectrum or singular vectors.
+A natural setting is when the covariance matrices $\Sigma_i$ are different across tasks, i.e. having different spectrum or singular vectors.
 This is also known as covariate shift in the literature.
 \todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
+A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
+%\begin{align}
+%	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim
+%\Sigma_i
+%\end{align}
 
-In this setting, we assume that the covariates of task $i$ are drawn from $\Sigma_i \in \real^{d \times d}$, but the models are the same across all the tasks, i.e.
-\begin{align}
-	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
-\end{align}
-
-When the models are the same for all tasks, we use a simplified objective as follows.
+Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
 \begin{align}
@@
 %   \end{align}
-Equation \eqref{eq_mtl_basic} is simplified from Equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
+Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
 
@@
 	Suppose that $n > p$.
-  When there is no model shift, adding the source task data always reduces the estimation error, i.e.
-	\[ e(\hat{\beta}_{s,t}) \le e(\hat{\beta}_t). \]
+  When there is no model shift, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
+	\begin{align}
+		e(\hat{\beta}_{s,t})  &\le e(\hat{\beta}_t), \text{ and} \label{eq_mono_e}\\
+		te(\hat{\beta}_{s,t}) &\le te(\hat{\beta}_t) \label{eq_mono_te}
+	\end{align}
 \end{proposition}
@@
 \begin{proof}
-	This is simply because $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}}$.
+	Equation \eqref{eq_mono_e} is simply because
+		\[ e(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = e(\hat{\beta}_t). \]
+	Equation \eqref{eq_mono_te} follows because
+	\begin{align*}
+		te(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} &= \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
+		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
+			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = te(\hat{\beta}_t).
+	\end{align*}
 \end{proof}
@@
 
-\paragraph{Sparse models.}
+\subsection{Sparse models}
 One important case is the sparse case, where we assume that the $\beta_i$'s are sparse in the sense 

### 2020-03-17 writeup/setup.tex
wip

@@
 %We remove the assumption that the models are the same.
-The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
-\begin{align}
-	Y_i = X_i \beta_i + \varepsilon_i.
-\end{align}
+%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
+%\begin{align}
+%	Y_i = X_i \beta_i + \varepsilon_i.
+%\end{align}
 
-\subsection{Sparse models}
+\subsection{The Sparse Setting}
 One important case is the sparse case, where we assume that the $\beta_i$'s are sparse in the sense 

### 2020-03-25 writeup/setup.tex
wip
setup scale

@@
 	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
-	\item Controlling the capacity $r$ of $B$.
+	\item Controlling the capacity $r$ of $B$, e.g.
+\cite{KD12,WZR20}.
+Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
 \end{itemize}
@@
 Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
+We assume that for every row $x$ of $X_i$, we have
+\[ \ex{xx^{\top}} = \Sigma_i. \]
+We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
 
@@
 	\item Estimation error for the target model $\beta_t$: we consider their distance
-		\[ e(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
+		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
 	\item Test error for the target task:
 		\begin{align*}
-			te(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
+			\te(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
 			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
@@
 	\begin{align}
-		e(\hat{\beta}_{s,t})  &\le e(\hat{\beta}_t), \text{ and} \label{eq_mono_e}\\
-		te(\hat{\beta}_{s,t}) &\le te(\hat{\beta}_t) \label{eq_mono_te}
+		\err(\hat{\beta}_{s,t})  &\le \err(\hat{\beta}_t), \text{ and} \label{eq_mono_e}\\
+		\te(\hat{\beta}_{s,t}) &\le \te(\hat{\beta}_t) \label{eq_mono_te}
 	\end{align}
@@
 	Equation \eqref{eq_mono_e} is simply because
-		\[ e(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = e(\hat{\beta}_t). \]
+		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
 	Equation \eqref{eq_mono_te} follows because
 	\begin{align*}
-		te(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} &= \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
+		\te(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} &= \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
 		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = te(\hat{\beta}_t).
+			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t).
 	\end{align*}

### 2020-03-27 writeup/extension.tex
reorg

--- 2020-03-17 writeup/setup.tex
@@
-\section{Problem Setup}\label{sec_setup}
-
-In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
-We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{A_i \in \real^{r}}_{i=1}^k$ for each task.
-%    \paragraph{Different covariates:}
-This corresponds to minimizing the following optimization objective.
-\begin{align}
-	\label{eq_mtl}
-	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \norm{X_i B A_i - Y_i}^2.
-\end{align}
-Note that we consider the natural parameterization without reweighting the tasks above.
-The shared body $B$ plays an important role because it allows information transfer between different task data.
-There are two ways to ensure the sharing of information between tasks.
-\begin{itemize}
-	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
-	\item Controlling the capacity $r$ of $B$.
-\end{itemize}
-
-\paragraph{Data generation.} We shall assume that each task data follows a linear model.
-For every $1\le i\le k$, we assume that
-\[ Y_i = X_i \beta_i + \varepsilon_i, \]
-where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
-
-\paragraph{Objectives.}
-We will designate the $k$-th task as the target.
-Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
-Concretely, we focus on two objectives.
-\begin{itemize}
-	\item Estimation error for the target model $\beta_t$: we consider their distance
-		\[ e(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
-	\item Test error for the target task:
-		\begin{align*}
-			te(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
-			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
-		\end{align*}
-\end{itemize}
-%\todo{may also consider test error}
-%Several relevant directions on this setting.
-%\begin{itemize}
-%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
-%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
-%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
-%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
-%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
-%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
-%\end{itemize}
-
-\subsection{Hypothesis}
-
-Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
-%\todo{Add some references to add spice on these takes.}
-We consider two natural questions within each category.
-\begin{itemize}
-	\item How does covariate shift affect the rate of information transfer? For example, is it better to have the same covariance matrix or not?
-	\item Under model shift, when do we get positive vs. negative transfer? How does the type of transfer depend on the number of data points, the distance of the task models etc?
-\end{itemize}
-
-\subsubsection{Covariate Shift}
-
-A natural setting is when the covariance matrices $\Sigma_i$ are different across tasks, i.e. having different spectrum or singular vectors.
-This is also known as covariate shift in the literature.
-\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
-A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
-%\begin{align}
-%	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim
-%\Sigma_i
-%\end{align}
-
-Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
-\begin{align}
-	\label{eq_mtl_basic}
-	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
-\end{align}
-%{\bf The distributed learning problem.}
-%    \begin{align}
-%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
-%   \end{align}
-Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
-
-\begin{proposition}\label{prop_monotone}
-	Suppose that $n > p$.
-  When there is no model shift, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
-	\begin{align}
-		e(\hat{\beta}_{s,t})  &\le e(\hat{\beta}_t), \text{ and} \label{eq_mono_e}\\
-		te(\hat{\beta}_{s,t}) &\le te(\hat{\beta}_t) \label{eq_mono_te}
-	\end{align}
-\end{proposition}
-
-\begin{proof}
-	Equation \eqref{eq_mono_e} is simply because
-		\[ e(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = e(\hat{\beta}_t). \]
-	Equation \eqref{eq_mono_te} follows because
-	\begin{align*}
-		te(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} &= \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
-		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = te(\hat{\beta}_t).
-	\end{align*}
-\end{proof}
-
-\subsubsection{Model Shift}
-
-In addition to covariate shift, in general the single-task models can also be different across different tasks.
-\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.}
-%We remove the assumption that the models are the same.
-%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
-%\begin{align}
-%	Y_i = X_i \beta_i + \varepsilon_i.
-%\end{align}
-
-\subsection{The Sparse Setting}
+\section{Extensions to the Sparse Setting}
 One important case is the sparse case, where we assume that the $\beta_i$'s are sparse in the sense

### 2020-03-27 writeup/setup.tex
reorg

@@
 
-\subsection{The Sparse Setting}
-One important case is the sparse case, where we assume that the $\beta_i$'s are sparse in the sense 
-that each $\beta_i$ is in a subspace of dimension $k_i\ll p$. In other words,
-$$\beta_i = \sum_{j=1}^{k_i} a^{(i)}_j v^{(i)}_j,$$
-where $\{v^{(i)}_j\}$ is a set of $k_i$ orthonormal vectors. For $X_i= Z_i \Sigma_i^{1/2}$, we have 
-$$ X_i \beta_i = Z_i \Sigma_i^{1/2}\beta_i=  Z_i \Sigma_i^{1/2}P_i\beta_i,\quad P_i:= \sum_{j=1}^{k_i}v_j^{(i)}(v_j^{(i)})^\top.$$
-Then we have 
-$$\frac{1}{n_i}\mathbb E\left[P_i \Sigma_i^{1/2} Z_i^T Z_i \Sigma_i^{1/2}P_i\right]=P_i \Sigma_i P_i.$$
-Hence our analysis will be valid with projected covariance matrices $P_i \Sigma_i P_i$. Moreover, due to the sparsity assumption, it is natural to have restricted isometry property: 
-$$\frac{1}{n_i} P_i \Sigma_i^{1/2} Z_i^T Z_i \Sigma_i^{1/2}P_i \approx P_i \Sigma_i P_i.$$
-Finally, for our analysis it is not necessary to assume that $\beta_T$ is sparse for the target.
+\subsection{The High-Dimensional Setting}
+
+\todo{setup motivation and notations}

### 2020-03-28 writeup/setup.tex
reorg
add intro

@@
+\section{Introduction}
+
+Multi-task learning that is applied on heterogenous data can often result in suboptimal models (or negative transfer in more technical terms).
+In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
+In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works under covariate and model shifts.
+By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
+These are achieved through tight generalization bounds established in the high-dimensional linear regression setting.
+\begin{enumerate}
+	\item {\bf Negative transfer:} we establish a fundamental limit that is caused by model shift.
+	Moreover, this cannot be corrected via changing the model capacity or reweighting the tasks.
+	\item {\bf De-noising effect of MTL:} we show that multi-task transfer has a de-noising effect of reducing the variance of the estimator.
+	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
+	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
+\end{enumerate}
+
 \section{Problem Setup}\label{sec_setup}
@@
 \todo{setup motivation and notations}
+We would like to get insight on how covariate and model shifts affect the rate of transfer.
+For the case of two tasks, we can get precise rates using random matrix theory.
+For the sake of clarity, we call task 1 the source task and task 2 the target task,
+i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.

### 2020-03-31 writeup/setup.tex
edit

@@
 \begin{enumerate}
-	\item {\bf Negative transfer:} we establish a fundamental limit that is caused by model shift.
-	Moreover, this cannot be corrected via changing the model capacity or reweighting the tasks.
 	\item {\bf De-noising effect of MTL:} we show that multi-task transfer has a de-noising effect of reducing the variance of the estimator.
@@
 	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
+	\item {\bf Negative transfer from model shift:} we establish a fundamental limit that is caused by model shift.
+	Moreover, this cannot be corrected via changing the model capacity or reweighting the tasks.
 \end{enumerate}
@@
 \begin{itemize}
-	\item How does covariate shift affect the rate of information transfer? For example, is it better to have the same covariance matrix or not?
-	\item Under model shift, when do we get positive vs. negative transfer? How does the type of transfer depend on the number of data points, the distance of the task models etc?
+	\item How does covariate shift affect the rate of information transfer?
+	For example, is it better to have the same covariance matrix or not?
+	\item Under model shift, when do we get positive vs. negative transfer?
+	How does the type of transfer depend on the number of data points, the distance of the task models etc?
 \end{itemize}
+
+\subsubsection{Model Shift}
+
+In general the single-task models can also be different across different tasks.
+We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
+
+\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
+%We remove the assumption that the models are the same.
+%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
+%\begin{align}
+%	Y_i = X_i \beta_i + \varepsilon_i.
+%\end{align}
 
@@
 
-\subsubsection{Model Shift}
-
-In addition to covariate shift, in general the single-task models can also be different across different tasks.
-\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.}
-%We remove the assumption that the models are the same.
-%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
-%\begin{align}
-%	Y_i = X_i \beta_i + \varepsilon_i.
-%\end{align}
-
 \subsection{The High-Dimensional Setting}
 
-\todo{setup motivation and notations}
+%\todo{setup motivation and notations}
 We would like to get insight on how covariate and model shifts affect the rate of transfer.
-For the case of two tasks, we can get precise rates using random matrix theory.
+We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
+This setting captures a wide range of applications of multi-task learning where we would like to use auxillary task data to help train tasks with limited labeled data.
+
+\paragraph{The case of two tasks.}
+We can get precise rates using random matrix theory.
 For the sake of clarity, we call task 1 the source task and task 2 the target task,
 i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
+We introduce the following notations for the high-dimensional setting
+\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
+for some constants $c_1, c_2 \in (1,\infty)$.
+
+% \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,

### 2020-04-01 writeup/setup.tex
small edit

@@
 
-Multi-task learning that is applied on heterogenous data can often result in suboptimal models (or negative transfer in more technical terms).
+Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
 In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
-In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works under covariate and model shifts.
+In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
+We study a high-dimensional linear regression setting under covariate and model shifts.
 By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
-These are achieved through tight generalization bounds established in the high-dimensional linear regression setting.
+These are achieved through tight generalization bounds established in the high-dimensional regression setting.
 \begin{enumerate}
-	\item {\bf De-noising effect of MTL:} we show that multi-task transfer has a de-noising effect of reducing the variance of the estimator.
+	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
 	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
 	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
-	\item {\bf Negative transfer from model shift:} we establish a fundamental limit that is caused by model shift.
-	Moreover, this cannot be corrected via changing the model capacity or reweighting the tasks.
+	\item {\bf Negative transfer from model shift:} we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
+	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
 \end{enumerate}
@@
 
-\subsubsection{Model Shift}
-
+\paragraph{Model shift.}
 In general the single-task models can also be different across different tasks.
@@
 
-\subsubsection{Covariate Shift}
-
-A natural setting is when the covariance matrices $\Sigma_i$ are different across tasks, i.e. having different spectrum or singular vectors.
+\paragraph{Covariate shift.}
+The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
 This is also known as covariate shift in the literature.

### 2020-04-01 writeup/setup.tex
edits

@@
 These are achieved through tight generalization bounds established in the high-dimensional regression setting.
+
+First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
 \begin{enumerate}
@@
 \end{enumerate}
+
+Secondly for the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediciton labels/tasks for every image \cite{EA20}.
+\todo{We show the following results.}
 

### 2020-04-03 writeup/setup.tex
reorg
sec 2

@@
 
-In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
-We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{A_i \in \real^{r}}_{i=1}^k$ for each task.
-%    \paragraph{Different covariates:}
-This corresponds to minimizing the following optimization objective.
-\begin{align}
-	\label{eq_mtl}
-	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \norm{X_i B A_i - Y_i}^2.
-\end{align}
-Note that we consider the natural parameterization without reweighting the tasks above.
-The shared body $B$ plays an important role because it allows information transfer between different task data.
-There are two ways to ensure the sharing of information between tasks.
-\begin{itemize}
-	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
-	\item Controlling the capacity $r$ of $B$, e.g.
-\cite{KD12,WZR20}.
-Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-\end{itemize}
-
-\paragraph{Data generation.} We shall assume that each task data follows a linear model.
+\paragraph{Data generation.}
+In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
+We shall assume that each task data follows a linear model.
 For every $1\le i\le k$, we assume that
@@
 
-\paragraph{Objectives.}
+\paragraph{Generalization error.}
 We will designate the $k$-th task as the target.
@@
 \end{itemize}
+
+\paragraph{The MTL problem.}
+We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
+%    \paragraph{Different covariates:}
+This corresponds to minimizing the following optimization objective.
+\begin{align}
+	\label{eq_mtl}
+	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
+\end{align}
+Note that we consider the natural parameterization without reweighting the tasks above.
+The shared body $B$ plays an important role because it allows information transfer between different task data.
+There are two ways to ensure the sharing of information between tasks.
+\begin{itemize}
+	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
+	\item Controlling the capacity $r$ of $B$, e.g.
+\cite{KD12,WZR20}.
+Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+\end{itemize}
+
+\paragraph{The case of two tasks.}
+
 %\todo{may also consider test error}
@@
 %\end{align}
+
+\paragraph{Problem statement.}
 

### 2020-04-03 writeup/setup.tex
sec 2

@@
 \paragraph{The case of two tasks.}
+From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
+Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
+Here, equation \eqref{eq_mtl} simplifies to the following
+\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
+where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
+To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
+\begin{align*}
+	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
+	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2),
+\end{align*}
+where we denote $w = w_1 / w_2$.
+As a remark, when $w = 1$, we recover the linear regression estimator.
+The test error of using $w_2 \hat{B}(w)$ for the target task is
+\begin{align*}
+	\te(w_2\hat{B}(w)) = w^2 \bignorm{\Sigma^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}.
+\end{align*}
+Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
+Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
+We will denote $\hat{\beta}_t^{\MTL} = w_2 \hat{B}(\hat{w})$.
 
@@
 
-\subsection{Hypothesis}
+\subsection{Hypothesis on Heterogeneous Task Data}
 
@@
 
-\paragraph{Problem statement.}
-
-Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
-\begin{align}
-	\label{eq_mtl_basic}
-	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
-\end{align}
+\paragraph{Problem statement.} Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
+The baseline where we solve the target task with its own data is
+\begin{align*}
+	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
+\end{align*}
+Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
+Our goal is provide conditions under which there is positive transfer ($\te(\hat{\beta}_t^{\MTL}) \le \hat{\beta}_t^{\STL}$) or negative transfer ($\te(\hat{\beta}_t^{\MTL}) \ge \hat{\beta}_t^{\STL}$).
+As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
+%Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
+%\begin{align}
+%	\label{eq_mtl_basic}
+%	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
+%\end{align}
 %{\bf The distributed learning problem.}
@@
 %   \end{align}
-Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
+%Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
 
@@
 	Suppose that $n > p$.
-  When there is no model shift, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
+  When there is no model shift, i.e. $\beta_s = \beta_t$, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
 	\begin{align}
-		\err(\hat{\beta}_{s,t})  &\le \err(\hat{\beta}_t), \text{ and} \label{eq_mono_e}\\
-		\te(\hat{\beta}_{s,t}) &\le \te(\hat{\beta}_t) \label{eq_mono_te}
+		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
+		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}) \label{eq_mono_te}
 	\end{align}

### 2020-04-03 writeup/setup.tex
finish sec 2

@@
 The test error of using $w_2 \hat{B}(w)$ for the target task is
-\begin{align*}
-	\te(w_2\hat{B}(w)) = w^2 \bignorm{\Sigma^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}.
-\end{align*}
+\begin{align}
+	\te(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
+			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
+\end{align}
+In the above, the first is a bias term introduced by the model shift between the source and target tasks.
+The second is a variance term, which decreases monotonically as we add more and more source task data.
 Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
@@
 	\begin{align}
-		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
-		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}) \label{eq_mono_te}
+%		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
+		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}). \label{eq_mono_te}
 	\end{align}
@@
 \begin{proof}
-	Equation \eqref{eq_mono_e} is simply because
-		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
-	Equation \eqref{eq_mono_te} follows because
+%	Equation \eqref{eq_mono_e} is simply because
+%		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
+%	Equation \eqref{eq_mono_te} follows because
+	Recall that $\hat{\beta}_t^{\MTL} = \hat{w} \cdot \hat{B}$.
+	By the optimality of $\hat{w}$, we have by setting $w = 1$ in equation \eqref{eq_te_mtl}
 	\begin{align*}
-		\te(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} &= \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
+		\te(\hat{\beta}_t^{\MTL}) &\le \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \\
+		&= \sigma^2 \cdot \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
 		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t).
+			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t^{\STL}),
 	\end{align*}
+	which concludes the proof.
 \end{proof}
+
+As a remark, we can derive a similar result for the estimation error as well. The details are omitted.
 
@@
 We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
-This setting captures a wide range of applications of multi-task learning where we would like to use auxillary task data to help train tasks with limited labeled data.
+This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
+Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.
 
@@
 for some constants $c_1, c_2 \in (1,\infty)$.
-
+A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
 % \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,

### 2020-04-03 writeup/setup.tex
sec 3 wip
sec 3.1 wip

@@
 	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
+
+	{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
+	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
 	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
-	\item {\bf Negative transfer from model shift:} we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
-	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
 \end{enumerate}
@@
 	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
-	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2),
+	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
+	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
 \end{align*}
@@
 % \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,
+
+\begin{lemma}\label{lem_minv}
+	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
+	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
+\end{lemma}

### 2020-04-08 writeup/setup.tex
change
proof
multi-task training

@@
 	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
-	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
+	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer. [\textbf{done}]
 
 	{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
-	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
-	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
+	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
+	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs. [\textbf{1/2 done}]
 \end{enumerate}
@@
 Secondly for the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediciton labels/tasks for every image \cite{EA20}.
-\todo{We show the following results.}
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
+\todo{We show the following results.} [\textbf{1/2 done}]
 
@@
 	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
-	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
+	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p}. \]
+	%{\color{blue} \[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p} . \]}
+	%\bigtr{\Sigma_2^{-1}}
 \end{lemma}

### 2020-04-08 writeup/setup.tex
revise intro

@@
 	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
-	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer. [\textbf{done}]
-
-	{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
-	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
-	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs. [\textbf{1/2 done}]
+	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
+	In particular, if model shift is too large, we get negative transfer from multi-task training. [\textbf{done}]
+	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
+	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
+	\item {\bf Covariate shift affects the rate of transfer:} next we show that fine tuning the multi-task model on the target task can correct the negative transfer.
+	We further show that covariate shift controls the rate in which transfer occurs. [\textbf{1/2 done}]
 \end{enumerate}

### 2020-04-08 writeup/setup.tex
intro

@@
 	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
-	\item {\bf Covariate shift affects the rate of transfer:} next we show that fine tuning the multi-task model on the target task can correct the negative transfer.
+	\item {\bf Covariate shift affects the rate of transfer:} next we show that if we optimize the multi-task model on the target task, this can correct the negative transfer.
 	We further show that covariate shift controls the rate in which transfer occurs. [\textbf{1/2 done}]

### 2020-04-09 writeup/setup.tex
multi task loss

@@
 As a remark, when $w = 1$, we recover the linear regression estimator.
-The test error of using $w_2 \hat{B}(w)$ for the target task is
+
+\medskip
+\noindent\textit{Jointly optimizing over both tasks.}
+Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
 \begin{align}
-	\te(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
+		&\val(\hat{B}; w_1, w_2) \nonumber\\
+	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \\
+	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}}
+\end{align}
+
+\todo{(multi-task training)}
+
+\medskip
+\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
+\begin{align}
+	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
 			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
@@
 We will denote $\hat{\beta}_t^{\MTL} = w_2 \hat{B}(\hat{w})$.
-
+\todo{(fine tuning)}
 %\todo{may also consider test error}

### 2020-04-09 writeup/setup.tex
sec 3.1

@@
 		&\val(\hat{B}; w_1, w_2) \nonumber\\
-	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \\
-	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}}
+	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
+	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
 \end{align}
-
-\todo{(multi-task training)}
+Minimizing the above loss is akin to performing multi-task training in practice.
+Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
+We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.
 
@@
 Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
-We will denote $\hat{\beta}_t^{\MTL} = w_2 \hat{B}(\hat{w})$.
-\todo{(fine tuning)}
+We will denote $\hat{\beta}_t^{\TL} = w_2 \hat{B}(\hat{w})$.
+
+There are two reasons for studying this setting.
+First, this is akin to performing transfer learning using the hard parameter sharing architecture.
+Another way to obtain $\hat{\beta}_t^{\TL}$ is that once we minimize the multi-task validation loss, we further minimize the validation loss on the target dataset, which is also known as fine-tuning in practice.
 %\todo{may also consider test error}

### 2020-04-18 writeup/many_tasks_same_covariates.tex
sec 5

\section{The Case with Many Tasks of the Same Covariates}

In this section we consider the setting with $k$ many that have the same covariates.
Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.

Concretely we will consider the following problem.
\begin{align}
	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
\end{align}
By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
\begin{align*}
	\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
	&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
\end{align*}
where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.

\paragraph{Jointly minimizing over all tasks.}
Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
The first part is the model shift bias, which is equal to
\begin{align*}
	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
\end{align*}
The second part is the variance, which is equal to
\begin{align*}
	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}
Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
We can now write the validation loss succinctly as follows.
\begin{align*}
	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{[\beta_1, \dots, \beta_k] Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
\end{align*}
From the above we can solve for $Q$ optimally as \todo{this}.

\paragraph{Minimizing over the target task alone.}
If we only minimize over the the validation loss for the target task, we shall get the following.
\begin{align*}
	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}

### 2020-04-18 writeup/many_tasks_same_covariates.tex
sec 5

@@
 Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
+Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
 We can now write the validation loss succinctly as follows.
 \begin{align*}
-	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{[\beta_1, \dots, \beta_k] Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
+	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
 \end{align*}
@@
 \end{align*}
+
+From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
+\begin{itemize}
+	\item The de-noising effect of multi-task learning.
+	\item Multi-task training vs single-task training can be either positive or negative.
+	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
+\end{itemize}

### 2020-04-23 writeup/setup.tex
wip

@@
 In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
-We study a high-dimensional linear regression setting under covariate and model shifts.
+We study a high-dimensional linear regression setting where the target task data size is limited.
+We formulate the heterogeneity between different task data under covariate and model shifts \cite{PY09,K18}.
 By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
-These are achieved through tight generalization bounds established in the high-dimensional regression setting.
+\todo{list those here}
+These are achieved through tight generalization bounds established in the high-dimensional regression setting using random matrix theory.
 

### 2020-04-23 writeup/setup.tex
setup

--- 2020-04-09 writeup/setup.tex
@@
 These are achieved through tight generalization bounds established in the high-dimensional regression setting.
-
-First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
+Our main results are described as follows.
 \begin{enumerate}
-	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
-	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
-	In particular, if model shift is too large, we get negative transfer from multi-task training. [\textbf{done}]
+	\item {\bf De-noising effect of information transfer.}
+	We provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
+	We show that multi-task learning helps improve performance over target tasks by \textit{reducing variance} through newly added source task data.
+	On the other hand, the difference between task models causes a negative effect that we call the \textit{model shift bias}.
+	We show upper and lower bounds on both the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
 	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
 	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
-	\item {\bf Covariate shift affects the rate of transfer:} next we show that if we optimize the multi-task model on the target task, this can correct the negative transfer.
-	We further show that covariate shift controls the rate in which transfer occurs. [\textbf{1/2 done}]
+	\item {\bf Effects of covariate shift, model distance, and data ratio.}
+	We apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
+	\begin{enumerate}
+		\item {\bf Multi-task training over single-task training.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
+	In particular, if model shift is too large, we get negative transfer from multi-task training.
+		\item {\bf Transfer learning over single-task training.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
+		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
+		\item {\bf Transfer learning over multi-task training.} Finally, we show that the transfer learning estimator always improves over mutli-task training.
+		The amount of improvement becomes more significant as the model distance becomes larger.
 	\end{enumerate}
-
-Secondly for the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
+	\item {\bf Extending to many tasks with the same covariates.} For the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
-\todo{We show the following results.} [\textbf{1/2 done}]
+	Since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
+	We show that our results and insights from the above can be extended to this setting as well.
+\end{enumerate}
 

### 2020-04-23 writeup/setup.tex
sec 2

@@
 Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
-Concretely, we focus on two objectives.
-\begin{itemize}
-	\item Estimation error for the target model $\beta_t$: we consider their distance
-		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
-	\item Test error for the target task:
+Concretely, we focus on the test error for the target task:
+%\begin{itemize}
+%	\item Estimation error for the target model $\beta_t$: we consider their distance
+%		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
 		\begin{align*}
-			\te(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
+			\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
 			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
 		\end{align*}
-\end{itemize}
+%\end{itemize}
 
@@
 
-\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
+%\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
 %We remove the assumption that the models are the same.
@@
 This is also known as covariate shift in the literature.
-\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
-A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
+%\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
+%A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
 %\begin{align}
@@
 
-\begin{lemma}\label{lem_minv}
+\begin{lemma}\label{lem_minv}[\todo{ref?}]
 	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,

### 2020-04-27 writeup/intro.tex
edits

--- 2020-04-23 writeup/setup.tex
@@
 In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
-We study a high-dimensional linear regression setting under covariate and model shifts.
+We study a high-dimensional linear regression setting where the target task data size is limited.
+We formulate the heterogeneity between different task data under covariate and model shifts \cite{PY09,K18}.
 By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
+\todo{list those here}
 These are achieved through tight generalization bounds established in the high-dimensional regression setting.
 Our main results are described as follows.
-\begin{enumerate}
-	\item {\bf De-noising effect of information transfer.}
-	We provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
+
+\smallskip
+\noindent{\bf Tight generalization bounds via random matrix theory.}
+	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
 	We show that multi-task learning helps improve performance over target tasks by \textit{reducing variance} through newly added source task data.
@@
 	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
-	\item {\bf Effects of covariate shift, model distance, and data ratio.}
-	We apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
+
+\smallskip
+\noindent{\bf Variance reduction from information transfer.}
+	Second, we apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
 	\begin{enumerate}
-		\item {\bf Multi-task training over single-task training.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
+		\item {\bf Model distance.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
 	In particular, if model shift is too large, we get negative transfer from multi-task training.
-		\item {\bf Transfer learning over single-task training.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
+
+	Finally, we show that the transfer learning estimator always improves over mutli-task training.
+		The amount of improvement becomes more significant as the model distance becomes larger.
+		\item {\bf Covariate shift.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
 		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
-		\item {\bf Transfer learning over multi-task training.} Finally, we show that the transfer learning estimator always improves over mutli-task training.
-		The amount of improvement becomes more significant as the model distance becomes larger.
+		\item {\bf Data ratio.}
 	\end{enumerate}
-	\item {\bf Extending to many tasks with the same covariates.} For the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
+
+	For the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
@@
 	We show that our results and insights from the above can be extended to this setting as well.
-\end{enumerate}
 
-\section{Problem Setup}\label{sec_setup}
-
-\paragraph{Data generation.}
-In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
-We shall assume that each task data follows a linear model.
-For every $1\le i\le k$, we assume that
-\[ Y_i = X_i \beta_i + \varepsilon_i, \]
-where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
-We assume that for every row $x$ of $X_i$, we have
-\[ \ex{xx^{\top}} = \Sigma_i. \]
-We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
-
-\paragraph{Generalization error.}
-We will designate the $k$-th task as the target.
-Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
-Concretely, we focus on two objectives.
-\begin{itemize}
-	\item Estimation error for the target model $\beta_t$: we consider their distance
-		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
-	\item Test error for the target task:
-		\begin{align*}
-			\te(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
-			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
-		\end{align*}
-\end{itemize}
-
-\paragraph{The MTL problem.}
-We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
-%    \paragraph{Different covariates:}
-This corresponds to minimizing the following optimization objective.
-\begin{align}
-	\label{eq_mtl}
-	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
-\end{align}
-Note that we consider the natural parameterization without reweighting the tasks above.
-The shared body $B$ plays an important role because it allows information transfer between different task data.
-There are two ways to ensure the sharing of information between tasks.
-\begin{itemize}
-	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
-	\item Controlling the capacity $r$ of $B$, e.g.
-\cite{KD12,WZR20}.
-Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-\end{itemize}
-
-\paragraph{The case of two tasks.}
-From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
-Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
-Here, equation \eqref{eq_mtl} simplifies to the following
-\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
-To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
-\begin{align*}
-	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
-	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
-\end{align*}
-where we denote $w = w_1 / w_2$.
-As a remark, when $w = 1$, we recover the linear regression estimator.
-
-\medskip
-\noindent\textit{Jointly optimizing over both tasks.}
-Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-\begin{align}
-		&\val(\hat{B}; w_1, w_2) \nonumber\\
-	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
-	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
-\end{align}
-Minimizing the above loss is akin to performing multi-task training in practice.
-Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
-We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.
-
-\medskip
-\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
-\begin{align}
-	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
-			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
-\end{align}
-In the above, the first is a bias term introduced by the model shift between the source and target tasks.
-The second is a variance term, which decreases monotonically as we add more and more source task data.
-Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
-Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
-We will denote $\hat{\beta}_t^{\TL} = w_2 \hat{B}(\hat{w})$.
-
-There are two reasons for studying this setting.
-First, this is akin to performing transfer learning using the hard parameter sharing architecture.
-Another way to obtain $\hat{\beta}_t^{\TL}$ is that once we minimize the multi-task validation loss, we further minimize the validation loss on the target dataset, which is also known as fine-tuning in practice.
-%\todo{may also consider test error}
-%Several relevant directions on this setting.
-%\begin{itemize}
-%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
-%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
-%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
-%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
-%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
-%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
-%\end{itemize}
-
-\subsection{Hypothesis on Heterogeneous Task Data}
-
-Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
-%\todo{Add some references to add spice on these takes.}
-We consider two natural questions within each category.
-\begin{itemize}
-	\item How does covariate shift affect the rate of information transfer?
-	For example, is it better to have the same covariance matrix or not?
-	\item Under model shift, when do we get positive vs. negative transfer?
-	How does the type of transfer depend on the number of data points, the distance of the task models etc?
-\end{itemize}
-
-\paragraph{Model shift.}
-In general the single-task models can also be different across different tasks.
-We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
-
-\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
-%We remove the assumption that the models are the same.
-%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
-%\begin{align}
-%	Y_i = X_i \beta_i + \varepsilon_i.
-%\end{align}
-
-\paragraph{Covariate shift.}
-The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
-This is also known as covariate shift in the literature.
-\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
-A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
-%\begin{align}
-%	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim
-%\Sigma_i
-%\end{align}
-
-\paragraph{Problem statement.} Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
-The baseline where we solve the target task with its own data is
-\begin{align*}
-	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
-\end{align*}
-Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
-Our goal is provide conditions under which there is positive transfer ($\te(\hat{\beta}_t^{\MTL}) \le \hat{\beta}_t^{\STL}$) or negative transfer ($\te(\hat{\beta}_t^{\MTL}) \ge \hat{\beta}_t^{\STL}$).
-As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
-%Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
-%\begin{align}
-%	\label{eq_mtl_basic}
-%	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
-%\end{align}
-%{\bf The distributed learning problem.}
-%    \begin{align}
-%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
-%   \end{align}
-%Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
-
-\begin{proposition}\label{prop_monotone}
-	Suppose that $n > p$.
-  When there is no model shift, i.e. $\beta_s = \beta_t$, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
-	\begin{align}
-%		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
-		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}). \label{eq_mono_te}
-	\end{align}
-\end{proposition}
-
-\begin{proof}
-%	Equation \eqref{eq_mono_e} is simply because
-%		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
-%	Equation \eqref{eq_mono_te} follows because
-	Recall that $\hat{\beta}_t^{\MTL} = \hat{w} \cdot \hat{B}$.
-	By the optimality of $\hat{w}$, we have by setting $w = 1$ in equation \eqref{eq_te_mtl}
-	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &\le \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \\
-		&= \sigma^2 \cdot \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
-		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t^{\STL}),
-	\end{align*}
-	which concludes the proof.
-\end{proof}
-
-As a remark, we can derive a similar result for the estimation error as well. The details are omitted.
-
-\subsection{The High-Dimensional Setting}
-
-%\todo{setup motivation and notations}
-We would like to get insight on how covariate and model shifts affect the rate of transfer.
-We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
-This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
-Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.
-
-\paragraph{The case of two tasks.}
-We can get precise rates using random matrix theory.
-For the sake of clarity, we call task 1 the source task and task 2 the target task,
-i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
-We introduce the following notations for the high-dimensional setting
-\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
-for some constants $c_1, c_2 \in (1,\infty)$.
-A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
-% \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,
-
-\begin{lemma}\label{lem_minv}
-	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
-	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p}. \]
-	%{\color{blue} \[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p} . \]}
-	%\bigtr{\Sigma_2^{-1}}
-\end{lemma}
+\smallskip
+\noindent\textbf{Experimental results.}

### 2020-04-27 writeup/proof_sketch.tex
edits

\section{Proof Overview of Theorem \ref{thm_model_shift}}

\noindent\todo{A proof outline; including the following key lemma.}
To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
\begin{equation}\label{eq_12moment} %\label{assm1}
\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
\end{equation}
%For now, we assume that the random variables $x_{ij}$ are i.i.d. Gaussian, but we know that universality holds for generally distributed entries. %have arbitrarily high moments,
%in the sense that for any fixed $k\in \mathbb N$, there is a constant $\mu_k>0$ such that
%\begin{equation}\label{eq_highmoment} %\label{eqn:subgaus}
%\max_{i,j}\left(\mathbb E|x_{ij}|^k\right)^{1/k} \le \mu_k n^{-1/2},  %\var \left(h_{xy}\right)^{1/2}
%\end{equation}
%for all $n$. %For simplicity, we assume that $k$ is a finite fixed integer, the strengths $d_1 > d_2 > \cdots > d_k >0$ are fixed constants, and $ \bu_i$,  $\bv_i$ are deterministic unit vectors.

\begin{lemma}\label{lem_cov_shift}
	In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
\begin{align}\label{lem_cov_shift_eq}
\tr ((w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2) = \frac{1}{n_1+n_2}\cdot \tr \left( \frac{1}{a_1 M^\top M + a_2} \right) +\bigo{ n^{-1/2+\epsilon}},
\end{align}
	for any constant $\epsilon>0$. %, where $a_{3,4}$ are found using equations in  \eqref{m35reduced}.
	Moreover, when $n_1 = 0$, we have %we have that $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, hence
	\begin{align}\label{lem_cov_shift_eq2} \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2-p} + \bigo{n^{-1/2+\epsilon}}, \end{align}
which is a well-known result for inverse Whishart matrices {\color{red}add some references}.
\end{lemma}
We will give the proof of this lemma in Section \ref{sec_maintools}.

\begin{lemma}\label{lem_minv}[\todo{ref?}]
	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p}. \]
	%{\color{blue} \[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p} . \]}
	%\bigtr{\Sigma_2^{-1}}
\end{lemma}

\paragraph{A tighter bound for a special case.} We can get a bound tighter than Theorem \ref{thm_model_shift} as follows.

	\begin{proposition}\label{prop_model_shift_tight}
		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
		and we have
		\begin{align*}
			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
		\end{align*}
	\end{proposition}

### 2020-04-27 writeup/setup.tex
edits

@@
-\section{Introduction}
-
-Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
-In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
-In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
-We study a high-dimensional linear regression setting under covariate and model shifts.
-By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
-These are achieved through tight generalization bounds established in the high-dimensional regression setting.
-Our main results are described as follows.
-\begin{enumerate}
-	\item {\bf De-noising effect of information transfer.}
-	We provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
-	We show that multi-task learning helps improve performance over target tasks by \textit{reducing variance} through newly added source task data.
-	On the other hand, the difference between task models causes a negative effect that we call the \textit{model shift bias}.
-	We show upper and lower bounds on both the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
-	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
-	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
-	\item {\bf Effects of covariate shift, model distance, and data ratio.}
-	We apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
-	\begin{enumerate}
-		\item {\bf Multi-task training over single-task training.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
-	In particular, if model shift is too large, we get negative transfer from multi-task training.
-		\item {\bf Transfer learning over single-task training.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
-		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
-		\item {\bf Transfer learning over multi-task training.} Finally, we show that the transfer learning estimator always improves over mutli-task training.
-		The amount of improvement becomes more significant as the model distance becomes larger.
-	\end{enumerate}
-	\item {\bf Extending to many tasks with the same covariates.} For the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
-	Since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
-	We show that our results and insights from the above can be extended to this setting as well.
-\end{enumerate}
-
-\section{Problem Setup}\label{sec_setup}
+\subsection{Setup and Main Results}\label{sec_setup}
 
@@
 
-\subsection{Hypothesis on Heterogeneous Task Data}
+Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
+The baseline where we solve the target task with its own data is
+\begin{align*}
+	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
+\end{align*}
+Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
+
+\begin{algorithm}[!t]
+	\caption{Comparing the generalization error of MTL, TL and STL estimators}
+	\begin{algorithmic}[1]
+		\Input $(X_1, Y_2)$, $(X_2, Y_2)$.
+		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
+		\State Training the shared body $B$.
+		\State Optimizing the task heads on the validation set
+
+		\begin{itemize}
+			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
+			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
+			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
+		\end{itemize}
+		\State Problem statement: Provide conditions to compare the test error of three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
+	\end{algorithmic}
+\end{algorithm}
+
+We state our main result for two tasks with both covariate and model shift in the following theorem.
+
+\begin{theorem}\label{thm_model_shift}
+	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
+	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
+	Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+	Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
+	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
+	With high probability we have
+	\begin{align}
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
+	\end{align}
+	where $\delta = \norm{Z} \cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2$ with $Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top}$, and
+	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
+		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t),
+	\end{align*}
+%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
+%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
+%	Otherwise, the two bounds has to be written into the form
+%	\begin{align*}
+%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
+%	\end{align*}
+%	and
+%	\begin{align*}
+%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
+%	\end{align*}
+%	}
+%
+%
+	and $a_1, a_2, a_3, a_4$ are the solutions of the following linear equations
+	\begin{gather}
+		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}, \label{eq_a2} \\
+		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
+		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
+		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
+		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
+	\end{gather}
+\end{theorem}
+
+%	We have the following conditions that guarantee the type of transfer we can get under model shift.
+%	\begin{itemize}
+
+%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
+%			\begin{align}
+%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
+%			\end{align}
+%	\end{itemize}
+%	\begin{align}
+%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
+%\label{eq_model_shift_pos}
+%	\end{align}
+%	where
+%{\cob
+%We have that
+%	\begin{align*}
+%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
+%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
+%		\end{align*}
+%		and
+%	\begin{align*}
+%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
+%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
+%	\end{align*}
+%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
+%\begin{align*}
+%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
+%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
+%		\end{align*}
+%	}
+
+Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
+The bounds get tighter and tighter as $n_1 / p$ increases.
+%\paragraph{Negative transfer: the Limit caused by model shifts.}
+%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
+%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
+%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
+%\te(\hat{\beta}_t)$ when
+%	\begin{align*}
+%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
+%	\end{align*}
+%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
+%\begin{align}
+%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
+%\end{align}
+%
+%\end{theorem}
+
+%From Lemma \ref{lem_cov_shift}, we know that
+%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
+%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
+%Hence the variance part is reduced by the following amount
+%\begin{align}
+%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
+%\end{align}
+%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
+%We are now interested in the following quantity
+
+\section{Preliminaries and Related Work}
+
+\paragraph{Hypothesis on Heterogeneous Task Data}
 
@@
 \begin{itemize}
-	\item How does covariate shift affect the rate of information transfer?
-	For example, is it better to have the same covariance matrix or not?
-	\item Under model shift, when do we get positive vs. negative transfer?
-	How does the type of transfer depend on the number of data points, the distance of the task models etc?
-\end{itemize}
-
-\paragraph{Model shift.}
+	\item \textbf{Model shift.}
 	In general the single-task models can also be different across different tasks.
 We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
+
+	Under model shift, when do we get positive vs. negative transfer?
+	How does the type of transfer depend on the number of data points, the distance of the task models etc?
+	\item \textbf{Covariate shift.}
+	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
+This is also known as covariate shift in the literature.
+	How does covariate shift affect the rate of information transfer?
+	For example, is it better to have the same covariance matrix or not?
+\end{itemize}
 
@@
 %\end{align}
-
-\paragraph{Covariate shift.}
-The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
-This is also known as covariate shift in the literature.
 %\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
@@
 
-\paragraph{Problem statement.} Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
-The baseline where we solve the target task with its own data is
-\begin{align*}
-	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
-\end{align*}
-Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
-Our goal is provide conditions under which there is positive transfer ($\te(\hat{\beta}_t^{\MTL}) \le \hat{\beta}_t^{\STL}$) or negative transfer ($\te(\hat{\beta}_t^{\MTL}) \ge \hat{\beta}_t^{\STL}$).
-As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
-%Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
-%\begin{align}
-%	\label{eq_mtl_basic}
-%	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
-%\end{align}
-%{\bf The distributed learning problem.}
-%    \begin{align}
-%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
-%   \end{align}
-%Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
-
-\begin{proposition}\label{prop_monotone}
-	Suppose that $n > p$.
-  When there is no model shift, i.e. $\beta_s = \beta_t$, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
-	\begin{align}
-%		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
-		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}). \label{eq_mono_te}
-	\end{align}
-\end{proposition}
-
-\begin{proof}
-%	Equation \eqref{eq_mono_e} is simply because
-%		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
-%	Equation \eqref{eq_mono_te} follows because
-	Recall that $\hat{\beta}_t^{\MTL} = \hat{w} \cdot \hat{B}$.
-	By the optimality of $\hat{w}$, we have by setting $w = 1$ in equation \eqref{eq_te_mtl}
-	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &\le \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \\
-		&= \sigma^2 \cdot \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
-		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t^{\STL}),
-	\end{align*}
-	which concludes the proof.
-\end{proof}
-
-As a remark, we can derive a similar result for the estimation error as well. The details are omitted.
-
-\subsection{The High-Dimensional Setting}
-
+\paragraph{The High-Dimensional Setting.}
 %\todo{setup motivation and notations}
@@
 
-\paragraph{The case of two tasks.}
-We can get precise rates using random matrix theory.
+For the case of two tasks, we can get precise rates using random matrix theory.
 For the sake of clarity, we call task 1 the source task and task 2 the target task,
@@
 % \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,
-
-\begin{lemma}\label{lem_minv}[\todo{ref?}]
-	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
-	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p}. \]
-	%{\color{blue} \[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p} . \]}
-	%\bigtr{\Sigma_2^{-1}}
-\end{lemma}

### 2020-04-27 writeup/setup.tex
reorg

@@
 
-\begin{algorithm}[!t]
-	\caption{Comparing the generalization error of MTL, TL and STL estimators}
-	\begin{algorithmic}[1]
-		\Input $(X_1, Y_2)$, $(X_2, Y_2)$.
-		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
-		\State Training the shared body $B$.
-		\State Optimizing the task heads on the validation set
-
-		\begin{itemize}
-			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
-			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
-			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
-		\end{itemize}
-		\State Problem statement: Provide conditions to compare the test error of three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
-	\end{algorithmic}
-\end{algorithm}
-
-We state our main result for two tasks with both covariate and model shift in the following theorem.
-
-\begin{theorem}\label{thm_model_shift}
-	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
-	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
-	Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-	Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
-	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
-	With high probability we have
-	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
-	\end{align}
-	where $\delta = \norm{Z} \cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2$ with $Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top}$, and
-	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
-		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t),
-	\end{align*}
-%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
-%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
-%	Otherwise, the two bounds has to be written into the form
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
-%	\end{align*}
-%	and
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
-%	\end{align*}
-%	}
-%
-%
-	and $a_1, a_2, a_3, a_4$ are the solutions of the following linear equations
-	\begin{gather}
-		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}, \label{eq_a2} \\
-		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
-		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
-		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
-		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
-	\end{gather}
-\end{theorem}
-
-%	We have the following conditions that guarantee the type of transfer we can get under model shift.
-%	\begin{itemize}
-
-%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
-%			\begin{align}
-%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%			\end{align}
-%	\end{itemize}
-%	\begin{align}
-%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
-%\label{eq_model_shift_pos}
-%	\end{align}
-%	where
-%{\cob
-%We have that
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
-%		\end{align*}
-%		and
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
-%	\end{align*}
-%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
-%\begin{align*}
-%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
-%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
-%		\end{align*}
-%	}
-
-Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
-The bounds get tighter and tighter as $n_1 / p$ increases.
-%\paragraph{Negative transfer: the Limit caused by model shifts.}
-%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
-%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
-%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
-%\te(\hat{\beta}_t)$ when
-%	\begin{align*}
-%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%	\end{align*}
-%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
-%\begin{align}
-%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
-%\end{align}
-%
-%\end{theorem}
-
-%From Lemma \ref{lem_cov_shift}, we know that
-%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
-%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
-%Hence the variance part is reduced by the following amount
-%\begin{align}
-%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
-%\end{align}
-%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
-%We are now interested in the following quantity
-
-\section{Preliminaries and Related Work}
+\section{Preliminaries}
 

### 2020-04-29 writeup/intro.tex
reorg

@@
 		The amount of improvement becomes more significant as the model distance becomes larger.
-		\item {\bf Covariate shift.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
+		\item {\bf Covariate shift and data ratio.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
 		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
-		\item {\bf Data ratio.}
 	\end{enumerate}
@@
 \noindent\textbf{Experimental results.}
+
+\subsection{Setup and Main Results}\label{sec_setup}
+
+\paragraph{Data generation.}
+In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
+We shall assume that each task data follows a linear model.
+For every $1\le i\le k$, we assume that
+\[ Y_i = X_i \beta_i + \varepsilon_i, \]
+where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
+Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
+We assume that for every row $x$ of $X_i$, we have
+\[ \ex{xx^{\top}} = \Sigma_i. \]
+We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
+
+\paragraph{The MTL problem.}
+We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
+%    \paragraph{Different covariates:}
+This corresponds to minimizing the following optimization objective.
+\begin{align}
+	\label{eq_mtl}
+	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
+\end{align}
+Note that we consider the natural parameterization without reweighting the tasks above.
+The shared body $B$ plays an important role because it allows information transfer between different task data.
+There are two ways to ensure the sharing of information between tasks.
+\begin{itemize}
+	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
+	\item Controlling the capacity $r$ of $B$, e.g.
+\cite{KD12,WZR20}.
+Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+\end{itemize}

### 2020-04-29 writeup/setup.tex
reorg

@@
-\subsection{Setup and Main Results}\label{sec_setup}
-
-\paragraph{Data generation.}
-In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
-We shall assume that each task data follows a linear model.
-For every $1\le i\le k$, we assume that
-\[ Y_i = X_i \beta_i + \varepsilon_i, \]
-where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
-We assume that for every row $x$ of $X_i$, we have
-\[ \ex{xx^{\top}} = \Sigma_i. \]
-We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
+\section{Preliminaries}
 
@@
 
-\paragraph{The MTL problem.}
-We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
-%    \paragraph{Different covariates:}
-This corresponds to minimizing the following optimization objective.
-\begin{align}
-	\label{eq_mtl}
-	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
-\end{align}
-Note that we consider the natural parameterization without reweighting the tasks above.
-The shared body $B$ plays an important role because it allows information transfer between different task data.
-There are two ways to ensure the sharing of information between tasks.
+\paragraph{Hypothesis on Heterogeneous Task Data}
+
+Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
+%\todo{Add some references to add spice on these takes.}
+We consider two natural questions within each category.
 \begin{itemize}
-	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
-	\item Controlling the capacity $r$ of $B$, e.g.
-\cite{KD12,WZR20}.
-Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+	\item \textbf{Model shift.}
+	In general the single-task models can also be different across different tasks.
+We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
+
+	Under model shift, when do we get positive vs. negative transfer?
+	How does the type of transfer depend on the number of data points, the distance of the task models etc?
+	\item \textbf{Covariate shift.}
+	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
+This is also known as covariate shift in the literature.
+	How does covariate shift affect the rate of information transfer?
+	For example, is it better to have the same covariance matrix or not?
 \end{itemize}
+
+%\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
+%We remove the assumption that the models are the same.
+%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
+%\begin{align}
+%	Y_i = X_i \beta_i + \varepsilon_i.
+%\end{align}
+%\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
+%A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
+%\begin{align}
+%	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim
+%\Sigma_i
+%\end{align}
+
+\paragraph{The High-Dimensional Setting.}
+%\todo{setup motivation and notations}
+We would like to get insight on how covariate and model shifts affect the rate of transfer.
+We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
+This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
+Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.
+
+For the case of two tasks, we can get precise rates using random matrix theory.
+For the sake of clarity, we call task 1 the source task and task 2 the target task,
+i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
+We introduce the following notations for the high-dimensional setting
+\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
+for some constants $c_1, c_2 \in (1,\infty)$.
+A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
+% \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,
 
@@
 Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
-
-\section{Preliminaries}
-
-\paragraph{Hypothesis on Heterogeneous Task Data}
-
-Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
-%\todo{Add some references to add spice on these takes.}
-We consider two natural questions within each category.
-\begin{itemize}
-	\item \textbf{Model shift.}
-	In general the single-task models can also be different across different tasks.
-We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
-
-	Under model shift, when do we get positive vs. negative transfer?
-	How does the type of transfer depend on the number of data points, the distance of the task models etc?
-	\item \textbf{Covariate shift.}
-	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
-This is also known as covariate shift in the literature.
-	How does covariate shift affect the rate of information transfer?
-	For example, is it better to have the same covariance matrix or not?
-\end{itemize}
-
-%\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
-%We remove the assumption that the models are the same.
-%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
-%\begin{align}
-%	Y_i = X_i \beta_i + \varepsilon_i.
-%\end{align}
-%\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
-%A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
-%\begin{align}
-%	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim
-%\Sigma_i
-%\end{align}
-
-\paragraph{The High-Dimensional Setting.}
-%\todo{setup motivation and notations}
-We would like to get insight on how covariate and model shifts affect the rate of transfer.
-We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
-This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
-Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.
-
-For the case of two tasks, we can get precise rates using random matrix theory.
-For the sake of clarity, we call task 1 the source task and task 2 the target task,
-i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
-We introduce the following notations for the high-dimensional setting
-\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
-for some constants $c_1, c_2 \in (1,\infty)$.
-A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
-% \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,

### 2020-04-29 writeup/transfer.tex
reorg

\section{Variance Reduction from Information Transfer}\label{sec_denoise}

In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
We achieve this through tight generalization bounds obtained from random matrix theory.
For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.

Recall that the test error of $\hat{\beta}_{t}^{\MTL}$ consists of two parts
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) = \hat{w}^2 \bignorm{\Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{w}\beta_t)}^2 + \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}. \label{eq_te_model_shift}
\end{align}
It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$ (following the argument of Proposition \ref{prop_monotone}), i.e.
\[ \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \sigma^2\cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
Because of model shift however, i.e. $\beta_s \neq \beta_t$.
We can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
The main result of this part show deterministic conditions under which we get positive or negative transfer.
And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
In order to characterize $\te(\hat{\beta}_t^{\MTL})$ and $\te(\hat{\beta}_t^{\STL})$, the technical crux of our approach relies on deriving the limit of the trace of matrix inverse in the high-dimensional setting.
To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
\todo{write a brief technical overview}

%In this case, $\beta_s$ and $\beta_t$ are different.
%, or implicitly add a regularization on $B$.
%\todo{We focus on the former case in this section.}
%, we consider the case when $r=1$ since there are only two tasks.
%We begin by considering the simplified equation \eqref{eq_mtl_basic} to solve for the target task.
%This is equivalent to setting $W_i = 1$ for the two tasks in equation \eqref{eq_mtl}.
%The result of this simplified setting will set up the ground for solving equation \eqref{eq_mtl} when we also optimize $W_1$ and $W_2$.
%By putting the two tasks together, we get
%\begin{align*}
%	\hat{\beta}_{s,t} &= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
%	&= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \bigbrace{(X_1^{\top}X_1\beta_s + X_2^{\top}X_2\beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)} \\
%	&= \beta_t + (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\beta_s - \beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}
%\end{align*}
%Hence
%\begin{align}
%	\err(\hat{\beta}_{s,t})
%	&= \bignorm{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2
%	+ \sigma^2 \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ and} \\
%	\te(\hat{\beta}_{s,t})
%	&= \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2 + \sigma^2\cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_te_model_shift}
%\end{align}

\begin{algorithm}[!t]
	\caption{Comparing the test error of MTL, TL and STL estimators}
	\begin{algorithmic}[1]
		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
		\State Training the shared body $B$.
		\State Optimizing the task heads on the validation set

		\begin{itemize}
			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
		\end{itemize}
		\State Problem statement: Provide conditions to compare the test error of the three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
	\end{algorithmic}
\end{algorithm}

We state our main result for two tasks with both covariate and model shift in the following theorem.

\begin{theorem}\label{thm_model_shift}
	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
	Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
	Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
	With high probability we have
	\begin{align}
	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
	\end{align}
	where $\delta = \norm{Z} \cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2$ with $Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top}$, and
	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t),
	\end{align*}
%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
%	Otherwise, the two bounds has to be written into the form
%	\begin{align*}
%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
%	\end{align*}
%	and
%	\begin{align*}
%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
%	\end{align*}
%	}
%
%
	and $a_1, a_2, a_3, a_4$ are the solutions of the following linear equations
	\begin{gather}
		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}, \label{eq_a2} \\
		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
	\end{gather}
\end{theorem}

%	We have the following conditions that guarantee the type of transfer we can get under model shift.
%	\begin{itemize}

%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
%			\begin{align}
%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
%			\end{align}
%	\end{itemize}
%	\begin{align}
%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
%\label{eq_model_shift_pos}
%	\end{align}
%	where
%{\cob
%We have that
%	\begin{align*}
%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
%		\end{align*}
%		and
%	\begin{align*}
%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
%	\end{align*}
%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
%\begin{align*}
%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
%		\end{align*}
%	}

Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
The bounds get tighter and tighter as $n_1 / p$ increases.
%\paragraph{Negative transfer: the Limit caused by model shifts.}
%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
%\te(\hat{\beta}_t)$ when
%	\begin{align*}
%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
%	\end{align*}
%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
%\begin{align}
%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
%\end{align}
%
%\end{theorem}

%From Lemma \ref{lem_cov_shift}, we know that
%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
%Hence the variance part is reduced by the following amount
%\begin{align}
%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
%\end{align}
%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
%We are now interested in the following quantity

%\todo{For technical reasons, we will consider the test error.}
%\section{Effects of Model Distance, Covariate Shift, and Data Ratio on Information Transfer}\label{sec_insight}
\subsection{Effect of Model Distance on Positive versus Negative Transfer}

As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
%Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
%\begin{align}
%	\label{eq_mtl_basic}
%	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
%\end{align}
%{\bf The distributed learning problem.}
%    \begin{align}
%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
%   \end{align}
%Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

\begin{proposition}\label{prop_monotone}
	Suppose that $n > p$.
  When there is no model shift, i.e. $\beta_s = \beta_t$, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
	\begin{align}
%		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}). \label{eq_mono_te}
	\end{align}
\end{proposition}

\begin{proof}
%	Equation \eqref{eq_mono_e} is simply because
%		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
%	Equation \eqref{eq_mono_te} follows because
	Recall that $\hat{\beta}_t^{\MTL} = \hat{w} \cdot \hat{B}$.
	By the optimality of $\hat{w}$, we have by setting $w = 1$ in equation \eqref{eq_te_mtl}
	\begin{align*}
		\te(\hat{\beta}_t^{\MTL}) &\le \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \\
		&= \sigma^2 \cdot \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t^{\STL}),
	\end{align*}
	which concludes the proof.
\end{proof}

As a remark, we can derive a similar result for the estimation error as well. The details are omitted.

We describe examples based on Theorem \ref{thm_model_shift} to show several conceptual insights.

\begin{example}[\textbf{Varying the distance of task models}]
	We consider a simple setting where $\Sigma_1 = \id$.
	Suppose that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$. Hence the task models have distance $d^2\cdot p$ in expectation.

	We first consider $\Sigma_2 = \id$. In this case, we can simplify $\Delta_{\beta}$ as follows
	\begin{align} \label{eq_delta_simple}
		\Delta_{\beta} \define d^2 \cdot \sum_{i=1}^p \frac{(1 + a_3)\lambda_i^2 + a_4 \lambda_i^4}{(a_1 \lambda_i^2 + a_2)^2}.
	\end{align}
	Now we solve the equations \eqref{eq_a2}, \eqref{eq_a3}, \eqref{eq_a4} to get
	\begin{align}
		a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
		a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)},
		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)}.
	\end{align}
%{\color{blue}if $\Sigma_1=\Sigma_2=\id$, then
%	\begin{align}
%		a_1 = c_1 \left( 1- \gamma_n\right) , \quad
%		a_2 = c_2 \left( 1- \gamma_n\right), \quad
%		a_3 = \frac{\gamma_n c_2}{1-\gamma_n}, \quad
%		a_4 =  \frac{\gamma_n c_1}{1-\gamma_n}.
%	\end{align}
%	where $\gamma_n=p/n$, $c_1=n_1/n$, and $c_2=n_2/n$.
%}

	Then we obtain
	\begin{align}
		\Delta_{\beta} = p \cdot d^2 \cdot \frac{c_1^2 (c_1 + c_2)}{(c_1 + c_2 - 1)^3},
		\Delta_{\vari} = \sigma^2 \cdot \frac{c_1}{(c_2 - 1)(c_1 + c_2 - 1)}.
	\end{align}

	We demonstrate our result with a simulation.
	We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
	\todo{Fill in other params.}
	We fix the target task and vary the source task, by varying the task model distance parameter $d$.
	We show that Theorem \ref{thm_model_shift} predicts whether we can get positive or negative transfer.
	Figure \ref{fig_model_shift_phasetrans} shows the result.
	We obtain the following insight from the simulation.
	\begin{itemize}
		\item Adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
		\item Model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
		Hence, the type of transfer is determined by the tradeoff between the bias caused by model shift and the reduction of variance.
	\end{itemize}
\end{example}

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/model_shift_phase_transition.eps}
	\caption{Positive vs negative transfer as a parameter of the task model distances.}
	\label{fig_model_shift_phasetrans}
\end{figure}

\subsection{Extension to Many Tasks of the Same Covariates}

In this section we consider the setting with $k$ many that have the same covariates.
Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.

Concretely we will consider the following problem.
\begin{align}
	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
\end{align}
By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
\begin{align*}
	\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
	&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
\end{align*}
where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.

\paragraph{Jointly minimizing over all tasks.}
Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
The first part is the model shift bias, which is equal to
\begin{align*}
	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
\end{align*}
The second part is the variance, which is equal to
\begin{align*}
	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}
Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
We can now write the validation loss succinctly as follows.
\begin{align*}
	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
\end{align*}
From the above we can solve for $Q$ optimally as \todo{this}.

\paragraph{Minimizing over the target task alone.}
If we only minimize over the the validation loss for the target task, we shall get the following.
\begin{align*}
	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}

From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
\begin{itemize}
	\item The de-noising effect of multi-task learning.
	\item Multi-task training vs single-task training can be either positive or negative.
	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
\end{itemize}

\section{Effect of Covariate Shift and Data Ratio on Transfer Rate}

%\subsubsection{Gains over Single-Task Training}

\paragraph{A precise bound when there is no model shift.}
As Proposition \ref{prop_monotone} shows, if $\beta_s$ and $\beta_t$ are equal, then adding the source task dataset always helps learn the target task.
The goal of this section is to understand how covariate shift affects the rate of transfer. \todo{add conceptual msg}

%The key quantity is to look at:
%The estimator using the source and target together from minimizing \eqref{eq_mtl_basic} is
%\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
%The estimation error of $\hat{\beta}_{s,t}$ is
%\begin{align}\label{eq_two_task}
%  \err(\hat{\beta}_{s,t}) = \sigma^2 \cdot \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}].
%\end{align}
%The estimation error using the target alone is
%\begin{align}\label{eq_target_task}
%	\err(\hat{\beta}_t) = \sigma^2 \cdot \tr[(X_2^{\top} X_2)^{-1}].
%\end{align}
%The improvement of estimation error from adding the source task is then given by
%$\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})$.
%For the test error on the target task, the improvement from adding the source task is
%\[ \te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t}) = \sigma^2\cdot\bigtr{\bigbrace{(X_2^{\top}X_2)^{-1} - (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}\cdot\Sigma_2}. \]

%We calculate the amount of improvement by comparing equation \eqref{eq_two_task} to equation \eqref{eq_target_task}.
A simple observation here is that when $\beta_s = \beta_t$, the optimal $\hat{w}$ for minimizing equation \eqref{eq_te_mtl} is equal to $1$.
Based on this observation, we can get a more precise result than Theorem \ref{thm_model_shift} on the improvement of adding the source task data that only depends on the covariance matrices $\Sigma_1, \Sigma_2$ and the number of data points $n_1, n_2$.

\begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
	When $\beta_s = \beta_t$, we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}.
	And
	\begin{align*}
		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}} + \bigo{\frac 1 {(n_1 + n_2)^2}},
	\end{align*}
	where $a_1, a_2$ are the solutions of equations \eqref{eq_a2}.
\end{proposition}

{\color{blue}
\begin{proposition}[Transfer rate without model shift] 
	Suppose $\beta_s = \beta_t$ with i.i.d. entries of mean zero and variance $d^2$. Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
	$$1\le \hat{w} \le w_0:=1 + \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^2 \|\Sigma_1\|_{\min}},$$ 
	where $\|\Sigma_1\|_{\min}$ is the smallest singular value of $\Sigma_1$. Note that $w_0$ is very close to $1$ up to a small error of order $n_1^{-1}$.
\end{proposition}
\begin{proof}
We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$. Under the assumption on $\beta_s$ and $\beta_t$, we can write
\begin{align}
	\val(w) =&~ d^2 \left( 1-\frac1w\right)^2 \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}\left(Z_1 \Sigma_1 Z_1^{\top}\right) Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right] \nonumber \\
			&~ + \sigma^2 \cdot \bigtr{(w^2 M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} \Sigma_2}.  \nonumber
\end{align}
Taking derivative with respect to $w$, we obtain that 
\begin{align*}
\val'(w) \ge &~ 2\frac{d^2}{w^2} \left( 1-\frac1w\right) \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}\left(Z_1 \Sigma_1 Z_1^{\top}\right) Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]   \\
			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(w^2 M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (w^2 M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1}\Sigma_2} \\
			=& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
\end{align*}
We can write $\id = P+ P_{\perp}$, where $P$ denotes the projection onto the subspace spanned by the columns of $Z_1$ and $P_{\perp}$ denotes the projection onto its orthogonal complement. Together with $P\preceq (\sqrt{n_1}-\sqrt{p})^{-2} Z_1 Z_1^\top$, we get
\begin{align*}
M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M  &\succeq M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} Z_1 Z_1^\top \right] Z_1 M  \\
&= M^\top Z_1^{\top}Z_1  \left[\left( w-1\right) \Sigma_1  - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} \right] Z_1^\top Z_1 M .
\end{align*}
Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$. 
\end{proof}
}

As a remark, we see that Proposition \ref{prop_monotone} follows from Theorem \ref{thm_cov_shift}.
The amount of reduction on test error for the target task is given as
	\begin{align*}
%		\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})
%		&= \sigma^2 p \cdot \bigtr{\frac 1 {(n_2 - p) \Sigma_2} - \frac 1 {(n_1 + n_2)a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2}}, \\
		\te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t})
		&= \sigma^2 \cdot \bigbrace{\frac p {n_2 - p} -  \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}}}.
	\end{align*}
Because
\begin{align*}
	\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)
	\Leftarrow~ & (n_2 - p)\Sigma_2 \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2 \\
	\Leftrightarrow~ & \zeroMatrix \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 - (n_1 + n_2)\cdot a_1) \Sigma_2,
\end{align*}
which is true since $a_1 \le n_1 / (n_1 + n_2)$ by equation \eqref{eq_a2}.
The proof for $\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)$ follows by multiplying $\Sigma_2^{-1/2}$ on both sides of the inequalities above.

\medskip
Now we apply Theorem \ref{thm_cov_shift} to show how covariate shift affects the rate of transfer.

%\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2$}]
%In this case, we have $\lambda_i = 1$ for all $1\le i\le p$.
%And $a_1 + a_2 = 1 - p / (n_1 + n_2)$.
%Hence
%\[ \te(\hat{\beta}_{s,t}) = \frac{\sigma^2 p^2}{n_1 + n_2 - p} \text{ and } \err(\hat{\beta}_{s,t}) = \frac {\sigma^2 p} {n_1 + n_2 - p} \bigtr{\Sigma_2^{-1}}. \]
%\end{example}

\smallskip
\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2 / \lambda$}]
In this case, equations \eqref{eq_a2} become
\[ a_1 + a_2 = 1 - p/(n_1 + n_2), a_1 + \frac{p}{n_1 + n_2} \cdot \frac {a_1} {a_1 + \lambda^2 a_2} = \frac{n_1} {n_1 + n_2}. \]
By solving these, we can get the test errors (the estimation error behaves similarly).
Figure \ref{fig_te_scaling} shows how they grow as we increase the number of source task data points.
Here $n_2 = 4p$ and $n_1$ ranges from $p$ to $20p$.
We can see that the smaller $\lambda$ is, the lower the test errors will be.
\end{example}

\smallskip
\begin{example}[\textbf{When $\Sigma_1$ and $\Sigma_2$ are complementary}]
	We consider two cases when $\Sigma_1$ and $\Sigma_2$ are \textit{different}
\begin{itemize}
	\item {\bf Different singular values:} Here we have that for $\Sigma_1^{-1/2}\Sigma_2^{1/2}$, the first $p/2$ singular values of $\Sigma_1$ is $\lambda$ and the rest is $1/\lambda$.
For this case, equations \eqref{eq_a2} become
\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}, a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}. \ee
It's not hard to verify that there is only one valid solution from the above.
After solving these, we get the test error for the target task as follows.
\be\label{testcomple} 
te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
	\item {\bf Different singular spaces {\color{blue}(actually they have the same singular spaces)}:}
	Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
$$\Sigma_1^{1/2} = 1+ U\Lambda U^\top, \quad \Sigma_2^{1/2} = 1+ V\Lambda V,$$
where
$$\Lambda = \diag(\wt\lambda_1,\cdots, \wt\lambda_{p/2}), \quad U= (u_1,\cdots, u_{p/2}), \quad V= (v_1,\cdots, v_{p/2}).$$
We consider two case: if $V=U$, then $M=\id;$ if $V=U_\perp$ (i.e. the space spanned by $V$ is perpendicular to that spanned by $U$), then
$$M=\Sigma_1^{1/2} \Sigma_2^{-1/2}=(1+\Lambda)UU^\top + (1+\Lambda)^{-1}V V^\top .$$
This is an extension of the above example of complementary case.
\end{itemize}
\end{example}

{\color{blue} Note that the curves in Figure 3 all cross at the point $n_1=n_2$. This can be understood in the following way. 
First, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$. Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
On the other hand, we write
$$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
We can compute that
\begin{align*}
te(\lambda) - te(1)&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)^2 a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
\end{align*}
If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}), and hence $te(\lambda)>te(1)$. Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$. 
}

{\color{blue}
Suppose we fix a scale of the covariate shift. That is given an $a>0$, we consider all possible covariate shift matrices $M^\top M$ such that 
\be\label{GMcons}\det(M^\top M)= a\Leftrightarrow \prod_{i=1}^p \lambda_i = a.\ee
We claim as long as we have sufficiently many datas (i.e. as long as $n_1$ is sufficiently large), then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error. In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$. Then we have 
$$te\approx \frac{\sigma^2}{n_1+n_2-p} \sum_{i=1}^p \frac{1}{\lambda_i}.$$
By AM-GM inequality, under the constraint \eqref{GMcons} the sum is smallest when $\lambda_1=\lambda_2=\cdots=\lambda_p = a^{1/p}$. 
}

In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
We observe the following two phases as we increase $n_1 / p$.
\begin{itemize}
	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
\end{itemize}

\begin{figure}
	\centering
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/scaling.eps}
		\caption{When $\Sigma_1 = \Sigma_2 / \lambda$.}
		\label{fig_te_scaling}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/complementary.eps}
		\caption{When $\Sigma_1$ and $\Sigma_2$ are complementary. The number of target task data points is $n_2 = 4p$.}
		\label{fig_te_complement}
	\end{minipage}
\end{figure}

\paragraph{Extending the intuition to the general case.}
When there is model shift, i.e. $\beta_s = \beta_t$, we can still use Theorem \ref{thm_model_shift} (and Proposition \ref{prop_model_shift_tight}) to get the result.
\begin{itemize}
	\item \textbf{The effect of covariate shift:}
	\item \textbf{The effect of data ratio:}
\end{itemize}

### 2020-04-29 writeup/intro.tex
reorg intro

@@
 
-Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
-In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
-In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
+The idea of transferring information across tasks has recently found applications in lots of work in deep learning.
+In our own experience as well as discussions with collaborators, we have often heard that multi-task learning that is applied on heterogeneous data often result in suboptimal models (or negative transfer in more technical terms).
+
+To gain insight into the working of these methods, we consider a principled study of how hard parameter sharing based multi-task and transfer learning works for learning multiple high-dimensional linear regression tasks.
+We follow the model proposed in \cite{WZR20} that to identify conditions on when multi-task and transfer learning works, and when it doesn't.
+We refine the task covariance part of \cite{WZR20} into three factors: model distance, covariate shift matrix and data ratio \cite{PY09,K18}.
 We study a high-dimensional linear regression setting where the target task data size is limited.
-We formulate the heterogeneity between different task data under covariate and model shifts \cite{PY09,K18}.
+We formulate the heterogeneity between different task data under covariate and model shifts .
 By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
@@
 \smallskip
-\noindent{\bf Tight generalization bounds via random matrix theory.}
+\noindent{\bf Variance reduction from information transfer.}
 	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
@@
 	We show upper and lower bounds on both the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
+
+	{\it Insight 1: MTL vs STL.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
+	In particular, if model shift is too large, we get negative transfer from multi-task training.
+
+	{\it Insight 2: TL vs MTL.} Finally, we show that the transfer learning estimator always improves over mutli-task training.
+		The amount of improvement becomes more significant as the model distance becomes larger.
+
+	We show the result for two settings: 2 tasks with different covariates, and $k$ tasks that all share the same covariates.
+	The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
+	We show that our results and insights from the above can be extended to this setting as well.
+
 	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
@@
 
+%\noindent{\bf Variance reduction from information transfer.}
+%	Second, we apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
+%	\begin{enumerate}
+
 \smallskip
-\noindent{\bf Variance reduction from information transfer.}
-	Second, we apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
-	\begin{enumerate}
-		\item {\bf Model distance.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
-	In particular, if model shift is too large, we get negative transfer from multi-task training.
+	\noindent\textbf{Covariate shift and data ratio.}
+	Since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
+	Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
+	We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
 
-	Finally, we show that the transfer learning estimator always improves over mutli-task training.
-		The amount of improvement becomes more significant as the model distance becomes larger.
-		\item {\bf Covariate shift and data ratio.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
-		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
-	\end{enumerate}
-
-	For the general setting with $k$ tasks, we study the case when all tasks share the same covariates.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
-	Since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
-	We show that our results and insights from the above can be extended to this setting as well.
+	\textit{Insight 3: TL vs STL.} When data ratio is small, having complementary covariance matrices is better. When data ratio is large, having the same covariance matrix is better.
 

### 2020-04-29 writeup/intro.tex
reorg intro setup

@@
 We study a high-dimensional linear regression setting where the target task data size is limited.
-We formulate the heterogeneity between different task data under covariate and model shifts .
+
+\smallskip
+\noindent\textbf{Setup.} We are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
+We shall assume that each task data follows a linear model.
+For every $1\le i\le k$, we assume that
+\[ Y_i = X_i \beta_i + \varepsilon_i, \]
+where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
+Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
+We assume that for every row $x$ of $X_i$, we have
+\[ \ex{xx^{\top}} = \Sigma_i. \]
+We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
+
+We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
+%    \paragraph{Different covariates:}
+This corresponds to minimizing the following optimization objective.
+\begin{align}
+	\label{eq_mtl}
+	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
+\end{align}
+Note that we consider the natural parameterization without reweighting the tasks above.
+The shared body $B$ plays an important role because it allows information transfer between different task data.
+This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
+Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+
+%We formulate the heterogeneity between different task data under covariate and model shifts .
 By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
@@
 	\noindent\textbf{Experimental results.}
-
-\subsection{Setup and Main Results}\label{sec_setup}
-
-\paragraph{Data generation.}
-In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
-We shall assume that each task data follows a linear model.
-For every $1\le i\le k$, we assume that
-\[ Y_i = X_i \beta_i + \varepsilon_i, \]
-where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
-We assume that for every row $x$ of $X_i$, we have
-\[ \ex{xx^{\top}} = \Sigma_i. \]
-We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
-
-\paragraph{The MTL problem.}
-We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
-%    \paragraph{Different covariates:}
-This corresponds to minimizing the following optimization objective.
-\begin{align}
-	\label{eq_mtl}
-	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
-\end{align}
-Note that we consider the natural parameterization without reweighting the tasks above.
-The shared body $B$ plays an important role because it allows information transfer between different task data.
-There are two ways to ensure the sharing of information between tasks.
-\begin{itemize}
-	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
-	\item Controlling the capacity $r$ of $B$, e.g.
-\cite{KD12,WZR20}.
-Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-\end{itemize}

### 2020-04-29 writeup/related.tex
reorg intro setup

\section{Related Work}

 Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.

### 2020-05-04 writeup/transfer.tex
revise mistakes

@@
 
-We state our main result for two tasks with both covariate and model shift in the following theorem.
+Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+Denote by ${\lambda}_1\ge {\lambda}_2 \ge \dots \ge {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
+Let $(a_1, a_2)$ be the solutions to the following system of equations
+	\be
+		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}.\label{eq_a2} \\
+		 \ee
+		 After obtaining $(a_1,a_2)$, we can solve the following linear equations to get $(a_3,a_4)$:
+\begin{gather}
+		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
+		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
+		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
+		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
+	\end{gather}
+Then we introduce the following matrix
+$$Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top},$$
+which can be regarded as the asymptotic limit of $\hat w \Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}$. Finally we introduce 
+$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
+{\cor may be able to get a better bound, but the statement will be long}
+
+We now state our main result for two tasks with both covariate and model shift in the following theorem.
 
@@
 	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
-	Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-	Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
+	%Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+	%Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
 	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
@@
 	\end{align}
-	where $\delta = \norm{Z} \cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2$ with $Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top}$, and
+	where 
 	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
 		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
-		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t),
+		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t).
 	\end{align*}
@@
 %	} 
-%
-%
-	and $a_1, a_2, a_3, a_4$ are the solutions of the following linear equations
-	\begin{gather}
-		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}, \label{eq_a2} \\
-		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
-		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
-		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
-		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
-	\end{gather}
 \end{theorem}
@@
 
-	We demonstrate our result with a simulation.
+	We demonstrate our result with a simulation. (\todo {uses the tighter bound Proposition \ref{prop_model_shift_tight}?})
 	We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
@@
 \begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
-	When $\beta_s = \beta_t$, we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}.
+	When $\beta_s = \beta_t$, we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
+	$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
+	where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$. 
 	And
@@
 		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
-		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}} + \bigo{\frac 1 {(n_1 + n_2)^2}},
+		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}} + \bigo{|w_0-1|},
 	\end{align*}
-	where $a_1, a_2$ are the solutions of equations \eqref{eq_a2}.
+where $a_1, a_2$ are the solutions of equations \eqref{eq_a2}. \cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
 \end{proposition}
 
-{\color{blue}
-\begin{proposition}[Transfer rate without model shift] 
-	Suppose $\beta_s = \beta_t$ with i.i.d. entries of mean zero and variance $d^2$. Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
-	$$1\le \hat{w} \le w_0:=1 + \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^2 \|\Sigma_1\|_{\min}},$$ 
-	where $\|\Sigma_1\|_{\min}$ is the smallest singular value of $\Sigma_1$. Note that $w_0$ is very close to $1$ up to a small error of order $n_1^{-1}$.
-\end{proposition}
+% \begin{proposition}[Transfer rate without model shift] 
+%	Suppose $\beta_s = \beta_t$ with i.i.d. entries of mean zero and variance $d^2$. Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
+%	$$1\le \hat{w} \le w_0:=1 + \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$ 
+%	where $\|\Sigma_1\|_{\min}$ is the smallest singular value of $\Sigma_1$. Note that $w_0$ is very close to $1$ up to a small error of order $n_1^{-1}$.
+%\end{proposition}
 \begin{proof}
-We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$. Under the assumption on $\beta_s$ and $\beta_t$, we can write
+We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
+We first notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
+Thus we have $\hat w\ge 1$.
+It suffices to consider the case with $w> 1$.
+Under the assumption on $\beta_s$ and $\beta_t$, we can write
 \begin{align}
-	\val(w) =&~ d^2 \left( 1-\frac1w\right)^2 \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}\left(Z_1 \Sigma_1 Z_1^{\top}\right) Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right] \nonumber \\
-			&~ + \sigma^2 \cdot \bigtr{(w^2 M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} \Sigma_2}.  \nonumber
+	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
+			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
 \end{align}
-Taking derivative with respect to $w$, we obtain that 
+Since 
+$$\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 = \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]$$
+is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
 \begin{align*}
-\val'(w) \ge &~ 2\frac{d^2}{w^2} \left( 1-\frac1w\right) \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}\left(Z_1 \Sigma_1 Z_1^{\top}\right) Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]   \\
-			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(w^2 M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (w^2 M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1}\Sigma_2} \\
-			=& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
+\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
+			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
+\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}.
+			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
 \end{align*}
-We can write $\id = P+ P_{\perp}$, where $P$ denotes the projection onto the subspace spanned by the columns of $Z_1$ and $P_{\perp}$ denotes the projection onto its orthogonal complement.
+%We can write $\id = P+ P_{\perp}$, where $P$ denotes the projection onto the subspace spanned by the columns of $Z_1$ and $P_{\perp}$ denotes the projection onto its orthogonal complement.
 Together with $P\preceq (\sqrt{n_1}-\sqrt{p})^{-2} Z_1 Z_1^\top$, we get
-\begin{align*}
-M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M  &\succeq M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} Z_1 Z_1^\top \right] Z_1 M  \\
-&= M^\top Z_1^{\top}Z_1  \left[\left( w-1\right) \Sigma_1  - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} \right] Z_1^\top Z_1 M .
-\end{align*}
+%\begin{align*}
+%M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M  &\succeq M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} Z_1 Z_1^\top \right] Z_1 M  \\
+%&= M^\top Z_1^{\top}Z_1  \left[\left( w-1\right) \Sigma_1  - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} \right] Z_1^\top Z_1 M .
+%\end{align*}
 Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$. 
 \end{proof}
-}
 

### 2020-05-06 writeup/intro.tex
edits

@@
 
-The idea of transferring information across tasks has recently found applications in lots of work in deep learning.
-In our own experience as well as discussions with collaborators, we have often heard that multi-task learning that is applied on heterogeneous data often result in suboptimal models (or negative transfer in more technical terms).
+Methods that can transfer the information from one task to help other tasks have recently found many applications in computer vision, natural language processing and reinforcement learning.
+In our own experience as well as discussions with collaborators, we have often observed that multi-task learning that is applied on heterogeneous data often result in suboptimal models (or negative transfer in more technical terms).
 
-To gain insight into the working of these methods, we consider a principled study of how hard parameter sharing based multi-task and transfer learning works for learning multiple high-dimensional linear regression tasks.
-We follow the model proposed in \cite{WZR20} that to identify conditions on when multi-task and transfer learning works, and when it doesn't.
-We refine the task covariance part of \cite{WZR20} into three factors: model distance, covariate shift matrix and data ratio \cite{PY09,K18}.
-We study a high-dimensional linear regression setting where the target task data size is limited.
+To gain insight into the working of multi-task learning, we consider a simplified setting for learning multiple high-dimensional linear regression tasks.
+A typical process to do multi-task learning involves two steps:
+(i) Jointly learn a shared representation for all the tasks;
+(ii) Fine-tune the learnt model on a specific target task.
+We focus on a hard parameter sharing model proposed in \cite{WZR20} and identify conditions on when multi-task and transfer learning works, and when it doesn't.
+The high-dimensional linear regression setting where the target task data size is limited captures the intuition that the target task only contains limited labeled data.
 
-\smallskip
-\noindent\textbf{Setup.} We are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
-We shall assume that each task data follows a linear model.
-For every $1\le i\le k$, we assume that
-\[ Y_i = X_i \beta_i + \varepsilon_i, \]
-where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
+Concretely, our input consists of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
+We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
+Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
 Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
-We assume that for every row $x$ of $X_i$, we have
-\[ \ex{xx^{\top}} = \Sigma_i. \]
-We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
-
-We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
+We use a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
 %    \paragraph{Different covariates:}
@@
 This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
-Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+
+We focus on comparing the test performance on a target task using estimators from doing multi-task training and transfer learning.
+We compare the test performance of these estimators to the single-task baseline.
+The details are described in Algorithm \ref{alg_estimator}.
 
@@
 \todo{list those here}
+We refine the task covariance part of \cite{WZR20} into three factors: model distance, covariate shift matrix and data ratio \cite{PY09,K18}.
 These are achieved through tight generalization bounds established in the high-dimensional regression setting.
@@
 
+\begin{algorithm}[!t]
+	\caption{Multi-task learning using a hard-parameter sharing architecture}
+	\label{alg_estimator}
+	\begin{algorithmic}[1]
+		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
+		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
+		\State Training the shared body $B$.
+		\State Optimizing the task heads on the validation set
+
+		\begin{itemize}
+			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
+			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
+			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
+		\end{itemize}
+		\State Problem statement: how can we compare the test error of the three estimators on the target task?
+		%, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$?
+	\end{algorithmic}
+\end{algorithm}
+
 \smallskip
 \noindent{\bf Variance reduction from information transfer.}
-	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
-	We show that multi-task learning helps improve performance over target tasks by \textit{reducing variance} through newly added source task data.
+	We show that the benefit from doing multi-task or transfer learning stems from reducing the variance of the estimator for the target task through newly added source task data.
+	We derive this result for the setting of two tasks with general inputs and $k$ tasks with the same covariates for any $k \ge 2$.
+	The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
+%	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
 	On the other hand, the difference between task models causes a negative effect that we call the \textit{model shift bias}.
-	We show upper and lower bounds on both the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
+	We show bounds on the trade-off between the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
 
-	{\it Insight 1: MTL vs STL.} With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
+	{\it Insight 1}: $\hat{\beta}_t^{\MTL}$ vs $\hat{\beta}_t^{\STL}$.
+	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
 	In particular, if model shift is too large, we get negative transfer from multi-task training.
 
-	{\it Insight 2: TL vs MTL.} Finally, we show that the transfer learning estimator always improves over mutli-task training.
+	{\it Insight 2}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\MTL}$.
+	Finally, we show that the transfer learning estimator always improves over mutli-task training.
 	The amount of improvement becomes more significant as the model distance becomes larger.
 
-	We show the result for two settings: 2 tasks with different covariates, and $k$ tasks that all share the same covariates.
-	The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
-	We show that our results and insights from the above can be extended to this setting as well.
-
+%	We show the result for two settings: 2 tasks with different covariates, and $k$ tasks that all share the same covariates.
+%	We show that our results and insights from the above can be extended to this setting as well.
 	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
@@
 	\noindent\textbf{Covariate shift and data ratio.}
-	Since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
-	Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
-	We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
+	For the case of two tasks with general inputs, we further study the factors that determine the transfer rate.
+	We identify two factors, the covariate shift matrix and the ratio between number of task data.
+%	Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
+%	We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
 
-	\textit{Insight 3: TL vs STL.} When data ratio is small, having complementary covariance matrices is better. When data ratio is large, having the same covariance matrix is better.
+	\textit{Insight 3}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\STL}$.
+	Our result has implications on the following question.
+	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices.
+	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.
+	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
+	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
 

### 2020-05-06 writeup/proof_sketch.tex
edits

@@
 \section{Proof Overview of Theorem \ref{thm_model_shift}}
+
+\todo{these calculation goes to appendix}
+\paragraph{The case of two tasks.}
+From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
+Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
+Here, equation \eqref{eq_mtl} simplifies to the following
+\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
+where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
+To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
+\begin{align*}
+	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
+	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
+	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
+\end{align*}
+where we denote $w = w_1 / w_2$.
+As a remark, when $w = 1$, we recover the linear regression estimator.
+
+\medskip
+\noindent\textit{Jointly optimizing over both tasks.}
+Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+\begin{align}
+		&\val(\hat{B}; w_1, w_2) \nonumber\\
+	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
+	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
+\end{align}
+Minimizing the above loss is akin to performing multi-task training in practice.
+Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
+We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.
+
+\medskip
+\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
+\begin{align}
+	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
+			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
+\end{align}
+In the above, the first is a bias term introduced by the model shift between the source and target tasks.
+The second is a variance term, which decreases monotonically as we add more and more source task data.
+Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
+Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
+We will denote $\hat{\beta}_t^{\TL} = w_2 \hat{B}(\hat{w})$.
+
+There are two reasons for studying this setting.
+First, this is akin to performing transfer learning using the hard parameter sharing architecture.
+Another way to obtain $\hat{\beta}_t^{\TL}$ is that once we minimize the multi-task validation loss, we further minimize the validation loss on the target dataset, which is also known as fine-tuning in practice.
+%\todo{may also consider test error}
+%Several relevant directions on this setting.
+%\begin{itemize}
+%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
+%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
+%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
+%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
+%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
+%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
+%\end{itemize}
+
+Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
+The baseline where we solve the target task with its own data is
+\begin{align*}
+	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
+\end{align*}
+Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
+
+\todo{connect here}
 

### 2020-05-06 writeup/setup.tex
reorg intro setup
edits

@@
-\section{Preliminaries}
+\subsection{Setup and Main Results}\label{sec_setup}
 
-\paragraph{Generalization error.}
+We assume that for every row $x$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
+We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
 We will designate the $k$-th task as the target.
@@
 %\end{itemize}
+
+\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}
 
@@
 
-%\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
-%We remove the assumption that the models are the same.
-%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
-%\begin{align}
-%	Y_i = X_i \beta_i + \varepsilon_i.
-%\end{align}
-%\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}
-%A special case of this setting is that the single-task models are the same across all the tasks, i.e. $\beta_i = \beta$, for all $1\le i\le k$.
-%\begin{align}
-%	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim
-%\Sigma_i
-%\end{align}
-
 \paragraph{The High-Dimensional Setting.}
@@
 % \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,
-
-\paragraph{The case of two tasks.}
-From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
-Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
-Here, equation \eqref{eq_mtl} simplifies to the following
-\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
-To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
-\begin{align*}
-	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
-	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
-\end{align*}
-where we denote $w = w_1 / w_2$.
-As a remark, when $w = 1$, we recover the linear regression estimator.
-
-\medskip
-\noindent\textit{Jointly optimizing over both tasks.}
-Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-\begin{align}
-		&\val(\hat{B}; w_1, w_2) \nonumber\\
-	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
-	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
-\end{align}
-Minimizing the above loss is akin to performing multi-task training in practice.
-Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
-We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.
-
-\medskip
-\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
-\begin{align}
-	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
-			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
-\end{align}
-In the above, the first is a bias term introduced by the model shift between the source and target tasks.
-The second is a variance term, which decreases monotonically as we add more and more source task data.
-Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
-Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
-We will denote $\hat{\beta}_t^{\TL} = w_2 \hat{B}(\hat{w})$.
-
-There are two reasons for studying this setting.
-First, this is akin to performing transfer learning using the hard parameter sharing architecture.
-Another way to obtain $\hat{\beta}_t^{\TL}$ is that once we minimize the multi-task validation loss, we further minimize the validation loss on the target dataset, which is also known as fine-tuning in practice.
-%\todo{may also consider test error}
-%Several relevant directions on this setting.
-%\begin{itemize}
-%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
-%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
-%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
-%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
-%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
-%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
-%\end{itemize}
-
-Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
-The baseline where we solve the target task with its own data is
-\begin{align*}
-	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
-\end{align*}
-Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.

### 2020-05-06 writeup/transfer.tex
edits

--- 2020-04-29 writeup/transfer.tex
@@
-\section{Variance Reduction from Information Transfer}\label{sec_denoise}
+\section{Illustrative Examples}
 
-In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
-We achieve this through tight generalization bounds obtained from random matrix theory.
-For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
-
-Recall that the test error of $\hat{\beta}_{t}^{\MTL}$ consists of two parts
-\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) = \hat{w}^2 \bignorm{\Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{w}\beta_t)}^2 + \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}.
-\label{eq_te_model_shift}
-\end{align}
-It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$ (following the argument of Proposition \ref{prop_monotone}), i.e.
-\[ \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \sigma^2\cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
-Because of model shift however, i.e. $\beta_s \neq \beta_t$.
-We can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
-The main result of this part show deterministic conditions under which we get positive or negative transfer.
-And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
-In order to characterize $\te(\hat{\beta}_t^{\MTL})$ and $\te(\hat{\beta}_t^{\STL})$, the technical crux of our approach relies on deriving the limit of the trace of matrix inverse in the high-dimensional setting.
-To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
-\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
-We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
-\todo{write a brief technical overview}
-
-%In this case, $\beta_s$ and $\beta_t$ are different.
-%, or implicitly add a regularization on $B$.
-%\todo{We focus on the former case in this section.}
-%, we consider the case when $r=1$ since there are only two tasks.
-%We begin by considering the simplified equation \eqref{eq_mtl_basic} to solve for the target task.
-%This is equivalent to setting $W_i = 1$ for the two tasks in equation \eqref{eq_mtl}.
-%The result of this simplified setting will set up the ground for solving equation \eqref{eq_mtl} when we also optimize $W_1$ and $W_2$.
-%By putting the two tasks together, we get
-%\begin{align*}
-%	\hat{\beta}_{s,t} &= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-%	&= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \bigbrace{(X_1^{\top}X_1\beta_s + X_2^{\top}X_2\beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)} \\
-%	&= \beta_t + (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\beta_s - \beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}
-%\end{align*}
-%Hence
-%\begin{align}
-%	\err(\hat{\beta}_{s,t})
-%	&= \bignorm{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2
-%	+ \sigma^2 \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ and} \\
-%	\te(\hat{\beta}_{s,t})
-%	&= \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2 + \sigma^2\cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_te_model_shift}
-%\end{align}
-
-\begin{algorithm}[!t]
-	\caption{Comparing the test error of MTL, TL and STL estimators}
-	\begin{algorithmic}[1]
-		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
-		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
-		\State Training the shared body $B$.
-		\State Optimizing the task heads on the validation set
-
-		\begin{itemize}
-			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
-			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
-			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
-		\end{itemize}
-		\State Problem statement: Provide conditions to compare the test error of the three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
-	\end{algorithmic}
-\end{algorithm}
-
-We state our main result for two tasks with both covariate and model shift in the following theorem.
-
-\begin{theorem}\label{thm_model_shift}
-	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
-	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
-	Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-	Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
-	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
-	With high probability we have
-	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
-	\end{align}
-	where $\delta = \norm{Z} \cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2$ with $Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top}$, and
-	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
-		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t),
-	\end{align*}
-%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
-%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
-%	Otherwise, the two bounds has to be written into the form
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
-%	\end{align*}
-%	and
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
-%	\end{align*}
-%	}
-%
-%
-	and $a_1, a_2, a_3, a_4$ are the solutions of the following linear equations
-	\begin{gather}
-		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}, \label{eq_a2} \\
-		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
-		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
-		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
-		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
-	\end{gather}
-\end{theorem}
-
-%	We have the following conditions that guarantee the type of transfer we can get under model shift.
-%	\begin{itemize}
-
-%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
-%			\begin{align}
-%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%			\end{align}
-%	\end{itemize}
-%	\begin{align}
-%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
-%\label{eq_model_shift_pos}
-%	\end{align}
-%	where
-%{\cob
-%We have that
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
-%		\end{align*}
-%		and
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
-%	\end{align*}
-%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
-%\begin{align*}
-%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
-%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
-%		\end{align*}
-%	}
-
-Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
-The bounds get tighter and tighter as $n_1 / p$ increases.
-%\paragraph{Negative transfer: the Limit caused by model shifts.}
-%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
-%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
-%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
-%\te(\hat{\beta}_t)$ when
-%	\begin{align*}
-%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%	\end{align*}
-%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
-%\begin{align}
-%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
-%\end{align}
-%
-%\end{theorem}
-
-%From Lemma \ref{lem_cov_shift}, we know that
-%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
-%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
-%Hence the variance part is reduced by the following amount
-%\begin{align}
-%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
-%\end{align}
-%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
-%We are now interested in the following quantity
-
-%\todo{For technical reasons, we will consider the test error.}
-%\section{Effects of Model Distance, Covariate Shift, and Data Ratio on Information Transfer}\label{sec_insight}
 \subsection{Effect of Model Distance on Positive versus Negative Transfer}
@@
 
-\subsection{Extension to Many Tasks of the Same Covariates}
-
-In this section we consider the setting with $k$ many that have the same covariates.
-Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-
-Concretely we will consider the following problem.
-\begin{align}
-	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
-\end{align}
-By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
-\begin{align*}
-	\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
-	&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
-\end{align*}
-where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
-%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.
-
-\paragraph{Jointly minimizing over all tasks.}
-Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
-We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
-The first part is the model shift bias, which is equal to
-\begin{align*}
-	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
-\end{align*}
-The second part is the variance, which is equal to
-\begin{align*}
-	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
-	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-\end{align*}
-Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
-Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
-Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-We can now write the validation loss succinctly as follows.
-\begin{align*}
-	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
-\end{align*}
-From the above we can solve for $Q$ optimally as \todo{this}.
-
-\paragraph{Minimizing over the target task alone.}
-If we only minimize over the the validation loss for the target task, we shall get the following.
-\begin{align*}
-	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
-	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-\end{align*}
-
-From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
-\begin{itemize}
-	\item The de-noising effect of multi-task learning.
-	\item Multi-task training vs single-task training can be either positive or negative.
-	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
-\end{itemize}
-
-\section{Effect of Covariate Shift and Data Ratio on Transfer Rate}
+\subsection{Effect of Covariate Shift and Data Ratio on Transfer Rate}
 
 %\subsubsection{Gains over Single-Task Training}
+
+Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
 
@@
 \end{itemize}
+
+\section{Main Results: Reducing Variance under Model Shift Biases}\label{sec_denoise}
+
+In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
+We achieve this through tight generalization bounds obtained from random matrix theory.
+For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
+
+Recall that the test error of $\hat{\beta}_{t}^{\MTL}$ consists of two parts
+\begin{align}
+	\te(\hat{\beta}_t^{\MTL}) = \hat{w}^2 \bignorm{\Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{w}\beta_t)}^2 + \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}.
+\label{eq_te_model_shift}
+\end{align}
+It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$ (following the argument of Proposition \ref{prop_monotone}), i.e.
+\[ \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \sigma^2\cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
+Because of model shift however, i.e. $\beta_s \neq \beta_t$.
+We can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
+The main result of this part show deterministic conditions under which we get positive or negative transfer.
+And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
+In order to characterize $\te(\hat{\beta}_t^{\MTL})$ and $\te(\hat{\beta}_t^{\STL})$, the technical crux of our approach relies on deriving the limit of the trace of matrix inverse in the high-dimensional setting.
+To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
+\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
+We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
+\todo{write a brief technical overview}
+We introduce these quantities, $Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top}$, and
+	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
+		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t),
+	\end{align*}
+%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
+%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
+%	Otherwise, the two bounds has to be written into the form
+%	\begin{align*}
+%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
+%	\end{align*}
+%	and
+%	\begin{align*}
+%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
+%	\end{align*}
+%	}
+%
+%
+	and $a_1, a_2, a_3, a_4$ are the solutions of the following linear equations
+	\begin{gather}
+		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}, \label{eq_a2} \\
+		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
+		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
+		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
+		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
+	\end{gather}
+
+%In this case, $\beta_s$ and $\beta_t$ are different.
+%, or implicitly add a regularization on $B$.
+%\todo{We focus on the former case in this section.}
+%, we consider the case when $r=1$ since there are only two tasks.
+%We begin by considering the simplified equation \eqref{eq_mtl_basic} to solve for the target task.
+%This is equivalent to setting $W_i = 1$ for the two tasks in equation \eqref{eq_mtl}.
+%The result of this simplified setting will set up the ground for solving equation \eqref{eq_mtl} when we also optimize $W_1$ and $W_2$.
+%By putting the two tasks together, we get
+%\begin{align*}
+%	\hat{\beta}_{s,t} &= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
+%	&= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \bigbrace{(X_1^{\top}X_1\beta_s + X_2^{\top}X_2\beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)} \\
+%	&= \beta_t + (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\beta_s - \beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}
+%\end{align*}
+%Hence
+%\begin{align}
+%	\err(\hat{\beta}_{s,t})
+%	&= \bignorm{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2
+%	+ \sigma^2 \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ and} \\
+%	\te(\hat{\beta}_{s,t})
+%	&= \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2 + \sigma^2\cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_te_model_shift}
+%\end{align}
+
+We state our main result for two tasks with both covariate and model shift in the following theorem.
+
+\begin{theorem}\label{thm_model_shift}
+	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
+	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
+	Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+	Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
+	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
+	Let $\delta = \norm{Z} \cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2$.
+	With high probability we have
+	\begin{align}
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
+	\end{align}
+\end{theorem}
+
+%	We have the following conditions that guarantee the type of transfer we can get under model shift.
+%	\begin{itemize}
+
+%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
+%			\begin{align}
+%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
+%			\end{align}
+%	\end{itemize}
+%	\begin{align}
+%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
+%\label{eq_model_shift_pos}
+%	\end{align}
+%	where
+%{\cob
+%We have that
+%	\begin{align*}
+%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
+%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
+%		\end{align*}
+%		and
+%	\begin{align*}
+%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
+%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
+%	\end{align*}
+%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
+%\begin{align*}
+%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
+%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
+%		\end{align*}
+%	}
+
+Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
+The bounds get tighter and tighter as $n_1 / p$ increases.
+%\paragraph{Negative transfer: the Limit caused by model shifts.}
+%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
+%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
+%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
+%\te(\hat{\beta}_t)$ when
+%	\begin{align*}
+%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
+%	\end{align*}
+%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
+%\begin{align}
+%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
+%\end{align}
+%
+%\end{theorem}
+
+%From Lemma \ref{lem_cov_shift}, we know that
+%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
+%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
+%Hence the variance part is reduced by the following amount
+%\begin{align}
+%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
+%\end{align}
+%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
+%We are now interested in the following quantity
+
+%\todo{For technical reasons, we will consider the test error.}
+%\section{Effects of Model Distance, Covariate Shift, and Data Ratio on Information Transfer}\label{sec_insight}
+
+\subsection{Extension to Many Tasks of the Same Covariates}
+
+In this section we consider the setting with $k$ many that have the same covariates.
+Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
+For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+
+Concretely we will consider the following problem.
+\begin{align}
+	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
+\end{align}
+By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
+\begin{align*}
+	\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
+	&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
+\end{align*}
+where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
+%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
+Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.
+
+\paragraph{Jointly minimizing over all tasks.}
+Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
+We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
+The first part is the model shift bias, which is equal to
+\begin{align*}
+	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
+\end{align*}
+The second part is the variance, which is equal to
+\begin{align*}
+	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
+	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+\end{align*}
+Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
+Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
+Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
+We can now write the validation loss succinctly as follows.
+\begin{align*}
+	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
+\end{align*}
+From the above we can solve for $Q$ optimally as \todo{this}.
+
+\paragraph{Minimizing over the target task alone.}
+If we only minimize over the the validation loss for the target task, we shall get the following.
+\begin{align*}
+	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
+	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+\end{align*}
+
+From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
+\begin{itemize}
+	\item The de-noising effect of multi-task learning.
+	\item Multi-task training vs single-task training can be either positive or negative.
+	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
+\end{itemize}

### 2020-05-06 writeup/technical.tex

--- 2020-05-04 writeup/transfer.tex
@@
-\section{Variance Reduction from Information Transfer}\label{sec_denoise}
+\section{Main Results: Reducing Variance under Model Shift Biases}\label{sec_denoise}
 
@@
 \todo{write a brief technical overview}
-
-%In this case, $\beta_s$ and $\beta_t$ are different.
-%, or implicitly add a regularization on $B$.
-%\todo{We focus on the former case in this section.}
-%, we consider the case when $r=1$ since there are only two tasks.
-%We begin by considering the simplified equation \eqref{eq_mtl_basic} to solve for the target task.
-%This is equivalent to setting $W_i = 1$ for the two tasks in equation \eqref{eq_mtl}.
-%The result of this simplified setting will set up the ground for solving equation \eqref{eq_mtl} when we also optimize $W_1$ and $W_2$.
-%By putting the two tasks together, we get
-%\begin{align*}
-%	\hat{\beta}_{s,t} &= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-%	&= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \bigbrace{(X_1^{\top}X_1\beta_s + X_2^{\top}X_2\beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)} \\
-%	&= \beta_t + (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\beta_s - \beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}
-%\end{align*}
-%Hence
-%\begin{align}
-%	\err(\hat{\beta}_{s,t})
-%	&= \bignorm{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2
-%	+ \sigma^2 \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ and} \\
-%	\te(\hat{\beta}_{s,t})
-%	&= \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2 + \sigma^2\cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_te_model_shift}
-%\end{align}
-
-\begin{algorithm}[!t]
-	\caption{Comparing the test error of MTL, TL and STL estimators}
-	\begin{algorithmic}[1]
-		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
-		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
-		\State Training the shared body $B$.
-		\State Optimizing the task heads on the validation set
-
-		\begin{itemize}
-			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
-			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
-			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
-		\end{itemize}
-		\State Problem statement: Provide conditions to compare the test error of the three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
-	\end{algorithmic}
-\end{algorithm}
 
@@
 
-%	We have the following conditions that guarantee the type of transfer we can get under model shift.
-%	\begin{itemize}
-
-%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
-%			\begin{align}
-%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%			\end{align}
-%	\end{itemize}
-%	\begin{align}
-%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
-%\label{eq_model_shift_pos}
-%	\end{align}
-%	where
-%{\cob
-%We have that
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
-%		\end{align*}
-%		and
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
-%	\end{align*}
-%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
-%\begin{align*}
-%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
-%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
-%		\end{align*}
-%	}
-
 Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
 The bounds get tighter and tighter as $n_1 / p$ increases.
-%\paragraph{Negative transfer: the Limit caused by model shifts.}
-%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
-%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
-%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
-%\te(\hat{\beta}_t)$ when
-%	\begin{align*}
-%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%	\end{align*}
-%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
-%\begin{align}
-%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
-%\end{align}
-%
-%\end{theorem}
-
-%From Lemma \ref{lem_cov_shift}, we know that
-%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
-%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
-%Hence the variance part is reduced by the following amount
-%\begin{align}
-%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
-%\end{align}
-%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
-%We are now interested in the following quantity
-
-%\todo{For technical reasons, we will consider the test error.}
-%\section{Effects of Model Distance, Covariate Shift, and Data Ratio on Information Transfer}\label{sec_insight}
-\subsection{Effect of Model Distance on Positive versus Negative Transfer}
-
-As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
-%Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
-%\begin{align}
-%	\label{eq_mtl_basic}
-%	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
-%\end{align}
-%{\bf The distributed learning problem.}
-%    \begin{align}
-%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
-%   \end{align}
-%Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
-
-\begin{proposition}\label{prop_monotone}
-	Suppose that $n > p$.
-  When there is no model shift, i.e. $\beta_s = \beta_t$, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
-	\begin{align}
-%		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
-		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}). \label{eq_mono_te}
-	\end{align}
-\end{proposition}
-
-\begin{proof}
-%	Equation \eqref{eq_mono_e} is simply because
-%		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
-%	Equation \eqref{eq_mono_te} follows because
-	Recall that $\hat{\beta}_t^{\MTL} = \hat{w} \cdot \hat{B}$.
-	By the optimality of $\hat{w}$, we have by setting $w = 1$ in equation \eqref{eq_te_mtl}
-	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &\le \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \\
-		&= \sigma^2 \cdot \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
-		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t^{\STL}),
-	\end{align*}
-	which concludes the proof.
-\end{proof}
-
-As a remark, we can derive a similar result for the estimation error as well. The details are omitted.
-
-We describe examples based on Theorem \ref{thm_model_shift} to show several conceptual insights.
-
-\begin{example}[\textbf{Varying the distance of task models}]
-	We consider a simple setting where $\Sigma_1 = \id$.
-	Suppose that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$. Hence the task models have distance $d^2\cdot p$ in expectation.
-
-	We first consider $\Sigma_2 = \id$. In this case, we can simplify $\Delta_{\beta}$ as follows
-	\begin{align} \label{eq_delta_simple}
-		\Delta_{\beta} \define d^2 \cdot \sum_{i=1}^p \frac{(1 + a_3)\lambda_i^2 + a_4 \lambda_i^4}{(a_1 \lambda_i^2 + a_2)^2}.
-	\end{align}
-	Now we solve the equations \eqref{eq_a2}, \eqref{eq_a3}, \eqref{eq_a4} to get
-	\begin{align}
-		a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)},
-		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)}.
-	\end{align}
-%{\color{blue}if $\Sigma_1=\Sigma_2=\id$, then
-%	\begin{align}
-%		a_1 = c_1 \left( 1- \gamma_n\right) , \quad
-%		a_2 = c_2 \left( 1- \gamma_n\right), \quad
-%		a_3 = \frac{\gamma_n c_2}{1-\gamma_n}, \quad
-%		a_4 =  \frac{\gamma_n c_1}{1-\gamma_n}.
-%	\end{align}
-%	where $\gamma_n=p/n$, $c_1=n_1/n$, and $c_2=n_2/n$.
-%}
-
-	Then we obtain
-	\begin{align}
-		\Delta_{\beta} = p \cdot d^2 \cdot \frac{c_1^2 (c_1 + c_2)}{(c_1 + c_2 - 1)^3},
-		\Delta_{\vari} = \sigma^2 \cdot \frac{c_1}{(c_2 - 1)(c_1 + c_2 - 1)}.
-	\end{align}
-
-	We demonstrate our result with a simulation. (\todo {uses the tighter bound Proposition \ref{prop_model_shift_tight}?})
-	We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
-	\todo{Fill in other params.}
-	We fix the target task and vary the source task, by varying the task model distance parameter $d$.
-	We show that Theorem \ref{thm_model_shift} predicts whether we can get positive or negative transfer.
-	Figure \ref{fig_model_shift_phasetrans} shows the result.
-	We obtain the following insight from the simulation.
-	\begin{itemize}
-		\item Adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
-		\item Model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
-		Hence, the type of transfer is determined by the tradeoff between the bias caused by model shift and the reduction of variance.
-	\end{itemize}
-\end{example}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/model_shift_phase_transition.eps}
-	\caption{Positive vs negative transfer as a parameter of the task model distances.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
 
@@
 \end{itemize}
-
-\section{Effect of Covariate Shift and Data Ratio on Transfer Rate}
-
-%\subsubsection{Gains over Single-Task Training}
-
-\paragraph{A precise bound when there is no model shift.}
-As Proposition \ref{prop_monotone} shows, if $\beta_s$ and $\beta_t$ are equal, then adding the source task dataset always helps learn the target task.
-The goal of this section is to understand how covariate shift affects the rate of transfer. \todo{add conceptual msg}
-
-%The key quantity is to look at:
-%The estimator using the source and target together from minimizing \eqref{eq_mtl_basic} is
-%\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
-%The estimation error of $\hat{\beta}_{s,t}$ is
-%\begin{align}\label{eq_two_task}
-%  \err(\hat{\beta}_{s,t}) = \sigma^2 \cdot \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The estimation error using the target alone is
-%\begin{align}\label{eq_target_task}
-%	\err(\hat{\beta}_t) = \sigma^2 \cdot \tr[(X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The improvement of estimation error from adding the source task is then given by
-%$\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})$.
-%For the test error on the target task, the improvement from adding the source task is
-%\[ \te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t}) = \sigma^2\cdot\bigtr{\bigbrace{(X_2^{\top}X_2)^{-1} - (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}\cdot\Sigma_2}. \]
-
-%We calculate the amount of improvement by comparing equation \eqref{eq_two_task} to equation \eqref{eq_target_task}.
-A simple observation here is that when $\beta_s = \beta_t$, the optimal $\hat{w}$ for minimizing equation \eqref{eq_te_mtl} is equal to $1$.
-Based on this observation, we can get a more precise result than Theorem \ref{thm_model_shift} on the improvement of adding the source task data that only depends on the covariance matrices $\Sigma_1, \Sigma_2$ and the number of data points $n_1, n_2$.
-
-\begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
-	When $\beta_s = \beta_t$, we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
-	$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-	where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$. 
-	And
-	\begin{align*}
-		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
-		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}} + \bigo{|w_0-1|},
-	\end{align*}
-where $a_1, a_2$ are the solutions of equations \eqref{eq_a2}. \cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
-\end{proposition}
-
-% \begin{proposition}[Transfer rate without model shift] 
-%	Suppose $\beta_s = \beta_t$ with i.i.d. entries of mean zero and variance $d^2$. Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
-%	$$1\le \hat{w} \le w_0:=1 + \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$ 
-%	where $\|\Sigma_1\|_{\min}$ is the smallest singular value of $\Sigma_1$. Note that $w_0$ is very close to $1$ up to a small error of order $n_1^{-1}$.
-%\end{proposition}
-\begin{proof}
-We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
-We first notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
-Thus we have $\hat w\ge 1$.
-It suffices to consider the case with $w> 1$.
-Under the assumption on $\beta_s$ and $\beta_t$, we can write
-\begin{align}
-	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
-			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
-\end{align}
-Since 
-$$\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 = \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]$$
-is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
-\begin{align*}
-\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
-			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
-\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}.
-			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
-\end{align*}
-%We can write $\id = P+ P_{\perp}$, where $P$ denotes the projection onto the subspace spanned by the columns of $Z_1$ and $P_{\perp}$ denotes the projection onto its orthogonal complement.
-Together with $P\preceq (\sqrt{n_1}-\sqrt{p})^{-2} Z_1 Z_1^\top$, we get
-%\begin{align*}
-%M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M  &\succeq M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} Z_1 Z_1^\top \right] Z_1 M  \\
-%&= M^\top Z_1^{\top}Z_1  \left[\left( w-1\right) \Sigma_1  - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} \right] Z_1^\top Z_1 M .
-%\end{align*}
-Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$. 
-\end{proof}
-
-As a remark, we see that Proposition \ref{prop_monotone} follows from Theorem \ref{thm_cov_shift}.
-The amount of reduction on test error for the target task is given as
-	\begin{align*}
-%		\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})
-%		&= \sigma^2 p \cdot \bigtr{\frac 1 {(n_2 - p) \Sigma_2} - \frac 1 {(n_1 + n_2)a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2}}, \\
-		\te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t})
-		&= \sigma^2 \cdot \bigbrace{\frac p {n_2 - p} -  \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}}}.
-	\end{align*}
-Because
-\begin{align*}
-	\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)
-	\Leftarrow~ & (n_2 - p)\Sigma_2 \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2 \\
-	\Leftrightarrow~ & \zeroMatrix \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 - (n_1 + n_2)\cdot a_1) \Sigma_2,
-\end{align*}
-which is true since $a_1 \le n_1 / (n_1 + n_2)$ by equation \eqref{eq_a2}.
-The proof for $\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)$ follows by multiplying $\Sigma_2^{-1/2}$ on both sides of the inequalities above.
-
-\medskip
-Now we apply Theorem \ref{thm_cov_shift} to show how covariate shift affects the rate of transfer.
-
-%\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2$}]
-%In this case, we have $\lambda_i = 1$ for all $1\le i\le p$.
-%And $a_1 + a_2 = 1 - p / (n_1 + n_2)$.
-%Hence
-%\[ \te(\hat{\beta}_{s,t}) = \frac{\sigma^2 p^2}{n_1 + n_2 - p} \text{ and } \err(\hat{\beta}_{s,t}) = \frac {\sigma^2 p} {n_1 + n_2 - p} \bigtr{\Sigma_2^{-1}}. \]
-%\end{example}
-
-\smallskip
-\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2 / \lambda$}]
-In this case, equations \eqref{eq_a2} become
-\[ a_1 + a_2 = 1 - p/(n_1 + n_2), a_1 + \frac{p}{n_1 + n_2} \cdot \frac {a_1} {a_1 + \lambda^2 a_2} = \frac{n_1} {n_1 + n_2}. \]
-By solving these, we can get the test errors (the estimation error behaves similarly).
-Figure \ref{fig_te_scaling} shows how they grow as we increase the number of source task data points.
-Here $n_2 = 4p$ and $n_1$ ranges from $p$ to $20p$.
-We can see that the smaller $\lambda$ is, the lower the test errors will be.
-\end{example}
-
-\smallskip
-\begin{example}[\textbf{When $\Sigma_1$ and $\Sigma_2$ are complementary}]
-	We consider two cases when $\Sigma_1$ and $\Sigma_2$ are \textit{different}
-\begin{itemize}
-	\item {\bf Different singular values:} Here we have that for $\Sigma_1^{-1/2}\Sigma_2^{1/2}$, the first $p/2$ singular values of $\Sigma_1$ is $\lambda$ and the rest is $1/\lambda$.
-For this case, equations \eqref{eq_a2} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}, a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
-\ee
-It's not hard to verify that there is only one valid solution from the above.
-After solving these, we get the test error for the target task as follows.
-\be\label{testcomple} 
-te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
-	\item {\bf Different singular spaces {\color{blue}(actually they have the same singular spaces)}:}
-	Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
-$$\Sigma_1^{1/2} = 1+ U\Lambda U^\top, \quad \Sigma_2^{1/2} = 1+ V\Lambda V,$$
-where
-$$\Lambda = \diag(\wt\lambda_1,\cdots, \wt\lambda_{p/2}), \quad U= (u_1,\cdots, u_{p/2}), \quad V= (v_1,\cdots, v_{p/2}).$$
-We consider two case: if $V=U$, then $M=\id;$ if $V=U_\perp$ (i.e. the space spanned by $V$ is perpendicular to that spanned by $U$), then
-$$M=\Sigma_1^{1/2} \Sigma_2^{-1/2}=(1+\Lambda)UU^\top + (1+\Lambda)^{-1}V V^\top .$$
-This is an extension of the above example of complementary case.
-\end{itemize}
-\end{example}
-
-{\color{blue} Note that the curves in Figure 3 all cross at the point $n_1=n_2$. This can be understood in the following way. 
-First, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
-$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-On the other hand, we write
-$$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
-We can compute that
-\begin{align*}
-te(\lambda) - te(1)&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)^2 a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-\end{align*}
-If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}), and hence $te(\lambda)>te(1)$.
-Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
-}
-
-{\color{blue}
-Suppose we fix a scale of the covariate shift. That is given an $a>0$, we consider all possible covariate shift matrices $M^\top M$ such that 
-\be\label{GMcons}\det(M^\top M)= a\Leftrightarrow \prod_{i=1}^p \lambda_i = a.\ee
-We claim as long as we have sufficiently many datas (i.e.
-as long as $n_1$ is sufficiently large), then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error.
-In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$.
-Then we have
-$$te\approx \frac{\sigma^2}{n_1+n_2-p} \sum_{i=1}^p \frac{1}{\lambda_i}.$$
-By AM-GM inequality, under the constraint \eqref{GMcons} the sum is smallest when $\lambda_1=\lambda_2=\cdots=\lambda_p = a^{1/p}$. 
-}
-
-In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
-We observe the following two phases as we increase $n_1 / p$.
-\begin{itemize}
-	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-\end{itemize}
-
-\begin{figure}
-	\centering
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/scaling.eps}
-		\caption{When $\Sigma_1 = \Sigma_2 / \lambda$.}
-		\label{fig_te_scaling}
-	\end{minipage}\hfill
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/complementary.eps}
-		\caption{When $\Sigma_1$ and $\Sigma_2$ are complementary. The number of target task data points is $n_2 = 4p$.}
-		\label{fig_te_complement}
-	\end{minipage}
-\end{figure}
-
-\paragraph{Extending the intuition to the general case.}
-When there is model shift, i.e. $\beta_s = \beta_t$, we can still use Theorem \ref{thm_model_shift} (and Proposition \ref{prop_model_shift_tight}) to get the result.
-\begin{itemize}
-	\item \textbf{The effect of covariate shift:}
-	\item \textbf{The effect of data ratio:}
-\end{itemize}

### 2020-05-06 writeup/transfer.tex

--- 2020-05-04 writeup/transfer.tex
@@
-\section{Variance Reduction from Information Transfer}\label{sec_denoise}
+\section{Illustrative Examples}
 
-In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
-We achieve this through tight generalization bounds obtained from random matrix theory.
-For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
-
-Recall that the test error of $\hat{\beta}_{t}^{\MTL}$ consists of two parts
-\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) = \hat{w}^2 \bignorm{\Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{w}\beta_t)}^2 + \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}.
-\label{eq_te_model_shift}
-\end{align}
-It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$ (following the argument of Proposition \ref{prop_monotone}), i.e.
-\[ \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \sigma^2\cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
-Because of model shift however, i.e. $\beta_s \neq \beta_t$.
-We can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
-The main result of this part show deterministic conditions under which we get positive or negative transfer.
-And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
-In order to characterize $\te(\hat{\beta}_t^{\MTL})$ and $\te(\hat{\beta}_t^{\STL})$, the technical crux of our approach relies on deriving the limit of the trace of matrix inverse in the high-dimensional setting.
-To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
-\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
-We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
-\todo{write a brief technical overview}
-
-%In this case, $\beta_s$ and $\beta_t$ are different.
-%, or implicitly add a regularization on $B$.
-%\todo{We focus on the former case in this section.}
-%, we consider the case when $r=1$ since there are only two tasks.
-%We begin by considering the simplified equation \eqref{eq_mtl_basic} to solve for the target task.
-%This is equivalent to setting $W_i = 1$ for the two tasks in equation \eqref{eq_mtl}.
-%The result of this simplified setting will set up the ground for solving equation \eqref{eq_mtl} when we also optimize $W_1$ and $W_2$.
-%By putting the two tasks together, we get
-%\begin{align*}
-%	\hat{\beta}_{s,t} &= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-%	&= (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \bigbrace{(X_1^{\top}X_1\beta_s + X_2^{\top}X_2\beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)} \\
-%	&= \beta_t + (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\beta_s - \beta_t) + (X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}
-%\end{align*}
-%Hence
-%\begin{align}
-%	\err(\hat{\beta}_{s,t})
-%	&= \bignorm{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2
-%	+ \sigma^2 \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ and} \\
-%	\te(\hat{\beta}_{s,t})
-%	&= \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}^2 + \sigma^2\cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_te_model_shift}
-%\end{align}
-
-\begin{algorithm}[!t]
-	\caption{Comparing the test error of MTL, TL and STL estimators}
-	\begin{algorithmic}[1]
-		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
-		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
-		\State Training the shared body $B$.
-		\State Optimizing the task heads on the validation set
-
-		\begin{itemize}
-			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
-			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
-			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
-		\end{itemize}
-		\State Problem statement: Provide conditions to compare the test error of the three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
-	\end{algorithmic}
-\end{algorithm}
-
-Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-Denote by ${\lambda}_1\ge {\lambda}_2 \ge \dots \ge {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
-Let $(a_1, a_2)$ be the solutions to the following system of equations
-	\be
-		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}.\label{eq_a2} \\
-		 \ee
-		 After obtaining $(a_1,a_2)$, we can solve the following linear equations to get $(a_3,a_4)$:
-\begin{gather}
-		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
-		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
-		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
-		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
-	\end{gather}
-Then we introduce the following matrix
-$$Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top},$$
-which can be regarded as the asymptotic limit of $\hat w \Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}$. Finally we introduce 
-$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
-{\cor may be able to get a better bound, but the statement will be long}
-
-We now state our main result for two tasks with both covariate and model shift in the following theorem.
-
-\begin{theorem}\label{thm_model_shift}
-	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
-	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
-	%Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-	%Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
-	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
-	With high probability we have
-	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
-	\end{align}
-	where 
-	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
-		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t).
-	\end{align*}
-%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
-%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
-%	Otherwise, the two bounds has to be written into the form
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
-%	\end{align*}
-%	and
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
-%	\end{align*}
-%	} 
-\end{theorem}
-
-%	We have the following conditions that guarantee the type of transfer we can get under model shift.
-%	\begin{itemize}
-
-%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
-%			\begin{align}
-%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%			\end{align}
-%	\end{itemize}
-%	\begin{align}
-%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
-%\label{eq_model_shift_pos}
-%	\end{align}
-%	where
-%{\cob
-%We have that
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
-%		\end{align*}
-%		and
-%	\begin{align*}
-%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
-%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
-%	\end{align*}
-%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
-%\begin{align*}
-%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
-%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
-%		\end{align*}
-%	}
-
-Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
-The bounds get tighter and tighter as $n_1 / p$ increases.
-%\paragraph{Negative transfer: the Limit caused by model shifts.}
-%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
-%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
-%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
-%\te(\hat{\beta}_t)$ when
-%	\begin{align*}
-%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
-%	\end{align*}
-%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
-%\begin{align}
-%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
-%\end{align}
-%
-%\end{theorem}
-
-%From Lemma \ref{lem_cov_shift}, we know that
-%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
-%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
-%Hence the variance part is reduced by the following amount
-%\begin{align}
-%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
-%\end{align}
-%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
-%We are now interested in the following quantity
-
-%\todo{For technical reasons, we will consider the test error.}
-%\section{Effects of Model Distance, Covariate Shift, and Data Ratio on Information Transfer}\label{sec_insight}
 \subsection{Effect of Model Distance on Positive versus Negative Transfer}
@@
 
-% \begin{proposition}[Transfer rate without model shift] 
-%	Suppose $\beta_s = \beta_t$ with i.i.d. entries of mean zero and variance $d^2$. Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
-%	$$1\le \hat{w} \le w_0:=1 + \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$ 
-%	where $\|\Sigma_1\|_{\min}$ is the smallest singular value of $\Sigma_1$. Note that $w_0$ is very close to $1$ up to a small error of order $n_1^{-1}$.
-%\end{proposition}
 \begin{proof}
@@
 \end{align*}
-%We can write $\id = P+ P_{\perp}$, where $P$ denotes the projection onto the subspace spanned by the columns of $Z_1$ and $P_{\perp}$ denotes the projection onto its orthogonal complement.
-Together with $P\preceq (\sqrt{n_1}-\sqrt{p})^{-2} Z_1 Z_1^\top$, we get
-%\begin{align*}
-%M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M  &\succeq M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} Z_1 Z_1^\top \right] Z_1 M  \\
-%&= M^\top Z_1^{\top}Z_1  \left[\left( w-1\right) \Sigma_1  - \frac{\sigma^2}{d^2(\sqrt{n_1}-\sqrt{p})^{2}} \right] Z_1^\top Z_1 M .
-%\end{align*}
 Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$.

### 2020-05-07 writeup/transfer.tex
add proposition

@@
 \smallskip
-\begin{example}[\textbf{When $\Sigma_1$ and $\Sigma_2$ are complementary}]
-	We consider two cases when $\Sigma_1$ and $\Sigma_2$ are \textit{different}
-\begin{itemize}
-	\item {\bf Different singular values:} Here we have that for $\Sigma_1^{-1/2}\Sigma_2^{1/2}$, the first $p/2$ singular values of $\Sigma_1$ is $\lambda$ and the rest is $1/\lambda$.
-For this case, equations \eqref{eq_a2} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}, a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
-\ee
-It's not hard to verify that there is only one valid solution from the above.
-After solving these, we get the test error for the target task as follows.
-\be\label{testcomple}
-te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
-	\item {\bf Different singular spaces {\color{blue}(actually they have the same singular spaces)}:}
-	Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
+\begin{example}[\textbf{When $\Sigma_1$ and $\Sigma_2$ are complementary}]\label{example comple}
+	We now consider another case when $\Sigma_1$ and $\Sigma_2$ have complementary eigenspaces. Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
 $$\Sigma_1^{1/2} = 1+ U\Lambda U^\top, \quad \Sigma_2^{1/2} = 1+ V\Lambda V,$$
@@
 $$\Lambda = \diag(\wt\lambda_1,\cdots, \wt\lambda_{p/2}), \quad U= (u_1,\cdots, u_{p/2}), \quad V= (v_1,\cdots, v_{p/2}).$$
-We consider two case: if $V=U$, then $M=\id;$ if $V=U_\perp$ (i.e. the space spanned by $V$ is perpendicular to that spanned by $U$), then
+If $V=U_\perp$, i.e. the vectors $v_1,\cdots, v_{p/2}$ are perpendicular to the vectors $u_1,\cdots, u_{p/2}$, then
 $$M=\Sigma_1^{1/2} \Sigma_2^{-1/2}=(1+\Lambda)UU^\top + (1+\Lambda)^{-1}V V^\top .$$
-This is an extension of the above example of complementary case.
-\end{itemize}
-\end{example}
 
-{\color{blue} Note that the curves in Figure 3 all cross at the point $n_1=n_2$. This can be understood in the following way.
-First, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
+As a concrete example we consider the case where $\wt \lambda_1=\cdots=\wt\lambda_{p/2}$ and we denote $\lambda:=1+\wt\lambda_1$.
+Thus for $M$, the first $p/2$ singular values are equal to $\lambda$ and the rest ones are equal to $\lambda^{-1}$.
+In this case, equations in \eqref{eq_a2} become
+\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2},  \ \ a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
+\ee
+It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. After solving these, we get the test error for the target task as follows.
+\be\label{testcomple}
+te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
+
+In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
+First we notice that the curves in Figure \ref{fig_te_complement} all cross at the point $n_1=n_2$.
+In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
 Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
 $$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-On the other hand, we write
+
+Second, we observe the following two phases as we increase $n_1 / p$.
+\begin{itemize}
+	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
+	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
+\end{itemize}
+%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
+$M=\id$ case) when $n_1<n_2$.
+On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
+This phenomenon can be also explained using our theory. With \eqref{compleeq}, we can write
 $$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
@@
 Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
-}
 
-{\color{blue}
-Suppose we fix a scale of the covariate shift. That is given an $a>0$, we consider all possible covariate shift matrices $M^\top M$ such that
-\be\label{GMcons}\det(M^\top M)= a\Leftrightarrow \prod_{i=1}^p \lambda_i = a.\ee
-We claim as long as we have sufficiently many datas (i.e.
-as long as $n_1$ is sufficiently large), then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error.
-In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$.
-Then we have
-$$te\approx \frac{\sigma^2}{n_1+n_2-p} \sum_{i=1}^p \frac{1}{\lambda_i}.$$
-By AM-GM inequality, under the constraint \eqref{GMcons} the sum is smallest when $\lambda_1=\lambda_2=\cdots=\lambda_p = a^{1/p}$.
-}
+\end{example}
 
-In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
-We observe the following two phases as we increase $n_1 / p$.
-\begin{itemize}
-	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-\end{itemize}
+We can extend the above observation for Example \ref{example comple} to more general cases with arbitrary covariate shift.
+To compare different choices of $M$, we need to fix a scaling for them, because otherwise $aM$ always achieves a smaller error than $M$ for $a>1$.
+For this purpose, we introduce the following condition
+\be\label{GMcons}\det(M^\top M)= a^p \Leftrightarrow \prod_{i=1}^p \lambda_i = a^p\ee
+for some constant $a>0$, and compare different choices of $M$ under this constraint.
+The next proposition shows that, roughly speaking, as long as there are sufficiently many source task datas, then $M=a\id$ always gives (approximately) the smallest test error.
+\begin{proposition}
+We have that the test error satisfies 
+\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
+where $\lambda_p$ is the smallest singular value of $p$ and
+$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
+Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$. 
+\end{proposition}
+\begin{proof}
+From equation \eqref{eq_a2}, we get
+$$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
+With these two bounds, we can easily conclude \eqref{approxteM}.
+
+For the second statement, we find that we need to minimize 
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i},\quad \text{under}\ \ \prod_{i=1}^p\lambda_i=a^p.$$
+Then using AM-GM inequality, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+\end{proof}
+
+From the above proposition, we see that when $n_1\gg n_2$, we have that the test error is approximately given by $te(M)$ (as long as we impose a proper lower bound on $\lambda_p$).
+Moreover, $te(M)$ is minimized when $\Sigma_1$ and $\Sigma_2$ are proportional to each other, i.e.
+there is no covariate shift between the source task data and target task data.
+This provides a theoretical evidence that in general covariate shift is unfavored in transfer learning if we have enough source task data, although Example \ref{example comple} show that this may not be true when the number of source task data is small.
+
+%then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error. In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$.
 

### 2020-05-08 writeup/intro.tex
intro + reorg edits

@@
 
-Methods that can transfer the information from one task to help other tasks have recently found many applications in computer vision, natural language processing and reinforcement learning.
-In our own experience as well as discussions with collaborators, we have often observed that multi-task learning that is applied on heterogeneous data often result in suboptimal models (or negative transfer in more technical terms).
+Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
+Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
+On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).
+
+\todo{Motivate high-dimensional data.} The technical challenge is to deal with high-dimensional data, in particular when the size of the training set is only a small constant times the feature dimension.
+Prior theory is unable to explain a phase transition that occurs when comparing multi-task learning to single-task learning.
+In particular in Figure \ref{fig_motivation}, we observe a shift from positive transfer to negative transfer as a parameter of task relatedness.
+The theory we develop will provide a precise explanation to such a phenomenon (and more).
 
@@
 This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
+
+\begin{figure}[!t]
+	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}
+	\caption{Phase transition as a parameter of model distance.}
+	\label{fig_motivation}
+\end{figure}
 

### 2020-05-08 writeup/technical.tex
intro + reorg edits

@@
-\section{Main Results: Reducing Variance under Model Shift Biases}\label{sec_denoise}
+\section{Main Results: A Model Shift Bias versus Variance Trade-off}\label{sec_denoise}
 
@@
 For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-
-Concretely we will consider the following problem.
-\begin{align}
-	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
-\end{align}
-By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
-\begin{align*}
-	\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
-	&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
-\end{align*}
-where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
-%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.
-
-\paragraph{Jointly minimizing over all tasks.}
-Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
-We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
-The first part is the model shift bias, which is equal to
-\begin{align*}
-	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
-\end{align*}
-The second part is the variance, which is equal to
-\begin{align*}
-	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
-	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-\end{align*}
-Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
-Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
-Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-We can now write the validation loss succinctly as follows.
-\begin{align*}
-	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
-\end{align*}
-From the above we can solve for $Q$ optimally as \todo{this}.
-
-\paragraph{Minimizing over the target task alone.}
-If we only minimize over the the validation loss for the target task, we shall get the following.
-\begin{align*}
-	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
-	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-\end{align*}
-
-From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
-\begin{itemize}
-	\item The de-noising effect of multi-task learning.
-	\item Multi-task training vs single-task training can be either positive or negative.
-	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
-\end{itemize}

### 2020-05-10 writeup/proof_transfer_ex.tex
wip

--- 2020-05-06 writeup/transfer.tex
@@
-\section{Illustrative Examples}
-
-\subsection{Effect of Model Distance on Positive versus Negative Transfer}
+\section{Supplementary Materials for Section \ref{sec_transfer}}
 
 As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
-%Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
-%\begin{align}
-%	\label{eq_mtl_basic}
-%	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
-%\end{align}
-%{\bf The distributed learning problem.}
-%    \begin{align}
-%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
-%   \end{align}
-%Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
 
@@
 As a remark, we can derive a similar result for the estimation error as well. The details are omitted.
-
-We describe examples based on Theorem \ref{thm_model_shift} to show several conceptual insights.
-
-\begin{example}[\textbf{Varying the distance of task models}]
-	We consider a simple setting where $\Sigma_1 = \id$.
-	Suppose that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$. Hence the task models have distance $d^2\cdot p$ in expectation.
-
-	We first consider $\Sigma_2 = \id$. In this case, we can simplify $\Delta_{\beta}$ as follows
-	\begin{align} \label{eq_delta_simple}
-		\Delta_{\beta} \define d^2 \cdot \sum_{i=1}^p \frac{(1 + a_3)\lambda_i^2 + a_4 \lambda_i^4}{(a_1 \lambda_i^2 + a_2)^2}.
-	\end{align}
-	Now we solve the equations \eqref{eq_a2}, \eqref{eq_a3}, \eqref{eq_a4} to get
-	\begin{align}
-		a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)},
-		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)}.
-	\end{align}
-%{\color{blue}if $\Sigma_1=\Sigma_2=\id$, then
-%	\begin{align}
-%		a_1 = c_1 \left( 1- \gamma_n\right) , \quad
-%		a_2 = c_2 \left( 1- \gamma_n\right), \quad
-%		a_3 = \frac{\gamma_n c_2}{1-\gamma_n}, \quad
-%		a_4 =  \frac{\gamma_n c_1}{1-\gamma_n}.
-%	\end{align}
-%	where $\gamma_n=p/n$, $c_1=n_1/n$, and $c_2=n_2/n$.
-%}
-
-	Then we obtain
-	\begin{align}
-		\Delta_{\beta} = p \cdot d^2 \cdot \frac{c_1^2 (c_1 + c_2)}{(c_1 + c_2 - 1)^3},
-		\Delta_{\vari} = \sigma^2 \cdot \frac{c_1}{(c_2 - 1)(c_1 + c_2 - 1)}.
-	\end{align}
-
-	We demonstrate our result with a simulation. (\todo {uses the tighter bound Proposition \ref{prop_model_shift_tight}?})
-	We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
-	\todo{Fill in other params.}
-	We fix the target task and vary the source task, by varying the task model distance parameter $d$.
-	We show that Theorem \ref{thm_model_shift} predicts whether we can get positive or negative transfer.
-	Figure \ref{fig_model_shift_phasetrans} shows the result.
-	We obtain the following insight from the simulation.
-	\begin{itemize}
-		\item Adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
-		\item Model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
-		Hence, the type of transfer is determined by the tradeoff between the bias caused by model shift and the reduction of variance.
-	\end{itemize}
-\end{example}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/model_shift_phase_transition.eps}
-	\caption{Positive vs negative transfer as a parameter of the task model distances.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
-
-\subsection{Effect of Covariate Shift and Data Ratio on Transfer Rate}
-
-%\subsubsection{Gains over Single-Task Training}
-
-Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
-
-\paragraph{A precise bound when there is no model shift.}
-As Proposition \ref{prop_monotone} shows, if $\beta_s$ and $\beta_t$ are equal, then adding the source task dataset always helps learn the target task.
-The goal of this section is to understand how covariate shift affects the rate of transfer. \todo{add conceptual msg}
-
-%The key quantity is to look at:
-%The estimator using the source and target together from minimizing \eqref{eq_mtl_basic} is
-%\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
-%The estimation error of $\hat{\beta}_{s,t}$ is
-%\begin{align}\label{eq_two_task}
-%  \err(\hat{\beta}_{s,t}) = \sigma^2 \cdot \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The estimation error using the target alone is
-%\begin{align}\label{eq_target_task}
-%	\err(\hat{\beta}_t) = \sigma^2 \cdot \tr[(X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The improvement of estimation error from adding the source task is then given by
-%$\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})$.
-%For the test error on the target task, the improvement from adding the source task is
-%\[ \te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t}) = \sigma^2\cdot\bigtr{\bigbrace{(X_2^{\top}X_2)^{-1} - (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}\cdot\Sigma_2}. \]
-
-%We calculate the amount of improvement by comparing equation \eqref{eq_two_task} to equation \eqref{eq_target_task}.
-A simple observation here is that when $\beta_s = \beta_t$, the optimal $\hat{w}$ for minimizing equation \eqref{eq_te_mtl} is equal to $1$.
-Based on this observation, we can get a more precise result than Theorem \ref{thm_model_shift} on the improvement of adding the source task data that only depends on the covariance matrices $\Sigma_1, \Sigma_2$ and the number of data points $n_1, n_2$.
-
-\begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
-	When $\beta_s = \beta_t$, we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies 
-	$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-	where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$. 
-	And
-	\begin{align*}
-		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
-		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}} + \bigo{|w_0-1|},
-	\end{align*}
-where $a_1, a_2$ are the solutions of equations \eqref{eq_a2}. \cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
-\end{proposition}
-
-\begin{proof}
-We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
-We first notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
-Thus we have $\hat w\ge 1$.
-It suffices to consider the case with $w> 1$.
-Under the assumption on $\beta_s$ and $\beta_t$, we can write
-\begin{align}
-	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
-			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
-\end{align}
-Since
-$$\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 = \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]$$
-is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
-\begin{align*}
-\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
-			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
-\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}.
-			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
-\end{align*}
-Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$.
-\end{proof}
-
-As a remark, we see that Proposition \ref{prop_monotone} follows from Theorem \ref{thm_cov_shift}.
-The amount of reduction on test error for the target task is given as
-	\begin{align*}
-%		\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})
-%		&= \sigma^2 p \cdot \bigtr{\frac 1 {(n_2 - p) \Sigma_2} - \frac 1 {(n_1 + n_2)a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2}}, \\
-		\te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t})
-		&= \sigma^2 \cdot \bigbrace{\frac p {n_2 - p} -  \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}}}.
-	\end{align*}
-Because
-\begin{align*}
-	\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)
-	\Leftarrow~ & (n_2 - p)\Sigma_2 \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2 \\
-	\Leftrightarrow~ & \zeroMatrix \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 - (n_1 + n_2)\cdot a_1) \Sigma_2,
-\end{align*}
-which is true since $a_1 \le n_1 / (n_1 + n_2)$ by equation \eqref{eq_a2}.
-The proof for $\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)$ follows by multiplying $\Sigma_2^{-1/2}$ on both sides of the inequalities above.
-
-\medskip
-Now we apply Theorem \ref{thm_cov_shift} to show how covariate shift affects the rate of transfer.
-
-%\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2$}]
-%In this case, we have $\lambda_i = 1$ for all $1\le i\le p$.
-%And $a_1 + a_2 = 1 - p / (n_1 + n_2)$.
-%Hence
-%\[ \te(\hat{\beta}_{s,t}) = \frac{\sigma^2 p^2}{n_1 + n_2 - p} \text{ and } \err(\hat{\beta}_{s,t}) = \frac {\sigma^2 p} {n_1 + n_2 - p} \bigtr{\Sigma_2^{-1}}. \]
-%\end{example}
-
-\smallskip
-\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2 / \lambda$}]
-In this case, equations \eqref{eq_a2} become
-\[ a_1 + a_2 = 1 - p/(n_1 + n_2), a_1 + \frac{p}{n_1 + n_2} \cdot \frac {a_1} {a_1 + \lambda^2 a_2} = \frac{n_1} {n_1 + n_2}. \]
-By solving these, we can get the test errors (the estimation error behaves similarly).
-Figure \ref{fig_te_scaling} shows how they grow as we increase the number of source task data points.
-Here $n_2 = 4p$ and $n_1$ ranges from $p$ to $20p$.
-We can see that the smaller $\lambda$ is, the lower the test errors will be.
-\end{example}
-
-\smallskip
-\begin{example}[\textbf{When $\Sigma_1$ and $\Sigma_2$ are complementary}]
-	We consider two cases when $\Sigma_1$ and $\Sigma_2$ are \textit{different}
-\begin{itemize}
-	\item {\bf Different singular values:} Here we have that for $\Sigma_1^{-1/2}\Sigma_2^{1/2}$, the first $p/2$ singular values of $\Sigma_1$ is $\lambda$ and the rest is $1/\lambda$.
-For this case, equations \eqref{eq_a2} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}, a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
-\ee
-It's not hard to verify that there is only one valid solution from the above.
-After solving these, we get the test error for the target task as follows.
-\be\label{testcomple}
-te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
-	\item {\bf Different singular spaces {\color{blue}(actually they have the same singular spaces)}:}
-	Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
-$$\Sigma_1^{1/2} = 1+ U\Lambda U^\top, \quad \Sigma_2^{1/2} = 1+ V\Lambda V,$$
-where
-$$\Lambda = \diag(\wt\lambda_1,\cdots, \wt\lambda_{p/2}), \quad U= (u_1,\cdots, u_{p/2}), \quad V= (v_1,\cdots, v_{p/2}).$$
-We consider two case: if $V=U$, then $M=\id;$ if $V=U_\perp$ (i.e. the space spanned by $V$ is perpendicular to that spanned by $U$), then
-$$M=\Sigma_1^{1/2} \Sigma_2^{-1/2}=(1+\Lambda)UU^\top + (1+\Lambda)^{-1}V V^\top .$$
-This is an extension of the above example of complementary case.
-\end{itemize}
-\end{example}
-
-{\color{blue} Note that the curves in Figure 3 all cross at the point $n_1=n_2$. This can be understood in the following way.
-First, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
-$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-On the other hand, we write
-$$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
-We can compute that
-\begin{align*}
-te(\lambda) - te(1)&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)^2 a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-\end{align*}
-If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}), and hence $te(\lambda)>te(1)$.
-Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
-}
-
-{\color{blue}
-Suppose we fix a scale of the covariate shift. That is given an $a>0$, we consider all possible covariate shift matrices $M^\top M$ such that
-\be\label{GMcons}\det(M^\top M)= a\Leftrightarrow \prod_{i=1}^p \lambda_i = a.\ee
-We claim as long as we have sufficiently many datas (i.e.
-as long as $n_1$ is sufficiently large), then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error.
-In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$.
-Then we have
-$$te\approx \frac{\sigma^2}{n_1+n_2-p} \sum_{i=1}^p \frac{1}{\lambda_i}.$$
-By AM-GM inequality, under the constraint \eqref{GMcons} the sum is smallest when $\lambda_1=\lambda_2=\cdots=\lambda_p = a^{1/p}$.
-}
-
-In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
-We observe the following two phases as we increase $n_1 / p$.
-\begin{itemize}
-	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-\end{itemize}
-
-\begin{figure}
-	\centering
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/scaling.eps}
-		\caption{When $\Sigma_1 = \Sigma_2 / \lambda$.}
-		\label{fig_te_scaling}
-	\end{minipage}\hfill
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/complementary.eps}
-		\caption{When $\Sigma_1$ and $\Sigma_2$ are complementary. The number of target task data points is $n_2 = 4p$.}
-		\label{fig_te_complement}
-	\end{minipage}
-\end{figure}
-
-\paragraph{Extending the intuition to the general case.}
-When there is model shift, i.e. $\beta_s = \beta_t$, we can still use Theorem \ref{thm_model_shift} (and Proposition \ref{prop_model_shift_tight}) to get the result.
-\begin{itemize}
-	\item \textbf{The effect of covariate shift:}
-	\item \textbf{The effect of data ratio:}
-\end{itemize}

### 2020-05-10 writeup/transfer.tex
intro + reorg edits
wip

@@
-\section{Illustrative Examples}
+\section{Illustrative Examples and Their Insights on Transfer}\label{sec_transfer}
 
-\subsection{Effect of Model Distance on Positive versus Negative Transfer}
+We illustrate our main results (to be presented in Section \ref{sec_main}) by considering a few special cases, namely special settings of the task models $\set{\beta_i}_{i=1}^k$, covariance matrices $\set{\Sigma_i}_{i=1}^k$, and number of data points $\set{n_i}_{i=1}^k$.
+We show that our results explain several phenomenon that cannot be explained before.
+\todo{list those here}
 
-As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
-%Since all tasks share the same underlying model $\beta$, we use a simplified objective as follows.
-%\begin{align}
-%	\label{eq_mtl_basic}
-%	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
-%\end{align}
-%{\bf The distributed learning problem.}
-%    \begin{align}
-%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
-%   \end{align}
-%Equation \eqref{eq_mtl_basic} is simplified from equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.
-
-\begin{proposition}\label{prop_monotone}
-	Suppose that $n > p$.
-  When there is no model shift, i.e. $\beta_s = \beta_t$, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
-	\begin{align}
-%		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
-		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}). \label{eq_mono_te}
-	\end{align}
-\end{proposition}
-
-\begin{proof}
-%	Equation \eqref{eq_mono_e} is simply because
-%		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
-%	Equation \eqref{eq_mono_te} follows because
-	Recall that $\hat{\beta}_t^{\MTL} = \hat{w} \cdot \hat{B}$.
-	By the optimality of $\hat{w}$, we have by setting $w = 1$ in equation \eqref{eq_te_mtl}
-	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &\le \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \\
-		&= \sigma^2 \cdot \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
-		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t^{\STL}),
-	\end{align*}
-	which concludes the proof.
-\end{proof}
-
-As a remark, we can derive a similar result for the estimation error as well. The details are omitted.
+\subsection{Model Distance}
 
@@
 
-\begin{example}[\textbf{Varying the distance of task models}]
+\textbf{Example.}
 	We consider a simple setting where $\Sigma_1 = \id$.
@@
 	\end{itemize}
-\end{example}
 
@@
 
-\subsection{Effect of Covariate Shift and Data Ratio on Transfer Rate}
+\subsection{Covariate Shift}
 
@@
 \end{itemize}
+
+\subsection{Data Ratio}

### 2020-05-11 writeup/proof_technical.tex
sec 3.1

\section{Supplementary Materials for Section \ref{sec_main}}

\subsection{Proof of Theorem \ref{thm_model_shift}}

\noindent\todo{A proof outline; including the following key lemma.}
To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
\begin{equation}\label{eq_12moment} %\label{assm1}
\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
\end{equation}

\paragraph{A tighter bound for a special case.} We can get a bound tighter than Theorem \ref{thm_model_shift} as follows.

	\begin{proposition}\label{prop_model_shift_tight}
		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
		and we have
		\begin{align*}
			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
		\end{align*}
	\end{proposition}

The proof of Theorem \ref{thm_model_shift} involves two parts.

\paragraph{Part I: Bounding the bias from model shift.}
We relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\beta}$.
\begin{proposition}\label{prop_model_shift}
	In the setting of Theorem \ref{thm_model_shift},
	denote by $K = (\hat{w}^2X_1^{\top}X_1 + X_2^{\top}X_1)^{-1}$, and
	\begin{align*}
		\delta_1 &= \hat{w}^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_s - \hat{w}\beta_t)}^2, \\
		\delta_2 &= n_1^2\cdot \hat{w}^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_s - \hat{w}\beta_t)}, \\
		\delta_3 &= n_1^2\cdot \hat{w}^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t)}^2.
	\end{align*}
	We have that
	\begin{align*}
		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
		\le  \delta_1 - \delta_2
		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
	\end{align*}
	For the special case when $\Sigma_1 = \id$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$, we further have
	\begin{align*}
		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}
		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \beta_t)}^2.
	\end{align*}
\end{proposition}

\begin{proof}
	The proof follows by applying equation \eqref{eq_isometric}.
	Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
	Denote by $\cE = Z_1^{\top}Z_1 - {n_1}\id$.
	Let
%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_s - \hat{w}\beta_t)}^2$.
	We have
	\begin{align}
%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \hat{w}\beta_t)}^2 \nonumber \\
		\delta_1 = \delta_2 + {2\hat{w}^2n_1}(\beta_s - \hat{w}\beta_t)^{\top}\Sigma_1^{1/2}\cE\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)
		+ \hat{w}^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2 \label{eq_lem_model_shift_1}
%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
	\end{align}
	Here we use the following on the second term in equation \eqref{eq_lem_model_shift_1}
	\begin{align*}
		& \bigabs{(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)} \\
		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}}} \\
		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t) (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \\
		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2 \tag{since the matrix inside is rank 1}
	\end{align*}
	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
	\begin{align*}
		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2
		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.
	\end{align*}
	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
\end{proof}

\paragraph{Part II: The limit of $\bignorm{\Sigma_2^{1/2} (\hat{w}^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1 (\beta_s - \hat{w}\beta_t)}^2$ using random matrix theory.}
We consider the same setting as in previous subsection:
$$ X_1^{\top}X_1:=\Sigma_1^{1/2}  Z_1^T Z_1 \Sigma_1^{1/2} ,\quad X_2^{\top}X_2= \Sigma_2^{1/2}  Z_2^T Z_2 \Sigma_2^{1/2},$$
where $z_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying \eqref{eq_12moment}. For now, we assume that the random variables $z_{ij}$ are i.i.d. Gaussian, but we know that universality holds for generally distributed entries. Assume that $p/n_1$ is a small number such that $Z_1^TZ_1$ is roughly an isometry, that is, under \eqref{eq_12moment},
%\todo{
%\begin{align}\left\| Z_1^T Z_1 -  \frac{n_1}{n} I \right\| \le 2\sqrt{\frac{p}{n}} + {\frac{p}{n}} .
%\end{align}}
{\color{blue}
If we assume the variances of the entries of $Z_1$ are $1$, then we have
\begin{align}
- {n_1} \left(2\sqrt{\frac{p}{n_1}} - {\frac{p}{n_1}}\right)  \le {Z_1^T Z_1 -  n_1 \id}  \le {n_1} \left(2\sqrt{\frac{p}{n_1}} + {\frac{p}{n_1}}\right) . \label{eq_isometric}
\end{align}
}

\begin{lemma}\label{lem_cov_derivative}
	In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
\begin{equation}\label{lem_cov_derv_eq}
\begin{split}
&\wh w^{2}(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (\hat{w}X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1 (\beta_s - {w}\beta_t)}^2 \\
&= (\beta_s - {w}\beta_t)^{\top} \Sigma_1^{1/2} {M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top} \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t) +\OO(n^{-1/2+\e}),
\end{split}
\end{equation}
	for any constant $\epsilon>0$. %, where $a_{3,4}$ are found using equations in  \eqref{m35reduced}
\end{lemma}
We will give the proof of this lemma in Section \ref{sec_maintools}.

{\cor add some arguments with $\e$-net.}

\subsection{Proof of Theorem ???}

\paragraph{Extension to Many Tasks of the Same Covariates}

In this section we consider the setting with $k$ many that have the same covariates.
Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.

Concretely we will consider the following problem.
\begin{align}
	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
\end{align}
By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
\begin{align*}
	\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
	&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
\end{align*}
where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.

\paragraph{Jointly minimizing over all tasks.}
Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
The first part is the model shift bias, which is equal to
\begin{align*}
	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
\end{align*}
The second part is the variance, which is equal to
\begin{align*}
	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}
Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
We can now write the validation loss succinctly as follows.
\begin{align*}
	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
\end{align*}
From the above we can solve for $Q$ optimally as \todo{this}.

\paragraph{Minimizing over the target task alone.}
If we only minimize over the the validation loss for the target task, we shall get the following.
\begin{align*}
	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}

From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
\begin{itemize}
	\item The de-noising effect of multi-task learning.
	\item Multi-task training vs single-task training can be either positive or negative.
	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
\end{itemize}

### 2020-05-11 writeup/proof_transfer_ex.tex
sec 3.1

@@
-\section{Supplementary Materials for Section \ref{sec_transfer}}
+\section{Supplementary Materials for Section \ref{sec_insight}}
 
-As a warm up, we show that when $\beta_s = \beta_t$, then the transfer is always positive.
+From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
+for the rest of the section, we shall consider the case when $r=1$ we are considering the case of two tasks.
+Here, equation \eqref{eq_mtl} simplifies to the following
+\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
+where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
+To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
+\begin{align*}
+	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
+	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
+	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
+\end{align*}
+where we denote $w = w_1 / w_2$.
+As a remark, when $w = 1$, we recover the linear regression estimator.
 
-\begin{proposition}\label{prop_monotone}
-	Suppose that $n > p$.
-  When there is no model shift, i.e. $\beta_s = \beta_t$, adding the source task data always reduces the estimation error and the test error for the target task, i.e.
+\medskip
+\noindent\textit{Jointly optimizing over both tasks.}
+Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
 \begin{align}
-%		\err(\hat{\beta}_{t}^{\MTL})  &\le \err(\hat{\beta}_t^{\STL}), \text{ and} \label{eq_mono_e}\\
-		\te(\hat{\beta}_{t}^{\MTL}) &\le \te(\hat{\beta}_t^{\STL}). \label{eq_mono_te}
+		&\val(\hat{B}; w_1, w_2) \nonumber\\
+	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
+	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
 \end{align}
-\end{proposition}
+Minimizing the above loss is akin to performing multi-task training in practice.
+Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
+We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.
 
-\begin{proof}
-%	Equation \eqref{eq_mono_e} is simply because
-%		\[ \err(\hat{\beta}_{s,t}) = \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}} \le \bigtr{(X_1^{\top}X_1)^{-1}} = \err(\hat{\beta}_t). \]
-%	Equation \eqref{eq_mono_te} follows because
-	Recall that $\hat{\beta}_t^{\MTL} = \hat{w} \cdot \hat{B}$.
-	By the optimality of $\hat{w}$, we have by setting $w = 1$ in equation \eqref{eq_te_mtl}
+Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
+The baseline where we solve the target task with its own data is
 \begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &\le \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \\
-		&= \sigma^2 \cdot \bigtr{\bigbrace{\Sigma_2^{-1/2}X_1^{\top}X_1\Sigma_2^{-1/2} + \Sigma_2^{-1/2}X_2^{\top}X_2\Sigma^{-1/2}}^{-1}} \\
-		&\le \bigtr{\bigbrace{\Sigma_2^{-1/2}X_2^{\top}X_2\Sigma_2^{-1/2}}^{-1}}
-			= \bigtr{(X_2^{\top}X_2)^{-1} \Sigma_2} = \te(\hat{\beta}_t^{\STL}),
+	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
 \end{align*}
-	which concludes the proof.
-\end{proof}
+Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
 
-As a remark, we can derive a similar result for the estimation error as well. The details are omitted.
+\begin{lemma}\label{lem_minv}[\todo{ref?}]
+	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
+	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p}. \]
+\end{lemma}
+
+\begin{lemma}\label{lem_cov_shift}
+	In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
+\begin{align}\label{lem_cov_shift_eq}
+\tr ((w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2) = \frac{1}{n_1+n_2}\cdot \tr \left( \frac{1}{a_1 M^\top M + a_2} \right) +\bigo{ n^{-1/2+\epsilon}},
+\end{align}
+	for any constant $\epsilon>0$.
+\end{lemma}
+We will give the proof of this lemma in Section \ref{sec_maintools}.
+
+\subsection{Proof of Proposition \ref{prop_transition}}
+
+Hence the task models have distance $d^2\cdot p$ in expectation.
+	We first consider $\Sigma_2 = \id$. In this case, we can simplify $\Delta_{\beta}$ as follows
+	\begin{align} \label{eq_delta_simple}
+		\Delta_{\beta} \define d^2 \cdot \sum_{i=1}^p \frac{(1 + a_3)\lambda_i^2 + a_4 \lambda_i^4}{(a_1 \lambda_i^2 + a_2)^2}.
+	\end{align}
+	Now we solve the equations \eqref{eq_a2}, \eqref{eq_a3}, \eqref{eq_a4} to get
+	\begin{align}
+		a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
+		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
+		a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)},
+		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)}.
+	\end{align}
+%{\color{blue}if $\Sigma_1=\Sigma_2=\id$, then
+%	\begin{align}
+%		a_1 = c_1 \left( 1- \gamma_n\right) , \quad
+%		a_2 = c_2 \left( 1- \gamma_n\right), \quad
+%		a_3 = \frac{\gamma_n c_2}{1-\gamma_n}, \quad
+%		a_4 =  \frac{\gamma_n c_1}{1-\gamma_n}.
+%	\end{align}
+%	where $\gamma_n=p/n$, $c_1=n_1/n$, and $c_2=n_2/n$.
+%}
+
+	Then we obtain
+	\begin{align}
+		\Delta_{\beta} = p \cdot d^2 \cdot \frac{c_1^2 (c_1 + c_2)}{(c_1 + c_2 - 1)^3},
+		\Delta_{\vari} = \sigma^2 \cdot \frac{c_1}{(c_2 - 1)(c_1 + c_2 - 1)}.
+	\end{align}

### 2020-05-11 writeup/transfer.tex
sec 3.1

@@
-\section{Illustrative Examples and Their Insights on Transfer}\label{sec_transfer}
+\section{Illustrative Examples and Their Insights on Transfer}\label{sec_insight}
 
@@
 
-We describe examples based on Theorem \ref{thm_model_shift} to show several conceptual insights.
+We compare the test error of $\hat{\beta}_t^{\MTL}$ to that of $\hat{\beta}_t^{\STL}$.
+For a simple example, we show that whether $\hat{\beta}_t^{\MTL}$ performs better than $\hat{\beta}_t^{\STL}$ is determined by the distance of the task models.
+We derive a sharp threshold when positive transfer transitions to negative transfer, as a ratio between the model distance and the noise level.
 
 \textbf{Example.}
-	We consider a simple setting where $\Sigma_1 = \id$.
-	Suppose that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$. Hence the task models have distance $d^2\cdot p$ in expectation.
+	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
+	For the task models, suppose that $\beta_t$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_s - \beta_t$ also has i.i.d. entries with mean $0$ and variance $d^2$.
+	We have $n = c \cdot p$ data points from each task.
 
-	We first consider $\Sigma_2 = \id$. In this case, we can simplify $\Delta_{\beta}$ as follows
-	\begin{align} \label{eq_delta_simple}
-		\Delta_{\beta} \define d^2 \cdot \sum_{i=1}^p \frac{(1 + a_3)\lambda_i^2 + a_4 \lambda_i^4}{(a_1 \lambda_i^2 + a_2)^2}.
-	\end{align}
-	Now we solve the equations \eqref{eq_a2}, \eqref{eq_a3}, \eqref{eq_a4} to get
-	\begin{align}
-		a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)},
-		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)}.
-	\end{align}
-%{\color{blue}if $\Sigma_1=\Sigma_2=\id$, then
-%	\begin{align}
-%		a_1 = c_1 \left( 1- \gamma_n\right) , \quad
-%		a_2 = c_2 \left( 1- \gamma_n\right), \quad
-%		a_3 = \frac{\gamma_n c_2}{1-\gamma_n}, \quad
-%		a_4 =  \frac{\gamma_n c_1}{1-\gamma_n}.
-%	\end{align}
-%	where $\gamma_n=p/n$, $c_1=n_1/n$, and $c_2=n_2/n$.
-%}
-
-	Then we obtain
-	\begin{align}
-		\Delta_{\beta} = p \cdot d^2 \cdot \frac{c_1^2 (c_1 + c_2)}{(c_1 + c_2 - 1)^3},
-		\Delta_{\vari} = \sigma^2 \cdot \frac{c_1}{(c_2 - 1)(c_1 + c_2 - 1)}.
-	\end{align}
-
+	We illustrate the example in a synthetic setting.
 	We demonstrate our result with a simulation. (\todo {uses the tighter bound Proposition \ref{prop_model_shift_tight}?})
@@
 	Figure \ref{fig_model_shift_phasetrans} shows the result.
-	We obtain the following insight from the simulation.
+
+Specifically, the transition threshold is derived in the following proposition.
+\begin{proposition}\label{prop_transition}
+	In the example described above, we have the following deterministic conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
 	\begin{itemize}
-		\item Adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
-		\item Model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
-		Hence, the type of transfer is determined by the tradeoff between the bias caused by model shift and the reduction of variance.
+		\item If ${p\cdot d^2}/{\sigma^2} < \frac{2(2c-1)^2}{(c-1)(2c+1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{2(2c-1)^2}{(c-1)(2c+1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
+\end{proposition}
+
+We obtain the following insight from Proposition \ref{prop_transition}.
+First, adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
+On the other hand, model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
+Hence, the type of transfer is determined by the trade-off between the bias caused by model shift and the reduction of variance.
 

### 2020-05-12 writeup/transfer.tex
sec 2 edits

@@
 \begin{proposition}\label{prop_transition}
-	In the example described above, we have the following deterministic conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
+	In the example described above, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
@@
 \end{figure}
+
+\subsection{Data Ratio}
 
@@
 \end{itemize}
-
-\subsection{Data Ratio}

### 2020-05-12 writeup/proof_transfer_ex.tex
sec 2 edits
proof of prop 3.1

@@
 Here, equation \eqref{eq_mtl} simplifies to the following
-\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
+\begin{align}\label{eq_mtl_2task}
+	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
+\end{align}
 where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
@@
 \begin{align*}
-	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
-	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
+	& \hat{B}(w_1, w_2) \\
+	=& (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
+	=& \frac{1}{w_2} ((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
+	=& \frac{1}{w_2}\bigbrace{\beta_t + ((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\frac{w_1}{w_2}\beta_s - w^2\beta_t) + (\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}}.
 \end{align*}
-where we denote $w = w_1 / w_2$.
-As a remark, when $w = 1$, we recover the linear regression estimator.
+As a remark, when $w_1 = w_2 = 1$, we recover the linear regression estimator.
+The advantage of using $f(B; w_1, w_2)$ is that if $\theta_1$ is a scaling of $\theta_2$, then this case can be solved optimally using equation \eqref{eq_mtl_2task} \cite{KD12}.
 
-\medskip
-\noindent\textit{Jointly optimizing over both tasks.}
+\textbf{Defining the multi-task learning estimator.}
 Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
 \begin{align}
-		&\val(\hat{B}; w_1, w_2) \nonumber\\
-	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
-	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
+		\val(\hat{B}; w_1, w_2)
+	= & n_1 \cdot \bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 \nonumber \\
+		&+ n_1 \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1} \nonumber \\
+		&+ n_2 \cdot w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 \nonumber \\
+		&+ n_2 \cdot \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_val_mtl}
 \end{align}
-Minimizing the above loss is akin to performing multi-task training in practice.
-Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
-We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.
+Let $\hat{w_1}, \hat{w_2}$ be the global minimizer of $\val(\hat{B}; w_1, w_2)$.
+We will define the multi-task learning estimator for the target task as
+	\[ \hat{\beta}_t^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2). \]
+
+The intuition for deriving $\hat{\beta}_t^{\MTL}$ is akin to performing multi-task training in practice.
+Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
+The test loss of using $\hat{\beta}_t^{\MTL}$ for the target task is
+\begin{align}
+	\te(\hat{\beta}_t^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
+			&~ + \sigma^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl_2task}
+\end{align}
 
@@
 \end{align*}
-Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
+%Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
 
+We first state several helper lemmas that can be viewed as corollaries of Theorem \ref{thm_model_shift}.
 \begin{lemma}\label{lem_minv}[\todo{ref?}]
-	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
-	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{p}{n_2 - p}. \]
+	Let $X\in\real^{n\times p}$ that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma$.
+	In the setting when $n = c p$ we have that as $p$ goes to infinity,
+	\[ \bigtr{(X^{\top}X)^{-1}\Sigma} = \frac{1}{c - 1}. \]
 \end{lemma}
@@
 \begin{lemma}\label{lem_cov_shift}
-	In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
+	\todo{restate the setting} In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
 \begin{align}\label{lem_cov_shift_eq}
-\tr ((w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2) = \frac{1}{n_1+n_2}\cdot \tr \left( \frac{1}{a_1 M^\top M + a_2} \right) +\bigo{ n^{-1/2+\epsilon}},
+\tr ((X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2) = \frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 M^\top M + a_2)^{-1}} +\bigo{ n^{-1/2+\epsilon}},
 \end{align}
@@
 \end{lemma}
-We will give the proof of this lemma in Section \ref{sec_maintools}.
+We will give the proof of Lemma \ref{lem_cov_shift} in Section \ref{sec_maintools}.
 
 \subsection{Proof of Proposition \ref{prop_transition}}
+
+Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
+The proof will consist of two main steps.
+\begin{itemize}
+	\item First, we show that $\hat{v}$ is close to $1$.
+	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ to show the result.
+\end{itemize}
 

### 2020-05-12 writeup/proof_transfer_ex.tex
A & A.1

@@
 
-We first state several helper lemmas that can be viewed as corollaries of Theorem \ref{thm_model_shift}.
+We state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$.
+The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.
 \begin{lemma}\label{lem_minv}[\todo{ref?}]
@@
 
+The second lemma is a corollary of Theorem \ref{thm_model_shift}.
 \begin{lemma}\label{lem_cov_shift}
-	\todo{restate the setting} In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
-\begin{align}\label{lem_cov_shift_eq}
-\tr ((X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2) = \frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 M^\top M + a_2)^{-1}} +\bigo{ n^{-1/2+\epsilon}},
+	Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i$, for $i = 1, 2$.
+	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in decreasing order.
+	When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
+	\begin{align}%\label{lem_cov_shift_eq}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{c_1+c_2}\cdot \bigtr{ \frac{1}{p}\cdot(a_1 M^\top M + a_2)^{-1}} +\bigo{ n^{-1/2+\epsilon}},
 	\end{align}
-	for any constant $\epsilon>0$.
+	for any constant $\epsilon>0$, where $a_1, a_2$ are solutions to the following deterministic equations:
+	\begin{align}
+		a_1 + a_2 = 1- \frac{1}{c_1 + c_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(c_1 + c_2)(a_1 + a_2/ \lambda_i^2)} = \frac{c_1}{c_1 + c_2}. \label{eq_a12}
+	\end{align}
 \end{lemma}
@@
 
-\subsection{Proof of Proposition \ref{prop_transition}}
+\subsection{Proof of Proposition \ref{prop_dist_transition}}
 
 Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
+
 The proof will consist of two main steps.
@@
 \end{itemize}
+
+\begin{lemma}
+	In the setting of Proposition \ref{prop_dist_transition}, we have that $\abs{\hat{v} = \hat{w_1} / \hat{w_2} - 1} \le o(1)$.
+\end{lemma}
+
+\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, upper bound]
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, lower bound]
+\end{proof}
 

### 2020-05-12 writeup/transfer.tex
A & A.1

--- 2020-05-11 writeup/transfer.tex
@@
 Specifically, the transition threshold is derived in the following proposition.
-\begin{proposition}\label{prop_transition}
-	In the example described above, we have the following deterministic conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
+\begin{proposition}\label{prop_dist_transition}
+	In the example described above, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
@@
 
-We obtain the following insight from Proposition \ref{prop_transition}.
+We obtain the following insight from Proposition \ref{prop_dist_transition}.
 First, adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.

### 2020-05-13 writeup/proof_technical.tex
add proof

@@
 
-\subsection{Proof of Theorem \ref{thm_model_shift}}
+\subsection{Proof of Theorem \ref{thm_model_shift}}\label{sec pfmain}
 
@@
 \end{equation}
-
-\paragraph{A tighter bound for a special case.} We can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
-
-	\begin{proposition}\label{prop_model_shift_tight}
-		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
-		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
-		and we have
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
-		\end{align*}
-	\end{proposition}
 
@@
 
+\begin{proof}[Proof of Proposition \ref{prop_model_shift_tight}]
+the proof for tighter bound ........... 
+\end{proof}
+
 {\cor add some arguments with $\e$-net.}

### 2020-05-13 writeup/proof_transfer_ex.tex
add proof

--- 2020-05-12 writeup/proof_transfer_ex.tex
@@
 		&+ n_2 \cdot w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 \nonumber \\
-		&+ n_2 \cdot \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_val_mtl}
+		&+ n_2 \cdot \sigma^2 \cdot w^2\bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_val_mtl}
 \end{align}
@@
 
+%\paragraph{A tighter bound for a special case.} 
+Under the setting of Proposition \ref{prop_transition}, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
+
+	\begin{proposition}\label{prop_model_shift_tight}
+		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$. 
+		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
+		and we have
+		\begin{align*}
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
+		\end{align*}
+	\end{proposition}
+We will give the proof of this proposition after proving Theorem \ref{thm_model_shift} in Section \ref{sec pfmain}	.
+
 Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
@@
 	\end{align}
+
+We denote
+\begin{align}
+	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& + n_2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} w^2(X_1^{\top}X_1)^2\right] \nonumber\\
+			& + (n_1+n_2 w^2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+\end{align}
+Under the setting of Proposition \ref{prop_model_shift_tight}, using concentration of random vector with i.i.d. entries, we have that
+$$\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\oo(1)\right)\quad \text{with probability }1-\oo(1).$$
+Thus it suffices to study the behavior of $\val (w)$. For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
+
+\begin{lemma} 
+Suppose the assumptions of Proposition \ref{prop_model_shift_tight} hold.
+Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
+Then we have that the optimal ratio for $\val(w)$ satisfies
+	$$|\hat w -1|=\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
+\end{lemma}
+\begin{proof}
+The proof is also similar to the one for Proposition \ref{thm_cov_shift}. First it is easy to observe that $\val(w)\le \val(-w)$ for $w\ge 0$. Hence it suffices to consider the $w\ge 0$ case.
+
+We first consider the case $w\ge 1$. We write
+\begin{align}
+	\val(w) &= n_1\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& + n_2\left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+			& + \sigma^2n_1 \cdot \bigtr{(w^{2}X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } +  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
+\end{align}
+
+Taking derivative of $\val(w)$ with respect to $w$, we obtain that 
+\begin{align*}
+\val'(w) \ge &~ n_1\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
++&~ n_2\left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+		-&~ 2n_1 \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_1 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
+\end{align*}
+where the matrix $\cal A$ is
+\begin{align*}
+\cal A :&= \left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2.
+- 2\frac{\sigma^2}{w^3}X_1^\top X_1
+\end{align*}
+Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
+\begin{align*}
+\cal A \succeq - \frac{4d^2}{w^5}(\sqrt{n_2}+\sqrt{p})^4 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](\sqrt{n_1}-\sqrt{p})^4 - 2\frac{\sigma^2}{w^3}(\sqrt{n_1}+\sqrt{p})^2\succ 0,
+\end{align*}
+as long as 
+$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{n_1(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
+Hence $\val'(w)>0$ on $(1+w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>1+w_1$. Hence we must have $\hat w\le 1+w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$.
+
+Then we consider the case $w\le 1$. Taking derivative of $\val(w)$ with respect to $w$, we obtain that 
+\begin{align}
+	\val'(w) &\le n_1 \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& + n_2\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+			& + 2n_2 w\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_2^\top X_2} = n_1 \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
+\end{align}
+where the matrix $\cal B$ is 
+$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2\frac{n_2}{n_1} w\sigma^2X_2^\top X_2.$$
+\cob Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
+\begin{align*}
+\cal A \succeq - \frac{4d^2}{w^5}(\sqrt{n_2}+\sqrt{p})^4 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](\sqrt{n_1}-\sqrt{p})^4 - 2\frac{\sigma^2}{w^3}(\sqrt{n_1}+\sqrt{p})^2\succ 0,
+\end{align*}
+as long as 
+$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{n_1(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
+Hence $\val'(w)>0$ on $(1+w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>1+w_1$. Hence we must have $\hat w\le 1+w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$. 
+\end{proof}

### 2020-05-13 writeup/transfer.tex
add proof

--- 2020-05-12 writeup/transfer.tex
@@
 \begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
-	When $\beta_s = \beta_t$, we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies
-	$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-	where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-	And
-	\begin{align*}
+Suppose $\beta_s = \beta_t$ and $\|\beta_t\|_2^2\sim p\sigma^2$ (i.e.
+the $l^2$-norm of the vector $\beta_t$ is of the same order as that of the error vector).
+Assume that the condition numbers of $\Sigma_1$, $\Sigma_2$ and $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all bounded by a constant $C>0$.
+Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies
+	$$1\le \hat{w} \le 1+\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
+	%where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+Moreover, we have
+	\begin{align}\label{tehatw1}
 		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
-		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}} + \bigo{|w_0-1|},
-	\end{align*}
-where $a_1, a_2$ are the solutions of equations \eqref{eq_a2}. \cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
+		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1 M^\top M  + (n_1 + n_2)a_2\id}^{-1}} \cdot \left(1+ \bigo{p^{-1}}\right),
+	\end{align}
+where $a_1, a_2$ are the solutions to equations \eqref{eq_a2}. %\cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
 \end{proposition}
@@
 We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
-We first notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
+Note that $\val(w)\le \val(-w)$ for $w\ge 0$.
+Hence we have $\hat w\ge 0$.
+Moreover, we notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
 Thus we have $\hat w\ge 1$.
@@
 Since
-$$\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 = \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]$$
+\begin{align*}
+&\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \\
+&= \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]
+\end{align*}
 is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
@@
 \end{align*}
-Hence $\val'(w)\ge 0$ if $w\ge w_0$, i.e. $\val(w)$ is an increasing function on $[1+w_0,\infty]$. Thus we get $\hat w$ is between $[1,w_0]$.
+Hence $\val'(w)\ge 0$ if $w>1+ \e_0$, where
+$$\e_0:= \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2}.$$
+In other words, $\val(w)$ is strictly increasing function on $[1+\e_0,\infty]$. Thus we get that $\hat w$ satisfies 
+\be\label{hatw1}1\le w \le 1+\e_0.\ee Using \eqref{eq_isometric}, we get that
+$$\e_0=\OO(\sigma^2/\|\beta_t\|_2^2)=\OO(p^{-1}).$$
+
+Finally, plugging \eqref{hatw1} into the expression $\te(\hat{\beta}^{\TL}_{t}) $, we obtain \eqref{tehatw1}.
+%$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$
 \end{proof}

### 2020-05-13 writeup/proof_transfer_ex.tex
A.1

--- 2020-05-12 writeup/proof_transfer_ex.tex
@@
 		\val(\hat{B}; w_1, w_2)
-	= & n_1 \cdot \bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 \nonumber \\
-		&+ n_1 \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1} \nonumber \\
-		&+ n_2 \cdot w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 \nonumber \\
-		&+ n_2 \cdot \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_val_mtl}
+	= & n_1 \cdot \bignorm{\Sigma_1^{1/2}((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - \frac{w_1}{w_2}\beta_t)}^2 \nonumber \\
+		&+ n_1 \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1} \nonumber \\
+		&+ n_2 \cdot w^2\bignorm{\Sigma_2^{1/2}((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \frac{w_1}{w_2}\beta_t)}^2 \nonumber \\
+		&+ n_2 \cdot \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_val_mtl}
 \end{align}
-Let $\hat{w_1}, \hat{w_2}$ be the global minimizer of $\val(\hat{B}; w_1, w_2)$.
+Let $\hat{w_1}/\hat{w_2}$ be the global minimizer of $\val(\hat{B}; w_1, w_2)$.
 We will define the multi-task learning estimator for the target task as
@@
 \begin{lemma}\label{lem_minv}[\todo{ref?}]
-	Let $X\in\real^{n\times p}$ that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma$.
+	Let $X\in\real^{n\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$.
 	In the setting when $n = c p$ we have that as $p$ goes to infinity,
@@
 
-The second lemma is a corollary of Theorem \ref{thm_model_shift}.
+The second lemma, which deals the inverse of the sum of two random matrices, can be viewed as a special case of Theorem \ref{thm_model_shift}.
 \begin{lemma}\label{lem_cov_shift}
-	Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i$, for $i = 1, 2$.
+	Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
 	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in decreasing order.
@@
 	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{c_1 + c_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(c_1 + c_2)(a_1 + a_2/ \lambda_i^2)} = \frac{c_1}{c_1 + c_2}. \label{eq_a12}
+		a_1 + a_2 = 1- \frac{1}{c_1 + c_2},~ a_1 + \frac{1}{p}\cdot\sum_{i=1}^p \frac{a_1}{(c_1 + c_2)(a_1 + a_2/ \lambda_i^2)} = \frac{c_1}{c_1 + c_2}. \label{eq_a12}
 	\end{align}
@@
 \subsection{Proof of Proposition \ref{prop_dist_transition}}
-
-Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
 
@@
 \begin{lemma}
-	In the setting of Proposition \ref{prop_dist_transition}, we have that $\abs{\hat{v} = \hat{w_1} / \hat{w_2} - 1} \le o(1)$.
+	Recall that $\hat{v} = \hat{w_1} / \hat{w_2}$.
+	In the setting of Proposition \ref{prop_dist_transition}, we have that
+	\[ \abs{\hat{v} - 1} \le o(1). \]
 \end{lemma}
+
+Since $\Sigma_1 = \Sigma_2$, we know that $M = \hat{v}\Sigma_1^{1/2}\Sigma_2^{-1/2} = \hat{v} \id$.
+Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
+\begin{align}
+	\Delta_{\vari} \define \sigma^2 \bigbrace{ - \frac{1}{c_2 - 1}},
+\end{align}
+where we solve equation \eqref{eq_a12} to obtain $a_1 = $ and $a_2 = $.
 

### 2020-05-13 writeup/proof_transfer_ex.tex

--- 2020-05-13 writeup/proof_transfer_ex.tex
@@
 
-\subsection{Proof of Proposition \ref{prop_transition}}
+\subsection{Proof of Proposition \ref{prop_dist_transition}}
 
 %\paragraph{A tighter bound for a special case.} 
-Under the setting of Proposition \ref{prop_transition}, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
+Under the setting of Proposition \ref{prop_dist_transition}, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
 
@@
 Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
+
 The proof will consist of two main steps.
@@
 \end{align}
-Under the setting of Proposition \ref{prop_model_shift_tight}, using concentration of random vector with i.i.d. entries, we have that
-$$\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\oo(1)\right)\quad \text{with probability }1-\oo(1).$$
+Under the setting of Proposition \ref{prop_model_shift_tight}, using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we have that
+$$\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2})\right)\quad \text{with probability }1-\oo(1).$$
 Thus it suffices to study the behavior of $\val (w)$. For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
@@
 $$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{n_1(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
-Hence $\val'(w)>0$ on $(1+w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>1+w_1$. Hence we must have $\hat w\le 1+w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$.
+Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$.
 
@@
 $$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2\frac{n_2}{n_1} w\sigma^2X_2^\top X_2.$$
-\cob Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
+Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
 \begin{align*}
-\cal A \succeq - \frac{4d^2}{w^5}(\sqrt{n_2}+\sqrt{p})^4 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](\sqrt{n_1}-\sqrt{p})^4 - 2\frac{\sigma^2}{w^3}(\sqrt{n_1}+\sqrt{p})^2\succ 0,
+\cal B \preceq - 2(1-w)\kappa^2(\sqrt{n_2}-\sqrt{p})^4 +2d^2 w\frac{n_2}{n_1}(\sqrt{n_1}+\sqrt{p})^4 +2\sigma^2 w \frac{n_2}{n_1}(\sqrt{n_2}+\sqrt{p})^2\prec 0,
 \end{align*}
 as long as 
-$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{n_1(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
-Hence $\val'(w)>0$ on $(1+w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>1+w_1$. Hence we must have $\hat w\le 1+w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$. 
+$$w< w_2:=1 - \left[ \frac{\sigma^2}{\kappa^2}\frac{n_2(\sqrt{n_2}+\sqrt{p})^2}{n_1(\sqrt{n_2}-\sqrt{p})^4}+ \frac{d^2}{\kappa^2}\frac{n_2(\sqrt{n_1}+\sqrt{p})^4}{n_1(\sqrt{n_2}-\sqrt{p})^4}\right].$$
+Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly increasing for $w<w_2$. Hence we must have $\hat w\le w_2$. Note that under our assumptions, we have $w_2=1-\OO(p^{-1})$. 
 \end{proof}

### 2020-05-13 writeup/transfer.tex

@@
 Specifically, the transition threshold is derived in the following proposition.
-\begin{proposition}\label{prop_transition}
+\begin{proposition}\label{prop_dist_transition}
 	In the example described above, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:

### 2020-05-13 writeup/proof_transfer_ex.tex
sec 3.1

--- 2020-05-13 writeup/proof_transfer_ex.tex
@@
 
+Finally, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
+\todo{restate this}
+\begin{lemma}\label{prop_model_shift_tight}
+		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
+		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
+		and we have
+		\begin{align*}
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
+		\end{align*}
+\end{lemma}
+
 \subsection{Proof of Proposition \ref{prop_dist_transition}}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem_hat_v}
 	Recall that $\hat{v} = \hat{w_1} / \hat{w_2}$.
 	In the setting of Proposition \ref{prop_dist_transition}, we have that
-	\[ \abs{\hat{v} - 1} \le o(1). \]
+	\[ \abs{\hat{v} - 1} \lesssim \frac 1 p. \]
 \end{lemma}
 
-Since $\Sigma_1 = \Sigma_2$, we know that $M = \hat{v}\Sigma_1^{1/2}\Sigma_2^{-1/2} = \hat{v} \id$.
-Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
-\begin{align}
-	\Delta_{\vari} \define \sigma^2 \bigbrace{ - \frac{1}{c_2 - 1}},
-\end{align}
-where we solve equation \eqref{eq_a12} to obtain $a_1 = $ and $a_2 = $.
-
-\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, upper bound]
+Based on Lemma \ref{lem_hat_v}, we can prove Proposition \ref{prop_dist_transition}.
+\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
+	Since $\Sigma_1 = \Sigma_2$, we know that $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \hat{v} \id$.
+	Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as whp
+	\begin{align*}
+		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{c_2 - 1} - \frac{1}{c_1 + c_2}\cdot\frac{1}{a_1\hat{v}^2 + a_2} + \bigo{p^{-1/2+\varepsilon}}} \\
+		&= \sigma^2 \bigbrace{\frac{c_1}{(c_2-1)(c_1 + c_2 -1)} + \bigo{p^{-1/2 + \varepsilon}}},
+	\end{align*}
+	where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
+	Next we consider the model shift bias
+	\begin{align*}
+		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
+		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}}
+	\end{align*}
+	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
+	\[ \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{\frac 1 p} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
+\]
+	By solving equations \eqref{eq_a12}, \eqref{eq_a3} and \eqref{eq_a4}, we get
+	\begin{align*}
+		& a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}),
+		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}), \\
+		& a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}),
+		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}).
+	\end{align*}
+	Hence we obtain that
+	\begin{align*}
+		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
+		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
+	\end{align*}
+	To sum up, we have shown that when
+	\[ \frac{p\cdot d^2}{\sigma^2} < \frac{(c_1 + c_2 - 1)^2}{c_1(c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 + \sqrt{\frac 1 {c_1}}}^{-4}, \]
+	we have that $\Delta_{\vari} > \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$.
+	When
+	\[ \frac{p\cdot d^2}{\sigma^2} > \frac{(c_1 + c_2 - 1)^2}{c_1 (c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 - \sqrt{\frac 1 {c_1}}}^{-4}, \]
+	we have that $\Delta_{\vari} < \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is higher than $\te(\hat{\beta}_t^{\STL})$.
+	The result follows by taking $c_1 = c_2 = c$ for the above equation.
 \end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, lower bound]
-\end{proof}
-
-Hence the task models have distance $d^2\cdot p$ in expectation.
-	We first consider $\Sigma_2 = \id$. In this case, we can simplify $\Delta_{\beta}$ as follows
-	\begin{align} \label{eq_delta_simple}
-		\Delta_{\beta} \define d^2 \cdot \sum_{i=1}^p \frac{(1 + a_3)\lambda_i^2 + a_4 \lambda_i^4}{(a_1 \lambda_i^2 + a_2)^2}.
-	\end{align}
-	Now we solve the equations \eqref{eq_a2}, \eqref{eq_a3}, \eqref{eq_a4} to get
-	\begin{align}
-		a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2},
-		a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)},
-		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)}.
-	\end{align}
-%{\color{blue}if $\Sigma_1=\Sigma_2=\id$, then
-%	\begin{align}
-%		a_1 = c_1 \left( 1- \gamma_n\right) , \quad
-%		a_2 = c_2 \left( 1- \gamma_n\right), \quad
-%		a_3 = \frac{\gamma_n c_2}{1-\gamma_n}, \quad
-%		a_4 =  \frac{\gamma_n c_1}{1-\gamma_n}.
-%	\end{align}
-%	where $\gamma_n=p/n$, $c_1=n_1/n$, and $c_2=n_2/n$.
-%}
-
-	Then we obtain
-	\begin{align}
-		\Delta_{\beta} = p \cdot d^2 \cdot \frac{c_1^2 (c_1 + c_2)}{(c_1 + c_2 - 1)^3},
-		\Delta_{\vari} = \sigma^2 \cdot \frac{c_1}{(c_2 - 1)(c_1 + c_2 - 1)}.
-	\end{align}

### 2020-05-13 writeup/transfer.tex
sec 3.1

--- 2020-05-12 writeup/transfer.tex
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the example described above, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
+	In the example described above, assume that $c > 50$ is a fixed constant.
+	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
-		\item If ${p\cdot d^2}/{\sigma^2} < \frac{2(2c-1)^2}{(c-1)(2c+1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{2(2c-1)^2}{(c-1)(2c+1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${p\cdot d^2}/{\sigma^2} < \frac 1 4 \frac{(2c-1)^2}{(c-1)c^2} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{(2c-1)^2}{(c-1)c^2} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}

### 2020-05-13 writeup/proof_transfer_ex.tex

@@
 		&+ n_2 \cdot w^2\bignorm{\Sigma_2^{1/2}((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \frac{w_1}{w_2}\beta_t)}^2 \nonumber \\
-		&+ n_2 \cdot \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \label{eq_val_mtl}
+		&+ n_2 \cdot \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}. \label{eq_val_mtl}
 \end{align}
@@
 
+We denote
+\begin{align}
+	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+			& + (n_1+n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+\end{align}
+Under the setting of Proposition \ref{prop_model_shift_tight}, using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we have that
+$$\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2})\right)\quad \text{with probability }1-\oo(1).$$
+Thus it suffices to study the behavior of $\val (w)$.
+For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
+
 \begin{lemma}\label{lem_hat_v}
-	Recall that $\hat{v} = \hat{w_1} / \hat{w_2}$.
-	In the setting of Proposition \ref{prop_dist_transition}, we have that
-	\[ \abs{\hat{v} - 1} \lesssim \frac 1 p. \]
+Suppose the assumptions of Proposition \ref{prop_model_shift_tight} hold.
+Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
+Then we have that the optimal ratio for $\val(w)$ satisfies
+	$$|\hat w -1|=\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
 \end{lemma}
+\begin{proof}
+The proof is also similar to the one for Proposition \ref{thm_cov_shift}. First it is easy to observe that $\val(w)\le \val(-w)$ for $w\ge 0$. Hence it suffices to consider the $w\ge 0$ case.
+
+We first consider the case $w\ge 1$. We write
+\begin{align}
+	\val(w) &= n_1\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& + n_2\left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+			& + \sigma^2(n_1+n_2) \cdot \bigtr{(w^{2}X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } .\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
+\end{align}
+
+Taking derivative of $\val(w)$ with respect to $w$, we obtain that
+\begin{align*}
+\val'(w) \ge &~ n_1\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
++&~ n_2\left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+		-&~ 2(n_1+n_2) \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_1 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
+\end{align*}
+where the matrix $\cal A$ is
+\begin{align*}
+\cal A :&= \left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2.
+- 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}X_1^\top X_1
+\end{align*}
+Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
+\begin{align*}
+\cal A \succeq - \frac{4d^2}{w^5}(\sqrt{n_2}+\sqrt{p})^4 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](\sqrt{n_1}-\sqrt{p})^4 - 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}(\sqrt{n_1}+\sqrt{p})^2\succ 0,
+\end{align*}
+as long as
+$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{(n_1+n_2)(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
+Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$.
+
+Then we consider the case $w\le 1$. Taking derivative of $\val(w)$ with respect to $w$, we obtain that
+\begin{align}
+	\val'(w) &\le n_1 \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& + n_2\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+			& = n_1 \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
+\end{align}
+where the matrix $\cal B$ is
+$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2.$$
+Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
+\begin{align*}
+\cal B \preceq - 2(1-w)\kappa^2(\sqrt{n_2}-\sqrt{p})^4 +2d^2 w\frac{n_2}{n_1}(\sqrt{n_1}+\sqrt{p})^4 \prec 0,
+\end{align*}
+as long as
+$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{n_2(\sqrt{n_1}+\sqrt{p})^4}{n_1(\sqrt{n_2}-\sqrt{p})^4}.$$
+Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly increasing for $w<w_2$. Hence we must have $\hat w\le w_2$. Note that under our assumptions, we have $w_2=1-\OO(p^{-1})$.
+\end{proof}
 

### 2020-05-14 writeup/transfer.tex
sec 3.1

@@
 
-\subsection{Model Distance}
+\subsection{Task Model Similarities}
 
@@
 	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
-	For the task models, suppose that $\beta_t$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_s - \beta_t$ also has i.i.d. entries with mean $0$ and variance $d^2$.
-	We have $n = c \cdot p$ data points from each task.
+	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
+	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
 
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the example described above, assume that $c > 50$ is a fixed constant.
+	In the example described above, assume that $c > 100$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
-		\item If ${p\cdot d^2}/{\sigma^2} < \frac 1 4 \frac{(2c-1)^2}{(c-1)c^2} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{(2c-1)^2}{(c-1)c^2} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${p\cdot d^2}/{\sigma^2} < \frac 2 3 \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac 3 2 \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 
-We obtain the following insight from Proposition \ref{prop_dist_transition}.
-First, adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
-On the other hand, model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
-Hence, the type of transfer is determined by the trade-off between the bias caused by model shift and the reduction of variance.
+The proof of Proposition \ref{prop_dist_transition} involves two parts.
+First, adding the source task has a positive effect of reducing the variance of the estimator, which scales with $n_1 = c_1 p$, the number of source task data points.
+Second, the difference between task models $\beta_1$ and $\beta_2$ introduces an additional bias term, which scales with $pd^2$, the distance between $\beta_1$ and $\beta_2$.
+Hence, the type of transfer is determined by the trade-off between model shift bias and the reduction of variance.
+The proof can be found in Appendix \ref{app_proof_31}, which is based on our main result described later in Theorem \ref{thm_model_shift}.
 
@@
 
-\subsection{Data Ratio}
+\textbf{Implications.} \todo{add connection to tasksonomy}
 
-\subsection{Covariate Shift}
+\subsection{Data Efficiency}
+
+\subsection{Covariance Alignment}
 

### 2020-05-15 writeup/transfer.tex
3.2

@@
 
-\subsection{Task Model Similarities}
+\subsection{Task Model Similarities versus Noise}
 
@@
 
-\textbf{Example.}
+\begin{example}\label{ex_basic}
 	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
@@
 	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
+\end{example}
 
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the example described above, assume that $c > 100$ is a fixed constant.
+	In the setting of Example \ref{ex_basic}, assume that $c > 100$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
-		\item If ${p\cdot d^2}/{\sigma^2} < \frac 2 3 \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac 3 2 \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 
+\begin{example} \todo{Add transfer from low accuracy to high accuracy}
+\end{example}
+
 \textbf{Implications.} \todo{add connection to tasksonomy}
 
-\subsection{Data Efficiency}
+\subsection{Data Size and Efficiency}
+
+In classical Rademacher or VC based theory of multi-task learning, adding more labeled data improves the generalization performance of a model.
+On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
+Using Example \ref{ex_basic}, we analyze the effect of varying the source task data size.
+
+\begin{proposition}\label{prop_data_size}
+	In the setting of Example \ref{ex_basic}, assume that $c_1 > ??$ and $c_2  > ??$ are fixed constants.
+	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
+	\begin{itemize}
+		\item If $d^2 < \frac{\sigma^2}{(c_2 - 1) p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
+		\item If $d^2 > \frac{\sigma^2}{(c_2 - 1) p}$, then we have the following transition depending on $c_1$:
+		\begin{itemize}
+			\item If $?? < c_1 < \frac{c_2 \sigma^2}{(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+			\item If $c_1 > \frac{c_2 \sigma^2}{(c_2 - 1)p d^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\end{itemize}
+	\end{itemize}
+	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
+\end{proposition}
 

### 2020-05-15 writeup/proof_transfer_ex.tex
sec 3.1
A.2
update

@@
 
-\subsection{Proof of Proposition \ref{prop_dist_transition}}
+\subsection{Proof of Proposition \ref{prop_dist_transition}}\label{app_proof_31}
 
@@
 \end{proof}
+
+\subsection{Proof of Proposition \ref{prop_data_size}}
+
+\subsection{Proof of ???}
+Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
+
+\paragraph{A precise bound when there is no model shift.}
+As Proposition \ref{prop_monotone} shows, if $\beta_s$ and $\beta_t$ are equal, then adding the source task dataset always helps learn the target task.
+The goal of this section is to understand how covariate shift affects the rate of transfer. \todo{add conceptual msg}
+
+%The key quantity is to look at:
+%The estimator using the source and target together from minimizing \eqref{eq_mtl_basic} is
+%\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
+%The estimation error of $\hat{\beta}_{s,t}$ is
+%\begin{align}\label{eq_two_task}
+%  \err(\hat{\beta}_{s,t}) = \sigma^2 \cdot \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}].
+%\end{align}
+%The estimation error using the target alone is
+%\begin{align}\label{eq_target_task}
+%	\err(\hat{\beta}_t) = \sigma^2 \cdot \tr[(X_2^{\top} X_2)^{-1}].
+%\end{align}
+%The improvement of estimation error from adding the source task is then given by
+%$\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})$.
+%For the test error on the target task, the improvement from adding the source task is
+%\[ \te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t}) = \sigma^2\cdot\bigtr{\bigbrace{(X_2^{\top}X_2)^{-1} - (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}\cdot\Sigma_2}. \]
+
+%We calculate the amount of improvement by comparing equation \eqref{eq_two_task} to equation \eqref{eq_target_task}.
+A simple observation here is that when $\beta_s = \beta_t$, the optimal $\hat{w}$ for minimizing equation \eqref{eq_te_mtl} is equal to $1$.
+Based on this observation, we can get a more precise result than Theorem \ref{thm_model_shift} on the improvement of adding the source task data that only depends on the covariance matrices $\Sigma_1, \Sigma_2$ and the number of data points $n_1, n_2$.
+
+\begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
+Suppose $\beta_s = \beta_t$ and $\|\beta_t\|_2^2\sim p\sigma^2$ (i.e.
+the $l^2$-norm of the vector $\beta_t$ is of the same order as that of the error vector).
+Assume that the condition numbers of $\Sigma_1$, $\Sigma_2$ and $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all bounded by a constant $C>0$.
+Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies
+	$$1\le \hat{w} \le 1+\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
+	%where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+Moreover, we have
+	\begin{align}\label{tehatw1}
+		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
+		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1 M^\top M  + (n_1 + n_2)a_2\id}^{-1}} \cdot \left(1+ \bigo{p^{-1}}\right),
+	\end{align}
+where $a_1, a_2$ are the solutions to equations \eqref{eq_a2}. %\cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
+\end{proposition}
+
+\begin{proof}
+We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
+Note that $\val(w)\le \val(-w)$ for $w\ge 0$.
+Hence we have $\hat w\ge 0$.
+Moreover, we notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
+Thus we have $\hat w\ge 1$.
+It suffices to consider the case with $w> 1$.
+Under the assumption on $\beta_s$ and $\beta_t$, we can write
+\begin{align}
+	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
+			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
+\end{align}
+Since
+\begin{align*}
+&\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \\
+&= \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]
+\end{align*}
+is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
+\begin{align*}
+\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
+			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
+\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}.
+			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
+\end{align*}
+Hence $\val'(w)\ge 0$ if $w>1+ \e_0$, where
+$$\e_0:= \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2}.$$
+In other words, $\val(w)$ is strictly increasing function on $[1+\e_0,\infty]$. Thus we get that $\hat w$ satisfies
+\be\label{hatw1}1\le w \le 1+\e_0.\ee Using \eqref{eq_isometric}, we get that
+$$\e_0=\OO(\sigma^2/\|\beta_t\|_2^2)=\OO(p^{-1}).$$
+
+Finally, plugging \eqref{hatw1} into the expression $\te(\hat{\beta}^{\TL}_{t}) $, we obtain \eqref{tehatw1}.
+%$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$
+\end{proof}
+
+As a remark, we see that Proposition \ref{prop_monotone} follows from Theorem \ref{thm_cov_shift}.
+The amount of reduction on test error for the target task is given as
+	\begin{align*}
+%		\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})
+%		&= \sigma^2 p \cdot \bigtr{\frac 1 {(n_2 - p) \Sigma_2} - \frac 1 {(n_1 + n_2)a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2}}, \\
+		\te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t})
+		&= \sigma^2 \cdot \bigbrace{\frac p {n_2 - p} -  \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}}}.
+	\end{align*}
+Because
+\begin{align*}
+	\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)
+	\Leftarrow~ & (n_2 - p)\Sigma_2 \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2 \\
+	\Leftrightarrow~ & \zeroMatrix \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 - (n_1 + n_2)\cdot a_1) \Sigma_2,
+\end{align*}
+which is true since $a_1 \le n_1 / (n_1 + n_2)$ by equation \eqref{eq_a2}.
+The proof for $\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)$ follows by multiplying $\Sigma_2^{-1/2}$ on both sides of the inequalities above.
+
+\medskip

### 2020-05-15 writeup/transfer.tex
edits
update

@@
 
-\subsection{Task Model Similarities versus Noise}
+\subsection{Task Model Similarity versus Noise}
 
@@
 
+\textbf{Implications.}
+
 \subsection{Covariance Alignment}
 
-%\subsubsection{Gains over Single-Task Training}
-
-Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
-
-\paragraph{A precise bound when there is no model shift.}
-As Proposition \ref{prop_monotone} shows, if $\beta_s$ and $\beta_t$ are equal, then adding the source task dataset always helps learn the target task.
-The goal of this section is to understand how covariate shift affects the rate of transfer. \todo{add conceptual msg}
-
-%The key quantity is to look at:
-%The estimator using the source and target together from minimizing \eqref{eq_mtl_basic} is
-%\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
-%The estimation error of $\hat{\beta}_{s,t}$ is
-%\begin{align}\label{eq_two_task}
-%  \err(\hat{\beta}_{s,t}) = \sigma^2 \cdot \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The estimation error using the target alone is
-%\begin{align}\label{eq_target_task}
-%	\err(\hat{\beta}_t) = \sigma^2 \cdot \tr[(X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The improvement of estimation error from adding the source task is then given by
-%$\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})$.
-%For the test error on the target task, the improvement from adding the source task is
-%\[ \te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t}) = \sigma^2\cdot\bigtr{\bigbrace{(X_2^{\top}X_2)^{-1} - (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}\cdot\Sigma_2}. \]
-
-%We calculate the amount of improvement by comparing equation \eqref{eq_two_task} to equation \eqref{eq_target_task}.
-A simple observation here is that when $\beta_s = \beta_t$, the optimal $\hat{w}$ for minimizing equation \eqref{eq_te_mtl} is equal to $1$.
-Based on this observation, we can get a more precise result than Theorem \ref{thm_model_shift} on the improvement of adding the source task data that only depends on the covariance matrices $\Sigma_1, \Sigma_2$ and the number of data points $n_1, n_2$.
-
-\begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
-Suppose $\beta_s = \beta_t$ and $\|\beta_t\|_2^2\sim p\sigma^2$ (i.e.
-the $l^2$-norm of the vector $\beta_t$ is of the same order as that of the error vector).
-Assume that the condition numbers of $\Sigma_1$, $\Sigma_2$ and $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all bounded by a constant $C>0$.
-Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies
-	$$1\le \hat{w} \le 1+\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-	%where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-Moreover, we have
-	\begin{align}\label{tehatw1}
-		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
-		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1 M^\top M  + (n_1 + n_2)a_2\id}^{-1}} \cdot \left(1+ \bigo{p^{-1}}\right),
-	\end{align}
-where $a_1, a_2$ are the solutions to equations \eqref{eq_a2}. %\cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
-\end{proposition}
-
-\begin{proof}
-We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
-Note that $\val(w)\le \val(-w)$ for $w\ge 0$.
-Hence we have $\hat w\ge 0$.
-Moreover, we notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
-Thus we have $\hat w\ge 1$.
-It suffices to consider the case with $w> 1$.
-Under the assumption on $\beta_s$ and $\beta_t$, we can write
-\begin{align}
-	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
-			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
-\end{align}
-Since
-\begin{align*}
-&\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \\
-&= \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]
-\end{align*}
-is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
-\begin{align*}
-\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
-			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
-\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}.
-			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
-\end{align*}
-Hence $\val'(w)\ge 0$ if $w>1+ \e_0$, where
-$$\e_0:= \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2}.$$
-In other words, $\val(w)$ is strictly increasing function on $[1+\e_0,\infty]$. Thus we get that $\hat w$ satisfies 
-\be\label{hatw1}1\le w \le 1+\e_0.\ee Using \eqref{eq_isometric}, we get that
-$$\e_0=\OO(\sigma^2/\|\beta_t\|_2^2)=\OO(p^{-1}).$$
-
-Finally, plugging \eqref{hatw1} into the expression $\te(\hat{\beta}^{\TL}_{t}) $, we obtain \eqref{tehatw1}.
-%$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$
-\end{proof}
-
-As a remark, we see that Proposition \ref{prop_monotone} follows from Theorem \ref{thm_cov_shift}.
-The amount of reduction on test error for the target task is given as
-	\begin{align*}
-%		\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})
-%		&= \sigma^2 p \cdot \bigtr{\frac 1 {(n_2 - p) \Sigma_2} - \frac 1 {(n_1 + n_2)a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2}}, \\
-		\te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t})
-		&= \sigma^2 \cdot \bigbrace{\frac p {n_2 - p} -  \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}}}.
-	\end{align*}
-Because
-\begin{align*}
-	\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)
-	\Leftarrow~ & (n_2 - p)\Sigma_2 \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2 \\
-	\Leftrightarrow~ & \zeroMatrix \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 - (n_1 + n_2)\cdot a_1) \Sigma_2,
-\end{align*}
-which is true since $a_1 \le n_1 / (n_1 + n_2)$ by equation \eqref{eq_a2}.
-The proof for $\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)$ follows by multiplying $\Sigma_2^{-1/2}$ on both sides of the inequalities above.
-
-\medskip
 Now we apply Theorem \ref{thm_cov_shift} to show how covariate shift affects the rate of transfer.
-
-%\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2$}]
-%In this case, we have $\lambda_i = 1$ for all $1\le i\le p$.
-%And $a_1 + a_2 = 1 - p / (n_1 + n_2)$.
-%Hence
-%\[ \te(\hat{\beta}_{s,t}) = \frac{\sigma^2 p^2}{n_1 + n_2 - p} \text{ and } \err(\hat{\beta}_{s,t}) = \frac {\sigma^2 p} {n_1 + n_2 - p} \bigtr{\Sigma_2^{-1}}. \]
-%\end{example}
 
@@
 \begin{figure}
-	\centering
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/scaling.eps}
-		\caption{When $\Sigma_1 = \Sigma_2 / \lambda$.}
-		\label{fig_te_scaling}
-	\end{minipage}\hfill
 	\begin{minipage}{0.48\textwidth}
@@
 \end{figure}
-
-\paragraph{Extending the intuition to the general case.}
-When there is model shift, i.e. $\beta_s = \beta_t$, we can still use Theorem \ref{thm_model_shift} (and Proposition \ref{prop_model_shift_tight}) to get the result.
-\begin{itemize}
-	\item \textbf{The effect of covariate shift:}
-	\item \textbf{The effect of data ratio:}
-\end{itemize}

### 2020-05-15 writeup/transfer.tex
sec 3.1 variance

@@
 	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
+	%The noise level for both tasks is equal to $\sigma > 0$.
 	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the setting of Example \ref{ex_basic}, assume that $c > 100$ is a fixed constant.
+	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c > 100$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
@@
 
-\begin{example} \todo{Add transfer from low accuracy to high accuracy}
-\end{example}
+Consider a more general setting where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
+We derive a sharp transition similar to Proposition \ref{prop_dist_transition}.
+
+\begin{proposition}\label{prop_var_transition}
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, we derive the following transition as a parameter of $\sigma_1$:
+	\begin{itemize}
+		\item If $\sigma_1^2 \le p d^2 \cdot c_1 + \frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > p d^2 \cdot c_1 + \frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{proposition}
 

### 2020-05-16 writeup/proof_transfer_ex.tex
sec 3.1 variance
proof

--- 2020-05-13 writeup/proof_transfer_ex.tex
@@
 	Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as whp
-	\begin{align*}
-		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{c_2 - 1} - \frac{1}{c_1 + c_2}\cdot\frac{1}{a_1\hat{v}^2 + a_2} + \bigo{p^{-1/2+\varepsilon}}} \\
-		&= \sigma^2 \bigbrace{\frac{c_1}{(c_2-1)(c_1 + c_2 -1)} + \bigo{p^{-1/2 + \varepsilon}}},
-	\end{align*}
+	\begin{align}
+		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{c_2 - 1} - \frac{1}{c_1 + c_2}\cdot\frac{1}{a_1\hat{v}^2 + a_2} + \bigo{p^{-1/2+\varepsilon}}} \nonumber\\
+		&= \sigma^2 \bigbrace{\frac{c_1}{(c_2-1)(c_1 + c_2 -1)} + \bigo{p^{-1/2 + \varepsilon}}},\label{Deltavar}
+	\end{align}
 	where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
@@
 		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
-		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}}
+		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
 	\end{align*}
 	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
-	\[ \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{\frac 1 p} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
-\]
+	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
+\ee
 	By solving equations \eqref{eq_a12}, \eqref{eq_a3} and \eqref{eq_a4}, we get
@@
 \end{proof}
+
+\subsection{Proof of Proposition \ref{prop_data_size}}
+
+Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
+\be\label{pos1}\left(pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
+otherwise if
+\be\label{neg1}\left(pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
+then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.
+
+Now we prove the first statement of Proposition \ref{prop_data_size}. Notice that the function
+$$ \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} =(c_2-1) \left(1 +\frac{c_2-2}{c_1}+\frac{1}{c_1(c_1+c_2)}\right)^{-1} $$
+is strictly increasing with respect to $c_1$ as long as $c_2\ge 3$. In particular, for $c_1\ge 100$, we get the bound by taking $c_1\to \infty$:
+$$\frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < 1.1^4 (c_2-1).$$
+ Hence we conclude that for $c_1\ge 100$, we always have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp as long as $pd^2 \le \frac{2\sigma^2}{3(c_2-1)}$. This gives the first statement.
+
+The second statement can be proved in a similar way. Suppose $c_1 \ge 110$ and $pd^2 > \frac{3\sigma^2}{2(c_2-1)}$. If $c_1 > \frac{(c_2-2) \sigma^2}{2(c_2 - 1) pd^2/3 - \sigma^2}$, we have
+\begin{align*}
+ pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac{2}{3} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  >\sigma^2, 
+ \end{align*}
+ where in the first step we used that 
+ $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac23$$
+ for $c_1 \ge 110$.
+This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds.
+On the other hand, if $100\le c_1 \le \frac{(c_2-2) \sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then we have
+ \begin{align*}
+ pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac{3}{2} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  < \sigma^2, 
+ \end{align*}
+ where in the first step we used that 
+ $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac32$$
+ for $c_1 \ge 100$. This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.

### 2020-05-16 writeup/transfer.tex
proof

--- 2020-05-15 writeup/transfer.tex
@@
 \begin{proposition}\label{prop_data_size}
-	In the setting of Example \ref{ex_basic}, assume that $c_1 > ??$ and $c_2  > ??$ are fixed constants.
+	In the setting of Example \ref{ex_basic}, assume that $c_1 \ge 100$ and $c_2  \ge 3$ are fixed constants.
 	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
 	\begin{itemize}
-		\item If $d^2 < \frac{\sigma^2}{(c_2 - 1) p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
-		\item If $d^2 > \frac{\sigma^2}{(c_2 - 1) p}$, then we have the following transition depending on $c_1$:
+		\item If $d^2 < \frac{2\sigma^2}{3(c_2 - 1) p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
+		\item If $d^2 > \frac{3\sigma^2}{2(c_2 - 1) p}$, then we have the following transition depending on $c_1$:
 		\begin{itemize}
-			\item If $?? < c_1 < \frac{c_2 \sigma^2}{(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-			\item If $c_1 > \frac{c_2 \sigma^2}{(c_2 - 1)p d^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+			\item If $100 \le c_1 < \frac{(c_2-2)\sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+			\item If $c_1 > \frac{c_2 \sigma^2}{2(c_2 - 1)p d^2/3 - \sigma^2}$ and $c_1\ge 110$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 		\end{itemize}
@@
 	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
+{\cor (cannot get this because we only have some bounds.
+If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
 \end{proposition}
+
+\textbf{Implications.}
 

### 2020-05-16 writeup/proof_transfer_ex.tex

--- 2020-05-15 writeup/proof_transfer_ex.tex
@@
 
-\subsection{Proof of Proposition \ref{prop_dist_transition}}\label{app_proof_31}
+\subsection{Proof of Proposition \ref{prop_dist_transition} and Proposition \ref{prop_var_transition}}\label{app_proof_31}
 
@@
 \subsection{Proof of Proposition \ref{prop_data_size}}
+
+Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
+\be\label{pos1}\left(pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
+otherwise if
+\be\label{neg1}\left(pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
+then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.
+
+Now we prove the first statement of Proposition \ref{prop_data_size}. Notice that the function
+$$ \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} =(c_2-1) \left(1 +\frac{c_2-2}{c_1}+\frac{1}{c_1(c_1+c_2)}\right)^{-1} $$
+is strictly increasing with respect to $c_1$ as long as $c_2\ge 3$. In particular, for $c_1\ge 100$, we get the bound by taking $c_1\to \infty$:
+$$\frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < 1.1^4 (c_2-1).$$
+ Hence we conclude that for $c_1\ge 100$, we always have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp as long as $pd^2 \le \frac{2\sigma^2}{3(c_2-1)}$. This gives the first statement.
+
+The second statement can be proved in a similar way. Suppose $c_1 \ge 110$ and $pd^2 > \frac{3\sigma^2}{2(c_2-1)}$. If $c_1 > \frac{(c_2-2) \sigma^2}{2(c_2 - 1) pd^2/3 - \sigma^2}$, we have
+\begin{align*}
+ pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac{2}{3} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  >\sigma^2, 
+ \end{align*}
+ where in the first step we used that 
+ $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac23$$
+ for $c_1 \ge 110$.
+This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds.
+On the other hand, if $100\le c_1 \le \frac{(c_2-2) \sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then we have
+ \begin{align*}
+ pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac{3}{2} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  < \sigma^2, 
+ \end{align*}
+ where in the first step we used that 
+ $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac32$$
+ for $c_1 \ge 100$. This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
 

### 2020-05-16 writeup/transfer.tex

--- 2020-05-15 writeup/transfer.tex
@@
 	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
+{\cor (cannot get this because we only have some bounds.
+If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
 \end{proposition}

### 2020-05-16 writeup/proof_transfer_ex.tex
proof

@@
 Then we have that the optimal ratio for $\val(w)$ satisfies
-	$$|\hat w -1|=\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
+	\be\label{hatw_add1}|\hat w -1|=\OO(p^{-1}).\ee
+	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
 \end{lemma}
@@
 
+\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
+
+Under the setting of Proposition \ref{prop_var_transition}, we have
+\begin{align*}
+	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
+			&~ + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)\hat v^2  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1}.
+\end{align*}
+Using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we obtain that
+\begin{align*}
+	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( w-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2})\right)\nonumber \\
+	& + (\sigma_1^2 -\sigma_2^2)\hat v^2  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }.
+\end{align*}
+In the setting of Proposition \ref{prop_var_transition}, we can also obtain that
+$$|\hat w-1|=\OO(p^{-1}).$$
+as in \eqref{hatw_add1}. We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. Thus $\te(\hat{\beta}_t^{\MTL}) $ can be reduced to 
+$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_\beta + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
+where $\Delta_\beta:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has been estimated in \eqref{Deltabeta} and $\Delta_{diff}$ is
+\begin{align*}	
+	\Delta_{diff}:=(\sigma_1^2 -\sigma_2^2) \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+\end{align*}
+Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
+$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
+
+Next we compare $\Delta_{\var}$ with $\Delta_\beta + \Delta_{diff}$.
+Under the condition $d^2 < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, if $\sigma_1^2\le \sigma_2^2$ then we always have that $\Delta_{\vari} > \Delta_{\beta}$ and hence $\te(\hat{\beta}_t^{\MTL})$ is smaller than $\te(\hat{\beta}_t^{\STL})$.
+It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
+If
+\begin{align} 
+&\sigma_2^2  \frac{c_1}{(c_2-1)(c_1 + c_2 -1)}\left(1 + \bigo{p^{-1/2 + \varepsilon}}\right) \label{cond sigma1}\\
+&> \left[\frac{c_1^2 (c_1+c_2)}{(c_1+c_2-1)^3} + \bigo{p^{-1/2 + \varepsilon}}\right]\left[pd^2 \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 + \frac{\sigma_1^2-\sigma_2^2}{c_1} \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2\right] ,\nonumber
+\end{align}
+then we have $\Delta_{\vari} > \Delta_{\beta}$ and we have $\te(\hat{\beta}_t^{\MTL})$ is smaller than $\te(\hat{\beta}_t^{\STL})$.
+For $c_1\ge 100$, we see that \eqref{cond sigma1} is implied by the following condition
+$$\sigma_1^2 \le pd^2 \cdot c_1 + \left[ 1+ \frac23\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \right]\sigma_2^2$$
+as long as $p$ is large enough. On the other hand, if 
+\begin{align} 
+&\sigma_2^2  \frac{c_1}{(c_2-1)(c_1 + c_2 -1)}\left(1 + \bigo{p^{-1/2 + \varepsilon}}\right) \label{cond sigma12}\\
+&< \left[\frac{c_1^2 (c_1+c_2)}{(c_1+c_2-1)^3} + \bigo{p^{-1/2 + \varepsilon}}\right]\left[pd^2 \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 + \frac{\sigma_1^2-\sigma_2^2}{c_1} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\right] ,\nonumber
+\end{align}
+then we have $\Delta_{\vari} < \Delta_{\beta}$ and we have $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$.
+For $c_1\ge 100$, we see that \eqref{cond sigma12} is implied by the following condition
+$$\sigma_1^2 \ge  pd^2 \cdot c_1 + \left[ 1+ \frac32\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \right]\sigma_2^2.$$
+\end{proof}
+
 \subsection{Proof of Proposition \ref{prop_data_size}}
@@
 Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
-\be\label{pos1}\left(pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
+\be\label{pos1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
 otherwise if
-\be\label{neg1}\left(pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
+\be\label{neg1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
 then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.

### 2020-05-16 writeup/transfer.tex
proof

@@
 \begin{proposition}\label{prop_dist_transition}
-	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c > 100$ is a fixed constant.
+	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c_1 > 100$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
-		\item If ${d^2} < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} $, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 \begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, we derive the following transition as a parameter of $\sigma_1$:
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $c_1 > 100$ is a fixed constant and $d^2 < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$.
+Then we derive the following transition as a parameter of $\sigma_1$:
 	\begin{itemize}
-		\item If $\sigma_1^2 \le p d^2 \cdot c_1 + \frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > p d^2 \cdot c_1 + \frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 \le p d^2 \cdot c_1 +\left[1+ \frac23\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right]\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > p d^2 \cdot c_1 +\left[1+ \frac32\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right] \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}

### 2020-05-16 writeup/transfer.tex
prop 3.4

--- 2020-05-16 writeup/transfer.tex
@@
 	\begin{itemize}
-		\item If $d^2 < \frac{2\sigma^2}{3(c_2 - 1) p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
-		\item If $d^2 > \frac{3\sigma^2}{2(c_2 - 1) p}$, then we have the following transition depending on $c_1$:
+		\item If $c_2 < \frac{2\sigma^2}{3p d^2} + 1$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
+		\item If $c_2 > \frac{3\sigma^2}{2p d^2} + 1$, then we have the following transition depending on $c_1$:
 		\begin{itemize}

### 2020-05-17 writeup/transfer.tex
wip

@@
-\section{Illustrative Examples and Their Insights on Transfer}\label{sec_insight}
+\section{Dissecting the Effects of Different Task Data in Multi-Task learning}\label{sec_insight}
 
@@
 	\begin{itemize}
-		\item If $c_2 < \frac{2\sigma^2}{3p d^2} + 1$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
-		\item If $c_2 > \frac{3\sigma^2}{2p d^2} + 1$, then we have the following transition depending on $c_1$:
+		\item If $d^2 < \frac{2\sigma^2}{3p (c_2 - 1)}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
+		\item If $d^2 > \frac{3\sigma^2}{2p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
 		\begin{itemize}
@@
 
-\textbf{Implications.}
+The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}.
+We compare the model shift bias and the amount of reduced variance of $\hat{\beta}_t^{\MTL}$.
+An intuitive interpretation of Proposition \ref{prop_data_size} is that:
+i) If the two task models are sufficiently similar (as specified under the first bullet), adding the source task always provides positive transfer;
+ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.
+
+\textbf{Implications.} We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
+This is formalized by a metric called the data efficiency ratio as follows.
+Given several tasks, let $\alpha$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha$ factor (compared to training independently) while keeping the performance nearly the same.
+We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.
+
+\begin{proposition}\label{prop_data_efficiency}
+\end{proposition}
 

### 2020-05-17 writeup/transfer.tex
wip

@@
 This is formalized by a metric called the data efficiency ratio as follows.
-Given several tasks, let $\alpha$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha$ factor (compared to training independently) while keeping the performance nearly the same.
+Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
+More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
+If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
+\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
 We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.

### 2020-05-17 writeup/proof_transfer_ex.tex
wip

@@
 
+\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
+{\cor (cannot get this because we only have some bounds.
+If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
+
 \subsection{Proof of ???}

### 2020-05-17 writeup/transfer.tex
wip

@@
 	\end{itemize}
-	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
-{\cor (cannot get this because we only have some bounds.
-If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
 \end{proposition}

### 2020-05-17 writeup/transfer.tex
sec 3.2

@@
 ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.
+We leave the proof of Proposition \ref{prop_data_size} to Appendix \ref{app_proof_data}.
 
@@
 \begin{proposition}\label{prop_data_efficiency}
+	In the setting of Example \ref{ex_basic}, assume that $c_1 = c_2 = c > ??$ and $d^2 \le {2\sigma^2} /{(p c)}$.
+	Then the data efficiency ratio is equal to $\frac{1}{2c} + \frac{\sigma^2}{2\sigma^2 - p d^2 c / 2}$.
 \end{proposition}
+Note that we have stated the result assuming that $c_1 = c_2$.
+Similar results can also be obtained when they are different.
+We omit the details.
+The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
 

### 2020-05-17 writeup/technical.tex
wip
tl

@@
-\section{Main Results: A Model Shift Bias versus Variance Trade-off}\label{sec_denoise}
+\section{Technical Tools: Quantifying Model Shift Bias versus Variance Trade-off}\label{sec_main}
 
@@
 For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+
+\section{Extension to Transfer Learning}
+
+We study the transfer function of taskonomy \cite{ZSSGM18}.
+The algorithm is as follows.
+First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
+This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
+Then, we learn the output layer on the target task.
+We use our tools to analyze this setting as follows.

### 2020-05-17 writeup/proof_transfer_ex.tex
sec 3.2
sec 3.3

@@
 
-\subsection{Proof of Proposition \ref{prop_data_size}}
+\subsection{Proof of Proposition \ref{prop_data_size}}\label{app_proof_data}
 
@@
 
-\subsection{Proof of ???}
+\subsection{Proofs of Proposition \ref{prop_covariate}}
+
+	We have that the test error satisfies
+\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
+where $\lambda_p$ is the smallest singular value of $p$ and
+$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
+Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+
+\begin{proof}
+From equation \eqref{eq_a2}, we get
+$$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
+With these two bounds, we can easily conclude \eqref{approxteM}.
+
+For the second statement, we find that we need to minimize
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i},\quad \text{under}\ \ \prod_{i=1}^p\lambda_i=a^p.$$
+Then using AM-GM inequality, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+\end{proof}
+
+\iffalse
 Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
@@
 \medskip
+\fi

### 2020-05-17 writeup/transfer.tex
sec 3.2
sec 3.3

@@
 
-\subsection{Covariance Alignment}
+\subsection{Covariate Shift}
 
-Now we apply Theorem \ref{thm_cov_shift} to show how covariate shift affects the rate of transfer.
+So far we have considered settings where $\Sigma_1 = \Sigma_2$.
+This setting is relevant for multi-class image classification settings, where different tasks share the same input features.
+In general, the covariance matrices of the two tasks may be different, e.g. in text classification.
+In this part, we use our tools to provide a case study on the effect of applying multi-task learning for two tasks when $\Sigma_1 \neq \Sigma_2$.
+
+For this setting, covariate shift is captured by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
+We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
+Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
+Our result shows that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix is equal to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
+On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
+
+\begin{example}
+	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, we assume an upper bound on the scale of $M$.
+	%, because otherwise $aM$ always achieves a smaller error than $M$ for $a>1$. For this purpose, we introduce the following condition
+	Consider the following family of matrices
+	\begin{align*}
+		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{\frac{1}{p}M^\top M} \le \mu}.
+	\end{align*}
+	We assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ has i.i.d. entries with mean $0$ and variance $d^2$.
+%	for some constant $a>0$, and compare different choices of $M$ under this constraint.
+The next proposition shows that, roughly speaking, as long as there are sufficiently many source task datas, then $M=a\id$ always gives (approximately) the smallest test error.
+	The following proposition shows that when $n_1$ is large enough compared to $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized within the family of $\cS_{\mu}$ when $M = \mu\id$.
+\end{example}
+
+\begin{proposition}\label{prop_covariate}
+	In the setting of Example \ref{ex_basic}, assume that $c_1 > ??$.
+	As a parameter of $M \in \cS_{\mu}$, we have that $\te(\hat{\beta}_t^{\MTL})$ is minimized when $M = \mu\id$.
+\end{proposition}
+
+From the above proposition, we see that when $n_1\gg n_2$, we have that the test error is approximately given by $te(M)$ (as long as we impose a proper lower bound on $\lambda_p$).
+Moreover, $te(M)$ is minimized when $\Sigma_1$ and $\Sigma_2$ are proportional to each other, i.e.
+there is no covariate shift between the source task data and target task data.
+This provides a theoretical evidence that in general covariate shift is unfavored in transfer learning if we have enough source task data, although Example \ref{example comple} show that this may not be true when the number of source task data is small.
+
+%then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error. In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$.
 
@@
 
-We can extend the above observation for Example \ref{example comple} to more general cases with arbitrary covariate shift.
-To compare different choices of $M$, we need to fix a scaling for them, because otherwise $aM$ always achieves a smaller error than $M$ for $a>1$.
-For this purpose, we introduce the following condition
-\be\label{GMcons}\det(M^\top M)= a^p \Leftrightarrow \prod_{i=1}^p \lambda_i = a^p\ee
-for some constant $a>0$, and compare different choices of $M$ under this constraint.
-The next proposition shows that, roughly speaking, as long as there are sufficiently many source task datas, then $M=a\id$ always gives (approximately) the smallest test error.
-\begin{proposition}
-We have that the test error satisfies
-\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-where $\lambda_p$ is the smallest singular value of $p$ and
-$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-\end{proposition}
-\begin{proof}
-From equation \eqref{eq_a2}, we get
-$$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
-With these two bounds, we can easily conclude \eqref{approxteM}.
-
-For the second statement, we find that we need to minimize
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i},\quad \text{under}\ \ \prod_{i=1}^p\lambda_i=a^p.$$
-Then using AM-GM inequality, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-\end{proof}
-
-From the above proposition, we see that when $n_1\gg n_2$, we have that the test error is approximately given by $te(M)$ (as long as we impose a proper lower bound on $\lambda_p$).
-Moreover, $te(M)$ is minimized when $\Sigma_1$ and $\Sigma_2$ are proportional to each other, i.e.
-there is no covariate shift between the source task data and target task data.
-This provides a theoretical evidence that in general covariate shift is unfavored in transfer learning if we have enough source task data, although Example \ref{example comple} show that this may not be true when the number of source task data is small.
-
-%then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error. In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$.
-
 \begin{figure}

### 2020-05-17 writeup/proof_transfer_ex.tex
wip

@@
 
+In this case, equations in \eqref{eq_a2} become
+\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2},  \ \ a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
+\ee
+It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. After solving these, we get the test error for the target task as follows.
+\be\label{testcomple}
+te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
+
+In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
+First we notice that the curves in Figure \ref{fig_te_complement} all cross at the point $n_1=n_2$.
+In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
+Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
+$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
+
+Second, we observe the following two phases as we increase $n_1 / p$.
+\begin{itemize}
+	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
+	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
+\end{itemize}
+%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
+$M=\id$ case) when $n_1<n_2$.
+On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
+This phenomenon can be also explained using our theory. With \eqref{compleeq}, we can write
+$$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
+We can compute that
+\begin{align*}
+te(\lambda) - te(1)&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)^2 a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
+\end{align*}
+If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}), and hence $te(\lambda)>te(1)$.
+Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
+
 \iffalse

### 2020-05-17 writeup/transfer.tex
wip

@@
 	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, we assume an upper bound on the scale of $M$.
-	%, because otherwise $aM$ always achieves a smaller error than $M$ for $a>1$. For this purpose, we introduce the following condition
 	Consider the following family of matrices
 	\begin{align*}
-		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{\frac{1}{p}M^\top M} \le \mu}.
+		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{\frac{1}{p}M^\top M} \le \mu, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
 	\end{align*}
-	We assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ has i.i.d. entries with mean $0$ and variance $d^2$.
-%	for some constant $a>0$, and compare different choices of $M$ under this constraint.
-The next proposition shows that, roughly speaking, as long as there are sufficiently many source task datas, then $M=a\id$ always gives (approximately) the smallest test error.
+	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
+	For the task models, we assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ has i.i.d. entries with mean $0$ and variance $d^2$.
 	The following proposition shows that when $n_1$ is large enough compared to $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized within the family of $\cS_{\mu}$ when $M = \mu\id$.
@@
 
-From the above proposition, we see that when $n_1\gg n_2$, we have that the test error is approximately given by $te(M)$ (as long as we impose a proper lower bound on $\lambda_p$).
-Moreover, $te(M)$ is minimized when $\Sigma_1$ and $\Sigma_2$ are proportional to each other, i.e.
-there is no covariate shift between the source task data and target task data.
-This provides a theoretical evidence that in general covariate shift is unfavored in transfer learning if we have enough source task data, although Example \ref{example comple} show that this may not be true when the number of source task data is small.
+Proposition \ref{prop_covariate} shows that when $n_1\gg n_2$, $te(\hat{\beta}_t^{\MTL})$ is minimized when $\Sigma_1$ and $\Sigma_2$ are proportional to each other.
+In other words, there is no covariate shift between the source task data and target task data.
+This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
+To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
 
-%then the choice $M^\top M = a^{1/p}\id $ achieves the smallest test error. In fact, for sufficiently large $n_1$, we have $a_1\approx 1-\gamma$ and $a_2\approx 0$.
-
-\smallskip
-\begin{example}[\textbf{When $\Sigma_1 = \Sigma_2 / \lambda$}]
-In this case, equations \eqref{eq_a2} become
-\[ a_1 + a_2 = 1 - p/(n_1 + n_2), a_1 + \frac{p}{n_1 + n_2} \cdot \frac {a_1} {a_1 + \lambda^2 a_2} = \frac{n_1} {n_1 + n_2}. \]
-By solving these, we can get the test errors (the estimation error behaves similarly).
-Figure \ref{fig_te_scaling} shows how they grow as we increase the number of source task data points.
-Here $n_2 = 4p$ and $n_1$ ranges from $p$ to $20p$.
-We can see that the smaller $\lambda$ is, the lower the test errors will be.
-\end{example}
-
-\smallskip
-\begin{example}[\textbf{When $\Sigma_1$ and $\Sigma_2$ are complementary}]\label{example comple}
+\begin{example}\label{ex_covariate}
 	We now consider another case when $\Sigma_1$ and $\Sigma_2$ have complementary eigenspaces. Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
@@
 Thus for $M$, the first $p/2$ singular values are equal to $\lambda$ and the rest ones are equal to $\lambda^{-1}$.
-In this case, equations in \eqref{eq_a2} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2},  \ \ a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
-\ee
-It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. After solving these, we get the test error for the target task as follows.
-\be\label{testcomple}
-te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
-
-In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
-First we notice that the curves in Figure \ref{fig_te_complement} all cross at the point $n_1=n_2$.
-In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
-$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-
-Second, we observe the following two phases as we increase $n_1 / p$.
-\begin{itemize}
-	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-\end{itemize}
-%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
-$M=\id$ case) when $n_1<n_2$.
-On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-This phenomenon can be also explained using our theory. With \eqref{compleeq}, we can write
-$$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
-We can compute that
-\begin{align*}
-te(\lambda) - te(1)&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)^2 a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-\end{align*}
-If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}), and hence $te(\lambda)>te(1)$.
-Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
-
 \end{example}

### 2020-05-17 writeup/proof_transfer_ex.tex
sec 3.3

@@
 
-\subsection{Proofs of Proposition \ref{prop_covariate}}
+\subsection{Proofs of Proposition \ref{prop_covariate}}\label{app_covariate}
 
@@
 
-In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
 First we notice that the curves in Figure \ref{fig_te_complement} all cross at the point $n_1=n_2$.
@@
 
-Second, we observe the following two phases as we increase $n_1 / p$.
-\begin{itemize}
-	\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-\end{itemize}
 %Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.

### 2020-05-17 writeup/transfer.tex
sec 3.3

@@
 
-\begin{example}
+\begin{example}\label{ex_cov_family}
 	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, we assume an upper bound on the scale of $M$.
@@
 \begin{example}\label{ex_covariate}
-	We now consider another case when $\Sigma_1$ and $\Sigma_2$ have complementary eigenspaces. Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
-$$\Sigma_1^{1/2} = 1+ U\Lambda U^\top, \quad \Sigma_2^{1/2} = 1+ V\Lambda V,$$
-where
-$$\Lambda = \diag(\wt\lambda_1,\cdots, \wt\lambda_{p/2}), \quad U= (u_1,\cdots, u_{p/2}), \quad V= (v_1,\cdots, v_{p/2}).$$
-If $V=U_\perp$, i.e. the vectors $v_1,\cdots, v_{p/2}$ are perpendicular to the vectors $u_1,\cdots, u_{p/2}$, then
-$$M=\Sigma_1^{1/2} \Sigma_2^{-1/2}=(1+\Lambda)UU^\top + (1+\Lambda)^{-1}V V^\top .$$
+	Within the setting of Example \ref{ex_cov_family}, we compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+	For simplicity, we assume that $d = 0$.
+	Hence the two tasks have the same model parameters.
+%	now consider another case when $\Sigma_1$ and $\Sigma_2$ have complementary eigenspaces. Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
+%$$\Sigma_1^{1/2} = 1+ U\Lambda U^\top, \quad \Sigma_2^{1/2} = 1+ V\Lambda V,$$
+%where
+%$$\Lambda = \diag(\wt\lambda_1,\cdots, \wt\lambda_{p/2}), \quad U= (u_1,\cdots, u_{p/2}), \quad V= (v_1,\cdots, v_{p/2}).$$
+%If $V=U_\perp$, i.e. the vectors $v_1,\cdots, v_{p/2}$ are perpendicular to the vectors $u_1,\cdots, u_{p/2}$, then
+%$$M=\Sigma_1^{1/2} \Sigma_2^{-1/2}=(1+\Lambda)UU^\top + (1+\Lambda)^{-1}V V^\top .$$
+%	As a concrete example we consider the case where $\wt \lambda_1=\cdots=\wt\lambda_{p/2}$ and we denote $\lambda:=1+\wt\lambda_1$.
+Thus for $M$, the first $p/2$ singular values are equal to $\lambda$ and the rest ones are equal to $\lambda^{-1}$.
 
-As a concrete example we consider the case where $\wt \lambda_1=\cdots=\wt\lambda_{p/2}$ and we denote $\lambda:=1+\wt\lambda_1$.
-Thus for $M$, the first $p/2$ singular values are equal to $\lambda$ and the rest ones are equal to $\lambda^{-1}$.
+	In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
+	Second, we observe the following two phases as we increase $n_1 / p$.
+	\begin{itemize}
+		\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
+		\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
+	\end{itemize}
 \end{example}
+
+A theoretical justification of Example \ref{ex_covariate} can be found in Appendix \ref{app_covariate}.
 
@@
 \end{figure}
+
+\textbf{Implications.}

### 2020-05-18 writeup/proof_transfer_ex.tex
proof reduce date ratio

@@
 
-\subsection{Proof of Proposition \ref{prop_data_size}}\label{app_proof_data}
+\subsection{Proof of Proposition \ref{prop_data_size} and Proposition \ref{prop_data_efficiency}}\label{app_proof_data}
 
+\begin{proof}[Proof of Proposition \ref{prop_data_size}]
 Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
@@
  for $c_1 \ge 100$. This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
+ \end{proof}
 
@@
 If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
+
+\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
+Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=n_2$.
+In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}, and by symmetry it suffices to focus on one of tasks, say task 2.
+Using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, we have that whp,
+\be\label{reduceproof1}
+\begin{split}
+\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{2\al c - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(2)}_{\beta},
+\end{split}
+\ee
+where $ \Delta^{(2)}_{\beta}$ satisfies 
+\be \nonumber
+\bigbrace{1 - \sqrt{\frac{1}{\al c}}}^4 \le \Delta^{(2)}_{\beta} /  \left( pd^2 \cdot \frac{2\al^3 c^3}{(2\al c-1)^3}+ \bigo{p^{1/2+\e}d^2}\right) \le \bigbrace{1 + \sqrt{\frac{1}{\al c}}}^4. 
+\ee
+On the other hand, using Lemma \ref{lem_minv}, we have whp
+\be\label{reduceproof2} 
+\te_2(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{c-1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right).
+\ee
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+
+Now for $c\ge 200$ and $\al \ge 1/2$, we have whp
+\be\label{reduceproof3} \te_2(\hat \beta(\al)) < \sigma^2 \frac{1}{2\al c - 1}+  \frac38 pd^2  \ee
+for large enough $p$. Moreover, if 
+$$\al \ge \al_0:=\frac{1}{2c} + \left(2-\frac{3}{4}c \cdot \frac{pd^2}{\sigma^2} \right)^{-1},$$
+we can check from \eqref{reduceproof3} that $\te_2(\hat \beta(\al))  < \te_2(\hat{\beta}_t^{\STL}) $.
+By symmetry, we also have $\te_1(\hat \beta(\al))  < \te_1(\hat{\beta}_t^{\STL}) $.
+Thus we conclude that
+$$\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$$
+for $\al\ge \al_0$, which shows that $\al^*\le \al_0$.
+\end{proof}
 

### 2020-05-18 writeup/transfer.tex
sec 3.3
proof reduce date ratio

@@
 \begin{proposition}\label{prop_data_efficiency}
-	In the setting of Example \ref{ex_basic}, assume that $c_1 = c_2 = c > ??$ and $d^2 \le {2\sigma^2} /{(p c)}$.
-	Then the data efficiency ratio is equal to $\frac{1}{2c} + \frac{\sigma^2}{2\sigma^2 - p d^2 c / 2}$.
+	In the setting of Example \ref{ex_basic}, assume that $c_1 = c_2 = c \ge 200$ and $d^2 < {8\sigma^2} /{(3p c)}$.
+	Then the data efficiency ratio is at most $\frac{1}{2c} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 c / 4}$.
 \end{proposition}
@@
 \begin{proposition}\label{prop_covariate}
-	In the setting of Example \ref{ex_basic}, assume that $c_1 > ??$.
+	In the setting of Example \ref{ex_basic}, assume that $d^2 < \sigma^2 / (c_1 p)$ and $c_1 > ??$.
 	As a parameter of $M \in \cS_{\mu}$, we have that $\te(\hat{\beta}_t^{\MTL})$ is minimized when $M = \mu\id$.

### 2020-05-18 writeup/technical.tex
sec 4 wip

@@
 
-In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
-We achieve this through tight generalization bounds obtained from random matrix theory.
-For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
+%In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
+%We achieve this through tight generalization bounds obtained from random matrix theory.
+%For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
+We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
+Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
+The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
+We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
+We compare it with the asympotic limit of $\te(\hat{\beta}_t{\STL})$, for settings where the target data size is limited.
+We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.
+
+\subsection{Two Tasks with General Covariance Matrices}
 
@@
 
-\subsection{Extension to Many Tasks of the Same Covariates}
+\subsection{Many Tasks with the Same Covariates}
 

### 2020-05-18 writeup/proof_technical.tex
sec 3.1
wip

@@
 \section{Supplementary Materials for Section \ref{sec_main}}
+
+Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+Denote by ${\lambda}_1\ge {\lambda}_2 \ge \dots \ge {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
+Let $(a_1, a_2)$ be the solutions to the following system of equations
+	\be
+		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}.\label{eq_a2} \\
+		 \ee
+		 After obtaining $(a_1,a_2)$, we can solve the following linear equations to get $(a_3,a_4)$:
+\begin{gather}
+		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
+		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
+		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
+		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
+	\end{gather}
+Then we introduce the following matrix
+$$Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top},$$
+which can be regarded as the asymptotic limit of $\hat w \Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}$. Finally we introduce
+$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
+{\cor may be able to get a better bound, but the statement will be long}
+
+We now state our main result for two tasks with both covariate and model shift in the following theorem.
+
+\begin{theorem}\label{thm_model_shift}
+	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
+	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
+	%Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+	%Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
+	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
+	With high probability we have
+	\begin{align}
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
+	\end{align}
+	where
+	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
+		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t).
+	\end{align*}
+\end{theorem}
 

### 2020-05-18 writeup/technical.tex
wip

@@
 
-Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-Denote by ${\lambda}_1\ge {\lambda}_2 \ge \dots \ge {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
-Let $(a_1, a_2)$ be the solutions to the following system of equations
-	\be
-		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}.\label{eq_a2} \\
-		 \ee
-		 After obtaining $(a_1,a_2)$, we can solve the following linear equations to get $(a_3,a_4)$:
-\begin{gather}
-		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
-		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
-		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
-		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
-	\end{gather}
-Then we introduce the following matrix
-$$Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top},$$
-which can be regarded as the asymptotic limit of $\hat w \Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}$. Finally we introduce
-$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
-{\cor may be able to get a better bound, but the statement will be long}
-
-We now state our main result for two tasks with both covariate and model shift in the following theorem.
-
-\begin{theorem}\label{thm_model_shift}
-	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
-	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
-	%Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-	%Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
-	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
-	With high probability we have
-	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
-	\end{align}
-	where
-	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
-		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t).
-	\end{align*}
-%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
-%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
-%	Otherwise, the two bounds has to be written into the form
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
-%	\end{align*}
-%	and
-%	\begin{align*}
-%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
-%	\end{align*}
-%	}
-\end{theorem}
-
 Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.

### 2020-05-18 writeup/technical.tex

@@
 
-Recall that the test error of $\hat{\beta}_{t}^{\MTL}$ consists of two parts
+For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
 \begin{align}
-	\te(\hat{\beta}_t^{\MTL}) = \hat{w}^2 \bignorm{\Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{w}\beta_t)}^2 + \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}.
-\label{eq_te_model_shift}
+	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
+	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
 \end{align}
-It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$ (following the argument of Proposition \ref{prop_monotone}), i.e.
-\[ \sigma^2\cdot \bigtr{(\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \sigma^2\cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
-Because of model shift however, i.e. $\beta_s \neq \beta_t$.
-We can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
-The main result of this part show deterministic conditions under which we get positive or negative transfer.
-And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
-In order to characterize $\te(\hat{\beta}_t^{\MTL})$ and $\te(\hat{\beta}_t^{\STL})$, the technical crux of our approach relies on deriving the limit of the trace of matrix inverse in the high-dimensional setting.
-To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
-\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
-We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
-\todo{write a brief technical overview}
+where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
+It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
+\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
+Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
+%The main result of this section show deterministic conditions under which we get positive or negative transfer.
+%And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
+The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
+A key highlight of our approach implies a precise limit on $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}$, which only depends on $\Sigma_1, \Sigma_2$ and $n_1, n_2$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
 
-Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
+\begin{theorem}\label{thm_main_informal}
+	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
+	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1 > ??$ and $c_2 > 3$ are fixed constants.
+	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depends on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
+	\begin{itemize}
+		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te{\hat{\beta}_t^{\MTL}} < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{theorem}
+
+Theorem \ref{thm_main_informal} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
 The bounds get tighter and tighter as $n_1 / p$ increases.

### 2020-05-18 writeup/technical.tex
sec 4.2

@@
 	\begin{itemize}
-		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te{\hat{\beta}_t^{\MTL}} < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
 		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
@@
 
-In this section we consider the setting with $k$ many that have the same covariates.
-Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+We extend the above result to any number of tasks that have the same covariates.
+%In this section we consider the setting with $k$ many that have the same covariates.
+Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
+We derive the model shift bias and variance in the following result.
+
+\begin{theorem}\label{thm_many_tasks}
+	Let $n = c \cdot p$.
+	Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $B^{\star}\Sigma B^{\star}$, where $U_r\in\real^{k\times r}$.
+	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
+	We have the following
+	\begin{itemize}
+		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} \ge \norm{\Sigma (B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} < \norm{\Sigma(B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{theorem}
+As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$, for any $1 \le i \le k$.
+Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$.
+The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-05-18 writeup/proof_technical.tex

@@
 \section{Supplementary Materials for Section \ref{sec_main}}
+
+%To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
+%\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
+%We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
+%\todo{write a brief technical overview}
 
@@
 
-\subsection{Proof of Theorem ???}
+\subsection{Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_many_tasks}
 
-\paragraph{Extension to Many Tasks of the Same Covariates}
+%In this section we consider the setting with $k$ many that have the same covariates.
+%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
 
-In this section we consider the setting with $k$ many that have the same covariates.
-Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-
-Concretely we will consider the following problem.
+For this setting, the problem reduces to the following.
 \begin{align}
@@
 \end{align}
+In order to prove Theorem \ref{thm_many_tasks}, we will derive a closed form solution for equation \eqref{eq_mtl_same_cov}.
+
+\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
 	By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
@@
 
-\paragraph{Jointly minimizing over all tasks.}
 	Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
@@
 	Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
-Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
+	Let us denote $Q = Z^{\top} (ZZ^{\top})^{-1} Z \in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
 	Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
@@
 	\begin{align*}
-	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
+		\val(\hat{B}; W_1, \dots, W_k) = \bignormFro{\Sigma^{1/2} \bigbrace{B^{\star} Q - B^{\star}}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
 	\end{align*}
-From the above we can solve for $Q$ optimally as \todo{this}.
-
-\paragraph{Minimizing over the target task alone.}
-If we only minimize over the the validation loss for the target task, we shall get the following.
+	From the above we can solve for $Q$ optimally as $U_{r}U_r^{\top}$.
+	Furthermore, we can solve $\hat{\beta}_i^{\MTL}$ as $B^{\star} U_r U_r(i)$.
+	Now we get that
 	\begin{align*}
-	\val_j(\hat{B} W_j) = \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
-	+ \sigma^2 \cdot W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
+		+ \sigma^2  W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(i)}}^2 + \sigma^2\norm{U_r(i)}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
 	\end{align*}
-
-From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
-\begin{itemize}
-	\item The de-noising effect of multi-task learning.
-	\item Multi-task training vs single-task training can be either positive or negative.
-	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
-\end{itemize}
+	By using Lemma \ref{lem_minv}, we conclude the proof.
+\end{proof}
+%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
+%\begin{itemize}
+%	\item The de-noising effect of multi-task learning.
+%	\item Multi-task training vs single-task training can be either positive or negative.
+%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
+%\end{itemize}

### 2020-05-19 writeup/proof_transfer_ex.tex
sec 4.1
sec 4.2
add

@@
 
-\subsection{Proofs of Proposition \ref{prop_covariate}}\label{app_covariate}
+\subsection{Proofs of Proposition \ref{prop_covariate} and Theoretical justification of Example \ref{ex_covariate}}\label{app_covariate}
+
+\begin{proof}[Proof of Proposition \ref{prop_covariate}]
 
@@
 
-\begin{proof}
 From equation \eqref{eq_a2}, we get
@@
 
-In this case, equations in \eqref{eq_a2} become
+\begin{proof}[Theoretical justification of Example \ref{ex_covariate}]
+In the setting of Example \ref{ex_covariate}, equations in \eqref{eq_a2} become
 \be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2},  \ \ a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
@@
 Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
+\end{proof}
 

### 2020-05-19 writeup/transfer.tex
add

@@
 	\begin{align*}
-		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{\frac{1}{p}M^\top M} \le \mu, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
+		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
 	\end{align*}
@@
 	For the task models, we assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ has i.i.d. entries with mean $0$ and variance $d^2$.
-	The following proposition shows that when $n_1$ is large enough compared to $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized within the family of $\cS_{\mu}$ when $M = \mu\id$.
+	The following proposition shows that when $n_1$ is large enough compared to $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized approximately within the family of $\cS_{\mu}$ when $M = \mu\id$.
 \end{example}
@@
 	In the setting of Example \ref{ex_basic}, assume that $d^2 < \sigma^2 / (c_1 p)$ and $c_1 > ??$.
-	As a parameter of $M \in \cS_{\mu}$, we have that $\te(\hat{\beta}_t^{\MTL})$ is minimized when $M = \mu\id$.
+	As a parameter of $M \in \cS_{\mu}$, we have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M$ satisfies that 
+$$ (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \inf_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) + {\cor\text{some errors}}.$$	
+	%is minimized when $M = \mu\id$.
 \end{proposition}

### 2020-05-19 writeup/transfer.tex
wip

--- 2020-05-17 writeup/transfer.tex
@@
 \begin{figure}
+	\begin{subfigure}[b]{0.31\textwidth}
 		\centering
-	\includegraphics[width=0.5\textwidth]{figures/model_shift_phase_transition.eps}
-	\caption{Positive vs negative transfer as a parameter of the task model distances.}
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\caption{Task model similarity}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.31\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\caption{Source task noise level}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.31\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\caption{\# Source task datapoints}
+	\end{subfigure}
+	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer as a parameter of: (a) Task model similarities (Proposition \ref{prop_dist_transition}); (b) Source task noise level (Proposition \ref{prop_var_transition}); (c) Source task datapoints (Proposition \ref{prop_data_size}).}
 	\label{fig_model_shift_phasetrans}

### 2020-05-19 writeup/proof_transfer_ex.tex
revise

@@
-\section{Supplementary Materials for Section \ref{sec_insight}}
+\section{Supplementary Materials for Section \ref{sec_insight}}\label{app_proof_main}
 
@@
 The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.
+
 \begin{lemma}\label{lem_minv}[\todo{ref?}]
@@
 The second lemma, which deals the inverse of the sum of two random matrices, can be viewed as a special case of Theorem \ref{thm_model_shift}.
+
 \begin{lemma}\label{lem_cov_shift}
@@
 $$ \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} =(c_2-1) \left(1 +\frac{c_2-2}{c_1}+\frac{1}{c_1(c_1+c_2)}\right)^{-1} $$
-is strictly increasing with respect to $c_1$ as long as $c_2\ge 3$. In particular, for $c_1\ge 100$, we get the bound by taking $c_1\to \infty$:
-$$\frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < 1.1^4 (c_2-1).$$
- Hence we conclude that for $c_1\ge 100$, we always have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp as long as $pd^2 \le \frac{2\sigma^2}{3(c_2-1)}$. This gives the first statement.
+is strictly increasing with respect to $c_1$ as long as $c_2\ge 3$. In particular, by taking $c_1\to \infty$, we get the bound:
+$$\frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  (c_2-1) \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.$$
+ Hence we conclude that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp as long as 
+ $$pd^2 +\oo(1) \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^{-4}\frac{\sigma^2}{c_2-1} .$$ 
+ This gives the first statement by taking $c_1 > a$.
 
-The second statement can be proved in a similar way. Suppose $c_1 \ge 110$ and $pd^2 > \frac{3\sigma^2}{2(c_2-1)}$. If $c_1 > \frac{(c_2-2) \sigma^2}{2(c_2 - 1) pd^2/3 - \sigma^2}$, we have
+The second statement can be proved in a similar way. Suppose $c_1 > a$ and 
+$pd^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{c_2-1}$. If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, we have
 \begin{align*}
- pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac{2}{3} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  >\sigma^2, 
+ & pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4  \\
+ &>  \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \left( 1-\frac{1}{(c_1+c_2-2)^2}\right)\cdot \frac{ pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  >\sigma^2\cdot (1+\oo(1)) , 
  \end{align*}
  where in the first step we used that 
- $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac23$$
- for $c_1 \ge 110$.
+ $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}   > 1-\frac{1}{(c_1+c_2-2)^2}.$$
 This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds.
-On the other hand, if $100\le c_1 \le \frac{(c_2-2) \sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then we have
+On the other hand, if $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then we have
  \begin{align*}
- pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac{3}{2} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  < \sigma^2, 
+ pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 \cdot \frac{pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  < \sigma^2\cdot (1-\oo(1)).
  \end{align*}
- where in the first step we used that 
- $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac32$$
- for $c_1 \ge 100$. This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
+ This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
  \end{proof}
@@
 
-	We have that the test error satisfies
+......... We have that the test error satisfies
 \be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
@@
 $$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
-With these two bounds, we can easily conclude \eqref{approxteM}.
+With these two bounds, we can easily conclude \eqref{approxteM}. Then solving equations \eqref{eq_a3} and \eqref{eq_a4}, we get that
+\begin{align*}
+a_3= \frac{ \frac{1}{n_2}\sum_{i=1}^p \frac{a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) +\left( \frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) } {\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} ,
+\end{align*}
+\begin{align*}
+a_4= \frac{\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }}{\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} ,
+\end{align*}
 

### 2020-05-19 writeup/transfer.tex
fig 2
revise

--- 2020-05-19 writeup/transfer.tex
@@
 \begin{proposition}\label{prop_data_size}
-	In the setting of Example \ref{ex_basic}, assume that $c_1 \ge 100$ and $c_2  \ge 3$ are fixed constants.
-	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
+	In the setting of Example \ref{ex_basic}, assume that $c_2  \ge 3$ is fixed and $c_1 > a$ for some fixed integer $a$.	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
 	\begin{itemize}
-		\item If $d^2 < \frac{2\sigma^2}{3p (c_2 - 1)}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
-		\item If $d^2 > \frac{3\sigma^2}{2p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
+\item If $d^2 \le (1 + a^{-1/2})^{-4}\frac{\sigma^2}{p(c_2-1)}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+
+\item If $d^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
 		\begin{itemize}
-			\item If $100 \le c_1 < \frac{(c_2-2)\sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-			\item If $c_1 > \frac{c_2 \sigma^2}{2(c_2 - 1)p d^2/3 - \sigma^2}$ and $c_1\ge 110$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+			\item If $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+			\item If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 		\end{itemize}
@@
 	As a parameter of $M \in \cS_{\mu}$, we have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M$ satisfies that 
-$$ (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \inf_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) + {\cor\text{some errors}}.$$	
+$$ (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ {\cor\text{some errors}}\right]\cdot\inf_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) .$$	
 	%is minimized when $M = \mu\id$.

### 2020-05-19 writeup/transfer.tex

@@
 \begin{figure}
+	\begin{subfigure}[b]{0.31\textwidth}
 		\centering
-	\includegraphics[width=0.5\textwidth]{figures/model_shift_phase_transition.eps}
-	\caption{Positive vs negative transfer as a parameter of the task model distances.}
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\caption{Task model similarity}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.31\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\caption{Source task noise level}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.31\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
+		\caption{\# Source task datapoints}
+	\end{subfigure}
+	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer as a parameter of: (a) Task model similarities (Proposition \ref{prop_dist_transition}); (b) Source task noise level (Proposition \ref{prop_var_transition}); (c) Source task datapoints (Proposition \ref{prop_data_size}).}
 	\label{fig_model_shift_phasetrans}

### 2020-05-19 writeup/proof_transfer_ex.tex
proof

@@
 \begin{proof}[Proof of Proposition \ref{prop_covariate}]
+Let 
+$$M_0:=\argmin_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M).$$ 
+We now calculate $(\te(\hat{\beta}_t^{\MTL}))(M_0)$. In this case, as in Lemma \ref{lem_hat_v} we also have that 
+\be\label{hatvM}|\hat v-1|=\OO(p^{-1}) \ee 
+in the setting Proposition \ref{prop_covariate}.
+In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $\lambda(M)\in [\mu_{\min},\mu_{\max}]$.
+We omit the details here.
 
-......... We have that the test error satisfies
-\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-where $\lambda_p$ is the smallest singular value of $p$ and
-$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+Now using \eqref{hatvM}, Lemma \ref{lem_cov_shift} and Lemma \ref{prop_model_shift_tight}, we get that whp,
+\begin{align*}
+(\te(\hat{\beta}_t^{\MTL}))(M_0)= \frac{\sigma^2}{c_1+c_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0 + a_2}\right)  + \Delta_\beta(M_0),
+\end{align*}
+where  $ \Delta_{\beta}(M_0)$ satisfies 
+\be \nonumber
+\begin{split}
+&\left| \Delta_{\beta}(M_0) - \frac{d^2\cdot c_1^2}{(c_1 + c_2)^2} \tr\left[{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\right]\right| \\
+&\le \left(\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4-1\right)\left( \frac{c_1\mu_{\max}}{(\sqrt{c_1}-1)^2 \mu_{\min} + (\sqrt{c_2}-1)^2}\right)^2 \cdot d^2\tr\left(\Sigma_1\right). 
+\end{split}
+\ee
+From equation \eqref{eq_a2}, we get
+$$a_1\ge \frac{c_1-1}{c_1+c_2},\quad a_2\le \frac{c_2}{c_1+c_2}.$$
+Then solving equations \eqref{eq_a3} and \eqref{eq_a4}, we get that
+\begin{align*}
+0\le a_3&= \frac{ \frac{1}{n_2}\sum_{i=1}^p \frac{a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) +\left( \frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) } {\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} \\
+&\le \frac{c_2^{-1}}{1-c_1^{-1}-c_2^{-1}}
+\end{align*}
+and
+\begin{align*}
+0\le a_4&= \frac{\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }}{\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} \\
+&\le  \frac{c_1^{-1}\cdot \mu_{\min}^{-2}}{1-c_1^{-1}-c_2^{-1}},
+\end{align*}
+where we also used that 
+$$\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)^2 \le \sum_{i=1}^p \frac{\lambda_i^4 }{  (a_2 + \lambda_i^2a_1)^2  }\cdot \sum_{i=1}^p \frac{1}{  (a_2 + \lambda_i^2a_1)^2  }$$
+by Cauchy-Schwarz inequality.
 
-From equation \eqref{eq_a2}, we get
-$$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
-With these two bounds, we can easily conclude \eqref{approxteM}. Then solving equations \eqref{eq_a3} and \eqref{eq_a4}, we get that
-\begin{align*}
-a_3= \frac{ \frac{1}{n_2}\sum_{i=1}^p \frac{a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) +\left( \frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) } {\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} ,
-\end{align*}
-\begin{align*}
-a_4= \frac{\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }}{\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} ,
-\end{align*}
+Combining the above estimates, we get that 
+\begin{align}\label{approximateteM}
+(\te(\hat{\beta}_t^{\MTL}))(M_0) =  \te(M_0) + \cal E,
+\end{align}
+where
+$$\te(M_0):=\frac{\sigma^2}{c_1+c_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0}\right)  +\frac{d^2\cdot c_1^2}{(c_1 + c_2)^2} \tr\left(\frac{1 + a_3}{a_1^2 M_0^{\top}{M_0}} \right),$$
+and the error satisfies
+$$|\cal E|\le C\left( \frac{c_2}{c_1} +c_1^{-1/2}\right)\te(M_0),$$
+Here the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $\|\Sigma_1\|$, but otherwise does not depend on $c_1$ and $c_2$.
 
-For the second statement, we find that we need to minimize
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i},\quad \text{under}\ \ \prod_{i=1}^p\lambda_i=a^p.$$
-Then using AM-GM inequality, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+%With these two bounds, we can easily conclude \eqref{approxteM}. 
+%
+%We have that the test error satisfies
+%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
+%where $\lambda_p$ is the smallest singular value of $p$ and
+%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
+%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+
+Finally using AM-GM inequality, we observe that 
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i}$$
+is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
+$$ \te (M_0)\le \te(\mu \id).$$
+Together with \eqref{approximateteM}, we conclude \eqref{formular_covariate0}.
+%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
 \end{proof}

### 2020-05-19 writeup/transfer.tex
proof

@@
 \begin{proposition}\label{prop_covariate}
-	In the setting of Example \ref{ex_basic}, assume that $d^2 < \sigma^2 / (c_1 p)$ and $c_1 > ??$.
-	As a parameter of $M \in \cS_{\mu}$, we have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M$ satisfies that 
-$$ (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ {\cor\text{some errors}}\right]\cdot\inf_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) .$$	
+	In the setting of Example \ref{ex_basic}, assume that $c_1 > 3$ and $c_2>3$,
+and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. As a parameter of $M \in \cS_{\mu}$, we have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M$ satisfies that 
+\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(c_2c_1^{-1} + c_1^{-1/2}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
+where the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $C_1$, but otherwise does not depend on $c_1$ and $c_2$. 
 	%is minimized when $M = \mu\id$.

### 2020-05-19 writeup/transfer.tex
fig 2

@@
 
-\subsection{Task Model Similarity versus Noise}
+\subsection{Task Model Similarity versus Noise}\label{sec_dist}
 
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
-		\caption{Source task noise level}
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
+		\caption{\# Source task datapoints}
 	\end{subfigure}\hfill
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
-		\caption{\# Source task datapoints}
+		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
+		\caption{Same vs. Diff. covariances}
 	\end{subfigure}
-	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer as a parameter of: (a) Task model similarities (Proposition \ref{prop_dist_transition}); (b) Source task noise level (Proposition \ref{prop_var_transition}); (c) Source task datapoints (Proposition \ref{prop_data_size}).}
+	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer.
+(a) Section \ref{sec_dist}: Task model similarities; (b) Section \ref{sec_data}: Source task noise level; (c) Section \ref{sec_covariate}: \todo{covariate shift}.}
 	\label{fig_model_shift_phasetrans}
@@
 
-\subsection{Data Size and Efficiency}
+\subsection{Data Size and Efficiency}\label{sec_data}
 
@@
 
-\subsection{Covariate Shift}
+\subsection{Covariate Shift}\label{sec_covariate}
 
@@
 
-\begin{figure}
-	\begin{minipage}{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/complementary.eps}
-		\caption{When $\Sigma_1$ and $\Sigma_2$ are complementary. The number of target task data points is $n_2 = 4p$.}
-		\label{fig_te_complement}
-	\end{minipage}
-\end{figure}
+%\begin{figure}
+%	\begin{minipage}{0.48\textwidth}
+%		\centering
+%		\includegraphics[width=0.9\textwidth]{figures/complementary.eps}
+%		\caption{When $\Sigma_1$ and $\Sigma_2$ are complementary. The number of target task data points is $n_2 = 4p$.}
+%		\label{fig_te_complement}
+%	\end{minipage}
+%\end{figure}
 

### 2020-05-19 writeup/technical.tex
reorg

@@
 The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
-
-\section{Extension to Transfer Learning}
-
-We study the transfer function of taskonomy \cite{ZSSGM18}.
-The algorithm is as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
-This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
-Then, we learn the output layer on the target task.
-We use our tools to analyze this setting as follows.

### 2020-05-20 writeup/experiments.tex

\section{Experiments}

\paragraph{A metric to determine when MTL performs better STL.}

\paragraph{When should we align task covariances in MTL.}

### 2020-05-20 writeup/extension_transfer.tex

--- 2020-05-18 writeup/technical.tex
@@
-\section{Technical Tools: Quantifying Model Shift Bias versus Variance Trade-off}\label{sec_main}
-
-%In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
-%We achieve this through tight generalization bounds obtained from random matrix theory.
-%For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
-We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
-One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
-Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
-The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
-We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
-We compare it with the asympotic limit of $\te(\hat{\beta}_t{\STL})$, for settings where the target data size is limited.
-We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.
-
-\subsection{Two Tasks with General Covariance Matrices}
-
-For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
-\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
-	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
-\end{align}
-where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
-It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
-\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
-Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
-%The main result of this section show deterministic conditions under which we get positive or negative transfer.
-%And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
-The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-A key highlight of our approach implies a precise limit on $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}$, which only depends on $\Sigma_1, \Sigma_2$ and $n_1, n_2$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-
-\begin{theorem}\label{thm_main_informal}
-	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
-	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1 > ??$ and $c_2 > 3$ are fixed constants.
-	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depends on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
-	\begin{itemize}
-		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te{\hat{\beta}_t^{\MTL}} < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{theorem}
-
-Theorem \ref{thm_main_informal} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
-The bounds get tighter and tighter as $n_1 / p$ increases.
-
-\subsection{Many Tasks with the Same Covariates}
-
-In this section we consider the setting with $k$ many that have the same covariates.
-Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-
 \section{Extension to Transfer Learning}

### 2020-05-20 writeup/transfer.tex
wip

@@
 		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
-		\caption{\# Source task datapoints}
+		\caption{Data size}
 	\end{subfigure}\hfill
@@
 		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
-		\caption{Same vs. Diff. covariances}
+		\caption{Covariate shift}
 	\end{subfigure}
 	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer.
-(a) Section \ref{sec_dist}: Task model similarities; (b) Section \ref{sec_data}: Source task noise level; (c) Section \ref{sec_covariate}: \todo{covariate shift}.}
+(a) Section \ref{sec_dist}: Task model similarities; (b) Section \ref{sec_data}: Source task noise level; (c) Section \ref{sec_covariate}: \todo{same vs.
+different covariance matrices}.}
 	\label{fig_model_shift_phasetrans}
@@
 
-%\begin{figure}
-%	\begin{minipage}{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.9\textwidth]{figures/complementary.eps}
-%		\caption{When $\Sigma_1$ and $\Sigma_2$ are complementary. The number of target task data points is $n_2 = 4p$.}
-%		\label{fig_te_complement}
-%	\end{minipage}
-%\end{figure}
-
 \textbf{Implications.}

### 2020-05-20 writeup/intro.tex
wip

@@
 
-Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
-Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).
+%Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
+%Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
+In multi-task learning, having related task data is fundamental to its performance.
+Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
+For example, many applications in computer vision \cite{ZSSGM18}, natural language processing \cite{MTDNN19}, and many other areas have been achieved by learning from multiple tasks together.
+In spite of these promising empirical results, multi-task learning is not well-understood because of the prevalence of \textit{negative transfer} -- when the trained multi-task model performs worse than single-task learning for the target task.
+\todo{transition}
+In this work, we present a theoretical study to better understand when multi-task learning works better than single-task learning. % for learning from multiple linear regression tasks.
+%We consider a setting where the target task has limited labeled data and show
+%On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).
 
@@
 \begin{figure}[!t]
+	\centering
 	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}

### 2020-05-20 writeup/extension_transfer.tex
transfer learning

@@
 We use our tools to analyze this setting as follows.
+
+The projection of $\beta_t$ onto the subspace spanned by $(\beta_1,\cdots, \beta_k)$ is 
+$$\hat \beta_t = \sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|} \beta_i .$$
+On the other hand, the single task estimator $\hat\beta_i$ is given by 
+$$\hat \beta_i = \beta_i + (X_i^\top X_i)^{-1}X_i \e_i.$$
+Then the projection of $\beta_t$ onto the subspace spanned by $(\hat\beta_1,\cdots, \hat\beta_k)$ is 
+$$ \hat \beta_t'= \sum_{i=1}^k\frac{\beta_t^\top \hat \beta_i}{\|\hat \beta_i\|} \hat \beta_i .$$
+We now calculate the estimation error $ \exarg{\varepsilon_i, \forall 1\le i\le k} {\|\hat \beta_t - \hat\beta_t'\|^2}.$ Without loss of generality, we assume that $\|\beta_i\|^2 \sim 1$ for all $1\le i \le k$ and $\sigma^2\le n^{-c}$ for some constant $c>0$.
+Then we calculate that
+\begin{align*}
+\|\hat\beta_i\|^2 &= \|\beta_i\|^2 + 2\beta_t^\top\cdot (X_i^\top X_i)^{-1}X_i \e_i + \|(X_i^\top X_i)^{-1}X_i \e_i \|^2 .
+\end{align*}
+We can use concentration of random vector with independent entries, Lemma \ref{largedeviation}, to get that for any $\e>0$,
+\be\label{largebetae}
+\beta_t^\top (X_i^\top X_i)^{-1}X_i \e_i  \le p^{\e/2}\cdot \sigma \left[\beta_t^\top (X_i^\top X_i)^{-1}\beta_t \right]^{1/2}\le \sigma p^{-1/2+\e},  
+\ee
+with high probability, and 
+\be\label{largebetae2}
+\begin{split}
+ \|(X_i^\top X_i)^{-1}X_i \e_i \|^2 - \sigma^2 \tr\left( (X_i^\top X_i)^{-1} \right)   \le p^{\e/2}\cdot \sigma^2 \left\{\tr\left[X_i^\top (X_i^\top X_i)^{-2}X_i\right]^2\right\}^{1/2} \\
+ = p^{\e/2}\cdot \sigma^2 \left[ \tr (X_i^\top X_i)^{-2} \right]^{1/2} \le \sigma^2 p^{-1/2+\e},  
+ \end{split}
+\ee
+with high probability, where we used Theorem \ref{LEM_SMALL} to get that
+$$\beta_t^\top (X_i^\top X_i)^{-1}\beta_t  \le p^{-1+\e/2} \quad \text{and}\quad \tr \left[ (X_i^\top X_i)^{-2} \right]  \le p^{-1+\e/2} \quad \text{whp}.$$
+Thus we get that with high probability,
+\begin{align}
+\|\hat\beta_i\|^2&= \|\beta_i\|^2 + \sigma^2\cdot \tr \left( (X_i^\top X_i)^{-1}\right) +\OO(\sigma p^{-1/2+\e}) \nonumber\\
+&=  \|\beta_i\|^2 + \frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) +\OO(\sigma p^{-1/2+\e}) ,\label{betanormi}
+\end{align}
+where in the second step we used Lemma \ref{lem_minv}.
+
+For simplicity we abbreviate $v_i:=(X_i^\top X_i)^{-1}X_i \e_i$. Then using \eqref{largebetae} and \eqref{betanormi} we can calculate that whp,
+\begin{align*}
+&\|\hat \beta_t - \hat\beta_t'\|^2= \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|} \beta_i - \sum_{i=1}^k\frac{\beta_t^\top (\beta_i + v_i)}{ \|\beta_i +v_i\| }(\beta_i + v_i) \right\|^2 \\
+&=  \left\|\sum_{i=1}^k\left(\frac{\beta_t^\top \beta_i}{\|\beta_i\|}-\frac{\beta_t^\top \beta_i}{\|\beta_i+v_i\|} \right)\beta_i - \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i+v_i\| } v_i - \sum_{i=1}^k\frac{\beta_t^\top v_i}{ \|\beta_i +v_i\| } (\beta_i+v_i) \right\|^2 \\
+%& = \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|}\left(1-\frac{\|\beta_i\|}{(\|\beta_i\|^2 + 2\beta_i^\top v_i + \|v_i\|^2)^{1/2}} \right)\beta_i - \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|+\OO(\sigma^2 + \sigma p^{-1/2+\e}) } v_i\right\|^2 + \OO\left(\sigma^2 p^{-1+2\e}\right) \\
+%&= \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|}\frac{2\beta_i^\top v_i + \|v_i\|^2}{2\|\beta_i\|^2}\beta_i \right\|^2+\left\| \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|} v_i\right\|^2 + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right)
+&= \left\| \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|} v_i\right\|^2 + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right).
+\end{align*}
+Thus taking expectation, we get that 
+\begin{align*}
+\exarg{\varepsilon_i, \forall 1\le i\le k} {\|\hat \beta_t - \hat\beta_t'\|^2}&=   \sum_{i=1}^k\frac{\left|\beta_t^\top \beta_i \right|^2}{ \|\beta_i\|^2 } \cdot \sigma^2 \tr \left( (X_i^\top X_i)^{-1}\right) + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right) \\
+ &= \sum_{i=1}^k\frac{\left|\beta_t^\top \beta_i \right|^2}{ \|\beta_i\|^2 } \cdot \frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) + \OO\left(\sigma^4+\sigma^2 p^{-1/2+2\e}\right) .
+\end{align*}
+Note the first term is of order $\sigma^2$, and hence the second stem is an error term.

### 2020-05-20 writeup/intro.tex

@@
 In this work, we present a theoretical study to better understand when multi-task learning works better than single-task learning. % for learning from multiple linear regression tasks.
+\todo{practical insight}
 %We consider a setting where the target task has limited labeled data and show
@@
 
-\todo{Motivate high-dimensional data.} The technical challenge is to deal with high-dimensional data, in particular when the size of the training set is only a small constant times the feature dimension.
-Prior theory is unable to explain a phase transition that occurs when comparing multi-task learning to single-task learning.
+The technical challenge to develop a theory for multi-task learning is how to capture generalization performance that scales tightly with the amount of labeled data, in particular when the size of the training set is small.
+Prior generalization theory using uniform stability \cite{LTSM16}, Rademacher complexity \cite{BS03,BBCKP10} is unable to explain the phenomenon of negative transfer because there is no tight bound on test error that scales with the amount of labeled data.
 In particular in Figure \ref{fig_motivation}, we observe a shift from positive transfer to negative transfer as a parameter of task relatedness.
-The theory we develop will provide a precise explanation to such a phenomenon (and more).
+The theory we develop will provide a precise explanation to such a phenomenon.
 
-To gain insight into the working of multi-task learning, we consider a simplified setting for learning multiple high-dimensional linear regression tasks.
-A typical process to do multi-task learning involves two steps:
-(i) Jointly learn a shared representation for all the tasks;
-(ii) Fine-tune the learnt model on a specific target task.
-We focus on a hard parameter sharing model proposed in \cite{WZR20} and identify conditions on when multi-task and transfer learning works, and when it doesn't.
+\textbf{Setup.} To gain insight into the working of multi-task learning, we consider a simplified setting for learning multiple high-dimensional linear regression tasks.
+%A typical process to do multi-task learning involves two steps:
+%(i) Jointly learn a shared representation for all the tasks;
+%(ii) Fine-tune the learnt model on a specific target task.
+We focus on a hard parameter sharing model proposed in \cite{R17,WZR20} and identify conditions on when multi-task and transfer learning works, and when it doesn't.
 The high-dimensional linear regression setting where the target task data size is limited captures the intuition that the target task only contains limited labeled data.
@@
 This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
+We focus on comparing the test performance on a target task using estimators from doing multi-task training and transfer learning.
+We compare the test performance of these estimators to the single-task baseline.
+%The details are described in Algorithm \ref{alg_estimator}.
 
@@
 	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}
-	\caption{Phase transition as a parameter of model distance.}
+	\caption{Positive to negative transfer as the source task rotates further away from the target task (left to right).}
 	\label{fig_motivation}
@@
 
-We focus on comparing the test performance on a target task using estimators from doing multi-task training and transfer learning.
-We compare the test performance of these estimators to the single-task baseline.
-The details are described in Algorithm \ref{alg_estimator}.
+%We formulate the heterogeneity between different task data under covariate and model shifts .
+%\begin{algorithm}[!t]
+%	\caption{Multi-task learning using a hard-parameter sharing architecture}
+%	\label{alg_estimator}
+%	\begin{algorithmic}[1]
+%		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
+%		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
+%		\State Training the shared body $B$.
+%		\State Optimizing the task heads on the validation set
 
-%We formulate the heterogeneity between different task data under covariate and model shifts .
-By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
-\todo{list those here}
-We refine the task covariance part of \cite{WZR20} into three factors: model distance, covariate shift matrix and data ratio \cite{PY09,K18}.
-These are achieved through tight generalization bounds established in the high-dimensional regression setting.
-Our main results are described as follows.
+%		\begin{itemize}
+%			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
+%			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
+%			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
+%		\end{itemize}
+%		\State Problem statement: how can we compare the test error of the three estimators on the target task?
+		%, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$?
+%	\end{algorithmic}
+%\end{algorithm}
 
-\begin{algorithm}[!t]
-	\caption{Multi-task learning using a hard-parameter sharing architecture}
-	\label{alg_estimator}
-	\begin{algorithmic}[1]
-		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
-		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
-		\State Training the shared body $B$.
-		\State Optimizing the task heads on the validation set
-
-		\begin{itemize}
-			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
-			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
-			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
-		\end{itemize}
-		\State Problem statement: how can we compare the test error of the three estimators on the target task?
-		%, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$?
-	\end{algorithmic}
-\end{algorithm}
-
-\smallskip
-\noindent{\bf Variance reduction from information transfer.}
+{\bf Quantifying model shift bias versus variance trade-off.}
 	We show that the benefit from doing multi-task or transfer learning stems from reducing the variance of the estimator for the target task through newly added source task data.
@@
 
-	{\it Insight 1}: $\hat{\beta}_t^{\MTL}$ vs $\hat{\beta}_t^{\STL}$.
-	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
-	In particular, if model shift is too large, we get negative transfer from multi-task training.
+	A crucial technical tool that we develop is the asymptotic limit of the trace of two random matrices.
+	The result extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent random matrices, which may be of independent interest.
 
-	{\it Insight 2}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\MTL}$.
-	Finally, we show that the transfer learning estimator always improves over mutli-task training.
-	The amount of improvement becomes more significant as the model distance becomes larger.
+\textbf{How task data affects transfer.}
+	We identify three factors: task model similarities and their noise level, data size and covariate shift \cite{PY09,K18}.
+	These are achieved through tight generalization bounds established in the high-dimensional regression setting.
+	Using these tools, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
+	\begin{itemize}
+		\item We provide a sharp transition to show that task model similarities can determine whether there is positive transfer.
+		For settings where tasks are similar, we further show that the transfer effect depends on the single-task accuracy of the source task.
+		\item We show how source task data size can also determine transfer by providing a sharp transition.
+		We use our tools to explain the result of taskonomy \cite{ZSSGM18}, regarding the data efficiency of multi-task learning.
+		\item Our result has implications on the following question.
+	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices.
+	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.
+	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
+	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
+	\end{itemize}
+
+Finally, we extend our reuslts to study the transfer functions used in taskonomy \cite{ZSSGM18}.
+%	{\it Insight 1}: $\hat{\beta}_t^{\MTL}$ vs $\hat{\beta}_t^{\STL}$.
+%	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
+%	In particular, if model shift is too large, we get negative transfer from multi-task training.
+
+%	{\it Insight 2}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\MTL}$.
+%	Finally, we show that the transfer learning estimator always improves over mutli-task training.
+%	The amount of improvement becomes more significant as the model distance becomes larger.
 
@@
 
-\smallskip
-	\noindent\textbf{Covariate shift and data ratio.}
-	For the case of two tasks with general inputs, we further study the factors that determine the transfer rate.
-	We identify two factors, the covariate shift matrix and the ratio between number of task data.
+%\smallskip
+%	\noindent\textbf{Covariate shift and data ratio.}
+%	For the case of two tasks with general inputs, we further study the factors that determine the transfer rate.
+%	We identify two factors, the covariate shift matrix and the ratio between number of task data.
 %	Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
@@
 
-	\textit{Insight 3}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\STL}$.
-	Our result has implications on the following question.
-	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices.
-	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.
-	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
-	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
-
-\smallskip
-	\noindent\textbf{Experimental results.}
+%	\textit{Insight 3}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\STL}$.
+\textbf{Experimental results.} We provide practical implications to validate our theory.
+\begin{itemize}
+	\item We validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.
+	\item We show that when the number of source task datapoints is large compared to the target task, then aligning task covariances always improves performance.
+	On the other hand, if the number of source task datapoints is comparable to the target task, aligning task covariances may hurt performance.
+\end{itemize}

### 2020-05-21 writeup/intro.tex
revision

@@
 
-	A crucial technical tool that we develop is the asymptotic limit of the trace of two random matrices.
-	The result extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent random matrices, which may be of independent interest.
+	A crucial technical tool that we develop is the asymptotic limit of the trace of the inverse of the sum of two independent sample covariance matrices.
+Our result not only extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent sample covariance matrices with general covariance matrices, but also gives an almost optimal error bound, which may be of independent interest.
 
@@
 		\item Our result has implications on the following question.
-	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices.
+	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices?
 	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.

### 2020-05-21 writeup/setup.tex
sec 3.1
revision

@@
-\subsection{Setup and Main Results}\label{sec_setup}
+\section{Preliminaries}\label{sec_setup}
 
-We assume that for every row $x$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
-We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.
+We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
+We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector that has i.i.d. entries with mean $0$ and variance $1$.
 We will designate the $k$-th task as the target.

### 2020-05-21 writeup/technical.tex
minor
intro quick pass
transfer learning
revision

@@
 We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
-We compare it with the asympotic limit of $\te(\hat{\beta}_t{\STL})$, for settings where the target data size is limited.
+We compare it with the asympotic limit of $\te(\hat{\beta}_t^{\STL})$, for settings where the target data size is limited.
 We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.
@@
 where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
-It is not hard to show that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
+It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
 \[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
@@
 	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
-	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1 > ??$ and $c_2 > 3$ are fixed constants.
-	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depends on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
+	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1>1$ and $c_2 >1$ are fixed constants.
+	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
 	\begin{itemize}
@@
 The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+
+%\section{Extension to Transfer Learning}
+
+%We study the transfer function of taskonomy \cite{ZSSGM18}.
+%The algorithm is as follows.
+%First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
+%This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
+%Then, we learn the output layer on the target task.
+%We use our tools to analyze this setting as follows.
+%G

### 2020-05-21 writeup/transfer.tex
revision

@@
 	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
+For the noises, we assume that $\e_i$ has i.i.d.
+entries with mean zero and variances $\sigma_i^2$, $i=1,2$.
 	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
@@
 	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
+For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.
 \end{example}
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c_1 > 100$ is a fixed constant.
+	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c_1 > 110$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
@@
 \end{proposition}
+
+Here the constants $\frac23$ and $\frac32$ in this proposition (and the following ones) can be replaced with $(1+c_1^{-1/2})^{-4}$ and $(1-c_1^{-1/2})^{-4}$.
+In particular, these bounds becomes tighter as $c_1$ increases.
 
@@
 \begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $c_1 > 100$ is a fixed constant and $d^2 < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$.
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $c_1 > 110$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, i.e.
+we have positive transfer when $\sigma_1=\sigma_2$.
 Then we derive the following transition as a parameter of $\sigma_1$:
@@
 
-\item If $d^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
+\item If $d^2 > (1 - a^{-1/2})^{-4}(1-(a+c_2-2)^{-2})^{-1}\frac{\sigma^2}{p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
 		\begin{itemize}
@@
 Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-Our result shows that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix is equal to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
+Our result shows that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
 On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
@@
 	In the setting of Example \ref{ex_basic}, assume that $c_1 > 3$ and $c_2>3$,
-and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. As a parameter of $M \in \cS_{\mu}$, we have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M$ satisfies that 
+and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. %As a parameter of $M \in \cS_{\mu}$, 
+We have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M\in \cS_{\mu}$ satisfies that 
 \be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(c_2c_1^{-1} + c_1^{-1/2}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee

### 2020-05-21 writeup/experiments.tex
add source/target task accuracy transfer table

@@
 \paragraph{A metric to determine when MTL performs better STL.}
+\begin{table}
+\begin{center}
+  \begin{tabular}{c c c}
+  \toprule
+    {\bf Threshold}  & {\bf Precision} &  {\bf Recall} \\
+    \midrule
+    0.0 & 0.596 & 1.000 \\
+    0.1 & 0.756 & 0.388 \\
+    0.2 & 0.919 & 0.065 \\
+    0.3 & 1.000 & 0.004 \\	
+  \bottomrule
+  \end{tabular}
+\end{center}
+\caption{Ablation study on when should use MTL via different source/target task accuracy. Note: source task size range [500, 1500], target task size: 1000}
+\label{tab:mtl_better_than_stl}
+\end{table}
 
 \paragraph{When should we align task covariances in MTL.}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+	\caption{Covariate shift experiment.}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mlp.pdf}
+	\caption{Covariate shift experiment.}
+\end{figure}

### 2020-05-22 writeup/intro.tex
intro wip

@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-In multi-task learning, having related task data is fundamental to its performance.
-Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
-For example, many applications in computer vision \cite{ZSSGM18}, natural language processing \cite{MTDNN19}, and many other areas have been achieved by learning from multiple tasks together.
-In spite of these promising empirical results, multi-task learning is not well-understood because of the prevalence of \textit{negative transfer} -- when the trained multi-task model performs worse than single-task learning for the target task.
-\todo{transition}
-In this work, we present a theoretical study to better understand when multi-task learning works better than single-task learning. % for learning from multiple linear regression tasks.
-\todo{practical insight}
+Multi-task learning has recently found many applications in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{MTDNN19} and numerous other areas \cite{R17,ZY17}.
+%In multi-task learning, having related task data is fundamental to its performance.
+%Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
+By learning from related information sources, models that are trained using multi-task learning can share information across different data \cite{C97}.
+%For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
+At the same time, negative results have also been reported in the literature \cite{AP16,BS17}, where training a multi-task model performs worse for predicting a task compared to learning the task in isolation (single-task learning).
+This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
+%\todo{transition}
+In this work, we provide a formal study to better understand when and why negative transfer happens for learning multiple high-dimensional linear regression tasks.
+% for learning from multiple linear regression tasks.
+Based on the theory, we develop practical insights to detect negative transfer and guide multi-task training.
 %We consider a setting where the target task has limited labeled data and show
@@
 
-The technical challenge to develop a theory for multi-task learning is how to capture generalization performance that scales tightly with the amount of labeled data, in particular when the size of the training set is small.
-Prior generalization theory using uniform stability \cite{LTSM16}, Rademacher complexity \cite{BS03,BBCKP10} is unable to explain the phenomenon of negative transfer because there is no tight bound on test error that scales with the amount of labeled data.
-In particular in Figure \ref{fig_motivation}, we observe a shift from positive transfer to negative transfer as a parameter of task relatedness.
-The theory we develop will provide a precise explanation to such a phenomenon.
+Comparing the performance of multi-task learning to single-task learning requires developing generalization bounds that scale tightly with the qualities of task data, such as the number of datapoints.
+Previous work has shown the benefit of multi-task learning for learning certain half-spaces \cite{MPR16} and sparse regression where the parameter vectors have the same support \cite{LPVT11}.
+\todo{unpack}
+Furthermore, classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented in a way so that the error goes down as more labeled data is added \cite{M06}.
+On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
 
-\textbf{Setup.} To gain insight into the working of multi-task learning, we consider a simplified setting for learning multiple high-dimensional linear regression tasks.
+%The technical challenge to develop a theory for multi-task learning is how to capture generalization performance that scales tightly with the amount of labeled data, in particular when the size of the training set is small.
+%Prior generalization theory using uniform stability \cite{LTSM16}, Rademacher complexity \cite{BS03,BBCKP10} is unable to explain the phenomenon of negative transfer because there is no tight bound on test error that scales with the amount of labeled data.
+%In particular in Figure \ref{fig_motivation}, we observe a shift from positive transfer to negative transfer as a parameter of task relatedness.
+%The theory we develop will provide a precise explanation to such a phenomenon.
+
+%To gain insight into the working of multi-task learning, we consider a simplified setting for learning multiple high-dimensional linear regression tasks.
 %A typical process to do multi-task learning involves two steps:
@@
 %(ii) Fine-tune the learnt model on a specific target task.
-We focus on a hard parameter sharing model proposed in \cite{R17,WZR20} and identify conditions on when multi-task and transfer learning works, and when it doesn't.
-The high-dimensional linear regression setting where the target task data size is limited captures the intuition that the target task only contains limited labeled data.
+%We focus on a hard parameter sharing model proposed in \cite{R17,WZR20} and identify conditions on when multi-task and transfer learning works, and when it doesn't.
+%The high-dimensional linear regression setting where the target task data size is limited captures the intuition that the target task only contains limited labeled data.
 
-Concretely, our input consists of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
+\textbf{Setup.} Concretely, our input consists of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
 We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
@@
 
-{\bf Quantifying model shift bias versus variance trade-off.}
+{\bf Main Results.}
 	We show that the benefit from doing multi-task or transfer learning stems from reducing the variance of the estimator for the target task through newly added source task data.
@@
 
-\textbf{How task data affects transfer.}
+\textbf{Quantitative insights.}
 	We identify three factors: task model similarities and their noise level, data size and covariate shift \cite{PY09,K18}.

### 2020-05-22 writeup/setup.tex
edits

@@
 
-\paragraph{Hypothesis on Heterogeneous Task Data}
+%\paragraph{Hypothesis on Heterogeneous Task Data}
 
-Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
+%Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
 %\todo{Add some references to add spice on these takes.}
-We consider two natural questions within each category.
-\begin{itemize}
-	\item \textbf{Model shift.}
-	In general the single-task models can also be different across different tasks.
-We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
+%We consider two natural questions within each category.
+%\begin{itemize}
+%	\item \textbf{Model shift.}
+%	In general the single-task models can also be different across different tasks.
+%We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
 
-	Under model shift, when do we get positive vs. negative transfer?
-	How does the type of transfer depend on the number of data points, the distance of the task models etc?
-	\item \textbf{Covariate shift.}
-	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
-This is also known as covariate shift in the literature.
-	How does covariate shift affect the rate of information transfer?
-	For example, is it better to have the same covariance matrix or not?
-\end{itemize}
+%	Under model shift, when do we get positive vs. negative transfer?
+%	How does the type of transfer depend on the number of data points, the distance of the task models etc?
+%	\item \textbf{Covariate shift.}
+%	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
+%This is also known as covariate shift in the literature.
+%	How does covariate shift affect the rate of information transfer?
+%	For example, is it better to have the same covariance matrix or not?
+%\end{itemize}
 

### 2020-05-23 writeup/intro.tex
edits
intro 1/2

@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning has recently found many applications in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{MTDNN19} and numerous other areas \cite{R17,ZY17}.
+Multi-task learning has recently become a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and numerous other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
 %Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
-By learning from related information sources, models that are trained using multi-task learning can share information across different data \cite{C97}.
+By combining multiple information sources, multi-task learning allows new information to be shared across different sources in a model \cite{C97}.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
-At the same time, negative results have also been reported in the literature \cite{AP16,BS17}, where training a multi-task model performs worse for predicting a task compared to learning the task in isolation (single-task learning).
-This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-%\todo{transition}
-In this work, we provide a formal study to better understand when and why negative transfer happens for learning multiple high-dimensional linear regression tasks.
-% for learning from multiple linear regression tasks.
-Based on the theory, we develop practical insights to detect negative transfer and guide multi-task training.
+At the same time, it is well-known that the performance of multi-task learning methods depends on the relationship between the information sources.
+\textit{Negative transfer}, the phenomenon where for a particular prediction task, multi-task learning performs worse than single-task learning, is prevalent when the information sources are heterogeneous \cite{AP16,BS17}.
+While numerous studies have sought to alleviate negative transfer when it occurs \cite{YKGLHF20}, a rigorous understanding to the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
+%This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
+In this work, we consider learning multiple high-dimensional linear regression tasks to better understand when and why negative transfer happens. % for learning from multiple linear regression tasks.
+We provide theoretical and practical insights to show how task data affects the transfer of information.
 %We consider a setting where the target task has limited labeled data and show
@@
 
-Comparing the performance of multi-task learning to single-task learning requires developing generalization bounds that scale tightly with the qualities of task data, such as the number of datapoints.
-Previous work has shown the benefit of multi-task learning for learning certain half-spaces \cite{MPR16} and sparse regression where the parameter vectors have the same support \cite{LPVT11}.
-\todo{unpack}
-Furthermore, classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented in a way so that the error goes down as more labeled data is added \cite{M06}.
+Identifying when negative transfer occurs requires comparing the performance of multi-task learning directly to single-task learning.
+The technical challenge is to develop generalization bounds that are able to scale tightly with the qualities of task data, such as the number of datapoints.
+In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented in a way so that the error goes down as more labeled data is added.
 On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
+More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and multipl sparse regressions \cite{LPTV09,LPVT11}.
 
@@
 
-\textbf{Setup.} Concretely, our input consists of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
-We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
-We use a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
+In this work, we consider multiple high-dimensional linear regression tasks as input and focus on predicting a particular task that only has limited amount of labeled data.
+Concretely, each task consists of $n_i$ datapoints in space $\real^p$ organized as matrix $X_i\in\real^{n_i\times p}$, for $1\le i\le p$.
+The labels of $X_i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i$ denotes the ground truth parameters for task $i$ and $\varepsilon_i$ denotes i.i.d.
+random noise with mean zero and variance $\sigma^2$.
+Importantly, we assume that the number of datapoints $n_i$ is a small constant $\rho_i$ times $p$ and that $p$ is large. \todo{rational}
+%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
+%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
+%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
+%distribution with covariance matrix $\Sigma_i$.
+We use a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^k$ for each task \cite{R17,MTDNN19}.
 %    \paragraph{Different covariates:}
@@
 \end{align}
-Note that we consider the natural parameterization without reweighting the tasks above.
-The shared body $B$ plays an important role because it allows information transfer between different task data.
-This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
-We focus on comparing the test performance on a target task using estimators from doing multi-task training and transfer learning.
-We compare the test performance of these estimators to the single-task baseline.
+%Note that we consider the natural parameterization without reweighting the tasks above.
+%The shared body $B$ plays an important role because it allows information transfer between different task data.
+%This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
+%We focus on comparing the test performance on a particular task solved with equation \eqref{eq_mtl} to single-task learning.
 %The details are described in Algorithm \ref{alg_estimator}.
+Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal predictor obtained from solving equation \eqref{eq_mtl} for task $t$.
+Our goal is to compare the test error of $\hat{\beta}_t^{\MTL}$, denoted as $\te(\hat{\beta}_t^{\MTL})$, to $\te(\hat{\beta}_t^{\STL})$, where $\hat{\beta}_t^{\STL}$ is likewise obtained from equation \eqref{eq_mtl} but with task $t$ in isolation.
 
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}
-	\caption{Positive to negative transfer as the source task rotates further away from the target task (left to right).}
-	\label{fig_motivation}
-\end{figure}
+%\begin{figure}[!t]
+%	\centering
+%	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}
+%	\caption{Positive to negative transfer as the source task rotates further away from the target task (left to right).}
+%	\label{fig_motivation}
+%\end{figure}
 
@@
 
-{\bf Main Results.}
-	We show that the benefit from doing multi-task or transfer learning stems from reducing the variance of the estimator for the target task through newly added source task data.
-	We derive this result for the setting of two tasks with general inputs and $k$ tasks with the same covariates for any $k \ge 2$.
-	The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{EA20}.
+	\textbf{Main results.}
+	We begin by observing that $\te(\hat{\beta}_t^{\MTL})$ can be decomposed into two parts, a variance part that is reduced from $\te(\hat{\beta}_t^{\STL})$, and a bias part that captures the difference between $\beta_t$ and the rest of $\beta$'s.
+	We term the bias part as \textit{model shift bias}.
+	Intuitively, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ depends on the trade-off between the amount of variance reduced and the model shift bias part.
+	For the high-dimensional regime when $p$ goes to infinity, we derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL}) - \te(\hat{\beta}_t^{\STL})$ as a function of the number of datapoints $\set{n_1, n_2}$, the covariance matrices $\set{\Sigma_1, \Sigma_2}$, the ground truth parameters $\set{\beta_1, \beta_2}$, and a certain fixed value derived from solving equation \eqref{eq_mtl}.
+	Then, we show a similar result for any number of tasks that have the same covariates, i.e. $X_i = X_j$ for any $i \neq j$.
+	This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+
+%the benefit from doing multi-task or transfer learning stems from reducing the variance of the estimator for the target task through newly added source task data.
+%	We derive this result for the setting of two tasks with general inputs
 %	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
-	On the other hand, the difference between task models causes a negative effect that we call the \textit{model shift bias}.
-	We show bounds on the trade-off between the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
+	%On the other hand,  task models causes a negative effect that we call the \textit{model shift bias}.
+	%We show bounds on the trade-off between the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
 
-	A crucial technical tool that we develop is the asymptotic limit of the trace of the inverse of the sum of two independent sample covariance matrices.
-Our result not only extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent sample covariance matrices with general covariance matrices, but also gives an almost optimal error bound, which may be of independent interest.
-
-\textbf{Quantitative insights.}
 	We identify three factors: task model similarities and their noise level, data size and covariate shift \cite{PY09,K18}.
@@
 Finally, we extend our reuslts to study the transfer functions used in taskonomy \cite{ZSSGM18}.
+
+A crucial technical tool that we develop is the asymptotic limit of the trace of the inverse of the sum of two independent sample covariance matrices.
+Our result not only extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent sample covariance matrices with general covariance matrices, but also gives an almost optimal error bound, which may be of independent interest.
+
 %	{\it Insight 1}: $\hat{\beta}_t^{\MTL}$ vs $\hat{\beta}_t^{\STL}$.

### 2020-05-23 writeup/intro.tex
intro 2nd 1/2 wip

@@
 	Intuitively, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ depends on the trade-off between the amount of variance reduced and the model shift bias part.
-	For the high-dimensional regime when $p$ goes to infinity, we derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL}) - \te(\hat{\beta}_t^{\STL})$ as a function of the number of datapoints $\set{n_1, n_2}$, the covariance matrices $\set{\Sigma_1, \Sigma_2}$, the ground truth parameters $\set{\beta_1, \beta_2}$, and a certain fixed value derived from solving equation \eqref{eq_mtl}.
-	Then, we show a similar result for any number of tasks that have the same covariates, i.e. $X_i = X_j$ for any $i \neq j$.
+	For the high-dimensional regime when $p$ goes to infinity, we derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL}) - \te(\hat{\beta}_t^{\STL})$ as a function of the number of datapoints $\set{n_1, n_2}$, the covariance matrices $\set{\Sigma_1, \Sigma_2}$, the ground truth parameters $\set{\beta_1, \beta_2}$, and a certain fixed value derived from solving equation \eqref{eq_mtl} (see Theorem \ref{thm_main_informal} for the statement).
+	Then, we show a similar result for any number of tasks that have the same covariates, i.e. the $X_i$'s are equal to each other in Theorem \ref{thm_many_tasks}.
 	This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
@@
 
-	We identify three factors: task model similarities and their noise level, data size and covariate shift \cite{PY09,K18}.
-	These are achieved through tight generalization bounds established in the high-dimensional regression setting.
-	Using these tools, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
-	\begin{itemize}
-		\item We provide a sharp transition to show that task model similarities can determine whether there is positive transfer.
+	Next, we use our technical tools to show how to determine negative transfer based on task data.
+%	These are achieved through tight generalization bounds established in the high-dimensional regression setting.
+%	Using these tools, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
+%	\begin{itemize}
+Our first theoretical insight is we provide a sharp transition to show that task model similarities can determine whether there is positive transfer.
 		For settings where tasks are similar, we further show that the transfer effect depends on the single-task accuracy of the source task.
-		\item We show how source task data size can also determine transfer by providing a sharp transition.
+
+Our second theoretical insight is we show how source task data size can also determine transfer by providing a sharp transition.
 		We use our tools to explain the result of taskonomy \cite{ZSSGM18}, regarding the data efficiency of multi-task learning.
-		\item Our result has implications on the following question.
+
+Our third theoretical insight is has implications on the following question.
 	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices?
@@
 	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
-	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
-	\end{itemize}
+%	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
 
@@
 \textbf{Experimental results.} We provide practical implications to validate our theory.
-\begin{itemize}
-	\item We validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.
-	\item We show that when the number of source task datapoints is large compared to the target task, then aligning task covariances always improves performance.
+	First, we validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.
+	\todo{Second}
+	Finally, We show that when the number of source task datapoints is large compared to the target task, then aligning task covariances always improves performance.
 	On the other hand, if the number of source task datapoints is comparable to the target task, aligning task covariances may hurt performance.
-\end{itemize}

### 2020-05-24 writeup/experiments.tex
add chest x-ray results

@@
 \begin{center}
-  \begin{tabular}{c c c}
+  \begin{tabular}{c c c c c}
   \toprule
-    {\bf Threshold}  & {\bf Precision} &  {\bf Recall} \\
-    \midrule
-    0.0 & 0.596 & 1.000 \\
-    0.1 & 0.756 & 0.388 \\
-    0.2 & 0.919 & 0.065 \\
-    0.3 & 1.000 & 0.004 \\	
+    \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
+    & Precision &  Recall & Precision &  Recall \\
+    \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
+    0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
+    0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
+    0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
+    0.3 & 1.000 & 0.004 &     - &     - \\
   \bottomrule
@@
 \end{center}
-\caption{Ablation study on when should use MTL via different source/target task accuracy. Note: source task size range [500, 1500], target task size: 1000}
+\caption{Ablation study on when should use MTL via different source/target task accuracy.
+Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.}
 \label{tab:mtl_better_than_stl}

### 2020-05-24 writeup/transfer.tex
reorg

@@
 
-\subsection{Task Model Similarity versus Noise}\label{sec_dist}
+\subsection{Model Shift Bias versus Variance Trade-off}\label{sec_main}
+
+%In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
+%We achieve this through tight generalization bounds obtained from random matrix theory.
+%For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
+We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
+Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
+The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
+We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
+We compare it with the asympotic limit of $\te(\hat{\beta}_t^{\STL})$, for settings where the target data size is limited.
+We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.
+
+\textbf{Two Tasks with General Covariance Matrices.}
+For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
+\begin{align}
+	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
+	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
+\end{align}
+where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
+It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
+\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
+Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
+%The main result of this section show deterministic conditions under which we get positive or negative transfer.
+%And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
+The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
+A key highlight of our approach implies a precise limit on $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}$, which only depends on $\Sigma_1, \Sigma_2$ and $n_1, n_2$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+
+\begin{theorem}\label{thm_main_informal}
+	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
+	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1>1$ and $c_2 >1$ are fixed constants.
+	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
+	\begin{itemize}
+		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{theorem}
+
+Theorem \ref{thm_main_informal} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
+The bounds get tighter and tighter as $n_1 / p$ increases.
+
+\textbf{Many Tasks with the Same Covariates.}
+We extend the above result to any number of tasks that have the same covariates.
+%In this section we consider the setting with $k$ many that have the same covariates.
+Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
+We derive the model shift bias and variance in the following result.
+
+\begin{theorem}\label{thm_many_tasks}
+	Let $n = c \cdot p$.
+	Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $B^{\star}\Sigma B^{\star}$, where $U_r\in\real^{k\times r}$.
+	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
+	We have the following
+	\begin{itemize}
+		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} \ge \norm{\Sigma (B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} < \norm{\Sigma(B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{theorem}
+As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$, for any $1 \le i \le k$.
+Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$.
+The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+
+\subsection{Task Model Similarity}\label{sec_dist}
 
@@
 \textbf{Implications.}
+
+\section{Extension to the Transfer Function of Taskonomy}
+
+We study the transfer function of taskonomy \cite{ZSSGM18}.
+The algorithm is as follows.
+First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
+This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
+Then, we learn the output layer on the target task.
+We use our tools to analyze this setting as follows.

### 2020-05-24 writeup/proof_technical.tex
re-structure

@@
 
+\begin{theorem}\label{thm_many_tasks}
+	Let $n = c \cdot p$.
+	Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $B^{\star}\Sigma B^{\star}$, where $U_r\in\real^{k\times r}$.
+	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
+	We have the following
+	\begin{itemize}
+		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} \ge \norm{\Sigma (B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} < \norm{\Sigma(B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{theorem}
+As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$, for any $1 \le i \le k$.
+Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$.
+The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+
 %In this section we consider the setting with $k$ many that have the same covariates.

### 2020-05-24 writeup/transfer.tex
re-structure

@@
 \subsection{Model Shift Bias versus Variance Trade-off}\label{sec_main}
+
+We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
+We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector that has i.i.d. entries with mean $0$ and variance $1$.
+We will designate the $k$-th task as the target.
+Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
+Concretely, we focus on the test error for the target task:
+		\begin{align*}
+			\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
+			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
+		\end{align*}
+%\end{itemize}
+
+\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}
+
+\textbf{The High-Dimensional Setting.}
+%\todo{setup motivation and notations}
+We would like to get insight on how covariate and model shifts affect the rate of transfer.
+We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
+This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
+Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.
+
+For the case of two tasks, we can get precise rates using random matrix theory.
+For the sake of clarity, we call task 1 the source task and task 2 the target task,
+i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
+We introduce the following notations for the high-dimensional setting
+\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
+for some constants $c_1, c_2 \in (1,\infty)$.
+A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
+%
 
@@
 We derive the model shift bias and variance in the following result.
-
-\begin{theorem}\label{thm_many_tasks}
-	Let $n = c \cdot p$.
-	Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $B^{\star}\Sigma B^{\star}$, where $U_r\in\real^{k\times r}$.
-	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
-	We have the following
-	\begin{itemize}
-		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} \ge \norm{\Sigma (B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} < \norm{\Sigma(B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{theorem}
-As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$, for any $1 \le i \le k$.
-Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$.
-The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-05-24 writeup/proof_examples.tex
restructure sec 3

--- 2020-05-19 writeup/proof_transfer_ex.tex
@@
-\section{Supplementary Materials for Section \ref{sec_insight}}\label{app_proof_main}
-
-From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
-for the rest of the section, we shall consider the case when $r=1$ we are considering the case of two tasks.
-Here, equation \eqref{eq_mtl} simplifies to the following
-\begin{align}\label{eq_mtl_2task}
-	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
-\end{align}
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
-To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
-\begin{align*}
-	& \hat{B}(w_1, w_2) \\
-	=& (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
-	=& \frac{1}{w_2} ((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-	=& \frac{1}{w_2}\bigbrace{\beta_t + ((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\frac{w_1}{w_2}\beta_s - w^2\beta_t) + (\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}}.
-\end{align*}
-As a remark, when $w_1 = w_2 = 1$, we recover the linear regression estimator.
-The advantage of using $f(B; w_1, w_2)$ is that if $\theta_1$ is a scaling of $\theta_2$, then this case can be solved optimally using equation \eqref{eq_mtl_2task} \cite{KD12}.
-
-\textbf{Defining the multi-task learning estimator.}
-Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-\begin{align}
-		\val(\hat{B}; w_1, w_2)
-	= & n_1 \cdot \bignorm{\Sigma_1^{1/2}((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - \frac{w_1}{w_2}\beta_t)}^2 \nonumber \\
-		&+ n_1 \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1} \nonumber \\
-		&+ n_2 \cdot w^2\bignorm{\Sigma_2^{1/2}((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \frac{w_1}{w_2}\beta_t)}^2 \nonumber \\
-		&+ n_2 \cdot \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}. \label{eq_val_mtl}
-\end{align}
-Let $\hat{w_1}/\hat{w_2}$ be the global minimizer of $\val(\hat{B}; w_1, w_2)$.
-We will define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_t^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2). \]
-
-The intuition for deriving $\hat{\beta}_t^{\MTL}$ is akin to performing multi-task training in practice.
-Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-The test loss of using $\hat{\beta}_t^{\MTL}$ for the target task is
-\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
-			&~ + \sigma^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl_2task}
-\end{align}
-
-Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
-The baseline where we solve the target task with its own data is
-\begin{align*}
-	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
-\end{align*}
-%Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
-
-We state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$.
-The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.
-
-\begin{lemma}\label{lem_minv}[\todo{ref?}]
-	Let $X\in\real^{n\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$.
-	In the setting when $n = c p$ we have that as $p$ goes to infinity,
-	\[ \bigtr{(X^{\top}X)^{-1}\Sigma} = \frac{1}{c - 1}. \]
-\end{lemma}
-
-The second lemma, which deals the inverse of the sum of two random matrices, can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-\begin{lemma}\label{lem_cov_shift}
-	Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in decreasing order.
-	When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}%\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{c_1+c_2}\cdot \bigtr{ \frac{1}{p}\cdot(a_1 M^\top M + a_2)^{-1}} +\bigo{ n^{-1/2+\epsilon}},
-	\end{align}
-	for any constant $\epsilon>0$, where $a_1, a_2$ are solutions to the following deterministic equations:
-	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{c_1 + c_2},~ a_1 + \frac{1}{p}\cdot\sum_{i=1}^p \frac{a_1}{(c_1 + c_2)(a_1 + a_2/ \lambda_i^2)} = \frac{c_1}{c_1 + c_2}. \label{eq_a12}
-	\end{align}
-\end{lemma}
-We will give the proof of Lemma \ref{lem_cov_shift} in Section \ref{sec_maintools}.
-
-Finally, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
-\todo{restate this}
-\begin{lemma}\label{prop_model_shift_tight}
-		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
-		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
-		and we have
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
-		\end{align*}
-\end{lemma}
-
-\subsection{Proof of Proposition \ref{prop_dist_transition} and Proposition \ref{prop_var_transition}}\label{app_proof_31}
+\subsection{Proofs for Section \ref{sec_similarity}}\label{app_proof_31}
 
@@
 
-\subsection{Proof of Proposition \ref{prop_data_size} and Proposition \ref{prop_data_efficiency}}\label{app_proof_data}
+\subsection{Proofs for Section \ref{sec_data_size}}\label{app_proof_data}
 
@@
 
-\subsection{Proofs of Proposition \ref{prop_covariate} and Theoretical justification of Example \ref{ex_covariate}}\label{app_covariate}
+\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}
 

### 2020-05-24 writeup/proof_main.tex
restructure sec 3

--- 2020-05-24 writeup/proof_technical.tex
@@
-\section{Supplementary Materials for Section \ref{sec_main}}
+\subsection{Proofs for Section \ref{sec_main}}
 
@@
 
-\subsection{Proof of Theorem \ref{thm_model_shift}}\label{sec pfmain}
+\subsubsection{Proof of Theorem \ref{thm_model_shift}}\label{sec pfmain}
 
@@
 
-\subsection{Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_many_tasks}
+\subsubsection{Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_many_tasks}
 

### 2020-05-24 writeup/proof_taskonomy.tex
restructure sec 3

--- 2020-05-20 writeup/extension_transfer.tex
@@
-\section{Extension to Transfer Learning}
-
-We study the transfer function of taskonomy \cite{ZSSGM18}.
-The algorithm is as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
-This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
-Then, we learn the output layer on the target task.
-We use our tools to analyze this setting as follows.
+\section{Proof of ???}
 

### 2020-05-24 writeup/proofs_sec3.tex
restructure sec 3

--- 2020-05-19 writeup/proof_transfer_ex.tex
@@
 The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.
+
 \begin{lemma}\label{lem_minv}[\todo{ref?}]
-	Let $X\in\real^{n\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$.
-	In the setting when $n = c p$ we have that as $p$ goes to infinity,
-	\[ \bigtr{(X^{\top}X)^{-1}\Sigma} = \frac{1}{c - 1}. \]
+	Let $X\in\real^{n\times p}$ be a random matrix that contains i.i.d.
+row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$.
+Let $A$ be a $p\times p$ matrix that is independent of $X$ and satisfies $\|A\|=\OO(1)$.
+	In the setting when $n = c p$ we have that
+	\[  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{c - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ p^{-1/2+\epsilon}} \]
+for any constant $\e>0$.
 \end{lemma}
@@
 \end{lemma}
-
-\subsection{Proof of Proposition \ref{prop_dist_transition} and Proposition \ref{prop_var_transition}}\label{app_proof_31}
-
-The proof will consist of two main steps.
-\begin{itemize}
-	\item First, we show that $\hat{v}$ is close to $1$.
-	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ to show the result.
-\end{itemize}
-
-We denote
-\begin{align}
-	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& + (n_1+n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
-\end{align}
-Under the setting of Proposition \ref{prop_model_shift_tight}, using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we have that
-$$\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2})\right)\quad \text{with probability }1-\oo(1).$$
-Thus it suffices to study the behavior of $\val (w)$.
-For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
-
-\begin{lemma}\label{lem_hat_v}
-Suppose the assumptions of Proposition \ref{prop_model_shift_tight} hold.
-Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Then we have that the optimal ratio for $\val(w)$ satisfies
-	\be\label{hatw_add1}|\hat w -1|=\OO(p^{-1}).\ee
-	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-\end{lemma}
-\begin{proof}
-The proof is also similar to the one for Proposition \ref{thm_cov_shift}. First it is easy to observe that $\val(w)\le \val(-w)$ for $w\ge 0$. Hence it suffices to consider the $w\ge 0$ case.
-
-We first consider the case $w\ge 1$. We write
-\begin{align}
-	\val(w) &= n_1\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + n_2\left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& + \sigma^2(n_1+n_2) \cdot \bigtr{(w^{2}X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } .\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
-\end{align}
-
-Taking derivative of $\val(w)$ with respect to $w$, we obtain that
-\begin{align*}
-\val'(w) \ge &~ n_1\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
-+&~ n_2\left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-		-&~ 2(n_1+n_2) \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_1 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
-\end{align*}
-where the matrix $\cal A$ is
-\begin{align*}
-\cal A :&= \left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2.
-- 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}X_1^\top X_1
-\end{align*}
-Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
-\begin{align*}
-\cal A \succeq - \frac{4d^2}{w^5}(\sqrt{n_2}+\sqrt{p})^4 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](\sqrt{n_1}-\sqrt{p})^4 - 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}(\sqrt{n_1}+\sqrt{p})^2\succ 0,
-\end{align*}
-as long as
-$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{(n_1+n_2)(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
-Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$.
-
-Then we consider the case $w\le 1$. Taking derivative of $\val(w)$ with respect to $w$, we obtain that
-\begin{align}
-	\val'(w) &\le n_1 \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + n_2\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& = n_1 \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
-\end{align}
-where the matrix $\cal B$ is
-$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2.$$
-Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
-\begin{align*}
-\cal B \preceq - 2(1-w)\kappa^2(\sqrt{n_2}-\sqrt{p})^4 +2d^2 w\frac{n_2}{n_1}(\sqrt{n_1}+\sqrt{p})^4 \prec 0,
-\end{align*}
-as long as
-$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{n_2(\sqrt{n_1}+\sqrt{p})^4}{n_1(\sqrt{n_2}-\sqrt{p})^4}.$$
-Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly increasing for $w<w_2$. Hence we must have $\hat w\le w_2$. Note that under our assumptions, we have $w_2=1-\OO(p^{-1})$.
-\end{proof}
-
-Based on Lemma \ref{lem_hat_v}, we can prove Proposition \ref{prop_dist_transition}.
-\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
-	Since $\Sigma_1 = \Sigma_2$, we know that $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \hat{v} \id$.
-	Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as whp
-	\begin{align}
-		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{c_2 - 1} - \frac{1}{c_1 + c_2}\cdot\frac{1}{a_1\hat{v}^2 + a_2} + \bigo{p^{-1/2+\varepsilon}}} \nonumber\\
-		&= \sigma^2 \bigbrace{\frac{c_1}{(c_2-1)(c_1 + c_2 -1)} + \bigo{p^{-1/2 + \varepsilon}}},\label{Deltavar}
-	\end{align}
-	where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
-	Next we consider the model shift bias
-	\begin{align*}
-		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
-		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
-	\end{align*}
-	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
-	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
-\ee
-	By solving equations \eqref{eq_a12}, \eqref{eq_a3} and \eqref{eq_a4}, we get
-	\begin{align*}
-		& a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}),
-		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}), \\
-		& a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}),
-		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}).
-	\end{align*}
-	Hence we obtain that
-	\begin{align*}
-		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
-		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
-	\end{align*}
-	To sum up, we have shown that when
-	\[ \frac{p\cdot d^2}{\sigma^2} < \frac{(c_1 + c_2 - 1)^2}{c_1(c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 + \sqrt{\frac 1 {c_1}}}^{-4}, \]
-	we have that $\Delta_{\vari} > \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$.
-	When
-	\[ \frac{p\cdot d^2}{\sigma^2} > \frac{(c_1 + c_2 - 1)^2}{c_1 (c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 - \sqrt{\frac 1 {c_1}}}^{-4}, \]
-	we have that $\Delta_{\vari} < \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is higher than $\te(\hat{\beta}_t^{\STL})$.
-	The result follows by taking $c_1 = c_2 = c$ for the above equation.
-\end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-
-Under the setting of Proposition \ref{prop_var_transition}, we have
-\begin{align*}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
-			&~ + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)\hat v^2  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1}.
-\end{align*}
-Using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we obtain that
-\begin{align*}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( w-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2})\right)\nonumber \\
-	& + (\sigma_1^2 -\sigma_2^2)\hat v^2  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }.
-\end{align*}
-In the setting of Proposition \ref{prop_var_transition}, we can also obtain that
-$$|\hat w-1|=\OO(p^{-1}).$$
-as in \eqref{hatw_add1}. We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. Thus $\te(\hat{\beta}_t^{\MTL}) $ can be reduced to 
-$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_\beta + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
-where $\Delta_\beta:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has been estimated in \eqref{Deltabeta} and $\Delta_{diff}$ is
-\begin{align*}	
-	\Delta_{diff}:=(\sigma_1^2 -\sigma_2^2) \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
-\end{align*}
-Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
-$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
-
-Next we compare $\Delta_{\var}$ with $\Delta_\beta + \Delta_{diff}$.
-Under the condition $d^2 < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, if $\sigma_1^2\le \sigma_2^2$ then we always have that $\Delta_{\vari} > \Delta_{\beta}$ and hence $\te(\hat{\beta}_t^{\MTL})$ is smaller than $\te(\hat{\beta}_t^{\STL})$.
-It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
-If
-\begin{align} 
-&\sigma_2^2  \frac{c_1}{(c_2-1)(c_1 + c_2 -1)}\left(1 + \bigo{p^{-1/2 + \varepsilon}}\right) \label{cond sigma1}\\
-&> \left[\frac{c_1^2 (c_1+c_2)}{(c_1+c_2-1)^3} + \bigo{p^{-1/2 + \varepsilon}}\right]\left[pd^2 \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 + \frac{\sigma_1^2-\sigma_2^2}{c_1} \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2\right] ,\nonumber
-\end{align}
-then we have $\Delta_{\vari} > \Delta_{\beta}$ and we have $\te(\hat{\beta}_t^{\MTL})$ is smaller than $\te(\hat{\beta}_t^{\STL})$.
-For $c_1\ge 100$, we see that \eqref{cond sigma1} is implied by the following condition
-$$\sigma_1^2 \le pd^2 \cdot c_1 + \left[ 1+ \frac23\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \right]\sigma_2^2$$
-as long as $p$ is large enough. On the other hand, if 
-\begin{align} 
-&\sigma_2^2  \frac{c_1}{(c_2-1)(c_1 + c_2 -1)}\left(1 + \bigo{p^{-1/2 + \varepsilon}}\right) \label{cond sigma12}\\
-&< \left[\frac{c_1^2 (c_1+c_2)}{(c_1+c_2-1)^3} + \bigo{p^{-1/2 + \varepsilon}}\right]\left[pd^2 \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 + \frac{\sigma_1^2-\sigma_2^2}{c_1} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\right] ,\nonumber
-\end{align}
-then we have $\Delta_{\vari} < \Delta_{\beta}$ and we have $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$.
-For $c_1\ge 100$, we see that \eqref{cond sigma12} is implied by the following condition
-$$\sigma_1^2 \ge  pd^2 \cdot c_1 + \left[ 1+ \frac32\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \right]\sigma_2^2.$$
-\end{proof}
-
-\subsection{Proof of Proposition \ref{prop_data_size} and Proposition \ref{prop_data_efficiency}}\label{app_proof_data}
-
-\begin{proof}[Proof of Proposition \ref{prop_data_size}]
-Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
-\be\label{pos1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
-otherwise if
-\be\label{neg1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
-then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.
-
-Now we prove the first statement of Proposition \ref{prop_data_size}. Notice that the function
-$$ \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} =(c_2-1) \left(1 +\frac{c_2-2}{c_1}+\frac{1}{c_1(c_1+c_2)}\right)^{-1} $$
-is strictly increasing with respect to $c_1$ as long as $c_2\ge 3$. In particular, for $c_1\ge 100$, we get the bound by taking $c_1\to \infty$:
-$$\frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < 1.1^4 (c_2-1).$$
- Hence we conclude that for $c_1\ge 100$, we always have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp as long as $pd^2 \le \frac{2\sigma^2}{3(c_2-1)}$. This gives the first statement.
-
-The second statement can be proved in a similar way. Suppose $c_1 \ge 110$ and $pd^2 > \frac{3\sigma^2}{2(c_2-1)}$. If $c_1 > \frac{(c_2-2) \sigma^2}{2(c_2 - 1) pd^2/3 - \sigma^2}$, we have
-\begin{align*}
- pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac{2}{3} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  >\sigma^2, 
- \end{align*}
- where in the first step we used that 
- $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 > \frac23$$
- for $c_1 \ge 110$.
-This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds.
-On the other hand, if $100\le c_1 \le \frac{(c_2-2) \sigma^2}{3(c_2 - 1) pd^2/2 - \sigma^2}$, then we have
- \begin{align*}
- pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac{3}{2} pd^2(c_2-1)\cdot \frac{c_1 }{c_1+(c_2-2)}  < \sigma^2, 
- \end{align*}
- where in the first step we used that 
- $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \frac32$$
- for $c_1 \ge 100$. This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
- \end{proof}
-
-\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
-{\cor (cannot get this because we only have some bounds.
-If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
-
-\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=n_2$.
-In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}, and by symmetry it suffices to focus on one of tasks, say task 2.
-Using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, we have that whp,
-\be\label{reduceproof1}
-\begin{split}
-\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{2\al c - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(2)}_{\beta},
-\end{split}
-\ee
-where $ \Delta^{(2)}_{\beta}$ satisfies 
-\be \nonumber
-\bigbrace{1 - \sqrt{\frac{1}{\al c}}}^4 \le \Delta^{(2)}_{\beta} /  \left( pd^2 \cdot \frac{2\al^3 c^3}{(2\al c-1)^3}+ \bigo{p^{1/2+\e}d^2}\right) \le \bigbrace{1 + \sqrt{\frac{1}{\al c}}}^4. 
-\ee
-On the other hand, using Lemma \ref{lem_minv}, we have whp
-\be\label{reduceproof2} 
-\te_2(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{c-1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right).
-\ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
-
-Now for $c\ge 200$ and $\al \ge 1/2$, we have whp
-\be\label{reduceproof3} \te_2(\hat \beta(\al)) < \sigma^2 \frac{1}{2\al c - 1}+  \frac38 pd^2  \ee
-for large enough $p$. Moreover, if 
-$$\al \ge \al_0:=\frac{1}{2c} + \left(2-\frac{3}{4}c \cdot \frac{pd^2}{\sigma^2} \right)^{-1},$$
-we can check from \eqref{reduceproof3} that $\te_2(\hat \beta(\al))  < \te_2(\hat{\beta}_t^{\STL}) $.
-By symmetry, we also have $\te_1(\hat \beta(\al))  < \te_1(\hat{\beta}_t^{\STL}) $.
-Thus we conclude that
-$$\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$$
-for $\al\ge \al_0$, which shows that $\al^*\le \al_0$.
-\end{proof}
-
-\subsection{Proofs of Proposition \ref{prop_covariate} and Theoretical justification of Example \ref{ex_covariate}}\label{app_covariate}
-
-\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-
-	We have that the test error satisfies
-\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-where $\lambda_p$ is the smallest singular value of $p$ and
-$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-
-From equation \eqref{eq_a2}, we get
-$$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
-With these two bounds, we can easily conclude \eqref{approxteM}.
-
-For the second statement, we find that we need to minimize
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i},\quad \text{under}\ \ \prod_{i=1}^p\lambda_i=a^p.$$
-Then using AM-GM inequality, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-\end{proof}
-
-\begin{proof}[Theoretical justification of Example \ref{ex_covariate}]
-In the setting of Example \ref{ex_covariate}, equations in \eqref{eq_a2} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2},  \ \ a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
-\ee
-It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. After solving these, we get the test error for the target task as follows.
-\be\label{testcomple}
-te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
-
-First we notice that the curves in Figure \ref{fig_te_complement} all cross at the point $n_1=n_2$.
-In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
-$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-
-%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
-$M=\id$ case) when $n_1<n_2$.
-On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-This phenomenon can be also explained using our theory. With \eqref{compleeq}, we can write
-$$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
-We can compute that
-\begin{align*}
-te(\lambda) - te(1)&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)^2 a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-\end{align*}
-If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}), and hence $te(\lambda)>te(1)$.
-Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
-\end{proof}
-
-\iffalse
-Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
-
-\paragraph{A precise bound when there is no model shift.}
-As Proposition \ref{prop_monotone} shows, if $\beta_s$ and $\beta_t$ are equal, then adding the source task dataset always helps learn the target task.
-The goal of this section is to understand how covariate shift affects the rate of transfer. \todo{add conceptual msg}
-
-%The key quantity is to look at:
-%The estimator using the source and target together from minimizing \eqref{eq_mtl_basic} is
-%\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
-%The estimation error of $\hat{\beta}_{s,t}$ is
-%\begin{align}\label{eq_two_task}
-%  \err(\hat{\beta}_{s,t}) = \sigma^2 \cdot \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The estimation error using the target alone is
-%\begin{align}\label{eq_target_task}
-%	\err(\hat{\beta}_t) = \sigma^2 \cdot \tr[(X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The improvement of estimation error from adding the source task is then given by
-%$\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})$.
-%For the test error on the target task, the improvement from adding the source task is
-%\[ \te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t}) = \sigma^2\cdot\bigtr{\bigbrace{(X_2^{\top}X_2)^{-1} - (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}\cdot\Sigma_2}. \]
-
-%We calculate the amount of improvement by comparing equation \eqref{eq_two_task} to equation \eqref{eq_target_task}.
-A simple observation here is that when $\beta_s = \beta_t$, the optimal $\hat{w}$ for minimizing equation \eqref{eq_te_mtl} is equal to $1$.
-Based on this observation, we can get a more precise result than Theorem \ref{thm_model_shift} on the improvement of adding the source task data that only depends on the covariance matrices $\Sigma_1, \Sigma_2$ and the number of data points $n_1, n_2$.
-
-\begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
-Suppose $\beta_s = \beta_t$ and $\|\beta_t\|_2^2\sim p\sigma^2$ (i.e.
-the $l^2$-norm of the vector $\beta_t$ is of the same order as that of the error vector).
-Assume that the condition numbers of $\Sigma_1$, $\Sigma_2$ and $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all bounded by a constant $C>0$.
-Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies
-	$$1\le \hat{w} \le 1+\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-	%where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-Moreover, we have
-	\begin{align}\label{tehatw1}
-		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
-		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1 M^\top M  + (n_1 + n_2)a_2\id}^{-1}} \cdot \left(1+ \bigo{p^{-1}}\right),
-	\end{align}
-where $a_1, a_2$ are the solutions to equations \eqref{eq_a2}. %\cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
-\end{proposition}
-
-\begin{proof}
-We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
-Note that $\val(w)\le \val(-w)$ for $w\ge 0$.
-Hence we have $\hat w\ge 0$.
-Moreover, we notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
-Thus we have $\hat w\ge 1$.
-It suffices to consider the case with $w> 1$.
-Under the assumption on $\beta_s$ and $\beta_t$, we can write
-\begin{align}
-	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
-			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
-\end{align}
-Since
-\begin{align*}
-&\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \\
-&= \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]
-\end{align*}
-is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
-\begin{align*}
-\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
-			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
-\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}.
-			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
-\end{align*}
-Hence $\val'(w)\ge 0$ if $w>1+ \e_0$, where
-$$\e_0:= \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2}.$$
-In other words, $\val(w)$ is strictly increasing function on $[1+\e_0,\infty]$. Thus we get that $\hat w$ satisfies
-\be\label{hatw1}1\le w \le 1+\e_0.\ee Using \eqref{eq_isometric}, we get that
-$$\e_0=\OO(\sigma^2/\|\beta_t\|_2^2)=\OO(p^{-1}).$$
-
-Finally, plugging \eqref{hatw1} into the expression $\te(\hat{\beta}^{\TL}_{t}) $, we obtain \eqref{tehatw1}.
-%$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$
-\end{proof}
-
-As a remark, we see that Proposition \ref{prop_monotone} follows from Theorem \ref{thm_cov_shift}.
-The amount of reduction on test error for the target task is given as
-	\begin{align*}
-%		\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})
-%		&= \sigma^2 p \cdot \bigtr{\frac 1 {(n_2 - p) \Sigma_2} - \frac 1 {(n_1 + n_2)a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2}}, \\
-		\te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t})
-		&= \sigma^2 \cdot \bigbrace{\frac p {n_2 - p} -  \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}}}.
-	\end{align*}
-Because
-\begin{align*}
-	\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)
-	\Leftarrow~ & (n_2 - p)\Sigma_2 \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2 \\
-	\Leftrightarrow~ & \zeroMatrix \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 - (n_1 + n_2)\cdot a_1) \Sigma_2,
-\end{align*}
-which is true since $a_1 \le n_1 / (n_1 + n_2)$ by equation \eqref{eq_a2}.
-The proof for $\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)$ follows by multiplying $\Sigma_2^{-1/2}$ on both sides of the inequalities above.
-
-\medskip
-\fi

### 2020-05-25 writeup/proof_taskonomy.tex
transfer wip

--- 2020-05-20 writeup/extension_transfer.tex
@@
-\section{Extension to Transfer Learning}
+\section{Extension to the Transfer Function of Taskonomy}
 
@@
 This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
-Then, we learn the output layer on the target task.
-We use our tools to analyze this setting as follows.
+Then, we learn the output layer on the target task by solving equation \eqref{eq_mtl}.
+We use our tools to compare the estimator of this setting to single-task learning.
 

### 2020-05-25 writeup/transfer.tex
restructure sec 3
edits
transfer wip

@@
-\section{Dissecting the Effects of Different Task Data in Multi-Task learning}\label{sec_insight}
+\section{Positive versus Negative Transfer in Multi-Task learning}
+\label{sec_insight}
 
@@
 
-\subsection{Task Model Similarity}\label{sec_dist}
+\subsection{Task Model Similarity}\label{sec_similarity}
 
@@
 
-\subsection{Data Size and Efficiency}\label{sec_data}
+\subsection{Data Size and Efficiency}\label{sec_data_size}
 
@@
 \textbf{Implications.}
-
-\section{Extension to the Transfer Function of Taskonomy}
-
-We study the transfer function of taskonomy \cite{ZSSGM18}.
-The algorithm is as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
-This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
-Then, we learn the output layer on the target task.
-We use our tools to analyze this setting as follows.

### 2020-05-25 writeup/proof_taskonomy.tex
clarify

@@
 First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
-This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
-Then, we learn the output layer on the target task by solving equation \eqref{eq_mtl}.
-We use our tools to compare the estimator of this setting to single-task learning.
+This forms the shared representation $B = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{k-1}]$.
+Then, we learn the output layer $W_k$ on the target task by solving equation:
+\begin{align}
+	\bignorm{X_k B W_k - Y_k}^2
+\end{align}
+After getting $W_k$, we use $B W_k$ as estimator and $\te(B W_k)$ is the test error of the estimator
+We use our tools to compare $\te(B W_k)$ to $\te(\beta_k^{\STL})$.
 

### 2020-05-25 writeup/proof_taskonomy.tex
pf taskonomy

@@
 
-The projection of $\beta_t$ onto the subspace spanned by $(\beta_1,\cdots, \beta_k)$ is 
-$$\hat \beta_t = \sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|} \beta_i .$$
-On the other hand, the single task estimator $\hat\beta_i$ is given by 
-$$\hat \beta_i = \beta_i + (X_i^\top X_i)^{-1}X_i \e_i.$$
-Then the projection of $\beta_t$ onto the subspace spanned by $(\hat\beta_1,\cdots, \hat\beta_k)$ is 
-$$ \hat \beta_t'= \sum_{i=1}^k\frac{\beta_t^\top \hat \beta_i}{\|\hat \beta_i\|} \hat \beta_i .$$
-We now calculate the estimation error $ \exarg{\varepsilon_i, \forall 1\le i\le k} {\|\hat \beta_t - \hat\beta_t'\|^2}.$ Without loss of generality, we assume that $\|\beta_i\|^2 \sim 1$ for all $1\le i \le k$ and $\sigma^2\le n^{-c}$ for some constant $c>0$.
-Then we calculate that
+For each task $i$, $1\le i \le k-1$, we can find that  
+$$\hat \beta_i = \beta_i + (X_i^\top X_i)^{-1}X_i^\top \e_i.$$
+We assume that $\sigma^2=\OO(1)$, $\|\beta_i\|^2 =\OO(1)$ for all $1\le i \le k$ and %$\sigma^2\ll 1$, i.e. the error is sufficiently small. Moreover, we make the extra assumption that 
+\be\label{BTBassm}
+\|(B_0^\top B_0)^{-1}\|\le C,\quad B_0: = [{\beta}_1,{\beta}_2,\dots,{\beta}_{k-1}], 
+\ee
+for some constant $C>0$. Then we calculate that
 \begin{align*}
-\|\hat\beta_i\|^2 &= \|\beta_i\|^2 + 2\beta_t^\top\cdot (X_i^\top X_i)^{-1}X_i \e_i + \|(X_i^\top X_i)^{-1}X_i \e_i \|^2 .
+\|\hat\beta_i\|^2 &= \|\beta_i\|^2 + 2\beta_i^\top\cdot (X_i^\top X_i)^{-1}X_i^\top \e_i + \|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 .
 \end{align*}
@@
 \be\label{largebetae}
-\beta_t^\top (X_i^\top X_i)^{-1}X_i \e_i  \le p^{\e/2}\cdot \sigma \left[\beta_t^\top (X_i^\top X_i)^{-1}\beta_t \right]^{1/2}\le \sigma p^{-1/2+\e},  
+\beta_t^\top (X_i^\top X_i)^{-1}X_i^\top \e_i  \le p^{\e/2}\cdot \sigma \left[\beta_t^\top (X_i^\top X_i)^{-1}\beta_t \right]^{1/2}\le \sigma p^{-1/2+\e},  
 \ee
@@
 \begin{split}
- \|(X_i^\top X_i)^{-1}X_i \e_i \|^2 - \sigma^2 \tr\left( (X_i^\top X_i)^{-1} \right)   \le p^{\e/2}\cdot \sigma^2 \left\{\tr\left[X_i^\top (X_i^\top X_i)^{-2}X_i\right]^2\right\}^{1/2} \\
+ \left|\|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 - \sigma^2 \tr\left( (X_i^\top X_i)^{-1} \right)\right|   \le p^{\e/2}\cdot \sigma^2 \left\{\tr\left[X_i (X_i^\top X_i)^{-2}X_i^\top\right]^2\right\}^{1/2} \\
  = p^{\e/2}\cdot \sigma^2 \left[ \tr (X_i^\top X_i)^{-2} \right]^{1/2} \le \sigma^2 p^{-1/2+\e},  
@@
 \|\hat\beta_i\|^2&= \|\beta_i\|^2 + \sigma^2\cdot \tr \left( (X_i^\top X_i)^{-1}\right) +\OO(\sigma p^{-1/2+\e}) \nonumber\\
-&=  \|\beta_i\|^2 + \frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) +\OO(\sigma p^{-1/2+\e}) ,\label{betanormi}
+&=  \|\beta_i\|^2 + \frac{\sigma^2}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) +\OO(\sigma p^{-1/2+\e}) ,\label{betanormi}
 \end{align}
-where in the second step we used Lemma \ref{lem_minv}.
+where in the second step we used Lemma \ref{lem_minv}. Similarly, we have
+\begin{align}\label{betanormij}
+\hat\beta_i^\top \hat \beta_j &=  \hat\beta_i^\top \hat\beta_j + \OO(\sigma p^{-1/2+\e})  ,
+\end{align}
+using \eqref{largebetae} and the concentration bound
+\be\nonumber%\label{largebetae3}
+\begin{split}
+\left| \e_j^\top X_j (X_j^\top X_j)^{-1}(X_i^\top X_i)^{-1}X_i^\top \e_i \right| \le   p^{\e/2}\cdot \sigma^2 \left\{ \tr \left[(X_i^\top X_i)^{-1}(X_j^\top X_j)^{-1}\right] \right\}^{1/2} \le \sigma^2 p^{-1/2+\e},
+ \end{split}
+\ee
+by Lemma \ref{largedeviation}. With \eqref{betanormi} and \eqref{betanormij}, we obtain that with high probability,
+\be\label{BTB}
+B^\top B=  B_0^\top B_0 + \cal M +\OO(\sigma p^{-1/2+\e}),
+\ee
+where $\cal M$ is a diagonal matrix with $\cal M_{ii}=\frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right)$ and $\OO(\sigma p^{-1/2+\e})$ means a $(k-1)\times (k-1)$ matrix, say $\cal E$, satisfying $\|\cal E\|\le C\sigma p^{-1/2+\e}$.
+Notice that by \eqref{BTBassm}, we also have
+$$\|(B^\top B)^{-1}\|\lesssim 1.$$
+Finally, using \eqref{largebetae} we can get that
+\be\label{BTBeta}
+B^\top \beta =  B_0^\top \beta + \OO(\sigma p^{-1/2+\e}),
+\ee
+for any deterministic vector $\|\beta\|$ of order 1.
 
-For simplicity we abbreviate $v_i:=(X_i^\top X_i)^{-1}X_i \e_i$. Then using \eqref{largebetae} and \eqref{betanormi} we can calculate that whp,
+For the $k$-th target model, by optimizing over $W_k$ we get
+$$\hat W_k= (B^\top X_k^\top X_k B)^{-1} B^\top X_k^\top Y_k =(B^\top X_k^\top X_k B)^{-1} B^\top X_k^\top (X_k \beta_k + \e_k) .$$
+We then calculate that 
+\be
+\begin{split}
+\exarg{\varepsilon_k} {\left\|\Sigma_k^{1/2}(B\hat W_k -\beta_k)\right\|^2} &= \left\| \Sigma_k^{1/2}\left[\id - B(B^\top X_k^\top X_k B)^{-1} B^\top X_k^\top X_k\right] \beta_k \right\|^2 \\
+&+\sigma^2\cdot \tr \left[\Sigma_k (B^\top X_k^\top X_k B)^{-1}\right]. \label{EBWk}
+%\\&= \sigma^2\cdot \tr (B^\top X_k^\top X_k B)^{-1} + \left\|\beta_k\right\|^2 - 2 \beta_k^\top B(B^\top X_k^\top X_k B)^{-1} B^\top X_k^\top X_k \beta_k \nonumber\\
+%&+ \beta_k^\top X_k^\top X_k B(B^\top X_k^\top X_k B)^{-1}B^\top B (B^\top X_k^\top X_k B)^{-1}B^\top X_k^\top X_k \beta_k.\label{EBWk}
+\end{split}
+\ee
+By the concentration of random vector with independent entries or the restricted isometry property for $X_k B$, we have with high probability, 
+$$ B^\top X_k^\top X_k B = n_k B^\top B\cdot \left( 1 + \OO(p^{-1/2+\e})\right),\quad B^\top X_k^\top X_k \beta_k = n_k B^\top \beta_k \cdot \left( 1 + \OO(p^{-1/2+\e})\right).$$
+Together with \eqref{BTB} and \eqref{BTBeta}, we can simplify the right-hand side of \eqref{EBWk} as
 \begin{align*}
-&\|\hat \beta_t - \hat\beta_t'\|^2= \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|} \beta_i - \sum_{i=1}^k\frac{\beta_t^\top (\beta_i + v_i)}{ \|\beta_i +v_i\| }(\beta_i + v_i) \right\|^2 \\
-&=  \left\|\sum_{i=1}^k\left(\frac{\beta_t^\top \beta_i}{\|\beta_i\|}-\frac{\beta_t^\top \beta_i}{\|\beta_i+v_i\|} \right)\beta_i - \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i+v_i\| } v_i - \sum_{i=1}^k\frac{\beta_t^\top v_i}{ \|\beta_i +v_i\| } (\beta_i+v_i) \right\|^2 \\
-%& = \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|}\left(1-\frac{\|\beta_i\|}{(\|\beta_i\|^2 + 2\beta_i^\top v_i + \|v_i\|^2)^{1/2}} \right)\beta_i - \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|+\OO(\sigma^2 + \sigma p^{-1/2+\e}) } v_i\right\|^2 + \OO\left(\sigma^2 p^{-1+2\e}\right) \\
-%&= \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|}\frac{2\beta_i^\top v_i + \|v_i\|^2}{2\|\beta_i\|^2}\beta_i \right\|^2+\left\| \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|} v_i\right\|^2 + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right)
-&= \left\| \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|} v_i\right\|^2 + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right).
+\exarg{\varepsilon_k} {\left\|\Sigma_k^{1/2} (B\hat W_k -\beta_k)\right\|^2} &=\left\|\Sigma_k^{1/2} \beta_k - \Sigma_k^{1/2} B(B^\top B)^{-1} B^\top \beta_k \right\|^2 + \OO(p^{-1/2+\e}) \\
+&=\left\|\Sigma_k^{1/2} \beta_k - \Sigma_k^{1/2} B(B_0^\top B_0 +\cal M)^{-1} B_0^\top \beta_k \right\|^2 + \OO(p^{-1/2+\e}). 
 \end{align*}
-Thus taking expectation, we get that 
+As in \eqref{BTB}, we can show by concentration that 
+\be\label{BTB2}
+B^\top \Sigma_k B=  B_0^\top \Sigma_k B_0 +\wt{ \cal M} +\OO(\sigma p^{-1/2+\e}),
+\ee
+where $\wt{\cal M}$ is a diagonal matrix with $\wt{\cal M}_{ii}=\frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\Sigma_k\right)$.
+Together with \eqref{BTB} and \eqref{BTBeta}, we can further simplify that
 \begin{align*}
-\exarg{\varepsilon_i, \forall 1\le i\le k} {\|\hat \beta_t - \hat\beta_t'\|^2}&=   \sum_{i=1}^k\frac{\left|\beta_t^\top \beta_i \right|^2}{ \|\beta_i\|^2 } \cdot \sigma^2 \tr \left( (X_i^\top X_i)^{-1}\right) + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right) \\
- &= \sum_{i=1}^k\frac{\left|\beta_t^\top \beta_i \right|^2}{ \|\beta_i\|^2 } \cdot \frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) + \OO\left(\sigma^4+\sigma^2 p^{-1/2+2\e}\right) .
+&\exarg{\varepsilon_i, \forall 1\le i\le k} {\left\|\Sigma_k^{1/2} (B\hat W_k -\beta_k)\right\|^2}= \left\|\Sigma_k^{1/2} \beta_k\right\|^2 - 2\beta_k^\top \Sigma_k B_0 (B_0^\top B_0 +\cal M)^{-1} B_0^\top \beta_k  \\
+&+ \beta_k^\top B_0 (B_0^\top B_0 +\cal M)^{-1} \left(B_0^\top \Sigma_k B_0 + \wt{\cal M}\right) (B_0^\top B_0 + {\cal M})^{-1}  B_0^\top \beta_k+ \OO(p^{-1/2+\e})\\
+& = \left\|\Sigma_k^{1/2} \beta_k - \Sigma_k^{1/2} B_0(B_0^\top B_0 +\cal M)^{-1} B_0^\top \beta_k \right\|^2  + \left\|\wt{\cal M}^{1/2}(B_0^\top B_0 + {\cal M})^{-1}  B_0^\top \beta_k \right\|^2+ \OO(p^{-1/2+\e}).
 \end{align*}
-Note the first term is of order $\sigma^2$, and hence the second stem is an error term.

### 2020-05-25 writeup/transfer.tex
sec 3 wip

@@
-\section{Positive versus Negative Transfer in Multi-Task learning}
+\section{Revisiting the Bias-Variance Trade-off for Multi-Task learning}
 \label{sec_insight}
@@
 
-\subsection{Model Shift Bias versus Variance Trade-off}\label{sec_main}
+\subsection{Two Effects: Model Shift Bias and Variance Reduction}\label{sec_main}
 
@@
 
-\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}
+%\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}
 
@@
 
-\textbf{Implications.} \todo{add connection to tasksonomy}
+\textbf{Implications.}
 

### 2020-05-25 writeup/transfer.tex
sec 2 wip

@@
 
-We illustrate our main results (to be presented in Section \ref{sec_main}) by considering a few special cases, namely special settings of the task models $\set{\beta_i}_{i=1}^k$, covariance matrices $\set{\Sigma_i}_{i=1}^k$, and number of data points $\set{n_i}_{i=1}^k$.
-We show that our results explain several phenomenon that cannot be explained before.
-\todo{list those here}
+We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
+For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^k$, covariance matrices $\set{\Sigma_i}_{i=1}^k$, and number of data points $\set{n_i}_{i=1}^k$.
+After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
+Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
 
@@
 
+\textbf{Notations.}
 We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
@@
 
-\textbf{The High-Dimensional Setting.}
+%\textbf{The High-Dimensional Setting.}
 %\todo{setup motivation and notations}
@@
 
-\textbf{Two Tasks with General Covariance Matrices.}
+\textbf{Setting one: Two tasks with general covariance matrices.}
 For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
@@
 
-\textbf{Many Tasks with the Same Covariates.}
+\textbf{Setting two: Many tasks with the same covariates.}
 We extend the above result to any number of tasks that have the same covariates.

### 2020-05-25 writeup/setup.tex
re-structure
wip

@@
 Concretely, we focus on the test error for the target task:
-%\begin{itemize}
-%	\item Estimation error for the target model $\beta_t$: we consider their distance
-%		\[ \err(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
 	\begin{align*}
@@
 	\end{align*}
-%\end{itemize}
 
-\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}
-
-%\paragraph{Hypothesis on Heterogeneous Task Data}
-
-%Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}.
-%\todo{Add some references to add spice on these takes.}
-%We consider two natural questions within each category.
-%\begin{itemize}
-%	\item \textbf{Model shift.}
-%	In general the single-task models can also be different across different tasks.
-%We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.
-
-%	Under model shift, when do we get positive vs. negative transfer?
-%	How does the type of transfer depend on the number of data points, the distance of the task models etc?
-%	\item \textbf{Covariate shift.}
-%	The covariance matrices $\Sigma_i$ may be be different across tasks, i.e. having different spectrum or singular vectors.
-%This is also known as covariate shift in the literature.
-%	How does covariate shift affect the rate of information transfer?
-%	For example, is it better to have the same covariance matrix or not?
-%\end{itemize}
-
-\paragraph{The High-Dimensional Setting.}
-%\todo{setup motivation and notations}
 We would like to get insight on how covariate and model shifts affect the rate of transfer.
@@
 Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
-% \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,
+%
+
+\textbf{Model shift bias.}
+
+We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
+Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
+The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
+We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
+We compare it with the asympotic limit of $\te(\hat{\beta}_t^{\STL})$, for settings where the target data size is limited.
+We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.
+
+\textbf{Variance reduction.}
+
+For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
+\begin{align}
+	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
+	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
+\end{align}
+where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
+It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
+\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
+Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.

### 2020-05-25 writeup/transfer.tex
wip

@@
 We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
-For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^k$, covariance matrices $\set{\Sigma_i}_{i=1}^k$, and number of data points $\set{n_i}_{i=1}^k$.
+For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
 After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
@@
 
-\subsection{Two Effects: Model Shift Bias and Variance Reduction}\label{sec_main}
+\subsection{Determining Positive versus Negative Transfer}\label{sec_main}
 
-\textbf{Notations.}
-We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
-We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector that has i.i.d. entries with mean $0$ and variance $1$.
-We will designate the $k$-th task as the target.
-Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
-Concretely, we focus on the test error for the target task:
-	\begin{align*}
-		\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
-		&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
-	\end{align*}
-%\end{itemize}
-
-%\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}
-
-%\textbf{The High-Dimensional Setting.}
-%\todo{setup motivation and notations}
-We would like to get insight on how covariate and model shifts affect the rate of transfer.
-We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
-This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
-Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.
-
-For the case of two tasks, we can get precise rates using random matrix theory.
-For the sake of clarity, we call task 1 the source task and task 2 the target task,
-i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
-We introduce the following notations for the high-dimensional setting
-\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
-for some constants $c_1, c_2 \in (1,\infty)$.
-A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
-%
-
-%In this part, we consider the case of two tasks to show  establish the intuition that adding more data helps in multi-task learning by reducing the variance of the estimator.
-%We achieve this through tight generalization bounds obtained from random matrix theory.
-%For the case of two tasks, we identify three factors that determine the type of transfer between tasks: model distance, covariate shift matrix, and data ratio.
-We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
-One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
-Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
-The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
-We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
-We compare it with the asympotic limit of $\te(\hat{\beta}_t^{\STL})$, for settings where the target data size is limited.
-We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.
-
-\textbf{Setting one: Two tasks with general covariance matrices.}
-For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
-\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
-	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
-\end{align}
-where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
-It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
-\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
-Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
-%The main result of this section show deterministic conditions under which we get positive or negative transfer.
-%And the conditions depend only on the covariate shift matrix $M$, the difference of the task models, and the number of per-task data points.
 The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
@@
 
-\begin{theorem}\label{thm_main_informal}
+\textbf{First setting: Two tasks with general covariance matrices.}
+
+\begin{theorem}[Informal]\label{thm_main_informal}
 	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
@@
 
-\textbf{Setting two: Many tasks with the same covariates.}
+\textbf{Second setting: Many tasks with the same covariates.}
 We extend the above result to any number of tasks that have the same covariates.

### 2020-05-25 writeup/experiments.tex

@@
 
-\paragraph{A metric to determine when MTL performs better STL.}
+\subsection{Experimental Setup}
+
+{\bf Datasets and models.} We describe the datasets and models we use in the experiments.
+
+{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
+
+{For each task, the goal is to categorize sentiment opinions expressed in the text.
+We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}\footnote{We also tested with multi-layer perceptron and CNN.
+The results are similar (cf.
+Appendix \ref{label:real_result_details}).}.
+}
+%multi-layer perceptron (MLP), LSTM, CNN on all tasks
+%We use this task to verify our theoretical results on model capacity and task covariance in real world.
+
+{\it ChestX-ray14:} This dataset contains 112,120 frontal-view X-ray images and each image has up to 14 diseases.
+This is a 14-task multi-label image classification problem.
+%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
+%This dataset is curated where the labels
+%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
+
+For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.
+
+\subsection{Results and Analysis}
+
+\textbf{A metric to determine positive versus negative transfer.}
+We propose a simple metric to determine whether multi-task learning performs better than single-task learning.
+The metric is as follows.
+First, we train 2 single-task models on 2 separate tasks.
+We take the prediction accuracy of the two tasks.
+Let $\tau$ be a fixed threshold.
+If the accuracy of the source task is higher than the accuracy of the target task by $\tau$, then we predict positive transfer.
+On the other hand, if the accuracy of the source task is lower than the accuracy of the target task by $\tau$, then we predict negative transfer.
+
+Table \ref{tab:mtl_better_than_stl} shows the results on a sentiment analysis and an image classification task.
+
 \begin{table}
@@
 
-\paragraph{When should we align task covariances in MTL.}
-\begin{figure}
+\textbf{Measuring data efficiency ratio.}
+We measure the data efficiency ratio on text classification tasks.
+We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.
+
+\textbf{Data size affects covariance alignment.}
+We validate that the performance of aligning task covariances depends on the size of source task data.
+Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+
+In Figure \ref{fig_covariate}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.
+
+\begin{figure}[!ht]
 	\centering
-	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-	\caption{Covariate shift experiment.}
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_lstm.pdf}
+		\caption{LSTM (averaged)}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_mlp.pdf}
+		\caption{MLP (averaged)}
+	\end{subfigure}\hfill
+		\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+		\caption{LSTM for one pair}
+	\end{subfigure}
+	\caption{The performance of aligning task covariances depends on data size.}
+	\label{fig_covariate}
 \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mlp.pdf}
-	\caption{Covariate shift experiment.}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mlp.pdf}
+%	\caption{Covariate shift experiment.}
+%\end{figure}

### 2020-05-25 writeup/setup.tex
sec 2

@@
 
-We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
-We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector that has i.i.d. entries with mean $0$ and variance $1$.
-We will designate the $k$-th task as the target.
-Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
-Concretely, we focus on the test error for the target task:
+Recall that we have $t$ labeled tasks available, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$.
+Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d.
+entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
+Without loss of generality, let the $t$-th task denote the target task.
+For an estimator $\hat{\beta}\in\real^p$, the test error for target task is defined as
 	\begin{align*}
-		\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
-		&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
+		\te_t(\hat{\beta}) \define \exarg{z}{\exarg{\varepsilon_t}{({(\Sigma_t^{1/2} z)}^{\top}\hat{\beta} - {(\Sigma_t^{1/2})}^{\top}\beta_t)^2}}
+		= \exarg{\varepsilon_t}{(\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)}.
 	\end{align*}
 
-We would like to get insight on how covariate and model shifts affect the rate of transfer.
-We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
-This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
-Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.
+Let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$ denote the linear regression estimator, which can be also be obtained from equation \eqref{eq_mtl} by using the target task alone.
+The bias-variance trade-off \cite{HTF09} says that
+	\[ \te_t(\hat{\beta}) =
+		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}. \]
+Recall that we assume $n_i > p$ for every $1\le i\le t$.
+Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $\sigma^2 \cdot \tr{(X_i^{\top}X_i)^{-1}\Sigma_i}$.
+
+For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
+\begin{align}
+	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
+	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
+\end{align}
+where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
 
@@
 
-For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
-\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
-	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
-\end{align}
-where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
 It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.

### 2020-05-25 writeup/intro.tex

@@
 In this work, we consider multiple high-dimensional linear regression tasks as input and focus on predicting a particular task that only has limited amount of labeled data.
-Concretely, each task consists of $n_i$ datapoints in space $\real^p$ organized as matrix $X_i\in\real^{n_i\times p}$, for $1\le i\le p$.
+Concretely, each task consists of $n_i$ datapoints in space $\real^p$ organized as matrix $X_i\in\real^{n_i\times p}$, for $1\le i\le t$.
 The labels of $X_i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i$ denotes the ground truth parameters for task $i$ and $\varepsilon_i$ denotes i.i.d.
@@
 %distribution with covariance matrix $\Sigma_i$.
-We use a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^k$ for each task \cite{R17,MTDNN19}.
+We use a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19}.
 %    \paragraph{Different covariates:}
@@
 	\label{eq_mtl}
-	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
+	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2.
 \end{align}

### 2020-05-25 writeup/setup.tex

@@
 Recall that we assume $n_i > p$ for every $1\le i\le t$.
-Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $\sigma^2 \cdot \tr{(X_i^{\top}X_i)^{-1}\Sigma_i}$.
+Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $\sigma^2 \cdot \tr[(X_i^{\top}X_i)^{-1}\Sigma_i]$.
+We focus on a setting where the data size $n_t$ of the target task is equal to a small constant $\rho_t > 1$ times $p$.
+This setting captures the need for adding more labeled data to reduce the test error of the target task.
 
-For the case of two tasks, we decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts
+To illustrate our intuition, we begin by considering the multi-task learning setting with one source task.
+Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
+We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts (to be derived in Appendix \ref{app_proof_main})
 \begin{align}
-	\te(\hat{\beta}_t^{\MTL}) =& \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \nonumber \\
-	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_model_shift}
+	\te_t(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
+	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
 \end{align}
-where $\hat{v}$ denotes the ratio of the output layer weights (to be defined more precisely in Appendix \ref{app_proof_main}).
+where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
+By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
 
-For the case of two tasks, we can get precise rates using random matrix theory.
-For the sake of clarity, we call task 1 the source task and task 2 the target task,
-i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
-We introduce the following notations for the high-dimensional setting
-\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
-for some constants $c_1, c_2 \in (1,\infty)$.
-A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
-%
-
-\textbf{Model shift bias.}
-
-We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
-One part captures how similar the task models are and the other part captures the variance of $\hat{\beta}_t^{\MTL}$.
-Compared with $\hat{\beta}_t^{\STL}$, we observe that the variance part of $\hat{\beta}_t^{\MTL}$ gets reduced, since more data is added from source tasks.
-The bias part of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, affects performance negatively.
-We derive the asympotic limit of $\te(\hat{\beta}_t^{\MTL})$ as $p$ approaches infinity.
-We compare it with the asympotic limit of $\te(\hat{\beta}_t^{\STL})$, for settings where the target data size is limited.
-We show sharp generalization bounds for two settings: i) two tasks with general covaraites; ii) many tasks with the same covariates.
+\textbf{Model-shift bias.}
+%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
+This part introduces a negative effect to multi-task learning.
+The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+The output layer of each task scales the direction of $B$ suitably to fit the task.
 
 \textbf{Variance reduction.}
+Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+This part introduces a positive variance reduction effect to performing multi-task learning.
+Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
+(i) the positive effect from variance reduction;
+(ii) the negative effect from model shift bias.
 
-It is not hard to see that the variance of $\hat{\beta}_t^{\MTL}$ is reduced compared to $\hat{\beta}_t^{\STL}$, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
-\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
-Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
+%, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
+%\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
+%Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
+
+\textbf{Notations.} For the sake of clarity, we denote the first task as the source task and last ($t$-th) task as the target task.

### 2020-05-26 writeup/experiments.tex
update figure 2

@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_lstm.pdf}
+		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
 		\caption{LSTM (averaged)}
@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_norm_mlp.pdf}
+		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
 		\caption{MLP (averaged)}
@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
 		\caption{LSTM for one pair}

### 2020-05-26 writeup/proof_taskonomy.tex
sec D

--- 2020-05-25 writeup/proof_taskonomy.tex
@@
 The algorithm is as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
-This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
-Then, we learn the output layer on the target task by solving equation \eqref{eq_mtl}.
-We use our tools to compare the estimator of this setting to single-task learning.
+First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le t$.
+This forms the shared representation $B = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+Then, we learn the output layer $W_t$ on the target task by solving equation:
+\begin{align}
+	\bignorm{X_t B W_t - Y_t}^2
+\end{align}
+After getting $W_t$, we use $B W_t$ as estimator and $\te(B W_t)$ is the test error of the estimator.
+We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
 
-The projection of $\beta_t$ onto the subspace spanned by $(\beta_1,\cdots, \beta_k)$ is 
-$$\hat \beta_t = \sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|} \beta_i .$$
-On the other hand, the single task estimator $\hat\beta_i$ is given by 
-$$\hat \beta_i = \beta_i + (X_i^\top X_i)^{-1}X_i \e_i.$$
-Then the projection of $\beta_t$ onto the subspace spanned by $(\hat\beta_1,\cdots, \hat\beta_k)$ is 
-$$ \hat \beta_t'= \sum_{i=1}^k\frac{\beta_t^\top \hat \beta_i}{\|\hat \beta_i\|} \hat \beta_i .$$
-We now calculate the estimation error $ \exarg{\varepsilon_i, \forall 1\le i\le k} {\|\hat \beta_t - \hat\beta_t'\|^2}.$ Without loss of generality, we assume that $\|\beta_i\|^2 \sim 1$ for all $1\le i \le k$ and $\sigma^2\le n^{-c}$ for some constant $c>0$.
+\begin{proposition}\label{prop_taskonomy}
+Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, \cdots, t$, where $\e_i$ are random vectors with i.i.d.
+entries of mean zero and variance $\sigma^2$.
+Let $\rho_i>1$, $1\le i \le t$ be fixed constants.
+Assume that $\max_{1\le i \le t}\|\beta_i\|=\OO(1)$, $\sigma^2=\OO(1)$ and
+\be\label{BTBassm}
+\left\|\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1}\right\|=\OO(1),\quad B_{t-1}^{\star}: = [{\beta}_1,{\beta}_2,\dots,{\beta}_{t-1}].
+\ee
+Suppose that all random variables have subexponential decay. Then we have with high probability,
+\be\label{eq_taskonomy}
+\te(B W_t) =\|\e_\beta + \sigma^2 \e_{\vari}^{(1)}\|^2+ \sigma^2 \|\e_{\vari}^{(2)}\|^2 + \OO(p^{-1/2+\e}),
+\ee
+where $B^{\star}_{t-1} := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t-1}]$, and
+\begin{align*}
+&\e_\beta:= \Sigma_k^{1/2}\left\{1 - B^\star_{t-1}\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1} (B^\star_{t-1})^\top\right\} \beta_t,\\
+&\e_{\vari}^{(1)}:=  \Sigma_k^{1/2}  B^\star_{t-1}\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1}\cal M_1 \left[(B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1\right]^{-1} (B^\star_{t-1})^\top \beta_t,\\
+&\e_{\vari}^{(2)}:= \cal M_2^{1/2}\left[(B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1\right]^{-1} (B^\star_{t-1})^\top \beta_t.
+\end{align*}
+Here $\cal M_1$ and $\cal M_2$ are $k\times k$ diagonal matrices with $(\cal M_1)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right)$ and $(\cal M_2)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\Sigma_k\right)$.
+\end{proposition}
+
+\begin{proof}[Proof of Proposition \ref{prop_taskonomy}]
+For each task $i$, $1\le i \le t-1$, we can find that  
+$$\hat \beta_i = \beta_i + (X_i^\top X_i)^{-1}X_i^\top \e_i.$$
 Then we calculate that
 \begin{align*}
-\|\hat\beta_i\|^2 &= \|\beta_i\|^2 + 2\beta_t^\top\cdot (X_i^\top X_i)^{-1}X_i \e_i + \|(X_i^\top X_i)^{-1}X_i \e_i \|^2 .
+\|\hat\beta_i\|^2 &= \|\beta_i\|^2 + 2\beta_i^\top\cdot (X_i^\top X_i)^{-1}X_i^\top \e_i + \|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 .
 \end{align*}
-We can use concentration of random vector with independent entries, Lemma \ref{largedeviation}, to get that for any $\e>0$,
+We can use concentration of random vector with independent entries, Lemma \ref{largedeviation}, to get that for any deterministic vector $\beta$ with $\|\beta\|=\OO(1)$,
 \be\label{largebetae}
-\beta_t^\top (X_i^\top X_i)^{-1}X_i \e_i  \le p^{\e/2}\cdot \sigma \left[\beta_t^\top (X_i^\top X_i)^{-1}\beta_t \right]^{1/2}\le \sigma p^{-1/2+\e},  
+\beta^\top (X_i^\top X_i)^{-1}X_i^\top \e_i  \le p^{\e/2}\cdot \sigma \left[\beta^\top (X_i^\top X_i)^{-1}\beta \right]^{1/2}\le \sigma p^{-1/2+\e},  
 \ee
-with high probability, and 
+with high probability for any constant $\e>0$, where we used Lemma \ref{SxxSyy} to bound 
+\be\label{opXiXi}\| (X_i^\top X_i)^{-1}\|\lesssim n_i^{-1} \quad \text{whp}. \ee
+Similarly, using Lemma \ref{largedeviation} we get with high probability,
 \be\label{largebetae2}
 \begin{split}
- \|(X_i^\top X_i)^{-1}X_i \e_i \|^2 - \sigma^2 \tr\left( (X_i^\top X_i)^{-1} \right)   \le p^{\e/2}\cdot \sigma^2 \left\{\tr\left[X_i^\top (X_i^\top X_i)^{-2}X_i\right]^2\right\}^{1/2} \\
+ \left|\|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 - \sigma^2 \tr\left( (X_i^\top X_i)^{-1} \right)\right|   \le p^{\e/2}\cdot \sigma^2 \left\{\tr\left[X_i (X_i^\top X_i)^{-2}X_i^\top\right]^2\right\}^{1/2} \\
  = p^{\e/2}\cdot \sigma^2 \left[ \tr (X_i^\top X_i)^{-2} \right]^{1/2} \le \sigma^2 p^{-1/2+\e},
@@
 \ee 
-with high probability, where we used Theorem \ref{LEM_SMALL} to get that
-$$\beta_t^\top (X_i^\top X_i)^{-1}\beta_t  \le p^{-1+\e/2} \quad \text{and}\quad \tr \left[ (X_i^\top X_i)^{-2} \right]  \le p^{-1+\e/2} \quad \text{whp}.$$
-Thus we get that with high probability,
+and for $i\ne j$,
+\be \label{largebetae3}
+\begin{split}
+\left| \e_j^\top X_j (X_j^\top X_j)^{-1}(X_i^\top X_i)^{-1}X_i^\top \e_i \right| &\le   p^{\e/2}\cdot \sigma^2 \left\{ \tr \left[(X_i^\top X_i)^{-1}(X_j^\top X_j)^{-1}\right] \right\}^{1/2} \\
+&\le \sigma^2 p^{-1/2+\e},  
+ \end{split}
+\ee
+%where in the we used Theorem \ref{LEM_SMALL} to get that
+%$$\beta_t^\top (X_i^\top X_i)^{-1}\beta_t  \le p^{-1+\e/2} \quad \text{and}\quad \tr \left[ (X_i^\top X_i)^{-2} \right]  \le p^{-1+\e/2} \quad \text{whp}.$$
+With \eqref{largebetae}-\eqref{largebetae3}, we get that with high probability,
 \begin{align}
 \|\hat\beta_i\|^2&= \|\beta_i\|^2 + \sigma^2\cdot \tr \left( (X_i^\top X_i)^{-1}\right) +\OO(\sigma p^{-1/2+\e}) \nonumber\\
-&=  \|\beta_i\|^2 + \frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) +\OO(\sigma p^{-1/2+\e}) ,\label{betanormi}
+&=  \|\beta_i\|^2 + \frac{\sigma^2}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) +\OO(\sigma p^{-1/2+\e}) ,\label{betanormi}
 \end{align}
-where in the second step we used Lemma \ref{lem_minv}.
+and %where in the second step we used Lemma \ref{lem_minv}. Similarly, we have
+\begin{align}\label{betanormij}
+\hat\beta_i^\top \hat \beta_j &= \beta_i^\top \beta_j + \OO(\sigma p^{-1/2+\e})  , \quad i\ne j.
+\end{align}
+With \eqref{betanormi} and \eqref{betanormij}, we obtain that with high probability,
+\be\label{BTB}
+B^\top B= (B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1 +\OO(\sigma p^{-1/2+\e}),
+\ee
+where $\OO(\sigma p^{-1/2+\e})$ means a $(t-1)\times (t-1)$ matrix, say $\cal E$, satisfying $\|\cal E\|\le C\sigma p^{-1/2+\e}$. Notice that by \eqref{BTBassm}, we also have with high probability,
+$$\|(B^\top B)^{-1}\| \lesssim \left\|\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1}\right\|= \OO( 1).$$
+Moreover, using \eqref{largebetae} we get that
+\be\label{BTBeta}
+B^\top \beta =  (B^\star_{t-1})^\top \beta + \OO(\sigma p^{-1/2+\e}),
+\ee
+for any deterministic vector $\beta$ with $\|\beta\|=\OO(1)$.
 
-For simplicity we abbreviate $v_i:=(X_i^\top X_i)^{-1}X_i \e_i$. Then using \eqref{largebetae} and \eqref{betanormi} we can calculate that whp,
+Now we are ready to calculate $\te(B W_t) $ using the above concentrations results. For the $t$-th target model, by optimizing over $W_t$ we get
+$$\hat W_t= (B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top Y_k =(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top (X_t \beta_t + \e_k) .$$
+We then calculate that 
+\be
+\begin{split}
+\exarg{\varepsilon_k} {\left\|\Sigma_k^{1/2}(B\hat W_t -\beta_t)\right\|^2} &= \left\| \Sigma_k^{1/2}\left[\id - B(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top X_t\right] \beta_t \right\|^2 \\
+&+\sigma^2\cdot \tr \left[\Sigma_k (B^\top X_t^\top X_t B)^{-1}\right]. \label{EBWk}
+%\\&= \sigma^2\cdot \tr (B^\top X_t^\top X_t B)^{-1} + \left\|\beta_t\right\|^2 - 2 \beta_t^\top B(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top X_t \beta_t \nonumber\\
+%&+ \beta_t^\top X_t^\top X_t B(B^\top X_t^\top X_t B)^{-1}B^\top B (B^\top X_t^\top X_t B)^{-1}B^\top X_t^\top X_t \beta_t.\label{EBWk}
+\end{split}
+\ee
+By the concentration of random vector with independent entries or the restricted isometry property for $X_t B$, we have with high probability, 
+$$ B^\top X_t^\top X_t B = n_k  \left( B^\top B + \OO(p^{-1/2+\e})\right),\quad B^\top X_t^\top X_t \beta_t = n_k  \left( B^\top \beta_t  + \OO(p^{-1/2+\e})\right).$$
+Together with \eqref{opXiXi}, \eqref{BTB} and \eqref{BTBeta}, we can simplify the right-hand side of \eqref{EBWk} as
+\begin{align}
+\exarg{\varepsilon_k} {\left\|\Sigma_k^{1/2} (B\hat W_k -\beta_t)\right\|^2} =\left\|\Sigma_k^{1/2} \beta_t - \Sigma_k^{1/2} B(B^\top B)^{-1} B^\top \beta_t \right\|^2 + \OO(p^{-1/2+\e}) \nonumber\\
+=\left\|\Sigma_k^{1/2} \beta_t - \Sigma_k^{1/2} B\left[ (B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1)^{-1} \right](B_{t-1}^{\star})^\top \beta_t \right\|^2 + \OO(p^{-1/2+\e}). \label{EBWk2}
+\end{align}
+As in \eqref{BTB}, we can show by concentration that 
+\be\label{BTB2}
+B^\top \Sigma_k B=  (B_{t-1}^{\star})^\top \Sigma_k B_{t-1}^{\star}+\sigma^2 {\cal M}_2 +\OO(\sigma p^{-1/2+\e}).
+\ee
+Together with \eqref{BTB} and \eqref{BTBeta}, we can further simplify \eqref{EBWk2} as
 \begin{align*}
-&\|\hat \beta_t - \hat\beta_t'\|^2= \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|} \beta_i - \sum_{i=1}^k\frac{\beta_t^\top (\beta_i + v_i)}{ \|\beta_i +v_i\| }(\beta_i + v_i) \right\|^2 \\
-&=  \left\|\sum_{i=1}^k\left(\frac{\beta_t^\top \beta_i}{\|\beta_i\|}-\frac{\beta_t^\top \beta_i}{\|\beta_i+v_i\|} \right)\beta_i - \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i+v_i\| } v_i - \sum_{i=1}^k\frac{\beta_t^\top v_i}{ \|\beta_i +v_i\| } (\beta_i+v_i) \right\|^2 \\
-%& = \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|}\left(1-\frac{\|\beta_i\|}{(\|\beta_i\|^2 + 2\beta_i^\top v_i + \|v_i\|^2)^{1/2}} \right)\beta_i - \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|+\OO(\sigma^2 + \sigma p^{-1/2+\e}) } v_i\right\|^2 + \OO\left(\sigma^2 p^{-1+2\e}\right) \\
-%&= \left\|\sum_{i=1}^k\frac{\beta_t^\top \beta_i}{\|\beta_i\|}\frac{2\beta_i^\top v_i + \|v_i\|^2}{2\|\beta_i\|^2}\beta_i \right\|^2+\left\| \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|} v_i\right\|^2 + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right)
-&= \left\| \sum_{i=1}^k\frac{\beta_t^\top \beta_i }{ \|\beta_i\|} v_i\right\|^2 + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right).
+&\exarg{\varepsilon_i, \forall 1\le i\le k} {\left\|\Sigma_k^{1/2} (B\hat W_k -\beta_t)\right\|^2}\\
+&= \OO(p^{-1/2+\e}) +\left\|\Sigma_k^{1/2} \beta_t\right\|^2 - 2\beta_t^\top \Sigma_k B_{t-1}^{\star} \left[(B_{t-1}^{\star})^\top B_{t-1}^{\star} +\sigma^2\cal M_1\right]^{-1} (B_{t-1}^{\star})^\top \beta_t  \\
+&+ \beta_t^\top B_{t-1}^\star \left[(B_{t-1}^{\star})^\top B_{t-1}^{\star} +\sigma^2\cal M_1\right]^{-1} \left((B_{t-1}^{\star})^\top \Sigma_k B_{t-1}^{\star}+\sigma^2 {\cal M}_2 \right) \left[(B_{t-1}^{\star})^\top B_{t-1}^{\star} +\sigma^2\cal M_1\right]^{-1}  (B_{t-1}^{\star})^\top \beta_t \\
+& =\|\e_\beta + \sigma^2 \e_{\vari}^{(1)}\|^2+ \sigma^2 \|\e_{\vari}^{(2)}\|^2 + \OO(p^{-1/2+\e}).
 \end{align*}
-Thus taking expectation, we get that 
-\begin{align*}
-\exarg{\varepsilon_i, \forall 1\le i\le k} {\|\hat \beta_t - \hat\beta_t'\|^2}&=   \sum_{i=1}^k\frac{\left|\beta_t^\top \beta_i \right|^2}{ \|\beta_i\|^2 } \cdot \sigma^2 \tr \left( (X_i^\top X_i)^{-1}\right) + \OO\left(\sigma^4+\sigma^2 p^{-1+2\e}\right) \\
- &= \sum_{i=1}^k\frac{\left|\beta_t^\top \beta_i \right|^2}{ \|\beta_i\|^2 } \cdot \frac{\sigma^2}{c_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) + \OO\left(\sigma^4+\sigma^2 p^{-1/2+2\e}\right) .
-\end{align*}
-Note the first term is of order $\sigma^2$, and hence the second stem is an error term.
+This concludes the proof.
+\end{proof}

### 2020-05-26 writeup/transfer.tex
sec 3.1

@@
 
-The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-A key highlight of our approach implies a precise limit on $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}$, which only depends on $\Sigma_1, \Sigma_2$ and $n_1, n_2$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
+For this purpose, we consider the high-dimensional setting where $p$ goes to infinity.
+A well-known result for this setting states that the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$ is $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
+Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
+However, this result only applies to the single-task setting.
+Therefore, we focus on deriving the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ when $p$ goes to infinity.
 
-\textbf{First setting: Two tasks with general covariance matrices.}
+Our first result applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
+%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
+We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+Based on the result, we show how to determine positive versus negative transfer as follows.
 
@@
 	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
-	Suppose that $n_1 = c_1 p$ and $n_2 = c_2 p$, where $c_1>1$ and $c_2 >1$ are fixed constants.
-	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, M, n_1, n_2, \beta_1, \beta_2}$ such that
+	Suppose that $n_1 = \rho_1 p$ and $n_2 = \rho_2 p$, where $\rho_1>1$ and $\rho_2 >1$ are fixed constants.
+	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, \Sigma_1^{}, n_1, n_2, \beta_1, \beta_2}$ such that
 	\begin{itemize}
@@
 
-Theorem \ref{thm_main_informal} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
-The bounds get tighter and tighter as $n_1 / p$ increases.
+Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
+%determined by the covariate shift matrix and the model shift.
+The bounds get tighter and tighter as $\rho_1$ increases.
+A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
 

### 2020-05-26 writeup/setup.tex

@@
 
-\textbf{Notations.} For the sake of clarity, we denote the first task as the source task and last ($t$-th) task as the target task.
+\textbf{Notations.} We refer to the last ($t$-th) task as the target task and the first task as the source task when there are only two tasks.
+When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
+We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
+%Same for $\hat{\beta}_t^{\STL}$.

### 2020-05-26 writeup/transfer.tex
add label

@@
 The bounds get tighter and tighter as $\rho_1$ increases.
-A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
+A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{sec_pfmain}.
 
-\textbf{Second setting: Many tasks with the same covariates.}
-We extend the above result to any number of tasks that have the same covariates.
+Our second result applies to the set setting of many tasks with the same covariates.
+%We extend the above result to any number of tasks that have the same covariates.
 %In this section we consider the setting with $k$ many that have the same covariates.
@@
 Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
-We derive the model shift bias and variance in the following result.
+We can also derive a tight trade-off between model shift bias and variance reduction for this setting.
+The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-05-26 writeup/transfer.tex
merge TL

@@
 
-Our second result applies to the set setting of many tasks with the same covariates.
+Our second result applies to the setting of any number of tasks with the same covariates.
 %We extend the above result to any number of tasks that have the same covariates.
@@
 \textbf{Implications.}
+
+\section{Extending the Bias-Variance Trade-off to Transfer Learning}\label{sec_taskonomy}
+
+We study the transfer function of taskonomy \cite{ZSSGM18}.
+The algorithm is as follows.
+First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le t$.
+This forms the shared representation $B = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+Then, we learn the output layer $W_t$ on the target task by solving equation:
+\begin{align}
+	\bignorm{X_t B W_t - Y_t}^2
+\end{align}
+After getting $W_t$, we use $B W_t$ as estimator and $\te(B W_t)$ is the test error of the estimator.
+We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.

### 2020-05-26 writeup/transfer.tex
sec 4

--- 2020-05-26 writeup/transfer.tex
@@
 A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{sec_pfmain}.
+While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we show that they provide nice interpretation for several simple settings in the rest of the section.
 
-Our second result applies to the set setting of many tasks with the same covariates.
+Our second result applies to the setting of any number of tasks with the same covariates.
 %We extend the above result to any number of tasks that have the same covariates.
@@
 
-We compare the test error of $\hat{\beta}_t^{\MTL}$ to that of $\hat{\beta}_t^{\STL}$.
-For a simple example, we show that whether $\hat{\beta}_t^{\MTL}$ performs better than $\hat{\beta}_t^{\STL}$ is determined by the distance of the task models.
-We derive a sharp threshold when positive transfer transitions to negative transfer, as a ratio between the model distance and the noise level.
+A folklore intuition since the seminal work of Caruana \cite{C97} is that task relatedness determines how well multi-task learning performs.
+We formalize the intuition using our setup and technical tools.
+For a simple example of two tasks, we show that whether $\hat{\beta}_t^{\MTL} \le \hat{\beta}_t^{\STL}$ is determined by $\norm{\beta_1 - \beta_2}^2$, the distance of the task models.
+We derive a sharp threshold when positive transfer transitions to negative transfer, as a function of model distance $\norm{\beta_1 - \beta_2}^2$, data size $n_1$ abd $n_2$ and the noise level $\sigma$.
 
@@
 
-We illustrate the example in a synthetic setting.
-We demonstrate our result with a simulation. (\todo {uses the tighter bound Proposition \ref{prop_model_shift_tight}?})
+We illustrate the example with a simulation.
 We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
-	\todo{Fill in other params.}
-We fix the target task and vary the source task, by varying the task model distance parameter $d$.
-We show that Theorem \ref{thm_model_shift} predicts whether we can get positive or negative transfer.
-Figure \ref{fig_model_shift_phasetrans} shows the result.
+We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
+Figure \ref{fig_model_shift} shows the result.
+Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
+Define the following function
+\begin{align*}
+	\Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
+\end{align*}
 
-Specifically, the transition threshold is derived in the following proposition.
 \begin{proposition}\label{prop_dist_transition}
-	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $c_1 > 110$ is a fixed constant.
+	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 110$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
-		\item If ${d^2} < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} $, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} < \frac {2\sigma^2} {3p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 
-Here the constants $\frac23$ and $\frac32$ in this proposition (and the following ones) can be replaced with $(1+c_1^{-1/2})^{-4}$ and $(1-c_1^{-1/2})^{-4}$.
-In particular, these bounds becomes tighter as $c_1$ increases.
+We remark that the constants $\frac23$ and $\frac32$ in the statement above are chosen for the simplicity of presentation.
+In general we can close the gap between the two constants by increasing $\rho_1$.
+While the statement of Theorem \ref{thm_main_informal} only applies to the asymptotic regime of $p$ going to infinity, Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift} when $p = 200$.
+%in this proposition (and the following ones) can be replaced with $(1+c_1^{-1/2})^{-4}$ and $(1-c_1^{-1/2})^{-4}$. In particular, these bounds becomes tighter as $c_1$ increases.
 
 The proof of Proposition \ref{prop_dist_transition} involves two parts.
-First, adding the source task has a positive effect of reducing the variance of the estimator, which scales with $n_1 = c_1 p$, the number of source task data points.
-Second, the difference between task models $\beta_1$ and $\beta_2$ introduces an additional bias term, which scales with $pd^2$, the distance between $\beta_1$ and $\beta_2$.
-Hence, the type of transfer is determined by the trade-off between model shift bias and the reduction of variance.
-The proof can be found in Appendix \ref{app_proof_31}, which is based on our main result described later in Theorem \ref{thm_model_shift}.
+First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
+Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
+The proof, which is based on Theorem \ref{thm_main_informal}, can be found in Appendix \ref{app_proof_31}. %, which is based on our main result described later in Theorem \ref{thm_model_shift}.
 
 \begin{figure}
-	\begin{subfigure}[b]{0.31\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 		\centering
@@
 		\caption{Task model similarity}
+		\label{fig_model_shift}
 	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.31\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 		\centering
@@
 	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.31\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 		\centering
@@
 	\end{subfigure}
-	\caption{Comparing the test error of multi-task learning to single-task learning: we observe transitions from positive to negative transfer.
-(a) Section \ref{sec_dist}: Task model similarities; (b) Section \ref{sec_data}: Source task noise level; (c) Section \ref{sec_covariate}: \todo{same vs.
-different covariance matrices}.}
+	\caption{Comparing the test error of multi-task learning to single-task learning: (a) positive to negative transfer as the task model dissimilarity increases (cf.
+Proposition \ref{prop_dist_transition}) (b) positive to negative transfer as the source task data size increases (cf.
+Proposition \ref{prop_data_size}); (c) }
 	\label{fig_model_shift_phasetrans}
@@
 
-Consider a more general setting where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-We derive a sharp transition similar to Proposition \ref{prop_dist_transition}.
+\textbf{Implications.}
+We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
+We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
 
 \begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $c_1 > 110$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, i.e.
-we have positive transfer when $\sigma_1=\sigma_2$.
-Then we derive the following transition as a parameter of $\sigma_1$:
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 110$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
+	We derive the following transition as a parameter of $\sigma_1^2$:
 	\begin{itemize}
-		\item If $\sigma_1^2 \le p d^2 \cdot c_1 +\left[1+ \frac23\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right]\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > p d^2 \cdot c_1 +\left[1+ \frac32\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)}\right] \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 \le p d^2 \cdot c_1 +\left(1+ \frac23 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > p d^2 \cdot c_1 +\left(1+ \frac32\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
 \end{proposition}
+As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
+The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+The details can be found in Appendix \ref{app_proof_31}.
 
-\textbf{Implications.}
-
-\subsection{Data Size and Efficiency}\label{sec_data_size}
+\subsection{Data Size}\label{sec_data_size}
 
@@
 \textbf{Implications.}
+
+\section{Extending the Bias-Variance Trade-off to Transfer Learning}\label{sec_taskonomy}
+
+While our focus is on multi-task learning, we show that our results extend to transfer learning settings naturally.
+We provide an analysis of the transfer function of Taskonomy (Figure 4 in \cite{ZSSGM18}) using our setup.
+Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
+The transfer function then tries to fix the target task data to the source task encoder.
+
+We map the procedure to our setup as follows.
+First, we obtain the single-task estimator $\hat{\beta}_i$ from the source tasks, for $1\le i \le t-1$.
+This forms the shared representation $B^{\star}_{t-1} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+Then, we learn the output layer $W_t$ on the target task by minimizing the following objective
+\begin{align}
+	g(W_t) = \bignorm{X_t B W_t - Y_t}^2.
+\end{align}
+After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the estimator for the target task.
+By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
+%We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
+The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.

### 2020-05-26 writeup/transfer.tex
sec 3.2

@@
 \begin{proposition}\label{prop_dist_transition}
-	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 110$ is a fixed constant.
+	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 40$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
 	\begin{itemize}
-		\item If ${d^2} < \frac {2\sigma^2} {3p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} < \frac {\sigma^2} {2p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} \ge \frac {2\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 
-We remark that the constants $\frac23$ and $\frac32$ in the statement above are chosen for the simplicity of presentation.
+We remark that the constants $1/2$ and $2$ in the statement above are chosen for the simplicity of presentation.
 In general we can close the gap between the two constants by increasing $\rho_1$.
@@
 \begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 110$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
 	We derive the following transition as a parameter of $\sigma_1^2$:
 	\begin{itemize}
-		\item If $\sigma_1^2 \le p d^2 \cdot c_1 +\left(1+ \frac23 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > p d^2 \cdot c_1 +\left(1+ \frac32\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 \begin{proposition}\label{prop_data_size}
-	In the setting of Example \ref{ex_basic}, assume that $c_2  \ge 3$ is fixed and $c_1 > a$ for some fixed integer $a$.	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
+	In the setting of Example \ref{ex_basic}, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants.
+	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
 	\begin{itemize}
-\item If $d^2 \le (1 + a^{-1/2})^{-4}\frac{\sigma^2}{p(c_2-1)}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+\item If $d^2 \le \frac{\sigma^2}{2p(\rho_2-1)}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
 
-\item If $d^2 > (1 - a^{-1/2})^{-4}(1-(a+c_2-2)^{-2})^{-1}\frac{\sigma^2}{p (c_2 - 1)}$, then we have the following transition depending on $c_1$:
+\item If $d^2 > \frac{2\sigma^2}{p (\rho_2 - 1)}$, then we have the following transition depending on $\rho_1$:
 		\begin{itemize}
-			\item If $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-			\item If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+			\item If $\rho_1 < \frac{(\rho_2-2)\sigma^2}{(1 + {\rho_1}^{-0.5})^4(\rho_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+			\item If $\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 		\end{itemize}
@@
 \begin{proposition}\label{prop_data_efficiency}
-	In the setting of Example \ref{ex_basic}, assume that $c_1 = c_2 = c \ge 200$ and $d^2 < {8\sigma^2} /{(3p c)}$.
-	Then the data efficiency ratio is at most $\frac{1}{2c} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 c / 4}$.
+	In the setting of Example \ref{ex_basic}, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
+	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
 \end{proposition}
-Note that we have stated the result assuming that $c_1 = c_2$.
+Note that we have stated the result assuming that $\rho_1 = \rho_2$.
 Similar results can also be obtained when they are different.
@@
 We have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M\in \cS_{\mu}$ satisfies that 
-\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(c_2c_1^{-1} + c_1^{-1/2}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
+\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
 where the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $C_1$, but otherwise does not depend on $c_1$ and $c_2$. 

### 2020-05-26 writeup/experiments.tex
sec 3

@@
 {For each task, the goal is to categorize sentiment opinions expressed in the text.
-We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}\footnote{We also tested with multi-layer perceptron and CNN.
-The results are similar (cf.
-Appendix \ref{label:real_result_details}).}.
+We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}.
 }
@@
 		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-		\caption{LSTM (averaged)}
+		\caption{Averaged}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+		\caption{Task pair TREC and CR}
 	\end{subfigure}\hfill
@@
 		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-		\caption{MLP (averaged)}
-	\end{subfigure}\hfill
-		\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-		\caption{LSTM for one pair}
+		\caption{Task pair MR and SST}
 	\end{subfigure}

### 2020-05-26 writeup/experiments.tex
sec 5

@@
 
-\textbf{Measuring data efficiency ratio.}
+\textbf{Multi-task learning provides labeled data efficiency.}
 We measure the data efficiency ratio on text classification tasks.
@@
 
-\textbf{Data size affects covariance alignment.}
+\textbf{Covariance alignment provides more improvement when data size is imbalanced.}
 We validate that the performance of aligning task covariances depends on the size of source task data.
@@
 	\end{subfigure}
-	\caption{The performance of aligning task covariances depends on data size.}
+	\caption{The performance of aligning task covariances depends on data size.
+As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
 	\label{fig_covariate}

### 2020-05-26 writeup/proofs_sec3.tex
add label
revise sec A

@@
-\section{Supplementary Materials for Section \ref{sec_insight}}\label{app_proof_main}
+\section{Supplementary Materials for Section \ref{sec_insight}}\label{app_proof_sec3}
 
@@
 The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.
+When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+Here we shall state a result that is a consequence of Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
 
-\begin{lemma}\label{lem_minv}[\todo{ref?}]
-	Let $X\in\real^{n\times p}$ be a random matrix that contains i.i.d.
+\begin{lemma}\label{lem_minv} 
+	Let $X = \Sigma^{1/2} Z\in\real^{n\times p}$ be a random matrix that contains i.i.d.
 row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$.
+Suppose the entries of $Z$ have finite moments up to any order.
 Let $A$ be a $p\times p$ matrix that is independent of $X$ and satisfies $\|A\|=\OO(1)$.
-	In the setting when $n = c p$ we have that
-	\[  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{c - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ p^{-1/2+\epsilon}} \]
+	In the setting when $n = \rho p$ for some constant $\rho>1$, we have that with high probability,
+	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ p^{-1/2+\epsilon}} \ee
 for any constant $\e>0$.
 \end{lemma}
+
+In this section, we will always consider random variables with finite moments up to any order.
+On the other hand, if the entries of $Z$ have finite $a$-th moment for some constant $a>4$, then \eqref{XXA} still holds except that the error bound becomes  $\OO( p^{-\frac12+\frac2a +\epsilon})$; see our Corollary \ref{main_cor} below.
 

### 2020-05-26 writeup/proof_taskonomy.tex

@@
-\section{Extension to the Transfer Function of Taskonomy}
-
-We study the transfer function of taskonomy \cite{ZSSGM18}.
-The algorithm is as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le t$.
-This forms the shared representation $B = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
-Then, we learn the output layer $W_t$ on the target task by solving equation:
-\begin{align}
-	\bignorm{X_t B W_t - Y_t}^2
-\end{align}
-After getting $W_t$, we use $B W_t$ as estimator and $\te(B W_t)$ is the test error of the estimator.
-We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
+\section{Supplementary Materials for Section \ref{sec_taskonomy}}\label{app_proof_sec4}
 

### 2020-05-26 writeup/transfer.tex

@@
 		\caption{Covariate shift}
+		\label{fig_covariate}
 	\end{subfigure}
@@
 \begin{proposition}\label{prop_covariate}
-	In the setting of Example \ref{ex_basic}, assume that $c_1 > 3$ and $c_2>3$,
+	In the setting of Example \ref{ex_basic}, assume that $\rho_1 > 3$ and $\rho_2>3$,
 and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. %As a parameter of $M \in \cS_{\mu}$, 
-We have that $(\te(\hat{\beta}_t^{\MTL}))(M)$ as a function of $M\in \cS_{\mu}$ satisfies that 
-\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
-where the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $C_1$, but otherwise does not depend on $c_1$ and $c_2$. 
+The test error $\te(\hat{\beta}_t^{\MTL})$, as a function of $M\in \cS_{\mu}$, is minimized at the identity matrix $\mu\id$ approximately by
+$1+ \bigo{\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}}$.
+%\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
+%where the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $C_1$, but otherwise does not depend on $c_1$ and $c_2$.
 	%is minimized when $M = \mu\id$.
 \end{proposition}
-
 Proposition \ref{prop_covariate} shows that when $n_1\gg n_2$, $te(\hat{\beta}_t^{\MTL})$ is minimized when $\Sigma_1$ and $\Sigma_2$ are proportional to each other.
@@
 
-\begin{example}\label{ex_covariate}
+\begin{example}\label{ex_complement}
 	Within the setting of Example \ref{ex_cov_family}, we compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
@@
 	Hence the two tasks have the same model parameters.
-%	now consider another case when $\Sigma_1$ and $\Sigma_2$ have complementary eigenspaces. Suppose $\Sigma_1$ and $\Sigma_2$ have the eigendecomposition
-%$$\Sigma_1^{1/2} = 1+ U\Lambda U^\top, \quad \Sigma_2^{1/2} = 1+ V\Lambda V,$$
-%where
-%$$\Lambda = \diag(\wt\lambda_1,\cdots, \wt\lambda_{p/2}), \quad U= (u_1,\cdots, u_{p/2}), \quad V= (v_1,\cdots, v_{p/2}).$$
-%If $V=U_\perp$, i.e. the vectors $v_1,\cdots, v_{p/2}$ are perpendicular to the vectors $u_1,\cdots, u_{p/2}$, then
-%$$M=\Sigma_1^{1/2} \Sigma_2^{-1/2}=(1+\Lambda)UU^\top + (1+\Lambda)^{-1}V V^\top .$$
-%	As a concrete example we consider the case where $\wt \lambda_1=\cdots=\wt\lambda_{p/2}$ and we denote $\lambda:=1+\wt\lambda_1$.
-Thus for $M$, the first $p/2$ singular values are equal to $\lambda$ and the rest ones are equal to $\lambda^{-1}$.
 
-	In Figure \ref{fig_te_complement}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
+	In Figure \ref{fig_covariate}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
 	Second, we observe the following two phases as we increase $n_1 / p$.
-	\begin{itemize}
-		\item When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-		\item When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	\end{itemize}
+	When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
+	When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
+	A theoretical justification can be found in Appendix \ref{app_covariate}.
 \end{example}
-
-A theoretical justification of Example \ref{ex_covariate} can be found in Appendix \ref{app_covariate}.
 
@@
 While our focus is on multi-task learning, we show that our results extend to transfer learning settings naturally.
-We provide an analysis of the transfer function of Taskonomy (Figure 4 in \cite{ZSSGM18}) using our setup.
+We provide an analysis of the transfer function of Taskonomy \cite{ZSSGM18} using our setup.
 Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
-The transfer function then tries to fix the target task data to the source task encoder.
+The transfer function then tries to fit the target task data to the source task encoder.
+For more details, we refer the reader to Figure 4 in Taskonomy.
 

### 2020-05-26 writeup/intro.tex

@@
 In this work, we consider multiple high-dimensional linear regression tasks as input and focus on predicting a particular task that only has limited amount of labeled data.
-Concretely, each task consists of $n_i$ datapoints in space $\real^p$ organized as matrix $X_i\in\real^{n_i\times p}$, for $1\le i\le t$.
-The labels of $X_i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i$ denotes the ground truth parameters for task $i$ and $\varepsilon_i$ denotes i.i.d.
-random noise with mean zero and variance $\sigma^2$.
-Importantly, we assume that the number of datapoints $n_i$ is a small constant $\rho_i$ times $p$ and that $p$ is large. \todo{rational}
+Following \cite{HMRT19,BLLT20}, we assume that for every task $1\le i\le t$, its features are random vectors $x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d.
+entries with mean zero and unit variance, and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
+The label of $x$ is given by $y_i = x^{\top}\beta_i + \varepsilon$, where $\beta_i\in\real^p$ denotes the ground truth parameters for task $i$ and $\varepsilon$ denotes random noise with mean zero and variance $\sigma^2$.
+Importantly, we assume that for the target task $t$, its training data size $n_t$ is a small constant $\rho_t$ times $p$. %\todo{rational}
 %We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
@@
 %    \paragraph{Different covariates:}
-This corresponds to minimizing the following optimization objective.
+This corresponds to minimizing the following objective.
 \begin{align}
@@
 	For the high-dimensional regime when $p$ goes to infinity, we derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL}) - \te(\hat{\beta}_t^{\STL})$ as a function of the number of datapoints $\set{n_1, n_2}$, the covariance matrices $\set{\Sigma_1, \Sigma_2}$, the ground truth parameters $\set{\beta_1, \beta_2}$, and a certain fixed value derived from solving equation \eqref{eq_mtl} (see Theorem \ref{thm_main_informal} for the statement).
-	Then, we show a similar result for any number of tasks that have the same covariates, i.e. the $X_i$'s are equal to each other in Theorem \ref{thm_many_tasks}.
+	Then, we show a similar result for any number of tasks that have the same covariates, i.e. the $X_i$'s are equal to each other.
 	This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+	Based on the technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
 
-%the benefit from doing multi-task or transfer learning stems from reducing the variance of the estimator for the target task through newly added source task data.
-%	We derive this result for the setting of two tasks with general inputs
-%	First, we provide a precise analysis for performing multi-task learning over two tasks under covariate and model shifts.
-	%On the other hand,  task models causes a negative effect that we call the \textit{model shift bias}.
-	%We show bounds on the trade-off between the amount of variance reduced and the amount of model shift bias incurred, which become tighter and tighter as the number of source task data points increases.
+	Our first theoretical insight is to explain a sharp transition from positive to negative transfer as a parameter of \textit{task model dissimilarity} $\norm{\beta_1 - \beta_2}^2$.
+	In Proposition \ref{prop_dist_transition}, we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
 
-	Next, we use our technical tools to show how to determine negative transfer based on task data.
-%	These are achieved through tight generalization bounds established in the high-dimensional regression setting.
-%	Using these tools, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
-%	\begin{itemize}
-Our first theoretical insight is we provide a sharp transition to show that task model similarities can determine whether there is positive transfer.
-		For settings where tasks are similar, we further show that the transfer effect depends on the single-task accuracy of the source task.
+	Our second theoretical insight is to show that performing multi-task learning reduces the need for labeled data, which is a key finding of Taskonomy \cite{ZSSGM18}.
+	We define \textit{data efficiency ratio} can be defined as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
+	In Proposition \ref{prop_data_efficiency}, we consider an example and show that the data efficiency ratio is $\alert{\frac {1}{2\rho_t}}$.
 
-Our second theoretical insight is we show how source task data size can also determine transfer by providing a sharp transition.
-		We use our tools to explain the result of taskonomy \cite{ZSSGM18}, regarding the data efficiency of multi-task learning.
+	Our third theoretical insight is that as the data size becomes more imbalanced between the source and target task, having mis-aligned task covariance matrices can result in suboptimal performance.
+	In Proposition \ref{prop_covariate}, we show that as $n_1 / n_2$ becomes large, the best performing source task has have the same covariance matrix as the target task.
+	On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
 
-Our third theoretical insight is has implications on the following question.
-	Is it better for two tasks to have the same covariance matrix or complementary covariance matrices?
-	For our setting, we show that when the data ratio is large, having the same covariance matrix provably yields the lowest test performance on the target task.
-	On the other hand, when data ratio is small, we find that there are cases when having complementary covariance matrices is better.
-%	The result provides insight into why the covariance alignment algorithm can help improve performance in \cite{WZR20}.
+Finally, while our focus is multi-task learning, our setup and technical tools are also applicable to transfer learning settings.
+In Section \ref{sec_taskonomy}, we provide a case study of the transfer function used in Taskonomy \cite{ZSSGM18}.
+We observe a similar trade-off between model-shift bias and variance for this setting.
 
-Finally, we extend our reuslts to study the transfer functions used in taskonomy \cite{ZSSGM18}.
+A crucial technical tool that we develop for showing Theorem \ref{thm_main_informal} is the asymptotic limit of the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ (for the setting of two tasks), which may be of independent interest.
+The result extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ \cite{S07}
+Furthermore, the error bound for the asymptotic limit is nearly optimal.
 
-A crucial technical tool that we develop is the asymptotic limit of the trace of the inverse of the sum of two independent sample covariance matrices.
-Our result not only extends the well-known Marchenko–Pastur law in random matrix theory to the sum of two independent sample covariance matrices with general covariance matrices, but also gives an almost optimal error bound, which may be of independent interest.
-
-%	{\it Insight 1}: $\hat{\beta}_t^{\MTL}$ vs $\hat{\beta}_t^{\STL}$.
-%	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
-%	In particular, if model shift is too large, we get negative transfer from multi-task training.
-
-%	{\it Insight 2}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\MTL}$.
-%	Finally, we show that the transfer learning estimator always improves over mutli-task training.
-%	The amount of improvement becomes more significant as the model distance becomes larger.
-
-%	We show the result for two settings: 2 tasks with different covariates, and $k$ tasks that all share the same covariates.
-%	We show that our results and insights from the above can be extended to this setting as well.
-	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
-	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
-
-%\noindent{\bf Variance reduction from information transfer.}
-%	Second, we apply our general theory to compare the performance of three different estimators for the target task: multi-task training, single-task training and transfer learning.
-%	\begin{enumerate}
-
-%\smallskip
-%	\noindent\textbf{Covariate shift and data ratio.}
-%	For the case of two tasks with general inputs, we further study the factors that determine the transfer rate.
-%	We identify two factors, the covariate shift matrix and the ratio between number of task data.
-%	Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
-%	We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
-
-%	\textit{Insight 3}: $\hat{\beta}_t^{\TL}$ vs $\hat{\beta}_t^{\STL}$.
-\textbf{Experimental results.} We provide practical implications to validate our theory.
-	First, we validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.
-	\todo{Second}
-	Finally, We show that when the number of source task datapoints is large compared to the target task, then aligning task covariances always improves performance.
-	On the other hand, if the number of source task datapoints is comparable to the target task, aligning task covariances may hurt performance.
+\textbf{Experimental results.} We show practical implications of our theoretical insights on text and image classification tasks.
+	First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.
+	%validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.
+	Second, we validate that performing multi-task learning can reduce the need for labeled data.
+	On 6 sentiment analysis tasks, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
+	Finally, we show that as the data size between the source and target task becomes more imbalanced, aligning the covariances of the tasks becomes more beneficial.
+%	On the other hand, if the number of source task datapoints is comparable to the target task, aligning task covariances may hurt performance.

### 2020-05-26 writeup/intro.tex
intro
intro edits

@@
 Our second theoretical insight is to show that performing multi-task learning reduces the need for labeled data, which is a key finding of Taskonomy \cite{ZSSGM18}.
-	We define \textit{data efficiency ratio} can be defined as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
-	In Proposition \ref{prop_data_efficiency}, we consider an example and show that the data efficiency ratio is $\alert{\frac {1}{2\rho_t}}$.
+	We define the \textit{data efficiency ratio} as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
+	In Proposition \ref{prop_data_efficiency}, we show that the data efficiency ratio of an illustrative example is at most $\alert{\frac {1}{2\rho_t}}$.
 

### 2020-05-26 writeup/setup.tex
re structure

@@
 
-To illustrate our intuition, we begin by considering the multi-task learning setting with one source task.
-Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
-We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts (to be derived in Appendix \ref{app_proof_main})
-\begin{align}
-	\te_t(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
-	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
-\end{align}
-where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
-By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
-
-\textbf{Model-shift bias.}
-%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
-We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
-This part introduces a negative effect to multi-task learning.
-The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
-The output layer of each task scales the direction of $B$ suitably to fit the task.
-
-\textbf{Variance reduction.}
-Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
-This part introduces a positive variance reduction effect to performing multi-task learning.
-Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
-(i) the positive effect from variance reduction;
-(ii) the negative effect from model shift bias.
-
 %, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.

### 2020-05-26 writeup/transfer.tex
re structure

@@
-\section{Revisiting the Bias-Variance Trade-off for Multi-Task learning}
-\label{sec_insight}
+\section{A Technical Tool for Determining Positive versus Negative Transfer}
+\label{sec_main}
 
@@
 For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
-After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
-Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
-
-\subsection{Determining Positive versus Negative Transfer}\label{sec_main}
 
@@
 Therefore, we focus on deriving the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ when $p$ goes to infinity.
+
+To illustrate our intuition, we begin by considering the multi-task learning setting with one source task.
+Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
+We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts (to be derived in Appendix \ref{app_proof_main})
+\begin{align}
+	\te_t(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
+	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
+\end{align}
+where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
+By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
+
+\textbf{Model-shift bias.}
+%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
+This part introduces a negative effect to multi-task learning.
+The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+The output layer of each task scales the direction of $B$ suitably to fit the task.
+
+\textbf{Variance reduction.}
+Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+This part introduces a positive variance reduction effect to performing multi-task learning.
+Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
+(i) the positive effect from variance reduction;
+(ii) the negative effect from model shift bias.
 
@@
 The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
+
+\section{Theoretical Implications}
+\label{sec_insight}
+After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
+Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
 
@@
 
-\section{Extending the Bias-Variance Trade-off to Transfer Learning}\label{sec_taskonomy}
+\subsection{Extension to Transfer Learning}\label{sec_taskonomy}
 

### 2020-05-26 writeup/proof_main.tex
sec 3.1
add label
sec A0

@@
-\subsection{Proofs for Section \ref{sec_main}}
+\subsection{Proofs for Section \ref{sec_main}}\label{app_proof_main}
 
@@
 
-\subsubsection{Proof of Theorem \ref{thm_model_shift}}\label{sec pfmain}
+Finally, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
+\todo{restate this}
+\begin{lemma}\label{prop_model_shift_tight}
+		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
+		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
+		and we have
+		\begin{align*}
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
+		\end{align*}
+\end{lemma}
+
+\subsubsection{Proof of Theorem \ref{thm_model_shift}}\label{sec_pfmain}
 

### 2020-05-26 writeup/proofs_sec3.tex
sec A0

--- 2020-05-24 writeup/proofs_sec3.tex
@@
 \end{align}
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
-To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
+where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
 \begin{align*}
@@
 	=& (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
-	=& \frac{1}{w_2} ((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
-	=& \frac{1}{w_2}\bigbrace{\beta_t + ((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(\frac{w_1}{w_2}\beta_s - w^2\beta_t) + (\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}}.
+	=& \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
+	=& \frac{1}{w_2}\bigbrace{\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_s - \frac{w_1^2}{w_2^2} \beta_t\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}}.
 \end{align*}
@@
 		\val(\hat{B}; w_1, w_2)
-	= & n_1 \cdot \bignorm{\Sigma_1^{1/2}((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - \frac{w_1}{w_2}\beta_t)}^2 \nonumber \\
-		&+ n_1 \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1} \nonumber \\
-		&+ n_2 \cdot w^2\bignorm{\Sigma_2^{1/2}((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \frac{w_1}{w_2}\beta_t)}^2 \nonumber \\
-		&+ n_2 \cdot \sigma^2 \cdot \bigtr{((\frac{w_1}{w_2})^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}. \label{eq_val_mtl}
+	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
 \end{align}
@@
 \begin{align}
-	\te(\hat{\beta}_t^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
-			&~ + \sigma^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl_2task}
+	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
+			&+~  \sigma^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl_2task}
 \end{align}
@@
 
-We state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$.
-The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.
+We now state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$.
+Before that, we first need to fix the setting for the discussions in this section.
 
-\begin{lemma}\label{lem_minv}[\todo{ref?}]
-	Let $X\in\real^{n\times p}$ be a random matrix that contains i.i.d.
-row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$.
-Let $A$ be a $p\times p$ matrix that is independent of $X$ and satisfies $\|A\|=\OO(1)$.
-	In the setting when $n = c p$ we have that
-	\[  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{c - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ p^{-1/2+\epsilon}} \]
-for any constant $\e>0$.
+\begin{assumption}\label{assm_secA1}
+We will consider two $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrices, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
+entries with mean zero and variance 1.
+Note that the rows of $X$ are i.i.d.
+centered random vectors with covariance matrix $\Sigma$.
+For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any $k\in \N$,
+\begin{equation}\label{assmAhigh}
+\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, 1\le j \le p,
+\end{equation}
+for some constant $C_k>0$.
+We assume that $n=\rho p$ for some fixed constant $\rho>1$.
+Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
+Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
+\end{assumption}
+
+Here we have assumed that \eqref{assmAhigh} holds solely for simplicity of representation.
+On the other hand, if the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-1/2+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in the error bounds.
+We will not get deeper into this issues in this section, but refer the reader to Corollary \ref{main_cor} below.
+
+The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p\to \infty$.
+When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
+Throughout the rest of this section, we shall say an event $\Xi$ holds with high probability (whp) if $\P(\Xi)\to 1$ as $p\to \infty$.
+
+\begin{lemma}\label{lem_minv} 
+Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
+	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
+with high probability.
 \end{lemma}
 
-The second lemma, which deals the inverse of the sum of two random matrices, can be viewed as a special case of Theorem \ref{thm_model_shift}.
+We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
+The second lemma extends Lemma \ref{lem_minv} for a single sample covariance matrices to the sum of two independent sample covariance matrices.
+It is the main random matrix theoretical input of this paper.
+%which deals with the inverse of the sum of two random matrices, which 
+%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
 
 \begin{lemma}\label{lem_cov_shift}
-	Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in decreasing order.
-	When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}%\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{c_1+c_2}\cdot \bigtr{ \frac{1}{p}\cdot(a_1 M^\top M + a_2)^{-1}} +\bigo{ n^{-1/2+\epsilon}},
+	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
+	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$. 
+	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
+We have that for any constant $\e>0$,
+	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
+	\begin{align}\label{lem_cov_shift_eq}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}},
 	\end{align}
-	for any constant $\epsilon>0$, where $a_1, a_2$ are solutions to the following deterministic equations:
-	\begin{align}
+with high probability, where $a_1, a_2$ are solutions to the following deterministic equations:
+	\begin{align*}
 		a_1 + a_2 = 1- \frac{1}{c_1 + c_2},~ a_1 + \frac{1}{p}\cdot\sum_{i=1}^p \frac{a_1}{(c_1 + c_2)(a_1 + a_2/ \lambda_i^2)} = \frac{c_1}{c_1 + c_2}. \label{eq_a12}
-	\end{align}
-\end{lemma}
-We will give the proof of Lemma \ref{lem_cov_shift} in Section \ref{sec_maintools}.
-
-Finally, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
-\todo{restate this}
-\begin{lemma}\label{prop_model_shift_tight}
-		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
-		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
-		and we have
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
 	\end{align*}
 \end{lemma}
+The proof of Lemma \ref{lem_cov_shift} is a main focus of Section \ref{sec_maintools}.
+We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
+\cite{nica2006lectures}), but our result \eqref{lem_cov_shift_eq} also gives an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.

### 2020-05-26 writeup/proofs_sec3.tex
minor revision

@@
 
-Here we have assumed that \eqref{assmAhigh} holds solely for simplicity of representation.
-On the other hand, if the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-1/2+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in the error bounds.
-We will not get deeper into this issues in this section, but refer the reader to Corollary \ref{main_cor} below.
+Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
+if the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in the error bounds.
+We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} below.
 
@@
 Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
-	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
+	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
 with high probability.

### 2020-05-26 writeup/proof_main.tex
minor changes

@@
 
-Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-Denote by ${\lambda}_1\ge {\lambda}_2 \ge \dots \ge {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
+Let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+Denote by ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ the singular values of $\hat{M}^{\top}\hat{M}$.
 Let $(a_1, a_2)$ be the solutions to the following system of equations

### 2020-05-26 writeup/intro.tex
wip

@@
 On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and multipl sparse regressions \cite{LPTV09,LPVT11}.
+More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and multiple sparse regressions \cite{LPTV09,LPVT11}.
 
@@
 
-%We formulate the heterogeneity between different task data under covariate and model shifts .
-%\begin{algorithm}[!t]
-%	\caption{Multi-task learning using a hard-parameter sharing architecture}
-%	\label{alg_estimator}
-%	\begin{algorithmic}[1]
-%		\Input Two regression tasks $(X_1, Y_2)$, $(X_2, Y_2)$.
-%		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
-%		\State Training the shared body $B$.
-%		\State Optimizing the task heads on the validation set
-
-%		\begin{itemize}
-%			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
-%			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
-%			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
-%		\end{itemize}
-%		\State Problem statement: how can we compare the test error of the three estimators on the target task?
-		%, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$?
-%	\end{algorithmic}
-%\end{algorithm}
-
 \textbf{Main results.}
@@
 	This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+
+	While our focus is multi-task learning, our setup and technical tools are also applicable to transfer learning settings.
+	In Section \ref{sec_taskonomy}, we provide a case study of the transfer function used in Taskonomy \cite{ZSSGM18}.
+	We observe a similar trade-off between model-shift bias and variance for this setting.
+
 	Based on the technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
-
-Our first theoretical insight is to explain a sharp transition from positive to negative transfer as a parameter of \textit{task model dissimilarity} $\norm{\beta_1 - \beta_2}^2$.
+	\begin{itemize}
+		\item First, we explain a sharp transition from positive to negative transfer as a parameter of \textit{task model dissimilarity} $\norm{\beta_1 - \beta_2}^2$.
 	In Proposition \ref{prop_dist_transition}, we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
 
-Our second theoretical insight is to show that performing multi-task learning reduces the need for labeled data, which is a key finding of Taskonomy \cite{ZSSGM18}.
+		First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.
+		\item Second, we show that performing multi-task learning reduces the need for labeled data, which is a key finding of Taskonomy \cite{ZSSGM18}.
 	We define the \textit{data efficiency ratio} as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
@@
 
-Our third theoretical insight is that as the data size becomes more imbalanced between the source and target task, having mis-aligned task covariance matrices can result in suboptimal performance.
+			Second, we validate that performing multi-task learning can reduce the need for labeled data.
+	On 6 sentiment analysis tasks, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
+		\item Finally, as the data size becomes more imbalanced between the source and target task, having mis-aligned task covariance matrices can result in suboptimal performance.
 		In Proposition \ref{prop_covariate}, we show that as $n_1 / n_2$ becomes large, the best performing source task has have the same covariance matrix as the target task.
@@
 
-Finally, while our focus is multi-task learning, our setup and technical tools are also applicable to transfer learning settings.
-In Section \ref{sec_taskonomy}, we provide a case study of the transfer function used in Taskonomy \cite{ZSSGM18}.
-We observe a similar trade-off between model-shift bias and variance for this setting.
+		Finally, we show that as the data size between the source and target task becomes more imbalanced, aligning the covariances of the tasks becomes more beneficial.
+	\end{itemize}
 
@@
 
-\textbf{Experimental results.} We show practical implications of our theoretical insights on text and image classification tasks.
-	First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.
+%\textbf{Experimental results.} We show practical implications of our theoretical insights on text and image classification tasks.
+
 	%validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.
-	Second, we validate that performing multi-task learning can reduce the need for labeled data.
-	On 6 sentiment analysis tasks, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
-	Finally, we show that as the data size between the source and target task becomes more imbalanced, aligning the covariances of the tasks becomes more beneficial.
+
 %	On the other hand, if the number of source task datapoints is comparable to the target task, aligning task covariances may hurt performance.

### 2020-05-26 writeup/setup.tex

@@
 Without loss of generality, let the $t$-th task denote the target task.
-For an estimator $\hat{\beta}\in\real^p$, the test error for target task is defined as
+For an estimator $\hat{\beta}\in\real^p$, the test error of the target task is defined as
 	\begin{align*}
@@
 		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}. \]
-Recall that we assume $n_i > p$ for every $1\le i\le t$.
+Recall that $n_i = \rho_i \cdot p$ where $\rho_i > 1$ is a fixed constant for every $1\le i\le t$.
 Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $\sigma^2 \cdot \tr[(X_i^{\top}X_i)^{-1}\Sigma_i]$.
@@
 
+In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
+For this purpose, we consider the high-dimensional setting where $p$ goes to infinity.
+A well-known result for this setting states that the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$ is $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
+Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
+However, this result only applies to the single-task setting.
+Therefore, we focus on deriving the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ when $p$ goes to infinity.
 %, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
@@
 %Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
+
+To illustrate our intuition, we begin by considering the multi-task learning setting with one source task.
+Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
+We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts (to be derived in Appendix \ref{app_proof_main})
+\begin{align}
+	\te_t(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
+	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
+\end{align}
+where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
 

### 2020-05-26 writeup/proof_main.tex
restructure appendix;

@@
-\subsection{Proofs for Section \ref{sec_main}}\label{app_proof_main}
+\subsection{Proof of Two Tasks with General Covariance}\label{app_proof_main}
 
@@
 \end{lemma}
-
-\subsubsection{Proof of Theorem \ref{thm_model_shift}}\label{sec_pfmain}
 
@@
 
-\subsubsection{Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_many_tasks}
+\subsection{Proof of Many Tasks with the Same Covariates}\label{app_proof_many_tasks}
 

### 2020-05-27 writeup/proof_main.tex
main thm

@@
 
-Let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-Denote by ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ the singular values of $\hat{M}^{\top}\hat{M}$.
-Let $(a_1, a_2)$ be the solutions to the following system of equations
+We now state the formal version of Theorem \ref{thm_main_informal}. First, we need to introduce several quantities that will be used in our statement.
+
+Given the optimal ratio $\hat v$, let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
+Denote by ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ the eigenvalues of $\hat{M}^{\top}\hat{M}$.
+Let $(\hat a_1, \hat a_2)$ be the solutions to the following deterministic equations
 	\be
-		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}.\label{eq_a2} \\
+		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat \lambda_i^2 \hat a_1}{ \hat \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
 		 \ee
-		 After obtaining $(a_1,a_2)$, we can solve the following linear equations to get $(a_3,a_4)$:
+		 After obtaining $(\hat a_1,\hat a_2)$, we can solve the following linear equations to get $(\hat a_3,\hat a_4)$:
 \begin{gather}
-		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
-		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
-		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
-		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
+		\left(\rho_2 \hat a_2^{-2}- \hat b_0\right)\cdot \hat  a_3 - \hat b_1 \cdot \hat a_4
+		=\hat b_0, \quad \left(\rho_1\hat a_1^{-2} - \hat b_2  \right)\cdot \hat a_4 - \hat b_1 \cdot \hat a_3 =\hat b_1 .\label{eq_a3} 
+%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
+%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
 	\end{gather}
+where we denoted
+$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat \lambda_i^{2k}}{ (\hat a_2 +\hat  \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
 Then we introduce the following matrix
-$$Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top},$$
-which can be regarded as the asymptotic limit of $\hat w \Sigma_2^{1/2} (\hat{w}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}$. Finally we introduce
-$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
-{\cor may be able to get a better bound, but the statement will be long}
+$$\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat a_2 +\hat  a_1 \hat {M}^{\top}\hat {M})^2} \hat {M}^{\top},$$
+which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
+$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
+We introduce two factors that will appear often in our statements and discussions:
+$$\al_-:=(1- \rho_1^{-1/2})^2,\quad \al_+:=(1 + \rho_1^{-1/2})^2.$$ 
+In fact, $\al_-^2$ and $\al_+^2$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
+In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry.
+Finally, we introduce the error term
+$$\delta:=\frac{\al_+^2 - 1 }{\al_-^{2}} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,$$
+where we recall that $\kappa(\hat M)$ is the condition number of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.
 
-We now state our main result for two tasks with both covariate and model shift in the following theorem.
+%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
+%{\cor may be able to get a better bound, but the statement will be long}
+
+Now we are ready to state our main result for two tasks with both covariate and model shift.
+It shows that the information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
 
 \begin{theorem}\label{thm_model_shift}
-	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
-	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
-	%Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-	%Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
-	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
-	With high probability we have
+For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are  random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+	Then with high probability, we have
 	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\beta} \ge  \delta \label{upper}\\
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\beta} \le -\delta, \label{lower}
 	\end{align}
@@
 	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
-		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t).
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} } \\
+		\Delta_{\beta} &\define (\beta_s - \hat{v}\beta_t)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_s - \hat{v}\beta_t).
 	\end{align*}
@@
 
-Finally, we can get a bound tighter than Theorem \ref{thm_model_shift} as follows.
-\todo{restate this}
+Under the simplifying setting in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
 \begin{lemma}\label{prop_model_shift_tight}
 		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_t$ is i.i.d. with mean $0$ and variance $\kappa^2$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$.
-		We set $\Delta_{\beta} = \bigbrace{(1 - \hat{w})^2 \kappa^2 + d^2)} \bigtr{Z}$
-		and we have
+		$\beta_t$ is a random vector with i.i.d.
+entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_2$ is a random vector such that $\beta_s - \beta_t$ is a random vector with i.i.d.
+entries with mean $0$, variance $d^2$ and all moments.
+Denote
+		$\wt \Delta_{\beta} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2)} \bigtr{\Pi}.$
+	Then we have
 		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } & \Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2+\oo(1))\cdot \wt \Delta_{\beta}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2-\oo(1))\cdot \wt\Delta_{\beta}.
 		\end{align*}
@@
 
+\begin{proof}[Proof of Theorem \ref{thm_model_shift}]
 \noindent\todo{A proof outline; including the following key lemma.}
@@
 We will give the proof of this lemma in Section \ref{sec_maintools}.
+\end{proof}
 
-\begin{proof}[Proof of Proposition \ref{prop_model_shift_tight}]
+\begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
 the proof for tighter bound ........... 

### 2020-05-27 writeup/proof_examples.tex
restructure appendix;
prop 4.4

@@
+\section{Supplementary Materials for the Theoretical Implications}
+
 \subsection{Proofs for Section \ref{sec_similarity}}\label{app_proof_31}
@@
 	By solving equations \eqref{eq_a12}, \eqref{eq_a3} and \eqref{eq_a4}, we get
-	\begin{align*}
+	\begin{align}
 		& a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}),
-		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}), \\
+		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}), \label{simplesovlea12}\\
 		& a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}),
-		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}).
-	\end{align*}
+		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}).\label{simplesovlea34}
+	\end{align}
 	Hence we obtain that
@@
 
-\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
+%\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
 {\cor (cannot get this because we only have some bounds.
@@
 \begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=n_2$.
-In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}, and by symmetry it suffices to focus on one of tasks, say task 2.
-Using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, we have that whp,
+Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$. 
+%For this proof, we introduce the notations 
+%$$\al_{\pm}^{(1)}\equiv \al_{\pm}^{(1)}(\al) = \left ( 1- (\al\rho_1)^{-1/2}\right)^2,\quad \al_{\pm}^{(2)}\equiv \al_{\pm}^{(2)}(\al) = \left ( 1- (\al\rho_2)^{-1/2}\right)^2.$$
+In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
+%and by symmetry it suffices to focus on one of tasks, say task 2. 
+Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
 \be\label{reduceproof1}
 \begin{split}
-\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{2\al c - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(2)}_{\beta},
+\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
 \end{split}
 \ee
-where $ \Delta^{(2)}_{\beta}$ satisfies 
+%and
+%\be\label{reduceproof1}
+%\begin{split}
+%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
+%\end{split}
+%\ee
+where $ \Delta^{(i)}_{\beta}$ satisfies 
 \be \nonumber
-\bigbrace{1 - \sqrt{\frac{1}{\al c}}}^4 \le \Delta^{(2)}_{\beta} /  \left( pd^2 \cdot \frac{2\al^3 c^3}{(2\al c-1)^3}+ \bigo{p^{1/2+\e}d^2}\right) \le \bigbrace{1 + \sqrt{\frac{1}{\al c}}}^4. 
+\bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \le \Delta^{(i)}_{\beta} /  \left[ pd^2 \cdot \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}\cdot\left(1+ \bigo{p^{-1/2+\e}}\right)\right] \le \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4.
 \ee
@@
 \be\label{reduceproof2} 
-\te_2(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{c-1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right).
+\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right),\quad i=1,2.
 \ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
+$$\al_l:=\frac1{\rho_1+\rho_2}\left[\frac{2(\rho_1-1)(\rho_2-1)}{\rho_1+\rho_2 -2}+1\right] \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
+In fact, one can see that if $\al\le \al_l$, then we have 
+$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
+that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \Delta^{(i)}_{\beta}$.
+Next we try to get more precise bounds on $\al^*$.
+In the following discussions, we only consider $\al$ such that $\al\rho \ge \al_l \rho \ge \min(\rho_1,\rho_2)$.
 
-Now for $c\ge 200$ and $\al \ge 1/2$, we have whp
-\be\label{reduceproof3} \te_2(\hat \beta(\al)) < \sigma^2 \frac{1}{2\al c - 1}+  \frac38 pd^2  \ee
-for large enough $p$. Moreover, if 
-$$\al \ge \al_0:=\frac{1}{2c} + \left(2-\frac{3}{4}c \cdot \frac{pd^2}{\sigma^2} \right)^{-1},$$
-we can check from \eqref{reduceproof3} that $\te_2(\hat \beta(\al))  < \te_2(\hat{\beta}_t^{\STL}) $.
-By symmetry, we also have $\te_1(\hat \beta(\al))  < \te_1(\hat{\beta}_t^{\STL}) $.
-Thus we conclude that
-$$\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$$
-for $\al\ge \al_0$, which shows that $\al^*\le \al_0$.
+%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+
+\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
+\be\label{solval1}
+\begin{split}
+&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
+&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
+\end{split}
+\ee
+For the sum on the left-hand side, we can rewrite it as
+\begin{align*}
+ pd^2 \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4,
+\end{align*}
+where $\rho:=\rho_1+\rho_2$.
+
+In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  1.32.$$%\frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
+Thus the following inequality implies \eqref{solval1}:
+\be\label{solval1add}
+\begin{split}
+&1.32 pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+In particular, if 
+\be\nonumber
+\begin{split}
+&1.32 pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+\end{split}
+\ee
+that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
+\begin{align*}
+\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - (\rho_1-1)(\rho_2-1) \cdot 1.32\frac{pd^2}{\sigma^2}}+ 1\right] \\
+& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \frac43\frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+
+\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
+\be\label{solval2}
+\begin{split}
+&(1-\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \\
+&\ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
+\end{split}
+\ee
+We then follow similar arguments as the above proof for the upper bound.
+
+In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
+where $\rho:=\rho_1+\rho_2$. 
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  0.33.$$
+Thus the following inequality implies \eqref{solval2}:
+\be\label{solval2add}
+\begin{split}
+&0.33 pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+There are two cases: if 
+\be\nonumber
+\begin{split}
+&0.33 pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
+\end{split}
+\ee
+then we always have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
+\begin{align*}
+\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - (\rho_1-1)(\rho_2-1) \cdot 0.33 \frac{pd^2}{\sigma^2}}+ 1\right] \\
+& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \frac14\frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+This concludes the proof.
+
+We remark that the constants 1.32 and 0.33 are chosen for all values of $\rho_1/\rho_2$. For a fixed ratio $\rho_1/\rho_2$, one can probably choose much better constants.
 \end{proof}

### 2020-05-27 writeup/intro.tex

@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning has recently become a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and numerous other areas \cite{ZY17}.
+Multi-task learning has become a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and numerous other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
 %Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
-By combining multiple information sources, multi-task learning allows new information to be shared across different sources in a model \cite{C97}.
+By combining multiple information sources, it is possible to share new information among different sources in the same model \cite{C97}.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
-At the same time, it is well-known that the performance of multi-task learning methods depends on the relationship between the information sources.
-\textit{Negative transfer}, the phenomenon where for a particular prediction task, multi-task learning performs worse than single-task learning, is prevalent when the information sources are heterogeneous \cite{AP16,BS17}.
+Intuitively, the performance of multi-task learning depends on the relationship of the information sources.
+When the information sources are heterogeneous, negative transfer -- where multi-task learning performs worse than single-task learning -- has often been observed \cite{AP16,BS17}.
 While numerous studies have sought to alleviate negative transfer when it occurs \cite{YKGLHF20}, a rigorous understanding to the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-In this work, we consider learning multiple high-dimensional linear regression tasks to better understand when and why negative transfer happens. % for learning from multiple linear regression tasks.
-We provide theoretical and practical insights to show how task data affects the transfer of information.
+In this work, we develop technical tools to better understand when and why negative transfer occurs for learning multiple linear regression tasks in high dimensions.
+% for learning from multiple linear regression tasks.
+We use the tools to show theoretical and practical implications for detecting and improving negative transfer.
 %We consider a setting where the target task has limited labeled data and show
@@
 
-Identifying when negative transfer occurs requires comparing the performance of multi-task learning directly to single-task learning.
-The technical challenge is to develop generalization bounds that are able to scale tightly with the qualities of task data, such as the number of datapoints.
+Identifying negative transfer requires developing tight generalization bounds for both multi-task learning and single-task learning.
 In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented in a way so that the error goes down as more labeled data is added.
@@
 More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and multiple sparse regressions \cite{LPTV09,LPVT11}.
+In order to rigorously understand negative transfer, the technical challenge is to develop generalization bounds that scale tightly with the qualities of the data.
 
@@
 
-In this work, we consider multiple high-dimensional linear regression tasks as input and focus on predicting a particular task that only has limited amount of labeled data.
-Following \cite{HMRT19,BLLT20}, we assume that for every task $1\le i\le t$, its features are random vectors $x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d.
+In this work, we consider a setting where multiple labeled linear regression tasks are available and focus on predicting a particular task whose amount of labeled data is limited.
+Following Hastie et al.
+\cite{HMRT19} and Bartlett et al.
+\cite{BLLT20}, we assume that for every task $1\le i\le t$, its features are random vectors $x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d.
 entries with mean zero and unit variance, and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
 The label of $x$ is given by $y_i = x^{\top}\beta_i + \varepsilon$, where $\beta_i\in\real^p$ denotes the ground truth parameters for task $i$ and $\varepsilon$ denotes random noise with mean zero and variance $\sigma^2$.
-Importantly, we assume that for the target task $t$, its training data size $n_t$ is a small constant $\rho_t$ times $p$. %\todo{rational}
+Importantly, we assume that the training data size of the target task $t$ is a small constant $\rho_t > 1$ times $p$ to capture the need for more labeled data.
 %We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
@@
 %distribution with covariance matrix $\Sigma_i$.
-We use a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19}.
+
+We combine all the available training data using a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
 %    \paragraph{Different covariates:}
@@
 \end{align}
-%Note that we consider the natural parameterization without reweighting the tasks above.
-%The shared body $B$ plays an important role because it allows information transfer between different task data.
-%This is known as the hard parameter sharing architecture in the literature, where we control the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}.
-%We focus on comparing the test performance on a particular task solved with equation \eqref{eq_mtl} to single-task learning.
-%The details are described in Algorithm \ref{alg_estimator}.
-Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal predictor obtained from solving equation \eqref{eq_mtl} for task $t$.
-Our goal is to compare the test error of $\hat{\beta}_t^{\MTL}$, denoted as $\te(\hat{\beta}_t^{\MTL})$, to $\te(\hat{\beta}_t^{\STL})$, where $\hat{\beta}_t^{\STL}$ is likewise obtained from equation \eqref{eq_mtl} but with task $t$ in isolation.
-
-%\begin{figure}[!t]
-%	\centering
-%	\includegraphics[width=0.8\textwidth]{figures/model_distance_motivation.pdf}
-%	\caption{Positive to negative transfer as the source task rotates further away from the target task (left to right).}
-%	\label{fig_motivation}
-%\end{figure}
+For a target task $t$,
+let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator by solving equation \eqref{eq_mtl}.
+Let $\hat{\beta}_t^{\STL}$ denote the standard linear regression estimator using task $t$ alone.
+We say there is negative transfer if the test error of $\hat{\beta}_t^{\MTL}$  is smaller than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
 
 \textbf{Main results.}
-	We begin by observing that $\te(\hat{\beta}_t^{\MTL})$ can be decomposed into two parts, a variance part that is reduced from $\te(\hat{\beta}_t^{\STL})$, and a bias part that captures the difference between $\beta_t$ and the rest of $\beta$'s.
-	We term the bias part as \textit{model shift bias}.
-	Intuitively, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ depends on the trade-off between the amount of variance reduced and the model shift bias part.
-	For the high-dimensional regime when $p$ goes to infinity, we derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL}) - \te(\hat{\beta}_t^{\STL})$ as a function of the number of datapoints $\set{n_1, n_2}$, the covariance matrices $\set{\Sigma_1, \Sigma_2}$, the ground truth parameters $\set{\beta_1, \beta_2}$, and a certain fixed value derived from solving equation \eqref{eq_mtl} (see Theorem \ref{thm_main_informal} for the statement).
-	Then, we show a similar result for any number of tasks that have the same covariates, i.e. the $X_i$'s are equal to each other.
+We revisit the bias-variance tradeoff of the multi-task estimator.
+Interestingly, the variance of $\hat{\beta}_t^{\MTL}$ is always smaller than that of $\hat{\beta}_t^{\STL}$, hence resulting in a positive effect of variance reduction.
+The bias of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, results in a negative effect caused by the difference between $\beta_t$ and the rest $\set{\beta_i}_{i=1}^{t-1}$.
+Hence, the tradeoff between the variance reduction effect and model shift bias determines whether we observe positive or negative transfer.
+
+To quantify the tradeoff more precisely, we develop a new technical result on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for two random matrices $X_1$ and $X_2$ when their dimensions $p$ are large and data sizes are fixed constants times $p$.
+Using the result, we provide a sharp bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for the setting of two tasks with general covariance matrices.
+When there are more than two tasks, we show a similar result if they all have the same covariates.
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+Finally, we apply our technical tools to the related setting of transfer learning.
+We study the transfer function used by Taskonomy \cite{ZSSGM18}, which pools learnt representations from source tasks into a shared body similar to $B$ in equation \eqref{eq_mtl}.
+We find that the model shift bias can be captured nicely by the orthogonal projection of $\beta_t$ to the subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+These results are presented more precisely in Section \ref{sec_main}.
 
-	While our focus is multi-task learning, our setup and technical tools are also applicable to transfer learning settings.
-	In Section \ref{sec_taskonomy}, we provide a case study of the transfer function used in Taskonomy \cite{ZSSGM18}.
-	We observe a similar trade-off between model-shift bias and variance for this setting.
-
-	Based on the technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
+The tradeoff that we developed in Section \ref{sec_main} depends on the qualities of each task dataset such as its data size and covariance matrix.
+In Section \ref{sec_insight}, we use the technical results to provide guidance on when positive transfer is likely to occur and identify causes of negative transfer.
 \begin{itemize}
-		\item First, we explain a sharp transition from positive to negative transfer as a parameter of \textit{task model dissimilarity} $\norm{\beta_1 - \beta_2}^2$.
-	In Proposition \ref{prop_dist_transition}, we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-
-		First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.
-		\item Second, we show that performing multi-task learning reduces the need for labeled data, which is a key finding of Taskonomy \cite{ZSSGM18}.
+		\item First, we provide a more precise interpretation to a folklore understanding in multi-task learning, which posits that negative transfer is caused by having dissimilar tasks.
+		For an example of two tasks, we show a sharp transition from positive to negative transfer determined by the ratio of $\norm{\beta_1 - \beta_2}^2$ and a certain function of data sizes (cf.
+Proposition \ref{prop_dist_transition}).
+		We further show that positive transfer is more likely to occur when transferring from a less noisy source task to a more noisy target task.
+		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
+%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
+		\item Second, we find that depending on how large $\norm{\beta_1 - \beta_2}^2$ is, adding more labeled data from the source task does not always reduce the test error of $\hat{\beta}_t^{\MTL}$ (cf.
+Proposition \ref{prop_data_size}).
+	We connect the observation to explain a key finding of Taskonomy \cite{ZSSGM18}.
 	We define the \textit{data efficiency ratio} as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
 	In Proposition \ref{prop_data_efficiency}, we show that the data efficiency ratio of an illustrative example is at most $\alert{\frac {1}{2\rho_t}}$.
-
-			Second, we validate that performing multi-task learning can reduce the need for labeled data.
-	On 6 sentiment analysis tasks, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
-		\item Finally, as the data size becomes more imbalanced between the source and target task, having mis-aligned task covariance matrices can result in suboptimal performance.
-		In Proposition \ref{prop_covariate}, we show that as $n_1 / n_2$ becomes large, the best performing source task has have the same covariance matrix as the target task.
-		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-		Finally, we show that as the data size between the source and target task becomes more imbalanced, aligning the covariances of the tasks becomes more beneficial.
+	In Section \ref{sec_validate}, we validate that performing multi-task learning can reduce the need for labeled data on 6 sentiment analysis tasks.
+%, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
+		\item Finally, we find that covariate shift, i.e. having different covariance matrices, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
+		We show that as $n_1 / n_2$ becomes large, the best performing source task has have the same covariance matrix as the target task (cf. Proposition \ref{prop_covariate}).
+%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
 \end{itemize}
 
-	A crucial technical tool that we develop for showing Theorem \ref{thm_main_informal} is the asymptotic limit of the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ (for the setting of two tasks), which may be of independent interest.
-	The result extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ \cite{S07}
-	Furthermore, the error bound for the asymptotic limit is nearly optimal.
+%	A crucial technical tool that we develop for showing Theorem \ref{thm_main_informal} is the asymptotic limit of the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ (for the setting of two tasks), which may be of independent interest.
+	The technical tool we developed extends a well-known result in the random matrix theory literature on the trace of $(X^{\top}X)^{-1}$ \cite{S07} for a single random matrix to two random matrices.
+	Our error bound for the asymptotic limit is nearly optimal, which may be of independent interest.
 
-%\textbf{Experimental results.} We show practical implications of our theoretical insights on text and image classification tasks.
-
+We show practical implications of our theory on text and image classification tasks.
+	First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.
+	Second, \todo{}
+	Finally, we show that as the data size between the source and target task becomes more imbalanced, aligning the covariances of the tasks becomes more beneficial.
+% as the data size becomes more imbalanced between the source and target task, having mis-aligned task covariance matrices can result in suboptimal performance.
 	%validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.

### 2020-05-27 writeup/proof_examples.tex
prop 4.4

@@
 In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  1.32.$$%\frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
 Thus the following inequality implies \eqref{solval1}:
@@
 \begin{split}
-&1.32 pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
 \end{split}
@@
 \begin{split}
-&1.32 pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
 \end{split}
@@
 \begin{align*}
-\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - (\rho_1-1)(\rho_2-1) \cdot 1.32\frac{pd^2}{\sigma^2}}+ 1\right] \\
-& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \frac43\frac{pd^2}{\sigma^2}}+ 1\right] .
+\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
+& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
 \end{align*}
@@
 In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
-where $\rho:=\rho_1+\rho_2$. 
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  0.33.$$
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
 Thus the following inequality implies \eqref{solval2}:
@@
 \begin{split}
-&0.33 pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
 \end{split}
@@
 \begin{split}
-&0.33 pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
 \end{split}
@@
 \begin{align*}
-\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - (\rho_1-1)(\rho_2-1) \cdot 0.33 \frac{pd^2}{\sigma^2}}+ 1\right] \\
-& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \frac14\frac{pd^2}{\sigma^2}}+ 1\right] .
+\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
+& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
 \end{align*}
 This concludes the proof.
-
-We remark that the constants 1.32 and 0.33 are chosen for all values of $\rho_1/\rho_2$. For a fixed ratio $\rho_1/\rho_2$, one can probably choose much better constants.
 \end{proof}

### 2020-05-27 writeup/intro.tex
abstract

@@
+\begin{abstract}
+	We consider multi-task and transfer learning approaches for multiple linear regressions in high dimensions.
+	We focus on predicting a particular task to better understand when we should expect multi-task and transfer learning approaches to perform better than using the task alone.
+	First, we provide sharp bias-variance tradeoffs for multi-task and transfer learning estimators obtained by solving a commonly used hard parameter sharing architecture.
+	Second, we use the technical result to provide more precise interpretations to many empirical phenomena in multi-task and transfer learning.
+	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
+	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
+	A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$, which may be of independent interest.
+\end{abstract}
+
 \section{Introduction}

### 2020-05-27 writeup/intro.tex
abstract

--- 2020-05-27 writeup/intro.tex
@@
+\begin{abstract}
+	We consider multi-task and transfer learning approaches to better understand when we should expect them to outperform single-task learning.
+	We study the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture.
+	For the setting of linear regressions in the high-dimensional regime, we provide sharp bias-variance tradeoffs for multi-task and transfer learning estimators.
+	A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
+	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
+	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
+	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
+\end{abstract}
+
 \section{Introduction}

### 2020-05-27 writeup/proof_main.tex
Update on Overleaf.

@@
 
-We now state the formal version of Theorem \ref{thm_main_informal}. First, we need to introduce several quantities that will be used in our statement.
+In this section, we state and prove the formal version of Theorem \ref{thm_main_informal}. First, we need to introduce several quantities that will be used in our statement.
 
@@
 
+Now we first give a proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift}.
+
 \begin{proof}[Proof of Theorem \ref{thm_model_shift}]
-\noindent\todo{A proof outline; including the following key lemma.}
-To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
-$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
-where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
-\begin{equation}\label{eq_12moment} %\label{assm1}
-\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
-\end{equation}
+%\noindent
+%To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
+%$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
+%where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
+%\begin{equation}\label{eq_12moment} %\label{assm1}
+%\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
+%\end{equation}
+\todo{A proof outline; including the following key lemma.}
 
-The proof of Theorem \ref{thm_model_shift} involves two parts.
+The proof is divided into four parts.
 
@@
 We will give the proof of this lemma in Section \ref{sec_maintools}.
+
+\paragraph{Part III: An $\e$-net argument.}
+
+{\cor add some arguments with $\e$-net.}
 \end{proof}
+
+{\cor add some remarks about the difficulty in random matrix theory}
+
+By applying a tighter bound to Part I of the above proof, we can conclude the proof Lemma \ref{prop_model_shift_tight}.
 
@@
 \end{proof}
-
-{\cor add some arguments with $\e$-net.}
 

### 2020-05-27 writeup/transfer.tex
merge?
Update on Overleaf.

--- 2020-05-26 writeup/transfer.tex
@@
-\section{Revisiting the Bias-Variance Trade-off for Multi-Task learning}
-\label{sec_insight}
+\section{A Technical Tool to Quantify the Trade-off}
+\label{sec_main}
 
@@
 For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
-After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
-Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
 
-\subsection{Determining Positive versus Negative Transfer}\label{sec_main}
-
-In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
-For this purpose, we consider the high-dimensional setting where $p$ goes to infinity.
-A well-known result for this setting states that the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$ is $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
-However, this result only applies to the single-task setting.
-Therefore, we focus on deriving the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ when $p$ goes to infinity.
-
-Our first result applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
+\textbf{Multi-task learning.} Our first result applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
 %The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
@@
 
+\textit{Proof overview.} By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
+%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
+This part introduces a negative effect to multi-task learning.
+The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+The output layer of each task scales the direction of $B$ suitably to fit the task.
+
+Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+This part introduces a positive variance reduction effect to performing multi-task learning.
+Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
+(i) the positive effect from variance reduction;
+(ii) the negative effect from model shift bias.
+
 Our second result applies to the setting of any number of tasks with the same covariates.
@@
 
-\subsection{Task Model Similarity}\label{sec_similarity}
+\textbf{Extensions to transfer learning.}
+While our focus is on multi-task learning, we show that our results extend to transfer learning settings naturally.
+We provide an analysis of the transfer function of Taskonomy \cite{ZSSGM18} using our setup.
+Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
+The transfer function then tries to fit the target task data to the source task encoder.
+For more details, we refer the reader to Figure 4 in Taskonomy.
+
+We map the procedure to our setup as follows.
+First, we obtain the single-task estimator $\hat{\beta}_i$ from the source tasks, for $1\le i \le t-1$.
+This forms the shared representation $B^{\star}_{t-1} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+Then, we learn the output layer $W_t$ on the target task by minimizing the following objective
+\begin{align}
+	g(W_t) = \bignorm{X_t B W_t - Y_t}^2.
+\end{align}
+After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the estimator for the target task.
+By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
+%We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
+The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.
+
+\section{Theoretical Implications}
+\label{sec_insight}
+
+After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
+Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
+
+\subsection{De-noising by Transferring from a Source Task}\label{sec_similarity}
 
@@
 
-\begin{example}\label{ex_basic}
+\textit{A simplifying setting.}\label{ex_basic}
 	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
@@
 	For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.
-\end{example}
 
@@
 
-\subsection{Data Size}\label{sec_data_size}
+\subsection{Improving Labeled Data Efficiency}\label{sec_data_size}
 
@@
 
-\subsection{Covariate Shift}\label{sec_covariate}
+\subsection{When to Align Task Covariances under Covariate Shift}\label{sec_covariate}
 
@@
 
-\section{Extending the Bias-Variance Trade-off to Transfer Learning}\label{sec_taskonomy}
-
-While our focus is on multi-task learning, we show that our results extend to transfer learning settings naturally.
-We provide an analysis of the transfer function of Taskonomy \cite{ZSSGM18} using our setup.
-Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
-The transfer function then tries to fit the target task data to the source task encoder.
-For more details, we refer the reader to Figure 4 in Taskonomy.
-
-We map the procedure to our setup as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from the source tasks, for $1\le i \le t-1$.
-This forms the shared representation $B^{\star}_{t-1} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
-Then, we learn the output layer $W_t$ on the target task by minimizing the following objective
-\begin{align}
-	g(W_t) = \bignorm{X_t B W_t - Y_t}^2.
-\end{align}
-After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the estimator for the target task.
-By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
-%We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
-The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.
+%\subsection{Extension to Transfer Learning}\label{sec_taskonomy}

### 2020-05-27 writeup/intro.tex
Updates from Overleaf

@@
 \begin{abstract}
+When does multi-task and transfer learning outperform single-task learning?
+In this paper, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
+In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators.
+A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
+	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
+	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
+	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
+
 	We consider multi-task and transfer learning approaches to better understand when we should expect them to outperform single-task learning.

### 2020-05-27 writeup/intro.tex

@@
 In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators.
-A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
-	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
-	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
-	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
-
-	We consider multi-task and transfer learning approaches to better understand when we should expect them to outperform single-task learning.
-	We study the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture.
-	For the setting of linear regressions in the high-dimensional regime, we provide sharp bias-variance tradeoffs for multi-task and transfer learning estimators.
 A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.

### 2020-05-27 writeup/intro.tex
abstract submitted

@@
 When does multi-task and transfer learning outperform single-task learning?
-In this paper, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
+In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
 In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators.

### 2020-05-27 writeup/proof_examples.tex
lem B.1

@@
 
-The proof will consist of two main steps.
-\begin{itemize}
-	\item First, we show that $\hat{v}$ is close to $1$.
-	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ to show the result.
-\end{itemize}
-
-We denote
+For the ratio $w=w_1/w_2$, we define the function
 \begin{align}
@@
 	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& + (n_1+n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+			& + (n_1 w^2 +n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
 \end{align}
-Under the setting of Proposition \ref{prop_model_shift_tight}, using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we have that
-$$\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2})\right)\quad \text{with probability }1-\oo(1).$$
-Thus it suffices to study the behavior of $\val (w)$.
-For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
-
+Under the setting of Lemma \ref{prop_model_shift_tight}, again using concentration for random vectors with i.i.d.
+entries, Lemma \ref{largedeviation}, we can obtain that for the validation loss in \eqref{eq_val_mtl},
+\be\label{boundv-w}\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2+\e})\right)\ee
+with high probability for any constant $\e>0$.
+Thus for the following discussions, it suffices focus on the behavior of $\val (w)$.
+Let $\hat w$ the minimizer of $\val(w)$.
+The proof will consist of two main steps.
+\begin{itemize}
+	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} gives that $|\hat v - \hat w|=\OO(p^{-1/2+\e})$ whp.
+	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
+\end{itemize}
+%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
+For the first step, we will prove the following result.
 \begin{lemma}\label{lem_hat_v}
-Suppose the assumptions of Proposition \ref{prop_model_shift_tight} hold.
-Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Then we have that the optimal ratio for $\val(w)$ satisfies
-	\be\label{hatw_add1}|\hat w -1|=\OO(p^{-1}).\ee
+%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
+We have that the minimizer for $\val(w)$ satisfies
+	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\ee
+	for some constant $C>0$.
 	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
@@
 \begin{proof}
-The proof is also similar to the one for Proposition \ref{thm_cov_shift}. First it is easy to observe that $\val(w)\le \val(-w)$ for $w\ge 0$. Hence it suffices to consider the $w\ge 0$ case.
+First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.
 
@@
 	& + n_2\left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& + \sigma^2(n_1+n_2) \cdot \bigtr{(w^{2}X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } .\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
+			& + n_1\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ n_2\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }.
+\nonumber
 \end{align}
-
-Taking derivative of $\val(w)$ with respect to $w$, we obtain that
+Notice that 
+$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
+are increasing functions in $w$. Hence taking derivative of $\val(w)$ with respect to $w$, we obtain that
 \begin{align*}
@@
 +&~ n_2\left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-		-&~ 2(n_1+n_2) \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_1 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
+		-&~ 2 n_2 \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_2 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
 \end{align*}
@@
 \begin{align*}
-\cal A :&= \left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2.
-- 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}X_1^\top X_1
+\cal A :&= \frac{n_1}{n_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
 \end{align*}
@@
 \begin{align*}
-\cal A \succeq - \frac{4d^2}{w^5}(\sqrt{n_2}+\sqrt{p})^4 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](\sqrt{n_1}-\sqrt{p})^4 - 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}(\sqrt{n_1}+\sqrt{p})^2\succ 0,
+\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
+&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
 \end{align*}
 as long as
-$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{(n_1+n_2)(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
-Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$.
+$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
+Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$.
 
-Then we consider the case $w\le 1$. Taking derivative of $\val(w)$ with respect to $w$, we obtain that
+Then we consider the case $w\le 1$, and the proof is similar as above. Taking derivative of $\val(w)$, we obtain that
 \begin{align}
 	\val'(w) &\le n_1 \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + n_2\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+	& + n_2\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+	&~ + n_1(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }\\
 			& = n_1 \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
@@
 where the matrix $\cal B$ is
-$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2.$$
+$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
 Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
 \begin{align*}
-\cal B \preceq - 2(1-w)\kappa^2(\sqrt{n_2}-\sqrt{p})^4 +2d^2 w\frac{n_2}{n_1}(\sqrt{n_1}+\sqrt{p})^4 \prec 0,
+\cal B \preceq - 2(1-w)\kappa^2 n_2^2 (\al_-(\rho_2) -\oo(1))^2 +2w d^2 n_1n_2 (\al_+(\rho_1) +\oo(1))^2 + 2w\sigma^2 n_2 (\al_+(\rho_2)+\oo(1)) \prec 0,
 \end{align*}
 as long as
-$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{n_2(\sqrt{n_1}+\sqrt{p})^4}{n_1(\sqrt{n_2}-\sqrt{p})^4}.$$
-Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly increasing for $w<w_2$. Hence we must have $\hat w\le w_2$. Note that under our assumptions, we have $w_2=1-\OO(p^{-1})$.
+$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
+Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly decreasing for $w<w_2$. Hence we must have $\hat w\le w_2$.
+
+In sum, we obtain that $w_2\le w\le w_1$. Note that under our assumptions, we have 
+$$\max(|w_1 -1|, |w_2 -1|) =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
+which concludes the proof.
 \end{proof}
+
+Combining \eqref{hatw_add1} and \eqref{boundv-w}, we obtain that whp,
+\be\label{hatv_add1} 
+|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2+\e} 
+\ee
+Inserting it into \eqref{eq_te_mtl_2task} and using a similar concentration result as in \eqref{boundv-w}, we get whp,
+\begin{align}
+\te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
+&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+\end{align}
+{\cor add about the choice of parameters}
 

### 2020-05-27 writeup/proof_main.tex
lem B.1

@@
 We introduce two factors that will appear often in our statements and discussions:
-$$\al_-:=(1- \rho_1^{-1/2})^2,\quad \al_+:=(1 + \rho_1^{-1/2})^2.$$ 
+$$\al_-(\rho_1):=(1- \rho_1^{-1/2})^2,\quad \al_+(\rho_1):=(1 + \rho_1^{-1/2})^2.$$ 
 In fact, $\al_-^2$ and $\al_+^2$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
@@
 Finally, we introduce the error term
-$$\delta:=\frac{\al_+^2 - 1 }{\al_-^{2}} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,$$
+$$\delta:=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,$$
 where we recall that $\kappa(\hat M)$ is the condition number of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.
@@
 		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2+\oo(1))\cdot \wt \Delta_{\beta}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2-\oo(1))\cdot \wt\Delta_{\beta}.
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot \wt \Delta_{\beta}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot \wt\Delta_{\beta}.
 		\end{align*}

### 2020-05-27 writeup/transfer.tex
lem B.1

@@
 The bounds get tighter and tighter as $\rho_1$ increases.
-A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{sec_pfmain}.
+A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
 While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we show that they provide nice interpretation for several simple settings in the rest of the section.
@@
 	%The noise level for both tasks is equal to $\sigma > 0$.
-	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
+	We have $n_i = \rho_i \cdot p$ data points from each task, for $i = 1, 2$.
 	For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 40$ is a fixed constant.
+	In the simplifying setting with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 40$ is a fixed constant.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:

### 2020-05-27 writeup/experiments.tex
re structure
reorg

@@
-\section{Experiments}
+\section{Practical Implications for Multi-Task Learning}
 
@@
 
-\subsection{Results and Analysis}
+\subsection{Detecting and Improving Negative Effects}
 
-\textbf{A metric to determine positive versus negative transfer.}
+\textbf{A Metric to Determine Positive or Negative Transfer}
 We propose a simple metric to determine whether multi-task learning performs better than single-task learning.
@@
 
-\textbf{Multi-task learning provides labeled data efficiency.}
-We measure the data efficiency ratio on text classification tasks.
-We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.
-
-\textbf{Covariance alignment provides more improvement when data size is imbalanced.}
+\textbf{Covariance Alignment for Imbalanced Tasks with Covariate Shift.}
 We validate that the performance of aligning task covariances depends on the size of source task data.
@@
 
+\subsection{Validating Theoretical Observations}
+
+\textbf{Benefits of multi-task learning.}
+
+\textit{Improving labeled data efficiency.}
+We measure the data efficiency ratio on text classification tasks.
+We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.
+
+\textit{Transferring from a high accuracy to low accuracy.}
+
+\textbf{Causes of negative transfer.}
+
 %\begin{figure}

### 2020-05-27 writeup/transfer.tex

--- 2020-05-27 writeup/transfer.tex
@@
 
-\subsection{De-noising by Transferring from a Source Task}\label{sec_similarity}
+\subsection{Benefits of Multi-task Learning}
+
+\textbf{De-noising by Transferring from a Source Task}
+We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
+We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
+
+\begin{proposition}\label{prop_var_transition}
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
+	We derive the following transition as a parameter of $\sigma_1^2$:
+	\begin{itemize}
+		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{proposition}
+As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
+The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+The details can be found in Appendix \ref{app_proof_31}.
+
+\textbf{Improving Labeled Data Efficiency}
+We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
+This is formalized by a metric called the data efficiency ratio as follows.
+Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
+More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
+If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
+\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
+We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.
+
+\begin{proposition}\label{prop_data_efficiency}
+	In the setting of Example \ref{ex_basic}, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
+	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
+\end{proposition}
+Note that we have stated the result assuming that $\rho_1 = \rho_2$.
+Similar results can also be obtained when they are different.
+We omit the details.
+The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
+
+\subsection{Contributing causes of negative transfer}
 
@@
 We formalize the intuition using our setup and technical tools.
+
+\textbf{Task model dissimilarity.}
 For a simple example of two tasks, we show that whether $\hat{\beta}_t^{\MTL} \le \hat{\beta}_t^{\STL}$ is determined by $\norm{\beta_1 - \beta_2}^2$, the distance of the task models.
@@
 
-\textbf{Implications.}
-We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
-
-\begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
-	We derive the following transition as a parameter of $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
-The details can be found in Appendix \ref{app_proof_31}.
-
-\subsection{Improving Labeled Data Efficiency}\label{sec_data_size}
-
+\textbf{Data size.}
 In classical Rademacher or VC based theory of multi-task learning, adding more labeled data improves the generalization performance of a model.
@@
 
-\textbf{Implications.} We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
-This is formalized by a metric called the data efficiency ratio as follows.
-Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
-More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
-\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
-We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.
-
-\begin{proposition}\label{prop_data_efficiency}
-	In the setting of Example \ref{ex_basic}, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
-	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
-\end{proposition}
-Note that we have stated the result assuming that $\rho_1 = \rho_2$.
-Similar results can also be obtained when they are different.
-We omit the details.
-The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
-
-\subsection{When to Align Task Covariances under Covariate Shift}\label{sec_covariate}
-
+\textbf{Covariate shift.}
 So far we have considered settings where $\Sigma_1 = \Sigma_2$.
@@
 \end{example}
-
-\textbf{Implications.}
-
-%\subsection{Extension to Transfer Learning}\label{sec_taskonomy}

### 2020-05-28 writeup/proof_examples.tex
B.1

@@
 \te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
-&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
 \end{align}
-{\cor add about the choice of parameters}
+In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order.
+With estimate \eqref{eq_isometric}, we see that
+$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim \frac{p}{n_1+n_2}.$$
+Hence we need to choose that $p\cdot d^2 \sim \sigma^2$.
+On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+2\e}\kappa^2  \ll d^2 \ll \kappa^2$.
+The above considerations lead to the following choices of parameters: there exists a constant $c>0$ such that
+\be\label{choiceofpara}
+pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c}\kappa^2  \le d^2 \le p^c \kappa^2.
+\ee
+Under this choice, we can write 
+\be\label{simpte1}
+\begin{split}
+\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
+&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  
+\end{split}
+\ee
+whp for some constant $\e>0$.
 
-Based on Lemma \ref{lem_hat_v}, we can prove Proposition \ref{prop_dist_transition}.
+With \eqref{simpte1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
+With slight abuse of notations, we shall write $\hat a_i$, $\hat b_k$ and $\hat M$ as $a_i$, $b_k$ and $M$, respectively, throughout the rest of this section.
+
 \begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
-	Since $\Sigma_1 = \Sigma_2$, we know that $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \hat{v} \id$.
-	Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as whp
+	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
+Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
 	\begin{align}
-		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{c_2 - 1} - \frac{1}{c_1 + c_2}\cdot\frac{1}{a_1\hat{v}^2 + a_2} + \bigo{p^{-1/2+\varepsilon}}} \nonumber\\
-		&= \sigma^2 \bigbrace{\frac{c_1}{(c_2-1)(c_1 + c_2 -1)} + \bigo{p^{-1/2 + \varepsilon}}},\label{Deltavar}
+		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
+		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
+		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
+		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
 	\end{align}
-	where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
-	Next we consider the model shift bias
-	\begin{align*}
-		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
-		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
-	\end{align*}
-	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
-	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
+	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
+$$\delta_{\vari}:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) $$
+with high probability, where 
+	\begin{align}
+		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.\label{Deltavar}
+	\end{align}
+	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
+	Next for the model shift bias
+	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
+	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of Lemma \ref{prop_model_shift_tight}) that
+\be\label{Deltabeta} 
+\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_\beta}{ \Delta_{\beta}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
+	where 
+	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
+%\begin{align*}
+%		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
+%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
+%	\end{align*}
+%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
+%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
 \ee
-	By solving equations \eqref{eq_a12}, \eqref{eq_a3} and \eqref{eq_a4}, we get
-	\begin{align}
-		& a_1 = \frac{c_1(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}),
-		a_2 = \frac{c_2(c_1 + c_2 - 1)}{(c_1 + c_2)^2} + O(p^{-1/2 + \varepsilon}), \label{simplesovlea12}\\
-		& a_3 = \frac{c_2}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}),
-		a_4 = \frac{c_1}{(c_1 + c_2)(c_1 + c_2 - 1)} + O(p^{-1/2 + \varepsilon}).\label{simplesovlea34}
-	\end{align}
-	Hence we obtain that
-	\begin{align*}
-		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
-		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
-	\end{align*}
-	To sum up, we have shown that when
-	\[ \frac{p\cdot d^2}{\sigma^2} < \frac{(c_1 + c_2 - 1)^2}{c_1(c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 + \sqrt{\frac 1 {c_1}}}^{-4}, \]
-	we have that $\Delta_{\vari} > \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$.
-	When
-	\[ \frac{p\cdot d^2}{\sigma^2} > \frac{(c_1 + c_2 - 1)^2}{c_1 (c_1 + c_2) (c_2 - 1)} \cdot \bigbrace{1 - \sqrt{\frac 1 {c_1}}}^{-4}, \]
-	we have that $\Delta_{\vari} < \Delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is higher than $\te(\hat{\beta}_t^{\STL})$.
-	The result follows by taking $c_1 = c_2 = c$ for the above equation.
+%	Hence we obtain that
+%	\begin{align*}
+%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
+%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
+%	\end{align*}
+With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
+\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
+	we have that $\delta_{\vari} > \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
+	\[   d^2  < \frac{\sigma^2}{p}\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1(\rho_1 + \rho_2) (\rho_2 - 1)} \cdot \left(\bigbrace{1 + \sqrt{\frac 1 {\rho_1}}}^{-4} - \oo(1)\right), \]
+Plugging into $\rho_1>40$, we obtain the first statement of Proposition \ref{prop_dist_transition}.
+
+On the other hand, if
+\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
+	we have that $\delta_{\vari} < \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
+	\[   d^2  > \frac{\sigma^2}{p}\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1(\rho_1 + \rho_2) (\rho_2 - 1)} \cdot \left(\bigbrace{1 - \sqrt{\frac 1 {\rho_1}}}^{-4} +\oo(1)\right), \]
+Plugging into $\rho_1>40$, we obtain the second statement of Proposition \ref{prop_dist_transition}.
 \end{proof}
 
+With similar techniques, we then show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
+
 \begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-
-Under the setting of Proposition \ref{prop_var_transition}, we have
+{\todo{rewrite the expressions for validation loss}} Under the setting of Proposition \ref{prop_var_transition}, we have
 \begin{align*}

### 2020-05-28 writeup/proofs_sec3.tex
restructure appendix;
Update on Overleaf.
B.1

@@
-\section{Supplementary Materials for Section \ref{sec_insight}}\label{app_proof_sec3}
+\section{Supplementary Materials for the Technical Results}\label{app_proof_sec3}
 
@@
 
-\textbf{Defining the multi-task learning estimator.}
+%For the discussions below, we assume that the entries of $\e_1$ and $\e_2$ all have the same variance $\sigma^2$.
+This holds for most parts of our discussion, except in Proposition \ref{prop_var_transition}.
+We will derive different expressions for the validation loss and the test error
+
+\textbf{Defining the multi-task learning estimator.} Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.
 Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
@@
 We will consider two $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrices, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
-entries with mean zero and variance 1.
+entries with mean zero and variance one.
 Note that the rows of $X$ are i.i.d.
@@
 	\begin{align*}
-		a_1 + a_2 = 1- \frac{1}{c_1 + c_2},~ a_1 + \frac{1}{p}\cdot\sum_{i=1}^p \frac{a_1}{(c_1 + c_2)(a_1 + a_2/ \lambda_i^2)} = \frac{c_1}{c_1 + c_2}. \label{eq_a12}
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+\label{eq_a12}
 	\end{align*}

### 2020-05-28 writeup/transfer.tex
wip

@@
-\section{A Technical Tool to Quantify the Trade-off}
+\section{A Technical Tool to Quantify the Bias-Variance Trade-off}
 \label{sec_main}
@@
 
-\subsection{Benefits of Multi-task Learning}
-
-\textbf{De-noising by Transferring from a Source Task}
-We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
-
-\begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
-	We derive the following transition as a parameter of $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
-The details can be found in Appendix \ref{app_proof_31}.
-
-\textbf{Improving Labeled Data Efficiency}
-We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
-This is formalized by a metric called the data efficiency ratio as follows.
-Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
-More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
-\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
-We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.
-
-\begin{proposition}\label{prop_data_efficiency}
-	In the setting of Example \ref{ex_basic}, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
-	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
-\end{proposition}
-Note that we have stated the result assuming that $\rho_1 = \rho_2$.
-Similar results can also be obtained when they are different.
-We omit the details.
-The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
-
 \subsection{Contributing causes of negative transfer}
@@
 \end{example}
+
+\subsection{Interpreting the Benefits of Multi-task Learning}
+
+\textbf{De-noising by Transferring from a Source Task}
+We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
+We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
+
+\begin{proposition}\label{prop_var_transition}
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
+	We derive the following transition as a parameter of $\sigma_1^2$:
+	\begin{itemize}
+		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{proposition}
+As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
+The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+The details can be found in Appendix \ref{app_proof_31}.
+
+\textbf{Improving Labeled Data Efficiency}
+We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
+This is formalized by a metric called the data efficiency ratio as follows.
+Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
+More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
+If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
+\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
+We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.
+
+\begin{proposition}\label{prop_data_efficiency}
+	In the setting of Example \ref{ex_basic}, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
+	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
+\end{proposition}
+Note that we have stated the result assuming that $\rho_1 = \rho_2$.
+Similar results can also be obtained when they are different.
+We omit the details.
+The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.

### 2020-05-28 writeup/proof_examples.tex
B.1, B.2

@@
 Under this choice, we can write 
-\be\label{simpte1}
+\be\label{simple1}
 \begin{split}
@@
 
-With \eqref{simpte1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
+With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
 With slight abuse of notations, we shall write $\hat a_i$, $\hat b_k$ and $\hat M$ as $a_i$, $b_k$ and $M$, respectively, throughout the rest of this section.
@@
 	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
-$$\delta_{\vari}:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) $$
+\be\label{Deltavar}
+\begin{split}
+\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
+&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
+\end{split}
+\ee
 with high probability, where 
-	\begin{align}
-		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.\label{Deltavar}
-	\end{align}
+	\begin{align*}
+		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
+	\end{align*}
 	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
@@
 \begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-{\todo{rewrite the expressions for validation loss}} Under the setting of Proposition \ref{prop_var_transition}, we have
+In the setting of Proposition \ref{prop_var_transition}, the validation loss and the test error become
+\begin{align*}
+		\val(\hat{B}; w_1, w_2)
+	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
+		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
+\end{align*}
+and 
 \begin{align*}
 	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
-			&~ + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)\hat v^2  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1}.
+			&~ + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2) \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2 X_1^\top X_1},
 \end{align*}
-Using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we obtain that
+where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$.
+Again using concentration of random vector with i.i.d.
+entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_t^{\MTL})$ as
 \begin{align*}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( w-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2})\right)\nonumber \\
-	& + (\sigma_1^2 -\sigma_2^2)\hat v^2  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }.
+	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( w-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
+	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
 \end{align*}
-In the setting of Proposition \ref{prop_var_transition}, we can also obtain that
-$$|\hat w-1|=\OO(p^{-1}).$$
-as in \eqref{hatw_add1}. We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. Thus $\te(\hat{\beta}_t^{\MTL}) $ can be reduced to 
-$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_\beta + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
-where $\Delta_\beta:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has been estimated in \eqref{Deltabeta} and $\Delta_{diff}$ is
+with high probability for any constant $\e>0$.
+
+In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
+Since the proof is almost the same as the one for Lemma \ref{lem_hat_v}, we omit the details. 
+%$$|\hat w-1|=\OO(p^{-1}).$$
+%as in \eqref{hatw_add1}. 
+%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
+Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_t^{\MTL}) $ can be simplified as in \eqref{simple1}: 
+\be \label{simple2}
+\begin{split}
+\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
+&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
+&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+\end{split}
+\ee
+Then we write 
+$$ \te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta - \delta_{\vari}^{(2)},$$
+where 
+$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
+satisfies \eqref{Deltavar} but with $\sigma^2$ replaced with $\sigma_2^2$, 
+$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
+satisfies \eqref{Deltabeta}, and 
 \begin{align*}	
-	\Delta_{diff}:=(\sigma_1^2 -\sigma_2^2) \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
 \end{align*}
-Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
-$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
+%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_\beta + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
+%where $\Delta_\beta:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
+To estimate this new term, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
+\be\label{Deltavar2} 
+\al_-(\rho_1) - \oo(1)  \le \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
+where 
+$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
+Next we compare $\delta_{\vari}$ with $\delta_\beta + \delta_{\vari}^{(2)}$. Our main goal is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
 
-Next we compare $\Delta_{\var}$ with $\Delta_\beta + \Delta_{diff}$.
-Under the condition $d^2 < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)}$, if $\sigma_1^2\le \sigma_2^2$ then we always have that $\Delta_{\vari} > \Delta_{\beta}$ and hence $\te(\hat{\beta}_t^{\MTL})$ is smaller than $\te(\hat{\beta}_t^{\STL})$.
+%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
+%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
+
+Note that the condition $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$ means the we have $\delta_{\vari}>\delta_{\beta} $ by Proposition \ref{prop_dist_transition}.
+Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\beta}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$.
+
 It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
-If
-\begin{align} 
-&\sigma_2^2  \frac{c_1}{(c_2-1)(c_1 + c_2 -1)}\left(1 + \bigo{p^{-1/2 + \varepsilon}}\right) \label{cond sigma1}\\
-&> \left[\frac{c_1^2 (c_1+c_2)}{(c_1+c_2-1)^3} + \bigo{p^{-1/2 + \varepsilon}}\right]\left[pd^2 \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 + \frac{\sigma_1^2-\sigma_2^2}{c_1} \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2\right] ,\nonumber
-\end{align}
-then we have $\Delta_{\vari} > \Delta_{\beta}$ and we have $\te(\hat{\beta}_t^{\MTL})$ is smaller than $\te(\hat{\beta}_t^{\STL})$.
-For $c_1\ge 100$, we see that \eqref{cond sigma1} is implied by the following condition
-$$\sigma_1^2 \le pd^2 \cdot c_1 + \left[ 1+ \frac23\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \right]\sigma_2^2$$
-as long as $p$ is large enough. On the other hand, if 
-\begin{align} 
-&\sigma_2^2  \frac{c_1}{(c_2-1)(c_1 + c_2 -1)}\left(1 + \bigo{p^{-1/2 + \varepsilon}}\right) \label{cond sigma12}\\
-&< \left[\frac{c_1^2 (c_1+c_2)}{(c_1+c_2-1)^3} + \bigo{p^{-1/2 + \varepsilon}}\right]\left[pd^2 \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 + \frac{\sigma_1^2-\sigma_2^2}{c_1} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\right] ,\nonumber
-\end{align}
-then we have $\Delta_{\vari} < \Delta_{\beta}$ and we have $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$.
-For $c_1\ge 100$, we see that \eqref{cond sigma12} is implied by the following condition
-$$\sigma_1^2 \ge  pd^2 \cdot c_1 + \left[ 1+ \frac32\frac{(c_1 + c_2 - 1)^2}{(c_1 + c_2) (c_2 - 1)} \right]\sigma_2^2.$$
+
+\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2} above, if
+\be\label{cond sigma1}
+\begin{split} 
+&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
+&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 ,
+\end{split}
+\ee
+then we have $\delta_{\vari} > \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
+\begin{align*}
+\sigma_1^2 < - pd^2 \cdot \rho_1\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1-\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1-\oo(1)).
+\end{align*}
+Plugging into $\rho_1>50$, we obtain the first claim of Proposition \ref{prop_var_transition} for positive transfer.
+
+\noindent{\bf Negative transfer.} On the other hand, if 
+\be\label{cond sigma12}
+\begin{split} 
+&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
+&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 ,
+\end{split}
+\ee
+then we have $\delta_{\vari} < \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
+\begin{align*}
+\sigma_1^2 > - pd^2 \cdot \rho_1\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1+\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1+\oo(1)).
+\end{align*}
+Plugging into $\rho_1>50$, we obtain the second claim of Proposition \ref{prop_var_transition} for negative transfer.
 \end{proof}
@@
 \subsection{Proofs for Section \ref{sec_data_size}}\label{app_proof_data}
+
+We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.
 
@@
 If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
+
+Then we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio.
 

### 2020-05-28 writeup/transfer.tex
B.1, B.2

--- 2020-05-27 writeup/transfer.tex
@@
 \begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
 	We derive the following transition as a parameter of $\sigma_1^2$:
 	\begin{itemize}
-		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > - \frac12p d^2 \cdot \rho_1 +\left(1+ \frac32\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}

### 2020-05-28 writeup/transfer.tex

--- 2020-05-28 writeup/transfer.tex
@@
 
+\textbf{Implications.}
+We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
+We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
+
+\begin{proposition}\label{prop_var_transition}
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
+	We derive the following transition as a parameter of $\sigma_1^2$:
+	\begin{itemize}
+		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > - \frac12p d^2 \cdot \rho_1 +\left(1+ \frac32\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{proposition}
+As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
+The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+The details can be found in Appendix \ref{app_proof_31}.
+
+\subsection{Improving Labeled Data Efficiency}\label{sec_data_size}
+
 \textbf{Data size.}

### 2020-05-28 writeup/transfer.tex
changes

@@
 
-\subsection{Contributing causes of negative transfer}
+\subsection{Contributing causes of negative transfer}\label{sec_similarity}
 
@@
 \end{figure}
-
-\textbf{Implications.}
-We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
-
-\begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
-	We derive the following transition as a parameter of $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > - \frac12p d^2 \cdot \rho_1 +\left(1+ \frac32\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
-The details can be found in Appendix \ref{app_proof_31}.
 
@@
 \begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 40$ is a fixed constant and $d^2 < \frac {2\sigma_2^2} {3p} \cdot \Phi(\rho_1, \rho_2)$.
+	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
 	We derive the following transition as a parameter of $\sigma_1^2$:
 	\begin{itemize}
-		\item If $\sigma_1^2 \le p d^2 \cdot \rho_1 +\left(1+ \frac12 \cdot \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > p d^2 \cdot \rho_1 +\left(1+ 2\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}

### 2020-05-28 writeup/transfer.tex
sec 4

--- 2020-05-28 writeup/transfer.tex
@@
 
-We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
-For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
+%We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
+We develop a technical tool to derive $\te(\hat{\beta}_t^{\MTL})$ that only depends on the qualities of task data such as data sizes and covariance matrices, for two tasks with general covariances.
+Then, we extend the result to more than two tasks that share the same features but have different labels.
+Finally, we show a sharp bias-variance tradeoff for transfer learning settings.
+%For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
 
-\textbf{Multi-task learning.} Our first result applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
+\textbf{Multi-task learning.} applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
 %The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
@@
 The bounds get tighter and tighter as $\rho_1$ increases.
-A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
-While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we show that they provide nice interpretation for several simple settings in the rest of the section.
+While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we will show that they provide nice interpretation for simplified settings later on in Section \ref{sec_insight}.
 
-\textit{Proof overview.} By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
+We describe an overview of the proof of Theorem \ref{thm_main_informal}.
+By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
 %We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
@@
 (ii) the negative effect from model shift bias.
+A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
 
-Our second result applies to the setting of any number of tasks with the same covariates.
+\textbf{Extension.} The above result also applies to the setting of more than two tasks with the same covariates.
 %We extend the above result to any number of tasks that have the same covariates.
@@
 %For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
-We can also derive a tight trade-off between model shift bias and variance reduction for this setting.
+%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
+We derive a similar trade-off between model shift bias and variance reduction for this setting as well.
 The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
 
-\textbf{Extensions to transfer learning.}
-While our focus is on multi-task learning, we show that our results extend to transfer learning settings naturally.
+\textbf{Transfer learning.}
+We extend the intuition behind Theorem \ref{thm_main_informal} to transfer learning settings.
 We provide an analysis of the transfer function of Taskonomy \cite{ZSSGM18} using our setup.
@@
 
-After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
-Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
+Based on Theorem \ref{thm_main_informal}, we provide precise interpretations of many empirical phenomena of multi-task learning.
+We show that negative transfer may result from three factors, including model dissimilarity, data size and covariate shift.
+Furthermore, we describe two benefits of multi-task learning, including de-noising via less noisy source labels and improving labeled data efficiency.
 
-\subsection{Contributing causes of negative transfer}
+%After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
+%Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
+
+\subsection{Contributing Causes of Negative Transfer}
 
@@
 
-\textbf{Task model dissimilarity.}
-For a simple example of two tasks, we show that whether $\hat{\beta}_t^{\MTL} \le \hat{\beta}_t^{\STL}$ is determined by $\norm{\beta_1 - \beta_2}^2$, the distance of the task models.
-We derive a sharp threshold when positive transfer transitions to negative transfer, as a function of model distance $\norm{\beta_1 - \beta_2}^2$, data size $n_1$ abd $n_2$ and the noise level $\sigma$.
-
-\textit{A simplifying setting.}\label{ex_basic}
+\textit{A simplifying setting.}
 	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
@@
 	For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.
+
+\textbf{Model dissimilarity.}
+For a simple example of two tasks, we show that whether $\hat{\beta}_t^{\MTL} \le \hat{\beta}_t^{\STL}$ is determined by $\norm{\beta_1 - \beta_2}^2$, the distance of the task models.
+We derive a sharp threshold when positive transfer transitions to negative transfer, as a function of model distance $\norm{\beta_1 - \beta_2}^2$, data size $n_1$ abd $n_2$ and the noise level $\sigma$.
 
@@
 	\begin{itemize}
-		\item If ${d^2} < \frac {\sigma^2} {2p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${d^2} \ge \frac {2\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} < \frac{1}{2}\cdot \frac {\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${d^2} \ge 2\cdot\frac {\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
-		\caption{Task model similarity}
+		\caption{Task model dissimilarity}
 		\label{fig_model_shift}
@@
 		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
-		\caption{Data size}
+		\caption{Large source task data size}
 	\end{subfigure}\hfill
@@
 	\end{subfigure}
-	\caption{Comparing the test error of multi-task learning to single-task learning: (a) positive to negative transfer as the task model dissimilarity increases (cf.
-Proposition \ref{prop_dist_transition}) (b) positive to negative transfer as the source task data size increases (cf.
-Proposition \ref{prop_data_size}); (c) }
+	\caption{Three contributing causes of negative transfer:
+	(a) As the task model dissimilarity increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
+	(b) As source task data size increases, we observe a positive to negative transfer as the source task data size increases (Proposition \ref{prop_data_size}).
+	(c) As covariate shift becomes more significant, test performance gets worse (Proposition \ref{prop_covariate}).}
 	\label{fig_model_shift_phasetrans}
 \end{figure}
-
-\textbf{Implications.}
-We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
-
-\begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
-	We derive the following transition as a parameter of $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > - \frac12p d^2 \cdot \rho_1 +\left(1+ \frac32\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
-The details can be found in Appendix \ref{app_proof_31}.
-
-\subsection{Improving Labeled Data Efficiency}\label{sec_data_size}
 
@@
 
-\subsection{Interpreting the Benefits of Multi-task Learning}
+\subsection{Implications on the Benefits of Multi-task Learning}
 

### 2020-05-28 writeup/setup.tex

@@
 
-Recall that we have $t$ labeled tasks available, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$.
-Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d.
+We describe the bias-variance tradeoff of our setting as a warmup.
+Recall that we have $t$ labeled tasks available, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
+%Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d.
 entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
@@
 	\end{align*}
+The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
+The bias-variance trade-off \cite{HTF09} says
+	\[ \te_t(\hat{\beta}) =
+		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\bignorm{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}^2}. \]
+In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
+For this purpose, we consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
+%Recall that $n_i = \rho_i \cdot p$ and we assume $\rho_i > 1$ is a fixed constant for every $1\le i\le t$.
 
-Let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$ denote the linear regression estimator, which can be also be obtained from equation \eqref{eq_mtl} by using the target task alone.
-The bias-variance trade-off \cite{HTF09} says that
-	\[ \te_t(\hat{\beta}) =
-		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}. \]
-Recall that $n_i = \rho_i \cdot p$ where $\rho_i > 1$ is a fixed constant for every $1\le i\le t$.
-Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $\sigma^2 \cdot \tr[(X_i^{\top}X_i)^{-1}\Sigma_i]$.
-We focus on a setting where the data size $n_t$ of the target task is equal to a small constant $\rho_t > 1$ times $p$.
+We focus on a setting where $\rho_t$ is a small constant.
 This setting captures the need for adding more labeled data to reduce the test error of the target task.
-
-In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
-For this purpose, we consider the high-dimensional setting where $p$ goes to infinity.
-A well-known result for this setting states that the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$ is $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
+A well-known result for this setting states that $\te_t(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \tr[(X_t^{\top}X_t)^{-1}\Sigma_t]$ is concentrated around $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
 Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
 However, this result only applies to the single-task setting.
-Therefore, we focus on deriving the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ when $p$ goes to infinity.
-%, i.e. %(following the argument of Proposition \ref{prop_monotone}), i.e.
-%\[ \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} \le \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}. \]
-%Because of model shift bias, we can no longer guarantee that $\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL})$.
+Therefore, our goal is to extend this result to the multi-task setting.
 
-To illustrate our intuition, we begin by considering the multi-task learning setting with one source task.
+To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.
 Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
-We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the targe task into two parts (to be derived in Appendix \ref{app_proof_main})
+We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts (to be derived in Appendix \ref{app_proof_sec3}) as follows
 \begin{align}
@@
 where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
+%Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $$.
 
-\textbf{Notations.} We refer to the last ($t$-th) task as the target task and the first task as the source task when there are only two tasks.
+\textbf{Notations.}
 When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
+We refer to the first task as the source task when there are only two tasks.
 We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.

### 2020-05-28 writeup/transfer.tex

@@
 
+\subsection{Improving Labeled Data Efficiency}\label{sec_data_size}
+
 \textbf{Data size.}

### 2020-05-28 writeup/transfer.tex
fix link

@@
 
-\textit{A simplifying setting.}
+\textit{A simplified model.}
 	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the simplifying setting with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 40$ is a fixed constant.
+	In the simplified model, assume that $\rho_1 > 40$ is a fixed constant.
+	Let $\sigma_1 = \sigma_2 = \sigma$.
 	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
@@
 
-\subsection{Improving Labeled Data Efficiency}\label{sec_data_size}
-
 \textbf{Data size.}
@@
 \begin{proposition}\label{prop_data_size}
-	In the setting of Example \ref{ex_basic}, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants.
+	In the simplified model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants.
 	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
@@
 
-\begin{example}\label{ex_cov_family}
 	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, we assume an upper bound on the scale of $M$.
@@
 	The following proposition shows that when $n_1$ is large enough compared to $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized approximately within the family of $\cS_{\mu}$ when $M = \mu\id$.
-\end{example}
 
 \begin{proposition}\label{prop_covariate}
-	In the setting of Example \ref{ex_basic}, assume that $\rho_1 > 3$ and $\rho_2>3$,
+	In the simplified model, assume that $\rho_1 > 3$ and $\rho_2>3$,
 and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. %As a parameter of $M \in \cS_{\mu}$,
@@
 \begin{proposition}\label{prop_var_transition}
-	In the setting of Example \ref{ex_basic} with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
+	In the simplified model with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
 	We derive the following transition as a parameter of $\sigma_1^2$:
@@
 \begin{proposition}\label{prop_data_efficiency}
-	In the setting of Example \ref{ex_basic}, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
+	In the simplified model, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
 	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.

### 2020-05-28 writeup/transfer.tex
fix

@@
 On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-Using Example \ref{ex_basic}, we analyze the effect of varying the source task data size.
+Using the simplified model, we analyze the effect of varying the source task data size.
 
@@
 \[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
-We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for Example \ref{ex_basic} as follows.
+We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for the simplified model as follows.
 

### 2020-05-28 writeup/proof_examples.tex
reorder

@@
 
-With similar techniques, we then show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
-
-\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-In the setting of Proposition \ref{prop_var_transition}, the validation loss and the test error become
-\begin{align*}
-		\val(\hat{B}; w_1, w_2)
-	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
-		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
-\end{align*}
-and 
-\begin{align*}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
-			&~ + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2) \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2 X_1^\top X_1},
-\end{align*}
-where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$.
-Again using concentration of random vector with i.i.d.
-entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_t^{\MTL})$ as
-\begin{align*}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( w-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
-	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
-\end{align*}
-with high probability for any constant $\e>0$.
-
-In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
-Since the proof is almost the same as the one for Lemma \ref{lem_hat_v}, we omit the details. 
-%$$|\hat w-1|=\OO(p^{-1}).$$
-%as in \eqref{hatw_add1}. 
-%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
-Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_t^{\MTL}) $ can be simplified as in \eqref{simple1}: 
-\be \label{simple2}
-\begin{split}
-\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
-&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
-&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
-\end{split}
-\ee
-Then we write 
-$$ \te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta - \delta_{\vari}^{(2)},$$
-where 
-$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
-satisfies \eqref{Deltavar} but with $\sigma^2$ replaced with $\sigma_2^2$, 
-$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
-satisfies \eqref{Deltabeta}, and 
-\begin{align*}	
-	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
-\end{align*}
-%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_\beta + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
-%where $\Delta_\beta:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
-To estimate this new term, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
-This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
-\be\label{Deltavar2} 
-\al_-(\rho_1) - \oo(1)  \le \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
-where 
-$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
-Next we compare $\delta_{\vari}$ with $\delta_\beta + \delta_{\vari}^{(2)}$. Our main goal is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
-
-%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
-%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
-
-Note that the condition $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$ means the we have $\delta_{\vari}>\delta_{\beta} $ by Proposition \ref{prop_dist_transition}.
-Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\beta}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$.
-
-It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
-
-\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2} above, if
-\be\label{cond sigma1}
-\begin{split} 
-&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
-&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 ,
-\end{split}
-\ee
-then we have $\delta_{\vari} > \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
-\begin{align*}
-\sigma_1^2 < - pd^2 \cdot \rho_1\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1-\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1-\oo(1)).
-\end{align*}
-Plugging into $\rho_1>50$, we obtain the first claim of Proposition \ref{prop_var_transition} for positive transfer.
-
-\noindent{\bf Negative transfer.} On the other hand, if 
-\be\label{cond sigma12}
-\begin{split} 
-&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
-&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 ,
-\end{split}
-\ee
-then we have $\delta_{\vari} < \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
-\begin{align*}
-\sigma_1^2 > - pd^2 \cdot \rho_1\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1+\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1+\oo(1)).
-\end{align*}
-Plugging into $\rho_1>50$, we obtain the second claim of Proposition \ref{prop_var_transition} for negative transfer.
-\end{proof}
-
-\subsection{Proofs for Section \ref{sec_data_size}}\label{app_proof_data}
-
-We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.
+Then we prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.
 
@@
  \end{proof}
-
-%\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
-{\cor (cannot get this because we only have some bounds.
-If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
-
-Then we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio.
-
-\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$. 
-%For this proof, we introduce the notations 
-%$$\al_{\pm}^{(1)}\equiv \al_{\pm}^{(1)}(\al) = \left ( 1- (\al\rho_1)^{-1/2}\right)^2,\quad \al_{\pm}^{(2)}\equiv \al_{\pm}^{(2)}(\al) = \left ( 1- (\al\rho_2)^{-1/2}\right)^2.$$
-In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
-%and by symmetry it suffices to focus on one of tasks, say task 2. 
-Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
-\be\label{reduceproof1}
-\begin{split}
-\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
-\end{split}
-\ee
-%and
-%\be\label{reduceproof1}
-%\begin{split}
-%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
-%\end{split}
-%\ee
-where $ \Delta^{(i)}_{\beta}$ satisfies 
-\be \nonumber
-\bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \le \Delta^{(i)}_{\beta} /  \left[ pd^2 \cdot \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}\cdot\left(1+ \bigo{p^{-1/2+\e}}\right)\right] \le \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4.
-\ee
-On the other hand, using Lemma \ref{lem_minv}, we have whp
-\be\label{reduceproof2} 
-\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right),\quad i=1,2.
-\ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
-$$\al_l:=\frac1{\rho_1+\rho_2}\left[\frac{2(\rho_1-1)(\rho_2-1)}{\rho_1+\rho_2 -2}+1\right] \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
-In fact, one can see that if $\al\le \al_l$, then we have 
-$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
-that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \Delta^{(i)}_{\beta}$.
-Next we try to get more precise bounds on $\al^*$.
-In the following discussions, we only consider $\al$ such that $\al\rho \ge \al_l \rho \ge \min(\rho_1,\rho_2)$.
-
-%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
-
-\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
-\be\label{solval1}
-\begin{split}
-&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
-&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
-\end{split}
-\ee
-For the sum on the left-hand side, we can rewrite it as
-\begin{align*}
- pd^2 \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4,
-\end{align*}
-where $\rho:=\rho_1+\rho_2$.
-
-In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
-Thus the following inequality implies \eqref{solval1}:
-\be\label{solval1add}
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
-\end{split}
-\ee
-In particular, if 
-\be\nonumber
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
-\end{split}
-\ee
-that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
-\begin{align*}
-\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
-& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-
-\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
-\be\label{solval2}
-\begin{split}
-&(1-\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \\
-&\ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
-\end{split}
-\ee
-We then follow similar arguments as the above proof for the upper bound.
-
-In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
-Thus the following inequality implies \eqref{solval2}:
-\be\label{solval2add}
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
-\end{split}
-\ee
-There are two cases: if 
-\be\nonumber
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
-\end{split}
-\ee
-then we always have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
-\begin{align*}
-\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
-& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-This concludes the proof.
-\end{proof}
-
-\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}
 
@@
 \fi
+
+\subsection{Proofs for Section \ref{sec_data_size}}\label{app_proof_data}
+
+With similar techniques, we then show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
+
+\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
+In the setting of Proposition \ref{prop_var_transition}, the validation loss and the test error become
+\begin{align*}
+		\val(\hat{B}; w_1, w_2)
+	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
+		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
+\end{align*}
+and 
+\begin{align*}
+	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
+			&~ + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2) \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2 X_1^\top X_1},
+\end{align*}
+where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$.
+Again using concentration of random vector with i.i.d.
+entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_t^{\MTL})$ as
+\begin{align*}
+	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( w-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
+	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
+\end{align*}
+with high probability for any constant $\e>0$.
+
+In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
+Since the proof is almost the same as the one for Lemma \ref{lem_hat_v}, we omit the details. 
+%$$|\hat w-1|=\OO(p^{-1}).$$
+%as in \eqref{hatw_add1}. 
+%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
+Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_t^{\MTL}) $ can be simplified as in \eqref{simple1}: 
+\be \label{simple2}
+\begin{split}
+\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
+&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
+&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+\end{split}
+\ee
+Then we write 
+$$ \te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta - \delta_{\vari}^{(2)},$$
+where 
+$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
+satisfies \eqref{Deltavar} but with $\sigma^2$ replaced with $\sigma_2^2$, 
+$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
+satisfies \eqref{Deltabeta}, and 
+\begin{align*}	
+	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+\end{align*}
+%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_\beta + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
+%where $\Delta_\beta:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
+To estimate this new term, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
+\be\label{Deltavar2} 
+\al_-(\rho_1) - \oo(1)  \le \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
+where 
+$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
+Next we compare $\delta_{\vari}$ with $\delta_\beta + \delta_{\vari}^{(2)}$. Our main goal is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
+
+%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
+%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
+
+Note that the condition $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$ means the we have $\delta_{\vari}>\delta_{\beta} $ by Proposition \ref{prop_dist_transition}.
+Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\beta}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$.
+
+It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
+
+\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2} above, if
+\be\label{cond sigma1}
+\begin{split} 
+&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
+&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 ,
+\end{split}
+\ee
+then we have $\delta_{\vari} > \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
+\begin{align*}
+\sigma_1^2 < - pd^2 \cdot \rho_1\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1-\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1-\oo(1)).
+\end{align*}
+Plugging into $\rho_1>50$, we obtain the first claim of Proposition \ref{prop_var_transition} for positive transfer.
+
+\noindent{\bf Negative transfer.} On the other hand, if 
+\be\label{cond sigma12}
+\begin{split} 
+&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
+&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 ,
+\end{split}
+\ee
+then we have $\delta_{\vari} < \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
+\begin{align*}
+\sigma_1^2 > - pd^2 \cdot \rho_1\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1+\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1+\oo(1)).
+\end{align*}
+Plugging into $\rho_1>50$, we obtain the second claim of Proposition \ref{prop_var_transition} for negative transfer.
+\end{proof}
+
+%\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
+{\cor (cannot get this because we only have some bounds.
+If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
+
+Then we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio.
+
+\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
+Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$. 
+%For this proof, we introduce the notations 
+%$$\al_{\pm}^{(1)}\equiv \al_{\pm}^{(1)}(\al) = \left ( 1- (\al\rho_1)^{-1/2}\right)^2,\quad \al_{\pm}^{(2)}\equiv \al_{\pm}^{(2)}(\al) = \left ( 1- (\al\rho_2)^{-1/2}\right)^2.$$
+In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
+%and by symmetry it suffices to focus on one of tasks, say task 2. 
+Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
+\be\label{reduceproof1}
+\begin{split}
+\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
+\end{split}
+\ee
+%and
+%\be\label{reduceproof1}
+%\begin{split}
+%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
+%\end{split}
+%\ee
+where $ \Delta^{(i)}_{\beta}$ satisfies 
+\be \nonumber
+\bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \le \Delta^{(i)}_{\beta} /  \left[ pd^2 \cdot \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}\cdot\left(1+ \bigo{p^{-1/2+\e}}\right)\right] \le \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4.
+\ee
+On the other hand, using Lemma \ref{lem_minv}, we have whp
+\be\label{reduceproof2} 
+\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right),\quad i=1,2.
+\ee
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
+$$\al_l:=\frac1{\rho_1+\rho_2}\left[\frac{2(\rho_1-1)(\rho_2-1)}{\rho_1+\rho_2 -2}+1\right] \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
+In fact, one can see that if $\al\le \al_l$, then we have 
+$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
+that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \Delta^{(i)}_{\beta}$.
+Next we try to get more precise bounds on $\al^*$.
+In the following discussions, we only consider $\al$ such that $\al\rho \ge \al_l \rho \ge \min(\rho_1,\rho_2)$.
+
+%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+
+\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
+\be\label{solval1}
+\begin{split}
+&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
+&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
+\end{split}
+\ee
+For the sum on the left-hand side, we can rewrite it as
+\begin{align*}
+ pd^2 \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4,
+\end{align*}
+where $\rho:=\rho_1+\rho_2$.
+
+In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
+Thus the following inequality implies \eqref{solval1}:
+\be\label{solval1add}
+\begin{split}
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+In particular, if 
+\be\nonumber
+\begin{split}
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+\end{split}
+\ee
+that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
+\begin{align*}
+\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
+& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+
+\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
+\be\label{solval2}
+\begin{split}
+&(1-\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \\
+&\ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
+\end{split}
+\ee
+We then follow similar arguments as the above proof for the upper bound.
+
+In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
+Thus the following inequality implies \eqref{solval2}:
+\be\label{solval2add}
+\begin{split}
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+There are two cases: if 
+\be\nonumber
+\begin{split}
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
+\end{split}
+\ee
+then we always have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
+\begin{align*}
+\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
+& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+This concludes the proof.
+\end{proof}
+
+%\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}

### 2020-05-28 writeup/transfer.tex
reorder

@@
 
-\subsection{Contributing Causes of Negative Transfer}
+\subsection{Contributing Causes of Negative Transfer}\label{sec_similarity}
 
@@
 ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.
-We leave the proof of Proposition \ref{prop_data_size} to Appendix \ref{app_proof_data}.
+We leave the proof of Proposition \ref{prop_data_size} to Appendix \ref{app_proof_31}.
 
@@
 	When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	A theoretical justification can be found in Appendix \ref{app_covariate}.
+	A theoretical justification can be found in Appendix \ref{app_proof_31}.
 \end{example}
@@
 The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
-The details can be found in Appendix \ref{app_proof_31}.
+The details can be found in Appendix \ref{app_proof_data}.
 

### 2020-05-28 writeup/transfer.tex
sec 4 wip

@@
 
-Based on Theorem \ref{thm_main_informal}, we provide precise interpretations of many empirical phenomena of multi-task learning.
-We show that negative transfer may result from three factors, including model dissimilarity, data size and covariate shift.
-Furthermore, we describe two benefits of multi-task learning, including de-noising via less noisy source labels and improving labeled data efficiency.
-
-%After describing this technical result, we provide theoretical insights over when multi-task learning performs better than single-task learning.
-%Our analysis reveals three contributing causes of negative transfer, including task model \textit{dissimilarity}, \textit{unbalanced} data size, and \textit{covariate shift}, which we describe in detail for the rest of the section.
+Based on Theorem \ref{thm_main_informal}, we provide precise interpretations of many empirical phenomena in multi-task learning.
+We explain three contributing causes of negative transfer, including model dissimilarity, large source data size and covariate shift.
+On the positive side, we describe two benefits of multi-task learning, including improving labeled data efficiency and de-noising via less noisy source labels.
 

### 2020-05-28 writeup/transfer.tex
sec 4.1

@@
 
-A folklore intuition since the seminal work of Caruana \cite{C97} is that task relatedness determines how well multi-task learning performs.
-We formalize the intuition using our setup and technical tools.
+It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
+As a warmup, we first describe an example that rigorously formalizes the belief using our setup.
 
-\textit{A simplified model.}
-	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
-For the noises, we assume that $\e_i$ has i.i.d.
-entries with mean zero and variances $\sigma_i^2$, $i=1,2$.
-	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
-	%The noise level for both tasks is equal to $\sigma > 0$.
-	We have $n_i = \rho_i \cdot p$ data points from each task, for $i = 1, 2$.
-	For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.
+\textit{The isotropic model.}
+	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
+	Recall that each task has data size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
+	And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denotes the covariates of the two tasks, respectively.
+	We assume that for the target task, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
+	For the source task, $\beta_1 $ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
+	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma_i^2$, for $i=1,2$.
+	\footnote{For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.}
 
 \textbf{Model dissimilarity.}
-For a simple example of two tasks, we show that whether $\hat{\beta}_t^{\MTL} \le \hat{\beta}_t^{\STL}$ is determined by $\norm{\beta_1 - \beta_2}^2$, the distance of the task models.
-We derive a sharp threshold when positive transfer transitions to negative transfer, as a function of model distance $\norm{\beta_1 - \beta_2}^2$, data size $n_1$ abd $n_2$ and the noise level $\sigma$.
-
-We illustrate the example with a simulation.
-We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
-We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
-Figure \ref{fig_model_shift} shows the result.
-Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
+We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
+We derive a sharp threshold when positive transfer transitions to negative transfer, as model dissimilarity increases.
+%Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
 Define the following function
@@
 \begin{proposition}\label{prop_dist_transition}
-	In the simplified model, assume that $\rho_1 > 40$ is a fixed constant.
+	In the isotropic model, assume that $\rho_1 > 40$ is a fixed constant.
 	Let $\sigma_1 = \sigma_2 = \sigma$.
-	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
+	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between model dissimilarity and $\Phi(\rho_1, \rho_2)$:
 	\begin{itemize}
-		\item If ${d^2} < \frac{1}{2}\cdot \frac {\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${d^2} \ge 2\cdot\frac {\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If ${p d^2} < \frac{1}{2}  {\sigma^2}  \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If ${p d^2} \ge 2 {\sigma^2} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\end{itemize}
@@
 
-We remark that the constants $1/2$ and $2$ in the statement above are chosen for the simplicity of presentation.
-In general we can close the gap between the two constants by increasing $\rho_1$.
-While the statement of Theorem \ref{thm_main_informal} only applies to the asymptotic regime of $p$ going to infinity, Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift} when $p = 200$.
+Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
+We remark that the constants $1/2$ and $2$ in the statement above are chosen for ease of presentation.
+In general we can close their gap by increasing $\rho_1$.
+
+\todo{} We illustrate the example with a simulation.
+We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
+We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
+Figure \ref{fig_model_shift} shows the result.
+We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
 %in this proposition (and the following ones) can be replaced with $(1+c_1^{-1/2})^{-4}$ and $(1-c_1^{-1/2})^{-4}$. In particular, these bounds becomes tighter as $c_1$ increases.
@@
 		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
-		\caption{Task model dissimilarity}
+		\caption{Model dissimilarity}
 		\label{fig_model_shift}
@@
 	\caption{Three contributing causes of negative transfer:
-	(a) As the task model dissimilarity increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
-	(b) As source task data size increases, we observe a positive to negative transfer as the source task data size increases (Proposition \ref{prop_data_size}).
-	(c) As covariate shift becomes more significant, test performance gets worse (Proposition \ref{prop_covariate}).}
+	(a) As model dissimilarity increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
+	(b) As source task data size increases, we observe a transition positive to negative transfer (Proposition \ref{prop_data_size}).
+	(c) As covariate shift becomes more severe, test performance gets worse (Proposition \ref{prop_covariate}).}
 	\label{fig_model_shift_phasetrans}
@@
 \textbf{Data size.}
-In classical Rademacher or VC based theory of multi-task learning, adding more labeled data improves the generalization performance of a model.
-On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-Using the simplified model, we analyze the effect of varying the source task data size.
+In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
+More generally, such results are still applicable when all task data are being added simultaneously.
+On the other hand, for many applications of multi-task learning, the data sources are usually heterogeneous.
+For such settings, we have observed that adding more labeled data from one task does not always help.
+%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
+Using the isotropic model, we consider what happens if we vary the source task data size.
 

### 2020-05-28 writeup/transfer.tex
sec 4

@@
 \begin{proposition}\label{prop_data_size}
-	In the simplified model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants.
+	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants.
 	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
 	\begin{itemize}
-\item If $d^2 \le \frac{\sigma^2}{2p(\rho_2-1)}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-
-\item If $d^2 > \frac{2\sigma^2}{p (\rho_2 - 1)}$, then we have the following transition depending on $\rho_1$:
+		\item[a)] If $pd^2 \le \frac{1}{2}\cdot \frac{\sigma^2}{\rho_2-1}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ for any $\rho_1 > 40$.
+		\item[b)] If $pd^2 > 2\cdot\frac{\sigma^2}{\rho_2 - 1}$, then we have the following transition depending on $\rho_1$:
 		\begin{itemize}
-			\item If $\rho_1 < \frac{(\rho_2-2)\sigma^2}{(1 + {\rho_1}^{-0.5})^4(\rho_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-			\item If $\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+			\item If $\rho_1 \cdot p < \frac{(\rho_2-2)\sigma^2}{(1 + {\rho_1}^{-0.5})^4(\rho_2 - 1) d^2 - \sigma^2 / p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+			\item If $\rho_1 \cdot p > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) d^2 - \sigma^2 / p}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 		\end{itemize}
@@
 \end{proposition}
-
-The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}.
-We compare the model shift bias and the amount of reduced variance of $\hat{\beta}_t^{\MTL}$.
-An intuitive interpretation of Proposition \ref{prop_data_size} is that:
-i) If the two task models are sufficiently similar (as specified under the first bullet), adding the source task always provides positive transfer;
-ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.
-We leave the proof of Proposition \ref{prop_data_size} to Appendix \ref{app_proof_31}.
+The intuition behind Proposition \ref{prop_data_size} is as follows.
+a) If $\norm{\beta_1 - \beta_2}^2 \approx pd^2$ is sufficiently small, then adding any amount of labeled data from the source task always provides positive transfer;
+ii) Otherwise, as source data size increases, we observe a transition from positive to negative transfer.
+The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}, and can be found in Appendix \ref{app_proof_31}.
 
 \textbf{Covariate shift.}
-So far we have considered settings where $\Sigma_1 = \Sigma_2$.
-This setting is relevant for multi-class image classification settings, where different tasks share the same input features.
-In general, the covariance matrices of the two tasks may be different, e.g. in text classification.
-In this part, we use our tools to provide a case study on the effect of applying multi-task learning for two tasks when $\Sigma_1 \neq \Sigma_2$.
+So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+In general, the covariance matrices of the two tasks may be different such as in text classification.
+In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
 
-For this setting, covariate shift is captured by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
+We measure covariate shift by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
 We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
 Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-Our result shows that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
+We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
 On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
 
-	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, we assume an upper bound on the scale of $M$.
-	Consider the following family of matrices
+	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
 	\begin{align*}
@@
 	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
-	For the task models, we assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ has i.i.d. entries with mean $0$ and variance $d^2$.
-	The following proposition shows that when $n_1$ is large enough compared to $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized approximately within the family of $\cS_{\mu}$ when $M = \mu\id$.
+	Similar to the isotropic model, we assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1$ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
+	The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
 
 \begin{proposition}\label{prop_covariate}
-	In the simplified model, assume that $\rho_1 > 3$ and $\rho_2>3$,
-and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$. %As a parameter of $M \in \cS_{\mu}$,
-The test error $\te(\hat{\beta}_t^{\MTL})$, as a function of $M\in \cS_{\mu}$, is minimized at the identity matrix $\mu\id$ approximately by
-$1+ \bigo{\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}}$.
-%\be\label{formular_covariate0} (\te(\hat{\beta}_t^{\MTL}))(\mu \id) \le \left[1+ C\left(\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}\right)\right]\cdot\min_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M) ,\ee
-%where the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $C_1$, but otherwise does not depend on $c_1$ and $c_2$.
-	%is minimized when $M = \mu\id$.
+	In the setting described above, assume that $\rho_1 > 3$ and $\rho_2>3$,
+and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$.
+	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
+	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}}} \min_{M\in\cS_{\mu}} g(M). \]
 \end{proposition}
-Proposition \ref{prop_covariate} shows that when $n_1\gg n_2$, $te(\hat{\beta}_t^{\MTL})$ is minimized when $\Sigma_1$ and $\Sigma_2$ are proportional to each other.
-In other words, there is no covariate shift between the source task data and target task data.
-This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
+Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
+%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
 
+\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
 \begin{example}\label{ex_complement}
-	Within the setting of Example \ref{ex_cov_family}, we compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+	In the setting of Proposition \ref{prop_covariate}, we compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
 	For simplicity, we assume that $d = 0$.
@@
 
-\subsection{Implications on the Benefits of Multi-task Learning}
+\subsection{Implications on the Benefits of Multi-task Learning}\label{sec_benefit}
 

### 2020-05-28 writeup/transfer.tex
sec 4

@@
 Based on Theorem \ref{thm_main_informal}, we provide precise interpretations of many empirical phenomena in multi-task learning.
-We explain three contributing causes of negative transfer, including model dissimilarity, large source data size and covariate shift.
-On the positive side, we describe two benefits of multi-task learning, including improving labeled data efficiency and de-noising via less noisy source labels.
+In Section \ref{sec_similarity}, we explain three contributing causes of negative transfer, including model dissimilarity, large source data size and covariate shift.
+In Section \ref{sec_benefit}, we describe two implications for positive transfer, including labeled data efficiency and de-noising.
 
@@
 It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-As a warmup, we first describe an example that rigorously formalizes the belief using our setup.
+As a warmup, we first describe an example that rigorously formalizes the connection using our setup.
 
@@
 
-\subsection{Implications on the Benefits of Multi-task Learning}\label{sec_benefit}
+\subsection{Implications for Positive Transfer}\label{sec_benefit}
 
-\textbf{De-noising by Transferring from a Source Task}
+On the positive side, we describe two implications for positive transfer, assuming that $\norm{\beta_1 - \beta_2}^2$ is small in the isotropic model.
+
+\textbf{Labeled data efficiency.}
+We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
+This is formalized by a metric called the data efficiency ratio as follows.
+
+Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the same performance.
+%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
+For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(\alpha)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
+The data efficiency ratio is defined as
+\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~
+		\te_1(\hat{\beta}_1^{\MTL}(\alpha)) + \te_2(\hat{\beta}_2^{\MTL}(\alpha))
+		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
+We quantify the data efficiency ratio of the isotropic model as follows.
+
+\begin{proposition}\label{prop_data_efficiency}
+	In the isotropic model, assume that $\rho_1$ and $\rho_2$, $pd^2 < {8\sigma^2} /{(3 \rho)}$.
+	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
+\end{proposition}
+The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
+
+\textbf{Labeled data de-noising.}
 We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
 Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-We derive a sharp transition from positive to negative transfer as a parameter of $\sigma_1^2$.
+We extend Proposition \ref{prop_dist_transition} as follows.
 
 \begin{proposition}\label{prop_var_transition}
-	In the simplified model with $d$ being fixed but $\sigma_1$ varies, assume that $\rho_1 > 50$ is a fixed constant and $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$.
+	In the isotropic model, assume that $\rho_1 > 40$ and $pd^2 < \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
 	We derive the following transition as a parameter of $\sigma_1^2$:
 	\begin{itemize}
-		\item If $\sigma_1^2 \le -\frac32 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 \le -2 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
 		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
@@
 The details can be found in Appendix \ref{app_proof_data}.
-
-\textbf{Improving Labeled Data Efficiency}
-We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
-This is formalized by a metric called the data efficiency ratio as follows.
-Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all the tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the performance nearly the same.
-More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-If we only use $\alpha n_i$ datapoints from every task to train the multi-task learning estimator $\hat{\beta}(\alpha)$, then $\alpha \in (0, 1)$ will be the smallest number such that
-\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~ \te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))\le \te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL}). \]
-We quantify the data efficiency ratio of $\hat{\beta}_t^{\MTL}$ for the simplified model as follows.
-
-\begin{proposition}\label{prop_data_efficiency}
-	In the simplified model, assume that $\rho_1 = \rho_2 = \rho \ge 200$ and $d^2 < {8\sigma^2} /{(3p \rho)}$.
-	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
-\end{proposition}
-Note that we have stated the result assuming that $\rho_1 = \rho_2$.
-Similar results can also be obtained when they are different.
-We omit the details.
-The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.

### 2020-05-28 writeup/proof_examples.tex
sec 4
prop 4.2 pf

@@
 %	\end{align*}
-With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
+Note that 
+ \be\label{var-beta}\te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta .\ee
+Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.
+
+\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
 \be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
 	we have that $\delta_{\vari} > \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
-	\[   d^2  < \frac{\sigma^2}{p}\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1(\rho_1 + \rho_2) (\rho_2 - 1)} \cdot \left(\bigbrace{1 + \sqrt{\frac 1 {\rho_1}}}^{-4} - \oo(1)\right), \]
+	\[   pd^2  <  \sigma^2 \Phi(\rho_1, \rho_2)\cdot \left(\bigbrace{1 + \sqrt{\frac 1 {\rho_1}}}^{-4} - \oo(1)\right), \]
 Plugging into $\rho_1>40$, we obtain the first statement of Proposition \ref{prop_dist_transition}.
 
-On the other hand, if
+\noindent{\bf Negative transfer.} On the other hand, if
 \be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
 	we have that $\delta_{\vari} < \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
-	\[   d^2  > \frac{\sigma^2}{p}\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1(\rho_1 + \rho_2) (\rho_2 - 1)} \cdot \left(\bigbrace{1 - \sqrt{\frac 1 {\rho_1}}}^{-4} +\oo(1)\right), \]
+	\[  p d^2  >  \sigma^2 \Phi(\rho_1, \rho_2) \cdot \left(\bigbrace{1 - \sqrt{\frac 1 {\rho_1}}}^{-4} +\oo(1)\right), \]
 Plugging into $\rho_1>40$, we obtain the second statement of Proposition \ref{prop_dist_transition}.
@@
 \begin{proof}[Proof of Proposition \ref{prop_data_size}]
-Recall that under the setting of Example \ref{ex_basic}, \eqref{Deltavar} and \eqref{Deltabeta} hold.  Then we get that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
-\be\label{pos1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}};\ee
-otherwise if
-\be\label{neg1}\left(pd^2 \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} + \bigo{p^{1/2+\e}d^2} \right)\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 >  \sigma^2 \bigbrace{1 + \bigo{p^{-1/2 + \varepsilon}}},\ee
-then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.
+Following the above proof of Proposition \ref{prop_dist_transition}, we get from \eqref{upper101} that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
+\be\label{pos1}
+pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
+and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ whp if
+\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
+%then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.
 
-Now we prove the first statement of Proposition \ref{prop_data_size}. Notice that the function
-$$ \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} =(c_2-1) \left(1 +\frac{c_2-2}{c_1}+\frac{1}{c_1(c_1+c_2)}\right)^{-1} $$
-is strictly increasing with respect to $c_1$ as long as $c_2\ge 3$. In particular, by taking $c_1\to \infty$, we get the bound:
-$$\frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 <  (c_2-1) \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.$$
- Hence we conclude that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp as long as 
- $$pd^2 +\oo(1) \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^{-4}\frac{\sigma^2}{c_2-1} .$$ 
- This gives the first statement by taking $c_1 > a$.
+For the first statement of Proposition \ref{prop_data_size}, we notice that the function
+$$\frac1{ \Phi(\rho_1, \rho_2)}=\frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}=(\rho_2-1) \left(1 +\frac{\rho_2-2}{\rho_1}+\frac{1}{\rho_1(\rho_1+\rho_2)}\right)^{-1} $$
+is strictly increasing with respect to $\rho_1$ as long as $\rho_2> 2$. In particular, by taking $\rho_1\to \infty$, we get the bound:
+$$\frac{\rho_1(\rho_1+\rho_2)(\rho_2-1)}{(\rho_1+\rho_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  (\rho_2-1) \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4.$$
+Hence as long as we take 
+ $$pd^2  \le \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
+ then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds whp. Plugging into $\rho_1>50$, we obtain the first statement.
 
-The second statement can be proved in a similar way. Suppose $c_1 > a$ and 
-$pd^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{c_2-1}$. If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, we have
-\begin{align*}
- & pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4  \\
- &>  \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \left( 1-\frac{1}{(c_1+c_2-2)^2}\right)\cdot \frac{ pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  >\sigma^2\cdot (1+\oo(1)) , 
- \end{align*}
- where in the first step we used that 
- $$ \frac{(c_1+c_2)(c_1+c_2-2)}{(c_1+c_2-1)^2}   > 1-\frac{1}{(c_1+c_2-2)^2}.$$
-This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds.
-On the other hand, if $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then we have
- \begin{align*}
- pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 \cdot \frac{pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  < \sigma^2\cdot (1-\oo(1)).
- \end{align*}
- This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
+The two bounds in the second statement follows directly from \eqref{pos1} and \eqref{neg1}. We will use the following trivial inequalities 
+\be\label{trivialphi}
+\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2} \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
+\ee
+
+%This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. 
+%
+%If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, we have
+%Suppose that
+%$$pd^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{c_2-1}.$$
+
+\noindent{\bf Positive transfer.} With \eqref{trivialphi}, we see that \eqref{pos1} is implied by the following inequality
+\begin{align}\label{pos1solv}
+ & pd^2 \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <\sigma^2\cdot (1-\oo(1)) .
+ \end{align}
+ then we can solve \eqref{pos1solv} to get
+ $$\rho_1 < \frac{(\rho_2-2) \sigma^2}{pd^2 \cdot (1+\rho_1^{-1/2})^4 (\rho_2 - 1)\cdot (1+\oo(1))  - \sigma^2}  .$$
+ %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
+ Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.
+
+%On the other hand, if $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then we have 
+% \begin{align*}
+% pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 \cdot \frac{pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  < \sigma^2\cdot (1-\oo(1)).
+% \end{align*}
+% This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
+
+ \noindent{\bf Negative transfer.} 
+With \eqref{trivialphi}, we see that \eqref{neg1} is implied by the following inequality
+\begin{align}\label{neg1solv}
+ & pd^2 \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >\sigma^2\cdot (1+\oo(1)) .
+ \end{align}
+If the following relation holds,
+$$pd^2 \cdot (1-\rho_1^{-1/2})^4(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) >  \sigma^2\cdot (1+\oo(1))  , $$
+ then we can solve \eqref{neg1solv} to get
+ $$\rho_1 > \frac{(\rho_2-2) \sigma^2}{pd^2 \cdot (1-\rho_1^{-1/2})^4(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1)\cdot (1-\oo(1))  - \sigma^2}  ,$$
+ %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
+ Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the lower bound for $\rho_1$ in order for negative transfer to hold.
  \end{proof}
 
+ Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix if there are sufficiently many source datas.
+
 \begin{proof}[Proof of Proposition \ref{prop_covariate}]
-Let 
+........ Let 
 $$M_0:=\argmin_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M).$$ 

### 2020-05-28 writeup/intro.tex

@@
 When the information sources are heterogeneous, negative transfer -- where multi-task learning performs worse than single-task learning -- has often been observed \cite{AP16,BS17}.
-While numerous studies have sought to alleviate negative transfer when it occurs \cite{YKGLHF20}, a rigorous understanding to the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
+While numerous studies have sought to alleviate negative transfer when it occurs \cite{ZY17}, a rigorous understanding to the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
@@
 entries with mean zero and unit variance, and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-The label of $x$ is given by $y_i = x^{\top}\beta_i + \varepsilon$, where $\beta_i\in\real^p$ denotes the ground truth parameters for task $i$ and $\varepsilon$ denotes random noise with mean zero and variance $\sigma^2$.
-Importantly, we assume that the training data size of the target task $t$ is a small constant $\rho_t > 1$ times $p$ to capture the need for more labeled data.
+Let $n_i$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$, for every $1\le i\le t$.
+The label of task $i$ is given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes the ground truth parameters for task $i$ and $\varepsilon_i$ denotes i.i.d.
+random noise with mean zero and variance $\sigma^2$.
+Without loss of generality, let the $t$-th task denote the target task.
+We assume that the data size of task $t$ is a small constant $\rho_t > 1$ times $p$ to capture the need for more labeled data.
 %We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
@@
 
-We combine all the available training data using a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
-%    \paragraph{Different covariates:}
+We combine all the labeled data using a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
 This corresponds to minimizing the following objective.
@@
 
-To quantify the tradeoff more precisely, we develop a new technical result on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for two random matrices $X_1$ and $X_2$ when their dimensions $p$ are large and data sizes are fixed constants times $p$.
-Using the result, we provide a sharp bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for the setting of two tasks with general covariance matrices.
+To quantify the tradeoff more precisely, we develop a new technical result on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for the setting of two tasks with general covariance matrices.
+Using the result, we provide a sharp bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
 When there are more than two tasks, we show a similar result if they all have the same covariates.

### 2020-05-28 writeup/proofs_sec3.tex

@@
 	\end{align}
-with high probability, where $a_1, a_2$ are solutions to the following deterministic equations:
+with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
 	\begin{align*}
@@
 \end{lemma}
-The proof of Lemma \ref{lem_cov_shift} is a main focus of Section \ref{sec_maintools}.
+
+Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}$.
+
+\begin{lemma}\label{lem_cov_derivative}
+In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any unit vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
+\begin{equation}\label{lem_cov_derv_eq}
+\begin{split}
+&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
+&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} \Sigma_2^{-1/2} \beta +\OO(n^{-1/2+\e}),
+\end{split}
+\end{equation}
+with high probability, where $a_{3}$ and $a_4$ satisfy the following system of linear equations: 
+\begin{gather}
+		\left(\rho_2  a_2^{-2}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
+		= b_0, \quad \left(\rho_1 a_1^{-2} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .  
+%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
+%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
+	\end{gather}
+Here $b_0$, $b_1$ and $b_2$ are defined as
+$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
+\end{lemma}
+%We will give the proof of this lemma in Section \ref{sec_maintools}.
+
+The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}.
 We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our result \eqref{lem_cov_shift_eq} also gives an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.
+\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.

### 2020-05-29 writeup/experiments.tex
taskonomy results

@@
 
-\subsection{Validating Theoretical Observations}
+\subsection{Validating Theoretical Implications}
+
+\textbf{Causes of negative transfer.}
 
@@
 
-\textbf{Causes of negative transfer.}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{c c c c c}
+		\toprule
+		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
+		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
+		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+		& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
+		\midrule
+		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
+		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
+		% {\bf CNN}  & 76\% & - & 32\% & -\\
+		\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Taskonomy experiment.}
+	\label{tab:taskonomy}
+	\end{table}
 

### 2020-05-29 writeup/transfer.tex
fig 1
sec 4

@@
 
-\textbf{Model dissimilarity.}
+\textbf{Cause 1.}
 We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
@@
 
-\begin{proposition}\label{prop_dist_transition}
+\begin{proposition}[Model dissimilarity]\label{prop_dist_transition}
 	In the isotropic model, assume that $\rho_1 > 40$ is a fixed constant.
@@
 	(b) As source task data size increases, we observe a transition positive to negative transfer (Proposition \ref{prop_data_size}).
-	(c) As covariate shift becomes more severe, test performance gets worse (Proposition \ref{prop_covariate}).}
+	(c) As covariate shift becomes more severe (measured by increasing $\lambda$), test performance gets worse (Proposition \ref{prop_covariate}).}
 	\label{fig_model_shift_phasetrans}
@@
 
-\textbf{Data size.}
+\textbf{Cause 2.}
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
@@
 
-\begin{proposition}\label{prop_data_size}
+\begin{proposition}[Source data size]\label{prop_data_size}
 	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants.
@@
 
-\textbf{Covariate shift.}
+\textbf{Cause 3.}
 So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
@@
 
-\begin{proposition}\label{prop_covariate}
+\begin{proposition}[Covariate shift]\label{prop_covariate}
 	In the setting described above, assume that $\rho_1 > 3$ and $\rho_2>3$,
@@
 
-\textbf{Labeled data efficiency.}
+\textbf{Implication 1.}
 We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
@@
 
-\begin{proposition}\label{prop_data_efficiency}
+\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
 	In the isotropic model, assume that $\rho_1$ and $\rho_2$, $pd^2 < {8\sigma^2} /{(3 \rho)}$.
@@
 
-\textbf{Labeled data de-noising.}
+\textbf{Implication 2.}
 We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
@@
 
-\begin{proposition}\label{prop_var_transition}
+\begin{proposition}[Labeled data de-noising]\label{prop_var_transition}
 	In the isotropic model, assume that $\rho_1 > 40$ and $pd^2 < \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.

### 2020-05-29 writeup/proof_main.tex
add

@@
 Finally, we introduce the error term
-$$\delta:=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,$$
+\be\label{eq_deltaextra}\delta:=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,\ee
 where we recall that $\kappa(\hat M)$ is the condition number of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.
@@
 	where
-	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
+	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
 		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} }  \\
 		\Delta_{\beta} &\define (\beta_s - \hat{v}\beta_t)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_s - \hat{v}\beta_t). 
-	\end{align*}
+	\end{align}
 \end{theorem}
@@
 
-\begin{lemma}\label{lem_cov_derivative}
-	In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-&\wh w^{2}(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (\hat{w}X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1 (\beta_s - {w}\beta_t)}^2 \\
-&= (\beta_s - {w}\beta_t)^{\top} \Sigma_1^{1/2} {M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top} \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t) +\OO(n^{-1/2+\e}),
-\end{split}
-\end{equation}
-	for any constant $\epsilon>0$. %, where $a_{3,4}$ are found using equations in  \eqref{m35reduced}
-\end{lemma}
-We will give the proof of this lemma in Section \ref{sec_maintools}.
-
 \paragraph{Part III: An $\e$-net argument.}

### 2020-05-29 writeup/transfer.tex
add

--- 2020-05-28 writeup/transfer.tex
@@
 	\end{align*}
-	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
-	Similar to the isotropic model, we assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1$ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
+	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$. We first assume that there is no model bias. 
+	Similar to the isotropic model, we assume that $\beta_1=\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
 	The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
@@
 \begin{proposition}\label{prop_covariate}
-	In the setting described above, assume that $\rho_1 > 3$ and $\rho_2>3$,
-and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$.
+	In the setting described above, assume that $\rho_1 > 1$ and $\rho_2>1$. 
+	%Moreover, up to some rescaling, we can assume that $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$.
 	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
-	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}}} \min_{M\in\cS_{\mu}} g(M). \]
+	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
 \end{proposition}
@@
 
-	In Figure \ref{fig_covariate}, we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
+	In Figure \ref{fig_model_shift_phasetrans} (c), we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
 	Second, we observe the following two phases as we increase $n_1 / p$.

### 2020-05-29 writeup/transfer.tex

--- 2020-05-29 writeup/transfer.tex
@@
 \begin{proposition}[Covariate shift]\label{prop_covariate}
-	In the setting described above, assume that $\rho_1 > 3$ and $\rho_2>3$,
-and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$.
+	In the setting described above, assume that $\rho_1 > 1$ and $\rho_2>1$.
 	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
-	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}}} \min_{M\in\cS_{\mu}} g(M). \]
+	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
 \end{proposition}

### 2020-05-29 writeup/proof_examples.tex

@@
 \be\label{choiceofpara}
-pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c}\kappa^2  \le d^2 \le p^c \kappa^2.
+pd^2 \sim \sigma^2 \sim 1,\quad p^{c}\kappa^2  \le \sigma^2 \le p^{1-c} \kappa^2.
 \ee
@@
 
- Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix if there are sufficiently many source datas.
+ Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is no model bias and enough source data.
 
 \begin{proof}[Proof of Proposition \ref{prop_covariate}]
-........ Let 
-$$M_0:=\argmin_{M\in \cal S_{\mu}}(\te(\hat{\beta}_t^{\MTL}))(M).$$ 
-We now calculate $(\te(\hat{\beta}_t^{\MTL}))(M_0)$. In this case, as in Lemma \ref{lem_hat_v} we also have that 
-\be\label{hatvM}|\hat v-1|=\OO(p^{-1}) \ee 
-in the setting Proposition \ref{prop_covariate}.
+Let 
+$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
+We now calculate $g(M_0)$.
+With the same arguments as in Lemma \ref{lem_hat_v} we can show that \eqref{hatv_add1} holds.
+Moreover, if the parameters are chosen such that $p^{c}\kappa^2  \le \sigma^2 \le p^{1-c} \kappa^2$ (recall \eqref{choiceofpara}), we can simplify
+\be \nonumber
+\begin{split}
+g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
+\end{split}
+\ee
+with high probability for any constant $\e>0$.
 In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $\lambda(M)\in [\mu_{\min},\mu_{\max}]$.
@@
 
-Now using \eqref{hatvM}, Lemma \ref{lem_cov_shift} and Lemma \ref{prop_model_shift_tight}, we get that whp,
-\begin{align*}
-(\te(\hat{\beta}_t^{\MTL}))(M_0)= \frac{\sigma^2}{c_1+c_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0 + a_2}\right)  + \Delta_\beta(M_0),
-\end{align*}
-where  $ \Delta_{\beta}(M_0)$ satisfies 
-\be \nonumber
-\begin{split}
-&\left| \Delta_{\beta}(M_0) - \frac{d^2\cdot c_1^2}{(c_1 + c_2)^2} \tr\left[{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\right]\right| \\
-&\le \left(\bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4-1\right)\left( \frac{c_1\mu_{\max}}{(\sqrt{c_1}-1)^2 \mu_{\min} + (\sqrt{c_2}-1)^2}\right)^2 \cdot d^2\tr\left(\Sigma_1\right). 
-\end{split}
+Now using Lemma \ref{lem_cov_shift}, we can obtain that with high probability,
+\begin{align}\label{gvar_extra}
+g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
+\end{align}
+From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
+\be\label{est_a12extra}
+\frac{\rho_1-1}{\rho_1+\rho_2} < a_1(M)<  \frac{\rho_1+\rho_2-1}{\rho_1+\rho_2},\quad a_2(M) < \frac{\rho_2}{\rho_1+\rho_2}.
 \ee
-From equation \eqref{eq_a2}, we get
-$$a_1\ge \frac{c_1-1}{c_1+c_2},\quad a_2\le \frac{c_2}{c_1+c_2}.$$
-Then solving equations \eqref{eq_a3} and \eqref{eq_a4}, we get that
-\begin{align*}
-0\le a_3&= \frac{ \frac{1}{n_2}\sum_{i=1}^p \frac{a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) +\left( \frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) } {\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} \\
-&\le \frac{c_2^{-1}}{1-c_1^{-1}-c_2^{-1}}
-\end{align*}
-and
-\begin{align*}
-0\le a_4&= \frac{\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2}{  (a_2 + \lambda_i^2a_1)^2  }}{\left(1- \frac1{n_2}\sum_{i=1}^p \frac{a_2^2}{ (a_2 + \lambda_i^2a_1)^2  }\right) \left(1 - \frac{1}{n_1} \sum_{i=1}^p \frac{\lambda_i^4 a_1^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right) - \left(\frac{1}{n_2}\sum_{i=1}^p \frac{  \lambda_i^2 a_2^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right) \left(\frac{1}{n_1}\sum_{i=1}^p \frac{\lambda_i^2 a_1^2 }{  (a_2 + \lambda_i^2a_1)^2  }\right)} \\
-&\le  \frac{c_1^{-1}\cdot \mu_{\min}^{-2}}{1-c_1^{-1}-c_2^{-1}},
-\end{align*}
-where we also used that 
-$$\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)^2 \le \sum_{i=1}^p \frac{\lambda_i^4 }{  (a_2 + \lambda_i^2a_1)^2  }\cdot \sum_{i=1}^p \frac{1}{  (a_2 + \lambda_i^2a_1)^2  }$$
-by Cauchy-Schwarz inequality.
-
-Combining the above estimates, we get that 
+Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $\lambda(M_0^\top M_0)\ge \mu_{\min}^2$, we obtain that with high probability,
 \begin{align}\label{approximateteM}
-(\te(\hat{\beta}_t^{\MTL}))(M_0) =  \te(M_0) + \cal E,
+\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}\wt g(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le \wt g(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
 \end{align}
 where
-$$\te(M_0):=\frac{\sigma^2}{c_1+c_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0}\right)  +\frac{d^2\cdot c_1^2}{(c_1 + c_2)^2} \tr\left(\frac{1 + a_3}{a_1^2 M_0^{\top}{M_0}} \right),$$
-and the error satisfies
-$$|\cal E|\le C\left( \frac{c_2}{c_1} +c_1^{-1/2}\right)\te(M_0),$$
-Here the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $\|\Sigma_1\|$, but otherwise does not depend on $c_1$ and $c_2$.
-
+$$\wt g(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
 %With these two bounds, we can easily conclude \eqref{approxteM}. 
@@
 %Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-
-Finally using AM-GM inequality, we observe that 
+By AM-GM inequality, we observe that 
 $$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i}$$
 is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
-$$ \te (M_0)\le \te(\mu \id).$$
-Together with \eqref{approximateteM}, we conclude \eqref{formular_covariate0}.
+\be\label{AMGM}\wt g(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
+
+On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we can obtain that with high probability,
+\begin{align}\label{gvar_extra2}
+\begin{split}
+g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
+&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
+\end{split}
+\end{align}
+Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
 %, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
@@
 
-\begin{proof}[Theoretical justification of Example \ref{ex_covariate}]
-In the setting of Example \ref{ex_covariate}, equations in \eqref{eq_a2} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{p}{n_1 + n_2},  \ \ a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{n_1}{n_1 + n_2}.
+%--------old arguments
+%With the same arguments as in Lemma \ref{lem_hat_v} we can show that \eqref{hatv_add1} holds, and under the choice of parameters \eqref{choiceofpara},
+%\be \nonumber
+%\begin{split}
+%g(M)&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1)(X_1^{\top}X_1 +X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)\right] \\ 
+%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  =: \delta_\beta(M)+ g_{\vari}(M),
+%\end{split}
+%\ee
+%with high probability for any constant $\e>0$.
+In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $\lambda(M)\in [\mu_{\min},\mu_{\max}]$.
+We omit the details here.
+%
+%
+%With Lemma \ref{lem_cov_shift}, we can obtain that with high probability,
+%\begin{align}\label{gvar_extra}
+%g_{\vari}(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0 + a_2}\right)  +\OO(p^{-1/2+\e}),
+%\end{align}
+%where $(a_1,a_2)$ satisfies \eqref{eq_a12extra}. On the other hand, by Theorem \ref{thm_model_shift} we can estimate $\delta_\beta$ as
+%\be \label{deltabeta_extra}
+%\begin{split}
+%&\left| \delta_{\beta}(M_0) - \frac{d^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \tr\left[\Sigma_1^{1/2}{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\Sigma_1^{1/2}\right]\right| \le \delta + \OO(p^{1-\e}d^2),
+%\end{split}
+%\ee
+%where $(a_3,a_4)$ satisfies \eqref{eq_a34extra} and $\delta$ is defined in \eqref{eq_deltaextra}.
+%
+%
+%Next we derive some estimates for $a_i$, $i=1,2,3,4$. From equation \eqref{eq_a12extra}, it is easy to see that
+%\be\label{est_a12extra}a_1\ge \frac{\rho_1-1}{\rho_1+\rho_2},\quad a_2\le \frac{\rho_2}{\rho_1+\rho_2}.\ee
+%Then solving \eqref{eq_a34extra}, we get that
+%\begin{align}
+%0\le a_3&= \frac{ b_0 (\rho_1a_1^{-2}-b_2) + b_1^2 }{  \left(\rho_2  a_2^{-2}-  b_0\right)\left(\rho_1 a_1^{-2} -  b_2  \right) - b_1^2} \le \frac{ b_0 \rho_1a_1^{-2}  }{  \rho_1\rho_2  a_1^{-2}a_2^{-2}-  b_0\rho_1 a_1^{-2} - b_2\rho_2  a_2^{-2}}\nonumber\\
+%&\le \frac{\rho_1}{\rho_1\rho_2-\rho_1 -\rho_2 },\label{est_a3extra}
+%\end{align}
+%and
+%\begin{align}
+%0\le a_4&= \frac{b_1\rho_2 a_2^{-2}}{\left(\rho_2  a_2^{-2}-  b_0\right)\left(\rho_1 a_1^{-2} -  b_2  \right) - b_1^2} \le  \frac{ b_1\rho_2 a_2^{-2} }{  \rho_1\rho_2  a_1^{-2}a_2^{-2}-  b_0\rho_1 a_1^{-2} - b_2\rho_2  a_2^{-2}} \nonumber\\
+%&\le  \frac{ \rho_2 (b_1a_1^{2}) }{  \rho_1\rho_2 -  \rho_1  - \rho_2 } \le \frac{\rho_2\cdot \mu_{\min}^{-2}}{\rho_1\rho_2-\rho_1-\rho_2}=\OO\left( \frac{1}{\rho_1}\right),\label{est_a4extra}
+%\end{align}
+%where in the above derivations we also used that $b_1^2\le b_0 b_2$ by Cauchy-Schwarz inequality, $b_0 a_2^2 < 1$, $b_2 a_1^2 < 1$, and $b_1 a_1^2 \le \mu_{\min}^{-2}$.
+%Inserting \eqref{est_a12extra} into \eqref{gvar_extra}, we obtain that with high probability,
+%\begin{align}\label{approximateteM}
+%\le g(M_0) \le  \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0}\right) \cdot \left(1 +\OO(p^{-\e})\right)
+%\end{align}
+%where
+%$$\wt g(M_0):=\frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0}\right)  +\frac{pd^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \cdot \frac1p\tr\left(\Sigma_1\frac{1 + a_3}{a_1^2 M_0^{\top}{M_0}} \right),$$
+%and the error satisfies
+%$$|\cal E|\le C\left( \frac{\rho_2}{\rho_1} +\rho_1^{-1/2} +\OO(p^{-\e})\right)\wt g(M_0).$$
+%Here the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $\|\Sigma_1\|$, but otherwise does not depend on $\rho_1$ and $\rho_2$. 
+%--------end old argument---------
+
+\begin{proof}[Theoretical justification of Example \ref{ex_complement}]
+We denote the test error as $\te_\lambda(\hat \beta_{t}^{\MTL})$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+Then equations in \eqref{eq_a12extra} become
+\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{\rho_1}{\rho_1 + \rho_2}.
 \ee
-It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. After solving these, we get the test error for the target task as follows.
+%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. 
+After solving these, with \eqref{gvar_extra} we get that whp,
 \be\label{testcomple}
-te(\lambda)=\frac{p}{2(n_1 + n_2)} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}}.\ee
+ \te_\lambda(\hat \beta_{t}^{\MTL})= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot g(\lambda) ,\quad g(\lambda): = \frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}.\ee
 
-First we notice that the curves in Figure \ref{fig_te_complement} all cross at the point $n_1=n_2$.
+%First we notice that the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
 In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
 Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
-$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
+%$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
 
@@
 On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-This phenomenon can be also explained using our theory. With \eqref{compleeq}, we can write
-$$te(\lambda)=\frac{\gamma}{2} \cdot \bigbrace{\frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}}.$$
+We now study the behavior of $g$ as $\lambda$ changes. 
+%This phenomenon can be also explained using our theory. 
+We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with \eqref{compleeq}, we can rewrite
+$$g(\lambda)= \frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}.$$
 We can compute that
 \begin{align*}
-te(\lambda) - te(1)&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\gamma}{2(1-\gamma)} (\lambda^2-1)^2 a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
+g(\lambda) - g(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
 \end{align*}
-If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}), and hence $te(\lambda)>te(1)$.
-Otherwise if $n_1< n_2$, we have $a_1< (1-\gamma)/2$, and hence $te(\lambda)< te(1)$.
+From this expressions, we observe the following behaviors.
+\begin{itemize}
+\item[(i)] If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}).
+Hence $g(\lambda)>g(1)$, which gives $\te_\lambda(\hat \beta_{t}^{\MTL})>\te_1(\hat \beta_{t}^{\MTL})$.
+
+\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $g(\lambda)< g(1)$, which gives $\te_\lambda(\hat \beta_{t}^{\MTL})<\te_1(\hat \beta_{t}^{\MTL})$.
+
+\item[(iii)] If $n_1=n_2$, we have $g(\lambda)=g(1)=2/(1-\gamma)$, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
+\end{itemize}
+These justify the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
 \end{proof}
+\todo{add a transition example}
 
@@
 
-\subsection{Proofs for Section \ref{sec_data_size}}\label{app_proof_data}
+\subsection{Proofs for Section \ref{sec_benefit}}\label{app_proof_data}
 
-With similar techniques, we then show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
+ We first prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio.
+
+\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
+Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
+Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(\al\rho_1,\al\rho_2)$.
+More precisely, we have
+	\begin{align*}
+		 a_1 = \frac{\rho_1(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,\quad
+		& a_2 = \frac{\rho_2(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,  \\
+		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}, \quad
+		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}. 
+	\end{align*}
+Moreover, we have that with high probability,
+	\be\label{reduceproof1}
+\begin{split}
+\te_i(\hat \beta(\al)) =  \frac{\sigma^2}{\al (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\beta}, \quad i=1,2.
+\end{split}
+\ee
+Here the model shift biases $\delta^{(i)}_{\beta}$ satisfy that  
+\be\nonumber %\label{Deltabeta} 
+\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_\beta^{(i)}}/{ \Delta_{\beta}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2,\ee	
+%In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
+%%and by symmetry it suffices to focus on one of tasks, say task 2. 
+%Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
+%\be\label{reduceproof1}
+%\begin{split}
+%\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
+%\end{split}
+%\ee
+%and
+%\be\label{reduceproof1}
+%\begin{split}
+%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
+%\end{split}
+%\ee
+where $ \Delta^{(i)}_{\beta}$ are defined as 
+\be \nonumber
+\Delta^{(i)}_{\beta} := pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,. 
+\ee
+On the other hand, using Lemma \ref{lem_minv}, we have whp,
+\be\label{reduceproof2} 
+\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
+\ee
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
+$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
+In fact, one can see that if $\al\le \al_l$, then we have 
+$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
+that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\beta}$.
+Next we try to get more precise bounds on $\al^*$.
+In the following discussions, we only consider $\al$ such that $\al(\rho_1+\rho_2) \ge \al_l (\rho_1+\rho_2) \ge \min(\rho_1,\rho_2)$.
+
+%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+
+\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
+\be\nonumber
+\begin{split}
+&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
+&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
+\end{split}
+\ee
+We rewrite the inequality as
+\be
+\begin{split}\label{solval1}
+  (1+\oo(1)) \cdot \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{\al \rho}}}^4\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho  - 1},
+\end{split}
+\ee
+where we abbreviated $\rho:=\rho_1+\rho_2$.
+
+In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
+Thus the following inequality implies \eqref{solval1}:
+\be\label{solval1add}
+\begin{split}
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+In particular, if 
+\be\nonumber
+\begin{split}
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+\end{split}
+\ee
+that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
+\begin{align*}
+\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
+& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+
+\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
+\be\label{solval2}
+\begin{split}
+&(1-\oo(1)) \cdot  \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{\al \rho}}}^4 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho - 1} .
+\end{split}
+\ee
+We then follow similar arguments as the above proof for the upper bound.
+
+In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
+Thus the following inequality implies \eqref{solval2}:
+\be\label{solval2add}
+\begin{split}
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+There are two cases: if 
+\be\nonumber
+\begin{split}
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
+\end{split}
+\ee
+then we have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
+\begin{align*}
+\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
+& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+This concludes the proof.
+\end{proof}
+
+Then we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
 
@@
 
-Then we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio.
-
-\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$. 
-%For this proof, we introduce the notations 
-%$$\al_{\pm}^{(1)}\equiv \al_{\pm}^{(1)}(\al) = \left ( 1- (\al\rho_1)^{-1/2}\right)^2,\quad \al_{\pm}^{(2)}\equiv \al_{\pm}^{(2)}(\al) = \left ( 1- (\al\rho_2)^{-1/2}\right)^2.$$
-In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
-%and by symmetry it suffices to focus on one of tasks, say task 2. 
-Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
-\be\label{reduceproof1}
-\begin{split}
-\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
-\end{split}
-\ee
-%and
-%\be\label{reduceproof1}
-%\begin{split}
-%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
-%\end{split}
-%\ee
-where $ \Delta^{(i)}_{\beta}$ satisfies 
-\be \nonumber
-\bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \le \Delta^{(i)}_{\beta} /  \left[ pd^2 \cdot \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}\cdot\left(1+ \bigo{p^{-1/2+\e}}\right)\right] \le \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4.
-\ee
-On the other hand, using Lemma \ref{lem_minv}, we have whp
-\be\label{reduceproof2} 
-\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \bigo{p^{-1/2 + \varepsilon}}\right),\quad i=1,2.
-\ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
-$$\al_l:=\frac1{\rho_1+\rho_2}\left[\frac{2(\rho_1-1)(\rho_2-1)}{\rho_1+\rho_2 -2}+1\right] \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
-In fact, one can see that if $\al\le \al_l$, then we have 
-$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
-that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \Delta^{(i)}_{\beta}$.
-Next we try to get more precise bounds on $\al^*$.
-In the following discussions, we only consider $\al$ such that $\al\rho \ge \al_l \rho \ge \min(\rho_1,\rho_2)$.
-
-%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
-
-\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
-\be\label{solval1}
-\begin{split}
-&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
-&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
-\end{split}
-\ee
-For the sum on the left-hand side, we can rewrite it as
-\begin{align*}
- pd^2 \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4,
-\end{align*}
-where $\rho:=\rho_1+\rho_2$.
-
-In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
-Thus the following inequality implies \eqref{solval1}:
-\be\label{solval1add}
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
-\end{split}
-\ee
-In particular, if 
-\be\nonumber
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
-\end{split}
-\ee
-that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
-\begin{align*}
-\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
-& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-
-\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
-\be\label{solval2}
-\begin{split}
-&(1-\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 - \sqrt{\frac{1}{\al \rho_i}}}^4 \\
-&\ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
-\end{split}
-\ee
-We then follow similar arguments as the above proof for the upper bound.
-
-In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
-Thus the following inequality implies \eqref{solval2}:
-\be\label{solval2add}
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
-\end{split}
-\ee
-There are two cases: if 
-\be\nonumber
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
-\end{split}
-\ee
-then we always have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
-\begin{align*}
-\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
-& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-This concludes the proof.
-\end{proof}
-
 %\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}

### 2020-05-29 writeup/proof_main.tex
minor

@@
 entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover suppose that $X_i$, $\beta_i$ and $\varepsilon_i$ are independent of each other.
 	Then with high probability, we have
@@
 \begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-	By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
+\todo{check!} By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
 	\begin{align*}

### 2020-05-29 writeup/proof_taskonomy.tex
minor

@@
-\section{Supplementary Materials for Section \ref{sec_taskonomy}}\label{app_proof_sec4}
+\subsection{Proof of the Transfer Learning Setting}\label{app_proof_sec4}
 
 \begin{proposition}\label{prop_taskonomy}
-Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, \cdots, t$, where $\e_i$ are random vectors with i.i.d.
+For $i=1,\cdot, t$, let $Y_i = X_i\beta_i + \varepsilon_i$ be independent data models, where $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are  random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover suppose that $X_i$, $\beta_i$ and $\varepsilon_i$ are independent of each other.
+%Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, \cdots, t$, where $\e_i$ are random vectors with i.i.d.
 entries of mean zero and variance $\sigma^2$.
@@
 \ee
-Suppose that all random variables have subexponential decay. Then we have with high probability,
+Then we have with high probability,
 \be\label{eq_taskonomy}
@@
 \ee
-where $B^{\star}_{t-1} := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t-1}]$, and
+where 
 \begin{align*}
-&\e_\beta:= \Sigma_k^{1/2}\left\{1 - B^\star_{t-1}\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1} (B^\star_{t-1})^\top\right\} \beta_t,\\
-&\e_{\vari}^{(1)}:=  \Sigma_k^{1/2}  B^\star_{t-1}\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1}\cal M_1 \left[(B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1\right]^{-1} (B^\star_{t-1})^\top \beta_t,\\
-&\e_{\vari}^{(2)}:= \cal M_2^{1/2}\left[(B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1\right]^{-1} (B^\star_{t-1})^\top \beta_t.
+\e_\beta &:= \Sigma_t^{1/2}\left\{1 - B^\star_{t-1}\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1} (B^\star_{t-1})^\top\right\} \beta_t,\\
+\e_{\vari}^{(1)}&:=  \Sigma_t^{1/2}  B^\star_{t-1}\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1}\cal M_1 \left[(B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1\right]^{-1} (B^\star_{t-1})^\top \beta_t,\\
+\e_{\vari}^{(2)}&:= \cal M_2^{1/2}\left[(B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1\right]^{-1} (B^\star_{t-1})^\top \beta_t.
 \end{align*}
-Here $\cal M_1$ and $\cal M_2$ are $k\times k$ diagonal matrices with $(\cal M_1)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right)$ and $(\cal M_2)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\Sigma_k\right)$.
+Here $\cal M_1$ and $\cal M_2$ are $(t-1)\times (t-1)$ diagonal matrices with $(\cal M_1)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right)$ and $(\cal M_2)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\Sigma_t\right)$.
 \end{proposition}
@@
 \begin{proof}[Proof of Proposition \ref{prop_taskonomy}]
-For each task $i$, $1\le i \le t-1$, we can find that  
+\todo{check!} For each task $i$, $1\le i \le t-1$, we can find that  
 $$\hat \beta_i = \beta_i + (X_i^\top X_i)^{-1}X_i^\top \e_i.$$

### 2020-05-29 writeup/proof_main.tex
Thm A.9

@@
 \begin{theorem}\label{thm_model_shift}
-For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
+For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
 entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover suppose that $X_i$, $\beta_i$ and $\varepsilon_i$ are independent of each other.
 	Then with high probability, we have

### 2020-05-29 writeup/proof_taskonomy.tex
Thm A.9

@@
 
-\begin{proposition}\label{prop_taskonomy}
-For $i=1,\cdot, t$, let $Y_i = X_i\beta_i + \varepsilon_i$ be independent data models, where $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are  random vectors with i.i.d.
+\begin{theorem}\label{prop_taskonomy}
+For $i=1,\cdots, t$, let $Y_i = X_i\beta_i + \varepsilon_i$ be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+Suppose $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are  random vectors with i.i.d.
 entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover suppose that $X_i$, $\beta_i$ and $\varepsilon_i$ are independent of each other.
-%Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, \cdots, t$, where $\e_i$ are random vectors with i.i.d.
-entries of mean zero and variance $\sigma^2$.
-Let $\rho_i>1$, $1\le i \le t$ be fixed constants.
-Assume that $\max_{1\le i \le t}\|\beta_i\|=\OO(1)$, $\sigma^2=\OO(1)$ and 
+Moreover, assume that $\max_{1\le i \le t}\|\beta_i\|=\OO(1)$, $\sigma^2=\OO(1)$ and
 \be\label{BTBassm}
@@
 \ee
-Then we have with high probability,
+Then for any constant $\e>0$, we have 
 \be\label{eq_taskonomy}
-\te(B W_t) =\|\e_\beta + \sigma^2 \e_{\vari}^{(1)}\|^2+ \sigma^2 \|\e_{\vari}^{(2)}\|^2 + \OO(p^{-1/2+\e}),
+\te(B W_t) =\|\e_\beta + \sigma^2 \e_{\vari}^{(1)}\|^2+ \sigma^2 \|\e_{\vari}^{(2)}\|^2 + \OO(p^{-1/2+\e})
 \ee
-where 
+with high probability, where 
 \begin{align*}
@@
 Here $\cal M_1$ and $\cal M_2$ are $(t-1)\times (t-1)$ diagonal matrices with $(\cal M_1)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right)$ and $(\cal M_2)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\Sigma_t\right)$.
-\end{proposition}
+\end{theorem}
 
-\begin{proof}[Proof of Proposition \ref{prop_taskonomy}]
-\todo{check!} For each task $i$, $1\le i \le t-1$, we can find that  
+\begin{proof}[Proof of Theorem \ref{prop_taskonomy}]
+ For each task $i$, $1\le i \le t-1$, we can find that  
 $$\hat \beta_i = \beta_i + (X_i^\top X_i)^{-1}X_i^\top \e_i.$$
-Then we calculate that
+We first calculate $B^\top B$, where recall that $B= [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+
+For the diagonal entries of $B^\top B$ we can calculate that
 \begin{align*}
-\|\hat\beta_i\|^2 &= \|\beta_i\|^2 + 2\beta_i^\top\cdot (X_i^\top X_i)^{-1}X_i^\top \e_i + \|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 .
+\|\hat\beta_i\|^2 &= \|\beta_i\|^2 + 2\beta_i^\top (X_i^\top X_i)^{-1}X_i^\top \e_i + \|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 .
 \end{align*}
-We can use concentration of random vector with independent entries, Lemma \ref{largedeviation}, to get that for any deterministic vector $\beta$ with $\|\beta\|=\OO(1)$,
+Using concentration of random vector with independent entries, Lemma \ref{largedeviation}, we get that for any deterministic vector $\beta$ with $\|\beta\|=\OO(1)$,
 \be\label{largebetae}
@@
 \ee
-with high probability for any constant $\e>0$, where we used Lemma \ref{SxxSyy} to bound 
+with high probability, where we used \eqref{eq_isometric} to bound 
 \be\label{opXiXi}\| (X_i^\top X_i)^{-1}\|\lesssim n_i^{-1} \quad \text{whp}. \ee
-Similarly, using Lemma \ref{largedeviation} we get with high probability,
+Similarly, using Lemma \ref{largedeviation} we get that with high probability,
 \be\label{largebetae2}
 \begin{split}
- \left|\|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 - \sigma^2 \tr\left( (X_i^\top X_i)^{-1} \right)\right|   \le p^{\e/2}\cdot \sigma^2 \left\{\tr\left[X_i (X_i^\top X_i)^{-2}X_i^\top\right]^2\right\}^{1/2} \\
- = p^{\e/2}\cdot \sigma^2 \left[ \tr (X_i^\top X_i)^{-2} \right]^{1/2} \le \sigma^2 p^{-1/2+\e},
+ \left|\|(X_i^\top X_i)^{-1}X_i^\top \e_i \|^2 - \sigma^2 \tr\left[ (X_i^\top X_i)^{-1} \right]\right|   \le p^{\e/2}\cdot \sigma^2 \tr^{1/2}\left\{\left[X_i (X_i^\top X_i)^{-2}X_i^\top\right]^2\right\} \\
+ = p^{\e/2}\cdot \sigma^2 \tr^{1/2} \left[  (X_i^\top X_i)^{-2} \right]\le \sigma^2 p^{-1/2+\e},
  \end{split}
@@
 \begin{split}
-\left| \e_j^\top X_j (X_j^\top X_j)^{-1}(X_i^\top X_i)^{-1}X_i^\top \e_i \right| &\le   p^{\e/2}\cdot \sigma^2 \left\{ \tr \left[(X_i^\top X_i)^{-1}(X_j^\top X_j)^{-1}\right] \right\}^{1/2} \\
-&\le \sigma^2 p^{-1/2+\e},  
+\left| \e_j^\top X_j (X_j^\top X_j)^{-1}(X_i^\top X_i)^{-1}X_i^\top \e_i \right| &\le   p^{\e/2}\cdot \sigma^2 \tr^{1/2} \left[(X_i^\top X_i)^{-1}(X_j^\top X_j)^{-1}\right]\\
+&\le \sigma^2 p^{-1/2+\e}.  
  \end{split}
@@
 \end{align}
+where we used Lemma \ref{lem_minv} in the second step, 
 and %where in the second step we used Lemma \ref{lem_minv}. Similarly, we have
@@
 \ee
-where $\OO(\sigma p^{-1/2+\e})$ means a $(t-1)\times (t-1)$ matrix, say $\cal E$, satisfying $\|\cal E\|\le C\sigma p^{-1/2+\e}$. Notice that by \eqref{BTBassm}, we also have with high probability,
-$$\|(B^\top B)^{-1}\| \lesssim \left\|\left[(B^\star_{t-1})^\top B^\star_{t-1}\right]^{-1}\right\|= \OO( 1).$$
-Moreover, using \eqref{largebetae} we get that
+where $\OO(\sigma p^{-1/2+\e})$ means a $(t-1)\times (t-1)$ matrix, say $\cal E$, satisfying $\|\cal E\|\le C\sigma p^{-1/2+\e}$. Notice that by \eqref{BTBassm}, we have that with high probability,
+$$\|(B^\top B)^{-1}\| = \OO( 1).$$
+Moreover, using \eqref{largebetae} we get 
 \be\label{BTBeta}
@@
 
-Now we are ready to calculate $\te(B W_t) $ using the above concentrations results. For the $t$-th target model, by optimizing over $W_t$ we get
-$$\hat W_t= (B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top Y_k =(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top (X_t \beta_t + \e_k) .$$
+Now we are ready to calculate $\te(B W_t) $ using the above estimates. For the $t$-th target model, by optimizing over $W_t$ we get
+$$\hat W_t= (B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top Y_k =(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top (X_t \beta_t + \e_t) .$$
 We then calculate that 
@@
 \begin{split}
-\exarg{\varepsilon_k} {\left\|\Sigma_k^{1/2}(B\hat W_t -\beta_t)\right\|^2} &= \left\| \Sigma_k^{1/2}\left[\id - B(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top X_t\right] \beta_t \right\|^2 \\
-&+\sigma^2\cdot \tr \left[\Sigma_k (B^\top X_t^\top X_t B)^{-1}\right]. \label{EBWk}
+\exarg{\varepsilon_t} {\left\|\Sigma_t^{1/2}(B\hat W_t -\beta_t)\right\|^2} &= \left\| \Sigma_t^{1/2}\left[\id - B(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top X_t\right] \beta_t \right\|^2 \\
+&+\sigma^2\cdot \tr \left[\Sigma_t (B^\top X_t^\top X_t B)^{-1}\right]. \label{EBWk}
 %\\&= \sigma^2\cdot \tr (B^\top X_t^\top X_t B)^{-1} + \left\|\beta_t\right\|^2 - 2 \beta_t^\top B(B^\top X_t^\top X_t B)^{-1} B^\top X_t^\top X_t \beta_t \nonumber\\
@@
 \ee
-By the concentration of random vector with independent entries or the restricted isometry property for $X_t B$, we have with high probability, 
-$$ B^\top X_t^\top X_t B = n_k  \left( B^\top B + \OO(p^{-1/2+\e})\right),\quad B^\top X_t^\top X_t \beta_t = n_k  \left( B^\top \beta_t  + \OO(p^{-1/2+\e})\right).$$
+Using the restricted isometry property for $X_t$ on the subspace spanned by the column vectors of $B$, we get that with high probability, 
+$$ B^\top X_t^\top X_t B = n_t  \left( B^\top B + \OO(p^{-1/2+\e})\right),\quad B^\top X_t^\top X_t \beta_t = n_t  \left( B^\top \beta_t  + \OO(p^{-1/2+\e})\right).$$
 Together with \eqref{opXiXi}, \eqref{BTB} and \eqref{BTBeta}, we can simplify the right-hand side of \eqref{EBWk} as
 \begin{align}
-\exarg{\varepsilon_k} {\left\|\Sigma_k^{1/2} (B\hat W_k -\beta_t)\right\|^2} =\left\|\Sigma_k^{1/2} \beta_t - \Sigma_k^{1/2} B(B^\top B)^{-1} B^\top \beta_t \right\|^2 + \OO(p^{-1/2+\e}) \nonumber\\
-=\left\|\Sigma_k^{1/2} \beta_t - \Sigma_k^{1/2} B\left[ (B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1)^{-1} \right](B_{t-1}^{\star})^\top \beta_t \right\|^2 + \OO(p^{-1/2+\e}). \label{EBWk2}
+&\exarg{\varepsilon_t} {\left\|\Sigma_t^{1/2} (B\hat W_t -\beta_t)\right\|^2} =\left\|\Sigma_t^{1/2} \beta_t - \Sigma_t^{1/2} B(B^\top B)^{-1} B^\top \beta_t \right\|^2 + \OO(p^{-1/2+\e}) \nonumber\\
+&=\left\|\Sigma_t^{1/2} \beta_t - \Sigma_t^{1/2} B\left[ (B^\star_{t-1})^\top B^\star_{t-1} + \sigma^2\cal M_1 \right]^{-1}(B_{t-1}^{\star})^\top \beta_t \right\|^2 + \OO(p^{-1/2+\e}). \label{EBWk2}
 \end{align}
-As in \eqref{BTB}, we can show by concentration that 
+As in \eqref{BTB}, we can show by concentration and Lemma \ref{lem_minv} that 
 \be\label{BTB2}
-B^\top \Sigma_k B=  (B_{t-1}^{\star})^\top \Sigma_k B_{t-1}^{\star}+\sigma^2 {\cal M}_2 +\OO(\sigma p^{-1/2+\e}).
+B^\top \Sigma_t B=  (B_{t-1}^{\star})^\top \Sigma_t B_{t-1}^{\star}+\sigma^2 {\cal M}_2 +\OO(\sigma p^{-1/2+\e}).
 \ee
-Together with \eqref{BTB} and \eqref{BTBeta}, we can further simplify \eqref{EBWk2} as
+Together with \eqref{BTB} and \eqref{BTBeta}, we can further take the expectation and simplify \eqref{EBWk2} as
 \begin{align*}
-&\exarg{\varepsilon_i, \forall 1\le i\le k} {\left\|\Sigma_k^{1/2} (B\hat W_k -\beta_t)\right\|^2}\\
-&= \OO(p^{-1/2+\e}) +\left\|\Sigma_k^{1/2} \beta_t\right\|^2 - 2\beta_t^\top \Sigma_k B_{t-1}^{\star} \left[(B_{t-1}^{\star})^\top B_{t-1}^{\star} +\sigma^2\cal M_1\right]^{-1} (B_{t-1}^{\star})^\top \beta_t  \\
-&+ \beta_t^\top B_{t-1}^\star \left[(B_{t-1}^{\star})^\top B_{t-1}^{\star} +\sigma^2\cal M_1\right]^{-1} \left((B_{t-1}^{\star})^\top \Sigma_k B_{t-1}^{\star}+\sigma^2 {\cal M}_2 \right) \left[(B_{t-1}^{\star})^\top B_{t-1}^{\star} +\sigma^2\cal M_1\right]^{-1}  (B_{t-1}^{\star})^\top \beta_t \\
-& =\|\e_\beta + \sigma^2 \e_{\vari}^{(1)}\|^2+ \sigma^2 \|\e_{\vari}^{(2)}\|^2 + \OO(p^{-1/2+\e}).
+&\exarg{\varepsilon_i, \forall 1\le i\le t} {\left\|\Sigma_t^{1/2} (B\hat W_t -\beta_t)\right\|^2}\\
+&= \left\|\Sigma_t^{1/2} \beta_t\right\|^2 - 2\beta_t^\top \Sigma_t B_{t-1}^{\star} \wt\beta_t + \wt\beta_t^\top \left((B_{t-1}^{\star})^\top \Sigma_t B_{t-1}^{\star}+\sigma^2 {\cal M}_2 \right) \wt\beta_t + \OO(p^{-1/2+\e}).
+%& =\|\e_\beta + \sigma^2 \e_{\vari}^{(1)}\|^2+ \sigma^2 \|\e_{\vari}^{(2)}\|^2 + \OO(p^{-1/2+\e}),
 \end{align*}
-This concludes the proof.
+where we abbreviated 
+$$\wt\beta_t:=\left[(B_{t-1}^{\star})^\top B_{t-1}^{\star} +\sigma^2\cal M_1\right]^{-1}  (B_{t-1}^{\star})^\top \beta_t .$$
+Finally, rearranging terms and performing some basic calculations we can conclude the proof.
 \end{proof}

### 2020-05-30 writeup/proof_main.tex
A.2

@@
 \begin{theorem}\label{thm_many_tasks}
-	Let $n = c \cdot p$.
-	Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $B^{\star}\Sigma B^{\star}$, where $U_r\in\real^{k\times r}$.
+Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star = [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
 	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
@@
 	\begin{itemize}
-		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} \ge \norm{\Sigma (B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} < \norm{\Sigma(B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\left(1 -\oo(1)- \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 $, then $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp.
+		\item If $\left(1 +\oo(1)- \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2$, then $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ whp.
 	\end{itemize}
 \end{theorem}
-As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$, for any $1 \le i \le k$.
+%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
 Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$.
@@
 
-For this setting, the problem reduces to the following.
+\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
+In this setting, we need to study the following loss function:
 \begin{align}
-	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
+	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
 \end{align}
-In order to prove Theorem \ref{thm_many_tasks}, we will derive a closed form solution for equation \eqref{eq_mtl_same_cov}.
+%In order to prove Theorem \ref{thm_many_tasks}, we will derive a closed form solution for equation \eqref{eq_mtl_same_cov}. \todo{check!} 
+For any fixed $W_1, W_2, \dots, W_t \in \R^r$, we can derive a closed form solution for $B$ as
+	\begin{align*}
+		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
+		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}
+	\end{align*}
+	where we denote $\cal W \in\real^{r\times t}$ as $\cal W=[W_1, W_2, \dots, W_t]$.
+	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
+	Then as in Section \ref{app_proof_sec3}, it remains to consider minimizing the validation loss 
+	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2}$$ 
+	over $\cal W$.
 
-\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-\todo{check!} By fixing $W_1, W_2, \dots, W_k$, we can derive a closed form solution for $B$ as
+	% Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$. 
+	It is easy to calculate that $\val( \cal W)$ contains two parts: $\val( \cal W)= \delta_{\beta}(\cal W) + \delta_{\vari}(\cal W)$. Here $\delta_{\beta}(\cal W) $ is the model shift bias term given by
 	\begin{align*}
-		\hat{B}(W_1, \dots, W_k) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^k Y_i W_i^{\top}} (Z Z^{\top})^{-1} \\
-		&= \sum_{i=1}^k \bigbrace{\beta_i W_i^{\top}} (ZZ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1}
+		\delta_{\beta}(\cal W) =\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
 	\end{align*}
-	where we denote $Z\in\real^{r\times k}$ as the $k$ vectors $W_1, W_2, \dots, W_k$ stacked together.
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	Similar to Section \ref{sec_setup}, we consider minimizing the validation loss over $W_1, W_2, \dots, W_k$ provided with $\hat{B}$.
-
-	Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
-	We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
-	The first part is the model shift bias, which is equal to
+	and $\delta_{\vari}(\cal W)$ is the variance term given by
 	\begin{align*}
-		\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
+		\delta_{\vari}(\cal W)= \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
 	\end{align*}
-	The second part is the variance, which is equal to
+	%Therefore we only need to focus on the minimizer for $\delta_{\beta}(\cal W) $ since the variance part does not depend on the weights. 
+	We denote $Q = \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{k\times k}$, whose $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$.
+	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
+	Now we can write the validation loss succinctly as 
 	\begin{align*}
-		& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
-		=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+		\val(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
 	\end{align*}
-	Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
-	Let us denote $Q = Z^{\top} (ZZ^{\top})^{-1} Z \in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
-	Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-	We can now write the validation loss succinctly as follows.
+	From this equation we can solve for $Q$ optimally as $\hat Q=U_{r}U_r^{\top}$.
+	In sum we have solved that $\hat{\beta}_i^{\MTL}=B^{\star} U_r U_r(i)$. Inserting it into the definition of the test error, we get that
 	\begin{align*}
-		\val(\hat{B}; W_1, \dots, W_k) = \bignormFro{\Sigma^{1/2} \bigbrace{B^{\star} Q - B^{\star}}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
+		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
+		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \sigma^2\norm{U_r(t)}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 \cdot \left( 1+\OO(p^{-1/2+\e})\right),
 	\end{align*}
-	From the above we can solve for $Q$ optimally as $U_{r}U_r^{\top}$.
-	Furthermore, we can solve $\hat{\beta}_i^{\MTL}$ as $B^{\star} U_r U_r(i)$.
-	Now we get that
-	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k W_i^{\top} (ZZ^{\top})^{-1}W_j \beta_i - \beta_j}}^2
-		+ \sigma^2  W_j^{\top} (ZZ^{\top})^{-1} W_j \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(i)}}^2 + \sigma^2\norm{U_r(i)}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-	\end{align*}
-	By using Lemma \ref{lem_minv}, we conclude the proof.
+	with high probability for any constant $\e>0$, where we used Lemma \ref{lem_minv} in the last step. Together with the fact that with high probability,
+	$$\te(\hat{\beta}_t^{\MTL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+	 also by Lemma \ref{lem_minv}, we conclude the proof.
 \end{proof}

### 2020-05-30 writeup/intro.tex
use squishlist
minor
wip

@@
 \begin{abstract}
-When does multi-task and transfer learning outperform single-task learning?
+When does multi-task learning outperform single-task learning?
 In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
-In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators.
+In the setting of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task learning estimators.
 A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
-	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
+	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task learning.
 	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning has become a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and numerous other areas \cite{ZY17}.
+Multi-task learning represents a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and numerous other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
 %Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
-By combining multiple information sources, it is possible to share new information among different sources in the same model \cite{C97}.
+By combining multiple information sources, it is possible to share all the information in the same model.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
-Intuitively, the performance of multi-task learning depends on the relationship of the information sources.
+The performance of multi-task learning depends on the relationship of the information sources \cite{C97}.
 When the information sources are heterogeneous, negative transfer -- where multi-task learning performs worse than single-task learning -- has often been observed \cite{AP16,BS17}.
@@
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-In this work, we develop technical tools to better understand when and why negative transfer occurs for learning multiple linear regression tasks in high dimensions.
+In this work, we develop technical tools to compare multi-task learning to single-task learning for the setting of high-dimensional linear regression.
 % for learning from multiple linear regression tasks.
-We use the tools to show theoretical and practical implications for detecting and improving negative transfer.
+We use the tools to explain negative transfer and provide implications for positive transfer.
+Based on the theory, we show practical implications for detecting and mitigating negative transfer.
 %We consider a setting where the target task has limited labeled data and show
@@
 In order to rigorously understand negative transfer, the technical challenge is to develop generalization bounds that scale tightly with the qualities of the data.
-
-%The technical challenge to develop a theory for multi-task learning is how to capture generalization performance that scales tightly with the amount of labeled data, in particular when the size of the training set is small.
-%Prior generalization theory using uniform stability \cite{LTSM16}, Rademacher complexity \cite{BS03,BBCKP10} is unable to explain the phenomenon of negative transfer because there is no tight bound on test error that scales with the amount of labeled data.
-%In particular in Figure \ref{fig_motivation}, we observe a shift from positive transfer to negative transfer as a parameter of task relatedness.
-%The theory we develop will provide a precise explanation to such a phenomenon.
-
-%To gain insight into the working of multi-task learning, we consider a simplified setting for learning multiple high-dimensional linear regression tasks.
-%A typical process to do multi-task learning involves two steps:
-%(i) Jointly learn a shared representation for all the tasks;
-%(ii) Fine-tune the learnt model on a specific target task.
-%We focus on a hard parameter sharing model proposed in \cite{R17,WZR20} and identify conditions on when multi-task and transfer learning works, and when it doesn't.
-%The high-dimensional linear regression setting where the target task data size is limited captures the intuition that the target task only contains limited labeled data.
 
@@
 Let $\hat{\beta}_t^{\STL}$ denote the standard linear regression estimator using task $t$ alone.
-We say there is negative transfer if the test error of $\hat{\beta}_t^{\MTL}$  is smaller than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+We say there is negative transfer if the test error of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
 
@@
 In Section \ref{sec_insight}, we use the technical results to provide guidance on when positive transfer is likely to occur and identify causes of negative transfer.
-\begin{itemize}
+\squishlist
 		\item First, we provide a more precise interpretation to a folklore understanding in multi-task learning, which posits that negative transfer is caused by having dissimilar tasks.
@@
 %		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-\end{itemize}
+\squishend
 

### 2020-05-30 writeup/intro.tex
intro

@@
 When does multi-task learning outperform single-task learning?
-In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
+In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture.
 In the setting of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task learning estimators.
@@
 	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task learning.
-	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
-	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
+	For example, we theoretically analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning.
+%, which has been a key empirical finding in recent work.
+	Finally, we show practical implications of our theory for detecting and mitigating negative effects in image and text classification tasks.
 \end{abstract}
@@
 When the information sources are heterogeneous, negative transfer -- where multi-task learning performs worse than single-task learning -- has often been observed \cite{AP16,BS17}.
-While numerous studies have sought to alleviate negative transfer when it occurs \cite{ZY17}, a rigorous understanding to the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
+While numerous studies have sought to alleviate negative transfer \cite{ZY17}, a rigorous understanding of the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
@@
 Identifying negative transfer requires developing tight generalization bounds for both multi-task learning and single-task learning.
-In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented in a way so that the error goes down as more labeled data is added.
-On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and multiple sparse regressions \cite{LPTV09,LPVT11}.
-In order to rigorously understand negative transfer, the technical challenge is to develop generalization bounds that scale tightly with the qualities of the data.
+In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented so that the error reduces as the data sizes of all tasks increase.
+For instance, the data sizes of all tasks are assumed to be equal \cite{B00}.
+On the other hand, uneven data sizes or dominating tasks have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
+More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+To rigorously study negative transfer, the technical challenge is to develop generalization bounds that scale tightly with properties of the data.
 
@@
 For a target task $t$,
-let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator by solving equation \eqref{eq_mtl}.
+let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator by minimizing equation \eqref{eq_mtl}.
 Let $\hat{\beta}_t^{\STL}$ denote the standard linear regression estimator using task $t$ alone.
@@
 We revisit the bias-variance tradeoff of the multi-task estimator.
-Interestingly, the variance of $\hat{\beta}_t^{\MTL}$ is always smaller than that of $\hat{\beta}_t^{\STL}$, hence resulting in a positive effect of variance reduction.
+Interestingly, we observe that the variance of $\hat{\beta}_t^{\MTL}$ is always smaller than that of $\hat{\beta}_t^{\STL}$, hence resulting in a positive effect of variance reduction.
 The bias of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, results in a negative effect caused by the difference between $\beta_t$ and the rest $\set{\beta_i}_{i=1}^{t-1}$.
-Hence, the tradeoff between the variance reduction effect and model shift bias determines whether we observe positive or negative transfer.
+Hence, the tradeoff between the variance reduction effect and model shift bias determines whether the transfer is positive.
 
-To quantify the tradeoff more precisely, we develop a new technical result on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for the setting of two tasks with general covariance matrices.
-Using the result, we provide a sharp bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
-When there are more than two tasks, we show a similar result if they all have the same covariates.
+To quantify the tradeoff more precisely, we develop a new technical result that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for the setting of two tasks with general covariance matrices.
+Our result extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ for a single random matrix \cite{S07}.
+Furthermore, we provide a nearly optimal error bound, which may be of independent interest.
+
+Using the result, we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for the setting of two tasks.
+For more than two tasks, we show a similar result if all tasks have the same features.
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
@@
 We study the transfer function used by Taskonomy \cite{ZSSGM18}, which pools learnt representations from source tasks into a shared body similar to $B$ in equation \eqref{eq_mtl}.
-We find that the model shift bias can be captured nicely by the orthogonal projection of $\beta_t$ to the subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+We find that the model shift bias can be captured by the orthogonal projection of $\beta_t$ to the subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
 These results are presented more precisely in Section \ref{sec_main}.
 
-The tradeoff that we developed in Section \ref{sec_main} depends on the qualities of each task dataset such as its data size and covariance matrix.
+The tradeoff that we develop in Section \ref{sec_main} depends on the properties of each task such as its data size and covariance matrix.
 In Section \ref{sec_insight}, we use the technical results to provide guidance on when positive transfer is likely to occur and identify causes of negative transfer.
@@
 %	A crucial technical tool that we develop for showing Theorem \ref{thm_main_informal} is the asymptotic limit of the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ (for the setting of two tasks), which may be of independent interest.
-	The technical tool we developed extends a well-known result in the random matrix theory literature on the trace of $(X^{\top}X)^{-1}$ \cite{S07} for a single random matrix to two random matrices.
-	Our error bound for the asymptotic limit is nearly optimal, which may be of independent interest.
 

### 2020-05-30 writeup/setup.tex
sec 2

@@
 
-We describe the bias-variance tradeoff of our setting as a warmup.
+We describe the bias-variance tradeoff of our setting more formally.
 Recall that we have $t$ labeled tasks available, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
@@
 Without loss of generality, let the $t$-th task denote the target task.
-For an estimator $\hat{\beta}\in\real^p$, the test error of the target task is defined as
+For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample (prediction) loss as
 	\begin{align*}
@@
 %Same for $\hat{\beta}_t^{\STL}$.
+
+\section{A Technical Tool to Quantify the Bias-Variance Trade-off}
+\label{sec_main}
+
+%We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
+We develop a technical tool to derive $\te(\hat{\beta}_t^{\MTL})$ that only depends on the qualities of task data such as data sizes and covariance matrices, for two tasks with general covariances.
+Then, we extend the result to more than two tasks that share the same features but have different labels.
+Finally, we show a sharp bias-variance tradeoff for transfer learning settings.
+%For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
+
+\textbf{Multi-task learning.} applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
+%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
+We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+Based on the result, we show how to determine positive versus negative transfer as follows.
+
+\begin{theorem}[Informal]\label{thm_main_informal}
+	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
+	Suppose that $n_1 = \rho_1 p$ and $n_2 = \rho_2 p$, where $\rho_1>1$ and $\rho_2 >1$ are fixed constants.
+	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, \Sigma_1^{}, n_1, n_2, \beta_1, \beta_2}$ such that
+	\begin{itemize}
+		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{theorem}
+
+Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
+%determined by the covariate shift matrix and the model shift.
+The bounds get tighter and tighter as $\rho_1$ increases.
+While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we will show that they provide nice interpretation for simplified settings later on in Section \ref{sec_insight}.
+
+We describe an overview of the proof of Theorem \ref{thm_main_informal}.
+By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
+%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
+This part introduces a negative effect to multi-task learning.
+The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+The output layer of each task scales the direction of $B$ suitably to fit the task.
+
+Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+This part introduces a positive variance reduction effect to performing multi-task learning.
+Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
+(i) the positive effect from variance reduction;
+(ii) the negative effect from model shift bias.
+A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
+
+\textbf{Extension.} The above result also applies to the setting of more than two tasks with the same covariates.
+%We extend the above result to any number of tasks that have the same covariates.
+%In this section we consider the setting with $k$ many that have the same covariates.
+Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
+We derive a similar trade-off between model shift bias and variance reduction for this setting as well.
+The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
+
+\textbf{Transfer learning.}
+We extend the intuition behind Theorem \ref{thm_main_informal} to transfer learning settings.
+We provide an analysis of the transfer function of Taskonomy \cite{ZSSGM18} using our setup.
+Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
+The transfer function then tries to fit the target task data to the source task encoder.
+For more details, we refer the reader to Figure 4 in Taskonomy.
+
+We map the procedure to our setup as follows.
+First, we obtain the single-task estimator $\hat{\beta}_i$ from the source tasks, for $1\le i \le t-1$.
+This forms the shared representation $B = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+Then, we learn the output layer $W_t$ on the target task by minimizing the following objective
+\begin{align}
+	g(W_t) = \bignorm{X_t B W_t - Y_t}^2.
+\end{align}
+After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the estimator for the target task.
+By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
+%We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
+The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.

### 2020-05-30 writeup/transfer.tex
Thm A.9
sec 2

@@
-\section{A Technical Tool to Quantify the Bias-Variance Trade-off}
-\label{sec_main}
-
-%We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
-We develop a technical tool to derive $\te(\hat{\beta}_t^{\MTL})$ that only depends on the qualities of task data such as data sizes and covariance matrices, for two tasks with general covariances.
-Then, we extend the result to more than two tasks that share the same features but have different labels.
-Finally, we show a sharp bias-variance tradeoff for transfer learning settings.
-%For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
-
-\textbf{Multi-task learning.} applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-Based on the result, we show how to determine positive versus negative transfer as follows.
-
-\begin{theorem}[Informal]\label{thm_main_informal}
-	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
-	Suppose that $n_1 = \rho_1 p$ and $n_2 = \rho_2 p$, where $\rho_1>1$ and $\rho_2 >1$ are fixed constants.
-	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, \Sigma_1^{}, n_1, n_2, \beta_1, \beta_2}$ such that
-	\begin{itemize}
-		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{theorem}
-
-Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
-%determined by the covariate shift matrix and the model shift.
-The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we will show that they provide nice interpretation for simplified settings later on in Section \ref{sec_insight}.
-
-We describe an overview of the proof of Theorem \ref{thm_main_informal}.
-By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
-%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
-We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
-This part introduces a negative effect to multi-task learning.
-The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
-The output layer of each task scales the direction of $B$ suitably to fit the task.
-
-Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
-This part introduces a positive variance reduction effect to performing multi-task learning.
-Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
-(i) the positive effect from variance reduction;
-(ii) the negative effect from model shift bias.
-A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
-
-\textbf{Extension.} The above result also applies to the setting of more than two tasks with the same covariates.
-%We extend the above result to any number of tasks that have the same covariates.
-%In this section we consider the setting with $k$ many that have the same covariates.
-Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
-We derive a similar trade-off between model shift bias and variance reduction for this setting as well.
-The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-
-\textbf{Transfer learning.}
-We extend the intuition behind Theorem \ref{thm_main_informal} to transfer learning settings.
-We provide an analysis of the transfer function of Taskonomy \cite{ZSSGM18} using our setup.
-Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
-The transfer function then tries to fit the target task data to the source task encoder.
-For more details, we refer the reader to Figure 4 in Taskonomy.
-
-We map the procedure to our setup as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from the source tasks, for $1\le i \le t-1$.
-This forms the shared representation $B^{\star}_{t-1} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
-Then, we learn the output layer $W_t$ on the target task by minimizing the following objective
-\begin{align}
-	g(W_t) = \bignorm{X_t B W_t - Y_t}^2.
-\end{align}
-After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the estimator for the target task.
-By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
-%We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
-The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.
-
 \section{Theoretical Implications}

### 2020-05-30 writeup/setup.tex
wip

@@
 
-%We revisit the classical bias-variance trade-off in the context of multi-task learning for linear regressions, in particular the setup of equation \eqref{eq_mtl}.
 We develop a technical tool to derive $\te(\hat{\beta}_t^{\MTL})$ that only depends on the qualities of task data such as data sizes and covariance matrices, for two tasks with general covariances.
@@
 Finally, we show a sharp bias-variance tradeoff for transfer learning settings.
+
+\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
 %For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
 
+\subsection{Applications to Multi-Task and Transfer Learning}
+
 \textbf{Multi-task learning.} applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
+The above result also applies to the setting of more than two tasks with the same covariates.
+%We extend the above result to any number of tasks that have the same covariates.
+%In this section we consider the setting with $k$ many that have the same covariates.
+Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
+The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
 %The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
@@
 
-\textbf{Extension.} The above result also applies to the setting of more than two tasks with the same covariates.
-%We extend the above result to any number of tasks that have the same covariates.
-%In this section we consider the setting with $k$ many that have the same covariates.
-Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
-We derive a similar trade-off between model shift bias and variance reduction for this setting as well.
-The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-
 \textbf{Transfer learning.}

### 2020-05-30 writeup/setup.tex
sec 4

@@
 \subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
-%For the high-dimensional setting where the data size of the target task is a small constant times dimension $p$, we quantify the trade-off as a function of the task models $\set{\beta_i}_{i=1}^t$, data size $\set{n_i}_{i=1}^t$, and covariance matrices $\set{\Sigma_i}_{i=1}^t$.
+
+\begin{lemma}[Informal statement of Lemma \ref{lem_cov_shift}]\label{lem_cov_shift_informal}
+	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ with $\rho_1=n_1/p>1$ and $\rho_2=n_2/p>1$.
+	Let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+	\begin{align*}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2} +\bigo{\|\Sigma_2\| p^{-1/2+\epsilon}},
+	\end{align*}
+where $(a_1, a_2)$ is the solution to the following deterministic equations:
+	\begin{align*}
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+	\end{align*}
+\end{lemma}
 
@@
 
-\begin{theorem}[Informal]\label{thm_main_informal}
+\begin{theorem}[Informal statement of Theorem \ref{thm_model_shift}]\label{thm_main_informal}
 	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
@@
 While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we will show that they provide nice interpretation for simplified settings later on in Section \ref{sec_insight}.
-
-We describe an overview of the proof of Theorem \ref{thm_main_informal}.
-By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
-%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
-We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
-This part introduces a negative effect to multi-task learning.
-The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
-The output layer of each task scales the direction of $B$ suitably to fit the task.
-
-Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
-This part introduces a positive variance reduction effect to performing multi-task learning.
-Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
-(i) the positive effect from variance reduction;
-(ii) the negative effect from model shift bias.
 A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.

### 2020-05-30 writeup/transfer.tex
sec 4

@@
 %Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
-Define the following function
+Define the following functions
 \begin{align*}
-	\Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
+	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
 \end{align*}
+Let $\alpha_{-} = (1 - \rho_1^{-1/2})^4$ and $\alpha_{+} = (1 + \rho_1^{-1/2})^4$.
 
 \begin{proposition}[Model dissimilarity]\label{prop_dist_transition}
-	In the isotropic model, assume that $\rho_1 > 40$ is a fixed constant.
-	Let $\sigma_1 = \sigma_2 = \sigma$.
-	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between model dissimilarity and $\Phi(\rho_1, \rho_2)$:
-	\begin{itemize}
-		\item If ${p d^2} < \frac{1}{2}  {\sigma^2}  \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If ${p d^2} \ge 2 {\sigma^2} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
+	In the isotropic model, suppose that $\rho_1 > 1$ and $\sigma_1 = \sigma_2 = \sigma$.
+	Then we have that
+	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
+	\squishlist
+		\item If $\Psi(\beta_1, \beta_2) < \alpha_{-} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) \ge \alpha_{+} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+	\squishend
 \end{proposition}
@@
 In general we can close their gap by increasing $\rho_1$.
+
+We describe an overview of the proof of Theorem \ref{thm_main_informal}.
+By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
+%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
+We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
+This part introduces a negative effect to multi-task learning.
+The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+The output layer of each task scales the direction of $B$ suitably to fit the task.
+Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+This part introduces a positive variance reduction effect to performing multi-task learning.
+Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
+(i) the positive effect from variance reduction;
+(ii) the negative effect from model shift bias.
 
@@
 \begin{proposition}[Source data size]\label{prop_data_size}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants.
-	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
-	\begin{itemize}
-		\item[a)] If $pd^2 \le \frac{1}{2}\cdot \frac{\sigma^2}{\rho_2-1}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ for any $\rho_1 > 40$.
-		\item[b)] If $pd^2 > 2\cdot\frac{\sigma^2}{\rho_2 - 1}$, then we have the following transition depending on $\rho_1$:
-		\begin{itemize}
-			\item If $\rho_1 \cdot p < \frac{(\rho_2-2)\sigma^2}{(1 + {\rho_1}^{-0.5})^4(\rho_2 - 1) d^2 - \sigma^2 / p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-			\item If $\rho_1 \cdot p > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) d^2 - \sigma^2 / p}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-		\end{itemize}
-	\end{itemize}
+	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+	We have that
+	\squishlist
+		\item If $\rho_1 < \frac{\rho_2-2}{\alpha_+ \cdot \Phi(\beta_1, \beta_2) (\rho_2 - 1) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\rho_1 > \frac{\rho_2-2}{\alpha_- \cdot \Phi(\beta_1, \beta_2) (\rho_2 - 3) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\squishend
 \end{proposition}
@@
 \begin{proposition}[Labeled data de-noising]\label{prop_var_transition}
-	In the isotropic model, assume that $\rho_1 > 40$ and $pd^2 < \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
+	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
 	We derive the following transition as a parameter of $\sigma_1^2$:

### 2020-05-30 writeup/transfer.tex
reorg

@@
 We extend Proposition \ref{prop_dist_transition} as follows.
-
-\begin{proposition}[Labeled data de-noising]\label{prop_var_transition}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
-	We derive the following transition as a parameter of $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 \le -2 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
-The details can be found in Appendix \ref{app_proof_data}.

### 2020-05-30 writeup/transfer.tex
merge

--- 2020-05-30 writeup/transfer.tex
@@
 We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
-This is formalized by a metric called the data efficiency ratio as follows.
+This is formalized as follows.
 
-Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the same performance.
+Given several tasks, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
 %More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(\alpha)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
+For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
 The data efficiency ratio is defined as
-\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~
-		\te_1(\hat{\beta}_1^{\MTL}(\alpha)) + \te_2(\hat{\beta}_2^{\MTL}(\alpha))
+\[ \argmin_{x\in(0, 1)} ~~
+		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
 		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
@@
 \begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1$ and $\rho_2$, $pd^2 < {8\sigma^2} /{(3 \rho)}$.
-	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
+	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
+	Let $$ the data efficiency ratio is bounded within
+	$[ ]$
 \end{proposition}

### 2020-05-30 writeup/proof_examples.tex

@@
 
+\begin{proposition}[Labeled data de-noising]\label{prop_var_transition}
+	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
+	We derive the following transition as a parameter of $\sigma_1^2$:
+	\begin{itemize}
+		\item If $\sigma_1^2 \le -2 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\end{itemize}
+\end{proposition}
+As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
+The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+%The details can be found in Appendix \ref{app_proof_data}.
+
 \begin{proof}[Proof of Proposition \ref{prop_var_transition}]

### 2020-05-30 writeup/proof_main.tex
A.1

@@
 %\end{equation}
-\todo{A proof outline; including the following key lemma.}
+%\todo{A proof outline; including the following key lemma.}
+The proof is divided into the following four steps. We first consider $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a fixed $v\ge 0$. 
+\begin{itemize}
+\item[(i)] We use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate 
+$$\sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}},\quad \sigma^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2},$$
+and the difference between them will lead to the $\Delta_{\vari}$ term.
 
-The proof is divided into four parts.
+\item[(ii)] Using the approximate isometry property of $X_1$ (see \eqref{eq_isometric} below), we will bound the bias term 
+$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - {v} \beta_t)}^2$$
+through 
+\be\label{deltabetapf}{v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_s - {v} \beta_t)}^2.\ee
 
-\paragraph{Part I: Bounding the bias from model shift.}
+\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\beta}$ term.
+
+\end{itemize}
+Finally, we have 
+\begin{itemize}
+\item[(iv)] We use a standard $\e$-net argument to extend the above results to $\hat M= \hat v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a possibly random $\hat v$.
+\end{itemize}
+
+\paragraph{Part I: Variance reduction.} Now fix a constant $v>0$. We have \todo{add details}
+
+\paragraph{Part II: Bounding the bias from model shift.}
 We relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\beta}$.

### 2020-05-30 writeup/transfer.tex

@@
 
-On the positive side, we describe two implications for positive transfer, assuming that $\norm{\beta_1 - \beta_2}^2$ is small in the isotropic model.
+On the positive side, we describe two implications for positive transfer, assuming that $\Psi(\beta_1, \beta_2)$ is small in the isotropic model.
 
@@
 	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
-	Let $$ the data efficiency ratio is bounded within
-	$[ ]$
+	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 2\Psi(\beta_1, \beta_2)}}. \]
 \end{proposition}

### 2020-05-30 writeup/experiments.tex
typos
merge
sec 3

@@
-\section{Practical Implications for Multi-Task Learning}
+\section{Experiments}
 
@@
 
-\subsection{Detecting and Improving Negative Effects}
+\subsection{Improving training efficiency in MTL}
+
+\subsection{Validating Algorithmic Implications}
 
 \textbf{A Metric to Determine Positive or Negative Transfer}
-We propose a simple metric to determine whether multi-task learning performs better than single-task learning.
-The metric is as follows.
-First, we train 2 single-task models on 2 separate tasks.
-We take the prediction accuracy of the two tasks.
-Let $\tau$ be a fixed threshold.
-If the accuracy of the source task is higher than the accuracy of the target task by $\tau$, then we predict positive transfer.
-On the other hand, if the accuracy of the source task is lower than the accuracy of the target task by $\tau$, then we predict negative transfer.
-
 Table \ref{tab:mtl_better_than_stl} shows the results on a sentiment analysis and an image classification task.
@@
 \end{table}
+
+\textbf{Improving labeled data efficiency.}
+We measure the data efficiency ratio on text classification tasks.
+We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.
 
@@
 
-\subsection{Validating Theoretical Implications}
+%\subsection{Validating Theoretical Implications}
 
-\textbf{Causes of negative transfer.}
+%\textbf{Contributing causes of negative transfer.}
 
-\textbf{Benefits of multi-task learning.}
+%\textbf{Implications for positive learning.}
 
-\textit{Improving labeled data efficiency.}
-We measure the data efficiency ratio on text classification tasks.
-We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.
-
-\textit{Transferring from a high accuracy to low accuracy.}
+%\textit{Transferring from a high accuracy to low accuracy.}%%%%%%%%
 
@@
 		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-		& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
+		& {\bf Standard} & {\bf Alignment} & {\bf Standard} & {\bf Alignment} \\
 		\midrule

### 2020-05-30 writeup/setup.tex
sec 3

@@
-\section{Preliminaries}\label{sec_setup}
+\section{A Technical Tool to Analyze the Bias-Variance Trade-off}
+\label{sec_main}
 
-We describe the bias-variance tradeoff of our setting more formally.
+We first describe the bias-variance tradeoff in our setting more formally.
+Then, we develop a key lemma for analyzing the tradeoff using random matrix theory.
+%We develop a technical tool to derive $\te(\hat{\beta}_t^{\MTL})$ that only depends on the qualities of task data such as data sizes and covariance matrices, for two tasks with general covariances.
+%Then, we extend the result to more than two tasks that share the same features but have different labels.
+Finally, we apply the key lemma to provide a sharp analysis of the bias-variance tradeoff of multi-task and transfer learning in our setting.
+
+\subsection{The Bias-Variance Tradeoff}\label{sec_setup}
+
 Recall that we have $t$ labeled tasks available, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
@@
 
+\textbf{Notations.}
+When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
+We refer to the first task as the source task when there are only two tasks.
+We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
+
+\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
+
 To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.
@@
 \begin{align}
-	\te_t(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
+	\te(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
 	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
@@
 where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
-%Hence the bias of $\te_t(\hat{\beta}_t^{\STL})$ is zero and its test error is equal to variance, given by $$.
+The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+The output layer of each task scales the direction of $B$ suitably to fit the task.
 
-\textbf{Notations.}
-When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
-We refer to the first task as the source task when there are only two tasks.
-We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
-%Same for $\hat{\beta}_t^{\STL}$.
-
-\section{A Technical Tool to Quantify the Bias-Variance Trade-off}
-\label{sec_main}
-
-We develop a technical tool to derive $\te(\hat{\beta}_t^{\MTL})$ that only depends on the qualities of task data such as data sizes and covariance matrices, for two tasks with general covariances.
-Then, we extend the result to more than two tasks that share the same features but have different labels.
-Finally, we show a sharp bias-variance tradeoff for transfer learning settings.
-
-\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
+We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
+This part introduces a negative effect to multi-task learning.
+Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+This part introduces a positive variance reduction effect to performing multi-task learning.
+Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the tradeoff between two effects:
+(i) the positive effect from variance reduction;
+(ii) the negative effect from model shift bias.
+In order to analyze the tradeoff, we present the following lemma, which provides a tight bound for equation \eqref{eq_te_var}.
 
 \begin{lemma}[Informal statement of Lemma \ref{lem_cov_shift}]\label{lem_cov_shift_informal}
-	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ with $\rho_1=n_1/p>1$ and $\rho_2=n_2/p>1$.
-	Let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+	In the setting of two tasks, let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
 	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
@@
 
-\subsection{Applications to Multi-Task and Transfer Learning}
+As a remark, when there is only the target task, $\rho_1$ equals zero.
+Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is to a well-known result in random matrix theory \cite{S07}.
 
-\textbf{Multi-task learning.} applies to the setting of two tasks where their covariance matrices may be arbitrarily different.
-The above result also applies to the setting of more than two tasks with the same covariates.
-%We extend the above result to any number of tasks that have the same covariates.
-%In this section we consider the setting with $k$ many that have the same covariates.
-Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
-The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
+\subsection{A Sharp Analysis of the Tradeoff for Multi-Task and Transfer Learning}
+
+\textbf{Multi-task learning.}
+We use Lemma \ref{lem_cov_shift_informal} to provide a sharp bias-variance tradeoff for two settings:
+(i) two tasks with general covariance matrices;
+(ii) any number of tasks that have the same features.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+We state our result for two tasks as follows.
+%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
 %The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-Based on the result, we show how to determine positive versus negative transfer as follows.
+%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+%Based on the result, we show how to determine positive versus negative transfer as follows.
 
 \begin{theorem}[Informal statement of Theorem \ref{thm_model_shift}]\label{thm_main_informal}
-	Let $X_i \in\real^{n_i \times p}$ and $Y_i = X_i\beta_i + \varepsilon_i$, for $i = 1, 2$.
-	Suppose that $n_1 = \rho_1 p$ and $n_2 = \rho_2 p$, where $\rho_1>1$ and $\rho_2 >1$ are fixed constants.
-	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ and a small deterministic error $\delta$ that only depend on $\set{\hat{v}, \Sigma_1^{}, n_1, n_2, \beta_1, \beta_2}$ such that
-	\begin{itemize}
+	For the setting of two tasks, let $\delta > 0$ be a desired error margin and $\rho_1 > ??$.
+	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1^{}, n_1, n_2, \beta_1, \beta_2}$ such that
+	\squishlist
 		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
 		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\end{itemize}
+	\squishend
 \end{theorem}
@@
 While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we will show that they provide nice interpretation for simplified settings later on in Section \ref{sec_insight}.
-A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
+The proof of Theorem \ref{thm_main_informal}  is presented in Appendix \ref{app_proof_main}.
+The result for more than two tasks is deferred to Appendix \ref{app_proof_many_tasks}.
 

### 2020-05-30 writeup/transfer.tex
sec 3

@@
-\section{Theoretical Implications}
-\label{sec_insight}
+\section{Understanding Negative Transfer and Their Algorithmic Implications}\label{sec_insight}
 
-Based on Theorem \ref{thm_main_informal}, we provide precise interpretations of many empirical phenomena in multi-task learning.
-In Section \ref{sec_similarity}, we explain three contributing causes of negative transfer, including model dissimilarity, large source data size and covariate shift.
-In Section \ref{sec_benefit}, we describe two implications for positive transfer, including labeled data efficiency and de-noising.
+Based on the key lemma, we explain three contributing factors of negative transfer, including model dissimilarity, large source data size and covariate shift.
+For each factor, we show how negative transfer occurs using a simplified isotropic model.
+Then, we describe the algorithmic implication of the theory.
 
-\subsection{Contributing Causes of Negative Transfer}\label{sec_similarity}
+\subsection{Model Dissimilarity}
 
@@
 
-\textbf{Cause 1.}
 We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
@@
 Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
-We remark that the constants $1/2$ and $2$ in the statement above are chosen for ease of presentation.
-In general we can close their gap by increasing $\rho_1$.
-
-We describe an overview of the proof of Theorem \ref{thm_main_informal}.
-By comparing the bias and variance of $\te_t(\hat{\beta}_t^{\MTL})$ to $\te_t(\hat{\beta}_t^{\STL})$, we observe the following two effects, respectively.
-%We begin by observing that the test error of $\hat{\beta}_t^{\MTL}$ consists of two parts.
-We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
-This part introduces a negative effect to multi-task learning.
-The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
-The output layer of each task scales the direction of $B$ suitably to fit the task.
-Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
-This part introduces a positive variance reduction effect to performing multi-task learning.
-Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the trade-off between two effects:
-(i) the positive effect from variance reduction;
-(ii) the negative effect from model shift bias.
-
 \todo{} We illustrate the example with a simulation.
@@
 We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-%in this proposition (and the following ones) can be replaced with $(1+c_1^{-1/2})^{-4}$ and $(1-c_1^{-1/2})^{-4}$. In particular, these bounds becomes tighter as $c_1$ increases.
 
@@
 
-\textbf{Cause 2.}
+\textbf{Algorithmic implication.}
+We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
+If $\sigma_1$ is too large, then the source task provides a negative transfer to the target.
+If $\sigma_1$ is small, then the transfer may be positive.
+Proposition \ref{prop_var_transition} formalizes the intuition.
+
+Based on the result, we propose a simple metric to determine whether multi-task learning performs better than single-task learning.
+The metric is as follows.
+First, we train 2 single-task models on 2 separate tasks.
+We take the prediction accuracy of the two tasks.
+Let $\tau$ be a fixed threshold.
+If the accuracy of the source task is higher than the accuracy of the target task by $\tau$, then we predict positive transfer.
+On the other hand, if the accuracy of the source task is lower than the accuracy of the target task by $\tau$, then we predict negative transfer.
+
+\subsection{Data Size.}
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
@@
 
-\textbf{Cause 3.}
+\textbf{Algorithmic implication.}
+We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
+This is formalized as follows.
+
+Given several tasks, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
+%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
+For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
+The data efficiency ratio is defined as
+\[ \argmin_{x\in(0, 1)} ~~
+		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
+		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
+We quantify the data efficiency ratio of the isotropic model as follows.
+
+\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
+	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
+	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 2\Psi(\beta_1, \beta_2)}}. \]
+\end{proposition}
+The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
+
+\subsection{Covariate Shift}
+
 So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
@@
 
-\subsection{Implications for Positive Transfer}\label{sec_benefit}
-
-On the positive side, we describe two implications for positive transfer, assuming that $\Psi(\beta_1, \beta_2)$ is small in the isotropic model.
-
-\textbf{Implication 1.}
-We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
-This is formalized as follows.
-
-Given several tasks, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
-%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
-The data efficiency ratio is defined as
-\[ \argmin_{x\in(0, 1)} ~~
-		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
-		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
-We quantify the data efficiency ratio of the isotropic model as follows.
-
-\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
-	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 2\Psi(\beta_1, \beta_2)}}. \]
-\end{proposition}
-The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
-
-\textbf{Implication 2.}
-We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-We extend Proposition \ref{prop_dist_transition} as follows.
+\textbf{Algorithmic implication.}

### 2020-05-30 writeup/experiments.tex
sec 5

@@
 \section{Experiments}
+
+We validate the algorithmic implications of our theory on image and text classification tasks.
+First, we show that our proposed metric is able to predict positive or negative transfer using only STL performances.
+Second, we show that MTL can improve data efficiency ratio.
+Finally, we show that performing covariance alignment is more significant when the source task data size is large compared to the target task.
 
@@
 
-\subsection{Validating Algorithmic Implications}
+\subsection{Validating the Algorithmic Implications}
 
-\textbf{A Metric to Determine Positive or Negative Transfer}
-Table \ref{tab:mtl_better_than_stl} shows the results on a sentiment analysis and an image classification task.
+\textbf{A Metric to determine positive or negative Transfer.}
+We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
+Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among ?? task pairs for the sentiment analysis tasks with $38.8\%$ recall.
+Similar for image classification task ??.
 
@@
 \textbf{Improving labeled data efficiency.}
-We measure the data efficiency ratio on text classification tasks.
-We find that by performing multi-task learning, only 40$\%$ of the data is needed to achieve comparable performance to single-task learning over all six tasks.
+We measure the data efficiency ratio on the sentiment analysis tasks.
+We find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks.
+If TREC is not included, we see that only $25\%$ of the labeled data is needed.
 
-\textbf{Covariance Alignment for Imbalanced Tasks with Covariate Shift.}
+\textbf{Covariance alignment.}
 We validate that the performance of aligning task covariances depends on the size of source task data.
-Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-
 In Figure \ref{fig_covariate}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.

### 2020-05-30 writeup/transfer.tex
sec 5

@@
 
-Based on the key lemma, we explain three contributing factors of negative transfer, including model dissimilarity, large source data size and covariate shift.
+Based on the key lemma, we explain three contributing factors of negative transfer, including task dissimilarity, large source data size and covariate shift.
 For each factor, we show how negative transfer occurs using a simplified isotropic model.
@@
 
-\subsection{Model Dissimilarity}
+\subsection{Task Dissimilarity}\label{sec_similarity}
 
@@
 
-\begin{proposition}[Model dissimilarity]\label{prop_dist_transition}
+\begin{proposition}[Task dissimilarity]\label{prop_dist_transition}
 	In the isotropic model, suppose that $\rho_1 > 1$ and $\sigma_1 = \sigma_2 = \sigma$.
@@
 
-\subsection{Data Size.}
+\subsection{Data Size}
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
@@
 \end{proposition}
-The intuition behind Proposition \ref{prop_data_size} is as follows.
-a) If $\norm{\beta_1 - \beta_2}^2 \approx pd^2$ is sufficiently small, then adding any amount of labeled data from the source task always provides positive transfer;
-ii) Otherwise, as source data size increases, we observe a transition from positive to negative transfer.
+Proposition \ref{prop_data_size} shows that as the source data size increases, we observe a transition from positive to negative transfer.
 The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}, and can be found in Appendix \ref{app_proof_31}.
@@
 	\end{align*}
-	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$. We first assume that there is no model bias. 
-	Similar to the isotropic model, we assume that $\beta_1=\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
+	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
+	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
 	The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
@@
 \begin{proposition}[Covariate shift]\label{prop_covariate}
-	In the setting described above, assume that $\rho_1 > 1$ and $\rho_2>1$.
+	In the setting described above, assume that $\rho_1, \rho_2>1$.
 	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
@@
 \textbf{Algorithmic implication.}
+Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+When the source task data size is particularly large compared to the target task, then we expect that applying the covariance alignment algorithm results in a more significant gain.

### 2020-05-30 writeup/experiments.tex
sec 4

@@
 We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
-Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among ?? task pairs for the sentiment analysis tasks with $38.8\%$ recall.
-Similar for image classification task ??.
+Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among 150 task pairs for the sentiment analysis tasks with $38.8\%$ recall.
+Similar for 91 image classification task pairs.
+Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.
 
@@
 \end{center}
-\caption{Ablation study on when should use MTL via different source/target task accuracy.
-Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.}
+\caption{Ablation study on when should use MTL via different source/target task accuracy.}
 \label{tab:mtl_better_than_stl}

### 2020-05-30 writeup/experiments.tex
sec 4.3

@@
 
-\textbf{A Metric to determine positive or negative Transfer.}
+\textbf{A metric to determine positive or negative transfer.}
 We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
@@
 
-\textbf{Improving labeled data efficiency.}
+\textbf{MTL improves labeled data efficiency.}
 We measure the data efficiency ratio on the sentiment analysis tasks.

### 2020-05-30 writeup/experiments.tex
update table layout

@@
 \begin{table}
-\begin{center}
+	\centering
+	\subfloat[Ablation study on when should use MTL via different source/target
+	task accuracy.\label{tab:mtl_better_than_stl}]{%
   \begin{tabular}{c c c c c}
 	\toprule
-    \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
+		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text
+		classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
 		& Precision &  Recall & Precision &  Recall \\
@@
 		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
-    0.3 & 1.000 & 0.004 &     - &     - \\
+		% 0.3 & 1.000 & 0.004 &     - &     - \\
 	\bottomrule
-  \end{tabular}
-\end{center}
-\caption{Ablation study on when should use MTL via different source/target task accuracy.}
-\label{tab:mtl_better_than_stl}
+	\end{tabular}}
+	\quad% --- set horizontal distance between tables here
+	\subfloat[Taskonomy experiment.\label{tab:taskonomy}]{%
+	\begin{tabular}{c c c}
+		\toprule
+		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
+		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
+		\cmidrule(lr){2-3}
+		& {\bf Standard} & {\bf Alignment} \\
+		\midrule
+		{\bf MLP}  & > 100\% & 39\% \\
+		{\bf LSTM} & 36\% & 36\% \\
+		\bottomrule
+		\end{tabular}}
 \end{table}
+
+% \begin{table}
+% \begin{center}
+%   \begin{tabular}{c c c c c}
+%   \toprule
+%     \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
+%     & Precision &  Recall & Precision &  Recall \\
+%     \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
+%     0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
+%     0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
+%     0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
+%     0.3 & 1.000 & 0.004 &     - &     - \\
+%   \bottomrule
+%   \end{tabular}
+% \end{center}
+% \caption{Ablation study on when should use MTL via different source/target task accuracy.}
+% \label{tab:mtl_better_than_stl}
+% \end{table}
 
@@
 
-\begin{table}
-	\begin{center}
-		\begin{tabular}{c c c c c}
-		\toprule
-		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-		& {\bf Standard} & {\bf Alignment} & {\bf Standard} & {\bf Alignment} \\
-		\midrule
-		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-		% {\bf CNN}  & 76\% & - & 32\% & -\\
-		\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Taskonomy experiment.}
-	\label{tab:taskonomy}
-	\end{table}
+% \begin{table}
+% 	\begin{center}
+% 		\begin{tabular}{c c c c c}
+% 		\toprule
+% 		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
+% 		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
+% 		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+% 		& {\bf Standard} & {\bf Alignment} & {\bf Standard} & {\bf Alignment} \\
+% 		\midrule
+% 		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
+% 		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
+% 		% {\bf CNN}  & 76\% & - & 32\% & -\\
+% 		\bottomrule
+% 		\end{tabular}
+% 	\end{center}
+% 	\caption{Taskonomy experiment.}
+% 	\label{tab:taskonomy}
+% 	\end{table}
 

### 2020-05-30 writeup/intro.tex
intro

@@
 We combine all the labeled data using a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
-This corresponds to minimizing the following objective.
-\begin{align}
-	\label{eq_mtl}
-	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2.
-\end{align}
+This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
 For a target task $t$,
@@
 
-To quantify the tradeoff more precisely, we develop a new technical result that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for the setting of two tasks with general covariance matrices.
+To quantify the tradeoff more precisely, we develop a new technical tool that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for the setting of two tasks with general covariance matrices.
 Our result extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ for a single random matrix \cite{S07}.
 Furthermore, we provide a nearly optimal error bound, which may be of independent interest.
-
-Using the result, we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for the setting of two tasks.
-For more than two tasks, we show a similar result if all tasks have the same features.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, we apply our technical tools to the related setting of transfer learning.
-We study the transfer function used by Taskonomy \cite{ZSSGM18}, which pools learnt representations from source tasks into a shared body similar to $B$ in equation \eqref{eq_mtl}.
-We find that the model shift bias can be captured by the orthogonal projection of $\beta_t$ to the subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+Using the result, we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
+(i) two tasks with general covariance matrice; (ii) any number of tasks that have the same features (e.g. images).
+Finally, we apply our technical tool to the related setting of transfer learning.
+We pool learnt representations from source tasks into a shared body similar to $B$ in equation \eqref{eq_mtl}, which has also been used in Taskonomy \cite{ZSSGM18}.
+For this setting, we show that the model shift bias can be captured by the orthogonal projection of $\beta_t$ to the subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
 These results are presented more precisely in Section \ref{sec_main}.
 
-The tradeoff that we develop in Section \ref{sec_main} depends on the properties of each task such as its data size and covariance matrix.
-In Section \ref{sec_insight}, we use the technical results to provide guidance on when positive transfer is likely to occur and identify causes of negative transfer.
+The tradeoff that we develop depends on the properties of each task such as its data size and covariance matrix.
+In Section \ref{sec_insight}, we use our technical tool to rigorously explain many phenomena in multi-task learning.
+We consider three factors including task dissimilarity, data size and covariate shift.
 \squishlist
-		\item First, we provide a more precise interpretation to a folklore understanding in multi-task learning, which posits that negative transfer is caused by having dissimilar tasks.
-		For an example of two tasks, we show a sharp transition from positive to negative transfer determined by the ratio of $\norm{\beta_1 - \beta_2}^2$ and a certain function of data sizes (cf.
-Proposition \ref{prop_dist_transition}).
-		We further show that positive transfer is more likely to occur when transferring from a less noisy source task to a more noisy target task.
-		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
+		\item First, we define task dissimilarity as the distance between $\beta_1$ and $\beta_2$ using a simplified isotropic setting of two tasks.
+		Using our technical tool, we show a sharp transition from positive to negative transfer as task dissimilarity increases.
+		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
+%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
 %	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-		\item Second, we find that depending on how large $\norm{\beta_1 - \beta_2}^2$ is, adding more labeled data from the source task does not always reduce the test error of $\hat{\beta}_t^{\MTL}$ (cf.
-Proposition \ref{prop_data_size}).
-	We connect the observation to explain a key finding of Taskonomy \cite{ZSSGM18}.
-	We define the \textit{data efficiency ratio} as the smallest $\alpha\in(0, 1)$ such that if we only use an $\alpha$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
-	In Proposition \ref{prop_data_efficiency}, we show that the data efficiency ratio of an illustrative example is at most $\alert{\frac {1}{2\rho_t}}$.
-	In Section \ref{sec_validate}, we validate that performing multi-task learning can reduce the need for labeled data on 6 sentiment analysis tasks.
+		\item Second, we consider the effect of uneven data sizes.
+	We begin by observing that adding more labeled data from the source task does not always improve performance.
+	Then, we theoretically analyze the benefit of multit-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy \cite{ZSSGM18}.
+%	We define the \textit{data efficiency ratio} as the smallest $x$ such that if we only use an $$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
+	%In Proposition \ref{prop_data_efficiency}, we show that the data efficiency ratio of an illustrative example is at most $\alert{\frac {1}{2\rho_t}}$.
+	%In Section \ref{sec_validate}, we validate that performing multi-task learning can reduce the need for labeled data on 6 sentiment analysis tasks.
 %, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
-		\item Finally, we find that covariate shift, i.e. having different covariance matrices, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-		We show that as $n_1 / n_2$ becomes large, the best performing source task has have the same covariance matrix as the target task (cf. Proposition \ref{prop_covariate}).
+		\item Finally, we show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
+		We show that as $n_1 / n_2$ becomes large, the source task should have the same covariance matrix as the target task to ensure the best performance.
 %		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
 \squishend
-
-%	A crucial technical tool that we develop for showing Theorem \ref{thm_main_informal} is the asymptotic limit of the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ (for the setting of two tasks), which may be of independent interest.
-
-We show practical implications of our theory on text and image classification tasks.
+We validate the above phenomena on text and image classification tasks.
+Based on the theory, we provide algorithmic implications for detecting and mitigating negative transfer.
 First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.
 Second, \todo{}
-	Finally, we show that as the data size between the source and target task becomes more imbalanced, aligning the covariances of the tasks becomes more beneficial.
-% as the data size becomes more imbalanced between the source and target task, having mis-aligned task covariance matrices can result in suboptimal performance.
-	%validate on text and image classification tasks that comparing single-task accuracies can help determine whether multi-task learning performs better than single-task learning.
-
-%	On the other hand, if the number of source task datapoints is comparable to the target task, aligning task covariances may hurt performance.
+Finally, we provide a new insight on the covariance alignment algorithm, proposed in \cite{WZR20}.
+We show that as the size of the source task becomes larger compared to the target task, the covariance alignment algorithm produces more significant results.

### 2020-05-30 writeup/setup.tex
intro

@@
 Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
+\begin{align}
+	\label{eq_mtl}
+	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2.
+\end{align}
 We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts (to be derived in Appendix \ref{app_proof_sec3}) as follows

### 2020-05-30 writeup/experiments.tex
update table layout
re structure

@@
 
-\subsection{Improving training efficiency in MTL}
+\subsection{Experimental Results}
 
-\subsection{Validating the Algorithmic Implications}
-
-\textbf{A metric to determine positive or negative transfer.}
+\textbf{A metric for the diagnosis of MTL.}
 We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
@@
 
+\textbf{Improving training efficiency via an incremental schedule.}
+\todo{}
+
+\subsection{Ablation Studies}
+
+\textbf{Task similarity.} \todo{}
+
 \begin{table}
+\begin{minipage}[t]{.58\textwidth}
 	\centering
-	\subfloat[Ablation study on when should use MTL via different source/target
-	task accuracy.\label{tab:mtl_better_than_stl}]{%
   \begin{tabular}{c c c c c}
@@
 	\bottomrule
-	\end{tabular}}
-	\quad% --- set horizontal distance between tables here
-	\subfloat[Taskonomy experiment.\label{tab:taskonomy}]{%
+	\end{tabular}
+	\vspace{0.1in}
+	\captionof{table}{Ablation study on when should use MTL via different source/target task accuracy.}
+	\label{tab:mtl_better_than_stl}
+\end{minipage}
+\quad
+% \vspace{}
+\begin{minipage}[t]{.40\textwidth}
+	\centering
 	\begin{tabular}{c c c}
@@
 		\bottomrule
-		\end{tabular}}
+		\end{tabular}
+	\vspace{0.1in}
+	\captionof{table}{Taskonomy experiment.}
+	\label{tab:taskonomy}
+\end{minipage}
 \end{table}
@@
 
-\textbf{MTL improves labeled data efficiency.}
+\textbf{Data size and efficiency.}
 We measure the data efficiency ratio on the sentiment analysis tasks.
@@
 
-\textbf{Covariance alignment.}
+\textbf{Covariate shift.}
 We validate that the performance of aligning task covariances depends on the size of source task data.

### 2020-05-30 writeup/transfer.tex
re structure

@@
 
-\subsection{Task Dissimilarity}\label{sec_similarity}
+\subsection{Task Similarity}\label{sec_similarity}
 
@@
 
-\textbf{Algorithmic implication.}
+\textbf{Algorithmic consequence.}
 We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
@@
 
-\subsection{Data Size}
+\subsection{Data Size and Efficiency}
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
@@
 
-\textbf{Algorithmic implication.}
 We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
@@
 The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
+
+\textbf{Algorithmic consequence.} \todo{}
 
@@
 
-\textbf{Algorithmic implication.}
+\textbf{Algorithmic consequence.}
 Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.

### 2020-05-30 writeup/intro.tex
sec 1

@@
 % for learning from multiple linear regression tasks.
-We use the tools to explain negative transfer and provide implications for positive transfer.
-Based on the theory, we show practical implications for detecting and mitigating negative transfer.
+We use the tools to rigorously explain the phenomena of negative transfer.
+Our theory also leads to practical implications: we propose a diagnostic metric and a training schedule to improve multi-task training.
 %We consider a setting where the target task has limited labeled data and show
@@
 In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented so that the error reduces as the data sizes of all tasks increase.
-For instance, the data sizes of all tasks are assumed to be equal \cite{B00}.
+For instance, the data sizes of all tasks are often assumed to be equal \cite{B00}.
 On the other hand, uneven data sizes or dominating tasks have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
@@
 
-In this work, we consider a setting where multiple labeled linear regression tasks are available and focus on predicting a particular task whose amount of labeled data is limited.
+In this work, we consider the setting of high-dimensional linear regression and focus on predicting a particular task whose amount of labeled data is limited.
 Following Hastie et al.
@@
 
-We combine all the labeled data using a hard parameter sharing architecture that contains a shared body $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
-This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-For a target task $t$,
-let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator by minimizing equation \eqref{eq_mtl}.
-Let $\hat{\beta}_t^{\STL}$ denote the standard linear regression estimator using task $t$ alone.
-We say there is negative transfer if the test error of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+We combine all the labeled data using a hard parameter sharing architecture with a linear shared layer $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
+%This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
+For a target task $t$, let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator (defined precisely in Section \ref{sec_setup}).
+Let $\hat{\beta}_t^{\STL}$ denote the standard linear regression estimator for task $t$.
+We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
 
@@
 Interestingly, we observe that the variance of $\hat{\beta}_t^{\MTL}$ is always smaller than that of $\hat{\beta}_t^{\STL}$, hence resulting in a positive effect of variance reduction.
-The bias of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, results in a negative effect caused by the difference between $\beta_t$ and the rest $\set{\beta_i}_{i=1}^{t-1}$.
+The bias of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
 Hence, the tradeoff between the variance reduction effect and model shift bias determines whether the transfer is positive.
 
-To quantify the tradeoff more precisely, we develop a new technical tool that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, for the setting of two tasks with general covariance matrices.
+To quantify the tradeoff more precisely, we develop a new technical tool that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which arises naturally from the setting of two tasks.
 Our result extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ for a single random matrix \cite{S07}.
@@
 Finally, we apply our technical tool to the related setting of transfer learning.
-We pool learnt representations from source tasks into a shared body similar to $B$ in equation \eqref{eq_mtl}, which has also been used in Taskonomy \cite{ZSSGM18}.
+We pool learnt representations from source tasks into a shared body similar to $B$ in the hard parameter sharing architecture, which has also been used in Taskonomy by Zamir et al.'18 \cite{ZSSGM18}.
 For this setting, we show that the model shift bias can be captured by the orthogonal projection of $\beta_t$ to the subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
@@
 The tradeoff that we develop depends on the properties of each task such as its data size and covariance matrix.
-In Section \ref{sec_insight}, we use our technical tool to rigorously explain many phenomena in multi-task learning.
-We consider three factors including task dissimilarity, data size and covariate shift.
+In Section \ref{sec_insight}, we use our technical tool to rigorously explain negative transfer in multi-task learning.
+We identify three factors including task similarity, data size and covariate shift.
 \squishlist

### 2020-05-30 writeup/setup.tex
sec 1

@@
-\section{A Technical Tool to Analyze the Bias-Variance Trade-off}
+\section{A Technical Tool to Analyze the Bias-Variance Tradeoff}
 \label{sec_main}
@@
 We first describe the bias-variance tradeoff in our setting more formally.
-Then, we develop a key lemma for analyzing the tradeoff using random matrix theory.
-%We develop a technical tool to derive $\te(\hat{\beta}_t^{\MTL})$ that only depends on the qualities of task data such as data sizes and covariance matrices, for two tasks with general covariances.
-%Then, we extend the result to more than two tasks that share the same features but have different labels.
-Finally, we apply the key lemma to provide a sharp analysis of the bias-variance tradeoff of multi-task and transfer learning in our setting.
+Then, we develop a key lemma that arises naturally in the high-dimensional setting.
+Finally, we apply the lemma to provide a sharp analysis of the bias-variance tradeoff of multi-task and transfer learning in our setting.
 

### 2020-05-31 writeup/intro.tex
sec 2

@@
 In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture.
-In the setting of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task learning estimators.
-A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
+In the setting of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task learning, and extend the result to transfer learning.
+A key technical tool we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1, X_2$ in the setting of two tasks.
 	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task learning.

### 2020-05-31 writeup/setup.tex
sec 2

@@
-\section{A Technical Tool to Analyze the Bias-Variance Tradeoff}
+\section{A Sharp Analysis of the Tradeoff for Multi-Task and Transfer Learning}
 \label{sec_main}
@@
 
-Recall that we have $t$ labeled tasks available, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
+Recall that we have $t$ labeled tasks as the training dataset, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
 %Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d.
@@
 Without loss of generality, let the $t$-th task denote the target task.
+We consider a linear multi-task learning architecture by minimizing the following
+\begin{align}
+	\label{eq_mtl}
+	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2,
+\end{align}
+where $B\in\real^{p\times r}$ and $W_i\in\real^r$.
+Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ to be the single-task optimum.
+Hence there is no positive or negative transfer.
+We define $\hat{\beta}_t^{\MTL}$ by two steps:
+(i) minimizing $f(\cdot)$ over $B$;
+(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set.
+For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
 For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample (prediction) loss as
@@
 Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
-\begin{align}
-	\label{eq_mtl}
-	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2.
-\end{align}
 We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts (to be derived in Appendix \ref{app_proof_sec3}) as follows
@@
 
-\subsection{A Sharp Analysis of the Tradeoff for Multi-Task and Transfer Learning}
+\subsection{Applying the Key Lemma to Analyze the Tradeoff}
 

### 2020-05-31 writeup/setup.tex
sec 2

@@
 where $B\in\real^{p\times r}$ and $W_i\in\real^r$.
+Here $B$ provides a shared subspace for all tasks and $W_i$ fits $B$ suitably to each task.
 Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ to be the single-task optimum.
@@
 	\begin{align*}
-		\te_t(\hat{\beta}) \define \exarg{z}{\exarg{\varepsilon_t}{({(\Sigma_t^{1/2} z)}^{\top}\hat{\beta} - {(\Sigma_t^{1/2})}^{\top}\beta_t)^2}}
-		= \exarg{\varepsilon_t}{(\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)}.
+		\te_t(\hat{\beta}) \define \exarg{x}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
+		= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t).
 	\end{align*}
@@
 We refer to the first task as the source task when there are only two tasks.
-We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
+%We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
 
@@
 To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.
-Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
-We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts (to be derived in Appendix \ref{app_proof_sec3}) as follows
+%Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
+We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
 \begin{align}
@@
 \end{align}
-where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
-The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
-The output layer of each task scales the direction of $B$ suitably to fit the task.
+Here $\hat{v}$ denotes a fixed value that depends on the output layer weights.
+$\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+These are derived in Appendix \ref{app_proof_sec3}.
 

### 2020-05-31 writeup/intro.tex
sec 2

@@
 
-We combine all the labeled data using a hard parameter sharing architecture with a linear shared layer $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
+We focus on the hard parameter sharing architecture with a linear shared layer $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-For a target task $t$, let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator (defined precisely in Section \ref{sec_setup}).
-Let $\hat{\beta}_t^{\STL}$ denote the standard linear regression estimator for task $t$.
+For a target task $t$, let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task (MTL) estimator (defined precisely in Section \ref{sec_setup}).
+Let $\hat{\beta}_t^{\STL}$ denote the standard single-task (STL) estimator for task $t$.
 We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.

### 2020-05-31 writeup/setup.tex
sec 2

@@
 For this purpose, we consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
-%Recall that $n_i = \rho_i \cdot p$ and we assume $\rho_i > 1$ is a fixed constant for every $1\le i\le t$.
-
-We focus on a setting where $\rho_t$ is a small constant.
+We focus on a setting where $\rho_t$ is small compared to $\set{\rho_i}_{i=1}^{t-1}$.
 This setting captures the need for adding more labeled data to reduce the test error of the target task.
@@
 \end{align}
-Here $\hat{v}$ denotes a fixed value that depends on the output layer weights.
-$\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
+Here $\hat{v}\in\real$ denotes a fixed value that depends on the output layer weights.
+The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
 These are derived in Appendix \ref{app_proof_sec3}.
@@
 (ii) the negative effect from model shift bias.
-In order to analyze the tradeoff, we present the following lemma, which provides a tight bound for equation \eqref{eq_te_var}.
+In order to analyze the tradeoff, we develop the following result, which provides a tight bound for equation \eqref{eq_te_var}.
 
@@
 As a remark, when there is only the target task, $\rho_1$ equals zero.
-Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is to a well-known result in random matrix theory \cite{S07}.
+Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is a well-known result in random matrix theory \cite{S07}.
+Hence our result provides a necessary tool to analyze MTL in high dimensions.
 
@@
 \textbf{Multi-task learning.}
-We use Lemma \ref{lem_cov_shift_informal} to provide a sharp bias-variance tradeoff for two settings:
+We apply Lemma \ref{lem_cov_shift_informal} to provide a sharp analysis of the bias-variance tradeoff for two settings:
 (i) two tasks with general covariance matrices;
-(ii) any number of tasks that have the same features.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+(ii) any number of tasks that have the same features, i.e. $X_i = X_j$ for any $i\neq j$.
+The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
 We state our result for two tasks as follows.
@@
 \begin{theorem}[Informal statement of Theorem \ref{thm_model_shift}]\label{thm_main_informal}
-	For the setting of two tasks, let $\delta > 0$ be a desired error margin and $\rho_1 > ??$.
-	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1^{}, n_1, n_2, \beta_1, \beta_2}$ such that
+	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \kappa(M)^4 \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
+	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
 	\squishlist
-		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Delta_{\vari} - \Delta_{\beta} \le \delta$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\vari} - \Delta_{\beta} \le -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 
-Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
+Theorem \ref{thm_main_informal} shows that as the source task data size increases, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\vari} - \Delta_{\beta}$.
 %determined by the covariate shift matrix and the model shift.
-The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we will show that they provide nice interpretation for simplified settings later on in Section \ref{sec_insight}.
+%The bounds get tighter and tighter as $\rho_1$ increases.
+While the general form of $\Delta_{\vari}-\Delta_{\beta}$ can be complex (as is preivous generalization bounds for MTL), they admit interpretable forms for simplified settings.
+This will be the focus of Section \ref{sec_insight}.
 The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
@@
 \textbf{Transfer learning.}
-We extend the intuition behind Theorem \ref{thm_main_informal} to transfer learning settings.
-We provide an analysis of the transfer function of Taskonomy \cite{ZSSGM18} using our setup.
-Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
-The transfer function then tries to fit the target task data to the source task encoder.
-For more details, we refer the reader to Figure 4 in Taskonomy.
-
-We map the procedure to our setup as follows.
-First, we obtain the single-task estimator $\hat{\beta}_i$ from the source tasks, for $1\le i \le t-1$.
-This forms the shared representation $B = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
-Then, we learn the output layer $W_t$ on the target task by minimizing the following objective
+We extend Theorem \ref{thm_main_informal} to transfer learning settings.
+We study the transfer procedure used in Taskonomy by Zamir et al.'18 \cite{ZSSGM18}.
+For the setting of high-dimensional linear regression, the transfer procedure is as follows.
+%Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
+%The transfer function then tries to fit the target task data to the source task encoder.
+\squishlist
+	\item Learning source task representations: we obtain $\hat{\beta}_i^{\STL}$ from each source task, for $1\le i \le t-1$.
+		This forms a shared representation $\hat{B} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+	\item Fine-tuning on the target task: we learn the output layer $W_t\in\real^{t-1}$ for the target task similar to equation \eqref{eq_mtl}
 		\begin{align}
@@
 		\end{align}
-After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the estimator for the target task.
-By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
+\squishend
+After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the transfer learning estimator for the target task.
+%By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
 %We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.

### 2020-05-31 writeup/proof_main.tex
Thm A.5

--- 2020-05-30 writeup/proof_main.tex
@@
 Then we introduce the following matrix
-$$\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat a_2 +\hat  a_1 \hat {M}^{\top}\hat {M})^2} \hat {M}^{\top},$$
+\be\label{defnpihat}\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat a_2 +\hat  a_1 \hat {M}^{\top}\hat {M})^2} \hat {M}^{\top},\ee
 which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
@@
 Finally, we introduce the error term
-\be\label{eq_deltaextra}\delta:=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,\ee
-where we recall that $\kappa(\hat M)$ is the condition number of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.
+\be\label{eq_deltaextra}\delta:=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\lambda_{\min}^2(\hat M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,\ee
+where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.
 
@@
 	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\beta} \ge   \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\beta} \le -\delta, \label{lower}
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\beta} \le - \delta, \label{lower}
 	\end{align}
@@
 	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} }  \\
-		\Delta_{\beta} &\define (\beta_s - \hat{v}\beta_t)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_s - \hat{v}\beta_t). 
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} } \label{Deltavarv} \\
+		\Delta_{\beta} &\define (\beta_s - \hat{v}\beta_t)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_s - \hat{v}\beta_t). \label{Deltabetav}
 	\end{align}
@@
 %\end{equation}
-\todo{A proof outline; including the following key lemma.}
+%\todo{A proof outline; including the following key lemma.}
+Note that 
+\begin{align*}
+L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL}) &=\left( \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} - \sigma^2 \cdot \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right) \\
+&- \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2=:\delta_{\vari}(\hat v) - \delta_{\beta}(\hat v).
+\end{align*}
+The proof is divided into the following four steps. 
+\begin{itemize}
+\item[(i)] We first consider $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a fixed $v\ge 0$.
+Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
+%$$\sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}},\quad \sigma^2 \cdot \bigtr{({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2},$$
+%and the difference between them
 
-The proof is divided into four parts.
+\item[(ii)] Using the approximate isometry property of $X_1$ (see \eqref{eq_isometric} below), we will bound the bias term $ \delta_{\beta}(v)$
+%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - {v} \beta_t)}^2$$
+through 
+\be\label{deltabetapf}
+\wt\delta_{\beta}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_s - {v} \beta_t)}^2.\ee
 
-\paragraph{Part I: Bounding the bias from model shift.}
-We relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\beta}$.
-\begin{proposition}\label{prop_model_shift}
+\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\beta}$ term.
+
+\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M= \hat v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a possibly random $\hat v$.
+\end{itemize}
+
+\paragraph{Step I: Variance reduction.} Let $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for any fixed constant $v\ge 0$. Then using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
+$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right) \quad \text{whp},$$
+and 
+$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} ,\quad \text{whp},$$
+where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2}. Combining them, we get 
+\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{whp},
+\ee 
+where $\Delta_{\vari}(v)$ is defined as in \eqref{Deltavarv} but with $\hat v$ replaced by $v$.
+
+\paragraph{Step II: Bounding the bias term.}
+In this step, we shall use the following the following bounds on the singular values of $Z_1$: for any fixed $\e>0$, we have
+\begin{align}
+\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq \frac{Z_1^T Z_1}{n_1}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e})   \label{eq_isometric}
+\end{align}
+with high probability.
+In fact, $Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its nonzero eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
+For the estimate \eqref{eq_isometric} we used \cite[Theorem 2.10]{isotropic} to get a stronger probability bound.
+
+Next we shall use \eqref{eq_isometric} to approximate $\delta_\beta(v)$ with $\wt\delta_\beta(v)$ in \eqref{deltabetapf}.  
+%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\beta}$.
+\begin{lemma}\label{prop_model_shift}
 	In the setting of Theorem \ref{thm_model_shift},
-	denote by $K = (\hat{w}^2X_1^{\top}X_1 + X_2^{\top}X_1)^{-1}$, and
+	we denote by $K = (v^2X_1^{\top}X_1 + X_2^{\top}X_1)^{-1}$, and
 	\begin{align*}
-		\delta_1 &= \hat{w}^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_s - \hat{w}\beta_t)}^2, \\
-		\delta_2 &= n_1^2\cdot \hat{w}^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_s - \hat{w}\beta_t)}, \\
-		\delta_3 &= n_1^2\cdot \hat{w}^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t)}^2.
+		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_s - v\beta_t)}^2, \\
+		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_s - v\beta_t)}, \\
+		\delta_\e(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2.
 	\end{align*}
-	We have that
+	Then we have whp,
 	\begin{align*}
-		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
-		\le  \delta_1 - \delta_2
-		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
+		 \left| \delta_\beta(v)-\wt\delta_\beta(v)\right| 
+		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_\e.
 	\end{align*}
-	For the special case when $\Sigma_1 = \id$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$, we further have
+%	We have that
+%	\begin{align*}
+%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
+%		\le  \delta_1 - \delta_2
+%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
+%	\end{align*}
+%	For the special case when $\Sigma_1 = \id$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$, we further have
+%	\begin{align*}
+%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}
+%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \beta_t)}^2.
+%	\end{align*}
+\end{lemma}
+
+\begin{proof}
+	%The proof follows by applying equation \eqref{eq_isometric}.
+	%Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
+	Denote by $\cE = Z_1^{\top}Z_1 - {n_1}\id$. Then we can write
+%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_s - \hat{w}\beta_t)}^2$.
+	%We have
+	\begin{align}
+%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \hat{w}\beta_t)}^2 \nonumber \\
+		 \delta_\beta(v)-\wt\delta_\beta(v)&= {2v^2n_1}(\beta_s - v\beta_t)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_s - v\beta_t) \nonumber
+		\\
+		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_s - v\beta_t)}^2. \label{eq_lem_model_shift_1}
+%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
+	\end{align}
+	Using \eqref{eq_isometric}, we can bound  
+	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{whp}.$$
+	Thus we can estimate that 
+	\begin{align*}
+	| \delta_\beta(v)-\wt\delta_\beta(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 \\
+	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 \\
+	& \le v^2 n_1^2 \left[\left( \al_+(\rho_1) + \OO(p^{-1/2+\e})\right)^2-1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2,
+	\end{align*}
+	which concludes the proof by the definition of $\delta_\e$.	
+%	we can bound the second term on the RHS of equation \eqref{eq_lem_model_shift_1} as
+%	\begin{align*}
+%		& \bigabs{(\beta_s -  \beta_t)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - v\beta_t)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 \\
+%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}}} \\
+%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t) (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \\
+%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
+%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2 \tag{since the matrix inside is rank 1}
+%	\end{align*}
+%	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
+%	\begin{align*}
+%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_s - v\beta_t)}^2
+%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s -  \beta_t)}^2.
+%	\end{align*}
+%	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
+%	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
+%	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
+\end{proof}
+Note by \eqref{eq_isometric}, we have with high probability,
+\begin{align*}
+&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} = \hat M\frac{1}{(\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^2}\hat M^\top \\
+&\preceq  n_1^2 \hat M\frac{1}{\left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) - \OO(p^{-1/2+\e})\right]^2}\hat M^\top \\
+&\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + 2\left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
+&\prec [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1} - c
+\end{align*}
+for some small enough constant $c>0$. Together with Lemma \ref{prop_model_shift}, we get
+\be\label{bounddelta-}
+\left| \delta_\beta(v)-\wt\delta_\beta(v)\right| 
+		\le (\al_+^2(\rho_1)-1) \left[\frac{1}{\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)}  - \frac{c}{2}\right]\cdot \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 :=\delta(v)
+\ee
+with high probability.
+
+\paragraph{Step III: The limit of $\wt\delta_\beta(v)$.}
+Using Lemma \ref{lem_cov_derivative} with $\Sigma_1$ and $M$ replaced by $v^2\Sigma_1$ and $\hat M$, respectively, we obtain that 
+\begin{align*}
+\wt\delta_\beta &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_s-v\beta_t)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 + \hat a_3)\id + \hat a_4 \hat{M}^{\top}\hat{M}}{(a_2 + a_1 \hat{M}^{\top}\hat{M})^2} \Sigma_2^{-1/2} \Sigma_1(\beta_s-v\beta_t) +\OO(p^{-1/2+\e}) \\
+&= (\beta_s - {v}\beta_t)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_s - {v}\beta_t) +\OO(p^{-1/2+\e}) =: \Delta_\beta(v) +\OO(p^{-1/2+\e}).
+\end{align*}
+Together with and \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that 
+\be\label{dicho_varbeta}
+\begin{cases}\delta_{\vari}(v)>\delta_{\beta}(v), & \text{ if } \Delta_{\vari}(v) - \Delta_{\beta}(v) \ge   \delta(v),\\
+\delta_{\vari}(v)<\delta_{\beta}(v),  & \text{ if }  \Delta_{\vari}(v) - \Delta_{\beta}(v) \le -  \delta(v).\end{cases}
+\ee
+
+\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result to $v=\hat v$, which is random and depend on $X_1$ and $X_2$.
+We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} hold uniformly for all $v\in [0, C_0]$.
+In fact, for a large constant $C_1>0$, we consider $v$ belonging to a discrete set
+$$V:=\{v_k = kN^{-C_1}: 1\le k \le C_0N^{C_1}+1\}.$$
+Then using the arguments for the first three steps, we get that
+\eqref{dicho_varbeta} holds simultaneously for all $v\in V$ with high probability. On the other hand, by \eqref{eq_isometric} the event
+$$\Xi_1:=\left\{ \al_-(\rho_1)/2 \preceq  \frac{Z_1^T Z_1}{n_1}  \preceq   2\al_+(\rho_1) ,\  \al_-(\rho_2)/2 \preceq  \frac{Z_2^T Z_2}{n_2}  \preceq   2\al_+(\rho_2)\right\}$$
+holds with high probability. Now it is easy to check that on $\Xi_1$, for all $v_k \le v\le v_{k+1}$ we have the following estimates:
+\begin{align*}
+& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|=\OO(N^{-C_0}),\quad |\delta_{\beta}(v) -\delta_{\beta}(v_k)|=\OO(N^{-C_0}), \quad |\delta(v)-\delta(v_k)|=\OO(N^{-C_0}),\\
+& |\Delta_{\beta}(v) -\Delta_{\beta}(v_k)|=\OO(N^{-C_0}),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|=\OO(N^{-C_0}).
+\end{align*}
+Then a simple application of triangle inequality gives that the event 
+$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }0\le v \le C_0\}$$
+holds with high probability. On the other hand, on $\Xi_1$ one can see that for any small constant $\e>0$,
+\begin{align*}
+& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e,\quad |\delta_{\beta}(v) -\delta_{\beta}(C_0)|\le \e, \quad |\delta(v)-\delta(C_0)|\le \e,\\
+& |\Delta_{\beta}(v) -\Delta_{\beta}(C_0)|\le \e,\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e,
+\end{align*}
+for all $v\ge C_0$ as long as $C_0$ is chosen large enough depending on $\e$.
+Together with the estimate at $C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\ge 0$ on he high probability event $\Xi_1\cap \Xi_2$.
+This concludes the proof since $v$ must be one of the positive values.
+\end{proof}
+
+{\cor add some remarks about the difficulty in random matrix theory}
+
+By replacing \eqref{bounddelta-} with a tighter bound in Step II of the above proof, we can conclude the proof Lemma \ref{prop_model_shift_tight}.
+
+\begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
+the proof for tighter bound ...........
+
+\begin{lemma}\label{prop_model_shift222}
+	In the setting of Lemma \ref{prop_model_shift}, assume that $\Sigma_1 = \id$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$. Then we have
 	\begin{align*}
@@
 	\end{align*}
-\end{proposition}
+\end{lemma}
 
-\begin{proof}
-	The proof follows by applying equation \eqref{eq_isometric}.
-	Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
-	Denote by $\cE = Z_1^{\top}Z_1 - {n_1}\id$.
-	Let
-%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_s - \hat{w}\beta_t)}^2$.
-	We have
-	\begin{align}
-%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \hat{w}\beta_t)}^2 \nonumber \\
-		\delta_1 = \delta_2 + {2\hat{w}^2n_1}(\beta_s - \hat{w}\beta_t)^{\top}\Sigma_1^{1/2}\cE\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)
-		+ \hat{w}^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2 \label{eq_lem_model_shift_1}
-%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
-	\end{align}
-	Here we use the following on the second term in equation \eqref{eq_lem_model_shift_1}
-	\begin{align*}
-		& \bigabs{(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)} \\
-		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}}} \\
-		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t) (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \\
-		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
-		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2 \tag{since the matrix inside is rank 1}
-	\end{align*}
-	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
-	\begin{align*}
-		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2
-		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.
-	\end{align*}
-	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
-	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
-	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
-\end{proof}
-
-\paragraph{Part II: The limit of $\bignorm{\Sigma_2^{1/2} (\hat{w}^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1 (\beta_s - \hat{w}\beta_t)}^2$ using random matrix theory.}
-We consider the same setting as in previous subsection:
-$$ X_1^{\top}X_1:=\Sigma_1^{1/2}  Z_1^T Z_1 \Sigma_1^{1/2} ,\quad X_2^{\top}X_2= \Sigma_2^{1/2}  Z_2^T Z_2 \Sigma_2^{1/2},$$
-where $z_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying \eqref{eq_12moment}.
-For now, we assume that the random variables $z_{ij}$ are i.i.d.
-Gaussian, but we know that universality holds for generally distributed entries.
-Assume that $p/n_1$ is a small number such that $Z_1^TZ_1$ is roughly an isometry, that is, under \eqref{eq_12moment},
-%\todo{
-%\begin{align}\left\| Z_1^T Z_1 -  \frac{n_1}{n} I \right\| \le 2\sqrt{\frac{p}{n}} + {\frac{p}{n}} .
-%\end{align}}
-{\color{blue}
-If we assume the variances of the entries of $Z_1$ are $1$, then we have
-\begin{align}
-- {n_1} \left(2\sqrt{\frac{p}{n_1}} - {\frac{p}{n_1}}\right)  \le {Z_1^T Z_1 -  n_1 \id}  \le {n_1} \left(2\sqrt{\frac{p}{n_1}} + {\frac{p}{n_1}}\right) . \label{eq_isometric}
-\end{align}
-}
-
-\paragraph{Part III: An $\e$-net argument.}
-
-{\cor add some arguments with $\e$-net.}
-\end{proof}
-
-{\cor add some remarks about the difficulty in random matrix theory}
-
-By applying a tighter bound to Part I of the above proof, we can conclude the proof Lemma \ref{prop_model_shift_tight}.
-
-\begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
-the proof for tighter bound ........... 
 \end{proof}

### 2020-05-31 writeup/setup.tex

@@
 		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\bignorm{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}^2}. \]
-In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
+In order to study the tradeoff between model shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
 For this purpose, we consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
@@
 
-We term equation \eqref{eq_te_model_shift} as \textit{model-shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
+We term equation \eqref{eq_te_model_shift} as \textit{model shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
 This part introduces a negative effect to multi-task learning.
@@
 \squishend
-After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the transfer learning estimator for the target task.
-%By comparing $\te(\hat{\beta}_t^{\TL})$ to $\te(\hat{\beta}_t^{\STL})$, we observe a similar trade-off between model-shift bias and variance reduction for this setting.
-%We use our tools to compare $\te(B W_t)$ to $\te(\beta_t^{\STL})$.
+After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the transfer learning (TL) estimator for the target task.
+Our result naturally applies to $\hat{\beta}_t^{\TL}$.
+Interestingly, we show that the model shift bias is simply the projection of $\beta_t$ to the orthogonal subspace of $B^{\star} = [\beta_1,\dots,\beta_{t-1}]$, or $\norm{\Sigma_t^{1/2}(\id - B^{\star}({B^{\star}}^{\top}B^{\star})^{-1}{B^{\star}}^{\top})}$ more precisely.
 The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.

### 2020-05-31 writeup/setup.tex
sec 2

@@
 		This forms a shared representation $\hat{B} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
-	\item Fine-tuning on the target task: we learn the output layer $W_t\in\real^{t-1}$ for the target task similar to equation \eqref{eq_mtl}
+	\item Fine-tuning on the target task: we learn the output layer $W_t\in\real^{t-1}$ similar to equation \eqref{eq_mtl}
 		\begin{align}
@@
 Our result naturally applies to $\hat{\beta}_t^{\TL}$.
-Interestingly, we show that the model shift bias is simply the projection of $\beta_t$ to the orthogonal subspace of $B^{\star} = [\beta_1,\dots,\beta_{t-1}]$, or $\norm{\Sigma_t^{1/2}(\id - B^{\star}({B^{\star}}^{\top}B^{\star})^{-1}{B^{\star}}^{\top})}$ more precisely.
+Interestingly, we show that the model shift bias is simply the projection of $\beta_t$ to the orthogonal subspace of $B^{\star} = [\beta_1,\dots,\beta_{t-1}]$, or $\norm{\Sigma_t^{1/2}(\id - B^{\star}({B^{\star}}^{\top}B^{\star})^{-1}{B^{\star}}^{\top})\beta_t}^2$ more precisely.
 The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.

### 2020-05-31 writeup/transfer.tex
sec 2
sec 3 wip

@@
-\section{Understanding Negative Transfer and Their Algorithmic Implications}\label{sec_insight}
+\section{Explaining the Phenomena of Negative Transfer in Multi-Task Learning}\label{sec_insight}
 
-Based on the key lemma, we explain three contributing factors of negative transfer, including task dissimilarity, large source data size and covariate shift.
-For each factor, we show how negative transfer occurs using a simplified isotropic model.
-Then, we describe the algorithmic implication of the theory.
+Based on the key lemma, we provide rigorous explanations to the phenomena of negative transfer in multi-task learning.
+We study three components, including task model, data size and covariate shift.
+For each component, we show how negative transfer occurs using a simplified isotropic model.
+Then, we describe the algorithmic consequence of the theory.
 
-\subsection{Task Similarity}\label{sec_similarity}
+\subsection{Task Model}\label{sec_similarity}
 

### 2020-05-31 writeup/transfer.tex
sec 3

@@
 \end{align*}
-Let $\alpha_{-} = (1 - \rho_1^{-1/2})^4$ and $\alpha_{+} = (1 + \rho_1^{-1/2})^4$.
+Let $\gamma_{-} = (1+o(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+o(1))(1 + \rho_1^{-1/2})^4$.
+Concretely, if $\rho_1 > 40$, then $\gamma_{-} < 2$ and $\gamma_{+} > 1/2$.
 
@@
 	\squishlist
-		\item If $\Psi(\beta_1, \beta_2) < \alpha_{-} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) \ge \alpha_{+} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) < \gamma_{-} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) \ge \gamma_{+} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 	\squishlist
-		\item If $\rho_1 < \frac{\rho_2-2}{\alpha_+ \cdot \Phi(\beta_1, \beta_2) (\rho_2 - 1) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\rho_1 > \frac{\rho_2-2}{\alpha_- \cdot \Phi(\beta_1, \beta_2) (\rho_2 - 3) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\rho_1 < \frac{\rho_2-2}{\gamma_+ \cdot \Psi(\beta_1, \beta_2) (\rho_2 - 1) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\rho_1 > \frac{\rho_2-2}{\gamma_- \cdot \Psi(\beta_1, \beta_2) (\rho_2 - 3) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 %More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
+For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $x \cdot n_i$ datapoints from every task.
 The data efficiency ratio is defined as
@@
 \begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
-	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 2\Psi(\beta_1, \beta_2)}}. \]
+	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
+	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 5\Psi(\beta_1, \beta_2)}}. \]
 \end{proposition}

### 2020-05-31 writeup/transfer.tex
sec 3 wip

@@
 
-\begin{proposition}[Task dissimilarity]\label{prop_dist_transition}
+\begin{proposition}[Model dissimilarity]\label{prop_dist_transition}
 	In the isotropic model, suppose that $\rho_1 > 1$ and $\sigma_1 = \sigma_2 = \sigma$.
@@
 		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
-		\caption{Model dissimilarity}
+		\caption{Task model}
 		\label{fig_model_shift}
@@
 		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
-		\caption{Large source task data size}
+		\caption{Data size}
 	\end{subfigure}\hfill
@@
 
-\subsection{Data Size and Efficiency}
+\subsection{Data Size}
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
@@
 
-\begin{proposition}[Source data size]\label{prop_data_size}
+\begin{proposition}[Unnecessary source data]\label{prop_data_size}
 	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.

### 2020-05-31 writeup/app_exp.tex

--- 2020-05-30 writeup/experiments.tex
@@
-\section{Experiments}
+\section{Supplementary Materials for the Experiments}
 
-We validate the algorithmic implications of our theory on image and text classification tasks.
-First, we show that our proposed metric is able to predict positive or negative transfer using only STL performances.
-Second, we show that MTL can improve data efficiency ratio.
-Finally, we show that performing covariance alignment is more significant when the source task data size is large compared to the target task.
-
-\subsection{Experimental Setup}
-
-{\bf Datasets and models.} We describe the datasets and models we use in the experiments.
-
-{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
-
-{For each task, the goal is to categorize sentiment opinions expressed in the text.
-We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}.
-}
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-
-{\it ChestX-ray14:} This dataset contains 112,120 frontal-view X-ray images and each image has up to 14 diseases.
-This is a 14-task multi-label image classification problem.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-
-For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.
-
-\subsection{Improving training efficiency in MTL}
-
-\subsection{Validating the Algorithmic Implications}
-
-\textbf{A metric to determine positive or negative transfer.}
-We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
-Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among 150 task pairs for the sentiment analysis tasks with $38.8\%$ recall.
-Similar for 91 image classification task pairs.
 Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.
-
-\begin{table}
-\begin{center}
-  \begin{tabular}{c c c c c}
-  \toprule
-    \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-    & Precision &  Recall & Precision &  Recall \\
-    \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-    0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-    0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
-    0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
-    0.3 & 1.000 & 0.004 &     - &     - \\
-  \bottomrule
-  \end{tabular}
-\end{center}
-\caption{Ablation study on when should use MTL via different source/target task accuracy.}
-\label{tab:mtl_better_than_stl}
-\end{table}
-
-\textbf{MTL improves labeled data efficiency.}
-We measure the data efficiency ratio on the sentiment analysis tasks.
-We find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks.
-If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-\textbf{Covariance alignment.}
-We validate that the performance of aligning task covariances depends on the size of source task data.
-In Figure \ref{fig_covariate}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.
 
@@
 	\centering
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-		\caption{Averaged}
-	\end{subfigure}\hfill
 	\begin{subfigure}[b]{0.33\textwidth}
@@
 \end{figure}
-
-%\subsection{Validating Theoretical Implications}
-
-%\textbf{Contributing causes of negative transfer.}
-
-%\textbf{Implications for positive learning.}
-
-%\textit{Transferring from a high accuracy to low accuracy.}%%%%%%%%
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{c c c c c}
-		\toprule
-		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-		& {\bf Standard} & {\bf Alignment} & {\bf Standard} & {\bf Alignment} \\
-		\midrule
-		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-		% {\bf CNN}  & 76\% & - & 32\% & -\\
-		\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Taskonomy experiment.}
-	\label{tab:taskonomy}
-	\end{table}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mlp.pdf}
-%	\caption{Covariate shift experiment.}
-%\end{figure}

### 2020-05-31 writeup/experiments.tex

@@
 
-We validate the algorithmic implications of our theory on image and text classification tasks.
-First, we show that our proposed metric is able to predict positive or negative transfer using only STL performances.
-Second, we show that MTL can improve data efficiency ratio.
-Finally, we show that performing covariance alignment is more significant when the source task data size is large compared to the target task.
+Our theory leads to algorithmic consequences of practical interest.
+First, we show that the diagnosis metric that we proposed in Section \ref{sec_similarity} can help predict positive or negative transfer using only STL performances.
+Second, \todo{}.
+Finally, we validate the three components of our theory on image and text classification tasks.
 
@@
 
-\textbf{A metric for the diagnosis of MTL.}
-We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
-Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among 150 task pairs for the sentiment analysis tasks with $38.8\%$ recall.
-Similar for 91 image classification task pairs.
-Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.
+\textbf{A single-task based diagnosis metric.}
+We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on single-task accuracies.
+Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
+We find that using a threshold of $0.1$, our predicts correctly predicts positive or negative transfer with $75.6\%$ accuracy among 150 task pairs with $38.8\%$ recall.
+We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
+The result shows that STL performances are indicative for the diagnosis of MTL performances.
 
@@
 
-\textbf{Data size and efficiency.}
+\textbf{Data size.}
+Recall that 
 We measure the data efficiency ratio on the sentiment analysis tasks.
@@
 		\caption{Averaged}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-		\caption{Task pair TREC and CR}
-	\end{subfigure}\hfill
-		\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-		\caption{Task pair MR and SST}
 	\end{subfigure}

### 2020-05-31 writeup/transfer.tex
add procedure

@@
 
-\textbf{Algorithmic consequence.} \todo{}
+\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that the $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho$.
+Instead, from the analysis, we observe that $L(\hat{\beta}_t^{\MTL})$ is quadratic.
+Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
+Algorithm \ref{alg_inc_train} shows the procedure.
 
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for multi-task learning}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\State as
+	\end{algorithmic}
+\end{algorithm}
 \subsection{Covariate Shift}

### 2020-05-31 writeup/setup.tex
sec 3 wip
minor

@@
 
-\subsection{Applying the Key Lemma to Analyze the Tradeoff}
+\subsection{Applying the Key Lemma to Analyze the Bias-Variance Tradeoff}
 
@@
 \begin{theorem}[Informal statement of Theorem \ref{thm_model_shift}]\label{thm_main_informal}
-	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \kappa(M)^4 \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
+	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$.
 	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that

### 2020-05-31 writeup/experiments.tex
wip
sec 4

@@
 Finally, we validate the three components of our theory on image and text classification tasks.
-
-\subsection{Experimental Setup}
-
-{\bf Datasets and models.} We describe the datasets and models we use in the experiments.
-
-{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
-
-{For each task, the goal is to categorize sentiment opinions expressed in the text.
-We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}.
-}
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-
-{\it ChestX-ray14:} This dataset contains 112,120 frontal-view X-ray images and each image has up to 14 diseases.
-This is a 14-task multi-label image classification problem.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-
-For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.
-
-\subsection{Experimental Results}
-
-\textbf{A single-task based diagnosis metric.}
-We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on single-task accuracies.
-Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
-We find that using a threshold of $0.1$, our predicts correctly predicts positive or negative transfer with $75.6\%$ accuracy among 150 task pairs with $38.8\%$ recall.
-We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
-The result shows that STL performances are indicative for the diagnosis of MTL performances.
-
-\textbf{Improving training efficiency via an incremental schedule.}
-\todo{}
-
-\subsection{Ablation Studies}
-
-\textbf{Task similarity.} \todo{}
 
@@
 
-% \begin{table}
-% \begin{center}
-%   \begin{tabular}{c c c c c}
-%   \toprule
-%     \multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%     & Precision &  Recall & Precision &  Recall \\
-%     \cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%     0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%     0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
-%     0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
-%     0.3 & 1.000 & 0.004 &     - &     - \\
-%   \bottomrule
-%   \end{tabular}
-% \end{center}
-% \caption{Ablation study on when should use MTL via different source/target task accuracy.}
-% \label{tab:mtl_better_than_stl}
-% \end{table}
+\subsection{Experimental Setup}
 
-\textbf{Data size.}
-Recall that 
+{\bf Datasets and models.} We describe the datasets and models we use in the experiments.
+
+{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
+
+{For each task, the goal is to categorize sentiment opinions expressed in the text.
+We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}.
+}
+%multi-layer perceptron (MLP), LSTM, CNN on all tasks
+%We use this task to verify our theoretical results on model capacity and task covariance in real world.
+
+{\it ChestX-ray14:} This dataset contains 112,120 frontal-view X-ray images and each image has up to 14 diseases.
+This is a 14-task multi-label image classification problem.
+%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
+%This dataset is curated where the labels
+%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
+
+For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.
+
+\subsection{Experimental Results}
+
+\textbf{A single-task based diagnosis metric.}
+We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on single-task accuracies.
+Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
+We find that using a threshold of $0.1$, our predicts correctly predicts positive or negative transfer with $75.6\%$ accuracy among 150 task pairs with $38.8\%$ recall.
+We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
+The result shows that STL performances are indicative for the diagnosis of MTL performances.
+
+\textbf{Improving training efficiency via an incremental schedule.}
+\todo{}
+
+\textbf{MTL improves labeled data efficiency.}
 We measure the data efficiency ratio on the sentiment analysis tasks.
@@
 
+\subsection{Ablation Studies}
+
+\textbf{Task similarity.} \todo{}
+
+\textbf{Data size.}
+Recall that Proposition \ref{prop_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+In Figure \ref{fig_ab_data}, we observe that for the task pair MR and SST, increasing the data size of MR is helpful initially, but then gets worse.
+
 \textbf{Covariate shift.}
 We validate that the performance of aligning task covariances depends on the size of source task data.
-In Figure \ref{fig_covariate}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.
+In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
 	\centering
@@
 		\centering
+		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_sst_trec_lstm.pdf}
+		\caption{Data size}
+		\label{fig_ab_data}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
 		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-		\caption{Averaged}
+		\caption{Covariate shift}
+		\label{fig_ab_cov}
 	\end{subfigure}
@@
 As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
-	\label{fig_covariate}
+	\label{fig_ablation}
 \end{figure}
-
-%\subsection{Validating Theoretical Implications}
-
-%\textbf{Contributing causes of negative transfer.}
-
-%\textbf{Implications for positive learning.}
-
-%\textit{Transferring from a high accuracy to low accuracy.}%%%%%%%%
-
-% \begin{table}
-% 	\begin{center}
-% 		\begin{tabular}{c c c c c}
-% 		\toprule
-% 		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-% 		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-% 		\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-% 		& {\bf Standard} & {\bf Alignment} & {\bf Standard} & {\bf Alignment} \\
-% 		\midrule
-% 		{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-% 		{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-% 		% {\bf CNN}  & 76\% & - & 32\% & -\\
-% 		\bottomrule
-% 		\end{tabular}
-% 	\end{center}
-% 	\caption{Taskonomy experiment.}
-% 	\label{tab:taskonomy}
-% 	\end{table}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_mlp.pdf}
-%	\caption{Covariate shift experiment.}
-%\end{figure}

### 2020-05-31 writeup/proof_main.tex

@@
 Finally, we introduce the error term
-\be\label{eq_deltaextra}\delta:=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\lambda_{\min}^2(\hat M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,\ee
+\be\label{eq_deltaextra}\delta\equiv \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\lambda_{\min}^2(\hat M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_s - \hat{v}\beta_t)}^2,\ee
 where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.

### 2020-05-31 writeup/transfer.tex

@@
 \begin{align*}
-	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
+	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
 \end{align*}
-Let $\gamma_{-} = (1+o(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+o(1))(1 + \rho_1^{-1/2})^4$.
+Let $\gamma_{-} = (1-\oo(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+\oo(1))\cdot(1 + \rho_1^{-1/2})^4$.
 Concretely, if $\rho_1 > 40$, then $\gamma_{-} < 2$ and $\gamma_{+} > 1/2$.
@@
 \begin{proposition}[Unnecessary source data]\label{prop_data_size}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 500$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 150$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
 	We have that

### 2020-05-31 writeup/proof_main.tex
lem A.6

@@
 \begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
-the proof for tighter bound ...........
-
-\begin{lemma}\label{prop_model_shift222}
-	In the setting of Lemma \ref{prop_model_shift}, assume that $\Sigma_1 = \id$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$. Then we have
+For any fixed $v\ge 0$, $\beta_s - v\beta_t$ is a random vector with i.i.d.
+entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
+Then using the concentration Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
+\begin{align}
+&\left|\delta_{\beta}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&=  \left|(\beta_s - {v} \beta_t)^\top \cal K^\top \cal K (\beta_s - {v} \beta_t) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&\le p^\e [(1-v)^2\kappa^2 + d^2] \tr^{1/2} \left[(\cal K^\top \cal K)^2\right] \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
+\end{align}
+where we denoted $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}.
+Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
 \begin{align*}
-		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}
-		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \beta_t)}^2.
+\wt \delta_\beta(v) =v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
 \end{align*}
-\end{lemma}
-
+Recalling that $\Sigma_1=\id$ and bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
+\be\label{anotherwtbeta}\wt \delta_\beta(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \wt \delta_\beta(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
+where 
+$$\wt\delta_\beta(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
+Note that $\wt\delta_\beta(v) \sim 1$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get 
+\be\label{replaceest}
+  \wt \delta_\beta(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\beta}(v)\le \wt \delta_\beta(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
+\ee
+Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Theorem \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
+We omit the details.
 \end{proof}

### 2020-05-31 writeup/intro.tex
sec 1

@@
 In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture.
-In the setting of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task learning, and extend the result to transfer learning.
-A key technical tool we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1, X_2$ in the setting of two tasks.
-	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task learning.
-	For example, we theoretically analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning.
+We consider multi-task learning in the setting of high-dimensional linear regression.
+First, we provide a sharp analysis of the bias-variance tradeoff for multi-task learning, and extend the result to the related setting of transfer learning.
+We develop a technical tool on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1, X_2$ in the setting of two tasks.
+Second, we apply our tool to rigorously explain when multi-task learning outperforms single-task learning.
+%And we theoretically analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning.
 %, which has been a key empirical finding in recent work.
@@
 %distribution with covariance matrix $\Sigma_i$.
-
 We focus on the hard parameter sharing architecture with a linear shared layer $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
@@
 
-To quantify the tradeoff more precisely, we develop a new technical tool that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which arises naturally from the setting of two tasks.
+Our first contribution is to develop a new technical tool that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which arises naturally from the setting of two tasks.
 Our result extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ for a single random matrix \cite{S07}.
 Furthermore, we provide a nearly optimal error bound, which may be of independent interest.
-Using the result, we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
+We apply our tool to both multi-task and transfer learning settings.
+We present the following results in Section \ref{sec_main}.
+\squishlist
+	\item We provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
 (i) two tasks with general covariance matrice; (ii) any number of tasks that have the same features (e.g. images).
-Finally, we apply our technical tool to the related setting of transfer learning.
-We pool learnt representations from source tasks into a shared body similar to $B$ in the hard parameter sharing architecture, which has also been used in Taskonomy by Zamir et al.'18 \cite{ZSSGM18}.
-For this setting, we show that the model shift bias can be captured by the orthogonal projection of $\beta_t$ to the subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-These results are presented more precisely in Section \ref{sec_main}.
+	\item We extend our result to transfer learning in the setting of high-dimensional linear regression.
+	We pool learnt source task representations into a shared body similar to $B$ in the hard parameter sharing architecture, as in Taskonomy by Zamir et al.'18 \cite{ZSSGM18}.
+	We show that the model shift bias can be captured by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+\squishend
 
-The tradeoff that we develop depends on the properties of each task such as its data size and covariance matrix.
-In Section \ref{sec_insight}, we use our technical tool to rigorously explain negative transfer in multi-task learning.
-We identify three factors including task similarity, data size and covariate shift.
+Our second contribution is to use our newly developed technical tool to rigorously explain negative transfer in multi-task learning.
+In Section \ref{sec_insight}, we identify three factors including task similarity, data size and covariate shift.
 \squishlist
@@
 \squishend
-We validate the above phenomena on text and image classification tasks.
-Based on the theory, we provide algorithmic implications for detecting and mitigating negative transfer.
+
+Our final contribution is to connect our theory to practical problems of interest.
 First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.

### 2020-05-31 writeup/intro.tex
sec 1

@@
 When does multi-task learning outperform single-task learning?
-In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture.
-We consider multi-task learning in the setting of high-dimensional linear regression.
-First, we provide a sharp analysis of the bias-variance tradeoff for multi-task learning, and extend the result to the related setting of transfer learning.
-We develop a technical tool on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1, X_2$ in the setting of two tasks.
+In this work, we address this question by studying the performance of predicting a particular task given multiple tasks.
+We consider a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
+First, for the setting of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff of multi-task learning estimators.
+We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
+We extend the result to the related setting of transfer learning.
 Second, we apply our tool to rigorously explain when multi-task learning outperforms single-task learning.
@@
 entries with mean zero and unit variance, and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-Let $n_i$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$, for every $1\le i\le t$.
-The label of task $i$ is given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes the ground truth parameters for task $i$ and $\varepsilon_i$ denotes i.i.d.
+Let $n_i$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
+The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d.
 random noise with mean zero and variance $\sigma^2$.
 Without loss of generality, let the $t$-th task denote the target task.
-We assume that the data size of task $t$ is a small constant $\rho_t > 1$ times $p$ to capture the need for more labeled data.
+Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
+Hence adding more labeled data can help improve its test performance.
 %We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
@@
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-For a target task $t$, let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task (MTL) estimator (defined precisely in Section \ref{sec_setup}).
-Let $\hat{\beta}_t^{\STL}$ denote the standard single-task (STL) estimator for task $t$.
+Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task (MTL) estimator for the target task.
+Let $\hat{\beta}_t^{\STL}$ denote the single-task (STL) estimator.
+We define these precisely in Section \ref{sec_setup}.
 We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
@@
 We revisit the bias-variance tradeoff of the multi-task estimator.
-Interestingly, we observe that the variance of $\hat{\beta}_t^{\MTL}$ is always smaller than that of $\hat{\beta}_t^{\STL}$, hence resulting in a positive effect of variance reduction.
-The bias of $\hat{\beta}_t^{\MTL}$, which we term as \textit{model shift bias}, results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
-Hence, the tradeoff between the variance reduction effect and model shift bias determines whether the transfer is positive.
+Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, hence resulting in a positive effect of variance reduction.
+The bias of the multi-task estimator results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
+Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
 
-Our first contribution is to develop a new technical tool that provides a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which arises naturally from the setting of two tasks.
-Our result extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ for a single random matrix \cite{S07}.
-Furthermore, we provide a nearly optimal error bound, which may be of independent interest.
-We apply our tool to both multi-task and transfer learning settings.
-We present the following results in Section \ref{sec_main}.
+Our first contribution is to develop a new technical tool for a quantity that arises naturally from the analysis of two tasks.
+Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ for the single-task setting \cite{S07}.
+Our analysis yields nearly optimal concentration error, which may be of independent interest.
+Using this tool, we show the following results in Section \ref{sec_main}.
 \squishlist

### 2020-05-31 writeup/proofs_sec3.tex
A.1
remarks

@@
 
-\textbf{Defining the multi-task learning estimator.} Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.
-Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+\textbf{Defining the multi-task learning estimator.} 
+{\cor We define $\hat{\beta}_t^{\MTL}$ by two steps:
+(i) minimizing $f(\cdot)$ over $B$;
+(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set.}
+\todo{add the missing steps about validation loss}
+
+Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
 \begin{align}
@@
 \begin{align*}
-	te(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
+	L(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{\Sigma_2(X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
 \end{align*}
@@
 Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
-Throughout the rest of this section, we shall say an event $\Xi$ holds with high probability (whp) if $\P(\Xi)\to 1$ as $p\to \infty$.
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
 
@@
 with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
-	\begin{align*}
+	\begin{align}
 		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12}
-	\end{align*}
+\label{eq_a12extra}
+	\end{align}
 \end{lemma}
@@
 &(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
-&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} \Sigma_2^{-1/2} \beta +\OO(n^{-1/2+\e}),
+&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}),
 \end{split}
@@
 with high probability, where $a_{3}$ and $a_4$ satisfy the following system of linear equations: 
-\begin{gather}
+\begin{gather}\label{eq_a34extra}
 		\left(\rho_2  a_2^{-2}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4

### 2020-05-31 writeup/setup.tex
sec 2

@@
 
-Recall that we have $t$ labeled tasks as the training dataset, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
+Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
 %Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d.
@@
 Without loss of generality, let the $t$-th task denote the target task.
-We consider a linear multi-task learning architecture by minimizing the following
+We consider the following linear multi-task learning architecture.
 \begin{align}
@@
 (i) minimizing $f(\cdot)$ over $B$;
-(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set.
+(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set, e.g. $O(p^{0.99})$ suffices.
 For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
@@
 The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
-The bias-variance trade-off \cite{HTF09} says
+The bias-variance tradeoff \cite{HTF09} says
 	\[ \te_t(\hat{\beta}) =
 		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\bignorm{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}^2}. \]
-In order to study the tradeoff between model shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
+In order to relate the tradeoff to properties of the data, we need tight concentration bounds for the bias and variance.
 For this purpose, we consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
 We focus on a setting where $\rho_t$ is small compared to $\set{\rho_i}_{i=1}^{t-1}$.
-This setting captures the need for adding more labeled data to reduce the test error of the target task.
+This setting captures the need for adding more labeled data to reduce the prediction loss of the target task.
 A well-known result for this setting states that $\te_t(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \tr[(X_t^{\top}X_t)^{-1}\Sigma_t]$ is concentrated around $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
 Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
-However, this result only applies to the single-task setting.
-Therefore, our goal is to extend this result to the multi-task setting.
+However, this result only applies to a single task.
+Therefore, our goal is to extend this result to multiple tasks.
 
@@
 
-We term equation \eqref{eq_te_model_shift} as \textit{model shift bias}, which captures how similar $\beta_1$ and $\beta_2$ are.
-This part introduces a negative effect to multi-task learning.
-Next, it is not hard to verify that equation \eqref{eq_te_var}, the variance of $\hat{\beta}_t^{\MTL}$, is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
-This part introduces a positive variance reduction effect to performing multi-task learning.
-Hence, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the tradeoff between two effects:
-(i) the positive effect from variance reduction;
-(ii) the negative effect from model shift bias.
-In order to analyze the tradeoff, we develop the following result, which provides a tight bound for equation \eqref{eq_te_var}.
+Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$, which captures how similar $\beta_1$ and $\beta_2$ are.
+Hence, the bias of $\hat{\beta}_t^{\MTL}$ introduces a negative effect from adding the source labels.
+Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, which is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+This part introduces a positive variance reduction effect from adding the source labels.
+Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined by the bias-variance tradeoff of
+(i) the negative effect from model shift bias.
+(ii) the positive effect from variance reduction;
+In order to analyze the tradeoff, we develop the following technical tool, which provides a tight bound for equation \eqref{eq_te_var}.
 
@@
 	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$.
-	There exists two deterministic functions $\Delta_{\beta}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
+	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
 	\squishlist
-		\item If $\Delta_{\vari} - \Delta_{\beta} \ge \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Delta_{\vari} - \Delta_{\beta} \le -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\bias} + \Delta_{\vari} < -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\bias} - \Delta_{\vari} > \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 
-Theorem \ref{thm_main_informal} shows that as the source task data size increases, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\vari} - \Delta_{\beta}$.
+Theorem \ref{thm_main_informal} shows that as the source task data size increases, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
 %determined by the covariate shift matrix and the model shift.
 %The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of $\Delta_{\vari}-\Delta_{\beta}$ can be complex (as is preivous generalization bounds for MTL), they admit interpretable forms for simplified settings.
+While the general form of the threshold can be complex (as is preivous generalization bounds for MTL), they admit interpretable forms for simplified settings.
 This will be the focus of Section \ref{sec_insight}.
@@
 \squishlist
-	\item Learning source task representations: we obtain $\hat{\beta}_i^{\STL}$ from each source task, for $1\le i \le t-1$.
+	\item \textit{Learning source task representations}: we obtain $\hat{\beta}_i^{\STL}$ from each source task, for $1\le i \le t-1$.
 		This forms a shared representation $\hat{B} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
-	\item Fine-tuning on the target task: we learn the output layer $W_t\in\real^{t-1}$ similar to equation \eqref{eq_mtl}
+	\item \textit{Fine-tuning on the target task}: we learn the output layer $W_t\in\real^{t-1}$ similar to equation \eqref{eq_mtl}
 		\begin{align}

### 2020-05-31 writeup/proof_main.tex

@@
 
-Now we first give a proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift}.
+Now we first give a proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
 
@@
 
-{\cor add some remarks about the difficulty in random matrix theory}
+One can see from the above proof that the main error, $\delta$, of Theorem \ref{thm_model_shift} comes from approximating $\delta_{\beta}$ by $\wt\delta_{\beta}$ in \eqref{bounddelta-}.
+In order to improve this estimate and obtain an exact asymptotic result as for the $\delta_{\vari}$ term, one needs to study the singular value distribution of the following random matrix:
+$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  {v}^2 .$$
+In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ has been studied in the name of Fisher matrices; see e.g.
+\cite{Fmatrix}.
+However, since $\cal X$ is not symmetric, it is known that its singular values are different from the eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix theory literature, and the study of the singular values of $\cal X + v^2$ will be even harder.
+We leave this problem to future study.
 

### 2020-05-31 writeup/intro.tex
sec 2

@@
 
-Our second contribution is to use our newly developed technical tool to rigorously explain negative transfer in multi-task learning.
-In Section \ref{sec_insight}, we identify three factors including task similarity, data size and covariate shift.
+Our second contribution is to use our newly developed tool to rigorously explain negative transfer in multi-task learning.
+In Section \ref{sec_insight}, we consider three factors including task model, data size and covariate shift.
 \squishlist
@@
 %	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-		\item Second, we consider the effect of uneven data sizes.
+		\item Second, we consider data size.
 	We begin by observing that adding more labeled data from the source task does not always improve performance.
-	Then, we theoretically analyze the benefit of multit-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy \cite{ZSSGM18}.
+	Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy \cite{ZSSGM18}.
 %	We define the \textit{data efficiency ratio} as the smallest $x$ such that if we only use an $$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.

### 2020-05-31 writeup/setup.tex
sec 2

@@
 For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
-For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample (prediction) loss as
+For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample prediction loss as
 	\begin{align*}
-		\te_t(\hat{\beta}) \define \exarg{x}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
-		= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t).
+		\te_t(\hat{\beta}) = \exarg{x}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
+		= \bignorm{\ex{\hat{\beta}} - \beta_t}^2 + \ex{\bignorm{\hat{\beta} - \ex{\hat{\beta}}}^2},
 	\end{align*}
+%= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t) \\
+which can be further decomposed as the bias-variance tradeoff.
 The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
-The bias-variance tradeoff \cite{HTF09} says
-	\[ \te_t(\hat{\beta}) =
-		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\bignorm{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}^2}. \]
 In order to relate the tradeoff to properties of the data, we need tight concentration bounds for the bias and variance.
@@
 
-As a remark, when there is only the target task, $\rho_1$ equals zero.
+\textbf{Remark.} When there is only the target task, $\rho_1$ equals zero.
 Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is a well-known result in random matrix theory \cite{S07}.

### 2020-05-31 writeup/setup.tex
sec 2

@@
 Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, which is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
-This part introduces a positive variance reduction effect from adding the source labels.
-Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined by the bias-variance tradeoff of
-(i) the negative effect from model shift bias.
-(ii) the positive effect from variance reduction;
+%This part introduces a positive variance reduction effect from adding the source labels.
+Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the bias-variance tradeoff!
+%(i) the negative effect from model shift bias.
+%(ii) the positive effect from variance reduction;
 In order to analyze the tradeoff, we develop the following technical tool, which provides a tight bound for equation \eqref{eq_te_var}.

### 2020-05-31 writeup/transfer.tex
sec 3 wip

@@
 
-Based on the key lemma, we provide rigorous explanations to the phenomena of negative transfer in multi-task learning.
-We study three components, including task model, data size and covariate shift.
-For each component, we show how negative transfer occurs using a simplified isotropic model.
-Then, we describe the algorithmic consequence of the theory.
+Based on Lemma \ref{lem_cov_shift_informal}, we rigorously explain the phenomena of negative transfer in multi-task learning.
+We explain from three perspectives, including \textit{task model}, \textit{data size} and \textit{covariate shift}.
+We show how negative transfer occurs as a result in a simplified model and describe the algorithmic consequence.
 
@@
 It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-As a warmup, we first describe an example that rigorously formalizes the connection using our setup.
+We formalize this connection in the following simplified setting.
 

### 2020-05-31 writeup/transfer.tex
fig 1

@@
 	\end{subfigure}
-	\caption{Three contributing causes of negative transfer:
-	(a) As model dissimilarity increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
-	(b) As source task data size increases, we observe a transition positive to negative transfer (Proposition \ref{prop_data_size}).
-	(c) As covariate shift becomes more severe (measured by increasing $\lambda$), test performance gets worse (Proposition \ref{prop_covariate}).}
+	\caption{Three takeaways of our theory in Section \ref{sec_insight}.
+	(a) As task model distance increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
+	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Proposition \ref{prop_data_size}).
+	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Proposition \ref{prop_covariate}).}
 	\label{fig_model_shift_phasetrans}

### 2020-05-31 writeup/transfer.tex
sec 3.1

@@
 	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma_i^2$, for $i=1,2$.
-	\footnote{For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.}
+	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{app_proof_sec3}.
 
-We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
-We derive a sharp threshold when positive transfer transitions to negative transfer, as model dissimilarity increases.
+In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+%We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
+Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
+{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
+Our result below will provide an explanation to this phenomenon.
 %Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
-Define the following functions
+We introduce the following notations.
 \begin{align*}
@@
 \end{align*}
-Let $\gamma_{-} = (1-\oo(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+\oo(1))\cdot(1 + \rho_1^{-1/2})^4$.
-Concretely, if $\rho_1 > 40$, then $\gamma_{-} < 2$ and $\gamma_{+} > 1/2$.
 
-\begin{proposition}[Model dissimilarity]\label{prop_dist_transition}
+\begin{proposition}[Task model distance]\label{prop_dist_transition}
 	In the isotropic model, suppose that $\rho_1 > 1$ and $\sigma_1 = \sigma_2 = \sigma$.
@@
 	\squishend
+	Here $\gamma_{-} = (1-\oo(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+\oo(1))\cdot(1 + \rho_1^{-1/2})^4$.
+	Concretely, if $\rho_1 > 40$, then $\gamma_{-} \in (1,2)$ and $\gamma_{+} \in (1/2, 1)$.
 \end{proposition}
@@
 Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
-\todo{} We illustrate the example with a simulation.
-We consider a setting where $p = 200$, $n_1 = 90p$, $n_2 = 30p$.
-We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
-Figure \ref{fig_model_shift} shows the result.
-We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-
-The proof of Proposition \ref{prop_dist_transition} involves two parts.
-First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-The proof, which is based on Theorem \ref{thm_main_informal}, can be found in Appendix \ref{app_proof_31}. %, which is based on our main result described later in Theorem \ref{thm_model_shift}.
+Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
+Prosposition \ref{prop_dist_transition} explains the transition observed in Figure \ref{fig_model_shift}.
+Note that there are several unexplained observations near the transition threshold $0$, which are caused by the concentration errors $\gamma_+, \gamma_-$.
+%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
+%Figure \ref{fig_model_shift} shows the result.
+%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
+%The proof of Proposition \ref{prop_dist_transition} involves two parts.
+%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
+%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
+The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}. %, which is based on our main result described later in Theorem \ref{thm_model_shift}.
 
@@
 \textbf{Algorithmic consequence.}
-We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
 Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-If $\sigma_1$ is too large, then the source task provides a negative transfer to the target.
-If $\sigma_1$ is small, then the transfer may be positive.
-Proposition \ref{prop_var_transition} formalizes the intuition.
-
-Based on the result, we propose a simple metric to determine whether multi-task learning performs better than single-task learning.
-The metric is as follows.
-First, we train 2 single-task models on 2 separate tasks.
-We take the prediction accuracy of the two tasks.
-Let $\tau$ be a fixed threshold.
-If the accuracy of the source task is higher than the accuracy of the target task by $\tau$, then we predict positive transfer.
-On the other hand, if the accuracy of the source task is lower than the accuracy of the target task by $\tau$, then we predict negative transfer.
+If $\sigma_1$ is too large, the source task provides a negative transfer to the target.
+If $\sigma_1$ is small, the source task is more helpful.
+We leave the result to the Appendix in Proposition \ref{prop_var_transition}.
+Inspired by the observation, we propose a single-task based metric to help understand MTL results using STL results.
+\squishlist
+	\item For each task, we train a single-task model.
+	Let $z_s$ and $z_t$ be the prediction accuracy of each task, respectively.
+	Let $\tau\in(0, 1)$ be a fixed threshold.
+	\item If $z_s - z_t > \tau$, then we predict that there will be positive transfer when combining the two tasks using MTL.
+	If $z_s - z_t < -\tau$, then we predict negative transfer.
+\squishend
 

### 2020-05-31 writeup/transfer.tex
sec 32

@@
 	\squishlist
-		\item If $\Psi(\beta_1, \beta_2) < \gamma_{-} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) \ge \gamma_{+} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) < \gamma_{-} \cdot \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) \ge \gamma_{+} \cdot \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 		\caption{Data size}
+		\label{fig_size}
 	\end{subfigure}\hfill
@@
 Using the isotropic model, we consider what happens if we vary the source task data size.
+Figure \ref{fig_size} provides a simulation result for such a setting.
+We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+Our result below explains this phenomenon.
 
-\begin{proposition}[Unnecessary source data]\label{prop_data_size}
+\begin{proposition}[Source/task data ratio]\label{prop_data_size}
 	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 150$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
@@
 	\squishlist
-		\item If $\rho_1 < \frac{\rho_2-2}{\gamma_+ \cdot \Psi(\beta_1, \beta_2) (\rho_2 - 1) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\rho_1 > \frac{\rho_2-2}{\gamma_- \cdot \Psi(\beta_1, \beta_2) (\rho_2 - 3) - 1}$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1 - 2\rho_2^{-1}}{\gamma_+ \cdot \Psi(\beta_1, \beta_2) (1 - \rho_2^{-1}) - \rho_2^{-1}}$, then w.h.p.
+$\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1 - 2\rho_2^{-1}}{\gamma_- \cdot \Psi(\beta_1, \beta_2) (1 - 3\rho_2^{-1}) - \rho_2^{-1}}$, then w.h.p.
+$\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
 \end{proposition}
-Proposition \ref{prop_data_size} shows that as the source data size increases, we observe a transition from positive to negative transfer.
-The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}, and can be found in Appendix \ref{app_proof_31}.
+Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the data ratio $n_1 / n_2$.
+From Figure \ref{fig_size}, we see that our result is able to explain the transition from positive to negative transfer.
+There are several unexplained observations near $y = 0$ caused by the errors $\gamma_-, \gamma_+$.
+The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_31}.
 
-We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
-This is formalized as follows.
-
-Given several tasks, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
+We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed from each task to achieve comparable performance to STL.
+Formally, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
 %More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
@@
 		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
-We quantify the data efficiency ratio of the isotropic model as follows.
 

### 2020-05-31 writeup/proof_main.tex
validation

@@
-\subsection{Proof of Two Tasks with General Covariance}\label{app_proof_main}
+\subsection{Proof for Two Tasks with General Covariance}\label{app_proof_main}
 
@@
 It shows that the information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
+For this theorem and next lemma, we assume that the entries of $\e_1$ and $\e_2$ have the same variance $\sigma_1^2=\sigma_2^2=\sigma^2$.
 
@@
 
-\subsection{Proof of Many Tasks with the Same Covariates}\label{app_proof_many_tasks}
+\subsection{Proof for Many Tasks with the Same Covariates}\label{app_proof_many_tasks}
 

### 2020-05-31 writeup/proofs_sec3.tex
validation

@@
 
+\subsection{The multi-task learning estimator}
 From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
-for the rest of the section, we shall consider the case when $r=1$ we are considering the case of two tasks.
-Here, equation \eqref{eq_mtl} simplifies to the following
+for the rest of the section, we shall consider the case of two tasks, where we need to take $r=1$. 
+Then equation \eqref{eq_mtl} simplifies to the following
 \begin{align}\label{eq_mtl_2task}
@@
 where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
-\begin{align*}
-	& \hat{B}(w_1, w_2) \\
-	=& (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
-	=& \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
-	=& \frac{1}{w_2}\bigbrace{\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_s - \frac{w_1^2}{w_2^2} \beta_t\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}}.
-\end{align*}
+\begin{align}
+	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
+	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
+	&= \frac{1}{w_2}\left[\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_s - \frac{w_1^2}{w_2^2} \beta_t\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+\nonumber
+\end{align}
 As a remark, when $w_1 = w_2 = 1$, we recover the linear regression estimator.
@@
 
-\textbf{Defining the multi-task learning estimator.} 
-{\cor We define $\hat{\beta}_t^{\MTL}$ by two steps:
-(i) minimizing $f(\cdot)$ over $B$;
-(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set.}
-\todo{add the missing steps about validation loss}
+Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N\}$ from task-$i$, $i=1,2$.
+With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N\times p}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
+Here we assume that $N_1$ and $N_2$ are of the same order and satisfy $N_1\sim N_2\ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
+Then we define the validation loss as
+\begin{align}\label{eq_mtl_2tasktilde}
+	\wt f(\hat B; w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
+\end{align}
+Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that $\wt f$ only depends on the ratio $v:=w_1/w_2$. Hence we will also write $\wt f(\hat B; v)$ in the following discussion.
 
-Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-\begin{align}
-		\val(\hat{B}; w_1, w_2)
-	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
-		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
-\end{align}
-Let $\hat{w_1}/\hat{w_2}$ be the global minimizer of $\val(\hat{B}; w_1, w_2)$.
-We will define the multi-task learning estimator for the target task as
+Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $\wt f(\hat B; v)$. We will define the multi-task learning estimator for the target task as
 	\[ \hat{\beta}_t^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2). \]
-
 The intuition for deriving $\hat{\beta}_t^{\MTL}$ is akin to performing multi-task training in practice.
-Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-The test loss of using $\hat{\beta}_t^{\MTL}$ for the target task is
+%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
+Then the test loss of using $\hat{\beta}_t^{\MTL}$ for the target task is
 \begin{align}
 	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
-			&+~  \sigma^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl_2task}
+			&+~  \sigma_2^2 \cdot \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }, \label{eq_te_mtl_2task}
 \end{align}
-
+which is well-defined since it only depends on $\hat v$, but otherwise does not depend on $\hat w_1$ or $\wh w_2$ separately.
 Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
@@
 \begin{align*}
-	L(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \bigtr{\Sigma_2(X_2^{\top}X_2)^{-1}}, \text{ where } \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
+	L(\hat{\beta}_t^{\STL}) = \sigma_2^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}, \ \text{ where } \ \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
 \end{align*}
@@
 
-We now state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$.
-Before that, we first need to fix the setting for the discussions in this section.
+One may observe that we can reduce $\wt f$ to an expression that is easier to handle using concentration of random vectors.
+Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+First, we give the basic assumptions for our main objects---the random matrices $X_i$, $i=1,2$.
 
@@
 \end{assumption}
-
 Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
@@
 
+Then we make the following assumptions on the data models.
+\begin{assumption}\label{assm_secA2}
+For $1\le i \le t$ for some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$ be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
+\end{assumption}
+
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+
+Now under Assumption \ref{assm_secA2} with $t=2$, we write \eqref{eq_mtl_2tasktilde} as
+$$	\wt f(\hat B; v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_1-\beta_i.$$
+Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration Lemma \ref{largedeviation} to get that for any constant $\e>0$,
+\begin{align*}
+\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - \wt{\E}\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 \right| =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+\end{align*}
+with high probability, where $\wt{\E}$ denotes the expectation with respect to $\wt X_i$ and $\wt\e_i$, $i=1,2$. Thus we obtain that 
+$$\wt f(B; v)= \left[\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using 
+the concentration result, Lemma \ref{largedeviation}, again, we obtain that
+$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(\hat B; v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+with high probability, where
+\begin{align*}
+		&\val(\hat{B}; v):= \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2} \\
+	&=  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - v\beta_t\right)}^2 \nonumber \\
+	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - v\beta_t\right)}^2 \nonumber \\
+		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\		
+		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{eq_val_mtl}
+\end{align*}
+%-----old-------
+%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+%\begin{align}
+%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
+%\end{align}
+%\nc
+%------------------
+In sum, we have obtained that 
+\be\label{approxvalid}
+\wt f(\hat B; v)=  \left[\val(\hat{B}; v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
+\ee
+Hence to minimize $\wt f$, it suffices to minimize $\val(\hat{B}; v)$ over $v$.
+
+We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$.
 The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p\to \infty$.
@@
 Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
-Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
-
 \begin{lemma}\label{lem_minv} 

### 2020-05-31 writeup/proof_examples.tex
sec 3.2

@@
 
+\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
+	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
+	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 5\Psi(\beta_1, \beta_2)}}. \]
+\end{proposition}
+
 \begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]

### 2020-05-31 writeup/transfer.tex
sec 3.2

@@
 
-We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed from each task to achieve comparable performance to STL.
+\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
 Formally, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
@@
 		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
+Using our tools, we show that in the isotropic model, the data efficiency ratio is
+equal to \[ \frac{1}{\rho_1 + \rho_2} {+ \frac{1}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
+In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
+The result can be found in Appendix \ref{app_proof_data}.
 
-\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
-	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 5\Psi(\beta_1, \beta_2)}}. \]
-\end{proposition}
-The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
-
-\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that the $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho$.
-Instead, from the analysis, we observe that $L(\hat{\beta}_t^{\MTL})$ is quadratic.
+\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
+In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
+More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
 Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-Algorithm \ref{alg_inc_train} shows the procedure.
+Algorithm \ref{alg_inc_train} describes the procedure.
 
 \begin{algorithm}[!t]
-	\caption{An incremental training schedule for multi-task learning}
+	\caption{An incremental training schedule for multi-task learning over two tasks}
 	\label{alg_inc_train}
 	\begin{algorithmic}[1]
-		\State as
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req Batch size $S$, number of epochs $T$, validation accuracy $\hat{g}(B; W_1, W_2)$.
+		\State Divide $(X_1, Y_1)$ randomly into $K$ batches of size $S$ as $(x^{(1)}, y^{(1)}), \dots, (x^{(K)}, y^{(K)})$.
+		\For{$i = 1,\dots, K$}
+			\For{$j = 1,\dots, T$}
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(j)}, x^{(j)}}_{j=1}^i$ and  $(X_2, Y_2)$.
+			\EndFor
+		\State Let $a_i = \hat{g}(B; W_1, W_2)$ be the validation loss after epoch $i$.
+			If $a_i < a_{i+1}$, \textbf{break}.
+		\EndFor
 	\end{algorithmic}
 \end{algorithm}
+
 \subsection{Covariate Shift}

### 2020-05-31 writeup/proof_examples.tex
sec 3.3

@@
 
+To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
+\begin{align*}
+		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
+\end{align*}
+	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
+	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
+The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
+
+\begin{proposition}[Covariate shift]\label{prop_covariate}
+	In the setting described above, assume that $\rho_1, \rho_2>1$.
+	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
+	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
+\end{proposition}
+Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
+%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
+
+%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
+
 \begin{proof}[Proof of Proposition \ref{prop_covariate}]
@@
 %--------end old argument---------
+we observe the following two phases as we increase $n_1 / p$ in Figure \ref{fig_covariate}.
+When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
+When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
+We provide a theoretical justification below.
 

### 2020-05-31 writeup/transfer.tex
sec 3.3

@@
 			\EndFor
-		\State Let $a_i = \hat{g}(B; W_1, W_2)$ be the validation loss after epoch $i$.
-			If $a_i < a_{i+1}$, \textbf{break}.
+		\State Let $a_i = \hat{g}(B; W_1, W_2)$ be the validation accuracy after epoch $i$.
+			If $a_i < a_{i-1}$, \textbf{break}.
 		\EndFor
@@
 In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
+We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
 
+\begin{example}\label{ex_complement}
 	We measure covariate shift by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
-We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
-Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
-On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
-	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
-	\begin{align*}
-		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
-	\end{align*}
-	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
-	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-	The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
-
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	In the setting described above, assume that $\rho_1, \rho_2>1$.
-	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
-	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{proposition}
-Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
-\begin{example}\label{ex_complement}
-	In the setting of Proposition \ref{prop_covariate}, we compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	For simplicity, we assume that $d = 0$.
-	Hence the two tasks have the same model parameters.
-
-	In Figure \ref{fig_model_shift_phasetrans} (c), we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
-	Second, we observe the following two phases as we increase $n_1 / p$.
-	When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-	A theoretical justification can be found in Appendix \ref{app_proof_31}.
+	Assume that $\Psi(\beta_1, \beta_2) = 0$ for simplicity.
+	We compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+	Hence, $\lambda$ measures the severity of covariate shift.
+	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
 \end{example}
+%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
+%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
+%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
+%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
 

### 2020-06-01 writeup/experiments.tex
sec 1
sec 3

@@
 \textbf{Covariate shift.}
+Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+When the source task data size is particularly large compared to the target task, then we expect that applying the covariance alignment algorithm results in a more significant gain.
 We validate that the performance of aligning task covariances depends on the size of source task data.
@@
 	\centering
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
+		\caption{Task model}
+		\label{fig_ab_sim}
+	\end{subfigure}%
 	\begin{subfigure}[b]{0.33\textwidth}

### 2020-06-01 writeup/proofs_sec3.tex
revision

@@
 From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
-for the rest of the section, we shall consider the case of two tasks, where we need to take $r=1$. 
-Then equation \eqref{eq_mtl} simplifies to the following
+for the rest of the section, we shall consider the case of two tasks with $r=1$. 
+Then equation \eqref{eq_mtl} simplifies to 
 \begin{align}\label{eq_mtl_2task}
@@
 	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
-	&= \frac{1}{w_2}\left[\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_s - \frac{w_1^2}{w_2^2} \beta_t\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+	&= \frac{1}{w_2}\left[\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
 \nonumber
@@
 As a remark, when $w_1 = w_2 = 1$, we recover the linear regression estimator.
-The advantage of using $f(B; w_1, w_2)$ is that if $\theta_1$ is a scaling of $\theta_2$, then this case can be solved optimally using equation \eqref{eq_mtl_2task} \cite{KD12}.
+The advantage of using $f(B; w_1, w_2)$ is that if $\beta_1$ is a scaling of $\beta_2$, then this case can be solved optimally using equation \eqref{eq_mtl_2task} \cite{KD12}.
 
@@
 
-Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N\}$ from task-$i$, $i=1,2$.
+Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
 With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N\times p}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
-Here we assume that $N_1$ and $N_2$ are of the same order and satisfy $N_1\sim N_2\ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
+Here we assume that $N_1$ and $N_2$ satisfies $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
 Then we define the validation loss as
@@
 \begin{align}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
+	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
 			&+~  \sigma_2^2 \cdot \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }, \label{eq_te_mtl_2task}
 \end{align}
-which is well-defined since it only depends on $\hat v$, but otherwise does not depend on $\hat w_1$ or $\wh w_2$ separately.
-Our goal is to study under model and covariate shifts, whether multi-task learning helps learn the target task better than single-task learning.
+which is well-defined since it only depends on $\hat v$, but otherwise does not depend on $\hat w_1$ or $\hat w_2$ separately.
+Our goal is to study under model and covariate shifts, whether multi-task learning helps to learn the target task better than single-task learning.
 The baseline where we solve the target task with its own data is
 \begin{align*}
-	L(\hat{\beta}_t^{\STL}) = \sigma_2^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}, \ \text{ where } \ \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
+	L(\hat{\beta}_t^{\STL}) = \sigma_2^2 \cdot \bigtr{\Sigma_2(X_2^{\top}X_2)^{-1}}, \ \text{ where } \ \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
 \end{align*}
@@
 
-One may observe that we can reduce $\wt f$ to an expression that is easier to handle using concentration of random vectors.
+One may observe that we can reduce $\wt f$ to an expression that is easier to handle using concentration of random vectors with i.i.d.
+entries.
 Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-First, we give the basic assumptions for our main objects---the random matrices $X_i$, $i=1,2$.
+First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
 
 \begin{assumption}\label{assm_secA1}
-We will consider two $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrices, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
+We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrices, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
 entries with mean zero and variance one.
@@
 \begin{equation}\label{assmAhigh}
-\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, 1\le j \le p,
+\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p,
 \end{equation}
@@
 Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
-if the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in the error bounds.
+If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
 We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} below.
@@
 \begin{assumption}\label{assm_secA2}
-For $1\le i \le t$ for some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$ be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+For for some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
 Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
@@
 
-Now under Assumption \ref{assm_secA2} with $t=2$, we write \eqref{eq_mtl_2tasktilde} as
-$$	\wt f(\hat B; v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_1-\beta_i.$$
-Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration Lemma \ref{largedeviation} to get that for any constant $\e>0$,
+Now suppose $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
+$$	\wt f(\hat B; v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
+Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d.
+centered entries, we can use the concentration estimate, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
 \begin{align*}
-\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - \wt{\E}\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 \right| =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
+&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
 \end{align*}
-with high probability, where $\wt{\E}$ denotes the expectation with respect to $\wt X_i$ and $\wt\e_i$, $i=1,2$. Thus we obtain that 
-$$\wt f(B; v)= \left[\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+with high probability. Thus we obtain that 
+$$\wt f(B; v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
 where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using 
-the concentration result, Lemma \ref{largedeviation}, again, we obtain that
+ again the concentration result, Lemma \ref{largedeviation}, we obtain that
 $$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(\hat B; v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
@@
 \begin{align*}
-		&\val(\hat{B}; v):= \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2} \\
-	&=  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - v\beta_t\right)}^2 \nonumber \\
-	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - v\beta_t\right)}^2 \nonumber \\
+		&\val(\hat{B}; v):= \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
+	&=  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
+	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
 		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\		
@@
 We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-The second lemma extends Lemma \ref{lem_minv} for a single sample covariance matrices to the sum of two independent sample covariance matrices.
+The second lemma extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
 It is the main random matrix theoretical input of this paper.
@@
 	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$. 
+	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
 	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
@@
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}},
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
 	\end{align}
@@
 
-Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}$.
+Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which will be needed when we estimate the first term on the right-hand side of \eqref{eq_te_mtl_2task}.
 
 \begin{lemma}\label{lem_cov_derivative}
-In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any unit vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
+In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
 \begin{equation}\label{lem_cov_derv_eq}
@@
 &(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
-&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}),
+&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M})^2+a_2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
 \end{split}

### 2020-06-01 writeup/transfer.tex
prop 3.2

@@
 	\squishlist
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1 - 2\rho_2^{-1}}{\gamma_+ \cdot \Psi(\beta_1, \beta_2) (1 - \rho_2^{-1}) - \rho_2^{-1}}$, then w.h.p.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\gamma_+} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \gamma_+^{-1}}$, then w.h.p.
 $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1 - 2\rho_2^{-1}}{\gamma_- \cdot \Psi(\beta_1, \beta_2) (1 - 3\rho_2^{-1}) - \rho_2^{-1}}$, then w.h.p.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1}{\gamma_-} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3) - \gamma_{-}^{-1}}$, then w.h.p.
 $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
@@
 	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
+	We observe that as $n_1/n_2$ increases, the performance gap between the case of $M = \id$ and $\lambda = 2$ or $4$ increases for MTL.
 \end{example}
+
+By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
+The result is left to Appendix \ref{app_proof_31}.
 %We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
@@
 \textbf{Algorithmic consequence.}
-Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-When the source task data size is particularly large compared to the target task, then we expect that applying the covariance alignment algorithm results in a more significant gain.
+Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
+Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.

### 2020-06-01 writeup/transfer.tex
sec 3

@@
 Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
+We consider a covariance alignment procedure proposed in Wu et al.'20 \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
+The idea is to add an alignment module between the input and the shared module $B$.
+This new module is then trained together with $B$ and the output layers.
+We validate our insight on this procedure in the experiments.

### 2020-06-01 writeup/experiments.tex
sec 4.3

@@
 	\end{subfigure}
-	\caption{The performance of aligning task covariances depends on data size.
-As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
+	\caption{Validating the three takeaways of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
+	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
+	(c) As source/target data ratio increases, the performance gains from the covariance alignment procedure \cite{WZR20} increase for LSTM and MLP.}
 	\label{fig_ablation}

### 2020-06-01 writeup/experiments.tex
sec 4

@@
 
-Our theory leads to algorithmic consequences of practical interest.
-First, we show that the diagnosis metric that we proposed in Section \ref{sec_similarity} can help predict positive or negative transfer using only STL performances.
+We connect our theory to pratical problems of interest.
+First, we validate the single-task based metric on text and image classification tasks.
+We show that for both datasets, single-task learning results can help predict positive or negative transfer in multi-task learning.
 Second, \todo{}.
-Finally, we validate the three components of our theory on image and text classification tasks.
+Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
+Finally, we validate the three components of our theory in Section \ref{sec_insight} on text classification tasks.
 
@@
 	\vspace{0.1in}
-	\captionof{table}{Ablation study on when should use MTL via different source/target task accuracy.}
+	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
 	\label{tab:mtl_better_than_stl}
@@
 	\vspace{0.1in}
-	\captionof{table}{Taskonomy experiment.}
+	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
 	\label{tab:taskonomy}
@@
 
-\textbf{A single-task based diagnosis metric.}
-We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on single-task accuracies.
+\textbf{Understanding MTL results via STL results.}
+We show that STL results can be used to help understand MTL results
+We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
 Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
-We find that using a threshold of $0.1$, our predicts correctly predicts positive or negative transfer with $75.6\%$ accuracy among 150 task pairs with $38.8\%$ recall.
+We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among 150 task pairs.
 We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
-The result shows that STL performances are indicative for the diagnosis of MTL performances.
+The results show that STL performances are indicative of MTL performances.
 
@@
 We measure the data efficiency ratio on the sentiment analysis tasks.
-We find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks.
-If TREC is not included, we see that only $25\%$ of the labeled data is needed.
+In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
+We further observe that adding the alignment module helps reduce the data efficiency ratio on MLP.
+%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
 
@@
 
-\textbf{Task similarity.} \todo{}
+\textbf{Task similarity.} We validate that MTL performs better when the source task is more similar to the target task.
+We show the result on the sentiment analysis tasks.
+For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+Figure \ref{fig_ab_sim} confirms the result.
 
 \textbf{Data size.}
-Recall that Proposition \ref{prop_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-In Figure \ref{fig_ab_data}, we observe that for the task pair MR and SST, increasing the data size of MR is helpful initially, but then gets worse.
+Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
 
 \textbf{Covariate shift.}
-Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-When the source task data size is particularly large compared to the target task, then we expect that applying the covariance alignment algorithm results in a more significant gain.
-We validate that the performance of aligning task covariances depends on the size of source task data.
-In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
 
@@
 		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-		\caption{Task model}
+		\caption{Task similarity}
 		\label{fig_ab_sim}
@@
 	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
-	(c) As source/target data ratio increases, the performance gains from the covariance alignment procedure \cite{WZR20} increase for LSTM and MLP.}
+	(c) As source/target data ratio increases, the performance gains from the covariance alignment procedure \cite{WZR20} increase for LSTM and MLP.
+	The $y$-axis measures the performance of MTL minus STL.}
 	\label{fig_ablation}

### 2020-06-01 writeup/transfer.tex
sec 4.3
sec 4

@@
 Based on Lemma \ref{lem_cov_shift_informal}, we rigorously explain the phenomena of negative transfer in multi-task learning.
-We explain from three perspectives, including \textit{task model}, \textit{data size} and \textit{covariate shift}.
+We explain from three perspectives, including \textit{task similarity}, \textit{data size} and \textit{covariate shift}.
 We show how negative transfer occurs as a result in a simplified model and describe the algorithmic consequence.
 
-\subsection{Task Model}\label{sec_similarity}
+\subsection{Task Similarity}\label{sec_similarity}
 
@@
 		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
-		\caption{Task model}
+		\caption{Task similarity}
 		\label{fig_model_shift}
@@
 	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Proposition \ref{prop_data_size}).
-	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Proposition \ref{prop_covariate}).}
+	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Proposition \ref{prop_covariate}).
+	The $y$-axis measures the performance of MTL minus STL.}
 	\label{fig_model_shift_phasetrans}
@@
 
-\subsection{Data Size}
+\subsection{Data Size}\label{sec_data_size}
+
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.

### 2020-06-01 writeup/experiments.tex
alg 1

@@
 	\toprule
-		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text
-		classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
+		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
+		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
 		& Precision &  Recall & Precision &  Recall \\
@@
 		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-		0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
+		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
 		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
@@
 		\cmidrule(lr){2-3}
-		& {\bf Standard} & {\bf Alignment} \\
+		& {\bf MTL} & {\bf Alignment} \\
 		\midrule
-		{\bf MLP}  & > 100\% & 39\% \\
-		{\bf LSTM} & 36\% & 36\% \\
+		{\bf MLP}  & 100\% & \textbf{39\%} \\
+		{\bf LSTM} & \textbf{36\%} & 36\% \\
 		\bottomrule
@@
 {For each task, the goal is to categorize sentiment opinions expressed in the text.
-We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}.
+We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
 }
@@
 
+\textbf{Baseline.} We compare Algorithm \ref{alg_inc_train} to a model trained with standard multi-task learning approaches.
+
 \subsection{Experimental Results}
@@
 
-\textbf{Improving training efficiency via an incremental schedule.}
+\textbf{Improving multi-task training efficiency.}
+We compare Algorithm \ref{alg_inc_train} to performing multi-task learning.
+Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the cost to achieve the same performance on the target task, compared to multi-task learning.
+
+\textbf{Improving transfer learning training efficiency.}
 \todo{}
-
-\textbf{MTL improves labeled data efficiency.}
-We measure the data efficiency ratio on the sentiment analysis tasks.
-In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
-We further observe that adding the alignment module helps reduce the data efficiency ratio on MLP.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
 
@@
 
+\textbf{Data efficiency.}
+We measure the data efficiency ratio on the sentiment analysis tasks.
+In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
+The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
+We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
+%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
+
 \begin{figure}[!t]
@@
 		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_sst_trec_lstm.pdf}
+		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
 		\caption{Data size}
@@
 	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
-	(c) As source/target data ratio increases, the performance gains from the covariance alignment procedure \cite{WZR20} increase for LSTM and MLP.
-	The $y$-axis measures the performance of MTL minus STL.}
+	(c) As source/target data ratio increases, the performance gain from the covariance alignment procedure \cite{WZR20} over MTL increases for LSTM and MLP.}
 	\label{fig_ablation}

### 2020-06-01 writeup/transfer.tex
alg 1

@@
 \begin{algorithm}[!t]
-	\caption{An incremental training schedule for multi-task learning over two tasks}
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
 	\label{alg_inc_train}
@@
 		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req Batch size $S$, number of epochs $T$, validation accuracy $\hat{g}(B; W_1, W_2)$.
-		\State Divide $(X_1, Y_1)$ randomly into $K$ batches of size $S$ as $(x^{(1)}, y^{(1)}), \dots, (x^{(K)}, y^{(K)})$.
-		\For{$i = 1,\dots, K$}
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
 			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(j)}, x^{(j)}}_{j=1}^i$ and  $(X_2, Y_2)$.
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+				\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy after epoch $i$.
+				\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+					\State \textbf{break}
+				\EndIf
 			\EndFor
-		\State Let $a_i = \hat{g}(B; W_1, W_2)$ be the validation accuracy after epoch $i$.
-			If $a_i < a_{i-1}$, \textbf{break}.
 		\EndFor

### 2020-06-01 writeup/proof_examples.tex
revisions

@@
 
-\subsection{Proofs for Section \ref{sec_similarity}}\label{app_proof_31}
+\subsection{Supplement to Section \ref{sec_similarity}}\label{app_proof_31}
 
@@
 \end{align}
-Under the setting of Lemma \ref{prop_model_shift_tight}, again using concentration for random vectors with i.i.d.
-entries, Lemma \ref{largedeviation}, we can obtain that for the validation loss in \eqref{eq_val_mtl},
+\cor Under the setting of Lemma \ref{prop_model_shift_tight}, again using concentration for random vectors with i.i.d.
+entries, Lemma \ref{largedeviation}, we can obtain that for the validation loss in \eqref{approxvalid},
 \be\label{boundv-w}\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2+\e})\right)\ee
 with high probability for any constant $\e>0$.
-Thus for the following discussions, it suffices focus on the behavior of $\val (w)$.
+\nc Thus for the following discussions, it suffices focus on the behavior of $\val (w)$.
 Let $\hat w$ the minimizer of $\val(w)$.
@@
 
-Then we prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.
+\subsection{Supplement to Section \ref{sec_datasize}} \label{app_proof_32}
+We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.
 
@@
 
- Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is no model bias and enough source data.
+Then we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio, denoted as $x^\star$.
+
+\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
+	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
+	Then the data efficiency ratio $x^\star$ satifies 
+	\[ \al_l - \oo(1) \le x^\star\le \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}}, \]
+	where we denoted
+	$$\al_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
+\end{proposition}
+
+\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
+Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
+Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(\al\rho_1,\al\rho_2)$.
+More precisely, we have
+	\begin{align*}
+		 a_1 = \frac{\rho_1(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,\quad
+		& a_2 = \frac{\rho_2(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,  \\
+		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}, \quad
+		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}. 
+	\end{align*}
+Moreover, we have that with high probability,
+	\be\label{reduceproof1}
+\begin{split}
+\te_i(\hat \beta(\al)) =  \frac{\sigma^2}{\al (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\beta}, \quad i=1,2.
+\end{split}
+\ee
+Here the model shift biases $\delta^{(i)}_{\beta}$ satisfy that  
+\be\nonumber %\label{Deltabeta} 
+\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_\beta^{(i)}}/{ \Delta_{\beta}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2,\ee	
+%In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
+%%and by symmetry it suffices to focus on one of tasks, say task 2. 
+%Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
+%\be\label{reduceproof1}
+%\begin{split}
+%\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
+%\end{split}
+%\ee
+%and
+%\be\label{reduceproof1}
+%\begin{split}
+%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
+%\end{split}
+%\ee
+where $ \Delta^{(i)}_{\beta}$ are defined as 
+\be \nonumber
+\Delta^{(i)}_{\beta} := pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,. 
+\ee
+On the other hand, using Lemma \ref{lem_minv}, we have whp,
+\be\label{reduceproof2} 
+\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
+\ee
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
+$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
+In fact, one can see that if $\al\le \al_l$, then we have 
+$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
+that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\beta}$.
+Next we try to get more precise bounds on $\al^*$.
+In the following discussions, we only consider $\al$ such that $\al(\rho_1+\rho_2) \ge \al_l (\rho_1+\rho_2) \ge \min(\rho_1,\rho_2)$.
+
+%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+
+\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
+\be\nonumber
+\begin{split}
+&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
+&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
+\end{split}
+\ee
+We rewrite the inequality as
+\be
+\begin{split}\label{solval1}
+  (1+\oo(1)) \cdot \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{\al \rho}}}^4\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho  - 1},
+\end{split}
+\ee
+where we abbreviated $\rho:=\rho_1+\rho_2$.
+
+In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
+Thus the following inequality implies \eqref{solval1}:
+\be\label{solval1add}
+\begin{split}
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+In particular, if 
+\be\nonumber
+\begin{split}
+&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+\end{split}
+\ee
+that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
+\begin{align*}
+\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
+& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+
+\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
+\be\label{solval2}
+\begin{split}
+&(1-\oo(1)) \cdot  \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{\al \rho}}}^4 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho - 1} .
+\end{split}
+\ee
+We then follow similar arguments as the above proof for the upper bound.
+
+In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
+$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
+Thus the following inequality implies \eqref{solval2}:
+\be\label{solval2add}
+\begin{split}
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+\end{split}
+\ee
+There are two cases: if 
+\be\nonumber
+\begin{split}
+&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
+\end{split}
+\ee
+then we have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
+\begin{align*}
+\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
+& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+This concludes the proof.
+\end{proof}
+
+\subsection{Supplement to Section \ref{sec_covshift}}\label{app_proof_33}
+
+% Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is no model bias and enough source data.
 
@@
 
-\subsection{Proofs for Section \ref{sec_benefit}}\label{app_proof_data}
-
- We first prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio.
-
-\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
-	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 5\Psi(\beta_1, \beta_2)}}. \]
-\end{proposition}
-
-\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
-Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(\al\rho_1,\al\rho_2)$.
-More precisely, we have
-	\begin{align*}
-		 a_1 = \frac{\rho_1(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,  \\
-		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}, \quad
-		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}. 
-	\end{align*}
-Moreover, we have that with high probability,
-	\be\label{reduceproof1}
-\begin{split}
-\te_i(\hat \beta(\al)) =  \frac{\sigma^2}{\al (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\beta}, \quad i=1,2.
-\end{split}
-\ee
-Here the model shift biases $\delta^{(i)}_{\beta}$ satisfy that  
-\be\nonumber %\label{Deltabeta} 
-\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_\beta^{(i)}}/{ \Delta_{\beta}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2,\ee	
-%In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
-%%and by symmetry it suffices to focus on one of tasks, say task 2. 
-%Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
-%\be\label{reduceproof1}
-%\begin{split}
-%\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
-%\end{split}
-%\ee
-%and
-%\be\label{reduceproof1}
-%\begin{split}
-%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
-%\end{split}
-%\ee
-where $ \Delta^{(i)}_{\beta}$ are defined as 
-\be \nonumber
-\Delta^{(i)}_{\beta} := pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,. 
-\ee
-On the other hand, using Lemma \ref{lem_minv}, we have whp,
-\be\label{reduceproof2} 
-\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
-\ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
-$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
-In fact, one can see that if $\al\le \al_l$, then we have 
-$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
-that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\beta}$.
-Next we try to get more precise bounds on $\al^*$.
-In the following discussions, we only consider $\al$ such that $\al(\rho_1+\rho_2) \ge \al_l (\rho_1+\rho_2) \ge \min(\rho_1,\rho_2)$.
-
-%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
-
-\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
-\be\nonumber
-\begin{split}
-&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
-&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
-\end{split}
-\ee
-We rewrite the inequality as
-\be
-\begin{split}\label{solval1}
-  (1+\oo(1)) \cdot \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{\al \rho}}}^4\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho  - 1},
-\end{split}
-\ee
-where we abbreviated $\rho:=\rho_1+\rho_2$.
-
-In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
-Thus the following inequality implies \eqref{solval1}:
-\be\label{solval1add}
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
-\end{split}
-\ee
-In particular, if 
-\be\nonumber
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
-\end{split}
-\ee
-that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
-\begin{align*}
-\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
-& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-
-\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
-\be\label{solval2}
-\begin{split}
-&(1-\oo(1)) \cdot  \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{\al \rho}}}^4 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho - 1} .
-\end{split}
-\ee
-We then follow similar arguments as the above proof for the upper bound.
-
-In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
-Thus the following inequality implies \eqref{solval2}:
-\be\label{solval2add}
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
-\end{split}
-\ee
-There are two cases: if 
-\be\nonumber
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
-\end{split}
-\ee
-then we have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
-\begin{align*}
-\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
-& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-This concludes the proof.
-\end{proof}
+\subsection{Labeled data de-noising}\label{app_proof_data}
 

### 2020-06-01 writeup/proof_main.tex
revisions

--- 2020-05-31 writeup/proof_main.tex
@@
 
-In this section, we state and prove the formal version of Theorem \ref{thm_main_informal}. First, we need to introduce several quantities that will be used in our statement.
+In this section, we state and prove the formal version of Theorem \ref{thm_main_informal}, which covers the two tasks case with $t=2$.
+In this section, we consider the case where the entries of $\e_1$ and $\e_2$ have the same variance $\sigma_1^2=\sigma_2^2=\sigma^2$.
+%Moreover, we shall denote $\beta_1$ and $\beta_2$ by $\beta_1$ and $\beta_2$, standing for ``source task" and ``target task", respectively.
 
-Given the optimal ratio $\hat v$, let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
-Denote by ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ the eigenvalues of $\hat{M}^{\top}\hat{M}$.
-Let $(\hat a_1, \hat a_2)$ be the solutions to the following deterministic equations
+First, we  introduce several quantities that will be used in our statement, and they are also related to the quantities in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+Given the optimal ratio $\hat v$, let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix, and ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ be the eigenvalues of $\hat{M}^{\top}\hat{M}$.
+Define $(\hat a_1, \hat a_2)$ as the solution to the following system of deterministic equations,
 	\be
@@
 Then we introduce the following matrix
-\be\label{defnpihat}\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat a_2 +\hat  a_1 \hat {M}^{\top}\hat {M})^2} \hat {M}^{\top},\ee
-which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
-$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
+\be\label{defnpihat}\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat  a_1 \hat {M}^{\top}\hat {M}+\hat a_2 )^2} \hat {M}^{\top}.\ee
+%which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
+%$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
 We introduce two factors that will appear often in our statements and discussions:
-$$\al_-(\rho_1):=(1- \rho_1^{-1/2})^2,\quad \al_+(\rho_1):=(1 + \rho_1^{-1/2})^2.$$ 
-In fact, $\al_-^2$ and $\al_+^2$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
+$$\al_-(\rho_1):=\left(1- \rho_1^{-1/2}\right)^2,\quad \al_+(\rho_1):=\left(1 + \rho_1^{-1/2}\right)^2.$$ 
+In fact, $\al_-(\rho_1)$ and $\al_+(\rho_1)$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
 In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry.
 Finally, we introduce the error term
-\be\label{eq_deltaextra}\delta\equiv \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\lambda_{\min}^2(\hat M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_s - \hat{v}\beta_t)}^2,\ee
-where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.
+\be\label{eq_deltaextra}\delta\equiv \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\lambda_{\min}^2(\hat M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2,\ee
+where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. Note that this factor converges to 0 as $\rho_1$ increases.
 
-%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2.$$
+%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2.$$
 %{\cor may be able to get a better bound, but the statement will be long}
@@
 Now we are ready to state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
+It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
 
 \begin{theorem}\label{thm_model_shift}
-For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+%For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
 Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
 entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-	Then with high probability, we have
+Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2}. With high probability, we have
 	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\beta} \ge   \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\beta} \le - \delta, \label{lower}
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta \label{upper}\\
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta, \label{lower}
 	\end{align}
@@
 		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} } \label{Deltavarv} \\
-		\Delta_{\beta} &\define (\beta_s - \hat{v}\beta_t)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_s - \hat{v}\beta_t). \label{Deltabetav}
+		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
 	\end{align}
@@
 
-Under the simplifying setting in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
+For the isotropic model in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
 \begin{lemma}\label{prop_model_shift_tight}
 		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_t$ is a random vector with i.i.d.
-entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_2$ is a random vector such that $\beta_s - \beta_t$ is a random vector with i.i.d.
+		$\beta_2$ is a random vector with i.i.d.
+entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_1$ is a random vector such that $(\beta_1 - \beta_2)$ is a random vector with i.i.d.
 entries with mean $0$, variance $d^2$ and all moments.
 Denote
-		$\wt \Delta_{\beta} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2)} \bigtr{\Pi}.$
+		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi}.$
 	Then we have
 		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot \wt \Delta_{\beta}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot \wt\Delta_{\beta}.
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}.
 		\end{align*}
@@
 
-Now we first give a proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift}.
+Now we give the proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
 
@@
 \begin{align*}
-L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL}) &=\left( \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} - \sigma^2 \cdot \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right) \\
-&- \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2=:\delta_{\vari}(\hat v) - \delta_{\beta}(\hat v).
+L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL}) &=\sigma^2 \left(  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} -  \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right) \\
+&- \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2=:\delta_{\vari}(\hat v) - \delta_{\bias}(\hat v).
 \end{align*}
@@
 
-\item[(ii)] Using the approximate isometry property of $X_1$ (see \eqref{eq_isometric} below), we will bound the bias term $ \delta_{\beta}(v)$
-%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - {v} \beta_t)}^2$$
+\item[(ii)] Using the approximate isometry property of $X_1$ (see \eqref{eq_isometric} below), we will bound the bias term $ \delta_{\bias}(v)$
+%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - {v} \beta_2)}^2$$
 through 
 \be\label{deltabetapf}
-\wt\delta_{\beta}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_s - {v} \beta_t)}^2.\ee
+\wt\delta_{\bias}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_1 - {v} \beta_2)}^2.\ee
 
-\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\beta}$ term.
+\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\bias}$ term.
 
-\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M= \hat v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a possibly random $\hat v$.
+\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M= \hat v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a possibly random $\hat v$ which depends on $Y_1$ and $Y_2$.
 \end{itemize}
 
-\paragraph{Step I: Variance reduction.} Let $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for any fixed constant $v\ge 0$. Then using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
-$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right) \quad \text{whp},$$
+\paragraph{Step I: Variance reduction.} Let $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for any fixed constant $v\ge 0$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
+$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
 and 
-$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} ,\quad \text{whp},$$
-where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2}. Combining them, we get 
+$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
+with high probability, where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2}. Combining them, we get 
 \be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{whp},
@@
 
-Next we shall use \eqref{eq_isometric} to approximate $\delta_\beta(v)$ with $\wt\delta_\beta(v)$ in \eqref{deltabetapf}.  
-%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\beta}$.
+Next we shall use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$ in \eqref{deltabetapf}.  
+%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
 \begin{lemma}\label{prop_model_shift}
@@
 	\begin{align*}
-		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_s - v\beta_t)}^2, \\
-		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_s - v\beta_t)}, \\
-		\delta_\e(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2.
+		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_1 - v\beta_2)}^2, \\
+		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
+		\delta_{\e}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
 	\end{align*}
@@
 	\begin{align*}
-		 \left| \delta_\beta(v)-\wt\delta_\beta(v)\right| 
+		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
 		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_\e.
@@
 %	\end{align*}
-%	For the special case when $\Sigma_1 = \id$ and $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$, we further have
+%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
 %	\begin{align*}
-%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}
-%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \beta_t)}^2.
+%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
+%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \beta_2)}^2.
 %	\end{align*}
@@
 	Denote by $\cE = Z_1^{\top}Z_1 - {n_1}\id$. Then we can write
-%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_s - \hat{w}\beta_t)}^2$.
+%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_1 - \hat{w}\beta_2)}^2$.
 	%We have
 	\begin{align}
-%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - \hat{w}\beta_t)}^2 \nonumber \\
-		 \delta_\beta(v)-\wt\delta_\beta(v)&= {2v^2n_1}(\beta_s - v\beta_t)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_s - v\beta_t) \nonumber
+%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \hat{w}\beta_2)}^2 \nonumber \\
+		 \delta_{\bias}(v)-\wt\delta_{\bias}(v)&= {2v^2n_1}(\beta_1 - v\beta_2)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_1 - v\beta_2) \nonumber
 		\\
-		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_s - v\beta_t)}^2. \label{eq_lem_model_shift_1}
+		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2. \label{eq_lem_model_shift_1}
 %		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
@@
 	\begin{align*}
-	| \delta_\beta(v)-\wt\delta_\beta(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 \\
-	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 \\
-	& \le v^2 n_1^2 \left[\left( \al_+(\rho_1) + \OO(p^{-1/2+\e})\right)^2-1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2,
+	| \delta_{\bias}(v)-\wt\delta_{\bias}(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
+	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
+	& \le v^2 n_1^2 \left[ \al_+^2(\rho_1) + \OO(p^{-1/2+\e}) -1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2,
 	\end{align*}
@@
 %	\begin{align*}
-%		& \bigabs{(\beta_s -  \beta_t)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - v\beta_t)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 \\
-%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}}} \\
-%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t) (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \\
-%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_s - \hat{w}\beta_t)(\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
-%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2 \tag{since the matrix inside is rank 1}
+%		& \bigabs{(\beta_1 -  \beta_2)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - v\beta_2)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
+%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}}} \\
+%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2) (\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \\
+%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
+%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2 \tag{since the matrix inside is rank 1}
 %	\end{align*}
@@
 %	\begin{align*}
-%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_s - v\beta_t)}^2
-%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_s -  \beta_t)}^2.
+%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2
+%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 -  \beta_2)}^2.
 %	\end{align*}
@@
 &v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} = \hat M\frac{1}{(\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^2}\hat M^\top \\
-&\preceq  n_1^2 \hat M\frac{1}{\left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) - \OO(p^{-1/2+\e})\right]^2}\hat M^\top \\
+&\preceq  n_1^2 \hat M\frac{1}{\left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^2}\hat M^\top \\
 &\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + 2\left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
-&\prec [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1} - c
+&\prec [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
 \end{align*}
-for some small enough constant $c>0$. Together with Lemma \ref{prop_model_shift}, we get
+for some small enough constant $c>0$. Together with Lemma \ref{prop_model_shift}, we get with high probability,
 \be\label{bounddelta-}
-\left| \delta_\beta(v)-\wt\delta_\beta(v)\right| 
-		\le (\al_+^2(\rho_1)-1) \left[\frac{1}{\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)}  - \frac{c}{2}\right]\cdot \bignorm{\Sigma_1^{1/2} (\beta_s - v\beta_t)}^2 :=\delta(v)
+\left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
+		\le (1-c) \delta(v)
 \ee
-with high probability.
+for some small constant $c>0$, where recall $\delta(v)$ defined in \eqref{eq_deltaextra}.
 
-\paragraph{Step III: The limit of $\wt\delta_\beta(v)$.}
-Using Lemma \ref{lem_cov_derivative} with $\Sigma_1$ and $M$ replaced by $v^2\Sigma_1$ and $\hat M$, respectively, we obtain that 
+\paragraph{Step III: The limit of $\wt\delta_{\bias}(v)$.} 
+Using Lemma \ref{lem_cov_derivative} with $\Sigma_1$ and $M$ replaced by $v^2\Sigma_1$ and $\hat M$, we obtain that 
 \begin{align*}
-\wt\delta_\beta &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_s-v\beta_t)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 + \hat a_3)\id + \hat a_4 \hat{M}^{\top}\hat{M}}{(a_2 + a_1 \hat{M}^{\top}\hat{M})^2} \Sigma_2^{-1/2} \Sigma_1(\beta_s-v\beta_t) +\OO(p^{-1/2+\e}) \\
-&= (\beta_s - {v}\beta_t)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_s - {v}\beta_t) +\OO(p^{-1/2+\e}) =: \Delta_\beta(v) +\OO(p^{-1/2+\e}).
+\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 + \hat a_3)\id + \hat a_4 \hat{M}^{\top}\hat{M}}{( a_1 \hat{M}^{\top}\hat{M}+a_2 )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
+&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
 \end{align*}
-Together with and \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that 
+with high probability. Together with and \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that whp,
 \be\label{dicho_varbeta}
-\begin{cases}\delta_{\vari}(v)>\delta_{\beta}(v), & \text{ if } \Delta_{\vari}(v) - \Delta_{\beta}(v) \ge   \delta(v),\\
-\delta_{\vari}(v)<\delta_{\beta}(v),  & \text{ if }  \Delta_{\vari}(v) - \Delta_{\beta}(v) \le -  \delta(v).\end{cases}
+\begin{cases}\delta_{\vari}(v)>\delta_{\bias}(v), & \text{ if } \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \ge   \delta(v),\\
+\delta_{\vari}(v)<\delta_{\bias}(v),  & \text{ if }  \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \le -  \delta(v).\end{cases}
 \ee
 
-\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result to $v=\hat v$, which is random and depend on $X_1$ and $X_2$.
-We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} hold uniformly for all $v\in [0, C_0]$.
-In fact, for a large constant $C_1>0$, we consider $v$ belonging to a discrete set
-$$V:=\{v_k = kN^{-C_1}: 1\le k \le C_0N^{C_1}+1\}.$$
-Then using the arguments for the first three steps, we get that
+\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result to $v=\hat v$, which is random and depends on $X_1$ and $X_2$.
+We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{dicho_varbeta}
+%\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
+holds uniformly for all $v\in [0, C_0]$. In fact, for a large constant $C_1>0$, we consider $v$ belonging to a discrete set 
+$$V:=\{v_k = kp^{-1}: 1\le k \le C_0p +1\}.$$
+Then using the arguments for the first three steps and a simple union bound, we get that
 \eqref{dicho_varbeta} holds simultaneously for all $v\in V$ with high probability. On the other hand, by \eqref{eq_isometric} the event
@@
 \begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|=\OO(N^{-C_0}),\quad |\delta_{\beta}(v) -\delta_{\beta}(v_k)|=\OO(N^{-C_0}), \quad |\delta(v)-\delta(v_k)|=\OO(N^{-C_0}),\\
-& |\Delta_{\beta}(v) -\Delta_{\beta}(v_k)|=\OO(N^{-C_0}),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|=\OO(N^{-C_0}).
+& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|\lesssim p^{-1}\delta_{\vari}(v_k),\ \ |\delta_{\bias}(v) -\delta_{\bias}(v_k)|\lesssim p^{-1}\delta_{\bias}(v_k), \ \   |\delta(v)-\delta(v_k)|\lesssim p^{-1}\delta(v_k),\\
+& |\Delta_{\bias}(v) -\Delta_{\bias}(v_k)|\lesssim p^{-1}\Delta_{\bias}(v_k),\ \ |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|\lesssim p^{-1}\Delta_{\vari}(v_k).
 \end{align*}
@@
 \begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e,\quad |\delta_{\beta}(v) -\delta_{\beta}(C_0)|\le \e, \quad |\delta(v)-\delta(C_0)|\le \e,\\
-& |\Delta_{\beta}(v) -\Delta_{\beta}(C_0)|\le \e,\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e,
+& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e\delta_{\vari}(C_0),\quad |\delta_{\bias}(v) -\delta_{\bias}(C_0)|\le \e\delta_{\bias}(C_0), \quad  |\delta(v)-\delta(C_0)|\le \e\delta(C_0),\\
+& |\Delta_{\bias}(v) -\Delta_{\bias}(C_0)|\le \e\Delta_{\bias}(C_0),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e\Delta_{\vari}(C_0),
 \end{align*}
 for all $v\ge C_0$ as long as $C_0$ is chosen large enough depending on $\e$.
-Together with the estimate at $C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\ge 0$ on he high probability event $\Xi_1\cap \Xi_2$.
+Together with the estimate at $C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\ge 0$ on the high probability event $\Xi_1\cap \Xi_2$.
 This concludes the proof since $v$ must be one of the positive values.
@@
 
-{\cor add some remarks about the difficulty in random matrix theory}
+One can see from the above proof that the main error, $\delta$, of Theorem \ref{thm_model_shift} comes from approximating $\delta_{\bias}$ by $\wt\delta_{\bias}$ in \eqref{bounddelta-}.
+In order to improve this estimate and obtain an exact asymptotic result as for the $\delta_{\vari}$ term, one needs to study the singular value distribution of the following random matrix:
+$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  {v}^2 .$$
+In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ have been studied in the name of Fisher matrices; see e.g.
+\cite{Fmatrix}.
+However, since $\cal X$ is not symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix theory literature, and the study of the singular values of $\cal X + v^2$ will be even harder.
+We leave this problem to future study.
 
-By replacing \eqref{bounddelta-} with a tighter bound in Step II of the above proof, we can conclude the proof Lemma \ref{prop_model_shift_tight}.
+By replacing \eqref{bounddelta-} with a tighter bound in Step II of the above proof, we can conclude the proof of Lemma \ref{prop_model_shift_tight}.
 
 \begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
-For any fixed $v\ge 0$, $\beta_s - v\beta_t$ is a random vector with i.i.d.
+For any fixed $v\ge 0$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
 entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
-Then using the concentration Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
+Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
 \begin{align}
-&\left|\delta_{\beta}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&=  \left|(\beta_s - {v} \beta_t)^\top \cal K^\top \cal K (\beta_s - {v} \beta_t) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&\le p^\e [(1-v)^2\kappa^2 + d^2] \tr^{1/2} \left[(\cal K^\top \cal K)^2\right] \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
+&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
 \end{align}
@@
 \begin{align*}
-\wt \delta_\beta(v) =v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
+v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
 \end{align*}
 Recalling that $\Sigma_1=\id$ and bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
-\be\label{anotherwtbeta}\wt \delta_\beta(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \wt \delta_\beta(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
+\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
 where 
-$$\wt\delta_\beta(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\wt\delta_\beta(v) \sim 1$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get 
+$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
+Note that $\delta^\star_{\bias}(v) \sim 1$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get 
 \be\label{replaceest}
-  \wt \delta_\beta(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\beta}(v)\le \wt \delta_\beta(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
+  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
 \ee
 Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Theorem \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
-We omit the details.
+In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term, We omit the details.
 \end{proof}
 
-\subsection{Proof of Many Tasks with the Same Covariates}\label{app_proof_many_tasks}
+\subsection{Proof for Many Tasks with the Same Covariates}\label{app_proof_many_tasks}
 
 \begin{theorem}\label{thm_many_tasks}
-Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
 Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
@@
 	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star = [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
+	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, that satisfy Assumption \ref{assm_secA2}.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
 	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
@@
 %As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
-Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$.
+Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
 The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
@@
 		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
-		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}
+		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1},
 	\end{align*}
@@
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	Then as in Section \ref{app_proof_sec3}, it remains to consider minimizing the validation loss 
+	\cor Then as in Section \ref{app_proof_sec3}, it remains to consider minimizing the validation loss 
 	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2}$$ 
-	over $\cal W$.
+	over $\cal W$. \nc
 
 	% Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$. 
-	It is easy to calculate that $\val( \cal W)$ contains two parts: $\val( \cal W)= \delta_{\beta}(\cal W) + \delta_{\vari}(\cal W)$. Here $\delta_{\beta}(\cal W) $ is the model shift bias term given by
+	It is easy to calculate that $\val( \cal W)$ contains two parts: $\val( \cal W)= \delta_{\bias}(\cal W) + \delta_{\vari}(\cal W)$. Here $\delta_{\bias}(\cal W) $ is the model shift bias term given by
 	\begin{align*}
-		\delta_{\beta}(\cal W) =\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
+		\delta_{\bias}(\cal W) =\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
 	\end{align*}
@@
 	\end{align*}
-	%Therefore we only need to focus on the minimizer for $\delta_{\beta}(\cal W) $ since the variance part does not depend on the weights. 
+	%Therefore we only need to focus on the minimizer for $\delta_{\bias}(\cal W) $ since the variance part does not depend on the weights. 
 	We denote $Q = \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{k\times k}$, whose $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$.
@@
 	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
+		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_2 \right) }^2
 		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \sigma^2\norm{U_r(t)}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 \cdot \left( 1+\OO(p^{-1/2+\e})\right),
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \sigma^2\norm{U_r(t)}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 \cdot \left( 1+\OO(p^{-1/2+\e})\right),
 	\end{align*}

### 2020-06-01 writeup/transfer.tex
revisions

--- 2020-06-01 writeup/transfer.tex
@@
 
-\subsection{Data Size}
+\subsection{Data Size}\label{sec_datasize}
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
@@
 There are several unexplained observations near $y = 0$ caused by the errors $\gamma_-, \gamma_+$.
-The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_31}.
+The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
 
@@
 In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-The result can be found in Appendix \ref{app_proof_data}.
+The result can be also found in Appendix \ref{app_proof_32}.
 
@@
 
-\subsection{Covariate Shift}
+\subsection{Covariate Shift}\label{sec_covshift}
 
@@
 By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-The result is left to Appendix \ref{app_proof_31}.
+The result is left to Appendix \ref{app_proof_33}.
 %We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
@@
 Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in Wu et al.'20 \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
-The idea is to add an alignment module between the input and the shared module $B$.
-This new module is then trained together with $B$ and the output layers.
-We validate our insight on this procedure in the experiments.

### 2020-06-01 writeup/experiments.tex

@@
 \textbf{Baseline.} We compare Algorithm \ref{alg_inc_train} to a model trained with standard multi-task learning approaches.
+We measure the prediction accuracy of a particular target task.
 
@@
 We compare Algorithm \ref{alg_inc_train} to performing multi-task learning.
-Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the cost to achieve the same performance on the target task, compared to multi-task learning.
+Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.
 

### 2020-06-01 writeup/proof_examples.tex

@@
 
-\subsection{Supplement to Section \ref{sec_datasize}} \label{app_proof_32}
+\subsection{Supplement to Section \ref{sec_data_size}} \label{app_proof_32}
 We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.

### 2020-06-01 writeup/experiments.tex
intro

@@
 We show that for both datasets, single-task learning results can help predict positive or negative transfer in multi-task learning.
-Second, \todo{}.
-Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-Finally, we validate the three components of our theory in Section \ref{sec_insight} on text classification tasks.
+Second, we show that our proposed incremental training schedule improves the training efficiency of multi-task learning for predicting a particular target task.
+%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
+Finally, we validate the three components of our theory and measure the data efficiency of multi-task learning on text classification tasks.
 

### 2020-06-01 writeup/intro.tex
intro

@@
 %, which has been a key empirical finding in recent work.
-Finally, we show practical implications of our theory for detecting and mitigating negative effects in image and text classification tasks.
+Finally, we show practical implications of our theory for detecting and mitigating negative effects.
+	For example, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
+	We validate our theory and proposed method on image and text classification tasks.
 \end{abstract}
@@
 Our second contribution is to use our newly developed tool to rigorously explain negative transfer in multi-task learning.
-In Section \ref{sec_insight}, we consider three factors including task model, data size and covariate shift.
+In Section \ref{sec_insight}, we consider three components including task model, data size and covariate shift for a simplified isotropic setting of two tasks.
 \squishlist
-		\item First, we define task dissimilarity as the distance between $\beta_1$ and $\beta_2$ using a simplified isotropic setting of two tasks.
-		Using our technical tool, we show a sharp transition from positive to negative transfer as task dissimilarity increases.
-		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
+		\item We measure task dissimilarity by how small is the distance between $\beta_1$ and $\beta_2$.
+		Using our technical tool, we explain a transition from positive to negative transfer as task similarity decreases.
+%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
 %		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
 %	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-		\item Second, we consider data size.
-	We begin by observing that adding more labeled data from the source task does not always improve performance.
+		\item We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
 	Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy \cite{ZSSGM18}.
@@
 		\item Finally, we show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-		We show that as $n_1 / n_2$ becomes large, the source task should have the same covariance matrix as the target task to ensure the best performance.
+		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
 %		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
@@
 Our final contribution is to connect our theory to practical problems of interest.
-First, we provide a metric to determine positive versus negative transfer by comparing the test accuracies of single-task models.
-Second, \todo{}
-Finally, we provide a new insight on the covariance alignment algorithm, proposed in \cite{WZR20}.
-We show that as the size of the source task becomes larger compared to the target task, the covariance alignment algorithm produces more significant results.
+First, we provide a single-task based metric to predict positive or negative transfer in multi-task learning.
+While it is generally not well-understood when multi-task learning provides positive transfer, we show that the STL results are indicative of and can help understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
+Second, we design an incremental training schedule to improve the efficiency of multi-task training for predicting a particular task.
+We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset, while keeping the accuracy the same.
+Finally, we validate the three components of our theory in Section \ref{sec_insight} and measure the data efficiency of multi-task learning on the sentiment analysis dataset.

### 2020-06-01 writeup/proofs_sec3.tex

@@
 Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $\wt f(\hat B; v)$. We will define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_t^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2). \]
+	\[ \hat{\beta}_t^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2), \]
+	where $t=2$ since we are considering the two task case, and it also stands for the ``target task". 
 The intuition for deriving $\hat{\beta}_t^{\MTL}$ is akin to performing multi-task training in practice.
@@
 &(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
-&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M})^2+a_2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
+&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
 \end{split}

### 2020-06-01 writeup/intro.tex
intro

@@
 Our second contribution is to use our newly developed tool to rigorously explain negative transfer in multi-task learning.
-In Section \ref{sec_insight}, we consider three components including task model, data size and covariate shift for a simplified isotropic setting of two tasks.
+In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
 \squishlist
-		\item We measure task dissimilarity by how small is the distance between $\beta_1$ and $\beta_2$.
-		Using our technical tool, we explain a transition from positive to negative transfer as task similarity decreases.
+		\item First, we measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
+		Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
 %		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
@@
 %	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-		\item We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
+		\item Second, we show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
 	Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy \cite{ZSSGM18}.

### 2020-06-01 writeup/experiments.tex
sec 5
sec 5 tl

@@
 \textbf{Improving multi-task training efficiency.}
-We compare Algorithm \ref{alg_inc_train} to performing multi-task learning.
+We compare Algorithm \ref{alg_inc_train} to performing multi-task learning for predicting a particular target dataset.
 Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.
@@
 \textbf{Improving transfer learning training efficiency.}
-\todo{}
-
-\subsection{Ablation Studies}
-
-\textbf{Task similarity.} We validate that MTL performs better when the source task is more similar to the target task.
-We show the result on the sentiment analysis tasks.
-For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
-Figure \ref{fig_ab_sim} confirms the result.
-
-\textbf{Data size.}
-Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-
-\textbf{Covariate shift.}
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-\textbf{Data efficiency.}
-We measure the data efficiency ratio on the sentiment analysis tasks.
-In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
-The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
+We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
+Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
 
@@
 \end{figure}
+
+\subsection{Ablation Studies}
+
+\textbf{Task similarity.} We validate that MTL performs better when the source task is more similar to the target task.
+We show the result on the sentiment analysis tasks.
+For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+Figure \ref{fig_ab_sim} confirms the result.
+
+\textbf{Data size.}
+Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+
+\textbf{Covariate shift.}
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
+
+\textbf{Data efficiency.}
+We measure the data efficiency ratio on the sentiment analysis tasks.
+In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
+The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
+We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
+%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

### 2020-06-01 writeup/intro.tex
intro

@@
 We extend the result to the related setting of transfer learning.
-Second, we apply our tool to rigorously explain when multi-task learning outperforms single-task learning.
-%And we theoretically analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning.
-%, which has been a key empirical finding in recent work.
+Second, we apply our tool to explain when multi-task learning outperforms single-task learning.
 Finally, we show practical implications of our theory for detecting and mitigating negative effects.
 	For example, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
-	We validate our theory and proposed method on image and text classification tasks.
+	We validate our theory and our proposed method on image and text classification tasks.
 \end{abstract}
@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning represents a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and numerous other areas \cite{ZY17}.
+Multi-task learning represents a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
@@
 When the information sources are heterogeneous, negative transfer -- where multi-task learning performs worse than single-task learning -- has often been observed \cite{AP16,BS17}.
-While numerous studies have sought to alleviate negative transfer \cite{ZY17}, a rigorous understanding of the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
+While many studies have sought to mitigate negative transfer \cite{ZY17}, a rigorous understanding of the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
@@
 % for learning from multiple linear regression tasks.
-We use the tools to rigorously explain the phenomena of negative transfer.
+We use the tools to explain the phenomena of negative transfer rigorously.
 Our theory also leads to practical implications: we propose a diagnostic metric and a training schedule to improve multi-task training.
@@
 
-In this work, we consider the setting of high-dimensional linear regression and focus on predicting a particular task whose amount of labeled data is limited.
+In this work, we consider the setting of high-dimensional linear regression and focus on predicting a particular task that only contains limited amount of labeled data.
 Following Hastie et al.
@@
 
-Our second contribution is to use our newly developed tool to rigorously explain negative transfer in multi-task learning.
+Our second contribution is to use our newly developed tool to explain negative transfer in multi-task learning rigorously.
 In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
@@
 
-Our final contribution is to connect our theory to practical problems of interest.
+Our last contribution is to connect our theory to practical problems of interest.
 First, we provide a single-task based metric to predict positive or negative transfer in multi-task learning.
-While it is generally not well-understood when multi-task learning provides positive transfer, we show that the STL results are indicative of and can help understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
+While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
 Second, we design an incremental training schedule to improve the efficiency of multi-task training for predicting a particular task.

### 2020-06-01 writeup/proof_main.tex
Sec A

@@
-\subsection{Proof for Two Tasks with General Covariance}\label{app_proof_main}
+\subsection{Proof for Two Tasks with General Covariates}\label{app_proof_main}
 
@@
 
-\subsection{Proof for Many Tasks with the Same Covariates}\label{app_proof_many_tasks}
+\subsection{Proof for Many Tasks with the Same Covariate}\label{app_proof_many_tasks}
 
@@
 	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
+Suppose $(B^{\star})^\top\Sigma B^{\star}$ is of full rank in the sense that $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$.
 Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
@@
 	\begin{itemize}
-		\item If $\left(1 -\oo(1)- \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 $, then $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ whp.
-		\item If $\left(1 +\oo(1)- \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2$, then $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ whp.
+		\item We have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
+		$$\left(1 - \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
+
+		\item We have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
+		$$\left(1 - \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
+
 	\end{itemize}
@@
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	\cor Then as in Section \ref{app_proof_sec3}, it remains to consider minimizing the validation loss 
-	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2}$$ 
-	over $\cal W$. \nc
+Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use concentration to get the validation loss as
+\be\label{eq_multival}\wt f(\hat B; \cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
+Here $\val(\cal W)$ is defined as 
+%it remains to consider minimizing the validation loss 
+	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari}(\cal W),$$ 
+where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
+	\begin{align*}
+		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
+	\end{align*}
+	and the variance term $\delta_{\vari}(\cal W)$ can be calculated as 
+	\begin{align*}
+		\delta_{\vari}(\cal W):= \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+	\end{align*}
+It suffices to minimize $\delta_{\bias}(\cal W)$ over $\cal W$, since both $t N \sigma^2$ and $\delta_{\vari}(\cal W)$ do not depend on the weights.
 
-	% Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$. 
-	It is easy to calculate that $\val( \cal W)$ contains two parts: $\val( \cal W)= \delta_{\bias}(\cal W) + \delta_{\vari}(\cal W)$. Here $\delta_{\bias}(\cal W) $ is the model shift bias term given by
+We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{k\times k}$, whose $(i,j)$-th entry is equal to $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$. 
+	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
+	Now we can write $\delta_{\bias}(\cal W)$ succinctly as 
 	\begin{align*}
-		\delta_{\bias}(\cal W) =\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
+		\delta_{\bias}(\cal W)= \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
 	\end{align*}
-	and $\delta_{\vari}(\cal W)$ is the variance term given by
-	\begin{align*}
-		\delta_{\vari}(\cal W)= \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-	\end{align*}
-	%Therefore we only need to focus on the minimizer for $\delta_{\bias}(\cal W) $ since the variance part does not depend on the weights. 
-	We denote $Q = \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{k\times k}$, whose $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$.
-	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-	Now we can write the validation loss succinctly as 
-	\begin{align*}
-		\val(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-	\end{align*}
-	From this equation we can solve for $Q$ optimally as $\hat Q=U_{r}U_r^{\top}$.
-	In sum we have solved that $\hat{\beta}_i^{\MTL}=B^{\star} U_r U_r(i)$. Inserting it into the definition of the test error, we get that
+	From this equation we can solve the minimizer optimally as $Q_0=U_{r}U_r^{\top}$.
+On the other hand, let $\hat {\cal W}$ be the minimizer of $\wt f$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
+We claim that $\hat Q$ satisfies
+	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\| = \oo(1) \quad \text{whp}.\ee
+	In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by \eqref{eq_isometric}, we obtain that
+	$$   \val(\hat {\cal W}) + t  \sigma^2 > (\val( {\cal W}_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ \wt f(\hat B; \hat{\cal W})>\wt f(\hat B; {\cal W}_0),$$
+	that is, $\hat {\cal W}$ is not a minimizer. This leads to a contradiction.
+
+	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r U_r(i) +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that
 	\begin{align*}
@@
 		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \sigma^2\norm{U_r(t)}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 \cdot \left( 1+\OO(p^{-1/2+\e})\right),
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
 	\end{align*}
-	with high probability for any constant $\e>0$, where we used Lemma \ref{lem_minv} in the last step. Together with the fact that with high probability,
-	$$\te(\hat{\beta}_t^{\MTL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
-	 also by Lemma \ref{lem_minv}, we conclude the proof.
+	with high probability, where we used Lemma \ref{lem_minv} in the last step. Similar, by Lemma \ref{lem_minv} we have
+	$$\te(\hat{\beta}_t^{\MTL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
+Combining the above two estimates, we conclude the proof.
 \end{proof}

### 2020-06-01 writeup/proof_taskonomy.tex
validation
Sec A

@@
-\subsection{Proof of the Transfer Learning Setting}\label{app_proof_sec4}
+\subsection{Proof for the Transfer Learning Setting}\label{app_proof_sec4}
 
 \begin{theorem}\label{prop_taskonomy}
-For $i=1,\cdots, t$, let $Y_i = X_i\beta_i + \varepsilon_i$ be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+%For $i=1,\cdots, t$, let $Y_i = X_i\beta_i + \varepsilon_i$ be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
 Suppose $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are  random vectors with i.i.d.
 entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $\max_{1\le i \le t}\|\beta_i\|=\OO(1)$, $\sigma^2=\OO(1)$ and
+Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, that satisfy Assumption \ref{assm_secA2}.
+Moreover, assume that $\max_{1\le i \le t}\|\beta_i\|=\OO(1)$, $\sigma^2=\OO(1)$, and 
 \be\label{BTBassm}
@@
 \end{align*}
-Here $\cal M_1$ and $\cal M_2$ are $(t-1)\times (t-1)$ diagonal matrices with $(\cal M_1)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right)$ and $(\cal M_2)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\Sigma_t\right)$.
+Here $\cal M_1$ and $\cal M_2$ are $(t-1)\times (t-1)$ diagonal matrices with 
+$$(\cal M_1)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right),\quad \text{and}\quad (\cal M_2)_{ii}=\frac{1}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\Sigma_t\right).$$
 \end{theorem}
@@
 \end{align*}
-Using concentration of random vector with independent entries, Lemma \ref{largedeviation}, we get that for any deterministic vector $\beta$ with $\|\beta\|=\OO(1)$,
+Using concentration of random vector with i.i.d. centered entries, Lemma \ref{largedeviation}, we get that for any deterministic vector $\beta$ with $\|\beta\|=\OO(1)$,
 \be\label{largebetae}
@@
 With \eqref{largebetae}-\eqref{largebetae3}, we get that with high probability,
+\begin{align}\label{betanormij}
+\hat\beta_i^\top \hat \beta_j &= \beta_i^\top \beta_j + \OO(\sigma p^{-1/2+\e})  , \quad i\ne j,
+\end{align}
+and
 \begin{align}
-\|\hat\beta_i\|^2&= \|\beta_i\|^2 + \sigma^2\cdot \tr \left( (X_i^\top X_i)^{-1}\right) +\OO(\sigma p^{-1/2+\e}) \nonumber\\
+\|\hat\beta_i\|^2&= \|\beta_i\|^2 + \sigma^2 \tr \left[ (X_i^\top X_i)^{-1}\right] +\OO(\sigma p^{-1/2+\e}) \nonumber\\
 &=  \|\beta_i\|^2 + \frac{\sigma^2}{\rho_i-1}\cdot \frac1p\tr \left(\Sigma_i^{-1}\right) +\OO(\sigma p^{-1/2+\e}) ,\label{betanormi}
 \end{align}
-where we used Lemma \ref{lem_minv} in the second step, 
-and %where in the second step we used Lemma \ref{lem_minv}. Similarly, we have
-\begin{align}\label{betanormij}
-\hat\beta_i^\top \hat \beta_j &= \beta_i^\top \beta_j + \OO(\sigma p^{-1/2+\e})  , \quad i\ne j.
-\end{align}
-With \eqref{betanormi} and \eqref{betanormij}, we obtain that with high probability,
+where we used Lemma \ref{lem_minv} in the second step. %where in the second step we used Lemma \ref{lem_minv}. Similarly, we have
+
+With \eqref{betanormij} and \eqref{betanormi}, we obtain that with high probability,
 \be\label{BTB}
@@
 \ee
-where $\OO(\sigma p^{-1/2+\e})$ means a $(t-1)\times (t-1)$ matrix, say $\cal E$, satisfying $\|\cal E\|\le C\sigma p^{-1/2+\e}$. Notice that by \eqref{BTBassm}, we have that with high probability,
-$$\|(B^\top B)^{-1}\| = \OO( 1).$$
+where $\OO(\sigma p^{-1/2+\e})$ means a $(t-1)\times (t-1)$ matrix, say $\cal E$, satisfying $\|\cal E\|\le C\sigma p^{-1/2+\e}$. Notice that by \eqref{BTBassm}, we have that 
+$$\|(B^\top B)^{-1}\| = \OO( 1) \quad \text{whp}.$$
 Moreover, using \eqref{largebetae} we get 
@@
 \end{align}
-As in \eqref{BTB}, we can show by concentration and Lemma \ref{lem_minv} that 
+Then as in \eqref{BTB}, we can show by concentration and Lemma \ref{lem_minv} that 
 \be\label{BTB2}
@@
 \ee
-Together with \eqref{BTB} and \eqref{BTBeta}, we can further take the expectation and simplify \eqref{EBWk2} as
+Combining \eqref{BTB}, \eqref{BTBeta} and \eqref{BTB2}, we can further take the expectation and simplify \eqref{EBWk2} as
 \begin{align*}

### 2020-06-01 writeup/proofs_sec3.tex
Sec A

@@
 
-\subsection{The multi-task learning estimator}
+\subsection{The multi-task learning estimator}\label{sec_MTLest}
 From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
@@
 centered random vectors with covariance matrix $\Sigma$.
-For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any $k\in \N$,
+For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
 \begin{equation}\label{assmAhigh}
-\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p,
+\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
 \end{equation}
-for some constant $C_k>0$.
  We assume that $n=\rho p$ for some fixed constant $\rho>1$.
@@
 Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Moreover, we shall use $\oo(1)$ to mean a small positive number that converges to 0 as $p\to \infty$.
 

### 2020-06-01 writeup/intro.tex

@@
 \begin{abstract}
-When does multi-task learning outperform single-task learning?
-In this work, we address this question by studying the performance of predicting a particular task given multiple tasks.
-We consider a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
-First, for the setting of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff of multi-task learning estimators.
+When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
+In this work, we address this question by studying
+% the performance of predicting a particular task given multiple tasks.
+a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
+First, for the setting of high-dimensional linear regression, we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
+We provide a sharp analysis of the tradeoff and extend the result to transfer learning.
 We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
-We extend the result to the related setting of transfer learning.
-Second, we apply our tool to explain when multi-task learning outperforms single-task learning.
-Finally, we show practical implications of our theory for detecting and mitigating negative effects.
-	For example, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
+Second, we identify three components including task similarity, data size and covariate shift to explain negative transfer in multi-task learning rigorously.
+Finally, we show practical implications of our theory for detecting and mitigating negative transfer.
+We propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
 We validate our theory and our proposed method on image and text classification tasks.
@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning represents a powerful paradigm to solve complex prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
+Multi-task learning represents a powerful paradigm to solve complex tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
@@
 The performance of multi-task learning depends on the relationship of the information sources \cite{C97}.
-When the information sources are heterogeneous, negative transfer -- where multi-task learning performs worse than single-task learning -- has often been observed \cite{AP16,BS17}.
+When the information sources are heterogeneous, negative transfer--where multi-task learning (MTL)  performs worse than single-task learning (STL)--has often been observed \cite{AP16,BS17}.
 While many studies have sought to mitigate negative transfer \cite{ZY17}, a rigorous understanding of the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
@@
 We use the tools to explain the phenomena of negative transfer rigorously.
-Our theory also leads to practical implications: we propose a diagnostic metric and a training schedule to improve multi-task training.
+Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
 %We consider a setting where the target task has limited labeled data and show
@@
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task (MTL) estimator for the target task.
-Let $\hat{\beta}_t^{\STL}$ denote the single-task (STL) estimator.
+Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator for the target task.
+Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
 We define these precisely in Section \ref{sec_setup}.
@@
 	\item We extend our result to transfer learning in the setting of high-dimensional linear regression.
-	We pool learnt source task representations into a shared body similar to $B$ in the hard parameter sharing architecture, as in Taskonomy by Zamir et al.'18 \cite{ZSSGM18}.
+	We pool learnt source task representations into a shared body similar to $B$ in the hard parameter sharing architecture, as in Taskonomy by Zamir et al. \cite{ZSSGM18}.
 	We show that the model shift bias can be captured by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
@@
 \squishlist
-		\item First, we measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
+		\item We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
 		Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
@@
 %	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-		\item Second, we show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-	Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy \cite{ZSSGM18}.
+		\item We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
+	Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy.
 %	We define the \textit{data efficiency ratio} as the smallest $x$ such that if we only use an $$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
@@
 %, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
-		\item Finally, we show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
+		\item We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
 		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
@@
 Our last contribution is to connect our theory to practical problems of interest.
-First, we provide a single-task based metric to predict positive or negative transfer in multi-task learning.
+(i) We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
 While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-Second, we design an incremental training schedule to improve the efficiency of multi-task training for predicting a particular task.
+(ii) We design an incremental training schedule to improve the efficiency of multi-task training for predicting a particular task.
 We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset, while keeping the accuracy the same.
-Finally, we validate the three components of our theory in Section \ref{sec_insight} and measure the data efficiency of multi-task learning on the sentiment analysis dataset.
+(iii) We validate the three components of our theory in Section \ref{sec_insight} and measure the data efficiency of multi-task learning on the sentiment analysis dataset.

### 2020-06-01 writeup/intro.tex
intro

@@
 The performance of multi-task learning depends on the relationship of the information sources \cite{C97}.
-When the information sources are heterogeneous, negative transfer--where multi-task learning (MTL)  performs worse than single-task learning (STL)--has often been observed \cite{AP16,BS17}.
-While many studies have sought to mitigate negative transfer \cite{ZY17}, a rigorous understanding of the contributing causes of negative transfer has remained elusive in the literature \cite{R17}.
+When the information sources are heterogeneous, negative transfer--where multi-task learning (MTL)  performs worse than single-task learning (STL)--has often been observed \cite{PY09,AP16,BS17}.
+While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs has remained elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-In this work, we develop technical tools to compare multi-task learning to single-task learning for the setting of high-dimensional linear regression.
+In this work, we show that negative transfer is determined by the bias-variance tradeoff of multi-task learning estimators for the setting of high-dimensional linear regression.
 % for learning from multiple linear regression tasks.
-We use the tools to explain the phenomena of negative transfer rigorously.
+We develop technical tools to analyze the tradeoff and use our tools to explain negative transfer precisely.
 Inspired by the theory, we propose an incremental training schedule to improve multi-task training.

### 2020-06-01 writeup/intro.tex
fig 1

@@
 More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+\todo{Add our ICLR work here.}
+\squishlist
+	\item \textbf{Task similarity:}
+	\item \textbf{Data sizes:}
+	\item \textbf{Covariate shift:}
+\squishend
 To rigorously study negative transfer, the technical challenge is to develop generalization bounds that scale tightly with properties of the data.
@@
 
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\caption{Task similarity}
+		\label{fig_model_shift}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
+		\caption{Data sizes}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
+		\caption{Covariate shift}
+		\label{fig_covariate}
+	\end{subfigure}
+	\caption{Three takeaways of our theory in Section \ref{sec_insight}.
+	(a) As task model distance increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
+	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Proposition \ref{prop_data_size}).
+	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Proposition \ref{prop_covariate}).
+	The $y$-axis measures the performance of MTL minus STL.}
+	\label{fig_model_shift_phasetrans}
+	\vspace{-0.2in}
+\end{figure}
+
 \textbf{Main results.}
@@
 In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-\squishlist
-		\item We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
+We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
 Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
@@
 %	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-		\item We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
+We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
 	Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy.
-%	We define the \textit{data efficiency ratio} as the smallest $x$ such that if we only use an $$ fraction of labeled data, then the test error of $\hat{\beta}_t^{\MTL}$ matches that of the $\hat{\beta}_t^{\STL}$ on the entire set.
-	%In Proposition \ref{prop_data_efficiency}, we show that the data efficiency ratio of an illustrative example is at most $\alert{\frac {1}{2\rho_t}}$.
-	%In Section \ref{sec_validate}, we validate that performing multi-task learning can reduce the need for labeled data on 6 sentiment analysis tasks.
-%, we observe that just by using \alert{40\%} of the labeled data, the overall accuracy of multi-task learning matches that of learning every task in isolation.
-		\item We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
+We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
 		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
 %		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-\squishend
 

### 2020-06-01 writeup/experiments.tex
sec 4

@@
-\section{Experiments}
+\section{Practical Connections for Detecting and Mitigating Negative Transfer}
 
@@
 
-\subsection{Experimental Results}
-
-\textbf{Understanding MTL results via STL results.}
-We show that STL results can be used to help understand MTL results
-We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
-Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
-We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among 150 task pairs.
-We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
-The results show that STL performances are indicative of MTL performances.
+\subsection{Experimental Results: Improving Data Efficiency}
 
@@
 Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
+
+\textbf{Data efficiency.}
+We measure the data efficiency ratio on the sentiment analysis tasks.
+In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
+The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
+We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
+%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
 
@@
 
+\textbf{Understanding MTL results via STL results.}
+We show that STL results can be used to help understand MTL results
+We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
+Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
+We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among 150 task pairs.
+We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
+The results show that STL performances are indicative of MTL performances.
+
 \textbf{Task similarity.} We validate that MTL performs better when the source task is more similar to the target task.
@@
 Figure \ref{fig_ab_sim} confirms the result.
-
-\textbf{Data size.}
 Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
 In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-
-\textbf{Covariate shift.}
 %Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
@@
 In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-\textbf{Data efficiency.}
-We measure the data efficiency ratio on the sentiment analysis tasks.
-In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
-The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

### 2020-06-01 writeup/proof_examples.tex
Sec B

@@
 
-For the ratio $w=w_1/w_2$, we define the function
+%For the case $\sigma_1^2=\sigma_2^2=\sigma^2$, 
+We define the function
 \begin{align}
-	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& + (n_1 w^2 +n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+	\val(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+			& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
 \end{align}
-\cor Under the setting of Lemma \ref{prop_model_shift_tight}, again using concentration for random vectors with i.i.d.
-entries, Lemma \ref{largedeviation}, we can obtain that for the validation loss in \eqref{approxvalid},
-\be\label{boundv-w}\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2+\e})\right)\ee
+%\cor Under the setting of Lemma \ref{prop_model_shift_tight}, 
+For the isotropic model with $\sigma_1^2=\sigma_2^2=\sigma^2$, using concentration for random vectors with i.i.d.
+entries, Lemma \ref{largedeviation}, we can obtain that $\val(\hat{B}; w_1, w_2)= \val(v) \cdot \left( 1+\OO(p^{-1/2+\e})\right)$.
+Hence the validation loss in \eqref{approxvalid} reduces to
+\be\label{boundv-w}
+\wt f(\hat B; v)=\left[N_2\cdot \val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
+\ee
 with high probability for any constant $\e>0$.
-\nc Thus for the following discussions, it suffices focus on the behavior of $\val (w)$.
-Let $\hat w$ the minimizer of $\val(w)$.
+\nc Thus for the following discussions, it suffices to focus on the behavior of $\val (v)$.
+Let $\hat w$ the minimizer of $\val(v)$.
 The proof will consist of two main steps.
 \begin{itemize}
-	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} gives that $|\hat v - \hat w|=\OO(p^{-1/2+\e})$ whp.
+	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} will give that $|\hat v - \hat w|=\OO(p^{-1/2+\e_0/2+\e})$ whp.
 	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
@@
 %Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
-We have that the minimizer for $\val(w)$ satisfies
-	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\ee
+For the isotropic model, the minimizer for $\val(v)$ satisfies
+	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{whp}\ee
 	for some constant $C>0$.
@@
 \begin{proof}
-First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.
+To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof.
+First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$.
+Hence it suffices to assume that $w\ge 0$.
 
@@
 \begin{align}
-	\val(w) &= n_1\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + n_2\left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& + n_1\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ n_2\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }.
+	\val(w) &=  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+			& +  \frac{\rho_1}{\rho_2}\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ \sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }.
 \nonumber
@@
 Notice that 
-$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
+$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
 are increasing functions in $w$. Hence taking derivative of $\val(w)$ with respect to $w$, we obtain that
 \begin{align*}
-\val'(w) \ge &~ n_1\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
-+&~ n_2\left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-		-&~ 2 n_2 \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_2 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
+\val'(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
++&~ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+		-&~ 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
 \end{align*}
@@
 \begin{align*}
-\cal A :&= \frac{n_1}{n_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
+\cal A :&= \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
 \end{align*}
@@
 \begin{align}
-	\val'(w) &\le n_1 \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + n_2\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-	&~ + n_1(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }\\
-			& = n_1 \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
+	\val'(w) &\le \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+	&~ + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }\\
+			& = \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
 \end{align}
 where the matrix $\cal B$ is
-$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
+$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{\rho_2}{\rho_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
 Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
@@
 $$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
-Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly decreasing for $w<w_2$. Hence we must have $\hat w\le w_2$.
+Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly decreasing for $w<w_2$. Hence we must have $\hat w\ge w_2$.
 
@@
 
-Combining \eqref{hatw_add1} and \eqref{boundv-w}, we obtain that whp,
+For the rest of this section, we choose the parameters that satisfy the following relations: \be\label{choiceofpara}
+pd^2 \sim \sigma^2 \sim 1,\quad p^{c_0}\kappa^2  \le \sigma^2 \le p^{1-\e_0-c_0} \kappa^2,
+\ee
+for some small constant $c_0>0$. We will explain below why we make this choice. Before that, we first prove the following result on the optimizer $\hat v$.
+\begin{lemma}
+For the isotropic model, we have
 \be\label{hatv_add1} 
-|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2+\e} 
-\ee
+|\hat v - 1|= \OO\left(\cal E\right) \quad \text{whp}, \ee
+where we used the notation
+$$\cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 + 3\e}. $$
+\end{lemma}
+\begin{proof}
+..........
+In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-\hat w| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'(w)|\gtrsim d^2$.
+Moreover, under the choice \eqref{choiceofpara} we have
+$$\val(w) =\OO(d^2),\quad \text{for}\quad   |w-\hat w|\le 2C\cal E.$$  
+Thus we obtain that for $|w-\hat w|\ge 2C\cal E$,
+$$\left|\val(w) - \val(\hat w)\right|\ge |\val(w)-\min(\val(w_1),\val(w_2))|\gtrsim d^2 \cal E \gtrsim \cal E \cdot \val(\hat w),$$
+which leads to 
+$$\wt f(\hat B; w) > \wt f(\hat B; \hat w) \quad \text{whp}.$$
+Thus $w$ cannot be a minimizer of $\wt f(\hat B; v) $ by \eqref{boundv-w}, and we must have $|\hat v - \hat w|\le 2C\cal E$. Together with \eqref{hatw_add1}, we conclude \eqref{choiceofpara}.
+\end{proof}
+
 Inserting it into \eqref{eq_te_mtl_2task} and using a similar concentration result as in \eqref{boundv-w}, we get whp,
@@
 On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+2\e}\kappa^2  \ll d^2 \ll \kappa^2$.
-The above considerations lead to the following choices of parameters: there exists a constant $c>0$ such that
-\be\label{choiceofpara}
-pd^2 \sim \sigma^2 \sim 1,\quad p^{c}\kappa^2  \le \sigma^2 \le p^{1-c} \kappa^2.
-\ee
+The above considerations lead to the following choices of parameters in \eqref{choiceofpara}.
+
 Under this choice, we can write 
@@
 \end{proof}
-\todo{add a transition example}
+%\todo{add a transition example}
 

### 2020-06-01 writeup/transfer.tex
intro

@@
 
-\begin{figure}
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
-		\caption{Task similarity}
-		\label{fig_model_shift}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
-		\caption{Data size}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
-		\caption{Covariate shift}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{Three takeaways of our theory in Section \ref{sec_insight}.
-	(a) As task model distance increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
-	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Proposition \ref{prop_data_size}).
-	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Proposition \ref{prop_covariate}).
-	The $y$-axis measures the performance of MTL minus STL.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
-
 \textbf{Algorithmic consequence.}
@@
 
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+			\For{$j = 1,\dots, T$}
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+			\EndFor
+			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+				\State \textbf{break}
+			\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
 \begin{proposition}[Source/task data ratio]\label{prop_data_size}
@@
 In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-The result can be also found in Appendix \ref{app_proof_32}.
+The result can be found in Appendix \ref{app_proof_32}.
 
@@
 Algorithm \ref{alg_inc_train} describes the procedure.
-
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-				\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy after epoch $i$.
-				\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-					\State \textbf{break}
-				\EndIf
-			\EndFor
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
 

### 2020-06-02 writeup/intro.tex
intro wip

@@
 
-In this work, we consider the setting of high-dimensional linear regression and focus on predicting a particular task that only contains limited amount of labeled data.
-Following Hastie et al.
-\cite{HMRT19} and Bartlett et al.
-\cite{BLLT20}, we assume that for every task $1\le i\le t$, its features are random vectors $x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d.
+\textbf{Setup and Main results.}
+In this work, we consider the setting of high-dimensional linear regression \cite{HMRT19,BLLT20} and focus on predicting a particular task that only contains limited amount of labeled data.
+%Following Hastie et al.  and Bartlett et al. \cite{},
+We assume that for every task $1\le i\le t$, its features are random vectors $x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d.
 entries with mean zero and unit variance, and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-Let $n_i$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
+Let $n_i = \rho_i \times p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
 The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d.
 random noise with mean zero and variance $\sigma^2$.
-Without loss of generality, let the $t$-th task denote the target task.
-Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-Hence adding more labeled data can help improve its test performance.
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-We focus on the hard parameter sharing architecture with a linear shared layer $B\in\real^{p\times r}$ for all tasks and a separate prediction head $\set{W_i \in \real^{r}}_{i=1}^t$ for each task \cite{R17,MTDNN19,WZR20}.
+We focus on the hard parameter sharing architecture with a linear shared layer for all tasks and a separate prediction head for each task \cite{R17,MTDNN19,WZR20}.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator for the target task.
-Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-We define these precisely in Section \ref{sec_setup}.
-We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
+Our main theoretical contribution is to develop a new technical tool for a quantity that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
+%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
+%Without loss of generality, let the $t$-th task denote the target task.
+%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
+%Hence adding more labeled data can help improve its test performance.
+%$B\in\real^{p\times r}$
+%$\set{W_i \in \real^{r}}_{i=1}^t$
 
@@
 
-\textbf{Main results.}
-We revisit the bias-variance tradeoff of the multi-task estimator.
-Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, hence resulting in a positive effect of variance reduction.
-The bias of the multi-task estimator results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
-Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
+%We revisit the bias-variance tradeoff of the multi-task estimator.
+%Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, hence resulting in a positive effect of variance reduction.
+%The bias of the multi-task estimator results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
+%Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
 
-Our first contribution is to develop a new technical tool for a quantity that arises naturally from the analysis of two tasks.
-Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which extends a well-known result on the trace of $(X_1^{\top}X_1)^{-1}$ for the single-task setting \cite{S07}.
-Our analysis yields nearly optimal concentration error, which may be of independent interest.
-Using this tool, we show the following results in Section \ref{sec_main}.
-\squishlist
-	\item We provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
+\begin{theorem}[Informal]\label{lem_cov_shift_informal}
+	In the setting of two tasks, let $a_1, a_2$ be fixed values solved from deterministic equations given by $\rho_1, \rho_2$ and the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1}\Sigma_1^{1/2}$.
+	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+	\begin{align*}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2} +\bigo{\frac{\|\Sigma_2\|}{p^{1/2-\epsilon}}}.
+	\end{align*}
+\end{theorem}
+
+%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
+Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting \cite{S07}, e.g. when $X_1 = 0$.
+The concentration error of our result, which is on the order of $O(p^{-1/2+\varepsilon})$, is nearly optimal.
+Using this tool,
+%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
+%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
+%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
+%distribution with covariance matrix $\Sigma_i$.
+%We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
 (i) two tasks with general covariance matrice; (ii) any number of tasks that have the same features (e.g. images).
-	\item We extend our result to transfer learning in the setting of high-dimensional linear regression.
-	We pool learnt source task representations into a shared body similar to $B$ in the hard parameter sharing architecture, as in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-	We show that the model shift bias can be captured by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-\squishend
+We extend our result to transfer learning in the setting of high-dimensional linear regression.
+We pool learnt source task representations into the shared body of the hard parameter sharing architecture, as in Taskonomy by Zamir et al. \cite{ZSSGM18}.
+We show that the bias of the transfer learning estimator can be captured by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+These results are described more precisely in Section \ref{sec_main}.
 
 Our second contribution is to use our newly developed tool to explain negative transfer in multi-task learning rigorously.
-In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
+In Section \ref{sec_insight}, we explain the three phenomena observed in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
+%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
+%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
+%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
 %		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
@@
 %	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
+%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
 Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy.
-We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
+%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
+%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
 %		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.

### 2020-06-02 writeup/setup.tex
sec 2
Sec A
intro wip

@@
 
-\begin{lemma}[Informal statement of Lemma \ref{lem_cov_shift}]\label{lem_cov_shift_informal}
-	In the setting of two tasks, let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-	\begin{align*}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2} +\bigo{\|\Sigma_2\| p^{-1/2+\epsilon}},
-	\end{align*}
 where $(a_1, a_2)$ is the solution to the following deterministic equations:
@@
 	\end{align*}
-\end{lemma}
 
@@
 	\squishlist
-		\item If $\Delta_{\bias} + \Delta_{\vari} < -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\bias} - \Delta_{\vari} < -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
 		\item If $\Delta_{\bias} - \Delta_{\vari} > \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
@@
 	\item \textit{Learning source task representations}: we obtain $\hat{\beta}_i^{\STL}$ from each source task, for $1\le i \le t-1$.
-		This forms a shared representation $\hat{B} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
+		This forms a shared representation ${B} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
 	\item \textit{Fine-tuning on the target task}: we learn the output layer $W_t\in\real^{t-1}$ similar to equation \eqref{eq_mtl}

### 2020-06-02 writeup/proof_examples.tex
sec B.1

@@
 \begin{itemize}
-	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} will give that $|\hat v - \hat w|=\OO(p^{-1/2+\e_0/2+\e})$ whp.
+	\item First, we show that $\hat{w}$ is close to $1$, and then \eqref{boundv-w} implies that $\hat v$ is also close to 1.
 	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
@@
 For the rest of this section, we choose the parameters that satisfy the following relations: \be\label{choiceofpara}
-pd^2 \sim \sigma^2 \sim 1,\quad p^{c_0}\kappa^2  \le \sigma^2 \le p^{1-\e_0-c_0} \kappa^2,
+pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 ,
 \ee
-for some small constant $c_0>0$. We will explain below why we make this choice. Before that, we first prove the following result on the optimizer $\hat v$.
-\begin{lemma}
-For the isotropic model, we have
+for some small constant $c_0>0$. We will explain below why we make this choice. Before that, we first show the following estimate on the optimizer $\hat v$: with high probability,
+%\begin{lemma}
+%For the isotropic model, we have
 \be\label{hatv_add1} 
-|\hat v - 1|= \OO\left(\cal E\right) \quad \text{whp}, \ee
-where we used the notation
-$$\cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 + 3\e}. $$
-\end{lemma}
-\begin{proof}
-..........
-In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-\hat w| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'(w)|\gtrsim d^2$.
+|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 /2+ 2\e}. 
+\ee
+%\end{lemma}
+%\begin{proof}
+ In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-\hat w| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'(w)|\gtrsim p d^2$.
 Moreover, under the choice \eqref{choiceofpara} we have
-$$\val(w) =\OO(d^2),\quad \text{for}\quad   |w-\hat w|\le 2C\cal E.$$  
+$$\val(w) =\OO(pd^2),\quad \text{for}\quad   |w-\hat w|\le 2C\cal E.$$  
 Thus we obtain that for $|w-\hat w|\ge 2C\cal E$,
-$$\left|\val(w) - \val(\hat w)\right|\ge |\val(w)-\min(\val(w_1),\val(w_2))|\gtrsim d^2 \cal E \gtrsim \cal E \cdot \val(\hat w),$$
-which leads to 
-$$\wt f(\hat B; w) > \wt f(\hat B; \hat w) \quad \text{whp}.$$
-Thus $w$ cannot be a minimizer of $\wt f(\hat B; v) $ by \eqref{boundv-w}, and we must have $|\hat v - \hat w|\le 2C\cal E$. Together with \eqref{hatw_add1}, we conclude \eqref{choiceofpara}.
-\end{proof}
+$$\left|\val(w) - \val(\hat w)\right|\ge |\val(w)-\min(\val(w_1),\val(w_2))|\gtrsim pd^2 \cal E \gtrsim \cal E \cdot \val(\hat w),$$
+which leads to $\wt f(\hat B; w) > \wt f(\hat B; \hat w)$ whp by \eqref{boundv-w}.
+Thus $w$ cannot be a minimizer of $\wt f(\hat B; v) $, and we must have $|\hat v - \hat w|\le 2C\cal E$.
+Together with \eqref{hatw_add1}, we conclude \eqref{hatv_add1}.
+%\end{proof}
 
-Inserting it into \eqref{eq_te_mtl_2task} and using a similar concentration result as in \eqref{boundv-w}, we get whp,
+Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$ again, we get whp,
 \begin{align}
 \te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
-&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
 \end{align}
@@
 Hence we need to choose that $p\cdot d^2 \sim \sigma^2$.
-On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+2\e}\kappa^2  \ll d^2 \ll \kappa^2$.
-The above considerations lead to the following choices of parameters in \eqref{choiceofpara}.
-
-Under this choice, we can write 
-\be\label{simple1}
-\begin{split}
-\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
-&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  
-\end{split}
-\ee
+On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$.
+The above considerations lead to the choices of parameters in \eqref{choiceofpara}.
+Moreover, under \eqref{choiceofpara} we can simplify \eqref{1Liso} to
+\begin{align}
+\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\ 
+&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
+\end{align}
 whp for some constant $\e>0$.
@@
 With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
-With slight abuse of notations, we shall write $\hat a_i$, $\hat b_k$ and $\hat M$ as $a_i$, $b_k$ and $M$, respectively, throughout the rest of this section.
+With slight abuse of notations, we shall write $\hat a_i$, $\hat b_k$ and $\hat M$ as $a_i$, $b_k$ and $M$ throughout the rest of this section.
 
@@
 	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
-	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of Lemma \ref{prop_model_shift_tight}) that
+	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of it) that
 \be\label{Deltabeta} 
@@
 	where 
-	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
+	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
 %\begin{align*}
@@
 \be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-	we have that $\delta_{\vari} > \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
-	\[   pd^2  <  \sigma^2 \Phi(\rho_1, \rho_2)\cdot \left(\bigbrace{1 + \sqrt{\frac 1 {\rho_1}}}^{-4} - \oo(1)\right), \]
-Plugging into $\rho_1>40$, we obtain the first statement of Proposition \ref{prop_dist_transition}.
+	we have that $\delta_{\vari} > \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
+	\[  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \]
+Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$, it gives the first statement of Proposition \ref{prop_dist_transition}.
 
@@
 \be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-	we have that $\delta_{\vari} < \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
-	\[  p d^2  >  \sigma^2 \Phi(\rho_1, \rho_2) \cdot \left(\bigbrace{1 - \sqrt{\frac 1 {\rho_1}}}^{-4} +\oo(1)\right), \]
-Plugging into $\rho_1>40$, we obtain the second statement of Proposition \ref{prop_dist_transition}.
+	we have that $\delta_{\vari} < \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
+	\[ \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \]
+which gives the second statement of Proposition \ref{prop_dist_transition}.
 \end{proof}

### 2020-06-02 writeup/intro.tex
sec 2

@@
 When the information sources are heterogeneous, negative transfer--where multi-task learning (MTL)  performs worse than single-task learning (STL)--has often been observed \cite{PY09,AP16,BS17}.
-While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs has remained elusive in the literature \cite{R17}.
+While many empirical approaches are proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
@@
 % for learning from multiple linear regression tasks.
-We develop technical tools to analyze the tradeoff and use our tools to explain negative transfer precisely.
-Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
+We develop new tools to analyze the tradeoff and explain negative transfer precisely.
+%Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
 %We consider a setting where the target task has limited labeled data and show
@@
 entries with mean zero and unit variance, and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-Let $n_i = \rho_i \times p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
+Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
 The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d.
@@
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-Let $\hat{\beta}_t^{\MTL} = B W_t$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
+Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
 Our main theoretical contribution is to develop a new technical tool for a quantity that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
@@
 	\end{subfigure}
-	\caption{Three takeaways of our theory in Section \ref{sec_insight}.
-	(a) As task model distance increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
-	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Proposition \ref{prop_data_size}).
-	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Proposition \ref{prop_covariate}).
-	The $y$-axis measures the performance of MTL minus STL.}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	(a) As task model distance increases, we observe a transition from positive to negative transfer  (Prop. \ref{prop_dist_transition}).
+	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Prop. \ref{prop_data_size}).
+	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Prop. \ref{prop_covariate}).
+	$y$-axis denotes the prediction loss of STL minus MTL.}
 	\label{fig_model_shift_phasetrans}
@@
 \begin{theorem}[Informal]\label{lem_cov_shift_informal}
-	In the setting of two tasks, let $a_1, a_2$ be fixed values solved from deterministic equations given by $\rho_1, \rho_2$ and the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1}\Sigma_1^{1/2}$.
+	In the setting of two tasks, let $a_1, a_2$ be fixed values solved from deterministic equations of $\rho_1, \rho_2$ and the spectrum of $\Sigma_1^{1/2}\Sigma_2^{-1}\Sigma_1^{1/2}$.
 	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
@@
 (i) two tasks with general covariance matrice; (ii) any number of tasks that have the same features (e.g. images).
-We extend our result to transfer learning in the setting of high-dimensional linear regression.
-We pool learnt source task representations into the shared body of the hard parameter sharing architecture, as in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-We show that the bias of the transfer learning estimator can be captured by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+We extend our result to transfer learning
+%in the setting of high-dimensional linear regression.
+by pooling source task representations into the shared body of the hard parameter sharing architecture, following Taskonomy by Zamir et al. \cite{ZSSGM18}.
+We show that the bias of the transfer learning estimator is captured by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
 These results are described more precisely in Section \ref{sec_main}.
 
-Our second contribution is to use our newly developed tool to explain negative transfer in multi-task learning rigorously.
+Our next contribution is to use our newly developed tool to explain negative transfer in multi-task learning rigorously.
 In Section \ref{sec_insight}, we explain the three phenomena observed in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.

### 2020-06-02 writeup/intro.tex
fig 1

@@
 	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	(a) As task model distance increases, we observe a transition from positive to negative transfer  (Prop. \ref{prop_dist_transition}).
-	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Prop. \ref{prop_data_size}).
-	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Prop. \ref{prop_covariate}).
+	We observe that MTL performance
+	(a) transitions from positive to negative transfer as \textit{task model distance} increases (Prop. \ref{prop_dist_transition});
+	(b) transitions from positive to negative transfer as source/target \text{data size} increases (Prop. \ref{prop_data_size});
+	(c) gets worse as \textit{covariate shift} gets more severe (increasing $\lambda$) and source/target \textit{data size} increases (Prop. \ref{prop_covariate}).
 	$y$-axis denotes the prediction loss of STL minus MTL.}
@@
 	\begin{align*}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2} +\bigo{\frac{\|\Sigma_2\|}{p^{1/2-\epsilon}}}.
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2} +\bigo{{p^{-1/2+\epsilon}}}.
 	\end{align*}

### 2020-06-02 writeup/intro.tex
intro

@@
 Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
-Our main theoretical contribution is to develop a new technical tool for a quantity that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
+Our main theoretical contribution is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
 %Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
@@
 %Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting \cite{S07}, e.g. when $X_1 = 0$.
+Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1 = 0$ \cite{S07}.
 The concentration error of our result, which is on the order of $O(p^{-1/2+\varepsilon})$, is nearly optimal.
-Using this tool,
 %We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
@@
 %We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
-we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
-(i) two tasks with general covariance matrice; (ii) any number of tasks that have the same features (e.g. images).
-We extend our result to transfer learning
+Based on Theorem \ref{lem_cov_shift_informal}, we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
+(i) two tasks with general covariance matrice; (ii) many tasks with the same features (e.g. images).
+We extend our result to the transfer learning
 %in the setting of high-dimensional linear regression.
-by pooling source task representations into the shared body of the hard parameter sharing architecture, following Taskonomy by Zamir et al. \cite{ZSSGM18}.
-We show that the bias of the transfer learning estimator is captured by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
+setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
+We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
 These results are described more precisely in Section \ref{sec_main}.
@@
 Our next contribution is to use our newly developed tool to explain negative transfer in multi-task learning rigorously.
-In Section \ref{sec_insight}, we explain the three phenomena observed in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
+In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
+It is crucial that the concentration error of Theorem \ref{lem_cov_shift_informal} is $O(p^{-1/2+\varepsilon})$ so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
+The unexplained observations are caused by an error term that arises from the bias of $\hat{\beta}_t^{\MTL}$ -- we discuss these in Section \ref{sec_insight} more precisely.
+Theorem \ref{lem_cov_shift_informal} allows use to compare MTL performance under different covariate shift, measured by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+When $\beta_1 = \beta_2$, we show that for a certain family of bounded $M$ matrices, having no covariate shift, i.e. all singular values of $M$ being equal, yields the optimal MTL performance.
 %In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
@@
 %We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-Then, we analyze the benefit of multi-task learning for reducing the amount of labeled data needed to achieve comparable performance to single-task learning, which is a key empirical finding of Taskonomy.
+Finally, we analyze the benefit of MTL for reducing the amount of labeled data needed to achieve comparable performance to STL, which is a key empirical finding of Taskonomy.
 %We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.

### 2020-06-02 writeup/intro.tex
wip

@@
 \textbf{Setup and Main results.}
-In this work, we consider the setting of high-dimensional linear regression \cite{HMRT19,BLLT20} and focus on predicting a particular task that only contains limited amount of labeled data.
+We consider the high-dimensional linear regression setting \cite{HMRT19,BLLT20} to explain the above phenomena.
+We focus on predicting a particular task that only contains limited amount of labeled data.
 %Following Hastie et al.  and Bartlett et al. \cite{},
@@
 
-Our next contribution is to use our newly developed tool to explain negative transfer in multi-task learning rigorously.
+Our next contribution is to use our newly developed tool to explain negative transfer in multi-task learning precisely.
 In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.

### 2020-06-02 writeup/intro.tex

@@
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-In this work, we show that negative transfer is determined by the bias-variance tradeoff of multi-task learning estimators for the setting of high-dimensional linear regression.
+In this work, we show that negative transfer is determined by the bias-variance tradeoff of multi-task learning estimators for the high-dimensional linear regression setting.
 % for learning from multiple linear regression tasks.
@@
 
-Identifying negative transfer requires developing tight generalization bounds for both multi-task learning and single-task learning.
+Understanding negative transfer requires developing tight generalization bounds for both multi-task learning and single-task learning.
 In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented so that the error reduces as the data sizes of all tasks increase.
-For instance, the data sizes of all tasks are often assumed to be equal \cite{B00}.
+For instance, the data sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11,MPR16}.
 On the other hand, uneven data sizes or dominating tasks have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
-More recent work has shown the benefit of learning multi-task representations for certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-\todo{Add our ICLR work here.}
-\squishlist
-	\item \textbf{Task similarity:}
-	\item \textbf{Data sizes:}
-	\item \textbf{Covariate shift:}
-\squishend
-To rigorously study negative transfer, the technical challenge is to develop generalization bounds that scale tightly with properties of the data.
+%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
+When all tasks are sufficiently similar, it is known that adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
+To motivate our study, we describe simulation results for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
+In Figure \ref{fig_model_shift_phasetrans}, we observe that negative transfer occurs as (a) tasks become more different; (b) source/target data size increases.
+%\textbf{Task similarity:}
+%\textbf{Data sizes:}
+%\textbf{Covariate shift:}
+Furthermore, MTL performance is negatively affected when (c) the covariance matrices of the two tasks become more different.
+The observations highlight that we need to develop generalization bounds that scale tightly with properties of the data in order to study MTL performance.
 
-\textbf{Setup and Main results.}
+\textbf{Setup and Main Results.}
 We consider the high-dimensional linear regression setting \cite{HMRT19,BLLT20} to explain the above phenomena.
@@
 		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\vspace{-0.075in}
 		\caption{Task similarity}
@@
 		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
+		\vspace{-0.075in}
 		\caption{Data sizes}
@@
 		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
+		\vspace{-0.075in}
 		\caption{Covariate shift}
@@
 	\label{fig_model_shift_phasetrans}
-	\vspace{-0.2in}
+	\vspace{-0.1in}
 \end{figure}

### 2020-06-02 writeup/setup.tex

@@
 
-\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
+\subsection{Applying Theorem \ref{thm_main_informal} to Analyze the Bias-Variance Tradeoff}
+%\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
 
@@
 %(ii) the positive effect from variance reduction;
-In order to analyze the tradeoff, we develop the following technical tool, which provides a tight bound for equation \eqref{eq_te_var}.
-
-where $(a_1, a_2)$ is the solution to the following deterministic equations:
-	\begin{align*}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-	\end{align*}
-
-\textbf{Remark.} When there is only the target task, $\rho_1$ equals zero.
-Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is a well-known result in random matrix theory \cite{S07}.
-Hence our result provides a necessary tool to analyze MTL in high dimensions.
-
-\subsection{Applying the Key Lemma to Analyze the Bias-Variance Tradeoff}
 
 \textbf{Multi-task learning.}
-We apply Lemma \ref{lem_cov_shift_informal} to provide a sharp analysis of the bias-variance tradeoff for two settings:
+We apply Theorem \ref{lem_cov_shift_informal} to provide a sharp analysis of the bias-variance tradeoff for two settings:
 (i) two tasks with general covariance matrices;
@@
 The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.
+
+%In order to analyze the tradeoff, we develop the following technical tool, which provides a tight bound for equation \eqref{eq_te_var}.
+%where $(a_1, a_2)$ is the solution to the following deterministic equations:
+%	\begin{align*}
+%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+%	\end{align*}
+
+\textbf{Remark.} When there is only the target task, $\rho_1$ equals zero.
+Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is a well-known result in random matrix theory \cite{S07}.
+Hence our result provides a necessary tool to analyze MTL in high dimensions.

### 2020-06-02 writeup/intro.tex
sec 12

@@
 First, for the setting of high-dimensional linear regression, we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
-We provide a sharp analysis of the tradeoff and extend the result to transfer learning.
+We provide an analysis of the tradeoff and extend the result to transfer learning.
 We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
@@
 
-\textbf{Setup and Main Results.}
+%\textbf{Setup and Main Results.}
 We consider the high-dimensional linear regression setting \cite{HMRT19,BLLT20} to explain the above phenomena.
@@
 Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
-Our main theoretical contribution is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
+\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
 %Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
@@
 %We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
-Based on Theorem \ref{lem_cov_shift_informal}, we provide a sharp analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
+Based on Theorem \ref{lem_cov_shift_informal}, we provide an analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
 (i) two tasks with general covariance matrice; (ii) many tasks with the same features (e.g. images).
@@
 
-Our next contribution is to use our newly developed tool to explain negative transfer in multi-task learning precisely.
+\textit{Our next contribution} is to use our newly developed tool to explain negative transfer in multi-task learning precisely.
 In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
@@
 The unexplained observations are caused by an error term that arises from the bias of $\hat{\beta}_t^{\MTL}$ -- we discuss these in Section \ref{sec_insight} more precisely.
-Theorem \ref{lem_cov_shift_informal} allows use to compare MTL performance under different covariate shift, measured by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shift, measured by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
 When $\beta_1 = \beta_2$, we show that for a certain family of bounded $M$ matrices, having no covariate shift, i.e. all singular values of $M$ being equal, yields the optimal MTL performance.
@@
 
-Our last contribution is to connect our theory to practical problems of interest.
+\textit{Our last contribution} is to connect our theory to practical problems of interest.
 (i) We provide a single-task based metric to predict positive or negative transfer in multi-task learning.

### 2020-06-02 writeup/proof_examples.tex
minor

@@
 	\item First, we show that $\hat{w}$ is close to $1$, and then \eqref{boundv-w} implies that $\hat v$ is also close to 1.
-	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
+	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_2^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
 \end{itemize}
@@
 \begin{align}
-\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\ 
+\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\ 
 &+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
@@
 	\end{align}
-	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
+	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
 \be\label{Deltavar}
@@
 	Next for the model shift bias
-	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
+	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
 	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of it) that
 \be\label{Deltabeta} 
-\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_\beta}{ \Delta_{\beta}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
+\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
 	where 
-	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
+	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
 %\begin{align*}
-%		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
+%		\Delta_{\bias} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
 %		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
 %	\end{align*}
-%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
-%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
+%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\bias}$ as
+%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\bias} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
 \ee
@@
 Note that 
- \be\label{var-beta}\te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta .\ee
+ \be\label{var-beta}\te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} .\ee
 Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.
@@
 \be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-	we have that $\delta_{\vari} > \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
-	\[  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \]
+	we have that $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper101} to
+	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
 Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$, it gives the first statement of Proposition \ref{prop_dist_transition}.
@@
 \be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-	we have that $\delta_{\vari} < \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
-	\[ \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \]
+	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper102} to
+	\be\label{neg1} \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
 which gives the second statement of Proposition \ref{prop_dist_transition}.
@@
 \subsection{Supplement to Section \ref{sec_data_size}} \label{app_proof_32}
-We first prove Proposition \ref{prop_data_size}, which describes the effect of source task data size on the information transfer.
+We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.
 
 \begin{proof}[Proof of Proposition \ref{prop_data_size}]
-Following the above proof of Proposition \ref{prop_dist_transition}, we get from \eqref{upper101} that $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ whp if
-\be\label{pos1}
-pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
-and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ whp if
-\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
+Following the above proof of Proposition \ref{prop_dist_transition}, we see that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ whp if \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ whp if \eqref{neg1} holds.
+%\be\label{pos1}
+%pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
+%and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ whp if
+%\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
 %then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.
 
-For the first statement of Proposition \ref{prop_data_size}, we notice that the function
-$$\frac1{ \Phi(\rho_1, \rho_2)}=\frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}=(\rho_2-1) \left(1 +\frac{\rho_2-2}{\rho_1}+\frac{1}{\rho_1(\rho_1+\rho_2)}\right)^{-1} $$
-is strictly increasing with respect to $\rho_1$ as long as $\rho_2> 2$. In particular, by taking $\rho_1\to \infty$, we get the bound:
-$$\frac{\rho_1(\rho_1+\rho_2)(\rho_2-1)}{(\rho_1+\rho_2-1)^2} \cdot \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  (\rho_2-1) \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4.$$
-Hence as long as we take 
- $$pd^2  \le \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
- then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds whp. Plugging into $\rho_1>50$, we obtain the first statement.
+We first explain the meaning of the condition 
+\be\label{explainpsi}\Psi(\beta_1,\beta_2)>2/(\rho_2-1).\ee 
+%For the first statement of Proposition \ref{prop_data_size}, we 
+Notice that the function
+$$ \Phi(\rho_1, \rho_2)=\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}=\frac{1}{\rho_2-1} \left(1 +\frac{\rho_2-2}{\rho_1}+\frac{1}{\rho_1(\rho_1+\rho_2)}\right)$$
+is strictly decreasing with respect to $\rho_1$ as long as $\rho_2> 2$, and $ \Phi(\rho_1, \rho_2)$ converges to $(\rho_2-1)^{-1}$ as $\rho_1\to \infty$.
+Moreover, we notice that $\left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} < 2$ for $\rho_1>40$.
+Hence \eqref{explainpsi} implies that \eqref{neg1} holds for all  large enough $\rho_1$.
+The transition from positive transfer when $\rho_1$ is small to negative transfer when $\rho_1$ is large is described by the two bounds in Proposition \ref{prop_data_size}.
 
-The two bounds in the second statement follows directly from \eqref{pos1} and \eqref{neg1}. We will use the following trivial inequalities 
+% $$ \Psi(\beta_1,\beta_2) \ge \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
+% then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds whp.
+Plugging into $\rho_1>50$, we obtain the first statement.
+......
+Note that for $\rho_1>40$, we have
+%$\gamma_+^{-1}$
+
+The two bounds follows directly from \eqref{pos1} and \eqref{neg1}. We will use the following trivial inequalities 
 \be\label{trivialphi}
-\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2} \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
+\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le  \Phi(\rho_1, \rho_2) \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
 \ee
@@
 
-\noindent{\bf Positive transfer.} With \eqref{trivialphi}, we see that \eqref{pos1} is implied by the following inequality
+\noindent{\bf Positive transfer.} With \eqref{trivialphi}, we see that \eqref{pos1} is implied by the following inequality:
 \begin{align}\label{pos1solv}
- & pd^2 \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <\sigma^2\cdot (1-\oo(1)) .
+ &  \Psi(\beta_1,\beta_2) \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}   < \gamma_+^{-1} .
  \end{align}
  then we can solve \eqref{pos1solv} to get
- $$\rho_1 < \frac{(\rho_2-2) \sigma^2}{pd^2 \cdot (1+\rho_1^{-1/2})^4 (\rho_2 - 1)\cdot (1+\oo(1))  - \sigma^2}  .$$
+ \be\label{addconstraint}\rho_1 < \frac{\rho_2-2}{\Psi(\beta_1,\beta_2) \cdot \gamma_+ (\rho_2 - 1) - 1}  .\ee
  %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
- Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.
+ This gives the first statement of Proposition \ref{prop_data_size}. %Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.
+
+ Note that if we require the RHS of \eqref{addconstraint} to be larger than $40$, that is, \eqref{addconstraint} is not a null condition. Then together with \eqref{explainpsi}, we get
+ $$ \rho_2 - 2>( 2\gamma_+ -1)\rho_1 .$$
+Plugging into $\rho_1>40$, we get $\rho_2 \ge 106$. This gives a constraint on $\rho_2$.
 
@@
  \noindent{\bf Negative transfer.} 
-With \eqref{trivialphi}, we see that \eqref{neg1} is implied by the following inequality
+With \eqref{trivialphi}, we see that \eqref{neg1} is implied by the following inequality:
 \begin{align}\label{neg1solv}
- & pd^2 \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >\sigma^2\cdot (1+\oo(1)) .
+ & \Psi(\beta_1,\beta_2)  \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) >  \Psi(\beta_1,\beta_2)  \cdot \frac{(\rho_2-1.5) \rho_1 }{\rho_1+\rho_2-2}> \gamma_-^{-1} .
  \end{align}
-If the following relation holds,
-$$pd^2 \cdot (1-\rho_1^{-1/2})^4(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) >  \sigma^2\cdot (1+\oo(1))  , $$
- then we can solve \eqref{neg1solv} to get
- $$\rho_1 > \frac{(\rho_2-2) \sigma^2}{pd^2 \cdot (1-\rho_1^{-1/2})^4(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1)\cdot (1-\oo(1))  - \sigma^2}  ,$$
- %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
- Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the lower bound for $\rho_1$ in order for negative transfer to hold.
+ where we used $(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) > \rho_2-1.5$ for $\rho_1>40$ and $\rho_2>110$. Then we can solve \eqref{neg1solv} to get
+ \be\label{addconstaint2}
+ \rho_1 > \frac{(\rho_2-2) \sigma^2}{\Psi(\beta_1, \beta_2) \cdot \gamma_-(\rho_2 - 1.5)  - 1}  ,
+ \ee
+which gives the second statement of Proposition \ref{prop_data_size}.
+We remark that condition \eqref{explainpsi} implies $\Psi(\beta_1, \beta_2) \cdot \gamma_-(\rho_2 - 1.5)>1$, so \eqref{addconstaint2} does not give a trivial bound. 
  \end{proof}
 
-Then we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio, denoted as $x^\star$.
+Next we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for taskonomy.
+%In the statement, we shall denote the data efficiency ratio as $\al^\star$.
 
 \begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
-	Then the data efficiency ratio $x^\star$ satifies 
-	\[ \al_l - \oo(1) \le x^\star\le \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}}, \]
+	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < (5\rho_1)^{-1} + (5\rho_2)^{-1}$.
+	Then the data efficiency ratio $x^\star$ satisfies 
+	\[ x_l  \le x^\star\le \frac{1}{\rho_1 + \rho_2} \bigbrace{  \frac{2}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}+1}, \]
 	where we denoted
-	$$\al_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
+	$$x_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
 \end{proposition}
@@
 \begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$\al n_1$ for task 1 and $\al n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
-Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(\al\rho_1,\al\rho_2)$.
+Suppose we have reduced number of datapoints---$x n_1$ for task 1 and $x n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
+Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(x\rho_1,x\rho_2)$.
 More precisely, we have
 	\begin{align*}
-		 a_1 = \frac{\rho_1(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(\al\rho_1 + \al\rho_2 - 1)}{\al(\rho_1 + \rho_2)^2} ,  \\
-		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}, \quad
-		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\al\rho_1 + \al\rho_2 - 1)}. 
+		 a_1 = \frac{\rho_1(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,\quad
+		& a_2 = \frac{\rho_2(x\rho_1 + \al\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,  \\
+		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}, \quad
+		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}. 
 	\end{align*}
-Moreover, we have that with high probability,
+Moreover, with high probability,
 	\be\label{reduceproof1}
 \begin{split}
-\te_i(\hat \beta(\al)) =  \frac{\sigma^2}{\al (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\beta}, \quad i=1,2.
+\te_i(\hat \beta_i^{\MTL}(x)) =  \frac{\sigma^2}{x (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\bias}, \quad i=1,2.
 \end{split}
 \ee
-Here the model shift biases $\delta^{(i)}_{\beta}$ satisfy that  
+ Here the model shift biases $\delta^{(i)}_{\bias}$ satisfy that  
 \be\nonumber %\label{Deltabeta} 
-\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_\beta^{(i)}}/{ \Delta_{\beta}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2,\ee	
-%In the setting of Proposition \ref{prop_data_efficiency}, we still have \eqref{hatw_add1}. 
-%%and by symmetry it suffices to focus on one of tasks, say task 2. 
-%Then using Lemmas \ref{lem_cov_shift} and \ref{prop_model_shift_tight}, and recalling \eqref{simplesovlea12} and \eqref{simplesovlea34}, we get that whp,
-%\be\label{reduceproof1}
-%\begin{split}
-%\te_i(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al (\rho_1+\rho_2) - 1}+ \bigo{p^{-1/2 + \varepsilon}}\right)+ \Delta^{(i)}_{\beta}, \quad i=1,2,
-%\end{split}
-%\ee
-%and
-%\be\label{reduceproof1}
-%\begin{split}
-%\te_2(\hat \beta(\al)) =\sigma^2\left( \frac{1}{\al ( \rho_1+\rho_2) - 1}+ \Delta^{(2)}_{\beta}+ \bigo{p^{-1/2 + \varepsilon}}\right),
-%\end{split}
-%\ee
-where $ \Delta^{(i)}_{\beta}$ are defined as 
+\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_{\bias}^{(i)}}/{ \Delta_{\bias}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2,\ee	
+where $ \Delta^{(i)}_{\bias}$ are defined as 
 \be \nonumber
-\Delta^{(i)}_{\beta} := pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,. 
+\Delta^{(i)}_{\bias} := pd^2 \frac{(x\rho_i)^2\cdot x (\rho_1+\rho_2)}{[x ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,. 
 \ee
-On the other hand, using Lemma \ref{lem_minv}, we have whp,
+On the other hand, using Lemma \ref{lem_minv} we have whp,
 \be\label{reduceproof2} 
-\te_i(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
+\te_i(\hat{\beta}_i^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
 \ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain a trivial lower bound $\al^*\ge \al_l -\oo(1)$, where
-$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
-In fact, one can see that if $\al\le \al_l$, then we have 
-$$ \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} \ge \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
-that is $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\beta}$.
-Next we try to get more precise bounds on $\al^*$.
-In the following discussions, we only consider $\al$ such that $\al(\rho_1+\rho_2) \ge \al_l (\rho_1+\rho_2) \ge \min(\rho_1,\rho_2)$.
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain the lower bound $x^*\ge x_l $. 
+%where
+%$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
+In fact, one can see that if $x< x_l$, then we have 
+$$ \frac{2\sigma^2}{x (\rho_1+\rho_2) - 1} > \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
+that is, $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\bias}$.
+
+Then we try to obtain an upper bound on $x^*$.
+In the following discussions, we only consider $x$ such that $x\ge \al_l$.
+In particular, we have $x(\rho_1+\rho_2) \ge x_l (\rho_1+\rho_2) \ge \min(\rho_1,\rho_2)$.
 
@@
 
-\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\le \al$ if $\al$ satisfies
+\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^*\le x$ if $x$ satisfies {\cor to revise}
 \be\nonumber
@@
 %g(M)&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1)(X_1^{\top}X_1 +X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)\right] \\ 
-%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  =: \delta_\beta(M)+ g_{\vari}(M),
+%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  =: \delta_{\bias}(M)+ g_{\vari}(M),
 %\end{split}
@@
 %\end{align}
-%where $(a_1,a_2)$ satisfies \eqref{eq_a12extra}. On the other hand, by Theorem \ref{thm_model_shift} we can estimate $\delta_\beta$ as
+%where $(a_1,a_2)$ satisfies \eqref{eq_a12extra}. On the other hand, by Theorem \ref{thm_model_shift} we can estimate $\delta_{\bias}$ as
 %\be \label{deltabeta_extra}
 %\begin{split}
-%&\left| \delta_{\beta}(M_0) - \frac{d^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \tr\left[\Sigma_1^{1/2}{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\Sigma_1^{1/2}\right]\right| \le \delta + \OO(p^{1-\e}d^2),
+%&\left| \delta_{\bias}(M_0) - \frac{d^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \tr\left[\Sigma_1^{1/2}{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\Sigma_1^{1/2}\right]\right| \le \delta + \OO(p^{1-\e}d^2),
 %\end{split}
@@
 Then we write 
-$$ \te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta - \delta_{\vari}^{(2)},$$
+$$ \te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
 where 
@@
 satisfies \eqref{Deltavar} but with $\sigma^2$ replaced with $\sigma_2^2$, 
-$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
+$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
 satisfies \eqref{Deltabeta}, and 
@@
 \end{align*}
-%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_\beta + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
-%where $\Delta_\beta:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
+%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
+%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
 To estimate this new term, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
@@
 $$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
-Next we compare $\delta_{\vari}$ with $\delta_\beta + \delta_{\vari}^{(2)}$. Our main goal is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
+Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main goal is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
 
@@
 
-Note that the condition $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$ means the we have $\delta_{\vari}>\delta_{\beta} $ by Proposition \ref{prop_dist_transition}.
-Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\beta}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$.
+Note that the condition $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$ means the we have $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
+Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$.
 
@@
 \ee
-then we have $\delta_{\vari} > \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
+then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
 \begin{align*}
@@
 \ee
-then we have $\delta_{\vari} < \delta_{\beta} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
+then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
 \begin{align*}

### 2020-06-02 writeup/proof_main.tex
minor

@@
 
+\begin{remark}
 One can see from the above proof that the main error, $\delta$, of Theorem \ref{thm_model_shift} comes from approximating $\delta_{\bias}$ by $\wt\delta_{\bias}$ in \eqref{bounddelta-}.
@@
 We leave this problem to future study.
+\end{remark}
 

### 2020-06-02 writeup/transfer.tex
sec B.1
sec 12
minor

@@
 	\squishlist
-		\item If $\Psi(\beta_1, \beta_2) < \gamma_{-} \cdot \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) \ge \gamma_{+} \cdot \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) < \gamma_{+}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) \ge \gamma_{-}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 \begin{proposition}[Source/task data ratio]\label{prop_data_size}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 150$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
 	We have that
@@
 $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1}{\gamma_-} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3) - \gamma_{-}^{-1}}$, then w.h.p.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1}{\gamma_-} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \gamma_{-}^{-1}}$, then w.h.p.
 $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.

### 2020-06-02 writeup/setup.tex

@@
-\section{A Sharp Analysis of the Tradeoff for Multi-Task and Transfer Learning}
+\section{Multi-Task vs. Single-Task Learning: The Bias-Variance Tradeoff}
 \label{sec_main}
@@
 
-\subsection{The Bias-Variance Tradeoff}\label{sec_setup}
+\subsection{Problem Setup}\label{sec_setup}
 
@@
 
-\subsection{Applying Theorem \ref{thm_main_informal} to Analyze the Bias-Variance Tradeoff}
-%\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
+\subsection{Analyzing the Tradeoff via Random Matrix Theory}
 
@@
 %(ii) the positive effect from variance reduction;
+
+%\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
 
@@
 This will be the focus of Section \ref{sec_insight}.
+
+\textbf{Proof Overview.}
 The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.

### 2020-06-02 writeup/setup.tex
sec 3

@@
 
-We first describe the bias-variance tradeoff in our setting more formally.
-Then, we develop a key lemma that arises naturally in the high-dimensional setting.
-Finally, we apply the lemma to provide a sharp analysis of the bias-variance tradeoff of multi-task and transfer learning in our setting.
+We begin by describing our problem setup more formally.
+Then, we describe our main result for the bias-variance tradeoff of multi-task and transfer learning estimators in our setting.
 
@@
 Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ to be the single-task optimum.
-Hence there is no positive or negative transfer.
+Hence, applying equation \eqref{eq_mtl} results in the same estimator as single-task learning.
 We define $\hat{\beta}_t^{\MTL}$ by two steps:
@@
 %= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t) \\
-which can be further decomposed as the bias-variance tradeoff.
+which can be further decomposed as the bias and variance of $\hat{\beta}$.
 The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
-In order to relate the tradeoff to properties of the data, we need tight concentration bounds for the bias and variance.
-For this purpose, we consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
+%In order to relate the btradeoff to properties of the data, we need tight concentration bounds for the bias and variance.
+We consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
 We focus on a setting where $\rho_t$ is small compared to $\set{\rho_i}_{i=1}^{t-1}$.
@@
 %We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
+We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$ is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+For a matrix $X\in\real^{p_1\times p_2}$, let $\lambda_{\min}(X)$ denote its minimum singular value.
 
@@
 \end{align}
-Here $\hat{v}\in\real$ denotes a fixed value that depends on the output layer weights.
+Here $\hat{v}\in\real$ denotes a fixed value that depends on the output layer weights $W_1, W_2$.
 The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
@@
 \textbf{Multi-task learning.}
-We apply Theorem \ref{lem_cov_shift_informal} to provide a sharp analysis of the bias-variance tradeoff for two settings:
+We provide a sharp analysis of the bias-variance tradeoff for two settings:
 (i) two tasks with general covariance matrices;
@@
 
-\textbf{Remark.} When there is only the target task, $\rho_1$ equals zero.
-Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is a well-known result in random matrix theory \cite{S07}.
-Hence our result provides a necessary tool to analyze MTL in high dimensions.
+%\textbf{Remark.} When there is only the target task, $\rho_1$ equals zero.
+%Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is a well-known result in random matrix theory \cite{S07}.
+%Hence our result provides a necessary tool to analyze MTL in high dimensions.

### 2020-06-02 writeup/transfer.tex
sec 3

--- 2020-06-01 writeup/transfer.tex
@@
-\section{Explaining the Phenomena of Negative Transfer in Multi-Task Learning}\label{sec_insight}
+\section{Explaining Negative Transfer in an Isotropic Setting}\label{sec_insight}
 
-Based on Lemma \ref{lem_cov_shift_informal}, we rigorously explain the phenomena of negative transfer in multi-task learning.
+We provide precise explanations to the phenomena of negative transfer in multi-task learning.
 We explain from three perspectives, including \textit{task similarity}, \textit{data size} and \textit{covariate shift}.
@@
 %We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
-Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
-{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
+%Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
+%{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
 Our result below will provide an explanation to this phenomenon.
@@
 Using the isotropic model, we consider what happens if we vary the source task data size.
-Figure \ref{fig_size} provides a simulation result for such a setting.
-We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-Our result below explains this phenomenon.
+%Figure \ref{fig_size} provides a simulation result for such a setting.
+%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+Our result below explains the phenomenon of Figure \ref{fig_size}.
 

### 2020-06-02 writeup/setup.tex
add overview

--- 2020-06-02 writeup/setup.tex
@@
 
-\textbf{Proof Overview.}
-The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
-The result for more than two tasks is deferred to Appendix \ref{app_proof_many_tasks}.
+\textbf{Proof Overview.} The proof of Theorem \ref{lem_cov_shift_informal} uses the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
+Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
+In particular, when $z=0$, $\tr R_\infty(0)$ gives the right hand side of \eqref{eq_introX1X2}, which concludes Theorem \ref{lem_cov_shift_informal}.
+The details can be found in Appendix \ref{sec_maintools}-\ref{sec_Gauss}.
+
+With  Theorem \ref{lem_cov_shift_informal}, we can calculate $\te(\hat{\beta}_t^{\MTL})$ and the term in \eqref{eq_te_var}, and their differences are given approximately by $\Delta_{\vari}$.
+On the other hand, the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
+During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
+All these estimates combined give Theorem \ref{thm_main_informal}, and the details are presented in Appendix \ref{app_proof_main}.
+
+%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
+We have a similar theorem for more than two tasks but with the matrix $X_i=X$, and it is deferred to Appendix \ref{app_proof_many_tasks}.
 

### 2020-06-02 writeup/app_exp.tex
sec 3.1
sec 3.3
sec 4

@@
 \section{Supplementary Materials for the Experiments}
+
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+			\For{$j = 1,\dots, T$}
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+			\EndFor
+			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+				\State \textbf{break}
+			\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Synthetic Settings}\label{app_synthetic}
+	In Figure \ref{fig_model_shift_phasetrans} (c), we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
+
+\subsection{Image and Text Classification Settings}
 
@@
 As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
-	\label{fig_covariate}
+	\label{fig_covariate_app}
 \end{figure}
+
+\textbf{Task similarity.} We validate that MTL performs better when the source task is more similar to the target task.
+We show the result on the sentiment analysis tasks.
+For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+Figure \ref{fig_ab_sim} confirms the result.
+Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

### 2020-06-02 writeup/experiments.tex
sec 4

@@
-\section{Practical Connections for Detecting and Mitigating Negative Transfer}
+\section{Practical Connections: Detecting and Mitigating Negative Transfer}
 
@@
 The results show that STL performances are indicative of MTL performances.
-
-\textbf{Task similarity.} We validate that MTL performs better when the source task is more similar to the target task.
-We show the result on the sentiment analysis tasks.
-For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
-Figure \ref{fig_ab_sim} confirms the result.
-Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

### 2020-06-02 writeup/proof_examples.tex
add overview
sec 4

@@
 
-To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
-\end{align*}
-	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
-	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
-
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	In the setting described above, assume that $\rho_1, \rho_2>1$.
-	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
-	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{proposition}
-Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
-
 \begin{proof}[Proof of Proposition \ref{prop_covariate}]

### 2020-06-02 writeup/transfer.tex
sec 4

@@
 
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
 \begin{proposition}[Source/task data ratio]\label{prop_data_size}
@@
 By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-The result is left to Appendix \ref{app_proof_33}.
+To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
+\begin{align*}
+		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
+\end{align*}
+	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
+	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
+The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
+
+\begin{proposition}[Covariate shift]\label{prop_covariate}
+	In the setting described above, assume that $\rho_1, \rho_2>1$.
+	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
+	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
+\end{proposition}
+Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
+%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
+
+%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
+
 %We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?

### 2020-06-02 writeup/intro.tex
sec 3
add overview
fred comments

@@
 %Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
-By combining multiple information sources, it is possible to share all the information in the same model.
+%By combining multiple information sources, it is possible to share all the information in the same model.
+In many settings, multiple information sources are available to help solve a particular task.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
-The performance of multi-task learning depends on the relationship of the information sources \cite{C97}.
+The performance of multi-task learning depends on the relationship between the information sources and the task \cite{C97}.
 When the information sources are heterogeneous, negative transfer--where multi-task learning (MTL)  performs worse than single-task learning (STL)--has often been observed \cite{PY09,AP16,BS17}.
@@
 	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-	\begin{align*}
+	\begin{align}\label{eq_introX1X2}
 		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2} +\bigo{{p^{-1/2+\epsilon}}}.
-	\end{align*}
+	\end{align}
 \end{theorem}
@@
 %distribution with covariance matrix $\Sigma_i$.
-%We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$  is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
 Based on Theorem \ref{lem_cov_shift_informal}, we provide an analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:

### 2020-06-02 writeup/setup.tex
fred comments

@@
 For a matrix $X\in\real^{p_1\times p_2}$, let $\lambda_{\min}(X)$ denote its minimum singular value.
+Let $\norm{X}$ denote the spectral norm of $X$.
 
@@
 %This part introduces a positive variance reduction effect from adding the source labels.
-Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the bias-variance tradeoff!
+Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
 %(i) the negative effect from model shift bias.
@@
 %Based on the result, we show how to determine positive versus negative transfer as follows.
-
+%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
 \begin{theorem}[Informal statement of Theorem \ref{thm_model_shift}]\label{thm_main_informal}
-	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$.
+	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
+	Let $\rho_2 > 1$ be a fixed value.
  	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
@@
 
-Theorem \ref{thm_main_informal} shows that as the source task data size increases, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
+Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target data size is small.
+For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
 %determined by the covariate shift matrix and the model shift.
@@
 %The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
-We have a similar theorem for more than two tasks but with the matrix $X_i=X$, and it is deferred to Appendix \ref{app_proof_many_tasks}.
+A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-06-02 writeup/transfer.tex
fred comments

@@
 We explain from three perspectives, including \textit{task similarity}, \textit{data size} and \textit{covariate shift}.
-We show how negative transfer occurs as a result in a simplified model and describe the algorithmic consequence.
+We show how negative transfer occurs by varying task similarity or data size.
+Then we show that when source task data size becomes large, covariate shift causes more negative effects.
 
@@
 \textbf{Algorithmic consequence.}
-As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
-If $\sigma_1$ is too large, the source task provides a negative transfer to the target.
-If $\sigma_1$ is small, the source task is more helpful.
+We can in fact extend the result to the cases where the noise variance is different.
+In this case, we will see that MTL is particularly effective.
+%As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+Concretely, suppose the noise variance $\sigma_1^2$ of task $1$ differs from the noise variance $\sigma_2^2$ of task $2$.
+If $\sigma_1^2$ is too large, the source task provides a negative transfer to the target.
+If $\sigma_1^2$ is small, the source task is more helpful.
 We leave the result to the Appendix in Proposition \ref{prop_var_transition}.
@@
 
-\begin{proposition}[Source/task data ratio]\label{prop_data_size}
+\begin{proposition}[Source/target data size]\label{prop_data_size}
 	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
@@
 \textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
-Formally, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
 %More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $x \cdot n_i$ datapoints from every task.
-The data efficiency ratio is defined as
+For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using $R \cdot n_i$ datapoints from every task.
+The data efficiency ratio roughly scales as
 \[ \argmin_{x\in(0, 1)} ~~
@@
 		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
+For example, the data efficiency ratio is $1$ if there is negative transfer.
 Using our tools, we show that in the isotropic model, the data efficiency ratio is
 equal to \[ \frac{1}{\rho_1 + \rho_2} {+ \frac{1}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
-In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-The result can be found in Appendix \ref{app_proof_32}.
+Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$, the transfer is positive.
+Hence the data efficiency ratio quantifies how effective is the positive transfer using MTL.
+%In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
+The precise statement can be found in Appendix \ref{app_proof_32}.
 
@@
 Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-Algorithm \ref{alg_inc_train} describes the procedure.
+\squishlist
+	\item We divide the source task data into $S$ batches.
+	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
+	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
+	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
+\squishend
 
@@
 
-By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
+%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
+To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in decreasing order.
+Let $\mu_{\min} < \mu < \mu_{\max}$ are fixed values that do not grow with $p$.
+Consider the following bounded set
 \begin{align*}
-		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
+		\cS_{\mu}\define\bigset{M \mid \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_p, \lambda_1 \le \mu_{\max}},
 \end{align*}
-	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
-	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.
+%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
 
 \begin{proposition}[Covariate shift]\label{prop_covariate}
-	In the setting described above, assume that $\rho_1, \rho_2>1$.
+	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
 	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
@@
 \end{proposition}
-Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
+The following proposition shows that when $n_1 \gg n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized when there is no covariate shift between source and target task.
+The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
+%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
 %This provides evidence that covariate shift is unfavorable when there are many source task datapoints,

### 2020-06-02 writeup/experiments.tex

@@
 \begin{table}
+\begin{minipage}[t]{.40\textwidth}
+	\centering
+	\begin{tabular}{c c c}
+		\toprule
+		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
+		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
+		\cmidrule(lr){2-3}
+		& {\bf MTL} & {\bf IncTrain} \\
+		\midrule
+		{\bf MLP}  & 100\% & \textbf{39\%} \\
+		{\bf LSTM} & \textbf{36\%} & 36\% \\
+		\bottomrule
+		\end{tabular}
+	\vspace{0.1in}
+	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
+	\label{tab:taskonomy}
+	\vspace{-0.2in}
+\end{minipage}%
+\quad
 \begin{minipage}[t]{.58\textwidth}
@@
 	\label{tab:mtl_better_than_stl}
-\end{minipage}
-\quad
-% \vspace{}
-\begin{minipage}[t]{.40\textwidth}
-	\centering
-	\begin{tabular}{c c c}
-		\toprule
-		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
-		\cmidrule(lr){2-3}
-		& {\bf MTL} & {\bf Alignment} \\
-		\midrule
-		{\bf MLP}  & 100\% & \textbf{39\%} \\
-		{\bf LSTM} & \textbf{36\%} & 36\% \\
-		\bottomrule
-		\end{tabular}
-	\vspace{0.1in}
-	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
-	\label{tab:taskonomy}
+	\vspace{-0.2in}
 \end{minipage}
@@
 
-\textbf{Baseline.} We compare Algorithm \ref{alg_inc_train} to a model trained with standard multi-task learning approaches.
-We measure the prediction accuracy of a particular target task.
+\textbf{Training procedures and baselines.} We use round-robin training schedule for the MTL model.
+We compare our incremental training scheduler of Algorithm \ref{alg_inc_train} to the round-robin training scheduler.
+We focus on the prediction accuracy of a particular target task.
 
@@
 	\label{fig_ablation}
+	\vspace{-0.15in}
 \end{figure}

### 2020-06-02 writeup/intro.tex
sec 2

@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
 		\vspace{-0.075in}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
 		\vspace{-0.075in}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
+		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
 		\vspace{-0.075in}

### 2020-06-02 writeup/setup.tex
sec 2

@@
 This will be the focus of Section \ref{sec_insight}.
+A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 
-\textbf{Proof Overview.} The proof of Theorem \ref{lem_cov_shift_informal} uses the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+\textbf{Proof Overview.} We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
+We use the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
 Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
 Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
-In particular, when $z=0$, $\tr R_\infty(0)$ gives the right hand side of \eqref{eq_introX1X2}, which concludes Theorem \ref{lem_cov_shift_informal}.
-The details can be found in Appendix \ref{sec_maintools}-\ref{sec_Gauss}.
+In particular, when $z=0$, $\tr[R_\infty(0)]$ gives the right hand side of \eqref{eq_introX1X2}, which concludes Theorem \ref{lem_cov_shift_informal}.
+The details can be found in Appendix \ref{sec_maintools} and \ref{sec_Gauss}.
 
-With  Theorem \ref{lem_cov_shift_informal}, we can calculate $\te(\hat{\beta}_t^{\MTL})$ and the term in \eqref{eq_te_var}, and their differences are given approximately by $\Delta_{\vari}$.
-On the other hand, the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
-During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-All these estimates combined give Theorem \ref{thm_main_informal}, and the details are presented in Appendix \ref{app_proof_main}.
+Using Theorem \ref{lem_cov_shift_informal} over \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL.
+The amount of reduced variance is given by $\Delta_{\vari}$.
+For the bias term of equation \eqref{eq_te_model_shift}, we apply a Gaussian concentration bound on $X_1^{\top}X_1$, whose expectation is $n_1^2\Sigma_1$.
+This results in the error term $\delta$, which scales as $(1 \pm 1/\sqrt{\rho_1})^4$.
+Then, we applying a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
+This leads to a negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
+%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
+The details are presented in Appendix \ref{app_proof_main}.
 
 %The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
-A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-06-02 writeup/experiments.tex
sec 4

@@
 		\midrule
-		{\bf MLP}  & 100\% & \textbf{39\%} \\
-		{\bf LSTM} & \textbf{36\%} & 36\% \\
+		{\bf MLP}  & 100\% & \textbf{xx\%} \\
+		{\bf LSTM} & \textbf{36\%} & xx\% \\
 		\bottomrule
@@
 
-\textbf{Data efficiency.}
+\textbf{MTL improves data efficiency ratio.}
 We measure the data efficiency ratio on the sentiment analysis tasks.
@@
 The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
+We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
 %If TREC is not included, we see that only $25\%$ of the labeled data is needed.
@@
 The results show that STL performances are indicative of MTL performances.
+
+\textbf{Validation our theory.} In Figure \ref{fig_ablation}, we validate the three components of our theory on the sentiment analysis dataset.
+The experimental procedure is left to Appendix \ref{app_it}.

### 2020-06-02 writeup/intro.tex
sec 4

@@
 To motivate our study, we describe simulation results for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
-In Figure \ref{fig_model_shift_phasetrans}, we observe that negative transfer occurs as (a) tasks become more different; (b) source/target data size increases.
+In Figure \ref{fig_model_shift_phasetrans}, we observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
 %\textbf{Task similarity:}
@@
 %\textbf{Covariate shift:}
-Furthermore, MTL performance is negatively affected when (c) the covariance matrices of the two tasks become more different.
-The observations highlight that we need to develop generalization bounds that scale tightly with properties of the data in order to study MTL performance.
+Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
+The observations highlight the need to develop generalization bounds that scale tightly with properties of the data in order to study MTL performance.
 

### 2020-06-02 writeup/intro.tex
rm tl

@@
 (i) two tasks with general covariance matrice; (ii) many tasks with the same features (e.g. images).
-We extend our result to the transfer learning
+%We extend our result to the transfer learning
 %in the setting of high-dimensional linear regression.
 %by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-These results are described more precisely in Section \ref{sec_main}.
+%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
+%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+%These results are described more precisely in Section \ref{sec_main}.
 

### 2020-06-02 writeup/proof_main.tex
rm tl

@@
 
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, that satisfy Assumption \ref{assm_secA2}.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
-Suppose $(B^{\star})^\top\Sigma B^{\star}$ is of full rank in the sense that $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
-	We have the following 
-	\begin{itemize}
-		\item We have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
-		$$\left(1 - \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
-
-		\item We have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
-		$$\left(1 - \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
-
-	\end{itemize}
-\end{theorem}
 %As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.

### 2020-06-02 writeup/setup.tex
rm tl

@@
 
-\textbf{Multi-task learning.}
-We provide a sharp analysis of the bias-variance tradeoff for two settings:
-(i) two tasks with general covariance matrices;
-(ii) any number of tasks that have the same features, i.e. $X_i = X_j$ for any $i\neq j$.
-The latter setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+%\textbf{Multi-task learning.}
+We provide a sharp analysis of the bias-variance tradeoff two tasks with general covariance matrices.
 We state our result for two tasks as follows.
@@
 %, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-\begin{theorem}[Informal statement of Theorem \ref{thm_model_shift}]\label{thm_main_informal}
+\begin{theorem}\label{thm_main_informal}
 	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
@@
 This will be the focus of Section \ref{sec_insight}.
-A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 
@@
 %The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
+Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+\begin{theorem}\label{thm_many_tasks}
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, that satisfy Assumption \ref{assm_secA2}.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
+Suppose $(B^{\star})^\top\Sigma B^{\star}$ is of full rank in the sense that $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$.
+Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
+	We have the following
+	\squishlist
+		\item We have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
+		$$\left(1 - \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
+		\item We have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
+		$$\left(1 - \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
+	\squishend
+\end{theorem}
+%A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 
+\iffalse
 \textbf{Transfer learning.}
@@
 The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.
+\fi
 

### 2020-06-02 writeup/intro.tex
abstract

@@
 \begin{abstract}
-When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
-In this work, we address this question by studying
+%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
+	Multi-task learning is a powerful approach to solve complex tasks in many applications such as image and text classification.
+	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
+	In this work, we study this question formally by considering three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
 % the performance of predicting a particular task given multiple tasks.
-a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
-First, for the setting of high-dimensional linear regression, we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
-We provide an analysis of the tradeoff and extend the result to transfer learning.
-We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
-Second, we identify three components including task similarity, data size and covariate shift to explain negative transfer in multi-task learning rigorously.
-Finally, we show practical implications of our theory for detecting and mitigating negative transfer.
-We propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
-We validate our theory and our proposed method on image and text classification tasks.
+%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
+	First, we show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of multi-task estimators.
+	We analyze the bias-variance tradeoff by developing technical tools using random matrix theory.
+	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
+	%We develop a technical tool to analyze the.
+%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
+	Second, we apply our tools to show that the performance of multi-task learning is negatively affected as a result of: (a) decreased task similarity;
+	(b) increased source sample size; (c) covariate shift under increased source sample sizes.
+	Finally, we validate the three components of our theory on image and text classification tasks.
+	Inspired by our theory, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
+%	We validate our theory and our proposed method .
 \end{abstract}

### 2020-06-02 writeup/intro.tex
intro

@@
 In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented so that the error reduces as the data sizes of all tasks increase.
-For instance, the data sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11,MPR16}.
-On the other hand, uneven data sizes or dominating tasks have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
+For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11,MPR16}.
+On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause of negative transfer \cite{YKGLHF20}.
 %The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
-When all tasks are sufficiently similar, it is known that adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
-To motivate our study, we describe simulation results for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
-In Figure \ref{fig_model_shift_phasetrans}, we observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
+When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
+To motivate our study, Figure \ref{fig_model_shift_phasetrans} shows three examples for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
+We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
 %\textbf{Task similarity:}
@@
 Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-The observations highlight the need to develop generalization bounds that scale tightly with properties of the data in order to study MTL performance.
+The observations highlight the need to develop generalization bounds that scale tightly with properties of multiple task data.
 
@@
 		\vspace{-0.075in}
-		\caption{Data sizes}
+		\caption{Sample size}
 		\label{fig_size}
@@
 	(a) transitions from positive to negative transfer as \textit{task model distance} increases (Prop. \ref{prop_dist_transition});
-	(b) transitions from positive to negative transfer as source/target \text{data size} increases (Prop. \ref{prop_data_size});
-	(c) gets worse as \textit{covariate shift} gets more severe (increasing $\lambda$) and source/target \textit{data size} increases (Prop. \ref{prop_covariate}).
-	$y$-axis denotes the prediction loss of STL minus MTL.}
+	(b) transitions from positive to negative transfer as source/target \text{sample size} increases (Prop. \ref{prop_data_size});
+	(c) gets worse as \textit{covariate shift} gets more severe (increasing $\lambda$) and source/target \textit{sample size} increases (Prop. \ref{prop_covariate}).
+	The $y$-axis measures the loss of STL minus MTL.}
 	\label{fig_model_shift_phasetrans}

### 2020-06-02 writeup/intro.tex
intro

@@
 %\textbf{Setup and Main Results.}
-We consider the high-dimensional linear regression setting \cite{HMRT19,BLLT20} to explain the above phenomena.
-We focus on predicting a particular task that only contains limited amount of labeled data.
+Our main contribution is to develop a concentration bound that scales tightly with sample size and covariate shift.
+We focus on predicting a particular task given multiple high-dimensional linear regression tasks \cite{HMRT19,BLLT20}.
+\squishlist
+	\item \textbf{Task similarity:} We assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $1\le i\le t$.
+	Hence, task similarity can be measured by the distance between the model parameters.
+	\item \textbf{Sample size:} Let $n_i = \rho_i \cdot p$ denote the sample size of task $i$, for a fixed value $\rho_i > 1$ that does not grow with $p$, for any $1\le i\le p$.
+	Hence, for a source task and a target task, their data ratio is measured by $n_1 / n_2 = \rho_1 / \rho_2$.
+	Importantly, we assume that for the $t$-th (target) task, $\rho_t$ is a small constant (say 2), to capture the need for adding more labeled data.
+	\item \textbf{Covariate shift:} We assume that for every task $1\le i\le t$, its features are random vectors with covariance matrix $\Sigma_i\in\real^{p\times p}$.
+	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
+	Given two tasks $i$ and $j$, we measure covariate shift by $\Sigma_i^{1/2}\Sigma_j^{-1/2}$.
+\squishend
+% that only contains limited amount of labeled data.
 %Following Hastie et al.  and Bartlett et al. \cite{},
-We assume that for every task $1\le i\le t$, its features are random vectors $x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d.
-entries with mean zero and unit variance, and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
-The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d.
+
+%Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
+%The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d.
 random noise with mean zero and variance $\sigma^2$.
@@
 Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
-\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
+We revisit the bias-variance tradeoff of the multi-task estimator.
+Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, because of an increased sample size.
+The bias of the multi-task estimator results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
+Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
+%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
 %Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
@@
 
-%We revisit the bias-variance tradeoff of the multi-task estimator.
-%Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, hence resulting in a positive effect of variance reduction.
-%The bias of the multi-task estimator results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
-%Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
-
+For the setting of two tasks, we show how the variance of $\hat{\beta}_t^{\MTL}$ scales with samples size and covariate shift in the following result.
 \begin{theorem}[Informal]\label{lem_cov_shift_informal}
-	In the setting of two tasks, let $a_1, a_2$ be fixed values solved from deterministic equations of $\rho_1, \rho_2$ and the spectrum of $\Sigma_1^{1/2}\Sigma_2^{-1}\Sigma_1^{1/2}$.
+	In the setting of two tasks, .
 	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
 	\begin{align}\label{eq_introX1X2}
@@
 	\end{align}
+	let $a_1, a_2$ be fixed values solved from deterministic equations of $\rho_1, \rho_2$ and the spectrum of $\Sigma_1^{1/2}\Sigma_2^{-1}\Sigma_1^{1/2}$
 \end{theorem}

### 2020-06-02 writeup/intro.tex
intro

@@
 %\textbf{Setup and Main Results.}
-Our main contribution is to develop a concentration bound that scales tightly with sample size and covariate shift.
+Our main contribution is to develop technical tools to explain the above phenomena.
 We focus on predicting a particular task given multiple high-dimensional linear regression tasks \cite{HMRT19,BLLT20}.
@@
 Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
+For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
 %\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
@@
 
-For the setting of two tasks, we show how the variance of $\hat{\beta}_t^{\MTL}$ scales with samples size and covariate shift in the following result.
 \begin{theorem}[Informal]\label{lem_cov_shift_informal}
-	In the setting of two tasks, .
+	In the setting of two tasks,
+	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
+	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
+	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
 	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
 %	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-	\begin{align}\label{eq_introX1X2}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{\rho_1+\rho_2}\cdot \frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2} +\bigo{{p^{-1/2+\epsilon}}}.
-	\end{align}
-	let $a_1, a_2$ be fixed values solved from deterministic equations of $\rho_1, \rho_2$ and the spectrum of $\Sigma_1^{1/2}\Sigma_2^{-1}\Sigma_1^{1/2}$
+{\small\begin{align*}%\label{eq_introX1X2}
+		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
+		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}}.
+	\end{align*}}%
+where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+A similar result on the bias of $\hat{\beta}_t^{\MTL}$ that scales with task similarity in addition to sample size and covariate shift holds.
 \end{theorem}
@@
 %Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1 = 0$ \cite{S07}.
-The concentration error of our result, which is on the order of $O(p^{-1/2+\varepsilon})$, is nearly optimal.
+Theorem \ref{lem_cov_shift_informal} allows us to analyze of the bias-variance tradeoff of the multi-task estimator for two settings:
+(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
+
 %We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
@@
 %distribution with covariance matrix $\Sigma_i$.
-Based on Theorem \ref{lem_cov_shift_informal}, we provide an analysis of the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two settings:
-(i) two tasks with general covariance matrice; (ii) many tasks with the same features (e.g. images).
+
 %We extend our result to the transfer learning
@@
 In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
-It is crucial that the concentration error of Theorem \ref{lem_cov_shift_informal} is $O(p^{-1/2+\varepsilon})$ so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
+It is crucial that the concentration error of Theorem \ref{lem_cov_shift_informal} is small so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
 The unexplained observations are caused by an error term that arises from the bias of $\hat{\beta}_t^{\MTL}$ -- we discuss these in Section \ref{sec_insight} more precisely.
-Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shift, measured by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-When $\beta_1 = \beta_2$, we show that for a certain family of bounded $M$ matrices, having no covariate shift, i.e. all singular values of $M$ being equal, yields the optimal MTL performance.
+Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shift.
+When task models are the same and the covariate shift matrix belongs to a certain bounded set, we show that having no covariate shift yields the optimal MTL performance.
 %In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
@@
 \textit{Our last contribution} is to connect our theory to practical problems of interest.
-(i) We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
+(i) We validate the three components of our theory in Section \ref{sec_insight} and measure the data efficiency of multi-task learning on the sentiment analysis dataset.
+(ii) We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
 While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-(ii) We design an incremental training schedule to improve the efficiency of multi-task training for predicting a particular task.
+(iii) We design an incremental training schedule to improve the efficiency of multi-task training for predicting a particular task.
 We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset, while keeping the accuracy the same.
-(iii) We validate the three components of our theory in Section \ref{sec_insight} and measure the data efficiency of multi-task learning on the sentiment analysis dataset.

### 2020-06-02 writeup/setup.tex
intro

@@
 %, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-\begin{theorem}\label{thm_main_informal}
+\begin{corollary}\label{thm_main_informal}
 	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
@@
 	\squishend
-\end{theorem}
+\end{corollary}
 
-Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target data size is small.
+Corollary \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target data size is small.
 For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
@@
 
+\textbf{Remark.} Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
+The concentration error of our result that is order $O(p^{-1/2+o(1)})$ is nearly optimal.
+
 \iffalse

### 2020-06-02 writeup/proof_examples.tex
revision

@@
 \begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < (5\rho_1)^{-1} + (5\rho_2)^{-1}$.
+	In the isotropic model, assume that $\rho_1,\rho_2 \ge 9$ and $\Psi(\beta_1, \beta_2) < (5(\rho_1-1))^{-1} + (5(\rho_2-1))^{-1}$.
 	Then the data efficiency ratio $x^\star$ satisfies 
-	\[ x_l  \le x^\star\le \frac{1}{\rho_1 + \rho_2} \bigbrace{  \frac{2}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}+1}, \]
+	\be\label{eq_uplowx} x_l  \le x^\star\le \frac{1}{\rho_1 + \rho_2} \bigbrace{  \frac{2}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}+1}, \ee
 	where we denoted
@@
 Then we try to obtain an upper bound on $x^*$.
-In the following discussions, we only consider $x$ such that $x\ge \al_l$.
-In particular, we have $x(\rho_1+\rho_2) \ge x_l (\rho_1+\rho_2) \ge \min(\rho_1,\rho_2)$.
+In the following discussions, we only consider $x$ such that $x> x_l$.
+In particular, we have $x\rho > x_l \rho \ge \min(\rho_1,\rho_2)$, where we abbreviated $\rho:=\rho_1+\rho_2$.
 
@@
 
-\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^*\le x$ if $x$ satisfies {\cor to revise}
+\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^*\le x$ if $x$ satisfies 
 \be\nonumber
 \begin{split}
-&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(\al\rho_i)^2\cdot \al (\rho_1+\rho_2)}{[\al ( \rho_1+\rho_2) - 1]^3}  \bigbrace{1 + \sqrt{\frac{1}{\al \rho_i}}}^4 \\
-&\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} . 
+&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(x\rho_i)^2\cdot x\rho }{(x\rho - 1)^3}  \bigbrace{1 + \sqrt{\frac{1}{x \rho_i}}}^4 \le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{x\rho  - 1} .
 \end{split}
@@
 \begin{split}\label{solval1}
-  (1+\oo(1)) \cdot \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{\al \rho}}}^4\le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho  - 1},
+  (1+\oo(1)) \cdot \frac{\Psi(\beta_1,\beta_2)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4\le \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2}{x \rho  - 1}.
 \end{split}
 \ee
-where we abbreviated $\rho:=\rho_1+\rho_2$.
+With $x\rho\ge \min(\rho_1,\rho_2)>9$, we can get the simple bound
+$$\frac{1+\oo(1)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4 < 5. $$
+Inserting it into \eqref{solval1}, we can solve for the upper bound in \eqref{eq_uplowx}.
+%where we abbreviated $\rho:=\rho_1+\rho_2$.
 
-In order to solve \eqref{solval1}, we now consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that in this case
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} + \sqrt{\frac{1}{\al \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32.$$
+We can get better bounds if the values of $\rho_1$ and $\rho_2$ increase.
+For example, if we consider the case $\min(\rho_1,\rho_2)\ge 100$, then with some basic calculations, one can show that in this case
+$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52.$$
 Thus the following inequality implies \eqref{solval1}:
-\be\label{solval1add}
+\be\nonumber %\label{solval1add}
 \begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+&\left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right) \Psi(\beta_1,\beta_2) < \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
 \end{split}
 \ee
-In particular, if 
-\be\nonumber
+%In particular, if 
+%\be\nonumber
+%\begin{split}
+%&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+%\end{split}
+%\ee
+%that is, we have positive transfer when using all the data, then 
+from which we can solve for the following upper bound on $\al^*$:
+\begin{align*}
+\al^* &<  \frac1{\rho} \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right)\Psi(\beta_1,\beta_2)}+ \frac1\rho .
+%\\
+%& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+Similarly, we can get a better lower bound. 
+%\noindent{\bf The lower bound.} 
+From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^*\ge x$ if $x$ satisfies
+\be\label{solval2}
 \begin{split} 
-&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+&(1-\oo(1)) \cdot  \frac{\Psi(\beta_1,\beta_2)}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x \rho}}}^4 \ge \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x \rho - 1} .
 \end{split}
 \ee
-that is, we have positive transfer when using all the data, then we can solve from \eqref{solval1add} the following upper bound on $\al^*$:
-\begin{align*}
-\al^* &<  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right)\frac{pd^2}{\sigma^2}}+ 1\right] \\
-& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-
-\noindent{\bf The lower bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $\al^*\ge \al$ if $\al$ satisfies
-\be\label{solval2}
-\begin{split}
-&(1-\oo(1)) \cdot  \frac{pd^2}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{\al \rho}}}^4 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al \rho - 1} .
-\end{split}
-\ee
-We then follow similar arguments as the above proof for the upper bound.
-
-In order to solve \eqref{solval2}, we consider the case $\min(\rho_1,\rho_2)\ge 200$. With some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
-$$ \frac{1}{[1 - (\al \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho_1+\rho_2}} - \sqrt{\frac{1}{\al \rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26 .$$
+%We then follow similar arguments as the above proof for the upper bound.
+Then in the case $\min(\rho_1,\rho_2)\ge 100$, with some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
+$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x\rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33 .$$
 Thus the following inequality implies \eqref{solval2}:
@@
 \begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{\al (\rho_1+\rho_2) - 1} .
+&\left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{x\rho - 1} ,
 \end{split}
 \ee
-There are two cases: if 
-\be\nonumber
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
-\end{split}
-\ee
-then we have negative transfer for all choice of $0\le \al \le 1$; otherwise, we can solve from \eqref{solval2add} the following lower bound on $\al^*$:
+%There are two cases: if 
+%\be\nonumber
+%\begin{split}
+%&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
+%\end{split}
+%\ee
+%then we have negative transfer for all choice of $0\le \al \le 1$; otherwise, 
+from which we can solve for the following lower bound on $x^*$:
 \begin{align*}
-\al^* &>  \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) \frac{pd^2}{\sigma^2}}+ 1\right] \\
-& >\frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -\frac13\right) \frac{pd^2}{\sigma^2}}+ 1\right] .
+x^* &>  \frac1\rho \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)}+ \frac1\rho .
 \end{align*}
-This concludes the proof.
+This gives a lower bound above $x_l$.
 \end{proof}
@@
 
-% Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is no model bias and enough source data.
+We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
 
@@
 With the same arguments as in Lemma \ref{lem_hat_v} we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{c}\kappa^2  \le \sigma^2 \le p^{1-c} \kappa^2$ (recall \eqref{choiceofpara}), we can simplify
+Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
 \be \nonumber
@@
 \ee
-with high probability for any constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $\lambda(M)\in [\mu_{\min},\mu_{\max}]$.
+with high probability for some constant $\e>0$.
+In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
 We omit the details here.
 
-Now using Lemma \ref{lem_cov_shift}, we can obtain that with high probability,
+Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
 \begin{align}\label{gvar_extra}
@@
 \begin{align}\label{approximateteM}
-\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}\wt g(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le \wt g(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
+\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
 \end{align}
 where
-$$\wt g(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
+$$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
 %With these two bounds, we can easily conclude \eqref{approxteM}. 
@@
 By AM-GM inequality, we observe that 
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i}$$
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
 is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
-\be\label{AMGM}\wt g(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
+\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
 
-On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we can obtain that with high probability,
+On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
 \begin{align}\label{gvar_extra2}
@@
 %--------end old argument---------
-we observe the following two phases as we increase $n_1 / p$ in Figure \ref{fig_covariate}.
+In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
 When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
 When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-We provide a theoretical justification below.
+We provide a theoretical justification now.
 
 \begin{proof}[Theoretical justification of Example \ref{ex_complement}]
-We denote the test error as $\te_\lambda(\hat \beta_{t}^{\MTL})$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
 Then equations in \eqref{eq_a12extra} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \frac{a_2}{\lambda^2}}} = \frac{\rho_1}{\rho_1 + \rho_2}.
+\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
 \ee
@@
 \be\label{testcomple}
- \te_\lambda(\hat \beta_{t}^{\MTL})= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot g(\lambda) ,\quad g(\lambda): = \frac{1}{\frac{a_1}{\lambda^2} + a_2} + \frac{1}{a_1\lambda^2 + a_2}.\ee
+ \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
 
@@
 On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-We now study the behavior of $g$ as $\lambda$ changes. 
+We now study the behavior of $f$ as $\lambda$ changes. 
 %This phenomenon can be also explained using our theory. 
 We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with \eqref{compleeq}, we can rewrite
-$$g(\lambda)= \frac{1}{\frac{a_1}{\lambda^2} + (1-\gamma - a_1)} + \frac{1}{a_1\lambda^2 + (1-\gamma - a_1)}.$$
-We can compute that
+$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
+Then we can compute that
 \begin{align*}
-g(\lambda) - g(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
 &= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
@@
 \item[(i)] If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}).
-Hence $g(\lambda)>g(1)$, which gives $\te_\lambda(\hat \beta_{t}^{\MTL})>\te_1(\hat \beta_{t}^{\MTL})$.
+Hence $f(\lambda)>f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)>\te(\hat \beta_{2}^{\MTL},1)$.
 
-\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $g(\lambda)< g(1)$, which gives $\te_\lambda(\hat \beta_{t}^{\MTL})<\te_1(\hat \beta_{t}^{\MTL})$.
+\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $f(\lambda)< f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
 
-\item[(iii)] If $n_1=n_2$, we have $g(\lambda)=g(1)=2/(1-\gamma)$, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
+\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
+%, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
 \end{itemize}
-These justify the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
+This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
 \end{proof}
@@
 
-Then we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
+In this section, we consider the case where the two tasks may have difference variances $\sigma_1^2\ne \sigma_2^2$ for the noises.
+In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
 
-\begin{proposition}[Labeled data de-noising]\label{prop_var_transition}
+\begin{proposition}%[Labeled data de-noising]
+\label{prop_var_transition}
 	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
-	We derive the following transition as a parameter of $\sigma_1^2$:
+	Then we have the following transition with respect to $\sigma_1^2$:
 	\begin{itemize}
-		\item If $\sigma_1^2 \le -2 \rho_1 \cdot p d^2+\left(1+ \frac34\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\sigma_1^2 > - \frac12\rho_1\cdot p d^2   +\left(1+ \frac32\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\sigma_1^2 < - \gamma_+^{1/2} \rho_1 \cdot p d^2+\left(1+ \gamma_+^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
+		\item If $\sigma_1^2 > -\gamma_-^{1/2}\rho_1\cdot p d^2   +\left(1+ \gamma_-^{-1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
 	\end{itemize}
@@
 As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+%The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
 %The details can be found in Appendix \ref{app_proof_data}.
@@
 \begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-In the setting of Proposition \ref{prop_var_transition}, the validation loss and the test error become
+In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
+%the validation loss and the test error become
+%\begin{align*}
+%		\val(\hat{B}; w_1, w_2)
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
+%\end{align*}
+%and 
+%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
+In the isotropic model, using again the concentration of random vector with i.i.d. entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
 \begin{align*}
-		\val(\hat{B}; w_1, w_2)
-	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
-		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
-\end{align*}
-and 
-\begin{align*}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v} \beta_t)}^2 \nonumber \\
-			&~ + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2) \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2 X_1^\top X_1},
-\end{align*}
-where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$.
-Again using concentration of random vector with i.i.d.
-entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_t^{\MTL})$ as
-\begin{align*}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( w-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
+	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
 	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
@@
 %We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
-Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_t^{\MTL}) $ can be simplified as in \eqref{simple1}: 
+Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
 \be \label{simple2}
 \begin{split}
-\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
+\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
 &+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
@@
 Then we write 
-$$ \te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
+$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
 where 
@@
 %where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
-To estimate this new term, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
 This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
@@
 $$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
-Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main goal is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
+Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
 
@@
 
-Note that the condition $d^2 < \frac {\sigma_2^2} {2p} \cdot \Phi(\rho_1, \rho_2)$ means the we have $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
-Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$.
-
+Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ means the we have $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
+Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
 It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
 
-\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2} above, if
+\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2}, if the following inequality holds,
 \be\label{cond sigma1}
@@
 &\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
-&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 ,
+&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_+^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_+(\rho_1)  , 
 \end{split}
@@
 \begin{align*}
-\sigma_1^2 < - pd^2 \cdot \rho_1\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1-\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1-\oo(1)).
+\sigma_1^2 < - pd^2\cdot \rho_1 \al_+(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2) \al_+^{-1}(\rho_1)\right]\cdot (1-\oo(1)).
 \end{align*}
-Plugging into $\rho_1>50$, we obtain the first claim of Proposition \ref{prop_var_transition} for positive transfer.
+This proves the first claim of Proposition \ref{prop_var_transition} for positive transfer.
 
-\noindent{\bf Negative transfer.} On the other hand, if 
+\noindent{\bf Negative transfer.} On the other hand, if the following inequality holds,
 \be\label{cond sigma12}
@@
 &\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
-&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 ,
+&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_-^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_-(\rho_1) , 
 \end{split}
@@
 \begin{align*}
-\sigma_1^2 > - pd^2 \cdot \rho_1\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^2 \cdot (1+\oo(1))+\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^{-2}\right]\cdot (1+\oo(1)).
+\sigma_1^2 > - pd^2 \cdot \rho_1 \al_-(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\al_-^{-1}(\rho_1)\right]\cdot (1+\oo(1)).
 \end{align*}
-Plugging into $\rho_1>50$, we obtain the second claim of Proposition \ref{prop_var_transition} for negative transfer.
+This proves the second claim of Proposition \ref{prop_var_transition} for negative transfer.
 \end{proof}

### 2020-06-02 writeup/intro.tex
revisions

@@
 	Second, we apply our tools to show that the performance of multi-task learning is negatively affected as a result of: (a) decreased task similarity;
-	(b) increased source sample size; (c) covariate shift under increased source sample sizes.
+	(b) increased source sample size; (c) covariate shift under increased source sample size.
 	Finally, we validate the three components of our theory on image and text classification tasks.
-	Inspired by our theory, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
+	Inspired by our theory, we propose an incremental training schedule for improving the efficiency of multi-task training for predicting a particular task.
 %	We validate our theory and our proposed method .
@@
 %By combining multiple information sources, it is possible to share all the information in the same model.
-In many settings, multiple information sources are available to help solve a particular task.
+In many settings, multiple information sources are available to help to solve a particular task.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
@@
 % for learning from multiple linear regression tasks.
-We develop new tools to analyze the tradeoff and explain negative transfer precisely.
+Moreover, we develop new tools to analyze the tradeoff and explain negative transfer precisely.
 %Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
@@
 For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11,MPR16}.
-On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause of negative transfer \cite{YKGLHF20}.
+On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
 %The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
@@
 Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-The observations highlight the need to develop generalization bounds that scale tightly with properties of multiple task data.
+The observations highlight the need to develop generalization bounds that scale tightly with properties of multiple tasks data.
 
@@
 	Hence, task similarity can be measured by the distance between the model parameters.
-	\item \textbf{Sample size:} Let $n_i = \rho_i \cdot p$ denote the sample size of task $i$, for a fixed value $\rho_i > 1$ that does not grow with $p$, for any $1\le i\le p$.
-	Hence, for a source task and a target task, their data ratio is measured by $n_1 / n_2 = \rho_1 / \rho_2$.
+	\item \textbf{Sample size:} Let $n_i = \rho_i \cdot p$ denote the sample size of task $i$, for a fixed value $\rho_i > 1$ that does not grow with $p$, for any $1\le i\le t$.
+	Hence, for a source task $s$ and a target task $t$, their data ratio is measured by $n_s / n_t = \rho_s / \rho_t$.
 	Importantly, we assume that for the $t$-th (target) task, $\rho_t$ is a small constant (say 2), to capture the need for adding more labeled data.
@@
 random noise with mean zero and variance $\sigma^2$.
-We focus on the hard parameter sharing architecture with a linear shared layer for all tasks and a separate prediction head for each task \cite{R17,MTDNN19,WZR20}.
+We focus on the hard parameter sharing architecture with a linear shared layer for all tasks and a separate prediction head for each task \cite{R17,WZR20,MTDNN19}.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
 Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
-We revisit the bias-variance tradeoff of the multi-task estimator.
+We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
 Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, because of an increased sample size.
@@
 	We observe that MTL performance
-	(a) transitions from positive to negative transfer as \textit{task model distance} increases (Prop. \ref{prop_dist_transition});
-	(b) transitions from positive to negative transfer as source/target \text{sample size} increases (Prop. \ref{prop_data_size});
-	(c) gets worse as \textit{covariate shift} gets more severe (increasing $\lambda$) and source/target \textit{sample size} increases (Prop. \ref{prop_covariate}).
+	(a) undergoes transition from positive to negative transfer as \textit{task model distance} increases (Prop.\;\ref{prop_dist_transition});
+	(b) undergoes transition from positive to negative transfer as source/target \text{sample size} increases (Prop.\;\ref{prop_data_size});
+	(c) gets worse as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample size} increases (Prop.\;\ref{prop_covariate}).
 	The $y$-axis measures the loss of STL minus MTL.}
@@
 		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}}.
+		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
 	\end{align*}}%
 where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-A similar result on the bias of $\hat{\beta}_t^{\MTL}$ that scales with task similarity in addition to sample size and covariate shift holds.
+A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
 \end{theorem}
@@
 %Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-Theorem \ref{lem_cov_shift_informal} allows us to analyze of the bias-variance tradeoff of the multi-task estimator for two settings:
+Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
 (i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
@@
 In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
-It is crucial that the concentration error of Theorem \ref{lem_cov_shift_informal} is small so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
+It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
 The unexplained observations are caused by an error term that arises from the bias of $\hat{\beta}_t^{\MTL}$ -- we discuss these in Section \ref{sec_insight} more precisely.
-Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shift.
+Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
 When task models are the same and the covariate shift matrix belongs to a certain bounded set, we show that having no covariate shift yields the optimal MTL performance.

### 2020-06-03 writeup/setup.tex
revisions

@@
 entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-Without loss of generality, let the $t$-th task denote the target task.
+Without loss of generality, let the $t$-th task be the target task.
 We consider the following linear multi-task learning architecture.
@@
 Here $B$ provides a shared subspace for all tasks and $W_i$ fits $B$ suitably to each task.
-Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ to be the single-task optimum.
-Hence, applying equation \eqref{eq_mtl} results in the same estimator as single-task learning.
+Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
+Then applying equation \eqref{eq_mtl} will give the same estimator as single-task learning.
 We define $\hat{\beta}_t^{\MTL}$ by two steps:
 (i) minimizing $f(\cdot)$ over $B$;
-(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set, e.g. $O(p^{0.99})$ suffices.
-For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
+(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set, e.g. $\OO(p^{0.99})$ suffices.
+For more details, we refer the reader to Appendix \ref{app_proof_sec3}. The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$. 
 For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample prediction loss as
@@
 %= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t) \\
-which can be further decomposed as the bias and variance of $\hat{\beta}$.
-The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
+which can be further decomposed as the bias plus the variance of $\hat{\beta}$.
 %In order to relate the btradeoff to properties of the data, we need tight concentration bounds for the bias and variance.
-We consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
+We consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$  multiple of $p$ for every $1\le i\le t$, and $p$ is sufficiently large.
 We focus on a setting where $\rho_t$ is small compared to $\set{\rho_i}_{i=1}^{t-1}$.
-This setting captures the need for adding more labeled data to reduce the prediction loss of the target task.
+This setting captures the need to add more labeled data to reduce the prediction loss of the target task.
 A well-known result for this setting states that $\te_t(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \tr[(X_t^{\top}X_t)^{-1}\Sigma_t]$ is concentrated around $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
@@
 \textbf{Notations.}
-When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
+When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ and write $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
 We refer to the first task as the source task when there are only two tasks.
@@
 We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$ is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
-For a matrix $X\in\real^{p_1\times p_2}$, let $\lambda_{\min}(X)$ denote its minimum singular value.
-Let $\norm{X}$ denote the spectral norm of $X$.
+For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
 

### 2020-06-03 writeup/proof_main.tex
revisions

@@
 \begin{itemize}
-\item[(i)] We first consider $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a fixed $v\ge 0$.
+\item[(i)] We first consider $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a fixed $v\in \R$.
 Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
@@
 
-\paragraph{Step I: Variance reduction.} Let $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for any fixed constant $v\ge 0$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
+\paragraph{Step I: Variance reduction.} Let $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for any fixed constant $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
 $$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
@@
 %\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
-holds uniformly for all $v\in [0, C_0]$. In fact, for a large constant $C_1>0$, we consider $v$ belonging to a discrete set 
-$$V:=\{v_k = kp^{-1}: 1\le k \le C_0p +1\}.$$
+holds uniformly for all $v\in [-C_0, C_0]$. In fact, for a large constant $C_1>0$, we consider $v$ belonging to a discrete set 
+$$V:=\{v_k = kp^{-1}: -(C_0p +1)\le k \le C_0p +1\}.$$
 Then using the arguments for the first three steps and a simple union bound, we get that
@@
 Then a simple application of triangle inequality gives that the event 
-$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }0\le v \le C_0\}$$
+$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }-C_0\le v \le C_0\}$$
 holds with high probability. On the other hand, on $\Xi_1$ one can see that for any small constant $\e>0$,
@@
 for all $v\ge C_0$ as long as $C_0$ is chosen large enough depending on $\e$.
-Together with the estimate at $C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\ge 0$ on the high probability event $\Xi_1\cap \Xi_2$.
-This concludes the proof since $v$ must be one of the positive values.
+Similar estimates hold for $v\le -C_0$ if we replace $C_0$ with $-C_0$ in the above estimates.
+Together with the estimate at $\pm C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\in \R$ on the high probability event $\Xi_1\cap \Xi_2$.
+This concludes the proof since $v$ must be one of the real values.
 \end{proof}
@@
 \begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
-For any fixed $v\ge 0$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
+For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
 entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.

### 2020-06-03 writeup/setup.tex
merge

--- 2020-06-02 writeup/setup.tex
@@
 A well-known result for this setting states that $\te_t(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \tr[(X_t^{\top}X_t)^{-1}\Sigma_t]$ is concentrated around $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
+Chapter 6 of \cite{S07}), which scales with the sample size and noise level of the target task.
 However, this result only applies to a single task.
@@
 
-Corollary \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target data size is small.
+Corollary \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target sample size is small.
 For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.

### 2020-06-03 writeup/setup.tex
revisions

--- 2020-06-03 writeup/setup.tex
@@
 
-Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$, which captures how similar $\beta_1$ and $\beta_2$ are.
+The term on the right-hand side of \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$, which captures how similar $\beta_1$ and $\beta_2$ are.
 Hence, the bias of $\hat{\beta}_t^{\MTL}$ introduces a negative effect from adding the source labels.
@@
 %\textbf{Multi-task learning.}
-We provide a sharp analysis of the bias-variance tradeoff two tasks with general covariance matrices.
-We state our result for two tasks as follows.
+We provide a sharp analysis of the bias-variance tradeoff for two tasks with general covariance matrices.
+We state our result as follows.
 %The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
@@
 \begin{corollary}\label{thm_main_informal}
-	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin and $\rho_1 \gtrsim \frac{1}{\delta^2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
-	Let $\rho_2 > 1$ be a fixed value.
+	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin, $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and $\rho_2 > 1$ be a fixed value.
  	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
@@
 %The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of the threshold can be complex (as is preivous generalization bounds for MTL), they admit interpretable forms for simplified settings.
+While the general form of the threshold can be complicated (as are the previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
 This will be the focus of Section \ref{sec_insight}.
@@
 Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
-In particular, when $z=0$, $\tr[R_\infty(0)]$ gives the right hand side of \eqref{eq_introX1X2}, which concludes Theorem \ref{lem_cov_shift_informal}.
+In particular, when $z=0$, $\tr[R_\infty(0)]$ gives the expression inTheorem \ref{lem_cov_shift_informal}.
 The details can be found in Appendix \ref{sec_maintools} and \ref{sec_Gauss}.
 
-Using Theorem \ref{lem_cov_shift_informal} over \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL.
-The amount of reduced variance is given by $\Delta_{\vari}$.
-For the bias term of equation \eqref{eq_te_model_shift}, we apply a Gaussian concentration bound on $X_1^{\top}X_1$, whose expectation is $n_1^2\Sigma_1$.
-This results in the error term $\delta$, which scales as $(1 \pm 1/\sqrt{\rho_1})^4$.
-Then, we applying a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-This leads to a negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
+Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
+For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
+This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
+Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
+This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
 %During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
@@
 	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, that satisfy Assumption \ref{assm_secA2}.
+	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.  
+	%that satisfy Assumption \ref{assm_secA2} in the appendix.
 	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
@@
 	\squishlist
-		\item We have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
+		\item $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
 		$$\left(1 - \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
-		\item We have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
+		\item $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
 		$$\left(1 - \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
@@
 \textbf{Remark.} Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-The concentration error of our result that is order $O(p^{-1/2+o(1)})$ is nearly optimal.
+The concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
 

### 2020-06-03 writeup/transfer.tex

@@
 We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-We explain from three perspectives, including \textit{task similarity}, \textit{data size} and \textit{covariate shift}.
-We show how negative transfer occurs by varying task similarity or data size.
-Then we show that when source task data size becomes large, covariate shift causes more negative effects.
+We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
+We show how negative transfer occurs by varying task similarity or sample size.
+Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
 
@@
 	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
-	Recall that each task has data size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
+	Recall that each task has sample size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
 	And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denotes the covariates of the two tasks, respectively.
@@
 
-\subsection{Data Size}\label{sec_data_size}
+\subsection{Sample Size}\label{sec_data_size}
 
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
+In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
 More generally, such results are still applicable when all task data are being added simultaneously.
@@
 %On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-Using the isotropic model, we consider what happens if we vary the source task data size.
+Using the isotropic model, we consider what happens if we vary the source task sample size.
 %Figure \ref{fig_size} provides a simulation result for such a setting.
@@
 
-\begin{proposition}[Source/target data size]\label{prop_data_size}
+\begin{proposition}[Source/target sample size]\label{prop_data_size}
 	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.

### 2020-06-03 writeup/transfer.tex
revisions

@@
 It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the following simplified setting.
+We formalize this connection in the following simplified setting, where we can perform explicit calculations.
 
@@
 	Recall that each task has sample size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
-	And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denotes the covariates of the two tasks, respectively.
+	And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
 	We assume that for the target task, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
@@
 	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma_i^2$, for $i=1,2$.
-	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{app_proof_sec3}.
+	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
 
@@
 		\item If $\Psi(\beta_1, \beta_2) < \gamma_{+}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) \ge \gamma_{-}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) > \gamma_{-}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
 	Here $\gamma_{-} = (1-\oo(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+\oo(1))\cdot(1 + \rho_1^{-1/2})^4$.
-	Concretely, if $\rho_1 > 40$, then $\gamma_{-} \in (1,2)$ and $\gamma_{+} \in (1/2, 1)$.
+	Concretely, if $\rho_1 > 40$, then $\gamma_{+} \in (1,2)$ and $\gamma_{-} \in (1/2, 1)$.
 \end{proposition}
 
-Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
+Proposition \ref{prop_dist_transition} simplifies Corollary \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
 Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
 Prosposition \ref{prop_dist_transition} explains the transition observed in Figure \ref{fig_model_shift}.
-Note that there are several unexplained observations near the transition threshold $0$, which are caused by the concentration errors $\gamma_+, \gamma_-$.
+Note that there are several unexplained observations near the transition threshold $0$, which are caused by the concentration errors $\gamma_+$ and $\gamma_-$.
 %We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
@@
 \textbf{Algorithmic consequence.}
-We can in fact extend the result to the cases where the noise variance is different.
+We can in fact extend the result to the cases where the noise variances are different.
 In this case, we will see that MTL is particularly effective.
@@
 If $\sigma_1^2$ is small, the source task is more helpful.
-We leave the result to the Appendix in Proposition \ref{prop_var_transition}.
+We leave the result to Proposition \ref{prop_var_transition} in Appendix \ref{app_proof_31}.
 Inspired by the observation, we propose a single-task based metric to help understand MTL results using STL results.
@@
 \begin{proposition}[Source/target sample size]\label{prop_data_size}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-	We have that
+	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+	Then we have that
 	\squishlist
@@
 
-\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
+\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.
+(2018) \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
 %More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using $R \cdot n_i$ datapoints from every task.
-The data efficiency ratio roughly scales as
+For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using $x \cdot n_i$ datapoints from every task. The data efficiency ratio is defined as
 \[ \argmin_{x\in(0, 1)} ~~
@@
 Using our tools, we show that in the isotropic model, the data efficiency ratio is
-equal to \[ \frac{1}{\rho_1 + \rho_2} {+ \frac{1}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
-Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$, the transfer is positive.
-Hence the data efficiency ratio quantifies how effective is the positive transfer using MTL.
+roughly 
+\[ \frac{1}{\rho_1 + \rho_2} {+ \frac{2}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
+Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$ (up to a constant multiple), the transfer is positive.
+Moreover, the data efficiency ratio quantifies how effective the positive transfer is using MTL.
 %In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-The precise statement can be found in Appendix \ref{app_proof_32}.
+The precise statement can be found in Proposition \ref{prop_data_efficiency} in Appendix \ref{app_proof_32}.
 
@@
 	We compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	Hence, $\lambda$ measures the severity of covariate shift.
+	Hence, $\lambda$ measures the severity of the covariate shift.
 	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as $n_1/n_2$ increases, the performance gap between the case of $M = \id$ and $\lambda = 2$ or $4$ increases for MTL.
+	We observe that as $n_1/n_2$ increases, the performance gap between case (i) $M = \id$ and case (ii) with $\lambda = 2$ or $4$ increases for MTL.
 \end{example}
@@
 %By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in decreasing order.
-Let $\mu_{\min} < \mu < \mu_{\max}$ are fixed values that do not grow with $p$.
+To compare different choices of $M$ regarding the performance of $\hat{\beta}_t^{\MTL}$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in decreasing order.
+Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
 Consider the following bounded set
 \begin{align*}
-		\cS_{\mu}\define\bigset{M \mid \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_p, \lambda_1 \le \mu_{\max}},
+		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_p\le \lambda_1 \le \mu_{\max}\right.},
 \end{align*}
@@
 	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
+	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
 	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
 \end{proposition}
-The following proposition shows that when $n_1 \gg n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized when there is no covariate shift between source and target task.
+This proposition shows that when $n_1 \gg n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized when there is no covariate shift between source and target tasks.
 The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
@@
 Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in Wu et al.'20 \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
+We consider a covariance alignment procedure proposed in Wu et al. (2020) \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
 The idea is to add an alignment module between the input and the shared module $B$.

### 2020-06-03 writeup/intro.tex
merge
reorg sec 23

@@
 
-\begin{theorem}[Informal]\label{lem_cov_shift_informal}
-	In the setting of two tasks,
-	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
-	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-{\small\begin{align*}%\label{eq_introX1X2}
-		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-	\end{align*}}%
-where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
-\end{theorem}
-
 %Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
@@
 
-\textit{Our next contribution} is to use our newly developed tool to explain negative transfer in multi-task learning precisely.
+Next, we use our newly developed tool to explain negative transfer in multi-task learning precisely.
 In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.

### 2020-06-03 writeup/setup.tex
reorg sec 23

@@
-\section{Multi-Task vs. Single-Task Learning: The Bias-Variance Tradeoff}
+\section{Technical Tools using Random Matrix Theory}
 \label{sec_main}
@@
 
-\subsection{Problem Setup}\label{sec_setup}
+%\subsection{Problem Setup}\label{sec_setup}
 
@@
 
-\subsection{Analyzing the Tradeoff via Random Matrix Theory}
+%\subsection{Analyzing the Tradeoff via Random Matrix Theory}
 
@@
 
+\begin{theorem}[Informal]\label{lem_cov_shift_informal}
+	In the setting of two tasks,
+	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
+	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
+	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
+	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+{\small\begin{align*}%\label{eq_introX1X2}
+		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
+		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
+	\end{align*}}%
+where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
+\end{theorem}
+
 %\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
@@
 %\textbf{Multi-task learning.}
-We provide a sharp analysis of the bias-variance tradeoff for two tasks with general covariance matrices.
-We state our result as follows.
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-\begin{corollary}\label{thm_main_informal}
-	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin, $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and $\rho_2 > 1$ be a fixed value.
- 	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
-	\squishlist
-		\item If $\Delta_{\bias} - \Delta_{\vari} < -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Delta_{\bias} - \Delta_{\vari} > \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
-\end{corollary}
-
-Corollary \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target data size is small.
-For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
-%determined by the covariate shift matrix and the model shift.
-%The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of the threshold can be complicated (as are the previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-This will be the focus of Section \ref{sec_insight}.
 
@@
 %The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
-Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.  
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
-Suppose $(B^{\star})^\top\Sigma B^{\star}$ is of full rank in the sense that $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
-	We have the following
-	\squishlist
-		\item $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
-		$$\left(1 - \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
-		\item $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
-		$$\left(1 - \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
-	\squishend
-\end{theorem}
-%A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-06-03 writeup/transfer.tex
reorg sec 23

--- 2020-06-03 writeup/transfer.tex
@@
-\section{Explaining Negative Transfer in an Isotropic Setting}\label{sec_insight}
+\section{Multi-Task vs. Single-Task Learning: The Bias-Variance Tradeoff}\label{sec_insight}
 
@@
 Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
+
+\subsection{General Settings}
+
+We provide a sharp analysis of the bias-variance tradeoff for two tasks with general covariance matrices.
+We state our result as follows.
+%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
+%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
+%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+%Based on the result, we show how to determine positive versus negative transfer as follows.
+%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
+\begin{corollary}\label{thm_main_informal}
+	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin, $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and $\rho_2 > 1$ be a fixed value.
+ 	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
+	\squishlist
+		\item If $\Delta_{\bias} - \Delta_{\vari} < -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Delta_{\bias} - \Delta_{\vari} > \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\squishend
+\end{corollary}
+
+Corollary \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target sample size is small.
+For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
+%determined by the covariate shift matrix and the model shift.
+%The bounds get tighter and tighter as $\rho_1$ increases.
+While the general form of the threshold can be complicated (as are the previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
+This will be the focus of Section \ref{sec_insight}.
+
+Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+\begin{theorem}\label{thm_many_tasks}
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
+	%that satisfy Assumption \ref{assm_secA2} in the appendix.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
+Suppose $(B^{\star})^\top\Sigma B^{\star}$ is of full rank in the sense that $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$.
+Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
+	We have the following
+	\squishlist
+		\item $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
+		$$\left(1 - \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
+		\item $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
+		$$\left(1 - \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
+	\squishend
+\end{theorem}
+%A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-06-03 writeup/intro.tex
revisions

--- 2020-06-02 writeup/intro.tex
@@
 	Finally, we validate the three components of our theory on image and text classification tasks.
-	Inspired by our theory, we propose an incremental training schedule for improving the efficiency of multi-task training for predicting a particular task.
+	Inspired by our theory, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
 %	We validate our theory and our proposed method .

### 2020-06-03 writeup/related.tex
Update on Overleaf.
revisions

@@
 
+\textbf{Multi-task learning.}
  Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
+Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+
+\textbf{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
+For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.
+It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}.
+On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
+To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
+
+\textbf{Transfer learning.}
+
+\section{Conclusions and Discussions}

### 2020-06-03 writeup/related.tex
related

--- 2020-04-29 writeup/related.tex
@@
 
- Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
+We refer the interested readers to several excellent surveys on multi-task and transfer learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
+
+\textbf{Multi-task learning theory.}
+Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
+Mauer \cite{M06} Generalization bounds for linear separation settings of MTL
+Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines empirical and target errors in an optimal way.
+The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+Our work is closely related to Wu et al. \cite{WZR20}.
+While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their results do not apply to explain the phenomena of negative transfer.
+
+% Adding a regularization over $B$, e.g. .
+\textbf{Multi-task learning methodology.}
+Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
+Argyriou et al. \cite{AEP08} presents a convex algorithm which learns common sparse representations across a pool of related tasks.
+Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
+\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,R17}.
+We believe that the technical tools we have developed can also be applied to many other multi-task learning models.
+
+\textbf{Random matrix theory.}
+
+\section{Conclusions and Discussions}

### 2020-06-03 writeup/experiments.tex

@@
 We measure the data efficiency ratio on the sentiment analysis tasks.
-In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
+In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ ({\cor or $36\%$?}) of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
 The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
@@
 \textbf{Understanding MTL results via STL results.}
-We show that STL results can be used to help understand MTL results
+We show that STL results can be used to help understand MTL results.
 We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.

### 2020-06-03 writeup/related.tex

@@
 
-\textbf{Random matrix theory.}
+\textbf{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
+For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.
+It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}.
+On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
+To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
 

### 2020-06-03 writeup/setup.tex
sec 2

@@
-\section{Technical Tools using Random Matrix Theory}
+\section{A Concentration Bound Generalizing Single-Task Settings}
 \label{sec_main}
 
-We begin by describing our problem setup more formally.
-Then, we describe our main result for the bias-variance tradeoff of multi-task and transfer learning estimators in our setting.
-
-%\subsection{Problem Setup}\label{sec_setup}
+In this section we describe how \textit{task similarity}, \textit{sample size} and \textit{covariate shift} arise from the bias-variance tradeoff in the multi-task setting.
+We illustrate how a natural quantity involving the spectrum of two random matrices arise, and then show a tight concentration bound for this quantity using random matrix theory.
 

### 2020-06-03 writeup/proofs_sec3.tex
revision
App A

@@
 
-\subsection{The multi-task learning estimator}\label{sec_MTLest}
+\subsection{Preliminaries}
+
+\subsubsection{Data models}
+First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
+
+\begin{assumption}\label{assm_secA1}
+We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrices, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
+entries with mean zero and variance one.
+Note that the rows of $X$ are i.i.d.
+centered random vectors with covariance matrix $\Sigma$.
+For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
+\begin{equation}\label{assmAhigh}
+\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
+\end{equation}
+ We assume that $n=\rho p$ for some fixed constant $\rho>1$.
+Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
+Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
+\end{assumption}
+Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
+If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
+We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} below.
+
+Then we make the following assumptions on the data models.
+\begin{assumption}\label{assm_secA2}
+For for some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
+\end{assumption}
+
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Moreover, we shall use $\oo(1)$ to mean a small positive number that converges to 0 as $p\to \infty$.
+
+\subsubsection{The Multi-Task Learning Estimator} %\label{sec_MTLest}
 From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
@@
 	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
-			&+~  \sigma_2^2 \cdot \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }, \label{eq_te_mtl_2task}
+			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
 \end{align}
@@
 Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
-
-\begin{assumption}\label{assm_secA1}
-We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrices, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
-entries with mean zero and variance one.
-Note that the rows of $X$ are i.i.d.
-centered random vectors with covariance matrix $\Sigma$.
-For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\begin{equation}\label{assmAhigh}
-\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
-\end{equation}
- We assume that $n=\rho p$ for some fixed constant $\rho>1$.
-Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
-Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
-\end{assumption}
-Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
-If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
-We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} below.
-
-Then we make the following assumptions on the data models.
-\begin{assumption}\label{assm_secA2}
-For for some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
-Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
-\end{assumption}
-
-Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
-Moreover, we shall use $\oo(1)$ to mean a small positive number that converges to 0 as $p\to \infty$.
 
@@
 \be\label{approxvalid}
-\wt f(\hat B; v)=  \left[\val(\hat{B}; v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
+\wt f(\hat B; v)=  \left[\val(\hat{B}; v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
 \ee
@@
 
+\subsubsection{Tools for Random Matrices}
 We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$.

### 2020-06-03 writeup/proofs_sec3.tex
sec 2

@@
 
-\subsubsection{Data models}
+\subsubsection{Data models}\label{app_data_model}
 First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
@@
 
-\subsubsection{The Multi-Task Learning Estimator} %\label{sec_MTLest}
+\subsubsection{The Multi-Task Learning Estimator}\label{sec_MTLest}
 From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
@@
 
-\subsubsection{Tools for Random Matrices}
+\subsubsection{Tools for Random Matrices}\label{app_tool}
 We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$.

### 2020-06-03 writeup/setup.tex
sec 2

--- 2020-06-03 writeup/setup.tex
@@
-\section{Technical Tools using Random Matrix Theory}
+\section{A Concentration Bound Generalizing Single-Task Settings}
 \label{sec_main}
 
-We begin by describing our problem setup more formally.
-Then, we describe our main result for the bias-variance tradeoff of multi-task and transfer learning estimators in our setting.
+We begin by defining the data model and the multi-task learning estimator that we study.
+Then, we study the bias-variance tradeoff of the MTL estimator, and show how \textit{task similarity}, \textit{sample size} and \textit{covariate shift} connect to the bias and variance of the estimator, respectively.
+Finally, we show a tight concentration bound for the bias and variance terms using random matrix theory.
 
-%\subsection{Problem Setup}\label{sec_setup}
-
+\textbf{Data models.}
 Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
@@
 Without loss of generality, let the $t$-th task be the target task.
+
+\textbf{MTL estimator.}
 We consider the following linear multi-task learning architecture.
@@
 
+\textbf{A concentration bound.}
 To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.

### 2020-06-03 writeup/proof_examples.tex
reorg

@@
-\section{Supplementary Materials for the Theoretical Implications}
+\section{Proofs for Isotropic Settings}
 
@@
 which gives the second statement of Proposition \ref{prop_dist_transition}.
+\end{proof}
+
+%\subsection{Labeled data de-noising}\label{app_proof_data}
+
+Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$.
+In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
+
+\begin{proposition}%[Labeled data de-noising]
+\label{prop_var_transition}
+	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
+	Then we have the following transition with respect to $\sigma_1^2$:
+	\begin{itemize}
+		\item If $\sigma_1^2 < - \gamma_+^{1/2} \rho_1 \cdot p d^2+\left(1+ \gamma_+^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
+		\item If $\sigma_1^2 > -\gamma_-^{1/2}\rho_1\cdot p d^2   +\left(1+ \gamma_-^{-1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
+	\end{itemize}
+\end{proposition}
+As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
+%The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+%The details can be found in Appendix \ref{app_proof_data}.
+
+\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
+In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
+%the validation loss and the test error become
+%\begin{align*}
+%		\val(\hat{B}; w_1, w_2)
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
+%\end{align*}
+%and 
+%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
+In the isotropic model, using again the concentration of random vector with i.i.d. entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
+\begin{align*}
+	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
+	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
+\end{align*}
+with high probability for any constant $\e>0$.
+
+In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
+Since the proof is almost the same as the one for Lemma \ref{lem_hat_v}, we omit the details. 
+%$$|\hat w-1|=\OO(p^{-1}).$$
+%as in \eqref{hatw_add1}. 
+%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
+Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
+\be \label{simple2}
+\begin{split}
+\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
+&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
+&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+\end{split}
+\ee
+Then we write 
+$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
+where 
+$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
+satisfies \eqref{Deltavar} but with $\sigma^2$ replaced with $\sigma_2^2$, 
+$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
+satisfies \eqref{Deltabeta}, and 
+\begin{align*}	
+	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+\end{align*}
+%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
+%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
+To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
+\be\label{Deltavar2} 
+\al_-(\rho_1) - \oo(1)  \le \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
+where 
+$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
+Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
+
+%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
+%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
+
+Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ means the we have $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
+Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
+It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
+
+\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2}, if the following inequality holds,
+\be\label{cond sigma1}
+\begin{split} 
+&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
+&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_+^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_+(\rho_1)  , 
+\end{split}
+\ee
+then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
+\begin{align*}
+\sigma_1^2 < - pd^2\cdot \rho_1 \al_+(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2) \al_+^{-1}(\rho_1)\right]\cdot (1-\oo(1)).
+\end{align*}
+This proves the first claim of Proposition \ref{prop_var_transition} for positive transfer.
+
+\noindent{\bf Negative transfer.} On the other hand, if the following inequality holds,
+\be\label{cond sigma12}
+\begin{split} 
+&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
+&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_-^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_-(\rho_1) , 
+\end{split}
+\ee
+then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
+\begin{align*}
+\sigma_1^2 > - pd^2 \cdot \rho_1 \al_-(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\al_-^{-1}(\rho_1)\right]\cdot (1+\oo(1)).
+\end{align*}
+This proves the second claim of Proposition \ref{prop_var_transition} for negative transfer.
 \end{proof}
@@
 
-\subsection{Labeled data de-noising}\label{app_proof_data}
-
-In this section, we consider the case where the two tasks may have difference variances $\sigma_1^2\ne \sigma_2^2$ for the noises.
-In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
-
-\begin{proposition}%[Labeled data de-noising]
-\label{prop_var_transition}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
-	Then we have the following transition with respect to $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 < - \gamma_+^{1/2} \rho_1 \cdot p d^2+\left(1+ \gamma_+^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
-		\item If $\sigma_1^2 > -\gamma_-^{1/2}\rho_1\cdot p d^2   +\left(1+ \gamma_-^{-1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-%The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
-%The details can be found in Appendix \ref{app_proof_data}.
-
-\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
-%the validation loss and the test error become
-%\begin{align*}
-%		\val(\hat{B}; w_1, w_2)
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
-%\end{align*}
-%and 
-%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
-In the isotropic model, using again the concentration of random vector with i.i.d. entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
-\begin{align*}
-	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
-	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
-\end{align*}
-with high probability for any constant $\e>0$.
-
-In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
-Since the proof is almost the same as the one for Lemma \ref{lem_hat_v}, we omit the details. 
-%$$|\hat w-1|=\OO(p^{-1}).$$
-%as in \eqref{hatw_add1}. 
-%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
-Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
-\be \label{simple2}
-\begin{split}
-\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
-&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
-&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
-\end{split}
-\ee
-Then we write 
-$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
-where 
-$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
-satisfies \eqref{Deltavar} but with $\sigma^2$ replaced with $\sigma_2^2$, 
-$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
-satisfies \eqref{Deltabeta}, and 
-\begin{align*}	
-	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
-\end{align*}
-%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
-%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
-To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
-This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
-\be\label{Deltavar2} 
-\al_-(\rho_1) - \oo(1)  \le \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
-where 
-$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
-Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
-
-%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
-%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
-
-Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ means the we have $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
-Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
-It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
-
-\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2}, if the following inequality holds,
-\be\label{cond sigma1}
-\begin{split} 
-&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
-&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_+^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_+(\rho_1)  , 
-\end{split}
-\ee
-then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
-\begin{align*}
-\sigma_1^2 < - pd^2\cdot \rho_1 \al_+(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2) \al_+^{-1}(\rho_1)\right]\cdot (1-\oo(1)).
-\end{align*}
-This proves the first claim of Proposition \ref{prop_var_transition} for positive transfer.
-
-\noindent{\bf Negative transfer.} On the other hand, if the following inequality holds,
-\be\label{cond sigma12}
-\begin{split} 
-&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
-&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_-^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_-(\rho_1) , 
-\end{split}
-\ee
-then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
-\begin{align*}
-\sigma_1^2 > - pd^2 \cdot \rho_1 \al_-(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\al_-^{-1}(\rho_1)\right]\cdot (1+\oo(1)).
-\end{align*}
-This proves the second claim of Proposition \ref{prop_var_transition} for negative transfer.
-\end{proof}
-
 %\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.

### 2020-06-03 writeup/proofs_sec3.tex
reorg

--- 2020-06-03 writeup/proofs_sec3.tex
@@
-\section{Supplementary Materials for the Technical Results}\label{app_proof_sec3}
+\section{Supplementary Materials for Section \ref{sec_main}}\label{app_proof_sec3}
 
-\subsection{Preliminaries}
-
-\subsubsection{Data models}
+\subsection{Data Models}\label{app_data_model}
 First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
@@
 
-\subsubsection{The Multi-Task Learning Estimator} %\label{sec_MTLest}
+\subsection{The Multi-Task Learning Estimator}\label{sec_MTLest}
 From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
@@
 
-\subsubsection{Tools for Random Matrices}
+\subsection{Concentration Bounds}\label{app_tool}
 We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$.

### 2020-06-03 writeup/setup.tex
reorg
sec 2

@@
 Then, we study the bias-variance tradeoff of the MTL estimator, and show how \textit{task similarity}, \textit{sample size} and \textit{covariate shift} connect to the bias and variance of the estimator, respectively.
-Finally, we show a tight concentration bound for the bias and variance terms using random matrix theory.
+Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
 
 \textbf{Data models.}
-Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
+Suppose we have $t$ training datasets denoted by $(X_1, Y_1), \dots, (X_t, Y_t)$.
+In the high-dimensional linear regression setting (e.g.
+\cite{HMRT19,BLLT20}), the features of the $k$-th task $X_k\in\real^{n_i\times p}$ consists of $n_k$ feature vectors given by $x_i = \Sigma_k^{1/2}z_i$, for $1\le i \le n_k$.
+Each $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
+%Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
 %Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d.
 entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-Without loss of generality, let the $t$-th task be the target task.
+%Without loss of generality, let the $t$-th task be the target task.
 
-\textbf{MTL estimator.}
-We consider the following linear multi-task learning architecture.
+\textbf{The MTL estimator.}
+We consider the following linear multi-task learning model \cite{R17,MTDNN19,WZR20}.
 \begin{align}
 	\label{eq_mtl}
-	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2,
+	f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2,
 \end{align}
-where $B\in\real^{p\times r}$ and $W_i\in\real^r$.
-Here $B$ provides a shared subspace for all tasks and $W_i$ fits $B$ suitably to each task.
+where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
+The linear layer $B$ provides a shared subspace for all tasks whereas each output layer $W_k$ fits the $k$-th task given the linear layer.
 Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
@@
 
-\textbf{A concentration bound.}
+\textbf{Concentration bounds.}
 To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.

### 2020-06-03 writeup/proof_main.tex
reorg
finish re structure

@@
+\section{Proofs for General Settings}
+
+We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$.
+The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p\to \infty$.
+When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
+\begin{lemma}\label{lem_minv}
+Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
+	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
+with high probability.
+\end{lemma}
+
+We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
+The second lemma extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
+It is the main random matrix theoretical input of this paper.
+%which deals with the inverse of the sum of two random matrices, which
+%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
+
+\begin{lemma}\label{lem_cov_shift}
+	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
+	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
+	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
+We have that for any constant $\e>0$,
+	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
+	\begin{align}\label{lem_cov_shift_eq}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
+	\end{align}
+with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
+	\begin{align}
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+\label{eq_a12extra}
+	\end{align}
+\end{lemma}
+
+\textbf{Proof Overview.} We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
+We use the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
+Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
+In particular, when $z=0$, $\tr[R_\infty(0)]$ gives the expression inTheorem \ref{lem_cov_shift_informal}.
+The details can be found in Appendix \ref{sec_maintools} and \ref{sec_Gauss}.
+
+Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which will be needed when we estimate the first term on the right-hand side of \eqref{eq_te_mtl_2task}.
+
+\begin{lemma}\label{lem_cov_derivative}
+In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
+\begin{equation}\label{lem_cov_derv_eq}
+\begin{split}
+&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
+&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
+\end{split}
+\end{equation}
+with high probability, where $a_{3}$ and $a_4$ satisfy the following system of linear equations:
+\begin{gather}\label{eq_a34extra}
+		\left(\rho_2  a_2^{-2}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
+		= b_0, \quad \left(\rho_1 a_1^{-2} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .
+%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
+%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
+	\end{gather}
+Here $b_0$, $b_1$ and $b_2$ are defined as
+$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
+\end{lemma}
+%We will give the proof of this lemma in Section \ref{sec_maintools}.
+
+The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}.
+We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
+\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.
+
 \subsection{Proof for Two Tasks with General Covariates}\label{app_proof_main}

### 2020-06-03 writeup/proofs_sec3.tex
finish re structure

@@
-\section{Supplementary Materials for Section \ref{sec_main}}\label{app_proof_sec3}
+\section{Assumptions and Models}\label{app_proof_sec3}
 
@@
 Hence to minimize $\wt f$, it suffices to minimize $\val(\hat{B}; v)$ over $v$.
-
-\subsection{Concentration Bounds}\label{app_tool}
-We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$.
-The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p\to \infty$.
-When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
-\begin{lemma}\label{lem_minv} 
-Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
-	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
-with high probability.
-\end{lemma}
-
-We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-The second lemma extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
-It is the main random matrix theoretical input of this paper.
-%which deals with the inverse of the sum of two random matrices, which 
-%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-\begin{lemma}\label{lem_cov_shift}
-	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
-We have that for any constant $\e>0$,
-	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
-	\end{align}
-with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
-	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12extra}
-	\end{align}
-\end{lemma}
-
-Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which will be needed when we estimate the first term on the right-hand side of \eqref{eq_te_mtl_2task}.
-
-\begin{lemma}\label{lem_cov_derivative}
-In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
-&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
-\end{split}
-\end{equation}
-with high probability, where $a_{3}$ and $a_4$ satisfy the following system of linear equations: 
-\begin{gather}\label{eq_a34extra}
-		\left(\rho_2  a_2^{-2}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
-		= b_0, \quad \left(\rho_1 a_1^{-2} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .  
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-Here $b_0$, $b_1$ and $b_2$ are defined as
-$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
-\end{lemma}
-%We will give the proof of this lemma in Section \ref{sec_maintools}.
-
-The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}.
-We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.

### 2020-06-03 writeup/setup.tex
finish re structure

@@
-\section{A Concentration Bound Generalizing Single-Task Settings}
-\label{sec_main}
+\section{Preliminaries}
+\label{sec_prelim}
 
 We begin by defining the data model and the multi-task learning estimator that we study.
-Then, we study the bias-variance tradeoff of the MTL estimator, and show how \textit{task similarity}, \textit{sample size} and \textit{covariate shift} connect to the bias and variance of the estimator, respectively.
-Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
+Then, we describe the bias-variance tradeoff of the MTL estimator, and show how \textit{task similarity}, \textit{sample size} and \textit{covariate shift} connect to the bias and variance of the estimator, respectively.
+%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
 
@@
 
-\textbf{The MTL estimator.}
+\textbf{The multi-task estimator.}
 We consider the following linear multi-task learning model \cite{R17,MTDNN19,WZR20}.
@@
 
-\textbf{Concentration bounds.}
+\textbf{Bias-variance tradeoff.}
 To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.
@@
 %(ii) the positive effect from variance reduction;
-
-\begin{theorem}[Informal]\label{lem_cov_shift_informal}
-	In the setting of two tasks,
-	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
-	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-{\small\begin{align*}%\label{eq_introX1X2}
-		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-	\end{align*}}%
-where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
-\end{theorem}
-
-%\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}
-
-%\textbf{Multi-task learning.}
-
-\textbf{Proof Overview.} We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
-We use the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
-Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
-In particular, when $z=0$, $\tr[R_\infty(0)]$ gives the expression inTheorem \ref{lem_cov_shift_informal}.
-The details can be found in Appendix \ref{sec_maintools} and \ref{sec_Gauss}.
-
-Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
-For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
-This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
-Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
-%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-The details are presented in Appendix \ref{app_proof_main}.
-
-%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
-
-\textbf{Remark.} Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-The concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
 

### 2020-06-03 writeup/transfer.tex
sec 2
finish re structure

@@
-\section{Multi-Task vs. Single-Task Learning: The Bias-Variance Tradeoff}\label{sec_insight}
+\section{Comparing Multi-Task Learning to Single-Task Learning}\label{sec_insight}
 
@@
 
-\subsection{General Settings}
+\subsection{Results for General Settings}\label{sec_main}
 
@@
 %, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-\begin{corollary}\label{thm_main_informal}
+\begin{theorem}\label{thm_main_informal}
 	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin, $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and $\rho_2 > 1$ be a fixed value.
@@
 	\squishend
-\end{corollary}
+\end{theorem}
 
@@
 This will be the focus of Section \ref{sec_insight}.
+
+\begin{lemma}[Informal]\label{lem_cov_shift_informal}
+	In the setting of two tasks,
+	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
+	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
+	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
+	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+{\small\begin{align*}%\label{eq_introX1X2}
+		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
+		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
+	\end{align*}}%
+where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
+\end{lemma}
+
+\textbf{Remark.} Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
+The concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
+
+Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
+For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
+This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
+Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
+This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
+%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
+The details are presented in Appendix \ref{app_proof_main}.
 

### 2020-06-03 writeup/experiments.tex
finish re structure
restructure

@@
-\section{Practical Connections: Detecting and Mitigating Negative Transfer}
+\section{Experiments}
 
@@
 
-\subsection{Experimental Results: Improving Data Efficiency}
+\subsection{Experimental Results}
 
@@
 
+\textbf{Explaining .} In Figure \ref{fig_ablation}, we validate the three components of our theory on the sentiment analysis dataset.
+The experimental procedure is left to Appendix \ref{app_it}.
+
 \textbf{Understanding MTL results via STL results.}
@@
 The results show that STL performances are indicative of MTL performances.
-
-\textbf{Validation our theory.} In Figure \ref{fig_ablation}, we validate the three components of our theory on the sentiment analysis dataset.
-The experimental procedure is left to Appendix \ref{app_it}.

### 2020-06-03 writeup/extensions.tex
restructure

--- 2020-06-03 writeup/transfer.tex
@@
-\section{Multi-Task vs. Single-Task Learning: The Bias-Variance Tradeoff}\label{sec_insight}
-
-We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
-We show how negative transfer occurs by varying task similarity or sample size.
-Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-
-\subsection{General Settings}
-
-We provide a sharp analysis of the bias-variance tradeoff for two tasks with general covariance matrices.
-We state our result as follows.
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-\begin{corollary}\label{thm_main_informal}
-	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin, $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and $\rho_2 > 1$ be a fixed value.
- 	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
-	\squishlist
-		\item If $\Delta_{\bias} - \Delta_{\vari} < -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Delta_{\bias} - \Delta_{\vari} > \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
-\end{corollary}
-
-Corollary \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target sample size is small.
-For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
-%determined by the covariate shift matrix and the model shift.
-%The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of the threshold can be complicated (as are the previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-This will be the focus of Section \ref{sec_insight}.
+\section{Extensions to Multiple Tasks and Transfer Learning Settings}
 
@@
 %A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
-
-\subsection{Task Similarity}\label{sec_similarity}
-
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the following simplified setting.
-
-\textit{The isotropic model.}
-	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
-	Recall that each task has sample size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
-	And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denotes the covariates of the two tasks, respectively.
-	We assume that for the target task, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
-	For the source task, $\beta_1 $ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
-	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma_i^2$, for $i=1,2$.
-	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{app_proof_sec3}.
-
-In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
-%We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
-%Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
-%{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
-Our result below will provide an explanation to this phenomenon.
-%Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
-We introduce the following notations.
-\begin{align*}
-	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
-\end{align*}
-
-\begin{proposition}[Task model distance]\label{prop_dist_transition}
-	In the isotropic model, suppose that $\rho_1 > 1$ and $\sigma_1 = \sigma_2 = \sigma$.
-	Then we have that
-	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
-	\squishlist
-		\item If $\Psi(\beta_1, \beta_2) < \gamma_{+}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) \ge \gamma_{-}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
-	\squishend
-	Here $\gamma_{-} = (1-\oo(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+\oo(1))\cdot(1 + \rho_1^{-1/2})^4$.
-	Concretely, if $\rho_1 > 40$, then $\gamma_{-} \in (1,2)$ and $\gamma_{+} \in (1/2, 1)$.
-\end{proposition}
-
-Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
-Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
-Prosposition \ref{prop_dist_transition} explains the transition observed in Figure \ref{fig_model_shift}.
-Note that there are several unexplained observations near the transition threshold $0$, which are caused by the concentration errors $\gamma_+, \gamma_-$.
-%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
-%Figure \ref{fig_model_shift} shows the result.
-%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-%The proof of Proposition \ref{prop_dist_transition} involves two parts.
-%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}. %, which is based on our main result described later in Theorem \ref{thm_model_shift}.
-
-\textbf{Algorithmic consequence.}
-We can in fact extend the result to the cases where the noise variance is different.
-In this case, we will see that MTL is particularly effective.
-%As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Concretely, suppose the noise variance $\sigma_1^2$ of task $1$ differs from the noise variance $\sigma_2^2$ of task $2$.
-If $\sigma_1^2$ is too large, the source task provides a negative transfer to the target.
-If $\sigma_1^2$ is small, the source task is more helpful.
-We leave the result to the Appendix in Proposition \ref{prop_var_transition}.
-Inspired by the observation, we propose a single-task based metric to help understand MTL results using STL results.
-\squishlist
-	\item For each task, we train a single-task model.
-	Let $z_s$ and $z_t$ be the prediction accuracy of each task, respectively.
-	Let $\tau\in(0, 1)$ be a fixed threshold.
-	\item If $z_s - z_t > \tau$, then we predict that there will be positive transfer when combining the two tasks using MTL.
-	If $z_s - z_t < -\tau$, then we predict negative transfer.
-\squishend
-
-\subsection{Sample Size}\label{sec_data_size}
-
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
-More generally, such results are still applicable when all task data are being added simultaneously.
-On the other hand, for many applications of multi-task learning, the data sources are usually heterogeneous.
-For such settings, we have observed that adding more labeled data from one task does not always help.
-%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-Using the isotropic model, we consider what happens if we vary the source task sample size.
-%Figure \ref{fig_size} provides a simulation result for such a setting.
-%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-Our result below explains the phenomenon of Figure \ref{fig_size}.
-
-\begin{proposition}[Source/target sample size]\label{prop_data_size}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-	We have that
-	\squishlist
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\gamma_+} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \gamma_+^{-1}}$, then w.h.p.
-$\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1}{\gamma_-} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \gamma_{-}^{-1}}$, then w.h.p.
-$\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
-\end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the data ratio $n_1 / n_2$.
-From Figure \ref{fig_size}, we see that our result is able to explain the transition from positive to negative transfer.
-There are several unexplained observations near $y = 0$ caused by the errors $\gamma_-, \gamma_+$.
-The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-
-\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
-%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using $R \cdot n_i$ datapoints from every task.
-The data efficiency ratio roughly scales as
-\[ \argmin_{x\in(0, 1)} ~~
-		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
-		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
-For example, the data efficiency ratio is $1$ if there is negative transfer.
-Using our tools, we show that in the isotropic model, the data efficiency ratio is
-equal to \[ \frac{1}{\rho_1 + \rho_2} {+ \frac{1}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
-Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$, the transfer is positive.
-Hence the data efficiency ratio quantifies how effective is the positive transfer using MTL.
-%In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-The precise statement can be found in Appendix \ref{app_proof_32}.
-
-\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
-In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-\squishlist
-	\item We divide the source task data into $S$ batches.
-	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
-	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
-	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\squishend
-
-\subsection{Covariate Shift}\label{sec_covshift}
-
-So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-In general, the covariance matrices of the two tasks may be different such as in text classification.
-In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
-We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
-
-\begin{example}\label{ex_complement}
-	We measure covariate shift by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
-	Assume that $\Psi(\beta_1, \beta_2) = 0$ for simplicity.
-	We compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	Hence, $\lambda$ measures the severity of covariate shift.
-	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as $n_1/n_2$ increases, the performance gap between the case of $M = \id$ and $\lambda = 2$ or $4$ increases for MTL.
-\end{example}
-
-%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in decreasing order.
-Let $\mu_{\min} < \mu < \mu_{\max}$ are fixed values that do not grow with $p$.
-Consider the following bounded set
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \mid \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_p, \lambda_1 \le \mu_{\max}},
-\end{align*}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
-	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{proposition}
-The following proposition shows that when $n_1 \gg n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized when there is no covariate shift between source and target task.
-The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
-
-%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
-%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
-%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
-\textbf{Algorithmic consequence.}
-Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
-Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in Wu et al.'20 \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
-The idea is to add an alignment module between the input and the shared module $B$.
-This new module is then trained together with $B$ and the output layers.
-We validate our insight on this procedure in the experiments.

### 2020-06-03 writeup/setup.tex
restructure

@@
-\section{Preliminaries}
+\section{Problem Formulation for Multi-Task Learning}
 \label{sec_prelim}
@@
 
-\textbf{Data models.}
+\textbf{Setup.}
 Suppose we have $t$ training datasets denoted by $(X_1, Y_1), \dots, (X_t, Y_t)$.
@@
 
-\textbf{The multi-task estimator.}
+\textbf{Model.}
 We consider the following linear multi-task learning model \cite{R17,MTDNN19,WZR20}.
@@
 
-\textbf{Bias-variance tradeoff.}
+\textbf{Problem statement.}
 To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.

### 2020-06-03 writeup/transfer.tex
restructure

@@
 
-\subsection{Results for General Settings}\label{sec_main}
+\subsection{Analyzing the Bias-Variance Tradeoff using Random Matrix Theory}\label{sec_main}
+
+\begin{lemma}[Informal]\label{lem_cov_shift_informal}
+	In the setting of two tasks,
+	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
+	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
+	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
+	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+{\small\begin{align*}%\label{eq_introX1X2}
+		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
+		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
+	\end{align*}}%
+where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
+\end{lemma}
 
@@
 
-\begin{lemma}[Informal]\label{lem_cov_shift_informal}
-	In the setting of two tasks,
-	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
-	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-{\small\begin{align*}%\label{eq_introX1X2}
-		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-	\end{align*}}%
-where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
-\end{lemma}
-
 \textbf{Remark.} Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
@@
 The details are presented in Appendix \ref{app_proof_main}.
-
-Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, where $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$.
-Suppose $(B^{\star})^\top\Sigma B^{\star}$ is of full rank in the sense that $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
-	We have the following
-	\squishlist
-		\item $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ with high probability if
-		$$\left(1 - \norm{U_r(t)}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r U_r(t) - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
-		\item $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$ with high probability if
-		$$\left(1 - \norm{U_r(t)}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r U_r(t) - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right).$$
-	\squishend
-\end{theorem}
-%A similar result for the second setting can be found in Appendix \ref{app_proof_many_tasks}.
 

### 2020-06-03 writeup/proofs_sec3.tex
wip

@@
-\section{Assumptions and Models}\label{app_proof_sec3}
+\section{Missing Details of Problem Formulation}\label{app_proof_sec3}
 
-\subsection{Data Models}\label{app_data_model}
+\textbf{Assumptions on task data generation.}
 First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
@@
 
-\subsection{The Multi-Task Learning Estimator}\label{sec_MTLest}
+\textbf{The multi-task learning estimator.}
 From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.

### 2020-06-03 writeup/proof_examples.tex
cs
reorg

@@
-\section{Proofs for Isotropic Settings}
+\section{Proofs for Isotropic and Covariate Shifted Settings}
 
-\subsection{Supplement to Section \ref{sec_similarity}}\label{app_proof_31}
+\subsection{Missing Proofs of Section \ref{sec_similarity}}\label{app_proof_31}
 
@@
 
-\subsection{Supplement to Section \ref{sec_data_size}} \label{app_proof_32}
+\subsection{Missing Proofs of Section \ref{sec_data_size}} \label{app_proof_32}
 We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.
@@
 
-\subsection{Supplement to Section \ref{sec_covshift}}\label{app_proof_33}
+\subsection{Missing Proofs of Section \ref{sec_covshift}}\label{app_proof_33}
 

### 2020-06-03 writeup/proof_extension.tex
reorg

--- 2020-06-02 writeup/proof_main.tex
@@
-\subsection{Proof for Two Tasks with General Covariates}\label{app_proof_main}
+\section{Proofs for the Extended Results}
 
-%To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
-%\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
-%We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
-%\todo{write a brief technical overview}
-
-In this section, we state and prove the formal version of Theorem \ref{thm_main_informal}, which covers the two tasks case with $t=2$.
-In this section, we consider the case where the entries of $\e_1$ and $\e_2$ have the same variance $\sigma_1^2=\sigma_2^2=\sigma^2$.
-%Moreover, we shall denote $\beta_1$ and $\beta_2$ by $\beta_1$ and $\beta_2$, standing for ``source task" and ``target task", respectively.
-
-First, we  introduce several quantities that will be used in our statement, and they are also related to the quantities in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-Given the optimal ratio $\hat v$, let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix, and ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ be the eigenvalues of $\hat{M}^{\top}\hat{M}$.
-Define $(\hat a_1, \hat a_2)$ as the solution to the following system of deterministic equations,
-	\be
-		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat \lambda_i^2 \hat a_1}{ \hat \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
-		 \ee
-		 After obtaining $(\hat a_1,\hat a_2)$, we can solve the following linear equations to get $(\hat a_3,\hat a_4)$:
-\begin{gather}
-		\left(\rho_2 \hat a_2^{-2}- \hat b_0\right)\cdot \hat  a_3 - \hat b_1 \cdot \hat a_4
-		=\hat b_0, \quad \left(\rho_1\hat a_1^{-2} - \hat b_2  \right)\cdot \hat a_4 - \hat b_1 \cdot \hat a_3 =\hat b_1 .\label{eq_a3} 
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-where we denoted
-$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat \lambda_i^{2k}}{ (\hat a_2 +\hat  \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
-Then we introduce the following matrix
-\be\label{defnpihat}\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat  a_1 \hat {M}^{\top}\hat {M}+\hat a_2 )^2} \hat {M}^{\top}.\ee
-%which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
-%$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
-We introduce two factors that will appear often in our statements and discussions:
-$$\al_-(\rho_1):=\left(1- \rho_1^{-1/2}\right)^2,\quad \al_+(\rho_1):=\left(1 + \rho_1^{-1/2}\right)^2.$$ 
-In fact, $\al_-(\rho_1)$ and $\al_+(\rho_1)$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
-In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry.
-Finally, we introduce the error term
-\be\label{eq_deltaextra}\delta\equiv \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\lambda_{\min}^2(\hat M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2,\ee
-where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. Note that this factor converges to 0 as $\rho_1$ increases.
-
-%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2.$$
-%{\cor may be able to get a better bound, but the statement will be long}
-
-Now we are ready to state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
-
-\begin{theorem}\label{thm_model_shift}
-%For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
-Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2}. With high probability, we have
-	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta, \label{lower}
-	\end{align}
-	where
-	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} } \label{Deltavarv} \\
-		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
-	\end{align}
-\end{theorem}
-
-For the isotropic model in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
-\begin{lemma}\label{prop_model_shift_tight}
-		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_2$ is a random vector with i.i.d.
-entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_1$ is a random vector such that $(\beta_1 - \beta_2)$ is a random vector with i.i.d.
-entries with mean $0$, variance $d^2$ and all moments.
-Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi}.$
-	Then we have
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}.
-		\end{align*}
-\end{lemma}
-
-Now we give the proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-
-\begin{proof}[Proof of Theorem \ref{thm_model_shift}]
-%\noindent
-%To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
-%$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
-%where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
-%\begin{equation}\label{eq_12moment} %\label{assm1}
-%\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
-%\end{equation}
-%\todo{A proof outline; including the following key lemma.}
-Note that 
-\begin{align*}
-L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL}) &=\sigma^2 \left(  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} -  \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right) \\
-&- \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2=:\delta_{\vari}(\hat v) - \delta_{\bias}(\hat v).
-\end{align*}
-The proof is divided into the following four steps. 
-\begin{itemize}
-\item[(i)] We first consider $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a fixed $v\ge 0$.
-Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
-%$$\sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}},\quad \sigma^2 \cdot \bigtr{({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2},$$
-%and the difference between them
-
-\item[(ii)] Using the approximate isometry property of $X_1$ (see \eqref{eq_isometric} below), we will bound the bias term $ \delta_{\bias}(v)$
-%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - {v} \beta_2)}^2$$
-through 
-\be\label{deltabetapf}
-\wt\delta_{\bias}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_1 - {v} \beta_2)}^2.\ee
-
-\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\bias}$ term.
-
-\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M= \hat v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a possibly random $\hat v$ which depends on $Y_1$ and $Y_2$.
-\end{itemize}
-
-\paragraph{Step I: Variance reduction.} Let $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for any fixed constant $v\ge 0$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
-$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
-and 
-$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
-with high probability, where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2}. Combining them, we get 
-\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{whp},
-\ee 
-where $\Delta_{\vari}(v)$ is defined as in \eqref{Deltavarv} but with $\hat v$ replaced by $v$.
-
-\paragraph{Step II: Bounding the bias term.}
-In this step, we shall use the following the following bounds on the singular values of $Z_1$: for any fixed $\e>0$, we have
-\begin{align}
-\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq \frac{Z_1^T Z_1}{n_1}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e})   \label{eq_isometric}
-\end{align}
-with high probability.
-In fact, $Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its nonzero eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
-For the estimate \eqref{eq_isometric} we used \cite[Theorem 2.10]{isotropic} to get a stronger probability bound.
-
-Next we shall use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$ in \eqref{deltabetapf}.  
-%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
-\begin{lemma}\label{prop_model_shift}
-	In the setting of Theorem \ref{thm_model_shift},
-	we denote by $K = (v^2X_1^{\top}X_1 + X_2^{\top}X_1)^{-1}$, and
-	\begin{align*}
-		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_1 - v\beta_2)}^2, \\
-		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
-		\delta_{\e}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
-	\end{align*}
-	Then we have whp,
-	\begin{align*}
-		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_\e.
-	\end{align*}
-%	We have that
-%	\begin{align*}
-%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
-%		\le  \delta_1 - \delta_2
-%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
-%	\end{align*}
-%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
-%	\begin{align*}
-%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
-%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \beta_2)}^2.
-%	\end{align*}
-\end{lemma}
-
-\begin{proof}
-	%The proof follows by applying equation \eqref{eq_isometric}.
-	%Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
-	Denote by $\cE = Z_1^{\top}Z_1 - {n_1}\id$. Then we can write
-%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_1 - \hat{w}\beta_2)}^2$.
-	%We have
-	\begin{align}
-%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \hat{w}\beta_2)}^2 \nonumber \\
-		 \delta_{\bias}(v)-\wt\delta_{\bias}(v)&= {2v^2n_1}(\beta_1 - v\beta_2)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_1 - v\beta_2) \nonumber
-		\\
-		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2. \label{eq_lem_model_shift_1}
-%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
-	\end{align}
-	Using \eqref{eq_isometric}, we can bound  
-	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{whp}.$$
-	Thus we can estimate that 
-	\begin{align*}
-	| \delta_{\bias}(v)-\wt\delta_{\bias}(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-	& \le v^2 n_1^2 \left[ \al_+^2(\rho_1) + \OO(p^{-1/2+\e}) -1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2,
-	\end{align*}
-	which concludes the proof by the definition of $\delta_\e$.	
-%	we can bound the second term on the RHS of equation \eqref{eq_lem_model_shift_1} as
-%	\begin{align*}
-%		& \bigabs{(\beta_1 -  \beta_2)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - v\beta_2)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}}} \\
-%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2) (\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \\
-%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
-%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2 \tag{since the matrix inside is rank 1}
-%	\end{align*}
-%	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
-%	\begin{align*}
-%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2
-%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 -  \beta_2)}^2.
-%	\end{align*}
-%	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
-%	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
-%	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
-\end{proof}
-Note by \eqref{eq_isometric}, we have with high probability,
-\begin{align*}
-&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} = \hat M\frac{1}{(\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^2}\hat M^\top \\
-&\preceq  n_1^2 \hat M\frac{1}{\left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^2}\hat M^\top \\
-&\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + 2\left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
-&\prec [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
-\end{align*}
-for some small enough constant $c>0$. Together with Lemma \ref{prop_model_shift}, we get with high probability,
-\be\label{bounddelta-}
-\left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le (1-c) \delta(v)
-\ee
-for some small constant $c>0$, where recall $\delta(v)$ defined in \eqref{eq_deltaextra}.
-
-\paragraph{Step III: The limit of $\wt\delta_{\bias}(v)$.} 
-Using Lemma \ref{lem_cov_derivative} with $\Sigma_1$ and $M$ replaced by $v^2\Sigma_1$ and $\hat M$, we obtain that 
-\begin{align*}
-\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 + \hat a_3)\id + \hat a_4 \hat{M}^{\top}\hat{M}}{( a_1 \hat{M}^{\top}\hat{M}+a_2 )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
-&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
-\end{align*}
-with high probability. Together with and \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that whp,
-\be\label{dicho_varbeta}
-\begin{cases}\delta_{\vari}(v)>\delta_{\bias}(v), & \text{ if } \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \ge   \delta(v),\\
-\delta_{\vari}(v)<\delta_{\bias}(v),  & \text{ if }  \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \le -  \delta(v).\end{cases}
-\ee
-
-\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result to $v=\hat v$, which is random and depends on $X_1$ and $X_2$.
-We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{dicho_varbeta}
-%\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
-holds uniformly for all $v\in [0, C_0]$. In fact, for a large constant $C_1>0$, we consider $v$ belonging to a discrete set 
-$$V:=\{v_k = kp^{-1}: 1\le k \le C_0p +1\}.$$
-Then using the arguments for the first three steps and a simple union bound, we get that
-\eqref{dicho_varbeta} holds simultaneously for all $v\in V$ with high probability. On the other hand, by \eqref{eq_isometric} the event
-$$\Xi_1:=\left\{ \al_-(\rho_1)/2 \preceq  \frac{Z_1^T Z_1}{n_1}  \preceq   2\al_+(\rho_1) ,\  \al_-(\rho_2)/2 \preceq  \frac{Z_2^T Z_2}{n_2}  \preceq   2\al_+(\rho_2)\right\}$$
-holds with high probability. Now it is easy to check that on $\Xi_1$, for all $v_k \le v\le v_{k+1}$ we have the following estimates:
-\begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|\lesssim p^{-1}\delta_{\vari}(v_k),\ \ |\delta_{\bias}(v) -\delta_{\bias}(v_k)|\lesssim p^{-1}\delta_{\bias}(v_k), \ \   |\delta(v)-\delta(v_k)|\lesssim p^{-1}\delta(v_k),\\
-& |\Delta_{\bias}(v) -\Delta_{\bias}(v_k)|\lesssim p^{-1}\Delta_{\bias}(v_k),\ \ |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|\lesssim p^{-1}\Delta_{\vari}(v_k).
-\end{align*}
-Then a simple application of triangle inequality gives that the event 
-$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }0\le v \le C_0\}$$
-holds with high probability. On the other hand, on $\Xi_1$ one can see that for any small constant $\e>0$,
-\begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e\delta_{\vari}(C_0),\quad |\delta_{\bias}(v) -\delta_{\bias}(C_0)|\le \e\delta_{\bias}(C_0), \quad  |\delta(v)-\delta(C_0)|\le \e\delta(C_0),\\
-& |\Delta_{\bias}(v) -\Delta_{\bias}(C_0)|\le \e\Delta_{\bias}(C_0),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e\Delta_{\vari}(C_0),
-\end{align*}
-for all $v\ge C_0$ as long as $C_0$ is chosen large enough depending on $\e$.
-Together with the estimate at $C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\ge 0$ on the high probability event $\Xi_1\cap \Xi_2$.
-This concludes the proof since $v$ must be one of the positive values.
-\end{proof}
-
-\begin{remark}
-One can see from the above proof that the main error, $\delta$, of Theorem \ref{thm_model_shift} comes from approximating $\delta_{\bias}$ by $\wt\delta_{\bias}$ in \eqref{bounddelta-}.
-In order to improve this estimate and obtain an exact asymptotic result as for the $\delta_{\vari}$ term, one needs to study the singular value distribution of the following random matrix:
-$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  {v}^2 .$$
-In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ have been studied in the name of Fisher matrices; see e.g.
-\cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix theory literature, and the study of the singular values of $\cal X + v^2$ will be even harder.
-We leave this problem to future study.
-\end{remark}
-
-By replacing \eqref{bounddelta-} with a tighter bound in Step II of the above proof, we can conclude the proof of Lemma \ref{prop_model_shift_tight}.
-
-\begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
-For any fixed $v\ge 0$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
-entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
-Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
-\begin{align}
-&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
-\end{align}
-where we denoted $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}.
-Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
-\begin{align*}
-v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
-\end{align*}
-Recalling that $\Sigma_1=\id$ and bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
-\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
-where 
-$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim 1$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get 
-\be\label{replaceest}
-  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
-\ee
-Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Theorem \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
-In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term, We omit the details.
-\end{proof}
-
-\subsection{Proof for Many Tasks with the Same Covariate}\label{app_proof_many_tasks}
+\subsection{Many Tasks with the Same Covariate}\label{app_proof_many_tasks}
 
@@
 %\end{itemize}
+
+\input{proof_taskonomy.tex}

### 2020-06-03 writeup/proof_main.tex
reorg

@@
-\section{Proofs for General Settings}
+\section{Proof of Theorem \ref{thm_main_informal}}
 
@@
 
-\subsection{Proof for Two Tasks with General Covariates}\label{app_proof_main}
+%\subsection{Proof for Two Tasks with General Covariates}\label{app_proof_main}
 
@@
 \end{proof}
-
-\subsection{Proof for Many Tasks with the Same Covariate}\label{app_proof_many_tasks}
-
-%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
-Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
-The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
-
-%In this section we consider the setting with $k$ many that have the same covariates.
-%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-
-\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-In this setting, we need to study the following loss function:
-\begin{align}
-	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
-\end{align}
-%In order to prove Theorem \ref{thm_many_tasks}, we will derive a closed form solution for equation \eqref{eq_mtl_same_cov}. \todo{check!} 
-For any fixed $W_1, W_2, \dots, W_t \in \R^r$, we can derive a closed form solution for $B$ as
-	\begin{align*}
-		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
-		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1},
-	\end{align*}
-	where we denote $\cal W \in\real^{r\times t}$ as $\cal W=[W_1, W_2, \dots, W_t]$.
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use concentration to get the validation loss as
-\be\label{eq_multival}\wt f(\hat B; \cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
-Here $\val(\cal W)$ is defined as 
-%it remains to consider minimizing the validation loss 
-	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari}(\cal W),$$ 
-where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
-	\begin{align*}
-		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
-	\end{align*}
-	and the variance term $\delta_{\vari}(\cal W)$ can be calculated as 
-	\begin{align*}
-		\delta_{\vari}(\cal W):= \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-	\end{align*}
-It suffices to minimize $\delta_{\bias}(\cal W)$ over $\cal W$, since both $t N \sigma^2$ and $\delta_{\vari}(\cal W)$ do not depend on the weights.
-
-We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{k\times k}$, whose $(i,j)$-th entry is equal to $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$. 
-	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-	Now we can write $\delta_{\bias}(\cal W)$ succinctly as 
-	\begin{align*}
-		\delta_{\bias}(\cal W)= \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
-	\end{align*}
-	From this equation we can solve the minimizer optimally as $Q_0=U_{r}U_r^{\top}$.
-On the other hand, let $\hat {\cal W}$ be the minimizer of $\wt f$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
-We claim that $\hat Q$ satisfies
-	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\| = \oo(1) \quad \text{whp}.\ee
-	In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by \eqref{eq_isometric}, we obtain that
-	$$   \val(\hat {\cal W}) + t  \sigma^2 > (\val( {\cal W}_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ \wt f(\hat B; \hat{\cal W})>\wt f(\hat B; {\cal W}_0),$$
-	that is, $\hat {\cal W}$ is not a minimizer. This leads to a contradiction.
-
-	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r U_r(i) +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that
-	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_2 \right) }^2
-		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
-	\end{align*}
-	with high probability, where we used Lemma \ref{lem_minv} in the last step. Similar, by Lemma \ref{lem_minv} we have
-	$$\te(\hat{\beta}_t^{\MTL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
-Combining the above two estimates, we conclude the proof.
-\end{proof}
-%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
-%\begin{itemize}
-%	\item The de-noising effect of multi-task learning.
-%	\item Multi-task training vs single-task training can be either positive or negative.
-%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
-%\end{itemize}

### 2020-06-03 writeup/setup.tex
wip

@@
 
-We begin by defining the data model and the multi-task learning estimator that we study.
-Then, we describe the bias-variance tradeoff of the MTL estimator, and show how \textit{task similarity}, \textit{sample size} and \textit{covariate shift} connect to the bias and variance of the estimator, respectively.
+We begin by defining our problem setup including the multi-task estimator we study.
+Then, we describe the bias-variance tradeoff of the multi-task estimator, and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
 %Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
 
-\textbf{Setup.}
+\textbf{Problem setup.}
 Suppose we have $t$ training datasets denoted by $(X_1, Y_1), \dots, (X_t, Y_t)$.
@@
 Each $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
+The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
 %Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
@@
 
-\textbf{Model.}
-We consider the following linear multi-task learning model \cite{R17,MTDNN19,WZR20}.
+We focus on the following problem that specializes the commonly used hard parameter sharing model (e.g. \cite{R17,MTDNN19}) to the linear regression setting \cite{WZR20}.
 \begin{align}
@@
 The linear layer $B$ provides a shared subspace for all tasks whereas each output layer $W_k$ fits the $k$-th task given the linear layer.
-Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
+Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
+
 Then applying equation \eqref{eq_mtl} will give the same estimator as single-task learning.

### 2020-06-03 writeup/setup.tex
wip

@@
 
-We focus on the following problem that specializes the commonly used hard parameter sharing model (e.g. \cite{R17,MTDNN19}) to the linear regression setting \cite{WZR20}.
+We focus on the commonly used hard parameter sharing model for multi-task learning \cite{R17,MTDNN19}.
+When specialized to the linear regression setting, the model consists of a linear layer $B\in\real^{p\times r}$ that is shared by all tasks and $t$ output layers $W_1, \dots, W_t$ that are in $\real^r$.
 \begin{align}
@@
 where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
-The linear layer $B$ provides a shared subspace for all tasks whereas each output layer $W_k$ fits the $k$-th task given the linear layer.
+
 Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.

### 2020-06-03 writeup/setup.tex
wip

@@
 \textbf{Problem setup.}
-Suppose we have $t$ training datasets denoted by $(X_1, Y_1), \dots, (X_t, Y_t)$.
+Suppose we have $t$ training datasets, where $t$ is a fixed value that does not grow with the feature dimension $p$.
 In the high-dimensional linear regression setting (e.g.
-\cite{HMRT19,BLLT20}), the features of the $k$-th task $X_k\in\real^{n_i\times p}$ consists of $n_k$ feature vectors given by $x_i = \Sigma_k^{1/2}z_i$, for $1\le i \le n_k$.
-Each $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+\cite{HMRT19,BLLT20}), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consists of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
+And each feature $x_i = \Sigma^{1/2}z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
 The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
@@
 When specialized to the linear regression setting, the model consists of a linear layer $B\in\real^{p\times r}$ that is shared by all tasks and $t$ output layers $W_1, \dots, W_t$ that are in $\real^r$.
+The width of $B$, denoted by $r$, plays an important regularization effect.
+As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
+Hence, we assume that $r < t$ in our study.
+Concretely, considering the following objective
 \begin{align}
 	\label{eq_mtl}
-	f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2,
+	f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2.
 \end{align}
-where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
-
-Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
-
+%where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
+%Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
+In general, the above objective $f(\cdot)$ is non-convex in $B$ and the $W_k$'s.
+Therefore, we consider the following
+We define $\hat{\beta}_t^{\MTL}$ by two steps:
 Then applying equation \eqref{eq_mtl} will give the same estimator as single-task learning.
-We define $\hat{\beta}_t^{\MTL}$ by two steps:
 (i) minimizing $f(\cdot)$ over $B$;

### 2020-06-04 writeup/setup.tex
wip

@@
 \textbf{Problem setup.}
-Suppose we have $t$ training datasets, where $t$ is a fixed value that does not grow with the feature dimension $p$.
+Suppose we have $t$ datasets, where $t$ is a fixed value that does not grow with the feature dimension $p$.
 In the high-dimensional linear regression setting (e.g.
@@
 And each feature $x_i = \Sigma^{1/2}z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+The sample size $n_k = \rho_k\times p$ for a fixed value $\rho_k$.
 The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
@@
 
-We focus on the commonly used hard parameter sharing model for multi-task learning \cite{R17,MTDNN19}.
+We focus on the commonly used hard parameter sharing model for multi-task learning \cite{R17}.
 When specialized to the linear regression setting, the model consists of a linear layer $B\in\real^{p\times r}$ that is shared by all tasks and $t$ output layers $W_1, \dots, W_t$ that are in $\real^r$.
@@
 Hence, we assume that $r < t$ in our study.
-Concretely, considering the following objective
-\begin{align}
-	\label{eq_mtl}
-	f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2.
-\end{align}
+Concretely, considering the following procedure that resembles how hard parameter sharing models are trained in practice (e.g. \cite{MTDNN19}).
+\squishlist
+	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
+	The size of each set is described below.
+	\item Learning the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a closed form equation for $\hat{B}$ that depends on $W_1,\dots, W_k$.
+		\vspace{-0.075in}
+		{\small\begin{align}\label{eq_mtl}
+			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{tr} B W_k - Y_k^{tr}}^2.
+		\end{align}}
+		\vspace{-0.075in}
+	\item Tuning the output layers $W_i$: set $B = \hat{B}$ and minimize the validation loss over $W_1,\dots, W_k$.
+		\vspace{-0.075in}
+		{\small\begin{align}\label{eq_mtl_eval}
+			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{val} \hat{B} W_k - Y_k^{val}}^2.
+		\end{align}}
+		\vspace{-0.075in}
+\squishend
+\vspace{-0.1in}
 %where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
 %Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
-In general, the above objective $f(\cdot)$ is non-convex in $B$ and the $W_k$'s.
-Therefore, we consider the following
-We define $\hat{\beta}_t^{\MTL}$ by two steps:
-Then applying equation \eqref{eq_mtl} will give the same estimator as single-task learning.
-(i) minimizing $f(\cdot)$ over $B$;
-(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set, e.g. $\OO(p^{0.99})$ suffices.
-For more details, we refer the reader to Appendix \ref{app_proof_sec3}. The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$. 
-For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample prediction loss as
-	\begin{align*}
-		\te_t(\hat{\beta}) = \exarg{x}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
-		= \bignorm{\ex{\hat{\beta}} - \beta_t}^2 + \ex{\bignorm{\hat{\beta} - \ex{\hat{\beta}}}^2},
-	\end{align*}
+We make several remarks.
+In general, the objective $f(\cdot)$ is non-convex in $B$ and the $W_k$'s.
+Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
+For our purpose, a validation set of size $\rho_i \cdot p^{0.99}$ suffices.
+The size of the training set is then $\rho_i (p - p^{0.99})$.
+%For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
+
+%The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
+%For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample prediction loss as
+%	\begin{align*}
+%		\te_t(\hat{\beta}) = \exarg{x}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
+%		= \bignorm{\ex{\hat{\beta}} - \beta_t}^2 + \ex{\bignorm{\hat{\beta} -
+%	\ex{\hat{\beta}}}^2},
+%	\end{align*}
 %= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t) \\
-which can be further decomposed as the bias plus the variance of $\hat{\beta}$.
+%which can be further decomposed as the bias plus the variance of $\hat{\beta}$.
 %In order to relate the btradeoff to properties of the data, we need tight concentration bounds for the bias and variance.
-We consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$  multiple of $p$ for every $1\le i\le t$, and $p$ is sufficiently large.
-We focus on a setting where $\rho_t$ is small compared to $\set{\rho_i}_{i=1}^{t-1}$.
-This setting captures the need to add more labeled data to reduce the prediction loss of the target task.
-A well-known result for this setting states that $\te_t(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \tr[(X_t^{\top}X_t)^{-1}\Sigma_t]$ is concentrated around $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
+%We consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$  multiple of $p$ for every $1\le i\le t$, and $p$ is sufficiently large.
+%We focus on a setting where $\rho_t$ is small compared to $\set{\rho_i}_{i=1}^{t-1}$.
+%This setting captures the need to add more labeled data to reduce the prediction loss of the target task.
+%A well-known result for this setting states that $\te_t(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \tr[(X_t^{\top}X_t)^{-1}\Sigma_t]$ is concentrated around $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
 Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
-However, this result only applies to a single task.
-Therefore, our goal is to extend this result to multiple tasks.
+%However, this result only applies to a single task.
+%Therefore, our goal is to extend this result to multiple tasks.
 
-\textbf{Notations.}
-When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ and write $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
-We refer to the first task as the source task when there are only two tasks.
+%\textbf{Notations.}
+%When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ and write $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
+%We refer to the first task as the source task when there are only two tasks.
 %We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
-We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$ is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
-For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+%We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$ is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+%For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
 

### 2020-06-04 writeup/setup.tex
sec 2

@@
 Hence, we assume that $r < t$ in our study.
-Concretely, considering the following procedure that resembles how hard parameter sharing models are trained in practice (e.g. \cite{MTDNN19}).
+For example, when there are only two tasks, $r = 1$ and $B$ reduces a vector whereas $W_1, W_2$ become scalars.
+We study the following procedure inspired by how hard parameter sharing models are trained in practice (e.g. \cite{MTDNN19}).
 \squishlist
@@
 Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
-For our purpose, a validation set of size $\rho_i \cdot p^{0.99}$ suffices.
+For our purpose, a validation set of size $\rho_i \cdot p^{0.99}$ that is much larger than the number of output layer parameters $kt$ suffices.
 The size of the training set is then $\rho_i (p - p^{0.99})$.
+The advantage of tuning the output layers on the validation set is to reduce the effect of noise from $\hat{B}$.
 %For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
@@
 %For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample prediction loss as
-%	\begin{align*}
-%		\te_t(\hat{\beta}) = \exarg{x}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
-%		= \bignorm{\ex{\hat{\beta}} - \beta_t}^2 + \ex{\bignorm{\hat{\beta} -
-%	\ex{\hat{\beta}}}^2},
-%	\end{align*}
-%= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t) \\
+
 %which can be further decomposed as the bias plus the variance of $\hat{\beta}$.
@@
 %We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
-%We say there is negative transfer if the prediction loss of $\hat{\beta}_t^{\MTL}$ is larger than that of $\hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+
 %For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
@@
 \textbf{Problem statement.}
-To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.
+We focus on predicting a particular task, say the $t$-th task without loss of generality.
+Let $\hat{\beta}_t^{\MTL}$ denote the multi-task estimator obtained from the procedure above.
+Our goal is to compare the prediction loss of $\hat{\beta}_t^{\MTL}$, defined by
+{\small\begin{align*}
+		\te(\hat{\beta}_t^{\MTL}) = \exargnob{\set{\varepsilon_i}_{i=1}^t}\exarg{x = \Sigma_t^{1/2} z}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
+		= \exargnob{\set{\varepsilon_i}_i^t}\bignorm{\Sigma_2^{1/2} (\hat{\beta}_t^{\MTL} - \beta_t)}^2,
+	\end{align*}}%
+%= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)
+to the prediction loss $L(\hat{\beta}_t^{\STL})$ of the single-task estimator $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$.
+We say there is negative transfer if  $L(\hat{\beta}_t^{\MTL}) > \hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+
+As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL})$ into a bias term and a variance term (that scales with noise variance $\sigma_2$) as follows (derived in Appendix \ref{app_proof_sec3}).
 %Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
-We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
-\begin{align}
+%We can  the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
+{\small\begin{align}
 	\te(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
 	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
-\end{align}
-Here $\hat{v}\in\real$ denotes a fixed value that depends on the output layer weights $W_1, W_2$.
+\end{align}}%
+Here $\hat{v} = W_1 / W_2$ where $W_1, W_2$ is the solutions from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
 The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
-These are derived in Appendix \ref{app_proof_sec3}.
 
-The term on the right-hand side of \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$, which captures how similar $\beta_1$ and $\beta_2$ are.
-Hence, the bias of $\hat{\beta}_t^{\MTL}$ introduces a negative effect from adding the source labels.
+Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$.
+Hence, the bias of $\hat{\beta}_t^{\MTL}$ introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
 Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, which is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
+Intuitively, the more \textit{samples} we add, the smaller the variance is.
 %This part introduces a positive variance reduction effect from adding the source labels.

### 2020-06-04 writeup/setup.tex
sec 3

@@
 And each feature $x_i = \Sigma^{1/2}z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-The sample size $n_k = \rho_k\times p$ for a fixed value $\rho_k$.
+The sample size $n_k $ equals $\rho_k\cdot p$ for a fixed value $\rho_k$.
 The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
@@
 %This setting captures the need to add more labeled data to reduce the prediction loss of the target task.
-%A well-known result for this setting states that $\te_t(\hat{\beta}_t^{\STL}) = \sigma^2 \cdot \tr[(X_t^{\top}X_t)^{-1}\Sigma_t]$ is concentrated around $\frac {\sigma^2} {\rho_t - 1}$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the data size and noise level of the target task.
+
 %However, this result only applies to a single task.
@@
 %We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
-
-%For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
 
@@
 to the prediction loss $L(\hat{\beta}_t^{\STL})$ of the single-task estimator $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$.
-We say there is negative transfer if  $L(\hat{\beta}_t^{\MTL}) > \hat{\beta}_t^{\STL}$, or positive transfer otherwise.
+We say there is negative transfer if  $L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL})$, or positive transfer otherwise.
 
-As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL})$ into a bias term and a variance term (that scales with noise variance $\sigma_2$) as follows (derived in Appendix \ref{app_proof_sec3}).
+As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\MTL})$ into a bias term and a variance term (that scales with noise variance $\sigma_2$) as follows (derived in Appendix \ref{app_proof_sec3}).
 %Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
@@
 {\small\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
-	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
+	\te(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
+	+&~ \sigma^2 \bigbrace{\bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} - \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}}. \label{eq_te_var}
 \end{align}}%
-Here $\hat{v} = W_1 / W_2$ where $W_1, W_2$ is the solutions from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
+In the above, $\hat{v} = W_1 / W_2$ where $W_1, W_2$ are obtained from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
 The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
@@
 Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$.
-Hence, the bias of $\hat{\beta}_t^{\MTL}$ introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
-Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, which is always smaller than the variance of $\hat{\beta}_t^{\STL}$.
-Intuitively, the more \textit{samples} we add, the smaller the variance is.
+Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
+Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
+Intuitively, the more \textit{samples} we have, the smaller the variance is.
+Meanwhile, \textit{covariate shift} also affects how small the variance can be.
 %This part introduces a positive variance reduction effect from adding the source labels.
-Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
+%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
 %(i) the negative effect from model shift bias.

### 2020-06-04 writeup/transfer.tex
sec 3

@@
 
-We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
-We show how negative transfer occurs by varying task similarity or sample size.
-Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
+%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
+We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
+We show theoretical implications for understanding the performance of multi-task learning.
+(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
+(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
+(c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
+%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
+%We show how negative transfer occurs by varying task similarity or sample size.
+%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
 
@@
 
-\begin{lemma}[Informal]\label{lem_cov_shift_informal}
+A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
+Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
+Our main technical contribution is to extend this result to two tasks.
+We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
+\begin{lemma}\label{lem_cov_shift_informal}
 	In the setting of two tasks,
+	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
+	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
 	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
 	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-	the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ is equal to  the following (times noise variance)
+	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals the following
 	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
@@
 		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-		\frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
+		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
 	\end{align*}}%
-where $a_1, a_2$ are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-A similar result on the bias of $\hat{\beta}_t^{\MTL}$ holds, and it also scales with task similarity in addition to sample size and covariate shift.
+	where $a_1, a_2$ are solutions of the following equations:
+	{\small\begin{align*}
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}\lambda_i^2 a_1}{\hat{v}\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+	\end{align*}}
+%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
 \end{lemma}
-
-We provide a sharp analysis of the bias-variance tradeoff for two tasks with general covariance matrices.
-We state our result as follows.
+Lemma \ref{lem_cov_shift_informal} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on the sample sizes and the covariate shift matrix.
+As a remark, the concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
+For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task similarity in addition to sample size and covariate shift holds (cf.
+Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
+Combining the two lemmas, we provide a sharp analysis of the bias-variance tradeoff of the multi-task estimator.
+For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
 %The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
@@
 \begin{theorem}\label{thm_main_informal}
-	For the setting of two tasks, let $M=\Sigma_1^{1/2}\Sigma_2^{-1/2}$, $\delta > 0$ be a desired error margin, $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and $\rho_2 > 1$ be a fixed value.
+	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(\Sigma_1^{1/2}\Sigma_2^{-1/2})^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and .
  	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
@@
 
-Corollary \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target sample size is small.
+Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target sample size is small.
 For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
@@
 %The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of the threshold can be complicated (as are the previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-This will be the focus of Section \ref{sec_insight}.
+While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
 
-\textbf{Remark.} Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-The concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
-
-Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
-For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
+%\textbf{Proof overview.}\todo{}
+%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
+%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
+%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
 This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
-Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
+%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
+%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
 %During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-The details are presented in Appendix \ref{app_proof_main}.
+The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
 
@@
 	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma_i^2$, for $i=1,2$.
-	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
+%	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
 
@@
 We introduce the following notations.
-\begin{align*}
+{\small\begin{align*}
 	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
-\end{align*}
+\end{align*}}
 
@@
 	\squishlist
-		\item If $\Psi(\beta_1, \beta_2) < \gamma_{+}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) > \gamma_{-}^{-1}  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) < \nu \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) > \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
-	Here $\gamma_{-} = (1-\oo(1))\cdot(1 - \rho_1^{-1/2})^4$ and $\gamma_{+} = (1+\oo(1))\cdot(1 + \rho_1^{-1/2})^4$.
-	Concretely, if $\rho_1 > 40$, then $\gamma_{+} \in (1,2)$ and $\gamma_{-} \in (1/2, 1)$.
+	Here $\nu = (1-\oo(1))\min(\cdot(1 - \rho_1^{-1/2})^4, (1 + \rho_1^{-1/2})^{-4})$.
+	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
 \end{proposition}
 
-Proposition \ref{prop_dist_transition} simplifies Corollary \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
+Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
 Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
 Prosposition \ref{prop_dist_transition} explains the transition observed in Figure \ref{fig_model_shift}.
-Note that there are several unexplained observations near the transition threshold $0$, which are caused by the concentration errors $\gamma_+$ and $\gamma_-$.
+Note that there are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
 %We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
@@
 
-\begin{proposition}[Source/target sample size]\label{prop_data_size}
+\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
 	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
@@
 	\squishlist
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\gamma_+} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \gamma_+^{-1}}$, then w.h.p.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
 $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1}{\gamma_-} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \gamma_{-}^{-1}}$, then w.h.p.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \nu^{-1}}$, then w.h.p.
 $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
@@
 From Figure \ref{fig_size}, we see that our result is able to explain the transition from positive to negative transfer.
-There are several unexplained observations near $y = 0$ caused by the errors $\gamma_-, \gamma_+$.
+There are several unexplained observations near $y = 0$ caused by the errors $\nu$.
 The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
@@
 For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using $x \cdot n_i$ datapoints from every task. The data efficiency ratio is defined as
-\[ \argmin_{x\in(0, 1)} ~~
+{\small\[ \argmin_{x\in(0, 1)} ~~
 		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
-		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
+		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]}
 For example, the data efficiency ratio is $1$ if there is negative transfer.
@@
 roughly 
-\[ \frac{1}{\rho_1 + \rho_2} {+ \frac{2}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
+{\small\[ \frac{1}{\rho_1 + \rho_2} {+ \frac{2}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]}
 Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$ (up to a constant multiple), the transfer is positive.
@@
 %In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-The precise statement can be found in Proposition \ref{prop_data_efficiency} in Appendix \ref{app_proof_32}.
+The result can be found in Proposition \ref{prop_data_efficiency} in Appendix \ref{app_proof_32}.
 
@@
 	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as $n_1/n_2$ increases, the performance gap between case (i) $M = \id$ and case (ii) with $\lambda = 2$ or $4$ increases for MTL.
+	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
 \end{example}
@@
 Consider the following bounded set
-\begin{align*}
+{\small\begin{align*}
 		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_p\le \lambda_1 \le \mu_{\max}\right.},
-\end{align*}
+\end{align*}}
 %	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
@@
 	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
-	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
+	We have that
+	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
 \end{proposition}
-This proposition shows that when $n_1 \gg n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized when there is no covariate shift between source and target tasks.
+This proposition shows that when the source sample size is much larger than the target sample size, $\te(\hat{\beta}^{\MTL})$ is minimized when there is no covariate shift between source and target tasks.
 The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.

### 2020-06-04 writeup/intro.tex
wip

@@
 	We observe that MTL performance
-	(a) undergoes transition from positive to negative transfer as \textit{task model distance} increases (Prop.\;\ref{prop_dist_transition});
-	(b) undergoes transition from positive to negative transfer as source/target \text{sample size} increases (Prop.\;\ref{prop_data_size});
-	(c) gets worse as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample size} increases (Prop.\;\ref{prop_covariate}).
+	(a) transitions from positive to negative transfer as \textit{task model distance} increases (Prop.\;\ref{prop_dist_transition});
+	(b) transitions from positive to negative transfer as source/target \text{sample size} increases (Prop.\;\ref{prop_data_size});
+	(c) worsens as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample size} increases (Prop.\;\ref{prop_covariate}).
 	The $y$-axis measures the loss of STL minus MTL.}
 	\label{fig_model_shift_phasetrans}
-	\vspace{-0.1in}
+	\vspace{-0.2in}
 \end{figure}
@@
 %Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
+%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
+%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
 

### 2020-06-04 writeup/transfer.tex
sec 3

@@
 (c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
+Finally, we extend our result from two tasks to many tasks with the same features.
 %We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
@@
 We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-\begin{lemma}\label{lem_cov_shift_informal}
+\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
 	In the setting of two tasks,
@@
 %, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-\begin{theorem}\label{thm_main_informal}
+\begin{theorem}[Two tasks]\label{thm_main_informal}
 	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(\Sigma_1^{1/2}\Sigma_2^{-1/2})^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and .
@@
 We validate our insight on this procedure in the experiments.
+
+\subsection{Extensions}
+
+Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+\begin{theorem}[Many tasks]\label{thm_many_tasks}
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
+	%that satisfy Assumption \ref{assm_secA2} in the appendix.
+	For the setting of $t$ tasks where $X_i = X$, for all $1\le i\le t$.
+	Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$ denote the linear model parameters.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$.
+	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
+	Let $v_i$ denote the $i$-th row vector of $U_r$.
+	We have the following
+	\squishlist
+		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r v_t - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right)$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$
+		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r v_t - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right)$, then w.h.p.
+$\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\squishend
+\end{theorem}
+Theorem \ref{thm_many_tasks} shows that when all tasks share the same features but have different labels, we can derive a sharp transition from positive to negative transfer.
+Specially, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of variance reduced using the multi-task estimator.
+On the other hand, $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
+The proof of \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.

### 2020-06-04 writeup/transfer.tex
sec 3

@@
 	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals the following
+	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
 	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
@@
 	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
-	Recall that each task has sample size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
-	And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
+	Each task has sample size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
+	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
 	We assume that for the target task, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
@@
 %{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
-Our result below will provide an explanation to this phenomenon.
+%Our result below will provide an explanation to this phenomenon.
 %Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
@@
 
-\begin{example}\label{ex_complement}
-	We measure covariate shift by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
+\textit{Example.}
+	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
 	Assume that $\Psi(\beta_1, \beta_2) = 0$ for simplicity.
@@
 	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-\end{example}
 
 %By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-To compare different choices of $M$ regarding the performance of $\hat{\beta}_t^{\MTL}$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in decreasing order.
+We compare different choices of $M$ that belong to the following bounded set.
+Let $\lambda_i$ be the $i$-th singular value of $M$.
 Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-Consider the following bounded set
+
 {\small\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_p\le \lambda_1 \le \mu_{\max}\right.},
+		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
 \end{align*}}
@@
 	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
+	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
 	We have that
-	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
+	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
 \end{proposition}
-This proposition shows that when the source sample size is much larger than the target sample size, $\te(\hat{\beta}^{\MTL})$ is minimized when there is no covariate shift between source and target tasks.
+This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
 The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
@@
 	Let $v_i$ denote the $i$-th row vector of $U_r$.
-	We have the following
+	There exists a value $\delta = \oo \left( \|B^\star\|^2 + \sigma^2\right)$ such that
 	\squishlist
-		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} > \norm{\Sigma (B^{\star} U_r v_t - \beta_t)}^2 +  \oo \left( \|B^\star\|^2 + \sigma^2\right)$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$
-		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} < \norm{\Sigma(B^{\star} U_r v_t - \beta_t)}^2 -  \oo \left( \|B^\star\|^2 + \sigma^2\right)$, then w.h.p.
-$\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
 \end{theorem}
-Theorem \ref{thm_many_tasks} shows that when all tasks share the same features but have different labels, we can derive a sharp transition from positive to negative transfer.
-Specially, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of variance reduced using the multi-task estimator.
-On the other hand, $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
+Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff beyond two tasks.
+Specially, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of reduced variance and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
 The proof of \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.

### 2020-06-04 writeup/intro.tex
abstract

@@
 	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
-	In this work, we study this question formally by considering three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
+	In this work, we study this question by considering three components including \textit{task model distance}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
 % the performance of predicting a particular task given multiple tasks.
 %a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
-	First, we show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of multi-task estimators.
-	We analyze the bias-variance tradeoff by developing technical tools using random matrix theory.
+	We show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of the multi-task estimator.
+	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
 	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
@@
 %	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
-	Second, we apply our tools to show that the performance of multi-task learning is negatively affected as a result of: (a) decreased task similarity;
+	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) increased task model distance;
 	(b) increased source sample size; (c) covariate shift under increased source sample size.
-	Finally, we validate the three components of our theory on image and text classification tasks.
-	Inspired by our theory, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
+	Finally, we validate the above results on text classification tasks.
+	Inspired by our theory, we show that single-task performance can help understand multi-task performance.
+We propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
 %	We validate our theory and our proposed method .

### 2020-06-04 writeup/setup.tex
abstract

@@
 We begin by defining our problem setup including the multi-task estimator we study.
-Then, we describe the bias-variance tradeoff of the multi-task estimator, and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
+Then, we describe the bias-variance tradeoff of the multi-task estimator, and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size} and \textit{covariate shift}.
 %Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

### 2020-06-04 writeup/transfer.tex
abstract

@@
 We show theoretical implications for understanding the performance of multi-task learning.
-(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
+(a) \textit{Task model distance}: we explain the phenomenon of negative transfer precisely as task models become different.
 (b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
@@
 As a remark, the concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
-For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task similarity in addition to sample size and covariate shift holds (cf.
+For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task model distance in addition to sample size and covariate shift holds (cf.
 Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
@@
 
-\subsection{Task Similarity}\label{sec_similarity}
+\subsection{Task Model Distance}\label{sec_similarity}
 

### 2020-06-04 writeup/intro.tex
intro

@@
 %When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
-	Multi-task learning is a powerful approach to solve complex tasks in many applications such as image and text classification.
+	Multi-task learning is a powerful approach in many applications such as image and text classification.
 	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
-	In this work, we study this question by considering three components including \textit{task model distance}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
+	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
+	In this work, we consider three components including \textit{task model distance}, \textit{sample size} and \textit{covariate shift} to determine positive vs. negative transfer.
+	We formally quantify each component in the setting of high-dimensional linear regression,
 % the performance of predicting a particular task given multiple tasks.
 %a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
-	We show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of the multi-task estimator.
-	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
+	and show that the bias-variance tradeoff of the multi-task estimator determines the effect of transfer..
+%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
 	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
@@
 	(b) increased source sample size; (c) covariate shift under increased source sample size.
-	Finally, we validate the above results on text classification tasks.
-	Inspired by our theory, we show that single-task performance can help understand multi-task performance.
-We propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
+	We validate the above results on text classification tasks.
+	Inspired by our theory, we show that single-task performance can help understand multi-task performance, and propose an incremental training scheduler for improving the efficiency of multi-task training.% for predicting a particular task.
 %	We validate our theory and our proposed method .
@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning represents a powerful paradigm to solve complex tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
+Multi-task learning is a powerful paradigm for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
@@
 %By combining multiple information sources, it is possible to share all the information in the same model.
-In many settings, multiple information sources are available to help to solve a particular task.
+In many settings, multiple data sources are available for predicting a particular target task.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
-The performance of multi-task learning depends on the relationship between the information sources and the task \cite{C97}.
-When the information sources are heterogeneous, negative transfer--where multi-task learning (MTL)  performs worse than single-task learning (STL)--has often been observed \cite{PY09,AP16,BS17}.
-While many empirical approaches are proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
+The performance of multi-task learning depends on the relationship between the data sources and the target \cite{C97}.
+When the data sources are relatively different from each other, negative transfer has often been observed \cite{PY09,AP16,BS17}.
+While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-In this work, we show that negative transfer is determined by the bias-variance tradeoff of multi-task learning estimators for the high-dimensional linear regression setting.
-% for learning from multiple linear regression tasks.
-Moreover, we develop new tools to analyze the tradeoff and explain negative transfer precisely.
+In this work, we provide a rigorous study to understand when positive or transfer occurs in the setting of high-dimensional linear regression.
+We show that the bias-variance tradeoff of multi-task learning estimators determines the transfer effect, and we develop new concentration bounds to analyze the tradeoff.
 %Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
@@
 
-Understanding negative transfer requires developing tight generalization bounds for both multi-task learning and single-task learning.
-In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented so that the error reduces as the data sizes of all tasks increase.
-For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11,MPR16}.
-On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
+Understanding positive vs. negative transfer requires developing generalization bounds that scale tightly with properties of the data such as sample size.
+This presents a technical challenge in the multi-task setting due to the presence of different task features, even for two tasks.
+For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
+Without a tight lower bound for the multi-task setting, it is unclear how to compare its performance to single-task learning.
+Furthermore, developing a better understanding of how multi-task learning performs in terms of properties of the data such as sample size is of practical importance, since a major application of multi-task learning is for settings where a particular task has limited amount of labeled data \cite{RH19}.
+%For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
+%On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
 %The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
-When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
+%When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
+
+%\textbf{Setup and Main Results.}
+In this work, we apply recent development in the random matrix theory literature to show how to determine positive vs.
+negative transfer in the setting of high-dimensional linear regression \cite{HMRT19,BLLT20}.
+This setting allows us to rigorously quantify three components, defined as follows.
+\squishlist
+	\item \textbf{Task model distance:} Assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $1\le i\le t$.
+	Hence, the distance between two tasks can be measured by the distance of their model parameters.
+	\item \textbf{Sample size:} Let $n_i = \rho_i \cdot p$ denote the sample size of task $i$, for a fixed value $\rho_i > 1$ that does not grow with $p$, for any $1\le i\le t$.
+	Hence, for two tasks $i$ and $j$, their data ratio is measured by $n_i / n_j = \rho_i / \rho_j$.
+	Importantly, we assume that for a particular (say $t$-th) task, $\rho_t$ is a small constant (say 2), to capture the need for adding more labeled data.
+	\item \textbf{Covariate shift:} We assume that for every task $1\le i\le t$, its features are random vectors with covariance matrix $\Sigma_i\in\real^{p\times p}$.
+	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
+	Given two tasks $i$ and $j$, covariate shift by $\Sigma_i^{1/2}\Sigma_j^{-1/2}$.
+\squishend
 To motivate our study, Figure \ref{fig_model_shift_phasetrans} shows three examples for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
@@
 The observations highlight the need to develop generalization bounds that scale tightly with properties of multiple tasks data.
-
-%\textbf{Setup and Main Results.}
-Our main contribution is to develop technical tools to explain the above phenomena.
-We focus on predicting a particular task given multiple high-dimensional linear regression tasks \cite{HMRT19,BLLT20}.
-\squishlist
-	\item \textbf{Task similarity:} We assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $1\le i\le t$.
-	Hence, task similarity can be measured by the distance between the model parameters.
-	\item \textbf{Sample size:} Let $n_i = \rho_i \cdot p$ denote the sample size of task $i$, for a fixed value $\rho_i > 1$ that does not grow with $p$, for any $1\le i\le t$.
-	Hence, for a source task $s$ and a target task $t$, their data ratio is measured by $n_s / n_t = \rho_s / \rho_t$.
-	Importantly, we assume that for the $t$-th (target) task, $\rho_t$ is a small constant (say 2), to capture the need for adding more labeled data.
-	\item \textbf{Covariate shift:} We assume that for every task $1\le i\le t$, its features are random vectors with covariance matrix $\Sigma_i\in\real^{p\times p}$.
-	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
-	Given two tasks $i$ and $j$, we measure covariate shift by $\Sigma_i^{1/2}\Sigma_j^{-1/2}$.
-\squishend
 % that only contains limited amount of labeled data.
@@
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_setup}.
+Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
 We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.

### 2020-06-04 writeup/intro.tex
intro

@@
+\vspace{-0.2in}
 \begin{abstract}
@@
 
+\vspace{-0.1in}
 \section{Introduction}
@@
 This setting allows us to rigorously quantify three components, defined as follows.
+For simplicity, we consider two tasks with first being the source and the second being the target, but our formulation applies more generally.
 \squishlist
-	\item \textbf{Task model distance:} Assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $1\le i\le t$.
-	Hence, the distance between two tasks can be measured by the distance of their model parameters.
+	\item \textbf{Task model distance:} Assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $i=1, 2$.
+	Hence, $\norm{\beta_1 - \beta_2}$ measure the distance of the two tasks.
 	\item \textbf{Sample size:} Let $n_i = \rho_i \cdot p$ denote the sample size of task $i$, for a fixed value $\rho_i > 1$ that does not grow with $p$, for any $1\le i\le t$.
-	Hence, for two tasks $i$ and $j$, their data ratio is measured by $n_i / n_j = \rho_i / \rho_j$.
-	Importantly, we assume that for a particular (say $t$-th) task, $\rho_t$ is a small constant (say 2), to capture the need for adding more labeled data.
-	\item \textbf{Covariate shift:} We assume that for every task $1\le i\le t$, its features are random vectors with covariance matrix $\Sigma_i\in\real^{p\times p}$.
+	Hence, the source/target sample ratio is measured by $n_1 / n_2 = \rho_1 / \rho_2$.
+	Importantly, we assume that $\rho_2$ is a small constant (say 2), to capture the need for adding more labeled data.
+	\item \textbf{Covariate shift:} We assume that for every task, its features are random vectors with covariance matrix $\Sigma_i\in\real^{p\times p}$.
 	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
-	Given two tasks $i$ and $j$, covariate shift by $\Sigma_i^{1/2}\Sigma_j^{-1/2}$.
+	We measure covariate shift by $\Sigma_i^{1/2}\Sigma_j^{-1/2}$.
 \squishend
@@
 	\label{fig_model_shift_phasetrans}
-	\vspace{-0.2in}
+	\vspace{-0.3in}
 \end{figure}

### 2020-06-04 writeup/transfer.tex
sec 3 fix

@@
 	For the source task, $\beta_1 $ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
-	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma_i^2$, for $i=1,2$.
+	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
 %	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
 
-In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$ (or $d$), there is a transition from positive transfer to negative transfer in MTL.
 %We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
@@
 \begin{proposition}[Task model distance]\label{prop_dist_transition}
-	In the isotropic model, suppose that $\rho_1 > 1$ and $\sigma_1 = \sigma_2 = \sigma$.
-	Then we have that
+	In the isotropic model, suppose that $\rho_1$ and $\rho_2 > 1$.
+	Then
 	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
@@
 Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
-Prosposition \ref{prop_dist_transition} explains the transition observed in Figure \ref{fig_model_shift}.
-Note that there are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
+We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+We can see that our result is able to predict positive or negative transfer  accuractly that matches the empirical curve.
+There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
 %We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
@@
 In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
-More generally, such results are still applicable when all task data are being added simultaneously.
-On the other hand, for many applications of multi-task learning, the data sources are usually heterogeneous.
-For such settings, we have observed that adding more labeled data from one task does not always help.
+%More generally, such results are still applicable when all task data are being added simultaneously.
+On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
+For such settings, we have also observed that adding more labeled data from one task does not always help.
 %On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
@@
 %We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-Our result below explains the phenomenon of Figure \ref{fig_size}.
 
@@
 Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the data ratio $n_1 / n_2$.
-From Figure \ref{fig_size}, we see that our result is able to explain the transition from positive to negative transfer.
+We apply the above result to the parameter setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+Our theory accuractly predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
 There are several unexplained observations near $y = 0$ caused by the errors $\nu$.
@@
 roughly
-{\small\[ \frac{1}{\rho_1 + \rho_2} {+ \frac{2}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]}
+{\small\[ \frac{1}{\rho_1 + \rho_2} {+ \frac{2}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]}%
 Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$ (up to a constant multiple), the transfer is positive.

### 2020-06-04 writeup/experiments.tex
sec 3
quick pass

@@
 
-\begin{table}
+\begin{table}[!b]
 \begin{minipage}[t]{.40\textwidth}
+	\vspace{-0.1in}
 	\centering
@@
 		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
+		Sentiment\\ analysis\end{center}\end{minipage}} \\
 		\cmidrule(lr){2-3}
@@
 	\label{tab:taskonomy}
-	\vspace{-0.2in}
 \end{minipage}%
@@
 \begin{minipage}[t]{.58\textwidth}
+	\vspace{-0.1in}
 	\centering
@@
 	\label{tab:mtl_better_than_stl}
-	\vspace{-0.2in}
 \end{minipage}
@@
 
-{\bf Datasets and models.} We describe the datasets and models we use in the experiments.
+We consider a text classification task and an image classification task as follows.
 
 {\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
-
 {For each task, the goal is to categorize sentiment opinions expressed in the text.
-We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
+We use an embedding layer with GloVe embeddings
+followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
 }
@@
 
+%\textbf{The training procedure and baseline.}
 For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.
-
-\textbf{Training procedures and baselines.} We use round-robin training schedule for the MTL model.
-We compare our incremental training scheduler of Algorithm \ref{alg_inc_train} to the round-robin training scheduler.
-We focus on the prediction accuracy of a particular target task.
+The baseline training schedule for MTL is the round-robin training schedule.
+%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
+We measure the test accuracy of predicting a target task.
 
@@
 
-\textbf{Improving multi-task training efficiency.}
-We compare Algorithm \ref{alg_inc_train} to performing multi-task learning for predicting a particular target dataset.
-Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.
+Our first result is to show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
+Our insight is that since adding more samples from the source task does not always improve performance, we can improve efficiency by adding the source samples \textit{incrementally} during training.
+Over six randomly selected task pairs from the sentiment analysis dataset, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.
 
-\textbf{Improving transfer learning training efficiency.}
-We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
+%\textbf{Improving transfer learning training efficiency.}
+%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
+%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
 
-\textbf{MTL improves data efficiency ratio.}
 We measure the data efficiency ratio on the sentiment analysis tasks.
@@
 	\end{subfigure}
-	\caption{Validating the three takeaways of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
-	(c) As source/target data ratio increases, the performance gain from the covariance alignment procedure \cite{WZR20} over MTL increases for LSTM and MLP.}
+	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
+	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer (red curve).
+	(c) As source/target sample ratio increases, the performance gain of aligning task covariances \cite{WZR20} compared to MTL increases for LSTM and MLP.}
 	\label{fig_ablation}
@@
 
-\textbf{Explaining .} In Figure \ref{fig_ablation}, we validate the three components of our theory on the sentiment analysis dataset.
+A common challenge in the study of multi-task learning is that the results can be hard to understand.
+It is difficult to predict when MTL performs well without running extensive trials.
+Our insight here is that we can use STL results to help understand MTL results.
+We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
+Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
+We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
+We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
+The results show that STL results are indicative of MTL results.
+
+Finally, we validate our theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.
+In Figure \ref{fig_ablation}, we show that MTL performance is affected by
+(a) decreased task similarity;
+(b) increased source/target sample ratio;
+(c) covariate shift under increased source sample size.
+For the last result, specifically we show that the alignment procedure proposed in \cite{WZR20} becomes more helpful when the sample ratio is large.
 The experimental procedure is left to Appendix \ref{app_it}.
-
-\textbf{Understanding MTL results via STL results.}
-We show that STL results can be used to help understand MTL results.
-We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
-Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
-We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among 150 task pairs.
-We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
-The results show that STL performances are indicative of MTL performances.

### 2020-06-04 writeup/intro.tex
intro
quick pass

@@
-\vspace{-0.2in}
+\vspace{-0.3in}
 \begin{abstract}
+\vspace{-0.1in}
 %When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
@@
 	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
-	In this work, we consider three components including \textit{task model distance}, \textit{sample size} and \textit{covariate shift} to determine positive vs. negative transfer.
+	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine positive vs. negative transfer.
 	We formally quantify each component in the setting of high-dimensional linear regression,
@@
 %	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
-	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) increased task model distance;
+	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) decreased task similarity;
 	(b) increased source sample size; (c) covariate shift under increased source sample size.

### 2020-06-04 writeup/related.tex
quick pass

@@
 
-\textbf{Multi-task learning theory.}
+\textit{Multi-task learning theory.}
 Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
@@
 % Adding a regularization over $B$, e.g. .
-\textbf{Multi-task learning methodology.}
+\textit{Multi-task learning methodology.}
 Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
@@
 
-\textbf{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
+\textit{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
 For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.

### 2020-06-04 writeup/transfer.tex
quick pass

@@
 We show theoretical implications for understanding the performance of multi-task learning.
-(a) \textit{Task model distance}: we explain the phenomenon of negative transfer precisely as task models become different.
+(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
 (b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
@@
 
-\subsection{Task Model Distance}\label{sec_similarity}
+\subsection{Task Similarity}\label{sec_similarity}
 
@@
 Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
+Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
 We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).

### 2020-06-04 writeup/experiments.tex
wip

@@
 We connect our theory to pratical problems of interest.
-First, we validate the single-task based metric on text and image classification tasks.
+(i) We validate the single-task based metric on text and image classification tasks.
 We show that for both datasets, single-task learning results can help predict positive or negative transfer in multi-task learning.
-Second, we show that our proposed incremental training schedule improves the training efficiency of multi-task learning for predicting a particular target task.
+(ii) We show that our proposed incremental training schedule improves the training efficiency of multi-task learning for predicting a particular target task.
 %Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-Finally, we validate the three components of our theory and measure the data efficiency of multi-task learning on text classification tasks.
+(iii) We validate our theoretical results in Section \ref{sec_insight} on text classification tasks.
 

### 2020-06-04 writeup/intro.tex
minor fix

@@
 	We observe that MTL performance
-	(a) transitions from positive to negative transfer as \textit{task model distance} increases (Prop.\;\ref{prop_dist_transition});
-	(b) transitions from positive to negative transfer as source/target \text{sample size} increases (Prop.\;\ref{prop_data_size});
-	(c) worsens as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample size} increases (Prop.\;\ref{prop_covariate}).
-	The $y$-axis measures the loss of STL minus MTL.}
+	(a) transitions from pos. to neg. transfer as \textit{task model distance} increases;
+	(b) transitions from pos. to neg. transfer as source/target \text{sample ratio} increases;
+	(c) worsens as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample ratio} increases -- tasks have the same model here.
+	The $y$-axis measures the loss of STL minus MTL.
+	}
 	\label{fig_model_shift_phasetrans}
@@
 In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
+Our theoretical results in Prop.\;\ref{prop_dist_transition} and Prop.\;\ref{prop_data_size} provide predictions that match the empirical result of (a) and (b).
+When $\beta_1 = \beta_2$, Lemma \ref{lem} Prop.\;\ref{prop_covariate}
 It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.

### 2020-06-04 writeup/transfer.tex
minor fix

@@
 \end{lemma}
-Lemma \ref{lem_cov_shift_informal} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on the sample sizes and the covariate shift matrix.
+Lemma \ref{lem_cov_shift_informal} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
 As a remark, the concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
@@
 	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
-	Each task has sample size $n_i = \rho_i \cdot p$, for $i = 1, 2$.
+	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 \rho_2 \cdot p$.
 	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	We assume that for the target task, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
+	Assume that for the target task, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
 	For the source task, $\beta_1 $ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
-	The labels are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
 %	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
@@
 %Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}. %, which is based on our main result described later in Theorem \ref{thm_model_shift}.
+The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
+A key part of the analysis shows that $\hat{v}\approx 1$ in the isotropic model,
+thus simplifyling the result of Theorem \ref{thm_main_informal}.
+%, which is based on our main result described later in Theorem \ref{thm_model_shift}.
 

### 2020-06-04 writeup/intro.tex
intro wip

@@
 Without a tight lower bound for the multi-task setting, it is unclear how to compare its performance to single-task learning.
-Furthermore, developing a better understanding of how multi-task learning performs in terms of properties of the data such as sample size is of practical importance, since a major application of multi-task learning is for settings where a particular task has limited amount of labeled data \cite{RH19}.
+Furthermore, developing a better understanding of how multi-task learning performs in terms of properties of the data is of practical importance, since a major application of multi-task learning is for settings where a particular task has limited amount of labeled data \cite{RH19}.
 %For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
@@
 %\textbf{Setup and Main Results.}
-In this work, we apply recent development in the random matrix theory literature to show how to determine positive vs.
+In this work, we apply recent development in the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to show how to determine positive vs.
 negative transfer in the setting of high-dimensional linear regression \cite{HMRT19,BLLT20}.
-This setting allows us to rigorously quantify three components, defined as follows.
-For simplicity, we consider two tasks with first being the source and the second being the target, but our formulation applies more generally.
+This setting allows us to measure the difference of task data by \textit{task similarity}, \textit{sample size} and \textit{covariate shift} precisely.
+We define each component for two tasks and our formulation applies more generally.
+We call the first task a source task and the second a target task.
 \squishlist

### 2020-06-04 writeup/intro.tex

@@
 \squishlist
-	\item \textbf{Task model distance:} Assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $i=1, 2$.
-	Hence, $\norm{\beta_1 - \beta_2}$ measure the distance of the two tasks.
-	\item \textbf{Sample size:} Let $n_i = \rho_i \cdot p$ denote the sample size of task $i$, for a fixed value $\rho_i > 1$ that does not grow with $p$, for any $1\le i\le t$.
+	\item \textbf{Task similarity:} Assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $i=1, 2$.
+	Hence, we measure the distance between the two tasks by $\norm{\beta_1 - \beta_2}$.
+	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample size of each task, where both $\rho_1, \rho_2 > 1$ are fixed values that do not grow with $p$.
 	Hence, the source/target sample ratio is measured by $n_1 / n_2 = \rho_1 / \rho_2$.
-	Importantly, we assume that $\rho_2$ is a small constant (say 2), to capture the need for adding more labeled data.
-	\item \textbf{Covariate shift:} We assume that for every task, its features are random vectors with covariance matrix $\Sigma_i\in\real^{p\times p}$.
+	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
+	\item \textbf{Covariate shift:} We assume that for every task, its features are random vectors with covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$.
 	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
-	We measure covariate shift by $\Sigma_i^{1/2}\Sigma_j^{-1/2}$.
+	Hence, we can measure covariate shift by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
 \squishend
-To motivate our study, Figure \ref{fig_model_shift_phasetrans} shows three examples for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
-We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-The observations highlight the need to develop generalization bounds that scale tightly with properties of multiple tasks data.
+
+%The observations highlight the need to develop generalization bounds that scale tightly with properties of multiple tasks data.
 % that only contains limited amount of labeled data.
@@
 Next, we use our newly developed tool to explain negative transfer in multi-task learning precisely.
+To motivate our study, Figure \ref{fig_model_shift_phasetrans} shows three examples for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
+We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
+%\textbf{Task similarity:}
+%\textbf{Data sizes:}
+%\textbf{Covariate shift:}
+Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
 In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.

### 2020-06-04 writeup/setup.tex

@@
 Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
-For our purpose, a validation set of size $\rho_i \cdot p^{0.99}$ that is much larger than the number of output layer parameters $kt$ suffices.
+For our purpose, a validation set of size $\rho_i \cdot p^{0.99}$ that is much larger than the number of output layer parameters $r\cdot t$ suffices.
 The size of the training set is then $\rho_i (p - p^{0.99})$.
@@
 
-As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\MTL})$ into a bias term and a variance term (that scales with noise variance $\sigma_2$) as follows (derived in Appendix \ref{app_proof_sec3}).
+As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL})$ into a bias term and a variance term as follows (derived in Appendix \ref{app_proof_sec3}).
 %Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
@@
 Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
-Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$, minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
+Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$ minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
 Intuitively, the more \textit{samples} we have, the smaller the variance is.

### 2020-06-04 writeup/intro.tex
intro wip

@@
 \begin{abstract}
-\vspace{-0.1in}
+\vspace{-0.05in}
 %When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
@@
 
-\vspace{-0.1in}
+\vspace{-0.15in}
 \section{Introduction}
@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning is a powerful paradigm for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
+Multi-task learning is a powerful approach for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
@@
 
-Understanding positive vs. negative transfer requires developing generalization bounds that scale tightly with properties of the data such as sample size.
+Understanding positive versus negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
 This presents a technical challenge in the multi-task setting due to the presence of different task features, even for two tasks.
 For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-Without a tight lower bound for the multi-task setting, it is unclear how to compare its performance to single-task learning.
-Furthermore, developing a better understanding of how multi-task learning performs in terms of properties of the data is of practical importance, since a major application of multi-task learning is for settings where a particular task has limited amount of labeled data \cite{RH19}.
+Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
+From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data is important because it is often applied to settings in which a particular task has limited amount of labeled data \cite{RH19}.
 %For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
@@
 %\textbf{Setup and Main Results.}
-In this work, we apply recent development in the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to show how to determine positive vs.
-negative transfer in the setting of high-dimensional linear regression \cite{HMRT19,BLLT20}.
-This setting allows us to measure the difference of task data by \textit{task similarity}, \textit{sample size} and \textit{covariate shift} precisely.
-We define each component for two tasks and our formulation applies more generally.
-We call the first task a source task and the second a target task.
+In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
+This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
+To be precise, we define each component for two tasks below and our definition applies more generally.
+We refer to the first task as the source and the second as the target.
 \squishlist
-	\item \textbf{Task similarity:} Assume that each task follows a linear model with parameters $\beta_i\in\real^p$, for $i=1, 2$.
-	Hence, we measure the distance between the two tasks by $\norm{\beta_1 - \beta_2}$.
-	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample size of each task, where both $\rho_1, \rho_2 > 1$ are fixed values that do not grow with $p$.
-	Hence, the source/target sample ratio is measured by $n_1 / n_2 = \rho_1 / \rho_2$.
-	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
-	\item \textbf{Covariate shift:} We assume that for every task, its features are random vectors with covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$.
+	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
+	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
+	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2$ are both fixed values that do not grow with $p$.
+	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
+%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
+	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
 	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
-	Hence, we can measure covariate shift by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
 \squishend
@@
 random noise with mean zero and variance $\sigma^2$.
-We focus on the hard parameter sharing architecture with a linear shared layer for all tasks and a separate prediction head for each task \cite{R17,WZR20,MTDNN19}.
+We consider a multi-task estimator obtained using a shared linear layer for all tasks and a separate output layer for each task \cite{WZR20}.
+This two layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
+%Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
 We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.

### 2020-06-04 writeup/intro.tex
abstract

@@
 	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
-	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine positive vs. negative transfer.
-	We formally quantify each component in the setting of high-dimensional linear regression,
+	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine transfer effect.
+	We study the high-dimensional linear regression setting that allows us to define each component precisely,
 % the performance of predicting a particular task given multiple tasks.
 %a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
-	and show that the bias-variance tradeoff of the multi-task estimator determines the effect of transfer..
+	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
 %	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
@@
 %	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
-	Then, we show that the performance of multi-task learning can be negatively affected as a result of: (a) decreased task similarity;
-	(b) increased source sample size; (c) covariate shift under increased source sample size.
-	We validate the above results on text classification tasks.
-	Inspired by our theory, we show that single-task performance can help understand multi-task performance, and propose an incremental training scheduler for improving the efficiency of multi-task training.% for predicting a particular task.
+	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size and covariate shift under increased source sample size.
+	We validate the three effects on text classification tasks.
+	Inspired by our theory, we show two practical connections of interest.
+	First, single-task performance can help understand multi-task performance.
+	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.% for predicting a particular task.
 %	We validate our theory and our proposed method .

### 2020-06-04 writeup/intro.tex
intro wip

@@
 	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
-	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2$ are both fixed values that do not grow with $p$.
+	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
 	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
@@
 This two layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
+We consider the bias and variance of the multi-task estimator, and connect them to the three components defined above.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
 %Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
-We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
-Interestingly, we observe that the variance of the multi-task estimator is always smaller than the variance of the single-task estimator, because of an increased sample size.
-The bias of the multi-task estimator results in a negative effect caused by the difference between $\beta_t$ and the rest of $\set{\beta_i}_{i=1}^{t-1}$.
+%We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
+
+Our main result is to develop tight concentration bounds for the bias and variance of the multi-task estimator for two tasks.
+Since the sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than the variance of the single-task estimator.
+In Lemma \ref{lem_cov_shift_informal}, we provide a sharp analysis of the reduced variance that scales only with sample size and covariate shift.
+Since task models are different, the bias of the multi-task estimator is \textit{always larger} than the bias of the single-task estimator (which is $0$).
 Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
-For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
+Using Lemma \ref{lem_cov_shift_informal}, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
+%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
 %\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.

### 2020-06-04 writeup/intro.tex

@@
 This two layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
-We consider the bias and variance of the multi-task estimator, and connect them to the three components defined above.
+We consider the bias and variance of the multi-task estimator for predicting a particular task, and compare its performance to single-task learning.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
@@
 
-Next, we use our newly developed tool to explain negative transfer in multi-task learning precisely.
-To motivate our study, Figure \ref{fig_model_shift_phasetrans} shows three examples for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
+Next, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
+We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
 We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
@@
 Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-In Section \ref{sec_insight}, we explain the three phenomena in Figure \ref{fig_model_shift_phasetrans} for a simplified isotropic setting of two tasks.
-Our theoretical results in Prop.\;\ref{prop_dist_transition} and Prop.\;\ref{prop_data_size} provide predictions that match the empirical result of (a) and (b).
-When $\beta_1 = \beta_2$, Lemma \ref{lem} Prop.\;\ref{prop_covariate}
-It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
+\squishlist
+	\item In Proposition \ref{prop_dist_transition}, Our theoretical results in  and  provide predictions that match the empirical result of (a) and (b).
+%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
 	The unexplained observations are caused by an error term that arises from the bias of $\hat{\beta}_t^{\MTL}$ -- we discuss these in Section \ref{sec_insight} more precisely.
-Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-When task models are the same and the covariate shift matrix belongs to a certain bounded set, we show that having no covariate shift yields the optimal MTL performance.
+	\item In Proposition \ref{prop_data_size},
+	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
+	\item In Proposition \ref{prop_covariate}, When task models are the same and the covariate shift matrix belongs to a certain bounded set, we show that having no covariate shift yields the optimal MTL performance.
+	When $\beta_1 = \beta_2$, Lemma \ref{lem}
+\squishend
 %In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.

### 2020-06-04 writeup/intro.tex
intro wip

@@
 
-Our main result is to develop tight concentration bounds for the bias and variance of the multi-task estimator for two tasks.
-Since the sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than the variance of the single-task estimator.
-In Lemma \ref{lem_cov_shift_informal}, we provide a sharp analysis of the reduced variance that scales only with sample size and covariate shift.
-Since task models are different, the bias of the multi-task estimator is \textit{always larger} than the bias of the single-task estimator (which is $0$).
-Hence, the bias-variance tradeoff determines whether we observe positive or negative transfer.
-Using Lemma \ref{lem_cov_shift_informal}, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
+Our main result is to develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
+Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
+Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator (which is $0$ since $n_1 > p$).
+Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
+In Lemma \ref{lem_cov_shift_informal}, we provide a sharp analysis of the variance that scales only with sample size and covariate shift and extend it to the bias.
+Combined together, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
 %For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
@@
 	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	We observe that MTL performance
-	(a) transitions from pos. to neg. transfer as \textit{task model distance} increases;
-	(b) transitions from pos. to neg. transfer as source/target \text{sample ratio} increases;
-	(c) worsens as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample ratio} increases -- tasks have the same model here.
-	The $y$-axis measures the loss of STL minus MTL.
-	}
+	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
+	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
+	The $y$-axis measures the loss of STL minus MTL.}
 	\label{fig_model_shift_phasetrans}

### 2020-06-05 writeup/intro.tex
intro

@@
 We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
-We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
+%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
 %\textbf{Task similarity:}
@@
 %\textbf{Covariate shift:}
-Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
+%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
 \squishlist
-	\item In Proposition \ref{prop_dist_transition}, Our theoretical results in  and  provide predictions that match the empirical result of (a) and (b).
+	\item In Proposition \ref{prop_dist_transition}, we provide a deterministic condition that depends on the sample sizes and model distance in the isotropic setting.
+	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
 %	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-	The unexplained observations are caused by an error term that arises from the bias of $\hat{\beta}_t^{\MTL}$ -- we discuss these in Section \ref{sec_insight} more precisely.
-	\item In Proposition \ref{prop_data_size},
+	The unexplained observations are caused by an error term that arises from the bias of the multi-task estimator.
+	We discuss these in Section \ref{sec_insight} more precisely.
+	\item In Proposition \ref{prop_data_size}, we provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance.
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item In Proposition \ref{prop_covariate}, When task models are the same and the covariate shift matrix belongs to a certain bounded set, we show that having no covariate shift yields the optimal MTL performance.
-	When $\beta_1 = \beta_2$, Lemma \ref{lem}
+	\item In Proposition \ref{prop_covariate}, we study a special case of having the same task models and show that MTL is best performing without covariate shift.
+	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
 \squishend
@@
 %We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-Finally, we analyze the benefit of MTL for reducing the amount of labeled data needed to achieve comparable performance to STL, which is a key empirical finding of Taskonomy.
+Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL, .
 %We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
@@
 
-\textit{Our last contribution} is to connect our theory to practical problems of interest.
-(i) We validate the three components of our theory in Section \ref{sec_insight} and measure the data efficiency of multi-task learning on the sentiment analysis dataset.
-(ii) We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
+Finally, we connect our theory to practical problems of interest.
+We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
 While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-(iii) We design an incremental training schedule to improve the efficiency of multi-task training for predicting a particular task.
+Inspired by our observation that adding more source task data does not always improve perfromance, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
 We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset, while keeping the accuracy the same.
+Last, we validate our three theoretical findings on sentiment analysis tasks.

### 2020-06-05 writeup/intro.tex

@@
 
-Our main result is to develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
+\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
 Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
@@
 Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-In Lemma \ref{lem_cov_shift_informal}, we provide a sharp analysis of the variance that scales only with sample size and covariate shift and extend it to the bias.
+We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Lemma \ref{lem_cov_shift_informal} and extend it to the bias.
 Combined together, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
@@
 
-Next, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
+Second, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
 We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
@@
 \squishlist
-	\item In Proposition \ref{prop_dist_transition}, we provide a deterministic condition that depends on the sample sizes and model distance in the isotropic setting.
+	\item We provide a deterministic condition that depends on the sample sizes and model distance in the isotropic setting (Proposition \ref{prop_dist_transition}).
 	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
@@
 	We discuss these in Section \ref{sec_insight} more precisely.
-	\item In Proposition \ref{prop_data_size}, we provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance.
+	\item We provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item In Proposition \ref{prop_covariate}, we study a special case of having the same task models and show that MTL is best performing without covariate shift.
+	\item We study a special case of having the same task models and show that MTL is best performing without covariate shift (Proposition \ref{prop_covariate}).
 	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
@@
 While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-Inspired by our observation that adding more source task data does not always improve perfromance, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
+Inspired by our observation that adding more source task data does not always improve performance, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
 We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset, while keeping the accuracy the same.

### 2020-06-05 writeup/experiments.tex
update exp
sec 4

@@
 		\toprule
-		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-		Sentiment\\ analysis\end{center}\end{minipage}} \\
-		\cmidrule(lr){2-3}
-		& {\bf MTL} & {\bf IncTrain} \\
+		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
+		% Sentiment\\ analysis\end{center}\end{minipage}} \\
+		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{Sentiment analysis} \\
+		% \cmidrule(lr){2-3}
+		& {\bf all tasks} & {\bf w/o TREC} \\
 		\midrule
-		{\bf MLP}  & 100\% & \textbf{xx\%} \\
-		{\bf LSTM} & \textbf{36\%} & xx\% \\
+		{\bf MLP}  & 66\% & 67\% \\
+		{\bf LSTM} & 71\% & 71\% \\
+		{\bf CNN}  & 63\% & 64\% \\
 		\bottomrule
@@
 	\vspace{0.1in}
-	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
+	\captionof{table}{Efficiency of incremental training compared to baseline MTL.}
 	\label{tab:taskonomy}
@@
 
-We measure the data efficiency ratio on the sentiment analysis tasks.
-In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ ({\cor or $36\%$?}) of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
-The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
+Our next result shows the incremental training schedule applies to multiple tasks as well.
+In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $71\%$ of the computational cost compared to baseline multi-task training, while achieving the same accuracy averaged over all six tasks.
+As a further validation, we exclude TREC from the six tasks and observe similar comparative results.
+%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
+%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
 %If TREC is not included, we see that only $25\%$ of the labeled data is needed.

### 2020-06-05 writeup/experiments.tex
sec 4

@@
 
-Our first result is to show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
+\textit{Predicting transfer effect via STL results.}
+We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
+A common challenge in the study of multi-task learning is that the results can be hard to understand.
+It is difficult to predict when MTL performs well without running extensive trials.
+Our insight here is that we can use STL results to help understand MTL results.
+Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
+We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
+We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
+%The results show that STL results are indicative of MTL results.
+
+\textit{Mitigating negative transfer via incremental training.}
+Our show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
 Our insight is that since adding more samples from the source task does not always improve performance, we can improve efficiency by adding the source samples \textit{incrementally} during training.
@@
 
-A common challenge in the study of multi-task learning is that the results can be hard to understand.
-It is difficult to predict when MTL performs well without running extensive trials.
-Our insight here is that we can use STL results to help understand MTL results.
-We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
-Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-The results show that STL results are indicative of MTL results.
-
 Finally, we validate our theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.

### 2020-06-05 writeup/related.tex
sec 4

@@
 \section{Conclusions and Discussions}
+
+In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
+We provided tight concentration bounds for the bias and the variance.
+Based on these bounds, we analyzed the impact of three properties, including task similarity, sample data and covariate shift on the bias and variance, to derive conditions where MTL performs better than STL.
+%Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
+We validated our theoretical results.
+Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed that our proposed method outperforms baseline multi-task training on sentiment analysis tasks.
+We described several open questions for future work.
+First, our result on the bias of multi-task learning (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
+Tightening this error bound can potentially cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
+Second, it would be interesting to extend our results to non-linear settings.
+This likely requires addressing significant technical challenges in order to deal with non-linearity.

### 2020-06-05 writeup/experiments.tex
edits

@@
 
-We connect our theory to pratical problems of interest.
-(i) We validate the single-task based metric on text and image classification tasks.
-We show that for both datasets, single-task learning results can help predict positive or negative transfer in multi-task learning.
-(ii) We show that our proposed incremental training schedule improves the training efficiency of multi-task learning for predicting a particular target task.
+We validate our theory and our algorithmic insights.
+First, we validate the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
+We show that single-task learning results can help predict positive or negative transfer for both datasets.
+Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
 %Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-(iii) We validate our theoretical results in Section \ref{sec_insight} on text classification tasks.
+Third, when source/target sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
+Finally, we validate our theoretical results on text classification tasks.
 
@@
 It is difficult to predict when MTL performs well without running extensive trials.
-Our insight here is that we can use STL results to help understand MTL results.
+Our insight is that we can use STL results to help understand MTL results.
 Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
@@
 \textit{Mitigating negative transfer via incremental training.}
-Our show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
-Our insight is that since adding more samples from the source task does not always improve performance, we can improve efficiency by adding the source samples \textit{incrementally} during training.
-Over six randomly selected task pairs from the sentiment analysis dataset, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.
+First, we show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
+Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{incrementally} during training.
+Over six randomly selected pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve similar performance on the target task, compared to the MTL baseline.
 
@@
 Our next result shows the incremental training schedule applies to multiple tasks as well.
-In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $71\%$ of the computational cost compared to baseline multi-task training, while achieving the same accuracy averaged over all six tasks.
-As a further validation, we exclude TREC from the six tasks and observe similar comparative results.
+In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $71\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
+As a further validation, excluding TREC, we observe similar comparative results.
 %The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
@@
 	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer (red curve).
-	(c) As source/target sample ratio increases, the performance gain of aligning task covariances \cite{WZR20} compared to MTL increases for LSTM and MLP.}
+	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
+	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves more over the baseline.}
 	\label{fig_ablation}
@@
 
-Finally, we validate our theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.
-In Figure \ref{fig_ablation}, we show that MTL performance is affected by
-(a) decreased task similarity;
-(b) increased source/target sample ratio;
-(c) covariate shift under increased source sample size.
-For the last result, specifically we show that the alignment procedure proposed in \cite{WZR20} becomes more helpful when the sample ratio is large.
+We validate our three theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.
+In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
+We select a pair of similar versus dissimilar task based on our domain knowledge or these tasks (cf. Appendix \ref{app_it} for the detailed procedure).
+We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
+In Figure \ref{fig_ab_data}, we validate the phenomenon that adding more source data samples does not always improve performance on the target task.
+In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL performance.
+We average the result over all 15 task pairs.
+The result shows that as source samples increases, performing the alignment procedure shows a bigger improvement over MTL.
 The experimental procedure is left to Appendix \ref{app_it}.

### 2020-06-05 writeup/transfer.tex
edits

@@
 We formalize this connection in the following simplified setting, where we can perform explicit calculations.
+We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
 
@@
 
-In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$ (or $d$), there is a transition from positive transfer to negative transfer in MTL.
+%In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$ (or $d$), there is a transition from positive transfer to negative transfer in MTL.
 %We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
@@
 	\squishlist
-		\item If $\Psi(\beta_1, \beta_2) < \nu \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) > \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
-	Here $\nu = (1-\oo(1))\min(\cdot(1 - \rho_1^{-1/2})^4, (1 + \rho_1^{-1/2})^{-4})$.
+	Here {\small$\nu = (1-\oo(1))\min((1 - 1/\sqrt{\rho_1})^{-4}, (1 + 1/\sqrt{\rho_1})^{4})$}.
 	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
@@
 We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-We can see that our result is able to predict positive or negative transfer  accuractly that matches the empirical curve.
+We can see that our result is able to predict positive or negative transfer  accurately that matches the empirical curve.
 There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
@@
 %On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-Using the isotropic model, we consider what happens if we vary the source task sample size.
+In the isotropic model, we consider what happens if we vary the source task sample size.
+Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
 %Figure \ref{fig_size} provides a simulation result for such a setting.
@@
 	\squishlist
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
 $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \nu^{-1}}$, then w.h.p.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \nu}$, then w.h.p.
 $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
@@
 \end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the data ratio $n_1 / n_2$.
-We apply the above result to the parameter setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-Our theory accuractly predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-There are several unexplained observations near $y = 0$ caused by the errors $\nu$.
+Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $n_1 / n_2$.
+We apply the result to the parameter setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+There are several unexplained observations near $y = 0$ caused by $\nu$.
 The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
@@
 Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-
+\vspace{-0.025in}
 {\small\begin{align*}
@@
 %	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-
 \begin{proposition}[Covariate shift]\label{prop_covariate}

### 2020-06-05 writeup/experiments.tex
writing

@@
 
-We validate our theory and our algorithmic insights.
+We validate our theory and algorithmic insights.
 First, we validate the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
@@
 %Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-Third, when source/target sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
+Third, when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
 Finally, we validate our theoretical results on text classification tasks.

### 2020-06-05 writeup/intro.tex
writing

@@
 	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
-	In this work, we consider three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} to determine transfer effect.
-	We study the high-dimensional linear regression setting that allows us to define each component precisely,
+	In this work, we consider three components including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} to determine transfer effect.
+	We study the high-dimensional linear regression setting that allows us to define each component precisely
 % the performance of predicting a particular task given multiple tasks.
@@
 %	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
-	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size and covariate shift under increased source sample size.
+	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
 	We validate the three effects on text classification tasks.
@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning is a powerful approach for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue} and many other areas \cite{ZY17}.
+Multi-task learning is a powerful approach for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue}, and many other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
@@
 %By combining multiple information sources, it is possible to share all the information in the same model.
-In many settings, multiple data sources are available for predicting a particular target task.
+In many settings, multiple source tasks are available for predicting a particular target task.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
-The performance of multi-task learning depends on the relationship between the data sources and the target \cite{C97}.
+The performance of multi-task learning depends on the relationship between the source and target tasks \cite{C97}.
 When the data sources are relatively different from each other, negative transfer has often been observed \cite{PY09,AP16,BS17}.
@@
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-In this work, we provide a rigorous study to understand when positive or transfer occurs in the setting of high-dimensional linear regression.
-We show that the bias-variance tradeoff of multi-task learning estimators determines the transfer effect, and we develop new concentration bounds to analyze the tradeoff.
+In this work, we provide a rigorous study to understand when positive or negative transfer occurs in the setting of high-dimensional linear regression.
+We show that the bias-variance tradeoff of multi-task learning estimators determines the transfer effect, and develop new concentration bounds to analyze the tradeoff.
 %Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
@@
 Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
-From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data is important because it is often applied to settings in which a particular task has limited amount of labeled data \cite{RH19}.
+From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data is important because it is often applied to settings in which a particular task has a limited amount of samples \cite{RH19}.
 %For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
@@
 In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
-This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
+This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
 To be precise, we define each component for two tasks below and our definition applies more generally.
@@
 We consider a multi-task estimator obtained using a shared linear layer for all tasks and a separate output layer for each task \cite{WZR20}.
-This two layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
-We consider the bias and variance of the multi-task estimator for predicting a particular task, and compare its performance to single-task learning.
+This two-layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
+We consider the bias and variance of the multi-task estimator for predicting a particular task and compare its performance to single-task learning.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
@@
 We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Lemma \ref{lem_cov_shift_informal} and extend it to the bias.
-Combined together, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with same features in Theorem \ref{thm_many_tasks}.
+Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
 %For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
@@
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item We study a special case of having the same task models and show that MTL is best performing without covariate shift (Proposition \ref{prop_covariate}).
+	\item We study a special case of having the same task models and show that MTL  performs best without covariate shift (Proposition \ref{prop_covariate}).
 	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
@@
 Inspired by our observation that adding more source task data does not always improve performance, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
-We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset, while keeping the accuracy the same.
+We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset while keeping the accuracy the same.
 Last, we validate our three theoretical findings on sentiment analysis tasks.

### 2020-06-05 writeup/setup.tex
writing

@@
 We begin by defining our problem setup including the multi-task estimator we study.
-Then, we describe the bias-variance tradeoff of the multi-task estimator, and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size} and \textit{covariate shift}.
+Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size}, and \textit{covariate shift}.
 %Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

### 2020-06-05 writeup/transfer.tex
writing

@@
 (b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
-(c) \textit{Covariate shift}: as source sample size increases, we show that covariate shift worsens the performance of the multi-task estimator.
-Finally, we extend our result from two tasks to many tasks with the same features.
+(c) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
+Finally, we extend our results from two tasks to many tasks with the same features.
 %We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.

### 2020-06-05 writeup/experiments.tex
8 pages

@@
 
+\vspace{-0.05in}
 We validate our theory and algorithmic insights.
@@
 
+\vspace{-0.07in}
 \subsection{Experimental Setup}
@@
 
-{\it Sentiment Analysis:} This dataset includes six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
-{For each task, the goal is to categorize sentiment opinions expressed in the text.
+{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
+The question is to predict positive or negative sentiment expressed in the text.
 We use an embedding layer with GloVe embeddings
 followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
-}
+
 %multi-layer perceptron (MLP), LSTM, CNN on all tasks
@@
 
-{\it ChestX-ray14:} This dataset contains 112,120 frontal-view X-ray images and each image has up to 14 diseases.
-This is a 14-task multi-label image classification problem.
+{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images.
+There are 14 diseases (tasks) for every image that we would like to predict.
+We use AlexNet as the shared module.
 %We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
@@
 
+\vspace{-0.07in}
 \subsection{Experimental Results}
@@
 
-\subsection{Ablation Studies}
+\vspace{-0.07in}
+\subsection{Validating the Theoretical Results}
 
@@
 In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
-We select a pair of similar versus dissimilar task based on our domain knowledge or these tasks (cf. Appendix \ref{app_it} for the detailed procedure).
+We select each task pair based on our domain knowledge.
 We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
@@
 In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL performance.
-We average the result over all 15 task pairs.
-The result shows that as source samples increases, performing the alignment procedure shows a bigger improvement over MTL.
-The experimental procedure is left to Appendix \ref{app_it}.
+We average the results over all 15 task pairs.
+The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
+The rest of experimental procedures are left to Appendix \ref{app_it}.

### 2020-06-05 writeup/related.tex
8 pages

--- 2020-06-04 writeup/related.tex
@@
+\vspace{-0.05in}
 \section{Related Work}
+\vspace{-0.05in}
 
-We refer the interested readers to several excellent surveys on multi-task and transfer learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
+We refer the interested readers to several excellent surveys on multi-task  learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
+Below, we describe several lines of work that are most related to this work.
 
@@
 Our work is closely related to Wu et al. \cite{WZR20}.
-While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their results do not apply to explain the phenomena of negative transfer.
+While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques do not explain the phenomena of negative transfer.
 
@@
 Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
-\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,R17}.
+%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,KD12,R17}.
 We believe that the technical tools we have developed can also be applied to many other multi-task learning models.
@@
 
-\section{Conclusions and Discussions}
+\vspace{-0.05in}
+\section{Conclusions and Open Problems}
+\vspace{-0.05in}
+
+In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
+We provided tight concentration bounds for the bias and the variance.
+Based on these bounds, we analyzed the impact of three properties, including task similarity, sample data and covariate shift on the bias and variance, to derive conditions for transfer.
+%Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
+We validated our theoretical results.
+Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging result inspired by our theory.
+We describe several open questions for future work.
+First, our bound on the bias term (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
+Tightening this error bound can potentially cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
+Second, it would be interesting to extend our results to non-linear settings.
+We remark that this likely requires addressing significant technical challenges in order to deal with non-linearity.

### 2020-06-05 writeup/experiments.tex
edits

@@
 We use an embedding layer with GloVe embeddings
-followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
+followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.
 
@@
 There are 14 diseases (tasks) for every image that we would like to predict.
-We use AlexNet as the shared module.
+We use densenet121 as the shared module.
 %We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.

### 2020-06-05 writeup/intro.tex
edits

@@
 	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
-	To be precise, we say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
+	We say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
 	In this work, we consider three components including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} to determine transfer effect.
@@
 Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
-From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data is important because it is often applied to settings in which a particular task has a limited amount of samples \cite{RH19}.
+From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data can provide guidance for downstream applications \cite{RH19}.
 %For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
@@
 %\textbf{Setup and Main Results.}
-In this work, we apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to determine transfer effect in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
+In this work, we study the bias and variance of multi-task learning in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
 This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
-To be precise, we define each component for two tasks below and our definition applies more generally.
+We apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to bound the bias and variance, and relate them to the three components.
+We define each component for two tasks below and our definition applies more generally.
 We refer to the first task as the source and the second as the target.
@@
 Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
-Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator (which is $0$ since $n_1 > p$).
+Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator.
 Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
@@
 \squishlist
-	\item We provide a deterministic condition that depends on the sample sizes and model distance in the isotropic setting (Proposition \ref{prop_dist_transition}).
+	\item We provide conditions to predict the effect of transfer in the isotropic setting (Proposition \ref{prop_dist_transition}).
 	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
 %	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-	The unexplained observations are caused by an error term that arises from the bias of the multi-task estimator.
-	We discuss these in Section \ref{sec_insight} more precisely.
+	The unexplained observations are caused by an error term from the bias.
+	We discuss these in Section \ref{sec_insight}.
 	\item We provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
@@
 %We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL, .
+Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL.
 %We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.

### 2020-06-05 writeup/related.tex
edits

@@
 \textit{Multi-task learning theory.}
-Some of the earliest work on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
-Mauer \cite{M06} Generalization bounds for linear separation settings of MTL
-Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines empirical and target errors in an optimal way.
+Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
+Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
+Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors in an optimal way.
 The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
@@
 Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-Argyriou et al. \cite{AEP08} presents a convex algorithm which learns common sparse representations across a pool of related tasks.
-Evgeniou et al. \cite{EMP05} develops a framework for multi-task learning in the context of kernel methods.
+Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
+Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
 %\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
@@
 
-\textit{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
+\textit{Random matrix theory.}
+The random matrix theory tool and related proof of our work fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
 For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.
 It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}.
-On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
+On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using the free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
 To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
@@
 We provided tight concentration bounds for the bias and the variance.
-Based on these bounds, we analyzed the impact of three properties, including task similarity, sample data and covariate shift on the bias and variance, to derive conditions for transfer.
+Based on these bounds, we analyzed the impact of three properties, including task similarity, sample size, and covariate shift on the bias and variance, to derive conditions for transfer.
 %Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
 We validated our theoretical results.
-Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging result inspired by our theory.
+Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging results inspired by our theory.
 We describe several open questions for future work.
@@
 Second, it would be interesting to extend our results to non-linear settings.
-We remark that this likely requires addressing significant technical challenges in order to deal with non-linearity.
+We remark that this likely requires addressing significant technical challenges  to deal with non-linearity.
+
+\newpage
+\section*{Broader Impacts}

### 2020-06-05 writeup/setup.tex
edits

@@
 We begin by defining our problem setup including the multi-task estimator we study.
-Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task model distance}, \textit{sample size}, and \textit{covariate shift}.
+Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
 %Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.

### 2020-06-05 writeup/intro.tex
intro quick pass

@@
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item We study a special case of having the same task models and show that MTL  performs best without covariate shift (Proposition \ref{prop_covariate}).
-	For this special case, the bound of Lemma \ref{lem_cov_shift_informal} matches the empirical curve in Figure \ref{fig_covariate} accurately.
+	\item We study a special case of having the same models and show that MTL  performs best without covariate shift (Proposition \ref{prop_covariate}).
+	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
 \squishend
@@
 
-Finally, we connect our theory to practical problems of interest.
-We provide a single-task based metric to predict positive or negative transfer in multi-task learning.
-While it is not well understood when multi-task learning provides positive transfer, we show that the STL results can help indicate and understand MTL results on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-Inspired by our observation that adding more source task data does not always improve performance, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
-We show that our training schedule reduces the computational cost by $55\%$ compared to baseline multi-task training on the sentiment analysis dataset while keeping the accuracy the same.
-Last, we validate our three theoretical findings on sentiment analysis tasks.
+Our study also leads to several algorithmic consequences with practical interest.
+First, we show that single-task learning results can help predict positive or negative transfer for multi-task learning.
+We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
+Second, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
+This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
+Using our incremental training schdule, we reduce the computational cost by $55\%$ compared to baseline multi-task training over six sentiment analysis dataset while keeping the accuracy the same.
+Third, we provide a fine-grained insight on a covariange alignment procedure proposed in \cite{WZR20}.
+We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
+Finally, we validate our three theoretical findings on sentiment analysis tasks.

### 2020-06-05 writeup/intro.tex
intro

@@
 \vspace{-0.05in}
-%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
 	Multi-task learning is a powerful approach in many applications such as image and text classification.
-	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
-	We say that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
-	In this work, we consider three components including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} to determine transfer effect.
-	We study the high-dimensional linear regression setting that allows us to define each component precisely
-% the performance of predicting a particular task given multiple tasks.
-%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
-	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
-%	We analyze the bias-variance tradeoff by developing tight concentration results using random matrix theory.
-	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
-	%We develop a technical tool to analyze the.
-%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
-	Then, we explain three negative effects in multi-task learning including decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
+	Yet, there is little rigorous understanding of when multi-task learning ouperforms single-task learning.
+	In this work, we provide a rigorous study of this question in the setting of high-dimensional linear regression.
+	We show that the bias-variance tradeoff of multi-task learning determines the  effect of transfer and develop new concentration bounds to analyze the tradeoff.
+	The high-dimensional linear regression setting allows us to define three components to measure the difference between tasks, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
+%	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
+	We relate each component to the bias and variance of multi-task learning to explain three negative effects as a result of decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
 	We validate the three effects on text classification tasks.
@@
 	First, single-task performance can help understand multi-task performance.
-	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.% for predicting a particular task.
-%	We validate our theory and our proposed method .
+	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.
 \end{abstract}
@@
 The performance of multi-task learning depends on the relationship between the source and target tasks \cite{C97}.
-When the data sources are relatively different from each other, negative transfer has often been observed \cite{PY09,AP16,BS17}.
+%	We define that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
+When the sources are relatively different from the target, multi-task learning has often been observed to perform worse than single-task learning \cite{AP16,BS17}, which is referred to as \textit{negative transfer} \cite{PY09}.
 While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
 %This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-In this work, we provide a rigorous study to understand when positive or negative transfer occurs in the setting of high-dimensional linear regression.
-We show that the bias-variance tradeoff of multi-task learning estimators determines the transfer effect, and develop new concentration bounds to analyze the tradeoff.
+
 %Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
@@
 
-Understanding positive versus negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
-This presents a technical challenge in the multi-task setting due to the presence of different task features, even for two tasks.
+Understanding negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
+This presents a technical challenge in the multi-task setting because of the difference between task features, even for two tasks.
 For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
@@
 In this work, we study the bias and variance of multi-task learning in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
+We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
 This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
-We apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to bound the bias and variance, and relate them to the three components.
-We define each component for two tasks below and our definition applies more generally.
+We apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to derive bounds on the bias and variance, and relate them to the three components.
+We define each component for two tasks and our definition applies to general settings.
 We refer to the first task as the source and the second as the target.
@@
 \textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
-Since the total sample size has increased, the variance of the multi-task estimator is \textit{always smaller} than that of the single-task estimator.
-Since task models are different, the bias of the multi-task estimator is \textit{always larger} than that of the single-task estimator.
+We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of additional source task samples.
+On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, due to model differences.
 Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
@@
 
-Second, we explain the performance of multi-task learning by varying the three components above in isotropic and covariate shifted settings.
-We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
+Second, we explain the performance of multi-task learning observed in Figure \ref{fig_model_shift_phasetrans} by varying the three components above in isotropic and covariate shifted settings.
 %We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
@@
 \squishlist
-	\item We provide conditions to predict the effect of transfer in the isotropic setting (Proposition \ref{prop_dist_transition}).
-	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
+	\item We provide conditions to predict the effect of transfer as a parameter of model distance (Section \ref{sec_similarity}).
+	As task model distance increases, the bias becomes larger, resulting in negative transfer.
+%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
 %	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-	The unexplained observations are caused by an error term from the bias.
-	We discuss these in Section \ref{sec_insight}.
-	\item We provide a similar condition that explains a curious phenomenon in Figure \ref{fig_size}, namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
+%	The unexplained observations are caused by an error term from the bias.
+%	We discuss these in Section \ref{sec_insight}.
+	\item We provide conditions to predict transfer as a parameter of sample ratio $n_1/n_2$ (Section \ref{sec_data_size}).
+	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
+	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item We study a special case of having the same models and show that MTL  performs best without covariate shift (Proposition \ref{prop_covariate}).
-	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
+	\item We study a special case of having the same models and show that MTL  performs best without covariate shift (Section \ref{prop_covariate}).
+	The bias is zero but the variance reduces less due to covariate shift.
+%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
 \squishend
@@
 %We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-Along the way, we explain a key empirical finding of Taskonomy by Zamir et al. \cite{ZSSGM18}, by analyzing the benefit of MTL for reducing labeled data to achieve comparable performance to STL.
+Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
 %We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
@@
 This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
-Using our incremental training schdule, we reduce the computational cost by $55\%$ compared to baseline multi-task training over six sentiment analysis dataset while keeping the accuracy the same.
-Third, we provide a fine-grained insight on a covariange alignment procedure proposed in \cite{WZR20}.
+Using our incremental training schedule, we reduce the computational cost by $55\%$ compared to baseline multi-task training over six sentiment analysis dataset while keeping the accuracy the same.
+Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
 We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.

### 2020-06-05 writeup/related.tex
intro

@@
 \section*{Broader Impacts}
+
+In this work, we provide a theoretical study to help understand when multi-task learning performs well.
+We approach this question by studying the bias-variance tradeoff of multi-task learning.
+We provide new technical tools to bound the bias and variance.
+We relate the bounds to three properties of task data.
+Overall, our theoretical study provides a framework to help understand multi-task learning performance.
+We further provide guidance for detecting and mitigating negative transfer on image and text classification tasks.
+
+Our theoretical framework has the potential to impact many other neighboring areas in the ML community.
+Multi-task learning connects to a wide range of areas \cite{V20}.
+To name a few, transfer learning, meta learning, multimodal learning, semi-supervised learning, and representation learning are all closely related areas to multi-task learning.
+Any learning scenario such as reinforcement learning \cite{YKGLHF20} that combines multiple datasets to supervise a model is using multi-task learning.
+While the theoretical results that we have provided are not directly applicable to these different settings, we believe that the tools we have developed and the framework we have provided can inspire followup works in different settings.
+For one specific example, we have developed new concentration bounds that may apply to many settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
+For another example, our results also allow extensions to transfer learning and domain adaptation \cite{K18}.
+The insights we have developed on positive and negative transfer can potentially find applications in multimodal learning, where the data sources are usually heterogeneous.
+Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where scarse labeled samples presents a significant challenge.
+
+Our algorithmic consequences that have from our theory have the potential to impact downstream applications of multi-task learning.
+For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
+Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult to acquire large amounts of labeled data.
+For such settings, training multi-task models can be very challenging.
+Our insight on using single-task learning results to help understand multi-task learning can be valuable for helping practitioners understand their results.

### 2020-06-05 writeup/intro.tex
intro

@@
 	We show that the bias-variance tradeoff of multi-task learning determines the  effect of transfer and develop new concentration bounds to analyze the tradeoff.
-	The high-dimensional linear regression setting allows us to define three components to measure the difference between tasks, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
+	The high-dimensional linear regression setting allows us to define three properties that measure the difference between task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
 %	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
-	We relate each component to the bias and variance of multi-task learning to explain three negative effects as a result of decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
+	We relate each property to the bias and variance of multi-task learning to explain three negative effects as a result of decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
 	We validate the three effects on text classification tasks.
@@
 In this work, we study the bias and variance of multi-task learning in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
-We describe three simulations in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of the single-task estimator minus the multi-task estimator.
-This setting allows us to measure the difference of task data by three components, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
-We apply recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic} to derive bounds on the bias and variance, and relate them to the three components.
-We define each component for two tasks and our definition applies to general settings.
+Our key observation is that three properties of task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} can affect whether multi-task learning outperforms single-task learning (which we refer to as \textit{positive transfer}).
+As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of single-task learning minus multi-task learning for predicting the second task.
+We observe that the effect of transfer can be positively or negatively affected as we vary each property.
+Moreover, these phenomena cannot be explained using previous techniques \cite{WZR20}.
+The high-dimensional linear regression setting allows us to measure the three properties precisely.
+We define each property for two tasks and our definition applies to general settings.
 We refer to the first task as the source and the second as the target.
@@
 
-\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks.
+\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic}.
 We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of additional source task samples.
@@
 
-Second, we explain the performance of multi-task learning observed in Figure \ref{fig_model_shift_phasetrans} by varying the three components above in isotropic and covariate shifted settings.
+Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
 %We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.

### 2020-06-05 writeup/experiments.tex
update table 1
submit v1

@@
 		\midrule
-		{\bf MLP}  & 66\% & 67\% \\
-		{\bf LSTM} & 71\% & 71\% \\
-		{\bf CNN}  & 63\% & 64\% \\
+		{\bf MLP}  & 31\% & 29\% \\
+		{\bf LSTM} & 35\% & 34\% \\
+		{\bf CNN}  & 30\% & 28\% \\
 		\bottomrule
@@
 Our next result shows the incremental training schedule applies to multiple tasks as well.
-In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $71\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
+In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
 As a further validation, excluding TREC, we observe similar comparative results.

### 2020-06-05 writeup/intro.tex
submit v1

@@
 	Multi-task learning is a powerful approach in many applications such as image and text classification.
-	Yet, there is little rigorous understanding of when multi-task learning ouperforms single-task learning.
+	Yet, there is little rigorous understanding of when multi-task learning outperforms single-task learning.
 	In this work, we provide a rigorous study of this question in the setting of high-dimensional linear regression.
@@
 	The high-dimensional linear regression setting allows us to define three properties that measure the difference between task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
-%	and show that the bias-variance tradeoff of multi-task estimators determines the transfer effect.
-	We relate each property to the bias and variance of multi-task learning to explain three negative effects as a result of decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
+	We relate each property to the bias and variance of multi-task learning to explain three negative effects because of decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
 	We validate the three effects on text classification tasks.
@@
 We observe that the effect of transfer can be positively or negatively affected as we vary each property.
-Moreover, these phenomena cannot be explained using previous techniques \cite{WZR20}.
+These phenomena cannot be explained using previous techniques \cite{WZR20}.
 The high-dimensional linear regression setting allows us to measure the three properties precisely.
@@
 We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of additional source task samples.
-On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, due to model differences.
+On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model differences.
 Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Lemma \ref{lem_cov_shift_informal} and extend it to the bias.
+We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Section \ref{sec_main} and extend the analysis to the bias.
 Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
@@
 \squishlist
-	\item We provide conditions to predict the effect of transfer as a parameter of model distance (Section \ref{sec_similarity}).
-	As task model distance increases, the bias becomes larger, resulting in negative transfer.
+	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
+	As model distance increases, the bias becomes larger, resulting in negative transfer.
 %	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
@@
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item We study a special case of having the same models and show that MTL  performs best without covariate shift (Section \ref{prop_covariate}).
-	The bias is zero but the variance reduces less due to covariate shift.
+	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are the same  (Section \ref{sec_covshift}).
+	Otherwise, the variance reduces less with covariate shift.
 %	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
@@
 This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
-Using our incremental training schedule, we reduce the computational cost by $55\%$ compared to baseline multi-task training over six sentiment analysis dataset while keeping the accuracy the same.
+Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis dataset while keeping the accuracy the same.
 Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.

### 2020-06-05 writeup/intro.tex
minor fix

@@
 Yet, there is little rigorous understanding of when multi-task learning outperforms single-task learning.
-	In this work, we provide a rigorous study of this question in the setting of high-dimensional linear regression.
-	We show that the bias-variance tradeoff of multi-task learning determines the  effect of transfer and develop new concentration bounds to analyze the tradeoff.
-	The high-dimensional linear regression setting allows us to define three properties that measure the difference between task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
-	We relate each property to the bias and variance of multi-task learning to explain three negative effects because of decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
-	We validate the three effects on text classification tasks.
+In this work, we provide a rigorous study to anwer the question in the high-dimensional linear regression setting.
+We show that the bias-variance tradeoff of multi-task learning determines the effect of information transfer and develop new concentration bounds to analyze the tradeoff.
+Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting.
+We relate each property to the bias and variance of multi-task learning and explain three negative effects with decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
+And we validate the three effects on text classification tasks.
 Inspired by our theory, we show two practical connections of interest.
@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning is a powerful approach for improving performance on prediction tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue}, and many other areas \cite{ZY17}.
+Multi-task learning is a powerful approach for improving performance on many tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue}, and other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.
@@
 %By combining multiple information sources, it is possible to share all the information in the same model.
-In many settings, multiple source tasks are available for predicting a particular target task.
+In many settings, multiple source tasks are available to help predict a particular target task.
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
@@
 
-Understanding negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
-This presents a technical challenge in the multi-task setting because of the difference between task features, even for two tasks.
+However, understanding negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
+This presents a technical challenge in the multi-task setting because of the difference among task features, even for two tasks.
 For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
@@
 Our key observation is that three properties of task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} can affect whether multi-task learning outperforms single-task learning (which we refer to as \textit{positive transfer}).
-As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the loss of single-task learning minus multi-task learning for predicting the second task.
-We observe that the effect of transfer can be positively or negatively affected as we vary each property.
+As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the improvement of multi-task learning over single-task learning for task two.
+We observe that the effect of transfer can be positive or negative as we vary each property.
 These phenomena cannot be explained using previous techniques \cite{WZR20}.
 The high-dimensional linear regression setting allows us to measure the three properties precisely.
-We define each property for two tasks and our definition applies to general settings.
-We refer to the first task as the source and the second as the target.
+We define each property for the case of two tasks and our definition applies to general settings.
+We refer to the first task as the source task and the second as the target task.
 \squishlist
@@
 This two-layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
-We consider the bias and variance of the multi-task estimator for predicting a particular task and compare its performance to single-task learning.
+We consider the bias and variance of the multi-task estimator for predicting a target task and compare its performance to single-task learning.
 %This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
@@
 
-\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development from the random matrix theory literature \cite{erdos2017dynamical,isotropic,Anisotropic}.
-We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of additional source task samples.
+\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
+We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
 On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model differences.
 Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-We provide a sharp analysis of the variance that scales only with sample size and covariate shift in Section \ref{sec_main} and extend the analysis to the bias.
+We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
+We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
 Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
@@
 We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-Second, we propose to train multi-task models by incrementally adding source task data for predicting a target task.
+Second, we propose a new multi-task training schedule by incrementally adding task data batches to the training procedure.
 This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.

### 2020-06-05 writeup/related.tex
minor fix

@@
 We relate the bounds to three properties of task data.
-Overall, our theoretical study provides a framework to help understand multi-task learning performance.
+%Overall, our theoretical study provides a framework to help understand multi-task learning performance.
 We further provide guidance for detecting and mitigating negative transfer on image and text classification tasks.
@@
 
-Our algorithmic consequences that have from our theory have the potential to impact downstream applications of multi-task learning.
+Our algorithmic consequences of our theory have the potential to impact downstream applications of multi-task learning.
 For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.

### 2020-06-05 writeup/intro.tex

@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning is a powerful approach for improving performance on many tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue}, and other areas \cite{ZY17}.
+Multi-task learning is a powerful approach to improve performance for many tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue}, and other areas \cite{ZY17}.
 %In multi-task learning, having related task data is fundamental to its performance.

### 2020-06-05 writeup/experiments.tex
update table 1
edits

@@
 \vspace{-0.05in}
-We validate our theory and algorithmic insights.
-First, we validate the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
-We show that single-task learning results can help predict positive or negative transfer for both datasets.
+We validate our  algorithmic insights and then our theory.
+In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
+%the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
 Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
 %Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-Third, when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
-Finally, we validate our theoretical results on text classification tasks.
+In Section \ref{sec_exp_ab}, validate our theoretical results.
+We show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
 
 \begin{table}[!b]
-\begin{minipage}[t]{.40\textwidth}
-	\vspace{-0.1in}
-	\centering
-	\begin{tabular}{c c c}
-		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-		& {\bf all tasks} & {\bf w/o TREC} \\
-		\midrule
-		{\bf MLP}  & 31\% & 29\% \\
-		{\bf LSTM} & 35\% & 34\% \\
-		{\bf CNN}  & 30\% & 28\% \\
-		\bottomrule
-		\end{tabular}
-	\vspace{0.1in}
-	\captionof{table}{Efficiency of incremental training compared to baseline MTL.}
-	\label{tab:taskonomy}
-\end{minipage}%
-\quad
 \begin{minipage}[t]{.58\textwidth}
@@
 	\label{tab:mtl_better_than_stl}
+\end{minipage}%
+\quad
+	\begin{minipage}[t]{.40\textwidth}
+	\vspace{-0.1in}
+	\centering
+	\begin{tabular}{c c c}
+		\toprule
+		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
+		% Sentiment\\ analysis\end{center}\end{minipage}} \\
+		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
+		% \cmidrule(lr){2-3}
+		& all tasks & w/o TREC \\
+		\midrule
+		{\bf MLP}  & 31\% & 29\% \\
+		{\bf LSTM} & 35\% & 34\% \\
+		{\bf CNN}  & 30\% & 28\% \\
+		\bottomrule
+		\end{tabular}
+	\vspace{0.1in}
+	\captionof{table}{Efficiency of incremental training compared to baseline MTL.}
+	\label{tab:taskonomy}
 \end{minipage}
@@
 %\textbf{The training procedure and baseline.}
-For all models, we share the main module across all tasks and assign a separate regression or classification layer on top of the shared module for each tasks.
+For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
 The baseline training schedule for MTL is the round-robin training schedule.
@@
 We measure the test accuracy of predicting a target task.
+We measure computional cost by summing over all epochs the number of samples used in every epoch.
 
 \vspace{-0.07in}
-\subsection{Experimental Results}
+\subsection{Experimental Results}\label{sec_exp_res}
 
@@
 We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-A common challenge in the study of multi-task learning is that the results can be hard to understand.
+A common challenge in the study of MTL is that the results can be hard to understand.
 It is difficult to predict when MTL performs well without running extensive trials.
@@
 Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
+We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
 We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
@@
 First, we show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
+Over all $15$ pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve similar performance on the target task, compared to the MTL baseline.
 Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{incrementally} during training.
-Over six randomly selected pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve similar performance on the target task, compared to the MTL baseline.
 
@@
 	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves more over the baseline.}
+	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves more over the baseline.
+	Note: (S) denotes the source task and (T) denotes the target task.}
 	\label{fig_ablation}
@@
 \vspace{-0.07in}
-\subsection{Validating the Theoretical Results}
+\subsection{Validating the Theoretical Results}\label{sec_exp_ab}
 
-We validate our three theoretical results in Section \ref{sec_insight} on the sentiment analysis tasks.
+We first validate our theoretical results in Section \ref{sec_similarity} and \ref{sec_data_size}.
 In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
@@
 We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
-In Figure \ref{fig_ab_data}, we validate the phenomenon that adding more source data samples does not always improve performance on the target task.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL performance.
+In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
+Finally, we validate the algorithmic consequence of Section \ref{sec_covshift}.
+In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL.
 We average the results over all 15 task pairs.

### 2020-06-05 writeup/intro.tex
edits

@@
 In this work, we provide a rigorous study to anwer the question in the high-dimensional linear regression setting.
-We show that the bias-variance tradeoff of multi-task learning determines the effect of information transfer and develop new concentration bounds to analyze the tradeoff.
+We show that a bias-variance tradeoff of multi-task learning determines the effect of information transfer and develop new concentration bounds to analyze the tradeoff.
 Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting.
 We relate each property to the bias and variance of multi-task learning and explain three negative effects with decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
-And we validate the three effects on text classification tasks.
+We validate the three effects on text classification tasks.
 Inspired by our theory, we show two practical connections of interest.
-	First, single-task performance can help understand multi-task performance.
+	First, single-task results can help understand when multi-task learning gives gains.
 	Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.
@@
 %	We define that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
-When the sources are relatively different from the target, multi-task learning has often been observed to perform worse than single-task learning \cite{AP16,BS17}, which is referred to as \textit{negative transfer} \cite{PY09}.
+When the sources are relatively different from the target, multi-task learning (MTL) has often been observed to perform worse than single-task learning (STL) \cite{AP16,BS17}, which is referred to as \textit{negative transfer} \cite{PY09}.
 While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
@@
 
-However, understanding negative transfer requires developing generalization bounds that scale tightly with properties of each task data such as its sample size.
+Understanding negative transfer requires developing generalization bounds that scale tightly with properties of each task data, such as its sample size.
 This presents a technical challenge in the multi-task setting because of the difference among task features, even for two tasks.
@@
 In this work, we study the bias and variance of multi-task learning in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
-Our key observation is that three properties of task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} can affect whether multi-task learning outperforms single-task learning (which we refer to as \textit{positive transfer}).
-As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the improvement of multi-task learning over single-task learning for task two.
+Our key observation is that three properties of task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}, can affect whether multi-task learning outperforms single-task learning (which we refer to as \textit{positive transfer}).
+As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the improvement of multi-task learning over single-task learning for a particular task.
 We observe that the effect of transfer can be positive or negative as we vary each property.
@@
 	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
-	We define covariate shift as the matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+	We measure covariate shift with matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
 \squishend
@@
 We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model differences.
+On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
 Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
@@
 %	We discuss these in Section \ref{sec_insight}.
-	\item We provide conditions to predict transfer as a parameter of sample ratio $n_1/n_2$ (Section \ref{sec_data_size}).
+	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
 	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
@@
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are the same  (Section \ref{sec_covshift}).
+	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
 	Otherwise, the variance reduces less with covariate shift.
@@
 This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
-Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis dataset while keeping the accuracy the same.
+Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis datasets while keeping the accuracy the same.
 Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.

### 2020-06-05 writeup/setup.tex
edits

@@
 In the high-dimensional linear regression setting (e.g.
-\cite{HMRT19,BLLT20}), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consists of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
+\cite{HMRT19,BLLT20}), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
 And each feature $x_i = \Sigma^{1/2}z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
@@
 When specialized to the linear regression setting, the model consists of a linear layer $B\in\real^{p\times r}$ that is shared by all tasks and $t$ output layers $W_1, \dots, W_t$ that are in $\real^r$.
-The width of $B$, denoted by $r$, plays an important regularization effect.
+The width of $B$, denoted by $r$, plays an important role in regularization.
 As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
 Hence, we assume that $r < t$ in our study.
-For example, when there are only two tasks, $r = 1$ and $B$ reduces a vector whereas $W_1, W_2$ become scalars.
+For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
 We study the following procedure inspired by how hard parameter sharing models are trained in practice (e.g. \cite{MTDNN19}).
@@
 	The size of each set is described below.
-	\item Learning the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a closed form equation for $\hat{B}$ that depends on $W_1,\dots, W_k$.
+	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a closed form equation for $\hat{B}$ that depends on $W_1,\dots, W_k$.
 		\vspace{-0.075in}
@@
 		\vspace{-0.075in}
-	\item Tuning the output layers $W_i$: set $B = \hat{B}$ and minimize the validation loss over $W_1,\dots, W_k$.
+	\item Tune the output layers $W_i$: set $B = \hat{B}$ and minimize the validation loss over $W_1,\dots, W_k$.
 		\vspace{-0.075in}
@@
 \textbf{Problem statement.}
-We focus on predicting a particular task, say the $t$-th task without loss of generality.
+We focus on predicting a particular task, say the $t$-th task, without loss of generality.
 Let $\hat{\beta}_t^{\MTL}$ denote the multi-task estimator obtained from the procedure above.

### 2020-06-05 writeup/transfer.tex
submit v1
edits

@@
 We show theoretical implications for understanding the performance of multi-task learning.
-(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as task models become different.
+(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as tasks become more different.
 (b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
@@
 \begin{theorem}[Two tasks]\label{thm_main_informal}
-	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(\Sigma_1^{1/2}\Sigma_2^{-1/2})^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$, and .
+	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(\Sigma_1^{1/2}\Sigma_2^{-1/2})^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
  	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
@@
 
-Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data is available but the target sample size is small.
+Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
 For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
@@
 	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
-	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 \rho_2 \cdot p$.
+	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
 	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	Assume that for the target task, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
+	Assume that for  task two, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
 	For the source task, $\beta_1 $ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
@@
 We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-We can see that our result is able to predict positive or negative transfer  accurately that matches the empirical curve.
+We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
 There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
@@
 \end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $n_1 / n_2$.
-We apply the result to the parameter setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
+We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
 There are several unexplained observations near $y = 0$ caused by $\nu$.
@@
 	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	For the setting of $t$ tasks where $X_i = X$, for all $1\le i\le t$.
-	Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$ denote the linear model parameters.
+	For the setting of $t$ tasks where $X_i = X$, for all $1\le i\le t$,
+	let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$ denote the linear model parameters.
 	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$.
@@
 Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff beyond two tasks.
-Specially, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of reduced variance and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
+Specifically, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of reduced variance and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
 The proof of \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.

### 2020-06-09 writeup/proofs_sec3.tex
submit v1
typos

@@
+\section{Extended Related Work}
+
+McNamara and Balcan \cite{NB17}
+
+Bullins et al. \cite{BHKL19}
+
+Cavallanti et al. \cite{CCG10}
+
+Daume and Marcu \cite{DM06}
+
+Zhao et al. \cite{ZD19}
+
 \section{Missing Details of Problem Formulation}\label{app_proof_sec3}
@@
 \begin{assumption}\label{assm_secA1}
-We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrices, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
+We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrix, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
 entries with mean zero and variance one.
@@
 \begin{assumption}\label{assm_secA2}
-For for some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+For some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
 Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
@@
 Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
-Moreover, we shall use $\oo(1)$ to mean a small positive number that converges to 0 as $p\to \infty$.
+Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
 
@@
 Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
-With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N\times p}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
+With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
 Here we assume that $N_1$ and $N_2$ satisfies $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.

### 2020-06-09 writeup/transfer.tex
typos

@@
 	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(\Sigma_1^{1/2}\Sigma_2^{-1/2})^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
- 	There exists two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
+ 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
 	\squishlist

### 2020-06-09 writeup/experiments.tex
merge

@@
 %Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-In Section \ref{sec_exp_ab}, validate our theoretical results.
-We show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
+In Section \ref{sec_exp_ab}, we validate our theoretical results.
+We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
 

### 2020-06-09 writeup/transfer.tex
merge

--- 2020-06-05 writeup/transfer.tex
@@
 \textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.
-(2018) \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
+\cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
 %More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
@@
 Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in Wu et al. (2020) \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
+We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
 The idea is to add an alignment module between the input and the shared module $B$.

### 2020-06-09 writeup/proof_main.tex
sec 3
app B

@@
-\section{Proof of Theorem \ref{thm_main_informal}}
+\section{Proof of Theorem \ref{thm_main_informal}}\label{app_proof_main_thm}
 
@@
 
-\begin{lemma}\label{lem_cov_shift}
+\begin{lemma}[Variance bound: Restate of Lemma \ref{lem_cov_shift_informal}]\label{lem_cov_shift}
 	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
@@
 
-\begin{lemma}\label{lem_cov_derivative}
+\begin{lemma}[Bias bound]\label{lem_cov_derivative}
 In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
@@
 %relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
-\begin{lemma}\label{prop_model_shift}
+\begin{claim}\label{prop_model_shift}
 	In the setting of Theorem \ref{thm_model_shift},
@@
 	\end{align*}
-	Then we have whp,
+	Then we have w.h.p.
 	\begin{align*}
@@
 %	\end{align*}
-\end{lemma}
+\end{claim}
 

### 2020-06-09 writeup/proofs_sec3.tex
merge
minor

@@
-\section{Extended Related Work}
+\section{Extended Background and Related Work}\label{app_proof_sec3}
 
-McNamara and Balcan \cite{NB17}
-
-Bullins et al. \cite{BHKL19}
-
-Cavallanti et al. \cite{CCG10}
-
-Daume and Marcu \cite{DM06}
-
-Zhao et al. \cite{ZD19}
-
-\section{Missing Details of Problem Formulation}\label{app_proof_sec3}
+%\section{Missing Details of Problem Formulation}
 
@@
 
-Throughout the appendix, we shall say an event $\Xi$ holds with high probability (whp) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
 Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
@@
 for the rest of the section, we shall consider the case of two tasks with $r=1$. 
-Then equation \eqref{eq_mtl} simplifies to 
+For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to 
 \begin{align}\label{eq_mtl_2task}
@@
 	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
-	&= \frac{1}{w_2}\left[\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+	&= \frac{1}{w_2}\left[\beta_2 + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
 \nonumber
@@
 With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
-Here we assume that $N_1$ and $N_2$ satisfies $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
-Then we define the validation loss as
+We assume that $N_1$ and $N_2$ satisfy $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
+Then we write the validation loss in \eqref{eq_mtl_eval} as
 \begin{align}\label{eq_mtl_2tasktilde}
-	\wt f(\hat B; w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
+	g(w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
 \end{align}
-Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that $\wt f$ only depends on the ratio $v:=w_1/w_2$. Hence we will also write $\wt f(\hat B; v)$ in the following discussion.
+Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that $g$ only depends on the ratio $v:=w_1/w_2$. Hence we will also write $g(v)$ in the following discussion.
 
-Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $\wt f(\hat B; v)$. We will define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_t^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2), \]
-	where $t=2$ since we are considering the two task case, and it also stands for the ``target task". 
-The intuition for deriving $\hat{\beta}_t^{\MTL}$ is akin to performing multi-task training in practice.
+Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$. We will define the multi-task learning estimator for the target task as
+	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
+%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task". 
+The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
 %Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-Then the test loss of using $\hat{\beta}_t^{\MTL}$ for the target task is
+Then the test loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
 \begin{align}
-	\te(\hat{\beta}_t^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
+	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
 			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
@@
 \begin{align*}
-	L(\hat{\beta}_t^{\STL}) = \sigma_2^2 \cdot \bigtr{\Sigma_2(X_2^{\top}X_2)^{-1}}, \ \text{ where } \ \hat{\beta}_t^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
+	L(\hat{\beta}_2^{\STL}) = \sigma_2^2 \cdot \bigtr{\Sigma_2(X_2^{\top}X_2)^{-1}}, \ \text{ where } \ \hat{\beta}_2^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
 \end{align*}
@@
 
-One may observe that we can reduce $\wt f$ to an expression that is easier to handle using concentration of random vectors with i.i.d.
-entries.
-Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-
-Now suppose $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
-$$	\wt f(\hat B; v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
+In fact using concentration of random vectors with i.i.d. entries, we can reduce $g$ to an expression that is easier to handle. 
+%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+Suppose $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
+$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
 Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d.
-centered entries, we can use the concentration estimate, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
+centered entries, we can use the concentration result, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
 \begin{align*}
@@
 with high probability. Thus we obtain that 
-$$\wt f(B; v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
 where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using 
- again the concentration result, Lemma \ref{largedeviation}, we obtain that
-$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(\hat B; v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+ again the concentration result, Lemma \ref{largedeviation}, we get that
+$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
 with high probability, where
 \begin{align*}
-		&\val(\hat{B}; v):= \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
+		&\val(v):= \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
 	&=  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
@@
 %------------------
-In sum, we have obtained that 
+Thus we conclude that 
 \be\label{approxvalid}
-\wt f(\hat B; v)=  \left[\val(\hat{B}; v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
+g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
 \ee
-Hence to minimize $\wt f$, it suffices to minimize $\val(\hat{B}; v)$ over $v$.
+Hence to minimize $g$, it suffices to minimize $\val(v)$ over $v$.
+
+\textbf{Extended related work.}
+McNamara and Balcan \cite{NB17}
+
+Bullins et al. \cite{BHKL19}
+
+Cavallanti et al. \cite{CCG10}
+
+Daume and Marcu \cite{DM06}
+
+Zhao et al. \cite{ZD19}

### 2020-06-09 writeup/proof_main.tex
minor
revisions

@@
 
-We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$.
-The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p\to \infty$.
+We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$ for $t=2$.
+The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$ as $p\to \infty$.
 When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
 Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
@@
 	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
 Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
@@
 \end{lemma}
-
-\textbf{Proof Overview.} We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
-We use the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
-Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
-In particular, when $z=0$, $\tr[R_\infty(0)]$ gives the expression inTheorem \ref{lem_cov_shift_informal}.
-The details can be found in Appendix \ref{sec_maintools} and \ref{sec_Gauss}.
 
@@
 
-The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}.
+\textbf{Proof Overview.} 
+%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
+The proofs of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} are based on the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
+Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
+In particular, when $z=0$, $\tr[\Sigma_2^{-1/2}A\Sigma_2^{-1/2}R_\infty(0)]$ gives the limit in \eqref{lem_cov_shift_eq}.
+On the other hand, we can write 
+$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2= \beta^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} \beta.$$ 
+Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+
+%expression inTheorem \ref{lem_cov_shift_informal}. ........ The details can be found in Appendix \ref{sec_maintools} and \ref{sec_Gauss}.
+
+%The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}. 
 We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
@@
 
-In this section, we state and prove the formal version of Theorem \ref{thm_main_informal}, which covers the two tasks case with $t=2$.
-In this section, we consider the case where the entries of $\e_1$ and $\e_2$ have the same variance $\sigma_1^2=\sigma_2^2=\sigma^2$.
+For the rest of this section, we shall state and prove the formal version of Theorem \ref{thm_main_informal}.
+%We shall consider the case where the entries of $\e_1$ and $\e_2$ have the same variance $\sigma_1^2=\sigma_2^2=\sigma^2$.
 %Moreover, we shall denote $\beta_1$ and $\beta_2$ by $\beta_1$ and $\beta_2$, standing for ``source task" and ``target task", respectively. 
-
 First, we introduce several quantities that will be used in our statement, and they are also related to the quantities in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
@@
 entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2}. With high probability, we have
+Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2} with $\sigma_1^2=\sigma_2^2=\sigma^2$. Then with high probability, we have
 	\begin{align}

### 2020-06-09 writeup/proof_main.tex
revise

@@
 $$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2= \beta^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} \beta.$$ 
-Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-
-%expression inTheorem \ref{lem_cov_shift_informal}. ........ The details can be found in Appendix \ref{sec_maintools} and \ref{sec_Gauss}.
+Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}. The details can be found in Appendix \ref{sec_maintools}.
 
@@
 First, we introduce several quantities that will be used in our statement, and they are also related to the quantities in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-Given the optimal ratio $\hat v$, let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix, and ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ be the eigenvalues of $\hat{M}^{\top}\hat{M}$.
-Define $(\hat a_1, \hat a_2)$ as the solution to the following system of deterministic equations,
+Given the optimal ratio $\hat v$,
+%let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix, and ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ be the eigenvalues of $\hat{M}^{\top}\hat{M}$.
+Define
+let $(\hat a_1, \hat a_2)$ be the solution to the following system of deterministic equations,
 	\be
-		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat \lambda_i^2 \hat a_1}{ \hat \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
+		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat v^2 \lambda_i^2 \hat a_1}{ \hat v^2 \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
 		 \ee
@@
 where we denoted
-$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat \lambda_i^{2k}}{ (\hat a_2 +\hat  \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
+$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat v^{2k} \lambda_i^{2k}}{ (\hat a_2 +\hat v^2 \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
 Then we introduce the following matrix
-\be\label{defnpihat}\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat  a_1 \hat {M}^{\top}\hat {M}+\hat a_2 )^2} \hat {M}^{\top}.\ee
+\be\label{defnpihat}\Pi \equiv \Pi(\hat v)= \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot \hat v^2{M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat v^2 {M}^{\top} {M}}{(\hat  a_1 \hat v^2{M}^{\top} {M}+\hat a_2 )^2} {M}^{\top}.\ee
 %which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
@@
 Finally, we introduce the error term
-\be\label{eq_deltaextra}\delta\equiv \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\lambda_{\min}^2(\hat M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2,\ee
-where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. Note that this factor converges to 0 as $\rho_1$ increases.
+\be\label{eq_deltaextra}\delta\equiv \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\hat v^2\lambda_{\min}^2(M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2.\ee
+%where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. 
+Note that this factor converges to 0 as $\rho_1$ increases.
 
@@
 	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta, \label{lower}
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta(\hat v) \label{upper}\\
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta(\hat v), \label{lower}
 	\end{align}
@@
 	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}} } \label{Deltavarv} \\
-		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat v^2 M^{\top}M + \hat a_2\id)^{-1}} } \label{Deltavarv} \\
+		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi (\hat v)\Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
 	\end{align}
@@
 Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi}.$
-	Then we have
+		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}.$
+	Then we have with high probability,
 		\begin{align*}
@@
 
-Now we give the proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+The proof of Theorem \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any fixed $\e>0$, we have
+\begin{align}
+\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq {n_1^{-1}}{Z_1^T Z_1}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e}) \quad \text{w.h.p.}  \label{eq_isometric}
+\end{align}
+%with high probability. 
+In fact, $Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
+For the estimate \eqref{eq_isometric} we used \cite[Theorem 2.10]{isotropic} to get a stronger probability bound.
 
@@
 \end{align*}
-The proof is divided into the following four steps. 
+We introduce the notation $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for $v\in \R$. Then the proof is divided into the following four steps. 
 \begin{itemize}
-\item[(i)] We first consider $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a fixed $v\in \R$.
+\item[(i)] We first consider $ \hat M(v)$ for a fixed $v\in \R$.
 Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
@@
 
-\item[(ii)] Using the approximate isometry property of $X_1$ (see \eqref{eq_isometric} below), we will bound the bias term $ \delta_{\bias}(v)$
+\item[(ii)] Using the approximate isometry property of $Z_1$ in \eqref{eq_isometric}, we will bound the bias term $ \delta_{\bias}(v)$
 %$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - {v} \beta_2)}^2$$
@@
 
-\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M= \hat v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for a possibly random $\hat v$ which depends on $Y_1$ and $Y_2$.
+\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M(\hat v)$ for a possibly random $\hat v$ which depends on $Y_1$ and $Y_2$.
 \end{itemize}
 
-\paragraph{Step I: Variance reduction.} Let $\hat M= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for any fixed constant $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
+\paragraph{Step I: Variance reduction.} Consider $\hat M(v)$ for any fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
 $$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
@@
 $$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
-with high probability, where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2}. Combining them, we get 
-\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{whp},
+with high probability, where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2} with $\hat v$ replaced by $v$. Combining them, we get 
+\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
 \ee 
@@
 \paragraph{Step II: Bounding the bias term.}
-In this step, we shall use the following the following bounds on the singular values of $Z_1$: for any fixed $\e>0$, we have
-\begin{align}
-\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq \frac{Z_1^T Z_1}{n_1}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e})   \label{eq_isometric}
-\end{align}
-with high probability.
-In fact, $Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its nonzero eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
-For the estimate \eqref{eq_isometric} we used \cite[Theorem 2.10]{isotropic} to get a stronger probability bound.
-
-Next we shall use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$ in \eqref{deltabetapf}.  
+Next we use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$. %in \eqref{deltabetapf}.  
 %relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
@@
 		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
-		\delta_{\e}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
+		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
 	\end{align*}
@@
 		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_\e.
+		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}.
 	\end{align*}
@@
 	Using \eqref{eq_isometric}, we can bound  
-	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{whp}.$$
+	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{w.h.p.}$$
 	Thus we can estimate that 
@@
 \begin{align*}
-&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} = \hat M\frac{1}{(\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^2}\hat M^\top \\
-&\preceq  n_1^2 \hat M\frac{1}{\left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^2}\hat M^\top \\
+&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} =n_1^2 \hat M (\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^{-2}\hat M^\top \\
+&\preceq  n_1^2 \hat M \left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^{-2}\hat M^\top \\
 &\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + 2\left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
-&\prec [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
+&\preceq [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
 \end{align*}
-for some small enough constant $c>0$. Together with Lemma \ref{prop_model_shift}, we get with high probability,
+for some small enough constant $c>0$. Together with Claim \ref{prop_model_shift}, we get with high probability,
 \be\label{bounddelta-}
@@
 \ee
-for some small constant $c>0$, where recall $\delta(v)$ defined in \eqref{eq_deltaextra}.
+for some small constant $c>0$, where we recall $\delta(v)$ defined in \eqref{eq_deltaextra}.
 
@@
 \end{align*}
-with high probability. Together with and \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that whp,
+with high probability. Together with and \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that w.h.p.,
 \be\label{dicho_varbeta}
@@
 
-\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result to $v=\hat v$, which is random and depends on $X_1$ and $X_2$.
+\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result \eqref{dicho_varbeta} to $v=\hat v$, which is random and depends on $X_1$ and $X_2$.
 We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{dicho_varbeta}
 %\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
-holds uniformly for all $v\in [-C_0, C_0]$. In fact, for a large constant $C_1>0$, we consider $v$ belonging to a discrete set 
+holds uniformly for all $v\in [-C_0, C_0]$. In fact, we consider $v$ belonging to a discrete set 
 $$V:=\{v_k = kp^{-1}: -(C_0p +1)\le k \le C_0p +1\}.$$
@@
 $$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }-C_0\le v \le C_0\}$$
-holds with high probability. On the other hand, on $\Xi_1$ one can see that for any small constant $\e>0$,
+holds with high probability. On the other hand, on $\Xi_1$ one can see that for any small constant $\e>0$, there exists a large enough constant $C_0>0$ depending on $\e$ such that
 \begin{align*}
@@
 \end{align*}
-for all $v\ge C_0$ as long as $C_0$ is chosen large enough depending on $\e$.
+for all $v\ge C_0$.
 Similar estimates hold for $v\le -C_0$ if we replace $C_0$ with $-C_0$ in the above estimates.
@@
 One can see from the above proof that the main error, $\delta$, of Theorem \ref{thm_model_shift} comes from approximating $\delta_{\bias}$ by $\wt\delta_{\bias}$ in \eqref{bounddelta-}.
-In order to improve this estimate and obtain an exact asymptotic result as for the $\delta_{\vari}$ term, one needs to study the singular value distribution of the following random matrix:
+In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
 $$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  {v}^2 .$$
@@
 \begin{align*}
-v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
+v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
 \end{align*}
-Recalling that $\Sigma_1=\id$ and bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
+Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
 \be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
@@
 $$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim 1$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get 
+Note that $\delta^\star_{\bias}(v) \sim p$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get 
 \be\label{replaceest}

### 2020-06-09 writeup/proof_examples.tex
sec 3
revise

@@
 \begin{align}
-	\val(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	\val_\star(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 %\cor Under the setting of Lemma \ref{prop_model_shift_tight}, 
-For the isotropic model with $\sigma_1^2=\sigma_2^2=\sigma^2$, using concentration for random vectors with i.i.d.
-entries, Lemma \ref{largedeviation}, we can obtain that $\val(\hat{B}; w_1, w_2)= \val(v) \cdot \left( 1+\OO(p^{-1/2+\e})\right)$.
+For the isotropic model, using the concentration result for random vectors with i.i.d.
+entries, Lemma \ref{largedeviation}, we can obtain that $\val(v)= N_2\cdot \val_\star(v)  \left( 1+\OO(p^{-1/2+\e})\right)$.
 Hence the validation loss in \eqref{approxvalid} reduces to
 \be\label{boundv-w}
-\wt f(\hat B; v)=\left[N_2\cdot \val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
+g(v)=\left[N_2\cdot \val_\star(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
 \ee
 with high probability for any constant $\e>0$.
-\nc Thus for the following discussions, it suffices to focus on the behavior of $\val (v)$.
-Let $\hat w$ the minimizer of $\val(v)$.
-The proof will consist of two main steps.
+\nc Thus for the following discussions, it suffices to focus on the behavior of $\val_\star (v)$.
+Let $\hat w$ the minimizer of $\val_\star(v)$.
+The proof will consist of two steps.
 \begin{itemize}
@@
 %Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
-For the isotropic model, the minimizer for $\val(v)$ satisfies
-	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{whp}\ee
+For the isotropic model, the minimizer for $\val_\star(v)$ satisfies
+	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{w.h.p.}\ee
 	for some constant $C>0$.
@@
 To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof.
-First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$.
+First it is easy to observe that $\val_\star(w)< \val_\star(-w)$ for $w> 0$.
 Hence it suffices to assume that $w\ge 0$.
@@
 \begin{align}
-	\val(w) &=  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	\val_\star(w) &=  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 $$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
-are increasing functions in $w$. Hence taking derivative of $\val(w)$ with respect to $w$, we obtain that
+are increasing functions in $w$. Hence taking derivative of $\val_\star(w)$ with respect to $w$, we obtain that
 \begin{align*}
-\val'(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
+\val'_\star(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
 +&~ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 $$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
-Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$.
+Hence $\val'_\star(w)>0$ on $(w_1,\infty)$, i.e. $\val_\star(w)$ is strictly increasing for $w>w_1$. This gives $\hat w\le w_1$.
 
-Then we consider the case $w\le 1$, and the proof is similar as above. Taking derivative of $\val(w)$, we obtain that
+Then we consider the case $w\le 1$, and the proof is similar as above. Taking derivative of $\val_\star(w)$, we obtain that
 \begin{align}
-	\val'(w) &\le \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	\val'_\star(w) &\le \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 $$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
-Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly decreasing for $w<w_2$. Hence we must have $\hat w\ge w_2$.
+Hence $\val'_\star(w)<0$ on $[0,w_2)$, i.e. $\val_\star(w)$ is strictly decreasing for $w<w_2$. This gives $\hat w\ge w_2$.
 
@@
 
-For the rest of this section, we choose the parameters that satisfy the following relations: \be\label{choiceofpara}
+For the rest of this section, we choose parameters that satisfy the following relations: \be\label{choiceofpara}
 pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 ,
@@
 %\begin{proof}
- In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-\hat w| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'(w)|\gtrsim p d^2$.
+ In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'_\star(w)|\gtrsim p d^2$.
 Moreover, under the choice \eqref{choiceofpara} we have
-$$\val(w) =\OO(pd^2),\quad \text{for}\quad   |w-\hat w|\le 2C\cal E.$$  
-Thus we obtain that for $|w-\hat w|\ge 2C\cal E$,
-$$\left|\val(w) - \val(\hat w)\right|\ge |\val(w)-\min(\val(w_1),\val(w_2))|\gtrsim pd^2 \cal E \gtrsim \cal E \cdot \val(\hat w),$$
-which leads to $\wt f(\hat B; w) > \wt f(\hat B; \hat w)$ whp by \eqref{boundv-w}.
-Thus $w$ cannot be a minimizer of $\wt f(\hat B; v) $, and we must have $|\hat v - \hat w|\le 2C\cal E$.
-Together with \eqref{hatw_add1}, we conclude \eqref{hatv_add1}.
+$$\val_\star(w) =\OO(pd^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$  
+Thus we obtain that for $|w-1|\ge 2C\cal E$,
+$$\left|\val_\star(w) - \val_\star(\hat w)\right|\ge |\val_\star(w)-\min(\val_\star(w_1),\val_\star(w_2))|\gtrsim pd^2 \cal E \gtrsim \cal E \cdot \val_\star(\hat w),$$
+which leads to $g(w) > g(\hat w)$ w.h.p.
+by \eqref{boundv-w}.
+Thus $w$ cannot be a minimizer of $g(v)$, and we must have $|\hat v - 1|\le 2C\cal E$.
+%Together with \eqref{hatw_add1}, we conclude \eqref{hatv_add1}.
 %\end{proof}
 
-Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$ again, we get whp,
+Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$ again, we get w.h.p.,
 \begin{align}
-\te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
+\te(\hat{\beta}_2^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
 &+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
@@
 $$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim \frac{p}{n_1+n_2}.$$
-Hence we need to choose that $p\cdot d^2 \sim \sigma^2$.
+Hence we need to choose that $p d^2 \sim \sigma^2$.
 On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$.
@@
 \end{align}
-whp for some constant $\e>0$.
+w.h.p. for some constant $\e>0$.
 
 With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
-With slight abuse of notations, we shall write $\hat a_i$, $\hat b_k$ and $\hat M$ as $a_i$, $b_k$ and $M$ throughout the rest of this section.
+With slight abuse of notations, we shall write $\hat a_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.
 
@@
 	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
-Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
+Then solving equations \eqref{eq_a12extra} and \eqref{eq_a34extra} with $\lambda_i=1$, we get that
 	\begin{align}
@@
 	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
-	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of it) that
+	we can get from Lemma \ref{prop_model_shift_tight} (or rather its proof) that
 \be\label{Deltabeta} 
@@
 	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
-Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$, it gives the first statement of Proposition \ref{prop_dist_transition}.
+Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$ and $\nu\ge \al_+^2(\rho_1) +  \oo(1) $, it gives the first statement of Proposition \ref{prop_dist_transition}.
 
@@
 	\begin{itemize}
-		\item If $\sigma_1^2 < - \gamma_+^{1/2} \rho_1 \cdot p d^2+\left(1+ \gamma_+^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
-		\item If $\sigma_1^2 > -\gamma_-^{1/2}\rho_1\cdot p d^2   +\left(1+ \gamma_-^{-1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then whp $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
+		\item If $\sigma_1^2 < - \nu^{1/2} \rho_1 \cdot p d^2+\left(1+ \nu^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
+		\item If $\sigma_1^2 > -\nu^{-1/2}\rho_1\cdot p d^2   +\left(1+ \nu^{1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
 	\end{itemize}
@@
 
-\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
+\begin{proof}%[Proof of Proposition \ref{prop_var_transition}]
+\todo{check!}In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
 %the validation loss and the test error become
@@
 \ee
-then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
+then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
 \begin{align*}
@@
 \end{align*}
-This proves the first claim of Proposition \ref{prop_var_transition} for positive transfer.
+This proves the first claim of Proposition \ref{prop_var_transition} for positive transfer. \cor $\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$\nc
 
@@
 \ee
-then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ whp, which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
+then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
 \begin{align*}
@@
 \begin{proof}[Proof of Proposition \ref{prop_data_size}]
-Following the above proof of Proposition \ref{prop_dist_transition}, we see that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ whp if \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ whp if \eqref{neg1} holds.
+Following the above proof of Proposition \ref{prop_dist_transition}, we see that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ w.h.p.
+if \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ w.h.p.
+if \eqref{neg1} holds.
 %\be\label{pos1}
 %pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
-%and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ whp if
+%and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ w.h.p. if
 %\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
-%then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ whp.
+%then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ w.h.p..
 
@@
 % $$ \Psi(\beta_1,\beta_2) \ge \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
-% then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds whp.
+% then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds w.h.p..
 Plugging into $\rho_1>50$, we obtain the first statement.
@@
 \ee
-On the other hand, using Lemma \ref{lem_minv} we have whp,
+On the other hand, using Lemma \ref{lem_minv} we have w.h.p.,
 \be\label{reduceproof2} 
@@
 %--------end old argument---------
+
+\iffalse
 In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
@@
 %It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. 
-After solving these, with \eqref{gvar_extra} we get that whp,
+After solving these, with \eqref{gvar_extra} we get that w.h.p.,
 \be\label{testcomple}
@@
 \end{proof}
+\fi
 %\todo{add a transition example}

### 2020-06-10 writeup/proof_examples.tex
revise

@@
 \begin{proof}%[Proof of Proposition \ref{prop_var_transition}]
-\todo{check!}In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
+In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
 %the validation loss and the test error become
@@
 %where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
-In the isotropic model, using again the concentration of random vector with i.i.d. entries, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
+In the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
 \begin{align*}
@@
 %We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
-Thus under the choice parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
+Thus under the choice of parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
 \be \label{simple2}
@@
 \ee
-Then we write 
+Then we have 
 $$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
@@
 $$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
-satisfies \eqref{Deltavar} but with $\sigma^2$ replaced with $\sigma_2^2$, 
+satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$, 
 $$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
-satisfies \eqref{Deltabeta}, and 
+satisfies \eqref{Deltabeta}, and $\delta_{\vari}^{(2)}$ is defined as
 \begin{align*}	
@@
 \be\label{Deltavar2} 
-\al_-(\rho_1) - \oo(1)  \le \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
+\al_-(\rho_1) - \oo(1)  \le  {\delta_{\vari}^{(2)}}/{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
 where 
@@
 
-Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ means the we have $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
+Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
 Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
@@
 \end{align*}
-This proves the first claim of Proposition \ref{prop_var_transition} for positive transfer. \cor $\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$\nc
+This proves the first claim of Proposition \ref{prop_var_transition} using $\nu\ge \al_+^2(\rho_1) +  \oo(1) $.
 
@@
 \end{align*}
-This proves the second claim of Proposition \ref{prop_var_transition} for negative transfer.
+This proves the second claim of Proposition \ref{prop_var_transition}.
 \end{proof}
@@
 \begin{proof}[Proof of Proposition \ref{prop_data_size}]
-Following the above proof of Proposition \ref{prop_dist_transition}, we see that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ w.h.p.
+Following the proof of Proposition \ref{prop_dist_transition}, we see that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ w.h.p.
 if \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ w.h.p.
@@
 \begin{align}\label{pos1solv}
- &  \Psi(\beta_1,\beta_2) \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}   < \gamma_+^{-1} .
+ &  \Psi(\beta_1,\beta_2) \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}   < \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1} .
  \end{align}
- then we can solve \eqref{pos1solv} to get
- \be\label{addconstraint}\rho_1 < \frac{\rho_2-2}{\Psi(\beta_1,\beta_2) \cdot \gamma_+ (\rho_2 - 1) - 1}  .\ee
+ Then we can solve \eqref{pos1solv} to get
+ \be\label{addconstraint}\rho_1 < \frac{\rho_2-2}{\Psi(\beta_1,\beta_2) \cdot (\rho_2 - 1)\left( \al_+^2(\rho_1) +  \oo(1) \right) - 1}  .\ee
  %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
- This gives the first statement of Proposition \ref{prop_data_size}. %Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.
+ This gives the first statement of Proposition \ref{prop_data_size} using $\nu\ge \al_+^2(\rho_1) +  \oo(1) $.
+%Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.
 
  Note that if we require the RHS of \eqref{addconstraint} to be larger than $40$, that is, \eqref{addconstraint} is not a null condition. Then together with \eqref{explainpsi}, we get
- $$ \rho_2 - 2>( 2\gamma_+ -1)\rho_1 .$$
+ $$ \rho_2 - 2>\left[ 2\left( \al_+^2(\rho_1) +  \oo(1) \right)  -1\right]\rho_1 .$$
 Plugging into $\rho_1>40$, we get $\rho_2 \ge 106$. This gives a constraint on $\rho_2$.
@@
 \begin{align}\label{neg1solv}
- & \Psi(\beta_1,\beta_2)  \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) >  \Psi(\beta_1,\beta_2)  \cdot \frac{(\rho_2-1.5) \rho_1 }{\rho_1+\rho_2-2}> \gamma_-^{-1} .
+ & \Psi(\beta_1,\beta_2)  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) >  \Psi(\beta_1,\beta_2) \frac{(\rho_2-1.5) \rho_1 }{\rho_1+\rho_2-2}> \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} .
  \end{align}
@@
  \be\label{addconstaint2}
- \rho_1 > \frac{(\rho_2-2) \sigma^2}{\Psi(\beta_1, \beta_2) \cdot \gamma_-(\rho_2 - 1.5)  - 1}  ,
+ \rho_1 > \frac{(\rho_2-2) \sigma^2}{\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)  - 1}  ,
  \ee
 which gives the second statement of Proposition \ref{prop_data_size}.
-We remark that condition \eqref{explainpsi} implies $\Psi(\beta_1, \beta_2) \cdot \gamma_-(\rho_2 - 1.5)>1$, so \eqref{addconstaint2} does not give a trivial bound. 
+We remark that condition \eqref{explainpsi} implies $\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)>1$, so \eqref{addconstaint2} does not give a trivial bound. 
  \end{proof}
 
-Next we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for taskonomy.
+Next we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
 %In the statement, we shall denote the data efficiency ratio as $\al^\star$.
 
-\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
+\begin{proposition}%[Labeled data efficiency]
+\label{prop_data_efficiency}
 	In the isotropic model, assume that $\rho_1,\rho_2 \ge 9$ and $\Psi(\beta_1, \beta_2) < (5(\rho_1-1))^{-1} + (5(\rho_2-1))^{-1}$.
@@
 
-\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
+\begin{proof}%[Proof of Proposition \ref{prop_data_efficiency}]
 Suppose we have reduced number of datapoints---$x n_1$ for task 1 and $x n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
@@
 		 a_1 = \frac{\rho_1(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(x\rho_1 + \al\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,  \\
+		& a_2 = \frac{\rho_2(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,  \\
 		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}, \quad
@@
 \ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain the lower bound $x^*\ge x_l $. 
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain the lower bound $x^\star\ge x_l $. 
 %where
@@
 $$ \frac{2\sigma^2}{x (\rho_1+\rho_2) - 1} > \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
-that is, $\te_1(\hat{\beta}(\alpha)) + \te_2(\hat{\beta}(\alpha))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\bias}$.
+that is, $\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\bias}$.
 
-Then we try to obtain an upper bound on $x^*$.
+Then we try to obtain an upper bound on $x^\star$.
 In the following discussions, we only consider $x$ such that $x> x_l$.
@@
 
-\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^*\le x$ if $x$ satisfies 
+\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies 
 \be\nonumber
@@
 \ee
-With $x\rho\ge \min(\rho_1,\rho_2)>9$, we can get the simple bound
+With $x\rho\ge \min(\rho_1,\rho_2)\ge 9$, we can get the simple bound
 $$\frac{1+\oo(1)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4 < 5. $$
@@
 %that is, we have positive transfer when using all the data, then 
-from which we can solve for the following upper bound on $\al^*$:
+from which we can solve for the following upper bound on $x^\star$:
 \begin{align*}
-\al^* &<  \frac1{\rho} \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right)\Psi(\beta_1,\beta_2)}+ \frac1\rho .
+x^\star &<  \frac1{\rho} \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right)\Psi(\beta_1,\beta_2)}+ \frac1\rho .
 %\\
@@
 %\noindent{\bf The lower bound.} 
-From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^*\ge x$ if $x$ satisfies
+From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\ge x$ if $x$ satisfies
 \be\label{solval2}
@@
 %then we have negative transfer for all choice of $0\le \al \le 1$; otherwise, 
-from which we can solve for the following lower bound on $x^*$:
+from which we can solve for the following lower bound on $x^\star$:
 \begin{align*}
-x^* &>  \frac1\rho \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)}+ \frac1\rho .
+x^\star &>  \frac1\rho \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)}+ \frac1\rho .
 \end{align*}
@@
 We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v} we can show that \eqref{hatv_add1} holds.
+With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
 Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
@@
 \ee
-Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $\lambda(M_0^\top M_0)\ge \mu_{\min}^2$, we obtain that with high probability,
+Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
 \begin{align}\label{approximateteM}

### 2020-06-10 writeup/proof_extension.tex
sec 3
revise

@@
-\section{Proofs for the Extended Results}
+%\section{Proofs for the Extended Results}
 
-\subsection{Many Tasks with the Same Covariate}\label{app_proof_many_tasks}
+\section{Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_many_tasks}
 
@@
 Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use concentration to get the validation loss as
-\be\label{eq_multival}\wt f(\hat B; \cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
+\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
 Here $\val(\cal W)$ is defined as
@@
 	\end{align*}
-It suffices to minimize $\delta_{\bias}(\cal W)$ over $\cal W$, since both $t N \sigma^2$ and $\delta_{\vari}(\cal W)$ do not depend on the weights.
+It suffices to minimize $\delta_{\bias}(\cal W)$ over $\cal W$, since both $t \sigma^2$ and $\delta_{\vari}$ do not depend on $\cal W$.
 
@@
 	\begin{align*}
-		\delta_{\bias}(\cal W)= \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
+		\delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
 	\end{align*}
-	From this equation we can solve the minimizer optimally as $Q_0=U_{r}U_r^{\top}$.
-On the other hand, let $\hat {\cal W}$ be the minimizer of $\wt f$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
+	From this equation we can solve the minimizer optimally as $Q_0\equiv  \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=U_{r}U_r^{\top}$.
+On the other hand, let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
 We claim that $\hat Q$ satisfies
-	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\| = \oo(1) \quad \text{whp}.\ee
+	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\| = \oo(1) \quad \text{w.h.p.}\ee
 	In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by \eqref{eq_isometric}, we obtain that
-	$$   \val(\hat {\cal W}) + t  \sigma^2 > (\val( {\cal W}_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ \wt f(\hat B; \hat{\cal W})>\wt f(\hat B; {\cal W}_0),$$
+	$$   \val(\hat {\cal W}) + t  \sigma^2 > (\val( {\cal W}_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
 	that is, $\hat {\cal W}$ is not a minimizer. This leads to a contradiction.
@@
 	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_2 \right) }^2
+		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
 		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_2}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
 	\end{align*}
@@
 %\end{itemize}
-
-\input{proof_taskonomy.tex}

### 2020-06-10 writeup/proof_main.tex
revise

@@
 %with high probability. 
-In fact, $Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
-For the estimate \eqref{eq_isometric} we used \cite[Theorem 2.10]{isotropic} to get a stronger probability bound.
+In fact, $n_1^{-1}Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
+The estimate \eqref{eq_isometric} has stronger probability and error bounds, and we refer the reader to Lemma \ref{SxxSyy} below for the proof.
+% we used \cite[Theorem 2.10]{isotropic} to get a stronger probability bound.
 

### 2020-06-10 writeup/proof_examples.tex
supp wip

@@
 
-\subsection{Missing Proofs of Section \ref{sec_similarity}}\label{app_proof_31}
+\subsection{Missing Proofs for Task Similarity}\label{app_proof_31}
 
@@
 
-\subsection{Missing Proofs of Section \ref{sec_data_size}} \label{app_proof_32}
+\subsection{Missing Proofs for Sample Size} \label{app_proof_32}
 We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.
@@
 
-\subsection{Missing Proofs of Section \ref{sec_covshift}}\label{app_proof_33}
+\subsection{Missing Proofs for Covariate Shift}\label{app_proof_33}
 

### 2020-06-10 writeup/proofs_sec3.tex
app wip

@@
+\textbf{Organizations.}
+The appendix is organized as follows.
+In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
+In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
+In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
+In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
+In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
+Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.
+
 \section{Extended Background and Related Work}\label{app_proof_sec3}
 
+We restate our linear regression setting, in particular the moment assumption required by our random matrix model.
+We then derive a closed-form solution of the multi-task estimator that is defined in Section \ref{sec_prelim}.
+Finally, we describe further related work that is covered in the main text.
 %\section{Missing Details of Problem Formulation}

### 2020-06-10 writeup/proof_examples.tex
app wip
sec ABC

@@
-\section{Proofs for Isotropic and Covariate Shifted Settings}
+\section{Proofs for Isotropic and Covariate Shifted Settings}\label{app_iso_cov}
 
-\subsection{Missing Proofs for Task Similarity}\label{app_proof_31}
-
-%For the case $\sigma_1^2=\sigma_2^2=\sigma^2$, 
+For the isotropic model, we will use Lemma \ref{prop_model_shift_tight} to analyze the bias-variance tradeoff.
+Our main observation is that the optimum of $\val(v)$ is approximately $1$.
+This allows us to simplify the bias and variance bounds significantly.
 We define the function
@@
 
+\subsection{Missing Proofs regarding Task Similarity}\label{app_proof_31}
+
 With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
@@
 \end{proof}
-
-%\subsection{Labeled data de-noising}\label{app_proof_data}
 
@@
 
-\subsection{Missing Proofs for Sample Size} \label{app_proof_32}
+\subsection{Missing Proofs regarding Sample Size} \label{app_proof_32}
 We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.
@@
 
-\subsection{Missing Proofs for Covariate Shift}\label{app_proof_33}
+\subsection{Missing Proofs regarding Covariate Shift}\label{app_proof_33}
 

### 2020-06-10 writeup/proof_main.tex
supp wip
app wip
sec ABC

@@
-\section{Proof of Theorem \ref{thm_main_informal}}\label{app_proof_main_thm}
+\section{Proof for the Case of Two Tasks}\label{app_proof_main_thm}
 
@@
 
-\textbf{Proof Overview.} 
+\textbf{Proof overview.}
 %We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
@@
 
-\begin{theorem}\label{thm_model_shift}
+\begin{theorem}[Restate of Theorem \ref{thm_main_informal}]\label{thm_model_shift}
 %For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
@@
 For the isotropic model in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
-\begin{lemma}\label{prop_model_shift_tight}
+\begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
 		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
@@
 In fact, $n_1^{-1}Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
-The estimate \eqref{eq_isometric} has stronger probability and error bounds, and we refer the reader to Lemma \ref{SxxSyy} below for the proof.
-% we used \cite[Theorem 2.10]{isotropic} to get a stronger probability bound.
+The estimate \eqref{eq_isometric} provides tight bounds for the concentration error.
+The result is formally stated in Lemma \ref{SxxSyy} in Section \ref{sec_maintools}.
 

### 2020-06-10 writeup/proofs_sec3.tex
sec ABC

@@
 
-\textbf{Assumptions on task data generation.}
+%\textbf{Assumptions on task data generation.}
 First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
 
-\begin{assumption}\label{assm_secA1}
+\begin{assumption}[Moment assumptions]\label{assm_secA1}
 We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrix, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
@@
 If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
-We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} below.
+We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} in Section \ref{sec locallaw1}.
 
 Then we make the following assumptions on the data models.
-\begin{assumption}\label{assm_secA2}
+\begin{assumption}[Linear regression model]\label{assm_secA2}
 For some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
-Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
+Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants.
+$\e_i\in \R^{n_i}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
 \end{assumption}
@@
 
-\textbf{The multi-task learning estimator.}
-From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
-for the rest of the section, we shall consider the case of two tasks with $r=1$. 
+Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
+From \cite{WZR20}, we know that we need to explicitly restrict the output dimension $r$ of $B$ so that there is transfer between the two tasks.
+Hence for the case of two tasks, we consider the setting where $r=1$.
 For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to 
@@
 \end{align}
-As a remark, when $w_1 = w_2 = 1$, we recover the linear regression estimator.
-The advantage of using $f(B; w_1, w_2)$ is that if $\beta_1$ is a scaling of $\beta_2$, then this case can be solved optimally using equation \eqref{eq_mtl_2task} \cite{KD12}.
+As a remark, when $w_1 = w_2 = 1$, we obtain linear regression.
+If $\beta_1$ is a scaling of $\beta_2$, then  $w_1, w_2$ can be scaled accordingly to fix both tasks more accurately than linear regression.
 
@@
 \end{align}
-Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that $g$ only depends on the ratio $v:=w_1/w_2$. Hence we will also write $g(v)$ in the following discussion.
+Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that the optimal solution of $g$ only depends on the ratio $v:=w_1/w_2$.
+Hence we overload the notation by writing $g(v)$ in the following discussion.
+The expectation of $g(v)$ can be written as follows.
+\begin{align*}
+		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
+	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
+	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
+		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
+		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{eq_val_mtl}
+\end{align*}
 
-Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$. We will define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
-%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task". 
-The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
-%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-Then the test loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
-\begin{align}
-	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
-			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
-\end{align}
-which is well-defined since it only depends on $\hat v$, but otherwise does not depend on $\hat w_1$ or $\hat w_2$ separately.
-Our goal is to study under model and covariate shifts, whether multi-task learning helps to learn the target task better than single-task learning.
-The baseline where we solve the target task with its own data is
-\begin{align*}
-	L(\hat{\beta}_2^{\STL}) = \sigma_2^2 \cdot \bigtr{\Sigma_2(X_2^{\top}X_2)^{-1}}, \ \text{ where } \ \hat{\beta}_2^{\STL} = (X_2^{\top}X_2)^{-1} X_2^{\top}Y_2.
-\end{align*}
-%Clearly, whether $\hat{\beta}_t^{\MTL}$ outperforms $\hat{\beta}_t^{\STL}$ depends on the covariate matrices, the difference of the task models, and the number of per-task data points.
-
-In fact using concentration of random vectors with i.i.d. entries, we can reduce $g$ to an expression that is easier to handle. 
+\begin{claim}
+	In the setting described above, we have that
+	\be\label{approxvalid}
+		g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
+	\ee
+\end{claim}
+\begin{proof}
+	We use the fact that our random vectors have i.i.d. entries.
 %Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-Suppose $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
+	Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
 $$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
@@
 $$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
-with high probability, where
-\begin{align*}
-		&\val(v):= \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
-	&=  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
-	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
-		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\		
-		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{eq_val_mtl}
-\end{align*}
+with high probability.
 %-----old-------
@@
 %------------------
-Thus we conclude that 
-\be\label{approxvalid}
-g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
-\ee
-Hence to minimize $g$, it suffices to minimize $\val(v)$ over $v$.
+Thus we conclude the proof.
+\end{proof}
+
+Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
+Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
+Now we can define the multi-task learning estimator for the target task as
+	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
+%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task". 
+%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
+%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
+The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
+\begin{align}
+	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
+			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
+\end{align}
+which is well-defined since it only depends on $\hat v$, but otherwise does not depend on $\hat w_1$ or $\hat w_2$ separately.
 

### 2020-06-10 writeup/app_exp.tex
fred comments
sec 4
restructure
sec 3
sec F

@@
-\section{Supplementary Materials for the Experiments}
+\section{Missing Details from the Experiments}\label{app_experiments}
 
-\begin{algorithm}[!t]
+\subsection{Synthetic Settings}\label{app_synthetic}
+	We describe the parameters used for producing Figure \ref{fig_model_shift_phasetrans}.
+	For all three simulations, we use dimension $p = 200$.
+	In Figure \ref{fig_model_shift}, we use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
+	The noise level is $\sigma = 5$.
+	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
+	The $x$-axis measure the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
+	In Figure \ref{fig_size}, we set $\kappa = 1$ and $d = 0.02$ for model distance.
+	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+	In Figure \ref{fig_covariate}, we set $\kappa = 1$ and $d = 0$.
+	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
+	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
+
+\subsection{Image and Text Classification Settings}\label{app_it}
+
+For the text classification experiment, we encode each word using the GLoVe word vectors.
+\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
+We apply an average pooling layer over the word embeddings.
+Then we add a multi-layer perception (MLP), LSTM, or CNN layer on top of the word embeddings \cite{lei2018simple}.
+
+\textbf{Single-task based metric.}
+
+\textbf{Incremental training schedule.}
+
+\begin{algorithm}[!h]
 	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
@@
 
-\subsection{Synthetic Settings}\label{app_synthetic}
-	In Figure \ref{fig_model_shift_phasetrans} (c), we plot the test error of the target task for $n_2 = 4p$ and $n_1$ ranging from $p$ to $20p$.
+\textbf{Theoretical validation.} We validate that MTL performs better when the source task is more similar to the target task.
+We show the result on the sentiment analysis tasks.
+For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+Figure \ref{fig_ab_sim} confirms the result.
+Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
 
-\subsection{Image and Text Classification Settings}
-
+\textbf{Further results on covariance alignment.}
 Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 	\centering
@@
 \end{figure}
-
-\textbf{Task similarity.} We validate that MTL performs better when the source task is more similar to the target task.
-We show the result on the sentiment analysis tasks.
-For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
-Figure \ref{fig_ab_sim} confirms the result.
-Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

### 2020-06-10 writeup/app_exp.tex
sec F

@@
 
-\textbf{Theoretical validation.} We validate that MTL performs better when the source task is more similar to the target task.
-We show the result on the sentiment analysis tasks.
-For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
-Figure \ref{fig_ab_sim} confirms the result.
-Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+\textbf{Theoretical validation.}
+
+%We validate that MTL performs better when the source task is more similar to the target task.
+%We show the result on the sentiment analysis tasks.
+%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+%Figure \ref{fig_ab_sim} confirms the result.
+%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
 %Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
 %Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
+%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
 
@@
 	\centering
-	\begin{subfigure}[b]{0.33\textwidth}
+	\begin{subfigure}[b]{0.48\textwidth}
 		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
 		\caption{Task pair TREC and CR}
 	\end{subfigure}\hfill
-		\begin{subfigure}[b]{0.33\textwidth}
+		\begin{subfigure}[b]{0.48\textwidth}
 		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
 		\caption{Task pair MR and SST}

### 2020-06-10 writeup/app_exp.tex
sec F

@@
 \textbf{Single-task based metric.}
+We simplify the setup of this experiment by fixing the sample sizes of every task pair.
+For sentiment analysis tasks, the source task uses xx training samples and the target task uses xx training samples for every task pair.
+For image classification tasks, the training sample size is 10,000 for every task.
 
@@
 
+\iffalse
 \textbf{Further results on covariance alignment.}
-Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.
+%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
 
@@
 	\end{subfigure}
-	\caption{The performance of aligning task covariances depends on data size.
-As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
+	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
+	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
+We suspect that this happens because of overfitting on the extra parameters in the additional covariance alignment module.}
 	\label{fig_covariate_app}
 \end{figure}
+\fi

### 2020-06-11 writeup/app_exp.tex
sec F

@@
 We simplify the setup of this experiment by fixing the sample sizes of every task pair.
-For sentiment analysis tasks, the source task uses xx training samples and the target task uses xx training samples for every task pair.
+For sentiment analysis tasks, the source task uses xx training samples and the target task uses $1000$ training samples for every task pair.
 For image classification tasks, the training sample size is 10,000 for every task.
@@
 \textbf{Incremental training schedule.}
+For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train} below to a round-robin training schedule baseline.
+We set the parameters of Algorithm \ref{alg_inc_train} using batch size $32$ and epochs $T = xx$.
+The threshold $\tau$ is set as the accuracy of the target task using the baseline training schedule.
+
+For the case of six tasks,
 
@@
 \textbf{Theoretical validation.}
+For Figure \ref{fig_ab_sim}, \todo{how do we select each task pair?}
+For Figure \ref{fig_ab_data} and Figure \ref{fig_ab_cov}, the sample size of the target task is fixed as $1000$.
+We vary the sample size of the source task from $100$ to $3000$.
 

### 2020-06-11 writeup/proof_examples.tex
revise

@@
 
-For the isotropic model, we will use Lemma \ref{prop_model_shift_tight} to analyze the bias-variance tradeoff.
-Our main observation is that the optimum of $\val(v)$ is approximately $1$.
-This allows us to simplify the bias and variance bounds significantly.
-We define the function
+For the isotropic model, we will use Lemma \ref{prop_model_shift_tight} to analyze the bias-variance tradeoff. We define the function
 \begin{align}
-	\val_\star(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	h(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 %\cor Under the setting of Lemma \ref{prop_model_shift_tight},
-For the isotropic model, using the concentration result for random vectors with i.i.d.
-entries, Lemma \ref{largedeviation}, we can obtain that $\val(v)= N_2\cdot \val_\star(v)  \left( 1+\OO(p^{-1/2+\e})\right)$.
+For the isotropic model, using the concentration result, Lemma \ref{largedeviation}, we can obtain that $\val(v)= N_2\cdot h(v)  \left( 1+\OO(p^{-1/2+\e})\right)$.
 Hence the validation loss in \eqref{approxvalid} reduces to
 \be\label{boundv-w}
-g(v)=\left[N_2\cdot \val_\star(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
+g(v)=\left[N_2\cdot h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
 \ee
-with high probability for any constant $\e>0$.
-\nc Thus for the following discussions, it suffices to focus on the behavior of $\val_\star (v)$.
-Let $\hat w$ the minimizer of $\val_\star(v)$.
-The proof will consist of two steps.
+with high probability for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
+
+We now show that for the isotropic model, the optimum of $\hat v$ is very close to 1. This allows us to simplify the expression of $\te(\hat{\beta}_2^{\MTL})$ significantly.
+%Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
+%Furthermore, under certain choice of parameters, we can simplify  
+More precisely, we have the following lemma.
+
+\begin{lemma}
+For the isotropic model, suppose that $\kappa^2$, $d^2$ and $\sigma^2$ satisfy the following relations: for some constant $c_0>0$,
+\be\label{choiceofpara}
+pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 .
+\ee
+Then we have
+\begin{align}
+\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
+&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
+\end{align}
+w.h.p. for some constant $\e>0$.
+\end{lemma}
+
+\begin{proof}
+
+Let $\hat w$ the minimizer of $h(v)$. The proof consists of two steps.
 \begin{itemize}
-	\item First, we show that $\hat{w}$ is close to $1$, and then \eqref{boundv-w} implies that $\hat v$ is also close to 1.
-	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_2^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
+	\item First, we show that $\hat{w}$ is close to $1$.
+	\item Second, with \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get \eqref{simple1}.
 \end{itemize}
@@
 For the first step, we will prove the following result.
-\begin{lemma}\label{lem_hat_v}
+
+\begin{claim}\label{lem_hat_v}
 %Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-For the isotropic model, the minimizer for $\val_\star(v)$ satisfies
+There exists a constant $C>0$ such that
 	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{w.h.p.}\ee
-	for some constant $C>0$.
 	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-\end{lemma}
+\end{claim}
 \begin{proof}
 To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof.
-First it is easy to observe that $\val_\star(w)< \val_\star(-w)$ for $w> 0$.
+First it is easy to observe that $h(w)< h(-w)$ for $w> 0$.
 Hence it suffices to assume that $w\ge 0$.
-
-We first consider the case $w\ge 1$. We write
+We first consider the case $w\ge 1$.
+We write
 \begin{align}
-	\val_\star(w) &=  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	h(w) &=  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 $$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
-are increasing functions in $w$. Hence taking derivative of $\val_\star(w)$ with respect to $w$, we obtain that
+are increasing functions in $w$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
 \begin{align*}
-\val'_\star(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
+h'(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
 +&~ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 $$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
-Hence $\val'_\star(w)>0$ on $(w_1,\infty)$, i.e. $\val_\star(w)$ is strictly increasing for $w>w_1$. This gives $\hat w\le w_1$.
+Hence $h'(w)>0$ on $(w_1,\infty)$, i.e. $h(w)$ is strictly increasing for $w>w_1$. This gives $\hat w\le w_1$.
 
-Then we consider the case $w\le 1$, and the proof is similar as above. Taking derivative of $\val_\star(w)$, we obtain that
+Then we consider the case $w\le 1$, and the proof is similar as above. Taking derivative of $h(w)$, we obtain that
 \begin{align}
-	\val'_\star(w) &\le \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	h'(w) &\le \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 $$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
-Hence $\val'_\star(w)<0$ on $[0,w_2)$, i.e. $\val_\star(w)$ is strictly decreasing for $w<w_2$. This gives $\hat w\ge w_2$.
+Hence $h'(w)<0$ on $[0,w_2)$, i.e. $h(w)$ is strictly decreasing for $w<w_2$. This gives $\hat w\ge w_2$.
 
@@
 
-For the rest of this section, we choose parameters that satisfy the following relations: \be\label{choiceofpara}
-pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 ,
-\ee
-for some small constant $c_0>0$. We will explain below why we make this choice. Before that, we first show the following estimate on the optimizer $\hat v$: with high probability,
+%For the rest of this section, we choose parameters that satisfy the following relations: \be\label{choiceofpara}
+%pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 ,
+%\ee
+%for some small constant $c_0>0$. 
+Next we prove the following estimate on the optimizer $\hat v$: with high probability,
 %\begin{lemma}
@@
 %\begin{proof}
- In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'_\star(w)|\gtrsim p d^2$.
-Moreover, under the choice \eqref{choiceofpara} we have
-$$\val_\star(w) =\OO(pd^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
+ In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim p d^2$.
+Moreover, under \eqref{choiceofpara} we have
+$$h(w) =\OO(pd^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
 Thus we obtain that for $|w-1|\ge 2C\cal E$,
-$$\left|\val_\star(w) - \val_\star(\hat w)\right|\ge |\val_\star(w)-\min(\val_\star(w_1),\val_\star(w_2))|\gtrsim pd^2 \cal E \gtrsim \cal E \cdot \val_\star(\hat w),$$
+$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min(h(w_1),h(w_2))|\gtrsim pd^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
 which leads to $g(w) > g(\hat w)$ w.h.p.
@@
 The above considerations lead to the choices of parameters in \eqref{choiceofpara}.
-Moreover, under \eqref{choiceofpara} we can simplify \eqref{1Liso} to
-\begin{align}
-\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
-&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
-\end{align}
-w.h.p. for some constant $\e>0$.
+Moreover, under \eqref{choiceofpara} we can simplify \eqref{1Liso} to \eqref{simple1}.
+%\begin{align}
+%\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
+%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
+%\end{align}
+%w.h.p. for some constant $\e>0$.
+\end{proof}
 

### 2020-06-11 writeup/proof_main.tex
revise

@@
 
-For the isotropic model in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
-\begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
-		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_2$ is a random vector with i.i.d.
-entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_1$ is a random vector such that $(\beta_1 - \beta_2)$ is a random vector with i.i.d.
-entries with mean $0$, variance $d^2$ and all moments.
-Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}.$
-	Then we have with high probability,
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}.
-		\end{align*}
-\end{lemma}
-
 The proof of Theorem \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any fixed $\e>0$, we have
@@
 The estimate \eqref{eq_isometric} provides tight bounds for the concentration error.
-The result is formally stated in Lemma \ref{SxxSyy} in Section \ref{sec_maintools}.
+The result is formally stated in Lemma \ref{SxxSyy} below.
+
+%\begin{remark}
+The main error $\delta$ of Theorem \ref{thm_model_shift} comes from approximating $n_1^{-1}Z_1^TZ_1$ by $\id$ using \eqref{eq_isometric}; see the estimate \eqref{bounddelta-} below.
+In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
+$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  \hat{v}^2 .$$
+In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ have been studied in the name of Fisher matrices; see e.g.
+\cite{Fmatrix}.
+However, since $\cal X$ is not symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix theory literature, and the study of the singular values of $\cal X +\hat v^2$ will be even harder.
+We leave this problem to future study.
+%\end{remark}
 
@@
 
-\begin{remark}
-One can see from the above proof that the main error, $\delta$, of Theorem \ref{thm_model_shift} comes from approximating $\delta_{\bias}$ by $\wt\delta_{\bias}$ in \eqref{bounddelta-}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
-$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  {v}^2 .$$
-In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ have been studied in the name of Fisher matrices; see e.g.
-\cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix theory literature, and the study of the singular values of $\cal X + v^2$ will be even harder.
-We leave this problem to future study.
-\end{remark}
+For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
+\begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
+		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+		$\beta_2$ is a random vector with i.i.d.
+entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_1$ is a random vector such that $(\beta_1 - \beta_2)$ is a random vector with i.i.d.
+entries with mean $0$, variance $d^2$ and all moments.
+Denote
+		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}.$
+	Then we have with high probability,
+		\begin{align*}
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}.
+		\end{align*}
+\end{lemma}
 
-By replacing \eqref{bounddelta-} with a tighter bound in Step II of the above proof, we can conclude the proof of Lemma \ref{prop_model_shift_tight}.
+\begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
+The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Theorem \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
+We only describe the main difference.
 
-\begin{proof}[Proof of Lemma \ref{prop_model_shift_tight}]
 For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.

### 2020-06-11 writeup/proof_examples.tex
edits

@@
 
-For the isotropic model, we will use Lemma \ref{prop_model_shift_tight} to analyze the bias-variance tradeoff. We define the function
-\begin{align}
-	h(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
-\end{align}
-%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
-For the isotropic model, using the concentration result, Lemma \ref{largedeviation}, we can obtain that $\val(v)= N_2\cdot h(v)  \left( 1+\OO(p^{-1/2+\e})\right)$.
-Hence the validation loss in \eqref{approxvalid} reduces to
-\be\label{boundv-w}
-g(v)=\left[N_2\cdot h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
-\ee
-with high probability for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
-
-We now show that for the isotropic model, the optimum of $\hat v$ is very close to 1. This allows us to simplify the expression of $\te(\hat{\beta}_2^{\MTL})$ significantly.
+We show that for the isotropic model, the optimum of $\hat v$ is very close to 1.
+This allows us to simplify the expression of $\te(\hat{\beta}_2^{\MTL})$ significantly.
 %Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
@@
 More precisely, we have the following lemma.
+Later on, we combine the following lemma with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.
 
 \begin{lemma}
-For the isotropic model, suppose that $\kappa^2$, $d^2$ and $\sigma^2$ satisfy the following relations: for some constant $c_0>0$,
+In the isotropic model, for some constant $c_0>0$, suppose that
 \be\label{choiceofpara}
-pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 .
+	\frac{pd^2}{\sigma^2} \le \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0}.
 \ee
@@
 \begin{align}
-\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
+\te(\hat{\beta}_2^{\MTL})=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
 &+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
@@
 \begin{proof}
+	Using Lemma \ref{largedeviation}, we obtain that $\val(v)= N_2\cdot h(v)  \left( 1+\OO(p^{-1/2+\e})\right)$.
+	We define the function
+	\begin{align}
+		h(v) =& \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+		& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+		& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+	\end{align}
+	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
+	Hence the validation loss in \eqref{approxvalid} reduces to
+	\be\label{boundv-w}
+		g(v)=\left[N_2\cdot h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
+	\ee
+	with high probability for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
 
@@
 \begin{align}
-	h(w) &=  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	h(w) =&  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
@@
 h'(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
-+&~ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-		-&~ 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
+ &+~ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+		&-~ 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
 \end{align*}
@@
 \begin{align}
-	h'(w) &\le \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+	h'(w) \le& \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
 	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-	&~ + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }\\
-			& = \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
+	& + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }\\
+			 =& \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
 \end{align}

### 2020-06-11 writeup/proofs_sec3.tex
sec AB

@@
 \begin{align}
-	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
+	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
 			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
 \end{align}
-which is well-defined since it only depends on $\hat v$, but otherwise does not depend on $\hat w_1$ or $\hat w_2$ separately.
+which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
 
 \textbf{Extended related work.}
-McNamara and Balcan \cite{NB17}
-
-Bullins et al. \cite{BHKL19}
-
-Cavallanti et al. \cite{CCG10}
-
-Daume and Marcu \cite{DM06}
-
-Zhao et al. \cite{ZD19}
+Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
+The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
+For such models, their output dimension plays an important role of regularization \cite{KD12}.
+Linear models in the context of multi-task learning have been studied in various settings, including representation learning \cite{BHKL19}, online learning \cite{CCG10,DCSP18}, and sparse regression \cite{LPVT11}.

### 2020-06-11 writeup/related.tex
sec AB

@@
 Our work is closely related to Wu et al. \cite{WZR20}.
-While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques do not explain the phenomena of negative transfer.
+While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
 

### 2020-06-11 writeup/app_exp.tex
F.1
sec F

@@
 	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
+	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
+	This can be achieved similarly by rescaling the task data.
 
@@
 
-\iffalse
 \textbf{Further results on covariance alignment.}
+Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
+In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
+In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
+In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always help.
+One possible explanation is overfitting because of additional parameters from the alignment module.
+It would be interesting to understand when adding the alignment module provides benefit to the multi-task learning model.
+We leave this question for future work.
 %Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
@@
 		\caption{Task pair TREC and CR}
+		\label{fig_cov_a}
 	\end{subfigure}\hfill
@@
 		\caption{Task pair MR and SST}
+			\label{fig_cov_b}
 	\end{subfigure}
@@
 \end{figure}
-\fi

### 2020-06-11 writeup/related.tex
impact

@@
 
-In this work, we provide a theoretical study to help understand when multi-task learning performs well.
+In this work, we provide a theoretical framework to help understand when multi-task learning performs well.
 We approach this question by studying the bias-variance tradeoff of multi-task learning.
 We provide new technical tools to bound the bias and variance.
-We relate the bounds to three properties of task data.
+%We relate the bounds to three properties of task data.
 %Overall, our theoretical study provides a framework to help understand multi-task learning performance.
-We further provide guidance for detecting and mitigating negative transfer on image and text classification tasks.
+%We further provide guidance for detecting and mitigating negative transfer on image and text classification tasks.
 
 Our theoretical framework has the potential to impact many other neighboring areas in the ML community.
-Multi-task learning connects to a wide range of areas \cite{V20}.
-To name a few, transfer learning, meta learning, multimodal learning, semi-supervised learning, and representation learning are all closely related areas to multi-task learning.
-Any learning scenario such as reinforcement learning \cite{YKGLHF20} that combines multiple datasets to supervise a model is using multi-task learning.
-While the theoretical results that we have provided are not directly applicable to these different settings, we believe that the tools we have developed and the framework we have provided can inspire followup works in different settings.
-For one specific example, we have developed new concentration bounds that may apply to many settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
-For another example, our results also allow extensions to transfer learning and domain adaptation \cite{K18}.
-The insights we have developed on positive and negative transfer can potentially find applications in multimodal learning, where the data sources are usually heterogeneous.
-Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where scarse labeled samples presents a significant challenge.
+(i) Our concentration bounds are applicable to different settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
+(ii) Our analysis of the bias-variance tradeoff can be extended to transfer learning and domain adaptation \cite{K18}.
+(iii) Our insights on positive and negative transfer can potentially find applications in multimodal learning, where the data sources are usually heterogeneous.
+(iv) Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where scarse labeled samples presents a significant challenge.
+Finally, since multi-task learning connects to a wide range of areas \cite{V20} such as semi-supervised learning, representation learning, and reinforcement learning \cite{YKGLHF20}.%
+We believe that the tools we have developed and the framework we have provided can inspire followup works in these different areas.
 
-Our algorithmic consequences of our theory have the potential to impact downstream applications of multi-task learning.
+Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their multi-task learning applications.
 For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
-Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult to acquire large amounts of labeled data.
-For such settings, training multi-task models can be very challenging.
-Our insight on using single-task learning results to help understand multi-task learning can be valuable for helping practitioners understand their results.
+Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult and expensive to acquire large amounts of labeled data.
+For such settings, our proposed training scheduler might improve the model training efficiency without requiring huge amounts of labeled data.
+For another example, practitioners in industry often need to improve prediction performance by training many related tasks.
+But the results are not always positive and practitioners have a hard time figuring out why.
+Our proposed metric can provide guidance for selecting which tasks should be trained together in a multi-task model.
+
+%Our algorithmic consequences of our theory have the potential to impact downstream applications of multi-task learning.
+%For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
+%Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult to acquire large amounts of labeled data.
+%For such settings, training multi-task models can be very challenging.
+%Our insight on using single-task learning results to help understand multi-task learning can be valuable for helping practitioners understand their results.

### 2020-06-11 writeup/app_exp.tex
sec F

@@
 We simplify the setup of this experiment by fixing the sample sizes of every task pair.
-For sentiment analysis tasks, the source task uses xx training samples and the target task uses $1000$ training samples for every task pair.
-For image classification tasks, the training sample size is 10,000 for every task.
+For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
+We randomly sample these many data points from the task.
+The sample size of the target task is $1000$.
+For image classification tasks, the training sample size is $10,000$ for every task.
 
@@
 For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train} below to a round-robin training schedule baseline.
-We set the parameters of Algorithm \ref{alg_inc_train} using batch size $32$ and epochs $T = xx$.
-The threshold $\tau$ is set as the accuracy of the target task using the baseline training schedule.
+We add $20\%$ of source task samples for every $T = 2$ epochs.
+The total number of epochs is $20$.
+We set the threshold $\tau$ as the accuracy of the target task using the baseline training schedule.
 
-For the case of six tasks,
+For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
+Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
+We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
+We run $20$ epochs in total.
 
-\begin{algorithm}[!h]
+\begin{algorithm}[!t]
 	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
@@
 \textbf{Theoretical validation.}
-For Figure \ref{fig_ab_sim}, \todo{how do we select each task pair?}
-For Figure \ref{fig_ab_data} and Figure \ref{fig_ab_cov}, the sample size of the target task is fixed as $1000$.
+For Figure \ref{fig_ab_sim}, we select a similar and a dissimilar source task compared to the target task using domain knowledge.
+First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
+Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
+TREC is less similar to MR because the task is about question types.
+Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
+
+For Figure \ref{fig_ab_data} and Figure \ref{fig_ab_cov}, we fix the sample size of the target task as $1000$.
 We vary the sample size of the source task from $100$ to $3000$.
+For Figure \ref{fig_ab_cov}, we implement the covariance alignment procedure following \cite{WZR20}.
 
@@
 
-\textbf{Further results on covariance alignment.}
+\textbf{Further results of the covariance alignment procedure.}
 Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
@@
 In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always help.
-One possible explanation is overfitting because of additional parameters from the alignment module.
-It would be interesting to understand when adding the alignment module provides benefit to the multi-task learning model.
+One explanation is over-fitting because of additional parameters from the alignment module.
+An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
 We leave this question for future work.
@@
 
-\begin{figure}[!h]
+\begin{figure}%[!t]
 	\centering
@@
 	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-We suspect that this happens because of overfitting on the extra parameters in the additional covariance alignment module.}
+	We suspect that this happens because of over-fitting on the extra parameters in the additional covariance alignment module.}
 	\label{fig_covariate_app}

### 2020-06-11 writeup/related.tex
sec F

@@
 
-Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their multi-task learning applications.
+Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their use cases of multi-task learning.
 For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.

### 2020-06-11 writeup/related.tex
edits

@@
 
-\textit{Multi-task learning theory.}
+\textit{Theoretical works.}
 Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
 Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors in an optimal way.
-The benefit of learning multi-task representations is studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors optimally.
+The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
 Our work is closely related to Wu et al. \cite{WZR20}.
@@
 % Adding a regularization over $B$, e.g. .
-\textit{Multi-task learning methodology.}
+\textit{Methodological works.}
 Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
@@
 %\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-The multi-task learning model that we have focused on is based on the idea of hard parameter sharing \cite{C93,KD12,R17}.
-We believe that the technical tools we have developed can also be applied to many other multi-task learning models.
+The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
+We believe that our theoretical framework can apply to other approaches to multi-task learning.
 
@@
 First, our bound on the bias term (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
-Tightening this error bound can potentially cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
+Tightening this error bound might cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
 Second, it would be interesting to extend our results to non-linear settings.
@@
 We approach this question by studying the bias-variance tradeoff of multi-task learning.
-We provide new technical tools to bound the bias and variance.
+We provide new technical tools to analyze the bias and variance of multi-task learning.
 %We relate the bounds to three properties of task data.
@@
 Our theoretical framework has the potential to impact many other neighboring areas in the ML community.
-(i) Our concentration bounds are applicable to different settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
-(ii) Our analysis of the bias-variance tradeoff can be extended to transfer learning and domain adaptation \cite{K18}.
-(iii) Our insights on positive and negative transfer can potentially find applications in multimodal learning, where the data sources are usually heterogeneous.
-(iv) Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where scarse labeled samples presents a significant challenge.
+(i) Our concentration bounds can apply to different settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
+(ii) Our analysis of the bias-variance tradeoff can extend to transfer learning and domain adaptation \cite{K18}.
+(iii) Our insights on positive and negative transfer can be useful in multimodal learning, where the data sources are usually heterogeneous.
+(iv) Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where limited labeled samples presents a significant challenge.
 Finally, since multi-task learning connects to a wide range of areas \cite{V20} such as semi-supervised learning, representation learning, and reinforcement learning \cite{YKGLHF20}.%
-We believe that the tools we have developed and the framework we have provided can inspire followup works in these different areas.
+We believe that the tools we have developed and the framework we have provided can inspire followup works in these areas.
 
 Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their use cases of multi-task learning.
-For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
-Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult and expensive to acquire large amounts of labeled data.
-For such settings, our proposed training scheduler might improve the model training efficiency without requiring huge amounts of labeled data.
+For one example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
+Unlike the applications of multi-task learning in text classification where we can collect large amounts of labeled data \cite{GLUE}, in medical applications it is typically difficult and expensive to acquire labeled data.
+For such settings, our proposed training scheduler might improve the model training efficiency by using less labeled data.
 For another example, practitioners in industry often need to improve prediction performance by training many related tasks.

### 2020-08-09 neurips20_response/response.tex
author response

\documentclass{article}

\usepackage{neurips_2020_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{enumitem}

\usepackage{xcolor}
\newcommand{\yell}[1]{\textcolor{red}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{{TODO: #1}}}
\newcommand{\num}[1]{\textcolor{black}{#1}}

% Squished list environment to save space
\newcommand{\squishlist}{
\begin{list}{$\bullet$}
{ \setlength{\itemsep}{0pt}
\setlength{\parsep}{1pt}
\setlength{\topsep}{1pt}
\setlength{\partopsep}{0pt}
% \setlength{\labelwidth}{1em}
}
}
\newcommand{\squishend}{\end{list}}

\begin{document}

We thank all of our reviewers for carefully reading our work and providing insightful reviews.
First, we address several main issues that are raised by the reviewers.
Then, we respond to each individual reviewer's feedback.

\textbf{Motivation for our setting. [R1, R2, R3]}
As R2 pointed out, we focus on a situation where we have a target task for which we only have limited labeled data and several source tasks.
We study when training the tasks together can benefit the target task.
While this setting is different from traditional MTL, it is commonly encountered in practice. For example, the task of interest might be about predicting a rare event or classifying an Xray-scan.
For such settings, collecting large amounts of labeled data for the task is either not possible or very expensive, but auxiliary labeled data are often easier to obtain.
Traditional MTL theory that studies the average performance of all tasks does not help predict when adding the source tasks provides positive transfer for the target task or not.
Our work applies to these settings and takes a step towards filling the gap.

\textbf{Extension to multiple tasks.}
We thank R1 and R2 for raising the important question of whether our setting applies to multiple tasks.
First, for multi-label settings where all tasks have the same features, i.e. $X_i = X$ for any $i$, our result in Theorem 3.6 provides a sharp bias-variance tradeoff of MTL and \textit{all of our insight for two tasks except covariate shift applies to multi-label settings}.
Due to page limit we have not elaborated on this part in the submission, but we will elaborate the theoretical implication in the next version.
The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.

Second, for settings where different tasks have different features, we can still extend our qualitative insight here.
That is, we can show that \textit{as long as the dimension of the shared layer ($B$) is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
We will include this result in the next version.

\textbf{Clarifying writing. [R2, R3]}
We thank R2 and R3 for providing numerous detailed feedback that help us improve writing.

\textbf{R1:}

\textbf{R2:}

\textbf{R3:}

\end{document}

### 2020-08-09 arxiv/app_exp.tex
author response

--- 2020-06-11 writeup/app_exp.tex
@@
 \subsection{Synthetic Settings}\label{app_synthetic}
-	We describe the parameters used for producing Figure \ref{fig_model_shift_phasetrans}.
-	For all three simulations, we use dimension $p = 200$.
-	In Figure \ref{fig_model_shift}, we use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
+	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
+	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
+	\squishlist
+		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
 	The noise level is $\sigma = 5$.
 	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
-	The $x$-axis measure the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
-	In Figure \ref{fig_size}, we set $\kappa = 1$ and $d = 0.02$ for model distance.
+	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
+	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
+		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
 	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
-	In Figure \ref{fig_covariate}, we set $\kappa = 1$ and $d = 0$.
+		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
 	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
@@
 	This can be achieved similarly by rescaling the task data.
+	\squishend
 
@@
 
-For the text classification experiment, we encode each word using the GLoVe word vectors.
+For the text classification experiment, we encode each word using the GLoVe word embeddings.%
 \footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-We apply an average pooling layer over the word embeddings.
-Then we add a multi-layer perception (MLP), LSTM, or CNN layer on top of the word embeddings \cite{lei2018simple}.
+We evaluate three model choices.
+For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
+For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
 
-\textbf{Single-task based metric.}
+\textit{Predicting transfer effect via STL results.}
 We simplify the setup of this experiment by fixing the sample sizes of every task pair.
@@
 
-\textbf{Incremental training schedule.}
-For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train} below to a round-robin training schedule baseline.
+\textit{Mitigating negative transfer via incremental training.}
+For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
 We add $20\%$ of source task samples for every $T = 2$ epochs.
 The total number of epochs is $20$.
-We set the threshold $\tau$ as the accuracy of the target task using the baseline training schedule.
+We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
 
@@
 
-\textbf{Theoretical validation.}
-For Figure \ref{fig_ab_sim}, we select a similar and a dissimilar source task compared to the target task using domain knowledge.
+\textit{Validating the Theoretical Results.}
+We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
+\squishlist
+	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
 First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
@@
 Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-
-For Figure \ref{fig_ab_data} and Figure \ref{fig_ab_cov}, we fix the sample size of the target task as $1000$.
-We vary the sample size of the source task from $100$ to $3000$.
-For Figure \ref{fig_ab_cov}, we implement the covariance alignment procedure following \cite{WZR20}.
+	\item Sample size: We vary the sample size of the source task from $100$ to $3000$.
+	\item Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
+	We fix the sample size of the target task as $1000$.
+\squishend
 
@@
 In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always help.
-One explanation is over-fitting because of additional parameters from the alignment module.
+In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
+One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
 An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
@@
 
-\begin{figure}%[!t]
+\begin{figure}[!h]
 	\centering
@@
 		\centering
-		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
 		\caption{Task pair TREC and CR}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
 		\caption{Task pair MR and SST}
@@
 	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-	We suspect that this happens because of over-fitting on the extra parameters in the additional covariance alignment module.}
+	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
 	\label{fig_covariate_app}

### 2020-08-09 arxiv/main.tex
author response

\documentclass{article}

%\usepackage[nonatbib]{neurips_2020}
\usepackage{fullpage}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{macro_math}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage{multirow}
\usepackage[us,12hr]{datetime}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{caption,subcaption}
%\usepackage{breqn}

% Squished list environment to save space
\newcommand{\squishlist}{
\begin{list}{$\bullet$}
{ \setlength{\itemsep}{0pt}
\setlength{\parsep}{2pt}
\setlength{\topsep}{2pt}
\setlength{\partopsep}{0pt}
\setlength{\itemindent}{2pt}
\setlength{\leftmargin}{0.5cm}
% \setlength{\labelwidth}{1em}
}
}
\newcommand{\squishend}{\end{list}}

\setlength{\parskip}{0.3em}

\begin{document}

\title{Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions}
\maketitle
%\date{{\ddmmyyyydate\today} at \currenttime}

\input{intro}
\input{setup}
\input{transfer}
%\input{extensions}
\input{experiments}
\input{related}

\bibliographystyle{unsrt}
\bibliography{rf,ref_mtl}

\appendix
\input{proofs_sec3}
\input{proof_main}
\input{proof_examples}
\input{proof_extension}
\input{proof_appd}
\input{app_exp}
\end{document}

### 2020-08-09 arxiv/proof_main.tex
author response

--- 2020-06-11 writeup/proof_main.tex
@@
 
-\begin{lemma}[Variance bound: Restate of Lemma \ref{lem_cov_shift_informal}]\label{lem_cov_shift}
+\begin{lemma}[Variance bound: Lemma \ref{lem_cov_shift_informal} restated]\label{lem_cov_shift}
 	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
@@
 
-\begin{theorem}[Restate of Theorem \ref{thm_main_informal}]\label{thm_model_shift}
+\begin{theorem}[Theorem \ref{thm_main_informal} restated]\label{thm_model_shift}
 %For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.

### 2020-08-09 neurips20_response/main.tex
author response

\documentclass{article}

\usepackage{neurips_2020_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{enumitem}

\usepackage{xcolor}
\newcommand{\yell}[1]{\textcolor{red}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{{TODO: #1}}}
\newcommand{\num}[1]{\textcolor{black}{#1}}

% Squished list environment to save space
\newcommand{\squishlist}{
\begin{list}{$\bullet$}
  { \setlength{\itemsep}{0pt}
    \setlength{\parsep}{1pt}
    \setlength{\topsep}{1pt}
    \setlength{\partopsep}{0pt}
    % \setlength{\labelwidth}{1em}
  }
}
\newcommand{\squishend}{\end{list}}

\begin{document}
We thank the reviewers for their time and thoughtful feedback.
Taking their helpful comments into account, we sought and received additional feedback to extend and clarify the presentation of our work.
Since submission, we have also achieved \textbf{state-of-the-art scores} on the SuperGLUE benchmark \num{by 2.7 points} using the proposed approach.

\begin{wrapfigure}[12]{r}{0.42\textwidth}
\vspace{-1.5em}
    \begin{center}
        \includegraphics[width=0.415\textwidth]{figures/ablation_noise.pdf}
    \end{center}
% \vspace{-1.5em}
\label{fig:ablation_noise}
% \caption{Denoising SFs using the slice indicator. Top: Noise is added as a proportion to the slice size. Bottom: These are heatmaps of the slice indicator outputs, where a larger number indicates higher likelihood of slice membership.}
\end{wrapfigure}

% Based on CR's comments, moving the ablation upfront
% version v2
\textbf{Ablation studies. [R1, R2, R3]}
We thank all reviewers for their detailed feedback about the proposed architecture. 
We have added ablation studies to Section~3.3 to clarify specific components and will include additional experiments and details in the final draft.
\textbf{Coping with noise}: We test the robustness of our approach on a simple synthetic example: in the Figure to the right, we show noisy SFs (top row: no noise, 40\% noise, 80\% noise) and the corresponding slice indicator's output as a heatmap (bottom row: darker indicates higher likelihood of slice-membership).
We show that the indicator assigns low relative probabilities on noisy (40\%) SF samples (bottom middle) and ignores a very noisy (80\%) SF, assigning relatively uniform scores to all samples (bottom right).
\textbf{Architecture ablations}: We thank R2 and R3 for suggestions to clarify the contributions of the architecture's components. 
We perform an ablation study using a synthetic, binary classification dataset with four slices covering random data subsets.
We observe that indicator outputs contribute \num{+3.4 F1}; without this indicator module, the model might fail to handle noisy SFs.
The predictor confidences contribute \num{+4.6 F1}; without considering these confidences, the attention mechanism might combine non-expert features into the reweighted representation. 
Compared to equal weights, our attention mechanism contributes \num{+5.6 F1}; without attention, there is no fine-grained combination of slice representations.

% our approach scored (\num{82.7 F1}).
% % We also try using slice labels only as additional input features, which achieved \num{XX F1}.
% In comparison, we report ablations of proposed modules (with relative scores): we modify the attention mechanism using 1) only prediction confidences (\num{-3.4 F1}), 2) only indicator outputs (\num{-4.6 F1}), 3) equal-weight for representations (\num{-5.6 F1}). 
% We interpret relative performance drops: 1) without the indicator, the model fails to handle noisy SFs, 2) without predictor confidence, non-expert features are combined into the reweighted representation, and 3) equal attention weights prevent fine-grained combination of slice representations.

% version v1
% \textbf{Additional ablation studies. [R1, R2, R3]} We thank all reviewers for their detailed feedback regarding specific components of our proposed architecture, and we have added multiple ablation studies to Section~3.3 as points of clarification.
% %Since submission, we have obtained \textbf{state-of-the-art scores} on three tasks in SuperGLUE benchmark (e.g., +\num{3.8/2.8} Avg. F1/acc. on CB, +\num{2.8} acc. on COPA, +\num{2.5} acc. on WiC). We have added those results with details about the slicing functions used in the appendix of the paper.
% \textbf{Coping with noise}: In this ablation, we study the robustness of our approach to noisy slicing functions.
% % We \yell{1) creating a slicing function that labels randomly (which the model learns to ignore), 2) defining multiple slices but only covering a portion of them with slicing functions (the model improves only on the targeted slices), and 3) depicting performance on a slice as its corresponding slicing function varies in precision over the true slice from 1 to 0}. 
% We add random noise to a slicing function (SF) output (top row if Figure) and visualize the slice indicator's output heatmap (Figure~\ref{fig:ablation_noise} bottom, where higher values indicate higher likelihood of slice-membership.) 
% We see that the indicator learns to denoise outputs (Figure, bottom middle) or effectively ignore extremely noisy SFs (Figure, bottom right). 
% \textbf{Comparison with more baselines}: We thank the suggestions from R3 for comparing with more baselines. We report the results of using different sources of attention on the synthetic dataset: 1) using only the prediction confidences with \num{XX F1}, 2) using only the indicator outputs with \num{XX F1}, 3) using equal-weight averaging with \num{XX F1}. We also try using slice labels only as additional input features, which achieved \num{XX F1}.

% \textbf{Clarification of the model architecture. [R1, R2, R3]}
% We appreciate the reviewers' suggestions about clarifying the modeling approach (Section 3.2).
% We agree with the points of confusion, and we have updated the text, making the notation modifications recommended by R2 for the equations in Sec. 3.2, and we have updated Figure 2 with annotated dimensions for each module in the architecture. 
% We briefly clarify the key components of the architecture: The architecture relies on a \textbf{backbone} architecture, which serves as a feature extractor (e.g. ResNet, BERT).
% Usnnng shared backbone features, we learn \textbf{slice-indicator modules}---one per slice---which classify slice membership for each example.
% Next, we map the backbone features to separate \textbf{slice-specific representations}---one per slice.
% Note: we treat the original task as a trivial \textit{base slice} (all examples are included) in order to model the residuals representations and slice-representations.
% A \textbf{shared slice prediction head} maps each slice-specific representation to a prediction---we note that each representation is trained only on examples belonging to the slice, such that slice-specific representation is an ``expert'' for a particular slice.
% We then combine each \textbf{slice-specific representation} as a weighted sum, using attention weights computed by the \textit{confidence of the prediction} computed by each slice-specific representation and the \textit{slice-membership classification} of each slice indicator module.
% Finally, we map the \textbf{re-weighted representation} to an output (i.e. binary classification) to make a final prediction on the original task.

% version v2
\textbf{Presentation of model architecture. [R2, R3]}
% Thanks to suggestions to clarify the model architecture, we have leveraged external feedback to improve the second half of the paper. 
% Readers were unclear about the dimensions of intermediate quantities in our architecture; 
In response to R2's feedback, we have updated each module with dimension annotations and updated Figure 2 with visual cues to specify where slice labels are used during training (i.e. as \textit{labels} for training indicators and \textit{masks} for training predictors).
Following R3's suggestion, we have more clearly expressed the costs (e.g. model size, training time) of each approach, especially \textsc{MoE}, with respect to \textsc{Ours} in Table~1.

We thank R2 for pointing out vague notation in Section~3.2, which we have clarified in the updated draft. 
In L160, we changed $p$ to $w$ to avoid confusion with probability notations.
In L165, $g(P)$ (from Section~3.2(e)) indeed refers to the concatenation of each $g(p_i)$ from Section~3.2(d).
Our notation refers to the binary setting, where $c=1$ such that $P \in \mathbb{R}^{h \times k + 1}$. 
In L166, we clarify that the predictor confidence is computed using the maximum probability over prediction classes.
Our experiments are binary classification tasks, for which we use the absolute value of the predictor logit as this confidence.
% To clarify R2's question about final predictions, we note that the model learns a prediction head (Section~3.2f) based on the reweighted representation.
Additionally, R2 is correct that $z$ is not used in these reweighted features, $z'$. 
Instead, the base representation is modeled as a trivial slice: $p_{\text{BASE}}$, and a final prediction is made based on the reweighted $z'$.
We clarify that $h$ is a hyperparameter for flexibility in specific applications; for simplicity, we set this to $r$ in experiments.

% version v1
% \textbf{Clarification of the model architecture. [R2, R3]}
% We agree with the reviewers' suggestions for clarifying the model architecture (Section 3.2).
% Following the reviewers' helpful feedback, we've taken additional reviewers into account to clarify the second half of the paper.
% We observed that readers were unclear about the dimensionalities of intermediate quantities in the network, so we updated each module in the architecture with dimension annotations.
% Additionally, we have updated the figure to denote explicitly where slice labels are used during training, as suggested by R2.
% Specifically, we clarify that during training, slicing functions outputs are simultaneously used as \textit{labels} to train slice indicator modules and as \textit{masks} for the loss terms of the slice predictor head + corresponding slice-specific representations.

% \textbf{Clarification of the model architecture. [R1, R2, R3]}
% We appreciate the reviewers' suggestions about clarifying the model architecture (Section 3.2).
% We agree with all reviewers and have updated our description to make these points clearer.
% % \textit{Slice-based Learning} (SL) includes several key components: 
% % To summarize, we briefly clarify the key components of the architecture here:
% % \textbf{backbone} which is a feature extractor from the data, \textbf{slice-indicator} which uses the extracted features from backbone and user-provided slicing function as ground truth to learn the slice membership, \textbf{slice-specific representations and predictors} which also use extracted features to learn the slice-specific representations and then learn a slice-specific predictor and \textbf{re-weighted representation} leverages all information from previous two components to learn the slice-aware representation and make the final prediction. [SHORTEN THIS PARA]

% \textit{Backbone.} Neural network architecture which serves as a feature extractor (e.g. ResNet, BERT) in the original learning pipeline, where extracted features (dim $r$) are directly fed into a prediction head to learn to predict the ground truth.
% In SL, we use the same backbone features as in original learning pipeline.

% \textit{Slice-indicator.} SL uses backbone features to learn a \textbf{slice-indicator} based on the user-provided slicing functions. In SL, we use linear classifier from backbone features to learn slice membership for each example. Note: this is particularly useful, because we don’t assume slicing functions are available at inference time.

% \textit{Slice-specific represesentations.} SL learns specific ``expert'' parameters for each slice by mapping from the backbone features (dim $r$) to to intermediate features (dim $h$).

% A \textit{shared slice prediction head} then acts as a linear classifier from each set of slice-specific representations to the original task's output space. Note, that each ``weak'', slice-specific classifier is trained only on examples belonging to the slice.

% \textit{Re-weighted representation.} SL then combines each \textbf{slice-specific representation} as a weighted sum, using attention weights based on the \textit{confidence of the prediction} on each slice-specific representation and the \textit{slice-membership classification} of each slice indicator module. Finally, we map the \textbf{re-weighted representation} to an output (i.e. binary classification) to make a final prediction on the original task.

% In response to R2's comment, we clarify that we compute the predictor confidence using the maximum probability over all prediction classes. In the binary case used in experimental validation, we use the absolute value as a proxy for this confidence; we will update the draft to clarify this usage.

% We have also made the notation modifications recommended by R2 for the equations in Sec. 3.2, and we have updated Figure 2 with annotated dimensions for each module in the architecture. We treat the original task as a trivial \textit{base slice} (all examples are included) in order to model the residuals representations and slice-representations. [ADD ALL MISSING ONES IF THERE EXISTS]

%   % \textbf{Coping with noise in the slicing function. [R1, R3]} We thank R1 and R3 for their thoughtful questions regarding how noise is handled in slice-based learning. 
% We performed an ablation study to evaluate XXX different scenarios on synthetic datasets: 
% 1) noisy slicing function (with randomly sampled data in the slice), where we expect performance to increase 
% 2) multiple slices in the dataset while slicing function only cover few slices. As shown in Figure XXX and we found that in 1) the noisy slicing function is ignored. 2) only the slices that covered by slicing functions are detected.  \todo{create a table if there is space?}
% \todo{ADD MORE DETAILS BASED ON NEW EXP.} \todo{Coping with noise experiment—showing improvement model performance with more noise}.

% \textbf{Experimental protocols. [R1, R2, R3]} We thank the reviewers for comments that have helped us increase the clarity of our experiments. 
% As per R1's suggestion, we move experimental details from the appendix into the body of the paper, including more detail on the specific slices used.
% We have improved the paper with the suggested changes, including additional context for the comparison to data programming [23], an approach from weak supervision literature which also proposes a programming abstraction for utilizing potentially noisy user-provided heuristics.
% % We anchor our work in this class of programming abstractions, as our combines noisy, domain-specific supervision using information about learned representations.

\textbf{R1:} We agree with R1 that Section~3.3 could be reframed more conservatively.
We have updated the title to ``Synthetic Experiments'' to clarify that our observations are grounded in the synthetic setting. 
R1 asked about a missing Figure 3c; Figure 3c refers to the right-most graphic in Figure~3, and we have labeled this more explicitly in the updated draft.

R1 asked for clarification about experimental details and provided feedback for the organization of Section 4. 
In our data splits, we ensure that the proportion of examples belonging to each slice is equivalent across train/valid/test for appropriate evaluation of slices; we did not collect/re-use different data sources.
% and do not use new data or re-use existing data.
Furthermore, we moved SF implementation/evaluation details and a description of slices from the appendix to the body of the paper.  
In Section~4.3, we have included an error analysis regarding counter-intuitive trends in slice-specific performance.
For example, results on \textsc{CoLA} may be explained by limitations in the backbone architecture; we observe low performance on \textsc{MoE}, which has extra capacity, on certain slices (e.g. \textit{ends with adverb} and \textit{has but}) where \textsc{Ours} also underperforms.
Following R1's suggestion, we have included detailed descriptions about the baselines.
Specifically, we anchor our work in data programming [23], a baseline from weak supervision literature that learns to combine noisy, user-provided heuristics.
% \yell{BETTER EXAMPLE For example, high-variance in the \textsc{CoLA} dataset is potentially because the adversarial defined slices, as indicated by similarly worsened relative improvements in the \textsc{MoE} model.}

\textbf{R2:} We thank R2 for feedback on our empirical evaluation.
In experiments, we use strong baselines as backbones: pre-trained \textsc{BERT++} (proposed by SuperGLUE organizers) for \textsc{CoLA}/\textsc{RTE} and pre-trained ResNet for \textsc{Cydet}. 
We thank R2 for the suggestion to report the evaluation server results; we obtain three new SOTA scores on SuperGLUE tasks: (+\num{3.8/+2.8} Avg. F1/acc. on CB, +\num{2.8} acc. on COPA, +\num{2.5} acc. on WiC).

\textbf{R3:} R3 asked about the weighting of our loss terms. 
In practice, one may set a hyperparameter for each loss term; to simplify our study, we set all weights to 1.
R3 is also correct that ``hard'' slice features would be more susceptible to noise; we will include this baseline in Table~1.
We emphasize, however, that introducing such features would violate the key assumption that slice information/metadata is not available during inference, as discussed in Section~3.1.
Finally, R3 asked how many slices our model can support. 
Our experiments include an average of \num{10} slices per application, while in an industrial collaboration, we have deployed the \textit{Slice-based Learning} on \num{hundreds} of production slices.

% \textbf{R1:}  
% We thank R1 for their helpful suggestions and detailed comments.
% \squishlist
% \item  We have reframed Section 3.3 more conservatively, updating the title to ``Synthetic Experiments'' to emphasize that the observations we make there are grounded in the synthetic setting.
% % \item R1 also asked for more experimental results demonstrating the ability of this approach to cope with noise in the slicing function specifications.
% % We have added this experiment to Section 3.3, including the \yell{plot shown below} which reports the improvement on a particular slice by the slice-aware model as the accuracy of the slicing function decreases (i.e., we increase the number of false positives that it labels for that slice).
% \item Figure 3c refers to the right-most graphic in Figure~3, which we have labeled more explicitly.
% \item We have included clarification about specific trends in the slice-specific performance in Section~4.3.
% For example, high-variance in the \textsc{CoLA} dataset could be explained by potentially adversarial defined slices, as indicated by similarly worsened relative improvements in the \textsc{MoE} model.
% In general, we acknowledge that there is indeed room for improvement in the specific modeling approach—our work highlights the high-level framing of \textit{Slice-based Learning} as a programming abstraction.
% \item We have spent significant time refactoring the second half of the paper for additional detail and clarity, in accordance with R1's suggestion.
% \squishend

% \textbf{R2:} We thank R2 for their detailed review and suggestions.
% \squishlist
%     \item We thank R2 for surfacing vague notation in line 165: the $g(P)$ term discussed in 3.2e indeed refers to the concatenated result of each $g(p_i)$ from section 3.2f. The  formulation specifically refers to the binary setting, where $c=1$, such that the concatenation of $P \in \mathbb{R}^{h \times k + 1}$.
%     \item We clarify that the model makes a final prediction based on the reweighted representation; R2 is correct in that $z$ is no longer used here; the base representation is considered as $p_{\text{BASE}}$.
%     \item We treat each dimension $h$ as a hyperparameter to afford maximum flexibility to the user for domain-specific applications. In our experiments, we trivially set this to the backbone dimension $r$.
%     \item In response to R2's comment, we have clarified in the paper that we compute the predictor's confidence using the maximum probability over all prediction classes. In the binary case used in experimental validation, we use the absolute value of the predictor logit as a proxy for this confidence.
%     \item Since submission, we have submitted to the official server and obtained new state-of-the-art scores on several SuperGLUE tasks using slicing functions: +\num{3.8/2.8} Avg. F1/acc. on CB, +\num{+2.8} acc. on COPA, +\num{2.5} acc. on WiC.
%     These gains are indeed with respect to strong baselines of pre-trained BERT models (\textsc{BERT++}) fine-tuned on the individual tasks.
%     We have added those full results with details about the slicing functions used in the appendix of the paper.
% \squishend

% \textbf{R3:} We thank R3 for their excellent suggestions.
% \squishlist
%     \item In practice, we apply a hyperparameter for each loss term for control in each application. For the purposes of this study, we set all weights to 1.
%     \item R3 asks how many slices our model can support. In our paper we operate on dozens of slices, but in an industrial collaboration, we have deployed the slicing architecture on thousands of production slices.
% \squishend

% \textbf{Summary:}
% In our paper, we proposed Slice-based Learning, a programming model in which \textit{slicing functions} (SFs), a programmer abstraction, can be used to improve performance on critical subsets (slices) of data with lower computational complexity and higher slice-specific performance than current methods.
% We review here how the high-level goals of Slice-based Learning inform our proposed architecture (Section 3.2).
% \begin{itemize}
%     \item Backbone: Our modeling approach is agnostic to the neural network architecture. We treat the backbone as a set of shared parameters for other modules, as is common in MTL formulations.
% \end{itemize}

\end{document}

### 2020-08-09 arxiv/setup.tex
author response
arxiv version begin

--- 2020-06-05 writeup/setup.tex
@@
-\section{Problem Formulation for Multi-Task Learning}
+\section{Preliminaries and Related Work}
 \label{sec_prelim}
@@
 
-\textbf{Problem setup.}
+\subsection{Problem Formulation for Multi-Task Learning}
+
 Suppose we have $t$ datasets, where $t$ is a fixed value that does not grow with the feature dimension $p$.
@@
 to the prediction loss $L(\hat{\beta}_t^{\STL})$ of the single-task estimator $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$.
-We say there is negative transfer if  $L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL})$, or positive transfer otherwise.
+We say there is negative transfer if  $L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL})$ and positive transfer otherwise.
 
@@
 %(ii) the positive effect from variance reduction;
+
+\subsection{Asymptotics for Single-Task Learning}
+
+\subsection{Related Work}
+
+We refer the interested readers to several excellent surveys on multi-task  learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
+Below, we describe several lines of work that are most related to this work.
+
+\textit{Theoretical works.}
+Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
+Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
+Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors optimally.
+The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+Our work is closely related to Wu et al. \cite{WZR20}.
+While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
+
+% Adding a regularization over $B$, e.g. .
+\textit{Methodological works.}
+Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
+Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
+Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
+%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
+We believe that our theoretical framework can apply to other approaches to multi-task learning.
+
+\textit{Random matrix theory.}
+The random matrix theory tool and related proof of our work fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
+For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.
+It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}.
+On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using the free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
+To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
 

### 2020-08-09 arxiv/transfer.tex
arxiv version begin
structure

--- 2020-06-09 writeup/transfer.tex
@@
-\section{Comparing Multi-Task Learning to Single-Task Learning}\label{sec_insight}
-
-%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
-We show theoretical implications for understanding the performance of multi-task learning.
-(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as tasks become more different.
-(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
-(c) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
-Finally, we extend our results from two tasks to many tasks with the same features.
-%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
-%We show how negative transfer occurs by varying task similarity or sample size.
-%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-
-\subsection{Analyzing the Bias-Variance Tradeoff using Random Matrix Theory}\label{sec_main}
+\section{The Bias-Variance Tradeoff using Random Matrix Theory}\label{sec_main}
 
@@
 We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
+
+\subsection{The Case of Two Tasks}
+
 \begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
@@
 	{\small\begin{align*}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}\lambda_i^2 a_1}{\hat{v}\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
 	\end{align*}}
@@
 
+\subsection{The Case of Multiple Tasks}
+
+Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+\begin{theorem}[Many tasks]\label{thm_many_tasks}
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
+	%that satisfy Assumption \ref{assm_secA2} in the appendix.
+	For the setting of $t$ tasks where $X_i = X$, for all $1\le i\le t$,
+	let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$ denote the linear model parameters.
+	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$.
+	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
+	Let $v_i$ denote the $i$-th row vector of $U_r$.
+	There exists a value $\delta = \oo \left( \|B^\star\|^2 + \sigma^2\right)$ such that
+	\squishlist
+		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\squishend
+\end{theorem}
+Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff beyond two tasks.
+Specifically, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of reduced variance and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
+The proof of \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+
+\section{Theoretical Implication}\label{sec_insight}
+
+%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
+We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
+We show theoretical implications for understanding the performance of multi-task learning.
+(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as tasks become more different.
+(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
+(c) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
+Finally, we extend our results from two tasks to many tasks with the same features.
+%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
+%We show how negative transfer occurs by varying task similarity or sample size.
+%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
+
 \subsection{Task Similarity}\label{sec_similarity}
@@
 	\squishend
-	Here {\small$\nu = (1-\oo(1))\min((1 - 1/\sqrt{\rho_1})^{-4}, (1 + 1/\sqrt{\rho_1})^{4})$}.
+	Here {\small$\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$}.
 	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
@@
 A key part of the analysis shows that $\hat{v}\approx 1$ in the isotropic model,
-thus simplifyling the result of Theorem \ref{thm_main_informal}.
+thus simplifying the result of Theorem \ref{thm_main_informal}.
 %, which is based on our main result described later in Theorem \ref{thm_model_shift}.
@@
 We validate our insight on this procedure in the experiments.
-
-\subsection{Extensions}
-
-Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-\begin{theorem}[Many tasks]\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	For the setting of $t$ tasks where $X_i = X$, for all $1\le i\le t$,
-	let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$ denote the linear model parameters.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$.
-	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-	Let $v_i$ denote the $i$-th row vector of $U_r$.
-	There exists a value $\delta = \oo \left( \|B^\star\|^2 + \sigma^2\right)$ such that
-	\squishlist
-		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
-\end{theorem}
-Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff beyond two tasks.
-Specifically, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of reduced variance and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
-The proof of \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.

### 2020-08-09 arxiv/experiments.tex
update

--- 2020-06-09 writeup/experiments.tex
@@
 
-\vspace{-0.05in}
 We validate our  algorithmic insights and then our theory.
@@
 
-{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
-The question is to predict positive or negative sentiment expressed in the text.
-We use an embedding layer with GloVe embeddings
+{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR) \cite{pang2005seeing}, sentence subjectivity (SUBJ) \cite{pang2004sentimental}, customer reviews (CR) \cite{hu2004mining}, question type (TREC) \cite{li2002learning}, opinion polarity (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) tasks \cite{socher2013recursive}.
+%The question is to predict positive or negative sentiment expressed in the text.
+We use an embedding layer with GloVe embeddings \cite{pennington2014glove}
 followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.
@@
 
-{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images.
+{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
 There are 14 diseases (tasks) for every image that we would like to predict.
-We use densenet121 as the shared module.
+We use densenet121 as the shared module \cite{huang2017densely}.
 %We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
@@
 		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
-		\caption{Data size}
+		\caption{Sample size}
 		\label{fig_ab_data}

### 2020-08-10 neurips20_response/response.tex

@@
 
-We thank all of our reviewers for carefully reading our work and providing insightful reviews.
-First, we address several main issues that are raised by the reviewers.
-Then, we respond to each individual reviewer's feedback.
+We thank the reviewers for their time and thoughtful feedback.
+Taking their helpful comments into account, we have sought to clarify the presentation of our work.
+We have also extended the bias-variance tradeoff from the two task case to multiple tasks (see description below), which addresses the main criticism by R1 and R2.
+%First, we address the main issues that are raised by the reviewers.
+%Then, we respond to each individual reviewer's feedback.
 
-\textbf{Motivation for our setting. [R1, R2, R3]}
+\textbf{Why do we focus on predicting a particular task? [R2]}
 As R2 pointed out, we focus on a situation where we have a target task for which we only have limited labeled data and several source tasks.
 We study when training the tasks together can benefit the target task.
-While this setting is different from traditional MTL, it is commonly encountered in practice. For example, the task of interest might be about predicting a rare event or classifying an Xray-scan.
+While this setting is different from traditional MTL that studies the average performance of all tasks, it is also a common setting in practice.
+For example, the task of interest might be about predicting a rare event or classifying an Xray-scan.
 For such settings, collecting large amounts of labeled data for the task is either not possible or very expensive, but auxiliary labeled data are often easier to obtain.
-Traditional MTL theory that studies the average performance of all tasks does not help predict when adding the source tasks provides positive transfer for the target task or not.
-Our work applies to these settings and takes a step towards filling the gap.
+Traditional MTL theory that studies the average performance of all tasks does not help predict whether training the tasks together can benefit the target task.
+Our theoretical framework applies to this setting and takes a step towards filling the gap.
+%We have included these discussion to our paper.
 
-\textbf{Extension to multiple tasks.}
-We thank R1 and R2 for raising the important question of whether our setting applies to multiple tasks.
-First, for multi-label settings where all tasks have the same features, i.e.
-$X_i = X$ for any $i$, our result in Theorem 3.6 provides a sharp bias-variance tradeoff of MTL and \textit{all of our insight for two tasks except covariate shift applies to multi-label settings}.
-Due to page limit we have not elaborated on this part in the submission, but we will elaborate the theoretical implication in the next version.
-The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.
+\textbf{What can we say for multiple tasks? [R1, R2]}
+%We thank R1 and R2 for raising the important question of whether our setting applies to multiple tasks.
+\textbf{(1)} We have focused on the two task setting in the submission to provide insight, since this is simplest setting which we don't understand how tasks transfer in MTL.
+\textbf{(2)} We understand that the setting of multiple tasks is more general, therefore, we have \textit{extended our result on bias-variance tradeoff of two tasks to multiple tasks}.
+That is, we can now show that \textit{as long as the output dimension of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
+We have included this result in the updated draft.
+\textbf{(3)} For multi-label settings where all tasks have the same features, i.e.
+$X_i = X$ for any $i$, using Theorem 3.6 \textit{all of our insight for two tasks except covariate shift applies to multi-label settings} (covariate shift does not apply since tasks have the same features).
+%The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.
+%Due to page limit we have not elaborated on this part in the submission, but we will elaborate the theoretical implication of this result for multiple tasks in the next version.
 
-Second, for settings where different tasks have different features, we can still extend our qualitative insight here.
-That is, we can show that \textit{as long as the dimension of the shared layer ($B$) is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
-We will include this result in the next version.
-
-\textbf{Clarifying writing. [R2, R3]}
-We thank R2 and R3 for providing numerous detailed feedback that help us improve writing.
+\textbf{Writing: [R2, R3]}
+We have corrected the typos that R2 pointed out and clarified the issues that R3 raised.
+\textbf{(1)} L112-118: we use $t$ to denote the number of tasks hence for two tasks $t = 2$.
+%We have improved this part to be more consistent in the use of $t$.
+\textbf{(2)} Validation set size: we only need it to be larger than the size of the hidden layer times the number of tasks, which can be much smaller compared to the size of the training set (cf.
+L108).
+\textbf{(3)} Def. of the prediction loss L113: the expectation is over a test sample $x$ whose label is $x^{\top}\beta_t$.
+Taking expectation over $\varepsilon$ gives  the bias-variance decomposition, following standard linear regression literature [17,18].
 
 \textbf{R1:}
+We thank R1 for suggesting that we look at qualitative predictions of Thm 3.6 as in the two-task case, which we have added in the updated draft.
+%As mentioned above, we have extended our result to show that the variance of the MTL estimator decreases compared to STL and the bias increases.
+%Hence the bias-variance tradeoff still decides whether MTL outperforms STL.
+%Task similarity appears in the projection term $\|{v_t}\|$.
+For task similarity, the more similar tasks are, the closer $\|{v_t}\|$ is to 1 and the more variance reduces, which leads to positive transfer as in Prop 3.3.
+For sample ratio, the more dissimilar tasks are, the more bias increases by source task samples, which leads to negative transfer as in Prop 3.4.
+R1 asks how does our method compares to standard techniques such as loss reweighing.
+Note that our method is equivalent to increasing the weight of a task until performance drops.
+Our method is preferable to loss reweighting since we require less compute over the training data as shown in Section 4.2.
+We thank R1 for pointing out the vague use of "similar performance" in experiments, which we have replaced w/ the accuracy numbers (that are comparable).
+%it means that the average accuracy of our method for all tasks is the same as the average accuracy of standard MTL training (cf.
+line 295).
+%Thus, our method achieves the same average accuracy as MTL with less computation.
+%We will clarify this part in the next version.
+
+Regarding R1's comment about computing similarity via distance between classifier parameters, we have tried it for predicting whether MTL outperforms STL (smaller distance implies better transfer) but the result is worse than Table 1.
+We suspect the reason is that the distance mainly captures difference between the trained model but does not capture other properties of task data.
+%The lesson that we have learned from our work is that in order to decide whether MTL outperforms STL, all three properties including model similarity, sample ratio, and covariate shift provably matter.
+%Thus, in order to define such a similarity measure, one has to carefully control the impact of the other two properties in addition to measuring the distance between parameters.
+We will include this discussion in the next version.
+%
+%R1 asks "how do the bounds differ compared to previous theory".
+The closest work to ours is [15] and that work uses standard concentration bounds to show that when two tasks are sufficiently similar, MTL guarantees positive transfer.
+Our result in Thm 3.2 does not make such an assumption by using advanced tools from random matrix theory.
+This also allows us to study the impact of varying sample sizes and covariate shift, both of which cannot be studied using standard concentration bounds.
 
 \textbf{R2:}
+We thank R2 for bringing up the confusion of which sample size regime does our theory/algorithm apply, which we have clarified in the updated draft.
+%Regarding R2's comments on motivation and theoretical limitation, as stated above, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
+While our setting is different from traditional MTL that measures average performance over all tasks, it is also a common setting in practice where MTL is used.
+\textbf{(1)} R2 is correct that "our theory applies when the sample sizes are tens or hundreds of feature dimension".
+We think this is a reasonable regime to consider; for example, in our sentiment analysis experiment, the feature dimension of a sentence is 300 and the training set size ranges from 3 to 10 thousand.
+%\textbf{(2)} As shown in Prop. 3.4, the ratio of sample sizes, instead of the sample size of a task, decides whether MTL can help STL.
+%Our theory makes no assumption on sample ratio (or imbalance) and applies to reasonable regimes (e.g. Fig 1(b,c)).
+\textbf{(2)} R2 mentions "having imbalanced sample size btw source/target task": Our incremental training scheme does not assume that the tasks have imbalanced sample size; for example, in our sentiment analysis experiment, we have observed that our method can be effective even when the source task is smaller than the target.
+As shown in our theory, the transition threshold between positive/negative transfer provably depends on task similarity and can be less than one (Prop. 3.4).
+
+We thank R2 for pointing out the connection between our incremental training procedure and curriculum learning.
+We are not aware of any previous work that proposes such an idea in MTL while having a strong theoretical basis.
+Adding more context, there is an ongoing discussion of how much data from each task the model should be trained on (cf. Google T5 and refs therein).
+While we have focused on evaluating training efficiency, it's conceivable that by combining our procedure w/ other ideas one might get better final performance of the target task.
+It is an interesting research question to further investigate the idea in future work.
+%R2 asks about why "the middle part btw negative/positive transfer cannot be predicted correctly".
+%\textbf{(1)} We emphasize that this experiment only uses STL performance without any MTL training.
+%\textbf{(2)} The middle part where the STL performances between tasks are close
+%One application of such a result is as a test diagnostic for task selection
+%it should not be taken for granted that STL information can predict MTL performance at all!
+%Before this work, we are not aware of any previous work that
 
 \textbf{R3:}
+Here's our detailed response.
+\textbf{L108:}
+%The validation set size $p^{0.99}$ is just an example and can be set smaller.
+We disagree that "the validation set is much larger than the training set" is suggested anywhere in the paper.
+\textbf{L113:} We disagree that "there are duplicate notations" in this line - $t$ is the number of tasks not samples.
+\textbf{L117:} The sample covariance of task 1 is \textit{not $\Sigma_1$} but $X_1^{\top}X_1$ and it shows up in both eqs.
+\textbf{L187:} $\gamma$ is a free parameter and by varying it one can recover the entire precision-recall curve.
+\textbf{L220:} Our theory provides a theoretical basis for the algorithm.
+For two tasks, the algorithm can provably find the optimal sample ratio.
+As shown in Fig 1b, the performance curve, which is a quadratic function, has a single peak and our algorithm stops at the peak.
+The fact that the curve is quadratic is shown in our proof and we have added the connection to the updated draft.
 

### 2020-08-10 arxiv/main.tex
response
restructure

@@
 
-\title{Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions}
+\title{Information Transfer in Multi-Task Learning via a Bias-Variance Tradeoff}
 \maketitle
@@
 \input{setup}
+\input{proofs_sec3}
 \input{transfer}
@@
 \appendix
-\input{proofs_sec3}
+\textbf{Organizations.}
+The appendix is organized as follows.
+In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
+In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
+In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
+In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
+In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
+Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.
+
+\input{proof_appd}
 \input{proof_main}
+\input{proof_extension}
 \input{proof_examples}
-\input{proof_extension}
-\input{proof_appd}
 \input{app_exp}

### 2020-08-10 arxiv/proofs_sec3.tex
restructure

--- 2020-06-11 writeup/proofs_sec3.tex
@@
-\textbf{Organizations.}
-The appendix is organized as follows.
-In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
-In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
-In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
-In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
-In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
-Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.
-
-\section{Extended Background and Related Work}\label{app_proof_sec3}
+\subsection{Extended Background and Related Work}\label{app_proof_sec3}
 
@@
 For such models, their output dimension plays an important role of regularization \cite{KD12}.
-Linear models in the context of multi-task learning have been studied in various settings, including representation learning \cite{BHKL19}, online learning \cite{CCG10,DCSP18}, and sparse regression \cite{LPVT11}.
+Linear models in multi-task learning have been studied in various settings, including representation learning \cite{BHKL19}, online learning \cite{CCG10,DCSP18}, and sparse regression \cite{LPVT11}.

### 2020-08-10 arxiv/experiments.tex
restructure

@@
 
-\vspace{-0.07in}
 \subsection{Experimental Setup}
@@
 We measure the test accuracy of predicting a target task.
-We measure computional cost by summing over all epochs the number of samples used in every epoch.
+We measure computational cost by summing over all epochs the number of samples used in every epoch.
 
-\vspace{-0.07in}
-\subsection{Experimental Results}\label{sec_exp_res}
+\subsection{Simulation Studies}
+
+\subsection{Validating the Theoretical Implication}\label{sec_exp_ab}
+
+We first validate our theoretical results in Section \ref{sec_similarity} and \ref{sec_data_size}.
+In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
+We select each task pair based on our domain knowledge.
+We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
+In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
+Finally, we validate the algorithmic consequence of Section \ref{sec_covshift}.
+In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL.
+We average the results over all 15 task pairs.
+The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
+The rest of experimental procedures are left to Appendix \ref{app_it}.
+
+\subsection{Validating the Algorithmic Consequences}\label{sec_exp_res}
 
@@
 \end{figure}
-
-\vspace{-0.07in}
-\subsection{Validating the Theoretical Results}\label{sec_exp_ab}
-
-We first validate our theoretical results in Section \ref{sec_similarity} and \ref{sec_data_size}.
-In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
-We select each task pair based on our domain knowledge.
-We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
-In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
-Finally, we validate the algorithmic consequence of Section \ref{sec_covshift}.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL.
-We average the results over all 15 task pairs.
-The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
-The rest of experimental procedures are left to Appendix \ref{app_it}.

### 2020-08-10 arxiv/conclusions.tex
update ref

--- 2020-06-11 writeup/related.tex
@@
-\vspace{-0.05in}
-\section{Related Work}
-\vspace{-0.05in}
-
-We refer the interested readers to several excellent surveys on multi-task  learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
-Below, we describe several lines of work that are most related to this work.
-
-\textit{Theoretical works.}
-Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
-Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors optimally.
-The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-Our work is closely related to Wu et al. \cite{WZR20}.
-While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-
-% Adding a regularization over $B$, e.g. .
-\textit{Methodological works.}
-Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\textit{Random matrix theory.}
-The random matrix theory tool and related proof of our work fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
-For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.
-It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}.
-On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using the free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
-To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
-
-\vspace{-0.05in}
 \section{Conclusions and Open Problems}
-\vspace{-0.05in}
 
@@
 
+\iffalse
 \newpage
@@
 Our proposed metric can provide guidance for selecting which tasks should be trained together in a multi-task model.
+\fi
 

### 2020-08-10 arxiv/proof_main.tex
finish restructure

@@
-\section{Proof for the Case of Two Tasks}\label{app_proof_main_thm}
+\section{Proof of Main Results}
+
+\subsection{Two Tasks}\label{app_proof_main_thm}
 
@@
 \end{proof}
+
+\subsection{Multiple Tasks}\label{app_proof_many_tasks}
+
+%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
+Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
+The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+
+%In this section we consider the setting with $k$ many that have the same covariates.
+%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+
+\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
+In this setting, we need to study the following loss function:
+\begin{align}
+	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
+\end{align}
+%In order to prove Theorem \ref{thm_many_tasks}, we will derive a closed form solution for equation \eqref{eq_mtl_same_cov}. \todo{check!}
+For any fixed $W_1, W_2, \dots, W_t \in \R^r$, we can derive a closed form solution for $B$ as
+	\begin{align*}
+		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
+		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1},
+	\end{align*}
+	where we denote $\cal W \in\real^{r\times t}$ as $\cal W=[W_1, W_2, \dots, W_t]$.
+	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
+Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use concentration to get the validation loss as
+\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
+Here $\val(\cal W)$ is defined as
+%it remains to consider minimizing the validation loss
+	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari}(\cal W),$$
+where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
+	\begin{align*}
+		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
+	\end{align*}
+	and the variance term $\delta_{\vari}(\cal W)$ can be calculated as
+	\begin{align*}
+		\delta_{\vari}(\cal W):= \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+	\end{align*}
+It suffices to minimize $\delta_{\bias}(\cal W)$ over $\cal W$, since both $t \sigma^2$ and $\delta_{\vari}$ do not depend on $\cal W$.
+
+We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{k\times k}$, whose $(i,j)$-th entry is equal to $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
+	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
+	Now we can write $\delta_{\bias}(\cal W)$ succinctly as
+	\begin{align*}
+		\delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
+	\end{align*}
+	From this equation we can solve the minimizer optimally as $Q_0\equiv  \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=U_{r}U_r^{\top}$.
+On the other hand, let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
+We claim that $\hat Q$ satisfies
+	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\| = \oo(1) \quad \text{w.h.p.}\ee
+	In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by \eqref{eq_isometric}, we obtain that
+	$$   \val(\hat {\cal W}) + t  \sigma^2 > (\val( {\cal W}_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
+	that is, $\hat {\cal W}$ is not a minimizer. This leads to a contradiction.
+
+	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r U_r(i) +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that
+	\begin{align*}
+		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
+		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
+	\end{align*}
+	with high probability, where we used Lemma \ref{lem_minv} in the last step. Similar, by Lemma \ref{lem_minv} we have
+	$$\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
+Combining the above two estimates, we conclude the proof.
+\end{proof}
+%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
+%\begin{itemize}
+%	\item The de-noising effect of multi-task learning.
+%	\item Multi-task training vs single-task training can be either positive or negative.
+%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
+%\end{itemize}

### 2020-08-10 arxiv/setup.tex
restructure
update
finish restructure

@@
-\section{Preliminaries and Related Work}
+\section{Problem Formulation and Related Work}
 \label{sec_prelim}
@@
 
-\subsection{Problem Formulation for Multi-Task Learning}
+\subsection{Problem Formulation}
 
@@
 
+\subsection{Bias and Variance}
+
 As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL})$ into a bias term and a variance term as follows (derived in Appendix \ref{app_proof_sec3}).
@@
 %(ii) the positive effect from variance reduction;
-
-\subsection{Asymptotics for Single-Task Learning}
 
@@
 %Hence our result provides a necessary tool to analyze MTL in high dimensions.
+
+\subsection{Extended Background and Related Work}\label{app_proof_sec3}
+
+We restate our linear regression setting, in particular the moment assumption required by our random matrix model.
+We then derive a closed-form solution of the multi-task estimator that is defined in Section \ref{sec_prelim}.
+Finally, we describe further related work that is covered in the main text.
+%\section{Missing Details of Problem Formulation}
+
+%\textbf{Assumptions on task data generation.}
+First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
+
+\begin{assumption}[Moment assumptions]\label{assm_secA1}
+We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrix, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
+entries with mean zero and variance one.
+Note that the rows of $X$ are i.i.d.
+centered random vectors with covariance matrix $\Sigma$.
+For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
+\begin{equation}\label{assmAhigh}
+\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
+\end{equation}
+ We assume that $n=\rho p$ for some fixed constant $\rho>1$.
+Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
+Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
+\end{assumption}
+Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
+If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
+We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} in Section \ref{sec locallaw1}.
+
+Then we make the following assumptions on the data models.
+\begin{assumption}[Linear regression model]\label{assm_secA2}
+For some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants.
+$\e_i\in \R^{n_i}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
+\end{assumption}
+
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
+
+Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
+From \cite{WZR20}, we know that we need to explicitly restrict the output dimension $r$ of $B$ so that there is transfer between the two tasks.
+Hence for the case of two tasks, we consider the setting where $r=1$.
+For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to
+\begin{align}\label{eq_mtl_2task}
+	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
+\end{align}
+where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
+\begin{align}
+	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
+	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
+	&= \frac{1}{w_2}\left[\beta_2 + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+\nonumber
+\end{align}
+As a remark, when $w_1 = w_2 = 1$, we obtain linear regression.
+If $\beta_1$ is a scaling of $\beta_2$, then  $w_1, w_2$ can be scaled accordingly to fix both tasks more accurately than linear regression.
+
+%For the discussions below, we assume that the entries of $\e_1$ and $\e_2$ all have the same variance $\sigma^2$.
+This holds for most parts of our discussion, except in Proposition \ref{prop_var_transition}.
+We will derive different expressions for the validation loss and the test error
+
+Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
+With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
+We assume that $N_1$ and $N_2$ satisfy $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
+Then we write the validation loss in \eqref{eq_mtl_eval} as
+\begin{align}\label{eq_mtl_2tasktilde}
+	g(w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
+\end{align}
+Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that the optimal solution of $g$ only depends on the ratio $v:=w_1/w_2$.
+Hence we overload the notation by writing $g(v)$ in the following discussion.
+The expectation of $g(v)$ can be written as follows.
+\begin{align*}
+		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
+	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
+	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
+		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
+		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{eq_val_mtl}
+\end{align*}
+
+\begin{claim}
+	In the setting described above, we have that
+	\be\label{approxvalid}
+		g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
+	\ee
+\end{claim}
+\begin{proof}
+	We use the fact that our random vectors have i.i.d. entries.
+%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+	Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
+$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
+Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d.
+centered entries, we can use the concentration result, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
+\begin{align*}
+\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
+&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+\end{align*}
+with high probability. Thus we obtain that
+$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
+ again the concentration result, Lemma \ref{largedeviation}, we get that
+$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+with high probability.
+%-----old-------
+%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+%\begin{align}
+%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
+%\end{align}
+%\nc
+%------------------
+Thus we conclude the proof.
+\end{proof}
+
+Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
+Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
+Now we can define the multi-task learning estimator for the target task as
+	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
+%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task".
+%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
+%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
+The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
+\begin{align}
+	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
+			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
+\end{align}
+which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
+
+\textbf{Extended related work.}
+Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
+The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
+For such models, their output dimension plays an important role of regularization \cite{KD12}.
+Linear models in multi-task learning have been studied in various settings, including representation learning \cite{BHKL19}, online learning \cite{CCG10,DCSP18}, and sparse regression \cite{LPVT11}.

### 2020-08-10 arxiv/intro.tex
author response
restructure

--- 2020-06-05 writeup/intro.tex
@@
-\vspace{-0.3in}
 \begin{abstract}
-\vspace{-0.05in}
 	Multi-task learning is a powerful approach in many applications such as image and text classification.
@@
 
-\vspace{-0.15in}
 \section{Introduction}
@@
 	\end{subfigure}
+	\vspace{-0.05in}
 	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
@@
 	\label{fig_model_shift_phasetrans}
-	\vspace{-0.3in}
+	\vspace{-0.2in}
 \end{figure}
@@
 Finally, we validate our three theoretical findings on sentiment analysis tasks.
+
+\paragraph{Organizations.}
+The appendix is organized as follows.
+In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
+In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
+In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
+In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
+In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
+Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.

### 2020-08-10 arxiv/experiments.tex
reorg

@@
 \end{figure}
+
+\subsection{Missing Details from the Experiments}\label{app_experiments}
+
+\subsection{Synthetic Settings}\label{app_synthetic}
+	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
+	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
+	\squishlist
+		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
+	The noise level is $\sigma = 5$.
+	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
+	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
+	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
+		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
+	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
+	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
+	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
+	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
+	This can be achieved similarly by rescaling the task data.
+	\squishend
+
+\subsection{Image and Text Classification Settings}\label{app_it}
+
+For the text classification experiment, we encode each word using the GLoVe word embeddings.%
+\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
+We evaluate three model choices.
+For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
+For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
+
+\textit{Predicting transfer effect via STL results.}
+We simplify the setup of this experiment by fixing the sample sizes of every task pair.
+For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
+We randomly sample these many data points from the task.
+The sample size of the target task is $1000$.
+For image classification tasks, the training sample size is $10,000$ for every task.
+
+\textit{Mitigating negative transfer via incremental training.}
+For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
+We add $20\%$ of source task samples for every $T = 2$ epochs.
+The total number of epochs is $20$.
+We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
+
+For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
+Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
+We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
+We run $20$ epochs in total.
+
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+			\For{$j = 1,\dots, T$}
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+			\EndFor
+			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+				\State \textbf{break}
+			\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
+\textit{Validating the Theoretical Results.}
+We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
+\squishlist
+	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
+First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
+Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
+TREC is less similar to MR because the task is about question types.
+Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
+	\item Sample size: We vary the sample size of the source task from $100$ to $3000$.
+	\item Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
+	We fix the sample size of the target task as $1000$.
+\squishend
+
+%We validate that MTL performs better when the source task is more similar to the target task.
+%We show the result on the sentiment analysis tasks.
+%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+%Figure \ref{fig_ab_sim} confirms the result.
+%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
+
+\textbf{Further results of the covariance alignment procedure.}
+Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
+In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
+In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
+In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
+One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
+An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
+We leave this question for future work.
+%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
+
+\begin{figure}[!h]
+	\centering
+	\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+		\caption{Task pair TREC and CR}
+		\label{fig_cov_a}
+	\end{subfigure}\hfill
+		\begin{subfigure}[b]{0.48\textwidth}
+		\centering
+		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+		\caption{Task pair MR and SST}
+			\label{fig_cov_b}
+	\end{subfigure}
+	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
+	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
+	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
+	\label{fig_covariate_app}
+\end{figure}

### 2020-08-10 arxiv/proof_examples.tex
author response
reorg

--- 2020-06-11 writeup/proof_examples.tex
@@
 \section{Proofs for Isotropic and Covariate Shifted Settings}\label{app_iso_cov}
+
+For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows.
+\begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
+		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+		$\beta_2$ is a random vector with i.i.d.
+entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_1$ is a random vector such that $(\beta_1 - \beta_2)$ is a random vector with i.i.d.
+entries with mean $0$, variance $d^2$ and all moments.
+Denote
+		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}.$
+	Then we have with high probability,
+		\begin{align*}
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias}, \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}.
+		\end{align*}
+\end{lemma}
+
+\begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
+The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Theorem \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
+We only describe the main difference.
+
+For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
+entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
+Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
+\begin{align}
+&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
+\end{align}
+where we denoted $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}.
+Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
+\begin{align*}
+v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
+\end{align*}
+Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
+\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
+where
+$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
+Note that $\delta^\star_{\bias}(v) \sim p$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
+\be\label{replaceest}
+  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
+\ee
+Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Theorem \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
+In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term, We omit the details.
+\end{proof}
 
@@
 Let $\hat w$ the minimizer of $h(v)$. The proof consists of two steps.
-\begin{itemize}
+\squishlist
 	\item First, we show that $\hat{w}$ is close to $1$.
 	\item Second, with \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get \eqref{simple1}.
-\end{itemize}
+\squishend
 %For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
@@
 
-\subsection{Missing Proofs regarding Task Similarity}\label{app_proof_31}
+\subsection{Task Similarity}\label{app_proof_31}
 
@@
 
-\subsection{Missing Proofs regarding Sample Size} \label{app_proof_32}
+\subsection{Sample Size} \label{app_proof_32}
 We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.
@@
 
-\subsection{Missing Proofs regarding Covariate Shift}\label{app_proof_33}
+\subsection{Covariate Shift}\label{app_proof_33}
 

### 2020-08-10 arxiv/proof_main.tex
reorg

@@
 
-\begin{lemma}[Bias bound]\label{lem_cov_derivative}
-In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
-&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
-\end{split}
-\end{equation}
-with high probability, where $a_{3}$ and $a_4$ satisfy the following system of linear equations:
-\begin{gather}\label{eq_a34extra}
-		\left(\rho_2  a_2^{-2}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
-		= b_0, \quad \left(\rho_1 a_1^{-2} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-Here $b_0$, $b_1$ and $b_2$ are defined as
-$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
-\end{lemma}
 %We will give the proof of this lemma in Section \ref{sec_maintools}.
@@
 
-For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
-\begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
-		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_2$ is a random vector with i.i.d.
-entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_1$ is a random vector such that $(\beta_1 - \beta_2)$ is a random vector with i.i.d.
-entries with mean $0$, variance $d^2$ and all moments.
-Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}.$
-	Then we have with high probability,
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}.
-		\end{align*}
-\end{lemma}
-
-\begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
-The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Theorem \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
-We only describe the main difference.
-
-For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
-entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
-Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
-\begin{align}
-&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
-\end{align}
-where we denoted $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}.
-Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
-\begin{align*}
-v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
-\end{align*}
-Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
-\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
-where 
-$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim p$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get 
-\be\label{replaceest}
-  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
-\ee
-Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Theorem \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
-In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term, We omit the details.
-\end{proof}
-
 \subsection{Multiple Tasks}\label{app_proof_many_tasks}

### 2020-08-10 arxiv/setup.tex
reorg

--- 2020-08-09 arxiv/setup.tex
@@
 
-\subsection{Asymptotics for Single-Task Learning}
-
 \subsection{Related Work}
@@
 We refer the interested readers to several excellent surveys on multi-task  learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
+Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
+The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
+For such models, their output dimension plays an important role of regularization \cite{KD12}.
+Linear models in multi-task learning have been studied in various settings, including representation learning \cite{BHKL19}, online learning \cite{CCG10,DCSP18}, and sparse regression \cite{LPVT11}.
 Below, we describe several lines of work that are most related to this work.
@@
 %Hence our result provides a necessary tool to analyze MTL in high dimensions.
+
+%\subsection{Extended Background and Related Work}\label{app_proof_sec3}
+
+%We restate our linear regression setting, in particular the moment assumption required by our random matrix model.
+%We then derive a closed-form solution of the multi-task estimator that is defined in Section \ref{sec_prelim}.
+%Finally, we describe further related work that is covered in the main text.
+%\section{Missing Details of Problem Formulation}
+%\textbf{Assumptions on task data generation.}
+
+\paragraph{Notations.}
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
+For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.

### 2020-08-10 arxiv/transfer.tex
restructure
update
reorg

@@
-\section{The Bias-Variance Tradeoff using Random Matrix Theory}\label{sec_main}
+\section{Main Results}
 
-A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
-Our main technical contribution is to extend this result to two tasks.
-We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
+\subsection{Two Tasks}
 
-\subsection{The Case of Two Tasks}
-
-\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
-	In the setting of two tasks,
-	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
-	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
-	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
-	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-	{\small\begin{align*}%\label{eq_introX1X2}
-		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-	\end{align*}}%
-	where $a_1, a_2$ are solutions of the following equations:
-	{\small\begin{align*}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-	\end{align*}}
-%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-\end{lemma}
-Lemma \ref{lem_cov_shift_informal} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
-For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task model distance in addition to sample size and covariate shift holds (cf.
-Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
-Combining the two lemmas, we provide a sharp analysis of the bias-variance tradeoff of the multi-task estimator.
-For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
 \begin{theorem}[Two tasks]\label{thm_main_informal}
@@
 
-\subsection{The Case of Multiple Tasks}
+%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
+%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
+%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+%Based on the result, we show how to determine positive versus negative transfer as follows.
+%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
+
+Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
+From \cite{WZR20}, we know that we need to explicitly restrict the output dimension $r$ of $B$ so that there is transfer between the two tasks.
+Hence for the case of two tasks, we consider the setting where $r=1$.
+For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to
+\begin{align}\label{eq_mtl_2task}
+	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
+\end{align}
+where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
+\begin{align}
+	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
+	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
+	&= \frac{1}{w_2}\left[\beta_2 + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+\nonumber
+\end{align}
+As a remark, when $w_1 = w_2 = 1$, we obtain linear regression.
+If $\beta_1$ is a scaling of $\beta_2$, then  $w_1, w_2$ can be scaled accordingly to fix both tasks more accurately than linear regression.
+
+%For the discussions below, we assume that the entries of $\e_1$ and $\e_2$ all have the same variance $\sigma^2$.
+This holds for most parts of our discussion, except in Proposition \ref{prop_var_transition}.
+We will derive different expressions for the validation loss and the test error
+
+Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
+With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
+We assume that $N_1$ and $N_2$ satisfy $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
+Then we write the validation loss in \eqref{eq_mtl_eval} as
+\begin{align}\label{eq_mtl_2tasktilde}
+	g(w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
+\end{align}
+Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that the optimal solution of $g$ only depends on the ratio $v:=w_1/w_2$.
+Hence we overload the notation by writing $g(v)$ in the following discussion.
+The expectation of $g(v)$ can be written as follows.
+\begin{align*}
+		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
+	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
+	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
+		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
+		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{eq_val_mtl}
+\end{align*}
+
+\begin{claim}
+	In the setting described above, we have that
+	\be\label{approxvalid}
+		g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
+	\ee
+\end{claim}
+\begin{proof}
+	We use the fact that our random vectors have i.i.d. entries.
+%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+	Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
+$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
+Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d.
+centered entries, we can use the concentration result, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
+\begin{align*}
+\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
+&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+\end{align*}
+with high probability. Thus we obtain that
+$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
+ again the concentration result, Lemma \ref{largedeviation}, we get that
+$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+with high probability.
+%-----old-------
+%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+%\begin{align}
+%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
+%\end{align}
+%\nc
+%------------------
+Thus we conclude the proof.
+\end{proof}
+
+Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
+Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
+Now we can define the multi-task learning estimator for the target task as
+	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
+%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task".
+%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
+%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
+The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
+\begin{align}
+	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
+			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
+\end{align}
+which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
+
+\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
+	In the setting of two tasks,
+	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
+	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
+	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
+	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
+	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
+	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+	{\small\begin{align*}%\label{eq_introX1X2}
+		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
+		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
+	\end{align*}}%
+	where $a_1, a_2$ are solutions of the following equations:
+	{\small\begin{align*}
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+	\end{align*}}
+%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+\end{lemma}
+Lemma \ref{lem_cov_shift_informal} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
+As a remark, the concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
+For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task model distance in addition to sample size and covariate shift holds (cf.
+Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
+
+\begin{lemma}[Bias bound]\label{lem_cov_derivative}
+In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
+\begin{equation}\label{lem_cov_derv_eq}
+\begin{split}
+&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
+&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
+\end{split}
+\end{equation}
+with high probability, where $a_{3}$ and $a_4$ satisfy the following system of linear equations:
+\begin{gather}\label{eq_a34extra}
+		\left(\rho_2  a_2^{-2}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
+		= b_0, \quad \left(\rho_1 a_1^{-2} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .
+%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
+%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
+	\end{gather}
+Here $b_0$, $b_1$ and $b_2$ are defined as
+$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
+\end{lemma}
+
+Combining the two lemmas, we provide a sharp analysis of the bias-variance tradeoff of the multi-task estimator.
+
+\subsection{Multiple Tasks}\label{sec_main}
+
+A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
+Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
+Our main technical contribution is to extend this result to two tasks.
+We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
+
+%\subsection{The Case of Two Tasks}
+
+%\subsection{The Case of Multiple Tasks}
 

### 2020-08-10 arxiv/experiments.tex
reorg

@@
 
+\paragraph{Synthetic Settings}\label{app_synthetic}
+	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
+	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
+	\squishlist
+		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
+	The noise level is $\sigma = 5$.
+	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
+	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
+	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
+		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
+	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
+	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
+	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
+	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
+	This can be achieved similarly by rescaling the task data.
+	\squishend
+
+\paragraph{Image and Text Classification Settings}\label{app_it}
+
+For the text classification experiment, we encode each word using the GLoVe word embeddings.%
+\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
+We evaluate three model choices.
+For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
+For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
+
+\textit{Predicting transfer effect via STL results.}
+We simplify the setup of this experiment by fixing the sample sizes of every task pair.
+For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
+We randomly sample these many data points from the task.
+The sample size of the target task is $1000$.
+For image classification tasks, the training sample size is $10,000$ for every task.
+
+\textit{Mitigating negative transfer via incremental training.}
+For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
+We add $20\%$ of source task samples for every $T = 2$ epochs.
+The total number of epochs is $20$.
+We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
+
+For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
+Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
+We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
+We run $20$ epochs in total.
 %\textbf{The training procedure and baseline.}
@@
 
-\subsection{Missing Details from the Experiments}\label{app_experiments}
-
-\subsection{Synthetic Settings}\label{app_synthetic}
-	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
-	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
-	\squishlist
-		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
-	The noise level is $\sigma = 5$.
-	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
-	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
-	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
-		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
-	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
-		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
-	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
-	This can be achieved similarly by rescaling the task data.
-	\squishend
-
-\subsection{Image and Text Classification Settings}\label{app_it}
-
-For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-We evaluate three model choices.
-For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
-For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
-
-\textit{Predicting transfer effect via STL results.}
-We simplify the setup of this experiment by fixing the sample sizes of every task pair.
-For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
-We randomly sample these many data points from the task.
-The sample size of the target task is $1000$.
-For image classification tasks, the training sample size is $10,000$ for every task.
-
-\textit{Mitigating negative transfer via incremental training.}
-For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
-We add $20\%$ of source task samples for every $T = 2$ epochs.
-The total number of epochs is $20$.
-We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
-
-For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
-Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
-We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
-We run $20$ epochs in total.
-
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
 \textit{Validating the Theoretical Results.}

### 2020-08-10 arxiv/transfer.tex
reorg

@@
 \section{Main Results}
+
+\begin{proposition}[Bias-variance tradeoff]
+	Variance always reduces and bias always increases.
+\end{proposition}
 
@@
 
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+			\For{$j = 1,\dots, T$}
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+			\EndFor
+			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+				\State \textbf{break}
+			\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
 \subsection{Covariate Shift}\label{sec_covshift}

### 2020-08-11 neurips20_response/response.tex
response

@@
 \usepackage{enumitem}
-
+\usepackage{mathabx}
 \usepackage{xcolor}
@@
 We thank the reviewers for their time and thoughtful feedback.
-Taking their helpful comments into account, we have sought to clarify the presentation of our work.
-We have also extended the bias-variance tradeoff from the two task case to multiple tasks (see description below), which addresses the main criticism by R1 and R2.
+Taking their helpful comments into account, we have sought to clarify the presentation of our work and  multiple tasks. %, which addresses the main criticism by R1 and R2.
+Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction, in response to the main criticism by R1 and R2 (L11-17).
 %First, we address the main issues that are raised by the reviewers.
@@
 
-\textbf{Why do we focus on predicting a particular task? [R2]}
-As R2 pointed out, we focus on a situation where we have a target task for which we only have limited labeled data and several source tasks.
+\vspace{-0.025in}
+\textbf{Predicting a particular task using MTL? [R2]}
+As R2 pointed out, we focus on a situation where we have a target task for which we only have limited labeled data and a source task.
 We study when training the tasks together can benefit the target task.
-While this setting is different from traditional MTL that studies the average performance of all tasks, it is also a common setting in practice.
-For example, the task of interest might be about predicting a rare event or classifying an Xray-scan.
-For such settings, collecting large amounts of labeled data for the task is either not possible or very expensive, but auxiliary labeled data are often easier to obtain.
-Traditional MTL theory that studies the average performance of all tasks does not help predict whether training the tasks together can benefit the target task.
-Our theoretical framework applies to this setting and takes a step towards filling the gap.
+While this setting is different from traditional MTL that studies the avg performance of all tasks, it is also a common setting for MTL in practice.
+For example, for predicting a rare event or classifying an Xray-scan, collecting large amounts of labeled data is either not possible or very expensive, but auxiliary labeled data are often easier to obtain.
+Traditional MTL theory that studies the average performance of all tasks does not predict whether using MTL can benefit the target task.
+Our work applies to this setting and takes a step towards filling the gap.
 %We have included these discussion to our paper.
 
+\vspace{-0.025in}
 \textbf{What can we say for multiple tasks? [R1, R2]}
 %We thank R1 and R2 for raising the important question of whether our setting applies to multiple tasks.
-\textbf{(1)} We have focused on the two task setting in the submission to provide insight, since this is simplest setting which we don't understand how tasks transfer in MTL.
-\textbf{(2)} We understand that the setting of multiple tasks is more general, therefore, we have \textit{extended our result on bias-variance tradeoff of two tasks to multiple tasks}.
-That is, we can now show that \textit{as long as the output dimension of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
-We have included this result in the updated draft.
-\textbf{(3)} For multi-label settings where all tasks have the same features, i.e.
-$X_i = X$ for any $i$, using Theorem 3.6 \textit{all of our insight for two tasks except covariate shift applies to multi-label settings} (covariate shift does not apply since tasks have the same features).
+We have focused on two tasks in the submission to provide insight, since this is the simplest setting.
+We understand that having multiple tasks is more general, therefore, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
+\textbf{(1)} We can now show that \textit{as long as the output dimension of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
+We have included this result in the draft.
+\textbf{(2)} For multi-label settings where all tasks have the same features, i.e.
+$X_i = X$ for any $i$, using Thm 3.6 \textit{all of our insight for two tasks still applies except covariate shift} (covariate shift doesn't apply since tasks have the same features).
 %The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.
@@
 
+\vspace{-0.025in}
 \textbf{Writing: [R2, R3]}
@@
 
+\vspace{-0.025in}
 \textbf{R1:}
-We thank R1 for suggesting that we look at qualitative predictions of Thm 3.6 as in the two-task case, which we have added in the updated draft.
+\textbf{($\blackdiamond$)} We thank R1 for suggesting looking at qualitative predictions of Thm 3.6 for multiple tasks, which we have added in the  draft.
 %As mentioned above, we have extended our result to show that the variance of the MTL estimator decreases compared to STL and the bias increases.
@@
 %Task similarity appears in the projection term $\|{v_t}\|$.
-For task similarity, the more similar tasks are, the closer $\|{v_t}\|$ is to 1 and the more variance reduces, which leads to positive transfer as in Prop 3.3.
-For sample ratio, the more dissimilar tasks are, the more bias increases by source task samples, which leads to negative transfer as in Prop 3.4.
-R1 asks how does our method compares to standard techniques such as loss reweighing.
-Note that our method is equivalent to increasing the weight of a task until performance drops.
-Our method is preferable to loss reweighting since we require less compute over the training data as shown in Section 4.2.
-We thank R1 for pointing out the vague use of "similar performance" in experiments, which we have replaced w/ the accuracy numbers (that are comparable).
+\textbf{(1)} For task similarity, the more similar tasks are, the more variance reduces ($\|{v_t}\|$ closer to 1), which leads to positive transfer as in Prop 3.3.
+\textbf{(2)} For sample ratio, the more dissimilar tasks are, the more bias increases w/ more source samples, which leads to negative transfer as in Prop 3.4.
+\textbf{($\blackdiamond$)} R1 asks how does our method compares to loss reweighing.
+Our method is equivalent to increasing task weight until performance drops.
+Our method is preferable since we only compute over a subset of samples whereas loss reweighting uses the full set.
+\textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of "similar performance" in experiments, which we replaced w/ (comparable) acc.
+numbers.
 %it means that the average accuracy of our method for all tasks is the same as the average accuracy of standard MTL training (cf.
@@
 
-Regarding R1's comment about computing similarity via distance between classifier parameters, we have tried it for predicting whether MTL outperforms STL (smaller distance implies better transfer) but the result is worse than Table 1.
-We suspect the reason is that the distance mainly captures difference between the trained model but does not capture other properties of task data.
+\vspace{-0.045in}
+\textbf{($\blackdiamond$)} R1 asks how does our theory compares to previous work.
+The closest work to ours is [15] and that work uses standard concentration bounds to show that when two tasks are similar enough, MTL guarantees positive transfer.
+Our work uses advanced tools from random matrix theory and Thm 3.2 does not make such an assumption.
+This also allows us to study the \textit{more challenging setting of varying sample size and covariate shift, both of which cannot be studied using standard concentration bounds}.
+\textbf{($\blackdiamond$)} R1 asks whether we can compute similarity via distance between classifier parameters,
+which we tried for predicting whether MTL outperforms STL but the result is worse than Table 1.
+We suspect the distance mainly captures difference between the trained model but does not capture properties of task data.
 %The lesson that we have learned from our work is that in order to decide whether MTL outperforms STL, all three properties including model similarity, sample ratio, and covariate shift provably matter.
@@
 %R1 asks "how do the bounds differ compared to previous theory".
-The closest work to ours is [15] and that work uses standard concentration bounds to show that when two tasks are sufficiently similar, MTL guarantees positive transfer.
-Our result in Thm 3.2 does not make such an assumption by using advanced tools from random matrix theory.
-This also allows us to study the impact of varying sample sizes and covariate shift, both of which cannot be studied using standard concentration bounds.
 
+\vspace{-0.025in}
 \textbf{R2:}
-We thank R2 for bringing up the confusion of which sample size regime does our theory/algorithm apply, which we have clarified in the updated draft.
+\textbf{($\blackdiamond$)} We thank R2 for bringing up the confusion of which sample size regime does our theory/algorithm apply, which we have clarified in the updated draft.
 %Regarding R2's comments on motivation and theoretical limitation, as stated above, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
@@
 
-We thank R2 for pointing out the connection between our incremental training procedure and curriculum learning.
+\vspace{-0.045in}
+\textbf{($\blackdiamond$)}  We thank R2 for pointing out the connection between our incremental training procedure and curriculum learning.
 We are not aware of any previous work that proposes such an idea in MTL while having a strong theoretical basis.
 Adding more context, there is an ongoing discussion of how much data from each task the model should be trained on (cf. Google T5 and refs therein).
-While we have focused on evaluating training efficiency, it's conceivable that by combining our procedure w/ other ideas one might get better final performance of the target task.
+We have focused on evaluating training efficiency as a further validation of our theory.
+It's conceivable that by combining our procedure w/ other ideas one might get better final performance of the target task.
 It is an interesting research question to further investigate the idea in future work.
@@
 
+\vspace{-0.025in}
 \textbf{R3:}
-Here's our detailed response.
+We thank R3 for commenting on our work.
 \textbf{L108:}
 %The validation set size $p^{0.99}$ is just an example and can be set smaller.
-We disagree that "the validation set is much larger than the training set" is suggested anywhere in the paper.
-\textbf{L113:} We disagree that "there are duplicate notations" in this line - $t$ is the number of tasks not samples.
-\textbf{L117:} The sample covariance of task 1 is \textit{not $\Sigma_1$} but $X_1^{\top}X_1$ and it shows up in both eqs.
+We thought we have clearly stated in L108 that "a validation set that's larger than $r\cdot t \le t^2$ suffices" but we will clarify more ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
+\textbf{L113:} $t$ always means the number of tasks so we're not where is the duplicate notation.
+\textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$ not $\Sigma_1$.
 \textbf{L187:} $\gamma$ is a free parameter and by varying it one can recover the entire precision-recall curve.
@@
 As shown in Fig 1b, the performance curve, which is a quadratic function, has a single peak and our algorithm stops at the peak.
-The fact that the curve is quadratic is shown in our proof and we have added the connection to the updated draft.
+The fact that the curve is quadratic is shown in our proof and we have added the connection to the draft.
 

### 2020-08-11 arxiv/intro.tex

@@
 %Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning is a powerful approach to improve performance for many tasks in computer vision \cite{chexnet17,ZSSGM18}, natural language processing \cite{GLUE,superglue}, and other areas \cite{ZY17}.
+Multi-task learning is a powerful approach to improve performance for many tasks in computer vision, natural language processing, and other areas \cite{C97,ZY17,R17}.
 %In multi-task learning, having related task data is fundamental to its performance.
@@
 In many settings, multiple source tasks are available to help predict a particular target task.
+\todo{clarify setting is different from traditional MTL}
 %For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
@@
 Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
+\todo{add more technical motivation (or maybe later)}
 From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data can provide guidance for downstream applications \cite{RH19}.

### 2020-08-11 arxiv/setup.tex

@@
 
-\textit{Theoretical works.}
+\medskip
+\noindent\textbf{Theoretical works.}
 Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
@@
 While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
+\todo{spell out the challenge more explicitly}
 
 % Adding a regularization over $B$, e.g. .
-\textit{Methodological works.}
+\medskip
+\noindent\textbf{Methodological works.}
 Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
@@
 
-\textit{Random matrix theory.}
+\medskip
+\noindent\textbf{Random matrix theory.}
 The random matrix theory tool and related proof of our work fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
@@
 
-\iffalse
-\textbf{Transfer learning.}
-We extend Theorem \ref{thm_main_informal} to transfer learning settings.
-We study the transfer procedure used in Taskonomy by Zamir et al.'18 \cite{ZSSGM18}.
-For the setting of high-dimensional linear regression, the transfer procedure is as follows.
-%Specifically, the source task encoder consists of the representations learnt from one or more source tasks.
-%The transfer function then tries to fit the target task data to the source task encoder.
-\squishlist
-	\item \textit{Learning source task representations}: we obtain $\hat{\beta}_i^{\STL}$ from each source task, for $1\le i \le t-1$.
-		This forms a shared representation ${B} = [\hat{\beta}_1,\hat{\beta}_2,\dots,\hat{\beta}_{t-1}]$.
-	\item \textit{Fine-tuning on the target task}: we learn the output layer $W_t\in\real^{t-1}$ similar to equation \eqref{eq_mtl}
-		\begin{align}
-			g(W_t) = \bignorm{X_t B W_t - Y_t}^2.
-		\end{align}
-\squishend
-After solving $W_t$, we use $\hat{\beta}_t^{\TL} = B W_t$ as the transfer learning (TL) estimator for the target task.
-Our result naturally applies to $\hat{\beta}_t^{\TL}$.
-Interestingly, we show that the model shift bias is simply the projection of $\beta_t$ to the orthogonal subspace of $B^{\star} = [\beta_1,\dots,\beta_{t-1}]$, or $\norm{\Sigma_t^{1/2}(\id - B^{\star}({B^{\star}}^{\top}B^{\star})^{-1}{B^{\star}}^{\top})\beta_t}^2$ more precisely.
-The formal statement is presented in Theorem \ref{prop_taskonomy} and its proof in Appendix \ref{app_proof_sec4}.
-\fi
-
-%In order to analyze the tradeoff, we develop the following technical tool, which provides a tight bound for equation \eqref{eq_te_var}.
-%where $(a_1, a_2)$ is the solution to the following deterministic equations:
-%	\begin{align*}
-%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-%	\end{align*}
-
-%\textbf{Remark.} When there is only the target task, $\rho_1$ equals zero.
-%Hence $a_2 = 1 - 1/ \rho_2, a_1 = 0$ and Lemma \ref{lem_cov_shift_informal} states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2] = \sigma^2 / (\rho_2 - 1)$, which is a well-known result in random matrix theory \cite{S07}.
-%Hence our result provides a necessary tool to analyze MTL in high dimensions.
-
-%\subsection{Extended Background and Related Work}\label{app_proof_sec3}
-
-%We restate our linear regression setting, in particular the moment assumption required by our random matrix model.
-%We then derive a closed-form solution of the multi-task estimator that is defined in Section \ref{sec_prelim}.
-%Finally, we describe further related work that is covered in the main text.
-%\section{Missing Details of Problem Formulation}
-%\textbf{Assumptions on task data generation.}
-
 \paragraph{Notations.}

### 2020-08-11 neurips20_response/response.tex
response

@@
 Taking their helpful comments into account, we have sought to clarify the presentation of our work and  multiple tasks. %, which addresses the main criticism by R1 and R2.
-Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction, in response to the main criticism by R1 and R2 (L11-17).
+Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction in response to a major criticism by R1 and R2 (L11-17).
 %First, we address the main issues that are raised by the reviewers.
@@
 
-\vspace{-0.025in}
+\vspace{-0.02in}
 \textbf{Predicting a particular task using MTL? [R2]}
@@
 We study when training the tasks together can benefit the target task.
-While this setting is different from traditional MTL that studies the avg performance of all tasks, it is also a common setting for MTL in practice.
-For example, for predicting a rare event or classifying an Xray-scan, collecting large amounts of labeled data is either not possible or very expensive, but auxiliary labeled data are often easier to obtain.
+While this setting differs from traditional MTL that studies the avg performance of all tasks, it is also a common setting for MTL in practice.
+For example, for predicting a rare event or classifying a Xray-scan, collecting large amounts of labeled data is not possible or very expensive, but auxiliary labeled data are often easier to obtain.
 Traditional MTL theory that studies the average performance of all tasks does not predict whether using MTL can benefit the target task.
@@
 We understand that having multiple tasks is more general, therefore, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
-\textbf{(1)} We can now show that \textit{as long as the output dimension of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
+\textbf{(1)} We can now show that \textit{as long as the output dim.
+of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
 We have included this result in the draft.
 \textbf{(2)} For multi-label settings where all tasks have the same features, i.e.
-$X_i = X$ for any $i$, using Thm 3.6 \textit{all of our insight for two tasks still applies except covariate shift} (covariate shift doesn't apply since tasks have the same features).
+$X_i = X$ for any $i$, using Thm 3.6 \textit{all of our insight into two tasks still applies except covariate shift} (covariate shift doesn't apply since tasks have the same features).
 %The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.
@@
 %We have improved this part to be more consistent in the use of $t$.
-\textbf{(2)} Validation set size: we only need it to be larger than the size of the hidden layer times the number of tasks, which can be much smaller compared to the size of the training set (cf.
-L108).
+\textbf{(2)} Validation set size L108: we only need it to be larger than the size of the hidden layer times the number of tasks, which is much smaller compared to the size of the training set.
 \textbf{(3)} Def. of the prediction loss L113: the expectation is over a test sample $x$ whose label is $x^{\top}\beta_t$.
@@
 \textbf{(2)} For sample ratio, the more dissimilar tasks are, the more bias increases w/ more source samples, which leads to negative transfer as in Prop 3.4.
-\textbf{($\blackdiamond$)} R1 asks how does our method compares to loss reweighing.
+\textbf{($\blackdiamond$)} R1 asks how does our method compare to loss reweighing.
 Our method is equivalent to increasing task weight until performance drops.
@@
 \vspace{-0.045in}
-\textbf{($\blackdiamond$)} R1 asks how does our theory compares to previous work.
-The closest work to ours is [15] and that work uses standard concentration bounds to show that when two tasks are similar enough, MTL guarantees positive transfer.
-Our work uses advanced tools from random matrix theory and Thm 3.2 does not make such an assumption.
-This also allows us to study the \textit{more challenging setting of varying sample size and covariate shift, both of which cannot be studied using standard concentration bounds}.
-\textbf{($\blackdiamond$)} R1 asks whether we can compute similarity via distance between classifier parameters,
-which we tried for predicting whether MTL outperforms STL but the result is worse than Table 1.
-We suspect the distance mainly captures difference between the trained model but does not capture properties of task data.
+\textbf{($\blackdiamond$)} R1 asks how do the bounds differ from previous theory.
+The closest work to ours is [15] and that work uses standard concentration bounds to show that when two tasks are similar enough, MTL ensures positive transfer.
+Our work uses new tools from random matrix theory and Thm 3.2 doesn't require tasks to be similar.
+Using the tools we \textit{rigorously study the phenomenon of negative transfer} including \textit{varying sample size and covariate shift, all of which aren't possible using standard concentration bounds}.
+\textbf{($\blackdiamond$)} R1 suggests computing similarity via distance between layer parameters,
+which we tried (along w/ SVCCA) as a proxy for task similarity but didn't work  (e.g. result worse than Table 1).
+Our framework also studied varying sample size and covariate shift in MTL, both of which are not known in prior work.
+%Our intuition is that while the distance captures model difference we also need to carefully control task data.
 %The lesson that we have learned from our work is that in order to decide whether MTL outperforms STL, all three properties including model similarity, sample ratio, and covariate shift provably matter.
@@
 \textbf{R2:}
-\textbf{($\blackdiamond$)} We thank R2 for bringing up the confusion of which sample size regime does our theory/algorithm apply, which we have clarified in the updated draft.
+\textbf{($\blackdiamond$)} We thank R2 for bringing up the confusion of which sample size regime does our theory/algorithm apply, which we have clarified in the draft.
 %Regarding R2's comments on motivation and theoretical limitation, as stated above, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
 While our setting is different from traditional MTL that measures average performance over all tasks, it is also a common setting in practice where MTL is used.
-\textbf{(1)} R2 is correct that "our theory applies when the sample sizes are tens or hundreds of feature dimension".
-We think this is a reasonable regime to consider; for example, in our sentiment analysis experiment, the feature dimension of a sentence is 300 and the training set size ranges from 3 to 10 thousand.
+\textbf{(1)} R2 is correct that "our theory applies when the sample sizes are 10-100x of feature dim.".
+We think this is a reasonable regime to consider; for example, in our sentiment analysis experiment, the feature dim. of a sentence is 300 and the training set size ranges from 3k to 10k.
 %\textbf{(2)} As shown in Prop. 3.4, the ratio of sample sizes, instead of the sample size of a task, decides whether MTL can help STL.
 %Our theory makes no assumption on sample ratio (or imbalance) and applies to reasonable regimes (e.g. Fig 1(b,c)).
-\textbf{(2)} R2 mentions "having imbalanced sample size btw source/target task": Our incremental training scheme does not assume that the tasks have imbalanced sample size; for example, in our sentiment analysis experiment, we have observed that our method can be effective even when the source task is smaller than the target.
-As shown in our theory, the transition threshold between positive/negative transfer provably depends on task similarity and can be less than one (Prop. 3.4).
+\textbf{(2)} R2 mentions "having imbalanced sample size btw source/target task": We will clarify the writing after Thm 3.2 but our incremental training scheme does not assume that the tasks have imbalanced sample size; for example, in our sentiment analysis experiment, we have observed that our method can help even when the source task is smaller than the target.
+The correct way to think about "imbalance" is that it also depends on task similarity, and it can be provably small (e.g. $\le 1$ cf. Prop 3.4).
 
@@
 %The validation set size $p^{0.99}$ is just an example and can be set smaller.
-We thought we have clearly stated in L108 that "a validation set that's larger than $r\cdot t \le t^2$ suffices" but we will clarify more ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
-\textbf{L113:} $t$ always means the number of tasks so we're not where is the duplicate notation.
+We thought we have stated in L108 that "a validation set that's larger than $r\cdot t \le t^2$ suffices" but we will clarify more ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
+\textbf{L113:} We did not use any duplicate notation for $t$ ($\varepsilon_i$ is the noise \textit{vector} for the $i$-th task).
 \textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$ not $\Sigma_1$.
@@
 As shown in Fig 1b, the performance curve, which is a quadratic function, has a single peak and our algorithm stops at the peak.
-The fact that the curve is quadratic is shown in our proof and we have added the connection to the draft.
+That the curve is quadratic is shown in our proof and we have added the connection to the draft.
 

### 2020-08-11 neurips20_response/response.tex
response

@@
 %We thank R1 and R2 for raising the important question of whether our setting applies to multiple tasks.
-We have focused on two tasks in the submission to provide insight, since this is the simplest setting.
+We have focused on two tasks in the submission to provide insights, since this is the simplest setting.
 We understand that having multiple tasks is more general, therefore, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
@@
 \textbf{(2)} For multi-label settings where all tasks have the same features, i.e.
-$X_i = X$ for any $i$, using Thm 3.6 \textit{all of our insight into two tasks still applies except covariate shift} (covariate shift doesn't apply since tasks have the same features).
+$X_i = X$ for any $i$, using Thm 3.6 \textit{all of our insights into two tasks still apply except for the covariate shift} (covariate shift doesn't apply since tasks have the same features).
 %The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.
@@
 We have corrected the typos that R2 pointed out and clarified the issues that R3 raised.
-\textbf{(1)} L112-118: we use $t$ to denote the number of tasks hence for two tasks $t = 2$.
+\textbf{(1)} L112-118: we use $t$ to denote the number of tasks, hence for two tasks $t = 2$.
 %We have improved this part to be more consistent in the use of $t$.
@@
 \textbf{(2)} For sample ratio, the more dissimilar tasks are, the more bias increases w/ more source samples, which leads to negative transfer as in Prop 3.4.
-\textbf{($\blackdiamond$)} R1 asks how does our method compare to loss reweighing.
+\textbf{($\blackdiamond$)} R1 asks how our method compares to loss reweighing.
 Our method is equivalent to increasing task weight until performance drops.
 Our method is preferable since we only compute over a subset of samples whereas loss reweighting uses the full set.
-\textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of "similar performance" in experiments, which we replaced w/ (comparable) acc.
-numbers.
+\textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of "similar performance" in experiments, which we replaced w/ (comparable) accurate numbers.
 %it means that the average accuracy of our method for all tasks is the same as the average accuracy of standard MTL training (cf.
@@
 The closest work to ours is [15] and that work uses standard concentration bounds to show that when two tasks are similar enough, MTL ensures positive transfer.
-Our work uses new tools from random matrix theory and Thm 3.2 doesn't require tasks to be similar.
-Using the tools we \textit{rigorously study the phenomenon of negative transfer} including \textit{varying sample size and covariate shift, all of which aren't possible using standard concentration bounds}.
+Our work uses new tools from random matrix theory, and Thm 3.2 doesn't require tasks to be similar.
+Using the tools we \textit{rigorously study the phenomenon of negative transfer} including \textit{varying sample size and covariate shift, which are not possible using standard concentration bounds only}.
 \textbf{($\blackdiamond$)} R1 suggests computing similarity via distance between layer parameters,
-which we tried (along w/ SVCCA) as a proxy for task similarity but didn't work  (e.g. result worse than Table 1).
+which we tried (along w/ SVCCA) as a proxy for task similarity but it didn't work (e.g.
+result is worse than Table 1).
 Our framework also studied varying sample size and covariate shift in MTL, both of which are not known in prior work.
@@
 \textbf{R2:}
-\textbf{($\blackdiamond$)} We thank R2 for bringing up the confusion of which sample size regime does our theory/algorithm apply, which we have clarified in the draft.
+\textbf{($\blackdiamond$)} We thank R2 for bringing up the confusion of which sample size regime our theory/algorithm applies, which we have clarified in the draft.
 %Regarding R2's comments on motivation and theoretical limitation, as stated above, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.

### 2020-08-11 neurips20_response/response.tex
response

@@
 We thank the reviewers for their time and thoughtful feedback.
-Taking their helpful comments into account, we have sought to clarify the presentation of our work and  multiple tasks. %, which addresses the main criticism by R1 and R2.
-Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction in response to a major criticism by R1 and R2 (L11-17).
+Taking their helpful comments into account, we have sought to clarify the presentation of our work. %, which addresses the main criticism by R1 and R2.
+Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction in response to a common criticism by R1 and R2 (L11-17).
 %First, we address the main issues that are raised by the reviewers.
@@
 We have focused on two tasks in the submission to provide insights, since this is the simplest setting.
-We understand that having multiple tasks is more general, therefore, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
+We have \textit{extended our result on bias-variance tradeoff to multiple tasks} as well.
 \textbf{(1)} We can now show that \textit{as long as the output dim.
@@
 Our method is preferable since we only compute over a subset of samples whereas loss reweighting uses the full set.
-\textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of "similar performance" in experiments, which we replaced w/ (comparable) accurate numbers.
+\textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of "similar performance" in experiments, which we replaced w/ (comparable) accuracy numbers.
 %it means that the average accuracy of our method for all tasks is the same as the average accuracy of standard MTL training (cf.
@@
 %The validation set size $p^{0.99}$ is just an example and can be set smaller.
-We thought we have stated in L108 that "a validation set that's larger than $r\cdot t \le t^2$ suffices" but we will clarify more ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
-\textbf{L113:} We did not use any duplicate notation for $t$ ($\varepsilon_i$ is the noise \textit{vector} for the $i$-th task).
+As stated on L108  "a validation set that's larger than $r\cdot t \le t^2$ suffices". We will further clarify as in L19 above ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
+\textbf{L113:} The use of $t$: We have used $t$ to denote the number of tasks as well as the index of the target task.
 \textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$ not $\Sigma_1$.
-\textbf{L187:} $\gamma$ is a free parameter and by varying it one can recover the entire precision-recall curve.
+\textbf{L187:} Parameter of the metric: by varying it one can recover the entire precision-recall curve.
 \textbf{L220:} Our theory provides a theoretical basis for the algorithm.
@@
 \end{document}
+
+%>>>>>>> bdfb263d5b2fe0cf68cb8be1ac53481042b5008f

### 2020-08-12 neurips20_response/response.tex
response

@@
 Taking their helpful comments into account, we have sought to clarify the presentation of our work. %, which addresses the main criticism by R1 and R2.
-Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction in response to a common criticism by R1 and R2 (L11-17).
+Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction for multiple tasks in response to a common criticism by R1 and R2 (L11-17).
 %First, we address the main issues that are raised by the reviewers.
@@
 We study when training the tasks together can benefit the target task.
-While this setting differs from traditional MTL that studies the avg performance of all tasks, it is also a common setting for MTL in practice.
+While this setting differs from traditional MTL that studies the average performance of all tasks, it is also a common setting for MTL in practice.
 For example, for predicting a rare event or classifying a Xray-scan, collecting large amounts of labeled data is not possible or very expensive, but auxiliary labeled data are often easier to obtain.
@@
 %We thank R1 and R2 for raising the important question of whether our setting applies to multiple tasks.
-We have focused on two tasks in the submission to provide insights, since this is the simplest setting.
-We have \textit{extended our result on bias-variance tradeoff to multiple tasks} as well.
+We have focused on two tasks in the submission to provide insights, since this is the foundational setting.
+In addition, we have \textit{extended our result on bias-variance tradeoff to multiple tasks} as well.
 \textbf{(1)} We can now show that \textit{as long as the output dim.
 of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
-We have included this result in the draft.
+The idea is simimlar to two tasks and we have included this result in the draft.
 \textbf{(2)} For multi-label settings where all tasks have the same features, i.e.
@@
 Our method is equivalent to increasing task weight until performance drops.
-Our method is preferable since we only compute over a subset of samples whereas loss reweighting uses the full set.
+An advantage of our method is that we only compute over a subset of samples whereas loss reweighting uses the full set.
 \textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of "similar performance" in experiments, which we replaced w/ (comparable) accuracy numbers.
@@
 Our work uses new tools from random matrix theory, and Thm 3.2 doesn't require tasks to be similar.
-Using the tools we \textit{rigorously study the phenomenon of negative transfer} including \textit{varying sample size and covariate shift, which are not possible using standard concentration bounds only}.
+Using the tools we \textit{rigorously study the phenomenon of negative transfer} including \textit{varying sample size and covariate shift, all of which aren't possible using standard concentration bounds}.
 \textbf{($\blackdiamond$)} R1 suggests computing similarity via distance between layer parameters,
-which we tried (along w/ SVCCA) as a proxy for task similarity but it didn't work (e.g.
-result is worse than Table 1).
+which we tried (along w/ SVCCA) as a proxy for task similarity but it didn't perform as well as our result in Table 1.
 Our framework also studied varying sample size and covariate shift in MTL, both of which are not known in prior work.
@@
 We are not aware of any previous work that proposes such an idea in MTL while having a strong theoretical basis.
-Adding more context, there is an ongoing discussion of how much data from each task the model should be trained on (cf. Google T5 and refs therein).
-We have focused on evaluating training efficiency as a further validation of our theory.
+Adding more context, there is an ongoing discussion of how much data from each task the model should be trained on (cf. Google T5 and references therein).
+We have focused on evaluating training efficiency as a \textit{further validation of our theory}.
 It's conceivable that by combining our procedure w/ other ideas one might get better final performance of the target task.
-It is an interesting research question to further investigate the idea in future work.
+As R1 pointed out, we think this is an interesting research question for future study.
 %R2 asks about why "the middle part btw negative/positive transfer cannot be predicted correctly".
@@
 %The validation set size $p^{0.99}$ is just an example and can be set smaller.
-As stated on L108  "a validation set that's larger than $r\cdot t \le t^2$ suffices". We will further clarify as in L19 above ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
+As stated on L108  "a validation set that's larger than $r\cdot t \le t^2$ suffices", we will further clarify here as in L19 above ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
 \textbf{L113:} The use of $t$: We have used $t$ to denote the number of tasks as well as the index of the target task.
 \textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$ not $\Sigma_1$.
-\textbf{L187:} Parameter of the metric: by varying it one can recover the entire precision-recall curve.
-\textbf{L220:} Our theory provides a theoretical basis for the algorithm.
-For two tasks, the algorithm can provably find the optimal sample ratio.
+\textbf{L187:} Parameter of the metric: yes one can recover the entire precision-recall curve by varying it.
+\textbf{L220:} Value of our theory to our algorithm:
+For two tasks, we can show that our algorithm can provably find the optimal sample ratio.
 As shown in Fig 1b, the performance curve, which is a quadratic function, has a single peak and our algorithm stops at the peak.

### 2020-08-12 neurips20_response/response.tex
edit response

@@
 of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
-The idea is simimlar to two tasks and we have included this result in the draft.
+The idea is similar to two tasks and we have included this result in the draft.
 \textbf{(2)} For multi-label settings where all tasks have the same features, i.e.
-$X_i = X$ for any $i$, using Thm 3.6 \textit{all of our insights into two tasks still apply except for the covariate shift} (covariate shift doesn't apply since tasks have the same features).
+$X_i = X$ for any $i$, using Thm 3.6, \textit{all of our insights into two tasks still apply except for the covariate shift} (covariate shift doesn't apply since tasks have the same features).
 %The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.
@@
 We have corrected the typos that R2 pointed out and clarified the issues that R3 raised.
-\textbf{(1)} L112-118: we use $t$ to denote the number of tasks, hence for two tasks $t = 2$.
+\textbf{L112-118}: we use $t$ to denote the number of tasks, hence for two tasks $t = 2$.
 %We have improved this part to be more consistent in the use of $t$.
-\textbf{(2)} Validation set size L108: we only need it to be larger than the size of the hidden layer times the number of tasks, which is much smaller compared to the size of the training set.
-\textbf{(3)} Def. of the prediction loss L113: the expectation is over a test sample $x$ whose label is $x^{\top}\beta_t$.
+\textbf{L108}, validation set size: we only need it to be larger than the size of the hidden layer times the number of tasks, which is much smaller compared to the size of the training set.
+\textbf{L113}, def. of the prediction loss: the expectation is over a test sample $x$ whose label is $x^{\top}\beta_t$.
 Taking expectation over $\varepsilon$ gives  the bias-variance decomposition, following standard linear regression literature [17,18].
@@
 \textbf{R1:}
-\textbf{($\blackdiamond$)} We thank R1 for suggesting looking at qualitative predictions of Thm 3.6 for multiple tasks, which we have added in the  draft.
+\textbf{($\blackdiamond$)} We thank R1 for suggesting we look at qualitative predictions of Thm 3.6 for multiple tasks, which we have added in the  draft.
 %As mentioned above, we have extended our result to show that the variance of the MTL estimator decreases compared to STL and the bias increases.
@@
 Our framework also studied varying sample size and covariate shift in MTL, both of which are not known in prior work.
+\textbf{($\blackdiamond$)} For R1's question about excluding TREC, this is just an additional validation for the multi-task setting.
 %Our intuition is that while the distance captures model difference we also need to carefully control task data.
@@
 \textbf{R2:}
-\textbf{($\blackdiamond$)} We thank R2 for bringing up the confusion of which sample size regime our theory/algorithm applies, which we have clarified in the draft.
+We thank R2 for bringing up the confusion of which sample size regime our theory/algorithm applies, which we have clarified in the draft.
 %Regarding R2's comments on motivation and theoretical limitation, as stated above, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
@@
 \vspace{-0.045in}
-\textbf{($\blackdiamond$)}  We thank R2 for pointing out the connection between our incremental training procedure and curriculum learning.
+We thank R2 for pointing out the connection between our incremental training procedure and curriculum learning.
 We are not aware of any previous work that proposes such an idea in MTL while having a strong theoretical basis.
@@
 %The validation set size $p^{0.99}$ is just an example and can be set smaller.
-As stated on L108  "a validation set that's larger than $r\cdot t \le t^2$ suffices", we will further clarify here as in L19 above ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
-\textbf{L113:} The use of $t$: We have used $t$ to denote the number of tasks as well as the index of the target task.
+As stated on L108  "a validation set larger than $r\cdot t$ suffices", we will further clarify as on L19 above ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
+%\textbf{L113:} The use of $t$: We have used $t$ to denote the number of tasks as well as the index of the target task.
 \textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$ not $\Sigma_1$.
-\textbf{L187:} Parameter of the metric: yes one can recover the entire precision-recall curve by varying it.
+\textbf{L187:} Parameter of the metric: One can recover the entire precision-recall curve by varying it.
 \textbf{L220:} Value of our theory to our algorithm:
@@
 As shown in Fig 1b, the performance curve, which is a quadratic function, has a single peak and our algorithm stops at the peak.
-That the curve is quadratic is shown in our proof and we have added the connection to the draft.
+That the curve is quadratic is shown in our proof and we have highlighted the connection in the draft.
 
 \end{document}
-
-%>>>>>>> bdfb263d5b2fe0cf68cb8be1ac53481042b5008f

### 2020-08-13 neurips20_response/response.tex
response

@@
 
-We thank the reviewers for their time and thoughtful feedback.
-Taking their helpful comments into account, we have sought to clarify the presentation of our work. %, which addresses the main criticism by R1 and R2.
-Besides clarifying our current result for multiple tasks, we have also extended our result on variance reduction for multiple tasks in response to a common criticism by R1 and R2 (L11-17).
+We thank the reviewers for their excellent feedback, which significantly improved our work.
+%Taking their helpful comments into account, we have sought to clarify the presentation of our work. %, which addresses the main criticism by R1 and R2.
+%Due to space limit, we only respond to the most salient comments, but have taken the rest into account.
+All reviewers agree that our work provides a solid foundation for understanding when MTL performs well compared to STL, a central open question in MTL.
+We offer better explanations of our theoretical/algorithmic contributions in this response.
+%Besides clarifying our current result, we've also extended our conceptual insight on bias-variance tradeoff to multiple tasks in response to R1 and R2's feedback.
 %First, we address the main issues that are raised by the reviewers.
@@
 
-\vspace{-0.02in}
-\textbf{Predicting a particular task using MTL? [R2]}
-As R2 pointed out, we focus on a situation where we have a target task for which we only have limited labeled data and a source task.
-We study when training the tasks together can benefit the target task.
-While this setting differs from traditional MTL that studies the average performance of all tasks, it is also a common setting for MTL in practice.
-For example, for predicting a rare event or classifying a Xray-scan, collecting large amounts of labeled data is not possible or very expensive, but auxiliary labeled data are often easier to obtain.
-Traditional MTL theory that studies the average performance of all tasks does not predict whether using MTL can benefit the target task.
-Our work applies to this setting and takes a step towards filling the gap.
+\textbf{Motivation. [R2]}
+We focus on a setting where we have a target task with limited labeled data and study when using MTL w/ multiple source tasks helps the target task. %,
+%which differs from traditional MTL that studies the average performance of all tasks.
+There are many practical applications for this setting from both industry and academia.
+For example, for predicting a rare video event or classifying an Xray scan, collecting large amounts of labeled data is very expensive.
+Still, auxiliary labeled data are often easier to obtain.
+For these settings, while applying MTL is natural, the result can be worse than STL.
+Classical MTL theory studies the average performance of all tasks and does not address whether MTL helps the target task.
+Our work builds a foundation for applying MTL to these settings.
 %We have included these discussion to our paper.
 
-\vspace{-0.025in}
 \textbf{What can we say for multiple tasks? [R1, R2]}
 %We thank R1 and R2 for raising the important question of whether our setting applies to multiple tasks.
-We have focused on two tasks in the submission to provide insights, since this is the foundational setting.
-In addition, we have \textit{extended our result on bias-variance tradeoff to multiple tasks} as well.
-\textbf{(1)} We can now show that \textit{as long as the output dim.
-of the shared layer $B$ is smaller than the total number of tasks, the variance of the MTL estimator for the target task is always smaller than the variance of the STL estimator but the bias is always larger}.
-The idea is similar to two tasks and we have included this result in the draft.
-\textbf{(2)} For multi-label settings where all tasks have the same features, i.e.
-$X_i = X$ for any $i$, using Thm 3.6, \textit{all of our insights into two tasks still apply except for the covariate shift} (covariate shift doesn't apply since tasks have the same features).
+While we have focused on the two-task case to explain our results in the original submission, we can apply all of our conceptual insights to the multi-task case.
+We have updated our draft to consolidate our results for the multi-task setting and now show the following.
+\textbf{(1)} We show that \textit{as long as the output dim.
+of the shared layer $B$ is smaller than the  number of tasks, the variance of the MTL estimator for the target task reduces compared to STL, but the bias increases}.
+The idea is similar to the two-task case, and we have included this result in the draft.
+\textbf{(2)} For multi-label settings where all tasks have the same features, i.e., $X_i = X$ for any $i$, using Thm 3.6, all of our insights from the two-task case still apply except for covariate shift, which doesn't apply since tasks have the same features.
+For task similarity, the more similar the models are, the more variance reduces ($\|{v_t}\|$ closer to 1), which leads to positive transfer as in Prop 3.3.
+For sample ratio, the more different the models are, the more bias increases w/ more source task samples, which leads to negative transfer as in Prop 3.4.
 %The reason why the issue about covariate shift does not apply to this setting is because the tasks have the same features, hence there is no covariate shift.
@@
 
-\vspace{-0.025in}
+\textbf{Related work: [R1, R2]} We clarify how our work differs from previous work.
+The closest work to ours is [15], which uses standard concentration bounds to show that when two tasks are similar, MTL ensures positive transfer.
+Our paper uses new tools from random matrix theory, and Thm 3.2 doesn't require tasks to be similar.
+Our tools allow us to analyze the empirical phenomenon of negative transfer that is challenging otherwise using standard techniques.
+In particular, Lemma 3.1 characterizes the variance of MTL w/ covariate shift, which may be of independent interest.
+
 \textbf{Writing: [R2, R3]}
-We have corrected the typos that R2 pointed out and clarified the issues that R3 raised.
-\textbf{L112-118}: we use $t$ to denote the number of tasks, hence for two tasks $t = 2$.
+We have corrected the typos that R2 pointed out and added more explanation for the questions that R3 asked.
+\textbf{L112-118}: We use $t$ to denote the number of tasks, hence for two tasks $t = 2$.
 %We have improved this part to be more consistent in the use of $t$.
-\textbf{L108}, validation set size: we only need it to be larger than the size of the hidden layer times the number of tasks, which is much smaller compared to the size of the training set.
-\textbf{L113}, def. of the prediction loss: the expectation is over a test sample $x$ whose label is $x^{\top}\beta_t$.
-Taking expectation over $\varepsilon$ gives  the bias-variance decomposition, following standard linear regression literature [17,18].
+\textbf{L108}: We only need the validation set to be larger than the size of the hidden layer times the number of tasks $t$, which is very small compared to the training set size.
+\textbf{L113}: For the prediction loss, the expectation is over a test sample $x$ whose label is $x^{\top}\beta_t$.
+Taking an expectation over $\varepsilon$ gives the bias-variance decomposition, following standard linear regression literature [17,18].
 
-\vspace{-0.025in}
 \textbf{R1:}
-\textbf{($\blackdiamond$)} We thank R1 for suggesting we look at qualitative predictions of Thm 3.6 for multiple tasks, which we have added in the  draft.
+%\textbf{($\blackdiamond$)} We thank R1 for suggesting we look at qualitative predictions of Thm 3.6 for multiple tasks, which we have added in the  draft.
 %As mentioned above, we have extended our result to show that the variance of the MTL estimator decreases compared to STL and the bias increases.
@@
 %Task similarity appears in the projection term $\|{v_t}\|$.
-\textbf{(1)} For task similarity, the more similar tasks are, the more variance reduces ($\|{v_t}\|$ closer to 1), which leads to positive transfer as in Prop 3.3.
-\textbf{(2)} For sample ratio, the more dissimilar tasks are, the more bias increases w/ more source samples, which leads to negative transfer as in Prop 3.4.
 \textbf{($\blackdiamond$)} R1 asks how our method compares to loss reweighing.
-Our method is equivalent to increasing task weight until performance drops.
-An advantage of our method is that we only compute over a subset of samples whereas loss reweighting uses the full set.
-\textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of "similar performance" in experiments, which we replaced w/ (comparable) accuracy numbers.
+Our approach is equivalent to increasing task weight until performance drops.
+An advantage of our approach is that we only train over a subset of samples, whereas loss reweighting uses the full set.
+\textbf{($\blackdiamond$)} We thank R1 for pointing out the vague use of ``similar performance'' in experiments, which we replaced w/ (comparable) accuracy numbers.
 %it means that the average accuracy of our method for all tasks is the same as the average accuracy of standard MTL training (cf.
 line 295).
+\textbf{($\blackdiamond$)} The setting of 5 tasks w/o TREC: For any set of 5 tasks w/o one task, the result is qualitatively similar.
+\textbf{($\blackdiamond$)} R1 suggests computing similarity via distance between layer parameters,
+which we tried (along w/ SVCCA) as a proxy for task similarity.
+It didn't perform as well as our result in Table 1.
 %Thus, our method achieves the same average accuracy as MTL with less computation.
@@
 
-\vspace{-0.045in}
-\textbf{($\blackdiamond$)} R1 asks how do the bounds differ from previous theory.
-The closest work to ours is [15] and that work uses standard concentration bounds to show that when two tasks are similar enough, MTL ensures positive transfer.
-Our work uses new tools from random matrix theory, and Thm 3.2 doesn't require tasks to be similar.
-Using the tools we \textit{rigorously study the phenomenon of negative transfer} including \textit{varying sample size and covariate shift, all of which aren't possible using standard concentration bounds}.
-\textbf{($\blackdiamond$)} R1 suggests computing similarity via distance between layer parameters,
-which we tried (along w/ SVCCA) as a proxy for task similarity but it didn't perform as well as our result in Table 1.
-Our framework also studied varying sample size and covariate shift in MTL, both of which are not known in prior work.
-\textbf{($\blackdiamond$)} For R1's question about excluding TREC, this is just an additional validation for the multi-task setting.
 %Our intuition is that while the distance captures model difference we also need to carefully control task data.
@@
 
-\vspace{-0.025in}
+\vspace{-0.02in}
 \textbf{R2:}
-We thank R2 for bringing up the confusion of which sample size regime our theory/algorithm applies, which we have clarified in the draft.
+We thank R2 for bringing up the confusion about the sample size regime our theory/algorithm applies. We have clarified this in the draft.
 %Regarding R2's comments on motivation and theoretical limitation, as stated above, we have \textit{extended our result on bias-variance tradeoff to multiple tasks}.
 While our setting is different from traditional MTL that measures average performance over all tasks, it is also a common setting in practice where MTL is used.
-\textbf{(1)} R2 is correct that "our theory applies when the sample sizes are 10-100x of feature dim.".
-We think this is a reasonable regime to consider; for example, in our sentiment analysis experiment, the feature dim. of a sentence is 300 and the training set size ranges from 3k to 10k.
+\textbf{(1)} R2 is correct that ``our theory applies when the sample sizes are 10-100x of feature dim''.
+We think this is a practical regime to consider.
+For example, in our sentiment analysis experiment, the feature dim. of a sentence is 300, while the training set size ranges from 3k to 15k.
 %\textbf{(2)} As shown in Prop. 3.4, the ratio of sample sizes, instead of the sample size of a task, decides whether MTL can help STL.
 %Our theory makes no assumption on sample ratio (or imbalance) and applies to reasonable regimes (e.g. Fig 1(b,c)).
-\textbf{(2)} R2 mentions "having imbalanced sample size btw source/target task": We will clarify the writing after Thm 3.2 but our incremental training scheme does not assume that the tasks have imbalanced sample size; for example, in our sentiment analysis experiment, we have observed that our method can help even when the source task is smaller than the target.
-The correct way to think about "imbalance" is that it also depends on task similarity, and it can be provably small (e.g. $\le 1$ cf. Prop 3.4).
+\textbf{(2)} R2 refers to having an imbalanced sample size while discussing our approach. We will clarify the writing after Thm 3.2.
+But our incremental training method does not assume that the tasks have imbalanced sample sizes.
+For example, in our sentiment analysis experiment, we have observed that our approach can help where the source/target sample ratio is $\le 1$.
+One practical takeaway of this work is that the level of ``imbalance'' depends on task similarity, and it can be provably small, e.g., $\le 1$ cf. Prop 3.4.
 
-\vspace{-0.045in}
-We thank R2 for pointing out the connection between our incremental training procedure and curriculum learning.
-We are not aware of any previous work that proposes such an idea in MTL while having a strong theoretical basis.
-Adding more context, there is an ongoing discussion of how much data from each task the model should be trained on (cf. Google T5 and references therein).
-We have focused on evaluating training efficiency as a \textit{further validation of our theory}.
-It's conceivable that by combining our procedure w/ other ideas one might get better final performance of the target task.
-As R1 pointed out, we think this is an interesting research question for future study.
+\vspace{-0.06in}
+We thank R2 for pointing out the connection between our incremental training method and curriculum learning.
+We are not aware of any previous work suggesting adding training data for MTL progressively while having a strong theoretical basis.
+More broadly, there is an ongoing discussion of how much data from each task the model should be trained on (cf. Google T5 and its references).
+We have focused on evaluating training efficiency since our primary goal is to build/validate the foundation.
+It's conceivable that combining our method w/ other ideas could improve the accuracy of predicting the target task.
+As R1 also suggested, we think this is an excellent direction for future research.
 %R2 asks about why "the middle part btw negative/positive transfer cannot be predicted correctly".
@@
 
-\vspace{-0.025in}
+\vspace{-0.02in}
 \textbf{R3:}
-We thank R3 for commenting on our work.
+We thank R3 for the comments.
+\textbf{L220:} Value of our theory to our algorithm:
+For two tasks, we can show that our algorithm provably finds the optimal sample ratio.
+As shown in Fig 1b, the performance curve, which is a quadratic function, has a single peak, and our algorithm stops at the peak point.
+We provide a proof that the curve is quadratic, and highlighted the connection in our draft.
+\textbf{L187:} Parameter of the metric: One can recover the entire precision-recall curve by varying it.
 \textbf{L108:}
 %The validation set size $p^{0.99}$ is just an example and can be set smaller.
-As stated on L108  "a validation set larger than $r\cdot t$ suffices", we will further clarify as on L19 above ($p^{0.99}$ can be replaced w/ $p^{0.5}$).
+As we stated, a validation set ... larger than $r\cdot t$ suffices.
+We will clarify a bit more. Replacing $p^{0.99}$ w/ $p^{0.5}$ fixes the issue.
 %\textbf{L113:} The use of $t$: We have used $t$ to denote the number of tasks as well as the index of the target task.
-\textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$ not $\Sigma_1$.
-\textbf{L187:} Parameter of the metric: One can recover the entire precision-recall curve by varying it.
-\textbf{L220:} Value of our theory to our algorithm:
-For two tasks, we can show that our algorithm can provably find the optimal sample ratio.
-As shown in Fig 1b, the performance curve, which is a quadratic function, has a single peak and our algorithm stops at the peak.
-That the curve is quadratic is shown in our proof and we have highlighted the connection in the draft.
+\textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$, not $\Sigma_1$.
 

### 2020-08-13 neurips20_response/response.tex
final response

@@
 %which differs from traditional MTL that studies the average performance of all tasks.
-There are many practical applications for this setting from both industry and academia.
+There are many practical applications in both industry and academia.
 For example, for predicting a rare video event or classifying an Xray scan, collecting large amounts of labeled data is very expensive.
@@
 %The validation set size $p^{0.99}$ is just an example and can be set smaller.
-As we stated, a validation set ... larger than $r\cdot t$ suffices.
-We will clarify a bit more. Replacing $p^{0.99}$ w/ $p^{0.5}$ fixes the issue.
+As we stated, a validation set ... larger than $r\cdot t$ suffices and
+we will clarify further. Replacing $p^{0.99}$ w/ $p^{0.5}$ fixes the issue.
 %\textbf{L113:} The use of $t$: We have used $t$ to denote the number of tasks as well as the index of the target task.
-\textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1$, not $\Sigma_1$.
+\textbf{L117:} The sample covariance of task 1 is  $X_1^{\top}X_1 / n_1$, not $\Sigma_1$.
+This is the prediction loss for the target task and our main results in Section 3 will relate the sample covariance of task 1 to the \textit{population} covariance $\Sigma_1$.
 

### 2020-08-15 arxiv/proof_main.tex
pf

@@
 
-We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$ for $t=2$.
-The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$ as $p\to \infty$.
-When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
-\begin{lemma}\label{lem_minv}
-Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
-	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
-with high probability.
-\end{lemma}
-
-We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
+%We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
 The second lemma extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
 It is the main random matrix theoretical input of this paper.
-%which deals with the inverse of the sum of two random matrices, which
-%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-\begin{lemma}[Variance bound: Lemma \ref{lem_cov_shift_informal} restated]\label{lem_cov_shift}
-	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
+%%which deals with the inverse of the sum of two random matrices, which
+%%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
+%
+%\begin{lemma}[Variance bound: Lemma \ref{lem_cov_shift_informal} restated]\label{lem_cov_shift}
+%	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
+%	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
+%	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
 Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
 We have that for any constant $\e>0$,
-	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
-	\end{align}
-with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
-	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+%	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
+%	\begin{align}\label{lem_cov_shift_eq}
+%		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
+%	\end{align}
+%with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
+%	\begin{align}
+%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
 \label{eq_a12extra}
-	\end{align}
-\end{lemma}
-
-Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which will be needed when we estimate the first term on the right-hand side of \eqref{eq_te_mtl_2task}.
+%	\end{align}
+%\end{lemma}
+%
+%Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which will be needed when we estimate the first term on the right-hand side of \eqref{eq_te_mtl_2task}.
 
 %We will give the proof of this lemma in Section \ref{sec_maintools}.
-
-\textbf{Proof overview.}
-%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
-The proofs of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} are based on the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
-Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
-In particular, when $z=0$, $\tr[\Sigma_2^{-1/2}A\Sigma_2^{-1/2}R_\infty(0)]$ gives the limit in \eqref{lem_cov_shift_eq}.
-On the other hand, we can write 
-$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2= \beta^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} \beta.$$ 
-Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}. The details can be found in Appendix \ref{sec_maintools}.
-
-%The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}. 
-We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.
 

### 2020-08-15 arxiv/transfer.tex
pf

@@
 
-\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
-	In the setting of two tasks,
-	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
-	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
-	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
-	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-	{\small\begin{align*}%\label{eq_introX1X2}
-		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-	\end{align*}}%
-	where $a_1, a_2$ are solutions of the following equations:
-	{\small\begin{align*}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-	\end{align*}}
-%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
+%	In the setting of two tasks,
+%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
+%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
+%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
+%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
+%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
+%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+%	{\small\begin{align*}%\label{eq_introX1X2}
+%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
+%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
+%	\end{align*}}%
+%	where $a_1, a_2$ are solutions of the following equations:
+%	{\small\begin{align*}
+%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+%	\end{align*}}
+%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+%\end{lemma}
+
+We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
+The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
+%which deals with the inverse of the sum of two random matrices, which
+%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
+
+\begin{lemma}[Variance bound]\label{lem_cov_shift}
+	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
+	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
+	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
+Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
+We have that for any constant $\e>0$,
+	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
+	\begin{align}\label{lem_cov_shift_eq}
+		\bigtr{(\hat v^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (\hat v^2 a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
+	\end{align}
+with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
+	\begin{align}
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat v^2 \lambda_i^2 a_1}{\hat v^2 \lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+\label{eq_a12extra}
+	\end{align}
 \end{lemma}
-Lemma \ref{lem_cov_shift_informal} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $\OO(p^{-1/2+o(1)})$ of our result is nearly optimal.
+
+Lemma \ref{lem_cov_shift} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
+As a remark, the concentration error $\bigo{\|A\| p^{-1/2+\epsilon}}$ of our result is nearly optimal.
 For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task model distance in addition to sample size and covariate shift holds (cf.
@@
 \begin{split}
-&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
-&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{( a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
+&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (\hat v^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
+&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + \hat v^2a_4 {M}^{\top}{M}}{( \hat v^2a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
 \end{split}
@@
 Here $b_0$, $b_1$ and $b_2$ are defined as
-$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
+$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \hat v^{2k}\lambda_i^{2k}}{ ( a_2 + \hat v^2\lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
 \end{lemma}
 
-Combining the two lemmas, we provide a sharp analysis of the bias-variance tradeoff of the multi-task estimator.
+\textbf{Proof overview.}
+%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
+The proofs of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} are based on the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
+Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
+In particular, when $z=0$, $\tr[\Sigma_2^{-1/2}A\Sigma_2^{-1/2}R_\infty(0)]$ gives the limit in \eqref{lem_cov_shift_eq}.
+On the other hand, we can write 
+$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2= \beta^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} \beta.$$ 
+Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}. The details can be found in Appendix \ref{sec_maintools}. 
+%The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}. 
+We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
+\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.
+
+%We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$ for $t=2$. 
+The next lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
+When the entries of $X_2$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
+\begin{lemma}\label{lem_minv}
+Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
+	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_2 - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
+with high probability.
+\end{lemma}
+Note that Lemma \ref{lem_cov_shift} extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
+
+Combining the above three lemmas, we can provide a sharp analysis of the bias-variance tradeoff of the multi-task estimator.
 

### 2020-08-16 arxiv/proof_main.tex
pf

@@
 
-For the rest of this section, we shall state and prove the formal version of Theorem \ref{thm_main_informal}.
+In this subsection, we give the proof Theorem \ref{thm_main_informal}.
+During the proof we shall also give explicit expressions for $\Delta_{\bias}$ and $\Delta_{\vari}$, which might be of interest to some readers.
 %We shall consider the case where the entries of $\e_1$ and $\e_2$ have the same variance $\sigma_1^2=\sigma_2^2=\sigma^2$.
 %Moreover, we shall denote $\beta_1$ and $\beta_2$ by $\beta_1$ and $\beta_2$, standing for ``source task" and ``target task", respectively. 
-First, we introduce several quantities that will be used in our statement, and they are also related to the quantities in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+%First, we introduce several quantities that will be used in our statement, and they are also related to the quantities in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
 Given the optimal ratio $\hat v$,
-%let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix, and ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ be the eigenvalues of $\hat{M}^{\top}\hat{M}$.
+%%let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix, and ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ be the eigenvalues of $\hat{M}^{\top}\hat{M}$.
 Define
-let $(\hat a_1, \hat a_2)$ be the solution to the following system of deterministic equations,
-	\be
-		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat v^2 \lambda_i^2 \hat a_1}{ \hat v^2 \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
-		 \ee
-		 After obtaining $(\hat a_1,\hat a_2)$, we can solve the following linear equations to get $(\hat a_3,\hat a_4)$:
-\begin{gather}
-		\left(\rho_2 \hat a_2^{-2}- \hat b_0\right)\cdot \hat  a_3 - \hat b_1 \cdot \hat a_4
-		=\hat b_0, \quad \left(\rho_1\hat a_1^{-2} - \hat b_2  \right)\cdot \hat a_4 - \hat b_1 \cdot \hat a_3 =\hat b_1 .\label{eq_a3} 
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-where we denoted
-$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat v^{2k} \lambda_i^{2k}}{ (\hat a_2 +\hat v^2 \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
-Then we introduce the following matrix
-\be\label{defnpihat}\Pi \equiv \Pi(\hat v)= \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot \hat v^2{M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat v^2 {M}^{\top} {M}}{(\hat  a_1 \hat v^2{M}^{\top} {M}+\hat a_2 )^2} {M}^{\top}.\ee
+%let $(\hat a_1, \hat a_2)$ be the solution to the following system of deterministic equations,
+%	\be
+%		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat v^2 \lambda_i^2 \hat a_1}{ \hat v^2 \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
+%		 \ee
+%		 After obtaining $(\hat a_1,\hat a_2)$, we can solve the following linear equations to get $(\hat a_3,\hat a_4)$:
+%\begin{gather}
+%		\left(\rho_2 \hat a_2^{-2}- \hat b_0\right)\cdot \hat  a_3 - \hat b_1 \cdot \hat a_4
+%		=\hat b_0, \quad \left(\rho_1\hat a_1^{-2} - \hat b_2  \right)\cdot \hat a_4 - \hat b_1 \cdot \hat a_3 =\hat b_1 .\label{eq_a3} 
+%%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
+%%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
+%	\end{gather}
+%where we denoted
+%$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat v^{2k} \lambda_i^{2k}}{ (\hat a_2 +\hat v^2 \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
+With $a_i$, $i=1,2,3,4$, given in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, 
+we define the following matrix
+\be\label{defnpihat}\Pi \equiv \Pi(\hat v)= \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot \hat v^2{M} \frac{(1 +   a_3)\id + \hat v^2 a_4 {M}^{\top} {M}}{( \hat v^2 a_1 {M}^{\top} {M}+ a_2 )^2} {M}^{\top}.\ee
 %which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
 %$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
-We introduce two factors that will appear often in our statements and discussions:
+Moreover, we introduce two factors that will appear often in our statements and discussions:
 $$\al_-(\rho_1):=\left(1- \rho_1^{-1/2}\right)^2,\quad \al_+(\rho_1):=\left(1 + \rho_1^{-1/2}\right)^2.$$ 
@@
 Finally, we introduce the error term
-\be\label{eq_deltaextra}\delta\equiv \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\hat v^2\lambda_{\min}^2(M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2.\ee
+\be\label{eq_deltaextra} 
+ \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\hat v^2\lambda_{\min}^2(M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2.\ee
 %where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. 
-Note that this factor converges to 0 as $\rho_1$ increases.
+Note that this factor converges to 0 as $\rho_1$ increases. It is not hard to see that Theorem \ref{thm_main_informal} is an immediate consequence of the following lemma.
 
@@
 
-Now we are ready to state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
-
-\begin{theorem}[Theorem \ref{thm_main_informal} restated]\label{thm_model_shift}
+\begin{lemma}%[Theorem \ref{thm_main_informal} restated]
+\label{thm_model_shift}
 %For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
@@
 	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta(\hat v) \label{upper}\\
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta(\hat v), \label{upper}\\
 		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta(\hat v), \label{lower}
@@
 	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat v^2 M^{\top}M + \hat a_2\id)^{-1}} } \label{Deltavarv} \\
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{( \hat v^2 a_1 M^{\top}M +  a_2\id)^{-1}} } \label{Deltavarv} \\
 		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi (\hat v)\Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
 	\end{align}
-\end{theorem}
+\end{lemma}
 
-The proof of Theorem \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any fixed $\e>0$, we have
+{\cor(start here)} The proof of Lemma \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any fixed $\e>0$, we have
 \begin{align}
@@
 
-\begin{proof}[Proof of Theorem \ref{thm_model_shift}]
+\begin{proof}[Proof of Lemma \ref{thm_model_shift}]
 %\noindent

### 2020-08-16 arxiv/transfer.tex
pf

@@
 \subsection{Two Tasks}
+
+We now state our main result for two tasks with both covariate and model shift.
+It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
+The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
 

### 2020-08-16 arxiv/proof_main.tex
pf

@@
 
-{\cor(start here)} The proof of Lemma \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any fixed $\e>0$, we have
+The proof of Lemma \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any constant $\e>0$, we have
 \begin{align}
@@
 %with high probability. 
-In fact, $n_1^{-1}Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
-The estimate \eqref{eq_isometric} provides tight bounds for the concentration error.
-The result is formally stated in Lemma \ref{SxxSyy} below.
+In fact, $n_1^{-1}Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
+The estimate \eqref{eq_isometric} provides tight bounds on the concentration errors, and it will be formally proved in Lemma \ref{SxxSyy} below.
 
 %\begin{remark}
-The main error $\delta$ of Theorem \ref{thm_model_shift} comes from approximating $n_1^{-1}Z_1^TZ_1$ by $\id$ using \eqref{eq_isometric}; see the estimate \eqref{bounddelta-} below.
+The main error $\delta$ in Lemma \ref{thm_model_shift} comes from approximating $n_1^{-1}Z_1^TZ_1$ by $\id$ using \eqref{eq_isometric}; see the estimate \eqref{bounddelta-} below.
 In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
@@
 \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix theory literature, and the study of the singular values of $\cal X +\hat v^2$ will be even harder.
+However, since $\cal X$ is non-symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix literature, and the study of the singular values of $\cal X +\hat v^2$ will be even harder.
 We leave this problem to future study.
@@
 %\todo{A proof outline; including the following key lemma.}
-Note that 
+By \eqref{eq_te_model_shift} and \eqref{eq_te_var}, we can write
 \begin{align*}
-L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL}) &=\sigma^2 \left(  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} -  \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right) \\
-&- \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2=:\delta_{\vari}(\hat v) - \delta_{\bias}(\hat v).
+L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL})=\delta_{\vari}(\hat v) - \delta_{\bias}(\hat v), 
+\end{align*}
+where we denote
+\begin{align*}
+\delta_{\vari}(\hat v)&=\sigma^2 \left(  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} -  \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right), 
+\end{align*}
+and
+\begin{align*}
+ \delta_{\bias}(\hat v)&= \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2.
 \end{align*}
@@
 
-\item[(ii)] Using the approximate isometry property of $Z_1$ in \eqref{eq_isometric}, we will bound the bias term $ \delta_{\bias}(v)$
+\item[(ii)] Using the approximate isometry property of $Z_1$ in \eqref{eq_isometric}, we will approximate the bias term $ \delta_{\bias}(v)$ by
 %$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - {v} \beta_2)}^2$$
-through 
+%through 
 \be\label{deltabetapf}
@@
 
-\paragraph{Step I: Variance reduction.} Consider $\hat M(v)$ for any fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
+\paragraph{Step I: Variance reduction.} ........ Consider $\hat M(v)$ for any fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
 $$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$

### 2020-08-16 arxiv/proof_main.tex
pf

@@
 
-\paragraph{Step I: Variance reduction.} ........ Consider $\hat M(v)$ for any fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
+\paragraph{Step I: Variance reduction.} Consider $\hat M(v)$ for a fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$,  
 $$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
 and 
-$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
-with high probability, where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2} with $\hat v$ replaced by $v$. Combining them, we get 
+$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{( a_1(v) \hat M^{\top}\hat M + a_2(v)\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
+with high probability, where $a_1(v)$ and $a_2(v)$ satify \eqref{eq_a12extra} with $\hat v$ replaced by $v$. The subtraction of these two terms gives 
 \be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
@@
 \begin{claim}\label{prop_model_shift}
-	In the setting of Theorem \ref{thm_model_shift},
-	we denote by $K = (v^2X_1^{\top}X_1 + X_2^{\top}X_1)^{-1}$, and
+	In the setting of Lemma \ref{thm_model_shift},
+	we denote $K(v) := (v^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, and
 	\begin{align*}
@@
 		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
-		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
+		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K(v) \Sigma_2 K(v) \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
 	\end{align*}
@@
 		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}.
+		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}(v).
 	\end{align*}
@@
 	%Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
-	Denote by $\cE = Z_1^{\top}Z_1 - {n_1}\id$. Then we can write
+We can calculate that
 %	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_1 - \hat{w}\beta_2)}^2$.
@@
 	\end{align}
-	Using \eqref{eq_isometric}, we can bound  
+	where we denote $\cE: = Z_1^{\top}Z_1 - {n_1}\id$. 
+	{\cor(start here)} Using \eqref{eq_isometric}, we can bound  
 	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{w.h.p.}$$

### 2020-08-16 arxiv/proof_main.tex
pf

@@
 	where we denote $\cE: = Z_1^{\top}Z_1 - {n_1}\id$. 
-	{\cor(start here)} Using \eqref{eq_isometric}, we can bound  
+  Using \eqref{eq_isometric}, we can bound  
 	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{w.h.p.}$$
@@
 	\end{align*}
-	which concludes the proof by the definition of $\delta_\e$.	
+	which concludes the proof by the definition of $\delta_{err}$.	
 %	we can bound the second term on the RHS of equation \eqref{eq_lem_model_shift_1} as
@@
 \end{proof}
-Note by \eqref{eq_isometric}, we have with high probability,
+Note by \eqref{eq_isometric}, we also obtain that with high probability,
 \begin{align*}
@@
 &\preceq  n_1^2 \hat M \left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^{-2}\hat M^\top \\
-&\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + 2\left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
+&\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + \left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
 &\preceq [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
 \end{align*}
-for some small enough constant $c>0$. Together with Claim \ref{prop_model_shift}, we get with high probability,
+for a small enough constant $c>0$. Together with Claim \ref{prop_model_shift}, we get that with high probability,
 \be\label{bounddelta-}
@@
 \ee
-for some small constant $c>0$, where we recall $\delta(v)$ defined in \eqref{eq_deltaextra}.
+for some small constant $c>0$, where recall that $\delta(v)$ was defined in \eqref{eq_deltaextra}.
 
 \paragraph{Step III: The limit of $\wt\delta_{\bias}(v)$.} 
-Using Lemma \ref{lem_cov_derivative} with $\Sigma_1$ and $M$ replaced by $v^2\Sigma_1$ and $\hat M$, we obtain that 
+Using Lemma \ref{lem_cov_derivative}, we obtain that with high probability,
 \begin{align*}
-\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 + \hat a_3)\id + \hat a_4 \hat{M}^{\top}\hat{M}}{( a_1 \hat{M}^{\top}\hat{M}+a_2 )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
-&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
+\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 +  a_3(v))\id +v^2 a_4(v) {M}^{\top}{M}}{( v^2 a_1(v) {M}^{\top}{M}+a_2(v) )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
+&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi(v) \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
 \end{align*}
-with high probability. Together with and \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that w.h.p.,
+where $a_3(v)$ and $a_4(v)$ satify \eqref{eq_a34extra} with $\hat v$ replaced by $v$, and $\Pi$ was defined in \eqref{defnpihat}.
+Together \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that w.h.p.,
 \be\label{dicho_varbeta}
@@
 %\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
-holds uniformly for all $v\in [-C_0, C_0]$. In fact, we consider $v$ belonging to a discrete set 
+holds uniformly for all $v\in [-C_0, C_0]$. In fact, we first consider $v$ that belongs to a discrete set 
 $$V:=\{v_k = kp^{-1}: -(C_0p +1)\le k \le C_0p +1\}.$$
@@
 $$\Xi_1:=\left\{ \al_-(\rho_1)/2 \preceq  \frac{Z_1^T Z_1}{n_1}  \preceq   2\al_+(\rho_1) ,\  \al_-(\rho_2)/2 \preceq  \frac{Z_2^T Z_2}{n_2}  \preceq   2\al_+(\rho_2)\right\}$$
-holds with high probability. Now it is easy to check that on $\Xi_1$, for all $v_k \le v\le v_{k+1}$ we have the following estimates:
+holds with high probability. Now it is easy to check that on $\Xi_1$, the following estimates holds simultaneously for all $v_k \le v\le v_{k+1}$:
 \begin{align*}
@@
 $$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }-C_0\le v \le C_0\}$$
-holds with high probability. On the other hand, on $\Xi_1$ one can see that for any small constant $\e>0$, there exists a large enough constant $C_0>0$ depending on $\e$ such that
+holds with high probability. On the other hand, on $\Xi_1$ it is easy to check that for any small constant $\e>0$, there exists a large enough constant $C_0>0$ depending on $\e$ such that
 \begin{align*}
@@
 Together with the estimate at $\pm C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\in \R$ on the high probability event $\Xi_1\cap \Xi_2$.
-This concludes the proof since $v$ must be one of the real values.
+This concludes the proof of Lemma \ref{thm_model_shift}, since $\hat v$ must be one of the real values.
 \end{proof}
@@
 %For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
 
@@
 \begin{align}
-	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2. \label{eq_mtl_same_cov}
+	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2,\label{eq_mtl_same_cov}
 \end{align}
-%In order to prove Theorem \ref{thm_many_tasks}, we will derive a closed form solution for equation \eqref{eq_mtl_same_cov}. \todo{check!}
-For any fixed $W_1, W_2, \dots, W_t \in \R^r$, we can derive a closed form solution for $B$ as
+for $W_1, W_2, \dots, W_t \in \R^r$. Then it is not hard to derive a closed form solution for $B$ as
 	\begin{align*}
@@
 	\end{align*}
-	where we denote $\cal W \in\real^{r\times t}$ as $\cal W=[W_1, W_2, \dots, W_t]$.
+	where $\cal W \in\real^{r\times t}$ is a matrix defined as $\cal W=[W_1, W_2, \dots, W_t]$.
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use concentration to get the validation loss as
+Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as {\cor{start here}}
 \be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee

### 2020-08-17 arxiv/conclusions.tex
pf

@@
 In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
-We provided tight concentration bounds for the bias and the variance.
-Based on these bounds, we analyzed the impact of three properties, including task similarity, sample size, and covariate shift on the bias and variance, to derive conditions for transfer.
+We provided almost tight concentration bounds on the bias and variance.
+Based on these bounds, we analyzed the impact of three properties, including task similarity, sample size, and covariate shift, on the bias and variance, based on which we derived conditions for transfer.
 %Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
 We validated our theoretical results.
-Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging results inspired by our theory.
+Based on the theory, we proposed to train multi-task models by incrementally adding labeled data, and showed encouraging results inspired by our theory.
 We describe several open questions for future work.
-First, our bound on the bias term (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
+First, our bound on the bias term (cf. Lemma \ref{thm_model_shift}) involves an error term that scales down with $\rho_1$.
 Tightening this error bound might cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.

### 2020-08-17 arxiv/proof_main.tex
pf

@@
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as {\cor{start here}}
+Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
 \be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
@@
 %it remains to consider minimizing the validation loss
-	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari}(\cal W),$$
+	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari} ,$$
 where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
@@
 	\end{align*}
-	and the variance term $\delta_{\vari}(\cal W)$ can be calculated as
+	and the variance term $\delta_{\vari} $ can be calculated as
 	\begin{align*}
-		\delta_{\vari}(\cal W):= \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+		\delta_{\vari} := \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
 	\end{align*}
@@
 
-We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{k\times k}$, whose $(i,j)$-th entry is equal to $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
+We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{t\times t}$, whose $(i,j)$-th entry is given by $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
 	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
@@
 	\begin{align*}
-		\delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
+		\delta_{\bias}(Q) \equiv \delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
 	\end{align*}
-	From this equation we can solve the minimizer optimally as $Q_0\equiv  \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=U_{r}U_r^{\top}$.
+	From this equation we can solve the minimizer explicitly as $Q_0=U_{r}U_r^{\top}$.
 On the other hand, let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
 We claim that $\hat Q$ satisfies
-	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\| = \oo(1) \quad \text{w.h.p.}\ee
-	In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by \eqref{eq_isometric}, we obtain that
-	$$   \val(\hat {\cal W}) + t  \sigma^2 > (\val( {\cal W}_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
-	that is, $\hat {\cal W}$ is not a minimizer. This leads to a contradiction.
+	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
+	In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
+	$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
+	where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence  $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
 
-	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r U_r(i) +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that
+	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that with high probability,
 	\begin{align*}
@@
 		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{U_r(t)}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r U_r(t)-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{U_r(t)}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{v_t}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
 	\end{align*}
-	with high probability, where we used Lemma \ref{lem_minv} in the last step. Similar, by Lemma \ref{lem_minv} we have
+ where we used Lemma \ref{lem_minv} in the last step. On the other hand, by Lemma \ref{lem_minv} we have
 	$$\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$

### 2020-08-17 arxiv/proof_examples.tex
pf

@@
 
-For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows.
+For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
 \begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
-		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_2$ is a random vector with i.i.d.
-entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_1$ is a random vector such that $(\beta_1 - \beta_2)$ is a random vector with i.i.d.
-entries with mean $0$, variance $d^2$ and all moments.
+		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+		$\beta_2$ is a random vector that has i.i.d.
+entries with mean $0$, variance $\kappa^2$ and finite moments up to any order, and $(\beta_1-\beta_2)$ is a random vector that is independent of $\beta_2$ and has i.i.d.
+entries with mean $0$, variance $d^2$ and finite moments up to any order.
 Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}.$
-	Then we have with high probability,
+		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in \eqref{defnpihat}.	Then we have with high probability,
 		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias}, \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}.
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
 		\end{align*}
+		where $\Delta_{\vari}$ was defined in \eqref{Deltavarv}.
 \end{lemma}
@@
 \begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
-The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Theorem \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
-We only describe the main difference.
+The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
+We only describe the main difference in the following proof.
 
@@
 entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
-Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
+Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$, {\cor(start here)}
 \begin{align}

### 2020-08-17 arxiv/transfer.tex
pf

@@
 Note that Lemma \ref{lem_cov_shift} extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
+Note that if we set $n_1=0$ and $n_2=n$, then $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution to \eqref{eq_a12extra}, and one can see that \eqref{lem_cov_shift_eq} reduces to \eqref{XXA}.
 
@@
 	\squishlist
-		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
+The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in \eqref{choiceofpara}.
 %	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.

### 2020-08-17 arxiv/intro.tex
sec 2 wip

@@
 Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.
+
+\paragraph{Notations.}
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
+For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.

### 2020-08-17 arxiv/setup.tex
sec 2 wip

@@
 
-Suppose we have $t$ datasets, where $t$ is a fixed value that does not grow with the feature dimension $p$.
-In the high-dimensional linear regression setting (e.g.
-\cite{HMRT19,BLLT20}), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
-And each feature $x_i = \Sigma^{1/2}z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-The sample size $n_k $ equals $\rho_k\cdot p$ for a fixed value $\rho_k$.
-The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
+\todo{Consider adding some motivation later.}
+
+\noindent\textbf{Data model.}
+Suppose we have $t$ labeled regression tasks. %where $t$ is a fixed value that does not grow with the feature dimension $p$.
+For each task $k$ from $1$ to $t$, we have $n_k$ samples $x_1, x_2, \dots, x_{n_k}$ that are all $p$-dimensional feature vectors with real-valued labels $y_1, y_2, \dots, y_{n_k}$.
+Without loss of generality, we focus on predicting the $t$-th task and refer the $t$-th task as the target.
+We refer to task $1$ to task $t-1$ as source tasks.
+We assume that the labels of each task $k$ satisfy the linear model with unknown parameters $\beta_k\in\real^p$, that is,
+	\[ y_i = x_i^{\top}\beta_k + e_i, \text{ for all } 1 \le i \le n_k, \]
+where $e_i$ denotes random noise with mean zero and variance $\sigma^2$.
+To write the above notations more succiently, let $X_k \in \real^{n_k \times p}$ denote the covariates that consists of a feature vector in every row.
+Let
+	\[ Y_k = X_k \beta_k + \varepsilon_k, \text{ for all } 1\le i \le t \] denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d. random vector with mean zero and variance $\sigma^2$.
+
+Following \citet{HMRT19} and \citet{BLLT20},
+%In the high-dimensional linear regression setting (e.g.
+), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
+we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$.
+This setting is also known as the high-dimensional linear regression setting in the literature.
+%The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
 %Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
@@
 
+\medskip
+\noindent\textbf{Hard parameter sharing.}
 We focus on the commonly used hard parameter sharing model for multi-task learning \cite{R17}.
@@
 
-\textbf{Problem statement.}
+\medskip
+\noindent\textbf{Problem statement.}
 We focus on predicting a particular task, say the $t$-th task, without loss of generality.
@@
 To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
-
-\paragraph{Notations.}
-Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
-Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
-For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.

### 2020-08-17 arxiv/proof_examples.tex
pf

@@
 For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
-\begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
+\begin{lemma}\label{prop_model_shift_tight}
 		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
@@
 entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
-Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$, {\cor(start here)}
+Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
 \begin{align}
@@
 &=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
+&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2] \quad \text{w.h.p.},\label{anotherbeta}
 \end{align}
-where we denoted $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}.
+where $\delta_{\bias}(v)$ was defined in \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}.
 Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
@@
 \end{align*}
-Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
+Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric}, we obtain that
 \be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
@@
 $$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim p$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
+Note that $\delta^\star_{\bias}(v) \sim p$ by \eqref{eq_isometric}. Hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
 \be\label{replaceest}
@@
 \ee
-Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Theorem \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
-In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term, We omit the details.
+Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
+In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
 \end{proof}
@@
 More precisely, we have the following lemma.
-Later on, we combine the following lemma with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.
+Later on, we will combine it with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.
 
 \begin{lemma}
-In the isotropic model, for some constant $c_0>0$, suppose that
+In the isotropic model, suppose for some constant $c_0>0$, 
 \be\label{choiceofpara}
-	\frac{pd^2}{\sigma^2} \le \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0}.
+	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
 \ee
-Then we have
+where $\e_0$ is the constant as appeared in \eqref{approxvalid}. Then we have
 \begin{align}
 \te(\hat{\beta}_2^{\MTL})=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
-&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
+&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \quad \text{w.h.p.} \label{simple1}
 \end{align}
-w.h.p. for some constant $\e>0$.
+for some constant $\e>0$.
 \end{lemma}
@@
 \begin{proof}
-	Using Lemma \ref{largedeviation}, we obtain that $\val(v)= N_2\cdot h(v)  \left( 1+\OO(p^{-1/2+\e})\right)$.
-	We define the function
+	Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
+	%We define the function
 	\begin{align}
@@
 	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
-	Hence the validation loss in \eqref{approxvalid} reduces to
+	Furthermore, the validation loss in \eqref{approxvalid} reduces to
 	\be\label{boundv-w}
-		g(v)=\left[N_2\cdot h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
+		g(v)=\left[N_2 h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)\quad \text{w.h.p.}
 	\ee
-	with high probability for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
-
-Let $\hat w$ the minimizer of $h(v)$. The proof consists of two steps.
+	for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
+Let $\hat w$ be the minimizer of $h(v)$. Our proof consists of the following two steps.
 \squishlist
@@
 For the first step, we will prove the following result.
-
 \begin{claim}\label{lem_hat_v}
@@
 \begin{proof}
-To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof.
+To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof.
 First it is easy to observe that $h(w)< h(-w)$ for $w> 0$.
@@
 \begin{align*}
-h'(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
- &+~ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-		&-~ 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
+h'(w) \ge & \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
+ &+ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+		&- 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
 \end{align*}
-where the matrix $\cal A$ is
+where the matrix $\cal A$ is defined as
 \begin{align*}

### 2020-08-17 arxiv/proof_examples.tex
pf

@@
 	\be\label{boundv-w}
-		g(v)=\left[N_2 h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)\quad \text{w.h.p.}
+		g(v)=\left[N_2 h(v) + (N_1+N_2)\sigma^2\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)\quad \text{w.h.p.}
 	\ee
@@
 First it is easy to observe that $h(w)< h(-w)$ for $w> 0$.
-Hence it suffices to assume that $w\ge 0$.
-We first consider the case $w\ge 1$.
-We write
+Second, using \eqref{eq_isometric}, it is easy to check that $h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.
+Hence it suffices to consider the case $1/2\le w\le 2$.
+
+We first consider the case $1\le w\le 2$. We write
 \begin{align}
@@
 $$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
-Hence $h'(w)>0$ on $(w_1,\infty)$, i.e. $h(w)$ is strictly increasing for $w>w_1$. This gives $\hat w\le w_1$.
+Hence $h'(w)>0$ on $(w_1,\infty)$, %i.e. $h(w)$ is strictly increasing for $w>w_1$. This 
+which gives $\hat w\le w_1$.
 
-Then we consider the case $w\le 1$, and the proof is similar as above. Taking derivative of $h(w)$, we obtain that
+For the case $1/2\le w\le 1$, the proof is similar as above. Taking derivative of $h(w)$, we obtain that
 \begin{align}
@@
 	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-	& + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }\\
-			 =& \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
+	& + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }= \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
 \end{align}
@@
 $$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
-Hence $h'(w)<0$ on $[0,w_2)$, i.e. $h(w)$ is strictly decreasing for $w<w_2$. This gives $\hat w\ge w_2$.
+Hence $h'(w)<0$ on $[0,w_2)$, %i.e. $h(w)$ is strictly decreasing for $w<w_2$. This 
+which gives $\hat w\ge w_2$.
 
-In sum, we obtain that $w_2\le w\le w_1$. Note that under our assumptions, we have
-$$\max(|w_1 -1|, |w_2 -1|) =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
-which concludes the proof.
+In sum, we have shown that $w_2\le w\le w_1$. Together with
+$$\max\{|w_1 -1|, |w_2 -1|\} =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
+we conclude \eqref{hatw_add1}.
 \end{proof}
@@
 %\begin{proof}
- In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim p d^2$.
+ In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim \sigma^2$.
 Moreover, under \eqref{choiceofpara} we have
-$$h(w) =\OO(pd^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
+$$h(w) =\OO(\sigma^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
 Thus we obtain that for $|w-1|\ge 2C\cal E$,
-$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min(h(w_1),h(w_2))|\gtrsim pd^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
-which leads to $g(w) > g(\hat w)$ w.h.p.
-by \eqref{boundv-w}.
+$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min\{h(w_1),h(w_2)\}|\gtrsim \sigma^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
+which leads to $g(w) > g(\hat w)$ with high probability by \eqref{boundv-w}.
 Thus $w$ cannot be a minimizer of $g(v)$, and we must have $|\hat v - 1|\le 2C\cal E$.
@@
 
-Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$ again, we get w.h.p.,
+Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$, we get that w.h.p.,
 \begin{align}
@@
 \end{align}
-In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order.
-With estimate \eqref{eq_isometric}, we see that
-$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim \frac{p}{n_1+n_2}.$$
+In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. With \eqref{eq_isometric}, we have that
+$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim 1.$$
 Hence we need to choose that $p d^2 \sim \sigma^2$.
 On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$.
-The above considerations lead to the choices of parameters in \eqref{choiceofpara}.
-Moreover, under \eqref{choiceofpara} we can simplify \eqref{1Liso} to \eqref{simple1}.
+The above considerations lead to the choices of parameters in \eqref{choiceofpara}, under which we can simplify \eqref{1Liso} to \eqref{simple1}.
 %\begin{align}
@@
 
-Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$.
-In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
-
-\begin{proposition}%[Labeled data de-noising]
-\label{prop_var_transition}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
-	Then we have the following transition with respect to $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 < - \nu^{1/2} \rho_1 \cdot p d^2+\left(1+ \nu^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
-		\item If $\sigma_1^2 > -\nu^{-1/2}\rho_1\cdot p d^2   +\left(1+ \nu^{1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-%The proof of Proposition \ref{prop_var_transition} is similar to Proposition \ref{prop_dist_transition}.
+The proof of Proposition \ref{prop_var_transition} is similar to the above proof of Proposition \ref{prop_dist_transition}.
 %The details can be found in Appendix \ref{app_proof_data}.
 
-\begin{proof}%[Proof of Proposition \ref{prop_var_transition}]
+\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
 In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 

### 2020-08-17 arxiv/transfer.tex
pf

@@
 \subsection{Two Tasks}
+
+First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
+
+\begin{assumption}[Moment assumptions]\label{assm_secA1}
+We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrix, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
+entries with mean zero and variance one.
+Note that the rows of $X$ are i.i.d.
+centered random vectors with covariance matrix $\Sigma$.
+For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
+\begin{equation}\label{assmAhigh}
+\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
+\end{equation}
+ We assume that $n=\rho p$ for some fixed constant $\rho>1$.
+Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
+Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
+\end{assumption}
+Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
+If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
+We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} in Section \ref{sec locallaw1}.
+
+Then we make the following assumptions on the data models.
+\begin{assumption}[Linear regression model]\label{assm_secA2}
+For some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants.
+$\e_i\in \R^{n_i}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
+\end{assumption}
 
@@
 The expectation of $g(v)$ can be written as follows.
-\begin{align*}
-		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \\
+\begin{align}
+		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \nonumber\\
 	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
@@
 		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
-		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{eq_val_mtl}
-\end{align*}
+		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{revise_eq_val_mtl}
+\end{align}
 
@@
 
+Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$.
+In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
+
+\begin{proposition}%[Labeled data de-noising]
+\label{prop_var_transition}
+	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
+	Then we have the following transition with respect to $\sigma_1^2$:
+	\begin{itemize}
+		\item If $\sigma_1^2 < - \nu^{1/2} \rho_1 \cdot p d^2+\left(1+ \nu^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
+		\item If $\sigma_1^2 > -\nu^{-1/2}\rho_1\cdot p d^2   +\left(1+ \nu^{1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
+	\end{itemize}
+\end{proposition}
+As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
+
 \textbf{Algorithmic consequence.}

### 2020-08-17 arxiv/setup.tex
sec 2 wip

@@
 ), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
-we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$, where $z_i\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$.
+we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$ for $i = 1, \dots, n_k$, where $z_i\in\real^p$ is an i.i.d.
+random vector with  mean zero and unit variance.
+The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$ that does not grow with feature dimension $p$.
 This setting is also known as the high-dimensional linear regression setting in the literature.
+There are two motivations for studying the high-dimensional linear regression setting for multi-task learning.
+First, this setting captures salient properties of modern large-scale datasets, where the sample sizes are usually on the order of tens to hundreds of the number of features \cite{sur2019modern}.
+Second, as we will see soon in Section \ref{sec_main}, we can derive precise asymptotics of the generalization error that scale with properties of the task data such as sample sizes.
 %The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.

### 2020-08-17 arxiv/proof_examples.tex
pf

@@
 With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
-With slight abuse of notations, we shall write $\hat a_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.
+%With slight abuse of notations, we shall write $\hat a_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.
 
@@
 	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
-Then solving equations \eqref{eq_a12extra} and \eqref{eq_a34extra} with $\lambda_i=1$, we get that
+Then solving equations \eqref{eq_a12extra} and \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
 	\begin{align}
@@
 \begin{split}
-\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
-&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
+\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
 \end{split}
@@
 	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
-	we can get from Lemma \ref{prop_model_shift_tight} (or rather its proof) that
+	we can get from Lemma \ref{prop_model_shift_tight} that
 \be\label{Deltabeta} 
@@
 %	\end{align*}
-Note that 
+Note that by \eqref{simple1}, we have
  \be\label{var-beta}\te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} .\ee
@@
 
+\vspace{5pt}
+
 \noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
 \be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-	we have that $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper101} to
+then $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper101} to
 	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
 Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$ and $\nu\ge \al_+^2(\rho_1) +  \oo(1) $, it gives the first statement of Proposition \ref{prop_dist_transition}.
+
+ \vspace{5pt}
 
@@
 	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper102} to
-	\be\label{neg1} \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
+	\be\label{neg1} \frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
 which gives the second statement of Proposition \ref{prop_dist_transition}.
@@
 %where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
-In the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
+For the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
 \begin{align*}
@@
 In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
-Since the proof is almost the same as the one for Lemma \ref{lem_hat_v}, we omit the details. 
+Since the proof is almost the same as the one for Claim \ref{lem_hat_v}, we omit the details. 
 %$$|\hat w-1|=\OO(p^{-1}).$$
@@
 %We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
-Thus under the choice of parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
+Thus under \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
 \be \label{simple2}
@@
 &+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
-&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} ,
 \end{split}
 \ee
-Then we have 
+with high probability for some small constant $\e>0$. Then we can write
 $$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
@@
 $$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
-satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$, 
+satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$; 
 $$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
-satisfies \eqref{Deltabeta}, and $\delta_{\vari}^{(2)}$ is defined as
+satisfies \eqref{Deltabeta}; $\delta_{\vari}^{(2)}$ is defined as
 \begin{align*}	
@@
 %where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
-To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
 This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
 \be\label{Deltavar2} 
-\al_-(\rho_1) - \oo(1)  \le  {\delta_{\vari}^{(2)}}/{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
+\al_-(\rho_1) - \oo(1)  \le  \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
 where 
@@
 
-Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
+{\cor(start here)} Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
 Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.

### 2020-08-17 arxiv/proof_examples.tex
pf

@@
 
-{\cor(start here)} Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
+ Note that the condition $pd^2< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
 Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
 It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
+
+\vspace{5pt}
 
@@
 \ee
-then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma1} to get
+then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can solve \eqref{cond sigma1} to get
 \begin{align*}
@@
 This proves the first claim of Proposition \ref{prop_var_transition} using $\nu\ge \al_+^2(\rho_1) +  \oo(1) $.
+
+\vspace{5pt}
 
@@
 
-Next we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
-%In the statement, we shall denote the data efficiency ratio as $\al^\star$.
+Next we prove Proposition \ref{prop_data_efficiency}, which gives upper and lower bounds on the data efficiency ratio for Taskonomy.
 
-\begin{proposition}%[Labeled data efficiency]
-\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 \ge 9$ and $\Psi(\beta_1, \beta_2) < (5(\rho_1-1))^{-1} + (5(\rho_2-1))^{-1}$.
-	Then the data efficiency ratio $x^\star$ satisfies 
-	\be\label{eq_uplowx} x_l  \le x^\star\le \frac{1}{\rho_1 + \rho_2} \bigbrace{  \frac{2}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}+1}, \ee
-	where we denoted
-	$$x_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
-\end{proposition}
-
-\begin{proof}%[Proof of Proposition \ref{prop_data_efficiency}]
+\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
 Suppose we have reduced number of datapoints---$x n_1$ for task 1 and $x n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.

### 2020-08-17 arxiv/transfer.tex
sec 2 wip
pf

@@
 %In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-The result can be found in Proposition \ref{prop_data_efficiency} in Appendix \ref{app_proof_32}.
+
+Next we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
+Its proof can be found in Appendix \ref{app_proof_32}.
+%In the statement, we shall denote the data efficiency ratio as $\al^\star$.
+
+\begin{proposition}%[Labeled data efficiency]
+\label{prop_data_efficiency}
+	In the isotropic model, assume that $\rho_1,\rho_2 \ge 9$ and $\Psi(\beta_1, \beta_2) < (5(\rho_1-1))^{-1} + (5(\rho_2-1))^{-1}$.
+	Then the data efficiency ratio $x^\star$ satisfies 
+	\be\label{eq_uplowx} x_l  \le x^\star\le \frac{1}{\rho_1 + \rho_2} \bigbrace{  \frac{2}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}+1}, \ee
+	where we denoted
+	$$x_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
+\end{proposition}
 

### 2020-08-17 arxiv/proof_examples.tex
pf

@@
 \begin{proof}[Proof of Proposition \ref{prop_data_size}]
-Following the proof of Proposition \ref{prop_dist_transition}, we see that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ w.h.p.
+Following the proof of Proposition \ref{prop_dist_transition}, we know that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ w.h.p.
 if \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ w.h.p.
@@
 is strictly decreasing with respect to $\rho_1$ as long as $\rho_2> 2$, and $ \Phi(\rho_1, \rho_2)$ converges to $(\rho_2-1)^{-1}$ as $\rho_1\to \infty$.
-Moreover, we notice that $\left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} < 2$ for $\rho_1>40$.
-Hence \eqref{explainpsi} implies that \eqref{neg1} holds for all  large enough $\rho_1$.
-The transition from positive transfer when $\rho_1$ is small to negative transfer when $\rho_1$ is large is described by the two bounds in Proposition \ref{prop_data_size}.
-
+Since $\left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} < 2$ for $\rho_1>40$,  \eqref{explainpsi} implies that \eqref{neg1} holds for large enough $\rho_1$.
+Moreover, the transition from positive transfer when $\rho_1$ is small to negative transfer when $\rho_1$ is large is described by the two bounds in Proposition \ref{prop_data_size}, which we will show now.
 % $$ \Psi(\beta_1,\beta_2) \ge \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
@@
 %$\gamma_+^{-1}$
-
-The two bounds follows directly from \eqref{pos1} and \eqref{neg1}. We will use the following trivial inequalities 
+%The two bounds follows directly from \eqref{pos1} and \eqref{neg1}. 
+In the following proof, we will use the following trivial inequalities 
 \be\label{trivialphi}
-\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le  \Phi(\rho_1, \rho_2) \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
+\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le  \frac1{\Phi(\rho_1, \rho_2)} \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
 \ee
@@
 
- Note that if we require the RHS of \eqref{addconstraint} to be larger than $40$, that is, \eqref{addconstraint} is not a null condition. Then together with \eqref{explainpsi}, we get
+ Note that if we require the RHS of \eqref{addconstraint} to be larger than $40$, that is, \eqref{addconstraint} is not a null condition, then with \eqref{explainpsi} we get
  $$ \rho_2 - 2>\left[ 2\left( \al_+^2(\rho_1) +  \oo(1) \right)  -1\right]\rho_1 .$$
@@
 
+\vspace{5pt}
+
  \noindent{\bf Negative transfer.} 
@@
  \end{align}
- where we used $(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) > \rho_2-1.5$ for $\rho_1>40$ and $\rho_2>110$. Then we can solve \eqref{neg1solv} to get
+ where we used $(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) > \rho_2-1.5$ for $\rho_1>40$ and $\rho_2>110$. Then we can solve \eqref{neg1solv} to get that
  \be\label{addconstaint2}
- \rho_1 > \frac{(\rho_2-2) \sigma^2}{\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)  - 1}  ,
+ \rho_1 > \frac{\rho_2-2 }{\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)  - 1}  ,
  \ee
@@
 
-Next we prove Proposition \ref{prop_data_efficiency}, which gives upper and lower bounds on the data efficiency ratio for Taskonomy.
+Next we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
 
@@
 	\end{align*}
-Moreover, with high probability,
+Then with Lemma \ref{lem_cov_shift} we can obtain that with high probability,
 	\be\label{reduceproof1}
 \begin{split}
-\te_i(\hat \beta_i^{\MTL}(x)) =  \frac{\sigma^2}{x (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\bias}, \quad i=1,2.
+\te_i(\hat \beta_i^{\MTL}(x)) =  \frac{\sigma^2}{x (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\bias}, \quad i=1,2,
 \end{split}
 \ee
- Here the model shift biases $\delta^{(i)}_{\bias}$ satisfy that  
+ where as in \eqref{Deltabeta}, the model shift biases $\delta^{(i)}_{\bias}$ satisfy that with high probability,
 \be\nonumber %\label{Deltabeta} 
-\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_{\bias}^{(i)}}/{ \Delta_{\bias}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2,\ee	
-where $ \Delta^{(i)}_{\bias}$ are defined as 
+\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_{\bias}^{(i)}}/{ \Delta_{\bias}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2.\ee	
+Here $ \Delta^{(i)}_{\bias}$ are defined as 
 \be \nonumber
@@
 \ee
-On the other hand, using Lemma \ref{lem_minv} we have w.h.p.,
+On the other hand, by Lemma \ref{lem_minv} we have that w.h.p.,
 \be\label{reduceproof2} 
@@
 %$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
-In fact, one can see that if $x< x_l$, then we have 
-$$ \frac{2\sigma^2}{x (\rho_1+\rho_2) - 1} > \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1},$$
-that is, $\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))$ is larger than $\te_1(\hat{\beta}_t^{\STL}) + \te_2(\hat{\beta}_t^{\STL})$ even if we do not take into account the model shift bias terms $ \delta^{(i)}_{\bias}$.
+In fact, if $x< x_l$, then we have that
+$$ \frac{2\sigma^2}{x (\rho_1+\rho_2) - 1} > \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1}.$$
+This shows that $\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))$ is larger than $\te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL})$ even if we do not take into account the model shift biases $ \delta^{(i)}_{\bias}$.
 
@@
 In particular, we have $x\rho > x_l \rho \ge \min(\rho_1,\rho_2)$, where we abbreviated $\rho:=\rho_1+\rho_2$.
-
 %Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
-
-\noindent{\bf The upper bound.} From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies 
+%\noindent{\bf The upper bound.} 
+From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies 
 \be\nonumber
@@
 %where we abbreviated $\rho:=\rho_1+\rho_2$. 
-
+\end{proof}
+\begin{remark}
 We can get better bounds if the values of $\rho_1$ and $\rho_2$ increase.
-For example, if we consider the case $\min(\rho_1,\rho_2)\ge 100$, then with some basic calculations, one can show that in this case
+For example, if we consider the case $\min(\rho_1,\rho_2)\ge 100$, then with some basic calculations, one can check that in this case
 $$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52.$$
@@
 \begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) pd^2 > \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{x\rho - 1} ,
+&\left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)  > \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
 \end{split}
@@
 This gives a lower bound above $x_l$.
-\end{proof}
+\end{remark}
 
@@
 
-We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
+Finally, in this subsection we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.
 
 \begin{proof}[Proof of Proposition \ref{prop_covariate}]
-Let 
+Denote the minimizer of $g$ by 
 $$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
 We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
+With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
+Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
 \be \nonumber
 \begin{split}
-g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
+g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
 \end{split}
 \ee
-with high probability for some constant $\e>0$.
+ for some constant $\e>0$.
 In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
@@
 \be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-
 On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,

### 2020-08-18 arxiv/setup.tex
sec 2

@@
 \noindent\textbf{Hard parameter sharing.}
-We focus on the commonly used hard parameter sharing model for multi-task learning \cite{R17}.
-When specialized to the linear regression setting, the model consists of a linear layer $B\in\real^{p\times r}$ that is shared by all tasks and $t$ output layers $W_1, \dots, W_t$ that are in $\real^r$.
+We study multi-task learning models that use hard parameter sharing, which is the most commonly used architecture in practice \cite{R17}.
+Specifically, we consider a two-layer neural network with a shared layer $B\in\real^{p\times r}$ for all tasks and $t$ output layers $W_1, \dots, W_t$ for every task from $1$ to $t$, where each output layer is a $r$-dimensional vector.
 The width of $B$, denoted by $r$, plays an important role in regularization.
@@
 Hence, we assume that $r < t$ in our study.
-For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following procedure inspired by how hard parameter sharing models are trained in practice (e.g. \cite{MTDNN19}).
-\squishlist
+%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
+We study the following procedure inspired by how hard parameter sharing models are trained in practice.
+\begin{enumerate}
 	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
@@
 	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a closed form equation for $\hat{B}$ that depends on $W_1,\dots, W_k$.
-		\vspace{-0.075in}
-		{\small\begin{align}\label{eq_mtl}
-			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{tr} B W_k - Y_k^{tr}}^2.
+		{\begin{align}\label{eq_mtl}
+			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{\text{tr}} B W_k - Y_k^{\text{tr}}}^2.
 		\end{align}}
-		\vspace{-0.075in}
 	\item Tune the output layers $W_i$: set $B = \hat{B}$ and minimize the validation loss over $W_1,\dots, W_k$.
-		\vspace{-0.075in}
-		{\small\begin{align}\label{eq_mtl_eval}
-			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{val} \hat{B} W_k - Y_k^{val}}^2.
+		{\begin{align}\label{eq_mtl_eval}
+			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{\text{val}} \hat{B} W_k - Y_k^{\text{val}}}^2.
 		\end{align}}
-		\vspace{-0.075in}
-\squishend
-\vspace{-0.1in}
+\end{enumerate}
+Let $\hat{\beta}_t^{\MTL}$ denote the multi-task learning estimator obtained from the procedure above.
+By contrast, let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$ denote the single-task learning estimator. % denoted by $L(\hat{\beta}_t^{\STL})$.
 %where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
 %Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
-We make several remarks.
 In general, the objective $f(\cdot)$ is non-convex in $B$ and the $W_k$'s.
 Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
-For our purpose, a validation set of size $\rho_i \cdot p^{0.99}$ that is much larger than the number of output layer parameters $r\cdot t$ suffices.
-The size of the training set is then $\rho_i (p - p^{0.99})$.
+For our purpose, a validation set that is much larger than the number of output layer parameters $r\cdot t$ suffices (e.g. $\rho_i \cdot p^{0.5}$).
+%The size of the training set is then $\rho_i (p - p^{0.99})$.
 The advantage of tuning the output layers on the validation set is to reduce the effect of noise from $\hat{B}$.
@@
 \noindent\textbf{Problem statement.}
-We focus on predicting a particular task, say the $t$-th task, without loss of generality.
-Let $\hat{\beta}_t^{\MTL}$ denote the multi-task estimator obtained from the procedure above.
-Our goal is to compare the prediction loss of $\hat{\beta}_t^{\MTL}$, defined by
-{\small\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) = \exargnob{\set{\varepsilon_i}_{i=1}^t}\exarg{x = \Sigma_t^{1/2} z}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
-		= \exargnob{\set{\varepsilon_i}_i^t}\bignorm{\Sigma_2^{1/2} (\hat{\beta}_t^{\MTL} - \beta_t)}^2,
+%We focus on predicting a particular task, say the $t$-th task, without loss of generality.
+For an estimator $\hat{\beta}$ of the target task model $\beta_t$, we define the prediction loss of the estimator $\hat{\beta}$ as
+	{\begin{align*}
+		\te(\hat{\beta}) = \exarg{x = \Sigma_t^{1/2} z}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
+		= \bignorm{\Sigma_t^{1/2} (\hat{\beta} - \beta_t)}^2,
 	\end{align*}}%
+where $x = \Sigma_t^{1/2} z$ denotes a random feature vector with covariance $\Sigma_t$.
+In the above equation, $x^{\top}\beta_t$ is the true label of $x$.
 %= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)
-to the prediction loss $L(\hat{\beta}_t^{\STL})$ of the single-task estimator $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$.
-We say there is negative transfer if  $L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL})$ and positive transfer otherwise.
+We say that the source tasks provide a \textit{positive transfer} to the target task if the prediction loss of the MTL estimator is lower than that of the STL estimator, that is, if
+	\[ L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL}). \]
+On the other hand, we say that the source tasks provide a \textit{negative transfer} to the target task if $L(\hat{\beta}_t^{\MTL}) < L(\hat{\beta}_t^{\STL})$.
+Our goal is to study when the source tasks provide a positive transfer to the target task.
 
-\subsection{Bias and Variance}
+\paragraph{Notations.}
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
+For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+%\subsection{Bias and Variance}
 
-As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL})$ into a bias term and a variance term as follows (derived in Appendix \ref{app_proof_sec3}).
-%Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
-%We can  the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
-{\small\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
-	+&~ \sigma^2 \bigbrace{\bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} - \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}}. \label{eq_te_var}
-\end{align}}%
-In the above, $\hat{v} = W_1 / W_2$ where $W_1, W_2$ are obtained from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
-The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
+%\noindent\textbf{Positive/Negative transfer.}
 
-Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$.
-Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
-Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$ minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Intuitively, the more \textit{samples} we have, the smaller the variance is.
-Meanwhile, \textit{covariate shift} also affects how small the variance can be.
 %This part introduces a positive variance reduction effect from adding the source labels.

### 2020-08-18 arxiv/transfer.tex
sec 2

--- 2020-08-17 arxiv/transfer.tex
@@
-\section{Main Results}
+\section{Main Results}\label{sec_main}
 
@@
 
-\subsection{Two Tasks}
+As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL})$ into a bias term and a variance term as follows (derived in Appendix \ref{app_proof_sec3}).
+%Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
+%We can  the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
+{\small\begin{align}
+	\te(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
+	+&~ \sigma^2 \bigbrace{\bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} - \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}}. \label{eq_te_var}
+\end{align}}%
+In the above, $\hat{v} = W_1 / W_2$ where $W_1, W_2$ are obtained from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
+The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
+
+Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$.
+Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
+Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$ minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
+Intuitively, the more \textit{samples} we have, the smaller the variance is.
+Meanwhile, \textit{covariate shift} also affects how small the variance can be.
+
+\subsection{Two Tasks}\label{sec_two}
 
@@
 
-\subsection{Multiple Tasks}\label{sec_main}
+\subsection{Multiple Tasks}\label{sec_multiple}
 
@@
 	\squishlist
-		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
 	\squishend
@@
 	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
-The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in \eqref{choiceofpara}.
 %	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.

### 2020-08-19 arxiv/proof_main.tex
pf

@@
 and
-\begin{align*}
+\begin{align}\label{revise_deltabias}
  \delta_{\bias}(\hat v)&= \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2.
-\end{align*}
+\end{align}
 We introduce the notation $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for $v\in \R$. Then the proof is divided into the following four steps. 
@@
 \be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
+
+{\color{red}
+\begin{align*}
+	f(W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X \hat B W_i - Y_i}^2 = \val(\cal W) \cdot \left( 1+\OO(p^{-1/2+\e})\right),
+\end{align*}
+where
+\begin{align*}
+	 \val(\cal W) &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \E_{\e_i:1\le i \le t}\sum_{i=1}^t\left\| X(X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}W_i -\e_i\right\| \\
+	 &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \sigma^2 (nt-pr).
+\end{align*}
+
+}
+
 Here $\val(\cal W)$ is defined as

### 2020-08-19 arxiv/transfer.tex
pf

@@
 \end{align}
+
+{\color{red}\begin{align*} 
+			& f(W_1, W_2) = \bignorm{X_1 \hat B w_1 - Y_1}^2 + \bignorm{X_2 \hat B w_2 - Y_2}^2\\
+			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}Y_1 + vX_2^{\top}Y_2\right) - Y_1}^2 \\
+			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}Y_1 + X_2^{\top}Y_2\right) - Y_2}^2 \\
+			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}\e_1 + vX_2^{\top}\e_2\right) - \e_1 + X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
+			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}\e_1 + X_2^{\top}\e_2\right) - \e_2 + vX_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
+			&=\val(v)\cdot \left( 1+\OO(p^{-1/2\e})\right) \quad \text{w.h.p.},
+		\end{align*}
+		where
+		\begin{align*}
+		\val(v)&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
+			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
+			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}   X_1^{\top} -\id\right)^2 \\
+			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_1^\top\right)\\
+			&+\sigma^2 \tr\left(X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^{\top} -\id\right)^2 \\
+			&+\sigma^2 \tr\left(v^2 X_2\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^\top\right)\\
+			&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
+			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 +(n_1+n_2-p)\sigma^2.
+		\end{align*}
+	}
 

### 2020-08-19 arxiv/setup.tex
pf
edits

@@
 \begin{enumerate}
-	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-	The size of each set is described below.
-	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a closed form equation for $\hat{B}$ that depends on $W_1,\dots, W_k$.
+%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
+%	The size of each set is described below.
+	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
 		{\begin{align}\label{eq_mtl}
-			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{\text{tr}} B W_k - Y_k^{\text{tr}}}^2.
+			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2.
 		\end{align}}
-	\item Tune the output layers $W_i$: set $B = \hat{B}$ and minimize the validation loss over $W_1,\dots, W_k$.
+	\item Learn the output layers $W_1, W_2, \dots, W_t$: set $B = \hat{B}$ and minimize the training loss over $W_1, W_2, \dots, W_t$.
 		{\begin{align}\label{eq_mtl_eval}
-			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{\text{val}} \hat{B} W_k - Y_k^{\text{val}}}^2.
+			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k \hat{B} W_k - Y_k}^2.
 		\end{align}}
@@
 Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
-For our purpose, a validation set that is much larger than the number of output layer parameters $r\cdot t$ suffices (e.g. $\rho_i \cdot p^{0.5}$).
+%For our purpose, a validation set that is much larger than the number of output layer parameters $r\cdot t$ suffices (e.g. $\rho_i \cdot p^{0.5}$).
 %The size of the training set is then $\rho_i (p - p^{0.99})$.
-The advantage of tuning the output layers on the validation set is to reduce the effect of noise from $\hat{B}$.
+%The advantage of tuning the output layers on the validation set is to reduce the effect of noise from $\hat{B}$.
 %For more details, we refer the reader to Appendix \ref{app_proof_sec3}.

### 2020-08-20 arxiv/transfer.tex
edits
wip

@@
-\section{Main Results}\label{sec_main}
+\section{Bias-variance Decomposition for the General Case}\label{sec_general}
 
-\begin{proposition}[Bias-variance tradeoff]
-	Variance always reduces and bias always increases.
-\end{proposition}
+%\begin{proposition}[Bias-variance tradeoff]
+%	Variance always reduces and bias always increases.
+%\end{proposition}
+In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
+First, we consider the two-task case.
+We provide precise asymptotics of the bias and variance of the multi-task learning estimator.
+We apply recent developments from the random matrix theory literature to characterize the bias and variance.
+The results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties (Section \ref{sec_special}).
+Second, we consider the multiple-task case where all tasks have the same features but different labels.
+We extend the bias-variance decomposition of the two-task case to this setting and show qualitatively similar results.
+%For the single-task learning estimator, there are well-known results that relate its prediction loss to sample size and noise variance.
+
+%We focus on the high-dimensional linear regression setting \cite{}
+
+\iffalse
+First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
+
+\begin{assumption}[Moment assumptions]%\label{assm_secA1}
+We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrix, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
+entries with mean zero and variance one.
+Note that the rows of $X$ are i.i.d.
+centered random vectors with covariance matrix $\Sigma$.
+For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
+\begin{equation}\label{assmAhigh}
+\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
+\end{equation}
+ We assume that $n=\rho p$ for some fixed constant $\rho>1$.
+Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
+Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
+\end{assumption}
+Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
+If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
+We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} in Section \ref{sec locallaw1}.
+\fi
+
+\subsection{Two-task Case}\label{sec_two}
 
@@
 
-\subsection{Two Tasks}\label{sec_two}
-
-First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
-
-\begin{assumption}[Moment assumptions]\label{assm_secA1}
-We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrix, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
-entries with mean zero and variance one.
-Note that the rows of $X$ are i.i.d.
-centered random vectors with covariance matrix $\Sigma$.
-For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\begin{equation}\label{assmAhigh}
-\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
-\end{equation}
- We assume that $n=\rho p$ for some fixed constant $\rho>1$.
-Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
-Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
-\end{assumption}
-Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
-If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
-We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} in Section \ref{sec locallaw1}.
-
-Then we make the following assumptions on the data models.
-\begin{assumption}[Linear regression model]\label{assm_secA2}
-For some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+%Then we make the following assumptions on the data models.
+%\begin{assumption}[Linear regression model]\label{assm_secA2}
+%For some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
 Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants.
-$\e_i\in \R^{n_i}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
-\end{assumption}
+%$\e_i\in \R^{n_i}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
+%\end{assumption}
 
@@
 
+\iffalse
 {\color{red}\begin{align*} 
@@
 	}
+\fi
 
@@
 
-\subsection{Multiple Tasks}\label{sec_multiple}
+\subsection{Multiple-task Case}\label{sec_multiple}
 
@@
 We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-
-%\subsection{The Case of Two Tasks}
-
-%\subsection{The Case of Multiple Tasks}
 
@@
 
-\section{Theoretical Implication}\label{sec_insight}
+\section{Special Case: Isotropic Covariance and Covariate Shift}\label{sec_special}
 
@@
 
+\subsection{Sample Ratio}\label{sec_data_size}
+
+In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
+%More generally, such results are still applicable when all task data are being added simultaneously.
+On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
+For such settings, we have also observed that adding more labeled data from one task does not always help.
+%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
+In the isotropic model, we consider what happens if we vary the source task sample size.
+Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
+%Figure \ref{fig_size} provides a simulation result for such a setting.
+%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+
+\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
+	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+	Then we have that
+	\squishlist
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
+$\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
+		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \nu}$, then w.h.p.
+$\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
+	\squishend
+\end{proposition}
+Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
+We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+There are several unexplained observations near $y = 0$ caused by $\nu$.
+The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
+
+\subsection{Covariate Shift}\label{sec_covshift}
+
+So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+In general, the covariance matrices of the two tasks may be different such as in text classification.
+In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
+We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
+
+\textit{Example.}
+	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
+	Assume that $\Psi(\beta_1, \beta_2) = 0$ for simplicity.
+	We compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+	Hence, $\lambda$ measures the severity of the covariate shift.
+	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
+	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
+
+%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
+We compare different choices of $M$ that belong to the following bounded set.
+Let $\lambda_i$ be the $i$-th singular value of $M$.
+Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
+\vspace{-0.025in}
+{\small\begin{align*}
+		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
+\end{align*}}
+%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
+\begin{proposition}[Covariate shift]\label{prop_covariate}
+	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
+	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
+	We have that
+	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
+\end{proposition}
+This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
+The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
+%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
+%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
+
+%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
+
+%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
+%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
+%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
+%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
+
+\subsection{Extension to Multiple Tasks}
+
+\section{Theoretical Implication}
+
 Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$.
@@
 \squishend
-
-\subsection{Sample Size}\label{sec_data_size}
-
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
-%More generally, such results are still applicable when all task data are being added simultaneously.
-On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
-For such settings, we have also observed that adding more labeled data from one task does not always help.
-%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-In the isotropic model, we consider what happens if we vary the source task sample size.
-Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-%Figure \ref{fig_size} provides a simulation result for such a setting.
-%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-
-\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
-	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-	Then we have that
-	\squishlist
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
-$\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \nu}$, then w.h.p.
-$\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
-\end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
-We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-There are several unexplained observations near $y = 0$ caused by $\nu$.
-The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
 
@@
 
-\subsection{Covariate Shift}\label{sec_covshift}
-
-So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-In general, the covariance matrices of the two tasks may be different such as in text classification.
-In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
-We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
-
-\textit{Example.}
-	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
-	Assume that $\Psi(\beta_1, \beta_2) = 0$ for simplicity.
-	We compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	Hence, $\lambda$ measures the severity of the covariate shift.
-	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-
-%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-We compare different choices of $M$ that belong to the following bounded set.
-Let $\lambda_i$ be the $i$-th singular value of $M$.
-Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-\vspace{-0.025in}
-{\small\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
-\end{align*}}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-	We have that
-	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
-\end{proposition}
-This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
-
-%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
-%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
-%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
 \textbf{Algorithmic consequence.}

### 2020-08-20 arxiv/intro.tex
wip

--- 2020-08-11 arxiv/intro.tex
@@
 We show that a bias-variance tradeoff of multi-task learning determines the effect of information transfer and develop new concentration bounds to analyze the tradeoff.
-Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample size}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting.
-We relate each property to the bias and variance of multi-task learning and explain three negative effects with decreased task similarity,	increased source sample size, and covariate shift under increased source sample size.
+Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample ratio}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting.
+We relate each property to the bias and variance of multi-task learning and explain three negative effects with decreased task similarity,	increased sample ratio, and covariate shift under increased sample ratio.
 We validate the three effects on text classification tasks.
@@
 In this work, we study the bias and variance of multi-task learning in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
-Our key observation is that three properties of task data, including \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}, can affect whether multi-task learning outperforms single-task learning (which we refer to as \textit{positive transfer}).
+Our key observation is that three properties of task data, including \textit{task similarity}, \textit{sample ratio}, and \textit{covariate shift}, can affect whether multi-task learning outperforms single-task learning (which we refer to as \textit{positive transfer}).
 As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the improvement of multi-task learning over single-task learning for a particular task.
@@
 	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
-	\item \textbf{Sample size:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
+	\item \textbf{Sample ratio:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
 	We measure the source/target sample ratio by $\rho_1 / \rho_2$.

### 2020-08-20 arxiv/proof_examples.tex
wip

@@
-\section{Proofs for Isotropic and Covariate Shifted Settings}\label{app_iso_cov}
+\section{Proof of the Special Case}\label{app_iso_cov}
 
@@
 
-The proof of Proposition \ref{prop_var_transition} is similar to the above proof of Proposition \ref{prop_dist_transition}.
-%The details can be found in Appendix \ref{app_proof_data}.
-
-\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
-%the validation loss and the test error become
-%\begin{align*}
-%		\val(\hat{B}; w_1, w_2)
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
-%\end{align*}
-%and 
-%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
-For the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
-\begin{align*}
-	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
-	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
-\end{align*}
-with high probability for any constant $\e>0$.
-
-In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
-Since the proof is almost the same as the one for Claim \ref{lem_hat_v}, we omit the details. 
-%$$|\hat w-1|=\OO(p^{-1}).$$
-%as in \eqref{hatw_add1}. 
-%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
-Thus under \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
-\be \label{simple2}
-\begin{split}
-\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
-&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
-&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} ,
-\end{split}
-\ee
-with high probability for some small constant $\e>0$. Then we can write
-$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
-where 
-$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
-satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$; 
-$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
-satisfies \eqref{Deltabeta}; $\delta_{\vari}^{(2)}$ is defined as
-\begin{align*}	
-	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
-\end{align*}
-%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
-%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
-To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
-This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
-\be\label{Deltavar2} 
-\al_-(\rho_1) - \oo(1)  \le  \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
-where 
-$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
-Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
-
-%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
-%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
-
- Note that the condition $pd^2< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
-Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
-It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
-
-\vspace{5pt}
-
-\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2}, if the following inequality holds,
-\be\label{cond sigma1}
-\begin{split} 
-&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
-&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_+^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_+(\rho_1)  , 
-\end{split}
-\ee
-then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can solve \eqref{cond sigma1} to get
-\begin{align*}
-\sigma_1^2 < - pd^2\cdot \rho_1 \al_+(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2) \al_+^{-1}(\rho_1)\right]\cdot (1-\oo(1)).
-\end{align*}
-This proves the first claim of Proposition \ref{prop_var_transition} using $\nu\ge \al_+^2(\rho_1) +  \oo(1) $.
-
-\vspace{5pt}
-
-\noindent{\bf Negative transfer.} On the other hand, if the following inequality holds,
-\be\label{cond sigma12}
-\begin{split} 
-&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
-&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_-^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_-(\rho_1) , 
-\end{split}
-\ee
-then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
-\begin{align*}
-\sigma_1^2 > - pd^2 \cdot \rho_1 \al_-(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\al_-^{-1}(\rho_1)\right]\cdot (1+\oo(1)).
-\end{align*}
-This proves the second claim of Proposition \ref{prop_var_transition}.
-\end{proof}
-
-\subsection{Sample Size} \label{app_proof_32}
+\subsection{Sample Ratio} \label{app_proof_32}
 We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.
@@
  \end{proof}
-
-Next we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
-
-\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$x n_1$ for task 1 and $x n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
-Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(x\rho_1,x\rho_2)$.
-More precisely, we have
-	\begin{align*}
-		 a_1 = \frac{\rho_1(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,  \\
-		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}, \quad
-		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}. 
-	\end{align*}
-Then with Lemma \ref{lem_cov_shift} we can obtain that with high probability,
-	\be\label{reduceproof1}
-\begin{split}
-\te_i(\hat \beta_i^{\MTL}(x)) =  \frac{\sigma^2}{x (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\bias}, \quad i=1,2,
-\end{split}
-\ee
- where as in \eqref{Deltabeta}, the model shift biases $\delta^{(i)}_{\bias}$ satisfy that with high probability,
-\be\nonumber %\label{Deltabeta} 
-\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_{\bias}^{(i)}}/{ \Delta_{\bias}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2.\ee	
-Here $ \Delta^{(i)}_{\bias}$ are defined as 
-\be \nonumber
-\Delta^{(i)}_{\bias} := pd^2 \frac{(x\rho_i)^2\cdot x (\rho_1+\rho_2)}{[x ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,. 
-\ee
-On the other hand, by Lemma \ref{lem_minv} we have that w.h.p.,
-\be\label{reduceproof2} 
-\te_i(\hat{\beta}_i^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
-\ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain the lower bound $x^\star\ge x_l $. 
-%where
-%$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
-In fact, if $x< x_l$, then we have that
-$$ \frac{2\sigma^2}{x (\rho_1+\rho_2) - 1} > \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1}.$$
-This shows that $\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))$ is larger than $\te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL})$ even if we do not take into account the model shift biases $ \delta^{(i)}_{\bias}$.
-
-Then we try to obtain an upper bound on $x^\star$.
-In the following discussions, we only consider $x$ such that $x> x_l$.
-In particular, we have $x\rho > x_l \rho \ge \min(\rho_1,\rho_2)$, where we abbreviated $\rho:=\rho_1+\rho_2$.
-%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
-%\noindent{\bf The upper bound.} 
-From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies 
-\be\nonumber
-\begin{split}
-&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(x\rho_i)^2\cdot x\rho }{(x\rho - 1)^3}  \bigbrace{1 + \sqrt{\frac{1}{x \rho_i}}}^4 \le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{x\rho  - 1} .
-\end{split}
-\ee
-We rewrite the inequality as
-\be
-\begin{split}\label{solval1}
-  (1+\oo(1)) \cdot \frac{\Psi(\beta_1,\beta_2)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4\le \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2}{x \rho  - 1}.
-\end{split}
-\ee
-With $x\rho\ge \min(\rho_1,\rho_2)\ge 9$, we can get the simple bound
-$$\frac{1+\oo(1)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4 < 5. $$
-Inserting it into \eqref{solval1}, we can solve for the upper bound in \eqref{eq_uplowx}.
-%where we abbreviated $\rho:=\rho_1+\rho_2$. 
-\end{proof}
-\begin{remark}
-We can get better bounds if the values of $\rho_1$ and $\rho_2$ increase.
-For example, if we consider the case $\min(\rho_1,\rho_2)\ge 100$, then with some basic calculations, one can check that in this case
-$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52.$$
-Thus the following inequality implies \eqref{solval1}:
-\be\nonumber %\label{solval1add}
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right) \Psi(\beta_1,\beta_2) < \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
-\end{split}
-\ee
-%In particular, if 
-%\be\nonumber
-%\begin{split}
-%&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
-%\end{split}
-%\ee
-%that is, we have positive transfer when using all the data, then 
-from which we can solve for the following upper bound on $x^\star$:
-\begin{align*}
-x^\star &<  \frac1{\rho} \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right)\Psi(\beta_1,\beta_2)}+ \frac1\rho .
-%\\
-%& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-Similarly, we can get a better lower bound. 
-%\noindent{\bf The lower bound.} 
-From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\ge x$ if $x$ satisfies
-\be\label{solval2}
-\begin{split} 
-&(1-\oo(1)) \cdot  \frac{\Psi(\beta_1,\beta_2)}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x \rho}}}^4 \ge \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x \rho - 1} .
-\end{split}
-\ee
-%We then follow similar arguments as the above proof for the upper bound.
-Then in the case $\min(\rho_1,\rho_2)\ge 100$, with some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies 
-$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x\rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33 .$$
-Thus the following inequality implies \eqref{solval2}:
-\be\label{solval2add}
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)  > \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
-\end{split}
-\ee
-%There are two cases: if 
-%\be\nonumber
-%\begin{split}
-%&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
-%\end{split}
-%\ee
-%then we have negative transfer for all choice of $0\le \al \le 1$; otherwise, 
-from which we can solve for the following lower bound on $x^\star$:
-\begin{align*}
-x^\star &>  \frac1\rho \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)}+ \frac1\rho .
-\end{align*}
-This gives a lower bound above $x_l$.
-\end{remark}
 
@@
 %\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}
+
+\subsection{Denoising}
+
+The proof of Proposition \ref{prop_var_transition} is similar to the above proof of Proposition \ref{prop_dist_transition}.
+%The details can be found in Appendix \ref{app_proof_data}.
+
+\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
+In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}.
+%the validation loss and the test error become
+%\begin{align*}
+%		\val(\hat{B}; w_1, w_2)
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)},
+%\end{align*}
+%and
+%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$.
+For the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
+\begin{align*}
+	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
+	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
+\end{align*}
+with high probability for any constant $\e>0$.
+
+In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$.
+Since the proof is almost the same as the one for Claim \ref{lem_hat_v}, we omit the details.
+%$$|\hat w-1|=\OO(p^{-1}).$$
+%as in \eqref{hatw_add1}.
+%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}.
+Thus under \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}:
+\be \label{simple2}
+\begin{split}
+\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\
+&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
+&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} ,
+\end{split}
+\ee
+with high probability for some small constant $\e>0$. Then we can write
+$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
+where
+$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
+satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$;
+$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
+satisfies \eqref{Deltabeta}; $\delta_{\vari}^{(2)}$ is defined as
+\begin{align*}
+	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
+\end{align*}
+%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
+%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has
+To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
+\be\label{Deltavar2}
+\al_-(\rho_1) - \oo(1)  \le  \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
+where
+$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
+Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
+
+%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
+%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
+
+ Note that the condition $pd^2< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
+Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
+It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
+
+\vspace{5pt}
+
+\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2}, if the following inequality holds,
+\be\label{cond sigma1}
+\begin{split}
+&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
+&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_+^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_+(\rho_1)  ,
+\end{split}
+\ee
+then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can solve \eqref{cond sigma1} to get
+\begin{align*}
+\sigma_1^2 < - pd^2\cdot \rho_1 \al_+(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2) \al_+^{-1}(\rho_1)\right]\cdot (1-\oo(1)).
+\end{align*}
+This proves the first claim of Proposition \ref{prop_var_transition} using $\nu\ge \al_+^2(\rho_1) +  \oo(1) $.
+
+\vspace{5pt}
+
+\noindent{\bf Negative transfer.} On the other hand, if the following inequality holds,
+\be\label{cond sigma12}
+\begin{split}
+&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
+&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_-^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_-(\rho_1) ,
+\end{split}
+\ee
+then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
+\begin{align*}
+\sigma_1^2 > - pd^2 \cdot \rho_1 \al_-(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\al_-^{-1}(\rho_1)\right]\cdot (1+\oo(1)).
+\end{align*}
+This proves the second claim of Proposition \ref{prop_var_transition}.
+\end{proof}
+
+\subsection{Data Efficiency}
+
+Next we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
+
+\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
+Suppose we have reduced number of datapoints---$x n_1$ for task 1 and $x n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
+Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(x\rho_1,x\rho_2)$.
+More precisely, we have
+	\begin{align*}
+		 a_1 = \frac{\rho_1(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,\quad
+		& a_2 = \frac{\rho_2(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,  \\
+		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}, \quad
+		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}.
+	\end{align*}
+Then with Lemma \ref{lem_cov_shift} we can obtain that with high probability,
+	\be\label{reduceproof1}
+\begin{split}
+\te_i(\hat \beta_i^{\MTL}(x)) =  \frac{\sigma^2}{x (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\bias}, \quad i=1,2,
+\end{split}
+\ee
+ where as in \eqref{Deltabeta}, the model shift biases $\delta^{(i)}_{\bias}$ satisfy that with high probability,
+\be\nonumber %\label{Deltabeta}
+\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_{\bias}^{(i)}}/{ \Delta_{\bias}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2.\ee
+Here $ \Delta^{(i)}_{\bias}$ are defined as
+\be \nonumber
+\Delta^{(i)}_{\bias} := pd^2 \frac{(x\rho_i)^2\cdot x (\rho_1+\rho_2)}{[x ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,.
+\ee
+On the other hand, by Lemma \ref{lem_minv} we have that w.h.p.,
+\be\label{reduceproof2}
+\te_i(\hat{\beta}_i^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
+\ee
+Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain the lower bound $x^\star\ge x_l $.
+%where
+%$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
+In fact, if $x< x_l$, then we have that
+$$ \frac{2\sigma^2}{x (\rho_1+\rho_2) - 1} > \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1}.$$
+This shows that $\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))$ is larger than $\te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL})$ even if we do not take into account the model shift biases $ \delta^{(i)}_{\bias}$.
+
+Then we try to obtain an upper bound on $x^\star$.
+In the following discussions, we only consider $x$ such that $x> x_l$.
+In particular, we have $x\rho > x_l \rho \ge \min(\rho_1,\rho_2)$, where we abbreviated $\rho:=\rho_1+\rho_2$.
+%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+%\noindent{\bf The upper bound.}
+From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies
+\be\nonumber
+\begin{split}
+&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(x\rho_i)^2\cdot x\rho }{(x\rho - 1)^3}  \bigbrace{1 + \sqrt{\frac{1}{x \rho_i}}}^4 \le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{x\rho  - 1} .
+\end{split}
+\ee
+We rewrite the inequality as
+\be
+\begin{split}\label{solval1}
+  (1+\oo(1)) \cdot \frac{\Psi(\beta_1,\beta_2)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4\le \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2}{x \rho  - 1}.
+\end{split}
+\ee
+With $x\rho\ge \min(\rho_1,\rho_2)\ge 9$, we can get the simple bound
+$$\frac{1+\oo(1)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4 < 5. $$
+Inserting it into \eqref{solval1}, we can solve for the upper bound in \eqref{eq_uplowx}.
+%where we abbreviated $\rho:=\rho_1+\rho_2$.
+\end{proof}
+\begin{remark}
+We can get better bounds if the values of $\rho_1$ and $\rho_2$ increase.
+For example, if we consider the case $\min(\rho_1,\rho_2)\ge 100$, then with some basic calculations, one can check that in this case
+$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52.$$
+Thus the following inequality implies \eqref{solval1}:
+\be\nonumber %\label{solval1add}
+\begin{split}
+&\left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right) \Psi(\beta_1,\beta_2) < \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
+\end{split}
+\ee
+%In particular, if
+%\be\nonumber
+%\begin{split}
+%&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
+%\end{split}
+%\ee
+%that is, we have positive transfer when using all the data, then
+from which we can solve for the following upper bound on $x^\star$:
+\begin{align*}
+x^\star &<  \frac1{\rho} \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right)\Psi(\beta_1,\beta_2)}+ \frac1\rho .
+%\\
+%& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
+\end{align*}
+Similarly, we can get a better lower bound.
+%\noindent{\bf The lower bound.}
+From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\ge x$ if $x$ satisfies
+\be\label{solval2}
+\begin{split}
+&(1-\oo(1)) \cdot  \frac{\Psi(\beta_1,\beta_2)}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x \rho}}}^4 \ge \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x \rho - 1} .
+\end{split}
+\ee
+%We then follow similar arguments as the above proof for the upper bound.
+Then in the case $\min(\rho_1,\rho_2)\ge 100$, with some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies
+$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x\rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33 .$$
+Thus the following inequality implies \eqref{solval2}:
+\be\label{solval2add}
+\begin{split}
+&\left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)  > \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
+\end{split}
+\ee
+%There are two cases: if
+%\be\nonumber
+%\begin{split}
+%&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
+%\end{split}
+%\ee
+%then we have negative transfer for all choice of $0\le \al \le 1$; otherwise,
+from which we can solve for the following lower bound on $x^\star$:
+\begin{align*}
+x^\star &>  \frac1\rho \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)}+ \frac1\rho .
+\end{align*}
+This gives a lower bound above $x_l$.
+\end{remark}

### 2020-08-20 arxiv/setup.tex
wip

@@
 First, this setting captures salient properties of modern large-scale datasets, where the sample sizes are usually on the order of tens to hundreds of the number of features \cite{sur2019modern}.
-Second, as we will see soon in Section \ref{sec_main}, we can derive precise asymptotics of the generalization error that scale with properties of the task data such as sample sizes.
+Second, as we will see soon in Section \ref{sec_general}, we can derive precise asymptotics of the generalization error that scale with properties of the task data such as sample sizes.
 %The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
@@
 The width of $B$, denoted by $r$, plays an important role in regularization.
-As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
+As observed in Proposition 1 of \citet{WZR20}, if $r \ge t$, there is no regularization effect.
 Hence, we assume that $r < t$ in our study.
@@
 %Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
-In general, the objective $f(\cdot)$ is non-convex in $B$ and the $W_k$'s.
+
+\smallskip
+\noindent\textit{Remark.}
+In general, the multi-task learning objective $f(\cdot)$ is non-convex with respect to $B$ and $W_1, \dots, W_t$.
 Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
-%For our purpose, a validation set that is much larger than the number of output layer parameters $r\cdot t$ suffices (e.g. $\rho_i \cdot p^{0.5}$).
-%The size of the training set is then $\rho_i (p - p^{0.99})$.
-%The advantage of tuning the output layers on the validation set is to reduce the effect of noise from $\hat{B}$.
-%For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
-
-%The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
-%For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample prediction loss as
-
-%which can be further decomposed as the bias plus the variance of $\hat{\beta}$.
-%In order to relate the btradeoff to properties of the data, we need tight concentration bounds for the bias and variance.
-%We consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$  multiple of $p$ for every $1\le i\le t$, and $p$ is sufficiently large.
-%We focus on a setting where $\rho_t$ is small compared to $\set{\rho_i}_{i=1}^{t-1}$.
-%This setting captures the need to add more labeled data to reduce the prediction loss of the target task.
-
-%However, this result only applies to a single task.
-%Therefore, our goal is to extend this result to multiple tasks.
-
-%\textbf{Notations.}
-%When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ and write $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
-%We refer to the first task as the source task when there are only two tasks.
-%We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.
-
-%\subsection{Analyzing the Tradeoff via Random Matrix Theory}
+For our results later in Section \ref{sec_general} and \ref{sec_special}, we will identify tractable cases and provide guarantees to the above procedure.
 
@@
 Our goal is to study when the source tasks provide a positive transfer to the target task.
+More specifically, we study how varying properties of task data including task similarity, sample ratio, and covariate shift affects information transfer in multi-task learning.
 

### 2020-08-20 arxiv/transfer.tex
wip

@@
 (a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as tasks become more different.
-(b) \textit{Sample size}: we further explain a curious phenomenon where increasing the source sample size helps initially, but hurts eventually.
+(b) \textit{Sample ratio}: we further explain a curious phenomenon where increasing the sample ratio helps initially, but hurts eventually.
 (c) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
@@
 thus simplifying the result of Theorem \ref{thm_main_informal}.
-%, which is based on our main result described later in Theorem \ref{thm_model_shift}.
 
@@
 
+\paragraph{Benefits of multi-task learning.}
+We can in fact extend the result to the cases where the noise variances are different.
+In this case, we will see that MTL is particularly effective.
+%As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
+Concretely, suppose the noise variance $\sigma_1^2$ of task $1$ differs from the noise variance $\sigma_2^2$ of task $2$.
+If $\sigma_1^2$ is too large, the source task provides a negative transfer to the target.
+If $\sigma_1^2$ is small, the source task is more helpful.
+We leave the result to Proposition \ref{prop_var_transition} in Appendix \ref{app_proof_31}.
 Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$.
@@
 
-\begin{proposition}%[Labeled data de-noising]
+\begin{proposition}[Label denoising]
 \label{prop_var_transition}
@@
 
-\textbf{Algorithmic consequence.}
-We can in fact extend the result to the cases where the noise variances are different.
-In this case, we will see that MTL is particularly effective.
-%As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Concretely, suppose the noise variance $\sigma_1^2$ of task $1$ differs from the noise variance $\sigma_2^2$ of task $2$.
-If $\sigma_1^2$ is too large, the source task provides a negative transfer to the target.
-If $\sigma_1^2$ is small, the source task is more helpful.
-We leave the result to Proposition \ref{prop_var_transition} in Appendix \ref{app_proof_31}.
-Inspired by the observation, we propose a single-task based metric to help understand MTL results using STL results.
-\squishlist
-	\item For each task, we train a single-task model.
-	Let $z_s$ and $z_t$ be the prediction accuracy of each task, respectively.
-	Let $\tau\in(0, 1)$ be a fixed threshold.
-	\item If $z_s - z_t > \tau$, then we predict that there will be positive transfer when combining the two tasks using MTL.
-	If $z_s - z_t < -\tau$, then we predict negative transfer.
-\squishend
-
-\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.
-\cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
+We use our tools to explain a key result of Taskonomy by Zamir et al. \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
 %More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
@@
 
-\begin{proposition}%[Labeled data efficiency]
+\begin{proposition}[Labeling efficiency]
 \label{prop_data_efficiency}
@@
 
-\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
+\paragraph{Algorithmic consequence.}
+
+\noindent\textit{Detecting negative transfer.}
+Inspired by the observation, we propose a single-task based metric to help understand MTL results using STL results.
+\squishlist
+	\item For each task, we train a single-task model.
+	Let $z_s$ and $z_t$ be the prediction accuracy of each task, respectively.
+	Let $\tau\in(0, 1)$ be a fixed threshold.
+	\item If $z_s - z_t > \tau$, then we predict that there will be positive transfer when combining the two tasks using MTL.
+	If $z_s - z_t < -\tau$, then we predict negative transfer.
+\squishend
+
+\noindent\textit{Mitigating negative transfer.}
+An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
 In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
@@
 
-\textbf{Algorithmic consequence.}
+\noindent\textit{Covariance alignemnt.}
 Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.

### 2020-08-23 arxiv/transfer.tex
sec 3 wip

@@
 
-As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL})$ into a bias term and a variance term as follows (derived in Appendix \ref{app_proof_sec3}).
+As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
+Therefore, we consider an arbitrary local minimum $B, W_1, W_2$, in particular when $B = \hat{B}(W_1, W_2)$ satisfies the local optimality condition.
+We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
+Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$ as follows
+\begin{align}
+	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
+	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
+			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
+\end{align}
+See Section \ref{sec_proof_general} for its derivation.
+Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
+equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
+%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
+Comparing the above to single-task learning, that is,
+\begin{align}
+	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
+\end{align}
+we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
+%As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL})$ into a bias term and a variance term as follows .
 %Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
 %We can  the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
-{\small\begin{align}
-	\te(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
-	+&~ \sigma^2 \bigbrace{\bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} - \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}}. \label{eq_te_var}
-\end{align}}%
-In the above, $\hat{v} = W_1 / W_2$ where $W_1, W_2$ are obtained from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
-The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
-
-Equation \eqref{eq_te_model_shift} corresponds to the bias of $\hat{\beta}_t^{\MTL}$.
+%{\small\begin{align}
+%	\te(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
+%	+&~ \sigma^2 \bigbrace{\bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} - \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}}. \label{eq_te_var}
+%\end{align}}%
+%In the above, $\hat{v} = W_1 / W_2$ where $W_1, W_2$ are obtained from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
+%The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
 Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
-Equation \eqref{eq_te_var} corresponds to the variance of $\hat{\beta}_t^{\MTL}$ minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
 Intuitively, the more \textit{samples} we have, the smaller the variance is.

### 2020-08-24 arxiv/setup.tex
sec 3 wip

@@
 %Without loss of generality, let the $t$-th task be the target task.
+
+We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.
+First, for every entry of $z_i$, we assume that its fourth moment exists \todo{check}, that is, there exists a constant $C > 0$ such that
+\begin{equation}\label{assmAhigh}
+	\ex{z_{i,j}^4} \le C,\ 1\le j \le p.
+\end{equation}
+Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
+This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
 

### 2020-08-24 arxiv/transfer.tex
sec 3 wip

@@
 %The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
-Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
-Intuitively, the more \textit{samples} we have, the smaller the variance is.
-Meanwhile, \textit{covariate shift} also affects how small the variance can be.
+In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
+Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
+%Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
+%Intuitively, the more \textit{samples} we have, the smaller the variance is.
+%Meanwhile, \textit{covariate shift} also affects how small the variance can be.
 
@@
 
-We now state our main result for two tasks with both covariate and model shift.
+Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
+
+%We now state our main result for two tasks with both covariate and model shift.
 It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
@@
 
-\begin{theorem}[Two tasks]\label{thm_main_informal}
+\begin{theorem}[Two-task case]\label{thm_main_informal}
 	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(\Sigma_1^{1/2}\Sigma_2^{-1/2})^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
- 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{\hat{v}, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
+	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
+ 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{W_1/W_2, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
 	\squishlist
@@
 %During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
-
+%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
+%
+%
+%
 %The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
@@
 
+\iffalse
 Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
@@
 
-\iffalse
 {\color{red}\begin{align*}
@@
 	}
-\fi
 
@@
 which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
+\fi
 
@@
 
+\paragraph{Proof overview.}
 We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.

### 2020-08-25 arxiv/transfer.tex
edit

@@
 \begin{theorem}[Two-task case]\label{thm_main_informal}
-	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(\Sigma_1^{1/2}\Sigma_2^{-1/2})^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
+	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
 	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on $\set{W_1/W_2, \Sigma_1, \Sigma_2, \rho_1, \rho_2, \beta_1, \beta_2}$ such that
-	\squishlist
-		\item If $\Delta_{\bias} - \Delta_{\vari} < -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Delta_{\bias} - \Delta_{\vari} > \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
+ 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $\rho_1, \rho_2$, and covariate shift matrix $M$ such that
+	\begin{enumerate}
+		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have
+			\[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}).  \]
+		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have
+			\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
+	\end{enumerate}
 \end{theorem}
 
+We make several remarks about Theorem \ref{thm_main_informal}.
+First, the result shows that provided with a large amount of source task data,
 Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.

### 2020-08-25 arxiv/transfer.tex
wip

@@
 Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
+We introduce a key quantity $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
 
@@
 	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $\rho_1, \rho_2$, and covariate shift matrix $M$ such that
+ 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
 	\begin{enumerate}
 		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have
-			\[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}).  \]
+			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
 		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have
-			\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
+			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
 	\end{enumerate}
@@
 
-\paragraph{Proof overview.}
+\paragraph{Key ingredients.}
 We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
 The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
+Let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
 %which deals with the inverse of the sum of two random matrices, which
@@
 
-\begin{lemma}[Variance bound]\label{lem_cov_shift}
+\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
 	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
-Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
-We have that for any constant $\e>0$,
+	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
+	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
+	In the setting of Theorem \ref{thm_main_informal}, let $\Sigma$ be any $p\times p$ fixed and deterministic matrix.
+	We have that %for any constant $\e>0$,
 	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(\hat v^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (\hat v^2 a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} + o(1)%\bigo{\|\| p^{-1/2+\epsilon}}
 	\end{align}
@@
 	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat v^2 \lambda_i^2 a_1}{\hat v^2 \lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
 \label{eq_a12extra}
@@
 As a remark, the concentration error $\bigo{\|A\| p^{-1/2+\epsilon}}$ of our result is nearly optimal.
+The next lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
+When the entries of $X_2$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
+\begin{corollary}[e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
+	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
+	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}A} + o(1). \ee
+\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
+Note that Lemma \ref{lem_cov_shift} extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
+Note that if we set $n_1=0$ and $n_2=n$, then $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution to \eqref{eq_a12extra}, and one can see that \eqref{lem_cov_shift_eq} reduces to \eqref{XXA}.
+
 For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task model distance in addition to sample size and covariate shift holds (cf.
@@
 
-\begin{lemma}[Bias bound]\label{lem_cov_derivative}
-In the setting of Lemma \ref{lem_cov_shift}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
+\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
+In the setting of Theorem \ref{thm_main_informal}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
 \begin{equation}\label{lem_cov_derv_eq}
@@
 
-\textbf{Proof overview.}
+\medskip
+\noindent\textbf{Proof overview.}
 %We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
@@
 %We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$ for $t=2$.
-The next lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-When the entries of $X_2$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
-\begin{lemma}\label{lem_minv}
-Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
-	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_2 - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
-with high probability.
-\end{lemma}
-Note that Lemma \ref{lem_cov_shift} extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
-Note that if we set $n_1=0$ and $n_2=n$, then $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution to \eqref{eq_a12extra}, and one can see that \eqref{lem_cov_shift_eq} reduces to \eqref{XXA}.
 

### 2020-08-26 arxiv/setup.tex
wip
sec 3 wip

@@
 random vector with  mean zero and unit variance.
+Recall that $\Sigma_k$ is the population covariance matrix task $k$'s feature vectors.
+Let $\Sigma_k = U_k D_k U_k^{\top}$ denote the singular value decomposition of $\Sigma_k$.
+We denote $\Sigma_k = U_k D_k^{1/2}$ as the square root of $\Sigma_k$.
 The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$ that does not grow with feature dimension $p$.
@@
 \begin{equation}\label{assmAhigh}
-	\ex{z_{i,j}^4} \le C,\ 1\le j \le p.
+	\ex{\abs{z_{i,j}}^4} \le C,\ 1\le j \le p.
 \end{equation}
@@
 For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
 %\subsection{Bias and Variance}

### 2020-08-26 arxiv/transfer.tex
sec 3 wip

@@
 \begin{theorem}[Two-task case]\label{thm_main_informal}
-	For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
+	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
+	For the setting of two tasks, let $C$ be a fixed constant and let $\delta = \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) }$.
 	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
@@
 	\begin{enumerate}
-		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -\delta$, then w.h.p. over the randomness of $X_1, X_2$, we have
+		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
 			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
-		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \delta$, then w.h.p. over the randomness of $X_1, X_2$, we have
+		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
 			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
@@
 \end{theorem}
-
+In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
 We make several remarks about Theorem \ref{thm_main_informal}.
-First, the result shows that provided with a large amount of source task data,
-Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
-For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
+First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
+This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
+%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
+%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
 %determined by the covariate shift matrix and the model shift.
 %The bounds get tighter and tighter as $\rho_1$ increases.
-While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
+Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
+Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
+%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
 
@@
 \paragraph{Key ingredients.}
-We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
-Let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
+We introduce two key lemmas that show tight asymptotic convergence rate of the bias equation \eqref{eq_bias_2task} and the variance equation  as sample sizes increase to infinity.
+%The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
+For the covariate shift matrix $M$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be its singular values in descending order.
 %which deals with the inverse of the sum of two random matrices, which
@@
 	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
-	In the setting of Theorem \ref{thm_main_informal}, let $\Sigma$ be any $p\times p$ fixed and deterministic matrix.
-	We have that %for any constant $\e>0$,
+	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
+	In the setting of Theorem \ref{thm_main_informal},
+	with high probability over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
 	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} + o(1)%\bigo{\|\| p^{-1/2+\epsilon}}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} + o(\norm{A}), %\bigo{\|\| p^{-1/2+\epsilon}}
 	\end{align}
-with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
+	where $(a_1, a_2)$ is the solution of the following deterministic equations:
 	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
 \label{eq_a12extra}
@@
 
-Lemma \ref{lem_cov_shift} allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $\bigo{\|A\| p^{-1/2+\epsilon}}$ of our result is nearly optimal.
-The next lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-When the entries of $X_2$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.
+Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
+To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
+%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
+As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
+Recall from Section \ref{sec_setup} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
+
+Lemma \ref{lem_cov_shift} also implies the asymptotic limit of the prediction loss of single-task learning.
+%The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
+In particular, by setting $X_1 = 0$, we obtain the following corollary, which is a well-known result in random matrix theory
 \begin{corollary}[e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
 	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}A} + o(1). \ee
+	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}A} + o(\norm{A}). \ee
 \end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
-Note that Lemma \ref{lem_cov_shift} extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
-Note that if we set $n_1=0$ and $n_2=n$, then $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution to \eqref{eq_a12extra}, and one can see that \eqref{lem_cov_shift_eq} reduces to \eqref{XXA}.
+To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that \eqref{lem_cov_shift_eq} reduces to \eqref{XXA}.
+We briefly describe the history behind the above well-known result.
+When the entries of $X_2$ are multivariate Gaussian, this result recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+Here we have stated a result from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp concentration error bound.
+One can see that our result extends Lemma \ref{lem_minv} from a single sample covariance matrix to the sum of two independent sample covariance matrices.
 
-For the bias term of equation \eqref{eq_te_model_shift}, a similar result that scales with task model distance in addition to sample size and covariate shift holds (cf.
+Interestingly, the asymptotic limit of the variance only depends on the sample sizes and the covariate shift matrix.
+Next, we derive the asymptotic limit of the bias equation \eqref{eq_bias_2task}, which depends on the scaled model distance in addition to sample size and covariate shift.
+%(cf.
 Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).

### 2020-08-26 arxiv/transfer.tex
reorganize

@@
 	In the setting of Theorem \ref{thm_main_informal},
-	with high probability over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
+	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
 	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds

### 2020-08-26 arxiv/transfer.tex
wip

@@
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} + o(\norm{A}), %\bigo{\|\| p^{-1/2+\epsilon}}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
 	\end{align}
@@
 As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
-Recall from Section \ref{sec_setup} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
 Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
@@
 %The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-In particular, by setting $X_1 = 0$, we obtain the following corollary, which is a well-known result in random matrix theory
-\begin{corollary}[e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
+In particular, by setting $X_1 = 0$, we obtain the following corollary, which is a well-known result in random matrix theory.
+\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
 	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
@@
 \end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
-To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that \eqref{lem_cov_shift_eq} reduces to \eqref{XXA}.
+To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.
 We briefly describe the history behind the above well-known result.
@@
 Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
+We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
+That is, assuming that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
+We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
 
 \begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-In the setting of Theorem \ref{thm_main_informal}, let $\beta \in \R^p$ be any vector that is independent of $X_1$ and $X_2$. We have that for any constant $\e>0$,
+In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
+With high probability, we have that
 \begin{equation}\label{lem_cov_derv_eq}
 \begin{split}
-&(n_1+n_2)^2\bignorm{\Sigma_2^{1/2} (\hat v^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2 \\
-&= \beta^{\top} \Sigma_2^{-1/2}  \frac{(1 + a_3)\id + \hat v^2a_4 {M}^{\top}{M}}{( \hat v^2a_1 {M}^{\top}{M}+a_2)^2} \Sigma_2^{-1/2} \beta +\OO(p^{-1/2+\e}\|\beta\|^2),
+\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} w}^2
+= w^{\top} \Sigma_2^{-1/2}  \frac{a_4 {M}^{\top}{M} + (1 + a_3)\id}{(a_1 {M}^{\top}{M}+a_2\id)^2} \Sigma_2^{-1/2} w + o(\|w\|^2),
 \end{split}
 \end{equation}
-with high probability, where $a_{3}$ and $a_4$ satisfy the following system of linear equations:
+where $a_{3}$ and $a_4$ satisfy the following system of linear equations:
 \begin{gather}\label{eq_a34extra}
-		\left(\rho_2  a_2^{-2}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
-		= b_0, \quad \left(\rho_1 a_1^{-2} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .
+		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
+		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .
 %		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
@@
 Here $b_0$, $b_1$ and $b_2$ are defined as
-$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{ \hat v^{2k}\lambda_i^{2k}}{ ( a_2 + \hat v^2\lambda_i^2 a_1)^2  },\quad k=0,1,2.$$
+$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad  \text{for } k=0,1,2.$$
 \end{lemma}
+To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
+The approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
 

### 2020-08-26 arxiv/transfer.tex
sec 3.1 finish

@@
 Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
+\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
+\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
 
@@
 %We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
-The proofs of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} are based on the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$.
-Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate.
-In particular, when $z=0$, $\tr[\Sigma_2^{-1/2}A\Sigma_2^{-1/2}R_\infty(0)]$ gives the limit in \eqref{lem_cov_shift_eq}.
-On the other hand, we can write 
-$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\beta}^2= \beta^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} \beta.$$ 
-Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}. The details can be found in Appendix \ref{sec_maintools}. 
+We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+We use the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+
+For the variance asymptotic limit, we study the resolvent
+	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
+In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
+	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
+
+For the bias asymptotic limit, we show in \todo{where?} that
+$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
+Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
+
 %The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}.
-We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.
 
 %We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$ for $t=2$.
-
-Combining the above three lemmas, we can provide a sharp analysis of the bias-variance tradeoff of the multi-task estimator.
 

### 2020-08-27 arxiv/transfer.tex
wip

@@
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-\begin{theorem}[Many tasks]\label{thm_many_tasks}
+\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
 %Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
@@
 	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	For the setting of $t$ tasks where $X_i = X$, for all $1\le i\le t$,
+	For the setting of multiple tasks where $X_i = X$, for all $1\le i\le t$,
 	let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$ denote the linear model parameters.
@@
 	Let $v_i$ denote the $i$-th row vector of $U_r$.
-	There exists a value $\delta = \oo \left( \|B^\star\|^2 + \sigma^2\right)$ such that
-	\squishlist
-		\item  If	$\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
+	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$ such that
+	\begin{itemize}
+		\item If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
+		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
+		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
+over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
+		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
+	\end{itemize}
 \end{theorem}

### 2020-08-27 arxiv/proof_main.tex
wip
sec 3 wip
sec 7.2

@@
-\section{Proof of Main Results}
+\section{Proof of the General Case}\label{sec_proof_general}
 
-\subsection{Two Tasks}\label{app_proof_main_thm}
-
-%We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-The second lemma extends Lemma \ref{lem_minv} for a single sample covariance matrix to the sum of two independent sample covariance matrices.
-It is the main random matrix theoretical input of this paper.
-%%which deals with the inverse of the sum of two random matrices, which
-%%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-%
-%\begin{lemma}[Variance bound: Lemma \ref{lem_cov_shift_informal} restated]\label{lem_cov_shift}
-%	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-%	Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-%	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
-Let $A$ be any $p\times p$ matrix that is independent of $X_1$ and $X_2$.
-We have that for any constant $\e>0$,
-%	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-%	\begin{align}\label{lem_cov_shift_eq}
-%		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}A} = \frac{1}{\rho_1+\rho_2}\frac1p\bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} A} +\bigo{\|A\| p^{-1/2+\epsilon}}
-%	\end{align}
-%with high probability, where $(a_1, a_2)$ is the solution to the following deterministic equations:
-%	\begin{align}
-%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12extra}
-%	\end{align}
-%\end{lemma}
-%
-%Finally, the last lemma describes the asymptotic limit of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which will be needed when we estimate the first term on the right-hand side of \eqref{eq_te_mtl_2task}.
-
-%We will give the proof of this lemma in Section \ref{sec_maintools}.
-
-%\subsection{Proof for Two Tasks with General Covariates}\label{app_proof_main}
-
-%To illustrate the idea, we observe that by using Lemma \ref{lem_minv}, we have that
-%\[ \te(\hat{\beta}_t^{\STL}) = \frac{\sigma^2}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
-%We shall also derive the limit of $\te(\hat{\beta}_t^{\MTL})$.
-%\todo{write a brief technical overview}
+\subsection{Two-task Case}\label{app_proof_main_thm}
 
@@
 During the proof we shall also give explicit expressions for $\Delta_{\bias}$ and $\Delta_{\vari}$, which might be of interest to some readers.
-%We shall consider the case where the entries of $\e_1$ and $\e_2$ have the same variance $\sigma_1^2=\sigma_2^2=\sigma^2$.
-%Moreover, we shall denote $\beta_1$ and $\beta_2$ by $\beta_1$ and $\beta_2$, standing for ``source task" and ``target task", respectively. 
-%First, we introduce several quantities that will be used in our statement, and they are also related to the quantities in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-Given the optimal ratio $\hat v$,
-%%let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix, and ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ be the eigenvalues of $\hat{M}^{\top}\hat{M}$.
-Define
-%let $(\hat a_1, \hat a_2)$ be the solution to the following system of deterministic equations,
-%	\be
-%		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat v^2 \lambda_i^2 \hat a_1}{ \hat v^2 \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
-%		 \ee
-%		 After obtaining $(\hat a_1,\hat a_2)$, we can solve the following linear equations to get $(\hat a_3,\hat a_4)$:
-%\begin{gather}
-%		\left(\rho_2 \hat a_2^{-2}- \hat b_0\right)\cdot \hat  a_3 - \hat b_1 \cdot \hat a_4
-%		=\hat b_0, \quad \left(\rho_1\hat a_1^{-2} - \hat b_2  \right)\cdot \hat a_4 - \hat b_1 \cdot \hat a_3 =\hat b_1 .\label{eq_a3} 
-%%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-%	\end{gather}
-%where we denoted
-%$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat v^{2k} \lambda_i^{2k}}{ (\hat a_2 +\hat v^2 \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
 With $a_i$, $i=1,2,3,4$, given in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, 
@@
 
-\subsection{Multiple Tasks}\label{app_proof_many_tasks}
+\subsection{Proof of the Multiple-task Case}\label{app_proof_many_tasks}
 
@@
 %For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
+%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
 
 \begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-In this setting, we need to study the following loss function:
+	We first introduce several notations.
+	Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
+	Let $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ denote the projection matrix to $X$.
+
+	Recall that all tasks have the same covariates in this setting.
+	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
 	\begin{align}
-	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2,\label{eq_mtl_same_cov}
+		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
 	\end{align}
-for $W_1, W_2, \dots, W_t \in \R^r$. Then it is not hard to derive a closed form solution for $B$ as
+	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
+	Using the local optimality condition over $B$, that is $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
 	\begin{align*}
 		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
-		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1},
+		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
 	\end{align*}
-	where $\cal W \in\real^{r\times t}$ is a matrix defined as $\cal W=[W_1, W_2, \dots, W_t]$.
+	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obatin
+	\begin{align}
+		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW)^{-1} W_j - Y_i}^2.
+\label{eq_mtl_output_layer}
+	\end{align}
+	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.
+	In order to derive the minimizer, our proof involves two steps.
+	First, we consider the expectation of $g(\cW)$ over $\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t$, and $X$.
+	We show that the minimizer of $\ex{g(\cW)}$ has a simple closed form solution similar to principal component analysis.
+	Second, we show that the concentration error between $g(\cW)$ and $\ex{g(\cW)}$ is small provided with $n$ samples.
+	Intuitively, this is because $\cW$ only has $r \times t$ parameters, which is much smaller than $n$ by our assumption.
+	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
-\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
+	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
 
+	\medskip
+	\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
+	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
+	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
+	\begin{align*}
+			\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
+		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \\
+		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_j}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} {\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \\
+		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \\
+		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) 	\end{align*}
+	The first equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$.
+	The second equation uses the same fact and in addition uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$.
+	We further take expectation over $X$ and obtain the following:
+	\begin{align*}
+		\ex{g(\cW)} = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 (n\cdot t - p \cdot r).
+	\end{align*}
+	%\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
+\iffalse
 {\color{red}
@@
 }
+\fi
+%Here $\val(\cal W)$ is defined as
+%it remains to consider minimizing the validation loss
+%	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari} ,$$
+%where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
+%	\begin{align*}
+%		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
+%	\end{align*}
+%	and the variance term $\delta_{\vari} $ can be calculated as
+%	\begin{align*}
+%		\delta_{\vari} := \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+%	\end{align*}
+	One can see that the above equation provides a bias-variance decomposition of $\ex{g(\cW)}$.
+	The first part measures the bias of multi-task learning compared to single-task learning for all tasks.
+	The second part measures the variance of multi-task learning and scales with $\sigma^2$.
+	In order to minimize $\ex{g(\cW)}$, it suffices to minimize the bias equation over $\cal W$, since the variance equation does not depend on $\cal W$.
+	%We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{t\times t}$, whose $(i,j)$-th entry is given by $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
+	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
+	%Now we can write $\delta_{\bias}(\cal W)$ succinctly as
+	%\begin{align*}
+	%	\delta_{\bias}(Q) \equiv \delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  %\bigbrace{Q -\id}}^2 .
+	%\end{align*}
+	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to $B^{\star} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
 
-Here $\val(\cal W)$ is defined as
-%it remains to consider minimizing the validation loss
-	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari} ,$$
-where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
-	\begin{align*}
-		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
-	\end{align*}
-	and the variance term $\delta_{\vari} $ can be calculated as
-	\begin{align*}
-		\delta_{\vari} := \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-	\end{align*}
-It suffices to minimize $\delta_{\bias}(\cal W)$ over $\cal W$, since both $t \sigma^2$ and $\delta_{\vari}$ do not depend on $\cal W$.
-
-We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{t\times t}$, whose $(i,j)$-th entry is given by $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
-	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-	Now we can write $\delta_{\bias}(\cal W)$ succinctly as
-	\begin{align*}
-		\delta_{\bias}(Q) \equiv \delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  \bigbrace{Q -\id}}^2 .
-	\end{align*}
-	From this equation we can solve the minimizer explicitly as $Q_0=U_{r}U_r^{\top}$.
-On the other hand, let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
-We claim that $\hat Q$ satisfies
+	\medskip
+	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
+	On the other hand, let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $. We claim that $\hat Q$ satisfies
 	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
@@
 
+	\medskip
+	\noindent\textbf{Putting both steps together.}
 	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that with high probability,

### 2020-08-27 arxiv/transfer.tex

@@
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
 	\end{align}
-	where $(a_1, a_2)$ is the solution of the following deterministic equations:
+	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
 	\begin{align}
@@
 \end{equation}
-where $a_{3}$ and $a_4$ satisfy the following system of linear equations:
+where $a_{3}$ and $a_4$ are the solutions of the following two equations:
 \begin{gather}\label{eq_a34extra}
@@
 	\end{gather}
-Here $b_0$, $b_1$ and $b_2$ are defined as
-$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}}{ ( a_2 + \lambda_i^2 a_1)^2  },\quad  \text{for } k=0,1,2.$$
+In the above equation, the definition of $b_0$, $b_1$ and $b_2$ is
+$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}}{ (\lambda_i^2 a_1 + a_2)^2  },\quad  \text{for } k=0,1,2.$$
 \end{lemma}

### 2020-08-28 arxiv/proof_main.tex
sec proof wip
edit

@@
 	\begin{align}
-		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW)^{-1} W_j - Y_i}^2.
+		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2.
 \label{eq_mtl_output_layer}
@@
 	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
+	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
+	\begin{align*}
+		Z_0 &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+		Z_1 &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j}, \\
+		Z_2 &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2.
+	\end{align*}
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
@@
 	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
-	\begin{align*}
+	\begin{align}
 		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \\
-		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_j}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} {\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \\
-		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \\
-		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) 	\end{align*}
+		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
+		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
+		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
+		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
+			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
+	\end{align}
 	The first equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$.
@@
 	%\end{align*}
-	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to $B^{\star} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
+	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to ${B^{\star}}^{\top} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
 
@@
 	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
-	On the other hand, let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $. We claim that $\hat Q$ satisfies
+	We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
+	\begin{align}
+		g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
+	\end{align}
+	Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.
+
+	For equation \eqref{approxvalid_1}, we observe that the summands of $g(\cW)$ w.r.t. $\varepsilon_1, \dots, \varepsilon_t$ belong to either of the following three types:
+	\begin{enumerate}
+		\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i$, for any $i = 1,\dots, t$ and a fixed $A\in\real^{n\times n}$ that is independent of $\varepsilon_i$;
+		\item[(ii)] $\varepsilon_i^{\top} A \varepsilon_j$, for any $i \neq j$ and a fixed $A$ that is independent of both $\varepsilon_i$ and $\varepsilon_j$;
+		\item[(iii)] $\varepsilon_i^{\top} A$, for any $i = 1,\dots, t$ and a fixed $A\in\real^n$ that is independent of $\varepsilon_i$.
+	\end{enumerate}
+	For all three types, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
+	\begin{enumerate}
+		\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i = \sigma^2 (1 + \OO(p^{-1/2 + c})) \normFro{A}^2$;
+		\item[(ii)] $\abs{}$
+		\item[(iii)]
+	\end{enumerate}
+
+	We use the fact that our random vectors have i.i.d. entries.
+%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+	Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
+$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
+Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration result,  to get that for any constant $\e>0$,
+\begin{align*}
+\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
+&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+\end{align*}
+with high probability. Thus we obtain that
+$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
+ again the concentration result, Lemma \ref{largedeviation}, we get that
+$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+with high probability.
+%-----old-------
+%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+%\begin{align}
+%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
+%\end{align}
+%\nc
+%------------------
+Thus we conclude the proof.
+
+	\medskip
+	\noindent\textbf{Dealing with the empirical minimizer.}
+	Let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $. We claim that $\hat Q$ satisfies
 	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee

### 2020-08-28 arxiv/transfer.tex
edit

@@
 
-\iffalse
+%\iffalse
 Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
@@
 
-\begin{claim}
-	In the setting described above, we have that
-	\be\label{approxvalid}
-		g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
-	\ee
-\end{claim}
-\begin{proof}
-	We use the fact that our random vectors have i.i.d. entries.
-%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-	Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
-$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
-Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d.
-centered entries, we can use the concentration result, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
-\begin{align*}
-\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
-&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
-\end{align*}
-with high probability. Thus we obtain that
-$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
-where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
- again the concentration result, Lemma \ref{largedeviation}, we get that
-$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
-with high probability.
-%-----old-------
-%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-%\begin{align}
-%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
-%\end{align}
-%\nc
-%------------------
-Thus we conclude the proof.
-\end{proof}
-
 Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
@@
 which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
-\fi
+%\fi
 

### 2020-08-28 arxiv/proof_main.tex
edits

--- 2020-08-27 arxiv/proof_main.tex
@@
 	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
+	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
+	\begin{align*}
+		Z_0 &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+		Z_1 &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
+				&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
+		Z_2 &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
+				&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
+	\end{align*}
+	For the second equation of $Z_1$, we use the fact that $\sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}$.
+	For the second equation of $Z_2$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$.
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
@@
 	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
-	\begin{align*}
-			\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \\
-		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_j}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} {\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \\
-		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \\
-		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) 	\end{align*}
-	The first equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$.
-	The second equation uses the same fact and in addition uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$.
-	We further take expectation over $X$ and obtain the following:
+	\begin{align}
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - Z_0
+		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{Z_2 \mid X}
+%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+		= \sigma^2(n\cdot t - p\cdot r) \nonumber
+	\end{align}
+%	\begin{align}
+%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
+%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
+%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
+%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
+%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
+%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
+%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
+%	\end{align}
+	The first equation uses the same fact the expectation of $Z_1$ over the random noise is zero.
+	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$.
+	We further take expectation over $X$ for $Z_0$ and obtain the following:
 	\begin{align*}
@@
 	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
-	On the other hand, let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $. We claim that $\hat Q$ satisfies
+	Next, we show that the concentration errors of $Z_0, Z_1, Z_2$ are all lower order terms compared to $\ex{g(\cW)}$ and scale with $1/\sqrt{p}$.
+	For $Z_1$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
+	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
+	where the second part follows by using Cauchy-Shwartz inequality.
+	For $Z_0$ and $Z_2$, \todo{add the spectral argument}
+	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
+	%\begin{align}
+	%	g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
+	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
+	%\end{align}
+	%Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.
+
+	%For equation \eqref{approxvalid_1}, we observe that the summands of $g(\cW)$ w.r.t. $\varepsilon_1, \dots, \varepsilon_t$ belong to either of the following three types:
+	%\begin{enumerate}
+	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i$, for any $i = 1,\dots, t$ and a fixed $A\in\real^{n\times n}$ that is independent of $\varepsilon_i$;
+	%	\item[(ii)] $\varepsilon_i^{\top} A \varepsilon_j$, for any $i \neq j$ and a fixed $A$ that is independent of both $\varepsilon_i$ and $\varepsilon_j$;
+	%	\item[(iii)] $\varepsilon_i^{\top} A$, for any $i = 1,\dots, t$ and a fixed $A\in\real^n$ that is independent of $\varepsilon_i$.
+	%\end{enumerate}
+	%For all three types, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
+	%\begin{enumerate}
+	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i = \sigma^2 (1 + \OO(p^{-1/2 + c})) \normFro{A}^2$;
+	%	\item[(ii)] $\abs{}$
+	%	\item[(iii)]
+	%\end{enumerate}
+
+	%We use the fact that our random vectors have i.i.d. entries.
+%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+	%Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + %\wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite %\eqref{eq_mtl_2tasktilde} as
+%$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat %B w_i-\beta_i.$$
+	%Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration result,  to get that for any constant $\e>0$,
+	%\begin{align*}
+		%\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  %- \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
+%&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+	%$\end{align*}
+	%with high probability. Thus we obtain that
+	%$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+%where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
+	% again the concentration result, Lemma \ref{largedeviation}, we get that
+	%$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+%with high probability.
+%-----old-------
+%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+%\begin{align}
+%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
+%\end{align}
+%\nc
+%------------------
+%Thus we conclude the proof.
+
+	\medskip
+	\noindent\textbf{Dealing with the empirical minimizer.}
+	Let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $. We claim that $\hat Q$ satisfies
 	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee

### 2020-08-28 arxiv/proof_main.tex
wip

@@
 
-\subsection{Two-task Case}\label{app_proof_main_thm}
+\subsection{Proof of the Two-task Case}\label{app_proof_main_thm}
 
-In this subsection, we give the proof Theorem \ref{thm_main_informal}.
+In this subsection, we provide the proof of Theorem \ref{thm_main_informal} using Lemma  \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
+First, we provide the steps for the bias-variance decomposition.
+Using the local optimality condition of $B$, we obtain that
+\begin{align*}
+	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
+	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
+	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+\end{align*}
+Recall that $\hat{\beta}_2^{\MTL} = \hat{B}(W_1, W_2) W_2$, and one can verify that equation \eqref{eq_bias_2task} and \eqref{eq_var_2task} hold.
+
 During the proof we shall also give explicit expressions for $\Delta_{\bias}$ and $\Delta_{\vari}$, which might be of interest to some readers.

### 2020-08-28 arxiv/transfer.tex
wip

@@
 \end{align}
-See Section \ref{sec_proof_general} for its derivation.
+See Section \ref{app_proof_main_thm} for its derivation.
 Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
@@
 
-%The proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} is a main focus of Section \ref{sec_maintools}.
-
-%We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$ for $t=2$.
-
 \subsection{Multiple-task Case}\label{sec_multiple}
 
-A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
+%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
 Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
-Our main technical contribution is to extend this result to two tasks.
-We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
+%Our main technical contribution is to extend this result to two tasks.
+%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
 
-Next, we describe our result for more than two tasks with same features, i.e. $X_i = X$ for any $i$.
+Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$ for all $i = 1, \dots, t$.
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+Similar to the two-task case, we consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
+We extend the bias-variance decomposition from the two-task case to the multiple-task case.
+More precisely, we observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
+\begin{align}
+	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
+	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
+	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}}
+\end{align}
+
 \begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}

### 2020-08-28 arxiv/proof_main.tex
update

@@
 
-%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
-Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
-The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
-
-%In this section we consider the setting with $k$ many that have the same covariates.
-%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
-
-\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-	We first introduce several notations.
-	Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
-	Let $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ denote the projection matrix to $X$.
-
+	First, we provide the steps for showing equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
 	Recall that all tasks have the same covariates in this setting.
@@
 	\end{align}
+
+%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
+Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
+The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+
+%In this section we consider the setting with $k$ many that have the same covariates.
+%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
+
+\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
+	We first introduce several notations.
+	Let $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ denote the projection matrix to $X$.
+
 	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.

### 2020-08-28 arxiv/proof_main.tex
add

--- 2020-08-28 arxiv/proof_main.tex
@@
 	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
+	\be\nonumber
+	g(\cal W)= g_0 + 2g_1 + g_2, 
+	\ee
+	where
 	\begin{align*}
-		Z_0 &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-		Z_1 &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
-				&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-		Z_2 &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
-				&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
+		g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+		g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
+				%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
+		g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
 					\end{align*}
-	For the second equation of $Z_1$, we use the fact that $\sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}$.
-	For the second equation of $Z_2$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$.
+
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
@@
 	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
-	\begin{align}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - Z_0
-		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{Z_2 \mid X}
+	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
+	\begin{align*}
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W) 
+		+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
+		&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
 %		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-		= \sigma^2(n\cdot t - p\cdot r) \nonumber
-	\end{align}
+		&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
+	\end{align*}
 %	\begin{align}
@@
 %	\end{align}
-	The first equation uses the same fact the expectation of $Z_1$ over the random noise is zero.
-	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$.
+	where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
+	the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.
+
 	We further take expectation over $X$ for $Z_0$ and obtain the following:
@@
 	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
-	Next, we show that the concentration errors of $Z_0, Z_1, Z_2$ are all lower order terms compared to $\ex{g(\cW)}$ and scale with $1/\sqrt{p}$.
-	For $Z_1$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
-	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
-	where the second part follows by using Cauchy-Shwartz inequality.
-	For $Z_0$ and $Z_2$, \todo{add the spectral argument}
+	Next, we show that the concentration errors of $g_0, g_1, g_2$ are all lower order terms compared to $\ex{g(\cW)}$.
+	For $g_1$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we can obtain the following estimates: for $1\le i , j \le t,$
+	$$ |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|,$$
+	and
+	\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
+	&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
+	\end{align*}
+	with high probability for any constant $\e>0$. Inserting the above estimates into $g_1$, we get that
+	\begin{align*} 
+	 g_1(\cal W)    &\lesssim p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \\
+	&\le  p^\e \sigma \sum_{j=1}^t \|  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)\| \cdot \|Z\| \\
+	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \|  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)\| \\
+	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 p^{1/2+\e} ,
+	\end{align*}
+	with high probability for any constant $\e>0$.
+Here in the second step we used $X=Z\Sigma^{1/2}$, in the third step we used the bound \eqref{eq_isometric} to bound the operator norm $\|Z\|$, and in the last step we used the simple AM-GM inequality.
+
+For $g_2$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we can obtain the following estimates: for $1\le i \ne j \le t,$
+\begin{align*}
+& |\|\e_j\|^2 - n\sigma^2|=| \langle \e_j ,\e_j\rangle - \E\langle \e_j ,\e_j\rangle | \le \sigma^2 p^{1/2+\e},\\
+& |\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
+ &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
+ &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
+ &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
+\end{align*}
+with high probability for any constant $\e>0$. Inserting the above estimates into $g_1$, we get that
+$$\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}$$
+with high probability for any constant $\e>0$.
+
+	Finally, for $g_0$ we write it as
+	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
+	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}. Hence by law of large numbers, we have 
+	$$\frac{\left\|Z v_j \right\|^2 }{ n \|v_j\|^2}=  1+\oo(1) \quad \text{with probability} \ 1-\oo(1), $$
+	which implies that 
+	$$g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1))$$
+	with probability $1-\oo(1)$.
+
+	Combining all the above estimates, we obtain that for any constant $\e>0$,
+	\begin{align*} 
+	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e})\\
+	&=\ex{g(\cW)} \cdot (1+\oo(1)) 
+	\end{align*}
+	with probability $1-\oo(1)$.
+
+%	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
+%	where the second part follows by using Cauchy-Shwartz inequality.
+
 	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.

### 2020-08-28 arxiv/setup.tex
reorganize

@@
 Let
-	\[ Y_k = X_k \beta_k + \varepsilon_k, \text{ for all } 1\le i \le t \] denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d. random vector with mean zero and variance $\sigma^2$.
+	\[ Y_k = X_k \beta_k + \varepsilon_k, \text{ for all } 1\le k \le t \] denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d. random vector with mean zero and variance $\sigma^2$.
 
@@
 We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.
-First, for every entry of $z_i$, we assume that its fourth moment exists \todo{check}, that is, there exists a constant $C > 0$ such that
+First, for every entry of $z_i$, we assume that its $(4+\e)$-th moment exists, that is, there exist constants $\e, C > 0$ such that
 \begin{equation}\label{assmAhigh}
-	\ex{\abs{z_{i,j}}^4} \le C,\ 1\le j \le p.
+	\ex{\abs{z_{i,j}}^{4+\e}} \le C,\ 1\le j \le p.
 \end{equation}
@@
 This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
+Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check}, the $l$-th moment of the noise entries exists:
+\begin{align*}
+	\ex{\abs{\varepsilon_{k, j}}^l \le C}, \text{ for all } j = 1, \dots, n_k.
+\end{align*}
 

### 2020-08-28 arxiv/transfer.tex

@@
 
-%\iffalse
+\iffalse
 Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
@@
 which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
-%\fi
+\fi
 
@@
 
-Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$ for all $i = 1, \dots, t$.
+Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$ and $n_i = n$ for all $i = 1, \dots, t$.
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
@@
 We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-More precisely, we observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
+Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
+We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
 \begin{align}
@@
 	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}}
+	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
 \end{align}
+One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
+Compared to the prediction loss of single-task learning (cf.
+equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
+On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
+
+Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
 

### 2020-08-28 arxiv/proof_main.tex
update

--- 2020-08-28 arxiv/proof_main.tex
@@
 	\end{align*}
-	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obatin
+	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} as follows
+	\begin{align*}
+		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \\
+		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \\
+		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
+		+ \exarg{\varepsilon_1, \dots, \varepsilon_t}
+	\end{align*}
+
+	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obtain
 	\begin{align}

### 2020-08-30 arxiv/proof_main.tex
wip

--- 2020-08-28 arxiv/proof_main.tex
@@
 	\end{align*}
-	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obatin
+	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} as follows
+	\begin{align*}
+		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \\
+		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \\
+		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
+		+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{x}
+	\end{align*}
+
+	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obtain
 	\begin{align}
@@
 	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
-	\be\nonumber
-	g(\cal W)= g_0 + 2g_1 + g_2, 
-	\ee
-	where
 	\begin{align*}
-		g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-		g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
-				%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-		g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
+		g_0(\cW) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+		g_1(\cW) &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
+		&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
+		g_2(\cW) &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
+		&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
 	\end{align*}
-
+	For the second equation of $g_1(\cW)$, we use the fact that
+		\[ \sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}. \]
+	For the second equation of $g_2(\cW)$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id_{r\times r}$ and rearrange the terms.
 	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
@@
 	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
-	\begin{align*}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W) 
-		+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
-		&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
+	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
+	\begin{align}
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - g_0(\cW)
+		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cW) \mid X}
 		%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-		&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
-	\end{align*}
+		= \sigma^2(n\cdot t - p\cdot r) \nonumber
+	\end{align}
 	%	\begin{align}
@@
 	%	\end{align}
-	where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
-	the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.
-
-	We further take expectation over $X$ for $Z_0$ and obtain the following:
+	The first equation uses the same fact the expectation of $g_1(\cW)$ over the random noise is zero.
+	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$, and
+		\[ \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}
+			= \id_{r\times r} = r. \]
+	%\be\nonumber
+	%g(\cal W)= g_0 + 2g_1 + g_2,
+	%\ee
+	%where
+	%\begin{align*}
+	%	g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+	%	g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
+	%			%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
+	%	g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
+	%				\end{align*}
+	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
+	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
+	%\medskip
+	%\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
+	%We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
+	%First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
+	%\begin{align*}
+	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W)
+	%	+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
+	%	&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
+%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+	%	&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
+	%\end{align*}
+%	\begin{align}
+%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
+%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
+%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
+%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
+%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
+%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
+%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
+%	\end{align}
+	%where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
+	%the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.
+	We further take expectation over $X$ for $g_0(\cW)$ and obtain the following:
 	\begin{align*}

### 2020-08-30 arxiv/proof_main.tex
wip

@@
 	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
-	Next, we show that the concentration errors of $g_0, g_1, g_2$ are all lower order terms compared to $\ex{g(\cW)}$.
-	For $g_1$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we can obtain the following estimates: for $1\le i , j \le t,$
-	$$ |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|,$$
-	and
-	\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
-	&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
+	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
+
+	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
+	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
+	%and
+	%\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
+	%&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
+	%\end{align*}
+	Applying the above estimates into $g_1(\cW)$, we get that
+	\begin{align}
+	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
+	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
+	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
+	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
+	\end{align}
+	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
+	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
+	In the last step, we use the AM-GM inequality.
+
+	Second, for $g_2(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for any $1\le i, j \le t$, the following holds with high probability:
+	\begin{align*}
+		\bigabs{\norm{\varepsilon_j}^2 - \ex{\norm{\varepsilon_j}^2}} &\le \sigma^2 p^{1/2+\e},\\
+		%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
+		\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
+		&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
+  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
+  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
+  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
 	\end{align*}
-	with high probability for any constant $\e>0$. Inserting the above estimates into $g_1$, we get that
-	\begin{align*} 
-	 g_1(\cal W)    &\lesssim p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \\
-	&\le  p^\e \sigma \sum_{j=1}^t \|  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)\| \cdot \|Z\| \\
-	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \|  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)\| \\
-	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 p^{1/2+\e} ,
-	\end{align*}
-	with high probability for any constant $\e>0$.
-Here in the second step we used $X=Z\Sigma^{1/2}$, in the third step we used the bound \eqref{eq_isometric} to bound the operator norm $\|Z\|$, and in the last step we used the simple AM-GM inequality.
+	Combining the above two inequalities together, we get that with high probability
+	\begin{align}
+		\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_est_g2}
+	\end{align}
 
-For $g_2$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we can obtain the following estimates: for $1\le i \ne j \le t,$
-\begin{align*}
-& |\|\e_j\|^2 - n\sigma^2|=| \langle \e_j ,\e_j\rangle - \E\langle \e_j ,\e_j\rangle | \le \sigma^2 p^{1/2+\e},\\
-& |\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
- &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
- &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
- &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
-\end{align*}
-with high probability for any constant $\e>0$. Inserting the above estimates into $g_1$, we get that
-$$\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}$$
-with high probability for any constant $\e>0$.
+	Finally, for $g_0(\cW)$, denote by $v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right)$, for any $j = 1,\dots,t$, we have that $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
+%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
+	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}.
+	Hence by law of large numbers, we have that with high probability
+	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1+\oo(1))$,
+	which implies that
+	\begin{align}
+		g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)). \label{eq_est_g0}
+	\end{align}
 
-	Finally, for $g_0$ we write it as
-	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
-	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}. Hence by law of large numbers, we have 
-	$$\frac{\left\|Z v_j \right\|^2 }{ n \|v_j\|^2}=  1+\oo(1) \quad \text{with probability} \ 1-\oo(1), $$
-	which implies that 
-	$$g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1))$$
-	with probability $1-\oo(1)$.
-
-	Combining all the above estimates, we obtain that for any constant $\e>0$,
+	Combining equation \eqref{eq_est_g1}, \eqref{eq_est_g2}, and \eqref{eq_est_g0}, we obtain that with high probability
 	\begin{align*}
 	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e})\\
-	&=\ex{g(\cW)} \cdot (1+\oo(1)) 
+	&=\ex{g(\cW)} \cdot (1+\oo(1)).
 	\end{align*}
-	with probability $1-\oo(1)$.
 

### 2020-08-30 arxiv/proof_main.tex
update

@@
 	Combining equation \eqref{eq_est_g1}, \eqref{eq_est_g2}, and \eqref{eq_est_g0}, we obtain that with high probability
-	\begin{align*}
-	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e})\\
-	&=\ex{g(\cW)} \cdot (1+\oo(1)).
-	\end{align*}
+	\begin{align}
+	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
+	&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
+	\end{align}
 
@@
 	\noindent\textbf{Dealing with the empirical minimizer.}
-	Let $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $. We claim that $\hat Q$ satisfies
-	\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
-	In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
-	$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
-	where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
+	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
+	We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
+	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
+	Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
+	\begin{align*}
+		g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
+		&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
+	\end{align*}
+	On the other hand, by equation \eqref{eq_est_g} and triangle inequality, we have that
+	\begin{align*}
+		g(U_r) - g(\hat{\cW}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{\cW})}) + \bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
+		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
+		&\le o(n) \cdot \sigma_{\max}({B^{\star}}^{\top} \Sigma B^{\star}) + O(\sigma^2 p^{1/2 +\e}).
+	\end{align*}
+	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish as $p$ grows.
+	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
+	%In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
+	%$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
+	%where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
 

### 2020-08-31 arxiv/proof_main.tex
update

@@
 
-	First, we provide the steps for showing equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
+	First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
 	Recall that all tasks have the same covariates in this setting.
@@
 	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
-	Using the local optimality condition over $B$, that is $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
+	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
 	\begin{align*}
@@
 	\end{align*}
-	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} as follows
+	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} by a decomposition of the expected prediction loss over the random noise condition on $X$ as follows
 	\begin{align*}
@@
 		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
-		+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{x}
+		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \\
+		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
+		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
 	\end{align*}
+	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+	The last step uses the fact that $\sum_{i=1}^t W_i W_i^{\top} = \cW \cW^{\top}$.
+	One can see that the first part of the last equation is the bias and the second part is the variance.
+	Hence the proof is complete.
 
-	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obtain
+	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we also obtain the objective $g(\cW)$.
 	\begin{align}
@@
 	\end{align}
+	Now we are ready to prove Theorem \ref{thm_many_tasks}.
+	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.
 
@@
 \begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-	We first introduce several notations.
-	Let $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ denote the projection matrix to $X$.
-
 	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.

### 2020-08-31 arxiv/proof_main.tex
sec 7.2

@@
 	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} by a decomposition of the expected prediction loss over the random noise condition on $X$ as follows
-	\begin{align*}
-		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \\
-		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \\
+	\begin{align}
+		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \nonumber \\
+		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \nonumber \\
 		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
-		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \\
+		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \nonumber \\
 		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
-		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-	\end{align*}
+		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}. \label{eq_ex_pred}
+	\end{align}
 	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
@@
 	\end{align*}
-	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish as $p$ grows.
+	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish to $o(1)$ as $p$ grows.
 	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
@@
 	\medskip
-	\noindent\textbf{Putting both steps together.}
-	In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$. Inserting it into the definition of the test loss, we get that with high probability,
-	\begin{align*}
-		\te(\hat{\beta}_t^{\MTL}) &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
-		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\|B^\star\|^2\right) + \sigma^2\norm{v_t}^2 \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1))\\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \|B^\star\|^2 + \sigma^2\right),
-	\end{align*}
- where we used Lemma \ref{lem_minv} in the last step. On the other hand, by Lemma \ref{lem_minv} we have
-	$$\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
-Combining the above two estimates, we conclude the proof.
+	\noindent\textbf{Putting all parts together.}
+	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
+	Now we are ready to finish the proof.
+	Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
+	\begin{align}
+		L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
+	\end{align}
+	Using equation \eqref{eq_ex_pred}, we have that
+	\begin{align}
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
+		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
+	\end{align}
+	In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
+	\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
+\]
+  In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
+	Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
 \end{proof}

### 2020-08-31 arxiv/transfer.tex
sec 3 finish

@@
 
-Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$ and $n_i = n$ for all $i = 1, \dots, t$.
+Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
 This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
@@
 Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
+Before stating the result, we define the following notations.
+Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
+Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
+\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
+For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
 
@@
 	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	For the setting of multiple tasks where $X_i = X$, for all $1\le i\le t$,
-	let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}]$ and $U_r\in\real^{t\times r}$ denote the linear model parameters.
-	Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$.
+	Consider the multiple-task case where all tasks have the same covariates.
 	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-	Let $v_i$ denote the $i$-th row vector of $U_r$.
-	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$ such that
+	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
+	Then, the following is true:
 	\begin{itemize}
-		\item If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
+		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
 		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
-		\item If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
+		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
 over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
@@
 \end{theorem}
-Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff beyond two tasks.
-Specifically, $(1 - \norm{v_t}^2)\sigma^2/(\rho - 1)$ shows the amount of reduced variance and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ shows the bias of the multi-task estimator.
-The proof of \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
+As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
+The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
 

### 2020-08-31 arxiv/transfer.tex
wip sec 4

@@
 %We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
+%We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
+The results in Section \ref{sec_general} provide conditions for when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
+Next, we relate the general conditions to specific properties of task data.
+In particular, we consider an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
 We show theoretical implications for understanding the performance of multi-task learning.
@@
 We introduce the following notations.
-{\small\begin{align*}
+{\begin{align*}
 	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
@@
 	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
-	\squishlist
-		\item If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$, $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
+	\begin{itemize}
+		\item \textbf{Positive transfer:} If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
+			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}). \]
+		\item \textbf{Negative transfer:} If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
+			$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
+	\end{itemize}
 	Here {\small$\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$}.
@@
 Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
-We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
+%We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+%We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
+%There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
 %We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
@@
 The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
-A key part of the analysis shows that $\hat{v}\approx 1$ in the isotropic model,
-thus simplifying the result of Theorem \ref{thm_main_informal}.
+A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
+thus simplifying the general condition in Theorem \ref{thm_main_informal}.
 
@@
 	Then we have that
-	\squishlist
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
-$\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
-		\item If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1.5) - \nu}$, then w.h.p.
-$\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
-	\squishend
+	\begin{itemize}
+		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
+$$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
+		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
+$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
+	\end{itemize}
 \end{proposition}
 Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
-We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-There are several unexplained observations near $y = 0$ caused by $\nu$.
+%We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+%There are several unexplained observations near $y = 0$ caused by $\nu$.
 The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
@@
 
-\textit{Example.}
-	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
-	Assume that $\Psi(\beta_1, \beta_2) = 0$ for simplicity.
-	We compare two cases: (i) when $M = \id$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+\noindent\textit{Example.}
+	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$ similar to Theorem \ref{thm_main_informal}.
+	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$ and $\Psi(\beta_1, \beta_2) = 0$.
+	We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
 	Hence, $\lambda$ measures the severity of the covariate shift.
-	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
+%	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
 	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
@@
 Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-\vspace{-0.025in}
-{\small\begin{align*}
+{\begin{align*}
 		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
@@
 \begin{proposition}[Covariate shift]\label{prop_covariate}
-	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
+	For the two-task case, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
 	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
 	We have that
-	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
+		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
 \end{proposition}
-This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
+Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
+The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
 %Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.

### 2020-08-31 arxiv/transfer.tex
wip

@@
 Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
-Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
-%We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-%We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-%There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
+%Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
+We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
+There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
 %We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
@@
 %We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-%The proof of Proposition \ref{prop_dist_transition} involves two parts.
-%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
+The proof of Proposition \ref{prop_dist_transition} involves two parts.
+First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
+Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
 The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
@@
 Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-%Figure \ref{fig_size} provides a simulation result for such a setting.
-%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+Figure \ref{fig_size} provides a simulation result for such a setting.
+We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
 
@@
 Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
-%We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-%There are several unexplained observations near $y = 0$ caused by $\nu$.
+We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+There are several unexplained observations near $y = 0$ caused by $\nu$.
 The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
@@
 	Hence, $\lambda$ measures the severity of the covariate shift.
-%	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
+	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
 	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
@@
 \begin{proposition}[Covariate shift]\label{prop_covariate}
-	For the two-task case, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
+	For the setting of the example above, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
 	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
@@
 %On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
-\subsection{Extension to Multiple Tasks}
 

### 2020-09-01 arxiv/intro.tex
edit

@@
 
-\begin{figure}[!t]
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-		\vspace{-0.075in}
-		\caption{Task similarity}
-		\label{fig_model_shift}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
-		\vspace{-0.075in}
-		\caption{Sample size}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
-		\vspace{-0.075in}
-		\caption{Covariate shift}
-		\label{fig_covariate}
-	\end{subfigure}
-	\vspace{-0.05in}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
-	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
-	The $y$-axis measures the loss of STL minus MTL.}
-	\label{fig_model_shift_phasetrans}
-	\vspace{-0.2in}
-\end{figure}
-
 %Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which

### 2020-09-01 arxiv/transfer.tex
edit

@@
 
-\section{Special Case: Isotropic Covariance and Covariate Shift}\label{sec_special}
+\section{Interpreting Bias and Variance in an Isotropic Covariance Setting}\label{sec_special}
 
@@
 We show theoretical implications for understanding the performance of multi-task learning.
-(a) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as tasks become more different.
-(b) \textit{Sample ratio}: we further explain a curious phenomenon where increasing the sample ratio helps initially, but hurts eventually.
-(c) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
-Finally, we extend our results from two tasks to many tasks with the same features.
+(i) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as tasks become more different.
+(ii) \textit{Sample ratio}: we further explain a curious phenomenon where increasing the sample ratio helps initially, but hurts eventually.
+(iii) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
+%Finally, we provide a extend our results from two tasks to many tasks with the same features.
 %We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
@@
 
-\subsection{Task Similarity}\label{sec_similarity}
-
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the following simplified setting, where we can perform explicit calculations.
-We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
-
-\textit{The isotropic model.}
+\smallskip
+\noindent\textbf{The isotropic covariance setting.}
 	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
@@
 	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
-The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in \eqref{choiceofpara}.
+%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
 %	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
@@
 \end{align*}}
+
+\subsection{Task Similarity}\label{sec_similarity}
+
+It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
+We formalize this connection in the following simplified setting, where we can perform explicit calculations.
+We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+In particular, the bias of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases.
+Therefore, while the variance of MTL still reduces compared to STL, if the bias increases more than the amount of variance reduced, we will observe negative transfer.
 
@@
 thus simplifying the general condition in Theorem \ref{thm_main_informal}.
+
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
+		\caption{Task similarity}
+		\label{fig_model_shift}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
+		\caption{Sample size}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
+		\caption{Covariate shift}
+		\label{fig_covariate}
+	\end{subfigure}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
+	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
+	The $y$-axis measures the loss of STL minus MTL.}
+	\label{fig_model_shift_phasetrans}
+\end{figure}
 

### 2020-09-01 arxiv/transfer.tex
wip

@@
 We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
-That is, assuming that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
+That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
 We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
+Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
 
-\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
-With high probability, we have that
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} w}^2
-= w^{\top} \Sigma_2^{-1/2}  \frac{a_4 {M}^{\top}{M} + (1 + a_3)\id}{(a_1 {M}^{\top}{M}+a_2\id)^2} \Sigma_2^{-1/2} w + o(\|w\|^2),
-\end{split}
-\end{equation}
+\begin{definition}[Limiting bias]
+Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
+	\[ \Pi \define  M \frac{a_4 M^{\top}M + (1 + a_3) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
 where $a_{3}$ and $a_4$ are the solutions of the following two equations:
@@
 	\end{gather}
-In the above equation, the definition of $b_0$, $b_1$ and $b_2$ is
-$$ b_k:= \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}}{ (\lambda_i^2 a_1 + a_2)^2  },\quad  \text{for } k=0,1,2.$$
+In the above equation, we denote $b_0$, $b_1$ and $b_2$ as
+$ b_k:= \frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
+\end{definition}
+
+Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
+\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
+In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
+With high probability, we have that
+\begin{equation}\label{lem_cov_derv_eq}
+\begin{split}
+\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
+= w^{\top} \Pi w + o(\|w\|^2),
+\end{split}
+\end{equation}
+
 \end{lemma}
 To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
-The approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
+Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
+As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
+Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
+In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
 

### 2020-09-01 arxiv/intro.tex

@@
 Yet, there is little rigorous understanding of when multi-task learning outperforms single-task learning.
-In this work, we provide a rigorous study to anwer the question in the high-dimensional linear regression setting.
-We show that a bias-variance tradeoff of multi-task learning determines the effect of information transfer and develop new concentration bounds to analyze the tradeoff.
+In this work, we provide a rigorous study to answer the question in the high-dimensional linear regression setting.
+We show that a bias-variance tradeoff of multi-task learning determines the effect of information transfer, and develop new concentration bounds to analyze the tradeoff.
 Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample ratio}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting.
@@
 Inspired by our theory, we show two practical connections of interest.
-	First, single-task results can help understand when multi-task learning gives gains.
+	First, single-task results can help to understand when multi-task learning gives gains.
 Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.
@@
 %By combining multiple information sources, it is possible to share all the information in the same model.
-In many settings, multiple source tasks are available to help predict a particular target task.
+In many settings, multiple source tasks are available to help with predicting a particular target task.
 \todo{clarify setting is different from traditional MTL}
@@
 As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the improvement of multi-task learning over single-task learning for a particular task.
-We observe that the effect of transfer can be positive or negative as we vary each property.
+We observe that the effect of transfer can be either positive or negative as we vary each property.
 These phenomena cannot be explained using previous techniques \cite{WZR20}.
 The high-dimensional linear regression setting allows us to measure the three properties precisely.
-We define each property for the case of two tasks and our definition applies to general settings.
+Here we define each property for the case of two tasks, while our definition applies to general settings.
 We refer to the first task as the source task and the second as the target task.
@@
 %	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
-	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrix $\Sigma_1,\Sigma_2\in\real^{p\times p}$, respectively.
+	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrices $\Sigma_1\in\real^{p\times p}$ and $\Sigma_2\in\real^{p\times p}$, respectively.
 	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
@@
 Our study also leads to several algorithmic consequences with practical interest.
-First, we show that single-task learning results can help predict positive or negative transfer for multi-task learning.
+First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
 We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
@@
 \paragraph{Organizations.}
-The appendix is organized as follows.
+\todo{revise} The appendix is organized as follows.
 In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.

### 2020-09-02 arxiv/transfer.tex
wip

@@
 	\end{gather}
-In the above equation, we denote $b_0$, $b_1$ and $b_2$ as
-$ b_k:= \frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
+In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
 \end{definition}
@@
 %We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
-The results in Section \ref{sec_general} provide conditions for when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
-Next, we relate the general conditions to specific properties of task data.
-In particular, we consider an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
-We show theoretical implications for understanding the performance of multi-task learning.
-(i) \textit{Task similarity}: we explain the phenomenon of negative transfer precisely as tasks become more different.
-(ii) \textit{Sample ratio}: we further explain a curious phenomenon where increasing the sample ratio helps initially, but hurts eventually.
-(iii) \textit{Covariate shift}: as the source sample size increases, we show that the covariate shift worsens the performance of the multi-task estimator.
+The results in Section \ref{sec_general} show when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
+In particular, the general conditions depend on specific properties of task data such as the covariate shift matrix.
+However, the conditions given by the limiting bias and variance of multi-task learning can be difficult to interpret.
+The goal of this section is to address this issue.
+We interpret the limiting bias and variance equations in an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
+We show that three properties of task data affect the performance of multi-task learning as follows.
+(i) \textit{Task similarity}: We explain the phenomenon of negative transfer precisely as tasks become more different.
+(ii) \textit{Sample ratio}: We further explain a curious phenomenon where increasing the sample ratio between the source and target task helps initially, but hurts eventually.
+(iii) \textit{Covariate shift}: Finally, we show that as the sample size of the source task increases, we show that the covariate shift worsens the performance of the multi-task estimator.
 %Finally, we provide a extend our results from two tasks to many tasks with the same features.
@@
 \noindent\textbf{The isotropic covariance setting.}
-	Consider two tasks with isotropic covariances $\Sigma_1 = \Sigma_2 = \id$.
-	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
+	For the two-task case, suppose that the covariates of both tasks have isotropic covariance matrices, that is, $\Sigma_1 = \Sigma_2 = \id$.
+%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
 	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	Assume that for  task two, $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
-	For the source task, $\beta_1 $ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
-	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
+	Assume that for task two, its model parameter, denoted by $\beta_2$, consist of i.i.d. entries with mean zero and variance $\kappa^2$.
+	For task one, its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
+%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+%	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
 %The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.

### 2020-09-03 arxiv/transfer.tex
update

@@
-\section{Bias-variance Decomposition for the General Case}\label{sec_general}
+\section{Illustrative Examples for Isotropic Features}\label{sec_special}
+
+%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
+%We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
+The results in Section \ref{sec_general} show when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
+In particular, the general conditions depend on specific properties of task data such as the covariate shift matrix.
+However, the conditions given by the limiting bias and variance of multi-task learning can be difficult to interpret.
+The goal of this section is to address this issue.
+We interpret the limiting bias and variance equations in an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
+We show that three properties of task data affect the performance of multi-task learning as follows.
+(i) \textit{Task similarity}: We explain the phenomenon of negative transfer precisely as tasks become more different.
+(ii) \textit{Sample ratio}: We further explain a curious phenomenon where increasing the sample ratio between the source and target task helps initially, but hurts eventually.
+(iii) \textit{Covariate shift}: Finally, we show that as the sample size of the source task increases, we show that the covariate shift worsens the performance of the multi-task estimator.
+%Finally, we provide a extend our results from two tasks to many tasks with the same features.
+%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
+%We show how negative transfer occurs by varying task similarity or sample size.
+%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
+
+\smallskip
+\noindent\textbf{The isotropic covariance setting.}
+	For the two-task case, suppose that the covariates of both tasks have isotropic covariance matrices, that is, $\Sigma_1 = \Sigma_2 = \id$.
+%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
+	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
+	Assume that for task two, its model parameter, denoted by $\beta_2$, consist of i.i.d. entries with mean zero and variance $\kappa^2$.
+	For task one, its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
+%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+%	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
+%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
+%	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
+
+%In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$ (or $d$), there is a transition from positive transfer to negative transfer in MTL.
+%We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
+%Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
+%{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
+%Our result below will provide an explanation to this phenomenon.
+%Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
+We introduce the following notations.
+{\begin{align*}
+	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
+\end{align*}}
+
+\subsection{Negative Transfer}
+It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
+We formalize this connection in the following simplified setting, where we can perform explicit calculations.
+We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+In particular, the bias of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases.
+Therefore, while the variance of MTL still reduces compared to STL, if the bias increases more than the amount of variance reduced, we will observe negative transfer.
+
+\begin{proposition}[Task model distance]\label{prop_dist_transition}
+	In the isotropic model, suppose that $\rho_1$ and $\rho_2 > 1$.
+	Then
+	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
+	\begin{itemize}
+		\item \textbf{Positive transfer:} If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
+			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}). \]
+		\item \textbf{Negative transfer:} If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
+			$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
+	\end{itemize}
+	Here {\small$\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$}.
+	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
+\end{proposition}
+
+Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
+Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
+%Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
+We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
+There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
+%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
+%Figure \ref{fig_model_shift} shows the result.
+%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
+The proof of Proposition \ref{prop_dist_transition} involves two parts.
+First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
+Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
+The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
+A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
+thus simplifying the general condition in Theorem \ref{thm_main_informal}.
+
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
+		\caption{Task similarity}
+		\label{fig_model_shift}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
+		\caption{Sample size}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
+		\caption{Covariate shift}
+		\label{fig_covariate}
+	\end{subfigure}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
+	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
+	The $y$-axis measures the loss of STL minus MTL.}
+	\label{fig_model_shift_phasetrans}
+\end{figure}
+
+%\subsection{Sample Ratio}\label{sec_data_size}
+
+In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
+%More generally, such results are still applicable when all task data are being added simultaneously.
+On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
+For such settings, we have also observed that adding more labeled data from one task does not always help.
+%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
+In the isotropic model, we consider what happens if we vary the source task sample size.
+Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
+Figure \ref{fig_size} provides a simulation result for such a setting.
+We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+
+\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
+	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+	Then we have that
+	\begin{itemize}
+		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
+$$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
+		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
+$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
+	\end{itemize}
+\end{proposition}
+Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
+We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+There are several unexplained observations near $y = 0$ caused by $\nu$.
+The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
+
+\subsection{Covariate Shift} \label{sec_covshift}
+So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+In general, the covariance matrices of the two tasks may be different such as in text classification.
+In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
+We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
+
+\noindent\textit{Example.}
+	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$ similar to Theorem \ref{thm_main_informal}.
+	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$ and $\Psi(\beta_1, \beta_2) = 0$.
+	We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+	Hence, $\lambda$ measures the severity of the covariate shift.
+	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
+	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
+
+%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
+We compare different choices of $M$ that belong to the following bounded set.
+Let $\lambda_i$ be the $i$-th singular value of $M$.
+Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
+{\begin{align*}
+		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
+\end{align*}}
+%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
+\begin{proposition}[Covariate shift]\label{prop_covariate}
+	For the setting of the example above, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
+	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
+	We have that
+		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
+\end{proposition}
+Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
+The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
+%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
+%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
+
+%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
+
+%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
+%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
+%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
+%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
+
+\subsection{Data Efficiency}
+
+observed in Taskonomy \cite{ZSSGM18}.
+
+\section{Main Results for General Features}\label{sec_general}
 
@@
 
-\iffalse
-First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.
+\paragraph{Same covariates.}
+%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
+Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
+%Our main technical contribution is to extend this result to two tasks.
+%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
+Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+Similar to the two-task case, we consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
+We extend the bias-variance decomposition from the two-task case to the multiple-task case.
+Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
+We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
+\begin{align}
+	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
+	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
+	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
+\end{align}
+One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
+Compared to the prediction loss of single-task learning (cf.
+equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
+On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
 
-\begin{assumption}[Moment assumptions]%\label{assm_secA1}
-We will consider $n\times p$ random matrices of the form $X=Z\Sigma^{1/2}$, where $\Sigma$  is a $p\times p$ deterministic positive definite symmetric matrix, and $Z=(z_{ij})$ is an $n\times p$ random matrix with real i.i.d.
-entries with mean zero and variance one.
-Note that the rows of $X$ are i.i.d.
-centered random vectors with covariance matrix $\Sigma$.
-For simplicity, we assume that all the moments of $z_{ij}$ exists, that is, for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\begin{equation}\label{assmAhigh}
-\mathbb{E} |z_{ij}|^k \le C_k ,\quad 1\le i \le n, \ \ 1\le j \le p.
-\end{equation}
- We assume that $n=\rho p$ for some fixed constant $\rho>1$.
-Without loss of generality, after a rescaling we can assume that the norm of $\Sigma$ is bounded by a constant $C>0$.
-Moreover, we assume that $\Sigma$ is well-conditioned: $\kappa(\Sigma)\le C$, where $\kappa(\cdot)$ denotes the condition number.
-\end{assumption}
-Here we have assumed \eqref{assmAhigh} solely for simplicity of representation.
-If the entries of $Z$ only have finite $a$-th moment for some $a>4$, then all the results below still hold except that we need to replace $\OO(p^{-\frac12+\e})$ with $\OO( p^{-\frac12+\frac2a +\epsilon})$ in some error bounds.
-We will not get deeper into this issue in this section, but refer the reader to Corollary \ref{main_cor} in Section \ref{sec locallaw1}.
-\fi
+Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
+Before stating the result, we define the following notations.
+Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
+Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
+\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
+For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
 
-\subsection{Two-task Case}\label{sec_two}
+\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
+	%that satisfy Assumption \ref{assm_secA2} in the appendix.
+	Consider the multiple-task case where all tasks have the same covariates.
+	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
+	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
+	Then, the following is true:
+	\begin{itemize}
+		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
+		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
+		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
+over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
+		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
+	\end{itemize}
+\end{theorem}
+Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
+As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
+The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
 
+\paragraph{Different covariates: the two-task case.}
 As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
@@
 we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-%As an example, for the setting of two tasks, we can decompose $L(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL})$ into a bias term and a variance term as follows .
-%Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
-%We can  the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
-%{\small\begin{align}
-%	\te(\hat{\beta}_t^{\MTL}) - L(\hat{\beta}_t^{\STL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
-%	+&~ \sigma^2 \bigbrace{\bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} - \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}}. \label{eq_te_var}
-%\end{align}}%
-%In the above, $\hat{v} = W_1 / W_2$ where $W_1, W_2$ are obtained from solving equation \eqref{eq_mtl_eval} (recalling that $W_1, W_2$ are scalars for two tasks).
-%The role of $\hat{v}$ is to scale the shared subspace $B$ to fit each task.
 In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
 Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-%Hence, the bias term introduces a negative effect that depends on the \textit{similarity} between $\beta_1$ and $\beta_2$.
-%Intuitively, the more \textit{samples} we have, the smaller the variance is.
-%Meanwhile, \textit{covariate shift} also affects how small the variance can be.
-
-%Then we make the following assumptions on the data models.
-%\begin{assumption}[Linear regression model]\label{assm_secA2}
-%For some fixed $t\in \N$, let $Y_i = X_i\beta_i + \varepsilon_i$, $1\le i \le t$, be independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
-Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants.
-%$\e_i\in \R^{n_i}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma_i^2$ and all moments as in \eqref{assmAhigh}.
-%\end{assumption}
 
@@
 
-\subsection{Multiple-task Case}\label{sec_multiple}
-
-%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
-%Our main technical contribution is to extend this result to two tasks.
-%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-
-Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Similar to the two-task case, we consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
-We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-\begin{align}
-	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-\end{align}
-One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-
-Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
-Before stating the result, we define the following notations.
-Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
-Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
-\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
-For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
-
-\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Consider the multiple-task case where all tasks have the same covariates.
-	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
-	Then, the following is true:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
-over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
-	\end{itemize}
-\end{theorem}
-Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
-As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
-The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
-
-\section{Interpreting Bias and Variance in an Isotropic Covariance Setting}\label{sec_special}
-
-%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-%We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
-The results in Section \ref{sec_general} show when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
-In particular, the general conditions depend on specific properties of task data such as the covariate shift matrix.
-However, the conditions given by the limiting bias and variance of multi-task learning can be difficult to interpret.
-The goal of this section is to address this issue.
-We interpret the limiting bias and variance equations in an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
-We show that three properties of task data affect the performance of multi-task learning as follows.
-(i) \textit{Task similarity}: We explain the phenomenon of negative transfer precisely as tasks become more different.
-(ii) \textit{Sample ratio}: We further explain a curious phenomenon where increasing the sample ratio between the source and target task helps initially, but hurts eventually.
-(iii) \textit{Covariate shift}: Finally, we show that as the sample size of the source task increases, we show that the covariate shift worsens the performance of the multi-task estimator.
-%Finally, we provide a extend our results from two tasks to many tasks with the same features.
-%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
-%We show how negative transfer occurs by varying task similarity or sample size.
-%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-
-\smallskip
-\noindent\textbf{The isotropic covariance setting.}
-	For the two-task case, suppose that the covariates of both tasks have isotropic covariance matrices, that is, $\Sigma_1 = \Sigma_2 = \id$.
-%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
-	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	Assume that for task two, its model parameter, denoted by $\beta_2$, consist of i.i.d. entries with mean zero and variance $\kappa^2$.
-	For task one, its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
-%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
-
-%In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$ (or $d$), there is a transition from positive transfer to negative transfer in MTL.
-%We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
-%Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
-%{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
-%Our result below will provide an explanation to this phenomenon.
-%Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
-We introduce the following notations.
-{\begin{align*}
-	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
-\end{align*}}
-
-\subsection{Task Similarity}\label{sec_similarity}
-
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the following simplified setting, where we can perform explicit calculations.
-We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
-In particular, the bias of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases.
-Therefore, while the variance of MTL still reduces compared to STL, if the bias increases more than the amount of variance reduced, we will observe negative transfer.
-
-\begin{proposition}[Task model distance]\label{prop_dist_transition}
-	In the isotropic model, suppose that $\rho_1$ and $\rho_2 > 1$.
-	Then
-	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-	Here {\small$\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$}.
-	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
-\end{proposition}
-
-Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
-Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
-%Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
-We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
-%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
-%Figure \ref{fig_model_shift} shows the result.
-%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-The proof of Proposition \ref{prop_dist_transition} involves two parts.
-First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
-A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
-thus simplifying the general condition in Theorem \ref{thm_main_informal}.
-
-\begin{figure}[!t]
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-		\caption{Task similarity}
-		\label{fig_model_shift}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
-		\caption{Sample size}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
-		\caption{Covariate shift}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
-	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
-	The $y$-axis measures the loss of STL minus MTL.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
-
-\subsection{Sample Ratio}\label{sec_data_size}
-
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
-%More generally, such results are still applicable when all task data are being added simultaneously.
-On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
-For such settings, we have also observed that adding more labeled data from one task does not always help.
-%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-In the isotropic model, we consider what happens if we vary the source task sample size.
-Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-Figure \ref{fig_size} provides a simulation result for such a setting.
-We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-
-\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
-	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-	Then we have that
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
-		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-\end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
-We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-There are several unexplained observations near $y = 0$ caused by $\nu$.
-The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-
-\subsection{Covariate Shift}\label{sec_covshift}
-
-So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-In general, the covariance matrices of the two tasks may be different such as in text classification.
-In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
-We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
-
-\noindent\textit{Example.}
-	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$ similar to Theorem \ref{thm_main_informal}.
-	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$ and $\Psi(\beta_1, \beta_2) = 0$.
-	We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	Hence, $\lambda$ measures the severity of the covariate shift.
-	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-
-%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-We compare different choices of $M$ that belong to the following bounded set.
-Let $\lambda_i$ be the $i$-th singular value of $M$.
-Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-{\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
-\end{align*}}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	For the setting of the example above, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
-	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-	We have that
-		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{proposition}
-Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
-The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
-%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
-
-%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
-%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
-%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
-\section{Theoretical Implication}
+\section{Implication for Mitigating Sample Imbalance and Covariate Shift}
 

### 2020-09-03 arxiv/transfer.tex
wip
edits

@@
-\section{Illustrative Examples for Isotropic Features}\label{sec_special}
+\section{Illustrative Examples in an Isotropic Setting}\label{sec_special}
 
@@
 %We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
-The results in Section \ref{sec_general} show when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
-In particular, the general conditions depend on specific properties of task data such as the covariate shift matrix.
-However, the conditions given by the limiting bias and variance of multi-task learning can be difficult to interpret.
-The goal of this section is to address this issue.
-We interpret the limiting bias and variance equations in an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
-We show that three properties of task data affect the performance of multi-task learning as follows.
-(i) \textit{Task similarity}: We explain the phenomenon of negative transfer precisely as tasks become more different.
-(ii) \textit{Sample ratio}: We further explain a curious phenomenon where increasing the sample ratio between the source and target task helps initially, but hurts eventually.
-(iii) \textit{Covariate shift}: Finally, we show that as the sample size of the source task increases, we show that the covariate shift worsens the performance of the multi-task estimator.
+%The results in Section \ref{sec_general} show when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
+%In particular, the general conditions depend on specific properties of task data such as the covariate shift matrix.
+%However, the conditions given by the limiting bias and variance of multi-task learning can be difficult to interpret.
+%The goal of this section is to address this issue.
+%We interpret the limiting bias and variance equations in an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
+%We show that three properties of task data affect the performance of multi-task learning as follows.
+%(i) \textit{Task similarity}: We explain the phenomenon of negative transfer precisely as tasks become more different.
+%(ii) \textit{Sample ratio}: We further explain a curious phenomenon where increasing the sample ratio between the source and target task helps initially, but hurts eventually.
+%(iii) \textit{Covariate shift}: Finally, we show that as the sample size of the source task increases, we show that the covariate shift worsens the performance of the multi-task estimator.
 %Finally, we provide a extend our results from two tasks to many tasks with the same features.
@@
 %Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
+We illustrate our main results (to be described in Section \ref{sec_general}) in a simplified setting.
+For this setting, we simulate several empirical phenomena that are well-known in hard parameter sharing approaches.
+We use our results to explain the empirical phenomena.
 
-\smallskip
-\noindent\textbf{The isotropic covariance setting.}
-	For the two-task case, suppose that the covariates of both tasks have isotropic covariance matrices, that is, $\Sigma_1 = \Sigma_2 = \id$.
+\medskip
+\noindent\textbf{Isotropic features and models.}
+	Imagine that we have two tasks and the covariates of both tasks have isotropic covariance matrices.
 %	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
 	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	Assume that for task two, its model parameter, denoted by $\beta_2$, consist of i.i.d. entries with mean zero and variance $\kappa^2$.
-	For task one, its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
+	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
+	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
+	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
+	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
+
+Using our techniques described later in Section \ref{sec_general}, we derive the limiting prediction loss of the hard parameter sharing estimator.
+Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
+
+\begin{corollary}[Derived from Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}]
+	In the isotropic setting described above, the prediction loss of the hard parameter sharing estimator for task two satisfies:
+	\[ L(\hat{\beta}_2^{\MTL}) = ?? \]
+\end{corollary}
+
 %	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.

### 2020-09-04 arxiv/transfer.tex
wip

@@
 
-\medskip
-\noindent\textbf{Isotropic features and models.}
-	Imagine that we have two tasks and the covariates of both tasks have isotropic covariance matrices.
-%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
-	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
-	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
-	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
-	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
-
-Using our techniques described later in Section \ref{sec_general}, we derive the limiting prediction loss of the hard parameter sharing estimator.
-Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
-
-\begin{corollary}[Derived from Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}]
-	In the isotropic setting described above, the prediction loss of the hard parameter sharing estimator for task two satisfies:
-	\[ L(\hat{\beta}_2^{\MTL}) = ?? \]
-\end{corollary}
-
 %	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
@@
 %Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
-We introduce the following notations.
-{\begin{align*}
-	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
-\end{align*}}
+%We introduce the following notations.
+%{\begin{align*}
+%	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
+%\end{align*}}
 
 \subsection{Negative Transfer}
+
+\noindent\textbf{Isotropic features and models.}
+	Imagine that we have two tasks and the covariates of both tasks have isotropic covariance matrices.
+%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
+	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
+	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
+	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
+	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
+	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
+
+\begin{example}[Varying model distance]
+\end{example}
+
+Using our techniques described later in Section \ref{sec_general}, we derive the limiting prediction loss of the hard parameter sharing estimator.
+Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
+
+\begin{corollary}[Derived from Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}]
+	In the isotropic setting described above, with high probability, the prediction loss of the hard parameter sharing estimator for task two satisfies:
+	\begin{align*}
+		& \bigabs{ L(\hat{\beta}_2^{\MTL}) - \frac{\sigma^2}{\rho_1 + \rho_2 - 1} - (1 + \frac{6}{\rho_1} + \frac{1}{\rho_1^2})pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} } \\
+		\le & 	\frac{4}{\sqrt{\rho_1}}(1 + \frac{1}{\rho_1})	pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} + \oo(\sigma^2 + pd^2).
+%	 \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4  +\oo(\sigma^2 + pd^2)  \le \\
+%	 \le  \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\oo(\sigma^2 + pd^2)
+	 \end{align*}
+\end{corollary}
+
 It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.

### 2020-09-08 arxiv/proof_main.tex
wip
revise

@@
 \section{Proof of the General Case}\label{sec_proof_general}
-
-\subsection{Proof of the Two-task Case}\label{app_proof_main_thm}
-
-In this subsection, we provide the proof of Theorem \ref{thm_main_informal} using Lemma  \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
-First, we provide the steps for the bias-variance decomposition.
-Using the local optimality condition of $B$, we obtain that
-\begin{align*}
-	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
-	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
-	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-\end{align*}
-Recall that $\hat{\beta}_2^{\MTL} = \hat{B}(W_1, W_2) W_2$, and one can verify that equation \eqref{eq_bias_2task} and \eqref{eq_var_2task} hold.
-
-During the proof we shall also give explicit expressions for $\Delta_{\bias}$ and $\Delta_{\vari}$, which might be of interest to some readers.
-With $a_i$, $i=1,2,3,4$, given in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, 
-we define the following matrix
-\be\label{defnpihat}\Pi \equiv \Pi(\hat v)= \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot \hat v^2{M} \frac{(1 +   a_3)\id + \hat v^2 a_4 {M}^{\top} {M}}{( \hat v^2 a_1 {M}^{\top} {M}+ a_2 )^2} {M}^{\top}.\ee
-%which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
-%$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
-Moreover, we introduce two factors that will appear often in our statements and discussions:
-$$\al_-(\rho_1):=\left(1- \rho_1^{-1/2}\right)^2,\quad \al_+(\rho_1):=\left(1 + \rho_1^{-1/2}\right)^2.$$ 
-In fact, $\al_-(\rho_1)$ and $\al_+(\rho_1)$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
-In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry.
-Finally, we introduce the error term
-\be\label{eq_deltaextra} 
- \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\hat v^2\lambda_{\min}^2(M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2.\ee
-%where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. 
-Note that this factor converges to 0 as $\rho_1$ increases. It is not hard to see that Theorem \ref{thm_main_informal} is an immediate consequence of the following lemma.
-
-%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2.$$
-%{\cor may be able to get a better bound, but the statement will be long}
-
-\begin{lemma}%[Theorem \ref{thm_main_informal} restated]
-\label{thm_model_shift}
-%For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
-Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2} with $\sigma_1^2=\sigma_2^2=\sigma^2$. Then with high probability, we have
-	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta(\hat v), \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta(\hat v), \label{lower}
-	\end{align}
-	where
-	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{( \hat v^2 a_1 M^{\top}M +  a_2\id)^{-1}} } \label{Deltavarv} \\
-		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi (\hat v)\Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
-	\end{align}
-\end{lemma}
-
-The proof of Lemma \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any constant $\e>0$, we have
-\begin{align}
-\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq {n_1^{-1}}{Z_1^T Z_1}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e}) \quad \text{w.h.p.}  \label{eq_isometric}
-\end{align}
-%with high probability. 
-In fact, $n_1^{-1}Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
-The estimate \eqref{eq_isometric} provides tight bounds on the concentration errors, and it will be formally proved in Lemma \ref{SxxSyy} below.
-
-%\begin{remark}
-The main error $\delta$ in Lemma \ref{thm_model_shift} comes from approximating $n_1^{-1}Z_1^TZ_1$ by $\id$ using \eqref{eq_isometric}; see the estimate \eqref{bounddelta-} below.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
-$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  \hat{v}^2 .$$
-In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ have been studied in the name of Fisher matrices; see e.g.
-\cite{Fmatrix}.
-However, since $\cal X$ is non-symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix literature, and the study of the singular values of $\cal X +\hat v^2$ will be even harder.
-We leave this problem to future study.
-%\end{remark}
-
-\begin{proof}[Proof of Lemma \ref{thm_model_shift}]
-%\noindent
-%To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
-%$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
-%where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
-%\begin{equation}\label{eq_12moment} %\label{assm1}
-%\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
-%\end{equation}
-%\todo{A proof outline; including the following key lemma.}
-By \eqref{eq_te_model_shift} and \eqref{eq_te_var}, we can write
-\begin{align*}
-L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL})=\delta_{\vari}(\hat v) - \delta_{\bias}(\hat v), 
-\end{align*}
-where we denote
-\begin{align*}
-\delta_{\vari}(\hat v)&=\sigma^2 \left(  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} -  \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right), 
-\end{align*}
-and
-\begin{align}\label{revise_deltabias}
- \delta_{\bias}(\hat v)&= \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2.
-\end{align}
-We introduce the notation $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for $v\in \R$. Then the proof is divided into the following four steps. 
-\begin{itemize}
-\item[(i)] We first consider $ \hat M(v)$ for a fixed $v\in \R$.
-Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
-%$$\sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}},\quad \sigma^2 \cdot \bigtr{({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2},$$
-%and the difference between them
-
-\item[(ii)] Using the approximate isometry property of $Z_1$ in \eqref{eq_isometric}, we will approximate the bias term $ \delta_{\bias}(v)$ by
-%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - {v} \beta_2)}^2$$
-%through 
-\be\label{deltabetapf}
-\wt\delta_{\bias}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_1 - {v} \beta_2)}^2.\ee
-
-\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\bias}$ term.
-
-\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M(\hat v)$ for a possibly random $\hat v$ which depends on $Y_1$ and $Y_2$.
-\end{itemize}
-
-\paragraph{Step I: Variance reduction.} Consider $\hat M(v)$ for a fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$,  
-$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
-and 
-$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{( a_1(v) \hat M^{\top}\hat M + a_2(v)\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
-with high probability, where $a_1(v)$ and $a_2(v)$ satify \eqref{eq_a12extra} with $\hat v$ replaced by $v$. The subtraction of these two terms gives 
-\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
-\ee 
-where $\Delta_{\vari}(v)$ is defined as in \eqref{Deltavarv} but with $\hat v$ replaced by $v$.
-
-\paragraph{Step II: Bounding the bias term.}
-Next we use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$. %in \eqref{deltabetapf}.  
-%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
-\begin{claim}\label{prop_model_shift}
-	In the setting of Lemma \ref{thm_model_shift},
-	we denote $K(v) := (v^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, and
-	\begin{align*}
-		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_1 - v\beta_2)}^2, \\
-		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
-		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K(v) \Sigma_2 K(v) \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
-	\end{align*}
-	Then we have w.h.p.
-	\begin{align*}
-		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}(v).
-	\end{align*}
-%	We have that
-%	\begin{align*}
-%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
-%		\le  \delta_1 - \delta_2
-%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
-%	\end{align*}
-%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
-%	\begin{align*}
-%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
-%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \beta_2)}^2.
-%	\end{align*}
-\end{claim}
-
-\begin{proof}
-	%The proof follows by applying equation \eqref{eq_isometric}.
-	%Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
-We can calculate that
-%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_1 - \hat{w}\beta_2)}^2$.
-	%We have
-	\begin{align}
-%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \hat{w}\beta_2)}^2 \nonumber \\
-		 \delta_{\bias}(v)-\wt\delta_{\bias}(v)&= {2v^2n_1}(\beta_1 - v\beta_2)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_1 - v\beta_2) \nonumber
-		\\
-		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2. \label{eq_lem_model_shift_1}
-%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
-	\end{align}
-	where we denote $\cE: = Z_1^{\top}Z_1 - {n_1}\id$. 
-  Using \eqref{eq_isometric}, we can bound  
-	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{w.h.p.}$$
-	Thus we can estimate that 
-	\begin{align*}
-	| \delta_{\bias}(v)-\wt\delta_{\bias}(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-	& \le v^2 n_1^2 \left[ \al_+^2(\rho_1) + \OO(p^{-1/2+\e}) -1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2,
-	\end{align*}
-	which concludes the proof by the definition of $\delta_{err}$.	
-%	we can bound the second term on the RHS of equation \eqref{eq_lem_model_shift_1} as
-%	\begin{align*}
-%		& \bigabs{(\beta_1 -  \beta_2)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - v\beta_2)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}}} \\
-%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2) (\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \\
-%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
-%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2 \tag{since the matrix inside is rank 1}
-%	\end{align*}
-%	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
-%	\begin{align*}
-%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2
-%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 -  \beta_2)}^2.
-%	\end{align*}
-%	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
-%	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
-%	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
-\end{proof}
-Note by \eqref{eq_isometric}, we also obtain that with high probability,
-\begin{align*}
-&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} =n_1^2 \hat M (\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^{-2}\hat M^\top \\
-&\preceq  n_1^2 \hat M \left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^{-2}\hat M^\top \\
-&\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + \left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
-&\preceq [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
-\end{align*}
-for a small enough constant $c>0$. Together with Claim \ref{prop_model_shift}, we get that with high probability,
-\be\label{bounddelta-}
-\left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le (1-c) \delta(v)
-\ee
-for some small constant $c>0$, where recall that $\delta(v)$ was defined in \eqref{eq_deltaextra}.
-
-\paragraph{Step III: The limit of $\wt\delta_{\bias}(v)$.} 
-Using Lemma \ref{lem_cov_derivative}, we obtain that with high probability,
-\begin{align*}
-\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 +  a_3(v))\id +v^2 a_4(v) {M}^{\top}{M}}{( v^2 a_1(v) {M}^{\top}{M}+a_2(v) )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
-&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi(v) \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
-\end{align*}
-where $a_3(v)$ and $a_4(v)$ satify \eqref{eq_a34extra} with $\hat v$ replaced by $v$, and $\Pi$ was defined in \eqref{defnpihat}.
-Together \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that w.h.p.,
-\be\label{dicho_varbeta}
-\begin{cases}\delta_{\vari}(v)>\delta_{\bias}(v), & \text{ if } \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \ge   \delta(v),\\
-\delta_{\vari}(v)<\delta_{\bias}(v),  & \text{ if }  \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \le -  \delta(v).\end{cases}
-\ee
-
-\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result \eqref{dicho_varbeta} to $v=\hat v$, which is random and depends on $X_1$ and $X_2$.
-We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{dicho_varbeta}
-%\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
-holds uniformly for all $v\in [-C_0, C_0]$. In fact, we first consider $v$ that belongs to a discrete set 
-$$V:=\{v_k = kp^{-1}: -(C_0p +1)\le k \le C_0p +1\}.$$
-Then using the arguments for the first three steps and a simple union bound, we get that
-\eqref{dicho_varbeta} holds simultaneously for all $v\in V$ with high probability. On the other hand, by \eqref{eq_isometric} the event
-$$\Xi_1:=\left\{ \al_-(\rho_1)/2 \preceq  \frac{Z_1^T Z_1}{n_1}  \preceq   2\al_+(\rho_1) ,\  \al_-(\rho_2)/2 \preceq  \frac{Z_2^T Z_2}{n_2}  \preceq   2\al_+(\rho_2)\right\}$$
-holds with high probability. Now it is easy to check that on $\Xi_1$, the following estimates holds simultaneously for all $v_k \le v\le v_{k+1}$:
-\begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|\lesssim p^{-1}\delta_{\vari}(v_k),\ \ |\delta_{\bias}(v) -\delta_{\bias}(v_k)|\lesssim p^{-1}\delta_{\bias}(v_k), \ \   |\delta(v)-\delta(v_k)|\lesssim p^{-1}\delta(v_k),\\
-& |\Delta_{\bias}(v) -\Delta_{\bias}(v_k)|\lesssim p^{-1}\Delta_{\bias}(v_k),\ \ |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|\lesssim p^{-1}\Delta_{\vari}(v_k).
-\end{align*}
-Then a simple application of triangle inequality gives that the event 
-$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }-C_0\le v \le C_0\}$$
-holds with high probability. On the other hand, on $\Xi_1$ it is easy to check that for any small constant $\e>0$, there exists a large enough constant $C_0>0$ depending on $\e$ such that
-\begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e\delta_{\vari}(C_0),\quad |\delta_{\bias}(v) -\delta_{\bias}(C_0)|\le \e\delta_{\bias}(C_0), \quad  |\delta(v)-\delta(C_0)|\le \e\delta(C_0),\\
-& |\Delta_{\bias}(v) -\Delta_{\bias}(C_0)|\le \e\Delta_{\bias}(C_0),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e\Delta_{\vari}(C_0),
-\end{align*}
-for all $v\ge C_0$.
-Similar estimates hold for $v\le -C_0$ if we replace $C_0$ with $-C_0$ in the above estimates.
-Together with the estimate at $\pm C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\in \R$ on the high probability event $\Xi_1\cap \Xi_2$.
-This concludes the proof of Lemma \ref{thm_model_shift}, since $\hat v$ must be one of the real values.
-\end{proof}
 
@@
 %\end{itemize}
+
+\subsection{Proof of the Two-task Case}\label{app_proof_main_thm}
+
+In this subsection, we provide the proof of Theorem \ref{thm_main_informal} using Lemma  \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
+First, we provide the steps for the bias-variance decomposition.
+Using the local optimality condition of $B$, we obtain that
+\begin{align*}
+	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
+	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
+	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+\end{align*}
+Recall that $\hat{\beta}_2^{\MTL} = \hat{B}(W_1, W_2) W_2$, and one can verify that equation \eqref{eq_bias_2task} and \eqref{eq_var_2task} hold.
+
+During the proof we shall also give explicit expressions for $\Delta_{\bias}$ and $\Delta_{\vari}$, which might be of interest to some readers.
+With $a_i$, $i=1,2,3,4$, given in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, 
+we define the following matrix
+\be\label{defnpihat}\Pi \equiv \Pi(\hat v)= \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot \hat v^2{M} \frac{(1 +   a_3)\id + \hat v^2 a_4 {M}^{\top} {M}}{( \hat v^2 a_1 {M}^{\top} {M}+ a_2 )^2} {M}^{\top}.\ee
+%which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
+%$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
+Moreover, we introduce two factors that will appear often in our statements and discussions:
+$$\al_-(\rho_1):=\left(1- \rho_1^{-1/2}\right)^2,\quad \al_+(\rho_1):=\left(1 + \rho_1^{-1/2}\right)^2.$$ 
+In fact, $\al_-(\rho_1)$ and $\al_+(\rho_1)$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
+In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry.
+Finally, we introduce the error term
+\be\label{eq_deltaextra} 
+ \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\hat v^2\lambda_{\min}^2(M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2.\ee
+%where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. 
+Note that this factor converges to 0 as $\rho_1$ increases. It is not hard to see that Theorem \ref{thm_main_informal} is an immediate consequence of the following lemma.
+
+%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2.$$
+%{\cor may be able to get a better bound, but the statement will be long}
+
+\begin{lemma}%[Theorem \ref{thm_main_informal} restated]
+\label{thm_model_shift}
+%For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
+Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2} with $\sigma_1^2=\sigma_2^2=\sigma^2$. Then with high probability, we have
+	\begin{align}
+	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta(\hat v), \label{upper}\\
+		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta(\hat v), \label{lower}
+	\end{align}
+	where
+	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
+		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{( \hat v^2 a_1 M^{\top}M +  a_2\id)^{-1}} } \label{Deltavarv} \\
+		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi (\hat v)\Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
+	\end{align}
+\end{lemma}
+
+The proof of Lemma \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any constant $\e>0$, we have
+\begin{align}
+\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq {n_1^{-1}}{Z_1^T Z_1}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e}) \quad \text{w.h.p.}  \label{eq_isometric}
+\end{align}
+%with high probability. 
+In fact, $n_1^{-1}Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
+The estimate \eqref{eq_isometric} provides tight bounds on the concentration errors, and it will be formally proved in Lemma \ref{SxxSyy} below.
+
+%\begin{remark}
+The main error $\delta$ in Lemma \ref{thm_model_shift} comes from approximating $n_1^{-1}Z_1^TZ_1$ by $\id$ using \eqref{eq_isometric}; see the estimate \eqref{bounddelta-} below.
+In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
+$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  \hat{v}^2 .$$
+In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ have been studied in the name of Fisher matrices; see e.g.
+\cite{Fmatrix}.
+However, since $\cal X$ is non-symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix literature, and the study of the singular values of $\cal X +\hat v^2$ will be even harder.
+We leave this problem to future study.
+%\end{remark}
+
+\begin{proof}[Proof of Lemma \ref{thm_model_shift}]
+%\noindent
+%To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
+%$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
+%where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
+%\begin{equation}\label{eq_12moment} %\label{assm1}
+%\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
+%\end{equation}
+%\todo{A proof outline; including the following key lemma.}
+By \eqref{eq_te_model_shift} and \eqref{eq_te_var}, we can write
+\begin{align*}
+L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL})=\delta_{\vari}(\hat v) - \delta_{\bias}(\hat v), 
+\end{align*}
+where we denote
+\begin{align*}
+\delta_{\vari}(\hat v)&=\sigma^2 \left(  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} -  \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right), 
+\end{align*}
+and
+\begin{align}\label{revise_deltabias}
+ \delta_{\bias}(\hat v)&= \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2.
+\end{align}
+We introduce the notation $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for $v\in \R$. Then the proof is divided into the following four steps. 
+\begin{itemize}
+\item[(i)] We first consider $ \hat M(v)$ for a fixed $v\in \R$.
+Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
+%$$\sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}},\quad \sigma^2 \cdot \bigtr{({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2},$$
+%and the difference between them
+
+\item[(ii)] Using the approximate isometry property of $Z_1$ in \eqref{eq_isometric}, we will approximate the bias term $ \delta_{\bias}(v)$ by
+%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - {v} \beta_2)}^2$$
+%through 
+\be\label{deltabetapf}
+\wt\delta_{\bias}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_1 - {v} \beta_2)}^2.\ee
+
+\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\bias}$ term.
+
+\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M(\hat v)$ for a possibly random $\hat v$ which depends on $Y_1$ and $Y_2$.
+\end{itemize}
+
+\paragraph{Step I: Variance reduction.} Consider $\hat M(v)$ for a fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$,  
+$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
+and 
+$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{( a_1(v) \hat M^{\top}\hat M + a_2(v)\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
+with high probability, where $a_1(v)$ and $a_2(v)$ satify \eqref{eq_a12extra} with $\hat v$ replaced by $v$. The subtraction of these two terms gives 
+\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
+\ee 
+where $\Delta_{\vari}(v)$ is defined as in \eqref{Deltavarv} but with $\hat v$ replaced by $v$.
+
+\paragraph{Step II: Bounding the bias term.}
+Next we use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$. %in \eqref{deltabetapf}.  
+%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
+\begin{claim}\label{prop_model_shift}
+	In the setting of Lemma \ref{thm_model_shift},
+	we denote $K(v) := (v^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, and
+	\begin{align*}
+		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_1 - v\beta_2)}^2, \\
+		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
+		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K(v) \Sigma_2 K(v) \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
+	\end{align*}
+	Then we have w.h.p.
+	\begin{align*}
+		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
+		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}(v).
+	\end{align*}
+%	We have that
+%	\begin{align*}
+%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
+%		\le  \delta_1 - \delta_2
+%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
+%	\end{align*}
+%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
+%	\begin{align*}
+%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
+%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \beta_2)}^2.
+%	\end{align*}
+\end{claim}
+
+\begin{proof}
+	%The proof follows by applying equation \eqref{eq_isometric}.
+	%Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
+We can calculate that
+%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_1 - \hat{w}\beta_2)}^2$.
+	%We have
+	\begin{align}
+%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \hat{w}\beta_2)}^2 \nonumber \\
+		 \delta_{\bias}(v)-\wt\delta_{\bias}(v)&= {2v^2n_1}(\beta_1 - v\beta_2)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_1 - v\beta_2) \nonumber
+		\\
+		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2. \label{eq_lem_model_shift_1}
+%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
+	\end{align}
+	where we denote $\cE: = Z_1^{\top}Z_1 - {n_1}\id$. 
+  Using \eqref{eq_isometric}, we can bound  
+	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{w.h.p.}$$
+	Thus we can estimate that 
+	\begin{align*}
+	| \delta_{\bias}(v)-\wt\delta_{\bias}(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
+	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
+	& \le v^2 n_1^2 \left[ \al_+^2(\rho_1) + \OO(p^{-1/2+\e}) -1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2,
+	\end{align*}
+	which concludes the proof by the definition of $\delta_{err}$.	
+%	we can bound the second term on the RHS of equation \eqref{eq_lem_model_shift_1} as
+%	\begin{align*}
+%		& \bigabs{(\beta_1 -  \beta_2)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - v\beta_2)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
+%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}}} \\
+%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2) (\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \\
+%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
+%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2 \tag{since the matrix inside is rank 1}
+%	\end{align*}
+%	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
+%	\begin{align*}
+%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2
+%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 -  \beta_2)}^2.
+%	\end{align*}
+%	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
+%	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
+%	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
+\end{proof}
+Note by \eqref{eq_isometric}, we also obtain that with high probability,
+\begin{align*}
+&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} =n_1^2 \hat M (\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^{-2}\hat M^\top \\
+&\preceq  n_1^2 \hat M \left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^{-2}\hat M^\top \\
+&\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + \left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
+&\preceq [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
+\end{align*}
+for a small enough constant $c>0$. Together with Claim \ref{prop_model_shift}, we get that with high probability,
+\be\label{bounddelta-}
+\left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
+		\le (1-c) \delta(v)
+\ee
+for some small constant $c>0$, where recall that $\delta(v)$ was defined in \eqref{eq_deltaextra}.
+
+\paragraph{Step III: The limit of $\wt\delta_{\bias}(v)$.} 
+Using Lemma \ref{lem_cov_derivative}, we obtain that with high probability,
+\begin{align*}
+\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 +  a_3(v))\id +v^2 a_4(v) {M}^{\top}{M}}{( v^2 a_1(v) {M}^{\top}{M}+a_2(v) )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
+&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi(v) \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
+\end{align*}
+where $a_3(v)$ and $a_4(v)$ satify \eqref{eq_a34extra} with $\hat v$ replaced by $v$, and $\Pi$ was defined in \eqref{defnpihat}.
+Together \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that w.h.p.,
+\be\label{dicho_varbeta}
+\begin{cases}\delta_{\vari}(v)>\delta_{\bias}(v), & \text{ if } \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \ge   \delta(v),\\
+\delta_{\vari}(v)<\delta_{\bias}(v),  & \text{ if }  \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \le -  \delta(v).\end{cases}
+\ee
+
+\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result \eqref{dicho_varbeta} to $v=\hat v$, which is random and depends on $X_1$ and $X_2$.
+We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{dicho_varbeta}
+%\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
+holds uniformly for all $v\in [-C_0, C_0]$. In fact, we first consider $v$ that belongs to a discrete set 
+$$V:=\{v_k = kp^{-1}: -(C_0p +1)\le k \le C_0p +1\}.$$
+Then using the arguments for the first three steps and a simple union bound, we get that
+\eqref{dicho_varbeta} holds simultaneously for all $v\in V$ with high probability. On the other hand, by \eqref{eq_isometric} the event
+$$\Xi_1:=\left\{ \al_-(\rho_1)/2 \preceq  \frac{Z_1^T Z_1}{n_1}  \preceq   2\al_+(\rho_1) ,\  \al_-(\rho_2)/2 \preceq  \frac{Z_2^T Z_2}{n_2}  \preceq   2\al_+(\rho_2)\right\}$$
+holds with high probability. Now it is easy to check that on $\Xi_1$, the following estimates holds simultaneously for all $v_k \le v\le v_{k+1}$:
+\begin{align*}
+& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|\lesssim p^{-1}\delta_{\vari}(v_k),\ \ |\delta_{\bias}(v) -\delta_{\bias}(v_k)|\lesssim p^{-1}\delta_{\bias}(v_k), \ \   |\delta(v)-\delta(v_k)|\lesssim p^{-1}\delta(v_k),\\
+& |\Delta_{\bias}(v) -\Delta_{\bias}(v_k)|\lesssim p^{-1}\Delta_{\bias}(v_k),\ \ |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|\lesssim p^{-1}\Delta_{\vari}(v_k).
+\end{align*}
+Then a simple application of triangle inequality gives that the event 
+$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }-C_0\le v \le C_0\}$$
+holds with high probability. On the other hand, on $\Xi_1$ it is easy to check that for any small constant $\e>0$, there exists a large enough constant $C_0>0$ depending on $\e$ such that
+\begin{align*}
+& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e\delta_{\vari}(C_0),\quad |\delta_{\bias}(v) -\delta_{\bias}(C_0)|\le \e\delta_{\bias}(C_0), \quad  |\delta(v)-\delta(C_0)|\le \e\delta(C_0),\\
+& |\Delta_{\bias}(v) -\Delta_{\bias}(C_0)|\le \e\Delta_{\bias}(C_0),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e\Delta_{\vari}(C_0),
+\end{align*}
+for all $v\ge C_0$.
+Similar estimates hold for $v\le -C_0$ if we replace $C_0$ with $-C_0$ in the above estimates.
+Together with the estimate at $\pm C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\in \R$ on the high probability event $\Xi_1\cap \Xi_2$.
+This concludes the proof of Lemma \ref{thm_model_shift}, since $\hat v$ must be one of the real values.
+\end{proof}
+
+Before the end of this section, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
+
+\medskip
+\noindent\textbf{An overview of the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.}
+%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
+%We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+We use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $(X_1^\top X_1+X_2^\top X_2)^{-1}$ for $X_1= Z_1\Sigma_1^{1/2}$ and $X_2= Z_2\Sigma_2^{1/2}$.
+Suppose $M=\Sig_1^{1/2} \Sig_2^{-1/2}$ has a singular value decomposition
+\be\label{eigen2}
+M= U\Lambda V^\top, \quad \Lambda=\text{diag}( \lambda_1, \ldots, \lambda_p).
+\ee
+Then using equation \eqref{eigen2}, we can write
+\be\label{eigen2extra}(X_1^\top X_1+X_2^\top X_2)^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
+We divide the proof into the following parts.
+
+\medskip
+\noindent\textbf{Defining the resolvents.} For our purpose, we introduce a convenient self-adjoint linearization trick, 
+%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein. 
+which has been proved to be useful in studying the local laws of random matrices of the Gram type \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
+We define the following $(p+n)\times (p+n)$ symmetric block matrix, which is a linear function of $Z_1$ and $Z_2$:
+%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
+%We define the $(n+N)\times (n+N)$ block matrix
+ \begin{equation}\label{linearize_block}
+    H(Z_1,Z_2): = n^{-1/2}\left( {\begin{array}{*{20}c}
+   { 0 } & \Lambda U^{\top}Z_1^\top & V^\top Z_2^\top  \\
+   {Z_1 U\Lambda  } & {0} & 0 \\
+   {Z_2V} & 0 & 0
+   \end{array}} \right).
+ \end{equation}
+For simplicity of notations, we define the index sets
+$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
+ We will consistently use the latin letters $i,j\in\sI_{0}$, greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$, and $\fa,\fb,\mathfrak c\in \cal I$.
+Correspondingly, the indices of the matrices $Z_1$ and $Z_2$ are labelled as
+ \be\label{labelZ}
+ Z_1= (z_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z_2= (z_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
+Now we define the resolvents as follows. 
+\begin{definition}[Resolvents]
+We define the resolvent (or Green's function) of $H$ as
+ \begin{equation}\label{eqn_defG}
+ G (Z_1,Z_2,z):= \left[H(Z_1,Z_2)-\left( {\begin{array}{*{20}c}
+   { z\id_{p}} & 0 & 0 \\
+   0 & { \id_{n_1}}  & 0\\
+      0 & 0  & { \id_{n_2}}\\
+\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C .
+ \end{equation}
+%It is easy to verify that the eigenvalues $\lambda_1(H)\ge \ldots \ge \lambda_{n+N}(H)$ of $H$ are related to the ones of $\mathcal Q_1$ through
+%\begin{equation}\label{Heigen}
+%\lambda_i(H)=-\lambda_{n+N-i+1}(H)=\sqrt{\lambda_i\left(\mathcal Q_2\right)}, \ \ 1\le i \le n\wedge N, \quad \text{and}\quad \lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.
+%\end{equation}
+%and
+%$$\lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.$$
+%where we used the notations $n\wedge N:=\min\{N,M\}$ and $n\vee N:=\max\{N,M\}$. 
+%\begin{definition}[Index sets]\label{def_index}
+and the resolvent of $  n^{-1}\left(\Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)$ as
+\be\label{mainG}
+\cal G(z):=\left( n^{-1}  \Lambda U^\top Z_1^\top Z_1 U\Lambda  + n^{-1}V^\top Z_2^\top Z_2V -z\right)^{-1},\quad z\in \C.
+\ee
+Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
+\be\label{defm}
+\begin{split} 
+m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
+ m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
+\end{split}
+\ee
+\end{definition}
+With Schur complement formula, we can check that
+ \begin{equation} \label{green2}
+ G (z):=  \left( {\begin{array}{*{20}c}
+   { \cal G (z)} & \cal G(z)W  \\
+   W^\top \cal G(z) & z (W^\top W - z)^{-1}
+\end{array}} \right)^{-1}, %\quad \cal G_R:=(W^\top W - z)^{-1} ,
+ \end{equation}
+ where we abbreviated $W:=n^{-1/2}(\Lambda U^\top Z_1^\top, V^\top Z_2^\top)$.
+This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
+On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
+%one can find that %(recall equation \eqref{mainG})
+%\be \label{green2}
+%\begin{split}
+%& \cal G_{L}=\left(WW^\top -z \right)^{-1} =\cal G ,\quad \cal G_{LR}=\cal G_{RL}^\top  = \cal G W , \quad \cal G_R= z\left(W^\top W - z\right)^{-1}.
+%\end{split}
+%\ee
+%, and the subindex of $\cal G_R$ means the lower-right block.
+
+%Now using Schur complement formula, we can verify that the (recall equation \eqref{def_green})
+%\begin{align} 
+%G = \left( {\begin{array}{*{20}c}
+%   { z\mathcal G_1} & \mathcal G_1 \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2}  \\
+%   {\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} \mathcal G_1} & { \mathcal G_2 }  \\
+%\end{array}} \right) = \left( {\begin{array}{*{20}c}
+%   { z\mathcal G_1} & \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2} \mathcal G_2   \\
+%   {\mathcal G_2}\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} & { \mathcal G_2 }  \\ 
+%\end{array}} \right). \label{green2}
+%\end{align}
+%where $\mathcal G_{1,2}$ are defined in (\ref{def_green}).
+
+\medskip
+\noindent\textbf{Defining the asymptotic limits of the resolvents.} 
+%\label{sec aymp_limit_G}
+%\subsection{Resolvents and limiting law}
+We now describe the asymptotic limit of $G(z)$ as $n\to \infty$.
+First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
+%\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)}, 
+the unique solution to the following system of equations
+\begin{equation}\label{selfomega}
+\begin{split}
+& \frac{r_1}{a_{1}(z)} = \frac{1}{n}\sum_{i=1}^p \frac{\lambda_i^2}{  z+\lambda_i^2 a_{1}(z) +a_{2} (z) } - 1 ,\ \  \ \frac{r_2}{a_{2}(z)} = \frac{1}{n}\sum_{i=1}^p \frac{1 }{  z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }- 1 ,
+\end{split}
+\ee
+satisfying that $\im a_{1}(z)>0$ and $\im a_{2}(z)>0$ for $z\in \C_+$ with $\im z$. 
+%Here, for simplicity of notations, we introduced the following ratios 
+%\be\label{ratios}
+% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
+%\ee
+We define the matrix limit of $G(z)$ as
+\be \label{defn_piw}
+\Pi(z) := \begin{pmatrix} -(z+a_{1}(z)\Lambda^2  +  a_{2}(z))^{-1} & 0 & 0 \\ 0 &  \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & \frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
+In particular, the matrix limit of $\cal G(z)$ is given by $-(z+a_{1}(z)\Lambda^2 + a_{2}(z))^{-1}$.
+
+\medskip
+\noindent{\bf Deriving the bias and variance asymptotics.} {\cor Notice that using equation \eqref{mainG}, we can write  equation \eqref{eigen2extra} as
+\be\label{rewrite X as R} (X_1^\top X_1+X_2^\top X_2)^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
+For the bias asymptotic limit, we show in \todo{where?} that
+$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+
+In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
+
+If $z=0$, then equation \eqref{selfomega} can be reduced to 
+\begin{equation}\label{selfomega0}
+\begin{split}
+&a_1 + a_2= 1-\gamma_n,\quad    a_1 +\frac{\gamma_n}p\sum_{i=1}^p \frac{\lambda_i^2 a_1}{ \lambda_i^2 a_1+ (1-\gamma_n - a_1) }=r_1 .
+\end{split}
+\ee
+where $a_1:=-r_1M_{1}(0)$ and $a_2:=-r_2M_{2}(0)$.
+
+For the variance asymptotic limit, we study the resolvent
+	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
+In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
+	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
+
+For the bias asymptotic limit, we show in \todo{where?} that
+$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
+Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
+}
+
+\medskip
+\noindent{\bf Defining the resolvent minor.} \ 
+%\HZ{Divide into several parts like sec 7 to improve readability.}
+Then we define the resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
+
+\begin{definition}[Resolvent minors]\label{defn_Minor}
+ For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $\fa \in \mathcal I$, we define the minor $\cal A^{(\mathfrak c)}:=(\cal A_{\fa\fb}:\fa,\fb \in \mathcal I\setminus \{\mathfrak a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $\mathfrak c$-th row and column in $\cal A$.
+Note that we keep the names of indices when defining $\cal A^{(\mathfrak c)}$, i.e.
+$(\cal A^{(\mathfrak c)})_{\fa\fb}= \cal A_{\fa\fb}$ for $\fa,\fb \ne \mathfrak c$.
+Correspondingly, we define the resolvent minor as %(recall equation \eqref{green2})
+\begin{align*}
+G^{(\mathfrak c)}:&=\left[\left(H - \left( {\begin{array}{*{20}c}
+   { zI_{p}} & 0  \\
+   0 & { I_{n}}  \\
+\end{array}} \right)\right)^{(\mathfrak c)}\right]^{-1} ,
+%= \left( {\begin{array}{*{20}c}
+%   { \mathcal G^{(\mathbb T)}} & \mathcal G^{(\mathbb T)} W^{(\mathbb T)}  \\
+%   {\left(W^{(\mathbb T)}\right)^\top\mathcal G^{(\mathbb T)}} & { \mathcal G_R^{(\mathbb T)} }  \\
+%\end{array}} \right)  ,
+\end{align*}
+and define the partial traces $m^{(\mathfrak c)}$ and $m^{(\mathfrak c)}_k$, $k=0,1,2,$ by replacing $G$ with $G^{(\mathfrak c)}$ in equation \eqref{defm}.
+For convenience, we will adopt the convention that for the resolvent minor $G^{(\mathfrak c)}$ defined as above, $G^{(\mathfrak c)}_{\fa\fb} = 0$ if $\fa =\mathfrak c$ or $\fb =\mathfrak c$.
+\end{definition}
+
+Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
+One will see a crucial use of this fact in the heuristic proof below.
+
+\medskip
+\noindent{\bf Schur complements and concentration.}
+Now we give a heuristic derivation of the matrix limit when the entries of $Z_1$ and $Z_2$ are i.i.d. Gaussian. Note that in this case,
+%However, notice that if the entries of $Z_1\equiv Z_1^{\text{Gauss}}$ and $Z_2\equiv Z_2^{\text{Gauss}}$ are i.i.d. Gaussian, then 
+by the rotational invariance of the multivariate Gaussian distribution we have
+\be\label{eq in Gauss} Z_1 U\Lambda \stackrel{d}{=} Z_1 \Lambda, \quad Z_2 V \stackrel{d}{=} Z_2,\ee
+where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent  
+ \begin{equation} \nonumber
+   G(z)= \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda Z_1^\top & n^{-1/2} Z_2^\top  \\
+   {n^{-1/2} Z_1 \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z_2} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{-1}.
+ \end{equation}
+Using Schur complement formula (see \alert{equation} (\ref{resolvent2}) \HZ{check other usage of equation ref}), we have that %for $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\begin{align}
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu},  \ \ \text{for }\  i \in \cal I_0 , \label{0self_Gii}\\
+\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j z_{\mu i}z_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  z_{\nu i}z_{\nu j}  G^{\left(\nu\right)}_{ij},  \ \ \text{for }\  \mu \in \cal I_1, \ \nu\in \cal I_2, \label{0self_Gmu1}
+\end{align}
+where we recall the notations in equation \eqref{labelZ}.
+For the right-hand side of equation \eqref{0self_Gii}, $G^{(i)}$ is independent of the entries $z_{\mu i}$ and $z_{\nu i}$.
+Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{z_{\mu i}: \mu \in \cal I_1\cup \cal I_2\}$, i.e., with high probability,
+\begin{align*}
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 r_1 m_1^{(i)}(z)-  r_2m_2^{(i)}(z)+\oo(1),
+\end{align*}
+where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$.
+Intuitively, since we have only removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
+Hence we obtain from the above equation that
+\begin{align}\label{1self_Gii}
+ G_{ii}  = -\frac{1}{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}.
+\end{align}
+Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\be\label{1self_Gmu} G_{\mu \mu }=-\frac{1}{1+\gamma_n m_0 + \oo(1)},\quad G_{\nu\nu}=-\frac1{1+\gamma_n m+\oo(1)},\ee
+with high probability.
+
+\medskip
+\noindent\textbf{Deriving the self-consistent equations.} Taking average we obtain that 
+\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\frac{1}{1+\gamma_n m_0 + \oo(1)},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\frac{1}{1+\gamma_n m + \oo(1)},
+\ee
+with high probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that 
+\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{\gamma_n}{p} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{\gamma_n}{p} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
+with high probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
+\begin{align*}
+& \frac1{m_1}= -1+ \frac{\gamma_n}{p} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}+ \oo(1),\\ 
+& \frac1{m_2}=-1+\frac{\gamma_n}{p} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}  + \oo(1),
+\end{align*}
+with high probability, which give the approximate self-consistent equations for $(m_1,m_2)$.
+Compare them to the deterministic self-consistent equations in equation \eqref{selfomega}, one can observe that we should have $(m_1,m_2) =(M_{1}, M_{2})+\oo(1)$ with high probability.
+
+\medskip
+\noindent\textbf{Deriving the matrix limit.} Inserting this approximate identity into equation \eqref{1self_Gii}-equation \eqref{2self_Gmu}, we see that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+$$G_{ii}=-(z +\lambda_i^2 r_1  M_{1} + r_2 M_{2}+\oo(1))^{1/2},\quad G_{\mu\mu}=M_{1}+\oo(1),\quad G_{\nu\nu}=M_{2}+\oo(1),$$
+with high probability.
+These explain the diagonal entries of $\Pi$ in equation \eqref{defn_piw}.
+For the off-diagonal entries, they are close to zero due to concentration.
+For example, for $i\ne j\in \cal I_1$, by Schur complement formula (see (\ref{resolvent3})), we have
+$$G_{ij}=-G_{ii}\left(\frac{\lambda_i}{n^{1/2}}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j} + \frac{1}{n^{1/2}}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j} \right).$$
+Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
+The other off-diagonal entries can be bounded in the same way.
+
+The above arguments are the core of the main proof.
+To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z_1$ and $Z_2$ only satisfy certain moment assumptions.
+These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
+For the full proof, we refer the reader to ...
+.

### 2020-09-08 arxiv/transfer.tex
revise

@@
 
-\medskip
-\noindent\textbf{Proof overview.}
-%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
-We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-We use the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-
-For the variance asymptotic limit, we study the resolvent
-	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
-Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
-In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
-	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
-
-For the bias asymptotic limit, we show in \todo{where?} that
-$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
-Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
-Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
+In Section \ref{app_proof_main_thm}, we will describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
 

### 2020-09-09 arxiv/proof_main.tex
pf overview

@@
 
-Before the end of this section, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
-
-\medskip
-\noindent\textbf{An overview of the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.}
+\subsection{Proof Overview for the Random Matrix Results}
+Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}. 
 %We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
@@
 \be\label{eigen2extra}(X_1^\top X_1+X_2^\top X_2)^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
-We divide the proof into the following parts.
+We divide the discussion into the following parts.
 
@@
 We now describe the asymptotic limit of $G(z)$ as $n\to \infty$.
-First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
+First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
 %\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)}, 
 the unique solution to the following system of equations
-\begin{equation}\label{selfomega}
+\begin{equation}\label{selfomega_a}
 \begin{split}
-& \frac{r_1}{a_{1}(z)} = \frac{1}{n}\sum_{i=1}^p \frac{\lambda_i^2}{  z+\lambda_i^2 a_{1}(z) +a_{2} (z) } - 1 ,\ \  \ \frac{r_2}{a_{2}(z)} = \frac{1}{n}\sum_{i=1}^p \frac{1 }{  z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }- 1 ,
+& \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) ,
 \end{split}
@@
 \be \label{defn_piw}
-\Pi(z) := \begin{pmatrix} -(z+a_{1}(z)\Lambda^2  +  a_{2}(z))^{-1} & 0 & 0 \\ 0 &  \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & \frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
-In particular, the matrix limit of $\cal G(z)$ is given by $-(z+a_{1}(z)\Lambda^2 + a_{2}(z))^{-1}$.
+\Gi(z) := \begin{pmatrix} (-z\id_p+a_{1}(z)\Lambda^2  +  a_{2}(z)\id_p)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
+In particular, the matrix limit of $\cal G(z)$ is given by $(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}$.
 
 \medskip
-\noindent{\bf Deriving the bias and variance asymptotics.} {\cor Notice that using equation \eqref{mainG}, we can write  equation \eqref{eigen2extra} as
+\noindent{\bf Deriving the bias and variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
 \be\label{rewrite X as R} (X_1^\top X_1+X_2^\top X_2)^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
-For the bias asymptotic limit, we show in \todo{where?} that
-$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
+Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
+Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.
 
-In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
+For the bias asymptotics, we can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
+More precisely, using equation \eqref{eigen2extra} we can obtain that
+\begin{align}
+n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
+&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
+\end{align}
+where we used equation \eqref{rewrite X as R} in the second step. It is natural to guess that the matrix limit of $\cal G'(0)$ is given by 
+\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
+If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
+Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
+\begin{align*}
+n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi w,
+\end{align*}
+which concludes \eqref{lem_cov_derv_eq}.
+Note that in order to have the approximate identity for $\cal G'(0)$ in \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
+This is the main reason why we need to take a general $z$ in the definition of resolvents.
 
-If $z=0$, then equation \eqref{selfomega} can be reduced to 
-\begin{equation}\label{selfomega0}
-\begin{split}
-&a_1 + a_2= 1-\gamma_n,\quad    a_1 +\frac{\gamma_n}p\sum_{i=1}^p \frac{\lambda_i^2 a_1}{ \lambda_i^2 a_1+ (1-\gamma_n - a_1) }=r_1 .
-\end{split}
-\ee
-where $a_1:=-r_1M_{1}(0)$ and $a_2:=-r_2M_{2}(0)$.
+%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
 
-For the variance asymptotic limit, we study the resolvent
-	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
-Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
-In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
-	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
-
-For the bias asymptotic limit, we show in \todo{where?} that
-$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
-Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
-Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
-}
+%For the variance asymptotic limit, we study the resolvent
+%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
+%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
+%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
+%
+%For the bias asymptotic limit, we show in \todo{where?} that
+%$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
+%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
 
 \medskip
-\noindent{\bf Defining the resolvent minor.} \ 
+\noindent{\bf Gaussian case.} Now we give a heuristic derivation of the matrix limit when the entries of $Z_1$ and $Z_2$ are i.i.d. Gaussian. In this case,
+%However, notice that if the entries of $Z_1\equiv Z_1^{\text{Gauss}}$ and $Z_2\equiv Z_2^{\text{Gauss}}$ are i.i.d. Gaussian, then 
+by the rotational invariance of the multivariate Gaussian distribution we have
+\be\label{eq in Gauss} Z_1 U\Lambda \stackrel{d}{=} Z_1 \Lambda, \quad Z_2 V \stackrel{d}{=} Z_2,\ee
+where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent  
+ \begin{equation} \label{resolv Gauss1}
+   G(z)= \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda Z_1^\top & n^{-1/2} Z_2^\top  \\
+   {n^{-1/2} Z_1 \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z_2} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{-1}.
+ \end{equation}
+
+\medskip
+\noindent{\bf Schur complements and concentration.} 
+%Now we discuss about how to obtain the matrix limit in equation \eqref{defn_piw}.
 %\HZ{Divide into several parts like sec 7 to improve readability.}
-Then we define the resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
+The core quantities of the derivation are the following resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
 
@@
 $(\cal A^{(\mathfrak c)})_{\fa\fb}= \cal A_{\fa\fb}$ for $\fa,\fb \ne \mathfrak c$.
-Correspondingly, we define the resolvent minor as %(recall equation \eqref{green2})
+Correspondingly, we define the resolvent minor for $G$ in \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
 \begin{align*}
-G^{(\mathfrak c)}:&=\left[\left(H - \left( {\begin{array}{*{20}c}
-   { zI_{p}} & 0  \\
-   0 & { I_{n}}  \\
-\end{array}} \right)\right)^{(\mathfrak c)}\right]^{-1} ,
+G^{(\mathfrak c)}:&=\left[ \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda Z_1^\top & n^{-1/2} Z_2^\top  \\
+   {n^{-1/2} Z_1 \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z_2} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{(\mathfrak c)}\right]^{-1} ,
 %= \left( {\begin{array}{*{20}c}
@@
 and define the partial traces $m^{(\mathfrak c)}$ and $m^{(\mathfrak c)}_k$, $k=0,1,2,$ by replacing $G$ with $G^{(\mathfrak c)}$ in equation \eqref{defm}.
-For convenience, we will adopt the convention that for the resolvent minor $G^{(\mathfrak c)}$ defined as above, $G^{(\mathfrak c)}_{\fa\fb} = 0$ if $\fa =\mathfrak c$ or $\fb =\mathfrak c$.
+For convenience, we adopt the convention that for the resolvent minor $G^{(\mathfrak c)}$ defined as above, $G^{(\mathfrak c)}_{\fa\fb} = 0$ if $\fa =\mathfrak c$ or $\fb =\mathfrak c$.
 \end{definition}
 
-Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
+%Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
 One will see a crucial use of this fact in the heuristic proof below.
 
-\medskip
-\noindent{\bf Schur complements and concentration.}
-Now we give a heuristic derivation of the matrix limit when the entries of $Z_1$ and $Z_2$ are i.i.d. Gaussian. Note that in this case,
-%However, notice that if the entries of $Z_1\equiv Z_1^{\text{Gauss}}$ and $Z_2\equiv Z_2^{\text{Gauss}}$ are i.i.d. Gaussian, then 
-by the rotational invariance of the multivariate Gaussian distribution we have
-\be\label{eq in Gauss} Z_1 U\Lambda \stackrel{d}{=} Z_1 \Lambda, \quad Z_2 V \stackrel{d}{=} Z_2,\ee
-where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent  
- \begin{equation} \nonumber
-   G(z)= \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda Z_1^\top & n^{-1/2} Z_2^\top  \\
-   {n^{-1/2} Z_1 \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z_2} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{-1}.
- \end{equation}
-Using Schur complement formula (see \alert{equation} (\ref{resolvent2}) \HZ{check other usage of equation ref}), we have that %for $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+ Using Schur complement formula (see {equation} (\ref{resolvent2})), we have that %for $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
 \begin{align}
@@
 where we recall the notations in equation \eqref{labelZ}.
-For the right-hand side of equation \eqref{0self_Gii}, $G^{(i)}$ is independent of the entries $z_{\mu i}$ and $z_{\nu i}$.
+For the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $z_{\mu i}$ and $z_{\nu i}$.
 Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{z_{\mu i}: \mu \in \cal I_1\cup \cal I_2\}$, i.e., with high probability,
 \begin{align*}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 r_1 m_1^{(i)}(z)-  r_2m_2^{(i)}(z)+\oo(1),
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
 \end{align*}
 where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$.
-Intuitively, since we have only removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
+Intuitively, since we have removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
 Hence we obtain from the above equation that
 \begin{align}\label{1self_Gii}
- G_{ii}  = -\frac{1}{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}.
+ G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)\right)^{-1}.
 \end{align}
 Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\be\label{1self_Gmu} G_{\mu \mu }=-\frac{1}{1+\gamma_n m_0 + \oo(1)},\quad G_{\nu\nu}=-\frac1{1+\gamma_n m+\oo(1)},\ee
+\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
 with high probability.
@@
 \medskip
-\noindent\textbf{Deriving the self-consistent equations.} Taking average we obtain that 
-\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\frac{1}{1+\gamma_n m_0 + \oo(1)},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\frac{1}{1+\gamma_n m + \oo(1)},
+\noindent\textbf{Deriving the self-consistent equations.} Taking average of \eqref{1self_Gmu}, we obtain that 
+\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
 \ee
 with high probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that 
-\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{\gamma_n}{p} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{\gamma_n}{p} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
+\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
 with high probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
 \begin{align*}
-& \frac1{m_1}= -1+ \frac{\gamma_n}{p} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}+ \oo(1),\\ 
-& \frac1{m_2}=-1+\frac{\gamma_n}{p} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}  + \oo(1),
+& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\ 
+& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
 \end{align*}
-with high probability, which give the approximate self-consistent equations for $(m_1,m_2)$.
-Compare them to the deterministic self-consistent equations in equation \eqref{selfomega}, one can observe that we should have $(m_1,m_2) =(M_{1}, M_{2})+\oo(1)$ with high probability.
+with high probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
+Compare them to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
+\be\label{approx m12 add}
+(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with high probability. }
+\ee
 
 \medskip
-\noindent\textbf{Deriving the matrix limit.} Inserting this approximate identity into equation \eqref{1self_Gii}-equation \eqref{2self_Gmu}, we see that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-$$G_{ii}=-(z +\lambda_i^2 r_1  M_{1} + r_2 M_{2}+\oo(1))^{1/2},\quad G_{\mu\mu}=M_{1}+\oo(1),\quad G_{\nu\nu}=M_{2}+\oo(1),$$
+\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii}-\eqref{2self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
 with high probability.
-These explain the diagonal entries of $\Pi$ in equation \eqref{defn_piw}.
+These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}.
 For the off-diagonal entries, they are close to zero due to concentration.
 For example, for $i\ne j\in \cal I_1$, by Schur complement formula (see (\ref{resolvent3})), we have
-$$G_{ij}=-G_{ii}\left(\frac{\lambda_i}{n^{1/2}}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j} + \frac{1}{n^{1/2}}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j} \right).$$
+$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j} \Big).$$
 Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
 The other off-diagonal entries can be bounded in the same way.
+\nc
 
@@
 These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
-For the full proof, we refer the reader to ...
-.
+For the full rigorous proof, we refer the reader to Section \ref{sec_maintools}.

### 2020-09-09 arxiv/transfer.tex
pf overview

@@
 Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
-	\[ \Pi \define  M \frac{a_4 M^{\top}M + (1 + a_3) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
+	\[ \Pi \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
 where $a_{3}$ and $a_4$ are the solutions of the following two equations:
 \begin{gather}\label{eq_a34extra}
-		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_3 - b_1 \cdot  a_4
-		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_4 -  b_1 \cdot  a_3 = b_1 .
+		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1 .
 %		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3

### 2020-09-10 arxiv/algorithm.tex
reorg

--- 2020-09-09 arxiv/transfer.tex
@@
-\section{Illustrative Examples in an Isotropic Setting}\label{sec_special}
-
-%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-%We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
-%The results in Section \ref{sec_general} show when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
-%In particular, the general conditions depend on specific properties of task data such as the covariate shift matrix.
-%However, the conditions given by the limiting bias and variance of multi-task learning can be difficult to interpret.
-%The goal of this section is to address this issue.
-%We interpret the limiting bias and variance equations in an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
-%We show that three properties of task data affect the performance of multi-task learning as follows.
-%(i) \textit{Task similarity}: We explain the phenomenon of negative transfer precisely as tasks become more different.
-%(ii) \textit{Sample ratio}: We further explain a curious phenomenon where increasing the sample ratio between the source and target task helps initially, but hurts eventually.
-%(iii) \textit{Covariate shift}: Finally, we show that as the sample size of the source task increases, we show that the covariate shift worsens the performance of the multi-task estimator.
-%Finally, we provide a extend our results from two tasks to many tasks with the same features.
-%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
-%We show how negative transfer occurs by varying task similarity or sample size.
-%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-We illustrate our main results (to be described in Section \ref{sec_general}) in a simplified setting.
-For this setting, we simulate several empirical phenomena that are well-known in hard parameter sharing approaches.
-We use our results to explain the empirical phenomena.
-
-%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
-
-%In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$ (or $d$), there is a transition from positive transfer to negative transfer in MTL.
-%We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
-%Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
-%{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
-%Our result below will provide an explanation to this phenomenon.
-%Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
-%We introduce the following notations.
-%{\begin{align*}
-%	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
-%\end{align*}}
-
-\subsection{Negative Transfer}
-
-\noindent\textbf{Isotropic features and models.}
-	Imagine that we have two tasks and the covariates of both tasks have isotropic covariance matrices.
-%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
-	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
-	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
-	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
-	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
-
-\begin{example}[Varying model distance]
-\end{example}
-
-Using our techniques described later in Section \ref{sec_general}, we derive the limiting prediction loss of the hard parameter sharing estimator.
-Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
-
-\begin{corollary}[Derived from Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}]
-	In the isotropic setting described above, with high probability, the prediction loss of the hard parameter sharing estimator for task two satisfies:
-	\begin{align*}
-		& \bigabs{ L(\hat{\beta}_2^{\MTL}) - \frac{\sigma^2}{\rho_1 + \rho_2 - 1} - (1 + \frac{6}{\rho_1} + \frac{1}{\rho_1^2})pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} } \\
-		\le & 	\frac{4}{\sqrt{\rho_1}}(1 + \frac{1}{\rho_1})	pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} + \oo(\sigma^2 + pd^2).
-%	 \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4  +\oo(\sigma^2 + pd^2)  \le \\
-%	 \le  \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\oo(\sigma^2 + pd^2)
-	 \end{align*}
-\end{corollary}
-
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the following simplified setting, where we can perform explicit calculations.
-We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
-In particular, the bias of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases.
-Therefore, while the variance of MTL still reduces compared to STL, if the bias increases more than the amount of variance reduced, we will observe negative transfer.
-
-\begin{proposition}[Task model distance]\label{prop_dist_transition}
-	In the isotropic model, suppose that $\rho_1$ and $\rho_2 > 1$.
-	Then
-	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-	Here {\small$\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$}.
-	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
-\end{proposition}
-
-Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
-Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
-%Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
-We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
-%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
-%Figure \ref{fig_model_shift} shows the result.
-%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-The proof of Proposition \ref{prop_dist_transition} involves two parts.
-First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
-A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
-thus simplifying the general condition in Theorem \ref{thm_main_informal}.
-
-\begin{figure}[!t]
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-		\caption{Task similarity}
-		\label{fig_model_shift}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
-		\caption{Sample size}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
-		\caption{Covariate shift}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
-	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
-	The $y$-axis measures the loss of STL minus MTL.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
-
-%\subsection{Sample Ratio}\label{sec_data_size}
-
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
-%More generally, such results are still applicable when all task data are being added simultaneously.
-On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
-For such settings, we have also observed that adding more labeled data from one task does not always help.
-%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-In the isotropic model, we consider what happens if we vary the source task sample size.
-Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-Figure \ref{fig_size} provides a simulation result for such a setting.
-We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-
-\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
-	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-	Then we have that
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
-		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-\end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
-We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-There are several unexplained observations near $y = 0$ caused by $\nu$.
-The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-
-\subsection{Covariate Shift} \label{sec_covshift}
-So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-In general, the covariance matrices of the two tasks may be different such as in text classification.
-In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
-We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
-
-\noindent\textit{Example.}
-	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$ similar to Theorem \ref{thm_main_informal}.
-	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$ and $\Psi(\beta_1, \beta_2) = 0$.
-	We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	Hence, $\lambda$ measures the severity of the covariate shift.
-	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-
-%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-We compare different choices of $M$ that belong to the following bounded set.
-Let $\lambda_i$ be the $i$-th singular value of $M$.
-Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-{\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
-\end{align*}}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	For the setting of the example above, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
-	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-	We have that
-		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{proposition}
-Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
-The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
-%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
-
-%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
-%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
-%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
-\subsection{Data Efficiency}
-
-observed in Taskonomy \cite{ZSSGM18}.
-
-\section{Main Results for General Features}\label{sec_general}
-
-%\begin{proposition}[Bias-variance tradeoff]
-%	Variance always reduces and bias always increases.
-%\end{proposition}
-In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
-First, we consider the two-task case.
-We provide precise asymptotics of the bias and variance of the multi-task learning estimator.
-We apply recent developments from the random matrix theory literature to characterize the bias and variance.
-The results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties (Section \ref{sec_special}).
-Second, we consider the multiple-task case where all tasks have the same features but different labels.
-We extend the bias-variance decomposition of the two-task case to this setting and show qualitatively similar results.
-%For the single-task learning estimator, there are well-known results that relate its prediction loss to sample size and noise variance.
-
-%We focus on the high-dimensional linear regression setting \cite{}
-
-\paragraph{Same covariates.}
-%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
-%Our main technical contribution is to extend this result to two tasks.
-%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Similar to the two-task case, we consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
-We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-\begin{align}
-	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-\end{align}
-One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-
-Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
-Before stating the result, we define the following notations.
-Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
-Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
-\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
-For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
-
-\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Consider the multiple-task case where all tasks have the same covariates.
-	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
-	Then, the following is true:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
-over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
-	\end{itemize}
-\end{theorem}
-Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
-As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
-The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
-
-\paragraph{Different covariates: the two-task case.}
-As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
-Therefore, we consider an arbitrary local minimum $B, W_1, W_2$, in particular when $B = \hat{B}(W_1, W_2)$ satisfies the local optimality condition.
-We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
-Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$ as follows
-\begin{align}
-	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
-	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
-			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
-\end{align}
-See Section \ref{app_proof_main_thm} for its derivation.
-Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
-equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
-%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Comparing the above to single-task learning, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-
-Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
-We introduce a key quantity $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
-
-%We now state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
-The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
-
-\begin{theorem}[Two-task case]\label{thm_main_informal}
-	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
-	For the setting of two tasks, let $C$ be a fixed constant and let $\delta = \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) }$.
-	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
-	\begin{enumerate}
-		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
-		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
-	\end{enumerate}
-\end{theorem}
-In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
-We make several remarks about Theorem \ref{thm_main_informal}.
-First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
-This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
-%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
-%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
-%determined by the covariate shift matrix and the model shift.
-%The bounds get tighter and tighter as $\rho_1$ increases.
-Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
-Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
-%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-
-%\textbf{Proof overview.}\todo{}
-%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
-%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
-This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
-%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
-%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
-%
-%
-%
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-
-\iffalse
-Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
-From \cite{WZR20}, we know that we need to explicitly restrict the output dimension $r$ of $B$ so that there is transfer between the two tasks.
-Hence for the case of two tasks, we consider the setting where $r=1$.
-For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to
-\begin{align}\label{eq_mtl_2task}
-	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
-\end{align}
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
-\begin{align}
-	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
-	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
-	&= \frac{1}{w_2}\left[\beta_2 + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-\nonumber
-\end{align}
-As a remark, when $w_1 = w_2 = 1$, we obtain linear regression.
-If $\beta_1$ is a scaling of $\beta_2$, then  $w_1, w_2$ can be scaled accordingly to fix both tasks more accurately than linear regression.
-
-%For the discussions below, we assume that the entries of $\e_1$ and $\e_2$ all have the same variance $\sigma^2$.
-This holds for most parts of our discussion, except in Proposition \ref{prop_var_transition}.
-We will derive different expressions for the validation loss and the test error
-
-Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
-With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
-We assume that $N_1$ and $N_2$ satisfy $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
-Then we write the validation loss in \eqref{eq_mtl_eval} as
-\begin{align}\label{eq_mtl_2tasktilde}
-	g(w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
-\end{align}
-Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that the optimal solution of $g$ only depends on the ratio $v:=w_1/w_2$.
-Hence we overload the notation by writing $g(v)$ in the following discussion.
-The expectation of $g(v)$ can be written as follows.
-\begin{align}
-		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \nonumber\\
-	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
-	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
-		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
-		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{revise_eq_val_mtl}
-\end{align}
-
-{\color{red}\begin{align*}
-			& f(W_1, W_2) = \bignorm{X_1 \hat B w_1 - Y_1}^2 + \bignorm{X_2 \hat B w_2 - Y_2}^2\\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}Y_1 + vX_2^{\top}Y_2\right) - Y_1}^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}Y_1 + X_2^{\top}Y_2\right) - Y_2}^2 \\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}\e_1 + vX_2^{\top}\e_2\right) - \e_1 + X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}\e_1 + X_2^{\top}\e_2\right) - \e_2 + vX_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&=\val(v)\cdot \left( 1+\OO(p^{-1/2\e})\right) \quad \text{w.h.p.},
-		\end{align*}
-		where
-		\begin{align*}
-		\val(v)&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}   X_1^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_1^\top\right)\\
-			&+\sigma^2 \tr\left(X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_2\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^\top\right)\\
-			&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 +(n_1+n_2-p)\sigma^2.
-		\end{align*}
-	}
-
-Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
-Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
-Now we can define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
-%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task".
-%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
-%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
-\begin{align}
-	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
-			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
-\end{align}
-which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
-\fi
-
-%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
-%	In the setting of two tasks,
-%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
-%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
-%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
-%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-%	{\small\begin{align*}%\label{eq_introX1X2}
-%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-%	\end{align*}}%
-%	where $a_1, a_2$ are solutions of the following equations:
-%	{\small\begin{align*}
-%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-%	\end{align*}}
-%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-%\end{lemma}
-
-\paragraph{Key ingredients.}
-We introduce two key lemmas that show tight asymptotic convergence rate of the bias equation \eqref{eq_bias_2task} and the variance equation  as sample sizes increase to infinity.
-%The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
-For the covariate shift matrix $M$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be its singular values in descending order.
-%which deals with the inverse of the sum of two random matrices, which
-%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
-	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
-	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
-	In the setting of Theorem \ref{thm_main_informal},
-	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
-	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
-	\end{align}
-	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
-	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12extra}
-	\end{align}
-\end{lemma}
-
-Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
-To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
-%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
-Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
-\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
-
-Lemma \ref{lem_cov_shift} also implies the asymptotic limit of the prediction loss of single-task learning.
-%The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-In particular, by setting $X_1 = 0$, we obtain the following corollary, which is a well-known result in random matrix theory.
-\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
-	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}A} + o(\norm{A}). \ee
-\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
-To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.
-We briefly describe the history behind the above well-known result.
-When the entries of $X_2$ are multivariate Gaussian, this result recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we have stated a result from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp concentration error bound.
-One can see that our result extends Lemma \ref{lem_minv} from a single sample covariance matrix to the sum of two independent sample covariance matrices.
-
-Interestingly, the asymptotic limit of the variance only depends on the sample sizes and the covariate shift matrix.
-Next, we derive the asymptotic limit of the bias equation \eqref{eq_bias_2task}, which depends on the scaled model distance in addition to sample size and covariate shift.
-%(cf.
-Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
-We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
-That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
-We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
-Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
-
-\begin{definition}[Limiting bias]
-Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
-	\[ \Pi \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
-where $a_{3}$ and $a_4$ are the solutions of the following two equations:
-\begin{gather}\label{eq_a34extra}
-		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1 .
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
-\end{definition}
-
-Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
-\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
-With high probability, we have that
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-= w^{\top} \Pi w + o(\|w\|^2),
-\end{split}
-\end{equation}
-
-\end{lemma}
-To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
-Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
-As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
-Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
-In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
-
-In Section \ref{app_proof_main_thm}, we will describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
-
 \section{Implication for Mitigating Sample Imbalance and Covariate Shift}

### 2020-09-10 arxiv/implications.tex
reorg

--- 2020-09-09 arxiv/transfer.tex
@@
-\section{Illustrative Examples in an Isotropic Setting}\label{sec_special}
+\section{Implications}\label{sec_special}
 
@@
 
-\subsection{Negative Transfer}
+\subsection{Sample Imbalance}
 
@@
 
-\subsection{Data Efficiency}
+\subsection{Sample Efficiency}
 
 observed in Taskonomy \cite{ZSSGM18}.
-
-\section{Main Results for General Features}\label{sec_general}
-
-%\begin{proposition}[Bias-variance tradeoff]
-%	Variance always reduces and bias always increases.
-%\end{proposition}
-In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
-First, we consider the two-task case.
-We provide precise asymptotics of the bias and variance of the multi-task learning estimator.
-We apply recent developments from the random matrix theory literature to characterize the bias and variance.
-The results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties (Section \ref{sec_special}).
-Second, we consider the multiple-task case where all tasks have the same features but different labels.
-We extend the bias-variance decomposition of the two-task case to this setting and show qualitatively similar results.
-%For the single-task learning estimator, there are well-known results that relate its prediction loss to sample size and noise variance.
-
-%We focus on the high-dimensional linear regression setting \cite{}
-
-\paragraph{Same covariates.}
-%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
-%Our main technical contribution is to extend this result to two tasks.
-%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Similar to the two-task case, we consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
-We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-\begin{align}
-	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-\end{align}
-One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-
-Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
-Before stating the result, we define the following notations.
-Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
-Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
-\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
-For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
-
-\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Consider the multiple-task case where all tasks have the same covariates.
-	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
-	Then, the following is true:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
-over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
-	\end{itemize}
-\end{theorem}
-Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
-As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
-The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
-
-\paragraph{Different covariates: the two-task case.}
-As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
-Therefore, we consider an arbitrary local minimum $B, W_1, W_2$, in particular when $B = \hat{B}(W_1, W_2)$ satisfies the local optimality condition.
-We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
-Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$ as follows
-\begin{align}
-	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
-	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
-			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
-\end{align}
-See Section \ref{app_proof_main_thm} for its derivation.
-Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
-equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
-%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Comparing the above to single-task learning, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-
-Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
-We introduce a key quantity $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
-
-%We now state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
-The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
-
-\begin{theorem}[Two-task case]\label{thm_main_informal}
-	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
-	For the setting of two tasks, let $C$ be a fixed constant and let $\delta = \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) }$.
-	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
-	\begin{enumerate}
-		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
-		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
-	\end{enumerate}
-\end{theorem}
-In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
-We make several remarks about Theorem \ref{thm_main_informal}.
-First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
-This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
-%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
-%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
-%determined by the covariate shift matrix and the model shift.
-%The bounds get tighter and tighter as $\rho_1$ increases.
-Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
-Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
-%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-
-%\textbf{Proof overview.}\todo{}
-%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
-%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
-This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
-%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
-%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
-%
-%
-%
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-
-\iffalse
-Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
-From \cite{WZR20}, we know that we need to explicitly restrict the output dimension $r$ of $B$ so that there is transfer between the two tasks.
-Hence for the case of two tasks, we consider the setting where $r=1$.
-For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to
-\begin{align}\label{eq_mtl_2task}
-	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
-\end{align}
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
-\begin{align}
-	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
-	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
-	&= \frac{1}{w_2}\left[\beta_2 + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-\nonumber
-\end{align}
-As a remark, when $w_1 = w_2 = 1$, we obtain linear regression.
-If $\beta_1$ is a scaling of $\beta_2$, then  $w_1, w_2$ can be scaled accordingly to fix both tasks more accurately than linear regression.
-
-%For the discussions below, we assume that the entries of $\e_1$ and $\e_2$ all have the same variance $\sigma^2$.
-This holds for most parts of our discussion, except in Proposition \ref{prop_var_transition}.
-We will derive different expressions for the validation loss and the test error
-
-Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
-With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
-We assume that $N_1$ and $N_2$ satisfy $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
-Then we write the validation loss in \eqref{eq_mtl_eval} as
-\begin{align}\label{eq_mtl_2tasktilde}
-	g(w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
-\end{align}
-Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that the optimal solution of $g$ only depends on the ratio $v:=w_1/w_2$.
-Hence we overload the notation by writing $g(v)$ in the following discussion.
-The expectation of $g(v)$ can be written as follows.
-\begin{align}
-		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \nonumber\\
-	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
-	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
-		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
-		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{revise_eq_val_mtl}
-\end{align}
-
-{\color{red}\begin{align*}
-			& f(W_1, W_2) = \bignorm{X_1 \hat B w_1 - Y_1}^2 + \bignorm{X_2 \hat B w_2 - Y_2}^2\\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}Y_1 + vX_2^{\top}Y_2\right) - Y_1}^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}Y_1 + X_2^{\top}Y_2\right) - Y_2}^2 \\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}\e_1 + vX_2^{\top}\e_2\right) - \e_1 + X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}\e_1 + X_2^{\top}\e_2\right) - \e_2 + vX_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&=\val(v)\cdot \left( 1+\OO(p^{-1/2\e})\right) \quad \text{w.h.p.},
-		\end{align*}
-		where
-		\begin{align*}
-		\val(v)&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}   X_1^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_1^\top\right)\\
-			&+\sigma^2 \tr\left(X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_2\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^\top\right)\\
-			&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 +(n_1+n_2-p)\sigma^2.
-		\end{align*}
-	}
-
-Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
-Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
-Now we can define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
-%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task".
-%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
-%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
-\begin{align}
-	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
-			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
-\end{align}
-which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
-\fi
-
-%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
-%	In the setting of two tasks,
-%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
-%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
-%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
-%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-%	{\small\begin{align*}%\label{eq_introX1X2}
-%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-%	\end{align*}}%
-%	where $a_1, a_2$ are solutions of the following equations:
-%	{\small\begin{align*}
-%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-%	\end{align*}}
-%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-%\end{lemma}
-
-\paragraph{Key ingredients.}
-We introduce two key lemmas that show tight asymptotic convergence rate of the bias equation \eqref{eq_bias_2task} and the variance equation  as sample sizes increase to infinity.
-%The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
-For the covariate shift matrix $M$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be its singular values in descending order.
-%which deals with the inverse of the sum of two random matrices, which
-%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
-	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
-	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
-	In the setting of Theorem \ref{thm_main_informal},
-	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
-	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
-	\end{align}
-	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
-	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12extra}
-	\end{align}
-\end{lemma}
-
-Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
-To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
-%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
-Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
-\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
-
-Lemma \ref{lem_cov_shift} also implies the asymptotic limit of the prediction loss of single-task learning.
-%The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-In particular, by setting $X_1 = 0$, we obtain the following corollary, which is a well-known result in random matrix theory.
-\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
-	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}A} + o(\norm{A}). \ee
-\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
-To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.
-We briefly describe the history behind the above well-known result.
-When the entries of $X_2$ are multivariate Gaussian, this result recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we have stated a result from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp concentration error bound.
-One can see that our result extends Lemma \ref{lem_minv} from a single sample covariance matrix to the sum of two independent sample covariance matrices.
-
-Interestingly, the asymptotic limit of the variance only depends on the sample sizes and the covariate shift matrix.
-Next, we derive the asymptotic limit of the bias equation \eqref{eq_bias_2task}, which depends on the scaled model distance in addition to sample size and covariate shift.
-%(cf.
-Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
-We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
-That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
-We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
-Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
-
-\begin{definition}[Limiting bias]
-Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
-	\[ \Pi \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
-where $a_{3}$ and $a_4$ are the solutions of the following two equations:
-\begin{gather}\label{eq_a34extra}
-		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1 .
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
-\end{definition}
-
-Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
-\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
-With high probability, we have that
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-= w^{\top} \Pi w + o(\|w\|^2),
-\end{split}
-\end{equation}
-
-\end{lemma}
-To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
-Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
-As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
-Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
-In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
-
-In Section \ref{app_proof_main_thm}, we will describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
-
-\section{Implication for Mitigating Sample Imbalance and Covariate Shift}
-
-\paragraph{Benefits of multi-task learning.}
-We can in fact extend the result to the cases where the noise variances are different.
-In this case, we will see that MTL is particularly effective.
-%As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Concretely, suppose the noise variance $\sigma_1^2$ of task $1$ differs from the noise variance $\sigma_2^2$ of task $2$.
-If $\sigma_1^2$ is too large, the source task provides a negative transfer to the target.
-If $\sigma_1^2$ is small, the source task is more helpful.
-We leave the result to Proposition \ref{prop_var_transition} in Appendix \ref{app_proof_31}.
-Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$.
-In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
-
-\begin{proposition}[Label denoising]
-\label{prop_var_transition}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
-	Then we have the following transition with respect to $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 < - \nu^{1/2} \rho_1 \cdot p d^2+\left(1+ \nu^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
-		\item If $\sigma_1^2 > -\nu^{-1/2}\rho_1\cdot p d^2   +\left(1+ \nu^{1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-
-We use our tools to explain a key result of Taskonomy by Zamir et al. \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
-%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using $x \cdot n_i$ datapoints from every task. The data efficiency ratio is defined as
-{\small\[ \argmin_{x\in(0, 1)} ~~
-		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
-		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]}
-For example, the data efficiency ratio is $1$ if there is negative transfer.
-Using our tools, we show that in the isotropic model, the data efficiency ratio is
-roughly
-{\small\[ \frac{1}{\rho_1 + \rho_2} {+ \frac{2}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]}%
-Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$ (up to a constant multiple), the transfer is positive.
-Moreover, the data efficiency ratio quantifies how effective the positive transfer is using MTL.
-%In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-
-Next we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
-Its proof can be found in Appendix \ref{app_proof_32}.
-%In the statement, we shall denote the data efficiency ratio as $\al^\star$.
-
-\begin{proposition}[Labeling efficiency]
-\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 \ge 9$ and $\Psi(\beta_1, \beta_2) < (5(\rho_1-1))^{-1} + (5(\rho_2-1))^{-1}$.
-	Then the data efficiency ratio $x^\star$ satisfies
-	\be\label{eq_uplowx} x_l  \le x^\star\le \frac{1}{\rho_1 + \rho_2} \bigbrace{  \frac{2}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}+1}, \ee
-	where we denoted
-	$$x_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
-\end{proposition}
-
-\paragraph{Algorithmic consequence.}
-
-\noindent\textit{Detecting negative transfer.}
-Inspired by the observation, we propose a single-task based metric to help understand MTL results using STL results.
-\squishlist
-	\item For each task, we train a single-task model.
-	Let $z_s$ and $z_t$ be the prediction accuracy of each task, respectively.
-	Let $\tau\in(0, 1)$ be a fixed threshold.
-	\item If $z_s - z_t > \tau$, then we predict that there will be positive transfer when combining the two tasks using MTL.
-	If $z_s - z_t < -\tau$, then we predict negative transfer.
-\squishend
-
-\noindent\textit{Mitigating negative transfer.}
-An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
-In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-\squishlist
-	\item We divide the source task data into $S$ batches.
-	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
-	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
-	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\squishend
-
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-\noindent\textit{Covariance alignemnt.}
-Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
-Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
-The idea is to add an alignment module between the input and the shared module $B$.
-This new module is then trained together with $B$ and the output layers.
-We validate our insight on this procedure in the experiments.

### 2020-09-10 arxiv/proof_main.tex
reorg

@@
-\section{Proof of the General Case}\label{sec_proof_general}
+%\section{Proofs}\label{sec_proof_general}
 
-\subsection{Proof of the Multiple-task Case}\label{app_proof_many_tasks}
+\subsection{The Multiple-task Case}\label{app_proof_many_tasks}
 
@@
 
-\subsection{Proof of the Two-task Case}\label{app_proof_main_thm}
-
-In this subsection, we provide the proof of Theorem \ref{thm_main_informal} using Lemma  \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
-First, we provide the steps for the bias-variance decomposition.
-Using the local optimality condition of $B$, we obtain that
-\begin{align*}
-	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
-	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
-	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-\end{align*}
-Recall that $\hat{\beta}_2^{\MTL} = \hat{B}(W_1, W_2) W_2$, and one can verify that equation \eqref{eq_bias_2task} and \eqref{eq_var_2task} hold.
-
-During the proof we shall also give explicit expressions for $\Delta_{\bias}$ and $\Delta_{\vari}$, which might be of interest to some readers.
-With $a_i$, $i=1,2,3,4$, given in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, 
-we define the following matrix
-\be\label{defnpihat}\Pi \equiv \Pi(\hat v)= \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot \hat v^2{M} \frac{(1 +   a_3)\id + \hat v^2 a_4 {M}^{\top} {M}}{( \hat v^2 a_1 {M}^{\top} {M}+ a_2 )^2} {M}^{\top}.\ee
-%which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
-%$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
-Moreover, we introduce two factors that will appear often in our statements and discussions:
-$$\al_-(\rho_1):=\left(1- \rho_1^{-1/2}\right)^2,\quad \al_+(\rho_1):=\left(1 + \rho_1^{-1/2}\right)^2.$$ 
-In fact, $\al_-(\rho_1)$ and $\al_+(\rho_1)$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}.
-In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry.
-Finally, we introduce the error term
-\be\label{eq_deltaextra} 
- \delta(\hat v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\hat v^2\lambda_{\min}^2(M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \hat{v}\beta_2)}^2.\ee
-%where $\lambda_{\min}(\hat M)$ is the smallest singular value of $\hat M$. 
-Note that this factor converges to 0 as $\rho_1$ increases. It is not hard to see that Theorem \ref{thm_main_informal} is an immediate consequence of the following lemma.
-
-%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2.$$
-%{\cor may be able to get a better bound, but the statement will be long}
-
-\begin{lemma}%[Theorem \ref{thm_main_informal} restated]
-\label{thm_model_shift}
-%For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other.
-Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2} with $\sigma_1^2=\sigma_2^2=\sigma^2$. Then with high probability, we have
-	\begin{align}
-	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta(\hat v), \label{upper}\\
-		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta(\hat v), \label{lower}
-	\end{align}
-	where
-	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
-		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{( \hat v^2 a_1 M^{\top}M +  a_2\id)^{-1}} } \label{Deltavarv} \\
-		\Delta_{\bias} &\define (\beta_1 - \hat{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi (\hat v)\Sigma_1^{1/2} (\beta_1 - \hat{v}\beta_2). \label{Deltabetav}
-	\end{align}
-\end{lemma}
-
-The proof of Lemma \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z_1$: for any constant $\e>0$, we have
-\begin{align}
-\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq {n_1^{-1}}{Z_1^T Z_1}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e}) \quad \text{w.h.p.}  \label{eq_isometric}
-\end{align}
-%with high probability. 
-In fact, $n_1^{-1}Z_1^TZ_1$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}.
-The estimate \eqref{eq_isometric} provides tight bounds on the concentration errors, and it will be formally proved in Lemma \ref{SxxSyy} below.
-
-%\begin{remark}
-The main error $\delta$ in Lemma \ref{thm_model_shift} comes from approximating $n_1^{-1}Z_1^TZ_1$ by $\id$ using \eqref{eq_isometric}; see the estimate \eqref{bounddelta-} below.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
-$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  \hat{v}^2 .$$
-In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ have been studied in the name of Fisher matrices; see e.g.
-\cite{Fmatrix}.
-However, since $\cal X$ is non-symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix literature, and the study of the singular values of $\cal X +\hat v^2$ will be even harder.
-We leave this problem to future study.
-%\end{remark}
-
-\begin{proof}[Proof of Lemma \ref{thm_model_shift}]
-%\noindent
-%To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
-%$$Q= \Sigma_1^{1/2}  Z_1^{\top} Z_1 \Sigma_1^{1/2}  + \Sigma_2^{1/2}  Z_2^{\top} Z_2 \Sigma_2^{1/2} ,$$
-%where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X_1=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X_2=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
-%\begin{equation}\label{eq_12moment} %\label{assm1}
-%\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
-%\end{equation}
-%\todo{A proof outline; including the following key lemma.}
-By \eqref{eq_te_model_shift} and \eqref{eq_te_var}, we can write
-\begin{align*}
-L(\hat{\beta}_t^{\STL}) - L(\hat{\beta}_t^{\MTL})=\delta_{\vari}(\hat v) - \delta_{\bias}(\hat v), 
-\end{align*}
-where we denote
-\begin{align*}
-\delta_{\vari}(\hat v)&=\sigma^2 \left(  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} -  \bigtr{( \hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}\right), 
-\end{align*}
-and
-\begin{align}\label{revise_deltabias}
- \delta_{\bias}(\hat v)&= \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2.
-\end{align}
-We introduce the notation $\hat M \equiv \hat M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for $v\in \R$. Then the proof is divided into the following four steps. 
-\begin{itemize}
-\item[(i)] We first consider $ \hat M(v)$ for a fixed $v\in \R$.
-Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
-%$$\sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}},\quad \sigma^2 \cdot \bigtr{({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2},$$
-%and the difference between them
-
-\item[(ii)] Using the approximate isometry property of $Z_1$ in \eqref{eq_isometric}, we will approximate the bias term $ \delta_{\bias}(v)$ by
-%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - {v} \beta_2)}^2$$
-%through 
-\be\label{deltabetapf}
-\wt\delta_{\bias}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_1 (\beta_1 - {v} \beta_2)}^2.\ee
-
-\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\bias}$ term.
-
-\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\hat M(\hat v)$ for a possibly random $\hat v$ which depends on $Y_1$ and $Y_2$.
-\end{itemize}
-
-\paragraph{Step I: Variance reduction.} Consider $\hat M(v)$ for a fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$,  
-$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
-and 
-$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{( a_1(v) \hat M^{\top}\hat M + a_2(v)\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
-with high probability, where $a_1(v)$ and $a_2(v)$ satify \eqref{eq_a12extra} with $\hat v$ replaced by $v$. The subtraction of these two terms gives 
-\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
-\ee 
-where $\Delta_{\vari}(v)$ is defined as in \eqref{Deltavarv} but with $\hat v$ replaced by $v$.
-
-\paragraph{Step II: Bounding the bias term.}
-Next we use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$. %in \eqref{deltabetapf}.  
-%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
-\begin{claim}\label{prop_model_shift}
-	In the setting of Lemma \ref{thm_model_shift},
-	we denote $K(v) := (v^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, and
-	\begin{align*}
-		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_1 - v\beta_2)}^2, \\
-		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
-		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K(v) \Sigma_2 K(v) \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
-	\end{align*}
-	Then we have w.h.p.
-	\begin{align*}
-		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}(v).
-	\end{align*}
-%	We have that
-%	\begin{align*}
-%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
-%		\le  \delta_1 - \delta_2
-%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
-%	\end{align*}
-%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
-%	\begin{align*}
-%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
-%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \beta_2)}^2.
-%	\end{align*}
-\end{claim}
-
-\begin{proof}
-	%The proof follows by applying equation \eqref{eq_isometric}.
-	%Recall that $X_1^{\top}X_1 = \Sigma_1^{1/2}Z_1^{\top}Z_1\Sigma_1^{1/2}$.
-We can calculate that
-%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_1 - \hat{w}\beta_2)}^2$.
-	%We have
-	\begin{align}
-%		& \bignorm{\Sigma_2^{1/2}(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \hat{w}\beta_2)}^2 \nonumber \\
-		 \delta_{\bias}(v)-\wt\delta_{\bias}(v)&= {2v^2n_1}(\beta_1 - v\beta_2)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_1 - v\beta_2) \nonumber
-		\\
-		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2. \label{eq_lem_model_shift_1}
-%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
-	\end{align}
-	where we denote $\cE: = Z_1^{\top}Z_1 - {n_1}\id$. 
-  Using \eqref{eq_isometric}, we can bound  
-	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{w.h.p.}$$
-	Thus we can estimate that 
-	\begin{align*}
-	| \delta_{\bias}(v)-\wt\delta_{\bias}(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-	& \le v^2 n_1^2 \left[ \al_+^2(\rho_1) + \OO(p^{-1/2+\e}) -1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2,
-	\end{align*}
-	which concludes the proof by the definition of $\delta_{err}$.	
-%	we can bound the second term on the RHS of equation \eqref{eq_lem_model_shift_1} as
-%	\begin{align*}
-%		& \bigabs{(\beta_1 -  \beta_2)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - v\beta_2)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
-%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}}} \\
-%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2) (\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \\
-%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \hat{w}\beta_2)(\beta_1 - \hat{w}\beta_2)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
-%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 - \hat{w}\beta_2)}^2 \tag{since the matrix inside is rank 1}
-%	\end{align*}
-%	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
-%	\begin{align*}
-%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2
-%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 -  \beta_2)}^2.
-%	\end{align*}
-%	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
-%	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
-%	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
-\end{proof}
-Note by \eqref{eq_isometric}, we also obtain that with high probability,
-\begin{align*}
-&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} =n_1^2 \hat M (\hat M^\top Z_1^\top Z_1 \hat M + Z_2^\top Z_2)^{-2}\hat M^\top \\
-&\preceq  n_1^2 \hat M \left[n_1 \al_-(\rho_1)\hat M^\top \hat M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^{-2}\hat M^\top \\
-&\preceq  \left[ \al_-^2(\rho_1) \hat M\hat M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + \left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\hat M \hat M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
-&\preceq [\al_-^2(\rho_1) \lambda_{\min}^2(\hat M)]^{-1}\cdot (1 - c)
-\end{align*}
-for a small enough constant $c>0$. Together with Claim \ref{prop_model_shift}, we get that with high probability,
-\be\label{bounddelta-}
-\left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
-		\le (1-c) \delta(v)
-\ee
-for some small constant $c>0$, where recall that $\delta(v)$ was defined in \eqref{eq_deltaextra}.
-
-\paragraph{Step III: The limit of $\wt\delta_{\bias}(v)$.} 
-Using Lemma \ref{lem_cov_derivative}, we obtain that with high probability,
-\begin{align*}
-\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 +  a_3(v))\id +v^2 a_4(v) {M}^{\top}{M}}{( v^2 a_1(v) {M}^{\top}{M}+a_2(v) )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
-&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi(v) \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
-\end{align*}
-where $a_3(v)$ and $a_4(v)$ satify \eqref{eq_a34extra} with $\hat v$ replaced by $v$, and $\Pi$ was defined in \eqref{defnpihat}.
-Together \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that w.h.p.,
-\be\label{dicho_varbeta}
-\begin{cases}\delta_{\vari}(v)>\delta_{\bias}(v), & \text{ if } \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \ge   \delta(v),\\
-\delta_{\vari}(v)<\delta_{\bias}(v),  & \text{ if }  \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \le -  \delta(v).\end{cases}
-\ee
-
-\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result \eqref{dicho_varbeta} to $v=\hat v$, which is random and depends on $X_1$ and $X_2$.
-We first show that for any fixed constant $C_0>0$, there exists a high probability event $\Xi$ on which \eqref{dicho_varbeta}
-%\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} 
-holds uniformly for all $v\in [-C_0, C_0]$. In fact, we first consider $v$ that belongs to a discrete set 
-$$V:=\{v_k = kp^{-1}: -(C_0p +1)\le k \le C_0p +1\}.$$
-Then using the arguments for the first three steps and a simple union bound, we get that
-\eqref{dicho_varbeta} holds simultaneously for all $v\in V$ with high probability. On the other hand, by \eqref{eq_isometric} the event
-$$\Xi_1:=\left\{ \al_-(\rho_1)/2 \preceq  \frac{Z_1^T Z_1}{n_1}  \preceq   2\al_+(\rho_1) ,\  \al_-(\rho_2)/2 \preceq  \frac{Z_2^T Z_2}{n_2}  \preceq   2\al_+(\rho_2)\right\}$$
-holds with high probability. Now it is easy to check that on $\Xi_1$, the following estimates holds simultaneously for all $v_k \le v\le v_{k+1}$:
-\begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|\lesssim p^{-1}\delta_{\vari}(v_k),\ \ |\delta_{\bias}(v) -\delta_{\bias}(v_k)|\lesssim p^{-1}\delta_{\bias}(v_k), \ \   |\delta(v)-\delta(v_k)|\lesssim p^{-1}\delta(v_k),\\
-& |\Delta_{\bias}(v) -\Delta_{\bias}(v_k)|\lesssim p^{-1}\Delta_{\bias}(v_k),\ \ |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|\lesssim p^{-1}\Delta_{\vari}(v_k).
-\end{align*}
-Then a simple application of triangle inequality gives that the event 
-$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }-C_0\le v \le C_0\}$$
-holds with high probability. On the other hand, on $\Xi_1$ it is easy to check that for any small constant $\e>0$, there exists a large enough constant $C_0>0$ depending on $\e$ such that
-\begin{align*}
-& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e\delta_{\vari}(C_0),\quad |\delta_{\bias}(v) -\delta_{\bias}(C_0)|\le \e\delta_{\bias}(C_0), \quad  |\delta(v)-\delta(C_0)|\le \e\delta(C_0),\\
-& |\Delta_{\bias}(v) -\Delta_{\bias}(C_0)|\le \e\Delta_{\bias}(C_0),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e\Delta_{\vari}(C_0),
-\end{align*}
-for all $v\ge C_0$.
-Similar estimates hold for $v\le -C_0$ if we replace $C_0$ with $-C_0$ in the above estimates.
-Together with the estimate at $\pm C_0$, we get that \eqref{dicho_varbeta} holds simultaneously for all $v\in \R$ on the high probability event $\Xi_1\cap \Xi_2$.
-This concludes the proof of Lemma \ref{thm_model_shift}, since $\hat v$ must be one of the real values.
-\end{proof}
-
-\subsection{Proof Overview for the Random Matrix Results}
+\subsection{The Bias and Variance Asymptotics}
 Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.

### 2020-09-10 arxiv/transfer.tex
reorg

@@
-\section{Illustrative Examples in an Isotropic Setting}\label{sec_special}
-
-%We provide precise explanations to the phenomena of negative transfer in multi-task learning.
-%We provide tight bounds on the bias and variance of the multi-task estimator for two tasks.
-%The results in Section \ref{sec_general} show when multi-task learning outperforms single-task learning for general task covariance matrices and ground truth model parameters.
-%In particular, the general conditions depend on specific properties of task data such as the covariate shift matrix.
-%However, the conditions given by the limiting bias and variance of multi-task learning can be difficult to interpret.
-%The goal of this section is to address this issue.
-%We interpret the limiting bias and variance equations in an isotropic covariance setting that is described below and a simplified covariate-shifted setting.
-%We show that three properties of task data affect the performance of multi-task learning as follows.
-%(i) \textit{Task similarity}: We explain the phenomenon of negative transfer precisely as tasks become more different.
-%(ii) \textit{Sample ratio}: We further explain a curious phenomenon where increasing the sample ratio between the source and target task helps initially, but hurts eventually.
-%(iii) \textit{Covariate shift}: Finally, we show that as the sample size of the source task increases, we show that the covariate shift worsens the performance of the multi-task estimator.
-%Finally, we provide a extend our results from two tasks to many tasks with the same features.
-%We explain from three perspectives, including \textit{task similarity}, \textit{sample size} and \textit{covariate shift}.
-%We show how negative transfer occurs by varying task similarity or sample size.
-%Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-We illustrate our main results (to be described in Section \ref{sec_general}) in a simplified setting.
-For this setting, we simulate several empirical phenomena that are well-known in hard parameter sharing approaches.
-We use our results to explain the empirical phenomena.
-
-%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%	For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%	We assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in Appendix \ref{sec_maintools}.
-
-%In the isotropic model, we show that as we increase the distance between $\beta_1$ and $\beta_2$ (or $d$), there is a transition from positive transfer to negative transfer in MTL.
-%We measure model dissimilarity as $\norm{\beta_1 - \beta_2}^2$, which is the distance between source and target in the isotropic model.
-%Figure \ref{fig_model_shift} provides a simulation when $p = 200$.
-%{The rest of parameter settings can be found in Appendix \ref{app_synthetic}.}
-%Our result below will provide an explanation to this phenomenon.
-%Based on Theorem \ref{thm_model_shift}, we derive the transition threshold in the following proposition.
-%We introduce the following notations.
-%{\begin{align*}
-%	\Psi(\beta_1, \beta_2) = {\ex{\bignorm{\beta_1 - \beta_2}^2}} / {\sigma^2},  \quad \Phi(\rho_1, \rho_2) = \frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}.
-%\end{align*}}
-
-\subsection{Negative Transfer}
-
-\noindent\textbf{Isotropic features and models.}
-	Imagine that we have two tasks and the covariates of both tasks have isotropic covariance matrices.
-%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
-	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
-	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
-	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
-	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
-
-\begin{example}[Varying model distance]
-\end{example}
-
-Using our techniques described later in Section \ref{sec_general}, we derive the limiting prediction loss of the hard parameter sharing estimator.
-Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
-
-\begin{corollary}[Derived from Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}]
-	In the isotropic setting described above, with high probability, the prediction loss of the hard parameter sharing estimator for task two satisfies:
-	\begin{align*}
-		& \bigabs{ L(\hat{\beta}_2^{\MTL}) - \frac{\sigma^2}{\rho_1 + \rho_2 - 1} - (1 + \frac{6}{\rho_1} + \frac{1}{\rho_1^2})pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} } \\
-		\le & 	\frac{4}{\sqrt{\rho_1}}(1 + \frac{1}{\rho_1})	pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} + \oo(\sigma^2 + pd^2).
-%	 \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4  +\oo(\sigma^2 + pd^2)  \le \\
-%	 \le  \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\oo(\sigma^2 + pd^2)
-	 \end{align*}
-\end{corollary}
-
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the following simplified setting, where we can perform explicit calculations.
-We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
-In particular, the bias of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases.
-Therefore, while the variance of MTL still reduces compared to STL, if the bias increases more than the amount of variance reduced, we will observe negative transfer.
-
-\begin{proposition}[Task model distance]\label{prop_dist_transition}
-	In the isotropic model, suppose that $\rho_1$ and $\rho_2 > 1$.
-	Then
-	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-	Here {\small$\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$}.
-	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
-\end{proposition}
-
-Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
-Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
-%Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
-We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
-%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
-%Figure \ref{fig_model_shift} shows the result.
-%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-The proof of Proposition \ref{prop_dist_transition} involves two parts.
-First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
-A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
-thus simplifying the general condition in Theorem \ref{thm_main_informal}.
-
-\begin{figure}[!t]
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-		\caption{Task similarity}
-		\label{fig_model_shift}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
-		\caption{Sample size}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
-		\caption{Covariate shift}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
-	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
-	The $y$-axis measures the loss of STL minus MTL.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
-
-%\subsection{Sample Ratio}\label{sec_data_size}
-
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
-%More generally, such results are still applicable when all task data are being added simultaneously.
-On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
-For such settings, we have also observed that adding more labeled data from one task does not always help.
-%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-In the isotropic model, we consider what happens if we vary the source task sample size.
-Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-Figure \ref{fig_size} provides a simulation result for such a setting.
-We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-
-\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
-	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-	Then we have that
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
-		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-\end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
-We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-There are several unexplained observations near $y = 0$ caused by $\nu$.
-The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-
-\subsection{Covariate Shift} \label{sec_covshift}
-So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-In general, the covariance matrices of the two tasks may be different such as in text classification.
-In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
-We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
-
-\noindent\textit{Example.}
-	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$ similar to Theorem \ref{thm_main_informal}.
-	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$ and $\Psi(\beta_1, \beta_2) = 0$.
-	We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	Hence, $\lambda$ measures the severity of the covariate shift.
-	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-
-%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-We compare different choices of $M$ that belong to the following bounded set.
-Let $\lambda_i$ be the $i$-th singular value of $M$.
-Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-{\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
-\end{align*}}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	For the setting of the example above, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
-	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-	We have that
-		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{proposition}
-Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
-The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
-%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
-
-%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
-%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
-%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
-\subsection{Data Efficiency}
-
-observed in Taskonomy \cite{ZSSGM18}.
-
-\section{Main Results for General Features}\label{sec_general}
+\section{Proof Overview}\label{sec_general}
 
@@
 In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
-
-\section{Implication for Mitigating Sample Imbalance and Covariate Shift}
-
-\paragraph{Benefits of multi-task learning.}
-We can in fact extend the result to the cases where the noise variances are different.
-In this case, we will see that MTL is particularly effective.
-%As an extension of Proposition \ref{prop_dist_transition}, we observe that MTL is particular powerful when the labeled data of the source task is less noisy compared to the target task.
-Concretely, suppose the noise variance $\sigma_1^2$ of task $1$ differs from the noise variance $\sigma_2^2$ of task $2$.
-If $\sigma_1^2$ is too large, the source task provides a negative transfer to the target.
-If $\sigma_1^2$ is small, the source task is more helpful.
-We leave the result to Proposition \ref{prop_var_transition} in Appendix \ref{app_proof_31}.
-Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$.
-In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.
-
-\begin{proposition}[Label denoising]
-\label{prop_var_transition}
-	In the isotropic model, assume that $\rho_1 > 40$ and $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$.
-	Then we have the following transition with respect to $\sigma_1^2$:
-	\begin{itemize}
-		\item If $\sigma_1^2 < - \nu^{1/2} \rho_1 \cdot p d^2+\left(1+ \nu^{-1/2}\rho_1 \Phi(\rho_1, \rho_2)\right)\cdot\sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL})$.
-		\item If $\sigma_1^2 > -\nu^{-1/2}\rho_1\cdot p d^2   +\left(1+ \nu^{1/2}\rho_1\Phi(\rho_1, \rho_2)\right) \cdot \sigma_2^2$, then w.h.p. $\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL})$.
-	\end{itemize}
-\end{proposition}
-As a corollary, if $\sigma_1^2 \le \sigma_2^2$, then we always get positive transfer.
-
-We use our tools to explain a key result of Taskonomy by Zamir et al. \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
-%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
-For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using $x \cdot n_i$ datapoints from every task. The data efficiency ratio is defined as
-{\small\[ \argmin_{x\in(0, 1)} ~~
-		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
-		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]}
-For example, the data efficiency ratio is $1$ if there is negative transfer.
-Using our tools, we show that in the isotropic model, the data efficiency ratio is
-roughly
-{\small\[ \frac{1}{\rho_1 + \rho_2} {+ \frac{2}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]}%
-Compared with Proposition \ref{prop_dist_transition}, we see that when $\Psi(\beta_1, \beta_2)$ is smaller than $\rho_1^{-1} + \rho_2^{-1}$ (up to a constant multiple), the transfer is positive.
-Moreover, the data efficiency ratio quantifies how effective the positive transfer is using MTL.
-%In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
-
-Next we state Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
-Its proof can be found in Appendix \ref{app_proof_32}.
-%In the statement, we shall denote the data efficiency ratio as $\al^\star$.
-
-\begin{proposition}[Labeling efficiency]
-\label{prop_data_efficiency}
-	In the isotropic model, assume that $\rho_1,\rho_2 \ge 9$ and $\Psi(\beta_1, \beta_2) < (5(\rho_1-1))^{-1} + (5(\rho_2-1))^{-1}$.
-	Then the data efficiency ratio $x^\star$ satisfies
-	\be\label{eq_uplowx} x_l  \le x^\star\le \frac{1}{\rho_1 + \rho_2} \bigbrace{  \frac{2}{(\rho_1-1)^{-1} + (\rho_2-1)^{-1} - 5\Psi(\beta_1, \beta_2)}+1}, \ee
-	where we denoted
-	$$x_l:= \frac1{\rho_1+\rho_2}\left(\frac{2}{(\rho_1-1)^{-1}+(\rho_2 -1)^{-1}}+1\right).$$
-\end{proposition}
-
-\paragraph{Algorithmic consequence.}
-
-\noindent\textit{Detecting negative transfer.}
-Inspired by the observation, we propose a single-task based metric to help understand MTL results using STL results.
-\squishlist
-	\item For each task, we train a single-task model.
-	Let $z_s$ and $z_t$ be the prediction accuracy of each task, respectively.
-	Let $\tau\in(0, 1)$ be a fixed threshold.
-	\item If $z_s - z_t > \tau$, then we predict that there will be positive transfer when combining the two tasks using MTL.
-	If $z_s - z_t < -\tau$, then we predict negative transfer.
-\squishend
-
-\noindent\textit{Mitigating negative transfer.}
-An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
-In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-\squishlist
-	\item We divide the source task data into $S$ batches.
-	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
-	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
-	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\squishend
-
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-\noindent\textit{Covariance alignemnt.}
-Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
-Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
-The idea is to add an alignment module between the input and the shared module $B$.
-This new module is then trained together with $B$ and the output layers.
-We validate our insight on this procedure in the experiments.

### 2020-09-10 arxiv/setup.tex
update
edit wip

@@
-\section{Problem Formulation and Related Work}
+\subsection{Setup and Main Results}
 \label{sec_prelim}
@@
 
-\subsection{Problem Formulation}
+%\subsection{Problem Formulation}
 
@@
 
-\paragraph{Notations.}
-Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
-Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
-For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
-We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-%\subsection{Bias and Variance}
-
-%\noindent\textbf{Positive/Negative transfer.}
-
 %This part introduces a positive variance reduction effect from adding the source labels.
@@
 To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
+
+\paragraph{Organizations.}
+\todo{revise} The appendix is organized as follows.
+In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
+In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
+In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
+In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
+In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
+Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.
+
+\section{Preliminaries}
+
+\paragraph{Notations.}
+Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
+For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
+%\subsection{Bias and Variance}
+
+%\noindent\textbf{Positive/Negative transfer.}

### 2020-09-11 arxiv/intro.tex
revision

@@
 
-\section{Introduction}
+\section{Introduction}\label{sec introduction}
 
@@
 Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-\paragraph{Organizations.}
-\todo{revise} The appendix is organized as follows.
-In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
-In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
-In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
-In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
-In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
-Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.

### 2020-09-11 arxiv/setup.tex
edits

@@
 
-\paragraph{Notations.}
+\subsection{Notations}
 Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
@@
 %\noindent\textbf{Positive/Negative transfer.}
+
+\subsection{Hard Parameter Sharing}
+
+\subsection{Bias and Variance}
+
+\subsection{Random Matrices}

### 2020-09-11 arxiv/transfer.tex
update
edit wip
edits

@@
-\section{Proof Overview}\label{sec_general}
+\section{Proof Overview of Main Results}\label{sec_general}
 
@@
 %\end{proposition}
-In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
-First, we consider the two-task case.
-We provide precise asymptotics of the bias and variance of the multi-task learning estimator.
-We apply recent developments from the random matrix theory literature to characterize the bias and variance.
-The results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties (Section \ref{sec_special}).
-Second, we consider the multiple-task case where all tasks have the same features but different labels.
-We extend the bias-variance decomposition of the two-task case to this setting and show qualitatively similar results.
+We describe the main ideas for showing the generalization error of hard parameter sharing estimators.
+There are two key ideas in the proof.
+First, we study a bias-variance decomposition of hard parameter sharing, and show that the variance always reduces compared to single-task learning, while the bias always increases.
+Second, we study the limiting bias and variance of hard parameter sharing, and derive their asymptotics using recent development from the random matrix theory literature.
+The asymptotic results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties, which will be the focus of Section \ref{sec_special}.
+%In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
+%First, we consider the two-task case.
+%We provide precise asymptotics of the bias and variance of the multi-task learning estimator.
+%We apply recent developments from the random matrix theory literature to characterize the bias and variance.
+%The results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties (Section \ref{sec_special}).
+%Second, we consider the multiple-task case where all tasks have the same features but different labels.
+%We extend the bias-variance decomposition of the two-task case to this setting and show qualitatively similar results.
 %For the single-task learning estimator, there are well-known results that relate its prediction loss to sample size and noise variance.
@@
 
-\paragraph{Same covariates.}
+\subsection{Same Covariates}
 %A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
@@
 
-\paragraph{Different covariates: the two-task case.}
+\subsection{Different Covariates: The Two-task Case}
 As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.

### 2020-09-11 arxiv/proof_main.tex

@@
 \medskip
-\noindent\textbf{Defining the resolvents.} For our purpose, we introduce a convenient self-adjoint linearization trick,
+\noindent\textbf{Defining the resolvents.} For our purpose, we introduce a convenient \alert{self-adjoint linearization trick}\HZ{what does this trick mean? use less technical words},
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
@@
 $$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
- We will consistently use the latin letters $i,j\in\sI_{0}$, greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$, and $\fa,\fb,\mathfrak c\in \cal I$.
+ We will consistently use the latin letters $i,j\in\sI_{0}$, greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$, and $\fa,\fb,\mathfrak c\in \cal I$ \HZ{This $\fa, \fb$ notation is ugly.
+Why not just use $a,b$?}.
 Correspondingly, the indices of the matrices $Z_1$ and $Z_2$ are labelled as
@@
 \end{definition}
-With Schur complement formula, we can check that
+With Schur complement formula, we can check that \HZ{Has $G(z)$ been defined before?}
  \begin{equation} \label{green2}
@@
  where we abbreviated $W:=n^{-1/2}(\Lambda U^\top Z_1^\top, V^\top Z_2^\top)$.
-This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
+\HZ{$W$ is overloaded with the output layers} This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
 On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
@@
 Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
-Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.
+\alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
 

### 2020-09-11 arxiv/proof_main.tex
more comment
edit

@@
 Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $(X_1^\top X_1+X_2^\top X_2)^{-1}$ for $X_1= Z_1\Sigma_1^{1/2}$ and $X_2= Z_2\Sigma_2^{1/2}$.
+\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
 Suppose $M=\Sig_1^{1/2} \Sig_2^{-1/2}$ has a singular value decomposition
@@
  Using Schur complement formula (see {equation} (\ref{resolvent2})), we have that %for $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\HZ{This part needs more explanation - cannot understand.}
 \begin{align}

### 2020-09-11 arxiv/proof_main.tex
restructure

@@
 
-\subsection{The Multiple-task Case}\label{app_proof_many_tasks}
-
-	First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
-	Recall that all tasks have the same covariates in this setting.
-	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
-	\begin{align}
-		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
-	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
-	\begin{align*}
-		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
-		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
-	\end{align*}
-	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} by a decomposition of the expected prediction loss over the random noise condition on $X$ as follows
-	\begin{align}
-		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \nonumber \\
-		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \nonumber \\
-		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
-		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \nonumber \\
-		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
-		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}. \label{eq_ex_pred}
-	\end{align}
-	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-	The last step uses the fact that $\sum_{i=1}^t W_i W_i^{\top} = \cW \cW^{\top}$.
-	One can see that the first part of the last equation is the bias and the second part is the variance.
-	Hence the proof is complete.
-
-	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we also obtain the objective $g(\cW)$.
-	\begin{align}
-		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2.
-\label{eq_mtl_output_layer}
-	\end{align}
-	Now we are ready to prove Theorem \ref{thm_many_tasks}.
-	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.
-
-%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
-Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
-The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
-
-%In this section we consider the setting with $k$ many that have the same covariates.
-%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
-
-\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.
-	In order to derive the minimizer, our proof involves two steps.
-	First, we consider the expectation of $g(\cW)$ over $\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t$, and $X$.
-	We show that the minimizer of $\ex{g(\cW)}$ has a simple closed form solution similar to principal component analysis.
-	Second, we show that the concentration error between $g(\cW)$ and $\ex{g(\cW)}$ is small provided with $n$ samples.
-	Intuitively, this is because $\cW$ only has $r \times t$ parameters, which is much smaller than $n$ by our assumption.
-	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
-	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
-	\begin{align*}
-		g_0(\cW) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-		g_1(\cW) &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
-		&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-		g_2(\cW) &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
-		&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
-	\end{align*}
-	For the second equation of $g_1(\cW)$, we use the fact that
-		\[ \sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}. \]
-	For the second equation of $g_2(\cW)$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id_{r\times r}$ and rearrange the terms.
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
-
-	\medskip
-	\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
-	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
-	\begin{align}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - g_0(\cW)
-		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cW) \mid X}
-		%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-		= \sigma^2(n\cdot t - p\cdot r) \nonumber
-	\end{align}
-	%	\begin{align}
-	%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
-	%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
-	%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
-	%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
-	%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
-	%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
-	%	\end{align}
-	The first equation uses the same fact the expectation of $g_1(\cW)$ over the random noise is zero.
-	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$, and
-		\[ \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}
-			= \id_{r\times r} = r. \]
-	%\be\nonumber
-	%g(\cal W)= g_0 + 2g_1 + g_2,
-	%\ee
-	%where
-	%\begin{align*}
-	%	g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-	%	g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
-	%			%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-	%	g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
-	%				\end{align*}
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
-	%\medskip
-	%\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
-	%We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	%First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
-	%\begin{align*}
-	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W)
-	%	+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
-	%	&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
-%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-	%	&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
-	%\end{align*}
-%	\begin{align}
-%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
-%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
-%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
-%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
-%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
-%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
-%	\end{align}
-	%where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
-	%the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.
-	We further take expectation over $X$ for $g_0(\cW)$ and obtain the following:
-	\begin{align*}
-		\ex{g(\cW)} = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 (n\cdot t - p \cdot r).
-	\end{align*}
-	%\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
-\iffalse
-{\color{red}
-\begin{align*}
-	f(W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X \hat B W_i - Y_i}^2 = \val(\cal W) \cdot \left( 1+\OO(p^{-1/2+\e})\right),
-\end{align*}
-where
-\begin{align*}
-	 \val(\cal W) &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \E_{\e_i:1\le i \le t}\sum_{i=1}^t\left\| X(X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}W_i -\e_i\right\| \\
-	 &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \sigma^2 (nt-pr).
-\end{align*}
-
-}
-\fi
-%Here $\val(\cal W)$ is defined as
-%it remains to consider minimizing the validation loss
-%	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari} ,$$
-%where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
-%	\begin{align*}
-%		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
-%	\end{align*}
-%	and the variance term $\delta_{\vari} $ can be calculated as
-%	\begin{align*}
-%		\delta_{\vari} := \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-%	\end{align*}
-	One can see that the above equation provides a bias-variance decomposition of $\ex{g(\cW)}$.
-	The first part measures the bias of multi-task learning compared to single-task learning for all tasks.
-	The second part measures the variance of multi-task learning and scales with $\sigma^2$.
-	In order to minimize $\ex{g(\cW)}$, it suffices to minimize the bias equation over $\cal W$, since the variance equation does not depend on $\cal W$.
-	%We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{t\times t}$, whose $(i,j)$-th entry is given by $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
-	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-	%Now we can write $\delta_{\bias}(\cal W)$ succinctly as
-	%\begin{align*}
-	%	\delta_{\bias}(Q) \equiv \delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  %\bigbrace{Q -\id}}^2 .
-	%\end{align*}
-	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to ${B^{\star}}^{\top} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
-
-	\medskip
-	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
-	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
-
-	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
-	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
-	%and
-	%\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
-	%&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
-	%\end{align*}
-	Applying the above estimates into $g_1(\cW)$, we get that
-	\begin{align}
-	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
-	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
-	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
-	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
-	\end{align}
-	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
-	In the last step, we use the AM-GM inequality.
-
-	Second, for $g_2(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for any $1\le i, j \le t$, the following holds with high probability:
-	\begin{align*}
-		\bigabs{\norm{\varepsilon_j}^2 - \ex{\norm{\varepsilon_j}^2}} &\le \sigma^2 p^{1/2+\e},\\
-		%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
-		\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
-		&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
-  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
-	\end{align*}
-	Combining the above two inequalities together, we get that with high probability
-	\begin{align}
-		\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_est_g2}
-	\end{align}
-
-	Finally, for $g_0(\cW)$, denote by $v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right)$, for any $j = 1,\dots,t$, we have that $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
-%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
-	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}.
-	Hence by law of large numbers, we have that with high probability
-	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1+\oo(1))$,
-	which implies that
-	\begin{align}
-		g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)). \label{eq_est_g0}
-	\end{align}
-
-	Combining equation \eqref{eq_est_g1}, \eqref{eq_est_g2}, and \eqref{eq_est_g0}, we obtain that with high probability
-	\begin{align}
-	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
-	&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
-	\end{align}
-
-%	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
-%	where the second part follows by using Cauchy-Shwartz inequality.
-
-	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
-	%\begin{align}
-	%	g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
-	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
-	%\end{align}
-	%Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.
-
-	%For equation \eqref{approxvalid_1}, we observe that the summands of $g(\cW)$ w.r.t. $\varepsilon_1, \dots, \varepsilon_t$ belong to either of the following three types:
-	%\begin{enumerate}
-	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i$, for any $i = 1,\dots, t$ and a fixed $A\in\real^{n\times n}$ that is independent of $\varepsilon_i$;
-	%	\item[(ii)] $\varepsilon_i^{\top} A \varepsilon_j$, for any $i \neq j$ and a fixed $A$ that is independent of both $\varepsilon_i$ and $\varepsilon_j$;
-	%	\item[(iii)] $\varepsilon_i^{\top} A$, for any $i = 1,\dots, t$ and a fixed $A\in\real^n$ that is independent of $\varepsilon_i$.
-	%\end{enumerate}
-	%For all three types, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
-	%\begin{enumerate}
-	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i = \sigma^2 (1 + \OO(p^{-1/2 + c})) \normFro{A}^2$;
-	%	\item[(ii)] $\abs{}$
-	%	\item[(iii)]
-	%\end{enumerate}
-
-	%We use the fact that our random vectors have i.i.d. entries.
-%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-	%Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + %\wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite %\eqref{eq_mtl_2tasktilde} as
-%$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat %B w_i-\beta_i.$$
-	%Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration result,  to get that for any constant $\e>0$,
-	%\begin{align*}
-		%\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  %- \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
-%&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
-	%$\end{align*}
-	%with high probability. Thus we obtain that
-	%$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
-%where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
-	% again the concentration result, Lemma \ref{largedeviation}, we get that
-	%$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
-%with high probability.
-%-----old-------
-%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-%\begin{align}
-%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
-%\end{align}
-%\nc
-%------------------
-%Thus we conclude the proof.
-
-	\medskip
-	\noindent\textbf{Dealing with the empirical minimizer.}
-	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
-	We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
-	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
-	Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
-		&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
-	\end{align*}
-	On the other hand, by equation \eqref{eq_est_g} and triangle inequality, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{\cW})}) + \bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le o(n) \cdot \sigma_{\max}({B^{\star}}^{\top} \Sigma B^{\star}) + O(\sigma^2 p^{1/2 +\e}).
-	\end{align*}
-	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish to $o(1)$ as $p$ grows.
-	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
-	%In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
-	%$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
-	%where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
-
-	\medskip
-	\noindent\textbf{Putting all parts together.}
-	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
-	Now we are ready to finish the proof.
-	Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
-	\begin{align}
-		L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
-	\end{align}
-	Using equation \eqref{eq_ex_pred}, we have that
-	\begin{align}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
-		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
-	\end{align}
-	In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
-	\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
-\]
-  In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
-	Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
-\end{proof}
-%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
-%\begin{itemize}
-%	\item The de-noising effect of multi-task learning.
-%	\item Multi-task training vs single-task training can be either positive or negative.
-%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
-%\end{itemize}
+%\subsection{The Multiple-task Case}\label{app_proof_many_tasks}
 

### 2020-09-11 arxiv/setup.tex
restructure

@@
-\subsection{Setup and Main Results}
-\label{sec_prelim}
-
-We begin by defining our problem setup including the multi-task estimator we study.
-Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
-%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
-
-%\subsection{Problem Formulation}
-
-\todo{Consider adding some motivation later.}
-
-\noindent\textbf{Data model.}
+\paragraph{Linear models.}
 Suppose we have $t$ labeled regression tasks. %where $t$ is a fixed value that does not grow with the feature dimension $p$.
@@
 
-We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.
-First, for every entry of $z_i$, we assume that its $(4+\e)$-th moment exists, that is, there exist constants $\e, C > 0$ such that
-\begin{equation}\label{assmAhigh}
-	\ex{\abs{z_{i,j}}^{4+\e}} \le C,\ 1\le j \le p.
-\end{equation}
-Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
-This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
-Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check}, the $l$-th moment of the noise entries exists:
-\begin{align*}
-	\ex{\abs{\varepsilon_{k, j}}^l \le C}, \text{ for all } j = 1, \dots, n_k.
-\end{align*}
-
-\medskip
-\noindent\textbf{Hard parameter sharing.}
+\paragraph{Hard parameter sharing estimators.}
 We study multi-task learning models that use hard parameter sharing, which is the most commonly used architecture in practice \cite{R17}.
@@
 
-\medskip
-\noindent\textbf{Problem statement.}
+\paragraph{Problem statement.}
 %We focus on predicting a particular task, say the $t$-th task, without loss of generality.
@@
 More specifically, we study how varying properties of task data including task similarity, sample ratio, and covariate shift affects information transfer in multi-task learning.
+
+\subsection{Summary of Results}
+\label{sec_prelim}
+
+%We begin by defining our problem setup including the multi-task estimator we study.
+%Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
+%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
+
+%\subsection{Problem Formulation}
 
@@
 \subsection{Random Matrices}
+
+We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.
+First, for every entry of $z_i$, we assume that its $(4+\e)$-th moment exists, that is, there exist constants $\e, C > 0$ such that
+\begin{equation}\label{assmAhigh}
+	\ex{\abs{z_{i,j}}^{4+\e}} \le C,\ 1\le j \le p.
+\end{equation}
+Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
+This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
+Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check}, the $l$-th moment of the noise entries exists:
+\begin{align*}
+	\ex{\abs{\varepsilon_{k, j}}^l \le C}, \text{ for all } j = 1, \dots, n_k.
+\end{align*}

### 2020-09-11 arxiv/transfer.tex
restructure

@@
-\section{Proof Overview of Main Results}\label{sec_general}
+\section{Main Results}\label{sec_general}
 
@@
 The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
+
+	First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
+	Recall that all tasks have the same covariates in this setting.
+	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
+	\begin{align}
+		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
+	\end{align}
+	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
+	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
+	\begin{align*}
+		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
+		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
+	\end{align*}
+	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} by a decomposition of the expected prediction loss over the random noise condition on $X$ as follows
+	\begin{align}
+		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \nonumber \\
+		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \nonumber \\
+		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
+		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \nonumber \\
+		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
+		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}. \label{eq_ex_pred}
+	\end{align}
+	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+	The last step uses the fact that $\sum_{i=1}^t W_i W_i^{\top} = \cW \cW^{\top}$.
+	One can see that the first part of the last equation is the bias and the second part is the variance.
+	Hence the proof is complete.
+
+	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we also obtain the objective $g(\cW)$.
+	\begin{align}
+		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2.
+\label{eq_mtl_output_layer}
+	\end{align}
+	Now we are ready to prove Theorem \ref{thm_many_tasks}.
+	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.
+
+%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
+Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
+The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
+
+%In this section we consider the setting with $k$ many that have the same covariates.
+%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
+%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
+%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
+
+\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
+	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.
+	In order to derive the minimizer, our proof involves two steps.
+	First, we consider the expectation of $g(\cW)$ over $\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t$, and $X$.
+	We show that the minimizer of $\ex{g(\cW)}$ has a simple closed form solution similar to principal component analysis.
+	Second, we show that the concentration error between $g(\cW)$ and $\ex{g(\cW)}$ is small provided with $n$ samples.
+	Intuitively, this is because $\cW$ only has $r \times t$ parameters, which is much smaller than $n$ by our assumption.
+	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
+	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
+	\begin{align*}
+		g_0(\cW) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+		g_1(\cW) &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
+		&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
+		g_2(\cW) &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
+		&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
+	\end{align*}
+	For the second equation of $g_1(\cW)$, we use the fact that
+		\[ \sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}. \]
+	For the second equation of $g_2(\cW)$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id_{r\times r}$ and rearrange the terms.
+	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
+	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
+
+	\medskip
+	\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
+	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
+	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
+	\begin{align}
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - g_0(\cW)
+		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cW) \mid X}
+		%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+		= \sigma^2(n\cdot t - p\cdot r) \nonumber
+	\end{align}
+	%	\begin{align}
+	%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
+	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
+	%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
+	%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
+	%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
+	%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
+	%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
+	%	\end{align}
+	The first equation uses the same fact the expectation of $g_1(\cW)$ over the random noise is zero.
+	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$, and
+		\[ \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}
+			= \id_{r\times r} = r. \]
+	%\be\nonumber
+	%g(\cal W)= g_0 + 2g_1 + g_2,
+	%\ee
+	%where
+	%\begin{align*}
+	%	g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+	%	g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
+	%			%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
+	%	g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
+	%				\end{align*}
+	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
+	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
+	%\medskip
+	%\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
+	%We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
+	%First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
+	%\begin{align*}
+	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W)
+	%	+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
+	%	&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
+%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+	%	&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
+	%\end{align*}
+%	\begin{align}
+%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
+%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
+%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
+%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
+%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
+%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
+%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
+%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
+%	\end{align}
+	%where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
+	%the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.
+	We further take expectation over $X$ for $g_0(\cW)$ and obtain the following:
+	\begin{align*}
+		\ex{g(\cW)} = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 (n\cdot t - p \cdot r).
+	\end{align*}
+	%\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
+\iffalse
+{\color{red}
+\begin{align*}
+	f(W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X \hat B W_i - Y_i}^2 = \val(\cal W) \cdot \left( 1+\OO(p^{-1/2+\e})\right),
+\end{align*}
+where
+\begin{align*}
+	 \val(\cal W) &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \E_{\e_i:1\le i \le t}\sum_{i=1}^t\left\| X(X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}W_i -\e_i\right\| \\
+	 &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \sigma^2 (nt-pr).
+\end{align*}
+
+}
+\fi
+%Here $\val(\cal W)$ is defined as
+%it remains to consider minimizing the validation loss
+%	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari} ,$$
+%where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
+%	\begin{align*}
+%		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
+%	\end{align*}
+%	and the variance term $\delta_{\vari} $ can be calculated as
+%	\begin{align*}
+%		\delta_{\vari} := \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
+%	\end{align*}
+	One can see that the above equation provides a bias-variance decomposition of $\ex{g(\cW)}$.
+	The first part measures the bias of multi-task learning compared to single-task learning for all tasks.
+	The second part measures the variance of multi-task learning and scales with $\sigma^2$.
+	In order to minimize $\ex{g(\cW)}$, it suffices to minimize the bias equation over $\cal W$, since the variance equation does not depend on $\cal W$.
+	%We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{t\times t}$, whose $(i,j)$-th entry is given by $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
+	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
+	%Now we can write $\delta_{\bias}(\cal W)$ succinctly as
+	%\begin{align*}
+	%	\delta_{\bias}(Q) \equiv \delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  %\bigbrace{Q -\id}}^2 .
+	%\end{align*}
+	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to ${B^{\star}}^{\top} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
+
+	\medskip
+	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
+	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
+
+	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
+	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
+	%and
+	%\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
+	%&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
+	%\end{align*}
+	Applying the above estimates into $g_1(\cW)$, we get that
+	\begin{align}
+	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
+	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
+	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
+	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
+	\end{align}
+	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
+	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
+	In the last step, we use the AM-GM inequality.
+
+	Second, for $g_2(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for any $1\le i, j \le t$, the following holds with high probability:
+	\begin{align*}
+		\bigabs{\norm{\varepsilon_j}^2 - \ex{\norm{\varepsilon_j}^2}} &\le \sigma^2 p^{1/2+\e},\\
+		%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
+		\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
+		&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
+  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
+  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
+  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
+	\end{align*}
+	Combining the above two inequalities together, we get that with high probability
+	\begin{align}
+		\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_est_g2}
+	\end{align}
+
+	Finally, for $g_0(\cW)$, denote by $v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right)$, for any $j = 1,\dots,t$, we have that $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
+%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
+	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}.
+	Hence by law of large numbers, we have that with high probability
+	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1+\oo(1))$,
+	which implies that
+	\begin{align}
+		g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)). \label{eq_est_g0}
+	\end{align}
+
+	Combining equation \eqref{eq_est_g1}, \eqref{eq_est_g2}, and \eqref{eq_est_g0}, we obtain that with high probability
+	\begin{align}
+	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
+	&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
+	\end{align}
+
+%	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
+%	where the second part follows by using Cauchy-Shwartz inequality.
+
+	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
+	%\begin{align}
+	%	g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
+	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
+	%\end{align}
+	%Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.
+
+	%For equation \eqref{approxvalid_1}, we observe that the summands of $g(\cW)$ w.r.t. $\varepsilon_1, \dots, \varepsilon_t$ belong to either of the following three types:
+	%\begin{enumerate}
+	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i$, for any $i = 1,\dots, t$ and a fixed $A\in\real^{n\times n}$ that is independent of $\varepsilon_i$;
+	%	\item[(ii)] $\varepsilon_i^{\top} A \varepsilon_j$, for any $i \neq j$ and a fixed $A$ that is independent of both $\varepsilon_i$ and $\varepsilon_j$;
+	%	\item[(iii)] $\varepsilon_i^{\top} A$, for any $i = 1,\dots, t$ and a fixed $A\in\real^n$ that is independent of $\varepsilon_i$.
+	%\end{enumerate}
+	%For all three types, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
+	%\begin{enumerate}
+	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i = \sigma^2 (1 + \OO(p^{-1/2 + c})) \normFro{A}^2$;
+	%	\item[(ii)] $\abs{}$
+	%	\item[(iii)]
+	%\end{enumerate}
+
+	%We use the fact that our random vectors have i.i.d. entries.
+%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+	%Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + %\wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite %\eqref{eq_mtl_2tasktilde} as
+%$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat %B w_i-\beta_i.$$
+	%Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration result,  to get that for any constant $\e>0$,
+	%\begin{align*}
+		%\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  %- \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
+%&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+	%$\end{align*}
+	%with high probability. Thus we obtain that
+	%$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+%where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
+	% again the concentration result, Lemma \ref{largedeviation}, we get that
+	%$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+%with high probability.
+%-----old-------
+%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+%\begin{align}
+%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
+%\end{align}
+%\nc
+%------------------
+%Thus we conclude the proof.
+
+	\medskip
+	\noindent\textbf{Dealing with the empirical minimizer.}
+	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
+	We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
+	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
+	Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
+	\begin{align*}
+		g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
+		&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
+	\end{align*}
+	On the other hand, by equation \eqref{eq_est_g} and triangle inequality, we have that
+	\begin{align*}
+		g(U_r) - g(\hat{\cW}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{\cW})}) + \bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
+		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
+		&\le o(n) \cdot \sigma_{\max}({B^{\star}}^{\top} \Sigma B^{\star}) + O(\sigma^2 p^{1/2 +\e}).
+	\end{align*}
+	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish to $o(1)$ as $p$ grows.
+	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
+	%In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
+	%$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
+	%where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
+
+	\medskip
+	\noindent\textbf{Putting all parts together.}
+	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
+	Now we are ready to finish the proof.
+	Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
+	\begin{align}
+		L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
+	\end{align}
+	Using equation \eqref{eq_ex_pred}, we have that
+	\begin{align}
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
+		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
+	\end{align}
+	In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
+	\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
+\]
+  In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
+	Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
+\end{proof}
+%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
+%\begin{itemize}
+%	\item The de-noising effect of multi-task learning.
+%	\item Multi-task training vs single-task training can be either positive or negative.
+%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
+%\end{itemize}
 

### 2020-09-11 arxiv/intro.tex
wip

@@
 %We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
-
-\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-\squishlist
-	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-Our study also leads to several algorithmic consequences with practical interest.
-First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-Second, we propose a new multi-task training schedule by incrementally adding task data batches to the training procedure.
-This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
-Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis datasets while keeping the accuracy the same.
-Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-Finally, we validate our three theoretical findings on sentiment analysis tasks.

### 2020-09-11 arxiv/proof_main.tex
wip

@@
 
-\subsection{The Bias and Variance Asymptotics}
-Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
+%\subsection{The Bias and Variance Asymptotics}
+\paragraph{Proof overview.} \todo{merge} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
 %We first describe the proof of Theorem \ref{lem_cov_shift_informal}.

### 2020-09-11 arxiv/setup.tex
wip

@@
 
+\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
+We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
+On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
+Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
+We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
+We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
+Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
+%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
+%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
+%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
+%Without loss of generality, let the $t$-th task denote the target task.
+%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
+%Hence adding more labeled data can help improve its test performance.
+%$B\in\real^{p\times r}$
+%$\set{W_i \in \real^{r}}_{i=1}^t$
+
+%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
+%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
+%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
+
+%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
+%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
+%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
+%distribution with covariance matrix $\Sigma_i$.
+
+%We extend our result to the transfer learning
+%in the setting of high-dimensional linear regression.
+%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
+%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
+%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
+%These results are described more precisely in Section \ref{sec_main}.
+
+Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
+%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
+%\textbf{Task similarity:}
+%\textbf{Data sizes:}
+%\textbf{Covariate shift:}
+%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
+\squishlist
+	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
+	As model distance increases, the bias becomes larger, resulting in negative transfer.
+%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
+%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
+%	The unexplained observations are caused by an error term from the bias.
+%	We discuss these in Section \ref{sec_insight}.
+	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
+	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
+	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
+	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
+	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
+	Otherwise, the variance reduces less with covariate shift.
+%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
+\squishend
+%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
+%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
+%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
+%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
+%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
+%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
+%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
+Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
+%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
+%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
+%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
+
+Our study also leads to several algorithmic consequences with practical interest.
+First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
+We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
+Second, we propose a new multi-task training schedule by incrementally adding task data batches to the training procedure.
+This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
+Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis datasets while keeping the accuracy the same.
+Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
+We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
+Finally, we validate our three theoretical findings on sentiment analysis tasks.
+
+We describe the main ideas for showing the generalization error of hard parameter sharing estimators.
+There are two key ideas in the proof.
+First, we study a bias-variance decomposition of hard parameter sharing, and show that the variance always reduces compared to single-task learning, while the bias always increases.
+Second, we study the limiting bias and variance of hard parameter sharing, and derive their asymptotics using recent development from the random matrix theory literature.
+The asymptotic results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties, which will be the focus of Section \ref{sec_special}.
+
 %This part introduces a positive variance reduction effect from adding the source labels.
@@
 
-\subsection{Bias and Variance}
-
 \subsection{Random Matrices}

### 2020-09-11 arxiv/transfer.tex
wip

@@
-\section{Main Results}\label{sec_general}
+%\section{Main Results}\label{sec_general}
 
@@
 %\end{proposition}
-We describe the main ideas for showing the generalization error of hard parameter sharing estimators.
-There are two key ideas in the proof.
-First, we study a bias-variance decomposition of hard parameter sharing, and show that the variance always reduces compared to single-task learning, while the bias always increases.
-Second, we study the limiting bias and variance of hard parameter sharing, and derive their asymptotics using recent development from the random matrix theory literature.
-The asymptotic results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties, which will be the focus of Section \ref{sec_special}.
+
 %In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
@@
 
-\subsection{Same Covariates}
+\section{Bias-Variance Decomposition, Same Covariates Setting}
 %A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
@@
 
-\subsection{Different Covariates: The Two-task Case}
+\section{The Different Covariates Setting}
 As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.

### 2020-09-11 arxiv/proof_main.tex
revise

--- 2020-09-11 arxiv/proof_main.tex
@@
 \subsection{The Bias and Variance Asymptotics}
-Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
+
+{\cor $X^{(1)}$, $X^{(2)}$} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
 %We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
@@
 \ee
+{\cor explain these terms}
 \end{definition}

### 2020-09-11 arxiv/proof_main.tex

--- 2020-09-11 arxiv/proof_main.tex
@@
 In particular, the matrix limit of $\cal G(z)$ is given by $(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}$.
-
 \medskip
@@
 \alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
-
 For the bias asymptotics, we can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
@@
 This is the main reason why we need to take a general $z$ in the definition of resolvents.
-
 %In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
-
 %For the variance asymptotic limit, we study the resolvent
@@
 %Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
-
 \medskip
@@
  \end{equation}
-
 \medskip
@@
 The core quantities of the derivation are the following resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
-
 \begin{definition}[Resolvent minors]\label{defn_Minor}
@@
 \end{definition}
-
 %Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
 One will see a crucial use of this fact in the heuristic proof below.
-
  Using Schur complement formula (see {equation} (\ref{resolvent2})), we have that %for $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
@@
 with high probability.
-
 \medskip
@@
 \ee
-
 \medskip
@@
 \nc
-
 The above arguments are the core of the main proof.

### 2020-09-12 arxiv/setup.tex
wip

@@
 \subsection{Notations}
-Throughout the appendix, we shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+We shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
 Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
 For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
-We shall refer to random matrices of the form $X^\top X$ as sample covariance matrices following the standard notations in high-dimensional statistics.
+We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
 %\subsection{Bias and Variance}

### 2020-09-12 arxiv/transfer.tex
wip

@@
 %We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
-This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Similar to the two-task case, we consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
+We describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
+%This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
 We extend the bias-variance decomposition from the two-task case to the multiple-task case.

### 2020-09-12 arxiv/proof_same_cov.tex
sec

--- 2020-09-12 arxiv/transfer.tex
@@
-%\section{Main Results}\label{sec_general}
-
-%\begin{proposition}[Bias-variance tradeoff]
-%	Variance always reduces and bias always increases.
-%\end{proposition}
-
-%In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
-%First, we consider the two-task case.
-%We provide precise asymptotics of the bias and variance of the multi-task learning estimator.
-%We apply recent developments from the random matrix theory literature to characterize the bias and variance.
-%The results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties (Section \ref{sec_special}).
-%Second, we consider the multiple-task case where all tasks have the same features but different labels.
-%We extend the bias-variance decomposition of the two-task case to this setting and show qualitatively similar results.
-%For the single-task learning estimator, there are well-known results that relate its prediction loss to sample size and noise variance.
-
-%We focus on the high-dimensional linear regression setting \cite{}
-
-\section{Bias-Variance Decomposition, Same Covariates Setting}
-%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
-%Our main technical contribution is to extend this result to two tasks.
-%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-We describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
-%This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
-We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-\begin{align}
-	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-\end{align}
-One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-
-Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
-Before stating the result, we define the following notations.
-Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
-Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
-\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
-For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
-
-\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Consider the multiple-task case where all tasks have the same covariates.
-	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
-	Then, the following is true:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
-over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
-	\end{itemize}
-\end{theorem}
-Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
-As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
-The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
-
-	First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
-	Recall that all tasks have the same covariates in this setting.
-	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
-	\begin{align}
-		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
-	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
-	\begin{align*}
-		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
-		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
-	\end{align*}
-	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} by a decomposition of the expected prediction loss over the random noise condition on $X$ as follows
-	\begin{align}
-		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \nonumber \\
-		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \nonumber \\
-		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
-		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \nonumber \\
-		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
-		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}. \label{eq_ex_pred}
-	\end{align}
-	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-	The last step uses the fact that $\sum_{i=1}^t W_i W_i^{\top} = \cW \cW^{\top}$.
-	One can see that the first part of the last equation is the bias and the second part is the variance.
-	Hence the proof is complete.
-
-	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we also obtain the objective $g(\cW)$.
-	\begin{align}
-		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2.
-\label{eq_mtl_output_layer}
-	\end{align}
-	Now we are ready to prove Theorem \ref{thm_many_tasks}.
-	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.
-
-%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
-Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
-The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
-
-%In this section we consider the setting with $k$ many that have the same covariates.
-%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
-
-\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.
-	In order to derive the minimizer, our proof involves two steps.
-	First, we consider the expectation of $g(\cW)$ over $\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t$, and $X$.
-	We show that the minimizer of $\ex{g(\cW)}$ has a simple closed form solution similar to principal component analysis.
-	Second, we show that the concentration error between $g(\cW)$ and $\ex{g(\cW)}$ is small provided with $n$ samples.
-	Intuitively, this is because $\cW$ only has $r \times t$ parameters, which is much smaller than $n$ by our assumption.
-	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
-	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
-	\begin{align*}
-		g_0(\cW) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-		g_1(\cW) &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
-		&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-		g_2(\cW) &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
-		&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
-	\end{align*}
-	For the second equation of $g_1(\cW)$, we use the fact that
-		\[ \sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}. \]
-	For the second equation of $g_2(\cW)$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id_{r\times r}$ and rearrange the terms.
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
-
-	\medskip
-	\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
-	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
-	\begin{align}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - g_0(\cW)
-		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cW) \mid X}
-		%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-		= \sigma^2(n\cdot t - p\cdot r) \nonumber
-	\end{align}
-	%	\begin{align}
-	%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
-	%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
-	%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
-	%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
-	%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
-	%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
-	%	\end{align}
-	The first equation uses the same fact the expectation of $g_1(\cW)$ over the random noise is zero.
-	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$, and
-		\[ \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}
-			= \id_{r\times r} = r. \]
-	%\be\nonumber
-	%g(\cal W)= g_0 + 2g_1 + g_2,
-	%\ee
-	%where
-	%\begin{align*}
-	%	g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-	%	g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
-	%			%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-	%	g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
-	%				\end{align*}
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
-	%\medskip
-	%\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
-	%We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	%First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
-	%\begin{align*}
-	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W)
-	%	+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
-	%	&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
-%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-	%	&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
-	%\end{align*}
-%	\begin{align}
-%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
-%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
-%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
-%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
-%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
-%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
-%	\end{align}
-	%where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
-	%the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.
-	We further take expectation over $X$ for $g_0(\cW)$ and obtain the following:
-	\begin{align*}
-		\ex{g(\cW)} = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 (n\cdot t - p \cdot r).
-	\end{align*}
-	%\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
-\iffalse
-{\color{red}
-\begin{align*}
-	f(W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X \hat B W_i - Y_i}^2 = \val(\cal W) \cdot \left( 1+\OO(p^{-1/2+\e})\right),
-\end{align*}
-where
-\begin{align*}
-	 \val(\cal W) &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \E_{\e_i:1\le i \le t}\sum_{i=1}^t\left\| X(X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}W_i -\e_i\right\| \\
-	 &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \sigma^2 (nt-pr).
-\end{align*}
-
-}
-\fi
-%Here $\val(\cal W)$ is defined as
-%it remains to consider minimizing the validation loss
-%	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari} ,$$
-%where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
-%	\begin{align*}
-%		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
-%	\end{align*}
-%	and the variance term $\delta_{\vari} $ can be calculated as
-%	\begin{align*}
-%		\delta_{\vari} := \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-%	\end{align*}
-	One can see that the above equation provides a bias-variance decomposition of $\ex{g(\cW)}$.
-	The first part measures the bias of multi-task learning compared to single-task learning for all tasks.
-	The second part measures the variance of multi-task learning and scales with $\sigma^2$.
-	In order to minimize $\ex{g(\cW)}$, it suffices to minimize the bias equation over $\cal W$, since the variance equation does not depend on $\cal W$.
-	%We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{t\times t}$, whose $(i,j)$-th entry is given by $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
-	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-	%Now we can write $\delta_{\bias}(\cal W)$ succinctly as
-	%\begin{align*}
-	%	\delta_{\bias}(Q) \equiv \delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  %\bigbrace{Q -\id}}^2 .
-	%\end{align*}
-	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to ${B^{\star}}^{\top} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
-
-	\medskip
-	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
+	\section{Proof of Lemma \ref{lem_error_same_cov}}\label{app_proof_error_same_cov}
 	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
@@
 	\end{align}
-
-%	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
-%	where the second part follows by using Cauchy-Shwartz inequality.
-
-	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
-	%\begin{align}
-	%	g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
-	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
-	%\end{align}
-	%Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.
-
-	%For equation \eqref{approxvalid_1}, we observe that the summands of $g(\cW)$ w.r.t. $\varepsilon_1, \dots, \varepsilon_t$ belong to either of the following three types:
-	%\begin{enumerate}
-	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i$, for any $i = 1,\dots, t$ and a fixed $A\in\real^{n\times n}$ that is independent of $\varepsilon_i$;
-	%	\item[(ii)] $\varepsilon_i^{\top} A \varepsilon_j$, for any $i \neq j$ and a fixed $A$ that is independent of both $\varepsilon_i$ and $\varepsilon_j$;
-	%	\item[(iii)] $\varepsilon_i^{\top} A$, for any $i = 1,\dots, t$ and a fixed $A\in\real^n$ that is independent of $\varepsilon_i$.
-	%\end{enumerate}
-	%For all three types, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
-	%\begin{enumerate}
-	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i = \sigma^2 (1 + \OO(p^{-1/2 + c})) \normFro{A}^2$;
-	%	\item[(ii)] $\abs{}$
-	%	\item[(iii)]
-	%\end{enumerate}
-
-	%We use the fact that our random vectors have i.i.d. entries.
-%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-	%Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + %\wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite %\eqref{eq_mtl_2tasktilde} as
-%$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat %B w_i-\beta_i.$$
-	%Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration result,  to get that for any constant $\e>0$,
-	%\begin{align*}
-		%\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  %- \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
-%&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
-	%$\end{align*}
-	%with high probability. Thus we obtain that
-	%$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
-%where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
-	% again the concentration result, Lemma \ref{largedeviation}, we get that
-	%$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
-%with high probability.
-%-----old-------
-%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-%\begin{align}
-%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
-%\end{align}
-%\nc
-%------------------
-%Thus we conclude the proof.
-
-	\medskip
-	\noindent\textbf{Dealing with the empirical minimizer.}
-	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
-	We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
-	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
-	Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
-		&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
-	\end{align*}
-	On the other hand, by equation \eqref{eq_est_g} and triangle inequality, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{\cW})}) + \bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le o(n) \cdot \sigma_{\max}({B^{\star}}^{\top} \Sigma B^{\star}) + O(\sigma^2 p^{1/2 +\e}).
-	\end{align*}
-	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish to $o(1)$ as $p$ grows.
-	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
-	%In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
-	%$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
-	%where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
-
-	\medskip
-	\noindent\textbf{Putting all parts together.}
-	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
-	Now we are ready to finish the proof.
-	Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
-	\begin{align}
-		L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
-	\end{align}
-	Using equation \eqref{eq_ex_pred}, we have that
-	\begin{align}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
-		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
-	\end{align}
-	In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
-	\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
-\]
-  In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
-	Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
-\end{proof}
-%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
-%\begin{itemize}
-%	\item The de-noising effect of multi-task learning.
-%	\item Multi-task training vs single-task training can be either positive or negative.
-%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
-%\end{itemize}
-
-\section{The Different Covariates Setting}
-As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
-Therefore, we consider an arbitrary local minimum $B, W_1, W_2$, in particular when $B = \hat{B}(W_1, W_2)$ satisfies the local optimality condition.
-We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
-Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$ as follows
-\begin{align}
-	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
-	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
-			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
-\end{align}
-See Section \ref{app_proof_main_thm} for its derivation.
-Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
-equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
-%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Comparing the above to single-task learning, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-
-Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
-We introduce a key quantity $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
-
-%We now state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
-The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
-
-\begin{theorem}[Two-task case]\label{thm_main_informal}
-	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
-	For the setting of two tasks, let $C$ be a fixed constant and let $\delta = \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) }$.
-	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
-	\begin{enumerate}
-		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
-		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
-	\end{enumerate}
-\end{theorem}
-In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
-We make several remarks about Theorem \ref{thm_main_informal}.
-First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
-This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
-%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
-%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
-%determined by the covariate shift matrix and the model shift.
-%The bounds get tighter and tighter as $\rho_1$ increases.
-Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
-Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
-%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-
-%\textbf{Proof overview.}\todo{}
-%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
-%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
-This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
-%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
-%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
-%
-%
-%
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-
-\iffalse
-Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
-From \cite{WZR20}, we know that we need to explicitly restrict the output dimension $r$ of $B$ so that there is transfer between the two tasks.
-Hence for the case of two tasks, we consider the setting where $r=1$.
-For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to
-\begin{align}\label{eq_mtl_2task}
-	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
-\end{align}
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
-\begin{align}
-	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
-	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
-	&= \frac{1}{w_2}\left[\beta_2 + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-\nonumber
-\end{align}
-As a remark, when $w_1 = w_2 = 1$, we obtain linear regression.
-If $\beta_1$ is a scaling of $\beta_2$, then  $w_1, w_2$ can be scaled accordingly to fix both tasks more accurately than linear regression.
-
-%For the discussions below, we assume that the entries of $\e_1$ and $\e_2$ all have the same variance $\sigma^2$.
-This holds for most parts of our discussion, except in Proposition \ref{prop_var_transition}.
-We will derive different expressions for the validation loss and the test error
-
-Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
-With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
-We assume that $N_1$ and $N_2$ satisfy $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
-Then we write the validation loss in \eqref{eq_mtl_eval} as
-\begin{align}\label{eq_mtl_2tasktilde}
-	g(w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
-\end{align}
-Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that the optimal solution of $g$ only depends on the ratio $v:=w_1/w_2$.
-Hence we overload the notation by writing $g(v)$ in the following discussion.
-The expectation of $g(v)$ can be written as follows.
-\begin{align}
-		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \nonumber\\
-	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
-	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
-		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
-		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{revise_eq_val_mtl}
-\end{align}
-
-{\color{red}\begin{align*}
-			& f(W_1, W_2) = \bignorm{X_1 \hat B w_1 - Y_1}^2 + \bignorm{X_2 \hat B w_2 - Y_2}^2\\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}Y_1 + vX_2^{\top}Y_2\right) - Y_1}^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}Y_1 + X_2^{\top}Y_2\right) - Y_2}^2 \\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}\e_1 + vX_2^{\top}\e_2\right) - \e_1 + X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}\e_1 + X_2^{\top}\e_2\right) - \e_2 + vX_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&=\val(v)\cdot \left( 1+\OO(p^{-1/2\e})\right) \quad \text{w.h.p.},
-		\end{align*}
-		where
-		\begin{align*}
-		\val(v)&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}   X_1^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_1^\top\right)\\
-			&+\sigma^2 \tr\left(X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_2\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^\top\right)\\
-			&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 +(n_1+n_2-p)\sigma^2.
-		\end{align*}
-	}
-
-Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
-Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
-Now we can define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
-%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task".
-%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
-%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
-\begin{align}
-	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
-			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
-\end{align}
-which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
-\fi
-
-%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
-%	In the setting of two tasks,
-%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
-%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
-%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
-%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-%	{\small\begin{align*}%\label{eq_introX1X2}
-%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-%	\end{align*}}%
-%	where $a_1, a_2$ are solutions of the following equations:
-%	{\small\begin{align*}
-%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-%	\end{align*}}
-%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-%\end{lemma}
-
-\paragraph{Key ingredients.}
-We introduce two key lemmas that show tight asymptotic convergence rate of the bias equation \eqref{eq_bias_2task} and the variance equation  as sample sizes increase to infinity.
-%The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
-For the covariate shift matrix $M$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be its singular values in descending order.
-%which deals with the inverse of the sum of two random matrices, which
-%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
-	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
-	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
-	In the setting of Theorem \ref{thm_main_informal},
-	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
-	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
-	\end{align}
-	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
-	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12extra}
-	\end{align}
-\end{lemma}
-
-Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
-To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
-%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
-Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
-\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
-
-Lemma \ref{lem_cov_shift} also implies the asymptotic limit of the prediction loss of single-task learning.
-%The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-In particular, by setting $X_1 = 0$, we obtain the following corollary, which is a well-known result in random matrix theory.
-\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
-	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}A} + o(\norm{A}). \ee
-\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
-To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.
-We briefly describe the history behind the above well-known result.
-When the entries of $X_2$ are multivariate Gaussian, this result recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we have stated a result from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp concentration error bound.
-One can see that our result extends Lemma \ref{lem_minv} from a single sample covariance matrix to the sum of two independent sample covariance matrices.
-
-Interestingly, the asymptotic limit of the variance only depends on the sample sizes and the covariate shift matrix.
-Next, we derive the asymptotic limit of the bias equation \eqref{eq_bias_2task}, which depends on the scaled model distance in addition to sample size and covariate shift.
-%(cf.
-Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
-We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
-That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
-We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
-Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
-
-\begin{definition}[Limiting bias]
-Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
-	\[ \Pi \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
-where $a_{3}$ and $a_4$ are the solutions of the following two equations:
-\begin{gather}\label{eq_a34extra}
-		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1 .
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
-\end{definition}
-
-Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
-\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
-With high probability, we have that
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-= w^{\top} \Pi w + o(\|w\|^2),
-\end{split}
-\end{equation}
-
-\end{lemma}
-To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
-Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
-As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
-Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
-In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
-
-In Section \ref{app_proof_main_thm}, we will describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.

### 2020-09-12 arxiv/transfer.tex
sec

@@
 %We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-We describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
+We begin by considering the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
 %This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
-We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-\begin{align}
-	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-\end{align}
-One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-Compared to the prediction loss of single-task learning (cf.
+%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
+%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
+%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
+%\begin{align}
+%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
+%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
+%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
+%\end{align}
+%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
+%Compared to the prediction loss of single-task learning (cf.
 equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-
-Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
+%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
+We show the generalization error of hard parameter sharing estimators.
 Before stating the result, we define the following notations.
@@
 For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
+Our main result in this section is stated as follows.
 
@@
 	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
-	Then, the following is true:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
+	Then, for any task $i$ from $1$ to $t$, the prediction loss of the hard parameter sharing estimator satisfies that
+	\begin{align}
+		\bigabs{L(\hat{\beta}_i^{\MTL}) - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 - \norm{v_t}^2 \frac{\sigma^2}{\rho - 1}} \le o(\bigtr{{B^{\star}}^{\top}\Sigma B^{\star}} + \sigma^2).
+	\end{align}
+	%\begin{itemize}
+	%	\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} -  > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
+	%	 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
+	%	\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
 over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
-	\end{itemize}
+	%	\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
+	%\end{itemize}
 \end{theorem}
-Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
+	Theorem \ref{thm_many_tasks} provides a sharp generalization error bound \todo{check}.
 	As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
-The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.
+	\todo{check}
 
-	First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
-	Recall that all tasks have the same covariates in this setting.
-	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
+	%First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
+	The key idea for proving Theorem \ref{thm_many_tasks} is a bias-variance decomposition of the prediction loss of hard parameter sharing.
+	We describe the idea in the following.
+	Since all tasks have the same covariates, the optimization objective \eqref{eq_mtl} becomes
 	\begin{align}
@@
 	\end{align}
-	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
+	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$. % for $1 < r < t$ by our assumption.
+	Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
 	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
@@
 	\end{align*}
-	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} by a decomposition of the expected prediction loss over the random noise condition on $X$ as follows
+	Recall that $\hat{\beta}_t^{\MTL} = \hat{B} W_t$.
+	The expected prediction loss over the random noise conditional on $X$ is equal to
 	\begin{align}
@@
 
-	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we also obtain the objective $g(\cW)$.
+	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we obtain the objective $g(\cW)$ that only depends on the output layers.
 	\begin{align}
@@
 	\end{align}
-	Now we are ready to prove Theorem \ref{thm_many_tasks}.
+	We state a concentration error bound between $g(\cal W)$ and its expectation.
+
+	\begin{lemma}\label{lem_error_same_cov}
+		In the setting of Theorem \ref{thm_many_tasks}, we have that
+		\[ g(\cW) = \ex{g(\cW)} \cdot (1 + o(1)) + \OO(\sigma^2 p^{1/2 + c}). \]
+	\end{lemma}
+	The proof of Lemma \ref{lem_error_same_cov} is via standard concentration bounds.
+	The details can be found in Appendix \ref{app_proof_error_same_cov}.
+	Based on the above result, we are ready to prove Theorem \ref{thm_many_tasks}.
 	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.
-
-%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$.
-Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$.
-The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.
-
-%In this section we consider the setting with $k$ many that have the same covariates.
-%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
-%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
-%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.
 
@@
 	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to ${B^{\star}}^{\top} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
-
-	\medskip
-	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
-	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
-
-	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
-	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
-	%and
-	%\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
-	%&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
-	%\end{align*}
-	Applying the above estimates into $g_1(\cW)$, we get that
-	\begin{align}
-	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
-	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
-	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
-	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
-	\end{align}
-	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
-	In the last step, we use the AM-GM inequality.
-
-	Second, for $g_2(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for any $1\le i, j \le t$, the following holds with high probability:
-	\begin{align*}
-		\bigabs{\norm{\varepsilon_j}^2 - \ex{\norm{\varepsilon_j}^2}} &\le \sigma^2 p^{1/2+\e},\\
-		%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
-		\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
-		&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
-  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
-	\end{align*}
-	Combining the above two inequalities together, we get that with high probability
-	\begin{align}
-		\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_est_g2}
-	\end{align}
-
-	Finally, for $g_0(\cW)$, denote by $v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right)$, for any $j = 1,\dots,t$, we have that $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
-%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
-	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}.
-	Hence by law of large numbers, we have that with high probability
-	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1+\oo(1))$,
-	which implies that
-	\begin{align}
-		g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)). \label{eq_est_g0}
-	\end{align}
-
-	Combining equation \eqref{eq_est_g1}, \eqref{eq_est_g2}, and \eqref{eq_est_g0}, we obtain that with high probability
-	\begin{align}
-	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
-	&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
-	\end{align}
 

### 2020-09-12 arxiv/transfer.tex
sec 4

@@
 
-\section{Bias-Variance Decomposition, Same Covariates Setting}
+\section{Bias-Variance Tradeoff in the Same Covariates Setting}
 %A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
@@
 We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
-Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$ as follows
+Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
+Using the local optimality condition of $B$, we obtain that
+\begin{align*}
+	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
+	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
+	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+\end{align*}
+Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
 \begin{align}
@@
 \end{align}
-See Section \ref{app_proof_main_thm} for its derivation.
 Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
@@
 
+\begin{definition}[Limiting variance]
+	Define the following
+	\[ \Pi_{\vari} \define \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma}. \]
+
+	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
+	\begin{align}
+		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
+\label{eq_a12extra}
+	\end{align}
+\end{definition}
 %We now state our main result for two tasks with both covariate and model shift.
@@
 
+\begin{definition}[Limiting bias]
+Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
+	\[ \Pi \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
+where $a_{3}$ and $a_4$ are the solutions of the following two equations:
+\begin{gather}\label{eq_a34extra}
+		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1 .
+%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
+%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
+	\end{gather}
+In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
+\end{definition}
+
 \begin{theorem}[Two-task case]\label{thm_main_informal}
 	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
-	For the setting of two tasks, let $C$ be a fixed constant and let $\delta = \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) }$.
+	For the setting of two tasks, let $C$ be a fixed constant.
 	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
-	\begin{enumerate}
-		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
-		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
-	\end{enumerate}
+ 	%There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
+	We have that
+	\begin{align*}
+		\bigabs{L(\hat{\beta}_2^{\MTL}) - \Pi_{\vari} - (\beta_1 - \frac{W_1}{W_2}\beta_2)^{\top}\Pi_{\bias} (\beta_1 - \frac{W_1}{W_2}\beta_2)} \le \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) } \cdot \frac{1}{\sqrt{\rho_1}}
+	\end{align*}
+%	\begin{enumerate}
+%		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
+%			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
+%		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
+%			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
+%	\end{enumerate}
 \end{theorem}
@@
 %, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-
-\iffalse
-Next, we derive a closed-form solution of the multi-task learning estimator for the case of two tasks.
-From \cite{WZR20}, we know that we need to explicitly restrict the output dimension $r$ of $B$ so that there is transfer between the two tasks.
-Hence for the case of two tasks, we consider the setting where $r=1$.
-For simplicity of notations, we shall denote $(X_i^{tr},Y_i^{tr})$ and $(X_i^{val},Y_i^{val})$ as $(X_i,Y_i)$ and  $(\wt X_i,\wt Y_i)$, respectively. Then equation \eqref{eq_mtl} simplifies to
-\begin{align}\label{eq_mtl_2task}
-	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
-\end{align}
-where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
-\begin{align}
-	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
-	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
-	&= \frac{1}{w_2}\left[\beta_2 + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-\nonumber
-\end{align}
-As a remark, when $w_1 = w_2 = 1$, we obtain linear regression.
-If $\beta_1$ is a scaling of $\beta_2$, then  $w_1, w_2$ can be scaled accordingly to fix both tasks more accurately than linear regression.
-
-%For the discussions below, we assume that the entries of $\e_1$ and $\e_2$ all have the same variance $\sigma^2$.
-This holds for most parts of our discussion, except in Proposition \ref{prop_var_transition}.
-We will derive different expressions for the validation loss and the test error
-
-Next we consider $N_i$ independent samples of the training set $\{(\wt x_k^{(i)},\wt y_k^{(i)}): 1\le k \le N_i\}$ from task-$i$, $i=1,2$.
-With these sample, we form the random matrices $\wt X_i \in \R^{N_i\times p}$ and $\wt Y_i\in \R^{N_i}$, $i=1,2,$ whose row vectors are given by $\wt x_k^{(i)}$ and $\wt y_k^{(i)}$.
-We assume that $N_1$ and $N_2$ satisfy $N_1/N_2=n_1/n_2$ and $N_i \ge n_i^{1-\e_0}$ for some constant $\e_0>0$.
-Then we write the validation loss in \eqref{eq_mtl_eval} as
-\begin{align}\label{eq_mtl_2tasktilde}
-	g(w_1,w_2) = \bignorm{\wt X_1 \hat B w_1 - \wt Y_1}^2 + \bignorm{\wt X_2 \hat B w_2 - \wt Y_2}^2.
-\end{align}
-Inserting \eqref{hatB} into \eqref{eq_mtl_2tasktilde}, one can see that the optimal solution of $g$ only depends on the ratio $v:=w_1/w_2$.
-Hence we overload the notation by writing $g(v)$ in the following discussion.
-The expectation of $g(v)$ can be written as follows.
-\begin{align}
-		\val(v) \define& \exarg{\varepsilon_1,\e_2} {\sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2} \nonumber\\
-	=&  N_1 \cdot \bignorm{\Sigma_1^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_1 - v\beta_2\right)}^2 \nonumber \\
-	&+ N_2 \cdot v^2\bignorm{\Sigma_2^{1/2}\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_1 - v\beta_2\right)}^2 \nonumber \\
-		&+ N_1   \cdot v^2 \bigtr{\Sigma_1\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2X_1^{\top}X_1 + \sigma_2^2 \cdot X_2^{\top}X_2\right)} \nonumber \\
-		&+ N_2  \cdot \bigtr{\Sigma_2\left(v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \cdot v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right)}. \label{revise_eq_val_mtl}
-\end{align}
-
-{\color{red}\begin{align*}
-			& f(W_1, W_2) = \bignorm{X_1 \hat B w_1 - Y_1}^2 + \bignorm{X_2 \hat B w_2 - Y_2}^2\\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}Y_1 + vX_2^{\top}Y_2\right) - Y_1}^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}Y_1 + X_2^{\top}Y_2\right) - Y_2}^2 \\
-			& =\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(v^2 X_1^{\top}\e_1 + vX_2^{\top}\e_2\right) - \e_1 + X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ \bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(vX_1^{\top}\e_1 + X_2^{\top}\e_2\right) - \e_2 + vX_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&=\val(v)\cdot \left( 1+\OO(p^{-1/2\e})\right) \quad \text{w.h.p.},
-		\end{align*}
-		where
-		\begin{align*}
-		\val(v)&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}   X_1^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_1^\top\right)\\
-			&+\sigma^2 \tr\left(X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^{\top} -\id\right)^2 \\
-			&+\sigma^2 \tr\left(v^2 X_2\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} X_2^\top\right)\\
-			&=\bignorm{X_1\left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_2^{\top}X_2(v\beta_2-\beta_1) }^2 \\
-			&+ v^2\bignorm{X_2 \left( v^2 X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}  X_1^{\top}X_1(\beta_1-v\beta_2) }^2 +(n_1+n_2-p)\sigma^2.
-		\end{align*}
-	}
-
-Hence to minimize $g(v)$, it suffices to minimize $\val(v)$ over $v$.
-Let $\hat v=\hat{w_1}/\hat{w_2}$ be the global minimizer of $g(v)$.
-Now we can define the multi-task learning estimator for the target task as
-	\[ \hat{\beta}_2^{\MTL} = \hat{w}_{2}\hat{B}(\hat{w}_1, \hat{w}_2) .\]
-%	where $t=2$ since we are considering the two task case, and it also stands for the ``target task".
-%The intuition for deriving $\hat{\beta}_2^{\MTL}$ is akin to performing multi-task training in practice.
-%Let $\hat{v} = \hat{w_1} / \hat{w_2}$ for the simplicity of notation.
-The prediction loss of using $\hat{\beta}_2^{\MTL}$ for the target task is
-\begin{align}
-	\te(\hat{\beta}_2^{\MTL}) =&~ \hat{v}^2 \bignorm{\Sigma_2^{1/2}(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \hat{v} \beta_2)}^2 \nonumber \\
-			&+~  \bigtr{\Sigma_2(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}\left(\sigma_1^2 \cdot \hat v^2  X_1^{\top}X_1 + \sigma_2^2  \cdot X_2^{\top}X_2\right) }, \label{eq_te_mtl_2task}
-\end{align}
-which only depends on $\hat v$, the sample covariance matrices, and $\beta_1,\beta_2$.
-\fi
 
@@
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \Pi_{\vari} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
 	\end{align}
-	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
-	\begin{align}
-		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12extra}
-	\end{align}
+
 \end{lemma}
@@
 
-\begin{definition}[Limiting bias]
-Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
-	\[ \Pi \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
-where $a_{3}$ and $a_4$ are the solutions of the following two equations:
-\begin{gather}\label{eq_a34extra}
-		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1 .
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-	\end{gather}
-In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
-\end{definition}
-
 Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.

### 2020-09-12 arxiv/transfer.tex
revise

--- 2020-09-12 arxiv/transfer.tex
@@
 %We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-We describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
-%This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
+Next, we describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
+This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+Similar to the two-task case, we consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
 We extend the bias-variance decomposition from the two-task case to the multiple-task case.
@@
 As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
+The formal proof of Theorem \ref{thm_main_informal} using Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be presented in Section \ref{app_proof_main_thm}.
 Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
@@
 
-In Section \ref{app_proof_main_thm}, we will describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+%In Section \ref{app_proof_main_thm},
+
+In the rest of section, we describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
 In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
+The full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be given in Section \ref{appendix RMT}

### 2020-09-12 arxiv/setup.tex

@@
 This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
-Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check}, the $l$-th moment of the noise entries exists:
+Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check, remove $c$ and $o(1)$ in main body}, the $l$-th moment of the noise entries exists:
 \begin{align*}

### 2020-09-12 arxiv/setup.tex
edit

@@
 
-\section{Preliminaries}
+%\section{Preliminaries}
 
-\subsection{Notations}
+\paragraph{Notations.}
 We shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
@@
 
-\subsection{Hard Parameter Sharing}
+%\subsection{Hard Parameter Sharing}
 
-\subsection{Random Matrices}
-
+%\subsection{Random Matrices}
+\todo{merge w/ theorem}
 We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.

### 2020-09-12 arxiv/proof_main.tex

--- 2020-09-11 arxiv/proof_main.tex
@@
-%\section{Proofs}\label{sec_proof_general}
-
-%\subsection{The Multiple-task Case}\label{app_proof_many_tasks}
-
 %\subsection{The Bias and Variance Asymptotics}
-\paragraph{Proof overview.} \todo{merge} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
+\paragraph{Proof overview.} 
+%\todo{merge} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
 %We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
@@
 Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $(X_1^\top X_1+X_2^\top X_2)^{-1}$ for $X_1= Z_1\Sigma_1^{1/2}$ and $X_2= Z_2\Sigma_2^{1/2}$.
-\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
+%\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
 Suppose $M=\Sig_1^{1/2} \Sig_2^{-1/2}$ has a singular value decomposition
@@
 
-For the bias asymptotics, we can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
-More precisely, using equation \eqref{eigen2extra} we can obtain that
-\begin{align}
-n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
-&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
-\end{align}
-where we used equation \eqref{rewrite X as R} in the second step. It is natural to guess that the matrix limit of $\cal G'(0)$ is given by
-\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
-If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
-Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
-\begin{align*}
-n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi w,
-\end{align*}
-which concludes \eqref{lem_cov_derv_eq}.
-Note that in order to have the approximate identity for $\cal G'(0)$ in \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
-This is the main reason why we need to take a general $z$ in the definition of resolvents.
-
-%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
-
-%For the variance asymptotic limit, we study the resolvent
-%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
-%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
-%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
-%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
-%
-%For the bias asymptotic limit, we show in \todo{where?} that
-%$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
-%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
-%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
-
 \medskip
@@
 The other off-diagonal entries can be bounded in the same way.
-\nc
+
+\medskip
+\noindent{\bf Deriving the bias asymptotics.} Finally, we describe ..........
+For the bias asymptotics, we can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
+More precisely, using equation \eqref{eigen2extra} we can obtain that
+\begin{align}
+n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
+&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
+\end{align}
+where we used equation \eqref{rewrite X as R} in the second step. It is natural to guess that the matrix limit of $\cal G'(0)$ is given by
+\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
+If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
+Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
+\begin{align*}
+n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi w,
+\end{align*}
+which concludes \eqref{lem_cov_derv_eq}.
+Note that in order to have the approximate identity for $\cal G'(0)$ in \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
+This is the main reason why we need to take a general $z$ in the definition of resolvents.
+%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
+%For the variance asymptotic limit, we study the resolvent
+%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
+%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
+%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
+%
+%For the bias asymptotic limit, we show in \todo{where?} that
+%$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
+%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
 

### 2020-09-12 arxiv/transfer.tex
wip

@@
-%\section{Main Results}\label{sec_general}
-
-%\begin{proposition}[Bias-variance tradeoff]
-%	Variance always reduces and bias always increases.
-%\end{proposition}
-
-%In this section, we compare the prediction loss of the multi-task learning estimator to that of the single-task learning estimator.
-%First, we consider the two-task case.
-%We provide precise asymptotics of the bias and variance of the multi-task learning estimator.
-%We apply recent developments from the random matrix theory literature to characterize the bias and variance.
-%The results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties (Section \ref{sec_special}).
-%Second, we consider the multiple-task case where all tasks have the same features but different labels.
-%We extend the bias-variance decomposition of the two-task case to this setting and show qualitatively similar results.
-%For the single-task learning estimator, there are well-known results that relate its prediction loss to sample size and noise variance.
-
-%We focus on the high-dimensional linear regression setting \cite{}
-
-\section{Bias-Variance Tradeoff in the Same Covariates Setting}
+\section{Warmup: Bias-Variance Tradeoff in the Same Covariates Setting}
 %A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
@@
 %We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-We begin by considering the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
+We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
+We provide a sharp generalization error bound of hard parameter sharing estimators.
+We show that the hard parameter sharing estimator finds a ``low-rank approximation of all tasks'', in the sense formalized below.
 %This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
@@
 %On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-We show the generalization error of hard parameter sharing estimators.
-Before stating the result, we define the following notations.
+%We show the generalization error of hard parameter sharing estimators.
+%Before stating the result, we define the following notations.
 Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
-Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
-\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
+Let $\Sigma$ denote the (same) population covariance matrix of all tasks.
+Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$, that is,
+\[ U_r \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}}. \]
 For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.

### 2020-09-12 arxiv/diff_cov.tex
edits

--- 2020-09-12 arxiv/transfer.tex
@@
-\section{Warmup: Bias-Variance Tradeoff in the Same Covariates Setting}
-%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g.
-Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
-%Our main technical contribution is to extend this result to two tasks.
-%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
-We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
-We provide a sharp generalization error bound of hard parameter sharing estimators.
-We show that the hard parameter sharing estimator finds a ``low-rank approximation of all tasks'', in the sense formalized below.
-%This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
-Let $\Sigma$ denote the (same) population covariance matrix of all tasks.
-Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$, that is,
-\[ U_r \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}}. \]
-For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
-Our main result in this section is stated as follows.
-
-\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Consider the multiple-task case where all tasks have the same covariates.
-	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
-	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
-	Then, for any task $i$ from $1$ to $t$, the prediction loss of the hard parameter sharing estimator satisfies that
-	\begin{align}
-		\bigabs{L(\hat{\beta}_i^{\MTL}) - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 - \norm{v_t}^2 \frac{\sigma^2}{\rho - 1}} \le o(\bigtr{{B^{\star}}^{\top}\Sigma B^{\star}} + \sigma^2).
-	\end{align}
-	%\begin{itemize}
-	%	\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} -  > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-	%	 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
-	%	\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p.
-over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
-	%	\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
-	%\end{itemize}
-\end{theorem}
-	Theorem \ref{thm_many_tasks} provides a sharp generalization error bound \todo{check}.
-	As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
-	\todo{check}
-
-	%First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
-	The key idea for proving Theorem \ref{thm_many_tasks} is a bias-variance decomposition of the prediction loss of hard parameter sharing.
-	We describe the idea in the following.
-	Since all tasks have the same covariates, the optimization objective \eqref{eq_mtl} becomes
-	\begin{align}
-		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$. % for $1 < r < t$ by our assumption.
-	Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
-	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
-	\begin{align*}
-		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
-		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
-	\end{align*}
-	Recall that $\hat{\beta}_t^{\MTL} = \hat{B} W_t$.
-	The expected prediction loss over the random noise conditional on $X$ is equal to
-	\begin{align}
-		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \nonumber \\
-		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \nonumber \\
-		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
-		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \nonumber \\
-		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
-		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}. \label{eq_ex_pred}
-	\end{align}
-	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-	The last step uses the fact that $\sum_{i=1}^t W_i W_i^{\top} = \cW \cW^{\top}$.
-	One can see that the first part of the last equation is the bias and the second part is the variance.
-	Hence the proof is complete.
-
-	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we obtain the objective $g(\cW)$ that only depends on the output layers.
-	\begin{align}
-		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2.
-\label{eq_mtl_output_layer}
-	\end{align}
-	We state a concentration error bound between $g(\cal W)$ and its expectation.
-
-	\begin{lemma}\label{lem_error_same_cov}
-		In the setting of Theorem \ref{thm_many_tasks}, we have that
-		\[ g(\cW) = \ex{g(\cW)} \cdot (1 + o(1)) + \OO(\sigma^2 p^{1/2 + c}). \]
-	\end{lemma}
-	The proof of Lemma \ref{lem_error_same_cov} is via standard concentration bounds.
-	The details can be found in Appendix \ref{app_proof_error_same_cov}.
-	Based on the above result, we are ready to prove Theorem \ref{thm_many_tasks}.
-	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.
-
-\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.
-	In order to derive the minimizer, our proof involves two steps.
-	First, we consider the expectation of $g(\cW)$ over $\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t$, and $X$.
-	We show that the minimizer of $\ex{g(\cW)}$ has a simple closed form solution similar to principal component analysis.
-	Second, we show that the concentration error between $g(\cW)$ and $\ex{g(\cW)}$ is small provided with $n$ samples.
-	Intuitively, this is because $\cW$ only has $r \times t$ parameters, which is much smaller than $n$ by our assumption.
-	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
-	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
-	\begin{align*}
-		g_0(\cW) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-		g_1(\cW) &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
-		&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-		g_2(\cW) &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
-		&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
-	\end{align*}
-	For the second equation of $g_1(\cW)$, we use the fact that
-		\[ \sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}. \]
-	For the second equation of $g_2(\cW)$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id_{r\times r}$ and rearrange the terms.
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
-
-	\medskip
-	\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
-	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
-	\begin{align}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - g_0(\cW)
-		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cW) \mid X}
-		%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-		= \sigma^2(n\cdot t - p\cdot r) \nonumber
-	\end{align}
-	%	\begin{align}
-	%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
-	%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
-	%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
-	%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
-	%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
-	%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-	%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
-	%	\end{align}
-	The first equation uses the same fact the expectation of $g_1(\cW)$ over the random noise is zero.
-	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$, and
-		\[ \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}
-			= \id_{r\times r} = r. \]
-	%\be\nonumber
-	%g(\cal W)= g_0 + 2g_1 + g_2,
-	%\ee
-	%where
-	%\begin{align*}
-	%	g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-	%	g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
-	%			%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
-	%	g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
-	%				\end{align*}
-	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
-	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as
-	%\medskip
-	%\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
-	%We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
-	%First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
-	%\begin{align*}
-	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W)
-	%	+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
-	%	&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
-%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-	%	&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
-	%\end{align*}
-%	\begin{align}
-%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
-%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
-%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
-%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
-%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
-%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
-%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
-%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
-%	\end{align}
-	%where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
-	%the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.
-	We further take expectation over $X$ for $g_0(\cW)$ and obtain the following:
-	\begin{align*}
-		\ex{g(\cW)} = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 (n\cdot t - p \cdot r).
-	\end{align*}
-	%\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
-\iffalse
-{\color{red}
-\begin{align*}
-	f(W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X \hat B W_i - Y_i}^2 = \val(\cal W) \cdot \left( 1+\OO(p^{-1/2+\e})\right),
-\end{align*}
-where
-\begin{align*}
-	 \val(\cal W) &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \E_{\e_i:1\le i \le t}\sum_{i=1}^t\left\| X(X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}W_i -\e_i\right\| \\
-	 &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \sigma^2 (nt-pr).
-\end{align*}
-
-}
-\fi
-%Here $\val(\cal W)$ is defined as
-%it remains to consider minimizing the validation loss
-%	$$\val( \cal W):=\exarg{\varepsilon_j, \forall 1\le j\le t}{ \sum_{i=1}^t \bignorm{\Sigma^{1/2}( \hat B W_i - \beta_i)}^2} =  \delta_{\bias}(\cal W) + \delta_{\vari} ,$$
-%where the model shift bias term $\delta_{\bias}(\cal W) $ is given by
-%	\begin{align*}
-%		\delta_{\bias}(\cal W) :=\sum_{i=1}^t  \bignorm{\Sigma^{1/2}\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2,
-%	\end{align*}
-%	and the variance term $\delta_{\vari} $ can be calculated as
-%	\begin{align*}
-%		\delta_{\vari} := \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
-%	\end{align*}
-	One can see that the above equation provides a bias-variance decomposition of $\ex{g(\cW)}$.
-	The first part measures the bias of multi-task learning compared to single-task learning for all tasks.
-	The second part measures the variance of multi-task learning and scales with $\sigma^2$.
-	In order to minimize $\ex{g(\cW)}$, it suffices to minimize the bias equation over $\cal W$, since the variance equation does not depend on $\cal W$.
-	%We denote $Q := \cal W^{\top} (\cal W\cal W^{\top})^{-1} \cal W \in\real^{t\times t}$, whose $(i,j)$-th entry is given by $W_i^{\top} (\cal W\cal W^{\top})^{-1} W_j$.
-	%Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
-	%Now we can write $\delta_{\bias}(\cal W)$ succinctly as
-	%\begin{align*}
-	%	\delta_{\bias}(Q) \equiv \delta_{\bias}(\cal W) = \bignormFro{\Sigma^{1/2}B^{\star}  %\bigbrace{Q -\id}}^2 .
-	%\end{align*}
-	From the bias equation, we observe that the minimizer is equal to the best rank-$r$ (subspace) approximation to ${B^{\star}}^{\top} \Sigma B^{\star}$, which is denoted by $U_{r} U_r^{\top}$.
-
-%	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
-%	where the second part follows by using Cauchy-Shwartz inequality.
-
-	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
-	%\begin{align}
-	%	g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
-	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
-	%\end{align}
-	%Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.
-
-	%For equation \eqref{approxvalid_1}, we observe that the summands of $g(\cW)$ w.r.t. $\varepsilon_1, \dots, \varepsilon_t$ belong to either of the following three types:
-	%\begin{enumerate}
-	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i$, for any $i = 1,\dots, t$ and a fixed $A\in\real^{n\times n}$ that is independent of $\varepsilon_i$;
-	%	\item[(ii)] $\varepsilon_i^{\top} A \varepsilon_j$, for any $i \neq j$ and a fixed $A$ that is independent of both $\varepsilon_i$ and $\varepsilon_j$;
-	%	\item[(iii)] $\varepsilon_i^{\top} A$, for any $i = 1,\dots, t$ and a fixed $A\in\real^n$ that is independent of $\varepsilon_i$.
-	%\end{enumerate}
-	%For all three types, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
-	%\begin{enumerate}
-	%	\item[(i)] $\varepsilon_i^{\top} A \varepsilon_i = \sigma^2 (1 + \OO(p^{-1/2 + c})) \normFro{A}^2$;
-	%	\item[(ii)] $\abs{}$
-	%	\item[(iii)]
-	%\end{enumerate}
-
-	%We use the fact that our random vectors have i.i.d. entries.
-%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-	%Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + %\wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite %\eqref{eq_mtl_2tasktilde} as
-%$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat %B w_i-\beta_i.$$
-	%Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d. centered entries, we can use the concentration result,  to get that for any constant $\e>0$,
-	%\begin{align*}
-		%\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  %- \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
-%&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
-	%$\end{align*}
-	%with high probability. Thus we obtain that
-	%$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
-%where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
-	% again the concentration result, Lemma \ref{largedeviation}, we get that
-	%$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
-%with high probability.
-%-----old-------
-%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-%\begin{align}
-%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
-%\end{align}
-%\nc
-%------------------
-%Thus we conclude the proof.
-
-	\medskip
-	\noindent\textbf{Dealing with the empirical minimizer.}
-	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
-	We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
-	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
-	Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
-		&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
-	\end{align*}
-	On the other hand, by equation \eqref{eq_est_g} and triangle inequality, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{\cW})}) + \bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le o(n) \cdot \sigma_{\max}({B^{\star}}^{\top} \Sigma B^{\star}) + O(\sigma^2 p^{1/2 +\e}).
-	\end{align*}
-	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish to $o(1)$ as $p$ grows.
-	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
-	%In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
-	%$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
-	%where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
-
-	\medskip
-	\noindent\textbf{Putting all parts together.}
-	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
-	Now we are ready to finish the proof.
-	Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
-	\begin{align}
-		L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
-	\end{align}
-	Using equation \eqref{eq_ex_pred}, we have that
-	\begin{align}
-		\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
-		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
-		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
-	\end{align}
-	In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
-	\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
-\]
-  In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
-	Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
-\end{proof}
-%From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
-%\begin{itemize}
-%	\item The de-noising effect of multi-task learning.
-%	\item Multi-task training vs single-task training can be either positive or negative.
-%	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
-%\end{itemize}
-
 \section{The Different Covariates Setting}

### 2020-09-13 arxiv/setup.tex
wip

@@
 
-%\section{Preliminaries}
+\section{Preliminaries}
 
-\paragraph{Notations.}
+\subsection{Notations.}
 We shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
@@
 
+Let $A = [a_1, a_2, \dots, a_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
+
 %\noindent\textbf{Positive/Negative transfer.}
 
-%\subsection{Hard Parameter Sharing}
+\subsection{Hard Parameter Sharing}
 
-%\subsection{Random Matrices}
+\subsection{Random Matrices}
 \todo{merge w/ theorem}

### 2020-09-13 arxiv/diff_cov.tex
revise

@@
 	Define the following
-	\[ \Pi_{\vari} \define \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma}. \]
+	\[ \Pi_{\vari} \define \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2}. \]
 
@@
 Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
-	\[ \Pi \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
+	\[ \Pi_\bias \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
 where $a_{3}$ and $a_4$ are the solutions of the following two equations:
@@
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \Pi_{\vari} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
 	\end{align}
@@
 	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}A} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}A} + o(\norm{A}). \ee
+	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}\Sigma} + o(\norm{\Sigma}). \ee
 \end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
@@
 \bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-= w^{\top} \Pi w + o(\|w\|^2),
+= w^{\top} \Pi_\bias w + o(\|w\|^2),
 \end{split}

### 2020-09-13 arxiv/proof_main.tex
revise

@@
 We use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $(X_1^\top X_1+X_2^\top X_2)^{-1}$ for $X_1= Z_1\Sigma_1^{1/2}$ and $X_2= Z_2\Sigma_2^{1/2}$.
+Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $[(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}$ for $X^{(1)}= Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}= Z^{(2)}\Sigma_2^{1/2}$.
 %\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
@@
 Then using equation \eqref{eigen2}, we can write
-\be\label{eigen2extra}(X_1^\top X_1+X_2^\top X_2)^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
+\be\label{eigen2extra}[(X^{(1)})^\top (X^{(1)})+(X^{(2)})^\top (X^{(2)})]^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
 We divide the discussion into the following parts.
@@
 \medskip
-\noindent\textbf{Defining the resolvents.} For our purpose, we introduce a convenient \alert{self-adjoint linearization trick}\HZ{what does this trick mean? use less technical words},
+\noindent\textbf{Defining the resolvents.} For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
+$$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
+which is linear in $A$.
+This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
+Our goal is to study the SVD of the rectangular matrix $(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top)$.
+%For this purpose,
+%}\HZ{what does this trick mean? use less technical words},
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-which has been proved to be useful in studying the local laws of random matrices of the Gram type \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
-We define the following $(p+n)\times (p+n)$ symmetric block matrix, which is a linear function of $Z_1$ and $Z_2$:
+Then we define the following $(p+n)\times (p+n)$ symmetric block matrix 
+%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
 %\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
@@
  \begin{equation}\label{linearize_block}
-    H(Z_1,Z_2): = n^{-1/2}\left( {\begin{array}{*{20}c}
-   { 0 } & \Lambda U^{\top}Z_1^\top & V^\top Z_2^\top  \\
-   {Z_1 U\Lambda  } & {0} & 0 \\
-   {Z_2V} & 0 & 0
+    H\left(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top\right): = n^{-1/2}\left( {\begin{array}{*{20}c}
+   { 0 } & \Lambda U^{\top}(Z^{(1)})^\top & V^\top (Z^{(2)})^\top  \\
+   {Z^{(1)} U\Lambda  } & {0} & 0 \\
+   {Z^{(2)}V} & 0 & 0
    \end{array}} \right).
  \end{equation}
-For simplicity of notations, we define the index sets
+For simplicity of notations, we abbreviate it as $H$ in the following discussion, and define the index sets
 $$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
- We will consistently use the latin letters $i,j\in\sI_{0}$, greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$, and $\fa,\fb,\mathfrak c\in \cal I$ \HZ{This $\fa, \fb$ notation is ugly.
-Why not just use $a,b$?}.
-Correspondingly, the indices of the matrices $Z_1$ and $Z_2$ are labelled as
+ We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
  \be\label{labelZ}
- Z_1= (z_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z_2= (z_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
+ Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
 Now we define the resolvents as follows.
@@
  \begin{equation}\label{eqn_defG}
- G (Z_1,Z_2,z):= \left[H(Z_1,Z_2)-\left( {\begin{array}{*{20}c}
+ G (z):= \left[H -\left( {\begin{array}{*{20}c}
    { z\id_{p}} & 0 & 0 \\
@@
       0 & 0  & { \id_{n_2}}\\
-\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C .
+\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C ,
  \end{equation}
@@
 %\begin{definition}[Index sets]\label{def_index}
-and the resolvent of $  n^{-1}\left(\Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)$ as
+and the resolvent of $  n^{-1}\left(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)$ as
 \be\label{mainG}
-\cal G(z):=\left( n^{-1}  \Lambda U^\top Z_1^\top Z_1 U\Lambda  + n^{-1}V^\top Z_2^\top Z_2V -z\right)^{-1},\quad z\in \C.
+\cal G(z):=\left( n^{-1}  \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + n^{-1}V^\top (Z^{(2)})^\top Z^{(2)}V -z\right)^{-1},\quad z\in \C.
 \ee
@@
 \ee
+We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof.
+We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
 \end{definition}
-With Schur complement formula, we can check that \HZ{Has $G(z)$ been defined before?}
+With Schur complement formula, we can check that %\HZ{Has $G(z)$ been defined before?}
  \begin{equation} \label{green2}
  G (z):=  \left( {\begin{array}{*{20}c}
-   { \cal G (z)} & \cal G(z)W  \\
-   W^\top \cal G(z) & z (W^\top W - z)^{-1}
+   { \cal G (z)} & \cal G(z)A  \\
+   A^\top \cal G(z) & z (A^\top A - z)^{-1}
 \end{array}} \right)^{-1}, %\quad \cal G_R:=(W^\top W - z)^{-1} ,
  \end{equation}
- where we abbreviated $W:=n^{-1/2}(\Lambda U^\top Z_1^\top, V^\top Z_2^\top)$.
-\HZ{$W$ is overloaded with the output layers} This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
+ where we abbreviated $A:= n^{-1/2}(\Lambda U^\top (Z^{(1)})^\top, V^\top (Z^{(2)})^\top)$. 
+ %\HZ{$W$ is overloaded with the output layers} 
+ This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
 On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
@@
 \Gi(z) := \begin{pmatrix} (-z\id_p+a_{1}(z)\Lambda^2  +  a_{2}(z)\id_p)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
-In particular, the matrix limit of $\cal G(z)$ is given by $(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}$.
+In particular, the matrix limit of $\cal G(z)$ is given by 
+\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}.\ee
 
 \medskip
-\noindent{\bf Deriving the bias and variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
-\be\label{rewrite X as R} (X_1^\top X_1+X_2^\top X_2)^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
+\noindent{\bf Deriving the variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
+\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
 When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
 Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
-\alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
+Then inserting this limit into \eqref{rewrite X as R}, we can write the left-hand side of \eqref{lem_cov_shift_eq} as
+\begin{align*}
+&\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \\
+&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,
+\end{align*}
+where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}.  This concludes \eqref{lem_cov_shift_eq} up to a small error.
+
+%\alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
 
 \medskip
-\noindent{\bf Gaussian case.} Now we give a heuristic derivation of the matrix limit when the entries of $Z_1$ and $Z_2$ are i.i.d. Gaussian. In this case,
-%However, notice that if the entries of $Z_1\equiv Z_1^{\text{Gauss}}$ and $Z_2\equiv Z_2^{\text{Gauss}}$ are i.i.d. Gaussian, then
+\noindent{\bf Gaussian case.} Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
+%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
 by the rotational invariance of the multivariate Gaussian distribution we have
-\be\label{eq in Gauss} Z_1 U\Lambda \stackrel{d}{=} Z_1 \Lambda, \quad Z_2 V \stackrel{d}{=} Z_2,\ee
+\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
 where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
@@
    G(z)= \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda Z_1^\top & n^{-1/2} Z_2^\top  \\
-   {n^{-1/2} Z_1 \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z_2} & 0 & {-\id_{n_2}}
+   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
    \end{array}} \right)^{-1}.
  \end{equation}
+
 \medskip
-\noindent{\bf Schur complements and concentration.}
+\noindent{\bf Schur complements.}
 %Now we discuss about how to obtain the matrix limit in equation \eqref{defn_piw}.
@@
 \begin{definition}[Resolvent minors]\label{defn_Minor}
- For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $\fa \in \mathcal I$, we define the minor $\cal A^{(\mathfrak c)}:=(\cal A_{\fa\fb}:\fa,\fb \in \mathcal I\setminus \{\mathfrak a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $\mathfrak c$-th row and column in $\cal A$.
-Note that we keep the names of indices when defining $\cal A^{(\mathfrak c)}$, i.e.
-$(\cal A^{(\mathfrak c)})_{\fa\fb}= \cal A_{\fa\fb}$ for $\fa,\fb \ne \mathfrak c$.
+ For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $a\in \mathcal I$, we define the minor $\cal A^{(a)}:=(\cal A_{a_1 a_2}:a_1, a_2 \in \mathcal I\setminus \{a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $a$-th row and column in $\cal A$.
+Note that we keep the names of indices when defining $\cal A^{(a)}$, i.e.
+$(\cal A^{(a)})_{a_1a_2}= \cal A_{a_1 a_2}$ for $a_1,a_2\ne a$.
 Correspondingly, we define the resolvent minor for $G$ in \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
@@
 G^{(\mathfrak c)}:&=\left[ \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda Z_1^\top & n^{-1/2} Z_2^\top  \\
-   {n^{-1/2} Z_1 \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z_2} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{(\mathfrak c)}\right]^{-1} ,
+   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{(a)}\right]^{-1} ,
 %= \left( {\begin{array}{*{20}c}
@@
 \end{align*}
-and define the partial traces $m^{(\mathfrak c)}$ and $m^{(\mathfrak c)}_k$, $k=0,1,2,$ by replacing $G$ with $G^{(\mathfrak c)}$ in equation \eqref{defm}.
-For convenience, we adopt the convention that for the resolvent minor $G^{(\mathfrak c)}$ defined as above, $G^{(\mathfrak c)}_{\fa\fb} = 0$ if $\fa =\mathfrak c$ or $\fb =\mathfrak c$.
+and define the partial traces $m^{(a)}$, $m_0^{(a)}$, $m_1^{(a)}$ and $m_2^{(a)}$ by replacing $G$ with $G^{(a)}$ in equation \eqref{defm}.
+We adopt the convention that for the resolvent minor $G^{(a)}$ defined as above, $G^{(a)}_{a_1a_2} = 0$ if $a_1 =a$ or $a_2=a$.
 \end{definition}
@@
 One will see a crucial use of this fact in the heuristic proof below.
- Using Schur complement formula (see {equation} (\ref{resolvent2})), we have that %for $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\HZ{This part needs more explanation - cannot understand.}
+ Using Schur complement formula (see {equation} (\ref{resolvent2})), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+%\HZ{This part needs more explanation - cannot understand.}
 \begin{align}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu},  \ \ \text{for }\  i \in \cal I_0 , \label{0self_Gii}\\
-\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j z_{\mu i}z_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  z_{\nu i}z_{\nu j}  G^{\left(\nu\right)}_{ij},  \ \ \text{for }\  \mu \in \cal I_1, \ \nu\in \cal I_2, \label{0self_Gmu1}
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} , \label{0self_Gii}
 \end{align}
-where we recall the notations in equation \eqref{labelZ}.
-For the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $z_{\mu i}$ and $z_{\nu i}$.
-Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{z_{\mu i}: \mu \in \cal I_1\cup \cal I_2\}$, i.e., with high probability,
+and for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\begin{align}
+\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij},
+\label{0self_Gmu1}
+\end{align}
+where we recall the notations in equation \eqref{labelZ}. To see why equation \eqref{0self_Gii} holds, we have that by Schur complement formula,
+\begin{align*}
+\frac{1}{G_{ii}}= -z - H_i G^{(i)}H_{i}^\top, \quad H_i = \left( \mathbf 0_{p-1}, (n^{-1/2}\lambda_i (Z^{(1)})^\top_{i\mu }:\mu \in \cal I_1),(n^{-1/2} (Z^{(2)})^\top_{i\nu }:\nu \in \cal I_2)\right),
+\end{align*}
+where $H_i$ is actually the $i$-th row of $H$ with the $(i,i)$-th entry removed.
+Expanding the above expression, we obtain equation \eqref{0self_Gii}.
+The two expressions in \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
+
+\medskip
+\noindent{\bf Concentration estimates.} Now for the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $Z^{(1)}_{\mu i}$ and $Z^{(2)}_{\nu i}$.
+Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with high probability,
 \begin{align*}
@@
 \begin{align}\label{1self_Gii}
- G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)\right)^{-1}.
+ G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1 +  \frac{\rho_2}{\rho_1+\rho_2}m_2+\oo(1)\right)^{-1}.
 \end{align}
@@
 with high probability.
+
 \medskip
-\noindent\textbf{Deriving the self-consistent equations.} Taking average of \eqref{1self_Gmu}, we obtain that
+\noindent\textbf{Deriving the self-consistent equations.} Now taking average of \eqref{1self_Gmu}, we obtain that
 \be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
 \ee
+with high probability. As a byproduct, comparing \eqref{1self_Gmu}  with \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
 with high probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
@@
 \medskip
-\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii}-\eqref{2self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
+\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
 with high probability.
@@
 For example, for $i\ne j\in \cal I_1$, by Schur complement formula (see (\ref{resolvent3})), we have
-$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j} \Big).$$
-Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
+$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
+Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
 The other off-diagonal entries can be bounded in the same way.
@@
 \medskip
-\noindent{\bf Deriving the bias asymptotics.} Finally, we describe ..........
-For the bias asymptotics, we can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
+\noindent{\bf Deriving the bias asymptotics.} Finally, we describe how to derive the bias asymptotics.
+We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
 More precisely, using equation \eqref{eigen2extra} we can obtain that
 \begin{align}
-n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
+&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
 &=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
 \end{align}
-where we used equation \eqref{rewrite X as R} in the second step. It is natural to guess that the matrix limit of $\cal G'(0)$ is given by
+where we used equation \eqref{rewrite X as R} in the second step.
+Since the matrix limit of $\cal G(z)$ is given by \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
 \be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
@@
 \begin{align*}
-n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ X_1^{\top}X_1 + X_2^{\top}X_2 }^{-1} \Sigma_1^{1/2} w}^2&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi w,
+& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2\\
+&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi w,
 \end{align*}
-which concludes \eqref{lem_cov_derv_eq}.
+where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$.
+This concludes \eqref{lem_cov_derv_eq}.
 Note that in order to have the approximate identity for $\cal G'(0)$ in \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
@@
 %For the variance asymptotic limit, we study the resolvent
-%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
 %Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
@@
 %For the bias asymptotic limit, we show in \todo{where?} that
-%$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
 %Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
@@
 The above arguments are the core of the main proof.
-To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z_1$ and $Z_2$ only satisfy certain moment assumptions.
+To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
 These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.

### 2020-09-13 arxiv/proof_main.tex
sec b.2

@@
 Then inserting this limit into \eqref{rewrite X as R}, we can write the left-hand side of \eqref{lem_cov_shift_eq} as
-\begin{align*}
-&\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \\
-&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,
-\end{align*}
+\begin{align}
+&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
+&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
+\end{align}
 where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}.  This concludes \eqref{lem_cov_shift_eq} up to a small error.
@@
 Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
-\begin{align*}
-& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2\\
-&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi w,
-\end{align*}
+\begin{align}
+& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+\end{align}
 where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$.

### 2020-09-15 arxiv/diff_cov.tex
sec b.2
wip

@@
 \begin{gather}\label{eq_a34extra}
-		\left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-		= b_0, \quad \left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1 .
+		\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+		= b_0 .
 %		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
@@
 %The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-In particular, by setting $X_1 = 0$, we obtain the following corollary, which is a well-known result in random matrix theory.
-\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
-	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}\Sigma} + o(\norm{\Sigma}). \ee
-\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
+In particular, by setting $X_1 = 0$, we obtain Lemma \ref{lem_minv}.
+%\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
+%	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
+%	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}\Sigma} + o(\norm{\Sigma}). \ee
+%\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
 To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.

### 2020-09-15 arxiv/setup.tex
sec b.2
wip

@@
 \subsection{Random Matrices}
-\todo{merge w/ theorem}
-We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.
-First, for every entry of $z_i$, we assume that its $(4+\e)$-th moment exists, that is, there exist constants $\e, C > 0$ such that
+
+We introduce several standard assumptions on the random matrices we study.
+\begin{assumption}\label{assume_rm}
+	Let $c > 4$ be a fixed value.
+	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
+entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
+	We assume that $\Sigma$ and $Z$ satisfy the following (standard) conditions, respectively.
+	\begin{enumerate}
+		\item[i)] Bounded moments: for every entry of $Z$, we assume that its $c$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
 			\begin{equation}\label{assmAhigh}
-	\ex{\abs{z_{i,j}}^{4+\e}} \le C,\ 1\le j \le p.
+				\ex{\abs{Z_{i,j}}^{c}} \le C, \text{ for any } 1\le i \le n, 1\le j \le p.
 			\end{equation}
-Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
-This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
-Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check, remove $c$ and $o(1)$ in main body}, the $l$-th moment of the noise entries exists:
-\begin{align*}
+		\item[ii)] Bounded singular values: the singular values of $\Sigma$ are bounded within a fixed range, that is, there exists two fixed values $C > C' > 0$ such that all of $\Sigma$'s singular values are bounded within $C'$ and $C$.
+	\end{enumerate}
+\end{assumption}
+
+\begin{lemma}[cf. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
+	Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
+	Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
+	Let $\e$ be any fixed value within $(0, \frac{c - 4}{2c})$.
+	With high probability over the randomness of $X$, we have that
+	\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 \cdot p}{n - p} + \OO(p^{-\e}). \]
+\end{lemma}
+
+%Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
+%This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
+Finally, for the random noise of every task, we assume that all $l$, the $l$-th moment of the noise entries exists:
+\begin{align}\label{assmAhigh2}
 	\ex{\abs{\varepsilon_{k, j}}^l \le C}, \text{ for all } j = 1, \dots, n_k.
-\end{align*}
+\end{align}

### 2020-09-16 arxiv/proof_same_cov.tex
sec 3 wip

@@
-	\section{Proof of Lemma \ref{lem_error_same_cov}}\label{app_proof_error_same_cov}
-	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
+	\section{Missing Proofs of Theorem \ref{thm_many_tasks}}\label{app_proof_error_same_cov}
+
+	\paragraph{Proof of equation \eqref{eq_gA}.}
+	To facilitate the analysis, we introduce the following notations.
+	Let
+		\[ \cE \define {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \text{ and } \cW \define U_X U_X^{\top} \cE (AA^{\top})^{-1}. \]
+	For any $j = 1,2,\dots, t$, let
+	\begin{align*}
+		H_j &\define B^{\star} A^{\top} (AA^{\top})^{-1} A_j - \beta^{(j)}, \\
+		E_j &\define \cW A_j - \varepsilon^{(j)}.
+	\end{align*}
+	Then, we have that
+	\[ g(A) = \sum_{j=1}^t \bignorm{H_j + E_j}^2. \]
+	To compute the expectation of $g(A)$, we first observe that for any first order terms of $\varepsilon^{(1)}, \dots, \varepsilon^{(t)}$, their expectation is zero. Therefore,
+	\begin{align*}
+		\exarg{\set{\varepsilon^{(j)}}_{j=1}^t }{g(A)} = \sum_{j=1}^t \norm{H_j}^2 + \exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{\sum_{j=1}^t \norm{E_j}^2}.
+	\end{align*}
+	Hence, it suffices to show that the second part of the equation above is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
+	Conditional on $X$, we have that
+	\begin{align*}
+		\exarg{\set{\varepsilon^{(j)}}_{j=1}^t}{\norm{E_j}^2}
+		= \exarg{\set{\varepsilon^{(j)}}_{j=1}^t}{\sum_{j=1}^t \bigbrace{\bignorm{\cW A_j}^2 - 2\inner{\cW A_j}{\varepsilon^{(j)}} }} + \sigma^2 \cdot n \cdot t.
+	\end{align*}
+	We consider both terms in the above equation one by one.
+	First, note that
+	\begin{align}
+		\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE (AA^{\top})^{-1} \cE^{\top}}.
+\label{eq_proof_same_cov_1}
+	\end{align}
+	We observe that
+	\begin{align*}
+			\exarg{\set{\varepsilon^{(j)}}_{i=1}^t}{\cE (AA^{\top})^{-1} \cE^{\top}}
+		&= \exarg{\set{\varepsilon^{(j)}}_{i=1}^t}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{-1} A_k {\varepsilon^{(k)}}^{\top}} \\
+		&= \exarg{\set{\varepsilon^{(j)}}_{i=1}^t}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{-1} A_j {\varepsilon^{(j)}}^{\top}} \\
+		&= \sigma^2 \cdot r \cdot \id_{n\times n}.
+	\end{align*}
+	In the above, the first equation uses the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
+	The second equation uses the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{-1} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
+	Therefore, we have that
+	\begin{align*}
+		\sum_{j=1}^t \norm{\cW A_j}^2 = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
+	\end{align*}
+	because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
+	Next, note that
+	\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW \cE^{\top}}, \]
+	which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$. Hence the proof is complete.
+
+	\paragraph{Proof of Lemma \ref{lem_error_same_cov}.} Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
 

### 2020-09-16 arxiv/setup.tex
sec 3 wip

@@
 
-\subsection{Notations.}
+\subsection{Notations}
 We shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
@@
 	\begin{enumerate}
-		\item[i)] Bounded moments: for every entry of $Z$, we assume that its $c$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-			\begin{equation}\label{assmAhigh}
-				\ex{\abs{Z_{i,j}}^{c}} \le C, \text{ for any } 1\le i \le n, 1\le j \le p.
-			\end{equation}
-		\item[ii)] Bounded singular values: the singular values of $\Sigma$ are bounded within a fixed range, that is, there exists two fixed values $C > C' > 0$ such that all of $\Sigma$'s singular values are bounded within $C'$ and $C$.
+		\item Bounded moments: for every entry of $Z$, we assume that its $c$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
+			\begin{align}\label{assmAhigh}
+				\ex{\abs{Z_{i,j}}^{c}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
+			\end{align}
+		\item Bounded singular values: the singular values of $\Sigma$ are bounded within a fixed range, that is, there exists two fixed values $C_{\max} > C_{\min} > 0$ such that all of $\Sigma$'s singular values are bounded within $C_{\min}$ and $C_{\max}$.
 	\end{enumerate}
@@
 
-\begin{lemma}[cf. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
-	Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
+Under the above assumption, we state several well-known facts regarding the random matrix $X$.
+
+\begin{fact}\label{lem_minv}
 	Let $\e$ be any fixed value within $(0, \frac{c - 4}{2c})$.
+	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
+	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
 	With high probability over the randomness of $X$, we have that
-	\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 \cdot p}{n - p} + \OO(p^{-\e}). \]
-\end{lemma}
+	\begin{enumerate}
+		\item The sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
+		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-\e})$, cf. Theorem 2.4 in \citet{isotropic}.
+	\end{enumerate}
+\end{fact}
 
@@
 %This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
-Finally, for the random noise of every task, we assume that all $l$, the $l$-th moment of the noise entries exists:
+Finally, for the random noise component, we assume that all of its moments exist.
+More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
 \begin{align}\label{assmAhigh2}
-	\ex{\abs{\varepsilon_{k, j}}^l \le C}, \text{ for all } j = 1, \dots, n_k.
+	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
 \end{align}

### 2020-09-17 arxiv/proof_same_cov.tex
polish

@@
 	\paragraph{Proof of equation \eqref{eq_gA}.}
-	To facilitate the analysis, we introduce the following notations.
+	To facilitate the analysis, we consider the following matrix notations.
 	Let
-		\[ \cE \define {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \text{ and } \cW \define U_X U_X^{\top} \cE (AA^{\top})^{-1}. \]
+		\[ \cE A^{\top} = {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \text{ and } \cW \define X(X^{\top} X)^{\top} X^{\top} \cE A^{\top} (AA^{\top})^{-1}. \]
 	For any $j = 1,2,\dots, t$, let
@@
 	\end{align*}
-	Then, we have that
-	\[ g(A) = \sum_{j=1}^t \bignorm{H_j + E_j}^2. \]
+	Then, we can write the function $g(A)$ conveniently as
+	\[ g(A) = \sum_{j=1}^t \bignorm{X H_j + E_j}^2. \]
 	To compute the expectation of $g(A)$, we first observe that for any first order terms of $\varepsilon^{(1)}, \dots, \varepsilon^{(t)}$, their expectation is zero. Therefore,
 	\begin{align*}
-		\exarg{\set{\varepsilon^{(j)}}_{j=1}^t }{g(A)} = \sum_{j=1}^t \norm{H_j}^2 + \exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{\sum_{j=1}^t \norm{E_j}^2}.
+		\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \sum_{j=1}^t \norm{\Sigma^{1/2} H_j}^2 + \exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{\sum_{j=1}^t \norm{E_j}^2}.
 	\end{align*}
@@
 	\begin{align}
-		\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE (AA^{\top})^{-1} \cE^{\top}}.
+		\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} \cE^{\top} A}.
 \label{eq_proof_same_cov_1}
@@
 	Next, note that
-	\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW \cE^{\top}}, \]
+	\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW \cE^{\top} A}, \]
 	which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$. Hence the proof is complete.

### 2020-09-18 arxiv/diff_cov.tex
revise

@@
 Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
-We introduce a key quantity $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
+We introduce a key matrix $M\equiv M(W_1/W_2): =\frac{W_1}{W_2} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
 
@@
 Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
-	\[ \Pi_\bias \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \]
+	\be\label{def Pibias} \Pi_\bias \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \ee
 where $a_{3}$ and $a_4$ are the solutions of the following two equations:
@@
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}). %\bigo{\|\| p^{-1/2+\epsilon}}
+		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
 	\end{align}
-
+where $(a_1,a_2)$ is the solution to equation \eqref{eq_a12extra} with $\lambda_i$ being the singular values of $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
 \end{lemma}
@@
 \end{equation}
-
+where $\Pi_\bias$ was defined in \eqref{def Pibias} with $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
 \end{lemma}

### 2020-09-19 arxiv/proof_same_cov.tex
wip

--- 2020-09-12 arxiv/proof_same_cov.tex
@@
-	\section{Proof of Lemma \ref{lem_error_same_cov}}\label{app_proof_error_same_cov}
-	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
+	\section{Missing Proofs of Theorem \ref{thm_many_tasks}}\label{app_proof_error_same_cov}
 
-	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
-	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
+	\paragraph{Proof of Claim \eqref{lem_exp_opt}.}
+	To facilitate the analysis, we consider the following matrix notations.
+	Let
+		\[ \cE A^{\top} = {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \text{ and } \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{-1}. \]
+	For any $j = 1,2,\dots, t$, let
+	\begin{align*}
+		H_j &\define B^{\star} A^{\top} (AA^{\top})^{-1} A_j - \beta^{(j)}, \\
+		E_j &\define \cW A_j - \varepsilon^{(j)}.
+	\end{align*}
+	Then, we can write the function $g(A)$ conveniently as
+	\[ g(A) = \sum_{j=1}^t \bignorm{X H_j + E_j}^2. \]
+	We will divide $g(A)$ into three parts.
+	First, we have that
+	\begin{align}\label{eq_gA_p1}
+		\sum_{j=1}^t \bignorm{X H_j}^2 = \bignorm{X (B^{\star} U_A U_A^{\top} - B^{\star})}^2,
+	\end{align}
+	whose expectation over $X$ is $\bignorm{\Sigma^{1/2}(B^{\star} U_A U_A^{\top} - B^{\star})}^2$.
+	Second, one can verify that the cross terms are equal to the following
+	\begin{align}\label{eq_gA_p2}
+		\sum_{j=1}^t\inner{XH_j}{E_j} = \inner{X(B^{\star} U_A U_A^{\top} - B^{\star})}{\cW A - \cE}
+		= - \inner{X (B^{\star} U_A U_A^{\top} - B^{\star})}{\cE},
+	\end{align}
+	which is zero in expectation over $\cE$.
+	Finally, we have that
+	\begin{align}\label{eq_gA_p3}
+		\sum_{j=1}^t \norm{E_j}^2 &= \bignorm{\cW A - \cE}^2
+		= \bignorm{\cE}^2 - \inner{\cW A}{\cE},
+	\end{align}
+	which is because $\norm{\cW A}^2 = \inner{\cW A}{\cE}$.
+	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
+	First, we have that $\ex{\cE} = \sigma^2 \cdot n \cdot t$.
+%	Conditional on $X$, we have that
+%	\begin{align*}
+%		\exarg{\cE}{\norm{E_j}^2}
+%		= \exarg{\cE}{\sum_{j=1}^t \bigbrace{\bignorm{\cW A_j}^2 - 2\inner{\cW A_j}{\varepsilon^{(j)}} }} + \sigma^2 \cdot n \cdot t.
+%	\end{align*}
+%	We consider both terms in the above equation one by one.
+	Second, note that
+	%\begin{align}
+	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}.
+\label{eq_proof_same_cov_1}
+	%\end{align}
+	%We observe that
+	\begin{align*}
+			\exarg{\cE}{\cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}
+		&= \exarg{\cE}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{-1} A_k {\varepsilon^{(k)}}^{\top}} \\
+		&= \exarg{\cE}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{-1} A_j {\varepsilon^{(j)}}^{\top}} \\
+		&= \sigma^2 \cdot r \cdot \id_{n\times n}.
+	\end{align*}
+	In the above, the first equation uses the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
+	The second equation uses the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{-1} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
+	Therefore, we have that
+	\begin{align*}
+		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
+	\end{align*}
+	because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
+	%Next, note that
+	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
+	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.
+	Hence the proof is complete.
+
+	\paragraph{Proof of Claim \ref{claim_opt_dist}.}
+	In order to show that the subspace spanned by the rows of $\hat{A}$ is close to $U_r$, we first show that $g(A)$ and its expectation is close as follows.
+	\begin{align}\label{eq_gA_err}
+		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-1/2 + e} \cdot \sigma^2 \cdot n \cdot t.
+	\end{align}
+	To show the above result, we consider the concentration error of each part of $g(A)$.
+
+	For equation \eqref{eq_gA_p1}, % $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
+%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
+	note that $X H_j = Z \Sigma^{1/2} H_j \in \real^n$ is a random vector with i.i.d.
+entries of mean zero, variance $\|\Sigma^{1/2}H_j\|^2$, and finite $\varphi$-th moment by Assumption \eqref{assume_rm}.
+	Hence by the law of large numbers, we have that with high probability
+	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1 + \OO(p^{-c}))$,
+	which implies that
+	\begin{align}
+		\abs{\sum_{j=1}^t \|X H_j\|^2 - \exarg{X}{\sum_{j=1}^t \norm{X H_j}^2}} \lesssim p^{-c} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
+	\end{align}
+
+	For equation \eqref{eq_gA_p2}, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, we obtain that the following holds with high probability:
+	\begin{align}
+		|\inner{XB^{\star} (U_AU_A^{\top} - \id)}{\cE}| &\le p^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id)} \nonumber \\
+		&\le p^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)} \nonumber \\
+		&\le p^{1/2 + \e} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}, \label{eq_gA_err2}
+	\end{align}
+	which is less than the right hand side of equation \eqref{eq_gA_err} by Cauchy-Schwartz inequality.
+	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
+	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
+
+	For equation \eqref{eq_gA_p3}, using Lemma \ref{largedeviation} and the fact that all moments of $\varepsilon_i$ exist, we obtain that with high probability
+	\begin{align}
+		\abs{\norm{\cE}^2 - \ex{\norm{\cE}^2}} \le p^{-1/2 + \e} \ex{\norm{\cE}^2}. \label{eq_gA_err3}
+	\end{align}
+	For the inner product between $\cW A$ and $\cE$, we have that
+	\begin{align}
+		\bigabs{\inner{\cW A}{\cE} - \ex{\inner{\cW A}{\cE}}} &= \bigabs{\bigtr{U_X U_X^{\top} (\cE U_AU_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n})}} \nonumber \\
+		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}}
+		&\le p^{1/2 + \e} \cdot sigma^2 r. \label{eq_gA_err4}
+	\end{align}
+	%\begin{align*}
+	%	%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
+	%	\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
+	%	&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
+  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
+  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
+  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
+	%\end{align*}
+	%Combining equation \eqref{eq_gA_}, we get that with high probability
+	%\begin{align}
+	%	\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_gA_err}
+	%\end{align}
+	Combining equation \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain that  equation \eqref{eq_gA_err} holds.
+
+	Next, we simplify $g(A)$ as follows
+	\begin{align*}
+		g(A)  &= \normFro{X (X^{\top}X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{-1} A - Y}^2 \\
+					&= \normFro{Y}^2 - \inner{A^{\top} (AA^{\top})^{-1} A}{Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y}.
+	\end{align*}
+	We denote $H = Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y$, which appears in the equation above.
+	Since $\hat{A}$ is a global minimum of $g(A)$, we have that
+	\begin{align*}
+		g(U_r) - g(\hat{A}) &= \abs{g(U_r) - g(\hat{A})} = \abs{\inner{H}{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top})^{-1} \hat{A}^{\top}}} \\
+												&\ge \lambda_{\min}(H) \cdot \normFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}.
+	\end{align*}
+	Recall that $Y = X B^{\star} + \cE$. Therefore, the minimum singular value of $H$ can be lowered bounded as follows
+	\begin{align*}
+		\lambda_{\min}(H) &= \lambda_{\min}({B^{\star}}^{\top} X^{\top} X B^{\star} + \cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE) \\
+		&\ge \lambda_{\min}({B^{\star}}^{\top}X^{\top}X B^{\star}) + \lambda_{\min}(\cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE) \\
+		&\ge \lambda_{\min}({B^{\star}}^{\top}\Sigma B^{\star}) \cdot \lambda_{\min}(Z^{\top}Z) + \lambda_{\min}(\cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE),
+	\end{align*}
+	where the second equation uses the fact that the minimum singular value of the sum of two PSD matrices is greater than the sum of the minimum singular value of each matrix, and the third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_la} in Appendix ??.
+
+		\medskip
+	\noindent\textbf{Dealing with the empirical minimizer.}
+	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
+	We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
+	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
+	Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
+	\begin{align*}
+		g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
+		&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
+	\end{align*}
+	On the other hand, by equation \eqref{eq_est_g} and triangle inequality, we have that
+	\begin{align*}
+		g(U_r) - g(\hat{\cW}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{\cW})}) + \bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
+		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
+		&\le o(n) \cdot \sigma_{\max}({B^{\star}}^{\top} \Sigma B^{\star}) + O(\sigma^2 p^{1/2 +\e}).
+	\end{align*}
+	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish to $o(1)$ as $p$ grows.
+	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
+	%In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
+	%$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
+	%where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
+	%with high probability
+	%\begin{align}
+	%g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
+	%&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
+	%\end{align}
+
+%		Applying the above estimates into $g_1(\cW)$, we get that
+%	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
+%	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
+%		Applying the above estimates into $g_1(\cW)$, we get that
+%	\begin{align}
+%	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
+%	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
+%	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
+%	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
+%	\end{align}
+%	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
+%	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
+%	In the last step, we use the AM-GM inequality.
+
+	\paragraph{Proof of Lemma \ref{lem_error_same_cov}.} Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
+
 	%and
@@
 	%\end{align*}
-	Applying the above estimates into $g_1(\cW)$, we get that
-	\begin{align}
-	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
-	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
-	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
-	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
-	\end{align}
-	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
-	In the last step, we use the AM-GM inequality.
 
-	Second, for $g_2(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for any $1\le i, j \le t$, the following holds with high probability:
 		\begin{align*}
-		\bigabs{\norm{\varepsilon_j}^2 - \ex{\norm{\varepsilon_j}^2}} &\le \sigma^2 p^{1/2+\e},\\
-		%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
-		\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
-		&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
-  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
+		g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+		g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
+				&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j},\\
+		g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
 					\end{align*}
-	Combining the above two inequalities together, we get that with high probability
-	\begin{align}
-		\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_est_g2}
-	\end{align}
-
-	Finally, for $g_0(\cW)$, denote by $v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right)$, for any $j = 1,\dots,t$, we have that $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
-%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
-	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}.
-	Hence by law of large numbers, we have that with high probability
-	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1+\oo(1))$,
-	which implies that
-	\begin{align}
-		g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)). \label{eq_est_g0}
-	\end{align}
-
-	Combining equation \eqref{eq_est_g1}, \eqref{eq_est_g2}, and \eqref{eq_est_g0}, we obtain that with high probability
-	\begin{align}
-	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
-	&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
-	\end{align}

### 2020-09-19 arxiv/setup.tex
wip

@@
 \begin{assumption}\label{assume_rm}
-	Let $c > 4$ be a fixed value.
+	Let $\varphi > 4$ be a fixed value.
 	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
@@
 			\begin{align}\label{assmAhigh}
-				\ex{\abs{Z_{i,j}}^{c}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
+				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
 			\end{align}
@@
 \begin{fact}\label{lem_minv}
-	Let $\e$ be any fixed value within $(0, \frac{c - 4}{2c})$.
+	Let $c$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
 	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
@@
 		\item The sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
-		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-\e})$, cf. Theorem 2.4 in \citet{isotropic}.
+		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-c})$, cf. Theorem 2.4 in \citet{isotropic}.
 	\end{enumerate}

### 2020-09-19 arxiv/proof_same_cov.tex
edit
wip

@@
 		\bigabs{\inner{\cW A}{\cE} - \ex{\inner{\cW A}{\cE}}} &= \bigabs{\bigtr{U_X U_X^{\top} (\cE U_AU_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n})}} \nonumber  \\
-		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}}
-		&\le p^{1/2 + \e} \cdot sigma^2 r. \label{eq_gA_err4}
+		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}} \nonumber \\
+		&\le p^{1/2 + \e} \cdot \sigma^2 r. \label{eq_gA_err4}
 	\end{align}
@@
 	Combining equation \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain that  equation \eqref{eq_gA_err} holds.
+	Next, using triangle inequality, we have that
+	\begin{align}
+		g(U_r) - g(\hat{A}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{A})}) + \bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
+		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
+		&\le p^{-c} \cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + e}\cdot \sigma^2 n \cdot t. \label{eq_g_gap}
+	\end{align}
+	The second equation uses the fact that $U_r$ is a global minimum of $\ex{g(\cdot)}$.
+	The third equation uses equation \eqref{eq_gA_err} and the fact that the spectral norm of an identity matrix minus a projection matrix is at most one.
+	On the other hand, we simplify $g(A)$ as follows
+	\begin{align*}
+		g(A)  &= \normFro{X (X^{\top}X)^{-1} X^{\top} Y U_A U_A^{\top} - Y}^2 \\
+					&= \normFro{Y}^2 - \inner{U_A U_A^{\top}}{Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y}.
+	\end{align*}
+	We denote $M = Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y$, which appears in the equation above.
+	Since $\hat{A}$ is a global minimum of $g(A)$, we have that
+	\begin{align}
+		g(U_r) - g(\hat{A}) &= \abs{g(U_r) - g(\hat{A})} = \abs{\inner{M}{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}} \nonumber \\
+												&\ge \lambda_{\min}(M) \cdot \normFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}. \label{eq_g_gap1}
+	\end{align}
+	Recall that $Y = X B^{\star} + \cE$. Therefore, the minimum singular value of $H$ can be lowered bounded as follows
+	\begin{align}
+		\lambda_{\min}(H) &= \lambda_{\min}({B^{\star}}^{\top} X^{\top} X B^{\star} + \cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE) \nonumber \\
+		&\ge \lambda_{\min}({B^{\star}}^{\top}X^{\top}X B^{\star}) + \lambda_{\min}(\cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE) \nonumber \\
+		&\ge \lambda_{\min}({B^{\star}}^{\top}\Sigma B^{\star}) \cdot \lambda_{\min}(Z^{\top}Z) + \lambda_{\min}(\cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE) \nonumber \\
+		&\ge \lambda_{\min}({B^{\star}}^{\top}\Sigma B^{\star}) \cdot ((\sqrt n - \sqrt p)^2 - n \cdot p^{-c}) + \sigma^2 \cdot p \cdot (1 - p^{-1/2 + \e}). \label{eq_g_gap2}
+	\end{align}
+	The second equation uses the fact that the minimum singular value of the sum of two PSD matrices is greater than the sum of the minimum singular value of each matrix.
+	The third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_la} in Appendix ??.
+	The last equation uses Fact \ref{lem_minv} for the minimum singular value of $Z^{\top}Z$ and Lemma \ref{largedeviation} for $\cE\cE^{\top}$.
 
-	Next, we simplify $g(A)$ as follows
+	%\noindent\textbf{Dealing with the empirical minimizer.}
+	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
+	%We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
+	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
+	%Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
+	%\begin{align*}
+	%	g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
+	%	&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
+	%\end{align*}
+	Combining equation \eqref{eq_g_gap}, \eqref{eq_g_gap1}, and \eqref{eq_g_gap2}, we conclude that
 	\begin{align*}
-		g(A)  &= \normFro{X (X^{\top}X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{-1} A - Y}^2 \\
-					&= \normFro{Y}^2 - \inner{A^{\top} (AA^{\top})^{-1} A}{Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y}.
+		\bignormFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}
+		\le \frac{p^{-c} \rho \normFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + \e} \cdot \sigma^2 \rho t}{\lambda_{\min}^2(\Sigma^{1/2} B^{\star}) ((\sqrt{\rho} - 1)^2 - \rho \cdot p^{-c}) + \sigma^2 (1 - p^{-1/2 + \e})}.
 	\end{align*}
-	We denote $H = Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y$, which appears in the equation above.
-	Since $\hat{A}$ is a global minimum of $g(A)$, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{A}) &= \abs{g(U_r) - g(\hat{A})} = \abs{\inner{H}{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top})^{-1} \hat{A}^{\top}}} \\
-												&\ge \lambda_{\min}(H) \cdot \normFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}.
-	\end{align*}
-	Recall that $Y = X B^{\star} + \cE$. Therefore, the minimum singular value of $H$ can be lowered bounded as follows
-	\begin{align*}
-		\lambda_{\min}(H) &= \lambda_{\min}({B^{\star}}^{\top} X^{\top} X B^{\star} + \cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE) \\
-		&\ge \lambda_{\min}({B^{\star}}^{\top}X^{\top}X B^{\star}) + \lambda_{\min}(\cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE) \\
-		&\ge \lambda_{\min}({B^{\star}}^{\top}\Sigma B^{\star}) \cdot \lambda_{\min}(Z^{\top}Z) + \lambda_{\min}(\cE^{\top} X (X^{\top} X)^{-1} X^{\top} \cE),
-	\end{align*}
-	where the second equation uses the fact that the minimum singular value of the sum of two PSD matrices is greater than the sum of the minimum singular value of each matrix, and the third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_la} in Appendix ??.
-
-		\medskip
-	\noindent\textbf{Dealing with the empirical minimizer.}
-	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
-	We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
-	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
-	Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
-		&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
-	\end{align*}
-	On the other hand, by equation \eqref{eq_est_g} and triangle inequality, we have that
-	\begin{align*}
-		g(U_r) - g(\hat{\cW}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{\cW})}) + \bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{\cW}) - \ex{g(\hat{\cW})}} \\
-		&\le o(n) \cdot \sigma_{\max}({B^{\star}}^{\top} \Sigma B^{\star}) + O(\sigma^2 p^{1/2 +\e}).
-	\end{align*}
-	Combined together, and using the assumption that the condition number of ${B^{\star}}^{\top}\Sigma B^{\star}$ does not grow with $p$ and $\sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \ge \sigma^2 / p^{1/2}$, we conclude that the distance between the two subspaces $\hat{\cW}^{\top}(\hat{\cW}\hat{\cW}^{\top})^{-1}\hat{\cW}$ and $U_r U_r^{\top}$ diminish to $o(1)$ as $p$ grows.
+	Hence for large enough $p$, we obtain that Claim \ref{claim_opt_dist} holds.
+	The proof is complete.
 	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
@@
 
-	\paragraph{Proof of Lemma \ref{lem_error_same_cov}.} Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
+	%\paragraph{Proof of Lemma \ref{lem_error_same_cov}.} Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
 
@@
 
-		\begin{align*}
-		g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-		g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
-				&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j},\\
-		g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
-					\end{align*}
+	%	\begin{align*}
+	%	g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
+	%	g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
+	%			&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j},\\
+	%	g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
+	%				\end{align*}

### 2020-09-19 arxiv/proof_same_cov.tex
sec 3

@@
 	The proof is complete.
+
+	\paragraph{Proof of Claim \ref{claim_pred_err}.}
+
+	\paragraph{Proof of Theorem \ref{thm_many_tasks}.}
+	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
+	Now we are ready to finish the proof.
+	Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
+	\begin{align}
+		L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
+	\end{align}
+	Using equation \eqref{eq_ex_pred}, we have that
+	\begin{align}
+		\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
+		+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
+		&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
+	\end{align}
+	In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
+	\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
+\]
+  In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
+	Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
 	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.

### 2020-09-19 arxiv/proof_main.tex
sec b.2
revise

@@
  \end{equation}
- where we abbreviated $A:= n^{-1/2}(\Lambda U^\top (Z^{(1)})^\top, V^\top (Z^{(2)})^\top)$. 
+ where we abbreviated 
+ \be\label{abbr_A}
+ A:= n^{-1/2}(\Lambda U^\top (Z^{(1)})^\top, V^\top (Z^{(2)})^\top).
+ \ee 
  %\HZ{$W$ is overloaded with the output layers} 
@@
 \begin{split}
-& \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) ,
+& \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
 \end{split}
 \ee
-satisfying that $\im a_{1}(z)>0$ and $\im a_{2}(z)>0$ for $z\in \C_+$ with $\im z$.
+%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
+The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}. 
 %Here, for simplicity of notations, we introduced the following ratios
@@
 \be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
-When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
+When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to equation \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
 Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
-Then inserting this limit into \eqref{rewrite X as R}, we can write the left-hand side of \eqref{lem_cov_shift_eq} as
+Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
 \begin{align}
@@
 \end{align}
-where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}.  This concludes \eqref{lem_cov_shift_eq} up to a small error.
+where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}.
+This concludes equation \eqref{lem_cov_shift_eq} up to a small error.
+The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
 
@@
 $(\cal A^{(a)})_{a_1a_2}= \cal A_{a_1 a_2}$ for $a_1,a_2\ne a$.
-Correspondingly, we define the resolvent minor for $G$ in \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
+Correspondingly, we define the resolvent minor for $G$ in equation \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
 \begin{align*}
@@
 One will see a crucial use of this fact in the heuristic proof below.
- Using Schur complement formula (see {equation} (\ref{resolvent2})), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+ Using Schur complement formulas in equation (\ref{resolvent2}), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
 %\HZ{This part needs more explanation - cannot understand.}
@@
 Expanding the above expression, we obtain equation \eqref{0self_Gii}.
-The two expressions in \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
+The two expressions in equation \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
 
@@
 \be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
-with high probability.
+with high probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
 
 \medskip
-\noindent\textbf{Deriving the self-consistent equations.} Now taking average of \eqref{1self_Gmu}, we obtain that
+\noindent\textbf{Deriving the self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
 \be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
 \ee
-with high probability. As a byproduct, comparing \eqref{1self_Gmu}  with \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+with high probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
 \be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
@@
 with high probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
-\begin{align*}
+\be\label{approximate m1m2}
+\begin{split}
 & \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
 & \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
-\end{align*}
+\end{split}
+\ee
 with high probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$. 
-Compare them to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
+A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}.
+Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
 \be\label{approx m12 add}
@@
 \ee
+To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
+This will be given by Lemma \ref{lem_stabw}.
 
@@
 For the off-diagonal entries, they are close to zero due to concentration.
-For example, for $i\ne j\in \cal I_1$, by Schur complement formula (see (\ref{resolvent3})), we have
+For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
 $$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
@@
 The other off-diagonal entries can be bounded in the same way.
+The bound on the off-diagonal entries will be given by Lemma \ref{Z_lemma}.
 
@@
 where we used equation \eqref{rewrite X as R} in the second step.
-Since the matrix limit of $\cal G(z)$ is given by \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
+Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
 \be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
@@
 \end{align}
-where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$.
-This concludes \eqref{lem_cov_derv_eq}.
-Note that in order to have the approximate identity for $\cal G'(0)$ in \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
+where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}. 
+Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
 This is the main reason why we need to take a general $z$ in the definition of resolvents.
+The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
 %In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
@@
 These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
-For the full rigorous proof, we refer the reader to Section \ref{sec_maintools}.
+For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-20 arxiv/diff_cov.tex
wip

@@
 We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
-Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
-Using the local optimality condition of $B$, we obtain that
-\begin{align*}
-	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
-	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
-	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-\end{align*}
-Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
-\begin{align}
-	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
-	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
-			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
-\end{align}
-Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
-equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
-%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Comparing the above to single-task learning, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
 

### 2020-09-20 arxiv/proof_same_cov.tex

@@
-	\section{Missing Proofs of Theorem \ref{thm_many_tasks}}\label{app_proof_error_same_cov}
+	\section{Missing Proof of the Same Covariates Setting}\label{app_proof_error_same_cov}
 
@@
 	The second equation uses the fact that the minimum singular value of the sum of two PSD matrices is greater than the sum of the minimum singular value of each matrix.
-	The third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_la} in Appendix ??.
+	The third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_proof_gA} in Appendix \ref{app_tool}.
 	The last equation uses Fact \ref{lem_minv} for the minimum singular value of $Z^{\top}Z$ and Lemma \ref{largedeviation} for $\cE\cE^{\top}$.

### 2020-09-20 arxiv/tools.tex

\section{Toolbox}\label{app_tool}

\subsection{Algebraic Inequalities}

\begin{fact}\label{fact_proof_gA}
	The minimum singular value of a matrix $X^{\top}YX$ is at least the minimum singular value of $Y$ times the minimum singular value of $X^{\top}X$.
\end{fact}

\subsection{Random Variables with Bounded Moments}
The following lemma gives (almost) sharp concentration bounds for linear and quadratic forms of bounded supported random variables.
%Besides the proof of Lemma \ref{prop_entry}, we also use it in several other places of this paper, including the proofs in Section \ref{sec_proof_general} and Section \ref{app_iso_cov}.
%It constitutes the main difference between our proof and the one in \cite{KY2}, where the authors used a large deviation bound for random variables with arbitrarily high moments.

\begin{lemma}[Lemma 3.8 of \cite{EKYY1} and Theorem B.1 of \cite{Delocal}]\label{largedeviation}
Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers. Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and $n^{-1/2}x_i$ and $n^{-1/2}y_j$ satisfy the bounded support condition (\ref{eq_support}) with $q\le n^{-\phi}$ for a small constant $\phi>0$. Then we have the following bounds:
%for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
\begin{align*}
\Big| \frac{1}{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  q \max_{i} \vert A_i \vert+ \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec q^2 B_d  + qB_o + \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}}, \\
\Big\vert \frac1n\sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec q B_d   , \quad &\Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec qB_o + \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,
\end{align*}
where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if all the moments of $\sqrt{n}x_i$ and $\sqrt{n}y_j$ exist in the sense of equation \eqref{assmAhigh2}, then we have stronger bounds
\begin{align}
\Big\vert \frac1{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
 \Big\vert  \frac1n \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec \frac1{n}\Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
\end{align}
\end{lemma}

### 2020-09-20 arxiv/proof_main.tex
revise

@@
 \noindent{\bf Concentration estimates.} Now for the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $Z^{(1)}_{\mu i}$ and $Z^{(2)}_{\nu i}$.
-Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with high probability,
+Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with overwhelming probability,
 \begin{align*}
@@
 \be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
-with high probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
+with overwhelming probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
 
@@
 \ee
-with high probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
 \be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
-with high probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
+with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
 \be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
-with high probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
+with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
 \be\label{approximate m1m2}
@@
 \ee
-with high probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$. 
+with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$. 
 A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}.
@@
 \be\label{approx m12 add}
-(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with high probability. }
+(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
 \ee
@@
 $$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
-with high probability.
+with overwhelming probability.
 These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}.
@@
 The other off-diagonal entries can be bounded in the same way.
-The bound on the off-diagonal entries will be given by Lemma \ref{Z_lemma}.
+The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
 

### 2020-09-20 arxiv/setup.tex
wip
revise

@@
 \subsection{Notations}
-We shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
-Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
+We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$. 
+We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)\ge 1- \oo(1)$, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
 For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
@@
 		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-c})$, cf. Theorem 2.4 in \citet{isotropic}.
+		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c}$.
 	\end{enumerate}

### 2020-09-20 arxiv/diff_cov.tex
wip

@@
 \section{The Different Covariates Setting}
+
 As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
-Therefore, we consider an arbitrary local minimum $B, W_1, W_2$, in particular when $B = \hat{B}(W_1, W_2)$ satisfies the local optimality condition.
-We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
+Therefore, we consider an arbitrary local minimum and provide generalization bounds that scale with key properties of task data such as sample sizes and covariate shifts.
+We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.
+%We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
+
+We first provide a key technical tool that we derived using recent developments in random matrix theory \cite{??}.
+To motivate our study, we consider a specialized setting where the output layer weights $A_1, A_2$ are both equal to one.
+Without loss of generality, we consider task two.
+For this setting, we can obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ by solving $B$ in equation \eqref{eq_mtl} as follows:
+\begin{align*}
+	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}
+\end{align*}
+Next, we derive the prediction loss of hard parameter sharing in expectation over the random noise, since the empirical quantity is close to the expectation similar to what we have shown in Claim \ref{claim_pred_err}:
+\begin{align*}
+	\exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}} =
+	\bignorm{(\Sigma^{(2)})^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2
+	+ \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}.
+\end{align*}
 
@@
 
-	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singluar values of the covariate shift matrix $M$:
+	In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singular values of the covariate shift matrix $M$:
 	\begin{align}

### 2020-09-20 arxiv/proof_main.tex
revise

@@
 %\subsection{The Bias and Variance Asymptotics}
-\paragraph{Proof overview.} 
+
 %\todo{merge} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
@@
 %We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-We use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $[(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}$ for $X^{(1)}= Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}= Z^{(2)}\Sigma_2^{1/2}$.
+
+\paragraph{Preliminaries.} Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $[(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}$ for $X^{(1)}= Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}= Z^{(2)}\Sigma_2^{1/2}$.
 %\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
@@
 \be\label{eigen2extra}[(X^{(1)})^\top (X^{(1)})+(X^{(2)})^\top (X^{(2)})]^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
-We divide the discussion into the following parts.
+%We divide the discussion into the following parts.
+To study the inverse $(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V)^{-1}$, we shall use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+We now give some preliminaries about
+this method before describing the proof strategy.
+
+\cor
+This has been more formal in work on deterministic equivalents, see e.g., \cite{Hachem2007deterministic,DS18}. 
+\nc
+
+\paragraph{Proof overview.} We divide the discussion into the following parts.
 

### 2020-09-22 arxiv/proof_main.tex

@@
 %We divide the discussion into the following parts.
-To study the inverse $(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V)^{-1}$, we shall use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-We now give some preliminaries about
-this method before describing the proof strategy.
+To study this expression, we shall use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+We now give some preliminaries about this method before discussing the proof strategy.
 
-\cor
-This has been more formal in work on deterministic equivalents, see e.g., \cite{Hachem2007deterministic,DS18}. 
-\nc
+For any measure $\mu$ supported on $[0,\infty)$, it defines a Stieltjes transform through
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z},\quad z\in \C\setminus [0,\infty).$$
+Conversely, given a Stieltjes transform $m_{\mu}(z)$, we can recover the measure $\mu$ through the inverse formula
+$$ \rho(x)=\frac{1}{\pi}\lim_{\eta \downarrow 0}\im m_{\mu}(x+\ii \eta),$$
+where $\rho(x)$ is the density for $\mu$, i.e.
+$\dd \mu(x)=\rho(x)\dd x$.
+Hence the Stieltjes transform method reduces the study of a measure $\mu$ to the study of an analytic function $m_\mu(z)$.
+Let $\mu=p^{-1}\sum_{i=1}^p \delta_{\sigma_i}$ be the empirical spectral distribution of the matrix $Y_p:=(n_1+n_2)^{-1}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V)$, where $\sigma_i$ denote the eigenvalues of $Y_p$, and the scaling $(n_1+n_2)^{-1}$ is chosen such that $\pi$ is supported on a bounded interval.
+Then with the above notations, the Stieltjes transform of the empirical spectral distribution $\mu$ is
+$$ m_{\mu}=\frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[ (Y_p-z\id_p)^{-1}\right].$$ 
+The Stieltjes transform method in random matrix theory aims to show that $m_{\mu}$ satisfies a fixed-point equation asymptotically, which allows us to derive the asymptotic limit of $\mu$.
+
+However, for our purpose, we not only need to know the limit of the trace $\tr\left[ (Y_p-z\id_p)^{-1}\right]$, but also need to obtain the limit of $\tr\left[ (Y_p-z\id_p)^{-1}B\right]$ for any given deterministic matrix $B$.
+This  requires us to study the matrix $(Y_p-z\id_p)^{-1}$ directly, which is called resolvent or Green's function.
+Roughly speaking, the resolvent can be regarded as a matrix version of the Stieltjes transform.
+The convergence of resolvent can be formulated formally in a slightly more modern language in terms of local laws, see e.g.
+\cite{isotropic,erdos2017dynamical,Anisotropic}, or deterministic equivalents, see e.g., \cite{Hachem2007deterministic,DS18}.
+More precisely, given a deterministic $p\times p$ matrix, say $R_p(z)$, of growing dimensions, we say that it is a deterministic equivalent of $(Y_p-z\id_p)^{-1}$ if for any sequence of deterministic matrices $B_p$ of uniformly bounded operator norms,
+$$\tr \left\{\left[ (Y_p-z\id_p)^{-1}-R_p(z)\right]B_p\right\}\to 0.$$
+If this holds, then we shall say that $(Y_p-z\id_p)^{-1}$ has a matrix limit $R_p$.
+In this paper, we shall prove a stronger convergence of the resolvent $(Y_p-z\id_p)^{-1}$ in the sense of local laws, which also gives an (almost) sharp convergence rate.
+Our proof will be centralized around the resolvent and its local law.
 

### 2020-09-24 arxiv/diff_cov.tex
wip

@@
 
-As mentioned in Section \ref{sec_prelim}, the optimization objective \eqref{eq_mtl} is non-convex in general.
-Therefore, we consider an arbitrary local minimum and provide generalization bounds that scale with key properties of task data such as sample sizes and covariate shifts.
+When the covariates across tasks are different, we can no longer obtain an optimal solution for minimizing equation \eqref{eq_mtl} as in Claim \ref{lem_exp_opt}.
+This is because the minimization problem is non-convex with respect to $A$ and $B$.
+Therefore, we consider an arbitrary local minimum of equation \eqref{eq_mtl} and provide generalization bounds that scale with key properties of task data such as sample sizes and covariate shifts.
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.
 %We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
+We will develop the key technical results in this section, and describe their implications in the next section.
 
@@
 To motivate our study, we consider a specialized setting where the output layer weights $A_1, A_2$ are both equal to one.
-Without loss of generality, we consider task two.
-For this setting, we can obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ by solving $B$ in equation \eqref{eq_mtl} as follows:
+Without loss of generality, we consider the prediction loss of hard parameter sharing for task two and the same analysis applies to task one.
+By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
 \begin{align*}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}
+	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
 \end{align*}
-Next, we derive the prediction loss of hard parameter sharing in expectation over the random noise, since the empirical quantity is close to the expectation similar to what we have shown in Claim \ref{claim_pred_err}:
+For the prediction loss, since the empirical loss is close to the expected loss similar to what we have shown in Claim \ref{claim_pred_err}, we consider the expected loss conditional on the covariates as follows:
 \begin{align*}

### 2020-09-24 arxiv/setup.tex
wip

@@
 		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-c})$, cf. Theorem 2.4 in \citet{isotropic}.
-		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c}$.
+		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c}$, cf.
+\citet[Theorem 2.10]{isotropic} and \citet[Lemma 3.12]{DY}.
 	\end{enumerate}
@@
 \end{align}
+Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
+Let $\e > 0$ denote \todo{?? to check}.

### 2020-09-24 arxiv/diff_cov.tex
wip

@@
 \end{align*}
-For the prediction loss, since the empirical loss is close to the expected loss similar to what we have shown in Claim \ref{claim_pred_err}, we consider the expected loss conditional on the covariates as follows:
+For the prediction loss, the empirical loss is close to the expected loss similar to what we have shown in Claim \ref{claim_pred_err}.
+Hence, we consider the expected loss conditional on the covariates as follows:
 \begin{align*}
@@
 
-Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
-We introduce a key matrix $M\equiv M(W_1/W_2): =\frac{W_1}{W_2} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
+Interestingly, the prediction loss admits a bias-variance decomposition similar to the same covariates setting.
+In both the bias and variance equations, the matrix inverse $\hat{\Sigma}^{-1}$ is a crucial quantity.
+Intuitively, this matrix inverse combines the sample covariance matrix of both tasks, and it is not hard to see that the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by the sample sizes.
+However, since the two tasks have different covariates, the scaling of $\hat{\Sigma}^{-1}$ not only depends on the tasks' sample sizes, but also depends on the covariate shift between the two tasks.
+We introduce a key result that show tight asymptotic convergence rate of the bias equation \eqref{eq_bias_2task} and the variance equation  as sample sizes increase to infinity.
+%The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
+We define a key quantity $M \define \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
+Let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
+%Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
 
-\begin{definition}[Limiting variance]
+\begin{theorem}
+	Suppose that $X_1$ and $X_2$ are both random matrices that satisfy Assumption \ref{assume_rm}.
+	Then we have the following asymptotic limits:
+	\begin{enumerate}
+		\item[i)] Limiting variance:
 		 	Define the following
 			\[ \Pi_{\vari} \define \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2}. \]
-
 			In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singular values of the covariate shift matrix $M$:
@@
 			\end{align}
-\end{definition}
-%We now state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
-The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
-
-\begin{definition}[Limiting bias]
-Recall that $a_1$ and $a_2$ are the solutions of the equation system \eqref{eq_a12extra}. Let
+			Then we have that
+			\begin{align}\label{lem_cov_shift_eq}
+				\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} = \bigtr{\Pi_{\vari}} + \OO(p^{-c}\norm{\Sigma^{(2)}}), %\bigo{\|\| p^{-1/2+\epsilon}}
+			\end{align}
+		\item[ii)] Limiting bias: Let
 			\be\label{def Pibias} \Pi_\bias \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \ee
@@
 				In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
-\end{definition}
+			Then, we have that
+			\begin{align}\label{lem_cov_derv_eq}
+				\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
+						= w^{\top} \Pi_\bias w + o(\|w\|^2),
+			\end{align}
+	\end{enumerate}
+\end{theorem}
 
-\begin{theorem}[Two-task case]\label{thm_main_informal}
+Lemma \ref{lem_cov_shift} also implies the asymptotic limit of the prediction loss of single-task learning.
+%The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
+In particular, by setting $X_1 = 0$, we obtain Lemma \ref{lem_minv}.
+%\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
+%	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
+%	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}\Sigma} + o(\norm{\Sigma}). \ee
+%\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
+To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.
+We briefly describe the history behind the above well-known result.
+When the entries of $X_2$ are multivariate Gaussian, this result recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
+Here we have stated a result from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp concentration error bound.
+One can see that our result extends Lemma \ref{lem_minv} from a single sample covariance matrix to the sum of two independent sample covariance matrices.
+%We now state our main result for two tasks with both covariate and model shift.
+It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
+The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
+
+Interestingly, the asymptotic limit of the variance only depends on the sample sizes and the covariate shift matrix.
+Next, we derive the asymptotic limit of the bias equation \eqref{eq_bias_2task}, which depends on the scaled model distance in addition to sample size and covariate shift.
+%(cf.
+Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
+
+\begin{corollary}[Two tasks with different covariates]\label{thm_main_informal}
 	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
@@
 %	\end{enumerate}
-\end{theorem}
+\end{corollary}
 In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
-We make several remarks about Theorem \ref{thm_main_informal}.
+We make several remarks about Corollary \ref{thm_main_informal}.
 First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
@@
 Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
+
+Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
+To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
+%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
+As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
+Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
+\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
+\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
+%We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
+%That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
+%We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
+%Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
+%Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
+%\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
+%In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
+%With high probability, we have that
+%\begin{equation}\label{lem_cov_derv_eq}
+%\begin{split}
+%\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
+%= w^{\top} \Pi_\bias w + o(\|w\|^2),
+%\end{split}
+%\end{equation}
+%where $\Pi_\bias$ was defined in \eqref{def Pibias} with $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+%\end{lemma}
+To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
+Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
+As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
+The formal proof of Theorem \ref{thm_main_informal} using Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be presented in Section \ref{app_proof_main_thm}.
+Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
+In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
 %While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
@@
 
-\paragraph{Key ingredients.}
-We introduce two key lemmas that show tight asymptotic convergence rate of the bias equation \eqref{eq_bias_2task} and the variance equation  as sample sizes increase to infinity.
-%The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
-For the covariate shift matrix $M$, let $\lambda_1, \lambda_2, \dots, \lambda_p$ be its singular values in descending order.
 %which deals with the inverse of the sum of two random matrices, which
@@
 
-\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
+%\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
 	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
@@
 	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
-	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
-	In the setting of Theorem \ref{thm_main_informal},
-	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
+%	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
+%	In the setting of Theorem \ref{thm_main_informal},
+%	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
 	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-	\begin{align}\label{lem_cov_shift_eq}
-		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
-	\end{align}
-where $(a_1,a_2)$ is the solution to equation \eqref{eq_a12extra} with $\lambda_i$ being the singular values of $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-\end{lemma}
-
-Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
-To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
-%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
-Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
-\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
-
-Lemma \ref{lem_cov_shift} also implies the asymptotic limit of the prediction loss of single-task learning.
-%The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-In particular, by setting $X_1 = 0$, we obtain Lemma \ref{lem_minv}.
-%\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
-%	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-%	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}\Sigma} + o(\norm{\Sigma}). \ee
-%\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
-To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.
-We briefly describe the history behind the above well-known result.
-When the entries of $X_2$ are multivariate Gaussian, this result recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we have stated a result from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp concentration error bound.
-One can see that our result extends Lemma \ref{lem_minv} from a single sample covariance matrix to the sum of two independent sample covariance matrices.
-
-Interestingly, the asymptotic limit of the variance only depends on the sample sizes and the covariate shift matrix.
-Next, we derive the asymptotic limit of the bias equation \eqref{eq_bias_2task}, which depends on the scaled model distance in addition to sample size and covariate shift.
-%(cf.
-Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
-We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
-That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
-We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
-Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
-
-Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
-\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
-With high probability, we have that
-\begin{equation}\label{lem_cov_derv_eq}
-\begin{split}
-\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-= w^{\top} \Pi_\bias w + o(\|w\|^2),
-\end{split}
-\end{equation}
-where $\Pi_\bias$ was defined in \eqref{def Pibias} with $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-\end{lemma}
-To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
-Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
-As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
-The formal proof of Theorem \ref{thm_main_informal} using Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be presented in Section \ref{app_proof_main_thm}.
-Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
-In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
-
-%In Section \ref{app_proof_main_thm},
+%	\begin{align}\label{lem_cov_shift_eq}
+%		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
+%	\end{align}
+%where $(a_1,a_2)$ is the solution to equation \eqref{eq_a12extra} with $\lambda_i$ being the singular values of $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+%\end{lemma}
 
@@
 In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
-The full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be given in Section \ref{appendix RMT}
+The full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be given in Section \ref{appendix RMT}.
+%\subsection{The Bias and Variance Asymptotics}
+
+%\todo{merge} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
+%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
+%We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+
+\paragraph{Preliminaries.} Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $[(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}$ for $X^{(1)}= Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}= Z^{(2)}\Sigma_2^{1/2}$.
+%\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
+Suppose $M=\Sig_1^{1/2} \Sig_2^{-1/2}$ has a singular value decomposition
+\be\label{eigen2}
+M= U\Lambda V^\top, \quad \Lambda=\text{diag}( \lambda_1, \ldots, \lambda_p).
+\ee
+Then using equation \eqref{eigen2}, we can write
+\be\label{eigen2extra}[(X^{(1)})^\top (X^{(1)})+(X^{(2)})^\top (X^{(2)})]^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
+%We divide the discussion into the following parts.
+To study this expression, we shall use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+We now give some preliminaries about this method before discussing the proof strategy.
+
+For any measure $\mu$ supported on $[0,\infty)$, it defines a Stieltjes transform through
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z},\quad z\in \C\setminus [0,\infty).$$
+Conversely, given a Stieltjes transform $m_{\mu}(z)$, we can recover the measure $\mu$ through the inverse formula
+$$ \rho(x)=\frac{1}{\pi}\lim_{\eta \downarrow 0}\im m_{\mu}(x+\ii \eta),$$
+where $\rho(x)$ is the density for $\mu$, i.e.
+$\dd \mu(x)=\rho(x)\dd x$.
+Hence the Stieltjes transform method reduces the study of a measure $\mu$ to the study of an analytic function $m_\mu(z)$.
+Let $\mu=p^{-1}\sum_{i=1}^p \delta_{\sigma_i}$ be the empirical spectral distribution of the matrix $Y_p:=(n_1+n_2)^{-1}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V)$, where $\sigma_i$ denote the eigenvalues of $Y_p$, and the scaling $(n_1+n_2)^{-1}$ is chosen such that $\pi$ is supported on a bounded interval.
+Then with the above notations, the Stieltjes transform of the empirical spectral distribution $\mu$ is
+$$ m_{\mu}=\frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[ (Y_p-z\id_p)^{-1}\right].$$
+The Stieltjes transform method in random matrix theory aims to show that $m_{\mu}$ satisfies a fixed-point equation asymptotically, which allows us to derive the asymptotic limit of $\mu$.
+
+However, for our purpose, we not only need to know the limit of the trace $\tr\left[ (Y_p-z\id_p)^{-1}\right]$, but also need to obtain the limit of $\tr\left[ (Y_p-z\id_p)^{-1}B\right]$ for any given deterministic matrix $B$.
+This  requires us to study the matrix $(Y_p-z\id_p)^{-1}$ directly, which is called resolvent or Green's function.
+Roughly speaking, the resolvent can be regarded as a matrix version of the Stieltjes transform.
+The convergence of resolvent can be formulated formally in a slightly more modern language in terms of local laws, see e.g.
+\cite{isotropic,erdos2017dynamical,Anisotropic}, or deterministic equivalents, see e.g., \cite{Hachem2007deterministic,DS18}.
+More precisely, given a deterministic $p\times p$ matrix, say $R_p(z)$, of growing dimensions, we say that it is a deterministic equivalent of $(Y_p-z\id_p)^{-1}$ if for any sequence of deterministic matrices $B_p$ of uniformly bounded operator norms,
+$$\tr \left\{\left[ (Y_p-z\id_p)^{-1}-R_p(z)\right]B_p\right\}\to 0.$$
+If this holds, then we shall say that $(Y_p-z\id_p)^{-1}$ has a matrix limit $R_p$.
+In this paper, we shall prove a stronger convergence of the resolvent $(Y_p-z\id_p)^{-1}$ in the sense of local laws, which also gives an (almost) sharp convergence rate.
+Our proof will be centralized around the resolvent and its local law.
+
+\paragraph{Proof overview.} We divide the discussion into the following parts.
+
+\medskip
+\noindent\textbf{Defining the resolvents.} For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
+$$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
+which is linear in $A$.
+This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
+Our goal is to study the SVD of the rectangular matrix $(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top)$.
+%For this purpose,
+%}\HZ{what does this trick mean? use less technical words},
+%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
+Then we define the following $(p+n)\times (p+n)$ symmetric block matrix
+%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
+%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
+%We define the $(n+N)\times (n+N)$ block matrix
+ \begin{equation}\label{linearize_block}
+    H\left(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top\right): = n^{-1/2}\left( {\begin{array}{*{20}c}
+   { 0 } & \Lambda U^{\top}(Z^{(1)})^\top & V^\top (Z^{(2)})^\top  \\
+   {Z^{(1)} U\Lambda  } & {0} & 0 \\
+   {Z^{(2)}V} & 0 & 0
+   \end{array}} \right).
+ \end{equation}
+For simplicity of notations, we abbreviate it as $H$ in the following discussion, and define the index sets
+$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
+ We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
+ \be\label{labelZ}
+ Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
+Now we define the resolvents as follows.
+\begin{definition}[Resolvents]
+We define the resolvent (or Green's function) of $H$ as
+ \begin{equation}\label{eqn_defG}
+ G (z):= \left[H -\left( {\begin{array}{*{20}c}
+   { z\id_{p}} & 0 & 0 \\
+   0 & { \id_{n_1}}  & 0\\
+      0 & 0  & { \id_{n_2}}\\
+\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C ,
+ \end{equation}
+%It is easy to verify that the eigenvalues $\lambda_1(H)\ge \ldots \ge \lambda_{n+N}(H)$ of $H$ are related to the ones of $\mathcal Q_1$ through
+%\begin{equation}\label{Heigen}
+%\lambda_i(H)=-\lambda_{n+N-i+1}(H)=\sqrt{\lambda_i\left(\mathcal Q_2\right)}, \ \ 1\le i \le n\wedge N, \quad \text{and}\quad \lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.
+%\end{equation}
+%and
+%$$\lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.$$
+%where we used the notations $n\wedge N:=\min\{N,M\}$ and $n\vee N:=\max\{N,M\}$.
+%\begin{definition}[Index sets]\label{def_index}
+and the resolvent of $  n^{-1}\left(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)$ as
+\be\label{mainG}
+\cal G(z):=\left( n^{-1}  \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + n^{-1}V^\top (Z^{(2)})^\top Z^{(2)}V -z\right)^{-1},\quad z\in \C.
+\ee
+Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
+\be\label{defm}
+\begin{split}
+m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
+ m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
+\end{split}
+\ee
+We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof.
+We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
+\end{definition}
+With Schur complement formula, we can check that %\HZ{Has $G(z)$ been defined before?}
+ \begin{equation} \label{green2}
+ G (z):=  \left( {\begin{array}{*{20}c}
+   { \cal G (z)} & \cal G(z)A  \\
+   A^\top \cal G(z) & z (A^\top A - z)^{-1}
+\end{array}} \right)^{-1}, %\quad \cal G_R:=(W^\top W - z)^{-1} ,
+ \end{equation}
+ where we abbreviated
+ \be\label{abbr_A}
+ A:= n^{-1/2}(\Lambda U^\top (Z^{(1)})^\top, V^\top (Z^{(2)})^\top).
+ \ee
+ %\HZ{$W$ is overloaded with the output layers}
+ This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
+On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
+%one can find that %(recall equation \eqref{mainG})
+%\be \label{green2}
+%\begin{split}
+%& \cal G_{L}=\left(WW^\top -z \right)^{-1} =\cal G ,\quad \cal G_{LR}=\cal G_{RL}^\top  = \cal G W , \quad \cal G_R= z\left(W^\top W - z\right)^{-1}.
+%\end{split}
+%\ee
+%, and the subindex of $\cal G_R$ means the lower-right block.
+
+%Now using Schur complement formula, we can verify that the (recall equation \eqref{def_green})
+%\begin{align}
+%G = \left( {\begin{array}{*{20}c}
+%   { z\mathcal G_1} & \mathcal G_1 \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2}  \\
+%   {\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} \mathcal G_1} & { \mathcal G_2 }  \\
+%\end{array}} \right) = \left( {\begin{array}{*{20}c}
+%   { z\mathcal G_1} & \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2} \mathcal G_2   \\
+%   {\mathcal G_2}\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} & { \mathcal G_2 }  \\
+%\end{array}} \right). \label{green2}
+%\end{align}
+%where $\mathcal G_{1,2}$ are defined in (\ref{def_green}).
+
+\medskip
+\noindent\textbf{Defining the asymptotic limits of the resolvents.}
+%\label{sec aymp_limit_G}
+%\subsection{Resolvents and limiting law}
+We now describe the asymptotic limit of $G(z)$ as $n\to \infty$.
+First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
+%\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)},
+the unique solution to the following system of equations
+\begin{equation}\label{selfomega_a}
+\begin{split}
+& \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
+\end{split}
+\ee
+%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
+The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}.
+%Here, for simplicity of notations, we introduced the following ratios
+%\be\label{ratios}
+% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
+%\ee
+We define the matrix limit of $G(z)$ as
+\be \label{defn_piw}
+\Gi(z) := \begin{pmatrix} (-z\id_p+a_{1}(z)\Lambda^2  +  a_{2}(z)\id_p)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
+In particular, the matrix limit of $\cal G(z)$ is given by
+\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}.\ee
+
+\medskip
+\noindent{\bf Deriving the variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
+\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
+When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to equation \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
+Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
+Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
+\begin{align}
+&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
+&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
+\end{align}
+where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}.
+This concludes equation \eqref{lem_cov_shift_eq} up to a small error.
+The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
+
+%\alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
+
+\medskip
+\noindent{\bf Gaussian case.} Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
+%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
+by the rotational invariance of the multivariate Gaussian distribution we have
+\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
+where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
+ \begin{equation} \label{resolv Gauss1}
+   G(z)= \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{-1}.
+ \end{equation}
+
+\medskip
+\noindent{\bf Schur complements.}
+%Now we discuss about how to obtain the matrix limit in equation \eqref{defn_piw}.
+%\HZ{Divide into several parts like sec 7 to improve readability.}
+The core quantities of the derivation are the following resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
+\begin{definition}[Resolvent minors]\label{defn_Minor}
+ For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $a\in \mathcal I$, we define the minor $\cal A^{(a)}:=(\cal A_{a_1 a_2}:a_1, a_2 \in \mathcal I\setminus \{a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $a$-th row and column in $\cal A$.
+Note that we keep the names of indices when defining $\cal A^{(a)}$, i.e.
+$(\cal A^{(a)})_{a_1a_2}= \cal A_{a_1 a_2}$ for $a_1,a_2\ne a$.
+Correspondingly, we define the resolvent minor for $G$ in equation \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
+\begin{align*}
+G^{(\mathfrak c)}:&=\left[ \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{(a)}\right]^{-1} ,
+%= \left( {\begin{array}{*{20}c}
+%   { \mathcal G^{(\mathbb T)}} & \mathcal G^{(\mathbb T)} W^{(\mathbb T)}  \\
+%   {\left(W^{(\mathbb T)}\right)^\top\mathcal G^{(\mathbb T)}} & { \mathcal G_R^{(\mathbb T)} }  \\
+%\end{array}} \right)  ,
+\end{align*}
+and define the partial traces $m^{(a)}$, $m_0^{(a)}$, $m_1^{(a)}$ and $m_2^{(a)}$ by replacing $G$ with $G^{(a)}$ in equation \eqref{defm}.
+We adopt the convention that for the resolvent minor $G^{(a)}$ defined as above, $G^{(a)}_{a_1a_2} = 0$ if $a_1 =a$ or $a_2=a$.
+\end{definition}
+%Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
+One will see a crucial use of this fact in the heuristic proof below.
+ Using Schur complement formulas in equation (\ref{resolvent2}), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+%\HZ{This part needs more explanation - cannot understand.}
+\begin{align}
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} , \label{0self_Gii}
+\end{align}
+and for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\begin{align}
+\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij},
+\label{0self_Gmu1}
+\end{align}
+where we recall the notations in equation \eqref{labelZ}. To see why equation \eqref{0self_Gii} holds, we have that by Schur complement formula,
+\begin{align*}
+\frac{1}{G_{ii}}= -z - H_i G^{(i)}H_{i}^\top, \quad H_i = \left( \mathbf 0_{p-1}, (n^{-1/2}\lambda_i (Z^{(1)})^\top_{i\mu }:\mu \in \cal I_1),(n^{-1/2} (Z^{(2)})^\top_{i\nu }:\nu \in \cal I_2)\right),
+\end{align*}
+where $H_i$ is actually the $i$-th row of $H$ with the $(i,i)$-th entry removed.
+Expanding the above expression, we obtain equation \eqref{0self_Gii}.
+The two expressions in equation \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
+
+\medskip
+\noindent{\bf Concentration estimates.} Now for the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $Z^{(1)}_{\mu i}$ and $Z^{(2)}_{\nu i}$.
+Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with overwhelming probability,
+\begin{align*}
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
+\end{align*}
+where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$.
+Intuitively, since we have removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
+Hence we obtain from the above equation that
+\begin{align}\label{1self_Gii}
+ G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1 +  \frac{\rho_2}{\rho_1+\rho_2}m_2+\oo(1)\right)^{-1}.
+\end{align}
+Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
+with overwhelming probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
+
+\medskip
+\noindent\textbf{Deriving the self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
+\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
+\ee
+with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
+with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
+\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
+with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
+\be\label{approximate m1m2}
+\begin{split}
+& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
+& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
+\end{split}
+\ee
+with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
+A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}.
+Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
+\be\label{approx m12 add}
+(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
+\ee
+To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
+This will be given by Lemma \ref{lem_stabw}.
+
+\medskip
+\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
+with overwhelming probability.
+These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}.
+For the off-diagonal entries, they are close to zero due to concentration.
+For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
+$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
+Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
+The other off-diagonal entries can be bounded in the same way.
+The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
+
+\medskip
+\noindent{\bf Deriving the bias asymptotics.} Finally, we describe how to derive the bias asymptotics.
+We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
+More precisely, using equation \eqref{eigen2extra} we can obtain that
+\begin{align}
+&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
+&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
+\end{align}
+where we used equation \eqref{rewrite X as R} in the second step.
+Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
+\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
+If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
+Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
+\begin{align}
+& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+\end{align}
+where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
+Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
+This is the main reason why we need to take a general $z$ in the definition of resolvents.
+The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
+%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
+%For the variance asymptotic limit, we study the resolvent
+%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
+%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
+%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
+%
+%For the bias asymptotic limit, we show in \todo{where?} that
+%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
+%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
+
+The above arguments are the core of the main proof.
+To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
+These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
+For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-24 arxiv/implications.tex
update
revise

@@
 %\end{align*}}
+
+\subsection{Sample Efficiency}
+
+observed in Taskonomy \cite{ZSSGM18}.
 
@@
 \end{proposition}
+\cor
+
+ \begin{claim}\label{claim_covar_shift}
+		In the setting of Proposition \ref{prop_covariate}, for any $M\in \cal S_\mu$ we have that
+		\[ g(M)=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.} \]
+	\end{claim}
+
+%Finally, in this subsection we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.
+
+\begin{proof}[Proof of Proposition \ref{prop_covariate}]
+
+ Denote the minimizer of $g$ by 
+$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
+We now calculate $g(M_0)$.
+
+Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
+\begin{align}\label{gvar_extra}
+g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
+\end{align}
+From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
+\be\label{est_a12extra}
+\frac{\rho_1-1}{\rho_1+\rho_2} < a_1(M)<  \frac{\rho_1+\rho_2-1}{\rho_1+\rho_2},\quad a_2(M) < \frac{\rho_2}{\rho_1+\rho_2}.
+\ee
+Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
+\begin{align}\label{approximateteM}
+\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
+\end{align}
+where
+$$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
+%With these two bounds, we can easily conclude \eqref{approxteM}. 
+%
+%We have that the test error satisfies
+%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
+%where $\lambda_p$ is the smallest singular value of $p$ and
+%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
+%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+By AM-GM inequality, we observe that 
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
+is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
+\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
+On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
+\begin{align}\label{gvar_extra2}
+\begin{split}
+g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
+&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
+\end{split}
+\end{align}
+Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
+%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+\end{proof}
+\nc
+
 Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
@@
 %On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
-\subsection{Sample Efficiency}
-
-observed in Taskonomy \cite{ZSSGM18}.

### 2020-09-24 arxiv/proof_examples.tex
wip
pf overview
revise

@@
 \section{Proof of the Special Case}\label{app_iso_cov}
+\todo{switch the $a_3$ and $a_4$}
 
@@
 
+\begin{proof}[Proof of Claim \ref{claim_covar_shift}]	
+	With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
+Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
+\be \nonumber
+\begin{split}
+g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
+\end{split}
+\ee
+ for some constant $\e>0$.
+In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
+We omit the details here.
+ \end{proof}
+
 \subsection{Task Similarity}\label{app_proof_31}
@@
 
+\iffalse
+
 \subsection{Covariate Shift}\label{app_proof_33}
@@
 
-%--------old arguments
-%With the same arguments as in Lemma \ref{lem_hat_v} we can show that \eqref{hatv_add1} holds, and under the choice of parameters \eqref{choiceofpara},
-%\be \nonumber
-%\begin{split}
-%g(M)&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1)(X_1^{\top}X_1 +X_2^{\top}X_2)^{-1}\Sigma_2(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)\right] \\ 
-%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  =: \delta_{\bias}(M)+ g_{\vari}(M),
-%\end{split}
-%\ee
-%with high probability for any constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $\lambda(M)\in [\mu_{\min},\mu_{\max}]$.
-We omit the details here.
-%
-%
-%With Lemma \ref{lem_cov_shift}, we can obtain that with high probability,
-%\begin{align}\label{gvar_extra}
-%g_{\vari}(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0 + a_2}\right)  +\OO(p^{-1/2+\e}),
-%\end{align}
-%where $(a_1,a_2)$ satisfies \eqref{eq_a12extra}. On the other hand, by Theorem \ref{thm_model_shift} we can estimate $\delta_{\bias}$ as
-%\be \label{deltabeta_extra}
-%\begin{split}
-%&\left| \delta_{\bias}(M_0) - \frac{d^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \tr\left[\Sigma_1^{1/2}{M_0} \frac{(1 + a_3)\id + a_4 {M_0}^{\top}{M_0}}{(a_2 + a_1 {M_0}^{\top}{M_0})^2} {M_0}^{\top}\Sigma_1^{1/2}\right]\right| \le \delta + \OO(p^{1-\e}d^2),
-%\end{split}
-%\ee
-%where $(a_3,a_4)$ satisfies \eqref{eq_a34extra} and $\delta$ is defined in \eqref{eq_deltaextra}.
-%
-%
-%Next we derive some estimates for $a_i$, $i=1,2,3,4$. From equation \eqref{eq_a12extra}, it is easy to see that
-%\be\label{est_a12extra}a_1\ge \frac{\rho_1-1}{\rho_1+\rho_2},\quad a_2\le \frac{\rho_2}{\rho_1+\rho_2}.\ee
-%Then solving \eqref{eq_a34extra}, we get that
-%\begin{align}
-%0\le a_3&= \frac{ b_0 (\rho_1a_1^{-2}-b_2) + b_1^2 }{  \left(\rho_2  a_2^{-2}-  b_0\right)\left(\rho_1 a_1^{-2} -  b_2  \right) - b_1^2} \le \frac{ b_0 \rho_1a_1^{-2}  }{  \rho_1\rho_2  a_1^{-2}a_2^{-2}-  b_0\rho_1 a_1^{-2} - b_2\rho_2  a_2^{-2}}\nonumber\\
-%&\le \frac{\rho_1}{\rho_1\rho_2-\rho_1 -\rho_2 },\label{est_a3extra}
-%\end{align}
-%and
-%\begin{align}
-%0\le a_4&= \frac{b_1\rho_2 a_2^{-2}}{\left(\rho_2  a_2^{-2}-  b_0\right)\left(\rho_1 a_1^{-2} -  b_2  \right) - b_1^2} \le  \frac{ b_1\rho_2 a_2^{-2} }{  \rho_1\rho_2  a_1^{-2}a_2^{-2}-  b_0\rho_1 a_1^{-2} - b_2\rho_2  a_2^{-2}} \nonumber\\
-%&\le  \frac{ \rho_2 (b_1a_1^{2}) }{  \rho_1\rho_2 -  \rho_1  - \rho_2 } \le \frac{\rho_2\cdot \mu_{\min}^{-2}}{\rho_1\rho_2-\rho_1-\rho_2}=\OO\left( \frac{1}{\rho_1}\right),\label{est_a4extra}
-%\end{align}
-%where in the above derivations we also used that $b_1^2\le b_0 b_2$ by Cauchy-Schwarz inequality, $b_0 a_2^2 < 1$, $b_2 a_1^2 < 1$, and $b_1 a_1^2 \le \mu_{\min}^{-2}$.
-%Inserting \eqref{est_a12extra} into \eqref{gvar_extra}, we obtain that with high probability,
-%\begin{align}\label{approximateteM}
-%\le g(M_0) \le  \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0}\right) \cdot \left(1 +\OO(p^{-\e})\right)
-%\end{align}
-%where
-%$$\wt g(M_0):=\frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1M_0^\top M_0}\right)  +\frac{pd^2\cdot \rho_1^2}{(\rho_1 + \rho_2)^2} \cdot \frac1p\tr\left(\Sigma_1\frac{1 + a_3}{a_1^2 M_0^{\top}{M_0}} \right),$$
-%and the error satisfies
-%$$|\cal E|\le C\left( \frac{\rho_2}{\rho_1} +\rho_1^{-1/2} +\OO(p^{-\e})\right)\wt g(M_0).$$
-%Here the constant $C>0$ depends only on $\mu_{\max}$, $\mu_{\min}$ and $\|\Sigma_1\|$, but otherwise does not depend on $\rho_1$ and $\rho_2$. 
-%--------end old argument---------
-
-\iffalse
 In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
@@
 
-%\subsection{Proofs for Section \ref{sec_covariate}}\label{app_covariate}
-
-\subsection{Denoising}
+\iffalse
+\subsection{Label Denoising}
 
@@
 \end{proof}
+\fi
 
-\subsection{Data Efficiency}
+\subsection{Labeling Efficiency}
 

### 2020-09-24 arxiv/diff_cov.tex
wip

@@
 			\begin{align}\label{lem_cov_derv_eq}
-				\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
+				\bignorm{\Sigma_2^{1/2} \bigbrace{\hat{\Sigma}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
 						= w^{\top} \Pi_\bias w + o(\|w\|^2),
@@
 Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
-
-\begin{corollary}[Two tasks with different covariates]\label{thm_main_informal}
-	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
-	For the setting of two tasks, let $C$ be a fixed constant.
-	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	%There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
-	We have that
-	\begin{align*}
-		\bigabs{L(\hat{\beta}_2^{\MTL}) - \Pi_{\vari} - (\beta_1 - \frac{W_1}{W_2}\beta_2)^{\top}\Pi_{\bias} (\beta_1 - \frac{W_1}{W_2}\beta_2)} \le \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) } \cdot \frac{1}{\sqrt{\rho_1}}
-	\end{align*}
-%	\begin{enumerate}
-%		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-%			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
-%		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-%			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
-%	\end{enumerate}
-\end{corollary}
-In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
-We make several remarks about Corollary \ref{thm_main_informal}.
-First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
-This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
-%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
-%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
-%determined by the covariate shift matrix and the model shift.
-%The bounds get tighter and tighter as $\rho_1$ increases.
-Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
-Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
-
-Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
-To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
-%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
-Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
-\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
-%We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
-%That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
-%We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
-%Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
-%Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
-%\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-%In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
-%With high probability, we have that
-%\begin{equation}\label{lem_cov_derv_eq}
-%\begin{split}
-%\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-%= w^{\top} \Pi_\bias w + o(\|w\|^2),
-%\end{split}
-%\end{equation}
-%where $\Pi_\bias$ was defined in \eqref{def Pibias} with $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-%\end{lemma}
-To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
-Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
-As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
-The formal proof of Theorem \ref{thm_main_informal} using Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be presented in Section \ref{app_proof_main_thm}.
-Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
-In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
-%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-
-%\textbf{Proof overview.}\todo{}
-%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
-%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
-This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
-%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
-%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
-%
-%
-%
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-
-%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
-%	In the setting of two tasks,
-%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
-%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
-%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
-%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-%	{\small\begin{align*}%\label{eq_introX1X2}
-%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-%	\end{align*}}%
-%	where $a_1, a_2$ are solutions of the following equations:
-%	{\small\begin{align*}
-%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-%	\end{align*}}
-%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-%\end{lemma}
-
-%which deals with the inverse of the sum of two random matrices, which
-%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-%\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
-	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
-%	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
-%	In the setting of Theorem \ref{thm_main_informal},
-%	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
-	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-%	\begin{align}\label{lem_cov_shift_eq}
-%		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
-%	\end{align}
-%where $(a_1,a_2)$ is the solution to equation \eqref{eq_a12extra} with $\lambda_i$ being the singular values of $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-%\end{lemma}
 
@@
 
-\medskip
-\noindent{\bf Gaussian case.} Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
+\begin{corollary}[Two tasks with different covariates]\label{thm_main_informal}
+	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
+	For the setting of two tasks, let $C$ be a fixed constant.
+	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
+ 	%There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
+	We have that
+	\begin{align*}
+		\bigabs{L(\hat{\beta}_2^{\MTL}) - \Pi_{\vari} - (\beta_1 - \frac{W_1}{W_2}\beta_2)^{\top}\Pi_{\bias} (\beta_1 - \frac{W_1}{W_2}\beta_2)} \le \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) } \cdot \frac{1}{\sqrt{\rho_1}}
+	\end{align*}
+%	\begin{enumerate}
+%		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
+%			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
+%		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
+%			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
+%	\end{enumerate}
+\end{corollary}
+In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
+We make several remarks about Corollary \ref{thm_main_informal}.
+First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
+This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
+%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
+%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
+%determined by the covariate shift matrix and the model shift.
+%The bounds get tighter and tighter as $\rho_1$ increases.
+Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
+Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
+
+Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
+To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
+%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
+As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
+Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
+Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
+\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
+\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
+%We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
+%That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
+%We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
+%Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
+%Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
+%\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
+%In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
+%With high probability, we have that
+%\begin{equation}\label{lem_cov_derv_eq}
+%\begin{split}
+%\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
+%= w^{\top} \Pi_\bias w + o(\|w\|^2),
+%\end{split}
+%\end{equation}
+%where $\Pi_\bias$ was defined in \eqref{def Pibias} with $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+%\end{lemma}
+To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
+Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
+As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
+The formal proof of Theorem \ref{thm_main_informal} using Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be presented in Section \ref{app_proof_main_thm}.
+Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
+In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
+%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
+
+%\textbf{Proof overview.}\todo{}
+%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
+%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
+%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
+This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
+%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
+%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
+%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
+%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
+%
+%
+%
+%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
+%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
+%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
+%Based on the result, we show how to determine positive versus negative transfer as follows.
+%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
+
+%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
+%	In the setting of two tasks,
+%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
+%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
+%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
+%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
+%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
+%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
+%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
+%	{\small\begin{align*}%\label{eq_introX1X2}
+%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
+%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
+%	\end{align*}}%
+%	where $a_1, a_2$ are solutions of the following equations:
+%	{\small\begin{align*}
+%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
+%	\end{align*}}
+%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
+%\end{lemma}
+
+%which deals with the inverse of the sum of two random matrices, which
+%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
+
+%\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
+	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
+	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
+	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
+%	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
+%	In the setting of Theorem \ref{thm_main_informal},
+%	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
+	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
+%	\begin{align}\label{lem_cov_shift_eq}
+%		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
+%	\end{align}
+%where $(a_1,a_2)$ is the solution to equation \eqref{eq_a12extra} with $\lambda_i$ being the singular values of $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
+%\end{lemma}
+
+\subsection{Warmup: Proof Overview for the Gaussian Case}
+Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
 %However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then

### 2020-09-24 arxiv/implications.tex
revise

@@
 %Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-We illustrate our main results (to be described in Section \ref{sec_general}) in a simplified setting.
+We illustrate our main results, Theorem \ref{thm_many_tasks}, Theorem \ref{thm main RMT} and Corollary \ref{thm_main_informal}, in a simplified setting.
 For this setting, we simulate several empirical phenomena that are well-known in hard parameter sharing approaches.
@@
 
-Using our techniques described later in Section \ref{sec_general}, we derive the limiting prediction loss of the hard parameter sharing estimator.
+Using Theorem \ref{thm main RMT}, %our techniques described later in Section \ref{sec_general}, 
+we derive the limiting prediction loss of the hard parameter sharing estimator.
 Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
 
-\begin{corollary}[Derived from Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}]
-	In the isotropic setting described above, with high probability, the prediction loss of the hard parameter sharing estimator for task two satisfies:
+\begin{corollary}[Derived from Theorem \ref{thm main RMT}]
+	Assume that the isotropic setting described above holds, and that there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy that
+\be\label{choiceofpara0}
+p^{ c_0} \le \frac{p\kappa^2}{\sigma^2 }  \le p^{1-c_0},\quad  \frac{pd^2}{\sigma^2}=\OO(1).
+\ee
+	Let $B, W_1, W_2$ be the global minimum of equation \eqref{eq_mtl}. Then with high probability, the prediction loss of the hard parameter sharing estimator for task two satisfies:
+	\begin{align*}
+	 \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} \\
+	 \le  \left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 )
+	 \end{align*}
+	 for any constant $c\in (0,c_0)$.
+	 \iffalse
 	\begin{align*}
@@
 	 \end{align*}
+	 \fi
 \end{corollary}
@@
 It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the following simplified setting, where we can perform explicit calculations.
+We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
 We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.

### 2020-09-24 arxiv/diff_cov.tex
revise
wip

@@
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.
-%We derive deterministic conditions to compare the prediction loss of the local minimum to single-task learning.
 We will develop the key technical results in this section, and describe their implications in the next section.
@@
 However, since the two tasks have different covariates, the scaling of $\hat{\Sigma}^{-1}$ not only depends on the tasks' sample sizes, but also depends on the covariate shift between the two tasks.
-We introduce a key result that show tight asymptotic convergence rate of the bias equation \eqref{eq_bias_2task} and the variance equation  as sample sizes increase to infinity.
-%The following two lemmas  are the main random matrix theoretical results of this paper, which will be used to estimate the two terms on the right-hand side of \eqref{eq_te_mtl_2task}.
+Building on the intuition, We introduce a key result that shows tight asymptotic convergence rate of the bias and variance as $p$ goes to infinity.
 We define a key quantity $M \define \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
-Let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M$ in descending order.
-%Based on the above intuition, in the following we develop generalization bounds that relate the bias and variance of multi-task learning to the sample sizes and the covariance matrices of both tasks.
+Let $U\Lambda V^\top$ denote the singular value decomposition of $M$, where $\Lambda\in\real^{p\times p}$ consists of the singular values of $M$, $\lambda_1, \lambda_2, \dots, \lambda_p$ in descending order.
 
@@
 	Suppose that $X_1$ and $X_2$ are both random matrices that satisfy Assumption \ref{assume_rm}.
-	Then we have the following asymptotic limits:
+	With high probability over the randomness of $X_1$ and $X_2$, we have the following limits:
 	\begin{enumerate}
-		\item[i)] Limiting variance:
-		 	Define the following
-			\[ \Pi_{\vari} \define \frac{1}{n_1 + n_2}\cdot \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma_2}. \]
-			In the above equation, $a_1$ and $a_2$ are the solutions of the following two equations that only depend on the sample sizes $\rho_1, \rho_2$, and the singular values of the covariate shift matrix $M$:
+		\item[i)]  The variance equation converges to the following asymptotic limit
+			\begin{align}\label{lem_cov_shift_eq}
+				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{\frac{\hat{\Sigma}^{-1}}{n_1 + n_2} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \lesssim p^{-c_{\varphi}}\norm{\Sigma^{(2)}},
+			\end{align}
+			where $a_1$ and $a_2$ are the solutions of the following two equations:
 			\begin{align}
@@
 			\end{align}
-			Then we have that
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} = \bigtr{\Pi_{\vari}} + \OO(p^{-c}\norm{\Sigma^{(2)}}), %\bigo{\|\| p^{-1/2+\epsilon}}
-			\end{align}
-		\item[ii)] Limiting bias: Let
+		\item[ii)] For any fixed vector $w\in\real^p$, the bias equation converges to the following asymptotic limit
 			\be\label{def Pibias} \Pi_\bias \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \ee
@@
 \paragraph{Preliminaries.} Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $[(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}$ for $X^{(1)}= Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}= Z^{(2)}\Sigma_2^{1/2}$.
-%\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
-Suppose $M=\Sig_1^{1/2} \Sig_2^{-1/2}$ has a singular value decomposition
-\be\label{eigen2}
-M= U\Lambda V^\top, \quad \Lambda=\text{diag}( \lambda_1, \ldots, \lambda_p).
-\ee
 Then using equation \eqref{eigen2}, we can write

### 2020-09-24 arxiv/diff_cov.tex
wip

@@
 We define a key quantity $M \define \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
-Let $U\Lambda V^\top$ denote the singular value decomposition of $M$, where $\Lambda\in\real^{p\times p}$ consists of the singular values of $M$, $\lambda_1, \lambda_2, \dots, \lambda_p$ in descending order.
+Let $U\Lambda V^\top$ denote the singular value decomposition of $M$, where $\Lambda\in\real^{p\times p}$ consists of $M$'s singular values $\lambda_1, \lambda_2, \dots, \lambda_p$ as its diagonal entries in descending order.
 
-\begin{theorem}
+\begin{theorem}\label{thm main RMT}
 	Suppose that $X_1$ and $X_2$ are both random matrices that satisfy Assumption \ref{assume_rm}.
@@
 			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{\frac{\hat{\Sigma}^{-1}}{n_1 + n_2} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \lesssim p^{-c_{\varphi}}\norm{\Sigma^{(2)}},
+				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \lesssim p^{-c_{\varphi}}\norm{\Sigma^{(2)}},
 			\end{align}
@@
 			\end{align}
-		\item[ii)] For any fixed vector $w\in\real^p$, the bias equation converges to the following asymptotic limit
-			\be\label{def Pibias} \Pi_\bias \define  M \frac{a_3 M^{\top}M + (1 + a_4) \id_{p\times p}}{(a_1 M^{\top}M + a_2\id_{p\times p})^2} M^{\top}, \ee
-				where $a_{3}$ and $a_4$ are the solutions of the following two equations:
-			\begin{gather}\label{eq_a34extra}
+		\item[ii)] For any fixed vector $w\in\real^p$ with unit norm, the bias equation converges to the following asymptotic limit
+			\begin{align}\label{def Pibias}
+				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \lesssim p^{-c_{\varphi}},
+			\end{align}
+				where $a_{3}$ and $a_4$ are the solutions of the following two equations with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+			\begin{align}\label{eq_a34extra}
 				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-				= b_0 .
-%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
-%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
-			\end{gather}
-				In the above equation, we denote $b_k$ as $\frac1{p}\sum_{i=1}^p {\lambda_i^{2k}} / { (\lambda_i^2 a_1 + a_2)^2  }$, for $k = 0, 1, 2$.
-			Then, we have that
-			\begin{align}\label{lem_cov_derv_eq}
-				\bignorm{\Sigma_2^{1/2} \bigbrace{\hat{\Sigma}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-						= w^{\top} \Pi_\bias w + o(\|w\|^2),
+				= b_0.
 			\end{align}

### 2020-09-24 arxiv/diff_cov.tex
reorg

@@
 %\alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
-
-\begin{corollary}[Two tasks with different covariates]\label{thm_main_informal}
-	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
-	For the setting of two tasks, let $C$ be a fixed constant.
-	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
- 	%There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
-	We have that
-	\begin{align*}
-		\bigabs{L(\hat{\beta}_2^{\MTL}) - \Pi_{\vari} - (\beta_1 - \frac{W_1}{W_2}\beta_2)^{\top}\Pi_{\bias} (\beta_1 - \frac{W_1}{W_2}\beta_2)} \le \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) } \cdot \frac{1}{\sqrt{\rho_1}}
-	\end{align*}
-%	\begin{enumerate}
-%		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-%			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
-%		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
-%			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
-%	\end{enumerate}
-\end{corollary}
-In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
-We make several remarks about Corollary \ref{thm_main_informal}.
-First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
-This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
-%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
-%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
-%determined by the covariate shift matrix and the model shift.
-%The bounds get tighter and tighter as $\rho_1$ increases.
-Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
-Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.
-
-Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
-To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
-%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
-As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
-Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
-Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
-\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g.
-\cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
-%We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
-%That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
-%We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
-%Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
-%Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
-%\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
-%In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
-%With high probability, we have that
-%\begin{equation}\label{lem_cov_derv_eq}
-%\begin{split}
-%\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
-%= w^{\top} \Pi_\bias w + o(\|w\|^2),
-%\end{split}
-%\end{equation}
-%where $\Pi_\bias$ was defined in \eqref{def Pibias} with $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-%\end{lemma}
-To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
-Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
-As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely.
-The formal proof of Theorem \ref{thm_main_informal} using Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be presented in Section \ref{app_proof_main_thm}.
-Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
-In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
-%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.
-
-%\textbf{Proof overview.}\todo{}
-%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
-%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
-%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$.
-This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
-%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
-%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
-%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
-%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
-%
-%
-%
-%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
-%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
-%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
-%Based on the result, we show how to determine positive versus negative transfer as follows.
-%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$
-
-%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
-%	In the setting of two tasks,
-%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
-%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
-%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
-%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
-%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
-%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
-%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
-%	{\small\begin{align*}%\label{eq_introX1X2}
-%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
-%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
-%	\end{align*}}%
-%	where $a_1, a_2$ are solutions of the following equations:
-%	{\small\begin{align*}
-%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
-%	\end{align*}}
-%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
-%\end{lemma}
-
-%which deals with the inverse of the sum of two random matrices, which
-%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.
-
-%\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
-	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
-	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
-	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
-%	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
-%	In the setting of Theorem \ref{thm_main_informal},
-%	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
-	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
-%	\begin{align}\label{lem_cov_shift_eq}
-%		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
-%	\end{align}
-%where $(a_1,a_2)$ is the solution to equation \eqref{eq_a12extra} with $\lambda_i$ being the singular values of $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-%\end{lemma}
-
-\subsection{Warmup: Proof Overview for the Gaussian Case}
-Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
-%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
-by the rotational invariance of the multivariate Gaussian distribution we have
-\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
-where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
- \begin{equation} \label{resolv Gauss1}
-   G(z)= \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
-   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{-1}.
- \end{equation}
-
-\medskip
-\noindent{\bf Schur complements.}
-%Now we discuss about how to obtain the matrix limit in equation \eqref{defn_piw}.
-%\HZ{Divide into several parts like sec 7 to improve readability.}
-The core quantities of the derivation are the following resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
-\begin{definition}[Resolvent minors]\label{defn_Minor}
- For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $a\in \mathcal I$, we define the minor $\cal A^{(a)}:=(\cal A_{a_1 a_2}:a_1, a_2 \in \mathcal I\setminus \{a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $a$-th row and column in $\cal A$.
-Note that we keep the names of indices when defining $\cal A^{(a)}$, i.e.
-$(\cal A^{(a)})_{a_1a_2}= \cal A_{a_1 a_2}$ for $a_1,a_2\ne a$.
-Correspondingly, we define the resolvent minor for $G$ in equation \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
-\begin{align*}
-G^{(\mathfrak c)}:&=\left[ \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
-   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{(a)}\right]^{-1} ,
-%= \left( {\begin{array}{*{20}c}
-%   { \mathcal G^{(\mathbb T)}} & \mathcal G^{(\mathbb T)} W^{(\mathbb T)}  \\
-%   {\left(W^{(\mathbb T)}\right)^\top\mathcal G^{(\mathbb T)}} & { \mathcal G_R^{(\mathbb T)} }  \\
-%\end{array}} \right)  ,
-\end{align*}
-and define the partial traces $m^{(a)}$, $m_0^{(a)}$, $m_1^{(a)}$ and $m_2^{(a)}$ by replacing $G$ with $G^{(a)}$ in equation \eqref{defm}.
-We adopt the convention that for the resolvent minor $G^{(a)}$ defined as above, $G^{(a)}_{a_1a_2} = 0$ if $a_1 =a$ or $a_2=a$.
-\end{definition}
-%Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
-One will see a crucial use of this fact in the heuristic proof below.
- Using Schur complement formulas in equation (\ref{resolvent2}), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-%\HZ{This part needs more explanation - cannot understand.}
-\begin{align}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} , \label{0self_Gii}
-\end{align}
-and for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\begin{align}
-\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij},
-\label{0self_Gmu1}
-\end{align}
-where we recall the notations in equation \eqref{labelZ}. To see why equation \eqref{0self_Gii} holds, we have that by Schur complement formula,
-\begin{align*}
-\frac{1}{G_{ii}}= -z - H_i G^{(i)}H_{i}^\top, \quad H_i = \left( \mathbf 0_{p-1}, (n^{-1/2}\lambda_i (Z^{(1)})^\top_{i\mu }:\mu \in \cal I_1),(n^{-1/2} (Z^{(2)})^\top_{i\nu }:\nu \in \cal I_2)\right),
-\end{align*}
-where $H_i$ is actually the $i$-th row of $H$ with the $(i,i)$-th entry removed.
-Expanding the above expression, we obtain equation \eqref{0self_Gii}.
-The two expressions in equation \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
-
-\medskip
-\noindent{\bf Concentration estimates.} Now for the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $Z^{(1)}_{\mu i}$ and $Z^{(2)}_{\nu i}$.
-Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with overwhelming probability,
-\begin{align*}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
-\end{align*}
-where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$.
-Intuitively, since we have removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
-Hence we obtain from the above equation that
-\begin{align}\label{1self_Gii}
- G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1 +  \frac{\rho_2}{\rho_1+\rho_2}m_2+\oo(1)\right)^{-1}.
-\end{align}
-Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
-with overwhelming probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
-
-\medskip
-\noindent\textbf{Deriving the self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
-\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
-\ee
-with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
-with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
-\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
-with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
-\be\label{approximate m1m2}
-\begin{split}
-& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
-& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
-\end{split}
-\ee
-with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
-A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}.
-Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
-\be\label{approx m12 add}
-(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
-\ee
-To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
-This will be given by Lemma \ref{lem_stabw}.
-
-\medskip
-\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
-with overwhelming probability.
-These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}.
-For the off-diagonal entries, they are close to zero due to concentration.
-For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
-$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
-Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
-The other off-diagonal entries can be bounded in the same way.
-The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
-
-\medskip
-\noindent{\bf Deriving the bias asymptotics.} Finally, we describe how to derive the bias asymptotics.
-We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
-More precisely, using equation \eqref{eigen2extra} we can obtain that
-\begin{align}
-&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
-&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
-\end{align}
-where we used equation \eqref{rewrite X as R} in the second step.
-Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
-\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
-If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
-Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
-\begin{align}
-& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
-\end{align}
-where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
-Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
-This is the main reason why we need to take a general $z$ in the definition of resolvents.
-The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
-%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
-%For the variance asymptotic limit, we study the resolvent
-%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
-%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
-%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
-%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
-%
-%For the bias asymptotic limit, we show in \todo{where?} that
-%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
-%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
-%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
-
-The above arguments are the core of the main proof.
-To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
-These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
-For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-24 arxiv/proof_gaussian_case.tex
reorg

--- 2020-09-20 arxiv/proof_main.tex
@@
-%\subsection{The Bias and Variance Asymptotics}
-\paragraph{Proof overview.} 
-%\todo{merge} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
-%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
-%We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-We use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $[(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}$ for $X^{(1)}= Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}= Z^{(2)}\Sigma_2^{1/2}$.
-%\HZ{Suggestion: focus on the proof overview of Lemma \ref{lem_cov_shift} only. Use one paragraph in the end to say how to extend the idea to Lemma \ref{lem_cov_derivative}}
-Suppose $M=\Sig_1^{1/2} \Sig_2^{-1/2}$ has a singular value decomposition
-\be\label{eigen2}
-M= U\Lambda V^\top, \quad \Lambda=\text{diag}( \lambda_1, \ldots, \lambda_p).
-\ee
-Then using equation \eqref{eigen2}, we can write
-\be\label{eigen2extra}[(X^{(1)})^\top (X^{(1)})+(X^{(2)})^\top (X^{(2)})]^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
-We divide the discussion into the following parts.
-
-\medskip
-\noindent\textbf{Defining the resolvents.} For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
-$$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
-which is linear in $A$.
-This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
-Our goal is to study the SVD of the rectangular matrix $(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top)$.
-%For this purpose,
-%}\HZ{what does this trick mean? use less technical words},
-%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Then we define the following $(p+n)\times (p+n)$ symmetric block matrix 
-%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
-%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
-%We define the $(n+N)\times (n+N)$ block matrix
- \begin{equation}\label{linearize_block}
-    H\left(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top\right): = n^{-1/2}\left( {\begin{array}{*{20}c}
-   { 0 } & \Lambda U^{\top}(Z^{(1)})^\top & V^\top (Z^{(2)})^\top  \\
-   {Z^{(1)} U\Lambda  } & {0} & 0 \\
-   {Z^{(2)}V} & 0 & 0
-   \end{array}} \right).
- \end{equation}
-For simplicity of notations, we abbreviate it as $H$ in the following discussion, and define the index sets
-$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
- We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
- \be\label{labelZ}
- Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
-Now we define the resolvents as follows.
-\begin{definition}[Resolvents]
-We define the resolvent (or Green's function) of $H$ as
- \begin{equation}\label{eqn_defG}
- G (z):= \left[H -\left( {\begin{array}{*{20}c}
-   { z\id_{p}} & 0 & 0 \\
-   0 & { \id_{n_1}}  & 0\\
-      0 & 0  & { \id_{n_2}}\\
-\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C ,
- \end{equation}
-%It is easy to verify that the eigenvalues $\lambda_1(H)\ge \ldots \ge \lambda_{n+N}(H)$ of $H$ are related to the ones of $\mathcal Q_1$ through
-%\begin{equation}\label{Heigen}
-%\lambda_i(H)=-\lambda_{n+N-i+1}(H)=\sqrt{\lambda_i\left(\mathcal Q_2\right)}, \ \ 1\le i \le n\wedge N, \quad \text{and}\quad \lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.
-%\end{equation}
-%and
-%$$\lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.$$
-%where we used the notations $n\wedge N:=\min\{N,M\}$ and $n\vee N:=\max\{N,M\}$.
-%\begin{definition}[Index sets]\label{def_index}
-and the resolvent of $  n^{-1}\left(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)$ as
-\be\label{mainG}
-\cal G(z):=\left( n^{-1}  \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + n^{-1}V^\top (Z^{(2)})^\top Z^{(2)}V -z\right)^{-1},\quad z\in \C.
-\ee
-Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
-\be\label{defm}
-\begin{split}
-m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
- m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
-\end{split}
-\ee
-We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof.
-We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
-\end{definition}
-With Schur complement formula, we can check that %\HZ{Has $G(z)$ been defined before?}
- \begin{equation} \label{green2}
- G (z):=  \left( {\begin{array}{*{20}c}
-   { \cal G (z)} & \cal G(z)A  \\
-   A^\top \cal G(z) & z (A^\top A - z)^{-1}
-\end{array}} \right)^{-1}, %\quad \cal G_R:=(W^\top W - z)^{-1} ,
- \end{equation}
- where we abbreviated 
- \be\label{abbr_A}
- A:= n^{-1/2}(\Lambda U^\top (Z^{(1)})^\top, V^\top (Z^{(2)})^\top).
- \ee 
- %\HZ{$W$ is overloaded with the output layers} 
- This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
-On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
-%one can find that %(recall equation \eqref{mainG})
-%\be \label{green2}
-%\begin{split}
-%& \cal G_{L}=\left(WW^\top -z \right)^{-1} =\cal G ,\quad \cal G_{LR}=\cal G_{RL}^\top  = \cal G W , \quad \cal G_R= z\left(W^\top W - z\right)^{-1}.
-%\end{split}
-%\ee
-%, and the subindex of $\cal G_R$ means the lower-right block.
-
-%Now using Schur complement formula, we can verify that the (recall equation \eqref{def_green})
-%\begin{align}
-%G = \left( {\begin{array}{*{20}c}
-%   { z\mathcal G_1} & \mathcal G_1 \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2}  \\
-%   {\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} \mathcal G_1} & { \mathcal G_2 }  \\
-%\end{array}} \right) = \left( {\begin{array}{*{20}c}
-%   { z\mathcal G_1} & \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2} \mathcal G_2   \\
-%   {\mathcal G_2}\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} & { \mathcal G_2 }  \\
-%\end{array}} \right). \label{green2}
-%\end{align}
-%where $\mathcal G_{1,2}$ are defined in (\ref{def_green}).
-
-\medskip
-\noindent\textbf{Defining the asymptotic limits of the resolvents.}
-%\label{sec aymp_limit_G}
-%\subsection{Resolvents and limiting law}
-We now describe the asymptotic limit of $G(z)$ as $n\to \infty$.
-First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
-%\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)},
-the unique solution to the following system of equations
-\begin{equation}\label{selfomega_a}
-\begin{split}
-& \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{split}
-\ee
-%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
-The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}. 
-%Here, for simplicity of notations, we introduced the following ratios
-%\be\label{ratios}
-% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
-%\ee
-We define the matrix limit of $G(z)$ as
-\be \label{defn_piw}
-\Gi(z) := \begin{pmatrix} (-z\id_p+a_{1}(z)\Lambda^2  +  a_{2}(z)\id_p)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
-In particular, the matrix limit of $\cal G(z)$ is given by 
-\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}.\ee
-
-\medskip
-\noindent{\bf Deriving the variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
-\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
-When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to equation \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
-Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
-Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
-\begin{align}
-&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
-&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
-\end{align}
-where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}.
-This concludes equation \eqref{lem_cov_shift_eq} up to a small error.
-The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
-
-%\alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}
-
-\medskip
-\noindent{\bf Gaussian case.} Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
+\subsection{Warmup: Proof Overview for the Gaussian Case}
+Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
 %However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then

### 2020-09-24 arxiv/proof_two_tasks.tex
reorg

\subsection{Generalization Bounds}\label{app_proof_main_thm}

\begin{corollary}[Two tasks with different covariates]\label{thm_main_informal}
	%For the setting of two tasks, let $\delta > 0$ be a fixed error margin, $\rho_2 > 1$ and $\rho_1 \gtrsim \delta^{-2}\cdot \lambda_{\min}(M)^{-4} \norm{\Sigma_1} \max(\norm{\beta_1}^2, \norm{\beta_2}^2)$.
	For the setting of two tasks, let $C$ be a fixed constant.
	Let $B, W_1, W_2$ be any local minimum of equation \eqref{eq_mtl}.
 	%There exist two deterministic functions $\Delta_{\bias}$ and $\Delta_{\vari}$ that only depend on scaled model distance $\beta_1 - \frac{W_1}{W_2} \beta_2$, sample sizes $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$, and covariate shift matrix $M$ such that
	We have that
	\begin{align*}
		\bigabs{L(\hat{\beta}_2^{\MTL}) - \Pi_{\vari} - (\beta_1 - \frac{W_1}{W_2}\beta_2)^{\top}\Pi_{\bias} (\beta_1 - \frac{W_1}{W_2}\beta_2)} \le \frac{ C\cdot \max(\norm{\beta_1}, \norm{\beta_2}) \cdot \sqrt{\norm{\Sigma_1}} } {\lambda_{\min}^2(M)) } \cdot \frac{1}{\sqrt{\rho_1}}
	\end{align*}
%	\begin{enumerate}
%		\item[a)] \textbf{Positive transfer:} If $\Delta_{\bias} < \Delta_{\vari} -  \frac{\delta}{\sqrt{\rho_1}} $, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
%			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).  \]
%		\item[b)] \textbf{Negative transfer:} If $\Delta_{\bias} > \Delta_{\vari} + \frac{\delta}{\sqrt{\rho_1}}$, then w.h.p. over the randomness of $X_1, X_2, \varepsilon_1, \varepsilon_2$, we have
%			\[ \te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}). \]
%	\end{enumerate}
\end{corollary}
In words, the above result shows that a deterministic function $\Delta_{\bias} - \Delta_{\vari}$ determines whether the prediction loss of the empirical multi-task learning estimator is lower than that of single-task learning, up to an error that scales as $\delta / \sqrt{\rho_1}$.
We make several remarks about Corollary \ref{thm_main_informal}.
First, as the amount of data from the source task increases, we get more accurate predictions  since the error scales down.
This applies to many practical settings where collecting labeled data for the target task is expensive and auxillary (source) task data is easier to obtain.
%Theorem \ref{thm_main_informal} applies to settings where large amounts of source task data are available but the target sample size is small.
%For such settings, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
%determined by the covariate shift matrix and the model shift.
%The bounds get tighter and tighter as $\rho_1$ increases.
Second, the deterministic function $\Delta_{\bias} - \Delta_{\vari}$ depends on the three task properties that we care about and the precise form can be found in Section \ref{sec_proof_general}.
Finally, later on in Section \ref{sec_special}, we will study how varying each task property affects the performance of multi-task learning in depth.

Lemma \ref{lem_cov_shift} derives the asymptotic limit of the variance equation \eqref{eq_var_2task}.
To see this, we rescale $X_1$ with $W_1 / W_2$ and set the matrix $\Sigma$ as $\sigma^2 \Sigma_2$.
%allows us to get a tight bound on equation \eqref{eq_te_var}, that only depends on \textit{sample size}, \textit{covariate shift} and the scalar $\hat{v}$.
As a remark, the concentration error $o(\|A\|)$ on the right hand side of equation \eqref{lem_cov_shift_eq} reduces provided with stronger moment assumptions on $X_1$ and $X_2$. % p^{-1/2+\epsilon}
Recall from Section \ref{sec_prelim} that the feature vectors are generated by $\Sigma_i^{1/2} z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance.
Provided that for every entry of $z$, its $k$-th moment exists, then we can obtain a concentration error at most $\bigo{\norm{A} p^{-1/2 + 2/k + o(1)}}$.
\todo{We remark that one can probably derive the same asymptotic result using free probability theory (see e.g. \cite{nica2006lectures}), but our results \eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq} also give an almost sharp error bound $\bigo{ p^{-1/2+\epsilon}}$.}
%We will use the matrix fractional notation $\frac{X}{Y}$ for two PSD matrices that share the same eigenspace.
%That is, suppose that the SVD of $X, Y$ is $X = U D_1 U^{\top}$ and $Y = U D_2 U^{\top}$.
%We denote $\frac{X}{Y} = U D_{1} D_2^{-1} U^{\top}$.
%Using the notation, we introduce an important quantity that describes the limit of the bias equation as $p$ goes to infinity.
%Our next result shows that the bias equation \eqref{eq_bias_2task} is described by the above limiting bias asymptotically.
%\begin{lemma}[Bias asymptotics]\label{lem_cov_derivative}
%In the setting of Theorem \ref{thm_main_informal}, let $w \in \R^p$ be any vector that is independent of $X_1$ and $X_2$.
%With high probability, we have that
%\begin{equation}\label{lem_cov_derv_eq}
%\begin{split}
%\bignorm{\Sigma_2^{1/2} \bigbrace{\frac{X_1^{\top}X_1 + X_2^{\top}X_2}{n_1 + n_2}}^{-1} \Sigma_1^{1/2} w}^2
%= w^{\top} \Pi_\bias w + o(\|w\|^2),
%\end{split}
%\end{equation}
%where $\Pi_\bias$ was defined in \eqref{def Pibias} with $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
%\end{lemma}
To apply the above result to equation \eqref{eq_bias_2task}, we first approximate $X_1^{\top}X_1$ by $\Sigma_1$, and then use Lemma \ref{lem_cov_derivative} with $w = \Sigma_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)$.
Note that we can rescale $X_1$ by $W_1 / W_2$ and $\Sigma_1$ by $(W_1 / W_2)^2$, and the rest of the steps follows.
As a remark, the approximation of $X_1^{\top}X_1$ by $\Sigma_1$ incurs a generalization error that scales down with $\rho_1$, which is the $\delta / \sqrt{\rho_1}$ term in Theorem \ref{thm_main_informal} more precisely. The formal proof of Theorem \ref{thm_main_informal} using Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be presented in Section \ref{app_proof_main_thm}.
Finally, while the limiting bias $\Pi$ provides a precise connection with general covariate shift matrices $M$, it can be difficult to interpret.
In Section \ref{sec_special}, we show that $\Pi$ can be significantly simplified in an isotropic covariance setting.
%While the general form of these functions can be complex (as are previous generalization bounds for MTL), they admit interpretable forms for simplified settings.

%\textbf{Proof overview.}\todo{}
%Theorem \ref{lem_cov_shift_informal} extends a well-known result for the single-task setting when $X_1, \rho_1, a_1$ are all equal to zero \cite{S07}.
%Applying Theorem \ref{lem_cov_shift_informal} to \eqref{eq_te_var}, we can calculate the amount of reduced variance compared to STL, which is given asymptotically by $\Delta_{\vari}$.
%For the bias term in equation \eqref{eq_te_model_shift}, we apply the approximate isometry property to $X_1^{\top}X_1$, which is close to $n_1^2\Sigma_1$. This results in the error term $\delta$, which scales as $(1 + 1/\sqrt{\rho_1})^4-1$.
%Then, we apply a similar identity to Theorem \ref{lem_cov_shift_informal} for bounding the bias term, noting that the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$.
%This estimates the negative effect given by $\Delta_{\bias}$. %, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}.
%During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$.
%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main_thm} and the proof of Lemma \ref{lem_cov_shift_informal} is in Appendix \ref{sec_maintools}.
%
%
%
%The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
%The technical crux of our approach is to derive the asymptotic limit of $\te(\hat{\beta}_t^{\MTL})$ in the high-dimensional setting, when $p$ approaches infinity.
%We derive a precise limit of $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}$, which is a deterministic function that only depends on $\Sigma_1, \Sigma_2$ and $n_1/p, n_2/p$ (see Lemma \ref{lem_cov_shift} in Appendix \ref{app_proof_main} for the result).
%Based on the result, we show how to determine positive versus negative transfer as follows.
%, where $\lambda_{\min}(M)$ is the smallest singular value of $M_1$

%\begin{lemma}[Variance bound]\label{lem_cov_shift_informal}
%	In the setting of two tasks,
%	let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot$ be the sample size of the two tasks.
%	Let $\lambda_1, \dots, \lambda_p$ be the singular values of the covariate shift matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ in decreasing order.
%	%let $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$ denote the sample sizes of each task.
%	%Let $\Sigma_1$ and $\Sigma_2$ denote the covariance matrix of each task.
%	With high probability, the variance of the multi-task estimator $\hat{\beta}_t^{\MTL}$ equals
%	%let $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in descending order.
%%	For any constant $\e>0$, w.h.p. over the randomness of $X_1, X_2$, we have that
%	{\small\begin{align*}%\label{eq_introX1X2}
%		%\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} =
%		\frac{\sigma^2}{n_1+n_2}\cdot \bigtr{ (\hat{v}^2 a_1 \Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id)^{-1}} +\bigo{{p^{-1/2+o(1)}}},
%	\end{align*}}%
%	where $a_1, a_2$ are solutions of the following equations:
%	{\small\begin{align*}
%		a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac{1}{p}\sum_{i=1}^p \frac{\hat{v}^2\lambda_i^2 a_1}{\hat{v}^2\lambda_i^2 a_1 + a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.
%	\end{align*}}
%%are both fixed values that roughly scales with the sample sizes $\rho_1, \rho_2$, and satisfy $a_1 + a_2 = 1 - (\rho_1 + \rho_2)^{-1}$ plus another deterministic equation.
%\end{lemma}

%which deals with the inverse of the sum of two random matrices, which
%any is can be viewed as a special case of Theorem \ref{thm_model_shift}.

%\begin{lemma}[Variance asymptotics]\label{lem_cov_shift}
	%Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i\in\real^{p\times p}$, for $i = 1, 2$.
	%Suppose $X_1=Z_1\Sigma_1^{1/2}\in \R^{n_1\times p}$ and $X_2=Z_2\Sigma_2^{1/2}\in \R^{n_2\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_1:=n_1/p>1$ and $\rho_2:=n_2/p>1$ being fixed constants.
	%Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and
%	Let $\Sigma \in \real^{p \times p}$ be any fixed and deterministic matrix.
%	In the setting of Theorem \ref{thm_main_informal},
%	with probability $1-\oo(1)$ over the randomness of $X_1$ and $X_2$, we have that %for any constant $\e>0$,
	%When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
%	\begin{align}\label{lem_cov_shift_eq}
%		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma} = \bigtr{ (a_1 \Sigma_1 + a_2\Sigma_2)^{-1} \Sigma} + o(\norm{\Sigma}), %\bigo{\|\| p^{-1/2+\epsilon}}
%	\end{align}
%where $(a_1,a_2)$ is the solution to equation \eqref{eq_a12extra} with $\lambda_i$ being the singular values of $M\equiv M(1): = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
%\end{lemma}

In this subsection, we provide the proof of Corollary \ref{thm_main_informal} using Theorem \ref{thm main RMT}.
%Lemma  \ref{lem_cov_shift} and \ref{lem_cov_derivative}.

Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
Using the local optimality condition of $B$, we obtain that
\begin{align*}
	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
\end{align*}
Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
\begin{align}
	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
\end{align}
Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
Comparing the above to single-task learning, that is,
\begin{align}
	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
\end{align}
we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!

 \todo{derive the test loss} Expectation was given in \eqref{eq_bias_2task} and \eqref{eq_var_2task}.

The proof of Lemma \ref{thm_model_shift} is based on Lemma \ref{lem_cov_shift}, Lemma \ref{lem_cov_derivative}, and the following bound on the singular values of $Z^{(1)}$: for any constant $\e>0$, we have
\begin{align}
\al_-(\rho_1) - \OO(p^{-1/2+e})  \preceq {n_1^{-1}}{(Z^{(1)})^{\top} Z^{(1)}}  \preceq   \al_+(\rho_1) + \OO(p^{-1/2+e}) \quad \text{w.h.p.}  \label{eq_isometric}
\end{align}
%with overwhelming probability.
In fact, $n_1^{-1}(Z^{(1)})^{\top}Z^{(1)}$ is a standard sample covariance matrix, and it is well-known that its eigenvalues are all inside the support of the Marchenko-Pastur law $[\al_-(\rho_1)-\oo(1) ,\al_+(\rho_1)+\oo(1)]$ with probability $1-\oo(1)$ \cite{No_outside}. The estimate \eqref{eq_isometric} provides tight bounds on the concentration errors, and it will be formally proved in Lemma \ref{SxxSyy} below.

%First, we provide the steps for the bias-variance decomposition.
%Using the local optimality condition of $B$, we obtain that
%\begin{align*}
%	 \wh{B}(W_1, W_2) &= (W_1^2 (X^{(1)})^{\top}X^{(1)} + W_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (W_1 (X^{(1)})^{\top}Y_1 + W_2 (X^{(2)})^{\top}Y_2)\\
%	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \left(\frac{W_1}{W_2} (X^{(1)})^{\top}Y_1 + (X^{(2)})^{\top}Y_2\right) \\
%	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{(X^{(1)})^{\top}X^{(1)}\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
%\end{align*}
%Recall that $\wh{\beta}_2^{\MTL} = \wh{B}(W_1, W_2) W_2$, and one can verify that equation \eqref{eq_bias_2task} and \eqref{eq_var_2task} hold.

During the proof we shall also give explicit expressions for $\Delta_{\bias}$ and $\Delta_{\vari}$, which might be of interest to some readers.
With $a_i$, $i=1,2,3,4$, given in Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative},
we define the following matrix
\be\label{defnpihat}\Pi \equiv \Pi(\wh v)= \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot \wh v^2{M} \frac{(1 +   a_3)\id + \wh v^2 a_4 {M}^{\top} {M}}{( \wh v^2 a_1 {M}^{\top} {M}+ a_2 )^2} {M}^{\top}.\ee
%which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix
%$$\wh v\Sigma_1^{1/2} (\wh{v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1} \Sigma_2 (\wh{v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1}\Sigma_1^{1/2}.$$
Moreover, we introduce two factors that will appear often in our statements and discussions:
$$\al_-(\rho_1):=\left(1- \rho_1^{-1/2}\right)^2,\quad \al_+(\rho_1):=\left(1 + \rho_1^{-1/2}\right)^2.$$
In fact, $\al_-(\rho_1)$ and $\al_+(\rho_1)$ correspond to the largest and smallest singular values of $Z^{(1)}/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}. In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z^{(1)}/\sqrt{n_1}$ will be more close to an isometry. Finally, we introduce the error term
\be\label{eq_deltaextra}
 \delta(\wh v):=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)\wh v^2\lambda_{\min}^2(M)} \cdot  \norm{\Sigma_1^{1/2}(\beta_1 - \wh{v}\beta_2)}^2.\ee
%where $\lambda_{\min}(\wh M)$ is the smallest singular value of $\wh M$.
Note that this factor converges to 0 as $\rho_1$ increases. It is not hard to see that Theorem \ref{thm_main_informal} is an immediate consequence of the following lemma.

%$$\delta:=\left[\frac{n_1 \lambda_1}{(\sqrt{n_1}-\sqrt{p})^2\lambda_p  +  (\sqrt{n_2}-\sqrt{p})^2}\right]^2\cdot \norm{\Sigma_1^{1/2}(\beta_1 - \wh{w}\beta_2)}^2.$$
%{\cor may be able to get a better bound, but the statement will be long}

\begin{lemma}%[Theorem \ref{thm_main_informal} restated]
\label{thm_model_shift}
%For $i=1,2$, let $Y_i = X_i\beta_i + \varepsilon_i$ be two independent data models, where $X_i$, $\beta_i$ and $\varepsilon_i$ are also independent of each other. Suppose that $X_i=Z_i\Sigma_i^{1/2}\in \R^{n_i\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho_i:=n_i/p>1$ being fixed constants, and $\e_i\in \R^{n_i}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
Consider two data models $Y_i = X_i\beta_i + \varepsilon_i$, $i=1,2$, that satisfy Assumption \ref{assm_secA2} with $\sigma_1^2=\sigma_2^2=\sigma^2$. Then with overwhelming probability, we have
	\begin{align}
	 	\te(\wh{\beta}_{t}^{\MTL}) \le \te(\wh{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \ge   \delta(\wh v), \label{upper}\\
		\te(\wh{\beta}_t^{\MTL}) \ge \te(\wh{\beta}_t^{\STL}) \quad \text{ when: } \ \ &\Delta_{\vari} - \Delta_{\bias} \le - \delta(\wh v), \label{lower}
	\end{align}
	where
	\begin{align} %\bigtr{{\Sigma_2^{-1}}}
		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{1}{\rho_2 - 1} -  \frac{1}{\rho_1 + \rho_2}\cdot \frac1p \bigtr{( \wh v^2 a_1 M^{\top}M +  a_2\id)^{-1}} } \label{Deltavarv} \\
		\Delta_{\bias} &\define (\beta_1 - \wh{v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi (\wh v)\Sigma_1^{1/2} (\beta_1 - \wh{v}\beta_2). \label{Deltabetav}
	\end{align}
\end{lemma}

%\begin{remark}
The main error $\delta$ in Lemma \ref{thm_model_shift} comes from approximating $n_1^{-1}(Z^{(1)})^{\top}Z^{(1)}$ by $\id$ using estimate \eqref{eq_isometric}; see the estimate \eqref{bounddelta-} below. In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the following random matrix:
$$((X^{(1)})^{\top}X^{(1)})^{-1}(X^{(2)})^{\top}X^{(2)} +  \wh{v}^2 .$$
In fact, the eigenvalues of $\cal X:=((X^{(1)})^{\top}X^{(1)})^{-1}(X^{(2)})^{\top}X^{(2)}$ have been studied in the name of Fisher matrices; see e.g. \cite{Fmatrix}. However, since $\cal X$ is non-symmetric, it is known that the singular values of $\cal X$ are different from its eigenvalues. To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix literature, and the study of the singular values of $\cal X +\wh v^2$ will be even harder. We leave this problem to future study.
%\end{remark}

\begin{proof}[Proof of Lemma \ref{thm_model_shift}]
%\noindent
%To prove Theorem \ref{thm_cov_shift}, we study the spectrum of the random matrix model:
%$$Q= \Sigma_1^{1/2}  (Z^{(1)})^{\top} Z^{(1)} \Sigma_1^{1/2}  + \Sigma_2^{1/2}  (Z^{(2)})^{\top} Z^{(2)} \Sigma_2^{1/2} ,$$
%where $\Sigma_{1,2}$ are $p\times p$ deterministic covariance matrices, and $X^{(1)}=(x_{ij})_{1\le i \le n_1, 1\le j \le p}$ and $X^{(2)}=(x_{ij})_{n_1+1\le i \le n_1+n_2, 1\le j \le p}$ are $n_1\times p$ and $n_2 \times p$ random matrices, respectively, where the entries $x_{ij}$, $1 \leq i \leq n_1+n_2\equiv n$, $1 \leq j \leq p$, are real independent random variables satisfying
%\begin{equation}\label{eq_12moment} %\label{assm1}
%\mathbb{E} z_{ij} =0, \ \quad \ \mathbb{E} \vert z_{ij} \vert^2  = 1.
%\end{equation}
%\todo{A proof outline; including the following key lemma.}
By equations \eqref{eq_te_model_shift} and \eqref{eq_te_var}, we can write
\begin{align*}
L(\wh{\beta}_t^{\STL}) - L(\wh{\beta}_t^{\MTL})=\delta_{\vari}(\wh v) - \delta_{\bias}(\wh v),
\end{align*}
where we denote
\begin{align*}
\delta_{\vari}(\wh v)&=\sigma^2 \left(  \bigtr{((X^{(2)})^{\top}X^{(2)})^{-1}\Sigma_2} -  \bigtr{( \wh{v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1} \Sigma_2}\right),
\end{align*}
and
\begin{align}\label{revise_deltabias}
 \delta_{\bias}(\wh v)&= \wh{v}^2 \bignorm{\Sigma_2^{1/2}(\wh{v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1} (X^{(1)})^{\top}X^{(1)} (\beta_1 - \wh{v} \beta_2)}^2.
\end{align}
We introduce the notation $\wh M \equiv \wh M(v)= v\Sigma_1^{1/2}\Sigma_2^{-1/2}$ for $v\in \R$. Then the proof is divided into the following four steps.
\begin{itemize}
\item[(i)] We first consider $ \wh M(v)$ for a fixed $v\in \R$. Then we use Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift} to calculate the variance reduction $\delta_{\vari}(v)$, which will lead to the $\Delta_{\vari}$ term.
%$$\sigma^2 \cdot \bigtr{((X^{(2)})^{\top}X^{(2)})^{-1}},\quad \sigma^2 \cdot \bigtr{({v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1} \Sigma_2},$$
%and the difference between them

\item[(ii)] Using the approximate isometry property of $Z^{(1)}$ in equation \eqref{eq_isometric}, we will approximate the bias term $ \delta_{\bias}(v)$ by
%$${v}^2 \bignorm{\Sigma_2^{1/2}({v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1} (X^{(1)})^{\top}X^{(1)} (\beta_1 - {v} \beta_2)}^2$$
%through
\be\label{deltabetapf}
\wt\delta_{\bias}(v):={v}^2 n_1^2\bignorm{\Sigma_2^{1/2}({v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1} \Sigma_1 (\beta_1 - {v} \beta_2)}^2.\ee

\item[(iii)] We use Lemma \ref{lem_cov_derivative} to calculate \eqref{deltabetapf}, which will lead to the $\Delta_{\bias}$ term.

\item[(iv)] Finally we use a standard $\e$-net argument to extend the above results to $\wh M(\wh v)$ for a possibly random $\wh v$ which depends on $Y_1$ and $Y_2$.
\end{itemize}

\paragraph{Step I: Variance reduction.} Consider $\wh M(v)$ for a fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$,
$$  \sigma^2 \cdot \bigtr{((X^{(2)})^{\top}X^{(2)})^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
and
$$ \sigma^2 \cdot \bigtr{( {v}^2 (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{( a_1(v) \wh M^{\top}\wh M + a_2(v)\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
with overwhelming probability, where $a_1(v)$ and $a_2(v)$ satify equation \eqref{eq_a12extra} with $\wh v$ replaced by $v$. The subtraction of these two terms gives
\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
\ee
where $\Delta_{\vari}(v)$ is defined as in equation \eqref{Deltavarv} but with $\wh v$ replaced by $v$.

\paragraph{Step II: Bounding the bias term.}
Next we use equation \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$. %in \eqref{deltabetapf}.
%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
\begin{claim}\label{prop_model_shift}
	In the setting of Lemma \ref{thm_model_shift},
	we denote $K(v) := (v^2(X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1}$, and
	\begin{align*}
		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K (X^{(1)})^{\top}X^{(1)}(\beta_1 - v\beta_2)}^2, \\
		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K(v) \Sigma_2 K(v) \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
	\end{align*}
	Then we have w.h.p.
	\begin{align*}
		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right|
		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}(v).
	\end{align*}
%	We have that
%	\begin{align*}
%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
%		\le  \delta_1 - \delta_2
%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
%	\end{align*}
%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
%	\begin{align*}
%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
%		\le \bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1}(X^{(1)})^{\top}X^{(1)}(\beta_1 - \beta_2)}^2.
%	\end{align*}
\end{claim}

\begin{proof}
	%The proof follows by applying equation \eqref{eq_isometric}.
	%Recall that $(X^{(1)})^{\top}X^{(1)} = \Sigma_1^{1/2}(Z^{(1)})^{\top}Z^{(1)}\Sigma_1^{1/2}$.
We can calculate that
%	Let $\alpha = \bignorm{\Sigma_2^{1/2} K \Sigma_1 (\beta_1 - \wh{w}\beta_2)}^2$.
	%We have
	\begin{align}
%		& \bignorm{\Sigma_2^{1/2}((X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)})^{-1}(X^{(1)})^{\top}X^{(1)}(\beta_1 - \wh{w}\beta_2)}^2 \nonumber \\
		 \delta_{\bias}(v)-\wt\delta_{\bias}(v)&= {2v^2n_1}(\beta_1 - v\beta_2)^{\top}\Sigma_1^{1/2} \cE\left(\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}\right) \Sigma_1^{1/2} (\beta_1 - v\beta_2) \nonumber
		\\
		&+ v^2\bignorm{\Sigma_2^{1/2} K \Sigma_1^{1/2}\cE \Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2. \label{eq_lem_model_shift_1}
%		\le& n_1\bigbrace{{n_1^2}{} + \frac{2n_1}p(p + 2\sqrt{{n_1}p}) + (p + 2\sqrt{{n_1}p})^2} \alpha = n_1^2\bigbrace{1 + \sqrt{\frac{p}{n_1}}}^4 \alpha. \nonumber
	\end{align}
	where we denote $\cE: = (Z^{(1)})^{\top}Z^{(1)} - {n_1}\id$.
  Using equation \eqref{eq_isometric}, we can bound
	$$\|\cal E\|\le \left( \al_+(\rho_1)-1 + \OO(p^{-1/2+\e})\right)n_1, \quad \text{w.h.p.}$$
	Thus we can estimate that
	\begin{align*}
	| \delta_{\bias}(v)-\wt\delta_{\bias}(v)|&\le v^2 \left( 2n_1  \|\cal E\| +  \|\cal E\|^2 \right) \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
	&=  v^2 \left[\left( n_1 + \|\cal E\|\right)^2 -n_1^2 \right] \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
	& \le v^2 n_1^2 \left[ \al_+^2(\rho_1) + \OO(p^{-1/2+\e}) -1\right]\bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2,
	\end{align*}
	which concludes the proof by the definition of $\delta_{err}$.
%	we can bound the second term on the RHS of equation \eqref{eq_lem_model_shift_1} as
%	\begin{align*}
%		& \bigabs{(\beta_1 -  \beta_2)^{\top} \Sigma_1^{1/2} \cE \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - v\beta_2)}\le n_1  \|\cal E\| \cdot \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2 \\
%		= & \bigabs{\bigtr{\cE \Sigma_1^{1/2}K\Sigma_2 K \Sigma_1(\beta_1 - \wh{w}\beta_2)(\beta_1 - \wh{w}\beta_2)^{\top} \Sigma_1^{1/2}}} \\
%		\le & \norm{\cE} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \wh{w}\beta_2) (\beta_1 - \wh{w}\beta_2)^{\top} \Sigma_1^{1/2}} \\
%		\le & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \cdot \bignormNuclear{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1 (\beta_1 - \wh{w}\beta_2)(\beta_1 - \wh{w}\beta_2)^{\top} \Sigma_1^{1/2}} \tag{by equation \eqref{eq_isometric}} \\
%		\le   & n_1 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}} \bignorm{\Sigma_1^{1/2}K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 - \wh{w}\beta_2)}^2 \tag{since the matrix inside is rank 1}
%	\end{align*}
%	The third term in equation \eqref{eq_lem_model_shift_1} can be bounded with
%	\begin{align*}
%		\bignorm{\Sigma_2^{1/2}K\Sigma_1^{1/2}\cE\Sigma_1^{1/2}(\beta_1 - v\beta_2)}^2
%		\le n_1^2 \bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}^2 \bignorm{\Sigma_1^{1/2}K\Sigma_{2}K\Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2}(\beta_1 -  \beta_2)}^2.
%	\end{align*}
%	Combined together we have shown the right direction for $\delta_1 - \delta_2$.
%	For the left direction, we simply note that the third term in equation \eqref{eq_lem_model_shift_1} is positive.
%	And the second term is bigger than $-2n_1^2(2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}) \alpha$ using equation \eqref{eq_isometric}.
\end{proof}
Note by equation \eqref{eq_isometric}, we also obtain that with overwhelming probability,
\begin{align*}
&v^2 n_1^2 \Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2} =n_1^2 \wh M (\wh M^\top (Z^{(1)})^{\top} Z^{(1)} \wh M + (Z^{(2)})^\top Z^{(2)})^{-2}\wh M^\top \\
&\preceq  n_1^2 \wh M \left[n_1 \al_-(\rho_1)\wh M^\top \wh M + n_2 \al_-(\rho_2) + \OO(p^{1/2+\e})\right]^{-2}\wh M^\top \\
&\preceq  \left[ \al_-^2(\rho_1) \wh M\wh M^\top + 2\frac{\rho_2}{\rho_1} \al_-(\rho_1)\al_-(\rho_2) + \left(\frac{\rho_2}{\rho_1}\right)^2 \al_-^2(\rho_2) (\wh M \wh M^\top )^{-1}\right]^{-1}+  \OO(p^{-1/2+\e}) \\
&\preceq [\al_-^2(\rho_1) \lambda_{\min}^2(\wh M)]^{-1}\cdot (1 - c)
\end{align*}
for a small enough constant $c>0$. Together with Claim \ref{prop_model_shift}, we get that with overwhelming probability,
\be\label{bounddelta-}
\left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right|
		\le (1-c) \delta(v)
\ee
for some small constant $c>0$, where recall that $\delta(v)$ was defined in equation \eqref{eq_deltaextra}.

\paragraph{Step III: The limit of $\wt\delta_{\bias}(v)$.}
Using Lemma \ref{lem_cov_derivative}, we obtain that with overwhelming probability,
\begin{align*}
\wt\delta_{\bias}(v) &=\frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot v^2 (\beta_1-v\beta_2)^\top\Sigma_1 \Sigma_2^{-1/2}  \frac{(1 +  a_3(v))\id +v^2 a_4(v) {M}^{\top}{M}}{( v^2 a_1(v) {M}^{\top}{M}+a_2(v) )^2} \Sigma_2^{-1/2} \Sigma_1(\beta_1-v\beta_2) +\OO(p^{-1/2+\e}) \\
&= (\beta_1 - {v}\beta_2)^{\top} \Sigma_1^{1/2} \Pi(v) \Sigma_1^{1/2} (\beta_1 - {v}\beta_2) +\OO(p^{-1/2+\e}) =: \Delta_{\bias}(v) +\OO(p^{-1/2+\e}),
\end{align*}
where $a_3(v)$ and $a_4(v)$ satify equation \eqref{eq_a34extra} with $\wh v$ replaced by $v$, and $\Pi$ was defined in equation \eqref{defnpihat}. Together equations \eqref{deltavaral-} and \eqref{bounddelta-}, we obtain that w.h.p.,
\be\label{dicho_varbeta}
\begin{cases}\delta_{\vari}(v)>\delta_{\bias}(v), & \text{ if } \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \ge   \delta(v),\\
\delta_{\vari}(v)<\delta_{\bias}(v),  & \text{ if }  \ \ \Delta_{\vari}(v) - \Delta_{\bias}(v) \le -  \delta(v).\end{cases}
\ee

\paragraph{Step IV: An $\e$-net argument.} Finally, it remains to extend the above result \eqref{dicho_varbeta} to $v=\wh v$, which is random and depends on $X^{(1)}$ and $X^{(2)}$. We first show that for any fixed constant $C_0>0$, there exists a overwhelming probability event $\Xi$ on which equation \eqref{dicho_varbeta}
%\eqref{lem_cov_shift_eq} and \eqref{lem_cov_derv_eq}
holds uniformly for all $v\in [-C_0, C_0]$. In fact, we first consider $v$ that belongs to a discrete set
$$V:=\{v_k = kp^{-1}: -(C_0p +1)\le k \le C_0p +1\}.$$
Then using the arguments for the first three steps and a simple union bound, we get that equation
\eqref{dicho_varbeta} holds simultaneously for all $v\in V$ with overwhelming probability. On the other hand, by equation \eqref{eq_isometric} the event
$$\Xi_1:=\left\{ \al_-(\rho_1)/2 \preceq  \frac{(Z^{(1)})^{\top} Z^{(1)}}{n_1}  \preceq   2\al_+(\rho_1) ,\  \al_-(\rho_2)/2 \preceq  \frac{(Z^{(2)})^\top Z^{(2)}}{n_2}  \preceq   2\al_+(\rho_2)\right\}$$
holds with overwhelming probability. Now it is easy to check that on $\Xi_1$, the following estimates holds simultaneously for all $v_k \le v\le v_{k+1}$:
\begin{align*}
& |\delta_{\vari}(v) -\delta_{\vari}(v_k)|\lesssim p^{-1}\delta_{\vari}(v_k),\ \ |\delta_{\bias}(v) -\delta_{\bias}(v_k)|\lesssim p^{-1}\delta_{\bias}(v_k), \ \   |\delta(v)-\delta(v_k)|\lesssim p^{-1}\delta(v_k),\\
& |\Delta_{\bias}(v) -\Delta_{\bias}(v_k)|\lesssim p^{-1}\Delta_{\bias}(v_k),\ \ |\Delta_{\vari}(v) -\Delta_{\vari}(v_k)|\lesssim p^{-1}\Delta_{\vari}(v_k).
\end{align*}
Then a simple application of triangle inequality gives that the event
$$\Xi_2=\{\eqref{dicho_varbeta} \text{ holds simultaneously for all }-C_0\le v \le C_0\}$$
holds with overwhelming probability. On the other hand, on $\Xi_1$ it is easy to check that for any small constant $\e>0$, there exists a large enough constant $C_0>0$ depending on $\e$ such that
\begin{align*}
& |\delta_{\vari}(v) -\delta_{\vari}(C_0)|\le \e\delta_{\vari}(C_0),\quad |\delta_{\bias}(v) -\delta_{\bias}(C_0)|\le \e\delta_{\bias}(C_0), \quad  |\delta(v)-\delta(C_0)|\le \e\delta(C_0),\\
& |\Delta_{\bias}(v) -\Delta_{\bias}(C_0)|\le \e\Delta_{\bias}(C_0),\quad |\Delta_{\vari}(v) -\Delta_{\vari}(C_0)|\le \e\Delta_{\vari}(C_0),
\end{align*}
for all $v\ge C_0$. Similar estimates hold for $v\le -C_0$ if we replace $C_0$ with $-C_0$ in the above estimates. Together with the estimate at $\pm C_0$, we get that equation \eqref{dicho_varbeta} holds simultaneously for all $v\in \R$ on the overwhelming probability event $\Xi_1\cap \Xi_2$. This concludes the proof of Lemma \ref{thm_model_shift}, since $\wh v$ must be one of the real values.
\end{proof}

### 2020-09-24 arxiv/implications.tex
reorg
revise

@@
 
-\begin{example}[Varying model distance]
-\end{example}
+%\begin{example}[Varying model distance]
+%\end{example}
 
@@
 
-\begin{corollary}[Derived from Theorem \ref{thm main RMT}]
+\begin{corollary}[Derived from Theorem \ref{thm main RMT}]\label{cor MTL loss}
 	Assume that the isotropic setting described above holds, and that there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy that
@@
 	\begin{align*}
-	 \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} \\
-	 \le  \left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 )
+	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
+	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 )
 	 \end{align*}
@@
 
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
-We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
+The prediction loss of MTL has been given in Corollary \ref{cor MTL loss}.
+We can also calculate the prediction STL easily using Fact \ref{lem_minv} (ii).
+The proof of the following claim will be given in Section \ref{app_iso_cov}.
+\begin{claim}
+Under the above isotropic setting for task two, we have that with high probability,
+\begin{align*}
+	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-c}\sigma^2 )
+	 \end{align*}
+	 for any constant $c\in (0,1/2)$.
+\end{claim}
+
+\medskip
+
+\noindent{\bf Varying model distance.} We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
  In particular, the bias of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases.
@@
 
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
+\medskip
+\noindent{\bf Varying sample ratio.} In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
 %More generally, such results are still applicable when all task data are being added simultaneously.
@@
 \end{proposition}
-\cor
+
+\iffalse
 
@@
 \end{proof}
-\nc
+\fi
 

### 2020-09-24 arxiv/diff_cov.tex
wip

@@
-\section{The Different Covariates Setting}
+\section{The Different Covariates Setting}\label{sec_diff}
 
@@
 Hence, we consider the expected loss conditional on the covariates as follows:
-\begin{align*}
+\begin{align}\label{eq_diff_cov}
 	\exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}} =
@@
 	+ \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}.
-\end{align*}
+\end{align}
 
 Interestingly, the prediction loss admits a bias-variance decomposition similar to the same covariates setting.
+The variance equation scales with the sample covariance matrice of both tsks, whereas the bias equation scales additionally with the distance between the beta vectors.
 In both the bias and variance equations, the matrix inverse $\hat{\Sigma}^{-1}$ is a crucial quantity.
@@
 
-\begin{theorem}\label{thm main RMT}
+\begin{theorem}\label{thm_main_RMT}
 	Suppose that $X_1$ and $X_2$ are both random matrices that satisfy Assumption \ref{assume_rm}.
@@
 \end{theorem}
+\noindent{\textbf{Remark.}} Our result extends a well-known result on the inverse of sample covariance matrices.
+In particular, by setting $X_1 = 0$, we obtain the second result in Fact \ref{lem_minv}.
+When $X_1=0$, it is not hard to solve $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ from equation \eqref{eq_a12extra}, and our result reduces to the case of a single sample covariance matrix.
+For the single-task case of a multivariate Gaussian random matrix, the result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For a non-Gaussian random matrix, the result can be obtained using the Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
 
-Lemma \ref{lem_cov_shift} also implies the asymptotic limit of the prediction loss of single-task learning.
-%The next lemma, which is , helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})=\sigma^2   \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2}$ as $p\to \infty$.
-In particular, by setting $X_1 = 0$, we obtain Lemma \ref{lem_minv}.
-%\begin{corollary}[See e.g. Theorem 2.4 in \citet{isotropic}]\label{lem_minv}
-%	In the setting of Lemma \ref{lem_cov_shift}, with high probability we have that
-%	\be\label{XXA}  \bigtr{(X_2^{\top}X_2)^{-1}\Sigma} = \frac{1}{n_2 - p} \cdot \bigtr{\Sigma_2^{-1}\Sigma} + o(\norm{\Sigma}). \ee
-%\end{corollary} %\bigo{ \|A\|p^{-1/2+\epsilon}}
-To see this, note that when $n_1=0$, $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ is the solution of \eqref{eq_a12extra}, and one can see that equation \eqref{lem_cov_shift_eq} reduces to equation \eqref{XXA}.
-We briefly describe the history behind the above well-known result.
-When the entries of $X_2$ are multivariate Gaussian, this result recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For general non-Gaussian random matrices, it can be obtained using Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}.
-Here we have stated a result from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp concentration error bound.
-One can see that our result extends Lemma \ref{lem_minv} from a single sample covariance matrix to the sum of two independent sample covariance matrices.
-%We now state our main result for two tasks with both covariate and model shift.
-It shows that the information transfer is determined by two deterministic quantities $\Delta_{\bias}$ and $\Delta_{\vari}$, which give the change of model shift bias and the change of variance, respectively.
-The exact forms of $\Delta_{\bias}$ and $\Delta_{\vari}$ will be given in Lemma \ref{thm_model_shift}.
-
-Interestingly, the asymptotic limit of the variance only depends on the sample sizes and the covariate shift matrix.
-Next, we derive the asymptotic limit of the bias equation \eqref{eq_bias_2task}, which depends on the scaled model distance in addition to sample size and covariate shift.
-%(cf.
-Lemma \ref{lem_cov_derivative} in Appendix \ref{app_proof_main_thm}).
-
-In the rest of section, we describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
-In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
-The full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} will be given in Section \ref{appendix RMT}.
-%\subsection{The Bias and Variance Asymptotics}
-
-%\todo{merge} Finally, in this subsection, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.
-%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
-%We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
+By combining the bias and variance asymptotics, we obtain the generalization error of $\hat{\beta}_2^{\MTL}$.
+Since the proof is similar to the same covariates setting, we describe the key differences and omit the rest of the details.
+First, we will rescale $X_1$ by $A_1 / A_2$ before appling Theorem \ref{thm_main_RMT}.
+Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov}.
+In the rest of section, we briefly the main ideas in the proof of Theorem \ref{thm_main_RMT}.
+%We will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
+The full proof can be found in Section \ref{sec_maintools}.
 
@@
 The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
-
-%\alert{Together with equation \eqref{rewrite X as R} and $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}, we can obtain equation \eqref{lem_cov_shift_eq} in the large $n$ limit.}\HZ{I do not understand this sentence.}

### 2020-09-24 arxiv/setup.tex
wip

@@
 \paragraph{Organizations.}
-\todo{revise} The appendix is organized as follows.
-In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
-In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
-In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
-In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
-In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
-Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.
+The rest of this paper is organized as follows.
+In Section \ref{set_prelim}, we present a preliminary of hard parameter sharing and random matrices. We describe several well-known facts.
+In Section \ref{sec_example}, we describe illustrative examples of our technical results and discuss their implications.
+In Section \ref{sec_same}, we consider the same covariates setting and show the generalization error of hard parameter sharing.
+In Section \ref{sec_diff}, we consider the different covariates setting and show the bias and variance asymptotics using random matrix theory.
 
-\section{Preliminaries}
+\section{Preliminaries}\label{sec_prelim}
 
@@
 We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-%\subsection{Bias and Variance}
 
@@
 \begin{fact}\label{lem_minv}
-	Let $c$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
+	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
 	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
@@
 Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-Let $\e > 0$ denote \todo{?? to check}.
+Let $\e$ be an fixed value within $(0, 1/2)$.

### 2020-09-24 arxiv/implications.tex
wip
revise+

@@
-\section{Implications}\label{sec_special}
+\section{Illustrative Examples}\label{sec_special}
 
@@
 
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
+It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
+We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
 The prediction loss of MTL has been given in Corollary \ref{cor MTL loss}.

### 2020-09-24 arxiv/diff_cov.tex

@@
 First, we will rescale $X_1$ by $A_1 / A_2$ before appling Theorem \ref{thm_main_RMT}.
-Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov}.
-In the rest of section, we briefly the main ideas in the proof of Theorem \ref{thm_main_RMT}.
+Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
+For the rest of this section, we the main ideas in the proof of Theorem \ref{thm_main_RMT}.
 %We will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
@@
 
-\paragraph{Preliminaries.} Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $[(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}$ for $X^{(1)}= Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}= Z^{(2)}\Sigma_2^{1/2}$.
-Then using equation \eqref{eigen2}, we can write
-\be\label{eigen2extra}[(X^{(1)})^\top (X^{(1)})+(X^{(2)})^\top (X^{(2)})]^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
-%We divide the discussion into the following parts.
-To study this expression, we shall use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-We now give some preliminaries about this method before discussing the proof strategy.
+\paragraph{Proof overview.} The central quantify of interest is the matrix inverse $\hat{\Sigma}^{-1}$.
+To study this quantity, we use the Stieltjes transform or the resolvent method in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+%We give some preliminaries about this method before discussing the proof strategy.
+For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z},\quad z\in \C\setminus [0,\infty).$$
+Conversely, given a Stieltjes transform $m_{\mu}(z)$, we can recover the measure $\mu$ through the inverse formula \HZ{add a ref to the equation below}
+$$ \frac{\dd \mu(x)}{\dd x} = \frac{1}{\pi}\lim_{\eta \downarrow 0}\im m_{\mu}(x+\ii \eta).$$
+%where $\rho(x)$ is the density for $\mu$, i.e. $\dd \mu(x)=\rho(x)\dd x$.
+Hence the Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
+To study the matrix inverse $\hat{\Sigma}^{-1}$, we consider its empirical spectral distribution.
+More precisely, since
+\begin{align}\label{eigen2extra}
+	\hat{\Sigma}^{-1}= \Sigma_2^{-1/2}V \frac{Y^{-1}}{n_1 + n_2} V^\top\Sigma_2^{-1/2}.
+\text{ where } Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V),
+\end{align}
+let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$.
+The scaling $(n_1+n_2)^{-1}$ ensures such that the support of $\mu$ is bounded.
+The Stieltjes transform of the empirical spectral distribution $\mu$ is as follows
+ \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[ (Y_p-z\id_p)^{-1}\right], \]
+and when $p$ goes to infinity, $m_{\mu}(z)$ converges to a fixed-point governed by a set of self-consistent equations.
+These self-consistent equations give the asymptotic limit of the trace of $\hat{\Sigma}^{-1}$.
 
-For any measure $\mu$ supported on $[0,\infty)$, it defines a Stieltjes transform through
-$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z},\quad z\in \C\setminus [0,\infty).$$
-Conversely, given a Stieltjes transform $m_{\mu}(z)$, we can recover the measure $\mu$ through the inverse formula
-$$ \rho(x)=\frac{1}{\pi}\lim_{\eta \downarrow 0}\im m_{\mu}(x+\ii \eta),$$
-where $\rho(x)$ is the density for $\mu$, i.e.
-$\dd \mu(x)=\rho(x)\dd x$.
-Hence the Stieltjes transform method reduces the study of a measure $\mu$ to the study of an analytic function $m_\mu(z)$.
-Let $\mu=p^{-1}\sum_{i=1}^p \delta_{\sigma_i}$ be the empirical spectral distribution of the matrix $Y_p:=(n_1+n_2)^{-1}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V)$, where $\sigma_i$ denote the eigenvalues of $Y_p$, and the scaling $(n_1+n_2)^{-1}$ is chosen such that $\pi$ is supported on a bounded interval.
-Then with the above notations, the Stieltjes transform of the empirical spectral distribution $\mu$ is
-$$ m_{\mu}=\frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[ (Y_p-z\id_p)^{-1}\right].$$
-The Stieltjes transform method in random matrix theory aims to show that $m_{\mu}$ satisfies a fixed-point equation asymptotically, which allows us to derive the asymptotic limit of $\mu$.
-
-However, for our purpose, we not only need to know the limit of the trace $\tr\left[ (Y_p-z\id_p)^{-1}\right]$, but also need to obtain the limit of $\tr\left[ (Y_p-z\id_p)^{-1}B\right]$ for any given deterministic matrix $B$.
-This  requires us to study the matrix $(Y_p-z\id_p)^{-1}$ directly, which is called resolvent or Green's function.
-Roughly speaking, the resolvent can be regarded as a matrix version of the Stieltjes transform.
-The convergence of resolvent can be formulated formally in a slightly more modern language in terms of local laws, see e.g.
-\cite{isotropic,erdos2017dynamical,Anisotropic}, or deterministic equivalents, see e.g., \cite{Hachem2007deterministic,DS18}.
-More precisely, given a deterministic $p\times p$ matrix, say $R_p(z)$, of growing dimensions, we say that it is a deterministic equivalent of $(Y_p-z\id_p)^{-1}$ if for any sequence of deterministic matrices $B_p$ of uniformly bounded operator norms,
-$$\tr \left\{\left[ (Y_p-z\id_p)^{-1}-R_p(z)\right]B_p\right\}\to 0.$$
-If this holds, then we shall say that $(Y_p-z\id_p)^{-1}$ has a matrix limit $R_p$.
-In this paper, we shall prove a stronger convergence of the resolvent $(Y_p-z\id_p)^{-1}$ in the sense of local laws, which also gives an (almost) sharp convergence rate.
-Our proof will be centralized around the resolvent and its local law.
-
-\paragraph{Proof overview.} We divide the discussion into the following parts.
+The above approach applies when $\Sigma^{(2)}$ is isotropic in Theorem \ref{thm_main_RMT}.
+For general covariances, we want to study the limit of $\tr\left[ (Y - z\id)^{-1}V^{\top}{\Sigma^{(2)}}^{-1}V \right]$ as shown in equation \eqref{eigen2extra}.
+Hence, we study the resolvent matrix or Green's function $(Y-z\id)^{-1}$.
+Compared to the Stieltjes transform, the resolvent also applies to random matrices.
+The convergence of resolvent is formally shown using the so-called ``local laws'' (cf.
+\cite{isotropic,erdos2017dynamical,Anisotropic}) or ``deterministic equivalents'' (cf.
+\cite{Hachem2007deterministic,DS18}).
+More precisely, given a deterministic $p\times p$ matrix $R(z)$, we say that $R(Z)$ and $(Y-z\id)^{-1}$ are equivalent if for any sequence of deterministic matrices $B$ of uniformly bounded operator norms,
+$$\tr \left\{\left[ (Y-z\id)^{-1}-R(z)\right]B\right\}\to 0.$$
+If the above equation holds for all $p$, then we say that $(Y-z\id)^{-1}$ has a matrix limit $R$.
+For our result, we shall prove the convergence of the resolvent $(Y-z\id)^{-1}$ using ``local laws'' with a sharp convergence rate.
 
 \medskip
-\noindent\textbf{Defining the resolvents.} For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
+\noindent\textbf{Resolvents.} For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
 $$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
@@
 \medskip
-\noindent\textbf{Defining the asymptotic limits of the resolvents.}
+\noindent\textbf{Asymptotic limits of resolvents.}
 %\label{sec aymp_limit_G}
@@
 \medskip
-\noindent{\bf Deriving the variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
+\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
 \be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee

### 2020-09-24 arxiv/proof_gaussian_case.tex
wip

@@
-\subsection{Warmup: Proof Overview for the Gaussian Case}
+\section{Missing Proof of the Different Covariates Setting}\label{sec_maintools}
+
+%\input{proof_two_tasks}
+
+\subsection{Warmup: The Gaussian Case}
 Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,

### 2020-09-25 arxiv/proof_gaussian_case.tex
wip

@@
 %\input{proof_two_tasks}
+
+\paragraph{Notations.}
+Define the index sets
+$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
+ We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
+ \be\label{labelZ}
+ Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
+
+Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
+\be\label{defm}
+\begin{split}
+m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
+ m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
+\end{split}
+\ee
+We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof.
+We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
 

### 2020-09-25 arxiv/implications.tex
revise

@@
-\section{Illustrative Examples}\label{sec_special}
+\section{Illustrative Examples}\label{sec_example}
 
@@
 
-Using Theorem \ref{thm main RMT}, %our techniques described later in Section \ref{sec_general}, 
-we derive the limiting prediction loss of the hard parameter sharing estimator.
+Using Theorem \ref{thm_main_RMT}, %our techniques described later in Section \ref{sec_general}, 
+we can derive the limiting prediction loss of the hard parameter sharing estimator.
 Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
 
-\begin{corollary}[Derived from Theorem \ref{thm main RMT}]\label{cor MTL loss}
+\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
 	Assume that the isotropic setting described above holds, and that there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy that
@@
 	Let $B, W_1, W_2$ be the global minimum of equation \eqref{eq_mtl}. Then with high probability, the prediction loss of the hard parameter sharing estimator for task two satisfies:
-	\begin{align*}
+	\begin{align}\label{cor_MTL_error}
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
 	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 )
-	 \end{align*}
+	 \end{align}
 	 for any constant $c\in (0,c_0)$.
@@
 We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
-The prediction loss of MTL has been given in Corollary \ref{cor MTL loss}.
-We can also calculate the prediction STL easily using Fact \ref{lem_minv} (ii).
+The prediction loss of MTL has been given in Corollary \ref{cor_MTL_loss}.
+We can also calculate the prediction loss of STL easily using Fact \ref{lem_minv} (ii).
 The proof of the following claim will be given in Section \ref{app_iso_cov}.
-\begin{claim}
+\begin{claim} \label{claim_STL_loss}
 Under the above isotropic setting for task two, we have that with high probability,
@@
 
+We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transition from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.
+
 \medskip
 
-\noindent{\bf Varying model distance.} We show that as we increase the distance between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
- In particular, the bias of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases.
-Therefore, while the variance of MTL still reduces compared to STL, if the bias increases more than the amount of variance reduced, we will observe negative transfer.
+\noindent{\bf Varying model distance.} 
+%With Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss}, it is not hard to see 
+One can observe that as we increase the distance $pd^2$ between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+More precisely, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases, while variance reduction from STL to MTL is $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$.
+%Therefore, while the variance of MTL still reduces compared to STL, 
+If the bias increases more than the amount of variance reduced, we will observe negative transfer.
 
+\iffalse
 \begin{proposition}[Task model distance]\label{prop_dist_transition}
@@
 \end{proposition}
-
 Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
@@
 %Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
-We apply Proposition \ref{prop_dist_transition} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+\fi
+
+We apply Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
 We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error $\nu$.
+There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
 %We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
@@
 %We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
+
+\iffalse
 The proof of Proposition \ref{prop_dist_transition} involves two parts.
@@
 thus simplifying the general condition in Theorem \ref{thm_main_informal}.
+\fi
 
@@
 In the isotropic model, we consider what happens if we vary the source task sample size.
+More precisely, for fixed model distance $pd^2$, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases and converges to $pd^2$ as the sample ratio $\rho_1/\rho_2$ increases.
+On the other hand, the variance reduction $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$ also increases and converges to $\frac{\sigma^2}{\rho_2-1}$ as the sample ratio $\rho_1/\rho_2$ increases.
+\todo{add more details}
+%Therefore, while the variance of MTL still reduces compared to STL, 
+%If the bias increases more than the amount of variance reduced, we will observe negative transfer.
 Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-Figure \ref{fig_size} provides a simulation result for such a setting.
+Figure \ref{fig_size} provides a simulation result for such a setting (described in Appendix \ref{app_synthetic}).
 We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
 
+\iffalse
 \begin{proposition}[Source/target sample ratio]\label{prop_data_size}
@@
 Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
+
 We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
@@
 The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
+\fi
 

### 2020-09-25 arxiv/diff_cov.tex

@@
 More precisely, given a deterministic $p\times p$ matrix $R(z)$, we say that $R(Z)$ and $(Y-z\id)^{-1}$ are equivalent if for any sequence of deterministic matrices $B$ of uniformly bounded operator norms,
-$$\tr \left\{\left[ (Y-z\id)^{-1}-R(z)\right]B\right\}\to 0.$$
-If the above equation holds for all $p$, then we say that $(Y-z\id)^{-1}$ has a matrix limit $R$.
+$$\bigtr{((Y-z\id)^{-1}-R(z))B}\to 0.$$
+If the above equation holds for all $p$, then we say that $(Y-z\id)^{-1}$ has a matrix limit $R(z)$.
 For our result, we shall prove the convergence of the resolvent $(Y-z\id)^{-1}$ using ``local laws'' with a sharp convergence rate.
 
-\medskip
-\noindent\textbf{Resolvents.} For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
-$$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
-which is linear in $A$.
-This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
-Our goal is to study the SVD of the rectangular matrix $(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top)$.
-%For this purpose,
+%For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
+%$$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
+%which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
+For the matrix $Y$ that we want to study, we can also write $Y = A A^{\top}$, where $A = [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top] \in \real^{p\times {n_1 + n_2}}$.
 %}\HZ{what does this trick mean? use less technical words},
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Then we define the following $(p+n)\times (p+n)$ symmetric block matrix
+Consider the following $(p+n)\times (p+n)$ symmetric block matrix
 %which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
@@
  \begin{equation}\label{linearize_block}
-    H\left(\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top\right): = n^{-1/2}\left( {\begin{array}{*{20}c}
+    H \define (n_1 + n_2)^{-1/2}\left( {\begin{array}{*{20}c}
    { 0 } & \Lambda U^{\top}(Z^{(1)})^\top & V^\top (Z^{(2)})^\top  \\
@@
  \end{equation}
-For simplicity of notations, we abbreviate it as $H$ in the following discussion, and define the index sets
-$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
- We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
- \be\label{labelZ}
- Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
-Now we define the resolvents as follows.
+The resolvent of $H$ is defined as follows.
 \begin{definition}[Resolvents]
-We define the resolvent (or Green's function) of $H$ as
- \begin{equation}\label{eqn_defG}
- G (z):= \left[H -\left( {\begin{array}{*{20}c}
-   { z\id_{p}} & 0 & 0 \\
-   0 & { \id_{n_1}}  & 0\\
-      0 & 0  & { \id_{n_2}}\\
-\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C ,
- \end{equation}
+We define the resolvent or Green's function of $H$ as
+ $G(z) \define (H - z\id_{p + n_1 + n_2})^{-1}$, for any complex value $z\in \mathbb C$.  %\left[H -\left( {\begin{array}{*{20}c}
+%   { z\id_{p}} & 0 & 0 \\
+%   0 & { \id_{n_1}}  & 0\\
+%      0 & 0  & { \id_{n_2}}\\
+%\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C ,
 %It is easy to verify that the eigenvalues $\lambda_1(H)\ge \ldots \ge \lambda_{n+N}(H)$ of $H$ are related to the ones of $\mathcal Q_1$ through
@@
 %\begin{definition}[Index sets]\label{def_index}
-and the resolvent of $  n^{-1}\left(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)$ as
-\be\label{mainG}
-\cal G(z):=\left( n^{-1}  \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + n^{-1}V^\top (Z^{(2)})^\top Z^{(2)}V -z\right)^{-1},\quad z\in \C.
-\ee
-Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
-\be\label{defm}
-\begin{split}
-m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
- m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
-\end{split}
-\ee
-We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof.
-We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
+Similarly, the resolvent of $Y$ is defined as $\cal G(z):=(Y - z\id_{p})^{-1}$, for any $z\in \mathbb C$.
 \end{definition}
-With Schur complement formula, we can check that %\HZ{Has $G(z)$ been defined before?}
+
+Using the Schur complement formula, we have that %\HZ{Has $G(z)$ been defined before?}
  \begin{equation} \label{green2}
- G (z):=  \left( {\begin{array}{*{20}c}
+  G(z) =  \left( {\begin{array}{*{20}c}
    { \cal G (z)} & \cal G(z)A  \\
@@
  \end{equation}
- where we abbreviated
- \be\label{abbr_A}
- A:= n^{-1/2}(\Lambda U^\top (Z^{(1)})^\top, V^\top (Z^{(2)})^\top).
- \ee
- %\HZ{$W$ is overloaded with the output layers}
 This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
 On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
-%one can find that %(recall equation \eqref{mainG})
-%\be \label{green2}
-%\begin{split}
-%& \cal G_{L}=\left(WW^\top -z \right)^{-1} =\cal G ,\quad \cal G_{LR}=\cal G_{RL}^\top  = \cal G W , \quad \cal G_R= z\left(W^\top W - z\right)^{-1}.
-%\end{split}
-%\ee
-%, and the subindex of $\cal G_R$ means the lower-right block.
 
-%Now using Schur complement formula, we can verify that the (recall equation \eqref{def_green})
-%\begin{align}
-%G = \left( {\begin{array}{*{20}c}
-%   { z\mathcal G_1} & \mathcal G_1 \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2}  \\
-%   {\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} \mathcal G_1} & { \mathcal G_2 }  \\
-%\end{array}} \right) = \left( {\begin{array}{*{20}c}
-%   { z\mathcal G_1} & \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2} \mathcal G_2   \\
-%   {\mathcal G_2}\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} & { \mathcal G_2 }  \\
-%\end{array}} \right). \label{green2}
-%\end{align}
-%where $\mathcal G_{1,2}$ are defined in (\ref{def_green}).
-
-\medskip
 \noindent\textbf{Asymptotic limits of resolvents.}
-%\label{sec aymp_limit_G}
-%\subsection{Resolvents and limiting law}
 We now describe the asymptotic limit of $G(z)$ as $n\to \infty$.

### 2020-09-25 arxiv/proof_examples.tex
reorg
fix links

@@
-\section{Proof of the Special Case}\label{app_iso_cov}
+\subsection{Proof of the Special Case}\label{app_iso_cov}
 \todo{switch the $a_3$ and $a_4$}
@@
 \end{align}
-where $\delta_{\bias}(v)$ was defined in \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}.
+where $\delta_{\bias}(v)$ was defined in \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
 Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
@@
 \end{align*}
-Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric}, we obtain that
+Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using Fact \eqref{lem_minv}, we obtain that
 \be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
@@
 $$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim p$ by \eqref{eq_isometric}. Hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
+Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
 \be\label{replaceest}
@@
 First it is easy to observe that $h(w)< h(-w)$ for $w> 0$.
-Second, using \eqref{eq_isometric}, it is easy to check that $h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.
+Second, using Fact \eqref{lem_minv}, it is easy to check that $h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.
 Hence it suffices to consider the case $1/2\le w\le 2$.
@@
 \end{align*}
-Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
+Using the estimate Fact \eqref{lem_minv}, we get that $\cal A$ is lower bounded as
 \begin{align*}
@@
 $$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{\rho_2}{\rho_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
-Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
+Using Fact \ref{lem_minv}, we get that $\cal B$ is upper bounded as
 \begin{align*}
@@
 \end{align}
-In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. With \eqref{eq_isometric}, we have that
+In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. Using Fact \eqref{lem_minv}, we have that
 $$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim 1.$$
@@
 
+\iffalse
 \subsection{Task Similarity}\label{app_proof_31}
@@
 In other words, $\val(w)$ is strictly increasing function on $[1+\e_0,\infty]$. Thus we get that $\hat w$ satisfies
-\be\label{hatw1}1\le w \le 1+\e_0.\ee Using \eqref{eq_isometric}, we get that
+\be\label{hatw1}1\le w \le 1+\e_0.\ee Using Fact \ref{lem_minv}, we get that
 $$\e_0=\OO(\sigma^2/\|\beta_t\|_2^2)=\OO(p^{-1}).$$
@@
 %where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has
-To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using Fact \eqref{lem_minv}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
 This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
@@
 Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
-
-%Using \eqref{eq_isometric} and Lemma \ref{lem_cov_derivative}, a similar bound holds for $\Delta_{diff}$ as in \eqref{Deltabeta}:
-%$$\bigbrace{1 - \sqrt{\frac{1}{c_1}}}^2\le \frac{\Delta_{diff}}{\sigma_1^2 -\sigma_2^2}\cdot \left( \frac{c_1 (c_1+c_2)}{(c_1+c_2-1)^3} + \OO(p^{-1/2+\e})\right)^{-1}\le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^2.$$
 
@@
 \end{remark}
+\fi

### 2020-09-25 arxiv/proof_same_cov.tex
fix links

--- 2020-09-19 arxiv/proof_same_cov.tex
@@
 	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
+	In the third step, we use Fact \ref{lem_minv} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
 
@@
 	The proof is complete.
+
+	\paragraph{Proof of Claim \ref{claim_pred_err}.}
+
+	\paragraph{Proof of Theorem \ref{thm_many_tasks}.}
+	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
+	%Now we are ready to finish the proof.
+	%Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
+	%\begin{align}
+	%	L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
+	%\end{align}
+	%Using equation \eqref{eq_ex_pred}, we have that
+	%\begin{align}
+	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
+	%	+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
+	%	&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
+	%	&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
+	%\end{align}
+	%In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
+	%\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
+\]
+  %In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
+	%Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
 	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.

### 2020-09-25 arxiv/implications.tex
revise

@@
 
-We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transition from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.
+We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transitions from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.
 

### 2020-09-25 arxiv/proof_examples.tex
revise

@@
 
-\begin{proof}[Proof of Claim \ref{claim_covar_shift}]	
+%\subsection{Covariate Shift}\label{app_proof_33}
+
+Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.
+
+%\begin{proof}[Proof of Claim \ref{claim_covar_shift}]	
+%	With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
+Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
+%\be \nonumber
+%\begin{split}
+%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
+%\end{split}
+%\ee
+% for some constant $\e>0$.
+In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
+We omit the details here.
+% \end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop_covariate}]
+Denote the minimizer of $g$ by 
+$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
+We now calculate $g(M_0)$.
 With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
@@
 We omit the details here.
+
+Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
+\begin{align}\label{gvar_extra}
+g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
+\end{align}
+From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
+\be\label{est_a12extra}
+\frac{\rho_1-1}{\rho_1+\rho_2} < a_1(M)<  \frac{\rho_1+\rho_2-1}{\rho_1+\rho_2},\quad a_2(M) < \frac{\rho_2}{\rho_1+\rho_2}.
+\ee
+Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
+\begin{align}\label{approximateteM}
+\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
+\end{align}
+where
+$$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
+%With these two bounds, we can easily conclude \eqref{approxteM}. 
+%
+%We have that the test error satisfies
+%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
+%where $\lambda_p$ is the smallest singular value of $p$ and
+%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
+%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+By AM-GM inequality, we observe that 
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
+is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
+\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
+On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
+\begin{align}\label{gvar_extra2}
+\begin{split}
+g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
+&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
+\end{split}
+\end{align}
+Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
+%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
 \end{proof}
+
+\iffalse
+
+In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
+When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
+When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
+We provide a theoretical justification now.
+
+\begin{proof}[Theoretical justification of Example \ref{ex_complement}]
+We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+Then equations in \eqref{eq_a12extra} become
+\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
+\ee
+%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. 
+After solving these, with \eqref{gvar_extra} we get that w.h.p.,
+\be\label{testcomple}
+ \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
+
+%First we notice that the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
+In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
+Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
+%$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
+
+%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
+$M=\id$ case) when $n_1<n_2$.
+On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
+We now study the behavior of $f$ as $\lambda$ changes. 
+%This phenomenon can be also explained using our theory. 
+We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with \eqref{compleeq}, we can rewrite
+$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
+Then we can compute that
+\begin{align*}
+f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
+\end{align*}
+From this expressions, we observe the following behaviors.
+\begin{itemize}
+\item[(i)] If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}).
+Hence $f(\lambda)>f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)>\te(\hat \beta_{2}^{\MTL},1)$.
+
+\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $f(\lambda)< f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
+
+\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
+%, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
+\end{itemize}
+This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
+\end{proof}
+\fi
 
@@
 
-\iffalse
-
-\subsection{Covariate Shift}\label{app_proof_33}
-
-Finally, in this subsection we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.
-
-\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-Denote the minimizer of $g$ by 
-$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
-We now calculate $g(M_0)$.
-With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
-\be \nonumber
-\begin{split}
-g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
-\end{split}
-\ee
- for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-
-Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-\begin{align}\label{gvar_extra}
-g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-\end{align}
-From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
-\frac{\rho_1-1}{\rho_1+\rho_2} < a_1(M)<  \frac{\rho_1+\rho_2-1}{\rho_1+\rho_2},\quad a_2(M) < \frac{\rho_2}{\rho_1+\rho_2}.
-\ee
-Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-\begin{align}\label{approximateteM}
-\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-\end{align}
-where
-$$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}. 
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that 
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
-\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-\begin{align}\label{gvar_extra2}
-\begin{split}
-g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-\end{split}
-\end{align}
-Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-\end{proof}
-
-In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
-When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-We provide a theoretical justification now.
-
-\begin{proof}[Theoretical justification of Example \ref{ex_complement}]
-We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-Then equations in \eqref{eq_a12extra} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\ee
-%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. 
-After solving these, with \eqref{gvar_extra} we get that w.h.p.,
-\be\label{testcomple}
- \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
-
-%First we notice that the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
-In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
-%$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-
-%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
-$M=\id$ case) when $n_1<n_2$.
-On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-We now study the behavior of $f$ as $\lambda$ changes. 
-%This phenomenon can be also explained using our theory. 
-We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with \eqref{compleeq}, we can rewrite
-$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
-Then we can compute that
-\begin{align*}
-f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-\end{align*}
-From this expressions, we observe the following behaviors.
-\begin{itemize}
-\item[(i)] If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}).
-Hence $f(\lambda)>f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)>\te(\hat \beta_{2}^{\MTL},1)$.
-
-\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $f(\lambda)< f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
-
-\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
-%, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
-\end{itemize}
-This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
-\end{proof}
-\fi
 %\todo{add a transition example}

### 2020-09-25 arxiv/diff_cov.tex
fix links
wip

@@
 		\item[ii)] For any fixed vector $w\in\real^p$ with unit norm, the bias equation converges to the following asymptotic limit
-			\begin{align}\label{def Pibias}
+			\begin{align}\label{lem_cov_derv_eq}
 				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \lesssim p^{-c_{\varphi}},
@@
 Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
-For the rest of this section, we the main ideas in the proof of Theorem \ref{thm_main_RMT}.
+For the rest of this section, we present the main ideas in the proof of Theorem \ref{thm_main_RMT}.
 %We will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
@@
 %which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
-For the matrix $Y$ that we want to study, we can also write $Y = A A^{\top}$, where $A = [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top] \in \real^{p\times {n_1 + n_2}}$.
+For the matrix $Y$ that we want to study, we can also write $Y = A A^{\top}$, where
+	\[ A = (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top] \]
+is a $p$ by $n_1 + n_2$ matrix.
 %}\HZ{what does this trick mean? use less technical words},
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Consider the following $(p+n)\times (p+n)$ symmetric block matrix
+Consider the following symmetric and square matrix whose dimension is $p + n_1 + n_2$.
 %which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
@@
 \begin{definition}[Resolvents]
-We define the resolvent or Green's function of $H$ as
- $G(z) \define (H - z\id_{p + n_1 + n_2})^{-1}$, for any complex value $z\in \mathbb C$.  %\left[H -\left( {\begin{array}{*{20}c}
+The resolvent or Green's function of $H$ is given by
+	\begin{align*}
+    G(z) \define (H - z\id)^{-1}, \text{ for any complex value } z\in \mathbb C.  %\left[H -\left( {\begin{array}{*{20}c}
+	\end{align*}
 %   { z\id_{p}} & 0 & 0 \\
@@
 %\begin{definition}[Index sets]\label{def_index}
-Similarly, the resolvent of $Y$ is defined as $\cal G(z):=(Y - z\id_{p})^{-1}$, for any $z\in \mathbb C$.
+Likewise, the resolvent of $Y$ is given by $\cal G(z) \define (Y - z\id)^{-1}$, for any $z\in \mathbb C$.
 \end{definition}
-
+Let $m_1(z):= \frac{1}{n_1}\sum_{i = p+1}^{p + n_1} G_{i, i}(z)$ and $m_2(z):= \frac{1}{n_2}\sum_{i = p + n_1 + 1}^{p + n_1 + n_2} G_{i, i}(z)$.
 Using the Schur complement formula, we have that %\HZ{Has $G(z)$ been defined before?}
@@
 
-\noindent\textbf{Asymptotic limits of resolvents.}
-We now describe the asymptotic limit of $G(z)$ as $n\to \infty$.
-First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
+%\noindent\textbf{Asymptotic limits of resolvents.}
+We now describe the asymptotic limit of $G(z)$ as $p$ goes to infinity.
+First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
 %\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)},
@@
 The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
+
+\paragraph{Notations.}
+Define the index sets
+$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
+ We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
+ \be\label{labelZ}
+ Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
+
+Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
+\be\label{defm}
+\begin{split}
+m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
+ m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
+\end{split}
+\ee
+We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof.
+We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
+
+\subsection{Warmup: The Gaussian Case}
+Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
+%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
+by the rotational invariance of the multivariate Gaussian distribution we have
+\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
+where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
+ \begin{equation} \label{resolv Gauss1}
+   G(z)= \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{-1}.
+ \end{equation}
+
+\medskip
+\noindent{\bf Schur complements.}
+%Now we discuss about how to obtain the matrix limit in equation \eqref{defn_piw}.
+%\HZ{Divide into several parts like sec 7 to improve readability.}
+The core quantities of the derivation are the following resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
+\begin{definition}[Resolvent minors]\label{defn_Minor}
+ For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $a\in \mathcal I$, we define the minor $\cal A^{(a)}:=(\cal A_{a_1 a_2}:a_1, a_2 \in \mathcal I\setminus \{a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $a$-th row and column in $\cal A$.
+Note that we keep the names of indices when defining $\cal A^{(a)}$, i.e.
+$(\cal A^{(a)})_{a_1a_2}= \cal A_{a_1 a_2}$ for $a_1,a_2\ne a$.
+Correspondingly, we define the resolvent minor for $G$ in equation \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
+\begin{align*}
+G^{(\mathfrak c)}:&=\left[ \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{(a)}\right]^{-1} ,
+%= \left( {\begin{array}{*{20}c}
+%   { \mathcal G^{(\mathbb T)}} & \mathcal G^{(\mathbb T)} W^{(\mathbb T)}  \\
+%   {\left(W^{(\mathbb T)}\right)^\top\mathcal G^{(\mathbb T)}} & { \mathcal G_R^{(\mathbb T)} }  \\
+%\end{array}} \right)  ,
+\end{align*}
+and define the partial traces $m^{(a)}$, $m_0^{(a)}$, $m_1^{(a)}$ and $m_2^{(a)}$ by replacing $G$ with $G^{(a)}$ in equation \eqref{defm}.
+We adopt the convention that for the resolvent minor $G^{(a)}$ defined as above, $G^{(a)}_{a_1a_2} = 0$ if $a_1 =a$ or $a_2=a$.
+\end{definition}
+%Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
+One will see a crucial use of this fact in the heuristic proof below.
+ Using Schur complement formulas in equation (\ref{resolvent2}), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+%\HZ{This part needs more explanation - cannot understand.}
+\begin{align}
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} , \label{0self_Gii}
+\end{align}
+and for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\begin{align}
+\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij},
+\label{0self_Gmu1}
+\end{align}
+where we recall the notations in equation \eqref{labelZ}. To see why equation \eqref{0self_Gii} holds, we have that by Schur complement formula,
+\begin{align*}
+\frac{1}{G_{ii}}= -z - H_i G^{(i)}H_{i}^\top, \quad H_i = \left( \mathbf 0_{p-1}, (n^{-1/2}\lambda_i (Z^{(1)})^\top_{i\mu }:\mu \in \cal I_1),(n^{-1/2} (Z^{(2)})^\top_{i\nu }:\nu \in \cal I_2)\right),
+\end{align*}
+where $H_i$ is actually the $i$-th row of $H$ with the $(i,i)$-th entry removed.
+Expanding the above expression, we obtain equation \eqref{0self_Gii}.
+The two expressions in equation \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
+
+\medskip
+\noindent{\bf Concentration estimates.} Now for the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $Z^{(1)}_{\mu i}$ and $Z^{(2)}_{\nu i}$.
+Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with overwhelming probability,
+\begin{align*}
+\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
+\end{align*}
+where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$.
+Intuitively, since we have removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
+Hence we obtain from the above equation that
+\begin{align}\label{1self_Gii}
+ G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1 +  \frac{\rho_2}{\rho_1+\rho_2}m_2+\oo(1)\right)^{-1}.
+\end{align}
+Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
+with overwhelming probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
+
+\medskip
+\noindent\textbf{Deriving the self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
+\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
+\ee
+with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
+with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
+\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
+with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
+\be\label{approximate m1m2}
+\begin{split}
+& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
+& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
+\end{split}
+\ee
+with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
+A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}.
+Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
+\be\label{approx m12 add}
+(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
+\ee
+To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
+This will be given by Lemma \ref{lem_stabw}.
+
+\medskip
+\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
+with overwhelming probability.
+These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}.
+For the off-diagonal entries, they are close to zero due to concentration.
+For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
+$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
+Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
+The other off-diagonal entries can be bounded in the same way.
+The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
+
+\medskip
+\noindent{\bf Deriving the bias asymptotics.} Finally, we describe how to derive the bias asymptotics.
+We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
+More precisely, using equation \eqref{eigen2extra} we can obtain that
+\begin{align}
+&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
+&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
+\end{align}
+where we used equation \eqref{rewrite X as R} in the second step.
+Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
+\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
+If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
+Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
+\begin{align}
+& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+\end{align}
+where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
+Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
+This is the main reason why we need to take a general $z$ in the definition of resolvents.
+The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
+%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
+%For the variance asymptotic limit, we study the resolvent
+%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
+%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
+%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
+%
+%For the bias asymptotic limit, we show in \todo{where?} that
+%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
+%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
+
+The above arguments are the core of the main proof.
+To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
+These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
+For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-25 arxiv/proof_gaussian_case.tex
wip

--- 2020-09-24 arxiv/proof_gaussian_case.tex
@@
 %\input{proof_two_tasks}
-
-\subsection{Warmup: The Gaussian Case}
-Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
-%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
-by the rotational invariance of the multivariate Gaussian distribution we have
-\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
-where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
- \begin{equation} \label{resolv Gauss1}
-   G(z)= \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
-   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{-1}.
- \end{equation}
-
-\medskip
-\noindent{\bf Schur complements.}
-%Now we discuss about how to obtain the matrix limit in equation \eqref{defn_piw}.
-%\HZ{Divide into several parts like sec 7 to improve readability.}
-The core quantities of the derivation are the following resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
-\begin{definition}[Resolvent minors]\label{defn_Minor}
- For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $a\in \mathcal I$, we define the minor $\cal A^{(a)}:=(\cal A_{a_1 a_2}:a_1, a_2 \in \mathcal I\setminus \{a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $a$-th row and column in $\cal A$.
-Note that we keep the names of indices when defining $\cal A^{(a)}$, i.e.
-$(\cal A^{(a)})_{a_1a_2}= \cal A_{a_1 a_2}$ for $a_1,a_2\ne a$.
-Correspondingly, we define the resolvent minor for $G$ in equation \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
-\begin{align*}
-G^{(\mathfrak c)}:&=\left[ \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
-   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{(a)}\right]^{-1} ,
-%= \left( {\begin{array}{*{20}c}
-%   { \mathcal G^{(\mathbb T)}} & \mathcal G^{(\mathbb T)} W^{(\mathbb T)}  \\
-%   {\left(W^{(\mathbb T)}\right)^\top\mathcal G^{(\mathbb T)}} & { \mathcal G_R^{(\mathbb T)} }  \\
-%\end{array}} \right)  ,
-\end{align*}
-and define the partial traces $m^{(a)}$, $m_0^{(a)}$, $m_1^{(a)}$ and $m_2^{(a)}$ by replacing $G$ with $G^{(a)}$ in equation \eqref{defm}.
-We adopt the convention that for the resolvent minor $G^{(a)}$ defined as above, $G^{(a)}_{a_1a_2} = 0$ if $a_1 =a$ or $a_2=a$.
-\end{definition}
-%Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
-One will see a crucial use of this fact in the heuristic proof below.
- Using Schur complement formulas in equation (\ref{resolvent2}), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-%\HZ{This part needs more explanation - cannot understand.}
-\begin{align}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} , \label{0self_Gii}
-\end{align}
-and for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\begin{align}
-\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij},
-\label{0self_Gmu1}
-\end{align}
-where we recall the notations in equation \eqref{labelZ}. To see why equation \eqref{0self_Gii} holds, we have that by Schur complement formula,
-\begin{align*}
-\frac{1}{G_{ii}}= -z - H_i G^{(i)}H_{i}^\top, \quad H_i = \left( \mathbf 0_{p-1}, (n^{-1/2}\lambda_i (Z^{(1)})^\top_{i\mu }:\mu \in \cal I_1),(n^{-1/2} (Z^{(2)})^\top_{i\nu }:\nu \in \cal I_2)\right),
-\end{align*}
-where $H_i$ is actually the $i$-th row of $H$ with the $(i,i)$-th entry removed.
-Expanding the above expression, we obtain equation \eqref{0self_Gii}.
-The two expressions in equation \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
-
-\medskip
-\noindent{\bf Concentration estimates.} Now for the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $Z^{(1)}_{\mu i}$ and $Z^{(2)}_{\nu i}$.
-Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with overwhelming probability,
-\begin{align*}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
-\end{align*}
-where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$.
-Intuitively, since we have removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
-Hence we obtain from the above equation that
-\begin{align}\label{1self_Gii}
- G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1 +  \frac{\rho_2}{\rho_1+\rho_2}m_2+\oo(1)\right)^{-1}.
-\end{align}
-Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
-with overwhelming probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
-
-\medskip
-\noindent\textbf{Deriving the self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
-\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
-\ee
-with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
-with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
-\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
-with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
-\be\label{approximate m1m2}
-\begin{split}
-& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
-& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
-\end{split}
-\ee
-with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
-A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}.
-Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
-\be\label{approx m12 add}
-(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
-\ee
-To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
-This will be given by Lemma \ref{lem_stabw}.
-
-\medskip
-\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
-with overwhelming probability.
-These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}.
-For the off-diagonal entries, they are close to zero due to concentration.
-For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
-$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
-Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
-The other off-diagonal entries can be bounded in the same way.
-The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
-
-\medskip
-\noindent{\bf Deriving the bias asymptotics.} Finally, we describe how to derive the bias asymptotics.
-We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
-More precisely, using equation \eqref{eigen2extra} we can obtain that
-\begin{align}
-&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
-&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
-\end{align}
-where we used equation \eqref{rewrite X as R} in the second step.
-Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
-\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
-If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
-Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
-\begin{align}
-& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
-\end{align}
-where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
-Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
-This is the main reason why we need to take a general $z$ in the definition of resolvents.
-The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
-%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
-%For the variance asymptotic limit, we study the resolvent
-%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
-%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
-%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
-%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
-%
-%For the bias asymptotic limit, we show in \todo{where?} that
-%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
-%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
-%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
-
-The above arguments are the core of the main proof.
-To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
-These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
-For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-25 arxiv/tools.tex
wip

@@
 \end{fact}
+
+The following simple resolvent identities are important tools for our proof. Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}.
+\begin{lemma}\label{lemm_resolvent}
+We have the following resolvent identities.
+\begin{itemize}
+\item[(i)]
+For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
+\begin{equation}
+\frac{1}{G_{ii}} =  - z - \left( {AG^{\left( i \right)} A^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {A^\top  G^{\left( \mu  \right)} A} \right)_{\mu \mu }.\label{resolvent2}
+\end{equation}
+
+ \item[(ii)]
+ For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
+\begin{equation}
+G_{ia}   = -G_{ii}  \left( AG^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( A^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
+\end{equation}
+%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
+%\begin{equation}\label{resolvent6}
+%\begin{split}
+% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}.
+%\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) .
+%, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
+%\end{split}
+%\end{equation}
+
+ \item[(iii)]
+ For $a \in \mathcal I$ and $a_1,a_2 \in \mathcal I \setminus \{a\}$, we have
+\begin{equation}
+G_{a_1a_2}^{\left( a \right)}  = G_{a_1a_2}  - \frac{G_{a_1a} G_{aa_2}}{G_{aa}} .
+%, \quad  \frac{1}{{G_{{b}{b}} }} = \frac{1}{{G_{{b}{b}}^{({a})} }} - \frac{{G_{{b}{a}} G_{{a}{b}} }}{{G_{{b}{b}} G_{{b}{b}}^{({a})} G_{{a}{a}} }}.
+\label{resolvent8}
+\end{equation}
+%and
+%\begin{equation}
+%\frac{1}{{G_{ss} }} = \frac{1}{{G_{ss}^{(r)} }} - \frac{{G_{sr} G_{rs} }}{{G_{ss} G_{ss}^{(r)} G_{rr} }}.
+%\label{resolvent9}
+%\end{equation}
+% \item[(iv)]
+%All of the above identities hold for $G^{(\mathbb T)}$ instead of $G$ for $\mathbb T \subset \mathcal I$, and in the case where $A$ and $B$ are not diagonal.
+\end{itemize}
+\end{lemma}
+\begin{proof}
+All these identities can be proved directly using Schur's complement formula. The reader can also refer to, for example, \cite[Lemma 4.4]{Anisotropic}.
+\end{proof}
 

### 2020-09-25 arxiv/diff_cov.tex
wip

@@
 %\begin{definition}[Index sets]\label{def_index}
-Likewise, the resolvent of $Y$ is given by $\cal G(z) \define (Y - z\id)^{-1}$, for any $z\in \mathbb C$.
+%Likewise, the resolvent of $Y$ is given by $\cal G(z) \define (Y - z\id)^{-1}$, for any $z\in \mathbb C$.
 \end{definition}
-Let $m_1(z):= \frac{1}{n_1}\sum_{i = p+1}^{p + n_1} G_{i, i}(z)$ and $m_2(z):= \frac{1}{n_2}\sum_{i = p + n_1 + 1}^{p + n_1 + n_2} G_{i, i}(z)$.
-Using the Schur complement formula, we have that %\HZ{Has $G(z)$ been defined before?}
- \begin{equation} \label{green2}
+%Let $m_1(z):= \frac{1}{n_1}\sum_{i = p+1}^{p + n_1} G_{i, i}(z)$ and $m_2(z):= \frac{1}{n_2}\sum_{i = p + n_1 + 1}^{p + n_1 + n_2} G_{i, i}(z)$.
+Using the Schur complement formula (cf. Section \ref{app_tool}), we have that %\HZ{Has $G(z)$ been defined before?}
+	\begin{equation*} %\label{green2}
 	  G(z) =  \left( {\begin{array}{*{20}c}
    { \cal G (z)} & \cal G(z)A  \\
-   A^\top \cal G(z) & z (A^\top A - z)^{-1}
-\end{array}} \right)^{-1}, %\quad \cal G_R:=(W^\top W - z)^{-1} ,
- \end{equation}
-This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
+   A^\top \cal G(z) & z (A^\top A - z\id)^{-1}
+		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
+  \end{equation*}
+%This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
 On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
-
 %\noindent\textbf{Asymptotic limits of resolvents.}
-We now describe the asymptotic limit of $G(z)$ as $p$ goes to infinity.
-First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
-%\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)},
-the unique solution to the following system of equations
+In Theorem \ref{LEM_SMALL}, we show that when $p$ goes to infinity, $G(z)$ converges to a matrix limit as follows:
+\be \label{defn_piw}
+	\Gi(z) \define \begin{pmatrix} (-z\id_p+a_{1}(z)\Lambda^2  +  a_{2}(z)\id_p)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix},\ee
+%In particular, the matrix limit of $\cal G(z)$ is given by
+%\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1},\ee
+where $(a_1(z), a_2(z))$ is the unique solution to the following system of equations
 \begin{equation}\label{selfomega_a}
@@
 \ee
+The existence and uniqueness of the solution to the above equation system are shown in Lemma \ref{lem_mbehaviorw}.
+%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
 %satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
-The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}.
+%The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}.
 %Here, for simplicity of notations, we introduced the following ratios
@@
 %\ee
-We define the matrix limit of $G(z)$ as
-\be \label{defn_piw}
-\Gi(z) := \begin{pmatrix} (-z\id_p+a_{1}(z)\Lambda^2  +  a_{2}(z)\id_p)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
-In particular, the matrix limit of $\cal G(z)$ is given by
-\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}.\ee
-
-\medskip
+We illustate that the above results directly imply the variance asymptotic in equation \eqref{lem_cov_shift_eq}.
 \noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as

### 2020-09-25 arxiv/implications.tex

@@
 For such settings, we have also observed that adding more labeled data from one task does not always help.
+Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
 %On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
-In the isotropic model, we consider what happens if we vary the source task sample size.
-More precisely, for fixed model distance $pd^2$, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases and converges to $pd^2$ as the sample ratio $\rho_1/\rho_2$ increases.
-On the other hand, the variance reduction $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$ also increases and converges to $\frac{\sigma^2}{\rho_2-1}$ as the sample ratio $\rho_1/\rho_2$ increases.
-\todo{add more details}
+
+More precisely, in the isotropic model, we consider what happens if we vary the source task sample size.
+For fixed model distance $pd^2$, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases and converges to $pd^2$ as the sample ratio $\rho_1/\rho_2$ increases, and the variance reduction $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$ also increases and converges to $\frac{\sigma^2}{\rho_2-1}$ as $\rho_1/\rho_2$ increases.
+The tradeoff between these two terms depends on $\rho_1$ in a nonlinear way that is more complicated than the one in the case of varying model distance.
+But from our results, one can check the following phenomena.
+If $\frac{\sigma^2}{\rho_2-1} > pd^2$, then the transfer is always positive.
+On the other hand, if $\frac{\sigma^2}{\rho_2-1} < pd^2$, then there is a transition from the positive transfer to negative transfer as $\rho_1/\rho_2$ increases.
 %Therefore, while the variance of MTL still reduces compared to STL, 
 %If the bias increases more than the amount of variance reduced, we will observe negative transfer.
-Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
 Figure \ref{fig_size} provides a simulation result for such a setting (described in Appendix \ref{app_synthetic}).
-We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer. 
 There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
@@
 
-\noindent\textit{Example.}
-	We measure covariate shift by $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$ similar to Theorem \ref{thm_main_informal}.
-	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$ and $\Psi(\beta_1, \beta_2) = 0$.
+%\noindent\textit{Example.}
+
+\begin{example}
+	We measure covariate shift by the transfer matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$. %similar to Theorem \ref{thm_main_informal}.
+	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$.
 	We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
@@
 	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
+	\end{example}
 
@@
 {\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.},
+		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.}.
 \end{align*}}

### 2020-09-25 arxiv/diff_cov.tex
wip

--- 2020-09-25 arxiv/diff_cov.tex
@@
 			\begin{align}
-				a_1 + a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad a_1 + \frac1{\rho_1 + \rho_2}\cdot \bigbrace{\frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\label{eq_a12extra}
+				a_1 + a_2 = 1- \frac{p}{n_1 + n_2},\quad a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
 			\end{align}
 		\item[ii)] For any fixed vector $w\in\real^p$ with unit norm, the bias equation converges to the following asymptotic limit
-			\begin{align}\label{def Pibias}
+			\begin{align}\label{lem_cov_derv_eq}
 				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \lesssim p^{-c_{\varphi}},
@@
 To study this quantity, we use the Stieltjes transform or the resolvent method in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-%We give some preliminaries about this method before discussing the proof strategy.
 For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
-$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z},\quad z\in \C\setminus [0,\infty).$$
-Conversely, given a Stieltjes transform $m_{\mu}(z)$, we can recover the measure $\mu$ through the inverse formula \HZ{add a ref to the equation below}
-$$ \frac{\dd \mu(x)}{\dd x} = \frac{1}{\pi}\lim_{\eta \downarrow 0}\im m_{\mu}(x+\ii \eta).$$
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \text{ for any complex number } z\in \C\setminus [0,\infty).$$
+%Conversely, given a Stieltjes transform $m_{\mu}(z)$, we can recover the measure $\mu$ through the inverse formula \HZ{add a ref to the equation below}
+%$$ \frac{\dd \mu(x)}{\dd x} = \frac{1}{\pi}\lim_{\eta \downarrow 0}\im m_{\mu}(x+\ii \eta).$$
 %where $\rho(x)$ is the density for $\mu$, i.e. $\dd \mu(x)=\rho(x)\dd x$.
-Hence the Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
-To study the matrix inverse $\hat{\Sigma}^{-1}$, we consider its empirical spectral distribution.
-More precisely, since
+Hence the Stieltjes transform method reduces the study of a probability measure to the study of a complex function.
+To study the matrix inverse $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
+More precisely, it suffices to study the spectra of another matrix as follows
 \begin{align}\label{eigen2extra}
 	\hat{\Sigma}^{-1}= \Sigma_2^{-1/2}V \frac{Y^{-1}}{n_1 + n_2} V^\top\Sigma_2^{-1/2}.
-\text{ where } Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V),
+\text{ where } Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
 \end{align}
-let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$.
-The scaling $(n_1+n_2)^{-1}$ ensures such that the support of $\mu$ is bounded.
-The Stieltjes transform of the empirical spectral distribution $\mu$ is as follows
- \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[ (Y_p-z\id_p)^{-1}\right], \]
-and when $p$ goes to infinity, $m_{\mu}(z)$ converges to a fixed-point governed by a set of self-consistent equations.
-These self-consistent equations give the asymptotic limit of the trace of $\hat{\Sigma}^{-1}$.
-
-The above approach applies when $\Sigma^{(2)}$ is isotropic in Theorem \ref{thm_main_RMT}.
-For general covariances, we want to study the limit of $\tr\left[ (Y - z\id)^{-1}V^{\top}{\Sigma^{(2)}}^{-1}V \right]$ as shown in equation \eqref{eigen2extra}.
-Hence, we study the resolvent matrix or Green's function $(Y-z\id)^{-1}$.
-Compared to the Stieltjes transform, the resolvent also applies to random matrices.
-The convergence of resolvent is formally shown using the so-called ``local laws'' (cf.
-\cite{isotropic,erdos2017dynamical,Anisotropic}) or ``deterministic equivalents'' (cf.
+It is not hard to see that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{Y^{-1}} / (n_1 + n_2)$.
+Let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$.
+%The scaling $(n_1+n_2)^{-1}$ ensures such that the support of $\mu$ is bounded.
+The Stieltjes transform of $\mu$ is as follows
+ \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(Y-z\id)^{-1}\right]. \]
+In the above equation, $(Y - z\id)^{-1}$ is known as the resolvent matrix or Green's function of $Y$.
+%When $p$ goes to infinity, it is well-known that $m_{\mu}(z)$ converges to a fixed distribution governed by a set of self-consistent equations.
+%These self-consistent equations give the asymptotic limit of the trace of $\hat{\Sigma}^{-1}$.
+%The above approach applies when $\Sigma^{(2)}$ is isotropic in Theorem \ref{thm_main_RMT}.
+%Since our goal is to show the limit of $\tr\left[ (Y - z\id)^{-1}V^{\top}{\Sigma^{(2)}}^{-1}V \right]$ as shown in equation \eqref{eigen2extra}, we study the  $(Y-z\id)^{-1}$.
+%Compared to the Stieltjes transform, the resolvent also applies to random matrices.
+We shall prove the convergence of the resolvent matrix of $Y$ using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
+%Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.
 \cite{Hachem2007deterministic,DS18}).
-More precisely, given a deterministic $p\times p$ matrix $R(z)$, we say that $R(Z)$ and $(Y-z\id)^{-1}$ are equivalent if for any sequence of deterministic matrices $B$ of uniformly bounded operator norms,
+More precisely, given a deterministic $p\times p$ matrix $R(z)$, we say that $R(z)$ and $(Y-z\id)^{-1}$ are equivalent if for any sequence of deterministic matrices $B$ with uniformly bounded operator norms,
 $$\bigtr{((Y-z\id)^{-1}-R(z))B}\to 0.$$
-If the above equation holds for all $p$, then we say that $(Y-z\id)^{-1}$ has a matrix limit $R(z)$.
-For our result, we shall prove the convergence of the resolvent $(Y-z\id)^{-1}$ using ``local laws'' with a sharp convergence rate.
-
+When the above equation holds for large enough $p$, we say that $(Y-z\id)^{-1}$ converges to the matrix limit $R(z)$.
 %For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
@@
 %which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
-For the matrix $Y$ that we want to study, we can also write $Y = A A^{\top}$, where $A = [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top] \in \real^{p\times {n_1 + n_2}}$.
+We observe that the matrix $Y$ can also be written as $A A^{\top}$ for a $p$ by $n_1 + n_2$ matrix defined as follows.
+	\[ A = (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
 %}\HZ{what does this trick mean? use less technical words},
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Consider the following $(p+n)\times (p+n)$ symmetric block matrix
+Consider the following symmetric and square matrix whose dimension is $p + n_1 + n_2$.
 %which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
@@
  \begin{equation}\label{linearize_block}
-    H \define (n_1 + n_2)^{-1/2}\left( {\begin{array}{*{20}c}
-   { 0 } & \Lambda U^{\top}(Z^{(1)})^\top & V^\top (Z^{(2)})^\top  \\
-   {Z^{(1)} U\Lambda  } & {0} & 0 \\
-   {Z^{(2)}V} & 0 & 0
+    H \define \left( {\begin{array}{*{20}c}
+   0 & A  \\
+   A^{\top} & 0
+%   {Z^{(2)}V} & 0 & 0
    \end{array}} \right).
  \end{equation}
-The resolvent of $H$ is defined as follows.
-\begin{definition}[Resolvents]
-We define the resolvent or Green's function of $H$ as
- $G(z) \define (H - z\id_{p + n_1 + n_2})^{-1}$, for any complex value $z\in \mathbb C$.  %\left[H -\left( {\begin{array}{*{20}c}
+%The resolvent of $H$ is defined as follows.
+%\begin{definition}[Resolvents]
+The resolvent of $H$ is given by $G(z) \define (H - z\id)^{-1}$, for any complex value $z\in \mathbb C$.  %\left[H -\left( {\begin{array}{*{20}c}
 %   { z\id_{p}} & 0 & 0 \\
@@
 %\begin{definition}[Index sets]\label{def_index}
-Similarly, the resolvent of $Y$ is defined as $\cal G(z):=(Y - z\id_{p})^{-1}$, for any $z\in \mathbb C$.
-\end{definition}
+%Likewise, the resolvent of $Y$ is given by $\cal G(z) \define (Y - z\id)^{-1}$, for any $z\in \mathbb C$.
+%Let $m_1(z):= \frac{1}{n_1}\sum_{i = p+1}^{p + n_1} G_{i, i}(z)$ and $m_2(z):= \frac{1}{n_2}\sum_{i = p + n_1 + 1}^{p + n_1 + n_2} G_{i, i}(z)$.
+Since $H$ has a specific block structure, it is not hard to verify that %\HZ{Has $G(z)$ been defined before?}
+	\begin{equation*} %\label{green2}
+	  G(z) =  \left( {\begin{array}{*{20}c}
+			(Y - z\id)^{-1} & (Y - z\id)^{-1} A  \\
+      A^\top (Y - z\id)^{-1} & (A^\top A - z\id)^{-1}
+		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
+  \end{equation*}
+%This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
+On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
+%\noindent\textbf{Asymptotic limits of resolvents.}
 
-Using the Schur complement formula, we have that %\HZ{Has $G(z)$ been defined before?}
- \begin{equation} \label{green2}
-  G(z) =  \left( {\begin{array}{*{20}c}
-   { \cal G (z)} & \cal G(z)A  \\
-   A^\top \cal G(z) & z (A^\top A - z)^{-1}
-\end{array}} \right)^{-1}, %\quad \cal G_R:=(W^\top W - z)^{-1} ,
- \end{equation}
-This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
-On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
-
-\noindent\textbf{Asymptotic limits of resolvents.}
-We now describe the asymptotic limit of $G(z)$ as $n\to \infty$.
-First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
-%\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)},
-the unique solution to the following system of equations
-\begin{equation}\label{selfomega_a}
-\begin{split}
-& \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{split}
-\ee
+\paragraph{Matrix limit.}
+In Theorem \ref{LEM_SMALL}, we show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to a matrix limit as follows:
+\be \label{defn_piw}
+	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix},\ee
+%In particular, the matrix limit of $\cal G(z)$ is given by
+%\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1},\ee
+where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following system of equations
+\begin{align}
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \nonumber\\
+	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}. \label{selfomega_a}
+% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
+\end{align}
+The existence and uniqueness of the solution to the above equation system are shown in Lemma \ref{lem_mbehaviorw}.
+%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
 %satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
-The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}.
+%The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}.
 %Here, for simplicity of notations, we introduced the following ratios
@@
 %\ee
-We define the matrix limit of $G(z)$ as
-\be \label{defn_piw}
-\Gi(z) := \begin{pmatrix} (-z\id_p+a_{1}(z)\Lambda^2  +  a_{2}(z)\id_p)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
-In particular, the matrix limit of $\cal G(z)$ is given by
-\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1}.\ee
-
-\medskip
-\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
-\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
-When $z=0$, it is easy to check that equation \eqref{selfomega_a} can be reduced to equation \eqref{eq_a12extra}, which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
+Given this result, we show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance asymptotic shown in equation \eqref{lem_cov_shift_eq}.
+First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
+Second, since $Y^{-1}$ is the upper-left block matrix of $G(0)$, we have that $Y^{-1}$ converges to $(a_1\Lambda^2 + a_2)^{-1}$.
+Using equation \eqref{eigen2extra}, we have that when $p$ goes to infinity, the trace of $\Sigma^{(2)} \hat{\Sigma}$ converges to \[ \bigtr{(a_1 \Lambda^2 + a_2\id)^{-1} V^{\top} {\Sigma^{(2)}}^{-1} V} = \bigtr{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}.
+\]
+%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
+%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
+%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
 Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
 Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
+%\begin{align}
+%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
+%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
+%\end{align}
+where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$.
+The concentration error of the above limit is shown in Appendix \ref{appendix RMT}.%The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
+
+For the bias asymptotic in equation \eqref{lem_cov_derv_eq}, We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
+More precisely, using equation \eqref{eigen2extra} we can obtain that
 \begin{align}
-&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
-&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
+&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
+&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
 \end{align}
-where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$ by equation \eqref{eigen2}.
-This concludes equation \eqref{lem_cov_shift_eq} up to a small error.
-The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
+where we used equation \eqref{rewrite X as R} in the second step.
+Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
+\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
+If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
+Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
+\begin{align}
+& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+\end{align}
+where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
+Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
+This is the main reason why we need to take a general $z$ in the definition of resolvents.
+The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
+%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
+%For the variance asymptotic limit, we study the resolvent
+%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
+%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
+%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
+%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
+%
+%For the bias asymptotic limit, we show in \todo{where?} that
+%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
+%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
+%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
+%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
+
+The above arguments are the core of the main proof.
+To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
+These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
+For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-25 arxiv/proof_gaussian_case.tex
wip

--- 2020-09-25 arxiv/proof_gaussian_case.tex
@@
 %\input{proof_two_tasks}
+The main goal of this section is to prove Theorem \ref{thm_main_RMT}.
+%Recall that $n:=n_1+n_2$, which is the total number of data in the two tasks.
+%Before giving the main proof, we first introduce some notations and tools.
+%Following the notations in \cite{EKYY,EKYY1}, we will use the following definition to characterize events of overwhelming probability.
+%
+%\begin{definition}[overwhelming probability event] \label{high_prob}
+%Define
+%\begin{equation}\label{def_phi}
+%\varphi:=(\log N)^{\log \log N}.
+%\end{equation}
+%We say that an $N$-dependent event $\Omega$ holds with {\it{$\xi$-overwhelming probability}} if there exist constant $c,C>0$ independent of $N$, such that
+%\begin{equation}
+%\mathbb{P}(\Omega) \geq 1-N^{C} \exp(- c\varphi^{\xi}),  \label{D25}
+%\end{equation}
+%for all sufficiently large $N$.
+For simplicity, for the case $\xi=1$, we just say {\it{overwhelming probability}}.
+Note that if (\ref{D25}) holds, then $\mathbb P(\Omega) \ge 1 - \exp(-c'\varphi^{\xi})$ for any constant $0\le c' <c$.
+%\end{definition}
+%\begin{remark}
+%For any $c, C>0$, there exists a $0< c^{\prime}<c$, such that $N^{C} \exp(-c \varphi^{\xi}) \leq \exp(-c^{\prime} \varphi^{\xi})$. Hence, if
+%\begin{equation}
+%\mathbb{P}(\Omega) \geq 1- \exp(-c \varphi^{\xi})
+%\end{equation}
+%$\Omega$ is also a $\xi$-overwhelming probability event.
+%\end{remark}
+For simplicity of notations, we will use the following notion of stochastic domination, which was first introduced in \cite{Average_fluc} and subsequently used in many works on random matrix theory.
+It greatly simplifies the presentation of the results and their proofs by systematizing statements of the form ``$\xi$ is bounded by $\zeta$ with overwhelming probability up to a small power of $n$".
+
+\begin{definition}[Stochastic domination]\label{stoch_domination}
+%\begin{itemize}
+%\item[(i)]
+Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
+%\begin{itemize} \item[(i)]
+We say $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any (small) constant $\e>0$ and (large) constant $D>0$,
+\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}\]
+for large enough $n\ge n_0(\e, D)$.
+Moreover, if $\xi$ and $\zeta$ depend on a parameter $u$, then we say $\xi$ is stochastically dominated by $\zeta$ uniformly in $u\in \cal U$,  if for any constants $\e,D>0$,
+\[\sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}\]
+for large enough $n\ge n_0(\e, D)$.
+%\item[(ii)]
+%\end{itemize}
+%(i) Let
+%\[\xi=\left(\xi^{(n)}(u):n\in\bbN, u\in U^{(n)}\right),\hskip 10pt \zeta=\left(\zeta^{(n)}(u):n\in\bbN, u\in U^{(n)}\right)\]
+%be two families of nonnegative random variables, where $U^{(n)}$ is a possibly $n$-dependent parameter set.
+We say $\xi$ is stochastically dominated by $\zeta$, uniformly in $u$, if for any fixed (small) $\epsilon>0$ and (large) $D>0$,
+%\[\sup_{u\in U^{(n)}}\bbP\left[\xi^{(n)}(u)>n^\epsilon\zeta^{(n)}(u)\right]\le n^{-D}\]
+%for large enough $n\ge n_0(\epsilon, D)$, and we shall use the notation $\xi\prec\zeta$.
+%%Throughout this paper, the stochastic domination will always be uniform in all parameters that are not explicitly fixed (such as matrix indices, and $z$ that takes values in some compact set).
+%%Note that $N_0(\epsilon, D)$ may depend on quantities that are explicitly constant, such as $\tau$ in Assumption \ref{assm_big1} and equation \eqref{assm_gap}.
+%If for some complex family $\xi$ we have $|\xi|\prec\zeta$, then we will also write $\xi \prec \zeta$ or $\xi=\OO_\prec(\zeta)$.
+%\item[(ii)]
+%(ii) We extend the definition of $\OO_\prec(\cdot)$ to matrices in the weak operator sense as follows.
+Let $A$ be a family of random matrices and $\zeta$ be a family of nonnegative random variables.
+Then $A=O_\prec(\zeta)$ means that $\left|\left\langle\mathbf v, A\mathbf w\right\rangle\right|\prec\zeta \| \mathbf v\|_2 \|\mathbf w\|_2 $ uniformly in any deterministic vectors $\mathbf v$ and $\mathbf w$.
+Here and throughout the following, whenever we say ``uniformly in any deterministic vectors", we mean that ``uniformly in any deterministic vectors belonging to a set of cardinality $N^{\OO(1)}$".
+%\item[(iv)]
+%\end{itemize}
+\end{definition}
+\begin{remark}
+Note that since we allow an $n^\e$ factor in the definition of stochastic domination, we have the seemingly strange inequality $(\log n)^C\prec 1$ for any constant $C>0$.
+\end{remark}
+
+\begin{example}\label{example stoc}
+Given a random variable $\xi$, if its moments exist up to any order, then we have $|\xi|\prec 1$. In fact, for any constants $\e, D>0$, by Markov's inequality we have
+$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D},$$
+if we choose $k$ large enough such that $k\e>D$. As a special case, we have $|\xi|\prec 1$ for a Gaussian random variable $\xi$ with unit variance.
+\end{example}
+
+%\HZ{Why is this below part of the def. of stochastic domination?}
+In the following proof, we say an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
+Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
+
+In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below.
+%\ref{sec_prelim}.
+ Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.
+
+%We summarize our basic assumptions here for future reference.
+%Note that this assumption is in accordance with the assumptions of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, except that we rescale the entries of $Z^{(1)}$ and $Z^{(2)}$ by $n^{-1/2}$.
+%and allow $\rho_1$ to be smaller than 1.
+\begin{assumption}\label{assm_big1}
+As in Section \todo{add reference}, we consider random matrices $X^{(1)}=Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}=Z^{(2)}\Sigma_2^{1/2}$, where $Z^{(1)}$ and $Z^{(2)}$ are independent $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
+entries of zero mean and unit variance.
+Recall that $\rho_1= n_1/p$ and $\rho_2=n_2/p$.
+We assume that for a small constant $0<\tau<1$,
+%\HZ{We have defined $\rho_1,\rho_2$ already in sec 2. Consider using ``Recall that $\rho_1 =, \rho_2 =$.''}
+\be\label{assm2}
+0\le \rho_1 \le \tau^{-1}, \quad 1+\tau \le \rho_{2} \le \tau^{-1}.
+\ee
+Recall that the singular value decomposition of $M = \Sig_1^{1/2} \Sig_2^{-1/2}$ is $U \Lambda V^{\top}$. We assume that
+\begin{equation}\label{assm32}
+\tau \le \lambda_p \le \lambda_1 \le \tau^{-1} .%, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
+\end{equation}
+Finally, recalling the notations in equation \eqref{labelZ}, we assume that $Z^{(1)}$ and $Z^{(2)}$ satisfy
+\begin{equation}
+n^{-1/2}\max_{i\in \cal I_0,\mu \in \cal I_1}\vert Z^{(1)}_{\mu i}\vert \prec q,\quad n^{-1/2}\max_{i\in \cal I_0,\nu \in \cal I_2}\vert Z^{(2)}_{\nu i}\vert \prec q, \label{eq_support}
+\end{equation}
+for some deterministic parameter $q$ satisfying $ n^{-{1}/{2}} \leq q \leq n^{- \tau} $ for a small constant $\tau>0$.
+%Here we recall the notations in \eqref{labelZ}.
+ %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
+\end{assumption}
+%\HZ{This is restating what's stated above again.
+Remove redundant statements (unless there's something critical missing in Sec 2).} [\cor FY: The setting in sec 1 is too vague for the purpose of this section in the sense that it is hard to find the exact properties we need.
+In this section, I want to state rigorous statements with a reference to an exact assumption.
+Moreover, the above assumption contains more.\nc]
+
+\begin{remark}
+The lower bound $\rho_2\ge 1+\tau$ in equation \eqref{assm2} is to ensure that the sample covariance matrix $(X^{(2)})^\top X^{(2)}$ is non-singular with overwhelming probability.
+Moreover, we have allowed that $\rho_1=0$, because we want to state a general result that also covers the special case with no source task.
+\end{remark}
+
+\begin{remark}\label{rem_athmoment}
+Whenever the estimates in equation \eqref{eq_support} hold, we say $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ satisfy the {\it{bounded support condition}} with $q$, or $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ have support $q$.
+%\begin{definition}\label{defn_support}
+%We say a (rescaled) random matrix $\cal M$ satisfies the {\it{bounded support condition}} with $q$, if
+%\begin{equation}
+%\max_{i,j}\vert \cal M_{ij}\vert \prec q. \label{eq_support}
+%\end{equation}
+%%Here $q\equiv q(n)$ is a deterministic parameter and usually satisfies $ n^{-{1}/{2}} \leq q \leq n^{- \phi} $ for some (small) constant $\phi>0$.
+%Whenever (\ref{eq_support}) holds, we say that $M$ has support $q$.
+%%Moreover, if the entries of $X$ satisfy (\ref{size_condition}), then $X$ trivially satisfies the bounded support condition with $q=N^{-\phi}$.
+%\end{definition}
+%\begin{example}
+%\todo{Talk about the Gaussian case and Bernoulli case.}
+By Example \ref{example stoc}, if the entries of $Z^{(1)}$ have finite moments up to any order, %as in equation \eqref{assmAhigh},
+then $n^{-1/2}Z^{(1)}$ has bounded support $n^{-1/2}$.
+More generally, if the entries of $Z^{(1)}$ have finite $\varphi$-th moment as in \eqref{assmAhigh}, then using Markov's inequality and a simple union bound we get that
+\be\label{Ptrunc}
+\P\left(n^{-1/2}\max_{i,\mu}|(Z^{(1)})_{\mu i}|\ge (\log n) n^{-\frac{\varphi-4}{2\varphi}}\right)=\OO((\log n)^{-\varphi}).\ee
+In other words, $n^{-1/2}Z^{(1)}$ has bounded support $q=n^{-\frac{\varphi-4}{2\varphi}}$ on a event with probability $1-\oo(1)$.
+This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}.
+%This fact will be used in the proof of Corollary \ref{main_cor} below.
+The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
+%is essentially introduced to deal with the moment conditions; see Corollary \ref{main_cor} below for more details.
+%\end{example}
+\end{remark}
 
@@
 The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
-
-\medskip
-\noindent{\bf Deriving the bias asymptotics.} Finally, we describe how to derive the bias asymptotics.
-We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
-More precisely, using equation \eqref{eigen2extra} we can obtain that
-\begin{align}
-&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
-&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
-\end{align}
-where we used equation \eqref{rewrite X as R} in the second step.
-Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
-\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
-If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
-Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
-\begin{align}
-& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
-\end{align}
-where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
-Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
-This is the main reason why we need to take a general $z$ in the definition of resolvents.
-The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
-%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
-%For the variance asymptotic limit, we study the resolvent
-%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
-%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
-%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
-%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
-%
-%For the bias asymptotic limit, we show in \todo{where?} that
-%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
-%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
-%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
-
-The above arguments are the core of the main proof.
-To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
-These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
-For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-25 arxiv/diff_cov.tex
wip

@@
 To study the matrix inverse $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
-More precisely, it suffices to study the spectra of another matrix as follows
+More precisely, it suffices to study another matrix
 \begin{align}\label{eigen2extra}
-	\hat{\Sigma}^{-1}= \Sigma_2^{-1/2}V \frac{Y^{-1}}{n_1 + n_2} V^\top\Sigma_2^{-1/2}.
-\text{ where } Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
+	Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V), \text{ since } (n_1 + n_2)\hat{\Sigma}^{-1}= \Sigma_2^{-1/2} VY^{-1}V^\top \Sigma_2^{-1/2}.
 \end{align}
-It is not hard to see that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{Y^{-1}} / (n_1 + n_2)$.
-Let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$.
+It is not hard to verify that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{Y^{-1}} / (n_1 + n_2)$.
+Let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$, where $\delta_{\lambda_i}$ is the indicator measure.
 %The scaling $(n_1+n_2)^{-1}$ ensures such that the support of $\mu$ is bounded.
@@
  \end{equation}
-%The resolvent of $H$ is defined as follows.
-%\begin{definition}[Resolvents]
-The resolvent of $H$ is given by $G(z) \define (H - z\id)^{-1}$, for any complex value $z\in \mathbb C$.  %\left[H -\left( {\begin{array}{*{20}c}
-%   { z\id_{p}} & 0 & 0 \\
-%   0 & { \id_{n_1}}  & 0\\
-%      0 & 0  & { \id_{n_2}}\\
-%\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C ,
-%It is easy to verify that the eigenvalues $\lambda_1(H)\ge \ldots \ge \lambda_{n+N}(H)$ of $H$ are related to the ones of $\mathcal Q_1$ through
-%\begin{equation}\label{Heigen}
-%\lambda_i(H)=-\lambda_{n+N-i+1}(H)=\sqrt{\lambda_i\left(\mathcal Q_2\right)}, \ \ 1\le i \le n\wedge N, \quad \text{and}\quad \lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.
-%\end{equation}
-%and
-%$$\lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.$$
-%where we used the notations $n\wedge N:=\min\{N,M\}$ and $n\vee N:=\max\{N,M\}$.
-%\begin{definition}[Index sets]\label{def_index}
-%Likewise, the resolvent of $Y$ is given by $\cal G(z) \define (Y - z\id)^{-1}$, for any $z\in \mathbb C$.
-%Let $m_1(z):= \frac{1}{n_1}\sum_{i = p+1}^{p + n_1} G_{i, i}(z)$ and $m_2(z):= \frac{1}{n_2}\sum_{i = p + n_1 + 1}^{p + n_1 + n_2} G_{i, i}(z)$.
-Since $H$ has a specific block structure, it is not hard to verify that %\HZ{Has $G(z)$ been defined before?}
+The resolvent of $H$ is given by $G(z) \define (H - z\id)^{-1}$, for any complex value $z\in \mathbb C$.
+Since $H$ has a specific block structure, it is not hard to verify that
 	\begin{equation*} %\label{green2}
@@
   \end{equation*}
-%This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block.
-On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information.
-%\noindent\textbf{Asymptotic limits of resolvents.}
 
@@
 %satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
-%The existence and uniqueness of the solution $(a_1(z), a_2(z))$ for $z$ around 0 will be proved in Section \ref{sec contract}.
-%Here, for simplicity of notations, we introduced the following ratios
 %\be\label{ratios}
@@
 Second, since $Y^{-1}$ is the upper-left block matrix of $G(0)$, we have that $Y^{-1}$ converges to $(a_1\Lambda^2 + a_2)^{-1}$.
-Using equation \eqref{eigen2extra}, we have that when $p$ goes to infinity, the trace of $\Sigma^{(2)} \hat{\Sigma}$ converges to \[ \bigtr{(a_1 \Lambda^2 + a_2\id)^{-1} V^{\top} {\Sigma^{(2)}}^{-1} V} = \bigtr{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}.
-\]
+Using equation \eqref{eigen2extra}, we have that when $p$ goes to infinity, the trace of $\Sigma^{(2)} \hat{\Sigma}$ converges to
+\[ \bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} = \bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} = \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}. \]
 %\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
@@
 %\end{align}
-where in the second step we used $V \Lambda^2 V^\top=M^\top M=\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2}$.
-The concentration error of the above limit is shown in Appendix \ref{appendix RMT}.%The rigorous proof of equation \eqref{lem_cov_shift_eq} will be given in Section \ref{sec pf RMTlemma}.
+where we note that the SVD of $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ is equal to $V^{\top}\Lambda^2 V$.
+For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
 
-For the bias asymptotic in equation \eqref{lem_cov_derv_eq}, We can write the left-hand side of equation \eqref{lem_cov_derv_eq} using the derivative of $\cal G$ with respect to $z$ at $z=0$.
-More precisely, using equation \eqref{eigen2extra} we can obtain that
-\begin{align}
-&n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)} }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&=n^2 w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\left(   \Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V\right)^{-2}V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w \nonumber\\
-&=  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\cal G'(0)V^\top\Sigma_2^{-1/2}\Sigma_1^{1/2}w,\label{calculate G'}
+For the bias asymptotic in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of the resolve of $Y$ with respect to $z$ at $z = 0$.
+More precisely, we have that
+	\[ (n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V Y^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}. \]
+Let $\cal G(z)$ denote the resolvent of $Y$.
+Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} = - \cal G^2(z)$.
+Given the matrix limit of $\cal G(z)$ from equation \eqref{defn_piw} above, we have that the matrix limit of $\frac{\dd{\cal G(0)}}{\dd z}$ is given by
+\begin{align}\label{cal G'0}
+	\frac{\dd \cal G(z)}{\dd z} = \frac{-\frac{\dd a_1(z)}{\dd z}\Lambda^2 - (\frac{\dd a_2(z)}{\dd z} - 1)\id}{(a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^2}.
 \end{align}
-where we used equation \eqref{rewrite X as R} in the second step.
-Since the matrix limit of $\cal G(z)$ is given by equation \eqref{matrix limit}, it is natural to guess that the matrix limit of $\cal G'(0)$ is given by
-\be\label{cal G'0}\cal G'(0) \approx \left.\frac{\dd}{\dd z}\right|_{z=0}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1} = \frac{\id_p- a_1'(0)\Lambda^2 - a_2'(0)\id_p}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.\ee
+As for the derivative of $a_1(z)$ and $a_2(z)$, we take the derivative on both sides of the equation system \eqref{selfomega_a} with respect to $z$.
+\begin{align*}
+	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
+	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_3)}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
+\end{align*}
 If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
@@
 & n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id_p)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
 \end{align}

### 2020-09-26 arxiv/diff_cov.tex
wip
revise
finish sec 5

@@
 			\begin{align}\label{lem_cov_derv_eq}
-				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \lesssim p^{-c_{\varphi}},
+				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \lesssim p^{-c_{\varphi}},
 			\end{align}
-				where $a_{3}$ and $a_4$ are the solutions of the following two equations with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+				where $a_{3}$ and $a_4$ are the solutions of the following two equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
 			\begin{align}\label{eq_a34extra}
-				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-				= b_0.
+				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
+				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_1 a_4 - a_2 a_3)}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
+%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+%				= b_0.
 			\end{align}
@@
 where we note that the SVD of $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ is equal to $V^{\top}\Lambda^2 V$.
-For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
+%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
 
@@
 More precisely, we have that
-	\[ (n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V Y^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}. \]
+\begin{align}\label{calculate G'}
+	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V Y^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
+\end{align}
 Let $\cal G(z)$ denote the resolvent of $Y$.
@@
 \end{align}
-As for the derivative of $a_1(z)$ and $a_2(z)$, we take the derivative on both sides of the equation system \eqref{selfomega_a} with respect to $z$.
-\begin{align*}
-	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
-	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_3)}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
-\end{align*}
-If we let $a_3:=-a_1'(0)$ and $a_4:=-a_2'(0)$, then taking implicit differentiation of equation \eqref{selfomega_a} we can check that $(a_3,a_4)$ satisfies equation \eqref{eq_a34extra}.
-Then inserting \eqref{cal G'0} into \eqref{calculate G'}, we obtain that
-\begin{align}
-& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
-\end{align}
-where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
-Note that in order to have the approximate identity for $\cal G'(0)$ in equation \eqref{cal G'0}, we not only need to know the asymptotics of $\cal G(0)$, but also need to know the asymptotics of $\cal G(z)$ for general $z$ around $z=0$.
-This is the main reason why we need to take a general $z$ in the definition of resolvents.
-The rigorous proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
+As for the derivative of $a_1(z)$ and $a_2(z)$, we solve them by taking the derivative on both sides of the equation system \eqref{selfomega_a} with respect to $z$.
+%\begin{align*}
+%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
+%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
+%\end{align*}
+Let $a_3$ be the derivative of $-a_1(z)$ and $a_4$ be the derivative of $-a_2(z)$, both evaluated at $z = 0$.
+%then taking implicit differentiation of equation \eqref{selfomega_a}
+We have that $a_3$ and $a_4$ satisfy the equation system \eqref{eq_a34extra}.
+Appling equation \eqref{cal G'0} into equation \eqref{calculate G'}, we obtain that the asymptotic limit of the bias equation.
+%\begin{align}
+%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+%\end{align}
+%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
+Note that for $\frac{\dd \cal G(z)}{\dd z}$ to be close to its limit at $z = 0$, we not only need the asymptotic limit of $\cal G(0)$, but also the asymptotic limit of $\cal G(z)$ for $z$ within a small neighborhood of $z = 0$.
+This is why consider the resolvent matrix of $Y$ as opposed to the Stieljes transform of its empirical spectral distribution.
+
+Next, we briefly describe how to derive the matrix limit $\Gi(z)$.
+First, we consider the case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
+By rotation invariance, we have that in the matrix $A$,  $Z^{(1)} U$ and $Z^{(2)} V$ are both multivariate Gaussian random matrices.
+We use Schur complement to obtain the entries of $G(z)$, and show that for the diagonal entries, they satisfy a set of self-consistent equations in the limit, which are stated above.
+On the other hand, for the off-diagonal entries, using standard concentration bounds, we show that they are approximately zero.
+Second, we extend our result for the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ satisfy the bounded moment assumption.
+We prove an anisotropic local law using standard proof techniques in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
+The full proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{sec pf RMTlemma}.
+
+%The proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
 %In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
@@
 %Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
-
-The above arguments are the core of the main proof.
-To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ only satisfy certain moment assumptions.
-These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
-For the full rigorous proof, we refer the reader to Section \ref{appendix RMT}.

### 2020-09-26 arxiv/algorithm.tex
start sec 3/6

@@
 \squishend
-
-\noindent\textit{Mitigating negative transfer.}
-An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
-In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-\squishlist
-	\item We divide the source task data into $S$ batches.
-	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
-	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
-	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\squishend
-
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-\noindent\textit{Covariance alignemnt.}
-Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
-Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
-The idea is to add an alignment module between the input and the shared module $B$.
-This new module is then trained together with $B$ and the output layers.
-We validate our insight on this procedure in the experiments.

### 2020-09-26 arxiv/examples.tex
start sec 3/6

--- 2020-09-25 arxiv/implications.tex
@@
 %Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-We illustrate our main results, Theorem \ref{thm_many_tasks}, Theorem \ref{thm main RMT} and Corollary \ref{thm_main_informal}, in a simplified setting.
-For this setting, we simulate several empirical phenomena that are well-known in hard parameter sharing approaches.
-We use our results to explain the empirical phenomena.
+We illustrate our main results in simplified settings.
+We explain several empirical phenomena that have often been observed when hard parameter sharing approaches are used.
 
@@
 %\end{align*}}
-
-\subsection{Sample Efficiency}
-
-observed in Taskonomy \cite{ZSSGM18}.
 
@@
 \begin{align*}
-	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-c}\sigma^2 )
+	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-\e}\sigma^2 )
 	 \end{align*}
-	 for any constant $c\in (0,1/2)$.
+	 for any constant $\e\in (0,1/2)$.
 \end{claim}
@@
 %On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
+
+\subsection{Sample Efficiency}
+
+observed in Taskonomy \cite{ZSSGM18}.

### 2020-09-26 arxiv/experiments.tex
wip
edits
start sec 3/6

--- 2020-08-10 arxiv/experiments.tex
@@
-\section{Experiments}
+\section{Numerical Results}
 
@@
 \begin{table}[!b]
-\begin{minipage}[t]{.58\textwidth}
-	\vspace{-0.1in}
-	\centering
-  \begin{tabular}{c c c c c}
-	\toprule
-		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-		& Precision &  Recall & Precision &  Recall \\
-		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
+%\begin{minipage}[t]{.58\textwidth}
+%	\vspace{-0.1in}
+%	\centering
+%  \begin{tabular}{c c c c c}
+%	\toprule
+%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
+%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
+%		& Precision &  Recall & Precision &  Recall \\
+%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
+%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
+%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
+%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
 		% 0.3 & 1.000 & 0.004 &     - &     - \\
-	\bottomrule
-	\end{tabular}
-	\vspace{0.1in}
-	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-	\label{tab:mtl_better_than_stl}
-\end{minipage}%
-\quad
+%	\bottomrule
+%	\end{tabular}
+%	\vspace{0.1in}
+%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
+%	\label{tab:mtl_better_than_stl}
+%\end{minipage}%
+%\quad
 	\begin{minipage}[t]{.40\textwidth}
@@
 
-\subsection{Simulation Studies}
+\textit{Validating the Theoretical Results.}
+We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
+\squishlist
+	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
+First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
+Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
+TREC is less similar to MR because the task is about question types.
+Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
+	\item Sample size: We vary the sample size of the source task from $100$ to $3000$.
+	\item Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
+	We fix the sample size of the target task as $1000$.
+\squishend
 
-\subsection{Validating the Theoretical Implication}\label{sec_exp_ab}
+%\subsection{Validating the Theoretical Results}\label{sec_exp_ab}
+%We first validate our theoretical results in Section \ref{sec_similarity} and \ref{sec_data_size}.
+%In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
+%We select each task pair based on our domain knowledge.
+%We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
+%The rest of experimental procedures are left to Appendix \ref{app_it}.
 
-We first validate our theoretical results in Section \ref{sec_similarity} and \ref{sec_data_size}.
-In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
-We select each task pair based on our domain knowledge.
-We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
+\subsection{Sample Imbalance}\label{sec_exp_sample}
+
+%\textit{Predicting transfer effect via STL results.}
+%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
+%A common challenge in the study of MTL is that the results can be hard to understand.
+%It is difficult to predict when MTL performs well without running extensive trials.
+%Our insight is that we can use STL results to help understand MTL results.
+%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
+%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
+%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
+%The results show that STL results are indicative of MTL results.
+
 In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
 Finally, we validate the algorithmic consequence of Section \ref{sec_covshift}.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL.
-We average the results over all 15 task pairs.
-The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
-The rest of experimental procedures are left to Appendix \ref{app_it}.
-
-\subsection{Validating the Algorithmic Consequences}\label{sec_exp_res}
-
-\textit{Predicting transfer effect via STL results.}
-We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-A common challenge in the study of MTL is that the results can be hard to understand.
-It is difficult to predict when MTL performs well without running extensive trials.
-Our insight is that we can use STL results to help understand MTL results.
-Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
 
 \textit{Mitigating negative transfer via incremental training.}
+\noindent\textit{Mitigating negative transfer.}
+An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
+In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
+More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
+Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
+\squishlist
+	\item We divide the source task data into $S$ batches.
+	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
+	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
+	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
+\squishend
+
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+			\For{$j = 1,\dots, T$}
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+			\EndFor
+			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+				\State \textbf{break}
+			\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
 First, we show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
@@
 
-\subsection{Missing Details from the Experiments}\label{app_experiments}
+\subsection{Covariate Shift}
 
-\subsection{Synthetic Settings}\label{app_synthetic}
-	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
-	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
-	\squishlist
-		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
-	The noise level is $\sigma = 5$.
-	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
-	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
-	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
-		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
-	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
-		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
-	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
-	This can be achieved similarly by rescaling the task data.
-	\squishend
+\noindent\textit{Covariance alignemnt.}
+Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
+Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
+We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
+The idea is to add an alignment module between the input and the shared module $B$.
+This new module is then trained together with $B$ and the output layers.
+We validate our insight on this procedure in the experiments.
 
-\subsection{Image and Text Classification Settings}\label{app_it}
-
-For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-We evaluate three model choices.
-For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
-For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
-
-\textit{Predicting transfer effect via STL results.}
-We simplify the setup of this experiment by fixing the sample sizes of every task pair.
-For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
-We randomly sample these many data points from the task.
-The sample size of the target task is $1000$.
-For image classification tasks, the training sample size is $10,000$ for every task.
-
-\textit{Mitigating negative transfer via incremental training.}
-For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
-We add $20\%$ of source task samples for every $T = 2$ epochs.
-The total number of epochs is $20$.
-We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
-
-For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
-Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
-We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
-We run $20$ epochs in total.
-
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-\textit{Validating the Theoretical Results.}
-We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-\squishlist
-	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-TREC is less similar to MR because the task is about question types.
-Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-	\item Sample size: We vary the sample size of the source task from $100$ to $3000$.
-	\item Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
-	We fix the sample size of the target task as $1000$.
-\squishend
-
-%We validate that MTL performs better when the source task is more similar to the target task.
-%We show the result on the sentiment analysis tasks.
-%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
-%Figure \ref{fig_ab_sim} confirms the result.
-%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
+In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL.
+We average the results over all 15 task pairs.
+The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
 
@@
 \end{figure}
+
+\subsection{Sample Efficiency}
+
+%We validate that MTL performs better when the source task is more similar to the target task.
+%We show the result on the sentiment analysis tasks.
+%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+%Figure \ref{fig_ab_sim} confirms the result.
+%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
+
+\begin{table}
+	\begin{center}
+		\begin{tabular}{c c c c c}
+			\toprule
+			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
+				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
+			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
+			\midrule
+			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
+			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
+			% {\bf CNN}  & 76\% & - & 32\% & -\\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Taskonomy experiment.}
+	\label{tab:taskonomy}
+\end{table}

### 2020-09-26 arxiv/examples.tex
wip

@@
 
-\noindent\textbf{Isotropic features and models.}
 	Imagine that we have two tasks and the covariates of both tasks have isotropic covariance matrices.
@@
 
-\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
+\begin{proposition}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
 	Assume that the isotropic setting described above holds, and that there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy that
@@
 	 \fi
-\end{corollary}
+\end{proposition}
 
-It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
+%It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
 We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
@@
 The proof of the following claim will be given in Section \ref{app_iso_cov}.
-\begin{claim} \label{claim_STL_loss}
-Under the above isotropic setting for task two, we have that with high probability,
-\begin{align*}
-	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-\e}\sigma^2 )
-	 \end{align*}
-	 for any constant $\e\in (0,1/2)$.
-\end{claim}
+%\begin{claim} \label{claim_STL_loss}
+%Under the above isotropic setting for task two, we have that with high probability,
+%\begin{align*}
+%	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-\e}\sigma^2 )
+%	 \end{align*}
+%	 for any constant $\e\in (0,1/2)$.
+%\end{claim}
+%We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transitions from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.
 
-We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transitions from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.
-
-\medskip
-
-\noindent{\bf Varying model distance.} 
+%\medskip
+%
+%\noindent{\bf Varying model distance.}
 %With Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss}, it is not hard to see 
-One can observe that as we increase the distance $pd^2$ between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+%One can observe that as we increase the distance $pd^2$ between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
 More precisely, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases, while variance reduction from STL to MTL is $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$.
 %Therefore, while the variance of MTL still reduces compared to STL, 
-If the bias increases more than the amount of variance reduced, we will observe negative transfer.
+%If the bias increases more than the amount of variance reduced, we will observe negative transfer.
 
-\iffalse
-\begin{proposition}[Task model distance]\label{prop_dist_transition}
-	In the isotropic model, suppose that $\rho_1$ and $\rho_2 > 1$.
-	Then
-	%Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between $\Psi(\beta_1, \beta_2)$ and $\Phi(\rho_1, \rho_2)$:
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\Psi(\beta_1, \beta_2) < \frac{1}{\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			\[ \te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}). \]
-		\item \textbf{Negative transfer:} If $\Psi(\beta_1, \beta_2) > {\nu} \cdot  \Phi(\rho_1, \rho_2)$, then w.h.p. over the randomness of $X_1,X_2$,
-			$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-	Here {\small$\nu = (1+\oo(1)) \cdot (1 - 1/\sqrt{\rho_1})^{-4}$}.
-	Concretely, if $\rho_1 > 40$, then $\nu\in (1,2)$.
-\end{proposition}
-Proposition \ref{prop_dist_transition} simplifies Theorem \ref{thm_main_informal} in the isotropic model, allowing for a more explicit statement of the bias-variance tradeoff.
-Concretely, $\Psi(\beta_1, \beta)$ and $\Phi(\rho_1, \rho_2)$ corresponds to $\Delta_{\bias}$ and $\Delta_{\vari}$, respectively.
-%Roughly speaking, the transition threshold scales as $\frac{pd^2}{\sigma^2} - \frac{1}{\rho_1} - \frac{1}{\rho_2}$.
-\fi
-
-We apply Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+We apply Corollary \ref{cor_MTL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
 We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
@@
 
-\iffalse
-The proof of Proposition \ref{prop_dist_transition} involves two parts.
-First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
-A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
-thus simplifying the general condition in Theorem \ref{thm_main_informal}.
-\fi
+%The proof of Proposition \ref{prop_dist_transition} involves two parts.
+%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
+%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
+%The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
+%A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
+%thus simplifying the general condition in Theorem \ref{thm_main_informal}.
 
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-		\caption{Task similarity}
-		\label{fig_model_shift}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
 		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
-		\caption{Sample size}
+		\caption{Sample imbalance}
 		\label{fig_size}
@@
 		\label{fig_covariate}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
+		\caption{Sample efficiency}
+		\label{fig_model_shift}
 	\end{subfigure}
@@
 
-%\subsection{Sample Ratio}\label{sec_data_size}
-
-\medskip
-\noindent{\bf Varying sample ratio.} In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
+In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
 %More generally, such results are still applicable when all task data are being added simultaneously.
@@
 
-\iffalse
-\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
-	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-	Then we have that
-	\begin{itemize}
-		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
+%\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
+%	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+%	Then we have that
+%	\begin{itemize}
+%		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
 $$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
-		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
+%		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
 $$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-	\end{itemize}
-\end{proposition}
-Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
+%	\end{itemize}
+%\end{proposition}
+%Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
 
@@
 The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-\fi
 

### 2020-09-26 arxiv/proof_gaussian_case.tex
wip

@@
 
-%\input{proof_two_tasks}
 The main goal of this section is to prove Theorem \ref{thm_main_RMT}.
-%Recall that $n:=n_1+n_2$, which is the total number of data in the two tasks.
-%Before giving the main proof, we first introduce some notations and tools.
-%Following the notations in \cite{EKYY,EKYY1}, we will use the following definition to characterize events of overwhelming probability.
-%
-%\begin{definition}[overwhelming probability event] \label{high_prob}
-%Define
-%\begin{equation}\label{def_phi}
-%\varphi:=(\log N)^{\log \log N}.
-%\end{equation}
-%We say that an $N$-dependent event $\Omega$ holds with {\it{$\xi$-overwhelming probability}} if there exist constant $c,C>0$ independent of $N$, such that
-%\begin{equation}
-%\mathbb{P}(\Omega) \geq 1-N^{C} \exp(- c\varphi^{\xi}),  \label{D25}
-%\end{equation}
-%for all sufficiently large $N$.
-For simplicity, for the case $\xi=1$, we just say {\it{overwhelming probability}}.
-Note that if (\ref{D25}) holds, then $\mathbb P(\Omega) \ge 1 - \exp(-c'\varphi^{\xi})$ for any constant $0\le c' <c$.
-%\end{definition}
-%\begin{remark}
-%For any $c, C>0$, there exists a $0< c^{\prime}<c$, such that $N^{C} \exp(-c \varphi^{\xi}) \leq \exp(-c^{\prime} \varphi^{\xi})$. Hence, if
-%\begin{equation}
-%\mathbb{P}(\Omega) \geq 1- \exp(-c \varphi^{\xi})
-%\end{equation}
-%$\Omega$ is also a $\xi$-overwhelming probability event.
-%\end{remark}
-For simplicity of notations, we will use the following notion of stochastic domination, which was first introduced in \cite{Average_fluc} and subsequently used in many works on random matrix theory.
-It greatly simplifies the presentation of the results and their proofs by systematizing statements of the form ``$\xi$ is bounded by $\zeta$ with overwhelming probability up to a small power of $n$".
-
-\begin{definition}[Stochastic domination]\label{stoch_domination}
-%\begin{itemize}
-%\item[(i)]
-Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
-%\begin{itemize} \item[(i)]
-We say $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any (small) constant $\e>0$ and (large) constant $D>0$,
-\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}\]
-for large enough $n\ge n_0(\e, D)$.
-Moreover, if $\xi$ and $\zeta$ depend on a parameter $u$, then we say $\xi$ is stochastically dominated by $\zeta$ uniformly in $u\in \cal U$,  if for any constants $\e,D>0$,
-\[\sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}\]
-for large enough $n\ge n_0(\e, D)$.
-%\item[(ii)]
-%\end{itemize}
-%(i) Let
-%\[\xi=\left(\xi^{(n)}(u):n\in\bbN, u\in U^{(n)}\right),\hskip 10pt \zeta=\left(\zeta^{(n)}(u):n\in\bbN, u\in U^{(n)}\right)\]
-%be two families of nonnegative random variables, where $U^{(n)}$ is a possibly $n$-dependent parameter set.
-We say $\xi$ is stochastically dominated by $\zeta$, uniformly in $u$, if for any fixed (small) $\epsilon>0$ and (large) $D>0$,
-%\[\sup_{u\in U^{(n)}}\bbP\left[\xi^{(n)}(u)>n^\epsilon\zeta^{(n)}(u)\right]\le n^{-D}\]
-%for large enough $n\ge n_0(\epsilon, D)$, and we shall use the notation $\xi\prec\zeta$.
-%%Throughout this paper, the stochastic domination will always be uniform in all parameters that are not explicitly fixed (such as matrix indices, and $z$ that takes values in some compact set).
-%%Note that $N_0(\epsilon, D)$ may depend on quantities that are explicitly constant, such as $\tau$ in Assumption \ref{assm_big1} and equation \eqref{assm_gap}.
-%If for some complex family $\xi$ we have $|\xi|\prec\zeta$, then we will also write $\xi \prec \zeta$ or $\xi=\OO_\prec(\zeta)$.
-%\item[(ii)]
-%(ii) We extend the definition of $\OO_\prec(\cdot)$ to matrices in the weak operator sense as follows.
-Let $A$ be a family of random matrices and $\zeta$ be a family of nonnegative random variables.
-Then $A=O_\prec(\zeta)$ means that $\left|\left\langle\mathbf v, A\mathbf w\right\rangle\right|\prec\zeta \| \mathbf v\|_2 \|\mathbf w\|_2 $ uniformly in any deterministic vectors $\mathbf v$ and $\mathbf w$.
-Here and throughout the following, whenever we say ``uniformly in any deterministic vectors", we mean that ``uniformly in any deterministic vectors belonging to a set of cardinality $N^{\OO(1)}$".
-%\item[(iv)]
-%\end{itemize}
-\end{definition}
-\begin{remark}
-Note that since we allow an $n^\e$ factor in the definition of stochastic domination, we have the seemingly strange inequality $(\log n)^C\prec 1$ for any constant $C>0$.
-\end{remark}
-
-\begin{example}\label{example stoc}
-Given a random variable $\xi$, if its moments exist up to any order, then we have $|\xi|\prec 1$. In fact, for any constants $\e, D>0$, by Markov's inequality we have
-$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D},$$
-if we choose $k$ large enough such that $k\e>D$. As a special case, we have $|\xi|\prec 1$ for a Gaussian random variable $\xi$ with unit variance.
-\end{example}
-
-%\HZ{Why is this below part of the def. of stochastic domination?}
-In the following proof, we say an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
-Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
-
-In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below.
-%\ref{sec_prelim}.
- Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.
-
-%We summarize our basic assumptions here for future reference.
-%Note that this assumption is in accordance with the assumptions of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, except that we rescale the entries of $Z^{(1)}$ and $Z^{(2)}$ by $n^{-1/2}$.
-%and allow $\rho_1$ to be smaller than 1.
-\begin{assumption}\label{assm_big1}
-As in Section \todo{add reference}, we consider random matrices $X^{(1)}=Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}=Z^{(2)}\Sigma_2^{1/2}$, where $Z^{(1)}$ and $Z^{(2)}$ are independent $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries of zero mean and unit variance.
-Recall that $\rho_1= n_1/p$ and $\rho_2=n_2/p$.
-We assume that for a small constant $0<\tau<1$,
-%\HZ{We have defined $\rho_1,\rho_2$ already in sec 2. Consider using ``Recall that $\rho_1 =, \rho_2 =$.''}
-\be\label{assm2}
-0\le \rho_1 \le \tau^{-1}, \quad 1+\tau \le \rho_{2} \le \tau^{-1}.
-\ee
-Recall that the singular value decomposition of $M = \Sig_1^{1/2} \Sig_2^{-1/2}$ is $U \Lambda V^{\top}$. We assume that
-\begin{equation}\label{assm32}
-\tau \le \lambda_p \le \lambda_1 \le \tau^{-1} .%, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
+We begin by providing a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
+%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
+By the rotational invariance of the multivariate Gaussian distribution, we have
+\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
+where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
+ \begin{equation} \label{resolv Gauss1}
+   G(z)= \left( {\begin{array}{*{20}c}
+   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
+   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+   \end{array}} \right)^{-1}.
  \end{equation}
-Finally, recalling the notations in equation \eqref{labelZ}, we assume that $Z^{(1)}$ and $Z^{(2)}$ satisfy
-\begin{equation}
-n^{-1/2}\max_{i\in \cal I_0,\mu \in \cal I_1}\vert Z^{(1)}_{\mu i}\vert \prec q,\quad n^{-1/2}\max_{i\in \cal I_0,\nu \in \cal I_2}\vert Z^{(2)}_{\nu i}\vert \prec q, \label{eq_support}
-\end{equation}
-for some deterministic parameter $q$ satisfying $ n^{-{1}/{2}} \leq q \leq n^{- \tau} $ for a small constant $\tau>0$.
-%Here we recall the notations in \eqref{labelZ}.
- %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-\end{assumption}
-%\HZ{This is restating what's stated above again.
-Remove redundant statements (unless there's something critical missing in Sec 2).} [\cor FY: The setting in sec 1 is too vague for the purpose of this section in the sense that it is hard to find the exact properties we need.
-In this section, I want to state rigorous statements with a reference to an exact assumption.
-Moreover, the above assumption contains more.\nc]
-
-\begin{remark}
-The lower bound $\rho_2\ge 1+\tau$ in equation \eqref{assm2} is to ensure that the sample covariance matrix $(X^{(2)})^\top X^{(2)}$ is non-singular with overwhelming probability.
-Moreover, we have allowed that $\rho_1=0$, because we want to state a general result that also covers the special case with no source task.
-\end{remark}
-
-\begin{remark}\label{rem_athmoment}
-Whenever the estimates in equation \eqref{eq_support} hold, we say $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ satisfy the {\it{bounded support condition}} with $q$, or $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ have support $q$.
-%\begin{definition}\label{defn_support}
-%We say a (rescaled) random matrix $\cal M$ satisfies the {\it{bounded support condition}} with $q$, if
-%\begin{equation}
-%\max_{i,j}\vert \cal M_{ij}\vert \prec q. \label{eq_support}
-%\end{equation}
-%%Here $q\equiv q(n)$ is a deterministic parameter and usually satisfies $ n^{-{1}/{2}} \leq q \leq n^{- \phi} $ for some (small) constant $\phi>0$.
-%Whenever (\ref{eq_support}) holds, we say that $M$ has support $q$.
-%%Moreover, if the entries of $X$ satisfy (\ref{size_condition}), then $X$ trivially satisfies the bounded support condition with $q=N^{-\phi}$.
-%\end{definition}
-%\begin{example}
-%\todo{Talk about the Gaussian case and Bernoulli case.}
-By Example \ref{example stoc}, if the entries of $Z^{(1)}$ have finite moments up to any order, %as in equation \eqref{assmAhigh},
-then $n^{-1/2}Z^{(1)}$ has bounded support $n^{-1/2}$.
-More generally, if the entries of $Z^{(1)}$ have finite $\varphi$-th moment as in \eqref{assmAhigh}, then using Markov's inequality and a simple union bound we get that
-\be\label{Ptrunc}
-\P\left(n^{-1/2}\max_{i,\mu}|(Z^{(1)})_{\mu i}|\ge (\log n) n^{-\frac{\varphi-4}{2\varphi}}\right)=\OO((\log n)^{-\varphi}).\ee
-In other words, $n^{-1/2}Z^{(1)}$ has bounded support $q=n^{-\frac{\varphi-4}{2\varphi}}$ on a event with probability $1-\oo(1)$.
-This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}.
-%This fact will be used in the proof of Corollary \ref{main_cor} below.
-The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
-%is essentially introduced to deal with the moment conditions; see Corollary \ref{main_cor} below for more details.
-%\end{example}
-\end{remark}
-
-\paragraph{Notations.}
 Define the index sets
@@
 We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
-
-\subsection{Warmup: The Gaussian Case}
-Now we give a heuristic derivation of the matrix limit when the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian. In this case,
-%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
-by the rotational invariance of the multivariate Gaussian distribution we have
-\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
-where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
- \begin{equation} \label{resolv Gauss1}
-   G(z)= \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
-   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{-1}.
- \end{equation}
 
@@
 \medskip
-\noindent\textbf{Deriving the self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
+\noindent\textbf{Self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
 \be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
@@
 \medskip
-\noindent\textbf{Deriving the matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+\noindent\textbf{The matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
 $$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
@@
 The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
+
+\paragraph{Notations.}
+We say an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
+Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
+We frequently use the following notion of stochastic domination, which was first introduced in \cite{Average_fluc} and subsequently used in many works on random matrix theory.
+%It greatly simplifies the presentation of the results and their proofs by systematizing statements of the form ``$\xi$ is bounded by $\zeta$ with overwhelming probability up to a small power of $n$".
+
+\begin{definition}[Stochastic domination]\label{stoch_domination}
+%\begin{itemize}
+%\item[(i)]
+Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
+\HZ{what is $n$-dependent rv?}
+We say $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any (small) constant $\e>0$ and (large) constant $D>0$
+\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}, \]
+for large enough $n\ge n_0(\e, D)$.
+Moreover, if $\xi$ and $\zeta$ depend on a parameter $u$, then we say $\xi$ is stochastically dominated by $\zeta$ uniformly in $u\in \cal U$,  if for any constants $\e,D>0$,
+\[\sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}, \]
+for large enough $n\ge n_0(\e, D)$.
+%\item[(ii)]
+%\end{itemize}
+%(i) Let
+%\[\xi=\left(\xi^{(n)}(u):n\in\bbN, u\in U^{(n)}\right),\hskip 10pt \zeta=\left(\zeta^{(n)}(u):n\in\bbN, u\in U^{(n)}\right)\]
+%be two families of nonnegative random variables, where $U^{(n)}$ is a possibly $n$-dependent parameter set.
+We say $\xi$ is stochastically dominated by $\zeta$, uniformly in $u$, if for any fixed (small) $\epsilon>0$ and (large) $D>0$,
+%\[\sup_{u\in U^{(n)}}\bbP\left[\xi^{(n)}(u)>n^\epsilon\zeta^{(n)}(u)\right]\le n^{-D}\]
+%for large enough $n\ge n_0(\epsilon, D)$, and we shall use the notation $\xi\prec\zeta$.
+%%Throughout this paper, the stochastic domination will always be uniform in all parameters that are not explicitly fixed (such as matrix indices, and $z$ that takes values in some compact set).
+%%Note that $N_0(\epsilon, D)$ may depend on quantities that are explicitly constant, such as $\tau$ in Assumption \ref{assm_big1} and equation \eqref{assm_gap}.
+%If for some complex family $\xi$ we have $|\xi|\prec\zeta$, then we will also write $\xi \prec \zeta$ or $\xi=\OO_\prec(\zeta)$.
+%\item[(ii)]
+%(ii) We extend the definition of $\OO_\prec(\cdot)$ to matrices in the weak operator sense as follows.
+Let $A$ be a family of random matrices and $\zeta$ be a family of nonnegative random variables.
+Then $A=O_\prec(\zeta)$ means that $\left|\left\langle\mathbf v, A\mathbf w\right\rangle\right|\prec\zeta \| \mathbf v\|_2 \|\mathbf w\|_2 $ uniformly in any deterministic vectors $\mathbf v$ and $\mathbf w$.
+Here and throughout the following, whenever we say ``uniformly in any deterministic vectors", we mean that ``uniformly in any deterministic vectors belonging to a set of cardinality $N^{\OO(1)}$".
+%\item[(iv)]
+%\end{itemize}
+\end{definition}
+
+For example, we say that $\xi$ is stochastically dominated by $\zeta$ with overwhelming probability if $\zeta$ is greater than $\xi$ up to a small power of $n^{\e}$.
+Since we allow an $n^\e$ factor in the definition of stochastic domination, we have the seemingly strange inequality $(\log n)^C\prec 1$ for any constant $C>0$.
+As another example, given a random variable $\xi$, if its moments exist up to any order, then we have $|\xi|\prec 1$. In fact, for any constants $\e, D>0$, by Markov's inequality we have
+$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D},$$
+if we choose $k$ large enough such that $k\e>D$. As a special case, we have $|\xi|\prec 1$ for a Gaussian random variable $\xi$ with unit variance.
+
+%\HZ{Why is this below part of the def. of stochastic domination?}
+
+In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below.
+%\ref{sec_prelim}.
+ Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.
+
+%We summarize our basic assumptions here for future reference.
+%Note that this assumption is in accordance with the assumptions of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, except that we rescale the entries of $Z^{(1)}$ and $Z^{(2)}$ by $n^{-1/2}$.
+%and allow $\rho_1$ to be smaller than 1.
+\begin{assumption}\label{assm_big1}
+As in Section \todo{add reference}, we consider random matrices $X^{(1)}=Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}=Z^{(2)}\Sigma_2^{1/2}$, where $Z^{(1)}$ and $Z^{(2)}$ are independent $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
+entries of zero mean and unit variance.
+Recall that $\rho_1= n_1/p$ and $\rho_2=n_2/p$.
+We assume that for a small constant $0<\tau<1$,
+%\HZ{We have defined $\rho_1,\rho_2$ already in sec 2. Consider using ``Recall that $\rho_1 =, \rho_2 =$.''}
+\be\label{assm2}
+0\le \rho_1 \le \tau^{-1}, \quad 1+\tau \le \rho_{2} \le \tau^{-1}.
+\ee
+Recall that the singular value decomposition of $M = \Sig_1^{1/2} \Sig_2^{-1/2}$ is $U \Lambda V^{\top}$. We assume that
+\begin{equation}\label{assm32}
+\tau \le \lambda_p \le \lambda_1 \le \tau^{-1} .%, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
+\end{equation}
+Finally, recalling the notations in equation \eqref{labelZ}, we assume that $Z^{(1)}$ and $Z^{(2)}$ satisfy
+\begin{equation}
+n^{-1/2}\max_{i\in \cal I_0,\mu \in \cal I_1}\vert Z^{(1)}_{\mu i}\vert \prec q,\quad n^{-1/2}\max_{i\in \cal I_0,\nu \in \cal I_2}\vert Z^{(2)}_{\nu i}\vert \prec q, \label{eq_support}
+\end{equation}
+for some deterministic parameter $q$ satisfying $ n^{-{1}/{2}} \leq q \leq n^{- \tau} $ for a small constant $\tau>0$.
+%Here we recall the notations in \eqref{labelZ}.
+ %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
+\end{assumption}
+%\HZ{This is restating what's stated above again.
+Remove redundant statements (unless there's something critical missing in Sec 2).} [\cor FY: The setting in sec 1 is too vague for the purpose of this section in the sense that it is hard to find the exact properties we need.
+In this section, I want to state rigorous statements with a reference to an exact assumption.
+Moreover, the above assumption contains more.\nc]
+
+%\begin{remark}
+%The lower bound $\rho_2\ge 1+\tau$ in equation \eqref{assm2} is to ensure that the sample covariance matrix $(X^{(2)})^\top X^{(2)}$ is non-singular with overwhelming probability.
+Moreover, we have allowed that $\rho_1=0$, because we want to state a general result that also covers the special case with no source task.
+%\end{remark}
+
+Whenever the estimates in equation \eqref{eq_support} hold, we say $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ satisfy the {\it{bounded support condition}} with $q$, or $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ have support $q$.
+%\begin{definition}\label{defn_support}
+%We say a (rescaled) random matrix $\cal M$ satisfies the {\it{bounded support condition}} with $q$, if
+%\begin{equation}
+%\max_{i,j}\vert \cal M_{ij}\vert \prec q. \label{eq_support}
+%\end{equation}
+%%Here $q\equiv q(n)$ is a deterministic parameter and usually satisfies $ n^{-{1}/{2}} \leq q \leq n^{- \phi} $ for some (small) constant $\phi>0$.
+%Whenever (\ref{eq_support}) holds, we say that $M$ has support $q$.
+%%Moreover, if the entries of $X$ satisfy (\ref{size_condition}), then $X$ trivially satisfies the bounded support condition with $q=N^{-\phi}$.
+%\end{definition}
+%\begin{example}
+%\todo{Talk about the Gaussian case and Bernoulli case.}
+As shown in the example above, if the entries of $Z^{(1)}$ have finite moments up to any order, %as in equation \eqref{assmAhigh},
+then $n^{-1/2}Z^{(1)}$ has bounded support $n^{-1/2}$.
+More generally, if the entries of $Z^{(1)}$ have finite $\varphi$-th moment as in \eqref{assmAhigh}, then using Markov's inequality and a simple union bound we get that
+\be\label{Ptrunc}
+\P\left(n^{-1/2}\max_{i,\mu}|(Z^{(1)})_{\mu i}|\ge (\log n) n^{-\frac{\varphi-4}{2\varphi}}\right)=\OO((\log n)^{-\varphi}).\ee
+In other words, $n^{-1/2}Z^{(1)}$ has bounded support $q=n^{-\frac{\varphi-4}{2\varphi}}$ on a event with probability $1-\oo(1)$.
+This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}.
+%This fact will be used in the proof of Corollary \ref{main_cor} below.
+The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
+%\end{example}
+
+%Recall that $n:=n_1+n_2$, which is the total number of data in the two tasks.
+%Before giving the main proof, we first introduce some notations and tools.
+%Following the notations in \cite{EKYY,EKYY1}, we will use the following definition to characterize events of overwhelming probability.
+%
+%\begin{definition}[overwhelming probability event] \label{high_prob}
+%Define
+%\begin{equation}\label{def_phi}
+%\varphi:=(\log N)^{\log \log N}.
+%\end{equation}
+%We say that an $N$-dependent event $\Omega$ holds with {\it{$\xi$-overwhelming probability}} if there exist constant $c,C>0$ independent of $N$, such that
+%\begin{equation}
+%\mathbb{P}(\Omega) \geq 1-N^{C} \exp(- c\varphi^{\xi}),  \label{D25}
+%\end{equation}
+%for all sufficiently large $N$.
+For simplicity, for the case $\xi=1$, we just say {\it{overwhelming probability}}.
+Note that if (\ref{D25}) holds, then $\mathbb P(\Omega) \ge 1 - \exp(-c'\varphi^{\xi})$ for any constant $0\le c' <c$.
+%\end{definition}
+%\begin{remark}
+%For any $c, C>0$, there exists a $0< c^{\prime}<c$, such that $N^{C} \exp(-c \varphi^{\xi}) \leq \exp(-c^{\prime} \varphi^{\xi})$. Hence, if
+%\begin{equation}
+%\mathbb{P}(\Omega) \geq 1- \exp(-c \varphi^{\xi})
+%\end{equation}
+%$\Omega$ is also a $\xi$-overwhelming probability event.
+%\end{remark}

### 2020-09-26 arxiv/proof_same_cov.tex
wip

@@
 	\begin{align}\label{eq_gA_p3}
-		\sum_{j=1}^t \norm{E_j}^2 &= \bignorm{\cW A - \cE}^2
-		= \bignorm{\cE}^2 - \inner{\cW A}{\cE},
+		\sum_{j=1}^t \norm{E_j}^2 &= \bignormFro{\cW A - \cE}^2
+		= \bignormFro{\cE}^2 - \inner{\cW A}{\cE},
 	\end{align}
@@
 	\begin{align}\label{eq_gA_err}
-		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-1/2 + e} \cdot \sigma^2 \cdot n \cdot t.
+		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
 	\end{align}
@@
 	Hence by the law of large numbers, we have that with high probability
-	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1 + \OO(p^{-c}))$,
+	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1 + \OO(p^{-\e}))$, for a small enough constant $\e$,
 	which implies that
@@
 	\begin{align}
-		\abs{\norm{\cE}^2 - \ex{\norm{\cE}^2}} \le p^{-1/2 + \e} \ex{\norm{\cE}^2}. \label{eq_gA_err3}
+		\abs{\normFro{\cE}^2 - \ex{\normFro{\cE}^2}} \le p^{-c_{\infty}} \ex{\normFro{\cE}^2}. \label{eq_gA_err3}
 	\end{align}
@@
 		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
-		&\le p^{-c} \cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + e}\cdot \sigma^2 n \cdot t. \label{eq_g_gap}
+		&\le p^{-c} \cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + \e}\cdot \sigma^2 n \cdot t. \label{eq_g_gap}
 	\end{align}

### 2020-09-26 arxiv/setup.tex
wip

@@
 \subsection{Summary of Results}
-\label{sec_prelim}
 
@@
 The rest of this paper is organized as follows.
-In Section \ref{set_prelim}, we present a preliminary of hard parameter sharing and random matrices. We describe several well-known facts.
+In Section \ref{sec_prelim}, we present a preliminary of hard parameter sharing and random matrices. We describe several well-known facts.
 In Section \ref{sec_example}, we describe illustrative examples of our technical results and discuss their implications.
@@
 Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-Let $\e$ be an fixed value within $(0, 1/2)$.
+Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
+We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.

### 2020-09-27 arxiv/diff_cov.tex
wip

@@
 	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix},\ee
-%In particular, the matrix limit of $\cal G(z)$ is given by
-%\be\label{matrix limit}(-z\id_p+a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^{-1},\ee
 where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following system of equations
@@
 We have that $a_3$ and $a_4$ satisfy the equation system \eqref{eq_a34extra}.
-Appling equation \eqref{cal G'0} into equation \eqref{calculate G'}, we obtain that the asymptotic limit of the bias equation.
+Applying equation \eqref{cal G'0} into equation \eqref{calculate G'}, we obtain that the asymptotic limit of the bias equation.
 %\begin{align}
@@
 The full proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{sec pf RMTlemma}.
-
-%The proof of equation \eqref{lem_cov_derv_eq} will be given in Section \ref{sec pf RMTlemma}, where we justify the approximate identity in equation \eqref{cal G'0}.
-%In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.
-%For the variance asymptotic limit, we study the resolvent
-%	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}))\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
-%Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
-%In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
-%	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]
-%
-%For the bias asymptotic limit, we show in \todo{where?} that
-%$$\bignorm{\Sigma_2^{1/2} ((X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)})^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
-%Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
-%We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
-%Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.

### 2020-09-27 arxiv/proof_gaussian_case.tex
wip

@@
 
-The main goal of this section is to prove Theorem \ref{thm_main_RMT}.
-We begin by providing a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
-%However, notice that if the entries of $(Z^{(1)})\equiv (Z^{(1)})^{\text{Gauss}}$ and $(Z^{(2)})\equiv (Z^{(2)})^{\text{Gauss}}$ are i.i.d. Gaussian, then
-By the rotational invariance of the multivariate Gaussian distribution, we have
-\be\label{eq in Gauss} Z^{(1)} U\Lambda \stackrel{d}{=} Z^{(1)} \Lambda, \quad Z^{(2)} V \stackrel{d}{=} Z^{(2)},\ee
-where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent
+\subsection{Proof of the Bias and Variance Asymptotics}\label{appendix RMT}
+
+We provide the proof of Theorem \ref{thm_main_RMT}.
+We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
+By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}$ also follow an isotropic Gaussian distribution.
+Hence it suffices to consider the following resolvent
  \begin{equation} \label{resolv Gauss1}
@@
  \end{equation}
+We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
+We first introduce several notations.
 Define the index sets
 $$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
- We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$. Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
+%We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$.
+Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
 	\be\label{labelZ}
- Z^{(1)}= (Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z^{(2)}= (Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
-
-Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
+ Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
+We will study the following partial traces of the resolve $G(z)$:
 \be\label{defm}
@@
 m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
- m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
+ m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z).
 \end{split}
 \ee
-We will show that these averaged resolvents satisfy some deterministic self-consistent equations asymptotically, which will be the core part of the proof.
-We refer the reader to the discussions below \eqref{0self_Gii} and \eqref{0self_Gmu1}.
-
-\medskip
-\noindent{\bf Schur complements.}
-%Now we discuss about how to obtain the matrix limit in equation \eqref{defn_piw}.
-%\HZ{Divide into several parts like sec 7 to improve readability.}
-The core quantities of the derivation are the following resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.
+To deal with the matrix inverse, we consider the following resolvent minors of $G(z)$.
 \begin{definition}[Resolvent minors]\label{defn_Minor}
- For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $a\in \mathcal I$, we define the minor $\cal A^{(a)}:=(\cal A_{a_1 a_2}:a_1, a_2 \in \mathcal I\setminus \{a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $a$-th row and column in $\cal A$.
-Note that we keep the names of indices when defining $\cal A^{(a)}$, i.e.
-$(\cal A^{(a)})_{a_1a_2}= \cal A_{a_1 a_2}$ for $a_1,a_2\ne a$.
-Correspondingly, we define the resolvent minor for $G$ in equation \eqref{resolv Gauss1} as %(recall equation \eqref{green2})
+	Let $X \in \real^{(p + n_1 + n_2)\times (p + n_1 + n_2)}$ and $i = 1, 2, \dots, p + n_1 + n_2$.
+	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1,a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
+	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1, a_2}$ to denote $ X_{a_1, a_2}$ when $a_1$ and $a_2$ both not equal to $i$, and $X^{(i)}_{a_1, a_2}$ to be zero when $a_1 = i$ or $a_2 = i$.
+	The resolvent minor of $G(z)$ after removing the $i$-th row and column is defined as
 	\begin{align*}
-G^{(\mathfrak c)}:&=\left[ \left( {\begin{array}{*{20}c}
+		G^{(i)}(z) := \left[ \left( {\begin{array}{*{20}c}
 		  { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
@@
 			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
-   \end{array}} \right)^{(a)}\right]^{-1} ,
-%= \left( {\begin{array}{*{20}c}
-%   { \mathcal G^{(\mathbb T)}} & \mathcal G^{(\mathbb T)} W^{(\mathbb T)}  \\
-%   {\left(W^{(\mathbb T)}\right)^\top\mathcal G^{(\mathbb T)}} & { \mathcal G_R^{(\mathbb T)} }  \\
-%\end{array}} \right)  ,
+    \end{array}} \right)^{(i)}\right]^{-1}.
 	\end{align*}
-and define the partial traces $m^{(a)}$, $m_0^{(a)}$, $m_1^{(a)}$ and $m_2^{(a)}$ by replacing $G$ with $G^{(a)}$ in equation \eqref{defm}.
-We adopt the convention that for the resolvent minor $G^{(a)}$ defined as above, $G^{(a)}_{a_1a_2} = 0$ if $a_1 =a$ or $a_2=a$.
 \end{definition}
-%Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$.
-One will see a crucial use of this fact in the heuristic proof below.
- Using Schur complement formulas in equation (\ref{resolvent2}), we have that for $i \in \cal I_0$, %$\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-%\HZ{This part needs more explanation - cannot understand.}
+As a remark, we denote the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G(z)^{(i)}$ in equation \eqref{defm}.
+
+\paragraph{Self-consistent equations.}
+We briefly describe the ideas for deriving the equation set \eqref{selfomega_a}.
+A complete full can be found in Lemma \ref{lemm_selfcons_weak}.
+The core idea is to study $G(z)$ using the Schur complement formula.
+We first introduce the following resolvent minors.
+
+First, we consider the diagonal entries of $G(z)$ for each block in $\cal I_0$, $\cal I_1$, and $\cal I_2$.
+For any $i$ in $\cal I_0$, we have that
 \begin{align}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu} , \label{0self_Gii}
+	G_{i,i}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu}(z) - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i} G^{\left( i \right)}_{\mu\nu}(z) -\frac{2\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu}(z).
+\label{0self_Gii}
 \end{align}
-and for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+For $\mu \in \cal I_1$ and $\nu\in \cal I_2$, we have that
 \begin{align}
-\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij},
+	G_{\mu,\mu}^{-1}(z) &=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \\
+	{G_{\nu,\nu}^{-1}(z) &=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij}.
 \label{0self_Gmu1}
 \end{align}
-where we recall the notations in equation \eqref{labelZ}. To see why equation \eqref{0self_Gii} holds, we have that by Schur complement formula,
-\begin{align*}
-\frac{1}{G_{ii}}= -z - H_i G^{(i)}H_{i}^\top, \quad H_i = \left( \mathbf 0_{p-1}, (n^{-1/2}\lambda_i (Z^{(1)})^\top_{i\mu }:\mu \in \cal I_1),(n^{-1/2} (Z^{(2)})^\top_{i\nu }:\nu \in \cal I_2)\right),
-\end{align*}
-where $H_i$ is actually the $i$-th row of $H$ with the $(i,i)$-th entry removed.
-Expanding the above expression, we obtain equation \eqref{0self_Gii}.
-The two expressions in equation \eqref{0self_Gmu1} are easier to obtain using Schur complement formula.
+To see why  holds, using Schur complement formula,
+$G_{ii}^{-1}(z) = -z - H_i G^{(i)}(z) H_{i}^\top$, where $H_i$ is the $i$-th row of $H$ with the $(i,i)$-th entry removed.
+Equation \eqref{0self_Gii} follows by expanding this formula.
 
-\medskip
-\noindent{\bf Concentration estimates.} Now for the right-hand side of equation \eqref{0self_Gii}, notice that the resolvent minor $G^{(i)}$ is defined such that it is independent of the entries $Z^{(1)}_{\mu i}$ and $Z^{(2)}_{\nu i}$.
-Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$, i.e., with overwhelming probability,
-\begin{align*}
-\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
-\end{align*}
-where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$.
-Intuitively, since we have removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$.
-Hence we obtain from the above equation that
-\begin{align}\label{1self_Gii}
- G_{ii}  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1 +  \frac{\rho_2}{\rho_1+\rho_2}m_2+\oo(1)\right)^{-1}.
-\end{align}
-Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
-with overwhelming probability. The rigorous derivation of the above concentration estimates will be given in the proof of Lemma \ref{lemm_selfcons_weak}; see equations \eqref{self_Gii}-\eqref{erri}.
+These two expressions are derived similarly using the Schur complement formula.
 
-\medskip
-\noindent\textbf{Self-consistent equations.} Now taking average of equation \eqref{1self_Gmu}, we obtain that
-\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},
-\ee
-with overwhelming probability. As a byproduct, comparing equations \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-\be\label{2.5self_Gmu} G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1),\ee
-with overwhelming probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that
-\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
-with overwhelming probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
+We show that with high probability, the following equations hold approximately:
 \be\label{approximate m1m2}
@@
 & \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
-& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1),
+& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1).
 \end{split}
 \ee
-with overwhelming probability, which give a system of approximate self-consistent equations for $(m_1,m_2)$.
-A rigorous derivation of these two equations will be given in the proof of Lemma \ref{lemm_selfcons_weak}.
+These are the self-consistent equations that we stated in equation \eqref{selfomega_a}.
 Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
@@
 \ee
+
+Combining equation \eqref{1self_Gii} and equation \eqref{3self_Gmu},
+
+For the right hand side of equation \eqref{0self_Gii}, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
+Hence by standard concentration inequalities (cf.
+Lemma \ref{largedeviation}), we have that the right hand side of equation \eqref{0self_Gii} is approximately equal to the expectation over $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$.
+More precisely, we have that with high probability the following holds
+\begin{align*}
+	\frac{1}{{G_{ii} }} &=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
+	&= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
+\end{align*}
+where we used the definition of $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ in equation \eqref{defm} with $G(z)$ replaced by $G^{(i)}(z)$.
+Since we removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
+Hence we obtain that
+\begin{align}\label{1self_Gii}
+	G_{ii}(z)  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2} m_2(z) + \oo(1)\right)^{-1}.
+\end{align}
+Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability the following holds
+\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
+The above inequalities are stated more precisely in the proof of Lemma \ref{lemm_selfcons_weak} (cf.  equations \eqref{self_Gii}-\eqref{erri}).
+By averaging equation \eqref{1self_Gmu} over $\mu \in \cal I_1$ and $\nu \in \cal I_2$, we obtain that with high probability
+\be\label{2self_Gmu}
+	m_1(z) = \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},
+	\quad m_2(z) =\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1}.
+\ee
+Combining equation \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability
+\be\label{2.5self_Gmu}
+	G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1).
+\ee
+Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that with high probability
+\be\label{3self_Gmu}
+	\frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1).
+\ee
+
 To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.

### 2020-09-27 arxiv/proof_gaussian_case.tex
sec B wip

@@
 A complete full can be found in Lemma \ref{lemm_selfcons_weak}.
-The core idea is to study $G(z)$ using the Schur complement formula.
-We first introduce the following resolvent minors.
-
-First, we consider the diagonal entries of $G(z)$ for each block in $\cal I_0$, $\cal I_1$, and $\cal I_2$.
-For any $i$ in $\cal I_0$, we have that
-\begin{align}
-	G_{i,i}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu}(z) - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i} G^{\left( i \right)}_{\mu\nu}(z) -\frac{2\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu}(z).
-\label{0self_Gii}
-\end{align}
-For $\mu \in \cal I_1$ and $\nu\in \cal I_2$, we have that
-\begin{align}
-	G_{\mu,\mu}^{-1}(z) &=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}, \\
-	{G_{\nu,\nu}^{-1}(z) &=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij}.
-\label{0self_Gmu1}
-\end{align}
-To see why  holds, using Schur complement formula,
-$G_{ii}^{-1}(z) = -z - H_i G^{(i)}(z) H_{i}^\top$, where $H_i$ is the $i$-th row of $H$ with the $(i,i)$-th entry removed.
-Equation \eqref{0self_Gii} follows by expanding this formula.
-
-These two expressions are derived similarly using the Schur complement formula.
-
 We show that with high probability, the following equations hold approximately:
@@
 \begin{split}
-& \frac1{m_1}= -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
-& \frac1{m_2}=-1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1).
+& m_1^{-1}(z) = -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
+& m_2^{-1}(z) = -1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1).
 \end{split}
@@
 These are the self-consistent equations that we stated in equation \eqref{selfomega_a}.
-Compare \eqref{approximate m1m2} to the deterministic self-consistent equations in equation \eqref{selfomega_a}, one can observe that we should have
-\be\label{approx m12 add}
-(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
-\ee
+More precisely, we have that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$.
 
-Combining equation \eqref{1self_Gii} and equation \eqref{3self_Gmu},
+The core idea is to study $G(z)$ using the Schur complement formula.
+First, we consider the diagonal entries of $G(z)$ for each block in $\cal I_0$, $\cal I_1$, and $\cal I_2$.
+For any $i$ in $\cal I_0$, any $\mu$ in $\cal I_1$, and any $\nu$ in $\cal I_2$, we have that
+\begin{align*}
+	&G_{i,i}^{-1}(z) = -z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i} G^{\left( i \right)}_{\mu,\nu}(z) -\frac{2\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) \\
+	&G_{\mu,\mu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}(z) \\
+	&G_{\nu,\nu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{i,j}(z).
+\end{align*}
+For the first equation, we expand the Schur complement formula $G_{ii}^{-1}(z) = -z - H_i G^{(i)}(z) H_{i}^\top$, where $H_i$ is the $i$-th row of $H$ with the $(i,i)$-th entry removed.
+The second and third equation follow by similar calculations.
 
-For the right hand side of equation \eqref{0self_Gii}, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
-Hence by standard concentration inequalities (cf.
-Lemma \ref{largedeviation}), we have that the right hand side of equation \eqref{0self_Gii} is approximately equal to the expectation over $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$.
-More precisely, we have that with high probability the following holds
+%\be\label{approx m12 add}
+%(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
+%\ee
+
+Next, we apply standard concentration bounds to simplify the above results.
+For $G^{-1}_{i, i}(z)$, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
+Hence by standard concentration inequalities, we have that the cross terms are approximately zero.
+%is approximately equal to the expectation over $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$.
+As shown in Lemma \ref{lemm_selfcons_weak}, we have that with high probability the following holds
 \begin{align*}
-	\frac{1}{{G_{ii} }} &=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
-	&= - z - \lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1^{(i)}(z)-  \frac{\rho_2}{\rho_1+\rho_2} m_2^{(i)}(z)+\oo(1),
+	G_{i,i}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
+	&= - z - \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1^{(i)}(z)-  \frac{n_2}{n_1 + n_2} m_2^{(i)}(z)+\oo(1)
 \end{align*}
-where we used the definition of $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ in equation \eqref{defm} with $G(z)$ replaced by $G^{(i)}(z)$.
+by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ with respect to the resolvent minor $G^{(i)}(z)$.
 Since we removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
@@
 \begin{align}\label{1self_Gii}
-	G_{ii}(z)  = -\left( z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2} m_2(z) + \oo(1)\right)^{-1}.
+	G_{i,i}(z)  = -\left(z + \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1 + n_2} m_2(z) + \oo(1)\right)^{-1}.
 \end{align}
-Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability the following holds
-\be\label{1self_Gmu} G_{\mu \mu }=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},\quad G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1},\ee
-The above inequalities are stated more precisely in the proof of Lemma \ref{lemm_selfcons_weak} (cf.  equations \eqref{self_Gii}-\eqref{erri}).
-By averaging equation \eqref{1self_Gmu} over $\mu \in \cal I_1$ and $\nu \in \cal I_2$, we obtain that with high probability
-\be\label{2self_Gmu}
-	m_1(z) = \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\left(1+\frac{p}{n} m_0 + \oo(1)\right)^{-1},
-	\quad m_2(z) =\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\left(1+\frac{p}{n} m+\oo(1)\right)^{-1}.
-\ee
-Combining equation \eqref{1self_Gmu} and \eqref{2self_Gmu}, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability
-\be\label{2.5self_Gmu}
-	G_{\mu \mu }=m_1 +\oo(1),\quad G_{\nu\nu}=m_2+\oo(1).
-\ee
-Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that with high probability
-\be\label{3self_Gmu}
-	\frac1{m_1}= -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{1}{n} \sum_{i=1}^p G_{ii}  + \oo(1).
-\ee
+For the other two blocks $\cal I_1$ and $\cal I_2$, using similar ideas we have that the following holds with high probability
+\begin{align*}
+	G_{\mu,\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} \\
+	G_{\nu,\nu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
+\end{align*}
+By averaging the above results over $\mu \in \cal I_1$ and $\nu \in \cal I_2$, we obtain that with high probability
+\begin{align*}
+	m_1(z) &= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu,\mu}(z) = -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} \\
+	m_2(z) &= \frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu,\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
+\end{align*}
+Furthermore, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability
+$G_{\mu,\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu, \nu}(z) = m_2+\oo(1)$.
+In other words, both block matrices within $\cal I_1$ and $\cal I_2$ are approximately a scaling of the identity matrix.
+The above results for $m_1(z)$ and $m_2(z)$ imply that
+\begin{align*}
+	m_1^{-1}(z) = -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{i,i}(z)+ \oo(1) \\
+	m_2^{-1}(z) = -1- \frac{1}{n} \sum_{i=1}^p G_{i,i}(z)  + \oo(1).
+\end{align*}
+where we used the definition of $m(z)$ and $m_0(z)$.
+By applying equation \eqref{1self_Gii} for $G_{i, i}(z)$, we obtain the self-consistent equations \ref{approximate m1m2}.
+In Lemma \ref{lem_stabw}, we show that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
 
-To justify this identity rigorously, we need to know that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
-This will be given by Lemma \ref{lem_stabw}.
-
-\medskip
-\noindent\textbf{The matrix limit.}  Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
+Finally, we derive the matrix limit $\Gi(z)$.
+Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
 $$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$

### 2020-09-27 arxiv/proof_gaussian_case.tex
sec B wip

@@
 %We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$.
-Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
-	\be\label{labelZ}
- Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
+%Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
+%	\be\label{labelZ}
+% Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
 We will study the following partial traces of the resolve $G(z)$:
@@
 \begin{split}
-& m_1^{-1}(z) = -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}+ \oo(1),\\
-& m_2^{-1}(z) = -1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{\rho_1}{\rho_1+\rho_2} m_1(z) +  \frac{\rho_2}{\rho_1+\rho_2}m_2(z)+\oo(1)}  + \oo(1).
+& m_1^{-1}(z) = -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{n_1}{n_1+ n_2} m_1(z) +  \frac{n_2}{n_1+n_2}m_2(z)+\oo(1)}+ \oo(1),\\
+& m_2^{-1}(z) = -1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1+n_2}m_2(z)+\oo(1)}  + \oo(1).
 \end{split}
@@
 These are the self-consistent equations that we stated in equation \eqref{selfomega_a}.
-More precisely, we have that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$.
+More precisely, we have that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_1} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$.
 
@@
 \begin{align*}
-	m_1^{-1}(z) = -1- \frac{1}{n} \sum_{i=1}^p \lambda_i^2 G_{i,i}(z)+ \oo(1) \\
-	m_2^{-1}(z) = -1- \frac{1}{n} \sum_{i=1}^p G_{i,i}(z)  + \oo(1).
+	m_1^{-1}(z) = -1- \frac{1}{n_1 + n_2} \sum_{i=1}^p \lambda_i^2 G_{i,i}(z)+ \oo(1) \\
+	m_2^{-1}(z) = -1- \frac{1}{n_1 + n_2} \sum_{i=1}^p G_{i,i}(z)  + \oo(1).
 \end{align*}

### 2020-09-27 arxiv/proof_examples.tex
wip
revise

@@
-\subsection{Proof of the Special Case}\label{app_iso_cov}
-\todo{switch the $a_3$ and $a_4$}
+\subsection{The Random-Effects Model}\label{app_iso_cov}
+We now give the proof of Proposition \ref{cor_MTL_loss}.
+As in the proof of Theorem \ref{thm_many_tasks}, we first derive a bias-variance decomposition of the prediction loss $L(\hat \eta_2^{\MTL})$.
+Then we can calculate the bias term and the variance term using Theorem \ref{thm_main_RMT}.
+
+Under the two-task setting of Corollary \ref{cor_MTL_loss}, the optimization objective \eqref{eq_mtl} becomes
+	\begin{align}
+		f(A, B) =   \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2+ \bignorm{X^{(2)} B A_2 - Y^{(2)}}^2, \label{eq_mtl_2task_cov}
+	\end{align}
+	where $B \in \real^{p}$ and $A_1, A_2\in \R$ because $r=1$ in the two-task case. % for $1 < r < t$ by our assumption.
+	Without loss of generality, we assume that both $A_1$ and $A_2$ are nonzero, since otherwise we can add a small perturbation $\delta$ to them and later remove this perturbation by taking $\delta\to 0$ in the final result.
+Again using the local optimality condition ${\partial f}/{\partial B} = 0$, for any $A_1$ and $A_2$ we obtain the optimal $\hat{B}$ as follows
+	\begin{align}
+		\hat{B} \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\
+		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
+	\end{align}
+ Now inserting $\hat B$ back into \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $A:=A_1/A_2$ as follows 
+ \begin{align}
+		g(A) \define  \sum_{i=1}^2 . \label{eq_mtl_A12}
+	\end{align}
+
+\cor
+%Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
+%Using the local optimality condition of $B$, we obtain that
+%\begin{align*}
+%	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
+%	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
+%	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+%\end{align*}
+Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
+\begin{align}
+	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
+	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
+			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
+\end{align}
+Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
+equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
+%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
+Comparing the above to single-task learning, that is,
+\begin{align}
+	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
+\end{align}
+we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
+In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
+Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
+
+% \todo{derive the test loss} Expectation was given in \eqref{eq_bias_2task} and \eqref{eq_var_2task}.
+ \nc
+
+Plugging $Y^{(1)}$ and $Y^{(2)}$ in \eqref{model_YvsX} into \eqref{eq_Bhat_2task}, we can rewrite that 
+ \begin{align}
+		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
+\label{eq_Bhat_2task2} %\\
+		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
+	\end{align}
+\todo{next derive the prediction loss} 
+ \cob
+
+ \begin{claim}
+	In the setting described above, we have that
+	\be\label{approxvalid}
+		g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
+	\ee
+\end{claim}
+\begin{proof}
+	We use the fact that our random vectors have i.i.d. entries.
+%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
+	Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
+$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
+Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d.
+centered entries, we can use the concentration result, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
+\begin{align*}
+\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
+&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
+\end{align*}
+with high probability. Thus we obtain that
+$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
+where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
+ again the concentration result, Lemma \ref{largedeviation}, we get that
+$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
+with high probability.
+%-----old-------
+%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
+%\begin{align}
+%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
+%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
+%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
+%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
+%\end{align}
+%\nc
+%------------------
+Thus we conclude the proof.
+\end{proof}
+
+\nc
+
+% \todo{switch the $a_3$ and $a_4$}
 
@@
 		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
-		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
-		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
+		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
+		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
 	\end{align}

### 2020-09-27 arxiv/setup.tex
revise

@@
 Let
-	\[ Y_k = X_k \beta_k + \varepsilon_k, \text{ for all } 1\le k \le t \] denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d. random vector with mean zero and variance $\sigma^2$.
+	\be\label{model_YvsX} Y^{(k)} = X^{(k)} \beta_k + \varepsilon_k, \text{ for all } 1\le k \le t \ee denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d.
+random vector with mean zero and variance $\sigma^2$.
 

### 2020-09-27 arxiv/proof_gaussian_case.tex
sec B wip

@@
 	&G_{i,i}^{-1}(z) = -z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i} G^{\left( i \right)}_{\mu,\nu}(z) -\frac{2\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) \\
-	&G_{\mu,\mu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}(z) \\
+	&G_{\mu,\mu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{i,j}(z) \\
 	&G_{\nu,\nu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{i,j}(z).
@@
 
+\paragraph{Matrix limit.}
 Finally, we derive the matrix limit $\Gi(z)$.
-Inserting the approximate identity \eqref{approx m12 add} into equations \eqref{1self_Gii} and \eqref{2.5self_Gmu}, we get that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
-$$G_{ii}(z)=(-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1)^{-1},\quad G_{\mu\mu}=-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z)+\oo(1),\quad G_{\nu\nu}=-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)+\oo(1),$$
-with overwhelming probability.
-These explain the diagonal entries of $\Gi$ in equation \eqref{defn_piw}.
-For the off-diagonal entries, they are close to zero due to concentration.
-For example, for $i\ne j\in \cal I_1$, by Schur complement formula in equation (\ref{resolvent3}), we have
-$$G_{ij}=-G_{ii}\Big({\lambda_i}{n^{-1/2}}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j} + {n^{-1/2}}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j} \Big).$$
-Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}$ are both close to zero.
-The other off-diagonal entries can be bounded in the same way.
-The bound on the off-diagonal entries will be proved rigorously in Lemma \ref{Z_lemma}.
+Applying our solution for $m_1(z)$ and $m_2(z)$ into equation \eqref{1self_Gii}, we get that for $i$ in $\cal I_0$,
+$G_{i, i}(z) = (-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1}$.
+Similarly, for $\mu$ in $\cal I_1$, we have that $G_{\mu, \mu}(z) = -\frac{n_1 + n_2}{n_1}a_{1}(z)+\oo(1)$, and for $\nu$ in $\cal I_2$, we have that $G_{\nu, \nu}(z) = -\frac{n_1 + n_2}{n_2}a_{2}(z)+\oo(1)$.
+Hence we have derived the diagonal entries of $\Gi(z)$.
+In Lemma \ref{Z_lemma}, we show that the off-diagonal entries are close to zero.
+For example, for $i\ne j\in \cal I_1$, by Schur complement, we have that
+$$G_{i,j}(z) = -G_{i,i}(z)\cdot {n^{-1/2}}\Big({\lambda_i}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu, j}(z) + \sum_{\mu \in \cal I_2} Z^{(2)}_{\mu, i} G^{(i)}_{\mu, j}(z) \Big).$$
+Using standard concentration inequalities, we show that $\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu, j}(z)$ and $\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu, j}(z)$ are both close to zero.
+The other off-diagonal entries are bounded similarly.
+%The bound on the off-diagonal entries will be proved rigorously .
 
 \paragraph{Notations.}
-We say an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
+We introduce several notations for the proof of Theorem \ref{thm_main_RMT}.
+We say that an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
 Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
-We frequently use the following notion of stochastic domination, which was first introduced in \cite{Average_fluc} and subsequently used in many works on random matrix theory.
-%It greatly simplifies the presentation of the results and their proofs by systematizing statements of the form ``$\xi$ is bounded by $\zeta$ with overwhelming probability up to a small power of $n$".
+The following notion of stochastic domination, which was first introduced in \cite{Average_fluc}, is commonly used in the study of random matrices.
 
 \begin{definition}[Stochastic domination]\label{stoch_domination}
-%\begin{itemize}
-%\item[(i)]
 Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
 \HZ{what is $n$-dependent rv?}
-We say $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any (small) constant $\e>0$ and (large) constant $D>0$
-\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}, \]
-for large enough $n\ge n_0(\e, D)$.
-Moreover, if $\xi$ and $\zeta$ depend on a parameter $u$, then we say $\xi$ is stochastically dominated by $\zeta$ uniformly in $u\in \cal U$,  if for any constants $\e,D>0$,
-\[\sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}, \]
-for large enough $n\ge n_0(\e, D)$.
-%\item[(ii)]
-%\end{itemize}
-%(i) Let
-%\[\xi=\left(\xi^{(n)}(u):n\in\bbN, u\in U^{(n)}\right),\hskip 10pt \zeta=\left(\zeta^{(n)}(u):n\in\bbN, u\in U^{(n)}\right)\]
-%be two families of nonnegative random variables, where $U^{(n)}$ is a possibly $n$-dependent parameter set.
-We say $\xi$ is stochastically dominated by $\zeta$, uniformly in $u$, if for any fixed (small) $\epsilon>0$ and (large) $D>0$,
-%\[\sup_{u\in U^{(n)}}\bbP\left[\xi^{(n)}(u)>n^\epsilon\zeta^{(n)}(u)\right]\le n^{-D}\]
-%for large enough $n\ge n_0(\epsilon, D)$, and we shall use the notation $\xi\prec\zeta$.
-%%Throughout this paper, the stochastic domination will always be uniform in all parameters that are not explicitly fixed (such as matrix indices, and $z$ that takes values in some compact set).
-%%Note that $N_0(\epsilon, D)$ may depend on quantities that are explicitly constant, such as $\tau$ in Assumption \ref{assm_big1} and equation \eqref{assm_gap}.
-%If for some complex family $\xi$ we have $|\xi|\prec\zeta$, then we will also write $\xi \prec \zeta$ or $\xi=\OO_\prec(\zeta)$.
-%\item[(ii)]
-%(ii) We extend the definition of $\OO_\prec(\cdot)$ to matrices in the weak operator sense as follows.
-Let $A$ be a family of random matrices and $\zeta$ be a family of nonnegative random variables.
-Then $A=O_\prec(\zeta)$ means that $\left|\left\langle\mathbf v, A\mathbf w\right\rangle\right|\prec\zeta \| \mathbf v\|_2 \|\mathbf w\|_2 $ uniformly in any deterministic vectors $\mathbf v$ and $\mathbf w$.
-Here and throughout the following, whenever we say ``uniformly in any deterministic vectors", we mean that ``uniformly in any deterministic vectors belonging to a set of cardinality $N^{\OO(1)}$".
-%\item[(iv)]
-%\end{itemize}
+We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for any $n > n_0(\e, D)$,
+\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
+In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if % for any constants $\e, D>0$,
+\[ \sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}. \]
 \end{definition}
 
-For example, we say that $\xi$ is stochastically dominated by $\zeta$ with overwhelming probability if $\zeta$ is greater than $\xi$ up to a small power of $n^{\e}$.
-Since we allow an $n^\e$ factor in the definition of stochastic domination, we have the seemingly strange inequality $(\log n)^C\prec 1$ for any constant $C>0$.
-As another example, given a random variable $\xi$, if its moments exist up to any order, then we have $|\xi|\prec 1$. In fact, for any constants $\e, D>0$, by Markov's inequality we have
-$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D},$$
-if we choose $k$ large enough such that $k\e>D$. As a special case, we have $|\xi|\prec 1$ for a Gaussian random variable $\xi$ with unit variance.
-
-%\HZ{Why is this below part of the def. of stochastic domination?}
+%For example, we say that $\xi$ is stochastically dominated by $\zeta$ with overwhelming probability if $\zeta$ is greater than $\xi$ up to a small power of $n^{\e}$.
+We make several remarks.
+First, since we allow an $n^\e$ factor in stochastic domination, we can ignore log factors without loss of generality since $(\log n)^C\prec 1$ for any constant $C>0$.
+Second, given a random variable $\xi$ whose moments exist up to any order, we have that $|\xi|\prec 1$.
+This is because by Markov's inequality, let $k$ be greater than $D/ \e$, then we have that
+$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D}.$$
+This implies that a Gaussian random variable $\xi$ with unit variance satisfies that $|\xi|\prec 1$.
 

### 2020-09-27 arxiv/proof_gaussian_case.tex
sec B wip

@@
 
-In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below.
+%In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below.
 %\ref{sec_prelim}.
- Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.
+%Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.
 
-%We summarize our basic assumptions here for future reference.
-%Note that this assumption is in accordance with the assumptions of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}, except that we rescale the entries of $Z^{(1)}$ and $Z^{(2)}$ by $n^{-1/2}$.
-%and allow $\rho_1$ to be smaller than 1.
-\begin{assumption}\label{assm_big1}
-As in Section \todo{add reference}, we consider random matrices $X^{(1)}=Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}=Z^{(2)}\Sigma_2^{1/2}$, where $Z^{(1)}$ and $Z^{(2)}$ are independent $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
+Next, we introduce the bounded support assumption for a random matrix.
+We say that a random matrix $Z \in\real^{n \times p}$ satisfies the {\it{bounded support condition}} with $q$ or $Z$ has support $q$ if
+\begin{equation}
+	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i, j} \vert \prec q. \label{eq_support}
+\end{equation}
+As shown in the example above, if the entries of $Z$ have finite moments up to any order, then $Z$ has bounded support $1$.
+More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that \HZ{I don't fully get the equation below}
+\be\label{Ptrunc}
+	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) \le \OO((\log n)^{-\varphi}).\ee
+In other words, $Z$ has bounded support $q=n^{\frac{2}{\varphi}}$ with high probability.
+%This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}. %This fact will be used in the proof of Corollary \ref{main_cor} below.
+%The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
+%\begin{assumption}%\label{assm_big1}
+%As in Section \todo{add reference}, we consider random matrices $X^{(1)}=Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}=Z^{(2)}\Sigma_2^{1/2}$, where $Z^{(1)}$ and $Z^{(2)}$ are independent $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
 entries of zero mean and unit variance.
@@
 %\HZ{We have defined $\rho_1,\rho_2$ already in sec 2. Consider using ``Recall that $\rho_1 =, \rho_2 =$.''}
-\be\label{assm2}
-0\le \rho_1 \le \tau^{-1}, \quad 1+\tau \le \rho_{2} \le \tau^{-1}.
-\ee
-Recall that the singular value decomposition of $M = \Sig_1^{1/2} \Sig_2^{-1/2}$ is $U \Lambda V^{\top}$. We assume that
-\begin{equation}\label{assm32}
-\tau \le \lambda_p \le \lambda_1 \le \tau^{-1} .%, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-Finally, recalling the notations in equation \eqref{labelZ}, we assume that $Z^{(1)}$ and $Z^{(2)}$ satisfy
-\begin{equation}
-n^{-1/2}\max_{i\in \cal I_0,\mu \in \cal I_1}\vert Z^{(1)}_{\mu i}\vert \prec q,\quad n^{-1/2}\max_{i\in \cal I_0,\nu \in \cal I_2}\vert Z^{(2)}_{\nu i}\vert \prec q, \label{eq_support}
-\end{equation}
-for some deterministic parameter $q$ satisfying $ n^{-{1}/{2}} \leq q \leq n^{- \tau} $ for a small constant $\tau>0$.
+%\be\label{assm2}
+%0\le \rho_1 \le \tau^{-1}, \quad 1+\tau \le \rho_{2} \le \tau^{-1}.
+%\ee
+%Recall that the singular value decomposition of $M = \Sig_1^{1/2} \Sig_2^{-1/2}$ is $U \Lambda V^{\top}$. We assume that
+%\begin{equation}\label{assm32}
+%\tau \le \lambda_p \le \lambda_1 \le \tau^{-1} .%, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
+%\end{equation}
+%Finally, recalling the notations in equation \eqref{labelZ}, we assume that $Z^{(1)}$ and $Z^{(2)}$ satisfy
+%\begin{equation}
+%n^{-1/2}\max_{i\in \cal I_0,\mu \in \cal I_1}\vert Z^{(1)}_{\mu i}\vert \prec q,\quad n^{-1/2}\max_{i\in \cal I_0,\nu \in \cal I_2}\vert Z^{(2)}_{\nu i}\vert \prec q, \label{eq_support}
+%\end{equation}
+%for some deterministic parameter $q$ satisfying $ n^{-{1}/{2}} \leq q \leq n^{- \tau} $ for a small constant $\tau>0$.
 %Here we recall the notations in \eqref{labelZ}.
  %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-\end{assumption}
+%\end{assumption}
 %\HZ{This is restating what's stated above again.
@@
 
-Whenever the estimates in equation \eqref{eq_support} hold, we say $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ satisfy the {\it{bounded support condition}} with $q$, or $n^{-1/2}Z^{(1)}$ and $n^{-1/2}Z^{(2)}$ have support $q$.
 %\begin{definition}\label{defn_support}
@@
 %\todo{Talk about the Gaussian case and Bernoulli case.}
-As shown in the example above, if the entries of $Z^{(1)}$ have finite moments up to any order, %as in equation \eqref{assmAhigh},
-then $n^{-1/2}Z^{(1)}$ has bounded support $n^{-1/2}$.
-More generally, if the entries of $Z^{(1)}$ have finite $\varphi$-th moment as in \eqref{assmAhigh}, then using Markov's inequality and a simple union bound we get that
-\be\label{Ptrunc}
-\P\left(n^{-1/2}\max_{i,\mu}|(Z^{(1)})_{\mu i}|\ge (\log n) n^{-\frac{\varphi-4}{2\varphi}}\right)=\OO((\log n)^{-\varphi}).\ee
-In other words, $n^{-1/2}Z^{(1)}$ has bounded support $q=n^{-\frac{\varphi-4}{2\varphi}}$ on a event with probability $1-\oo(1)$.
-This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}.
-%This fact will be used in the proof of Corollary \ref{main_cor} below.
-The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
+
 %\end{example}

### 2020-09-27 arxiv/setup.tex
sec B wip

@@
 	Let $\varphi > 4$ be a fixed value.
+	Let $\tau > 1$ be a small enough constant.
 	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
@@
 	\begin{enumerate}
-		\item Bounded moments: for every entry of $Z$, we assume that its $c$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
+		\item For every entry of $Z$, we assume that its $c$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
 			\begin{align}\label{assmAhigh}
@@
 			\end{align}
-		\item Bounded singular values: the singular values of $\Sigma$ are bounded within a fixed range, that is, there exists two fixed values $C_{\max} > C_{\min} > 0$ such that all of $\Sigma$'s singular values are bounded within $C_{\min}$ and $C_{\max}$.
+		\item The sample size $n$ grows to infinity proportionally with the dimension $p$, i.e. $n / p \rightarrow \rho \in (0, 1/\tau)$ as $p$ goes infinity.
 	\end{enumerate}

### 2020-09-27 arxiv/proof_gaussian_case.tex
finish pass over B

@@
 
+The following fact collects several basic properties that are often used in the proof.
+\begin{fact}[Lemma 3.2 in \cite{isotropic}]\label{lem_stodomin}
+Let $\xi$ and $\zeta$ be two families of nonnegative random variables depending on some parameters $u\in \cal U$ or $v\in \cal V$.
+\begin{itemize}
+\item[(i)] Suppose that $\xi (u,v)\prec \zeta(u,v)$ uniformly in $u\in \cal U$ and $v\in \cal V$.
+If $|\cal V|\le n^C$ for some constant $C>0$, then $\sum_{v\in \cal V} \xi(u,v) \prec \sum_{v\in \cal V} \zeta(u,v)$ uniformly in $u$.
+
+\item[(ii)] If $\xi_1 (u)\prec \zeta_1(u)$ and $\xi_2 (u)\prec  \zeta_2(u)$ uniformly in $u\in \cal U$, then $\xi_1(u)\xi_2(u) \prec \zeta_1(u) \zeta_2(u)$ uniformly in $u\in \cal U$.
+
+\item[(iii)] Suppose that $\Psi(u)\ge n^{-C}$ is a family of deterministic parameters, and $\xi(u)$ satisfies $\mathbb E\xi(u)^2 \le n^C$.
+If $\xi(u)\prec \Psi(u)$ uniformly in $u$, then we also have $\mathbb E\xi(u) \prec \Psi(u)$ uniformly in $u$.
+\end{itemize}
+\end{fact}
+
 %In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below.

### 2020-09-27 arxiv/proof_gaussian_case.tex
revise

@@
 Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
-\HZ{what is $n$-dependent rv?}
+\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents.
+Furthermore, the random matrix entries can also depend on $n$ if we want.
+One important example is Bernoulli random variable with sparsity $p=n^{-\theta}$.
+Furthermore, this also includes the random variables that do not depend on $n$ as a special case.}]
 We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for any $n > n_0(\e, D)$,
@@
 As shown in the example above, if the entries of $Z$ have finite moments up to any order, then $Z$ has bounded support $1$.
-More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that \HZ{I don't fully get the equation below}
-\be\label{Ptrunc}
-	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) \le \OO((\log n)^{-\varphi}).\ee
+More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that %\HZ{I don't fully get the equation below}
+\begin{align}
+	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) &\le \sum_{i=1}^n \sum_{j=1}^p \P\left(|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right)  \nonumber\\
+	&\le \sum_{i=1}^n \sum_{j=1}^p \frac{C}{\left[(\log n) n^{\frac{2}{\varphi}}\right]^\varphi} = \OO((\log n)^{-\varphi}).\label{Ptrunc}
+	\end{align}
 In other words, $Z$ has bounded support $q=n^{\frac{2}{\varphi}}$ with high probability.

### 2020-09-27 arxiv/diff_cov.tex
sec B wip
wip

@@
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.
-We will develop the key technical results in this section, and describe their implications in the next section.
 
@@
 	Suppose that $X_1$ and $X_2$ are both random matrices that satisfy Assumption \ref{assume_rm}.
+	Assume further that: a) the singular values of $M$ are all greater than $\tau$ and less than $1/\tau$; b) the sample size of task two is greater than $(1 + \tau) p$.
 	With high probability over the randomness of $X_1$ and $X_2$, we have the following limits:
@@
 When $X_1=0$, it is not hard to solve $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ from equation \eqref{eq_a12extra}, and our result reduces to the case of a single sample covariance matrix.
-For the single-task case of a multivariate Gaussian random matrix, the result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For a multivariate Gaussian random matrix, the result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
 For a non-Gaussian random matrix, the result can be obtained using the Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
@@
 Since the proof is similar to the same covariates setting, we describe the key differences and omit the rest of the details.
-First, we will rescale $X_1$ by $A_1 / A_2$ before appling Theorem \ref{thm_main_RMT}.
+First, we will rescale $X_1$ by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
 Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.

### 2020-09-27 arxiv/examples.tex
wip

@@
 %Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-We illustrate our main results in simplified settings.
-We explain several empirical phenomena that have often been observed when hard parameter sharing approaches are used.
-
+We discuss several examples to illustrate our results.
+Through these examples, we provide generalization bounds of hard parameter sharing estimators that depend explicitly on the sample sizes and the covariance matrices of the tasks.
+We use our generalization bounds to interpret several empirical phenomena that arises from applying hard parameter sharing in practice.
+For our examples, we assume that a random-effects model holds.
+We assume every $\beta_i$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
 %	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
@@
 
+\subsection{Sample Efficiency}
+
+We begin by considering a setting where the feature covariates are the same across all tasks but their labels are different.
+In the random-effects model, we assume that every $\beta_i$ is equal to a shared component $\beta_0$ plus a task-specific component.
+Suppose that the entries of $\beta_0$ are sampled i.i.d. from an isotropic Gaussian distribution.
+Suppose further that $\beta_i$ is equal to $\beta_0$ plus a random Gaussian vector whose coordinates all have mean zero and variance $p^{-1} d^2 / 2$.
+Thus, for any two $\beta_i$ and $\beta_j$, their distance is roughly $d^2$.
+Using our results, we show that the prediction loss of the hard parameter sharing estimator is as follows.
+
+\begin{corollary}[Derived from Theorem \ref{thm_many_tasks}]\label{prop_same_cov}
+	In the setting described above, for any task $i$, the prediction loss of $\hat{\beta}_i^{\MTL}$ satisfies that
+	\[ L(\hat{\beta}_i^{\MTL}). \]
+\end{corollary}
+
 \subsection{Sample Imbalance}
 
-	Imagine that we have two tasks and the covariates of both tasks have isotropic covariance matrices.
+The above setting assumes that the feature covariates are the same across all tasks.
+Hence, the sample sizes are also the same among all tasks.
+Next, we assume that the feature covariates are different and consider what happens the sample sizes are different for different tasks.
+We consider a two-task case where both tasks have isotropic covariance matrices.
 %	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
 	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
-	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
-	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
-	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
-
+%	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
+%	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
+%	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
+%	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
 %\begin{example}[Varying model distance]
 %\end{example}
-
-Using Theorem \ref{thm_main_RMT}, %our techniques described later in Section \ref{sec_general}, 
-we can derive the limiting prediction loss of the hard parameter sharing estimator.
+Using Theorem \ref{thm_main_RMT}, we derive the prediction loss of the hard parameter sharing estimator.
 Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
 
-\begin{proposition}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
-	Assume that the isotropic setting described above holds, and that there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy that
+\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
+	In the setting described above, assume that there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy that
 	\be\label{choiceofpara0}
@@
 	\ee
-	Let $B, W_1, W_2$ be the global minimum of equation \eqref{eq_mtl}. Then with high probability, the prediction loss of the hard parameter sharing estimator for task two satisfies:
+	%Let $B, A_1, A_2$ be the global minimum of equation \eqref{eq_mtl}. Then
+	The prediction loss of the hard parameter sharing estimator for task two satisfies that
 	\begin{align}\label{cor_MTL_error}
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
-	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 )
+	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c_{\varphi}}\sigma^2 ).
 	 \end{align}
-	 for any constant $c\in (0,c_0)$.
-	 \iffalse
-	\begin{align*}
-		& \bigabs{ L(\hat{\beta}_2^{\MTL}) - \frac{\sigma^2}{\rho_1 + \rho_2 - 1} - (1 + \frac{6}{\rho_1} + \frac{1}{\rho_1^2})pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} } \\
-		\le & 	\frac{4}{\sqrt{\rho_1}}(1 + \frac{1}{\rho_1})	pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} + \oo(\sigma^2 + pd^2).
-%	 \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4  +\oo(\sigma^2 + pd^2)  \le \\
-%	 \le  \frac{\sigma^2}{\rho_1+\rho_2-1}+\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4 pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\oo(\sigma^2 + pd^2)
-	 \end{align*}
-	 \fi
-\end{proposition}
+\end{corollary}
 
@@
 
-In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
+%In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
 %More generally, such results are still applicable when all task data are being added simultaneously.
-On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
-For such settings, we have also observed that adding more labeled data from one task does not always help.
-Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
+%On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
+%For such settings, we have also observed that adding more labeled data from one task does not always help.
+%Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
 %On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
@@
 
-We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-There are several unexplained observations near $y = 0$ caused by $\nu$.
-The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
+%We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+%There are several unexplained observations near $y = 0$ caused by $\nu$.
+%The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
 
 \subsection{Covariate Shift} \label{sec_covshift}
-So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-In general, the covariance matrices of the two tasks may be different such as in text classification.
-In this part, we consider what happens when $\Sigma_1 \neq \Sigma_2$.
-We show that when $n_1 / n_2$ is large, MTL with covariate shift can be suboptimal compared to MTL without covariate shift.
+%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+%In general, the covariance matrices of the two tasks may be different such as in text classification.
 
-%\noindent\textit{Example.}
-
-\begin{example}
-	We measure covariate shift by the transfer matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$. %similar to Theorem \ref{thm_main_informal}.
-	We assume that the two tasks have the same ground truth model parameters, that is, $\beta_1 = \beta_2$.
-	We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-	Hence, $\lambda$ measures the severity of the covariate shift.
-	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-	\end{example}
+In our final example, we consider what happens when the covariance matrices are also different between different tasks, which are often called ``covariate shift''.
+Our results apply to arbitrary ``covariate shift'' and we consider a simple setting of two tasks.
+As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
+To illustrate our result, we assume that the first half of the singular values of $\Sigma^{1/2}\Sigma^{-1/2}$ are all equal to a parameter $\lambda$ and the rest are all equal to one.
+Our results imply that the prediction loss of the hard parameter sharing estimator is given as follows.
+%We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+%Hence, $\lambda$ measures the severity of the covariate shift.
+%	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
+%	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
+%	\end{example}
 
 %By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-We compare different choices of $M$ that belong to the following bounded set.
-Let $\lambda_i$ be the $i$-th singular value of $M$.
-Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-{\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.}.
-\end{align*}}
+%We compare different choices of $M$ that belong to the following bounded set.
+%Let $\lambda_i$ be the $i$-th singular value of $M$.
+%Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
+%{\begin{align*}
+%		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.}.
+%\end{align*}}
 %	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-\begin{proposition}[Covariate shift]\label{prop_covariate}
-	For the setting of the example above, assume that $\beta_1 = \beta_2$, $\rho_1$ and $\rho_2$ are both greater than one.
-	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-	We have that
-		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{proposition}
+\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{prop_covariate}
+	In the setting described above, assume further that a random-effects model holds for both tasks.
+	The prediction loss of $\hat{\beta}_2^{\MTL}$ for task two satisfies that
+	\begin{align*}
+		L(\hat{\beta}_2^{\MTL})
+	\end{align*}
+%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
+%	We have that
+%		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
+\end{corollary}
 

### 2020-09-27 arxiv/setup.tex
wip

@@
 \subsection{Notations}
-We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$. 
-We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)\ge 1- \oo(1)$, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
+We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
+We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)$ goes to $1$ as $p$ goes to infinity.
+%, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
 For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
@@
 entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	We assume that $\Sigma$ and $Z$ satisfy the following (standard) conditions, respectively.
+	We assume the following standard conditions.
 	\begin{enumerate}
-		\item For every entry of $Z$, we assume that its $c$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
+		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
 			\begin{align}\label{assmAhigh}
@@
 	\begin{enumerate}
-		\item The sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
-		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-c})$, cf. Theorem 2.4 in \citet{isotropic}.
-		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c}$, cf.
+		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
+		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-c_{\varphi}})$, cf. Theorem 2.4 in \citet{isotropic}.
+		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf.
 \citet[Theorem 2.10]{isotropic} and \citet[Lemma 3.12]{DY}.

### 2020-09-28 arxiv/examples.tex
revise

@@
 In the random-effects model, we assume that every $\beta_i$ is equal to a shared component $\beta_0$ plus a task-specific component.
-Suppose that the entries of $\beta_0$ are sampled i.i.d. from an isotropic Gaussian distribution.
+Suppose that the entries of $\beta_0$ are sampled i.i.d. from an isotropic Gaussian distribution of mean zero and variance $p^{-1}\kappa^2$.
 Suppose further that $\beta_i$ is equal to $\beta_0$ plus a random Gaussian vector whose coordinates all have mean zero and variance $p^{-1} d^2 / 2$.
@@
 \begin{corollary}[Derived from Theorem \ref{thm_many_tasks}]\label{prop_same_cov}
-	In the setting described above, for any task $i$, the prediction loss of $\hat{\beta}_i^{\MTL}$ satisfies that
-	\[ L(\hat{\beta}_i^{\MTL}). \]
+	In the setting described above, the total prediction loss of the $t$ tasks satisfies that
+	\begin{align*} 
+	 \sum_{i=1}^t L(\hat{\beta}_i^{\MTL})&= (t-r) \kappa^2 \cdot \frac{\tr\Sigma}{p}  + \sigma^2 \cdot \frac{r}{\rho-1} +\OO\left( p^{-c_\infty} \cdot\frac{\rho t(\kappa^2 + d^2) \|\Sigma\|}{(\sqrt{\rho}-1)^2 \kappa^2  \|\Sigma\| + \sigma^2}   \left( t \kappa^2 \|\Sigma \| + \frac{\sigma^2 r}{\rho-1} \right)  \right) .
+	 %& = \sum_{i=r+1}^t \lambda_i^2 (\Sigma^{1/2} B^{\star}) + \sigma^2 \frac{r}{\rho-1} +\OO\left(  p^{-c_\infty} \frac{t(\kappa^2 + d^2)\cdot (p^{-1}\tr \Sigma)}{(\sqrt{\rho}-1)^2 \kappa^2 \cdot (p^{-1}\tr \Sigma) + \sigma^2}   \left( t \kappa^2 \frac{\tr \Sigma}{p} + \frac{\sigma^2 r}{\rho-1} \right) \right) \\
+%	 &= (t-r) \kappa^2 \cdot \frac{\tr\Sigma}{p}  + \sigma^2 \cdot \frac{r}{\rho-1} \\
+%	 &+\OO\left( p^{-c_\infty}t(\kappa^2+d^2) \cdot p^{-1/2} \|\Sigma\|_F + p^{-c_\infty} \frac{t(\kappa^2 + d^2)\cdot (p^{-1}\tr \Sigma)}{(\sqrt{\rho}-1)^2 \kappa^2 \cdot (p^{-1}\tr \Sigma) + \sigma^2}   \left( t \kappa^2 \frac{\tr \Sigma}{p} + \frac{\sigma^2 r}{\rho-1} \right)  \right) .
+	\end{align*}
+%and $\lambda_{r+1} (\Sigma^{1/2} B^{\star}) \ge \cdots\ge  \lambda_{t} (\Sigma^{1/2} B^{\star})$ denote the smallest $(t-r)$ singular values of $\Sigma^{1/2} B^{\star}$.
 \end{corollary}
+On the other hand, the total STL predication loss is 
+\begin{align*}
+ \sum_{i=1}^t L(\hat{\beta}_i^{\STL}) =\sigma^2\cdot \frac{t}{ \rho-1}  +\OO(p^{-c_\infty}\cdot t \sigma^2 ).
+	 \end{align*}
 

### 2020-09-30 arxiv/proof_gaussian_case.tex
revise

@@
 Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
-\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents.
+%\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents.
 Furthermore, the random matrix entries can also depend on $n$ if we want.

### 2020-09-30 arxiv/examples.tex
revise

@@
 \begin{corollary}[Derived from Theorem \ref{thm_many_tasks}]\label{prop_same_cov}
-	In the setting described above, the total prediction loss of the $t$ tasks satisfies that
+	In the setting described above, if the sample size $n$ is greater than $(1 + \tau) p$, then the total prediction loss of the $t$ tasks satisfies that
 	\begin{align*} 
@@
 \begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
-	In the setting described above, assume that there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy that
+	In the setting described above, assume further that a) the sample size $n_2$ of task two is greater than $(1 + \tau) p$, and b) there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy
 	\be\label{choiceofpara0}
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
-	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c_{\varphi}}\sigma^2 ).
+	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 ),
 	 \end{align}
+	 for any constant $c\in (0,c_0)$.
 \end{corollary}

### 2020-09-30 arxiv/proof_examples.tex
revise

@@
  \begin{align}
-		g(A) \define  \sum_{i=1}^2 . \label{eq_mtl_A12}
+		 g(A) \define & \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\hat \Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\hat \Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+		 + & \left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)+ \left(X^{(2)}\hat \Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} + A X^{(2)}\hat \Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2,
+		\label{eq_mtl_A12}
 	\end{align}
+	where we denote
+	$$\hat \Sigma:= A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
+\begin{align*}	
+&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2} \\
+&= \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
+& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\hat \Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon_1} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
+&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\hat \Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)}}  +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  (X^{(2)})^\top X^{(2)}\hat \Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
+		&= \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
+		&+ \sigma^2\tr\left[ \left(A^2 X^{(1)}\hat \Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\right] +\sigma^2\tr\left[ \left(X^{(2)}\hat \Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
+&+ 2 A^2 \sigma^2 \tr\left[ \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
+		& = \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
+\end{align*}
+Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation.
+%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}$.
+ \begin{claim}\label{claim_largedev1}
+ In the setting of Proposition \ref{cor_MTL_loss}, we have that 
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\|\beta_1\|^2 +\|\beta_2\|^2 \right). $$
+ \end{claim}
+ \begin{proof}
+ \todo{add proof}
+ \end{proof}
+
+For the random-effects model, we can further take the partial expectation over $\beta_1$ and $\beta_2$:
+
+\iffalse
+
+ \begin{claim}\label{claim_largedev2}
+ In the setting of Proposition \ref{cor_MTL_loss}, we have that 
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\|\beta_1\|^2 +\|\beta_2\|^2 \right). $$
+ \end{claim}
+ \begin{proof}
+ \todo{add proof}
+ \end{proof}
 
@@
 \todo{next derive the prediction loss}
- \cob
-
- \begin{claim}
-	In the setting described above, we have that
-	\be\label{approxvalid}
-		g(v)=  \left[\val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).
-	\ee
-\end{claim}
-\begin{proof}
-	We use the fact that our random vectors have i.i.d. entries.
-%Before doing that, we first need to fix the setting for the following discussions, because we want to keep track of the error rate carefully instead of obtaining an asymptotic result only.
-	Recall that $Y_i = X_i\beta_i + \varepsilon_i$ and $\wt Y_i = \wt X_i\beta_i + \wt\varepsilon_i$, $i=1,2$, all satisfy Assumption \ref{assm_secA2}. Then we rewrite \eqref{eq_mtl_2tasktilde} as
-$$	g( v) = \sum_{i=1}^2\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 , \quad \wt\beta:=\hat B w_i-\beta_i.$$
-Since $ \wt X_i\wt\beta$ and $ \wt \e_i$ are independent random vectors with i.i.d.
-centered entries, we can use the concentration result, Lemma \ref{largedeviation}, to get that for any constant $\e>0$,
-\begin{align*}
-\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 -  \exarg{\wt X_i,\wt{\e}_i} {\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2} \right| & =\left|\left\| \wt X_i\wt\beta_i  - \wt \e_i\right\|^2 - N_i (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2) \right| \\
-&\le N_i^{1/2+\e} (\wt\beta_i^\top \Sigma_i \wt\beta_i + \sigma_i^2),
-\end{align*}
-with high probability. Thus we obtain that
-$$g(v)= \left[\sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_i - \beta_i) \right\|^2 + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right),$$
-where we also used $N_i\ge p^{-1+\e_0}$. Inserting \eqref{hatB} into the above expression and using
- again the concentration result, Lemma \ref{largedeviation}, we get that
-$$ \sum_{i=1}^2 N_i\left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 = \val(v)\cdot \left( 1+\OO(p^{-1/2+\e})\right)$$
-with high probability.
-%-----old-------
-%Suppose that the entries of $\e_1$ and $\e_2$ have variance $\sigma^2$.  Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
-%\begin{align}
-%		&\val(\hat{B}; w_1, w_2):= \exarg{\varepsilon_1,\e_2} \sum_{i=1}^2 \left\|\Sigma_i^{1/2}( \hat B w_1 - \beta_i) \right\|^2 \\
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_1} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\Sigma_2}. \label{eq_val_mtl}
-%\end{align}
-%\nc
-%------------------
-Thus we conclude the proof.
-\end{proof}
-
-\nc
 
@@
 \end{proof}
+
+\fi
 

### 2020-09-30 arxiv/examples.tex
revise

@@
 \begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
-	In the setting described above, assume further that a) the sample size $n_2$ of task two is greater than $(1 + \tau) p$, and b) there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy
+	In the setting described above, assume further that a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy
 	\be\label{choiceofpara0}
-		p^{ c_0} \le \frac{p\kappa^2}{\sigma^2 }  \le p^{1-c_0},\quad  \frac{pd^2}{\sigma^2}=\OO(1).
+		p^{ c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{1-c_0},\quad  \frac{d^2}{\sigma^2}=\OO(1).
 	\ee

### 2020-09-30 arxiv/proof_examples.tex
revise

@@
 \subsection{The Random-Effects Model}\label{app_iso_cov}
-We now give the proof of Proposition \ref{cor_MTL_loss}.
+
+\paragraph{Proofs for two tasks.}  We now give the proof of Proposition \ref{cor_MTL_loss}.
 As in the proof of Theorem \ref{thm_many_tasks}, we first derive a bias-variance decomposition of the prediction loss $L(\hat \eta_2^{\MTL})$.
@@
 &+ 2 A^2 \sigma^2 \tr\left[ \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
-		& = \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
+		& = \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
 \end{align*}
+For the random-effects model, we can further take the partial expectation over $\beta_1$ and $\beta_2$: 
+\begin{align*}	
+&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \\
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]\\
+&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p),
+\end{align*}
+where we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d. random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$.
+
 Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation.
@@
  In the setting of Proposition \ref{cor_MTL_loss}, we have that 
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\|\beta_1\|^2 +\|\beta_2\|^2 \right). $$
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right). $$
  \end{claim}
@@
 
-For the random-effects model, we can further take the partial expectation over $\beta_1$ and $\beta_2$:
+Then we calculate the predication loss ...
 

### 2020-09-30 arxiv/proof_examples.tex
revise

@@
 
-\paragraph{Proofs for two tasks.}  We now give the proof of Proposition \ref{cor_MTL_loss}.
-As in the proof of Theorem \ref{thm_many_tasks}, we first derive a bias-variance decomposition of the prediction loss $L(\hat \eta_2^{\MTL})$.
-Then we can calculate the bias term and the variance term using Theorem \ref{thm_main_RMT}.
+\subsubsection{Proof for Sample Imbalance}  
+We now give the proof of Proposition \ref{cor_MTL_loss}. As in the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following steps: 
+\begin{itemize}
+\item simplifying the optimization objective using concentration estimates;
 
+\item finding the minimizer of the optimization objective;
+
+\item deriving a bias-variance decomposition of the prediction loss $L(\hat \beta_2^{\MTL})$;
+
+\item calculating the bias term and the variance term using Theorem \ref{thm_main_RMT}. 
+\end{itemize}
+
+\paragraph{Simplifying the optimization objective.} 
 Under the two-task setting of Corollary \ref{cor_MTL_loss}, the optimization objective \eqref{eq_mtl} becomes
 	\begin{align}
-		f(A, B) =   \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2+ \bignorm{X^{(2)} B A_2 - Y^{(2)}}^2, \label{eq_mtl_2task_cov}
+		f(A_1,A_2, B) =   \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2+ \bignorm{X^{(2)} B A_2 - Y^{(2)}}^2, \label{eq_mtl_2task_cov}
 	\end{align}
@@
 &=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]\\
-&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p),
+&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p)\\
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p),
 \end{align*}
-where we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d. random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$.
+where in the first step we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d.
+random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
+\begin{align*}
+ &\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] \\
+ &=\tr\left[  \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} \left( \hat\Sigma- A^2 (X^{(1)})^\top X^{(1)} \right)^2\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}\left( \hat\Sigma- A^2 (X^{(1)})^\top X^{(1)} \right) \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] \\
+ &=\tr\left[  (X^{(1)})^\top X^{(1)}\right] - A^2\tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)}\right] = \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right] .
+\end{align*}
 
@@
 
-Then we calculate the predication loss ...
-
-\iffalse
-
- \begin{claim}\label{claim_largedev2}
- In the setting of Proposition \ref{cor_MTL_loss}, we have that 
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\|\beta_1\|^2 +\|\beta_2\|^2 \right). $$
- \end{claim}
- \begin{proof}
- \todo{add proof}
- \end{proof}
-
-\cor
-%Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
-%Using the local optimality condition of $B$, we obtain that
-%\begin{align*}
-%	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
-%	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
-%	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-%\end{align*}
-Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
-\begin{align}
-	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
-	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
-			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
-\end{align}
-Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
-equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
-%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Comparing the above to single-task learning, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-
-% \todo{derive the test loss} Expectation was given in \eqref{eq_bias_2task} and \eqref{eq_var_2task}.
- \nc
-
-Plugging $Y^{(1)}$ and $Y^{(2)}$ in \eqref{model_YvsX} into \eqref{eq_Bhat_2task}, we can rewrite that 
- \begin{align}
-		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
-\label{eq_Bhat_2task2} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
-\todo{next derive the prediction loss}
-
-% \todo{switch the $a_3$ and $a_4$}
-
-For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
-\begin{lemma}\label{prop_model_shift_tight}
-		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_2$ is a random vector that has i.i.d.
-entries with mean $0$, variance $\kappa^2$ and finite moments up to any order, and $(\beta_1-\beta_2)$ is a random vector that is independent of $\beta_2$ and has i.i.d.
-entries with mean $0$, variance $d^2$ and finite moments up to any order.
-Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in \eqref{defnpihat}.	Then we have with high probability,
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
-		\end{align*}
-		where $\Delta_{\vari}$ was defined in \eqref{Deltavarv}.
-\end{lemma}
-
-\begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
-The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
-We only describe the main difference in the following proof.
-
-For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
-entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
-Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
-\begin{align}
-&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2] \quad \text{w.h.p.},\label{anotherbeta}
-\end{align}
-where $\delta_{\bias}(v)$ was defined in \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
-Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
-\begin{align*}
-v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
-\end{align*}
-Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using Fact \eqref{lem_minv}, we obtain that
-\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
-where
-$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
-\be\label{replaceest}
-  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
-\ee
-Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
-In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
-\end{proof}
-
-\fi
-
-We show that for the isotropic model, the optimum of $\hat v$ is very close to 1.
+ \paragraph{Minimizer of the optimization objective.} We show that for the isotropic model, the optimum of $\hat v$ is very close to 1.
 This allows us to simplify the expression of $\te(\hat{\beta}_2^{\MTL})$ significantly.
@@
 %\end{proof}
+\end{proof}
+
+\paragraph{Calculating the prediction loss.} Then we calculate the predication loss ...
+
+ \begin{claim}\label{claim_largedev2}
+ In the setting of Proposition \ref{cor_MTL_loss}, we have that 
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\|\beta_1\|^2 +\|\beta_2\|^2 \right). $$
+ \end{claim}
+ \begin{proof}
+ \todo{add proof}
+ \end{proof}
+
+\cor
+%Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
+%Using the local optimality condition of $B$, we obtain that
+%\begin{align*}
+%	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
+%	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
+%	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+%\end{align*}
+Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
+\begin{align}
+	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
+	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
+			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
+\end{align}
+Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
+equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
+%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
+Comparing the above to single-task learning, that is,
+\begin{align}
+	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
+\end{align}
+we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
+In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
+Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
+
+% \todo{derive the test loss} Expectation was given in \eqref{eq_bias_2task} and \eqref{eq_var_2task}.
+ \nc
+
+Plugging $Y^{(1)}$ and $Y^{(2)}$ in \eqref{model_YvsX} into \eqref{eq_Bhat_2task}, we can rewrite that 
+ \begin{align}
+		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
+\label{eq_Bhat_2task2} %\\
+		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
+	\end{align}
+\todo{next derive the prediction loss}
 
@@
 %w.h.p. for some constant $\e>0$.
+
+% \todo{switch the $a_3$ and $a_4$}
+\paragraph{Calculating the variance and bias terms.} For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}.
+%as follows.
+\begin{lemma}\label{prop_model_shift_tight}
+		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+		$\beta_2$ is a random vector that has i.i.d.
+entries with mean $0$, variance $\kappa^2$ and finite moments up to any order, and $(\beta_1-\beta_2)$ is a random vector that is independent of $\beta_2$ and has i.i.d.
+entries with mean $0$, variance $d^2$ and finite moments up to any order.
+Denote
+		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in \eqref{defnpihat}.	Then we have with high probability,
+		\begin{align*}
+			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
+			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
+		\end{align*}
+		where $\Delta_{\vari}$ was defined in \eqref{Deltavarv}.
+\end{lemma}
+
+\begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
+The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
+We only describe the main difference in the following proof.
+
+For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
+entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
+Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
+\begin{align}
+&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2] \quad \text{w.h.p.},\label{anotherbeta}
+\end{align}
+where $\delta_{\bias}(v)$ was defined in \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
+Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
+\begin{align*}
+v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
+\end{align*}
+Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using Fact \eqref{lem_minv}, we obtain that
+\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
+where
+$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
+Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
+\be\label{replaceest}
+  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
+\ee
+Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
+In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
 \end{proof}
 
-%\subsection{Covariate Shift}\label{app_proof_33}
+\subsection{Covariate Shift}\label{app_proof_33}
 

### 2020-10-01 arxiv/proof_examples.tex
revise

@@
  \begin{claim}\label{claim_largedev1}
- In the setting of Proposition \ref{cor_MTL_loss}, we have that 
+ In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
 $$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right). $$
@@
 
- \paragraph{Minimizer of the optimization objective.} We show that for the isotropic model, the optimum of $\hat v$ is very close to 1.
-This allows us to simplify the expression of $\te(\hat{\beta}_2^{\MTL})$ significantly.
+ \paragraph{Minimizer of the optimization objective.} We show that for the isotropic model, the minimizer of $g(A)$, denoted by $\hat A$, is very close to 1 under the condition \eqref{choiceofpara0}.
+This will be used to calculate the predication loss $\te(\hat{\beta}_2^{\MTL})$ loss.
 %Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
 %Furthermore, under certain choice of parameters, we can simplify  
-More precisely, we have the following lemma.
-Later on, we will combine it with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.
+%More precisely, we have the following claim.
+%Later on, we will combine it with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.
 
-\begin{lemma}
-In the isotropic model, suppose for some constant $c_0>0$, 
-\be\label{choiceofpara}
-	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
+\begin{claim}\label{lem_hat_v}
+%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
+ In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
+%There exists a constant $C>0$ such that
+	\be\label{hatw_add1}|\hat A -1|\lesssim \frac{d^2}{\kappa^2} + \frac{\sigma^2}{\kappa^2} + p^{-c_\infty}. 
 	\ee
-where $\e_0$ is the constant as appeared in \eqref{approxvalid}. Then we have
-\begin{align}
-\te(\hat{\beta}_2^{\MTL})=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
-&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \quad \text{w.h.p.} \label{simple1}
-\end{align}
-for some constant $\e>0$.
-\end{lemma}
+	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
+\end{claim}
 
 \begin{proof}
-	Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
+\todo{revise the proof}	Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
 	%We define the function
@@
 For the first step, we will prove the following result.
-\begin{claim}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-There exists a constant $C>0$ such that
-	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{w.h.p.}\ee
-	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-\end{claim}
+
 \begin{proof}
@@
 	\end{align}
-\todo{next derive the prediction loss}
+
+\begin{lemma}
+In the isotropic model, suppose for some constant $c_0>0$, 
+\be\label{choiceofpara}
+	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
+\ee
+where $\e_0$ is the constant as appeared in \eqref{approxvalid}. Then we have
+\begin{align}
+\te(\hat{\beta}_2^{\MTL})=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
+&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \quad \text{w.h.p.} \label{simple1}
+\end{align}
+for some constant $\e>0$.
+\end{lemma}
+\begin{proof}
 
@@
 %w.h.p. for some constant $\e>0$.
+\end{proof}
 

### 2020-10-01 arxiv/proof_examples.tex
revise

@@
 For the random-effects model, we can further take the partial expectation over $\beta_1$ and $\beta_2$: 
-\begin{align*}	
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]\\
-&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p)\\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p),
-\end{align*}
+\begin{align}	
+&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \nonumber\\
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
+&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+\end{align}
 where in the first step we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d.
@@
 \begin{proof}
-\todo{revise the proof}	Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
-	%We define the function
-	\begin{align}
-		h(v) =& \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-		& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-		& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
-	\end{align}
-	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
-	Furthermore, the validation loss in \eqref{approxvalid} reduces to
-	\be\label{boundv-w}
-		g(v)=\left[N_2 h(v) + (N_1+N_2)\sigma^2\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)\quad \text{w.h.p.}
-	\ee
-	for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
-Let $\hat w$ be the minimizer of $h(v)$. Our proof consists of the following two steps.
-\squishlist
-	\item First, we show that $\hat{w}$ is close to $1$.
-	\item Second, with \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get \eqref{simple1}.
-\squishend
-%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
-For the first step, we will prove the following result.
+We abbreviate
+$$h(A):=\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} .$$
+We first find the minimizer of $h(A)$, denoted by $A^\star$.
 
-\begin{proof}
-To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof.
+%Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
+%	%We define the function
+%	\begin{align}
+%		h(v) =& \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+%		& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+%		& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
+%	\end{align}
+%	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
+%	Furthermore, the validation loss in \eqref{approxvalid} reduces to
+%	\be\label{boundv-w}
+%		g(v)=\left[N_2 h(v) + (N_1+N_2)\sigma^2\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)\quad \text{w.h.p.}
+%	\ee
+%	for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
+%Let $\hat w$ be the minimizer of $h(v)$. Our proof consists of the following two steps.
+%\squishlist
+%	\item First, we show that $\hat{w}$ is close to $1$.
+%	\item Second, with \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get \eqref{simple1}.
+%\squishend
+%%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
+%For the first step, we will prove the following result.
+
+%To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof. 
 First it is easy to observe that $h(w)< h(-w)$ for $w> 0$.
@@
 we conclude \eqref{hatw_add1}.
-\end{proof}
 
@@
 %for some small constant $c_0>0$. 
-Next we prove the following estimate on the optimizer $\hat v$: with high probability,
+Next we prove the following estimate on the optimizer $\hat A$: with high probability,
 %\begin{lemma}

### 2020-10-01 arxiv/proof_examples.tex
revise

@@
 \begin{proof}
-We abbreviate
-$$h(A):=\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} .$$
+Corresponding to \eqref{EgA}, we define the function
+\begin{align*}
+h(A):= [(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right].
+\end{align*}
+Using Fact \ref{lem_minv} (iii), we can obtain that with high probability,
+\begin{align*} 
+&\left( A^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\\
+&\preceq (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
+&\preceq \left( A^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}.
+\end{align*}
+Then we get that
+\be\label{eq_h1}h(1)= d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2\left(\rho_1^{-1} + \rho_2^{-1}\right)^{-1}\lesssim pd^2.\ee
+where we used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$. On the other hand, if $|A-1|\ge \delta$ for a small constant $\delta>0$, then we have 
+\begin{align}\label{eq_hA}
+h(A)\gtrsim (1+A^2)\kappa^2 \cdot p\left(\rho_1^{-1} + A^2 \rho_2^{-1}\right)^{-1} \gtrsim p\kappa^2 ,
+\end{align}
+where in the first step we used that $|A-1|^2\gtrsim 1+A^2$ for $|A-1|\ge \delta$, $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$, and in the second step we used \eqref{choiceofpara0}.
+Hence using Claim \ref{claim_largedev1}, \eqref{eq_h1} and \eqref{eq_hA}, we obtain that with high probability,
+\begin{align*}
+g(A)&\ge  h(A) +\sigma^2(n_1+n_2-p) -p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \\
+&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1).
+\end{align*}
+This gives that
+\be\label{rough A-1}
+|\hat A-1|\le \delta
+\ee
+for any small constant $\delta>0$.
+
+{\cor require $k^2\gg d^2 + p^{-1/2+c}\sigma^2$}
+
+Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
+
 We first find the minimizer of $h(A)$, denoted by $A^\star$. 
-
 %Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
@@
 %For the first step, we will prove the following result.
+%To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof. 
+First it is easy to observe that $h(A)< h(-A)$ for $A> 0$. 
+%$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
+Then we consider the case $A\ge 1$. We write
+\begin{align*}
+h(A):= [(1-A^{-1})^2\kappa^2 + (1+A^{-2})d^2/2] \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right).
+\end{align*}
+Notice that
+$$\tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right).$$
+is an increasing functions in $A$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
+\begin{align*}
+h'(A) \ge \left[2(1-A^{-1})\frac{\kappa^2}{A^2} - \frac{d^2}{A^3}\right] \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right) \ge 0,
+\end{align*}
+as long as $A \ge 1+d^2/(2\kappa^2)$.  
+%\begin{align}
+%	h(w) =&  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+%	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+%			& +  \frac{\rho_1}{\rho_2}\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ \sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }.
+\nonumber
+%\end{align}
+%Notice that
+%$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
+%are increasing functions in $w$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
+%\begin{align*}
+%h'(w) \ge & \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
+% &+ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+%		&- 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
+%\end{align*}
+%where the matrix $\cal A$ is defined as 
+%\begin{align*}
+%\cal A :&= \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
+%\end{align*}
+%Using the estimate Fact \eqref{lem_minv}, we get that $\cal A$ is lower bounded as
+%\begin{align*}
+%\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
+%&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
+%\end{align*}
+%as long as
+%$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
+%Hence $h'(w)>0$ on $(w_1,\infty)$, %i.e. $h(w)$ is strictly increasing for $w>w_1$. This 
+%which gives $\hat w\le w_1$.
+Next we consider the case $1-\delta\le A\le 1$. Notice that
+$$\tr\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right).$$
+is a decreasing functions in $A$. Hence taking derivative of $h(A)$, we obtain that
+\begin{align*}
+	h'(A)\le [-2(1-A)\kappa^2 + Ad^2] \cdot p^{-1} \tr\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)\le 0,
+\end{align*}
+as long as $A \le 1-d^2/(2\kappa^2)$. In sum, we see that the minimizer $A^\star$ must satisfy
+$$1-d^2/(2\kappa^2)\le A^\star \le 1+d^2/(2\kappa^2).$$
 
-%To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof. 
-First it is easy to observe that $h(w)< h(-w)$ for $w> 0$.
-Second, using Fact \eqref{lem_minv}, it is easy to check that $h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.
-Hence it suffices to consider the case $1/2\le w\le 2$.
+%Taking derivative of $h(w)$, we obtain that
+%\begin{align}
+%	h'(w) \le& \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
+%	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
+%	& + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }= \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
+%\end{align}
+%where the matrix $\cal B$ is
+%$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{\rho_2}{\rho_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
+%Using Fact \ref{lem_minv}, we get that $\cal B$ is upper bounded as
+%\begin{align*}
+%\cal B \preceq - 2(1-w)\kappa^2 n_2^2 (\al_-(\rho_2) -\oo(1))^2 +2w d^2 n_1n_2 (\al_+(\rho_1) +\oo(1))^2 + 2w\sigma^2 n_2 (\al_+(\rho_2)+\oo(1)) \prec 0,
+%\end{align*}
+%as long as
+%$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
+%Hence $h'(w)<0$ on $[0,w_2)$, %i.e. $h(w)$ is strictly decreasing for $w<w_2$. This 
+%which gives $\hat w\ge w_2$.
 
-We first consider the case $1\le w\le 2$. We write
-\begin{align}
-	h(w) =&  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-			& +  \frac{\rho_1}{\rho_2}\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ \sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }.
-\nonumber
-\end{align}
-Notice that
-$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
-are increasing functions in $w$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
-\begin{align*}
-h'(w) \ge & \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
- &+ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-		&- 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
-\end{align*}
-where the matrix $\cal A$ is defined as 
-\begin{align*}
-\cal A :&= \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
-\end{align*}
-Using the estimate Fact \eqref{lem_minv}, we get that $\cal A$ is lower bounded as
-\begin{align*}
-\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
-&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
-\end{align*}
-as long as
-$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
-Hence $h'(w)>0$ on $(w_1,\infty)$, %i.e. $h(w)$ is strictly increasing for $w>w_1$. This 
-which gives $\hat w\le w_1$.
-
-For the case $1/2\le w\le 1$, the proof is similar as above. Taking derivative of $h(w)$, we obtain that
-\begin{align}
-	h'(w) \le& \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-	& + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }= \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
-\end{align}
-where the matrix $\cal B$ is
-$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{\rho_2}{\rho_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
-Using Fact \ref{lem_minv}, we get that $\cal B$ is upper bounded as
-\begin{align*}
-\cal B \preceq - 2(1-w)\kappa^2 n_2^2 (\al_-(\rho_2) -\oo(1))^2 +2w d^2 n_1n_2 (\al_+(\rho_1) +\oo(1))^2 + 2w\sigma^2 n_2 (\al_+(\rho_2)+\oo(1)) \prec 0,
-\end{align*}
-as long as
-$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
-Hence $h'(w)<0$ on $[0,w_2)$, %i.e. $h(w)$ is strictly decreasing for $w<w_2$. This 
-which gives $\hat w\ge w_2$.
-
-In sum, we have shown that $w_2\le w\le w_1$. Together with
-$$\max\{|w_1 -1|, |w_2 -1|\} =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
-we conclude \eqref{hatw_add1}.
+%In sum, we have shown that $w_2\le w\le w_1$. Together with
+%$$\max\{|w_1 -1|, |w_2 -1|\} =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
+%we conclude \eqref{hatw_add1}.
 
@@
 %for some small constant $c_0>0$.
+
+Next we prove \eqref{hatw_add1}.
+
 Next we prove the following estimate on the optimizer $\hat A$: with high probability,

### 2020-10-01 arxiv/proof_examples.tex
revise

@@
  &\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] \\
- &=\tr\left[  \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} \left( \hat\Sigma- A^2 (X^{(1)})^\top X^{(1)} \right)^2\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}\left( \hat\Sigma- A^2 (X^{(1)})^\top X^{(1)} \right) \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] \\
- &=\tr\left[  (X^{(1)})^\top X^{(1)}\right] - A^2\tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)}\right] = \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right] .
+ &=\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \right] \\
+ & = \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right] .
 \end{align*}
+ In the first step of the above derivation, we used that 
+ $$(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)}.$$
 
@@
  In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right). $$
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-1/2+c}\cdot p\left(\sigma^2 + \kappa^2+d^2 \right) $$
+for any small constant $c>0$.
  \end{claim}
@@
 Using Fact \ref{lem_minv} (iii), we can obtain that with high probability,
-\begin{align*} 
-&\left( A^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\\
-&\preceq (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
-&\preceq \left( A^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}.
-\end{align*}
+\begin{align} 
+&\left( A^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
+&\preceq (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
+&\preceq \left( A^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}. \label{op_uplow}
+\end{align}
 Then we get that
@@
 \begin{align*}
-g(A)&\ge  h(A) +\sigma^2(n_1+n_2-p) -p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \\
-&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-c_\infty}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1).
+g(A)&\ge  h(A) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \\
+&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1)
 \end{align*}
+under \eqref{choiceofpara0}.
 This gives that
@@
 
-{\cor require $k^2\gg d^2 + p^{-1/2+c}\sigma^2$}
-
-Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
-
-We first find the minimizer of $h(A)$, denoted by $A^\star$. 
+%Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$. 
+To obtain the better bound \eqref{hatw_add1}, we study the function $h(A)$ more closely and find its minimizer of $h(A)$, denoted by $A^\star$. 
 %Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
@@
 is an increasing functions in $A$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
-\begin{align*}
+\begin{align}\label{h'(A)1}
 h'(A) \ge \left[2(1-A^{-1})\frac{\kappa^2}{A^2} - \frac{d^2}{A^3}\right] \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right) \ge 0,
-\end{align*}
+\end{align}
 as long as $A \ge 1+d^2/(2\kappa^2)$.  
@@
 is a decreasing functions in $A$. Hence taking derivative of $h(A)$, we obtain that
-\begin{align*}
+\begin{align}\label{h'(A)2}
 	h'(A)\le [-2(1-A)\kappa^2 + Ad^2] \cdot p^{-1} \tr\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)\le 0,
-\end{align*}
+\end{align}
 as long as $A \le 1-d^2/(2\kappa^2)$. In sum, we see that the minimizer $A^\star$ must satisfy
@@
 
-Next we prove \eqref{hatw_add1}.
+Now we are ready to prove \eqref{hatw_add1}.
+We choose the constant $c$ in Claim \eqref{claim_largedev1} small enough such that $1/2-c> c_\infty$.
+First using \eqref{op_uplow} and \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le A\le 1+\delta$,
+$$h'(A)\ge \frac{2(A-1)\kappa^2 - d^2}{A^3} \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right) \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
+Thus we get that if $1+d^2/\kappa^2 +p^{-c_\infty}\le A\le 1+\delta$,
 
@@
 %\end{proof}
+
+{\cor require $\kappa^2\gg d^2 + p^{-1/2+c}\sigma^2$}
 \end{proof}

### 2020-10-01 arxiv/proof_examples.tex
revise

@@
 	\begin{align}
-		\hat{B} \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\
+		\hat{B}(A) \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\
 		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
@@
  In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-1/2+c}\cdot p\left(\sigma^2 + \kappa^2+d^2 \right) $$
-for any small constant $c>0$.
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-1/2+e_1}\cdot p\left(\sigma^2 + \kappa^2+d^2 \right) $$
+for any small constant $e_1>0$.
  \end{claim}
@@
 %There exists a constant $C>0$ such that
-	\be\label{hatw_add1}|\hat A -1|\lesssim \frac{d^2}{\kappa^2} + \frac{\sigma^2}{\kappa^2} + p^{-c_\infty}. 
+	\be\label{hatw_add1}|\hat A -1|\le  \frac{d^2}{\kappa^2} + p^{-1/4+e_2}. 
 	\ee
+	for any small constant $e_2>0$.
 	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
@@
 Hence using Claim \ref{claim_largedev1}, \eqref{eq_h1} and \eqref{eq_hA}, we obtain that with high probability,
-\begin{align*}
-g(A)&\ge  h(A) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \\
-&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1)
-\end{align*}
+\begin{align}
+g(A)&\ge  h(A) +\sigma^2(n_1+n_2-p) -p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
+&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1) \label{gA>g1}
+\end{align}
 under \eqref{choiceofpara0}.
@@
 
-Now we are ready to prove \eqref{hatw_add1}.
-We choose the constant $c$ in Claim \eqref{claim_largedev1} small enough such that $1/2-c> c_\infty$.
-First using \eqref{op_uplow} and \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le A\le 1+\delta$,
+Now we are ready to prove \eqref{hatw_add1}. First using \eqref{op_uplow} and \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le A\le 1+\delta$,
 $$h'(A)\ge \frac{2(A-1)\kappa^2 - d^2}{A^3} \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right) \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
-Thus we get that if $1+d^2/\kappa^2 +p^{-c_\infty}\le A\le 1+\delta$,
-
-Next we prove the following estimate on the optimizer $\hat A$: with high probability,
-%\begin{lemma}
-%For the isotropic model, we have
-\be\label{hatv_add1}
-|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 /2+ 2\e}.
-\ee
-%\end{lemma}
-%\begin{proof}
- In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim \sigma^2$.
+Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+e_2}\le A\le 1+\delta$,
+\begin{align*}
+h(A)-h(1)\ge h(A)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^A h'(x)\dd x \gtrsim p\kappa^2 \cdot |A-1|^2  \gtrsim p\frac{d^2}{\kappa^2} + p^{-1/2+2e_2}\cdot p\kappa^2.
+\end{align*}
+Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have 
+$$ h(A)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
+under \eqref{choiceofpara0}, which implies the inequality as in \eqref{gA>g1}. Second using \eqref{op_uplow} and \eqref{h'(A)2}, we obtain that for $1-\delta \le A \le 1-d^2/\kappa^2$,
+$$- h'(A)\ge  [2(1-A)\kappa^2 - Ad^2] \cdot p^{-1} \tr\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)  \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
+Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-\frac12c_\infty}\le A\le 1-\delta$, then 
+$$ h(A)-h(1) \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
+under \eqref{choiceofpara0}, which implies the inequality as in \eqref{gA>g1}. In sum, we obtain that the minimizer $\hat A$ must satisfy \eqref{hatw_add1}.
+%Next we prove the following estimate on the optimizer $\hat A$: with high probability,
+%%\begin{lemma}
+%%For the isotropic model, we have
+%\be\label{hatv_add1}
+%|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 /2+ 2\e}.
+%\ee
+%%\end{lemma}
+%%\begin{proof}
+% In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim \sigma^2$.
 Moreover, under \eqref{choiceofpara} we have
-$$h(w) =\OO(\sigma^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
-Thus we obtain that for $|w-1|\ge 2C\cal E$,
-$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min\{h(w_1),h(w_2)\}|\gtrsim \sigma^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
-which leads to $g(w) > g(\hat w)$ with high probability by \eqref{boundv-w}.
+%$$h(w) =\OO(\sigma^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
+%Thus we obtain that for $|w-1|\ge 2C\cal E$,
+%$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min\{h(w_1),h(w_2)\}|\gtrsim \sigma^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
+%which leads to $g(w) > g(\hat w)$ with high probability by \eqref{boundv-w}.
 Thus $w$ cannot be a minimizer of $g(v)$, and we must have $|\hat v - 1|\le 2C\cal E$.
 %Together with \eqref{hatw_add1}, we conclude \eqref{hatv_add1}.
-%\end{proof}
-
-{\cor require $\kappa^2\gg d^2 + p^{-1/2+c}\sigma^2$}
+%%\end{proof}
+%
+%{\cor require $\kappa^2\gg d^2 + p^{-1/2+c}\sigma^2$}
 \end{proof}
 
-\paragraph{Calculating the prediction loss.} Then we calculate the predication loss ...
+\paragraph{Calculating the prediction loss.} Now we calculate the predication loss using the optimal $\hat B(\hat A) $ in \eqref{eq_Bhat_2task}. ......
+
+Plugging $Y^{(1)}$ and $Y^{(2)}$ in \eqref{model_YvsX} into \eqref{eq_Bhat_2task}, we can rewrite that 
+ \begin{align}
+		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
+\label{eq_Bhat_2task2} %\\
+		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
+	\end{align}
 
@@
  \nc
-
-Plugging $Y^{(1)}$ and $Y^{(2)}$ in \eqref{model_YvsX} into \eqref{eq_Bhat_2task}, we can rewrite that 
- \begin{align}
-		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
-\label{eq_Bhat_2task2} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
 

### 2020-10-02 arxiv/examples.tex
revise

--- 2020-09-30 arxiv/examples.tex
@@
 \begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
-	In the setting described above, assume further that a) the sample size $n_2$ of task two is greater than $(1 + \tau) p$, and b) there exists a small constant $c_0>0$ such that the signal-to-noise ratios satisfy
+	In the setting described above, assume further that a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
+	the signal and noise variances satisfy 
+%	\be\label{choiceofpara0}
+%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
 	\be\label{choiceofpara0}
-		p^{ c_0} \le \frac{p\kappa^2}{\sigma^2 }  \le p^{1-c_0},\quad  \frac{pd^2}{\sigma^2}=\OO(1).
+	\sigma^2 \lesssim  \kappa^2   ,\quad  d^2 \ll {\kappa^2}.
 	\ee
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
-	 & \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2 ),
+	  \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le & \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+	& +Cp \left[p^{-c_\varphi}(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + d^4/\kappa^2\right],\nonumber
 	 \end{align}
-	 for any constant $c\in (0,c_0)$.
+	 for a large constant $C>0$.
 \end{corollary}

### 2020-10-02 arxiv/proof_examples.tex
revise

@@
 
+\iffalse
+%Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
+%Using the local optimality condition of $B$, we obtain that
+%\begin{align*}
+%	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
+%	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
+%	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
+%\end{align*}
+Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
+\begin{align}
+	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
+	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
+			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
+\end{align}
+equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
+equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
+%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
+Comparing the above to single-task learning, that is,
+\begin{align}
+	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
+\end{align}
+we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
+In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
+Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
+
+% \todo{derive the test loss} Expectation was given in equation \eqref{eq_bias_2task} and equation \eqref{eq_var_2task}.
+ \fi
+
 \paragraph{Simplifying the optimization objective.} 
@@
 	\begin{align}
-		\hat{B}(A) \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\
+		\hat{B} \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\
 		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
 	\end{align}
- Now inserting $\hat B$ back into \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $A:=A_1/A_2$ as follows 
+ Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $A:=A_1/A_2$ as follows 
  \begin{align}
-		 g(A) \define & \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\hat \Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\hat \Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)+ \left(X^{(2)}\hat \Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} + A X^{(2)}\hat \Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2,
+		 g(A) \define & \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+		 + & \left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)+ \left(X^{(2)}\Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} + A X^{(2)}\Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2,
 		\label{eq_mtl_A12}
@@
 	where we denote
-	$$\hat \Sigma:= A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+	$$\Sigma\equiv \Sigma(A):= A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
 We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
@@
 &\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-&= \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\hat \Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon_1} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
-&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\hat \Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)}}  +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  (X^{(2)})^\top X^{(2)}\hat \Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
-		&= \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-		&+ \sigma^2\tr\left[ \left(A^2 X^{(1)}\hat \Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\right] +\sigma^2\tr\left[ \left(X^{(2)}\hat \Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
-&+ 2 A^2 \sigma^2 \tr\left[ \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
-		& = \left\| X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
+&= \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
+& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon_1} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
+&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)}}  +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma^{-1}  (X^{(2)})^\top X^{(2)}\Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
+		&= \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
+		&+ \sigma^2\tr\left[ \left(A^2 X^{(1)}\Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\right] +\sigma^2\tr\left[ \left(X^{(2)}\Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
+&+ 2 A^2 \sigma^2 \tr\left[ \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\Sigma^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
+		& = \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
 \end{align*}
@@
 &\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \nonumber\\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
-&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
+&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
 \end{align}
@@
 \begin{align*}
- &\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \hat \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] \\
- &=\tr\left[  (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} \right] \\
- & = \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right] .
+ &\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] \\
+ &=\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} \right] \\
+ & = \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right] .
 \end{align*}
  In the first step of the above derivation, we used that 
- $$(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \hat \Sigma^{-1}(X^{(1)})^\top X^{(1)}.$$
+ $$(X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)}.$$
 
@@
 \begin{proof}
-Corresponding to \eqref{EgA}, we define the function
+Corresponding to equation \eqref{EgA}, we define the function
 \begin{align*}
-h(A):= [(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right].
+h(A):= [(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}\right].
 \end{align*}
@@
 &\left( A^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
-&\preceq (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
+&\preceq (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
 &\preceq \left( A^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}. \label{op_uplow}
@@
 Then we get that
-\be\label{eq_h1}h(1)= d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2\left(\rho_1^{-1} + \rho_2^{-1}\right)^{-1}\lesssim pd^2.\ee
+\be\label{eq_h1}h(1)= d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2\left(\rho_1^{-1} + \rho_2^{-1}\right)^{-1}\lesssim pd^2.\ee
 where we used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$. On the other hand, if $|A-1|\ge \delta$ for a small constant $\delta>0$, then we have 
@@
 \end{align}
-where in the first step we used that $|A-1|^2\gtrsim 1+A^2$ for $|A-1|\ge \delta$, $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$, and in the second step we used \eqref{choiceofpara0}.
-Hence using Claim \ref{claim_largedev1}, \eqref{eq_h1} and \eqref{eq_hA}, we obtain that with high probability,
+where in the first step we used that $|A-1|^2\gtrsim 1+A^2$ for $|A-1|\ge \delta$, $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$, and in the second step we used equation \eqref{choiceofpara0}.
+Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability,
 \begin{align}
@@
 \end{align}
-under \eqref{choiceofpara0}.
+under condition \eqref{choiceofpara0}.
 This gives that
-\be\label{rough A-1}
-|\hat A-1|\le \delta
-\ee
-for any small constant $\delta>0$.
+%\be\label{rough A-1}
+$|\hat A-1|\le \delta$ for any small constant $\delta>0$.
 
@@
 To obtain the better bound \eqref{hatw_add1}, we study the function $h(A)$ more closely and find its minimizer of $h(A)$, denoted by $A^\star$. 
-%Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
+%Using Lemma \ref{largedeviation} again, we can simplify equation \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
 %	%We define the function
@@
 %	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
-%	Furthermore, the validation loss in \eqref{approxvalid} reduces to
+%	Furthermore, the validation loss in equation \eqref{approxvalid} reduces to
 %	\be\label{boundv-w}
@@
 %	\item First, we show that $\hat{w}$ is close to $1$.
-%	\item Second, with \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get \eqref{simple1}.
+%	\item Second, with equation \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get equation \eqref{simple1}.
 %\squishend
@@
 \begin{align*}
-h(A):= [(1-A^{-1})^2\kappa^2 + (1+A^{-2})d^2/2] \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right).
+h(A):= [(1-A^{-1})^2\kappa^2 + (1+A^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
 \end{align*}
 Notice that
-$$\tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right).$$
+$$\tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]$$
 is an increasing functions in $A$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
 \begin{align}\label{h'(A)1}
-h'(A) \ge \left[2(1-A^{-1})\frac{\kappa^2}{A^2} - \frac{d^2}{A^3}\right] \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right) \ge 0,
+h'(A) \ge \left[2(1-A^{-1})\frac{\kappa^2}{A^2} - \frac{d^2}{A^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,
 \end{align}
@@
 %\end{align*}
-%Using the estimate Fact \eqref{lem_minv}, we get that $\cal A$ is lower bounded as
+%Using the estimate Fact equation \eqref{lem_minv}, we get that $\cal A$ is lower bounded as
 %\begin{align*}
@@
 Next we consider the case $1-\delta\le A\le 1$. Notice that
-$$\tr\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right).$$
+$$\tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
 is a decreasing functions in $A$. Hence taking derivative of $h(A)$, we obtain that
 \begin{align}\label{h'(A)2}
-	h'(A)\le [-2(1-A)\kappa^2 + Ad^2] \cdot p^{-1} \tr\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)\le 0,
+	h'(A)\le [-2(1-A)\kappa^2 + Ad^2] \cdot p^{-1} \tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,
 \end{align}
@@
 %$$\max\{|w_1 -1|, |w_2 -1|\} =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
-%we conclude \eqref{hatw_add1}.
+%we conclude equation \eqref{hatw_add1}.
 
@@
 
-Now we are ready to prove \eqref{hatw_add1}. First using \eqref{op_uplow} and \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le A\le 1+\delta$,
-$$h'(A)\ge \frac{2(A-1)\kappa^2 - d^2}{A^3} \cdot p^{-1} \tr\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right) \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
+Now we are ready to prove equation \eqref{hatw_add1}. First using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le A\le 1+\delta$,
+$$h'(A)\ge \frac{2(A-1)\kappa^2 - d^2}{A^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
 Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+e_2}\le A\le 1+\delta$,
@@
 $$ h(A)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
-under \eqref{choiceofpara0}, which implies the inequality as in \eqref{gA>g1}. Second using \eqref{op_uplow} and \eqref{h'(A)2}, we obtain that for $1-\delta \le A \le 1-d^2/\kappa^2$,
-$$- h'(A)\ge  [2(1-A)\kappa^2 - Ad^2] \cdot p^{-1} \tr\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)  \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
+under equation \eqref{choiceofpara0}, which implies the inequality \eqref{gA>g1}. Second using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le A \le 1-d^2/\kappa^2$,
+$$- h'(A)\ge  [2(1-A)\kappa^2 - Ad^2] \cdot p^{-1} \tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
 Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-\frac12c_\infty}\le A\le 1-\delta$, then 
 $$ h(A)-h(1) \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
-under \eqref{choiceofpara0}, which implies the inequality as in \eqref{gA>g1}. In sum, we obtain that the minimizer $\hat A$ must satisfy \eqref{hatw_add1}.
+under equation \eqref{choiceofpara0}, which implies the inequality \eqref{gA>g1}. In sum, we obtain that the minimizer $\hat A$ must satisfy equation \eqref{hatw_add1}.
 %Next we prove the following estimate on the optimizer $\hat A$: with high probability,
@@
 % In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim \sigma^2$.
-Moreover, under \eqref{choiceofpara} we have
+Moreover, under equation \eqref{choiceofpara} we have
 %$$h(w) =\OO(\sigma^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
@@
 %$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min\{h(w_1),h(w_2)\}|\gtrsim \sigma^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
-%which leads to $g(w) > g(\hat w)$ with high probability by \eqref{boundv-w}.
+%which leads to $g(w) > g(\hat w)$ with high probability by equation \eqref{boundv-w}.
 Thus $w$ cannot be a minimizer of $g(v)$, and we must have $|\hat v - 1|\le 2C\cal E$.
-%Together with \eqref{hatw_add1}, we conclude \eqref{hatv_add1}.
+%Together with equation \eqref{hatw_add1}, we conclude equation \eqref{hatv_add1}.
 %%\end{proof}
@@
 
-\paragraph{Calculating the prediction loss.} Now we calculate the predication loss using the optimal $\hat B(\hat A) $ in \eqref{eq_Bhat_2task}. ......
+\paragraph{Calculating the prediction loss.} Now we calculate the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat A=\hat A_1/\hat A_2$:
+\begin{align*}
+L(\hat{\beta}_2^{\MTL}) &=\left|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right| \\
+&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,
+\end{align*}
+where we denoted
+$$\hat \Sigma:= \hat A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+To illustrate the idea of bias-variance decomposition, we assume that $\hat A$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
+Then we can calculate the partial expectation of $L(\hat{\beta}_2^{\MTL})$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
+ \begin{align}
+	&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2,\beta_1,\beta_2} \nonumber \\
+&	=  \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 \nonumber\\ %\label{eq_bias_2task} 
+			& + \sigma^2\cdot \bigtr{ X^{(2)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(2)})^\top}+ \sigma^2\cdot \hat A^2 \bigtr{ X^{(1)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(1)})^\top}\nonumber\\
+			%+\sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } \nonumber\\ 
+			&= \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).\nonumber
+			%\label{eq_var_2task}
+\end{align}
+This gives a bias-variance decomposition of the MTL prediction loss: the first term on the right-hand side is the bias term, while the second term is the variance term.
+For the random-effects model, we further take the partial expectation over $\beta_1$ and $\beta_2$:
+ \begin{align}
+	\exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}&	=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} }\nonumber \\
+	&+\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
+			\label{eq_var_2task}
+\end{align}
+One can compare the above expression with the predication loss for STL, that is,
+\begin{align}
+	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
+\end{align}
+we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over the second term on the right-hand side of equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
+In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
+Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
 
-Plugging $Y^{(1)}$ and $Y^{(2)}$ in \eqref{model_YvsX} into \eqref{eq_Bhat_2task}, we can rewrite that 
- \begin{align}
-		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
+%Plugging $Y^{(1)}$ and $Y^{(2)}$ in equation \eqref{model_YvsX} into equation \eqref{eq_Bhat_2task}, we can rewrite that 
+% \begin{align}
+%		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
 \label{eq_Bhat_2task2} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
+%		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
+%	\end{align}
 
+In general, for $\hat A$ as  the minimizer of $g(A)$, it depends on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+However, using the concentration estimates in Lemma \ref{largedeviation}, we can still obtain the expression on the right-hand side of \eqref{eq_var_2task} up to a small error.
+In particular, our proof will not use Lemma \ref{lem_hat_v}.
+
+%control the difference between $g(A)$ and its partial expectation. 
  \begin{claim}\label{claim_largedev2}
- In the setting of Proposition \ref{cor_MTL_loss}, we have that 
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}\right| \le p^{-c_\infty}\cdot p\left(\sigma^2 +\|\beta_1\|^2 +\|\beta_2\|^2 \right). $$
+ In the setting of Proposition \ref{cor_MTL_loss}, if $\hat A=\OO(1)$, then we have that with high probability,
+$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat A)\right| \le p^{-1/2+e}\cdot p\left(\sigma^2 +\kappa^2 +d^2 \right),$$
+for any small constant $e>0$. Here we introduced the function
+\begin{align*}
+	\cal L(\hat A)	:=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} } +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
+\end{align*}
  \end{claim}
@@
 
-\cor
-%Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
-%Using the local optimality condition of $B$, we obtain that
-%\begin{align*}
-%	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
-%	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
-%	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-%\end{align*}
-Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
-\begin{align}
-	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
-	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
-			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
-\end{align}
-Equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
-equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
-%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Comparing the above to single-task learning, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-
-% \todo{derive the test loss} Expectation was given in \eqref{eq_bias_2task} and \eqref{eq_var_2task}.
- \nc
+In the specific setting in Proposition \ref{cor_MTL_loss}, we can further simplify $\cal L(\hat A)$ using Lemma \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
 
 \begin{lemma}
-In the isotropic model, suppose for some constant $c_0>0$, 
-\be\label{choiceofpara}
-	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
-\ee
-where $\e_0$ is the constant as appeared in \eqref{approxvalid}. Then we have
+In the setting of Proposition \ref{cor_MTL_loss}, we have
+%\be\label{choiceofpara}
+%	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
+%\ee
+%where $\e_0$ is the constant as appeared in equation \eqref{approxvalid}. Then we have
 \begin{align}
-\te(\hat{\beta}_2^{\MTL})=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
+\cal L(\hat A)=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
 &+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \quad \text{w.h.p.} \label{simple1}
@@
 
- Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$, we get that w.h.p.,
+ Inserting equation \eqref{hatv_add1} into equation \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$, we get that w.h.p.,
 \begin{align}
@@
 \end{align}
-In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. Using Fact \eqref{lem_minv}, we have that
+In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order.
+Using Fact equation \eqref{lem_minv}, we have that
 $$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim 1.$$
@@
 On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$.
-The above considerations lead to the choices of parameters in \eqref{choiceofpara}, under which we can simplify \eqref{1Liso} to \eqref{simple1}.
+The above considerations lead to the choices of parameters in equation \eqref{choiceofpara}, under which we can simplify equation \eqref{1Liso} to equation \eqref{simple1}.
 %\begin{align}
@@
 Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in \eqref{defnpihat}.	Then we have with high probability,
+		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in equation \eqref{defnpihat}.	Then we have with high probability,
 		\begin{align*}
@@
 		\end{align*}
-		where $\Delta_{\vari}$ was defined in \eqref{Deltavarv}.
+		where $\Delta_{\vari}$ was defined in equation \eqref{Deltavarv}.
 \end{lemma}
@@
 \begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
-The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace \eqref{bounddelta-} with a tighter bound.
+The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace equation \eqref{bounddelta-} with a tighter bound.
 We only describe the main difference in the following proof.
@@
 \end{align}
-where $\delta_{\bias}(v)$ was defined in \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
+where $\delta_{\bias}(v)$ was defined in equation \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
 Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
@@
 \end{align*}
-Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using Fact \eqref{lem_minv}, we obtain that
+Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using Fact equation \eqref{lem_minv}, we obtain that
 \be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
@@
 $$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
+Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining equation \eqref{anotherbeta} and equation \eqref{anotherwtbeta} we get
 \be\label{replaceest}
@@
 \ee
-Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
+Now we can replace the estimate equation \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
 In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
 \end{proof}
+
+\cor
+
+	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
+Then solving equations equation \eqref{eq_a12extra} and equation \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
+	\begin{align}
+		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
+		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
+		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
+		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
+	\end{align}
+	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
+\be\label{Deltavar}
+\begin{split}
+\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
+\end{split}
+\ee
+with high probability, where 
+	\begin{align*}
+		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
+	\end{align*}
+	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
+	Next for the model shift bias
+	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
+	we can get from Lemma \ref{prop_model_shift_tight} that
+\be\label{Deltabeta} 
+\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
+	where 
+	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$
+	\nc
 
@@
 %\begin{proof}[Proof of Claim \ref{claim_covar_shift}]	
-%	With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
+%	With the same arguments as in Claim \ref{lem_hat_v}, we can show that equation \eqref{hatv_add1} holds.
+Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in equation \eqref{choiceofpara}, we can simplify $g(M_0)$ as
 %\be \nonumber
@@
 We now calculate $g(M_0)$.
-With the same arguments as in Claim \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify $g(M_0)$ as
+With the same arguments as in Claim \ref{lem_hat_v}, we can show that equation \eqref{hatv_add1} holds.
+Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in equation \eqref{choiceofpara}, we can simplify $g(M_0)$ as
 \be \nonumber
@@
 \ee
-Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
+Inserting equation \eqref{est_a12extra} into equation \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
 \begin{align}\label{approximateteM}
@@
 $$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}. 
+%With these two bounds, we can easily conclude equation \eqref{approxteM}. 
 %
@@
 %$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+%Moreover, for all $M$ satisfying equation \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
 By AM-GM inequality, we observe that 
@@
 \end{align}
-Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
+Combining equation \eqref{est_a12extra}, equation \eqref{approximateteM}, equation \eqref{AMGM} and equation \eqref{gvar_extra2}, we conclude the proof.
 %, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
@@
 We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-Then equations in \eqref{eq_a12extra} become
+Then equations in equation \eqref{eq_a12extra} become
 \be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
 \ee
-%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to \eqref{compleeq}. 
-After solving these, with \eqref{gvar_extra} we get that w.h.p.,
+%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to equation \eqref{compleeq}. 
+After solving these, with equation \eqref{gvar_extra} we get that w.h.p.,
 \be\label{testcomple}
@@
 In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in \eqref{testcomple} takes the value
+Then for any $\lambda$, the test error in equation \eqref{testcomple} takes the value
 %$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
@@
 %This phenomenon can be also explained using our theory. 
-We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with \eqref{compleeq}, we can rewrite
+We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with equation \eqref{compleeq}, we can rewrite
 $$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
@@
 
-With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
+With equation \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
 %With slight abuse of notations, we shall write $\hat a_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.
@@
 	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
-Then solving equations \eqref{eq_a12extra} and \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
+Then solving equations equation \eqref{eq_a12extra} and equation \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
 	\begin{align}
@@
 %	\end{align*}
-Note that by \eqref{simple1}, we have
+Note that by equation \eqref{simple1}, we have
  \be\label{var-beta}\te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} .\ee
-Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.
+Then we can track its sign using equation \eqref{Deltavar} and equation \eqref{Deltabeta}.
 
@@
 
-\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
+\noindent{\bf Positive transfer.} With equation \eqref{Deltavar} and equation \eqref{Deltabeta}, we conclude that if
 \be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-then $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper101} to
+then $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify equation \eqref{upper101} to
 	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
@@
 \be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper102} to
+	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify equation \eqref{upper102} to
 	\be\label{neg1} \frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
@@
 Following the proof of Proposition \ref{prop_dist_transition}, we know that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ w.h.p.
-if \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ w.h.p.
-if \eqref{neg1} holds.
+if equation \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ w.h.p.
+if equation \eqref{neg1} holds.
 %\be\label{pos1}
 %pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
-%and we get from \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ w.h.p. if
+%and we get from equation \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ w.h.p. if
 %\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
@@
 is strictly decreasing with respect to $\rho_1$ as long as $\rho_2> 2$, and $ \Phi(\rho_1, \rho_2)$ converges to $(\rho_2-1)^{-1}$ as $\rho_1\to \infty$.
-Since $\left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} < 2$ for $\rho_1>40$,  \eqref{explainpsi} implies that \eqref{neg1} holds for large enough $\rho_1$.
+Since $\left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} < 2$ for $\rho_1>40$,  equation \eqref{explainpsi} implies that equation \eqref{neg1} holds for large enough $\rho_1$.
 Moreover, the transition from positive transfer when $\rho_1$ is small to negative transfer when $\rho_1$ is large is described by the two bounds in Proposition \ref{prop_data_size}, which we will show now.
 % $$ \Psi(\beta_1,\beta_2) \ge \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
-% then \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds w.h.p..
+% then equation \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds w.h.p..
 Plugging into $\rho_1>50$, we obtain the first statement.
@@
 %$\gamma_+^{-1}$
-%The two bounds follows directly from \eqref{pos1} and \eqref{neg1}. 
+%The two bounds follows directly from equation \eqref{pos1} and equation \eqref{neg1}. 
 In the following proof, we will use the following trivial inequalities 
@@
 
-%This shows that \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. 
+%This shows that equation \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. 
 %
@@
 
-\noindent{\bf Positive transfer.} With \eqref{trivialphi}, we see that \eqref{pos1} is implied by the following inequality:
+\noindent{\bf Positive transfer.} With equation \eqref{trivialphi}, we see that equation \eqref{pos1} is implied by the following inequality:
 \begin{align}\label{pos1solv}
@@
  \end{align}
- Then we can solve \eqref{pos1solv} to get
+ Then we can solve equation \eqref{pos1solv} to get
  \be\label{addconstraint}\rho_1 < \frac{\rho_2-2}{\Psi(\beta_1,\beta_2) \cdot (\rho_2 - 1)\left( \al_+^2(\rho_1) +  \oo(1) \right) - 1}  .\ee
@@
 
- Note that if we require the RHS of \eqref{addconstraint} to be larger than $40$, that is, \eqref{addconstraint} is not a null condition, then with \eqref{explainpsi} we get
+ Note that if we require the RHS of equation \eqref{addconstraint} to be larger than $40$, that is, equation \eqref{addconstraint} is not a null condition, then with equation \eqref{explainpsi} we get
  $$ \rho_2 - 2>\left[ 2\left( \al_+^2(\rho_1) +  \oo(1) \right)  -1\right]\rho_1 .$$
@@
 % \end{align*}
-% This shows that \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
+% This shows that equation \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
 
@@
  \noindent{\bf Negative transfer.} 
-With \eqref{trivialphi}, we see that \eqref{neg1} is implied by the following inequality:
+With equation \eqref{trivialphi}, we see that equation \eqref{neg1} is implied by the following inequality:
 \begin{align}\label{neg1solv}
@@
  \end{align}
- where we used $(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) > \rho_2-1.5$ for $\rho_1>40$ and $\rho_2>110$. Then we can solve \eqref{neg1solv} to get that
+ where we used $(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) > \rho_2-1.5$ for $\rho_1>40$ and $\rho_2>110$. Then we can solve equation \eqref{neg1solv} to get that
  \be\label{addconstaint2}
@@
 which gives the second statement of Proposition \ref{prop_data_size}.
-We remark that condition \eqref{explainpsi} implies $\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)>1$, so \eqref{addconstaint2} does not give a trivial bound. 
+We remark that condition equation \eqref{explainpsi} implies $\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)>1$, so equation \eqref{addconstaint2} does not give a trivial bound.
  \end{proof}
@@
 %The key quantity is to look at:
-%The estimator using the source and target together from minimizing \eqref{eq_mtl_basic} is
+%The estimator using the source and target together from minimizing equation \eqref{eq_mtl_basic} is
 %\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
@@
 	\end{align}
-where $a_1, a_2$ are the solutions to equations \eqref{eq_a2}. %\cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
+where $a_1, a_2$ are the solutions to equations equation \eqref{eq_a2}. %\cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
 \end{proposition}
@@
 
-Finally, plugging \eqref{hatw1} into the expression $\te(\hat{\beta}^{\TL}_{t}) $, we obtain \eqref{tehatw1}.
+Finally, plugging equation \eqref{hatw1} into the expression $\te(\hat{\beta}^{\TL}_{t}) $, we obtain equation \eqref{tehatw1}.
 %$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$
@@
 \begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}.
+In the setting of Proposition \ref{prop_var_transition}, the test loss is given by equation \eqref{eq_te_mtl_2task}.
 %the validation loss and the test error become
@@
 
-In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$.
+In the current setting, we can also show that  equation \eqref{hatv_add1}  holds for $\hat v$.
 Since the proof is almost the same as the one for Claim \ref{lem_hat_v}, we omit the details.
 %$$|\hat w-1|=\OO(p^{-1}).$$
-%as in \eqref{hatw_add1}.
+%as in equation \eqref{hatw_add1}.
 %We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}.
-Thus under \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}:
+Thus under equation \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in equation \eqref{simple1}:
 \be \label{simple2}
@@
 $$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
-satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$;
+satisfies equation \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$;
 $$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
-satisfies \eqref{Deltabeta}; $\delta_{\vari}^{(2)}$ is defined as
+satisfies equation \eqref{Deltabeta}; $\delta_{\vari}^{(2)}$ is defined as
 \begin{align*}
@@
 %where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has
-To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using Fact \eqref{lem_minv}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
+To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using Fact equation \eqref{lem_minv}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
 This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
@@
 
-\noindent{\bf Positive transfer.} By \eqref{Deltavar}, \eqref{Deltabeta} and \eqref{Deltavar2}, if the following inequality holds,
+\noindent{\bf Positive transfer.} By equation \eqref{Deltavar}, equation \eqref{Deltabeta} and equation \eqref{Deltavar2}, if the following inequality holds,
 \be\label{cond sigma1}
@@
 \ee
-then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can solve \eqref{cond sigma1} to get
+then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can solve equation \eqref{cond sigma1} to get
 \begin{align*}
@@
 \ee
-then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve \eqref{cond sigma12} to get
+then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve equation \eqref{cond sigma12} to get
 \begin{align*}
@@
 \ee
- where as in \eqref{Deltabeta}, the model shift biases $\delta^{(i)}_{\bias}$ satisfy that with high probability,
+ where as in equation \eqref{Deltabeta}, the model shift biases $\delta^{(i)}_{\bias}$ satisfy that with high probability,
 \be\nonumber %\label{Deltabeta}
@@
 \ee
-Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we immediately obtain the lower bound $x^\star\ge x_l $.
+Comparing equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we immediately obtain the lower bound $x^\star\ge x_l $.
 %where
@@
 In particular, we have $x\rho > x_l \rho \ge \min(\rho_1,\rho_2)$, where we abbreviated $\rho:=\rho_1+\rho_2$.
-%Comparing \eqref{reduceproof1} and \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
+%Comparing equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
 %\noindent{\bf The upper bound.}
-From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies
+From equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies
 \be\nonumber
@@
 $$\frac{1+\oo(1)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4 < 5. $$
-Inserting it into \eqref{solval1}, we can solve for the upper bound in \eqref{eq_uplowx}.
+Inserting it into equation \eqref{solval1}, we can solve for the upper bound in equation \eqref{eq_uplowx}.
 %where we abbreviated $\rho:=\rho_1+\rho_2$.
@@
 $$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52.$$
-Thus the following inequality implies \eqref{solval1}:
+Thus the following inequality implies equation \eqref{solval1}:
 \be\nonumber %\label{solval1add}
@@
 %\noindent{\bf The lower bound.}
-From \eqref{reduceproof1} and \eqref{reduceproof2}, we see that $x^\star\ge x$ if $x$ satisfies
+From equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we see that $x^\star\ge x$ if $x$ satisfies
 \be\label{solval2}
@@
 %We then follow similar arguments as the above proof for the upper bound.
-Then in the case $\min(\rho_1,\rho_2)\ge 100$, with some basic calculations, one can show that the sum on the left-hand side of \eqref{solval2} satisfies
+Then in the case $\min(\rho_1,\rho_2)\ge 100$, with some basic calculations, one can show that the sum on the left-hand side of equation \eqref{solval2} satisfies
 $$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x\rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33 .$$
-Thus the following inequality implies \eqref{solval2}:
+Thus the following inequality implies equation \eqref{solval2}:
 \be\label{solval2add}

### 2020-10-02 arxiv/setup.tex
revise

@@
 For an estimator $\hat{\beta}$ of the target task model $\beta_t$, we define the prediction loss of the estimator $\hat{\beta}$ as
-	{\begin{align*}
+	{\begin{align}\label{eq1_prediction_loss}
 		\te(\hat{\beta}) = \exarg{x = \Sigma_t^{1/2} z}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
 		= \bignorm{\Sigma_t^{1/2} (\hat{\beta} - \beta_t)}^2,
-	\end{align*}}%
+	\end{align}}%
 where $x = \Sigma_t^{1/2} z$ denotes a random feature vector with covariance $\Sigma_t$.
@@
 	Let $\varphi > 4$ be a fixed value.
-	Let $\tau > 1$ be a small enough constant.
+	Let $\tau > 0$ be a small enough constant.
 	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.

### 2020-10-02 arxiv/proof_examples.tex
revise

@@
 \begin{lemma}
-In the setting of Proposition \ref{cor_MTL_loss}, we have
+In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
 %\be\label{choiceofpara}
@@
 \begin{align}
-\cal L(\hat A)=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
-&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \quad \text{w.h.p.} \label{simple1}
-\end{align}
-for some constant $\e>0$.
+&\left|\cal L(\hat A)-\frac{d^2}{p}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\Sigma(1)^{-1}  }\right| \nonumber\\
+&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2e}\kappa^2 +  p^{-1/4+e} (\sigma^2 +d^2) , \label{simple1}
+\end{align}
+for any small constant $e>0$, where we recall that $\Sigma(1)= (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
 \end{lemma}
 \begin{proof}
-
- Inserting equation \eqref{hatv_add1} into equation \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$, we get that w.h.p.,
-\begin{align}
-\te(\hat{\beta}_2^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\
-&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
-\end{align}
-In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order.
+Using Lemma \ref{lem_hat_v} and Fact \ref{lem_minv} (iii), we can obtain that with high probability,
+\begin{align}
+&\|\Sigma(1)^{-1}-\hat\Sigma^{-1}\| \le |\hat A-1|\|\Sigma(1)^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma^{-1}\| \label{est111}\\
+&\lesssim \left(\frac{d^2}{\kappa^2} + p^{-1/4+e}\right)\frac{(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}}{ \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}  + (\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^2  }\lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+e}\right),\nonumber
+\end{align}
+for any small constant $e>0$. With similar arguments, we can get that with high probability,
+\begin{align}\label{est222}
+&\left\|\left(\Sigma(1)^{-2}-\hat\Sigma^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+e} .
+\end{align}
+Moreover, using Fact \ref{lem_minv} (iii) we can bound that with high probability,
+$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
+which further implies that with high probability,
+\be\label{est333}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim p.\ee
+Now we bound the left-hand side of \eqref{simple1} as
+\begin{align*}
+&\left|\cal L(\hat A)-\frac{d^2}{p}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\Sigma(1)^{-1}  }\right| \\
+&\lesssim \left(|\hat A-1|^2 \kappa^2 + |\hat A-1|d^2\right)\cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} } \\
+&+ \frac{d^2}{p}\left|\tr\left[\left(\Sigma(1)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\Sigma(1)^{-1}-\hat\Sigma^{-1}  }\right|.
+\end{align*}
+Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple1}.
+% Inserting equation \eqref{hatv_add1} into equation \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$, we get that w.h.p.,
+%\begin{align}
+%\te(\hat{\beta}_2^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\
+%&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
+%\end{align}
+%In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order.
 Using Fact equation \eqref{lem_minv}, we have that
-$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim 1.$$
-Hence we need to choose that $p d^2 \sim \sigma^2$.
+%$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim 1.$$
+%Hence we need to choose that $p d^2 \sim \sigma^2$.
 On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$.

### 2020-10-02 arxiv/proof_examples.tex
revise

@@
 \begin{align}
-&\left|\cal L(\hat A)-\frac{d^2}{p}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\Sigma(1)^{-1}  }\right| \nonumber\\
+&\left|\cal L(\hat A)- d^2\cdot {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\Sigma(1)^{-1}  }\right| \nonumber\\
 &\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2e}\kappa^2 +  p^{-1/4+e} (\sigma^2 +d^2) , \label{simple1}
@@
 % \todo{switch the $a_3$ and $a_4$}
-\paragraph{Calculating the variance and bias terms.} For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}.
-%as follows.
-\begin{lemma}\label{prop_model_shift_tight}
-		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-		$\beta_2$ is a random vector that has i.i.d.
+\paragraph{Calculating the variance and bias terms.} Finally, we calculate the variance term $\sigma^2  \bigtr{\Sigma(1)^{-1}  }$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}, which will conclude Proposition \ref{cor_MTL_loss}.
+%For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
+%\begin{lemma}\label{prop_model_shift_tight}
+%		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
+%		$\beta_2$ is a random vector that has i.i.d.
 entries with mean $0$, variance $\kappa^2$ and finite moments up to any order, and $(\beta_1-\beta_2)$ is a random vector that is independent of $\beta_2$ and has i.i.d.
@@
 Denote
-		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in equation \eqref{defnpihat}.	Then we have with high probability,
-		\begin{align*}
-			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
-			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
-		\end{align*}
-		where $\Delta_{\vari}$ was defined in equation \eqref{Deltavarv}.
-\end{lemma}
-
-\begin{proof}%[Proof of Lemma \ref{prop_model_shift_tight}]
-The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace equation \eqref{bounddelta-} with a tighter bound.
+%		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in equation \eqref{defnpihat}.	Then we have with high probability,
+%		\begin{align*}
+%			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
+%			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
+%		\end{align*}
+%		where $\Delta_{\vari}$ was defined in equation \eqref{Deltavarv}.
+%\end{lemma}
+
+\begin{proof}[Proof of Proposition \ref{cor_MTL_loss}]
+%The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace equation \eqref{bounddelta-} with a tighter bound.
 We only describe the main difference in the following proof.
-
-For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
+%
+%For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
 entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
 Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
-\begin{align}
-&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2] \quad \text{w.h.p.},\label{anotherbeta}
-\end{align}
-where $\delta_{\bias}(v)$ was defined in equation \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
+%\begin{align}
+%&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+%&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
+%&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2] \quad \text{w.h.p.},\label{anotherbeta}
+%\end{align}
+%where $\delta_{\bias}(v)$ was defined in equation \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
 Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
-\begin{align*}
-v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
-\end{align*}
+%\begin{align*}
+%v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
+%\end{align*}
+
 Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using Fact equation \eqref{lem_minv}, we obtain that
@@
 In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
-\end{proof}
-
-\cor
 
@@
 	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$
-	\nc
+
+	will also use equation \eqref{apply derivlocal}
+\end{proof}
+
+\iffalse
 
@@
 \end{proof}
-
-\iffalse
 

### 2020-10-02 arxiv/diff_cov.tex
merge examples with Section 3 and 4

@@
 The full proof can be found in Section \ref{sec_maintools}.
+
+\paragraph{Example: Sample imbalance.}
+The above setting assumes that the feature covariates are the same across all tasks.
+Hence, the sample sizes are also the same among all tasks.
+Next, we assume that the feature covariates are different and consider what happens the sample sizes are different for different tasks.
+We consider a two-task case where both tasks have isotropic covariance matrices.
+%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
+	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
+%	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
+%	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
+%	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
+%	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
+%\begin{example}[Varying model distance]
+%\end{example}
+Using Theorem \ref{thm_main_RMT}, we derive the prediction loss of the hard parameter sharing estimator.
+Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
+
+\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
+	In the setting described above, assume further that a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
+	the signal and noise variances satisfy
+%	\be\label{choiceofpara0}
+%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
+	\be\label{choiceofpara0}
+	\sigma^2 \lesssim  \kappa^2   ,\quad  d^2 \ll {\kappa^2}.
+	\ee
+	%Let $B, A_1, A_2$ be the global minimum of equation \eqref{eq_mtl}. Then
+	The prediction loss of the hard parameter sharing estimator for task two satisfies that
+	\begin{align}\label{cor_MTL_error}
+	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
+	  \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  & \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+	& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + \frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
+	 \end{align}
+	 for a large constant $C>0$.
+\end{corollary}
+
+%It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
+We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
+The prediction loss of MTL has been given in Corollary \ref{cor_MTL_loss}.
+We can also calculate the prediction loss of STL easily using Fact \ref{lem_minv} (ii).
+The proof of the following claim will be given in Section \ref{app_iso_cov}.
+%\begin{claim} \label{claim_STL_loss}
+%Under the above isotropic setting for task two, we have that with high probability,
+%\begin{align*}
+%	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-\e}\sigma^2 )
+%	 \end{align*}
+%	 for any constant $\e\in (0,1/2)$.
+%\end{claim}
+%We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transitions from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.
+
+%\medskip
+%
+%\noindent{\bf Varying model distance.}
+%With Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss}, it is not hard to see
+%One can observe that as we increase the distance $pd^2$ between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
+More precisely, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases, while variance reduction from STL to MTL is $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$.
+%Therefore, while the variance of MTL still reduces compared to STL,
+%If the bias increases more than the amount of variance reduced, we will observe negative transfer.
+
+We apply Corollary \ref{cor_MTL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
+There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
+%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
+%Figure \ref{fig_model_shift} shows the result.
+%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
+
+%The proof of Proposition \ref{prop_dist_transition} involves two parts.
+%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
+%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
+%The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
+%A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
+%thus simplifying the general condition in Theorem \ref{thm_main_informal}.
+
+%In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
+%More generally, such results are still applicable when all task data are being added simultaneously.
+%On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
+%For such settings, we have also observed that adding more labeled data from one task does not always help.
+%Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
+%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
+
+More precisely, in the isotropic model, we consider what happens if we vary the source task sample size.
+For fixed model distance $pd^2$, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases and converges to $pd^2$ as the sample ratio $\rho_1/\rho_2$ increases, and the variance reduction $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$ also increases and converges to $\frac{\sigma^2}{\rho_2-1}$ as $\rho_1/\rho_2$ increases.
+The tradeoff between these two terms depends on $\rho_1$ in a nonlinear way that is more complicated than the one in the case of varying model distance.
+But from our results, one can check the following phenomena.
+If $\frac{\sigma^2}{\rho_2-1} > pd^2$, then the transfer is always positive.
+On the other hand, if $\frac{\sigma^2}{\rho_2-1} < pd^2$, then there is a transition from the positive transfer to negative transfer as $\rho_1/\rho_2$ increases.
+%Therefore, while the variance of MTL still reduces compared to STL,
+%If the bias increases more than the amount of variance reduced, we will observe negative transfer.
+Figure \ref{fig_size} provides a simulation result for such a setting (described in Appendix \ref{app_synthetic}).
+%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
+There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
+
+%\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
+%	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
+%	Then we have that
+%	\begin{itemize}
+%		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
+$$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
+%		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
+$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
+%	\end{itemize}
+%\end{proposition}
+%Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
+
+%We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
+%There are several unexplained observations near $y = 0$ caused by $\nu$.
+%The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
+
+\paragraph{Example: Covariate shift.} \label{sec_covshift}
+%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+%In general, the covariance matrices of the two tasks may be different such as in text classification.
+
+In our final example, we consider what happens when the covariance matrices are also different between different tasks, which are often called ``covariate shift''.
+Our results apply to arbitrary ``covariate shift'' and we consider a simple setting of two tasks.
+As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
+To illustrate our result, we assume that the first half of the singular values of $\Sigma^{1/2}\Sigma^{-1/2}$ are all equal to a parameter $\lambda$ and the rest are all equal to one.
+Our results imply that the prediction loss of the hard parameter sharing estimator is given as follows.
+%We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+%Hence, $\lambda$ measures the severity of the covariate shift.
+%	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
+%	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
+%	\end{example}
+
+%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
+%We compare different choices of $M$ that belong to the following bounded set.
+%Let $\lambda_i$ be the $i$-th singular value of $M$.
+%Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
+%{\begin{align*}
+%		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.}.
+%\end{align*}}
+%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
+\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{prop_covariate}
+	In the setting described above, assume further that a random-effects model holds for both tasks.
+	The prediction loss of $\hat{\beta}_2^{\MTL}$ for task two satisfies that
+	\begin{align*}
+		L(\hat{\beta}_2^{\MTL})
+	\end{align*}
+%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
+%	We have that
+%		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
+\end{corollary}
+
+\iffalse
+
+ \begin{claim}\label{claim_covar_shift}
+		In the setting of Proposition \ref{prop_covariate}, for any $M\in \cal S_\mu$ we have that
+		\[ g(M)=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.} \]
+	\end{claim}
+
+%Finally, in this subsection we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.
+
+\begin{proof}[Proof of Proposition \ref{prop_covariate}]
+
+ Denote the minimizer of $g$ by
+$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$
+We now calculate $g(M_0)$.
+
+Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
+\begin{align}\label{gvar_extra}
+g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
+\end{align}
+From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
+\be\label{est_a12extra}
+\frac{\rho_1-1}{\rho_1+\rho_2} < a_1(M)<  \frac{\rho_1+\rho_2-1}{\rho_1+\rho_2},\quad a_2(M) < \frac{\rho_2}{\rho_1+\rho_2}.
+\ee
+Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
+\begin{align}\label{approximateteM}
+\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
+\end{align}
+where
+$$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
+%With these two bounds, we can easily conclude \eqref{approxteM}.
+%
+%We have that the test error satisfies
+%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
+%where $\lambda_p$ is the smallest singular value of $p$ and
+%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
+%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+By AM-GM inequality, we observe that
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
+is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that
+\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
+On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
+\begin{align}\label{gvar_extra2}
+\begin{split}
+g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
+&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
+\end{split}
+\end{align}
+Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
+%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+\end{proof}
+\fi
+
+Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
+The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
+%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
+%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
+
+%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
+
+%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
+%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
+%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
+%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
 

### 2020-10-02 arxiv/experiments.tex
merge examples with Section 3 and 4

@@
 
-\subsection{Sample Imbalance}\label{sec_exp_sample}
+\subsection{The Same Covariates Setting: Sample Efficiency}
+
+%We validate that MTL performs better when the source task is more similar to the target task.
+%We show the result on the sentiment analysis tasks.
+%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
+%Figure \ref{fig_ab_sim} confirms the result.
+%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
+
+\begin{table}
+	\begin{center}
+		\begin{tabular}{c c c c c}
+			\toprule
+			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
+				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
+			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
+			\midrule
+			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
+			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
+			% {\bf CNN}  & 76\% & - & 32\% & -\\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+	\caption{Taskonomy experiment.}
+	\label{tab:taskonomy}
+\end{table}
+
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
+		\caption{Sample imbalance}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
+		\caption{Covariate shift}
+		\label{fig_covariate}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
+		\caption{Sample efficiency}
+		\label{fig_model_shift}
+	\end{subfigure}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
+	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
+	The $y$-axis measures the loss of STL minus MTL.}
+	\label{fig_model_shift_phasetrans}
+\end{figure}
+
+\subsection{The Different Covariates Setting: Sample Imbalance and Covariate Shift}\label{sec_exp_sample}
 
@@
 
-\subsection{Covariate Shift}
-
 \noindent\textit{Covariance alignemnt.}
@@
 \end{figure}
-
-\subsection{Sample Efficiency}
-
-%We validate that MTL performs better when the source task is more similar to the target task.
-%We show the result on the sentiment analysis tasks.
-%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
-%Figure \ref{fig_ab_sim} confirms the result.
-%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{c c c c c}
-			\toprule
-			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
-			\midrule
-			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-			% {\bf CNN}  & 76\% & - & 32\% & -\\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Taskonomy experiment.}
-	\label{tab:taskonomy}
-\end{table}

### 2020-10-03 arxiv/proof_examples.tex
revise

@@
 \subsubsection{Proof for Sample Imbalance}  
-We now give the proof of Proposition \ref{cor_MTL_loss}. As in the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following steps: 
+We now give the proof of Proposition \ref{cor_MTL_loss}. Similar to the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following steps: 
 \begin{itemize}
@@
 
-In the specific setting in Proposition \ref{cor_MTL_loss}, we can further simplify $\cal L(\hat A)$ using Lemma \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
-
-\begin{lemma}
+In the specific setting in Proposition \ref{cor_MTL_loss}, we can further simplify $\cal L(\hat A)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
+
+\begin{claim}
 In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
@@
 for any small constant $e>0$, where we recall that $\Sigma(1)= (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
-\end{lemma}
+\end{claim}
 \begin{proof}
@@
 We only describe the main difference in the following proof.
-%
 %For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
@@
 %\end{align*}
-
-Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using Fact equation \eqref{lem_minv}, we obtain that
-\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
-where
-$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining equation \eqref{anotherbeta} and equation \eqref{anotherwtbeta} we get
-\be\label{replaceest}
-  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
-\ee
-Now we can replace the estimate equation \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
-In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
-
-In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
-Then solving equations equation \eqref{eq_a12extra} and equation \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
+%Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ 
+Using \eqref{lem_cov_shift_eq}, we obtain that 
+\be\label{eq_var111}\bigtr{\Sigma(1)^{-1}  } = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1\id_p+a_2\id_p)^{-1}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
+with high probability. Then solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that with high probability,
 	\begin{align}
 		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
+		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} . \label{simplesovlea12}
+			\end{align}
+Inserting it into \eqref{eq_var111}, we obtain that 
+\be\label{eq_var112}\bigtr{\Sigma(1)^{-1}  } = \frac{p}{n_1+n_2} \cdot \frac{\rho_1+\rho_2}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})=  \frac{1}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})\ee
+with high probability.
+
+On the other hand, using Fact \ref{lem_minv} (iii), we can bound that with high probability,
+\begin{align}
+ \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii}  &\le {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
+ &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii} .\nonumber
+\end{align}
+To obtain this inequality, we used  
+$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \prec \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
+by Fact \ref{lem_minv} (iii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
+Using \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_p$ and $w$ being the $i$-th coordinate vector, we can calculate that 
+\begin{align}\label{eq_bias112}
+ \left(\Sigma(1)^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})
+\end{align}
+with high probability. Solving equation \eqref{eq_a34extra} with $a_1, a_2$ in \eqref{simplesovlea12} and $\lambda_i\equiv 1$, $1\le i\le p$, we can obtain that
+	\begin{align}
+		% a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad & a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
 		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
@@
 	\end{align}
-	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
-\be\label{Deltavar}
-\begin{split}
-\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
-\end{split}
-\ee
-with high probability, where 
-	\begin{align*}
-		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
-	\end{align*}
-	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
-	Next for the model shift bias
-	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
-	we can get from Lemma \ref{prop_model_shift_tight} that
-\be\label{Deltabeta} 
-\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
-	where 
-	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$
-
-	will also use equation \eqref{apply derivlocal}
-\end{proof}
+Inserting them into \eqref{eq_bias112}, we obtain that 
+\begin{align*}%\label{eq_bias113}
+ \left(\Sigma(1)^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} +\OO(p^{-c_\varphi})
+\end{align*}
+with high probability. In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use \eqref{apply derivlocal} to get that 
+\begin{align*}%\label{eq_bias113}
+\left| \left(\Sigma(1)^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{-\frac{\varphi-4}{2\varphi}}
+\end{align*}
+on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that 
+\begin{align*} 
+\left| \sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{1-\frac{\varphi-4}{2\varphi}}
+\end{align*}
+with high probability, which by Definition \ref{stoch_domination} gives that
+\begin{align}\label{eq_bias113}
+\left| p^{-1}\sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\le p^{-c_\varphi}
+\end{align}
+with high probability. Inserting \eqref{eq_bias113} into \eqref{eq_bias111}. we get
+\begin{align}
+& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\nonumber \\
+&\le  {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} \nonumber\\
+&  \le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\label{eq_bias114}
+\end{align}
+with high probability.
+
+Now plugging \eqref{eq_var112} and \eqref{eq_bias114} into \eqref{simple1}, we get
+\begin{align}
+\left|\cal L(\hat A)- -\frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right| \le   \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \nonumber\\
++C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2e}\kappa^2 +  p^{-1/4+e} (\sigma^2 +d^2) \right) \label{simple1add}
+\end{align}
+with high probability for some constant $C>0$. Then using Claim \ref{claim_largedev2} and noticing that the constant $e>0$ can be arbitrarily small, we conclude \eqref{cor_MTL_error}.
+\end{proof}
+%\begin{align}
+%				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
+%				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_1 a_4 - a_2 a_3)}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
+%%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+%%				= b_0.
+%			\end{align}
+%\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
+%where
+%$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
+%Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining equation \eqref{anotherbeta} and equation \eqref{anotherwtbeta} we get
+%\be\label{replaceest}
+%  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
+%\ee
+%Now we can replace the estimate equation \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
+In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
+
+%In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
+Then solving equations equation \eqref{eq_a12extra} and equation \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
+%	\begin{align}
+%		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
+%		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
+%		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
+%		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
+%	\end{align}
+%	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
+%\be\label{Deltavar}
+%\begin{split}
+%\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
+%\end{split}
+%\ee
+%with high probability, where 
+%	\begin{align*}
+%		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
+%	\end{align*}
+%	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
+%	Next for the model shift bias
+%	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
+%	we can get from Lemma \ref{prop_model_shift_tight} that
+%\be\label{Deltabeta} 
+%\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
+%	where 
+%	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$
 

### 2020-10-03 arxiv/examples.tex
revise

@@
-\section{Illustrative Examples}\label{sec_example}
+%\section{Illustrative Examples}\label{sec_example}
 
@@
 %Then we show that when source task sample size becomes large, covariate shift causes more negative effects.
-We discuss several examples to illustrate our results.
-Through these examples, we provide generalization bounds of hard parameter sharing estimators that depend explicitly on the sample sizes and the covariance matrices of the tasks.
-We use our generalization bounds to interpret several empirical phenomena that arises from applying hard parameter sharing in practice.
-For our examples, we assume that a random-effects model holds.
-We assume every $\beta_i$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
+%We discuss several examples to illustrate our results.
+%Through these examples, we provide generalization bounds of hard parameter sharing estimators that depend explicitly on the sample sizes and the covariance matrices of the tasks.
+%We use our generalization bounds to interpret several empirical phenomena that arises from applying hard parameter sharing in practice.
+%For our examples, we assume that a random-effects model holds.
+%We assume every $\beta_i$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
 %	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le 
-	  \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  \le & \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	& +Cp \left[p^{-c_\varphi}(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + d^4/\kappa^2\right],\nonumber
+	  \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  & \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+	& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + \frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
 	 \end{align}

### 2020-10-03 arxiv/examples.tex
finish section 3 with examples

@@
 We begin by considering a setting where the feature covariates are the same across all tasks but their labels are different.
-In the random-effects model, we assume that every $\beta_i$ is equal to a shared component $\beta_0$ plus a task-specific component.
-Suppose that the entries of $\beta_0$ are sampled i.i.d. from an isotropic Gaussian distribution of mean zero and variance $p^{-1}\kappa^2$.
-Suppose further that $\beta_i$ is equal to $\beta_0$ plus a random Gaussian vector whose coordinates all have mean zero and variance $p^{-1} d^2 / 2$.
-Thus, for any two $\beta_i$ and $\beta_j$, their distance is roughly $d^2$.
+
 Using our results, we show that the prediction loss of the hard parameter sharing estimator is as follows.

### 2020-10-03 arxiv/setup.tex
finish section 3 with examples

@@
 
-%\noindent\textbf{Positive/Negative transfer.}
-
-\subsection{Hard Parameter Sharing}
-
 \subsection{Random Matrices}
@@
 We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
+
+\subsection{Hard Parameter Sharing}\label{sec_hps}
+
+\paragraph{Random-effects model.}
+A natural special case of the linear model is when every $\beta_i$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
+Let $\beta_0$ denote the shared component whose entries are sampled i.i.d. from an isotropic Gaussian distribution of mean zero and variance $p^{-1}\kappa^2$.
+Let the task-specific component be a random Gaussian vector whose coordinates all have mean zero and variance $p^{-1} d^2 / 2$.
+Thus, for any two different $\beta_i$ and $\beta_j$, their distance is roughly $d^2$.
+%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+For our purpose, it is enough to think of the order of $d$ being $1/\sqrt{p}$ and $pd^2/\sigma^2$ being constant.
+%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
+We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.

### 2020-10-03 arxiv/proof_examples.tex
revise

@@
  \begin{align}
-		 g(A) \define & \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)+ \left(X^{(2)}\Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} + A X^{(2)}\Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2,
+		 g(A) \define & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+		 + & \left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)+ \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} + A X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2,
 		\label{eq_mtl_A12}
@@
 	where we denote
-	$$\Sigma\equiv \Sigma(A):= A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+	$$ \Sigma(A):= A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
 We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
@@
 &\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-&= \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon_1} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
-&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\Sigma^{-1} (X^{(2)})^\top \epsilon^{(2)}}  +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma^{-1}  (X^{(2)})^\top X^{(2)}\Sigma^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
-		&= \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-		&+ \sigma^2\tr\left[ \left(A^2 X^{(1)}\Sigma^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\right] +\sigma^2\tr\left[ \left(X^{(2)}\Sigma^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
-&+ 2 A^2 \sigma^2 \tr\left[ \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\Sigma^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
-		& = \left\| X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
+&= \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
+& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
+&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}}  +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
+		&= \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
+		&+ \sigma^2\tr\left[ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\right] +\sigma^2\tr\left[ \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
+&+ 2 A^2 \sigma^2 \tr\left[ \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
+		& = \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
 \end{align*}
@@
 &\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \nonumber\\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
-&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
+&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
+&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
 \end{align}
 where in the first step we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d.
-random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
-\begin{align*}
- &\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} \Sigma^{-1} (X^{(1)})^\top X^{(1)}\right] \\
- &=\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1} (X^{(2)})^\top X^{(2)}\right]+ A^2 \tr\left[  (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} \right] \\
- & = \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)}\right] .
-\end{align*}
- In the first step of the above derivation, we used that 
- $$(X^{(1)})^\top X^{(1)} \Sigma^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \Sigma^{-1}(X^{(1)})^\top X^{(1)}.$$
+Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
+\begin{align*}
+ & (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} + A^2   (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)}  \\
+ &=  (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} + A^2  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}  \\
+ & =   (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} .
+\end{align*}
+Here in the first step of the above derivation, we used that 
+ $$(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)}.$$
 
@@
  In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{-1/2+e_1}\cdot p\left(\sigma^2 + \kappa^2+d^2 \right) $$
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{1/2+e_1} \left(\sigma^2 + \kappa^2+d^2 \right) $$
 for any small constant $e_1>0$.
@@
  \begin{proof}
- \todo{add proof}
+By Fact \ref{lem_minv} (iii), we have that with high probability,
+ \be\label{op_X12}
+\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
+ \ee
+ and
+ \be\label{op_Sig1}
+\| \Sigma(A)^{-1}\|\le \frac1{A^2((\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}})+((\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}) }\lesssim \frac{1}{(A^2+1)p},
+ \ee
+ where we also used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$ for a small constant $\tau>0$.
+
+ Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
+ \begin{align*}
+ & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+ &=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,
+ \end{align*}
+ where
+ \begin{align*}
+&h_1(A):=  (\beta_1-A\beta_2)^\top (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)  ,\\
+& h_2(A) := {(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon_1}  ,\\
+& h_3(A):=  A^2 { (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
+& h_4(A):=  (\epsilon^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1), \\
+&h_5(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1),\\
+&h_6(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
+\end{align*}
+Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.
+
+For $h_1(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, we obtain the following estimate with high probability:
+\begin{align*}
+&\left|h_1(A) - \exarg{\beta_1,\beta_2}{h_1(A) \mid X_1, X_2}\right| \\
+&\le p^{\e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \\
+&\le p^{e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \\
+&\lesssim p^{1/2+e_1}\cdot \frac{(A-1)^2\kappa^2 + (A^2+1)d^2/2}{(A^2+1)^2}\lesssim p^{1/2+e_1}(\kappa^2 + d^2),
+\end{align*}
+for any small constant $\e_1>0$. Here in the last step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
+\begin{align*}
+&\left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \\
+&\le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \Sigma(A)^{-1} \right\|^2 \lesssim \frac{p}{(A^2+1)^2}.
+\end{align*}
+
  \end{proof}

### 2020-10-03 arxiv/proof_same_cov.tex
revise

@@
 
-	For equation \eqref{eq_gA_p2}, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, we obtain that the following holds with high probability:
+	For equation \eqref{eq_gA_p2}, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, we obtain that the following holds with high probability:
 	\begin{align}

### 2020-10-04 arxiv/proof_examples.tex
revise

@@
 & + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
-&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}}  +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
+&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \\
+& +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
 		&= \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
@@
 &h_1(A):=  (\beta_1-A\beta_2)^\top (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)  ,\\
-& h_2(A) := {(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon_1}  ,\\
+& h_2(A) := {(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
 & h_3(A):=  A^2 { (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
@@
 For $h_1(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, we obtain the following estimate with high probability:
-\begin{align*}
-&\left|h_1(A) - \exarg{\beta_1,\beta_2}{h_1(A) \mid X_1, X_2}\right| \\
-&\le p^{\e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \\
-&\le p^{e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \\
-&\lesssim p^{1/2+e_1}\cdot \frac{(A-1)^2\kappa^2 + (A^2+1)d^2/2}{(A^2+1)^2}\lesssim p^{1/2+e_1}(\kappa^2 + d^2),
-\end{align*}
-for any small constant $\e_1>0$. Here in the last step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
+Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $\e_1>0$:
+\begin{align}
+&\left|h_1(A) - \exarg{\beta_1,\beta_2}{h_1(A) \mid X_1, X_2}\right|\nonumber \\
+&\le p^{\e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
+&\le p^{e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
+&\lesssim p^{1/2+e_1}\cdot \frac{(A-1)^2\kappa^2 + (A^2+1)d^2/2}{(A^2+1)^2}\lesssim p^{1/2+e_1}(\kappa^2 + d^2).\label{eq_hA1}
+\end{align}
+ Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
 \begin{align*}
@@
 \end{align*}  
-
+Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+\be\label{eq_hA23}\left|h_2(A) - \exarg{\epsilon^{(1)}}{h_2(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2, \quad \left|h_3(A) - \exarg{\epsilon^{(2)}}{h_3(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2.\ee
+For $h_4(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $\e_1>0$:
+\begin{align}
+\left|h_4(A)\right| &\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]}\cdot \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
+&\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{e_1}\cdot \sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2} \cdot \left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\cdot  \left\|X^{(1)}\right\| \left\|\Sigma(A)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{1/2+e_1}\frac{\sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2}}{A^2+1} \lesssim p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
+\end{align}
+where in the fourth step we used $\left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
+With same argument, we can show that
+\be\label{eq_hA56} \left|h_5(A)\right| \le p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(A)\right| \le p^{1/2+e_1}\sigma^2,\ee
+with high probability for any small constant $e_1>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
+
+Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, which conclude the proof of Claim \ref{claim_largedev1}.
  \end{proof}
@@
 \paragraph{Calculating the prediction loss.} Now we calculate the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat A=\hat A_1/\hat A_2$:
-\begin{align*}
-L(\hat{\beta}_2^{\MTL}) &=\left|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right| \\
-&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,
-\end{align*}
+\begin{align}
+L(\hat{\beta}_2^{\MTL}) &=\left|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right| \nonumber\\
+&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,\label{Lbeta_HPS}
+\end{align}
 where we denoted
@@
  \begin{proof}
- \todo{add proof}
+ The proof of this claim is the same as the one for Claim \ref{claim_largedev1}, so we only give an outlier of proof without writing down all the details.
+We expand $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
+ \begin{align*}
+\cor L(\hat{\beta}_2^{\MTL}) &=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,
+\end{align*}
  \end{proof}

### 2020-10-04 arxiv/diff_cov.tex
finish section 3 with examples

@@
 \section{The Different Covariates Setting}\label{sec_diff}
+
+The different covariates setting differs from the same covariates setting in two key aspects.
+First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
+Second, the features of different tasks may have different shapes, a phenomenon that is often called ``covariate shift''.
+In this section, we show how to deal with the the above two aspects.
 
@@
 This is because the minimization problem is non-convex with respect to $A$ and $B$.
-Therefore, we consider an arbitrary local minimum of equation \eqref{eq_mtl} and provide generalization bounds that scale with key properties of task data such as sample sizes and covariate shifts.
+Therefore, we consider an arbitrary local minimum of equation \eqref{eq_mtl} and provide generalization bounds that scale with key properties of task data.
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.
 
-We first provide a key technical tool that we derived using recent developments in random matrix theory \cite{??}.
+We develop a key technical result using recent developments in random matrix theory.
 To motivate our study, we consider a specialized setting where the output layer weights $A_1, A_2$ are both equal to one.
@@
 	With high probability over the randomness of $X_1$ and $X_2$, we have the following limits:
-	\begin{enumerate}
-		\item[i)]  The variance equation converges to the following asymptotic limit
+
+	\noindent (i) The variance equation converges to the following asymptotic limit
 			\begin{align}\label{lem_cov_shift_eq}
@@
 			\end{align}
-		\item[ii)] For any fixed vector $w\in\real^p$ with unit norm, the bias equation converges to the following asymptotic limit
+	\noindent (ii) For any fixed vector $w\in\real^p$ with unit norm, the bias equation converges to the following asymptotic limit
 			\begin{align}\label{lem_cov_derv_eq}
@@
 			\end{align}
-	\end{enumerate}
 \end{theorem}
-\noindent{\textbf{Remark.}} Our result extends a well-known result on the inverse of sample covariance matrices.
+Our result extends a well-known result on the inverse of sample covariance matrices.
 In particular, by setting $X_1 = 0$, we obtain the second result in Fact \ref{lem_minv}.
 When $X_1=0$, it is not hard to solve $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ from equation \eqref{eq_a12extra}, and our result reduces to the case of a single sample covariance matrix.
-For a multivariate Gaussian random matrix, the result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, the result can be obtained using the Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
+For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
 
-By combining the bias and variance asymptotics, we obtain the generalization error of $\hat{\beta}_2^{\MTL}$.
-Since the proof is similar to the same covariates setting, we describe the key differences and omit the rest of the details.
-First, we will rescale $X_1$ by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
-Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
-For the rest of this section, we present the main ideas in the proof of Theorem \ref{thm_main_RMT}.
-%We will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
-The full proof can be found in Section \ref{sec_maintools}.
+As mentioned in the beginning of this section, different tasks may have different sample sizes and different feature covariance matrices.
+Under these scenarios, Theorem \ref{thm_main_RMT} shows the bias and variance asymptotics for the two-task case.
+Next, we use this result to study the impact of sample sizes and covariate shifts in hard parameter sharing.
 
-\paragraph{Example: Sample imbalance.}
-The above setting assumes that the feature covariates are the same across all tasks.
-Hence, the sample sizes are also the same among all tasks.
-Next, we assume that the feature covariates are different and consider what happens the sample sizes are different for different tasks.
-We consider a two-task case where both tasks have isotropic covariance matrices.
-%	Each task has sample size $n_1 = \rho_1 \cdot p$ and $n_2 = \rho_2 \cdot p$.
-	%And $X_1\in\real^{n_1\times p}, X_2\in\real^{n_2\times p}$ denote the covariates of the two tasks, respectively.
-%	For the ground truth linear model, we consider a random-effects model where the two tasks differ by an independent Gaussian vector.
-%	Specially, for task two, we assume that its model parameter, denoted by $\beta_2$, consists of i.i.d. Gaussian entries with mean zero and variance $\kappa^2$.
-%	For task one, we assume that its model parameter, denoted by $\beta_1$, is equal to $\beta_2$ plus i.i.d. Gaussian entries with mean $0$ and variance $d^2$.
-%	Therefore, the two tasks have different ground truth models. In particular, the distance between $\beta_1$ and $\beta_2$ roughly scales as $d^2 \cdot p$.
-%\begin{example}[Varying model distance]
-%\end{example}
-Using Theorem \ref{thm_main_RMT}, we derive the prediction loss of the hard parameter sharing estimator.
-Without loss of generality, we describe the result for task two and remark that a similar result for task one holds.
+\begin{example}[Sample ratio]
+	Our first example considers the impact of sample sizes on the prediction loss of hard parameter sharing.
+	We illustrate the above result in the random-effects model described in Section \ref{sec_hps}.
+	We further assume that the population covariance matrices of both tasks are isotropic.
 
-\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{cor_MTL_loss}
-	In the setting described above, assume further that a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-	the signal and noise variances satisfy
+	To apply Theorem \ref{thm_main_RMT}, we solve the self-consistent equations \eqref{eq_a12extra} and \eqref{eq_a34extra} by using $\lambda_i = 1$ for all $1\le i\le p$, and obtain explicit solutions for the weights $\set{a_i}_{i=1}^4$.
+Using the solved weights in the bias and variance asymptotic equations, we obtain the following result.
+
+\begin{corollary}\label{cor_MTL_loss}
+	In the setting of this example, assume further that
+	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
+	(i) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
 %	\be\label{choiceofpara0}
 %	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-	\be\label{choiceofpara0}
-	\sigma^2 \lesssim  \kappa^2   ,\quad  d^2 \ll {\kappa^2}.
-	\ee
-	%Let $B, A_1, A_2$ be the global minimum of equation \eqref{eq_mtl}. Then
-	The prediction loss of the hard parameter sharing estimator for task two satisfies that
+	%\be\label{choiceofpara0}
+	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength $d^2 \ll {\kappa^2}$. \HZ{what does $\ll$ mean exactly?}
+	The prediction loss of hard parameter sharing for task two satisfies that
 	\begin{align}\label{cor_MTL_error}
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  \left|L(\hat{\beta}_2^{\MTL}) -\frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right|  & \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|  & \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
 	& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + \frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
@@
 There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
+\end{example}
 
@@
 
-\paragraph{Example: Covariate shift.} \label{sec_covshift}
+\begin{example}[Covariate shift]\label{sec_covshift}
 %So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
@@
 %In general, the covariance matrices of the two tasks may be different such as in text classification.
-
 In our final example, we consider what happens when the covariance matrices are also different between different tasks, which are often called ``covariate shift''.
@@
 
-\iffalse
-
- \begin{claim}\label{claim_covar_shift}
-		In the setting of Proposition \ref{prop_covariate}, for any $M\in \cal S_\mu$ we have that
-		\[ g(M)=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.} \]
-	\end{claim}
-
-%Finally, in this subsection we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.
-
-\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-
- Denote the minimizer of $g$ by
-$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$
-We now calculate $g(M_0)$.
-
-Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-\begin{align}\label{gvar_extra}
-g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-\end{align}
-From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
-\frac{\rho_1-1}{\rho_1+\rho_2} < a_1(M)<  \frac{\rho_1+\rho_2-1}{\rho_1+\rho_2},\quad a_2(M) < \frac{\rho_2}{\rho_1+\rho_2}.
-\ee
-Inserting \eqref{est_a12extra} into \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-\begin{align}\label{approximateteM}
-\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-\end{align}
-where
-$$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}.
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that
-\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-\begin{align}\label{gvar_extra2}
-\begin{split}
-g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-\end{split}
-\end{align}
-Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-\end{proof}
-\fi
-
 Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
 The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
+\end{example}
+
+By combining the bias and variance asymptotics, we obtain the generalization error of $\hat{\beta}_2^{\MTL}$.
+Since the proof is similar to the same covariates setting, we describe the key differences and omit the rest of the details.
+First, we will rescale $X_1$ by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
+Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
+%For the rest of this section, we present the main ideas in the proof of Theorem \ref{thm_main_RMT}.
+%The full proof can be found in Section \ref{sec_maintools}.
 %Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.

### 2020-10-04 arxiv/diff_cov.tex
revise

@@
 	%\be\label{choiceofpara0}
-	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength $d^2 \ll {\kappa^2}$. \HZ{what does $\ll$ mean exactly?}
+	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
+	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$. 
 	The prediction loss of hard parameter sharing for task two satisfies that

### 2020-10-04 arxiv/proof_examples.tex
revise

@@
  \begin{proof}
- The proof of this claim is the same as the one for Claim \ref{claim_largedev1}, so we only give an outlier of proof without writing down all the details.
+ The proof of this claim is very similar to the one for Claim \ref{claim_largedev1}, where the only difference is that $\hat A$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat A$ can be pulled out as a coefficient.
+Here we only give an outline of the proof without writing down all the details.
 We expand $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
  \begin{align*}
-\cor L(\hat{\beta}_2^{\MTL}) &=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,
-\end{align*}
+L(\hat{\beta}_2^{\MTL}) &\cor  =  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2\\
+&=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,
+\end{align*}
+where
+
  \end{proof}

### 2020-10-04 arxiv/diff_cov.tex
section 4 wip

--- 2020-10-04 arxiv/diff_cov.tex
@@
 Under these scenarios, Theorem \ref{thm_main_RMT} shows the bias and variance asymptotics for the two-task case.
-Next, we use this result to study the impact of sample sizes and covariate shifts in hard parameter sharing.
+Next, we use this result to study the impact of varying sample sizes and covariate shifts in hard parameter sharing.
 
-\begin{example}[Sample ratio]
-	Our first example considers the impact of sample sizes on the prediction loss of hard parameter sharing.
+\begin{example}[Sample ratio]\label{ex_sample_ratio}
+	Our first example considers the impact of varying sample sizes on the prediction loss of hard parameter sharing.
 	We illustrate the above result in the random-effects model described in Section \ref{sec_hps}.
@@
 
-	To apply Theorem \ref{thm_main_RMT}, we solve the self-consistent equations \eqref{eq_a12extra} and \eqref{eq_a34extra} by using $\lambda_i = 1$ for all $1\le i\le p$, and obtain explicit solutions for the weights $\set{a_i}_{i=1}^4$.
-Using the solved weights in the bias and variance asymptotic equations, we obtain the following result.
+	To apply Theorem \ref{thm_main_RMT}, we solve the self-consistent equations \eqref{eq_a12extra} and \eqref{eq_a34extra} by using $\lambda_i = 1$ for all $1\le i\le p$.
+	For the variance limit, since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$, we have that $\tr[(a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] / (n_1 + n_2) = \frac{p}{n_1 + n_2 - p}$.
+	For the bias limit, we first solve $a_1$ and $a_2$ from equation \eqref{eq_a12extra}, and then solve $a_3$ and $a_4$ by using the solutions to equation \eqref{eq_a34extra}.
+	Using the solved weights in the bias and variance limit equations, we obtain the following result.
 
 \begin{corollary}\label{cor_MTL_loss}
-	In the setting of this example, assume further that
+	In the setting of Example \ref{ex_sample_ratio}, assume that
 	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-	(i) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
+	(i) task one's sample size is at least $n_1 \ge \min(\frac{17}{\varepsilon^2}, 50) \cdot p$ for a fixed positive value $\varepsilon$, and task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
+	(ii) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
 %	\be\label{choiceofpara0}
@@
 	%\be\label{choiceofpara0}
-	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength $d^2 \ll {\kappa^2}$. \HZ{what does $\ll$ mean exactly?}
+	(iii) the task-specific variance of $\beta_i$ is much smaller than the signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$. \HZ{check}
 	The prediction loss of hard parameter sharing for task two satisfies that
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|  & \le  \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + \frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
+	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2).
+	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
 	 \end{align}
-	 for a large constant $C>0$.
+%	 for a large constant $C>0$.
 \end{corollary}
@@
 
-%\medskip
-%
 %\noindent{\bf Varying model distance.}
@@
 
-We apply Corollary \ref{cor_MTL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
+%We apply Corollary \ref{cor_MTL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
 We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
+%There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
 %We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
@@
 
-More precisely, in the isotropic model, we consider what happens if we vary the source task sample size.
-For fixed model distance $pd^2$, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases and converges to $pd^2$ as the sample ratio $\rho_1/\rho_2$ increases, and the variance reduction $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$ also increases and converges to $\frac{\sigma^2}{\rho_2-1}$ as $\rho_1/\rho_2$ increases.
+In the above result, we see that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance and a noise variance term.
+We use the above result to explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
+In particular, consider the prediction loss of hard parameter sharing as we fix $n_2$ and vary $n_1$.
+First, the noise variance term always reduces as $n_1$ increases.
+Second, when $n_2 \ge \frac{3}{2} p$, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
+Therefore, we conclude that the \textit{optimal} sample ratio between $n_1$ and $n_2$ is one of three cases:
+(i) $n_1 = 0$, and the prediction loss reduces to that of single-task learning for task two;
+(ii) $n_1 = \infty$, and the prediction loss reduces to the task-specific variance $d^2$;
+(iii) the critial point where the derivative of the bias and variance terms is zero.
+Furthermore, we observe the following trend by comparing the conditions of $n_1 = 0$ and $n_1 = \infty$:
+\begin{itemize}
+	\item If $d^2$ is smaller than the prediction loss of STL for task two, then the prediction loss of hard parameter sharing is always lower than STL.
+That is, task one always transfers positively to task two.
+	\item Otherwise, as the sample ratio between $n_1$ and $n_2$ increases, task one transfers positively to task two initially, but transfers negatively eventually.
+\end{itemize}
+%Therefore, while the variance of MTL still reduces compared to STL,
+%If the bias increases more than the amount of variance reduced, we observe negative transfer.
+%of MTL increases and converges to $pd^2$ as the sample ratio $\rho_1/\rho_2$ increases, and the variance reduction $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$ also increases and converges to $\frac{\sigma^2}{\rho_2-1}$ as $\rho_1/\rho_2$ increases.
 The tradeoff between these two terms depends on $\rho_1$ in a nonlinear way that is more complicated than the one in the case of varying model distance.
@@
 %If the bias increases more than the amount of variance reduced, we will observe negative transfer.
-Figure \ref{fig_size} provides a simulation result for such a setting (described in Appendix \ref{app_synthetic}).
+%Figure \ref{fig_size} provides a simulation result for such a setting (described in Appendix \ref{app_synthetic}).
 %We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
+%There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
 \end{example}
@@
 Our results imply that the prediction loss of the hard parameter sharing estimator is given as follows.
+
+	In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
+When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
+When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
+We provide a theoretical justification now.
+
+\begin{proof}[Theoretical justification of Example \ref{ex_complement}]
+We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+Then equations in equation \eqref{eq_a12extra} become
+\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
+\ee
+%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to equation \eqref{compleeq}.
+After solving these, with equation \eqref{gvar_extra} we get that w.h.p.,
+\be\label{testcomple}
+ \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
+
+%First we notice that the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
+In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
+Then for any $\lambda$, the test error in equation \eqref{testcomple} takes the value
+%$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
+
+%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
+$M=\id$ case) when $n_1<n_2$.
+On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
+We now study the behavior of $f$ as $\lambda$ changes.
+%This phenomenon can be also explained using our theory.
+We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with equation \eqref{compleeq}, we can rewrite
+$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
+Then we can compute that
+\begin{align*}
+f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
+\end{align*}
+From this expressions, we observe the following behaviors.
+\begin{itemize}
+\item[(i)] If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}).
+Hence $f(\lambda)>f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)>\te(\hat \beta_{2}^{\MTL},1)$.
+
+\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $f(\lambda)< f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
+
+\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
+%, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
+\end{itemize}
+This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c),
+\end{proof}
+
 %We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
@@
 %	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{prop_covariate}
-	In the setting described above, assume further that a random-effects model holds for both tasks.
-	The prediction loss of $\hat{\beta}_2^{\MTL}$ for task two satisfies that
-	\begin{align*}
-		L(\hat{\beta}_2^{\MTL})
-	\end{align*}
+%\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{prop_covariate}
+%	In the setting described above, assume further that a random-effects model holds for both tasks.
+%	The prediction loss of $\hat{\beta}_2^{\MTL}$ for task two satisfies that
+%	\begin{align*}
+%		L(\hat{\beta}_2^{\MTL})
+%	\end{align*}
 %	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
@@
 %		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-\end{corollary}
-
-Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
-The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
+%\end{corollary}
+%Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
+%The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
 \end{example}

### 2020-10-04 arxiv/proof_examples.tex
section 4 wip

--- 2020-10-04 arxiv/proof_examples.tex
@@
 
-\subsubsection{Proof for Sample Imbalance}  
+%\subsubsection{Proof for Sample Imbalance}
 We now give the proof of Proposition \ref{cor_MTL_loss}. Similar to the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following steps: 
@@
 \end{proof}
-
+ \fi
+
+\iffalse
 In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.

### 2020-10-04 arxiv/proof_examples.tex
revise

@@
  Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
- \begin{align*}
+ \begin{align}
  & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
- &=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,
- \end{align*}
+ &=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,\label{expand_6}
+ \end{align}
  where
@@
  In the setting of Proposition \ref{cor_MTL_loss}, if $\hat A=\OO(1)$, then we have that with high probability,
-$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat A)\right| \le p^{-1/2+e}\cdot p\left(\sigma^2 +\kappa^2 +d^2 \right),$$
+$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat A)\right| \le p^{-1/2+e} \left(\sigma^2 +\kappa^2 +d^2 \right),$$
 for any small constant $e>0$. Here we introduced the function
@@
 Here we only give an outline of the proof without writing down all the details.
-We expand $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
- \begin{align*}
-L(\hat{\beta}_2^{\MTL}) &\cor  =  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2\\
-&=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,
-\end{align*}
-where
-
+Recall that $\beta_0$ is the shared component of $\beta_1$ and $\beta_2$ with i.i.d.
+Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
+Moreover, we denote the task-specific components by $\wt\beta_1$ and $\wt\beta_2$, whose entries i.i.d.
+Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$.
+Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
+ \begin{align}
+L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A -\hat A^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat A\wt \beta_1 - (X^{(1)})^\top X^{(1)}  \hat A^2\wt \beta_2 \right] \right.
+\\
+&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
+\end{align}
+As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}.
+For example, for the main term $\hat A^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
+Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $e>0$:
+\begin{align*}
+&\hat A^2 \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1 - d^2 \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
+&\le p^e\cdot p^{-1}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
+&\le p^{-1/2+\e}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+\e}d^2.
+\end{align*} 
+For the cross term $\hat A \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $e>0$:
+\begin{align*}
+&|\hat A |\cdot \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right| \le p^e \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \|_F \\
+&\lesssim p^{e}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \| \lesssim p^{-1/2+e}\sigma d\le p^{-1/2+e}(\sigma^2+ d^2).
+\end{align*}
+The rest of the terms in the expansion of \eqref{expand_15} can be bounded in the same way, and we omit the details.
  \end{proof}

### 2020-10-04 arxiv/diff_cov.tex
revise
finish section 4

@@
 	Suppose that $X_1$ and $X_2$ are both random matrices that satisfy Assumption \ref{assume_rm}.
-	Assume further that: a) the singular values of $M$ are all greater than $\tau$ and less than $1/\tau$; b) the sample size of task two is greater than $(1 + \tau) p$.
+	Assume that: a) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$; b) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
 	With high probability over the randomness of $X_1$ and $X_2$, we have the following limits:
@@
 Our result extends a well-known result on the inverse of sample covariance matrices.
-In particular, by setting $X_1 = 0$, we obtain the second result in Fact \ref{lem_minv}.
-When $X_1=0$, it is not hard to solve $a_1 = 0$ and $a_2 = (n_2-p) / n_2$ from equation \eqref{eq_a12extra}, and our result reduces to the case of a single sample covariance matrix.
+If $X_1$ is zero, then we obtain Fact \ref{lem_minv}(ii) as a special case.
+To see this, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to the variance limit.
+\HZ{go to intro}
 For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
@@
 
-As mentioned in the beginning of this section, different tasks may have different sample sizes and different feature covariance matrices.
-Under these scenarios, Theorem \ref{thm_main_RMT} shows the bias and variance asymptotics for the two-task case.
-Next, we use this result to study the impact of varying sample sizes and covariate shifts in hard parameter sharing.
+%As mentioned in the beginning of this section, different tasks may have different sample sizes and different feature covariance matrices.
+%Under these scenarios, Theorem \ref{thm_main_RMT} shows the bias and variance asymptotics for the two-task case.
+One can see that both the variance limit and the bias limit depend heavily on both tasks' samples sizes and the covariate shift matrix $M$.
+Next, we use our result to study how varying sample sizes and covariate shifts affects hard parameter sharing, respectively.
 
 \begin{example}[Sample ratio]\label{ex_sample_ratio}
-	Our first example considers the impact of varying sample sizes on the prediction loss of hard parameter sharing.
-	We illustrate the above result in the random-effects model described in Section \ref{sec_hps}.
-	We further assume that the population covariance matrices of both tasks are isotropic.
+	We first consider the impact of varying sample sizes.
+	Consider the random-effects model from Section \ref{sec_hps}, with both tasks having an isotropic population covariance matrix.
 
-	To apply Theorem \ref{thm_main_RMT}, we solve the self-consistent equations \eqref{eq_a12extra} and \eqref{eq_a34extra} by using $\lambda_i = 1$ for all $1\le i\le p$.
-	For the variance limit, since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$, we have that $\tr[(a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] / (n_1 + n_2) = \frac{p}{n_1 + n_2 - p}$.
-	For the bias limit, we first solve $a_1$ and $a_2$ from equation \eqref{eq_a12extra}, and then solve $a_3$ and $a_4$ by using the solutions to equation \eqref{eq_a34extra}.
-	Using the solved weights in the bias and variance limit equations, we obtain the following result.
+	In applying Theorem \ref{thm_main_RMT} to the above setting, we first solve the self-consistent equations \eqref{eq_a12extra} by using $\lambda_i = 1$ for all $1\le i\le p$.
+	This gives us the variance limit $\tr[(a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] / (n_1 + n_2) = \frac{p}{n_1 + n_2 - p}$, since we have that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$.
+	Secondly, we solve the self-consistent equations \eqref{eq_a34extra} given that we already know $a_1$ and $a_2$.
+	This gives us the bias limit.
+	Combined together, we obtain the following corollary, which requires natural assumptions over the random-effects model.
 
@@
 	%\be\label{choiceofpara0}
-	(iii) the task-specific variance of $\beta_i$ is much smaller than the signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$. \HZ{check}
+%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
+%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
+	(iii) the task-specific variance of $\beta_i$ is much smaller than the shared signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$.
 	The prediction loss of hard parameter sharing for task two satisfies that
@@
 
-In the above result, we see that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance and a noise variance term.
-We use the above result to explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
-In particular, consider the prediction loss of hard parameter sharing as we fix $n_2$ and vary $n_1$.
-First, the noise variance term always reduces as $n_1$ increases.
-Second, when $n_2 \ge \frac{3}{2} p$, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
-Therefore, we conclude that the \textit{optimal} sample ratio between $n_1$ and $n_2$ is one of three cases:
-(i) $n_1 = 0$, and the prediction loss reduces to that of single-task learning for task two;
-(ii) $n_1 = \infty$, and the prediction loss reduces to the task-specific variance $d^2$;
-(iii) the critial point where the derivative of the bias and variance terms is zero.
-Furthermore, we observe the following trend by comparing the conditions of $n_1 = 0$ and $n_1 = \infty$:
+Our result shows that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance $d^2$ and a noise variance term that scales with $\sigma^2$.
+In the following, we explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
+Consider the prediction loss if we fix $n_2$ and increase $n_1$.
+First, the noise variance term in Corollary \ref{cor_MTL_loss} always reduces as $n_1$ increases.
+Second, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
+Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
+(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
+(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
+(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
+
+Based on this observation, we have the following trend when we fix $n_2$ and increase $n_1$:
 \begin{itemize}
-	\item If $d^2$ is smaller than the prediction loss of STL for task two, then the prediction loss of hard parameter sharing is always lower than STL.
+	\item If $d^2$ is smaller than the prediction loss of STL for task two $\frac{\sigma^2 p}{n_2 - p}$, then the prediction loss of hard parameter sharing is always lower than STL.
 That is, task one always transfers positively to task two.
-	\item Otherwise, as the sample ratio between $n_1$ and $n_2$ increases, task one transfers positively to task two initially, but transfers negatively eventually.
+	\item Otherwise, task one transfers positively to task two initially, but transfers negatively eventually.
 \end{itemize}
@@
 %In general, the covariance matrices of the two tasks may be different such as in text classification.
-In our final example, we consider what happens when the covariance matrices are also different between different tasks, which are often called ``covariate shift''.
-Our results apply to arbitrary ``covariate shift'' and we consider a simple setting of two tasks.
-As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-To illustrate our result, we assume that the first half of the singular values of $\Sigma^{1/2}\Sigma^{-1/2}$ are all equal to a parameter $\lambda$ and the rest are all equal to one.
-Our results imply that the prediction loss of the hard parameter sharing estimator is given as follows.
-
-	In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
-When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-We provide a theoretical justification now.
-
-\begin{proof}[Theoretical justification of Example \ref{ex_complement}]
-We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
+Our second example studies the impact of varying covariate shifts on the variance limit.
+%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
+Recall that the matrix $M$ captures the geometry of covariate shifts.
+Suppose that half of the singular values of $M$ are equal to a parameter $\lambda > 0$ and the other half are equal to $\lambda^{-1}$.
+We observe the following dichotomy on the impact of covariate shifts.
+\begin{itemize}
+	\item If $n_1 \ge n_2$, then the variance (limit) of hard parameter sharing is smallest when $\lambda = 1$ or there is no covariate shift.
+	\item If $n_1 < n_2$, then having covariate shifts ($\lambda \neq 1$) always helps reduce variance (limit).
+\end{itemize}
+To see this, we first write the variance limit for different values of $\lambda$ as follows
+\begin{align*}
+	\bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
+	= \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}
+	= \frac{1}{2}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
+\end{align*}
+Denote the above function by $f(\lambda)$.
+We compare $f(\lambda)$ with $f(1)$, and observe that
+\[ 2f(\lambda) - 2f(1) = {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
+	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p}, \]
+where we used the first part of equation \eqref{lem_cov_shift_eq}.
+Next, one can verify that the above equation is equal to $(2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1)$, for a fixed and positive function $g(\lambda, a_1)$ (details omitted).
+Hence, whether or not $f(\lambda)$ is small than $f(1)$ is decided by $a_1$.
+To solve $a_1$, we present an informal argument that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
+Intuitively, with the current spectrum of $M$, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations.
+Hence, when $n_1 \ge n_2$, we expect that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
+Vice serva when $n_1 < n_2$.
+A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} by replacing half of the singular with $\lambda$ and the other half with $\lambda^{-1}$.
+We omit the details.
+%We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
 Then equations in equation \eqref{eq_a12extra} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\ee
+%\begin{align*}
+%	a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{n_1}{n_1 + n_2}.
+%\end{align*}
 %It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to equation \eqref{compleeq}.
-After solving these, with equation \eqref{gvar_extra} we get that w.h.p.,
-\be\label{testcomple}
- \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
-
+%After solving these, with equation \eqref{gvar_extra} we get that w.h.p.,
+%\be\label{testcomple}
+% \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
 %First we notice that the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
@@
 %$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-
 %Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
@@
 On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-We now study the behavior of $f$ as $\lambda$ changes.
+%We now study the behavior of $f$ as $\lambda$ changes.
 %This phenomenon can be also explained using our theory.
-We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with equation \eqref{compleeq}, we can rewrite
-$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
-Then we can compute that
-\begin{align*}
-f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-\end{align*}
-From this expressions, we observe the following behaviors.
-\begin{itemize}
-\item[(i)] If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}).
-Hence $f(\lambda)>f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)>\te(\hat \beta_{2}^{\MTL},1)$.
-
-\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $f(\lambda)< f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
-
-\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
+%We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with equation \eqref{compleeq}, we can rewrite
+%$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
+%Then we can compute that
+%\begin{align*}
+%f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+%&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
+%\end{align*}
+Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$; if $n_1< n_2$, then $f(\lambda)< f(1)$. % which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
+%\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
 %, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
-\end{itemize}
-This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c),
-\end{proof}
+%\end{itemize}
+%This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c),
 
@@
 %	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-%	\end{example}
 
@@
 
-By combining the bias and variance asymptotics, we obtain the generalization error of $\hat{\beta}_2^{\MTL}$.
-Since the proof is similar to the same covariates setting, we describe the key differences and omit the rest of the details.
+As a remark, by combining the bias and variance asymptotics, we can obtain the generalization error of hard parameter sharing for any local minimum solutions $(A, B)$.
+Since the proof is similar to the same covariates setting and Example \ref{cor_MTL_loss}, we describe the main differences and omit the rest of the details.
 First, we will rescale $X_1$ by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
-Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ with $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
-%For the rest of this section, we present the main ideas in the proof of Theorem \ref{thm_main_RMT}.
-%The full proof can be found in Section \ref{sec_maintools}.
+Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ by $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
+For the rest of this section, we present the main ideas in the proof of Theorem \ref{thm_main_RMT}.
+The full proof can be found in Section \ref{sec_maintools}.
 %Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.

### 2020-10-04 arxiv/diff_cov.tex
section 5 wip

@@
 Second, the features of different tasks may have different shapes, a phenomenon that is often called ``covariate shift''.
-In this section, we show how to deal with the the above two aspects.
+In this section, we show how to deal with these two aspects.
 
-When the covariates across tasks are different, we can no longer obtain an optimal solution for minimizing equation \eqref{eq_mtl} as in Claim \ref{lem_exp_opt}.
+Unlike the previous section, we no longer have an optimal solution for $A$.
 This is because the minimization problem is non-convex with respect to $A$ and $B$.
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2).
+	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2) +{\color{red} p^{-c_\infty}\cdot \OO(\kappa^2)}.
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
@@
 	 \end{align}
+	 {\color{red}[FY: there is an extra $\kappa^2$ term]}
 %	 for a large constant $C>0$.
@@
 (iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
+The proof can be found in Appendix \ref{app_iso_cov}.
 
@@
 
-As a remark, by combining the bias and variance asymptotics, we can obtain the generalization error of hard parameter sharing for any local minimum solutions $(A, B)$.
-Since the proof is similar to the same covariates setting and Example \ref{cor_MTL_loss}, we describe the main differences and omit the rest of the details.
-First, we will rescale $X_1$ by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
-Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ by $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
-For the rest of this section, we present the main ideas in the proof of Theorem \ref{thm_main_RMT}.
-The full proof can be found in Section \ref{sec_maintools}.
+As a remark, by combining the bias and variance asymptotics, we can also obtain a generalization bound for any local minimum solutions $(A, B)$.
+The proof is similar to Theorem \ref{thm_many_tasks} and Corollary \ref{cor_MTL_loss}.
+We describe the differences and omit the details.
+First, we rescale $X_1$ (and $\Sigma^{(1)}$) by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
+Second, we approximate sample covariance ${X^{(1)}}^{\top}X^{(1)} / n_1$ by its expectation $\Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
+For the rest of this section, we present the main ideas for proving Theorem \ref{thm_main_RMT}.
 %Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
 %This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.
 

### 2020-10-04 arxiv/experiments.tex
section 5 wip

@@
 We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
+
+\subsection{Simulation Studies}\label{sec_simulation}
+
+	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
+	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
+	\begin{itemize}
+		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
+	The noise level is $\sigma = 5$.
+	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
+	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
+	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
+		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
+	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
+	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
+	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
+	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
+	This can be achieved similarly by rescaling the task data.
+	\end{itemize}
+
+%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
+%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
+%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
+%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
+%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
+%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
+
+%\begin{table}
+%	\begin{center}
+%		\begin{tabular}{c c c c c}
+%			\toprule
+%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
+%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
+%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
+%			\midrule
+%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
+%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
+			% {\bf CNN}  & 76\% & - & 32\% & -\\
+%			\bottomrule
+%		\end{tabular}
+%	\end{center}
+%	\caption{Taskonomy experiment.}
+%	\label{tab:taskonomy}
+%\end{table}
+
+\begin{figure}[!t]
+		\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
+		\caption{Sample efficiency}
+		\label{fig_model_shift}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
+		\caption{Sample ratio}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.32\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
+		\caption{Covariate shift}
+		\label{fig_covariate}
+	\end{subfigure}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
+	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
+	The $y$-axis measures the loss of STL minus MTL.}
+	\label{fig_model_shift_phasetrans}
+\end{figure}
+
+\subsection{Further Studies on a Text Classification Task}\label{sec_text}
+
+We consider a text classification task as follows.
+
+{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR) \cite{pang2005seeing}, sentence subjectivity (SUBJ) \cite{pang2004sentimental}, customer reviews (CR) \cite{hu2004mining}, question type (TREC) \cite{li2002learning}, opinion polarity (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) tasks \cite{socher2013recursive}.
+%The question is to predict positive or negative sentiment expressed in the text.
+We use an embedding layer with GloVe embeddings \cite{pennington2014glove}
+followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.
+
+%multi-layer perceptron (MLP), LSTM, CNN on all tasks
+%We use this task to verify our theoretical results on model capacity and task covariance in real world.
+
+%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
+%There are 14 diseases (tasks) for every image that we would like to predict.
+%We use densenet121 as the shared module \cite{huang2017densely}.
+%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
+%This dataset is curated where the labels
+%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
+
+%\paragraph{Image and Text Classification Settings}\label{app_it}
+
+For the text classification experiment, we encode each word using the GLoVe word embeddings.%
+\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
+We evaluate three model choices.
+For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
+For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
+
+%\textit{Predicting transfer effect via STL results.}
+%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
+%A common challenge in the study of MTL is that the results can be hard to understand.
+%It is difficult to predict when MTL performs well without running extensive trials.
+%Our insight is that we can use STL results to help understand MTL results.
+%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
+%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
+%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
+%The results show that STL results are indicative of MTL results.
+
+\paragraph{Sample ratio.}
+In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
+Sample size: We vary the sample size of the source task from $100$ to $3000$.
+
+\textit{Towards computing the optimal sample ratio.}
+An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
+In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
+More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
+Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
+\squishlist
+	\item We divide the source task data into $S$ batches.
+	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
+	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
+	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
+\squishend
+
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+			\For{$j = 1,\dots, T$}
+				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+			\EndFor
+			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+				\State \textbf{break}
+			\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
+For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
+We add $20\%$ of source task samples for every $T = 2$ epochs.
+The total number of epochs is $20$.
+We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
+
+For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
+Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
+We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
+We run $20$ epochs in total.
+%\textbf{The training procedure and baseline.}
+For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
+The baseline training schedule for MTL is the round-robin training schedule.
+%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
+We measure the test accuracy of predicting a target task.
+We measure computational cost by summing over all epochs the number of samples used in every epoch.
+
+%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
+%\squishlist
+%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
+%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
+%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
+%TREC is less similar to MR because the task is about question types.
+%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
+
+First, we show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
+Over all $15$ pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve similar performance on the target task, compared to the MTL baseline.
+Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{incrementally} during training.
+
+%\textbf{Improving transfer learning training efficiency.}
+%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
+%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
+
+Our next result shows the incremental training schedule applies to multiple tasks as well.
+In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
+As a further validation, excluding TREC, we observe similar comparative results.
+%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
+%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
+%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
+
+\begin{figure}[!t]
+	\centering
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
+		\caption{Task similarity}
+		\label{fig_ab_sim}
+	\end{subfigure}%
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
+		\caption{Sample size}
+		\label{fig_ab_data}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
+		\caption{Covariate shift}
+		\label{fig_ab_cov}
+	\end{subfigure}
+	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
+	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
+	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves more over the baseline.
+	Note: (S) denotes the source task and (T) denotes the target task.}
+	\label{fig_ablation}
+	\vspace{-0.15in}
+\end{figure}
 
@@
 
-\subsection{Experimental Setup}
-
-We consider a text classification task and an image classification task as follows.
-
-{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR) \cite{pang2005seeing}, sentence subjectivity (SUBJ) \cite{pang2004sentimental}, customer reviews (CR) \cite{hu2004mining}, question type (TREC) \cite{li2002learning}, opinion polarity (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) tasks \cite{socher2013recursive}.
-%The question is to predict positive or negative sentiment expressed in the text.
-We use an embedding layer with GloVe embeddings \cite{pennington2014glove}
-followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.
-
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-
-{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-There are 14 diseases (tasks) for every image that we would like to predict.
-We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-
-\paragraph{Synthetic Settings}\label{app_synthetic}
-	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
-	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
-	\squishlist
-		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
-	The noise level is $\sigma = 5$.
-	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
-	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
-	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
-		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
-	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
-		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
-	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
-	This can be achieved similarly by rescaling the task data.
-	\squishend
-
-\paragraph{Image and Text Classification Settings}\label{app_it}
-
-For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-We evaluate three model choices.
-For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
-For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
-
-\textit{Predicting transfer effect via STL results.}
-We simplify the setup of this experiment by fixing the sample sizes of every task pair.
-For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
-We randomly sample these many data points from the task.
-The sample size of the target task is $1000$.
-For image classification tasks, the training sample size is $10,000$ for every task.
-
-\textit{Mitigating negative transfer via incremental training.}
-For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
-We add $20\%$ of source task samples for every $T = 2$ epochs.
-The total number of epochs is $20$.
-We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
-
-For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
-Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
-We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
-We run $20$ epochs in total.
-%\textbf{The training procedure and baseline.}
-For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
-The baseline training schedule for MTL is the round-robin training schedule.
-%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
-We measure the test accuracy of predicting a target task.
-We measure computational cost by summing over all epochs the number of samples used in every epoch.
-
-\textit{Validating the Theoretical Results.}
-We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-\squishlist
-	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-TREC is less similar to MR because the task is about question types.
-Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-	\item Sample size: We vary the sample size of the source task from $100$ to $3000$.
-	\item Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
-	We fix the sample size of the target task as $1000$.
-\squishend
-
-%\subsection{Validating the Theoretical Results}\label{sec_exp_ab}
-%We first validate our theoretical results in Section \ref{sec_similarity} and \ref{sec_data_size}.
-%In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
-%We select each task pair based on our domain knowledge.
-%We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
-%The rest of experimental procedures are left to Appendix \ref{app_it}.
-
-\subsection{The Same Covariates Setting: Sample Efficiency}
-
-%We validate that MTL performs better when the source task is more similar to the target task.
-%We show the result on the sentiment analysis tasks.
-%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
-%Figure \ref{fig_ab_sim} confirms the result.
-%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{c c c c c}
-			\toprule
-			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
-			\midrule
-			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-			% {\bf CNN}  & 76\% & - & 32\% & -\\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-	\caption{Taskonomy experiment.}
-	\label{tab:taskonomy}
-\end{table}
-
-\begin{figure}[!t]
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
-		\caption{Sample imbalance}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
-		\caption{Covariate shift}
-		\label{fig_covariate}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-		\caption{Sample efficiency}
-		\label{fig_model_shift}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
-	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
-	The $y$-axis measures the loss of STL minus MTL.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
-
-\subsection{The Different Covariates Setting: Sample Imbalance and Covariate Shift}\label{sec_exp_sample}
-
-%\textit{Predicting transfer effect via STL results.}
-%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-%A common challenge in the study of MTL is that the results can be hard to understand.
-%It is difficult to predict when MTL performs well without running extensive trials.
-%Our insight is that we can use STL results to help understand MTL results.
-%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
-
-In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
-Finally, we validate the algorithmic consequence of Section \ref{sec_covshift}.
-
-\textit{Mitigating negative transfer via incremental training.}
-\noindent\textit{Mitigating negative transfer.}
-An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
-In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-\squishlist
-	\item We divide the source task data into $S$ batches.
-	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
-	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
-	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\squishend
-
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-First, we show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
-Over all $15$ pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve similar performance on the target task, compared to the MTL baseline.
-Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{incrementally} during training.
-
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-
-Our next result shows the incremental training schedule applies to multiple tasks as well.
-In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
-As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-\begin{figure}[!t]
-	\centering
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-		\caption{Task similarity}
-		\label{fig_ab_sim}
-	\end{subfigure}%
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
-		\caption{Sample size}
-		\label{fig_ab_data}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-		\caption{Covariate shift}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves more over the baseline.
-	Note: (S) denotes the source task and (T) denotes the target task.}
-	\label{fig_ablation}
-	\vspace{-0.15in}
-\end{figure}
-
-\noindent\textit{Covariance alignemnt.}
+\paragraph{Covariance shift.}
 Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
@@
 
+Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
+We fix the sample size of the target task as $1000$.
+
 In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL.
@@
 
-\textbf{Further results of the covariance alignment procedure.}
-Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
-In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
-In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
-One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
-An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
-We leave this question for future work.
+%\textbf{Further results of the covariance alignment procedure.}
+%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
+%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
+%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
+%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
+%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
+%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
+%We leave this question for future work.
 %Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
 
-\begin{figure}[!h]
-	\centering
-	\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-		\caption{Task pair TREC and CR}
-		\label{fig_cov_a}
-	\end{subfigure}\hfill
-		\begin{subfigure}[b]{0.48\textwidth}
-		\centering
-		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-		\caption{Task pair MR and SST}
-			\label{fig_cov_b}
-	\end{subfigure}
-	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
-	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
-	\label{fig_covariate_app}
-\end{figure}
+%\begin{figure}[!h]
+%	\centering
+%	\begin{subfigure}[b]{0.48\textwidth}
+%		\centering
+%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+%		\caption{Task pair TREC and CR}
+%		\label{fig_cov_a}
+%	\end{subfigure}\hfill
+%		\begin{subfigure}[b]{0.48\textwidth}
+%		\centering
+%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+%		\caption{Task pair MR and SST}
+%			\label{fig_cov_b}
+%	\end{subfigure}
+%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
+%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
+%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
+%	\label{fig_covariate_app}
+%\end{figure}

### 2020-10-05 arxiv/diff_cov.tex
update simulation figures

@@
-\section{The Different Covariates Setting}\label{sec_diff}
+\section{The Different Covariates Case}\label{sec_diff}
 
-The different covariates setting differs from the same covariates setting in two key aspects.
+The different covariates case differs from the same covariates case in two key aspects.
 First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
@@
 
+\begin{example}[Covariate shift]\label{sec_covshift}
+%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+%In general, the covariance matrices of the two tasks may be different such as in text classification.
+Our second example studies the impact of varying covariate shifts on the variance limit.
+%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
+Recall that the matrix $M$ captures the geometry of covariate shifts.
+Suppose that half of the singular values of $M$ are equal to a parameter $\lambda > 0$ and the other half are equal to $\lambda^{-1}$.
+We observe the following dichotomy on the impact of covariate shifts.
+\begin{itemize}
+	\item If $n_1 \ge n_2$, then the variance (limit) of hard parameter sharing is smallest when $\lambda = 1$ or there is no covariate shift.
+	\item If $n_1 < n_2$, then having covariate shifts ($\lambda \neq 1$) always helps reduce variance (limit).
+\end{itemize}
+To see this, we first write the variance limit for different values of $\lambda$ as follows
+\begin{align*}
+	\bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
+	= \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}
+	= \frac{1}{2}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
+\end{align*}
+Denote the above function by $f(\lambda)$.
+We compare $f(\lambda)$ with $f(1)$, and observe that
+\[ 2f(\lambda) - 2f(1) = {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
+	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p}, \]
+where we used the first part of equation \eqref{lem_cov_shift_eq}.
+Next, one can verify that the above equation is equal to $(2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1)$, for a fixed and positive function $g(\lambda, a_1)$ (details omitted).
+Hence, whether or not $f(\lambda)$ is small than $f(1)$ is decided by $a_1$.
+To solve $a_1$, we present an informal argument that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
+Intuitively, with the current spectrum of $M$, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations.
+Hence, when $n_1 \ge n_2$, we expect that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
+Vice serva when $n_1 < n_2$.
+A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} by replacing half of the singular with $\lambda$ and the other half with $\lambda^{-1}$.
+We omit the details.
+Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$; if $n_1< n_2$, then $f(\lambda)< f(1)$.
+\end{example}
+
 \begin{example}[Sample ratio]\label{ex_sample_ratio}
@@
 	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-	(i) task one's sample size is at least $n_1 \ge \min(\frac{17}{\varepsilon^2}, 50) \cdot p$ for a fixed positive value $\varepsilon$, and task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
+	(i) task one's sample size is at least $n_1 \ge \max(\frac{17}{\varepsilon^2}, 50) \cdot p$ for a fixed positive value $\varepsilon$, and task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
 	(ii) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
@@
 %The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-
-\begin{example}[Covariate shift]\label{sec_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-Our second example studies the impact of varying covariate shifts on the variance limit.
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Recall that the matrix $M$ captures the geometry of covariate shifts.
-Suppose that half of the singular values of $M$ are equal to a parameter $\lambda > 0$ and the other half are equal to $\lambda^{-1}$.
-We observe the following dichotomy on the impact of covariate shifts.
-\begin{itemize}
-	\item If $n_1 \ge n_2$, then the variance (limit) of hard parameter sharing is smallest when $\lambda = 1$ or there is no covariate shift.
-	\item If $n_1 < n_2$, then having covariate shifts ($\lambda \neq 1$) always helps reduce variance (limit).
-\end{itemize}
-To see this, we first write the variance limit for different values of $\lambda$ as follows
-\begin{align*}
-	\bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}
-	= \frac{1}{2}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
-\end{align*}
-Denote the above function by $f(\lambda)$.
-We compare $f(\lambda)$ with $f(1)$, and observe that
-\[ 2f(\lambda) - 2f(1) = {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
-	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p}, \]
-where we used the first part of equation \eqref{lem_cov_shift_eq}.
-Next, one can verify that the above equation is equal to $(2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1)$, for a fixed and positive function $g(\lambda, a_1)$ (details omitted).
-Hence, whether or not $f(\lambda)$ is small than $f(1)$ is decided by $a_1$.
-To solve $a_1$, we present an informal argument that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
-Intuitively, with the current spectrum of $M$, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations.
-Hence, when $n_1 \ge n_2$, we expect that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
-Vice serva when $n_1 < n_2$.
-A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} by replacing half of the singular with $\lambda$ and the other half with $\lambda^{-1}$.
-We omit the details.
-%We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-Then equations in equation \eqref{eq_a12extra} become
-%\begin{align*}
-%	a_1 + \frac{p}{2(n_1 + n_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{n_1}{n_1 + n_2}.
-%\end{align*}
-%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to equation \eqref{compleeq}.
-%After solving these, with equation \eqref{gvar_extra} we get that w.h.p.,
-%\be\label{testcomple}
-% \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
-%First we notice that the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
-In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in equation \eqref{testcomple} takes the value
-%$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
-$M=\id$ case) when $n_1<n_2$.
-On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-%We now study the behavior of $f$ as $\lambda$ changes.
-%This phenomenon can be also explained using our theory.
-%We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with equation \eqref{compleeq}, we can rewrite
-%$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
-%Then we can compute that
-%\begin{align*}
-%f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-%&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-%\end{align*}
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$; if $n_1< n_2$, then $f(\lambda)< f(1)$. % which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
-%\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
-%, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
-%\end{itemize}
-%This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c),
-
-%We compare two cases: (i) when $M = \id_{p\times p}$; (ii) when $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-%Hence, $\lambda$ measures the severity of the covariate shift.
-%	Figure \ref{fig_covariate} shows a simulation of this setting by varying $\lambda$.
-%	We observe that as source/target sample ratio increases, the performance gap between the two cases increases.
-
-%By applying Lemma \ref{lem_cov_shift_informal}, we find that when $n_1 / n_2$ is large, having no covariate shift is the optimal choice provided that the determinant of $M^{\top}M$ is bounded.
-%We compare different choices of $M$ that belong to the following bounded set.
-%Let $\lambda_i$ be the $i$-th singular value of $M$.
-%Let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-%{\begin{align*}
-%		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i \le \mu^p, \mu_{\min} \le \lambda_i\le \mu_{\max}, \text{ for all } 1\le i\le p\right.}.
-%\end{align*}}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-%\begin{corollary}[Derived from Theorem \ref{thm_main_RMT}]\label{prop_covariate}
-%	In the setting described above, assume further that a random-effects model holds for both tasks.
-%	The prediction loss of $\hat{\beta}_2^{\MTL}$ for task two satisfies that
-%	\begin{align*}
-%		L(\hat{\beta}_2^{\MTL})
-%	\end{align*}
-%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-%	We have that
-%		\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
-%\end{corollary}
-%Proposition \ref{prop_covariate} shows that when the sample ratio is large, having no covariate shift gives the optimal performance for multi-task learning.
-%The proof of Proposition \ref{prop_covariate} can be found in Appendix \ref{app_proof_33}.
-\end{example}
-
 As a remark, by combining the bias and variance asymptotics, we can also obtain a generalization bound for any local minimum solutions $(A, B)$.
-The proof is similar to Theorem \ref{thm_many_tasks} and Corollary \ref{cor_MTL_loss}.
-We describe the differences and omit the details.
-First, we rescale $X_1$ (and $\Sigma^{(1)}$) by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
-Second, we approximate sample covariance ${X^{(1)}}^{\top}X^{(1)} / n_1$ by its expectation $\Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
+The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
+%First, we rescale $X_1$ (and $\Sigma^{(1)}$) by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
+%Second, we approximate sample covariance ${X^{(1)}}^{\top}X^{(1)} / n_1$ by its expectation $\Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
 For the rest of this section, we present the main ideas for proving Theorem \ref{thm_main_RMT}.

### 2020-10-05 arxiv/experiments.tex
update simulation figures

@@
 
-	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
-	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
-	\begin{itemize}
-		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
-	The noise level is $\sigma = 5$.
-	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
-	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
-	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
-		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
-	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
-		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
+We verify our theoretical results in synthetic settings.
+We consider the feature covariates to have dimension $p = 200$.
+
+\paragraph{The same covariates case.}
+We first study the setting of Example \ref{ex_same_cov}. We vary the per-task sample size $n$ from $2p$ to $10p$. We set $\sigma = 0.5$. Figure \ref{fig_same_cov} shows the result.
+First, we can see that for various different values of $d$ and $n$, our estimated loss matches the empirical loss accurately.
+Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
+On the other hand when $d = 0.2$, this is not always the case, and indeed we observe a crossover point between the average prediction loss of hard parameter sharing and STL.
+Finally, we see that to achieve comparable loss to STL, hard parameter sharing requires 3x less samples per-task.
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
+	\caption{Validating our result for the same covariates setting. Our estimated loss (solid line) matches the empirical loss (dotted line) accurately, for various values of $d$ and sample sizes.}
+	\label{fig_same_cov}
+\end{figure}
+
+	\paragraph{The different covarates case.}
+
+	Covariate shift: We set $\kappa = 1$ and $d = 0$.
 	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
@@
 	This can be achieved similarly by rescaling the task data.
-	\end{itemize}
+
+Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
+	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
 
@@
 \begin{figure}[!t]
-		\begin{subfigure}[b]{0.32\textwidth}
+%		\begin{subfigure}[b]{0.32\textwidth}
+%		\centering
+%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
+%		\caption{Sample efficiency}
+%		\label{fig_model_shift}
+%	\end{subfigure}\hfill
 	\centering
-		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-		\caption{Sample efficiency}
-		\label{fig_model_shift}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.5\textwidth}
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
+		\includegraphics[width=0.9\textwidth]{figures/sample_ratio.eps}
 		\caption{Sample ratio}
@@
 	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.5\textwidth}
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
+		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
 		\caption{Covariate shift}

### 2020-10-06 arxiv/diff_cov.tex
section 5 v0 wip

@@
 Next, we use our result to study how varying sample sizes and covariate shifts affects hard parameter sharing, respectively.
-
-\begin{example}[Covariate shift]\label{sec_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-Our second example studies the impact of varying covariate shifts on the variance limit.
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Recall that the matrix $M$ captures the geometry of covariate shifts.
-Suppose that half of the singular values of $M$ are equal to a parameter $\lambda > 0$ and the other half are equal to $\lambda^{-1}$.
-We observe the following dichotomy on the impact of covariate shifts.
-\begin{itemize}
-	\item If $n_1 \ge n_2$, then the variance (limit) of hard parameter sharing is smallest when $\lambda = 1$ or there is no covariate shift.
-	\item If $n_1 < n_2$, then having covariate shifts ($\lambda \neq 1$) always helps reduce variance (limit).
-\end{itemize}
-To see this, we first write the variance limit for different values of $\lambda$ as follows
-\begin{align*}
-	\bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}
-	= \frac{1}{2}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
-\end{align*}
-Denote the above function by $f(\lambda)$.
-We compare $f(\lambda)$ with $f(1)$, and observe that
-\[ 2f(\lambda) - 2f(1) = {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
-	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p}, \]
-where we used the first part of equation \eqref{lem_cov_shift_eq}.
-Next, one can verify that the above equation is equal to $(2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1)$, for a fixed and positive function $g(\lambda, a_1)$ (details omitted).
-Hence, whether or not $f(\lambda)$ is small than $f(1)$ is decided by $a_1$.
-To solve $a_1$, we present an informal argument that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
-Intuitively, with the current spectrum of $M$, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations.
-Hence, when $n_1 \ge n_2$, we expect that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
-Vice serva when $n_1 < n_2$.
-A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} by replacing half of the singular with $\lambda$ and the other half with $\lambda^{-1}$.
-We omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$; if $n_1< n_2$, then $f(\lambda)< f(1)$.
-\end{example}
 
@@
 Consider the prediction loss if we fix $n_2$ and increase $n_1$.
+We show that as a function of $n_1$, the limit equation always decreases first from $\frac{\sigma^2 p}{n - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
+We describe an informal proof.
 First, the noise variance term in Corollary \ref{cor_MTL_loss} always reduces as $n_1$ increases.
 Second, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
-Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
-(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
-(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
-(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
-The proof can be found in Appendix \ref{app_iso_cov}.
+Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the decrease in variance, and there is only one positive root for the derivative being zero.
+%Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
+%(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
+%(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
+%(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
+The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
 
-Based on this observation, we have the following trend when we fix $n_2$ and increase $n_1$:
-\begin{itemize}
-	\item If $d^2$ is smaller than the prediction loss of STL for task two $\frac{\sigma^2 p}{n_2 - p}$, then the prediction loss of hard parameter sharing is always lower than STL.
-That is, task one always transfers positively to task two.
-	\item Otherwise, task one transfers positively to task two initially, but transfers negatively eventually.
-\end{itemize}
+%Based on this observation, we have the following trend when we fix $n_2$ and increase $n_1$:
+%\begin{itemize}
+%	\item If $d^2$ is smaller than $\frac{\sigma^2 p}{n_2 - p}$, then the prediction loss of hard parameter sharing is always lower than STL. That is, task one always transfers positively to task two.
+%	\item Otherwise, task one transfers positively to task two initially, but transfers negatively eventually.
+%\end{itemize}
 %Therefore, while the variance of MTL still reduces compared to STL,
@@
 
+\begin{example}[Covariate shift]\label{ex_covshift}
+%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+%In general, the covariance matrices of the two tasks may be different such as in text classification.
+Our second example studies the impact of varying covariate shifts on the variance limit.
+%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
+Recall that the matrix $M$ captures the geometry of covariate shifts.
+Suppose that half of the singular values of $M$ are equal to a parameter $\lambda > 0$ and the other half are equal to $\lambda^{-1}$.
+We observe the following dichotomy on the impact of covariate shifts.
+\begin{itemize}
+	\item If $n_1 \ge n_2$, then the variance (limit) of hard parameter sharing is smallest when $\lambda = 1$ or there is no covariate shift.
+	\item If $n_1 < n_2$, then having covariate shifts ($\lambda \neq 1$) always helps reduce variance (limit).
+\end{itemize}
+To see this, we first write the variance limit for different values of $\lambda$ as follows
+\begin{align*}
+	\bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
+	= \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}
+	= \frac{1}{2}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
+\end{align*}
+Denote the above function by $f(\lambda)$.
+We compare $f(\lambda)$ with $f(1)$, and observe that
+\[ 2f(\lambda) - 2f(1) = {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
+	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p}, \]
+where we used the first part of equation \eqref{lem_cov_shift_eq}.
+Next, one can verify that the above equation is equal to $(2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1)$, for a fixed and positive function $g(\lambda, a_1)$ (details omitted).
+Hence, whether or not $f(\lambda)$ is small than $f(1)$ is decided by $a_1$.
+To solve $a_1$, we present an informal argument that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
+Intuitively, with the current spectrum of $M$, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations.
+Hence, when $n_1 \ge n_2$, we expect that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
+Vice serva when $n_1 < n_2$.
+A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} by replacing half of the singular with $\lambda$ and the other half with $\lambda^{-1}$.
+We omit the details.
+Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$; if $n_1< n_2$, then $f(\lambda)< f(1)$.
+\end{example}
 %\begin{proposition}[Source/target sample ratio]\label{prop_data_size}

### 2020-10-06 arxiv/experiments.tex
section 5 v0 wip

@@
 
-\subsection{Simulation Studies}\label{sec_simulation}
-
-We verify our theoretical results in synthetic settings.
-We consider the feature covariates to have dimension $p = 200$.
-
-\paragraph{The same covariates case.}
-We first study the setting of Example \ref{ex_same_cov}. We vary the per-task sample size $n$ from $2p$ to $10p$. We set $\sigma = 0.5$. Figure \ref{fig_same_cov} shows the result.
-First, we can see that for various different values of $d$ and $n$, our estimated loss matches the empirical loss accurately.
-Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
-On the other hand when $d = 0.2$, this is not always the case, and indeed we observe a crossover point between the average prediction loss of hard parameter sharing and STL.
-Finally, we see that to achieve comparable loss to STL, hard parameter sharing requires 3x less samples per-task.
-
 \begin{figure}[!t]
@@
 	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
-	\caption{Validating our result for the same covariates setting. Our estimated loss (solid line) matches the empirical loss (dotted line) accurately, for various values of $d$ and sample sizes.}
+	\caption{Validating Example \ref{ex_same_cov} in the same covariates case.
+Our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d$ and sample size $n$ settings.
+The noise variance $\sigma^2$ is $1/4$.}
 	\label{fig_same_cov}
@@
 
-	\paragraph{The different covarates case.}
+\subsection{Simulation Studies}\label{sec_simulation}
 
-	Covariate shift: We set $\kappa = 1$ and $d = 0$.
-	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
-	This can be achieved similarly by rescaling the task data.
+We show that our asymptotic estimates match extremely well with empirical prediction losses in modest dimensions.
+This study complements our high-dimensional asymptotic results whose error term vanishes when $p$ is sufficiently large.
+We simulate the settings of the three examples in Section \ref{sec_same} and \ref{sec_diff} in dimension $p = 200$.
 
-Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
-	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+\paragraph{The same covariates case.}
+First, we study the setting of Example \ref{ex_same_cov}.
+Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task sample from $400$ to $4000$.
+For all the parameter settings, we can estimate the empirical loss accurately using our results.
+We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
+Our result explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
+%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
+Indeed, we observe a crossover point between hard parameter sharing and STL.
+Finally, by looking horizontally at the same level of prediction loss, we observe that hard parameter sharing requires 3x less samples per-task than STL.
+
+\paragraph{The different covariates case.}
+Second, we show how varying sample ratio affects hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
+Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
+Again, our estimates are fairly accurate compared to the empirical losses.
+We consider a larger sample size regime here where task two consists of $100,000$ samples and task one's sample size varies from $10,000$ to $70,000$.
+We observe that as we increase the sample ratio, task two's prediction loss decreases intially but increases above the initial loss level.
+Our result explains this trend since the task-specific variance $d^2 = 0.08$ is greater than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
+%We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+
+Finally, we show that varying covariate shift affects hard parameter sharing in the setting of Example \ref{ex_covshift}.
+Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
+Recall that $\lambda$ measures the severity of covariate shift -- a higher $\lambda$ means more covariate shift.
+Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
+The noise variance $\sigma^2$ is $1/4$.
+%Covariate shift: We set $\kappa = 1$ and $d = 0$.
+%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
+%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
 
@@
 		\includegraphics[width=0.9\textwidth]{figures/sample_ratio.eps}
-		\caption{Sample ratio}
+		\caption{Example \ref{ex_sample_ratio}}
 		\label{fig_size}
@@
 		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
-		\caption{Covariate shift}
+		\caption{Example \ref{ex_covshift}}
 		\label{fig_covariate}
@@
 	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
-	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
-	The $y$-axis measures the loss of STL minus MTL.}
+	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in the different covariates case.
+	In both experiments, our estimated loss (solid line) matches with the empirical loss (dotted line) accurately.
+	In Figure \ref{fig_size}, we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
+	We observe that task two's prediction loss decreases initially before increasing again, and our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
+	In Figure \ref{fig_covariate}, we show how covariate shift affects hard parameter sharing.
+We observe that when task two's sample size is greater than that of task one, covariate shift increases the prediction loss.
+Otherwise, covariate shift actually decreases the prediction loss (surprisingly).
+	.}
 	\label{fig_model_shift_phasetrans}
@@
 
-We consider a text classification task as follows.
-
-{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR) \cite{pang2005seeing}, sentence subjectivity (SUBJ) \cite{pang2004sentimental}, customer reviews (CR) \cite{hu2004mining}, question type (TREC) \cite{li2002learning}, opinion polarity (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) tasks \cite{socher2013recursive}.
+Our results and their implications are all in the high-dimensional linear regression setting.
+How well do they extend to other settings?
+In this section, we conduct further studies on a text classification task, for predicting whether the sentiment of a sentence is positive or negative.
+We use six datasets including a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, a opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
 %The question is to predict positive or negative sentiment expressed in the text.
-We use an embedding layer with GloVe embeddings \cite{pennington2014glove}
-followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.
+We use an embedding layer with GloVe embeddings \cite{pennington2014glove} followed by an LSTM, MLP or CNN layer proposed by~\citet{lei2018simple}.\footnote{For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
+For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.}
 
@@
 %We use this task to verify our theoretical results on model capacity and task covariance in real world.
-
 %{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
@@
 %We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-
-%\paragraph{Image and Text Classification Settings}\label{app_it}
-
-For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-We evaluate three model choices.
-For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
-For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.
-
+%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
+%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
+%We evaluate three model choices.
 %\textit{Predicting transfer effect via STL results.}
@@
 \paragraph{Sample ratio.}
-In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
-Sample size: We vary the sample size of the source task from $100$ to $3000$.
+First, we validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
+Figure \ref{fig_ab_data} shows the result for three example task pairs. We fix task one's sample size as $1000$ and increase task two's number of samples from $100$ to $3000$.
 
-\textit{Towards computing the optimal sample ratio.}
-An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
-In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
-\squishlist
+Next, we propose a natural progressive training schedule for finding the optimal sample ratio.
+Our training schedule is motivated by Corollary \ref{cor_MTL_loss}, which shows that as we increase the sample ratio, the prediction loss always decreases first and then increases.
+%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
+%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
+Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
+\begin{itemize}
 	\item We divide the source task data into $S$ batches.
@@
 	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\squishend
+\end{itemize}
 
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-			\For{$j = 1,\dots, T$}
-				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-			\EndFor
-			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-				\State \textbf{break}
-			\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
-We add $20\%$ of source task samples for every $T = 2$ epochs.
-The total number of epochs is $20$.
-We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.
-
-For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
-Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
-We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
-We run $20$ epochs in total.
-%\textbf{The training procedure and baseline.}
-For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
-The baseline training schedule for MTL is the round-robin training schedule.
-%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
-We measure the test accuracy of predicting a target task.
-We measure computational cost by summing over all epochs the number of samples used in every epoch.
+%\begin{algorithm}[!t]
+%	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+%	\label{alg_inc_train}
+%	\begin{algorithmic}[1]
+%		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+%		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+%		\Output The trained modules $B, W_2$ optimized for task $2$.
+%		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+%		\For{$i = 1,\dots, S$}
+%			\For{$j = 1,\dots, T$}
+%				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+%			\EndFor
+%			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+%				\State \textbf{break}
+%			\EndIf
+%		\EndFor
+%	\end{algorithmic}
+%\end{algorithm}
 
@@
 %Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-
-First, we show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
+Our results show that progressive training requires less computation compared to a baseline round-robin training schedule, without sacrificing accuracy.
+First, we show that our proposed progressive training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
 Over all $15$ pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve similar performance on the target task, compared to the MTL baseline.
 Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{incrementally} during training.
-
 %\textbf{Improving transfer learning training efficiency.}
@@
 %Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-
-Our next result shows the incremental training schedule applies to multiple tasks as well.
+Second, we show the progressive training schedule applies to multiple tasks as well.
 In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
@@
 
-\begin{figure}[!t]
+\begin{figure}%[!t]
+	\begin{minipage}[t]{0.5\textwidth}
 		\centering
-	\begin{subfigure}[b]{0.33\textwidth}
+		\vspace{0pt}
+		\includegraphics[width=0.6\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
+		\caption{Varying sample ratio}
+		\label{fig_ab_data}
+	\end{minipage}%\hfill
+	\begin{minipage}[t]{0.4\textwidth}
 		\centering
-		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-		\caption{Task similarity}
-		\label{fig_ab_sim}
-	\end{subfigure}%
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
-		\caption{Sample size}
-		\label{fig_ab_data}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-		\caption{Covariate shift}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves more over the baseline.
-	Note: (S) denotes the source task and (T) denotes the target task.}
-	\label{fig_ablation}
-	\vspace{-0.15in}
+		\vspace{0pt}
+		\begin{tabular}{c c c}
+		\toprule
+		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
+		% Sentiment\\ analysis\end{center}\end{minipage}} \\
+		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
+		% \cmidrule(lr){2-3}
+		& all tasks & w/o TREC \\
+		\midrule
+		{\bf MLP}  & 31\% & 29\% \\
+		{\bf LSTM} & 35\% & 34\% \\
+		{\bf CNN}  & 30\% & 28\% \\
+		\bottomrule
+		\end{tabular}
+		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
+%		\label{tab:taskonomy}
+	\end{minipage}
 \end{figure}
 
-\begin{table}[!b]
+%	\begin{subfigure}[b]{0.33\textwidth}
+%		\centering
+%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
+%		\caption{Task similarity}
+%		\label{fig_ab_sim}
+%	\end{subfigure}%
+%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
+%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
+%	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves
+%more over the baseline.
+%	Note: (S) denotes the source task and (T) denotes the target task.}
+
 %\begin{minipage}[t]{.58\textwidth}
@@
 %\quad
-	\begin{minipage}[t]{.40\textwidth}
-	\vspace{-0.1in}
+
+\begin{figure}
 	\centering
-	\begin{tabular}{c c c}
-		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-		& all tasks & w/o TREC \\
-		\midrule
-		{\bf MLP}  & 31\% & 29\% \\
-		{\bf LSTM} & 35\% & 34\% \\
-		{\bf CNN}  & 30\% & 28\% \\
-		\bottomrule
-		\end{tabular}
-	\vspace{0.1in}
-	\captionof{table}{Efficiency of incremental training compared to baseline MTL.}
-	\label{tab:taskonomy}
-\end{minipage}
-\end{table}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
+		\caption{Averaged over all 16 task pairs}
+		\label{fig_ab_cov}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+		\caption{An example task pair}
+		\label{fig_cov_a}
+	\end{subfigure}
+	\caption{ (TREC and CR)}
+\end{figure}
 
@@
 We validate our insight on this procedure in the experiments.
-
-Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
+We implement the covariance alignment procedure following \cite{WZR20}.
 We fix the sample size of the target task as $1000$.

### 2020-10-06 arxiv/proof_same_cov.tex
section 5 v0 wip

@@
 	\begin{align*}
-		H_j &\define B^{\star} A^{\top} (AA^{\top})^{-1} A_j - \beta^{(j)}, \\
+		H_j &\define B^{\star} A^{\top} (AA^{\top})^{\dagger} A_j - \beta^{(j)}, \\
 		E_j &\define \cW A_j - \varepsilon^{(j)}.
@@
 	\begin{align*}
-			\exarg{\cE}{\cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}
-		&= \exarg{\cE}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{-1} A_k {\varepsilon^{(k)}}^{\top}} \\
-		&= \exarg{\cE}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{-1} A_j {\varepsilon^{(j)}}^{\top}} \\
+			\exarg{\cE}{\cE A^{\top} (AA^{\top})^{\dagger} A \cE^{\top}}
+		&= \exarg{\cE}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{\dagger} A_k {\varepsilon^{(k)}}^{\top}} \\
+		&= \exarg{\cE}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{\dagger} A_j {\varepsilon^{(j)}}^{\top}} \\
 		&= \sigma^2 \cdot r \cdot \id_{n\times n}.
@@
 	In the above, the first equation uses the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
-	The second equation uses the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{-1} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
+	The second equation uses the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{\dagger} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
 	Therefore, we have that

### 2020-10-06 arxiv/diff_cov.tex
section 5 close to finish

@@
 	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-	(i) task one's sample size is at least $n_1 \ge \max(\frac{17}{\varepsilon^2}, 50) \cdot p$ for a fixed positive value $\varepsilon$, and task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
+	(i) task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
 	(ii) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
@@
 	(iii) the task-specific variance of $\beta_i$ is much smaller than the shared signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$.
+	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
 	The prediction loss of hard parameter sharing for task two satisfies that
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2) +{\color{red} p^{-c_\infty}\cdot \OO(\kappa^2)}.
+	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2).
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
@@
 	 \end{align}
-	 {\color{red}[FY: there is an extra $\kappa^2$ term]}
+%	 {\color{red}[FY: there is an extra $\kappa^2$ term]} + p^{-c_\infty}\cdot \OO(\kappa^2)
 %	 for a large constant $C>0$.

### 2020-10-06 arxiv/experiments.tex
section 5 close to finish

@@
 Again, our estimates are fairly accurate compared to the empirical losses.
-We consider a larger sample size regime here where task two consists of $100,000$ samples and task one's sample size varies from $10,000$ to $70,000$.
+We consider a larger sample size regime here where task two consists of $70,000$ samples and task one's sample size varies from $10,000$ to $56,000$.
 We observe that as we increase the sample ratio, task two's prediction loss decreases intially but increases above the initial loss level.
@@
 We use an embedding layer with GloVe embeddings \cite{pennington2014glove} followed by an LSTM, MLP or CNN layer proposed by~\citet{lei2018simple}.\footnote{For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
-For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings \cite{lei2018simple}.}
+For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings.}
 
@@
 \begin{figure}%[!t]
-	\begin{minipage}[t]{0.5\textwidth}
+	\begin{subfigure}[t]{0.5\textwidth}
 		\centering
@@
 		\includegraphics[width=0.6\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
-		\caption{Varying sample ratio}
+		\caption{HPS vs. STL}
 		\label{fig_ab_data}
-	\end{minipage}%\hfill
-	\begin{minipage}[t]{0.4\textwidth}
+	\end{subfigure}\hfill
+	\begin{subfigure}[t]{0.5\textwidth}
 		\centering
 		\vspace{0pt}
-		\begin{tabular}{c c c}
-		\toprule
+		\includegraphics[width=0.6\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
+		\caption{HPS vs. covariance alignment}
+		\label{fig_ab_cov}
+	\end{subfigure}
+	\caption{A}
+%	\begin{minipage}[t]{0.4\textwidth}
+%		\centering
+%		\vspace{0pt}
+%		\begin{tabular}{c c c}
+%		\toprule
 		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
 		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
+%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
 		% \cmidrule(lr){2-3}
-		& all tasks & w/o TREC \\
-		\midrule
-		{\bf MLP}  & 31\% & 29\% \\
-		{\bf LSTM} & 35\% & 34\% \\
-		{\bf CNN}  & 30\% & 28\% \\
-		\bottomrule
-		\end{tabular}
-		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
+%		& all tasks & w/o TREC \\
+%		\midrule
+%		{\bf MLP}  & 31\% & 29\% \\
+%		{\bf LSTM} & 35\% & 34\% \\
+%		{\bf CNN}  & 30\% & 28\% \\
+%		\bottomrule
+%		\end{tabular}
+%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
 %		\label{tab:taskonomy}
-	\end{minipage}
+%	\end{minipage}
 \end{figure}
@@
 
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-		\caption{Averaged over all 16 task pairs}
-		\label{fig_ab_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-		\caption{An example task pair}
-		\label{fig_cov_a}
-	\end{subfigure}
-	\caption{ (TREC and CR)}
-\end{figure}
-
-\paragraph{Covariance shift.}
+\paragraph{Covariate shift.}
 Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
@@
 The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
+
+%\begin{figure}[!t]
+%	\centering
+%	\begin{subfigure}[b]{0.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
+%		\caption{Averaged over all 16 task pairs}
+%		\label{fig_ab_cov}
+%	\end{subfigure}\hfill
+%	\begin{subfigure}[b]{0.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+%		\caption{An example task pair}
+%		\label{fig_cov_a}
+%	\end{subfigure}
+%	\caption{ (TREC and CR)}
+%\end{figure}
 

### 2020-10-06 arxiv/proof_examples.tex
section 5 close to finish

@@
 	\end{align}
- Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $A:=A_1/A_2$ as follows 
+ Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $A:=A_1/A_2$ as follows \HZ{$A$ has been used to denote the output layers.
+Could you replace $A$ with another symbol (say $x$)?}
  \begin{align}
@@
 	\end{align}
+	\HZ{the above Eq is overline}
 	where we denote
@@
 We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
+\HZ{could you align the Eq so that they look better on page?}
 \begin{align*}	
@@
 for any small constant $e_1>0$.
+	 \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
  \end{claim}

### 2020-10-06 arxiv/diff_cov.tex
section 4 edit

@@
 Consider the prediction loss if we fix $n_2$ and increase $n_1$.
-We show that as a function of $n_1$, the limit equation always decreases first from $\frac{\sigma^2 p}{n - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
+We show that as a function of $n_1$, the limit equation always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
 We describe an informal proof.

### 2020-10-07 arxiv/proof_examples.tex
revise

@@
 &\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-&= \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
+= &\left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
+& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \\
+&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
 &+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \\
@@
  In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{1/2+e_1} \left(\sigma^2 + \kappa^2+d^2 \right) $$
-for any small constant $e_1>0$.
+$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right) $$
+for any small constant $c>0$.
 	 \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}

### 2020-10-07 arxiv/experiments.tex
finish section 5

@@
 \paragraph{Sample ratio.}
-First, we validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-Figure \ref{fig_ab_data} shows the result for three example task pairs. We fix task one's sample size as $1000$ and increase task two's number of samples from $100$ to $3000$.
+In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
+On the $y$-axis, we plot task two's prediction accuracy using HPS, subtracted by its STL prediction accuracy.
+%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
+We fix task one's sample size as $1000$ and increase task two's number of samples from $100$ to $3000$.
 
@@
 	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
-	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
+%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
 \end{itemize}
@@
 Our results show that progressive training requires less computation compared to a baseline round-robin training schedule, without sacrificing accuracy.
-First, we show that our proposed progressive training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
-Over all $15$ pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve similar performance on the target task, compared to the MTL baseline.
-Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{incrementally} during training.
+First, we show that our proposed progressive training schedule (can help mitigate negative transfer for predicting a particular target task.
+Over all $15$ pairs from the sentiment analysis tasks, we find that progressive training requires only $45\%$ of the computational cost to achieve the same test accuracy on the target task, compared to HPS trained using round-robin.
+Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
 %\textbf{Improving transfer learning training efficiency.}
@@
 Second, we show the progressive training schedule applies to multiple tasks as well.
-In Table \ref{tab:taskonomy}, we find that over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
-As a further validation, excluding TREC, we observe similar comparative results.
+Over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
+%As a further validation, excluding TREC, we observe similar comparative results.
 %The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
@@
 	\end{subfigure}
-	\caption{A}
+	\caption{Comparing hard parameter sharing to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}.
+	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
+	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS. }
+	\label{fig_text}
 %	\begin{minipage}[t]{0.4\textwidth}
@@
 %	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c) As source/target sample ratio increases, aligning task covariances \cite{WZR20} improves
-%more over the baseline.
+%	(c)
 %	Note: (S) denotes the source task and (T) denotes the target task.}
@@
 \paragraph{Covariate shift.}
-Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
-Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
+Recall from Example \ref{ex_covshift} that when the sample ratio increases, covariate shift worsens.
+Hence when the sample ratio increases, we expect procedures that aim at correcting covariate shift to provide more significant gains.
+To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, which is designed for correcting covariate shift.
 The idea is to add an alignment module between the input and the shared module $B$.
-This new module is then trained together with $B$ and the output layers.
-We validate our insight on this procedure in the experiments.
-We implement the covariance alignment procedure following \cite{WZR20}.
-We fix the sample size of the target task as $1000$.
+This new module is then trained together with $B$ and the output layers -- more details on the procedure and the implementation can be found in that paper.
+%We validate our insight on this procedure in the experiments.
+%We implement the covariance alignment procedure following \cite{WZR20}.
 
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing the alignment procedure proposed in \cite{WZR20} minus baseline MTL.
+In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
 We average the results over all 15 task pairs.
-The result shows that as the source samples increases, the alignment procedure shows a bigger improvement over MTL.
+The result shows that as the source samples increases, covariance alignment improves more over HPS.
+We fix task two's sample size at $1,000$ and increase task one's sample size from $1,000$ to $3,000$.
 

### 2020-10-07 arxiv/proof_examples.tex
finish section 5

@@
 %\subsubsection{Proof for Sample Imbalance}
-We now give the proof of Proposition \ref{cor_MTL_loss}. Similar to the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following steps: 
+We provide the proof of Proposition \ref{cor_MTL_loss}. Similar to the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following parts:
 \begin{itemize}
-\item simplifying the optimization objective using concentration estimates;
-
-\item finding the minimizer of the optimization objective;
-
-\item deriving a bias-variance decomposition of the prediction loss $L(\hat \beta_2^{\MTL})$;
-
-\item calculating the bias term and the variance term using Theorem \ref{thm_main_RMT}. 
+\item First, we reduce the optimization objective to another function $g(x)$ that only depends on the sample covariance matrices.
+\item Second, we show that the global minimizer of $g(x)$ is approximate $1$.
+\item Finally, we use the above result and Theorem \ref{thm_main_RMT} to prove the proposition.
 \end{itemize}
@@
 
-\paragraph{Simplifying the optimization objective.} 
+\paragraph{Part $1$: the reduction.}
 Under the two-task setting of Corollary \ref{cor_MTL_loss}, the optimization objective \eqref{eq_mtl} becomes
@@
 
- \paragraph{Minimizer of the optimization objective.} We show that for the isotropic model, the minimizer of $g(A)$, denoted by $\hat A$, is very close to 1 under the condition \eqref{choiceofpara0}.
-This will be used to calculate the predication loss $\te(\hat{\beta}_2^{\MTL})$ loss.
+\paragraph{Part $2$: approximating the global minimum.}
+	Let $\hat{A}$ denote the minimizer of $g(A)$.\HZ{change $\hat{A}$ to say $\hat{x}$.}
+	We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat A$ is close to 1.% This will be used to calculate the predication loss $\te(\hat{\beta}_2^{\MTL})$ loss.
 %Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
@@
 \end{align}
-where in the first step we used that $|A-1|^2\gtrsim 1+A^2$ for $|A-1|\ge \delta$, $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$, and in the second step we used equation \eqref{choiceofpara0}.
+where in the first step we used that $|A-1|^2\gtrsim 1+A^2$ for $|A-1|\ge \delta$, $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$, and in the second step we use equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use?
+put it here}.
 Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability,
@@
 g(A)&\ge  h(A) +\sigma^2(n_1+n_2-p) -p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
-&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1) \label{gA>g1}
-\end{align}
-under condition \eqref{choiceofpara0}.
+&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
+\end{align}
+under condition \eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
 This gives that
@@
 Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have 
-$$ h(A)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
-under equation \eqref{choiceofpara0}, which implies the inequality \eqref{gA>g1}. Second using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le A \le 1-d^2/\kappa^2$,
+$$ h(A)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$
+where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
+Second using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le A \le 1-d^2/\kappa^2$,
 $$- h'(A)\ge  [2(1-A)\kappa^2 - Ad^2] \cdot p^{-1} \tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
@@
 $$ h(A)-h(1) \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
-under equation \eqref{choiceofpara0}, which implies the inequality \eqref{gA>g1}. In sum, we obtain that the minimizer $\hat A$ must satisfy equation \eqref{hatw_add1}.
+under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?}, which implies the inequality \eqref{gA>g1}.
+In sum, we obtain that the minimizer $\hat A$ must satisfy equation \eqref{hatw_add1}.
 %Next we prove the following estimate on the optimizer $\hat A$: with high probability,
@@
 
-\paragraph{Calculating the prediction loss.} Now we calculate the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat A=\hat A_1/\hat A_2$:
+\paragraph{Part $3$: Applying Theorem \ref{thm_main_RMT}.}
+We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat A=\hat A_1/\hat A_2$:
 \begin{align}
@@
 \be\label{est333}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim p.\ee
-Now we bound the left-hand side of \eqref{simple1} as
+Now we bound the left-hand side of \eqref{simple1} as \HZ{replace $\Sigma(1)$ with $\hat{\Sigma}$ throughout}
 \begin{align*}
@@
 % \todo{switch the $a_3$ and $a_4$}
-\paragraph{Calculating the variance and bias terms.} Finally, we calculate the variance term $\sigma^2  \bigtr{\Sigma(1)^{-1}  }$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}, which will conclude Proposition \ref{cor_MTL_loss}.
+Finally, we are ready to present the proof of Proposition \ref{cor_MTL_loss}.
+We derive the variance term $\sigma^2  \bigtr{\Sigma(1)^{-1}  }$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
 %For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.

### 2020-10-07 arxiv/proof_examples.tex
revise

@@
 \item First, we reduce the optimization objective to another function $g(x)$ that only depends on the sample covariance matrices.
-\item Second, we show that the global minimizer of $g(x)$ is approximate $1$.
+\item Second, we show that the global minimizer of $g(x)$ is approximately equal to $1$.
 \item Finally, we use the above result and Theorem \ref{thm_main_RMT} to prove the proposition.
@@
 	\end{align}
- Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $A:=A_1/A_2$ as follows \HZ{$A$ has been used to denote the output layers.
+ Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers.
 Could you replace $A$ with another symbol (say $x$)?}
  \begin{align}
-		 g(A) \define & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)+ \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} + A X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2,
+		 g(x) \define & \left\| X^{(1)} \Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		& \left. + x X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+		 + & \left\| X^{(2)} \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
+		 &\left. + x X^{(2)}\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 
 		\label{eq_mtl_A12}
 	\end{align}
-	\HZ{the above Eq is overline}
-	where we denote
-	$$ \Sigma(A):= A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+	where we denote {\cor revise}
+	$$ \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
 We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:

### 2020-10-07 arxiv/proof_examples.tex
revise

@@
  \begin{align}
-		 g(x) \define & \left\| X^{(1)} \Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
-		& \left. + x X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
-		 &\left. + x X^{(2)}\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 
+		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
+		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 
 		\label{eq_mtl_A12}
 	\end{align}
-	where we denote {\cor revise}
-	$$ \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
-We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
-\HZ{could you align the Eq so that they look better on page?}
-\begin{align*}	
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-= &\left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \\
-&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
-&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \\
-& +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
+	where we denote $ \hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$ We can calculate the partial expectation of $g(x)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
+%\HZ{could you align the Eq so that they look better on page?}
+\begin{align}	
+&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \nonumber\\
+&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2 \nonumber\\
+&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2  \nonumber\\
+& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \nonumber\\
+&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
+&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
+& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
+\end{align}
+Using the following identity
+\begin{align*}
+(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} & =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
+&= (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)},
+\end{align*}
+we can simplify that 
+\begin{align*}
+&  \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2 \\
+&=
+\end{align*}
+
+Hence \eqref{Eg(x)} can be simplified to 
+\begin{align*}
 		&= \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
@@
 \end{align*}
-Here in the first step of the above derivation, we used that 
- $$(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)}.$$
 

### 2020-10-07 arxiv/proof_examples.tex
revise

--- 2020-10-07 arxiv/proof_examples.tex
@@
  \begin{align}
-		 g(x) \define & \left\| X^{(1)} \Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
-		& \left. + x X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
-		 &\left. + x X^{(2)}\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 
+		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
+		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 
 		\label{eq_mtl_A12}
 	\end{align}
-	where we denote {\cor revise}
-	$$ \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
-We can calculate the partial expectation of $g(A)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
-\HZ{could you align the Eq so that they look better on page?}
-\begin{align*}	
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-= &\left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \\
-&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\
-&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \\
-& +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\
-		&= \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
-		&+ \sigma^2\tr\left[ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\right] +\sigma^2\tr\left[ \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
-&+ 2 A^2 \sigma^2 \tr\left[ \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
-		& = \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)\right\|^2 +A^2\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-A\beta_2)\right\|^2 +\sigma^2(n_1+n_2-p).
+	where we denote $ \hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$ We can calculate the partial expectation of $g(x)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
+%\HZ{could you align the Eq so that they look better on page?}
+\begin{align}	
+&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \nonumber\\
+&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2 \nonumber\\
+&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2  \nonumber\\
+& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \nonumber\\
+&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
+&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
+& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
+\end{align}
+Using the following identity
+\begin{align*}
+(X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} & =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
+&= (X^{(2)})^\top X^{(2)} \hat \Sigma(x)^{-1}(X^{(1)})^\top X^{(1)},
+\end{align*}
+we can simplify that 
+\begin{align*}
+&  \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2 \\
+&=(\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta_1-x\beta_2)\\
+&+(\beta_1-x\beta_2)^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\\
+%&=(\beta_1-x\beta_2)^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\\
+&=(\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2).
+\end{align*}
+Using this identity and taking expectation over $\epsilon^{(1)}$ and $\epsilon^{(2)}$, we can simplify \eqref{Eg(x)}  to 
+\begin{align*}
+		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \\
+		&= (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  \\
+		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
+&+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
+		& = (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2) +\sigma^2(n_1+n_2-p).
 \end{align*}
@@
 \begin{align}	
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2} \nonumber\\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
-&+ A^2[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-&=[(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
-\end{align}
-where in the first step we used that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
-\begin{align*}
- & (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} + A^2   (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)}  \\
- &=  (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} + A^2  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}  \\
- & =   (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} .
-\end{align*}
-Here in the first step of the above derivation, we used that 
- $$(X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} = (X^{(2)})^\top X^{(2)} \Sigma(A)^{-1}(X^{(1)})^\top X^{(1)}.$$
-
-Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation.
-%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}$.
+&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2} \nonumber\\
+%&=[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
+%&+ A^2[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
+&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+\end{align}
+where we used that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$. 
+%and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
+%\begin{align*}
+% & (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} + A^2   (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}  \\
+% &=  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} + A^2  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}  \\
+% & =   (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} .
+%\end{align*}
+
+Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(x)$ and its partial expectation.
+%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
  \begin{claim}\label{claim_largedev1}
  In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right) $$
+$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right) $$
 for any small constant $c>0$.
-	 \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
+	% \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
  \end{claim}
@@
  \be\label{op_Sig1}
-\| \Sigma(A)^{-1}\|\le \frac1{A^2((\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}})+((\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}) }\lesssim \frac{1}{(A^2+1)p},
- \ee
- where we also used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$ for a small constant $\tau>0$.
+\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
+ \ee
+where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
 
@@
  \begin{align}
- & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
- &=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,\label{expand_6}
+ & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
  \end{align}
@@
  \begin{align*}
-&h_1(A):=  (\beta_1-A\beta_2)^\top (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)  ,\\
-& h_2(A) := {(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
-& h_3(A):=  A^2 { (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
-& h_4(A):=  (\epsilon^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1), \\
-&h_5(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1),\\
-&h_6(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
+&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
+& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
+& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
+& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
+&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
+&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
 \end{align*}
@@
 
-For $h_1(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $\e_1>0$:
-\begin{align}
-&\left|h_1(A) - \exarg{\beta_1,\beta_2}{h_1(A) \mid X_1, X_2}\right|\nonumber \\
-&\le p^{\e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
-&\le p^{e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
-&\lesssim p^{1/2+e_1}\cdot \frac{(A-1)^2\kappa^2 + (A^2+1)d^2/2}{(A^2+1)^2}\lesssim p^{1/2+e_1}(\kappa^2 + d^2).\label{eq_hA1}
+For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
+\begin{align}
+&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
+&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
 \end{align}
@@
 \begin{align*}
-&\left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \\
-&\le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \Sigma(A)^{-1} \right\|^2 \lesssim \frac{p}{(A^2+1)^2}.
+ \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
+ & \lesssim \frac{p}{(x^2+1)^2}.
 \end{align*}  
@@
 Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
-\be\label{eq_hA23}\left|h_2(A) - \exarg{\epsilon^{(1)}}{h_2(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2, \quad \left|h_3(A) - \exarg{\epsilon^{(2)}}{h_3(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2.\ee
-For $h_4(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $\e_1>0$:
-\begin{align}
-\left|h_4(A)\right| &\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]}\cdot \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
-&\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{e_1}\cdot \sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2} \cdot \left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\cdot  \left\|X^{(1)}\right\| \left\|\Sigma(A)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{1/2+e_1}\frac{\sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2}}{A^2+1} \lesssim p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
-\end{align}
-where in the fourth step we used $\left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
+\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
+For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
+\begin{align}
+&\left|h_4(x)\right| \nonumber\\
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
+\end{align}
+where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
 With same argument, we can show that
-\be\label{eq_hA56} \left|h_5(A)\right| \le p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(A)\right| \le p^{1/2+e_1}\sigma^2,\ee
-with high probability for any small constant $e_1>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
+\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
+with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
 
@@
 \paragraph{Part $2$: approximating the global minimum.}
-	Let $\hat{A}$ denote the minimizer of $g(A)$.\HZ{change $\hat{A}$ to say $\hat{x}$.}
-	We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat A$ is close to 1.% This will be used to calculate the predication loss $\te(\hat{\beta}_2^{\MTL})$ loss.
+	Let $\hat{x}$ denote the minimizer of $g(x)$. 
+	We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat x$ is close to 1.% This will be used to calculate the predication loss $\te(\hat{\beta}_2^{\MTL})$ loss.
 %Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
@@
 %There exists a constant $C>0$ such that
-	\be\label{hatw_add1}|\hat A -1|\le  \frac{d^2}{\kappa^2} + p^{-1/4+e_2}. 
+	\be\label{hatw_add1}|\hat x -1|\le  \frac{d^2}{\kappa^2} + p^{-1/4+e_2}. 
 	\ee
@@
 \begin{align*}
-h(A):= [(A-1)^2\kappa^2 + (A^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)}\right].
+h(x):= [(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right].
 \end{align*}
@@
 \begin{align} 
-&\left( A^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
-&\preceq (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1}(X^{(2)})^\top X^{(2)} =\left( A^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
-&\preceq \left( A^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}. \label{op_uplow}
-\end{align}
-Then we get that
-\be\label{eq_h1}h(1)= d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2\left(\rho_1^{-1} + \rho_2^{-1}\right)^{-1}\lesssim pd^2.\ee
-where we used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$. On the other hand, if $|A-1|\ge \delta$ for a small constant $\delta>0$, then we have 
+p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
+&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
+&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
+\end{align}
+where we also used that $1+\tau\le \rho_1=n_1/p \le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
+\be\label{eq_h1}h(1)= d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
+On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have 
 \begin{align}\label{eq_hA}
-h(A)\gtrsim (1+A^2)\kappa^2 \cdot p\left(\rho_1^{-1} + A^2 \rho_2^{-1}\right)^{-1} \gtrsim p\kappa^2 ,
-\end{align}
-where in the first step we used that $|A-1|^2\gtrsim 1+A^2$ for $|A-1|\ge \delta$, $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$, and in the second step we use equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use?
-put it here}.
-Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability,
-\begin{align}
-g(A)&\ge  h(A) +\sigma^2(n_1+n_2-p) -p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
+h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
+\end{align}
+where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and \eqref{op_uplow}. 
+%and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}. 
+Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability, {\cor here}
+\begin{align}
+g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
 &\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
@@
 %Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$. 
-To obtain the better bound \eqref{hatw_add1}, we study the function $h(A)$ more closely and find its minimizer of $h(A)$, denoted by $A^\star$. 
+To obtain the better bound \eqref{hatw_add1}, we study the function $h(x)$ more closely and find its minimizer of $h(x)$, denoted by $A^\star$. 
 %Using Lemma \ref{largedeviation} again, we can simplify equation \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
@@
 %To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof. 
-First it is easy to observe that $h(A)< h(-A)$ for $A> 0$. 
+First it is easy to observe that $h(x)< h(-A)$ for $A> 0$. 
 %$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
@@
 \begin{align*}
-h(A):= [(1-A^{-1})^2\kappa^2 + (1+A^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
+h(x):= [(1-A^{-1})^2\kappa^2 + (1+A^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
 \end{align*}
@@
 $$\tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
-is a decreasing functions in $A$. Hence taking derivative of $h(A)$, we obtain that
+is a decreasing functions in $A$. Hence taking derivative of $h(x)$, we obtain that
 \begin{align}\label{h'(A)2}
@@
 \begin{align*}
-h(A)-h(1)\ge h(A)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^A h'(x)\dd x \gtrsim p\kappa^2 \cdot |A-1|^2  \gtrsim p\frac{d^2}{\kappa^2} + p^{-1/2+2e_2}\cdot p\kappa^2.
+h(x)-h(1)\ge h(x)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^A h'(x)\dd x \gtrsim p\kappa^2 \cdot |A-1|^2  \gtrsim p\frac{d^2}{\kappa^2} + p^{-1/2+2e_2}\cdot p\kappa^2.
 \end{align*}
 Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have 
-$$ h(A)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$
+$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$
 where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
@@
 Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-\frac12c_\infty}\le A\le 1-\delta$, then 
-$$ h(A)-h(1) \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
+$$ h(x)-h(1) \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
 under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?}, which implies the inequality \eqref{gA>g1}.
@@
 
-In general, for $\hat A$ as  the minimizer of $g(A)$, it depends on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+In general, for $\hat A$ as  the minimizer of $g(x)$, it depends on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
 However, using the concentration estimates in Lemma \ref{largedeviation}, we can still obtain the expression on the right-hand side of \eqref{eq_var_2task} up to a small error.
@@
 
-%control the difference between $g(A)$ and its partial expectation. 
+%control the difference between $g(x)$ and its partial expectation. 
  \begin{claim}\label{claim_largedev2}
@@
 &|\hat A |\cdot \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right| \le p^e \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \|_F \\
-&\lesssim p^{e}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \| \lesssim p^{-1/2+e}\sigma d\le p^{-1/2+e}(\sigma^2+ d^2).
+&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \| \lesssim p^{-1/2+e}\sigma d\le p^{-1/2+e}(\sigma^2+ d^2).
 \end{align*}

### 2020-10-07 arxiv/setup.tex
fix notation A
introduction wip

@@
-\paragraph{Linear models.}
+\subsection{Setup and Main Results}
+
 Suppose we have $t$ labeled regression tasks. %where $t$ is a fixed value that does not grow with the feature dimension $p$.
@@
 More specifically, we study how varying properties of task data including task similarity, sample ratio, and covariate shift affects information transfer in multi-task learning.
-
-\subsection{Summary of Results}
 
@@
 
-Let $A = [a_1, a_2, \dots, a_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
+Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
 

### 2020-10-08 arxiv/proof_examples.tex
revise

@@
 %There exists a constant $C>0$ such that
-	\be\label{hatw_add1}|\hat x -1|\le  \frac{d^2}{\kappa^2} + p^{-1/4+e_2}. 
-	\ee
-	for any small constant $e_2>0$.
+	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}. 
+	\ee
+	for any small constant $c>0$.
 	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
@@
 %and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}. 
-Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability, {\cor here}
+Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability,  
 \begin{align}
@@
 \end{align}
-under condition \eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
+under conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
 This gives that
 %\be\label{rough A-1}
-$|\hat A-1|\le \delta$ for any small constant $\delta>0$.
+$|\hat x-1|\le \delta$ for any small constant $\delta>0$.
 
 %Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$. 
-To obtain the better bound \eqref{hatw_add1}, we study the function $h(x)$ more closely and find its minimizer of $h(x)$, denoted by $A^\star$. 
+To obtain the better bound \eqref{hatw_add1}, we study the function $h(x)$ more closely and find its minimizer, denoted by $x^\star$. 
 %Using Lemma \ref{largedeviation} again, we can simplify equation \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
@@
 %To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof. 
-First it is easy to observe that $h(x)< h(-A)$ for $A> 0$. 
+First it is easy to observe that $h(x)< h(-x)$ for $x> 0$. 
 %$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
-Then we consider the case $A\ge 1$. We write
-\begin{align*}
-h(x):= [(1-A^{-1})^2\kappa^2 + (1+A^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
+Then we consider the case $x\ge 1$. We write
+\begin{align*}
+h(x):= [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
 \end{align*}
 Notice that
-$$\tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]$$
-is an increasing functions in $A$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
+$$\tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]$$
+is an increasing functions in $x$. Hence taking derivative of $h(x)$ with respect to $x$, we obtain that
 \begin{align}\label{h'(A)1}
-h'(A) \ge \left[2(1-A^{-1})\frac{\kappa^2}{A^2} - \frac{d^2}{A^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,
-\end{align}
-as long as $A \ge 1+d^2/(2\kappa^2)$.  
+h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - \frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,
+\end{align}
+as long as $x \ge 1+d^2/(2\kappa^2)$.  
 %\begin{align}
@@
 %which gives $\hat w\le w_1$.
-Next we consider the case $1-\delta\le A\le 1$. Notice that
-$$\tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
-is a decreasing functions in $A$. Hence taking derivative of $h(x)$, we obtain that
+Next we consider the case $1-\delta\le x\le 1$. Notice that
+$$\tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
+is a decreasing functions in $x$. Hence taking derivative of $h(x)$, we obtain that
 \begin{align}\label{h'(A)2}
-	h'(A)\le [-2(1-A)\kappa^2 + Ad^2] \cdot p^{-1} \tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,
-\end{align}
-as long as $A \le 1-d^2/(2\kappa^2)$. In sum, we see that the minimizer $A^\star$ must satisfy
-$$1-d^2/(2\kappa^2)\le A^\star \le 1+d^2/(2\kappa^2).$$
+	h'(x)\le [-2(1-x)\kappa^2 + xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,
+\end{align}
+as long as $x\le 1-d^2/(2\kappa^2)$. In sum, we see that the minimizer $x^\star$ must satisfy
+$$1-d^2/(2\kappa^2)\le x^\star \le 1+d^2/(2\kappa^2).$$
 
@@
 
-Now we are ready to prove equation \eqref{hatw_add1}. First using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le A\le 1+\delta$,
-$$h'(A)\ge \frac{2(A-1)\kappa^2 - d^2}{A^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + A^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
-Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+e_2}\le A\le 1+\delta$,
-\begin{align*}
-h(x)-h(1)\ge h(x)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^A h'(x)\dd x \gtrsim p\kappa^2 \cdot |A-1|^2  \gtrsim p\frac{d^2}{\kappa^2} + p^{-1/2+2e_2}\cdot p\kappa^2.
-\end{align*}
-Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have 
-$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$
-where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
-Second using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le A \le 1-d^2/\kappa^2$,
-$$- h'(A)\ge  [2(1-A)\kappa^2 - Ad^2] \cdot p^{-1} \tr\left[\left(A^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |A-1|\kappa^2\right).$$
-Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-\frac12c_\infty}\le A\le 1-\delta$, then 
-$$ h(x)-h(1) \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right)$$
-under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?}, which implies the inequality \eqref{gA>g1}.
-In sum, we obtain that the minimizer $\hat A$ must satisfy equation \eqref{hatw_add1}.
+Now we are ready to prove equation \eqref{hatw_add1}. First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le x\le 1+\delta$,
+$$h'(x)\ge \frac{2(x-1)\kappa^2 - d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
+Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+c}\le x\le 1+\delta$,
+\begin{align*}
+h(x)-h(1)\ge h(x)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot |x-1|^2  \gtrsim p\frac{d^4}{\kappa^2} + p^{-1/2+2c}\cdot p\kappa^2 .
+\end{align*}
+On the other hand, by Claim \ref{claim_largedev1} we have that
+$$ g(x)=h(x)+\sigma^2 (n_1+n_2-p)+\OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right)$$
+with high probability. Combining the above two estimates, we obtain that under the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$,
+$$g(x)-g(1) = h(x)-h(1) + \OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right) >0$$
+with high probability, i.e. $x$ cannot be the minimizer of $g$. 
+%Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have 
+%$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$ where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
+Second, using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le x \le 1-d^2/\kappa^2$,
+$$- h'(x)\ge  [2(1-x)\kappa^2 - xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
+Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-1/4+c}\le x\le 1-\delta$, then 
+$$ h(x)-h(1) \gtrsim p\frac{d^4}{\kappa^2} +p^{1/2+2c} \kappa^2, $$
+%under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?}, 
+which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ must satisfy equation \eqref{hatw_add1}.
 %Next we prove the following estimate on the optimizer $\hat A$: with high probability,
@@
 \paragraph{Part $3$: Applying Theorem \ref{thm_main_RMT}.}
-We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat A=\hat A_1/\hat A_2$:
+We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat x=\hat A_1/\hat A_2$:
 \begin{align}
 L(\hat{\beta}_2^{\MTL}) &=\left|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right| \nonumber\\
-&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,\label{Lbeta_HPS}
-\end{align}
-where we denoted
-$$\hat \Sigma:= \hat A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
-To illustrate the idea of bias-variance decomposition, we assume that $\hat A$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
+&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta_1-\hat x^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
+\end{align}
+%where we denoted $$\hat \Sigma:= \hat A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+To illustrate the idea of bias-variance decomposition, we assume that $\hat x$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
 Then we can calculate the partial expectation of $L(\hat{\beta}_2^{\MTL})$ over the randomness in $\epsilon_1$ and $\epsilon_2$:

### 2020-10-08 arxiv/intro.tex
abstract

@@
 \begin{abstract}
-	Multi-task learning is a powerful approach in many applications such as image and text classification.
+	Hard parameter sharing is a widely used approach to learn from multiple tasks in many applications, such as text classification.
+	The idea is that all tasks share the same feature layer, while each task uses a specific output layer for prediction.
+	Intuitively, the performance of hard parameter sharing depends on dataset properties such as their sample sizes.
+	Yet, rigorously formulating such intuition can be technically challenging.
+	This paper analyzes the generalization performance of hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio.
+	We present tight generalization bounds
+	%that scale with datasets' sample sizes and the spectrum of their feature covariates
+	for two canonical cases:
+	(i) multiple tasks with the same feature covariates;
+	(ii) two tasks with arbitrarily different sample sizes and covariance matrices.
+	We also demonstrate that these estimates for the empirical loss of hard parameter sharing are incredibly accurate in modest dimensions.
+	Finally, we apply our results to explain several intriguing phenomena; for example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
+	This suggests progressively adding data as a more efficient procedure for optimizing hard parameter sharing, and we validate its efficiency in a text classification task.
+%	Multi-task learning is a powerful approach in many applications such as image and text classification.
 Yet, there is little rigorous understanding of when multi-task learning outperforms single-task learning.
@@
 Inspired by our theory, we show two practical connections of interest.
-	First, single-task results can help to understand when multi-task learning gives gains.
+%	First, single-task results can help to understand when multi-task learning gives gains.
 Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.
@@
 
+\iffalse
 %Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
@@
 %We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
+\fi

### 2020-10-08 arxiv/diff_cov.tex
revise

@@
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
-\begin{align*}
+\begin{align}\label{def hatsig}
 	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
-\end{align*}
+\end{align}
 For the prediction loss, the empirical loss is close to the expected loss similar to what we have shown in Claim \ref{claim_pred_err}.
@@
 	 \end{align}
-%	 {\color{red}[FY: there is an extra $\kappa^2$ term]} + p^{-c_\infty}\cdot \OO(\kappa^2)
-%	 for a large constant $C>0$.
+	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
+We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
 	 \end{corollary}

### 2020-10-08 arxiv/proof_examples.tex
revise

@@
 which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ must satisfy equation \eqref{hatw_add1}.
-%Next we prove the following estimate on the optimizer $\hat A$: with high probability,
+%Next we prove the following estimate on the optimizer $\hat x$: with high probability,
 %%\begin{lemma}
@@
 \paragraph{Part $3$: Applying Theorem \ref{thm_main_RMT}.}
-We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat x=\hat A_1/\hat A_2$:
-\begin{align}
-L(\hat{\beta}_2^{\MTL}) &=\left|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right| \nonumber\\
+We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat x=\hat x_1/\hat x_2$:
+\begin{align}
+L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat x_2 - \beta_2\right)\right\| \nonumber\\
 &=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta_1-\hat x^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
 \end{align}
-%where we denoted $$\hat \Sigma:= \hat A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+%where we denoted $$\hat \Sigma:= \hat x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
 To illustrate the idea of bias-variance decomposition, we assume that $\hat x$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
@@
  \begin{align}
-	&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2,\beta_1,\beta_2} \nonumber \\
-&	=  \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 \nonumber\\ %\label{eq_bias_2task} 
-			& + \sigma^2\cdot \bigtr{ X^{(2)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(2)})^\top}+ \sigma^2\cdot \hat A^2 \bigtr{ X^{(1)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(1)})^\top}\nonumber\\
+	\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2,\beta_1,\beta_2}  &=  \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} (\hat x \beta_1 - \hat x^2\beta_2)}^2 \nonumber\\ %\label{eq_bias_2task}
+			& + \sigma^2\cdot \bigtr{ X^{(2)} \hat\Sigma(\hat x)^{-1}\Sigma^{(2)}\hat\Sigma(\hat x)^{-1} (X^{(2)})^\top} \nonumber\\
+			&+ \sigma^2\cdot \hat x^2 \bigtr{ X^{(1)} \hat\Sigma(\hat x)^{-1}\Sigma^{(2)}\hat\Sigma(\hat x)^{-1} (X^{(1)})^\top}\nonumber\\
 			%+\sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } \nonumber\\ 
-			&= \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).\nonumber
+			&= \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} (\hat x \beta_1 - \hat x^2\beta_2)}^2 +\sigma^2  \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).\nonumber
 			%\label{eq_var_2task}
@@
  \begin{align}
-	\exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}&	=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} }\nonumber \\
-	&+\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
+	& \exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2} \nonumber\\
+	&	=  \hat x^2 \left[(\hat x-1)^2 \kappa^2 + \frac{(\hat x^2+1)d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} }\nonumber \\
+	&+\sigma^2 \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
 			\label{eq_var_2task}
@@
 \begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
+	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma^{(2)} (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
 \end{align}
@@
 
-In general, for $\hat A$ as  the minimizer of $g(x)$, it depends on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
-However, using the concentration estimates in Lemma \ref{largedeviation}, we can still obtain the expression on the right-hand side of \eqref{eq_var_2task} up to a small error.
+In general, for $\hat x$ as  the minimizer of $g(x)$, it depends on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+However, using the concentration estimates in Lemma \ref{largedeviation}, we can still obtain the expression in equation \eqref{eq_var_2task} up to a small error.
 In particular, our proof will not use Lemma \ref{lem_hat_v}.
@@
  \begin{claim}\label{claim_largedev2}
- In the setting of Proposition \ref{cor_MTL_loss}, if $\hat A=\OO(1)$, then we have that with high probability,
-$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat A)\right| \le p^{-1/2+e} \left(\sigma^2 +\kappa^2 +d^2 \right),$$
-for any small constant $e>0$. Here we introduced the function
-\begin{align*}
-	\cal L(\hat A)	:=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} } +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
+ In the setting of Proposition \ref{cor_MTL_loss}, if $\hat x=\OO(1)$, then we have that with high probability,
+$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),$$
+for any small constant $c>0$. Here we introduced the function
+\begin{align*}
+	\cal L(\hat x)	:=  &\hat x^2\left[(\hat x-1)^2 \kappa^2 + \frac{(\hat x^2+1)d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} } \\
+	& +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
 \end{align*}
@@
  \begin{proof}
- The proof of this claim is very similar to the one for Claim \ref{claim_largedev1}, where the only difference is that $\hat A$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
-In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat A$ can be pulled out as a coefficient.
+ The proof of this claim is very similar to the one for Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
 Here we only give an outline of the proof without writing down all the details.
@@
 Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
-Moreover, we denote the task-specific components by $\wt\beta_1$ and $\wt\beta_2$, whose entries i.i.d.
+Moreover, we denote the task-specific components by $\wt\beta_1$ and $\wt\beta_2$, whose entries are i.i.d.
 Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$.
@@
  \begin{align}
-L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A -\hat A^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat A\wt \beta_1 - (X^{(1)})^\top X^{(1)}  \hat A^2\wt \beta_2 \right] \right.
-\\
-&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
+L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta_1 - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta_2 \right] \right.
+\nonumber\\
+&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
 \end{align}
 As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}.
-For example, for the main term $\hat A^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
-Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $e>0$:
-\begin{align*}
-&\hat A^2 \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1 - d^2 \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
-&\le p^e\cdot p^{-1}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
-&\le p^{-1/2+\e}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+\e}d^2.
-\end{align*} 
-For the cross term $\hat A \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $e>0$:
-\begin{align*}
-&|\hat A |\cdot \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right| \le p^e \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \|_F \\
-&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma^{-1}  \Sigma^{(2)} \hat \Sigma^{-1}  (X^{(2)})^\top  \| \lesssim p^{-1/2+e}\sigma d\le p^{-1/2+e}(\sigma^2+ d^2).
+For example, for the main term $\hat x^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
+Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+\begin{align*}
+&  \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1 - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
+&\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
+&\le p^{-1/2+c}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+c}d^2.
+\end{align*} 
+For the cross term $\hat x \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+\begin{align*}
+ \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
+&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
+&\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
 \end{align*}
@@
 
-In the specific setting in Proposition \ref{cor_MTL_loss}, we can further simplify $\cal L(\hat A)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
+In the setting of Proposition \ref{cor_MTL_loss}, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
 
@@
 \begin{align}
-&\left|\cal L(\hat A)- d^2\cdot {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\Sigma(1)^{-1}  }\right| \nonumber\\
-&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2e}\kappa^2 +  p^{-1/4+e} (\sigma^2 +d^2) , \label{simple1}
-\end{align}
-for any small constant $e>0$, where we recall that $\Sigma(1)= (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
+&\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
+&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple1}
+\end{align}
+for any small constant $c>0$, where we recall that $\hat \Sigma=\hat \Sigma(1)$ as defined in \eqref{def hatsig}.
 \end{claim}
 \begin{proof}
-Using Lemma \ref{lem_hat_v} and Fact \ref{lem_minv} (iii), we can obtain that with high probability,
-\begin{align}
-&\|\Sigma(1)^{-1}-\hat\Sigma^{-1}\| \le |\hat A-1|\|\Sigma(1)^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma^{-1}\| \label{est111}\\
-&\lesssim \left(\frac{d^2}{\kappa^2} + p^{-1/4+e}\right)\frac{(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}}{ \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}  + (\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^2  }\lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+e}\right),\nonumber
-\end{align}
-for any small constant $e>0$. With similar arguments, we can get that with high probability,
+Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+\begin{align}
+ \|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1|\|\hat\Sigma^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right),\label{est111}
+\end{align}
+for any small constant $c>0$. With similar arguments, we can get that with high probability,
 \begin{align}\label{est222}
-&\left\|\left(\Sigma(1)^{-2}-\hat\Sigma^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+e} .
-\end{align}
-Moreover, using Fact \ref{lem_minv} (iii) we can bound that with high probability,
-$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
-which further implies that with high probability,
-\be\label{est333}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim p.\ee
-Now we bound the left-hand side of \eqref{simple1} as \HZ{replace $\Sigma(1)$ with $\hat{\Sigma}$ throughout}
-\begin{align*}
-&\left|\cal L(\hat A)-\frac{d^2}{p}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\Sigma(1)^{-1}  }\right| \\
-&\lesssim \left(|\hat A-1|^2 \kappa^2 + |\hat A-1|d^2\right)\cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} } \\
-&+ \frac{d^2}{p}\left|\tr\left[\left(\Sigma(1)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\Sigma(1)^{-1}-\hat\Sigma^{-1}  }\right|.
+&\left\|\left(\hat\Sigma^{-2}-\hat\Sigma(\hat x)^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+c} .
+\end{align}
+Moreover, using equations \eqref{op_X12}-\eqref{op_Sig1} we can bound that with high probability,
+%$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
+%which further implies that with high probability,
+\begin{align}
+& \bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}  \le p \bignorm{\hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}\lesssim p.\label{est333}
+\end{align}
+Now we bound the left-hand side of \eqref{simple1} as % \HZ{replace $\Sigma(1)$ with $\hat{\Sigma}$ throughout}
+\begin{align*}
+&\left|\cal L(\hat x)-\frac{d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat\Sigma^{-1}  }\right)\right| \\
+&\lesssim \left(|\hat x-1|^2 \kappa^2 + |\hat x-1|d^2\right)\cdot p^{-1}\bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2 } \\
+&+ \frac{d^2}{p}\left|\tr\left[\left(\hat\Sigma(\hat x)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\hat\Sigma(\hat x)^{-1}-\hat\Sigma^{-1}  }\right|.
 \end{align*}
@@
 % \todo{switch the $a_3$ and $a_4$}
-Finally, we are ready to present the proof of Proposition \ref{cor_MTL_loss}.
-We derive the variance term $\sigma^2  \bigtr{\Sigma(1)^{-1}  }$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
+Finally, we are ready to complete the proof of Proposition \ref{cor_MTL_loss}.
+We derive the variance term $\sigma^2  \tr(\hat\Sigma^{-1})$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
 %For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
@@
 Using \eqref{lem_cov_shift_eq}, we obtain that 
-\be\label{eq_var111}\bigtr{\Sigma(1)^{-1}  } = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1\id_p+a_2\id_p)^{-1}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Then solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that with high probability,
+\be\label{eq_var111}\tr(\hat\Sigma^{-1}) = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1\id_p+a_2\id_p)^{-1}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
+with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
 	\begin{align}
@@
 Inserting it into \eqref{eq_var111}, we obtain that 
-\be\label{eq_var112}\bigtr{\Sigma(1)^{-1}  } = \frac{p}{n_1+n_2} \cdot \frac{\rho_1+\rho_2}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})=  \frac{1}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})\ee
+\be\label{eq_var112}\tr(\hat\Sigma^{-1})  = \frac{p}{n_1+n_2} \cdot \frac{\rho_1+\rho_2}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})=  \frac{1}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})\ee
 with high probability.
 
-On the other hand, using Fact \ref{lem_minv} (iii), we can bound that with high probability,
-\begin{align}
- \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii}  &\le {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
- &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii} .\nonumber
+On the other hand, we have that with high probability,
+\begin{align}
+ \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\hat \Sigma^{-2}\right)_{ii}  &\le {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
+ &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} .\nonumber
 \end{align}
 To obtain this inequality, we used  
-$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \prec \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
+$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
 by Fact \ref{lem_minv} (iii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
@@
 \begin{align}\label{eq_bias112}
- \left(\Sigma(1)^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})
+ \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})
 \end{align}
@@
 \begin{align*}%\label{eq_bias113}
- \left(\Sigma(1)^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} +\OO(p^{-c_\varphi})
+ \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} +\OO(p^{-c_\varphi})
 \end{align*}
@@
 \begin{align*}%\label{eq_bias113}
-\left| \left(\Sigma(1)^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{-\frac{\varphi-4}{2\varphi}}
+\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{-\frac{\varphi-4}{2\varphi}}
 \end{align*}
@@
 \begin{align*} 
-\left| \sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{1-\frac{\varphi-4}{2\varphi}}
+\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{1-\frac{\varphi-4}{2\varphi}}
 \end{align*}
@@
 \end{align}
-with high probability. Inserting \eqref{eq_bias113} into \eqref{eq_bias111}. we get
+with high probability. Inserting \eqref{eq_bias113} into \eqref{eq_bias111}, we get that
 \begin{align}
 & \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\nonumber \\
-&\le  {p}^{-1}\tr\left[\Sigma(1)^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} \nonumber\\
+&\le  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} \nonumber\\
 &  \le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\label{eq_bias114}
@@
 \begin{align}
-\left|\cal L(\hat A)- -\frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right| \le   \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \nonumber\\
-+C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2e}\kappa^2 +  p^{-1/4+e} (\sigma^2 +d^2) \right) \label{simple1add}
-\end{align}
-with high probability for some constant $C>0$. Then using Claim \ref{claim_largedev2} and noticing that the constant $e>0$ can be arbitrarily small, we conclude \eqref{cor_MTL_error}.
+\left|\cal L(\hat x)- \frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right| \le   \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \nonumber\\
++C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right) \label{simple1add}
+\end{align}
+with high probability for some constant $C>0$.
+Then using Claim \ref{claim_largedev2} and the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$, we conclude \eqref{cor_MTL_error} by noticing that the constant $c>0$ can be arbitrarily small.
+%, we conclude \eqref{cor_MTL_error}
 \end{proof}
@@
 With equation \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
-%With slight abuse of notations, we shall write $\hat a_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.
+%With slight abuse of notations, we shall write $\hat x_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.
 

### 2020-10-08 arxiv/intro.tex
introduction wip

@@
 This paper analyzes the generalization performance of hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio.
-	We present tight generalization bounds
-	%that scale with datasets' sample sizes and the spectrum of their feature covariates
-	for two canonical cases:
-	(i) multiple tasks with the same feature covariates;
-	(ii) two tasks with arbitrarily different sample sizes and covariance matrices.
+We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample sizes and covariance matrices.
 We also demonstrate that these estimates for the empirical loss of hard parameter sharing are incredibly accurate in modest dimensions.
-	Finally, we apply our results to explain several intriguing phenomena; for example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
-	This suggests progressively adding data as a more efficient procedure for optimizing hard parameter sharing, and we validate its efficiency in a text classification task.
+Finally, we explain several intriguing empirical phenomena.
+For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
+This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in a text classification task.
 %	Multi-task learning is a powerful approach in many applications such as image and text classification.

### 2020-10-08 arxiv/diff_cov.tex
restructure B.2

@@
 	 \end{align}
-	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
+%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
 We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}

### 2020-10-08 arxiv/proof_examples.tex
restructure B.2

@@
 
-%\subsubsection{Proof for Sample Imbalance}
-We provide the proof of Proposition \ref{cor_MTL_loss}. Similar to the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following parts:
-\begin{itemize}
-\item First, we reduce the optimization objective to another function $g(x)$ that only depends on the sample covariance matrices.
-\item Second, we show that the global minimizer of $g(x)$ is approximately equal to $1$.
-\item Finally, we use the above result and Theorem \ref{thm_main_RMT} to prove the proposition.
-\end{itemize}
-
-\iffalse
-%Our key insight is a bias-variance decomposition of the expected prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} W_2$.
-%Using the local optimality condition of $B$, we obtain that
-%\begin{align*}
-%	 \hat{B}(W_1, W_2) &= (W_1^2 X_1^{\top}X_1 + W_2^2 X_2^{\top}X_2)^{-1} (W_1 X_1^{\top}Y_1 + W_2 X_2^{\top}Y_2)\\
-%	&= \frac{1}{W_2} \left( \frac{W_1^2}{W_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{W_1}{W_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \\
-%	&= \frac{1}{W_2}\left[\beta_2 + \left(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{W_1}{W_2}\beta_1 - \frac{W_1^2}{W_2^2} \beta_2\right) + \left(\frac{W_1}{W_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right].
-%\end{align*}
-Recall that $\hat{\beta}_i^{\MTL} = \hat{B} W_i$. Therefore, we have
-\begin{align}
-	\exarg{\epsilon_1, \epsilon_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}
-	=&~ \frac{W_1^2}{W_2^2} \bignorm{\Sigma_2^{1/2}(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_1 - \frac{W_1}{W_2} \beta_2)}^2 \label{eq_bias_2task} \\
-			&+~  \sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }. \label{eq_var_2task}
-\end{align}
-equation \eqref{eq_bias_2task} is the bias of $\hat{\beta}_t^{\MTL}$ and
-equation \eqref{eq_var_2task} is the variance of $\hat{\beta}_t^{\MTL}$.
-%minus the variance of $\hat{\beta}_t^{\STL}$, which is always negative.
-Comparing the above to single-task learning, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-
-% \todo{derive the test loss} Expectation was given in equation \eqref{eq_bias_2task} and equation \eqref{eq_var_2task}.
- \fi
-
-\paragraph{Part $1$: the reduction.}
-Under the two-task setting of Corollary \ref{cor_MTL_loss}, the optimization objective \eqref{eq_mtl} becomes
-	\begin{align}
-		f(A_1,A_2, B) =   \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2+ \bignorm{X^{(2)} B A_2 - Y^{(2)}}^2, \label{eq_mtl_2task_cov}
-	\end{align}
-	where $B \in \real^{p}$ and $A_1, A_2\in \R$ because $r=1$ in the two-task case. % for $1 < r < t$ by our assumption.
-	Without loss of generality, we assume that both $A_1$ and $A_2$ are nonzero, since otherwise we can add a small perturbation $\delta$ to them and later remove this perturbation by taking $\delta\to 0$ in the final result.
-Again using the local optimality condition ${\partial f}/{\partial B} = 0$, for any $A_1$ and $A_2$ we obtain the optimal $\hat{B}$ as follows
+We provide the proof of Corollary \ref{cor_MTL_loss}. The proof is similar to that of Theorem \ref{thm_many_tasks}.
+First, we reduce the optimization objective to another function $g(x)$ that only depends on the sample covariance matrices.
+Second, we show that the global minimizer of $g(x)$ is approximately equal to $1$.
+Finally, we use the above result and Theorem \ref{thm_main_RMT} to prove the proposition.
+
+In the setting of Corollary \ref{cor_MTL_loss}, the optimization objective \eqref{eq_mtl} is equal to
+	\begin{align}
+		f(A, B) =   \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2+ \bignorm{X^{(2)} B A_2 - Y^{(2)}}^2, \label{eq_mtl_2task_cov}
+	\end{align}
+	where $B \in \real^{p}$ and $A = [A_1, A_2]\in \real^{2}$ because the width of $B$ is one.
+We assume that $A_1$ and $A_2$ are both nonzero.
+Otherwise, we add a tiny amount of perturbation $\delta$ to them and the result remains the same.
+Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we have that $\hat{B}$ satisfies the following
 	\begin{align}
@@
 	\end{align}
- Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers.
+Let denote $\hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
+Applying $\hat B$ to equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers.
 Could you replace $A$ with another symbol (say $x$)?}
@@
 		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
-		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 
+		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2.
 		\label{eq_mtl_A12}
 	\end{align}
-	where we denote $ \hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$ We can calculate the partial expectation of $g(x)$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
+The conditional expectation of $g(x)$ over $\epsilon_1$ and $\epsilon_2$ is
 %\HZ{could you align the Eq so that they look better on page?}
 \begin{align}
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \nonumber\\
+\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}
 &= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2 \nonumber\\
@@
  & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2 \\
-&=(\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta_1-x\beta_2)\\
+=&(\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta_1-x\beta_2)\\
 &+(\beta_1-x\beta_2)^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\\
 %&=(\beta_1-x\beta_2)^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\\
-&=(\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2).
+=&(\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2).
 \end{align*}
@@
 		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-		&= (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  \\
+		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  \\
 		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
 &+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
-		& = (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2) +\sigma^2(n_1+n_2-p).
-\end{align*}
-For the random-effects model, we can further take the partial expectation over $\beta_1$ and $\beta_2$: 
+		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2) +\sigma^2(n_1+n_2-p).
+\end{align*}
+For the random-effects model, we take the expectation over $\beta_1$ and $\beta_2$:
 \begin{align}
@@
 where we used that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$.
-%and in the second step we used  %Using $(X^{(2)})^\top X^{(2)}=\hat\Sigma- A^2 (X^{(1)})^\top X^{(1)}$, we can further simplify that
-%\begin{align*}
-% & (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} + A^2   (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}  \\
-% &=  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} + A^2  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}  \\
-% & =   (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} .
-%\end{align*}
-
-Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(x)$ and its partial expectation.
-%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
- \begin{claim}\label{claim_largedev1}
- In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right) $$
-for any small constant $c>0$.
-	% \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
- \end{claim}
- \begin{proof}
-By Fact \ref{lem_minv} (iii), we have that with high probability,
- \be\label{op_X12}
-\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
- \ee
- and
- \be\label{op_Sig1}
-\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
- \ee
-where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
-
- Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
- \begin{align}
- & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
-		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
- \end{align}
- where
- \begin{align*}
-&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
-& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
-& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
-& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
-&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
-&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
-\end{align*}
-Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.
-
-For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
-\begin{align}
-&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
-&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
-\end{align}
- Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
-\begin{align*}
- \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
- & \lesssim \frac{p}{(x^2+1)^2}.
-\end{align*}  
-Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
-\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
-For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
-\begin{align}
-&\left|h_4(x)\right| \nonumber\\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
-\end{align}
-where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
-With same argument, we can show that
-\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
-with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
-
-Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, which conclude the proof of Claim \ref{claim_largedev1}.
- \end{proof}
-
-\paragraph{Part $2$: approximating the global minimum.}
+
+\paragraph{Part $1$: approximating the global minimum.}
 	Let $\hat{x}$ denote the minimizer of $g(x)$.
@@
 %Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
- In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
+ In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability,
 %There exists a constant $C>0$ such that
@@
 	\ee
-	for any small constant $c>0$.
+%	for any small constant $c>0$.
 	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
@@
 
-\paragraph{Part $3$: Applying Theorem \ref{thm_main_RMT}.}
+\paragraph{Part $2$: reducing the random-effects model to Theorem \ref{thm_main_RMT}.}
+Using the concentration estimates in Lemma \ref{largedeviation}, we first show that $g(x)$ and its conditional expectation over $X^{(1)}, X^{(2)}$ are close.
+%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
+ \begin{claim}\label{claim_largedev1}
+ In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
+$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right)$$.
+%for any small constant $c>0$.
+	% \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
+ \end{claim}
+ \begin{proof}
+By Fact \ref{lem_minv} (iii), we have that with high probability,
+ \be\label{op_X12}
+\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
+ \ee
+ and
+ \be\label{op_Sig1}
+\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
+ \ee
+where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
+
+ Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
+ \begin{align}
+ & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
+ \end{align}
+ where
+ \begin{align*}
+&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
+& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
+& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
+& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
+&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
+&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
+\end{align*}
+Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.
+
+For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
+\begin{align}
+&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
+&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
+\end{align}
+ Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
+\begin{align*}
+ \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
+ & \lesssim \frac{p}{(x^2+1)^2}.
+\end{align*}  
+Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
+For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
+\begin{align}
+&\left|h_4(x)\right| \nonumber\\
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
+\end{align}
+where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
+With same argument, we can show that
+\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
+with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
+
+Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, which conclude the proof of Claim \ref{claim_largedev1}.
+ \end{proof}
+
 We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat x=\hat x_1/\hat x_2$:
@@
 
-% \todo{switch the $a_3$ and $a_4$}
-Finally, we are ready to complete the proof of Proposition \ref{cor_MTL_loss}.
+\paragraph{Part $3$: Applying Theorem \ref{thm_main_RMT}.}
+Finally, we are ready to complete the proof of Corollary \ref{cor_MTL_loss}.
 We derive the variance term $\sigma^2  \tr(\hat\Sigma^{-1})$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
@@
 
-\begin{proof}[Proof of Proposition \ref{cor_MTL_loss}]
+\begin{proof}[Proof of Corollary \ref{cor_MTL_loss}]
 %The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace equation \eqref{bounddelta-} with a tighter bound.

### 2020-10-08 arxiv/proof_examples.tex
comments B.2

@@
 \paragraph{Part $2$: reducing the random-effects model to Theorem \ref{thm_main_RMT}.}
+\HZ{restructure this part. merge the result of B.17 and B.18, and state it upfront. separate its proof into two parts}
 Using the concentration estimates in Lemma \ref{largedeviation}, we first show that $g(x)$ and its conditional expectation over $X^{(1)}, X^{(2)}$ are close.
@@
 
+\HZ{just say that this calculation of B.97 is similar to B.81?}
 We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat x=\hat x_1/\hat x_2$:

### 2020-10-08 arxiv/proof_examples.tex
B.2 touch base

@@
 Let $\hat{x}$ denote the minimizer of $g(x)$.
-	We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat x$ is close to 1.% This will be used to calculate the predication loss $\te(\hat{\beta}_2^{\MTL})$ loss.
-%Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
-%Furthermore, under certain choice of parameters, we can simplify
-%More precisely, we have the following claim.
-%Later on, we will combine it with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.
+We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat x$ is close to 1.
+
+Using the concentration estimates in Lemma \ref{largedeviation}, we first show that $g(x)$ and its conditional expectation over $X^{(1)}, X^{(2)}$ are close.
+%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
+ \begin{claim}\label{claim_largedev1}
+ In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
+$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right)$$.
+%for any small constant $c>0$.
+	% \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
+ \end{claim}
+ \begin{proof}
+By Fact \ref{lem_minv} (iii), we have that with high probability,
+ \be\label{op_X12}
+\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
+ \ee
+ and
+ \be\label{op_Sig1}
+\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
+ \ee
+where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
+
+ Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}:
+ \begin{align}
+ & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
+ \end{align}
+ where
+ \begin{align*}
+&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
+& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
+& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
+& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
+&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
+&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
+\end{align*}
+Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.
+
+For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
+\begin{align}
+&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
+&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
+\end{align}
+ Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
+\begin{align*}
+ \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
+ & \lesssim \frac{p}{(x^2+1)^2}.
+\end{align*}
+Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
+For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
+\begin{align}
+&\left|h_4(x)\right| \nonumber\\
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
+\end{align}
+where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
+With same argument, we can show that
+\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
+with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
+
+Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, which conclude the proof of Claim \ref{claim_largedev1}.
+ \end{proof}
 
@@
 \HZ{restructure this part. merge the result of B.17 and B.18, and state it upfront. separate its proof into two parts}
-Using the concentration estimates in Lemma \ref{largedeviation}, we first show that $g(x)$ and its conditional expectation over $X^{(1)}, X^{(2)}$ are close.
-%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
- \begin{claim}\label{claim_largedev1}
- In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
-$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right)$$.
-%for any small constant $c>0$.
-	% \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
- \end{claim}
- \begin{proof}
-By Fact \ref{lem_minv} (iii), we have that with high probability,
- \be\label{op_X12}
-\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
- \ee
- and
- \be\label{op_Sig1}
-\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
- \ee
-where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
-
- Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
- \begin{align}
- & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
-		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
- \end{align}
- where
- \begin{align*}
-&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
-& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
-& h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
-& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
-&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
-&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
-\end{align*}
-Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.
-
-For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
-\begin{align}
-&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
-&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
-\end{align}
- Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
-\begin{align*}
- \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
- & \lesssim \frac{p}{(x^2+1)^2}.
-\end{align*}  
-Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
-\be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
-For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
-\begin{align}
-&\left|h_4(x)\right| \nonumber\\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
-\end{align}
-where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
-With same argument, we can show that
-\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
-with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
-
-Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, which conclude the proof of Claim \ref{claim_largedev1}.
- \end{proof}
 

### 2020-10-08 arxiv/diff_cov.tex
section 3 4 polish writing

@@
 
-The different covariates case differs from the same covariates case in two key aspects.
+The different covariates case differs from the same covariates case in two aspects.
 First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
@@
 
-Unlike the previous section, we no longer have an optimal solution for $A$.
-This is because the minimization problem is non-convex with respect to $A$ and $B$.
-Therefore, we consider an arbitrary local minimum of equation \eqref{eq_mtl} and provide generalization bounds that scale with key properties of task data.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.
+Unlike the previous section, we no longer have an optimal solution for $f(A, B)$.
+This is because $f(A, B)$ is in general non-convex.
+Our result implies tight generalization bounds for any local minimum of $f(A, B)$.
+We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
 
-We develop a key technical result using recent developments in random matrix theory.
-To motivate our study, we consider a specialized setting where the output layer weights $A_1, A_2$ are both equal to one.
-Without loss of generality, we consider the prediction loss of hard parameter sharing for task two and the same analysis applies to task one.
+Our key result characterizes the asymptotic limit of the sum of two arbitrarily different sample covariance matrices.
+To motivate our study, consider a special case where $A$ is equal to one.
+Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
@@
 \end{align}
-For the prediction loss, the empirical loss is close to the expected loss similar to what we have shown in Claim \ref{claim_pred_err}.
+The matrix $\hat{\Sigma}$ adds up both tasks' sample covariances, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
+The empirical loss of $\hat{\beta}_2^{\MTL}$ is close to its expectation similar to Claim \ref{claim_pred_err}.
 Hence, we consider the expected loss conditional on the covariates as follows:
@@
 
-Interestingly, the prediction loss admits a bias-variance decomposition similar to the same covariates setting.
-The variance equation scales with the sample covariance matrice of both tsks, whereas the bias equation scales additionally with the distance between the beta vectors.
-In both the bias and variance equations, the matrix inverse $\hat{\Sigma}^{-1}$ is a crucial quantity.
-Intuitively, this matrix inverse combines the sample covariance matrix of both tasks, and it is not hard to see that the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by the sample sizes.
-However, since the two tasks have different covariates, the scaling of $\hat{\Sigma}^{-1}$ not only depends on the tasks' sample sizes, but also depends on the covariate shift between the two tasks.
-Building on the intuition, We introduce a key result that shows tight asymptotic convergence rate of the bias and variance as $p$ goes to infinity.
-We define a key quantity $M \define \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
+Interestingly, the expected loss also admits a nice bias-variance decomposition.
+Our main result in this section characterizes the asymptotic limit of the above equation, when both sample size and feature dimension become increasingly large at a fixed ratio.
+The main technical challenge of our result deals with the ``covariate shift'' between task one and two.
+Intuitively, the scaling of $\hat{\Sigma}^{-1}$ not only depends on both tasks' sample sizes, but also depends on their covariance matrices.
+We introduce a key quantity $M \define \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
 Let $U\Lambda V^\top$ denote the singular value decomposition of $M$, where $\Lambda\in\real^{p\times p}$ consists of $M$'s singular values $\lambda_1, \lambda_2, \dots, \lambda_p$ as its diagonal entries in descending order.
+Our main result is stated as follows.
 
 \begin{theorem}\label{thm_main_RMT}
-	Suppose that $X_1$ and $X_2$ are both random matrices that satisfy Assumption \ref{assume_rm}.
+	Suppose that $X^{(1)}$ and $X^{(2)}$ are both random matrices that satisfy Assumption \ref{assume_rm}.
 	Assume that: a) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$; b) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-	With high probability over the randomness of $X_1$ and $X_2$, we have the following limits:
+	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
 
@@
 \end{theorem}
-Our result extends a well-known result on the inverse of sample covariance matrices.
-If $X_1$ is zero, then we obtain Fact \ref{lem_minv}(ii) as a special case.
+Our result extends a well-known result on the inverse of a sample covariance matrix.
+In particular, when $X_1$ is zero, we obtain Fact \ref{lem_minv}(ii) as a corollary.
 To see this, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to the variance limit.
-\HZ{go to intro}
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
-
-%As mentioned in the beginning of this section, different tasks may have different sample sizes and different feature covariance matrices.
-%Under these scenarios, Theorem \ref{thm_main_RMT} shows the bias and variance asymptotics for the two-task case.
 One can see that both the variance limit and the bias limit depend heavily on both tasks' samples sizes and the covariate shift matrix $M$.
-Next, we use our result to study how varying sample sizes and covariate shifts affects hard parameter sharing, respectively.
+Next, we illustrate how varying sample sizes and covariate shifts affects hard parameter sharing, respectively.
 

### 2020-10-08 arxiv/diff_cov.tex
section 4 polish

@@
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
-\begin{align}\label{def hatsig}
+\begin{align*}%\label{def hatsig}
 	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
-\end{align}
+\end{align*}
 The matrix $\hat{\Sigma}$ adds up both tasks' sample covariances, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
@@
 Hence, we consider the expected loss conditional on the covariates as follows:
-\begin{align}\label{eq_diff_cov}
+\begin{align}
 	\exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}} =
-	\bignorm{(\Sigma^{(2)})^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2
-	+ \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}.
+	& \bignorm{(\Sigma^{(2)})^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
+	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
 \end{align}
@@
 \begin{theorem}\label{thm_main_RMT}
-	Suppose that $X^{(1)}$ and $X^{(2)}$ are both random matrices that satisfy Assumption \ref{assume_rm}.
+	Suppose that $X^{(1)} \in \real^{n_1 \times p}$ and $X^{(2)} \in \real^{n_2 \times p}$ are both random matrices that satisfy Assumption \ref{assume_rm}.
 	Assume that: a) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$; b) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
@@
 
-	\noindent (i) The variance equation converges to the following asymptotic limit
+	\noindent (i) The variance equation \eqref{eq_variance_2task} satisfies the following limit
 			\begin{align}\label{lem_cov_shift_eq}
@@
 			\end{align}
-			where $a_1$ and $a_2$ are the solutions of the following two equations:
+			where $a_1$ and $a_2$ are the solutions of the following self-consistent equations
 			\begin{align}
@@
 			\end{align}
-	\noindent (ii) For any fixed vector $w\in\real^p$ with unit norm, the bias equation converges to the following asymptotic limit
+	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit for any fixed vector $w\in\real^p$ with unit norm,
 			\begin{align}\label{lem_cov_derv_eq}
@@
 			\end{align}
-				where $a_{3}$ and $a_4$ are the solutions of the following two equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
 			\begin{align}\label{eq_a34extra}
@@
 
-	In applying Theorem \ref{thm_main_RMT} to the above setting, we first solve the self-consistent equations \eqref{eq_a12extra} by using $\lambda_i = 1$ for all $1\le i\le p$.
-	This gives us the variance limit $\tr[(a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] / (n_1 + n_2) = \frac{p}{n_1 + n_2 - p}$, since we have that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$.
-	Secondly, we solve the self-consistent equations \eqref{eq_a34extra} given that we already know $a_1$ and $a_2$.
-	This gives us the bias limit.
-	Combined together, we obtain the following corollary, which requires natural assumptions over the random-effects model.
+	Applying Theorem \ref{thm_main_RMT} to the above setting, we first solve the self-consistent equations \eqref{eq_a12extra} by using $\lambda_i = 1$ for all $1\le i\le p$.
+	This gives us the variance limit
+	\[ \frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] = \frac{p}{(n_1 + n_2)(a_1 + a_2)} = \frac{p}{n_1 + n_2 - p}, \]
+	since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$.
+	Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} since we have obtained $a_1, a_2$.
+	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
+\end{example}
 
@@
 	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-	(i) task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
-	(ii) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
+	(i) both tasks sample sizes are at least $\frac{3}{2}p$;
+	(ii) noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
 %	\be\label{choiceofpara0}
@@
 %	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-	(iii) the task-specific variance of $\beta_i$ is much smaller than the shared signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$.
+	(iii) task-specific variance is much smaller than the shared signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$.
 	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
@@
 
-Our result shows that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance $d^2$ and a noise variance term that scales with $\sigma^2$.
-In the following, we explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
-Consider the prediction loss if we fix $n_2$ and increase $n_1$.
-We show that as a function of $n_1$, the limit equation always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
-We describe an informal proof.
-First, the noise variance term in Corollary \ref{cor_MTL_loss} always reduces as $n_1$ increases.
-Second, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
-Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the decrease in variance, and there is only one positive root for the derivative being zero.
+The above result provides a more concrete interpretation of the bias-variance decomposition, since the result depends explicitly on datasets' properties of interest.
+The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
+As a remark, by combining the bias and variance limits, we can also obtain a generalization bound for any local minimum of $f(A, B)$.
+The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
+
+Next, we illustrate an interesting phenomenon where adding task one's samples helps task two initially, but hurts eventually.
+Consider the limiting estimate in the left hand side of equation \eqref{cor_MTL_error}.
+We vary sample ratio $n_1 / n_2$ by fixing $n_2$ and increasing $n_1$.
+As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
+We describe a proof sketch.
+\begin{enumerate}
+	\item The variance term always reduces as $n_1$ increases.
+	\item The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
+	\item Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the decrease in variance, and there is only one positive root for the derivative being zero.
 %Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
@@
 %(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
+\end{enumerate}
 
@@
 %There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
-\end{example}
 
@@
 %In general, the covariance matrices of the two tasks may be different such as in text classification.
-Our second example studies the impact of varying covariate shifts on the variance limit.
+Our second example studies the impact of varying covariate shifts on variance in the left hand side of equation \eqref{lem_cov_shift_eq}:
+	\[ \bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} \rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
+\]
 %As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Recall that the matrix $M$ captures the geometry of covariate shifts.
-Suppose that half of the singular values of $M$ are equal to a parameter $\lambda > 0$ and the other half are equal to $\lambda^{-1}$.
-We observe the following dichotomy on the impact of covariate shifts.
+Hence the variance estimate is determined by the spectrum of $M$.
+
+To illustrate this result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
+Hence, when $\lambda = 1$, then there is no covariate shift.
+As $\lambda$ increases, the severity of covariate shift increases.
+We observe the following dichotomy.
 \begin{itemize}
-	\item If $n_1 \ge n_2$, then the variance (limit) of hard parameter sharing is smallest when $\lambda = 1$ or there is no covariate shift.
-	\item If $n_1 < n_2$, then having covariate shifts ($\lambda \neq 1$) always helps reduce variance (limit).
+	\item If $n_1 \ge n_2$, then the variance estimate is smallest when there is no covariate shift.
+	\item If $n_1 < n_2$, then the variance estimate is largest when there is no covariate shift.
 \end{itemize}
-To see this, we first write the variance limit for different values of $\lambda$ as follows
+\end{example}
+To see this, the variance estimate in this example is equal to
 \begin{align*}
-	\bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}
-	= \frac{1}{2}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
+	\frac{p}{2(n_1 + n_2)}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
 \end{align*}
-Denote the above function by $f(\lambda)$.
-We compare $f(\lambda)$ with $f(1)$, and observe that
-\[ 2f(\lambda) - 2f(1) = {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
-	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p}, \]
-where we used the first part of equation \eqref{lem_cov_shift_eq}.
-Next, one can verify that the above equation is equal to $(2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1)$, for a fixed and positive function $g(\lambda, a_1)$ (details omitted).
-Hence, whether or not $f(\lambda)$ is small than $f(1)$ is decided by $a_1$.
-To solve $a_1$, we present an informal argument that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
-Intuitively, with the current spectrum of $M$, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations.
-Hence, when $n_1 \ge n_2$, we expect that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
-Vice serva when $n_1 < n_2$.
-A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} by replacing half of the singular with $\lambda$ and the other half with $\lambda^{-1}$.
-We omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$; if $n_1< n_2$, then $f(\lambda)< f(1)$.
-\end{example}
+Denote the above function by $f(\lambda)$ without the scaling $\frac{p}{2(n_1 + n_2)}$.
+We compare $f(\lambda)$ to $f(1)$, and observe that
+\begin{align*}
+	f(\lambda) - f(1) &= {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
+	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
+	&= (2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1),
+\end{align*}
+where $g(\lambda, a_1) > 0$ is a fixed function.
+The first step uses equation \eqref{lem_cov_shift_eq} and the second step follows from algebraic calculation (details omitted).
+Hence, whether or not $f(\lambda)$ is small than $f(1)$ depends on $a_1$.
+
+We show that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
+In Example \ref{ex_covshift}, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations \eqref{lem_cov_shift_eq}.
+Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
+The other case is similar.
+A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
+Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
+If $n_1< n_2$, then $f(\lambda)< f(1)$.
 %\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
@@
 %The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-As a remark, by combining the bias and variance asymptotics, we can also obtain a generalization bound for any local minimum solutions $(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-%First, we rescale $X_1$ (and $\Sigma^{(1)}$) by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
-%Second, we approximate sample covariance ${X^{(1)}}^{\top}X^{(1)} / n_1$ by its expectation $\Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
-For the rest of this section, we present the main ideas for proving Theorem \ref{thm_main_RMT}.
+
 %Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
@@
 
-\paragraph{Proof overview.} The central quantify of interest is the matrix inverse $\hat{\Sigma}^{-1}$.
-To study this quantity, we use the Stieltjes transform or the resolvent method in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+\paragraph{Proof overview.}
+%First, we rescale $X_1$ (and $\Sigma^{(1)}$) by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
+%Second, we approximate sample covariance ${X^{(1)}}^{\top}X^{(1)} / n_1$ by its expectation $\Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
+For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
+The central quantify of interest is the inverse of the sample covariance matrices $\hat{\Sigma}^{-1}$.
+Our study of this quantity uses the Stieltjes transform or the resolvent method in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
 For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
@@
 Hence the Stieltjes transform method reduces the study of a probability measure to the study of a complex function.
-To study the matrix inverse $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
+To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
 More precisely, it suffices to study another matrix

### 2020-10-08 arxiv/proof_examples.tex
revise

@@
 \paragraph{Part $2$: reducing the random-effects model to Theorem \ref{thm_main_RMT}.}
-\HZ{restructure this part. merge the result of B.17 and B.18, and state it upfront. separate its proof into two parts}
-
-\HZ{just say that this calculation of B.97 is similar to B.81?}
+%\HZ{restructure this part. merge the result of B.17 and B.18, and state it upfront. separate its proof into two parts}
+%\HZ{just say that this calculation of B.97 is similar to B.81?}
 We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat x=\hat x_1/\hat x_2$:
@@
 %where we denoted $$\hat \Sigma:= \hat x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
-To illustrate the idea of bias-variance decomposition, we assume that $\hat x$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
+The main goal of this step is to prove the following two claims.  
+\begin{claim}
+In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
+%\be\label{choiceofpara}
+%	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
+%\ee
+%where $\e_0$ is the constant as appeared in equation \eqref{approxvalid}. Then we have
+\begin{align}
+&\left|L(\hat{\beta}_2^{\MTL}) - d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
+&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple1}
+\end{align}
+for any small constant $c>0$, where we recall that $\hat \Sigma=\hat \Sigma(1)$ as defined in \eqref{def hatsig}.
+\end{claim}
+\begin{proof}
+{\cor simplify} To illustrate the idea of bias-variance decomposition, we assume that $\hat x$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
 Then we can calculate the partial expectation of $L(\hat{\beta}_2^{\MTL})$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
@@
 &\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
-&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple1}
+&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple12}
 \end{align}
@@
 %w.h.p. for some constant $\e>0$.
+\end{proof}
 \end{proof}

### 2020-10-08 arxiv/diff_cov.tex
section 4 polish

@@
 One can see that both the variance limit and the bias limit depend heavily on both tasks' samples sizes and the covariate shift matrix $M$.
-Next, we illustrate how varying sample sizes and covariate shifts affects hard parameter sharing, respectively.
+Next, we illustrate how varying sample sizes and covariate shifts impact hard parameter sharing, respectively.
 
@@
 \end{example}
-To see this, the variance estimate in this example is equal to
+We explain why the dichotomy happens. The variance estimate for this example is equal to
 \begin{align*}
-	\frac{p}{2(n_1 + n_2)}\bigbrace{(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
+	\frac{p}{2(n_1 + n_2)} f(\lambda), \text{ where } f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
 \end{align*}
-Denote the above function by $f(\lambda)$ without the scaling $\frac{p}{2(n_1 + n_2)}$.
-We compare $f(\lambda)$ to $f(1)$, and observe that
+Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$, we have that
 \begin{align*}
@@
 	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-	&= (2a_1 - \frac{n_1 + n_2 - p} {n_1 + n_2}) g(\lambda, a_1),
+	&= (2a_1 - \frac{n_1 + n_2} {n_1 + n_2 - p}) g(\lambda, a_1),
 \end{align*}
-where $g(\lambda, a_1) > 0$ is a fixed function.
-The first step uses equation \eqref{lem_cov_shift_eq} and the second step follows from algebraic calculation (details omitted).
-Hence, whether or not $f(\lambda)$ is small than $f(1)$ depends on $a_1$.
+where $g(\lambda, a_1) > 0$ is a fixed function and can be derived from algebraic calculation (details omitted).
+%Hence, whether or not $f(\lambda)$ is small than $f(1)$ depends on $a_1$.
+We show that $a_1 \ge \frac{n_1 + n_2}{2(n_1 + n_2 - p)}$ if and only if $n_1 \ge n_2$, thus explaining the dichonomy.
 
-We show that $a_1 \ge \frac{(n_1 + n_2 - p)}{2(n_1 + n_2)}$ if and only if $n_1 \ge n_2$.
 In Example \ref{ex_covshift}, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations \eqref{lem_cov_shift_eq}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2})$.
-The other case is similar.
+Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
+The other case when $n_1 < n_2$ is similar.
 A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
@@
 
-\paragraph{Proof overview.}
-%First, we rescale $X_1$ (and $\Sigma^{(1)}$) by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
-%Second, we approximate sample covariance ${X^{(1)}}^{\top}X^{(1)} / n_1$ by its expectation $\Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
+\paragraph{Overview of Stieltjes transform.}
 For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
 The central quantify of interest is the inverse of the sample covariance matrices $\hat{\Sigma}^{-1}$.
-Our study of this quantity uses the Stieltjes transform or the resolvent method in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
+Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
+We briefly describe the key ideas and refer interested readers to classical texts such as  \citet{bai2009spectral,tao2012topics,erdos2017dynamical}.
 For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
 $$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \text{ for any complex number } z\in \C\setminus [0,\infty).$$
-%Conversely, given a Stieltjes transform $m_{\mu}(z)$, we can recover the measure $\mu$ through the inverse formula \HZ{add a ref to the equation below}
-%$$ \frac{\dd \mu(x)}{\dd x} = \frac{1}{\pi}\lim_{\eta \downarrow 0}\im m_{\mu}(x+\ii \eta).$$
-%where $\rho(x)$ is the density for $\mu$, i.e. $\dd \mu(x)=\rho(x)\dd x$.
 Hence the Stieltjes transform method reduces the study of a probability measure to the study of a complex function.
 To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
-More precisely, it suffices to study another matrix
+Let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$, where $\delta_{\lambda_i}$ is the indicator measure, and $Y$ is defined as follows
 \begin{align}\label{eigen2extra}
-	Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V), \text{ since } (n_1 + n_2)\hat{\Sigma}^{-1}= \Sigma_2^{-1/2} VY^{-1}V^\top \Sigma_2^{-1/2}.
+	Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
 \end{align}
-It is not hard to verify that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{Y^{-1}} / (n_1 + n_2)$.
-Let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$, where $\delta_{\lambda_i}$ is the indicator measure.
-%The scaling $(n_1+n_2)^{-1}$ ensures such that the support of $\mu$ is bounded.
+Recall that $\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix, ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrix with isotropic covariance.
+It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= \Sigma_2^{-1/2} VY^{-1}V^\top \Sigma_2^{-1/2}$ and $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{Y^{-1}} / (n_1 + n_2)$.
 The Stieltjes transform of $\mu$ is as follows
  \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(Y-z\id)^{-1}\right]. \]
-In the above equation, $(Y - z\id)^{-1}$ is known as the resolvent matrix or Green's function of $Y$.
+Above, $(Y - z\id)^{-1}$ is known as $Y$'s resolvent matrix or Green's function.
 %When $p$ goes to infinity, it is well-known that $m_{\mu}(z)$ converges to a fixed distribution governed by a set of self-consistent equations.
@@
 %Compared to the Stieltjes transform, the resolvent also applies to random matrices.
-We shall prove the convergence of the resolvent matrix of $Y$ using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
+We will prove the convergence of $Y$'s resolvent matrix using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
 %Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.
 \cite{Hachem2007deterministic,DS18}).
-More precisely, given a deterministic $p\times p$ matrix $R(z)$, we say that $R(z)$ and $(Y-z\id)^{-1}$ are equivalent if for any sequence of deterministic matrices $B$ with uniformly bounded operator norms,
+We say that $(Y-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic matrices $B$ with uniformly bounded operator norms, when $p$ is large enough
 $$\bigtr{((Y-z\id)^{-1}-R(z))B}\to 0.$$
-When the above equation holds for large enough $p$, we say that $(Y-z\id)^{-1}$ converges to the matrix limit $R(z)$.
 %For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
@@
 %which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
-We observe that the matrix $Y$ can also be written as $A A^{\top}$ for a $p$ by $n_1 + n_2$ matrix defined as follows.
+
+To study $Y$'s resolvent, we observe that $Y$ is equal to $A A^{\top}$ for a $p$ by $n_1 + n_2$ matrix
 	\[ A = (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
@@
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Consider the following symmetric and square matrix whose dimension is $p + n_1 + n_2$.
+Consider the following symmetric and square matrix whose dimension is $p + n_1 + n_2$
 %which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
@@
  \end{equation}
-The resolvent of $H$ is given by $G(z) \define (H - z\id)^{-1}$, for any complex value $z\in \mathbb C$.
-Since $H$ has a specific block structure, it is not hard to verify that
+We denote $G(z) \define (H - z\id)^{-1}$ as the resolvent of $H$, for any complex value $z\in \mathbb C$.
+Since $H$ has a block structure, it is not hard to verify that
 	\begin{equation*} %\label{green2}
@@
 
-\paragraph{Matrix limit.}
-In Theorem \ref{LEM_SMALL}, we show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to a matrix limit as follows:
+\paragraph{Variance asymptotic limit.}
+In Theorem \ref{LEM_SMALL}, we show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
 \be \label{defn_piw}
 	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix},\ee
-where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following system of equations
+where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
 \begin{align}
@@
 \end{align}
-The existence and uniqueness of the solution to the above equation system are shown in Lemma \ref{lem_mbehaviorw}.
+The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
 %First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
@@
 %\ee
-Given this result, we show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance asymptotic shown in equation \eqref{lem_cov_shift_eq}.
+Given this result, we show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
 First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
-Second, since $Y^{-1}$ is the upper-left block matrix of $G(0)$, we have that $Y^{-1}$ converges to $(a_1\Lambda^2 + a_2)^{-1}$.
-Using equation \eqref{eigen2extra}, we have that when $p$ goes to infinity, the trace of $\Sigma^{(2)} \hat{\Sigma}$ converges to
-\[ \bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} = \bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} = \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}. \]
+Second, since $Y^{-1}$ is the upper-left block matrix of $G(0)$, we have that $Y^{-1}$ converges to $(a_1\Lambda^2 + a_2\id)^{-1}$.
+Using equation \eqref{eigen2extra}, we have that when $p$ goes to infinity, % the trace of $$ converges to
+\[ \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} = \bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} = \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}. \]
 %\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
@@
 %\end{align}
-where we note that the SVD of $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ is equal to $V^{\top}\Lambda^2 V$.
+where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
 %For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
 
-For the bias asymptotic in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of the resolve of $Y$ with respect to $z$ at $z = 0$.
-More precisely, we have that
+\paragraph{Bias asymptotic limit.}
+For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(Y - z\id)^2$ with respect to $z$ at $z = 0$.
+First, we reduce the empirical bias term in equation \eqref{lem_cov_derv_eq} to $Y$
 \begin{align}\label{calculate G'}
@@
 Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} = - \cal G^2(z)$.
-Given the matrix limit of $\cal G(z)$ from equation \eqref{defn_piw} above, we have that the matrix limit of $\frac{\dd{\cal G(0)}}{\dd z}$ is given by
+Hence, provided that limit of $(Y - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
 \begin{align}\label{cal G'0}
-	\frac{\dd \cal G(z)}{\dd z} = \frac{-\frac{\dd a_1(z)}{\dd z}\Lambda^2 - (\frac{\dd a_2(z)}{\dd z} - 1)\id}{(a_{1}(z)\Lambda^2 + a_{2}(z)\id_p)^2}.
+	\frac{\dd \cal G(0)}{\dd z} = \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
 \end{align}
-As for the derivative of $a_1(z)$ and $a_2(z)$, we solve them by taking the derivative on both sides of the equation system \eqref{selfomega_a} with respect to $z$.
+For the derivative of $a_1(z)$ and $a_2(z)$, we take the derivative on both sides of equation \eqref{selfomega_a}.
 %\begin{align*}
@@
 %\end{align*}
-Let $a_3$ be the derivative of $-a_1(z)$ and $a_4$ be the derivative of $-a_2(z)$, both evaluated at $z = 0$.
+Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(z)}{\dd z}$.
 %then taking implicit differentiation of equation \eqref{selfomega_a}
-We have that $a_3$ and $a_4$ satisfy the equation system \eqref{eq_a34extra}.
-Applying equation \eqref{cal G'0} into equation \eqref{calculate G'}, we obtain that the asymptotic limit of the bias equation.
+One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations \eqref{eq_a34extra} (details omitted).
+Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain that the asymptotic limit of the bias term.
 %\begin{align}
@@
 %where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
-Note that for $\frac{\dd \cal G(z)}{\dd z}$ to be close to its limit at $z = 0$, we not only need the asymptotic limit of $\cal G(0)$, but also the asymptotic limit of $\cal G(z)$ for $z$ within a small neighborhood of $z = 0$.
-This is why consider the resolvent matrix of $Y$ as opposed to the Stieljes transform of its empirical spectral distribution.
 
-Next, we briefly describe how to derive the matrix limit $\Gi(z)$.
+As a remark, for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
+This is why we consider $Y$'s resolvent matrix as opposed to the Stieljes transform of its empirical spectral distribution.
+
+\paragraph{Schur complement and self-consistent equations.}
+We briefly describe how to derive the matrix limit $\Gi(z)$.
 First, we consider the case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
-By rotation invariance, we have that in the matrix $A$,  $Z^{(1)} U$ and $Z^{(2)} V$ are both multivariate Gaussian random matrices.
-We use Schur complement to obtain the entries of $G(z)$, and show that for the diagonal entries, they satisfy a set of self-consistent equations in the limit, which are stated above.
-On the other hand, for the off-diagonal entries, using standard concentration bounds, we show that they are approximately zero.
-Second, we extend our result for the Gaussian case to the more general case where the entries of $Z^{(1)}$ and $Z^{(2)}$ satisfy the bounded moment assumption.
-We prove an anisotropic local law using standard proof techniques in the random matrix literature \cite{erdos2017dynamical,Anisotropic}.
-The full proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{sec pf RMTlemma}.
+By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are both still multivariate Gaussian random matrices.
+Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
+We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equation \eqref{selfomega_a}.
+$G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
+Finally, we extend our result to general random matrices under the moment condition in Assumption \ref{assume_rm}.
+We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
+A complete proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{appendix RMT}.

### 2020-10-09 arxiv/diff_cov.tex
revise

@@
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
-\begin{align*}%\label{def hatsig}
+\begin{align}\label{def hatsig}
 	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
-\end{align*}
+\end{align}
 The matrix $\hat{\Sigma}$ adds up both tasks' sample covariances, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.

### 2020-10-09 arxiv/proof_examples.tex
revise

--- 2020-10-08 arxiv/proof_examples.tex
@@
 
-Using the concentration estimates in Lemma \ref{largedeviation}, we first show that $g(x)$ and its conditional expectation over $X^{(1)}, X^{(2)}$ are close.
+First, using the concentration estimates in Lemma \ref{largedeviation}, we show that $g(x)$ and its conditional expectation over $X^{(1)}, X^{(2)}$ are close.
 %$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
@@
  \end{proof}
+
+Next, bu studying the conditional expectation in \eqref{EgA}, we show that $\hat x$ is close to 1.
 
@@
 %where we denoted $$\hat \Sigma:= \hat x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
+Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as in the following claim.
+
+\begin{claim}
+In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
+%\be\label{choiceofpara}
+%	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
+%\ee
+%where $\e_0$ is the constant as appeared in equation \eqref{approxvalid}. Then we have
+\begin{align}
+&\left|L(\hat{\beta}_2^{\MTL}) - d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
+&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple1}
+\end{align}
+for any small constant $c>0$, where we recall that $\hat \Sigma=\hat \Sigma(1)$ was defined in \eqref{def hatsig}.
+\end{claim}
+\begin{proof}
+ \iffalse
  To illustrate the idea of bias-variance decomposition, we assume that $\hat x$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
@@
 In particular, our proof will not use Lemma \ref{lem_hat_v}.
-
+\fi
+Our proof is divided into two steps.
+First, with the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows.
+With high probability, we have that for any small constant $c>0$,
 %control the difference between $g(x)$ and its partial expectation. 
- \begin{claim}\label{claim_largedev2}
- In the setting of Proposition \ref{cor_MTL_loss}, if $\hat x=\OO(1)$, then we have that with high probability,
-$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),$$
-for any small constant $c>0$. Here we introduced the function
+% \begin{claim}\label{claim_largedev2}
+ %In the setting of Proposition \ref{cor_MTL_loss}, if $\hat x=\OO(1)$, then we have that 
+\be\label{claim_largedev2} \left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),
+\ee
+where the function $\cal L(\hat x)$ is defined as
 \begin{align*}
@@
 \end{align*}
- \end{claim}
- \begin{proof}
- The proof of this claim is very similar to the one for Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
-In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
-Here we only give an outline of the proof without writing down all the details.
-Recall that $\beta_0$ is the shared component of $\beta_1$ and $\beta_2$ with i.i.d.
-Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
-Moreover, we denote the task-specific components by $\wt\beta_1$ and $\wt\beta_2$, whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$.
-Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
- \begin{align}
-L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta_1 - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta_2 \right] \right.
-\nonumber\\
-&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
-\end{align}
-As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}.
-For example, for the main term $\hat x^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
-Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
-\begin{align*}
-&  \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1 - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
-&\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
-&\le p^{-1/2+c}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+c}d^2.
-\end{align*} 
-For the cross term $\hat x \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
-\begin{align*}
- \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
-&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
-&\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
-\end{align*}
-The rest of the terms in the expansion of \eqref{expand_15} can be bounded in the same way, and we omit the details.
- \end{proof}
-
-In the setting of Proposition \ref{cor_MTL_loss}, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
-
-\begin{claim}
-In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
+% \end{claim}
+We postpone the proof of equation \eqref{claim_largedev2} until we complete the proof of \eqref{simple1}.
+Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
+More precisely, we claim that with high probability,
+%\begin{claim}
+%In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
 %\be\label{choiceofpara}
@@
 &\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
-&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple1}
-\end{align}
-for any small constant $c>0$, where we recall that $\hat \Sigma=\hat \Sigma(1)$ as defined in \eqref{def hatsig}.
-\end{claim}
-\begin{proof}
-Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple12}
+\end{align}
+for any small constant $c>0$.
+Combining \eqref{claim_largedev2} and \eqref{simple12}, we immediately obtain \eqref{simple1}.
+%, where we recall that $\hat \Sigma=\hat \Sigma(1)$ as defined in \eqref{def hatsig}.
+%\end{claim}
+%\begin{proof}
+
+It remains to prove \eqref{simple12}. Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we obtain that with high probability,
 \begin{align}
@@
 \end{align*}
-Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple1}.
+Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple12}.
 % Inserting equation \eqref{hatv_add1} into equation \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$, we get that w.h.p.,
@@
 %w.h.p. for some constant $\e>0$.
+%\end{proof}
+\end{proof}
+Now we give the proof of the estimate \eqref{claim_largedev2}.
+ \begin{proof}[Proof of equation \eqref{claim_largedev2}]
+ The proof of this claim is very similar to the one for Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
+Here we only give an outline of the proof without writing down all the details.
+Recall that $\beta_0$ is the shared component of $\beta_1$ and $\beta_2$ with i.i.d.
+Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
+Moreover, we denote the task-specific components by $\wt\beta_1$ and $\wt\beta_2$, whose entries are i.i.d.
+Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$.
+Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
+ \begin{align}
+L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta_1 - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta_2 \right] \right.
+\nonumber\\
+&\left. + (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1}\left[ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2. \label{expand_15}
+\end{align}
+As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}.
+For example, for the main term $\hat x^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
+Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+\begin{align*}
+&  \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1 - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
+&\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
+&\le p^{-1/2+c}d^2 \cdot  \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|  \lesssim p^{-1/2+c}d^2.
+\end{align*} 
+For the cross term $\hat x \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+\begin{align*}
+ \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
+&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
+&\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
+\end{align*}
+The rest of the terms in the expansion of \eqref{expand_15} can be bounded in the same way, and we omit the details.
  \end{proof}

### 2020-10-09 arxiv/tools.tex
revise

@@
 The following lemma gives (almost) sharp concentration bounds for linear and quadratic forms of bounded supported random variables.
+Here we recall that the stochastic domination ``$\prec$" was defined in Definition \ref{stoch_domination}.
 %Besides the proof of Lemma \ref{prop_entry}, we also use it in several other places of this paper, including the proofs in Section \ref{sec_proof_general} and Section \ref{app_iso_cov}.
@@
 \end{align*}
-where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if all the moments of $\sqrt{n}x_i$ and $\sqrt{n}y_j$ exist in the sense of equation \eqref{assmAhigh2}, then we have stronger bounds
+where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if all the moments of $ x_i$ and $ y_j$ exist in the sense of equation \eqref{assmAhigh2}, then we have stronger bounds
 \begin{align}

### 2020-10-09 arxiv/experiments.tex
section 4 polish

@@
 	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
-	\caption{Validating Example \ref{ex_same_cov} in the same covariates case.
-Our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d$ and sample size $n$ settings.
-The noise variance $\sigma^2$ is $1/4$.}
+	\caption{Validating Example \ref{ex_same_cov} in the same covariates case: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d$ and sample size $n$ settings.
+The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
 	\label{fig_same_cov}
@@
 
-We show that our asymptotic estimates match extremely well with empirical prediction losses in modest dimensions.
-This study complements our high-dimensional asymptotic results whose error term vanishes when $p$ is sufficiently large.
-We simulate the settings of the three examples in Section \ref{sec_same} and \ref{sec_diff} in dimension $p = 200$.
+We demonstrate the accuracy of our results via some empirical results.
+While our theory is asymptotic (with error terms that vanish when $p$ is sufficiently large), we observe that they are accurate in a modest dimension of $p = 200$.
 
@@
 Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task sample from $400$ to $4000$.
-For all the parameter settings, we can estimate the empirical loss accurately using our results.
+For all the parameter settings, our results estimate the empirical losses accurately.
 We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
-Our result explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
+Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
 %Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
 Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, by looking horizontally at the same level of prediction loss, we observe that hard parameter sharing requires 3x less samples per-task than STL.
+Finally, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires 3x fewer samples per-task than STL.
 
 \paragraph{The different covariates case.}
-Second, we show how varying sample ratio affects hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
+Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
 Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-Again, our estimates are fairly accurate compared to the empirical losses.
-We consider a larger sample size regime here where task two consists of $70,000$ samples and task one's sample size varies from $10,000$ to $56,000$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases intially but increases above the initial loss level.
-Our result explains this trend since the task-specific variance $d^2 = 0.08$ is greater than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
+Again, our estimates are reasonably accurate compared to the empirical losses.
+We consider a regime where task two consists of $80,000$ samples, and task one's sample size vary from $8,000$ to $56,000$.
+We observe that as we increase the sample ratio, task two's prediction loss decreases initially but increases above the initial loss level.
+Our work explains this trend since the task-specific variance $d^2 = 0.08$ is higher than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
 %We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
 
-Finally, we show that varying covariate shift affects hard parameter sharing in the setting of Example \ref{ex_covshift}.
+Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}.
 Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shift -- a higher $\lambda$ means more covariate shift.
+Recall that $\lambda$ measures the severity of covariate shifts -- a higher $\lambda$ means more covariate shift.
 Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{figures/sample_ratio.eps}
+		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_c2_400.eps}
 		\caption{Example \ref{ex_sample_ratio}}
@@
 	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in the different covariates case.
-	In both experiments, our estimated loss (solid line) matches with the empirical loss (dotted line) accurately.
+	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in the different covariates case:
+	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
 	In Figure \ref{fig_size}, we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
-	We observe that task two's prediction loss decreases initially before increasing again, and our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
-	In Figure \ref{fig_covariate}, we show how covariate shift affects hard parameter sharing.
-We observe that when task two's sample size is greater than that of task one, covariate shift increases the prediction loss.
-Otherwise, covariate shift actually decreases the prediction loss (surprisingly).
-	.}
+	We observe that task two's prediction loss decreases initially before increasing again.
+Our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
+	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing.
+	Having covariate shifts increases task two's prediction loss when task two's sample size is larger than task one.
+Otherwise, having covariate shifts decreases task two's prediction loss (surprisingly).}
 	\label{fig_model_shift_phasetrans}
@@
 How well do they extend to other settings?
-In this section, we conduct further studies on a text classification task, for predicting whether the sentiment of a sentence is positive or negative.
-We use six datasets including a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, a opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
+In this section, we conduct further studies on a text classification task, for predicting whether  a sentence has a positive or negative sentiment.
+Our datasets include a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
 %The question is to predict positive or negative sentiment expressed in the text.
-We use an embedding layer with GloVe embeddings \cite{pennington2014glove} followed by an LSTM, MLP or CNN layer proposed by~\citet{lei2018simple}.\footnote{For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
+Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \citet{lei2018simple}.\footnote{For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
 For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings.}
@@
 \paragraph{Sample ratio.}
-In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
-On the $y$-axis, we plot task two's prediction accuracy using HPS, subtracted by its STL prediction accuracy.
+In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
+On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
 %validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task one's sample size as $1000$ and increase task two's number of samples from $100$ to $3000$.
-
-Next, we propose a natural progressive training schedule for finding the optimal sample ratio.
-Our training schedule is motivated by Corollary \ref{cor_MTL_loss}, which shows that as we increase the sample ratio, the prediction loss always decreases first and then increases.
+We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
+These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
 %In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
 %More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
+%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
+Concretely,
 \begin{itemize}
-	\item We divide the source task data into $S$ batches.
+	\item we divide the source task data into $S$ batches.
 	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
@@
 \end{itemize}
+For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
+The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
 
@@
 %Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-Our results show that progressive training requires less computation compared to a baseline round-robin training schedule, without sacrificing accuracy.
-First, we show that our proposed progressive training schedule (can help mitigate negative transfer for predicting a particular target task.
-Over all $15$ pairs from the sentiment analysis tasks, we find that progressive training requires only $45\%$ of the computational cost to achieve the same test accuracy on the target task, compared to HPS trained using round-robin.
-Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
+We evaluate the progressive training procedure on the six text classification datasets.
+First, we conduct multi-task training over all $15$ pairs from the six datasets.
+We find that adding task one's samples progressive requires only $45\%$ of the computational cost to achieve the same test accuracy for task two than standard round-robin training schedules.
+%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
 %\textbf{Improving transfer learning training efficiency.}
@@
 %Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we show the progressive training schedule applies to multiple tasks as well.
-Over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
+Second, we conduct multi-task training on all six datasets.
+We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than standard round-robin training schedules.
 %As a further validation, excluding TREC, we observe similar comparative results.
@@
 	\end{subfigure}
-	\caption{Comparing hard parameter sharing to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}.
+	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}:
 	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS. }
+	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
 	\label{fig_text}
@@
 \paragraph{Covariate shift.}
-Recall from Example \ref{ex_covshift} that when the sample ratio increases, covariate shift worsens.
-Hence when the sample ratio increases, we expect procedures that aim at correcting covariate shift to provide more significant gains.
-To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, which is designed for correcting covariate shift.
+Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
+This highlights the need for correcting covariate shifts when the sample ratio rises.
+To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, designed to correct covariate shifts.
 The idea is to add an alignment module between the input and the shared module $B$.
-This new module is then trained together with $B$ and the output layers -- more details on the procedure and the implementation can be found in that paper.
+This module is then trained together with $B$ and the output layers. We refer to \citet{WZR20} for more details about the procedure and the implementation.
 %We validate our insight on this procedure in the experiments.
@@
 
+We conduct multi-task training on all $15$ task pairs from the six datasets.
 In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-We average the results over all 15 task pairs.
-The result shows that as the source samples increases, covariance alignment improves more over HPS.
-We fix task two's sample size at $1,000$ and increase task one's sample size from $1,000$ to $3,000$.
+To get a robust comparison, we average the improvements over the 15 task pairs.
+The result shows that as the sample ratio increases, performing covariance alignment provides more significant gains over HPS.
+We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
 

### 2020-10-09 arxiv/conclusions.tex
wip
add conclusion

--- 2020-08-10 arxiv/conclusions.tex
@@
-\section{Conclusions and Open Problems}
+\section{Conclusions and Discussions}\label{sec_conclude}
 
-In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
-We provided tight concentration bounds for the bias and the variance.
-Based on these bounds, we analyzed the impact of three properties, including task similarity, sample size, and covariate shift on the bias and variance, to derive conditions for transfer.
-%Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
-We validated our theoretical results.
-Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed encouraging results inspired by our theory.
+This work proposed a formal study of a widely used hard paramaeter sharing approach in high-dimensional linear regression, where the sample size and feature dimension increase at a fixed ratio.
+We provided tight generalization bounds that scale with dataset properties such as their sample sizes and covariate shifts.
+Based on these bounds, we analyzed the impact of varying sample sizes and covariate shifts on the prediction loss of hard parameter sharing.
+Our work rigorously explains several empirical phenomena such as sample efficiency and negative transfer related to these dataset properties.
+We validated our results and conducted further studies on a real world classification task.
+
 We describe several open questions for future work.
-First, our bound on the bias term (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
-Tightening this error bound might cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
-Second, it would be interesting to extend our results to non-linear settings.
-We remark that this likely requires addressing significant technical challenges  to deal with non-linearity.
-
-\iffalse
-\newpage
-\section*{Broader Impacts}
-
-In this work, we provide a theoretical framework to help understand when multi-task learning performs well.
-We approach this question by studying the bias-variance tradeoff of multi-task learning.
-We provide new technical tools to analyze the bias and variance of multi-task learning.
-%We relate the bounds to three properties of task data.
-%Overall, our theoretical study provides a framework to help understand multi-task learning performance.
-%We further provide guidance for detecting and mitigating negative transfer on image and text classification tasks.
-
-Our theoretical framework has the potential to impact many other neighboring areas in the ML community.
-(i) Our concentration bounds can apply to different settings such as soft parameter sharing \cite{R17} , kernel methods \cite{EMP05}, and convex formulation of multi-task learning \cite{ZY14}.
-(ii) Our analysis of the bias-variance tradeoff can extend to transfer learning and domain adaptation \cite{K18}.
-(iii) Our insights on positive and negative transfer can be useful in multimodal learning, where the data sources are usually heterogeneous.
-(iv) Our fine-gained study on sample sizes have the potential to provide new insight in meta learning, where limited labeled samples presents a significant challenge.
-Finally, since multi-task learning connects to a wide range of areas \cite{V20} such as semi-supervised learning, representation learning, and reinforcement learning \cite{YKGLHF20}.%
-We believe that the tools we have developed and the framework we have provided can inspire followup works in these areas.
-
-Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their use cases of multi-task learning.
-For one example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
-Unlike the applications of multi-task learning in text classification where we can collect large amounts of labeled data \cite{GLUE}, in medical applications it is typically difficult and expensive to acquire labeled data.
-For such settings, our proposed training scheduler might improve the model training efficiency by using less labeled data.
-For another example, practitioners in industry often need to improve prediction performance by training many related tasks.
-But the results are not always positive and practitioners have a hard time figuring out why.
-Our proposed metric can provide guidance for selecting which tasks should be trained together in a multi-task model.
-\fi
-
-%Our algorithmic consequences of our theory have the potential to impact downstream applications of multi-task learning.
-%For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
-%Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult to acquire large amounts of labeled data.
-%For such settings, training multi-task models can be very challenging.
-%Our insight on using single-task learning results to help understand multi-task learning can be valuable for helping practitioners understand their results.
+First, our bound in Corollary \eqref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two random matrices $Z^{(1)}, Z^{(2)}$ with isotropic covariances.
+This might require new techniques beyond \HZ{to add}.
+Second, it would be interesting to extend our results to classification problems.
+Several recent work have made remarkable progress in the (one-sample) high-dimensional logistic regression setting \cite{sur2019modern}.
+An interesting question is to study hard parameter sharing in (multiple-sample) high-dimensional logistitic regression.

### 2020-10-09 arxiv/experiments.tex
add conclusion

@@
 
-We validate our  algorithmic insights and then our theory.
-In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
+%We validate our  algorithmic insights and then our theory.
+%In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
 %the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
-Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
+%Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
 %Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-In Section \ref{sec_exp_ab}, we validate our theoretical results.
-We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
+%In Section \ref{sec_exp_ab}, we validate our theoretical results.
+%We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
 
@@
 
-\subsection{Further Studies on a Text Classification Task}\label{sec_text}
+\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
 
 Our results and their implications are all in the high-dimensional linear regression setting.
-How well do they extend to other settings?
-In this section, we conduct further studies on a text classification task, for predicting whether  a sentence has a positive or negative sentiment.
+How well do they extend to other scenarios?
+In this section, we conduct further studies on six text classification datasets, for predicting whether a sentence has a positive or a negative sentiment.
 Our datasets include a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
 %The question is to predict positive or negative sentiment expressed in the text.
-Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \citet{lei2018simple}.\footnote{For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings.
-For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings.}
+Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
+For LSTM, we add a shared feature representation layer on top of word embeddings.}
 
@@
 We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
+These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops:
 %In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
@@
 %Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
-Concretely,
 \begin{itemize}
-	\item we divide the source task data into $S$ batches.
+	\item We divide the source task data into $S$ batches.
 	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.

### 2020-10-09 arxiv/intro.tex
section 3 4 polish writing
add conclusion

@@
 For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
-This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in a text classification task.
+This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
 %	Multi-task learning is a powerful approach in many applications such as image and text classification.
@@
 %We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
+
+\HZ{go to intro}
+For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
 \fi

### 2020-10-09 arxiv/proof_examples.tex
B.2 polish

@@
 
-We provide the proof of Corollary \ref{cor_MTL_loss}. The proof is similar to that of Theorem \ref{thm_many_tasks}.
-First, we reduce the optimization objective to another function $g(x)$ that only depends on the sample covariance matrices.
-Second, we show that the global minimizer of $g(x)$ is approximately equal to $1$.
-Finally, we use the above result and Theorem \ref{thm_main_RMT} to prove the proposition.
-
-In the setting of Corollary \ref{cor_MTL_loss}, the optimization objective \eqref{eq_mtl} is equal to
+We provide the proof of Corollary \ref{cor_MTL_loss}.
+We characterize the global minimizer of $f(A, B)$ in the random-effects model.
+Based on the characterization, we reduce the prediction loss of hard parameter sharing to the asymptotic limits provided in Theorem \ref{thm_main_RMT}.
+Then, we prove Corollary \ref{cor_MTL_loss} based on the bias and variance limits.
+We set up several notations.
+In the two-task case, the optimization objective $f(A, B)$ is equal to
 	\begin{align}
@@
 	\end{align}
-Let denote $\hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
+We denote $\hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
 Applying $\hat B$ to equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers.
@@
 \end{align*}
-Using this identity and taking expectation over $\epsilon^{(1)}$ and $\epsilon^{(2)}$, we can simplify \eqref{Eg(x)}  to
+Using this identity, we can simplify equation \eqref{Eg(x)}  to
 \begin{align*}
@@
 \end{align*}
-For the random-effects model, we take the expectation over $\beta_1$ and $\beta_2$:
+For the random-effects model, recall that the entries of $\beta_1, \beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $\kappa^2/p, d^2/p$, respectively.
+Hence,
 \begin{align}
@@
 \end{align}
-where we used that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$.
 
-\paragraph{Part $1$: approximating the global minimum.}
+\paragraph{Part $1$: characterizing the global minimum of $f(A, B)$.}
 Let $\hat{x}$ denote the minimizer of $g(x)$.
 We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat x$ is close to 1.
+This gives us the global minimum of $f(A, B)$, combined with the local optimality condition for $\hat{B}$.
 
-First, using the concentration estimates in Lemma \ref{largedeviation}, we show that $g(x)$ and its conditional expectation over $X^{(1)}, X^{(2)}$ are close.
-%$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}$.
+First, we show that $g(x)$ and $\ex{g(x) \mid X^{(1)}, X^{(2)}}$ are close using standard concentration bounds.
 \begin{claim}\label{claim_largedev1}
  In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
-$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right)$$.
+$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right).$$
 %for any small constant $c>0$.
-	% \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
  \end{claim}
@@
 
-Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, which conclude the proof of Claim \ref{claim_largedev1}.
+Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}.
+Hence the proof is complete.
  \end{proof}
 
-Next, bu studying the conditional expectation in \eqref{EgA}, we show that $\hat x$ is close to 1.
-
+Next, we show that $\hat x$ is close to 1.
 \begin{claim}\label{lem_hat_v}
@@
 
-\paragraph{Part $2$: reducing the random-effects model to Theorem \ref{thm_main_RMT}.}
-%\HZ{restructure this part. merge the result of B.17 and B.18, and state it upfront. separate its proof into two parts}
-%\HZ{just say that this calculation of B.97 is similar to B.81?}
-We provide the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat x=\hat x_1/\hat x_2$:
+\paragraph{Part $2$: a reduction to the bias and variance limits.}
+Recall that the hard parameter sharing estimator $\hat{\beta}_2^{\MTL}$ is equal to $\hat{B} \hat{A}_2$.
+The predication loss of hard parameter sharing is as follows
 \begin{align}
-L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat x_2 - \beta_2\right)\right\| \nonumber\\
+L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right\| \nonumber\\
 &=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta_1-\hat x^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
 \end{align}
-%where we denoted $$\hat \Sigma:= \hat x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
 Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as in the following claim.
 
-\begin{claim}
-In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-%\be\label{choiceofpara}
-%	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
-%\ee
-%where $\e_0$ is the constant as appeared in equation \eqref{approxvalid}. Then we have
-\begin{align}
-&\left|L(\hat{\beta}_2^{\MTL}) - d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
-&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple1}
-\end{align}
-for any small constant $c>0$, where we recall that $\hat \Sigma=\hat \Sigma(1)$ was defined in \eqref{def hatsig}.
+\begin{claim}\label{claim_reduction}
+Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. Section \ref{sec_diff}).
+In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability
+\begin{align*}
+&\left|L(\hat{\beta}_2^{\MTL}) - d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{{\hat \Sigma^{-1}  }}\right| \nonumber\\
+\lesssim&  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2).
+\end{align*}
 \end{claim}
 \begin{proof}
- \iffalse
- To illustrate the idea of bias-variance decomposition, we assume that $\hat x$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now.
-Then we can calculate the partial expectation of $L(\hat{\beta}_2^{\MTL})$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
- \begin{align}
-	\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2,\beta_1,\beta_2}  &=  \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} (\hat x \beta_1 - \hat x^2\beta_2)}^2 \nonumber\\ %\label{eq_bias_2task}
-			& + \sigma^2\cdot \bigtr{ X^{(2)} \hat\Sigma(\hat x)^{-1}\Sigma^{(2)}\hat\Sigma(\hat x)^{-1} (X^{(2)})^\top} \nonumber\\
-			&+ \sigma^2\cdot \hat x^2 \bigtr{ X^{(1)} \hat\Sigma(\hat x)^{-1}\Sigma^{(2)}\hat\Sigma(\hat x)^{-1} (X^{(1)})^\top}\nonumber\\
-			%+\sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } \nonumber\\ 
-			&= \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} (\hat x \beta_1 - \hat x^2\beta_2)}^2 +\sigma^2  \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).\nonumber
-			%\label{eq_var_2task}
-\end{align}
-This gives a bias-variance decomposition of the MTL prediction loss: the first term on the right-hand side is the bias term, while the second term is the variance term.
-For the random-effects model, we further take the partial expectation over $\beta_1$ and $\beta_2$:
- \begin{align}
-	& \exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2} \nonumber\\
-	&	=  \hat x^2 \left[(\hat x-1)^2 \kappa^2 + \frac{(\hat x^2+1)d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} }\nonumber \\
-	&+\sigma^2 \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
-			\label{eq_var_2task}
-\end{align}
-One can compare the above expression with the predication loss for STL, that is,
-\begin{align}
-	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma^{(2)} (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
-\end{align}
-we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over the second term on the right-hand side of equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
-In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
-Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!
-
-%Plugging $Y^{(1)}$ and $Y^{(2)}$ in equation \eqref{model_YvsX} into equation \eqref{eq_Bhat_2task}, we can rewrite that 
-% \begin{align}
-%		\hat{B}= \frac{1}{A_2}\left[\beta_2 + \left(\frac{A_1^2}{A_2^2}(X^{(1)})^{\top}X^{(1)} +  (X^{(2)})^{\top}X^{(2)}\right)^{-1}\bigbrace{ (X^{(1)})^{\top}X_1\left(\frac{A_1}{A_2}\beta_1 - \frac{A_1^2}{A_2^2} \beta_2\right) + \left(\frac{A_1}{A_2} (X^{(1)})^{\top}\varepsilon_1 + (X^{(2)})^{\top}\varepsilon_2\right)}\right].
-\label{eq_Bhat_2task2} %\\
-%		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-%	\end{align}
-
-In general, for $\hat x$ as  the minimizer of $g(x)$, it depends on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
-However, using the concentration estimates in Lemma \ref{largedeviation}, we can still obtain the expression in equation \eqref{eq_var_2task} up to a small error.
-In particular, our proof will not use Lemma \ref{lem_hat_v}.
-\fi
 Our proof is divided into two steps.
@@
 With high probability, we have that for any small constant $c>0$,
-%control the difference between $g(x)$ and its partial expectation. 
-% \begin{claim}\label{claim_largedev2}
- %In the setting of Proposition \ref{cor_MTL_loss}, if $\hat x=\OO(1)$, then we have that 
 \be\label{claim_largedev2} \left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),
@@
 % \end{claim}
-We postpone the proof of equation \eqref{claim_largedev2} until we complete the proof of \eqref{simple1}.
+We are ready to finish the proof of Claim \ref{claim_reduction}.
+We defer the proof of equation \eqref{claim_largedev2} until the end.
 Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
-More precisely, we claim that with high probability,
-%\begin{claim}
-%In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
-%\be\label{choiceofpara}
-%	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
-%\ee
-%where $\e_0$ is the constant as appeared in equation \eqref{approxvalid}. Then we have
+More precisely, we claim that with high probability
 \begin{align}
-&\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
-&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) , \label{simple12}
+&\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\hat \Sigma^{-1}  }\right| \nonumber\\
+&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
 \end{align}
-for any small constant $c>0$.
-Combining \eqref{claim_largedev2} and \eqref{simple12}, we immediately obtain \eqref{simple1}.
-%, where we recall that $\hat \Sigma=\hat \Sigma(1)$ as defined in \eqref{def hatsig}.
-%\end{claim}
-%\begin{proof}
+Combining \eqref{claim_largedev2} and \eqref{simple12}, we obtain Claim \ref{claim_reduction}.
 
-It remains to prove \eqref{simple12}. Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we obtain that with high probability,
+It remains to prove equation \eqref{simple12}. Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we obtain that with high probability,
 \begin{align}
- \|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1|\|\hat\Sigma^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right),\label{est111}
+ \|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1|\|\hat\Sigma^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right).\label{est111}
 \end{align}
-for any small constant $c>0$. With similar arguments, we can get that with high probability,
+Using similar arguments, we get that with high probability,
 \begin{align}\label{est222}
@@
 \end{align}
-Now we bound the left-hand side of \eqref{simple1} as % \HZ{replace $\Sigma(1)$ with $\hat{\Sigma}$ throughout}
+Now we bound the left hand side of equation \eqref{simple12} as
 \begin{align*}
@@
 Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple12}.
-% Inserting equation \eqref{hatv_add1} into equation \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$, we get that w.h.p.,
-%\begin{align}
-%\te(\hat{\beta}_2^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\
-%&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
-%\end{align}
-%In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order.
-Using Fact equation \eqref{lem_minv}, we have that
-%$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim 1.$$
-%Hence we need to choose that $p d^2 \sim \sigma^2$.
-On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$.
-The above considerations lead to the choices of parameters in equation \eqref{choiceofpara}, under which we can simplify equation \eqref{1Liso} to equation \eqref{simple1}.
-%\begin{align}
-%\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
-%&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
-%\end{align}
-%w.h.p. for some constant $\e>0$.
-%\end{proof}
-\end{proof}
+
 Now we give the proof of the estimate \eqref{claim_largedev2}.
- \begin{proof}[Proof of equation \eqref{claim_largedev2}]
- The proof of this claim is very similar to the one for Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
 In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
-Here we only give an outline of the proof without writing down all the details.
+Here we only give a proof sketch and omit the details.
 Recall that $\beta_0$ is the shared component of $\beta_1$ and $\beta_2$ with i.i.d.
@@
 For example, for the main term $\hat x^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
-Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+Lemma \ref{largedeviation} and equation \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability:
 \begin{align*}
@@
 
-\paragraph{Part $3$: Applying Theorem \ref{thm_main_RMT}.}
+\paragraph{Part $3$: applying the bias and variance limits.}
 Finally, we are ready to complete the proof of Corollary \ref{cor_MTL_loss}.
-We derive the variance term $\sigma^2  \tr(\hat\Sigma^{-1})$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
-%For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
-%\begin{lemma}\label{prop_model_shift_tight}
-%		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
-%		$\beta_2$ is a random vector that has i.i.d.
-entries with mean $0$, variance $\kappa^2$ and finite moments up to any order, and $(\beta_1-\beta_2)$ is a random vector that is independent of $\beta_2$ and has i.i.d.
-entries with mean $0$, variance $d^2$ and finite moments up to any order.
-Denote
-%		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in equation \eqref{defnpihat}.	Then we have with high probability,
-%		\begin{align*}
-%			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
-%			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
-%		\end{align*}
-%		where $\Delta_{\vari}$ was defined in equation \eqref{Deltavarv}.
-%\end{lemma}
+We derive the variance term $\sigma^2  \tr[\hat\Sigma^{-1}]$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
 
 \begin{proof}[Proof of Corollary \ref{cor_MTL_loss}]
-%The proof of Lemma \ref{prop_model_shift_tight} is similar to that for Lemma \ref{thm_model_shift}, except that we can replace equation \eqref{bounddelta-} with a tighter bound.
-We only describe the main difference in the following proof.
-%For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d.
-entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$.
-Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$,
-%\begin{align}
-%&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-%&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
-%&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2] \quad \text{w.h.p.},\label{anotherbeta}
-%\end{align}
-%where $\delta_{\bias}(v)$ was defined in equation \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by Fact \ref{lem_minv}.
-Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
-%\begin{align*}
-%v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
-%\end{align*}
-%Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ 
 Using \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr(\hat\Sigma^{-1}) = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1\id_p+a_2\id_p)^{-1}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
+\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1\id_p+a_2\id_p)^{-1}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
 with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
@@
 			\end{align}
-Inserting it into \eqref{eq_var111}, we obtain that 
-\be\label{eq_var112}\tr(\hat\Sigma^{-1})  = \frac{p}{n_1+n_2} \cdot \frac{\rho_1+\rho_2}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})=  \frac{1}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})\ee
+Applying the above to equation \eqref{eq_var111}, we obtain that
+\be\label{eq_var112}\bigtr{\hat\Sigma^{-1}}  = \frac{p}{n_1+n_2} \cdot \frac{\rho_1+\rho_2}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})=  \frac{1}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})\ee
 with high probability.
@@
 with high probability. Solving equation \eqref{eq_a34extra} with $a_1, a_2$ in \eqref{simplesovlea12} and $\lambda_i\equiv 1$, $1\le i\le p$, we can obtain that
-	\begin{align}
+	\begin{align*}
 		% a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad & a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
 		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
-		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
-	\end{align}
+		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}. %\label{simplesovlea34}
+	\end{align*}
 Inserting them into \eqref{eq_bias112}, we obtain that 
@@
 with high probability. Inserting \eqref{eq_bias113} into \eqref{eq_bias111}, we get that
-\begin{align}
+\begin{align*}
 		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\nonumber \\
-&\le  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} \nonumber\\
-&  \le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\label{eq_bias114}
-\end{align}
+		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} \nonumber\\
+		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}
+\end{align*}
 with high probability.
 
-Now plugging \eqref{eq_var112} and \eqref{eq_bias114} into \eqref{simple1}, we get
-\begin{align}
+Combining equation \eqref{eq_var112} and the above with Claim \ref{claim_reduction}, we get that
+\begin{align*}
 	\left|\cal L(\hat x)- \frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right| \le   \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \nonumber\\
-+C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right) \label{simple1add}
-\end{align}
-with high probability for some constant $C>0$.
-Then using Claim \ref{claim_largedev2} and the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$, we conclude \eqref{cor_MTL_error} by noticing that the constant $c>0$ can be arbitrarily small.
-%, we conclude \eqref{cor_MTL_error}
++C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
+\end{align*}
+Then using Claim \ref{claim_largedev2} and the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$, we conclude the proof.
 \end{proof}
-%\begin{align}
-%				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
-%				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_1 a_4 - a_2 a_3)}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
-%%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%%				= b_0.
-%			\end{align}
-%\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
-%where
-%$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
-%Note that $\delta^\star_{\bias}(v) \sim p$ by Fact \ref{lem_minv}. Hence combining equation \eqref{anotherbeta} and equation \eqref{anotherwtbeta} we get
-%\be\label{replaceest}
-%  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
-%\ee
-%Now we can replace the estimate equation \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}.
-In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term.
-
-%In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
-Then solving equations equation \eqref{eq_a12extra} and equation \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
-%	\begin{align}
-%		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
-%		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
-%		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
-%		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
-%	\end{align}
-%	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
-%\be\label{Deltavar}
-%\begin{split}
-%\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
-%\end{split}
-%\ee
-%with high probability, where 
-%	\begin{align*}
-%		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
-%	\end{align*}
-%	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
-%	Next for the model shift bias
-%	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
-%	we can get from Lemma \ref{prop_model_shift_tight} that
-%\be\label{Deltabeta} 
-%\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
-%	where 
-%	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$
-
-\iffalse
-
-\subsection{Covariate Shift}\label{app_proof_33}
-
-Finally, we prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}_2^{\MTL})$ is minimized approximately when $M$ is a scalar matrix, provided that there is enough source data.
-
-%\begin{proof}[Proof of Claim \ref{claim_covar_shift}]	
-%	With the same arguments as in Claim \ref{lem_hat_v}, we can show that equation \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in equation \eqref{choiceofpara}, we can simplify $g(M_0)$ as
-%\be \nonumber
-%\begin{split}
-%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
-%\end{split}
-%\ee
-% for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-% \end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-Denote the minimizer of $g$ by 
-$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
-We now calculate $g(M_0)$.
-With the same arguments as in Claim \ref{lem_hat_v}, we can show that equation \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in equation \eqref{choiceofpara}, we can simplify $g(M_0)$ as
-\be \nonumber
-\begin{split}
-g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \quad \text{w.h.p.}
-\end{split}
-\ee
- for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-
-Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-\begin{align}\label{gvar_extra}
-g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-\end{align}
-From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
-\frac{\rho_1-1}{\rho_1+\rho_2} < a_1(M)<  \frac{\rho_1+\rho_2-1}{\rho_1+\rho_2},\quad a_2(M) < \frac{\rho_2}{\rho_1+\rho_2}.
-\ee
-Inserting equation \eqref{est_a12extra} into equation \eqref{gvar_extra} and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-\begin{align}\label{approximateteM}
-\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-\end{align}
-where
-$$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
-%With these two bounds, we can easily conclude equation \eqref{approxteM}. 
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying equation \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that 
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
-\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-\begin{align}\label{gvar_extra2}
-\begin{split}
-g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-\end{split}
-\end{align}
-Combining equation \eqref{est_a12extra}, equation \eqref{approximateteM}, equation \eqref{AMGM} and equation \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-\end{proof}
- \fi
-
-\iffalse
-In the simulation of Figure \ref{fig_covariate}, we observe the following two phases as  $n_1 / p$ increases.
-When $n_1 \le n_2$, having complementary covariance matrices leads to lower test error compared to the case when $\Sigma_1 = \Sigma_2$.
-When $n_1 > n_2$, having complementary covariance matrices leads to higher test error compared to the case when $\Sigma_1 = \Sigma_2$.
-We provide a theoretical justification now.
-
-\begin{proof}[Theoretical justification of Example \ref{ex_complement}]
-We denote the test error as $\te(\hat \beta_{2}^{\MTL},\lambda)$ in the setting where $M$ has $p/2$ singular values that are equal to $\lambda$ and $p/2$ singular values that are equal to $1 / \lambda$.
-Then equations in equation \eqref{eq_a12extra} become
-\be\label{compleeq} a_1 + a_2 = 1 - \frac{1}{\rho_1 + \rho_2},  \ \ a_1 + \frac{1}{2(\rho_1 + \rho_2)}\cdot \bigbrace{\frac{a_1}{a_1 + \lambda^2 a_2} + \frac{a_1}{a_1 + \lambda^{-2} a_2}} = \frac{\rho_1}{\rho_1 + \rho_2}.
-\ee
-%It's not hard to verify that there is only one valid solution $(a_1,a_2)$ to equation \eqref{compleeq}. 
-After solving these, with equation \eqref{gvar_extra} we get that w.h.p.,
-\be\label{testcomple}
- \te(\hat \beta_{2}^{\MTL},\lambda)= \frac{\sigma^2}{2(\rho_1 + \rho_2)}(1+\OO(p^{-\e}))\cdot f(\lambda) ,\quad f(\lambda): = \frac{1}{\lambda^{-2}{a_1} + a_2} + \frac{1}{\lambda^2a_1 + a_2}.\ee
-
-%First we notice that the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
-In fact, if $n_1=n_2$, then it is easy to observe that $a_1=a_2=(1-\gamma)/2$ is the solution to equation \eqref{compleeq}, where we denote $ \gamma=p/(n_1+n_2)$.
-Then for any $\lambda$, the test error in equation \eqref{testcomple} takes the value
-%$$te(\lambda)= \frac{\gamma}{2}\frac{1}{(1-\gamma)/2}=\frac{p}{n_1+n_2-p}.$$
-
-%Second, from Figure \ref{fig_te_complement} we observe that the complementary cases with $\lambda>1$ is better than the case without covariate shift (i.e.
-$M=\id$ case) when $n_1<n_2$.
-On the other hand, if we have enough source task data such that $n_1>n_2$, then it is always better to have no covariate shift.
-We now study the behavior of $f$ as $\lambda$ changes. 
-%This phenomenon can be also explained using our theory. 
-We abbreviate $\gamma:=(\rho_1 + \rho_2)^{-1}$. Then with equation \eqref{compleeq}, we can rewrite
-$$f(\lambda)= \frac{1}{\lambda^{-2}{a_1} + (1-\gamma - a_1)} + \frac{1}{\lambda^2a_1 + (1-\gamma - a_1)}.$$
-Then we can compute that
-\begin{align*}
-f(\lambda) - f(1)&= \frac{ \lambda^2-1}{1-\gamma} a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{(\lambda^2-1)^2}{1-\gamma}  a_1\cdot  \frac{2a_1 - (1-\gamma) }{[-a_1(\lambda^2-1)+(1-\gamma)\lambda^2 ][a_1(\lambda^2-1) + (1-\gamma)]} .
-\end{align*}
-From this expressions, we observe the following behaviors.
-\begin{itemize}
-\item[(i)] If $n_1>n_2$, we have $a_1>(1-\gamma)/2$ (because $a_1>a_2$ as observed from the equation \eqref{compleeq}).
-Hence $f(\lambda)>f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)>\te(\hat \beta_{2}^{\MTL},1)$.
-
-\item[(ii)] If $n_1< n_2$, we have $a_1< (1-\gamma)/2$. Hence $f(\lambda)< f(1)$, which gives $\te(\hat \beta_{2}^{\MTL},\lambda)<\te(\hat \beta_{2}^{\MTL},1)$.
-
-\item[(iii)] If $n_1=n_2$, we have $f(\lambda)=f(1)=2/(1-\gamma)$, which means $\te(\hat \beta_{2}^{\MTL},\lambda)$ and $\te(\hat \beta_{2}^{\MTL},1)$ are roughly the same.
-%, which explains why the curves in Figure  \ref{fig_model_shift_phasetrans} (c) all cross at the point $n_1=n_2$.
-\end{itemize}
-This also partially justifies Proposition \ref{prop_covariate}. %Theorem  the observations in Figure \ref{fig_model_shift_phasetrans} (c), 
-\end{proof}
-\fi
-
-\iffalse
-\subsection{Task Similarity}\label{app_proof_31}
-
-With equation \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level.
-%With slight abuse of notations, we shall write $\hat x_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.
-
-\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
-	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$.
-Then solving equations equation \eqref{eq_a12extra} and equation \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
-	\begin{align}
-		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
-		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
-		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
-	\end{align}
-	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
-\be\label{Deltavar}
-\begin{split}
-\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
-\end{split}
-\ee
-with high probability, where 
-	\begin{align*}
-		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
-	\end{align*}
-	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
-	Next for the model shift bias
-	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
-	we can get from Lemma \ref{prop_model_shift_tight} that
-\be\label{Deltabeta} 
-\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
-	where 
-	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
-%\begin{align*}
-%		\Delta_{\bias} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
-%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
-%	\end{align*}
-%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\bias}$ as
-%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\bias} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4.
-\ee
-%	Hence we obtain that
-%	\begin{align*}
-%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
-%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
-%	\end{align*}
-Note that by equation \eqref{simple1}, we have
- \be\label{var-beta}\te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} .\ee
-Then we can track its sign using equation \eqref{Deltavar} and equation \eqref{Deltabeta}.
-
-\vspace{5pt}
-
-\noindent{\bf Positive transfer.} With equation \eqref{Deltavar} and equation \eqref{Deltabeta}, we conclude that if
-\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-then $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify equation \eqref{upper101} to
-	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
-Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$ and $\nu\ge \al_+^2(\rho_1) +  \oo(1) $, it gives the first statement of Proposition \ref{prop_dist_transition}.
-
- \vspace{5pt}
-
-\noindent{\bf Negative transfer.} On the other hand, if
-\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
-	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify equation \eqref{upper102} to
-	\be\label{neg1} \frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
-which gives the second statement of Proposition \ref{prop_dist_transition}.
-\end{proof}
-
-\subsection{Sample Ratio} \label{app_proof_32}
-We first prove Proposition \ref{prop_data_size}, which describes the effect of source/task data ratio on the information transfer.
-
-\begin{proof}[Proof of Proposition \ref{prop_data_size}]
-Following the proof of Proposition \ref{prop_dist_transition}, we know that $\te(\hat{\beta}_2^{\MTL})< \te(\hat{\beta}_2^{\STL})$ w.h.p.
-if equation \eqref{pos1} holds, while $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$ w.h.p.
-if equation \eqref{neg1} holds.
-%\be\label{pos1}
-%pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^4 <  \sigma^2  \bigbrace{1 - \oo(1)},\ee
-%and we get from equation \eqref{upper102} that $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$ w.h.p. if
-%\be\label{neg1}pd^2  \cdot \frac{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}{(\rho_1 + \rho_2 - 1)^2}\bigbrace{1 - \sqrt{\frac{1}{\rho_1}}}^4 >  \sigma^2  \bigbrace{1 + \oo(1)}.\ee
-%then we have $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ w.h.p..
-
-We first explain the meaning of the condition 
-\be\label{explainpsi}\Psi(\beta_1,\beta_2)>2/(\rho_2-1).\ee 
-%For the first statement of Proposition \ref{prop_data_size}, we 
-Notice that the function
-$$ \Phi(\rho_1, \rho_2)=\frac{(\rho_1 + \rho_2 - 1)^2}{\rho_1 (\rho_1 + \rho_2) (\rho_2 - 1)}=\frac{1}{\rho_2-1} \left(1 +\frac{\rho_2-2}{\rho_1}+\frac{1}{\rho_1(\rho_1+\rho_2)}\right)$$
-is strictly decreasing with respect to $\rho_1$ as long as $\rho_2> 2$, and $ \Phi(\rho_1, \rho_2)$ converges to $(\rho_2-1)^{-1}$ as $\rho_1\to \infty$.
-Since $\left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} < 2$ for $\rho_1>40$,  equation \eqref{explainpsi} implies that equation \eqref{neg1} holds for large enough $\rho_1$.
-Moreover, the transition from positive transfer when $\rho_1$ is small to negative transfer when $\rho_1$ is large is described by the two bounds in Proposition \ref{prop_data_size}, which we will show now.
-% $$ \Psi(\beta_1,\beta_2) \ge \bigbrace{1 + \sqrt{\frac{1}{\rho_1}}}^{-4}\frac{\sigma^2}{\rho_2-1}\left(1 -\oo(1)\right),$$ 
-% then equation \eqref{pos1} holds, which shows that  $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ holds w.h.p..
-Plugging into $\rho_1>50$, we obtain the first statement.
-......
-Note that for $\rho_1>40$, we have
-%$\gamma_+^{-1}$
-%The two bounds follows directly from equation \eqref{pos1} and equation \eqref{neg1}. 
-In the following proof, we will use the following trivial inequalities 
-\be\label{trivialphi}
-\frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\cdot \left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) \le  \frac1{\Phi(\rho_1, \rho_2)} \le  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}.
-\ee
-
-%This shows that equation \eqref{neg1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})> \te(\hat{\beta}_t^{\STL})$ holds. 
-%
-%If $c_1 > \frac{(c_2-2) \sigma^2}{(1-a^{-1/2})^4(1-(a+c_2-2)^{-2})(c_2 - 1) pd^2 - \sigma^2}$, we have
-%Suppose that
-%$$pd^2 > (1 - a^{-1/2})^{-4}\frac{\sigma^2}{c_2-1}.$$
-
-\noindent{\bf Positive transfer.} With equation \eqref{trivialphi}, we see that equation \eqref{pos1} is implied by the following inequality:
-\begin{align}\label{pos1solv}
- &  \Psi(\beta_1,\beta_2) \cdot \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}   < \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1} .
- \end{align}
- Then we can solve equation \eqref{pos1solv} to get
- \be\label{addconstraint}\rho_1 < \frac{\rho_2-2}{\Psi(\beta_1,\beta_2) \cdot (\rho_2 - 1)\left( \al_+^2(\rho_1) +  \oo(1) \right) - 1}  .\ee
- %$$\rho_1 > \frac{(\rho_2-2) \sigma^2}{(1 - {\rho_1}^{-0.5})^4 (\rho_2 - 3) pd^2 - \sigma^2}$$
- This gives the first statement of Proposition \ref{prop_data_size} using $\nu\ge \al_+^2(\rho_1) +  \oo(1) $.
-%Plugging into $\rho_1>40$ and $\rho_2>500$, we conclude the upper bound for $\rho_1$ in order for positive transfer to hold.
-
- Note that if we require the RHS of equation \eqref{addconstraint} to be larger than $40$, that is, equation \eqref{addconstraint} is not a null condition, then with equation \eqref{explainpsi} we get
- $$ \rho_2 - 2>\left[ 2\left( \al_+^2(\rho_1) +  \oo(1) \right)  -1\right]\rho_1 .$$
-Plugging into $\rho_1>40$, we get $\rho_2 \ge 106$. This gives a constraint on $\rho_2$.
-
-%On the other hand, if $c_1 < \frac{(c_2-2)\sigma^2}{(1+a^{-1/2})^4(c_2 - 1) pd^2 - \sigma^2}$, then we have 
-% \begin{align*}
-% pd^2 \cdot \frac{c_1(c_1+c_2)(c_2-1)}{(c_1+c_2-1)^2}  \cdot \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 < \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4 \cdot \frac{pd^2(c_2-1) c_1 }{c_1+(c_2-2)}  < \sigma^2\cdot (1-\oo(1)).
-% \end{align*}
-% This shows that equation \eqref{pos1} holds as long as $p$ is large enough, and hence $\te(\hat{\beta}_t^{\MTL})< \te(\hat{\beta}_t^{\STL})$ holds.
-
-\vspace{5pt}
-
- \noindent{\bf Negative transfer.} 
-With equation \eqref{trivialphi}, we see that equation \eqref{neg1} is implied by the following inequality:
-\begin{align}\label{neg1solv}
- & \Psi(\beta_1,\beta_2)  \frac{(\rho_2-1) \rho_1 }{\rho_1+\rho_2-2}\left( 1-\frac{1}{(\rho_1+\rho_2-2)^2}\right) >  \Psi(\beta_1,\beta_2) \frac{(\rho_2-1.5) \rho_1 }{\rho_1+\rho_2-2}> \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1} .
- \end{align}
- where we used $(1-(\rho_1+\rho_2-2)^{-2})(\rho_2 - 1) > \rho_2-1.5$ for $\rho_1>40$ and $\rho_2>110$. Then we can solve equation \eqref{neg1solv} to get that
- \be\label{addconstaint2}
- \rho_1 > \frac{\rho_2-2 }{\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)  - 1}  ,
- \ee
-which gives the second statement of Proposition \ref{prop_data_size}.
-We remark that condition equation \eqref{explainpsi} implies $\Psi(\beta_1, \beta_2) \cdot  (\rho_2 - 1.5)\left( \al_-^2(\rho_1) -  \oo(1) \right)>1$, so equation \eqref{addconstaint2} does not give a trivial bound.
- \end{proof}
-
-%\todo{add a transition example}
-
-\iffalse
-Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.
-
-\paragraph{A precise bound when there is no model shift.}
-As Proposition \ref{prop_monotone} shows, if $\beta_s$ and $\beta_t$ are equal, then adding the source task dataset always helps learn the target task.
-The goal of this section is to understand how covariate shift affects the rate of transfer. \todo{add conceptual msg}
-
-%The key quantity is to look at:
-%The estimator using the source and target together from minimizing equation \eqref{eq_mtl_basic} is
-%\[ \hat{\beta}_{s,t} = (X_1^{\top} X_1 + X_2^{\top} X_2)^{-1} (X_1^{\top}Y_1 + X_2^{\top}Y_2)\]
-%The estimation error of $\hat{\beta}_{s,t}$ is
-%\begin{align}\label{eq_two_task}
-%  \err(\hat{\beta}_{s,t}) = \sigma^2 \cdot \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The estimation error using the target alone is
-%\begin{align}\label{eq_target_task}
-%	\err(\hat{\beta}_t) = \sigma^2 \cdot \tr[(X_2^{\top} X_2)^{-1}].
-%\end{align}
-%The improvement of estimation error from adding the source task is then given by
-%$\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})$.
-%For the test error on the target task, the improvement from adding the source task is
-%\[ \te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t}) = \sigma^2\cdot\bigtr{\bigbrace{(X_2^{\top}X_2)^{-1} - (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}}\cdot\Sigma_2}. \]
-
-%We calculate the amount of improvement by comparing equation \eqref{eq_two_task} to equation \eqref{eq_target_task}.
-A simple observation here is that when $\beta_s = \beta_t$, the optimal $\hat{w}$ for minimizing equation \eqref{eq_te_mtl} is equal to $1$.
-Based on this observation, we can get a more precise result than Theorem \ref{thm_model_shift} on the improvement of adding the source task data that only depends on the covariance matrices $\Sigma_1, \Sigma_2$ and the number of data points $n_1, n_2$.
-
-\begin{proposition}[Transfer rate without model shift]\label{thm_cov_shift}
-Suppose $\beta_s = \beta_t$ and $\|\beta_t\|_2^2\sim p\sigma^2$ (i.e.
-the $l^2$-norm of the vector $\beta_t$ is of the same order as that of the error vector).
-Assume that the condition numbers of $\Sigma_1$, $\Sigma_2$ and $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all bounded by a constant $C>0$.
-Then we have that the optimal ratio for $W_1/W_2$ in equation \eqref{eq_te_mtl} satisfies
-	$$1\le \hat{w} \le 1+\OO(p^{-1}).$$%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
-	%where $M:=\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-Moreover, we have
-	\begin{align}\label{tehatw1}
-		%\err(\hat{\beta}^{\TL}_{s,t}) &= \sigma^2 \cdot \bigtr{\frac 1 {(n_1 + n_2)a_1\Sigma_1 + (n_1 + n_2)a_2\Sigma_2}} \\
-		\te(\hat{\beta}^{\TL}_{t}) &= \sigma^2 \cdot \bigtr{\bigbrace{(n_1 + n_2)a_1 M^\top M  + (n_1 + n_2)a_2\id}^{-1}} \cdot \left(1+ \bigo{p^{-1}}\right),
-	\end{align}
-where $a_1, a_2$ are the solutions to equations equation \eqref{eq_a2}. %\cor $w_0$ is close to 1 if the signal strength $\beta_t$ is much larger than the noise strength \nc
-\end{proposition}
-
-\begin{proof}
-We abbreviate $\val(w_2\hat{B}(w)):=\val(w)$.
-Note that $\val(w)\le \val(-w)$ for $w\ge 0$.
-Hence we have $\hat w\ge 0$.
-Moreover, we notice that $\val (w) < \val (1)$ for all $0\le w < 1$.
-Thus we have $\hat w\ge 1$.
-It suffices to consider the case with $w> 1$.
-Under the assumption on $\beta_s$ and $\beta_t$, we can write
-\begin{align}
-	\val(w) =&~  \left( 1-\frac1w\right)^2 \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \nonumber \\
-			&~ + \frac{\sigma^2}{w^2} \cdot \bigtr{( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} }. \nonumber
-\end{align}
-Since
-\begin{align*}
-&\left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2 \\
-&= \tr \left[ ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-2}M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t\beta_t^\top \Sigma_1^{1/2}Z_1^{\top} Z_1  M\right]
-\end{align*}
-is increasing with respect to $w$, then the derivative of $\val(w)$ can be bounded from below as
-\begin{align*}
-\val'(w) \ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   \\
-			&~ - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M +w^{-2}  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top}Z_1 M (M^\top Z_1^{\top}Z_1 M + w^{-2} Z_2^{\top}Z_2)^{-1}} \\
-\ge &~ 2\frac{w-1}{w^3} \left\|( M^\top Z_1^{\top}Z_1 M +  Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2   - 2 \frac{\sigma^2}{w^3} \cdot \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}}.
-			%\\ =& ~ 2\frac{d^2}{w^3} \tr\left[( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} \left[\left( w-1\right)\left(Z_1 \Sigma_1 Z_1^{\top}\right) - \frac{\sigma^2}{d^2}\id \right] Z_1 M ( M^\top Z_1^{\top}Z_1 M + w^{-2}Z_2^{\top}Z_2)^{-1}\right]  .
-\end{align*}
-Hence $\val'(w)\ge 0$ if $w>1+ \e_0$, where
-$$\e_0:= \frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2}.$$
-In other words, $\val(w)$ is strictly increasing function on $[1+\e_0,\infty]$. Thus we get that $\hat w$ satisfies
-\be\label{hatw1}1\le w \le 1+\e_0.\ee Using Fact \ref{lem_minv}, we get that
-$$\e_0=\OO(\sigma^2/\|\beta_t\|_2^2)=\OO(p^{-1}).$$
-
-Finally, plugging equation \eqref{hatw1} into the expression $\te(\hat{\beta}^{\TL}_{t}) $, we obtain equation \eqref{tehatw1}.
-%$$1\le \hat{w} \le w_0:=1 +\frac{\sigma^2  \bigtr{(M^\top Z_1^{\top}Z_1 M)^{-1}} }{\left\|( M^\top Z_1^{\top}Z_1 M + Z_2^{\top}Z_2)^{-1} M^\top Z_1^{\top} Z_1 \Sigma_1^{1/2}\beta_t \right\|^2},$$
-\end{proof}
-
-As a remark, we see that Proposition \ref{prop_monotone} follows from Theorem \ref{thm_cov_shift}.
-The amount of reduction on test error for the target task is given as
-	\begin{align*}
-%		\err(\hat{\beta}_t) - \err(\hat{\beta}_{s,t})
-%		&= \sigma^2 p \cdot \bigtr{\frac 1 {(n_2 - p) \Sigma_2} - \frac 1 {(n_1 + n_2)a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2}}, \\
-		\te(\hat{\beta}_t) - \te(\hat{\beta}_{s,t})
-		&= \sigma^2 \cdot \bigbrace{\frac p {n_2 - p} -  \bigtr{\bigbrace{(n_1 + n_2)a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + (n_1 + n_2)a_2\id}^{-1}}}.
-	\end{align*}
-Because
-\begin{align*}
-	\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)
-	\Leftarrow~ & (n_2 - p)\Sigma_2 \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 + n_2)a_2 \Sigma_2 \\
-	\Leftrightarrow~ & \zeroMatrix \preceq (n_1 + n_2) a_1 \Sigma_1 + (n_1 - (n_1 + n_2)\cdot a_1) \Sigma_2,
-\end{align*}
-which is true since $a_1 \le n_1 / (n_1 + n_2)$ by equation \eqref{eq_a2}.
-The proof for $\te(\hat{\beta}_{s,t}) \le \te(\hat{\beta}_t)$ follows by multiplying $\Sigma_2^{-1/2}$ on both sides of the inequalities above.
-
-\medskip
-\fi
-
-%\textbf{Remark.} Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
-{\cor (cannot get this because we only have some bounds.
-If we let $c_1\to \infty$, then the curve of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ already becomes flat, and it is meaningless to discuss the minimum of this function at this point?)}
-
-\iffalse
-\subsection{Label Denoising}
-
-The proof of Proposition \ref{prop_var_transition} is similar to the above proof of Proposition \ref{prop_dist_transition}.
-%The details can be found in Appendix \ref{app_proof_data}.
-
-\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
-In the setting of Proposition \ref{prop_var_transition}, the test loss is given by equation \eqref{eq_te_mtl_2task}.
-%the validation loss and the test error become
-%\begin{align*}
-%		\val(\hat{B}; w_1, w_2)
-%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
-%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
-%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)},
-%\end{align*}
-%and
-%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$.
-For the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
-\begin{align*}
-	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
-	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
-\end{align*}
-with high probability for any constant $\e>0$.
-
-In the current setting, we can also show that  equation \eqref{hatv_add1}  holds for $\hat v$.
-Since the proof is almost the same as the one for Claim \ref{lem_hat_v}, we omit the details.
-%$$|\hat w-1|=\OO(p^{-1}).$$
-%as in equation \eqref{hatw_add1}.
-%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}.
-Thus under equation \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in equation \eqref{simple1}:
-\be \label{simple2}
-\begin{split}
-\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\
-&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
-&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} ,
-\end{split}
-\ee
-with high probability for some small constant $\e>0$. Then we can write
-$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
-where
-$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
-satisfies equation \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$;
-$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
-satisfies equation \eqref{Deltabeta}; $\delta_{\vari}^{(2)}$ is defined as
-\begin{align*}
-	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
-\end{align*}
-%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
-%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has
-To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using Fact equation \eqref{lem_minv}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$.
-This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
-\be\label{Deltavar2}
-\al_-(\rho_1) - \oo(1)  \le  \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
-where
-$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
-Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.
-
- Note that the condition $pd^2< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}.
-Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.
-It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
-
-\vspace{5pt}
-
-\noindent{\bf Positive transfer.} By equation \eqref{Deltavar}, equation \eqref{Deltabeta} and equation \eqref{Deltavar2}, if the following inequality holds,
-\be\label{cond sigma1}
-\begin{split}
-&\sigma_2^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)} \cdot (1-\oo(1)) \\
-&>pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_+^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_+(\rho_1)  ,
-\end{split}
-\ee
-then we have $\delta_{\vari} > \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can solve equation \eqref{cond sigma1} to get
-\begin{align*}
-\sigma_1^2 < - pd^2\cdot \rho_1 \al_+(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2) \al_+^{-1}(\rho_1)\right]\cdot (1-\oo(1)).
-\end{align*}
-This proves the first claim of Proposition \ref{prop_var_transition} using $\nu\ge \al_+^2(\rho_1) +  \oo(1) $.
-
-\vspace{5pt}
-
-\noindent{\bf Negative transfer.} On the other hand, if the following inequality holds,
-\be\label{cond sigma12}
-\begin{split}
-&\sigma_2^2 \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}\cdot \left(1 + \oo(1)\right) \\
-&< pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\al_-^2(\rho_1)  + (\sigma_1^2 -\sigma_2^2)\cdot \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3} \al_-(\rho_1) ,
-\end{split}
-\ee
-then we have $\delta_{\vari} < \delta_{\bias} + \delta_{\vari}^{(2)}$ w.h.p., which gives $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can solve equation \eqref{cond sigma12} to get
-\begin{align*}
-\sigma_1^2 > - pd^2 \cdot \rho_1 \al_-(\rho_1) +\sigma_2^2 \left[ 1+ \rho_1\Phi(\rho_1, \rho_2)\al_-^{-1}(\rho_1)\right]\cdot (1+\oo(1)).
-\end{align*}
-This proves the second claim of Proposition \ref{prop_var_transition}.
-\end{proof}
-\fi
-
-\subsection{Labeling Efficiency}
-
-Next we prove Proposition \ref{prop_data_efficiency}, which gives precise upper and lower bounds on the data efficiency ratio for Taskonomy.
-
-\begin{proof}[Proof of Proposition \ref{prop_data_efficiency}]
-Suppose we have reduced number of datapoints---$x n_1$ for task 1 and $x n_2$ for task 2 with $n_1=\rho_1 p$ and $n_2=\rho_2 p$.
-Then all the results in the proof of Proposition \ref{prop_dist_transition} still hold, except that we need to replace $(\rho_1,\rho_2)$ with $(x\rho_1,x\rho_2)$.
-More precisely, we have
-	\begin{align*}
-		 a_1 = \frac{\rho_1(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(x\rho_1 + x\rho_2 - 1)}{x(\rho_1 + \rho_2)^2} ,  \\
-		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}, \quad
-		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(x\rho_1 + x\rho_2 - 1)}.
-	\end{align*}
-Then with Lemma \ref{lem_cov_shift} we can obtain that with high probability,
-	\be\label{reduceproof1}
-\begin{split}
-\te_i(\hat \beta_i^{\MTL}(x)) =  \frac{\sigma^2}{x (\rho_1+\rho_2) - 1}\left(1+ \oo(1)\right)+ \delta^{(i)}_{\bias}, \quad i=1,2,
-\end{split}
-\ee
- where as in equation \eqref{Deltabeta}, the model shift biases $\delta^{(i)}_{\bias}$ satisfy that with high probability,
-\be\nonumber %\label{Deltabeta}
-\al_-^2(\al\rho_i) - \oo(1)  \le {\delta_{\bias}^{(i)}}/{ \Delta_{\bias}^{(i)}} \le \al_+^2(\al\rho_i) +  \oo(1) , \quad i=1,2.\ee
-Here $ \Delta^{(i)}_{\bias}$ are defined as
-\be \nonumber
-\Delta^{(i)}_{\bias} := pd^2 \frac{(x\rho_i)^2\cdot x (\rho_1+\rho_2)}{[x ( \rho_1+\rho_2) - 1]^3} ,\quad i=1,2,.
-\ee
-On the other hand, by Lemma \ref{lem_minv} we have that w.h.p.,
-\be\label{reduceproof2}
-\te_i(\hat{\beta}_i^{\STL}) = \frac{\sigma^2}{\rho_i -1} \left( 1+ \oo(1)\right),\quad i=1,2.
-\ee
-Comparing equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we immediately obtain the lower bound $x^\star\ge x_l $.
-%where
-%$$\al_l:=\frac1{\rho_1+\rho_2}\left(\frac{2}{\frac1{\rho_1-1}+\frac1{\rho_2 -1}}+1\right) \ge \frac{\min(\rho_1,\rho_2)}{\rho_1+\rho_2}.$$
-In fact, if $x< x_l$, then we have that
-$$ \frac{2\sigma^2}{x (\rho_1+\rho_2) - 1} > \frac{\sigma^2}{\rho_1-1}+\frac{\sigma^2}{\rho_2-1}.$$
-This shows that $\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))$ is larger than $\te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL})$ even if we do not take into account the model shift biases $ \delta^{(i)}_{\bias}$.
-
-Then we try to obtain an upper bound on $x^\star$.
-In the following discussions, we only consider $x$ such that $x> x_l$.
-In particular, we have $x\rho > x_l \rho \ge \min(\rho_1,\rho_2)$, where we abbreviated $\rho:=\rho_1+\rho_2$.
-%Comparing equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we observe that $\te_2(\hat \beta(\al))  \ge \te_2(\hat{\beta}_t^{\STL}) $ for $\al \le 1/2-\oo(1)$, which gives $\al^* \ge 1/2 - \oo(1)$.
-%\noindent{\bf The upper bound.}
-From equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we see that $x^\star\le x$ if $x$ satisfies
-\be\nonumber
-\begin{split}
-&(1+\oo(1)) \cdot \sum_{i=1}^2 pd^2 \frac{(x\rho_i)^2\cdot x\rho }{(x\rho - 1)^3}  \bigbrace{1 + \sqrt{\frac{1}{x \rho_i}}}^4 \le \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{x\rho  - 1} .
-\end{split}
-\ee
-We rewrite the inequality as
-\be
-\begin{split}\label{solval1}
-  (1+\oo(1)) \cdot \frac{\Psi(\beta_1,\beta_2)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4\le \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2}{x \rho  - 1}.
-\end{split}
-\ee
-With $x\rho\ge \min(\rho_1,\rho_2)\ge 9$, we can get the simple bound
-$$\frac{1+\oo(1)}{[1 - (x\rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x\rho}}}^4 < 5. $$
-Inserting it into equation \eqref{solval1}, we can solve for the upper bound in equation \eqref{eq_uplowx}.
-%where we abbreviated $\rho:=\rho_1+\rho_2$.
-\end{proof}
-\begin{remark}
-We can get better bounds if the values of $\rho_1$ and $\rho_2$ increase.
-For example, if we consider the case $\min(\rho_1,\rho_2)\ge 100$, then with some basic calculations, one can check that in this case
-$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} + \sqrt{\frac{1}{x \rho}}}^4 <  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52.$$
-Thus the following inequality implies equation \eqref{solval1}:
-\be\nonumber %\label{solval1add}
-\begin{split}
-&\left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right) \Psi(\beta_1,\beta_2) < \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
-\end{split}
-\ee
-%In particular, if
-%\be\nonumber
-%\begin{split}
-%&\left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + 0.32\right) pd^2 < \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1} - \frac{2\sigma^2}{(\rho_1+\rho_2) - 1} ,
-%\end{split}
-%\ee
-%that is, we have positive transfer when using all the data, then
-from which we can solve for the following upper bound on $x^\star$:
-\begin{align*}
-x^\star &<  \frac1{\rho} \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  -  \left(  \frac{\rho_1^2 + \rho_2^2}{\rho^2} + 0.52\right)\Psi(\beta_1,\beta_2)}+ \frac1\rho .
-%\\
-%& < \frac1{\rho_1+\rho_2}\left[\frac{2 }{\frac{1}{\rho_1}+\frac1{\rho_2}  - \left(  \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} + \frac13\right)\frac{pd^2}{\sigma^2}}+ 1\right] .
-\end{align*}
-Similarly, we can get a better lower bound.
-%\noindent{\bf The lower bound.}
-From equation \eqref{reduceproof1} and equation \eqref{reduceproof2}, we see that $x^\star\ge x$ if $x$ satisfies
-\be\label{solval2}
-\begin{split}
-&(1-\oo(1)) \cdot  \frac{\Psi(\beta_1,\beta_2)}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x \rho}}}^4 \ge \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x \rho - 1} .
-\end{split}
-\ee
-%We then follow similar arguments as the above proof for the upper bound.
-Then in the case $\min(\rho_1,\rho_2)\ge 100$, with some basic calculations, one can show that the sum on the left-hand side of equation \eqref{solval2} satisfies
-$$ \frac{1}{[1 - (x \rho)^{-1}]^3} \sum_{i=1}^2 \bigbrace{\sqrt{\frac{\rho_i}{\rho}} - \sqrt{\frac{1}{x\rho}}}^4 >  \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33 .$$
-Thus the following inequality implies equation \eqref{solval2}:
-\be\label{solval2add}
-\begin{split}
-&\left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)  > \frac{1}{\rho_1 -1}+\frac{1}{\rho_2 -1} - \frac{2 }{x\rho - 1} ,
-\end{split}
-\ee
-%There are two cases: if
-%\be\nonumber
-%\begin{split}
-%&\left( \frac{\rho_1^2 + \rho_2^2}{(\rho_1+\rho_2)^2} -0.26\right) pd^2 \ge \frac{\sigma^2}{\rho_1 -1}+\frac{\sigma^2}{\rho_2 -1},
-%\end{split}
-%\ee
-%then we have negative transfer for all choice of $0\le \al \le 1$; otherwise,
-from which we can solve for the following lower bound on $x^\star$:
-\begin{align*}
-x^\star &>  \frac1\rho \frac{2 }{\frac{1}{\rho_1-1}+\frac1{\rho_2-1}  - \left( \frac{\rho_1^2 + \rho_2^2}{\rho^2} -0.33\right) \Psi(\beta_1,\beta_2)}+ \frac1\rho .
-\end{align*}
-This gives a lower bound above $x_l$.
-\end{remark}
-\fi

### 2020-10-09 arxiv/proof_same_cov.tex
restructure B.2
sec A

@@
-	\section{Missing Proof of the Same Covariates Setting}\label{app_proof_error_same_cov}
+	\section{Missing Proof of the Same Covariates Case}\label{app_proof_error_same_cov}
 
-	\paragraph{Proof of Claim \eqref{lem_exp_opt}.}
+	\paragraph{Proof of Claim \ref{lem_exp_opt}.}
 	To facilitate the analysis, we consider the following matrix notations.

### 2020-10-10 arxiv/tools.tex
sec C

@@
 Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers.
-Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and $n^{-1/2}x_i$ and $n^{-1/2}y_j$ satisfy the bounded support condition (\ref{eq_support}) with $q\le n^{-\phi}$ for a small constant $\phi>0$.
+Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and $ x_i$ and $ y_j$ satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $q$.
+%with $q\le n^{-\phi}$ for a small constant $\phi>0$.
 Then we have the following bounds:
 %for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
-\begin{align*}
-\Big| \frac{1}{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  q \max_{i} \vert A_i \vert+ \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec q^2 B_d  + qB_o + \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}}, \\
-\Big\vert \frac1n\sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec q B_d   , \quad &\Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec qB_o + \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,
-\end{align*}
+\begin{align}
+\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec  q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec q^2 B_d  + q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
+\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20}
+\end{align}
 where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if all the moments of $ x_i$ and $ y_j$ exist in the sense of equation \eqref{assmAhigh2}, then we have stronger bounds
 \begin{align}
-\Big\vert \frac1{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
- \Big\vert  \frac1n \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec \frac1{n}\Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
+\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
+ \Big\vert  \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec  \Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert  \sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
 \end{align}
+%\begin{align}
+%\Big\vert \frac1{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
+% \Big\vert  \frac1n \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec \frac1{n}\Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
+%\end{align}
 \end{lemma}
+
+As a corollary, we can obtain the following concentration estimates for random variables with bounded moments as in equation \eqref{assmAhigh}.
+
+\begin{corollary} \label{cor_largedeviation}
+Let $Z\in \R^{n\times p}$ be a random matrix as in Assumption \ref{assume_rm}. Then for any deterministic vector $v\in \R^p$, we have that
+$$\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-2c_\varphi} \max_{1\le i\le p}|v(i)|^2$$
+with high probability.
+\end{corollary}
+ \begin{proof}
+ Using \eqref{eq largedev10} and \eqref{eq largedev20}
+ \end{proof}

### 2020-10-10 arxiv/experiments.tex
introduction wip;

@@
 
-\paragraph{The same covariates case.}
+\paragraph{Sample efficiency.}
 First, we study the setting of Example \ref{ex_same_cov}.
@@
 
-\paragraph{The different covariates case.}
+\paragraph{Sample ratio.}
 Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
@@
 
+\paragraph{Covariate shift.}
 Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}.

### 2020-10-10 arxiv/setup.tex
section 3 4 polish writing
introduction wip;

--- 2020-10-02 arxiv/setup.tex
@@
-\paragraph{Linear models.}
+\subsection{Problem Formulation and Main Results}
+
 Suppose we have $t$ labeled regression tasks. %where $t$ is a fixed value that does not grow with the feature dimension $p$.
@@
 
-\medskip
-\noindent\textbf{Theoretical works.}
 Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
@@
 
-% Adding a regularization over $B$, e.g. .
-\medskip
-\noindent\textbf{Methodological works.}
 Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
@@
 
-\medskip
-\noindent\textbf{Random matrix theory.}
 The random matrix theory tool and related proof of our work fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
@@
 The rest of this paper is organized as follows.
-In Section \ref{sec_prelim}, we present a preliminary of hard parameter sharing and random matrices. We describe several well-known facts.
+In Section \ref{sec_prelim}, we describe and random matrices. We describe several well-known facts.
 In Section \ref{sec_example}, we describe illustrative examples of our technical results and discuss their implications.
@@
 
-\section{Preliminaries}\label{sec_prelim}
-
-\subsection{Notations}
+\paragraph{Notations.}
+Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
+Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
 We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
@@
 We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-
-Let $A = [a_1, a_2, \dots, a_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-
-%\noindent\textbf{Positive/Negative transfer.}
-
-\subsection{Hard Parameter Sharing}
-
-\subsection{Random Matrices}
-
-We introduce several standard assumptions on the random matrices we study.
-\begin{assumption}\label{assume_rm}
-	Let $\varphi > 4$ be a fixed value.
-	Let $\tau > 0$ be a small enough constant.
-	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
-entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	We assume the following standard conditions.
-	\begin{enumerate}
-		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-			\begin{align}\label{assmAhigh}
-				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
-			\end{align}
-		\item The sample size $n$ grows to infinity proportionally with the dimension $p$, i.e. $n / p \rightarrow \rho \in (0, 1/\tau)$ as $p$ goes infinity.
-	\end{enumerate}
-\end{assumption}
-
-Under the above assumption, we state several well-known facts regarding the random matrix $X$.
-
-\begin{fact}\label{lem_minv}
-	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	With high probability over the randomness of $X$, we have that
-	\begin{enumerate}
-		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
-		\item $\bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(p^{-c_{\varphi}})$, cf. Theorem 2.4 in \citet{isotropic}.
-		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf.
-\citet[Theorem 2.10]{isotropic} and \citet[Lemma 3.12]{DY}.
-	\end{enumerate}
-\end{fact}
-
-%Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
-%This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
-Finally, for the random noise component, we assume that all of its moments exist.
-More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
-\begin{align}\label{assmAhigh2}
-	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
-\end{align}
-Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
-We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.

### 2020-10-10 arxiv/proof_same_cov.tex
sec C

@@
 	To facilitate the analysis, we consider the following matrix notations.
-	Let
-		\[ \cE A^{\top} = {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \text{ and } \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{-1}. \]
+	Denote
+		%\[ \cE A^{\top} := {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \]
+\[\cE  :=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}],  \quad \text{ and } \quad \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{\dag}. \]
 	For any $j = 1,2,\dots, t$, let
 	\begin{align*}
-		H_j &\define B^{\star} A^{\top} (AA^{\top})^{\dagger} A_j - \beta^{(j)}, \\
-		E_j &\define \cW A_j - \varepsilon^{(j)}.
+		H_j &\define B^{\star} A^{\top} (AA^{\top})^{\dagger} A_j - \beta^{(j)}, \quad \text{ and } \quad E_j \define \cW A_j - \varepsilon^{(j)}.
 	\end{align*}
@@
 	\end{align}
-	whose expectation over $X$ is $\bignorm{\Sigma^{1/2}(B^{\star} U_A U_A^{\top} - B^{\star})}^2$.
+	where $U_{A} U_{A}^{\top} \in\real^{t\times t}$ denotes the subspace $ {A}^{\top} ( {A}{A}^{\top})^{\dagger}  {A}$.
+Note that the expectation of equation \eqref{eq_gA_p1} over $X$ is $\bignorm{\Sigma^{1/2}(B^{\star} U_A U_A^{\top} - B^{\star})}^2$.
 	Second, one can verify that the cross terms are equal to the following
@@
 	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
-	First, we have that $\ex{\cE} = \sigma^2 \cdot n \cdot t$.
+	First, we have that $\ex{\|\cE\|_F^2} = \sigma^2 \cdot n \cdot t$.
 %	Conditional on $X$, we have that
@@
 %	We consider both terms in the above equation one by one.
-	Second, note that
+	Second, notice that
 	%\begin{align}
@@
 	\end{align*}
-	In the above, the first equation uses the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
-	The second equation uses the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{\dagger} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
+	In the above derivation, the second step used the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
+	The third step used the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{\dagger} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
 	Therefore, we have that
+%	\begin{align*}
+%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
+%	\end{align*}
+%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
 	\begin{align*}
-		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
+		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{X(X^{\top} X)^{-1} X^{\top}} =  \sigma^2 \cdot r \cdot \bigtr{ X^{\top}X(X^{\top} X)^{-1}}  = \sigma^2 \cdot r \cdot p.
 	\end{align*}
-	because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
+   because $X^\top X$ is a $p\times p$ matrix.	
 	%Next, note that

### 2020-10-10 arxiv/proof_same_cov.tex
section 2 wip

--- 2020-10-09 arxiv/proof_same_cov.tex
@@
-	\section{Missing Proof of the Same Covariates Case}\label{app_proof_error_same_cov}
+\section{Missing Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_error_same_cov}
 
@@
 	To facilitate the analysis, we consider the following matrix notations.
-	Let
-		\[ \cE A^{\top} = {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \text{ and } \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{-1}. \]
+	Denote
+		\[ \cE A^{\top} := {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \quad \text{ and } \quad \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{\dag}. \]
 	For any $j = 1,2,\dots, t$, let
 	\begin{align*}
-		H_j &\define B^{\star} A^{\top} (AA^{\top})^{\dagger} A_j - \beta^{(j)}, \\
-		E_j &\define \cW A_j - \varepsilon^{(j)}.
+		H_j &\define B^{\star} A^{\top} (AA^{\top})^{\dagger} A_j - \beta^{(j)}, \quad \text{ and } \quad E_j \define \cW A_j - \varepsilon^{(j)}.
 	\end{align*}

### 2020-10-10 arxiv/setup.tex

@@
 \paragraph{Notations.}
+Let $B^\star \define [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
+Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
 Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
 We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.

### 2020-10-10 arxiv/tools.tex

@@
 Let $Z\in \R^{n\times p}$ be a random matrix as in Assumption \ref{assume_rm}. Then for any deterministic vector $v\in \R^p$, we have that
-$$\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-2c_\varphi} \max_{1\le i\le p}|v(i)|^2$$
+\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2\ee
 with high probability.
@@
  \begin{proof}
- Using \eqref{eq largedev10} and \eqref{eq largedev20}
+We introduce the truncated matrices $\wt Z$ with entries
+$ \wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le q \right)\cdot Z_{ij} $
+for $q= n^{1/2-\frac{\varphi - 4}{2\varphi}}\log n$. By equation \eqref{Ptrunc}, we have that
+\begin{equation}\label{XneX222}
+\mathbb P(\wt Z= Z) =1-\OO ( (\log n)^{-\varphi}).
+\end{equation}
+Furthermore, by equation \eqref{meanshif} we have that
+\be\label{meanshif222}
+|\mathbb E  \wt  Z_{ij}| =\OO(n^{-3/2}), \quad  \mathbb E |\wt  Z_{ij}|^2 =1+ \OO(n^{-1}).
+\ee
+%From the first estimate in equation \eqref{meanshif}, we can also get a bound on the operator norm:
+%\be\label{EZ norm222}\|\E \wt Z^{(1)}\|=\OO(n^{-1/2}) .
+%\ee
+Then we can centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$ 
+It suffices to show that 
+\be\label{show_whZ}
+ \left|\|\wh Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2.
+\ee 
+In fact, provided that \eqref{show_whZ} holds, using \eqref{meanshif222} it is easy to get that 
+$$ \left|\|\wt Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2,$$
+which implies \eqref{Zv_cor} for any fixed value $c_{\varphi}$ within $(0, \frac{\varphi - 4}{2\varphi})$.
+
+For \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$.
+Moreover, using \eqref{eq largedev10} we get that
+$$ |(\wh Zv)_i| \prec q \max_{1\le i\le p}|v_i| + \|v\| . $$
+Together with the trivial $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $q$.
+Then applying \eqref{eq largedev20}, we get that
+$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\prec n^{1/2} q  \|v\|^2 .
+ $$
+This concludes \eqref{show_whZ}.
  \end{proof}

### 2020-10-10 arxiv/proof_same_cov.tex

--- 2020-10-10 arxiv/proof_same_cov.tex
@@
 	\begin{align*}
-		H_j &\define B^{\star} A^{\top} (AA^{\top})^{\dagger} A_j - \beta^{(j)}, \quad \text{ and } \quad E_j \define \cW A_j - \varepsilon^{(j)}.
+		H_j &\define B^{\star} A^{\top} (AA^{\top})^{+} A_j - \beta^{(j)}, \quad \text{ and } \quad E_j \define \cW A_j - \varepsilon^{(j)}.
 	\end{align*}
@@
 	We will divide $g(A)$ into three parts.
-	First, we have that
+	We will use matrix notations in the proof since they are more compact.
+	That is, stacking $[H_j]_j$ gives matrix $B^{\star} A^{\top} (AA^{\top}) A - B^{\star}$,
+	and stacking $[E_j]_j$ gives $\cW A - \cE$.
+
+	\paragraph{Part 1:} The first part is the square of $XH_j$,
 	\begin{align}\label{eq_gA_p1}
-		\sum_{j=1}^t \bignorm{X H_j}^2 = \bignorm{X (B^{\star} U_A U_A^{\top} - B^{\star})}^2,
+		\sum_{j=1}^t \bignorm{X H_j}^2
+		= \bignormFro{X (B^{\star} A^{\top} (AA^{\top}) A - B^{\star})}^2
+		= \bignormFro{X (B^{\star} U_A U_A^{\top} - B^{\star})}^2,
 	\end{align}
-	where $U_{A} U_{A}^{\top} \in\real^{t\times t}$ denotes the subspace $ {A}^{\top} ( {A}{A}^{\top})^{\dagger}  {A}$.
-Note that the expectation of equation \eqref{eq_gA_p1} over $X$ is $\bignorm{\Sigma^{1/2}(B^{\star} U_A U_A^{\top} - B^{\star})}^2$.
-	Second, one can verify that the cross terms are equal to the following
+	where $U_{A} U_{A}^{\top} \in\real^{t\times t}$ denotes the subspace $ {A}^{\top} ( {A}{A}^{\top})^{+}  {A}$.
+	Taking expectation of equation \eqref{eq_gA_p1} over $X$, we get
+		\[ \bignorm{\Sigma^{1/2}(B^{\star} U_A U_A^{\top} - B^{\star})}^2. \]
+
+	\paragraph{Part 2:} The second part is the cross term, which is equal to the following using the matrix notations
 	\begin{align}\label{eq_gA_p2}
@@
 	which is zero in expectation over $\cE$.
-	Finally, we have that
+
+	\paragraph{Part 3:} The last part is the square of $E_j$,
 	\begin{align}\label{eq_gA_p3}
@@
 	\end{align}
-	which is because $\norm{\cW A}^2 = \inner{\cW A}{\cE}$.
+	which is because $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
 	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
@@
 	Combining equation \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain that equation \eqref{eq_gA_err} holds.
-	Next, using triangle inequality, we have that
+
+	\bigskip
+	Next, we use equation \eqref{eq_gA_err} to prove the claim.
+	Using triangle inequality, we upper bound the gap between $g(A^{\star})$ and $g(\hat{A})$
 	\begin{align}
-		g(U_r) - g(\hat{A}) &\le \bigabs{g(U_r) - \ex{g(U_r)}} + (\ex{g(U_r)} - \ex{g(\hat{A})}) + \bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
-		&\le \bigabs{g(U_r) - \ex{g(U_r)}} +\bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
+		g(A^{\star}) - g(\hat{A}) &\le \bigabs{g(A^{\star}) - \ex{g(A^{\star})}} + (\ex{g(A^{\star})} - \ex{g(\hat{A})}) + \bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
+		&\le \bigabs{g(A^{\star}) - \ex{g(A^{\star})}} +\bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
 		&\le p^{-c} \cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + \e}\cdot \sigma^2 n \cdot t. \label{eq_g_gap}
 	\end{align}
-	The second equation uses the fact that $U_r$ is a global minimum of $\ex{g(\cdot)}$.
-	The third equation uses equation \eqref{eq_gA_err} and the fact that the spectral norm of an identity matrix minus a projection matrix is at most one.
-	On the other hand, we simplify $g(A)$ as follows
+	The second equation uses the fact that $A^{\star}$ is a global minimum of $\ex{g(\cdot)}$, hence $\ex{g(A^{\star})} \le \ex{g(\hat{A})}$.
+	The third equation uses equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id$ is at most one.
+
+	We can also derive a lower bound on the gap as follows.
+	We simplify $g(A)$ as
 	\begin{align*}
@@
 	\end{align*}
-	We denote $M = Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y$, which appears in the equation above.
-	Since $\hat{A}$ is a global minimum of $g(A)$, we have that
+	We denote $H = Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y$, which appears in the equation above.
+	Since $\hat{A}$ is a global minimum of $g(A)$, we have that $g(A^{\star}) \ge g(\hat{A})$.
+	Hence,
 	\begin{align}
-		g(U_r) - g(\hat{A}) &= \abs{g(U_r) - g(\hat{A})} = \abs{\inner{M}{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}} \nonumber \\
-												&\ge \lambda_{\min}(M) \cdot \normFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}. \label{eq_g_gap1}
+		g(A^{\star}) - g(\hat{A}) &= \abs{g(A^{\star}) - g(\hat{A})} = \abs{\inner{H}{A^{\star} {A^{\star}}^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}} \nonumber \\
+												&\ge \lambda_{\min}(H) \cdot \normFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}. \label{eq_g_gap1}
 	\end{align}
-	Recall that $Y = X B^{\star} + \cE$. Therefore, the minimum singular value of $H$ can be lowered bounded as follows
+	Recall that $Y = X B^{\star} + \cE$ in matrix notation.
+	We bound the minimum singular value of $H$ as follows
 	\begin{align}
@@
 
-	%\noindent\textbf{Dealing with the empirical minimizer.}
-	%eet $\hat {\cal W}$ be the minimizer of $g$, and denote $\hat Q:= \hat{\cal W}^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat{\cal W} $.
-	%We show that $\norm{\hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p.
-	%\be\label{Q-Q}\|Q_0^{-1}\hat Q - \id\|_F = \oo(1) \quad \text{w.h.p.}\ee
-	%Since $\hat{\cW}$ is the minimizer of $g(\cdot)$, we have that
-	%\begin{align*}
-	%	g(U_r) - g(\hat{\cW}) = \bigabs{g(\hat{\cW}) - g(U_r)} &= n \cdot \bigabs{\inner{{B^{\star}}^{\top} \Sigma B^{\star}}{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}}\\
-	%	&\ge n \cdot \sigma_{\min}({B^{\star}}^{\top} \Sigma B^{\star}) \cdot \bignormFro{U_r U_r^{\top} - \hat{\cW}^{\top} (\hat{\cW}\hat{\cW}^{\top})^{-1} \hat{\cW}}.
-	%\end{align*}
 	Combining equation \eqref{eq_g_gap}, \eqref{eq_g_gap1}, and \eqref{eq_g_gap2}, we conclude that
@@
 		\bignormFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}
-		\le \frac{p^{-c} \rho \normFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + \e} \cdot \sigma^2 \rho t}{\lambda_{\min}^2(\Sigma^{1/2} B^{\star}) ((\sqrt{\rho} - 1)^2 - \rho \cdot p^{-c}) + \sigma^2 (1 - p^{-1/2 + \e})}.
+		&\le \frac{p^{-c} \cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + c} \cdot \sigma^2 nt} {\lambda_{\min}(H)} \\
+		&\le \frac{p^{-c} \rho \normFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + \e} \cdot \sigma^2 \rho t}{\lambda_{\min}^2(\Sigma^{1/2} B^{\star}) ((\sqrt{\rho} - 1)^2 - \rho \cdot p^{-c}) + \sigma^2 (1 - p^{-1/2 + \e})}
 	\end{align*}
@@
 	\paragraph{Proof of Claim \ref{claim_pred_err}.}
+	We apply similar arguments to Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
+	The prediction loss of hard parameter sharing for task $i$ is equal to
+	\begin{align*}
+		L(\hat{\beta}_i^{\MTL}) &= \bignorm{\Sigma^{1/2} (\hat{B} \hat{A}_i - \beta_i)}^2 \\
+		&= \bignorm{\Sigma^{1/2} ((X^{\top} X)^{-1} X^{\top} Y \hat{A}^{\top} (\hat{A} \hat{A}^{\top})^{+} \hat{A}_i - \beta_i)}^2 \\
+		&= \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i + E_i)}^2,
+	\end{align*}
+	where we denote $E_i = (X^{\top} X)^{-1} X^{\top} \cE \hat{a}_i$.
+	We divide the prediction loss to three parts.
+
+	\paragraph{Part 1:} The first part is the bias term:
+	$\norm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)}^2 = L(B^{\star} \hat{a}_i)$.
+
+	\paragraph{Part 2:} The second part is the cross term, whose expectation over $\cE$ is zero. The concentration error is
+	\begin{align*}
+		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}E_i}}
+		\le \bignormFro{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)} \cdot \bignorm{\Sigma^{1/2} E_i}.
+	\end{align*}
+	Next, we use the fact that the spectral norm of $\cE$ is at most $\sigma \cdot p^{\e}$.
+	Hence, the spectral norm of $\Sigma^{1/2} E_i$ is at most
+		\[ \sigma \cdot p^{\e} \cdot \norm{\Sigma^{1/2} (X^{\top} X)^{-1} X^{\top}} \cdot \norm{\hat{a}_i}. \]
+	Therefore, the cross term is bounded by $\sigma \cdot p^{\e}$ times
+	\begin{align*}
+			& \bignormFro{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)} \cdot \norm{\Sigma^{1/2} (X^{\top} X)^{-1} X^{\top}} \cdot \norm{\hat{a}_i} \\
+		\le & \bignormFro{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)}^2 + \norm{\hat{a}_i}^2 \cdot \bignorm{\Sigma^{1/2} (X^{\top} X)^{-1} X^{\top}}^2 \tag{by Cauchy-Shwartz inequality} \\
+		\le & \bignormFro{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} + \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top} X)^{-1}}.
+	\end{align*}
+
+	\paragraph{Part 3:} The final part is the square of $E_i$. One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
+	Next, we bound the concentration error.
+	Let $A = X (X^{\top} X)^{-1} \Sigma (X^{\top} X)^{-1} X^{\top}$.
+	We have that
+	\begin{align*}
+		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 - \exarg{\cE}{\bignorm{\Sigma^{1/2} E_i}^2}}
+		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
+	\end{align*}
+	In the above equation, we note that the trace of $A$ is precisely the trace of $\Sigma (X^{\top} X)^{-1}$.
+	On the other hand, the concentration error of the spectral norm of $\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top}$ is at most $\sigma^2 \e $.
+
+	Combining the three parts together, we conclude the proof of Claim \ref{claim_pred_err}.
 

### 2020-10-10 arxiv/proof_same_cov.tex
sec A minor edit

@@
 	\begin{align*}
-			\exarg{\cE}{\cE A^{\top} (AA^{\top})^{\dagger} A \cE^{\top}}
-		&= \exarg{\cE}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{\dagger} A_k {\varepsilon^{(k)}}^{\top}} \\
-		&= \exarg{\cE}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{\dagger} A_j {\varepsilon^{(j)}}^{\top}} \\
+			\exarg{\cE}{\cE A^{\top} (AA^{\top})^{+} A \cE^{\top}}
+		&= \exarg{\cE}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{+} A_k {\varepsilon^{(k)}}^{\top}} \\
+		&= \exarg{\cE}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{+} A_j {\varepsilon^{(j)}}^{\top}} \\
 		&= \sigma^2 \cdot r \cdot \id_{n\times n}.
@@
 	In the above derivation, the second step used the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
-	The third step used the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{\dagger} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
+	The third step used the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{+} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
 	Therefore, we have that
@@
 		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}} \nonumber \\
-		&\le p^{1/2 + \e} \cdot \sigma^2 r. \label{eq_gA_err4}
+		&\le p^{1/2} \cdot (\sigma^2 r\cdot p^{\e}). \label{eq_gA_err4}
 	\end{align}
@@
 	\paragraph{Proof of Claim \ref{claim_pred_err}.}
-	We apply similar arguments to Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
+	We apply similar arguments from Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
 	The prediction loss of hard parameter sharing for task $i$ is equal to
@@
 		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}E_i}}
-		\le \bignormFro{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)} \cdot \bignorm{\Sigma^{1/2} E_i}.
+		\le \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)} \cdot \bignorm{\Sigma^{1/2} E_i}.
 	\end{align*}
@@
 	\begin{align*}
-			& \bignormFro{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)} \cdot \norm{\Sigma^{1/2} (X^{\top} X)^{-1} X^{\top}} \cdot \norm{\hat{a}_i} \\
-		\le & \bignormFro{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)}^2 + \norm{\hat{a}_i}^2 \cdot \bignorm{\Sigma^{1/2} (X^{\top} X)^{-1} X^{\top}}^2 \tag{by Cauchy-Shwartz inequality} \\
-		\le & \bignormFro{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} + \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top} X)^{-1}}.
+			& \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)} \cdot \norm{\Sigma^{1/2} (X^{\top} X)^{-1} X^{\top}} \cdot \norm{\hat{a}_i} \\
+		\le & \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)}^2 + \norm{\hat{a}_i}^2 \cdot \bignorm{\Sigma^{1/2} (X^{\top} X)^{-1} X^{\top}}^2 \tag{by Cauchy-Shwartz inequality} \\
+		\le & \bignorm{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} + \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top} X)^{-1}}.
 	\end{align*}
 
-	\paragraph{Part 3:} The final part is the square of $E_i$. One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
+	\paragraph{Part 3:} The final part is the square of $E_i$.
+One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\sigma^2 \norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
 	Next, we bound the concentration error.
@@
 		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 - \exarg{\cE}{\bignorm{\Sigma^{1/2} E_i}^2}}
-		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
+		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top} - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
 	\end{align*}
@@
 
-	\paragraph{Proof of Theorem \ref{thm_many_tasks}.}
+	%\paragraph{Proof of Theorem \ref{thm_many_tasks}.}
 	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.

### 2020-10-10 arxiv/proof_same_cov.tex
sec A

--- 2020-10-10 arxiv/proof_same_cov.tex
@@
 %	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
-	note that $X H_j = Z \Sigma^{1/2} H_j \in \real^n$ is a random vector with i.i.d.
+%	note that $X H_j = Z \Sigma^{1/2} H_j \in \real^n$ is a random vector with i.i.d.
 entries of mean zero, variance $\|\Sigma^{1/2}H_j\|^2$, and finite $\varphi$-th moment by Assumption \eqref{assume_rm}.
-	Hence by the law of large numbers, we have that with high probability
-	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1 + \OO(p^{-\e}))$, for a small enough constant $\e$,
-	which implies that
+%	Hence by the law of large numbers, we have that with high probability	
+	applying Corollary \ref{cor_largedeviation} to $X H_j = Z \Sigma^{1/2} H_j$, we obtain that 
+	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(p^{-c_\varphi}))$ with high probability. 
+	%, for a small enough constant $\e$,
+	This implies that
 	\begin{align}
-		\abs{\sum_{j=1}^t \|X H_j\|^2 - \exarg{X}{\sum_{j=1}^t \norm{X H_j}^2}} \lesssim p^{-c} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
+		\abs{\sum_{j=1}^t \|X H_j\|^2 - \exarg{X}{\sum_{j=1}^t \norm{X H_j}^2}} \lesssim p^{-c_\varphi} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
 	\end{align}
 
-	For equation \eqref{eq_gA_p2}, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, we obtain that the following holds with high probability:
+	For equation \eqref{eq_gA_p2}, 
+	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
+	using Corollary \ref{cor_calE}, we obtain that the following holds with high probability:
 	\begin{align}
@@
 		&\le p^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)} \nonumber \\
-		&\le p^{1/2 + \e} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}, \label{eq_gA_err2}
+		&\lesssim p^{\e} \cdot \sigma \cdot \sqrt{n}\cdot \sqrt{t}\bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}, \label{eq_gA_err2}
 	\end{align}
-	which is less than the right hand side of equation \eqref{eq_gA_err} by Cauchy-Schwartz inequality.
-	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we use Fact \ref{lem_minv} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
+	which is bounded by the right hand side of equation \eqref{eq_gA_err} by AM-GM inequality.
+	In the second step, we used the fact that $X=Z\Sigma^{1/2}$.
+	In the third step, we used Fact \ref{lem_minv} (iii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)$ has rank at most $t$.
 

### 2020-10-10 arxiv/proof_examples.tex
introduction wip;
section 2 wip
section 2 restructure

@@
-\subsection{The Random-Effects Model}\label{app_iso_cov}
+\section{Proof of Corollary \ref{cor_MTL_loss}}\label{app_iso_cov}
 
-We provide the proof of Corollary \ref{cor_MTL_loss}.
+We follow a similar logic from Theorem \ref{thm_many_tasks}.
 We characterize the global minimizer of $f(A, B)$ in the random-effects model.
@@
  \begin{proof}
-By Fact \ref{lem_minv} (iii), we have that with high probability,
+By Fact \ref{fact_minv}(ii), we have that with high probability,
  \be\label{op_X12}
@@
 \end{align*}
-Using Fact \ref{lem_minv} (iii), we can obtain that with high probability,
+Using Fact \ref{fact_minv}(ii), we can obtain that with high probability,
 \begin{align}
@@
 $$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
-by Fact \ref{lem_minv} (iii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
+by Fact \ref{fact_minv}(ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
 Using \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_p$ and $w$ being the $i$-th coordinate vector, we can calculate that 

### 2020-10-10 arxiv/proof_same_cov.tex
section 2 restructure

@@
 	Therefore, we have that
-%	\begin{align*}
-%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
-%	\end{align*}
-%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
 	\begin{align*}
@@
 	In the second step, we used the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we used Fact \ref{lem_minv} (iii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)$ has rank at most $t$.
+	In the third step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)$ has rank at most $t$.
 
@@
 	The third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_proof_gA} in Appendix \ref{app_tool}.
-	The last equation uses Fact \ref{lem_minv} for the minimum singular value of $Z^{\top}Z$ and Lemma \ref{largedeviation} for $\cE\cE^{\top}$.
+	The last equation uses Fact \ref{fact_minv} (ii) for the minimum singular value of $Z^{\top}Z$ and Lemma \ref{largedeviation} for $\cE\cE^{\top}$.
 

### 2020-10-10 arxiv/proof_same_cov.tex
sec A

--- 2020-10-10 arxiv/proof_same_cov.tex
@@
 %	We consider both terms in the above equation one by one.
+	Second, notice that for $U_XU_X^\top:=X(X^{\top} X)^{-1} X^{\top}$ and $1\le i, j \le t$,
+	%\begin{align}
+	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}.
+\label{eq_proof_same_cov_1}
+	%\end{align}
+	%We observe that
+	\begin{align*}
+			\exarg{\cE}{(\cE^{\top}U_XU_X^\top \cE)_{ij} }
+		&= \exarg{\cE}{{\varepsilon^{(i)}}^\top U_X U_X^\top  \varepsilon^{(j)} } = \sigma^2 \cdot \tr\left( U_XU_X^\top \right) \cdot \delta_{ij} = p\sigma^2 \cdot \delta_{ij},
+	\end{align*}
+	which implies that $\exarg{\cE}{\cE^{\top}U_XU_X^\top \cE }=p\sigma^2 \cdot \id_{t\times t}$.
+	In the above derivation, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
+	Therefore, we have that
+%	\begin{align*}
+%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
+%	\end{align*}
+%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
+	\begin{align*}
+		\exarg{\cE}{ \inner{\cW A}{\cE}} = p\sigma^2 \cdot \bigtr{\id_{t\times t}U_AU_A^\top} =  p \sigma^2 \cdot r ,
+			\end{align*}
+   because $U_AU_A^\top$ has rank $r$.	
+	%Next, note that
+	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
+	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.
+	Hence the proof is complete.
+
+	\iffalse
 	Second, notice that
@@
 	\begin{align*}
-		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{X(X^{\top} X)^{-1} X^{\top}} =  \sigma^2 \cdot r \cdot \bigtr{ X^{\top}X(X^{\top} X)^{-1}}  = \sigma^2 \cdot r \cdot p.
+		\exarg{\cE}{ \inner{\cW A}{\cE}} = \sigma^2 \cdot r \cdot \bigtr{X(X^{\top} X)^{-1} X^{\top}} =  \sigma^2 \cdot r \cdot \bigtr{ X^{\top}X(X^{\top} X)^{-1}}  = \sigma^2 \cdot r \cdot p.
 	\end{align*}
@@
 	Hence the proof is complete.
+\fi
 
@@
 
-	For equation \eqref{eq_gA_p3}, using Lemma \ref{largedeviation} and the fact that all moments of $\varepsilon_i$ exist, we obtain that with high probability
+	For equation \eqref{eq_gA_p3}, using Corollary \ref{cor_calE},
+	%Lemma \ref{largedeviation} and the fact that all moments of $\varepsilon_i$ exist, 
+	we obtain that with high probability,
 	\begin{align}
-		\abs{\normFro{\cE}^2 - \ex{\normFro{\cE}^2}} \le p^{-c_{\infty}} \ex{\normFro{\cE}^2}. \label{eq_gA_err3}
+		\abs{\normFro{\cE}^2 - \ex{\normFro{\cE}^2}} \le p^{c} \sigma^2 \| \id_{n\times n}\|_F = p^{c} \cdot \sqrt{n} \cdot \sigma^2 \le p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t, \label{eq_gA_err3}
 	\end{align}
-	For the inner product between $\cW A$ and $\cE$, we have that
+	as long as the constant $c$ is taken sufficiently small. 
+	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
 	\begin{align}
-		\bigabs{\inner{\cW A}{\cE} - \ex{\inner{\cW A}{\cE}}} &= \bigabs{\bigtr{U_X U_X^{\top} (\cE U_AU_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n})}} \nonumber  \\
-		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}} \nonumber \\
-		&\le p^{1/2} \cdot (\sigma^2 r\cdot p^{\e}). \label{eq_gA_err4}
+		\bigabs{\inner{\cW A}{\cE} - \exarg{\cE}{\inner{\cW A}{\cE}} } &= \bigabs{\bigtr{\left(\cE^\top U_X U_X^{\top}\cE  - p\sigma^2 \cdot  \id_{t\times t} \right)  U_AU_A^{\top} }} \nonumber  \\
+		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignormFro{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
+		&\le \sqrt{r} \cdot (p^{\e}\sigma^2\cdot \|U_X U_X^\top\|_F) \nonumber \\
+		&\le p^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r} \nonumber\\
+		& \le  p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t .\label{eq_gA_err4}
 	\end{align}
+
+%	\begin{align}
+%		\bigabs{\inner{\cW A}{\cE} - \ex{\inner{\cW A}{\cE}}} &= \bigabs{\bigtr{U_X U_X^{\top} (\cE U_AU_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n})}} \nonumber  \\
+%		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}} \nonumber \\
+%		&\le p^{1/2} \cdot (\sigma^2 r\cdot p^{\e}). \label{eq_gA_err4}
+%	\end{align}
 	%\begin{align*}
@@
 	%\end{align}
-	Combining equation \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain that equation \eqref{eq_gA_err} holds.
+	Combining equations \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain equation \eqref{eq_gA_err}.
 

### 2020-10-10 arxiv/diff_cov.tex

@@
-\section{The Different Covariates Case}\label{sec_diff}
+\section{Bias and Variance Limits when Tasks have Different Sample Sizes and Covariate Shifts}\label{sec_diff}
 
@@
 Our result extends a well-known result on the inverse of a sample covariance matrix.
-In particular, when $X_1$ is zero, we obtain Fact \ref{lem_minv}(ii) as a corollary.
+In particular, when $X_1$ is zero, we obtain Fact \ref{fact_tr} as a corollary.
 To see this, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to the variance limit.
@@
 	We first consider the impact of varying sample sizes.
-	Consider the random-effects model from Section \ref{sec_hps}, with both tasks having an isotropic population covariance matrix.
+	Consider the random-effects model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
 

### 2020-10-10 arxiv/tools.tex
sec A

@@
-\section{Toolbox}\label{app_tool}
+\section{Notations and Tools}\label{app_tool}
 
@@
 \subsection{Random Variables with Bounded Moments}
+
+\begin{fact}\label{fact_minv}
+	In the setting of Theorem \ref{thm_many_tasks}, with high probability over the randomness of $X$, we have that
+	\begin{enumerate}
+		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
+		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf.
+\citet[Theorem 2.10]{isotropic} and \citet[Lemma 3.12]{DY}.
+	\end{enumerate}
+\end{fact}
+
 The following lemma gives (almost) sharp concentration bounds for linear and quadratic forms of bounded supported random variables.
@@
  \end{proof}
+
+ Moreover, we can obtain the following concentration estimates for random noise satisfying \eqref{assmAhigh2}.
+
+ \begin{corollary}\label{cor_calE}
+ add corollary
+
+ using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}
+ \end{corollary}

### 2020-10-10 arxiv/setup.tex

@@
 
-\paragraph{Organizations.}
+\smallskip
+\noindent\textbf{Organizations.}
 The rest of this paper is organized as follows.
-In Section \ref{sec_prelim}, we describe and random matrices. We describe several well-known facts.
-In Section \ref{sec_example}, we describe illustrative examples of our technical results and discuss their implications.
-In Section \ref{sec_same}, we consider the same covariates setting and show the generalization error of hard parameter sharing.
-In Section \ref{sec_diff}, we consider the different covariates setting and show the bias and variance asymptotics using random matrix theory.
+In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
+In Section \ref{sec_diff}, we present our technical results for showing how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
+In Section \ref{sec_exp}, we validate our theory in both simulations and a real world classification task.
+In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.
 
@@
 Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
+Let $Y$ denote $[Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$.
+We can also write $Y = XB^{\star} + \cE$.
 Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
@@
 For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+Let $X^+$ denote its Moore-Penrose psuedoinverse.
 We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.

### 2020-10-10 arxiv/proof_same_cov.tex
sec A

@@
 	\paragraph{Proof of Claim \ref{claim_opt_dist}.}
-	In order to show that the subspace spanned by the rows of $\hat{A}$ is close to $U_r$, we first show that $g(A)$ and its expectation is close as follows.
+	Corresponding to the right-hand side of \eqref{eq_gA}, we define the function
+	$$h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r)$$
+	In order to show that the $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
 	\begin{align}\label{eq_gA_err}
-		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
+		\bigabs{g(A) - h(A)} \lesssim  n^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t,
 	\end{align}
+	for any fixed values $c_{\varphi}$ within $(0, \frac{\varphi-4}{2\varphi})$ and $c_{\infty}$ within $(0, 1/2)$. 
+%	\begin{align}\label{eq_gA_err}
+%		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
+%	\end{align}
 	To show the above result, we consider the concentration error of each part of $g(A)$.
@@
 	\begin{align}
-		\abs{\sum_{j=1}^t \|X H_j\|^2 - \exarg{X}{\sum_{j=1}^t \norm{X H_j}^2}} \lesssim p^{-c_\varphi} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
+		\abs{\sum_{j=1}^t \|X H_j\|^2 -  \sum_{j=1}^t n\norm{\Sigma^{1/2} H_j}^2} \lesssim   n^{-c_{\varphi}} \cdot n  \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2.
+\label{eq_gA_err1}
 	\end{align}
@@
 	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
-	using Corollary \ref{cor_calE}, we obtain that the following holds with high probability:
+	using Corollary \ref{cor_calE}, we obtain that the following holds with high probability for any small constant $\e>0$:
 	\begin{align}
-		|\inner{XB^{\star} (U_AU_A^{\top} - \id)}{\cE}| &\le p^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id)} \nonumber \\
-		&\le p^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)} \nonumber \\
-		&\lesssim p^{\e} \cdot \sigma \cdot \sqrt{n}\cdot \sqrt{t}\bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}, \label{eq_gA_err2}
+		|\inner{XB^{\star} (U_AU_A^{\top} - \id)}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id)} \nonumber \\
+		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)} \nonumber \\
+		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n}\cdot \sqrt{t}\bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)} \nonumber \\
+		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t
+		\label{eq_gA_err2}
 	\end{align}
-	which is bounded by the right hand side of equation \eqref{eq_gA_err} by AM-GM inequality.
+	which is bounded by the right hand side of equation \eqref{eq_gA_err} as long as $c$ is taken sufficiently small.
 	In the second step, we used the fact that $X=Z\Sigma^{1/2}$.
 	In the third step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)$ has rank at most $t$.
+In the fourth step, we used AM-GM inequality.
 
@@
 	\begin{align}
-		\abs{\normFro{\cE}^2 - \ex{\normFro{\cE}^2}} \le p^{c} \sigma^2 \| \id_{n\times n}\|_F = p^{c} \cdot \sqrt{n} \cdot \sigma^2 \le p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t, \label{eq_gA_err3}
+		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left( \cal E^\top \id_{n\times n}\cal E\right) - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F \nonumber\\
+		&= n^{1/2+c} \cdot \sigma^2 \le n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t, \label{eq_gA_err3}
 	\end{align}
-	as long as the constant $c$ is taken sufficiently small. 
+	as long as $c$ is taken sufficiently small. 
 	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
 	\begin{align}
-		\bigabs{\inner{\cW A}{\cE} - \exarg{\cE}{\inner{\cW A}{\cE}} } &= \bigabs{\bigtr{\left(\cE^\top U_X U_X^{\top}\cE  - p\sigma^2 \cdot  \id_{t\times t} \right)  U_AU_A^{\top} }} \nonumber  \\
-		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignormFro{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
-		&\le \sqrt{r} \cdot (p^{\e}\sigma^2\cdot \|U_X U_X^\top\|_F) \nonumber \\
-		&\le p^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r} \nonumber\\
-		& \le  p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t .\label{eq_gA_err4}
+		\bigabs{\inner{\cW A}{\cE} - \sigma^2\cdot p \cdot r } &= \bigabs{\bigtr{\left(\cE^\top U_X U_X^{\top}\cE  - p\sigma^2 \cdot  \id_{t\times t} \right)  U_AU_A^{\top} }} \nonumber  \\
+		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
+		&\le \sqrt{r} \cdot (n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F) \nonumber \\
+		&\le n^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r}  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t ,\label{eq_gA_err4}
 	\end{align}
+as long as $c$ is taken sufficiently small.
+Here in the third step, we applied Corollary \ref{cor_calE} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and used that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ is of rank $r$.
+In the fourth step, we used that $\|U_X U_X^\top\|_F=\sqrt{p}\le \sqrt{n}$ because $U_X$ is of rank $p$.
 
@@
 	Next, we use equation \eqref{eq_gA_err} to prove the claim.
-	Using triangle inequality, we upper bound the gap between $g(A^{\star})$ and $g(\hat{A})$
+	Using triangle inequality, we upper bound the gap between $g(A^{\star})$ and $g(\hat{A})$:
 	\begin{align}
-		g(A^{\star}) - g(\hat{A}) &\le \bigabs{g(A^{\star}) - \ex{g(A^{\star})}} + (\ex{g(A^{\star})} - \ex{g(\hat{A})}) + \bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
-		&\le \bigabs{g(A^{\star}) - \ex{g(A^{\star})}} +\bigabs{g(\hat{A}) - \ex{g(\hat{A})}} \nonumber \\
-		&\le p^{-c} \cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + \e}\cdot \sigma^2 n \cdot t. \label{eq_g_gap}
+		g(A^{\star}) - g(\hat{A}) &\le \bigabs{g(A^{\star}) - h(A^{\star})} + (h(A^{\star}) - h(\hat{A})) + \big|g(\hat{A}) - h(\hat{A})\big| \nonumber \\
+		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
+		&\lesssim n^{-c_\varphi}\cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
 	\end{align}
-	The second equation uses the fact that $A^{\star}$ is a global minimum of $\ex{g(\cdot)}$, hence $\ex{g(A^{\star})} \le \ex{g(\hat{A})}$.
-	The third equation uses equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id$ is at most one.
+	The second step used the fact that $A^{\star}$ is a global minimum of $h(\cdot)$, so that $h(A^{\star}) \le h(\hat{A})$.
+	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id$ is at most one.
 
-	We can also derive a lower bound on the gap as follows.
-	We simplify $g(A)$ as
+	Using \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows.
+	We simplify equation \eqref{eq_mtl_output_layer} as
 	\begin{align*}
@@
 	\end{align*}
-	We denote $H = Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y$, which appears in the equation above.
+	We denote $H = Y^{\top} X (X^{\top} X)^{-1} X^{\top} Y$, which appears in the above equation.
 	Since $\hat{A}$ is a global minimum of $g(A)$, we have that $g(A^{\star}) \ge g(\hat{A})$.
-	Hence,
+	Hence, we have
 	\begin{align}
 		g(A^{\star}) - g(\hat{A}) &= \abs{g(A^{\star}) - g(\hat{A})} = \abs{\inner{H}{A^{\star} {A^{\star}}^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}} \nonumber \\
-												&\ge \lambda_{\min}(H) \cdot \normFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}. \label{eq_g_gap1}
+												&\ge \lambda_{\min}(H) \cdot \normFro{A^{\star} {A^{\star}}^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}. \label{eq_g_gap1}
 	\end{align}
@@
 	\begin{align*}
-		\bignormFro{U_r U_r^{\top} - U_{\hat{A}} U_{\hat{A}}^{\top}}
+		\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}
 		&\le \frac{p^{-c} \cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + p^{-1/2 + c} \cdot \sigma^2 nt} {\lambda_{\min}(H)} \\

### 2020-10-11 arxiv/proof_same_cov.tex
sec A

@@
 	Corresponding to the right-hand side of \eqref{eq_gA}, we define the function
-	$$h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r)$$
+	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
 	In order to show that the $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
@@
 	\begin{align}
-		g(A^{\star}) - g(\hat{A}) &\le \bigabs{g(A^{\star}) - h(A^{\star})} + (h(A^{\star}) - h(\hat{A})) + \big|g(\hat{A}) - h(\hat{A})\big| \nonumber \\
+		h(\hat{A})- h(A^{\star})   &\le \bigabs{g(A^{\star}) - h(A^{\star})} + (g(\hat A) - g({A}^{\star})) + \big|g(\hat{A}) - h(\hat{A})\big| \nonumber \\
 		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
@@
 	\end{align}
-	The second step used the fact that $A^{\star}$ is a global minimum of $h(\cdot)$, so that $h(A^{\star}) \le h(\hat{A})$.
+	The second step used the fact that $\hat A$ is the global minimizer of $g(\cdot)$, so that $g(\hat A) \le g({A}^\star)$.
 	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id$ is at most one. 
-
-	Using \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows.
+	%With \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows. 
+	Using equation \eqref{same_hA}, we can obtain that
+	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
+	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$, and $v_i$, $1\le i \le t$, be the corresponding eigenvectors.
+Then we have $A^\star {A^\star}^\top =\sum_{i=1}^r v_i v_i^\top$, and
+	\begin{align}
+	h(\hat A)-h(A^\star) = n \sum_{i=1}^r \lambda_i - n\sum_{i=1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 &= n\sum_{i=1}^r \lambda_i\left(1 -  \| U^\top_{\hat A} v_i\|^2\right)-n\sum_{i=r+1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 \nonumber\\
+	&\ge  n(\lambda_r-\lambda_{r+1}) \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 , \label{bdd_A-A}
+	\end{align}
+	where we used $\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) = r- \sum_{i=1}^r  \| U^\top_{\hat A} v_i\|^2 =\sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2  $ in the last step.
+On the other hand, we have
+	\begin{align*}
+	\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2 & =\sum_{i=1}^t v_i^\top (A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})^2 v_i \\
+	& =\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) + \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2.
+	\end{align*}
+	Thus from \eqref{bdd_A-A}, we obtain that 
+	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}.$$
+	This completes the proof of Claim \ref{claim_opt_dist}.
+	\iffalse
 	We simplify equation \eqref{eq_mtl_output_layer} as
@@
 	Hence for large enough $p$, we obtain that Claim \ref{claim_opt_dist} holds.
-	The proof is complete.
+	\fi
 

### 2020-10-11 arxiv/proof_same_cov.tex
sec A

@@
 	\paragraph{Proof of Claim \ref{claim_pred_err}.}
-	We apply similar arguments from Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
+	%We apply similar arguments from Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
+	The proof is similar to the one for equation \eqref{eq_gA_err}. 
 	The prediction loss of hard parameter sharing for task $i$ is equal to
@@
 
-	\paragraph{Part 2:} The second part is the cross term, whose expectation over $\cE$ is zero. The concentration error is
+	\paragraph{Part 2:} The second part is the cross term, whose expectation over $\cE$ is zero. Using Corollary \ref{cor_calE}, the concentration error can be bounded as 
 	\begin{align*}
-		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}E_i}}
-		\le \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)} \cdot \bignorm{\Sigma^{1/2} E_i}.
+		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}E_i}} &= \bigabs{\inner{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}{\cal E}} \\
+		&\le n^{c}\sigma \cdot \bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}\\
+		&\le n^{c}\sigma \cdot\|\hat a_i\| \cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\| \cdot \| (Z^\top Z)^{-1} \|^{1/2} \\
+		&\lesssim n^{-1/2+c}\sigma \cdot\|\hat a_i\| \cdot \bignorm{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} \\
+		&\le n^{-1/2+c}\sigma^2  \cdot\|\hat a_i\|^2 + n^{-1/2+c} L(B^{\star} \hat{a}_i), 
 	\end{align*}
+	with high probability for any small constant $c>0$. Here in the third step we used 
+	\begin{align*}
+	\bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)} &=\|\hat a_i\|\cdot \left[ (B^{\star} \hat{a}_i - \beta_i)^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i) \right]^{1/2} \\
+	&\le \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2} \\
+	&= \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}
+	\end{align*}
+	because $X=Z\Sigma^{1/2}$.
+In the fourth step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\left\| (Z^\top Z)^{-1}\right\|$ by $\OO(n^{-1})$.
+In the last step we used AM-GM inequality.
+
+	\iffalse
 	Next, we use the fact that the spectral norm of $\cE$ is at most $\sigma \cdot p^{\e}$.
@@
 	\end{align*}
+	\fi
 
-	\paragraph{Part 3:} The final part is the square of $E_i$.
-One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\sigma^2 \norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
-	Next, we bound the concentration error.
-	Let $A = X (X^{\top} X)^{-1} \Sigma (X^{\top} X)^{-1} X^{\top}$.
-	We have that
+	\paragraph{Part 3:} The final part is $\|E_i\|^2$. We rewrite it as 
+	\begin{align}
+	\|\Sigma^{1/2}E_i\|^2 &= \left\|\sum_{j=1}^t \hat{a}_j \Sigma^{1/2}(X^{\top} X)^{-1} X^{\top} \epsilon^{(j)}\right\|^2 \nonumber\\
+	& = \sum_{1\le j , k \le t}\hat a_i(j) \hat a_i(k)  {\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}}.\label{E_i^2}
+	\end{align}
+	If $j\ne k$, using Corollary \ref{cor_calE} we obtain that 
+	\begin{align}
+	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} \right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
+	& =\sigma^2 \cdot \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
+	&  \le \sigma^2 \cdot p^{1/2} \cdot \bignorm{(Z^{\top} Z)^{-1}} \lesssim \sigma^2 \cdot n^{-1/2+c} \label{jnek}
+	\end{align}
+	with high probability for any small constant $c>0$. On the other hand, if $j=k$, we notice that 
+	$$\exarg{\epsilon^{(j)}}{{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} \epsilon^{(j)}}= \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right] .$$
+	Then using Corollary \ref{cor_calE}, we obtain that 
+	\begin{align}
+	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(j)}} -\sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right]\right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
+	& \lesssim \sigma^2 \cdot n^{-1/2+c} . \label{jeqk}
+	\end{align}
+	Plugging \eqref{jnek} and \eqref{jeqk} into \eqref{E_i^2}, we obtain that 
 	\begin{align*}
-		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 - \exarg{\cE}{\bignorm{\Sigma^{1/2} E_i}^2}}
-		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top} - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
+		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 -  \sigma^2 \|\hat a_i\|^2 \cdot\tr\left[\Sigma(X^\top X)^{-1}\right]} \lesssim  \sigma^2 \cdot n^{-1/2+c} \cdot \sum_{j,k}|\hat a_i(j)||\hat a_i(k)|\lesssim  n^{-1/2+c} \sigma^2 \cdot  \|\hat a_i\|^2.
 	\end{align*}
-	In the above equation, we note that the trace of $A$ is precisely the trace of $\Sigma (X^{\top} X)^{-1}$.
-	On the other hand, the concentration error of the spectral norm of $\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top}$ is at most $\sigma^2 \e $.
 
-	Combining the three parts together, we conclude the proof of Claim \ref{claim_pred_err}.
+%	One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\sigma^2 \norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
+%	Next, we bound the concentration error.
+%	Let $A = X (X^{\top} X)^{-1} \Sigma (X^{\top} X)^{-1} X^{\top}$.
+%	We have that
+%	\begin{align*}
+%		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 - \exarg{\cE}{\bignorm{\Sigma^{1/2} E_i}^2}}
+%		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top} - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
+%	\end{align*}
+%	In the above equation, we note that the trace of $A$ is precisely the trace of $\Sigma (X^{\top} X)^{-1}$.
+%	On the other hand, the concentration error of the spectral norm of $\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top}$ is at most $\sigma^2 \e $.
+
+	Finally, combining the three parts together, we conclude the proof of Claim \ref{claim_pred_err}.
 

### 2020-10-11 arxiv/tools.tex
fix missing ref
sec A

@@
-\section{Notations and Tools}\label{app_tool}
+\section{Tools}\label{app_tool}
 
@@
 \end{align}
-where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if all the moments of $ x_i$ and $ y_j$ exist in the sense of equation \eqref{assmAhigh2}, then we have stronger bounds
+where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have stronger bounds
 \begin{align}
@@
 
- Moreover, we can obtain the following concentration estimates for random noise satisfying \eqref{assmAhigh2}.
+ Moreover, we can obtain the following concentration estimates for random noise in the setting of Section \ref{sec_same}.
 
  \begin{corollary}\label{cor_calE}
- add corollary
+Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d.
+random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order.
+Then we have that
 

### 2020-10-11 arxiv/diff_cov.tex

@@
-\section{Bias and Variance Limits when Tasks have Different Sample Sizes and Covariate Shifts}\label{sec_diff}
+\section{Bias-variance Limits: Different Sample Sizes and Covariate Shifts}\label{sec_diff}
 
@@
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
+Suppose that $X^{(1)} = Z^{(1)}{\Sigma^{(1)}}^{1/2} \in \real^{n_1 \times p}$ and $X^{(2)} = Z^{(2)}{\Sigma^{(2)}}^{1/2} \in \real^{n_2 \times p}$, where every entry of $Z^{(1)}, Z^{(2)}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for $\varphi > 4$.
 
@@
 \begin{theorem}\label{thm_main_RMT}
-	Suppose that $X^{(1)} \in \real^{n_1 \times p}$ and $X^{(2)} \in \real^{n_2 \times p}$ are both random matrices that satisfy Assumption \ref{assume_rm}.
-	Assume that: a) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$; b) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
+	Let $c_{\varphi}$ be a fixed value in $(0, \frac{\varphi - 4}{2\varphi})$.
+	Assume that: a) $Z^{(1)}, Z^{(2)}$ both satisfy assumption \ref{assume_rm};
+	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
+	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
 	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
@@
 \end{theorem}
-Our result extends a well-known result on the inverse of a sample covariance matrix.
-In particular, when $X_1$ is zero, we obtain Fact \ref{fact_tr} as a corollary.
-To see this, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to the variance limit.
+Our result extends Fact \ref{fact_tr} on the inverse of a sample covariance matrix.
+When $X_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to the variance limit.
+
+\paragraph{How does hard parameter sharing scale with sample size and covariate shift?}
 One can see that both the variance limit and the bias limit depend heavily on both tasks' samples sizes and the covariate shift matrix $M$.
-Next, we illustrate how varying sample sizes and covariate shifts impact hard parameter sharing, respectively.
-
+Next, we illustrate how varying them impact prediction loss, respectively.
 \begin{example}[Sample ratio]\label{ex_sample_ratio}
@@
 $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
-Finally, we extend our result to general random matrices under the moment condition in Assumption \ref{assume_rm}.
+Finally, we extend our result to general random matrices under constant moment condition.
 We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.

### 2020-10-11 arxiv/diff_cov.tex
sec A

@@
 This is because $f(A, B)$ is in general non-convex.
-Our result implies tight generalization bounds for any local minimum of $f(A, B)$.
+Instead, our result implies tight generalization bounds for any \emph{local minimum} of $f(A, B)$.
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Suppose that $X^{(1)} = Z^{(1)}{\Sigma^{(1)}}^{1/2} \in \real^{n_1 \times p}$ and $X^{(2)} = Z^{(2)}{\Sigma^{(2)}}^{1/2} \in \real^{n_2 \times p}$, where every entry of $Z^{(1)}, Z^{(2)}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for $\varphi > 4$.
+Suppose that $X^{(1)} = Z^{(1)}{\Sigma^{(1)}}^{1/2} \in \real^{n_1 \times p}$ and $X^{(2)} = Z^{(2)}{\Sigma^{(2)}}^{1/2} \in \real^{n_2 \times p}$, where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+The matrices $\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
 
-Our key result characterizes the asymptotic limit of the sum of two arbitrarily different sample covariance matrices.
-To motivate our study, consider a special case where $A$ is equal to one.
+Our key result characterizes the asymptotic limit of the inverse of the sum of two different sample covariance matrices.
+Recall that in the hard parameter sharing, we have to take $r<t$.
+Hence in the two-task case, we must have $r=1$.
+To motivate our study, consider a special case where $A_1=A_2=1$. 
 Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
@@
 \begin{align}\label{def hatsig}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where } \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
+	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \ \ \text{ where } \ \ \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
 \end{align}
@@
 	\exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}} =
-	& \bignorm{(\Sigma^{(2)})^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
+	& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
 	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
@@
 Our main result in this section characterizes the asymptotic limit of the above equation, when both sample size and feature dimension become increasingly large at a fixed ratio.
-The main technical challenge of our result deals with the ``covariate shift'' between task one and two.
-Intuitively, the scaling of $\hat{\Sigma}^{-1}$ not only depends on both tasks' sample sizes, but also depends on their covariance matrices.
-We introduce a key quantity $M \define \Sigma_1^{1/2}\Sigma_2^{-1/2}$ that captures the covariate shift between task $1$ and task $2$.
-Let $U\Lambda V^\top$ denote the singular value decomposition of $M$, where $\Lambda\in\real^{p\times p}$ consists of $M$'s singular values $\lambda_1, \lambda_2, \dots, \lambda_p$ as its diagonal entries in descending order.
+The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
+Intuitively, the scaling of $\hat{\Sigma}^{-1}$ not only depends on both tasks' sample sizes, but also depends on their population covariance matrices.
+We introduce a key quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$ that captures the covariate shift between task one and task two.
+Let $U\Lambda V^\top$ denote the singular value decomposition of $M$, where $\Lambda\in\real^{n\times p}$ consists of $M$'s singular values $\lambda_1\ge \lambda_2\ge \dots \ge \lambda_p$ as its diagonal entries in descending order.
 Our main result is stated as follows.
@@
 	Let $c_{\varphi}$ be a fixed value in $(0, \frac{\varphi - 4}{2\varphi})$.
-	Assume that: a) $Z^{(1)}, Z^{(2)}$ both satisfy assumption \ref{assume_rm};
+	Assume that: a) $Z^{(1)}, Z^{(2)}$ both satisfy Assumption \ref{assume_rm};
 	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
 	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
+	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits.
 
-	\noindent (i) The variance equation \eqref{eq_variance_2task} satisfies the following limit
+	\noindent (i) The variance equation \eqref{eq_variance_2task} satisfies the following estimate with high probability:
 			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \lesssim p^{-c_{\varphi}}\norm{\Sigma^{(2)}},
+				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
 			\end{align}
@@
 			\end{align}
-	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit for any fixed vector $w\in\real^p$ with unit norm,
+	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed vector $w\in\real^p$ with unit norm,
 			\begin{align}\label{lem_cov_derv_eq}
-				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \lesssim p^{-c_{\varphi}},
+				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
 			\end{align}
@@
 			\begin{align}\label{eq_a34extra}
-				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
+				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \ 
 				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_1 a_4 - a_2 a_3)}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
@@
 \end{theorem}
-Our result extends Fact \ref{fact_tr} on the inverse of a sample covariance matrix.
-When $X_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to the variance limit.
+Our result extends Fact \ref{fact_tr} on the inverse of a single sample covariance matrix.
+When $n_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
 
@@
 	\[ \frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] = \frac{p}{(n_1 + n_2)(a_1 + a_2)} = \frac{p}{n_1 + n_2 - p}, \]
-	since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$.
-	Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} since we have obtained $a_1, a_2$.
+	since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$.
+	Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
 	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
@@
 %	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-	(iii) task-specific variance is much smaller than the shared signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$.
+	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\delta}{\kappa^2}$ for a small constant $\delta>0$.
 	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2).
+	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c } \cdot \OO(d^2 + \sigma^2).
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
@@
 	 \end{align}
+	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
 %	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
@@
 
-The above result provides a more concrete interpretation of the bias-variance decomposition, since the result depends explicitly on datasets' properties of interest.
+The above result provides a more concrete interpretation of the bias-variance decomposition, since it depends explicitly on datasets' properties of interest.
 The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, by combining the bias and variance limits, we can also obtain a generalization bound for any local minimum of $f(A, B)$.
+As a remark, in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $\hat A$ and $\hat B$.
+By combining the bias and variance limits, we can also obtain a generalization bound for any local minimizer of $f(A, B)$.
 The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
@@
 Next, we illustrate an interesting phenomenon where adding task one's samples helps task two initially, but hurts eventually.
-Consider the limiting estimate in the left hand side of equation \eqref{cor_MTL_error}.
+Consider the limiting estimate on the left hand side of equation \eqref{cor_MTL_error}.
 We vary sample ratio $n_1 / n_2$ by fixing $n_2$ and increasing $n_1$.
-As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
-We describe a proof sketch.
+As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
+We describe a sketch of the proof.
 \begin{enumerate}
@@
 	\item The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
-	\item Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the decrease in variance, and there is only one positive root for the derivative being zero.
+	\item Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one positive root for the derivative being zero.
 %Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:

### 2020-10-11 arxiv/diff_cov.tex
sec A

@@
 %In general, the covariance matrices of the two tasks may be different such as in text classification.
-Our second example studies the impact of varying covariate shifts on variance in the left hand side of equation \eqref{lem_cov_shift_eq}:
+Our second example studies the effect of varying covariate shifts on the variance limit in equation \eqref{lem_cov_shift_eq}:
+%in the left hand side of equation \eqref{lem_cov_shift_eq}:
 	\[ \bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} \rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
@@
 %As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance estimate is determined by the spectrum of $M$.
+Hence the variance limit is determined by the spectrum of $M$.
 
 To illustrate this result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
-Hence, when $\lambda = 1$, then there is no covariate shift.
+In particular, when $\lambda = 1$, there is no covariate shift.
 As $\lambda$ increases, the severity of covariate shift increases.
@@
 \begin{itemize}
-	\item If $n_1 \ge n_2$, then the variance estimate is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance estimate is largest when there is no covariate shift.
+	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
+	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
 \end{itemize}
@@
 \begin{align*}
-	\frac{p}{2(n_1 + n_2)} f(\lambda), \text{ where } f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
+	\frac{p}{2(n_1 + n_2)} f(\lambda), \ \ \text{ where }\ \  f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
 \end{align*}
-Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 - p}$, we have that
+Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 }$, we can obtain that
 \begin{align*}
-	f(\lambda) - f(1) &= {(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1})^{-1}
-	+ (\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-	&= (2a_1 - \frac{n_1 + n_2} {n_1 + n_2 - p}) g(\lambda, a_1),
+	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1}
+	+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
+	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)\cdot (\lambda^2-1)^2  g(\lambda, a_1),
 \end{align*}
-where $g(\lambda, a_1) > 0$ is a fixed function and can be derived from algebraic calculation (details omitted).
+where $g(\lambda, a_1) > 0$ is a fixed function and can be derived from algebraic calculations (details omitted).
 %Hence, whether or not $f(\lambda)$ is small than $f(1)$ depends on $a_1$.
-We show that $a_1 \ge \frac{n_1 + n_2}{2(n_1 + n_2 - p)}$ if and only if $n_1 \ge n_2$, thus explaining the dichonomy.
+We now show that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, and hence explain the dichonomy. 
+%In Example \ref{ex_covshift}, with the fact $M=M^{-1}$, we observe that $a_1$ and $a_2$ play a symmetric role. 
+%in the self-consistent equations \eqref{lem_cov_shift_eq}.
+In fact, if $a_1>a_2$, then the equations in \eqref{eq_a12extra} give that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and
+$$ 
+ \frac{n_1}{n_1 + n_2}=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} 
+> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) >\frac{1}{2}. 
+$$
+This implies $n_1>n_2$.
+Similarly, if $a_1<a_2$, equations in \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
+Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
 
-In Example \ref{ex_covshift}, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations \eqref{lem_cov_shift_eq}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
+\iffalse
+Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, which gives $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 }) = \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$.
 The other case when $n_1 < n_2$ is similar.
-A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
-If $n_1< n_2$, then $f(\lambda)< f(1)$.
+A formal proof follows from a study of the self-consistent equations \eqref{eq_a12extra} and we omit the details.
+Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.  If $n_1< n_2$, then $f(\lambda)< f(1)$.
+\fi
 %\begin{proposition}[Source/target sample ratio]\label{prop_data_size}

### 2020-10-11 arxiv/diff_cov.tex
sec A

@@
 			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
+				\bigabs{p^{-1}\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
 			\end{align}
@@
 For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
-The central quantify of interest is the inverse of the sample covariance matrices $\hat{\Sigma}^{-1}$.
+The central quantity of interest is the inverse of the sum of two sample covariance matrices $\hat{\Sigma}^{-1}$.
 Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
@@
 For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
-$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \text{ for any complex number } z\in \C\setminus [0,\infty).$$
-Hence the Stieltjes transform method reduces the study of a probability measure to the study of a complex function.
-To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
-Let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$, where $\delta_{\lambda_i}$ is the indicator measure, and $Y$ is defined as follows
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \ \ \text{ for any complex number } z\in \C\setminus [0,\infty).$$
+The Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
+%To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
+
+We define the matrix $W$ as follows
 \begin{align}\label{eigen2extra}
-	Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
+	W \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
 \end{align}
-Recall that $\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix, ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrix with isotropic covariance.
-It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= \Sigma_2^{-1/2} VY^{-1}V^\top \Sigma_2^{-1/2}$ and $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{Y^{-1}} / (n_1 + n_2)$.
-The Stieltjes transform of $\mu$ is as follows
- \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(Y-z\id)^{-1}\right]. \]
-Above, $(Y - z\id)^{-1}$ is known as $Y$'s resolvent matrix or Green's function.
+Recall that  $U\Lambda V^\top$ is the singular value decomposition of $M$, %$\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix, 
+and ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance.
+It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= (\Sigma^{(2)})^{-1/2} V W^{-1}V^\top (\Sigma^{(2)})^{-1/2}$ and $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$.
+Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$.
+Then it is easy to see that the Stieltjes transform of $\mu$ is equal to
+ \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(W-z\id)^{-1}\right]. \]
+Above, the matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
 %When $p$ goes to infinity, it is well-known that $m_{\mu}(z)$ converges to a fixed distribution governed by a set of self-consistent equations.
@@
 %Compared to the Stieltjes transform, the resolvent also applies to random matrices.
-We will prove the convergence of $Y$'s resolvent matrix using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
+We will prove the convergence of $W$'s resolvent using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
 %Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.
 \cite{Hachem2007deterministic,DS18}).
-We say that $(Y-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic matrices $B$ with uniformly bounded operator norms, when $p$ is large enough
-$$\bigtr{((Y-z\id)^{-1}-R(z))B}\to 0.$$
+We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm, 
+$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
+}$$
+
 %For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
@@
 
-To study $Y$'s resolvent, we observe that $Y$ is equal to $A A^{\top}$ for a $p$ by $n_1 + n_2$ matrix
-	\[ A = (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
+To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
+	\[ \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
 %}\HZ{what does this trick mean? use less technical words},
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Consider the following symmetric and square matrix whose dimension is $p + n_1 + n_2$
+Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
 %which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
@@
     H \define \left( {\begin{array}{*{20}c}
-   0 & A  \\
-   A^{\top} & 0
+   0 & \AF  \\
+   \AF^{\top} & 0
 %   {Z^{(2)}V} & 0 & 0
@@
  \end{equation}
-We denote $G(z) \define (H - z\id)^{-1}$ as the resolvent of $H$, for any complex value $z\in \mathbb C$.
-Since $H$ has a block structure, it is not hard to verify that
+For this block matrix, we define its resolvent as
+$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$ 
+%as the resolvent of $H$, 
+for any complex value $z\in \mathbb C$.
+Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
 	\begin{equation*} %\label{green2}
 	  G(z) =  \left( {\begin{array}{*{20}c}
-			(Y - z\id)^{-1} & (Y - z\id)^{-1} A  \\
-      A^\top (Y - z\id)^{-1} & (A^\top A - z\id)^{-1}
+			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
+      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
 		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
@@
 \paragraph{Variance asymptotic limit.}
-In Theorem \ref{LEM_SMALL}, we show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
+In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
 \be \label{defn_piw}
-	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix},\ee
+	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
 where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
-\begin{align}
-	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \nonumber\\
-	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}. \label{selfomega_a}
+\be
+\begin{split}\label{selfomega_a}
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}},  \\
+	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}. 
 % \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{align}
+\end{split}
+\ee
 The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
@@
 First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
-Second, since $Y^{-1}$ is the upper-left block matrix of $G(0)$, we have that $Y^{-1}$ converges to $(a_1\Lambda^2 + a_2\id)^{-1}$.
-Using equation \eqref{eigen2extra}, we have that when $p$ goes to infinity, % the trace of $$ converges to
-\[ \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} = \bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} = \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}. \]
+Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
+Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$, we get that when $p$ goes to infinity, % the trace of $$ converges to
+\begin{align*}
+  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
+  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}, 
+  \end{align*}
 %\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as

### 2020-10-11 arxiv/diff_cov.tex
sec 3

@@
 				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \ 
-				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_1 a_4 - a_2 a_3)}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
+				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
 %				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
@@
 \paragraph{Bias asymptotic limit.}
-For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(Y - z\id)^2$ with respect to $z$ at $z = 0$.
-First, we reduce the empirical bias term in equation \eqref{lem_cov_derv_eq} to $Y$
+For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
+First, we reduce the empirical bias term in equation \eqref{lem_cov_derv_eq} to $W$
 \begin{align}\label{calculate G'}
-	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V Y^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
+	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
 \end{align}
-Let $\cal G(z)$ denote the resolvent of $Y$.
-Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} = - \cal G^2(z)$.
-Hence, provided that limit of $(Y - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
+Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
+Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
+Hence, provided that limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
 \begin{align}\label{cal G'0}
-	\frac{\dd \cal G(0)}{\dd z} = \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
+	\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
 \end{align}
-For the derivative of $a_1(z)$ and $a_2(z)$, we take the derivative on both sides of equation \eqref{selfomega_a}.
+To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of equation \eqref{selfomega_a}.
 %\begin{align*}
@@
 One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations \eqref{eq_a34extra} (details omitted).
-Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain that the asymptotic limit of the bias term.
+Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
 %\begin{align}
@@
 
-As a remark, for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
-This is why we consider $Y$'s resolvent matrix as opposed to the Stieljes transform of its empirical spectral distribution.
+As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
+This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.
 
@@
 We briefly describe how to derive the matrix limit $\Gi(z)$.
-First, we consider the case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
-By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are both still multivariate Gaussian random matrices.
+First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
+By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
 Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
 We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equation \eqref{selfomega_a}.
-$G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
-Finally, we extend our result to general random matrices under constant moment condition.
+On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
+Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
 We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.

### 2020-10-11 arxiv/experiments.tex
fix missing ref
sec 3

@@
-\section{Numerical Results}
+\section{Numerical Results}\label{sec_exp}
 
@@
 	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
-	\caption{Validating Example \ref{ex_same_cov} in the same covariates case: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d$ and sample size $n$ settings.
+	\caption{Validating Example \ref{ex_same_cov} in the same covariates case: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
 The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
@@
 		\vspace{0pt}
-		\includegraphics[width=0.6\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
+		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
 		\caption{HPS vs. STL}
@@
 		\vspace{0pt}
-		\includegraphics[width=0.6\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
+		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
 		\caption{HPS vs. covariance alignment}

### 2020-10-12 arxiv/diff_cov.tex
sec 4

@@
 	(i) both tasks sample sizes are at least $\frac{3}{2}p$;
-	(ii) noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
+	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
 %	\be\label{choiceofpara0}
@@
 %As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit is determined by the spectrum of $M$.
+Hence the variance limit is determined by the spectrum of $M$. To be clear, for this example we assume that the bias is $0$.
 

### 2020-10-12 arxiv/experiments.tex
sec 4

@@
 	\caption{Validating Example \ref{ex_same_cov} in the same covariates case: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
+The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.
+\FY{What is $t$ in this setting?}}
 	\label{fig_same_cov}
@@
 We demonstrate the accuracy of our results via some empirical results.
-While our theory is asymptotic (with error terms that vanish when $p$ is sufficiently large), we observe that they are accurate in a modest dimension of $p = 200$.
+While our theory is asymptotic (with error terms that is negligible when $p$ is sufficiently large), we observe that they are accurate in a moderate dimension of $p = 200$.
 
@@
 First, we study the setting of Example \ref{ex_same_cov}.
-Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task sample from $400$ to $4000$.
-For all the parameter settings, our results estimate the empirical losses accurately.
+Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task   from $400$ to $2000$.
+In all the parameter settings, our results estimate the empirical losses accurately.
 We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
@@
 Finally, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires 3x fewer samples per-task than STL.
+\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
+For example, at the cross point, this ratio is 1.
+}
 
@@
 Again, our estimates are reasonably accurate compared to the empirical losses.
-We consider a regime where task two consists of $80,000$ samples, and task one's sample size vary from $8,000$ to $56,000$.
+We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
+The  task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is \FY{What is $\kappa^2$?}.
+We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.
+Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}.
+
+\iffalse
 We observe that as we increase the sample ratio, task two's prediction loss decreases initially but increases above the initial loss level.
@@
 %We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+\fi
 
@@
 Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts -- a higher $\lambda$ means more covariate shift.
+Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means more covariate shift.
 Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
@@
 Our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
-	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing.
-	Having covariate shifts increases task two's prediction loss when task two's sample size is larger than task one.
-Otherwise, having covariate shifts decreases task two's prediction loss (surprisingly).}
+	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
+	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one.
+Otherwise, having covariate shift decreases task two's prediction loss (surprisingly).}
 	\label{fig_model_shift_phasetrans}

### 2020-10-12 arxiv/diff_cov.tex
section 1.1 wip

--- 2020-10-11 arxiv/diff_cov.tex
@@
 			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{p^{-1}\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
+				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
 			\end{align}
@@
 We vary sample ratio $n_1 / n_2$ by fixing $n_2$ and increasing $n_1$.
-As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-We describe a sketch of the proof.
+%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
+%We describe a sketch of the proof.
+The variance term always reduces as $n_1$ increases.
+The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
 \begin{enumerate}
-	\item The variance term always reduces as $n_1$ increases.
-	\item The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
-	\item Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one positive root for the derivative being zero.
+	\item When $\frac{2d^2}{d^2 + \sigma^2} > \frac{p}{n_2 - p}$, the prediction loss decreases monotonically as $n_1$ increases.
+	\item When $\frac{2d^2}{d^2 + \sigma^2} < \frac{p}{n_2 - p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
+	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one positive root for the derivative being zero.
 %Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
@@
 For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
-The central quantity of interest is the inverse of the sum of two sample covariance matrices $\hat{\Sigma}^{-1}$.
+The central quantify of interest is the inverse of the sample covariance matrices $\hat{\Sigma}^{-1}$.
 Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
@@
 For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
-$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \ \ \text{ for any complex number } z\in \C\setminus [0,\infty).$$
-The Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
-%To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
-
-We define the matrix $W$ as follows
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \text{ for any complex number } z\in \C\setminus [0,\infty).$$
+Hence the Stieltjes transform method reduces the study of a probability measure to the study of a complex function.
+To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
+Let $\mu=p^{-1}\sum_{i} \delta_{\lambda_i}$ denote the empirical spectral distribution of $Y$, where $\delta_{\lambda_i}$ is the indicator measure, and $Y$ is defined as follows
 \begin{align}\label{eigen2extra}
-	W \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
+	Y \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
 \end{align}
-Recall that  $U\Lambda V^\top$ is the singular value decomposition of $M$, %$\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix, 
-and ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance.
-It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= (\Sigma^{(2)})^{-1/2} V W^{-1}V^\top (\Sigma^{(2)})^{-1/2}$ and $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$.
-Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$.
-Then it is easy to see that the Stieltjes transform of $\mu$ is equal to
- \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(W-z\id)^{-1}\right]. \]
-Above, the matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
+Recall that $\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix, ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrix with isotropic covariance.
+It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= \Sigma_2^{-1/2} VY^{-1}V^\top \Sigma_2^{-1/2}$ and $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{Y^{-1}} / (n_1 + n_2)$.
+The Stieltjes transform of $\mu$ is as follows
+ \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(Y-z\id)^{-1}\right]. \]
+Above, $(Y - z\id)^{-1}$ is known as $Y$'s resolvent matrix or Green's function.
 %When $p$ goes to infinity, it is well-known that $m_{\mu}(z)$ converges to a fixed distribution governed by a set of self-consistent equations.
@@
 %Compared to the Stieltjes transform, the resolvent also applies to random matrices.
-We will prove the convergence of $W$'s resolvent using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
+We will prove the convergence of $Y$'s resolvent matrix using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
 %Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.
 \cite{Hachem2007deterministic,DS18}).
-We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm, 
-$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
-}$$
-
+We say that $(Y-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic matrices $B$ with uniformly bounded operator norms, when $p$ is large enough
+$$\bigtr{((Y-z\id)^{-1}-R(z))B}\to 0.$$
 %For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
@@
 
-To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
-	\[ \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
+To study $Y$'s resolvent, we observe that $Y$ is equal to $A A^{\top}$ for a $p$ by $n_1 + n_2$ matrix
+	\[ A = (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
 %}\HZ{what does this trick mean? use less technical words},
 %This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
+Consider the following symmetric and square matrix whose dimension is $p + n_1 + n_2$
 %which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
@@
     H \define \left( {\begin{array}{*{20}c}
-   0 & \AF  \\
-   \AF^{\top} & 0
+   0 & A  \\
+   A^{\top} & 0
 %   {Z^{(2)}V} & 0 & 0
@@
  \end{equation}
-For this block matrix, we define its resolvent as
-$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$ 
-%as the resolvent of $H$, 
-for any complex value $z\in \mathbb C$.
-Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
+We denote $G(z) \define (H - z\id)^{-1}$ as the resolvent of $H$, for any complex value $z\in \mathbb C$.
+Since $H$ has a block structure, it is not hard to verify that
 	\begin{equation*} %\label{green2}
 	  G(z) =  \left( {\begin{array}{*{20}c}
-			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
-      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
+			(Y - z\id)^{-1} & (Y - z\id)^{-1} A  \\
+      A^\top (Y - z\id)^{-1} & (A^\top A - z\id)^{-1}
 		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
@@
 \paragraph{Variance asymptotic limit.}
-In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
+In Theorem \ref{LEM_SMALL}, we show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
 \be \label{defn_piw}
-	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
+	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id)^{-1} & 0 & 0 \\ 0 & - \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & -\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix},\ee
 where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
-\be
-\begin{split}\label{selfomega_a}
-	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}},  \\
-	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}. 
+\begin{align}
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \nonumber\\
+	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}. \label{selfomega_a}
 % \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{split}
-\ee
+\end{align}
 The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
@@
 First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
-Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
-Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$, we get that when $p$ goes to infinity, % the trace of $$ converges to
-\begin{align*}
-  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
-  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}, 
-  \end{align*}
+Second, since $Y^{-1}$ is the upper-left block matrix of $G(0)$, we have that $Y^{-1}$ converges to $(a_1\Lambda^2 + a_2\id)^{-1}$.
+Using equation \eqref{eigen2extra}, we have that when $p$ goes to infinity, % the trace of $$ converges to
+\[ \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} = \bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} = \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}. \]
 %\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as

### 2020-10-12 arxiv/setup.tex
section 1.1 wip

@@
 
-Suppose we have $t$ labeled regression tasks. %where $t$ is a fixed value that does not grow with the feature dimension $p$.
-For each task $k$ from $1$ to $t$, we have $n_k$ samples $x_1, x_2, \dots, x_{n_k}$ that are all $p$-dimensional feature vectors with real-valued labels $y_1, y_2, \dots, y_{n_k}$.
-Without loss of generality, we focus on predicting the $t$-th task and refer the $t$-th task as the target.
-We refer to task $1$ to task $t-1$ as source tasks.
-We assume that the labels of each task $k$ satisfy the linear model with unknown parameters $\beta_k\in\real^p$, that is,
-	\[ y_i = x_i^{\top}\beta_k + e_i, \text{ for all } 1 \le i \le n_k, \]
-where $e_i$ denotes random noise with mean zero and variance $\sigma^2$.
-To write the above notations more succiently, let $X_k \in \real^{n_k \times p}$ denote the covariates that consists of a feature vector in every row.
-Let
-	\be\label{model_YvsX} Y^{(k)} = X^{(k)} \beta_k + \varepsilon_k, \text{ for all } 1\le k \le t \ee denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d.
+%Suppose we have $t$ labeled regression tasks. %where $t$ is a fixed value that does not grow with the feature dimension $p$.
+%For each task $k$ from $1$ to $t$, we have $n_k$ samples $x_1, x_2, \dots, x_{n_k}$ that are all $p$-dimensional feature vectors with real-valued labels $y_1, y_2, \dots, y_{n_k}$.
+%Without loss of generality, we focus on predicting the $t$-th task and refer the $t$-th task as the target.
+%We refer to task $1$ to task $t-1$ as source tasks.
+%We assume that the labels of each task $k$ satisfy the linear model with unknown parameters $\beta_k\in\real^p$, that is,
+%	\[ y_i = x_i^{\top}\beta_k + e_i, \text{ for all } 1 \le i \le n_k, \]
+%where $e_i$ denotes random noise with mean zero and variance $\sigma^2$.
+%To write the above notations more succiently, let $X_k \in \real^{n_k \times p}$ denote the covariates that consists of a feature vector in every row.
+%Let
+%	\be\label{model_YvsX} Y^{(k)} = X^{(k)} \beta_k + \varepsilon_k, \text{ for all } 1\le k \le t \ee denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d.
 random vector with mean zero and variance $\sigma^2$.
-
-Following \citet{HMRT19} and \citet{BLLT20},
+%Following \citet{HMRT19} and \citet{BLLT20},
 %In the high-dimensional linear regression setting (e.g.
 ), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
-we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$ for $i = 1, \dots, n_k$, where $z_i\in\real^p$ is an i.i.d.
+%we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$ for $i = 1, \dots, n_k$, where $z_i\in\real^p$ is an i.i.d.
 random vector with  mean zero and unit variance.
-Recall that $\Sigma_k$ is the population covariance matrix task $k$'s feature vectors.
-Let $\Sigma_k = U_k D_k U_k^{\top}$ denote the singular value decomposition of $\Sigma_k$.
-We denote $\Sigma_k = U_k D_k^{1/2}$ as the square root of $\Sigma_k$.
-The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$ that does not grow with feature dimension $p$.
-This setting is also known as the high-dimensional linear regression setting in the literature.
-There are two motivations for studying the high-dimensional linear regression setting for multi-task learning.
-First, this setting captures salient properties of modern large-scale datasets, where the sample sizes are usually on the order of tens to hundreds of the number of features \cite{sur2019modern}.
-Second, as we will see soon in Section \ref{sec_general}, we can derive precise asymptotics of the generalization error that scale with properties of the task data such as sample sizes.
+%Recall that $\Sigma_k$ is the population covariance matrix task $k$'s feature vectors.
+%Let $\Sigma_k = U_k D_k U_k^{\top}$ denote the singular value decomposition of $\Sigma_k$.
+%We denote $\Sigma_k = U_k D_k^{1/2}$ as the square root of $\Sigma_k$.
+%The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$ that does not grow with feature dimension $p$.
+%This setting is also known as the high-dimensional linear regression setting in the literature.
+%There are two motivations for studying the high-dimensional linear regression setting for multi-task learning.
+%First, this setting captures salient properties of modern large-scale datasets, where the sample sizes are usually on the order of tens to hundreds of the number of features \cite{sur2019modern}.
+%Second, as we will see soon in Section \ref{sec_general}, we can derive precise asymptotics of the generalization error that scale with properties of the task data such as sample sizes.
 %The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
@@
 
-\paragraph{Hard parameter sharing estimators.}
-We study multi-task learning models that use hard parameter sharing, which is the most commonly used architecture in practice \cite{R17}.
-Specifically, we consider a two-layer neural network with a shared layer $B\in\real^{p\times r}$ for all tasks and $t$ output layers $W_1, \dots, W_t$ for every task from $1$ to $t$, where each output layer is a $r$-dimensional vector.
-The width of $B$, denoted by $r$, plays an important role in regularization.
-As observed in Proposition 1 of \citet{WZR20}, if $r \ge t$, there is no regularization effect.
-Hence, we assume that $r < t$ in our study.
+Regression analysis is arguably one of the most fundamental methods in statistics and machine learning.
+In many applications of multi-task learning, the amount of labeled data from each dataset is usually insufficient for learning a single task.
+For example, this is the case if a dataset's sample size is only a small constant times the dimension of the feature vectors \cite{GLUE}.
+In this paper, we consider multi-task learning in a high-dimensional linear regression setting.
+We assume that there are multiple datasets that all follow a (potentially different) linear model.
+In each dataset, we assume the feature vector $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with mean zero, unit variance, and covariance $\Sigma \in\real^{p \times p}$ that is deterministic and positive semidefinite.
+We are mainly interested in the \textit{high-dimensional} setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
+This setting is particularly challenging, but is crucial for understanding how datasets' properties such as their sample sizes impact generalization performance.
+
+We study a hard parameter sharing architecture to learn jointly from multiple datasets.
+In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks, and a task-specific output layer $A_i \in \real^r$ for every task $i$ to $t$.
+Suppose we have $t$ datasets.
+For each task $i = 1, 2, \dots, t$, let $n_i$ denote its sample size, $X^{(i)} \in \real^{n_i \times p}$ denote its feature covariates, and $Y^{(i)} \in \real^{n_i}$ denote all the labels.
+%The width of $B$, denoted by $r$, plays an important role in regularization.
+%As observed in Proposition 1 of \citet{WZR20}, if $r \ge t$, there is no regularization effect.
+%Hence, we assume that $r < t$ in our study.
 %For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following procedure inspired by how hard parameter sharing models are trained in practice.
-\begin{enumerate}
+Let $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
+We study the following optimization objective.
 %	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
 %	The size of each set is described below.
-	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-		{\begin{align}\label{eq_mtl}
-			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2.
-		\end{align}}
-	\item Learn the output layers $W_1, W_2, \dots, W_t$: set $B = \hat{B}$ and minimize the training loss over $W_1, W_2, \dots, W_t$.
-		{\begin{align}\label{eq_mtl_eval}
-			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k \hat{B} W_k - Y_k}^2.
-		\end{align}}
-\end{enumerate}
-Let $\hat{\beta}_t^{\MTL}$ denote the multi-task learning estimator obtained from the procedure above.
-By contrast, let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$ denote the single-task learning estimator. % denoted by $L(\hat{\beta}_t^{\STL})$.
+%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
+\begin{align}\label{eq_mtl}
+			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2.
+\end{align}
+Given a solution $\hat{A}, \hat{B}$ from the above optimization, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the hard parameter sharing (HPS) estimator for task $i$.
+The important questions here are:
+(i) how well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
+(ii) for datasets with different sample sizes and covariate shifts, how do they impact the estimator?
+
+%	\item Learn the output layers $W_1, W_2, \dots, W_t$: set $B = \hat{B}$ and minimize the training loss over $W_1, W_2, \dots, W_t$.
+%		{\begin{align}\label{eq_mtl_eval}
+%			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k \hat{B} W_k - Y_k}^2.
+%		\end{align}}
+%\end{enumerate}
+%Let $\hat{\beta}_t^{\MTL}$ denote the multi-task learning estimator obtained from the procedure above.
+%By contrast, let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$ denote the single-task learning estimator. % denoted by $L(\hat{\beta}_t^{\STL})$.
 %where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
 %Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
-
-\smallskip
-\noindent\textit{Remark.}
-In general, the multi-task learning objective $f(\cdot)$ is non-convex with respect to $B$ and $W_1, \dots, W_t$.
-Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
-For our results later in Section \ref{sec_general} and \ref{sec_special}, we will identify tractable cases and provide guarantees to the above procedure.
-
-\paragraph{Problem statement.}
+%\smallskip
+%\noindent\textit{Remark.}
+%In general, the multi-task learning objective $f(\cdot)$ is non-convex with respect to $B$ and $W_1, \dots, W_t$.
+%Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
+%For our results later in Section \ref{sec_general} and \ref{sec_special}, we will identify tractable cases and provide guarantees to the above procedure.
+%\paragraph{Problem statement.}
 %We focus on predicting a particular task, say the $t$-th task, without loss of generality.
-For an estimator $\hat{\beta}$ of the target task model $\beta_t$, we define the prediction loss of the estimator $\hat{\beta}$ as
-	{\begin{align}\label{eq1_prediction_loss}
-		\te(\hat{\beta}) = \exarg{x = \Sigma_t^{1/2} z}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
-		= \bignorm{\Sigma_t^{1/2} (\hat{\beta} - \beta_t)}^2,
-	\end{align}}%
-where $x = \Sigma_t^{1/2} z$ denotes a random feature vector with covariance $\Sigma_t$.
-In the above equation, $x^{\top}\beta_t$ is the true label of $x$.
+%For an estimator $\hat{\beta}$ of the target task model $\beta_t$, we define the prediction loss of the estimator $\hat{\beta}$ as
+%	{\begin{align}\label{eq1_prediction_loss}
+%		\te(\hat{\beta}) = \exarg{x = \Sigma_t^{1/2} z}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
+%		= \bignorm{\Sigma_t^{1/2} (\hat{\beta} - \beta_t)}^2,
+%	\end{align}}%
+%where $x = \Sigma_t^{1/2} z$ denotes a random feature vector with covariance $\Sigma_t$.
+%In the above equation, $x^{\top}\beta_t$ is the true label of $x$.
 %= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)
-We say that the source tasks provide a \textit{positive transfer} to the target task if the prediction loss of the MTL estimator is lower than that of the STL estimator, that is, if
-	\[ L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL}). \]
-On the other hand, we say that the source tasks provide a \textit{negative transfer} to the target task if $L(\hat{\beta}_t^{\MTL}) < L(\hat{\beta}_t^{\STL})$.
-Our goal is to study when the source tasks provide a positive transfer to the target task.
-More specifically, we study how varying properties of task data including task similarity, sample ratio, and covariate shift affects information transfer in multi-task learning.
+%We say that the source tasks provide a \textit{positive transfer} to the target task if the prediction loss of the MTL estimator is lower than that of the STL estimator, that is, if
+%	\[ L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL}). \]
+%On the other hand, we say that the source tasks provide a \textit{negative transfer} to the target task if $L(\hat{\beta}_t^{\MTL}) < L(\hat{\beta}_t^{\STL})$.
+%Our goal is to study when the source tasks provide a positive transfer to the target task.
+%More specifically, we study how varying properties of task data including task similarity, sample ratio, and covariate shift affects information transfer in multi-task learning.
 
@@
 
-\textbf{Main results.} First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
+%In the worst case, the optimization objective \eqref{eq_mtl} is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
+%Therefore, we work in cases where a global and/or local minimum characterization is possible
+
+\paragraph{Main results.}
+Our first result (Theorem \ref{thm_many_tasks}) applies to the multi-label prediction setting where all datasets have the same features, and we want to make multiple predictions (e.g.
+\cite{hsu2009multi}).
+We analyze the global minimum of $f(A, B)$, and provide a sharp generalization bound for its (out-of-sample) prediction loss for any task.
+This is a tractable special case of the general problem because in the worst case, $f(A, B)$ is non-convex in $A$ and $B$ (e.g.
+matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
+We show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition.
+Our results imply that hard parameter sharing helps by reducing variance compared to single-task learning, but hurts by increasing bias.
+Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample sizes and covariance matrices.
+We analyze the local minimum of $f(A, B)$, and provide a sharp generalization bound for its prediction loss for both tasks.
+Despite its simplicity, we show several rich phenomena by varying sample sizes and covariate shifts in this setting.
+See Figure \ref{fig_intro_sample_size} for an illustration.
+
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.65\textwidth]{figures/mtl_model.pdf}
+		\caption{A hard parameter sharing architecture}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_several_d.eps}
+		\caption{Different patterns of varying sample sizes}
+	\end{subfigure}
+	\caption{We observe that task two's prediction loss decreases initially before increasing again.
+Our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
+\HZ{rewrite}}
+	\label{fig_intro_sample_size}
+\end{figure}
+
+As a consequence of our concrete and precise loss estimates, we make qualititative predictions that are related to commonly observed empirical phenomena in hard parameter sharing.
+\begin{enumerate}
+	\item \textit{Sample efficiency depends on task-specific variance vs. noise variance}:
+	\item \textit{Increasing one task's sample size does not always reduce another task's loss}:
+	\item \textit{Covariate shift worsens when sample size ratio increases}:
+\end{enumerate}
+Second, we propose a new multi-task training schedule by incrementally adding task data batches to the training procedure.
+This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
+Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis datasets while keeping the accuracy the same.
+
+%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
+%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
+%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
+%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
+%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
+%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
+%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
 %For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
@@
 
-Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
+%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
 %We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
@@
 %Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-\squishlist
-	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-	As model distance increases, the bias becomes larger, resulting in negative transfer.
+%\squishlist
+%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
+%	As model distance increases, the bias becomes larger, resulting in negative transfer.
 %	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
@@
 %	We discuss these in Section \ref{sec_insight}.
-	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
+%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
+%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
 	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
 	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-	Otherwise, the variance reduces less with covariate shift.
+%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
+%	Otherwise, the variance reduces less with covariate shift.
 %	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-\squishend
+%\squishend
 %In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
@@
 %We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
+%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
 %We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
@@
 
-Our study also leads to several algorithmic consequences with practical interest.
-First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-Second, we propose a new multi-task training schedule by incrementally adding task data batches to the training procedure.
-This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
-Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis datasets while keeping the accuracy the same.
-Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-Finally, we validate our three theoretical findings on sentiment analysis tasks.
+%Our study also leads to several algorithmic consequences with practical interest.
+%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
+%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
 
-We describe the main ideas for showing the generalization error of hard parameter sharing estimators.
+%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
+%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
+%Finally, we validate our three theoretical findings on sentiment analysis tasks.
+
+\paragraph{Our techniques.} \todo{rewrite} We describe the main ideas for showing the generalization error of hard parameter sharing estimators.
 There are two key ideas in the proof.
@@
 Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
+
+For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+Let $\lambda_1(X) \ge \lambda_2(X) \ge \cdots \ge \lambda_t(X)$ denote the eigenvalues of $X$.
+Let $X^+$ denote its Moore-Penrose psuedoinverse.
+We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
 We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
 We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)$ goes to $1$ as $p$ goes to infinity.
-%, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
-For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
-Let $X^+$ denote its Moore-Penrose psuedoinverse.
-We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.

### 2020-10-12 arxiv/setup.tex
add fig 1

@@
 
-As a consequence of our concrete and precise loss estimates, we make qualititative predictions that are related to commonly observed empirical phenomena in hard parameter sharing.
+As a consequence of our concrete and precise loss estimates, we observe qualitative properties of hard parameter sharing for varying datasets' properties.
 \begin{enumerate}
-	\item \textit{Sample efficiency depends on task-specific variance vs. noise variance}:
-	\item \textit{Increasing one task's sample size does not always reduce another task's loss}:
-	\item \textit{Covariate shift worsens when sample size ratio increases}:
+	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
+	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that is empirically observed in Taskonomy \cite{ZSSGM18}.
+	Our results further show that HPS's sample efficiency depends on task-specific variance vs.
+noise variance.
+It is generally high when the noise variance is large compared to model-specific variance across tasks.
+	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help reduce another task's loss.
+We find in a simplified setting that the task loss either decreases first before increasing afterwards, or decreases monotinically.
+These two trends result from different tradeoffs between increasing bias and decreasing variance.
+	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
+For high sample size ratio, variance is smallest when there is no covariate shift.
+Counterintuitively, for low sample size ratio, having covariate shift reduces variance through a complementary spectrum.
 \end{enumerate}
+One natural implication from these results is that adding more data
 Second, we propose a new multi-task training schedule by incrementally adding task data batches to the training procedure.
-This is inspired by our observation in Figure \ref{fig_size} where adding more source task data helps initially, but hurts eventually.
+This is inspired by our observation in Figure \ref{fig_size} where .
 Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis datasets while keeping the accuracy the same.

### 2020-10-12 arxiv/experiments.tex
section 1.1 wip
finish section 1.1

@@
 	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
-	\caption{Validating Example \ref{ex_same_cov} in the same covariates case: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.
-\FY{What is $t$ in this setting?}}
+	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
+The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
 	\label{fig_same_cov}
@@
 We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
-The  task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is \FY{What is $\kappa^2$?}.
+The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is $1$.
 We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.
-Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}.
+On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases monotonically.
+Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}. \HZ{check}
 
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_c2_400.eps}
+		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_several_d.eps}
 		\caption{Example \ref{ex_sample_ratio}}
@@
 	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in the different covariates case:
+	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in Section \ref{sec_diff} for two tasks:
 	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
-	In Figure \ref{fig_size}, we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
-	We observe that task two's prediction loss decreases initially before increasing again.
-Our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
+	In Figure \ref{fig_size}, we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
 	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
 	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one.
-Otherwise, having covariate shift decreases task two's prediction loss (surprisingly).}
+Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
 	\label{fig_model_shift_phasetrans}
@@
 
-\paragraph{Sample ratio.}
+\paragraph{Sample size ratio.}
 In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.

### 2020-10-12 arxiv/setup.tex

@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_several_d.eps}
-		\caption{Different patterns of varying sample sizes}
+		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_c2_400.eps}
+		\caption{Varying sample size ratio}
+		\label{fig_intro_sample_size}
 	\end{subfigure}
-	\caption{We observe that task two's prediction loss decreases initially before increasing again.
-Our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
-\HZ{rewrite}}
+	\caption{An illustrative example of our result:
+	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
+	Increasing task one's sample size helps reduce task two's prediction loss initially, but increases afterwards.
+Our result provides an estimated loss (solid line) that matches the empirical loss (dotted line) accurately.
+This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
+	See Section \ref{sec_simulation} for the precise setting.}
 	\label{fig_intro_sample_size}
@@
 	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help reduce another task's loss.
-We find in a simplified setting that the task loss either decreases first before increasing afterwards, or decreases monotinically.
+We find in a simplified setting that depending on how much bias increases, the task loss either decreases first before increasing afterwards, or decreases monotinically.
 These two trends result from different tradeoffs between increasing bias and decreasing variance.
@@
 \end{enumerate}
-One natural implication from these results is that adding more data
-Second, we propose a new multi-task training schedule by incrementally adding task data batches to the training procedure.
-This is inspired by our observation in Figure \ref{fig_size} where .
-Using our incremental training schedule, we reduce the computational cost by $65\%$ compared to baseline multi-task training over six sentiment analysis datasets while keeping the accuracy the same.
 
@@
 
-\paragraph{Our techniques.} \todo{rewrite} We describe the main ideas for showing the generalization error of hard parameter sharing estimators.
-There are two key ideas in the proof.
-First, we study a bias-variance decomposition of hard parameter sharing, and show that the variance always reduces compared to single-task learning, while the bias always increases.
-Second, we study the limiting bias and variance of hard parameter sharing, and derive their asymptotics using recent development from the random matrix theory literature.
-The asymptotic results scale with key properties of task data such as sample size and covariance shift, and allow us to study the performance of multi-task learning by varying these properties, which will be the focus of Section \ref{sec_special}.
+There are two main ideas in our analysis. The proof of our first result is based on a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
+We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and their population version.
+The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
+\HZ{add several sentences on the technical insight}
+One limitation of our analysis is that for two tasks with different sample sizes, there is extra error term in the prediction loss of hard parameter sharing (cf.
+equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
+\HZ{add why this is challenging}
+
+Finally, we discuss the practical implications of work.
+One natural implication from our sample size ratio study is a progressive training procedure that gradually adds more data until performance drops.
+For example, in the setting of Figure \ref{fig_intro_sample_size}, this procedure will stop right at the minimum of the local basin.
+We conduct further studies of this procedure on six text classification datasets, and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure, while keeping average accuracy of all tasks at the same level.
 
@@
 \paragraph{Notations.}
-Let $B^\star \define [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
-Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-Let $Y$ denote $[Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$.
-We can also write $Y = XB^{\star} + \cE$.
-Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-
+%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
+%We can also write $Y = XB^{\star} + \cE$.
+%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
 For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
@@
 We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
-We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)$ goes to $1$ as $p$ goes to infinity.
+We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
+%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.

### 2020-10-12 arxiv/experiments.tex
revise
fix grammar

@@
 Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires 3x fewer samples per-task than STL.
-\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
+Finally, for $d = 0.2$, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires fewer samples per-task than STL.
+%\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
 For example, at the cross point, this ratio is 1.

### 2020-10-12 arxiv/setup.tex
fix grammar

@@
 Regression analysis is arguably one of the most fundamental methods in statistics and machine learning.
-In many applications of multi-task learning, the amount of labeled data from each dataset is usually insufficient for learning a single task.
-For example, this is the case if a dataset's sample size is only a small constant times the dimension of the feature vectors \cite{GLUE}.
+In many multi-task learning applications, the amount of labeled data from each dataset is usually insufficient for learning a single task.
+For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension \cite{GLUE}.
 In this paper, we consider multi-task learning in a high-dimensional linear regression setting.
 We assume that there are multiple datasets that all follow a (potentially different) linear model.
-In each dataset, we assume the feature vector $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with mean zero, unit variance, and covariance $\Sigma \in\real^{p \times p}$ that is deterministic and positive semidefinite.
+In each dataset, suppose the feature vector $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with mean zero, unit variance, and covariance $\Sigma \in\real^{p \times p}$ that is deterministic and positive semidefinite.
 We are mainly interested in the \textit{high-dimensional} setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
-This setting is particularly challenging, but is crucial for understanding how datasets' properties such as their sample sizes impact generalization performance.
+This setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
 
 We study a hard parameter sharing architecture to learn jointly from multiple datasets.
-In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks, and a task-specific output layer $A_i \in \real^r$ for every task $i$ to $t$.
+In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a task-specific output layer $A_i \in \real^r$ for every task $i$ to $t$.
 Suppose we have $t$ datasets.
@@
 Given a solution $\hat{A}, \hat{B}$ from the above optimization, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the hard parameter sharing (HPS) estimator for task $i$.
-The important questions here are:
+The critical questions here are:
 (i) how well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
@@
 We analyze the global minimum of $f(A, B)$, and provide a sharp generalization bound for its (out-of-sample) prediction loss for any task.
-This is a tractable special case of the general problem because in the worst case, $f(A, B)$ is non-convex in $A$ and $B$ (e.g.
-matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
+This case is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
 We show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition.
@@
 Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample sizes and covariance matrices.
-We analyze the local minimum of $f(A, B)$, and provide a sharp generalization bound for its prediction loss for both tasks.
+We analyze the local minimum of $f(A, B)$ and provide a sharp generalization bound for both tasks' prediction loss.
 Despite its simplicity, we show several rich phenomena by varying sample sizes and covariate shifts in this setting.
@@
 		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size}
+		\label{fig_intro_sample_size_b}
 	\end{subfigure}
@@
 	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
-	Increasing task one's sample size helps reduce task two's prediction loss initially, but increases afterwards.
-Our result provides an estimated loss (solid line) that matches the empirical loss (dotted line) accurately.
+	Increasing task one's sample size helps reduce task two's prediction loss initially, but increases afterward.
+Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
 This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
@@
 
-As a consequence of our concrete and precise loss estimates, we observe qualitative properties of hard parameter sharing for varying datasets' properties.
+Consequently, we observe qualitative properties of hard parameter sharing for varying datasets' properties using our precise loss estimates.
 \begin{enumerate}
 	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that is empirically observed in Taskonomy \cite{ZSSGM18}.
+	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that \citet{ZSSGM18} has observed empirically observed.
 	Our results further show that HPS's sample efficiency depends on task-specific variance vs.
@@
 	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help reduce another task's loss.
-We find in a simplified setting that depending on how much bias increases, the task loss either decreases first before increasing afterwards, or decreases monotinically.
+In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how much bias increases.
 These two trends result from different tradeoffs between increasing bias and decreasing variance.
 	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
-For high sample size ratio, variance is smallest when there is no covariate shift.
-Counterintuitively, for low sample size ratio, having covariate shift reduces variance through a complementary spectrum.
+For a high sample size ratio, HPS's  variance is smallest when there is no covariate shift.
+Counterintuitively, for a low sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
 \end{enumerate}
@@
 
-There are two main ideas in our analysis. The proof of our first result is based on a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
+There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
 We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and their population version.
@@
 Finally, we discuss the practical implications of work.
-One natural implication from our sample size ratio study is a progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets, and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure, while keeping average accuracy of all tasks at the same level.
+Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
+For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
+We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
 

### 2020-10-12 arxiv/conclusions.tex
sec 6

@@
 We describe several open questions for future work.
-First, our bound in Corollary \eqref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
 Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two random matrices $Z^{(1)}, Z^{(2)}$ with isotropic covariances.
-This might require new techniques beyond \HZ{to add}.
+This requires studying the asymptotic distribution of the singular values of $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)} + 1$, which is still an open problem in random matrix theory.
+We remark that the eigenvalues distribution of this matrix have been studied in the name of Fisher matrices \cite{Fmatrix}, but its singular values will follow a different distribution since the matrix is not symmetric.
+ %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
 Second, it would be interesting to extend our results to classification problems.

### 2020-10-12 arxiv/intro.tex
fix comments in section 2
section 1.1 wip
polish writing

@@
 \begin{abstract}
-	Hard parameter sharing is a widely used approach to learn from multiple tasks in many applications, such as text classification.
-The idea is that all tasks share the same feature layer, while each task uses a specific output layer for prediction.
-Intuitively, the performance of hard parameter sharing depends on dataset properties such as their sample sizes.
-Yet, rigorously formulating such intuition can be technically challenging.
-This paper analyzes the generalization performance of hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio.
+	Hard parameter sharing is a widely used approach to learn jointly from multiple tasks in many applications, such as text classification.
+The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making prediction.
+It becomes increasingly important to understand when they work well on typical data.
+For example, the performance of hard parameter sharing depends on dataset properties such as their sample sizes.
+Yet, rigorously formulating such intuition can be challenging.
+
+	This paper analyzes hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio.
 We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample sizes and covariance matrices.
-We also demonstrate that these estimates for the empirical loss of hard parameter sharing are incredibly accurate in modest dimensions.
-Finally, we explain several intriguing empirical phenomena.
+We also demonstrate that these estimates for the empirical loss are incredibly accurate in modest dimensions.
+Finally, our results provide new explainanations to several intriguing empirical phenomena.
 For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
 This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-%	Multi-task learning is a powerful approach in many applications such as image and text classification.
-Yet, there is little rigorous understanding of when multi-task learning outperforms single-task learning.
-In this work, we provide a rigorous study to answer the question in the high-dimensional linear regression setting.
-We show that a bias-variance tradeoff of multi-task learning determines the effect of information transfer, and develop new concentration bounds to analyze the tradeoff.
-Our key observation is that three properties of task data, namely \textit{task similarity}, \textit{sample ratio}, and \textit{covariate shift} can affect transfer in the high-dimensional linear regression setting.
-We relate each property to the bias and variance of multi-task learning and explain three negative effects with decreased task similarity,	increased sample ratio, and covariate shift under increased sample ratio.
-We validate the three effects on text classification tasks.
-Inspired by our theory, we show two practical connections of interest.
-%	First, single-task results can help to understand when multi-task learning gives gains.
-Second, incrementally adding training data can mitigate negative transfer and improve multi-task training efficiency.
 \end{abstract}

### 2020-10-12 arxiv/setup.tex
minor
polish writing

@@
 For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension \cite{GLUE}.
-In this paper, we consider multi-task learning in a high-dimensional linear regression setting.
+In this paper, we consider multi-task learning in a \textit{high-dimensional} linear regression setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
 We assume that there are multiple datasets that all follow a (potentially different) linear model.
 In each dataset, suppose the feature vector $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with mean zero, unit variance, and covariance $\Sigma \in\real^{p \times p}$ that is deterministic and positive semidefinite.
-We are mainly interested in the \textit{high-dimensional} setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
-This setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
+The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
 
 We study a hard parameter sharing architecture to learn jointly from multiple datasets.
-In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a task-specific output layer $A_i \in \real^r$ for every task $i$ to $t$.
+In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a separate output layer $A_i \in \real^r$ for every task $i$.
 Suppose we have $t$ datasets.
-For each task $i = 1, 2, \dots, t$, let $n_i$ denote its sample size, $X^{(i)} \in \real^{n_i \times p}$ denote its feature covariates, and $Y^{(i)} \in \real^{n_i}$ denote all the labels.
+For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size, $X^{(i)} \in \real^{n_i \times p}$ denote its feature covariates, and $Y^{(i)} \in \real^{n_i}$ denote all the labels.
 %The width of $B$, denoted by $r$, plays an important role in regularization.
@@
 	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
-	Increasing task one's sample size helps reduce task two's prediction loss initially, but increases afterward.
+	Increasing task one's sample size decreases task two's prediction loss initially, but increases afterward.
+This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
 Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
 	See Section \ref{sec_simulation} for the precise setting.}
@@
 	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that \citet{ZSSGM18} has observed empirically observed.
-	Our results further show that HPS's sample efficiency depends on task-specific variance vs.
+	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that \citet{ZSSGM18} has observed empirically.
+	Our results further imply that HPS's sample efficiency depends on model-specific variance vs.
 noise variance.
@@
 In Section \ref{sec_diff}, we present our technical results for showing how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Section \ref{sec_exp}, we validate our theory in both simulations and a real world classification task.
+In Section \ref{sec_simulation} and \ref{sec_text}, we validate our theory in both simulations and a real world classification task.
 In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.

### 2020-10-12 arxiv/setup.tex
minor

--- 2020-10-12 arxiv/setup.tex
@@
 Our results imply that hard parameter sharing helps by reducing variance compared to single-task learning, but hurts by increasing bias.
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample sizes and covariance matrices.
+Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample sizes and population covariance matrices.
 We analyze the local minimum of $f(A, B)$ and provide a sharp generalization bound for both tasks' prediction loss.
@@
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-\HZ{add several sentences on the technical insight}
+We use some modern random matrix theory techniques developed in the past decade to obtain the sharp generalization bound \cite{erdos2017dynamical}.
+In particular, we use the novel technique in \cite{Anisotropic} to obtain a sharp estimate on the inverse of the sum of two sample covariance matrices with arbitrary population covariance matrices, which is commonly referred to as the \emph{local law}.
+%\HZ{add several sentences on the technical insight} 
 One limitation of our analysis is that for two tasks with different sample sizes, there is extra error term in the prediction loss of hard parameter sharing (cf.
 equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
-\HZ{add why this is challenging}
+This involves a study of the asymptotic singular values distribution of a non-symmetric random matrix plus an identity matrix, which is still an open problem in random matrix theory due to lack of freeness.
+%\HZ{add why this is challenging}
 

### 2020-10-12 arxiv/setup.tex
section 1.2

--- 2020-10-12 arxiv/setup.tex
@@
 equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
-\HZ{add why this is challenging}
+This involves a study of the asymptotic singular values distribution of a non-symmetric random matrix plus an identity matrix, which is still an open problem in random matrix theory due to lack of freeness.
+%\HZ{add why this is challenging}
 
@@
 
-We refer the interested readers to several excellent surveys on multi-task  learning for a comprehensive survey \cite{PY09,R17,ZY17,V20}.
-Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-For such models, their output dimension plays an important role of regularization \cite{KD12}.
-Linear models in multi-task learning have been studied in various settings, including representation learning \cite{BHKL19}, online learning \cite{CCG10,DCSP18}, and sparse regression \cite{LPVT11}.
-Below, we describe several lines of work that are most related to this work.
+There is a large body of both classical and recent work on multi-task learning.
+We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,R17,ZY17,V20}.
+The early work of \citet{B00,BS03,M06} have sought a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+An influential paper by \citet{BBCK10} provides uniform convergence bounds that combines multiple datasets in certain settings.
+One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, e.g. \citet{B00,MPR16}.
+To the best of our knowledge, we are not aware of any previous work that provide explicit generalization bounds under different sample sizes and covariate shifts.
 
-Some of the earliest works on multi-task learning are Baxter \cite{B00}, Ben-David and Schuller \cite{BS03}.
-Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-Ben-David et al. \cite{BBCK10} provides uniform convergence bounds that combines source and target errors optimally.
-The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-Our work is closely related to Wu et al. \cite{WZR20}.
-While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-\todo{spell out the challenge more explicitly}
+The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
+For example, \citet{li2020transfer} provides minimax optimal rates for predicting a target regression task given multiple source tasks.
+One closely related work is \citet{WZR20}, which studies hard parameter sharing for two linear regression tasks.
+\citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
+%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
 
-Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
+%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
+%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
+%For such models, their output dimension plays an important role of regularization \cite{KD12}.
+%Below, we describe several lines of work that are most related to this work.
+
+%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
+%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
+%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+%Our work is closely related to Wu et al. \cite{WZR20}.
+%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
+%\todo{spell out the challenge more explicitly}
+
+%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
+%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
+%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
 %\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-We believe that our theoretical framework can apply to other approaches to multi-task learning.
+%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
+%We believe that our theoretical framework can apply to other approaches to multi-task learning.
 
@@
 It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}.
-On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using the free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
+On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
 To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.

### 2020-10-12 arxiv/setup.tex

@@
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-\HZ{add several sentences on the technical insight}
+We use some modern random matrix theory techniques developed in the past decade to obtain the sharp generalization bound \cite{erdos2017dynamical}.
+In particular, we use the novel technique in \cite{Anisotropic} to obtain a sharp estimate on the inverse of the sum of two sample covariance matrices with arbitrary population covariance matrices, which is commonly referred to as the \emph{local law}.
+%\HZ{add several sentences on the technical insight} 
 One limitation of our analysis is that for two tasks with different sample sizes, there is extra error term in the prediction loss of hard parameter sharing (cf.

### 2020-10-12 arxiv/setup.tex

@@
 
+Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, which is a recent development in the random matrix theory literature.
+\citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
+This result is later extended to non-identity covariance \cite{Anisotropic} and separable covariance matrices \cite{yang2019spiked}.
+%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
+These techniques provide the most sharp convergence rates for the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
+To the best of my knowledge, we are not aware of any previous result for the sum of two sample covariance matrices with arbitrary covariance matrices.
+
 The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \citet{li2020transfer} provides minimax optimal rates for predicting a target regression task given multiple source tasks.
+For example, \citet{li2020transfer} provides minimax optimal rates for predicting a target regression task given multiple sparse regression tasks.
 One closely related work is \citet{WZR20}, which studies hard parameter sharing for two linear regression tasks.
@@
 
-The random matrix theory tool and related proof of our work fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}.
-For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}.
-It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}.
-On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in free probability theory \cite{nica2006lectures}.
-To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
-
 \smallskip

### 2020-10-12 arxiv/setup.tex
minor

@@
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-We use some modern random matrix theory techniques developed in the past decade to obtain the sharp generalization bound \cite{erdos2017dynamical}.
-In particular, we use the novel technique in \cite{Anisotropic} to obtain a sharp estimate on the inverse of the sum of two sample covariance matrices with arbitrary population covariance matrices, which is commonly referred to as the \emph{local law}.
+Using some novel random matrix theory techniques developed recently \cite{Anisotropic}, we show that inverse of the sum of two sample covariance matrices with arbitrary population covariance matrices converge to a deterministic diagonal matrix asymptotically.
+Moreover, we can obtain a sharp bound on the concentration error.
+% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}. 
 %\HZ{add several sentences on the technical insight} 
@@
 equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
-This involves a study of the asymptotic singular values distribution of a non-symmetric random matrix plus an identity matrix, which is still an open problem in random matrix theory due to lack of freeness.
+This involves a study of the asymptotic singular values distribution of a certain non-symmetric random matrix, which requires new techniques beyond the ones used in this paper.
+% plus an identity matrix,  due to lack of freeness
 %\HZ{add why this is challenging}

### 2020-10-12 arxiv/intro.tex
edit section 1.2 and abstract

@@
 The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making prediction.
-It becomes increasingly important to understand when they work well on typical data.
+%	It becomes increasingly important to understand when they work well on typical data.
 For example, the performance of hard parameter sharing depends on dataset properties such as their sample sizes.
@@
 
-	This paper analyzes hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio.
+	This paper studies a fundamental question: How does hard parameter sharing work in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio?
 We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample sizes and covariance matrices.

### 2020-10-12 arxiv/setup.tex
edit section 1.2 and abstract

--- 2020-10-12 arxiv/setup.tex
@@
 One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, e.g. \citet{B00,MPR16}.
-To the best of our knowledge, we are not aware of any previous work that provide explicit generalization bounds under different sample sizes and covariate shifts.
+Secondly, these techniques do not apply to the high-dimensional setting, because the results usually require a sample size at least $p \log p$.
 
@@
 These techniques provide the most sharp convergence rates for the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
-To the best of my knowledge, we are not aware of any previous result for the sum of two sample covariance matrices with arbitrary covariance matrices.
+To the best of my knowledge, we are not aware of any previous result for the sum of two sample covariance matrices with arbitrary covariate shifts.
 

### 2020-10-12 arxiv/conclusions.tex

--- 2020-10-09 arxiv/conclusions.tex
@@
 We describe several open questions for future work.
-First, our bound in Corollary \eqref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
 Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two random matrices $Z^{(1)}, Z^{(2)}$ with isotropic covariances.
-This might require new techniques beyond \HZ{to add}.
+This requires studying the asymptotic distribution of the {singular values} of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)} + 1$, which is still an open problem in random matrix theory.
+The eigenvalues distribution of this matrix have been obtained in \cite{Fmatrix}, which might be relevant.
+%but its singular values will follow a different distribution since the matrix is not symmetric.
+ %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
 Second, it would be interesting to extend our results to classification problems.

### 2020-10-12 arxiv/diff_cov.tex
minor

@@
 Next, we illustrate how varying them impact prediction loss, respectively.
-\begin{example}[Sample ratio]\label{ex_sample_ratio}
+\begin{example}[Sample size ratio]\label{ex_sample_ratio}
 	We first consider the impact of varying sample sizes.
@@
 	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-	(i) both tasks sample sizes are at least $\frac{3}{2}p$;
+	(i) both tasks sample sizes are at least $3p$;
 	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
@@
 \begin{enumerate}
-	\item When $\frac{2d^2}{d^2 + \sigma^2} > \frac{p}{n_2 - p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	\item When $\frac{2d^2}{d^2 + \sigma^2} < \frac{p}{n_2 - p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
+	\item When $\frac{2d^2}{d^2 + \sigma^2} > \frac{p}{n_2 - p}$, \FY{$\frac{d^2}{\sigma^2}<\frac{p}{2n_2-3p} $} the prediction loss decreases monotonically as $n_1$ increases.
+	\item When $\frac{2d^2}{d^2 + \sigma^2} < \frac{p}{n_2 - p}$, \FY{$\frac{d^2}{\sigma^2}>\frac{p}{2n_2-3p}$} the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
 	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one positive root for the derivative being zero.

### 2020-10-12 arxiv/tools.tex
revise

@@
 
- Moreover, we can obtain the following concentration estimates for random noise in the setting of Section \ref{sec_same}.
+Next we can obtain the following concentration estimates for random noise in the setting of Section \ref{sec_same}.
 
@@
 random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order.
-Then we have that
+Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
+\be\label{vcalE} |v^\top \epsilon^{(i)}| \le \sigma n^{c} \|v\|, \ee
+and
+\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c} \|B\|_F ,\ee
+for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
+\be\label{vcalAE3}
+\|v^\top \cal E\| \le \sigma n^{c} \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \|B\|_F ,
+\ee
+ with high probability for any small constant $c>0$.
+ \end{corollary}
+ \begin{proof}
 
- using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}
- \end{corollary}
+ \end{proof}

### 2020-10-13 arxiv/diff_cov.tex
various edits to polish draft

--- 2020-10-12 arxiv/diff_cov.tex
@@
 
-The different covariates case differs from the same covariates case in two aspects.
-First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-Second, the features of different tasks may have different shapes, a phenomenon that is often called ``covariate shift''.
-In this section, we show how to deal with these two aspects.
+The previous section assumes that all tasks have the same sample size and feature vectors.
+This section studies how different sample sizes and different features impact hard parameter sharing.
+%The different covariates case differs from the same covariates case in two aspects.
+%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
+The setting where features differ across tasks is often also called ``covariate shift''.
 
@@
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Suppose that $X^{(1)} = Z^{(1)}{\Sigma^{(1)}}^{1/2} \in \real^{n_1 \times p}$ and $X^{(2)} = Z^{(2)}{\Sigma^{(2)}}^{1/2} \in \real^{n_2 \times p}$, where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+Suppose that $X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p}$ and $X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p}$, where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
 The matrices $\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
@@
 Our key result characterizes the asymptotic limit of the inverse of the sum of two different sample covariance matrices.
-Recall that in the hard parameter sharing, we have to take $r<t$.
-Hence in the two-task case, we must have $r=1$.
 To motivate our study, consider a special case where $A_1=A_2=1$. 
 Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
+By Proposition 1 of \citet{WZR20}, we consider the case of $r = 1 < t = 2$, since when $r > 1$, the optimal solution of $f(A, B)$ is equivalent to single-task learning.
+When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
+Hence we can write down a closed form equation for any local minimum of $f(A, B)$.
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
@@
 The matrix $\hat{\Sigma}$ adds up both tasks' sample covariances, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-The empirical loss of $\hat{\beta}_2^{\MTL}$ is close to its expectation similar to Claim \ref{claim_pred_err}.
-Hence, we consider the expected loss conditional on the covariates as follows:
+
+To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to its expectation similar to Claim \ref{claim_pred_err}):
 \begin{align}
@@
 \end{align}
+Our main result in this section characterizes the asymptotic limit of the above equation under the high-dimensional assumption.
+Intuitively, the spectrum of $\hat{\Sigma}^{-1}$ (and hence its trace) not only depends on both tasks' sample sizes, but also depends on the ``alignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
+However, capturing this intuition quantitatively turns out to be technically challenging.
+%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
+We introduce a key quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and as we show below, the trace of $\hat{\Sigma}^{-1}$ has an intricate dependence on the spectrum of $M$.
 
-Interestingly, the expected loss also admits a nice bias-variance decomposition.
-Our main result in this section characterizes the asymptotic limit of the above equation, when both sample size and feature dimension become increasingly large at a fixed ratio.
-The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-Intuitively, the scaling of $\hat{\Sigma}^{-1}$ not only depends on both tasks' sample sizes, but also depends on their population covariance matrices.
-We introduce a key quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$ that captures the covariate shift between task one and task two.
-Let $U\Lambda V^\top$ denote the singular value decomposition of $M$, where $\Lambda\in\real^{n\times p}$ consists of $M$'s singular values $\lambda_1\ge \lambda_2\ge \dots \ge \lambda_p$ as its diagonal entries in descending order.
+Let $U\Lambda V^\top$ denote the SVD of $M$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote $M$'s singular values in descending order.
 Our main result is stated as follows.
@@
 	Let $c_{\varphi}$ be a fixed value in $(0, \frac{\varphi - 4}{2\varphi})$.
-	Assume that: a) $Z^{(1)}, Z^{(2)}$ both satisfy Assumption \ref{assume_rm};
+	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
 	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
@@
 \end{theorem}
-Our result extends Fact \ref{fact_tr} on the inverse of a single sample covariance matrix.
-When $n_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
+Part (i) of our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
+To see this, when $n_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
 
 \paragraph{How does hard parameter sharing scale with sample size and covariate shift?}
-One can see that both the variance limit and the bias limit depend heavily on both tasks' samples sizes and the covariate shift matrix $M$.
+One can see that the bias-variance limits depend intricately on both tasks' samples sizes and covariate shift.
 Next, we illustrate how varying them impact prediction loss, respectively.
-\begin{example}[Sample ratio]\label{ex_sample_ratio}
+\begin{example}[Sample size ratio]\label{ex_sample_ratio}
 	We first consider the impact of varying sample sizes.
@@
 %	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\delta}{\kappa^2}$ for a small constant $\delta>0$.
+	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$.
 	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c } \cdot \OO(d^2 + \sigma^2).
+	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
@@
 	 \end{align}
-	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
+%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
 %	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
@@
 The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
+Furthermore, by calculating the derivative of the bias-variance limits with respect to $n_1$, we obtain the following dichotomy (details omitted).
 \begin{enumerate}
-	\item When $\frac{2d^2}{d^2 + \sigma^2} > \frac{p}{n_2 - p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	\item When $\frac{2d^2}{d^2 + \sigma^2} < \frac{p}{n_2 - p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
+	\item When $\frac{2d^2}{d^2 + \sigma^2} < \frac{p}{n_2 - p}$, the prediction loss decreases monotonically as $n_1$ increases.
+	\item When $\frac{2d^2}{d^2 + \sigma^2} > \frac{p}{n_2 - p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
 	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one positive root for the derivative being zero.
-%Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
-%(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
-%(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
-%(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
 \end{enumerate}
-
-%Based on this observation, we have the following trend when we fix $n_2$ and increase $n_1$:
-%\begin{itemize}
-%	\item If $d^2$ is smaller than $\frac{\sigma^2 p}{n_2 - p}$, then the prediction loss of hard parameter sharing is always lower than STL. That is, task one always transfers positively to task two.
-%	\item Otherwise, task one transfers positively to task two initially, but transfers negatively eventually.
-%\end{itemize}
-%Therefore, while the variance of MTL still reduces compared to STL,
-%If the bias increases more than the amount of variance reduced, we observe negative transfer.
-%of MTL increases and converges to $pd^2$ as the sample ratio $\rho_1/\rho_2$ increases, and the variance reduction $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$ also increases and converges to $\frac{\sigma^2}{\rho_2-1}$ as $\rho_1/\rho_2$ increases.
-The tradeoff between these two terms depends on $\rho_1$ in a nonlinear way that is more complicated than the one in the case of varying model distance.
-But from our results, one can check the following phenomena.
-If $\frac{\sigma^2}{\rho_2-1} > pd^2$, then the transfer is always positive.
-On the other hand, if $\frac{\sigma^2}{\rho_2-1} < pd^2$, then there is a transition from the positive transfer to negative transfer as $\rho_1/\rho_2$ increases.
-%Therefore, while the variance of MTL still reduces compared to STL,
-%If the bias increases more than the amount of variance reduced, we will observe negative transfer.
-%Figure \ref{fig_size} provides a simulation result for such a setting (described in Appendix \ref{app_synthetic}).
-%We observe that as $n_1 / n_2$ increases, there is a transition from positive to negative transfer.
-%There are several unexplained observations near $y = 0$ caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
 
@@
 %In general, the covariance matrices of the two tasks may be different such as in text classification.
-Our second example studies the effect of varying covariate shifts on the variance limit in equation \eqref{lem_cov_shift_eq}:
+Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}, which shows that
 %in the left hand side of equation \eqref{lem_cov_shift_eq}:
@@
 %As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit is determined by the spectrum of $M$. To be clear, for this example we assume that the bias is $0$.
+Hence the variance limit is determined by the spectrum of $M$.% To be clear, for this example we assume that the bias is $0$.
 
-To illustrate this result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
+To illustrate the above result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
 In particular, when $\lambda = 1$, there is no covariate shift.
@@
 	+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)\cdot (\lambda^2-1)^2  g(\lambda, a_1),
+	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
 \end{align*}
 where $g(\lambda, a_1) > 0$ is a fixed function and can be derived from algebraic calculations (details omitted).
-%Hence, whether or not $f(\lambda)$ is small than $f(1)$ depends on $a_1$.
 We now show that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, and hence explain the dichonomy.
-%In Example \ref{ex_covshift}, with the fact $M=M^{-1}$, we observe that $a_1$ and $a_2$ play a symmetric role. 
-%in the self-consistent equations \eqref{lem_cov_shift_eq}.
-In fact, if $a_1>a_2$, then the equations in \eqref{eq_a12extra} give that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and
+In fact, if $a_1>a_2$, then the equations in \eqref{eq_a12extra} give that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and one can verify that
 $$ 
  \frac{n_1}{n_1 + n_2}=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} 
-> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) >\frac{1}{2}. 
+> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
 $$
@@
 
-\iffalse
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, which gives $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 }) = \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$.
-The other case when $n_1 < n_2$ is similar.
-A formal proof follows from a study of the self-consistent equations \eqref{eq_a12extra} and we omit the details.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.  If $n_1< n_2$, then $f(\lambda)< f(1)$.
-\fi
-%\begin{proposition}[Source/target sample ratio]\label{prop_data_size}
-%	In the isotropic model, suppose that $\rho_1 > 40$ and $\rho_2 > 110$ are fixed constants, and $\Psi(\beta_1, \beta_2) > 2/(\rho_2 - 1)$.
-%	Then we have that
-%	\begin{itemize}
-%		\item \textbf{Positive transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} < \frac{1}{\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 1) - \nu^{-1}}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) < \te(\hat{\beta}_2^{\STL}).$$
-%		\item \textbf{Negative transfer:} If $\frac{n_1}{n_2} = \frac{\rho_1}{\rho_2} > {\nu} \cdot \frac{1 - 2\rho_2^{-1}}{\Psi(\beta_1, \beta_2) (\rho_2 - 3/2) - \nu}$, then w.h.p.
-$$\te(\hat{\beta}_2^{\MTL}) > \te(\hat{\beta}_2^{\STL}).$$
-%	\end{itemize}
-%\end{proposition}
-%Proposition \ref{prop_data_size} describes the bias-variance tradeoff in terms of the sample ratio $\rho_1 / \rho_2$.
-
-%We apply the result to the setting of Figure \ref{fig_size} (described in Appendix \ref{app_synthetic}).
-%There are several unexplained observations near $y = 0$ caused by $\nu$.
-%The proof of Proposition \ref{prop_data_size} can be found in Appendix \ref{app_proof_32}.
-
-%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
-%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
-
-%We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
-%Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
-%We show that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix should be proportional to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
-%On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.
-
 \paragraph{Overview of Stieltjes transform.}
@@
 The central quantity of interest is the inverse of the sum of two sample covariance matrices $\hat{\Sigma}^{-1}$.
+We note that the variance equation $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ is equal to $(n_1 + n_2)^{-1} \bigtr{W^{-1}}$, where $W$ is
+\begin{align}\label{eigen2extra}
+	W \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
+\end{align}
+This formulation is helpful because we know that ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance, and $U, V$ are both orthonormal matrices.
+
 Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
@@
 
-We define the matrix $W$ as follows
-\begin{align}\label{eigen2extra}
-	W \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
-\end{align}
-Recall that  $U\Lambda V^\top$ is the singular value decomposition of $M$, %$\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix, 
-and ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance.
-It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= (\Sigma^{(2)})^{-1/2} V W^{-1}V^\top (\Sigma^{(2)})^{-1/2}$ and $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$.
+%Recall that  $U\Lambda V^\top$ is the singular value decomposition of $M$, %$\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix,
+%It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= (\Sigma^{(2)})^{-1/2} V W^{-1}V^\top (\Sigma^{(2)})^{-1/2}$ and .
 Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$.

### 2020-10-13 arxiv/setup.tex

@@
 In this paper, we consider multi-task learning in a \textit{high-dimensional} linear regression setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
+The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
 We assume that there are multiple datasets that all follow a (potentially different) linear model.
 In each dataset, suppose the feature vector $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with mean zero, unit variance, and covariance $\Sigma \in\real^{p \times p}$ that is deterministic and positive semidefinite.
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
 
@@
 \begin{figure}[!t]
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[t]{0.5\textwidth}
 		\centering
-		\includegraphics[width=0.65\textwidth]{figures/mtl_model.pdf}
+		\includegraphics[width=0.5\textwidth,valign=t]{figures/mtl_model_arch.pdf}
 		\caption{A hard parameter sharing architecture}
 	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[t]{0.5\textwidth}
 		\centering
-		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_c2_400.eps}
+		\includegraphics[width=0.713\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
 		\caption{Varying sample size ratio}
@@
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-Using some novel random matrix theory techniques developed recently \cite{Anisotropic}, we show that inverse of the sum of two sample covariance matrices with arbitrary population covariance matrices converge to a deterministic diagonal matrix asymptotically.
-Moreover, we can obtain a sharp bound on the concentration error.
+Using recently developed techniques from the random matrix theory technique \cite{Anisotropic}, we show that inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
+Theorem \ref{thm_main_RMT}(i)).
+% Moreover, we can obtain a sharp bound on the concentration error.
 % to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}. 
@@
 equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
-This involves a study of the asymptotic singular values distribution of a certain non-symmetric random matrix, which requires new techniques beyond the ones used in this paper.
+This requires studying the spectrum of non-symmetric random matrices, which is an intriguing open question (see Section \ref{sec_conclude} for more discussion).
 % plus an identity matrix,  due to lack of freeness
@@
 \citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-This result is later extended to non-identity covariance \cite{Anisotropic} and separable covariance matrices \cite{yang2019spiked}.
+\citet{Anisotropic} later extended this result to arbitrary covariances.
 %On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
 These techniques provide the most sharp convergence rates for the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
-To the best of my knowledge, we are not aware of any previous result for the sum of two sample covariance matrices with arbitrary covariate shifts.
+To the best of our knowledge, we are not aware of any previous result for the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
 

### 2020-10-13 arxiv/conclusions.tex
polish section 3 and 5

@@
 First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two random matrices $Z^{(1)}, Z^{(2)}$ with isotropic covariances.
-This requires studying the asymptotic distribution of the {singular values} of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)} + 1$, which is still an open problem in random matrix theory.
-The eigenvalues distribution of this matrix have been obtained in \cite{Fmatrix}, which might be relevant.
+Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic random matrices.
+This requires studying the asymptotic distribution of the {singular values} of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}$, which is still an open problem in random matrix theory.
+The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
 %but its singular values will follow a different distribution since the matrix is not symmetric.
@@
 Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress in the (one-sample) high-dimensional logistic regression setting \cite{sur2019modern}.
-An interesting question is to study hard parameter sharing in (multiple-sample) high-dimensional logistitic regression.
+Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \cite{sur2019modern}.
+An interesting question is to study logistic regression in a multiple-sample setting.

### 2020-10-13 arxiv/diff_cov.tex
polish section 3 and 5

@@
 
+\paragraph{Bias-variance equations.}
 Our key result characterizes the asymptotic limit of the inverse of the sum of two different sample covariance matrices.
@@
 \end{align}
-Our main result in this section characterizes the asymptotic limit of the above equation under the high-dimensional assumption.
+Equation \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of hard parameter sharing for two tasks, respectively.
+Our main result in this section characterizes the asymptotic bias-variance limits under the high-dimensional assumption.
 Intuitively, the spectrum of $\hat{\Sigma}^{-1}$ (and hence its trace) not only depends on both tasks' sample sizes, but also depends on the ``alignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.

### 2020-10-13 arxiv/diff_cov.tex
polish section 2/3

@@
 \begin{enumerate}
-	\item When $\frac{2d^2}{d^2 + \sigma^2} < \frac{p}{n_2 - p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	\item When $\frac{2d^2}{d^2 + \sigma^2} > \frac{p}{n_2 - p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one positive root for the derivative being zero.
+	\item When $\frac{d^2}{\sigma^2} < \frac{p}{2n_2 - 3p}$, the prediction loss decreases monotonically as $n_1$ increases.
+	Intuitively, this regime of $d^2$ always helps task two.
+	\item When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
+	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one critical point for the derivative being zero, which corresponds to the \textit{optimal sample size ratio}.
 \end{enumerate}

### 2020-10-13 arxiv/intro.tex
finish intro

@@
 Yet, rigorously formulating such intuition can be challenging.
-
-	This paper studies a fundamental question: How does hard parameter sharing work in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio?
-We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample sizes and covariance matrices.
+	This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks?
+	We consider the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio, and present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample size ratios and covariance matrices.
 We also demonstrate that these estimates for the empirical loss are incredibly accurate in modest dimensions.
@@
 This presents a technical challenge in the multi-task setting because of the difference among task features, even for two tasks.
-For Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-Without a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
+ithout a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
 \todo{add more technical motivation (or maybe later)}
 From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data can provide guidance for downstream applications \cite{RH19}.
-%For example, the sample sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11}.
+%For example,
 %On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
@@
 \squishend
+\fi
 
-%The observations highlight the need to develop generalization bounds that scale tightly with properties of multiple tasks data.
-% that only contains limited amount of labeled data.
-%Following Hastie et al.  and Bartlett et al. \cite{},
+Hard parameter sharing (HPS) is a widely used approach to learn from multiple tasks and goes back to the seminal work of \citet{C97}.
+It is generally applied by sharing the feature layers between all tasks, while keeping an output layer for every task.
+Recent work has revived interest in this classical approach through many applications \cite{MTDNN19,ZSSGM18}.
+Hard parameter sharing offers two critical advantages:
+(i) it reduces model parameters since all tasks use the same feature space;
+(ii) it reduces the need for labeled data from each task while augmenting the entire training dataset.
 
-%Let $n_i = \rho_i \cdot p$ denote the data size and $X_i\in\real^{n_i\times p}$ denote the features of task $i$.
-%The labels of task $i$ are given by $Y_i = X_i\beta_i + \varepsilon_i$, where $\beta_i\in\real^p$ denotes task $i$'s ground truth parameters and $\varepsilon_i$ denotes i.i.d.
-random noise with mean zero and variance $\sigma^2$.
-We consider a multi-task estimator obtained using a shared linear layer for all tasks and a separate output layer for each task \cite{WZR20}.
-This two-layer model is inspired by a commonly used idea of hard parameter sharing in multi-task learning \cite{R17,MTDNN19}.
-We consider the bias and variance of the multi-task estimator for predicting a target task and compare its performance to single-task learning.
-%This corresponds to minimizing $ \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2$.
-%Let $\hat{\beta}_t^{\MTL}$ denote the optimal multi-task estimator for the target task, which is defined precisely in Section \ref{sec_prelim}.
-%We revisit the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$.
+Hard parameter sharing is often thought of as a mechanism for inducing inductive bias.
+Since all tasks share the same feature space, by restricting the size of the space, HPS acts as a regularizer and reduces overfitting \cite{KD12,WZR20}.
+Another source of inductive bias comes from the tasks, and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
+Previous generalization theories have considered when all tasks' sample sizes are equal \cite{B00,MPR16}.
+Using Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase \cite{AZ05,M06}.
+%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
 
-\HZ{go to intro}
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
-\fi
+In this paper, we present a new generalization theory for hard parameter sharing by studying its  performance in the high-dimensional linear regression setting.
+Linear regression is arguably one of the most fundamental problem in statistics and machine learning.
+We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
+This is motivated by many multi-task learning applications, where the amount of labeled data from each dataset is usually insufficient for learning a single task.
+For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension \cite{socher2013recursive}.
+The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.

### 2020-10-13 arxiv/setup.tex
polish section 2/3
finish intro

@@
-\subsection{Problem Formulation and Main Results}
+\subsection{Setup and Main Results}
 
@@
 
-Regression analysis is arguably one of the most fundamental methods in statistics and machine learning.
-In many multi-task learning applications, the amount of labeled data from each dataset is usually insufficient for learning a single task.
-For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension \cite{GLUE}.
-In this paper, we consider multi-task learning in a \textit{high-dimensional} linear regression setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
 We assume that there are multiple datasets that all follow a (potentially different) linear model.
 In each dataset, suppose the feature vector $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with mean zero, unit variance, and covariance $\Sigma \in\real^{p \times p}$ that is deterministic and positive semidefinite.
-
 We study a hard parameter sharing architecture to learn jointly from multiple datasets.
@@
 Our results imply that hard parameter sharing helps by reducing variance compared to single-task learning, but hurts by increasing bias.
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample sizes and population covariance matrices.
+Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and population covariance matrices.
 We analyze the local minimum of $f(A, B)$ and provide a sharp generalization bound for both tasks' prediction loss.
@@
 Let $X^+$ denote its Moore-Penrose psuedoinverse.
-We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
+We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
 We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.

### 2020-10-13 arxiv/intro.tex
fix grammar issue

@@
 	Hard parameter sharing is a widely used approach to learn jointly from multiple tasks in many applications, such as text classification.
-The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making prediction.
+The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making the prediction.
 %	It becomes increasingly important to understand when they work well on typical data.
@@
 	This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks?
-	We consider the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio, and present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample size ratios and covariance matrices.
+	We consider the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio.
+We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample size ratios and covariance matrices.
 We also demonstrate that these estimates for the empirical loss are incredibly accurate in modest dimensions.
-Finally, our results provide new explainanations to several intriguing empirical phenomena.
+Finally, our results provide new explanations for several intriguing phenomena.
 For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
@@
 Hard parameter sharing (HPS) is a widely used approach to learn from multiple tasks and goes back to the seminal work of \citet{C97}.
-It is generally applied by sharing the feature layers between all tasks, while keeping an output layer for every task.
+It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
 Recent work has revived interest in this classical approach through many applications \cite{MTDNN19,ZSSGM18}.
@@
 Hard parameter sharing is often thought of as a mechanism for inducing inductive bias.
-Since all tasks share the same feature space, by restricting the size of the space, HPS acts as a regularizer and reduces overfitting \cite{KD12,WZR20}.
-Another source of inductive bias comes from the tasks, and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
+Since all tasks share the same feature space, by restricting the space's, HPS acts as a regularizer and reduces overfitting \cite{KD12,WZR20}.
+Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
 Previous generalization theories have considered when all tasks' sample sizes are equal \cite{B00,MPR16}.
-Using Rademacher complexity or VC-based techniques, the generalization error scales down as the sample sizes of all tasks increase \cite{AZ05,M06}.
+Using Rademacher complexity or VC-based techniques, the generalization error scales down as all tasks' sample sizes increase \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
 
-In this paper, we present a new generalization theory for hard parameter sharing by studying its  performance in the high-dimensional linear regression setting.
-Linear regression is arguably one of the most fundamental problem in statistics and machine learning.
+This paper presents a new generalization theory to understand the hard parameter sharing approach by studying its performance in the high-dimensional linear regression setting.
+Linear regression is arguably one of the most fundamental problems in statistics and machine learning.
 We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.

### 2020-10-13 arxiv/intro.tex
minor intro

@@
 We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample size ratios and covariance matrices.
-We also demonstrate that these estimates for the empirical loss are incredibly accurate in modest dimensions.
+We also demonstrate that these estimates for the empirical loss are incredibly accurate in moderate dimensions.
 Finally, our results provide new explanations for several intriguing phenomena.
@@
 Hard parameter sharing is often thought of as a mechanism for inducing inductive bias.
-Since all tasks share the same feature space, by restricting the space's, HPS acts as a regularizer and reduces overfitting \cite{KD12,WZR20}.
+Since all tasks share the same feature space, by restricting the space's \FY{what is "space's"}, HPS acts as a regularizer and reduces overfitting \cite{KD12,WZR20}.
 Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-Previous generalization theories have considered when all tasks' sample sizes are equal \cite{B00,MPR16}.
+Previous generalization theories have considered the case where all tasks' sample sizes are equal \cite{B00,MPR16}.
 Using Rademacher complexity or VC-based techniques, the generalization error scales down as all tasks' sample sizes increase \cite{AZ05,M06}.
@@
 Linear regression is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and the feature dimension grow linearly at a fixed ratio.
+We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly at a fixed ratio.
 This is motivated by many multi-task learning applications, where the amount of labeled data from each dataset is usually insufficient for learning a single task.

### 2020-10-13 arxiv/setup.tex
start formatting
minor intro
typos

@@
 
-We assume that there are multiple datasets that all follow a (potentially different) linear model.
-In each dataset, suppose the feature vector $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with mean zero, unit variance, and covariance $\Sigma \in\real^{p \times p}$ that is deterministic and positive semidefinite.
+We assume that there are multiple datasets that all follow (potentially different) linear models.
+In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
 We study a hard parameter sharing architecture to learn jointly from multiple datasets.
@@
 \end{align}
-Given a solution $\hat{A}, \hat{B}$ from the above optimization, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the hard parameter sharing (HPS) estimator for task $i$.
-The critical questions here are:
-(i) how well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) for datasets with different sample sizes and covariate shifts, how do they impact the estimator?
+Given a solution $(\hat{A}, \hat{B})$ to the above optimization problem, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the hard parameter sharing (HPS) estimator for task $i$.
+Some critical questions are:
+(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
+(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
 
@@
 \paragraph{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to the multi-label prediction setting where all datasets have the same features, and we want to make multiple predictions (e.g.
+Our first result (Theorem \ref{thm_many_tasks}) applies to the multi-label prediction setting where all datasets have the same features, and we want to make multiple predictions (see e.g.
 \cite{hsu2009multi}).
-We analyze the global minimum of $f(A, B)$, and provide a sharp generalization bound for its (out-of-sample) prediction loss for any task.
+We analyze the global minimizer of $f(A, B)$, and provide a sharp generalization bound on its (out-of-sample) prediction loss for any task.
 This case is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
@@
 Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and population covariance matrices.
-We analyze the local minimum of $f(A, B)$ and provide a sharp generalization bound for both tasks' prediction loss.
-Despite its simplicity, we show several rich phenomena by varying sample sizes and covariate shifts in this setting.
+We analyze the local minimizers of $f(A, B)$ and provide a sharp generalization bound on both tasks' prediction loss.
+Despite its simplicity, we show several interesting phenomena by varying sample sizes and covariate shifts in this setting.
 See Figure \ref{fig_intro_sample_size} for an illustration.
@@
 	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
-	Increasing task one's sample size decreases task two's prediction loss initially, but increases afterward.
+	Increasing task one's sample size decreases task two's prediction loss initially, but increases afterwards.
 This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
@@
 
-Consequently, we observe qualitative properties of hard parameter sharing for varying datasets' properties using our precise loss estimates.
+Consequently, using our precise loss estimates, we observe qualitative properties of hard parameter sharing for varying datasets' properties.
 \begin{enumerate}
@@
 noise variance.
-It is generally high when the noise variance is large compared to model-specific variance across tasks.
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how much bias increases.
+It is generally high when the noise variance is large compared to model-specific variance across different tasks.
+	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help to reduce another task's loss.
+In a simplified setting, we find that the task loss either decreases first before increasing afterwards, or decreases monotonically depending on how fast the bias increases.
 These two trends result from different tradeoffs between increasing bias and decreasing variance.
 	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
-For a high sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a low sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
+For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
+Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
 \end{enumerate}
@@
 There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and their population version.
+We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and its population version.
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-Using recently developed techniques from the random matrix theory technique \cite{Anisotropic}, we show that inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
+Using recently developed techniques from random matrix theory \cite{Anisotropic}, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
 Theorem \ref{thm_main_RMT}(i)).
@@
 %\HZ{add several sentences on the technical insight} 
-One limitation of our analysis is that for two tasks with different sample sizes, there is extra error term in the prediction loss of hard parameter sharing (cf.
+One limitation of our analysis is that for two tasks with different sample sizes, there is an extra error term in the prediction loss of hard parameter sharing (cf.
 equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
@@
 
-There is a large body of both classical and recent work on multi-task learning.
+There is a large body of both classical and recent works on multi-task learning.
 We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,R17,ZY17,V20}.
-The early work of \citet{B00,BS03,M06} have sought a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \citet{BBCK10} provides uniform convergence bounds that combines multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, e.g. \citet{B00,MPR16}.
-Secondly, these techniques do not apply to the high-dimensional setting, because the results usually require a sample size at least $p \log p$.
+The early work of \citet{B00,BS03,M06} have sought for a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+An influential paper by \citet{BBCK10} provides uniform convergence bound that combines multiple datasets in certain settings.
+One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \citet{B00,MPR16}.
+Moreover, these techniques do not apply to the high-dimensional setting, because the results usually require a sample size at least $p \log p$.
 
@@
 \citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\citet{Anisotropic} later extended this result to arbitrary covariances.
+\citet{Anisotropic} later extended this result to arbitrary covariance setting.
 %On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide the most sharp convergence rates for the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous result for the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
+These techniques provide almost sharp convergence rates to the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
+To the best of our knowledge, we are not aware of any previous results about the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
 
@@
 For example, \citet{li2020transfer} provides minimax optimal rates for predicting a target regression task given multiple sparse regression tasks.
-One closely related work is \citet{WZR20}, which studies hard parameter sharing for two linear regression tasks.
+One closely related work is \citet{WZR20}, which studied hard parameter sharing for two linear regression tasks.
 \citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
@@
 In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we present our technical results for showing how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Section \ref{sec_simulation} and \ref{sec_text}, we validate our theory in both simulations and a real world classification task.
+In Section \ref{sec_diff}, we present our technical results that describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
+In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in both simulations and a real world classification task.
 In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.
@@
 %Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
-Let $\lambda_1(X) \ge \lambda_2(X) \ge \cdots \ge \lambda_t(X)$ denote the eigenvalues of $X$.
-Let $X^+$ denote its Moore-Penrose psuedoinverse.
+For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+Let $\lambda_1(X) \ge \lambda_2(X) \ge \cdots \ge \lambda_{p\wedge n}(X)$ denote the singular values of $X$.
+Let $X^+$ denote the Moore-Penrose psuedoinverse.
 We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.

### 2020-10-13 arxiv/intro.tex
polish introduction

@@
+% The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making the prediction.
 \begin{abstract}
-	Hard parameter sharing is a widely used approach to learn jointly from multiple tasks in many applications, such as text classification.
-The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making the prediction.
-%	It becomes increasingly important to understand when they work well on typical data.
-For example, the performance of hard parameter sharing depends on dataset properties such as their sample sizes.
-Yet, rigorously formulating such intuition can be challenging.
+	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that their generalization properties have not been established in many cases.
 This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks?
-	We consider the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio.
-We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample size ratios and covariance matrices.
-We also demonstrate that these estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, our results provide new explanations for several intriguing phenomena.
-For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias.
+We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio.
+First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
+Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
+We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
+Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
 This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
@@
 
-Hard parameter sharing (HPS) is a widely used approach to learn from multiple tasks and goes back to the seminal work of \citet{C97}.
+Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \citet{C97}.
+Recent work has revived interest in this approach because it improves performance and reduces the cost of collecting labeled data \cite{MTDNN19,ZSSGM18}.
 It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Recent work has revived interest in this classical approach through many applications \cite{MTDNN19,ZSSGM18}.
-Hard parameter sharing offers two critical advantages:
-(i) it reduces model parameters since all tasks use the same feature space;
-(ii) it reduces the need for labeled data from each task while augmenting the entire training dataset.
+Often, hard parameter sharing offers two critical advantages if successfully applied.
+(i) It reduces model parameters since all tasks use the same feature space.
+(ii) It reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
 
-Hard parameter sharing is often thought of as a mechanism for inducing inductive bias.
-Since all tasks share the same feature space, by restricting the space's \FY{what is "space's"}, HPS acts as a regularizer and reduces overfitting \cite{KD12,WZR20}.
+Hard parameter sharing offers great intuitive appeal as an inductive transfer mechanism.
+It reduces overfitting by acting as a regularizer \cite{R17}.
+For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
 Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-Previous generalization theories have considered the case where all tasks' sample sizes are equal \cite{B00,MPR16}.
-Using Rademacher complexity or VC-based techniques, the generalization error scales down as all tasks' sample sizes increase \cite{AZ05,M06}.
+However, how these dataset properties impacts HPS has not been established.
+%It becomes increasingly important to understand HPS' formal generalization properties.
+Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, not amenable to standard concentration results.
+Previous results based on Rademacher complexity or VC dimensions have considered when all tasks' sample sizes are equal to logarithm factors of feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
 
-This paper presents a new generalization theory to understand the hard parameter sharing approach by studying its performance in the high-dimensional linear regression setting.
-Linear regression is arguably one of the most fundamental problems in statistics and machine learning.
+This paper presents new techniques to study hard parameter sharing and establish a number of new results.
+We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
 We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly at a fixed ratio.
 This is motivated by many multi-task learning applications, where the amount of labeled data from each dataset is usually insufficient for learning a single task.
-For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension \cite{socher2013recursive}.
+For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension.
 The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.

### 2020-10-13 arxiv/intro.tex
polish introduction

@@
 
-\section{Introduction}\label{sec introduction}
-
-\iffalse
-%Multi-task learning is an inductive learning mechanism to improve generalization performance using related task data.
-%Many state-of-the-art results in computer vision and natural language processing are obtained using multi-task learning.
-Multi-task learning is a powerful approach to improve performance for many tasks in computer vision, natural language processing, and other areas \cite{C97,ZY17,R17}.
-%In multi-task learning, having related task data is fundamental to its performance.
-%Multi-task learning is particularly powerful when there is limited labeled data for a task to be solved, meanwhile more labeled data from different but related tasks is available.
-%By combining multiple information sources, it is possible to share all the information in the same model.
-In many settings, multiple source tasks are available to help with predicting a particular target task.
-\todo{clarify setting is different from traditional MTL}
-%For example, many applications in , and many other areas have been achieved by learning from multiple tasks together.
-The performance of multi-task learning depends on the relationship between the source and target tasks \cite{C97}.
-%	We define that multi-task learning provides \textit{positive transfer} if it outperforms single-task learning, or \textit{negative transfer} otherwise.
-When the sources are relatively different from the target, multi-task learning (MTL) has often been observed to perform worse than single-task learning (STL) \cite{AP16,BS17}, which is referred to as \textit{negative transfer} \cite{PY09}.
-While many empirical approaches have been proposed to mitigate negative transfer \cite{ZY17}, a precise understanding of when negative transfer occurs remains elusive in the literature \cite{R17}.
-%This phenomenon, known as \textit{negative transfer}, is fundamental to the understanding of multi-task learning.
-
-%Inspired by the theory, we propose an incremental training schedule to improve multi-task training.
-%We consider a setting where the target task has limited labeled data and show
-%On the other hand, unless the structures across task data are well-understood, applying multi-task learning on several different datasets often result in suboptimal models (or negative transfer in more technical terms).
-
-Understanding negative transfer requires developing generalization bounds that scale tightly with properties of each task data, such as its sample size.
-This presents a technical challenge in the multi-task setting because of the difference among task features, even for two tasks.
-ithout a tight lower bound for multi-task learning, comparing its performance to single-task learning results in vacuous bounds.
-\todo{add more technical motivation (or maybe later)}
-From a practical standpoint, developing a better understanding of multi-task learning in terms of properties of task data can provide guidance for downstream applications \cite{RH19}.
-%For example,
-%On the other hand, uneven sample sizes (or dominating tasks) have been empirically observed to cause negative transfer \cite{YKGLHF20}.
-%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
-%When all tasks are sufficiently similar, adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
-
-%\textbf{Setup and Main Results.}
-In this work, we study the bias and variance of multi-task learning in the high-dimensional linear regression setting \cite{HMRT19,BLLT20}.
-Our key observation is that three properties of task data, including \textit{task similarity}, \textit{sample ratio}, and \textit{covariate shift}, can affect whether multi-task learning outperforms single-task learning (which we refer to as \textit{positive transfer}).
-As an example, we vary each property in Figure \ref{fig_model_shift_phasetrans} for two linear regression tasks and measure the improvement of multi-task learning over single-task learning for a particular task.
-We observe that the effect of transfer can be either positive or negative as we vary each property.
-These phenomena cannot be explained using previous techniques \cite{WZR20}.
-The high-dimensional linear regression setting allows us to measure the three properties precisely.
-Here we define each property for the case of two tasks, while our definition applies to general settings.
-We refer to the first task as the source task and the second as the target task.
-\squishlist
-	\item \textbf{Task similarity:} Assume that both tasks follow a linear model with parameters $\beta_1, \beta_2\in\real^p$, respectively.
-	We measure the distance between them by $\norm{\beta_1 - \beta_2}$.
-	\item \textbf{Sample ratio:} Let $n_1 = \rho_1 \cdot p, n_2 = \rho_2 \cdot p$ be the sample size of each task, where $\rho_1, \rho_2>1$ are both fixed values that do not grow with $p$.
-	We measure the source/target sample ratio by $\rho_1 / \rho_2$.
-%	Importantly, $\rho_2$ can be a small constant (say $2$) to capture the need for more labeled data.
-	\item \textbf{Covariate shift:} Assume that the task features are random vectors with positive semidefinite covariance matrices $\Sigma_1\in\real^{p\times p}$ and $\Sigma_2\in\real^{p\times p}$, respectively.
-	%$x = \Sigma_i^{1/2}z$, where $z\in\real^p$ consists of i.i.d. entries with mean zero and unit variance, and is a positive semidefinite matrix.
-	We measure covariate shift with matrix $\Sigma_1^{1/2}\Sigma_2^{-1/2}$.
-\squishend
-\fi
+\section{Introduction}\label{sec_introduction}
 
@@
 
+\begin{figure*}[!t]
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.5\textwidth,valign=t]{figures/mtl_model_arch.pdf}
+		\caption{A hard parameter sharing architecture}
+	\end{subfigure}\hfill
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.713\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
+		\caption{Varying sample size ratio}
+		\label{fig_intro_sample_size_b}
+	\end{subfigure}
+	\caption{An illustrative example of our result:
+	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
+	Increasing task one's sample size decreases task two's prediction loss initially, but increases afterwards.
+This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
+Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
+	See Section \ref{sec_simulation} for the precise setting.}
+	\label{fig_intro_sample_size}
+\end{figure*}
+
 This paper presents new techniques to study hard parameter sharing and establish a number of new results.

### 2020-10-13 arxiv/intro.tex
abstract

@@
 \begin{abstract}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that their generalization properties have not been established in many cases.
+	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that their generalization properties have not been well established in many cases.
 This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks?
@@
 We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
+Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing the variance but hurts eventually due to the increasing bias.
 This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.

### 2020-10-13 arxiv_full_version/same_cov.tex
start formatting

\section{A Bias-variance Decomposition for Multiple Tasks}\label{sec_same}

%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
%We provide a sharp generalization error bound of hard parameter sharing estimators.
In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same sample size and features.
%\FY{Is it should be "same covariate" or "same covariates"?}
%This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
%\begin{align}
%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
%\end{align}
%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
%Compared to the prediction loss of single-task learning (cf. equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
%We show the generalization error of hard parameter sharing estimators.
%Before stating the result, we define the following notations.

\paragraph{Setting.} Suppose we have $t$ datasets whose samples size are all equal to $n$ and whose features are all denoted by $X \in \real^{n \times p}$, and the label (vector) of the $i$-th task follows a linear model $Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}$.
Let $\Sigma\in \R^{p\times p}$ denote the population covariance matrix of all tasks.
We assume that:
\begin{itemize}
	\item $X = Z \Sigma^{1/2}$ and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with mean zero, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$;
	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional ditribution with mean zero, variance $\sigma^2$, and bounded moment up to any order.\footnote{More precisely, there exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
\end{itemize}
For an estimator $\hat{\beta}_i$ of task $i$, we are interested in its (out-of-sample) prediction loss
\[ L(\hat{\beta}_i) = \bignorm{\Sigma^{1/2} (\hat{\beta_i} - \beta^{(i)})}^2. \]

Our main result shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
To formalize this intuition, we introduce several notations.
Let $B^\star \define [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$.
Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$:\footnote{To ensure that $A^{\star}$ is unique, we assume that $\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.}
\[ A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}}. \]
Let $a_i^{\star} \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$.
We show that the prediction loss of hard parameter sharing decomposes to a bias term $L(B^{\star} a_i^{\star})$ measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with $\norm{a_i^{\star}}^2$.
% $B^{\star} A^{\star} {A^{\star}}^{\top}$.

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	Assume that $n > \rho p$ for a fixed constant $\rho > 1$.
	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
	Let $\hat{A}, \hat{B}$ be a global minimum of $f(A, B)$.
	For any task $i = 1, 2, \dots, t$, the prediction loss of $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ satisfies that with high probability,
	\begin{align*}
		\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}}
		\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align*}
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
\end{theorem}

%\FY{why not use $C_1: = \frac{ \normFro{\Sigma^{1/2} B^{\star}}^2}{ \lambda_{\min}^2(\Sigma^{1/2} B^{\star}) + \sigma^2}$? $C_2$ does not seem to be correct because the dimension does not match. I will check the proof to see whether $C_2 =  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}^2$ or $C_1\cdot \sigma\norm{\Sigma^{1/2} B^{\star}}$?}
Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
One direct implication of our result is that compared to single-task learning, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
On the other hand, the bias always increases.

\paragraph{How does hard parameter sharing scale with sample size $n$?}
Obviously, the concentration error decreases with $n$.
How about the variance $\bigtr{\Sigma (X^{\top} X)^{-1}}$?
It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.

\begin{assumption}\label{assume_rm}
	Let $\tau > 0$ be a small enough constant.
%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d. entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
	In the high-dimensional setting,
%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
%			\begin{align}\label{assmAhigh}
%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
%			\end{align}
  the sample size $n$ grows to infinity proportionally with the dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
%	\end{enumerate}
\end{assumption}
Under the above assumption, the following result is well-known.

\begin{fact}[cf. Theorem 2.4 in \citet{isotropic}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	With high probability over the randomness of $X$, we have that
		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(n^{-c_{\varphi}}). \]
\end{fact}
Applying \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p}. \]
As a remark, Fact \ref{fact_tr} has a rich history in random matrix theory.
For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
%Finally, for the random noise component, we assume that all of its moments exist.
%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
%\begin{align}\label{assmAhigh2}
%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
%\end{align}
%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.

Next, we consider the bias $L(B^{\star} a^{\star}_i)$.
We illustrate through a random-effects model, which has been studied for a single task case \cite{dobriban2020wonder}.
Suppose every $\beta_i$ consists of two random components, one that is shared among all tasks and one that is task-specific.
Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
Let $\beta_0$ denote the shared component whose entries are sampled i.i.d. from an isotropic Gaussian distribution of mean zero and variance $p^{-1}\kappa^2$.
Let the task-specific component be a random Gaussian vector with i.i.d. entries of mean zero and variance $p^{-1} d^2$.
Thus, for any two different $\beta_i$ and $\beta_j$, their distance is roughly $2d^2$.
%	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
Concretely, we can think of $\kappa = 1$ and $d^2/\sigma^2 = \OO(1)$.
%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.

\begin{example}[Sample efficiency]\label{ex_same_cov}
In the random-effects model described above, we further assume that $\Sigma$ is isotropic for illustration. We show that when the rank of hard parameter sharing is one, the bias $L(B^{\star} a_i^{\star})$ satisfies that with high probability, 
\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
Since $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$, and the $(i, j)$-th entry of this matrix is roughly equal to
%\begin{align*}
%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
%\end{align*}
\begin{align*}
	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \begin{cases}
																								0, &\text{ if } i \neq j \\
																								d^2, &\text{ if } i = j
	\end{cases}
\end{align*}
which follows from the definition of the random-effects model.
Note that $\norm{\beta_0}^2$ is roughly $\kappa^2$.
One can verify that the top eigenvalue of ${B^{\star}}^{\top} B^{\star}$ is approximately $t \kappa^2 + d^2$ and the rest of its eigenvalues are all equal to $d^2$.
Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss as above.

For the variance term, since $A^{\star}$ has rank-$1$, we have that $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$. Moreover, we can use Fact \ref{fact_tr} to calculate $\bigtr{\Sigma (X^{\top} X)^{-1}}$. 
Combined together, the average prediction loss of hard parameter sharing is as follows
\[ \frac{1}{t}\sum_{i=1}^t L(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{1}{t}} {d^2}{} + \frac{1}{t} \cdot \frac{\sigma^2 p}{n - p} \pm \OO(n^{-c_{\varphi} / 2}) .\] %\pm \OO(n^{-c_\varphi} (\sigma^2 +\kappa^2 +d^2)). \]
%In fact, the error for this approximate equation is at most $\OO(n^{-c_\varphi/2} (\sigma^2 +\kappa^2 +d^2))$.
\end{example}
We compare hard parameter sharing to single-task learning.
Using Fact \ref{fact_tr} above, the average prediction loss of single-task learning is $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}  \pm \OO(n^{-c_\varphi} \sigma^2)$ with high probability.
	Suppose $n$ is sufficiently large so that the error is negligible.
\begin{enumerate}
	\item The prediction loss of hard parameter sharing is less than single-task learning if and only if ${d^2}{} < \frac{\sigma^2 p}{n - p}$, that is, the ``task-specific variance'' of $\beta_i$ is smaller than the ``noise variance''.
	\item When ${d^2}{} < \frac{\sigma^2 p}{n - p}$, increasing $r$ does not help.
	To see this, one can verify what when $r$ increases by one, bias reduces by ${d^2}{}$, but variance increases by $\frac{\sigma^2 p}{n-1}$ (details omitted).
	\item Hard parameter sharing requires at most $p + \frac{n - p}{t - (t - 1)\frac{d^2 (n - p)}{\sigma^2 p}} < n$ samples to get comparable loss to single-task learning.
	This follows by using this sample size in the average prediction loss equation above.
\end{enumerate}
%\FY{I think these two facts probably need more clarification?}

\paragraph{Proof overview.} The key idea for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
	Since all tasks have the same covariates, the optimization objective \eqref{eq_mtl} becomes
	\begin{align}
		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
	\end{align}
	where we recall that $B \in \real^{p \times r}$ and $A_1, A_2, \dots, A_t \in \R^r$.
	Let $Y = [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$.
	Using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of the output layers as follows
	\begin{align} \label{eq_Bhat}
		\hat{B}(A) \define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+}
		= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}.
	\end{align}
	Here we have used that $X^{\top}X$ is invertible since $n > \rho p$ (cf. Fact \ref{fact_minv}).
	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on the output layer:
	\begin{align}
		g(A) \define \sum_{j=1}^t \bignorm{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A_j - Y^{(j)}}^2. \label{eq_mtl_output_layer}
	\end{align}
	Let $\hat{A}$ be the global minimizer of $g(A)$. Then  $(\hat{A}, \hat{B}(\hat A))$ is the global minimizer of $f(A, B)$. 
	%Recall that $(\hat{A}, \hat{B})$ is the global minimizer of $f(A, B)$, where $\hat{B}$ is equal to $\hat{B}(\hat{A})$ given by equation \eqref{eq_Bhat}.
	%Furthermore, $\hat{A}$ is a global minimizer of $g(A)$ in equation \eqref{eq_mtl_output_layer}.
	Our next claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
	\begin{claim}\label{claim_opt_dist}
		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
		In the setting of Theorem \ref{thm_many_tasks}, we have that
		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
				\le  p^{-c_{\varphi}} \cdot C_1. \]
	\end{claim}
	The proof of the above claim is based on the following characterization.

	\begin{claim}\label{lem_exp_opt}
		In the setting of Theorem \ref{thm_many_tasks}, we have that
		\begin{align}
			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r). \label{eq_gA}
		\end{align}
		As a result, the minimum of $\ex{g(A)}$, denoted by $A^{\star}{A^\star}^\top$, is the best rank-$r$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star}$.
	\end{claim}

	 One can see that the expected optimization objective also admits a nice bias-variance decomposition.
	Furthermore, its minimizer only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.

	The next piece of our proof deals with the prediction loss of hard parameter sharing.
	\begin{claim}\label{claim_pred_err}
		In the setting of Theorem \ref{thm_many_tasks},
		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
		\begin{align*}
			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
			\le  n^{-1/4} \left( L(B^{\star} \hat{a}_i)+ \sigma^2  \cdot\|\hat a_i\|^2\right) .
		\end{align*}
	\end{claim}
	The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is within an $\OO(n^{-1/4})$ fraction of $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$. Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$. With this estimate, we can bound the difference
		$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
		Combined together, our proof is complete. We omit the details.
%		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
%		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
%		Combined together, our proof is complete.
	\end{proof}

### 2020-10-13 arxiv/diff_cov.tex
formatting

@@
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
-\begin{align}\label{def hatsig}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \ \ \text{ where } \ \ \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
+\begin{align}
+	\hat{\beta}_2^{\MTL} &= {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \ \ \text{ where } \nonumber \\
+	\hat{\Sigma} &= {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
 \end{align}
@@
 \begin{align}
-	\exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}} =
-	& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
+	& \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}  \nonumber \\
+	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
 	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
@@
 	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits.
-
-	\noindent (i) The variance equation \eqref{eq_variance_2task} satisfies the following estimate with high probability:
+	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have that
+	the variance equation \eqref{eq_variance_2task} satisfies the following estimate with high probability:
 			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{p^{-1}\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
+				&\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{\frac{n_1 + n_2}p{\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{p} }}} \nonumber \\
+			&\le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
 			\end{align}
@@
 			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2},\quad a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed vector $w\in\real^p$ with unit norm,
-			\begin{align}\label{lem_cov_derv_eq}
-				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
-			\end{align}
-				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-			\begin{align}\label{eq_a34extra}
-				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \ 
-				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
+				&a_1 + a_2 = 1- \frac{p}{n_1 + n_2},\\
+				&a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
 			\end{align}
 \end{theorem}
-Part (i) of our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
+The bias limit can be found in Section \ref{appendix RMT}.
+Our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
 To see this, when $n_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
@@
 	This gives us the variance limit
-	\[ \frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] = \frac{p}{(n_1 + n_2)(a_1 + a_2)} = \frac{p}{n_1 + n_2 - p}, \]
+	\begin{align*}
+		&\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]  \\
+		=& \frac{p}{(n_1 + n_2)(a_1 + a_2)}
+		= \frac{p}{n_1 + n_2 - p},
+	\end{align*}
 	since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$.
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).
+	  & \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \\
+	\le& \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
@@
 Furthermore, by calculating the derivative of the bias-variance limits with respect to $n_1$, we obtain the following dichotomy (details omitted).
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{2n_2 - 3p}$, the prediction loss decreases monotonically as $n_1$ increases.
+%\begin{enumerate}
+
+(i) When $\frac{d^2}{\sigma^2} < \frac{p}{2n_2 - 3p}$, the prediction loss decreases monotonically as $n_1$ increases.
 	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
+
+(ii) When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
 	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one critical point for the derivative being zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
+%\end{enumerate}
 
@@
 %in the left hand side of equation \eqref{lem_cov_shift_eq}:
-	\[ \bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} \rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
-\]
+\begin{align*}
+	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}} \\
+	&= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
+\end{align*}
 %As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
@@
 We observe the following dichotomy.
-\begin{itemize}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-\end{itemize}
+%\begin{itemize}
+(i) If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
+
+(ii) If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
+%\end{itemize}
 \end{example}
+
 We explain why the dichotomy happens. The variance estimate for this example is equal to
-\begin{align*}
-	\frac{p}{2(n_1 + n_2)} f(\lambda), \ \ \text{ where }\ \  f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
-\end{align*}
+$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
+\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
 Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 }$, we can obtain that
 \begin{align*}
-	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1}
-	+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
+	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
 	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
@@
 In fact, if $a_1>a_2$, then the equations in \eqref{eq_a12extra} give that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and one can verify that
-$$ 
- \frac{n_1}{n_1 + n_2}=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} 
-> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-$$
+\begin{align*}
+ \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
+	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
+\end{align*}
 This implies $n_1>n_2$.
@@
 \begin{align}\label{eigen2extra}
-	W \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
+	\frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
 \end{align}
@@
 %To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
+
+\begin{figure*}[!t]
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/same_covariates.eps}
+		\caption{Example \ref{ex_same_cov}}
+		\label{fig_same_cov}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/sample_ratio_several_d.eps}
+		\caption{Example \ref{ex_sample_ratio}}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/covariate_shift.eps}
+		\caption{Example \ref{ex_covshift}}
+		\label{fig_covariate}
+	\end{subfigure}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks:
+	In Figure \ref{fig_same_cov}, our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
+The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.
+	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in Section \ref{sec_diff} for two tasks:
+	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
+	In Figure \ref{fig_size}, we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
+	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
+	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one.
+Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
+	\label{fig_model_shift_phasetrans}
+\end{figure*}
 
@@
 \cite{Hachem2007deterministic,DS18}).
-We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm, 
-$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
-}$$
 
@@
 %which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
-
-To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
-	\[ \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
-%}\HZ{what does this trick mean? use less technical words},
-%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
-%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
-%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
-%We define the $(n+N)\times (n+N)$ block matrix
- \begin{equation}\label{linearize_block}
-    H \define \left( {\begin{array}{*{20}c}
-   0 & \AF  \\
-   \AF^{\top} & 0
-%   {Z^{(2)}V} & 0 & 0
-   \end{array}} \right).
- \end{equation}
-For this block matrix, we define its resolvent as
-$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$ 
-%as the resolvent of $H$, 
-for any complex value $z\in \mathbb C$.
-Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
-	\begin{equation*} %\label{green2}
-	  G(z) =  \left( {\begin{array}{*{20}c}
-			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
-      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
-		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
-  \end{equation*}
-
-\paragraph{Variance asymptotic limit.}
-In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
-\be \label{defn_piw}
-	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
-where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
-\be
-\begin{split}\label{selfomega_a}
-	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}},  \\
-	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}. 
-% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{split}
-\ee
-The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
-%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
-%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
-%\be\label{ratios}
-% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
-%\ee
-Given this result, we show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
-First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
-Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
-Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$, we get that when $p$ goes to infinity, % the trace of $$ converges to
-\begin{align*}
-  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
-  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}, 
-  \end{align*}
-%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
-%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
-%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
-Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
-Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
-%\begin{align}
-%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
-%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
-%\end{align}
-where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
-%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
-
-\paragraph{Bias asymptotic limit.}
-For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
-First, we reduce the empirical bias term in equation \eqref{lem_cov_derv_eq} to $W$
-\begin{align}\label{calculate G'}
-	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
-\end{align}
-Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
-Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
-Hence, provided that limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
-\begin{align}\label{cal G'0}
-	\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
-\end{align}
-To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of equation \eqref{selfomega_a}.
-%\begin{align*}
-%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
-%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
-%\end{align*}
-Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(z)}{\dd z}$.
-%then taking implicit differentiation of equation \eqref{selfomega_a}
-One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations \eqref{eq_a34extra} (details omitted).
-Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
-%\begin{align}
-%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
-%\end{align}
-%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
-
-As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
-This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.
-
-\paragraph{Schur complement and self-consistent equations.}
-We briefly describe how to derive the matrix limit $\Gi(z)$.
-First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
-By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
-Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
-We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equation \eqref{selfomega_a}.
-On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
-Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
-We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
-A complete proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{appendix RMT}.

### 2020-10-13 arxiv/experiments.tex
formatting

@@
-\section{Numerical Results}\label{sec_exp}
-
-%We validate our  algorithmic insights and then our theory.
-%In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
-%the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
-%Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
-%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
-%In Section \ref{sec_exp_ab}, we validate our theoretical results.
-%We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
-	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
-	\label{fig_same_cov}
-\end{figure}
-
-\subsection{Simulation Studies}\label{sec_simulation}
+\section{Simulation Studies}\label{sec_simulation}
 
@@
 
-\paragraph{Sample efficiency.}
+\textbf{Sample efficiency.}
 First, we study the setting of Example \ref{ex_same_cov}.
@@
 
-\paragraph{Sample ratio.}
+\textbf{Sample ratio.}
 Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
@@
 
-\iffalse
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but increases above the initial loss level.
-Our work explains this trend since the task-specific variance $d^2 = 0.08$ is higher than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
-%We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
-\fi
-
-\paragraph{Covariate shift.}
+\textbf{Covariate shift.}
 Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}. 
@@
 %\end{table}
-
-\begin{figure}[!t]
-%		\begin{subfigure}[b]{0.32\textwidth}
-%		\centering
-%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
-%		\caption{Sample efficiency}
-%		\label{fig_model_shift}
-%	\end{subfigure}\hfill
-	\centering
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_several_d.eps}
-		\caption{Example \ref{ex_sample_ratio}}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
-		\caption{Example \ref{ex_covshift}}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in Section \ref{sec_diff} for two tasks:
-	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
-	In Figure \ref{fig_size}, we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
-	\label{fig_model_shift_phasetrans}
-\end{figure}
-
-\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
-
-Our results and their implications are all in the high-dimensional linear regression setting.
-How well do they extend to other scenarios?
-In this section, we conduct further studies on six text classification datasets, for predicting whether a sentence has a positive or a negative sentiment.
-Our datasets include a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
-%The question is to predict positive or negative sentiment expressed in the text.
-Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
-For LSTM, we add a shared feature representation layer on top of word embeddings.}
-
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-%There are 14 diseases (tasks) for every image that we would like to predict.
-%We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-%We evaluate three model choices.
-%\textit{Predicting transfer effect via STL results.}
-%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-%A common challenge in the study of MTL is that the results can be hard to understand.
-%It is difficult to predict when MTL performs well without running extensive trials.
-%Our insight is that we can use STL results to help understand MTL results.
-%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
-
-\paragraph{Sample size ratio.}
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
-On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops:
-%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
-\begin{itemize}
-	\item We divide the source task data into $S$ batches.
-	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
-	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
-%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\end{itemize}
-For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
-The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-
-%\begin{algorithm}[!t]
-%	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-%		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, W_2$ optimized for task $2$.
-%		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}
-
-%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-%\squishlist
-%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-%TREC is less similar to MR because the task is about question types.
-%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ pairs from the six datasets.
-We find that adding task one's samples progressive requires only $45\%$ of the computational cost to achieve the same test accuracy for task two than standard round-robin training schedules.
-%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we conduct multi-task training on all six datasets.
-We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than standard round-robin training schedules.
-%As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-\begin{figure}%[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
-		\caption{HPS vs. STL}
-		\label{fig_ab_data}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
-		\caption{HPS vs. covariance alignment}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
-	\label{fig_text}
-%	\begin{minipage}[t]{0.4\textwidth}
-%		\centering
-%		\vspace{0pt}
-%		\begin{tabular}{c c c}
-%		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-%		& all tasks & w/o TREC \\
-%		\midrule
-%		{\bf MLP}  & 31\% & 29\% \\
-%		{\bf LSTM} & 35\% & 34\% \\
-%		{\bf CNN}  & 30\% & 28\% \\
-%		\bottomrule
-%		\end{tabular}
-%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
-%		\label{tab:taskonomy}
-%	\end{minipage}
-\end{figure}
-
-%	\begin{subfigure}[b]{0.33\textwidth}
-%		\centering
-%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-%		\caption{Task similarity}
-%		\label{fig_ab_sim}
-%	\end{subfigure}%
-%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c)
-%	Note: (S) denotes the source task and (T) denotes the target task.}
-
-%\begin{minipage}[t]{.58\textwidth}
-%	\vspace{-0.1in}
-%	\centering
-%  \begin{tabular}{c c c c c}
-%	\toprule
-%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%		& Precision &  Recall & Precision &  Recall \\
-%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
-		% 0.3 & 1.000 & 0.004 &     - &     - \\
-%	\bottomrule
-%	\end{tabular}
-%	\vspace{0.1in}
-%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-%	\label{tab:mtl_better_than_stl}
-%\end{minipage}%
-%\quad
-
-\paragraph{Covariate shift.}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample ratio rises.
-To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \citet{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
-
 %\begin{figure}[!t]
 %	\centering
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-%		\caption{Averaged over all 16 task pairs}
-%		\label{fig_ab_cov}
-%	\end{subfigure}\hfill
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{An example task pair}
-%		\label{fig_cov_a}
-%	\end{subfigure}
-%	\caption{ (TREC and CR)}
+%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
+%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
+The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
+%	\label{fig_same_cov}
 %\end{figure}
-
-%\textbf{Further results of the covariance alignment procedure.}
-%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
-%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
-%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
-%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
-%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
-%We leave this question for future work.
-%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
-
-%\begin{figure}[!h]
-%	\centering
-%	\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{Task pair TREC and CR}
-%		\label{fig_cov_a}
-%	\end{subfigure}\hfill
-%		\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-%		\caption{Task pair MR and SST}
-%			\label{fig_cov_b}
-%	\end{subfigure}
-%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
-%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
-%	\label{fig_covariate_app}
-%\end{figure}

### 2020-10-13 arxiv/proof_gaussian_case.tex
section 5 wip
restructure B.2
introduction wip;
formatting

@@
-\section{Missing Proof of the Different Covariates Setting}\label{sec_maintools}
+\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
 
-\subsection{Proof of the Bias and Variance Asymptotics}\label{appendix RMT}
+	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed vector $w\in\real^p$ with unit norm,
+			\begin{align}\label{lem_cov_derv_eq}
+				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
+			\end{align}
+				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+			\begin{align}\label{eq_a34extra}
+				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \
+				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
+%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+%				= b_0.
+			\end{align}
 
-We provide the proof of Theorem \ref{thm_main_RMT}.
+We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm,
+$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
+}$$
+
+To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
+	\[ \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
+%}\HZ{what does this trick mean? use less technical words},
+%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
+Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
+%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
+%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
+%We define the $(n+N)\times (n+N)$ block matrix
+ \begin{equation}\label{linearize_block}
+    H \define \left( {\begin{array}{*{20}c}
+   0 & \AF  \\
+   \AF^{\top} & 0
+%   {Z^{(2)}V} & 0 & 0
+   \end{array}} \right).
+ \end{equation}
+For this block matrix, we define its resolvent as
+$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$
+%as the resolvent of $H$,
+for any complex value $z\in \mathbb C$.
+Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
+	\begin{equation*} %\label{green2}
+	  G(z) =  \left( {\begin{array}{*{20}c}
+			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
+      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
+		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
+  \end{equation*}
+
+\paragraph{Variance asymptotic limit.}
+In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
+\be \label{defn_piw}
+	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
+where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
+\be
+\begin{split}\label{selfomega_a}
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}},  \\
+	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
+% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
+\end{split}
+\ee
+The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
+%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
+%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
+%\be\label{ratios}
+% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
+%\ee
+Given this result, we show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
+First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
+Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
+Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$, we get that when $p$ goes to infinity, % the trace of $$ converges to
+\begin{align*}
+  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
+  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}},
+  \end{align*}
+%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
+%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
+%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
+Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
+Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
+%\begin{align}
+%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
+%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
+%\end{align}
+where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
+%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
+
+\paragraph{Bias asymptotic limit.}
+For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
+First, we reduce the empirical bias term in equation \eqref{lem_cov_derv_eq} to $W$
+\begin{align}\label{calculate G'}
+	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
+\end{align}
+Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
+Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
+Hence, provided that limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
+\begin{align}\label{cal G'0}
+	\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
+\end{align}
+To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of equation \eqref{selfomega_a}.
+%\begin{align*}
+%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
+%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
+%\end{align*}
+Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(z)}{\dd z}$.
+%then taking implicit differentiation of equation \eqref{selfomega_a}
+One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations \eqref{eq_a34extra} (details omitted).
+Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
+%\begin{align}
+%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+%\end{align}
+%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
+
+As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
+This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.
+
+\paragraph{Schur complement and self-consistent equations.}
+We briefly describe how to derive the matrix limit $\Gi(z)$.
+First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
+By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
+Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
+We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equation \eqref{selfomega_a}.
+On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
+Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
+We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
+A complete proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{appendix RMT}.
+
 We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.

### 2020-10-13 arxiv/proof_same_cov.tex
formatting

@@
 \section{Missing Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_error_same_cov}
+
+	Our next claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
+	\begin{claim}\label{claim_opt_dist}
+		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
+		In the setting of Theorem \ref{thm_many_tasks}, we have that
+		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
+				\le  p^{-c_{\varphi}} \cdot C_1. \]
+	\end{claim}
+	The proof of the above claim is based on the following characterization.
+
+	\begin{claim}\label{lem_exp_opt}
+		In the setting of Theorem \ref{thm_many_tasks}, we have that
+		\begin{align}
+			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).
+\label{eq_gA}
+		\end{align}
+		As a result, the minimum of $\ex{g(A)}$, denoted by $A^{\star}{A^\star}^\top$, is the best rank-$r$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star}$.
+	\end{claim}
+
+	 One can see that the expected optimization objective also admits a nice bias-variance decomposition.
+	Furthermore, its minimizer only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.
+
+	The next piece of our proof deals with the prediction loss of hard parameter sharing.
+	\begin{claim}\label{claim_pred_err}
+		In the setting of Theorem \ref{thm_many_tasks},
+		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
+		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
+		\begin{align*}
+			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
+			\le  n^{-1/4} \left( L(B^{\star} \hat{a}_i)+ \sigma^2  \cdot\|\hat a_i\|^2\right) .
+		\end{align*}
+	\end{claim}
+	The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
+	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
+	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
+		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is within an $\OO(n^{-1/4})$ fraction of $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$.
+Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$.
+With this estimate, we can bound the difference
+		$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
+		Combined together, our proof is complete. We omit the details.
+%		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
+%		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
+%		Combined together, our proof is complete.
+	\end{proof}
 

### 2020-10-13 arxiv/intro.tex
typos

@@
 \begin{abstract}
+	\vspace{-0.15in}
 	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that their generalization properties have not been well established in many cases.
@@
 This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
+	\vspace{-0.1in}
 \end{abstract}
 
+\vspace{-0.15in}
 \section{Introduction}\label{sec_introduction}
+\vspace{-0.1in}
 
 Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \citet{C97}.
-Recent work has revived interest in this approach because it improves performance and reduces the cost of collecting labeled data \cite{MTDNN19,ZSSGM18}.
+Recent work has revived interest in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
 It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
@@
 
-Hard parameter sharing offers great intuitive appeal as an inductive transfer mechanism.
+Hard parameter sharing is intuitively appealing as an inductive transfer mechanism.
 It reduces overfitting by acting as a regularizer \cite{R17}.
@@
 Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impacts HPS has not been established.
+However, how these dataset properties impact HPS has not been well established.
 %It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered when all tasks' sample sizes are equal to logarithm factors of feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
+Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
+Previous results based on Rademacher complexity or VC dimensions have considered cases when all tasks' sample sizes are equal to logarithm factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
@@
 		\centering
-		\includegraphics[width=0.5\textwidth,valign=t]{figures/mtl_model_arch.pdf}
+		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
 		\caption{A hard parameter sharing architecture}
@@
 		\centering
-		\includegraphics[width=0.713\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
+		\includegraphics[width=0.6417\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
 		\caption{Varying sample size ratio}
@@
 	\end{subfigure}
+	\vspace{-0.1in}
 	\caption{An illustrative example of our result:
@@
 	\label{fig_intro_sample_size}
+	\vspace{-0.1in}
 \end{figure*}

### 2020-10-13 arxiv/setup.tex
typos

@@
 \subsection{Setup and Main Results}
-
-%Suppose we have $t$ labeled regression tasks. %where $t$ is a fixed value that does not grow with the feature dimension $p$.
-%For each task $k$ from $1$ to $t$, we have $n_k$ samples $x_1, x_2, \dots, x_{n_k}$ that are all $p$-dimensional feature vectors with real-valued labels $y_1, y_2, \dots, y_{n_k}$.
-%Without loss of generality, we focus on predicting the $t$-th task and refer the $t$-th task as the target.
-%We refer to task $1$ to task $t-1$ as source tasks.
-%We assume that the labels of each task $k$ satisfy the linear model with unknown parameters $\beta_k\in\real^p$, that is,
-%	\[ y_i = x_i^{\top}\beta_k + e_i, \text{ for all } 1 \le i \le n_k, \]
-%where $e_i$ denotes random noise with mean zero and variance $\sigma^2$.
-%To write the above notations more succiently, let $X_k \in \real^{n_k \times p}$ denote the covariates that consists of a feature vector in every row.
-%Let
-%	\be\label{model_YvsX} Y^{(k)} = X^{(k)} \beta_k + \varepsilon_k, \text{ for all } 1\le k \le t \ee denote the label vector of task $k$ and $\varepsilon_k$ denote an i.i.d.
-random vector with mean zero and variance $\sigma^2$.
-%Following \citet{HMRT19} and \citet{BLLT20},
-%In the high-dimensional linear regression setting (e.g.
-), the features of the $k$-th task, denoted by $X_k\in\real^{n_i\times p}$, consist of $n_k$ feature vectors given by $x_1, x_2, \dots, x_{n_k}$.
-%we assume that for each task $k$ from $1$ to $t$, each feature vector $x_i = \Sigma^{1/2}_k z_i$ for $i = 1, \dots, n_k$, where $z_i\in\real^p$ is an i.i.d.
-random vector with  mean zero and unit variance.
-%Recall that $\Sigma_k$ is the population covariance matrix task $k$'s feature vectors.
-%Let $\Sigma_k = U_k D_k U_k^{\top}$ denote the singular value decomposition of $\Sigma_k$.
-%We denote $\Sigma_k = U_k D_k^{1/2}$ as the square root of $\Sigma_k$.
-%The sample size of task $k$, given by $n_k$, is equal to $\rho_k\cdot p$ for a fixed value $\rho_k$ that does not grow with feature dimension $p$.
-%This setting is also known as the high-dimensional linear regression setting in the literature.
-%There are two motivations for studying the high-dimensional linear regression setting for multi-task learning.
-%First, this setting captures salient properties of modern large-scale datasets, where the sample sizes are usually on the order of tens to hundreds of the number of features \cite{sur2019modern}.
-%Second, as we will see soon in Section \ref{sec_general}, we can derive precise asymptotics of the generalization error that scale with properties of the task data such as sample sizes.
-%The labels $Y_k = X_k \beta_k + \varepsilon_k$, where $\beta_k$ denotes the linear model parameters and $\varepsilon_k$ denotes i.i.d. noise with mean zero and variance $\sigma^2$.
-%Recall that we have $t$ labeled training datasets, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
-%Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d.
-entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
-%Without loss of generality, let the $t$-th task be the target task.
 
@@
 In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
+
 We study a hard parameter sharing architecture to learn jointly from multiple datasets.
@@
 %	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
+\vspace{-0.1in}
 \begin{align}\label{eq_mtl}
@@
 \end{align}
-Given a solution $(\hat{A}, \hat{B})$ to the above optimization problem, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the hard parameter sharing (HPS) estimator for task $i$.
+%\vspace{-0.1in}
+Given a solution $(\hat{A}, \hat{B})$ of $f(A, B)$, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
 Some critical questions are:
@@
 
-%	\item Learn the output layers $W_1, W_2, \dots, W_t$: set $B = \hat{B}$ and minimize the training loss over $W_1, W_2, \dots, W_t$.
-%		{\begin{align}\label{eq_mtl_eval}
-%			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k \hat{B} W_k - Y_k}^2.
-%		\end{align}}
-%\end{enumerate}
-%Let $\hat{\beta}_t^{\MTL}$ denote the multi-task learning estimator obtained from the procedure above.
-%By contrast, let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$ denote the single-task learning estimator. % denoted by $L(\hat{\beta}_t^{\STL})$.
-%where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
-%Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
-%\smallskip
-%\noindent\textit{Remark.}
-%In general, the multi-task learning objective $f(\cdot)$ is non-convex with respect to $B$ and $W_1, \dots, W_t$.
-%Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
-%For our results later in Section \ref{sec_general} and \ref{sec_special}, we will identify tractable cases and provide guarantees to the above procedure.
-%\paragraph{Problem statement.}
-%We focus on predicting a particular task, say the $t$-th task, without loss of generality.
-%For an estimator $\hat{\beta}$ of the target task model $\beta_t$, we define the prediction loss of the estimator $\hat{\beta}$ as
-%	{\begin{align}\label{eq1_prediction_loss}
-%		\te(\hat{\beta}) = \exarg{x = \Sigma_t^{1/2} z}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
-%		= \bignorm{\Sigma_t^{1/2} (\hat{\beta} - \beta_t)}^2,
-%	\end{align}}%
-%where $x = \Sigma_t^{1/2} z$ denotes a random feature vector with covariance $\Sigma_t$.
-%In the above equation, $x^{\top}\beta_t$ is the true label of $x$.
-%= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)
-%We say that the source tasks provide a \textit{positive transfer} to the target task if the prediction loss of the MTL estimator is lower than that of the STL estimator, that is, if
-%	\[ L(\hat{\beta}_t^{\MTL}) > L(\hat{\beta}_t^{\STL}). \]
-%On the other hand, we say that the source tasks provide a \textit{negative transfer} to the target task if $L(\hat{\beta}_t^{\MTL}) < L(\hat{\beta}_t^{\STL})$.
-%Our goal is to study when the source tasks provide a positive transfer to the target task.
-%More specifically, we study how varying properties of task data including task similarity, sample ratio, and covariate shift affects information transfer in multi-task learning.
-
-%We begin by defining our problem setup including the multi-task estimator we study.
-%Then, we describe the bias-variance tradeoff of the multi-task estimator and connect the bias and variance of the estimator to \textit{task similarity}, \textit{sample size}, and \textit{covariate shift}.
-%Finally, we show a tight concentration bound for the bias and variance quantities using random matrix theory.
-
-%\subsection{Problem Formulation}
-
-%In the worst case, the optimization objective \eqref{eq_mtl} is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%Therefore, we work in cases where a global and/or local minimum characterization is possible
-
-\paragraph{Main results.}
+\textbf{Main results.}
 Our first result (Theorem \ref{thm_many_tasks}) applies to the multi-label prediction setting where all datasets have the same features, and we want to make multiple predictions (see e.g.
@@
 We show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition.
-Our results imply that hard parameter sharing helps by reducing variance compared to single-task learning, but hurts by increasing bias.
+Our results imply that hard parameter sharing helps by reducing the variance compared to single-task learning, but hurts by increasing the bias.
 Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and population covariance matrices.
@@
 
-\begin{figure}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.5\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.713\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\caption{An illustrative example of our result:
-	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
-	Increasing task one's sample size decreases task two's prediction loss initially, but increases afterwards.
-This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure}
+Consequently, using our precise loss estimates, we observe several qualitative properties of hard parameter sharing for varying datasets' properties.
+%\begin{enumerate}
 
-Consequently, using our precise loss estimates, we observe qualitative properties of hard parameter sharing for varying datasets' properties.
-\begin{enumerate}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
+\textit{Sample efficiency (Example \ref{ex_same_cov})}:
 	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that \citet{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variance vs.
-noise variance.
-It is generally high when the noise variance is large compared to model-specific variance across different tasks.
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help to reduce another task's loss.
+	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance, and is generally high when the latter is large.
+
+\textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help to reduce another task's loss.
 In a simplified setting, we find that the task loss either decreases first before increasing afterwards, or decreases monotonically depending on how fast the bias increases.
-These two trends result from different tradeoffs between increasing bias and decreasing variance.
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
+These two trends result from different bias-variance tradeoffs.
+
+\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
 For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
 Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-\end{enumerate}
+%\end{enumerate}
 
@@
 Using recently developed techniques from random matrix theory \cite{Anisotropic}, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
-Theorem \ref{thm_main_RMT}(i)).
+Theorem \ref{thm_main_RMT}).
 % Moreover, we can obtain a sharp bound on the concentration error.
@@
 equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
-This requires studying the spectrum of non-symmetric random matrices, which is an intriguing open question (see Section \ref{sec_conclude} for more discussion).
+This requires studying the singular value spectrum of certain non-symmetric random matrices, which is an intriguing open question (see Section \ref{sec_conclude} for more discussion).
 % plus an identity matrix,  due to lack of freeness
@@
 The early work of \citet{B00,BS03,M06} have sought for a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \citet{BBCK10} provides uniform convergence bound that combines multiple datasets in certain settings.
+An influential paper by \citet{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
 One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \citet{B00,MPR16}.
@@
 
-\smallskip
-\noindent\textbf{Organizations.}
+\textbf{Organizations.}
 The rest of this paper is organized as follows.
@@
 
-\paragraph{Notations.}
+\textbf{Notations.}
 %Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.

### 2020-10-13 arxiv/tools.tex
typos

@@
 	\begin{enumerate}
-		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
+		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is of full rank.
 		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf.
@@
 
-As a corollary, we can obtain the following concentration estimates for random variables with bounded moments as in equation \eqref{assmAhigh}.
+As a corollary, we can obtain the following concentration estimates for random variables with bounded $\varphi$-th moment.
 
@@
  \begin{proof}
-
+Note that $\epsilon^{(i)}_j/\sigma$, $1\le i \le t,1\le j \le n$, are i.i.d.
+random variable of mean zero, variable one and bounded moments up to any order.
+Then using the first estimate in equation \eqref{eq largedev1}, we can obtain that $|v^\top \epsilon^{(i)}| = \Big|\sum_{j=1}^n v_j \epsilon^{(i)}_j \Big| \prec \sigma \|v\|,$  which concludes \eqref{vcalE} together with the definition of stochastic domination in Definition \ref{stoch_domination}.
+Similarly, using the second estimate in equation \eqref{eq largedev1}, we can obtain that for $i\ne j$,
+ \begin{align*}
+\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \prec \sigma^2 \Big(\sum_{k,l}|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
+ \end{align*}
+Using the two estimates in equation \eqref{eq largedev2}, we obtain that 
+\begin{align*}
+\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
+&\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
+\end{align*}
+The above two estimates conclude  \eqref{vcalA2}.
+Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.
  \end{proof}

### 2020-10-13 arxiv/diff_cov.tex
typos

@@
 The previous section assumes that all tasks have the same sample size and feature vectors.
-This section studies how different sample sizes and different features impact hard parameter sharing.
+In this section, we study how different sample sizes and different features impact hard parameter sharing.
 %The different covariates case differs from the same covariates case in two aspects.
 %First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-The setting where features differ across tasks is often also called ``covariate shift''.
+The setting where features differ across tasks is often called ``covariate shift''.
 
-Unlike the previous section, we no longer have an optimal solution for $f(A, B)$.
+Unlike the previous section, we no longer have an optimal solution to $f(A, B)$.
 This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies tight generalization bounds for any \emph{local minimum} of $f(A, B)$.
+Instead, our result implies tight generalization bounds for any \emph{local minimizer} of $f(A, B)$.
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
@@
 Our key result characterizes the asymptotic limit of the inverse of the sum of two different sample covariance matrices.
-To motivate our study, consider a special case where $A_1=A_2=1$. 
 Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
@@
 When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-Hence we can write down a closed form equation for any local minimum of $f(A, B)$.
+To motivate our study, we consider a special case where $A_1=A_2=1$. 
+%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
@@
 \end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariances, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
+The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
 
@@
 To see this, when $n_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
+We also remark that for general $A_1$ and $A_2$ that are not equal to 1, we need to replace $\hat \Sigma$ with $\frac{A_1^2}{A_2^2}{X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}$.
+This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
 

### 2020-10-14 arxiv/diff_cov.tex
sec 3 revise

@@
 
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to its expectation similar to Claim \ref{claim_pred_err}):
+ To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is actually close to this expectation as will be shown in equation \eqref{claim_largedev2}):
+ %similar to Claim \ref{claim_pred_err}
 \begin{align}
@@
 \end{align}
-Equation \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of hard parameter sharing for two tasks, respectively.
-Our main result in this section characterizes the asymptotic bias-variance limits under the high-dimensional assumption.
+Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of hard parameter sharing for two tasks, respectively.
+Our main result in this section characterizes the asymptotic bias-variance limits in the high-dimensional setting.
 Intuitively, the spectrum of $\hat{\Sigma}^{-1}$ (and hence its trace) not only depends on both tasks' sample sizes, but also depends on the ``alignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
@@
 \begin{theorem}\label{thm_main_RMT}
-	Let $c_{\varphi}$ be a fixed value in $(0, \frac{\varphi - 4}{2\varphi})$.
+	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
 	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
@@
 	the variance equation \eqref{eq_variance_2task} satisfies the following estimate with high probability:
-			\begin{align}\label{lem_cov_shift_eq}
-				&\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{\frac{n_1 + n_2}p{\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{p} }}} \nonumber \\
-			&\le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
+			\begin{align}
+				&\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{ {\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{n_1+n_2} }}}\nonumber \\
+				&\le  p^{-c_{\varphi}}, \label{lem_cov_shift_eq} %\norm{\Sigma^{(2)}},
 			\end{align}
@@
 			\begin{align}
-				&a_1 + a_2 = 1- \frac{p}{n_1 + n_2},\\
+				&a_1 + a_2 = 1- \frac{p}{n_1 + n_2},\label{eq_a12extra000}\\
 				&a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
@@
 Our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
-To see this, when $n_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
+To see this, when $n_1$ is zero, we solve equations \eqref{eq_a12extra000} and  \eqref{eq_a12extra} to obtain that $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
 We also remark that for general $A_1$ and $A_2$ that are not equal to 1, we need to replace $\hat \Sigma$ with $\frac{A_1^2}{A_2^2}{X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}$.
@@
 We now show that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, and hence explain the dichonomy.
+
+\iffalse
+In Example \ref{ex_covshift}, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations \eqref{lem_cov_shift_eq}.
+Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
+The other case when $n_1 < n_2$ is similar.
+A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
+Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
+If $n_1< n_2$, then $f(\lambda)< f(1)$.
+\fi
+
 In fact, if $a_1>a_2$, then the equations in \eqref{eq_a12extra} give that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and one can verify that

### 2020-10-14 arxiv/diff_cov.tex
sec 3 revise

@@
 
-Let $U\Lambda V^\top$ denote the SVD of $M$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote $M$'s singular values in descending order.
+%Let $U\Lambda V^\top$ denote the SVD of $M$ and 
+Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote $M$'s singular values in descending order.
 Our main result is stated as follows.
@@
 				&\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{ {\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{n_1+n_2} }}}\nonumber \\
-				&\le  p^{-c_{\varphi}}, \label{lem_cov_shift_eq} %\norm{\Sigma^{(2)}},
+				\le & p^{-c_{\varphi}}, \label{lem_cov_shift_eq} %\norm{\Sigma^{(2)}},
 			\end{align}
@@
 \end{theorem}
-The bias limit can be found in Section \ref{appendix RMT}.
+The bias limit can be found in equation \eqref{lem_cov_derv_eq}.
 Our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
 To see this, when $n_1$ is zero, we solve equations \eqref{eq_a12extra000} and  \eqref{eq_a12extra} to obtain that $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
-We also remark that for general $A_1$ and $A_2$ that are not equal to 1, we need to replace $\hat \Sigma$ with $\frac{A_1^2}{A_2^2}{X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}$.
+We also remark that for general $A_1$ and $A_2$, we need to replace $\hat \Sigma$ with $\frac{A_1^2}{A_2^2}{X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}$.
 This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
@@
 \paragraph{How does hard parameter sharing scale with sample size and covariate shift?}
-One can see that the bias-variance limits depend intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact prediction loss, respectively.
+One can see that both the variance limit and the bias limit (in equation \eqref{lem_cov_derv_eq}) depend intricately on both tasks' samples sizes and covariate shift.
+Next, we illustrate how varying them impact the prediction loss.
 \begin{example}[Sample size ratio]\label{ex_sample_ratio}
@@
 
-	Applying Theorem \ref{thm_main_RMT} to the above setting, we first solve the self-consistent equations \eqref{eq_a12extra} by using $\lambda_i = 1$ for all $1\le i\le p$.
-	This gives us the variance limit
+	Applying Theorem \ref{thm_main_RMT} to the above setting, we first solve the self-consistent equations \eqref{eq_a12extra000} and \eqref{eq_a12extra} using $\lambda_i = 1$ for all $1\le i\le p$.
+	This gives us the following variance limit by equation \eqref{eq_a12extra000}: 
 	\begin{align*}
@@
 	\end{align*}
-	since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$.
-	Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
+	%since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$.
+	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
+	Similarly, we can calculate the bias limit using equation \eqref{lem_cov_derv_eq}. 
 	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
@@
 %	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$.
+	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
 	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-	The prediction loss of hard parameter sharing for task two satisfies that
-	\begin{align}\label{cor_MTL_error}
+	The prediction loss of hard parameter sharing for task two satisfies that with high probability,
+	\begin{align}
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  & \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \\
-	\le& \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).
+	  & \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \nonumber\\
+	\le& \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
@@
 The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $\hat A$ and $\hat B$.
-By combining the bias and variance limits, we can also obtain a generalization bound for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
+As a remark, in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$.
+By combining the bias and variance limits, we can also obtain a generalization bound for any local minimizer of $f(A, B)$ in a similar way.
+%The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
 
-Next, we illustrate an interesting phenomenon where adding task one's samples helps task two initially, but hurts eventually.
+Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
 Consider the limiting estimate on the left hand side of equation \eqref{cor_MTL_error}.
@@
 %We describe a sketch of the proof.
-The variance term always reduces as $n_1$ increases.
-The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
+The variance term always reduces as $n_1$ increases, while the bias term always increases as $n_1$ increases (which can be verified by calculating the derivative of the bias term).
 Furthermore, by calculating the derivative of the bias-variance limits with respect to $n_1$, we obtain the following dichotomy (details omitted).
@@
 
-(ii) When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one critical point for the derivative being zero, which corresponds to the \textit{optimal sample size ratio}.
+(ii) When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
+	To see this, near the point where $n_1$ is zero, one can verify that the bias increases slower than the variance decreases, and there is only one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
 %\end{enumerate}
@@
 %In general, the covariance matrices of the two tasks may be different such as in text classification.
-Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}, which shows that
+Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}, which gives that
 %in the left hand side of equation \eqref{lem_cov_shift_eq}:
@@
 %As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit is determined by the spectrum of $M$.% To be clear, for this example we assume that the bias is $0$.
-
+Hence the variance limit is determined by the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
 To illustrate the above result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
@@
 %\begin{itemize}
+
 (i) If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
@@
 \[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 }$, we can obtain that
+With equation \eqref{eq_a12extra000} and a straightforward calculation (details omitted), we can verify that
+%\begin{align*}
+%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
+%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
+%\end{align*}
 \begin{align*}
-	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
+	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
 \end{align*}
-where $g(\lambda, a_1) > 0$ is a fixed function and can be derived from algebraic calculations (details omitted).
-We now show that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, and hence explain the dichonomy.
+where $g(\lambda, a_1) \ge 0$ is a fixed function. 
+%and can be derived from algebraic calculations (details omitted).
+We claim that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, which explains the dichonomy.
+In fact, if $a_1>a_2$, then equation \eqref{eq_a12extra000} gives that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and equation \eqref{eq_a12extra} gives that
+\begin{align*}
+ \frac{n_1}{n_1 + n_2} &> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) >\frac{1}{2}.
+\end{align*}
+%\begin{align*}
+% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
+%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
+%\end{align*}
+This implies $n_1>n_2$. Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$. 
+%Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
 
 \iffalse
-In Example \ref{ex_covshift}, $a_1$ and $a_2$ have a symmetric role in the self-consistent equations \eqref{lem_cov_shift_eq}.
+%FY: Below was the word explanation. I still think the above simple proof is clearer.
+In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
 Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
 The other case when $n_1 < n_2$ is similar.
-A formal proof requires solving the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
+A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
 Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
@@
 \fi
-
-In fact, if $a_1>a_2$, then the equations in \eqref{eq_a12extra} give that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and one can verify that
-\begin{align*}
- \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-\end{align*}
-This implies $n_1>n_2$.
-Similarly, if $a_1<a_2$, equations in \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
 
@@
 \begin{align}\label{eigen2extra}
-	\frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
+	\frac{\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V}{n_1 + n_2}.
 \end{align}
+Here $U\Lambda V^\top$ is defined as the SVD of $M$.
 This formulation is helpful because we know that ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance, and $U, V$ are both orthonormal matrices.
@@
 Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
-We briefly describe the key ideas and refer interested readers to classical texts such as  \citet{bai2009spectral,tao2012topics,erdos2017dynamical}.
-For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
-$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \ \ \text{ for any complex number } z\in \C\setminus [0,\infty).$$
+We briefly describe the key ideas and refer the interested readers to classical texts such as  \citet{bai2009spectral,tao2012topics,erdos2017dynamical}.
+For any probability measure $\mu$ supported on $[0,\infty)$ and complex number $ z\in \C\setminus [0,\infty)$, the Stieltjes transform of $\mu$ is a complex function defined as
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z} .$$ %, \ \ \text{ for any complex number } z\in \C\setminus [0,\infty).$$
 The Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
@@
 %Compared to the Stieltjes transform, the resolvent also applies to random matrices.
-We will prove the convergence of $W$'s resolvent using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
+We will prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
+The full details will be given in Section \ref{appendix RMT}.
 %Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.

### 2020-10-14 arxiv/conclusions.tex
typos

@@
 This work proposed a formal study of a widely used hard paramaeter sharing approach in high-dimensional linear regression, where the sample size and feature dimension increase at a fixed ratio.
-We provided tight generalization bounds that scale with dataset properties such as their sample sizes and covariate shifts.
+We provided tight generalization bounds that scale with dataset properties such as the sample sizes and covariate shifts.
 Based on these bounds, we analyzed the impact of varying sample sizes and covariate shifts on the prediction loss of hard parameter sharing.
@@
 First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic random matrices.
-This requires studying the asymptotic distribution of the {singular values} of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}$, which is still an open problem in random matrix theory.
+Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
+This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
 The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
@@
 Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \cite{sur2019modern}.
+Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \citet{sur2019modern}.
 An interesting question is to study logistic regression in a multiple-sample setting.

### 2020-10-14 arxiv/experiments.tex
typos

@@
 We demonstrate the accuracy of our results via some empirical results.
-While our theory is asymptotic (with error terms that is negligible when $p$ is sufficiently large), we observe that they are accurate in a moderate dimension of $p = 200$.
+While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are accurate in a moderate dimension of $p = 200$.
 
@@
 In all the parameter settings, our results estimate the empirical losses accurately.
-We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
+We also observe a trend that the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
 Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
@@
 Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means more covariate shift.
+Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
 Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.

### 2020-10-14 arxiv/intro.tex
address vaggos comments

@@
 
-Hard parameter sharing is intuitively appealing as an inductive transfer mechanism.
-It reduces overfitting by acting as a regularizer \cite{R17}.
+Hard parameter sharing is an intuitively appealing mechanism for inductive transfer, and reduces overfitting by acting as a regularizer \cite{R17}.
 For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
@@
 Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases when all tasks' sample sizes are equal to logarithm factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
+Previous results based on Rademacher complexity or VC dimensions have considered cases when all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
@@
 		\caption{A hard parameter sharing architecture}
+		\label{fig_intro_arch}
 	\end{subfigure}\hfill
@@
 		\centering
-		\includegraphics[width=0.6417\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
+		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
 		\caption{Varying sample size ratio}
@@
 	\vspace{-0.1in}
-	\caption{An illustrative example of our result:
-	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
-	Increasing task one's sample size decreases task two's prediction loss initially, but increases afterwards.
-This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
+	\caption{
+	Left: an illustrative picture of HPS.
+	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
+	Increasing $n_1/n_2$ decreases task two's prediction loss initially, but increases afterwards.
+This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
 Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
@@
 
-This paper presents new techniques to study hard parameter sharing and establish a number of new results.
+This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
 We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly at a fixed ratio.
-This is motivated by many multi-task learning applications, where the amount of labeled data from each dataset is usually insufficient for learning a single task.
-For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension.
+We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmicly.
+This setting captures the fact that in many applications, a single task's sample size is usually insufficient for accurate learning.
+For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
 The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.

### 2020-10-14 arxiv/setup.tex
address vaggos comments

@@
 
-We assume that there are multiple datasets that all follow (potentially different) linear models.
-In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
-
-We study a hard parameter sharing architecture to learn jointly from multiple datasets.
+%We assume that there are multiple datasets that all follow (potentially different) linear models.
+%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
+Suppose we have $t$ datasets.
+For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
+Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
+We assume that the label vector $Y^{(i)} \in \real^{n_i}$ follows a linear model plus random noise.
+We study the standard hard parameter sharing architecture to learn jointly from multiple datasets.
 In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a separate output layer $A_i \in \real^r$ for every task $i$.
-Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size, $X^{(i)} \in \real^{n_i \times p}$ denote its feature covariates, and $Y^{(i)} \in \real^{n_i}$ denote all the labels.
+See Figure \ref{fig_intro_arch} for an illustration.
 %The width of $B$, denoted by $r$, plays an important role in regularization.
@@
 %For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-Let $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-We study the following optimization objective.
+We study the following minimization problem:
 %	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
@@
 %	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-\vspace{-0.1in}
+%\vspace{-0.1in}
 \begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2.
+			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
 \end{align}
 %\vspace{-0.1in}
-Given a solution $(\hat{A}, \hat{B})$ of $f(A, B)$, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-Some critical questions are:
+where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
+Given a solution $(\hat{A}, \hat{B})$ of $f(A, B)$ (which we will specify later), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+The critical questions here are:
 (i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
@@
 This case is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-We show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition.
-Our results imply that hard parameter sharing helps by reducing the variance compared to single-task learning, but hurts by increasing the bias.
+We show that the prediction loss of HPS admits a clean bias-variance decomposition.
+Our results imply that in the same covariates setting where the sample sizes are also equal, HPS helps by reducing the variance compared to single-task learning, but hurts by increasing the bias.
+
 Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and population covariance matrices.
@@
 See Figure \ref{fig_intro_sample_size} for an illustration.
-
 Consequently, using our precise loss estimates, we observe several qualitative properties of hard parameter sharing for varying datasets' properties.
@@
 \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that \citet{ZSSGM18} has observed empirically.
+	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \citet{ZSSGM18} has observed empirically.
 	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance, and is generally high when the latter is large.
@@
 These two trends result from different bias-variance tradeoffs.
+This result is surprising because previous generalization bounds in MTL typically scale down as the sample sizes of all tasks increase, thus do not apply for different sample sizes.
 
@@
 
+% plus an identity matrix,  due to lack of freeness
+%\HZ{add why this is challenging}
+
+Finally, we discuss the practical implications of our work.
+Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
+For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
+We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
+
+\textbf{Proof techniques.}
 There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
@@
 %\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that for two tasks with different sample sizes, there is an extra error term in the prediction loss of hard parameter sharing (cf.
-equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
-This requires studying the singular value spectrum of certain non-symmetric random matrices, which is an intriguing open question (see Section \ref{sec_conclude} for more discussion).
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
-Finally, we discuss the practical implications of work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
+One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds equation for very small $n_1$ (cf. equation \eqref{cor_MTL_error})).
+We believe that our analysis has provided important initial insight and it is an interesting question to tighten our result (see Section \ref{sec_conclude} for more discussion).
 

### 2020-10-14 arxiv/conclusions.tex
various polish

@@
 
-This work proposed a formal study of a widely used hard paramaeter sharing approach in high-dimensional linear regression, where the sample size and feature dimension increase at a fixed ratio.
-We provided tight generalization bounds that scale with dataset properties such as the sample sizes and covariate shifts.
-Based on these bounds, we analyzed the impact of varying sample sizes and covariate shifts on the prediction loss of hard parameter sharing.
-Our work rigorously explains several empirical phenomena such as sample efficiency and negative transfer related to these dataset properties.
-We validated our results and conducted further studies on a real world classification task.
-
+This work proposed a formal study of a widely used hard paramaeter sharing approach in multi-task learning.
+We provided sharp bias-variance tradeoffs of HPS given multiple linear gression tasks.
+Based on these results, we analyzed how varying sample sizes and covariate shifts impacts HPS.
+Our work rigorously explains several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
+We validated our theory and conducted further studies on a real world classification task.
 We describe several open questions for future work.
-First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+First, it would be interesting to tighten our result in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
+Second, it would be very interesting to extend our result to classification problems such as logistic regression.
+%First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
+%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
 %FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
+%The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
 %but its singular values will follow a different distribution since the matrix is not symmetric.
  %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \citet{sur2019modern}.
-An interesting question is to study logistic regression in a multiple-sample setting.
+%Second, it would be interesting to extend our results to classification problems.
+%Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \citet{sur2019modern}.
+%An interesting question is to study logistic regression in a multiple-sample setting.

### 2020-10-14 arxiv/diff_cov.tex
typos
various polish

@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{figures/same_covariates.eps}
+		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
 		\caption{Example \ref{ex_same_cov}}
@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{figures/sample_ratio_several_d.eps}
+		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
 		\caption{Example \ref{ex_sample_ratio}}
@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{figures/covariate_shift.eps}
+		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
 		\caption{Example \ref{ex_covshift}}
@@
 	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks:
-	In Figure \ref{fig_same_cov}, our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.
-	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in Section \ref{sec_diff} for two tasks:
-	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
-	In Figure \ref{fig_size}, we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
+	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
+	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
 	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one.
+	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
+	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
 Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}

### 2020-10-14 arxiv/experiments.tex
typos
various polish

@@
 
-We demonstrate the accuracy of our results via some empirical results.
-While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are accurate in a moderate dimension of $p = 200$.
+We demonstrate the accuracy of our results in simulations.
+While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.
 
@@
 Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, for $d = 0.2$, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires fewer samples per-task than STL.
+Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level.
 %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
@@
 Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-Again, our estimates are reasonably accurate compared to the empirical losses.
+%Again, our estimates are accurate compared to the empirical losses.
 We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
 The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is $1$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.
+We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
 On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases monotonically.
-Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}. \HZ{check}
+Our result from Corollary \ref{cor_MTL_loss} explains this trend. \HZ{check}
 
@@
 Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
-The noise variance $\sigma^2$ is $1/4$.
+We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
+The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
 %Covariate shift: We set $\kappa = 1$ and $d = 0$.

### 2020-10-14 arxiv/experiments_text.tex
various polish

\section{Further Studies on Text Classification Tasks}\label{sec_text}

Our results and their implications are all in the high-dimensional linear regression setting.
How well do they extend to other scenarios?
In this section, we conduct further studies on six text classification datasets, for predicting whether a sentence has a positive or a negative sentiment.
Our datasets include a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
%The question is to predict positive or negative sentiment expressed in the text.
Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings. For LSTM, we add a shared feature representation layer on top of word embeddings.}

%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.
%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
%There are 14 diseases (tasks) for every image that we would like to predict.
%We use densenet121 as the shared module \cite{huang2017densely}.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
%We evaluate three model choices.
%\textit{Predicting transfer effect via STL results.}
%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
%A common challenge in the study of MTL is that the results can be hard to understand.
%It is difficult to predict when MTL performs well without running extensive trials.
%Our insight is that we can use STL results to help understand MTL results.
%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
%The results show that STL results are indicative of MTL results.

\paragraph{Sample size ratio.}
In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops:
%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
\begin{itemize}
	\item We divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\end{itemize}
For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.

%\begin{algorithm}[!t]
%	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
%	\label{alg_inc_train}
%	\begin{algorithmic}[1]
%		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
%		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
%		\Output The trained modules $B, W_2$ optimized for task $2$.
%		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
%		\For{$i = 1,\dots, S$}
%			\For{$j = 1,\dots, T$}
%				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
%			\EndFor
%			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
%				\State \textbf{break}
%			\EndIf
%		\EndFor
%	\end{algorithmic}
%\end{algorithm}

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
We evaluate the progressive training procedure on the six text classification datasets.
First, we conduct multi-task training over all $15$ pairs from the six datasets.
We find that adding task one's samples progressive requires only $45\%$ of the computational cost to achieve the same test accuracy for task two than standard round-robin training schedules.
%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
Second, we conduct multi-task training on all six datasets.
We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than standard round-robin training schedules.
%As a further validation, excluding TREC, we observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

%	\begin{subfigure}[b]{0.33\textwidth}
%		\centering
%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
%		\caption{Task similarity}
%		\label{fig_ab_sim}
%	\end{subfigure}%
%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
%	(c)
%	Note: (S) denotes the source task and (T) denotes the target task.}

%\begin{minipage}[t]{.58\textwidth}
%	\vspace{-0.1in}
%	\centering
%  \begin{tabular}{c c c c c}
%	\toprule
%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
%		& Precision &  Recall & Precision &  Recall \\
%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
%	\bottomrule
%	\end{tabular}
%	\vspace{0.1in}
%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
%	\label{tab:mtl_better_than_stl}
%\end{minipage}%
%\quad

\paragraph{Covariate shift.}
Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
This highlights the need for correcting covariate shifts when the sample ratio rises.
To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, designed to correct covariate shifts.
The idea is to add an alignment module between the input and the shared module $B$.
This module is then trained together with $B$ and the output layers. We refer to \citet{WZR20} for more details about the procedure and the implementation.
%We validate our insight on this procedure in the experiments.
%We implement the covariance alignment procedure following \cite{WZR20}.

We conduct multi-task training on all $15$ task pairs from the six datasets.
In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
To get a robust comparison, we average the improvements over the 15 task pairs.
The result shows that as the sample ratio increases, performing covariance alignment provides more significant gains over HPS.
We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.

%\begin{figure}[!t]
%	\centering
%	\begin{subfigure}[b]{0.5\textwidth}
%		\centering
%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
%		\caption{Averaged over all 16 task pairs}
%		\label{fig_ab_cov}
%	\end{subfigure}\hfill
%	\begin{subfigure}[b]{0.5\textwidth}
%		\centering
%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
%		\caption{An example task pair}
%		\label{fig_cov_a}
%	\end{subfigure}
%	\caption{ (TREC and CR)}
%\end{figure}

%\textbf{Further results of the covariance alignment procedure.}
%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
%We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

%\begin{figure}[!h]
%	\centering
%	\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
%		\caption{Task pair TREC and CR}
%		\label{fig_cov_a}
%	\end{subfigure}\hfill
%		\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
%		\caption{Task pair MR and SST}
%			\label{fig_cov_b}
%	\end{subfigure}
%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
%	\label{fig_covariate_app}
%\end{figure}

\begin{figure}%[!t]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
		\caption{HPS vs. STL}
		\label{fig_ab_data}
	\end{subfigure}\hfill
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
		\caption{HPS vs. covariance alignment}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}:
	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
	\label{fig_text}
%	\begin{minipage}[t]{0.4\textwidth}
%		\centering
%		\vspace{0pt}
%		\begin{tabular}{c c c}
%		\toprule
		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
		% Sentiment\\ analysis\end{center}\end{minipage}} \\
%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
		% \cmidrule(lr){2-3}
%		& all tasks & w/o TREC \\
%		\midrule
%		{\bf MLP}  & 31\% & 29\% \\
%		{\bf LSTM} & 35\% & 34\% \\
%		{\bf CNN}  & 30\% & 28\% \\
%		\bottomrule
%		\end{tabular}
%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
%		\label{tab:taskonomy}
%	\end{minipage}
\end{figure}

### 2020-10-14 arxiv/setup.tex
various polish

@@
 We assume that the label vector $Y^{(i)} \in \real^{n_i}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture to learn jointly from multiple datasets.
-In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a separate output layer $A_i \in \real^r$ for every task $i$.
+We study the standard hard parameter sharing architecture:
+there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a separate output layer $A_i \in \real^r$ for every task $i$.
 See Figure \ref{fig_intro_arch} for an illustration.
@@
 \end{align}
-%\vspace{-0.1in}
+%\vspace{-0.05in}
 where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
@@
 \textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to the multi-label prediction setting where all datasets have the same features, and we want to make multiple predictions (see e.g.
+Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make multiple predictions (see e.g.
 \cite{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp generalization bound on its (out-of-sample) prediction loss for any task.
-This case is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our results imply that in the same covariates setting where the sample sizes are also equal, HPS helps by reducing the variance compared to single-task learning, but hurts by increasing the bias.
+We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
+This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
+%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
+Our result implies that when all tasks have the same covariates, HPS helps by reducing variance compared to single-task learning, but hurts by increasing bias.
 
@@
 
-\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
+\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
 For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
 Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
+We achieve this result through a novel characterization on the sum of two sample covariance matrices with arbitrary covariate shifts.
+See our discussion of proof techniques below for more details.
 %\end{enumerate}
@@
 In Section \ref{sec_diff}, we present our technical results that describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in both simulations and a real world classification task.
+In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in simulations and real world classification tasks.
 In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.
+Section \ref{app_proof_error_same_cov} and \ref{appendix RMT} present proofs of our results.
 
@@
 %Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
-Let $\lambda_1(X) \ge \lambda_2(X) \ge \cdots \ge \lambda_{p\wedge n}(X)$ denote the singular values of $X$.
-Let $X^+$ denote the Moore-Penrose psuedoinverse.
+For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
+Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
+Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
 We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.

### 2020-10-14 arxiv/setup.tex
edits

@@
 where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution $(\hat{A}, \hat{B})$ of $f(A, B)$ (which we will specify later), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+Given a solution $(\hat{A}, \hat{B})$ of $f(A, B)$ (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
 The critical questions here are:
@@
 Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for more details.
+We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
+See our discussion of proof techniques below for details.
 %\end{enumerate}
@@
 In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in simulations and real world classification tasks.
-In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.
-Section \ref{app_proof_error_same_cov} and \ref{appendix RMT} present proofs of our results.
+In Section \ref{sec_conclude}, we summarize our work and discuss future work.
+Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
 

### 2020-10-14 arxiv/intro.tex
section 1 and 2

@@
 
-Hard parameter sharing is an intuitively appealing mechanism for inductive transfer, and reduces overfitting by acting as a regularizer \cite{R17}.
+Hard parameter sharing works as an inductive transfer mechnism and a regularizer that reduces overfitting, both of which are intuitively appealing \cite{R17}.
 For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.

### 2020-10-14 arxiv/setup.tex
section 1 and 2

@@
 We study the standard hard parameter sharing architecture:
-there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a separate output layer $A_i \in \real^r$ for every task $i$.
+there is a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
 See Figure \ref{fig_intro_arch} for an illustration.
@@
 where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution $(\hat{A}, \hat{B})$ of $f(A, B)$ (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+Given a solution of $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
 The critical questions here are:
@@
 \textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make multiple predictions (see e.g.
-\cite{hsu2009multi}).
+Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
+examples in \citet{hsu2009multi}).
 We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
@@
 
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and population covariance matrices.
-We analyze the local minimizers of $f(A, B)$ and provide a sharp generalization bound on both tasks' prediction loss.
+Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
+While we no longer have a characterization of $f(A, B)$'s global minimum because of non-convexity, for any local minimizer of $f(A, B)$, we provide a sharp bias-variance tradeoff of both tasks' prediction loss.
 Despite its simplicity, we show several interesting phenomena by varying sample sizes and covariate shifts in this setting.
@@
 There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and its population version.
+We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
@@
 %\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds equation for very small $n_1$ (cf. equation \eqref{cor_MTL_error})).
-We believe that our analysis has provided important initial insight and it is an interesting question to tighten our result (see Section \ref{sec_conclude} for more discussion).
+One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error})).
+We believe that our analysis has provided important initial insight and it is an interesting question to tighten our result.
 
@@
 One closely related work is \citet{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-\citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
+However, their results only apply to sample size regimes at least logarithmic factors of dimension.
+%\citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
 %Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.

### 2020-10-15 arxiv/diff_cov.tex
section 3 half done

@@
 This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies tight generalization bounds for any \emph{local minimizer} of $f(A, B)$.
+Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
 We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Suppose that $X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p}$ and $X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p}$, where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+Let $n_1, n_2$ denote task one  and two's sample size, respectively.
+Suppose that
+\begin{align*}
+	X^{(1)} &= Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p}, \text{ and} \\
+	X^{(2)} &= Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
+\end{align*}
+where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
 The matrices $\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
@@
 \paragraph{Bias-variance equations.}
-Our key result characterizes the asymptotic limit of the inverse of the sum of two different sample covariance matrices.
+Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
 Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-By Proposition 1 of \citet{WZR20}, we consider the case of $r = 1 < t = 2$, since when $r > 1$, the optimal solution of $f(A, B)$ is equivalent to single-task learning.
+By Proposition 1 of \citet{WZR20}, we consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ is equivalent to single-task learning.
 When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
 To motivate our study, we consider a special case where $A_1=A_2=1$.
+Hence the HPS estimator is equal to $B$.
 %Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
+By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
 \begin{align}
@@
 
- To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is actually close to this expectation as will be shown in equation \eqref{claim_largedev2}):
+ To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
  %similar to Claim \ref{claim_pred_err}
@@
 \end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of hard parameter sharing for two tasks, respectively.
+Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
 Our main result in this section characterizes the asymptotic bias-variance limits in the high-dimensional setting.
@@
 	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have that
-	the variance equation \eqref{eq_variance_2task} satisfies the following estimate with high probability:
-			\begin{align}
-				&\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{ {\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{n_1+n_2} }}}\nonumber \\
-				\le & p^{-c_{\varphi}}, \label{lem_cov_shift_eq} %\norm{\Sigma^{(2)}},
+	the variance equation \eqref{eq_variance_2task} satisfies the following estimate:
+			\begin{align}\label{lem_cov_shift_eq}
+				\resizebox{0.869\hsize}{!}{%
+				$\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{ {\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{n_1+n_2} }}}
+				\le p^{-c_{\varphi}}$
+				}%
 			\end{align}
@@
 \end{theorem}
-The bias limit can be found in equation \eqref{lem_cov_derv_eq}.
+Due to space limit, we defer the bias limit result to Appendix \eqref{appendix RMT}.
 Our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
-To see this, when $n_1$ is zero, we solve equations \eqref{eq_a12extra000} and  \eqref{eq_a12extra} to obtain that $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.
-We also remark that for general $A_1$ and $A_2$, we need to replace $\hat \Sigma$ with $\frac{A_1^2}{A_2^2}{X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}$.
-This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
+To see this, when $n_1$ is zero, we solve equations \eqref{eq_a12extra000} and  \eqref{eq_a12extra} to obtain that $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply them to equation \eqref{lem_cov_shift_eq}.
+For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
+We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
+%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
 
-\paragraph{How does hard parameter sharing scale with sample size and covariate shift?}
-One can see that both the variance limit and the bias limit (in equation \eqref{lem_cov_derv_eq}) depend intricately on both tasks' samples sizes and covariate shift.
+\paragraph{How does hard parameter sharing scale with sample sizes and covariate shift $M$?}
+One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
 Next, we illustrate how varying them impact the prediction loss.
@@
 
-	Applying Theorem \ref{thm_main_RMT} to the above setting, we first solve the self-consistent equations \eqref{eq_a12extra000} and \eqref{eq_a12extra} using $\lambda_i = 1$ for all $1\le i\le p$.
-	This gives us the following variance limit by equation \eqref{eq_a12extra000}: 
+	Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
 	\begin{align*}
 		&\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] \\
-		=& \frac{p}{(n_1 + n_2)(a_1 + a_2)}
+		=& \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
 		= \frac{p}{n_1 + n_2 - p},
 	\end{align*}
-	%since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$.
+	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra000}.
 	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit using equation \eqref{lem_cov_derv_eq}. 
+	Similarly, we can calculate the bias limit (details omitted).
 	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
@@
 	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-	The prediction loss of hard parameter sharing for task two satisfies that with high probability,
+	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
+	With high probability over the randomness of the input,
+	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
 	\begin{align}
@@
 
-The above result provides a more concrete interpretation of the bias-variance decomposition, since it depends explicitly on datasets' properties of interest.
+In the above equation, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
+This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
 The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$.
-By combining the bias and variance limits, we can also obtain a generalization bound for any local minimizer of $f(A, B)$ in a similar way.
-%The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
+As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
+by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
+The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
 

### 2020-10-15 arxiv/diff_cov.tex
section 4

@@
 
-Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-Consider the limiting estimate on the left hand side of equation \eqref{cor_MTL_error}.
-We vary sample ratio $n_1 / n_2$ by fixing $n_2$ and increasing $n_1$.
+Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
+For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
+We assume that $n_2$ is fixed for simplicity.
+%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
+The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
+It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
 %As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
 %We describe a sketch of the proof.
-The variance term always reduces as $n_1$ increases, while the bias term always increases as $n_1$ increases (which can be verified by calculating the derivative of the bias term).
-Furthermore, by calculating the derivative of the bias-variance limits with respect to $n_1$, we obtain the following dichotomy (details omitted).
+By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
 %\begin{enumerate}
@@
 (ii) When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify that the bias increases slower than the variance decreases, and there is only one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
+	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
 %\end{enumerate}
@@
 
-We explain why the dichotomy happens. The variance estimate for this example is equal to
+We explain why the dichotomy happens. The variance limit in this example is equal to
 $\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
 \[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-With equation \eqref{eq_a12extra000} and a straightforward calculation (details omitted), we can verify that
+Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
 %\begin{align*}
@@
 %\end{align*}
-This implies $n_1>n_2$. Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$. 
+This implies $n_1>n_2$.
+The other direction follows from similar arguments.
+% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
 %Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
@@
 
-\paragraph{Overview of Stieltjes transform.}
+\textbf{Overview of Stieltjes transform.}
 For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
-The central quantity of interest is the inverse of the sum of two sample covariance matrices $\hat{\Sigma}^{-1}$.
+The central quantity of interest is the inverse of the sum of two sample covariance matrices.
 We note that the variance equation $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ is equal to $(n_1 + n_2)^{-1} \bigtr{W^{-1}}$, where $W$ is
@@
 Here $U\Lambda V^\top$ is defined as the SVD of $M$.
-This formulation is helpful because we know that ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance, and $U, V$ are both orthonormal matrices.
+This formulation is helpful because we know that $(Z^{(1)})^{\top} Z^{(1)}$ and $(Z^{(2)})^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance, and $U, V$ are both orthonormal matrices.
+For example, if $Z^{(1)},Z^{(2)}$ are both Gaussian random matrices, by rotational invariance, $Z^{(1)} U, Z^{(2)}V$ are still Gaussian random matrices.
 
@@
 We briefly describe the key ideas and refer the interested readers to classical texts such as  \citet{bai2009spectral,tao2012topics,erdos2017dynamical}.
-For any probability measure $\mu$ supported on $[0,\infty)$ and complex number $ z\in \C\setminus [0,\infty)$, the Stieltjes transform of $\mu$ is a complex function defined as
-$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z} .$$ %, \ \ \text{ for any complex number } z\in \C\setminus [0,\infty).$$
-The Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
+For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is a complex function defined as
+$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \text{ for any complex } z\in \C\setminus \set{0}.$$
+Thus, the Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
 %To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
@@
 %It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= (\Sigma^{(2)})^{-1/2} V W^{-1}V^\top (\Sigma^{(2)})^{-1/2}$ and .
-Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$.
+Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where the $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$.
 Then it is easy to see that the Stieltjes transform of $\mu$ is equal to
  \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(W-z\id)^{-1}\right]. \]
-Above, the matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
+The above matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
 %When $p$ goes to infinity, it is well-known that $m_{\mu}(z)$ converges to a fixed distribution governed by a set of self-consistent equations.
@@
 %Compared to the Stieltjes transform, the resolvent also applies to random matrices.
-We will prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
+We prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
 The full details will be given in Section \ref{appendix RMT}.

### 2020-10-15 arxiv/intro.tex
section 3 half done
section 4

--- 2020-10-14 arxiv/intro.tex
@@
 \begin{abstract}
-	\vspace{-0.15in}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that their generalization properties have not been well established in many cases.
-This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio.
+	\vspace{-0.1in}
+	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties has not been well established in many cases.
+This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
+We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
 First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
@@
 We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing the variance but hurts eventually due to the increasing bias.
+Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
 This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-	\vspace{-0.1in}
+	\vspace{-0.15in}
 \end{abstract}
 
-\vspace{-0.15in}
+\vspace{-0.1in}
 \section{Introduction}\label{sec_introduction}
-\vspace{-0.1in}
 
@@
 
-Hard parameter sharing is an intuitively appealing mechanism for inductive transfer, and reduces overfitting by acting as a regularizer \cite{R17}.
+Hard parameter sharing works as an inductive transfer mechnism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
 For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
@@
 Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases when all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
+Previous results based on Rademacher complexity or VC dimensions have considered when all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
@@
 	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially, but increases afterwards.
+	Increasing $n_1/n_2$ decreases task two's prediction loss initially, but increases afterward.
 This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
@@
 	\label{fig_intro_sample_size}
-	\vspace{-0.1in}
+	\vspace{-0.07in}
 \end{figure*}

### 2020-10-15 arxiv/setup.tex
section 4

@@
 %We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same covariates, HPS helps by reducing variance compared to single-task learning, but hurts by increasing bias.
+Our result implies that when all tasks have the same features but different labels, HPS helps by reducing variance compared to single-task learning, but hurts by increasing bias.
 
 Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we no longer have a characterization of $f(A, B)$'s global minimum because of non-convexity, for any local minimizer of $f(A, B)$, we provide a sharp bias-variance tradeoff of both tasks' prediction loss.
-Despite its simplicity, we show several interesting phenomena by varying sample sizes and covariate shifts in this setting.
-See Figure \ref{fig_intro_sample_size} for an illustration.
-Consequently, using our precise loss estimates, we observe several qualitative properties of hard parameter sharing for varying datasets' properties.
+While we no longer have a characterization of $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
+Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
+See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
+Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
 %\begin{enumerate}
@@
 These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in MTL typically scale down as the sample sizes of all tasks increase, thus do not apply for different sample sizes.
+This result is surprising because previous generalization bounds in multi-task learning typically scale down as the sample sizes of all tasks increase, thus do not apply for different sample size ratios.
 

### 2020-10-15 arxiv/conclusions.tex
update figure

@@
 
-This work proposed a formal study of a widely used hard paramaeter sharing approach in multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS given multiple linear gression tasks.
+This work proposed a formal study of a widely used hard parameter sharing approach in multi-task learning.
+We provided sharp bias-variance tradeoffs of HPS given multiple linear regression tasks.
 Based on these results, we analyzed how varying sample sizes and covariate shifts impacts HPS.

### 2020-10-15 arxiv/diff_cov.tex
revise

@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  & \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \nonumber\\
+	  & \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \nonumber\\
 	\le& \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
@@
 
-(i) When $\frac{d^2}{\sigma^2} < \frac{p}{2n_2 - 3p}$, the prediction loss decreases monotonically as $n_1$ increases.
+(i) When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
 	Intuitively, this regime of $d^2$ always helps task two.
 
-(ii) When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
+(ii) When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
 	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.

### 2020-10-15 arxiv/diff_cov.tex
polish

--- 2020-10-15 arxiv/diff_cov.tex
@@
 Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-By Proposition 1 of \citet{WZR20}, we consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ is equivalent to single-task learning.
+We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \citet{WZR20}).
 When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
@@
 	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have that
-	the variance equation \eqref{eq_variance_2task} satisfies the following estimate:
+	the variance equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
 			\begin{align}\label{lem_cov_shift_eq}
@@
 
-In the above equation, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
+In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
 This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
@@
 %In general, the covariance matrices of the two tasks may be different such as in text classification.
-Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}, which gives that
+Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}. For large enough $p$,
 %in the left hand side of equation \eqref{lem_cov_shift_eq}:
@@
 \end{align*}
-where $g(\lambda, a_1) \ge 0$ is a fixed function. 
+where $g(\lambda, a_1) \ge 0$.
 %and can be derived from algebraic calculations (details omitted).
@@
 
-\textbf{Overview of Stieltjes transform.}
+\textbf{Proof overview of Theorem \ref{thm_main_RMT}.}
 For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
@@
 	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
+	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
+%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
 	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.

### 2020-10-15 arxiv/experiments.tex
polish

@@
 \textbf{Sample efficiency.}
-First, we study the setting of Example \ref{ex_same_cov}.
+First, we validate the result of Example \ref{ex_same_cov}.
 Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task   from $400$ to $2000$.
 In all the parameter settings, our results estimate the empirical losses accurately.
-We also observe a trend that the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
+We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
 Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
@@
 
-\textbf{Sample ratio.}
-Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
+\textbf{Sample size ratio.}
+Second, we validate the result of Example \ref{ex_sample_ratio}.
 Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
@@
 We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
-The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is $1$.
+The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
 We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
-On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases monotonically.
-Our result from Corollary \ref{cor_MTL_loss} explains this trend. \HZ{check}
+On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases faster.
+Intuitively, this is because bias increases less for smaller $d^2$.
+%Our result from Corollary \ref{cor_MTL_loss} explains this trend.
 
 \textbf{Covariate shift.}
-Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}. 
+Finally, we validate the result of Example \ref{ex_covshift}.
 Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.

### 2020-10-15 arxiv/intro.tex
polish

@@
 Often, hard parameter sharing offers two critical advantages if successfully applied.
-(i) It reduces model parameters since all tasks use the same feature space.
-(ii) It reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
+First, it reduces model parameters since all tasks use the same feature space.
+Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
 
@@
 Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered when all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
+Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.

### 2020-10-15 arxiv/setup.tex
polish

@@
 Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ follows a linear model plus random noise.
+We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
 We study the standard hard parameter sharing architecture:
@@
 where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution of $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions here are:
+Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+The critical questions are:
 (i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
@@
 %We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, HPS helps by reducing variance compared to single-task learning, but hurts by increasing bias.
+Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning, but increases bias.
 
@@
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-Using recently developed techniques from random matrix theory \cite{Anisotropic}, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
+Using recently developed techniques from random matrix theory, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
 Theorem \ref{thm_main_RMT}).
@@
 %\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error})).
-We believe that our analysis has provided important initial insight and it is an interesting question to tighten our result.
+One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
+We believe our result has provided important initial insights and it is an interesting question to tighten our result.
 
@@
 
-There is a large body of both classical and recent works on multi-task learning.
-We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,R17,ZY17,V20}.
-The early work of \citet{B00,BS03,M06} have sought for a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+There is a large body of classical and recent works on multi-task learning.
+We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
+The early work of \citet{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
 An influential paper by \citet{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
@@
 Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, which is a recent development in the random matrix theory literature.
-\citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
+In the single task case, \citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
 \citet{Anisotropic} later extended this result to arbitrary covariance setting.
@@
 These techniques provide almost sharp convergence rates to the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results about the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
+To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covarite shifts).
 

### 2020-10-15 arxiv/experiments_text.tex

@@
 \end{itemize}
-For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
+For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
 The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
@@
 First, we conduct multi-task training over all $15$ pairs from the six datasets.
-We find that adding task one's samples progressive requires only $45\%$ of the computational cost to achieve the same test accuracy for task two than standard round-robin training schedules.
+We find that adding task one's samples progressively requires only $45\%$ of the computational cost to achieve the same test accuracy for task two compared to the standard round-robin training schedules.
 %Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
@@
 Second, we conduct multi-task training on all six datasets.
-We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than standard round-robin training schedules.
+We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than the standard round-robin training schedules.
 %As a further validation, excluding TREC, we observe similar comparative results.

### 2020-10-15 arxiv/conclusions.tex
final edits

--- 2020-10-14 arxiv/conclusions.tex
@@
+\vspace{-0.06in}
 \section{Conclusions and Discussions}\label{sec_conclude}
+\vspace{-0.06in}
 
-This work proposed a formal study of a widely used hard paramaeter sharing approach in multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS given multiple linear gression tasks.
-Based on these results, we analyzed how varying sample sizes and covariate shifts impacts HPS.
-Our work rigorously explains several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on a real world classification task.
-We describe several open questions for future work.
-First, it would be interesting to tighten our result in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-Second, it would be very interesting to extend our result to classification problems such as logistic regression.
+This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
+We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
+Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
+We validated our theory and conducted further studies on text classification tasks.
+We describe open questions for future work.
+First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
+Second, it would be interesting to extend our result to classification problems such as logistic regression.
 %First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.

### 2020-10-15 arxiv/intro.tex
upload pdf

@@
 	\vspace{-0.1in}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties has not been well established in many cases.
+	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
 This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?

### 2020-10-15 arxiv/setup.tex
fix typo

@@
 We study the standard hard parameter sharing architecture:
-there is a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
+a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
 See Figure \ref{fig_intro_arch} for an illustration.

### 2020-10-15 arxiv/setup.tex
grammar

@@
 %We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning, but increases bias.
+Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
 
 Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we no longer have a characterization of $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
+While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
 Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
@@
 	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \citet{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance, and is generally high when the latter is large.
+	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
 
-\textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help to reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterwards, or decreases monotonically depending on how fast the bias increases.
+\textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
+In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
 These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as the sample sizes of all tasks increase, thus do not apply for different sample size ratios.
+This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
 

### 2020-10-15 arxiv/proof_same_cov.tex
address vaggos comments
appendix

@@
 		\begin{align}
-			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).
-\label{eq_gA}
+			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r). \label{eq_gA}
 		\end{align}
@@
 	\end{claim}
-	The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
+	%The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
 	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
@@
 
-	\paragraph{Proof of Claim \ref{lem_exp_opt}.}
+Next we present the proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err}. 
+	\begin{proof}[Proof of Claim \ref{lem_exp_opt}]
 	To facilitate the analysis, we consider the following matrix notations.
@@
 		%\[ \cE A^{\top} := {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \]
-\[\cE  :=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}],  \quad \text{ and } \quad \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{\dag}. \]
+\[\cE  :=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}],  \quad \text{ and } \quad \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{+}. \]
 	For any $j = 1,2,\dots, t$, let
@@
 	\end{align*}
-	Then, we can write the function $g(A)$ conveniently as
+	Then we can write the function $g(A)$ conveniently as
 	\[ g(A) = \sum_{j=1}^t \bignorm{X H_j + E_j}^2. \]
 	We will divide $g(A)$ into three parts.
-	We will use matrix notations in the proof since they are more compact.
-	That is, stacking $[H_j]_j$ gives matrix $B^{\star} A^{\top} (AA^{\top}) A - B^{\star}$,
+	For simplicity, we will use matrix notations in the proof, %since they are more compact.
+	that is, stacking $[H_j]_j$ gives matrix $B^{\star} A^{\top} (AA^{\top}) A - B^{\star}$,
 	and stacking $[E_j]_j$ gives $\cW A - \cE$.
@@
 	\end{align}
-	where $U_{A} U_{A}^{\top} \in\real^{t\times t}$ denotes the subspace $ {A}^{\top} ( {A}{A}^{\top})^{+}  {A}$.
+	where $U_{A} U_{A}^{\top} \in\real^{t\times t}$ denotes the subspace projection $ {A}^{\top} ( {A}{A}^{\top})^{+}  {A}$.
 	Taking expectation of equation \eqref{eq_gA_p1} over $X$, we get
-		\[ \bignorm{\Sigma^{1/2}(B^{\star} U_A U_A^{\top} - B^{\star})}^2. \]
+		\[ \sum_{j=1}^t \bignorm{X H_j}^2=n\bignorm{\Sigma^{1/2}(B^{\star} U_A U_A^{\top} - B^{\star})}^2. \]
 
-	\paragraph{Part 2:} The second part is the cross term, which is equal to the following using the matrix notations
+	\paragraph{Part 2:} The second part is the cross term, which is equal to the following using the matrix notations:
 	\begin{align}\label{eq_gA_p2}
@@
 
-	\paragraph{Part 3:} The last part is the square of $E_j$,
+	\paragraph{Part 3:} The last part is the square of $E_j$:
 	\begin{align}\label{eq_gA_p3}
@@
 	\end{align}
-	which is because $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
+	where in the second step we used $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
 	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
@@
 %	We consider both terms in the above equation one by one.
-	Second, notice that for $U_XU_X^\top:=X(X^{\top} X)^{-1} X^{\top}$ and $1\le i, j \le t$,
+	Second, notice that for the subspace projection $U_XU_X^\top:=X(X^{\top} X)^{-1} X^{\top}$ and $1\le i, j \le t$,
 	%\begin{align}
@@
 	which implies that $\exarg{\cE}{\cE^{\top}U_XU_X^\top \cE }=p\sigma^2 \cdot \id_{t\times t}$.
-	In the above derivation, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
+	Above, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
 	Therefore, we have that
@@
 	\begin{align*}
-		\exarg{\cE}{ \inner{\cW A}{\cE}} = p\sigma^2 \cdot \bigtr{\id_{t\times t}U_AU_A^\top} =  p \sigma^2 \cdot r ,
+		\exarg{\cE}{ \inner{\cW A}{\cE}} =\E \bigtr{\cal E^\top U_X U_X^\top \cal E U_AU_A^\top}= p\sigma^2 \cdot \bigtr{ U_AU_A^\top} =  p \sigma^2 \cdot r ,
 			\end{align*}
@@
 	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.
-	Hence the proof is complete.
+
+	Combining the above three parts, the proof of Claim \ref{lem_exp_opt} is completed.
+	\end{proof}
 
@@
 
-	\paragraph{Proof of Claim \ref{claim_opt_dist}.}
+	\begin{proof}[Proof of Claim \ref{claim_opt_dist}]
 	Corresponding to the right-hand side of \eqref{eq_gA}, we define the function
-	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
+	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
 	In order to show that the $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
@@
 	applying Corollary \ref{cor_largedeviation} to $X H_j = Z \Sigma^{1/2} H_j$, we obtain that 
-	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(p^{-c_\varphi}))$ with high probability. 
+	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(n^{-c_\varphi}))$ with high probability. 
 	%, for a small enough constant $\e$,
@@
 	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
-	using Corollary \ref{cor_calE}, we obtain that the following holds with high probability for any small constant $\e>0$:
+	using Corollary \ref{cor_calE}, we obtain the following with high probability for any small constant $\e>0$:
 	\begin{align}
-		|\inner{XB^{\star} (U_AU_A^{\top} - \id)}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id)} \nonumber \\
-		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)} \nonumber \\
-		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n}\cdot \sqrt{t}\bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)} \nonumber \\
-		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t
+		|\inner{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})} \nonumber \\
+		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
+		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n}\cdot \sqrt{t}\bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
+		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t,
 		\label{eq_gA_err2}
 	\end{align}
-	which is bounded by the right hand side of equation \eqref{eq_gA_err} as long as $c$ is taken sufficiently small.
+	which is bounded by the right hand side of equation \eqref{eq_gA_err} as long as $c$ is sufficiently small.
 	In the second step, we used the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id)$ has rank at most $t$.
+	In the third step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})$ has rank at most $t$.
 In the fourth step, we used AM-GM inequality.
@@
 	\end{align}
-	as long as $c$ is taken sufficiently small. 
+	as long as $c$ is sufficiently small. 
 	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
@@
 	\end{align}
-as long as $c$ is taken sufficiently small.
-Here in the third step, we applied Corollary \ref{cor_calE} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and used that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ is of rank $r$.
+as long as $c$ is sufficiently small.
+Here in the third step, we applied equation \eqref{vcalAE3} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and used that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ is of rank $r$.
 In the fourth step, we used that $\|U_X U_X^\top\|_F=\sqrt{p}\le \sqrt{n}$ because $U_X$ is of rank $p$.
@@
 	Next, we use equation \eqref{eq_gA_err} to prove the claim.
-	Using triangle inequality, we upper bound the gap between $g(A^{\star})$ and $g(\hat{A})$:
+	Using triangle inequality, we upper bound the gap between $h(A^{\star})$ and $h(\hat{A})$:
 	\begin{align}
@@
 	The second step used the fact that $\hat A$ is the global minimizer of $g(\cdot)$, so that $g(\hat A) \le g({A}^\star)$.
-	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id$ is at most one. 
+	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id_{t\times t}$ is at most one. 
 	%With \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows. 
-	Using equation \eqref{same_hA}, we can obtain that
+	Using equation \eqref{same_hA}, we can verify that
 	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
+	.....
 Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$, and $v_i$, $1\le i \le t$, be the corresponding eigenvectors.
@@
 	This completes the proof of Claim \ref{claim_opt_dist}.
+	\end{proof}
+
 	\iffalse

### 2020-10-16 arxiv/proof_same_cov.tex
appendix

@@
 		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
-				\le  p^{-c_{\varphi}} \cdot C_1. \]
+				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r- \lambda_{r+1}}. \]
 	\end{claim}
@@
 			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
-			\le  n^{-1/4} \left( L(B^{\star} \hat{a}_i)+ \sigma^2  \cdot\|\hat a_i\|^2\right) .
+			\le  n^{-1/4} \left(\|\Sigma^{1/2}B^{\star} \|^2+ \sigma^2  \cdot\|\hat a_i\|^2\right) .
 		\end{align*}
@@
 	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is within an $\OO(n^{-1/4})$ fraction of $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$.
+		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a small enough error.
 Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$.
@@
 		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
-		&\lesssim n^{-c_\varphi}\cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
+		&\lesssim n^{-c_\varphi}\cdot n \bignorm{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
 	\end{align}
@@
 	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
-	.....
 	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$, and $v_i$, $1\le i \le t$, be the corresponding eigenvectors.
@@
 	Thus from \eqref{bdd_A-A}, we obtain that 
-	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}.$$
+	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignorm{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}  .$$
 	This completes the proof of Claim \ref{claim_opt_dist}.
@@
 
-	\paragraph{Proof of Claim \ref{claim_pred_err}.}
+	\begin{proof}[Proof of Claim \ref{claim_pred_err}]
 	%We apply similar arguments from Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
@@
 	\begin{align*}
-		L(\hat{\beta}_i^{\MTL}) &= \bignorm{\Sigma^{1/2} (\hat{B} \hat{A}_i - \beta_i)}^2 \\
-		&= \bignorm{\Sigma^{1/2} ((X^{\top} X)^{-1} X^{\top} Y \hat{A}^{\top} (\hat{A} \hat{A}^{\top})^{+} \hat{A}_i - \beta_i)}^2 \\
-		&= \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i + E_i)}^2,
+		L(\hat{\beta}_i^{\MTL}) &= \bignorm{\Sigma^{1/2} (\hat{B} \hat{A}_i - \beta^{(i)})}^2 \\
+		&= \bignorm{\Sigma^{1/2} ((X^{\top} X)^{-1} X^{\top} Y \hat{A}^{\top} (\hat{A} \hat{A}^{\top})^{+} \hat{A}_i - \beta^{(i)})}^2 \\
+		&= \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta^{(i)} + R_i)}^2,
 	\end{align*}
-	where we denote $E_i = (X^{\top} X)^{-1} X^{\top} \cE \hat{a}_i$.
-	We divide the prediction loss to three parts.
+	where we denote $R_i = (X^{\top} X)^{-1} X^{\top} \cE \hat{a}_i$.
+	We divide the prediction loss into three parts.
 
@@
 	\begin{align*}
-		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}E_i}} &= \bigabs{\inner{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}{\cal E}} \\
-		&\le n^{c}\sigma \cdot \bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}\\
-		&\le n^{c}\sigma \cdot\|\hat a_i\| \cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\| \cdot \| (Z^\top Z)^{-1} \|^{1/2} \\
-		&\lesssim n^{-1/2+c}\sigma \cdot\|\hat a_i\| \cdot \bignorm{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} \\
-		&\le n^{-1/2+c}\sigma^2  \cdot\|\hat a_i\|^2 + n^{-1/2+c} L(B^{\star} \hat{a}_i), 
+		& \bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta^{(i)})}{\Sigma^{1/2}R_i}} \\
+		\le &\sum_{1\le j, k\le t}|\hat a_i(j)| |\hat a_i(k)| \bigabs{ \inner{ X(X^\top X)^{-1}\Sigma \beta^{(j)} }{\epsilon^{(k)}}}  + \sum_{  j =1}^{t}|\hat a_i(j)|\bigabs{ \inner{ X(X^\top X)^{-1}\Sigma \beta^{(i)}}{\epsilon^{(j)}}} \\
+		\le & n^{c}\sigma \cdot \bignormFro{ X(X^\top X)^{-1}\Sigma B^{\star} } \cdot \left[ \sum_{j=1}^t |\hat a_i(j)| + \sum_{1\le j,k \le t} |\hat a_i(j)| |\hat a_i(k)| \right] \\
+		 \lesssim & n^{c}\sigma   \cdot \|\hat a_i\|\cdot \|\Sigma^{1/2}B^{\star} \| \cdot \| (Z^\top Z)^{-1} \|^{1/2}  \le  n^{-1/2+c}\sigma^2 \|\hat a_i\|^2 + n^{-1/2+c} \|\Sigma^{1/2}B^{\star} \|^2 , 
 	\end{align*}	
-	with high probability for any small constant $c>0$. Here in the third step we used 
+%	\begin{align*}
+%		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}R_i}} &= \bigabs{\inner{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}{\cal E}} \\
+%		&\le n^{c}\sigma \cdot \bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}\\
+%		&\le n^{c}\sigma \cdot\|\hat a_i\| \cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\| \cdot \| (Z^\top Z)^{-1} \|^{1/2} \\
+%		&\lesssim n^{-1/2+c}\sigma \cdot\|\hat a_i\| \cdot \bignorm{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} \\
+%		&\le n^{-1/2+c}\sigma^2  \cdot\|\hat a_i\|^2 + n^{-1/2+c} L(B^{\star} \hat{a}_i), 
+%	\end{align*}
+	with high probability for any small constant $c>0$.
+Here in the first step, we expand $B^\star \hat a_i=\sum_{1\le j \le t} \hat a_i(j) \beta^{(j)}$ amd $\cal E \hat a_i=\sum_{1\le j \le t} \hat a_i(j) \epsilon^{(j)}$.
+In the second step, we used equation \eqref{vcalE}.
+In the third step we used $\sum_j |\hat a_i(j)|\le \sqrt{t}\|\hat a_i\|$ by Cauchy-Schwarz inequality, and
 	\begin{align*}
-	\bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)} &=\|\hat a_i\|\cdot \left[ (B^{\star} \hat{a}_i - \beta_i)^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i) \right]^{1/2} \\
-	&\le \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2} \\
-	&= \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}
+	\bignormFro{ X(X^\top X)^{-1}\Sigma B^{\star}} &=\left[ {B^{\star}}^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma B^{\star} \right]^{1/2} \\
+	&\le  \|\Sigma^{1/2} B^{\star} \|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2}  =   \|\Sigma^{1/2} B^{\star} \|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2},
 	\end{align*}
-	because $X=Z\Sigma^{1/2}$.
-In the fourth step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\left\| (Z^\top Z)^{-1}\right\|$ by $\OO(n^{-1})$.
-In the last step we used AM-GM inequality.
+%	\begin{align*}
+%	\bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)} &=\|\hat a_i\|\cdot \left[ (B^{\star} \hat{a}_i - \beta_i)^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i) \right]^{1/2} \\
+%	&\le \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2} \\
+%	&= \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}
+%	\end{align*}
+	because $X=Z\Sigma^{1/2}$. In the fourth step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\left\| (Z^\top Z)^{-1}\right\|$ by $\OO(n^{-1})$, and applied the AM-GM inequality.
 
@@
 
-	\paragraph{Part 3:} The final part is $\|E_i\|^2$. We rewrite it as 
+	\paragraph{Part 3:} The final part is $\|R_i\|^2$. We rewrite it as 
 	\begin{align}
-	\|\Sigma^{1/2}E_i\|^2 &= \left\|\sum_{j=1}^t \hat{a}_j \Sigma^{1/2}(X^{\top} X)^{-1} X^{\top} \epsilon^{(j)}\right\|^2 \nonumber\\
+	\|\Sigma^{1/2}R_i\|^2 &= \left\|\sum_{j=1}^t \hat{a}_i(j) \Sigma^{1/2}(X^{\top} X)^{-1} X^{\top} \epsilon^{(j)}\right\|^2 \nonumber\\
 	& = \sum_{1\le j , k \le t}\hat a_i(j) \hat a_i(k)  {\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}}.\label{E_i^2}
 	\end{align}	
-	If $j\ne k$, using Corollary \ref{cor_calE} we obtain that 
+%	If $j\ne k$, using Corollary \ref{cor_calE} we obtain that 
+%	\begin{align}
+%	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} \right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
+%	& =\sigma^2 \cdot \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
+%	&  \le \sigma^2 \cdot p^{1/2} \cdot \bignorm{(Z^{\top} Z)^{-1}} \lesssim \sigma^2 \cdot n^{-1/2+c} \label{jnek}
+%	\end{align}
+%	with high probability for any small constant $c>0$. On the other hand, if $j=k$, 
+	First we can calculate that 
+	$$\exarg{\cal E}{{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} \epsilon^{(k)}}=\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right] .$$
+	Then using equation \eqref{vcalA2}, we obtain that 
 	\begin{align}
-	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} \right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
-	& =\sigma^2 \cdot \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
-	&  \le \sigma^2 \cdot p^{1/2} \cdot \bignorm{(Z^{\top} Z)^{-1}} \lesssim \sigma^2 \cdot n^{-1/2+c} \label{jnek}
+	& \left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} -\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right]\right|\nonumber \\
+	\le &n^c\cdot \sigma^2  \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} }   = n^c\cdot \sigma^2  \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
+	  \le &\sigma^2 \cdot p^{1/2} \cdot  \bignorm{(Z^{\top} Z)^{-1}}^{1/2} \lesssim \sigma^2 \cdot n^{-1/2+c}, \label{jeqk}
 	\end{align}
-	with high probability for any small constant $c>0$. On the other hand, if $j=k$, we notice that 
-	$$\exarg{\epsilon^{(j)}}{{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} \epsilon^{(j)}}= \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right] .$$
-	Then using Corollary \ref{cor_calE}, we obtain that 
-	\begin{align}
-	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(j)}} -\sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right]\right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
-	& \lesssim \sigma^2 \cdot n^{-1/2+c} . \label{jeqk}
-	\end{align}
-	Plugging \eqref{jnek} and \eqref{jeqk} into \eqref{E_i^2}, we obtain that 
+	with high probability for any small constant $c>0$. 
+	Above, we used Fact \ref{fact_minv} (ii) in the last step to bound $ \bignorm{(Z^{\top} Z)^{-1}}$ by $\OO(n^{-1})$.
+	Plugging equation \eqref{jeqk} into equation \eqref{E_i^2}, we obtain that 
 	\begin{align*}
-		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 -  \sigma^2 \|\hat a_i\|^2 \cdot\tr\left[\Sigma(X^\top X)^{-1}\right]} \lesssim  \sigma^2 \cdot n^{-1/2+c} \cdot \sum_{j,k}|\hat a_i(j)||\hat a_i(k)|\lesssim  n^{-1/2+c} \sigma^2 \cdot  \|\hat a_i\|^2.
+		\bigabs{\bignorm{\Sigma^{1/2} R_i}^2 -  \sigma^2 \|\hat a_i\|^2 \cdot\tr\left[\Sigma(X^\top X)^{-1}\right]} \lesssim  \sigma^2 \cdot n^{-1/2+c}  \sum_{1\le j,k\le t}|\hat a_i(j)||\hat a_i(k)|\lesssim  n^{-1/2+c} \sigma^2 \cdot  \|\hat a_i\|^2.
 	\end{align*}
@@
 	Finally, combining the three parts together, we conclude the proof of Claim \ref{claim_pred_err}.
-
+\end{proof}
 	%\paragraph{Proof of Theorem \ref{thm_many_tasks}.}

### 2020-10-16 arxiv/tools.tex
appendix

@@
 Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
-\be\label{vcalE} |v^\top \epsilon^{(i)}| \le \sigma n^{c} \|v\|, \ee
+\be\label{vcalE} |v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \ee
 and
-\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c} \|B\|_F ,\ee
+\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F ,\ee
 for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
 \be\label{vcalAE3}
-\|v^\top \cal E\| \le \sigma n^{c} \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \|B\|_F ,
+\|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \cdot  \sigma^2\|B\|_F ,
 \ee

### 2020-10-16 arxiv/proof_gaussian_case.tex
appendix

@@
 \section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
+We first state the bias limit for the term in equation \eqref{eq_bias_2task}.
 
-	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed vector $w\in\real^p$ with unit norm,
+\begin{theorem}\label{thm_main_RMT_app}
+	In the setting of Theorem \ref{thm_main_RMT}, the bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed unit vector $w\in\real^p$:
 			\begin{align}\label{lem_cov_derv_eq}
-				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
+				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - \frac{1}{(n_1+n_2)^2}{\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
 			\end{align}
@@
 			\end{align}
+\end{theorem}
+In this section, we give the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}
 
+\subsection{Proof Overview}
+Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
+
+Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$. 
 We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm,

### 2020-10-16 arxiv/diff_cov.tex
final edits
minor grammar fixes

@@
 The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we study how different sample sizes and different features impact hard parameter sharing.
+In this section, we study how having different sample sizes and different covariance matrices impact hard parameter sharing.
 %The different covariates case differs from the same covariates case in two aspects.
 %First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-The setting where features differ across tasks is often called ``covariate shift''.
+The setting where covariates differ across tasks is often called ``covariate shift''.
 
-Unlike the previous section, we no longer have an optimal solution to $f(A, B)$.
+Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
 This is because $f(A, B)$ is in general non-convex.
@@
 Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose that
+Suppose
 \begin{align*}
@@
 where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-The matrices $\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
+$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
 
@@
 	We first consider the impact of varying sample sizes.
-	Consider the random-effects model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
+	Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
 
@@
 We prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
-The full details will be given in Section \ref{appendix RMT}.
+The complete proof is provided in Section \ref{appendix RMT}.
 %Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.

### 2020-10-16 arxiv/setup.tex
minor grammar fixes

@@
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-Using recently developed techniques from random matrix theory, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
+We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
 Theorem \ref{thm_main_RMT}).
-% Moreover, we can obtain a sharp bound on the concentration error.
+We use recently developed techniques from random matrix theory to show a sharp convergence rate.
 % to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
@@
 One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided important initial insights and it is an interesting question to tighten our result.
+We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
 
@@
 There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
+We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
 The early work of \citet{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
@@
 One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \citet{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting, because the results usually require a sample size at least $p \log p$.
+Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
 
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, which is a recent development in the random matrix theory literature.
-In the single task case, \citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\citet{Anisotropic} later extended this result to arbitrary covariance setting.
+Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
+In the single-task case, \citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
+\citet{Anisotropic} later extended this result to arbitrary covariance matrices.
 %On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covarite shifts).
+These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
+To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
 
 The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \citet{li2020transfer} provides minimax optimal rates for predicting a target regression task given multiple sparse regression tasks.
+For example, \citet{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
 One closely related work is \citet{WZR20}, which studied hard parameter sharing for two linear regression tasks.
@@
 In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we present our technical results that describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in simulations and real world classification tasks.
+In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
+In Sections \ref{sec_simulation}, we validate our results in simulations.
 In Section \ref{sec_conclude}, we summarize our work and discuss future work.
+Section \ref{sec_text} describes our study on text classification tasks.
 Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.

### 2020-10-16 arxiv/proof_gaussian_case.tex
appendix

@@
 Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$. 
-We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm,
+We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic unit vectors $v\in \R^p$,
 $$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
@@
 where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
-\be
-\begin{split}\label{selfomega_a}
-	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}},  \\
-	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
+\begin{align}
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \label{selfomega_a000} \\
+	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.\label{selfomega_a}
 % \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{split}
-\ee
+\end{align}
 The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
@@
 %\ee
-Given this result, we show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
-First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
+Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
+First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equations \eqref{selfomega_a000} and \eqref{selfomega_a} reduce to equations \eqref{eq_a12extra000} and \eqref{eq_a12extra} when $z=0$.
 Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
-Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$, we get that when $p$ goes to infinity, % the trace of $$ converges to
+Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, % the trace of $$ converges to
 \begin{align*}
@@
  For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
-First, we reduce the empirical bias term in equation \eqref{lem_cov_derv_eq} to $W$
+First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %$W$
 \begin{align}\label{calculate G'}
@@
 Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
-Hence, provided that limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
+Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
 \begin{align}\label{cal G'0}
@@
 %then taking implicit differentiation of equation \eqref{selfomega_a}
-One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations \eqref{eq_a34extra} (details omitted).
+One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
 Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.

### 2020-10-16 arxiv/proof_gaussian_case.tex
appendix

@@
 Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
-We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equation \eqref{selfomega_a}.
+We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations \eqref{selfomega_a000} and \eqref{selfomega_a}.
 On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
@@
 We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
-A complete proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{appendix RMT}.
+A complete proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{sec pf RMTlemma}-Appendix \ref{sec entry}. %Appendix \ref{appendix RMT}.
 
 We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution. 
-By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}$ also follow an isotropic Gaussian distribution.
+By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}V$ also follow an isotropic Gaussian distribution.
 Hence it suffices to consider the following resolvent
@@
    G(z)= \left( {\begin{array}{*{20}c}
-   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
-   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
-   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+   { -z\id_{p\times p} } & (n_1+n_2)^{-1/2}\Lambda (Z^{(1)})^\top & (n_1+n_2)^{-1/2} (Z^{(2)})^\top  \\
+   {(n_1+n_2)^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
+   {(n_1+n_2)^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
    \end{array}} \right)^{-1}.
  \end{equation}
-We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
-We first introduce several notations.
-Define the index sets
+We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a000} and \eqref{selfomega_a}.
+We first introduce several useful notations. We define $n:=n_1+n_2$ and the following index sets
 $$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$

### 2020-10-16 arxiv/proof_gaussian_case.tex
appendix

@@
 where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
-\begin{align}
-	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \label{selfomega_a000} \\
-	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.\label{selfomega_a}
+\be\label{selfomega_a}
+\begin{split}
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %\label{selfomega_a000} \\
+	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
 % \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{align}
+\end{split}
+\ee
 The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
@@
 Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
-First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equations \eqref{selfomega_a000} and \eqref{selfomega_a} reduce to equations \eqref{eq_a12extra000} and \eqref{eq_a12extra} when $z=0$.
+First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since the equations in \eqref{selfomega_a} reduce to equations \eqref{eq_a12extra000} and \eqref{eq_a12extra} when $z=0$.
 Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
@@
 \end{align}
-To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of equation \eqref{selfomega_a}.
+To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of the system of equations \eqref{selfomega_a}.
 %\begin{align*}
@@
 Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
-We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations \eqref{selfomega_a000} and \eqref{selfomega_a}.
+We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
 On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
@@
  \end{equation}
-We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a000} and \eqref{selfomega_a}.
+We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
 We first introduce several useful notations. We define $n:=n_1+n_2$ and the following index sets
@@
 	Let $X \in \real^{(p + n_1 + n_2)\times (p + n_1 + n_2)}$ and $i = 1, 2, \dots, p + n_1 + n_2$.
-	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1,a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
-	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1, a_2}$ to denote $ X_{a_1, a_2}$ when $a_1$ and $a_2$ both not equal to $i$, and $X^{(i)}_{a_1, a_2}$ to be zero when $a_1 = i$ or $a_2 = i$.
+	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
+	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1 a_2}$ to denote $ X_{a_1 a_2}$ when $a_1$ and $a_2$ are both not equal to $i$, and $X^{(i)}_{a_1 a_2}=0$ when $a_1 = i$ or $a_2 = i$.
 	The resolvent minor of $G(z)$ after removing the $i$-th row and column is defined as
@@
 		G^{(i)}(z) := \left[ \left( {\begin{array}{*{20}c}
-		  { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
-      {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
-			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
+		  { -z\id_{p\times p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
+      {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1\times n_1}} & 0 \\
+			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2\times n_2}}
     \end{array}} \right)^{(i)}\right]^{-1}.
@@
 \end{definition}
-As a remark, we denote the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G(z)^{(i)}$ in equation \eqref{defm}.
+As a remark, we define the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G^{(i)}(z)$ in equation \eqref{defm}.
 
 \paragraph{Self-consistent equations.}
-We briefly describe the ideas for deriving the equation set \eqref{selfomega_a}.
-A complete full can be found in Lemma \ref{lemm_selfcons_weak}.
+We briefly describe the ideas for deriving the system of self-consistent equations \eqref{selfomega_a}.
+A complete proof can be found in Lemma \ref{lemm_selfcons_weak}.
 We show that with high probability, the following equations hold approximately:
@@
 \ee
-These are the self-consistent equations that we stated in equation \eqref{selfomega_a}.
+With algebraic calculations, it is not hard to verify that these equations reduce to the self-consistent equations that we stated in equation \eqref{selfomega_a} up to a small error $\oo(1)$.
 More precisely, we have that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_1} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$.
@@
 \begin{align*}
-	&G_{i,i}^{-1}(z) = -z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i} G^{\left( i \right)}_{\mu,\nu}(z) -\frac{2\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) \\
-	&G_{\mu,\mu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{i,j}(z) \\
-	&G_{\nu,\nu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{i,j}(z).
+	&G_{ii}^{-1}(z) = -z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu\nu}(z) - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i} G^{\left( i \right)}_{\mu\nu}(z) -\frac{2\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu\nu}(z) \\
+	&G_{\mu\mu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{ij}(z) \\
+	&G_{\nu\nu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{ij}(z).
 \end{align*}
 For the first equation, we expand the Schur complement formula $G_{ii}^{-1}(z) = -z - H_i G^{(i)}(z) H_{i}^\top$, where $H_i$ is the $i$-th row of $H$ with the $(i,i)$-th entry removed.
-The second and third equation follow by similar calculations.
+The second and third equations follow by similar calculations.
 
@@
 Next, we apply standard concentration bounds to simplify the above results.
-For $G^{-1}_{i, i}(z)$, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
+For $G^{-1}_{i i}(z)$, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
 Hence by standard concentration inequalities, we have that the cross terms are approximately zero.
@@
 \begin{align*}
-	G_{i,i}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
-	&= - z - \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1^{(i)}(z)-  \frac{n_2}{n_1 + n_2} m_2^{(i)}(z)+\oo(1)
+	G_{ii}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
+	&= - z - \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1^{(i)}(z)-  \frac{n_2}{n_1 + n_2} m_2^{(i)}(z)+\oo(1),
 \end{align*}
-by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ with respect to the resolvent minor $G^{(i)}(z)$.
-Since we removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
+by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$. %with respect to the resolvent minor $G^{(i)}(z)$.
+Since we have removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
 Hence we obtain that
 \begin{align}\label{1self_Gii}
-	G_{i,i}(z)  = -\left(z + \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1 + n_2} m_2(z) + \oo(1)\right)^{-1}.
+	G_{ii}(z)  = -\left(z + \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1 + n_2} m_2(z) + \oo(1)\right)^{-1}.
 \end{align}
-For the other two blocks $\cal I_1$ and $\cal I_2$, using similar ideas we have that the following holds with high probability
+For the other two blocks $\cal I_1$ and $\cal I_2$, using similar ideas we obtain the following equations with high probability:
 \begin{align*}
-	G_{\mu,\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} \\
-	G_{\nu,\nu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
+	G_{\mu\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1},\quad G_{\nu\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
 \end{align*}
@@
 \begin{align*}
-	m_1(z) &= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu,\mu}(z) = -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} \\
-	m_2(z) &= \frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu,\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
+	m_1(z) &= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) = -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} ,\\
+	m_2(z) &= \frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
 \end{align*}
 Furthermore, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability
-$G_{\mu,\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu, \nu}(z) = m_2+\oo(1)$.
+$G_{\mu\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu\nu}(z) = m_2+\oo(1)$.
 In other words, both block matrices within $\cal I_1$ and $\cal I_2$ are approximately a scaling of the identity matrix.
@@
 \begin{align*}
-	m_1^{-1}(z) = -1- \frac{1}{n_1 + n_2} \sum_{i=1}^p \lambda_i^2 G_{i,i}(z)+ \oo(1) \\
-	m_2^{-1}(z) = -1- \frac{1}{n_1 + n_2} \sum_{i=1}^p G_{i,i}(z)  + \oo(1).
+	m_1^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p \lambda_i^2 G_{i,i}(z)+ \oo(1),\quad  m_2^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p G_{i,i}(z)  + \oo(1).
 \end{align*}
-where we used the definition of $m(z)$ and $m_0(z)$.
-By applying equation \eqref{1self_Gii} for $G_{i, i}(z)$, we obtain the self-consistent equations \ref{approximate m1m2}.
+where we used the definitions of $m(z)$ and $m_0(z)$.
+By applying equation \eqref{1self_Gii} for $G_{i i}(z)$ to these two equations, we obtain the system of self-consistent equations \eqref{approximate m1m2}.
 In Lemma \ref{lem_stabw}, we show that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.
@@
 Finally, we derive the matrix limit $\Gi(z)$.
-Applying our solution for $m_1(z)$ and $m_2(z)$ into equation \eqref{1self_Gii}, we get that for $i$ in $\cal I_0$,
-$G_{i, i}(z) = (-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1}$.
-Similarly, for $\mu$ in $\cal I_1$, we have that $G_{\mu, \mu}(z) = -\frac{n_1 + n_2}{n_1}a_{1}(z)+\oo(1)$, and for $\nu$ in $\cal I_2$, we have that $G_{\nu, \nu}(z) = -\frac{n_1 + n_2}{n_2}a_{2}(z)+\oo(1)$.
+We have shown that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_1} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$ because we know that \eqref{approximate m1m2} holds.
+Inserting $m_1(z)$ and $m_2(z)$ into equation \eqref{1self_Gii}, we get that for $i$ in $\cal I_0$,
+$G_{ii}(z) = (-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1}$ with high probability.
+For $\mu$ in $\cal I_1$ and $\nu$ in $\cal I_2$, by $G_{\mu\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu\nu}(z) = m_2+\oo(1)$, we have that $G_{\mu \mu}(z) = -\frac{n_1 + n_2}{n_1}a_{1}(z)+\oo(1)$ and $G_{\nu\nu}(z) = -\frac{n_1 + n_2}{n_2}a_{2}(z)+\oo(1)$ with high probability.
 Hence we have derived the diagonal entries of $\Gi(z)$.
 In Lemma \ref{Z_lemma}, we show that the off-diagonal entries are close to zero.
-For example, for $i\ne j\in \cal I_1$, by Schur complement, we have that
-$$G_{i,j}(z) = -G_{i,i}(z)\cdot {n^{-1/2}}\Big({\lambda_i}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu, j}(z) + \sum_{\mu \in \cal I_2} Z^{(2)}_{\mu, i} G^{(i)}_{\mu, j}(z) \Big).$$
-Using standard concentration inequalities, we show that $\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu, j}(z)$ and $\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu, j}(z)$ are both close to zero.
+For example, for $i\ne j\in \cal I_0$, by Schur complement, we have that
+$$G_{ij}(z) = -G_{ii}(z)\cdot {n^{-1/2}}\Big({\lambda_i}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}(z) + \sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}(z) \Big).$$
+Using standard concentration inequalities, we can show that $\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu j}(z)$ and $\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu j}(z)$ are both close to zero.
 The other off-diagonal entries are bounded similarly.
@@
 \paragraph{Notations.}
-We introduce several notations for the proof of Theorem \ref{thm_main_RMT}.
+We introduce several useful notations for the proof of Theorem \ref{thm_main_RMT}.
 We say that an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
@@
 Furthermore, this also includes the random variables that do not depend on $n$ as a special case.}]
-We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for any $n > n_0(\e, D)$,
+We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for all $n > n_0(\e, D)$,
 \[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
@@
 We make several remarks.
-First, since we allow an $n^\e$ factor in stochastic domination, we can ignore log factors without loss of generality since $(\log n)^C\prec 1$ for any constant $C>0$.
+First, since we allow an $n^\e$ factor in stochastic domination, we can ignore $\log$ factors without loss of generality since $(\log n)^C\prec 1$ for any constant $C>0$.
 Second, given a random variable $\xi$ whose moments exist up to any order, we have that $|\xi|\prec 1$.
-This is because by Markov's inequality, let $k$ be greater than $D/ \e$, then we have that
+This is because by Markov's inequality, let $k$ be larger than $D/ \e$, then we have that
 $$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D}.$$
-This implies that a Gaussian random variable $\xi$ with unit variance satisfies that $|\xi|\prec 1$.
+As a special case, this implies that a Gaussian random variable $\xi$ with unit variance satisfies that $|\xi|\prec 1$.
 
 The following fact collects several basic properties that are often used in the proof.
+Roughly speaking, it shows that  the stochastic domination ``$\prec$" behaves in the same way as  ``$<$" in some sense.
+
 \begin{fact}[Lemma 3.2 in \cite{isotropic}]\label{lem_stodomin}
@@
 \begin{equation}
-	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i, j} \vert \prec q. \label{eq_support}
+	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i j} \vert \prec q. \label{eq_support}
 \end{equation}
@@
 \begin{align}
-	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) &\le \sum_{i=1}^n \sum_{j=1}^p \P\left(|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right)  \nonumber\\
-	&\le \sum_{i=1}^n \sum_{j=1}^p \frac{C}{\left[(\log n) n^{\frac{2}{\varphi}}\right]^\varphi} = \OO((\log n)^{-\varphi}).\label{Ptrunc}
+	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i  j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) &\le \sum_{i=1}^n \sum_{j=1}^p \P\left(|Z_{i j}|\ge (\log n) n^{\frac{2}{\varphi}}\right)  \nonumber\\
+	&\le \sum_{i=1}^n \sum_{j=1}^p \frac{C(\varphi)}{\left[(\log n) n^{\frac{2}{\varphi}}\right]^\varphi} = \OO((\log n)^{-\varphi}).\label{Ptrunc}
 	\end{align}
-In other words, $Z$ has bounded support $q=n^{\frac{2}{\varphi}}$ with high probability.
+In other words, $Z$ has bounded support $q=n^{\frac{2}{\varphi}}$. %with high probability.
 %This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}. %This fact will be used in the proof of Corollary \ref{main_cor} below.

### 2020-10-17 arxiv/proof_gaussian_case.tex
appendix

@@
 To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
-	\[ \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
+	\be\label{defn AF} \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \ee
 %}\HZ{what does this trick mean? use less technical words},
@@
 Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
-	\begin{equation*} %\label{green2}
+	\begin{equation} \label{green2}
 	  G(z) =  \left( {\begin{array}{*{20}c}
@@
 		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
-  \end{equation*}
+  \end{equation}
 
@@
 %\end{align*}
-Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(z)}{\dd z}$.
+Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(0)}{\dd z}$.
 %then taking implicit differentiation of equation \eqref{selfomega_a}
@@
 Next, we introduce the bounded support assumption for a random matrix.
-We say that a random matrix $Z \in\real^{n \times p}$ satisfies the {\it{bounded support condition}} with $q$ or $Z$ has support $q$ if
+We say that a random matrix $Z \in\real^{n \times p}$ satisfies the {\it{bounded support condition}} with $Q$ or $Z$ has support $Q$ if
 \begin{equation}
-	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i j} \vert \prec q. \label{eq_support}
+	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i j} \vert \prec Q. \label{eq_support}
 \end{equation}
@@
 	\end{align}
-In other words, $Z$ has bounded support $q=n^{\frac{2}{\varphi}}$. %with high probability.
+In other words, $Z$ has bounded support $Q=n^{\frac{2}{\varphi}}$ with high probability.
 %This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}. %This fact will be used in the proof of Corollary \ref{main_cor} below.

### 2020-10-17 arxiv/proof_examples.tex
appendix

@@
 
-We follow a similar logic from Theorem \ref{thm_many_tasks}.
-We characterize the global minimizer of $f(A, B)$ in the random-effects model.
+We follow a similar logic as in the proof of Theorem \ref{thm_many_tasks}.
+We first characterize the global minimizer of $f(A, B)$ in the random-effects model.
 Based on the characterization, we reduce the prediction loss of hard parameter sharing to the asymptotic limits provided in Theorem \ref{thm_main_RMT}.
@@
 Otherwise, we add a tiny amount of perturbation $\delta$ to them and the result remains the same.
-Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we have that $\hat{B}$ satisfies the following
+Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we obtain that $\hat{B}$ satisfies the following
 	\begin{align}
-		\hat{B} \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\
+		\hat{B} \define  \left[A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)}\right]^{-1} \left[A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}\right]. \label{eq_Bhat_2task} %\\
 		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
@@
  \begin{align}
-		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)})+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)} \right.
+\nonumber\\
 		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
+		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta^{(1)}-x^2\beta^{(2)})+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} \right.
+\nonumber\\
 		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2.
@@
 	\end{align}
-The conditional expectation of $g(x)$ over $\epsilon_1$ and $\epsilon_2$ is
+The conditional expectation of $g(x)$ over $\epsilon^{(1)}$ and $\epsilon^{(2)}$ is
 %\HZ{could you align the Eq so that they look better on page?}
 \begin{align}
-\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}
-&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2 \nonumber\\
-&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2  \nonumber\\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \nonumber\\
-&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
+\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}}
+&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \nonumber\\
+&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  \nonumber\\
+& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}} \nonumber\\
+&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
 &+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
@@
 \begin{align*}
- & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2 \\
-=&(\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta_1-x\beta_2)\\
-&+(\beta_1-x\beta_2)^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\\
-%&=(\beta_1-x\beta_2)^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\\
-=&(\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2).
+ & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \\
+=&(\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta^{(1)}-x\beta^{(2)})\\
+&+(\beta^{(1)}-x\beta^{(2)})^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\\
+%&=(\beta^{(1)}-x\beta^{(2)})^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\\
+=&(\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}).
 \end{align*}
@@
 \begin{align*}
-		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  \\
-		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
+		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}} \\
+		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  \\
+		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2 \right]\\
 &+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
-		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2) +\sigma^2(n_1+n_2-p).
+		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}) +\sigma^2(n_1+n_2-p).
 \end{align*}
-For the random-effects model, recall that the entries of $\beta_1, \beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $\kappa^2/p, d^2/p$, respectively.
+For the random-effects model, recall that the entries of $(\beta^{(1)}- x\beta^{(2)})\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 +(1+x^2) d^2]$.
 Hence, 
 \begin{align}
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2} \nonumber\\
+&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta^{(1)},\beta^{(2)}}{g(x) \mid X_1, X_2} \nonumber\\
 %&=[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
 %&+ A^2[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
 \end{align}
@@
  In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
-$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right).$$
-%for any small constant $c>0$.
+$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta^{(1)},\beta^{(2)}}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right)$$
+for any small constant $c>0$.
  \end{claim}
  \begin{proof}
-By Fact \ref{fact_minv}(ii), we have that with high probability,
+By Fact \ref{fact_minv} (ii), we have that with high probability,
  \be\label{op_X12}
@@
  \ee
-where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
+where we used that $3\le n_1/p\le \tau^{-1}$ and $3\le n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
 
@@
  \begin{align}
- & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+ & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)})+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)} \right.
+\nonumber\\
 		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
@@
  \begin{align*}
-&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
-& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
+&h_1(x):=  (\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  ,\\
+& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}}  ,\\
 & h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
-& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
-&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
-&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
+& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)}), \\
+&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)}),\\
+&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}.
 \end{align*}
@@
 
-For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
+For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $(\beta^{(1)}-x\beta^{(2)})\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]$, we obtain the following estimate with high probability for any small constant $c>0$:
 \begin{align}
-&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
-&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
+&\left|h_1(x) - \exarg{\beta^{(1)},\beta^{(2)}}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
+&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
+&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
 \end{align}
@@
 Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+Gaussian random variables with mean zero and variances $\sigma^2$, and the bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
 \be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
@@
 &\left|h_4(x)\right| \nonumber\\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
+&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\le  p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2} \cdot \left\|  \id_{n_1\times n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2).\label{eq_hA4}
 \end{align}
-where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
-With same argument, we can show that
+Above, in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and equations \eqref{op_X12} and \eqref{op_Sig1}.
+In the last step we used AM-GM inequality.
+With the same argument, we can show that
 \be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
@@
 %There exists a constant $C>0$ such that
-	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}.
+	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}
 	\ee
-%	for any small constant $c>0$.
+	for any small constant $c>0$.
 	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
@@
 \begin{align*}
-h(x):= [(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right].
+h(x):= [(x-1)^2\kappa^2 + (x^2+1)d^2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right].
 \end{align*}
-Using Fact \ref{fact_minv}(ii), we can obtain that with high probability,
+Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
 \begin{align}
@@
 \end{align}
-where we also used that $1+\tau\le \rho_1=n_1/p \le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
-\be\label{eq_h1}h(1)= d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
+where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
+\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
 On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
@@
 \end{align}
-where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and \eqref{op_uplow}.
+where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
 %and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
-Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability,
+Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1} and \eqref{eq_hA}, we obtain that with high probability,
 \begin{align}
-g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
-&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
+g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
+&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
 \end{align}
-under conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
+under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
 This gives that
@@
 \begin{align}
-L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right\| \nonumber\\
-&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta_1-\hat x^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
+L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta^{(2)}\right)\right\| \nonumber\\
+&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta^{(1)}-\hat x^2\beta^{(2)})+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
 \end{align}
@@
 Now we give the proof of the estimate \eqref{claim_largedev2}.
-The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
+The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$ and $\beta^{(2)}$.
 In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
 Here we only give a proof sketch and omit the details.
-Recall that $\beta_0$ is the shared component of $\beta_1$ and $\beta_2$ with i.i.d.
+Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d.
 Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
-Moreover, we denote the task-specific components by $\wt\beta_1$ and $\wt\beta_2$, whose entries are i.i.d.
+Moreover, we denote the task-specific components by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, whose entries are i.i.d.
 Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$.
@@
 \begin{align}
-L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta_1 - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta_2 \right] \right.
+L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta^{(1)} - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta^{(2)} \right] \right.
 \nonumber\\
@@
 As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}.
-For example, for the main term $\hat x^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
+For example, for the main term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using
 Lemma \ref{largedeviation} and equation \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability:
 \begin{align*}
-&  \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1 - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
+&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
 &\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
@@
 \end{align*} 
-For the cross term $\hat x \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
 \begin{align*}
- \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
+ \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
 &\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\

### 2020-10-17 arxiv/proof_examples.tex
appendix

@@
 \begin{align*}
-h(x):= [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
+h(x):= [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
 \end{align*}
@@
 \begin{align}\label{h'(A)1}
-h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - \frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,
+h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - 2\frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,
 \end{align}
-as long as $x \ge 1+d^2/(2\kappa^2)$.
+as long as $x \ge 1+d^2/\kappa^2$.
 %\begin{align}
@@
 \begin{align}\label{h'(A)2}
-	h'(x)\le [-2(1-x)\kappa^2 + xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,
+	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,
 \end{align}
-as long as $x\le 1-d^2/(2\kappa^2)$. In sum, we see that the minimizer $x^\star$ must satisfy
-$$1-d^2/(2\kappa^2)\le x^\star \le 1+d^2/(2\kappa^2).$$
+as long as $x\le 1-d^2/\kappa^2$. In sum, we see that the minimizer $x^\star$ must satisfy
+$$1-d^2/\kappa^2\le x^\star \le 1+d^2/\kappa^2.$$
 
@@
 
-Now we are ready to prove equation \eqref{hatw_add1}. First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le x\le 1+\delta$,
-$$h'(x)\ge \frac{2(x-1)\kappa^2 - d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
+Now we are ready to prove equation \eqref{hatw_add1}. First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+3d^2/(2\kappa^2) \le x\le 1+\delta$,
+$$h'(x)\ge \frac{2(x-1)\kappa^2 - 2d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
 Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+c}\le x\le 1+\delta$,
 \begin{align*}
-h(x)-h(1)\ge h(x)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot |x-1|^2  \gtrsim p\frac{d^4}{\kappa^2} + p^{-1/2+2c}\cdot p\kappa^2 .
+h(x)-h(1)\ge h(x)-h\left(1+\frac{3d^2}{2\kappa^2}\right) \ge \int_{1+\frac{3d^2}{2\kappa^2}}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot |x-1|^2  \gtrsim p\frac{d^4}{\kappa^2} + p^{1/2+2c} \kappa^2 .
 \end{align*}
@@
 $$ g(x)=h(x)+\sigma^2 (n_1+n_2-p)+\OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right)$$
-with high probability. Combining the above two estimates, we obtain that under the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$,
+with high probability. Combining the above two estimates, we obtain that under the conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$,
 $$g(x)-g(1) = h(x)-h(1) + \OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right) >0$$
@@
 %$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$ where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
-Second, using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le x \le 1-d^2/\kappa^2$,
-$$- h'(x)\ge  [2(1-x)\kappa^2 - xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
+Second, using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le x \le 1-3d^2/(2\kappa^2)$,
+$$- h'(x)\ge  [2(1-x)\kappa^2 - 2xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
 Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-1/4+c}\le x\le 1-\delta$, then
@@
 %under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?},
-which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ must satisfy equation \eqref{hatw_add1}.
+which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ of $g$ must satisfy equation \eqref{hatw_add1}.
 %Next we prove the following estimate on the optimizer $\hat x$: with high probability,
@@
 \begin{align}
-L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta^{(2)}\right)\right\| \nonumber\\
+L(\hat{\beta}_2^{\MTL}) &=\left\|(\Sigma^{(2)})^{1/2} \left( \hat B \hat A_2 - \beta^{(2)}\right)\right\| \nonumber\\
 &=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta^{(1)}-\hat x^2\beta^{(2)})+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
 \end{align}
-Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as in the following claim.
+Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows.
 
 \begin{claim}\label{claim_reduction}
-Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. Section \ref{sec_diff}).
-In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability
+Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. equation \eqref{def hatsig}).
+In the setting of Proposition \ref{cor_MTL_loss}, we have the following estimate with high probability for any small constant $c>0$:
 \begin{align*}
-&\left|L(\hat{\beta}_2^{\MTL}) - d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{{\hat \Sigma^{-1}  }}\right| \nonumber\\
+&\left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
 \lesssim&  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2).
@@
 \begin{align*}
-	\cal L(\hat x)	:=  &\hat x^2\left[(\hat x-1)^2 \kappa^2 + \frac{(\hat x^2+1)d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} } \\
+	\cal L(\hat x)	:=  &\hat x^2\left[(\hat x-1)^2 \kappa^2 +  (\hat x^2+1)d^2 \right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} } \\
 	& +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
@@
 % \end{claim}
-We are ready to finish the proof of Claim \ref{claim_reduction}.
+%We are now ready to finish the proof of Claim \ref{claim_reduction}.
 We defer the proof of equation \eqref{claim_largedev2} until the end.
-Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
+Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_{p\times p}$.
 More precisely, we claim that with high probability
 \begin{align}
-&\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\hat \Sigma^{-1}  }\right| \nonumber\\
-&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
+&\left|\cal L(\hat x)- \frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left(\hat \Sigma^{-1}  \right)\right| \nonumber\\
+\lesssim & \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
 \end{align}
-Combining \eqref{claim_largedev2} and \eqref{simple12}, we obtain Claim \ref{claim_reduction}.
+Combining equations \eqref{claim_largedev2} and \eqref{simple12}, we conclude Claim \ref{claim_reduction}.
 
-It remains to prove equation \eqref{simple12}. Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we obtain that with high probability,
+Now we prove equation \eqref{simple12}. Using Claim \ref{lem_hat_v} and equations \eqref{op_X12} and \eqref{op_Sig1}, we obtain that with high probability,
 \begin{align}
@@
 \end{align}
-Moreover, using equations \eqref{op_X12}-\eqref{op_Sig1} we can bound that with high probability,
+Moreover, using equations \eqref{op_X12} and \eqref{op_Sig1}, we can bound that with high probability,
 %$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
@@
 \end{align}
-Now we bound the left hand side of equation \eqref{simple12} as
+We can bound the left hand side of equation \eqref{simple12} as
 \begin{align*}
-&\left|\cal L(\hat x)-\frac{d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat\Sigma^{-1}  }\right)\right| \\
-&\lesssim \left(|\hat x-1|^2 \kappa^2 + |\hat x-1|d^2\right)\cdot p^{-1}\bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2 } \\
+&\left|\cal L(\hat x)-\frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat\Sigma^{-1}  }\right)\right| \\
+\lesssim &\left(|\hat x-1|^2 \kappa^2 + |\hat x-1|d^2\right)\cdot p^{-1}\bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2 } \\
 &+ \frac{d^2}{p}\left|\tr\left[\left(\hat\Sigma(\hat x)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\hat\Sigma(\hat x)^{-1}-\hat\Sigma^{-1}  }\right|.
@@
 
-Now we give the proof of the estimate \eqref{claim_largedev2}.
+Finally we give the proof of the estimate \eqref{claim_largedev2}.
 The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$ and $\beta^{(2)}$.
@@
 Moreover, we denote the task-specific components by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$.
+Gaussian random variables of mean zero and variance $p^{-1} d^2 $.
 Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
@@
 \end{align}
-As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}.
+As in equation \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in equations \eqref{eq_hA1}-\eqref{eq_hA56}.
 For example, for the main term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using
-Lemma \ref{largedeviation} and equation \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability:
+Lemma \ref{largedeviation} and equations \eqref{op_X12} and \eqref{op_Sig1}, we can obtain the following estimate with high probability:
 \begin{align*}
-&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
+&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{p}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
 &\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
@@
 \end{align*} 
-For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and equations \eqref{op_X12} and \eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
 \begin{align*}
  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
-&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
+&\lesssim p^{c}\cdot \sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
 &\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
@@
 Finally, we are ready to complete the proof of Corollary \ref{cor_MTL_loss}.
-We derive the variance term $\sigma^2  \tr[\hat\Sigma^{-1}]$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
+We derive the variance term $\sigma^2  \tr[\hat\Sigma^{-1}]$ and the bias term $\frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
 
 \begin{proof}[Proof of Corollary \ref{cor_MTL_loss}]
-Using \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1\id_p+a_2\id_p)^{-1}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
+Using equation \eqref{lem_cov_shift_eq}, we obtain that
+\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
 with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
 	\begin{align}
-		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} . \label{simplesovlea12}
+		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
+		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
 			\end{align}
 Applying the above to equation \eqref{eq_var111}, we obtain that
-\be\label{eq_var112}\bigtr{\hat\Sigma^{-1}}  = \frac{p}{n_1+n_2} \cdot \frac{\rho_1+\rho_2}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})=  \frac{1}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})\ee
+\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi})\ee
 with high probability.
@@
 $$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
-by Fact \ref{fact_minv}(ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
-Using \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_p$ and $w$ being the $i$-th coordinate vector, we can calculate that 
+by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
+Using equation \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$ and $w$ being the $i$-th coordinate vector, we can calculate that 
 \begin{align}\label{eq_bias112}
- \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})
+ \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right]
 \end{align}
@@
 		% a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad & a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
-		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
-		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}. %\label{simplesovlea34}
+		a_3 = \frac{p\cdot n_1}{(n_1 +n_2)(n_1 +n_2 - p)}, \quad
+		&  a_4 = \frac{p\cdot n_2}{(n_1 + n_2)(n_1 + n_2 - p)}. %\label{simplesovlea34}
 	\end{align*}
-Inserting them into \eqref{eq_bias112}, we obtain that 
+Inserting them into equation \eqref{eq_bias112}, we obtain that 
 \begin{align*}%\label{eq_bias113}
- \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} +\OO(p^{-c_\varphi})
+ \left(\hat\Sigma^{-2}\right)_{ii} =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right]
 \end{align*}
-with high probability. In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use \eqref{apply derivlocal} to get that 
+with high probability. In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that 
 \begin{align*}%\label{eq_bias113}
-\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{-\frac{\varphi-4}{2\varphi}}
+\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
 \end{align*}
@@
 \begin{align*} 
-\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{1-\frac{\varphi-4}{2\varphi}}
+\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{1-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
 \end{align*}
@@
 \begin{align}\label{eq_bias113}
-\left| p^{-1}\sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\le p^{-c_\varphi}
+\left| p^{-1}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\le \frac{p^{-c_\varphi}}{(n_1+n_2)^2}
 \end{align}
-with high probability. Inserting \eqref{eq_bias113} into \eqref{eq_bias111}, we get that
+with high probability. Inserting equation \eqref{eq_bias113} into equation \eqref{eq_bias111}, we get that
 \begin{align*}
-		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\nonumber \\
-		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} \nonumber\\
-		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}
+		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\nonumber \\
+		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3} \nonumber\\
+		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}
 \end{align*}
@@
 \begin{align*}
-	\left|\cal L(\hat x)- \frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right| \le   \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \nonumber\\
+	\left|L(\hat{\beta}_2^{\MTL})  - \frac{\sigma^2 p}{n_1+n_2-p} -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3}\right| \le   \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \nonumber\\
 +C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
 \end{align*}
-Then using Claim \ref{claim_largedev2} and the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$, we conclude the proof.
+Then using the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-\e}{\kappa^2}$, we conclude the proof.
 \end{proof}

### 2020-10-18 arxiv/tools.tex
appendix

@@
 
-The following simple resolvent identities are important tools for our proof. Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}.
+The following simple resolvent identities are important tools for our proof.
+Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{diagW}.
 \begin{lemma}\label{lemm_resolvent}
@@
 \begin{equation}
-\frac{1}{G_{ii}} =  - z - \left( {AG^{\left( i \right)} A^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {A^\top  G^{\left( \mu  \right)} A} \right)_{\mu \mu }.\label{resolvent2}
+\frac{1}{G_{ii}} =  - z - \left( {\AF G^{\left( i \right)} \AF^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {\AF^\top  G^{\left( \mu  \right)} \AF} \right)_{\mu \mu }.\label{resolvent2}
 \end{equation}
@@
 \begin{equation}
-G_{ia}   = -G_{ii}  \left( AG^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( A^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
+G_{ia}   = -G_{ii}  \left( \AF G^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( \AF^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
 \end{equation}
@@
 \begin{fact}\label{fact_minv}
-	In the setting of Theorem \ref{thm_many_tasks}, with high probability over the randomness of $X$, we have that
+	In the setting of Theorem \ref{thm_many_tasks}, with overwhelming probability over the randomness of $X$, we have the following:
 	\begin{enumerate}
-		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is of full rank.
+		\item When $n / p$ converges to a fixed $\rho > 1$, the sample covariance matrix ${X^{\top}X} $ is of full rank.
 		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf.
@@
 Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers.
-Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and $ x_i$ and $ y_j$ satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $q$.
+Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $Q$.
 %with $q\le n^{-\phi}$ for a small constant $\phi>0$.
@@
 \begin{align}
-\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec  q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec q^2 B_d  + q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
-\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20}
+\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec Q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec Q^2 B_d  + Q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
+\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec Q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec Qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20}
 \end{align}
-where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have stronger bounds
+where we denote $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have stronger bounds
 \begin{align}
-\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
+\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i, j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
  \Big\vert  \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec  \Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert  \sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
@@
 \begin{corollary} \label{cor_largedeviation}
-Let $Z\in \R^{n\times p}$ be a random matrix as in Assumption \ref{assume_rm}. Then for any deterministic vector $v\in \R^p$, we have that
+Let $Z\in \R^{n\times p}$ be a random matrix in the setting of Section \ref{sec_same}. Then for any deterministic vector $v\in \R^p$, we have that
 \be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2\ee
@@
 We introduce the truncated matrices $\wt Z$ with entries
-$ \wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le q \right)\cdot Z_{ij} $
-for $q= n^{1/2-\frac{\varphi - 4}{2\varphi}}\log n$. By equation \eqref{Ptrunc}, we have that
+$ \wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le Q \right)\cdot Z_{ij} $
+for $Q= n^{ \frac{2}{\varphi}}\log n$. By equation \eqref{Ptrunc}, we have that
 \begin{equation}\label{XneX222}
@@
 \be\label{show_whZ}
- \left|\|\wh Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2.
+ \left|\|\wh Zv\|^2- n\|v\|^2\right|\prec n^{1/2} Q\|v\|^2.
 \ee 
 In fact, provided that \eqref{show_whZ} holds, using \eqref{meanshif222} it is easy to get that 
-$$ \left|\|\wt Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2,$$
+$$ \left|\|\wt Zv\|^2- n\|v\|^2\right|\prec n^{1/2} Q\|v\|^2,$$
 which implies \eqref{Zv_cor} for any fixed value $c_{\varphi}$ within $(0, \frac{\varphi - 4}{2\varphi})$.
 
-For \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$.
-Moreover, using \eqref{eq largedev10} we get that
-$$ |(\wh Zv)_i| \prec q \max_{1\le i\le p}|v_i| + \|v\| . $$
-Together with the trivial $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $q$.
-Then applying \eqref{eq largedev20}, we get that
-$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\prec n^{1/2} q  \|v\|^2 .
+To prove equation \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$.
+Moreover, using equation \eqref{eq largedev10} we get that
+$$ |(\wh Zv)_i| \prec Q\max_{1\le i\le p}|v_i| + \|v\| . $$
+Together with the trivial bound $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $Q$.
+Then applying equation \eqref{eq largedev20}, we get that
+$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\prec n^{1/2} Q  \|v\|^2 .
  $$
-This concludes \eqref{show_whZ}.
+This concludes equation \eqref{show_whZ}.
  \end{proof}
@@
 random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order.
-Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
+Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B$, we have that with high probability,
 \be\label{vcalE} |v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \ee
@@
 \begin{align*}
-\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
+\left|(\epsilon^{(i)})^\top B \epsilon^{(i)} - \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
 &\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
 \end{align*}
-The above two estimates conclude  \eqref{vcalA2}.
+The above two estimates conclude equation \eqref{vcalA2}.
 Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.

### 2020-10-18 arxiv/experiments_text.tex
section A B

@@
 
-Our results and their implications are all in the high-dimensional linear regression setting.
+Our results and simulations are all in the high-dimensional linear regression setting.
 How well do they extend to other scenarios?
-In this section, we conduct further studies on six text classification datasets, for predicting whether a sentence has a positive or a negative sentiment.
-Our datasets include a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
+In this section, we conduct further studies on six text classification datasets.
+Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
 %The question is to predict positive or negative sentiment expressed in the text.
@@
 \paragraph{Sample size ratio.}
+First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
 In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
@@
 %validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops:
+We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.
+
+These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
+Concretely, here is one implementation of this idea.
 %In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
@@
 \begin{itemize}
-	\item We divide the source task data into $S$ batches.
-	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
-	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
+	\item We divide the training data into $S$ batches.
+	We divide the training procedure into $S$ stages. During every stage, we progressively add one more data batch.
+	\item During every stage, we train for $T$ epochs using only the $S$ batches.
+If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
 %	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
@@
 For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
+%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
 The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-
-%\begin{algorithm}[!t]
-%	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-%		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, W_2$ optimized for task $2$.
-%		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}
+For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
 
@@
 We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ pairs from the six datasets.
-We find that adding task one's samples progressively requires only $45\%$ of the computational cost to achieve the same test accuracy for task two compared to the standard round-robin training schedules.
+First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
+We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
+We include all of task two's data and progressively add task one's data using the procedure described above.
+Since the prediction accuracy has been controlled the same, we compare the computational cost.
+We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
 %Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
@@
 %Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we conduct multi-task training on all six datasets.
-We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than the standard round-robin training schedules.
+Second, we conduct multi-task training on all six datasets jointly.
+We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
+We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
+We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
 %As a further validation, excluding TREC, we observe similar comparative results.
@@
 Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample ratio rises.
+This highlights the need for correcting covariate shifts when the sample size ratio rises.
 To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, designed to correct covariate shifts.
@@
 To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample ratio increases, performing covariance alignment provides more significant gains over HPS.
+The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
 We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
@@
 	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
+	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
 	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
@@
 \end{figure}
+
+%\begin{algorithm}[!t]
+%	\caption{A progressive training schedule given two tasks}
+%	\label{alg_inc_train}
+%	\begin{algorithmic}[1]
+%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
+%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
+%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+%		\Output The trained modules $B, A_2$ optimized for task $2$.
+%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+%		\For{$i = 1,\dots, S$}
+%			\For{$j = 1,\dots, T$}
+%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
+%			\EndFor
+%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
+%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+%				\State \textbf{break}
+%			\EndIf
+%		\EndFor
+%	\end{algorithmic}
+%\end{algorithm}

### 2020-10-18 arxiv/proof_same_cov.tex
section A B

@@
 
-	Our next claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
+	We fill in missing details in the proof. Our first claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
 	\begin{claim}\label{claim_opt_dist}
@@
 		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
-				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r- \lambda_{r+1}}. \]
+				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r({B^{\star}}^{\top}\Sigma B^{\star})- \lambda_{r+1}({B^{\star}}^{\top}\Sigma B^{\star})}. \]
 	\end{claim}
@@
 			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
-			\le  n^{-1/4} \left(\|\Sigma^{1/2}B^{\star} \|^2+ \sigma^2  \cdot\|\hat a_i\|^2\right) .
+			\le  n^{-1/4} \left(L(B^{\star} \hat{a}_i) + \sigma^2  \cdot\|\hat a_i\|^2\right) .
 		\end{align*}
@@
 		$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
-		Combined together, our proof is complete. We omit the details.
+		Combined together, our proof is complete.
 %		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
@@
 	\end{align}
-	where in the second step we used $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
+	where in the second step we use $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
 	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
@@
 %	We consider both terms in the above equation one by one.
-	Second, notice that for the subspace projection $U_XU_X^\top:=X(X^{\top} X)^{-1} X^{\top}$ and $1\le i, j \le t$,
+	Second, we show that
+	%	\begin{align*}
+	%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
+	%	\end{align*}
+	%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
+	\begin{align*}
+		\exarg{\cE}{ \inner{\cW A}{\cE}} =\exarg{\cE}{\bigtr{\cal E^\top U_X U_X^\top \cal E U_AU_A^\top} }= p\sigma^2 \cdot \bigtr{ U_AU_A^\top} =  p \sigma^2 \cdot r,
+	\end{align*}
+	where $U_XU_X^\top = X(X^{\top} X)^{-1} X^{\top}$.
+	The first step follows by applying the definition of $\cW$.
+	The last step is because $U_AU_A^\top$ has rank $r$.
+	Hence, it suffices to show the second step is correct.
+	For any $1\le i, j \le t$, let $\delta_{i, j} = 1$ if $i = j$, and $0$ otherwise.
 	%\begin{align}
@@
 	%We observe that
+	Because $\varepsilon^{(i)}$ and $\varepsilon^{(j)}$ are pairwise independent, we have that
 	\begin{align*}
 			 \exarg{\cE}{(\cE^{\top}U_XU_X^\top \cE)_{ij} }
-		&= \exarg{\cE}{{\varepsilon^{(i)}}^\top U_X U_X^\top  \varepsilon^{(j)} } = \sigma^2 \cdot \tr\left( U_XU_X^\top \right) \cdot \delta_{ij} = p\sigma^2 \cdot \delta_{ij},
+		&= \exarg{\cE}{{\varepsilon^{(i)}}^\top U_X U_X^\top  \varepsilon^{(j)} } = \sigma^2 \cdot \tr\left[U_XU_X^\top \right] \cdot \delta_{ij} = p\sigma^2 \cdot \delta_{ij}.
 	\end{align*}
-	which implies that $\exarg{\cE}{\cE^{\top}U_XU_X^\top \cE }=p\sigma^2 \cdot \id_{t\times t}$.
-	Above, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
-	Therefore, we have that
-%	\begin{align*}
-%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
-%	\end{align*}
-%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
-	\begin{align*}
-		\exarg{\cE}{ \inner{\cW A}{\cE}} =\E \bigtr{\cal E^\top U_X U_X^\top \cal E U_AU_A^\top}= p\sigma^2 \cdot \bigtr{ U_AU_A^\top} =  p \sigma^2 \cdot r ,
-			\end{align*}
-   because $U_AU_A^\top$ has rank $r$.	
+	The last step uses the fact that $\tr[U_XU_X^\top] = p$.
+	Hence, the second step is correct.
+	%Above, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
 	%Next, note that
@@
 
-	Combining the above three parts, the proof of Claim \ref{lem_exp_opt} is completed.
+	Combining the three parts, the proof is complete.
 	\end{proof}
@@
 	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
-	In order to show that the $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
+	Let $\e$ be a fixed constant that is sufficiently small.
+	Let $c_{\infty}$ be any fixed value within $(0, 1/2 - \e)$.
+	To show that $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
 	\begin{align}\label{eq_gA_err}
-		\bigabs{g(A) - h(A)} \lesssim  n^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t,
+		\bigabs{g(A) - h(A)} \lesssim  n^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}_F^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
 	\end{align}
-	for any fixed values $c_{\varphi}$ within $(0, \frac{\varphi-4}{2\varphi})$ and $c_{\infty}$ within $(0, 1/2)$. 
 %	\begin{align}\label{eq_gA_err}
@@
 %	\end{align}
-	To show the above result, we consider the concentration error of each part of $g(A)$.
+	We consider the concentration error of each part of $g(A)$.
 
@@
 	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(n^{-c_\varphi}))$ with high probability. 
-	%, for a small enough constant $\e$,
 	This implies that
@@
 	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
-	using Corollary \ref{cor_calE}, we obtain the following with high probability for any small constant $\e>0$:
+	using Corollary \ref{cor_calE}, we obtain the following with high probability:
 	\begin{align}
@@
 		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
-		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n}\cdot \sqrt{t}\bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
-		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t,
-		\label{eq_gA_err2}
+		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \label{eq_gA_err2}
+%		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
 	\end{align}
-	which is bounded by the right hand side of equation \eqref{eq_gA_err} as long as $c$ is sufficiently small.
-	In the second step, we used the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})$ has rank at most $t$.
-In the fourth step, we used AM-GM inequality.
+	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
+	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$, and use $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})$ has rank at most $t$.
+	By the AM-GM inequality, equation \eqref{eq_gA_err2} is bounded by the right-hand side of \eqref{eq_gA_err}.
 
@@
 	\begin{align}
-		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left( \cal E^\top \id_{n\times n}\cal E\right) - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F \nonumber\\
-		&= n^{1/2+c} \cdot \sigma^2 \le n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t, \label{eq_gA_err3}
+		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left[ \cal E^\top \id_{n\times n}\cal E\right] - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F \nonumber\\
+		&= n^{1/2+c} \cdot \sigma^2 \le n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t. \label{eq_gA_err3}
 	\end{align}
-	as long as $c$ is sufficiently small. 
 	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
@@
 		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
-		&\le \sqrt{r} \cdot (n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F) \nonumber \\
-		&\le n^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r}  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t ,\label{eq_gA_err4}
+		&\le \sqrt{r} \cdot n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F \nonumber \\
+		&\le n^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r}  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.\label{eq_gA_err4}
 	\end{align}
-as long as $c$ is sufficiently small.
-Here in the third step, we applied equation \eqref{vcalAE3} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and used that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ is of rank $r$.
-In the fourth step, we used that $\|U_X U_X^\top\|_F=\sqrt{p}\le \sqrt{n}$ because $U_X$ is of rank $p$.
+	Here in the third step, we apply equation \eqref{vcalAE3} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and use that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ has rank $r$.
+In the fourth step, we use $\|U_X U_X^\top\|_F=\sqrt{p}$ because $U_X$ has rank $p$.
 
-%	\begin{align}
-%		\bigabs{\inner{\cW A}{\cE} - \ex{\inner{\cW A}{\cE}}} &= \bigabs{\bigtr{U_X U_X^{\top} (\cE U_AU_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n})}} \nonumber  \\
-%		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}} \nonumber \\
-%		&\le p^{1/2} \cdot (\sigma^2 r\cdot p^{\e}). \label{eq_gA_err4}
-%	\end{align}
-	%\begin{align*}
-	%	%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
-	%	\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
-	%	&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
-  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
-  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
-	%\end{align*}
-	%Combining equation \eqref{eq_gA_}, we get that with high probability
-	%\begin{align}
-	%	\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_gA_err}
-	%\end{align}
 	Combining equations \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain equation \eqref{eq_gA_err}.
@@
 		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
-		&\lesssim n^{-c_\varphi}\cdot n \bignorm{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
+		&\lesssim n^{-c_\varphi}\cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
 	\end{align}
@@
 	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
-	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$, and $v_i$, $1\le i \le t$, be the corresponding eigenvectors.
-Then we have $A^\star {A^\star}^\top =\sum_{i=1}^r v_i v_i^\top$, and
+	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$.
+	Let $v_i$ be the corresponding eigenvector of $\lambda_i$.
+	Then, we have $A^\star {A^\star}^\top =\sum_{i=1}^r v_i v_i^\top$, and
 	\begin{align}
@@
 	\end{align}
-	where we used $\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) = r- \sum_{i=1}^r  \| U^\top_{\hat A} v_i\|^2 =\sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2  $ in the last step.
+	where we use $\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) = r- \sum_{i=1}^r  \| U^\top_{\hat A} v_i\|^2 =\sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2  $ in the last step.
 	On the other hand, we have
 	\begin{align*}
-	\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2 & =\sum_{i=1}^t v_i^\top (A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})^2 v_i \\
-	& =\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) + \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2.
+	\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2
+	&= 2r - 2\inner{A^{\star}{A^{\star}}^{\top}}{U_{\hat{A}} {U_{\hat{A}}}^{\top}} \\
+	&= 2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2.
 	\end{align*}
-	Thus from \eqref{bdd_A-A}, we obtain that 
-	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignorm{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}  .$$
-	This completes the proof of Claim \ref{claim_opt_dist}.
+	Thus from equation \eqref{eq_g_gap} and  \eqref{bdd_A-A}, we obtain that
+	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}  .$$
+	Hence the proof is complete.
 	\end{proof}
@@
 	%We apply similar arguments from Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
-	The proof is similar to the one for equation \eqref{eq_gA_err}. 
+	The proof is similar to that of equation \eqref{eq_gA_err}.
 	The prediction loss of hard parameter sharing for task $i$ is equal to
@@
 	\paragraph{Part 1:} The first part is the bias term:
-	$\norm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta_i)}^2 = L(B^{\star} \hat{a}_i)$.
+	$\norm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta^{(i)})}^2 = L(B^{\star} \hat{a}_i)$.
 
-	\paragraph{Part 2:} The second part is the cross term, whose expectation over $\cE$ is zero. Using Corollary \ref{cor_calE}, the concentration error can be bounded as 
+	\paragraph{Part 2:} The second part is the cross term, whose expectation over $\cE$ is zero.
+	Let $b = B^{\star} \hat{a}_i - \beta^{(i)}$ for simplicity.
+	Using Corollary \ref{cor_calE}, the concentration error can be bounded as
 	\begin{align*}
-		& \bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta^{(i)})}{\Sigma^{1/2}R_i}} \\
-		\le &\sum_{1\le j, k\le t}|\hat a_i(j)| |\hat a_i(k)| \bigabs{ \inner{ X(X^\top X)^{-1}\Sigma \beta^{(j)} }{\epsilon^{(k)}}}  + \sum_{  j =1}^{t}|\hat a_i(j)|\bigabs{ \inner{ X(X^\top X)^{-1}\Sigma \beta^{(i)}}{\epsilon^{(j)}}} \\
-		\le & n^{c}\sigma \cdot \bignormFro{ X(X^\top X)^{-1}\Sigma B^{\star} } \cdot \left[ \sum_{j=1}^t |\hat a_i(j)| + \sum_{1\le j,k \le t} |\hat a_i(j)| |\hat a_i(k)| \right] \\
-		 \lesssim & n^{c}\sigma   \cdot \|\hat a_i\|\cdot \|\Sigma^{1/2}B^{\star} \| \cdot \| (Z^\top Z)^{-1} \|^{1/2}  \le  n^{-1/2+c}\sigma^2 \|\hat a_i\|^2 + n^{-1/2+c} \|\Sigma^{1/2}B^{\star} \|^2 , 
+		\bigabs{\inner{\Sigma^{1/2}b}{\Sigma^{1/2}R_i}}
+		&= \bigabs{\inner{X (X^{\top}X)^{-1} \Sigma b \hat{a}_i^{\top}}{\cE}} \\
+		&\le \sum_{j=1}^t \abs{\hat{a}_i(j)} \cdot \bigabs{\inner{X (X^{\top} X)^{-1} \Sigma b}{\varepsilon^{(j)}}} \\
+		&\le \sum_{j=1}^t \abs{\hat{a}_i(j)} \cdot n^{\e}\sigma \bignorm{X (X^{\top}X)^{-1} \Sigma b} \\
+		&\le \sqrt{t} \norm{\hat{a}_i} \cdot n^{\e} \sigma \bignormFro{X (X^{\top} X)^{-1} \Sigma b}.
 	\end{align*}
@@
 %	\end{align*}
-	with high probability for any small constant $c>0$.
-Here in the first step, we expand $B^\star \hat a_i=\sum_{1\le j \le t} \hat a_i(j) \beta^{(j)}$ amd $\cal E \hat a_i=\sum_{1\le j \le t} \hat a_i(j) \epsilon^{(j)}$.
-In the second step, we used equation \eqref{vcalE}.
-In the third step we used $\sum_j |\hat a_i(j)|\le \sqrt{t}\|\hat a_i\|$ by Cauchy-Schwarz inequality, and
+	In the first step, we plug in the definition of $R_i$ and re-arrange terms.
+	In the second step, we use $\hat{a}_i(j)$ to denote the $j$-th coordinate of $\hat{a}_i$.
+	In the third step, we use equation \eqref{vcalE}.
+	In the last step, we use $\sum_j |\hat a_i(j)|\le \sqrt{t}\|\hat a_i\|$ by Cauchy-Schwarz inequality.
+	Finally, we have
 	\begin{align*}
-	\bignormFro{ X(X^\top X)^{-1}\Sigma B^{\star}} &=\left[ {B^{\star}}^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma B^{\star} \right]^{1/2} \\
-	&\le  \|\Sigma^{1/2} B^{\star} \|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2}  =   \|\Sigma^{1/2} B^{\star} \|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2},
+		\bignormFro{ X(X^\top X)^{-1}\Sigma b} &=\left[ {b}^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma b \right]^{1/2} \\
+		&\le  \|\Sigma^{1/2} b \|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2}  =   \|\Sigma^{1/2} b \|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2} \\
+		&\le n^{-1/2} \cdot \norm{\Sigma^{1/2} b}.
 	\end{align*}
@@
 %	\end{align*}
-	because $X=Z\Sigma^{1/2}$. In the fourth step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\left\| (Z^\top Z)^{-1}\right\|$ by $\OO(n^{-1})$, and applied the AM-GM inequality.
+	Above, we use $X=Z\Sigma^{1/2}$. In the last step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z^\top Z$ by $\OO(n^{-1})$. %, and apply the AM-GM inequality.
+	One can see that the concentration error from this part is upper bounded by the result in Claim \ref{claim_pred_err}.
 
@@
 
-	\paragraph{Part 3:} The final part is $\|R_i\|^2$. We rewrite it as 
+	\paragraph{Part 3:} The final part is the squared term of $R_i$. We rewrite it as
 	\begin{align}
@@
 %	with high probability for any small constant $c>0$. On the other hand, if $j=k$, 
-	First we can calculate that 
+	First, for any $1 \le j, k \le t$, the expectation is
 	$$\exarg{\cal E}{{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} \epsilon^{(k)}}=\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right] .$$
-	Then using equation \eqref{vcalA2}, we obtain that 
+	Second, using equation \eqref{vcalA2}, the concentration error is at most
 	\begin{align}
@@
 	\le &n^c\cdot \sigma^2  \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} }   = n^c\cdot \sigma^2  \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
-	  \le &\sigma^2 \cdot p^{1/2} \cdot  \bignorm{(Z^{\top} Z)^{-1}}^{1/2} \lesssim \sigma^2 \cdot n^{-1/2+c}, \label{jeqk}
+	  \le &\sigma^2 \cdot p^{1/2} \cdot  \bignorm{(Z^{\top} Z)^{-1}}^{1/2} \lesssim \sigma^2 \cdot n^{-1/2+c}. \label{jeqk}
 	\end{align}
-	with high probability for any small constant $c>0$. 
-	Above, we used Fact \ref{fact_minv} (ii) in the last step to bound $ \bignorm{(Z^{\top} Z)^{-1}}$ by $\OO(n^{-1})$.
+	Above, we used Fact \ref{fact_minv}(ii) in the last step to bound the operator norm of $(Z^{\top} Z)^{-1}$.
 	Plugging equation \eqref{jeqk} into equation \eqref{E_i^2}, we obtain that 
 	\begin{align*}
-		\bigabs{\bignorm{\Sigma^{1/2} R_i}^2 -  \sigma^2 \|\hat a_i\|^2 \cdot\tr\left[\Sigma(X^\top X)^{-1}\right]} \lesssim  \sigma^2 \cdot n^{-1/2+c}  \sum_{1\le j,k\le t}|\hat a_i(j)||\hat a_i(k)|\lesssim  n^{-1/2+c} \sigma^2 \cdot  \|\hat a_i\|^2.
+		\bigabs{\bignorm{\Sigma^{1/2} R_i}^2 -  \sigma^2 \|\hat a_i\|^2 \cdot\tr\left[\Sigma(X^\top X)^{-1}\right]} \lesssim  \sigma^2 \cdot n^{-1/2+c}  \sum_{1\le j,k\le t}|\hat a_i(j)||\hat a_i(k)| =  n^{-1/2+c} \sigma^2 \cdot  \|\hat a_i\|^2.
 	\end{align*}
-
 %	One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\sigma^2 \norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
@@
 
-	Finally, combining the three parts together, we conclude the proof of Claim \ref{claim_pred_err}.
+	Finally, combining the three parts together, we complete the proof.
 \end{proof}
-	%\paragraph{Proof of Theorem \ref{thm_many_tasks}.}
-	%In sum, we have solved that $\hat{\beta}_i^{\MTL}=B^{\star}\left( U_r v_i +\oo(1)\right)$.
-	%Now we are ready to finish the proof.
-	%Similar to the proof of equation \eqref{eq_est_g1} and \eqref{eq_est_g2}, we have that
-	%\begin{align}
-	%	L(\hat{\beta}_t^{\MTL}) = \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL})} (1 + O(p^{-1/2+c})) + O(\sigma^2 \cdot p^{-1/2 + c}). \label{eq_multiple_last1}
-	%\end{align}
-	%Using equation \eqref{eq_ex_pred}, we have that
-	%\begin{align}
-	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{\hat{\beta}_t^{\MTL}} &= \bignorm{\Sigma^{1/2} \left((B^\star \hat{\cal W}^\top) (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t - \beta_t \right) }^2
-	%	+ \sigma^2  \hat W_t^{\top} (\hat{\cal W}\hat{\cal W}^{\top})^{-1} \hat W_t \cdot \bigtr{\Sigma (X^{\top}X)^{-1}} \nonumber \\
-	%	&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \oo\left(\bigtr{{B^{\star}}^{\top} \Sigma B^{\star}}\right) + \sigma^2(\norm{v_t}^2 + o(1)) \bigtr{\Sigma (X^{\top}X)^{-1}} \cdot (1+\oo(1)) \nonumber \\
-	%	&= \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} U_r v_t-\beta_t}}^2 + \frac{\sigma^2}{\rho-1}\norm{v_t}^2 + \oo \left( \bigtr{{B^{\star}}^{\top} \Sigma B^{\star}} + \sigma^2\right), \label{eq_multiple_last2}
-	%\end{align}
-	%In the second step, we use that $\norm{\hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \cW - U_r U_r^{\top}} \le o(1)$ w.h.p., which implies that
-	%\[ \bignorm{U_r v_t - \hat{\cW}^{\top} (\cW \cW^{\top})^{-1} \hat{\cW}_t} \le o(1) \quad \text{ and } \quad \bigabs{\hat{\cW}_t^{\top} (\hat{\cW} \hat{\cW}^{\top})^{-1} \hat{W}_t - \norm{v_t}^2} \le o(1).
-\]
-  %In the last step, we use Lemma \ref{lem_minv}, that is, $\bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \cdot (1 + o(1))/ (\rho - 1)$.
-	%Combining equation \eqref{eq_multiple_last1}, \eqref{eq_multiple_last2}, and $\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right)$, we conclude the proof.
-	%The second step uses the fact that $U_r U_r^{\top}$ is the global minimum of $\ex{g(\cdot)}$.
-	%In fact, if \eqref{Q-Q} does not hold, then using the condition $\lambda_{\min}((B^{\star})^\top\Sigma B^{\star})\gtrsim \sigma^2$ and that $\delta_{\vari}(\cal W)=\OO(\sigma^2)$ by  Lemma \ref{lem_minv}, we obtain that
-	%$$   \val(\hat {Q}) + t  \sigma^2 > (\val( Q_0) + t \sigma^2 )\cdot (1+\oo(1)) \ \Rightarrow \ g( \hat{\cal W})>g( {\cal W}_0),$$
-	%where $\cal W_0\in \R^{r\times t}$ is a matrix such that  $ \cal W_0^{\top} (\cal W_0\cal W_0^{\top})^{-1} \cal W_0=Q_0$. Hence $\hat {\cal W}$ is not a minimizer, which leads to a contradiction.
-	%with high probability
-	%\begin{align}
-	%g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
-	%&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
-	%\end{align}
-
-%		Applying the above estimates into $g_1(\cW)$, we get that
-%	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
-%	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
-%		Applying the above estimates into $g_1(\cW)$, we get that
-%	\begin{align}
-%	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
-%	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
-%	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
-%	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
-%	\end{align}
-%	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
-%	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
-%	In the last step, we use the AM-GM inequality.
-
-	%\paragraph{Proof of Lemma \ref{lem_error_same_cov}.} Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.
-
-	%and
-	%\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
-	%&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
-	%\end{align*}
-
-	%	\begin{align*}
-	%	g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
-	%	g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
-	%			&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j},\\
-	%	g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
-	%				\end{align*}

### 2020-10-18 arxiv/proof_gaussian_case.tex
appendix
section C

@@
 \section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
-We first state the bias limit for the term in equation \eqref{eq_bias_2task}.
+We first state the asymptotic limit for the bias equation \eqref{eq_bias_2task}.
 
@@
 			\begin{align}\label{lem_cov_derv_eq}
-				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - \frac{1}{(n_1+n_2)^2}{\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
+				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - \frac{1}{(n_1+n_2)^2}{\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
 			\end{align}
@@
 \end{theorem}
-In this section, we give the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}
+%For the rest of this section, we present the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}
 
-\subsection{Proof Overview}
-Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
-
+\paragraph{Proof Overview (cont'd).}
+We continue the proof overview of Theorem \ref{thm_main_RMT} and \ref{thm_main_RMT_app} from Section \ref{sec_diff}.
+%Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
 Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$.
@@
 
-\paragraph{Schur complement and self-consistent equations.}
-We briefly describe how to derive the matrix limit $\Gi(z)$.
-First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
-By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
-Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
-We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
-On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
-Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
-We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
-A complete proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{sec pf RMTlemma}-Appendix \ref{sec entry}. %Appendix \ref{appendix RMT}.
+%\paragraph{Schur complement and self-consistent equations.}
+%
+%First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
+%By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
+%Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
+%We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
+%On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
+%Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
+%We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
+%A complete proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{sec pf RMTlemma}-Appendix \ref{sec entry}. %Appendix \ref{appendix RMT}.
 
+\paragraph{How to derive the matrix limit?}
 We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
@@
 \begin{align*}
-	m_1^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p \lambda_i^2 G_{i,i}(z)+ \oo(1),\quad  m_2^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p G_{i,i}(z)  + \oo(1).
+	m_1^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p \lambda_i^2 G_{ii}(z)+ \oo(1),\quad  m_2^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p G_{ii}(z)  + \oo(1).
 \end{align*}

### 2020-10-18 arxiv/proof_examples.tex
section D wip

@@
 
-We follow a similar logic as in the proof of Theorem \ref{thm_many_tasks}.
-We first characterize the global minimizer of $f(A, B)$ in the random-effects model.
-Based on the characterization, we reduce the prediction loss of hard parameter sharing to the asymptotic limits provided in Theorem \ref{thm_main_RMT}.
-Then, we prove Corollary \ref{cor_MTL_loss} based on the bias and variance limits.
+We follow a similar logic to the proof of Theorem \ref{thm_many_tasks}.
+We first characterize the global minimizer of $f(A, B)$ in the random-effect model.
+Based on the characterization, we reduce the prediction loss of hard parameter sharing to the bias-variance asymptotic limits.
+Finally, we prove Corollary \ref{cor_MTL_loss} based on these limiting estimates.
 We set up several notations.
@@
 	where $B \in \real^{p}$ and $A = [A_1, A_2]\in \real^{2}$ because the width of $B$ is one.
-We assume that $A_1$ and $A_2$ are both nonzero.
-Otherwise, we add a tiny amount of perturbation $\delta$ to them and the result remains the same.
+Without loss of generality, we assume that $A_1$ and $A_2$ are both nonzero.
+Otherwise, the problem reduces to STL. % we add a tiny amount of perturbation $\delta$ to them and the result remains the same.
 Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we obtain that $\hat{B}$ satisfies the following
@@
 	\end{align}
-We denote $\hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
+We denote $\hat \Sigma(x)= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
 Applying $\hat B$ to equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers.
@@
 			& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta^{(1)}-x^2\beta^{(2)})+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} \right.
+		  & + \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta^{(1)}-x^2\beta^{(2)})+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} \right.
 \nonumber\\
-		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2.
-		\label{eq_mtl_A12}
+		  &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
 	\end{align}
-The conditional expectation of $g(x)$ over $\epsilon^{(1)}$ and $\epsilon^{(2)}$ is
-%\HZ{could you align the Eq so that they look better on page?}
-\begin{align}
-\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}}
-&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \nonumber\\
-&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  \nonumber\\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}} \nonumber\\
-&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
-&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
-& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
-\end{align}
-Using the following identity
-\begin{align*}
-(X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} & =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
-&= (X^{(2)})^\top X^{(2)} \hat \Sigma(x)^{-1}(X^{(1)})^\top X^{(1)},
-\end{align*}
-we can simplify that
-\begin{align*}
- & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \\
-=&(\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta^{(1)}-x\beta^{(2)})\\
-&+(\beta^{(1)}-x\beta^{(2)})^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\\
-%&=(\beta^{(1)}-x\beta^{(2)})^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\\
-=&(\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}).
-\end{align*}
-Using this identity, we can simplify equation \eqref{Eg(x)}  to
+We have that the conditional expectation of $g(x)$ over $\epsilon^{(1)}$ and $\epsilon^{(2)}$ is
 \begin{align*}
 		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}} \\
-		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  \\
-		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2 \right]\\
-&+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
+%		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  \\
+%		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2 \right]\\
+%&+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
 		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}) +\sigma^2(n_1+n_2-p).
 \end{align*}
-For the random-effects model, recall that the entries of $(\beta^{(1)}- x\beta^{(2)})\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 +(1+x^2) d^2]$.
-Hence, 
+The calculation is tedious but rather straightforward, so we leave the details to the reader.
+In the random-effect model, recall that the entries of $(\beta^{(1)}- x\beta^{(2)})\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 +(1+x^2) d^2]$.
+Hence, by further taking expectation over $\beta^{(1)}$ and $\beta^{(2)}$, we obtain
 \begin{align}
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta^{(1)},\beta^{(2)}}{g(x) \mid X_1, X_2} \nonumber\\
+	&\ex{g(x) \mid X_1, X_2} \nonumber\\
 %&=[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
 %&+ A^2[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+	=& ((x-1)^2\kappa^2 + (x^2+1)d^2){p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
 \end{align}
 
+%\HZ{could you align the Eq so that they look better on page?}
+%\begin{align}
+%\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}}
+%&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \nonumber\\
+%&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  \nonumber\\
+%& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}} \nonumber\\
+%&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
+%&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
+%& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
+%\end{align}
+%Using the following identity
+%\begin{align*}
+%(X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} & =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
+%&= (X^{(2)})^\top X^{(2)} \hat \Sigma(x)^{-1}(X^{(1)})^\top X^{(1)},
+%\end{align*}
+%we can simplify that
+%\begin{align*}
+% & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \\
+%=&(\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta^{(1)}-x\beta^{(2)})\\
+%&+(\beta^{(1)}-x\beta^{(2)})^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\\
+%&=(\beta^{(1)}-x\beta^{(2)})^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\\
+%=&(\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}).
+%\end{align*}
+%Using this identity, we can simplify equation \eqref{Eg(x)}  to
+
 \paragraph{Part $1$: characterizing the global minimum of $f(A, B)$.}
-Let $\hat{x}$ denote the minimizer of $g(x)$.
+Let $\hat{x}$ denote the global minimizer of $g(x)$.
 We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat x$ is close to 1.
-This gives us the global minimum of $f(A, B)$, combined with the local optimality condition for $\hat{B}$.
-
+This gives us the global minimum of $f(A, B)$, since $\hat{B}$ is given by $\hat{x}$ using local optimality conditions.
 First, we show that $g(x)$ and $\ex{g(x) \mid X^{(1)}, X^{(2)}}$ are close using standard concentration bounds.
 \begin{claim}\label{claim_largedev1}
- In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
-$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta^{(1)},\beta^{(2)}}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right)$$
-for any small constant $c>0$.
+ In the setting of Corollary \ref{cor_MTL_loss}, for any $x = O(1)$, we have that with high probability
+$$\left| g(x) - \ex{g(x) \mid X^{(1)}, X^{(2)} }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right).$$
 \end{claim}
 \begin{proof}
-By Fact \ref{fact_minv} (ii), we have that with high probability,
- \be\label{op_X12}
-\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
- \ee
- and
- \be\label{op_Sig1}
-\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
- \ee
-where we used that $3\le n_1/p\le \tau^{-1}$ and $3\le n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
-
- Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}:
+ There are two terms in $g(A)$ from equation \eqref{eq_mtl_A12}.
+ We will focus on dealing with the concentration error of the first term. The second term is similar to the first and we omit the details.
+ For the first term, we expand into several equations under various situations involving the random noise and the random-effect model.
  \begin{align}
@@
 \nonumber\\
-		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
+		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x), \label{expand_6}
  \end{align}
@@
 \end{align*}
-Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.
+Next, we estimate each term using Lemma \ref{largedeviation} for random variables with bounded moment up to any order.
+We first state several facts that will be commonly used in the proof.
+By Fact \ref{fact_minv} (ii), we have that w.h.p. the operator norm of $X^{(1)}$ and $X^{(2)}$ are both bounded by $O(\sqrt{n})$.
+Furthermore, the operator norm of $\hat\Sigma(x)^{-1}$ is bounded by $(x^2 + 1)^{-1} O(n_1 + n_2) = (x^2 + 1) O(p)$.
+ % \be\label{op_X12}
+%\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
+% \ee
+% and
+% \be\label{op_Sig1}
+%\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
+% \ee
+%where we used that $3\le n_1/p\le \tau^{-1}$ and $3\le n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
 
-For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $(\beta^{(1)}-x\beta^{(2)})\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]$, we obtain the following estimate with high probability for any small constant $c>0$:
+For $h_1(x)$, using Lemma \ref{largedeviation} and the fact that the entries of $(\beta^{(1)}-x\beta^{(2)})\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variance $b = p^{-1}((x-1)^2\kappa^2 + (x^2+1)d^2)$, we obtain the following estimate w.h.p.
 \begin{align}
 	&\left|h_1(x) - \exarg{\beta^{(1)},\beta^{(2)}}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
-&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
+\le& p^{c}\cdot p^{-1} b \cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
+	\le& p^{c}\cdot p^{-1} b \cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
+	\lesssim& p^{1/2+c}\cdot \frac{b}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
 \end{align}
- Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
-\begin{align*}
- \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
- & \lesssim \frac{p}{(x^2+1)^2}.
-\end{align*}
-Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variances $\sigma^2$, and the bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+In the third step we use the operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)^{-1}$. % as follows
+%\begin{align*}
+%	\left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
+%  & \lesssim \frac{p}{(x^2+1)^2}.
+%\end{align*}
+
+For $h_2(x)$ and $h_3(x)$, since the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variances $\sigma^2$, using Lemma \ref{largedeviation}, we obtain w.h.p.
 \be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
-For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
+For $h_4(x)$, using Lemma \ref{largedeviation}, we obtain w.h.p.:
 \begin{align}
 			&\left|h_4(x)\right| \nonumber\\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\le  p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2} \cdot \left\|  \id_{n_1\times n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2).\label{eq_hA4}
+	\le& p^{c}\cdot \sigma \cdot \sqrt{b / p}\left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
+	\le& p^{c}\cdot \sigma \sqrt{b / p} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+	\le&  p^{c}\cdot \sigma \sqrt{b} \cdot \left\|  x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top - \id_{n_1\times n_1} \right\| \cdot \left\|X^{(1)}\right\| \cdot \left\|\hat\Sigma(x)^{-1}\right\| \cdot \left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+	\lesssim& p^{1/2+c}\frac{\sigma \sqrt{b}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2).\label{eq_hA4}
 \end{align}
-Above, in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and equations \eqref{op_X12} and \eqref{op_Sig1}.
-In the last step we used AM-GM inequality.
-With the same argument, we can show that
-\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
-with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
-
-Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}.
-Hence the proof is complete.
+Above, in the fourth step we use the operator norm of $x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top - \id$ being at most one and the operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)^{-1}$.
+In the last step we use AM-GM inequality. Using the same argument, we can show that
+$\left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2)$ and $\left|h_6(x)\right| \le p^{1/2+c}\sigma^2$.
+Combining the concentration error bound for $h_1(x), h_2(x), \dots, h_6(x)$, we complete the proof.
+The second term of $g(A)$ can be dealt in similar ways and we omit the details.
 \end{proof}
 
-Next, we show that $\hat x$ is close to 1.
+Next, we show that the global minimizer $\hat x$ of $g(x)$ is close to 1.
 \begin{claim}\label{lem_hat_v}
 %Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
+	Let $c$ be a sufficiently small fixed constant.
 	In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability,
 %There exists a constant $C>0$ such that
-	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}
+	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}.
 	\ee
-	for any small constant $c>0$.
-	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
 \end{claim}
@@
 \begin{align*}
-h(x):= [(x-1)^2\kappa^2 + (x^2+1)d^2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right].
+	h(x)  =& [(x-1)^2\kappa^2 + (x^2+1)d^2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right] \\
+				=& [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
 \end{align*}
-Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
-\begin{align}
-p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
-&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
-&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
-\end{align}
-where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
-\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
-On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
-\begin{align}\label{eq_hA}
-h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
-\end{align}
-where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
-%and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
-Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1} and \eqref{eq_hA}, we obtain that with high probability,
-\begin{align}
-g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
-&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
-\end{align}
-under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
-This gives that
-%\be\label{rough A-1}
-$|\hat x-1|\le \delta$ for any small constant $\delta>0$.
-
-%Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
-To obtain the better bound \eqref{hatw_add1}, we study the function $h(x)$ more closely and find its minimizer, denoted by $x^\star$.
+Let $x^{\star}$ denote the global minimizer of $h(x)$.
+Our proof involves two steps.
+First, we will show that $\abs{x^{\star} - 1} \le d^2 / \kappa^2$.
+Second, we will use Claim \ref{claim_largedev1} to show that the global minimizer of $g(x)$ and $h(x)$ are close to each other.
 %Using Lemma \ref{largedeviation} again, we can simplify equation \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
@@
 %To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof.
-First it is easy to observe that $h(x)< h(-x)$ for $x> 0$.
+
+For the first step, it is easy to observe that $h(x)< h(-x)$ for any positive $x$.
+Hence the minimum of $h(x)$ is achieved when $x$ is positive.
 %$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
-Then we consider the case $x\ge 1$. We write
-\begin{align*}
-h(x):= [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
-\end{align*}
-Notice that
+Next, we consider the case where $x\ge 1$.
+Notice that the following function always increases when $x$ increases in the positive orthant:
 $$\tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]$$
-is an increasing functions in $x$. Hence taking derivative of $h(x)$ with respect to $x$, we obtain that
+By taking the derivative of $h(x)$, we obtain that for any $x > 1+d^2/\kappa^2$,
 \begin{align}\label{h'(A)1}
-h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - 2\frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,
+h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - 2\frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] > 0,
 \end{align}
-as long as $x \ge 1+d^2/\kappa^2$.
-%\begin{align}
-%	h(w) =&  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-%	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-%			& +  \frac{\rho_1}{\rho_2}\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ \sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }.
-\nonumber
-%\end{align}
-%Notice that
-%$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
-%are increasing functions in $w$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
-%\begin{align*}
-%h'(w) \ge & \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
-% &+ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-%		&- 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
-%\end{align*}
-%where the matrix $\cal A$ is defined as
-%\begin{align*}
-%\cal A :&= \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
-%\end{align*}
-%Using the estimate Fact equation \eqref{lem_minv}, we get that $\cal A$ is lower bounded as
-%\begin{align*}
-%\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
-%&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
-%\end{align*}
-%as long as
-%$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
-%Hence $h'(w)>0$ on $(w_1,\infty)$, %i.e. $h(w)$ is strictly increasing for $w>w_1$. This
-%which gives $\hat w\le w_1$.
-Next we consider the case $1-\delta\le x\le 1$. Notice that
+Finally, we consider the case where $x \le 1$. Notice that the following function always decreases when $x$ decreases from $1$:
 $$\tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
-is a decreasing functions in $x$. Hence taking derivative of $h(x)$, we obtain that
+Hence, by taking derivative of $h(x)$, we obtain that for any $x\le 1-d^2/\kappa^2$,
 \begin{align}\label{h'(A)2}
-	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,
+	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] < 0,
 \end{align}
-as long as $x\le 1-d^2/\kappa^2$. In sum, we see that the minimizer $x^\star$ must satisfy
-$$1-d^2/\kappa^2\le x^\star \le 1+d^2/\kappa^2.$$
+In summary, the global minimizer of $h(x)$ lies within $1-d^2/\kappa^2$ and $1+d^2/\kappa^2$.
 
@@
 
-Now we are ready to prove equation \eqref{hatw_add1}. First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+3d^2/(2\kappa^2) \le x\le 1+\delta$,
+For the second step, we first argue that $\hat{x}$ is $O(1)$. Hence we can apply Claim \ref{claim_largedev1} to bound the concentration error of $g(x)$.
+Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
+\begin{align}
+p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
+&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
+&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
+\end{align}
+where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
+\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
+On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
+\begin{align}\label{eq_hA}
+h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
+\end{align}
+where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
+and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
+\begin{align}
+g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
+&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
+\end{align}
+under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
+This gives that
+Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
+
+First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+3d^2/(2\kappa^2) \le x\le 1+\delta$,
 $$h'(x)\ge \frac{2(x-1)\kappa^2 - 2d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$

### 2020-10-18 arxiv/proof_same_cov.tex
section D wip

@@
 	 One can see that the expected optimization objective also admits a nice bias-variance decomposition.
-	Furthermore, its minimizer only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.
+	Furthermore, its minimum only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.
 
@@
 	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a small enough error.
-Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$.
-With this estimate, we can bound the difference
-		$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
-		Combined together, our proof is complete.
-%		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
-%		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
-%		Combined together, our proof is complete.
+		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a multiplicative error of order $n^{-1/4}$.
+		%Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$. With this estimate, we can bound the difference
+		%$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
+		%Combined together, our proof is complete.
+		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
+		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
+		Combined together, we obtain the difference if we replace $\hat{a}_i$ with $a^{\star}_i$ in Claim \ref{claim_pred_err}, and the proof is complete.
 	\end{proof}
@@
 		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
-		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \label{eq_gA_err2}
+		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \label{eq_gA_err2}
 %		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
@@
 	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
-	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$, and use $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})$ has rank at most $t$.
+	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$.
 	By the AM-GM inequality, equation \eqref{eq_gA_err2} is bounded by the right-hand side of \eqref{eq_gA_err}.
@@
 	\begin{align}
-		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left[ \cal E^\top \id_{n\times n}\cal E\right] - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F \nonumber\\
-		&= n^{1/2+c} \cdot \sigma^2 \le n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t. \label{eq_gA_err3}
+		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left[ \cal E^\top \id_{n\times n}\cal E\right] - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F
+		= n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err3}
 	\end{align}
@@
 		&\le \sqrt{r} \cdot n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F \nonumber \\
-		&\le n^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r}  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.\label{eq_gA_err4}
+		&\le \sqrt{r} \cdot n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err4} %  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
 	\end{align}
@@
 
-	Combining equations \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain equation \eqref{eq_gA_err}.
+	Combining the concentration error estimate for all three parts, we obtain equation \eqref{eq_gA_err}.
 
@@
 		&\le \sum_{j=1}^t \abs{\hat{a}_i(j)} \cdot n^{\e}\sigma \bignorm{X (X^{\top}X)^{-1} \Sigma b} \\
-		&\le \sqrt{t} \norm{\hat{a}_i} \cdot n^{\e} \sigma \bignormFro{X (X^{\top} X)^{-1} \Sigma b}.
+		&\le \sqrt{t} \norm{\hat{a}_i} \cdot n^{\e} \sigma \bignorm{X (X^{\top} X)^{-1} \Sigma b}.
 	\end{align*}

### 2020-10-18 arxiv/proof_examples.tex
section D wip

@@
 This gives us the global minimum of $f(A, B)$, since $\hat{B}$ is given by $\hat{x}$ using local optimality conditions.
-First, we show that $g(x)$ and $\ex{g(x) \mid X^{(1)}, X^{(2)}}$ are close using standard concentration bounds.
+First, we show that $g(x)$ and its expectation are close using standard concentration bounds.
 \begin{claim}\label{claim_largedev1}
- In the setting of Corollary \ref{cor_MTL_loss}, for any $x = O(1)$, we have that with high probability
+ In the setting of Corollary \ref{cor_MTL_loss}, for any $x$, we have that with high probability
 $$\left| g(x) - \ex{g(x) \mid X^{(1)}, X^{(2)} }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right).$$
@@
 By Fact \ref{fact_minv} (ii), we have that w.h.p. the operator norm of $X^{(1)}$ and $X^{(2)}$ are both bounded by $O(\sqrt{n})$.
-Furthermore, the operator norm of $\hat\Sigma(x)^{-1}$ is bounded by $(x^2 + 1)^{-1} O(n_1 + n_2) = (x^2 + 1) O(p)$.
+Furthermore, the operator norm of $\hat\Sigma(x)^{-1}$ is bounded by $(x^2 + 1)^{-1} O(n_1 + n_2) = (x^2 + 1)^{-1} O(p)$.
  % \be\label{op_X12}
@@
 
-For the second step, we first argue that $\hat{x}$ is $O(1)$. Hence we can apply Claim \ref{claim_largedev1} to bound the concentration error of $g(x)$.
-Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
-\begin{align}
-p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
-&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
-&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
-\end{align}
-where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
-\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
-On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
-\begin{align}\label{eq_hA}
-h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
-\end{align}
-where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
-and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
-\begin{align}
-g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
-&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
-\end{align}
-under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
-This gives that
-Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
+For the second step, using Claim \ref{claim_largedev1}, we have that $g(x)$ and $h(x)$ differ by at most $p^{1/2 + \e}(\sigma^2 + \kappa^2 + d^2)$.
+Therefore, our goal reduces to showing that if $\hat{x}$ deviates too far from $1 \pm d^2 / \kappa^2$, it is no longer a global minimum of $g(x)$.
+%we first argue that $\hat{x}$ is $O(1)$. Hence we can apply Claim \ref{claim_largedev1} to bound the concentration error of $g(x)$.
+%Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
+%\begin{align}
+%p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
+%&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
+%&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
+%\end{align}
+%where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
+%\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
+%On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
+%\begin{align}\label{eq_hA}
+%h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
+%\end{align}
+%where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
+%and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
+%\begin{align}
+%g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
+%&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
+%\end{align}
+%under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
+%This gives that
+%Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
+We prove by contradiction.
+First, suppose that $\hat{x} \ge 1 + 2d^2 /\kappa^2 + p^{-1/2 + \e}$.
+For any $x \ge 1+3d^2/(2\kappa^2)$, we can lower bound the derivative of $h(x)$ using equation \eqref{h'(A)1} as follows
+	\[ h'(x) \ge \frac{2(x-1)\kappa^2 - 2d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]
+	\gtrsim p\kappa^2\cdot \frac{x-1}{x (1 + x^2)}. \]
+Therefore, the difference between $h(x)$ and $h(1)$ is at least the following
+\begin{align*}
+		h(x)-h(1) \ge h(x) - h\left(1+\frac{3d^2}{2\kappa^2}\right)
+	\ge \int_{1+\frac{3d^2}{2\kappa^2}}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot \int_{1 + \frac{3d^2}{2\kappa^2}}^x \frac{x-1}{x(1 + x^2)} \dd x.
+\end{align*}
+When $\hat{x}$ is sufficiently far from $1$ (e.g.
+$2d^2 / \kappa^2 + p^{-1/4+\e}$), one can verify that $h(x) - h(1)$ is at least $\OO(p\frac{d^4}{\kappa^2} + p^{1/2+2c} \kappa^2) > \OO(p^{1/2 + c} (\sigma^2 + \kappa^2 + d^2))$, under the condition that $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$.
+On the other hand, by triangle inequality and Claim \ref{claim_largedev1} we have that
+\begin{align*}
+	h(\hat{x}) - h(1) = g(\hat{x}) - g(1) + (h(\hat{x}) - g(\hat{x})) + (g(1) - h(1))
+	\le \OO\left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right).
+\end{align*}
+Hence, we have arrived at a contradition.
 
-First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+3d^2/(2\kappa^2) \le x\le 1+\delta$,
-$$h'(x)\ge \frac{2(x-1)\kappa^2 - 2d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
-Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+c}\le x\le 1+\delta$,
-\begin{align*}
-h(x)-h(1)\ge h(x)-h\left(1+\frac{3d^2}{2\kappa^2}\right) \ge \int_{1+\frac{3d^2}{2\kappa^2}}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot |x-1|^2  \gtrsim p\frac{d^4}{\kappa^2} + p^{1/2+2c} \kappa^2 .
-\end{align*}
-On the other hand, by Claim \ref{claim_largedev1} we have that
-$$ g(x)=h(x)+\sigma^2 (n_1+n_2-p)+\OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right)$$
-with high probability. Combining the above two estimates, we obtain that under the conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$,
-$$g(x)-g(1) = h(x)-h(1) + \OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right) >0$$
-with high probability, i.e. $x$ cannot be the minimizer of $g$.
 %Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have
 %$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$ where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
-Second, using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le x \le 1-3d^2/(2\kappa^2)$,
-$$- h'(x)\ge  [2(1-x)\kappa^2 - 2xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
-Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-1/4+c}\le x\le 1-\delta$, then
-$$ h(x)-h(1) \gtrsim p\frac{d^4}{\kappa^2} +p^{1/2+2c} \kappa^2, $$
+Second, suppose that $\hat{x} \le 1 - 2d^2/ \kappa^2 - p^{-1/2 + \e}$.
+Using equation \eqref{h'(A)2}, we obtain that for any $x \le 1 - 3d^2/(2\kappa^2)$,
+	\[ -h'(x)\ge  [2(1-x)\kappa^2 - 2xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\kappa^2 \cdot \frac{(1 - x)x^2}{1 + x^2}.
+\]
+Using a similar argument to the first case, we get that the difference between $h(x)$ and $h(1)$ is at least the integral of the abvoe derivative.
 %under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?},
-which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ of $g$ must satisfy equation \eqref{hatw_add1}.
+This implies that $\hat{x}$ cannot be too far from one.
+Hence we have completed the proof.
 %Next we prove the following estimate on the optimizer $\hat x$: with high probability,
@@
 Recall that the hard parameter sharing estimator $\hat{\beta}_2^{\MTL}$ is equal to $\hat{B} \hat{A}_2$.
-The predication loss of hard parameter sharing is as follows
+Using the local optimility condition for $\hat{B}$, we obtain the predication loss of HPS as follows
 \begin{align}
@@
 \end{align}
-Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows.
+Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we simplify $L(\hat{\beta}_2^{\MTL})$ as follows.
 
@@
 Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. equation \eqref{def hatsig}).
-In the setting of Proposition \ref{cor_MTL_loss}, we have the following estimate with high probability for any small constant $c>0$:
+In the setting of Claim \ref{cor_MTL_loss}, we have the following estimate w.h.p.
 \begin{align*}
-&\left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat \Sigma^{-1}  }\right)\right| \nonumber\\
+&\left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{{\hat \Sigma^{-1}  }}\right| \nonumber\\
 \lesssim&  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2).
@@
 \begin{proof}
-Our proof is divided into two steps.
-First, with the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows.
-With high probability, we have that for any small constant $c>0$,
+Our proof is divided into two steps. First, using Lemma \ref{largedeviation}, we show that
 \be\label{claim_largedev2} \left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),
 \ee
-where the function $\cal L(\hat x)$ is defined as
+where $\cal L(\hat x)$ is defined as
 \begin{align*}
-	\cal L(\hat x)	:=  &\hat x^2\left[(\hat x-1)^2 \kappa^2 +  (\hat x^2+1)d^2 \right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} } \\
-	& +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
+	\resizebox{0.97\hsize}{!}{%
+	$\cal L(\hat x)	:=  \hat x^2\left[(\hat x-1)^2 \kappa^2 +  (\hat x^2+1)d^2 \right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} }
+	 +\sigma^2\cdot \bigtr{\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}}.$
+	}%
 \end{align*}
@@
 %We are now ready to finish the proof of Claim \ref{claim_reduction}.
-We defer the proof of equation \eqref{claim_largedev2} until the end.
-Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_{p\times p}$.
-More precisely, we claim that with high probability
+Next, we further simplify $\cal L(\hat x)$ since $\hat{x}$ is close to one and $\Sigma^{(1)},\Sigma^{(2)}$ are both isotropic
 \begin{align}
-&\left|\cal L(\hat x)- \frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left(\hat \Sigma^{-1}  \right)\right| \nonumber\\
+	&\left|\cal L(\hat x)- \frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\hat \Sigma^{-1}}\right| \nonumber\\
 \lesssim & \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
 \end{align}
-Combining equations \eqref{claim_largedev2} and \eqref{simple12}, we conclude Claim \ref{claim_reduction}.
+Combining equation \eqref{claim_largedev2} and \eqref{simple12}, we obtain the desired claim.
+We prove these two equations one by one as follows.
 
-Now we prove equation \eqref{simple12}. Using Claim \ref{lem_hat_v} and equations \eqref{op_X12} and \eqref{op_Sig1}, we obtain that with high probability,
-\begin{align}
- \|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1|\|\hat\Sigma^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right).\label{est111}
-\end{align}
-Using similar arguments, we get that with high probability,
-\begin{align}\label{est222}
-&\left\|\left(\hat\Sigma^{-2}-\hat\Sigma(\hat x)^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+c} .
-\end{align}
-Moreover, using equations \eqref{op_X12} and \eqref{op_Sig1}, we can bound that with high probability,
-%$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
-%which further implies that with high probability,
-\begin{align}
-& \bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}  \le p \bignorm{\hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}\lesssim p.\label{est333}
-\end{align}
+First, we prove equation \eqref{simple12}.
 We can bound the left hand side of equation \eqref{simple12} as
@@
 \end{align*}
-Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple12}.
+We deal with the trace terms in the above equation one by one.
+Using Claim \ref{lem_hat_v} and operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)$, we have that w.h.p.
+\begin{align}
+	\|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1| \cdot \|\hat\Sigma^{-1}\| \cdot \| (X^{(1)})^\top X^{(1)}\| \cdot \|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right).\label{est111}
+\end{align}
+Using similar arguments, we get that w.h.p.
+\begin{align}\label{est222}
+&\left\|\left(\hat\Sigma^{-2}-\hat\Sigma(\hat x)^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+c},
+\end{align}
+and
+\begin{align}
+& \bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}  \le p \bignorm{\hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2}\lesssim p.\label{est333}
+\end{align}
+Applying the above results \eqref{est111}, \eqref{est222}, and \eqref{est333} to the bound of $\cL(\hat{x})$ above, we have shown that equation \eqref{simple12} holds.
 
-Finally we give the proof of the estimate \eqref{claim_largedev2}.
-The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$ and $\beta^{(2)}$.
-In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
-Here we only give a proof sketch and omit the details.
-Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d.
-Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
-Moreover, we denote the task-specific components by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2 $.
-Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
+Second, we prove equation \eqref{claim_largedev2}.
+The proof is very similar to Claim \ref{claim_largedev1}.
+The key difference is that $\hat x$ correlates with $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$, and $\beta^{(2)}$.
+Nevertheless, Lemma \ref{largedeviation} still applies for any arbitrary $\hat x$.
+We describe a proof sketch and omit the details.
+Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d. Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
+The task-specific components, denoted by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, consist of i.i.d. Gaussian random variables with mean zero and variance $p^{-1} d^2$.
+We write $L(\hat{\beta}_2^{\MTL}) $ from equation \eqref{Lbeta_HPS} as:
 \begin{align}
@@
 \end{align}
-As in equation \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in equations \eqref{eq_hA1}-\eqref{eq_hA56}.
-For example, for the main term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using
-Lemma \ref{largedeviation} and equations \eqref{op_X12} and \eqref{op_Sig1}, we can obtain the following estimate with high probability:
+Similar to the analysis of $g(x)$, we expand $L(\hat{\beta}_2^{\MTL})$ into the sum of 15 terms, and bound the concentration error of each term similar to $h_1(x), \dots, h_6(x)$.
+For example, for the leading term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using
+Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
 \begin{align*}
@@
 \end{align*} 
-For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and equations \eqref{op_X12} and \eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
 \begin{align*}
@@
 \end{align*}
-The rest of the terms in the expansion of \eqref{expand_15} can be bounded in the same way, and we omit the details.
+The rest of the terms in the expansion of $L(\hat{\beta}_2^{\MTL})$ can be dealt with similarly, and we omit the details.
  \end{proof}
 
-\paragraph{Part $3$: applying the bias and variance limits.}
+\paragraph{Part $3$: applying the bias-variance limits.}
 Finally, we are ready to complete the proof of Corollary \ref{cor_MTL_loss}.
-We derive the variance term $\sigma^2  \tr[\hat\Sigma^{-1}]$ and the bias term $\frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
+We derive the variance term $\sigma^2  \tr[\hat\Sigma^{-1}]$ and the bias term $\frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using our random matrix theory results.
 
 \begin{proof}[Proof of Corollary \ref{cor_MTL_loss}]
-Using equation \eqref{lem_cov_shift_eq}, we obtain that
+For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
 \be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
@@
 
-On the other hand, we have that with high probability,
+For the bias term, since the spectrum of $(X^{(1)})^{\top} X^{(1)}$ is tightly concentrated by Fact \ref{fact_minv}, we have that
 \begin{align}
- \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\hat \Sigma^{-2}\right)_{ii}  &\le {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
- &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} .\nonumber
+ \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p} \bigtr{\hat \Sigma^{-2}}  &\le {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
+ &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p} \bigtr{\hat\Sigma^{-2}}.\nonumber
 \end{align}
-To obtain this inequality, we used  
-$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
-by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
-Using equation \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$ and $w$ being the $i$-th coordinate vector, we can calculate that 
-\begin{align}\label{eq_bias112}
- \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right]
-\end{align}
-with high probability. Solving equation \eqref{eq_a34extra} with $a_1, a_2$ in \eqref{simplesovlea12} and $\lambda_i\equiv 1$, $1\le i\le p$, we can obtain that
+%To obtain this inequality, we used
+%$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
+%by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
+Using the bias limit \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$, and $w = e_i$ (the $i$-th coordinate vector), we have w.h.p.
+\begin{align*}%\label{eq_bias112}
+ \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right].
+\end{align*}
+We solve the self-consistent equations \eqref{eq_a34extra} given $a_1, a_2$, and obtain
 	\begin{align*}
-		% a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad & a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
 		a_3 = \frac{p\cdot n_1}{(n_1 +n_2)(n_1 +n_2 - p)}, \quad
@@
 	\end{align*}
-Inserting them into equation \eqref{eq_bias112}, we obtain that 
+Applying them to the above equation, we obtain that w.h.p.
 \begin{align*}%\label{eq_bias113}
- \left(\hat\Sigma^{-2}\right)_{ii} =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right]
+ \left(\hat\Sigma^{-2}\right)_{ii} =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right].
 \end{align*}
-with high probability. In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that 
+In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that
 \begin{align*}%\label{eq_bias113}

### 2020-10-19 arxiv/proof_examples.tex
finish section D

@@
 %by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
-Using the bias limit \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$, and $w = e_i$ (the $i$-th coordinate vector), we have w.h.p.
+Using the bias limit \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$, and $w = e_i$ (the $i$-th coordinate vector), we have w.h.p. (via a union bound)
 \begin{align*}%\label{eq_bias112}
- \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right].
+ e_i^{\top}\hat\Sigma^{-2} e_i = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
 \end{align*}
@@
 \end{align*}
-Applying them to the above equation, we obtain that w.h.p.
+Applying them to the above equation, we obtain
 \begin{align*}%\label{eq_bias113}
- \left(\hat\Sigma^{-2}\right)_{ii} =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right].
+ e_i^{\top}\hat\Sigma^{-2}e_i =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right].
 \end{align*}
-In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that
-\begin{align*}%\label{eq_bias113}
-\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
-\end{align*}
-on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that 
-\begin{align*} 
-\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{1-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
-\end{align*}
-with high probability, which by Definition \ref{stoch_domination} gives that
-\begin{align}\label{eq_bias113}
-\left| p^{-1}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\le \frac{p^{-c_\varphi}}{(n_1+n_2)^2}
-\end{align}
-with high probability. Inserting equation \eqref{eq_bias113} into equation \eqref{eq_bias111}, we get that
-\begin{align*}
-		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\nonumber \\
-		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3} \nonumber\\
-		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}
-\end{align*}
-with high probability.
-
-Combining equation \eqref{eq_var112} and the above with Claim \ref{claim_reduction}, we get that
+%In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that
+%\begin{align*}%\label{eq_bias113}
+%\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
+%\end{align*}
+%on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that
+%\begin{align*}
+%\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{1-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
+%\end{align*}
+%with high probability, which by Definition \ref{stoch_domination} gives that
+%\begin{align}\label{eq_bias113}
+%\left| p^{-1}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\le \frac{p^{-c_\varphi}}{(n_1+n_2)^2}
+%\end{align}
+%with high probability.
+Applying the above equation to equation \eqref{eq_bias111}, we get the desired result for the bias term.
+%\begin{align*}
+%		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\nonumber \\
+%		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3} \nonumber\\
+%		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}.
+%\end{align*}
+Combining the bias and variance estimates, we get that
 \begin{align*}
@@
 \end{align*}
-Then using the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-\e}{\kappa^2}$, we conclude the proof.
+Since $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-\e}{\kappa^2}$ by our assumption, we obtain the desired result.
+The proof is complete.
 \end{proof}

### 2020-10-19 arxiv/proof_gaussian_case.tex
finish section D

@@
 \begin{theorem}\label{thm_main_RMT_app}
-	In the setting of Theorem \ref{thm_main_RMT}, the bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed unit vector $w\in\real^p$:
+	Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$.
+	In the setting of Theorem \ref{thm_main_RMT}, the bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any unit vector $w\in S$:
 			\begin{align}\label{lem_cov_derv_eq}

### 2020-10-19 arxiv/proof_gaussian_case.tex
appendix

@@
 Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
-The following notion of stochastic domination, which was first introduced in \cite{Average_fluc}, is commonly used in the study of random matrices.
+The following notion of stochastic domination, which was first introduced in \citet{Average_fluc}, is commonly used in the study of random matrices.
 
@@
 
-\begin{fact}[Lemma 3.2 in \cite{isotropic}]\label{lem_stodomin}
+\begin{fact}[Lemma 3.2 in \citet{isotropic}]\label{lem_stodomin}
 Let $\xi$ and $\zeta$ be two families of nonnegative random variables depending on some parameters $u\in \cal U$ or $v\in \cal V$.

### 2020-10-20 arxiv/proof_gaussian_case.tex
section E

@@
 In other words, $Z$ has bounded support $Q=n^{\frac{2}{\varphi}}$ with high probability.
-%This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}. %This fact will be used in the proof of Corollary \ref{main_cor} below.
-%The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
-%\begin{assumption}%\label{assm_big1}
-%As in Section \todo{add reference}, we consider random matrices $X^{(1)}=Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}=Z^{(2)}\Sigma_2^{1/2}$, where $Z^{(1)}$ and $Z^{(2)}$ are independent $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries of zero mean and unit variance.
-Recall that $\rho_1= n_1/p$ and $\rho_2=n_2/p$.
-We assume that for a small constant $0<\tau<1$,
-%\HZ{We have defined $\rho_1,\rho_2$ already in sec 2. Consider using ``Recall that $\rho_1 =, \rho_2 =$.''}
-%\be\label{assm2}
-%0\le \rho_1 \le \tau^{-1}, \quad 1+\tau \le \rho_{2} \le \tau^{-1}.
-%\ee
-%Recall that the singular value decomposition of $M = \Sig_1^{1/2} \Sig_2^{-1/2}$ is $U \Lambda V^{\top}$. We assume that
-%\begin{equation}\label{assm32}
-%\tau \le \lambda_p \le \lambda_1 \le \tau^{-1} .%, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
+
+The following resolvent identities are important tools for our proof.
+Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{diagW}.
+\begin{lemma}\label{lemm_resolvent}
+We have the following resolvent identities.
+\begin{itemize}
+	\item[(i)] For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
+		\begin{equation}
+			\frac{1}{G_{ii}} =  - z - \left( {\AF G^{\left( i \right)} \AF^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {\AF^\top  G^{\left( \mu  \right)} \AF} \right)_{\mu \mu }.\label{resolvent2}
+		\end{equation}
+	\item[(ii)] For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
+		\begin{equation}
+			G_{ia}   = -G_{ii}  \left( \AF G^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( \AF^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
+		\end{equation}
+%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
+%\begin{equation}\label{resolvent6}
+%\begin{split}
+% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}.
+%\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) .
+%, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
+%\end{split}
 %\end{equation}
-%Finally, recalling the notations in equation \eqref{labelZ}, we assume that $Z^{(1)}$ and $Z^{(2)}$ satisfy
+ \item[(iii)] For $a \in \mathcal I$ and $a_1,a_2 \in \mathcal I \setminus \{a\}$, we have
+		\begin{equation}
+			G_{a_1a_2}^{\left( a \right)}  = G_{a_1a_2}  - \frac{G_{a_1a} G_{aa_2}}{G_{aa}}.
+%, \quad  \frac{1}{{G_{{b}{b}} }} = \frac{1}{{G_{{b}{b}}^{({a})} }} - \frac{{G_{{b}{a}} G_{{a}{b}} }}{{G_{{b}{b}} G_{{b}{b}}^{({a})} G_{{a}{a}} }}.
+			\label{resolvent8}
+		\end{equation}
+%and
 %\begin{equation}
-%n^{-1/2}\max_{i\in \cal I_0,\mu \in \cal I_1}\vert Z^{(1)}_{\mu i}\vert \prec q,\quad n^{-1/2}\max_{i\in \cal I_0,\nu \in \cal I_2}\vert Z^{(2)}_{\nu i}\vert \prec q, \label{eq_support}
+%\frac{1}{{G_{ss} }} = \frac{1}{{G_{ss}^{(r)} }} - \frac{{G_{sr} G_{rs} }}{{G_{ss} G_{ss}^{(r)} G_{rr} }}.
+%\label{resolvent9}
 %\end{equation}
-%for some deterministic parameter $q$ satisfying $ n^{-{1}/{2}} \leq q \leq n^{- \tau} $ for a small constant $\tau>0$.
-%Here we recall the notations in \eqref{labelZ}.
- %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-%\end{assumption}
-%\HZ{This is restating what's stated above again.
-Remove redundant statements (unless there's something critical missing in Sec 2).} [\cor FY: The setting in sec 1 is too vague for the purpose of this section in the sense that it is hard to find the exact properties we need.
-In this section, I want to state rigorous statements with a reference to an exact assumption.
-Moreover, the above assumption contains more.\nc]
+% \item[(iv)]
+%All of the above identities hold for $G^{(\mathbb T)}$ instead of $G$ for $\mathbb T \subset \mathcal I$, and in the case where $A$ and $B$ are not diagonal.
+\end{itemize}
+\end{lemma}
+The above result can be proved using Schur's complement formula, cf. \citet[Lemma 4.4]{Anisotropic}.
 
-%\begin{remark}
-%The lower bound $\rho_2\ge 1+\tau$ in equation \eqref{assm2} is to ensure that the sample covariance matrix $(X^{(2)})^\top X^{(2)}$ is non-singular with overwhelming probability.
-Moreover, we have allowed that $\rho_1=0$, because we want to state a general result that also covers the special case with no source task.
-%\end{remark}
-
-%\begin{definition}\label{defn_support}
-%We say a (rescaled) random matrix $\cal M$ satisfies the {\it{bounded support condition}} with $q$, if
-%\begin{equation}
-%\max_{i,j}\vert \cal M_{ij}\vert \prec q. \label{eq_support}
-%\end{equation}
-%%Here $q\equiv q(n)$ is a deterministic parameter and usually satisfies $ n^{-{1}/{2}} \leq q \leq n^{- \phi} $ for some (small) constant $\phi>0$.
-%Whenever (\ref{eq_support}) holds, we say that $M$ has support $q$.
-%%Moreover, if the entries of $X$ satisfy (\ref{size_condition}), then $X$ trivially satisfies the bounded support condition with $q=N^{-\phi}$.
-%\end{definition}
-%\begin{example}
-%\todo{Talk about the Gaussian case and Bernoulli case.}
-
-%\end{example}
-
-%Recall that $n:=n_1+n_2$, which is the total number of data in the two tasks.
-%Before giving the main proof, we first introduce some notations and tools.
-%Following the notations in \cite{EKYY,EKYY1}, we will use the following definition to characterize events of overwhelming probability.
-%
-%\begin{definition}[overwhelming probability event] \label{high_prob}
-%Define
-%\begin{equation}\label{def_phi}
-%\varphi:=(\log N)^{\log \log N}.
-%\end{equation}
-%We say that an $N$-dependent event $\Omega$ holds with {\it{$\xi$-overwhelming probability}} if there exist constant $c,C>0$ independent of $N$, such that
-%\begin{equation}
-%\mathbb{P}(\Omega) \geq 1-N^{C} \exp(- c\varphi^{\xi}),  \label{D25}
-%\end{equation}
-%for all sufficiently large $N$.
-For simplicity, for the case $\xi=1$, we just say {\it{overwhelming probability}}.
-Note that if (\ref{D25}) holds, then $\mathbb P(\Omega) \ge 1 - \exp(-c'\varphi^{\xi})$ for any constant $0\le c' <c$.
-%\end{definition}
-%\begin{remark}
-%For any $c, C>0$, there exists a $0< c^{\prime}<c$, such that $N^{C} \exp(-c \varphi^{\xi}) \leq \exp(-c^{\prime} \varphi^{\xi})$. Hence, if
-%\begin{equation}
-%\mathbb{P}(\Omega) \geq 1- \exp(-c \varphi^{\xi})
-%\end{equation}
-%$\Omega$ is also a $\xi$-overwhelming probability event.
-%\end{remark}
+The following lemma gives sharp concentration bounds for linear and quadratic forms of bounded random variables.
+We recall that the stochastic domination ``$\prec$" has been defined in Definition \ref{stoch_domination}.
+%Besides the proof of Lemma \ref{prop_entry}, we also use it in several other places of this paper, including the proofs in Section \ref{sec_proof_general} and Section \ref{app_iso_cov}.
+%It constitutes the main difference between our proof and the one in \cite{KY2}, where the authors used a large deviation bound for random variables with arbitrarily high moments.
+\begin{lemma}[Lemma 3.8 of \cite{EKYY1} and Theorem B.1 of \cite{Delocal}]\label{largedeviation}
+Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers.
+Suppose the entries $x_i$ and $y_j$ have variance at most $1$, and satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $Q$.
+%with $q\le n^{-\phi}$ for a small constant $\phi>0$.
+Then we have the following results:
+%for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
+\begin{align}
+\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec Q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec Q^2 B_d  + Q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
+\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec Q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec Qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20}
+\end{align}
+where we denote $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have the following stronger results:
+\begin{align}
+\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i, j} |B_{ij}|^2\Big)^{{1}/{2}}, \label{eq largedev1} \\
+ \Big\vert  \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec  \Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert  \sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}}.\label{eq largedev2}
+\end{align}
+\end{lemma}

### 2020-10-20 arxiv/proof_same_cov.tex
section E

@@
 	\end{align}
-	Here in the third step, we apply equation \eqref{vcalAE3} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and use that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ has rank $r$.
+	Here in the third step, we apply equation \eqref{vcalA2} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and use that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ has rank $r$.
 In the fourth step, we use $\|U_X U_X^\top\|_F=\sqrt{p}$ because $U_X$ has rank $p$.

### 2020-10-20 arxiv/tools.tex
finish Section D
section E

@@
-\section{Tools}\label{app_tool}
+\section{Random Matrices with Bounded Moments}\label{app_tool}
 
-\subsection{Algebraic Inequalities}
-
-\begin{fact}\label{fact_proof_gA}
-	The minimum singular value of a matrix $X^{\top}YX$ is at least the minimum singular value of $Y$ times the minimum singular value of $X^{\top}X$.
-\end{fact}
-
-The following simple resolvent identities are important tools for our proof.
-Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{diagW}.
-\begin{lemma}\label{lemm_resolvent}
-We have the following resolvent identities.
-\begin{itemize}
-\item[(i)]
-For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
-\begin{equation}
-\frac{1}{G_{ii}} =  - z - \left( {\AF G^{\left( i \right)} \AF^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {\AF^\top  G^{\left( \mu  \right)} \AF} \right)_{\mu \mu }.\label{resolvent2}
-\end{equation}
-
- \item[(ii)]
- For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
-\begin{equation}
-G_{ia}   = -G_{ii}  \left( \AF G^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( \AF^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
-\end{equation}
-%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
-%\begin{equation}\label{resolvent6}
-%\begin{split}
-% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}.
-%\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) .
-%, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
-%\end{split}
-%\end{equation}
-
- \item[(iii)]
- For $a \in \mathcal I$ and $a_1,a_2 \in \mathcal I \setminus \{a\}$, we have
-\begin{equation}
-G_{a_1a_2}^{\left( a \right)}  = G_{a_1a_2}  - \frac{G_{a_1a} G_{aa_2}}{G_{aa}} .
-%, \quad  \frac{1}{{G_{{b}{b}} }} = \frac{1}{{G_{{b}{b}}^{({a})} }} - \frac{{G_{{b}{a}} G_{{a}{b}} }}{{G_{{b}{b}} G_{{b}{b}}^{({a})} G_{{a}{a}} }}.
-\label{resolvent8}
-\end{equation}
-%and
-%\begin{equation}
-%\frac{1}{{G_{ss} }} = \frac{1}{{G_{ss}^{(r)} }} - \frac{{G_{sr} G_{rs} }}{{G_{ss} G_{ss}^{(r)} G_{rr} }}.
-%\label{resolvent9}
-%\end{equation}
-% \item[(iv)]
-%All of the above identities hold for $G^{(\mathbb T)}$ instead of $G$ for $\mathbb T \subset \mathcal I$, and in the case where $A$ and $B$ are not diagonal.
-\end{itemize}
-\end{lemma}
-\begin{proof}
-All these identities can be proved directly using Schur's complement formula. The reader can also refer to, for example, \cite[Lemma 4.4]{Anisotropic}.
-\end{proof}
-
-\subsection{Random Variables with Bounded Moments}
+We state several concentration results for dealing with random matrices with bounded moments.
+Recall from Section \ref{sec_same} that we consider random matrices $Z \in \real^{n\times p}$ whose entries are i.i.d. with zero mean, unit variance, and bounded $\varphi$-th moment.
+The following facts are well-known.
 
 \begin{fact}\label{fact_minv}
-	In the setting of Theorem \ref{thm_many_tasks}, with overwhelming probability over the randomness of $X$, we have the following:
+	Suppose Assumption \ref{assume_rm} holds. With probability $1- 1 / \poly(n)$ over the randomness of $Z$, we have:
 	\begin{enumerate}
-		\item When $n / p$ converges to a fixed $\rho > 1$, the sample covariance matrix ${X^{\top}X} $ is of full rank.
+		\item When $n / p$ converges to a fixed $\rho > 1$, the sample covariance matrix ${X^{\top}X} / n$ has full rank $p$.
 		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf.
@@
 
-The following lemma gives (almost) sharp concentration bounds for linear and quadratic forms of bounded supported random variables.
-Here we recall that the stochastic domination ``$\prec$" was defined in Definition \ref{stoch_domination}.
-%Besides the proof of Lemma \ref{prop_entry}, we also use it in several other places of this paper, including the proofs in Section \ref{sec_proof_general} and Section \ref{app_iso_cov}.
-%It constitutes the main difference between our proof and the one in \cite{KY2}, where the authors used a large deviation bound for random variables with arbitrarily high moments.
-
-\begin{lemma}[Lemma 3.8 of \cite{EKYY1} and Theorem B.1 of \cite{Delocal}]\label{largedeviation}
-Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers.
-Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $Q$.
-%with $q\le n^{-\phi}$ for a small constant $\phi>0$.
-Then we have the following bounds:
-%for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
-\begin{align}
-\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec Q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec Q^2 B_d  + Q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
-\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec Q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec Qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20}
-\end{align}
-where we denote $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have stronger bounds
-\begin{align}
-\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i, j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
- \Big\vert  \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec  \Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert  \sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
-\end{align}
-%\begin{align}
-%\Big\vert \frac1{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
-% \Big\vert  \frac1n \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec \frac1{n}\Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
-%\end{align}
-\end{lemma}
-
-As a corollary, we can obtain the following concentration estimates for random variables with bounded $\varphi$-th moment.
+Next, we state a concentration result for $Z$.
 
 \begin{corollary} \label{cor_largedeviation}
-Let $Z\in \R^{n\times p}$ be a random matrix in the setting of Section \ref{sec_same}. Then for any deterministic vector $v\in \R^p$, we have that
-\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2\ee
-with high probability.
+For any deterministic vector $v\in \R^p$, we have that w.h.p.
+\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2.\ee
 \end{corollary}
 \begin{proof}
-We introduce the truncated matrices $\wt Z$ with entries
-$ \wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le Q \right)\cdot Z_{ij} $
-for $Q= n^{ \frac{2}{\varphi}}\log n$. By equation \eqref{Ptrunc}, we have that
+	Let $Q= n^{ \frac{2}{\varphi}}\log n$.
+	We introduce a truncated matrix $\wt Z$ with entries $\wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le Q \right)\cdot Z_{ij}$
+. By equation \eqref{Ptrunc}, we have that
 \begin{equation}\label{XneX222}
@@
 \end{equation}
-Furthermore, by equation \eqref{meanshif} we have that
+Furthermore, by equation \eqref{meanshif}, we have that
 \be\label{meanshif222}
@@
 %\ee
-Then we can centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$ 
+We centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$
 It suffices to show that 
 \be\label{show_whZ}
- \left|\|\wh Zv\|^2- n\|v\|^2\right|\prec n^{1/2} Q\|v\|^2.
+ \left|\|\wh Zv\|^2- n\|v\|^2\right| \le n^{1/2 + \e} Q\|v\|^2.
 \ee 
-In fact, provided that \eqref{show_whZ} holds, using \eqref{meanshif222} it is easy to get that 
-$$ \left|\|\wt Zv\|^2- n\|v\|^2\right|\prec n^{1/2} Q\|v\|^2,$$
+This is because provided with equation \eqref{show_whZ}, using \eqref{meanshif222} we can get that
+$$ \left|\|\wt Zv\|^2- n\|v\|^2\right| \le n^{1/2 + \e} Q\|v\|^2,$$
 which implies \eqref{Zv_cor} for any fixed value $c_{\varphi}$ within $(0, \frac{\varphi - 4}{2\varphi})$.
@@
 
-Next we can obtain the following concentration estimates for random noise in the setting of Section \ref{sec_same}.
+Next, we provide several concentration results for $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$, which consists of i.i.d.
+random variables with mean zero, variance $\sigma^2$ and bounded moments up to any order.
 
 \begin{corollary}\label{cor_calE}
-Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d.
-random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order.
-Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B$, we have that with high probability,
-\be\label{vcalE} |v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \ee
-and
-\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F ,\ee
-for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
-\be\label{vcalAE3}
-\|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \cdot  \sigma^2\|B\|_F ,
+Let $\e>0$ be a sufficiently small fixed constant.
+For any deterministic vector $v\in \R^n$, we have that w.h.p.
+\be\label{vcalE}
+	|v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \text{ and } \|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|.
 \ee
- with high probability for any small constant $c>0$.
+For any deterministic matrix $B \in \real^{n\times n}$, we have that w.h.p.
+\begin{align}\label{vcalA2}
+	\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F, \text{ and }
+	\left\| \cal E^\top B \cal E - \sigma^2 \tr[B]\cdot \id_{t\times t}\right\|_F \le n^{c} \cdot  \sigma^2\|B\|_F.
+\end{align}
+%\be\label{vcalAE3}
+%,
+%\ee
 \end{corollary}
 \begin{proof}
-Note that $\epsilon^{(i)}_j/\sigma$, $1\le i \le t,1\le j \le n$, are i.i.d.
-random variable of mean zero, variable one and bounded moments up to any order.
-Then using the first estimate in equation \eqref{eq largedev1}, we can obtain that $|v^\top \epsilon^{(i)}| = \Big|\sum_{j=1}^n v_j \epsilon^{(i)}_j \Big| \prec \sigma \|v\|,$  which concludes \eqref{vcalE} together with the definition of stochastic domination in Definition \ref{stoch_domination}.
-Similarly, using the second estimate in equation \eqref{eq largedev1}, we can obtain that for $i\ne j$,
+Rescaling $\epsilon^{(i)}$ by $\sigma$, we get a random vector with zero mean, unit variance, and bounded moments up to any order.
+Using the first estimate in equation \eqref{eq largedev1} of Lemma \ref{largedeviation} (recall that the stochastic domination notation means the inequality holds with a multiplicative factor of $p^{\e}$ on the right), we obtain that equation \eqref{vcalE} holds (the second result is a consequence of the first).
+Using the second estimate in equation \eqref{eq largedev1}, we obtain that for $i\ne j$,
  \begin{align*}
-\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \prec \sigma^2 \Big(\sum_{k,l}|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
+\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \le p^{\e} \cdot \sigma^2 \Big(\sum_{k,l=1}^n|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
  \end{align*}
@@
 \begin{align*}
-\left|(\epsilon^{(i)})^\top B \epsilon^{(i)} - \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
-&\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
+\left|(\epsilon^{(i)})^\top B \epsilon^{(i)} - \sigma^2 \tr[B]\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
+&\le p^{\e}\cdot \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+ p^{\e}\cdot \sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\le n^{\e}\cdot\sigma^2 \|B\|_F.
 \end{align*}
-The above two estimates conclude equation \eqref{vcalA2}.
-Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.
+Hence, we have shown equation \eqref{vcalA2} (the second result is again a consequence of the first result).
 \end{proof}

### 2020-10-20 arxiv/tools.tex
appendix

@@
 	Let $Q= n^{ \frac{2}{\varphi}}\log n$.
-	We introduce a truncated matrix $\wt Z$ with entries $\wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le Q \right)\cdot Z_{ij}$
-. By equation \eqref{Ptrunc}, we have that
+	We introduce a truncated matrix $\wt Z$ with entries $\wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le Q \right)\cdot Z_{ij}$.
+Then $\wt Z$ is equal to $Z$ when all the entries of $Z$ are smaller than $Q$.
+Using Markov's inequality and a simple union bound (cf.
+equation \eqref{Ptrunc}), this happens with probability
 \begin{equation}\label{XneX222}
@@
 \end{equation}
-Furthermore, by equation \eqref{meanshif}, we have that
+Furthermore, using the finite $\varphi$-th moment condition and the tail probabilities, we can show that the mean and variance of $Z-\wt Z$ are small, which gives that (cf.
+equation \eqref{meanshif}) %, we have that
 \be\label{meanshif222}
@@
 To prove equation \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$.
-Moreover, using equation \eqref{eq largedev10} we get that
-$$ |(\wh Zv)_i| \prec Q\max_{1\le i\le p}|v_i| + \|v\| . $$
+Moreover, using equation \eqref{eq largedev10} we get that with overwhelming probability
+$$ |(\wh Zv)_i| \le n^\e Q\max_{1\le i\le p}|v_i| + n^\e \|v\| . $$
 Together with the trivial bound $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $Q$.
 Then applying equation \eqref{eq largedev20}, we get that
-$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\prec n^{1/2} Q  \|v\|^2 .
+$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\le n^{1/2+\e} Q  \|v\|^2 .
  $$

### 2020-10-20 arxiv_full_version/intro.tex
start creating arxiv version

--- 2020-10-15 arxiv/intro.tex
@@
 Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \citet{C97}.
-Recent work has revived interest in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
+Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
 It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
@@
 
-Hard parameter sharing works as an inductive transfer mechnism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
+Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
 For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
@@
 	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially, but increases afterward.
+	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
 This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
@@
 We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmicly.
-This setting captures the fact that in many applications, a single task's sample size is usually insufficient for accurate learning.
+We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
+This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
 For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).

### 2020-10-20 arxiv_full_version/proof_examples.tex
start formatting
start creating arxiv version

--- 2020-10-10 arxiv/proof_examples.tex
@@
 
-We follow a similar logic from Theorem \ref{thm_many_tasks}.
-We characterize the global minimizer of $f(A, B)$ in the random-effects model.
-Based on the characterization, we reduce the prediction loss of hard parameter sharing to the asymptotic limits provided in Theorem \ref{thm_main_RMT}.
-Then, we prove Corollary \ref{cor_MTL_loss} based on the bias and variance limits.
+We follow a similar logic to the proof of Theorem \ref{thm_many_tasks}.
+We first characterize the global minimizer of $f(A, B)$ in the random-effect model.
+Based on the characterization, we reduce the prediction loss of hard parameter sharing to the bias-variance asymptotic limits.
+Finally, we prove Corollary \ref{cor_MTL_loss} based on these limiting estimates.
 We set up several notations.
@@
 	where $B \in \real^{p}$ and $A = [A_1, A_2]\in \real^{2}$ because the width of $B$ is one.
-We assume that $A_1$ and $A_2$ are both nonzero.
-Otherwise, we add a tiny amount of perturbation $\delta$ to them and the result remains the same.
-Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we have that $\hat{B}$ satisfies the following
+Without loss of generality, we assume that $A_1$ and $A_2$ are both nonzero.
+Otherwise, the problem reduces to STL. % we add a tiny amount of perturbation $\delta$ to them and the result remains the same.
+Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we obtain that $\hat{B}$ satisfies the following
 	\begin{align}
-		\hat{B} \define  (A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)})^{-1} (A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}). \label{eq_Bhat_2task} %\\
+		\hat{B} \define  \left[A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)}\right]^{-1} \left[A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}\right]. \label{eq_Bhat_2task} %\\
 		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
 	\end{align}
-We denote $\hat \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
+We denote $\hat \Sigma(x)= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
 Applying $\hat B$ to equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers.
@@
  \begin{align}
-		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
+		 g(x) \define & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)})+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)} \right.
+\nonumber\\
 			& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		 + & \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
-		 &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2.
-		\label{eq_mtl_A12}
+		  & + \left\| X^{(2)} \hat \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta^{(1)}-x^2\beta^{(2)})+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} \right.
+\nonumber\\
+		  &\left. + x X^{(2)}\hat \Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
 	\end{align}
-The conditional expectation of $g(x)$ over $\epsilon_1$ and $\epsilon_2$ is
-%\HZ{could you align the Eq so that they look better on page?}
+We have that the conditional expectation of $g(x)$ over $\epsilon^{(1)}$ and $\epsilon^{(2)}$ is
+\begin{align*}
+		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}} \\
+%		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  \\
+%		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2 \right]\\
+%&+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
+		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}) +\sigma^2(n_1+n_2-p).
+\end{align*}
+The calculation is tedious but rather straightforward, so we leave the details to the reader.
+In the random-effect model, recall that the entries of $(\beta^{(1)}- x\beta^{(2)})\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 +(1+x^2) d^2]$.
+Hence, by further taking expectation over $\beta^{(1)}$ and $\beta^{(2)}$, we obtain
 \begin{align}
-\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2}
-&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2 \nonumber\\
-&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2  \nonumber\\
-& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \nonumber\\
-&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
-&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
-& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
-\end{align}
-Using the following identity
-\begin{align*}
-(X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} & =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
-&= (X^{(2)})^\top X^{(2)} \hat \Sigma(x)^{-1}(X^{(1)})^\top X^{(1)},
-\end{align*}
-we can simplify that
-\begin{align*}
- & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\right\|^2 \\
-=&(\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta_1-x\beta_2)\\
-&+(\beta_1-x\beta_2)^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta_1-x\beta_2)\\
-%&=(\beta_1-x\beta_2)^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)\\
-=&(\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2).
-\end{align*}
-Using this identity, we can simplify equation \eqref{Eg(x)}  to
-\begin{align*}
-		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta_1,\beta_2} \\
-		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  \\
-		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2 \right]\\
-&+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
-		=& (\beta_1-x\beta_2)^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2) +\sigma^2(n_1+n_2-p).
-\end{align*}
-For the random-effects model, recall that the entries of $\beta_1, \beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $\kappa^2/p, d^2/p$, respectively.
-Hence,
-\begin{align}
-&\exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2} \nonumber\\
+	&\ex{g(x) \mid X_1, X_2} \nonumber\\
 %&=[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
 %&+ A^2[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-&=\frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{p} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+	=& ((x-1)^2\kappa^2 + (x^2+1)d^2){p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
 \end{align}
 
+%\HZ{could you align the Eq so that they look better on page?}
+%\begin{align}
+%\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}}
+%&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \nonumber\\
+%&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  \nonumber\\
+%& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}} \nonumber\\
+%&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
+%&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
+%& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
+%\end{align}
+%Using the following identity
+%\begin{align*}
+%(X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} & =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
+%&= (X^{(2)})^\top X^{(2)} \hat \Sigma(x)^{-1}(X^{(1)})^\top X^{(1)},
+%\end{align*}
+%we can simplify that
+%\begin{align*}
+% & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \\
+%=&(\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta^{(1)}-x\beta^{(2)})\\
+%&+(\beta^{(1)}-x\beta^{(2)})^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\\
+%&=(\beta^{(1)}-x\beta^{(2)})^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\\
+%=&(\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}).
+%\end{align*}
+%Using this identity, we can simplify equation \eqref{Eg(x)}  to
+
 \paragraph{Part $1$: characterizing the global minimum of $f(A, B)$.}
-Let $\hat{x}$ denote the minimizer of $g(x)$.
+Let $\hat{x}$ denote the global minimizer of $g(x)$.
 We show that in the setting of Corollary \ref{cor_MTL_loss}, $\hat x$ is close to 1.
-This gives us the global minimum of $f(A, B)$, combined with the local optimality condition for $\hat{B}$.
-
-First, we show that $g(x)$ and $\ex{g(x) \mid X^{(1)}, X^{(2)}}$ are close using standard concentration bounds.
+This gives us the global minimum of $f(A, B)$, since $\hat{B}$ is given by $\hat{x}$ using local optimality conditions.
+First, we show that $g(x)$ and its expectation are close using standard concentration bounds.
 \begin{claim}\label{claim_largedev1}
- In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability
-$$\left| g(x) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(x) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right).$$
-%for any small constant $c>0$.
+ In the setting of Corollary \ref{cor_MTL_loss}, for any $x$, we have that with high probability
+$$\left| g(x) - \ex{g(x) \mid X^{(1)}, X^{(2)} }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right).$$
 \end{claim}
 \begin{proof}
-By Fact \ref{fact_minv}(ii), we have that with high probability,
- \be\label{op_X12}
-\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
- \ee
- and
- \be\label{op_Sig1}
-\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
- \ee
-where we used that $1+\tau\le \rho_1=n_1/p\le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
-
- Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}:
+ There are two terms in $g(A)$ from equation \eqref{eq_mtl_A12}.
+ We will focus on dealing with the concentration error of the first term. The second term is similar to the first and we omit the details.
+ For the first term, we expand into several equations under various situations involving the random noise and the random-effect model.
  \begin{align}
- & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
-		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x) ,\label{expand_6}
+ & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)})+ \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)} \right.
+\nonumber\\
+		& \left. + x X^{(1)}\hat \Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2=h_1(x) + h_2(x) +h_3(x) + 2h_4(x) + 2h_5(x) + 2h_6(x), \label{expand_6}
  \end{align}
@@
  \begin{align*}
-&h_1(x):=  (\beta_1-x\beta_2)^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-x\beta_2)  ,\\
-& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
+&h_1(x):=  (\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  ,\\
+& h_2(x) := {(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}}  ,\\
 & h_3(x):=  x^2 { (\epsilon^{(2)} )^\top X^{(2)} \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
-& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1), \\
-&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1),\\
-&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
+& h_4(x):=  (\epsilon^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)}), \\
+&h_5(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta^{(2)}-\beta^{(1)}),\\
+&h_6(x):=x (\epsilon^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}.
 \end{align*}
-Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.
+Next, we estimate each term using Lemma \ref{largedeviation} for random variables with bounded moment up to any order.
+We first state several facts that will be commonly used in the proof.
+By Fact \ref{fact_minv} (ii), we have that w.h.p. the operator norm of $X^{(1)}$ and $X^{(2)}$ are both bounded by $O(\sqrt{n})$.
+Furthermore, the operator norm of $\hat\Sigma(x)^{-1}$ is bounded by $(x^2 + 1)^{-1} O(n_1 + n_2) = (x^2 + 1)^{-1} O(p)$.
+ % \be\label{op_X12}
+%\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
+% \ee
+% and
+% \be\label{op_Sig1}
+%\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
+% \ee
+%where we used that $3\le n_1/p\le \tau^{-1}$ and $3\le n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
 
-For $h_1(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-x\beta_2\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variance $p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $c>0$:
+For $h_1(x)$, using Lemma \ref{largedeviation} and the fact that the entries of $(\beta^{(1)}-x\beta^{(2)})\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variance $b = p^{-1}((x-1)^2\kappa^2 + (x^2+1)d^2)$, we obtain the following estimate w.h.p.
 \begin{align}
-&\left|h_1(x) - \exarg{\beta_1,\beta_2}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
-&\le p^{c}\cdot p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
-&\lesssim p^{1/2+c}\cdot \frac{(x-1)^2\kappa^2 + (x^2+1)d^2/2}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
+	&\left|h_1(x) - \exarg{\beta^{(1)},\beta^{(2)}}{h_1(x) \mid X_1, X_2}\right|\nonumber \\
+\le& p^{c}\cdot p^{-1} b \cdot \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
+	\le& p^{c}\cdot p^{-1} b \cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
+	\lesssim& p^{1/2+c}\cdot \frac{b}{(x^2+1)^2}\lesssim p^{1/2+c}(\kappa^2 + d^2).\label{eq_hA1}
 \end{align}
- Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
-\begin{align*}
- \left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
- & \lesssim \frac{p}{(x^2+1)^2}.
-\end{align*}
-Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
-Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
+In the third step we use the operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)^{-1}$. % as follows
+%\begin{align*}
+%	\left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
+%  & \lesssim \frac{p}{(x^2+1)^2}.
+%\end{align*}
+
+For $h_2(x)$ and $h_3(x)$, since the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d.
+Gaussian random variables with mean zero and variances $\sigma^2$, using Lemma \ref{largedeviation}, we obtain w.h.p.
 \be\label{eq_hA23}\left|h_2(x) - \exarg{\epsilon^{(1)}}{h_2(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2, \quad \left|h_3(x) - \exarg{\epsilon^{(2)}}{h_3(x) \mid X_1, X_2}\right| \lesssim p^{1/2+c}\sigma^2.\ee
-For $h_4(x)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $ c>0$:
+For $h_4(x)$, using Lemma \ref{largedeviation}, we obtain w.h.p.:
 \begin{align}
 			&\left|h_4(x)\right| \nonumber\\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]}\cdot \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
-&\le p^{c}\cdot \sigma \sqrt{p^{-1}[(x-1)^2\kappa^2 + (x^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{c}\cdot \sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2} \cdot \left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|  \left\|X^{(1)}\right\| \left\|\hat\Sigma(x)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
-&\lesssim p^{1/2+c}\frac{\sigma \sqrt{ (x-1)^2\kappa^2 + (x^2+1)d^2/2}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
+	\le& p^{c}\cdot \sigma \cdot \sqrt{b / p}\left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
+	\le& p^{c}\cdot \sigma \sqrt{b / p} \cdot p^{1/2} \left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+	\le&  p^{c}\cdot \sigma \sqrt{b} \cdot \left\|  x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top - \id_{n_1\times n_1} \right\| \cdot \left\|X^{(1)}\right\| \cdot \left\|\hat\Sigma(x)^{-1}\right\| \cdot \left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
+	\lesssim& p^{1/2+c}\frac{\sigma \sqrt{b}}{x^2+1} \lesssim p^{1/2+c}(\sigma^2 + \kappa^2 + d^2).\label{eq_hA4}
 \end{align}
-where in the fourth step we used $\left\|  \id_{n_1}-x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality.
-With same argument, we can show that
-\be\label{eq_hA56} \left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(x)\right| \le p^{1/2+c}\sigma^2,\ee
-with high probability for any small constant $c>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that
-
-Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}.
-Hence the proof is complete.
+Above, in the fourth step we use the operator norm of $x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top - \id$ being at most one and the operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)^{-1}$.
+In the last step we use AM-GM inequality. Using the same argument, we can show that
+$\left|h_5(x)\right| \le p^{1/2+c}(\sigma^2 + \kappa^2 + d^2)$ and $\left|h_6(x)\right| \le p^{1/2+c}\sigma^2$.
+Combining the concentration error bound for $h_1(x), h_2(x), \dots, h_6(x)$, we complete the proof.
+The second term of $g(A)$ can be dealt in similar ways and we omit the details.
 \end{proof}
 
-Next, we show that $\hat x$ is close to 1.
+Next, we show that the global minimizer $\hat x$ of $g(x)$ is close to 1.
 \begin{claim}\label{lem_hat_v}
 %Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
+	Let $c$ be a sufficiently small fixed constant.
 	In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability,
@@
 	\ee
-%	for any small constant $c>0$.
-	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
 \end{claim}
@@
 \begin{align*}
-h(x):= [(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right].
+	h(x)  =& [(x-1)^2\kappa^2 + (x^2+1)d^2] \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right] \\
+				=& [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
 \end{align*}
-Using Fact \ref{fact_minv}(ii), we can obtain that with high probability,
-\begin{align}
-p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
-&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
-&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
-\end{align}
-where we also used that $1+\tau\le \rho_1=n_1/p \le \tau^{-1}$ and $1+\tau\le \rho_2=n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
-\be\label{eq_h1}h(1)= d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
-On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
-\begin{align}\label{eq_hA}
-h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
-\end{align}
-where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and \eqref{op_uplow}.
-%and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
-Hence using Claim \ref{claim_largedev1} and equations \eqref{eq_h1}-\eqref{eq_hA}, we obtain that with high probability,
-\begin{align}
-g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
-&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
-\end{align}
-under conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
-This gives that
-%\be\label{rough A-1}
-$|\hat x-1|\le \delta$ for any small constant $\delta>0$.
-
-%Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
-To obtain the better bound \eqref{hatw_add1}, we study the function $h(x)$ more closely and find its minimizer, denoted by $x^\star$.
+Let $x^{\star}$ denote the global minimizer of $h(x)$.
+Our proof involves two steps.
+First, we will show that $\abs{x^{\star} - 1} \le d^2 / \kappa^2$.
+Second, we will use Claim \ref{claim_largedev1} to show that the global minimizer of $g(x)$ and $h(x)$ are close to each other.
 %Using Lemma \ref{largedeviation} again, we can simplify equation \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
@@
 %To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof.
-First it is easy to observe that $h(x)< h(-x)$ for $x> 0$.
+
+For the first step, it is easy to observe that $h(x)< h(-x)$ for any positive $x$.
+Hence the minimum of $h(x)$ is achieved when $x$ is positive.
 %$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
-Then we consider the case $x\ge 1$. We write
-\begin{align*}
-h(x):= [(1-x^{-1})^2\kappa^2 + (1+x^{-2})d^2/2] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].
-\end{align*}
-Notice that
+Next, we consider the case where $x\ge 1$.
+Notice that the following function always increases when $x$ increases in the positive orthant:
 $$\tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]$$
-is an increasing functions in $x$. Hence taking derivative of $h(x)$ with respect to $x$, we obtain that
+By taking the derivative of $h(x)$, we obtain that for any $x > 1+d^2/\kappa^2$,
 \begin{align}\label{h'(A)1}
-h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - \frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \ge 0,
+h'(x) \ge \left[2(1-x^{-1})\frac{\kappa^2}{x^2} - 2\frac{d^2}{x^3}\right] \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] > 0,
 \end{align}
-as long as $x \ge 1+d^2/(2\kappa^2)$.
-%\begin{align}
-%	h(w) =&  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-%	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-%			& +  \frac{\rho_1}{\rho_2}\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ \sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }.
-\nonumber
-%\end{align}
-%Notice that
-%$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
-%are increasing functions in $w$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
-%\begin{align*}
-%h'(w) \ge & \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
-% &+ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-%		&- 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
-%\end{align*}
-%where the matrix $\cal A$ is defined as
-%\begin{align*}
-%\cal A :&= \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
-%\end{align*}
-%Using the estimate Fact equation \eqref{lem_minv}, we get that $\cal A$ is lower bounded as
-%\begin{align*}
-%\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
-%&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
-%\end{align*}
-%as long as
-%$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
-%Hence $h'(w)>0$ on $(w_1,\infty)$, %i.e. $h(w)$ is strictly increasing for $w>w_1$. This
-%which gives $\hat w\le w_1$.
-Next we consider the case $1-\delta\le x\le 1$. Notice that
+Finally, we consider the case where $x \le 1$. Notice that the following function always decreases when $x$ decreases from $1$:
 $$\tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} +  [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right].$$
-is a decreasing functions in $x$. Hence taking derivative of $h(x)$, we obtain that
+Hence, by taking derivative of $h(x)$, we obtain that for any $x\le 1-d^2/\kappa^2$,
 \begin{align}\label{h'(A)2}
-	h'(x)\le [-2(1-x)\kappa^2 + xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]\le 0,
+	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] < 0,
 \end{align}
-as long as $x\le 1-d^2/(2\kappa^2)$. In sum, we see that the minimizer $x^\star$ must satisfy
-$$1-d^2/(2\kappa^2)\le x^\star \le 1+d^2/(2\kappa^2).$$
+In summary, the global minimizer of $h(x)$ lies within $1-d^2/\kappa^2$ and $1+d^2/\kappa^2$.
 
@@
 
-Now we are ready to prove equation \eqref{hatw_add1}. First, using equations \eqref{op_uplow} and  \eqref{h'(A)1}, we obtain that for $1+d^2/\kappa^2 \le x\le 1+\delta$,
-$$h'(x)\ge \frac{2(x-1)\kappa^2 - d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
-Thus we get that if $1+2d^2/\kappa^2 +p^{-1/4+c}\le x\le 1+\delta$,
+For the second step, using Claim \ref{claim_largedev1}, we have that $g(x)$ and $h(x)$ differ by at most $p^{1/2 + \e}(\sigma^2 + \kappa^2 + d^2)$.
+Therefore, our goal reduces to showing that if $\hat{x}$ deviates too far from $1 \pm d^2 / \kappa^2$, it is no longer a global minimum of $g(x)$.
+%we first argue that $\hat{x}$ is $O(1)$. Hence we can apply Claim \ref{claim_largedev1} to bound the concentration error of $g(x)$.
+%Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
+%\begin{align}
+%p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
+%&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
+%&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
+%\end{align}
+%where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
+%\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
+%On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
+%\begin{align}\label{eq_hA}
+%h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
+%\end{align}
+%where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
+%and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
+%\begin{align}
+%g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
+%&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
+%\end{align}
+%under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
+%This gives that
+%Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
+We prove by contradiction.
+First, suppose that $\hat{x} \ge 1 + 2d^2 /\kappa^2 + p^{-1/2 + \e}$.
+For any $x \ge 1+3d^2/(2\kappa^2)$, we can lower bound the derivative of $h(x)$ using equation \eqref{h'(A)1} as follows
+	\[ h'(x) \ge \frac{2(x-1)\kappa^2 - 2d^2}{x^3} \cdot p^{-1} \tr\left[\left([(X^{(2)})^\top X^{(2)}]^{-1} + x^{-2} [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]
+	\gtrsim p\kappa^2\cdot \frac{x-1}{x (1 + x^2)}. \]
+Therefore, the difference between $h(x)$ and $h(1)$ is at least the following
 \begin{align*}
-h(x)-h(1)\ge h(x)-h(1+d^2/\kappa^2) \ge \int_{1+d^2/\kappa^2}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot |x-1|^2  \gtrsim p\frac{d^4}{\kappa^2} + p^{-1/2+2c}\cdot p\kappa^2 .
+		h(x)-h(1) \ge h(x) - h\left(1+\frac{3d^2}{2\kappa^2}\right)
+	\ge \int_{1+\frac{3d^2}{2\kappa^2}}^x h'(x)\dd x \gtrsim p\kappa^2 \cdot \int_{1 + \frac{3d^2}{2\kappa^2}}^x \frac{x-1}{x(1 + x^2)} \dd x.
 \end{align*}
-On the other hand, by Claim \ref{claim_largedev1} we have that
-$$ g(x)=h(x)+\sigma^2 (n_1+n_2-p)+\OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right)$$
-with high probability. Combining the above two estimates, we obtain that under the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$,
-$$g(x)-g(1) = h(x)-h(1) + \OO \left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right) >0$$
-with high probability, i.e. $x$ cannot be the minimizer of $g$.
+When $\hat{x}$ is sufficiently far from $1$ (e.g.
+$2d^2 / \kappa^2 + p^{-1/4+\e}$), one can verify that $h(x) - h(1)$ is at least $\OO(p\frac{d^4}{\kappa^2} + p^{1/2+2c} \kappa^2) > \OO(p^{1/2 + c} (\sigma^2 + \kappa^2 + d^2))$, under the condition that $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$.
+On the other hand, by triangle inequality and Claim \ref{claim_largedev1} we have that
+\begin{align*}
+	h(\hat{x}) - h(1) = g(\hat{x}) - g(1) + (h(\hat{x}) - g(\hat{x})) + (g(1) - h(1))
+	\le \OO\left(p^{1/2+c}\left(\sigma^2 +\kappa^2+d^2 \right)\right).
+\end{align*}
+Hence, we have arrived at a contradition.
+
 %Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have
 %$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$ where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
-Second, using equations \eqref{op_uplow} and  \eqref{h'(A)2}, we obtain that for $1-\delta \le x \le 1-d^2/\kappa^2$,
-$$- h'(x)\ge  [2(1-x)\kappa^2 - xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\left(d^2 + |x-1|\kappa^2\right).$$
-Then with a similar argument as above, we can get that if $1-2d^2/\kappa^2 - p^{-1/4+c}\le x\le 1-\delta$, then
-$$ h(x)-h(1) \gtrsim p\frac{d^4}{\kappa^2} +p^{1/2+2c} \kappa^2, $$
+Second, suppose that $\hat{x} \le 1 - 2d^2/ \kappa^2 - p^{-1/2 + \e}$.
+Using equation \eqref{h'(A)2}, we obtain that for any $x \le 1 - 3d^2/(2\kappa^2)$,
+	\[ -h'(x)\ge  [2(1-x)\kappa^2 - 2xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right]  \gtrsim p\kappa^2 \cdot \frac{(1 - x)x^2}{1 + x^2}.
+\]
+Using a similar argument to the first case, we get that the difference between $h(x)$ and $h(1)$ is at least the integral of the abvoe derivative.
 %under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?},
-which again implies that $g(x)>g(1)$, i.e. $x$ cannot be the minimizer of $g$. In sum, we obtain that the minimizer $\hat x$ must satisfy equation \eqref{hatw_add1}.
+This implies that $\hat{x}$ cannot be too far from one.
+Hence we have completed the proof.
 %Next we prove the following estimate on the optimizer $\hat x$: with high probability,
@@
 Recall that the hard parameter sharing estimator $\hat{\beta}_2^{\MTL}$ is equal to $\hat{B} \hat{A}_2$.
-The predication loss of hard parameter sharing is as follows
+Using the local optimility condition for $\hat{B}$, we obtain the predication loss of HPS as follows
 \begin{align}
-L(\hat{\beta}_2^{\MTL}) &=\left\|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right\| \nonumber\\
-&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta_1-\hat x^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
+L(\hat{\beta}_2^{\MTL}) &=\left\|(\Sigma^{(2)})^{1/2} \left( \hat B \hat A_2 - \beta^{(2)}\right)\right\| \nonumber\\
+&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x\beta^{(1)}-\hat x^2\beta^{(2)})+ (X^{(2)})^\top \epsilon^{(2)} + \hat x   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
 \end{align}
-Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as in the following claim.
+Using Lemma \ref{lem_hat_v} and the concentration estimates in Lemma \ref{largedeviation}, we simplify $L(\hat{\beta}_2^{\MTL})$ as follows.
 
 \begin{claim}\label{claim_reduction}
-Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. Section \ref{sec_diff}).
-In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability
+Recall that $\hat \Sigma(1)$ is equal to $\hat \Sigma$ (cf. equation \eqref{def hatsig}).
+In the setting of Claim \ref{cor_MTL_loss}, we have the following estimate w.h.p.
 \begin{align*}
-&\left|L(\hat{\beta}_2^{\MTL}) - d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{{\hat \Sigma^{-1}  }}\right| \nonumber\\
+&\left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{{\hat \Sigma^{-1}  }}\right| \nonumber\\
 \lesssim&  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2).
@@
 \begin{proof}
-Our proof is divided into two steps.
-First, with the concentration estimates in Lemma \ref{largedeviation}, we can simplify $L(\hat{\beta}_2^{\MTL})$ as follows.
-With high probability, we have that for any small constant $c>0$,
+Our proof is divided into two steps. First, using Lemma \ref{largedeviation}, we show that
 \be\label{claim_largedev2} \left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat x)\right| \le p^{-1/2+c} \left(\sigma^2 +\kappa^2 +d^2 \right),
 \ee
-where the function $\cal L(\hat x)$ is defined as
+where $\cal L(\hat x)$ is defined as
 \begin{align*}
-	\cal L(\hat x)	:=  &\hat x^2\left[(\hat x-1)^2 \kappa^2 + \frac{(\hat x^2+1)d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} } \\
-	& +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}\right).
+	\resizebox{0.97\hsize}{!}{%
+	$\cal L(\hat x)	:=  \hat x^2\left[(\hat x-1)^2 \kappa^2 +  (\hat x^2+1)d^2 \right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma(\hat x)^{-1} \Sigma^{(2)} \hat\Sigma(\hat x)^{-1} (X^{(1)})^{\top}X^{(1)} }
+	 +\sigma^2\cdot \bigtr{\Sigma^{(2)}\hat \Sigma(\hat x)^{-1}}.$
+	}%
 \end{align*}
 % \end{claim}
-We are ready to finish the proof of Claim \ref{claim_reduction}.
-We defer the proof of equation \eqref{claim_largedev2} until the end.
-Next, we can further simplify $\cal L(\hat x)$ using Claim \ref{lem_hat_v} and $\Sigma^{(1)}=\Sigma^{(2)}=\id_p$.
-More precisely, we claim that with high probability
+%We are now ready to finish the proof of Claim \ref{claim_reduction}.
+Next, we further simplify $\cal L(\hat x)$ since $\hat{x}$ is close to one and $\Sigma^{(1)},\Sigma^{(2)}$ are both isotropic
 \begin{align}
-&\left|\cal L(\hat x)- d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\hat \Sigma^{-1}  }\right| \nonumber\\
-&\lesssim  \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
+	&\left|\cal L(\hat x)- \frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \bigtr{\hat \Sigma^{-1}}\right| \nonumber\\
+\lesssim & \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2). \label{simple12}
 \end{align}
-Combining \eqref{claim_largedev2} and \eqref{simple12}, we obtain Claim \ref{claim_reduction}.
+Combining equation \eqref{claim_largedev2} and \eqref{simple12}, we obtain the desired claim.
+We prove these two equations one by one as follows.
 
-It remains to prove equation \eqref{simple12}. Using Lemma \ref{lem_hat_v} and equations \eqref{op_X12}-\eqref{op_Sig1}, we obtain that with high probability,
+First, we prove equation \eqref{simple12}.
+We can bound the left hand side of equation \eqref{simple12} as
+\begin{align*}
+	&\left|\cal L(\hat x)-\frac{2d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat\Sigma^{-1}  }\right)\right| \\
+	\lesssim &\left(|\hat x-1|^2 \kappa^2 + |\hat x-1|d^2\right)\cdot p^{-1}\bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2 } \\
+	&+ \frac{d^2}{p}\left|\tr\left[\left(\hat\Sigma(\hat x)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\hat\Sigma(\hat x)^{-1}-\hat\Sigma^{-1}  }\right|.
+\end{align*}
+We deal with the trace terms in the above equation one by one.
+Using Claim \ref{lem_hat_v} and operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)$, we have that w.h.p.
 \begin{align}
- \|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1|\|\hat\Sigma^{-1}\| \| (X^{(1)})^\top X^{(1)}\|\|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right).\label{est111}
+	\|\hat\Sigma^{-1}-\hat\Sigma(\hat x)^{-1}\| &\le |\hat x^2-1| \cdot \|\hat\Sigma^{-1}\| \cdot \| (X^{(1)})^\top X^{(1)}\| \cdot \|\hat\Sigma(\hat x)^{-1}\|  \lesssim p^{-1}\left(\frac{d^2}{\kappa^2} + p^{-1/4+c}\right).\label{est111}
 \end{align}
-Using similar arguments, we get that with high probability,
+Using similar arguments, we get that w.h.p.
 \begin{align}\label{est222}
-&\left\|\left(\hat\Sigma^{-2}-\hat\Sigma(\hat x)^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+c} .
+&\left\|\left(\hat\Sigma^{-2}-\hat\Sigma(\hat x)^{-2}\right)\left((X^{(1)})^\top X^{(1)} \right)^2\right\| \lesssim  \frac{d^2}{\kappa^2} + p^{-1/4+c},
 \end{align}
-Moreover, using equations \eqref{op_X12}-\eqref{op_Sig1} we can bound that with high probability,
-%$$\bignorm{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)}}\lesssim 1.$$
-%which further implies that with high probability,
+and
 \begin{align}
@@
 \end{align}
-Now we bound the left hand side of equation \eqref{simple12} as
-\begin{align*}
-&\left|\cal L(\hat x)-\frac{d^2}{p}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] -\sigma^2  \tr\left({\hat\Sigma^{-1}  }\right)\right| \\
-&\lesssim \left(|\hat x-1|^2 \kappa^2 + |\hat x-1|d^2\right)\cdot p^{-1}\bigtr{ \hat\Sigma^{-2} \left((X^{(1)})^{\top}X^{(1)}\right)^2 } \\
-&+ \frac{d^2}{p}\left|\tr\left[\left(\hat\Sigma(\hat x)^{-2}-\hat\Sigma^{-2}\right) \left((X^{(1)})^\top X^{(1)} \right)^2\right]\right|+ \sigma^2  \left|\bigtr{\hat\Sigma(\hat x)^{-1}-\hat\Sigma^{-1}  }\right|.
-\end{align*}
-Applying the estimates \eqref{hatw_add1}, \eqref{est111}, \eqref{est222} and \eqref{est333} to the three terms on the right-hand side, we can conclude \eqref{simple12}.
+Applying the above results \eqref{est111}, \eqref{est222}, and \eqref{est333} to the bound of $\cL(\hat{x})$ above, we have shown that equation \eqref{simple12} holds.
 
-Now we give the proof of the estimate \eqref{claim_largedev2}.
-The proof of this claim is very similar to Claim \ref{claim_largedev1}, where the only difference is that $\hat x$ now may depend on $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$.
-In this case, we can still use  Lemma \ref{largedeviation} to conclude the proof because $\hat x$ can be pulled out as a coefficient.
-Here we only give a proof sketch and omit the details.
-Recall that $\beta_0$ is the shared component of $\beta_1$ and $\beta_2$ with i.i.d.
-Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
-Moreover, we denote the task-specific components by $\wt\beta_1$ and $\wt\beta_2$, whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2 / 2$.
-Then we write $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
+Second, we prove equation \eqref{claim_largedev2}.
+The proof is very similar to Claim \ref{claim_largedev1}.
+The key difference is that $\hat x$ correlates with $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta^{(1)}$, and $\beta^{(2)}$.
+Nevertheless, Lemma \ref{largedeviation} still applies for any arbitrary $\hat x$.
+We describe a proof sketch and omit the details.
+Recall that $\beta_0$ is the shared component of $\beta^{(1)}$ and $\beta^{(2)}$ with i.i.d. Gaussian entries of mean zero and variance $p^{-1}\kappa^2$.
+The task-specific components, denoted by $\wt\beta^{(1)}$ and $\wt\beta^{(2)}$, consist of i.i.d. Gaussian random variables with mean zero and variance $p^{-1} d^2$.
+We write $L(\hat{\beta}_2^{\MTL}) $ from equation \eqref{Lbeta_HPS} as:
 \begin{align}
-L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta_1 - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta_2 \right] \right.
+L(\hat{\beta}_2^{\MTL})  =&  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat x)^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat x -\hat x^2)\beta_0+(X^{(1)})^\top X^{(1)} \hat x\wt \beta^{(1)} - (X^{(1)})^\top X^{(1)}  \hat x^2\wt \beta^{(2)} \right] \right.
 \nonumber\\
@@
 \end{align}
-As in \eqref{expand_6}, we can expand this expression into the sum of 15 terms, and bound each term as in \eqref{eq_hA1}-\eqref{eq_hA56}.
-For example, for the main term $\hat x^2 \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1$, using
-Lemma \ref{largedeviation} and equation \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability:
+Similar to the analysis of $g(x)$, we expand $L(\hat{\beta}_2^{\MTL})$ into the sum of 15 terms, and bound the concentration error of each term similar to $h_1(x), \dots, h_6(x)$.
+For example, for the leading term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using
+Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
 \begin{align*}
-&  \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta_1 - \frac{d^2}{2} \cdot p^{-1}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
+&  \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)} - \frac{d^2}{p}\bigtr{(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}}\right| \\
 &\le p^{-1+c}d^2 \cdot \left\| (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)} \right\|_F \\
@@
 \end{align*} 
-For the cross term $\hat x \wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and \eqref{op_X12}-\eqref{op_Sig1}, we can obtain the following estimate with high probability for any small constant $c>0$:
+For the cross term $\hat x (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}$, using Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
 \begin{align*}
- \left|\wt \beta_1^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
-&\lesssim p^{c}\sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
+ \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
+&\lesssim p^{c}\cdot \sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
 &\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
 \end{align*}
-The rest of the terms in the expansion of \eqref{expand_15} can be bounded in the same way, and we omit the details.
+The rest of the terms in the expansion of $L(\hat{\beta}_2^{\MTL})$ can be dealt with similarly, and we omit the details.
  \end{proof}
 
-\paragraph{Part $3$: applying the bias and variance limits.}
+\paragraph{Part $3$: applying the bias-variance limits.}
 Finally, we are ready to complete the proof of Corollary \ref{cor_MTL_loss}.
-We derive the variance term $\sigma^2  \tr[\hat\Sigma^{-1}]$ and the bias term $d^2\cdot {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using Theorem \ref{thm_main_RMT}.
+We derive the variance term $\sigma^2  \tr[\hat\Sigma^{-1}]$ and the bias term $\frac{2d^2}{p} \tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right]$ using our random matrix theory results.
 
 \begin{proof}[Proof of Corollary \ref{cor_MTL_loss}]
-Using \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1\id_p+a_2\id_p)^{-1}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
+For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
+\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
 with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
 	\begin{align}
-		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
-		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} . \label{simplesovlea12}
+		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
+		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
 			\end{align}
 Applying the above to equation \eqref{eq_var111}, we obtain that
-\be\label{eq_var112}\bigtr{\hat\Sigma^{-1}}  = \frac{p}{n_1+n_2} \cdot \frac{\rho_1+\rho_2}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})=  \frac{1}{\rho_1+\rho_2-1}+\OO(p^{-c_\varphi})\ee
+\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi})\ee
 with high probability.
 
-On the other hand, we have that with high probability,
+For the bias term, since the spectrum of $(X^{(1)})^{\top} X^{(1)}$ is tightly concentrated by Fact \ref{fact_minv}, we have that
 \begin{align}
- \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\hat \Sigma^{-2}\right)_{ii}  &\le {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
- &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} .\nonumber
+ \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi})}{p} \bigtr{\hat \Sigma^{-2}}  &\le {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] \label{eq_bias111}\\
+ &\le \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi})}{p} \bigtr{\hat\Sigma^{-2}}.\nonumber
 \end{align}
-To obtain this inequality, we used  
-$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
-by Fact \ref{fact_minv}(ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
-Using \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_p$ and $w$ being the $i$-th coordinate vector, we can calculate that 
-\begin{align}\label{eq_bias112}
- \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})
-\end{align}
-with high probability. Solving equation \eqref{eq_a34extra} with $a_1, a_2$ in \eqref{simplesovlea12} and $\lambda_i\equiv 1$, $1\le i\le p$, we can obtain that
+%To obtain this inequality, we used
+%$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
+%by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
+Using the bias limit \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$, and $w = e_i$ (the $i$-th coordinate vector), we have w.h.p. (via a union bound)
+\begin{align*}%\label{eq_bias112}
+ e_i^{\top}\hat\Sigma^{-2} e_i = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
+\end{align*}
+We solve the self-consistent equations \eqref{eq_a34extra} given $a_1, a_2$, and obtain
 \begin{align*}
-		% a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad & a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
-		a_3 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
-		&  a_4 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}. %\label{simplesovlea34}
+		a_3 = \frac{p\cdot n_1}{(n_1 +n_2)(n_1 +n_2 - p)}, \quad
+		&  a_4 = \frac{p\cdot n_2}{(n_1 + n_2)(n_1 + n_2 - p)}. %\label{simplesovlea34}
 \end{align*}
-Inserting them into \eqref{eq_bias112}, we obtain that 
+Applying $a_3, a_4$ to the equation above, we obtain
 \begin{align*}%\label{eq_bias113}
- \left(\hat\Sigma^{-2}\right)_{ii} = \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} +\OO(p^{-c_\varphi})
+ e_i^{\top}\hat\Sigma^{-2}e_i =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
 \end{align*}
-with high probability. In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use \eqref{apply derivlocal} to get that 
-\begin{align*}%\label{eq_bias113}
-\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{-\frac{\varphi-4}{2\varphi}}
+%In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that
+%\begin{align*}%\label{eq_bias113}
+%\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
+%\end{align*}
+%on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that
+%\begin{align*}
+%\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{1-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
+%\end{align*}
+%with high probability, which by Definition \ref{stoch_domination} gives that
+%\begin{align}\label{eq_bias113}
+%\left| p^{-1}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\le \frac{p^{-c_\varphi}}{(n_1+n_2)^2}
+%\end{align}
+%with high probability.
+Applying the above result to equation \eqref{eq_bias111}, we get the desired result for the bias term.
+%\begin{align*}
+%		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\nonumber \\
+%		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3} \nonumber\\
+%		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}.
+%\end{align*}
+Combining the bias and variance estimates, we get that
+\begin{align*}
+	\left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right| &\le   \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
+	&+\OO\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
 \end{align*}
-on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that 
-\begin{align*} 
-\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\prec p^{1-\frac{\varphi-4}{2\varphi}}
-\end{align*}
-with high probability, which by Definition \ref{stoch_domination} gives that
-\begin{align}\label{eq_bias113}
-\left| p^{-1}\sum_{i=1}^p \left(\Sigma(1)^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\right|\le p^{-c_\varphi}
-\end{align}
-with high probability. Inserting \eqref{eq_bias113} into \eqref{eq_bias111}, we get that
-\begin{align*}
-		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}\nonumber \\
-		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3} \nonumber\\
-		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot  \frac{(\rho_1+\rho_2)^3}{(\rho_1+\rho_2-1)^3}
-\end{align*}
-with high probability.
-
-Combining equation \eqref{eq_var112} and the above with Claim \ref{claim_reduction}, we get that
-\begin{align*}
-	\left|\cal L(\hat x)- \frac{\sigma^2}{\rho_1+\rho_2-1} - d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}\right| \le   \left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \nonumber\\
-+C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
-\end{align*}
-Then using Claim \ref{claim_largedev2} and the conditions $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-c_{\varphi}}{\kappa^2}$, we conclude the proof.
+Since $\sigma^2 \lesssim  \kappa^2$ and $d^2 \le p^{-\e}{\kappa^2}$ by our assumption, we obtain the desired result.
+The proof is complete.
 \end{proof}

### 2020-10-20 arxiv_full_version/same_cov.tex
start creating arxiv version

@@
 %We provide a sharp generalization error bound of hard parameter sharing estimators.
-In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same sample size and features.
+In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
 %\FY{Is it should be "same covariate" or "same covariates"?}
@@
 
-\paragraph{Setting.} Suppose we have $t$ datasets whose samples size are all equal to $n$ and whose features are all denoted by $X \in \real^{n \times p}$, and the label (vector) of the $i$-th task follows a linear model $Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}$.
-Let $\Sigma\in \R^{p\times p}$ denote the population covariance matrix of all tasks.
-We assume that:
-\begin{itemize}
-	\item $X = Z \Sigma^{1/2}$ and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with mean zero, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$;
-	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional ditribution with mean zero, variance $\sigma^2$, and bounded moment up to any order.\footnote{More precisely, there exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-\end{itemize}
+\textbf{Setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose features are all denoted by $X \in \real^{n \times p}$.
+The label vector of the $i$-th task follows a linear model $Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}$.
+We assume:
+
+\vspace{-0.05in}
+(i) $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+
+\vspace{-0.05in}
+(ii) every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
+
+%\end{itemize}
 For an estimator $\hat{\beta}_i$ of task $i$, we are interested in its (out-of-sample) prediction loss
 \[ L(\hat{\beta}_i) = \bignorm{\Sigma^{1/2} (\hat{\beta_i} - \beta^{(i)})}^2. \]
+Recall that $r$ is the width of $B$.
+We focus on cases where $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \citet{WZR20}).
 
-Our main result shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this intuition, we introduce several notations.
-Let $B^\star \define [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$:\footnote{To ensure that $A^{\star}$ is unique, we assume that $\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.}
-\[ A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}}. \]
+Our first main result shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
+To formalize this geometric intuition, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ which contains all the linear model parameters.
+Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is task labels' ``covariance''):\footnote{To ensure that $A^{\star}$ is unique, we assume that $\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.}
+\begin{align}\label{eq_A_star}
+	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}}.
+\end{align}
 Let $a_i^{\star} \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$.
-We show that the prediction loss of hard parameter sharing decomposes to a bias term $L(B^{\star} a_i^{\star})$ measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with $\norm{a_i^{\star}}^2$.
+We show that the prediction loss of HPS decomposes into a bias term $L(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
 % $B^{\star} A^{\star} {A^{\star}}^{\top}$.
+Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
+Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
+Our result is stated as follows.
 
@@
 	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	Assume that $n > \rho p$ for a fixed constant $\rho > 1$.
+	Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
 	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-	Let $\hat{A}, \hat{B}$ be a global minimum of $f(A, B)$.
-	For any task $i = 1, 2, \dots, t$, the prediction loss of $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ satisfies that with high probability,
+%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
+	For any task $i = 1, 2, \dots, t$, with high probability over the randomness of the input, the prediction loss of $\hat{\beta}_i^{\MTL}$ satisfies that
 	\begin{align*}
-		\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}}
-		\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
+		&\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}} \\
+		\le& n^{-\frac{c_{\varphi}}2} \cdot \frac{t \bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2}^2} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}.
+		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
 	\end{align*}
@@
 I will check the proof to see whether $C_2 =  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}^2$ or $C_1\cdot \sigma\norm{\Sigma^{1/2} B^{\star}}$?}
+\textbf{Comparison to single-task learning (STL).}
 Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
@@
 %	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-One direct implication of our result is that compared to single-task learning, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
+One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
 On the other hand, the bias always increases.
@@
 Obviously, the concentration error decreases with $n$.
-How about the variance $\bigtr{\Sigma (X^{\top} X)^{-1}}$?
+First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
 It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
@@
 %			\end{align}
-  the sample size $n$ grows to infinity proportionally with the dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
+  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
 %	\end{enumerate}
 \end{assumption}
-Under the above assumption, the following result is well-known.
+Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
 
@@
 	With high probability over the randomness of $X$, we have that
-		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} + \OO(n^{-c_{\varphi}}). \]
+		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
 \end{fact}
-Applying \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
-		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p}. \]
-As a remark, Fact \ref{fact_tr} has a rich history in random matrix theory.
+\textit{Remark.} The above result has a long history in random matrix theory.
 For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
 For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
+Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
+		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
+
 %Finally, for the random noise component, we assume that all of its moments exist.
@@
 
-Next, we consider the bias $L(B^{\star} a^{\star}_i)$.
-We illustrate through a random-effects model, which has been studied for a single task case \cite{dobriban2020wonder}.
-Suppose every $\beta_i$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
+We illustrate the bias through a random-effect model, which has been studied for a single-task case \cite{dobriban2020wonder}.
+Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
 Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
 Let $\beta_0$ denote the shared component whose entries are sampled i.i.d. from an isotropic Gaussian distribution of mean zero and variance $p^{-1}\kappa^2$.
-Let the task-specific component be a random Gaussian vector with i.i.d. entries of mean zero and variance $p^{-1} d^2$.
-Thus, for any two different $\beta_i$ and $\beta_j$, their distance is roughly $2d^2$.
+Let $\beta^{(i)}$ be equal to $\beta_0$ plus a task-specific component that is a random Gaussian vector with i.i.d. entries of mean zero and variance $p^{-1} d^2$.
+Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
 %	The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
@@
 \begin{example}[Sample efficiency]\label{ex_same_cov}
-In the random-effects model described above, we further assume that $\Sigma$ is isotropic for illustration.
-We show that when the rank of hard parameter sharing is one, the bias $L(B^{\star} a_i^{\star})$ satisfies that with high probability,
+In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
+We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
+\[ \frac{1}{t}\sum_{i=1}^t L(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{1}{t}} {d^2}{} + \frac{1}{t} \cdot \frac{\sigma^2 p}{n - p} \pm \OO(n^{- \frac {c_{\varphi}} 2}) .\]
+We describe a proof sketch.
+First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
 \[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
-Since $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$, and the $(i, j)$-th entry of this matrix is roughly equal to
+To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
+Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
+Based on the definition of the random-effect model, the $(i, j)$-th entry of ${B^{\star}}^{\top} B^{\star}$ is equal to (ignoring lower order terms)
 %\begin{align*}
@@
 \begin{align*}
-	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \begin{cases}
+	\beta_i^{\top} \beta_j = \norm{\beta_0}^2 + \begin{cases}
 																								0, &\text{ if } i \neq j \\
@@
 \end{align*}
-which follows from the definition of the random-effects model.
-Note that $\norm{\beta_0}^2$ is roughly $\kappa^2$.
-One can verify that the top eigenvalue of ${B^{\star}}^{\top} B^{\star}$ is approximately $t \kappa^2 + d^2$ and the rest of its eigenvalues are all equal to $d^2$.
-Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss as above.
+Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
+Then, one can verify that the top eigenvalue of ${B^{\star}}^{\top} B^{\star}$ is $t \kappa^2 + d^2$ and the rest of its eigenvalues are all $d^2$.
+Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
 
-For the variance term, since $A^{\star}$ has rank-$1$, we have that $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$. Moreover, we can use Fact \ref{fact_tr} to calculate $\bigtr{\Sigma (X^{\top} X)^{-1}}$. 
-Combined together, the average prediction loss of hard parameter sharing is as follows
-\[ \frac{1}{t}\sum_{i=1}^t L(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{1}{t}} {d^2}{} + \frac{1}{t} \cdot \frac{\sigma^2 p}{n - p} \pm \OO(n^{-c_{\varphi} / 2}) .\] %\pm \OO(n^{-c_\varphi} (\sigma^2 +\kappa^2 +d^2)).
-\]
-%In fact, the error for this approximate equation is at most $\OO(n^{-c_\varphi/2} (\sigma^2 +\kappa^2 +d^2))$.
+Second, using Fact \ref{fact_tr}, one can see that the average variance is
+\begin{align*}
+	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} &= \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p} \\
+	&= \frac{1}{t}\frac{\sigma^2 p}{n - p},
+\end{align*}
+because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
+Combined together, we have derived the average prediction loss in the random-effect model.
 \end{example}
-We compare hard parameter sharing to single-task learning.
-Using Fact \ref{fact_tr} above, the average prediction loss of single-task learning is $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}  \pm \OO(n^{-c_\varphi} \sigma^2)$ with high probability.
-	Suppose $n$ is sufficiently large so that the error is negligible.
-\begin{enumerate}
-	\item The prediction loss of hard parameter sharing is less than single-task learning if and only if ${d^2}{} < \frac{\sigma^2 p}{n - p}$, that is, the ``task-specific variance'' of $\beta_i$ is smaller than the ``noise variance''.
-	\item When ${d^2}{} < \frac{\sigma^2 p}{n - p}$, increasing $r$ does not help.
-	To see this, one can verify what when $r$ increases by one, bias reduces by ${d^2}{}$, but variance increases by $\frac{\sigma^2 p}{n-1}$ (details omitted).
-	\item Hard parameter sharing requires at most $p + \frac{n - p}{t - (t - 1)\frac{d^2 (n - p)}{\sigma^2 p}} < n$ samples to get comparable loss to single-task learning.
-	This follows by using this sample size in the average prediction loss equation above.
-\end{enumerate}
+
+\textbf{Comparison to single-task learning.}
+Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
+Comparing HPS to STL, we have the following qualitative properties.
+%	Suppose $n$ is sufficiently large so that the error is negligible.
+%\begin{enumerate}
+
+(i) The prediction loss of HPS is smaller than STL if and only if ${d^2}{} < \frac{\sigma^2 p}{n - p}$, that is, the ``task-specific variance'' of $\beta^{(i)}$ is smaller than the ``noise variance''.
+
+(iii) HPS requires at most $p + \frac{n - p}{t - (t - 1)\frac{d^2 (n - p)}{\sigma^2 p}}$ samples that is less than $n$ samples to get comparable loss to STL.
+	This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
+
+(ii) When ${d^2}{} < \frac{\sigma^2 p}{n - p}$, increasing $r$ does not help.
+	To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
+%\end{enumerate}
 %\FY{I think these two facts probably need more clarification?}
 
-\paragraph{Proof overview.} The key idea for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-	Since all tasks have the same covariates, the optimization objective \eqref{eq_mtl} becomes
+\textbf{Proof overview.} The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
+	In the setting of this theorem, the minimization problem \eqref{eq_mtl} becomes
 	\begin{align}
@@
 	where we recall that $B \in \real^{p \times r}$ and $A_1, A_2, \dots, A_t \in \R^r$.
-	Let $Y = [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$.
-	Using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of the output layers as follows
-	\begin{align} \label{eq_Bhat}
-		\hat{B}(A) \define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+}
-		= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}.
+	Using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$ as follows
+	\begin{align}
+		\hat{B}(A) &\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
+		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
 	\end{align}
-	Here we have used that $X^{\top}X$ is invertible since $n > \rho p$ (cf. Fact \ref{fact_minv}).
+	where $Y = [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$.
+	Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
 	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on the output layer:
-	\begin{align}
-		g(A) \define \sum_{j=1}^t \bignorm{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A_j - Y^{(j)}}^2. \label{eq_mtl_output_layer}
+	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
+	\begin{align}\label{eq_mtl_output_layer}
+		\resizebox{0.869\hsize}{!}{%
+		$g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.$
+		}%
 	\end{align}
@@
 	%Furthermore, $\hat{A}$ is a global minimizer of $g(A)$ in equation \eqref{eq_mtl_output_layer}.
-	Our next claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
-	\begin{claim}\label{claim_opt_dist}
-		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
-		In the setting of Theorem \ref{thm_many_tasks}, we have that
-		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
-				\le  p^{-c_{\varphi}} \cdot C_1. \]
-	\end{claim}
-	The proof of the above claim is based on the following characterization.
-
-	\begin{claim}\label{lem_exp_opt}
-		In the setting of Theorem \ref{thm_many_tasks}, we have that
-		\begin{align}
-			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{\dagger} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).
-\label{eq_gA}
-		\end{align}
-		As a result, the minimum of $\ex{g(A)}$, denoted by $A^{\star}{A^\star}^\top$, is the best rank-$r$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star}$.
-	\end{claim}
-
-	 One can see that the expected optimization objective also admits a nice bias-variance decomposition.
-	Furthermore, its minimizer only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.
-
-	The next piece of our proof deals with the prediction loss of hard parameter sharing.
-	\begin{claim}\label{claim_pred_err}
-		In the setting of Theorem \ref{thm_many_tasks},
-		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
-		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
-		\begin{align*}
-			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
-			\le  n^{-1/4} \left( L(B^{\star} \hat{a}_i)+ \sigma^2  \cdot\|\hat a_i\|^2\right) .
-		\end{align*}
-	\end{claim}
-	The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
-	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
-	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is within an $\OO(n^{-1/4})$ fraction of $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$.
-Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$.
-With this estimate, we can bound the difference
-		$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
-		Combined together, our proof is complete. We omit the details.
-%		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
-%		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
-%		Combined together, our proof is complete.
-	\end{proof}
+	Our main idea is to show that the subspaces spanned by the rows of $\hat{A}$ and $A^{\star}$ are close to each other.
+	We carefully keep track of the concentration error between $\hat{A}$ and $A^{\star}$.
+	The proof can be found in Section \ref{app_proof_error_same_cov}.

### 2020-10-20 full_version_1013/diff_cov.tex
start creating arxiv version

\section{Bias-variance Limits: Different Sample Sizes and Covariate Shifts}\label{sec_diff}

The previous section assumes that all tasks have the same sample size and feature vectors.
This section studies how different sample sizes and different features impact hard parameter sharing.
%The different covariates case differs from the same covariates case in two aspects.
%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
The setting where features differ across tasks is often also called ``covariate shift''.

Unlike the previous section, we no longer have an optimal solution for $f(A, B)$.
This is because $f(A, B)$ is in general non-convex.
Instead, our result implies tight generalization bounds for any \emph{local minimum} of $f(A, B)$.
We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
Suppose that $X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p}$ and $X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p}$, where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$. The matrices $\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.

\paragraph{Bias-variance equations.}
Our key result characterizes the asymptotic limit of the inverse of the sum of two different sample covariance matrices.
To motivate our study, consider a special case where $A_1=A_2=1$. 
Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
By Proposition 1 of \citet{WZR20}, we consider the case of $r = 1 < t = 2$, since when $r > 1$, the optimal solution of $f(A, B)$ is equivalent to single-task learning.
When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
Hence we can write down a closed form equation for any local minimum of $f(A, B)$.
By solving $B$ in equation \eqref{eq_mtl}, we obtain the hard parameter sharing estimator $\hat{\beta}_2^{\MTL} = B A_2 = B$ as follows:
\begin{align}\label{def hatsig}
	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \ \ \text{ where } \ \ \hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}.
\end{align}
The matrix $\hat{\Sigma}$ adds up both tasks' sample covariances, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.

To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to its expectation similar to Claim \ref{claim_pred_err}):
\begin{align}
	\exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}} =
	& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
\end{align}
Equation \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of hard parameter sharing for two tasks, respectively.
Our main result in this section characterizes the asymptotic bias-variance limits under the high-dimensional assumption.
Intuitively, the spectrum of $\hat{\Sigma}^{-1}$ (and hence its trace) not only depends on both tasks' sample sizes, but also depends on the ``alignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
However, capturing this intuition quantitatively turns out to be technically challenging.
%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
We introduce a key quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and as we show below, the trace of $\hat{\Sigma}^{-1}$ has an intricate dependence on the spectrum of $M$.

Let $U\Lambda V^\top$ denote the SVD of $M$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote $M$'s singular values in descending order.
Our main result is stated as follows.

\begin{theorem}\label{thm_main_RMT}
	Let $c_{\varphi}$ be a fixed value in $(0, \frac{\varphi - 4}{2\varphi})$.
	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits.

	\noindent (i) The variance equation \eqref{eq_variance_2task} satisfies the following estimate with high probability:
			\begin{align}\label{lem_cov_shift_eq}
				\bigabs{p^{-1}\bigtr{\Sigma^{(2)} \bigbrace{(n_1 + n_2){\hat{\Sigma}^{-1}} - (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}}} \le  p^{-c_{\varphi}}, %\norm{\Sigma^{(2)}},
			\end{align}
			where $a_1$ and $a_2$ are the solutions of the following self-consistent equations
			\begin{align}
				a_1 + a_2 = 1- \frac{p}{n_1 + n_2},\quad a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
			\end{align}
	\noindent (ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any fixed vector $w\in\real^p$ with unit norm,
			\begin{align}\label{lem_cov_derv_eq}
				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{(n_1+n_2)^2\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - {\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  p^{-c_{\varphi}},
			\end{align}
				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
			\begin{align}\label{eq_a34extra}
				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \ 
				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{align}
\end{theorem}
Part (i) of our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
To see this, when $n_1$ is zero, we solve equation \eqref{eq_a12extra} and obtain $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply these solutions to equation \eqref{lem_cov_shift_eq}.

\paragraph{How does hard parameter sharing scale with sample size and covariate shift?}
One can see that the bias-variance limits depend intricately on both tasks' samples sizes and covariate shift.
Next, we illustrate how varying them impact prediction loss, respectively.
\begin{example}[Sample size ratio]\label{ex_sample_ratio}
	We first consider the impact of varying sample sizes.
	Consider the random-effects model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.

	Applying Theorem \ref{thm_main_RMT} to the above setting, we first solve the self-consistent equations \eqref{eq_a12extra} by using $\lambda_i = 1$ for all $1\le i\le p$.
	This gives us the variance limit
	\[ \frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] = \frac{p}{(n_1 + n_2)(a_1 + a_2)} = \frac{p}{n_1 + n_2 - p}, \]
	since $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$.
	Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
\end{example}

\begin{corollary}\label{cor_MTL_loss}
	In the setting of Example \ref{ex_sample_ratio}, assume that
	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
	(i) both tasks sample sizes are at least $3p$;
	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
%	\be\label{choiceofpara0}
%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
	%\be\label{choiceofpara0}
%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$.
	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
	The prediction loss of hard parameter sharing for task two satisfies that
	\begin{align}\label{cor_MTL_error}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).
	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
	 \end{align}
%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$. We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
	 \end{corollary}

%It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness. We formalize this connection in the above isotropic setting, where we can perform explicit calculations. The prediction loss of MTL has been given in Corollary \ref{cor_MTL_loss}. We can also calculate the prediction loss of STL easily using Fact \ref{lem_minv} (ii). The proof of the following claim will be given in Section \ref{app_iso_cov}.
%\begin{claim} \label{claim_STL_loss}
%Under the above isotropic setting for task two, we have that with high probability,
%\begin{align*}
%	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-\e}\sigma^2 )
%	 \end{align*}
%	 for any constant $\e\in (0,1/2)$.
%\end{claim}
%We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transitions from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.

%\noindent{\bf Varying model distance.}
%With Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss}, it is not hard to see
%One can observe that as we increase the distance $pd^2$ between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL. More precisely, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases, while variance reduction from STL to MTL is $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$.
%Therefore, while the variance of MTL still reduces compared to STL,
%If the bias increases more than the amount of variance reduced, we will observe negative transfer.

%We apply Corollary \ref{cor_MTL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}). We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
%There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
%Figure \ref{fig_model_shift} shows the result.
%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.

%The proof of Proposition \ref{prop_dist_transition} involves two parts.
%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
%The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
%A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
%thus simplifying the general condition in Theorem \ref{thm_main_informal}.

%In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
%More generally, such results are still applicable when all task data are being added simultaneously.
%On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
%For such settings, we have also observed that adding more labeled data from one task does not always help.
%Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.

The above result provides a more concrete interpretation of the bias-variance decomposition, since it depends explicitly on datasets' properties of interest.
The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
As a remark, in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $\hat A$ and $\hat B$. By combining the bias and variance limits, we can also obtain a generalization bound for any local minimizer of $f(A, B)$.
The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.

Next, we illustrate an interesting phenomenon where adding task one's samples helps task two initially, but hurts eventually.
Consider the limiting estimate on the left hand side of equation \eqref{cor_MTL_error}.
We vary sample ratio $n_1 / n_2$ by fixing $n_2$ and increasing $n_1$.
%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
%We describe a sketch of the proof.
The variance term always reduces as $n_1$ increases.
The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
Furthermore, by calculating the derivative of the bias-variance limits with respect to $n_1$, we obtain the following dichotomy (details omitted).
\begin{enumerate}
	\item When $\frac{d^2}{\sigma^2} < \frac{p}{2n_2 - 3p}$, the prediction loss decreases monotonically as $n_1$ increases.
	Intuitively, this regime of $d^2$ always helps task two.
	\item When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one critical point for the derivative being zero, which corresponds to the \textit{optimal sample size ratio}.
\end{enumerate}

\begin{example}[Covariate shift]\label{ex_covshift}
%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
%In general, the covariance matrices of the two tasks may be different such as in text classification.
Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}, which shows that
%in the left hand side of equation \eqref{lem_cov_shift_eq}:
	\[ \bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} \rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}. \]
%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
Hence the variance limit is determined by the spectrum of $M$.% To be clear, for this example we assume that the bias is $0$.

To illustrate the above result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
In particular, when $\lambda = 1$, there is no covariate shift.
As $\lambda$ increases, the severity of covariate shift increases.
We observe the following dichotomy.
\begin{itemize}
	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
\end{itemize}
\end{example}
We explain why the dichotomy happens. The variance estimate for this example is equal to
\begin{align*}
	\frac{p}{2(n_1 + n_2)} f(\lambda), \ \ \text{ where }\ \  f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}.
\end{align*}
Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2 }$, we can obtain that
\begin{align*}
	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1}
	+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1}  - \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
\end{align*}
where $g(\lambda, a_1) > 0$ is a fixed function and can be derived from algebraic calculations (details omitted).
We now show that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, and hence explain the dichonomy.
In fact, if $a_1>a_2$, then the equations in \eqref{eq_a12extra} give that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and one can verify that
$$ 
 \frac{n_1}{n_1 + n_2}=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} 
> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) >\frac{1}{2}.
$$
This implies $n_1>n_2$. Similarly, if $a_1<a_2$, equations in \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$. Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.

\paragraph{Overview of Stieltjes transform.}
For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
The central quantity of interest is the inverse of the sum of two sample covariance matrices $\hat{\Sigma}^{-1}$.
We note that the variance equation $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ is equal to $(n_1 + n_2)^{-1} \bigtr{W^{-1}}$, where $W$ is
\begin{align}\label{eigen2extra}
	W \define \frac{1}{n_1 + n_2}(\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V).
\end{align}
This formulation is helpful because we know that ${Z^{(1)}}^{\top} Z^{(1)}$ and ${Z^{(2)}}^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance, and $U, V$ are both orthonormal matrices.

Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
We briefly describe the key ideas and refer interested readers to classical texts such as  \citet{bai2009spectral,tao2012topics,erdos2017dynamical}.
For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is given by
$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \ \ \text{ for any complex number } z\in \C\setminus [0,\infty).$$
The Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
%To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.

%Recall that  $U\Lambda V^\top$ is the singular value decomposition of $M$, %$\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix,
%It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= (\Sigma^{(2)})^{-1/2} V W^{-1}V^\top (\Sigma^{(2)})^{-1/2}$ and .
Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$. Then it is easy to see that the Stieltjes transform of $\mu$ is equal to
 \[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(W-z\id)^{-1}\right]. \]
Above, the matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
%When $p$ goes to infinity, it is well-known that $m_{\mu}(z)$ converges to a fixed distribution governed by a set of self-consistent equations.
%These self-consistent equations give the asymptotic limit of the trace of $\hat{\Sigma}^{-1}$.
%The above approach applies when $\Sigma^{(2)}$ is isotropic in Theorem \ref{thm_main_RMT}.
%Since our goal is to show the limit of $\tr\left[ (Y - z\id)^{-1}V^{\top}{\Sigma^{(2)}}^{-1}V \right]$ as shown in equation \eqref{eigen2extra}, we study the  $(Y-z\id)^{-1}$.
%Compared to the Stieltjes transform, the resolvent also applies to random matrices.
We will prove the convergence of $W$'s resolvent using the so-called ``local laws'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
%Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf. \cite{Hachem2007deterministic,DS18}).
We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic vectors $v\in \R^p$ with unit norm, 
$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
}$$

%For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
%$$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
%which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.

To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
	\[ \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \]
%}\HZ{what does this trick mean? use less technical words},
%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
%We define the $(n+N)\times (n+N)$ block matrix
 \begin{equation}\label{linearize_block}
    H \define \left( {\begin{array}{*{20}c}
   0 & \AF  \\
   \AF^{\top} & 0
%   {Z^{(2)}V} & 0 & 0
   \end{array}} \right).
 \end{equation}
For this block matrix, we define its resolvent as
$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$ 
%as the resolvent of $H$, 
for any complex value $z\in \mathbb C$.
Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
	\begin{equation*} %\label{green2}
	  G(z) =  \left( {\begin{array}{*{20}c}
			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
  \end{equation*}

\paragraph{Variance asymptotic limit.}
In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
\be \label{defn_piw}
	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
\be
\begin{split}\label{selfomega_a}
	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}},  \\
	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}. 
% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
\end{split}
\ee
The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
%\be\label{ratios}
% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
%\ee
Given this result, we show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since equation \eqref{selfomega_a} reduces to equation \eqref{eq_a12extra}.
Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = \bigtr{W^{-1}} / (n_1 + n_2)$, we get that when $p$ goes to infinity, % the trace of $$ converges to
\begin{align*}
  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}, 
  \end{align*}
%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$. Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$. Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
%\begin{align}
%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
%\end{align}
where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.

\paragraph{Bias asymptotic limit.}
For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
First, we reduce the empirical bias term in equation \eqref{lem_cov_derv_eq} to $W$
\begin{align}\label{calculate G'}
	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
\end{align}
Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
Hence, provided that limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
\begin{align}\label{cal G'0}
	\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
\end{align}
To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of equation \eqref{selfomega_a}.
%\begin{align*}
%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
%\end{align*}
Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(z)}{\dd z}$.
%then taking implicit differentiation of equation \eqref{selfomega_a}
One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations \eqref{eq_a34extra} (details omitted).
Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
%\begin{align}
%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
%\end{align}
%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.

As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.

\paragraph{Schur complement and self-consistent equations.}
We briefly describe how to derive the matrix limit $\Gi(z)$.
First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equation \eqref{selfomega_a}.
On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
A complete proof of Theorem \ref{thm_main_RMT} can be found in Appendix \ref{appendix RMT}.

### 2020-10-20 full_version_1013/sample_paper.tex
start creating arxiv version

\documentclass[twoside]{article}

\usepackage{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
%\usepackage[accepted]{aistats2021}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

% If you set papersize explicitly, activate the following three lines:
%\special{papersize = 8.5in, 11in}
%\setlength{\pdfpageheight}{11in}
%\setlength{\pdfpagewidth}{8.5in}

% If you use natbib package, activate the following three lines:
%\usepackage[round]{natbib}
%\renewcommand{\bibname}{References}
%\renewcommand{\bibsection}{\subsubsection*{\bibname}}

% If you use BibTeX in apalike style, activate the following line:
%\bibliographystyle{apalike}

\begin{document}

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
%\runningtitle{I use this title instead because the last one was very long}

% If your paper is accepted and the number of authors is large, the
% style will print as headings an error message. Use the following
% command to supply a shorter version of the authors names so that
% they can be used as headings (for example, use only the surnames)
%
%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}

\twocolumn[

\aistatstitle{Instructions for Paper Submissions to AISTATS 2021}

\aistatsauthor{ Author 1 \And Author 2 \And  Author 3 }

\aistatsaddress{ Institution 1 \And  Institution 2 \And Institution 3 } ]

\begin{abstract}
  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  both left and right-hand margins. Use 10~point type, with a vertical
  spacing of 11~points. The \textbf{Abstract} heading must be centered,
  bold, and in point size 12. Two line spaces precede the
  Abstract. The Abstract must be limited to one paragraph.
\end{abstract}

\section{GENERAL FORMATTING INSTRUCTIONS}

The camera-ready versions of the accepted papers are 8 pages,
plus any additional pages needed for references.

Papers are in 2 columns with the overall line width of 6.75~inches (41~picas).
Each column is 3.25~inches wide (19.5~picas).  The space
between the columns is .25~inches wide (1.5~picas).  The left margin is 0.88~inches (5.28~picas).
Use 10~point type with a vertical spacing of
11~points. Please use US Letter size paper instead of A4.

Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.
Top rule is 4~points thick and bottom rule is 1~point thick.
Allow 1/4~inch space above and below title to rules.

Author descriptions are center-justified, initial caps.  The lead
author is to be listed first (left-most), and the Co-authors are set
to follow.  If up to three authors, use a single row of author
descriptions, each one center-justified, and all set side by side;
with more authors or unusually long names or institutions, use more
rows.

Use one-half line space between paragraphs, with no indent.

\section{FIRST LEVEL HEADINGS}

First level headings are all caps, flush left, bold, and in point size
12. Use one line space before the first level heading and one-half line space
after the first level heading.

\subsection{Second Level Heading}

Second level headings are initial caps, flush left, bold, and in point
size 10. Use one line space before the second level heading and one-half line
space after the second level heading.

\subsubsection{Third Level Heading}

Third level headings are flush left, initial caps, bold, and in point
size 10. Use one line space before the third level heading and one-half line
space after the third level heading.

\paragraph{Fourth Level Heading}

Fourth level headings must be flush left, initial caps, bold, and
Roman type.  Use one line space before the fourth level heading, and
place the section text immediately after the heading with no line
break, but an 11 point horizontal space.

%%%
\subsection{Citations, Figure, References}

\subsubsection{Citations in Text}

Citations within the text should include the author's last name and
year, e.g., (Cheesman, 1985). 
%Apart from including the author's last name and year, citations can follow any style, as long as the style is consistent throughout the paper.  
Be sure that the sentence reads
correctly if the citation is deleted: e.g., instead of ``As described
by (Cheesman, 1985), we first frobulate the widgets,'' write ``As
described by Cheesman (1985), we first frobulate the widgets.''

The references listed at the end of the paper can follow any style as long as it is used consistently.

%Be sure to avoid
%accidentally disclosing author identities through citations.

\subsubsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Use 8 point type for footnotes. Place the
footnotes at the bottom of the column in which their markers appear,
continuing to the next column if required. Precede the footnote
section of a column with a 0.5 point horizontal rule 1~inch (6~picas)
long.\footnote{Sample of the second footnote.}

\subsubsection{Figures}

All artwork must be centered, neat, clean, and legible.  All lines
should be very dark for purposes of reproduction, and art work should
not be hand-drawn.  Figures may appear at the top of a column, at the
top of a page spanning multiple columns, inline within a column, or
with text wrapped around them, but the figure number and caption
always appear immediately below the figure.  Leave 2 line spaces
between the figure and the caption. The figure caption is initial caps
and each figure should be numbered consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page rather than
splitting the figure and figure caption.
\begin{figure}[h]
\vspace{.3in}
\centerline{\fbox{This figure intentionally left non-blank}}
\vspace{.3in}
\caption{Sample Figure Caption}
\end{figure}

\subsubsection{Tables}

All tables must be centered, neat, clean, and legible. Do not use hand-drawn tables.
Table number and title always appear above the table.
See Table~\ref{sample-table}.

Use one line space before the table title, one line space after the table title,
and one line space after the table. The table title must be
initial caps and each table numbered consecutively.

\begin{table}[h]
\caption{Sample Table Title} \label{sample-table}
\begin{center}
\begin{tabular}{ll}
\textbf{PART}  &\textbf{DESCRIPTION} \\
\hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\section{SUPPLEMENTARY MATERIAL}

If you need to include additional appendices during submission, you can include them in the supplementary material file.
You can submit a single file of additional supplementary material which may be either a pdf file (such as proof details) or a zip file for other formats/more files (such as code or videos). 
Note that reviewers are under no obligation to examine your supplementary material. 
If you have only one supplementary pdf file, please upload it as is; otherwise gather everything to the single zip file.

You must use \texttt{aistats2021.sty} as a style file for your supplementary pdf file and follow the same formatting instructions as in the main paper. 
The only difference is that it must be in a \emph{single-column} format.
You can use \texttt{supplement.tex} in our starter pack as a starting point.
Alternatively, you may append the supplementary content to the main paper and split the final PDF into two separate files.

\section{SUBMISSION INSTRUCTIONS}

To submit your paper to AISTATS 2021, please follow these instructions.

\begin{enumerate}
    \item Download \texttt{aistats2021.sty}, \texttt{fancyhdr.sty}, and \texttt{sample\_paper.tex} provided in our starter pack. 
    Please, do not modify the style files as this might result in a formatting violation.

    \item Use \texttt{sample\_paper.tex} as a starting point.
    \item Begin your document with
    \begin{flushleft}
    \texttt{\textbackslash documentclass[twoside]\{article\}}\\
    \texttt{\textbackslash usepackage\{aistats2021\}}
    \end{flushleft}
    The \texttt{twoside} option for the class article allows the
    package \texttt{fancyhdr.sty} to include headings for even and odd
    numbered pages.
    \item When you are ready to submit the manuscript, compile the latex file to obtain the pdf file.
    \item Check that the content of your submission, \emph{excluding} references, is limited to \textbf{8 pages}. The number of pages containing references alone is not limited.
    \item Upload the PDF file along with other supplementary material files to the CMT website.
\end{enumerate}

\subsection{Camera-ready Papers}

%For the camera-ready paper, if you are using \LaTeX, please make sure
%that you follow these instructions.  
% (If you are not using \LaTeX,
%please make sure to achieve the same effect using your chosen
%typesetting package.)

If your papers are accepted, you will need to submit the camera-ready version. Please make sure that you follow these instructions:
\begin{enumerate}
    %\item Download \texttt{fancyhdr.sty} -- the
    %\texttt{aistats2021.sty} file will make use of it.
    \item Change the beginning of your document to
    \begin{flushleft}
    \texttt{\textbackslash documentclass[twoside]\{article\}}\\
    \texttt{\textbackslash usepackage[accepted]\{aistats2021\}}
    \end{flushleft}
    The option \texttt{accepted} for the package
    \texttt{aistats2021.sty} will write a copyright notice at the end of
    the first column of the first page. This option will also print
    headings for the paper.  For the \emph{even} pages, the title of
    the paper will be used as heading and for \emph{odd} pages the
    author names will be used as heading.  If the title of the paper
    is too long or the number of authors is too large, the style will
    print a warning message as heading. If this happens additional
    commands can be used to place as headings shorter versions of the
    title and the author names. This is explained in the next point.
    \item  If you get warning messages as described above, then
    immediately after $\texttt{\textbackslash
    begin\{document\}}$, write
    \begin{flushleft}
    \texttt{\textbackslash runningtitle\{Provide here an alternative
    shorter version of the title of your paper\}}\\
    \texttt{\textbackslash runningauthor\{Provide here the surnames of
    the authors of your paper, all separated by commas\}}
    \end{flushleft}
    Note that the text that appears as argument in \texttt{\textbackslash
      runningtitle} will be printed as a heading in the \emph{even}
    pages. The text that appears as argument in \texttt{\textbackslash
      runningauthor} will be printed as a heading in the \emph{odd}
    pages.  If even the author surnames do not fit, it is acceptable
    to give a subset of author names followed by ``et al.''

    %\item Use the file sample\_paper.tex as an example.

    \item The camera-ready versions of the accepted papers are 8
      pages, plus any additional pages needed for references.

    \item If you need to include additional appendices,
      you can include them in the supplementary
      material file.

    \item Please, do not change the layout given by the above
      instructions and by the style file.

\end{enumerate}

\subsubsection*{Acknowledgements}
All acknowledgments go at the end of the paper, including thanks to reviewers who gave useful comments, to colleagues who contributed to the ideas, and to funding agencies and corporate sponsors that provided financial support. 
To preserve the anonymity, please include acknowledgments \emph{only} in the camera-ready papers.

\subsubsection*{References}

References follow the acknowledgements.  Use an unnumbered third level
heading for the references section.  Please use the same font
size for references as for the body of the paper---remember that
references do not count against your page length total.

\begin{thebibliography}{}
\setlength{\itemindent}{-\leftmargin}
\makeatletter\renewcommand{\@biblabel}[1]{}\makeatother
\bibitem{} J.~Alspector, B.~Gupta, and R.~B.~Allen (1989).
    \newblock Performance of a stochastic learning microchip.
    \newblock In D. S. Touretzky (ed.),
    \textit{Advances in Neural Information Processing Systems 1}, 748--760.
    San Mateo, Calif.: Morgan Kaufmann.

\bibitem{} F.~Rosenblatt (1962).
    \newblock \textit{Principles of Neurodynamics.}
    \newblock Washington, D.C.: Spartan Books.

\bibitem{} G.~Tesauro (1989).
    \newblock Neurogammon wins computer Olympiad.
    \newblock \textit{Neural Computation} \textbf{1}(3):321--323.
\end{thebibliography}

\end{document}

### 2020-10-20 full_version_1013/setup.tex
start creating arxiv version

--- 2020-10-15 arxiv/setup.tex
@@
 
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
+We assume that there are multiple datasets that all follow (potentially different) linear models.
+In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
+
+We study a hard parameter sharing architecture to learn jointly from multiple datasets.
+In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a separate output layer $A_i \in \real^r$ for every task $i$.
 Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
+For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size, $X^{(i)} \in \real^{n_i \times p}$ denote its feature covariates, and $Y^{(i)} \in \real^{n_i}$ denote all the labels.
 %The width of $B$, denoted by $r$, plays an important role in regularization.
@@
 %For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
+Let $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
+We study the following optimization objective.
 %	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
@@
 %	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
 \begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
+			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2.
 \end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
+Given a solution $(\hat{A}, \hat{B})$ to the above optimization problem, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the hard parameter sharing (HPS) estimator for task $i$.
+Some critical questions are:
 (i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
@@
 
-\textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \citet{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning, but increases bias.
+\paragraph{Main results.}
+Our first result (Theorem \ref{thm_many_tasks}) applies to the multi-label prediction setting where all datasets have the same features, and we want to make multiple predictions (see e.g.
+\cite{hsu2009multi}).
+We analyze the global minimizer of $f(A, B)$, and provide a sharp generalization bound on its (out-of-sample) prediction loss for any task.
+This case is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
+We show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition.
+Our results imply that hard parameter sharing helps by reducing variance compared to single-task learning, but hurts by increasing bias.
+Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and population covariance matrices.
+We analyze the local minimizers of $f(A, B)$ and provide a sharp generalization bound on both tasks' prediction loss.
+Despite its simplicity, we show several interesting phenomena by varying sample sizes and covariate shifts in this setting.
+See Figure \ref{fig_intro_sample_size} for an illustration.
 
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we no longer have a characterization of $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-%\begin{enumerate}
-
-\textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \citet{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance, and is generally high when the latter is large.
-
-\textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help to reduce another task's loss.
+Consequently, using our precise loss estimates, we observe qualitative properties of hard parameter sharing for varying datasets' properties.
+\begin{enumerate}
+	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
+	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL, a phenomenon that \citet{ZSSGM18} has observed empirically.
+	Our results further imply that HPS's sample efficiency depends on model-specific variance vs.
+noise variance.
+It is generally high when the noise variance is large compared to model-specific variance across different tasks.
+	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always help to reduce another task's loss.
 In a simplified setting, we find that the task loss either decreases first before increasing afterwards, or decreases monotonically depending on how fast the bias increases.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as the sample sizes of all tasks increase, thus do not apply for different sample size ratios.
-
-\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
+These two trends result from different tradeoffs between increasing bias and decreasing variance.
+	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
 For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
 Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
-%\end{enumerate}
+\end{enumerate}
 
@@
 
+There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
+We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and its population version.
+The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
+Using recently developed techniques from random matrix theory \cite{Anisotropic}, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
+Theorem \ref{thm_main_RMT}(i)).
+% Moreover, we can obtain a sharp bound on the concentration error.
+% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}. 
+%\HZ{add several sentences on the technical insight} 
+One limitation of our analysis is that for two tasks with different sample sizes, there is an extra error term in the prediction loss of hard parameter sharing (cf.
+equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
+This requires studying the spectrum of non-symmetric random matrices, which is an intriguing open question (see Section \ref{sec_conclude} for more discussion).
 % plus an identity matrix,  due to lack of freeness
@@
 
-Finally, we discuss the practical implications of our work.
+Finally, we discuss the practical implications of work.
 Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
@@
 We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
-
-\textbf{Proof techniques.}
-There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
-The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-Using recently developed techniques from random matrix theory, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
-Theorem \ref{thm_main_RMT}).
-% Moreover, we can obtain a sharp bound on the concentration error.
-% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
-%\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided important initial insights and it is an interesting question to tighten our result.
 
@@
 
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \citet{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \citet{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
+There is a large body of both classical and recent works on multi-task learning.
+We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,R17,ZY17,V20}.
+The early work of \citet{B00,BS03,M06} have sought for a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+An influential paper by \citet{BBCK10} provides uniform convergence bound that combines multiple datasets in certain settings.
 One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \citet{B00,MPR16}.
@@
 Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, which is a recent development in the random matrix theory literature.
-In the single task case, \citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
+\citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
 \citet{Anisotropic} later extended this result to arbitrary covariance setting.
@@
 These techniques provide almost sharp convergence rates to the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covarite shifts).
+To the best of our knowledge, we are not aware of any previous results about the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
 
@@
 One closely related work is \citet{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
+\citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
 %Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
@@
 
-\textbf{Organizations.}
+\smallskip
+\noindent\textbf{Organizations.}
 The rest of this paper is organized as follows.
@@
 In Section \ref{sec_diff}, we present our technical results that describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in simulations and real world classification tasks.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
+In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in both simulations and a real world classification task.
+In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.
 
-\textbf{Notations.}
+\paragraph{Notations.}
 %Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
@@
 %Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
+For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
+Let $\lambda_1(X) \ge \lambda_2(X) \ge \cdots \ge \lambda_{p\wedge n}(X)$ denote the singular values of $X$.
+Let $X^+$ denote the Moore-Penrose psuedoinverse.
 We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.

### 2020-10-20 arxiv_full_version/conclusions.tex
arxiv version

--- 2020-10-15 arxiv/conclusions.tex
@@
-\vspace{-0.06in}
 \section{Conclusions and Discussions}\label{sec_conclude}
-\vspace{-0.06in}
 
@@
 We validated our theory and conducted further studies on text classification tasks.
-We describe open questions for future work.
-First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-Second, it would be interesting to extend our result to classification problems such as logistic regression.
-%First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+We describe several open questions for future work.
+%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
+%Second, it would be interesting to extend our result to classification problems such as logistic regression.
+First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
+This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
 %FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-%The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
+The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
 %but its singular values will follow a different distribution since the matrix is not symmetric.
  %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-%Second, it would be interesting to extend our results to classification problems.
-%Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \citet{sur2019modern}.
-%An interesting question is to study logistic regression in a multiple-sample setting.
+Second, it would be interesting to extend our results to classification problems.
+Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \citet{sur2019modern}.
+An interesting question is to study logistic regression in a multiple-sample setting.

### 2020-10-20 arxiv_full_version/diff_cov.tex
arxiv version

--- 2020-10-16 arxiv/diff_cov.tex
@@
 \begin{align*}
-	X^{(1)} &= Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p}, \text{ and} \\
-	X^{(2)} &= Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
+	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p}, \text{ and}
+	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
 \end{align*}
@@
 \begin{align}
-	\hat{\beta}_2^{\MTL} &= {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \ \ \text{ where } \nonumber \\
-	\hat{\Sigma} &= {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
+	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
+	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
 \end{align}
@@
 \begin{align}
-	& \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}  \nonumber \\
+	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
 	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
@@
 	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have that
-	the variance equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
+
+\noindent(i) The variance equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
 			\begin{align}\label{lem_cov_shift_eq}
-				\resizebox{0.869\hsize}{!}{%
-				$\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{ {\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{n_1+n_2} }}}
-				\le p^{-c_{\varphi}}$
-				}%
+				\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{ {\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{n_1+n_2} }}}
+				\le p^{-c_{\varphi}},
 			\end{align}
@@
 			\begin{align}
-				&a_1 + a_2 = 1- \frac{p}{n_1 + n_2},\label{eq_a12extra000}\\
-				&a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
+				a_1 + a_2 = 1- \frac{p}{n_1 + n_2},
+				a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
+			\end{align}
+
+\noindent(ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
+			\begin{align}\label{lem_cov_derv_eq}
+				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - \frac{1}{(n_1+n_2)^2}{\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
+			\end{align}
+				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+			\begin{align}\label{eq_a34extra}
+				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \
+				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
+%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+%				= b_0.
 			\end{align}
 \end{theorem}
-Due to space limit, we defer the bias limit result to Appendix \eqref{appendix RMT}.
+%Due to space limit, we defer the bias limit result to Appendix \eqref{appendix RMT}.
 Our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
-To see this, when $n_1$ is zero, we solve equations \eqref{eq_a12extra000} and  \eqref{eq_a12extra} to obtain that $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply them to equation \eqref{lem_cov_shift_eq}.
+To see this, when $n_1$ is zero, we solve equation \eqref{eq_a12extra} to obtain that $a_1 = 0$ and $a_2 = (n_2-p) / n_2$, and apply them to equation \eqref{lem_cov_shift_eq}.
 For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
@@
 	\begin{align*}
-		&\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}] \\
-		=& \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
+		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
+		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
 		= \frac{p}{n_1 + n_2 - p},
 	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra000}.
+	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
 	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit (details omitted).
+	Similarly, we can calculate the bias limit.
 	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
@@
 	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	  & \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \nonumber\\
-	\le& \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
+	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
+	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
@@
 	 \end{corollary}
-
-%It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
-We formalize this connection in the above isotropic setting, where we can perform explicit calculations.
-The prediction loss of MTL has been given in Corollary \ref{cor_MTL_loss}.
-We can also calculate the prediction loss of STL easily using Fact \ref{lem_minv} (ii).
-The proof of the following claim will be given in Section \ref{app_iso_cov}.
-%\begin{claim} \label{claim_STL_loss}
-%Under the above isotropic setting for task two, we have that with high probability,
-%\begin{align*}
-%	 L(\hat{\beta}_2^{\STL}) = \frac{\sigma^2}{ \rho_2-1}  +\OO(p^{-\e}\sigma^2 )
-%	 \end{align*}
-%	 for any constant $\e\in (0,1/2)$.
-%\end{claim}
-%We now discuss two implications of Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss} regarding the information transfer in MTL: the transitions from positive transfer to negative transfer with respect to varying model distance and varying sample ratio, respectively.
-
-%\noindent{\bf Varying model distance.}
-%With Corollary \ref{cor_MTL_loss} and Claim \ref{claim_STL_loss}, it is not hard to see
-%One can observe that as we increase the distance $pd^2$ between $\beta_1$ and $\beta_2$, there is a transition from positive transfer to negative transfer in MTL.
-More precisely, the bias term $  pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}$ of MTL increases as the distance between $\beta_1$ and $\beta_2$ increases, while variance reduction from STL to MTL is $\frac{\sigma^2}{ \rho_2-1}  -\frac{\sigma^2}{\rho_1+\rho_2-1}$.
-%Therefore, while the variance of MTL still reduces compared to STL,
-%If the bias increases more than the amount of variance reduced, we will observe negative transfer.
-
-%We apply Corollary \ref{cor_MTL_loss} to the parameter setting of Figure \ref{fig_model_shift} (the details are left to Appendix \ref{app_synthetic}).
-We can see that our result is able to predict positive or negative transfer  accurately and matches the empirical curve.
-%There are several unexplained observations near the transition threshold $0$, which are caused by the concentration error on the right-hand side of \eqref{cor_MTL_error}.
-%We fix the target task and vary the source task, in particular the parameter $d$ which determines $\norm{\beta_1 - \beta_2}$.
-%Figure \ref{fig_model_shift} shows the result.
-%We observe that Proposition \ref{prop_dist_transition} explains most of the observations in Figure \ref{fig_model_shift}.
-
-%The proof of Proposition \ref{prop_dist_transition} involves two parts.
-%First, in equation \eqref{eq_te_var}, the positive variance reduction effect scales with $n_1 = \rho_1 p$, the number of source task data points.
-%Second, we show that the negative effect of model-shift bias scales with $pd^2$, which is the expectation of $\norm{\beta_1 - \beta_2}^2$.
-%The proof of Proposition \ref{prop_dist_transition} can be found in Appendix \ref{app_proof_31}.
-%A key part of the analysis shows that $\hat{W}_1 / \hat{W}_2$ is roughly equal to one in the isotropic model,
-%thus simplifying the general condition in Theorem \ref{thm_main_informal}.
-
-%In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the sample sizes are equal for all tasks \cite{B00,M06,MPR16}.
-%More generally, such results are still applicable when all task data are being added simultaneously.
-%On the other hand, uneven sample sizes between different tasks (or even dominating tasks) have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
-%For such settings, we have also observed that adding more labeled data from one task does not always help.
-%Our theory accurately predicts a curious phenomenon, where increasing the sample size of the source task results in negative transfer!
-%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
 
@@
 By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-%\begin{enumerate}
-
-(i) When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
+\begin{enumerate}
+	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
 	Intuitively, this regime of $d^2$ always helps task two.
-
-(ii) When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
+	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
 	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-%\end{enumerate}
+\end{enumerate}
 
@@
 We observe the following dichotomy.
-%\begin{itemize}
-
-(i) If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-
-(ii) If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-%\end{itemize}
+\begin{enumerate}
+	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
+	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
+\end{enumerate}
 \end{example}
@@
 We claim that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, which explains the dichonomy.
-In fact, if $a_1>a_2$, then equation \eqref{eq_a12extra000} gives that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and equation \eqref{eq_a12extra} gives that
+In fact, if $a_1>a_2$, then equation \eqref{eq_a12extra} gives that $a_1> \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$, and equation \eqref{eq_a12extra} gives that
 \begin{align*}
@@
 
-\textbf{Proof overview of Theorem \ref{thm_main_RMT}.}
+\paragraph{Proof overview of Theorem \ref{thm_main_RMT}.}
 For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
@@
 
-\begin{figure*}[!t]
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
-		\caption{Example \ref{ex_same_cov}}
-		\label{fig_same_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
-		\caption{Example \ref{ex_sample_ratio}}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
-		\caption{Example \ref{ex_covshift}}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
-	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
-%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
-	\label{fig_model_shift_phasetrans}
-\end{figure*}
-
 %Recall that  $U\Lambda V^\top$ is the singular value decomposition of $M$, %$\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix,
@@
 We prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
-The complete proof is provided in Section \ref{appendix RMT}.
 %Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.
@@
 %which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
+We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic unit vectors $v\in \R^p$,
+$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
+}$$
+
+To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
+	\be\label{defn AF} \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \ee
+%}\HZ{what does this trick mean? use less technical words},
+%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
+Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
+%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
+%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
+%We define the $(n+N)\times (n+N)$ block matrix
+ \begin{equation}\label{linearize_block}
+    H \define \left( {\begin{array}{*{20}c}
+   0 & \AF  \\
+   \AF^{\top} & 0
+%   {Z^{(2)}V} & 0 & 0
+   \end{array}} \right).
+ \end{equation}
+For this block matrix, we define its resolvent as
+$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$
+%as the resolvent of $H$,
+for any complex value $z\in \mathbb C$.
+Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
+	\begin{equation} \label{green2}
+	  G(z) =  \left( {\begin{array}{*{20}c}
+			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
+      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
+		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
+  \end{equation}
+
+\paragraph{Variance asymptotic limit.}
+In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
+\be \label{defn_piw}
+	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
+where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
+\be\label{selfomega_a}
+\begin{split}
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %\label{selfomega_a000} \\
+	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
+% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
+\end{split}
+\ee
+The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
+%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
+%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
+%\be\label{ratios}
+% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
+%\ee
+Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
+First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since the equations in \eqref{selfomega_a} reduce to equation \eqref{eq_a12extra} when $z=0$.
+Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
+Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, % the trace of $$ converges to
+\begin{align*}
+  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
+  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}},
+  \end{align*}
+%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
+%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
+%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
+Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
+Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
+%\begin{align}
+%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
+%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
+%\end{align}
+where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
+%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
+
+\paragraph{Bias asymptotic limit.}
+ For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
+First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %$W$
+\begin{align}\label{calculate G'}
+	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
+\end{align}
+Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
+Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
+Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
+\begin{align}\label{cal G'0}
+	\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
+\end{align}
+To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of the system of equations \eqref{selfomega_a}.
+%\begin{align*}
+%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
+%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
+%\end{align*}
+Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(0)}{\dd z}$.
+%then taking implicit differentiation of equation \eqref{selfomega_a}
+One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
+Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
+%\begin{align}
+%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
+%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
+%\end{align}
+%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
+
+As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
+This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.
+
+\paragraph{Schur complement and self-consistent equations.}
+First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
+By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
+Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
+We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
+On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
+Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
+We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
+A complete proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{sec pf RMTlemma}-Appendix \ref{sec entry}. %Appendix \ref{appendix RMT}.

### 2020-10-20 arxiv_full_version/experiments.tex
arxiv version

--- 2020-10-15 arxiv/experiments.tex
@@
-\section{Simulation Studies}\label{sec_simulation}
+\section{Numerical Results}
+
+\subsection{Simulation Studies}\label{sec_simulation}
 
@@
 
-\textbf{Sample efficiency.}
+\begin{figure*}[!t]
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
+		\caption{Example \ref{ex_same_cov}}
+		\label{fig_same_cov}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
+		\caption{Example \ref{ex_sample_ratio}}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
+		\caption{Example \ref{ex_covshift}}
+		\label{fig_covariate}
+	\end{subfigure}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
+	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
+	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
+%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
+	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
+	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
+Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
+	\label{fig_model_shift_phasetrans}
+\end{figure*}
+
+\paragraph{Sample efficiency.}
 First, we validate the result of Example \ref{ex_same_cov}.
-Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task   from $400$ to $2000$.
+Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
 In all the parameter settings, our results estimate the empirical losses accurately.
@@
 
-\textbf{Sample size ratio.}
+\paragraph{Sample size ratio.}
 Second, we validate the result of Example \ref{ex_sample_ratio}.
@@
 We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
-The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
+The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
 We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
-On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases faster.
+On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
 Intuitively, this is because bias increases less for smaller $d^2$.
@@
 
-\textbf{Covariate shift.}
+\paragraph{Covariate shift.}
 Finally, we validate the result of Example \ref{ex_covshift}.

### 2020-10-20 arxiv_full_version/intro.tex
arxiv version

@@
 \begin{abstract}
-	\vspace{-0.1in}
 	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
@@
 This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-	\vspace{-0.15in}
 \end{abstract}
 
-\vspace{-0.1in}
 \section{Introduction}\label{sec_introduction}
@@
 	\label{fig_intro_sample_size}
-	\vspace{-0.07in}
 \end{figure*}

### 2020-10-20 arxiv_full_version/main.tex
arxiv version

--- 2020-08-09 arxiv/main.tex
@@
 %\usepackage[nonatbib]{neurips_2020}
-\usepackage{fullpage}
+
+\def\shownotes{0}
+\usepackage{natbib}
+\setcitestyle{authoryear,open={(},close={)}}
+\renewcommand{\cite}{\citep}
+\usepackage[export]{adjustbox}
+\usepackage[margin=1in]{geometry}
+%\usepackage{fullpage}
 \usepackage{subfloat}
@@
 
-% Squished list environment to save space
-\newcommand{\squishlist}{
-\begin{list}{$\bullet$}
-{ \setlength{\itemsep}{0pt}
-\setlength{\parsep}{2pt}
-\setlength{\topsep}{2pt}
-\setlength{\partopsep}{0pt}
-\setlength{\itemindent}{2pt}
-\setlength{\leftmargin}{0.5cm}
-% \setlength{\labelwidth}{1em}
-}
-}
-\newcommand{\squishend}{\end{list}}
+\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
 
-\setlength{\parskip}{0.3em}
+%\setlength{\parskip}{0.3em}
+
+%\title{Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions}
+\title{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}
+\usepackage{authblk}
+\author[$\dagger$]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu.}}
+\author[$\ddagger$]{Fan Yang\samethanks}
+\author[$\mathsection$]{Sen Wu}
+\author[$\ddagger$]{Weijie S. Su}
+\author[$\mathsection$]{Christopher R\'e}
+\affil[$\dagger$]{Khoury College of Computer Sciences, Northeastern University}
+\affil[$\ddagger$]{Department of Statistics, Wharton School, University of Pennsylvania}
+\affil[$\mathsection$]{Department of Computer Science, Stanford University}
 
 \begin{document}
-
-\title{Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions}
 \maketitle
-%\date{{\ddmmyyyydate\today} at \currenttime}
 
@@
 \input{setup}
-\input{transfer}
+%\input{examples}
+\input{same_cov}
+\input{diff_cov}
 %\input{extensions}
+%\input{algorithm}
 \input{experiments}
-\input{related}
+\input{experiments_text}
+\input{conclusions}
+\bibliographystyle{plainnat}
+\bibliography{rf,ref_mtl}
+\appendix
 
-\bibliographystyle{unsrt}
-\bibliography{rf,ref_mtl}
-
-\appendix
-\input{proofs_sec3}
-\input{proof_main}
+\input{proof_same_cov}
+\input{proof_gaussian_case}
+\input{proof_appd}
 \input{proof_examples}
-\input{proof_extension}
-\input{proof_appd}
-\input{app_exp}
+\input{tools}
 \end{document}

### 2020-10-20 arxiv_full_version/proof_gaussian_case.tex
arxiv version

--- 2020-10-20 arxiv/proof_gaussian_case.tex
@@
 \section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
-We first state the asymptotic limit for the bias equation \eqref{eq_bias_2task}.
+%We first state the asymptotic limit for the bias equation \eqref{eq_bias_2task}.
 
-\begin{theorem}\label{thm_main_RMT_app}
-	Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$.
-	In the setting of Theorem \ref{thm_main_RMT}, the bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability for any unit vector $w\in S$:
-			\begin{align}\label{lem_cov_derv_eq}
-				\bigabs{w^{\top} \Sigma^{(1)} \bigbrace{\hat{\Sigma}^{-1} \Sigma^{(2)} \hat{\Sigma}^{-1} - \frac{1}{(n_1+n_2)^2}{\Sigma^{(2)}}^{-1/2} V {\frac{a_3 \Lambda^2 + (a_4 + 1)\id}{(a_1 \Lambda^2 + a_2\id)^2}} V^{\top} {\Sigma^{(2)}}^{-1/2}} \Sigma^{(1)} w} \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-			\end{align}
-				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-			\begin{align}\label{eq_a34extra}
-				a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \ \
-				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{align}
-\end{theorem}
+%\begin{theorem}\label{thm_main_RMT_app}
+%
+%	In the setting of Theorem \ref{thm_main_RMT},
+%\end{theorem}
 %For the rest of this section, we present the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}
 
-\paragraph{Proof Overview (cont'd).}
-We continue the proof overview of Theorem \ref{thm_main_RMT} and \ref{thm_main_RMT_app} from Section \ref{sec_diff}.
+%\paragraph{Proof Overview (cont'd).}
+%We continue the proof overview of Theorem \ref{thm_main_RMT} and \ref{thm_main_RMT_app} from Section \ref{sec_diff}.
 %Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
-Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$.
-We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic unit vectors $v\in \R^p$,
-$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
-}$$
+%Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$.
 
-To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
-	\be\label{defn AF} \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \ee
-%}\HZ{what does this trick mean? use less technical words},
-%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
-Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
-%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
-%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
-%We define the $(n+N)\times (n+N)$ block matrix
- \begin{equation}\label{linearize_block}
-    H \define \left( {\begin{array}{*{20}c}
-   0 & \AF  \\
-   \AF^{\top} & 0
-%   {Z^{(2)}V} & 0 & 0
-   \end{array}} \right).
- \end{equation}
-For this block matrix, we define its resolvent as
-$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$
-%as the resolvent of $H$,
-for any complex value $z\in \mathbb C$.
-Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
-	\begin{equation} \label{green2}
-	  G(z) =  \left( {\begin{array}{*{20}c}
-			(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
-      \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
-		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
-  \end{equation}
-
-\paragraph{Variance asymptotic limit.}
-In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
-\be \label{defn_piw}
-	\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
-where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
-\be\label{selfomega_a}
-\begin{split}
-	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %\label{selfomega_a000} \\
-	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
-% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
-\end{split}
-\ee
-The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
-%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
-%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
-%\be\label{ratios}
-% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
-%\ee
-Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
-First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since the equations in \eqref{selfomega_a} reduce to equations \eqref{eq_a12extra000} and \eqref{eq_a12extra} when $z=0$.
-Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
-Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, % the trace of $$ converges to
-\begin{align*}
-  \bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
-  &=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}},
-  \end{align*}
-%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
-%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
-%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
-Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
-Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
-%\begin{align}
-%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
-%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
-%\end{align}
-where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
-%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
-
-\paragraph{Bias asymptotic limit.}
- For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
-First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %$W$
-\begin{align}\label{calculate G'}
-	(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
-\end{align}
-Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
-Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
-Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
-\begin{align}\label{cal G'0}
-	\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
-\end{align}
-To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of the system of equations \eqref{selfomega_a}.
-%\begin{align*}
-%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
-%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
-%\end{align*}
-Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(0)}{\dd z}$.
-%then taking implicit differentiation of equation \eqref{selfomega_a}
-One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
-Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
-%\begin{align}
-%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
-%\end{align}
-%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
-
-As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
-This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.
-
-%\paragraph{Schur complement and self-consistent equations.}
-%
-%First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
-%By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
-%Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
-%We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
-%On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
-%Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
-%We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
-%A complete proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{sec pf RMTlemma}-Appendix \ref{sec entry}. %Appendix \ref{appendix RMT}.
-
-\paragraph{How to derive the matrix limit?}
 We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.

### 2020-10-20 arxiv_full_version/proof_same_cov.tex
arxiv version

--- 2020-10-20 arxiv/proof_same_cov.tex
@@
 \section{Missing Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_error_same_cov}
-
-	We fill in missing details in the proof. Our first claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
-	\begin{claim}\label{claim_opt_dist}
-		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
-		In the setting of Theorem \ref{thm_many_tasks}, we have that
-		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
-				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r({B^{\star}}^{\top}\Sigma B^{\star})- \lambda_{r+1}({B^{\star}}^{\top}\Sigma B^{\star})}. \]
-	\end{claim}
-	The proof of the above claim is based on the following characterization.
-
-	\begin{claim}\label{lem_exp_opt}
-		In the setting of Theorem \ref{thm_many_tasks}, we have that
-		\begin{align}
-			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r). \label{eq_gA}
-		\end{align}
-		As a result, the minimum of $\ex{g(A)}$, denoted by $A^{\star}{A^\star}^\top$, is the best rank-$r$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star}$.
-	\end{claim}
-
-	 One can see that the expected optimization objective also admits a nice bias-variance decomposition.
-	Furthermore, its minimum only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.
-
-	The next piece of our proof deals with the prediction loss of hard parameter sharing.
-	\begin{claim}\label{claim_pred_err}
-		In the setting of Theorem \ref{thm_many_tasks},
-		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
-		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
-		\begin{align*}
-			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
-			\le  n^{-1/4} \left(L(B^{\star} \hat{a}_i) + \sigma^2  \cdot\|\hat a_i\|^2\right) .
-		\end{align*}
-	\end{claim}
-	%The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
-	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
-	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a multiplicative error of order $n^{-1/4}$.
-		%Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$. With this estimate, we can bound the difference
-		%$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
-		%Combined together, our proof is complete.
-		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
-		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
-		Combined together, we obtain the difference if we replace $\hat{a}_i$ with $a^{\star}_i$ in Claim \ref{claim_pred_err}, and the proof is complete.
-	\end{proof}
 

### 2020-10-20 arxiv_full_version/same_cov.tex
arxiv version

@@
 
-\textbf{Setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose features are all denoted by $X \in \real^{n \times p}$.
+\medskip
+\noindent\textbf{Setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose features are all denoted by $X \in \real^{n \times p}$.
 The label vector of the $i$-th task follows a linear model $Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}$.
 We assume:
-
-\vspace{-0.05in}
-(i) $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-
-\vspace{-0.05in}
-(ii) every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-
-%\end{itemize}
+\begin{enumerate}
+	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
+\end{enumerate}
 For an estimator $\hat{\beta}_i$ of task $i$, we are interested in its (out-of-sample) prediction loss
@@
 	\begin{align*}
-		&\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}} \\
-		\le& n^{-\frac{c_{\varphi}}2} \cdot \frac{t \bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2}^2} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}.
+		\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}}
+		\le n^{-\frac{c_{\varphi}}2} \cdot \frac{t \bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2}^2} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}.
 		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
@@
 I will check the proof to see whether $C_2 =  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}^2$ or $C_1\cdot \sigma\norm{\Sigma^{1/2} B^{\star}}$?}
-\textbf{Comparison to single-task learning (STL).}
+\noindent\textbf{Comparison to single-task learning (STL).}
 Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
@@
 \end{fact}
-\textit{Remark.} The above result has a long history in random matrix theory.
+\noindent\textit{Remark.} The above result has a long history in random matrix theory.
 For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
@@
 \begin{align*}
-	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} &= \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p} \\
-	&= \frac{1}{t}\frac{\sigma^2 p}{n - p},
+	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
+	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
 \end{align*}
@@
 
-\textbf{Comparison to single-task learning.}
+\noindent\textbf{Comparison to single-task learning.}
 Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
@@
 %\begin{enumerate}
-
-(i) The prediction loss of HPS is smaller than STL if and only if ${d^2}{} < \frac{\sigma^2 p}{n - p}$, that is, the ``task-specific variance'' of $\beta^{(i)}$ is smaller than the ``noise variance''.
-
-(iii) HPS requires at most $p + \frac{n - p}{t - (t - 1)\frac{d^2 (n - p)}{\sigma^2 p}}$ samples that is less than $n$ samples to get comparable loss to STL.
+\begin{enumerate}
+	\item The prediction loss of HPS is smaller than STL if and only if ${d^2}{} < \frac{\sigma^2 p}{n - p}$, that is, the ``task-specific variance'' of $\beta^{(i)}$ is smaller than the ``noise variance''.
+	\item HPS requires at most $p + \frac{n - p}{t - (t - 1)\frac{d^2 (n - p)}{\sigma^2 p}}$ samples that is less than $n$ samples to get comparable loss to STL.
 	This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
-
-(ii) When ${d^2}{} < \frac{\sigma^2 p}{n - p}$, increasing $r$ does not help.
+	\item When ${d^2}{} < \frac{\sigma^2 p}{n - p}$, increasing $r$ does not help.
 	To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-%\end{enumerate}
+\end{enumerate}
 %\FY{I think these two facts probably need more clarification?}
 
-\textbf{Proof overview.} The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
+\noindent\textbf{Proof overview.} The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
 	In the setting of this theorem, the minimization problem \eqref{eq_mtl} becomes
@@
 	\begin{align}\label{eq_mtl_output_layer}
-		\resizebox{0.869\hsize}{!}{%
-		$g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.$
-		}%
+		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
 	\end{align}
@@
 	The proof can be found in Section \ref{app_proof_error_same_cov}.
+	We fill in missing details in the proof. Our first claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
+	\begin{claim}\label{claim_opt_dist}
+		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
+		In the setting of Theorem \ref{thm_many_tasks}, we have that
+		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
+				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r({B^{\star}}^{\top}\Sigma B^{\star})- \lambda_{r+1}({B^{\star}}^{\top}\Sigma B^{\star})}. \]
+	\end{claim}
+	The proof of the above claim is based on the following characterization.
+
+	\begin{claim}\label{lem_exp_opt}
+		In the setting of Theorem \ref{thm_many_tasks}, we have that
+		\begin{align}
+			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r). \label{eq_gA}
+		\end{align}
+		As a result, the minimum of $\ex{g(A)}$, denoted by $A^{\star}{A^\star}^\top$, is the best rank-$r$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star}$.
+	\end{claim}
+
+	 One can see that the expected optimization objective also admits a nice bias-variance decomposition.
+	Furthermore, its minimum only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.
+
+	The next piece of our proof deals with the prediction loss of hard parameter sharing.
+	\begin{claim}\label{claim_pred_err}
+		In the setting of Theorem \ref{thm_many_tasks},
+		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
+		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
+		\begin{align*}
+			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
+			\le  n^{-1/4} \left(L(B^{\star} \hat{a}_i) + \sigma^2  \cdot\|\hat a_i\|^2\right) .
+		\end{align*}
+	\end{claim}
+	%The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
+	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
+	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
+		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a multiplicative error of order $n^{-1/4}$.
+		%Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$. With this estimate, we can bound the difference
+		%$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
+		%Combined together, our proof is complete.
+		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
+		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
+		Combined together, we obtain the difference if we replace $\hat{a}_i$ with $a^{\star}_i$ in Claim \ref{claim_pred_err}, and the proof is complete.
+	\end{proof}

### 2020-10-20 arxiv_full_version/setup.tex
arxiv version

--- 2020-10-16 arxiv/setup.tex
@@
 
-\textbf{Main results.}
+\medskip
+\noindent\textbf{Main results.}
 Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
@@
 Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-%\begin{enumerate}
-
-\textit{Sample efficiency (Example \ref{ex_same_cov})}:
+\begin{itemize}
+	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
 	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \citet{ZSSGM18} has observed empirically.
@@
 
-\textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
+	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
 In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
@@
 
-\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
+	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
 For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
@@
 See our discussion of proof techniques below for details.
-%\end{enumerate}
+\end{itemize}
 
@@
 
-\textbf{Proof techniques.}
+\medskip
+\noindent\textbf{Proof techniques.}
 There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
@@
 
-\textbf{Notations.}
+\medskip
+\noindent\textbf{Notations.}
 %Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.

### 2020-10-20 arxiv_full_version/main.tex
add acknowledgement

@@
 \documentclass{article}
-
-%\usepackage[nonatbib]{neurips_2020}
 
@@
 
+\usepackage{dsfont}
+
 \newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
 
-%\setlength{\parskip}{0.3em}
-
-%\title{Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions}
-\title{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}
 \usepackage{authblk}
-\author[$\dagger$]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu.}}
-\author[$\ddagger$]{Fan Yang\samethanks}
-\author[$\mathsection$]{Sen Wu}
-\author[$\ddagger$]{Weijie S. Su}
-\author[$\mathsection$]{Christopher R\'e}
-\affil[$\dagger$]{Khoury College of Computer Sciences, Northeastern University}
-\affil[$\ddagger$]{Department of Statistics, Wharton School, University of Pennsylvania}
-\affil[$\mathsection$]{Department of Computer Science, Stanford University}
 
 \begin{document}
+
+\title{\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}}
+\vspace{0.15in}
+\author[1]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu.}}
+\author[2]{Fan Yang\samethanks}
+\author[3]{Sen Wu}
+\author[2]{Weijie S. Su}
+\author[3]{Christopher R\'e}
+\vspace{0.15in}
+\affil[1]{Khoury College of Computer Sciences, Northeastern University}
+\affil[2]{Department of Statistics, Wharton School, University of Pennsylvania}
+\affil[3]{Department of Computer Science, Stanford University}
+
 \maketitle
@@
 \input{conclusions}
+
+\subsection*{Acknowledgements:}
+Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
+HZ and SW's contributions were in part supported by Wharton Dean's Fund for Postdoctoral Research.
+
 \bibliographystyle{plainnat}

### 2020-10-20 arxiv_full_version/proof_examples.tex
appendix

@@
 %&+ A^2[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-	=& ((x-1)^2\kappa^2 + (x^2+1)d^2){p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+	=& [(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot {p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
 \end{align}
@@
 \begin{align}\label{h'(A)2}
-	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] < 0,
+	h'(x)\le [-2(1-x)\kappa^2 +2 xd^2] \cdot p^{-1} \tr\left[\left(x^2[(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1}\right)^{-1}\right] < 0.
 \end{align}
@@
 Similar to the analysis of $g(x)$, we expand $L(\hat{\beta}_2^{\MTL})$ into the sum of 15 terms, and bound the concentration error of each term similar to $h_1(x), \dots, h_6(x)$.
-For example, for the leading term $\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)}$, using
-Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
+For example, for the leading term 
+\[\hat x^2 (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(1)})^\top X^{(1)}\wt\beta^{(1)},\] 
+using Lemma \ref{largedeviation} and the operator norm bounds, we obtain the following estimate w.h.p.
 \begin{align*}
@@
 \begin{align*}
- \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  & \le p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
-&\lesssim p^{c}\cdot \sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
-&\lesssim p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
+& \left| (\wt \beta^{(1)})^\top (X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \epsilon^{(2)}\right|  \\
+  \le & p^c \cdot \sigma\sqrt{p^{-1}d^2} \cdot \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \|_F \\
+ \lesssim & p^{c}\cdot \sigma d \cdot  \|(X^{(1)})^\top X^{(1)} \hat \Sigma(\hat x)^{-1}  \Sigma^{(2)} \hat \Sigma(\hat x)^{-1}  (X^{(2)})^\top  \| \\
+ \lesssim & p^{-1/2+c}\sigma d\le p^{-1/2+c}(\sigma^2+ d^2).
 \end{align*}
@@
 \begin{align*}
-	\left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right| &\le   \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
+	& \left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right| \\
+	  \le &  \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
 	&+\OO\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).

### 2020-10-21 arxiv_full_version/diff_cov.tex
arxiv full version

@@
 \begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p}, \text{ and}
+	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
 	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
@@
 We introduce a key quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and as we show below, the trace of $\hat{\Sigma}^{-1}$ has an intricate dependence on the spectrum of $M$.
-
 %Let $U\Lambda V^\top$ denote the SVD of $M$ and
@@
 	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have that
+	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
 
@@
 \begin{align*}
-	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}} \\
-	&= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
+	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
+	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
 \end{align*}
 %As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit is determined by the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
-To illustrate the above result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
+Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
+To illustrate the result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
 In particular, when $\lambda = 1$, there is no covariate shift.
@@
 \end{example}
-
-We explain why the dichotomy happens. The variance limit in this example is equal to
+\noindent We explain why the dichotomy happens. The variance limit in this example is equal to
 $\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
@@
 }$$
-
 To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
@@
 Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
-Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies that
+Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies
 \begin{align}\label{cal G'0}
@@
 One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
-Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the asymptotic limit of the bias term.
+Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the bias limit.
 %\begin{align}
@@
 As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
-This is why we consider $W$'s resolvent for a general $z$. %as opposed to the Stieljes transform of its empirical spectral distribution.
+This is why we consider $W$'s resolvent for a general $z$ (as opposed to the Stieljes transform of its empirical spectral distribution discussed earlier).
 
@@
 We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
-A complete proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{sec pf RMTlemma}-Appendix \ref{sec entry}. %Appendix \ref{appendix RMT}.
+The proof of Theorem \ref{thm_main_RMT} is shown in Appendix \ref{appendix RMT}. %Appendix \ref{appendix RMT}.

### 2020-10-21 arxiv_full_version/experiments_text.tex
arxiv version
arxiv full version

--- 2020-10-18 arxiv/experiments_text.tex
@@
-\section{Further Studies on Text Classification Tasks}\label{sec_text}
+\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
 
@@
 \end{itemize}
-For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
+If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
 %See Algorithm \ref{alg_inc_train} for a complete description for two tasks.

### 2020-10-21 arxiv_full_version/main.tex
appendix
arxiv full version

@@
 
-\def\shownotes{0}
+\def\shownotes{1}
 \usepackage{natbib}
@@
 \vspace{0.15in}
-\author[1]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu.}}
+\author[1]{Hongyang R. Zhang\thanks{Equal contribution. Correspondence to hrzhang@northeastern.edu or fyang75@wharton.upenn.edu.}}
 \author[2]{Fan Yang\samethanks}
 \author[3]{Sen Wu}
-\author[2]{Weijie S. Su}
+\author[2]{Weijie J. Su}
 \author[3]{Christopher R\'e}
@@
 Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
-HZ and SW's contributions were in part supported by Wharton Dean's Fund for Postdoctoral Research.
+HZ and WS's contributions were in part supported by Wharton Dean's Fund for Postdoctoral Research.
+We gratefully acknowledge the support of DARPA under Nos.
+FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.
+U54EB020405 (Mobilize), NSF under Nos.
+CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No.
+N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, [STANFORD/STUDENT-SPECIFIC FELLOWSHIPS], and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys.
+The U.S.
+Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.
+Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S.
+Government.
 

### 2020-10-21 arxiv_full_version/same_cov.tex
arxiv full version

@@
 %	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-	For any task $i = 1, 2, \dots, t$, with high probability over the randomness of the input, the prediction loss of $\hat{\beta}_i^{\MTL}$ satisfies that
+	For any task $i = 1, 2, \dots, t$, with high probability over the randomness of the input, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that
 	\begin{align*}

### 2020-10-21 arxiv_full_version/proof_examples.tex
edit

@@
 \begin{align}
-			&\left|h_4(x)\right| \nonumber\\
+			\left|h_4(x)\right|
 	\le& p^{c}\cdot \sigma \cdot \sqrt{b / p}\left\| \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right) X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
@@
 Our proof involves two steps.
-First, we will show that $\abs{x^{\star} - 1} \le d^2 / \kappa^2$.
-Second, we will use Claim \ref{claim_largedev1} to show that the global minimizer of $g(x)$ and $h(x)$ are close to each other.
+First, we  show that $\abs{x^{\star} - 1} \le d^2 / \kappa^2$.
+Second, we use Claim \ref{claim_largedev1} to show that the global minimizer of $g(x)$ and $h(x)$ are close to each other.
 %Using Lemma \ref{largedeviation} again, we can simplify equation \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
@@
 Recall that the hard parameter sharing estimator $\hat{\beta}_2^{\MTL}$ is equal to $\hat{B} \hat{A}_2$.
-Using the local optimility condition for $\hat{B}$, we obtain the predication loss of HPS as follows
+Using the local optimality condition for $\hat{B}$, we obtain the predication loss of HPS:
 \begin{align}
@@
 			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi})\ee
-with high probability.
-
+Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
+\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
 For the bias term, since the spectrum of $(X^{(1)})^{\top} X^{(1)}$ is tightly concentrated by Fact \ref{fact_minv}, we have that
@@
 \begin{align*}
-	& \left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right| \\
-	  \le &  \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
-	&+\OO\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
+	 \left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right|&
+	  \le   \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
+	&\hspace{-2cm}+\OO\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
 \end{align*}

### 2020-10-22 arxiv_full_version/diff_cov.tex
polish typo

@@
 The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we study how having different sample sizes and different covariance matrices impact hard parameter sharing.
+This section discusses how having different sample sizes and different covariance matrices impact hard parameter sharing.
 %The different covariates case differs from the same covariates case in two aspects.
 %First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-The setting where covariates differ across tasks is often called ``covariate shift''.
+The setting where covariates differ across tasks is often known as ``covariate shift''.
 
@@
 Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
+We focus on the two-task case to better understand the impact of having different sample sizes and covariates.
 Let $n_1, n_2$ denote task one  and two's sample size, respectively.
@@
 Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
+Without loss of generality, we consider task two's prediction loss, and the same result applies to task one.
 We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \citet{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
+When $r = 1$, $B$ is a vector, and $A_1, A_2$ are both scalars.
 To motivate our study, we consider a special case where $A_1=A_2=1$.
@@
 Our main result in this section characterizes the asymptotic bias-variance limits in the high-dimensional setting.
-Intuitively, the spectrum of $\hat{\Sigma}^{-1}$ (and hence its trace) not only depends on both tasks' sample sizes, but also depends on the ``alignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
+Intuitively, the spectrum of $\hat{\Sigma}^{-1}$ (and hence its trace) not only depends on both tasks' sample sizes but also depends on the ``alignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
 However, capturing this intuition quantitatively turns out to be technically challenging.
 %The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-We introduce a key quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and as we show below, the trace of $\hat{\Sigma}^{-1}$ has an intricate dependence on the spectrum of $M$.
+We introduce a critical quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and as we show below, the trace of $\hat{\Sigma}^{-1}$ has an intricate dependence on the spectrum of $M$.
 %Let $U\Lambda V^\top$ denote the SVD of $M$ and
@@
 
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
+In the above inequality, the $d^2$ scaling term is the bias limit, and the $\sigma^2$ scaling term is the variance limit.
 This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
@@
 %Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
+The variance limit in equation \eqref{cor_MTL_error} obviously decreases with $n_1$.
 It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.

### 2020-10-22 arxiv_full_version/same_cov.tex
polish typo

@@
 %We provide a sharp generalization error bound of hard parameter sharing estimators.
-In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
+This section describes our result that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition when all tasks have the same features.
 %\FY{Is it should be "same covariate" or "same covariates"?}
@@
 Recall that $r$ is the width of $B$.
-We focus on cases where $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \citet{WZR20}).
+We focus on cases where $r < t$, because otherwise, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \citet{WZR20}).
 
 Our first main result shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ which contains all the linear model parameters.
+To formalize this geometric intuition, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$, which contains all the linear model parameters.
 Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is task labels' ``covariance''):\footnote{To ensure that $A^{\star}$ is unique, we assume that $\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.}
@@
 %	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-On the other hand, the bias always increases.
+One direct implication of our result is the variance always decreases when compared to STL, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
+On the other hand,  bias always increases.
 
@@
 Obviously, the concentration error decreases with $n$.
+Therefore, we consider the bias and variance, respectively.
 First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
-It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
+It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which we define formally below.
 
@@
 \noindent\textit{Remark.} The above result has a long history in random matrix theory.
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
+For a multivariate Gaussian random matrix, this result follows from the classical work for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For non-Gaussian random matrices, this result can be derived via the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
 Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
@@
 
-Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
+Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, which is $L(B^{\star} a^{\star}_i)$.
 We illustrate the bias through a random-effect model, which has been studied for a single-task case \cite{dobriban2020wonder}.

### 2020-10-22 arxiv_full_version/setup.tex
arxiv full version
polish typo

@@
 \noindent\textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \citet{hsu2009multi}).
+Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (e.g.
+\citet{hsu2009multi}).
 We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
@@
 For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
+We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by more than half compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
 
@@
 We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
+See Section \ref{sec_conclude} for more discussions of the technical challenge.
 
@@
 In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation}, we validate our results in simulations.
+In Sections \ref{sec_exp}, we validate our results in simulations and conduct further studies on text classification tasks.
 In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{sec_text} describes our study on text classification tasks.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
+Section \ref{app_proof_error_same_cov} presents the missing proofs of Section \ref{sec_same}.
+Section \ref{appendix RMT} and \ref{app_iso_cov} show the missing proofs of Section \ref{sec_diff}.
 
@@
 We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
+We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C  f(n)$ for large enough $n$.
 %We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.

### 2020-10-22 abridged/diff_cov.tex
reorg

--- 2020-10-16 arxiv/diff_cov.tex
@@
 				$\bigabs{\bigtr{\Sigma^{(2)} \bigbrace{ {\hat{\Sigma}^{-1}} - \frac{(a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}{n_1+n_2} }}}
-				\le p^{-c_{\varphi}}$
+				\le p^{-c_{\varphi}}$,
 				}%
@@
 	  & \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \nonumber\\
-	\le& \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
+	\le& \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
 	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\

### 2020-10-22 abridged/experiments_text.tex
reorg

--- 2020-10-18 arxiv/experiments_text.tex
@@
 \paragraph{Sample size ratio.}
-First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
+First, we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
 In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
@@
 We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
+First, we conduct multi-task training over all the $15$ two-task pairs from the six datasets.
 We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
@@
 Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
+We find that when averaged over all the $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
 %Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
@@
 We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
+We set $\tau$ to be the average test accuracy of all the six tasks obtained using standard round-robin training.
 We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.

### 2020-10-22 abridged/same_cov.tex
reorg

--- 2020-10-20 arxiv_full_version/same_cov.tex
@@
 
-\medskip
-\noindent\textbf{Setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose features are all denoted by $X \in \real^{n \times p}$.
+\textbf{Setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose features are all denoted by $X \in \real^{n \times p}$.
 The label vector of the $i$-th task follows a linear model $Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}$.
 We assume:
-\begin{enumerate}
-	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-\end{enumerate}
+
+\vspace{-0.05in}
+(i) $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+
+\vspace{-0.05in}
+(ii) every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
+
+%\end{itemize}
 For an estimator $\hat{\beta}_i$ of task $i$, we are interested in its (out-of-sample) prediction loss
@@
 	\begin{align*}
-		\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}}
-		\le n^{-\frac{c_{\varphi}}2} \cdot \frac{t \bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2}^2} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}.
+		&\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star}a_i^{\star}) - \sigma^2 \norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top}X)^{-1}}} \\
+		\le& n^{-\frac{c_{\varphi}}2} \cdot \frac{t \bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2}^2} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}.
 		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
@@
 I will check the proof to see whether $C_2 =  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}^2$ or $C_1\cdot \sigma\norm{\Sigma^{1/2} B^{\star}}$?}
-\noindent\textbf{Comparison to single-task learning (STL).}
+\textbf{Comparison to single-task learning (STL).}
 Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
@@
 \end{fact}
-\noindent\textit{Remark.} The above result has a long history in random matrix theory.
+\textit{Remark.} The above result has a long history in random matrix theory.
 For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
+For non-Gaussian random matrices, this result can be derived via the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}).
 Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
@@
 \begin{align*}
-	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
-	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
+	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} &= \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p} \\
+	&= \frac{1}{t}\frac{\sigma^2 p}{n - p},
 \end{align*}
@@
 
-\noindent\textbf{Comparison to single-task learning.}
+\textbf{Comparison to single-task learning.}
 Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
@@
 %\begin{enumerate}
-\begin{enumerate}
-	\item The prediction loss of HPS is smaller than STL if and only if ${d^2}{} < \frac{\sigma^2 p}{n - p}$, that is, the ``task-specific variance'' of $\beta^{(i)}$ is smaller than the ``noise variance''.
-	\item HPS requires at most $p + \frac{n - p}{t - (t - 1)\frac{d^2 (n - p)}{\sigma^2 p}}$ samples that is less than $n$ samples to get comparable loss to STL.
+
+(i) The prediction loss of HPS is smaller than STL if and only if ${d^2}{} < \frac{\sigma^2 p}{n - p}$, that is, the ``task-specific variance'' of $\beta^{(i)}$ is smaller than the ``noise variance''.
+
+(iii) HPS requires at most $p + \frac{n - p}{t - (t - 1)\frac{d^2 (n - p)}{\sigma^2 p}}$ samples that is less than $n$ samples to get comparable loss to STL.
 	This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
-	\item When ${d^2}{} < \frac{\sigma^2 p}{n - p}$, increasing $r$ does not help.
+
+(ii) When ${d^2}{} < \frac{\sigma^2 p}{n - p}$, increasing $r$ does not help.
 	To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-\end{enumerate}
+%\end{enumerate}
 %\FY{I think these two facts probably need more clarification?}
 
-\noindent\textbf{Proof overview.} The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
+\textbf{Proof overview.} The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
 	In the setting of this theorem, the minimization problem \eqref{eq_mtl} becomes
@@
 	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
+		\resizebox{0.869\hsize}{!}{%
+		$g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.$
+		}%
 	\end{align}
@@
 	The proof can be found in Section \ref{app_proof_error_same_cov}.
-	We fill in missing details in the proof. Our first claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
-	\begin{claim}\label{claim_opt_dist}
-		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
-		In the setting of Theorem \ref{thm_many_tasks}, we have that
-		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
-				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r({B^{\star}}^{\top}\Sigma B^{\star})- \lambda_{r+1}({B^{\star}}^{\top}\Sigma B^{\star})}. \]
-	\end{claim}
-	The proof of the above claim is based on the following characterization.
-
-	\begin{claim}\label{lem_exp_opt}
-		In the setting of Theorem \ref{thm_many_tasks}, we have that
-		\begin{align}
-			\exarg{\set{\varepsilon^{(j)}}_{j=1}^t, X}{g(A)} = n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r). \label{eq_gA}
-		\end{align}
-		As a result, the minimum of $\ex{g(A)}$, denoted by $A^{\star}{A^\star}^\top$, is the best rank-$r$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star}$.
-	\end{claim}
-
-	 One can see that the expected optimization objective also admits a nice bias-variance decomposition.
-	Furthermore, its minimum only depends on the bias term since the variance term is fixed, and the minimizer of the bias term is precisely $A^{\star} {A^{\star}}^{\top}$.
-
-	The next piece of our proof deals with the prediction loss of hard parameter sharing.
-	\begin{claim}\label{claim_pred_err}
-		In the setting of Theorem \ref{thm_many_tasks},
-		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
-		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
-		\begin{align*}
-			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
-			\le  n^{-1/4} \left(L(B^{\star} \hat{a}_i) + \sigma^2  \cdot\|\hat a_i\|^2\right) .
-		\end{align*}
-	\end{claim}
-	%The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
-	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
-	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
-		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a multiplicative error of order $n^{-1/4}$.
-		%Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$. With this estimate, we can bound the difference
-		%$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
-		%Combined together, our proof is complete.
-		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
-		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
-		Combined together, we obtain the difference if we replace $\hat{a}_i$ with $a^{\star}_i$ in Claim \ref{claim_pred_err}, and the proof is complete.
-	\end{proof}

### 2020-10-22 abridged/tools.tex
reorg

--- 2020-10-20 arxiv/tools.tex
@@
 For any deterministic vector $v\in \R^p$, we have that w.h.p.
-\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2.\ee
+\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le 2n^{1-c_\varphi} \|v\|^2.\ee
 \end{corollary}
@@
 We centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$
-It suffices to show that 
+Let $\e$ be a sufficiently small fixed constant.
+To prove the result, it suffices to show that
 \be\label{show_whZ}
@@
 \ee 
-This is because provided with equation \eqref{show_whZ}, using \eqref{meanshif222} we can get that
+This is because provided with equation \eqref{meanshif222} and \eqref{show_whZ}, we can get that
 $$ \left|\|\wt Zv\|^2- n\|v\|^2\right| \le n^{1/2 + \e} Q\|v\|^2,$$
-which implies \eqref{Zv_cor} for any fixed value $c_{\varphi}$ within $(0, \frac{\varphi - 4}{2\varphi})$.
-
-To prove equation \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$.
-Moreover, using equation \eqref{eq largedev10} we get that with overwhelming probability
-$$ |(\wh Zv)_i| \le n^\e Q\max_{1\le i\le p}|v_i| + n^\e \|v\| . $$
-Together with the trivial bound $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $Q$.
-Then applying equation \eqref{eq largedev20}, we get that
-$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\le n^{1/2+\e} Q  \|v\|^2 .
+which implies the desired our (recall that $c_{\varphi} < 1/2 - \e$).
+To prove equation \eqref{show_whZ}, we first show that for any $i = 1, 2, \dots, n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ is at most $2n^{\e} Q$.
+Since $\wh{Z} v$ consists of i.i.d random variables with mean zero and variance $\|v\|^2$,
+using equation \eqref{eq largedev10} from Lemma \ref{largedeviation}, we get that with overwhelming probability
+$$ |(\wh Zv)_i| \le n^\e Q\max_{1\le i\le p}|v_i| + n^\e \|v\| \le 2n^{\e} Q. $$
+Hence, $\frac{(\wh Zv)}{\|v\|}$ consists of i.i.d random variables with mean zero, unit variance, and bounded support $2n^{\e}Q$.
+Applying equation \eqref{eq largedev20}, we get that
+$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\le 2n^{1/2+2\e} Q  \|v\|^2 .
  $$
-This concludes equation \eqref{show_whZ}.
+Hence the proof is complete.
  \end{proof}

### 2020-10-22 arxiv/experiments_text.tex
reorg

@@
 Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
-%The question is to predict positive or negative sentiment expressed in the text.
 Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
@@
 
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-%There are 14 diseases (tasks) for every image that we would like to predict.
-%We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-%We evaluate three model choices.
-%\textit{Predicting transfer effect via STL results.}
-%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-%A common challenge in the study of MTL is that the results can be hard to understand.
-%It is difficult to predict when MTL performs well without running extensive trials.
-%Our insight is that we can use STL results to help understand MTL results.
-%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
-
 \paragraph{Sample size ratio.}
-First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
+First, we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
+In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially but hurts eventually.
 On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
 We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.
 
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
+These examples and Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
 Concretely, here is one implementation of this idea.
-%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
 \begin{itemize}
@@
 	\item During every stage, we train for $T$ epochs using only the $S$ batches.
-If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
-%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
+If the validation accuracy drops compared to the previous round's result or reaches the desired threshold $\tau$, we terminate.
 \end{itemize}
-For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
-%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
+If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
 The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
+For example, if the process terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
 
-%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-%\squishlist
-%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-%TREC is less similar to MR because the task is about question types.
-%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
 We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
+First, we conduct multi-task training over all the $15$ two-task pairs from the six datasets.
 We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
@@
 Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
-%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
+We find that when averaged over all the $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
 Second, we conduct multi-task training on all six datasets jointly.
 We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
+We set $\tau$ to be the average test accuracy of all the six tasks obtained using standard round-robin training.
 We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
-%As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-%	\begin{subfigure}[b]{0.33\textwidth}
-%		\centering
-%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-%		\caption{Task similarity}
-%		\label{fig_ab_sim}
-%	\end{subfigure}%
-%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c)
-%	Note: (S) denotes the source task and (T) denotes the target task.}
-
-%\begin{minipage}[t]{.58\textwidth}
-%	\vspace{-0.1in}
-%	\centering
-%  \begin{tabular}{c c c c c}
-%	\toprule
-%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%		& Precision &  Recall & Precision &  Recall \\
-%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
-		% 0.3 & 1.000 & 0.004 &     - &     - \\
-%	\bottomrule
-%	\end{tabular}
-%	\vspace{0.1in}
-%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-%	\label{tab:mtl_better_than_stl}
-%\end{minipage}%
-%\quad
 
@@
 This module is then trained together with $B$ and the output layers. We refer to \citet{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
 
@@
 
-%\begin{figure}[!t]
-%	\centering
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-%		\caption{Averaged over all 16 task pairs}
-%		\label{fig_ab_cov}
-%	\end{subfigure}\hfill
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{An example task pair}
-%		\label{fig_cov_a}
-%	\end{subfigure}
-%	\caption{ (TREC and CR)}
-%\end{figure}
-
-%\textbf{Further results of the covariance alignment procedure.}
-%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
-%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
-%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
-%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
-%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
-%We leave this question for future work.
-%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
-
-%\begin{figure}[!h]
-%	\centering
-%	\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{Task pair TREC and CR}
-%		\label{fig_cov_a}
-%	\end{subfigure}\hfill
-%		\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-%		\caption{Task pair MR and SST}
-%			\label{fig_cov_b}
-%	\end{subfigure}
-%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
-%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
-%	\label{fig_covariate_app}
-%\end{figure}
-
-\begin{figure}%[!t]
+\begin{figure}%
 	\begin{subfigure}[t]{0.5\textwidth}
@@
 	\label{fig_text}
-%	\begin{minipage}[t]{0.4\textwidth}
-%		\centering
-%		\vspace{0pt}
-%		\begin{tabular}{c c c}
-%		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-%		& all tasks & w/o TREC \\
-%		\midrule
-%		{\bf MLP}  & 31\% & 29\% \\
-%		{\bf LSTM} & 35\% & 34\% \\
-%		{\bf CNN}  & 30\% & 28\% \\
-%		\bottomrule
-%		\end{tabular}
-%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
-%		\label{tab:taskonomy}
-%	\end{minipage}
 \end{figure}
-
-%\begin{algorithm}[!t]
-%	\caption{A progressive training schedule given two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
-%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, A_2$ optimized for task $2$.
-%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}

### 2020-10-22 arxiv/main.tex
sec E
restructure
update ref
revise
edit
reorg
response
wip
edits
separate
add
finish sec 5
start sec 3/6
merge examples with Section 3 and 4
section 5 wip
fix missing ref
move exp text
various edits to polish draft

--- 2020-08-09 arxiv/main.tex
@@
 
-%\usepackage[nonatbib]{neurips_2020}
-\usepackage{fullpage}
+\def\shownotes{0}
+\usepackage{natbib}
+\setcitestyle{authoryear,open={(},close={)}}
+\renewcommand{\cite}{\citep}
+\usepackage[export]{adjustbox}
+\usepackage[margin=1in]{geometry}
 \usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
+\usepackage[T1]{fontenc}    %
+\usepackage{nicefrac}       %
+\usepackage{microtype}      %
 \usepackage{graphicx}
@@
 \usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[utf8]{inputenc} %
 \usepackage{caption,subcaption}
-%\usepackage{breqn}
 
-% Squished list environment to save space
-\newcommand{\squishlist}{
-\begin{list}{$\bullet$}
-{ \setlength{\itemsep}{0pt}
-\setlength{\parsep}{2pt}
-\setlength{\topsep}{2pt}
-\setlength{\partopsep}{0pt}
-\setlength{\itemindent}{2pt}
-\setlength{\leftmargin}{0.5cm}
-% \setlength{\labelwidth}{1em}
-}
-}
-\newcommand{\squishend}{\end{list}}
+\usepackage{dsfont}
 
-\setlength{\parskip}{0.3em}
+\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
+
+\usepackage{authblk}
 
@@
 
-\title{Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions}
+\title{\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}}
+\vspace{0.15in}
+\author[1]{Hongyang R.
+Zhang\thanks{HZ and FY contributed equally to the theoretical results.
+SW conducted the experimental analysis.
+Correspondence to hrzhang@northeastern.edu or fyang75@wharton.upenn.edu.}}
+\author[2]{Fan Yang\samethanks}
+\author[3]{Sen Wu\samethanks}
+\author[2]{Weijie J. Su}
+\author[3]{Christopher R\'e}
+\vspace{0.15in}
+\affil[1]{Khoury College of Computer Sciences, Northeastern University}
+\affil[2]{Department of Statistics, The Wharton School, University of Pennsylvania}
+\affil[3]{Department of Computer Science, Stanford University}
+
 \maketitle
-%\date{{\ddmmyyyydate\today} at \currenttime}
 
@@
 \input{setup}
-\input{transfer}
-%\input{extensions}
+\input{same_cov}
+\input{diff_cov}
 \input{experiments}
-\input{related}
+\input{experiments_text}
+\input{conclusions}
 
-\bibliographystyle{unsrt}
+\subsection*{Acknowledgements:}
+Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
+HZ and WS's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
+We gratefully acknowledge the support of DARPA under Nos.
+FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.
+U54EB020405 (Mobilize), NSF under Nos.
+CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No.
+N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys.
+The U.S.
+Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.
+Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S.
+Government.
+
+\bibliographystyle{plainnat}
 \bibliography{rf,ref_mtl}
+\appendix
 
-\appendix
-\input{proofs_sec3}
-\input{proof_main}
+\input{proof_same_cov}
+\input{proof_gaussian_case}
+\input{proof_appd}
 \input{proof_examples}
-\input{proof_extension}
-\input{proof_appd}
-\input{app_exp}
+\input{tools}
 \end{document}

### 2020-10-22 old/arxiv_full_version/setup.tex
reorg

--- 2020-10-22 arxiv_full_version/setup.tex
@@
 One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \citet{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
+Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least logartithmic factors of the dimension.
 

### 2020-10-22 old/full_version_1013/conclusions.tex
reorg

--- 2020-10-20 arxiv_full_version/conclusions.tex
@@
 
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on text classification tasks.
+This work proposed a formal study of a widely used hard paramaeter sharing approach in high-dimensional linear regression, where the sample size and feature dimension increase at a fixed ratio.
+We provided tight generalization bounds that scale with dataset properties such as their sample sizes and covariate shifts.
+Based on these bounds, we analyzed the impact of varying sample sizes and covariate shifts on the prediction loss of hard parameter sharing.
+Our work rigorously explains several empirical phenomena such as sample efficiency and negative transfer related to these dataset properties.
+We validated our results and conducted further studies on a real world classification task.
+
 We describe several open questions for future work.
-%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-%Second, it would be interesting to extend our result to classification problems such as logistic regression.
-First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic random matrices.
+This requires studying the asymptotic distribution of the {singular values} of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
 %FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
@@
 Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \citet{sur2019modern}.
+Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \cite{sur2019modern}.
 An interesting question is to study logistic regression in a multiple-sample setting.

### 2020-10-22 old/writeup/app_exp.tex
reorg

--- 2020-08-09 arxiv/app_exp.tex
@@
 		\centering
-		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
+		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
 		\caption{Task pair TREC and CR}
@@
 		\centering
-		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
+		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
 		\caption{Task pair MR and SST}

### 2020-10-22 old/writeup/proof_extension.tex
reorg

--- 2020-06-10 writeup/proof_extension.tex
@@
-%\section{Proofs for the Extended Results}
-
-\section{Proof of Theorem \ref{thm_many_tasks}}\label{app_proof_many_tasks}
+\section{Proof for Many Tasks}\label{app_proof_many_tasks}
 
@@
 	with high probability, where we used Lemma \ref{lem_minv} in the last step. Similar, by Lemma \ref{lem_minv} we have
-	$$\te(\hat{\beta}_t^{\MTL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
+	$$\te(\hat{\beta}_t^{\STL})=\frac{\sigma^2}{\rho-1} \cdot \left( 1+\oo(1)\right).$$
 Combining the above two estimates, we conclude the proof.

### 2020-10-22 src/.venv/lib/python3.6/__future__.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/__future__.py

### 2020-10-22 src/.venv/lib/python3.6/_bootlocale.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/_bootlocale.py

### 2020-10-22 src/.venv/lib/python3.6/_collections_abc.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/_collections_abc.py

### 2020-10-22 src/.venv/lib/python3.6/_weakrefset.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/_weakrefset.py

### 2020-10-22 src/.venv/lib/python3.6/abc.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/abc.py

### 2020-10-22 src/.venv/lib/python3.6/base64.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/base64.py

### 2020-10-22 src/.venv/lib/python3.6/bisect.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/bisect.py

### 2020-10-22 src/.venv/lib/python3.6/codecs.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/codecs.py

### 2020-10-22 src/.venv/lib/python3.6/copy.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/copy.py

### 2020-10-22 src/.venv/lib/python3.6/enum.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/enum.py

### 2020-10-22 src/.venv/lib/python3.6/genericpath.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/genericpath.py

### 2020-10-22 src/.venv/lib/python3.6/heapq.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/heapq.py

### 2020-10-22 src/.venv/lib/python3.6/imp.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/imp.py

### 2020-10-22 src/.venv/lib/python3.6/io.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/io.py

### 2020-10-22 src/.venv/lib/python3.6/keyword.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/keyword.py

### 2020-10-22 src/.venv/lib/python3.6/locale.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/locale.py

### 2020-10-22 src/.venv/lib/python3.6/posixpath.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/posixpath.py

### 2020-10-22 src/.venv/lib/python3.6/re.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/re.py

### 2020-10-22 src/.venv/lib/python3.6/reprlib.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/reprlib.py

### 2020-10-22 src/.venv/lib/python3.6/sre_compile.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/sre_compile.py

### 2020-10-22 src/.venv/lib/python3.6/sre_constants.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/sre_constants.py

### 2020-10-22 src/.venv/lib/python3.6/stat.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/stat.py

### 2020-10-22 src/.venv/lib/python3.6/struct.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/struct.py

### 2020-10-22 src/.venv/lib/python3.6/tempfile.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/tempfile.py

### 2020-10-22 src/.venv/lib/python3.6/token.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/token.py

### 2020-10-22 src/.venv/lib/python3.6/tokenize.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/tokenize.py

### 2020-10-22 src/.venv/lib/python3.6/warnings.py

@@ -1,0 +1,1 @@
+/Users/hongyang/anaconda3/lib/python3.6/warnings.py

### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
response

\documentclass{article}

\usepackage{aistats2021_author_response}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % define colors in text
\usepackage{xspace}         % fix spacing around commands

\begin{document}

	We thank all the reviewers for providing detailed comments.
	We are more than happy to address the weaknesses pointed out by the reviewers and improve our work.
	In this response, we first clarify several high-level questions and then respond to each reviewer's comments.

	\textbf{Clarifying the setting of Section 3.} Both R2 and R3 pointed out that our covariate shift analysis only applies to two tasks where the rank of the shared matrix $B$ is $1$.
	While this setting is only a special case of the two-layer linear neural net formulation, it corresponds to the important setting of transfer learning (specifically solving $f(B) = ||X^{(1)} B - Y^{(1)}||_F^2 + ||X^{(2)} B - Y^{(2)}||_F^2$).
	The transfer learning problem with two tasks is well motivated from a practical perspective, and to the best of our knowledge, we are the first work to study the transfer learning setting of linear regression under covariate shift.
	We think it is an excellent research question to study the multiple task setting under covariate shift.
	Several recent work has made progress in the multiple linear regression setting, including (Li et al., 2020), (Chen et al., 2020 arXiv:2009.11282), (Kong et al., 2020 arXiv:2002.08936).
	However, they all assume that the feature vectors are drawn from an isotropic Gaussian distribution.
	Therefore, while we acknowledge that our analysis only applies to two tasks, we believe our work has made an important contribution toward studying multi-task learning under covariate shift.

	\textbf{The gap between the theory and experiment in Fig 2.b?} Thanks to R2 and R3 for pointing out this gap.
	We have improved our result so that the theory matches experiment in Fig 2.b (see Figure \ref{fig_update} for the updated result).
	DESCRIBE THE IDEA.

	\textbf{Can any of our results in Section 3 be obtained from a straightforward application of a generalized MP theorem?}
	Thanks for raising this question. R3 is correct that the variance equation in Corollary 3.3 can be obtained from the MP law.
	However, to the best of our knowledge, the bias equation in Corollary 3.3 and Example 3.4 cannot be obtained from the MP law.
	ADD COMMENT TO THAT PAPER.

	\textbf{Response to R1.}

	\textbf{Response to R2.}

	\textbf{Response to R3.}

	\textbf{Response to R5.}
\end{document}

### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
update

@@
 	While this setting is only a special case of the two-layer linear neural net formulation, it corresponds to the important setting of transfer learning (specifically solving $f(B) = ||X^{(1)} B - Y^{(1)}||_F^2 + ||X^{(2)} B - Y^{(2)}||_F^2$).
-	The transfer learning problem with two tasks is well motivated from a practical perspective, and to the best of our knowledge, we are the first work to study the transfer learning setting of linear regression under covariate shift.
+	The transfer learning problem with two tasks is well motivated from a practical perspective, and to the best of our knowledge, our work provides the first upper bound in the transfer learning setting of linear regression under covariate shift.
 	We think it is an excellent research question to study the multiple task setting under covariate shift.
@@
 
-	\textbf{Can any of our results in Section 3 be obtained from a straightforward application of a generalized MP theorem?}
+	\textbf{Can any of the results in Section 3 be obtained from a straightforward application of a generalized MP theorem?}
 	Thanks for raising this question. R3 is correct that the variance equation in Corollary 3.3 can be obtained from the MP law.

### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
update;

@@
 
-	\textbf{Response to R1.}
+	\textbf{Response to R1.} Please see our response to the detailed comments.
+	\textbf{(8-i)} Yes, the variance decreases because $||{a_i^{\star}}||^2 \le 1$.
+	The bias increases because the bias of single-task learning (the ordinary least squares solution) is zero when $n > p$.
+	\textbf{(8-ii)} By lower order terms, we mean any term that vanishes to zero when $p$ increases to infinity.
+	\textbf{(8-iii)} The sum of $||{a_i^{\star}}||^2$ is one (or $r$ in general), because $A^{\star}$ is a (subspace) projection matrix.
+	\textbf{(8-iv)} %We want to point out that the problem setting in Section 3 is in general non-convex. Therefore, it is not possible to explicitly solve $A_1, A_2$ without making further assumptions.
+	We can assume knowledge of $A_1 \in \mathbb R, A_2 \in \mathbb R$ without loss of generality since they can be solved numerically by using a subset of training data points (e.g. $\sqrt{p}$ suffices).
+	The sampling error of the numerical solution is $O(\exp(-p))$.
 
-	\textbf{Response to R2.}
+	\textbf{Response to R2.} We thank the reviewer for providing detailed feedback.
+	Response to questions under Section 8.
+	\textbf{(i)}
+	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning.
+	Hence, studing this regime is problematic without adding explicit regularization or implicit algorithmic biases.
+	These are interesting research questions, but beyond the scope of our work.
+	\textbf{(ii)}
+
+	Response to questions under Section 3.
+	\textbf{(1-i)}
 

### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex

@@
 \usepackage{xspace}         % fix spacing around commands
+\usepackage{macro_math}
+\usepackage{macro_fan}
 
@@
 	\textbf{(8-ii)} By lower order terms, we mean any term that vanishes to zero when $p$ increases to infinity.
-	\textbf{(8-iii)} The sum of $||{a_i^{\star}}||^2$ is one (or $r$ in general), because $A^{\star}$ is a (subspace) projection matrix.
+	\textbf{(8-iii)} The sum of $||{a_i^{\star}}||^2$ is one because $A^{\star}$ is a rank-$1$ projection matrix.
 	\textbf{(8-iv)} %We want to point out that the problem setting in Section 3 is in general non-convex. Therefore, it is not possible to explicitly solve $A_1, A_2$ without making further assumptions.
@@
 	\textbf{(i)}
-	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning.
+	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning  (cf. Proposition 1 in Wu et al., 20).
 	Hence, studing this regime is problematic without adding explicit regularization or implicit algorithmic biases.
 	These are interesting research questions, but beyond the scope of our work.
-	\textbf{(ii)}
 
 	Response to questions under Section 3.
-	\textbf{(1-i)}
+	\textbf{(1-ii)} We would like to reminder the reviewer that the purpose of the examples is to explain the empirical phenomena of multi-task and transfer learning.
+	We believe that our examples have provided important initial insights toward understanding the effect of varying sample size ratios and covariate shifts.
+	See Appendix A for evaluation in a real world data setting.
+	We will address these issues and the other clarification questions in the next version of the paper.
 
 	\textbf{Response to R3.}
+	We thank the reviewer for the encouraging review.
+	Regarding the question of how the prediction loss varies with $r$, we would like to point out that in the setting of Theorem 2.1, our result implies the following simple corollary.
+	Suppose that the singular values of ${B^{\star}}^{\top}\Sigma B^{\star}$ are $\lambda_1, \lambda_2, \dots, \lambda_t$ in decreasing order.
+	If we increase $r$ by $1$, the bias reduces by $\lambda_{r+1}$ while the variance increases, the amount of which depends on the singular vector of  ${B^{\star}}^{\top}\Sigma B^{\star}$ corresponding to $\lambda_{r+1}$.
+	As an example of this corollary, we can show that in the setting of Example 2.2, the average prediction loss of all tasks is minimized when $r$ is one.
+	We also thank the reviewer for suggesting the related work.
+	Our work is heavily inspired by Hastie et al., 2019.
+	We will add these related work to the next version of the paper.
 

### 2020-12-03 arxiv/conclusions.tex

@@
-\vspace{-0.06in}
 \section{Conclusions and Discussions}\label{sec_conclude}
-\vspace{-0.06in}
 
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
+This work studied the generalization properties of a widely used hard parameter sharing approach for multi-task learning.
 We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
+Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS.
+We rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
 We validated our theory and conducted further studies on text classification tasks.
-We describe open questions for future work.
-First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-Second, it would be interesting to extend our result to classification problems such as logistic regression.
-%First, our bound in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-%The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might be helpful towards resolving this problem.
-%but its singular values will follow a different distribution since the matrix is not symmetric.
- %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-%Second, it would be interesting to extend our results to classification problems.
-%Several recent work have made remarkable progress for logistic regression in the high-dimensional  setting, e.g. \citet{sur2019modern}.
-%An interesting question is to study logistic regression in a multiple-sample setting.
+
+We describe several open questions for future work.
+First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
+This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+The eigenvalue distribution of this matrix, which has been obtained in \citet{Fmatrix}, might help resolve this problem.
+Second, it would be interesting to extend our results to classification problems.
+Several recent work has made remarkable progress for logistic regression in the high-dimensional setting (e.g. \citet{sur2019modern}).
+It is an interesting question to study logistic regression in a multiple-sample setting.

### 2020-12-03 arxiv/intro.tex

--- 2020-10-15 arxiv/intro.tex
@@
-% The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making the prediction.
 \begin{abstract}
-	\vspace{-0.1in}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties has not been well established in many cases.
+	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
 This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
@@
 
-Hard parameter sharing works as an inductive transfer mechnism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
+Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
+For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12,WZR20}.
 Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
 However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
 Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
 Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
 
@@
 		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
+		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400-eps-converted-to.pdf}
 		\caption{Varying sample size ratio}

### 2020-12-03 arxiv/proof_examples.tex
finish section D

@@
 Without loss of generality, we assume that $A_1$ and $A_2$ are both nonzero.
-Otherwise, the problem reduces to STL. % we add a tiny amount of perturbation $\delta$ to them and the result remains the same.
+Otherwise, the problem reduces to STL. %
 Using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we obtain that $\hat{B}$ satisfies the following
 	\begin{align}
-		\hat{B} \define  \left[A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)}\right]^{-1} \left[A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}\right]. \label{eq_Bhat_2task} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
+		\hat{B} \define  \left[A_1^2 (X^{(1)})^{\top}X^{(1)} + A_2^2 (X^{(2)})^{\top}X^{(2)}\right]^{-1} \left[A_1 (X^{(1))})^{\top}Y^{(1)} + A_2 (X^{(2)})^{\top}Y^{(2)}\right]. \label{eq_Bhat_2task} %
 	\end{align}
 We denote $\hat \Sigma(x)= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
-Applying $\hat B$ to equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers.
-Could you replace $A$ with another symbol (say $x$)?}
+Applying $\hat B$ to equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %
  \begin{align}
@@
 		&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}} \\
-%		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})  \\
-%		&+ \sigma^2\tr\left[ \left(x^2 X^{(1)}\hat\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2+ \left(X^{(2)}\hat\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2 \right]\\
-%&+ 2 x^2 \sigma^2 \tr\left[ \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right]  \nonumber\\
 		=& (\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}) +\sigma^2(n_1+n_2-p).
@@
 	&\ex{g(x) \mid X_1, X_2} \nonumber\\
-%&=[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1}(X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}\right] \nonumber\\
-%&+ A^2[(x-1)^2\kappa^2 + (x^2+1)d^2/2] \cdot p^{-1}\tr\left[  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)}\right] +\sigma^2(n_1+n_2-p) \nonumber\\
-	=& ((x-1)^2\kappa^2 + (x^2+1)d^2){p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
+	=& [(x-1)^2\kappa^2 + (x^2+1)d^2]\cdot {p^{-1}} \tr\left[ (X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)}\right]+\sigma^2(n_1+n_2-p), \label{EgA}
 \end{align}
-
-%\HZ{could you align the Eq so that they look better on page?}
-%\begin{align}
-%\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(x) \mid X_1, X_2 ,\beta^{(1)},\beta^{(2)}}
-%&= \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \nonumber\\
-%&+x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  \nonumber\\
-%& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(x^2 X^{(1)}\hat \Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)^2\epsilon^{(1)}} \nonumber\\
-%&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\hat \Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)^2\epsilon^{(2)}}   \nonumber\\
-%&+  x^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)}\hat \Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)}\hat\Sigma(x)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \nonumber\\
-%& +x^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)}\hat \Sigma(x)^{-1}  (X^{(2)})^\top X^{(2)}\hat\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }. \label{Eg(x)}
-%\end{align}
-%Using the following identity
-%\begin{align*}
-%(X^{(1)})^\top X^{(1)} \hat \Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} & =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \\
-%&= (X^{(2)})^\top X^{(2)} \hat \Sigma(x)^{-1}(X^{(1)})^\top X^{(1)},
-%\end{align*}
-%we can simplify that
-%\begin{align*}
-% & \left\| X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\right\|^2  +x^2 \left\| X^{(2)} \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\right\|^2 \\
-%=&(\beta^{(1)}-x\beta^{(2)})^\top (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)}  (\beta^{(1)}-x\beta^{(2)})\\
-%&+(\beta^{(1)}-x\beta^{(2)})^\top x^2 (X^{(1)})^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)} )^\top X^{(2)}  \hat\Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (\beta^{(1)}-x\beta^{(2)})\\
-%&=(\beta^{(1)}-x\beta^{(2)})^\top\left[ x^2 (X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}  \right]\hat\Sigma(x)^{-1} (X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)})\\
-%=&(\beta^{(1)}-x\beta^{(2)})^\top(X^{(1)} )^\top X^{(1)}  \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (\beta^{(1)}-x\beta^{(2)}).
-%\end{align*}
-%Using this identity, we can simplify equation \eqref{Eg(x)}  to
 
@@
 Furthermore, the operator norm of $\hat\Sigma(x)^{-1}$ is bounded by $(x^2 + 1)^{-1} O(n_1 + n_2) = (x^2 + 1)^{-1} O(p)$.
- % \be\label{op_X12}
-%\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p},
-% \ee
-% and
-% \be\label{op_Sig1}
-%\| \hat\Sigma(x)^{-1}\|\le \frac1{x^2[(\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}}]+[(\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}] }\lesssim \frac{1}{(x^2+1)p},
-% \ee
-%where we used that $3\le n_1/p\le \tau^{-1}$ and $3\le n_2/p\le \tau^{-1}$ for a small constant $\tau>0$.
 
@@
 \end{align}
-In the third step we use the operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)^{-1}$. % as follows
-%\begin{align*}
-%	\left\| (X^{(2)})^\top X^{(2)}  \hat\Sigma(x)^{-1}  (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} \right\| & \le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \hat\Sigma(x)^{-1} \right\|^2 \\
-%  & \lesssim \frac{p}{(x^2+1)^2}.
-%\end{align*}
+In the third step we use the operator norm bound of $X^{(1)}$, $X^{(2)}$, and $\hat{\Sigma}(x)^{-1}$. %
 
@@
 \begin{claim}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
 	Let $c$ be a sufficiently small fixed constant.
 	In the setting of Corollary \ref{cor_MTL_loss}, we have that with high probability,
-%There exists a constant $C>0$ such that
 	\be\label{hatw_add1}|\hat x -1|\le  \frac{2d^2}{\kappa^2} + p^{-1/4+c}.
@@
 Our proof involves two steps.
-First, we will show that $\abs{x^{\star} - 1} \le d^2 / \kappa^2$.
-Second, we will use Claim \ref{claim_largedev1} to show that the global minimizer of $g(x)$ and $h(x)$ are close to each other.
-%Using Lemma \ref{largedeviation} again, we can simplify equation \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
-%	%We define the function
-%	\begin{align}
-%		h(v) =& \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-%		& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-%		& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
-%	\end{align}
-%	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
-%	Furthermore, the validation loss in equation \eqref{approxvalid} reduces to
-%	\be\label{boundv-w}
-%		g(v)=\left[N_2 h(v) + (N_1+N_2)\sigma^2\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)\quad \text{w.h.p.}
-%	\ee
-%	for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
-%Let $\hat w$ be the minimizer of $h(v)$. Our proof consists of the following two steps.
-%\squishlist
-%	\item First, we show that $\hat{w}$ is close to $1$.
-%	\item Second, with equation \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get equation \eqref{simple1}.
-%\squishend
-%%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
-%For the first step, we will prove the following result.
-%To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof.
+First, we  show that $\abs{x^{\star} - 1} \le d^2 / \kappa^2$.
+Second, we use Claim \ref{claim_largedev1} to show that the global minimizer of $g(x)$ and $h(x)$ are close to each other.
 
@@
 Hence the minimum of $h(x)$ is achieved when $x$ is positive.
-%$h(1)=\OO(pd^2 + \sigma^2)$ and $ h(w)\gtrsim p\kappa^2 \gg h(1)$ for $w\ge 2$ or $w\le 1/2$.  Hence it suffices to consider the case $1/2\le w\le 2$.
 Next, we consider the case where $x\ge 1$.
@@
 
-%Taking derivative of $h(w)$, we obtain that
-%\begin{align}
-%	h'(w) \le& \frac{\rho_1}{\rho_2} \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
-%	& +  \left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
-%	& + \frac{\rho_1}{\rho_2}(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }= \frac{\rho_1}{\rho_2} \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
-%\end{align}
-%where the matrix $\cal B$ is
-%$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{\rho_2}{\rho_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
-%Using Fact \ref{lem_minv}, we get that $\cal B$ is upper bounded as
-%\begin{align*}
-%\cal B \preceq - 2(1-w)\kappa^2 n_2^2 (\al_-(\rho_2) -\oo(1))^2 +2w d^2 n_1n_2 (\al_+(\rho_1) +\oo(1))^2 + 2w\sigma^2 n_2 (\al_+(\rho_2)+\oo(1)) \prec 0,
-%\end{align*}
-%as long as
-%$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
-%Hence $h'(w)<0$ on $[0,w_2)$, %i.e. $h(w)$ is strictly decreasing for $w<w_2$. This
-%which gives $\hat w\ge w_2$.
-
-%In sum, we have shown that $w_2\le w\le w_1$. Together with
-%$$\max\{|w_1 -1|, |w_2 -1|\} =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
-%we conclude equation \eqref{hatw_add1}.
-
-%For the rest of this section, we choose parameters that satisfy the following relations: \be\label{choiceofpara}
-%pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 ,
-%\ee
-%for some small constant $c_0>0$.
-
 For the second step, using Claim \ref{claim_largedev1}, we have that $g(x)$ and $h(x)$ differ by at most $p^{1/2 + \e}(\sigma^2 + \kappa^2 + d^2)$.
 Therefore, our goal reduces to showing that if $\hat{x}$ deviates too far from $1 \pm d^2 / \kappa^2$, it is no longer a global minimum of $g(x)$.
-%we first argue that $\hat{x}$ is $O(1)$. Hence we can apply Claim \ref{claim_largedev1} to bound the concentration error of $g(x)$.
-%Using Fact \ref{fact_minv} (ii), we can obtain that with high probability,
-%\begin{align}
-%p(x^2+1)^{-1}&\lesssim \left( x^2 \left[(\sqrt{n_2}-\sqrt{p})^{2}-n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}-\sqrt{p})^{2}-n_1p^{-c_\varphi}\right]^{-1} \right)^{-1} \nonumber\\
-%&\preceq (X^{(1)})^\top X^{(1)} \hat\Sigma(x)^{-1}(X^{(2)})^\top X^{(2)} =\left( x^2 [(X^{(2)})^\top X^{(2)}]^{-1} + [(X^{(1)})^\top X^{(1)}]^{-1} \right)^{-1} \nonumber\\
-%&\preceq \left( x^2 \left[(\sqrt{n_2}+\sqrt{p})^{2}+n_2p^{-c_\varphi}\right]^{-1} +\left[(\sqrt{n_1}+\sqrt{p})^{2}+n_1p^{-c_\varphi}\right]^{-1} \right)^{-1}\lesssim p(x^2+1)^{-1}, \label{op_uplow}
-%\end{align}
-%where we also used that $3\le n_1/p \le \tau^{-1}$ and $3\le  n_2/p \le \tau^{-1}$ for a small constant $\tau>0$. Then we get that
-%\be\label{eq_h1}h(1)= 2d^2 \cdot p^{-1} \tr\left[ (X^{(1)})^\top X^{(1)} \hat\Sigma(1)^{-1}(X^{(2)})^\top X^{(2)}\right]\lesssim pd^2 .\ee
-%On the other hand, if $|x-1|\ge \delta$ for a small constant $\delta>0$, then we have
-%\begin{align}\label{eq_hA}
-%h(x)\gtrsim (1+x^2)\kappa^2 \cdot p\left( x^2 +1\right)^{-1} =p\kappa^2 ,
-%\end{align}
-%where in the first step we used that $|x-1|^2\gtrsim 1+x^2$ for $|x-1|\ge \delta$ and equation \eqref{op_uplow}.
-%and in the second step we used equation \eqref{choiceofpara0} \HZ{I'm not sure which condition we use? put it here}.
-%\begin{align}
-%g(x)&\ge  h(x) +\sigma^2(n_1+n_2-p) -p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \nonumber\\
-%&\ge h(1) +\sigma^2(n_1+n_2-p) + p^{-1/2+c}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right) \ge g(1), \label{gA>g1}
-%\end{align}
-%under conditions $\sigma^2 =\OO( \kappa^2)$ and $d^2 =\oo({\kappa^2})$. %\eqref{choiceofpara0} \HZ{again, I don't see which condition we use here?}.
-%This gives that
-%Hence it remains to consider the region $|A-1|\le \delta$ for a small enough constant $\delta>0$.
 We prove by contradiction.
@@
 
-%Then if we choose the constant $c$ in Claim \ref{claim_largedev1} such that $e_1<2e_2$, we have
-%$$ h(x)-h(1)\gtrsim  p^{-1/2+2e_2}\cdot p\kappa^2 \gg p^{-1/2+e_1}\cdot p\left(\sigma^2 +\kappa^2+d^2 \right),$$ where we use the assumption that $\sigma^2$ and $d^2$ are both at most $\OO(\kappa^2)$, which implies the inequality \eqref{gA>g1}.
 Second, suppose that $\hat{x} \le 1 - 2d^2/ \kappa^2 - p^{-1/2 + \e}$.
@@
 Using a similar argument to the first case, we get that the difference between $h(x)$ and $h(1)$ is at least the integral of the abvoe derivative.
-%under equation \eqref{choiceofpara0} \HZ{I don't see which condition we want to use here?},
 This implies that $\hat{x}$ cannot be too far from one.
 Hence we have completed the proof.
-%Next we prove the following estimate on the optimizer $\hat x$: with high probability,
-%%\begin{lemma}
-%%For the isotropic model, we have
-%\be\label{hatv_add1}
-%|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 /2+ 2\e}.
-%\ee
-%%\end{lemma}
-%%\begin{proof}
-% In fact, from the proof of Claim \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-1| \le 2C\cal E$ for a large enough constant $C>1$, then $|h'(w)|\gtrsim \sigma^2$.
-Moreover, under equation \eqref{choiceofpara} we have
-%$$h(w) =\OO(\sigma^2),\quad \text{for}\quad   |w-1|\le 2C\cal E.$$
-%Thus we obtain that for $|w-1|\ge 2C\cal E$,
-%$$\left|h(w) - h(\hat w)\right|\ge |h(w)-\min\{h(w_1),h(w_2)\}|\gtrsim \sigma^2 \cal E \gtrsim \cal E \cdot h(\hat w),$$
-%which leads to $g(w) > g(\hat w)$ with high probability by equation \eqref{boundv-w}.
-Thus $w$ cannot be a minimizer of $g(v)$, and we must have $|\hat v - 1|\le 2C\cal E$.
-%Together with equation \eqref{hatw_add1}, we conclude equation \eqref{hatv_add1}.
-%%\end{proof}
-%
-%{\cor require $\kappa^2\gg d^2 + p^{-1/2+c}\sigma^2$}
 \end{proof}
@@
 \end{align*}
-% \end{claim}
-%We are now ready to finish the proof of Claim \ref{claim_reduction}.
 Next, we further simplify $\cal L(\hat x)$ since $\hat{x}$ is close to one and $\Sigma^{(1)},\Sigma^{(2)}$ are both isotropic
@@
 \end{align}
-%To obtain this inequality, we used
-%$$ (\sqrt{n_1}-\sqrt{p})^4 \cdot (1-p^{-c_\varphi}) \preceq \left((X^{(1)})^\top X^{(1)} \right)^2 \preceq (\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) \quad \text{with high probability},$$
-%by Fact \ref{fact_minv} (ii), and the fact that for the product of two PSD matrices, its trace is always nonnegative.
 Using the bias limit \eqref{lem_cov_derv_eq} with $\Sigma^{(1)}=\Sigma^{(2)}=\Lambda=V=\id_{p\times p}$, and $w = e_i$ (the $i$-th coordinate vector), we have w.h.p. (via a union bound)
-\begin{align*}%\label{eq_bias112}
+\begin{align*}%
  e_i^{\top}\hat\Sigma^{-2} e_i = \frac{1}{(n_1+n_2)^2} \left[\frac{a_3+a_4+1}{(a_1+a_2)^2} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
@@
 		a_3 = \frac{p\cdot n_1}{(n_1 +n_2)(n_1 +n_2 - p)}, \quad
-		&  a_4 = \frac{p\cdot n_2}{(n_1 + n_2)(n_1 + n_2 - p)}. %\label{simplesovlea34}
+		&  a_4 = \frac{p\cdot n_2}{(n_1 + n_2)(n_1 + n_2 - p)}. %
 \end{align*}
-Applying them to the above equation, we obtain
-\begin{align*}%\label{eq_bias113}
- e_i^{\top}\hat\Sigma^{-2}e_i =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right].
+Applying $a_3, a_4$ to the equation above, we obtain
+\begin{align*}%
+ e_i^{\top}\hat\Sigma^{-2}e_i =  \frac{1}{(n_1+n_2)^2} \left[  \frac{ (n_1+n_2)^3 }{(n_1+n_2-p)^3} +\OO(p^{-c_\varphi})\right], \text{ for all } i = 1, 2, \dots, p.
 \end{align*}
-%In fact, we need this estimate to hold simultaneously for all $1\le i \le p$ with high probability. For this purpose, we shall use equation \eqref{apply derivlocal} to get that
-%\begin{align*}%\label{eq_bias113}
-%\left| \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
-%\end{align*}
-%on a high probability event that does not depend on $i$. Then using Fact \ref{lem_stodomin} (i), we obtain that
-%\begin{align*}
-%\left| \sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{p}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\prec \frac{p^{1-\frac{\varphi-4}{2\varphi}}}{(n_1+n_2)^2}
-%\end{align*}
-%with high probability, which by Definition \ref{stoch_domination} gives that
-%\begin{align}\label{eq_bias113}
-%\left| p^{-1}\sum_{i=1}^p \left(\hat\Sigma^{-2}\right)_{ii} - \frac{1}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\right|\le \frac{p^{-c_\varphi}}{(n_1+n_2)^2}
-%\end{align}
-%with high probability.
-Applying the above equation to equation \eqref{eq_bias111}, we get the desired result for the bias term.
-%\begin{align*}
-%		& \frac{(\sqrt{n_1}-\sqrt{p})^4 \cdot (1- p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}\nonumber \\
-%		\le &  {p}^{-1}\tr\left[\hat\Sigma^{-2} \left((X^{(1)})^\top X^{(1)} \right)^2\right] - \frac{n_1^2}{(n_1+n_2)^2}\cdot  \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3} \nonumber\\
-%		\le &  \frac{(\sqrt{n_1}+\sqrt{p})^4 \cdot (1+ p^{-c_\varphi}) - n_1^2 \cdot (1+\OO(p^{-c_\varphi}))}{(n_1+n_2)^2}\cdot   \frac{(n_1+n_2)^3}{(n_1+n_2-p)^3}.
-%\end{align*}
+Applying the above result to equation \eqref{eq_bias111}, we get the desired result for the bias term.
 Combining the bias and variance estimates, we get that
 \begin{align*}
-	\left|L(\hat{\beta}_2^{\MTL})  - \frac{\sigma^2 p}{n_1+n_2-p} -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3}\right| \le   \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \nonumber\\
-+C\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
+	 \left|L(\hat{\beta}_2^{\MTL})  -  \frac{2d^2 n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} - \frac{\sigma^2 p}{n_1+n_2-p}   \right|&
+	  \le   \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4-1\right] \cdot \frac{2d^2n_1^2 (n_1+n_2)}{(n_1 + n_2 - p)^3} \\
+	&\hspace{-2cm}+\OO\left( p^{-c_\varphi} (\sigma^2 + d^2)+ \frac{d^4 + \sigma^2 d^2}{\kappa^2}+p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) \right).
 \end{align*}

### 2020-12-03 arxiv/tools.tex

@@
 Furthermore, using the finite $\varphi$-th moment condition and the tail probabilities, we can show that the mean and variance of $Z-\wt Z$ are small, which gives that (cf.
-equation \eqref{meanshif}) %, we have that
+equation \eqref{meanshif}) %
 \be\label{meanshif222}
@@
 \ee
-%From the first estimate in equation \eqref{meanshif}, we can also get a bound on the operator norm:
-%\be\label{EZ norm222}\|\E \wt Z^{(1)}\|=\OO(n^{-1/2}) .
-%\ee
 We centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$
-It suffices to show that 
+Let $\e$ be a sufficiently small fixed constant.
+To prove the result, it suffices to show that
 \be\label{show_whZ}
@@
 \be\label{vcalE}
-	|v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \text{ and } \|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|.
+	|v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \ \ \text{ and }\ \ \|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|.
 \ee
@@
 \begin{align}\label{vcalA2}
-	\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F, \text{ and }
+	\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F,  \ \ \text{ and }\ \
 	\left\| \cal E^\top B \cal E - \sigma^2 \tr[B]\cdot \id_{t\times t}\right\|_F \le n^{c} \cdot  \sigma^2\|B\|_F.
 \end{align}
-%\be\label{vcalAE3}
-%,
-%\ee
 \end{corollary}

### 2020-12-03 old/arxiv_full_version/experiments_text.tex

--- 2020-10-22 abridged/experiments_text.tex
@@
 First, we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
+In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially but hurts eventually.
 On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
@@
 
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
+These examples and Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
 Concretely, here is one implementation of this idea.
@@
 	\item During every stage, we train for $T$ epochs using only the $S$ batches.
-If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
+If the validation accuracy drops compared to the previous round's result or reaches the desired threshold $\tau$, we terminate.
 %	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
 \end{itemize}
-For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
+If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
 %See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
 The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
+For example, if the process terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
 

### 2020-12-03 old/arxiv_full_version/proof_same_cov.tex

--- 2020-10-20 arxiv_full_version/proof_same_cov.tex
@@
 		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
-		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \label{eq_gA_err2}
+		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} . \label{eq_gA_err2}
 %		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
@@
 
-	\bigskip
+	\medskip
 	Next, we use equation \eqref{eq_gA_err} to prove the claim.
@@
 		\bignormFro{ X(X^\top X)^{-1}\Sigma b} &=\left[ {b}^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma b \right]^{1/2} \\
-		&\le  \|\Sigma^{1/2} b \|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2}  =   \|\Sigma^{1/2} b \|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2} \\
-		&\le n^{-1/2} \cdot \norm{\Sigma^{1/2} b}.
+		&\le  \|\Sigma^{1/2} b \|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2}  \\
+		&=   \|\Sigma^{1/2} b \|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}  \\
+		& \lesssim n^{-1/2} \cdot \norm{\Sigma^{1/2} b}.
 	\end{align*}
@@
 	& \left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} -\delta_{jk}\cdot \sigma^2\tr\left[\Sigma(X^\top X)^{-1}\right]\right|\nonumber \\
-	\le &n^c\cdot \sigma^2  \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} }   = n^c\cdot \sigma^2  \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
-	  \le &\sigma^2 \cdot p^{1/2} \cdot  \bignorm{(Z^{\top} Z)^{-1}}^{1/2} \lesssim \sigma^2 \cdot n^{-1/2+c}. \label{jeqk}
+	\le &n^c\cdot \sigma^2  \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber \\
+	 = & n^c\cdot \sigma^2  \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
+	  \le &\sigma^2 \cdot p^{1/2} \cdot  \bignorm{(Z^{\top} Z)^{-1}}^{1/2} \nonumber\\
+	  \lesssim &\sigma^2 \cdot n^{-1/2+c}. \label{jeqk}
 	\end{align}

### 2020-12-03 old/full_version_1013/experiments.tex

--- 2020-10-14 arxiv/experiments.tex
@@
+%\section{Numerical Results}\label{sec_exp}
+
+%We validate our  algorithmic insights and then our theory.
+%In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
+%the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
+%Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
+%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
+%In Section \ref{sec_exp_ab}, we validate our theoretical results.
+%We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
+	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
+The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
+	\label{fig_same_cov}
+\end{figure}
+
 \section{Simulation Studies}\label{sec_simulation}
 
-We demonstrate the accuracy of our results in simulations.
-While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.
+We demonstrate the accuracy of our results via some empirical results.
+While our theory is asymptotic (with error terms that is negligible when $p$ is sufficiently large), we observe that they are accurate in a moderate dimension of $p = 200$.
 
-\textbf{Sample efficiency.}
+\paragraph{Sample efficiency.}
 First, we study the setting of Example \ref{ex_same_cov}.
@@
 In all the parameter settings, our results estimate the empirical losses accurately.
-We also observe a trend that the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
+We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
 Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
@@
 Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level.
+Finally, for $d = 0.2$, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires fewer samples per-task than STL.
 %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
@@
 
-\textbf{Sample ratio.}
+\paragraph{Sample ratio.}
 Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
 Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-%Again, our estimates are accurate compared to the empirical losses.
+Again, our estimates are reasonably accurate compared to the empirical losses.
 We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
 The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is $1$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
+We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.
 On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases monotonically.
-Our result from Corollary \ref{cor_MTL_loss} explains this trend. \HZ{check}
+Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}. \HZ{check}
 
-\textbf{Covariate shift.}
+\iffalse
+We observe that as we increase the sample ratio, task two's prediction loss decreases initially but increases above the initial loss level.
+Our work explains this trend since the task-specific variance $d^2 = 0.08$ is higher than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
+%We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
+\fi
+
+\paragraph{Covariate shift.}
 Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}. 
 Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
-The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
+Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means more covariate shift.
+Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
+The noise variance $\sigma^2$ is $1/4$.
 %Covariate shift: We set $\kappa = 1$ and $d = 0$.
@@
 %\end{table}
-%\begin{figure}[!t]
+
+\begin{figure}[!t]
+%		\begin{subfigure}[b]{0.32\textwidth}
 %		\centering
-%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
-%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
-%	\label{fig_same_cov}
-%\end{figure}
+%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
+%		\caption{Sample efficiency}
+%		\label{fig_model_shift}
+%	\end{subfigure}\hfill
+	\centering
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_several_d.eps}
+		\caption{Example \ref{ex_sample_ratio}}
+		\label{fig_size}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
+		\caption{Example \ref{ex_covshift}}
+		\label{fig_covariate}
+	\end{subfigure}
+	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in Section \ref{sec_diff} for two tasks:
+	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
+	In Figure \ref{fig_size}, we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
+	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
+	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one.
+Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
+	\label{fig_model_shift_phasetrans}
+\end{figure}

### 2020-12-03 old/full_version_1013/proof_gaussian_case.tex

\section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}

We begin with a warm up analysis when the entries of $Z^{(1)}$ and $Z^{(2)}$ are drawn i.i.d. from an isotropic Gaussian distribution.
By the rotational invariance of the multivariate Gaussian distribution, we have that the entries of $Z^{(1)} U$ and $Z^{(2)}$ also follow an isotropic Gaussian distribution.
Hence it suffices to consider the following resolvent
 \begin{equation} \label{resolv Gauss1}
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
   {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
   {n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}
We show how to derive the matrix limit $\Gi(z)$ and the self-consistent equation system \eqref{selfomega_a}.
We first introduce several notations.
Define the index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
%We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$.
%Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
%	\be\label{labelZ}
% Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
We will study the following partial traces of the resolve $G(z)$:
\be\label{defm}
\begin{split}
m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
 m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z).
\end{split}
\ee
To deal with the matrix inverse, we consider the following resolvent minors of $G(z)$.
\begin{definition}[Resolvent minors]\label{defn_Minor}
	Let $X \in \real^{(p + n_1 + n_2)\times (p + n_1 + n_2)}$ and $i = 1, 2, \dots, p + n_1 + n_2$.
	The minor of $X$ after removing the $i$-th row and column of $X$ is denoted by $X^{(i)} := [X_{a_1,a_2}:a_1, a_2 \in \mathcal I\setminus \{i\}]$ as a square matrix with dimension $p + n_1 + n_2 - 1$.
	For the indices of $X^{(i)}$, we use $X^{(i)}_{a_1, a_2}$ to denote $ X_{a_1, a_2}$ when $a_1$ and $a_2$ both not equal to $i$, and $X^{(i)}_{a_1, a_2}$ to be zero when $a_1 = i$ or $a_2 = i$.
	The resolvent minor of $G(z)$ after removing the $i$-th row and column is defined as
	\begin{align*}
		G^{(i)}(z) := \left[ \left( {\begin{array}{*{20}c}
		  { -z\id_{p} } & n^{-1/2}\Lambda (Z^{(1)})^\top & n^{-1/2} (Z^{(2)})^\top  \\
      {n^{-1/2} Z^{(1)} \Lambda  } & {-\id_{n_1}} & 0 \\
			{n^{-1/2} Z^{(2)}} & 0 & {-\id_{n_2}}
    \end{array}} \right)^{(i)}\right]^{-1}.
	\end{align*}
\end{definition}
As a remark, we denote the partial traces $m^{(i)}(z)$, $m_0^{(i)}(z)$, $m_1^{(i)}(z)$, and $m_2^{(i)}(z)$ by replacing $G(z)$ with $G(z)^{(i)}$ in equation \eqref{defm}.

\paragraph{Self-consistent equations.}
We briefly describe the ideas for deriving the equation set \eqref{selfomega_a}.
A complete full can be found in Lemma \ref{lemm_selfcons_weak}.
We show that with high probability, the following equations hold approximately:
\be\label{approximate m1m2}
\begin{split}
& m_1^{-1}(z) = -1+ \frac{1}{n} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 \frac{n_1}{n_1+ n_2} m_1(z) +  \frac{n_2}{n_1+n_2}m_2(z)+\oo(1)}+ \oo(1),\\
& m_2^{-1}(z) = -1+\frac{1}{n} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 \frac{n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1+n_2}m_2(z)+\oo(1)}  + \oo(1).
\end{split}
\ee
These are the self-consistent equations that we stated in equation \eqref{selfomega_a}.
More precisely, we have that $m_1(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_1} a_1(z) $ and $m_2(z)$ is approximately equal to $-\frac{n_1 + n_2}{n_2} a_2(z)$.

The core idea is to study $G(z)$ using the Schur complement formula.
First, we consider the diagonal entries of $G(z)$ for each block in $\cal I_0$, $\cal I_1$, and $\cal I_2$.
For any $i$ in $\cal I_0$, any $\mu$ in $\cal I_1$, and any $\nu$ in $\cal I_2$, we have that
\begin{align*}
	&G_{i,i}^{-1}(z) = -z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} Z^{(1)}_{\mu i}Z^{(1)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} Z^{(2)}_{\mu i}Z^{(2)}_{\nu i} G^{\left( i \right)}_{\mu,\nu}(z) -\frac{2\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} Z^{(1)}_{\mu i}Z^{(2)}_{\nu i}G^{\left( i \right)}_{\mu,\nu}(z) \\
	&G_{\mu,\mu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j Z^{(1)}_{\mu i}Z^{(1)}_{\mu j} G^{\left(\mu\right)}_{i,j}(z) \\
	&G_{\nu,\nu}^{-1}(z) =  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  Z^{(2)}_{\nu i}Z^{(2)}_{\nu j}  G^{\left(\nu\right)}_{i,j}(z).
\end{align*}
For the first equation, we expand the Schur complement formula $G_{ii}^{-1}(z) = -z - H_i G^{(i)}(z) H_{i}^\top$, where $H_i$ is the $i$-th row of $H$ with the $(i,i)$-th entry removed.
The second and third equation follow by similar calculations.

%\be\label{approx m12 add}
%(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
%\ee

Next, we apply standard concentration bounds to simplify the above results.
For $G^{-1}_{i, i}(z)$, recall that the resolvent minor $G^{(i)}$ is defined such that it is independent of the $i$-th row and column of $Z^{(1)}$ and $Z^{(2)}$.
Hence by standard concentration inequalities, we have that the cross terms are approximately zero.
%is approximately equal to the expectation over $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$.
As shown in Lemma \ref{lemm_selfcons_weak}, we have that with high probability the following holds
\begin{align*}
	G_{i,i}^{-1}(z) &= -z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1) \\
	&= - z - \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1^{(i)}(z)-  \frac{n_2}{n_1 + n_2} m_2^{(i)}(z)+\oo(1)
\end{align*}
by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ with respect to the resolvent minor $G^{(i)}(z)$.
Since we removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
Hence we obtain that
\begin{align}\label{1self_Gii}
	G_{i,i}(z)  = -\left(z + \frac{\lambda_i^2 \cdot n_1}{n_1 + n_2} m_1(z) +  \frac{n_2}{n_1 + n_2} m_2(z) + \oo(1)\right)^{-1}.
\end{align}
For the other two blocks $\cal I_1$ and $\cal I_2$, using similar ideas we have that the following holds with high probability
\begin{align*}
	G_{\mu,\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} \\
	G_{\nu,\nu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
\end{align*}
By averaging the above results over $\mu \in \cal I_1$ and $\nu \in \cal I_2$, we obtain that with high probability
\begin{align*}
	m_1(z) &= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu,\mu}(z) = -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1} \\
	m_2(z) &= \frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu,\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
\end{align*}
Furthermore, we obtain that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$, with high probability
$G_{\mu,\mu}(z) = m_1(z) +\oo(1)$ and $G_{\nu, \nu}(z) = m_2+\oo(1)$.
In other words, both block matrices within $\cal I_1$ and $\cal I_2$ are approximately a scaling of the identity matrix.
The above results for $m_1(z)$ and $m_2(z)$ imply that
\begin{align*}
	m_1^{-1}(z) = -1- \frac{1}{n_1 + n_2} \sum_{i=1}^p \lambda_i^2 G_{i,i}(z)+ \oo(1) \\
	m_2^{-1}(z) = -1- \frac{1}{n_1 + n_2} \sum_{i=1}^p G_{i,i}(z)  + \oo(1).
\end{align*}
where we used the definition of $m(z)$ and $m_0(z)$.
By applying equation \eqref{1self_Gii} for $G_{i, i}(z)$, we obtain the self-consistent equations \ref{approximate m1m2}.
In Lemma \ref{lem_stabw}, we show that the self-consistent equations are stable, that is, a small perturbation of the equations leads to a small perturbation of the solution.

\paragraph{Matrix limit.}
Finally, we derive the matrix limit $\Gi(z)$.
Applying our solution for $m_1(z)$ and $m_2(z)$ into equation \eqref{1self_Gii}, we get that for $i$ in $\cal I_0$,
$G_{i, i}(z) = (-z +\lambda_i^2 a_{1}(z) + a_2(z)+\oo(1))^{-1}$.
Similarly, for $\mu$ in $\cal I_1$, we have that $G_{\mu, \mu}(z) = -\frac{n_1 + n_2}{n_1}a_{1}(z)+\oo(1)$, and for $\nu$ in $\cal I_2$, we have that $G_{\nu, \nu}(z) = -\frac{n_1 + n_2}{n_2}a_{2}(z)+\oo(1)$.
Hence we have derived the diagonal entries of $\Gi(z)$.
In Lemma \ref{Z_lemma}, we show that the off-diagonal entries are close to zero.
For example, for $i\ne j\in \cal I_1$, by Schur complement, we have that
$$G_{i,j}(z) = -G_{i,i}(z)\cdot {n^{-1/2}}\Big({\lambda_i}\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu, j}(z) + \sum_{\mu \in \cal I_2} Z^{(2)}_{\mu, i} G^{(i)}_{\mu, j}(z) \Big).$$
Using standard concentration inequalities, we show that $\sum_{\mu \in \cal I_1} Z^{(1)}_{\mu i} G^{(i)}_{\mu, j}(z)$ and $\sum_{\mu \in \cal I_2} Z^{(2)}_{\mu i} G^{(i)}_{\mu, j}(z)$ are both close to zero.
The other off-diagonal entries are bounded similarly.
%The bound on the off-diagonal entries will be proved rigorously .

\paragraph{Notations.}
We introduce several notations for the proof of Theorem \ref{thm_main_RMT}.
We say that an event $\Xi$ holds with overwhelming probability if for any constant $D>0$, $\mathbb P(\Xi)\ge 1- n^{-D}$ for large enough $n$.
Moreover, we say $\Xi$ holds with overwhelming probability in an event $\Omega$ if for any constant $D>0$, $\mathbb P(\Omega\setminus \Xi)\le n^{-D}$ for large enough $n$.
The following notion of stochastic domination, which was first introduced in \cite{Average_fluc}, is commonly used in the study of random matrices.

\begin{definition}[Stochastic domination]\label{stoch_domination}
Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
%\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents. Furthermore, the random matrix entries can also depend on $n$ if we want. One important example is Bernoulli random variable with sparsity $p=n^{-\theta}$. Furthermore, this also includes the random variables that do not depend on $n$ as a special case.}]
We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for any $n > n_0(\e, D)$,
\[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if % for any constants $\e, D>0$,
\[ \sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}. \]
\end{definition}

%For example, we say that $\xi$ is stochastically dominated by $\zeta$ with overwhelming probability if $\zeta$ is greater than $\xi$ up to a small power of $n^{\e}$.
We make several remarks.
First, since we allow an $n^\e$ factor in stochastic domination, we can ignore log factors without loss of generality since $(\log n)^C\prec 1$ for any constant $C>0$.
Second, given a random variable $\xi$ whose moments exist up to any order, we have that $|\xi|\prec 1$.
This is because by Markov's inequality, let $k$ be greater than $D/ \e$, then we have that
$$ \P(|\xi|\ge n^{\e})\le n^{-k\e}{\E |\xi|^k}\le n^{-D}.$$
This implies that a Gaussian random variable $\xi$ with unit variance satisfies that $|\xi|\prec 1$.

The following fact collects several basic properties that are often used in the proof.
\begin{fact}[Lemma 3.2 in \cite{isotropic}]\label{lem_stodomin}
Let $\xi$ and $\zeta$ be two families of nonnegative random variables depending on some parameters $u\in \cal U$ or $v\in \cal V$.
\begin{itemize}
\item[(i)] Suppose that $\xi (u,v)\prec \zeta(u,v)$ uniformly in $u\in \cal U$ and $v\in \cal V$. If $|\cal V|\le n^C$ for some constant $C>0$, then $\sum_{v\in \cal V} \xi(u,v) \prec \sum_{v\in \cal V} \zeta(u,v)$ uniformly in $u$.

\item[(ii)] If $\xi_1 (u)\prec \zeta_1(u)$ and $\xi_2 (u)\prec  \zeta_2(u)$ uniformly in $u\in \cal U$, then $\xi_1(u)\xi_2(u) \prec \zeta_1(u) \zeta_2(u)$ uniformly in $u\in \cal U$.

\item[(iii)] Suppose that $\Psi(u)\ge n^{-C}$ is a family of deterministic parameters, and $\xi(u)$ satisfies $\mathbb E\xi(u)^2 \le n^C$. If $\xi(u)\prec \Psi(u)$ uniformly in $u$, then we also have $\mathbb E\xi(u) \prec \Psi(u)$ uniformly in $u$.
\end{itemize}
\end{fact}

%In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below. %\ref{sec_prelim}.
%Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.

Next, we introduce the bounded support assumption for a random matrix.
We say that a random matrix $Z \in\real^{n \times p}$ satisfies the {\it{bounded support condition}} with $q$ or $Z$ has support $q$ if
\begin{equation}
	\max_{1\le i \le n, 1 \le j \le p}\vert Z_{i, j} \vert \prec q. \label{eq_support}
\end{equation}
As shown in the example above, if the entries of $Z$ have finite moments up to any order, then $Z$ has bounded support $1$.
More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that %\HZ{I don't fully get the equation below}
\begin{align}
	\P\left(\max_{1\le i\le n, 1\le j \le p}|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right) &\le \sum_{i=1}^n \sum_{j=1}^p \P\left(|Z_{i, j}|\ge (\log n) n^{\frac{2}{\varphi}}\right)  \nonumber\\
	&\le \sum_{i=1}^n \sum_{j=1}^p \frac{C}{\left[(\log n) n^{\frac{2}{\varphi}}\right]^\varphi} = \OO((\log n)^{-\varphi}).\label{Ptrunc}
	\end{align}
In other words, $Z$ has bounded support $q=n^{\frac{2}{\varphi}}$ with high probability.
%This leads to the exponent $\frac{\varphi-4}{2\varphi}$ in Fact \ref{lem_minv}. %This fact will be used in the proof of Corollary \ref{main_cor} below.
%The above discussion shows that the bounded support condition provides great flexibility in dealing with finite moment conditions.
%\begin{assumption}%\label{assm_big1}
%As in Section \todo{add reference}, we consider random matrices $X^{(1)}=Z^{(1)}\Sigma_1^{1/2}$ and $X^{(2)}=Z^{(2)}\Sigma_2^{1/2}$, where $Z^{(1)}$ and $Z^{(2)}$ are independent $n_1\times p$ and $n_2\times p$ random matrices with i.i.d. entries of zero mean and unit variance. Recall that $\rho_1= n_1/p$ and $\rho_2=n_2/p$. We assume that for a small constant $0<\tau<1$,
%\HZ{We have defined $\rho_1,\rho_2$ already in sec 2. Consider using ``Recall that $\rho_1 =, \rho_2 =$.''}
%\be\label{assm2}
%0\le \rho_1 \le \tau^{-1}, \quad 1+\tau \le \rho_{2} \le \tau^{-1}.
%\ee
%Recall that the singular value decomposition of $M = \Sig_1^{1/2} \Sig_2^{-1/2}$ is $U \Lambda V^{\top}$. We assume that
%\begin{equation}\label{assm32}
%\tau \le \lambda_p \le \lambda_1 \le \tau^{-1} .%, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
%\end{equation}
%Finally, recalling the notations in equation \eqref{labelZ}, we assume that $Z^{(1)}$ and $Z^{(2)}$ satisfy
%\begin{equation}
%n^{-1/2}\max_{i\in \cal I_0,\mu \in \cal I_1}\vert Z^{(1)}_{\mu i}\vert \prec q,\quad n^{-1/2}\max_{i\in \cal I_0,\nu \in \cal I_2}\vert Z^{(2)}_{\nu i}\vert \prec q, \label{eq_support}
%\end{equation}
%for some deterministic parameter $q$ satisfying $ n^{-{1}/{2}} \leq q \leq n^{- \tau} $ for a small constant $\tau>0$.
%Here we recall the notations in \eqref{labelZ}.
 %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
%\end{assumption}
%\HZ{This is restating what's stated above again. Remove redundant statements (unless there's something critical missing in Sec 2).} [\cor FY: The setting in sec 1 is too vague for the purpose of this section in the sense that it is hard to find the exact properties we need. In this section, I want to state rigorous statements with a reference to an exact assumption. Moreover, the above assumption contains more.\nc]

%\begin{remark}
%The lower bound $\rho_2\ge 1+\tau$ in equation \eqref{assm2} is to ensure that the sample covariance matrix $(X^{(2)})^\top X^{(2)}$ is non-singular with overwhelming probability. Moreover, we have allowed that $\rho_1=0$, because we want to state a general result that also covers the special case with no source task.
%\end{remark}

%\begin{definition}\label{defn_support}
%We say a (rescaled) random matrix $\cal M$ satisfies the {\it{bounded support condition}} with $q$, if
%\begin{equation}
%\max_{i,j}\vert \cal M_{ij}\vert \prec q. \label{eq_support}
%\end{equation}
%%Here $q\equiv q(n)$ is a deterministic parameter and usually satisfies $ n^{-{1}/{2}} \leq q \leq n^{- \phi} $ for some (small) constant $\phi>0$.
%Whenever (\ref{eq_support}) holds, we say that $M$ has support $q$.
%%Moreover, if the entries of $X$ satisfy (\ref{size_condition}), then $X$ trivially satisfies the bounded support condition with $q=N^{-\phi}$.
%\end{definition}
%\begin{example}
%\todo{Talk about the Gaussian case and Bernoulli case.}

%\end{example}

%Recall that $n:=n_1+n_2$, which is the total number of data in the two tasks.
%Before giving the main proof, we first introduce some notations and tools.
%Following the notations in \cite{EKYY,EKYY1}, we will use the following definition to characterize events of overwhelming probability.
%
%\begin{definition}[overwhelming probability event] \label{high_prob}
%Define
%\begin{equation}\label{def_phi}
%\varphi:=(\log N)^{\log \log N}.
%\end{equation}
%We say that an $N$-dependent event $\Omega$ holds with {\it{$\xi$-overwhelming probability}} if there exist constant $c,C>0$ independent of $N$, such that
%\begin{equation}
%\mathbb{P}(\Omega) \geq 1-N^{C} \exp(- c\varphi^{\xi}),  \label{D25}
%\end{equation}
%for all sufficiently large $N$. For simplicity, for the case $\xi=1$, we just say {\it{overwhelming probability}}. Note that if (\ref{D25}) holds, then $\mathbb P(\Omega) \ge 1 - \exp(-c'\varphi^{\xi})$ for any constant $0\le c' <c$.
%\end{definition}
%\begin{remark}
%For any $c, C>0$, there exists a $0< c^{\prime}<c$, such that $N^{C} \exp(-c \varphi^{\xi}) \leq \exp(-c^{\prime} \varphi^{\xi})$. Hence, if
%\begin{equation}
%\mathbb{P}(\Omega) \geq 1- \exp(-c \varphi^{\xi})
%\end{equation}
%$\Omega$ is also a $\xi$-overwhelming probability event.
%\end{remark}

### 2020-12-03 old/full_version_1013/tools.tex

\section{Tools}\label{app_tool}

\subsection{Algebraic Inequalities}

\begin{fact}\label{fact_proof_gA}
	The minimum singular value of a matrix $X^{\top}YX$ is at least the minimum singular value of $Y$ times the minimum singular value of $X^{\top}X$.
\end{fact}

The following simple resolvent identities are important tools for our proof. Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}.
\begin{lemma}\label{lemm_resolvent}
We have the following resolvent identities.
\begin{itemize}
\item[(i)]
For $i\in \mathcal I_1$ and $\mu\in \mathcal I_1\cup \cal I_2$, we have
\begin{equation}
\frac{1}{G_{ii}} =  - z - \left( {AG^{\left( i \right)} A^\top} \right)_{ii} ,\quad  \frac{1}{{G_{\mu \mu } }} =  - 1  - \left( {A^\top  G^{\left( \mu  \right)} A} \right)_{\mu \mu }.\label{resolvent2}
\end{equation}

 \item[(ii)]
 For $i\in \mathcal I_1$, $\mu \in \mathcal I_1\cup \cal I_2$, $a\in \cal I\setminus \{i\}$ and $b\in \cal I\setminus \{ \mu\}$, we have
\begin{equation}
G_{ia}   = -G_{ii}  \left( AG^{\left( {i} \right)} \right)_{ia},\quad  G_{\mu b }  = - G_{\mu \mu }  \left( A^\top  G^{\left( {\mu } \right)}  \right)_{\mu b }. \label{resolvent3}
\end{equation}
%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
%\begin{equation}\label{resolvent6}
%\begin{split}
% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}. %\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) . %, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
%\end{split}
%\end{equation}

 \item[(iii)]
 For $a \in \mathcal I$ and $a_1,a_2 \in \mathcal I \setminus \{a\}$, we have
\begin{equation}
G_{a_1a_2}^{\left( a \right)}  = G_{a_1a_2}  - \frac{G_{a_1a} G_{aa_2}}{G_{aa}} .
%, \quad  \frac{1}{{G_{{b}{b}} }} = \frac{1}{{G_{{b}{b}}^{({a})} }} - \frac{{G_{{b}{a}} G_{{a}{b}} }}{{G_{{b}{b}} G_{{b}{b}}^{({a})} G_{{a}{a}} }}.
\label{resolvent8}
\end{equation}
%and
%\begin{equation}
%\frac{1}{{G_{ss} }} = \frac{1}{{G_{ss}^{(r)} }} - \frac{{G_{sr} G_{rs} }}{{G_{ss} G_{ss}^{(r)} G_{rr} }}.
%\label{resolvent9}
%\end{equation}
% \item[(iv)]
%All of the above identities hold for $G^{(\mathbb T)}$ instead of $G$ for $\mathbb T \subset \mathcal I$, and in the case where $A$ and $B$ are not diagonal.
\end{itemize}
\end{lemma}
\begin{proof}
All these identities can be proved directly using Schur's complement formula. The reader can also refer to, for example, \cite[Lemma 4.4]{Anisotropic}.
\end{proof}

\subsection{Random Variables with Bounded Moments}

\begin{fact}\label{fact_minv}
	In the setting of Theorem \ref{thm_many_tasks}, with high probability over the randomness of $X$, we have that
	\begin{enumerate}
		\item When $n / p$ converges to $\rho > 1$, the sample covariance matrix $\frac{X^{\top}X}{n}$ is full rank.
		\item The singular values of $Z^{\top}Z$ are greater than $(\sqrt{n} - \sqrt{p})^2 - n \cdot p^{-c_{\varphi}}$ and less than $(\sqrt{n} + \sqrt{p})^2 + n \cdot p^{-c_{\varphi}}$, cf. \citet[Theorem 2.10]{isotropic} and \citet[Lemma 3.12]{DY}.
	\end{enumerate}
\end{fact}

The following lemma gives (almost) sharp concentration bounds for linear and quadratic forms of bounded supported random variables. Here we recall that the stochastic domination ``$\prec$" was defined in Definition \ref{stoch_domination}.
%Besides the proof of Lemma \ref{prop_entry}, we also use it in several other places of this paper, including the proofs in Section \ref{sec_proof_general} and Section \ref{app_iso_cov}.
%It constitutes the main difference between our proof and the one in \cite{KY2}, where the authors used a large deviation bound for random variables with arbitrarily high moments.

\begin{lemma}[Lemma 3.8 of \cite{EKYY1} and Theorem B.1 of \cite{Delocal}]\label{largedeviation}
Let $(x_i)$, $(y_j)$ be independent families of centered and independent random variables, and $(A_i)$, $(B_{ij})$ be families of deterministic complex numbers. Suppose the entries $x_i$ and $y_j$ have variances at most $1$, and $ x_i$ and $ y_j$ satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $q$. %with $q\le n^{-\phi}$ for a small constant $\phi>0$. 
Then we have the following bounds:
%for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
\begin{align}
\Big| \sum_{i=1}^n A_i x_i \Big\vert \prec  q \max_{i} \vert A_i \vert+ \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad &\Big\vert  \sum_{i,j=1}^n x_i B_{ij} y_j \Big\vert \prec q^2 B_d  + q n^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}},\label{eq largedev10}  \\
\Big\vert  \sum_{i=1}^n (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec q n^{1/2}B_d   , \quad &\Big\vert  \sum_{1\le i\ne j\le n} \bar x_i B_{ij} x_j \Big\vert  \prec qn^{1/2}B_o +  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev20} 
\end{align}
where $B_d:=\max_{i} |B_{ii} |$ and $B_o:= \max_{i\ne j} |B_{ij}|.$ Moreover, if the moments of $ x_i$ and $ y_j$ exist up to any order, then we have stronger bounds
\begin{align}
\Big\vert \sum_i A_i x_i \Big\vert \prec  \Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
 \Big\vert  \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec  \Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert  \sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec \Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
\end{align}
%\begin{align}
%\Big\vert \frac1{\sqrt{n}}\sum_i A_i x_i \Big\vert \prec  \frac{1}{\sqrt{n}}\Big(\sum_i |A_i|^2 \Big)^{1/2} , \quad  & \Big\vert \frac1n\sum_{i,j} x_i B_{ij} y_j \Big\vert \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} ,\label{eq largedev1} \\
% \Big\vert  \frac1n \sum_{i} (|x_i|^2-\mathbb E|x_i|^2) B_{ii}  \Big\vert  \prec \frac1{n}\Big( \sum_i |B_{ii} |^2\Big)^{1/2}  ,\quad & \Big\vert \frac1n\sum_{i\ne j} \bar x_i B_{ij} x_j \Big\vert  \prec  \frac{1}{n}\Big(\sum_{i\ne j} |B_{ij}|^2\Big)^{{1}/{2}} .\label{eq largedev2}
%\end{align}
\end{lemma}

As a corollary, we can obtain the following concentration estimates for random variables with bounded $\varphi$-th moment.

\begin{corollary} \label{cor_largedeviation}
Let $Z\in \R^{n\times p}$ be a random matrix as in Assumption \ref{assume_rm}. Then for any deterministic vector $v\in \R^p$, we have that
\be\label{Zv_cor}\left|\|Zv\|^2- n\|v\|^2\right|\le  n^{1-c_\varphi} \|v\|^2\ee
with high probability.
\end{corollary}
 \begin{proof}
We introduce the truncated matrices $\wt Z$ with entries
$ \wt Z_{ij}:= \mathbf 1\left( |Z_{ij}|\le q \right)\cdot Z_{ij} $
for $q= n^{1/2-\frac{\varphi - 4}{2\varphi}}\log n$. By equation \eqref{Ptrunc}, we have that
\begin{equation}\label{XneX222}
\mathbb P(\wt Z= Z) =1-\OO ( (\log n)^{-\varphi}).
\end{equation}
Furthermore, by equation \eqref{meanshif} we have that
\be\label{meanshif222}
|\mathbb E  \wt  Z_{ij}| =\OO(n^{-3/2}), \quad  \mathbb E |\wt  Z_{ij}|^2 =1+ \OO(n^{-1}).
\ee
%From the first estimate in equation \eqref{meanshif}, we can also get a bound on the operator norm:
%\be\label{EZ norm222}\|\E \wt Z^{(1)}\|=\OO(n^{-1/2}) .
%\ee
Then we can centralize and rescale $\wt Z$ as $ \wh Z:=\frac{\wt Z - \E \wt Z }{ (\E|\wt Z_{11}|^2)^{1/2}}.$ 
It suffices to show that 
\be\label{show_whZ}
 \left|\|\wh Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2.
\ee 
In fact, provided that \eqref{show_whZ} holds, using \eqref{meanshif222} it is easy to get that 
$$ \left|\|\wt Zv\|^2- n\|v\|^2\right|\prec n^{1/2} q \|v\|^2,$$
which implies \eqref{Zv_cor} for any fixed value $c_{\varphi}$ within $(0, \frac{\varphi - 4}{2\varphi})$.

For \eqref{show_whZ}, we first observe that for $1\le i \le n$, $(\wh Zv)_i=\sum_{1\le j \le p} \wh Z_{ij}v_j$ are i.i.d random variables of mean zero and variance $\|v\|^2$. Moreover, using \eqref{eq largedev10} we get that 
$$ |(\wh Zv)_i| \prec q \max_{1\le i\le p}|v_i| + \|v\| . $$
Together with the trivial $\max_{1\le i\le p}|v_i| \le \|v\|$, this implies that the random variables $\frac{(\wh Zv)_i}{\|v\|}$, $1\le i \le p$, are i.i.d random variables of mean zero, variance 1 and bounded support $q$. Then applying \eqref{eq largedev20}, we get that
$$ \left|\|\wh Zv\|^2 - n\|v\|^2\right|=\left|\sum_i \left(|(\wh Zv)_i|^2-\E|(\wh Zv)_i|^2\right)\right|\prec n^{1/2} q  \|v\|^2 .
 $$
This concludes \eqref{show_whZ}.
 \end{proof}

Next we can obtain the following concentration estimates for random noise in the setting of Section \ref{sec_same}.

 \begin{corollary}\label{cor_calE}
Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d. random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order. Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
\be\label{vcalE} |v^\top \epsilon^{(i)}| \le \sigma n^{c} \|v\|, \ee
and
\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c} \|B\|_F ,\ee
for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
\be\label{vcalAE3}
\|v^\top \cal E\| \le \sigma n^{c} \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \|B\|_F ,
\ee
 with high probability for any small constant $c>0$.
 \end{corollary}
 \begin{proof}
Note that $\epsilon^{(i)}_j/\sigma$, $1\le i \le t,1\le j \le n$, are i.i.d. random variable of mean zero, variable one and bounded moments up to any order. Then using the first estimate in equation \eqref{eq largedev1}, we can obtain that $|v^\top \epsilon^{(i)}| = \Big|\sum_{j=1}^n v_j \epsilon^{(i)}_j \Big| \prec \sigma \|v\|,$  which concludes \eqref{vcalE} together with the definition of stochastic domination in Definition \ref{stoch_domination}. Similarly, using the second estimate in equation \eqref{eq largedev1}, we can obtain that for $i\ne j$,
 \begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \prec \sigma^2 \Big(\sum_{k,l}|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
 \end{align*}
Using the two estimates in equation \eqref{eq largedev2}, we obtain that 
\begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
&\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
\end{align*}
The above two estimates conclude  \eqref{vcalA2}. Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.
 \end{proof}

### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
edit
add

@@
 	We have improved our result so that the theory matches experiment in Fig 2.b (see Figure \ref{fig_update} for the updated result).
-	DESCRIBE THE IDEA.
+	For the new results, we use some delicate free probability techniques to obtain an exact asymptotic limit of the bias term {\color{red}(I am not sure what details you need here)}. %DESCRIBE THE IDEA.
 
@@
 	However, to the best of our knowledge, the bias equation in Corollary 3.3 and Example 3.4 cannot be obtained from the MP law.
-	ADD COMMENT TO THAT PAPER.
+	Regarding the paper Ledoit and P{\'e}ch{\'e} (2011) mentioned by R2, the authors deal with a single sample covariance matrix $X^\top X$, where the row vectors of $X$ have the same population covariance matrix.
+This case cannot be reduced to our case with two sample covariance matrices $X_1^\top X_1$ and $X_2^\top X_2$ that have different population covariance matrices.
+In particular, if we stack the rows of $X_1$ and $X_2$ into one random matrix $X$, then the row vectors of $X$ have different covariance matrices.
+Moreover, in order to get the best convergence rates, the method in  Ledoit and P{\'e}ch{\'e} (2011) is not sufficient, and some new techniques in random matrix theory are needed.
 

### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
edit

--- 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
@@
 	\textbf{(i)}
-	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning  (cf. Proposition 1 in Wu et al., 20).
+	In the over-parametrized regime, the minimum solution of $f(A ,B)$ (equation 1) reduces to single-task learning  (cf. Proposition 1 in Wu et al., 2020).
 	Hence, studing this regime is problematic without adding explicit regularization or implicit algorithmic biases.
@@
 	As an example of this corollary, we can show that in the setting of Example 2.2, the average prediction loss of all tasks is minimized when $r$ is one.
-	We also thank the reviewer for suggesting the related work.
-	Our work is heavily inspired by Hastie et al., 2019.
+	We also thank the reviewer for suggesting the related work (indeed our work has been heavily inspired by Hastie et al., 2019).
 	We will add these related work to the next version of the paper.
@@
 	\textbf{Response to R5.}
+	In response to the reviewer's comments, we explain the high-level purpose of our work and the importance of why one should care about analyzing the sample size ratios.
+	(1) Hard parameter sharing is a widely used empirical approach to performing multi-task learning.
+	(2) However, there remain critical challenges of applying hard parameter sharing successfully in practice.
+	The first challenge is negative transfer -- this occurs commonly
 \end{document}

### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
add

--- 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
@@
 	We have improved our result so that the theory matches experiment in Fig 2.b (see Figure \ref{fig_update} for the updated result).
-	For the new results, we use some delicate free probability techniques to obtain an exact asymptotic limit of the bias term {\color{red}(I am not sure what details you need here)}. %DESCRIBE THE IDEA.
+	To derive the new results, we use the identity $\tr\left[(X_1^\top X_1 + X_2^\top X_2)^{-2}(X_1^\top X_1)^2\right]= \left.\frac{\rm{d}}{{\rm d} t}\right|_{t=0} \tr\left[(X_1^\top X_1 + t(X_1^\top X_1)^2 + X_2^\top X_2)^{-1}\right]$.
+To calculate the trace of the inverse of $X_1^\top X_1 + t(X_1^\top X_1)^2 + X_2^\top X_2$, we need to study its asymptotic eigenvalue distribution for $t$ close to 0.
+This is complicated but can be done with an extension of the method in our paper.
+%DESCRIBE THE IDEA.
 
@@
 	\textbf{Response to R5.}
+
 \end{document}

### 2021-06-12 revision_journal/abstract.tex
revision wip

--- 2020-10-20 arxiv_full_version/intro.tex
@@
-% The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making the prediction.
+\iffalse
+\begin{frontmatter}
+
+\title{Precise Asymptotics of Transferring from Different Regression in High Dimensions}
+
+\runtitle{Precise Asymptotics of Transferring from Different Regression}
+
+\begin{aug}
+	\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{}},
+	\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2]{}},
+	\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3]{}},\\
+	\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4]{}},
+	\and
+	\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5]{}}
+	\address{${ }^{1}$University of Pennsylvania, ${ }^{2}$Northeastern University, ${ }^{3}$Stanford University
+}
+\end{aug}
+\fi
+
 \begin{abstract}
@@
 
-\section{Introduction}\label{sec_introduction}
+%\begin{keyword}[class=MSC2020]
+%\kwd[Primary ]{62J05}
+%\kwd{60B20}
+%\kwd[; secondary ]{62E20, 62H10}
+%\end{keyword}
 
-Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \citet{C97}.
-Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
+%\begin{keyword}
+%\kwd{Transfer learning, random matrix theory, covariate shift, sample covariance matrices.}
+%\end{keyword}
 
-Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
-		\label{fig_intro_arch}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure*}
-
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
+%\end{frontmatter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please use \tableofcontents for articles %%
+%% with 50 pages and more                   %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\tableofcontents

### 2021-06-12 revision_journal/backup/03:06:2021/examples.tex
revision wip

\section{Theoretical insights}

\subsection{Covariate shift}
\begin{example} %[Covariate shift]
\label{ex_covshift}
%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
%In general, the covariance matrices of the two tasks may be different such as in text classification.
To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds. In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error. Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
\begin{align*}
		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
\end{align*}
%belong to the following bounded set.
%Let $\lambda_i$ be the $i$-th singular value of $M$.
%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
%\vspace{-0.025in}
%{\small}
%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
%\begin{proposition}[Covariate shift]\label{prop_covariate}
%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
%	We have that
%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
%\end{proposition}
%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix.
%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
%Let
%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$
%We now calculate $g(M_0)$. With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds. Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
%\be \nonumber
%\begin{split}
%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
%\end{split}
%\ee
%with high probability for some constant $\e>0$. In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$. We omit the details here.
%
%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
%\begin{align}\label{gvar_extra}
%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
%\end{align}
In fact, from equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
\be\label{est_a12extra}
 a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
\ee
Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that
%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
%\begin{align}\label{approximateteM}
%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
%\end{align}
%where
$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
%With these two bounds, we can easily conclude \eqref{approxteM}.
%
%We have that the test error satisfies
%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
%where $\lambda_p$ is the smallest singular value of $p$ and
%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
By AM-GM inequality, we observe that
$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.

%Hence we get that
%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
%
%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
%\begin{align}\label{gvar_extra2}
%\begin{split}
%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
%\end{split}
%\end{align}
%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
%\end{proof}

\iffalse
For large enough $p$,
%in the left hand side of equation \eqref{lem_cov_shift_eq}:
\begin{align*}
	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
\end{align*}
%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
\fi

%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}.
%Our first observation is that:
However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$. We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$. In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$. When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
%while as As $\lambda$ increases, the severity of covariate shift increases.
We claim the following dichotomy.
\begin{enumerate}
	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
\end{enumerate}
We explain why the above dichotomy happens. We can write the variance limit as
$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
\begin{align*}
\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
\end{align*}
%in this example is equal to
%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
%\begin{align*}
%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
%\end{align*}
%\begin{align*}
%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
%\end{align*}
%where $g(\lambda, a_1) \ge 0$.
%and can be derived from algebraic calculations (details omitted).
We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy. In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
\begin{align*}
 \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
\end{align*}
%\begin{align*}
% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
%\end{align*}
This implies $n_1>n_2$. The other direction follows from a similar argument. % Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$. Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
\end{example}

\iffalse
%FY: Below was the word explanation. I still think the above simple proof is clearer.
In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
The other case when $n_1 < n_2$ is similar.
A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
If $n_1< n_2$, then $f(\lambda)< f(1)$.
\fi

For the bias limit, we have the following proposition.

\begin{proposition}\label{prop_main_RMT}
%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
			\begin{align}
				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
			\end{align}
%			\begin{align}\label{lem_cov_derv_eq}
%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
%			\end{align}
				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
		\be  \label{eq_a34extra}
		\begin{split}
				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{split}
			\ee
			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
\end{proposition}

Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$. Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$. Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$
and
$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
Using these estimates, it is easy to check that
\begin{align}
& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  . \label{bias_LLN}
\end{align}
Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$. However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.

\begin{remark}
%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
%\begin{remark}
The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}. In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$. We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}. However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues. To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder. We leave this problem to future study.

We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
%\end{remark}
\end{remark}

%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}

%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.

To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g. \cite{dobriban2020wonder,dobriban2018high}).

 %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift. Next, we illustrate how varying them impact the prediction loss.
\begin{example}%[Sample sizes]
\label{ex_sample_ratio}
	%We first consider the impact of varying sample sizes.
	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
and $\wt \beta^{(i)}$ denotes the $i$-th
%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.

	\begin{proposition}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
Suppose Assumption \ref{assm_big1} and the above setting of random effect model hold. %in Example \ref{ex_same_cov} hold.
Suppose that for a constant $c_0>0$,
	\be\label{para_rel}
	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
	\ee
 Then we have that for any small constant $c>0$ and large constant $ C>0$,
	%Let $c$ be a sufficiently small fixed constant.
	%In the setting of Corollary \ref{cor_MTL_loss},
%There exists a constant $C>0$ such that
	\be\label{hatw_add1}
	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
	\ee
\end{proposition}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
%and $\wt \beta^{(i)}$ denotes the $i$-th
%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.

We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$. Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations.
Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}. First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero). This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator. Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$. Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.

Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
First, we have positive (resp. negative) transfer if and only if $h(\rho)>0$ (resp. $h(\rho)<0$). Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
\begin{enumerate}
\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.

\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.

\begin{itemize}
\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.

\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$. Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
\end{itemize}
\end{enumerate}
Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial
\be\label{poly2}
 \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
\begin{enumerate}
\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.

\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$. Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
\end{enumerate}

%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance.
%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
\iffalse
Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than

Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
	\begin{align*}
		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
		= \frac{p}{n_1 + n_2 - p},
	\end{align*}
	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
	Similarly, we can calculate the bias limit.
	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.

In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.

{\cor
For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that
	\begin{align}
		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
			\end{align}
Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
For the bias term,
}

Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
We assume that $n_2$ is fixed for simplicity.
%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
%We describe a sketch of the proof.
By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
\begin{enumerate}
	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
	Intuitively, this regime of $d^2$ always helps task two.
	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
\end{enumerate}
\fi
	\end{example}

\paragraph{How does hard parameter sharing scale with sample size $n$?}
Obviously, the concentration error decreases with $n$.
First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.

\begin{assumption}\label{assume_rm}
	Let $\tau > 0$ be a small enough constant.
%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d. entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
	In the high-dimensional setting,
%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
%			\begin{align}\label{assmAhigh}
%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
%			\end{align}
  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
%	\end{enumerate}
\end{assumption}
Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.

\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	With high probability over the randomness of $X$, we have that
		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
\end{fact}
\noindent\textit{Remark.} The above result has a long history in random matrix theory.
For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]

%Finally, for the random noise component, we assume that all of its moments exist.
%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
%\begin{align}\label{assmAhigh2}
%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
%\end{align}
%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.

%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
To illustrate the {bias-variance tradeoff quantitively, we consider an extension of the random-effect model in Example \ref{ex_sample_ratio} to the multi-task setting. %which has been studied for  single-task linear regression and ridge regression (see e.g. \cite{dobriban2020wonder,dobriban2018high}).

\begin{example}%[Random-effect model]
\label{ex_same_cov}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
Suppose that {$\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$} for $ i=1,2,\cdots, t,$
where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
and $\wt \beta^{(i)}$ denotes the $i$-th
%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
In this random-effect model, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}),
%Based on the definition of the random-effect model,
the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
%\begin{align*}
%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
%\end{align*}
\begin{align}\label{betaSbeta}
	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
\end{align}
 with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}.
%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by
$$\lambda_1=\left[1+\OO(p^{-1/2+c})\right]\cdot\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
and
$$ \lambda_i=\left[1+\OO(p^{-1/2+c})\right]\cdot \frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
with high probability.
%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
Then using \eqref{Li_multi2}, we obtain that
\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p. }\]
%We describe a proof sketch.
%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
%Second, using Fact \ref{fact_tr}, one can see that the average variance is
%\begin{align*}
%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
%\end{align*}
%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
%Combined together, we have derived the average prediction loss in the random-effect model.
%If the error is sufficiently small, then
Comparing the above equation with \eqref{L_STL_simple01} (and ignoring the small error), we have the following observations.
%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
%Comparing HPS to STL, we have the following qualitative properties.
%	Suppose $n$ is sufficiently large so that the error is negligible.
%\begin{enumerate}
\begin{enumerate}
	\item {\bf Positive vs. negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.

	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$. Hence increasing the width $r$ of the shared feature representation layer does not help.
	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).

	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$. Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression. More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability. }\]
	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$
	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.

	%samples that is less than $n$ samples to get comparable loss to STL.
	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
	\end{enumerate}

\end{example}

We demonstrate the accuracy of our results in simulations.
While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.

\begin{figure*}[!t]
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
		\caption{Example \ref{ex_same_cov}}
		\label{fig_same_cov}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one. Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
	\label{fig_model_shift_phasetrans}
\end{figure*}

\paragraph{Sample efficiency}
First, we validate the result of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level. %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at. For example, at the cross point, this ratio is 1. }

\paragraph{Sample size ratio}
Second, we validate the result of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
%Again, our estimates are accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$.
The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
Intuitively, this is because bias increases less for smaller $d^2$.
%Our result from Corollary \ref{cor_MTL_loss} explains this trend.

\paragraph{Covariate shift}
Finally, we validate the result of Example \ref{ex_covshift}.
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

%\begin{table}
%	\begin{center}
%		\begin{tabular}{c c c c c}
%			\toprule
%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
%			\midrule
%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
			% {\bf CNN}  & 76\% & - & 32\% & -\\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Taskonomy experiment.}
%	\label{tab:taskonomy}
%\end{table}
%\begin{figure}[!t]
%	\centering
%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
%	\label{fig_same_cov}
%\end{figure}

### 2021-06-12 revision_journal/backup/03:06:2021/exp.tex
revision wip

--- 2020-10-21 arxiv_full_version/experiments_text.tex
@@
-\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
+\section{Algorithmic implications}
+
+%\subsection{Comparison between the averaging and HPS estimators}
+
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+		\For{$j = 1,\dots, T$}
+		\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+		\EndFor
+		\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+		\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+		\State \textbf{break}
+		\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
+One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
+\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
+where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
+$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
+The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
+In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
+
+%\section{Experimental results}
+
+\paragraph{Further Studies on Text Classification Tasks}%\label{sec_text}
 
@@
 
-\paragraph{Covariate shift.}
+\paragraph{Covariate shift}
 Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
 This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, designed to correct covariate shifts.
+To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
 The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \citet{WZR20} for more details about the procedure and the implementation.
+This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
 %We validate our insight on this procedure in the experiments.
@@
 	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}:
+	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \cite{WZR20}:
 	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.

### 2021-06-12 revision_journal/backup/03:06:2021/intro.tex
revision wip

--- 2020-10-16 arxiv/setup.tex
@@
-\subsection{Setup and Main Results}
+\begin{abstract}
+	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
+This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
+We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
+First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
+Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
+We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
+Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
+This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
+\end{abstract}
 
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
-Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \citet{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
-\begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-\end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
+\begin{keyword}[class=MSC2020]
+\kwd[Primary ]{62J05}
+\kwd{60B20}
+\kwd[; secondary ]{62E20, 62H10}
+\end{keyword}
+
+\begin{keyword}
+\kwd{Transfer learning, random matrix theory, covariate shift, sample covariance matrices.}
+\end{keyword}
+
+\end{frontmatter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Please use \tableofcontents for articles %%
+%% with 50 pages and more                   %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\tableofcontents
+
+\section{Introduction}\label{sec_introduction}
+
+Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
+Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
+It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
+Often, hard parameter sharing offers two critical advantages if successfully applied.
+First, it reduces model parameters since all tasks use the same feature space.
+Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
+
+Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
+For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
+Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
+However, how these dataset properties impact HPS has not been well established.
+%It becomes increasingly important to understand HPS' formal generalization properties.
+Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
+Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
+%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
+
+\begin{figure*}[!t]
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
+		\caption{A hard parameter sharing architecture}
+		\label{fig_intro_arch}
+	\end{subfigure}\hfill
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
+		\caption{Varying sample size ratio}
+		\label{fig_intro_sample_size_b}
+	\end{subfigure}
+	\vspace{-0.1in}
+	\caption{
+	Left: an illustrative picture of HPS.
+	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
+	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
+This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
+Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
+	See Section \ref{sec_simulation} for the precise setting.}
+	\label{fig_intro_sample_size}
+\end{figure*}
+
+This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
+We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
+We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
+This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
+For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
+The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
+
+\subsection{Setup and definitions}
+Consider the transfer learning setting with two data sets.
+We denote their sample sizes by $n_1$ and $n_2$.
+For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
+We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
+$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
+In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
+We remark that all these assumptions are natural in high-dimensional statistics.
+
+We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let
+\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
+where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
+entries satisfying
+\begin{equation}\label{assm1}
+\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1,
+\end{equation}
+
+Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
+$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
+
 Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
@@
 
-\textbf{Main results.}
+\subsection{Main results}
 Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \citet{hsu2009multi}).
+examples in \cite{hsu2009multi}).
 We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
@@
 Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-%\begin{enumerate}
-
-\textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \citet{ZSSGM18} has observed empirically.
+\begin{itemize}
+	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
+	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
 	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
 
-\textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
+	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
 In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
@@
 See our discussion of proof techniques below for details.
-%\end{enumerate}
-
-%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-%\squishlist
-%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-%	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-%	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-%\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-%Our study also leads to several algorithmic consequences with practical interest.
-%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-
-%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-%Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
+\end{itemize}
 
@@
 We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
-
-%This part introduces a positive variance reduction effect from adding the source labels.
-%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
-%(i) the negative effect from model shift bias.
-%(ii) the positive effect from variance reduction;
+See Section \ref{sec_conclude} for more discussions of the technical challenge.
 
@@
 We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \citet{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \citet{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \citet{B00,MPR16}.
+The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
+One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
 Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
@@
 Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\citet{Anisotropic} later extended this result to arbitrary covariance matrices.
+In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
+\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
 %On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
@@
 To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
+\HZ{can you please add a discussion of the related work from RMT?}
 
 The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \citet{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \citet{WZR20}, which studied hard parameter sharing for two linear regression tasks.
+For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
+One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
 However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
+%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
 %Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
@@
 
-\textbf{Organizations.}
+\subsection{Organizations}
 The rest of this paper is organized as follows.
@@
 Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
-
-\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.

### 2021-06-12 revision_journal/backup/03:06:2021/manuscript.tex
revision wip

\documentclass[aos,preprint]{imsart}
\usepackage{xr}
	\externaldocument{./suppl}

%% Packages
\def\shownotes{1}
%\usepackage{natbib}
%\setcitestyle{authoryear,open={(},close={)}}
%\renewcommand{\cite}{\citep}
\usepackage[export]{adjustbox}
%\usepackage[margin=1in]{geometry}
%\usepackage{fullpage}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{macro_math}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage{multirow}
\usepackage[us,12hr]{datetime}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{caption,subcaption}
%\usepackage{breqn}

\usepackage{dsfont}

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

\endlocaldefs

\begin{document}

\begin{frontmatter}

\title{High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression}

\runtitle{High-dimensional Asymptotics of Transferring from Different Domains}
%\thankstext{T1}{A sample additional note to the title.}

\begin{aug}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Only one address is permitted per author. %%
%%Only division, organization and e-mail is %%
%%included in the address.                  %%
%%Additional information can be included in %%
%%the Acknowledgments section if necessary. %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{}},
\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2]{}},
\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3]{}},\\
\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4]{} },
\and
\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5]{}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Addresses                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address{${ }^{1}$University of Pennsylvania, ${ }^{2}$Northeastern University, ${ }^{3}$Stanford University
}
%}\address[C]{
%}

\end{aug}

\input{intro}

\medskip
\noindent\textbf{Notations.}
%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
%We can also write $Y = XB^{\star} + \cE$.
%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$. Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$. In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions. 
%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.

\section{Main Results and Proof Techniques}\label{sec_HPS}
In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.

\subsection{Assumptions}
Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
\be \label{conditionA2}
\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
\ee
for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
\be\label{eigen}
\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
\ee
where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
\begin{equation}\label{assm3}
 \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
\ee
%for a small constant $\tau>0$.

We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that 
\be\label{eq_highmoments}
\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
\ee
Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$. 
%Moreover, we assume that 
%\be\label{eq_SNR}
%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
%\ee
%for a small constant $\tau >0$. The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.

In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that 
\be\label{assm2}
1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
\ee
for a small constant $\tau >0$. If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper. The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$ 
are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.

We summarize our basic assumptions here for future reference.
\begin{assumption}\label{assm_big1}
Let $\tau$ be a small constant. 
\begin{enumerate}
\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}. %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).

\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.

\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.

\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.

\end{enumerate}
\end{assumption}

%\subsection{Transfer learning estimators}

%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}

In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error). Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable. We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$ 
Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
\be\label{HPS_loss}
L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
 \ee
We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.

%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.

Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
\begin{align}
L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
\end{align}
Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
where 
\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
is called the bias term, which depends on the model bias between task 1 and task 2, and
\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
is called the variance term, which depends on the noise variance. Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma. In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
%predication loss for the HPS and OLS estimators.

 \begin{lemma}\label{lem_HPS_loss}
 Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$: 
\begin{align}
L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
\end{align}
\begin{align}
L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
& + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
\end{align}
and 
\begin{align}
L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
\end{align}
%Moreover, there exists a constant $C_0>0$ such that with high probability,
%\be\label{loss_large}
%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
%\ee
%with high probability for any small constant $\e>0$. 
\end{lemma}

Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$. In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$. (In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}. To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $. Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small. The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.

%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.

For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.

\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } 
		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
		with high probability for any small constant $\e>0$.
\end{lemma}
 %The above result has a long history in random matrix theory.
If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of 
the inverse Wishart distribution \cite{anderson1958introduction}. For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}). Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate. With Lemma \ref{fact_tr}, we obtain that w.h.p.,
\begin{align}
L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
\end{align}
and
\begin{align}
L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
 \end{align}

On the other hand, much less is known about the predication loss of the HPS estimator. In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far. %\FY{What is known so far about this topic?} 
In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in two different settings: (i) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices. In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates. We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}. In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift. On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$. %Here case (ii) is actually more general than (i) 
%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.   
In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks. We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory. Due to length constraint, we will explore the multi-task learning setting in greater details in other works.

%{\cor discuss about the bias-variance trade-off}
%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.

%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}

\subsection{Covariate shift}\label{sec_diff}

%The previous section assumes that all tasks have the same sample size and feature vectors.
In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
%The different covariates case differs from the same covariates case in two aspects.
%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$. 
In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.

\iffalse
Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
This is because $f(A, B)$ is in general non-convex.
Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
Let $n_1, n_2$ denote task one  and two's sample size, respectively.
Suppose
\begin{align*}
	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
\end{align*}
where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$. $\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.

Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
To motivate our study, we consider a special case where $A_1=A_2=1$.
Hence the HPS estimator is equal to $B$.
%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
\begin{align}
	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
\end{align}
The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.

To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
 %similar to Claim \ref{claim_pred_err}
\begin{align}
	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
\end{align}
Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
\fi

%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$. 
%However, capturing this intuition quantitatively turns out to be technically challenging.
%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$) 
$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
%Let $U\Lambda V^\top$ denote the SVD of $M$ and
Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
\begin{equation}\label{assm32}
|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
\end{equation}
%for some small constant $0<\tau<1$. 
The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.

\begin{theorem}\label{thm_main_RMT}
%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}: 
%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
			\begin{align}\label{lem_cov_shift_eq}
				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
			\end{align}
			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
			\begin{align}
				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
			\end{align}

\end{theorem}

 With \eqref{assm32}, it is easy to see that 
$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor. Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}. %also extends  to the inverse of the sum of two sample covariance matrices.
To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
and plug them into \eqref{lem_cov_shift_eq}.  The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.

\subsection{The case of isotropic covariances} \label{sec_sizeratio}

 In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$. However, the two tasks can have different sample sizes $n_1\ne n_2$. In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}. We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.

\begin{theorem}\label{cor_MTL_loss}
Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian random variables. Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
\be\label{Lvar_samplesize}
L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
\ee
and
\begin{align}
L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
	 \end{align}
Here we define the functions
\begin{align*}
&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
\end{align*}
where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
\begin{align*}
\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}.
%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)}
 \end{align*}
%	In the setting of Example \ref{ex_sample_ratio}, assume that
%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
%	(i) both tasks sample sizes are at least $3p$;
%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
%%	\be\label{choiceofpara0}
%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
%	%\be\label{choiceofpara0}
%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
%	With high probability over the randomness of the input,
%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
%	\begin{align}
%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
%	 \end{align}
%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$. We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
	 \end{theorem}

\iffalse
 We need to state a result for Gaussian matrix ...... Consider
$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
Then we define the following parameters:
\begin{align*}
x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
\end{align*}
We have that
$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter
%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
%where
$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
\fi

We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor. The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}. For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries. In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$. On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}. In the setting of Theorem \ref{cor_MTL_loss}, we can write
\begin{align*}
L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
\end{align*}
where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
\begin{align}\label{Lbias_idea}
L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
\end{align}
up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
\begin{align}\nonumber %\label{Lbias_idea2}
L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
\end{align}
It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}. From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$. Due to the rotational invariance of multivariate Gaussian distributions,
%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence
the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}. In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures. We use that result to obtain a convergence estimate on
$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$. We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.

We believe that the above argument can be extended to the case without the Gaussian assumption. For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}. However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work. Hence we do not pursue this direction in this paper.

\subsection{Proof overview}
For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
The central quantity of interest is the inverse of the sum of two sample covariance matrices.
We note that the variance equation $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ is equal to $(n_1 + n_2)^{-1} \bigtr{W^{-1}}$, where $W$ is
\begin{align}\label{eigen2extra}
\frac{\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V}{n_1 + n_2}.
\end{align}
Here $U\Lambda V^\top$ is defined as the SVD of $M$.
This formulation is helpful because we know that $(Z^{(1)})^{\top} Z^{(1)}$ and $(Z^{(2)})^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance, and $U, V$ are both orthonormal matrices.
For example, if $Z^{(1)},Z^{(2)}$ are both Gaussian random matrices, by rotational invariance, $Z^{(1)} U, Z^{(2)}V$ are still Gaussian random matrices.

Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
We briefly describe the key ideas and refer the interested readers to classical texts such as  \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is a complex function defined as
$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \text{ for any complex } z\in \C\setminus \set{0}.$$
Thus, the Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.

Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where the $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$. Then it is easy to see that the Stieltjes transform of $\mu$ is equal to
\[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(W-z\id)^{-1}\right]. \]
The above matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
We prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.

We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic unit vectors $v\in \R^p$,
$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
}$$
To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
\be\label{defn AF} \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \ee
Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
\begin{equation}\label{linearize_block}
H \define \left( {\begin{array}{*{20}c}
0 & \AF  \\
\AF^{\top} & 0
\end{array}} \right).
\end{equation}
For this block matrix, we define its resolvent as
$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$
for any complex value $z\in \mathbb C$.
Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
\begin{equation} \label{green2}
G(z) =  \left( {\begin{array}{*{20}c}
(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
\AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
\end{array}} \right).%
\end{equation}

\textbf{Variance asymptotic limit.}
In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
\be \label{defn_piw}
\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
\be\label{selfomega_a}
\begin{split}
&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %
&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
\end{split}
\ee
The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since the equations in \eqref{selfomega_a} reduce to equation \eqref{eq_a12extra} when $z=0$.
Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, %
\begin{align*}
\bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
&=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}},
\end{align*}
where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.

\textbf{Bias asymptotic limit.}
For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %
\begin{align}\label{calculate G'}
(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
\end{align}
Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies
\begin{align}\label{cal G'0}
\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
\end{align}
To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of the system of equations \eqref{selfomega_a}.
Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(0)}{\dd z}$.
One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the bias limit.

As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
This is why we consider $W$'s resolvent for a general $z$ (as opposed to the Stieljes transform of its empirical spectral distribution discussed earlier).

\textbf{Schur complement and self-consistent equations.}
First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
The proof of Theorem \ref{thm_main_RMT} is shown in Appendix \ref{appendix RMT}.

\input{examples}

\input{exp}

\input{multitask}

\section{Conclusions}\label{sec_conclude}

This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
We validated our theory and conducted further studies on text classification tasks.
We describe several open questions for future work.
%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
%Second, it would be interesting to extend our result to classification problems such as logistic regression.
First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
%but its singular values will follow a different distribution since the matrix is not symmetric.
 %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
An interesting question is to study logistic regression in a multiple-sample setting.

\begin{supplement}
\textbf{Supplement to ``High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression"}.
In the Internet Appendix \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
%and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
\end{supplement}

\bibliographystyle{imsart-number}
\bibliography{rf,ref_mtl}

\end{document}

### 2021-06-12 revision_journal/backup/03:06:2021/multitask.tex
revision wip

\section{Transferring from multiple source tasks}\label{sec_same}

%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
%We provide a sharp generalization error bound of hard parameter sharing estimators.

Hard parameter sharing is a commonly used architecture in multi-task learning. However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning. In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates. We make this extension for the following reasons. First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly. Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below. Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}. Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}

%Suppose we have $t$ datasets.
%For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
%Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
%We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
%We study the standard hard parameter sharing architecture:
%a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
%See Figure \ref{fig_intro_arch} for an illustration.
%The width of $B$, denoted by $r$, plays an important role in regularization.
%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
%Hence, we assume that $r < t$ in our study.
%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
%We study the following minimization problem:
%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
%	The size of each set is described below.
%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
%\vspace{-0.1in}
%\begin{align}\label{eq_mtl}
%			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
%\end{align}
%\vspace{-0.05in}
%where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.

\vspace{5pt}
\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model
$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}. $\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}. Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.

%\begin{enumerate}
%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
%\end{enumerate}

	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
	\begin{align}
		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
	\end{align}
	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$. %Recall that $r$ is the width of $B$.
We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).

	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss. Hence we only consider the case with $r<t$. \FY{Correct it if the reason is wrong.}

	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
	\begin{align}
		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
	\end{align}
	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
	\begin{align}\label{eq_mtl_output_layer}
		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
	\end{align}
%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$.
Let $\hat A$ be the global minimizer of $g(A)$. Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$. We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in
and its (out-of-sample) prediction loss as
\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee

Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace. To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
\begin{align}\label{eq_A_star}
	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
\end{align}
where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices.
 To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue. Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
 %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction. Then we have the following result.

% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
%Our result is stated as follows.

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}.
Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability,
\be\label{minimizer_beta}
\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
\ee
where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$. Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
	\begin{align}
		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right). \label{Li_multi1}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
Finally, we have a better bound for the averaged prediction loss:  with high probability,
\begin{align}
&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
 &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
\end{align}

\end{theorem}

Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$. Moreover, the factor $(\lambda_r - \lambda_{r+1})^{-1}$ is natural, because the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not stable when $\lambda_r $ and $\lambda_{r+1} $ are close to each other.  The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace. The estimate \eqref{Li_multi1}
 gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$. Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases for the multi-task HPS estimator. On the other hand, the bias term always increases (because the bias in single-task linear regression is zero). Hence as in the transfer learning setting, whether the HPS estimator is better than the OLS estimator depends on an intricate  {bias-variance tradeoff}.
%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
%On the other hand, the bias always increases.}
We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$. Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique. For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.

The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}. Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$. For the reader's convenience, we give the precise statement in Corollary \ref{thm_two_tasks}.
%Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
%In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
% is the matrix formed by the linear model parameters of the two tasks.
Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined. %Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.

\begin{corollary}\label{thm_two_tasks}
Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2\equiv n$. Let $c>0$ be an arbitrary (small) constant. Then we have that with high probability,
\be\label{minimizer_beta1}
\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
\ee
where $u_{\hat a}$ is the unit vector defined as
$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
%for task 2,  % over the randomness of the input,
Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
	\begin{align}
		& \bigabs{L_2(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) \cdot B^{\star}A^{\star}  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	 where $A^\star(2)$ denotes the second entry of $A^\star$.
	 \end{corollary}

%The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.

%It is not hard to extend the above result to the cases with more than two tasks. We make this extension for the following reasons. First, it provides a clearer geometric intuition than the two-task setting as we will discuss below. Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}. Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.

%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
%\begin{align}
%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
%\end{align}
%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
%Compared to the prediction loss of single-task learning (cf. equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
%We show the generalization error of hard parameter sharing estimators.
%Before stating the result, we define the following notations.

%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
%\medskip
%
%\noindent\textbf{Comparison to single-task learning (STL).}
%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
%On the other hand, the bias always increases.

%\FY{add simulations to check our results; discuss motivations and possible applications}
\iffalse
In this paper, we consider a natural extension of the estimator $\hat \beta^{\rm{TL}} $, that is, the \emph{hard parameter sharing} (HPS) estimator, which has been a standard type of estimator in multi-task learning \FY{citations}. More precisely, we study the following HPS architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$. Then we study the following minimization problem:
\begin{align}\label{eq_tsl}
			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
\end{align}
where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as
\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
Note that $\hat \beta^{\rm{TL}}$ is a special case of $\hat{\beta}_i^{\MTL}$ by setting $A_1=A_2=1$.

For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that
	\begin{align}
		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
	\end{align}
where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers. Could you replace $A$ with another symbol (say $x$)?}
 \begin{align}
		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
	\end{align}
Let $\hat a$ be the minimizer of $g(a)$. Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.  Then the HPS estimator \eqref{def_HPS} for the target task 2 is
\be\label{HPS_est}
\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
\ee
\fi

### 2021-06-12 revision_journal/backup/Jan 01 2021/manuscript.tex
revision wip

\documentclass[aos,preprint]{imsart}
\usepackage{xr}
	\externaldocument{./suppl}

%% Packages
\def\shownotes{0}
%\usepackage{natbib}
%\setcitestyle{authoryear,open={(},close={)}}
%\renewcommand{\cite}{\citep}
\usepackage[export]{adjustbox}
%\usepackage[margin=1in]{geometry}
%\usepackage{fullpage}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{macro_math}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage{multirow}
\usepackage[us,12hr]{datetime}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{caption,subcaption}
%\usepackage{breqn}

\usepackage{dsfont}

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Uncomment next line to change            %%
%% the type of equation numbering           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Axiom, Claim, Corollary, Hypothezis, %%
%% Lemma, Theorem, Proposition              %%
%% use \theoremstyle{plain}                 %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\theoremstyle{plain}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Assumption, Definition, Example,     %%
%% Notation, Property, Remark, Fact         %%
%% use \theoremstyle{remark}                %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please put your definitions here:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\endlocaldefs

\begin{document}

\begin{frontmatter}
\title{Hard Parameter Sharing in High-dimensional Linear Regression}
%\title{A sample article title with some additional note\thanksref{t1}}
\runtitle{Hard Parameter Sharing in High-dimensional Linear Regression}
%\thankstext{T1}{A sample additional note to the title.}

\begin{aug}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Only one address is permitted per author. %%
%%Only division, organization and e-mail is %%
%%included in the address.                  %%
%%Additional information can be included in %%
%%the Acknowledgments section if necessary. %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu} \thanks{Fan Yang and Hongyang R. Zhang contributed equally.}}
\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}\samethanks} 
\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3,mark]{senwu@stanford.edu}} 
\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4,mark]{suw@wharton.upenn.edu} }
\and
\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5,mark]{chrismre@cs.stanford.edu}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Addresses                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address[A]{Department of Statistics,
University of Pennsylvania,
\printead{e1,e4}}
\address[B]{Khoury College of Computer Sciences, Northeastern University,
\printead{e2}}
\address[C]{Department of Computer Science, Stanford University,
\printead{e3,e5}}

\end{aug}

\begin{abstract}
	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases. This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks? We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio. First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features. Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts. We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions. Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias. This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
\end{abstract}

\begin{keyword}[class=MSC2020]
\kwd[Primary ]{62J05}
\kwd{60B20}
\kwd[; secondary ]{62E20, 62H10}
\end{keyword}

\begin{keyword}
\kwd{Hard parameter sharing, high-dimensional linear regression, random matrix theory, sample covariance matrices}
\end{keyword}

\end{frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please use \tableofcontents for articles %%
%% with 50 pages and more                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\tableofcontents

\section{Introduction}\label{sec_introduction}

Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
Often, hard parameter sharing offers two critical advantages if successfully applied.
First, it reduces model parameters since all tasks use the same feature space.
Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.

Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
However, how these dataset properties impact HPS has not been well established.
%It becomes increasingly important to understand HPS' formal generalization properties.
Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.

\begin{figure*}[!t]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
		\caption{A hard parameter sharing architecture}
		\label{fig_intro_arch}
	\end{subfigure}\hfill
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
		\caption{Varying sample size ratio}
		\label{fig_intro_sample_size_b}
	\end{subfigure}
	\vspace{-0.1in}
	\caption{
	Left: an illustrative picture of HPS.
	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward. This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases. Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
	See Section \ref{sec_simulation} for the precise setting.}
	\label{fig_intro_sample_size}
\end{figure*}

This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.

\subsection{Setup and Main Results}

%We assume that there are multiple datasets that all follow (potentially different) linear models.
%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
Suppose we have $t$ datasets.
For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
We study the standard hard parameter sharing architecture:
a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
See Figure \ref{fig_intro_arch} for an illustration.
%The width of $B$, denoted by $r$, plays an important role in regularization.
%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
%Hence, we assume that $r < t$ in our study.
%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
We study the following minimization problem:
%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
%	The size of each set is described below.
%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
%\vspace{-0.1in}
\begin{align}\label{eq_mtl}
			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
\end{align}
%\vspace{-0.05in}
where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
The critical questions are:
(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?

\medskip
\noindent\textbf{Main results.}
Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf. examples in \cite{hsu2009multi}).
We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.

Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
\begin{itemize}
	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.

	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss. In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows. These two trends result from different bias-variance tradeoffs. This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.

	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts. For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift. Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum. We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts. See our discussion of proof techniques below for details.
\end{itemize}

%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
%Without loss of generality, let the $t$-th task denote the target task.
%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
%Hence adding more labeled data can help improve its test performance.
%$B\in\real^{p\times r}$
%$\set{W_i \in \real^{r}}_{i=1}^t$

%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.

%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
%distribution with covariance matrix $\Sigma_i$.

%We extend our result to the transfer learning
%in the setting of high-dimensional linear regression.
%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
%These results are described more precisely in Section \ref{sec_main}.

%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
%\textbf{Task similarity:}
%\textbf{Data sizes:}
%\textbf{Covariate shift:}
%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
%\squishlist
%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
%	As model distance increases, the bias becomes larger, resulting in negative transfer.
%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
%	The unexplained observations are caused by an error term from the bias.
%	We discuss these in Section \ref{sec_insight}.
%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
%	Otherwise, the variance reduces less with covariate shift.
%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
%\squishend
%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.

%Our study also leads to several algorithmic consequences with practical interest.
%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.

%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
%Finally, we validate our three theoretical findings on sentiment analysis tasks.

% plus an identity matrix,  due to lack of freeness
%\HZ{add why this is challenging}

Finally, we discuss the practical implications of our work.
Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.

\medskip
\noindent\textbf{Proof techniques.}
There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
The proof of our second result is significantly more involved because of different sample sizes and covariate shifts. We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf. Theorem \ref{thm_main_RMT}).
We use recently developed techniques from random matrix theory to show a sharp convergence rate.
% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
%\HZ{add several sentences on the technical insight}
One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
See Section \ref{sec_conclude} for more discussions of the technical challenge.

%This part introduces a positive variance reduction effect from adding the source labels.
%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
%(i) the negative effect from model shift bias.
%(ii) the positive effect from variance reduction;

\subsection{Related Work}

There is a large body of classical and recent works on multi-task learning.
We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.

Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).

The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
However, their results only apply to sample size regimes at least logarithmic factors of dimension.
%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.

%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
%For such models, their output dimension plays an important role of regularization \cite{KD12}.
%Below, we describe several lines of work that are most related to this work.

%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
%Our work is closely related to Wu et al. \cite{WZR20}.
%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
%\todo{spell out the challenge more explicitly}

%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
%We believe that our theoretical framework can apply to other approaches to multi-task learning.

\smallskip
\noindent\textbf{Organizations.}
The rest of this paper is organized as follows.
In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
In Sections \ref{sec_simulation}, we validate our results in simulations.
In Section \ref{sec_conclude}, we summarize our work and discuss future work.
Section \ref{sec_text} describes our study on text classification tasks.
Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.

\medskip
\noindent\textbf{Notations.}
%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
%We can also write $Y = XB^{\star} + \cE$.
%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$. Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$. In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions. 
%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.

\section{Hard parameter sharing estimator}\label{sec_HPS}

Consider the transfer learning setting with two data sets. We denote their sample sizes by $n_1$ and $n_2$. For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates. We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
We study the standard hard parameter sharing architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$. Then we study the following minimization problem:
\begin{align}\label{eq_tsl}
			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
\end{align}
where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$. We remark that all these assumptions are natural in high-dimensional statistics.

We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let 
\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d. entries satisfying
\begin{equation}\label{assm1}
\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1, 
\end{equation}
Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
\be \label{conditionA2}
\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
\ee
for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
\be\label{eigen}
\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
\ee
where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
\begin{equation}\label{assm3}
 \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
\ee
%for a small constant $\tau>0$.

We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that 
\be\label{eq_highmoments}
\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
\ee
Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$. 
%Moreover, we assume that 
%\be\label{eq_SNR}
%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
%\ee
%for a small constant $\tau >0$. The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.

In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that 
\be\label{assm2}
1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
\ee
for a small constant $\tau >0$. If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper. The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$ 
are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.

We summarize our basic assumptions here for future reference.
\begin{assumption}\label{assm_big1}
Let $\tau$ be a small constant. 
\begin{enumerate}
\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}. %and (\ref{assm2}). We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).

\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.

\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.

\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.

\end{enumerate}
\end{assumption}

For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that  
	\begin{align}
		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
	\end{align}
where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers. Could you replace $A$ with another symbol (say $x$)?}
 \begin{align}
		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
	\end{align}
Let $\hat a$ be the minimizer of $g(a)$. Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.  Then the HPS estimator \eqref{def_HPS} for the target task 2 is
\be\label{HPS_est}
\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
\ee

In this paper, we study the out-of-sample predication loss (test error) of $\hat{\beta}_2^{\MTL} (\hat a)$. Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable. We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$ 
Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
\be\label{HPS_loss}
L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
 \ee
We will compare it to the out-of-sample predication loss $L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator 
$$\hat \beta^{\STL}= [(X^{(2)})^\top X^{(2)}]^{-1}(X^{(2)})^\top Y^{(2)}$$ as a baseline.

Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
\begin{align}
L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
\end{align}
Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
where 
\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
is called the bias term, which depends on the model bias between task 1 and task 2, and
\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
is called the variance term, which depends on the noise variance. Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma. In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
%predication loss for the HPS and OLS estimators.

 \begin{lemma}\label{lem_HPS_loss}
 Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$: 
\begin{align}
L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
\end{align}
and 
\begin{align}
L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
\end{align}
%Moreover, there exists a constant $C_0>0$ such that with high probability,
%\be\label{loss_large}
%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
%\ee
%with high probability for any small constant $\e>0$. 
\end{lemma}

Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$. In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$. (In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}. To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $. Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small. The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.

%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.

For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.

\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	Under Assumption \ref{assm_big1}, we have that
		\[ \bigtr{\Sigma^{(2)} \frac1{(X^{(2)})^\top X^{(2)} }  } = \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } = \frac{p}{n_2 - p} \cdot \left[1+ \OO\left( \frac{p^{\e}}{\sqrt{np}} \right)\right] \]
		with high probability for any small constant $\e>0$.
\end{lemma}
 %The above result has a long history in random matrix theory.
If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}. For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}). Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate. With Lemma \ref{fact_tr}, we obtain that w.h.p.,
\begin{align}
L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   . \label{L_STL_simple01}
\end{align}

On the other hand, much less is known about the predication loss of the HPS estimator. In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far. \FY{What is known so far about this topic?} In the rest of this paper, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in three different settings of increasing complexity: (i) same covariates $X^{(1)}=X^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (iii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices. In each case, we provide the exact asymptotic bias and variance limits, together with almost sharp convergence rates.  
In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.

%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.

\section{HPS estimator: Bias-variance tradeoff}\label{sec_same}

%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
%We provide a sharp generalization error bound of hard parameter sharing estimators.

In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$. We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix  
$ {B^\star}^\top \Sigma  B^\star,$ where $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ is the matrix formed by the linear model parameters of the two tasks. Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is well-defined. Otherwise, Theorem \ref{thm_two_tasks} will give a null result.

\begin{theorem}\label{thm_two_tasks}
Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2$. Let $c>0$ be an arbitrary small constant. Then we have that with high probability, 
\be\label{minimizer_beta1}
\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2}, 
\ee
where $u_{\hat a}$ is a unit vector defined as
$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
%for task 2,  % over the randomness of the input, 
Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
	\begin{align}
		& \bigabs{L(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) (B^{\star}A^{\star})  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	 where $A^\star(2)$ denotes the second entry of $A^\star$.
	 \end{theorem}

Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$. Moreover, the factor $(\lambda_1 - \lambda_{2})^{-1}$ is natural, because the two eigenspaces of ${B^{\star}}^{\top}\Sigma B^{\star}$ are not stable when $\lambda_1 $ and $\lambda_{2} $ are close to each other. The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.

It is not hard to extend the above result to the cases with more than two tasks. We make this extension for the following reasons. First, it provides a clearer geometric intuition than the two-task setting as we will discuss below. Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}. Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.

%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
%\begin{align}
%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
%\end{align}
%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
%Compared to the prediction loss of single-task learning (cf. equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
%We show the generalization error of hard parameter sharing estimators.
%Before stating the result, we define the following notations.

\vspace{5pt}
\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model 
$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d. entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}. $\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}. Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.

%\begin{enumerate}
%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
%\end{enumerate}

	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
	\begin{align}
		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
	\end{align}
	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$. %Recall that $r$ is the width of $B$.
We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).

	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss. Hence we only consider the case with $r<t$. \FY{Correct it if the reason is wrong.}

	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
	\begin{align}
		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
	\end{align}
	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
	\begin{align}\label{eq_mtl_output_layer}
		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
	\end{align}
%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
Let $\hat A$ be the global minimizer of $g(A)$. Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$. We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
and its (out-of-sample) prediction loss as
\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee

Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace. To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is the covariance of the task labels):
\begin{align}\label{eq_A_star}
	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
\end{align}
where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
 To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue. Otherwise, Theorem \ref{thm_many_tasks} will give a null result. 
 %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction. Then we have the following result.

% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
%Our result is stated as follows.

\begin{theorem}\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary small constant. Then for any task $i = 1,  \cdots, t$, we have that high probability, 
\be\label{minimizer_beta}
\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} , 
\ee
where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$. Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  
	\begin{align}
		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right). \label{Li_multi1}
		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
	\end{align}
	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$. %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
Finally, we have a better bound for the averaged prediction loss:  
\begin{align}
&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
 &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 ,\label{Li_multi2}
\end{align}
with high probability.
\end{theorem}

 The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace. The estimate \eqref{Li_multi1} shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$. Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases in the HPS for multi-task setting. On the other hand, the bias term always increases, because the bias in single-task linear regression is zero. Hence whether the HPS estimator is better than the OLS estimator depends on an intricate \emph{bias-variance tradeoff}. 
%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
%On the other hand, the bias always increases.}
We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$. Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique. For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.

The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}. Moreover, Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.

%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
%\medskip
%
%\noindent\textbf{Comparison to single-task learning (STL).}
%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
%On the other hand, the bias always increases.

\iffalse
\paragraph{How does hard parameter sharing scale with sample size $n$?}
Obviously, the concentration error decreases with $n$.
First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.

\begin{assumption}\label{assume_rm}
	Let $\tau > 0$ be a small enough constant.
%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d. entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
	In the high-dimensional setting,
%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
%			\begin{align}\label{assmAhigh}
%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
%			\end{align}
  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
%	\end{enumerate}
\end{assumption}
Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.

\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	With high probability over the randomness of $X$, we have that
		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
\end{fact}
\noindent\textit{Remark.} The above result has a long history in random matrix theory.
For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
		\fi

%Finally, for the random noise component, we assume that all of its moments exist.
%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
%\begin{align}\label{assmAhigh2}
%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
%\end{align}
%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.

%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
To illustrate the {bias-variance tradeoff quantitively, we consider a random-effect model, which has been studied for  single-task linear regression and ridge regression (see e.g. \cite{dobriban2020wonder,dobriban2018high}).

\begin{example}[Random-effect model]\label{ex_same_cov}
Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
More precisely, %we have
$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
and $\wt \beta^{(i)}$ denotes the $i$-th 
%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. 
%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.

In the random-effect model described above, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
%Based on the definition of the random-effect model, 
the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
%\begin{align*}
%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
%\end{align*}
\begin{align}\label{betaSbeta}
	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
\end{align}
 with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}. 
%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
$$\lambda_1=(1+\OO(p^{-1/2+c}))\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
and
$$ \lambda_i=(1+\OO(p^{-1/2+c}))\frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
with high probability. 
%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
Then using \eqref{Li_multi2}, we obtain that
\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p. }\]
%We describe a proof sketch.
%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
%Second, using Fact \ref{fact_tr}, one can see that the average variance is
%\begin{align*}
%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
%\end{align*}
%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
%Combined together, we have derived the average prediction loss in the random-effect model.
If the error is sufficiently small, then comparing the above equation with \eqref{L_STL_simple01}, we have the following observations. 
%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
%Comparing HPS to STL, we have the following qualitative properties.
%	Suppose $n$ is sufficiently large so that the error is negligible.
%\begin{enumerate}
\begin{enumerate}
	\item {\bf Positive vs. negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.

	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$. Hence increasing the width $r$ of the shared feature representation layer does not help.
	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).

	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$. Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression. More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability. }\]
	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$ 
	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.

	%samples that is less than $n$ samples to get comparable loss to STL.
	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
	\end{enumerate}

\end{example}

\FY{add applications, simulations, and algorithm consequences of the results in this section}

\section{HPS estimator: Varying sample sizes} 	\label{sec_sizeratio}

 In this section, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$. However, the two tasks can have different sample sizes $n_1\ne n_2$. In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}. We will use these results to illustrate the effect of the sample sizes on the predication loss of the $\MTL$ estimator.

\begin{theorem}\label{cor_MTL_loss}
Under Assumption \ref{assm_big1} holds, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian random variables. Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$: 
\be\label{Lvar_samplesize}
L_{\var}(a)= \left[ \cal L_1(a)+ \OO\left(\frac{p^{c}}{n_1}\right)\right] \cdot   \sigma^2 ,
\ee
and 
\begin{align}
L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right]   \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
	 \end{align}
Here we define the functions  
\begin{align*}
&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
\end{align*}
where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
\begin{align*}
\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}. 
%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)} 
 \end{align*}
%	In the setting of Example \ref{ex_sample_ratio}, assume that
%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
%	(i) both tasks sample sizes are at least $3p$;
%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
%%	\be\label{choiceofpara0}
%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
%	%\be\label{choiceofpara0}
%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
%	With high probability over the randomness of the input,
%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
%	\begin{align}
%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
%	 \end{align}
%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$. We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
	 \end{theorem}

\iffalse
 We need to state a result for Gaussian matrix ...... Consider 
$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
Then we define the following parameters:
\begin{align*}
x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
\end{align*}
We have that
$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter 
%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
%where 
$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
\fi
The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}. For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$. In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$. On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}. In the setting of Theorem \ref{cor_MTL_loss}, we can write  
\begin{align*}
L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
\end{align*}
where we denote $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. Using the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
\begin{align}\label{Lbias_idea}
L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
\end{align}
up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
\begin{align}\nonumber %\label{Lbias_idea2}
L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
\end{align}
It is well-known that the empirical eigenvalue distributions (ESD) of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$ satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}. From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$. Due to the Gaussian assumption, $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other. Hence the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$. In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measure. We use that result to obtain a convergence estimate on 
$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.

We believe that the above argument can be extended to the case without Gaussian assumption. For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}. However, to apply the result in \cite{EKN_poly}, we need to check some hard technical conditions for our setting. Hence we do not pursue this direction in this paper.
%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}

Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.

 %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift. Next, we illustrate how varying them impact the prediction loss.
\begin{example}[Sample sizes]\label{ex_sample_ratio}
	%We first consider the impact of varying sample sizes.
	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
	We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$. First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
	\begin{proposition}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
Suppose Assumption \ref{assm_big1} and the setting in Example \ref{ex_same_cov} hold. Suppose that
	\be\label{para_rel}
	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
	\ee
 for a constant $c_0>0$. Then we have that for any small constant $c>0$ and large constant $ C>0$,
	%Let $c$ be a sufficiently small fixed constant.
	%In the setting of Corollary \ref{cor_MTL_loss}, 
%There exists a constant $C>0$ such that
	\be\label{hatw_add1}
	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
	\ee
\end{proposition}
%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
%More precisely, %we have
%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
%and $\wt \beta^{(i)}$ denotes the $i$-th 
%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.

Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (1+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations. 
Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}. First, we notice that the variance term is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term is always positive. Moreover, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.

For a fixed $n_2$, we study the intricate bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$,
$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, which gives the quantitive information transfer from the source task to the target task.
First, we have positive (resp. negative) transfer if and only if $h(\rho)>0$ (resp. $h(\rho)<0$). Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
Then we observe the following dichotomy.
\begin{enumerate}
\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.

\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.

\begin{itemize}
\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.

\item If $(1+\rho_2)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$. Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
\end{itemize}
\end{enumerate}
Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial 
\be\label{poly2}
 \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
Then we observe the following dichotomy.
\begin{enumerate}
\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.

\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$. Hence the information transfer achieves the global minimum at $\rho=\rho_c$.
\end{enumerate}

%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance. 
%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
\iffalse
Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than

Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
	\begin{align*}
		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
		= \frac{p}{n_1 + n_2 - p},
	\end{align*}
	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
	Similarly, we can calculate the bias limit.
	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.

In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.

{\cor 
For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
	\begin{align}
		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
			\end{align}
Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
For the bias term,
}

Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
We assume that $n_2$ is fixed for simplicity.
%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
%We describe a sketch of the proof.
By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
\begin{enumerate}
	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
	Intuitively, this regime of $d^2$ always helps task two.
	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
\end{enumerate}
\fi

	\end{example}

	\FY{add applications, simulations, and algorithm consequences of the results in this section}

\section{HPS estimator: Covariate shift}\label{sec_diff}

%The previous section assumes that all tasks have the same sample size and feature vectors.
Finally, in this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
%The different covariates case differs from the same covariates case in two aspects.
%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift'', which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$. In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give a rough estimate on it.

\iffalse
Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
This is because $f(A, B)$ is in general non-convex.
Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
Let $n_1, n_2$ denote task one  and two's sample size, respectively.
Suppose
\begin{align*}
	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
\end{align*}
where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$. $\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.

Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
To motivate our study, we consider a special case where $A_1=A_2=1$.
Hence the HPS estimator is equal to $B$.
%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
\begin{align}
	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
\end{align}
The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.

To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
 %similar to Claim \ref{claim_pred_err}
\begin{align}
	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
\end{align}
Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
\fi

%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$. 
%However, capturing this intuition quantitatively turns out to be technically challenging.
%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
To capture this misalignment quantitatively, we introduce the covariate shift matrix (rescaled by $a$) 
$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
%Let $U\Lambda V^\top$ denote the SVD of $M$ and
Let $\lambda_1(a), \lambda_2(a), \dots, \lambda_p(a)$ denote the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
\begin{equation}\label{assm32}
|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
\end{equation}
%for some small constant $0<\tau<1$. 
The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.

\begin{theorem}\label{thm_main_RMT}
%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for the variance term $L_{\var}(a)$ in \eqref{Lvar}: 
%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
			\begin{align}\label{lem_cov_shift_eq}
				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
			\end{align}
			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following self-consistent equations
			\begin{align}
				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
			\end{align}

\end{theorem}

 With \eqref{assm32}, it is easy to see that 
$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$. Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}. %also extends  to the inverse of the sum of two sample covariance matrices.
To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
and plug them into equation \eqref{lem_cov_shift_eq}.  The proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{appendix RMT} in the supplement \cite{MTL_suppl}.
%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.

\begin{example}[Covariate shift]\label{ex_covshift}
%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
%In general, the covariance matrices of the two tasks may be different such as in text classification.
To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds. In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error. Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
\begin{align*}
		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
\end{align*}
%belong to the following bounded set.
%Let $\lambda_i$ be the $i$-th singular value of $M$.
%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
%\vspace{-0.025in}
%{\small}
%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
%\begin{proposition}[Covariate shift]\label{prop_covariate}
%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
%	We have that
%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
%\end{proposition}
%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix. 
%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
%Let 
%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
%We now calculate $g(M_0)$. With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds. Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
%\be \nonumber
%\begin{split}
%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
%\end{split}
%\ee
%with high probability for some constant $\e>0$. In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$. We omit the details here. 
%
%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
%\begin{align}\label{gvar_extra}
%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
%\end{align}
From equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
\be\label{est_a12extra}
 a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
\ee
Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that 
%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
%\begin{align}\label{approximateteM}
%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
%\end{align}
%where
$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
%With these two bounds, we can easily conclude \eqref{approxteM}. 
%
%We have that the test error satisfies
%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
%where $\lambda_p$ is the smallest singular value of $p$ and
%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
By AM-GM inequality, we observe that 
$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.

%Hence we get that 
%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
%
%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
%\begin{align}\label{gvar_extra2}
%\begin{split}
%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
%\end{split}
%\end{align}
%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
%\end{proof}

\iffalse
For large enough $p$,
%in the left hand side of equation \eqref{lem_cov_shift_eq}:
\begin{align*}
	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
\end{align*}
%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
\fi

%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}. 
%Our first observation is that:
However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$. We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$. In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$. When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift. 
%while as As $\lambda$ increases, the severity of covariate shift increases.
We claim the following dichotomy.
\begin{enumerate}
	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
\end{enumerate}
We explain why the above dichotomy happens. We can write that variance limit as
$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
\begin{align*}
\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
\end{align*}
%in this example is equal to
%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
%\begin{align*}
%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
%\end{align*}
%\begin{align*}
%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
%\end{align*}
%where $g(\lambda, a_1) \ge 0$.
%and can be derived from algebraic calculations (details omitted).
We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy. In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
\begin{align*}
 \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
\end{align*}
%\begin{align*}
% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
%\end{align*}
This implies $n_1>n_2$. The other direction follows from a similar argument. % Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$. Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
\end{example}

\iffalse
%FY: Below was the word explanation. I still think the above simple proof is clearer.
In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
The other case when $n_1 < n_2$ is similar.
A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
If $n_1< n_2$, then $f(\lambda)< f(1)$.
\fi

For the bias limit, we have the following proposition.

\begin{proposition}\label{prop_main_RMT}
%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for the bais term $L_{\bias}(a)$ in \eqref{Lbias}: 
			\begin{align}
				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 + n_1^{-1/2+2/\varphi + c}\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
			\end{align}
%			\begin{align}\label{lem_cov_derv_eq}
%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
%			\end{align}
				uniformly in all $a\in \R$. Here $\Pi(a)$ is a $p\times p$ matrix defined as
				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
				$\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, and $(a_{3},a_4)$ is the solution of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
		\be  \label{eq_a34extra}
		\begin{split}
				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
%				= b_0.
			\end{split}
			\ee  
			where recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
\end{proposition}

Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$. Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$. Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$ 
and
$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
Using these estimates, it is easy to check that  
\begin{align}
& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  . \label{bias_LLN}
\end{align}
Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ by the law of large numbers in the regime $n_1\gg p$. However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.

\begin{remark}
%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
%\begin{remark}
The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}. In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$. We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}. However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues. To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder. We leave this problem to future study.

We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for dealing with the bias term also fails, because we cannot reduce the problem into the study of the addition of two random matrices that are asymptotically freely independent. 
%\end{remark}
\end{remark}

\FY{add applications, simulations, and algorithm consequences of the results in this section}

\section{Experiments}

\subsection{Simulation Studies}\label{sec_simulation}

We demonstrate the accuracy of our results in simulations.
While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.

\begin{figure*}[!t]
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
		\caption{Example \ref{ex_same_cov}}
		\label{fig_same_cov}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one. Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
	\label{fig_model_shift_phasetrans}
\end{figure*}

\paragraph{Sample efficiency.}
First, we validate the result of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level. %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at. For example, at the cross point, this ratio is 1. }

\paragraph{Sample size ratio.}
Second, we validate the result of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
%Again, our estimates are accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
Intuitively, this is because bias increases less for smaller $d^2$.
%Our result from Corollary \ref{cor_MTL_loss} explains this trend.

\paragraph{Covariate shift.}
Finally, we validate the result of Example \ref{ex_covshift}.
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

%\begin{table}
%	\begin{center}
%		\begin{tabular}{c c c c c}
%			\toprule
%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
%			\midrule
%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
			% {\bf CNN}  & 76\% & - & 32\% & -\\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Taskonomy experiment.}
%	\label{tab:taskonomy}
%\end{table}
%\begin{figure}[!t]
%	\centering
%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
%	\label{fig_same_cov}
%\end{figure}

\subsection{Further Studies on Text Classification Tasks}\label{sec_text}

Our results and simulations are all in the high-dimensional linear regression setting.
How well do they extend to other scenarios?
In this section, we conduct further studies on six text classification datasets.
Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
%The question is to predict positive or negative sentiment expressed in the text.
Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings. For LSTM, we add a shared feature representation layer on top of word embeddings.}

%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.
%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
%There are 14 diseases (tasks) for every image that we would like to predict.
%We use densenet121 as the shared module \cite{huang2017densely}.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
%We evaluate three model choices.
%\textit{Predicting transfer effect via STL results.}
%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
%A common challenge in the study of MTL is that the results can be hard to understand.
%It is difficult to predict when MTL performs well without running extensive trials.
%Our insight is that we can use STL results to help understand MTL results.
%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
%The results show that STL results are indicative of MTL results.

\paragraph{Sample size ratio.}
First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.

These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
Concretely, here is one implementation of this idea.
%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
\begin{itemize}
	\item We divide the training data into $S$ batches.
	We divide the training procedure into $S$ stages. During every stage, we progressively add one more data batch.
	\item During every stage, we train for $T$ epochs using only the $S$ batches. If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\end{itemize}
If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
We evaluate the progressive training procedure on the six text classification datasets.
First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
We include all of task two's data and progressively add task one's data using the procedure described above.
Since the prediction accuracy has been controlled the same, we compare the computational cost.
We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
Second, we conduct multi-task training on all six datasets jointly.
We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
%As a further validation, excluding TREC, we observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

%	\begin{subfigure}[b]{0.33\textwidth}
%		\centering
%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
%		\caption{Task similarity}
%		\label{fig_ab_sim}
%	\end{subfigure}%
%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
%	(c)
%	Note: (S) denotes the source task and (T) denotes the target task.}

%\begin{minipage}[t]{.58\textwidth}
%	\vspace{-0.1in}
%	\centering
%  \begin{tabular}{c c c c c}
%	\toprule
%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
%		& Precision &  Recall & Precision &  Recall \\
%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
%	\bottomrule
%	\end{tabular}
%	\vspace{0.1in}
%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
%	\label{tab:mtl_better_than_stl}
%\end{minipage}%
%\quad

\paragraph{Covariate shift.}
Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
This highlights the need for correcting covariate shifts when the sample size ratio rises.
To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
The idea is to add an alignment module between the input and the shared module $B$.
This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
%We validate our insight on this procedure in the experiments.
%We implement the covariance alignment procedure following \cite{WZR20}.

We conduct multi-task training on all $15$ task pairs from the six datasets.
In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
To get a robust comparison, we average the improvements over the 15 task pairs.
The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.

%\begin{figure}[!t]
%	\centering
%	\begin{subfigure}[b]{0.5\textwidth}
%		\centering
%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
%		\caption{Averaged over all 16 task pairs}
%		\label{fig_ab_cov}
%	\end{subfigure}\hfill
%	\begin{subfigure}[b]{0.5\textwidth}
%		\centering
%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
%		\caption{An example task pair}
%		\label{fig_cov_a}
%	\end{subfigure}
%	\caption{ (TREC and CR)}
%\end{figure}

%\textbf{Further results of the covariance alignment procedure.}
%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
%We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

%\begin{figure}[!h]
%	\centering
%	\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
%		\caption{Task pair TREC and CR}
%		\label{fig_cov_a}
%	\end{subfigure}\hfill
%		\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
%		\caption{Task pair MR and SST}
%			\label{fig_cov_b}
%	\end{subfigure}
%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
%	\label{fig_covariate_app}
%\end{figure}

\begin{figure}%[!t]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
		\caption{HPS vs. STL}
		\label{fig_ab_data}
	\end{subfigure}\hfill
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
		\caption{HPS vs. covariance alignment}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \cite{WZR20}:
	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
	\label{fig_text}
%	\begin{minipage}[t]{0.4\textwidth}
%		\centering
%		\vspace{0pt}
%		\begin{tabular}{c c c}
%		\toprule
		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
		% Sentiment\\ analysis\end{center}\end{minipage}} \\
%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
		% \cmidrule(lr){2-3}
%		& all tasks & w/o TREC \\
%		\midrule
%		{\bf MLP}  & 31\% & 29\% \\
%		{\bf LSTM} & 35\% & 34\% \\
%		{\bf CNN}  & 30\% & 28\% \\
%		\bottomrule
%		\end{tabular}
%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
%		\label{tab:taskonomy}
%	\end{minipage}
\end{figure}

%\begin{algorithm}[!t]
%	\caption{A progressive training schedule given two tasks}
%	\label{alg_inc_train}
%	\begin{algorithmic}[1]
%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
%		\Output The trained modules $B, A_2$ optimized for task $2$.
%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
%		\For{$i = 1,\dots, S$}
%			\For{$j = 1,\dots, T$}
%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
%			\EndFor
%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
%				\State \textbf{break}
%			\EndIf
%		\EndFor
%	\end{algorithmic}
%\end{algorithm}

\iffalse
\section{Conclusions and Discussions}\label{sec_conclude}

This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
We validated our theory and conducted further studies on text classification tasks.
We describe several open questions for future work.
%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
%Second, it would be interesting to extend our result to classification problems such as logistic regression.
First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
%but its singular values will follow a different distribution since the matrix is not symmetric.
 %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
Second, it would be interesting to extend our results to classification problems.
Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
An interesting question is to study logistic regression in a multiple-sample setting.
\fi

 \section*{Acknowledgements}
Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work. Hongyang R. Zhang and Weijie J. Su's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
We gratefully acknowledge the support of DARPA under Nos. FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No. U54EB020405 (Mobilize), NSF under Nos. CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No. N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys. The U.S. Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S. Government.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, if any, should   %%
%% be provided in {supplement} environment  %%
%% with title and short description.        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
\textbf{Supplement to ``Hard Parameter Sharing in High-dimensional Linear Regression"}.
In \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}. 
%and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
\end{supplement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  imsart-???.bst  will be used to                        %%
%%  create a .BBL file for submission.                     %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%  MR numbers will be added by VTeX.                      %%
%%                                                         %%
%%  Use \cite{...} to cite references in text.             %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% if your bibliography is in bibtex format, uncomment commands:
\bibliographystyle{imsart-number}
%\bibliographystyle{imsart-nameyear}

%\bibliographystyle{abbrv}
%\bibliographystyle{plain}
\bibliography{rf,ref_mtl}
 % Style BST file (imsart-number.bst or imsart-nameyear.bst)
%\bibliography{bibliography}       % Bibliography file (usually '*.bib')

%% or include bibliography directly:
%\begin{thebibliography}{4}
%%%
%\bibitem{r1}
%\textsc{Billingsley, P.} (1999). \textit{Convergence of
%Probability Measures}, 2nd ed.
%Wiley, New York.
%
%\bibitem{r2}
%\textsc{Bourbaki, N.}  (1966). \textit{General Topology}  \textbf{1}.
%Addison--Wesley, Reading, MA.
%
%\bibitem{r3}
%\textsc{Ethier, S. N.} and \textsc{Kurtz, T. G.} (1985).
%\textit{Markov Processes: Characterization and Convergence}.
%Wiley, New York.
%
%\bibitem{r4}
%\textsc{Prokhorov, Yu.} (1956).
%Convergence of random processes and limit theorems in probability
%theory. \textit{Theory  Probab.  Appl.}
%\textbf{1} 157--214.
%\end{thebibliography}

\end{document}

### 2021-06-12 revision_journal/backup/Jan 29 2021/manuscript.tex
revision wip

--- 2021-06-12 revision_journal/backup/Jan 01 2021/manuscript.tex
@@
 \begin{frontmatter}
-\title{Hard Parameter Sharing in High-dimensional Linear Regression}
+%\title{High-dimensional Asymptotics of Linear Regression with Different Covariates and Sample Sizes}
 %\title{A sample article title with some additional note\thanksref{t1}}
-\runtitle{Hard Parameter Sharing in High-dimensional Linear Regression}
+
+\title{High-dimensional Asymptotics of Transfer Learning for Linear Regression} 
+%with Different Covariates and Sample Sizes}
+
+\runtitle{Linear Regression with Different Covariates and Sample Sizes}
 %\thankstext{T1}{A sample additional note to the title.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu} \thanks{Fan Yang and Hongyang R. Zhang contributed equally.}}
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}\samethanks} 
+\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu}}
+\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}}
 \author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3,mark]{senwu@stanford.edu}} 
@@
 \begin{abstract}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
+	{\cor rewrite} Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
 This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
@@
 
-Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
+{\cor rewrite} Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
 Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
@@
 
-\section{Hard parameter sharing estimator}\label{sec_HPS}
-
+\section{Transfer learning for high-dimensional linear regression}\label{sec_HPS}
+In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
+
+\subsection{The model}
 Consider the transfer learning setting with two data sets.
@@
 $$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-We study the standard hard parameter sharing architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
-Then we study the following minimization problem:
-\begin{align}\label{eq_tsl}
-			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
-\end{align}
-where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
-\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
 In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
@@
 
+\subsection{Transfer learning estimators}
+
+\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
+
+We study the standard hard parameter sharing architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
+Then we study the following minimization problem:
+\begin{align}\label{eq_tsl}
+			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
+\end{align}
+where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
+\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
+
 For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that  
@@
 
+{\cor discuss about the bias-variance trade-off}
 %However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
 
-\section{HPS estimator: Bias-variance tradeoff}\label{sec_same}
-
-%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
-%We provide a sharp generalization error bound of hard parameter sharing estimators.
-
-In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
-We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
-$ {B^\star}^\top \Sigma  B^\star,$ where $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ is the matrix formed by the linear model parameters of the two tasks.
-Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is well-defined.
-Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
-
-\begin{theorem}\label{thm_two_tasks}
-Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2$. Let $c>0$ be an arbitrary small constant. Then we have that with high probability, 
-\be\label{minimizer_beta1}
-\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
-\ee
-where $u_{\hat a}$ is a unit vector defined as
-$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-%for task 2,  % over the randomness of the input, 
-Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
-	\begin{align}
-		& \bigabs{L(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) (B^{\star}A^{\star})  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
-		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	 where $A^\star(2)$ denotes the second entry of $A^\star$.
-	 \end{theorem}
-
-Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
-Moreover, the factor $(\lambda_1 - \lambda_{2})^{-1}$ is natural, because the two eigenspaces of ${B^{\star}}^{\top}\Sigma B^{\star}$ are not stable when $\lambda_1 $ and $\lambda_{2} $ are close to each other.
-The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-It is not hard to extend the above result to the cases with more than two tasks.
-We make this extension for the following reasons.
-First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
-Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-
-\vspace{5pt}
-\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
-The label vector of the $i$-th task follows a linear model
-$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
-We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
-
-%\begin{enumerate}
-%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-%\end{enumerate}
-
-	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
-	\begin{align}
-		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
-%Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-
-	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
-Hence we only consider the case with $r<t$.
-\FY{Correct it if the reason is wrong.}
-
-	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
-	\begin{align}
-		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
-		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
-	\end{align}
-	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
-	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
-	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
-	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
-	\end{align}
-%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
-%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
-%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
-
-Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is the covariance of the task labels):
-\begin{align}\label{eq_A_star}
-	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
-\end{align}
-where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
- To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
-Otherwise, Theorem \ref{thm_many_tasks} will give a null result.
- %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
-Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
-Then we have the following result.
-
-% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
-%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
-%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
-%Our result is stated as follows.
-
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
-	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
-Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary small constant. Then for any task $i = 1,  \cdots, t$, we have that high probability, 
-\be\label{minimizer_beta}
-\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
-\ee
-where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that
-	\begin{align}
-		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
-		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
-\label{Li_multi1}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
-%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
-%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
-Finally, we have a better bound for the averaged prediction loss:  
-\begin{align}
-&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
- &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 ,\label{Li_multi2}
-\end{align}
-with high probability.
-\end{theorem}
-
- The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
-The estimate \eqref{Li_multi1} shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
-Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases in the HPS for multi-task setting.
-On the other hand, the bias term always increases, because the bias in single-task linear regression is zero.
-Hence whether the HPS estimator is better than the OLS estimator depends on an intricate \emph{bias-variance tradeoff}.
-%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.}
-We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
-Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
-For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
-
-The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
-Moreover, Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
-
-%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-%\medskip
-%
-%\noindent\textbf{Comparison to single-task learning (STL).}
-%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
-%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
-%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
-%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.
-
-\iffalse
-\paragraph{How does hard parameter sharing scale with sample size $n$?}
-Obviously, the concentration error decreases with $n$.
-First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
-It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
-
-\begin{assumption}\label{assume_rm}
-	Let $\tau > 0$ be a small enough constant.
-%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
-entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	In the high-dimensional setting,
-%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-%			\begin{align}\label{assmAhigh}
-%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
-%			\end{align}
-  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
-%	\end{enumerate}
-\end{assumption}
-Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
-
-\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	With high probability over the randomness of $X$, we have that
-		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
-\end{fact}
-\noindent\textit{Remark.} The above result has a long history in random matrix theory.
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
-Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
-		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
-		\fi
-
-%Finally, for the random noise component, we assume that all of its moments exist.
-%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
-%\begin{align}\label{assmAhigh2}
-%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
-%\end{align}
-%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
-%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
-
-%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
-To illustrate the {bias-variance tradeoff quantitively, we consider a random-effect model, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
-\begin{example}[Random-effect model]\label{ex_same_cov}
-Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-More precisely, %we have
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-and $\wt \beta^{(i)}$ denotes the $i$-th 
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. 
-%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
-%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
-
-In the random-effect model described above, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
-%Based on the definition of the random-effect model, 
-the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
-%\begin{align*}
-%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
-%\end{align*}
-\begin{align}\label{betaSbeta}
-	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
-\end{align}
- with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}. 
-%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
-With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
-$$\lambda_1=(1+\OO(p^{-1/2+c}))\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
-and
-$$ \lambda_i=(1+\OO(p^{-1/2+c}))\frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
-Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
-$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
-with high probability. 
-%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
-%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
-%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
-%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
-Then using \eqref{Li_multi2}, we obtain that
-\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p.
-}\]
-%We describe a proof sketch.
-%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
-%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
-%Second, using Fact \ref{fact_tr}, one can see that the average variance is
-%\begin{align*}
-%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
-%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
-%\end{align*}
-%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
-%Combined together, we have derived the average prediction loss in the random-effect model.
-If the error is sufficiently small, then comparing the above equation with \eqref{L_STL_simple01}, we have the following observations. 
-%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
-%Comparing HPS to STL, we have the following qualitative properties.
-%	Suppose $n$ is sufficiently large so that the error is negligible.
-%\begin{enumerate}
-\begin{enumerate}
-	\item {\bf Positive vs.
-negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
-
-	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
-Hence increasing the width $r$ of the shared feature representation layer does not help.
-	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-
-	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
-Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
-More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
-	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
-}\]
-	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
-	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$ 
-	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
-
-	%samples that is less than $n$ samples to get comparable loss to STL.
-	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
-	\end{enumerate}
-
-\end{example}
-
-\FY{add applications, simulations, and algorithm consequences of the results in this section}
-
-\section{HPS estimator: Varying sample sizes} 	\label{sec_sizeratio}
+\section{Predication loss for HPS estimator}
+
+\subsection{Varying sample sizes} \label{sec_sizeratio}
 
@@
 \be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-Then we observe the following dichotomy.
+Then we observe the following dichotomy. \FY{add several plots to illustrate this dichotomy}
 \begin{enumerate}
@@
  \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy.
+Then we observe the following dichotomy. \FY{add several plots to illustrate this dichotomy}
 \begin{enumerate}
@@
 \item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global minimum at $\rho=\rho_c$.
+Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
 \end{enumerate}
@@
 
-\section{HPS estimator: Covariate shift}\label{sec_diff}
+\subsection{Covariate shift}\label{sec_diff}
 
@@
 
+\section{Extension to multi-task learning}\label{sec_same}
+
+%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
+%We provide a sharp generalization error bound of hard parameter sharing estimators.
+
+In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
+We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
+$ {B^\star}^\top \Sigma  B^\star,$ where $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ is the matrix formed by the linear model parameters of the two tasks.
+Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is well-defined.
+Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
+
+\begin{theorem}\label{thm_two_tasks}
+Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2$. Let $c>0$ be an arbitrary small constant. Then we have that with high probability, 
+\be\label{minimizer_beta1}
+\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
+\ee
+where $u_{\hat a}$ is a unit vector defined as
+$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
+%for task 2,  % over the randomness of the input, 
+Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
+	\begin{align}
+		& \bigabs{L(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) (B^{\star}A^{\star})  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
+		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
+		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
+	\end{align}
+	 where $A^\star(2)$ denotes the second entry of $A^\star$.
+	 \end{theorem}
+
+Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
+Moreover, the factor $(\lambda_1 - \lambda_{2})^{-1}$ is natural, because the two eigenspaces of ${B^{\star}}^{\top}\Sigma B^{\star}$ are not stable when $\lambda_1 $ and $\lambda_{2} $ are close to each other.
+The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
+
+It is not hard to extend the above result to the cases with more than two tasks.
+We make this extension for the following reasons.
+First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
+Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
+
+%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
+%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
+%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
+%\begin{align}
+%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
+%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
+%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
+%\end{align}
+%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
+%Compared to the prediction loss of single-task learning (cf.
+equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
+%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
+%We show the generalization error of hard parameter sharing estimators.
+%Before stating the result, we define the following notations.
+
+\vspace{5pt}
+\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
+The label vector of the $i$-th task follows a linear model
+$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
+We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
+entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
+$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
+Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
+
+%\begin{enumerate}
+%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
+%\end{enumerate}
+
+	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
+	\begin{align}
+		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
+	\end{align}
+	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
+%Recall that $r$ is the width of $B$.
+We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
+
+	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
+Hence we only consider the case with $r<t$.
+\FY{Correct it if the reason is wrong.}
+
+	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
+	\begin{align}
+		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
+		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
+	\end{align}
+	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
+	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
+	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
+	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
+	\begin{align}\label{eq_mtl_output_layer}
+		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
+	\end{align}
+%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
+%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
+%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
+Let $\hat A$ be the global minimizer of $g(A)$.
+Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
+We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
+%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
+and its (out-of-sample) prediction loss as
+\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
+
+Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
+To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
+Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is the covariance of the task labels):
+\begin{align}\label{eq_A_star}
+	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
+\end{align}
+where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
+ To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
+Otherwise, Theorem \ref{thm_many_tasks} will give a null result.
+ %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
+Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
+Then we have the following result.
+
+% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
+%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
+%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
+%Our result is stated as follows.
+
+\begin{theorem}\label{thm_many_tasks}
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
+	%that satisfy Assumption \ref{assm_secA2} in the appendix.
+	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
+	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
+%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
+%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
+Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary small constant. Then for any task $i = 1,  \cdots, t$, we have that high probability, 
+\be\label{minimizer_beta}
+\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
+\ee
+where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
+Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that
+	\begin{align}
+		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
+		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
+\label{Li_multi1}
+		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
+	\end{align}
+	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
+%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
+%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
+Finally, we have a better bound for the averaged prediction loss:  
+\begin{align}
+&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
+ &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 ,\label{Li_multi2}
+\end{align}
+with high probability.
+\end{theorem}
+
+ The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
+The estimate \eqref{Li_multi1} shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
+Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases in the HPS for multi-task setting.
+On the other hand, the bias term always increases, because the bias in single-task linear regression is zero.
+Hence whether the HPS estimator is better than the OLS estimator depends on an intricate \emph{bias-variance tradeoff}.
+%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
+%On the other hand, the bias always increases.}
+We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
+Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
+For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
+
+The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
+Moreover, Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
+
+%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
+%\medskip
+%
+%\noindent\textbf{Comparison to single-task learning (STL).}
+%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
+%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
+%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
+%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
+%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
+%On the other hand, the bias always increases.
+
+\iffalse
+\paragraph{How does hard parameter sharing scale with sample size $n$?}
+Obviously, the concentration error decreases with $n$.
+First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
+It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
+
+\begin{assumption}\label{assume_rm}
+	Let $\tau > 0$ be a small enough constant.
+%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
+entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
+	In the high-dimensional setting,
+%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
+%			\begin{align}\label{assmAhigh}
+%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
+%			\end{align}
+  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
+%	\end{enumerate}
+\end{assumption}
+Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
+
+\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
+	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
+	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
+	With high probability over the randomness of $X$, we have that
+		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
+\end{fact}
+\noindent\textit{Remark.} The above result has a long history in random matrix theory.
+For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
+Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
+		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
+		\fi
+
+%Finally, for the random noise component, we assume that all of its moments exist.
+%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
+%\begin{align}\label{assmAhigh2}
+%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
+%\end{align}
+%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
+%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
+%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
+
+%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
+To illustrate the {bias-variance tradeoff quantitively, we consider a random-effect model, which has been studied for  single-task linear regression and ridge regression (see e.g.
+\cite{dobriban2020wonder,dobriban2018high}).
+
+\begin{example}[Random-effect model]\label{ex_same_cov}
+Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
+More precisely, %we have
+$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
+where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
+and $\wt \beta^{(i)}$ denotes the $i$-th 
+%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
+task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. 
+%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
+%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
+%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
+%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
+
+In the random-effect model described above, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
+%Based on the definition of the random-effect model, 
+the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
+%\begin{align*}
+%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
+%\end{align*}
+\begin{align}\label{betaSbeta}
+	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
+\end{align}
+ with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}. 
+%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
+With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
+$$\lambda_1=(1+\OO(p^{-1/2+c}))\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
+and
+$$ \lambda_i=(1+\OO(p^{-1/2+c}))\frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
+Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
+$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
+with high probability. 
+%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
+%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
+%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
+%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
+Then using \eqref{Li_multi2}, we obtain that
+\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p.
+}\]
+%We describe a proof sketch.
+%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
+%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
+%Second, using Fact \ref{fact_tr}, one can see that the average variance is
+%\begin{align*}
+%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
+%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
+%\end{align*}
+%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
+%Combined together, we have derived the average prediction loss in the random-effect model.
+If the error is sufficiently small, then comparing the above equation with \eqref{L_STL_simple01}, we have the following observations. 
+%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
+%Comparing HPS to STL, we have the following qualitative properties.
+%	Suppose $n$ is sufficiently large so that the error is negligible.
+%\begin{enumerate}
+\begin{enumerate}
+	\item {\bf Positive vs.
+negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
+
+	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
+Hence increasing the width $r$ of the shared feature representation layer does not help.
+	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
+
+	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
+Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
+More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
+	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
+}\]
+	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
+	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$ 
+	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
+
+	%samples that is less than $n$ samples to get comparable loss to STL.
+	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
+	\end{enumerate}
+
+\end{example}
+
+\FY{add applications, simulations, and algorithm consequences of the results in this section}
+
 \section{Experiments}
@@
 
- \section*{Acknowledgements}
-Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
+% \section*{Acknowledgements}
+%Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
 Hongyang R.
@@
 Su's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
-We gratefully acknowledge the support of DARPA under Nos.
+%We gratefully acknowledge the support of DARPA under Nos.
 FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.

### 2021-06-12 revision_journal/backup/Jan 31 2021/manuscript.tex
revision wip

--- 2021-06-12 revision_journal/backup/Jan 29 2021/manuscript.tex
@@
 \begin{abstract}
-	{\cor rewrite} Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
+	\FY{rewrite the abstract} Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
 This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
@@
 
-{\cor rewrite} Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
+\FY{rewrite the introduction}  Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
 Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
@@
 
-\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-
-We study the standard hard parameter sharing architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
+One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
+\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
+where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by  
+$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
+The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}. 
+In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
+
+Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
+$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
+%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
+In this paper, we consider a natural extension of the estimator $\hat \beta^{\rm{TL}} $, that is, the \emph{hard parameter sharing} (HPS) estimator, which has been a standard type of estimator in multi-task learning \FY{citations}.
+More precisely, we study the following HPS architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
 Then we study the following minimization problem:
@@
 \be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
+Note that $\hat \beta^{\rm{TL}}$ is a special case of $\hat{\beta}_i^{\MTL}$ by setting $A_1=A_2=1$.
 
@@
 
-In this paper, we study the out-of-sample predication loss (test error) of $\hat{\beta}_2^{\MTL} (\hat a)$.
+In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error).
 Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
@@
  \ee
-We will compare it to the out-of-sample predication loss $L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator 
-$$\hat \beta^{\STL}= [(X^{(2)})^\top X^{(2)}]^{-1}(X^{(2)})^\top Y^{(2)}$$ as a baseline.
+We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.
+
+%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
 
@@
  \begin{lemma}\label{lem_HPS_loss}
- Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$: 
+ Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
 \begin{align}
@@
 &+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
+\end{align}
+\begin{align}
+L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
+& + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
 \end{align}
@@
 	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that
-		\[ \bigtr{\Sigma^{(2)} \frac1{(X^{(2)})^\top X^{(2)} }  } = \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } = \frac{p}{n_2 - p} \cdot \left[1+ \OO\left( \frac{p^{\e}}{\sqrt{np}} \right)\right] \]
+	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
+		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } 
+		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
 		with high probability for any small constant $\e>0$.
@@
  %The above result has a long history in random matrix theory.
-If the entries of $Z^{(2)}$ are i.i.d.
-Gaussian, then this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
+If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of 
+the inverse Wishart distribution \cite{anderson1958introduction}.
 For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
@@
 \begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   . \label{L_STL_simple01}
+L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
+\end{align}
+and
+\begin{align}
+L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
  \end{align}
@@
 In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-\FY{What is known so far about this topic?} In the rest of this paper, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in three different settings of increasing complexity: (i) same covariates $X^{(1)}=X^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (iii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In each case, we provide the exact asymptotic bias and variance limits, together with almost sharp convergence rates.
-In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.
-
-{\cor discuss about the bias-variance trade-off}
+%\FY{What is known so far about this topic?}
+In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in two different settings: (i) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
+In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
+We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
+In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
+On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
+%Here case (ii) is actually more general than (i)
+%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.   
+In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
+We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
+Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
+
+%{\cor discuss about the bias-variance trade-off}
 %However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
 
-\section{Predication loss for HPS estimator}
+\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
 
@@
 
- In this section, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
+ In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
 However, the two tasks can have different sample sizes $n_1\ne n_2$.
 In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effect of the sample sizes on the predication loss of the $\MTL$ estimator.
+We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
 
 \begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1} holds, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
+Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
 Gaussian random variables.
@@
 \be\label{Lvar_samplesize}
-L_{\var}(a)= \left[ \cal L_1(a)+ \OO\left(\frac{p^{c}}{n_1}\right)\right] \cdot   \sigma^2 ,
+L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
 \ee
@@
 \begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right]   \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
+L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
 &+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
@@
 \fi
+
+We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
 The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
+For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
 In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
@@
 \end{align*}
-where we denote $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. Using the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
+where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
 \begin{align}\label{Lbias_idea}
@@
 \end{align}
-It is well-known that the empirical eigenvalue distributions (ESD) of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$ satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
+It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
 From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the Gaussian assumption, $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other.
-Hence the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measure.
+Due to the rotational invariance of multivariate Gaussian distributions,
+%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence 
+the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
+In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
 We use that result to obtain a convergence estimate on
@@
 Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-
-We believe that the above argument can be extended to the case without Gaussian assumption.
+We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
+
+We believe that the above argument can be extended to the case without the Gaussian assumption.
 For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some hard technical conditions for our setting.
+However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
 Hence we do not pursue this direction in this paper.
@@
 
-Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
+%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
+
+To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
+\cite{dobriban2020wonder,dobriban2018high}).
 
@@
 Next, we illustrate how varying them impact the prediction loss.
-\begin{example}[Sample sizes]\label{ex_sample_ratio}
+\begin{example}%[Sample sizes]
+\label{ex_sample_ratio}
 	%We first consider the impact of varying sample sizes.
 	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
+	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$. 
+	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
+$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
+where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
+and $\wt \beta^{(i)}$ denotes the $i$-th 
+%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
+task-specific component whose entries are i.i.d.
+Gaussian random variables of mean zero and variance $p^{-1} d^2$.
 First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
 	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
+
 	\begin{proposition}\label{lem_hat_v}
 %Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Suppose Assumption \ref{assm_big1} and the setting in Example \ref{ex_same_cov} hold. Suppose that
+Suppose Assumption \ref{assm_big1} and the above setting of random effect model hold. %in Example \ref{ex_same_cov} hold. 
+Suppose that for a constant $c_0>0$,
 	\be\label{para_rel}
@@
 	\ee
- for a constant $c_0>0$. Then we have that for any small constant $c>0$ and large constant $ C>0$,
+ Then we have that for any small constant $c>0$ and large constant $ C>0$,
 	%Let $c$ be a sufficiently small fixed constant.
@@
 
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (1+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
+We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
+Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
 $$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
@@
 Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term is always positive.
-Moreover, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-
-For a fixed $n_2$, we study the intricate bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$,
+First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
+This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
+Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
+Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
+
+Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
 $$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, which gives the quantitive information transfer from the source task to the target task.
+This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
 First, we have positive (resp.
@@
 \be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-Then we observe the following dichotomy. \FY{add several plots to illustrate this dichotomy}
+We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
 \begin{enumerate}
@@
 
-\item If $(1+\rho_2)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
+\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
 Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
@@
  \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy. \FY{add several plots to illustrate this dichotomy}
+Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
 \begin{enumerate}
@@
 \fi
-
 	\end{example}
 
-	\FY{add applications, simulations, and algorithm consequences of the results in this section}
+	\FY{add simulations to check our results and the above dichotomies}
 
@@
 %The previous section assumes that all tasks have the same sample size and feature vectors.
-Finally, in this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
+In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
 %The different covariates case differs from the same covariates case in two aspects.
 %First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift'', which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give a rough estimate on it.
+In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$. 
+In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
 
@@
 %The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix (rescaled by $a$) 
+To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$) 
 $$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
 %Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a), \lambda_2(a), \dots, \lambda_p(a)$ denote the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
+Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
 \begin{equation}\label{assm32}
@@
 %	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for the variance term $L_{\var}(a)$ in \eqref{Lvar}: 
+Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}: 
 %equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
@@
 			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following self-consistent equations
+			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
 			\begin{align}
@@
 $$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$.
+Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
 Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
@@
 $$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
-and plug them into equation \eqref{lem_cov_shift_eq}.  The proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{appendix RMT} in the supplement \cite{MTL_suppl}.
+and plug them into \eqref{lem_cov_shift_eq}.
+The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
 %For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
@@
 
-\begin{example}[Covariate shift]\label{ex_covshift}
+\begin{example} %[Covariate shift]
+\label{ex_covshift}
 %So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
@@
 %\end{align}
-From equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
+In fact, from equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
 \be\label{est_a12extra}
@@
 \end{enumerate}
-We explain why the above dichotomy happens. We can write that variance limit as
+We explain why the above dichotomy happens. We can write the variance limit as
 $$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
@@
 %The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for the bais term $L_{\bias}(a)$ in \eqref{Lbias}:
+Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
 			\begin{align}
 				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 + n_1^{-1/2+2/\varphi + c}\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
+				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
 				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
@@
 %			\end{align}
-				uniformly in all $a\in \R$. Here $\Pi(a)$ is a $p\times p$ matrix defined as
+				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
 				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				$\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, and $(a_{3},a_4)$ is the solution of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
 		\be  \label{eq_a34extra}
@@
 			\ee  
-			where recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
+			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
 \end{proposition}
@@
 \end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ by the law of large numbers in the regime $n_1\gg p$.
+Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
 However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
@@
 
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for dealing with the bias term also fails, because we cannot reduce the problem into the study of the addition of two random matrices that are asymptotically freely independent.
+We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
 %\end{remark}
@@
 
-\FY{add applications, simulations, and algorithm consequences of the results in this section}
+\FY{add simulations to check our results}
+
+\section{Insights for transfer learning}
+
+\FY{discuss applications and insights of our results}
+
+\subsection{Comparison between the averaging and HPS estimators}
+
+\subsection{Algorithmic implications}
+\FY{the progressive training; covariance alignment; and others?}
 
@@
 
-In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
+Hard parameter sharing is a commonly used architecture in multi-task learning.
+However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning.
+In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates.
+We make this extension for the following reasons.
+First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly.
+Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below.
+Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
+%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}
+
+\vspace{5pt}
+\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
+The label vector of the $i$-th task follows a linear model
+$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
+We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
+entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
+$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
+Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
+
+%\begin{enumerate}
+%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
+%\end{enumerate}
+
+	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
+	\begin{align}
+		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
+	\end{align}
+	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
+%Recall that $r$ is the width of $B$.
+We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
+
+	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
+Hence we only consider the case with $r<t$.
+\FY{Correct it if the reason is wrong.}
+
+	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
+	\begin{align}
+		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
+		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
+	\end{align}
+	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
+	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
+	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
+	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
+	\begin{align}\label{eq_mtl_output_layer}
+		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
+	\end{align}
+%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
+%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
+%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
+Let $\hat A$ be the global minimizer of $g(A)$.
+Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
+We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
+%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
+and its (out-of-sample) prediction loss as
+\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
+
+Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
+To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
+Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
+\begin{align}\label{eq_A_star}
+	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
+\end{align}
+where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
+ To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
+Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
+ %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
+Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
+Then we have the following result.
+
+% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
+%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
+%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
+%Our result is stated as follows.
+
+\begin{theorem}\label{thm_many_tasks}
+%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
+Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
+entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
+Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
+	%Let $n = c \cdot p$.
+	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
+%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
+	%that satisfy Assumption \ref{assm_secA2} in the appendix.
+	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
+	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
+%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
+%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
+Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability, 
+\be\label{minimizer_beta}
+\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
+\ee
+where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
+Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
+	\begin{align}
+		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
+		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
+\label{Li_multi1}
+		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
+	\end{align}
+	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
+%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
+%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
+Finally, we have a better bound for the averaged prediction loss:  with high probability,
+\begin{align}
+&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
+ &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
+\end{align}
+
+\end{theorem}
+
+Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
+Moreover, the factor $(\lambda_r - \lambda_{r+1})^{-1}$ is natural, because the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not stable when $\lambda_r $ and $\lambda_{r+1} $ are close to each other.
+The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
+The estimate \eqref{Li_multi1}
+ gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
+Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases for the multi-task HPS estimator.
+On the other hand, the bias term always increases (because the bias in single-task linear regression is zero).
+Hence as in the transfer learning setting, whether the HPS estimator is better than the OLS estimator depends on an intricate  {bias-variance tradeoff}.
+%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
+%On the other hand, the bias always increases.}
+We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
+Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
+For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
+
+The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
+Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
+For the reader's convenience, we give the precise statement in Corollary \ref{thm_two_tasks}.
+%Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.  
+%In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$. 
 We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix  
-$ {B^\star}^\top \Sigma  B^\star,$ where $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ is the matrix formed by the linear model parameters of the two tasks.
-Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is well-defined.
-Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
-
-\begin{theorem}\label{thm_two_tasks}
-Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2$. Let $c>0$ be an arbitrary small constant. Then we have that with high probability, 
+$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
+% is the matrix formed by the linear model parameters of the two tasks. 
+Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined.
+%Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
+In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
+
+\begin{corollary}\label{thm_two_tasks}
+Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2\equiv n$. Let $c>0$ be an arbitrary (small) constant. Then we have that with high probability, 
 \be\label{minimizer_beta1}
@@
 \ee
-where $u_{\hat a}$ is a unit vector defined as
+where $u_{\hat a}$ is the unit vector defined as
 $ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
@@
 	\begin{align}
-		& \bigabs{L(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) (B^{\star}A^{\star})  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
+		& \bigabs{L_2(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) \cdot B^{\star}A^{\star}  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
 		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
@@
 	 where $A^\star(2)$ denotes the second entry of $A^\star$.
-	 \end{theorem}
-
-Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
-Moreover, the factor $(\lambda_1 - \lambda_{2})^{-1}$ is natural, because the two eigenspaces of ${B^{\star}}^{\top}\Sigma B^{\star}$ are not stable when $\lambda_1 $ and $\lambda_{2} $ are close to each other.
-The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-It is not hard to extend the above result to the cases with more than two tasks.
+	 \end{corollary}
+
+%The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
+
+%It is not hard to extend the above result to the cases with more than two tasks.
 We make this extension for the following reasons.
@@
 
-\vspace{5pt}
-\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
-The label vector of the $i$-th task follows a linear model
-$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
-We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
-
-%\begin{enumerate}
-%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-%\end{enumerate}
-
-	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
-	\begin{align}
-		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
-%Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-
-	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
-Hence we only consider the case with $r<t$.
-\FY{Correct it if the reason is wrong.}
-
-	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
-	\begin{align}
-		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
-		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
-	\end{align}
-	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
-	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
-	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
-	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
-	\end{align}
-%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
-%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
-%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
-
-Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is the covariance of the task labels):
-\begin{align}\label{eq_A_star}
-	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
-\end{align}
-where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
- To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
-Otherwise, Theorem \ref{thm_many_tasks} will give a null result.
- %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
-Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
-Then we have the following result.
-
-% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
-%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
-%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
-%Our result is stated as follows.
-
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
-	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
-Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary small constant. Then for any task $i = 1,  \cdots, t$, we have that high probability, 
-\be\label{minimizer_beta}
-\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
-\ee
-where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that
-	\begin{align}
-		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
-		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
-\label{Li_multi1}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
-%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
-%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
-Finally, we have a better bound for the averaged prediction loss:  
-\begin{align}
-&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
- &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 ,\label{Li_multi2}
-\end{align}
-with high probability.
-\end{theorem}
-
- The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
-The estimate \eqref{Li_multi1} shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
-Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases in the HPS for multi-task setting.
-On the other hand, the bias term always increases, because the bias in single-task linear regression is zero.
-Hence whether the HPS estimator is better than the OLS estimator depends on an intricate \emph{bias-variance tradeoff}.
-%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.}
-We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
-Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
-For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
-
-The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
-Moreover, Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
-
 %The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
@@
 %Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
-To illustrate the {bias-variance tradeoff quantitively, we consider a random-effect model, which has been studied for  single-task linear regression and ridge regression (see e.g.
+To illustrate the {bias-variance tradeoff quantitively, we consider an extension of the random-effect model in Example \ref{ex_sample_ratio} to the multi-task setting.
+%which has been studied for  single-task linear regression and ridge regression (see e.g.
 \cite{dobriban2020wonder,dobriban2018high}).
 
-\begin{example}[Random-effect model]\label{ex_same_cov}
-Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+\begin{example}%[Random-effect model]
+\label{ex_same_cov}
+%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
 %Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-More precisely, %we have
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
+%More precisely, %we have
+Suppose that {$\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$} for $ i=1,2,\cdots, t,$
 where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
@@
 %We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
-
-In the random-effect model described above, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
+In this random-effect model, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
 %Based on the definition of the random-effect model, 
@@
 With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
-$$\lambda_1=(1+\OO(p^{-1/2+c}))\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
+$$\lambda_1=\left[1+\OO(p^{-1/2+c})\right]\cdot\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
 and
-$$ \lambda_i=(1+\OO(p^{-1/2+c}))\frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
+$$ \lambda_i=\left[1+\OO(p^{-1/2+c})\right]\cdot \frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
 Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
@@
 %Combined together, we have derived the average prediction loss in the random-effect model.
-If the error is sufficiently small, then comparing the above equation with \eqref{L_STL_simple01}, we have the following observations. 
+%If the error is sufficiently small, then 
+Comparing the above equation with \eqref{L_STL_simple01} (and ignoring the small error), we have the following observations. 
 %Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
@@
 
-\FY{add applications, simulations, and algorithm consequences of the results in this section}
+\FY{add simulations to check our results; discuss possible applications}
 
@@
 
+\FY{move the simulations results to previous sections}
 We demonstrate the accuracy of our results in simulations.
@@
 
-\paragraph{Sample efficiency.}
+\paragraph{Sample efficiency}
 First, we validate the result of Example \ref{ex_same_cov}.
@@
 
-\paragraph{Sample size ratio.}
+\paragraph{Sample size ratio}
 Second, we validate the result of Example \ref{ex_sample_ratio}.
@@
 
-\paragraph{Covariate shift.}
+\paragraph{Covariate shift}
 Finally, we validate the result of Example \ref{ex_covshift}.
@@
 
-\paragraph{Covariate shift.}
+\paragraph{Covariate shift}
 Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.

### 2021-06-12 revision_journal/comments.tex
revision wip

--- 2021-06-12 revision_journal/backup/03:06:2021/manuscript.tex
@@
-\documentclass[aos,preprint]{imsart}
-\usepackage{xr}
-	\externaldocument{./suppl}
-
-%% Packages
-\def\shownotes{1}
-%\usepackage{natbib}
-%\setcitestyle{authoryear,open={(},close={)}}
-%\renewcommand{\cite}{\citep}
-\usepackage[export]{adjustbox}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{fullpage}
-\usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
-\usepackage{macro_fan}
-\usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage{caption,subcaption}
-%\usepackage{breqn}
-
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression}
-
-\runtitle{High-dimensional Asymptotics of Transferring from Different Domains}
-%\thankstext{T1}{A sample additional note to the title.}
-
-\begin{aug}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Only one address is permitted per author. %%
-%%Only division, organization and e-mail is %%
-%%included in the address.                  %%
-%%Additional information can be included in %%
-%%the Acknowledgments section if necessary. %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{}},
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2]{}},
-\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3]{}},\\
-\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4]{} },
-\and
-\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5]{}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Addresses                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address{${ }^{1}$University of Pennsylvania, ${ }^{2}$Northeastern University, ${ }^{3}$Stanford University
-}
-%}\address[C]{
-%}
-
-\end{aug}
-
-\input{intro}
-
-\medskip
-\noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$.
-Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$.
-In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-
-\section{Main Results and Proof Techniques}\label{sec_HPS}
-In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
-
-\subsection{Assumptions}
-Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
-\be \label{conditionA2}
-\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
-\ee
-for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee
-%for a small constant $\tau>0$.
-
-We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\be\label{eq_highmoments}
-\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
-\ee
-Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$. 
-%Moreover, we assume that 
-%\be\label{eq_SNR}
-%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
-%\ee
-%for a small constant $\tau >0$.
-The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.
-
-In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that 
-\be\label{assm2}
-1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
-\ee
-for a small constant $\tau >0$.
-If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper.
-The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
-are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.
-
-We summarize our basic assumptions here for future reference.
-\begin{assumption}\label{assm_big1}
-Let $\tau$ be a small constant. 
-\begin{enumerate}
-\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}.
-%and (\ref{assm2}).
-We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-
-\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-
-\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
-
-\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.
-
-\end{enumerate}
-\end{assumption}
-
-%\subsection{Transfer learning estimators}
-
-%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-
-In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error).
-Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
-$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$ 
-Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
-\be\label{HPS_loss}
-L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
- \ee
-We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.
-
-%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
-
-Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-\end{align}
-Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-where 
-\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-is called the bias term, which depends on the model bias between task 1 and task 2, and
-\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-%predication loss for the HPS and OLS estimators.
-
- \begin{lemma}\label{lem_HPS_loss}
- Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
-\end{align}
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-& + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
-\end{align}
-and 
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-\end{align}
-%Moreover, there exists a constant $C_0>0$ such that with high probability,
-%\be\label{loss_large}
-%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-%\ee
-%with high probability for any small constant $\e>0$. 
-\end{lemma}
-
-Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$.
-In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
-(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}.
-To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
-Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.
-
-%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
-
-For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.
-
-\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
-		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } 
-		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
-		with high probability for any small constant $\e>0$.
-\end{lemma}
- %The above result has a long history in random matrix theory.
-If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of 
-the inverse Wishart distribution \cite{anderson1958introduction}.
-For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
-Lemma 3.11 of \cite{bai2009spectral}).
-Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate.
-With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
- \end{align}
-
-On the other hand, much less is known about the predication loss of the HPS estimator.
-In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-%\FY{What is known so far about this topic?}
-In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in two different settings: (i) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
-We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
-In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
-On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
-%Here case (ii) is actually more general than (i)
-%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.   
-In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
-We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
-Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
-
-%{\cor discuss about the bias-variance trade-off}
-%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
-
-\subsection{Covariate shift}\label{sec_diff}
-
-%The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$. 
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
-
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$) 
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-%for some small constant $0<\tau<1$. 
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
-
-\begin{theorem}\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}: 
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
-			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
-			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that 
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
-Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
-%also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
-and plug them into \eqref{lem_cov_shift_eq}.
-The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
-
-\subsection{The case of isotropic covariances} \label{sec_sizeratio}
-
- In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
-
-\begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
-\ee
-and
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}.
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)}
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
-
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
-
-We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the rotational invariance of multivariate Gaussian distributions,
-%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence
-the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
-
-We believe that the above argument can be extended to the case without the Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
-Hence we do not pursue this direction in this paper.
-
 \subsection{Proof overview}
@@
 The proof of Theorem \ref{thm_main_RMT} is shown in Appendix \ref{appendix RMT}.
-
-\input{examples}
-
-\input{exp}
-
-\input{multitask}
-
-\section{Conclusions}\label{sec_conclude}
-
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on text classification tasks.
-We describe several open questions for future work.
-%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-%Second, it would be interesting to extend our result to classification problems such as logistic regression.
-First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
-%but its singular values will follow a different distribution since the matrix is not symmetric.
- %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
-An interesting question is to study logistic regression in a multiple-sample setting.
-
-\begin{supplement}
-\textbf{Supplement to ``High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression"}.
-In the Internet Appendix \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
-%and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
-\end{supplement}
-
-\bibliographystyle{imsart-number}
-\bibliography{rf,ref_mtl}
-
-\end{document}

### 2021-06-12 revision_journal/conclusions.tex
revision wip

--- 2021-06-12 revision_journal/backup/03:06:2021/manuscript.tex
@@
-\documentclass[aos,preprint]{imsart}
-\usepackage{xr}
-	\externaldocument{./suppl}
-
-%% Packages
-\def\shownotes{1}
-%\usepackage{natbib}
-%\setcitestyle{authoryear,open={(},close={)}}
-%\renewcommand{\cite}{\citep}
-\usepackage[export]{adjustbox}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{fullpage}
-\usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
-\usepackage{macro_fan}
-\usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage{caption,subcaption}
-%\usepackage{breqn}
-
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression}
-
-\runtitle{High-dimensional Asymptotics of Transferring from Different Domains}
-%\thankstext{T1}{A sample additional note to the title.}
-
-\begin{aug}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Only one address is permitted per author. %%
-%%Only division, organization and e-mail is %%
-%%included in the address.                  %%
-%%Additional information can be included in %%
-%%the Acknowledgments section if necessary. %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{}},
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2]{}},
-\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3]{}},\\
-\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4]{} },
-\and
-\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5]{}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Addresses                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address{${ }^{1}$University of Pennsylvania, ${ }^{2}$Northeastern University, ${ }^{3}$Stanford University
-}
-%}\address[C]{
-%}
-
-\end{aug}
-
-\input{intro}
-
-\medskip
-\noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$.
-Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$.
-In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-
-\section{Main Results and Proof Techniques}\label{sec_HPS}
-In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
-
-\subsection{Assumptions}
-Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
-\be \label{conditionA2}
-\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
-\ee
-for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee
-%for a small constant $\tau>0$.
-
-We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\be\label{eq_highmoments}
-\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
-\ee
-Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$. 
-%Moreover, we assume that 
-%\be\label{eq_SNR}
-%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
-%\ee
-%for a small constant $\tau >0$.
-The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.
-
-In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that 
-\be\label{assm2}
-1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
-\ee
-for a small constant $\tau >0$.
-If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper.
-The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
-are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.
-
-We summarize our basic assumptions here for future reference.
-\begin{assumption}\label{assm_big1}
-Let $\tau$ be a small constant. 
-\begin{enumerate}
-\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}.
-%and (\ref{assm2}).
-We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-
-\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-
-\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
-
-\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.
-
-\end{enumerate}
-\end{assumption}
-
-%\subsection{Transfer learning estimators}
-
-%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-
-In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error).
-Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
-$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$ 
-Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
-\be\label{HPS_loss}
-L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
- \ee
-We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.
-
-%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
-
-Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-\end{align}
-Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-where 
-\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-is called the bias term, which depends on the model bias between task 1 and task 2, and
-\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-%predication loss for the HPS and OLS estimators.
-
- \begin{lemma}\label{lem_HPS_loss}
- Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
-\end{align}
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-& + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
-\end{align}
-and 
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-\end{align}
-%Moreover, there exists a constant $C_0>0$ such that with high probability,
-%\be\label{loss_large}
-%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-%\ee
-%with high probability for any small constant $\e>0$. 
-\end{lemma}
-
-Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$.
-In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
-(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}.
-To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
-Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.
-
-%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
-
-For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.
-
-\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
-		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } 
-		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
-		with high probability for any small constant $\e>0$.
-\end{lemma}
- %The above result has a long history in random matrix theory.
-If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of 
-the inverse Wishart distribution \cite{anderson1958introduction}.
-For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
-Lemma 3.11 of \cite{bai2009spectral}).
-Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate.
-With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
- \end{align}
-
-On the other hand, much less is known about the predication loss of the HPS estimator.
-In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-%\FY{What is known so far about this topic?}
-In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in two different settings: (i) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
-We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
-In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
-On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
-%Here case (ii) is actually more general than (i)
-%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.   
-In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
-We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
-Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
-
-%{\cor discuss about the bias-variance trade-off}
-%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
-
-\subsection{Covariate shift}\label{sec_diff}
-
-%The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$. 
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
-
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$) 
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-%for some small constant $0<\tau<1$. 
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
-
-\begin{theorem}\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}: 
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
-			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
-			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that 
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
-Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
-%also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
-and plug them into \eqref{lem_cov_shift_eq}.
-The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
-
-\subsection{The case of isotropic covariances} \label{sec_sizeratio}
-
- In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
-
-\begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
-\ee
-and
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}.
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)}
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
-
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
-
-We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the rotational invariance of multivariate Gaussian distributions,
-%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence
-the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
-
-We believe that the above argument can be extended to the case without the Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
-Hence we do not pursue this direction in this paper.
-
-\subsection{Proof overview}
-For the rest of this section, we present an overview of the proof of Theorem \ref{thm_main_RMT}.
-The central quantity of interest is the inverse of the sum of two sample covariance matrices.
-We note that the variance equation $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ is equal to $(n_1 + n_2)^{-1} \bigtr{W^{-1}}$, where $W$ is
-\begin{align}\label{eigen2extra}
-\frac{\Lambda U^\top (Z^{(1)})^\top Z^{(1)} U\Lambda  + V^\top (Z^{(2)})^\top Z^{(2)}V}{n_1 + n_2}.
-\end{align}
-Here $U\Lambda V^\top$ is defined as the SVD of $M$.
-This formulation is helpful because we know that $(Z^{(1)})^{\top} Z^{(1)}$ and $(Z^{(2)})^{\top} Z^{(2)}$ are both sample covariance matrices with isotropic population covariance, and $U, V$ are both orthonormal matrices.
-For example, if $Z^{(1)},Z^{(2)}$ are both Gaussian random matrices, by rotational invariance, $Z^{(1)} U, Z^{(2)}V$ are still Gaussian random matrices.
-
-Our proof uses the Stieltjes transform or the resolvent method in random matrix theory.
-We briefly describe the key ideas and refer the interested readers to classical texts such as  \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.
-For any probability measure $\mu$ supported on $[0,\infty)$, the Stieltjes transform of $\mu$ is a complex function defined as
-$$m_\mu(z):= \int_0^\infty \frac{\dd\mu(x)}{x-z}, \text{ for any complex } z\in \C\setminus \set{0}.$$
-Thus, the Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
-
-Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where the $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$.
-Then it is easy to see that the Stieltjes transform of $\mu$ is equal to
-\[ m_{\mu}(z) \define \frac{1}{p}\sum_{i=1}^p \frac{1}{\sigma_i - z}= p^{-1}\tr\left[(W-z\id)^{-1}\right]. \]
-The above matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
-We prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
-
-We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic unit vectors $v\in \R^p$,
-$$v^\top \left[(W-z\id)^{-1}-R(z)\right]v\to 0\ \ \ \text{when $p$ goes to infinity.
-}$$
-To study $W$'s resolvent, we observe that $W$ is equal to $\AF\AF^{\top}$ for a $p$ by $n_1 + n_2$ matrix
-\be\label{defn AF} \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \ee
-Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
-\begin{equation}\label{linearize_block}
-H \define \left( {\begin{array}{*{20}c}
-0 & \AF  \\
-\AF^{\top} & 0
-\end{array}} \right).
-\end{equation}
-For this block matrix, we define its resolvent as
-$$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$
-for any complex value $z\in \mathbb C$.
-Using Schur complement formula for the inverse of a block matrix, it is not hard to verify that
-\begin{equation} \label{green2}
-G(z) =  \left( {\begin{array}{*{20}c}
-(W- z\id)^{-1} & (W - z\id)^{-1} \AF  \\
-\AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
-\end{array}} \right).%
-\end{equation}
-
-\textbf{Variance asymptotic limit.}
-In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
-\be \label{defn_piw}
-\Gi(z) \define \begin{pmatrix} (a_{1}(z)\Lambda^2  +  (a_{2}(z)- z)\id_{p\times p})^{-1} & 0 & 0 \\ 0 & - \frac{n_1+n_2}{n_1} a_{1}(z)\id_{n_1\times n_1} & 0 \\ 0 & 0 & -\frac{n_1+n_2}{n_2}a_{2}(z)\id_{n_2\times n_2}  \end{pmatrix},\ee
-where $a_1(z)$ and $a_2(z)$ are the unique solutions to the following self-consistent equations
-\be\label{selfomega_a}
-\begin{split}
-&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %
-&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
-\end{split}
-\ee
-The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
-Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
-First, we have that $a_1 = a_1(0)$ and $a_2 = a_2(0)$ since the equations in \eqref{selfomega_a} reduce to equation \eqref{eq_a12extra} when $z=0$.
-Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
-Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, %
-\begin{align*}
-\bigtr{\Sigma^{(2)} \hat{\Sigma}} \rightarrow \frac{1}{n_1+n_2}\bigtr{(a_1 \Lambda^2 + a_2\id)^{-1}} &= \frac1{n_1+n_2}\bigtr{(a_1 M^{\top}M + a_2 \id)^{-1}} \\
-&=\frac{1}{n_1+n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}},
-\end{align*}
-where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
-
-\textbf{Bias asymptotic limit.}
-For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
-First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %
-\begin{align}\label{calculate G'}
-(n_1 + n_2)^2 \hat{\Sigma}^{-1}\Sigma^{(2)}\hat{\Sigma}^{-1} = {\Sigma^{(2)}}^{-1/2} V W^{-2} V^{\top} {\Sigma^{(2)}}^{-1/2}.
-\end{align}
-Let $\cal G(z):=(W-z\id )^{-1}$ denote the resolvent of $W$.
-Our key observation is that $\frac{\dd{\cal G(z)}}{\dd z} =  \cal G^2(z)$.
-Hence, provided that the limit of $(W - z\id)^{-1}$ is $(a_1(z) \Lambda^2 + (a_2(z) - z) \id)^{-1}$ near $z = 0$, the limit of $\frac{\dd{\cal G(0)}}{\dd z}$ satisfies
-\begin{align}\label{cal G'0}
-\frac{\dd \cal G(0)}{\dd z} \to \frac{-\frac{\dd a_1(0)}{\dd z}\Lambda^2 - (\frac{\dd a_2(0)}{\dd z} - 1)\id}{(a_{1}(0)\Lambda^2 + a_{2}(0)\id_p)^2}.
-\end{align}
-To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of the system of equations \eqref{selfomega_a}.
-Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(0)}{\dd z}$.
-One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
-Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the bias limit.
-
-As a remark, in order for $\frac{\dd \cal G(z)}{\dd z}$ to stay close to its limit at $z = 0$, we not only need to find the limit of $\cal G(0)$, but also the limit of $\cal G(z)$ within a small neighborhood of $0$.
-This is why we consider $W$'s resolvent for a general $z$ (as opposed to the Stieljes transform of its empirical spectral distribution discussed earlier).
-
-\textbf{Schur complement and self-consistent equations.}
-First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
-By rotational invariance, we have that $Z^{(1)} U$ and $Z^{(2)} V$ are still multivariate Gaussian random matrices.
-Next, we use the Schur complement formula to deal with the resolvent $G(z)$.
-We show that $G(z)$'s diagonal entries satisfy a set of self-consistent equations in the limit, leading to equations in \eqref{selfomega_a}.
-On the other hand, $G(z)$'s off-diagonal entries are approximately zero using standard concentration bounds.
-Finally, we extend our result to general random matrices under the finite $\varphi$-th moment condition.
-We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
-The proof of Theorem \ref{thm_main_RMT} is shown in Appendix \ref{appendix RMT}.
-
-\input{examples}
-
-\input{exp}
-
-\input{multitask}
-
 \section{Conclusions}\label{sec_conclude}
@@
 
-\begin{supplement}
-\textbf{Supplement to ``High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression"}.
-In the Internet Appendix \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
+%\begin{supplement}
+%\textbf{Supplement to ``High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression"}.
+%In the Internet Appendix \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
 %and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
-\end{supplement}
-
-\bibliographystyle{imsart-number}
-\bibliography{rf,ref_mtl}
-
-\end{document}
+%\end{supplement}

### 2021-06-12 revision_journal/intro.tex
revision wip

--- 2021-06-12 revision_journal/backup/03:06:2021/intro.tex
@@
-\begin{abstract}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
-First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
-Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
-We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
-This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-\end{abstract}
-
-\begin{keyword}[class=MSC2020]
-\kwd[Primary ]{62J05}
-\kwd{60B20}
-\kwd[; secondary ]{62E20, 62H10}
-\end{keyword}
-
-\begin{keyword}
-\kwd{Transfer learning, random matrix theory, covariate shift, sample covariance matrices.}
-\end{keyword}
-
-\end{frontmatter}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please use \tableofcontents for articles %%
-%% with 50 pages and more                   %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\tableofcontents
-
 \section{Introduction}\label{sec_introduction}

### 2021-06-12 revision_journal/main_arxiv.tex
revision wip

--- 2020-10-22 arxiv/main.tex
@@
 
-\def\shownotes{0}
+\def\shownotes{1}
+
 \usepackage{natbib}
@@
 \renewcommand{\cite}{\citep}
+\newcommand{\yell}[1]{{\color{red}#1}}
+\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
+\usepackage{authblk}
+\usepackage[margin=1in]{geometry}
+%\usepackage{hyperref}
+
+\usepackage{macro_math}
+\usepackage[us,12hr]{datetime} % `us' makes \today behave as usual in TeX/LaTeX
+\usepackage{graphicx, subcaption}
 \usepackage[export]{adjustbox}
-\usepackage[margin=1in]{geometry}
 \usepackage{subfloat}
@@
 \usepackage{microtype}      %
-\usepackage{graphicx}
 \usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
+\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}
 \usepackage{macro_fan}
 \usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
 \usepackage[utf8]{inputenc} %
@@
 
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-\usepackage{authblk}
+%\newcommand{\citet}{\cite}
 
@@
 
-\title{\textbf{Sharp Bias-variance Tradeoffs of Hard Parameter Sharing in High-dimensional Linear Regression}}
+	\iffalse
 	\vspace{0.15in}
@@
 	\affil[3]{Department of Computer Science, Stanford University}
-
+	\fi
+	\title{Precise Asymptotics of Transferring from Different Regression in High Dimensions}
 	\maketitle
-
+	\input{abstract}
 	\input{intro}
-\input{setup}
-\input{same_cov}
-\input{diff_cov}
-\input{experiments}
-\input{experiments_text}
+	\input{results}
+	\input{examples}
+	\input{multitask}
+	\input{exp}
 	\input{conclusions}
-
-\subsection*{Acknowledgements:}
-Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
-HZ and WS's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
-We gratefully acknowledge the support of DARPA under Nos.
-FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.
-U54EB020405 (Mobilize), NSF under Nos.
-CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No.
-N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys.
-The U.S.
-Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S.
-Government.
-
 	\bibliographystyle{plainnat}
 	\bibliography{rf,ref_mtl}
-\appendix
 
-\input{proof_same_cov}
-\input{proof_gaussian_case}
-\input{proof_appd}
-\input{proof_examples}
-\input{tools}
 \end{document}

### 2021-06-12 revision_journal/multitask.tex
revision wip

--- 2021-06-12 revision_journal/backup/Jan 31 2021/manuscript.tex
@@
-\documentclass[aos,preprint]{imsart}
-\usepackage{xr}
-	\externaldocument{./suppl}
-
-%% Packages
-\def\shownotes{0}
-%\usepackage{natbib}
-%\setcitestyle{authoryear,open={(},close={)}}
-%\renewcommand{\cite}{\citep}
-\usepackage[export]{adjustbox}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{fullpage}
-\usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
-\usepackage{macro_fan}
-\usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage{caption,subcaption}
-%\usepackage{breqn}
-
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Uncomment next line to change            %%
-%% the type of equation numbering           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\numberwithin{equation}{section}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Axiom, Claim, Corollary, Hypothezis, %%
-%% Lemma, Theorem, Proposition              %%
-%% use \theoremstyle{plain}                 %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\theoremstyle{plain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Assumption, Definition, Example,     %%
-%% Notation, Property, Remark, Fact         %%
-%% use \theoremstyle{remark}                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please put your definitions here:        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-%\title{High-dimensional Asymptotics of Linear Regression with Different Covariates and Sample Sizes}
-%\title{A sample article title with some additional note\thanksref{t1}}
-
-\title{High-dimensional Asymptotics of Transfer Learning for Linear Regression} 
-%with Different Covariates and Sample Sizes}
-
-\runtitle{Linear Regression with Different Covariates and Sample Sizes}
-%\thankstext{T1}{A sample additional note to the title.}
-
-\begin{aug}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Only one address is permitted per author. %%
-%%Only division, organization and e-mail is %%
-%%included in the address.                  %%
-%%Additional information can be included in %%
-%%the Acknowledgments section if necessary. %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu}}
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}}
-\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3,mark]{senwu@stanford.edu}} 
-\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4,mark]{suw@wharton.upenn.edu} }
-\and
-\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5,mark]{chrismre@cs.stanford.edu}} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Addresses                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address[A]{Department of Statistics,
-University of Pennsylvania,
-\printead{e1,e4}}
-\address[B]{Khoury College of Computer Sciences, Northeastern University,
-\printead{e2}}
-\address[C]{Department of Computer Science, Stanford University,
-\printead{e3,e5}}
-
-\end{aug}
-
-\begin{abstract}
-	\FY{rewrite the abstract} Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
-First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
-Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
-We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
-This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-\end{abstract}
-
-\begin{keyword}[class=MSC2020]
-\kwd[Primary ]{62J05}
-\kwd{60B20}
-\kwd[; secondary ]{62E20, 62H10}
-\end{keyword}
-
-\begin{keyword}
-\kwd{Hard parameter sharing, high-dimensional linear regression, random matrix theory, sample covariance matrices}
-\end{keyword}
-
-\end{frontmatter}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please use \tableofcontents for articles %%
-%% with 50 pages and more                   %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\tableofcontents
-
-\section{Introduction}\label{sec_introduction}
-
-\FY{rewrite the introduction}  Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
-Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
-
-Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
-		\label{fig_intro_arch}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure*}
-
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
-
-\subsection{Setup and Main Results}
-
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
-Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
-\begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-\end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
-
-\medskip
-\noindent\textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \cite{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
-
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-\begin{itemize}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
-
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
-
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
-For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
-\end{itemize}
-
-%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-%\squishlist
-%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-%	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-%	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-%\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-%Our study also leads to several algorithmic consequences with practical interest.
-%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-
-%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-%Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
-
-\medskip
-\noindent\textbf{Proof techniques.}
-There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
-The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
-Theorem \ref{thm_main_RMT}).
-We use recently developed techniques from random matrix theory to show a sharp convergence rate.
-% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
-%\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
-See Section \ref{sec_conclude} for more discussions of the technical challenge.
-
-%This part introduces a positive variance reduction effect from adding the source labels.
-%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
-%(i) the negative effect from model shift bias.
-%(ii) the positive effect from variance reduction;
-
-\subsection{Related Work}
-
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\smallskip
-\noindent\textbf{Organizations.}
-The rest of this paper is organized as follows.
-In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation}, we validate our results in simulations.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{sec_text} describes our study on text classification tasks.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
-
-\medskip
-\noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$.
-Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$.
-In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-
-\section{Transfer learning for high-dimensional linear regression}\label{sec_HPS}
-In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
-
-\subsection{The model}
-Consider the transfer learning setting with two data sets.
-We denote their sample sizes by $n_1$ and $n_2$.
-For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
-$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
-We remark that all these assumptions are natural in high-dimensional statistics.
-
-We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let 
-\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
-where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
-entries satisfying
-\begin{equation}\label{assm1}
-\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1, 
-\end{equation}
-Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
-\be \label{conditionA2}
-\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
-\ee
-for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee
-%for a small constant $\tau>0$.
-
-We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\be\label{eq_highmoments}
-\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
-\ee
-Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$. 
-%Moreover, we assume that 
-%\be\label{eq_SNR}
-%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
-%\ee
-%for a small constant $\tau >0$.
-The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.
-
-In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that 
-\be\label{assm2}
-1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
-\ee
-for a small constant $\tau >0$.
-If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper.
-The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
-are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.
-
-We summarize our basic assumptions here for future reference.
-\begin{assumption}\label{assm_big1}
-Let $\tau$ be a small constant. 
-\begin{enumerate}
-\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}.
-%and (\ref{assm2}).
-We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-
-\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-
-\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
-
-\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.
-
-\end{enumerate}
-\end{assumption}
-
-\subsection{Transfer learning estimators}
-
-One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
-\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
-where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by  
-$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
-The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}. 
-In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
-
-Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
-$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
-%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-In this paper, we consider a natural extension of the estimator $\hat \beta^{\rm{TL}} $, that is, the \emph{hard parameter sharing} (HPS) estimator, which has been a standard type of estimator in multi-task learning \FY{citations}.
-More precisely, we study the following HPS architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
-Then we study the following minimization problem:
-\begin{align}\label{eq_tsl}
-			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
-\end{align}
-where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
-\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
-Note that $\hat \beta^{\rm{TL}}$ is a special case of $\hat{\beta}_i^{\MTL}$ by setting $A_1=A_2=1$.
-
-For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that  
-	\begin{align}
-		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
-where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
-Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers.
-Could you replace $A$ with another symbol (say $x$)?}
- \begin{align}
-		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
-			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
-		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
-	\end{align}
-Let $\hat a$ be the minimizer of $g(a)$.
-Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.
-Then the HPS estimator \eqref{def_HPS} for the target task 2 is
-\be\label{HPS_est}
-\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
-\ee
-
-In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error).
-Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
-$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$ 
-Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
-\be\label{HPS_loss}
-L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
- \ee
-We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.
-
-%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
-
-Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-\end{align}
-Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-where 
-\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-is called the bias term, which depends on the model bias between task 1 and task 2, and
-\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-%predication loss for the HPS and OLS estimators.
-
- \begin{lemma}\label{lem_HPS_loss}
- Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
-\end{align}
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-& + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
-\end{align}
-and 
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-\end{align}
-%Moreover, there exists a constant $C_0>0$ such that with high probability,
-%\be\label{loss_large}
-%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-%\ee
-%with high probability for any small constant $\e>0$. 
-\end{lemma}
-
-Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$.
-In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
-(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}.
-To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
-Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.
-
-%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
-
-For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.
-
-\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
-		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } 
-		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
-		with high probability for any small constant $\e>0$.
-\end{lemma}
- %The above result has a long history in random matrix theory.
-If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of 
-the inverse Wishart distribution \cite{anderson1958introduction}.
-For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
-Lemma 3.11 of \cite{bai2009spectral}).
-Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate.
-With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
- \end{align}
-
-On the other hand, much less is known about the predication loss of the HPS estimator.
-In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-%\FY{What is known so far about this topic?}
-In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in two different settings: (i) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
-We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
-In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
-On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
-%Here case (ii) is actually more general than (i)
-%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.   
-In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
-We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
-Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
-
-%{\cor discuss about the bias-variance trade-off}
-%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
-
-\subsection{Varying sample sizes} \label{sec_sizeratio}
-
- In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
-
-\begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
-\ee
-and 
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions  
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}. 
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)} 
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
-
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider 
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter 
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where 
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
-
-We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the rotational invariance of multivariate Gaussian distributions,
-%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence 
-the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
-
-We believe that the above argument can be extended to the case without the Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
-Hence we do not pursue this direction in this paper.
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
-
-%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
-
-To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-\begin{example}%[Sample sizes]
-\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$. 
-	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-and $\wt \beta^{(i)}$ denotes the $i$-th 
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-task-specific component whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
-	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
-
-	\begin{proposition}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Suppose Assumption \ref{assm_big1} and the above setting of random effect model hold. %in Example \ref{ex_same_cov} hold. 
-Suppose that for a constant $c_0>0$,
-	\be\label{para_rel}
-	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
-	\ee
- Then we have that for any small constant $c>0$ and large constant $ C>0$,
-	%Let $c$ be a sufficiently small fixed constant.
-	%In the setting of Corollary \ref{cor_MTL_loss}, 
-%There exists a constant $C>0$ such that
-	\be\label{hatw_add1}
-	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
-	\ee
-\end{proposition}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-%and $\wt \beta^{(i)}$ denotes the $i$-th 
-%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-
-We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
-$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
-with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations. 
-Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
-This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
-Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
-
-Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
-$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
-First, we have positive (resp.
-negative) transfer if and only if $h(\rho)>0$ (resp.
-$h(\rho)<0$).
-Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
-\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
-
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
-
-\begin{itemize}
-\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
-
-\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
-Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
-\end{itemize}
-\end{enumerate}
-Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial 
-\be\label{poly2}
- \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
-
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
-\end{enumerate}
-
-%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance. 
-%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
-\iffalse
-Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
-
-Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
-	\begin{align*}
-		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
-		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
-		= \frac{p}{n_1 + n_2 - p},
-	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit.
-	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
-
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
-This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
-by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-
-{\cor 
-For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
-	\begin{align}
-		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
-		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
-			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
-For the bias term,
-}
-
-Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
-For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
-We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
-It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
-By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
-\fi
-	\end{example}
-
-	\FY{add simulations to check our results and the above dichotomies}
-
-\subsection{Covariate shift}\label{sec_diff}
-
-%The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$. 
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
-
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$) 
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-%for some small constant $0<\tau<1$. 
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
-
-\begin{theorem}\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}: 
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
-			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
-			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that 
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
-Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
-%also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
-and plug them into \eqref{lem_cov_shift_eq}.
-The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
-
-\begin{example} %[Covariate shift]
-\label{ex_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds.
-In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
-Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
-$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
-where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
-We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
-\end{align*}
-%belong to the following bounded set.
-%Let $\lambda_i$ be the $i$-th singular value of $M$.
-%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-%\vspace{-0.025in}
-%{\small}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-%\begin{proposition}[Covariate shift]\label{prop_covariate}
-%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-%	We have that
-%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
-%\end{proposition}
-%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
-Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix. 
-%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-%Let 
-%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
-%We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
-%\be \nonumber
-%\begin{split}
-%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
-%\end{split}
-%\ee
-%with high probability for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-%
-%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-%\begin{align}\label{gvar_extra}
-%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-%\end{align}
-In fact, from equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
- a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
-\ee
-Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that 
-%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-%\begin{align}\label{approximateteM}
-%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-%\end{align}
-%where
-$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}. 
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that 
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
-
-%Hence we get that 
-%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-%
-%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-%\begin{align}\label{gvar_extra2}
-%\begin{split}
-%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-%\end{split}
-%\end{align}
-%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-%\end{proof}
-
-\iffalse
-For large enough $p$,
-%in the left hand side of equation \eqref{lem_cov_shift_eq}:
-\begin{align*}
-	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
-\end{align*}
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
-\fi
-
-%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}. 
-%Our first observation is that:
-However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
-We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$.
-In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
-When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
-%while as As $\lambda$ increases, the severity of covariate shift increases.
-We claim the following dichotomy.
-\begin{enumerate}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-\end{enumerate}
-We explain why the above dichotomy happens. We can write the variance limit as
-$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
-When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
-$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
-where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
-\begin{align*}
-\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
-\end{align*}
-%in this example is equal to
-%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
-%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%where $g(\lambda, a_1) \ge 0$.
-%and can be derived from algebraic calculations (details omitted).
-We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
-In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
-\begin{align*}
- \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
-\end{align*}
-%\begin{align*}
-% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-%\end{align*}
-This implies $n_1>n_2$.
-The other direction follows from a similar argument.
-% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
-\end{example}
-
-\iffalse
-%FY: Below was the word explanation. I still think the above simple proof is clearer.
-In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
-The other case when $n_1 < n_2$ is similar.
-A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
-If $n_1< n_2$, then $f(\lambda)< f(1)$.
-\fi
-
-For the bias limit, we have the following proposition.
-
-\begin{proposition}\label{prop_main_RMT}
-%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
-			\begin{align}
-				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
-				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
-			\end{align}
-%			\begin{align}\label{lem_cov_derv_eq}
-%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-%			\end{align}
-				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
-				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-		\be  \label{eq_a34extra}
-		\begin{split}
-				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
-				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{split}
-			\ee  
-			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
-
-Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
-Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
-Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
-$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$ 
-and
-$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
-Using these estimates, it is easy to check that  
-\begin{align}
-& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
-&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
-\label{bias_LLN}
-\end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
-However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
-
-\begin{remark}
-%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%\begin{remark}
-The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
-We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
-We leave this problem to future study.
-
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
-%\end{remark}
-\end{remark}
-
-\FY{add simulations to check our results}
-
-\section{Insights for transfer learning}
-
-\FY{discuss applications and insights of our results}
-
-\subsection{Comparison between the averaging and HPS estimators}
-
-\subsection{Algorithmic implications}
-\FY{the progressive training; covariance alignment; and others?}
-
-\section{Extension to multi-task learning}\label{sec_same}
+\section{Asymptotics for Multiple Tasks}\label{sec_same}
 
@@
 %It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}
+
+%Suppose we have $t$ datasets.
+%For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
+%Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
+%We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
+%We study the standard hard parameter sharing architecture:
+%a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
+%See Figure \ref{fig_intro_arch} for an illustration.
+%The width of $B$, denoted by $r$, plays an important role in regularization.
+%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
+%Hence, we assume that $r < t$ in our study.
+%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
+%We study the following minimization problem:
+%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
+%	The size of each set is described below.
+%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
+%\vspace{-0.1in}
+%\begin{align}\label{eq_mtl}
+%			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
+%\end{align}
+%\vspace{-0.05in}
+%where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
 
@@
 
-%The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-%It is not hard to extend the above result to the cases with more than two tasks.
-We make this extension for the following reasons.
-First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
-Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-
-%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-%\medskip
-%
-%\noindent\textbf{Comparison to single-task learning (STL).}
-%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
-%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
-%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
-%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.
-
-\iffalse
 \paragraph{How does hard parameter sharing scale with sample size $n$?}
@@
 		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
-		\fi
 
@@
 
-\FY{add simulations to check our results; discuss possible applications}
-
-\section{Experiments}
-
-\subsection{Simulation Studies}\label{sec_simulation}
-
-\FY{move the simulations results to previous sections}
 We demonstrate the accuracy of our results in simulations.
@@
 
-\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
+%The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
 
-Our results and simulations are all in the high-dimensional linear regression setting.
-How well do they extend to other scenarios?
-In this section, we conduct further studies on six text classification datasets.
-Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
-%The question is to predict positive or negative sentiment expressed in the text.
-Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
-For LSTM, we add a shared feature representation layer on top of word embeddings.}
+%It is not hard to extend the above result to the cases with more than two tasks.
+We make this extension for the following reasons.
+First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
+Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
+Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
 
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-%There are 14 diseases (tasks) for every image that we would like to predict.
-%We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-%We evaluate three model choices.
-%\textit{Predicting transfer effect via STL results.}
-%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-%A common challenge in the study of MTL is that the results can be hard to understand.
-%It is difficult to predict when MTL performs well without running extensive trials.
-%Our insight is that we can use STL results to help understand MTL results.
-%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
+%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
+%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
+%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
+%\begin{align}
+%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
+%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
+%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
+%\end{align}
+%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
+%Compared to the prediction loss of single-task learning (cf.
+equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
+%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
+%We show the generalization error of hard parameter sharing estimators.
+%Before stating the result, we define the following notations.
 
-\paragraph{Sample size ratio.}
-First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
-On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.
+%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
+%\medskip
+%
+%\noindent\textbf{Comparison to single-task learning (STL).}
+%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
+%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
+%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
+%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
+%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
+%On the other hand, the bias always increases.
 
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
-Concretely, here is one implementation of this idea.
-%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
-\begin{itemize}
-	\item We divide the training data into $S$ batches.
-	We divide the training procedure into $S$ stages. During every stage, we progressively add one more data batch.
-	\item During every stage, we train for $T$ epochs using only the $S$ batches.
-If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
-%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\end{itemize}
-If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
-%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
-The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
+%\FY{add simulations to check our results; discuss motivations and possible applications}
+\iffalse
+In this paper, we consider a natural extension of the estimator $\hat \beta^{\rm{TL}} $, that is, the \emph{hard parameter sharing} (HPS) estimator, which has been a standard type of estimator in multi-task learning \FY{citations}.
+More precisely, we study the following HPS architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
+Then we study the following minimization problem:
+\begin{align}\label{eq_tsl}
+			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
+\end{align}
+where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as
+\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
+Note that $\hat \beta^{\rm{TL}}$ is a special case of $\hat{\beta}_i^{\MTL}$ by setting $A_1=A_2=1$.
 
-%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-%\squishlist
-%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-%TREC is less similar to MR because the task is about question types.
-%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
-We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
-We include all of task two's data and progressively add task one's data using the procedure described above.
-Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
-%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we conduct multi-task training on all six datasets jointly.
-We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
-We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
-%As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-%	\begin{subfigure}[b]{0.33\textwidth}
-%		\centering
-%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-%		\caption{Task similarity}
-%		\label{fig_ab_sim}
-%	\end{subfigure}%
-%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c)
-%	Note: (S) denotes the source task and (T) denotes the target task.}
-
-%\begin{minipage}[t]{.58\textwidth}
-%	\vspace{-0.1in}
-%	\centering
-%  \begin{tabular}{c c c c c}
-%	\toprule
-%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%		& Precision &  Recall & Precision &  Recall \\
-%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
-		% 0.3 & 1.000 & 0.004 &     - &     - \\
-%	\bottomrule
-%	\end{tabular}
-%	\vspace{0.1in}
-%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-%	\label{tab:mtl_better_than_stl}
-%\end{minipage}%
-%\quad
-
-\paragraph{Covariate shift}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
-
-%\begin{figure}[!t]
-%	\centering
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-%		\caption{Averaged over all 16 task pairs}
-%		\label{fig_ab_cov}
-%	\end{subfigure}\hfill
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{An example task pair}
-%		\label{fig_cov_a}
-%	\end{subfigure}
-%	\caption{ (TREC and CR)}
-%\end{figure}
-
-%\textbf{Further results of the covariance alignment procedure.}
-%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
-%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
-%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
-%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
-%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
-%We leave this question for future work.
-%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
-
-%\begin{figure}[!h]
-%	\centering
-%	\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{Task pair TREC and CR}
-%		\label{fig_cov_a}
-%	\end{subfigure}\hfill
-%		\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-%		\caption{Task pair MR and SST}
-%			\label{fig_cov_b}
-%	\end{subfigure}
-%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
-%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
-%	\label{fig_covariate_app}
-%\end{figure}
-
-\begin{figure}%[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
-		\caption{HPS vs. STL}
-		\label{fig_ab_data}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
-		\caption{HPS vs. covariance alignment}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \cite{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
-	\label{fig_text}
-%	\begin{minipage}[t]{0.4\textwidth}
-%		\centering
-%		\vspace{0pt}
-%		\begin{tabular}{c c c}
-%		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-%		& all tasks & w/o TREC \\
-%		\midrule
-%		{\bf MLP}  & 31\% & 29\% \\
-%		{\bf LSTM} & 35\% & 34\% \\
-%		{\bf CNN}  & 30\% & 28\% \\
-%		\bottomrule
-%		\end{tabular}
-%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
-%		\label{tab:taskonomy}
-%	\end{minipage}
-\end{figure}
-
-%\begin{algorithm}[!t]
-%	\caption{A progressive training schedule given two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
-%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, A_2$ optimized for task $2$.
-%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}
-
-\iffalse
-\section{Conclusions and Discussions}\label{sec_conclude}
-
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on text classification tasks.
-We describe several open questions for future work.
-%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-%Second, it would be interesting to extend our result to classification problems such as logistic regression.
-First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
-%but its singular values will follow a different distribution since the matrix is not symmetric.
- %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
-An interesting question is to study logistic regression in a multiple-sample setting.
+For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that
+	\begin{align}
+		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
+		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
+	\end{align}
+where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
+Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers.
+Could you replace $A$ with another symbol (say $x$)?}
+ \begin{align}
+		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
+			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
+		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
+		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
+	\end{align}
+Let $\hat a$ be the minimizer of $g(a)$.
+Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.
+Then the HPS estimator \eqref{def_HPS} for the target task 2 is
+\be\label{HPS_est}
+\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
+\ee
 \fi
-
-% \section*{Acknowledgements}
-%Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
-Hongyang R.
-Zhang and Weijie J.
-Su's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
-%We gratefully acknowledge the support of DARPA under Nos.
-FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.
-U54EB020405 (Mobilize), NSF under Nos.
-CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No.
-N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys.
-The U.S.
-Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S.
-Government.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Material, if any, should   %%
-%% be provided in {supplement} environment  %%
-%% with title and short description.        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{supplement}
-\textbf{Supplement to ``Hard Parameter Sharing in High-dimensional Linear Regression"}.
-In \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
-%and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
-\end{supplement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                  The Bibliography                       %%
-%%                                                         %%
-%%  imsart-???.bst  will be used to                        %%
-%%  create a .BBL file for submission.                     %%
-%%                                                         %%
-%%  Note that the displayed Bibliography will not          %%
-%%  necessarily be rendered by Latex exactly as specified  %%
-%%  in the online Instructions for Authors.                %%
-%%                                                         %%
-%%  MR numbers will be added by VTeX.                      %%
-%%                                                         %%
-%%  Use \cite{...} to cite references in text.             %%
-%%                                                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% if your bibliography is in bibtex format, uncomment commands:
-\bibliographystyle{imsart-number}
-%\bibliographystyle{imsart-nameyear}
-
-%\bibliographystyle{abbrv}
-%\bibliographystyle{plain}
-\bibliography{rf,ref_mtl}
- % Style BST file (imsart-number.bst or imsart-nameyear.bst)
-%\bibliography{bibliography}       % Bibliography file (usually '*.bib')
-
-%% or include bibliography directly:
-%\begin{thebibliography}{4}
-%%%
-%\bibitem{r1}
-%\textsc{Billingsley, P.} (1999). \textit{Convergence of
-%Probability Measures}, 2nd ed.
-%Wiley, New York.
-%
-%\bibitem{r2}
-%\textsc{Bourbaki, N.}  (1966). \textit{General Topology}  \textbf{1}.
-%Addison--Wesley, Reading, MA.
-%
-%\bibitem{r3}
-%\textsc{Ethier, S. N.} and \textsc{Kurtz, T. G.} (1985).
-%\textit{Markov Processes: Characterization and Convergence}.
-%Wiley, New York.
-%
-%\bibitem{r4}
-%\textsc{Prokhorov, Yu.} (1956).
-%Convergence of random processes and limit theorems in probability
-%theory. \textit{Theory  Probab.  Appl.}
-%\textbf{1} 157--214.
-%\end{thebibliography}
-
-\end{document}

### 2021-06-12 revision_journal/results.tex
revision wip

--- 2021-06-12 revision_journal/backup/Jan 31 2021/manuscript.tex
@@
-\documentclass[aos,preprint]{imsart}
-\usepackage{xr}
-	\externaldocument{./suppl}
-
-%% Packages
-\def\shownotes{0}
-%\usepackage{natbib}
-%\setcitestyle{authoryear,open={(},close={)}}
-%\renewcommand{\cite}{\citep}
-\usepackage[export]{adjustbox}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{fullpage}
-\usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
-\usepackage{macro_fan}
-\usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage{caption,subcaption}
-%\usepackage{breqn}
-
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Uncomment next line to change            %%
-%% the type of equation numbering           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\numberwithin{equation}{section}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Axiom, Claim, Corollary, Hypothezis, %%
-%% Lemma, Theorem, Proposition              %%
-%% use \theoremstyle{plain}                 %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\theoremstyle{plain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Assumption, Definition, Example,     %%
-%% Notation, Property, Remark, Fact         %%
-%% use \theoremstyle{remark}                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please put your definitions here:        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-%\title{High-dimensional Asymptotics of Linear Regression with Different Covariates and Sample Sizes}
-%\title{A sample article title with some additional note\thanksref{t1}}
-
-\title{High-dimensional Asymptotics of Transfer Learning for Linear Regression} 
-%with Different Covariates and Sample Sizes}
-
-\runtitle{Linear Regression with Different Covariates and Sample Sizes}
-%\thankstext{T1}{A sample additional note to the title.}
-
-\begin{aug}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Only one address is permitted per author. %%
-%%Only division, organization and e-mail is %%
-%%included in the address.                  %%
-%%Additional information can be included in %%
-%%the Acknowledgments section if necessary. %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu}}
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}}
-\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3,mark]{senwu@stanford.edu}} 
-\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4,mark]{suw@wharton.upenn.edu} }
-\and
-\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5,mark]{chrismre@cs.stanford.edu}} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Addresses                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address[A]{Department of Statistics,
-University of Pennsylvania,
-\printead{e1,e4}}
-\address[B]{Khoury College of Computer Sciences, Northeastern University,
-\printead{e2}}
-\address[C]{Department of Computer Science, Stanford University,
-\printead{e3,e5}}
-
-\end{aug}
-
-\begin{abstract}
-	\FY{rewrite the abstract} Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
-First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
-Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
-We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
-This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-\end{abstract}
-
-\begin{keyword}[class=MSC2020]
-\kwd[Primary ]{62J05}
-\kwd{60B20}
-\kwd[; secondary ]{62E20, 62H10}
-\end{keyword}
-
-\begin{keyword}
-\kwd{Hard parameter sharing, high-dimensional linear regression, random matrix theory, sample covariance matrices}
-\end{keyword}
-
-\end{frontmatter}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please use \tableofcontents for articles %%
-%% with 50 pages and more                   %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\tableofcontents
-
-\section{Introduction}\label{sec_introduction}
-
-\FY{rewrite the introduction}  Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
-Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
-
-Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
-		\label{fig_intro_arch}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure*}
-
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
-
-\subsection{Setup and Main Results}
-
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
-Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
-\begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-\end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
-
-\medskip
-\noindent\textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \cite{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
-
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-\begin{itemize}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
-
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
-
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
-For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
-\end{itemize}
-
-%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-%\squishlist
-%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-%	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-%	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-%\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-%Our study also leads to several algorithmic consequences with practical interest.
-%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-
-%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-%Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
-
-\medskip
-\noindent\textbf{Proof techniques.}
-There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
-The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
-Theorem \ref{thm_main_RMT}).
-We use recently developed techniques from random matrix theory to show a sharp convergence rate.
-% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
-%\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
-See Section \ref{sec_conclude} for more discussions of the technical challenge.
-
-%This part introduces a positive variance reduction effect from adding the source labels.
-%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
-%(i) the negative effect from model shift bias.
-%(ii) the positive effect from variance reduction;
-
-\subsection{Related Work}
-
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\smallskip
-\noindent\textbf{Organizations.}
-The rest of this paper is organized as follows.
-In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation}, we validate our results in simulations.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{sec_text} describes our study on text classification tasks.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
-
-\medskip
-\noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$.
-Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$.
-In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-
-\section{Transfer learning for high-dimensional linear regression}\label{sec_HPS}
+\section{Preliminaries and Notations}\label{sec_HPS}
 In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
 
-\subsection{The model}
-Consider the transfer learning setting with two data sets.
-We denote their sample sizes by $n_1$ and $n_2$.
-For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
-$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
-We remark that all these assumptions are natural in high-dimensional statistics.
-
-We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let 
-\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
-where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
-entries satisfying
-\begin{equation}\label{assm1}
-\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1, 
-\end{equation}
+\subsection{Assumptions}
 Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
@@
 
-\subsection{Transfer learning estimators}
-
-One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
-\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
-where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by  
-$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
-The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}. 
-In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
-
-Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
-$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
+%\subsection{Transfer learning estimators}
+
 %\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-In this paper, we consider a natural extension of the estimator $\hat \beta^{\rm{TL}} $, that is, the \emph{hard parameter sharing} (HPS) estimator, which has been a standard type of estimator in multi-task learning \FY{citations}.
-More precisely, we study the following HPS architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
-Then we study the following minimization problem:
-\begin{align}\label{eq_tsl}
-			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
-\end{align}
-where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
-\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
-Note that $\hat \beta^{\rm{TL}}$ is a special case of $\hat{\beta}_i^{\MTL}$ by setting $A_1=A_2=1$.
-
-For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that  
-	\begin{align}
-		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
-where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
-Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers.
-Could you replace $A$ with another symbol (say $x$)?}
- \begin{align}
-		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
-			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
-		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
-	\end{align}
-Let $\hat a$ be the minimizer of $g(a)$.
-Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.
-Then the HPS estimator \eqref{def_HPS} for the target task 2 is
-\be\label{HPS_est}
-\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
-\ee
 
@@
 
-\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
-
-\subsection{Varying sample sizes} \label{sec_sizeratio}
-
- In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
-
-\begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
-\ee
-and 
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions  
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}. 
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)} 
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
-
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider 
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter 
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where 
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
-
-We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the rotational invariance of multivariate Gaussian distributions,
-%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence 
-the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
-
-We believe that the above argument can be extended to the case without the Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
-Hence we do not pursue this direction in this paper.
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
-
-%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
-
-To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-\begin{example}%[Sample sizes]
-\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$. 
-	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-and $\wt \beta^{(i)}$ denotes the $i$-th 
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-task-specific component whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
-	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
-
-	\begin{proposition}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Suppose Assumption \ref{assm_big1} and the above setting of random effect model hold. %in Example \ref{ex_same_cov} hold. 
-Suppose that for a constant $c_0>0$,
-	\be\label{para_rel}
-	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
-	\ee
- Then we have that for any small constant $c>0$ and large constant $ C>0$,
-	%Let $c$ be a sufficiently small fixed constant.
-	%In the setting of Corollary \ref{cor_MTL_loss}, 
-%There exists a constant $C>0$ such that
-	\be\label{hatw_add1}
-	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
-	\ee
-\end{proposition}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-%and $\wt \beta^{(i)}$ denotes the $i$-th 
-%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-
-We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
-$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
-with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations. 
-Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
-This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
-Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
-
-Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
-$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
-First, we have positive (resp.
-negative) transfer if and only if $h(\rho)>0$ (resp.
-$h(\rho)<0$).
-Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
-\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
-
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
-
-\begin{itemize}
-\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
-
-\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
-Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
-\end{itemize}
-\end{enumerate}
-Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial 
-\be\label{poly2}
- \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
-
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
-\end{enumerate}
-
-%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance. 
-%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
-\iffalse
-Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
-
-Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
-	\begin{align*}
-		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
-		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
-		= \frac{p}{n_1 + n_2 - p},
-	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit.
-	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
-
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
-This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
-by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-
-{\cor 
-For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
-	\begin{align}
-		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
-		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
-			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
-For the bias term,
-}
-
-Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
-For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
-We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
-It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
-By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
-\fi
-	\end{example}
-
-	\FY{add simulations to check our results and the above dichotomies}
-
-\subsection{Covariate shift}\label{sec_diff}
+%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
+
+\section{Asymptotics under Covariate Shift}\label{sec_diff}
 
@@
 
-\FY{add simulations to check our results}
-
-\section{Insights for transfer learning}
-
-\FY{discuss applications and insights of our results}
-
-\subsection{Comparison between the averaging and HPS estimators}
-
-\subsection{Algorithmic implications}
-\FY{the progressive training; covariance alignment; and others?}
-
-\section{Extension to multi-task learning}\label{sec_same}
-
-%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
-%We provide a sharp generalization error bound of hard parameter sharing estimators.
-
-Hard parameter sharing is a commonly used architecture in multi-task learning.
-However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning.
-In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates.
-We make this extension for the following reasons.
-First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly.
-Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below.
-Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}
-
-\vspace{5pt}
-\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
-The label vector of the $i$-th task follows a linear model
-$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
-We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
-
-%\begin{enumerate}
-%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-%\end{enumerate}
-
-	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
-	\begin{align}
-		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
-%Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-
-	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
-Hence we only consider the case with $r<t$.
-\FY{Correct it if the reason is wrong.}
-
-	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
-	\begin{align}
-		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
-		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
-	\end{align}
-	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
-	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
-	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
-	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
-	\end{align}
-%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
-%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
-%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
-
-Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
-\begin{align}\label{eq_A_star}
-	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
-\end{align}
-where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
- To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
-Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
- %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
-Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
-Then we have the following result.
-
-% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
-%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
-%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
-%Our result is stated as follows.
-
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
-	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
-Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability, 
-\be\label{minimizer_beta}
-\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
-\ee
-where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
-	\begin{align}
-		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
-		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
-\label{Li_multi1}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
-%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
-%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
-Finally, we have a better bound for the averaged prediction loss:  with high probability,
-\begin{align}
-&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
- &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
-\end{align}
-
+%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
+
+%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
+
+\section{Asymptotics under Imbalanced Sample Sizes} \label{sec_sizeratio}
+
+ In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
+However, the two tasks can have different sample sizes $n_1\ne n_2$.
+In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
+We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
+
+\begin{theorem}\label{cor_MTL_loss}
+Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
+Gaussian random variables.
+Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
+\be\label{Lvar_samplesize}
+L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
+\ee
+and
+\begin{align}
+L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
+&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
+	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
+	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
+	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
+	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
+	 \end{align}
+Here we define the functions
+\begin{align*}
+&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
+&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
+\end{align*}
+where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
+\begin{align*}
+\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}.
+%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
+%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)}
+ \end{align*}
+%	In the setting of Example \ref{ex_sample_ratio}, assume that
+%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
+%	(i) both tasks sample sizes are at least $3p$;
+%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
+%%	\be\label{choiceofpara0}
+%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
+%	%\be\label{choiceofpara0}
+%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
+%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
+%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
+%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
+%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
+%	With high probability over the randomness of the input,
+%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
+%	\begin{align}
+%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
+%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
+%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
+%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
+%	 \end{align}
+%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
+%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
+We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
 	 \end{theorem}
 
-Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
-Moreover, the factor $(\lambda_r - \lambda_{r+1})^{-1}$ is natural, because the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not stable when $\lambda_r $ and $\lambda_{r+1} $ are close to each other.
-The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
-The estimate \eqref{Li_multi1}
- gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
-Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases for the multi-task HPS estimator.
-On the other hand, the bias term always increases (because the bias in single-task linear regression is zero).
-Hence as in the transfer learning setting, whether the HPS estimator is better than the OLS estimator depends on an intricate  {bias-variance tradeoff}.
-%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.}
-We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
-Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
-For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
-
-The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
-Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
-For the reader's convenience, we give the precise statement in Corollary \ref{thm_two_tasks}.
-%Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.  
-%In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$. 
-We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix  
-$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
-% is the matrix formed by the linear model parameters of the two tasks. 
-Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined.
-%Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
-In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-\begin{corollary}\label{thm_two_tasks}
-Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2\equiv n$. Let $c>0$ be an arbitrary (small) constant. Then we have that with high probability, 
-\be\label{minimizer_beta1}
-\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
-\ee
-where $u_{\hat a}$ is the unit vector defined as
-$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-%for task 2,  % over the randomness of the input, 
-Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
-	\begin{align}
-		& \bigabs{L_2(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) \cdot B^{\star}A^{\star}  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
-		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	 where $A^\star(2)$ denotes the second entry of $A^\star$.
-	 \end{corollary}
-
-%The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-%It is not hard to extend the above result to the cases with more than two tasks.
-We make this extension for the following reasons.
-First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
-Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-
-%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-%\medskip
-%
-%\noindent\textbf{Comparison to single-task learning (STL).}
-%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
-%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
-%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
-%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.
-
 \iffalse
-\paragraph{How does hard parameter sharing scale with sample size $n$?}
-Obviously, the concentration error decreases with $n$.
-First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
-It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
-
-\begin{assumption}\label{assume_rm}
-	Let $\tau > 0$ be a small enough constant.
-%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
-entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	In the high-dimensional setting,
-%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-%			\begin{align}\label{assmAhigh}
-%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
-%			\end{align}
-  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
-%	\end{enumerate}
-\end{assumption}
-Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
-
-\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	With high probability over the randomness of $X$, we have that
-		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
-\end{fact}
-\noindent\textit{Remark.} The above result has a long history in random matrix theory.
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
-Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
-		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
+ We need to state a result for Gaussian matrix ...... Consider
+$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
+In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
+$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
+Then we define the following parameters:
+\begin{align*}
+x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
+\end{align*}
+We have that
+$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
+In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter
+%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
+%where
+$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
 \fi
 
-%Finally, for the random noise component, we assume that all of its moments exist.
-%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
-%\begin{align}\label{assmAhigh2}
-%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
-%\end{align}
-%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
-%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
-
-%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
-To illustrate the {bias-variance tradeoff quantitively, we consider an extension of the random-effect model in Example \ref{ex_sample_ratio} to the multi-task setting.
-%which has been studied for  single-task linear regression and ridge regression (see e.g.
+We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
+The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
+For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
+In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
+On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
+In the setting of Theorem \ref{cor_MTL_loss}, we can write
+\begin{align*}
+L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
+\end{align*}
+where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
+\begin{align}\label{Lbias_idea}
+L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
+\end{align}
+up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
+\begin{align}\nonumber %\label{Lbias_idea2}
+L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
+\end{align}
+It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
+From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
+Due to the rotational invariance of multivariate Gaussian distributions,
+%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence
+the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
+In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
+We use that result to obtain a convergence estimate on
+$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
+Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
+We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
+
+We believe that the above argument can be extended to the case without the Gaussian assumption.
+For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
+However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
+Hence we do not pursue this direction in this paper.
+
+To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
 \cite{dobriban2020wonder,dobriban2018high}).
 
-\begin{example}%[Random-effect model]
-\label{ex_same_cov}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-Suppose that {$\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$} for $ i=1,2,\cdots, t,$
+ %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
+Next, we illustrate how varying them impact the prediction loss.
+\begin{example}%[Sample sizes]
+\label{ex_sample_ratio}
+	%We first consider the impact of varying sample sizes.
+	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
+	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
+	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
+$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
 where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
@@
 %Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. 
-%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
-%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
-In this random-effect model, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
-%Based on the definition of the random-effect model, 
-the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
-%\begin{align*}
-%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
-%\end{align*}
-\begin{align}\label{betaSbeta}
-	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
-\end{align}
- with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}. 
-%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
-With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
-$$\lambda_1=\left[1+\OO(p^{-1/2+c})\right]\cdot\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
-and
-$$ \lambda_i=\left[1+\OO(p^{-1/2+c})\right]\cdot \frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
-Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
-$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
-with high probability. 
-%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
-%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
-%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
-%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
-Then using \eqref{Li_multi2}, we obtain that
-\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p.
-}\]
-%We describe a proof sketch.
-%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
-%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
-%Second, using Fact \ref{fact_tr}, one can see that the average variance is
-%\begin{align*}
-%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
-%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
-%\end{align*}
-%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
-%Combined together, we have derived the average prediction loss in the random-effect model.
-%If the error is sufficiently small, then 
-Comparing the above equation with \eqref{L_STL_simple01} (and ignoring the small error), we have the following observations. 
-%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
-%Comparing HPS to STL, we have the following qualitative properties.
-%	Suppose $n$ is sufficiently large so that the error is negligible.
-%\begin{enumerate}
+task-specific component whose entries are i.i.d.
+Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
+	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
+
+	\begin{proposition}\label{lem_hat_v}
+%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
+Suppose Assumption \ref{assm_big1} and the above setting of random effect model hold. %in Example \ref{ex_same_cov} hold.
+Suppose that for a constant $c_0>0$,
+	\be\label{para_rel}
+	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
+	\ee
+ Then we have that for any small constant $c>0$ and large constant $ C>0$,
+	%Let $c$ be a sufficiently small fixed constant.
+	%In the setting of Corollary \ref{cor_MTL_loss},
+%There exists a constant $C>0$ such that
+	\be\label{hatw_add1}
+	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
+	\ee
+\end{proposition}
+%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
+%More precisely, %we have
+%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
+%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
+%and $\wt \beta^{(i)}$ denotes the $i$-th
+%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
+%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+
+We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
+Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
+$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
+with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations.
+Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
+First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
+This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
+Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
+Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
+
+Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
+$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
+This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
+First, we have positive (resp.
+negative) transfer if and only if $h(\rho)>0$ (resp.
+$h(\rho)<0$).
+Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
+\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
+We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
 \begin{enumerate}
-	\item {\bf Positive vs.
-negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
-
-	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
-Hence increasing the width $r$ of the shared feature representation layer does not help.
-	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-
-	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
-Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
-More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
-	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
-}\]
-	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
-	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$ 
-	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
-
-	%samples that is less than $n$ samples to get comparable loss to STL.
-	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
+\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
+
+\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
+
+\begin{itemize}
+\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
+
+\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
+Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
+\end{itemize}
 \end{enumerate}
-
+Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial
+\be\label{poly2}
+ \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
+Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
+\begin{enumerate}
+\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
+
+\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
+Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
+\end{enumerate}
+
+%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance.
+%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
+\iffalse
+Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
+
+Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
+	\begin{align*}
+		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
+		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
+		= \frac{p}{n_1 + n_2 - p},
+	\end{align*}
+	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
+	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
+	Similarly, we can calculate the bias limit.
+	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
+
+In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
+This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
+The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
+As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
+by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
+The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
+
+{\cor
+For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
+\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
+with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that
+	\begin{align}
+		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
+		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
+			\end{align}
+Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
+\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
+For the bias term,
+}
+
+Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
+For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
+We assume that $n_2$ is fixed for simplicity.
+%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
+The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
+It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
+%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
+%We describe a sketch of the proof.
+By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
+\begin{enumerate}
+	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
+	Intuitively, this regime of $d^2$ always helps task two.
+	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
+	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
+\end{enumerate}
+\fi
 	\end{example}
-
-\FY{add simulations to check our results; discuss possible applications}
-
-\section{Experiments}
-
-\subsection{Simulation Studies}\label{sec_simulation}
-
-\FY{move the simulations results to previous sections}
-We demonstrate the accuracy of our results in simulations.
-While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
-		\caption{Example \ref{ex_same_cov}}
-		\label{fig_same_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
-		\caption{Example \ref{ex_sample_ratio}}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
-		\caption{Example \ref{ex_covshift}}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
-	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
-%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
-	\label{fig_model_shift_phasetrans}
-\end{figure*}
-
-\paragraph{Sample efficiency}
-First, we validate the result of Example \ref{ex_same_cov}.
-Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
-In all the parameter settings, our results estimate the empirical losses accurately.
-We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
-Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
-%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
-Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level.
-%\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
-For example, at the cross point, this ratio is 1.
-}
-
-\paragraph{Sample size ratio}
-Second, we validate the result of Example \ref{ex_sample_ratio}.
-Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-%Again, our estimates are accurate compared to the empirical losses.
-We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
-The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
-On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
-Intuitively, this is because bias increases less for smaller $d^2$.
-%Our result from Corollary \ref{cor_MTL_loss} explains this trend.
-
-\paragraph{Covariate shift}
-Finally, we validate the result of Example \ref{ex_covshift}.
-Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
-The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
-%Covariate shift: We set $\kappa = 1$ and $d = 0$.
-%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-
-%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-%\begin{table}
-%	\begin{center}
-%		\begin{tabular}{c c c c c}
-%			\toprule
-%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
-%			\midrule
-%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-			% {\bf CNN}  & 76\% & - & 32\% & -\\
-%			\bottomrule
-%		\end{tabular}
-%	\end{center}
-%	\caption{Taskonomy experiment.}
-%	\label{tab:taskonomy}
-%\end{table}
-%\begin{figure}[!t]
-%	\centering
-%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
-%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
-%	\label{fig_same_cov}
-%\end{figure}
-
-\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
-
-Our results and simulations are all in the high-dimensional linear regression setting.
-How well do they extend to other scenarios?
-In this section, we conduct further studies on six text classification datasets.
-Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
-%The question is to predict positive or negative sentiment expressed in the text.
-Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
-For LSTM, we add a shared feature representation layer on top of word embeddings.}
-
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-%There are 14 diseases (tasks) for every image that we would like to predict.
-%We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-%We evaluate three model choices.
-%\textit{Predicting transfer effect via STL results.}
-%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-%A common challenge in the study of MTL is that the results can be hard to understand.
-%It is difficult to predict when MTL performs well without running extensive trials.
-%Our insight is that we can use STL results to help understand MTL results.
-%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
-
-\paragraph{Sample size ratio.}
-First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
-On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.
-
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
-Concretely, here is one implementation of this idea.
-%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
-\begin{itemize}
-	\item We divide the training data into $S$ batches.
-	We divide the training procedure into $S$ stages. During every stage, we progressively add one more data batch.
-	\item During every stage, we train for $T$ epochs using only the $S$ batches.
-If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
-%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\end{itemize}
-If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
-%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
-The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
-
-%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-%\squishlist
-%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-%TREC is less similar to MR because the task is about question types.
-%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
-We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
-We include all of task two's data and progressively add task one's data using the procedure described above.
-Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
-%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we conduct multi-task training on all six datasets jointly.
-We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
-We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
-%As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-%	\begin{subfigure}[b]{0.33\textwidth}
-%		\centering
-%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-%		\caption{Task similarity}
-%		\label{fig_ab_sim}
-%	\end{subfigure}%
-%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c)
-%	Note: (S) denotes the source task and (T) denotes the target task.}
-
-%\begin{minipage}[t]{.58\textwidth}
-%	\vspace{-0.1in}
-%	\centering
-%  \begin{tabular}{c c c c c}
-%	\toprule
-%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%		& Precision &  Recall & Precision &  Recall \\
-%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
-		% 0.3 & 1.000 & 0.004 &     - &     - \\
-%	\bottomrule
-%	\end{tabular}
-%	\vspace{0.1in}
-%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-%	\label{tab:mtl_better_than_stl}
-%\end{minipage}%
-%\quad
-
-\paragraph{Covariate shift}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
-
-%\begin{figure}[!t]
-%	\centering
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-%		\caption{Averaged over all 16 task pairs}
-%		\label{fig_ab_cov}
-%	\end{subfigure}\hfill
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{An example task pair}
-%		\label{fig_cov_a}
-%	\end{subfigure}
-%	\caption{ (TREC and CR)}
-%\end{figure}
-
-%\textbf{Further results of the covariance alignment procedure.}
-%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
-%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
-%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
-%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
-%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
-%We leave this question for future work.
-%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
-
-%\begin{figure}[!h]
-%	\centering
-%	\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{Task pair TREC and CR}
-%		\label{fig_cov_a}
-%	\end{subfigure}\hfill
-%		\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-%		\caption{Task pair MR and SST}
-%			\label{fig_cov_b}
-%	\end{subfigure}
-%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
-%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
-%	\label{fig_covariate_app}
-%\end{figure}
-
-\begin{figure}%[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
-		\caption{HPS vs. STL}
-		\label{fig_ab_data}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
-		\caption{HPS vs. covariance alignment}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \cite{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
-	\label{fig_text}
-%	\begin{minipage}[t]{0.4\textwidth}
-%		\centering
-%		\vspace{0pt}
-%		\begin{tabular}{c c c}
-%		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-%		& all tasks & w/o TREC \\
-%		\midrule
-%		{\bf MLP}  & 31\% & 29\% \\
-%		{\bf LSTM} & 35\% & 34\% \\
-%		{\bf CNN}  & 30\% & 28\% \\
-%		\bottomrule
-%		\end{tabular}
-%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
-%		\label{tab:taskonomy}
-%	\end{minipage}
-\end{figure}
-
-%\begin{algorithm}[!t]
-%	\caption{A progressive training schedule given two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
-%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, A_2$ optimized for task $2$.
-%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}
-
-\iffalse
-\section{Conclusions and Discussions}\label{sec_conclude}
-
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on text classification tasks.
-We describe several open questions for future work.
-%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-%Second, it would be interesting to extend our result to classification problems such as logistic regression.
-First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
-%but its singular values will follow a different distribution since the matrix is not symmetric.
- %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
-An interesting question is to study logistic regression in a multiple-sample setting.
-\fi
-
-% \section*{Acknowledgements}
-%Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
-Hongyang R.
-Zhang and Weijie J.
-Su's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
-%We gratefully acknowledge the support of DARPA under Nos.
-FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.
-U54EB020405 (Mobilize), NSF under Nos.
-CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No.
-N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys.
-The U.S.
-Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S.
-Government.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Material, if any, should   %%
-%% be provided in {supplement} environment  %%
-%% with title and short description.        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{supplement}
-\textbf{Supplement to ``Hard Parameter Sharing in High-dimensional Linear Regression"}.
-In \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
-%and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
-\end{supplement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                  The Bibliography                       %%
-%%                                                         %%
-%%  imsart-???.bst  will be used to                        %%
-%%  create a .BBL file for submission.                     %%
-%%                                                         %%
-%%  Note that the displayed Bibliography will not          %%
-%%  necessarily be rendered by Latex exactly as specified  %%
-%%  in the online Instructions for Authors.                %%
-%%                                                         %%
-%%  MR numbers will be added by VTeX.                      %%
-%%                                                         %%
-%%  Use \cite{...} to cite references in text.             %%
-%%                                                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% if your bibliography is in bibtex format, uncomment commands:
-\bibliographystyle{imsart-number}
-%\bibliographystyle{imsart-nameyear}
-
-%\bibliographystyle{abbrv}
-%\bibliographystyle{plain}
-\bibliography{rf,ref_mtl}
- % Style BST file (imsart-number.bst or imsart-nameyear.bst)
-%\bibliography{bibliography}       % Bibliography file (usually '*.bib')
-
-%% or include bibliography directly:
-%\begin{thebibliography}{4}
-%%%
-%\bibitem{r1}
-%\textsc{Billingsley, P.} (1999). \textit{Convergence of
-%Probability Measures}, 2nd ed.
-%Wiley, New York.
-%
-%\bibitem{r2}
-%\textsc{Bourbaki, N.}  (1966). \textit{General Topology}  \textbf{1}.
-%Addison--Wesley, Reading, MA.
-%
-%\bibitem{r3}
-%\textsc{Ethier, S. N.} and \textsc{Kurtz, T. G.} (1985).
-%\textit{Markov Processes: Characterization and Convergence}.
-%Wiley, New York.
-%
-%\bibitem{r4}
-%\textsc{Prokhorov, Yu.} (1956).
-%Convergence of random processes and limit theorems in probability
-%theory. \textit{Theory  Probab.  Appl.}
-%\textbf{1} 157--214.
-%\end{thebibliography}
-
-\end{document}

### 2021-06-12 revision_journal/exp.tex
revision wip
restructure exp

--- 2021-06-12 revision_journal/backup/03:06:2021/exp.tex
@@
-\section{Algorithmic implications}
+\section{Theoretical Implications}
 
@@
 
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
-	\label{alg_inc_train}
-	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-		\For{$i = 1,\dots, S$}
-		\For{$j = 1,\dots, T$}
-		\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
-		\EndFor
-		\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
-		\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-		\State \textbf{break}
-		\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
+\subsection{Covariance Alignment}
 
-One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
-\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
-where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
-$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
-The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
-In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
+\paragraph{Covariate shift}
+Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
+This highlights the need for correcting covariate shifts when the sample size ratio rises.
+To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
+The idea is to add an alignment module between the input and the shared module $B$.
+This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
+%We validate our insight on this procedure in the experiments.
+%We implement the covariance alignment procedure following \cite{WZR20}.
+
+We conduct multi-task training on all $15$ task pairs from the six datasets.
+In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
+To get a robust comparison, we average the improvements over the 15 task pairs.
+The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
+We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
+
+%One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
+%\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
+%where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
+%$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
+%The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
+%In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
 
@@
 
-\paragraph{Further Studies on Text Classification Tasks}%\label{sec_text}
+\subsection{Progressive Training}%\label{sec_text}
 
@@
 
+\begin{algorithm}[!t]
+	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+	\label{alg_inc_train}
+	\begin{algorithmic}[1]
+		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
+		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
+		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, W_2$ optimized for task $2$.
+		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\For{$i = 1,\dots, S$}
+		\For{$j = 1,\dots, T$}
+		\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+		\EndFor
+		\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+		\If{$a_i < a_{i-1}$ or $a_i > \tau$}
+		\State \textbf{break}
+		\EndIf
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
 %We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
@@
 We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
+
+\subsection{Rank Selection}
 %As a further validation, excluding TREC, we observe similar comparative results.
@@
 %\quad
-
-\paragraph{Covariate shift}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
 

### 2021-06-12 revision_journal/multitask.tex
restructure

@@
 
+\begin{figure*}[!t]
+	\centering
+	\includegraphics[width=0.3\textwidth,valign=t]{figures/mtl_model_arch.pdf}
+	\caption{A hard parameter sharing architecture}
+	\label{fig_intro_arch}
+\end{figure*}
 %\begin{enumerate}
@@
 
-\paragraph{How does hard parameter sharing scale with sample size $n$?}
+\paragraph{Examples.}
 Obviously, the concentration error decreases with $n$.
@@
 
-\paragraph{Sample efficiency}
+\paragraph{Simulations.}
 First, we validate the result of Example \ref{ex_same_cov}.
@@
 
-\paragraph{Sample size ratio}
-Second, we validate the result of Example \ref{ex_sample_ratio}.
-Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-%Again, our estimates are accurate compared to the empirical losses.
-We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$.
-The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
-On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
-Intuitively, this is because bias increases less for smaller $d^2$.
 %Our result from Corollary \ref{cor_MTL_loss} explains this trend.
 
-\paragraph{Covariate shift}
-Finally, we validate the result of Example \ref{ex_covshift}.
-Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
-The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
 %Covariate shift: We set $\kappa = 1$ and $d = 0$.

### 2021-06-12 revision_journal/results.tex
restructure

@@
 
+For the bias limit, we have the following proposition.
+
+\begin{proposition}\label{prop_main_RMT}
+%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
+Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
+			\begin{align}
+				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
+				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
+				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
+			\end{align}
+%			\begin{align}\label{lem_cov_derv_eq}
+%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
+%			\end{align}
+				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
+				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
+				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+		\be  \label{eq_a34extra}
+		\begin{split}
+				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
+				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
+%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+%				= b_0.
+			\end{split}
+			\ee
+			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
+\end{proposition}
+
+Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
+Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
+Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
+$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$
+and
+$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
+Using these estimates, it is easy to check that
+\begin{align}
+& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
+&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
+\label{bias_LLN}
+\end{align}
+Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
+However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
+
+\begin{remark}
+%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
+%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+%\begin{remark}
+The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
+In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
+We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
+However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
+We leave this problem to future study.
+
+We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
+%\end{remark}
+\end{remark}
+
+\paragraph{Examples.}
 \begin{example} %[Covariate shift]
@@
 
-For the bias limit, we have the following proposition.
-
-\begin{proposition}\label{prop_main_RMT}
-%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
-			\begin{align}
-				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
-				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
-			\end{align}
-%			\begin{align}\label{lem_cov_derv_eq}
-%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-%			\end{align}
-				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
-				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-		\be  \label{eq_a34extra}
-		\begin{split}
-				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
-				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{split}
-			\ee
-			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
-
-Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
-Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
-Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
-$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$
-and
-$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
-Using these estimates, it is easy to check that
-\begin{align}
-& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
-&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
-\label{bias_LLN}
-\end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
-However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
-
-\begin{remark}
-%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%\begin{remark}
-The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
-We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
-We leave this problem to future study.
-
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
-%\end{remark}
-\end{remark}
+\paragraph{Simulations.}
+Finally, we validate the result of Example \ref{ex_covshift}.
+Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
+Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
+We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
+The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
 
@@
 
+\paragraph{Examples.}
 To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
@@
 	\end{example}
+
+\paragraph{Simulations.}
+Second, we validate the result of Example \ref{ex_sample_ratio}.
+Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
+%Again, our estimates are accurate compared to the empirical losses.
+We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$.
+The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
+We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
+On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
+Intuitively, this is because bias increases less for smaller $d^2$.

### 2021-06-14 revision_journal/intro.tex
restructure
sec 2/3 wip

@@
 		\centering
-		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
+		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
+		\caption{Covariate shift}
 		\label{fig_intro_arch}
@@
 
-\subsection{Setup and definitions}
-Consider the transfer learning setting with two data sets.
-We denote their sample sizes by $n_1$ and $n_2$.
-For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
-$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
-We remark that all these assumptions are natural in high-dimensional statistics.
+\subsection{Summary of Results}
 
-We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let
-\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
-where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
-entries satisfying
-\begin{equation}\label{assm1}
-\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1,
-\end{equation}
-
-Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
-$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
-
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
-
-\subsection{Main results}
 Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
@@
 
-\medskip
-\noindent\textbf{Proof techniques.}
-There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
-The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
+%\medskip
+%\noindent\textbf{Proof techniques.}
+%There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
+%We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
+%The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
 We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
 Theorem \ref{thm_main_RMT}).
-We use recently developed techniques from random matrix theory to show a sharp convergence rate.
+%We use recently developed techniques from random matrix theory to show a sharp convergence rate.
 % to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
 %\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
-See Section \ref{sec_conclude} for more discussions of the technical challenge.
+%One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
+%We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
+%See Section \ref{sec_conclude} for more discussions of the technical challenge.
 
@@
 
-\subsection{Organizations}
+\paragraph{Organizations.}
 The rest of this paper is organized as follows.

### 2021-06-14 revision_journal/results.tex
sec 2/3 wip

@@
 
-\subsection{Assumptions}
+\subsection{Models and Assumptions}
+
+Consider the transfer learning setting with two data sets.
+We denote their sample sizes by $n_1$ and $n_2$.
+For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
+We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
+$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
+In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
+We remark that all these assumptions are natural in high-dimensional statistics.
+
+We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let
+\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
+where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
+entries satisfying
+\begin{equation}\label{assm1}
+\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1,
+\end{equation}
+
+Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
+$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
+
+Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+The critical questions are:
+(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
+(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
+
 Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
@@
 
-%\subsection{Transfer learning estimators}
+\subsection{Transfer Learning Estimators}
 
@@
 We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
-Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
+%Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
 
@@
 \paragraph{Examples.}
+To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
+\cite{dobriban2020wonder,dobriban2018high}).
+
+ %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
+Next, we illustrate how varying them impact the prediction loss.
+\begin{example}%[Sample sizes]
+\label{ex_sample_ratio}
+	%We first consider the impact of varying sample sizes.
+	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
+	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
+	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
+$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
+where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
+and $\wt \beta^{(i)}$ denotes the $i$-th
+%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
+task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+
 \begin{example} %[Covariate shift]
@@
 
-\section{Asymptotics under Imbalanced Sample Sizes} \label{sec_sizeratio}
+\section{Asymptotics under Sample Size Imbalance}\label{sec_sizeratio}
 
@@
 \paragraph{Examples.}
-To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-\begin{example}%[Sample sizes]
-\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
-	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
-and $\wt \beta^{(i)}$ denotes the $i$-th
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2$.
 First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.

### 2021-06-15 arxiv/intro.tex
Updates from Overleaf

--- 2020-10-15 arxiv/intro.tex
@@
 \begin{abstract}
-	\vspace{-0.1in}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties has not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
+	\vspace{-0.15in}
+	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that their generalization properties have not been well established in many cases.
+This paper studies a fundamental question to better understand this approach: How does hard parameter sharing work given multiple linear regression tasks?
+We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension become increasingly large in a fixed ratio.
 First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
@@
 We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
+Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing the variance but hurts eventually due to the increasing bias.
 This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-	\vspace{-0.15in}
+	\vspace{-0.1in}
 \end{abstract}
 
+\vspace{-0.15in}
+\section{Introduction}\label{sec_introduction}
 \vspace{-0.1in}
-\section{Introduction}\label{sec_introduction}
 
@@
 Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
+(i) It reduces model parameters since all tasks use the same feature space.
+(ii) It reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
 
-Hard parameter sharing works as an inductive transfer mechnism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
+Hard parameter sharing is intuitively appealing as an inductive transfer mechanism.
+\textbf{awkward sentence, maybe merge.}It reduces overfitting by acting as a regularizer \cite{R17}.
 For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
@@
 Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
+Previous results based on Rademacher complexity or VC dimensions have considered cases when all tasks' sample sizes are equal to \textbf{logarithmic?} logarithm factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
@@
 		\caption{A hard parameter sharing architecture}
-		\label{fig_intro_arch}
 	\end{subfigure}\hfill
@@
 		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
+		\includegraphics[width=0.6417\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
 		\caption{Varying sample size ratio}
@@
 	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially, but increases afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
+	\caption{\textbf{say task X1 X2, i was a bit confused with the right fig. is it observed? caption should have (right) somewhere.}An illustrative example of our result:
+	Consider the prediction loss of hard parameter sharing (left) for task two, given two linear regression tasks.
+	Increasing task one's sample size decreases task two's prediction loss initially, but increases afterwards.
+This phenomenon occurs due to different bias-variance tradeoffs as the sample size ratio increases.
 Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
@@
 	\label{fig_intro_sample_size}
-	\vspace{-0.07in}
+	\vspace{-0.1in}
 \end{figure*}
 
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
+This paper presents new techniques to study hard parameter sharing and establish a number of new results.
 We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmicly.
-This setting captures the fact that in many applications, a single task's sample size is usually insufficient for accurate learning.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
+We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly \textbf{instead of logarithmic} at a fixed ratio.
+This is motivated by many multi-task learning applications, where the amount of labeled data from each dataset is usually insufficient for learning a single task.
+For example, this is the case if a dataset's sample size is only a small constant factor of the feature dimension.
 The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.

### 2021-06-15 arxiv/setup.tex
Updates from Overleaf

--- 2020-10-15 arxiv/setup.tex
@@
 
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
+We assume that there are multiple datasets that all follow (potentially different) linear models.
+In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
+
+We study a hard parameter sharing architecture to learn jointly from multiple datasets.\textbf{
+I would reorder the next sentence with the 2 that follows it as Xi and the datasets come first}In this architecture, there is a shared feature representation layer $B\in\real^{p\times r}$ for all tasks and a separate output layer $A_i \in \real^r$ for every task $i$.
 Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
+For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size, $X^{(i)} \in \real^{n_i \times p}$ denote its feature covariates, and $Y^{(i)} \in \real^{n_i}$ denote all the labels.
 %The width of $B$, denoted by $r$, plays an important role in regularization.
@@
 %For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
+Let $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
+We study the following optimization \textbf{minimization? better} objective.
 %	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
@@
 %	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
+\vspace{-0.1in}
+\begin{align}\label{eq_mtl}
+			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2.
+\end{align}
 %\vspace{-0.1in}
-\begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-\end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
+Given a solution $(\hat{A}, \hat{B})$ of $f(A, B)$, let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+Some critical questions are:
 (i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
+(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator? \textbf{I guess this architecture you are talking about is the standard form for HPS right?}
 
 \textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \citet{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning, but increases bias.
+Our first result (Theorem \ref{thm_many_tasks}) applies to the multi-label prediction setting where all datasets have the same features, and we want to make multiple predictions (see e.g.
+\cite{hsu2009multi}).
+We analyze the global minimizer of $f(A, B)$, and provide a sharp generalization bound on its (out-of-sample) prediction loss for any task.
+This case is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
+We show that the prediction loss of hard parameter sharing\textbf{ HPS maybe be consistent with it?} admits a clean bias-variance decomposition.\textbf{
+for next sentence is this true regardless of sample sizes and the ratio? it sounds too strong. is it?}
+Our results imply that hard parameter sharing helps by reducing the variance compared to single-task learning, but hurts by increasing the bias.
+Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and population covariance matrices.
+We analyze the local minimizers of $f(A, B)$ and provide a sharp generalization bound on both tasks' prediction loss.
+Despite its simplicity, we show several interesting phenomena by varying sample sizes and covariate shifts in this setting.
+See Figure \ref{fig_intro_sample_size} for an illustration.
 
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we no longer have a characterization of $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
+Consequently, using our precise loss estimates, we observe several qualitative properties of hard parameter sharing for varying datasets' properties.
 %\begin{enumerate}
@@
 \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \citet{ZSSGM18} has observed empirically.
+	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to STL\textbf{what is STL?}, a phenomenon that \citet{ZSSGM18} has observed empirically.
 	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance, and is generally high when the latter is large.
@@
 These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as the sample sizes of all tasks increase, thus do not apply for different sample size ratios.
 
-\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
+\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with the covariate shift between different datasets.
 For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
 Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
 %\end{enumerate}
@@
 %Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
-
-\textbf{Proof techniques.}
+\textbf{in the 3 examples above, all three phenomena are new? or how surprising/challenging are they? maybe just a brief line commenting will put it into context}
+\textbf{maybe say Techniques?}
 There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
+We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and its population version.
 The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-Using recently developed techniques from random matrix theory, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
+Using recently developed techniques from random matrix theory \cite{Anisotropic}, we show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
 Theorem \ref{thm_main_RMT}).
@@
 %\HZ{add several sentences on the technical insight} 
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided important initial insights and it is an interesting question to tighten our result.
+One limitation of our analysis is that for two tasks with different sample sizes, there is an extra error term in the prediction loss of hard parameter sharing (cf.
+equation \eqref{cor_MTL_error}), which can be large for very small $n_1$.
+This requires studying the singular value spectrum of certain non-symmetric random matrices, which is an intriguing open question (see Section \ref{sec_conclude} for more discussion).
+% plus an identity matrix,  due to lack of freeness
+%\HZ{add why this is challenging}
+\textbf{i think this experimental advice that stems from your work is nice, and you can motivate it further up in the text?
+maybe right after the 3 examples?
+even by looking at Fig1 it suggests that you should increase data up to some point then stop.
+You experimentally verify this.}
+Finally, we discuss the practical implications of work.
+Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
+For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
+We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
 
@@
 
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \citet{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+There is a large body of both classical and recent works on multi-task learning.
+We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,R17,ZY17,V20}.
+The early work of \citet{B00,BS03,M06} have sought for a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
 An influential paper by \citet{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
@@
 In Section \ref{sec_diff}, we present our technical results that describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in simulations and real world classification tasks.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
+In Sections \ref{sec_simulation} and \ref{sec_text}, we validate our theory in both simulations and a real world classification task.
+In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.
 

### 2021-06-15 src/.venv/lib/python3.6/__future__.py
set up overleaf

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/__future__.py

### 2021-06-15 src/.venv/lib/python3.6/_bootlocale.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/_bootlocale.py

### 2021-06-15 src/.venv/lib/python3.6/_collections_abc.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/_collections_abc.py

### 2021-06-15 src/.venv/lib/python3.6/_dummy_thread.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/_dummy_thread.py

### 2021-06-15 src/.venv/lib/python3.6/_weakrefset.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/_weakrefset.py

### 2021-06-15 src/.venv/lib/python3.6/abc.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/abc.py

### 2021-06-15 src/.venv/lib/python3.6/base64.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/base64.py

### 2021-06-15 src/.venv/lib/python3.6/bisect.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/bisect.py

### 2021-06-15 src/.venv/lib/python3.6/codecs.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/codecs.py

### 2021-06-15 src/.venv/lib/python3.6/copy.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/copy.py

### 2021-06-15 src/.venv/lib/python3.6/copyreg.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/copyreg.py

### 2021-06-15 src/.venv/lib/python3.6/enum.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/enum.py

### 2021-06-15 src/.venv/lib/python3.6/fnmatch.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/fnmatch.py

### 2021-06-15 src/.venv/lib/python3.6/functools.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/functools.py

### 2021-06-15 src/.venv/lib/python3.6/genericpath.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/genericpath.py

### 2021-06-15 src/.venv/lib/python3.6/hashlib.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/hashlib.py

### 2021-06-15 src/.venv/lib/python3.6/heapq.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/heapq.py

### 2021-06-15 src/.venv/lib/python3.6/hmac.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/hmac.py

### 2021-06-15 src/.venv/lib/python3.6/imp.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/imp.py

### 2021-06-15 src/.venv/lib/python3.6/io.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/io.py

### 2021-06-15 src/.venv/lib/python3.6/keyword.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/keyword.py

### 2021-06-15 src/.venv/lib/python3.6/linecache.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/linecache.py

### 2021-06-15 src/.venv/lib/python3.6/locale.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/locale.py

### 2021-06-15 src/.venv/lib/python3.6/ntpath.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/ntpath.py

### 2021-06-15 src/.venv/lib/python3.6/operator.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/operator.py

### 2021-06-15 src/.venv/lib/python3.6/os.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/os.py

### 2021-06-15 src/.venv/lib/python3.6/posixpath.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/posixpath.py

### 2021-06-15 src/.venv/lib/python3.6/random.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/random.py

### 2021-06-15 src/.venv/lib/python3.6/re.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/re.py

### 2021-06-15 src/.venv/lib/python3.6/reprlib.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/reprlib.py

### 2021-06-15 src/.venv/lib/python3.6/rlcompleter.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/rlcompleter.py

### 2021-06-15 src/.venv/lib/python3.6/shutil.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/shutil.py

### 2021-06-15 src/.venv/lib/python3.6/sre_compile.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/sre_compile.py

### 2021-06-15 src/.venv/lib/python3.6/sre_constants.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/sre_constants.py

### 2021-06-15 src/.venv/lib/python3.6/sre_parse.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/sre_parse.py

### 2021-06-15 src/.venv/lib/python3.6/stat.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/stat.py

### 2021-06-15 src/.venv/lib/python3.6/struct.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/struct.py

### 2021-06-15 src/.venv/lib/python3.6/tarfile.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/tarfile.py

### 2021-06-15 src/.venv/lib/python3.6/tempfile.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/tempfile.py

### 2021-06-15 src/.venv/lib/python3.6/token.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/token.py

### 2021-06-15 src/.venv/lib/python3.6/tokenize.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/tokenize.py

### 2021-06-15 src/.venv/lib/python3.6/types.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/types.py

### 2021-06-15 src/.venv/lib/python3.6/warnings.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/warnings.py

### 2021-06-15 src/.venv/lib/python3.6/weakref.py

@@ -1,1 +1,0 @@
-/Users/hongyang/anaconda3/lib/python3.6/weakref.py

### 2021-06-21 revision_journal/intro.tex
reorg wip

@@
 
-\subsection{Summary of Results}
+%\subsection{Summary of Results}
 
@@
 
-\subsection{Related Work}
-
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-\HZ{can you please add a discussion of the related work from RMT?}
-
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\paragraph{Organizations.}
+%\paragraph{Organizations.}
 The rest of this paper is organized as follows.

### 2021-06-21 revision_journal/results.tex
reorg wip

--- 2021-06-12 revision_journal/results.tex
@@
-\section{Preliminaries and Notations}\label{sec_HPS}
-In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
+\section{Main results}
 
-\subsection{Assumptions}
-Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
-\be \label{conditionA2}
-\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
-\ee
-for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee
-%for a small constant $\tau>0$.
-
-We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\be\label{eq_highmoments}
-\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
-\ee
-Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
-%Moreover, we assume that
-%\be\label{eq_SNR}
-%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
-%\ee
-%for a small constant $\tau >0$.
-The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.
-
-In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that
-\be\label{assm2}
-1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
-\ee
-for a small constant $\tau >0$.
-If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper.
-The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
-are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.
-
-We summarize our basic assumptions here for future reference.
-\begin{assumption}\label{assm_big1}
-Let $\tau$ be a small constant.
-\begin{enumerate}
-\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}.
-%and (\ref{assm2}).
-We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-
-\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-
-\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
-
-\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.
-
-\end{enumerate}
-\end{assumption}
-
-%\subsection{Transfer learning estimators}
-
-%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-
-In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error).
-Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
-$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$
-Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
-\be\label{HPS_loss}
-L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
- \ee
-We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.
-
-%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
-
-Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-\end{align}
-Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-where
-\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-is called the bias term, which depends on the model bias between task 1 and task 2, and
-\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-%predication loss for the HPS and OLS estimators.
-
-\begin{lemma}\label{lem_HPS_loss}
- Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
-\end{align}
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-& + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-\end{align}
-%Moreover, there exists a constant $C_0>0$ such that with high probability,
-%\be\label{loss_large}
-%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-%\ee
-%with high probability for any small constant $\e>0$.
-\end{lemma}
-
-Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$.
-In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
-(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}.
-To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
-Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.
-
-%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
-
-For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.
-
-\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
-		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
-		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
-		with high probability for any small constant $\e>0$.
-\end{lemma}
- %The above result has a long history in random matrix theory.
-If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of
-the inverse Wishart distribution \cite{anderson1958introduction}.
-For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
-Lemma 3.11 of \cite{bai2009spectral}).
-Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate.
-With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
- \end{align}
-
-On the other hand, much less is known about the predication loss of the HPS estimator.
-In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-%\FY{What is known so far about this topic?}
-In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in two different settings: (i) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
-We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
-In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
-On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
-%Here case (ii) is actually more general than (i)
-%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.
-In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
-We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
-Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
-
-%{\cor discuss about the bias-variance trade-off}
-%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
-
-\section{Asymptotics under Covariate Shift}\label{sec_diff}
+\subsection{Covariate shift}\label{sec_diff}
 
@@
 
-\section{Asymptotics under Imbalanced Sample Sizes} \label{sec_sizeratio}
+\subsection{Task size imbalance}\label{sec_sizeratio}
 

### 2021-06-21 revision_journal/setup.tex
reorg wip

--- 2021-06-12 revision_journal/backup/Jan 31 2021/manuscript.tex
@@
-\documentclass[aos,preprint]{imsart}
-\usepackage{xr}
-	\externaldocument{./suppl}
-
-%% Packages
-\def\shownotes{0}
-%\usepackage{natbib}
-%\setcitestyle{authoryear,open={(},close={)}}
-%\renewcommand{\cite}{\citep}
-\usepackage[export]{adjustbox}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{fullpage}
-\usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
-\usepackage{macro_fan}
-\usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage{caption,subcaption}
-%\usepackage{breqn}
-
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Uncomment next line to change            %%
-%% the type of equation numbering           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\numberwithin{equation}{section}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Axiom, Claim, Corollary, Hypothezis, %%
-%% Lemma, Theorem, Proposition              %%
-%% use \theoremstyle{plain}                 %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\theoremstyle{plain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Assumption, Definition, Example,     %%
-%% Notation, Property, Remark, Fact         %%
-%% use \theoremstyle{remark}                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please put your definitions here:        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-%\title{High-dimensional Asymptotics of Linear Regression with Different Covariates and Sample Sizes}
-%\title{A sample article title with some additional note\thanksref{t1}}
-
-\title{High-dimensional Asymptotics of Transfer Learning for Linear Regression} 
-%with Different Covariates and Sample Sizes}
-
-\runtitle{Linear Regression with Different Covariates and Sample Sizes}
-%\thankstext{T1}{A sample additional note to the title.}
-
-\begin{aug}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Only one address is permitted per author. %%
-%%Only division, organization and e-mail is %%
-%%included in the address.                  %%
-%%Additional information can be included in %%
-%%the Acknowledgments section if necessary. %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu}}
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}}
-\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3,mark]{senwu@stanford.edu}} 
-\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4,mark]{suw@wharton.upenn.edu} }
-\and
-\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5,mark]{chrismre@cs.stanford.edu}} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Addresses                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address[A]{Department of Statistics,
-University of Pennsylvania,
-\printead{e1,e4}}
-\address[B]{Khoury College of Computer Sciences, Northeastern University,
-\printead{e2}}
-\address[C]{Department of Computer Science, Stanford University,
-\printead{e3,e5}}
-
-\end{aug}
-
-\begin{abstract}
-	\FY{rewrite the abstract} Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
-First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
-Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
-We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
-This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-\end{abstract}
-
-\begin{keyword}[class=MSC2020]
-\kwd[Primary ]{62J05}
-\kwd{60B20}
-\kwd[; secondary ]{62E20, 62H10}
-\end{keyword}
-
-\begin{keyword}
-\kwd{Hard parameter sharing, high-dimensional linear regression, random matrix theory, sample covariance matrices}
-\end{keyword}
-
-\end{frontmatter}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please use \tableofcontents for articles %%
-%% with 50 pages and more                   %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\tableofcontents
-
-\section{Introduction}\label{sec_introduction}
-
-\FY{rewrite the introduction}  Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
-Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
-
-Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
-		\label{fig_intro_arch}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure*}
-
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
-
-\subsection{Setup and Main Results}
-
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
-Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
-\begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-\end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
-
-\medskip
-\noindent\textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \cite{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
-
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-\begin{itemize}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
-
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
-
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
-For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
-\end{itemize}
-
-%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-%\squishlist
-%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-%	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-%	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-%\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-%Our study also leads to several algorithmic consequences with practical interest.
-%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-
-%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-%Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
-
-\medskip
-\noindent\textbf{Proof techniques.}
-There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
-The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
-Theorem \ref{thm_main_RMT}).
-We use recently developed techniques from random matrix theory to show a sharp convergence rate.
-% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
-%\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
-See Section \ref{sec_conclude} for more discussions of the technical challenge.
-
-%This part introduces a positive variance reduction effect from adding the source labels.
-%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
-%(i) the negative effect from model shift bias.
-%(ii) the positive effect from variance reduction;
-
-\subsection{Related Work}
-
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\smallskip
-\noindent\textbf{Organizations.}
-The rest of this paper is organized as follows.
-In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation}, we validate our results in simulations.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{sec_text} describes our study on text classification tasks.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
-
-\medskip
-\noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$.
-Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$.
-In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-
-\section{Transfer learning for high-dimensional linear regression}\label{sec_HPS}
+\section{Preliminaries and related work}\label{sec_HPS}
 In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
 
-\subsection{The model}
+\subsection{Large dimensional random matrices}
+
 Consider the transfer learning setting with two data sets.
@@
 \end{equation}
+
+Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
+$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
+
+Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+The critical questions are:
+(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
+(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
+
 Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
@@
 
-\subsection{Transfer learning estimators}
+\subsection{Hard parameter sharing estimators}
 
-One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
-\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
-where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by  
-$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
-The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}. 
-In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
-
-Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
-$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
 %\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-In this paper, we consider a natural extension of the estimator $\hat \beta^{\rm{TL}} $, that is, the \emph{hard parameter sharing} (HPS) estimator, which has been a standard type of estimator in multi-task learning \FY{citations}.
-More precisely, we study the following HPS architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
-Then we study the following minimization problem:
-\begin{align}\label{eq_tsl}
-			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
-\end{align}
-where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
-\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
-Note that $\hat \beta^{\rm{TL}}$ is a special case of $\hat{\beta}_i^{\MTL}$ by setting $A_1=A_2=1$.
-
-For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that  
-	\begin{align}
-		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
-where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
-Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers.
-Could you replace $A$ with another symbol (say $x$)?}
- \begin{align}
-		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
-			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
-		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
-	\end{align}
-Let $\hat a$ be the minimizer of $g(a)$.
-Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.
-Then the HPS estimator \eqref{def_HPS} for the target task 2 is
-\be\label{HPS_est}
-\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
-\ee
 
@@
 
-\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
+%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
 
-\subsection{Varying sample sizes} \label{sec_sizeratio}
+\subsection{Related work}
 
- In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
+There is a large body of classical and recent works on multi-task learning.
+We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
+The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
+One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
+Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
 
-\begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
-\ee
-and 
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions  
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}. 
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)} 
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
+Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
+In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
+\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
+%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
+These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
+To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
+\HZ{can you please add a discussion of the related work from RMT?}
 
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider 
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter 
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where 
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
+The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
+For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
+One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
+However, their results only apply to sample size regimes at least logarithmic factors of dimension.
+%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
+%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
 
-We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the rotational invariance of multivariate Gaussian distributions,
-%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence 
-the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
+%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
+%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
+%For such models, their output dimension plays an important role of regularization \cite{KD12}.
+%Below, we describe several lines of work that are most related to this work.
 
-We believe that the above argument can be extended to the case without the Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
-Hence we do not pursue this direction in this paper.
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
+%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
+%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
+%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+%Our work is closely related to Wu et al. \cite{WZR20}.
+%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
+%\todo{spell out the challenge more explicitly}
 
-%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
-
-To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-\begin{example}%[Sample sizes]
-\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$. 
-	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-and $\wt \beta^{(i)}$ denotes the $i$-th 
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-task-specific component whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
-	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
-
-	\begin{proposition}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Suppose Assumption \ref{assm_big1} and the above setting of random effect model hold. %in Example \ref{ex_same_cov} hold. 
-Suppose that for a constant $c_0>0$,
-	\be\label{para_rel}
-	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
-	\ee
- Then we have that for any small constant $c>0$ and large constant $ C>0$,
-	%Let $c$ be a sufficiently small fixed constant.
-	%In the setting of Corollary \ref{cor_MTL_loss}, 
-%There exists a constant $C>0$ such that
-	\be\label{hatw_add1}
-	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
-	\ee
-\end{proposition}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-%and $\wt \beta^{(i)}$ denotes the $i$-th 
-%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-
-We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
-$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
-with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations. 
-Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
-This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
-Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
-
-Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
-$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
-First, we have positive (resp.
-negative) transfer if and only if $h(\rho)>0$ (resp.
-$h(\rho)<0$).
-Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
-\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
-
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
-
-\begin{itemize}
-\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
-
-\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
-Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
-\end{itemize}
-\end{enumerate}
-Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial 
-\be\label{poly2}
- \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
-
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
-\end{enumerate}
-
-%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance. 
-%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
-\iffalse
-Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
-
-Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
-	\begin{align*}
-		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
-		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
-		= \frac{p}{n_1 + n_2 - p},
-	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit.
-	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
-
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
-This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
-by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-
-{\cor 
-For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
-	\begin{align}
-		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
-		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
-			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
-For the bias term,
-}
-
-Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
-For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
-We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
-It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
-By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
-\fi
-	\end{example}
-
-	\FY{add simulations to check our results and the above dichotomies}
-
-\subsection{Covariate shift}\label{sec_diff}
-
-%The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$. 
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
-
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$) 
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-%for some small constant $0<\tau<1$. 
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
-
-\begin{theorem}\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}: 
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
-			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
-			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that 
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
-Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
-%also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
-and plug them into \eqref{lem_cov_shift_eq}.
-The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
-
-\begin{example} %[Covariate shift]
-\label{ex_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds.
-In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
-Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
-$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
-where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
-We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
-\end{align*}
-%belong to the following bounded set.
-%Let $\lambda_i$ be the $i$-th singular value of $M$.
-%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-%\vspace{-0.025in}
-%{\small}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-%\begin{proposition}[Covariate shift]\label{prop_covariate}
-%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-%	We have that
-%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
-%\end{proposition}
-%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
-Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix. 
-%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-%Let 
-%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
-%We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
-%\be \nonumber
-%\begin{split}
-%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
-%\end{split}
-%\ee
-%with high probability for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-%
-%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-%\begin{align}\label{gvar_extra}
-%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-%\end{align}
-In fact, from equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
- a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
-\ee
-Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that 
-%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-%\begin{align}\label{approximateteM}
-%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-%\end{align}
-%where
-$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}. 
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that 
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
-
-%Hence we get that 
-%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-%
-%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-%\begin{align}\label{gvar_extra2}
-%\begin{split}
-%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-%\end{split}
-%\end{align}
-%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-%\end{proof}
-
-\iffalse
-For large enough $p$,
-%in the left hand side of equation \eqref{lem_cov_shift_eq}:
-\begin{align*}
-	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
-\end{align*}
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
-\fi
-
-%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}. 
-%Our first observation is that:
-However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
-We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$.
-In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
-When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
-%while as As $\lambda$ increases, the severity of covariate shift increases.
-We claim the following dichotomy.
-\begin{enumerate}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-\end{enumerate}
-We explain why the above dichotomy happens. We can write the variance limit as
-$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
-When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
-$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
-where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
-\begin{align*}
-\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
-\end{align*}
-%in this example is equal to
-%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
-%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%where $g(\lambda, a_1) \ge 0$.
-%and can be derived from algebraic calculations (details omitted).
-We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
-In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
-\begin{align*}
- \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
-\end{align*}
-%\begin{align*}
-% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-%\end{align*}
-This implies $n_1>n_2$.
-The other direction follows from a similar argument.
-% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
-\end{example}
-
-\iffalse
-%FY: Below was the word explanation. I still think the above simple proof is clearer.
-In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
-The other case when $n_1 < n_2$ is similar.
-A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
-If $n_1< n_2$, then $f(\lambda)< f(1)$.
-\fi
-
-For the bias limit, we have the following proposition.
-
-\begin{proposition}\label{prop_main_RMT}
-%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
-			\begin{align}
-				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
-				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
-			\end{align}
-%			\begin{align}\label{lem_cov_derv_eq}
-%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-%			\end{align}
-				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
-				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-		\be  \label{eq_a34extra}
-		\begin{split}
-				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
-				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{split}
-			\ee  
-			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
-
-Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
-Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
-Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
-$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$ 
-and
-$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
-Using these estimates, it is easy to check that  
-\begin{align}
-& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
-&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
-\label{bias_LLN}
-\end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
-However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
-
-\begin{remark}
-%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%\begin{remark}
-The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
-We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
-We leave this problem to future study.
-
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
-%\end{remark}
-\end{remark}
-
-\FY{add simulations to check our results}
-
-\section{Insights for transfer learning}
-
-\FY{discuss applications and insights of our results}
-
-\subsection{Comparison between the averaging and HPS estimators}
-
-\subsection{Algorithmic implications}
-\FY{the progressive training; covariance alignment; and others?}
-
-\section{Extension to multi-task learning}\label{sec_same}
-
-%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
-%We provide a sharp generalization error bound of hard parameter sharing estimators.
-
-Hard parameter sharing is a commonly used architecture in multi-task learning.
-However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning.
-In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates.
-We make this extension for the following reasons.
-First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly.
-Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below.
-Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}
-
-\vspace{5pt}
-\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
-The label vector of the $i$-th task follows a linear model
-$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
-We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
-
-%\begin{enumerate}
-%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-%\end{enumerate}
-
-	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
-	\begin{align}
-		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
-%Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-
-	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
-Hence we only consider the case with $r<t$.
-\FY{Correct it if the reason is wrong.}
-
-	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
-	\begin{align}
-		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
-		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
-	\end{align}
-	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
-	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
-	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
-	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
-	\end{align}
-%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
-%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
-%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
-
-Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
-\begin{align}\label{eq_A_star}
-	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
-\end{align}
-where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
- To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
-Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
- %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
-Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
-Then we have the following result.
-
-% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
-%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
-%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
-%Our result is stated as follows.
-
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
-	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
-Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability, 
-\be\label{minimizer_beta}
-\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
-\ee
-where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
-	\begin{align}
-		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
-		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
-\label{Li_multi1}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
-%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
-%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
-Finally, we have a better bound for the averaged prediction loss:  with high probability,
-\begin{align}
-&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
- &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
-\end{align}
-
-\end{theorem}
-
-Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
-Moreover, the factor $(\lambda_r - \lambda_{r+1})^{-1}$ is natural, because the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not stable when $\lambda_r $ and $\lambda_{r+1} $ are close to each other.
-The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
-The estimate \eqref{Li_multi1}
- gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
-Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases for the multi-task HPS estimator.
-On the other hand, the bias term always increases (because the bias in single-task linear regression is zero).
-Hence as in the transfer learning setting, whether the HPS estimator is better than the OLS estimator depends on an intricate  {bias-variance tradeoff}.
-%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.}
-We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
-Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
-For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
-
-The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
-Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
-For the reader's convenience, we give the precise statement in Corollary \ref{thm_two_tasks}.
-%Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.  
-%In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$. 
-We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix  
-$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
-% is the matrix formed by the linear model parameters of the two tasks. 
-Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined.
-%Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
-In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-\begin{corollary}\label{thm_two_tasks}
-Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2\equiv n$. Let $c>0$ be an arbitrary (small) constant. Then we have that with high probability, 
-\be\label{minimizer_beta1}
-\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
-\ee
-where $u_{\hat a}$ is the unit vector defined as
-$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-%for task 2,  % over the randomness of the input, 
-Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
-	\begin{align}
-		& \bigabs{L_2(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) \cdot B^{\star}A^{\star}  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
-		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	 where $A^\star(2)$ denotes the second entry of $A^\star$.
-	 \end{corollary}
-
-%The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-%It is not hard to extend the above result to the cases with more than two tasks.
-We make this extension for the following reasons.
-First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
-Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-
-%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-%\medskip
-%
-%\noindent\textbf{Comparison to single-task learning (STL).}
-%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
-%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
-%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
-%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.
-
-\iffalse
-\paragraph{How does hard parameter sharing scale with sample size $n$?}
-Obviously, the concentration error decreases with $n$.
-First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
-It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
-
-\begin{assumption}\label{assume_rm}
-	Let $\tau > 0$ be a small enough constant.
-%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
-entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	In the high-dimensional setting,
-%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-%			\begin{align}\label{assmAhigh}
-%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
-%			\end{align}
-  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
-%	\end{enumerate}
-\end{assumption}
-Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
-
-\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	With high probability over the randomness of $X$, we have that
-		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
-\end{fact}
-\noindent\textit{Remark.} The above result has a long history in random matrix theory.
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
-Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
-		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
-		\fi
-
-%Finally, for the random noise component, we assume that all of its moments exist.
-%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
-%\begin{align}\label{assmAhigh2}
-%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
-%\end{align}
-%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
-%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
-
-%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
-To illustrate the {bias-variance tradeoff quantitively, we consider an extension of the random-effect model in Example \ref{ex_sample_ratio} to the multi-task setting.
-%which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
-\begin{example}%[Random-effect model]
-\label{ex_same_cov}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-Suppose that {$\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$} for $ i=1,2,\cdots, t,$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-and $\wt \beta^{(i)}$ denotes the $i$-th 
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. 
-%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
-%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
-In this random-effect model, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
-%Based on the definition of the random-effect model, 
-the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
-%\begin{align*}
-%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
-%\end{align*}
-\begin{align}\label{betaSbeta}
-	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
-\end{align}
- with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}. 
-%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
-With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
-$$\lambda_1=\left[1+\OO(p^{-1/2+c})\right]\cdot\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
-and
-$$ \lambda_i=\left[1+\OO(p^{-1/2+c})\right]\cdot \frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
-Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
-$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
-with high probability. 
-%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
-%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
-%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
-%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
-Then using \eqref{Li_multi2}, we obtain that
-\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p.
-}\]
-%We describe a proof sketch.
-%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
-%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
-%Second, using Fact \ref{fact_tr}, one can see that the average variance is
-%\begin{align*}
-%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
-%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
-%\end{align*}
-%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
-%Combined together, we have derived the average prediction loss in the random-effect model.
-%If the error is sufficiently small, then 
-Comparing the above equation with \eqref{L_STL_simple01} (and ignoring the small error), we have the following observations. 
-%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
-%Comparing HPS to STL, we have the following qualitative properties.
-%	Suppose $n$ is sufficiently large so that the error is negligible.
-%\begin{enumerate}
-\begin{enumerate}
-	\item {\bf Positive vs.
-negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
-
-	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
-Hence increasing the width $r$ of the shared feature representation layer does not help.
-	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-
-	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
-Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
-More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
-	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
-}\]
-	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
-	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$ 
-	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
-
-	%samples that is less than $n$ samples to get comparable loss to STL.
-	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
-	\end{enumerate}
-
-\end{example}
-
-\FY{add simulations to check our results; discuss possible applications}
-
-\section{Experiments}
-
-\subsection{Simulation Studies}\label{sec_simulation}
-
-\FY{move the simulations results to previous sections}
-We demonstrate the accuracy of our results in simulations.
-While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
-		\caption{Example \ref{ex_same_cov}}
-		\label{fig_same_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
-		\caption{Example \ref{ex_sample_ratio}}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
-		\caption{Example \ref{ex_covshift}}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
-	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
-%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
-	\label{fig_model_shift_phasetrans}
-\end{figure*}
-
-\paragraph{Sample efficiency}
-First, we validate the result of Example \ref{ex_same_cov}.
-Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
-In all the parameter settings, our results estimate the empirical losses accurately.
-We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
-Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
-%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
-Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level.
-%\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
-For example, at the cross point, this ratio is 1.
-}
-
-\paragraph{Sample size ratio}
-Second, we validate the result of Example \ref{ex_sample_ratio}.
-Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-%Again, our estimates are accurate compared to the empirical losses.
-We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
-The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
-On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
-Intuitively, this is because bias increases less for smaller $d^2$.
-%Our result from Corollary \ref{cor_MTL_loss} explains this trend.
-
-\paragraph{Covariate shift}
-Finally, we validate the result of Example \ref{ex_covshift}.
-Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
-The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
-%Covariate shift: We set $\kappa = 1$ and $d = 0$.
-%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-
-%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-%\begin{table}
-%	\begin{center}
-%		\begin{tabular}{c c c c c}
-%			\toprule
-%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
-%			\midrule
-%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-			% {\bf CNN}  & 76\% & - & 32\% & -\\
-%			\bottomrule
-%		\end{tabular}
-%	\end{center}
-%	\caption{Taskonomy experiment.}
-%	\label{tab:taskonomy}
-%\end{table}
-%\begin{figure}[!t]
-%	\centering
-%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
-%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
-%	\label{fig_same_cov}
-%\end{figure}
-
-\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
-
-Our results and simulations are all in the high-dimensional linear regression setting.
-How well do they extend to other scenarios?
-In this section, we conduct further studies on six text classification datasets.
-Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
-%The question is to predict positive or negative sentiment expressed in the text.
-Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
-For LSTM, we add a shared feature representation layer on top of word embeddings.}
-
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-%There are 14 diseases (tasks) for every image that we would like to predict.
-%We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-%We evaluate three model choices.
-%\textit{Predicting transfer effect via STL results.}
-%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-%A common challenge in the study of MTL is that the results can be hard to understand.
-%It is difficult to predict when MTL performs well without running extensive trials.
-%Our insight is that we can use STL results to help understand MTL results.
-%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
-
-\paragraph{Sample size ratio.}
-First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
-On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.
-
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
-Concretely, here is one implementation of this idea.
-%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
-\begin{itemize}
-	\item We divide the training data into $S$ batches.
-	We divide the training procedure into $S$ stages. During every stage, we progressively add one more data batch.
-	\item During every stage, we train for $T$ epochs using only the $S$ batches.
-If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
-%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\end{itemize}
-If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
-%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
-The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
-
-%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-%\squishlist
-%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-%TREC is less similar to MR because the task is about question types.
-%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
-We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
-We include all of task two's data and progressively add task one's data using the procedure described above.
-Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
-%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we conduct multi-task training on all six datasets jointly.
-We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
-We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
-%As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-%	\begin{subfigure}[b]{0.33\textwidth}
-%		\centering
-%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-%		\caption{Task similarity}
-%		\label{fig_ab_sim}
-%	\end{subfigure}%
-%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c)
-%	Note: (S) denotes the source task and (T) denotes the target task.}
-
-%\begin{minipage}[t]{.58\textwidth}
-%	\vspace{-0.1in}
-%	\centering
-%  \begin{tabular}{c c c c c}
-%	\toprule
-%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%		& Precision &  Recall & Precision &  Recall \\
-%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
-		% 0.3 & 1.000 & 0.004 &     - &     - \\
-%	\bottomrule
-%	\end{tabular}
-%	\vspace{0.1in}
-%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-%	\label{tab:mtl_better_than_stl}
-%\end{minipage}%
-%\quad
-
-\paragraph{Covariate shift}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
-
-%\begin{figure}[!t]
-%	\centering
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-%		\caption{Averaged over all 16 task pairs}
-%		\label{fig_ab_cov}
-%	\end{subfigure}\hfill
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{An example task pair}
-%		\label{fig_cov_a}
-%	\end{subfigure}
-%	\caption{ (TREC and CR)}
-%\end{figure}
-
-%\textbf{Further results of the covariance alignment procedure.}
-%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
-%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
-%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
-%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
-%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
-%We leave this question for future work.
-%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
-
-%\begin{figure}[!h]
-%	\centering
-%	\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{Task pair TREC and CR}
-%		\label{fig_cov_a}
-%	\end{subfigure}\hfill
-%		\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-%		\caption{Task pair MR and SST}
-%			\label{fig_cov_b}
-%	\end{subfigure}
-%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
-%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
-%	\label{fig_covariate_app}
-%\end{figure}
-
-\begin{figure}%[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
-		\caption{HPS vs. STL}
-		\label{fig_ab_data}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
-		\caption{HPS vs. covariance alignment}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \cite{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
-	\label{fig_text}
-%	\begin{minipage}[t]{0.4\textwidth}
-%		\centering
-%		\vspace{0pt}
-%		\begin{tabular}{c c c}
-%		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-%		& all tasks & w/o TREC \\
-%		\midrule
-%		{\bf MLP}  & 31\% & 29\% \\
-%		{\bf LSTM} & 35\% & 34\% \\
-%		{\bf CNN}  & 30\% & 28\% \\
-%		\bottomrule
-%		\end{tabular}
-%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
-%		\label{tab:taskonomy}
-%	\end{minipage}
-\end{figure}
-
-%\begin{algorithm}[!t]
-%	\caption{A progressive training schedule given two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
-%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, A_2$ optimized for task $2$.
-%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}
-
-\iffalse
-\section{Conclusions and Discussions}\label{sec_conclude}
-
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on text classification tasks.
-We describe several open questions for future work.
-%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-%Second, it would be interesting to extend our result to classification problems such as logistic regression.
-First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
-%but its singular values will follow a different distribution since the matrix is not symmetric.
- %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
-An interesting question is to study logistic regression in a multiple-sample setting.
-\fi
-
-% \section*{Acknowledgements}
-%Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
-Hongyang R.
-Zhang and Weijie J.
-Su's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
-%We gratefully acknowledge the support of DARPA under Nos.
-FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.
-U54EB020405 (Mobilize), NSF under Nos.
-CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No.
-N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys.
-The U.S.
-Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S.
-Government.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Material, if any, should   %%
-%% be provided in {supplement} environment  %%
-%% with title and short description.        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{supplement}
-\textbf{Supplement to ``Hard Parameter Sharing in High-dimensional Linear Regression"}.
-In \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
-%and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
-\end{supplement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                  The Bibliography                       %%
-%%                                                         %%
-%%  imsart-???.bst  will be used to                        %%
-%%  create a .BBL file for submission.                     %%
-%%                                                         %%
-%%  Note that the displayed Bibliography will not          %%
-%%  necessarily be rendered by Latex exactly as specified  %%
-%%  in the online Instructions for Authors.                %%
-%%                                                         %%
-%%  MR numbers will be added by VTeX.                      %%
-%%                                                         %%
-%%  Use \cite{...} to cite references in text.             %%
-%%                                                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% if your bibliography is in bibtex format, uncomment commands:
-\bibliographystyle{imsart-number}
-%\bibliographystyle{imsart-nameyear}
-
-%\bibliographystyle{abbrv}
-%\bibliographystyle{plain}
-\bibliography{rf,ref_mtl}
- % Style BST file (imsart-number.bst or imsart-nameyear.bst)
-%\bibliography{bibliography}       % Bibliography file (usually '*.bib')
-
-%% or include bibliography directly:
-%\begin{thebibliography}{4}
-%%%
-%\bibitem{r1}
-%\textsc{Billingsley, P.} (1999). \textit{Convergence of
-%Probability Measures}, 2nd ed.
-%Wiley, New York.
-%
-%\bibitem{r2}
-%\textsc{Bourbaki, N.}  (1966). \textit{General Topology}  \textbf{1}.
-%Addison--Wesley, Reading, MA.
-%
-%\bibitem{r3}
-%\textsc{Ethier, S. N.} and \textsc{Kurtz, T. G.} (1985).
-%\textit{Markov Processes: Characterization and Convergence}.
-%Wiley, New York.
-%
-%\bibitem{r4}
-%\textsc{Prokhorov, Yu.} (1956).
-%Convergence of random processes and limit theorems in probability
-%theory. \textit{Theory  Probab.  Appl.}
-%\textbf{1} 157--214.
-%\end{thebibliography}
-
-\end{document}
+%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
+%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
+%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
+%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
+%We believe that our theoretical framework can apply to other approaches to multi-task learning.

### 2021-06-28 revision_journal/setup.tex
update intro wip

@@
 
+\paragraph{Transfer learning.}
 There is a large body of classical and recent works on multi-task learning.
@@
 Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
+The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting}.
+For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
+One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
+However, their results only apply to sample size regimes at least logarithmic factors of dimension.
+\todo{a list of relevant papers}
+\begin{itemize}
+	\item \citet{lei2021nearoptimal}
+	\item \citet{kalan2020minimax}
+	\item \citet{cao2019learning}
+\end{itemize}
+\textit{Other related works.} Distributed learning \cite{dobriban2018high}.
+\citet{chen2021weighted}
+
+\paragraph{Random matrix theory.}
+\todo{write a paragraph regarding applications of RMT to modern machine learning.}
 
@@
 
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
 %\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.

### 2021-06-28 revision_journal/setup.tex
add references

@@
 For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
+\citet{tian2021transfer}
 One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
@@
 	\item \citet{cao2019learning}
+	\item \citet{hanneke2020value,hanneke2020no}
 \end{itemize}
@@
 \todo{write a paragraph regarding applications of RMT to modern machine learning.}
+\begin{itemize}
+	\item \citet{hastie2019surprises}
+	\item \citet{bartlett2020benign}
+	\item \citet{liang2020just}
+	\item \citet{montanari2019generalization}, \citet{liang2020precise}
+\end{itemize}
 
@@
 To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-\HZ{can you please add a discussion of the related work from RMT?}
+%\HZ{can you please add a discussion of the related work from RMT?}
 

### 2021-06-29 revision_journal/intro.tex
intro wip

--- 2021-06-14 revision_journal/intro.tex
@@
 
-\subsection{Summary of Results}
+\todo{mention connection to pooling \cite{hanneke2020no}}
+%\subsection{Summary of Results}
 
@@
 
-\subsection{Related Work}
+%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
 
+\subsection{Related work}
+
+\paragraph{Transfer learning.}
 There is a large body of classical and recent works on multi-task learning.
@@
 Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
+The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting}.
+For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
+\citet{tian2021transfer}
+One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
+However, their results only apply to sample size regimes at least logarithmic factors of dimension.
+\todo{a list of relevant papers}
+\begin{itemize}
+	\item \citet{lei2021nearoptimal}
+	\item \citet{kalan2020minimax}
+	\item \citet{cao2019learning}
+	\item \citet{hanneke2020value,hanneke2020no}, \citet{cai2021transfer}
+\end{itemize}
+\textit{Other related works.} Distributed learning \cite{dobriban2018high}.
+\citet{chen2021weighted}
+
+\paragraph{Random matrix theory.}
+\todo{write a paragraph regarding applications of RMT to modern machine learning.}
+\begin{itemize}
+	\item \citet{hastie2019surprises}
+	\item \citet{bartlett2020benign}
+	\item \citet{liang2020just}
+	\item \citet{montanari2019generalization}, \citet{liang2020precise}
+\end{itemize}
 
@@
 To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-\HZ{can you please add a discussion of the related work from RMT?}
+%\HZ{can you please add a discussion of the related work from RMT?}
 
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
 %\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
@@
 
-\paragraph{Organizations.}
+\subsection{Organizations}
 The rest of this paper is organized as follows.

### 2021-06-29 revision_journal/setup.tex
intro wip

--- 2021-06-21 revision_journal/setup.tex
@@
-\section{Preliminaries and related work}\label{sec_HPS}
+\section{Preliminaries}\label{sec_HPS}
 In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
@@
 %However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
-
-\subsection{Related work}
-
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-\HZ{can you please add a discussion of the related work from RMT?}
-
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.

### 2021-06-30 revision_journal/results.tex
update intro wip
intro wip
sec 2 wip

@@
 
-\subsection{Covariate shift}\label{sec_diff}
-
-%The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
-
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$)
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-%for some small constant $0<\tau<1$.
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
-
-\begin{theorem}\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
-			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
-			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
-Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
-%also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$
-and plug them into \eqref{lem_cov_shift_eq}.
-The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
-
-For the bias limit, we have the following proposition.
-
-\begin{proposition}\label{prop_main_RMT}
-%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
-			\begin{align}
-				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
-				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
-			\end{align}
-%			\begin{align}\label{lem_cov_derv_eq}
-%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-%			\end{align}
-				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
-				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-		\be  \label{eq_a34extra}
-		\begin{split}
-				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
-				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{split}
-			\ee
-			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
-
-Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
-Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
-Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
-$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$
-and
-$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
-Using these estimates, it is easy to check that
-\begin{align}
-& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
-&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
-\label{bias_LLN}
-\end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
-However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
-
-\begin{remark}
-%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%\begin{remark}
-The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
-We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
-We leave this problem to future study.
-
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
-%\end{remark}
-\end{remark}
-
-\paragraph{Examples.}
-To describe quantitively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-\begin{example}%[Sample sizes]
-\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
-	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
-and $\wt \beta^{(i)}$ denotes the $i$-th
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-
-\begin{example} %[Covariate shift]
-\label{ex_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds.
-In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
-Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
-$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
-where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
-We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
-\end{align*}
-%belong to the following bounded set.
-%Let $\lambda_i$ be the $i$-th singular value of $M$.
-%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-%\vspace{-0.025in}
-%{\small}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-%\begin{proposition}[Covariate shift]\label{prop_covariate}
-%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-%	We have that
-%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
-%\end{proposition}
-%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
-Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix.
-%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-%Let
-%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$
-%We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
-%\be \nonumber
-%\begin{split}
-%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
-%\end{split}
-%\ee
-%with high probability for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-%
-%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-%\begin{align}\label{gvar_extra}
-%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-%\end{align}
-In fact, from equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
- a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
-\ee
-Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that
-%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-%\begin{align}\label{approximateteM}
-%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-%\end{align}
-%where
-$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}.
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
-
-%Hence we get that
-%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-%
-%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-%\begin{align}\label{gvar_extra2}
-%\begin{split}
-%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-%\end{split}
-%\end{align}
-%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-%\end{proof}
-
-\iffalse
-For large enough $p$,
-%in the left hand side of equation \eqref{lem_cov_shift_eq}:
-\begin{align*}
-	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
-\end{align*}
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
-\fi
-
-%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}.
-%Our first observation is that:
-However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
-We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$.
-In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
-When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
-%while as As $\lambda$ increases, the severity of covariate shift increases.
-We claim the following dichotomy.
-\begin{enumerate}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-\end{enumerate}
-We explain why the above dichotomy happens. We can write the variance limit as
-$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
-When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
-$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
-where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
-\begin{align*}
-\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
-\end{align*}
-%in this example is equal to
-%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
-%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%where $g(\lambda, a_1) \ge 0$.
-%and can be derived from algebraic calculations (details omitted).
-We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
-In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
-\begin{align*}
- \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
-\end{align*}
-%\begin{align*}
-% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-%\end{align*}
-This implies $n_1>n_2$.
-The other direction follows from a similar argument.
-% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
-\end{example}
-
-\iffalse
-%FY: Below was the word explanation. I still think the above simple proof is clearer.
-In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
-The other case when $n_1 < n_2$ is similar.
-A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
-If $n_1< n_2$, then $f(\lambda)< f(1)$.
-\fi
-
-\paragraph{Simulations.}
-Finally, we validate the result of Example \ref{ex_covshift}.
-Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
-The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
-
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
-
-%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
-
-\subsection{Task size imbalance}\label{sec_sizeratio}
+\subsection{Uneven sample sizes}\label{sec_sizeratio}
 
@@
 \fi
-	\end{example}
+%	\end{example}
 
@@
 Intuitively, this is because bias increases less for smaller $d^2$.
+
+\subsection{Covariate shift}\label{sec_diff}
+
+%The previous section assumes that all tasks have the same sample size and feature vectors.
+In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
+%The different covariates case differs from the same covariates case in two aspects.
+%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
+In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
+In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
+
+\iffalse
+Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
+This is because $f(A, B)$ is in general non-convex.
+Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
+We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
+Let $n_1, n_2$ denote task one  and two's sample size, respectively.
+Suppose
+\begin{align*}
+	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
+	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
+\end{align*}
+where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
+$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
+
+Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
+We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
+When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
+To motivate our study, we consider a special case where $A_1=A_2=1$.
+Hence the HPS estimator is equal to $B$.
+%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
+By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
+\begin{align}
+	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
+	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
+\end{align}
+The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
+
+To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
+ %similar to Claim \ref{claim_pred_err}
+\begin{align}
+	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
+	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
+	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
+\end{align}
+Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
+\fi
+
+%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
+Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
+%However, capturing this intuition quantitatively turns out to be technically challenging.
+%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
+To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$)
+$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$
+%Let $U\Lambda V^\top$ denote the SVD of $M$ and
+Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
+\begin{equation}\label{assm32}
+|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
+\end{equation}
+%for some small constant $0<\tau<1$.
+The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
+
+\begin{theorem}\label{thm_main_RMT}
+%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
+%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
+%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
+%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
+%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
+Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
+%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
+			\begin{align}\label{lem_cov_shift_eq}
+				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
+				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
+			\end{align}
+			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
+			\begin{align}
+				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
+				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
+			\end{align}
+
+\end{theorem}
+
+ With \eqref{assm32}, it is easy to see that
+$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
+Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
+Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
+%also extends  to the inverse of the sum of two sample covariance matrices.
+To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that
+$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$
+and plug them into \eqref{lem_cov_shift_eq}.
+The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
+%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
+%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
+%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
+
+For the bias limit, we have the following proposition.
+
+\begin{proposition}\label{prop_main_RMT}
+%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
+Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
+			\begin{align}
+				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
+				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
+				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
+			\end{align}
+%			\begin{align}\label{lem_cov_derv_eq}
+%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
+%			\end{align}
+				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
+				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
+				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+		\be  \label{eq_a34extra}
+		\begin{split}
+				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
+				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
+%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+%				= b_0.
+			\end{split}
+			\ee
+			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
+\end{proposition}
+
+Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
+Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
+Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
+$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$
+and
+$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
+Using these estimates, it is easy to check that
+\begin{align}
+& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
+&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
+\label{bias_LLN}
+\end{align}
+Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
+However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
+
+\begin{remark}
+%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
+%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+%\begin{remark}
+The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
+In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
+We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
+However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
+We leave this problem to future study.
+
+We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
+%\end{remark}
+\end{remark}
+
+\todo{describe comparison to the TL estimator and the weighted OLS estimator.}
+
+\paragraph{Examples.}
+To describe quantitatively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
+\cite{dobriban2020wonder,dobriban2018high}).
+
+ %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
+Next, we illustrate how varying them impact the prediction loss.
+%\begin{example}%[Sample sizes]
+%\label{ex_sample_ratio}
+	%We first consider the impact of varying sample sizes.
+	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
+	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
+	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
+$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
+where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
+and $\wt \beta^{(i)}$ denotes the $i$-th
+%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
+task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+
+%\begin{example} %[Covariate shift]
+%\label{ex_covshift}
+%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
+%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
+%In general, the covariance matrices of the two tasks may be different such as in text classification.
+To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds.
+In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
+Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
+$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
+where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
+We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
+\begin{align*}
+		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
+\end{align*}
+%belong to the following bounded set.
+%Let $\lambda_i$ be the $i$-th singular value of $M$.
+%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
+%\vspace{-0.025in}
+%{\small}
+%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
+%\begin{proposition}[Covariate shift]\label{prop_covariate}
+%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
+%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
+%	We have that
+%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
+%\end{proposition}
+%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
+%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
+%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
+Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix.
+%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
+%Let
+%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$
+%We now calculate $g(M_0)$.
+With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
+Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
+%\be \nonumber
+%\begin{split}
+%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
+%\end{split}
+%\ee
+%with high probability for some constant $\e>0$.
+In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
+We omit the details here.
+%
+%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
+%\begin{align}\label{gvar_extra}
+%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
+%\end{align}
+In fact, from equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
+\be\label{est_a12extra}
+ a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
+\ee
+Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that
+%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
+%\begin{align}\label{approximateteM}
+%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
+%\end{align}
+%where
+$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
+%With these two bounds, we can easily conclude \eqref{approxteM}.
+%
+%We have that the test error satisfies
+%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
+%where $\lambda_p$ is the smallest singular value of $p$ and
+%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
+%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
+By AM-GM inequality, we observe that
+$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
+is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
+
+%Hence we get that
+%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
+%
+%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
+%\begin{align}\label{gvar_extra2}
+%\begin{split}
+%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
+%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
+%\end{split}
+%\end{align}
+%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
+%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+%\end{proof}
+
+\iffalse
+For large enough $p$,
+%in the left hand side of equation \eqref{lem_cov_shift_eq}:
+\begin{align*}
+	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
+	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
+\end{align*}
+%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
+Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
+\fi
+
+%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}.
+%Our first observation is that:
+However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
+We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$.
+In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
+When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
+%while as As $\lambda$ increases, the severity of covariate shift increases.
+We claim the following dichotomy.
+\begin{enumerate}
+	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
+	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
+\end{enumerate}
+We explain why the above dichotomy happens. We can write the variance limit as
+$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
+When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
+$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
+where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
+\begin{align*}
+\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
+\end{align*}
+%in this example is equal to
+%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
+%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
+%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
+%\begin{align*}
+%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
+%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
+%\end{align*}
+%\begin{align*}
+%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
+%\end{align*}
+%where $g(\lambda, a_1) \ge 0$.
+%and can be derived from algebraic calculations (details omitted).
+We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
+In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
+\begin{align*}
+ \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
+\end{align*}
+%\begin{align*}
+% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
+%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
+%\end{align*}
+This implies $n_1>n_2$.
+The other direction follows from a similar argument.
+% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
+Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
+%\end{example}
+
+\todo{draw a connection to \citet{david2010impossibility}}
+
+\iffalse
+%FY: Below was the word explanation. I still think the above simple proof is clearer.
+In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
+Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
+The other case when $n_1 < n_2$ is similar.
+A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
+Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
+If $n_1< n_2$, then $f(\lambda)< f(1)$.
+\fi
+
+\paragraph{Simulations.}
+Finally, we validate the result of Example \ref{ex_covshift}.
+Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
+Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
+We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
+The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
+
+%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
+
+%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
+
+\input{multitask.tex}

### 2021-06-30 revision_journal/setup.tex
sec 2 wip

@@
 
-Consider the transfer learning setting with two data sets.
-We denote their sample sizes by $n_1$ and $n_2$.
-For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
+Consider the transfer learning setting with two data sets. We denote their sample sizes by $n_1$ and $n_2$.
+For $i=1,2,$ let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
 We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
 $$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
-We remark that all these assumptions are natural in high-dimensional statistics.
+Throughout the paper, we make the following assumptions on the feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$, following the work of \citet{hastie2019surprises} (see also \citet{wu2020optimal,richards2021asymptotics} and the references therein).
+%We remark that all these assumptions are natural in high-dimensional statistics.
 
@@
 \end{equation}
-
-Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
-$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
-
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
 
@@
 %\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
+Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
+$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
+
+Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
+The critical questions are:
+(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
+(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
 

### 2021-06-30 revision_journal/setup.tex
Updates from Overleaf

@@
 
-\subsection{Large dimensional random matrices}
+\subsection{Data model}
 
-Consider the transfer learning setting with two data sets. We denote their sample sizes by $n_1$ and $n_2$.
-For $i=1,2,$ let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
-$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-Throughout the paper, we make the following assumptions on the feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$, following the work of \citet{hastie2019surprises} (see also \citet{wu2020optimal,richards2021asymptotics} and the references therein).
+We describe the data model and the underlying assumptions.
+Suppose we have two regression datasets.
+We denote their sample sizes by $n_1$ and $n_2$, respectively.
+Consider either $i = 1$ or $i = 2$.
+Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
+We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for the feature covariates $X^{(i)}$ follows a linear model plus random noise $\varepsilon^{(i)}$:
+$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)}.$
+Both $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of the feature covariates and the noise vector.
+Throughout the paper, we make the following assumptions on  $X^{(i)}$ and  $\varepsilon^{(i)}$, which are standard in recent  random matrix theory literature (see e.g.
+\citet{tulino2004random,bai2010spectral}).
 %We remark that all these assumptions are natural in high-dimensional statistics.
 
-We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let
-\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
-where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
-entries satisfying
-\begin{equation}\label{assm1}
-\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1,
-\end{equation}
+First, we assume the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)} \in \real^{p \times p}$. More precisely, let
+\be\label{XofZ}
+    X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},
+\ee
+where $\Sigma^{(i)}$ is a deterministic positive definite symmetric matrices, $Z^{(i)}=(z^{(i)}_{j,k})$ is a $n_i\times p$ random matrix with real-valued independent entries having zero mean and unit variance.
+%\begin{equation}\label{assm1}
+%\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1,
+%\end{equation}
+Let $\tau>0$ be a small constant.
+We assume that for some constant $\varphi>4$, the $\varphi$-th moment of each entry $z^{(i)}_{j, k}$ is bounded from above by $1/\tau$:
+\be \label{conditionA2}
+\ex{\vert z^{(i)}_{j, k} \vert^\varphi}  \le \frac 1{\tau}. %,\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
+\ee
 
-Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
-\be \label{conditionA2}
-\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
+Second, we assume that $\varepsilon^{(i)} \in \real^{n_i}$ is a random noise vector with i.i.d entries having mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
+\be\label{eq_highmoments}
+\ex{| \ve^{(i)}_{j} |^k} \le C_k.
 \ee
-for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee
-%for a small constant $\tau>0$.
 
-We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\be\label{eq_highmoments}
-\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
-\ee
-Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
 %Moreover, we assume that
@@
 
-In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that
+Finally, we assume a high-dimensional setting when the sample sizes are proportional to the dimension up to a constant factor.
+Denote by $\rho_i = n_i / p$, we require that
 \be\label{assm2}
-1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
+1+\tau \le \rho_i \le p^{\tau^{-1}}.
 \ee
-for a small constant $\tau >0$.
-If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper.
-The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
-are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.
+The first inequality ($1 + \tau \le \rho_i$) ensures that the sample covariance matrices $(X^{(1)})^\top X^{(1)}$ and $(X^{(2)})^\top X^{(2)}$ are non-singular with high probability.
+%Thus, the ordinary least squares estimator is well-defined for the linear regression problem on each (single) task.
+%This setting encompasses many 
+The second inequality ($\rho_i \le p^{\tau^{-1}}$) is without loss of generality.
+Otherwise, standard concentration results such as the central limit theorem already imply accurate estimates of the linear model under the setting defined by equation \eqref{assm2}.
 
-We summarize our basic assumptions here for future reference.
-\begin{assumption}\label{assm_big1}
+To summarize, the underlying assumptions in our data model are as follows.
+\begin{assumption}[Data model]\label{assm_big1}
 Let $\tau$ be a small constant.
+Let $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices whose eigenvalues are bounded between $\tau$ and $1 / \tau$.
 \begin{enumerate}
-\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}.
-%and (\ref{assm2}).
-We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
+\item  $X^{(1)}$ and $X^{(2)}$ take the form of equation \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are both random matrices with i.i.d.
+entries having zero mean, unit variance, and bounded moments as in equation \eqref{conditionA2}.
 
-\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
+\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in equation \eqref{eq_highmoments}.
 
-\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
-
-\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.
-
+\item $\rho_{1}$ and $\rho_{2}$ satisfy equation \eqref{assm2}. Furthermore, $\tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1}$.
 \end{enumerate}
@@
 
-\subsection{Hard parameter sharing estimators}
+%\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
 
+\todo{
+We assume that $\Sig^{(i)}$ has eigendecomposition
+\be\label{eigen}
+\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
+\ee
+where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
+\begin{equation}\label{assm3}
+ \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
+\ee}
+%for a small constant $\tau>0$.
+
+\subsection{Estimators}
+
+We describe our estimators that combine the information from both datasets.
+We learn a two-layer linear neural network with parameters $A \in \real^{p\times r}$, $B_1 \in \real^{r}$, and $B_2 \in \real^r$ by minimizing the following optimization objective:
+\begin{align}\label{eq_hps}
+    f(A, B_1, B_2) = \bignorm{X^{(1)} A B_1 - Y^{(1)}}_2^2 + \bignorm{X^{(2)} A B_2 - Y^{(2)}}_2^2.
+\end{align}
+The above two-layer neural network (also called hard parameter sharing \cite{C97}) captures the intuition that both datasets share the feature space (i.e.
+the subspace spanned by the columns of $A$) while each having a separate prediction head.
+Suppose that $(\hat{A}, \hat{B_1}, \hat{B_2})$ is a minimizer of $f(\cdot)$.
+We define the hard parameter sharing estimator for task $i$ as
+\[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
+Our study of such estimators is motivated by the fact that hard paratemer sharing is widely used in empirical studies of multi-task learning \cite{R17}.
+\todo{Later on in Section \ref{sec_diff}, we will further compare the HPS estimator to other natural transfer learning estimators.} %$L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.}
+
+We measure the performance of $\hat{\beta}_i^{\MTL}$ through the out-of-sample predication risk (or test loss).
+Consider a datapoint $(x,y)$ generated from the same model as dataset $i$: $y= x^\top \beta^{(i)} + \ve$.
+%, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
+%We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure
+The expected predication risk (under mean squared error) is given by
+$$\exarg{x, \varepsilon}{\left\|y-x^\top \hat{\beta}_i^{\MTL} \right\|^2}= \left\|\big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 + \sigma^2.$$
+%Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
+The excess risk is defined without the constant term $\sigma^2$:
+\be\label{HPS_loss}
+    L(\hat{\beta}_i^{\MTL}):= \left\| \big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 .
+\ee
+
+We focus on the setting where the hidden dimension $r = 1$.
+Otherwise, the excess risk of the HPS estimator and that of the ordinary least squares (OLS) estimator are equal to each other \cite{WZR20}.
+\begin{proposition}\label{prop_large_r}
+    Suppose that Assumption \ref{assm_big1} holds.
+    Let $\hat{\beta}_i^{\STL} = \big( {X^{(i)}}^{\top} X^{(i)} \big)^{-1} {X^{(i)}}^{\top} Y^{(i)}$ denote the OLS estimator, for either $i = 1$ or $i = 2$.
+    Then, for any $r \ge 2$, we have that $L(\hat{\beta}_i^{\MTL}) = L(\hat{\beta}_i^{\STL})$.
+\end{proposition}
+
+\begin{proof}
+    Since both $n_1$ and $n_2$ are at least $(1 + \tau) p$, the inverse of both ${X^{(1)}}^{\top} X^{(1)}$ and ${X^{(2)}}^{\top} X^{(2)}$ exists.
+    Thus, both $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are well-defined.
+    The global minimum of each summand of equation \eqref{eq_hps} is achieved if and only if $\hat{\beta}_1^{\STL}$ and $\hat{\beta}_2^{\STL}$ are both in the column subspace of $A$.
+    In this case, $\hat{\beta}_1^{\MTL} = A B_1$ must be equal to $\hat{\beta}_1^{\STL}$ (same for $\hat{\beta}_2^{\MTL}$).
+\end{proof}
+%Our goal is to characterize the 
+%$The minimizers of $f(\cdot)$
 %\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
-Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{bastani2020predicting, li2020transfer}:
-$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
 
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
+When $r = 1$, both $B_1$ and $B_2$ reduce to scalars.
+In particular, the case when $B_1$ and $B_2$ are both equal to $1$ reduces to a pooling estimator, which treats both datasets as if they are drawn independently from the same distribution.
+Such pooling estimators have been shown to be effective on e-commence and healthcare datasets \cite{bastani2020predicting}.
+Additionally, they have been used as a preprocessing step of minimax optimal estimators, under certain conditions of the data \cite{li2020transfer} (see also Section \ref{sec_related} for further discussion of both works).
+%Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{, li2020transfer}:
+%$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
 
-In this paper, we measure the performance of $\hat{\beta}_2^{\MTL} (\hat a)$ through the out-of-sample predication loss (test error).
-Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
-$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$
-Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
-\be\label{HPS_loss}
-L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
- \ee
-We will compare it to the out-of-sample predication losses of the baseline estimators, $L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.
+%Given a solution from minimizing $f(A, B)$, denoted by   (which we will specify below), let  denote the HPS estimator for task $i$.
+%The critical questions are:
+%(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
+%(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
 
 %$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
+\subsection{Bias and variance}
 
-Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-\end{align}
-Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-where
-\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-is called the bias term, which depends on the model bias between task 1 and task 2, and
-\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-%predication loss for the HPS and OLS estimators.
+Proposition \ref{prop_large_r} suggests that the two-layer neural network provides information transfer only when $r = 1$.
+Next, we provide the bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ under this setting.
+As a remark, for general $r$, problem \eqref{eq_hps} is non-convex since $f(\cdot)$ is a degree-four polynomial.
+Nevertheless, the setting when $r = 1$ remain tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.
 
-\begin{lemma}\label{lem_HPS_loss}
+\begin{proposition}\label{lem_HPS_loss}
      Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
@@
     %with high probability for any small constant $\e>0$.
-\end{lemma}
+\end{proposition}
+
+\begin{proof}[Proof sketch]
+    Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
+    \begin{align}
+    L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
+    &\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
+    \end{align}
+    Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
+    \be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
+    where
+    \be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
+    is called the bias term, which depends on the model bias between task 1 and task 2, and
+    \be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
+    is called the variance term, which depends on the noise variance.
+Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
+In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
+    %predication loss for the HPS and OLS estimators.
+\end{proof}
 
@@
 %However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
+
+\todo{clarify overparametrize}
+As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)

### 2021-06-30 revision_journal/intro.tex
sec 2 wip
Updates from Overleaf

@@
 
-Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
+Many modern machine learning methods
+%Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
 Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
@@
 
+\subsection{Summary of results}
 \todo{mention connection to pooling \cite{hanneke2020no}}
@@
 
-\subsection{Related work}
+\subsection{Related work}\label{sec_related}
 
@@
 In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
+\cite{Anisotropic} later extended this result to sample covariance matrices with arbitrary covariance.
 %On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .

### 2021-07-01 revision_journal/results.tex
Updates from Overleaf

@@
 
-\subsection{Uneven sample sizes}\label{sec_sizeratio}
+%In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term  and variance term  in two different settings:
+In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
+We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
+In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
+On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
+%Here case (ii) is actually more general than (i)
+
+\subsection{Model shift}\label{sec_sizeratio}
 
@@
 
-\begin{theorem}\label{cor_MTL_loss}
+\begin{theorem}[Bias-variance asymptotics of HPS estimators under model shift]\label{cor_MTL_loss}
 Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
@@
 
-\paragraph{Examples.}
+\paragraph{Illustrative examples.}
 First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
@@
 
-\paragraph{Simulations.}
+\paragraph{Comparison to other estimators.}
+    \begin{align}
+    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
+    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
+    \end{align}
+    and
+    \begin{align}
+    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
+    \end{align}
+    %Moreover, there exists a constant $C_0>0$ such that with high probability,
+    %\be\label{loss_large}
+    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
+    %\ee
+    %with high probability for any small constant $\e>0$.
+
+ With Lemma \ref{fact_tr}, we obtain that w.h.p.,
+\begin{align}
+L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
+\end{align}
+and
+\begin{align}
+L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
+ \end{align}
+
+\todo{merge into prev paragraphs {Simulations.}}
 Second, we validate the result of Example \ref{ex_sample_ratio}.
@@
 
-For the bias limit, we have the following proposition.
-
-\begin{proposition}\label{prop_main_RMT}
-%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
-			\begin{align}
-				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
-				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
-			\end{align}
-%			\begin{align}\label{lem_cov_derv_eq}
-%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-%			\end{align}
-				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
-				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-		\be  \label{eq_a34extra}
-		\begin{split}
-				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
-				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{split}
-			\ee
-			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
-
-Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
-Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
-Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
-$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$
-and
-$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
-Using these estimates, it is easy to check that
-\begin{align}
-& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
-&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
-\label{bias_LLN}
-\end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
-However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
-
-\begin{remark}
-%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%\begin{remark}
-The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
-We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
-We leave this problem to future study.
-
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
-%\end{remark}
-\end{remark}
-
-\todo{describe comparison to the TL estimator and the weighted OLS estimator.}
-
-\paragraph{Examples.}
+\paragraph{Illustrative examples.}
 To describe quantitatively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
@@
 
-\paragraph{Simulations.}
+\paragraph{Comparison to other estimators.}
+
+\todo{merge into previous paragraphs {Simulations.}}
 Finally, we validate the result of Example \ref{ex_covshift}.
@@
 
-\input{multitask.tex}
+\subsection{Model and covariate shift}
+
+For the bias limit, we have the following proposition.
+
+\begin{proposition}\label{prop_main_RMT}
+%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
+Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for $L_{\bias}(a)$ in \eqref{Lbias}:
+			\begin{align}
+				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
+				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 +\OO\left( n_1^{-1/2+2/\varphi + c}\right)\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
+				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
+			\end{align}
+%			\begin{align}\label{lem_cov_derv_eq}
+%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
+%			\end{align}
+				uniformly in all $a\in \R$. Here $\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, $\Pi(a)$ is a $p\times p$ matrix defined as
+				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
+				 and $(a_{3},a_4)$ is the solution of the following system of equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+		\be  \label{eq_a34extra}
+		\begin{split}
+				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
+				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
+%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
+%				= b_0.
+			\end{split}
+			\ee
+			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
+\end{proposition}
+
+Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
+Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
+Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
+$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$
+and
+$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
+Using these estimates, it is easy to check that
+\begin{align}
+& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
+&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
+\label{bias_LLN}
+\end{align}
+Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ using the law of large numbers in the regime $n_1\gg p$.
+However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
+
+\begin{remark}
+%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
+%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
+%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+%\begin{remark}
+The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
+In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
+We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
+However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
+To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
+We leave this problem to future study.
+
+We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for the bias term also fails, because we cannot reduce the problem into the free addition of two random matrices that are asymptotically freely independent.
+%\end{remark}
+\end{remark}
+
+\todo{describe comparison to the TL estimator and the weighted OLS estimator.}

### 2021-07-01 revision_journal/setup.tex
Updates from Overleaf

@@
 In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
+In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
+We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
+%Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
 
@@
 We describe the data model and the underlying assumptions.
-Suppose we have two regression datasets.
+Suppose we have two regression datasets (or tasks).
 We denote their sample sizes by $n_1$ and $n_2$, respectively.
@@
 
-\todo{
-We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee}
-%for a small constant $\tau>0$.
-
 \subsection{Estimators}
@@
     Suppose that Assumption \ref{assm_big1} holds.
-    Let $\hat{\beta}_i^{\STL} = \big( {X^{(i)}}^{\top} X^{(i)} \big)^{-1} {X^{(i)}}^{\top} Y^{(i)}$ denote the OLS estimator, for either $i = 1$ or $i = 2$.
+    Let $\hat{\beta}_i^{\STL} = \big( (X^{(i)})^{\top} X^{(i)} \big)^{-1} (X^{(i)})^{\top} Y^{(i)}$ denote the OLS estimator, for either $i = 1$ or $i = 2$.
     Then, for any $r \ge 2$, we have that $L(\hat{\beta}_i^{\MTL}) = L(\hat{\beta}_i^{\STL})$.
@@
 Proposition \ref{prop_large_r} suggests that the two-layer neural network provides information transfer only when $r = 1$.
-Next, we provide the bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ under this setting.
+Next, we provide the bias-variance decomposition of the excess risk under this setting.
+Without loss of generality, we focus on task two's excess risk $L(\hat{\beta}^{\MTL}_2)$.
 As a remark, for general $r$, problem \eqref{eq_hps} is non-convex since $f(\cdot)$ is a degree-four polynomial.
-Nevertheless, the setting when $r = 1$ remain tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.
+Nevertheless, the setting when $r = 1$ remains tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.
+Since $B_1$ and $B_2$ are both scalars, let $a = B_1 / B_2$.
+Let $\hat{\Sigma}(a) \define a^2 (X^{(1)})^{\top} X^{(1)} + (X^{(2)})^{\top} X^{(2)}$ be a weighted combination of the sample covariance matrices.
+We present a bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ for the setting of $r = 1$ as follows.
 
-\begin{proposition}\label{lem_HPS_loss}
+\begin{proposition}[Bias-variance decomposition]\label{lem_HPS_loss}
      Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
     \begin{align}
-    L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
-    &+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
+        L(\hat{\beta}_2^{\MTL}) =& \left( 1+ \OO(p^{-1/2+c})\right)\cdot \left(L_{\bias} (a) + L_{\var}(a)\right) %\nonumber\\
+        + \OO \left( p^{-C}\big( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\big)   \right), \label{L_HPS_simple}
     \end{align}
+    where the bias and variance equations are defined as follows:
     \begin{align}
-    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
+        L_{\bias} (a) &\define \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2,  \label{Lbias} \\
+        L_{\var}(a)   &\define \sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }}.  \label{Lvar}
     \end{align}
-    and
-    \begin{align}
-    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-    \end{align}
-    %Moreover, there exists a constant $C_0>0$ such that with high probability,
-    %\be\label{loss_large}
-    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-    %\ee
-    %with high probability for any small constant $\e>0$.
 \end{proposition}
 
-\begin{proof}[Proof sketch]
-    Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-    \begin{align}
-    L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-    &\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-    \end{align}
-    Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-    \be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-    where
-    \be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-    is called the bias term, which depends on the model bias between task 1 and task 2, and
-    \be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-    is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-    %predication loss for the HPS and OLS estimators.
-\end{proof}
-
-Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$.
-In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
-(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}.
+Equation \eqref{L_HPS_simple} shows that the excess risk of the HPS estimator admits a clean bias-variance decomposition plus lower-order terms that decrease to zero with the dimension $p$.
+Since equation \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can apply the result to $a = \hat{B}_1 / \hat{B}_2$, for any $\hat{B}_1$ and $\hat{B}_2$ that may depend on $\ve^{(1)}$ and $\ve^{(2)}$ (after solving problem \eqref{eq_hps}).
+%The proof of Proposition \ref{lem_HPS_loss} involves
+We briefly describe why Proposition \ref{lem_HPS_loss} holds.
+First, suppose that $a$ is an arbitrary value that is independent of the random noise vectors$ \varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
+By taking the expectation over both of them, we get the following result:
+\be\label{partial-L}
+    \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}) } = L_{\bias} (a) + L_{\var}(a).
+\ee
+Secondly, using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
+For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of Section \ref{??}.
 To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
 Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.
+The proof of Proposition \ref{lem_HPS_loss} can be found in Section  \ref{app_firstpf}.
+
+\paragraph{Connection to information transfer.}
+To be precise, we say that task one provides a positive transfer to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
+Otherwise, we say that task one provides a negative transfer to task two.
+We now illustrate that the bias-variance decomposition of Proposition \ref{lem_HPS_loss} characterizes whether or not the information transfer is positive.
+
+First, we compare the bias. Since $n_1 \ge (1 + \tau) p$ by Assumption \ref{assm_big1}, the bias of $\hat{\beta}_2^{\STL}$ is zero.
+Thus, the bias of $\hat{\beta}_2^{\MTL}$ is always higher than that of $\hat{\beta}_2^{\STL}$.
+Second, we compare the variance.
+By a similar argument as in Proposition \ref{lem_HPS_loss}, the variance of $\hat{\beta}_2^{\STL}$ is equal to $\sigma^2 \bigtr{\Sigma^{(2)} ((X^{(2)})^{\top} X^{(2)})^{-1}}$.
+Then, a straightforward algebraic calculation (e.g. using the Woodbury matrix identity) shows that the variance of $\hat{\beta}_2^{\MTL}$ is always higher than that of $\hat{\beta}_2^{\STL}$:
+\begin{align*}
+    \bigtr{\Sigma^{(2)} \big(\hat{\Sigma}(a)\big)^{-1}} \le \bigtr{\Sigma^{(2)} \big((X^{(2)})^{\top} X^{(2)}\big)^{-1}}.
+\end{align*}
+Combining both comparisons, we conclude that HPS affects the excess risk in two ways: the bias always increases while the variance always decreases.
+Thus, whether or not task one provides a positive transfer to task two depends on which effect is more significant.
+
+%The bias equation \eqref{Lbias} captures the 
+%Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
+%\begin{align}
+%    L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
+%    &\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
+%\end{align}
+%Note that 
+%    is called the variance term, which depends on the noise variance. 
+    %predication loss for the HPS and OLS estimators.
+%\end{proof}
+
+%In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
+(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.)
 
@@
 
-For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.
+\paragraph{Bias and variance asymptotics.}
+Building on the above connection, we apply recent developments from random matrix theory to analyze information transfer.
+As a warmup, we describe the following classical result in multivariate statistics that characterizes the excess risk (or equivalently, the variance) of the OLS estimator.
 
-\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
+\begin{lemma}[Variance asymtotics of OLS estimators, cf. Theorem 2.4 of \citet{isotropic} and Theorem 3.14 of \citet{DY}]\label{fact_tr}
 	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
@@
 If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of
-the inverse Wishart distribution \cite{anderson1958introduction}.
+the inverse Wishart distribution \citet{anderson1958introduction}.
 For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
-Lemma 3.11 of \cite{bai2009spectral}).
-Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate.
-With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
- \end{align}
+Lemma 3.11 of \citet{bai2009spectral}).
+Here we have presented the results from \citet{isotropic} and \citet{DY}, who give an almost sharp convergence rate.
 
-On the other hand, much less is known about the predication loss of the HPS estimator.
-In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
+On the other hand, characterizing the risk of the HPS estimator requires dealing with several challenges.
+First, characterizing bias (cf. equation \eqref{Lbias}) introduces the issue of \textit{model shift}, when $\beta^{(1)}$ differs from $\beta^{(2)}$.
+Second, characterizing variance (cf. equation \eqref{Lvar}) introduces  the issue of \textit{covariate shift}, when $\Sigma^{(1)}$ differs from $\Sigma^{(2)}$.
+More precisely, we define the two settings as follows:
+\begin{itemize}
+    \item \textbf{Model shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices (i.e.
+$\Sigma^{(1)}=\Sigma^{(2)}$) but different models (i.e.
+$\beta^{(1)} \neq \beta^{(2)}$).
+    \item \textbf{Covariate shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices and but different models.
+\end{itemize}
+Our main results in the next section provide precise bias-variance asymptotics under both settings.
+%In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
 %\FY{What is known so far about this topic?}
-In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in two different settings: (i) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
-We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
-In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
-On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
-%Here case (ii) is actually more general than (i)
+
 %In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.
-In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
-We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
-%Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
 
@@
 %However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
+\begin{remark}
     \todo{clarify overparametrize}
     As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
+\end{remark}
+
+\subsection{Notations}
+
+\todo{
+We assume that $\Sig^{(i)}$ has eigendecomposition
+\be\label{eigen}
+\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
+\ee
+where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
+\begin{equation}\label{assm3}
+ \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
+\ee}
+%for a small constant $\tau>0$.
+
+In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.

### 2021-07-02 revision_journal/exp.tex
restructure
reorg wip
update intro wip
Updates from Overleaf

@@
-\section{Theoretical Implications}
+\section{Empirical results}
 
 %\subsection{Comparison between the averaging and HPS estimators}
+\subsection{Regression tasks}
 
-\subsection{Covariance Alignment}
-
-\paragraph{Covariate shift}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
-
-%One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
-%\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
-%where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
-%$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
-%The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
-%In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
-
-%\section{Experimental results}
-
-\subsection{Progressive Training}%\label{sec_text}
-
+\subsection{Text classification tasks}
 Our results and simulations are all in the high-dimensional linear regression setting.
@@
 
+\paragraph{Progressively increasing source dataset sizes.}%\label{sec_text}
 %multi-layer perceptron (MLP), LSTM, CNN on all tasks
@@
 %The results show that STL results are indicative of MTL results.
-
-\paragraph{Sample size ratio.}
+%\paragraph{Sample size ratio.}
 First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
@@
 
-\subsection{Rank Selection}
+\paragraph{Covariate alignment.}
+Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
+This highlights the need for correcting covariate shifts when the sample size ratio rises.
+To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
+The idea is to add an alignment module between the input and the shared module $B$.
+This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
+%We validate our insight on this procedure in the experiments.
+%We implement the covariance alignment procedure following \cite{WZR20}.
+
+We conduct multi-task training on all $15$ task pairs from the six datasets.
+In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
+To get a robust comparison, we average the improvements over the 15 task pairs.
+The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
+We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
+
+%One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
+%\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
+%where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
+%$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
+%The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
+%In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
+
+%\section{Experimental results}
+
+%\subsection{Model width selection}
 %As a further validation, excluding TREC, we observe similar comparative results.

### 2021-07-02 revision_journal/intro.tex
Updates from Overleaf

@@
 \end{itemize}
+\begin{remark}
+    \todo{clarify overparametrize}
+    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
+\end{remark}
 
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
+In the single task case, if the data is Gaussian distributed, then precise variance can be derived immediately from properties of Wishart distribution.
+In particular, in the high dimensional setting, the eigenvalues of Wishart matrices satisfy the famous Marchenko–Pastur (MP) law \cite{MP}.
+It well-known that the MP law holds universally regardless of the detailed data distribution \cite{bai2010spectral}.
 In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
@@
 %On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
+Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
 These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
@@
 
+%\subsection{Notations}
+
+%for a small constant $\tau>0$.
+
 \subsection{Organizations}

### 2021-07-02 revision_journal/results.tex
Updates from Overleaf

@@
 
-%In Section \ref{sec_HPS_loss}, we give a rigorous analysis of the bias term  and variance term  in two different settings:
 In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
@@
 
-\subsection{Model shift}\label{sec_sizeratio}
-
- In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
-
-\begin{theorem}[Bias-variance asymptotics of HPS estimators under model shift]\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
-\ee
-and
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}.
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)}
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
-
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
-
-We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the rotational invariance of multivariate Gaussian distributions,
-%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence
-the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
-
-We believe that the above argument can be extended to the case without the Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
-Hence we do not pursue this direction in this paper.
-
-\paragraph{Illustrative examples.}
-First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
-	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
-
-	\begin{proposition}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Suppose Assumption \ref{assm_big1} and the above setting of random effect model hold. %in Example \ref{ex_same_cov} hold.
-Suppose that for a constant $c_0>0$,
-	\be\label{para_rel}
-	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
-	\ee
- Then we have that for any small constant $c>0$ and large constant $ C>0$,
-	%Let $c$ be a sufficiently small fixed constant.
-	%In the setting of Corollary \ref{cor_MTL_loss},
-%There exists a constant $C>0$ such that
-	\be\label{hatw_add1}
-	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
-	\ee
-\end{proposition}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
-%and $\wt \beta^{(i)}$ denotes the $i$-th
-%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-
-We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
-$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
-with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations.
-Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
-This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
-Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
-
-Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
-$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
-First, we have positive (resp.
-negative) transfer if and only if $h(\rho)>0$ (resp.
-$h(\rho)<0$).
-Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
-\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
-
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
-
-\begin{itemize}
-\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
-
-\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
-Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
-\end{itemize}
-\end{enumerate}
-Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial
-\be\label{poly2}
- \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
-
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
-\end{enumerate}
-
-%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance.
-%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
-\iffalse
-Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
-
-Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
-	\begin{align*}
-		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
-		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
-		= \frac{p}{n_1 + n_2 - p},
-	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit.
-	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
-
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
-This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
-by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-
-{\cor
-For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that
-	\begin{align}
-		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
-		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
-			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
-For the bias term,
-}
-
-Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
-For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
-We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
-It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
-By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
-\fi
-%	\end{example}
-
-\paragraph{Comparison to other estimators.}
-    \begin{align}
-    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
-    \end{align}
-    and
-    \begin{align}
-    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-    \end{align}
-    %Moreover, there exists a constant $C_0>0$ such that with high probability,
-    %\be\label{loss_large}
-    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-    %\ee
-    %with high probability for any small constant $\e>0$.
-
- With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
- \end{align}
-
-\todo{merge into prev paragraphs {Simulations.}}
-Second, we validate the result of Example \ref{ex_sample_ratio}.
-Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-%Again, our estimates are accurate compared to the empirical losses.
-We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$.
-The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
-On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
-Intuitively, this is because bias increases less for smaller $d^2$.
-
 \subsection{Covariate shift}\label{sec_diff}
@@
 %The previous section assumes that all tasks have the same sample size and feature vectors.
-In this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
+We begin by considering the covariate shift setting where both tasks have the same linear model but different population covariance matrices.
 %The different covariates case differs from the same covariates case in two aspects.
 %First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give an estimate on it.
+%In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
+We show the exact asymptotic limit of the excess risk of the HPS estimator in the high-dimensional setting.
 
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
+%By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
+%\begin{align}
+%	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
+%	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
+%\end{align}
+First, we consider the variance. Recall from equation \eqref{Lvar} that the variance equation is equal to $\sigma^2 \cdot \bigtr{\Sigma^{(2)} (\hat\Sigma(a))^{-1}}$.
+In particular, the matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices.
+Thus, the expectation of $\hat{\Sigma}(a)$ is equal to a mixture of both tasks' population covariance matrices, with mixing proportions determined by their sample sizes.
+%To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
  %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
+%\begin{align}
+%	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
+%	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
+%	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
+%\end{align}
+%Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
 %Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
+Intuitively, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on how well ``aligned'' $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are.
 %However, capturing this intuition quantitatively turns out to be technically challenging.
 %The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$)
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$
+To capture this alignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$)
+$$ M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$
 %Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a)\ge \lambda_2(a)\ge \dots\ge \lambda_p(a)$ be the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
+Let $\lambda_1 \ge \lambda_2 \ge \dots\ge \lambda_p $ be the singular values of $M$ in descending order. %By \eqref{assm3}, these singular values satisfy that
+%\begin{equation}\label{assm32}
+%|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
+%\end{equation}
 %for some small constant $0<\tau<1$.
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
+Our first main result is the following theorem on the variance limit, which characterizes the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
 
-\begin{theorem}\label{thm_main_RMT}
+\begin{theorem}[Variance asymptotics under covariate shift]\label{thm_main_RMT}
 %	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
@@
 %	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
+Under Assumption \ref{assm_big1} (recalling $\varphi > 4$), for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
 %equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
 	\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
+		\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 a^2\cdot M^\top M + a_2  }  }}
+		\le \frac{(n_1+n_2)^{\frac 2{\varphi} - \frac 1 2 + c}}{p^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2},
 	\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following system of equations
+	uniformly in all $a\in \R$. Here $(\alpha_1, \alpha_2)$ is the solution of the following system of equations
 	\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
+		\alpha_1 + \alpha_2 = 1- \frac{p}{n_1 + n_2}, \quad
+		\alpha_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 \alpha_1 a^2}{\lambda_i^2 \alpha_1 a^2 + \alpha_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
 	\end{align}
+\end{theorem}
+\todo{changed $a_1, a_2$ to $\alpha_1, \alpha_2$ since they conflict with $a$}
 
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that
+Equation \eqref{lem_cov_shift_eq} thus characterizes the variance of the HPS estimator, up to an error term on the order of $O\big(\frac{\sigma^2}{p^{-1/2}}\big)$ (recall that $\varphi > 4$, $c$ is an arbitrarily small constant, $\frac{p}{n_1+n_2} \in (2 {\tau}, \frac 2 {\tau})$).
+With Assumption \ref{assm_big1},
 $$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
@@
 \paragraph{Illustrative examples.}
-To describe quantitatively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model}, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-%\begin{example}%[Sample sizes]
-%\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
-	Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, we let
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, $$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
-and $\wt \beta^{(i)}$ denotes the $i$-th
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+To describe quantitatively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model},
 
@@
 
-\paragraph{Comparison to other estimators.}
+\paragraph{Comparing HPS to other estimators.}
 
@@
 
-\subsection{Model and covariate shift}
+\subsection{Model shift}\label{sec_sizeratio}
+
+ In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
+However, the two tasks can have different sample sizes $n_1\ne n_2$.
+In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
+We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
+
+\begin{theorem}[Bias-variance asymptotics of HPS estimators under model shift]\label{cor_MTL_loss}
+Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
+Gaussian random variables.
+Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
+\be\label{Lvar_samplesize}
+L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
+\ee
+and
+\begin{align}
+L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
+&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
+	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
+	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
+	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
+	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
+	 \end{align}
+Here we define the functions
+\begin{align*}
+&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
+&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
+\end{align*}
+where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
+\begin{align*}
+\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}.
+%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
+%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)}
+ \end{align*}
+%	In the setting of Example \ref{ex_sample_ratio}, assume that
+%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
+%	(i) both tasks sample sizes are at least $3p$;
+%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
+%%	\be\label{choiceofpara0}
+%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
+%	%\be\label{choiceofpara0}
+%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
+%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
+%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
+%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
+%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
+%	With high probability over the randomness of the input,
+%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
+%	\begin{align}
+%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
+%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
+%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
+%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
+%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
+%	 \end{align}
+%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
+%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
+We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
+	 \end{theorem}
+
+\iffalse
+ We need to state a result for Gaussian matrix ...... Consider
+$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
+In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
+$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
+Then we define the following parameters:
+\begin{align*}
+x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
+\end{align*}
+We have that
+$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
+In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter
+%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
+%where
+$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
+\fi
+
+We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
+The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
+For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
+In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
+On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
+In the setting of Theorem \ref{cor_MTL_loss}, we can write
+\begin{align*}
+L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
+\end{align*}
+where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
+\begin{align}\label{Lbias_idea}
+L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
+\end{align}
+up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
+\begin{align}\nonumber %\label{Lbias_idea2}
+L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
+\end{align}
+It is well-known that the empirical spectral distributions (ESD) of $(Z^{(i)})^\top Z^{(i)}$, $i=1,2$, satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
+From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
+Due to the rotational invariance of multivariate Gaussian distributions,
+%$a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other \cite{nica2006lectures}. Hence
+the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
+In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
+We use that result to obtain a convergence estimate on
+$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
+Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
+We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
+
+We believe that the above argument can be extended to the case without the Gaussian assumption.
+For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
+However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
+Hence we do not pursue this direction in this paper.
+
+\paragraph{Illustrative examples.}
+Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
+$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
+with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations.
+Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
+First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
+This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
+Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
+Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
+
+Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
+$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
+This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
+First, we have positive (resp.
+negative) transfer if and only if $h(\rho)>0$ (resp.
+$h(\rho)<0$).
+Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
+\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
+We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
+\begin{enumerate}
+\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
+
+\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
+
+\begin{itemize}
+\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
+
+\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
+Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
+\end{itemize}
+\end{enumerate}
+Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial
+\be\label{poly2}
+ \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
+Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
+\begin{enumerate}
+\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
+
+\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
+Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
+\end{enumerate}
+
+%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance.
+%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
+\iffalse
+Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
+
+Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
+	\begin{align*}
+		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
+		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
+		= \frac{p}{n_1 + n_2 - p},
+	\end{align*}
+	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
+	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
+	Similarly, we can calculate the bias limit.
+	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
+
+In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
+This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
+The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
+As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
+by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
+The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
+
+{\cor
+For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
+\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
+with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that
+	\begin{align}
+		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
+		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
+			\end{align}
+Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
+\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
+For the bias term,
+}
+
+Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
+For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
+We assume that $n_2$ is fixed for simplicity.
+%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
+The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
+It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
+%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
+%We describe a sketch of the proof.
+By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
+\begin{enumerate}
+	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
+	Intuitively, this regime of $d^2$ always helps task two.
+	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
+	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
+\end{enumerate}
+\fi
+%	\end{example}
+
+\paragraph{Comparing HPS to other estimators.}
+    \begin{align}
+    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
+    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
+    \end{align}
+    and
+    \begin{align}
+    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
+    \end{align}
+    %Moreover, there exists a constant $C_0>0$ such that with high probability,
+    %\be\label{loss_large}
+    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
+    %\ee
+    %with high probability for any small constant $\e>0$.
+
+ With Lemma \ref{fact_tr}, we obtain that w.h.p.,
+\begin{align}
+L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
+\end{align}
+and
+\begin{align}
+L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
+ \end{align}
+
+\todo{merge into prev paragraphs {Simulations.}}
+Second, we validate the result of Example \ref{ex_sample_ratio}.
+Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
+%Again, our estimates are accurate compared to the empirical losses.
+We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$.
+The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
+We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
+On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
+Intuitively, this is because bias increases less for smaller $d^2$.
+
+\subsection{Covariate and model shift}
 

### 2021-07-02 revision_journal/setup.tex
Updates from Overleaf

@@
 \section{Preliminaries}\label{sec_HPS}
-In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
-In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
+We begin by formally defining the data model involving large dimensional random matrices together with the underling assumptions.
+We define the model shift and covariate shift settings, in which we will analyze transfer learning in the next section.
+Then, we describe the estimators for the model using two-layer linear neural networks.
+Finally, we present a bias-variance decomposition of our estimators.
+We explain why this decomposition is crucial for analyzing information transfer and the need for new techniques in the analysis.
+Our setup in this section concerns the case of a single data source.
+Later on in Section \ref{sec_same}, we will extend the setup to the case of multiple data sources.
+%In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
 We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
@@
 \ee
+%$Denote by $\Sig^{(i)} = O_i\Lambda_i O_i^\top$ its eigendecomposition, where $\Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n)$.
+%\be\label{eigen}
+%\Sig^{(i)}, \quad  ,  \quad i=1,2,
+%\ee
+Additionally, We assume that the eigenvalues of $\Sigma^{(i)}$ are bounded between $\tau$ and $1 / \tau$.
+%\begin{equation}\label{assm3}
+%    \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
+%\end{equation}
 
@@
 
+Having defined the data model for each task, next, we describe typical scenarios in transfer learning under our setup.
+We define two settings as follows:
+\begin{itemize}
+    \item \textbf{Covariate shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices but different models.
+    \item \textbf{Model shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices (i.e.
+$\Sigma^{(1)}=\Sigma^{(2)}$) but different models (i.e.
+$\beta^{(1)} \neq \beta^{(2)}$).
+\end{itemize}
+One interesting special case of capturing different models is the following random-effect model, which has been studied in several recent works concerning high-dimensional (single-task) ridge regression \cite{dobriban2018high} and distributed regression \cite{dobriban2020wonder}.
+ %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
+Next, we illustrate how varying them impact the prediction loss.
+%\begin{example}%[Sample sizes]
+%\label{ex_sample_ratio}
+	%We first consider the impact of varying sample sizes.
+	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
+	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
+Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, let
+\begin{align}
+    \beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2, \label{eq_re}
+\end{align}
+where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
+and $\wt \beta^{(i)}$ denotes the $i$-th
+%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
+task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+
 %\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
@@
 
-We describe our estimators that combine the information from both datasets.
+%We describe our estimators that combine the information from both datasets.
 We learn a two-layer linear neural network with parameters $A \in \real^{p\times r}$, $B_1 \in \real^{r}$, and $B_2 \in \real^r$ by minimizing the following optimization objective:
@@
 Additionally, they have been used as a preprocessing step of minimax optimal estimators, under certain conditions of the data \cite{li2020transfer} (see also Section \ref{sec_related} for further discussion of both works).
-%Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{, li2020transfer}:
-%$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
 
-%Given a solution from minimizing $f(A, B)$, denoted by   (which we will specify below), let  denote the HPS estimator for task $i$.
-%The critical questions are:
-%(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-%(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
+\todo{edit the transition here} We show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
+The proof of Proposition \ref{lem_hat_v} can be found in Section \ref{app_iso_cov_prop}.
 
-%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
+\begin{proposition}[Optimum under the random-effect model]\label{lem_hat_v}
+%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
+    Suppose Assumption \ref{assm_big1} and the above random-effect model under equation \eqref{eq_re} holds. %in Example \ref{ex_same_cov} hold.
+    Suppose that for a constant $c_0>0$,
+	\be\label{para_rel}
+	    \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
+	\ee
+    Then we have that for any small constant $c>0$ and large constant $ C>0$,
+	%Let $c$ be a sufficiently small fixed constant.
+	%In the setting of Corollary \ref{cor_MTL_loss},
+%There exists a constant $C>0$ such that
+	\be\label{hatw_add1}
+	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
+	\ee
+\end{proposition}
+In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
+
+%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
+%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
+%More precisely, %we have
+%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
+%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
+%and $\wt \beta^{(i)}$ denotes the $i$-th
+%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
+%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+%We emphasize that unlike Theorem \ref{cor_MTL_loss}, for Proposition \ref{lem_hat_v} we do not assume $\Sigma^{(1)}=\Sigma^{(2)}$ and the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
+%In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
+%\FY{What is known so far about this topic?}
+
+%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.
+
+%{\cor discuss about the bias-variance trade-off}
+%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
+
 \subsection{Bias and variance}
 
-Proposition \ref{prop_large_r} suggests that the two-layer neural network provides information transfer only when $r = 1$.
+%Proposition \ref{prop_large_r} suggests that the two-layer neural network provides information transfer only when $r = 1$.
+
 Next, we provide the bias-variance decomposition of the excess risk under this setting.
@@
 The proof of Proposition \ref{lem_HPS_loss} can be found in Section  \ref{app_firstpf}.
+%Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{, li2020transfer}:
+%$$\hat \beta^{\rm{TL}} := \argmin\left[ \norm{X^{(1)} \beta - Y^{(1)}}^2 + \norm{X^{(2)} \beta - Y^{(2)}}^2\right].$$
 
-\paragraph{Connection to information transfer.}
-To be precise, we say that task one provides a positive transfer to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
+%Given a solution from minimizing $f(A, B)$, denoted by   (which we will specify below), let  denote the HPS estimator for task $i$.
+%The critical questions are:
+%(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
+%(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
+
+%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
+
+\paragraph{Connection to information transfer.} To be precise, we say that task one provides a positive transfer to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
 Otherwise, we say that task one provides a negative transfer to task two.
@@
 
-\paragraph{Bias and variance asymptotics.}
+%\paragraph{Random matrix theory.}
 Building on the above connection, we apply recent developments from random matrix theory to analyze information transfer.
@@
 Second, characterizing variance (cf. equation \eqref{Lvar}) introduces  the issue of \textit{covariate shift}, when $\Sigma^{(1)}$ differs from $\Sigma^{(2)}$.
-More precisely, we define the two settings as follows:
-\begin{itemize}
-    \item \textbf{Model shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices (i.e.
-$\Sigma^{(1)}=\Sigma^{(2)}$) but different models (i.e.
-$\beta^{(1)} \neq \beta^{(2)}$).
-    \item \textbf{Covariate shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices and but different models.
-\end{itemize}
-Our main results in the next section provide precise bias-variance asymptotics under both settings.
-%In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-%\FY{What is known so far about this topic?}
-
-%In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.
-
-%{\cor discuss about the bias-variance trade-off}
-%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-\begin{remark}
-    \todo{clarify overparametrize}
-    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
-\end{remark}
-
-\subsection{Notations}
-
-\todo{
-We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee}
-%for a small constant $\tau>0$.
-
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
+Our main results in the next section provide precise bias-variance asymptotics under either (or both) shift(s).

### 2021-07-03 revision_journal/results.tex
Updates from Overleaf

@@
 
-%The previous section assumes that all tasks have the same sample size and feature vectors.
 We begin by considering the covariate shift setting where both tasks have the same linear model but different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-%In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift''. %which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
 We show the exact asymptotic limit of the excess risk of the HPS estimator in the high-dimensional setting.
@@
 To capture this alignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$)
-$$ M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$
+$$ M \define (\Sigma^{(1)})^{\frac 1 2}(\Sigma^{(2)})^{-\frac 1 2}.$$
 %Let $U\Lambda V^\top$ denote the SVD of $M$ and
@@
 \begin{theorem}[Variance asymptotics under covariate shift]\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
 Under Assumption \ref{assm_big1} (recalling $\varphi > 4$), for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
 	\begin{align}\label{lem_cov_shift_eq}
-		\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 a^2\cdot M^\top M + a_2  }  }}
+		\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{\alpha_1 a^2\cdot M^\top M + \alpha_2}  }}
 		\le \frac{(n_1+n_2)^{\frac 2{\varphi} - \frac 1 2 + c}}{p^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2},
@@
 		\alpha_1 + \alpha_2 = 1- \frac{p}{n_1 + n_2}, \quad
-		\alpha_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 \alpha_1 a^2}{\lambda_i^2 \alpha_1 a^2 + \alpha_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
+		\alpha_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{(a \lambda_i)^2 \alpha_1}{(a \lambda_i)^2 \alpha_1 + \alpha_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
 	\end{align}
@@
 Equation \eqref{lem_cov_shift_eq} thus characterizes the variance of the HPS estimator, up to an error term on the order of $O\big(\frac{\sigma^2}{p^{-1/2}}\big)$ (recall that $\varphi > 4$, $c$ is an arbitrarily small constant, $\frac{p}{n_1+n_2} \in (2 {\tau}, \frac 2 {\tau})$).
-With Assumption \ref{assm_big1},
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
+Our result can be viewed as a generalization of the classical result in Lemma \ref{fact_tr} to the \textit{covariate shift} setting.
+In particular, Lemma \ref{fact_tr} corresponds to a setting where the singular values $\lambda_1,\dots,\lambda_p$ are all equal to one, and $a = 1$.
+Then, the second part of equation \eqref{eq_a12extra} simplifies to
+\[ \alpha_1 + \frac{p}{n_1 + n_2}\cdot \frac{\alpha_1}{\alpha_1 + \alpha_2} = \frac{n_1}{n_1 + n_2}. \]
+By solving the above together with the first part of equation \eqref{eq_a12extra}, we obtain that
+$$\alpha_1 = \frac{n_1}{n_1+n_2},\quad \alpha_2 = \frac{n_2-p}{n_1+ n_2}.$$
+Plugging the above solutions back to the variance limit, we thus find that the limit is equal to
+\begin{align*}
+    \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}} &= \frac{\sigma^2}{n_1 + n_2} \frac{p}{\alpha_1 + \alpha_2} \tag{since the singular values of $M$ are equal to $1$} \\
+    &= \frac{\sigma^2}{n_1 + n_2} \cdot\frac{p (n_1 + n_2)}{n_1 + n_2 - p} \tag{applying $\alpha_1$ and $\alpha_2$ from above} \\
+    &= \frac{\sigma^2 p}{n_1 + n_2 - p},
+\end{align*}
+which is precisely the limit in Lemma \ref{fact_tr}.
+Additionally, the convergence rate in equation \eqref{lem_cov_shift_eq} matches the one in Lemma \ref{fact_tr} for this special case.
+%With Assumption \ref{assm_big1},
+%$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
+%Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$, which we believe to be sharp up to the $(n_1+n_2)^c$ factor.
 Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
 %also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$
-and plug them into \eqref{lem_cov_shift_eq}.
-The proof of Theorem \ref{thm_main_RMT} is based on some recent developments in random matrix theory \cite{Anisotropic}, and will be given in Appendix \ref{appendix RMT} of the supplement \cite{MTL_suppl}.
+%To see this, when $M(a)=0$,
+The proof of Theorem \ref{thm_main_RMT}, which is based on recent developments in random matrix theory \cite{Anisotropic}, can be found in Section \ref{appendix RMT}.
 %For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
@@
 
-\paragraph{Illustrative examples.}
-To describe quantitatively the bias-variance tradeoff phenomenon and the effect of varying sample sizes on the predication loss, we consider a \emph{random-effect model},
+Second, we consider the bias.
+Note that the setting where $\beta_1 = \beta_2$ can be viewed as a special case of the random-effect model with $d = 0$, thus, assuming that $\norm{\beta_1}_2^2 \ge \sigma^2 / p^{1/2 - c_0}$ for a small constant $c_0 > 0$, we have that $\hat B_1 / \hat B_2$ is equal to $1$ plus lower-order terms that scale to zero as $p$ goes to infinity (see equation \eqref{hatw_add1} for the precise scaling).
+In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
+Thus, the bias equation $L_{\bias}(\hat B_1 / \hat B_2)$ is equal to $0$ plus the above lower-order terms.
+We summarize this discussion in the following corollary:
 
-%\begin{example} %[Covariate shift]
-%\label{ex_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds.
-In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
-Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
-$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
-where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
+\begin{corollary}[Asymptotics for HPS under covariate shift]\label{cor_hps_cov}
+    Under Assumption \ref{assm_big1}, suppose further that $\beta_1 = \beta_2$ and $\norm{\beta_1}^2_2 \ge \frac{\sigma^2}{p^{1/2 - c_0}}$ for a constant $c_0 > 0$.
+    Then, for any constant $c > 0$, the following estimate on the excess risk of the HPS estimator holds w.h.p.
+    \begin{align}
+        \bigabs{L(\hat{\beta}_2^{\MTL}) - \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac{1}{\alpha_1 M^{\top} M + \alpha_2}}}
+        \le
+        \OO\bigbrace{\frac{(n_1+n_2)^{\frac 2{\varphi} - \frac 1 2 + c}}{p^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}
+        + p^{-c_0 + 2c}},
+    \end{align}
+    where $\alpha_1$ and $\alpha_2$ are the solutions of equation \eqref{eq_a12extra} after taking $a = 1$.
+\end{corollary}
+
+Next, we illustrate the result of Corollary \ref{cor_hps_cov} in several examples.
+
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
+		\caption{Example \ref{ex_covshift}}
+		\label{fig_covariate}
+	\end{subfigure}
+\end{figure}
+
+\begin{example}[Whether or not covariate shift helps depends on sample sizes]
+    %However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
+    Our first example illustrates that the effect of covariate shift depends on the sample sizes of each dataset in an intricate manner.
+    Let $\lambda > 0$ be a variable that captures the degree of covariate shift: higher values imply worse covariate shift.
+    Suppose that half of the singular values of $M$ are equal to $\lambda$ while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
+When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
+%while as As $\lambda$ increases, the severity of covariate shift increases.
+We claim the following dichotomy.
+\begin{enumerate}
+	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
+	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
+\end{enumerate}
+We explain why the above dichotomy happens. We can write the variance limit as
+$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
+When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
+$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
+where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
+\begin{align*}
+\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
+\end{align*}
+%in this example is equal to
+%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
+%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
+%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
+%\begin{align*}
+%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
+%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
+%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
+%\end{align*}
+%\begin{align*}
+%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
+%\end{align*}
+%where $g(\lambda, a_1) \ge 0$.
+%and can be derived from algebraic calculations (details omitted).
+We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
+In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
+\begin{align*}
+ \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
+\end{align*}
+%\begin{align*}
+% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
+%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
+%\end{align*}
+This implies $n_1>n_2$.
+The other direction follows from a similar argument.
+% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
+Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
+%\end{example}
+
+\todo{draw a connection to \citet{david2010impossibility}}
+\end{example}
+
+%\paragraph{Illustrative examples.}
+%Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
+%$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
+%where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
+\begin{example}[Covariate shift hurts more under imbalanced sample sizes]
 We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
@@
 is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
-
+\end{example}
 %Hence we get that
@@
 %Our first observation is that:
-However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
-We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$.
-In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
-When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
-%while as As $\lambda$ increases, the severity of covariate shift increases.
-We claim the following dichotomy.
-\begin{enumerate}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-\end{enumerate}
-We explain why the above dichotomy happens. We can write the variance limit as
-$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
-When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
-$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
-where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
-\begin{align*}
-\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
-\end{align*}
-%in this example is equal to
-%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
-%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%where $g(\lambda, a_1) \ge 0$.
-%and can be derived from algebraic calculations (details omitted).
-We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
-In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
-\begin{align*}
- \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
-\end{align*}
-%\begin{align*}
-% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-%\end{align*}
-This implies $n_1>n_2$.
-The other direction follows from a similar argument.
-% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
-%\end{example}
-
-\todo{draw a connection to \citet{david2010impossibility}}
 

### 2021-07-03 revision_journal/setup.tex
Updates from Overleaf

@@
 		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
-		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
+		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|\Sigma\|_{op} \right) \]
 		with high probability for any small constant $\e>0$.
 \end{lemma}
+\todo{the scaling $\sqrt{n_2}$ above doesn't seem correct}
+
  %The above result has a long history in random matrix theory.

### 2021-07-05 revision_journal/intro.tex
Updates from Overleaf

@@
 
+These previous works mainly consider cases where there is only one high-dimensional sample covariance matrix involved.
+.........
 In the single task case, if the data is Gaussian distributed, then precise variance can be derived immediately from properties of Wishart distribution.
@@
 Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature. 
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
+%These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
+%We also extend the techniques in ?, which is one contribution of this work.
+
+There exists another method to derive the asymptotic variance limit using free addition in free probability theory \cite{nica2006lectures}.
+We do not take this procedure because this method is not completely justified in the general non-Gaussian setting (in the sense that it is hard to establish rigorously the free independence between two sample covariance matrices with non-diagonal covariate shift).
+Furthermore, our techniques provide almost sharp convergence rates to the asymptotic limit, which cannot be given by free probability theory.
 To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
+
+On the other hand, the bias limit is much harder to derive. However, when the data is Gaussian distributed and there is no covariante shift, we can use recent results in ... to derive the bias limit.
+
 %\HZ{can you please add a discussion of the related work from RMT?}

### 2021-07-05 revision_journal/results.tex
Updates from Overleaf

@@
 
-Next, we illustrate the result of Corollary \ref{cor_hps_cov} in several examples.
-
 \begin{figure}[!t]
@@
 		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
-		\caption{Example \ref{ex_covshift}}
-		\label{fig_covariate}
+		\caption{HPS estimator under covariate shift}
+		\label{fig_sec3_covariate}
 	\end{subfigure}
+	\caption{The dimension $p = 200$, $n_2 = 800$, and the noise variance $\sigma^2 = 1/4$.}
 \end{figure}
 
-\begin{example}[Whether or not covariate shift helps depends on sample sizes]
+\subsubsection{Illustrative examples}
+
+Next, we illustrate the result of Corollary \ref{cor_hps_cov} in several examples.
+
+\begin{example}[Does covariate shift help or hurt information transfer?]
     %However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
     Our first example illustrates that the effect of covariate shift depends on the sample sizes of each dataset in an intricate manner.
-    Let $\lambda > 0$ be a variable that captures the degree of covariate shift: higher values imply worse covariate shift.
-    Suppose that half of the singular values of $M$ are equal to $\lambda$ while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
-When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
-%while as As $\lambda$ increases, the severity of covariate shift increases.
-We claim the following dichotomy.
+    While the folklore belief is that transferring from a covariate-shifted distribution performs worse than an identical distribution, we show that, surprisingly, the former can sometimes outperform the latter.
+
+    We first describe a setting for modeling covariate shift.
+    Let $\cS$ be the set of positive definite matrices $M^{\top} M$ such that for $i = 1,2,\dots,\floor{\frac p 2}$, $\lambda_{p - i}  = \frac 1 {\lambda_i}$, where $\lambda_1 \ge \lambda_2 \ge \cdots \ge \lambda_p$ are the eigenvalues of $M$.
+    Under this setting, we ask: suppose that the sample sizes $n_1$ and $n_2$ are both fixed, which $M$ provides the best ``transfer'' in the sense of HPS estimator's excess risk?
+    We observe a dichotomy that depends on whether or not $n_1$ is greater than $n_2$.
+    \begin{claim}\label{claim_dichotomy}
+        Let $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
+        Suppose that $n_1$ and $n_2$ are both fixed.
+        Within the set of all possible covariate shift matrix $M$ described above, the following dichotomy holds:
         \begin{enumerate}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
+	        \item If $n_1 \ge n_2$, then $g(M)$ is minimized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
+	        \item If $n_1 < n_2$, then $g(M)$ is maximized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
         \end{enumerate}
-We explain why the above dichotomy happens. We can write the variance limit as
-$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
+    \end{claim}
+
+\begin{proof}
+    We explain why the above dichotomy happens. We can write $g(M)$ for any $M \in \cS$ as
+    $$g(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right).$$
     When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
-$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
-where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
+    $$g(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma},$$
+    where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $\alpha_1 + \alpha_2 = 1-\gamma$, through a direct calculation we find that %we can calculate that
     \begin{align*}
-\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
+        g(M) - g(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
+        &= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 \alpha_1 \left[ \alpha_1 - \alpha_2\right] }{[\alpha_1 + \lambda_i^2 \alpha_2][\lambda_i^2 \alpha_1 + \alpha_2]} .
     \end{align*}
@@
     %and can be derived from algebraic calculations (details omitted).
-We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
-In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
+    We claim that $\alpha_1 > \alpha_2$ if and only if $n_1 > n_2$, which then explains the dichotomy.
+    In fact, if $\alpha_1 > \alpha_2$, then the first part of equation \eqref{eq_a12extra} gives that $\alpha_1 > (1-\gamma)/2$.
+    The second part of equation \eqref{eq_a12extra} gives that
     \begin{align*}
- \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
+     \frac{n_1}{n_1 + n_2} &> \alpha_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
     \end{align*}
@@
     %\end{align*}
-This implies $n_1>n_2$.
+    This is equivalent to $n_1>n_2$.
 The other direction follows from a similar argument.
@@
     %\end{example}
+\end{proof}
 
-\todo{draw a connection to \citet{david2010impossibility}}
+Figure \ref{fig_sec3_covariate} illustrates a special case where $\lambda_1 = \cdots = \lambda_{\floor{p /2}} = \lambda > 0$ for $M^{\top}M$ and the rest of the eigenvalues are all equal to $1 / \lambda$.
+Thus, $\lambda > 0$ captures the degree of covariate shift: higher $\lambda$ implies worse covariate shift.
+We observe that our theoretical estimates using Corollary \ref{cor_hps_cov} matches the empirical risks incredibly accurately.
+As a result, we indeed observe the dichotomy shown in Claim \ref{claim_dichotomy}.
 \end{example}
@@
 \begin{example}[Covariate shift hurts more under imbalanced sample sizes]
-We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
-\end{align*}
-%belong to the following bounded set.
-%Let $\lambda_i$ be the $i$-th singular value of $M$.
-%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-%\vspace{-0.025in}
-%{\small}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-%\begin{proposition}[Covariate shift]\label{prop_covariate}
+Our second example illustrates that the effect of covariate shift worsens as the sample size of task one increases.
+We consider a set of covariate shift matrices $M^{\top} M$ whose determinant are all equal to one, and the eigenvalues are bounded between $\tau^2$ and $1 / \tau^2$.
+Let $\cS$ denote the set of $M\in\real^{p\times p}$ such that $M^{\top} M$ satisfies both conditions.
+%\begin{align*}
+%		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
+%\end{align*}
+\begin{claim}\label{prop_covariate}
 %	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
 %	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-%	We have that
-%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
-%\end{proposition}
-%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
-Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix.
-%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-%Let
-%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$
-%We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
-%\be \nonumber
-%\begin{split}
-%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
-%\end{split}
-%\ee
-%with high probability for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-%
-%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-%\begin{align}\label{gvar_extra}
-%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-%\end{align}
-In fact, from equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
- a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
-\ee
-Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that
-%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-%\begin{align}\label{approximateteM}
-%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-%\end{align}
-%where
-$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
+    Recall that $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
+	We have the following relation between $g(\id_{p \times p})$ and the rest of $g(M)$ for any $M \in\cS$:
+	\[ g(\id_{p\times p}) \le \bigbrace{1+ \bigo{\frac{n_2}{n_1}  }} g(M), \text{ for any } M \in \cS. \]
+\end{claim}
+\begin{proof}
+    From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $\alpha_1$ and $\alpha_2$ for any $M\in \cS$:
+    \begin{align*}%\label{est_a12extra}
+        \frac{n_1 - p}{n_1 + n_2} < \alpha_1 <  \frac{n_1 + n_2 - p}{n_1 + n_2},\quad \alpha_2 < \frac{n_2}{n_1 + n_2}.
+    \end{align*}
+    Applying the above into $g(M)$, and using the fact that the minimum eigenvalue of $ M^\top M$ is at least $\tau^2$, we obtain
+    \begin{align}\label{approximateteM}
+    \left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
+    \end{align}
+    where
+    $$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
     %With these two bounds, we can easily conclude \eqref{approxteM}. 
@@
     $$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
+    is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
+    \be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
+
+    On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
+    \begin{align}\label{gvar_extra2}
+    \begin{split}
+    g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
+    &\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
+    \end{split}
+    \end{align}
+    Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
+    %, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+\end{proof}
+\todo{draw a connection to \citet{david2010impossibility}}
 \end{example}
-%Hence we get that
-%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-%
-%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-%\begin{align}\label{gvar_extra2}
-%\begin{split}
-%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-%\end{split}
-%\end{align}
-%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-%\end{proof}
 
-\iffalse
-For large enough $p$,
-%in the left hand side of equation \eqref{lem_cov_shift_eq}:
-\begin{align*}
-	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
-\end{align*}
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
-\fi
-
-%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}.
-%Our first observation is that:
-
-\iffalse
-%FY: Below was the word explanation. I still think the above simple proof is clearer.
-In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
-The other case when $n_1 < n_2$ is similar.
-A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
-If $n_1< n_2$, then $f(\lambda)< f(1)$.
-\fi
-
-\paragraph{Comparing HPS to other estimators.}
+\subsubsection{Comparing HPS to other estimators}
 

### 2021-07-06 revision_journal/results.tex
Updates from Overleaf

@@
 Plugging the above solutions back to the variance limit, we thus find that the limit is equal to
-\begin{align*}
-    \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}} &= \frac{\sigma^2}{n_1 + n_2} \frac{p}{\alpha_1 + \alpha_2} \tag{since the singular values of $M$ are equal to $1$} \\
-    &= \frac{\sigma^2}{n_1 + n_2} \cdot\frac{p (n_1 + n_2)}{n_1 + n_2 - p} \tag{applying $\alpha_1$ and $\alpha_2$ from above} \\
-    &= \frac{\sigma^2 p}{n_1 + n_2 - p},
-\end{align*}
+\begin{align}
+    \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}} &= \frac{\sigma^2}{n_1 + n_2} \frac{p}{\alpha_1 + \alpha_2} \tag{since the singular values of $M$ are equal to $1$} \nonumber \\
+    &= \frac{\sigma^2}{n_1 + n_2} \cdot\frac{p (n_1 + n_2)}{n_1 + n_2 - p} \tag{applying $\alpha_1$ and $\alpha_2$ from above} \nonumber \\
+    &= \frac{\sigma^2 p}{n_1 + n_2 - p}, \label{g_id}
+\end{align}
 which is precisely the limit in Lemma \ref{fact_tr}.
@@
 %where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
-\begin{example}[Covariate shift hurts more under imbalanced sample sizes]
+\begin{example}
 Our second example illustrates that the effect of covariate shift worsens as the sample size of task one increases.
@@
 %\end{align*}
-\begin{claim}\label{prop_covariate}
+\begin{claim}[Identical covariance provides approximately optimal transfer under imbalanced dataset sizes]\label{prop_covariate}
 %	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
@@
 	We have the following relation between $g(\id_{p \times p})$ and the rest of $g(M)$ for any $M \in\cS$:
-	\[ g(\id_{p\times p}) \le \bigbrace{1+ \bigo{\frac{n_2}{n_1}  }} g(M), \text{ for any } M \in \cS. \]
+	\begin{align} g(\id_{p\times p}) \le \bigbrace{1+ {\frac{n_2}{\tau^2\cdot n_1}  }} g(M), \text{ for any } M \in \cS. \label{eq_claim_id}
+	\end{align}
 \end{claim}
 \begin{proof}
-    From equation \eqref{eq_a12extra}, it is easy to obtain the following estimates on $\alpha_1$ and $\alpha_2$ for any $M\in \cS$:
-    \begin{align*}%\label{est_a12extra}
-        \frac{n_1 - p}{n_1 + n_2} < \alpha_1 <  \frac{n_1 + n_2 - p}{n_1 + n_2},\quad \alpha_2 < \frac{n_2}{n_1 + n_2}.
+    We can write down the trace of $(\alpha_1 M^{\top} M + \alpha_2)^{-1}$ using the eigenvalues of $M^{\top} M$ as follows:
+    \begin{align*}
+        (\alpha_1 M^{\top} M + \alpha_2)^{-1} &= \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2} \\
+        &\ge \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2 \cdot {\lambda_i^2} / {\tau^2}} \tag{since $\lambda_i \le \tau$, for any $i$} \\
+        &= \frac 1 {\alpha_1 + \alpha_2 / \tau^2} \sum_{i=1}^ p \frac 1 {\lambda_i^2} \\
+        &\ge \frac 1 {\alpha_1 + \alpha_2 /\tau^2} p\cdot \bigbrace{\prod_{i=1}^p \frac 1 {\lambda_i^2}}^{1/ p} \tag{by the AM-GM inequality} \\
+        &= \frac{p}{\alpha_1 + \alpha_2 / \tau^2} \tag{since $\prod_{i=1}^p \lambda_i^2 = \det(M^{\top} M) = 1$}
     \end{align*}
-    Applying the above into $g(M)$, and using the fact that the minimum eigenvalue of $ M^\top M$ is at least $\tau^2$, we obtain
-    \begin{align}\label{approximateteM}
-    \left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
+    Next, recall from equation \eqref{g_id} that
+    $g(\id_{p\times p}) = \frac{\sigma^2 p}{n_1 + n_2 - p}$.
+    Thus, equation \eqref{eq_claim_id} follows if we show that (after rearranging terms)
+    \begin{align}
+        \frac{n_1 + n_2}{n_1 + n_2 - p} \cdot \frac 1 {\alpha_1 + \frac{\alpha_2}{\tau^2}} \le 1 + \frac{n_2}{\tau^2 \cdot n_1}. \label{eq_claim_id_step}
     \end{align}
-    where
-    $$h(M_0):=\frac{\sigma^2}{(\rho_1+\rho_2)a_1(M_0)}\cdot \frac1p\tr\left( \frac{1}{M_0^\top M_0}\right) .$$
-    %With these two bounds, we can easily conclude \eqref{approxteM}. 
-    %
-    %We have that the test error satisfies
-    %\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-    %where $\lambda_p$ is the smallest singular value of $p$ and
-    %$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-    %Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-    By AM-GM inequality, we observe that 
-    $$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-    is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i\le \mu^p$. Hence we get that 
-    \be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-
-    On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-    \begin{align}\label{gvar_extra2}
-    \begin{split}
-    g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-    &\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-    \end{split}
-    \end{align}
-    Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-    %, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
+    From the second part of equation \eqref{eq_a12extra}, we have that
+    \begin{align*}
+        \frac{n_1} {n_1 + n_2} &= \alpha_1 + \frac 1 {n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2\alpha_1}{\lambda_i^2\alpha_1 + \alpha_2}} \\
+        &< \alpha_1 + \frac p {n_1 + n_2}.
+    \end{align*}
+    Thus, $\alpha_1 > \frac{n_1 - p}{n_1 + n_2}$, which implies that $\alpha_2 < \frac{n_2}{n_1 + n_2}$.
+    Hence, $\alpha_1 + \frac{\alpha_2}{\tau^2} = 1 - \frac{p}{n_1 + n_2} - \alpha_2 + \frac{\alpha_2}{\tau^2} \le 1 - \frac{p}{n_1 + n_2} + \frac{n_2}{n_1 + n_2} \frac 1 {\tau^2}$, which implies
+    equation \eqref{eq_claim_id_step} by straightforward calculations.
+    Thus, the proof is complete.
 \end{proof}

### 2021-07-07 revision_journal/exp.tex
Updates from Overleaf

@@
 
-%\subsection{Comparison between the averaging and HPS estimators}
+\subsection{Comparing HPS to other estimators}
+
+    \begin{align}
+    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
+    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
+    \end{align}
+    and
+    \begin{align}
+    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
+    \end{align}
+    %Moreover, there exists a constant $C_0>0$ such that with high probability,
+    %\be\label{loss_large}
+    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
+    %\ee
+    %with high probability for any small constant $\e>0$.
+
+ With Lemma \ref{fact_tr}, we obtain that w.h.p.,
+\begin{align}
+L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
+\end{align}
+and
+\begin{align}
+L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
+ \end{align}
+
+\todo{merge into previous paragraphs {Simulations.}}
+Finally, we validate the result of Example \ref{ex_covshift}.
+Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
+Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
+We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
+The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
+
+%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
+
 \subsection{Regression tasks}

### 2021-07-07 revision_journal/intro.tex
Updates from Overleaf

--- 2021-06-30 revision_journal/intro.tex
@@
 \end{itemize}
+\begin{remark}
+    \todo{clarify overparametrize}
+    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
+\end{remark}
 
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to sample covariance matrices with arbitrary covariance.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
+These previous works mainly consider cases where there is only one high-dimensional sample covariance matrix involved. %need to check 
+In the single task case, if the data is Gaussian, then the precise variance limit can be derived directly from properties of Wishart distribution.
+In the high-dimensional setting, the eigenvalues of Wishart matrices satisfy the famous Marchenko–Pastur (MP) law \cite{MP}, whose Stieltjes transform characterizes the variance limit.
+Furthermore, it is well-known that the MP law holds universally regardless of the detailed data distribution \cite{bai2010spectral}.
+\cite{isotropic} obtained a sharp converge rate of the empirical spectral distribution (ESD) to the MP law for sample covariance matrices with isotropic covariance.
+\cite{Anisotropic,DY} later extended this result to sample covariance matrices with arbitrary population covariances.
+These results are proved by establishing certain optimal convergence estimates of the Stieltjes transforms of sample covariance matrices, which are referred to as \emph{local laws} in the random matrix theory literature.
+We refer the reader to \cite{erdos2017dynamical} and the references therein for a detailed review of related concepts.
+In this paper, we extend these techniques to the two-task setting and prove the local law for the sum of two sample covariance matrices with an arbitrary covariate shift, which is one technical contribution of this work.
+From the local law, we can derive the variance limit with a precise dependence on the singular values of the covariate shift matrix.
+
+%Our proof techniques use the so-called local law of random matrices, a recent development in the random matrix theory literature, called the \emph{local law} of
+
+%These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
+%We also extend the techniques in ?, which is one contribution of this work.
+
+%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in theory.
+
+There is another method to derive the asymptotic variance limit using free addition in free probability theory \cite{nica2006lectures}.
+We do not take this procedure because this method is not completely justified in the general non-Gaussian setting with non-diagonal covariate shift matrix.
+%(in the sense that it is hard to establish rigorously the free independence between two sample covariance matrices). 
+Furthermore, our techniques provide almost sharp convergence rates to the asymptotic limit, which is not given by free probability techniques.
+
+On the other hand, the bias limit is much harder to derive.
+However, when the data is Gaussian distributed and there is no covariante shift, we can use recent results in ...
+to derive the bias limit.
+To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for cases without covariate shifts.
+
 %\HZ{can you please add a discussion of the related work from RMT?}

### 2021-07-07 revision_journal/results.tex
Updates from Overleaf

@@
 On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
-%Here case (ii) is actually more general than (i)
 
@@
 
-%By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-%\begin{align}
-%	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-%	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-%\end{align}
 First, we consider the variance. Recall from equation \eqref{Lvar} that the variance equation is equal to $\sigma^2 \cdot \bigtr{\Sigma^{(2)} (\hat\Sigma(a))^{-1}}$.
@@
 Thus, the expectation of $\hat{\Sigma}(a)$ is equal to a mixture of both tasks' population covariance matrices, with mixing proportions determined by their sample sizes.
-%To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-%\begin{align}
-%	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-%	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-%	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-%\end{align}
-%Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
 Intuitively, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on how well ``aligned'' $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
 To capture this alignment quantitatively, we introduce the covariate shift matrix %(rescaled by $a$)
 $$ M \define (\Sigma^{(1)})^{\frac 1 2}(\Sigma^{(2)})^{-\frac 1 2}.$$
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1 \ge \lambda_2 \ge \dots\ge \lambda_p $ be the singular values of $M$ in descending order. %By \eqref{assm3}, these singular values satisfy that
-%\begin{equation}\label{assm32}
-%|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-%\end{equation}
-%for some small constant $0<\tau<1$.
+Let $\lambda_1 \ge \lambda_2 \ge \dots\ge \lambda_p $ be the singular values of $M$ in descending order.
 Our first main result is the following theorem on the variance limit, which characterizes the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
@@
 %also extends  to the inverse of the sum of two sample covariance matrices.
-%To see this, when $M(a)=0$,
 The proof of Theorem \ref{thm_main_RMT}, which is based on recent developments in random matrix theory \cite{Anisotropic}, can be found in Section \ref{appendix RMT}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
 
@@
 
-\begin{corollary}[Asymptotics for HPS under covariate shift]\label{cor_hps_cov}
+\begin{corollary}[Excess risk of HPS under covariate shift]\label{cor_hps_cov}
     Under Assumption \ref{assm_big1}, suppose further that $\beta_1 = \beta_2$ and $\norm{\beta_1}^2_2 \ge \frac{\sigma^2}{p^{1/2 - c_0}}$ for a constant $c_0 > 0$.
@@
 		\centering
+		\includegraphics[width=0.9\textwidth]{figures/verify_covariate_shift.eps}
+		\caption{Verify variance asymptotics in finite dimensions}
+		\label{fig_sec3_covariate}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
 		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
@@
 	\end{subfigure}
-	\caption{The dimension $p = 200$, $n_2 = 800$, and the noise variance $\sigma^2 = 1/4$.}
+	\caption{Figure \ref{fig_sec3_covariate}: we verify that Theorem \ref{thm_main_RMT} provides incredibly accurate estimates of the empirical variance under various finite sample sizes and dimensions.
+	Figure \ref{fig_sec3_covariate}: We illustrate an intriguing dichotomy between covariate shift and sample size ratio: The dimension $p = 200$, $n_2 = 800$, and the noise variance $\sigma^2 = 1/4$.}
 \end{figure}
 
-\subsubsection{Illustrative examples}
-
+\paragraph{Illustrative examples.}
 Next, we illustrate the result of Corollary \ref{cor_hps_cov} in several examples.
@@
 \begin{example}[Does covariate shift help or hurt information transfer?]
-    %However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
     Our first example illustrates that the effect of covariate shift depends on the sample sizes of each dataset in an intricate manner.
@@
     $$g(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma},$$
-    where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $\alpha_1 + \alpha_2 = 1-\gamma$, through a direct calculation we find that %we can calculate that
+    where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $\alpha_1 + \alpha_2 = 1-\gamma$, through a direct calculation we find that
     \begin{align*}
@@
 As a result, we indeed observe the dichotomy shown in Claim \ref{claim_dichotomy}.
+Furthermore, for higher $\lambda$, HPS' excess risk decreases slower--indicating a worse rate of ``transfer'' from task one. 
+As a remark, the classical work of \citet{david2010impossibility} have likewise shown impossibility results for transfer learning under covariate shift in a classification setting.
+By contrast, our analysis applies to a (high-dimensional) regression setting.
 \end{example}
 
-%\paragraph{Illustrative examples.}
-%Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
-%$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
-%where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
 \begin{example}
@@
 Let $\cS$ denote the set of $M\in\real^{p\times p}$ such that $M^{\top} M$ satisfies both conditions.
-%\begin{align*}
-%		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
-%\end{align*}
 \begin{claim}[Identical covariance provides approximately optimal transfer under imbalanced dataset sizes]\label{prop_covariate}
-%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
     Recall that $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
-	We have the following relation between $g(\id_{p \times p})$ and the rest of $g(M)$ for any $M \in\cS$:
-	\begin{align} g(\id_{p\times p}) \le \bigbrace{1+ {\frac{n_2}{\tau^2\cdot n_1}  }} g(M), \text{ for any } M \in \cS. \label{eq_claim_id}
+	We have the following result regarding $g(\id_{p \times p})$:
+	\begin{align} g(\id_{p\times p}) \le \bigbrace{1+ {\frac{n_2}{\tau^2 n_1}  }} g(M), \text{ for any } M \in \cS. \label{eq_claim_id}
 	\end{align}
@@
         (\alpha_1 M^{\top} M + \alpha_2)^{-1} &= \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2} \\
-        &\ge \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2 \cdot {\lambda_i^2} / {\tau^2}} \tag{since $\lambda_i \le \tau$, for any $i$} \\
+        &\ge \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2 \cdot {\lambda_i^2} / {\tau^2}} \tag{since $\lambda_i \ge \tau$, for any $i$} \\
         &= \frac 1 {\alpha_1 + \alpha_2 / \tau^2} \sum_{i=1}^ p \frac 1 {\lambda_i^2} \\
@@
 \end{proof}
-\todo{draw a connection to \citet{david2010impossibility}}
+As a corollary of Claim \ref{prop_covariate}, when $n_1$ is much larger than $n_2 / \tau^2$, the excess risk of HPS is approximately optimal in the set of all possible $M\in\cS$ when there is no covariate shift between dataset one and two.
 \end{example}
-
-\subsubsection{Comparing HPS to other estimators}
-
-\todo{merge into previous paragraphs {Simulations.}}
-Finally, we validate the result of Example \ref{ex_covshift}.
-Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
-The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
-
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
-
-%Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
 
@@
 
-\begin{theorem}[Bias-variance asymptotics of HPS estimators under model shift]\label{cor_MTL_loss}
+\begin{theorem}[Excess risk of HPS under model shift]\label{cor_MTL_loss}
 Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
@@
 
-\paragraph{Comparing HPS to other estimators.}
-    \begin{align}
-    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
-    \end{align}
-    and
-    \begin{align}
-    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-    \end{align}
-    %Moreover, there exists a constant $C_0>0$ such that with high probability,
-    %\be\label{loss_large}
-    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-    %\ee
-    %with high probability for any small constant $\e>0$.
-
- With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-\end{align}
-and
-\begin{align}
-L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
- \end{align}
+%\paragraph{Comparing HPS to other estimators.}
 

### 2021-07-08 revision_journal/exp.tex
finish sec 3.1

--- 2021-07-02 revision_journal/exp.tex
@@
 
-%\subsection{Comparison between the averaging and HPS estimators}
-\subsection{Regression tasks}
+\subsection{Evaluating HPS under model and covariate shifts}
 
-\subsection{Text classification tasks}
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.98\textwidth]{figures/compare_risk_covariate_shift.eps}
+		\caption{Covariate shift}
+		\label{fig_sec5_covariate}
+	\end{subfigure}
+	\caption{Comparing HPS to several natural estimators for transfer learning.
+We find that HPS enjoys superior performance under covariate and/or model shifts.
+The results are averaged over five random seeds.}
+	\label{fig_sec51}
+\end{figure}
+
+We show that HPS estimators enjoy superior empirical performance compared to several natural transfer learning estimators.
+We consider the following estimators for this comparative study:
+\begin{itemize}
+    \item {\bf Averaging estimator (AVG):} given two tasks, take a convex combination of their OLS estimators $b \cdot \hat{\beta}^{\STL}_1 + (1 - b) \cdot \hat{\beta}^{\STL}_2$.
+    \item {\bf STL estimator (STL):} simply use the OLS estimator of task two $\hat{\beta}^{\STL}_2$ without using task one's data.
+    \item {\bf Transfer learning estimator (TL):} simply use the OLS estimator of task one $\hat{\beta}^{\STL}_1$ without using task two's data.
+\end{itemize}
+
+Figure \ref{fig_sec51} shows the result under covariate and/or model shifts.
+Figure \ref{fig_sec5_covariate} considers the same example as Figure \ref{fig_sec31}.
+%    \begin{align}
+%    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+%    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
+%    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
+%    \end{align}
+%    and
+%    \begin{align}
+%    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
+%    \end{align}
+    %Moreover, there exists a constant $C_0>0$ such that with high probability,
+    %\be\label{loss_large}
+    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
+    %\ee
+    %with high probability for any small constant $\e>0$.
+
+ %With Lemma \ref{fact_tr}, we obtain that w.h.p.,
+%\begin{align}
+%L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
+%\end{align}
+%and
+%\begin{align}
+%L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
+%&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
+% \end{align}
+
+\todo{merge into previous paragraphs {Simulations.}}
+Finally, we validate the result of Example \ref{ex_covshift}.
+Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
+Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
+We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
+The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
+
+%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
+
+\subsection{Implications for regression methods}
+
+\subsection{Implications for text classification}
 Our results and simulations are all in the high-dimensional linear regression setting.

### 2021-07-08 revision_journal/intro.tex
finish sec 3.1

@@
 
-These previous works mainly consider cases where there is only one high-dimensional sample covariance matrix involved. %need to check 
+These previous works mainly consider cases with only one high-dimensional sample covariance matrix involved. %need to check 
 In the single task case, if the data is Gaussian, then the precise variance limit can be derived directly from properties of Wishart distribution.
@@
 We refer the reader to \cite{erdos2017dynamical} and the references therein for a detailed review of related concepts.
-In this paper, we extend these techniques to the two-task setting and prove the local law for the sum of two sample covariance matrices with an arbitrary covariate shift, which is one technical contribution of this work.
+We extend these techniques to the two-task setting and prove a local law for the sum of two sample covariance matrices with an arbitrary covariate shift, which is one technical contribution of this work.
 From the local law, we can derive the variance limit with a precise dependence on the singular values of the covariate shift matrix.
@@
 
-On the other hand, the bias limit is much harder to derive.
-However, when the data is Gaussian distributed and there is no covariante shift, we can use recent results in ...
-to derive the bias limit.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for cases without covariate shifts.
+On the other hand, the bias limit is much harder to study, and its exact dependence on the sample ratio and the covariate shift matrix is still an open problem in random matrix theory in the most general setting.
+However, when the data is Gaussian distributed and there is no covariante shift, we can use recent results in \cite{BES_free1,BES_free2} to derive the bias limit.
+To the best of our knowledge, we are not aware of any previous result in the high-dimensional setting, even for two sample covariance matrices with isotropic population covariances and the same sample size.
+
+%previous results in the multi-task case, even for cases without covariate shifts.
 

### 2021-07-08 revision_journal/intro.tex
sec 4 wip

@@
 
-On the other hand, the bias limit is much harder to study, and its exact dependence on the sample ratio and the covariate shift matrix is still an open problem in random matrix theory in the most general setting.
-However, when the data is Gaussian distributed and there is no covariante shift, we can use recent results in \cite{BES_free1,BES_free2} to derive the bias limit.
-To the best of our knowledge, we are not aware of any previous result in the high-dimensional setting, even for two sample covariance matrices with isotropic population covariances and the same sample size.
+On the other hand, the bias limit is much harder to study, and its dependence on the sample ratio and the covariate shift is still an open problem in random matrix theory in the most general setting.
+However, when the data is Gaussian distributed and the two tasks have the same population covariance, we find a way to calculate the exact bias limit using free probability techniques.
+Leveraging on the recent results \cite{BES_free1,BES_free2}, we can obtain a sharp convergence rate to the bias limit.
+To the best of our knowledge, we are not aware of any previous result on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same sample size.
 

### 2021-07-08 revision_journal/multitask.tex
reorg wip
update intro wip
Updates from Overleaf
sec 4 wip

@@
-\section{Asymptotics for Multiple Tasks}\label{sec_same}
+\section{Extension to multiple data sources}\label{sec_same}
 
@@
 
-Hard parameter sharing is a commonly used architecture in multi-task learning.
+%Hard parameter sharing is a commonly used architecture in multi-task learning.
 However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning.
@@
 
-\vspace{5pt}
-\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
+Our setup and the results in Section \ref{sec_main} are both for transferring from one data source.
+This section extends our setup to transfer learning from multiple data sources.
+We focus on a natural setting where all the tasks have the same covariates but different labels.
+
+\paragraph{Data model.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
 The label vector of the $i$-th task follows a linear model
-$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
-We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
+\begin{align}
+    Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}, \text{ for } i=1, 2,\cdots, t.
+\end{align}
+We assume several standard conditions on $X$ and each of $\varepsilon^{(i)}$.
+First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}.
+%that is, $Z$ is an $n\times p$ random matrix with i.i.d.
 entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
+Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in equation \eqref{eq_highmoments}.
+Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from the other linear models, the feature covariates, and all noise vectors.
 
-\begin{figure*}[!t]
-	\centering
-	\includegraphics[width=0.3\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-	\caption{A hard parameter sharing architecture}
-	\label{fig_intro_arch}
-\end{figure*}
+%\begin{figure*}[!t]
+%	\centering
+%	\includegraphics[width=0.3\textwidth,valign=t]{figures/mtl_model_arch.pdf}
+%	\caption{A hard parameter sharing architecture}
+%	\label{fig_intro_arch}
+%\end{figure*}
 %\begin{enumerate}
@@
 
-	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
+\paragraph{Estimator.} We extend the two-layer linear neural network from equation \eqref{eq_hps} to combine multiple data sources as follows:
 \begin{align}
@@
 %Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
+We will focus on cases with $r < t$.
+Otherwise, the global minimum of $f(A, B)$ reduces to single-task learning, similar to Proposition \ref{prop_large_r} (details omitted).
 
-	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
-Hence we only consider the case with $r<t$.
-\FY{Correct it if the reason is wrong.}
+Let $\hat A$ be the global minimizer of $g(A)$.
+Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
+We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
+%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in
+and its (out-of-sample) prediction loss as
+\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
 
@@
 %	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$.
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
 
-Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
+\paragraph{Result.} Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
 To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
@@
 \end{align}
-
 \end{theorem}
@@
 The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
-Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
+
+\begin{figure*}[!t]
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{figures/same_covariates.eps}
+		\caption{Example \ref{ex_same_cov}}
+		\label{fig_same_cov}
+	\end{subfigure}\hfill
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{figures/same_covariates.eps}
+		\caption{Example \ref{ex_sample_ratio}}
+		\label{fig_width}
+	\end{subfigure}
+%	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+%	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
+%	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
+%	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+%	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
+%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
+%	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
+%	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
+Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
+%	\label{fig_model_shift_phasetrans}
+\end{figure*}
+
+%Moreover, by setting $t=2$ in Theorem \ref{thm_many_tasks}, we can obtain the prediction loss for the HPS estimator for the transfer learning setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
 For the reader's convenience, we give the precise statement in Corollary \ref{thm_two_tasks}.
@@
 %In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
-We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
-$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
+%We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
+%$ {B^\star}^\top \Sigma  B^\star,$ where recall that $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ by definition.
 % is the matrix formed by the linear model parameters of the two tasks.
-Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined.
+%Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is uniquely defined.
 %Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
-In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
+%In the following corollary, the estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
 
-\begin{corollary}\label{thm_two_tasks}
-Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2\equiv n$. Let $c>0$ be an arbitrary (small) constant. Then we have that with high probability,
-\be\label{minimizer_beta1}
-\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
-\ee
-where $u_{\hat a}$ is the unit vector defined as
-$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
+%\begin{corollary}\label{thm_two_tasks}
+%Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2\equiv n$. Let $c>0$ be an arbitrary (small) constant. Then we have that with high probability,
+%\be\label{minimizer_beta1}
+%\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
+%\ee
+%where $u_{\hat a}$ is the unit vector defined as
+%$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ %1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
 %for task 2,  % over the randomness of the input,
-Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
-	\begin{align}
-		& \bigabs{L_2(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) \cdot B^{\star}A^{\star}  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
-		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
+%Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
+%	\begin{align}
+%		& \bigabs{L_2(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) \cdot B^{\star}A^{\star}  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
+%		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
 		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	 where $A^\star(2)$ denotes the second entry of $A^\star$.
-	 \end{corollary}
-
-\paragraph{Examples.}
-Obviously, the concentration error decreases with $n$.
-First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
-It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
-
-\begin{assumption}\label{assume_rm}
-	Let $\tau > 0$ be a small enough constant.
-%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
-entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	In the high-dimensional setting,
-%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-%			\begin{align}\label{assmAhigh}
-%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
 %	\end{align}
-  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
-%	\end{enumerate}
-\end{assumption}
-Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
-
-\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	With high probability over the randomness of $X$, we have that
-		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
-\end{fact}
-\noindent\textit{Remark.} The above result has a long history in random matrix theory.
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
-Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
-		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
-
-%Finally, for the random noise component, we assume that all of its moments exist.
-%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
-%\begin{align}\label{assmAhigh2}
-%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
-%\end{align}
-%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
-%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
-
-%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
-To illustrate the {bias-variance tradeoff quantitively, we consider an extension of the random-effect model in Example \ref{ex_sample_ratio} to the multi-task setting.
-%which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
+%	 where $A^\star(2)$ denotes the second entry of $A^\star$.
+%	 \end{corollary}
 
@@
 
-	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
+%	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
 Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
 More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
-	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
+%	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
 }\]
-	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
-	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$
-	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
-
+%	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
+%	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$
+%	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
 	%samples that is less than $n$ samples to get comparable loss to STL.
@@
 	\end{enumerate}
-
 \end{example}
 
-We demonstrate the accuracy of our results in simulations.
-While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.
+%We demonstrate the accuracy of our results in simulations.
+%While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.
 
-\begin{figure*}[!t]
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
-		\caption{Example \ref{ex_same_cov}}
-		\label{fig_same_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
-		\caption{Example \ref{ex_sample_ratio}}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
-		\caption{Example \ref{ex_covshift}}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
-	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
-%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
-	\label{fig_model_shift_phasetrans}
-\end{figure*}
-
-\paragraph{Simulations.}
 First, we validate the result of Example \ref{ex_same_cov}.

### 2021-07-08 revision_journal/results.tex
finish sec 3.1
sec 4 wip

@@
-\section{Main results}
+\section{Main results}\label{sec_main}
 
@@
 		\caption{Verify variance asymptotics in finite dimensions}
-		\label{fig_sec3_covariate}
+		\label{fig_sec3_verify_cov}
 	\end{subfigure}
@@
 		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
-		\caption{HPS estimator under covariate shift}
+		\caption{Sample size ratios vs. covariate shift}
 		\label{fig_sec3_covariate}
@@
 	Figure \ref{fig_sec3_covariate}: We illustrate an intriguing dichotomy between covariate shift and sample size ratio: The dimension $p = 200$, $n_2 = 800$, and the noise variance $\sigma^2 = 1/4$.}
+	\label{fig_sec31}
 \end{figure}
@@
     We observe a dichotomy that depends on whether or not $n_1$ is greater than $n_2$.
-    \begin{claim}\label{claim_dichotomy}
+    \begin{claim}[Covariate shift vs. sample size ratios]\label{claim_dichotomy}
         Let $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
         Suppose that $n_1$ and $n_2$ are both fixed.
-        Within the set of all possible covariate shift matrix $M$ described above, the following dichotomy holds:
-        \begin{enumerate}
+        Within the set of all possible covariate shift matrix $M\in\cS$, the following dichotomy holds:
+        \begin{itemize}
 	        \item If $n_1 \ge n_2$, then $g(M)$ is minimized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
 	        \item If $n_1 < n_2$, then $g(M)$ is maximized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
-        \end{enumerate}
+        \end{itemize}
     \end{claim}

### 2021-07-10 revision_journal/multitask.tex
finish sec 4 edits

@@
 \section{Extension to multiple data sources}\label{sec_same}
-
-%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
-%We provide a sharp generalization error bound of hard parameter sharing estimators.
-
-%Hard parameter sharing is a commonly used architecture in multi-task learning.
-However, there have been few theoretical results on the performance of the HPS estimators in high-dimensional multi-task learning.
-In this section, we extend our results on the predication loss of the HPS estimator to a multi-task linear regression, where all tasks have the same covariates.
-We make this extension for the following reasons.
-First, its restriction to the two-task case provides a rare example where the output layers $A_1$ and $A_2$ can be characterized exactly.
-Second, the proof of the multi-task case is no harder than the two-task case, but it can provide much clearer geometric intuition  as we will discuss below.
-Third, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-%It is not hard to extend the above result to the cases with more than two tasks. {\cor For the general case, we study them in a future work.}
-
-%Suppose we have $t$ datasets.
-%For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-%Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-%We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-%We study the standard hard parameter sharing architecture:
-%a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-%See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-%We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
-%\begin{align}\label{eq_mtl}
-%			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-%\end{align}
-%\vspace{-0.05in}
-%where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
 
@@
 The label vector of the $i$-th task follows a linear model
-\begin{align}
+\begin{align}\label{eq_mtl_data}
     Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}, \text{ for } i=1, 2,\cdots, t.
 \end{align}
-We assume several standard conditions on $X$ and each of $\varepsilon^{(i)}$.
-First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}.
-%that is, $Z$ is an $n\times p$ random matrix with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in equation \eqref{eq_highmoments}.
-Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from the other linear models, the feature covariates, and all noise vectors.
+Similar to Section \ref{sec_main}, we use the first $(t-1)$ datasets as sources to predict the $t$-th task.
+However, there is a \text{model shift} between the data sources and the task we would like to predict.
+We make several standard assumptions on $X$ and each of $\varepsilon^{(i)}$.
+First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying Assumption \ref{assm_big1} (same as $X^{(2)}$).
+In particular, the sample size $n$ is greater than the dimension $p$.
+Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments up to any order (cf. equation \eqref{eq_highmoments}).
+Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from any other $\beta^{(j)}$ for $j \neq i$, the matrix $X$, and $\varepsilon^{(j)}$ for any $j$.
 
-%\begin{figure*}[!t]
-%	\centering
-%	\includegraphics[width=0.3\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-%	\caption{A hard parameter sharing architecture}
-%	\label{fig_intro_arch}
-%\end{figure*}
-%\begin{enumerate}
-%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-%\end{enumerate}
-
-\paragraph{Estimator.} We extend the two-layer linear neural network from equation \eqref{eq_hps} to combine multiple data sources as follows:
+\paragraph{Estimator.} We combine multiple data sources by extending the two-layer linear neural network from equation \eqref{eq_hps} as follows:
 \begin{align}
@@
 \end{align}
-where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
-%Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$.
-Otherwise, the global minimum of $f(A, B)$ reduces to single-task learning, similar to Proposition \ref{prop_large_r} (details omitted).
+where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ denotes the output layer and $B \in \real^{p \times r}$ denotes the (shared) feature layer.
+We set the width of the feature layer $r$ less than the number of tasks $t$.
+Otherwise, when $r \ge t$, the global minimum of $f(A, B)$ reduces to single-task learning, similar to Proposition \ref{prop_large_r} (details omitted).
 
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
+Let $(\hat A, \hat B)$ denote a global minimizer of $f(A, B)$.
+We define the HPS estimator for task $t$ as $\hat \beta_t^{\MTL} := \hat B \hat A_i$, where $\hat A_i$ denotes the $i$-th column of $\hat A$.
+We evaluate the performance of $\hat{\beta}_t^{\MTL}$ according to its excess risk:
+\be\label{ith_loss}
+    L_t(\hat{\beta}_t^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta}^{\MTL}_t - \beta^{(t)}\right)}^2.
+\ee
 
-	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
-	\begin{align}
-		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
-		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
-	\end{align}
-	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
-	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
-	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
-	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
-	\end{align}
-%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
-%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
-%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$.
-
-\paragraph{Result.} Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which can be regarded as the covariance of the task labels):
+\paragraph{Result.} We show that in the multi-task setting, hard parameter sharing finds the ``best'' rank-$r$ approximation to all tasks.
+To formally describe our result, we introduce several notations.
+Let $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ be the concatenated model vectors of all tasks.
+Let $A^{\star} {A^{\star}}^{\top}$ be the best rank-$r$ approximation of ${B^{\star}}^\top\Sigma B^{\star}$ in the following sense:
 \begin{align}\label{eq_A_star}
@@
 where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices.
- To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
-Otherwise, $A^{\star}$ is not well-defined and Theorem \ref{thm_many_tasks} will give a null result.
- %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
-Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
-Then we have the following result.
+Let $a_i^{\star}\in\real^r$ be the $i$-th column vector of $A^{\star}{A^{\star}}^{\top}$.
+We characterize the excess risk $L_t(\hat{\beta}_t^{\MTL})$ precisely in the following result.
 
-% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
-%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
-%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
-%Our result is stated as follows.
-
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
-	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary (small) constant. Then for any task $i = 1,  \cdots, t$, we have that with high probability,
-\be\label{minimizer_beta}
-\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
-\ee
-where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that  with high probability,
+\begin{theorem}[Excess risk of HPS for multiple tasks under model shift]\label{thm_many_tasks}
+Suppose the multi-task setting according to equation \eqref{eq_mtl_data} holds.
+Let $r$ be any positive integer less than $t$.
+Suppose the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than its $(r+1)$-th largest eigenvalue. 
+Let $c>0$ be an arbitrary (small) constant.
+The following estimates for $L_t(\hat{\beta}_t^{\MTL})$ holds with high probability:
 \begin{align}
-		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
-		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
+	\bigabs{L_t(\hat{\beta}_t^{\MTL}) - L_t(B^{\star}a_t^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_t^{\star}}^2  } 
+	\le  \sqrt{\bignorm{{B^\star}^\top\Sigma B^\star}_{\op} \cdot n^{-\frac 1 2+ \frac 2{\varphi} + c}  + \sigma^2 n^{-\frac 1 2 + c}} \cdot \frac{\bignorm{{B^\star}^\top\Sigma B^\star}_{\op}+  \sigma^2}{\lambda_r - \lambda_{r+1}}.
 \label{Li_multi1}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
 \end{align}
@@
 %and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
-Finally, we have a better bound for the averaged prediction loss:  with high probability,
-\begin{align}
-&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
- &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
-\end{align}
+%Finally, we have a better bound for the averaged prediction loss:  with high probability,
+%\begin{align}
+%&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
+% &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 .\label{Li_multi2}
+%\end{align}
 \end{theorem}
 
-Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
-Moreover, the factor $(\lambda_r - \lambda_{r+1})^{-1}$ is natural, because the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not stable when $\lambda_r $ and $\lambda_{r+1} $ are close to each other.
-The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
+Recall that $\varphi > 4$ according to Assumption \ref{assm_big1}, thus, $\frac {2}{\varphi} \le \frac 1 2$ and $n^{-\frac 1 2 + \frac 2 {\varphi} + c}$ vanishes to zero for a small enough constant $c$.
+Therefore, equation \eqref{Li_multi1} precisely characterizes the excess risk of the HPS estimator.
+As a remark, the same result applies to any other tasks although we have focused on predicting task $t$.
+Theorem \ref{thm_many_tasks} significantly extends the two-task model shift setting of Theorem \ref{cor_MTL_loss}.
+The term $L_t(B^{\star} a_t^{\star})$ captures the bias of the HPS estimator and $\frac{p \sigma^2}{n - p} \bignorm{a_t^{\star}}^2$ captures the estimator's variance.
+%The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
 The estimate \eqref{Li_multi1}
- gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
+% gives the exact asymptotic limit of $L_i(\hat{\beta}_i^{\MTL}(\hat a))$, which shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
 Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases for the multi-task HPS estimator.
@@
 %On the other hand, the bias always increases.}
-We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
+%We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
 Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
 For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
-
-The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
+%	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
+%	\begin{align}
+%		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
+%		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
+%	\end{align}
+%	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
+	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
+	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
+%	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
+%	\begin{align}\label{eq_mtl_output_layer}
+%		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
+%	\end{align}
+The proof of Theorem \ref{thm_many_tasks}, which is based on a characterization of the global minimum of problem \eqref{eq_mtl_same_cov}, can be found in Section  \ref{app_proof_error_same_cov}.
 
@@
 
-\begin{example}%[Random-effect model]
+\begin{example}[How to set the width $r$ in HPS?]
 \label{ex_same_cov}
@@
 %More precisely, %we have
-Suppose that {$\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$} for $ i=1,2,\cdots, t,$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$,
-and $\wt \beta^{(i)}$ denotes the $i$-th
+An important question in applications of HPS is how to set the width $r$ of the feature layer.
+We use our estimates to show that the optimal width depends on the tradeoff between the estimator's bias and variance.
+Concretely, consider a random-effect model where all tasks share a model vector $\beta_0$ plus perturbations.
+For every $i=1,2,\cdots, t,$, $\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$}, where $\wt \beta^{(i)}$ denotes the $i$-th
 %Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
-%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
+task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $\frac {\kappa^2} p$.
+
+\begin{claim}
+\begin{enumerate}
+	\item {\bf Positive vs.
+negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
+
+	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
+Hence increasing the width $r$ of the shared feature representation layer does not help.
+\end{enumerate}
+\end{claim}
 %For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
@@
 %We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
+\begin{proof}
     In this random-effect model, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}),
@@
     %If the error is sufficiently small, then
-Comparing the above equation with \eqref{L_STL_simple01} (and ignoring the small error), we have the following observations.
     %Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
@@
     %	Suppose $n$ is sufficiently large so that the error is negligible.
-%\begin{enumerate}
-\begin{enumerate}
-	\item {\bf Positive vs.
-negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
-
-	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
-Hence increasing the width $r$ of the shared feature representation layer does not help.
-	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-
-%	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
-Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
-More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
-%	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
-}\]
-%	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
-%	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$
-%	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
-	%samples that is less than $n$ samples to get comparable loss to STL.
-	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
-	\end{enumerate}
+\end{proof}
 \end{example}

### 2021-07-10 revision_journal/multitask.tex
minor edit

@@
 Concretely, consider a random-effect model where all tasks share a model vector $\beta_0$ plus perturbations.
-For every $i=1,2,\cdots, t,$, $\beta^{(i)}=\beta_0 +\wt \beta^{(i)}$}, where $\wt \beta^{(i)}$ denotes the $i$-th
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $\frac {\kappa^2} p$.
+For every $i=1,2,\cdots, t,$, $\beta^{(i)} = \beta_0 + \wt \beta^{(i)}$, where $\wt \beta^{(i)}$ denotes the $i$-th task-specific component whose entries are i.i.d.
+Gaussian random variables of mean zero and variance $\frac {\kappa^2} p$.
 

### 2021-07-11 revision_journal/results.tex
wip

@@
 
-\begin{theorem}[Variance asymptotics under covariate shift]\label{thm_main_RMT}
+\begin{theorem}[Variance estimates under covariate shift]\label{thm_main_RMT}
 Under Assumption \ref{assm_big1} (recalling $\varphi > 4$), for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for $L_{\var}(a)$ in \eqref{Lvar}:
@@
 
-\begin{proposition}\label{prop_main_RMT}
+\begin{theorem}[Bias estimates under covariate and model shift]\label{prop_main_RMT}
 %The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
@@
 			where we recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
+\end{theorem}
 

### 2021-07-13 revision_journal/exp.tex
sec 4 wip
sec 3.2 wip

@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/compare_risk_covariate_shift.eps}
+		\includegraphics[width=0.95\textwidth]{figures/compare_risk_covariate_shift.eps}
+		\caption{Covariate shift}
+		\label{fig_sec5_covariate}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/compare_risk_model_shift.eps}
+		\caption{Model shift}
+		\label{fig_sec5_covariate}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/compare_risk_covariate_shift.eps}
 		\caption{Covariate shift}
@@
 
-\subsection{Implications for text classification}
+\subsection{Implications for neural networks}
 Our results and simulations are all in the high-dimensional linear regression setting.

### 2021-07-13 revision_journal/results.tex
sec 3.2 wip

@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{figures/verify_covariate_shift.eps}
+		\includegraphics[width=0.8\textwidth]{figures/verify_covariate_shift.eps}
 		\caption{Verify variance asymptotics in finite dimensions}
@@
 		\centering
-		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
+		\includegraphics[width=0.8\textwidth]{figures/covariate_shift.eps}
 		\caption{Sample size ratios vs. covariate shift}
@@
 
-\paragraph{Illustrative examples.}
-Next, we illustrate the result of Corollary \ref{cor_hps_cov} in several examples.
-
-\begin{example}[Does covariate shift help or hurt information transfer?]
+\paragraph{Illustrative examples.} Next, we illustrate the result of Corollary \ref{cor_hps_cov} in several examples.
+We use our estimates to explore whether covariate shift helps or hurts information transfer.
 Our first example illustrates that the effect of covariate shift depends on the sample sizes of each dataset in an intricate manner.
@@
 By contrast, our analysis applies to a (high-dimensional) regression setting.
-\end{example}
 
-\begin{example}
 Our second example illustrates that the effect of covariate shift worsens as the sample size of task one increases.
@@
 As a corollary of Claim \ref{prop_covariate}, when $n_1$ is much larger than $n_2 / \tau^2$, the excess risk of HPS is approximately optimal in the set of all possible $M\in\cS$ when there is no covariate shift between dataset one and two.
-\end{example}
 
@@
 
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/model_shift_positive.eps}
+		\caption{Positive transfer}
+		\label{fig_sec5_covariate}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/model_shift_transition.eps}
+		\caption{From positive to negative transfer}
+		\label{fig_sec5_covariate}
+	\end{subfigure}\hfill%
+	\begin{subfigure}[b]{0.33\textwidth}
+		\centering
+		\includegraphics[width=0.95\textwidth]{figures/model_shift_negative.eps}
+		\caption{Negative transfer}
+		\label{fig_sec5_covariate}
+	\end{subfigure}	
+	\caption{Comparing HPS to several natural estimators for transfer learning.
+We find that HPS enjoys superior performance under covariate and/or model shifts.
+The results are averaged over five random seeds.}
+	\label{fig_sec51}
+\end{figure}
+
 \paragraph{Illustrative examples.}
+Based on the estimates provided in Theorem \ref{cor_MTL_loss}, we now provide a detailed analysis in the random-effect model.
+\begin{claim}[Estimating information transfer in the random-effect model]
+
+\end{claim}
+
+\begin{proof}
+We would like to show that as a 
 Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
@@
 \fi
-%	\end{example}
+\end{proof}
 

### 2021-07-14 revision_journal/results.tex
finish sec 3.2

@@
     We observe a dichotomy that depends on whether or not $n_1$ is greater than $n_2$.
-    \begin{claim}[Covariate shift vs. sample size ratios]\label{claim_dichotomy}
+    \begin{claim}[Sample sizes vs. covariate shift]\label{claim_dichotomy}
         Let $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
@@
         Within the set of all possible covariate shift matrix $M\in\cS$, the following dichotomy holds:
-        \begin{itemize}
-	        \item If $n_1 \ge n_2$, then $g(M)$ is minimized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
-	        \item If $n_1 < n_2$, then $g(M)$ is maximized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
+        \begin{enumerate}
+	        \item[i)] If $n_1 \ge n_2$, then $g(M)$ is minimized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
+	        \item[ii)] If $n_1 < n_2$, then $g(M)$ is maximized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
         \end{itemize}
@@
 \begin{proof}
-    We explain why the above dichotomy happens. We can write $g(M)$ for any $M \in \cS$ as
-    $$g(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right).$$
+    For any $M \in \cS$, we can write $g(M)$ as
+    $$g(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} \alpha_1 + \alpha_2} + \frac1{\lambda_i^{-2} \alpha_1 + \alpha_2} \right).$$
     When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
     $$g(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma},$$
-    where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $\alpha_1 + \alpha_2 = 1-\gamma$, through a direct calculation we find that
+    where we abbreviate $\gamma:=p/(n_1+n_2)$.
+    Using $\alpha_1 + \alpha_2 = 1-\gamma$, we further have that
     \begin{align*}
@@
     %and can be derived from algebraic calculations (details omitted).
-    We claim that $\alpha_1 > \alpha_2$ if and only if $n_1 > n_2$, which then explains the dichotomy.
+    We claim that $\alpha_1 > \alpha_2$ if and only if $n_1 > n_2$, which proves claim i).
     In fact, if $\alpha_1 > \alpha_2$, then the first part of equation \eqref{eq_a12extra} gives that $\alpha_1 > (1-\gamma)/2$.
@@
     \begin{align*}
-     \frac{n_1}{n_1 + n_2} &> \alpha_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
+     \frac{n_1}{n_1 + n_2} &> \alpha_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2},
     \end{align*}
@@
     %\end{align*}
-    This is equivalent to $n_1>n_2$.
-The other direction follows from a similar argument.
+    which is equivalent to $n_1>n_2$.
+The proof of claim ii) follows from a similar argument.
 % Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
@@
 
- In this subsection, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effects of the bias-variance tradeoff and varying sample sizes on the performance of the $\MTL$ estimator.
+Next, we consider a model shift setting where task one and two have the same linear model but different population covariance matrices.
+We show the exact asymptotic limits of the bias and variance of HPS.
 
 \begin{theorem}[Excess risk of HPS under model shift]\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \sigma^2  \left[ \cal L_1(a)+ \OO\left({p^{c}}/{n_1}\right)\right]  ,
-\ee
-and
+Under Assumption \ref{assm_big1}, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d. Gaussian random variables.
+Denote by $\xi_1:=p/n_1$ and $\xi_2:=p/n_2$.
+Then, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
 \begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right] \cdot  \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
+L_{\var}(a) &= \sigma^2  \cal L_1(a)+ \OO\Big(\frac {\sigma^2 p^{c}} {n_1}\Big), \label{Lvar_samplesize} \\
+L_{\bias}(a)&= \bignorm{\beta^{(1)}-a\beta^{(2)}}^2 \cal L_2(a) +  \OO\Big(p^{-\frac 1 2 + c}  \norm{\beta^{(1)}-a\beta^{(2)}}^2
++ p^{-C}\big( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\big)   \Big),\label{Lbias_samplesize}
 \end{align}
-Here we define the functions
+where $\cL_1(a)$ and $\cL_2(a)$ are defined as follows
 \begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}.
+\cal L_1(a) &:= {2p}\cdot\left((n_2 - p) + a^2 (n_1 - p) + \sqrt{\big( (n_2 - p) + a^2 (n_1 - p)\big)^2 + 4a^2(n_1 p + n_2 p - n_1 n_2)}\right)^{-1}, \\
+\cal L_2(a) &:= \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2(1 + \cal L_1(a))} + \kappa(a)}{1- \xi_2 \kappa(a)}, \text{ in which }
+\kappa(a) := \frac{\cal L_1(a)^2}{\xi_2^2(1+\cal L_1(a))^2}  \left(1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1(1+a^2\cal L_1(a) )^2}\right)^{-1}.
 %f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
@@
 
-We believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
+Combining equation \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize}, we thus obtain an estimate for the excess risk of HPS.
+We provide some intuition behind both estimates.
+%For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the $Z^{(1)}$ and $Z^{(2)}$ entries.
+First, the variance estimate is a special case of Theorem \ref{thm_main_RMT} where $\Sigma^{(1)} = \Sigma^{(2)}$ but $n_1 \neq n_2$.
+In fact, the result can be obtained by solving $\alpha_1, \alpha_2$ in equation \eqref{eq_a12extra} using $\lambda_i = 1$ for all $i = 1,\dots, p$.
+%On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
+Second, the bias estimate is obtained based on a sharp convergence estimate proved in \citet{BES_free1,BES_free2} for the free addition of two probability measures.
+To illustrate, denote by $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$.
+We can write the bias equation as
 \begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
+    L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} { \left(a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right)^{-2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
 \end{align*}
-where we abbreviate $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
+By the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that
 \begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
+    L_{\bias} (a)&\approx \|\bv_a\|^2 \cdot \frac1p\bigtr{ \big((Z^{(1)})^\top Z^{(1)}\big)^2 { \left(a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right)^{-2}}}
 \end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
+up to a small error.
+
+Our key idea is to write equation \eqref{Lbias_idea} as the derivative of a certain polynomial with respect to $x$ at $x = 0$:
 \begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
+L_{\bias} (a)&\approx \|\bv_a\|^2 \cdot\left.
+\frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \Big( a^2(Z^{(1)})^\top Z^{(1)} + x \big((Z^{(1)})^\top Z^{(1)}\big)^2 + (Z^{(2)})^\top Z^{(2)} \Big)^{-1}  }.
 \end{align}
@@
 the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$\cite{nica2006lectures}.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-We refer the reader to Appendix \ref{app_iso_cov} of the supplement \cite{MTL_suppl} for more details.
+%In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measures.
+Finally, We use the result of \citet{BES_free1,BES_free2} to obtain a sharp estimate of
+$$\frac1p\bigtr{  \Big( a^2(Z^{(1)})^\top Z^{(1)}+ x \big((Z^{(1)})^\top Z^{(1)}\big)^2+(Z^{(2)})^\top Z^{(2)} \Big)^{-1}},$$
+which implies a sharp estimate of $L_{\bias}(a)$.
+%Taking the derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
+The complete proof of Theorem \ref{cor_MTL_loss} can be found in Section \ref{app_iso_cov}.
 
-We believe that the above argument can be extended to the case without the Gaussian assumption.
+\medskip
+\noindent\textit{Remarks.}
+First, we believe the convergence rates $p^c/n_1$ and $p^{-1/2+c}$ in \eqref{Lvar_samplesize} and \eqref{Lbias_samplesize} are both sharp up to the $p^c$ factor.
+\todo{the rate in \eqref{Lvar_samplesize} seems different from Thm 3.1?}
+Second, we believe that the above argument can be extended to the case without the Gaussian assumption.
 For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some difficult technical regularity conditions for our setting, which is not the focus of this work.
-Hence we do not pursue this direction in this paper.
+However, applying the result of \citet{EKN_poly} requires checking certain technical regularity conditions for our setting.
+We leave this as an open question for future work.
 
@@
 		\caption{Positive transfer}
-		\label{fig_sec5_covariate}
+		\label{fig_sec3_model_positive}
 	\end{subfigure}\hfill%
@@
 		\caption{From positive to negative transfer}
-		\label{fig_sec5_covariate}
+		\label{fig_sec3_model_transition}
 	\end{subfigure}\hfill%
@@
 		\caption{Negative transfer}
-		\label{fig_sec5_covariate}
+		\label{fig_sec3_model_negative}
 	\end{subfigure}	
-	\caption{Comparing HPS to several natural estimators for transfer learning.
-We find that HPS enjoys superior performance under covariate and/or model shifts.
-The results are averaged over five random seeds.}
-	\label{fig_sec51}
+	\caption{We illustrate three regimes of information transfer in HPS under model shift.
+When $\mu$ is small, HPS outperforms the OLS estimator irrespective of $n_1$.
+When $\mu$ is large, HPS performs worse than OLS.
+For an intermediate range of $\mu$, HPS outperforms OLS only for a restricted range of $n_1$.
+See Claim \ref{claim_model_shift} for the precise range of each regime.
+This simulation uses $p = 100, n_2 = 300, \sigma = 1/2$.}
+	\label{fig_sec3_model_shift}
 \end{figure}
@@
 \paragraph{Illustrative examples.}
-Based on the estimates provided in Theorem \ref{cor_MTL_loss}, we now provide a detailed analysis in the random-effect model.
-\begin{claim}[Estimating information transfer in the random-effect model]
+While the estimates from Theorem \ref{cor_MTL_loss} are generally complex, we describe a simplified result for the random-effect model (cf. Section \ref{sec_data}).
+Under the assumptions stated in Proposition \ref{lem_hat_v}, $\hat{a}$ is approximately equal to one.
+Then, we can calculate that
+\[ \cL_1(1) = \frac{p}{n_1 + n_2 - p} \text{ and } \cL_2(1) = \frac{n_1^2(n_1 + n_2 - p) + p n_1 n_2}{(n_1 + n_2)^2 (n_1 + n_2 - p)}, \text{ in which } \kappa(1) = \frac{n_2^2}{(n_1 + n_2)^2 - n_1 p}.
+\]
+Thus, using that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))\mu^2$ w.h.p., we conclude that for the random-effect model, the excess risk $L(\hat{\beta}_2^{\MTL}$ is approximately equal to
+$$ g(n_1) \define \sigma^2 \cal L_1(1) +   2\mu^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2\mu^2 \cdot \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}$$
+plus lower order terms (that vanishes to zero as $p$ goes to infinity).
+Next, we provide a detailed analysis of when combining task one using HPS transfers positively to task two, depending on sample sizes $n_1, n_2$, and model shift $\mu$.
 
+\begin{claim}[Sample sizes vs. model shift]\label{claim_model_shift}
+    Suppose Assumption \ref{assm_big1} and the random-effect model under equation \eqref{eq_re} and \eqref{para_rel} holds.
+    Suppose further that $n_2 \ge 3p$.
+    Then, there exists a large constant $C > 0$ such that the following holds w.h.p.,
+    \begin{enumerate}
+        \item[i)] If $\mu^2 \le \frac{\sigma^2 p}{2(n_2 - p)}$, then $L(\hat{\beta}_2^{\MTL}) \le L(\hat{\beta}_2^{\STL}) + \OO(p^{-C})$.
+        \item[ii)] If $\frac{\sigma^2 p}{2(n_2 - p)} < \mu^2 < \frac{\sigma^2 n_2}{2(n_2 - p)}$, then there exists a deterministic constant $\rho$ such that if $n_1 \le \rho\cdot p$, then $L(\hat{\beta}_2^{\MTL}) \le L(\hat{\beta}_2^{\STL}) + \OO(p^{-C})$, else $L(\hat{\beta}_2^{\STL}) \le L(\hat{\beta}_2^{\MTL}) + \OO(p^{-C})$.
+        \item[iii)] If $\frac{\sigma^2 n_2} {2(n_2 - p)} \le \mu^2$, then $L(\hat{\beta}_2^{\STL}) \le L(\hat{\beta}_2^{\MTL}) + \OO(p^{-C})$.
+    \end{enumerate}
 \end{claim}
@@
 \begin{proof}
-We would like to show that as a 
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
-$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
-with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations.
-Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term $\sigma^2 \cal L_1(1)$ is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term always increases (because the bias in single-task linear regression is zero).
-This gives a \emph{bias-variance tradeoff} for the predication loss of the HPS estimator.
-Second, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-Hence how the performance of the HPS estimator changes with respect to $n_1$ also depends on an intricate bias-variance tradeoff.
+By Theorem \ref{cor_MTL_loss} and the discussion above, we have that $L(\hat{\beta}_2^{\MTL}) = g(n) + \OO(p^{-C})$ w.h.p.
+By Lemma \ref{fact_tr}, we have that the excess risk of the OLS estimator for task two satisfies
+\begin{align*}
+    L(\hat{\beta}_2^{\STL})
+    = \sigma^2 \cdot \bigtr{\Sigma^{(2)}\Big((X^{(2)})^{\top} X^{(2)} \Big)^{-1}}
+    = \frac{\sigma^2 p}{n_2 - p} + \OO(p^{-C}).
+\end{align*}
+Thus, whether or not $L(\hat{\beta}_2^{\MTL}) \le L(\hat{\beta}_2^{\STL})$ reduces to comparing $g(n_1)$ and $\frac{\sigma^2 p}{n_2 - p}$---let $h(n_1)$ be their difference.
+We can write $h(n_1)$ as
+\[ h(n_1) = 2\mu^2 \cdot \frac{n_1^2 (n_1 + n_2 - p) + p n_1 n_2}{(n_1 + n_2)^2 (n_1 + n_2 - p)} - \frac{\sigma^2 p n_1}{(n_1 + n_2 - p)(n_2 - p)}. \]
+We observe that the sign of $h(n_1)$ is the same as the sign of the following simplified polynomial
+\begin{align*}
+    \tilde h(n_1) &= 2\mu^2 (n_2 - p) (n_1 (n_1 + n_2 - p) + p n_2) - \sigma^2 (n_1 + n_2)^2 \\
+    &= \big(2\mu^2 (n_2 - p) - \sigma^2\big) n_1^2 + (2\mu^2 (n_2 - p)^2 - 2\sigma^2 p n_2) n_1 + \big(2\mu^2 (n_2 - p) p n_2 - \sigma^2 p n_2^2\big).
+\end{align*}
+Let $C_0, C_1, C_2$ be the coefficient of $n_1^0, n_1^1, n_1^2$ above, respectively.
+We argue about each claim as follows.
 
-Now fix an $n_2$, we study the bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$, which is $L(\hat{\beta}_2^{\STL} )-\ell(n_1,n_2)$ divided by $2d^2$:
-$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, and hence gives the quantitive information transfer from the source task to the target task.
-First, we have positive (resp.
-negative) transfer if and only if $h(\rho)>0$ (resp.
-$h(\rho)<0$).
-Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
-\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-We observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
+For claim i), if $\mu^2 \le \frac{\sigma^2 p}{2(n_2 - p)}$, then $C_0, C_1, C_2$ are all at most zero.
+Thus, $\tilde h(n_1) \le 0$, which implies that $h(n_1) \le 0$.
 
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
+For claim ii), if $\frac{\sigma^2 p}{2(n_2 - p)}< \mu^2 < \frac{\sigma^2 n_2}{2(n_2 - p)}$ (recall that $n_2 > p$ by Assumption \ref{assm_big1}), then $C_2 > 0$ and $C_0 < 0$.
+Thus, $\tilde{h}(n_1)$ has a positive root and a negative root.
+Let $\rho$ be the positive root.
+Hence, if $n_1 \le \rho \cdot p$, then $\tilde h(n_1) \le 0$.
+Otherwise, $\tilde h(n_1) \ge 0$.
 
-\begin{itemize}
-\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
-
-\item If $(\rho_2+1)^2 > 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
-Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
-\end{itemize}
-\end{enumerate}
-Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial
-\be\label{poly2}
- \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy. %\FY{add several plots to illustrate this dichotomy}
-\begin{enumerate}
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
-
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global maximum at $\rho=\rho_c$.
-\end{enumerate}
-
-%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance.
-%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
-\iffalse
-Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
-
-Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
-	\begin{align*}
-		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
-		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
-		= \frac{p}{n_1 + n_2 - p},
-	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit.
-	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
-
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
-This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
-by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-
-{\cor
-For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that
-	\begin{align}
-		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
-		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
-			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
-For the bias term,
-}
-
-Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
-For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
-We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
-It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
-By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
-\fi
+For claim iii), if $\frac{\sigma^2 n_2}{2(n_2 - p)} \le \mu^2$, then $C_1 \ge 0$ and $C_2 \ge 0$.
+Furthermore, $\frac{\sigma^2 p n_2}{(n_2 - p)^2} \le \frac{\sigma^2 n_2}{2(n_2 - p)}$ because $n_2 \ge 3p$ by our assumption.
+Thus, $C_2$ is non-negative as well, which implies $\tilde h(n_1) \ge 0$.
 \end{proof}
 
-%\paragraph{Comparing HPS to other estimators.}
-
-\todo{merge into prev paragraphs {Simulations.}}
-Second, we validate the result of Example \ref{ex_sample_ratio}.
-Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-%Again, our estimates are accurate compared to the empirical losses.
-We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$.
-The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$.
-We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
-On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
-Intuitively, this is because bias increases less for smaller $d^2$.
+As a remark, when $p < n_2 < 3p$, similar results can be derived using the above arguments (details omitted).
+Figure \ref{fig_sec3_model_shift} illustrates Claim \ref{claim_model_shift} for different regimes of model shift.
+First, we observe that our estimates accurately match with the empirical risks.
+Second, as we vary the model shift parameter $\mu$, we observe the three information transfer regimes, as Claim \ref{claim_model_shift} suggests.
 

### 2021-07-14 revision_journal/setup.tex
finish sec 3.2

@@
 
-\subsection{Data model}
+\subsection{Data model}\label{sec_data}
 
@@
 %Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
+task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} \mu^2$.
 
@@
 Our study of such estimators is motivated by the fact that hard paratemer sharing is widely used in empirical studies of multi-task learning \cite{R17}.
-\todo{Later on in Section \ref{sec_diff}, we will further compare the HPS estimator to other natural transfer learning estimators.} %$L(\hat{\beta}_2^{\STL})$ and $L(\hat{\beta}^{\AV}(\lambda))$ for some properly chosen $\lambda\in [0,1]$.}
+\todo{Later on in Section \ref{sec_diff}, we will further compare the HPS estimator to other natural transfer learning estimators.}
 
@@
 Consider a datapoint $(x,y)$ generated from the same model as dataset $i$: $y= x^\top \beta^{(i)} + \ve$.
-%, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-%We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure
 The expected predication risk (under mean squared error) is given by
 $$\exarg{x, \varepsilon}{\left\|y-x^\top \hat{\beta}_i^{\MTL} \right\|^2}= \left\|\big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 + \sigma^2.$$
-%Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
 The excess risk is defined without the constant term $\sigma^2$:
@@
 	\be\label{para_rel}
-	    \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
+	    \|\beta_0\|^2 \ge p^{c_0}\mu^2 +p^{-1/2+c_0}\sigma^2.
 	\ee
@@
 	\be\label{hatw_add1}
-	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
+	 \hat a =1+ \OO\left(\frac{\mu^2}{\|\beta_0\|^2} + p^{-\frac 1 4 + c} \frac{\mu+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
 	\ee
@@
 In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-
+\todo{change $d$ to $\mu$ because a reviewer complained}
 %Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
@@
 
-%$L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator  as a baseline.
-
 \paragraph{Connection to information transfer.} To be precise, we say that task one provides a positive transfer to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
@@
 %\end{align}
-%Note that 
-%    is called the variance term, which depends on the noise variance. 
-    %predication loss for the HPS and OLS estimators.
-%\end{proof}
 
@@
 
-%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
-
-%\paragraph{Random matrix theory.}
 Building on the above connection, we apply recent developments from random matrix theory to analyze information transfer.
@@
 	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
-		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
+	Under Assumption \ref{assm_big1}, we have that for any deterministic  matrix $\Sigma\in\real^{p\times p}$,
+		\[ \bigtr{\Sigma \Big((X^{(2)})^\top X^{(2)} \Big)^{-1}  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
 		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|\Sigma\|_{op} \right) \]

### 2021-07-15 revision_journal/exp.tex
finish sec 5

@@
 
-\subsection{Evaluating HPS under model and covariate shifts}
+\subsection{Evaluating HPS under covariate and model shifts}
 
@@
 		\caption{Model shift}
-		\label{fig_sec5_covariate}
+		\label{fig_sec5_model}
 	\end{subfigure}\hfill%
@@
 		\centering
-		\includegraphics[width=0.95\textwidth]{figures/compare_risk_covariate_shift.eps}
-		\caption{Covariate shift}
-		\label{fig_sec5_covariate}
+		\includegraphics[width=0.95\textwidth]{figures/compare_risk_cov_model_shift.eps}
+		\caption{Covariate and model shift}
+		\label{fig_sec5_cov_model}
 	\end{subfigure}
-	\caption{Comparing HPS to several natural estimators for transfer learning.
-We find that HPS enjoys superior performance under covariate and/or model shifts.
-The results are averaged over five random seeds.}
+	\caption{We compare the empirical excess risk of HPS and several natural transfer learning estimators.
+We find that HPS achieves the lowest excess risk for predicting task two under (either or both) covariate and model shift.
+This simulation uses $p = 100, n_1 = n_2 = 200, \sigma = 1/2$.
+Figure \ref{fig_sec5_cov_model} uses $\lambda = 4$ for generating covariate-shifted data.}
 	\label{fig_sec51}
@@
 \end{itemize}
+The parameter $b$ in the averaging estimator is optimized using a validation set of the same size as the training set.
+Additionally, we extend the two-layer neural network formulation of HPS (cf. equation \eqref{eq_hps}) to a weighted objective:
+$b \cdot \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2 + (1 - b) \cdot  \bignorm{X^{2} B A_2 - Y^{(2)}}^2$, and optimize $b$ using the same validation set.
 
-Figure \ref{fig_sec51} shows the result under covariate and/or model shifts.
-Figure \ref{fig_sec5_covariate} considers the same example as Figure \ref{fig_sec31}.
-%    \begin{align}
-%    L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-%    &+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2   \lambda^2 \bigtr{\Sigma^{(2)} [(X^{(1)})^\top X^{(1)}]^{-1}  }\nonumber\\
-%    & + \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  (1-\lambda)^2 \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_AVE_simple}
-%    \end{align}
-%    and
-%    \begin{align}
-%    L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-%    \end{align}
-    %Moreover, there exists a constant $C_0>0$ such that with high probability,
-    %\be\label{loss_large}
-    %g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-    %\ee
-    %with high probability for any small constant $\e>0$.
+Figure \ref{fig_sec51} shows the result under (either or both) covariate and model shift.
+Figure \ref{fig_sec5_covariate} uses the same data generating process as Figure \ref{fig_sec31}.
+Figure \ref{fig_sec5_model} uses the same data generating process as Figure \ref{fig_sec3_model_shift}.
+Figure \ref{fig_sec5_cov_model} further combines the covariate-shifted data and the model shift setting.
+For reach run, we average the result over 100 random seeds because of high variance from using only a limited number of samples.
+We find that HPS outperforms all the other estimators in this simulation (the result for the TL estimator is worse than STL and is omitted from the figure).
 
- %With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-%\begin{align}
-%L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   , \label{L_STL_simple01}
-%\end{align}
-%and
-%\begin{align}
-%L(\hat{\beta}^{\AV}(\lambda) ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \lambda^2 \left\| (\Sigma^{(2)})^{1/2}(\beta^{(1)}-\beta^{(2)})\right\|^2 \nonumber \\
-%&+  \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2 \left[\frac{ \lambda^2}{n_1-p}\bigtr{\Sigma^{(2)}(\Sigma^{(1)})^{-1}} + \frac{(1-\lambda)^2p  }{n_2-p}\right] . \label{L_AVE_simple01}
-% \end{align}
-
-\todo{merge into previous paragraphs {Simulations.}}
-Finally, we validate the result of Example \ref{ex_covshift}.
-Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
-Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
-We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
-The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
-
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
-
-\subsection{Implications for regression methods}
+%\subsection{Implications for regression methods}
 
 \subsection{Implications for neural networks}
-Our results and simulations are all in the high-dimensional linear regression setting.
-How well do they extend to other scenarios?
-In this section, we conduct further studies on six text classification datasets.
-Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
+
+\begin{wrapfigure}[12]{r}{0.3\textwidth}
+	\vspace{-0.35in}
+	\begin{center}
+		\includegraphics[width=0.27\textwidth]{figures/mtl_model_arch.pdf}
+	\end{center}
+	\vspace{-0.28in}
+	\caption{A hard parameter sharing architecture.}
+	\label{fig_intro_arch}
+\end{wrapfigure}
+We conduct further studies of HPS for text classification tasks.
+We consider six datasets for predicting movie review sentiment (MR and SST) \cite{pang2005seeing,socher2013recursive}, sentence subjectivity (SUBJ) \cite{pang2004sentimental}, customer review sentiment (CR) \cite{hu2004mining}, question types (TREC) \cite{li2002learning}, and polarity of a phrase (MPQA) \cite{wiebe2005annotating}.\footnote{The datasets can be downloaded at \url{https://github.com/harvardnlp/sent-conv-torch/tree/master/data}.
+Further statistics of each dataset can also be found following the link.}
 %The question is to predict positive or negative sentiment expressed in the text.
-Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
-For LSTM, we add a shared feature representation layer on top of word embeddings.}
+We learn a hard parameter sharing model that consists of a word embedding layer using GloVe \cite{pennington2014glove}, followed by a shared feature representation layer.\footnote{The GloVe word vectors can be downloaded at \url{https://nlp.stanford.edu/projects/glove/}.}
+A separate output layer is used for predicting the labels of each dataset.
+We evaluate on three possibilities of feature representation layers including LSTM, MLP, and CNN \cite{lei2018simple}.\footnote{Before the MLP layer, we apply an average pooling layer over the embedding of every word in the sentence.}
+See Figure \ref{fig_intro_arch} for an illustration of the network architecture.
 
-\paragraph{Progressively increasing source dataset sizes.}%\label{sec_text}
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-%There are 14 diseases (tasks) for every image that we would like to predict.
-%We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
+\paragraph{Covariate alignment for mitigating covariate shift.}
+We apply our theoretical insights to conduct detailed analysis of a covariate alignment procedure proposed by \citet{WZR20}.
+The idea of this procedure is to insert an ``alignment'' module (or matrix) between every input $X_i$ and the shared module $B$.
+During training, the entire network is optimized together with this alignment module (see \citet{WZR20} for more details about the implementation).
+
+Our hypothesis is that as $n_1 / n_2$ increases, performing covariate alignment leads to larger accuracy improvement over the baseline HPS.
+Recall from Claim \ref{prop_covariate} that covariate shift between the data source and the target task worsens the performance of HPS.
+The effect is further exacerbated when the sample size of the data source is larger than the target task.
+%This observation highlights the need for mitigating covariate shift when $n_1 / n_2$ increases.
+To verify the hypothesis, we conduct multi-task training over all 15 pairwise tasks (among the six datasets).
+We measure the average accuracy improvement from performing covariance alignment vs. HPS (trained using stochastic gradient descent (SGD)) over the 15 task pairs.
+Figure \ref{fig_ab_cov} confirms our hypothesis.
+We observe that covariate alignment achieves up to 4\% accuracy improvement as $n_1 / n_2$ increases.
+%We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
+
+\begin{figure}[!t]
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\vspace{0pt}
+		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
+		\caption{Covariate alignment under varying sample sizes}
+		\label{fig_ab_cov}
+	\end{subfigure}\hfill
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\vspace{0pt}
+		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
+		\caption{Information transfer under varying sample sizes}
+		\label{fig_ab_data}
+	\end{subfigure}
+	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariate alignment approach proposed by \cite{WZR20}:
+	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
+	This experiment fixes $n_2 = 1000$ while varying $n_1$.
+	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.
+	On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
+    We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.}
+	\label{fig_text}
+\end{figure}
+
 %For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-%We evaluate three model choices.
 %\textit{Predicting transfer effect via STL results.}
@@
 %The results show that STL results are indicative of MTL results.
-%\paragraph{Sample size ratio.}
-First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
-On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.
 
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
-Concretely, here is one implementation of this idea.
-%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
-\begin{itemize}
-	\item We divide the training data into $S$ batches.
-	We divide the training procedure into $S$ stages. During every stage, we progressively add one more data batch.
-	\item During every stage, we train for $T$ epochs using only the $S$ batches.
-If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
-%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\end{itemize}
-If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
-%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
-The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
+\paragraph{Progressive training for mitigating model shift.}
+Inspired by our theoretical analysis, we propose a progressive training procedure that reduces the computational cost of learning HPS networks.
+To motivate this procedure, we first conduct an experiment similar to Figure \ref{fig_sec3_model_transition}) but using the text classification datasets instead.
+In Figure \ref{fig_ab_data}, we find that for multiple pairs of datasets, increasing $n_1$ improves task two's test accuracy initially, but hurts eventually.
 
-\begin{algorithm}[!t]
-	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
+These examples and the ones in Figure \ref{fig_sec3_model_transition} suggest a natural progressive training procedure that increases $n_1$ progressively until performance drops.
+Concretely, we first divide the training data into $S$ batches.
+Then, we progress in $S$ stages during training. During each stage, we progressively add one more minibatch of data from the data source(s).
+During each stage, we run SGD for $T$ epochs using only the available minibatches of data.
+We terminate once task two's validation accuracy drops compared to the previous round's result or reaches a desired threshold $\tau$.
+See Algorithm \ref{alg_inc_train} for the complete procedure.
+As an example, this procedure will terminate at the optimal value of $n_1$ if applied to the settings of Figures  \ref{fig_sec3_model_transition} and \ref{fig_ab_data}.
+In light of these observations, our hypothesis is that this procedure requires a lower computational cost compared to SGD.
+%For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
+
+\begin{algorithm}[!h]
+	\caption{Progressive training of hard parameter sharing networks}
 	\label{alg_inc_train}
 	\begin{algorithmic}[1]
-		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
-		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
-		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, W_2$ optimized for task $2$.
-		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
+		\Param A shared module $B$, and output layers $A_1, A_2$.
+		\Req Number of batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; A_2)$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, A_2$ optimized for task $2$.
+		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
 		\For{$i = 1,\dots, S$}
 		\For{$j = 1,\dots, T$}
-		\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
+		\State Minimize the cross-entropy loss of $B, A_1, A_2$ on $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$ using SGD.
 		\EndFor
-		\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
+		\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
 		\If{$a_i < a_{i-1}$ or $a_i > \tau$}
@@
 
-%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-%\squishlist
-%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-%TREC is less similar to MR because the task is about question types.
-%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
-We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
-We include all of task two's data and progressively add task one's data using the procedure described above.
-Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
+\begin{wrapfigure}[9]{r}{0.3\textwidth}
+	\vspace{0.0in}
+	\centering
+	\begin{tabular}{c c c}
+		\toprule
+		Models & Relative cost \\
+		\midrule
+		{\bf CNN}  & 30\% \\
+		{\bf LSTM} & 35\% \\
+		{\bf MLP}  & 31\%  \\
+		\bottomrule
+		\end{tabular}
+		\captionof{table}{The computational cost of running Algorithm \ref{alg_inc_train} relative to the cost of running SGD.}
+		\label{tab:taskonomy}
+	\label{fig_intro_arch}
+\end{wrapfigure}
+We evaluate Algorithm \ref{alg_inc_train} under two scenarios.
+First, we consider all $15$ pairwise tasks and use the first task as a data source to help predict the second task.
+We find that when averaged over all $15$ two-task pairs, our procedure requires less than $35\%$ of the computational cost relative to SGD while reaching the same level of test accuracy for predicting task two.
 %Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
@@
 %Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we conduct multi-task training on all six datasets jointly.
+Second, we consider using all six datasets as data sources to help predict every other task---that is, we measure the average accuracy of predicting all six tasks.
+We find that a similar progressive training style procedure requires less than $35\%$ of the computational cost for reaching the same average test accuracy compared to SGD.
+
+\medskip
+\noindent\textit{Further details.} We task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
+We include all of task two's data and progressively add task one's data using the procedure described above.
+Since the prediction accuracy has been controlled the same, we compare the computational cost.
+We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
 We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
-We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
-
-\paragraph{Covariate alignment.}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
-
-%One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
-%\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
-%where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
-%$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
-%The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
-%In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.
-
-%\section{Experimental results}
-
-%\subsection{Model width selection}
-%As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-%	\begin{subfigure}[b]{0.33\textwidth}
-%		\centering
-%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-%		\caption{Task similarity}
-%		\label{fig_ab_sim}
-%	\end{subfigure}%
-%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c)
-%	Note: (S) denotes the source task and (T) denotes the target task.}
-
-%\begin{minipage}[t]{.58\textwidth}
-%	\vspace{-0.1in}
-%	\centering
-%  \begin{tabular}{c c c c c}
-%	\toprule
-%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%		& Precision &  Recall & Precision &  Recall \\
-%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
-		% 0.3 & 1.000 & 0.004 &     - &     - \\
-%	\bottomrule
-%	\end{tabular}
-%	\vspace{0.1in}
-%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-%	\label{tab:mtl_better_than_stl}
-%\end{minipage}%
-%\quad
 
@@
 %\end{figure}
-
-\begin{figure}%[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
-		\caption{HPS vs. STL}
-		\label{fig_ab_data}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
-		\caption{HPS vs. covariance alignment}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \cite{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
-	\label{fig_text}
-%	\begin{minipage}[t]{0.4\textwidth}
-%		\centering
-%		\vspace{0pt}
-%		\begin{tabular}{c c c}
-%		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-%		& all tasks & w/o TREC \\
-%		\midrule
-%		{\bf MLP}  & 31\% & 29\% \\
-%		{\bf LSTM} & 35\% & 34\% \\
-%		{\bf CNN}  & 30\% & 28\% \\
-%		\bottomrule
-%		\end{tabular}
-%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
-%		\label{tab:taskonomy}
-%	\end{minipage}
-\end{figure}
-
-%\begin{algorithm}[!t]
-%	\caption{A progressive training schedule given two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
-%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, A_2$ optimized for task $2$.
-%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}

### 2021-07-15 revision_journal/results.tex
minor fix
finish sec 5

@@
 		\includegraphics[width=0.8\textwidth]{figures/verify_covariate_shift.eps}
-		\caption{Verify variance asymptotics in finite dimensions}
+		\caption{Illustrating variance estimates for finite $p$}
 		\label{fig_sec3_verify_cov}
@@
 		\includegraphics[width=0.8\textwidth]{figures/covariate_shift.eps}
-		\caption{Sample size ratios vs. covariate shift}
+		\caption{Sample sizes vs. covariate shift}
 		\label{fig_sec3_covariate}
 	\end{subfigure}
-	\caption{Figure \ref{fig_sec3_covariate}: we verify that Theorem \ref{thm_main_RMT} provides incredibly accurate estimates of the empirical variance under various finite sample sizes and dimensions.
-	Figure \ref{fig_sec3_covariate}: We illustrate an intriguing dichotomy between covariate shift and sample size ratio: The dimension $p = 200$, $n_2 = 800$, and the noise variance $\sigma^2 = 1/4$.}
+	\caption{We verify that Theorem \ref{thm_main_RMT} provides incredibly accurate estimates of the empirical variance under various finite sample sizes and dimensions.
+	Furthermore, we illustrate an intriguing dichotomy between sample sizes and covariate (cf. Claim \ref{claim_dichotomy}).
+	When $n_1 \ge n_2$, the lowest risk for predicting task two's labels is achieved by transferring from a dataset that has the same covariance matrix as task two. 
+	When $n_1 < n_2$, the lowest risk is instead achieved by transferring a covariate-shifted dataset.
+	Both simulation uses $\sigma = 1/2$.
+	Figure \ref{fig_sec3_verify_cov} fixes $\lambda = 4$ and varies $n_1, p$.
+	Figure \ref{fig_sec3_covariate} fixes $p = 100, n_2 = 300$ while varying $n_1, \lambda$.}
 	\label{fig_sec31}
@@
 	        \item[ii)] If $n_1 < n_2$, then $g(M)$ is maximized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
-        \end{itemize}
+        \end{enumerate}
     \end{claim}
@@
 
-Figure \ref{fig_sec3_covariate} illustrates a special case where $\lambda_1 = \cdots = \lambda_{\floor{p /2}} = \lambda > 0$ for $M^{\top}M$ and the rest of the eigenvalues are all equal to $1 / \lambda$.
+Figure \ref{fig_sec3_covariate} illustrates a special case where $\lambda_1 = \cdots = \lambda_{\floor{p /2}} = \lambda > 0$ and the rest of the eigenvalues are all equal to $1 / \lambda$.
 Thus, $\lambda > 0$ captures the degree of covariate shift: higher $\lambda$ implies worse covariate shift.
@@
 See Claim \ref{claim_model_shift} for the precise range of each regime.
-This simulation uses $p = 100, n_2 = 300, \sigma = 1/2$.}
+This simulation fixes $p = 100, n_2 = 300, \sigma = 1/2$ while varying $n_1, \mu$.}
 	\label{fig_sec3_model_shift}
@@
 \end{remark}
-
-\todo{describe comparison to the TL estimator and the weighted OLS estimator.}

### 2021-07-15 revision_journal/exp.tex
sec 4 wip

@@
 
-\subsection{Evaluating HPS under covariate and model shifts}
+This section complements our theoretical analysis of HPS with empirical evaluations.
+First, we evaluate the performance of HPS estimators against several natural transfer learning estimators.
+We show that HPS achieves superior performance under various settings of covariate and model shifts.
+Second, we provide empirical implications that are inspired by our theoretical insights for mitigating covariate and model shifts.
+One concerns a certain covariate alignment procedure for mitigating covariate shift.
+We show that such alignment procedures provide greater gains for larger regimes of $n_1 / n_2$.
+The other is a progressive training procedure for mitigating model shift.
+We show that progressively increasing the sample sizes of data sources significantly reduces the computational cost of learning HPS neural networks while achieving the same accuracy for predicting the target task.
+
+\subsection{Evaluating HPS under covariate and model shifts}\label{sec_diff}
 
@@
 	\vspace{-0.28in}
-	\caption{A hard parameter sharing architecture.}
+	\caption{A hard parameter sharing neural network.}
 	\label{fig_intro_arch}
@@
 	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariate alignment approach proposed by \cite{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	This experiment fixes $n_2 = 1000$ while varying $n_1$.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.
-	On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-    We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.}
+	\caption{
+	We extend some of our theoretical observations to text classification tasks using HPS neural networks.
+	Figure \ref{fig_ab_cov} shows that covariance alignment improves the task two's test accuracy more for larger sample size ratio $n_1 / n_2$.
+ 	Figure \ref{fig_ab_data} shows that task one provides a positive transfer to task two in HPS only for a restricted range of $n_1$ (similar to Figure \ref{fig_sec3_model_transition}).
+    Both experiments fixes $n_2 = 1000$ while varying $n_1$ from $100$ to $3000$.
+	The $y$-axis measures task two's test accuracy using HPS subtracted by its test accuracy without using task one's data.}
 	\label{fig_text}
@@
 
-%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
 %\textit{Predicting transfer effect via STL results.}
@@
 We find that when averaged over all $15$ two-task pairs, our procedure requires less than $35\%$ of the computational cost relative to SGD while reaching the same level of test accuracy for predicting task two.
-%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
 Second, we consider using all six datasets as data sources to help predict every other task---that is, we measure the average accuracy of predicting all six tasks.
@@
 \medskip
-\noindent\textit{Further details.} We task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
-We include all of task two's data and progressively add task one's data using the procedure described above.
-Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
-We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
+\noindent\textit{Further details.}
+Algorithm \ref{alg_inc_train} uses SGD during the minimization step.
+We randomly shuffle the data of both tasks and apply SGD on the shuffled data.
+For the two-task experiment, we set $\tau$ to be task two's (STL) test accuracy trained without using any other task's data.
+%We include all of task two's data and progressively add task one's data using the procedure described above.
+As a result, once Algorithm \ref{alg_inc_train} terminates, task two's test accuracy is at least $\tau$.
+For the six-task experiment, We set $\tau$ to be the average test accuracy of all six tasks trained using all tasks' data.
+We include the data from all tasks except SST. For SST, we progressively increasing its sample size similar to Algorithm \ref{alg_inc_train}.
 

### 2021-07-15 revision_journal/results.tex
sec 4 wip

@@
 
-In case (i), we provide the exact asymptotics for both the bias and variance terms, together with almost sharp convergence rates.
-We will use these results to illustrate the effects of the \emph{bias-variance tradeoff} and \emph{varying sample sizes}.
-In case (ii), we will prove an exact asymptotic variance limit, and employ the result to show the intricate effect of the covariate shift.
-On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
+We show precise estimates of the bias and variance of HPS and almost sharp convergence rates.
+In Section \ref{sec3_cov}, we characterize the variance of HPS under covariate shift, which extends the classical result from Lemma \ref{fact_tr} to the sum of two sample covariance matrices.
+We provide a detailed analysis of the impact of covariate shift on the excess risk of HPS.
+In Section \ref{sec_sizeratio}, we characterize the bias of HPS under model shift.
+Combined with the variance estimates, we describe three regimes of information transfer in the random-effect model, depending on the sample size $n_1$ and the model shift parameter $\mu$.
+Finally, Section \ref{sec3_combined} extends our results to settings with both covariate and model shift.
+%On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
 
-\subsection{Covariate shift}\label{sec_diff}
+\subsection{Covariate shift}\label{sec3_cov}
 
@@
 First, we observe that our estimates accurately match with the empirical risks.
-Second, as we vary the model shift parameter $\mu$, we observe the three information transfer regimes, as Claim \ref{claim_model_shift} suggests.
+Second, as we vary the model shift parameter $\mu$, we observe the three information transfer regimes shown in Claim \ref{claim_model_shift}.
 
-\subsection{Covariate and model shift}
+\subsection{Covariate and model shift}\label{sec3_combined}
 

### 2021-07-15 revision_journal/setup.tex
sec 4 wip

@@
 We begin by formally defining the data model involving large dimensional random matrices together with the underling assumptions.
-We define the model shift and covariate shift settings, in which we will analyze transfer learning in the next section.
-Then, we describe the estimators for the model using two-layer linear neural networks.
-Finally, we present a bias-variance decomposition of our estimators.
+We define the covariate shift and model shift settings.
+Then, we describe the HPS estimators for these settings using two-layer linear neural networks.
+Finally, we present a bias-variance decomposition of the HPS estimators.
 We explain why this decomposition is crucial for analyzing information transfer and the need for new techniques in the analysis.
@@
 \[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
-Our study of such estimators is motivated by the fact that hard paratemer sharing is widely used in empirical studies of multi-task learning \cite{R17}.
-\todo{Later on in Section \ref{sec_diff}, we will further compare the HPS estimator to other natural transfer learning estimators.}
+Our study of such estimators is motivated by the fact that hard parameter sharing is widely used in empirical studies of multi-task learning \cite{R17}.
+Later on in Section \ref{sec_diff}, we will evaluate the performance of HPS estimators against several natural transfer learning estimators.
 
-We measure the performance of $\hat{\beta}_i^{\MTL}$ through the out-of-sample predication risk (or test loss).
-Consider a datapoint $(x,y)$ generated from the same model as dataset $i$: $y= x^\top \beta^{(i)} + \ve$.
-The expected predication risk (under mean squared error) is given by
+We measure the performance of $\hat{\beta}_i^{\MTL}$ over samples $(x,y)$ generated from the $i$-th data model: $y= x^\top \beta^{(i)} + \ve$.
+The expected prediction risk (under mean squared loss) is given by
 $$\exarg{x, \varepsilon}{\left\|y-x^\top \hat{\beta}_i^{\MTL} \right\|^2}= \left\|\big(\Sigma^{(i)}\big)^{1/2} \left(\hat{\beta}_i^{\MTL} - \beta^{(i)}\right)\right\|^2 + \sigma^2.$$
-The excess risk is defined without the constant term $\sigma^2$:
+The excess risk is the difference between the above risk and the expected risk of the population risk optimizer (which is equal to $\sigma^2$):
 \be\label{HPS_loss}
@@
 \end{proof}
-%Our goal is to characterize the 
-%$The minimizers of $f(\cdot)$
-%\FY{Introduce some popular transfer learning estimators: total loss estimator, and model averaging estimator.}
 
@@
 
-\todo{edit the transition here} We show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
+\subsection{Bias and variance}
+
+%Proposition \ref{prop_large_r} suggests that the two-layer neural network provides information transfer only when $r = 1$.
+
+Next, we provide the bias-variance decomposition of the excess risk under this setting.
+Without loss of generality, we focus on task two's excess risk $L(\hat{\beta}^{\MTL}_2)$.
+As a remark, for general $r$, problem \eqref{eq_hps} is non-convex since $f(\cdot)$ is a degree-four polynomial.
+Nevertheless, the setting when $r = 1$ remains tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.
+Since $B_1$ and $B_2$ are both scalars, let $a = B_1 / B_2$.
+Let $\hat{\Sigma}(a) \define a^2 (X^{(1)})^{\top} X^{(1)} + (X^{(2)})^{\top} X^{(2)}$ be a weighted combination of the sample covariance matrices.
+We present a bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ for the setting of $r = 1$ as follows.
+We say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
+
+\begin{proposition}[Bias-variance decomposition]\label{lem_HPS_loss}
+     Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists an event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$ w.h.p.:
+    \begin{align}
+        L(\hat{\beta}_2^{\MTL}) =& \left( 1+ \OO(p^{-1/2+c})\right)\cdot \left(L_{\bias} (a) + L_{\var}(a)\right) %\nonumber\\
+        + \OO \left( p^{-C}\big( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\big)   \right), \label{L_HPS_simple}
+    \end{align}
+    where the bias and variance equations are defined as follows:
+    \begin{align}
+        L_{\bias} (a) &\define \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2,  \label{Lbias} \\
+        L_{\var}(a)   &\define \sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }}.  \label{Lvar}
+    \end{align}
+\end{proposition}
+
+Equation \eqref{L_HPS_simple} shows that the excess risk of the HPS estimator admits a clean bias-variance decomposition plus lower-order terms that decrease to zero with the dimension $p$.
+Since equation \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can apply the result to $\hat a = \hat{B}_1 / \hat{B}_2$, for any $\hat{B}_1$ and $\hat{B}_2$ that may depend on $\ve^{(1)}$ and $\ve^{(2)}$ (after solving problem \eqref{eq_hps}).
+%The proof of Proposition \ref{lem_HPS_loss} involves
+We briefly describe why Proposition \ref{lem_HPS_loss} holds.
+First, suppose that $a$ is an arbitrary value that is independent of the random noise vectors $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
+By taking the expectation over both of them, we get the following result:
+\be\label{partial-L}
+    \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}) } = L_{\bias} (\hat a) + L_{\var}(\hat a).
+\ee
+Secondly, using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
+For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of Section \ref{??}.
+To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
+Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
+The proof of Proposition \ref{lem_HPS_loss} can be found in Section  \ref{app_firstpf}.
+
+Equation \eqref{partial-L} suggests that the bias and variance of HPS both depend on the scalar $\hat a$.
+We provide some intuition about this scalar in the setting of random-effect models.
+We show that under natural assumptions, the global minimizer $\hat a = \hat B_1 / \hat B_2$ is approximately equal to $1$.
 The proof of Proposition \ref{lem_hat_v} can be found in Section \ref{app_iso_cov_prop}.
 
-\begin{proposition}[Optimum under the random-effect model]\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-    Suppose Assumption \ref{assm_big1} and the above random-effect model under equation \eqref{eq_re} holds. %in Example \ref{ex_same_cov} hold.
+\begin{proposition}[Random-effect model]\label{lem_hat_v}
+    Suppose Assumption \ref{assm_big1} and the random-effect model under equation \eqref{eq_re} holds. 
     Suppose that for a constant $c_0>0$,
@@
 \end{proposition}
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
 \todo{change $d$ to $\mu$ because a reviewer complained}
@@
 %However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-\subsection{Bias and variance}
-
-%Proposition \ref{prop_large_r} suggests that the two-layer neural network provides information transfer only when $r = 1$.
-
-Next, we provide the bias-variance decomposition of the excess risk under this setting.
-Without loss of generality, we focus on task two's excess risk $L(\hat{\beta}^{\MTL}_2)$.
-As a remark, for general $r$, problem \eqref{eq_hps} is non-convex since $f(\cdot)$ is a degree-four polynomial.
-Nevertheless, the setting when $r = 1$ remains tractable since we can write a closed-form solution of $A$ given any (scalar) $B_1$ and $B_2$.
-Since $B_1$ and $B_2$ are both scalars, let $a = B_1 / B_2$.
-Let $\hat{\Sigma}(a) \define a^2 (X^{(1)})^{\top} X^{(1)} + (X^{(2)})^{\top} X^{(2)}$ be a weighted combination of the sample covariance matrices.
-We present a bias-variance decomposition of $L(\hat{\beta}^{\MTL}_2)$ for the setting of $r = 1$ as follows.
-
-\begin{proposition}[Bias-variance decomposition]\label{lem_HPS_loss}
-     Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$ and $\lambda\in [0,1]$:
-    \begin{align}
-        L(\hat{\beta}_2^{\MTL}) =& \left( 1+ \OO(p^{-1/2+c})\right)\cdot \left(L_{\bias} (a) + L_{\var}(a)\right) %\nonumber\\
-        + \OO \left( p^{-C}\big( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\big)   \right), \label{L_HPS_simple}
-    \end{align}
-    where the bias and variance equations are defined as follows:
-    \begin{align}
-        L_{\bias} (a) &\define \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2,  \label{Lbias} \\
-        L_{\var}(a)   &\define \sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }}.  \label{Lvar}
-    \end{align}
-\end{proposition}
-
-Equation \eqref{L_HPS_simple} shows that the excess risk of the HPS estimator admits a clean bias-variance decomposition plus lower-order terms that decrease to zero with the dimension $p$.
-Since equation \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can apply the result to $a = \hat{B}_1 / \hat{B}_2$, for any $\hat{B}_1$ and $\hat{B}_2$ that may depend on $\ve^{(1)}$ and $\ve^{(2)}$ (after solving problem \eqref{eq_hps}).
-%The proof of Proposition \ref{lem_HPS_loss} involves
-We briefly describe why Proposition \ref{lem_HPS_loss} holds.
-First, suppose that $a$ is an arbitrary value that is independent of the random noise vectors$ \varepsilon^{(1)}$ and $\varepsilon^{(2)}$.
-By taking the expectation over both of them, we get the following result:
-\be\label{partial-L}
-    \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}) } = L_{\bias} (a) + L_{\var}(a).
-\ee
-Secondly, using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of Section \ref{??}.
-To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
-Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Proposition \ref{lem_HPS_loss} can be found in Section  \ref{app_firstpf}.
 %Another commonly used transfer learning estimator is defined as the minimizer of the total loss function \cite{, li2020transfer}:
@@
 
-\paragraph{Connection to information transfer.} To be precise, we say that task one provides a positive transfer to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
-Otherwise, we say that task one provides a negative transfer to task two.
+\paragraph{Connection to information transfer.} To be precise, we say that task one provides a \textit{positive transfer} to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
+Otherwise, we say that task one provides a \textit{negative transfer} to task two.
 We now illustrate that the bias-variance decomposition of Proposition \ref{lem_HPS_loss} characterizes whether or not the information transfer is positive.
@@
 
-\begin{lemma}[Variance asymtotics of OLS estimators, cf. Theorem 2.4 of \citet{isotropic} and Theorem 3.14 of \citet{DY}]\label{fact_tr}
+\begin{lemma}[Variance estimates of OLS estimators, cf. Theorem 2.4 of \citet{isotropic} and Theorem 3.14 of \citet{DY}]\label{fact_tr}
 	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
@@
 Second, characterizing variance (cf. equation \eqref{Lvar}) introduces  the issue of \textit{covariate shift}, when $\Sigma^{(1)}$ differs from $\Sigma^{(2)}$.
-Our main results in the next section provide precise bias-variance asymptotics under either (or both) shift(s).
+Our main results in the next section provide precise bias-variance asymptotics under (either or both) covariate and model shifts.

### 2021-07-16 revision_journal/exp.tex
finish sec 4 figures

@@
 This simulation uses $p = 100, n_1 = n_2 = 200, \sigma = 1/2$.
-Figure \ref{fig_sec5_cov_model} uses $\lambda = 4$ for generating covariate-shifted data.}
+Figure \ref{fig_sec5_cov_model} uses $\lambda = 4$ for generating covariate-shifted features.}
 	\label{fig_sec51}
@@
 
-Figure \ref{fig_sec51} shows the result under (either or both) covariate and model shift.
+Figure \ref{fig_sec51} shows the result under (either or both) covariate and model shifts.
 Figure \ref{fig_sec5_covariate} uses the same data generating process as Figure \ref{fig_sec31}.
 Figure \ref{fig_sec5_model} uses the same data generating process as Figure \ref{fig_sec3_model_shift}.
-Figure \ref{fig_sec5_cov_model} further combines the covariate-shifted data and the model shift setting.
-For reach run, we average the result over 100 random seeds because of high variance from using only a limited number of samples.
+Figure \ref{fig_sec5_cov_model} combines both by generating covariate-shifted features and different linear models for each dataset.
+For reach run, we average the result over 100 random seeds because of high variance from the small sample sizes.
 We find that HPS outperforms all the other estimators in this simulation (the result for the TL estimator is worse than STL and is omitted from the figure).

### 2021-07-16 revision_journal/results.tex
finish sec 4 figures

@@
 
-Equation \eqref{lem_cov_shift_eq} thus characterizes the variance of the HPS estimator, up to an error term on the order of $O\big(\frac{\sigma^2}{p^{-1/2}}\big)$ (recall that $\varphi > 4$, $c$ is an arbitrarily small constant, $\frac{p}{n_1+n_2} \in (2 {\tau}, \frac 2 {\tau})$).
-Our result can be viewed as a generalization of the classical result in Lemma \ref{fact_tr} to the \textit{covariate shift} setting.
-In particular, Lemma \ref{fact_tr} corresponds to a setting where the singular values $\lambda_1,\dots,\lambda_p$ are all equal to one, and $a = 1$.
-Then, the second part of equation \eqref{eq_a12extra} simplifies to
+Equation \eqref{lem_cov_shift_eq} thus characterizes the variance of the HPS estimator, up to an error term on the order of $O\big(\frac{\sigma^2}{p^{1/2}}\big)$ (recall that $\varphi > 4$, $c$ is an arbitrarily small constant, and $\frac{p}{n_1+n_2} \le \frac 1 {2 + 2\tau}$).
+Theorem \ref{thm_main_RMT} generalizes the classical result from Lemma \ref{fact_tr} to the sum of two independent sample covariance matrices.
+To see this, we note that Lemma \ref{fact_tr} corresponds to a setting where the singular values $\lambda_1,\dots,\lambda_p$ (of the matrix $M$) are all equal to one, and $a = 1$.
+In this setting, the second part of equation \eqref{eq_a12extra} simplifies to
 \[ \alpha_1 + \frac{p}{n_1 + n_2}\cdot \frac{\alpha_1}{\alpha_1 + \alpha_2} = \frac{n_1}{n_1 + n_2}. \]
-By solving the above together with the first part of equation \eqref{eq_a12extra}, we obtain that
+By solving the above equation and the first part of equation \eqref{eq_a12extra}, we obtain that
 $$\alpha_1 = \frac{n_1}{n_1+n_2},\quad \alpha_2 = \frac{n_2-p}{n_1+ n_2}.$$
-Plugging the above solutions back to the variance limit, we thus find that the limit is equal to
+Plugging the solutions of $\alpha_1, \alpha_2$ back to the LHS of equation \eqref{lem_cov_shift_eq}, we thus find that
 \begin{align}
-    \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}} &= \frac{\sigma^2}{n_1 + n_2} \frac{p}{\alpha_1 + \alpha_2} \tag{since the singular values of $M$ are equal to $1$} \nonumber \\
-    &= \frac{\sigma^2}{n_1 + n_2} \cdot\frac{p (n_1 + n_2)}{n_1 + n_2 - p} \tag{applying $\alpha_1$ and $\alpha_2$ from above} \nonumber \\
+    \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}} &= \frac{\sigma^2}{n_1 + n_2} \frac{p}{\alpha_1 + \alpha_2} \tag{since $\lambda_i = 1$ for all $i=1,\dots,p$} \nonumber \\
+    &= \frac{\sigma^2}{n_1 + n_2} \cdot\frac{p (n_1 + n_2)}{n_1 + n_2 - p} \tag{applying the solutions of $\alpha_1$ and $\alpha_2$} \nonumber \\
     &= \frac{\sigma^2 p}{n_1 + n_2 - p}, \label{g_id}
@@
 which is precisely the limit in Lemma \ref{fact_tr}.
-Additionally, the convergence rate in equation \eqref{lem_cov_shift_eq} matches the one in Lemma \ref{fact_tr} for this special case.
+Additionally, the convergence rate in equation \eqref{lem_cov_shift_eq} matches the rate in Lemma \ref{fact_tr} for this particular setting.
 %With Assumption \ref{assm_big1},
@@
 \begin{proof}
-    We can write down the trace of $(\alpha_1 M^{\top} M + \alpha_2)^{-1}$ using the eigenvalues of $M^{\top} M$ as follows:
+    We can write the trace of $(\alpha_1 M^{\top} M + \alpha_2)^{-1}$ using the eigenvalues of $M^{\top} M$ as follows:
     \begin{align*}
-        (\alpha_1 M^{\top} M + \alpha_2)^{-1} &= \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2} \\
+        \bigtr{(\alpha_1 M^{\top} M + \alpha_2)^{-1}} &= \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2} \\
         &\ge \sum_{i=1}^p \frac{1} {\alpha_1 \lambda_i^2 + \alpha_2 \cdot {\lambda_i^2} / {\tau^2}} \tag{since $\lambda_i \ge \tau$, for any $i$} \\
@@
 \]
-Thus, using that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))\mu^2$ w.h.p., we conclude that for the random-effect model, the excess risk $L(\hat{\beta}_2^{\MTL}$ is approximately equal to
+Thus, using that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (2+\oo(1))\mu^2$ w.h.p., we conclude that for the random-effect model, the excess risk $L(\hat{\beta}_2^{\MTL})$ is approximately equal to
 $$ g(n_1) \define \sigma^2 \cal L_1(1) +   2\mu^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2\mu^2 \cdot \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}$$
 plus lower order terms (that vanishes to zero as $p$ goes to infinity).
-Next, we provide a detailed analysis of when combining task one using HPS transfers positively to task two, depending on sample sizes $n_1, n_2$, and model shift $\mu$.
+Next, we analyze when combining task one using HPS transfers positively to task two, depending on sample sizes $n_1, n_2$, and the model shift parameter $\mu$ in the random-effect model.
 
@@
 As a remark, when $p < n_2 < 3p$, similar results can be derived using the above arguments (details omitted).
-Figure \ref{fig_sec3_model_shift} illustrates Claim \ref{claim_model_shift} for different regimes of model shift.
-First, we observe that our estimates accurately match with the empirical risks.
-Second, as we vary the model shift parameter $\mu$, we observe the three information transfer regimes shown in Claim \ref{claim_model_shift}.
+Figure \ref{fig_sec3_model_shift} illustrates Claim \ref{claim_model_shift} for different regimes of model shift parameter $\mu$ in the random-effect model.
+This simulation affirms that our estimates accurately match with the empirical bias equation \eqref{Lbias} plus the variance equation \eqref{Lvar}.
+Furthermore, we observe the three information transfer regimes shown in Claim \ref{claim_model_shift} by varying $\mu$ in the random-effect model.
 

### 2021-07-17 revision_journal/exp.tex
finish sec 4

@@
 
-\begin{figure}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
-		\caption{Covariate alignment under varying sample sizes}
-		\label{fig_ab_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
-		\caption{Information transfer under varying sample sizes}
-		\label{fig_ab_data}
-	\end{subfigure}
-	\caption{
-	We extend some of our theoretical observations to text classification tasks using HPS neural networks.
-	Figure \ref{fig_ab_cov} shows that covariance alignment improves the task two's test accuracy more for larger sample size ratio $n_1 / n_2$.
- 	Figure \ref{fig_ab_data} shows that task one provides a positive transfer to task two in HPS only for a restricted range of $n_1$ (similar to Figure \ref{fig_sec3_model_transition}).
-    Both experiments fixes $n_2 = 1000$ while varying $n_1$ from $100$ to $3000$.
-	The $y$-axis measures task two's test accuracy using HPS subtracted by its test accuracy without using task one's data.}
-	\label{fig_text}
-\end{figure}
-
 %\textit{Predicting transfer effect via STL results.}
@@
 
+\begin{figure}[!t]
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\vspace{0pt}
+		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
+		\caption{Covariate alignment under varying sample sizes}
+		\label{fig_ab_cov}
+	\end{subfigure}\hfill
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\vspace{0pt}
+		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
+		\caption{Information transfer under varying sample sizes}
+		\label{fig_ab_data}
+	\end{subfigure}
+	\caption{
+	We extend some of our theoretical observations to text classification tasks using HPS neural networks.
+	Figure \ref{fig_ab_cov} shows that covariance alignment improves the task two's test accuracy more for larger sample size ratio $n_1 / n_2$.
+ 	Figure \ref{fig_ab_data} shows that task one provides a positive transfer to task two in HPS only for a restricted range of $n_1$ (similar to Figure \ref{fig_sec3_model_transition}).
+    Both experiments fixes $n_2 = 1000$ while varying $n_1$ from $100$ to $3000$.
+	The $y$-axis measures task two's test accuracy using HPS subtracted by its test accuracy without using task one's data.}
+	\label{fig_text}
+\end{figure}
+
 \begin{algorithm}[!h]
@@
 	\begin{algorithmic}[1]
-		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
+		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$, divided into a training, validation, and test set.
 		\Param A shared module $B$, and output layers $A_1, A_2$.
-		\Req Number of batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; A_2)$, a threshold $\tau\in(0,1)$.
-		\Output The trained modules $B, A_2$ optimized for task $2$.
-		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
+		\Req Number of batches $S$, epochs $T$, a threshold $\tau\in(0,1)$.
+		\Output The trained modules $B, A_2$ optimized for task two.
+		\State Divide the training set of $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
 		\For{$i = 1,\dots, S$}
 		\For{$j = 1,\dots, T$}
-		\State Minimize the cross-entropy loss of $B, A_1, A_2$ on $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$ using SGD.
+		\State Minimize the cross-entropy loss of $B, A_1, A_2$ on  $\set{(x^{(k)}, y^{(k))}}_{k=1}^i$ and the training set of $(X^{(2)}, Y^{(2)})$ using SGD.
 		\EndFor
-		\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
+		\State Let $a_i$ be the current validation accuracy for task two.
 		\If{$a_i < a_{i-1}$ or $a_i > \tau$}
@@
 
-\begin{wrapfigure}[9]{r}{0.3\textwidth}
-	\vspace{0.0in}
+\smallskip
+\begin{wrapfigure}[10]{r}{0.26\textwidth}
+	\vspace{-0.15in}
 	\centering
@@
 \end{wrapfigure}
-We evaluate Algorithm \ref{alg_inc_train} under two scenarios.
-First, we consider all $15$ pairwise tasks and use the first task as a data source to help predict the second task.
-We find that when averaged over all $15$ two-task pairs, our procedure requires less than $35\%$ of the computational cost relative to SGD while reaching the same level of test accuracy for predicting task two.
-Second, we consider using all six datasets as data sources to help predict every other task---that is, we measure the average accuracy of predicting all six tasks.
-We find that a similar progressive training style procedure requires less than $35\%$ of the computational cost for reaching the same average test accuracy compared to SGD.
+We evaluate Algorithm \ref{alg_inc_train} in two scenarios.
+First, we consider transferring from single data source to a target task.
+We evaluate over all $15$ two-task pairs.
+We find that when averaged over all the pairs, our procedure requires less than $35\%$ of the computational cost relative to SGD while reaching the same level of test accuracy for predicting task two.
+Second, we consider transferring from multiple data sources.
+We use all six datasets as data sources to help predict every other task---that is, we measure the average accuracy of predicting all six tasks.
+We find that a similar progressive training style procedure requires less than $35\%$ of the computational cost (relative to the cost of running SGD) for reaching the same average test accuracy of SGD.
 
@@
 %We include all of task two's data and progressively add task one's data using the procedure described above.
-As a result, once Algorithm \ref{alg_inc_train} terminates, task two's test accuracy is at least $\tau$.
+%As a result, once Algorithm \ref{alg_inc_train} terminates, task two's test accuracy is at least $\tau$.
 For the six-task experiment, We set $\tau$ to be the average test accuracy of all six tasks trained using all tasks' data.

### 2021-07-17 revision_journal/multitask.tex
wip
finish sec 5
finish sec 4 figures
finish sec 4

@@
 Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments up to any order (cf. equation \eqref{eq_highmoments}).
-Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from any other $\beta^{(j)}$ for $j \neq i$, the matrix $X$, and $\varepsilon^{(j)}$ for any $j$.
+Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from any other $\beta^{(j)}$ for $j \neq i$, the matrix $X$, and $\varepsilon^{(j)}$ for any $j=1,\dots,t$.
 
@@
 Let $(\hat A, \hat B)$ denote a global minimizer of $f(A, B)$.
-We define the HPS estimator for task $t$ as $\hat \beta_t^{\MTL} := \hat B \hat A_i$, where $\hat A_i$ denotes the $i$-th column of $\hat A$.
-We evaluate the performance of $\hat{\beta}_t^{\MTL}$ according to its excess risk:
+We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B \hat A_i$, where $\hat A_i$ denotes the $i$-th column of $\hat A$.
+We evaluate the performance of $\hat{\beta}_i^{\MTL}$ according to its excess risk:
 \be\label{ith_loss}
-    L_t(\hat{\beta}_t^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta}^{\MTL}_t - \beta^{(t)}\right)}^2.
+    L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta}^{\MTL}_i - \beta^{(i)}\right)}^2.
 \ee
@@
 Let $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ be the concatenated model vectors of all tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ be the best rank-$r$ approximation of ${B^{\star}}^\top\Sigma B^{\star}$ in the following sense:
+Let $A^{\star} {A^{\star}}^{\top}$ be the best approximation of ${B^{\star}}^\top\Sigma B^{\star}$ in the set of rank-$r$ subspaces:
 \begin{align}\label{eq_A_star}
-	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
+	A^{\star} \define \argmax{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
 \end{align}
@@
 Let $a_i^{\star}\in\real^r$ be the $i$-th column vector of $A^{\star}{A^{\star}}^{\top}$.
-We characterize the excess risk $L_t(\hat{\beta}_t^{\MTL})$ precisely in the following result.
+We show a precise estimate of $L_i(\hat{\beta}_i^{\MTL})$ based on $a_i^{\star}$ as follows.
 
@@
 Suppose the multi-task setting according to equation \eqref{eq_mtl_data} holds.
-Let $r$ be any positive integer less than $t$.
+Let $r < t$ be a positive integer.
 Suppose the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than its $(r+1)$-th largest eigenvalue. 
-Let $c>0$ be an arbitrary (small) constant.
-The following estimates for $L_t(\hat{\beta}_t^{\MTL})$ holds with high probability:
+Let $c>0$ be an arbitrarily (small) constant.
+The following estimate of $L_i(\hat{\beta}_i^{\MTL})$ holds w.h.p., for any $i = 1,\dots,t$:
 \begin{align}
-	\bigabs{L_t(\hat{\beta}_t^{\MTL}) - L_t(B^{\star}a_t^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_t^{\star}}^2  } 
-	\le  \sqrt{\bignorm{{B^\star}^\top\Sigma B^\star}_{\op} \cdot n^{-\frac 1 2+ \frac 2{\varphi} + c}  + \sigma^2 n^{-\frac 1 2 + c}} \cdot \frac{\bignorm{{B^\star}^\top\Sigma B^\star}_{\op}+  \sigma^2}{\lambda_r - \lambda_{r+1}}.
+	\bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p} \cdot \norm{a_i^{\star}}^2} 
+	\le  \sqrt{\norm{{B^\star}^\top\Sigma B^\star}_{2} \cdot n^{-\frac 1 2+ \frac 2{\varphi} + c}  + \sigma^2 n^{-\frac 1 2 + c}} \cdot \frac{\norm{{B^\star}^\top\Sigma B^\star}_{2}+  \sigma^2}{\lambda_r - \lambda_{r+1}}.
 \label{Li_multi1}
@@
 Recall that $\varphi > 4$ according to Assumption \ref{assm_big1}, thus, $\frac {2}{\varphi} \le \frac 1 2$ and $n^{-\frac 1 2 + \frac 2 {\varphi} + c}$ vanishes to zero for a small enough constant $c$.
-Therefore, equation \eqref{Li_multi1} precisely characterizes the excess risk of the HPS estimator.
-As a remark, the same result applies to any other tasks although we have focused on predicting task $t$.
-Theorem \ref{thm_many_tasks} significantly extends the two-task model shift setting of Theorem \ref{cor_MTL_loss}.
-The term $L_t(B^{\star} a_t^{\star})$ captures the bias of the HPS estimator and $\frac{p \sigma^2}{n - p} \bignorm{a_t^{\star}}^2$ captures the estimator's variance.
+Thus, $L_i(B^{\star} a_i^{\star}) + \frac{p\sigma^2}{n - p} \norm{a_i^{\star}}^2$ is the limit of $L_i(\hat{\beta}_i^{\MTL})$ as $p$ approaches infinity---$L_i(B^{\star} a_i^{\star})$ is the limiting bias of $\hat{\beta}_i^{\MTL}$ and $\frac{p \sigma^2}{n - p} \bignorm{a_i^{\star}}^2$ is its limiting variance.
+The proof of Theorem \ref{thm_many_tasks}, which characterizes the global minimum of problem \eqref{eq_mtl_same_cov} through a connection to PCA, can be found in Section \ref{app_proof_error_same_cov}.
+%We also point out that equation \eqref{Li_multi1} similarly applies to any other task $t' \neq t$.
 %The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
@@
 %	\end{align}
-The proof of Theorem \ref{thm_many_tasks}, which is based on a characterization of the global minimum of problem \eqref{eq_mtl_same_cov}, can be found in Section  \ref{app_proof_error_same_cov}.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/same_covariates.eps}
-		\caption{Example \ref{ex_same_cov}}
-		\label{fig_same_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{figures/same_covariates.eps}
-		\caption{Example \ref{ex_sample_ratio}}
-		\label{fig_width}
-	\end{subfigure}
-%	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-%	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
-%	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-%	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-%	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
-%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-%	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-%	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
-%	\label{fig_model_shift_phasetrans}
-\end{figure*}
 
@@
 
-\begin{example}[How to set the width $r$ in HPS?]
-\label{ex_same_cov}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-An important question in applications of HPS is how to set the width $r$ of the feature layer.
-We use our estimates to show that the optimal width depends on the tradeoff between the estimator's bias and variance.
-Concretely, consider a random-effect model where all tasks share a model vector $\beta_0$ plus perturbations.
-For every $i=1,2,\cdots, t,$, $\beta^{(i)} = \beta_0 + \wt \beta^{(i)}$, where $\wt \beta^{(i)}$ denotes the $i$-th task-specific component whose entries are i.i.d.
-Gaussian random variables of mean zero and variance $\frac {\kappa^2} p$.
-
-\begin{claim}
+\paragraph{Illustrative examples.}
+We give an example of our estimate in the random-effect model.
+In this setting, the model vector of every task is the sum of a shared vector $\beta_0$ plus a task-specific component $\wt \beta^{(i)}$:
+\begin{align}
+    \beta^{(i)} = \beta_0 + \wt \beta^{(i)}, \text{ for every } i=1,2,\cdots, t, \label{eq_re_mt}
+\end{align}
+where every entry of $\wt \beta^{(i)}$ is drawn i.i.d. from a Gaussian distribution with zero mean and ${\mu^2}/p$ variance.
+Thus, $\mu$ is a parameter for modeling the difference between different tasks.
+We study two fundamental questions in this setting.
+First, what should the width ($r$) of the feature layer $B$ be?
+Second, when does HPS transfer positively to a particular task, depending the sample size $n$ and the (model shift) parameter $\mu$?
+Since all tasks are symmetric in this setting, we analyze the average (limiting) risk
+\[ g_r(n, \mu) = \frac {1}{t} \sum_{i=1}^t \big(L_i(B^{\star} a_i^{\star}) + \frac{p \sigma^2}{n - p} \cdot \norm{a_i^{\star}}^2\big). \]
+We address both questions by characterizing $g_r(n, \mu)$, which accurately approximates $\frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL})$ according to Theorem \ref{thm_many_tasks}.
+Recall from Lemma \ref{lem_hat_v} that the excess risk of the OLS estimator satisfies that $L_i(\hat{\beta}_i^{\STL}) = \frac{\sigma^2 p}{n - p} + o_p(1)$, in which $o_p(1)$ vanishes to zero as $p$ approaches infinity.
+We compare $g_r(n, \mu)$ with the OLS estimate in the following claim.
+\begin{claim}[Choosing $r$ for HPS in the random-effect model]\label{claim_re_multi}
+    Suppose the multi-task setting with random-effect linear models under equation \eqref{eq_mtl_data} and \eqref{eq_re_mt} holds.
+    Let $\epsilon = o_p(\norm{\beta_0}^2 + \mu^2)$ be a small error term that decreases to zero as $p$ goes to infinity.
+    Let $r \in [1, r]$.
+    W.h.p. over the randomness of $B^{\star}$, the following holds:
     \begin{enumerate}
-	\item {\bf Positive vs.
-negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
-
-	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
-Hence increasing the width $r$ of the shared feature representation layer does not help.
+        \item[i)] If $\mu^2 \ge \frac{\sigma^2 p^2}{(n - p) \tr[\Sigma]}$, then $g_r(n, \mu) \ge \frac{\sigma^2 p}{n - p} + \epsilon$, for any $1\le r < t$.
+    	\item[i)] If $\mu^2 < \frac{\sigma^2 p^2}{(n - p)\tr[\Sigma]} - \frac{t p}{\bigtr{\Sigma}} \epsilon$, then $g_r(n, \mu)$ is minimized when $r=1$.
+    	Additionally, $g_1(n, \mu) \le \frac{\sigma^2 p}{n - p} + \epsilon$.
     \end{enumerate}
@@
 \begin{proof}
-    In this random-effect model, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}),
-    %Based on the definition of the random-effect model,
-    the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
-    %\begin{align*}
-    %	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
-    %\end{align*}
+    We first simplify the expression of $g_r(n, \mu)$ using its definition
+    \begin{align*}
+        g_r(n, \mu) &= \frac 1 t \sum_{i=1}^t \big(L_i(B^{\star} a_i^{\star}) + \frac{p\sigma^2}{n - p} \cdot \norm{a_i^{\star}}^2\big) \\
+        &= \Big(\frac 1 t \sum_{i=1}^t \bignorm{\Sigma^{1/2} (B^{\star} a_i^{\star} - \beta^{(i)})}^2 \Big)
+        + \Big(\frac 1 t \sum_{i=1}^t \frac{p\sigma^2}{n - p} \cdot \norm{a_i^{\star}}^2 \Big) \\
+        &= \frac 1 t \bignormFro{\Sigma^{1/2} (B^{\star} A^{\star} - B^{\star})}^2 + \frac{r}{t} \cdot \frac{p\sigma^2}{n - p}.
+    \end{align*}
+    In the last step, we use the matrix notation to write the sum for the first part.
+    We use the fact that $\sum_{i=1}^t \norm{a_i^{\star}}^2 = r$ because $A^{\star} = [a_1^{\star}, \dots, a_t^{\star}]$ satisfies that ${A^{\star}}^{\top} A^{\star} = \id_{p\times p}$ following its definition in equation \eqref{eq_A_star}.
+    Using this condition on $A^{\star}$, we further get that
+    \begin{align*}
+        \bignormFro{\Sigma^{1/2}(B^{\star} A^{\star} - B^{\star})}^2
+        = \bigtr{{B^{\star}}^{\top} \Sigma B^{\star} (\id_{p \times p} - A^{\star}{A^{\star}}^{\top})},
+    \end{align*}
+    which is precisely equal to the smallest $(t - r)$ eigenvalues of ${B^{\star}}^{\top}\Sigma B^{\star}$.
+    Using the concentration of Gaussian random vectors in Lemma \ref{largedeviation}, w.h.p. the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to
     \begin{align}\label{betaSbeta}
-    	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
+    	{\beta^{(i)}}^{\top}\Sigma  {\beta^{(j)}} =\beta_0^\top \Sigma \beta_0 + \delta_{i,j} \frac{\mu^2 }{p}\bigtr{\Sigma} + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} \mu^2\right)
     \end{align}
-     with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}.
-    %Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
-    With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by
-    $$\lambda_1=\left[1+\OO(p^{-1/2+c})\right]\cdot\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
-    and
-    $$ \lambda_i=\left[1+\OO(p^{-1/2+c})\right]\cdot \frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
-    Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
-    $$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
-    with high probability.
+    for any constant $c>0$, where $\delta_{i,j} = 1$ if and only if $i = j$.
+    Thus, ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to a rank-$1$ matrix with (spectral) norm $t\cdot \beta_0^{\top} \Sigma \beta_0$ plus Gaussian perturbation.
+    Using the concentration result of Lemma \ref{largedeviation} \todo{check}, we have that
+    \begin{align*}
+        \lambda_1 &= \Big(1+\OO(p^{-1/2+c})\Big)\cdot\left(t\cdot \beta_0^\top \Sigma \beta_0  + \frac{\mu^2}{ p}\bigtr{\Sigma}\right) , \text{ and } \\
+        \lambda_i &= \Big(1+\OO(p^{-1/2+c})\Big)\cdot \frac{\mu^2}{ p}\bigtr{\Sigma}, \text{ for } i=2,\cdots, t.
+    \end{align*}
+    Thus, w.h.p. the sum of smallest $(t - r)$ eigenvalues of ${B^{\star}}^{\top}\Sigma  B^{\star}$ is equal to
+    $(1+\OO(p^{-1/2+c}))\cdot(t-r)\frac{\mu^2 \bigtr{\Sigma}}{p}$.
+    Let $\epsilon = o_p(1)$ denote the error term.
     %To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
@@
     %We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
-    Then using \eqref{Li_multi2}, we obtain that
-    \[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p.
-}\]
-    %We describe a proof sketch.
-    %First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
-    %\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
-    %Second, using Fact \ref{fact_tr}, one can see that the average variance is
-    %\begin{align*}
-    %	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
-    %	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
-    %\end{align*}
-    %because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
-    %Combined together, we have derived the average prediction loss in the random-effect model.
-    %If the error is sufficiently small, then
-    %Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
-    %Comparing HPS to STL, we have the following qualitative properties.
-    %	Suppose $n$ is sufficiently large so that the error is negligible.
+    We conclude that w.h.p.,
+    \begin{align}
+        g_r(n, \mu) - \frac{\sigma^2 p}{n - p} &= \bigbrace{1 - \frac{r}{t}} \frac{\mu^2}{p}\bigtr{\Sigma} + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} + \epsilon - \frac{\sigma^2 p}{n - p} \nonumber \\
+        &= \Big(1 - \frac r t\Big) \cdot \Big(\frac{\mu^2\bigtr{\Sigma}}{p} - \frac{p\sigma^2}{n - p}\Big) + \epsilon. \label{eq_re_final}
+    \end{align}
+    Now we are ready to finish the proof.
+    For claim i), if $\mu^2 \ge \frac{\sigma^2 p^2}{(n - p) \bigtr{\Sigma}}$, the coefficient of $(1 - \frac r t)$ in equation \eqref{eq_re_final} is non-negative, and claim i) follows.
+    For claim ii), if $\mu^2 < \frac{\sigma^2 p^2}{(n - p)\bigtr{\Sigma}} - \frac{p t}{\bigtr{\Sigma}}\epsilon$, the coefficient of $(1 - \frac r t)$ in equation \eqref{eq_re_final} is negative.
+    Furthermore, equation \eqref{eq_re_final} is minimized when $r = 1$, and claim ii) follows since the RHS of equation \eqref{eq_re_final} is at most $\epsilon$.
 \end{proof}
-\end{example}
 
-%We demonstrate the accuracy of our results in simulations.
-%While our theory is asymptotic (with error terms that are negligible when $p$ is sufficiently large), we observe that they are incredibly accurate in a moderate dimension of $p = 200$.
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/multitask_width.eps}
+		\caption{Varying width}
+		\label{fig_sec4_width}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/multitask_transfer.eps}
+		\caption{Varying sample size and model shift parameter}
+		\label{fig_sec4_transfer}
+	\end{subfigure}
+	\caption{We illustrate the performance of HPS in the random-effect model with $p = 100, t = 10, \sigma = 1/2$.
+	Figure \ref{fig_sec4_width} shows that from $1$ to $t = 10$, setting width $r = 1$ gives the lowest excess risk for task $t$.
+	The result is averaged over three random seeds.
+	This simulation uses $\mu = 0.05$.
+	Figure \ref{fig_sec4_transfer} fixes $r = 1$ while varying $\mu$ and $n$.
+We observe that depending on $\mu$ and $n$, HPS may provide a positive transfer or a negative transfer to task $t$ (similar to Figure \ref{fig_sec3_model_shift}).
+The precise condition for deciding which one is provided in Claim \ref{claim_re_multi}.}
+	\label{fig_sec4}
+\end{figure}
 
-First, we validate the result of Example \ref{ex_same_cov}.
-Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
-In all the parameter settings, our results estimate the empirical losses accurately.
-We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
-Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
-%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
-Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level.
-%\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
-For example, at the cross point, this ratio is 1.
-}
-
-%Our result from Corollary \ref{cor_MTL_loss} explains this trend.
-
-%Covariate shift: We set $\kappa = 1$ and $d = 0$.
-%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-
-%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-%\begin{table}
-%	\begin{center}
-%		\begin{tabular}{c c c c c}
-%			\toprule
-%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
-%			\midrule
-%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-			% {\bf CNN}  & 76\% & - & 32\% & -\\
-%			\bottomrule
-%		\end{tabular}
-%	\end{center}
-%	\caption{Taskonomy experiment.}
-%	\label{tab:taskonomy}
-%\end{table}
-%\begin{figure}[!t]
-%	\centering
-%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
-%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
-%	\label{fig_same_cov}
-%\end{figure}
-
-%The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L_2(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-%It is not hard to extend the above result to the cases with more than two tasks.
-We make this extension for the following reasons.
-First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
-Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-
-%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-%\medskip
-%
-%\noindent\textbf{Comparison to single-task learning (STL).}
-%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
-%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
-%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
-%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.
+Figure \ref{fig_sec4} validates Claim \ref{claim_re_multi}.
+First, we see that the empirical excess risk (measured on a particular task) is indeed smallest when the width $r$ is equal to $1$.
+Second, we see that HPS provides a positive transfer (to a particular task) depending on the sample size $n$ and the model shift parameter $\mu$.
+The results match with the condition (on $\mu$) suggested by our estimates.
 

### 2021-07-17 revision_journal/results.tex
finish sec 4

@@
 \end{remark}
+
+Consider the special case with $\Sigma^{(2)}=\id$, $a=1$ and the random effect model. Let $\sigma_i^{(1)}$ be the eigenvalues of $\Sigma^{(1)}$. Define the function 
+\be\label{g1new} g_0(x)= \frac{1}{n_1}\sum_{i=1}^p \frac{\sigma_i^{(1)}}{1+ \sigma_i^{(1)} x} -\frac{1}{x} .\ee
+Let $y$ be the unique positive solution to the equation 
+\be\nonumber
+\frac{n_1+n_2-p}{n_1} + g_0(y) \cdot \left( 1+    y\right)=0 .
+\ee
+Define the following three functions of $y$:
+$$f_1= \frac{n_1}{p}y + \frac{n_1-p}{p}\frac1{g_0(y)},\quad f_2= \frac{n_1}{p}\frac{1}{g_0'(y)}- \frac{n_1-p}{p}\frac1{[g_0(y)]^2},\quad f_3= - g_0(y),$$
+where $g_0'(y)$ is the derivative
+$$ g_0'(y)=  -\frac{1}{n_1}\sum_{i=1}^p \frac{(\sigma_i^{(1)})^2}{(1+ \sigma_i^{(1)} y)^2} +\frac{1}{y^2}. $$
+Then the variance limit is given by
+$$ L_{\var}(1)=\sigma^2 \frac{p}{n_1}f_1,$$
+and the bias limit is given by 
+$$ L_{\bias}(1)=2\mu^2 \frac{1 - 2f_1 f_3  +f_2 f_3^2  }{ 1 - \frac{p}{n_2}f_2 f_3^2 }.$$
+(Here $2\mu^2$ represents $\|\beta^{(1)}-\beta^{(2)}\|^2$.)

### 2021-07-17 revision_journal/results.tex
figs for sec 3.3

@@
 		\includegraphics[width=0.8\textwidth]{figures/covariate_shift.eps}
-		\caption{Sample sizes vs. covariate shift}
+		\caption{Varying the covariate shift parameter $\lambda$}
 		\label{fig_sec3_covariate}
@@
 
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_a.eps}
+		\caption{Varying sample size under covariate shift}
+		\label{fig_sec3_cov_mo_a}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_b.eps}
+		\caption{Varying sample size under model shift}
+		\label{fig_sec3_cov_mo_b}
+	\end{subfigure}
+	\caption{We further show that our observations in Figures \ref{fig_sec31} and \ref{fig_sec3_model_shift} extend to settings with both covariate and model shift.
+	Both simulation use $p = 100, n_2 = 300, \sigma = 1/2$.
+	Figure \ref{fig_sec3_cov_mo_a} fixes $\mu = 0.1$ while varying $\lambda, n_1$.
+	Figure \ref{fig_sec3_cov_mo_b} fixes $\lambda = 4$ while varying $\mu, n_1$.}
+	\label{fig_sec33}
+\end{figure}
+
 Consider the special case with $\Sigma^{(2)}=\id$, $a=1$ and the random effect model. Let $\sigma_i^{(1)}$ be the eigenvalues of $\Sigma^{(1)}$. Define the function 

### 2021-07-20 revision_journal/results.tex
start intro

@@
 %Taking the derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
+\todo{can we add a few sentences to describe any technical challenge here? right now it sounds like our result is a direct corollary, which is not good?}
 The complete proof of Theorem \ref{cor_MTL_loss} can be found in Section \ref{app_iso_cov}.
@@
 		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_a.eps}
-		\caption{Varying sample size under covariate shift}
+		\caption{Fixed $\mu$, different $\lambda$}
 		\label{fig_sec3_cov_mo_a}
@@
 		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_b.eps}
-		\caption{Varying sample size under model shift}
+		\caption{Fixed $\lambda$, different $\mu$}
 		\label{fig_sec3_cov_mo_b}

### 2021-07-22 revision_journal/abstract.tex
intro wip

@@
-\iffalse
-\begin{frontmatter}
-
-\title{Precise Asymptotics of Transferring from Different Regression in High Dimensions}
-
-\runtitle{Precise Asymptotics of Transferring from Different Regression}
-
-\begin{aug}
-	\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{}},
-	\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2]{}},
-	\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3]{}},\\
-	\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4]{}},
-	\and
-	\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5]{}}
-	\address{${ }^{1}$University of Pennsylvania, ${ }^{2}$Northeastern University, ${ }^{3}$Stanford University
-}
-\end{aug}
-\fi
-
 \begin{abstract}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
+%	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
 This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
@@
 \end{abstract}
-
-%\begin{keyword}[class=MSC2020]
-%\kwd[Primary ]{62J05}
-%\kwd{60B20}
-%\kwd[; secondary ]{62E20, 62H10}
-%\end{keyword}
-
-%\begin{keyword}
-%\kwd{Transfer learning, random matrix theory, covariate shift, sample covariance matrices.}
-%\end{keyword}
-
-%\end{frontmatter}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please use \tableofcontents for articles %%
-%% with 50 pages and more                   %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\tableofcontents

### 2021-07-22 revision_journal/intro.tex
intro wip

@@
 
-Many modern machine learning methods
+%Many modern machine learning methods
 %Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
-Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
+%Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
+%It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
+%Often, hard parameter sharing offers two critical advantages if successfully applied.
+%First, it reduces model parameters since all tasks use the same feature space.
+%Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
 
-Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impact HPS has not been well established.
+%Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
+%For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
+%Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
+%However, how these dataset properties impact HPS has not been well established.
 %It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
+%Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
+%Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
 %For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
 
-\begin{figure*}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Covariate shift}
-		\label{fig_intro_arch}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure*}
+%This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
+%We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
+%We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
+%This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
+%For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
+%The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
 
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
+\subsection{Setup and motivating examples}\label{sec_HPS_loss}
 
@@
 \todo{mention connection to pooling \cite{hanneke2020no}}
-%\subsection{Summary of Results}
 
@@
 Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
+%See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
 Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-\begin{itemize}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
+%\begin{itemize}
+%	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
+%	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
+%	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
 
@@
 See our discussion of proof techniques below for details.
-\end{itemize}
+%\end{itemize}
 
@@
 %See Section \ref{sec_conclude} for more discussions of the technical challenge.
-
-%\section{Predication loss for HPS estimator}\label{sec_HPS_loss}
 
@@
 
-%\subsection{Notations}
-
-%for a small constant $\tau>0$.
-
 \subsection{Organizations}
 The rest of this paper is organized as follows.
-In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation}, we validate our results in simulations.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{sec_text} describes our study on text classification tasks.
+In Section \ref{sec_HPS}, we formally define the data model and the assumptions.
+We describe a bias-variance decomposition of the HPS estimator, and connect the decomposition to random matrix theory.
+In Section \ref{sec_main}, we show precise estimates for the excess risk of the HPS estimator under covariate and model shifts.
+In Section \ref{sec_same}, we extend our setup to transferring from multiple data sources under model shift.
+In Section \ref{sec_exp}, we evaluate the performance of HPS estimators against several commonly used transfer learning estimators, and present two implications for migating covariate and model shift in neural networks.
+Section \ref{sec_conclude} concludes the paper and discusses potential future directions.
 Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.

### 2021-07-22 revision_journal/main_arxiv.tex
reorg wip
update intro wip
sec 2 wip
Updates from Overleaf
finish sec 4 edits
finish sec 3.2
start intro
intro wip

@@
 \def\shownotes{1}
-
+\setlength{\columnsep}{0.35in}
 \usepackage{natbib}
@@
 \newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-\usepackage{authblk}
+%\usepackage{authblk}
 \usepackage[margin=1in]{geometry}
@@
 
-	\iffalse
-	\vspace{0.15in}
-	\author[1]{Hongyang R.
-Zhang\thanks{HZ and FY contributed equally to the theoretical results.
-SW conducted the experimental analysis.
-Correspondence to hrzhang@northeastern.edu or fyang75@wharton.upenn.edu.}}
-	\author[2]{Fan Yang\samethanks}
-	\author[3]{Sen Wu\samethanks}
-	\author[2]{Weijie J. Su}
-	\author[3]{Christopher R\'e}
-	\vspace{0.15in}
-	\affil[1]{Khoury College of Computer Sciences, Northeastern University}
-	\affil[2]{Department of Statistics, The Wharton School, University of Pennsylvania}
-	\affil[3]{Department of Computer Science, Stanford University}
-	\fi
-	\title{Precise Asymptotics of Transferring from Different Regression in High Dimensions}
+	\title{Estimating Information Transfer from Different Sources in High-dimensional Linear Regression}
+
+    \author{Fan Yang\thanks{University of Pennsylvania.
+fyang75@wharton.upenn.edu}\and Hongyang R.
+Zhang \thanks{Northeastern University.
+ho.zhang@northeastern.edu.
+Part of this work was done while the author was at UPenn.}\and Sen Wu\thanks{Stanford University.
+senwu@stanford.edu}\and Weijie J.
+Su \thanks{University of Pennsylvania.
+suw@wharton.upenn.edu}\and Christopher R\'e\thanks{Stanford University.
+chrismre@stanford.edu}}
+
 	\maketitle
@@
 	\input{intro}
+	\input{setup}
 	\input{results}
-	\input{examples}
-	\input{multitask}
 	\input{exp}
+    \input{multitask.tex}
 	\input{conclusions}
 	\bibliographystyle{plainnat}
-	\bibliography{rf,ref_mtl}
+	\bibliography{rf,rf_tl,ref_mtl}
 

### 2021-07-22 revision_journal/intro.tex
intro wip

@@
 
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
+ \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
 In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
@@
 
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
+ \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
 For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.

### 2021-07-22 revision_journal/exp.tex
intro wip

@@
-\section{Empirical results}
+\section{Empirical results}\label{sec_exp}
 
@@
 We conduct further studies of HPS for text classification tasks.
-We consider six datasets for predicting movie review sentiment (MR and SST) \cite{pang2005seeing,socher2013recursive}, sentence subjectivity (SUBJ) \cite{pang2004sentimental}, customer review sentiment (CR) \cite{hu2004mining}, question types (TREC) \cite{li2002learning}, and polarity of a phrase (MPQA) \cite{wiebe2005annotating}.\footnote{The datasets can be downloaded at \url{https://github.com/harvardnlp/sent-conv-torch/tree/master/data}.
+We consider six datasets for predicting movie review sentiment (MR and SST), sentence subjectivity (SUBJ), customer review sentiment (CR), question types (TREC), and polarity of a phrase (MPQA).\footnote{The datasets can be downloaded at \url{https://github.com/harvardnlp/sent-conv-torch/tree/master/data}.
 Further statistics of each dataset can also be found following the link.}
+%\cite{pang2005seeing,socher2013recursive}
+%\cite{pang2004sentimental}
+%\cite{pang2004sentimental}
+%\cite{pang2004sentimental}
+%\cite{pang2004sentimental}
+% \cite{lei2018simple}
 %The question is to predict positive or negative sentiment expressed in the text.
@@
 A separate output layer is used for predicting the labels of each dataset.
-We evaluate on three possibilities of feature representation layers including LSTM, MLP, and CNN \cite{lei2018simple}.\footnote{Before the MLP layer, we apply an average pooling layer over the embedding of every word in the sentence.}
+We evaluate on three possibilities of feature representation layers including LSTM, MLP, and CNN, as implemented by PyTorch.\footnote{\url{pytorch} Before the MLP layer, we apply an average pooling layer over the embedding of every word in the sentence.}
 See Figure \ref{fig_intro_arch} for an illustration of the network architecture.

### 2021-07-22 revision_journal/intro.tex
intro wip

@@
 
-\subsection{Setup and motivating examples}\label{sec_HPS_loss}
+\subsection{Setup and motivating examples}
+
+We first define the data model.
+Suppose we have two datasets (or tasks). We refer the first one as the (data) source and the second one as the target.
+Suppose that $i = 1$ or $i = 2$.
+Let $n_i$ be the sample size of dataset $i$.
+Let $x_1^{(i)}, x_2^{\ss (i)}, \dots, x_{n_1}^{(i)}$ be $p$-dimensional covariates of the $n_i$ datapoints.
+Let $y_1^{(i)}, y_2^{(i)}, \dots, y_{n_1}^{(i)}$ be the real-valued labels of these datapoints.
+We assume that a linear model holds:
+\begin{align}
+    y_j^{(i)} = \inner{x_j^{(i)}}{\beta^{(i)}} + \varepsilon_j^{(i)}, \text{ for any } j = 1,\dots,n_i, \label{eq_linear}
+\end{align}
+where $\beta^{(i)} \in \real^p$ denotes an unknown model vector and $\varepsilon^{(i)}_j$ denotes an additive noise (independent of the covariates).
+%Let $(x_1^{(2)}, y_1^{(2)}), \dots, (x_{n_2}^{(2)}, y_{n_2}^{(2)})$ be $n_2$ labeled examples, where $x_i^{(2)}$ denotes the covariates and $y_i^{(2)}$ denotes the label, for any $i = 1,\dots, n_2$.
+%Similar to the first dataset, we assume that
+%for an unknown vector $\beta^{(2)}\in\real^p$ and an additive noise $\varepsilon^{(2)}_i$.
+Our goal is to learn an estimator to predict the target task (two) given both datasets.
+
+We consider a high-dimensional setting (e.g., \citet{hastie2019surprises}) where the sample size $n_i$ increases with $p$ proportionally by a constant factor.
+Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.
+We assume that
+\begin{align}
+    x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)}, \text{ for any } j = 1,\dots,n_i, \label{eq_rvm}
+\end{align}
+where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition. 
+We focus on the so called \textit{underparametrized} setting for task two where $n_2 > \rho p$ for a constant $\rho > 1$ whereas for task one $n_1$ can be smaller than $p$.
+%A distinction between our setup and \citet{hastie2019surprises} is that we 
+See Section \ref{sec_data} for the precise assumptions underlying the above data model.
+
+We learn a two-layer linear neural network with parameters $A \in \real^{p\times r}$, $B_1 \in \real^{r}$, and $B_2 \in \real^r$ by minimizing the following optimization objective:
+\begin{align}\label{eq_hps}
+    f(A, B_1, B_2) = \bignorm{X^{(1)} A B_1 - Y^{(1)}}_2^2 + \bignorm{X^{(2)} A B_2 - Y^{(2)}}_2^2.
+\end{align}
+The above two-layer neural network (also called hard parameter sharing \cite{C97}) captures the intuition that both datasets share the feature space (i.e.
+the subspace spanned by the columns of $A$) while each having a separate prediction head.
+Suppose that $(\hat{A}, \hat{B_1}, \hat{B_2})$ is a minimizer of $f(\cdot)$.
+We define the hard parameter sharing estimator for task $i$ as
+\[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
+Our study of such estimators is motivated by the fact that hard parameter sharing is widely used in empirical studies of transfer learning \cite{R17}.
+%Later on in Section \ref{sec_diff}, we will evaluate the performance of HPS estimators against several natural transfer learning estimators.
 
 \subsection{Summary of results}
-\todo{mention connection to pooling \cite{hanneke2020no}}
+%\todo{mention connection to pooling \cite{hanneke2020no}}
 
+\paragraph{Precise estimates under distribution shift.}
+Having defined the data model for each task, next, we describe typical scenarios in transfer learning under our setup.
+We define two settings as follows:
+\begin{itemize}
+    \item \textbf{Covariate shift:}
+    independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices but different models.
+    Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
+    While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
+    Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
+    \item \textbf{Model shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices (i.e.
+$\Sigma^{(1)}=\Sigma^{(2)}$) but different models (i.e.
+$\beta^{(1)} \neq \beta^{(2)}$).
+    \item \textbf{Covariate and model shift.}
+\end{itemize}
+
+Theoretical insights
+\begin{itemize}
+    \item \textit{Whether or not covariate shift helps depends on sample sizes:} In addition to sample sizes, variance also scales with two datasets' covariate shifts.
+For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
+Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
+We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
+See our discussion of proof techniques below for details.
+    \item \textit{Identical covariance provides approximately optimal transfer under imbalanced sizes:}
+    \item \textit{Determining information transfer under model shift}: Increasing one task's sample size does not always reduce another task's loss.
+In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
+These two trends result from different bias-variance tradeoffs.
+This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
+\end{itemize}
+
+\paragraph{Empirical results.}
+Finally, we discuss the practical implications of our work.
+Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
+For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
+We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
+
+\paragraph{Extension to multiple sources.}
 Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
@@
 
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
 %See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
@@
 
- \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
-
- \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
-For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
 %\end{itemize}
-
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
 
@@
 
-\paragraph{Transfer learning.}
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-\citet{tian2021transfer}
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-\todo{a list of relevant papers}
-\begin{itemize}
-	\item \citet{lei2021nearoptimal}
-	\item \citet{kalan2020minimax}
-	\item \citet{cao2019learning}
-	\item \citet{hanneke2020value,hanneke2020no}, \citet{cai2021transfer}
-\end{itemize}
-\textit{Other related works.} Distributed learning \cite{dobriban2018high}.
-\citet{chen2021weighted}
-
-\paragraph{Random matrix theory.}
-\todo{write a paragraph regarding applications of RMT to modern machine learning.}
-\begin{itemize}
-	\item \citet{hastie2019surprises}
-	\item \citet{bartlett2020benign}
-	\item \citet{liang2020just}
-	\item \citet{montanari2019generalization}, \citet{liang2020precise}
-\end{itemize}
-\begin{remark}
-    \todo{clarify overparametrize}
-    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
-\end{remark}
-
+\paragraph{Sample covariance matrices under distribution shift.}
 These previous works mainly consider cases with only one high-dimensional sample covariance matrix involved. %need to check 
@@
 Leveraging on the recent results \cite{BES_free1,BES_free2}, we can obtain a sharp convergence rate to the bias limit.
-To the best of our knowledge, we are not aware of any previous result on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same sample size.
+To the best of our knowledge, we are not aware of any previous result on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same population covariance matrix.
 
-%previous results in the multi-task case, even for cases without covariate shifts.
+\paragraph{Random matrix theory and machine learning.} \todo{write a paragraph regarding applications of RMT to modern machine learning.}
+\begin{itemize}
+	\item \citet{hastie2019surprises}
+	\item \citet{bartlett2020benign}
+	\item \citet{liang2020just}
+	\item \citet{montanari2019generalization}, \citet{liang2020precise}
+\end{itemize}
+\begin{remark}
+    \todo{clarify overparametrize}
+    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
+\end{remark}
 
-%\HZ{can you please add a discussion of the related work from RMT?}
+\paragraph{Transfer learning and related problems.}
+There is a large body of classical and recent works on multi-task learning.
+The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
+An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
+One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
+\citet{pontil2013excess}
+Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
+The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting}.
+For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
+One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
+However, their results only apply to sample size regimes at least logarithmic factors of dimension.
+\todo{a list of relevant papers}
+\begin{itemize}
+	\item \citet{lei2021nearoptimal}
+	\item \citet{kalan2020minimax}
+	\item  \citet{cai2021transfer}
+	\item \citet{lounici2011oracle}
+\end{itemize}
+\textit{Other related works.} Distributed learning \cite{dobriban2018high}.
 
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
 %Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
@@
 The rest of this paper is organized as follows.
-In Section \ref{sec_HPS}, we formally define the data model and the assumptions.
-We describe a bias-variance decomposition of the HPS estimator, and connect the decomposition to random matrix theory.
+In Section \ref{sec_HPS}, we formally define the data model and describe the underlying assumptions.
+We show a bias-variance decomposition of the HPS estimator, and connect the bias and variance equations to random matrix theory.
 In Section \ref{sec_main}, we show precise estimates for the excess risk of the HPS estimator under covariate and model shifts.
+In Section \ref{sec_exp}, we evaluate the performance of HPS estimators against several commonly used transfer learning estimators, and present two implications for migating covariate and model shift in neural networks.
 In Section \ref{sec_same}, we extend our setup to transferring from multiple data sources under model shift.
-In Section \ref{sec_exp}, we evaluate the performance of HPS estimators against several commonly used transfer learning estimators, and present two implications for migating covariate and model shift in neural networks.
 Section \ref{sec_conclude} concludes the paper and discusses potential future directions.

### 2021-07-22 revision_journal/setup.tex
intro wip

@@
 
-We describe the data model and the underlying assumptions.
-Suppose we have two regression datasets (or tasks).
-We denote their sample sizes by $n_1$ and $n_2$, respectively.
-Consider either $i = 1$ or $i = 2$.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for the feature covariates $X^{(i)}$ follows a linear model plus random noise $\varepsilon^{(i)}$:
+%We describe the data model and the underlying assumptions.
+Recall we have two regression datasets (or tasks) with sample sizes denoted as $n_1$ and $n_2$, respectively.
+Suppose that $i = 1$ or $i = 2$.
+Let $X^{(i)} \in \real^{n_i \times p}$ be the matrix notation corresponding to dataset $i$'s covariates.
+Let $Y^{(i)} \in \real^{n_i}$ and $\varepsilon \in \real^{n_i}$ be the vector notation corresponding to its labels and additive noise.
+Equation \eqref{eq_linear} thus implies that
 $Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)}.$
 Both $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of the feature covariates and the noise vector.
-Throughout the paper, we make the following assumptions on  $X^{(i)}$ and  $\varepsilon^{(i)}$, which are standard in recent  random matrix theory literature (see e.g.
-\citet{tulino2004random,bai2010spectral}).
+Throughout the paper, we make the following assumptions on  $X^{(i)}$ and  $\varepsilon^{(i)}$, which are standard in the random matrix theory literature (see e.g., \citet{tulino2004random,Bai2006}).
 %We remark that all these assumptions are natural in high-dimensional statistics.
 
-First, we assume the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)} \in \real^{p \times p}$. More precisely, let
+First, we assume the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)} \in \real^{p \times p}$. Equation \eqref{eq_rvm} implies that
 \be\label{XofZ}
@@
 \ee
-where $\Sigma^{(i)}$ is a deterministic positive definite symmetric matrices, $Z^{(i)}=(z^{(i)}_{j,k})$ is a $n_i\times p$ random matrix with real-valued independent entries having zero mean and unit variance.
+recalling that $\Sigma^{(i)}$ is a deterministic positive definite symmetric matrices, $Z^{(i)}=(z^{(i)}_{j,k})$ is a $n_i\times p$ random matrix with real-valued independent entries having zero mean and unit variance.
 %\begin{equation}\label{assm1}
@@
 \be\label{assm2}
-1+\tau \le \rho_i \le p^{\tau^{-1}}.
+    \tau \le \rho_1 \le p^{\tau^{-1}} \text{ and } 1+\tau \le \rho_2 \le p^{\tau^{-1}}.
 \ee
@@
 
-Having defined the data model for each task, next, we describe typical scenarios in transfer learning under our setup.
-We define two settings as follows:
-\begin{itemize}
-    \item \textbf{Covariate shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices but different models.
-    \item \textbf{Model shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices (i.e.
-$\Sigma^{(1)}=\Sigma^{(2)}$) but different models (i.e.
-$\beta^{(1)} \neq \beta^{(2)}$).
-\end{itemize}
-One interesting special case of capturing different models is the following random-effect model, which has been studied in several recent works concerning high-dimensional (single-task) ridge regression \cite{dobriban2018high} and distributed regression \cite{dobriban2020wonder}.
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-%\begin{example}%[Sample sizes]
-%\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	%We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
+We will consider a random-effect model as our running example, which has been studied in several recent works concerning high-dimensional (single-task) ridge regression \cite{dobriban2018high} and distributed regression \cite{dobriban2020wonder}.
 Suppose each $\beta^{(i)}$ consists of two random components, one that is shared among the two tasks and one that is task-specific. More precisely, let
@@
 %Let $\beta^{(i)}$ be equal to $\beta_0$ plus a
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} \mu^2$.
+task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $\mu^2 / p$.
 
@@
 
-\subsection{Estimators}
-
-%We describe our estimators that combine the information from both datasets.
-We learn a two-layer linear neural network with parameters $A \in \real^{p\times r}$, $B_1 \in \real^{r}$, and $B_2 \in \real^r$ by minimizing the following optimization objective:
-\begin{align}\label{eq_hps}
-    f(A, B_1, B_2) = \bignorm{X^{(1)} A B_1 - Y^{(1)}}_2^2 + \bignorm{X^{(2)} A B_2 - Y^{(2)}}_2^2.
-\end{align}
-The above two-layer neural network (also called hard parameter sharing \cite{C97}) captures the intuition that both datasets share the feature space (i.e.
-the subspace spanned by the columns of $A$) while each having a separate prediction head.
-Suppose that $(\hat{A}, \hat{B_1}, \hat{B_2})$ is a minimizer of $f(\cdot)$.
-We define the hard parameter sharing estimator for task $i$ as
-\[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
-Our study of such estimators is motivated by the fact that hard parameter sharing is widely used in empirical studies of multi-task learning \cite{R17}.
-Later on in Section \ref{sec_diff}, we will evaluate the performance of HPS estimators against several natural transfer learning estimators.
+\subsection{Risks}
 
@@
 Additionally, they have been used as a preprocessing step of minimax optimal estimators, under certain conditions of the data \cite{li2020transfer} (see also Section \ref{sec_related} for further discussion of both works).
+
+\paragraph{Information transfer.} To be precise, we say that task one provides a \textit{positive transfer} to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
+Otherwise, we say that task one provides a \textit{negative transfer} to task two.
 
@@
 
-\paragraph{Connection to information transfer.} To be precise, we say that task one provides a \textit{positive transfer} to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
-Otherwise, we say that task one provides a \textit{negative transfer} to task two.
 We now illustrate that the bias-variance decomposition of Proposition \ref{lem_HPS_loss} characterizes whether or not the information transfer is positive.
-
 First, we compare the bias. Since $n_1 \ge (1 + \tau) p$ by Assumption \ref{assm_big1}, the bias of $\hat{\beta}_2^{\STL}$ is zero.

### 2021-07-22 revision_journal/intro.tex
wip

@@
 
-We consider a high-dimensional setting (e.g., \citet{hastie2019surprises}) where the sample size $n_i$ increases with $p$ proportionally by a constant factor.
+We consider a high-dimensional setting (e.g., \citet{hastie2019surprises}) where the sample size $n_i$ increases with $p$ to infinity proportionally by a constant factor.
 Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.

### 2021-07-22 revision_journal/main_arxiv.tex
intro wip
wip

@@
 \usepackage{caption,subcaption}
-
+\DeclareMathSizes{10}{10}{7}{4}
 %\newcommand{\citet}{\cite}
-
+%\catcode`^=\active
+%\newcommand^[1]{\ensuremath{\smallp{\scriptscriptstyle #1}}}
 \begin{document}
 
-	\title{Estimating Information Transfer from Different Sources in High-dimensional Linear Regression}
+	\title{Analyzing Information Transfer from Heterogeneous Sources via Precise High-dimensional Asymptotics}
 
-    \author{Fan Yang\thanks{University of Pennsylvania.
+    %\author{Fan Yang\thanks{University of Pennsylvania.
 fyang75@wharton.upenn.edu}\and Hongyang R.
@@
 	\input{exp}
-    \input{multitask.tex}
+    \input{multitask}
 	\input{conclusions}

### 2021-07-23 revision_journal/intro.tex
start sec 1.2

--- 2021-07-22 revision_journal/intro.tex
@@
 We first define the data model.
-Suppose we have two datasets (or tasks). We refer the first one as the (data) source and the second one as the target.
-Suppose that $i = 1$ or $i = 2$.
-Let $n_i$ be the sample size of dataset $i$.
-Let $x_1^{(i)}, x_2^{\ss (i)}, \dots, x_{n_1}^{(i)}$ be $p$-dimensional covariates of the $n_i$ datapoints.
-Let $y_1^{(i)}, y_2^{(i)}, \dots, y_{n_1}^{(i)}$ be the real-valued labels of these datapoints.
-We assume that a linear model holds:
+Suppose we have two datasets (or tasks).
+We refer the first dataset as the source and the second task as the target.
+Let $i = 1$ or $2$.
+Let $n_i$ be dataset $i$'s sample size.
+Let $x_1^{(i)}, x_2^{\ss (i)}, \dots, x_{n_i}^{(i)}$ be the $n_i$ datapoints' $p$-dimensional covariates.
+Let $y_1^{(i)}, y_2^{(i)}, \dots, y_{n_i}^{(i)}$ be these datapoints' labels.
+We assume a linear model specified by an unknown model vector $\beta^{(i)} \in \real^p$ as follows:
 \begin{align}
@@
 \end{align}
-where $\beta^{(i)} \in \real^p$ denotes an unknown model vector and $\varepsilon^{(i)}_j$ denotes an additive noise (independent of the covariates).
+where $\varepsilon^{(i)}_j$ denotes an additive noise (independent of the covariates).
 %Let $(x_1^{(2)}, y_1^{(2)}), \dots, (x_{n_2}^{(2)}, y_{n_2}^{(2)})$ be $n_2$ labeled examples, where $x_i^{(2)}$ denotes the covariates and $y_i^{(2)}$ denotes the label, for any $i = 1,\dots, n_2$.
@@
 %for an unknown vector $\beta^{(2)}\in\real^p$ and an additive noise $\varepsilon^{(2)}_i$.
-Our goal is to learn an estimator to predict the target task (two) given both datasets.
+Our goal is to learn an estimator to predict the target task given both datasets.
 
-We consider a high-dimensional setting (e.g., \citet{hastie2019surprises}) where the sample size $n_i$ increases with $p$ proportionally by a constant factor.
+We consider a high-dimensional setting on each dataset where the sample size $n_i$ increases with $p$ to infinity proportionally by a constant factor, which has recently received lots of interests (see e.g., \citet{hastie2019surprises} and Section \ref{sec_related} for more references).
 Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.
-We assume that
+The covariates are assumed to have population covariance equal to $\Sigma^{(i)}$:
 \begin{align}
@@
 We focus on the so called \textit{underparametrized} setting for task two where $n_2 > \rho p$ for a constant $\rho > 1$ whereas for task one $n_1$ can be smaller than $p$.
-%A distinction between our setup and \citet{hastie2019surprises} is that we 
 See Section \ref{sec_data} for the precise assumptions underlying the above data model.
@@
 \end{align}
-The above two-layer neural network (also called hard parameter sharing \cite{C97}) captures the intuition that both datasets share the feature space (i.e.
-the subspace spanned by the columns of $A$) while each having a separate prediction head.
-Suppose that $(\hat{A}, \hat{B_1}, \hat{B_2})$ is a minimizer of $f(\cdot)$.
-We define the hard parameter sharing estimator for task $i$ as
-\[ \hat{\beta}_i^{\MTL} \define \hat{B} \hat{A}_i. \]
-Our study of such estimators is motivated by the fact that hard parameter sharing is widely used in empirical studies of transfer learning \cite{R17}.
-%Later on in Section \ref{sec_diff}, we will evaluate the performance of HPS estimators against several natural transfer learning estimators.
+The above two-layer neural network uses a shared feature space $A$ for both tasks while using a separate prediction head for each task.\footnote{A popular variant of objective function \eqref{eq_hps} adds a weight parameter to each summand.
+We focus on the unweighted objective for simplicity and all of our results apply to the weighted objective.}
+Such models are also known as \textit{hard parameter sharing} in the machine learning literature \cite{C97,R17}.
+Suppose that $(\hat{A}, \hat{B}_1, \hat{B}_2)$ is a global minimizer of $f(\cdot)$.
+We define the hard parameter sharing (HPS) estimator for the target task as $\hat{\beta}_2^{\MTL} \define \hat{B} \hat{A}_2$.
+In order to evaluate the estimator, we will study the excess risk at a new (unseen) test datapoint from task two, denoted as $L(\hat{\beta}_2^{\MTL})$ (see Section \ref{sec_risk} for its precise definition).
+
+As a motivating example of the above setup, we show an intriguing simulation where combining both datasets jointly results in different transfer effect on $L(\hat{\beta}_2^{\MTL})$, depending on the distance between $\beta^{(1)}$ and $\beta^{(2)}$.
+Figure \ref{fig_motivation} shows the result for a setting where every entry of $X_1, X_2$ is generated from an isotropic Gaussian, and $\beta_1,\beta_2$ are generated such that $\norm{\beta^{(1)} - \beta^{(2)}}^2 \approx 2\mu^2$.
+We observe that for $\mu = 0.25$, $L(\hat{\beta}_2^{\MTL})$ is always smaller than the excess risk of OLS.
+For the other $\mu$ values, $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of OLS for a restricted range of $n_1$.
+Such a scenario, where combining both datasets jointly improves over learning the target task individually, and is also called a \textit{positive information transfer} \cite{PY09}.
+Our main contribution is to precisely analyze a number of interesting phenomena including the above that are prevalent in transfer learning, depending on geometries of the covariance matrices and model distances.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/motivation.eps}
+    \caption{We illustrate that our setup can reproduce the phenomenon of \textit{positive} (or \textit{negative}) \textit{information transfer}, which is prevalent in the context of transfer learning.
+    We vary the sample size of dataset one and the distance parameter $\mu$ such that $\norm{\beta^{(1)} - \beta^{(2)}}^2 = 2\mu^2$.
+The region below the excess risk of the ordinary least squares (OLS) estimator corresponds to the range of $n_1$ in which $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of the OLS estimator.
+See also Figure \ref{fig_ab_data} for a similar phenomenon observed in text classification tasks.}
+    \label{fig_motivation}
+\end{figure*}
 
@@
 
-\paragraph{Precise estimates under distribution shift.}
+\paragraph{Precise asymptotics given heterogeneous sources.}
 Having defined the data model for each task, next, we describe typical scenarios in transfer learning under our setup.
@@
 
-\paragraph{Sample covariance matrices under distribution shift.}
+\paragraph{Sample covariance matrices with distribution shift.}
 These previous works mainly consider cases with only one high-dimensional sample covariance matrix involved. %need to check 

### 2021-07-23 revision_journal/intro.tex
finish sec 1.2, begin sec 1.3

@@
 
-\subsection{Setup and motivating examples}
+\subsection{Setup and motivating examples}\label{sec_mot}
 
@@
 \end{align}
-where $\varepsilon^{(i)}_j$ denotes an additive noise (independent of the covariates).
-%Let $(x_1^{(2)}, y_1^{(2)}), \dots, (x_{n_2}^{(2)}, y_{n_2}^{(2)})$ be $n_2$ labeled examples, where $x_i^{(2)}$ denotes the covariates and $y_i^{(2)}$ denotes the label, for any $i = 1,\dots, n_2$.
-%Similar to the first dataset, we assume that
-%for an unknown vector $\beta^{(2)}\in\real^p$ and an additive noise $\varepsilon^{(2)}_i$.
+where $\varepsilon^{(i)}_j\in\real$ denotes a random noise variable with mean zero and variance $\sigma^2$.
 Our goal is to learn an estimator to predict the target task given both datasets.
-
-We consider a high-dimensional setting on each dataset where the sample size $n_i$ increases with $p$ to infinity proportionally by a constant factor, which has recently received lots of interests (see e.g., \citet{hastie2019surprises} and Section \ref{sec_related} for more references).
-Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.
-The covariates are assumed to have population covariance equal to $\Sigma^{(i)}$:
-\begin{align}
-    x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)}, \text{ for any } j = 1,\dots,n_i, \label{eq_rvm}
-\end{align}
-where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition. 
-We focus on the so called \textit{underparametrized} setting for task two where $n_2 > \rho p$ for a constant $\rho > 1$ whereas for task one $n_1$ can be smaller than $p$.
-See Section \ref{sec_data} for the precise assumptions underlying the above data model.
 
@@
 \end{align}
-The above two-layer neural network uses a shared feature space $A$ for both tasks while using a separate prediction head for each task.\footnote{A popular variant of objective function \eqref{eq_hps} adds a weight parameter to each summand.
-We focus on the unweighted objective for simplicity and all of our results apply to the weighted objective.}
+The above two-layer neural network uses a shared feature space $A$ for both tasks while using a separate prediction head for each task.\footnote{Popular variants of the objective function \eqref{eq_hps} include adding a weight parameter to each summand and adding ridge regularization.
+We focus on the unweighted and unregularized objective for simplicity.
+All of the asymptotic limits we show below can be straightforwardly extended to weighted and regularized objectives.}
 Such models are also known as \textit{hard parameter sharing} in the machine learning literature \cite{C97,R17}.
@@
 We observe that for $\mu = 0.25$, $L(\hat{\beta}_2^{\MTL})$ is always smaller than the excess risk of OLS.
-For the other $\mu$ values, $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of OLS for a restricted range of $n_1$.
-Such a scenario, where combining both datasets jointly improves over learning the target task individually, and is also called a \textit{positive information transfer} \cite{PY09}.
+For $\mu = 0.3$ or $0.35$, $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of OLS for a restricted range of $n_1$.
+Such a scenario, where combining both datasets jointly improves over learning the target task individually, is also called a \textit{positive information transfer} \cite{PY09}.
+On the other hand, for $\mu = 0.45$, HPS is always worse than OLS, thus providing a \textit{negative information transfer}.  
 Our main contribution is to precisely analyze a number of interesting phenomena including the above that are prevalent in transfer learning, depending on geometries of the covariance matrices and model distances.
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{figures/motivation.eps}
+    \includegraphics[width=0.8\textwidth]{figures/motivation.eps}
     \caption{We illustrate that our setup can reproduce the phenomenon of \textit{positive} (or \textit{negative}) \textit{information transfer}, which is prevalent in the context of transfer learning.
-    We vary the sample size of dataset one and the distance parameter $\mu$ such that $\norm{\beta^{(1)} - \beta^{(2)}}^2 = 2\mu^2$.
-The region below the excess risk of the ordinary least squares (OLS) estimator corresponds to the range of $n_1$ in which $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of the OLS estimator.
+    We vary the sample size of dataset one and the distance parameter $\mu$ such that $\norm{\beta^{(1)} - \beta^{(2)}}^2 \approx 2\mu^2$.
+The region below the excess risk of the ordinary least squares (OLS) estimator corresponds to \textit{positive information transfer} when $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of the OLS estimator.
+This simulation uses $p = 100, n_2 = 300, \sigma = 1/2$.
 See also Figure \ref{fig_ab_data} for a similar phenomenon observed in text classification tasks.}
@@
 \subsection{Summary of results}
-%\todo{mention connection to pooling \cite{hanneke2020no}}
 
-\paragraph{Precise asymptotics given heterogeneous sources.}
-Having defined the data model for each task, next, we describe typical scenarios in transfer learning under our setup.
-We define two settings as follows:
+We consider a high-dimensional setting on each dataset where the sample size $n_i$ increases with $p$ to infinity proportionally by a constant factor, which has recently received lots of interests (see e.g., \citet{hastie2019surprises} and Section \ref{sec_related} for more references).
+Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.
+The covariates are assumed to have population covariance equal to $\Sigma^{(i)}$:
+\begin{align}
+    x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)}, \text{ for any } j = 1,\dots,n_i, \label{eq_rvm}
+\end{align}
+where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition (see Section \ref{sec_data} for the precise assumptions).
+
+We focus on the so called \textit{underparametrized} setting for the target task where $n_2 > p$ whereas for dataset one $n_1$ can be either smaller or greater than $p$.
+Thus, the OLS estimator exists and it is well-known that the limit of its excess risk when $p$ approaches infinity is equal to $\frac{\sigma^2 p}{n_2 - p}$ (see e.g., \citet{bai2009spectral}).
+By contrast, showing the asymptotic limit of $L(\hat{\beta}^{\MTL}_2)$ in the high-dimensional setting requires dealing with the inverse of the sum of two sample covariance matrices.
+The first challenge is dealing with \textit{covariate shift}---when $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are different.
+The second challenge is dealing with \textit{model shift}---when $\beta^{(1)}$ and $\beta^{(2)}$ are different.
+Our main result addresses both challenges by \todo{illustrate}.
 \begin{itemize}
     \item \textbf{Covariate shift:}
-    independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices but different models.
-    Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-    While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-    Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-    \item \textbf{Model shift:} independent $X^{(1)}$ and $X^{(2)}$ with the same population covariance matrices (i.e.
-$\Sigma^{(1)}=\Sigma^{(2)}$) but different models (i.e.
-$\beta^{(1)} \neq \beta^{(2)}$).
-    \item \textbf{Covariate and model shift.}
+    Our first result applies to settings where $\Sigma^{(1)}$ and $\Sigma^{(2)}$ can be arbitrarily different but $\beta^{(1)} = \beta^{(2)}$.
+    For such settings, we show in Theorem \ref{thm_main_RMT} the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the singular values of the matrix $\big(\Sigma^{(1)}\big)^{1/2}\big(\Sigma^{(2)}\big)^{-1/2}$ and the sample sizes $n_1, n_2$.
+    \item \textbf{Model shift:} Our second result applies to settings where $\beta^{(1)}$ and $\beta^{(2)}$ can be arbitrarily different but $\Sigma^{(1)} = \Sigma^{(2)}$.
+    For such settings, we show in Theorem \ref{cor_MTL_loss} the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the $\ell_2$ distance between $\beta^{(1)}$ and $\beta^{(2)}$, and the sample sizes.
+    \item \textbf{Covariate and model shift:} Our third result applies to settings with both covariate shift and model shift.
+    When $\Sigma^{(2)}$ is isotropic, we show in Theorem \ref{???} the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the singular values of $\Sigma^{(1)}$, the $\ell_2$ distance between $\beta^{(1)}$ and $\beta^{(2)}$), and the sample sizes.
+    For the most general setting when $\Sigma^{(2)}$ is unisotropic, we show in Theorem \ref{prop_main_RMT} an estimate of $L(\hat{\beta}_2^{\MTL})$ that is accurate when $n_1$ is much larger than $n_2$.
 \end{itemize}
 
-Theoretical insights
-\begin{itemize}
-    \item \textit{Whether or not covariate shift helps depends on sample sizes:} In addition to sample sizes, variance also scales with two datasets' covariate shifts.
-For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
-    \item \textit{Identical covariance provides approximately optimal transfer under imbalanced sizes:}
-    \item \textit{Determining information transfer under model shift}: Increasing one task's sample size does not always reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
-\end{itemize}
+Next, we demonstrate the power of these precise asymptotics by explaining a number of empirical phenomena in the context of transfer learning.
+We consider a random-effect model where $\beta^{(i)}$ is equal to a shared model vector plus per-task variances (cf. \citet{dobriban2018high}).
+Under this model, we show the following \textit{theoretical insights}.
+\begin{enumerate}
+    \item[i)] \textit{Whether or not covariate shift helps depends on sample sizes:} We consider the covariate shift setting and show that (cf.
+Proposition \ref{claim_dichotomy}) when $n_1 < n_2$, transferring from a data source with $\Sigma^{(1)} \neq \Sigma^{(2)}$ can achieve a smaller $L(\hat{\beta}_2^{\MTL})$ compared to transferring from a data source with $\Sigma^{(1)} = \Sigma^{(2)}$.
+When $n_1 > n_2$, transferring from from a data source with $\Sigma^{(1)} \neq \Sigma^{(2)}$ always results in higher $L(\hat{\beta}_2^{\MTL})$ than transferring from a data source with $\Sigma^{(1)} = \Sigma^{(2)}$.
+    \item[ii)] \textit{Identical covariance provides approximately optimal transfer under imbalanced sizes:} Additionally, in Proposition \ref{prop_covariate}, we show that when $n_1$ is greater than $n_2$ times a certain large constant factor, transferring from a data source with $\Sigma^{(1)} = \Sigma^{(2)}$ achieves an approximately minimum excess risk value, within a certain family of covariance matrices of $\Sigma^{(1)}$.
+    \item[iii)] \textit{Three regimes of information transfer under model shift}: Next, we consider the model shift setting and characterize the precise range of $n_1$ under which there is a positive transfer.
+    In Proposition \ref{claim_model_shift}, we show that when $\mu^2 \le \frac{\sigma^2 p}{2(n_2 - p)}$ (recall that $\norm{\beta^{(1)} - \beta^{(2)}}^2 \approx 2\mu^2$) is small, the transfer effect is positive for any $n_1$.
+    When $\frac{\sigma^2 p}{2(n_2 - p)} < \mu^2 < \frac{\sigma^2 n_2}{2(n_2 - p)}$, there is a transition from positive to negative transfer, as $n_1$ increases.
+    When $\frac{\sigma^2 n_2}{2(n_2 - p)} \le \mu^2$, the transfer effect is negative for any $n_1$.
+    Additionally, we illustrate that these three regimes of information transfer arises under both covariate and model shift (cf. Figure \ref{fig_sec3_cov_mo_b}).
+\end{enumerate}
 
 \paragraph{Empirical results.}
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
+We also complement our theoretical analysis with empirical evaluations.
+As mentioned in Section \ref{sec_mot}, our motivation for studying the HPS estimator stems from its superior empirical performance for transfer learning.
+We affirm that HPS indeed outperforms several commonly used estimators including weighted averages of the OLS estimators of each task (cf.
+\citet{bastani2020predicting}) and the ridge estimator of the target task in our setting.
+See Figure \ref{fig_sec51} for the result.
+
+We then conduct a case study on six text classification tasks using HPS neural network models.
+We demonstrate that our theoretical insights above imply interesting new methods for mitigating covariate shift and model shift, respectively.
+
+First, our insight ii) above suggests the importance of mitigating covariate shift under imbalanced dataset sizes.
+To this end, we consider a certain covariance alignment procedure proposed in \citet{WZR20} for mitigating covariate shift.
+We show that such an alignment procedure provides more significant improvement when $n_1 / n_2$ increases.
+
+Second, our insight iii) above suggests subsampling the source dataset under model shift.
+An efficient instantiation of this above would be to increase the sample size of the source dataset gradually until performance drops.
+For example, in the setting of Figure \ref{fig_motivation}, this procedure will stop right at the minimum of the local basin.
+On both two-task and multi-task case studies using the six text classification datasets, such a training procedure can reduce the computational cost by $65\%$ compared to a stochastic gradient descent procedure without sacrificing accuracy.
 
 \paragraph{Extension to multiple sources.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \cite{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
-
-%See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-%\begin{itemize}
-%	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-%	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
-%	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
-
-%\end{itemize}
+Finally, we also extend our setup to the case of having multiple data sources.
+We consider a setting where all datasets have the same features but different labels, which is also known as multi-label prediction \cite{hsu2009multi}.
+We show the asymptotic limit of $L(\hat{\beta}_i^{\MTL})$ under model shift (cf. Theorem \ref{thm_many_tasks}) and use the result to illustrate how to select the hidden width $r$ of $B$.
+%Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
 
@@
 
-\paragraph{Sample covariance matrices with distribution shift.}
-These previous works mainly consider cases with only one high-dimensional sample covariance matrix involved. %need to check 
-In the single task case, if the data is Gaussian, then the precise variance limit can be derived directly from properties of Wishart distribution.
-In the high-dimensional setting, the eigenvalues of Wishart matrices satisfy the famous Marchenko–Pastur (MP) law \cite{MP}, whose Stieltjes transform characterizes the variance limit.
-Furthermore, it is well-known that the MP law holds universally regardless of the detailed data distribution \cite{bai2010spectral}.
-\cite{isotropic} obtained a sharp converge rate of the empirical spectral distribution (ESD) to the MP law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic,DY} later extended this result to sample covariance matrices with arbitrary population covariances.
-These results are proved by establishing certain optimal convergence estimates of the Stieltjes transforms of sample covariance matrices, which are referred to as \emph{local laws} in the random matrix theory literature.
-We refer the reader to \cite{erdos2017dynamical} and the references therein for a detailed review of related concepts.
-We extend these techniques to the two-task setting and prove a local law for the sum of two sample covariance matrices with an arbitrary covariate shift, which is one technical contribution of this work.
-From the local law, we can derive the variance limit with a precise dependence on the singular values of the covariate shift matrix.
-
-%Our proof techniques use the so-called local law of random matrices, a recent development in the random matrix theory literature, called the \emph{local law} of
-
-%These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-%We also extend the techniques in ?, which is one contribution of this work.
-
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in theory.
-
-There is another method to derive the asymptotic variance limit using free addition in free probability theory \cite{nica2006lectures}.
-We do not take this procedure because this method is not completely justified in the general non-Gaussian setting with non-diagonal covariate shift matrix.
-%(in the sense that it is hard to establish rigorously the free independence between two sample covariance matrices). 
-Furthermore, our techniques provide almost sharp convergence rates to the asymptotic limit, which is not given by free probability techniques.
-
-On the other hand, the bias limit is much harder to study, and its dependence on the sample ratio and the covariate shift is still an open problem in random matrix theory in the most general setting.
-However, when the data is Gaussian distributed and the two tasks have the same population covariance, we find a way to calculate the exact bias limit using free probability techniques.
-Leveraging on the recent results \cite{BES_free1,BES_free2}, we can obtain a sharp convergence rate to the bias limit.
-To the best of our knowledge, we are not aware of any previous result on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same population covariance matrix.
-
-\paragraph{Random matrix theory and machine learning.} \todo{write a paragraph regarding applications of RMT to modern machine learning.}
-\begin{itemize}
-	\item \citet{hastie2019surprises}
-	\item \citet{bartlett2020benign}
-	\item \citet{liang2020just}
-	\item \citet{montanari2019generalization}, \citet{liang2020precise}
-\end{itemize}
-\begin{remark}
-    \todo{clarify overparametrize}
-    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
-\end{remark}
-
-\paragraph{Transfer learning and related problems.}
+\paragraph{Generalization theory for transfer learning.}
 There is a large body of classical and recent works on multi-task learning.
@@
 
+\paragraph{Random matrix theory and machine learning.} \todo{write a paragraph regarding applications of RMT to modern machine learning.}
+\begin{itemize}
+	\item \citet{hastie2019surprises}
+	\item \citet{bartlett2020benign}
+	\item \citet{liang2020just}
+	\item \citet{montanari2019generalization}, \citet{liang2020precise}
+\end{itemize}
+\begin{remark}
+    \todo{clarify overparametrize}
+    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
+\end{remark}
+
+\paragraph{Sample covariance matrices with distribution shift.}
+These previous works mainly consider cases with only one high-dimensional sample covariance matrix involved. %need to check 
+In the single task case, if the data is Gaussian, then the precise variance limit can be derived directly from properties of Wishart distribution.
+In the high-dimensional setting, the eigenvalues of Wishart matrices satisfy the famous Marchenko–Pastur (MP) law \cite{MP}, whose Stieltjes transform characterizes the variance limit.
+Furthermore, it is well-known that the MP law holds universally regardless of the detailed data distribution \cite{bai2010spectral}.
+\cite{isotropic} obtained a sharp converge rate of the empirical spectral distribution (ESD) to the MP law for sample covariance matrices with isotropic covariance.
+\cite{Anisotropic,DY} later extended this result to sample covariance matrices with arbitrary population covariances.
+These results are proved by establishing certain optimal convergence estimates of the Stieltjes transforms of sample covariance matrices, which are referred to as \emph{local laws} in the random matrix theory literature.
+We refer the reader to \cite{erdos2017dynamical} and the references therein for a detailed review of related concepts.
+We extend these techniques to the two-task setting and prove a local law for the sum of two sample covariance matrices with an arbitrary covariate shift, which is one technical contribution of this work.
+From the local law, we can derive the variance limit with a precise dependence on the singular values of the covariate shift matrix.
+
+%Our proof techniques use the so-called local law of random matrices, a recent development in the random matrix theory literature, called the \emph{local law} of
+
+%These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
+%We also extend the techniques in ?, which is one contribution of this work.
+
+%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in theory.
+
+There is another method to derive the asymptotic variance limit using free addition in free probability theory \cite{nica2006lectures}.
+We do not take this procedure because this method is not completely justified in the general non-Gaussian setting with non-diagonal covariate shift matrix.
+%(in the sense that it is hard to establish rigorously the free independence between two sample covariance matrices). 
+Furthermore, our techniques provide almost sharp convergence rates to the asymptotic limit, which is not given by free probability techniques.
+
+On the other hand, the bias limit is much harder to study, and its dependence on the sample ratio and the covariate shift is still an open problem in random matrix theory in the most general setting.
+However, when the data is Gaussian distributed and the two tasks have the same population covariance, we find a way to calculate the exact bias limit using free probability techniques.
+Leveraging on the recent results \cite{BES_free1,BES_free2}, we can obtain a sharp convergence rate to the bias limit.
+To the best of our knowledge, we are not aware of any previous result on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same population covariance matrix.
+
 \subsection{Organizations}

### 2021-07-23 revision_journal/results.tex
intro wip
start sec 1.2
finish sec 1.2, begin sec 1.3

@@
-\section{Main results}\label{sec_main}
+\section{Precise asymptotics under distribution shift}\label{sec_main}
 
@@
 		\includegraphics[width=0.8\textwidth]{figures/verify_covariate_shift.eps}
-		\caption{Illustrating variance estimates for finite $p$}
+		\caption{Illustrating HPS estimates in finite dimensions}
 		\label{fig_sec3_verify_cov}
@@
     We observe a dichotomy that depends on whether or not $n_1$ is greater than $n_2$.
-    \begin{claim}[Sample sizes vs. covariate shift]\label{claim_dichotomy}
+    \begin{proposition}[Sample sizes vs. covariate shift]\label{claim_dichotomy}
         Let $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
@@
         \end{enumerate}
-    \end{claim}
+    \end{proposition}
 
@@
 Let $\cS$ denote the set of $M\in\real^{p\times p}$ such that $M^{\top} M$ satisfies both conditions.
-\begin{claim}[Identical covariance provides approximately optimal transfer under imbalanced dataset sizes]\label{prop_covariate}
+\begin{proposition}[Identical covariance provides approximately optimal transfer under imbalanced dataset sizes]\label{prop_covariate}
     Recall that $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
@@
 	\end{align}
-\end{claim}
+\end{proposition}
 \begin{proof}
@@
 
-\begin{claim}[Sample sizes vs. model shift]\label{claim_model_shift}
+\begin{proposition}[Sample sizes vs. model shift]\label{claim_model_shift}
     Suppose Assumption \ref{assm_big1} and the random-effect model under equation \eqref{eq_re} and \eqref{para_rel} holds.
@@
     \end{enumerate}
-\end{claim}
+\end{proposition}
 
@@
 \subsection{Covariate and model shift}\label{sec3_combined}
+
+Consider the special case with $\Sigma^{(2)}=\id$, $a=1$ and the random effect model. Let $\sigma_i^{(1)}$ be the eigenvalues of $\Sigma^{(1)}$. Define the function 
+\be\label{g1new} g_0(x)= \frac{1}{n_1}\sum_{i=1}^p \frac{\sigma_i^{(1)}}{1+ \sigma_i^{(1)} x} -\frac{1}{x} .\ee
+Let $y$ be the unique positive solution to the equation 
+\be\nonumber
+\frac{n_1+n_2-p}{n_1} + g_0(y) \cdot \left( 1+    y\right)=0 .
+\ee
+Define the following three functions of $y$:
+$$f_1= \frac{n_1}{p}y + \frac{n_1-p}{p}\frac1{g_0(y)},\quad f_2= \frac{n_1}{p}\frac{1}{g_0'(y)}- \frac{n_1-p}{p}\frac1{[g_0(y)]^2},\quad f_3= - g_0(y),$$
+where $g_0'(y)$ is the derivative
+$$ g_0'(y)=  -\frac{1}{n_1}\sum_{i=1}^p \frac{(\sigma_i^{(1)})^2}{(1+ \sigma_i^{(1)} y)^2} +\frac{1}{y^2}. $$
+Then the variance limit is given by
+$$ L_{\var}(1)=\sigma^2 \frac{p}{n_1}f_1,$$
+and the bias limit is given by 
+$$ L_{\bias}(1)=2\mu^2 \frac{1 - 2f_1 f_3  +f_2 f_3^2  }{ 1 - \frac{p}{n_2}f_2 f_3^2 }.$$
+(Here $2\mu^2$ represents $\|\beta^{(1)}-\beta^{(2)}\|^2$.)
+
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_a.eps}
+		\caption{Fixed $\mu$, different $\lambda$}
+		\label{fig_sec3_cov_mo_a}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_b.eps}
+		\caption{Fixed $\lambda$, different $\mu$}
+		\label{fig_sec3_cov_mo_b}
+	\end{subfigure}
+	\caption{We further show that our observations in Figures \ref{fig_sec31} and \ref{fig_sec3_model_shift} extend to settings with both covariate and model shift.
+	Both simulation use $p = 100, n_2 = 300, \sigma = 1/2$.
+	Figure \ref{fig_sec3_cov_mo_a} fixes $\mu = 0.1$ while varying $\lambda, n_1$.
+	Figure \ref{fig_sec3_cov_mo_b} fixes $\lambda = 4$ while varying $\mu, n_1$.}
+	\label{fig_sec33}
+\end{figure}
 
@@
 \end{remark}
-
-\begin{figure}[!t]
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_a.eps}
-		\caption{Fixed $\mu$, different $\lambda$}
-		\label{fig_sec3_cov_mo_a}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_b.eps}
-		\caption{Fixed $\lambda$, different $\mu$}
-		\label{fig_sec3_cov_mo_b}
-	\end{subfigure}
-	\caption{We further show that our observations in Figures \ref{fig_sec31} and \ref{fig_sec3_model_shift} extend to settings with both covariate and model shift.
-	Both simulation use $p = 100, n_2 = 300, \sigma = 1/2$.
-	Figure \ref{fig_sec3_cov_mo_a} fixes $\mu = 0.1$ while varying $\lambda, n_1$.
-	Figure \ref{fig_sec3_cov_mo_b} fixes $\lambda = 4$ while varying $\mu, n_1$.}
-	\label{fig_sec33}
-\end{figure}
-
-Consider the special case with $\Sigma^{(2)}=\id$, $a=1$ and the random effect model. Let $\sigma_i^{(1)}$ be the eigenvalues of $\Sigma^{(1)}$. Define the function 
-\be\label{g1new} g_0(x)= \frac{1}{n_1}\sum_{i=1}^p \frac{\sigma_i^{(1)}}{1+ \sigma_i^{(1)} x} -\frac{1}{x} .\ee
-Let $y$ be the unique positive solution to the equation 
-\be\nonumber
-\frac{n_1+n_2-p}{n_1} + g_0(y) \cdot \left( 1+    y\right)=0 .
-\ee
-Define the following three functions of $y$:
-$$f_1= \frac{n_1}{p}y + \frac{n_1-p}{p}\frac1{g_0(y)},\quad f_2= \frac{n_1}{p}\frac{1}{g_0'(y)}- \frac{n_1-p}{p}\frac1{[g_0(y)]^2},\quad f_3= - g_0(y),$$
-where $g_0'(y)$ is the derivative
-$$ g_0'(y)=  -\frac{1}{n_1}\sum_{i=1}^p \frac{(\sigma_i^{(1)})^2}{(1+ \sigma_i^{(1)} y)^2} +\frac{1}{y^2}. $$
-Then the variance limit is given by
-$$ L_{\var}(1)=\sigma^2 \frac{p}{n_1}f_1,$$
-and the bias limit is given by 
-$$ L_{\bias}(1)=2\mu^2 \frac{1 - 2f_1 f_3  +f_2 f_3^2  }{ 1 - \frac{p}{n_2}f_2 f_3^2 }.$$
-(Here $2\mu^2$ represents $\|\beta^{(1)}-\beta^{(2)}\|^2$.)

### 2021-07-23 revision_journal/setup.tex
start sec 1.2
finish sec 1.2, begin sec 1.3

@@
 Later on in Section \ref{sec_same}, we will extend the setup to the case of multiple data sources.
-%In Section \ref{sec_same}, we will consider a simple extension to a multi-task learning setting with more than two tasks and  the same covariates for all tasks.
-We will give the asymptotic limit of the predication loss for the HPS estimator, which provides useful insights into the more rich multi-task learning theory.
-%Due to length constraint, we will explore the multi-task learning setting in greater details in other works.
 
@@
 
-\subsection{Risks}
+\subsection{Risks}\label{sec_risk}
 
@@
 If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of
-the inverse Wishart distribution \citet{anderson1958introduction}.
+the inverse Wishart distribution \cite{anderson1958introduction}.
 For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
@@
 Here we have presented the results from \citet{isotropic} and \citet{DY}, who give an almost sharp convergence rate.
-
-On the other hand, characterizing the risk of the HPS estimator requires dealing with several challenges.
-First, characterizing bias (cf. equation \eqref{Lbias}) introduces the issue of \textit{model shift}, when $\beta^{(1)}$ differs from $\beta^{(2)}$.
-Second, characterizing variance (cf. equation \eqref{Lvar}) introduces  the issue of \textit{covariate shift}, when $\Sigma^{(1)}$ differs from $\Sigma^{(2)}$.
-Our main results in the next section provide precise bias-variance asymptotics under (either or both) covariate and model shifts.

### 2021-07-24 revision_journal/exp.tex
start sec 1.1

@@
 
-\subsection{Evaluating HPS under covariate and model shifts}\label{sec_diff}
+\subsection{Evaluating HPS under distribution shift}\label{sec_diff}
 
@@
 We find that HPS achieves the lowest excess risk for predicting task two under (either or both) covariate and model shift.
-This simulation uses $p = 100, n_1 = n_2 = 200, \sigma = 1/2$.
+This simulation uses $p = 50, n_1 = n_2 = 100, \sigma = 1/2$.
 Figure \ref{fig_sec5_cov_model} uses $\lambda = 4$ for generating covariate-shifted features.}
@@
 We consider the following estimators for this comparative study:
-\begin{itemize}
-    \item {\bf Averaging estimator (AVG):} given two tasks, take a convex combination of their OLS estimators $b \cdot \hat{\beta}^{\STL}_1 + (1 - b) \cdot \hat{\beta}^{\STL}_2$.
-    \item {\bf STL estimator (STL):} simply use the OLS estimator of task two $\hat{\beta}^{\STL}_2$ without using task one's data.
-    \item {\bf Transfer learning estimator (TL):} simply use the OLS estimator of task one $\hat{\beta}^{\STL}_1$ without using task two's data.
-\end{itemize}
+\begin{enumerate}
+    \item[i)] STL estimator (OLS): $\hat{\beta}_2^{\STL} = \big((X^{(2)})^{\top} X^{(2)}\big)^{-1} (X^{(2)})^{\top} Y^{(2)}$.
+    \item[ii)] Averaging estimator (AVG): given two tasks, take a convex combination of their OLS estimators $b \cdot \hat{\beta}^{\STL}_1 + (1 - b) \cdot \hat{\beta}^{\STL}_2$.
+    \item[iii)] Ridge estimator (RIDGE): $\hat{\beta}_2^{\RIDGE} = \big((X^{(2)})^{\top} X^{(2)} + \lambda \cdot \id_{p\times p}\big)^{-1} (X^{(2)})^{\top} Y^{(2)}$.
+\end{enumerate}
 The parameter $b$ in the averaging estimator is optimized using a validation set of the same size as the training set.
-Additionally, we extend the two-layer neural network formulation of HPS (cf. equation \eqref{eq_hps}) to a weighted objective:
-$b \cdot \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2 + (1 - b) \cdot  \bignorm{X^{2} B A_2 - Y^{(2)}}^2$, and optimize $b$ using the same validation set.
+Additionally, we extend the two-layer neural network formulation of HPS (cf. equation \eqref{eq_hps}) to a weighted and regularized objective:
+$b \cdot \bignorm{X^{(1)} B A_1 - Y^{(1)}}^2 + (1 - b) \cdot  \bignorm{X^{2} B A_2 - Y^{(2)}}^2 + \frac{\lambda}{2} \cdot \norm{B}^2$, and optimize $b, \lambda$ using the same validation set.
 
-Figure \ref{fig_sec51} shows the result under (either or both) covariate and model shifts.
+Figure \ref{fig_sec51} shows the result under various settings of covariate shift and model shift.
 Figure \ref{fig_sec5_covariate} uses the same data generating process as Figure \ref{fig_sec31}.

### 2021-07-24 revision_journal/intro.tex
start sec 1.1

@@
 
-\paragraph{Generalization theory for transfer learning.}
-There is a large body of classical and recent works on multi-task learning.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-\citet{pontil2013excess}
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-\todo{a list of relevant papers}
-\begin{itemize}
-	\item \citet{lei2021nearoptimal}
-	\item \citet{kalan2020minimax}
-	\item  \citet{cai2021transfer}
-	\item \citet{lounici2011oracle}
-\end{itemize}
-\textit{Other related works.} Distributed learning \cite{dobriban2018high}.
-
 %Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
@@
 
-\paragraph{Random matrix theory and machine learning.} \todo{write a paragraph regarding applications of RMT to modern machine learning.}
-\begin{itemize}
-	\item \citet{hastie2019surprises}
-	\item \citet{bartlett2020benign}
-	\item \citet{liang2020just}
-	\item \citet{montanari2019generalization}, \citet{liang2020precise}
-\end{itemize}
-\begin{remark}
-    \todo{clarify overparametrize}
-    As a clar,  following the work of \citet{hastie2019surprises} (see also \citet{bartlett2020benign} and the references therein)
-\end{remark}
+\paragraph{Random matrix theory in machine learning.}
+This work is inspired by an emerging line of recent work that has found random matrix theory useful for studying modern machine learning techniques.
+A prominent line of recent work in this direction has been to understand the generalization properties of interpolators \cite{bartlett2020benign,hastie2019surprises,montanari2019generalization,liang2020just,liang2020precise}.
+Interpolators such as minimum-norm estimators (in the context of linear regression) share similar behavior with modern neural networks in the sense that such models learn by ``memorizing'' the data with lots of parameters \cite{mei2019generalization}.
+The study of such interpolators has also led to an explanation of the double-descent phenomenon \cite{belkin2019reconciling}.
 
-\paragraph{Sample covariance matrices with distribution shift.}
-These previous works mainly consider cases with only one high-dimensional sample covariance matrix involved. %need to check 
-In the single task case, if the data is Gaussian, then the precise variance limit can be derived directly from properties of Wishart distribution.
-In the high-dimensional setting, the eigenvalues of Wishart matrices satisfy the famous Marchenko–Pastur (MP) law \cite{MP}, whose Stieltjes transform characterizes the variance limit.
-Furthermore, it is well-known that the MP law holds universally regardless of the detailed data distribution \cite{bai2010spectral}.
-\cite{isotropic} obtained a sharp converge rate of the empirical spectral distribution (ESD) to the MP law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic,DY} later extended this result to sample covariance matrices with arbitrary population covariances.
+\paragraph{Sample covariance matrices and distribution shift.}
+These previous works primarily deal with a single high-dimensional sample covariance matrix. %need to check 
+In the \textit{underparametrized} setting ($n_2 > p$) which this work focuses on, when the covariates are sampled from Gaussian distributions, the precise asymptotic limit can be derived directly from properties of the Wishart distribution (see also Lemma \ref{fact_tr} and the historical notes in Section \ref{sec_bv}).
+In the high-dimensional setting, the eigenvalues of Wishart matrices satisfy the well-known Marchenko–Pastur (MP) law \cite{MP}, whose Stieltjes transform characterizes the variance limit.
+Furthermore, it is well-known that the MP law holds universally regardless of the underlying data distribution of the covariates \cite{bai2010spectral}.
+\citet{isotropic} obtained a sharp convergence rate of the empirical spectral distribution (ESD) of the MP law for sample covariance matrices with isotropic population covariance matrices.
+\citet{Anisotropic,DY} later extended this result to sample covariance matrices with arbitrary population covariances.
 These results are proved by establishing certain optimal convergence estimates of the Stieltjes transforms of sample covariance matrices, which are referred to as \emph{local laws} in the random matrix theory literature.
 We refer the reader to \cite{erdos2017dynamical} and the references therein for a detailed review of related concepts.
-We extend these techniques to the two-task setting and prove a local law for the sum of two sample covariance matrices with an arbitrary covariate shift, which is one technical contribution of this work.
-From the local law, we can derive the variance limit with a precise dependence on the singular values of the covariate shift matrix.
+Our technical contribution is to extend these techniques to the two-task setting and prove a local law for the sum of two sample covariance matrices with arbitrary covariate shifts.
+Using the local law, we can then derive the variance limit with a precise dependence on the singular values of the covariate shift matrix $\big(\Sigma^{(1)}\big)^{1/2} \big(\Sigma^{(2)}\big)^{-1/2}$.
 
@@
 
-There is another method to derive the asymptotic variance limit using free addition in free probability theory \cite{nica2006lectures}.
-We do not take this procedure because this method is not completely justified in the general non-Gaussian setting with non-diagonal covariate shift matrix.
+The asymptotic limit of the variance of $L(\hat{\beta}_2^{\MTL})$ (cf.
+equation \eqref{Lvar}) under covariate shift may also be derived using free addition in free probability theory \cite{nica2006lectures}.
+However, this approach is not completely justified when the covariates are sampled from non-Gaussian distributions with non-diagonal covariate shift matrices. 
 %(in the sense that it is hard to establish rigorously the free independence between two sample covariance matrices). 
-Furthermore, our techniques provide almost sharp convergence rates to the asymptotic limit, which is not given by free probability techniques.
+Furthermore, our technique provides almost sharp convergence rates to the asymptotic limit, while it is unclear how to obtain such rates using free probability techniques, to the best of our knowledge.
 
-On the other hand, the bias limit is much harder to study, and its dependence on the sample ratio and the covariate shift is still an open problem in random matrix theory in the most general setting.
-However, when the data is Gaussian distributed and the two tasks have the same population covariance, we find a way to calculate the exact bias limit using free probability techniques.
-Leveraging on the recent results \cite{BES_free1,BES_free2}, we can obtain a sharp convergence rate to the bias limit.
-To the best of our knowledge, we are not aware of any previous result on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same population covariance matrix.
+The asymptotic limit of the bias of $L(\hat{\beta}_2^{\MTL})$ (cf. equation \eqref{Lbias}) involves ``asymmetric'' additions of two sample covariance matrices, whose analysis is technically involved.
+Our result on the bias limit is inspired by the recent work of \citet{BES_free1,BES_free2}.
+Additionally, we show a sharp convergence rate to the bias limit using free probability techniques.
+Our work provides the first result in the model shift setting assuming that $\Sigma^{(1)} = \Sigma^{(2)}$ or that $\Sigma^{(2)}$ is isotropic, and the covariates are sampled from Gaussian distributions.
+%To the best of our knowledge, we are not aware of any prior work on the precise bias limit in the high-dimensional setting, even for two Wishart matrices with the same population covariance matrix.
+Showing the asymptotic bias limit under the most general covariate shift and model shift is an interesting open problem for future work.
+See Section \ref{sec_conclude} for further discussion on the technical challenges.
+
+\paragraph{Transfer learning and domain adaptation theory.}
+Earlier works on transfer learning and domain adaptation use uniform convergence to obtain generalization bounds \cite{B00,BS03,M06}.
+The influential paper by \citet{BBCK10} proposes a rigorous model for domain adaptation in classification (see also \citet{crammer2008learning} for an earlier result).
+The main result provides a generalization bound for combining multiple data sources using an objective that averages over the risk of every datapoint.
+This bound provides a principled way to reweight each data source by minimizing the bound.
+From a technical perspective, uniform convergence based techniques provide upper bounds on the excess risks.
+On the other hand, analyzing the empirical phenomena of information transfer such as the ones in Figure \ref{fig_motivation} requires tight lower bounds on the excess risks.
+
+%One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
+%\citet{pontil2013excess}
+%Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
+Finally, we discuss several concurrent works that study transfer learning in linear regression settings.
+The work of \citet{li2020transfer} considers the problem of how to select useful data sources for transfer learning under model shift.
+Their work provides an adaptive procedure that applies even when the set of useful data sources are unknown.
+Our work differs from theirs in two aspects.
+First, we considered a high-dimensional setting where the sample size increases with dimension proportionally.
+Such a setting allows us to derive precise asymptotics of the excess risks, which is then used to explain a number of interesting phenomena in transfer learning.
+Second, our result applies to covariate-shifted (and not necessarily Gaussian) source datasets whereas the setting of \citet{li2020transfer} assumes the covariates of all data sources and the target are drawn from a Gaussian distribution with the same population covariance matrix.
+The work of \citet{lei2021nearoptimal} considers a setting of linear regression under distribution shift including covariate shift and model shift similar to our setting.
+The difference is that our setting deals with a labeled target dataset whereas the result of \citet{lei2021nearoptimal} applies to settings with an unlabeled target dataset.
+%One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
+%	\item \citet{kalan2020minimax}
+%	\item \citet{lounici2011oracle}
 

### 2021-07-25 revision_journal/intro.tex
finish intro

@@
 
-%Many modern machine learning methods
-%Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
-%Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-%It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-%Often, hard parameter sharing offers two critical advantages if successfully applied.
-%First, it reduces model parameters since all tasks use the same feature space.
-%Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
+Given data from two related tasks, how much does combining both data for learning a joint model help predict one of the tasks of interest?
+For example, suppose you have $n_1$ datapoints with $p$-dimensional covariates (sampled from a distribution $D_1$) and real-valued labels in the first task, and $n_2$ datapoints with $p$-dimensional covariates (sampled from a different distribution $D_2$) and real-valued labels in the second task.
+Does combining the $n_1 + n_2$ datapoints help learn a model whose performance is better than a model learned using the $n_2$ datapoints alone?
+Such questions are prevalent in transfer learning, where one often uses data from related tasks to expand the sample size of a task of interest.
+A frequent impediment to applying transfer learning is \textit{negative information transfer} if combining both data performs worse than learning a single task clone \cite{PY09}.
+\textit{Positive information transfer} refers to the desirable scenario where a task of interest benefits when combined with another task.
 
-%Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-%For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-%Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-%However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
-%Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-%Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
+The answer to the two questions above hinges on the tasks' heterogeneity.
+For example, negative information transfer can happen if the label distribution of the second task conditional on the covariates deviates significantly from that of the first task.
+Additionally, the ``information transfer effect'' also hinges on the covariates' distributions, $D_1$ and $D_2$.
+Following the existing literature (e.g., \citet{kouw2018introduction}), we refer to settings where $D_1 \neq D_2$ as \textit{covariate shift} and settings where label distributions differ (conditional on the covariates) as \textit{model shift}.
+Both covariate and model shifts are prevalent in modern datasets (see e.g., \citet{koh2021wilds}).
 
-%This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-%We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-%We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-%This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-%For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-%The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
+This paper studies a linear regression setting involving two tasks with covariate and model shifts.
+We use a two-layer linear neural network to combine the data from both tasks and show that this network reproduces several interesting phenomena in transfer learning.
+We analyze the prediction risk of this network and its transfer effect, providing precise conditions based on geometries of $D_1, D_2$, and the sample sizes $n_1, n_2$.
+The analysis has also inspired several insights for understanding and mitigating covariate and model shifts.
+
+The key ingredient of our analysis is showing the asymptotic limit of certain combinations of sample covariance matrices under distribution shift, using the local laws developed recently by \citet{isotropic} and \citet{BES_free1}.
+After formally defining the specific problem that we tackle, in Section \ref{sec_related}, we provide a technical discussion of the related works in random matrix theory.
+
+%Our main contribution is to precisely analyze a number of interesting phenomena including the above that are prevalent in transfer learning, depending on .
+ %an analysis of the precise causes of negative transfer is of significant practical interest.
 
@@
 
-We first define the data model.
-Suppose we have two datasets (or tasks).
-We refer the first dataset as the source and the second task as the target.
 Let $i = 1$ or $2$.
-Let $n_i$ be dataset $i$'s sample size.
-Let $x_1^{(i)}, x_2^{\ss (i)}, \dots, x_{n_i}^{(i)}$ be the $n_i$ datapoints' $p$-dimensional covariates.
-Let $y_1^{(i)}, y_2^{(i)}, \dots, y_{n_i}^{(i)}$ be these datapoints' labels.
+Let $x_1^{(i)}, x_2^{\ss (i)}, \dots, x_{n_i}^{(i)}$ be the covariates.
+Let $y_1^{(i)}, y_2^{(i)}, \dots, y_{n_i}^{(i)}$ be the corresponding labels.
 We assume a linear model specified by an unknown model vector $\beta^{(i)} \in \real^p$ as follows:
@@
 where $\varepsilon^{(i)}_j\in\real$ denotes a random noise variable with mean zero and variance $\sigma^2$.
-Our goal is to learn an estimator to predict the target task given both datasets.
+For the ease of presentation, we refer to the first dataset as the source and the second task as the target.
+%Our goal is to learn an estimator to predict the target task given both datasets.
 
@@
 \end{align}
-The above two-layer neural network uses a shared feature space $A$ for both tasks while using a separate prediction head for each task.\footnote{Popular variants of the objective function \eqref{eq_hps} include adding a weight parameter to each summand and adding ridge regularization.
+The above objective uses $A$ as the shared feature space for both tasks and $B_1, B_2$ as the prediction head for each task.\footnote{Popular variants of the objective function \eqref{eq_hps} include adding a weight parameter to each summand and adding ridge regularization.
 We focus on the unweighted and unregularized objective for simplicity.
 All of the asymptotic limits we show below can be straightforwardly extended to weighted and regularized objectives.}
-Such models are also known as \textit{hard parameter sharing} in the machine learning literature \cite{C97,R17}.
-Suppose that $(\hat{A}, \hat{B}_1, \hat{B}_2)$ is a global minimizer of $f(\cdot)$.
-We define the hard parameter sharing (HPS) estimator for the target task as $\hat{\beta}_2^{\MTL} \define \hat{B} \hat{A}_2$.
-In order to evaluate the estimator, we will study the excess risk at a new (unseen) test datapoint from task two, denoted as $L(\hat{\beta}_2^{\MTL})$ (see Section \ref{sec_risk} for its precise definition).
+Such models are also known as \textit{hard parameter sharing} \cite{C97,R17}.
+We focus on the case of $r = 1$---otherwise, the global minimizer of $f(A, B_1, B_2)$ reduces to learning each task alone, resulting in no transfer effect (cf.
+Proposition \ref{prop_large_r} in Section \ref{sec_risk}).
+In this case, let $(\hat{A}, \hat{B}_1, \hat{B}_2)$ be a global minimizer of $f(\cdot)$.
+The hard parameter sharing (HPS) estimator for the target task is defined as $\hat{\beta}_2^{\MTL} \define \hat{B} \hat{A}_2$.
+In order to evaluate the estimator, we will study the excess risk, which is the prediction risk at an unseen datapoint (of task two) minus $\sigma^2$, denoted as $L(\hat{\beta}_2^{\MTL})$.
 
-As a motivating example of the above setup, we show an intriguing simulation where combining both datasets jointly results in different transfer effect on $L(\hat{\beta}_2^{\MTL})$, depending on the distance between $\beta^{(1)}$ and $\beta^{(2)}$.
-Figure \ref{fig_motivation} shows the result for a setting where every entry of $X_1, X_2$ is generated from an isotropic Gaussian, and $\beta_1,\beta_2$ are generated such that $\norm{\beta^{(1)} - \beta^{(2)}}^2 \approx 2\mu^2$.
-We observe that for $\mu = 0.25$, $L(\hat{\beta}_2^{\MTL})$ is always smaller than the excess risk of OLS.
-For $\mu = 0.3$ or $0.35$, $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of OLS for a restricted range of $n_1$.
-Such a scenario, where combining both datasets jointly improves over learning the target task individually, is also called a \textit{positive information transfer} \cite{PY09}.
-On the other hand, for $\mu = 0.45$, HPS is always worse than OLS, thus providing a \textit{negative information transfer}.  
-Our main contribution is to precisely analyze a number of interesting phenomena including the above that are prevalent in transfer learning, depending on geometries of the covariance matrices and model distances.
+As a motivating example of the above setup, we show an intriguing simulation where combining both datasets results in different transfer effects.
+Figure \ref{fig_motivation} illustrates a setting where $X_1, X_2$ are sampled from an isotropic Gaussian and $\beta_1,\beta_2$ are generated so that $\norm{\beta^{(1)} - \beta^{(2)}}^2 \approx 2\mu^2$.
+We observe that for $\mu = 0.25$, the transfer effect is always positive---$L(\hat{\beta}_2^{\MTL})$ is always smaller than the excess risk of OLS.
+For $\mu = 0.3$ or $0.35$, the transfer effect is positive only for a restricted range of $n_1$.
+On the other hand, for $\mu = 0.45$, the transfer effect is always negative.  
+Our result below will imply the exact conditions for positive information transfer, depending on $\mu$ and $n_1$.
 
@@
     \includegraphics[width=0.8\textwidth]{figures/motivation.eps}
-    \caption{We illustrate that our setup can reproduce the phenomenon of \textit{positive} (or \textit{negative}) \textit{information transfer}, which is prevalent in the context of transfer learning.
+    \caption{We illustrate that our setup can reproduce the phenomenon of \textit{positive} (or \textit{negative}) \textit{information transfer}, which is prevalent in transfer learning.
     We vary the sample size of dataset one and the distance parameter $\mu$ such that $\norm{\beta^{(1)} - \beta^{(2)}}^2 \approx 2\mu^2$.
-The region below the excess risk of the ordinary least squares (OLS) estimator corresponds to \textit{positive information transfer} when $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of the OLS estimator.
+The region below the excess risk of the ordinary least squares (OLS) estimator corresponds to \textit{positive information transfer}.
 This simulation uses $p = 100, n_2 = 300, \sigma = 1/2$.
@@
 \end{figure*}
+% when $L(\hat{\beta}_2^{\MTL})$ is smaller than the excess risk of the OLS estimator
 
@@
 Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.
-The covariates are assumed to have population covariance equal to $\Sigma^{(i)}$:
-\begin{align}
-    x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)}, \text{ for any } j = 1,\dots,n_i, \label{eq_rvm}
-\end{align}
+The covariates are assumed to have population covariance equal to $\Sigma^{(i)}$: $x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)},$ for any $j = 1,\dots,n_i,$
 where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition (see Section \ref{sec_data} for the precise assumptions).
 
-We focus on the so called \textit{underparametrized} setting for the target task where $n_2 > p$ whereas for dataset one $n_1$ can be either smaller or greater than $p$.
+\paragraph{Main results.} We focus on the so called \textit{underparametrized} setting for the target task where $n_2 > p$ whereas for dataset one $n_1$ can be either smaller or greater than $p$.
 Thus, the OLS estimator exists and it is well-known that the limit of its excess risk when $p$ approaches infinity is equal to $\frac{\sigma^2 p}{n_2 - p}$ (see e.g., \citet{bai2009spectral}).
-By contrast, showing the asymptotic limit of $L(\hat{\beta}^{\MTL}_2)$ in the high-dimensional setting requires dealing with the inverse of the sum of two sample covariance matrices.
-The first challenge is dealing with \textit{covariate shift}---when $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are different.
-The second challenge is dealing with \textit{model shift}---when $\beta^{(1)}$ and $\beta^{(2)}$ are different.
+By contrast, showing the asymptotic limit of $L(\hat{\beta}^{\MTL}_2)$ in the high-dimensional setting requires dealing with the inverse of the sum of two sample covariance matrices under distribution shift.
+%The first challenge is dealing with \textit{covariate shift}---when $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are different.
+%The second challenge is dealing with \textit{model shift}---when $\beta^{(1)}$ and $\beta^{(2)}$ are different.
 Our main result addresses both challenges by \todo{illustrate}.
 \begin{itemize}
-    \item \textbf{Covariate shift:}
+    \item %\textbf{Covariate shift:}
     Our first result applies to settings where $\Sigma^{(1)}$ and $\Sigma^{(2)}$ can be arbitrarily different but $\beta^{(1)} = \beta^{(2)}$.
-    For such settings, we show in Theorem \ref{thm_main_RMT} the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the singular values of the matrix $\big(\Sigma^{(1)}\big)^{1/2}\big(\Sigma^{(2)}\big)^{-1/2}$ and the sample sizes $n_1, n_2$.
-    \item \textbf{Model shift:} Our second result applies to settings where $\beta^{(1)}$ and $\beta^{(2)}$ can be arbitrarily different but $\Sigma^{(1)} = \Sigma^{(2)}$.
-    For such settings, we show in Theorem \ref{cor_MTL_loss} the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the $\ell_2$ distance between $\beta^{(1)}$ and $\beta^{(2)}$, and the sample sizes.
-    \item \textbf{Covariate and model shift:} Our third result applies to settings with both covariate shift and model shift.
-    When $\Sigma^{(2)}$ is isotropic, we show in Theorem \ref{???} the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the singular values of $\Sigma^{(1)}$, the $\ell_2$ distance between $\beta^{(1)}$ and $\beta^{(2)}$), and the sample sizes.
-    For the most general setting when $\Sigma^{(2)}$ is unisotropic, we show in Theorem \ref{prop_main_RMT} an estimate of $L(\hat{\beta}_2^{\MTL})$ that is accurate when $n_1$ is much larger than $n_2$.
+    In Theorem \ref{thm_main_RMT}, we characterize the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the singular values of the matrix $\big(\Sigma^{(1)}\big)^{1/2}\big(\Sigma^{(2)}\big)^{-1/2}$ and the sample sizes $n_1, n_2$.
+    \item %\textbf{Model shift:}
+    Our second result applies to settings where $\beta^{(1)}$ and $\beta^{(2)}$ can be arbitrarily different but $\Sigma^{(1)} = \Sigma^{(2)}$.
+    In Theorem \ref{cor_MTL_loss}, we provide the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ as a function of the $\ell_2$ distance between $\beta^{(1)}$ and $\beta^{(2)}$, and the sample sizes $n_1, n_2$.
+    \item %\textbf{Covariate and model shift:}
+    Our third result applies to settings where both the covariance matrices and the model vectors are different between the two tasks.
+    In Theorem \ref{???}, we show that when $\Sigma^{(2)}$ is isotropic, the asymptotic limit of $L(\hat{\beta}_2^{\MTL})$ is characterized by the singular values of $\Sigma^{(1)}$, the $\ell_2$ distance between $\beta^{(1)}$ and $\beta^{(2)}$), and the sample sizes $n_1, n_2$.
+    Next, in Theorem \ref{prop_main_RMT}, we consider the most general setting concerning an arbitrary $\Sigma^{(2)}$.
+We identify an estimate of $L(\hat{\beta}_2^{\MTL})$ that becomes more and more accurate as $n_1 / n_2$ increases.
 \end{itemize}
 
-Next, we demonstrate the power of these precise asymptotics by explaining a number of empirical phenomena in the context of transfer learning.
+\noindent\textit{Extension to multiple sources.}
+We also extend our setup to the case of having multiple data sources.
+We consider a setting where all datasets have the same features but different labels, which is also known as multi-label prediction \cite{hsu2009multi}.
+We show the asymptotic limit of $L(\hat{\beta}_i^{\MTL})$ under model shift (cf. Theorem \ref{thm_many_tasks}) and use the result to illustrate how to select the hidden width $r$ of $B$.
+
+\paragraph{Theoretical insights and empirical implications.} Next, we demonstrate the power of these precise asymptotics by explaining several empirical phenomena in transfer learning.
 We consider a random-effect model where $\beta^{(i)}$ is equal to a shared model vector plus per-task variances (cf. \citet{dobriban2018high}).
@@
 
-\paragraph{Empirical results.}
 We also complement our theoretical analysis with empirical evaluations.
@@
 
-\paragraph{Extension to multiple sources.}
-Finally, we also extend our setup to the case of having multiple data sources.
-We consider a setting where all datasets have the same features but different labels, which is also known as multi-label prediction \cite{hsu2009multi}.
-We show the asymptotic limit of $L(\hat{\beta}_i^{\MTL})$ under model shift (cf. Theorem \ref{thm_many_tasks}) and use the result to illustrate how to select the hidden width $r$ of $B$.
 %Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
@@
 
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\paragraph{Random matrix theory in machine learning.}
-This work is inspired by an emerging line of recent work that has found random matrix theory useful for studying modern machine learning techniques.
-A prominent line of recent work in this direction has been to understand the generalization properties of interpolators \cite{bartlett2020benign,hastie2019surprises,montanari2019generalization,liang2020just,liang2020precise}.
-Interpolators such as minimum-norm estimators (in the context of linear regression) share similar behavior with modern neural networks in the sense that such models learn by ``memorizing'' the data with lots of parameters \cite{mei2019generalization}.
-The study of such interpolators has also led to an explanation of the double-descent phenomenon \cite{belkin2019reconciling}.
-
-\paragraph{Sample covariance matrices and distribution shift.}
-These previous works primarily deal with a single high-dimensional sample covariance matrix. %need to check 
+\paragraph{Sample covariance matrices under distribution shift.}
 In the \textit{underparametrized} setting ($n_2 > p$) which this work focuses on, when the covariates are sampled from Gaussian distributions, the precise asymptotic limit can be derived directly from properties of the Wishart distribution (see also Lemma \ref{fact_tr} and the historical notes in Section \ref{sec_bv}).
@@
 These results are proved by establishing certain optimal convergence estimates of the Stieltjes transforms of sample covariance matrices, which are referred to as \emph{local laws} in the random matrix theory literature.
-We refer the reader to \cite{erdos2017dynamical} and the references therein for a detailed review of related concepts.
+We refer interested readers to \citet{erdos2017dynamical} and the references therein for a detailed review of related concepts.
 Our technical contribution is to extend these techniques to the two-task setting and prove a local law for the sum of two sample covariance matrices with arbitrary covariate shifts.
@@
 
-\paragraph{Transfer learning and domain adaptation theory.}
-Earlier works on transfer learning and domain adaptation use uniform convergence to obtain generalization bounds \cite{B00,BS03,M06}.
+\paragraph{Transfer learning theory.}
+Earlier works such as \citet{B00,BS03,M06} use uniform convergence to obtain generalization bounds on transfer learning (also called domain adaptation).
 The influential paper by \citet{BBCK10} proposes a rigorous model for domain adaptation in classification (see also \citet{crammer2008learning} for an earlier result).
-The main result provides a generalization bound for combining multiple data sources using an objective that averages over the risk of every datapoint.
+Their main result provides a generalization bound for combining multiple data sources using an objective that averages over the risk of every datapoint.
 This bound provides a principled way to reweight each data source by minimizing the bound.
-From a technical perspective, uniform convergence based techniques provide upper bounds on the excess risks.
-On the other hand, analyzing the empirical phenomena of information transfer such as the ones in Figure \ref{fig_motivation} requires tight lower bounds on the excess risks.
+From a technical perspective, uniform convergence-based techniques provide upper bounds on the excess risks.
+However, analyzing the empirical phenomena of information transfer such as the ones in Figure \ref{fig_motivation} requires tight lower bounds on the excess risks.
+The very recent work of \citet{mousavi2020minimax} introduced a minimax framework to quantify the fundamental limit of transfer learning.
+Their result quantities the minimax risk using the distance between the source and target models.
+Our work provides precise estimates that accurately match the empirical risk of commonly used estimators compared to their work.
+These precise estimates are necessary for analyzing these estimators' transfer effect.
 
@@
 The work of \citet{li2020transfer} considers the problem of how to select useful data sources for transfer learning under model shift.
-Their work provides an adaptive procedure that applies even when the set of useful data sources are unknown.
+Their work provides an adaptive procedure that applies even when the set of beneficial data sources is unknown.
 Our work differs from theirs in two aspects.
-First, we considered a high-dimensional setting where the sample size increases with dimension proportionally.
-Such a setting allows us to derive precise asymptotics of the excess risks, which is then used to explain a number of interesting phenomena in transfer learning.
-Second, our result applies to covariate-shifted (and not necessarily Gaussian) source datasets whereas the setting of \citet{li2020transfer} assumes the covariates of all data sources and the target are drawn from a Gaussian distribution with the same population covariance matrix.
-The work of \citet{lei2021nearoptimal} considers a setting of linear regression under distribution shift including covariate shift and model shift similar to our setting.
-The difference is that our setting deals with a labeled target dataset whereas the result of \citet{lei2021nearoptimal} applies to settings with an unlabeled target dataset.
+First, we considered a high-dimensional setting where the sample size increases with dimension proportionally by a constant factor.
+We use this setting to reproduce several interesting phenomena in  transfer learning.
+Second, our estimates apply even under covariate shift, whereas the result of \citet{li2020transfer} requires that there is no covariate shift between the data sources and the target task.
+Another work by \citet{lei2021near} considers a  linear regression setting under distribution shift, including covariate shift and model shift.
+The difference is that our setting deals with a labeled target dataset. In contrast, \citet{lei2021near} deal with an unlabeled target dataset (i.e., unsupervised domain adaptation).
+%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
+
+%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
+%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
+%For such models, their output dimension plays an important role of regularization \cite{KD12}.
+%Below, we describe several lines of work that are most related to this work.
+
+%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
+%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
+%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
+%Our work is closely related to Wu et al. \cite{WZR20}.
+%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
+%\todo{spell out the challenge more explicitly}
+
+%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
+%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
+%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
+%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
+%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
+%We believe that our theoretical framework can apply to other approaches to multi-task learning.
+
 %One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
@@
 %	\item \citet{lounici2011oracle}
+\paragraph{Random matrix theory in machine learning.}
+This work joins an emerging line of recent work that has found random matrix theory useful for studying modern machine learning techniques.
+A prominent example is looking at interpolators in over-parametrized linear and logistic regression \cite{bartlett2020benign,hastie2019surprises,montanari2019generalization,liang2020just,liang2020precise}.
+Interpolators can reproduce similar phenomena observed under neural networks because both models learn by ``interpolating'' the data using many parameters \cite{mei2019generalization}.
+The precise rates achieved via random matrix theory can also explain the double-descent phenomenon \cite{belkin2019reconciling}.
+Whereas these works deal with covariates drawn from a single distribution, our work instead tackles distribution shift given covariates sampled from two distributions.
 

### 2021-07-25 revision_journal/multitask.tex
move figs around
start sec 1.2
finish sec 1.2, begin sec 1.3
finish intro

@@
-\section{Extension to multiple data sources}\label{sec_same}
+\section{Extension to multiple sources}\label{sec_same}
 
@@
 Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from any other $\beta^{(j)}$ for $j \neq i$, the matrix $X$, and $\varepsilon^{(j)}$ for any $j=1,\dots,t$.
+As a remark, the above data model is similar in spirit to the setting of \citet{lounici2011oracle}.
+While that work assumes all of the model vectors $\beta^{(1)}, \beta^{(2)}, \dots, \beta^{(t)}$ share the same subset of non-zero coordinates, our result below will apply even when these vectors do not satisfy such conditions.
 
@@
 
+\begin{figure}[!t]
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/multitask_width.eps}
+		\caption{Varying width}
+		\label{fig_sec4_width}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{figures/multitask_b.eps}
+		\caption{Varying sample size and model shift parameter}
+		\label{fig_sec4_transfer}
+	\end{subfigure}
+	\caption{We illustrate the performance of HPS in the random-effect model with $p = 100, t = 10, \sigma = 1/2$.
+	Figure \ref{fig_sec4_width} shows that from $1$ to $t = 10$, setting width $r = 1$ gives the lowest excess risk for task $t$.
+	The result is averaged over three random seeds.
+	This simulation uses $\mu = 0.05$.
+	Figure \ref{fig_sec4_transfer} fixes $r = 1$ while varying $\mu$ and $n$.
+We observe that depending on $\mu$ and $n$, HPS may provide a positive transfer or a negative transfer to task $t$ (similar to Figure \ref{fig_sec3_model_shift}).
+The precise condition for determining the transfer effect can be found in Claim \ref{claim_re_multi}.}
+	\label{fig_sec4}
+\end{figure}
+
 \paragraph{Illustrative examples.}
@@
 
-\begin{figure}[!t]
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.8\textwidth]{figures/multitask_width.eps}
-		\caption{Varying width}
-		\label{fig_sec4_width}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.8\textwidth]{figures/multitask_transfer.eps}
-		\caption{Varying sample size and model shift parameter}
-		\label{fig_sec4_transfer}
-	\end{subfigure}
-	\caption{We illustrate the performance of HPS in the random-effect model with $p = 100, t = 10, \sigma = 1/2$.
-	Figure \ref{fig_sec4_width} shows that from $1$ to $t = 10$, setting width $r = 1$ gives the lowest excess risk for task $t$.
-	The result is averaged over three random seeds.
-	This simulation uses $\mu = 0.05$.
-	Figure \ref{fig_sec4_transfer} fixes $r = 1$ while varying $\mu$ and $n$.
-We observe that depending on $\mu$ and $n$, HPS may provide a positive transfer or a negative transfer to task $t$ (similar to Figure \ref{fig_sec3_model_shift}).
-The precise condition for deciding which one is provided in Claim \ref{claim_re_multi}.}
-	\label{fig_sec4}
-\end{figure}
-
-Figure \ref{fig_sec4} validates Claim \ref{claim_re_multi}.
+Figure \ref{fig_sec4} validates the result of Claim \ref{claim_re_multi} in finite dimensions.
 First, we see that the empirical excess risk (measured on a particular task) is indeed smallest when the width $r$ is equal to $1$.
 Second, we see that HPS provides a positive transfer (to a particular task) depending on the sample size $n$ and the model shift parameter $\mu$.
-The results match with the condition (on $\mu$) suggested by our estimates.
+The results under different $\mu$ values match with the condition in Claim \ref{claim_re_multi}.
 

### 2021-07-25 revision_journal/abstract.tex
abstract

@@
 \begin{abstract}
-%	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
-First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
+    We consider the problem of transfer learning---gaining knowledge from one task and applying it to a different but related target task.
+    A fundamental question in transfer learning is when combining the data of both tasks works better than using only the target task's data (equivalently, when there is a ``positive information transfer'').
+    We study this question formally in a linear regression setting where a certain two-layer linear neural network estimator is used to combine both tasks' data.
+    Under various settings involving covariate and model shifts, the estimator reproduces several interesting behaviors regarding positive (and negative) information transfer observed on real-world data.
+
+    We then show the precise asymptotic limit of risk of the estimator in terms of geometries of the data in a high-dimensional setting, where the sample sizes increase with the feature dimension proportionally at a fixed ratio.
+    We also find that the asymptotics is accurate for finite dimensions and apply them to analyze the exact conditions for positive information transfer.
+    This analysis leads to several novel insights regarding covariate and model shifts.
+    For example, the risk curve is non-monotone under model shift, thus motivating a more efficient procedure for progressively adding data.
+    The main ingredient of our analysis is showing the asymptotic limit of certain combinations of independent sample covariance matrices under covariate shift and different sample sizes, which may be of independent interest.
+
+%	We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
 Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.

### 2021-07-25 revision_journal/exp.tex
finish intro
abstract

@@
 		\includegraphics[width=0.95\textwidth]{figures/compare_risk_cov_model_shift.eps}
-		\caption{Covariate and model shift}
+		\caption{Covariate and model shifts}
 		\label{fig_sec5_cov_model}
@@
 	\caption{We compare the empirical excess risk of HPS and several natural transfer learning estimators.
-We find that HPS achieves the lowest excess risk for predicting task two under (either or both) covariate and model shift.
+We find that HPS achieves the lowest excess risk for predicting task two under covariate and model shifts.
 This simulation uses $p = 50, n_1 = n_2 = 100, \sigma = 1/2$.
@@
 
-\begin{wrapfigure}[12]{r}{0.3\textwidth}
-	\vspace{-0.35in}
+\begin{wrapfigure}[11]{r}{0.3\textwidth}
+	\vspace{-0.15in}
 	\begin{center}
-		\includegraphics[width=0.27\textwidth]{figures/mtl_model_arch.pdf}
+		\includegraphics[width=0.25\textwidth]{figures/mtl_model_arch.pdf}
 	\end{center}
@@
 A separate output layer is used for predicting the labels of each dataset.
-We evaluate on three possibilities of feature representation layers including LSTM, MLP, and CNN, as implemented by PyTorch.\footnote{\url{pytorch} Before the MLP layer, we apply an average pooling layer over the embedding of every word in the sentence.}
+We evaluate on three possibilities of feature representation layers including LSTM, MLP, and CNN, all of which are implemented using PyTorch.\footnote{The PyTorch neural network modules are available at \url{https://pytorch.org/docs/stable/nn.html}.}
 See Figure \ref{fig_intro_arch} for an illustration of the network architecture.

### 2021-07-25 revision_journal/intro.tex
abstract

@@
 A frequent impediment to applying transfer learning is \textit{negative information transfer} if combining both data performs worse than learning a single task clone \cite{PY09}.
-\textit{Positive information transfer} refers to the desirable scenario where a task of interest benefits when combined with another task.
+\textit{Positive information transfer} refers to the desirable scenario where a task of interest benefits from another task's data.
 
@@
 
-The key ingredient of our analysis is showing the asymptotic limit of certain combinations of sample covariance matrices under distribution shift, using the local laws developed recently by \citet{isotropic} and \citet{BES_free1}.
+The key ingredient of our analysis is showing the asymptotic limit of certain combinations of sample covariance matrices under distribution shift, using the \textit{local laws} developed recently by \citet{isotropic} and \citet{BES_free1}.
 After formally defining the specific problem that we tackle, in Section \ref{sec_related}, we provide a technical discussion of the related works in random matrix theory.
@@
 where $\varepsilon^{(i)}_j\in\real$ denotes a random noise variable with mean zero and variance $\sigma^2$.
-For the ease of presentation, we refer to the first dataset as the source and the second task as the target.
-%Our goal is to learn an estimator to predict the target task given both datasets.
+We focus on the so called \textit{underparametrized} setting for the target task where $n_2 > p$ whereas for dataset one $n_1$ can be either smaller or greater than $p$  (see Section \ref{sec_data} for the precise assumptions).
+For the ease of presentation, we refer to the first task as the source and the second task as the target.
 
@@
 \end{align}
-The above objective uses $A$ as the shared feature space for both tasks and $B_1, B_2$ as the prediction head for each task.\footnote{Popular variants of the objective function \eqref{eq_hps} include adding a weight parameter to each summand and adding ridge regularization.
+The above objective uses $A$ as the shared feature space for both tasks and $B_1, B_2$ as the prediction head for each task.\footnote{Popular variants of the objective function \eqref{eq_hps} also involve weight parameters for each task and ridge regularization.
 We focus on the unweighted and unregularized objective for simplicity.
-All of the asymptotic limits we show below can be straightforwardly extended to weighted and regularized objectives.}
+All of the asymptotic limits described below can be straightforwardly extended to weighted and regularized objectives.}
 Such models are also known as \textit{hard parameter sharing} \cite{C97,R17}.
-We focus on the case of $r = 1$---otherwise, the global minimizer of $f(A, B_1, B_2)$ reduces to learning each task alone, resulting in no transfer effect (cf.
+We focus on the case of $r = 1$---otherwise, the global minimizer of $f(A, B_1, B_2)$ reduces to learning each task alone, resulting in zero information transfer (cf.
 Proposition \ref{prop_large_r} in Section \ref{sec_risk}).
-In this case, let $(\hat{A}, \hat{B}_1, \hat{B}_2)$ be a global minimizer of $f(\cdot)$.
+For the case of $r = 1$, let $(\hat{A}, \hat{B}_1, \hat{B}_2)$ be $f(\cdot)$'s global minimizer, which is unique because $n_2 > p$.
 The hard parameter sharing (HPS) estimator for the target task is defined as $\hat{\beta}_2^{\MTL} \define \hat{B} \hat{A}_2$.
@@
 The covariates are assumed to have population covariance equal to $\Sigma^{(i)}$: $x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)},$ for any $j = 1,\dots,n_i,$
-where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition (see Section \ref{sec_data} for the precise assumptions).
+where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition.
 
-\paragraph{Main results.} We focus on the so called \textit{underparametrized} setting for the target task where $n_2 > p$ whereas for dataset one $n_1$ can be either smaller or greater than $p$.
+\paragraph{Main results.} 
 Thus, the OLS estimator exists and it is well-known that the limit of its excess risk when $p$ approaches infinity is equal to $\frac{\sigma^2 p}{n_2 - p}$ (see e.g., \citet{bai2009spectral}).
@@
     When $\frac{\sigma^2 n_2}{2(n_2 - p)} \le \mu^2$, the transfer effect is negative for any $n_1$.
-    Additionally, we illustrate that these three regimes of information transfer arises under both covariate and model shift (cf. Figure \ref{fig_sec3_cov_mo_b}).
+    Figure \ref{fig_motivation} suggests that the asymptotic limits are also accurate in finite dimensions.
+    Additionally, these three regimes of information transfer can be observed in settings of covariate and model shifts (cf. Figure \ref{fig_sec3_cov_mo_b}).
 \end{enumerate}

### 2022-02-13 prior_versions/abridged/experiments.tex
update

--- 2021-06-12 revision_journal/backup/Jan 01 2021/manuscript.tex
@@
-\documentclass[aos,preprint]{imsart}
-\usepackage{xr}
-	\externaldocument{./suppl}
-
-%% Packages
-\def\shownotes{0}
-%\usepackage{natbib}
-%\setcitestyle{authoryear,open={(},close={)}}
-%\renewcommand{\cite}{\citep}
-\usepackage[export]{adjustbox}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{fullpage}
-\usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
-\usepackage{macro_fan}
-\usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage{caption,subcaption}
-%\usepackage{breqn}
-
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Uncomment next line to change            %%
-%% the type of equation numbering           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\numberwithin{equation}{section}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Axiom, Claim, Corollary, Hypothezis, %%
-%% Lemma, Theorem, Proposition              %%
-%% use \theoremstyle{plain}                 %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\theoremstyle{plain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Assumption, Definition, Example,     %%
-%% Notation, Property, Remark, Fact         %%
-%% use \theoremstyle{remark}                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please put your definitions here:        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-\title{Hard Parameter Sharing in High-dimensional Linear Regression}
-%\title{A sample article title with some additional note\thanksref{t1}}
-\runtitle{Hard Parameter Sharing in High-dimensional Linear Regression}
-%\thankstext{T1}{A sample additional note to the title.}
-
-\begin{aug}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Only one address is permitted per author. %%
-%%Only division, organization and e-mail is %%
-%%included in the address.                  %%
-%%Additional information can be included in %%
-%%the Acknowledgments section if necessary. %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu} \thanks{Fan Yang and Hongyang R. Zhang contributed equally.}}
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}\samethanks} 
-\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3,mark]{senwu@stanford.edu}} 
-\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4,mark]{suw@wharton.upenn.edu} }
-\and
-\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5,mark]{chrismre@cs.stanford.edu}} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Addresses                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address[A]{Department of Statistics,
-University of Pennsylvania,
-\printead{e1,e4}}
-\address[B]{Khoury College of Computer Sciences, Northeastern University,
-\printead{e2}}
-\address[C]{Department of Computer Science, Stanford University,
-\printead{e3,e5}}
-
-\end{aug}
-
-\begin{abstract}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
-First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
-Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
-We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
-This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-\end{abstract}
-
-\begin{keyword}[class=MSC2020]
-\kwd[Primary ]{62J05}
-\kwd{60B20}
-\kwd[; secondary ]{62E20, 62H10}
-\end{keyword}
-
-\begin{keyword}
-\kwd{Hard parameter sharing, high-dimensional linear regression, random matrix theory, sample covariance matrices}
-\end{keyword}
-
-\end{frontmatter}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please use \tableofcontents for articles %%
-%% with 50 pages and more                   %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\tableofcontents
-
-\section{Introduction}\label{sec_introduction}
-
-Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
-Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
-
-Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
-		\label{fig_intro_arch}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure*}
-
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
-
-\subsection{Setup and Main Results}
-
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
-Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
-\begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-\end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
-
-\medskip
-\noindent\textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \cite{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
-
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-\begin{itemize}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
-
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
-
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
-For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
-\end{itemize}
-
-%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-%\squishlist
-%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-%	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-%	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-%\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-%Our study also leads to several algorithmic consequences with practical interest.
-%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-
-%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-%Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
-
-\medskip
-\noindent\textbf{Proof techniques.}
-There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
-The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
-Theorem \ref{thm_main_RMT}).
-We use recently developed techniques from random matrix theory to show a sharp convergence rate.
-% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
-%\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
-See Section \ref{sec_conclude} for more discussions of the technical challenge.
-
-%This part introduces a positive variance reduction effect from adding the source labels.
-%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
-%(i) the negative effect from model shift bias.
-%(ii) the positive effect from variance reduction;
-
-\subsection{Related Work}
-
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\smallskip
-\noindent\textbf{Organizations.}
-The rest of this paper is organized as follows.
-In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation}, we validate our results in simulations.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{sec_text} describes our study on text classification tasks.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
-
-\medskip
-\noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$.
-Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$.
-In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-
-\section{Hard parameter sharing estimator}\label{sec_HPS}
-
-Consider the transfer learning setting with two data sets.
-We denote their sample sizes by $n_1$ and $n_2$.
-For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
-$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-We study the standard hard parameter sharing architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
-Then we study the following minimization problem:
-\begin{align}\label{eq_tsl}
-			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
-\end{align}
-where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
-\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
-In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
-We remark that all these assumptions are natural in high-dimensional statistics.
-
-We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let 
-\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
-where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
-entries satisfying
-\begin{equation}\label{assm1}
-\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1, 
-\end{equation}
-Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
-\be \label{conditionA2}
-\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
-\ee
-for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee
-%for a small constant $\tau>0$.
-
-We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\be\label{eq_highmoments}
-\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
-\ee
-Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$. 
-%Moreover, we assume that 
-%\be\label{eq_SNR}
-%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
-%\ee
-%for a small constant $\tau >0$.
-The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.
-
-In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that 
-\be\label{assm2}
-1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
-\ee
-for a small constant $\tau >0$.
-If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper.
-The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
-are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.
-
-We summarize our basic assumptions here for future reference.
-\begin{assumption}\label{assm_big1}
-Let $\tau$ be a small constant. 
-\begin{enumerate}
-\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}.
-%and (\ref{assm2}).
-We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-
-\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-
-\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
-
-\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.
-
-\end{enumerate}
-\end{assumption}
-
-For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that  
-	\begin{align}
-		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
-where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
-Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers.
-Could you replace $A$ with another symbol (say $x$)?}
- \begin{align}
-		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
-			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
-		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
-	\end{align}
-Let $\hat a$ be the minimizer of $g(a)$.
-Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.
-Then the HPS estimator \eqref{def_HPS} for the target task 2 is
-\be\label{HPS_est}
-\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
-\ee
-
-In this paper, we study the out-of-sample predication loss (test error) of $\hat{\beta}_2^{\MTL} (\hat a)$.
-Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
-$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$ 
-Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
-\be\label{HPS_loss}
-L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
- \ee
-We will compare it to the out-of-sample predication loss $L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator 
-$$\hat \beta^{\STL}= [(X^{(2)})^\top X^{(2)}]^{-1}(X^{(2)})^\top Y^{(2)}$$ as a baseline.
-
-Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-\end{align}
-Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-where 
-\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-is called the bias term, which depends on the model bias between task 1 and task 2, and
-\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-%predication loss for the HPS and OLS estimators.
-
- \begin{lemma}\label{lem_HPS_loss}
- Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$: 
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
-\end{align}
-and 
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-\end{align}
-%Moreover, there exists a constant $C_0>0$ such that with high probability,
-%\be\label{loss_large}
-%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-%\ee
-%with high probability for any small constant $\e>0$. 
-\end{lemma}
-
-Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$.
-In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
-(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}.
-To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
-Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.
-
-%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
-
-For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.
-
-\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that
-		\[ \bigtr{\Sigma^{(2)} \frac1{(X^{(2)})^\top X^{(2)} }  } = \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } = \frac{p}{n_2 - p} \cdot \left[1+ \OO\left( \frac{p^{\e}}{\sqrt{np}} \right)\right] \]
-		with high probability for any small constant $\e>0$.
-\end{lemma}
- %The above result has a long history in random matrix theory.
-If the entries of $Z^{(2)}$ are i.i.d.
-Gaussian, then this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
-Lemma 3.11 of \cite{bai2009spectral}).
-Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate.
-With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   . \label{L_STL_simple01}
-\end{align}
-
-On the other hand, much less is known about the predication loss of the HPS estimator.
-In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-\FY{What is known so far about this topic?} In the rest of this paper, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in three different settings of increasing complexity: (i) same covariates $X^{(1)}=X^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (iii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In each case, we provide the exact asymptotic bias and variance limits, together with almost sharp convergence rates.
-In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.
-
-%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-\section{HPS estimator: Bias-variance tradeoff}\label{sec_same}
-
-%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
-%We provide a sharp generalization error bound of hard parameter sharing estimators.
-
-In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
-We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
-$ {B^\star}^\top \Sigma  B^\star,$ where $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ is the matrix formed by the linear model parameters of the two tasks.
-Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is well-defined.
-Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
-
-\begin{theorem}\label{thm_two_tasks}
-Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2$. Let $c>0$ be an arbitrary small constant. Then we have that with high probability, 
-\be\label{minimizer_beta1}
-\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
-\ee
-where $u_{\hat a}$ is a unit vector defined as
-$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-%for task 2,  % over the randomness of the input, 
-Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
-	\begin{align}
-		& \bigabs{L(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) (B^{\star}A^{\star})  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
-		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	 where $A^\star(2)$ denotes the second entry of $A^\star$.
-	 \end{theorem}
-
-Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
-Moreover, the factor $(\lambda_1 - \lambda_{2})^{-1}$ is natural, because the two eigenspaces of ${B^{\star}}^{\top}\Sigma B^{\star}$ are not stable when $\lambda_1 $ and $\lambda_{2} $ are close to each other.
-The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-It is not hard to extend the above result to the cases with more than two tasks.
-We make this extension for the following reasons.
-First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
-Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-
-\vspace{5pt}
-\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
-The label vector of the $i$-th task follows a linear model
-$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
-We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
-
-%\begin{enumerate}
-%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-%\end{enumerate}
-
-	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
-	\begin{align}
-		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
-%Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-
-	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
-Hence we only consider the case with $r<t$.
-\FY{Correct it if the reason is wrong.}
-
-	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
-	\begin{align}
-		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
-		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
-	\end{align}
-	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
-	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
-	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
-	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
-	\end{align}
-%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
-%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
-%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
-
-Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is the covariance of the task labels):
-\begin{align}\label{eq_A_star}
-	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
-\end{align}
-where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
- To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
-Otherwise, Theorem \ref{thm_many_tasks} will give a null result.
- %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
-Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
-Then we have the following result.
-
-% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
-%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
-%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
-%Our result is stated as follows.
-
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
-	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
-Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary small constant. Then for any task $i = 1,  \cdots, t$, we have that high probability, 
-\be\label{minimizer_beta}
-\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
-\ee
-where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that
-	\begin{align}
-		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
-		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
-\label{Li_multi1}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
-%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
-%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
-Finally, we have a better bound for the averaged prediction loss:  
-\begin{align}
-&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
- &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 ,\label{Li_multi2}
-\end{align}
-with high probability.
-\end{theorem}
-
- The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
-The estimate \eqref{Li_multi1} shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
-Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases in the HPS for multi-task setting.
-On the other hand, the bias term always increases, because the bias in single-task linear regression is zero.
-Hence whether the HPS estimator is better than the OLS estimator depends on an intricate \emph{bias-variance tradeoff}.
-%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.}
-We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
-Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
-For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
-
-The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
-Moreover, Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
-
-%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-%\medskip
-%
-%\noindent\textbf{Comparison to single-task learning (STL).}
-%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
-%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
-%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
-%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.
-
-\iffalse
-\paragraph{How does hard parameter sharing scale with sample size $n$?}
-Obviously, the concentration error decreases with $n$.
-First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
-It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
-
-\begin{assumption}\label{assume_rm}
-	Let $\tau > 0$ be a small enough constant.
-%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
-entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	In the high-dimensional setting,
-%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-%			\begin{align}\label{assmAhigh}
-%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
-%			\end{align}
-  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
-%	\end{enumerate}
-\end{assumption}
-Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
-
-\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	With high probability over the randomness of $X$, we have that
-		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
-\end{fact}
-\noindent\textit{Remark.} The above result has a long history in random matrix theory.
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
-Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
-		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
-		\fi
-
-%Finally, for the random noise component, we assume that all of its moments exist.
-%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
-%\begin{align}\label{assmAhigh2}
-%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
-%\end{align}
-%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
-%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
-
-%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
-To illustrate the {bias-variance tradeoff quantitively, we consider a random-effect model, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
-\begin{example}[Random-effect model]\label{ex_same_cov}
-Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-More precisely, %we have
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-and $\wt \beta^{(i)}$ denotes the $i$-th 
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. 
-%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
-%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
-
-In the random-effect model described above, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
-%Based on the definition of the random-effect model, 
-the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
-%\begin{align*}
-%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
-%\end{align*}
-\begin{align}\label{betaSbeta}
-	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
-\end{align}
- with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}. 
-%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
-With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
-$$\lambda_1=(1+\OO(p^{-1/2+c}))\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
-and
-$$ \lambda_i=(1+\OO(p^{-1/2+c}))\frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
-Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
-$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
-with high probability. 
-%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
-%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
-%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
-%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
-Then using \eqref{Li_multi2}, we obtain that
-\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p.
-}\]
-%We describe a proof sketch.
-%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
-%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
-%Second, using Fact \ref{fact_tr}, one can see that the average variance is
-%\begin{align*}
-%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
-%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
-%\end{align*}
-%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
-%Combined together, we have derived the average prediction loss in the random-effect model.
-If the error is sufficiently small, then comparing the above equation with \eqref{L_STL_simple01}, we have the following observations. 
-%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
-%Comparing HPS to STL, we have the following qualitative properties.
-%	Suppose $n$ is sufficiently large so that the error is negligible.
-%\begin{enumerate}
-\begin{enumerate}
-	\item {\bf Positive vs.
-negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
-
-	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
-Hence increasing the width $r$ of the shared feature representation layer does not help.
-	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-
-	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
-Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
-More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
-	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
-}\]
-	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
-	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$ 
-	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
-
-	%samples that is less than $n$ samples to get comparable loss to STL.
-	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
-	\end{enumerate}
-
-\end{example}
-
-\FY{add applications, simulations, and algorithm consequences of the results in this section}
-
-\section{HPS estimator: Varying sample sizes} 	\label{sec_sizeratio}
-
- In this section, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effect of the sample sizes on the predication loss of the $\MTL$ estimator.
-
-\begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1} holds, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \left[ \cal L_1(a)+ \OO\left(\frac{p^{c}}{n_1}\right)\right] \cdot   \sigma^2 ,
-\ee
-and 
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right]   \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions  
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}. 
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)} 
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
-
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider 
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter 
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where 
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we denote $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. Using the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical eigenvalue distributions (ESD) of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$ satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the Gaussian assumption, $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other.
-Hence the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measure.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-
-We believe that the above argument can be extended to the case without Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some hard technical conditions for our setting.
-Hence we do not pursue this direction in this paper.
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
-
-Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-\begin{example}[Sample sizes]\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
-First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
-	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
-	\begin{proposition}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Suppose Assumption \ref{assm_big1} and the setting in Example \ref{ex_same_cov} hold. Suppose that
-	\be\label{para_rel}
-	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
-	\ee
- for a constant $c_0>0$. Then we have that for any small constant $c>0$ and large constant $ C>0$,
-	%Let $c$ be a sufficiently small fixed constant.
-	%In the setting of Corollary \ref{cor_MTL_loss}, 
-%There exists a constant $C>0$ such that
-	\be\label{hatw_add1}
-	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
-	\ee
-\end{proposition}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-%and $\wt \beta^{(i)}$ denotes the $i$-th 
-%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (1+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
-$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
-with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations. 
-Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term is always positive.
-Moreover, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-
-For a fixed $n_2$, we study the intricate bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$,
-$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, which gives the quantitive information transfer from the source task to the target task.
-First, we have positive (resp.
-negative) transfer if and only if $h(\rho)>0$ (resp.
-$h(\rho)<0$).
-Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
-\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-Then we observe the following dichotomy.
-\begin{enumerate}
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
-
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
-
-\begin{itemize}
-\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
-
-\item If $(1+\rho_2)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
-Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
-\end{itemize}
-\end{enumerate}
-Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial 
-\be\label{poly2}
- \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy.
-\begin{enumerate}
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
-
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global minimum at $\rho=\rho_c$.
-\end{enumerate}
-
-%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance. 
-%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
-\iffalse
-Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
-
-Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
-	\begin{align*}
-		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
-		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
-		= \frac{p}{n_1 + n_2 - p},
-	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit.
-	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
-
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
-This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
-by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-
-{\cor 
-For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
-	\begin{align}
-		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
-		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
-			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
-For the bias term,
-}
-
-Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
-For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
-We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
-It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
-By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
-\fi
-
-	\end{example}
-
-	\FY{add applications, simulations, and algorithm consequences of the results in this section}
-
-\section{HPS estimator: Covariate shift}\label{sec_diff}
-
-%The previous section assumes that all tasks have the same sample size and feature vectors.
-Finally, in this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift'', which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give a rough estimate on it.
-
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix (rescaled by $a$) 
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a), \lambda_2(a), \dots, \lambda_p(a)$ denote the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-%for some small constant $0<\tau<1$. 
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
-
-\begin{theorem}\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for the variance term $L_{\var}(a)$ in \eqref{Lvar}: 
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
-			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following self-consistent equations
-			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that 
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$.
-Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
-%also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
-and plug them into equation \eqref{lem_cov_shift_eq}.  The proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{appendix RMT} in the supplement \cite{MTL_suppl}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
-
-\begin{example}[Covariate shift]\label{ex_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds.
-In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
-Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
-$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
-where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
-We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
-\end{align*}
-%belong to the following bounded set.
-%Let $\lambda_i$ be the $i$-th singular value of $M$.
-%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-%\vspace{-0.025in}
-%{\small}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-%\begin{proposition}[Covariate shift]\label{prop_covariate}
-%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-%	We have that
-%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
-%\end{proposition}
-%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
-Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix. 
-%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-%Let 
-%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
-%We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
-%\be \nonumber
-%\begin{split}
-%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
-%\end{split}
-%\ee
-%with high probability for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-%
-%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-%\begin{align}\label{gvar_extra}
-%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-%\end{align}
-From equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
- a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
-\ee
-Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that 
-%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-%\begin{align}\label{approximateteM}
-%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-%\end{align}
-%where
-$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}. 
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that 
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
-
-%Hence we get that 
-%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-%
-%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-%\begin{align}\label{gvar_extra2}
-%\begin{split}
-%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-%\end{split}
-%\end{align}
-%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-%\end{proof}
-
-\iffalse
-For large enough $p$,
-%in the left hand side of equation \eqref{lem_cov_shift_eq}:
-\begin{align*}
-	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
-\end{align*}
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
-\fi
-
-%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}. 
-%Our first observation is that:
-However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
-We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$.
-In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
-When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
-%while as As $\lambda$ increases, the severity of covariate shift increases.
-We claim the following dichotomy.
-\begin{enumerate}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-\end{enumerate}
-We explain why the above dichotomy happens. We can write that variance limit as
-$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
-When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
-$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
-where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
-\begin{align*}
-\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
-\end{align*}
-%in this example is equal to
-%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
-%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%where $g(\lambda, a_1) \ge 0$.
-%and can be derived from algebraic calculations (details omitted).
-We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
-In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
-\begin{align*}
- \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
-\end{align*}
-%\begin{align*}
-% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-%\end{align*}
-This implies $n_1>n_2$.
-The other direction follows from a similar argument.
-% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
-\end{example}
-
-\iffalse
-%FY: Below was the word explanation. I still think the above simple proof is clearer.
-In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
-The other case when $n_1 < n_2$ is similar.
-A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
-If $n_1< n_2$, then $f(\lambda)< f(1)$.
-\fi
-
-For the bias limit, we have the following proposition.
-
-\begin{proposition}\label{prop_main_RMT}
-%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for the bais term $L_{\bias}(a)$ in \eqref{Lbias}:
-			\begin{align}
-				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 + n_1^{-1/2+2/\varphi + c}\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
-				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
-			\end{align}
-%			\begin{align}\label{lem_cov_derv_eq}
-%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-%			\end{align}
-				uniformly in all $a\in \R$. Here $\Pi(a)$ is a $p\times p$ matrix defined as
-				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				$\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, and $(a_{3},a_4)$ is the solution of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-		\be  \label{eq_a34extra}
-		\begin{split}
-				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
-				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{split}
-			\ee  
-			where recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
-
-Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
-Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
-Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
-$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$ 
-and
-$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
-Using these estimates, it is easy to check that  
-\begin{align}
-& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
-&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
-\label{bias_LLN}
-\end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ by the law of large numbers in the regime $n_1\gg p$.
-However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
-
-\begin{remark}
-%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%\begin{remark}
-The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
-We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
-We leave this problem to future study.
-
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for dealing with the bias term also fails, because we cannot reduce the problem into the study of the addition of two random matrices that are asymptotically freely independent.
-%\end{remark}
-\end{remark}
-
-\FY{add applications, simulations, and algorithm consequences of the results in this section}
-
-\section{Experiments}
-
-\subsection{Simulation Studies}\label{sec_simulation}
+\vspace{-0.05in}
+\section{Simulation Studies}\label{sec_simulation}
+\vspace{-0.05in}
 
@@
 
-\begin{figure*}[!t]
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
-		\caption{Example \ref{ex_same_cov}}
-		\label{fig_same_cov}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
-		\caption{Example \ref{ex_sample_ratio}}
-		\label{fig_size}
-	\end{subfigure}\hfill
-	\begin{subfigure}[b]{0.33\textwidth}
-		\centering
-		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
-		\caption{Example \ref{ex_covshift}}
-		\label{fig_covariate}
-	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
-	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
-	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
-	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
-%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
-	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
-	\label{fig_model_shift_phasetrans}
-\end{figure*}
-
-\paragraph{Sample efficiency.}
+\textbf{Sample efficiency.}
 First, we validate the result of Example \ref{ex_same_cov}.
@@
 
-\paragraph{Sample size ratio.}
+\textbf{Sample size ratio.}
 Second, we validate the result of Example \ref{ex_sample_ratio}.
@@
 
-\paragraph{Covariate shift.}
+\textbf{Covariate shift.}
 Finally, we validate the result of Example \ref{ex_covshift}.
@@
 %\end{figure}
-
-\subsection{Further Studies on Text Classification Tasks}\label{sec_text}
-
-Our results and simulations are all in the high-dimensional linear regression setting.
-How well do they extend to other scenarios?
-In this section, we conduct further studies on six text classification datasets.
-Our datasets include a movie review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
-%The question is to predict positive or negative sentiment expressed in the text.
-Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \cite{lei2018simple}.\footnote{For MLP, we apply an average pooling layer over word embeddings.
-For LSTM, we add a shared feature representation layer on top of word embeddings.}
-
-%multi-layer perceptron (MLP), LSTM, CNN on all tasks
-%We use this task to verify our theoretical results on model capacity and task covariance in real world.
-%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
-%There are 14 diseases (tasks) for every image that we would like to predict.
-%We use densenet121 as the shared module \cite{huang2017densely}.
-%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
-%This dataset is curated where the labels
-%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
-%For the text classification experiment, we encode each word using the GLoVe word embeddings.%
-%\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}
-%We evaluate three model choices.
-%\textit{Predicting transfer effect via STL results.}
-%We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
-%A common challenge in the study of MTL is that the results can be hard to understand.
-%It is difficult to predict when MTL performs well without running extensive trials.
-%Our insight is that we can use STL results to help understand MTL results.
-%Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
-%We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ precision and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
-%We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
-%The results show that STL results are indicative of MTL results.
-
-\paragraph{Sample size ratio.}
-First, we we show that our observation in Figure \ref{fig_size} also occurs in the text classification tasks.
-In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
-On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
-%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
-We fix task two's sample size at $1000$ and increase task one's sample size from $100$ to $3000$.
-
-These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
-Concretely, here is one implementation of this idea.
-%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
-%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
-%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
-\begin{itemize}
-	\item We divide the training data into $S$ batches.
-	We divide the training procedure into $S$ stages. During every stage, we progressively add one more data batch.
-	\item During every stage, we train for $T$ epochs using only the $S$ batches.
-If the validation accuracy drops compared to the previous round's result or reach a desired threshold $\tau$, we terminate.
-%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
-\end{itemize}
-If we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate once reaching the optimal sample ratio.
-%See Algorithm \ref{alg_inc_train} for a complete description for two tasks.
-The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
-For example, if the procedure terminates at 30\% of all batches, then SGD only passes over 30\% of its data, whereas standard round-robin training passes over 100\% of task one's data.
-
-%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
-%\squishlist
-%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
-%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
-%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
-%TREC is less similar to MR because the task is about question types.
-%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
-We evaluate the progressive training procedure on the six text classification datasets.
-First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
-We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
-We include all of task two's data and progressively add task one's data using the procedure described above.
-Since the prediction accuracy has been controlled the same, we compare the computational cost.
-We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
-%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
-%\textbf{Improving transfer learning training efficiency.}
-%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
-%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
-Second, we conduct multi-task training on all six datasets jointly.
-We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
-We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
-We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
-%As a further validation, excluding TREC, we observe similar comparative results.
-%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
-%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
-%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
-
-%	\begin{subfigure}[b]{0.33\textwidth}
-%		\centering
-%		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
-%		\caption{Task similarity}
-%		\label{fig_ab_sim}
-%	\end{subfigure}%
-%	\caption{Validating the three results of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
-%	(b) As source/target sample ratio increases, we observe a transition from positive to negative transfer.
-%	(c)
-%	Note: (S) denotes the source task and (T) denotes the target task.}
-
-%\begin{minipage}[t]{.58\textwidth}
-%	\vspace{-0.1in}
-%	\centering
-%  \begin{tabular}{c c c c c}
-%	\toprule
-%		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
-%		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
-%		& Precision &  Recall & Precision &  Recall \\
-%		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
-%		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
-%		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
-		% 0.3 & 1.000 & 0.004 &     - &     - \\
-%	\bottomrule
-%	\end{tabular}
-%	\vspace{0.1in}
-%	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
-%	\label{tab:mtl_better_than_stl}
-%\end{minipage}%
-%\quad
-
-\paragraph{Covariate shift.}
-Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
-This highlights the need for correcting covariate shifts when the sample size ratio rises.
-To this end, we study a covariance alignment procedure proposed in \cite{WZR20}, designed to correct covariate shifts.
-The idea is to add an alignment module between the input and the shared module $B$.
-This module is then trained together with $B$ and the output layers. We refer to \cite{WZR20} for more details about the procedure and the implementation.
-%We validate our insight on this procedure in the experiments.
-%We implement the covariance alignment procedure following \cite{WZR20}.
-
-We conduct multi-task training on all $15$ task pairs from the six datasets.
-In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
-To get a robust comparison, we average the improvements over the 15 task pairs.
-The result shows that as the sample size ratio increases, performing covariance alignment provides more significant gains over HPS.
-We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
-
-%\begin{figure}[!t]
-%	\centering
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
-%		\caption{Averaged over all 16 task pairs}
-%		\label{fig_ab_cov}
-%	\end{subfigure}\hfill
-%	\begin{subfigure}[b]{0.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.5\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{An example task pair}
-%		\label{fig_cov_a}
-%	\end{subfigure}
-%	\caption{ (TREC and CR)}
-%\end{figure}
-
-%\textbf{Further results of the covariance alignment procedure.}
-%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
-%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
-%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
-%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
-%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
-%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
-%We leave this question for future work.
-%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,
-
-%\begin{figure}[!h]
-%	\centering
-%	\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
-%		\caption{Task pair TREC and CR}
-%		\label{fig_cov_a}
-%	\end{subfigure}\hfill
-%		\begin{subfigure}[b]{0.48\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
-%		\caption{Task pair MR and SST}
-%			\label{fig_cov_b}
-%	\end{subfigure}
-%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
-%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
-%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
-%	\label{fig_covariate_app}
-%\end{figure}
-
-\begin{figure}%[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3a.pdf}
-		\caption{HPS vs. STL}
-		\label{fig_ab_data}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\vspace{0pt}
-		\includegraphics[width=0.8\textwidth]{figures/fig3b.pdf}
-		\caption{HPS vs. covariance alignment}
-		\label{fig_ab_cov}
-	\end{subfigure}
-	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \cite{WZR20}:
-	In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
-	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
-	\label{fig_text}
-%	\begin{minipage}[t]{0.4\textwidth}
-%		\centering
-%		\vspace{0pt}
-%		\begin{tabular}{c c c}
-%		\toprule
-		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
-		% Sentiment\\ analysis\end{center}\end{minipage}} \\
-%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
-		% \cmidrule(lr){2-3}
-%		& all tasks & w/o TREC \\
-%		\midrule
-%		{\bf MLP}  & 31\% & 29\% \\
-%		{\bf LSTM} & 35\% & 34\% \\
-%		{\bf CNN}  & 30\% & 28\% \\
-%		\bottomrule
-%		\end{tabular}
-%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
-%		\label{tab:taskonomy}
-%	\end{minipage}
-\end{figure}
-
-%\begin{algorithm}[!t]
-%	\caption{A progressive training schedule given two tasks}
-%	\label{alg_inc_train}
-%	\begin{algorithmic}[1]
-%		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
-%		\Param A shared module $B$, output layers $A_1, A_2$ as in the hard parameter sharing architecture.
-%		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
-%		\Output The trained modules $B, A_2$ optimized for task $2$.
-%		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
-%		\For{$i = 1,\dots, S$}
-%			\For{$j = 1,\dots, T$}
-%				\State Update $B, A_1, A_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$.
-%			\EndFor
-%			\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
-%			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
-%				\State \textbf{break}
-%			\EndIf
-%		\EndFor
-%	\end{algorithmic}
-%\end{algorithm}
-
-\iffalse
-\section{Conclusions and Discussions}\label{sec_conclude}
-
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on text classification tasks.
-We describe several open questions for future work.
-%First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
-%Second, it would be interesting to extend our result to classification problems such as logistic regression.
-First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
-%but its singular values will follow a different distribution since the matrix is not symmetric.
- %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
-An interesting question is to study logistic regression in a multiple-sample setting.
-\fi
-
- \section*{Acknowledgements}
-Thanks to Edgar Dobriban, Vaggos Chatziafratis, Mayee Chen, and Ruoxuan Xiong for helpful discussions at various stages of this work.
-Hongyang R.
-Zhang and Weijie J.
-Su's contributions were in part supported by the Wharton Dean's Fund for Postdoctoral Research.
-We gratefully acknowledge the support of DARPA under Nos.
-FA86501827865 (SDH) and FA86501827882 (ASED); NIH under No.
-U54EB020405 (Mobilize), NSF under Nos.
-CCF1763315 (Beyond Sparsity), CCF1563078 (Volume to Velocity), and 1937301 (RTML); ONR under No.
-N000141712266 (Unifying Weak Supervision); the Moore Foundation, NXP, Xilinx, LETI-CEA, Intel, IBM, Microsoft, NEC, Toshiba, TSMC, ARM, Hitachi, BASF, Accenture, Ericsson, Qualcomm, Analog Devices, the Okawa Foundation, American Family Insurance, Google Cloud, Swiss Re, the HAI-AWS Cloud Credits for Research program, and members of the Stanford DAWN project: Teradata, Facebook, Google, Ant Financial, NEC, VMWare, and Infosys.
-The U.S.
-Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views, policies, or endorsements, either expressed or implied, of DARPA, NIH, ONR, or the U.S.
-Government.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Supplementary Material, if any, should   %%
-%% be provided in {supplement} environment  %%
-%% with title and short description.        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{supplement}
-\textbf{Supplement to ``Hard Parameter Sharing in High-dimensional Linear Regression"}.
-In \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.
-%and give the technical proofs of the main theorems, Theorems \ref{thm_regularbm}, \ref{thm_twgram}, \ref{thm_twgraph} and  \ref{thm_twgraph_sparse}.
-\end{supplement}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                  The Bibliography                       %%
-%%                                                         %%
-%%  imsart-???.bst  will be used to                        %%
-%%  create a .BBL file for submission.                     %%
-%%                                                         %%
-%%  Note that the displayed Bibliography will not          %%
-%%  necessarily be rendered by Latex exactly as specified  %%
-%%  in the online Instructions for Authors.                %%
-%%                                                         %%
-%%  MR numbers will be added by VTeX.                      %%
-%%                                                         %%
-%%  Use \cite{...} to cite references in text.             %%
-%%                                                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% if your bibliography is in bibtex format, uncomment commands:
-\bibliographystyle{imsart-number}
-%\bibliographystyle{imsart-nameyear}
-
-%\bibliographystyle{abbrv}
-%\bibliographystyle{plain}
-\bibliography{rf,ref_mtl}
- % Style BST file (imsart-number.bst or imsart-nameyear.bst)
-%\bibliography{bibliography}       % Bibliography file (usually '*.bib')
-
-%% or include bibliography directly:
-%\begin{thebibliography}{4}
-%%%
-%\bibitem{r1}
-%\textsc{Billingsley, P.} (1999). \textit{Convergence of
-%Probability Measures}, 2nd ed.
-%Wiley, New York.
-%
-%\bibitem{r2}
-%\textsc{Bourbaki, N.}  (1966). \textit{General Topology}  \textbf{1}.
-%Addison--Wesley, Reading, MA.
-%
-%\bibitem{r3}
-%\textsc{Ethier, S. N.} and \textsc{Kurtz, T. G.} (1985).
-%\textit{Markov Processes: Characterization and Convergence}.
-%Wiley, New York.
-%
-%\bibitem{r4}
-%\textsc{Prokhorov, Yu.} (1956).
-%Convergence of random processes and limit theorems in probability
-%theory. \textit{Theory  Probab.  Appl.}
-%\textbf{1} 157--214.
-%\end{thebibliography}
-
-\end{document}

### 2022-02-13 prior_versions/abridged/setup.tex
update

--- 2020-10-20 arxiv_full_version/setup.tex
@@
 
-\medskip
-\noindent\textbf{Main results.}
+\textbf{Main results.}
 Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
@@
 Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-\begin{itemize}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
+%\begin{enumerate}
+
+\textit{Sample efficiency (Example \ref{ex_same_cov})}:
 	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \citet{ZSSGM18} has observed empirically.
@@
 
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
+\textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
 In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
@@
 
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
+\textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
 For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
@@
 See our discussion of proof techniques below for details.
-\end{itemize}
+%\end{enumerate}
 
@@
 
-\medskip
-\noindent\textbf{Proof techniques.}
+\textbf{Proof techniques.}
 There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
@@
 One limitation of uniform convergence based techniques is that the results often assume that all tasks have the same sample size, see e.g. \citet{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
+Besides, these techniques do not apply to the high-dimensional setting where the sample size is only a small constant times the dimension.
 
@@
 
-\medskip
-\noindent\textbf{Notations.}
+\textbf{Notations.}
 %Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.

### 2022-02-13 prior_versions/arxiv_full_version/experiments.tex
update

--- 2021-06-12 revision_journal/backup/Jan 01 2021/manuscript.tex
@@
-\documentclass[aos,preprint]{imsart}
-\usepackage{xr}
-	\externaldocument{./suppl}
-
-%% Packages
-\def\shownotes{0}
-%\usepackage{natbib}
-%\setcitestyle{authoryear,open={(},close={)}}
-%\renewcommand{\cite}{\citep}
-\usepackage[export]{adjustbox}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{fullpage}
-\usepackage{subfloat}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{macro_math}
-\usepackage{macro_fan}
-\usepackage{stmaryrd}
-\usepackage{multirow}
-\usepackage[us,12hr]{datetime}
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage{caption,subcaption}
-%\usepackage{breqn}
-
-\usepackage{dsfont}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Uncomment next line to change            %%
-%% the type of equation numbering           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\numberwithin{equation}{section}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Axiom, Claim, Corollary, Hypothezis, %%
-%% Lemma, Theorem, Proposition              %%
-%% use \theoremstyle{plain}                 %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\theoremstyle{plain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% For Assumption, Definition, Example,     %%
-%% Notation, Property, Remark, Fact         %%
-%% use \theoremstyle{remark}                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please put your definitions here:        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\endlocaldefs
-
-\begin{document}
-
-\begin{frontmatter}
-\title{Hard Parameter Sharing in High-dimensional Linear Regression}
-%\title{A sample article title with some additional note\thanksref{t1}}
-\runtitle{Hard Parameter Sharing in High-dimensional Linear Regression}
-%\thankstext{T1}{A sample additional note to the title.}
-
-\begin{aug}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%Only one address is permitted per author. %%
-%%Only division, organization and e-mail is %%
-%%included in the address.                  %%
-%%Additional information can be included in %%
-%%the Acknowledgments section if necessary. %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[A]{\fnms{Fan} \snm{Yang}\ead[label=e1]{fyang75@wharton.upenn.edu} \thanks{Fan Yang and Hongyang R. Zhang contributed equally.}}
-\author[B]{\fnms{Hongyang R.} \snm{Zhang}\ead[label=e2,mark]{hrzhang@northeastern.edu}\samethanks} 
-\author[C]{\fnms{Sen} \snm{Wu}\ead[label=e3,mark]{senwu@stanford.edu}} 
-\author[A]{\fnms{Weijie J.} \snm{Su}\ead[label=e4,mark]{suw@wharton.upenn.edu} }
-\and
-\author[C]{\fnms{Christopher} \snm{R\'e}\ead[label=e5,mark]{chrismre@cs.stanford.edu}} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Addresses                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\address[A]{Department of Statistics,
-University of Pennsylvania,
-\printead{e1,e4}}
-\address[B]{Khoury College of Computer Sciences, Northeastern University,
-\printead{e2}}
-\address[C]{Department of Computer Science, Stanford University,
-\printead{e3,e5}}
-
-\end{aug}
-
-\begin{abstract}
-	Hard parameter sharing for multi-task learning is widely used in empirical research despite the fact that its generalization properties have not been well established in many cases.
-This paper studies its generalization properties in a fundamental setting: How does hard parameter sharing work given multiple linear regression tasks?
-We develop new techniques and establish a number of new results in the high-dimensional setting, where the sample size and feature dimension increase at a fixed ratio.
-First, we show a sharp bias-variance decomposition of hard parameter sharing, given multiple tasks with the same features.
-Second, we characterize the asymptotic bias-variance limit for two tasks, even when they have arbitrarily different sample size ratios and covariate shifts.
-We also demonstrate that these limiting estimates for the empirical loss are incredibly accurate in moderate dimensions.
-Finally, we explain an intriguing phenomenon where increasing one task's sample size helps another task initially by reducing variance but hurts eventually due to increasing bias.
-This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
-\end{abstract}
-
-\begin{keyword}[class=MSC2020]
-\kwd[Primary ]{62J05}
-\kwd{60B20}
-\kwd[; secondary ]{62E20, 62H10}
-\end{keyword}
-
-\begin{keyword}
-\kwd{Hard parameter sharing, high-dimensional linear regression, random matrix theory, sample covariance matrices}
-\end{keyword}
-
-\end{frontmatter}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Please use \tableofcontents for articles %%
-%% with 50 pages and more                   %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\tableofcontents
-
-\section{Introduction}\label{sec_introduction}
-
-Hard parameter sharing (HPS) for multi-task learning is widely used in empirical research and goes back to the seminal work of \cite{C97}.
-Recent work has revived interests in this approach because it improves performance and reduces the cost of collecting labeled data \cite{R17}.
-It is generally applied by sharing the feature layers between all tasks while keeping an output layer for every task.
-Often, hard parameter sharing offers two critical advantages if successfully applied.
-First, it reduces model parameters since all tasks use the same feature space.
-Second, it reduces the amount of labeled data needed from each task by augmenting the entire training dataset.
-
-Hard parameter sharing works as an inductive transfer mechanism and a regularizer that reduces overfitting, both of which have great intuitive appeal \cite{R17}.
-For example, by restricting the shared space's size, HPS encourages information sharing among multiple tasks \cite{KD12}.
-Another source of inductive bias comes from the tasks and depends on datasets' properties such as sample sizes and task covariances \cite{WZR20}.
-However, how these dataset properties impact HPS has not been well established.
-%It becomes increasingly important to understand HPS' formal generalization properties.
-Part of the challenge may be that HPS' generalization performance depends intricately on the sample size ratios and covariate shifts between tasks, and is not amenable to standard concentration results.
-Previous results based on Rademacher complexity or VC dimensions have considered cases where all tasks' sample sizes are equal to logarithmic factors of the feature dimension \cite{B00,MPR16}, and when all tasks' sample sizes increase simultaneously \cite{AZ05,M06}.
-%For, the generalization error scales down as the sample sizes of all tasks increase, when applied to the multi-task setting \cite{B00,AZ05,M06,MPR16,WZR20}.
-
-\begin{figure*}[!t]
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.45\textwidth,valign=t]{figures/mtl_model_arch.pdf}
-		\caption{A hard parameter sharing architecture}
-		\label{fig_intro_arch}
-	\end{subfigure}\hfill
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.745\textwidth,valign=t]{figures/sample_ratio_c2_400.eps}
-		\caption{Varying sample size ratio}
-		\label{fig_intro_sample_size_b}
-	\end{subfigure}
-	\vspace{-0.1in}
-	\caption{
-	Left: an illustrative picture of HPS.
-	Right: an illustrative example of using HPS for two tasks $X_1, Y_1$ and $X_2, Y_2$ with sample size $n_1, n_2$, respectively.
-	Increasing $n_1/n_2$ decreases task two's prediction loss initially but increase afterward.
-This phenomenon occurs due to different bias-variance tradeoffs as $n_1/n_2$ increases.
-Our result provides an estimated loss (solid line) that accurately matches the empirical loss (dotted line).
-	See Section \ref{sec_simulation} for the precise setting.}
-	\label{fig_intro_sample_size}
-\end{figure*}
-
-This paper presents new techniques to study hard parameter sharing and establishes a number of new results.
-We consider regression analysis, which is arguably one of the most fundamental problems in statistics and machine learning.
-We are interested in the \textit{high-dimensional} setting, where each dataset's sample size and feature dimension grow linearly instead of logarithmically.
-This setting captures the fact that a single task's sample size is usually insufficient for accurate learning in many applications.
-For example, if a dataset's sample size is only a constant factor of dimension in linear regression, the variance is also constant (cf. Fact \ref{fact_tr}).
-The high-dimensional setting is challenging but is crucial for understanding how datasets' sample sizes impact generalization performance.
-
-\subsection{Setup and Main Results}
-
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
-Suppose we have $t$ datasets.
-For each dataset $i$ from $1$ to $t$, let $n_i$ denote its sample size.
-Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise.
-We study the standard hard parameter sharing architecture:
-a shared feature representation layer $B\in\real^{p\times r}$ for all datasets and a separate output layer $A_i \in \real^r$ for every dataset $i$.
-See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
-We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
-\begin{align}\label{eq_mtl}
-			f(A, B) = \sum_{i=1}^t \norm{X^{(i)} B A_i - Y^{(i)}}^2,
-\end{align}
-%\vspace{-0.05in}
-where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
-Given a solution from minimizing $f(A, B)$, denoted by $(\hat{A}, \hat{B})$  (which we will specify below), let $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$ denote the HPS estimator for task $i$.
-The critical questions are:
-(i) How well does the estimator work? In particular, how does the performance of the estimator scale with sample size?
-(ii) For datasets with different sample sizes and covariate shifts, how do they affect the estimator?
-
-\medskip
-\noindent\textbf{Main results.}
-Our first result (Theorem \ref{thm_many_tasks}) applies to multi-label prediction settings where all datasets have the same features (and sample size), and we want to make several predictions for every input (cf.
-examples in \cite{hsu2009multi}).
-We analyze the global minimizer of $f(A, B)$, and provide a sharp bias-variance decomposition of its (out-of-sample) prediction loss for any task.
-This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
-Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
-
-Our second result (Theorem \ref{thm_main_RMT}) applies to two tasks with arbitrarily different sample size ratios and covariate shifts.
-While we can no longer characterize $f(A, B)$'s global minimum because of non-convexity, we can still provide a sharp bias-variance tradeoff of any local minimizer's prediction loss for both tasks.
-Despite being a simple setting, we observe several non-trivial phenomena by varying sample size ratios and covariate shifts between the two tasks.
-See Figure \ref{fig_intro_sample_size_b} for an illustration of the former.
-Consequently, using our precise loss estimates, we observe several qualitative properties of HPS for varying dataset properties.
-\begin{itemize}
-	\item \textit{Sample efficiency (Example \ref{ex_same_cov})}:
-	One advantage of combining multiple datasets is that the requirement for labeled data reduces compared to single-task learning, a phenomenon that \cite{ZSSGM18} has observed empirically.
-	Our results further imply that HPS's sample efficiency depends on model-specific variances across tasks vs. the noise variance and is generally high when the latter is large.
-
-	\item \textit{Sample size ratio (Example \ref{ex_sample_ratio})}: Increasing one task's sample size does not always reduce another task's loss.
-In a simplified setting, we find that the task loss either decreases first before increasing afterward or decreases monotonically depending on how fast the bias grows.
-These two trends result from different bias-variance tradeoffs.
-This result is surprising because previous generalization bounds in multi-task learning typically scale down as all tasks' sample sizes increase, thus do not apply for different sample size ratios.
-
-	\item \textit{Covariate shift (Example \ref{ex_covshift})}: In addition to sample sizes, variance also scales with two datasets' covariate shifts.
-For a large sample size ratio, HPS's  variance is smallest when there is no covariate shift.
-Counterintuitively, for a small sample size ratio, having covariate shifts reduces variance through a complementary spectrum.
-We achieve this result through a novel characterization on the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts.
-See our discussion of proof techniques below for details.
-\end{itemize}
-
-%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-%\squishlist
-%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-%	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-%	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-%\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-%Our study also leads to several algorithmic consequences with practical interest.
-%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-
-%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-%Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
-Finally, we discuss the practical implications of our work.
-Our sample size ratio study implies a concrete progressive training procedure that gradually adds more data until performance drops.
-For example, in the setting of Figure \ref{fig_intro_sample_size_b}, this procedure will stop right at the minimum of the local basin.
-We conduct further studies of this procedure on six text classification datasets and observe that it reduces the computational cost by $65\%$ compared to a standard round-robin training procedure while keeping the average accuracy of all tasks simultaneously.
-
-\medskip
-\noindent\textbf{Proof techniques.}
-There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
-We carefully keep track of the concentration error between the global minimizer of $f(A, B)$ and its population version (cf. equation \eqref{eq_A_star}).
-The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
-We show that the inverse of the sum of two sample covariance matrices with arbitrary covariate shifts converges to a deterministic diagonal matrix asymptotically (cf.
-Theorem \ref{thm_main_RMT}).
-We use recently developed techniques from random matrix theory to show a sharp convergence rate.
-% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
-%\HZ{add several sentences on the technical insight}
-One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
-We believe our result has provided significant initial insights, and it is an interesting question to tighten our result.
-See Section \ref{sec_conclude} for more discussions of the technical challenge.
-
-%This part introduces a positive variance reduction effect from adding the source labels.
-%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
-%(i) the negative effect from model shift bias.
-%(ii) the positive effect from variance reduction;
-
-\subsection{Related Work}
-
-There is a large body of classical and recent works on multi-task learning.
-We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
-The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
-An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
-One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
-
-Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
-In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
-\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
-These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
-To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
-
-The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting} and distributed learning \cite{dobriban2018high}.
-For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
-One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\cite{WZR20} (and an earlier work by \cite{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
-
-\smallskip
-\noindent\textbf{Organizations.}
-The rest of this paper is organized as follows.
-In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
-In Section \ref{sec_diff}, we describe how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
-In Sections \ref{sec_simulation}, we validate our results in simulations.
-In Section \ref{sec_conclude}, we summarize our work and discuss future work.
-Section \ref{sec_text} describes our study on text classification tasks.
-Section \ref{app_proof_error_same_cov}, \ref{appendix RMT}, and \ref{app_iso_cov} present proofs of our results.
-
-\medskip
-\noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
-For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
-Let $\lambda_1(X), \lambda_2(X), \cdots, \lambda_{p\wedge n}(X)$ denote the singular values of $X$ in decreasing order.
-Let $X^+$ denote the Moore-Penrose psuedoinverse of $X$.
-We refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices.
-We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C \dot f(n)$ for large enough $n$.
-Moreover, we use the notation $g(n)\lesssim f(n)$ if $g(n) = \OO(f(n))$, and the notation $g(n)\sim f(n)$ if $g(n) \lesssim f(n))$ and $f(n) \lesssim g(n)$.
-In this paper, we will often write an identity matrix $\id_{n\times n}$ as $1$ without causing any confusions.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
-
-\section{Hard parameter sharing estimator}\label{sec_HPS}
-
-Consider the transfer learning setting with two data sets.
-We denote their sample sizes by $n_1$ and $n_2$.
-For $i=1,2,$ Let $X^{(i)} \in \real^{n_i \times p}$ denote dataset $i$'s feature covariates.
-We assume that the label vector $Y^{(i)} \in \real^{n_i}$ for $X^{(i)}$ follows a linear model plus random noise:
-$$Y^{(i)}= X^{(i)}\beta^{(i)} + \varepsilon^{(i)},\quad i=1,2.$$
-We study the standard hard parameter sharing architecture: a shared feature representation layer $B\in\real^{p}$ for all datasets and a separate output layer $A_i \in \real$ for every dataset $i$.
-Then we study the following minimization problem:
-\begin{align}\label{eq_tsl}
-			f(A, B) = \norm{X^{(1)} B A_1 - Y^{(1)}}^2 + \norm{X^{(2)} B A_2 - Y^{(2)}}^2,
-\end{align}
-where we abbreviate $A = [A_1, A_2]$. Let $(\hat{A}, \hat{B})$ be the minimizer of $f(A, B)$. We define the hard parameter sharing (HPS) estimator for task $i$ as 
-\be\label{def_HPS}\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i,\quad i=1,2.\ee
-In this paper, we make the following assumptions on feature covariates $X^{(i)}$ and the noise vectors $\varepsilon^{(i)}$.
-We remark that all these assumptions are natural in high-dimensional statistics.
-
-We assume that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)}$. More precisely, let 
-\be\label{XofZ}X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},\quad i=1,2, \ee
-where each $\Sigma^{(1)}$ and $\Sigma^{(2)}$ are $p\times p$ deterministic positive definite symmetric matrices, and $Z^{(1)}=(z^{(1)}_{ij})$ and $Z^{(2)}=(z^{(2)}_{ij})$ are $n_1\times p$ and $n_2\times p$ random matrices with real i.i.d.
-entries satisfying
-\begin{equation}\label{assm1}
-\mathbb{E} z^{(1)}_{ij}=\mathbb{E} z^{(2)}_{ij} =0, \ \quad \ \mathbb{E} \vert z^{(1)}_{ij} \vert^2=\mathbb{E} \vert z^{(2)}_{ij} \vert^2 =1, 
-\end{equation}
-Furthermore, we assume that the entries $z^{(1)}_{ij}$ and $z^{(2)}_{ij}$ have finite $\varphi$-th moment for some constant $\varphi>4$:
-\be \label{conditionA2}
-\mathbb{E} \vert z^{(1)}_{ij} \vert^\varphi  \le \tau^{-1},\quad \mathbb{E} \vert  z^{(2)}_{ij} \vert^\varphi   \le \tau^{-1}
-\ee
-for a small constant $\tau>0$. We assume that $\Sig^{(i)}$ has eigendecomposition
-\be\label{eigen}
-\Sig^{(i)}= O_i\Lambda_i O_i^\top, \quad  \Lambda_1=\text{diag}(\si_1^{(i)}, \ldots, \si^{(i)}_n),  \quad i=1,2,
-\ee
-where $O_i$ is the eigenmatrix and the eigenvalues satisfy that
-\begin{equation}\label{assm3}
- \tau \le  \si^{(i)}_p \le\cdots\le \si^{(i)}_2 \le \si^{(i)}_1 \le \tau^{-1} \quad i=1,2.
-\ee
-%for a small constant $\tau>0$.
-
-We assume that $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are two independent random noise vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moment up to any order: for any fixed $k\in \N$, there exists a constant $C_k>0$ such that
-\be\label{eq_highmoments}
-\E  | \ve^{(1)}_{i} |^k \le C_k,\quad \E  | \ve^{(2)}_{i} |^k \le C_k.
-\ee
-Finally, we assume that $\beta^{(1)}$ and $\beta^{(2)}$ are two arbitrary deterministic or random vectors that are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$. 
-%Moreover, we assume that 
-%\be\label{eq_SNR}
-%\tau\le \frac{\|\beta^{(1)}\|^2}{\|\beta^{(2)}\|^2} \le \tau^{-1},\quad  \frac{\|\beta^{(1)}\|^2}{\sigma^2} \ge \tau,
-%\ee
-%for a small constant $\tau >0$.
-The first condition means that the norms of the two model parameters $\beta^{(1)}$ and $\beta^{(2)}$ are comparable, while the second condition means that the singal-to-noise ratio cannot be too small.
-
-In this paper, we consider the high-dimensional setting, where the sample ratios satisfy that  %We assume that the aspect ratios $d_1:= p/n_1$ and $d_2:=p/n_2$ satisfy that 
-\be\label{assm2}
-1+\tau \le \rho_1:=\frac{n_1}{p} \le p^{\tau^{-1}}, \quad 1+\tau \le \rho_2:=\frac{n_2}{p} \le p^{\tau^{-1}}, \quad \tau \le \frac{\rho_1}{\rho_2}\le \tau^{-1},
-\ee
-for a small constant $\tau >0$.
-If $\rho_i>p^{\tau^{-1}}$, $i=1,2$, we are basically in the low-dimensional region, where the law of large numbers and central limit theorem already  give good enough results without using the theory developed in this paper.
-The lower bounds $\rho_1> 1+\tau$ and ${\rho_2 > 1+ \tau}$
-are to ensure that the sample covariance matrices $  (X^{(1)})^\top X^{(1)} $ and $  (X^{(2)})^\top X^{(2)} $ are non-singular with high probability, so that the ordinary least squares (OLS) estimator is well-defined for the linear regression problem on each task.
-
-We summarize our basic assumptions here for future reference.
-\begin{assumption}\label{assm_big1}
-Let $\tau$ be a small constant. 
-\begin{enumerate}
-\item  $X^{(1)}$ and $X^{(2)}$ take the form \eqref{XofZ}, where $Z^{(1)}$ and $Z^{(2)}$ are respectively $n_1\times p$ and $n_2\times p$ random matrices with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig^{(1)}$ and $\Sig^{(2)}$ are deterministic positive definite symmetric matrices satisfying \eqref{eigen} and \eqref{assm3}.
-%and (\ref{assm2}).
-We assume that $T$ is an $M\times M$ deterministic diagonal matrix satisfying (\ref{simple_assumption}) and (\ref{assm3}).
-
-\item $\varepsilon^{(1)} \in \real^{n}$ and $\varepsilon^{(2)} \in \real^{n}$ are random vectors independent from $X^{(1)}$ and $X^{(2)}$, and with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-
-\item $\beta^{(1)}$ and $\beta^{(2)} $ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)} $. %, and satisfy \eqref{eq_SNR}.
-
-\item $\rho_{1}$ and $\rho_{2}$ satisfy \eqref{assm2}.
-
-\end{enumerate}
-\end{assumption}
-
-For the optimization objective $f(A, B)$ in \eqref{eq_tsl}, using the local optimality condition $\frac{\partial f}{\partial B} = 0$, we can solve that  
-	\begin{align}
-		\hat{B} = A_2^{-1} \hat \Sigma(a)^{-1} \left[a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right], \label{eq_Bhat_2task} %\\
-		%&= (B^\star A ^{\top}) (A A^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{j=1}^t \varepsilon_i A_i^{\top}} (A  A^{\top})^{-1}.
-	\end{align}
-where we denote $a:=A_1/A_2$ and $\hat \Sigma(a):= a^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}$.
-Applying $\hat B$ to equation \eqref{eq_tsl}, we obtain an objective that only depends on $a $ as follows %\HZ{$A$ has been used to denote the output layers.
-Could you replace $A$ with another symbol (say $x$)?}
- \begin{align}
-		 g(a) \define & \left\| X^{(1)} \hat\Sigma(a)^{-1} (X^{(2)})^\top X^{(2)} (a\beta^{(2)}-\beta^{(1)}) \right. \nonumber\\
-			& \left. + \left(a^2 X^{(1)}\hat \Sigma(a)^{-1} (X^{(1)})^\top-\id_{n_1\times n_1}\right)\epsilon^{(1)}+ a X^{(1)}\hat \Sigma(a)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
-		   +& \left\| X^{(2)} \hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} (a\beta^{(1)}-a^2\beta^{(2)}) \right. \nonumber\\
-		  &\left.+ \left(X^{(2)}\hat\Sigma(a)^{-1} (X^{(2)})^\top-\id_{n_2\times n_2}\right)\epsilon^{(2)} + a X^{(2)}\hat \Sigma(a)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2. \label{eq_mtl_A12}
-	\end{align}
-Let $\hat a$ be the minimizer of $g(a)$.
-Throughout this paper, we regard $Y^{(1)}$ as the source data, and $Y^{(2)}$ as the target data.
-Then the HPS estimator \eqref{def_HPS} for the target task 2 is
-\be\label{HPS_est}
-\hat{\beta}_2^{\MTL} (\hat a) = \hat \Sigma(\hat a)^{-1}  \left[\hat a (X^{(1))})^{\top}Y^{(1)} +  (X^{(2)})^{\top}Y^{(2)}\right].
-\ee
-
-In this paper, we study the out-of-sample predication loss (test error) of $\hat{\beta}_2^{\MTL} (\hat a)$.
-Consider a test data point $(x,y)$ generated from the same model as task 2: $y= x^\top \beta^{(2)} + \ve$, where $x \in \R^p$ and $\ve\in \R$ are independent of $X^{(1)}$, $X^{(2)}$, $\varepsilon^{(1)}$ and $\varepsilon^{(2)}$, and only $x$ is observable.
-We want to use $x^\top \hat{\beta}_2^{\MTL} (\hat a) $ to predict $y$, and we measure the predication loss using the mean squared error
-$$\exarg{x}{\left\|y-x^\top \hat{\beta}_2^{\MTL} (\hat a) \right\|^2}= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 + \sigma^2.  $$ 
-Since $\sigma^2$ is a constant that does not depend on the model, we ignore it and define the predication loss as
-\be\label{HPS_loss}
-L(\hat{\beta}_2^{\MTL}(\hat a)):= \left\|(\Sigma^{(2)})^{1/2} \left(\hat{\beta}_2^{\MTL} (\hat a)  - \beta^{(2)}\right)\right\|^2 .
- \ee
-We will compare it to the out-of-sample predication loss $L(\hat{\beta}_2^{\STL})$ of the single-task OLS estimator 
-$$\hat \beta^{\STL}= [(X^{(2)})^\top X^{(2)}]^{-1}(X^{(2)})^\top Y^{(2)}$$ as a baseline.
-
-Plugging \eqref{HPS_est} into \eqref{HPS_loss}, we get
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(\hat a))  =  &\left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} (X^{(1)})^\top X^{(1)} (\hat a\beta^{(1)}-\hat a^2\beta^{(2)}) \right. \nonumber\\
-&\left. +(\Sigma^{(2)})^{1/2}\hat \Sigma(\hat a)^{-1} \left[ (X^{(2)})^\top \epsilon^{(2)} + \hat a  (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2.\label{Lbeta_HPS}
-\end{align}
-Note that if we replace $\hat a$ with a fixed number $a$ in \eqref{Lbeta_HPS}, then taking the expectation over $\ve^{(1)}$ and $\ve^{(2)}$, we can get a clean bias-variance decomposition of the predication loss:
-\be\label{partial-L} \exarg{\ve^{(1)},\ve^{(2)}}{L(\hat{\beta}_2^{\MTL}(a)) } = L_{\bias} (a) + L_{\var}(a),\ee
-where 
-\be\label{Lbias} L_{\bias} (a) := \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma(a)^{-1} (X^{(1)})^\top X^{(1)} \left(a\beta^{(1)}- a^2\beta^{(2)}\right) \right\|^2 \ee
-is called the bias term, which depends on the model bias between task 1 and task 2, and
-\be\label{Lvar}  L_{\var}(a):=\sigma^2  \bigtr{{\Sigma^{(2)}\hat \Sigma(a)^{-1}  }} \ee
-is called the variance term, which depends on the noise variance.
-Using concentration of the noise vectors $\ve^{(1)}$ and $\ve^{(2)}$, we can show that $L(\hat{\beta}_2^{\MTL}(a))$ is close to \eqref{partial-L} up to a small error as in the next lemma.
-In this paper, we say that an event $\Xi$ holds \emph{with high probability} (w.h.p.) if $\mathbb P(\Xi)\to 1$ as $p\to \infty$.
-%predication loss for the HPS and OLS estimators.
-
- \begin{lemma}\label{lem_HPS_loss}
- Under Assumption \ref{assm_big1}, for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in $a\in \R$: 
-\begin{align}
-L(\hat{\beta}_2^{\MTL}(a)) &=\left[ 1+ \OO(p^{-1/2+c})\right]\cdot \left[L_{\bias} (a) + L_{\var}(a)\right] \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right], \label{L_HPS_simple}
-\end{align}
-and 
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \sigma^2  \bigtr{\Sigma^{(2)} [(X^{(2)})^\top X^{(2)}]^{-1}  }  . \label{L_STL_simple}
-\end{align}
-%Moreover, there exists a constant $C_0>0$ such that with high probability,
-%\be\label{loss_large}
-%g(a) > g(0) \quad \text{for all $a$ such that }|a|\ge C_0.
-%\ee
-%with high probability for any small constant $\e>0$. 
-\end{lemma}
-
-Since \eqref{L_HPS_simple} holds uniformly for all $a\in \R$, we can also apply it to $\hat{\beta}_2^{\MTL}(\hat a)$, where $\hat a$ is a random variable that may depend on $\ve^{(1)}$ and $\ve^{(2)}$.
-In practice, the parameter $ a$  is up to one's choice and may not be the global minimizer, so we have stated the result for an completely arbitrary $a$.
-(In fact, the optimization objective $g(a)$ is generally non-convex, so in some cases one can only find a local minimizer.) For a fixed $a\in \R$, the proof of \eqref{L_HPS_simple} is based on the sharp concentration bounds in Lemma \ref{largedeviation} of the supplement \cite{MTL_suppl}.
-To extend uniformly to all $a\in \R$, we will use a standard $\ve$-net argument, which leads to a small error $ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right) $.
-Note that this error is negligible unless $\beta^{(1)}$ and $ a\beta^{(2)}$ cancel each other almost exactly, and the noise variance $\sigma$ is very small.
-The proof of Lemma \ref{lem_HPS_loss} will be given in Appendix  \ref{app_firstpf} of the supplement \cite{MTL_suppl}.
-
-%In this section, we show that the prediction loss of hard parameter sharing admits a clean bias-variance decomposition, when all tasks have the same features.
-
-For the single-task predication loss \eqref{L_STL_simple}, we can calculate its asymptotic limit exactly using the following classical result in multivariate statistics.
-
-\begin{lemma}[Theorem 2.4 of \cite{isotropic} and Theorem 3.14 of \cite{DY}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	Under Assumption \ref{assm_big1}, we have that
-		\[ \bigtr{\Sigma^{(2)} \frac1{(X^{(2)})^\top X^{(2)} }  } = \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  } = \frac{p}{n_2 - p} \cdot \left[1+ \OO\left( \frac{p^{\e}}{\sqrt{np}} \right)\right] \]
-		with high probability for any small constant $\e>0$.
-\end{lemma}
- %The above result has a long history in random matrix theory.
-If the entries of $Z^{(2)}$ are i.i.d.
-Gaussian, then this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf.
-Lemma 3.11 of \cite{bai2009spectral}).
-Here we have presented the results from \cite{isotropic,DY}, which give an almost sharp convergence rate.
-With Lemma \ref{fact_tr}, we obtain that w.h.p.,
-\begin{align}
-L(\hat{\beta}_2^{\STL} ) &= \left[ 1+ \OO(p^{-1/2+c})\right] \cdot \frac{p \sigma^2 }{n_2-p}   . \label{L_STL_simple01}
-\end{align}
-
-On the other hand, much less is known about the predication loss of the HPS estimator.
-In particular, its exact dependence on the model parameters, including the model bias, noise variance, sample sizes, and population covariance matrices, is not well-understood so far.
-\FY{What is known so far about this topic?} In the rest of this paper, we give a rigorous analysis of the bias term \eqref{Lbias} and variance term \eqref{Lvar} in three different settings of increasing complexity: (i) same covariates $X^{(1)}=X^{(2)}$; (ii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$; (iii) independent $X^{(1)}$ and $X^{(2)}$ with different sample sizes and different population covariance matrices.
-In each case, we provide the exact asymptotic bias and variance limits, together with almost sharp convergence rates.
-In particular, we will use our results to analyze the effect of the following factors: \emph{bias-variance tradeoff}, \emph{sample sizes}, and \emph{covariate shift}.
-
-%However, to the best of our knowledge, the asymptotic limit of $L(\hat{\beta}_2^{\MTL}(a))$ has never been calculated exactly in any high-dimensional setting.
-
-\section{HPS estimator: Bias-variance tradeoff}\label{sec_same}
-
-%We begin by considering the case where all tasks have the same sample size and feature covariates, that is, $n_i = n$ and $X^{(i)} = X\in\real^{n\times p}$ for all $i = 1, \dots, t$.
-%We provide a sharp generalization error bound of hard parameter sharing estimators.
-
-In this section, we consider the setting where the two tasks have the same covariates  $X^{(1)}=X^{(2)}$.
-We define $A^\star \in \R^{2}$ as the normalized eigenvector corresponding to the larger eigenvalue of the $2\times 2$ matrix
-$ {B^\star}^\top \Sigma  B^\star,$ where $B^\star \define [{\beta}^{(1)},{\beta}^{(2)}] \in \real^{p\times 2}$ is the matrix formed by the linear model parameters of the two tasks.
-Without loss of generality, we assume that the two eigenvalues of ${B^\star}^\top \Sigma B^\star$ are not degenerate, so that $A^\star$ is well-defined.
-Otherwise, Theorem \ref{thm_two_tasks} will give a null result.
-
-\begin{theorem}\label{thm_two_tasks}
-Under Assumption \ref{assm_big1}, suppose that $X^{(1)}=X^{(2)}$ and $n_1=n_2$. Let $c>0$ be an arbitrary small constant. Then we have that with high probability, 
-\be\label{minimizer_beta1}
-\left\| u_{\hat a}u_{\hat a}^\top - A^\star {A^\star}^\top\right\|_F  \le  \left[\frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_1 - \lambda_{2} } \right]^{1/2},
-\ee
-where $u_{\hat a}$ is a unit vector defined as
-$ u_{\hat a}:= \frac1{\hat a^2 +1} \begin{pmatrix} {\hat a}\\ 1\end{pmatrix},$ and $\lambda_1 $ and $\lambda_{2}$ are respectively the larger and smaller eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-%for task 2,  % over the randomness of the input, 
-Moreover, the prediction loss of the HPS estimator satisfies that with high probability,
-	\begin{align}
-		& \bigabs{L(\hat{\beta}_2^{\MTL}(\hat a)) - \left\|(\Sigma^{(2)})^{1/2} \left(A^\star(2) (B^{\star}A^{\star})  - \beta^{(2)}\right)\right\|^2  - |A^\star(2)|^2  \frac{p\sigma^2}{n-p} } \nonumber\\
-		& \le  \left[  \frac{  n^{-1/2+2/\varphi+c} \|{B^{\star}}^{\top}\Sigma B^{\star}\|+n^{-1/2+c} \sigma^2} {\lambda_1  - \lambda_2 }\right]^{1/2}   \left(\norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2\right), \label{Li_multi0}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	 where $A^\star(2)$ denotes the second entry of $A^\star$.
-	 \end{theorem}
-
-Recall that $\varphi$ is a constant larger than 4, hence $n^{-1/2+2/\varphi+c}$ is a negligible  factor asymptotically as long as $c$ is smaller than $1/2-2/\varphi$.
-Moreover, the factor $(\lambda_1 - \lambda_{2})^{-1}$ is natural, because the two eigenspaces of ${B^{\star}}^{\top}\Sigma B^{\star}$ are not stable when $\lambda_1 $ and $\lambda_{2} $ are close to each other.
-The estimate \eqref{minimizer_beta1} shows that the minimizer $\hat a$ is approximately equal to $A^\star(1)/A^\star(2)$, while \eqref{Li_multi0} gives the exact asymptotic limit of $L(\hat{\beta}_2^{\MTL}(\hat a)) $, together with an explicit convergence rate that we believe to be sharp.
-
-It is not hard to extend the above result to the cases with more than two tasks.
-We make this extension for the following reasons.
-First, it provides a clearer geometric intuition than the two-task setting as we will discuss below.
-Second, the corresponding multi-task setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
-Finally, it provides useful insights into a more general theory of multi-task learning, which we will explore in greater details in future works.
-
-%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
-%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
-%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
-%\begin{align}
-%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
-%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
-%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
-%\end{align}
-%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
-%Compared to the prediction loss of single-task learning (cf.
-equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
-%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
-%We show the generalization error of hard parameter sharing estimators.
-%Before stating the result, we define the following notations.
-
-\vspace{5pt}
-\noindent\textbf{Multi-task setting.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$.
-The label vector of the $i$-th task follows a linear model
-$$Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)},\quad i=1,2,\cdots, t.$$
-We assume that $X=Z\Sigma^{1/2}$ is a random matrix satisfying the same assumption as $X^{(2)}$ in Assumption \ref{assm_big1}, that is, $Z$ is an $n\times p$ random matrix with i.i.d.
-entries satisfying (\ref{assm1}) and \eqref{conditionA2}, $\Sig$ is a deterministic positive definite symmetric matrix satisfying \eqref{eigen} and \eqref{assm3}, and $\rho:=n/p$ satisfies \eqref{assm2}.
-$\varepsilon^{(i)} \in \real^{n}$, $i=1,2,\cdots, t$, are independent random vectors with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments as in \eqref{eq_highmoments}.
-Finally, $X$, $\ve^{(i)}$ and $\beta^{(i)}$, $i=1,2,\cdots, t$, are all  independent from each other.
-
-%\begin{enumerate}
-%	\item $X = Z \Sigma^{1/2} \in \real^{n\times p}$ for a positive semidefinite matrix $\Sigma\in \R^{p\times p}$, and every entry of $Z \in \real^{n \times p}$ is drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-%	\item every entry of $\varepsilon^{(i)} \in \real^{n \times t}$ is drawn indepdently from a one dimensional distribution with zero mean, variance $\sigma^2$, and bounded moment up to any order.\footnote{There exists a fixed function $C: \mathbb{N} \rightarrow \real^+$ such that for any $k \in \N$, the $k$-th moment is bounded by $C(k)$.}
-%\end{enumerate}
-
-	To define the HPS parameter for the above setting, we study the following minimization problem % \eqref{eq_tsl} becomes
-	\begin{align}
-		f(A, B) = \sum_{j=1}^t \bignorm{X B A_j - Y^{(j)}}^2, \label{eq_mtl_same_cov}
-	\end{align}
-	where $B \in \real^{p \times r}$ is a rank-$r$ shared feature representation layer, and $A := [A_1, A_2, \dots, A_t] \in \real^{r \times t}$ with $A_i \in \R^r$ being a separate output layer for task $i$.
-%Recall that $r$ is the width of $B$.
-We will focus on cases with $r < t$, because otherwise the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-
-	%If $r\ge t$, then it is trivial to observe that we can always choose the parameters $A$ and $B$ such that $BA_i$ can fit any parameter $\beta^{(i)}\in \R^p$, which leads to a vanishing predication loss.
-Hence we only consider the case with $r<t$.
-\FY{Correct it if the reason is wrong.}
-
-	For the optimization objective  in \eqref{eq_mtl_same_cov}, using the local optimality condition over $B$, that is, $\frac{\partial f}{\partial B} = 0$, we obtain $\hat{B}$ as a function of $A$:
-	\begin{align}
-		\hat{B}(A) %&\define (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{j=1}^t Y^{(j)} A_j^{\top}} (A  A^{\top})^{+} \nonumber \\
-		&= (X^{\top} X)^{-1} X^{\top} Y A^{\top} (AA^{\top})^{+}, \label{eq_Bhat}
-	\end{align}
-	where $Y := [Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$ and $(AA^{\top})^{+}$ denotes the pseudoinverse of $AA^{\top}$.
-	%Here we have used that $X^{\top}X$ is invertible since $n > \rho \cdot p$ and $\rho > 1$ (cf. Fact \ref{fact_minv}).
-	%\FY{Is $\dag$ a standard notation? It is a bad notation at least for me because $\dag$ is more often used as Hermitian conjugate. Wiki page uses $(AA^{\top})^{+}$ for pseudo-inverse.}
-	Plugging $\hat{B}(A)$ into equation \eqref{eq_mtl_same_cov}, we obtain the following objective that only depends on $A$ (in matrix notation):
-	\begin{align}\label{eq_mtl_output_layer}
-		g(A) = \bignormFro{X (X^{\top}X)^{-1}X^{\top} Y A^{\top} (AA^{\top})^{+} A - Y}^2.
-	\end{align}
-%	Note that $A^{\top} (AA^{\top})^{+} A$ is a projection onto the subspace spanned by the rows of $A$. For simplicity, we write it into the form
-%	$$A^{\top} (AA^{\top})^{+} A= U_A U_A^\top,$$
-%	where $U_A \in \R^{t\times r}$ is a $t\times r$ partial orthonormal matrix (i.e. $U_A^\top U_A=\id_{r\times r}$). Hence we also denote the function $g(A)$ by $g(U_A)$. 	
-Let $\hat A$ be the global minimizer of $g(A)$.
-Then $(\hat A,\hat B(\hat A))$ is the global minimizer of $f(A,B)$.
-We define the HPS estimator for task $i$ as $\hat \beta_i^{\MTL} := \hat B(\hat A) \hat A_i,$
-%For an estimator $\hat{\beta}_i$ of task $i$, we are interested in 
-and its (out-of-sample) prediction loss as
-\be\label{ith_loss} L_i(\hat{\beta}_i^{\MTL}) = \bignorm{\Sigma^{1/2} \left(\hat{\beta_i}^{\MTL} - \beta^{(i)}\right)}^2. \ee
-
-Our main result of this section, Theorem \ref{thm_many_tasks}, shows that hard parameter sharing essentially approximates all tasks through a rank-$r$ subspace.
-To formalize this geometric intuition, as in the two-task case, we introduce the matrix $B^\star \define [{\beta}^{(1)},{\beta}^{(2)},\dots,{\beta}^{(t)}] \in \real^{p\times t}$ formed by the linear model parameters of all the $t$ tasks.
-Let $A^{\star} {A^{\star}}^{\top}$ denote the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ (which is the covariance of the task labels):
-\begin{align}\label{eq_A_star}
-	A^{\star} \define \argmin_{U\in\real^{t\times r} : U^{\top} U = \id_{r\times r}} \inner{U U^{\top}} {{B^{\star}}^{\top} \Sigma B^{\star}},
-\end{align}
-where $\langle \cdot ,\cdot \rangle $ denotes the Frobenius inner product between two matrices. 
- To ensure that $A^{\star}$ is unique, we assume that the $r$-th largest eigenvalue of ${B^\star}^\top \Sigma B^\star$ is strictly larger than the $(r+1)$-th largest eigenvalue.
-Otherwise, Theorem \ref{thm_many_tasks} will give a null result.
- %$\lambda_{r+1}({B^\star}^\top \Sigma B^\star)$ is strictly smaller than $\lambda_{r}({B^\star}^\top \Sigma B^\star)$.
-Let $a_i^{\star}:= A^{\star}{A^{\star}}^{\top} e_i \in\real^r$ denote the $i$-th column of $A^{\star}{A^{\star}}^{\top}$, where $e_i$ is the standard basis unit vector along $i$-th direction.
-Then we have the following result.
-
-% $B^{\star} A^{\star} {A^{\star}}^{\top}$.
-%Let $(\hat{A}, \hat{B})$ be the global minimizer of $f(A, B)$.
-%Recall that the HPS estimator is defined as $\hat{\beta}_i^{\MTL} = \hat{B} \hat{A}_i$.
-%Our result is stated as follows.
-
-\begin{theorem}\label{thm_many_tasks}
-%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant.
-Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d.
-entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}.
-Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
-	%Let $n = c \cdot p$.
-	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
-%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.gT
-	%that satisfy Assumption \ref{assm_secA2} in the appendix.
-	%Assume that $n > \rho \cdot p$ for a fixed constant $\rho > 1$.
-	%Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi-4}{2\varphi})$.
-%	Let $L(B^{\star}a_i^{\star}): = \norm{\Sigma^{1/2} (B^{\star} a_i^{\star}- \beta^{(i)})}^2$.
-%Suppose $X\in \R^{n\times p}$ is an $n\times p$ random matrix satisfying the same assumptions as $X^{(1)}$ and $X^{(2)}$ in Assumption \ref{assm_big1}, and $\rho:=n/p$ satisfies \eqref{assm2}. 
-Suppose the above multi-task setting holds. Let $c>0$ be an arbitrary small constant. Then for any task $i = 1,  \cdots, t$, we have that high probability, 
-\be\label{minimizer_beta}
-\left\|  \hat A^{\top} (\hat A\hat A^{\top})^{+} \hat A - A^\star {A^\star}^\top\right\|_F  \le \left[ \frac{ n^{-1/2+2/\varphi+c}  \|{B^{\star}}^{\top}\Sigma B^{\star}\|  + n^{-1/2+c} \sigma^2 }{\lambda_r - \lambda_{r+1} }\right]^{1/2} ,
-\ee
-where $\lambda_r $ and $\lambda_{r+1}$ are respectively the $r$-th and $(r+1)$-th largest eigenvalues of ${B^\star}^\top\Sigma B^\star$.
-Moreover, the prediction loss of the HPS estimator $\hat{\beta}_i^{\MTL}$ satisfies that
-	\begin{align}
-		& \bigabs{L_i(\hat{\beta}_i^{\MTL}) - L_i(B^{\star}a_i^{\star}) -\frac{p\sigma^2}{n-p}  \norm{a_i^{\star}}^2  } \nonumber\\
-		& \le  \left[ \frac{  n^{-1/2+ 2/\varphi +c}   \norm{{B^\star}^\top\Sigma B^\star} +n^{-1/2+c}  \sigma^2} {\lambda_r  - \lambda_{r+1} }\right]^{1/2}  \left(\norm{{B^\star}^\top\Sigma B^\star}+  \sigma^2\right).
-\label{Li_multi1}
-		%\le n^{-\frac{c_{\varphi}}2} \cdot \frac{\bigbrace{ \norm{\Sigma^{1/2} B^{\star}}^2+  \sigma^2} \cdot (\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t)} {\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)},
-	\end{align}
-	%where $\lambda_r({B^\star}^\top\Sigma B^\star)$ and $\lambda_{r+1}({B^\star}^\top\Sigma B^\star)$ are respectively be the $r$-th and $(r+1)$-th largest eigenvalue of ${B^\star}^\top\Sigma B^\star$.
-%	where $C_1: = \frac{\bignormFro{\Sigma^{1/2} B^{\star}}^2 + \sigma^2 t}{\lambda_r ({B^\star}^\top \Sigma B^\star)- \lambda_{r+1}({B^\star}^\top \Sigma B^\star)}$.
-%and $C_2 :=  C_1\cdot \norm{\Sigma^{1/2} B^{\star}}$.
-Finally, we have a better bound for the averaged prediction loss:  
-\begin{align}
-&\left|\frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) - \frac1t\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2 - \frac{p \sigma^2}{n-p}\cdot \frac{r}{t}  \right| \nonumber \\
- &\le n^{-1/2+2/\varphi+c}  \norm{{B^\star}^\top\Sigma B^\star}+ n^{-1/2+c}   \sigma^2 ,\label{Li_multi2}
-\end{align}
-with high probability.
-\end{theorem}
-
- The bound \eqref{minimizer_beta} verifies our intuition that hard parameter sharing approximates the matrix ${B^{\star}}^\top\Sigma B^{\star}$ through a best rank-$r$ subspace.
-The estimate \eqref{Li_multi1} shows that the prediction loss of $\hat{\beta}_i^{\MTL}$ decomposes into a bias term $L_i(B^{\star} a_i^{\star})$ that measures the prediction loss of $B^{\star} a_i^{\star}$, plus a variance term that scales with $\norm{a_i^{\star}}^2$.
-Since $\norm{a_i^{\star}}^2\le 1$, compared with the single-task predication loss \eqref{L_STL_simple01}, the variance term always decreases in the HPS for multi-task setting.
-On the other hand, the bias term always increases, because the bias in single-task linear regression is zero.
-Hence whether the HPS estimator is better than the OLS estimator depends on an intricate \emph{bias-variance tradeoff}.
-%{\cor One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.}
-We can observe a similar {bias-variance tradeoff} for the averaged predication loss in \eqref{Li_multi2} using the fact that $r<t$.
-Note that the estimate \eqref{Li_multi2} can be applied even when the best rank-$r$ subspace approximation of ${B^{\star}}^\top\Sigma B^{\star}$ is not unique.
-For all the estimates in Theorem \ref{thm_many_tasks}, we believe that their convergence rates are asymptotically tight when $n$ goes to infinity.
-
-The proof of Theorem \ref{thm_many_tasks} will be given in Appendix  \ref{app_proof_error_same_cov} of the supplement \cite{MTL_suppl}.
-Moreover, Theorem \ref{thm_many_tasks} implies Theorem \ref{thm_two_tasks} as a special case with $t=2$ and $r=1$.
-
-%The key step for proving Theorem \ref{thm_many_tasks} is a characterization of $f(A, B)$'s global minimizer.
-%\medskip
-%
-%\noindent\textbf{Comparison to single-task learning (STL).}
-%Theorem \ref{thm_many_tasks} provides a sharp generalization error bound that is asymptotically tight when $n$ goes to infinity.
-%%The limiting loss of hard parameter sharing consists of two parts, a bias term $L(B^{\star} a_i^{\star})$ that measures the error of $B^{\star} a_i^{\star}$, and a variance term that scales with noise variance $\sigma^2$.
-%%	Our result implies that the variance of hard parameter sharing is always smaller than single-task learning.
-%%	This is because	STL's variance is equal to $\frac{\sigma^2 \cdot p} {n - p}$ by Fact \ref{lem_minv}, and $\norm{a_i^{\star}}^2 \le 1$ since the spectral norm of $U_r$, which is a projection matrix, is at most one.
-%One direct implication of our result is that compared to STL, the variance always decreases, since STL's variance is equal to $\sigma^2 \tr[\Sigma (X^{\top} X)^{-1}]$.
-%On the other hand, the bias always increases.
-
-\iffalse
-\paragraph{How does hard parameter sharing scale with sample size $n$?}
-Obviously, the concentration error decreases with $n$.
-First, we consider the variance of $\hat{\beta}_i^{\MTL}$, which is $\sigma^2\norm{a_i^{\star}} \bigtr{\Sigma (X^{\top} X)^{-1}}$?
-It turns out that this quantity converges to a fixed limit in the high-dimensional setting, which is formally stated in the following assumption.
-
-\begin{assumption}\label{assume_rm}
-	Let $\tau > 0$ be a small enough constant.
-%	Let $X = Z \Sigma^{1/2} \in\real^{n\times p}$ be a random matrix where $Z \in \real^{n\times p}$ consists of i.i.d.
-entries with zero mean and unit variance and $\Sigma \in \real^{p\times p}$ is a positive semidefinite matrix.
-	In the high-dimensional setting,
-%		\item For every entry of $Z$, we assume that its $\varphi$-th moment exists, that is, there exist a fixed constant $C > 0$ such that
-%			\begin{align}\label{assmAhigh}
-%				\ex{\abs{Z_{i,j}}^{\varphi}} \le C, \text{ for any } 1\le i \le n \text{ and } 1\le j \le p.
-%			\end{align}
-  the sample size $n$ grows to infinity proportionally with the feature dimension $p$, i.e. $n / p \rightarrow \rho \in (\tau, 1/\tau)$ as $p$ goes to infinity.
-%	\end{enumerate}
-\end{assumption}
-Under the above assumption, we can use the following result to simplify the variance of $\hat{\beta}_i^{\MTL}$.
-
-\begin{fact}[cf. Theorem 2.4 in \cite{isotropic}]\label{fact_tr}
-	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
-	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
-	With high probability over the randomness of $X$, we have that
-		\[ \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{p}{n - p} \pm \OO(n^{-c_{\varphi}}). \]
-\end{fact}
-\noindent\textit{Remark.} The above result has a long history in random matrix theory.
-For a multivariate Gaussian random matrix, this result follows from the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}.
-For a non-Gaussian random matrix, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \cite{bai2009spectral}).
-Applying Fact \ref{fact_tr} to Theorem \ref{thm_many_tasks}, we obtain that hard parameter sharing's variance is
-		\[ \sigma^2 \norm{a^{\star}_i}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \sigma^2 \norm{a^{\star}_i}^2 \frac{p}{n- p} \pm \OO(p^{- {c_{\varphi}} }). \]
-		\fi
-
-%Finally, for the random noise component, we assume that all of its moments exist.
-%More precisely, there exists a fixed function $C(\cdot) : \mathbb{Z} \rightarrow \real^+$ such that for any $a = 1, 2, \dots, \infty$, we have that
-%\begin{align}\label{assmAhigh2}
-%	\ex{\abs{\varepsilon_{j}^{(i)}}^a} \le C(a), \text{ for any } 1\le i\le t \text{ and } 1\le j\le n_i.
-%\end{align}
-%Hence, for any value $\varphi > 4$, we get that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$, for all $i = 1, 2, \dots, t$.
-%Let $\e$ be a small enough fixed value and let $c_{\infty}$ be any fixed value within $(0, 1/2-\e)$.
-%We have that Fact \ref{lem_minv} holds for $\varepsilon^{(i)}$ where $c_{\varphi}$ becomes $c_{\infty}$ instead.
-
-%Next, we consider the bias of $\hat{\beta}_i^{\MTL}$, that is $L(B^{\star} a^{\star}_i)$.
-To illustrate the {bias-variance tradeoff quantitively, we consider a random-effect model, which has been studied for  single-task linear regression and ridge regression (see e.g.
-\cite{dobriban2020wonder,dobriban2018high}).
-
-\begin{example}[Random-effect model]\label{ex_same_cov}
-Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-More precisely, %we have
-$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-and $\wt \beta^{(i)}$ denotes the $i$-th 
-%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$. 
-%Thus, for any two different $\beta^{(i)}$ and $\beta^{(j)}$, their distance is roughly $2d^2$.
-%The labels are $Y_i = X_i\beta_i + \varepsilon_i$, where $\e_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
-%For our discussion below, we assume that $\kappa^2 \sim d^2 \sim \sigma^2$ and $n\sim p$. %and $d^2=\OO(\kappa^2)$.
-%The more precise conditions on the relations between $d^2$, $\sigma^2$ and $\kappa^2$ are given in  \eqref{choiceofpara}.
-%We assume that all the random variables have finite moments up to any order as in equation \eqref{assmAhigh2}.
-
-In the random-effect model described above, using the concentration of Gaussian random vectors (e.g. Lemma \ref{largedeviation} in the supplement  \cite{MTL_suppl}), 
-%Based on the definition of the random-effect model, 
-the $(i, j)$-th entry of ${B^{\star}}^{\top} \Sigma B^{\star}$ is equal to %(ignoring lower order terms)
-%\begin{align*}
-%	\beta_i^{\top} \beta_j \approx \norm{\beta_0}^2 + \frac{d^2}{2}\delta_{ij},\quad 1\le i,j \le t,
-%\end{align*}
-\begin{align}\label{betaSbeta}
-	\beta_i^{\top}\Sigma  \beta_j =\beta_0^\top \Sigma \beta_0 + \delta_{ij} \frac{d^2 }{p}\tr \Sigma + \OO\left(p^{-1/2+c}\|\beta_0\|^2+ p^{-1/2+c} d^2\right),
-\end{align}
- with high probability for any constant $c>0$. We omit the details to show the error bound using Lemma \ref{largedeviation}. 
-%Note that $\norm{\beta_0}^2$ is approximately $\kappa^2$.
-With \eqref{betaSbeta}, it is easy to calculate that with high probability, the eigenvalues of ${B^{\star}}^{\top} \Sigma B^{\star}$ are given by 
-$$\lambda_1=(1+\OO(p^{-1/2+c}))\left(t \beta_0^\top \Sigma \beta_0  + \frac{d^2}{ p}\tr \Sigma\right) ,$$
-and
-$$ \lambda_i=(1+\OO(p^{-1/2+c}))\frac{d^2}{ p}\tr \Sigma , \ \ i=2,\cdots, t.$$ %Therefore, by taking a rank-$1$ approximation of ${B^{\star}}^{\top} B^{\star}$, we get the average prediction loss of $B^{\star} a_i^{\star}$.
-Thus for the best rank-$r$ approximation $A^\star {A^\star}^\top$  of ${B^{\star}}^{\top}\Sigma  B^{\star}$, we have
-$$\bignorm{\Sigma^{1/2} B^{\star} (A^\star {A^\star}^{\top} - \id_{t\times t})}_F^2= [1+\OO(p^{-1/2+c})]\cdot(t-r)\frac{d^2}{ p}\tr \Sigma $$
-with high probability. 
-%To see this, recall that $r$ is one and $A^{\star} {A^{\star}}^{\top}$ is the best rank-$1$ approximation of ${B^{\star}}^{\top}\Sigma B^{\star} = {B^{\star}}^{\top} B^{\star}$.
-%Hence, the above expression is equal to the sum of ${B^{\star}}^{\top} {B^{\star}}$'s bottom $t-1$ singular values.
-%In the random-effect model described above, we further assume that $\Sigma$ is isotropic as an example.
-%We show that when the rank $r$ is one, the average prediction loss of hard parameter sharing is as follows
-Then using \eqref{Li_multi2}, we obtain that
-\[ \frac{1}{t}\sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL}) = \bigbrace{1 - \frac{r}{t}} \frac{d^2}{p}\tr \Sigma + \frac{r}{t} \cdot \frac{p\sigma^2 }{n - p} +\oo(\|\beta_0\|^2+d^2 + \sigma^2) ,\quad \text{w.h.p.
-}\]
-%We describe a proof sketch.
-%First, we show that the bias equation $L(B^{\star} a_i^{\star})$ simplifies to the following
-%\[ \frac{1}{t} \sum_{i=1}^t L(B^{\star} a_i^{\star}) = \frac{1}{t}\normFro{B^{\star} A^{\star} {A^{\star}}^{\top} - B^{\star}}^2 \approx \left(1 - \frac{1}{t}\right) {d^2}{}  . \]
-%Second, using Fact \ref{fact_tr}, one can see that the average variance is
-%\begin{align*}
-%	\frac{1}{t} \sum_{i=1}^t \sigma^2\norm{a_i^{\star}}^2 \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2}{t} \sum_{i=1}^t \norm{a_i^{\star}}^2 \frac{p}{n - p}
-%	= \frac{1}{t}\frac{\sigma^2 p}{n - p},
-%\end{align*}
-%because $A^{\star}$ has rank-$1$ and $\sum_{i=1}^t \norm{a_i^{\star}}^2 = 1$.
-%Combined together, we have derived the average prediction loss in the random-effect model.
-If the error is sufficiently small, then comparing the above equation with \eqref{L_STL_simple01}, we have the following observations. 
-%Recall that the average prediction loss of STL scales as $\sigma^2\cdot \bigtr{\Sigma (X^{\top} X)^{-1}} = \frac{\sigma^2 p}{n - p}$ by Fact \ref{fact_tr}.
-%Comparing HPS to STL, we have the following qualitative properties.
-%	Suppose $n$ is sufficiently large so that the error is negligible.
-%\begin{enumerate}
-\begin{enumerate}
-	\item {\bf Positive vs.
-negative transfer.} The averaged HPS prediction loss is smaller than the single-task OLS prediction loss if and only if $\frac{d^2}{p}\tr \Sigma  < \frac{p\sigma^2 }{n - p}$, that is, the ``task-specific variance'' is smaller than the ``noise variance'' up to some constant factor.
-
-	\item {\bf The optimal rank $r$.} If $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$, then the smallest averaged HPS  prediction loss is achieved when $r=1$.
-Hence increasing the width $r$ of the shared feature representation layer does not help.
-	%To see this, one can verify what when $r$ increases by one, bias reduces by $\frac{d^2}{t}$, but variance increases by $\frac{\sigma^2 p}{t(n-p)} > \frac{d^2}{t}$ (details omitted).
-
-	\item {\bf Sample efficiency.} Suppose $\frac{d^2}{p}\tr \Sigma  < \frac{\sigma^2 p}{n - p}$ and we choose the optimal rank $r=1$.
-Following \FY{add citation}, we define the data efficiency ratio of HPS as the proportion of labelled data needed to achieve comparable performance to single-task linear regression.
-More precisely, for some $x\in (0,1)$, if we only use $xn$ many data, then the averaged HPS predication loss is
-	\[ \frac{1}{t} \sum_{i=1}^t L_i(\hat{\beta}_i^{\MTL},x) = \bigbrace{1 - \frac{1}{t}} \frac{d^2}{p}\tr \Sigma  + \frac{1}{t} \cdot \frac{p\sigma^2 }{xn - p}+\oo(d^2 + \sigma^2) ,\quad \text{with high probability.
-}\]
-	Comparing it to the single-task OLS predication loss $t^{-1} \sum_{i=1}^t L_i(\hat{\beta}_i^{\STL})$, we find that HPS requires at most (recall that $\rho=n/p$)
-	$$x= \frac{1}{\rho} + \frac{1 - \rho^{-1}}{t - (t - 1)(\rho-1)\frac{d^2 }{\sigma^2 } \cdot \frac1p\tr\Sigma}$$ 
-	proportion of the samples to achieve the same performance. This is the data efficiency ratio for the above random-effect model.
-
-	%samples that is less than $n$ samples to get comparable loss to STL.
-	%This follows by using this sample size in the average prediction loss equation in Example \ref{ex_same_cov}.
-	\end{enumerate}
-
-\end{example}
-
-\FY{add applications, simulations, and algorithm consequences of the results in this section}
-
-\section{HPS estimator: Varying sample sizes} 	\label{sec_sizeratio}
-
- In this section, we consider the setting where $X^{(1)}$ and $X^{(2)}$ are independent and have the same population covariance matrices $\Sigma^{(1)}=\Sigma^{(2)}$.
-However, the two tasks can have different sample sizes $n_1\ne n_2$.
-In this case, we can obtain the exact asymptotic limits of the bias term \eqref{Lbias} and the variance term \eqref{Lvar}.
-We will use these results to illustrate the effect of the sample sizes on the predication loss of the $\MTL$ estimator.
-
-\begin{theorem}\label{cor_MTL_loss}
-Under Assumption \ref{assm_big1} holds, suppose that $\Sigma^{(1)}=\Sigma^{(2)}$ and the entries of $Z^{(1)}$ and $Z^{(2)}$ are i.i.d.
-Gaussian random variables.
-Then for any small constant $\e>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimates hold uniformly in all $a\in \R$:
-\be\label{Lvar_samplesize}
-L_{\var}(a)= \left[ \cal L_1(a)+ \OO\left(\frac{p^{c}}{n_1}\right)\right] \cdot   \sigma^2 ,
-\ee
-and 
-\begin{align}
-L_{\bias}(a)&= \left[ \cal L_2(a)+  \OO\left(p^{-1/2+c}\right)\right]   \|\beta^{(1)}-a\beta^{(2)}\|^2 \nonumber\\
-&+ \OO \left[ p^{-C}\left( \|\beta^{(1)} \|^2  +  \|\beta^{(2)} \|^2\right)   \right].\label{Lbias_samplesize}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-	%   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-	% \le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-	 \end{align}
-Here we define the functions  
-\begin{align*}
-&\cal L_1(a):= \frac{2p}{  {n_2} (1-\xi_2) + a^2 n_1 (1-\xi_1)+ \sqrt{[ {n_2} (1-\xi_2) +a^2 n_1 (1-\xi_1)]^2 + 4a^2{n_2}{n_1} (\xi_1+\xi_2 -\xi_1\xi_2)}}, \\
-&\cal L_2(a): = \frac1{a^2}\cdot \frac{1- 2\frac{\cal L_1(a)}{\xi_2[1 + \cal L_1(a)]} + \kappa(a)}{1- \xi_2 \kappa(a)},
-\end{align*}
-where we abbreviate $\xi_1:=p/n_1$, $\xi_2:=p/n_2$ and
-\begin{align*}
-\kappa(a):= \frac{\cal L_1(a)^2}{\xi_2^2[1+\cal L_1(a)]^2}  \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1}. 
-%f_2(a):= \frac{a^4 \cal L_1(a)^2}{\xi_1^2 } \left[1 - \frac{a^4 \cal L_1(a)^2 }{\xi_1[1+a^2\cal L_1(a) ]^2}\right]^{-1},\\
-%f_3(a):= \frac1{a^2}\frac{\xi_1}{\xi_2 +\cal L_1(a)} 
- \end{align*}
-%	In the setting of Example \ref{ex_sample_ratio}, assume that
-%	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
-%	(i) both tasks sample sizes are at least $3p$;
-%	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%%	\be\label{choiceofpara0}
-%%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-%	%\be\label{choiceofpara0}
-%%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
-%	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
-%	Let $\varepsilon = (1 + \sqrt{p/n_1})^ 4 - 1$, which decreases as $n_1$ increases.
-%	Let $\hat{A},\hat{B}$ be the global minimizer of $f(A, B)$.
-%	With high probability over the randomness of the input,
-%	the prediction loss of $\hat{\beta}_2^{\MTL} = \hat{B} \hat{A}_2$ for task two satisfies that
-%	\begin{align}
-%	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
-%	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
-%	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-%	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-%	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
-%	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
-	 \end{theorem}
-
-\iffalse
- We need to state a result for Gaussian matrix ...... Consider 
-$$f (\al,n_1,n_2)= \frac1p\tr\left[\frac{1}{ (X_1^\top X_1 + \al \cdot X_2^\top X_2)^2} (X_1^\top X_1)^2\right].$$
-In our case, we have $\al=1$, but we can handle more general $\al$. We introduce two parameters:
-$$a= \al \frac{n_2}{n_1} \left( \frac{p}{n_1} + \frac{p}{n_2}- \frac{p}{n_1 }\cdot \frac{p}{n_2}\right),\quad b= \al \frac{n_2}{n_1}\left( 1- \frac{p}{n_2}\right) + \left( 1- \frac{p}{n_1}\right). $$
-Then we define the following parameters:
-\begin{align*}
-x= \frac{-b+ \sqrt{b^2 + 4a}}{2a},\quad y= \left[ x^{-2} - \frac{p}{n_1}\left( 1+\frac{p}{n_1}x\right)^{-2}\right]^{-1},\quad \omega= \al\frac{n_2}{n_1} \left( 1 + \al \frac{p}{n_1}x\right)^{-1}.
-\end{align*}
-We have that
-$$f(\al,n_1,n_2)= \frac{1 - 2\omega x + \omega^2 y}{ 1 - \frac{p}{n_2} \cdot \omega^2 y } +\oo(1)\quad \text{w.h.p.} $$
-In the setting $\al=1$, both $\omega x$ and $\omega^2 y$ can be written in terms of only one parameter 
-%$$f(\al,n_1,n_2)= \frac{\left(u^2 -\frac{p}{n_1}\right) \left(1- 2\frac{n_2}{n_1}  u^{-1}\right) + \frac{n_2^2}{n_1^2} }{ u^2 -\frac{p}{n_1}\left(1 + \frac{n_2}{n_1}\right) } +\oo(1)\quad \text{w.h.p.} $$
-%where 
-$$u: = x^{-1}\left(1+\frac{p}{n_1}x\right)=   \frac{ b+\sqrt{b^2+4a}}{2} +\frac{p}{n_1}   .$$
-\fi
-The proof of Theorem \ref{cor_MTL_loss} will be given in Appendix \ref{app_iso_cov} in the supplement \cite{MTL_suppl}.
-For the variance estimate in \eqref{Lvar_samplesize}, it is not necessary to assume the Gaussian distributions of the entries of $Z^{(1)}$ and $Z^{(2)}$.
-In fact, \eqref{Lvar_samplesize} is a special case of Theorem \ref{thm_main_RMT} below for the more general case with possibly different $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-On the other hand, the Gaussian assumption is needed in our current proof of the bias limit \eqref{Lbias_samplesize}.
-In the setting of Theorem \ref{cor_MTL_loss}, we can write
-\begin{align*}
-L_{\bias} (a)&=\bv_a^\top (Z^{(1)})^\top Z^{(1)} \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}  \right]^{2}}(Z^{(1)})^\top Z^{(1)} \bv_a,
-\end{align*}
-where we denote $\bv(a):=(\Sigma^{(1)})^{1/2}\left(a\beta^{(1)}- a^2\beta^{(2)}\right)$. Using the rotational invariance of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$, we have that  
-\begin{align}\label{Lbias_idea}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \frac1p\bigtr{ [(Z^{(1)})^\top Z^{(1)}]^2 \frac1{ \left[a^2(Z^{(1)})^\top Z^{(1)}+ (Z^{(2)})^\top Z^{(2)}\right]^{2}}  },
-\end{align}
-up to a small error. Notice that we can write \eqref{Lbias_idea} into a simpler form
-\begin{align}\nonumber %\label{Lbias_idea2}
-L_{\bias} (a)&\approx \|\bv_a\|^2 \left. \frac{\dd }{\dd x}\right|_{x=0}\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.
-\end{align}
-It is well-known that the empirical eigenvalue distributions (ESD) of $(Z^{(1)})^\top Z^{(1)}$ and $(Z^{(2)})^\top Z^{(2)}$ satisfy the famous Marchenko-Pastur (MP) law asymptotically \cite{MP}.
-From the MP law of $(Z^{(1)})^\top Z^{(1)}$, we can also derive the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ for any fixed $a\in \R$ and $x>0$.
-Due to the Gaussian assumption, $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and $(Z^{(2)})^\top Z^{(2)}$ are asymptotically freely independent from each other.
-Hence the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)}$ is given by the free additive convolution (or free addition) of the asymptotic ESD of $a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2$ and the MP law of $(Z^{(2)})^\top Z^{(2)}$.
-In particular, a sharp convergence estimate has been proved in \cite{BES_free1,BES_free2} for the free addition of two probability measure.
-We use that result to obtain a convergence estimate on
-$$\frac1p\bigtr{  \frac1{ a^2(Z^{(1)})^\top Z^{(1)}+ x[(Z^{(1)})^\top Z^{(1)}]^2+(Z^{(2)})^\top Z^{(2)} }  }.$$
-Taking derivative with respect to $x$ at $x=0$ gives the exact asymptotic limit of $L_{\bias}(a)$.
-
-We believe that the above argument can be extended to the case without Gaussian assumption.
-For example, instead of using the results in \cite{BES_free1,BES_free2} on free addition, we can use the sharp local laws on polynomials of random matrices in \cite{EKN_poly}.
-However, to apply the result in \cite{EKN_poly}, we need to check some hard technical conditions for our setting.
-Hence we do not pursue this direction in this paper.
-%{\cob The idea of proof: proved using free probability; can also use polynomials of random matrices.}
-
-Now we use the following example to illustrate the effect of varying sample sizes on the predication loss of the HPS estimator.
-
- %{How does hard parameter sharing scale with sample sizes and covariate shift $M$?} One can see that the variance limit depends intricately on both tasks' samples sizes and covariate shift.
-Next, we illustrate how varying them impact the prediction loss.
-\begin{example}[Sample sizes]\label{ex_sample_ratio}
-	%We first consider the impact of varying sample sizes.
-	%Consider the random-effect model from Section \ref{sec_same}, with both tasks having an isotropic population covariance matrix.
-	We again consider the random effect model in Example \ref{ex_same_cov} with $t=2$.
-First, we show that if $\|\beta_0\|^2 \gg d^2$, then the global minimizer $\hat a$ of the function $g(a)$ in \eqref{eq_mtl_A12} is close to $1$.
-	The proof of Proposition \ref{lem_hat_v} will be given in Appendix \ref{app_iso_cov_prop}.
-	\begin{proposition}\label{lem_hat_v}
-%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
-Suppose Assumption \ref{assm_big1} and the setting in Example \ref{ex_same_cov} hold. Suppose that
-	\be\label{para_rel}
-	 \|\beta_0\|^2 \ge p^{c_0}d^2 +p^{-1/2+c_0}\sigma^2.
-	\ee
- for a constant $c_0>0$. Then we have that for any small constant $c>0$ and large constant $ C>0$,
-	%Let $c$ be a sufficiently small fixed constant.
-	%In the setting of Corollary \ref{cor_MTL_loss}, 
-%There exists a constant $C>0$ such that
-	\be\label{hatw_add1}
-	 \hat a =1+ \OO\left(\frac{d^2}{\|\beta_0\|^2} + p^{-1/4+c} \frac{d+\sigma}{\|\beta_0\|} + p^{-C}\right) \quad \text{w.h.p.}
-	\ee
-\end{proposition}
-%Suppose every $\beta^{(i)}$ consists of two random components, one that is shared among all tasks and one that is task-specific.
-%%Thus, each task contributes a certain amount to the shared component and injects a task-specific bias.
-%More precisely, %we have
-%$$\beta^{(i)}=\beta_0 +\wt \beta^{(i)},\quad i=1,2,\cdots, t,$$
-%where $\beta_0$ denotes the shared component, %whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1}\kappa^2$, 
-%and $\wt \beta^{(i)}$ denotes the $i$-th 
-%%Let $\beta^{(i)}$ be equal to $\beta_0$ plus a 
-%task-specific component whose entries are i.i.d. Gaussian random variables of mean zero and variance $p^{-1} d^2$.
-
-Combining Lemma \ref{lem_HPS_loss}, Theorem \ref{cor_MTL_loss} and Proposition \ref{lem_hat_v}, and using  that $\|\beta^{(1)}-\beta^{(2)}\|^2 = (1+\oo(1))d^2$ with high probability, the predication loss $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is approximately equal to
-$$\ell(n_1,n_2)= \sigma^2 \cal L_1(1) +   2d^2 \cal L_2(1)= \frac{p\sigma^2}{n_1+n_2-p} +  2d^2  \frac{n_1^2 (n_1+n_2-p)+p n_1n_2}{(n_1+n_2)^2(n_1+n_2-p)}, $$
-with high probability, where in the second step we obtain $\cal L_1(1)$ and $\cal L_2(1)$ through direct calculations. 
-Now we compare $\ell(n_1,n_2)$ with \eqref{L_STL_simple01}.
-First, we notice that the variance term is smaller than $L(\hat{\beta}_2^{\STL} )$, while the bias term is always positive.
-Moreover, calculating the derivative with respect to $n_1$, it is not hard to see that the variance term always decreases as $n_1$ increases, while the bias term always increases with $n_1$.
-
-For a fixed $n_2$, we study the intricate bias-variance tradeoff with respect to $n_1$ using the following function of $\rho:=\rho_1+\rho_2$,
-$$h(\rho):=\frac{p }{n_2-p}\cdot \frac{\sigma^2}{2d^2}- \frac{\ell(\rho_1p , \rho_2p)}{2d^2}  = \frac{\rho-\rho_2}{(\rho-1)(\rho_2-1)}\cdot \frac{\sigma^2}{2d^2}- \frac{(\rho-\rho_2)^2 (\rho-1)+(\rho-\rho_2)\rho_2}{\rho^2(\rho-1)}  .$$
-This function characterizes $L(\hat{\beta}_2^{\STL} )-L(\hat{\beta}_2^{\MTL}(\hat a)) $, which gives the quantitive information transfer from the source task to the target task.
-First, we have positive (resp.
-negative) transfer if and only if $h(\rho)>0$ (resp.
-$h(\rho)<0$).
-Moreover, the sign of $h(\rho)$ is determined by the sign of the second order polynomial %which is equivalent to the following inequality:
-\be\label{poly1} \left( \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 \right)\rho^2 + ( \rho_2+1)\rho - 2\rho_2 .\ee
-Then we observe the following dichotomy.
-\begin{enumerate}
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 >0$, then the polynomial \eqref{poly1} is positive for all $\rho\in (\rho_2+1,\infty)$, so that the transfer is always positive.
-
-\item If $\frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}-1 < 0$, then we have the following cases.
-
-\begin{itemize}
-\item If $(\rho_2+1)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} is negative for all $\rho$, so that the transfer is always negative.
-
-\item If $(1+\rho_2)^2 < 8\rho_2 \left( 1- \frac{1}{\rho_2-1}\cdot \frac{\sigma^2}{2d^2}  \right)$, the polynomial \eqref{poly1} has two positive roots, where one of them is always smaller than $\rho_2+1$.
-Hence if the larger root, say $\rho_c$, is smaller than $\rho_2+1$, then the transfer is always negative for $\rho\in (\rho_2+1,\infty)$; otherwise, there is a transition from positive transfer to negative transfer as $\rho$ crosses $\rho_c$.
-\end{itemize}
-\end{enumerate}
-Second, we calculate the derivative of $h(\rho)$, and find that its sign  is determined by the sign of the third order polynomial 
-\be\label{poly2}
- \frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} \rho^3 - 2(\rho-\rho_2)(\rho-1)(\rho-2)   - (\rho_2-1)\rho .\ee
-Then we observe the following dichotomy.
-\begin{enumerate}
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} > 2$, the polynomial \eqref{poly2} is always positive for all $\rho\in (\rho_2+1,\infty)$, so that the information transfer always increases as $n_1$ increases.
-
-\item If $\frac{1}{\rho_2}\cdot \frac{\sigma^2}{2d^2} < 2$, the polynomial \eqref{poly2} is positive initially around $\rho=\rho_2+1$, and then becomes negative when $\rho$ crosses its unique root, say $\rho_c$, in $(\rho_2+1,\infty)$.
-Hence the information transfer achieves the global minimum at $\rho=\rho_c$.
-\end{enumerate}
-
-%where $w_0:={\sigma^2}/{2d^2}$ is the ratio between the model bias and the noise variance. 
-%and $$ h_1(\rho_1,\rho_2):= \frac{\rho_1}{(\rho_1+\rho_2-1)(\rho_2-1)},\quad h_2(\rho_1,\rho_2):= \frac{\rho_1^2 (\rho_1+\rho_2-1)+\rho_1\rho_2}{(\rho_1+\rho_2)^2(\rho_1+\rho_2-1)}.$$
-\iffalse
-Then whether $L(\hat{\beta}_2^{\MTL}(\hat a)) $ is larger or smaller than
-
-Applying Theorem \ref{thm_main_RMT} to the above setting, we get that
-	\begin{align*}
-		\frac{1}{n_1 + n_2} \tr[\Sigma^{(2)} (a_1\Sigma^{(1)} + a_2\Sigma^{(2)})^{-1}]
-		= \frac{1}{n_1 + n_2} \bigtr{((a_1 + a_2)\id_p)^{-1}}
-		= \frac{p}{n_1 + n_2 - p},
-	\end{align*}
-	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
-	Similarly, we can calculate the bias limit.
-	Combined together, we obtain the following corollary of Theorem \ref{thm_main_RMT}.
-
-In the above inequality, the $d^2$ scaling term is the bias limit and the $\sigma^2$ scaling term is the variance limit.
-This result allows for a more concrete interpretation since the dependence on datasets' properties is explicit.
-The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
-by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
-The proof is similar to Corollary \ref{cor_MTL_loss}, so we omit the details.
-
-{\cor 
-For the variance term, using equation \eqref{lem_cov_shift_eq}, we obtain that
-\be\label{eq_var111}\tr[\hat\Sigma^{-1}] = \tr\left[ \left((X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)}\right)^{-1}\right]=\bigtr{\frac{(a_1 +a_2)^{-1}\id_{p\times p}}{n_{1}+n_2} }+\OO(p^{-c_\varphi})\ee
-with high probability. Solving equation \eqref{eq_a12extra} with $\lambda_i\equiv 1$, $1\le i\le p$, we get that  
-	\begin{align}
-		 a_1 = \frac{n_1(n_1 + n_2 - p)}{(n_1 + n_2)^2} ,\quad
-		& a_2 = \frac{n_2(n_1 + n_2 - p)}{(n_1 +n_2)^2} . \label{simplesovlea12}
-			\end{align}
-Applying the above to equation \eqref{eq_var111}, we obtain that with high probability
-\be\label{eq_var112}\tr[\hat\Sigma^{-1}]  = \frac{p}{n_1+n_2} \cdot \frac{n_1+n_2}{n_1+n_2-p}+\OO(p^{-c_\varphi})=  \frac{p}{n_1+n_2-p}+\OO(p^{-c_\varphi}).\ee
-For the bias term,
-}
-
-Next, we use the bias-variance limits to study how varying sample sizes impacts HPS.
-For example, imagine if we want to decide whether to collect more of task one's data or not, how does increasing $n_1$ affect the prediction loss?
-We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
-The variance limit in equation \eqref{cor_MTL_error} obvious decreases with $n_1$.
-It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
-By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
-\begin{enumerate}
-	\item When $\frac{d^2}{\sigma^2} < \frac{p}{4n_2 - 6p}$, the prediction loss decreases monotonically as $n_1$ increases.
-	Intuitively, this regime of $d^2$ always helps task two.
-	\item When $\frac{d^2}{\sigma^2} > \frac{p}{4n_2 - 6p}$, the prediction loss always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
-	To see this, near the point where $n_1$ is zero, one can verify (from the derivatives) that bias increases less while variance decreases more, and there is \textit{exactly} one critical point where the derivative is zero, which corresponds to the \textit{optimal sample size ratio}.
-\end{enumerate}
-\fi
-
-	\end{example}
-
-	\FY{add applications, simulations, and algorithm consequences of the results in this section}
-
-\section{HPS estimator: Covariate shift}\label{sec_diff}
-
-%The previous section assumes that all tasks have the same sample size and feature vectors.
-Finally, in this section, we consider the most general setting, where the feature covariates $X^{(1)}$ and $X^{(2)}$ of the two tasks have both different sample sizes and different population covariance matrices.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
-In particular, the fact that population covariance matrices differ across tasks is often called ``covariate shift'', which is characterized by the matrix $(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$.
-In this section, we describe the exact asymptotic variance limit in the high-dimensional setting, while the bias limit is much more complicated, and we can only give a rough estimate on it.
-
-\iffalse
-Unlike the previous section, we can no longer characterize the global minimum of $f(A, B)$.
-This is because $f(A, B)$ is in general non-convex.
-Instead, our result implies sharp bias-variance tradeoffs for any \emph{local minimizer} of $f(A, B)$.
-We focus on the two-task case to better understand the impact of having different sample sizes and different covariates.
-Let $n_1, n_2$ denote task one  and two's sample size, respectively.
-Suppose
-\begin{align*}
-	X^{(1)} = Z^{(1)}(\Sigma^{(1)})^{1/2} \in \real^{n_1 \times p} \text{ and }
-	X^{(2)} = Z^{(2)}(\Sigma^{(2)})^{1/2} \in \real^{n_2 \times p},
-\end{align*}
-where the entries of $Z^{(1)}$ and $ Z^{(2)}$ are drawn independently from a one dimensional distribution with zero mean, unit variance, and constant $\varphi$-th moment for a fixed $\varphi > 4$.
-$\Sigma^{(1)}\in \R^{p\times p}$ and $\Sigma^{(2)}\in \R^{p\times p}$ denote the population covariance matrices of task 1 and task 2, respectively.
-
-Without loss of generality, we consider task two's prediction loss and the same result applies to task one.
-We consider the case of $r = 1 < t = 2$, since when $r > 1$, the global minimum of $f(A, B)$ reduces to single-task learning (cf. Proposition 1 of \cite{WZR20}).
-When $r = 1$, $B$ is a vector and $A_1, A_2$ are both scalars.
-To motivate our study, we consider a special case where $A_1=A_2=1$.
-Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
-By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
-\begin{align}
-	\hat{\beta}_2^{\MTL} = {\hat{\Sigma}}^{-1} ({X^{(1)}}^{\top} Y^{(1)} + {X^{(2)}}^{\top} Y^{(2)}), \text{ where }
-	\hat{\Sigma} = {X^{(1)}}^{\top} X^{(1)} + {X^{(2)}}^{\top} X^{(2)}. \label{def hatsig}
-\end{align}
-The matrix $\hat{\Sigma}$ adds up both tasks' sample covariance matrices, and the expectation of $\hat{\Sigma}$ is equal to a mixture of their population covariance matrices, with mixing proportions determined by their sample sizes.
-
-To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
-\begin{align}
-	 \exarg{\cE}{L(\hat{\beta}_2^{\MTL}) \mid X^{(1)}, X^{(2)}}
-	=& \bignorm{{\Sigma^{(2)}}^{1/2} \hat{\Sigma}^{-1} {X^{(1)}}^{\top} X^{(1)} (\beta^{(1)} - \beta^{(2)})}^2 \label{eq_bias_2task} \\
-	& + \sigma^2 \bigtr{\Sigma^{(2)}\hat{\Sigma}^{-1}}. \label{eq_variance_2task}
-\end{align}
-Equations \eqref{eq_bias_2task} and \eqref{eq_variance_2task} correspond to the bias and variance of HPS for two tasks, respectively.
-\fi
-
-%Our key result characterizes the asymptotic limit of the inverse of the sum of two arbitrarily different sample covariance matrices.
-Compared to the results in Section \ref{sec_sizeratio}, the spectrum of $\hat{\Sigma}(a)^{-1}$ now not only depends on the sample sizes of both tasks, but also depends on the ``misalignment'' between $\Sigma^{(1)}$ and $\Sigma^{(2)}$.
-%However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
-To capture this misalignment quantitatively, we introduce the covariate shift matrix (rescaled by $a$) 
-$$ M(a) \define a(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}.$$ 
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
-Let $\lambda_1(a), \lambda_2(a), \dots, \lambda_p(a)$ denote the singular values of $M$ in descending order. By \eqref{assm3}, these singular values satisfy that
-\begin{equation}\label{assm32}
-|a| \tau \le  \lambda_p(a) \le \cdots \le \lambda_2(a)\le \lambda_1(a) \le |a|\tau^{-1}. %, \quad \max\left\{\pi_A^{(n)}([0,\tau]), \pi_B^{(n)}([0,\tau])\right\} \le 1 - \tau .
-\end{equation}
-%for some small constant $0<\tau<1$. 
-The main result of this section is the following theorem on the variance limit, which characterizes  the exact dependence of $L_{\var}(a)$ on the singular values of $M$.
-
-\begin{theorem}\label{thm_main_RMT}
-%	Let $c_{\varphi}$ be any fixed value within $(0, \frac{\varphi - 4}{2\varphi})$.
-%	Assume that: a) the sample sizes $n_1$ and $n_2$ both satisfy Assumption \ref{assume_rm};
-%	b) $M$'s singular values are all greater than $\tau$ and less than $1/\tau$;
-%	c) task one's sample size is greater than $\tau p$ and task two's sample size is greater than $(1 + \tau) p$.
-%	With high probability over the randomness of $X^{(1)}$ and $X^{(2)}$, we have the following limits:
-Under Assumption \ref{assm_big1}, for any small constant $c>0$, there exists a high probability event $\Xi$, on which the following estimate holds for the variance term $L_{\var}(a)$ in \eqref{Lvar}: 
-%equation \eqref{eq_variance_2task} $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}]$ (leaving out $\sigma^2$) satisfies the following estimate:
-			\begin{align}\label{lem_cov_shift_eq}
-				\bigabs{L_{\var}(a)- \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  }}
-				\le \frac{(n_1+n_2)^{2/\varphi + c}}{p^{1/2} (n_1+n_2)^{1/2}}\cdot\frac{p \sigma^2}{n_1+ n_2}  ,
-			\end{align}
-			 uniformly in all $a\in \R$. Here $(a_1,a_2)$ is the solution of the following self-consistent equations
-			\begin{align}
-				a_1 + a_2 = 1- \frac{p}{n_1 + n_2}, \quad
-				a_1 + \frac1{n_1 + n_2}  \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} = \frac{n_1}{n_1 + n_2}. \label{eq_a12extra}
-			\end{align}
-
-\end{theorem}
-
- With \eqref{assm32}, it is easy to see that 
-$$ \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1 M(a)^\top M(a) + a_2  }  } \sim \frac{p \sigma^2}{n_1+ n_2}.$$
-Hence the right-hand side of \eqref{lem_cov_shift_eq} is much smaller than this main term by a factor of $p^{-1/2} (n_1+n_2)^{-1/2+2/\varphi + c}$.
-Lemma \ref{fact_tr} can be also regarded as a special case of Theorem \ref{thm_main_RMT}.
-%also extends  to the inverse of the sum of two sample covariance matrices.
-To see this, when $M(a)=0$, we solve equation \eqref{eq_a12extra} to obtain that 
-$$a_1 = \frac{n_1}{n_1+n_2},\quad a_2 = \frac{n_2-p}{n_1+ n_2},$$ 
-and plug them into equation \eqref{lem_cov_shift_eq}.  The proof of Theorem \ref{thm_main_RMT} will be given in Appendix \ref{appendix RMT} in the supplement \cite{MTL_suppl}.
-%For general $A_1,A_2$ that are not equal to one, we can still apply our result by rescaling $X^{(1)}$ and $M$ with $A_1 / A_2$.
-%We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
-
-\begin{example}[Covariate shift]\label{ex_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
-To illustrate the effect of covariate shift, we consider a similar setting as in Example \ref{ex_sample_ratio}, such that \eqref{para_rel} holds.
-In Proposition \ref{lem_hat_v}, we have seen that the global minimizer $\hat a$ is close to 1 up to a small error.
-Hence we take $a=1$ in \eqref{lem_cov_shift_eq}, and study the asymptotic limit
-$$\ell_{\var}(M):= \frac{\sigma^2}{n_1+n_2}\bigtr{  \frac{1}{a_1(M) \cdot M^\top M + a_2(M)  }  }, $$
-where $ M=(\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and $a_1(M)$ and $a_2(M)$ are defined through \eqref{eq_a12extra}.
-We compare different choices of $M$ that are scaled to have the same determinant. More precisely, for a fixed $\mu>0$ we define
-\begin{align*}
-		\cS_{\mu}\define\bigset{M \left| \prod_{i=1}^p \lambda_i = \mu^p, \tau \le \lambda_p \le \lambda_1 \le \tau^{-1}\right.}.
-\end{align*}
-%belong to the following bounded set.
-%Let $\lambda_i$ be the $i$-th singular value of $M$.
-%let $\mu_{\min} < \mu < \mu_{\max}$ be fixed values that do not grow with $p$.
-%\vspace{-0.025in}
-%{\small}
-%	We assume that $\beta_1$ and $\beta_2$ are generated following the isotropic model with $d = 0$.
-%\begin{proposition}[Covariate shift]\label{prop_covariate}
-%	Assume that $\Psi(\beta_1, \beta_2) = 0$ and $\rho_1, \rho_2>1$.
-%	Let $g(M)$ denote the prediction loss of $\hat{\beta}_t^{\MTL}$ when $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} \in\cS_{\mu}$.
-%	We have that
-%	{\small\[ g(\mu\id) \le \bigbrace{1+ \bigo{{\rho_2}/{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]}
-%\end{proposition}
-%This proposition shows that when source/target sample ratio is large, then having no covariate shift is optimal.
-%The proof of Proposition \ref{prop_covariate} is left to Appendix \ref{app_proof_33}.
-%We now prove Proposition \ref{prop_covariate}, which shows that $\te(\hat{\beta}^{\MTL})$ is minimized approximately when $M$ is a scalar matrix where there is enough source data.
-Our first observation is that if $n_1 \gg n_2$, i.e. there is enough source data compared to the target data, then $\ell_{\var}(M)$ is minimized approximately when $M$ is a scalar matrix. 
-%\begin{proof}[Proof of Proposition \ref{prop_covariate}]
-%Let 
-%$$M_0:=\argmin_{M\in \cal S_{\mu}}g(M).$$ 
-%We now calculate $g(M_0)$.
-With the same arguments as in Lemma \ref{lem_hat_v}, we can show that \eqref{hatv_add1} holds.
-Moreover, if the parameters are chosen such that $p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2$ as in \eqref{choiceofpara}, we can simplify
-%\be \nonumber
-%\begin{split}
-%g(M_0)&=(1+\OO(p^{-\e}))\cdot \sigma^2  \bigtr{\Sigma_2(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  ,
-%\end{split}
-%\ee
-%with high probability for some constant $\e>0$.
-In fact, Lemma \ref{lem_hat_v} was proved assuming that $M=\id$, but its proof can be easily extended to the case with general $M\in \cal S_{\mu}$ by using that $ \mu_{\min}\le \lambda_p(M)\le \lambda_1(M)\le \mu_{\max}$.
-We omit the details here.
-%
-%Now using Lemma \ref{lem_cov_shift}, we obtain that with high probability,
-%\begin{align}\label{gvar_extra}
-%g(M_0)= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{a_1(M_0)\cdot M_0^\top M_0 + a_2(M_0)}\right) \cdot \left(1 +\OO(p^{-\e})\right).
-%\end{align}
-From equation \eqref{eq_a12extra}, we obtain the following estimates on $ a_1(M)$ and $a_2(M)$ for any $M\in \cal S_\mu$:
-\be\label{est_a12extra}
- a_1(M) = \frac{n_1+\OO(p)}{n_1+n_2},\quad a_2(M) =\frac{n_2+\OO(p)}{n_1+n_2}.
-\ee
-Inserting \eqref{est_a12extra} into $\ell_{\var}(M)$, we obtain that 
-%and using $ M_0^\top M_0\succeq \mu_{\min}^2$, we obtain that with high probability,
-%\begin{align}\label{approximateteM}
-%\left(1+\frac{\rho_2}{(\rho_1-1)\mu_{\min}^2}\right)^{-1}h(M_0) \cdot \left(1 - \OO(p^{-\e})\right) \le g(M_0) \le h(M_0) \cdot \left(1 +\OO(p^{-\e})\right),
-%\end{align}
-%where
-$$\ell_{\var}(M)= \left[ 1+\OO\left(\frac{n_2}{n_1}\right)\right] \cdot \frac{\sigma^2}{n_1} \tr\left( \frac{1}{M^\top M}\right) .$$
-%With these two bounds, we can easily conclude \eqref{approxteM}. 
-%
-%We have that the test error satisfies
-%\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
-%where $\lambda_p$ is the smallest singular value of $p$ and
-%$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
-%Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
-By AM-GM inequality, we observe that 
-$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i^2}$$
-is minimized when $\lambda_1 = \cdots\lambda_p=\mu$ under the restriction $\prod_{i=1}^p\lambda_i =\mu^p$. Hence in this case, $M=\mu \id_{p\times p}$ is approximately the optimal choice.
-
-%Hence we get that 
-%\be\label{AMGM} h(M_0) \le \frac{\sigma^2}{\mu^2 (\rho_1+\rho_2)a_1(M_0)}.\ee
-%
-%On the other hand, when $M=\mu \id$, applying Lemma \ref{lem_cov_shift} we obtain that with high probability,
-%\begin{align}\label{gvar_extra2}
-%\begin{split}
-%g(\mu \id)&= \frac{\sigma^2}{\rho_1+\rho_2}\cdot \frac1p\tr\left( \frac{1}{\mu^2 a_1 (\mu\id) + a_2(\mu\id)}\right) \cdot \left(1 +\OO(p^{-\e})\right)\\
-%&\le \frac{\sigma^2}{\mu^2(\rho_1+\rho_2)a_1 (\mu\id)}.
-%\end{split}
-%\end{align}
-%Combining \eqref{est_a12extra}, \eqref{approximateteM}, \eqref{AMGM} and \eqref{gvar_extra2}, we conclude the proof.
-%, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
-%\end{proof}
-
-\iffalse
-For large enough $p$,
-%in the left hand side of equation \eqref{lem_cov_shift_eq}:
-\begin{align*}
-	\bigtr{\Sigma^{(2)} \hat{\Sigma}^{-1}} &\rightarrow \frac{1}{n_1 + n_2} \bigtr{\Sigma^{(2)} (a_1 \Sigma^{(1)} + a_2 \Sigma^{(2)})^{-1}}
-	= \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top} M + a_2 \id)^{-1}}.
-\end{align*}
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
-\fi
-
-%Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}. 
-%Our first observation is that:
-However, we now use an example to show that the above observation fails when $n_1$ is comparable to $n_2$.
-We take $\mu =1$, and consider the subset of covariate shift matrices satisfying $M=M^{-1}$.
-In other words, half of the singular values of $M$ satisfy that $\lambda_1 \ge \lambda_2\ge \cdots \ge \lambda_{p/2} \ge 1$, while the other half eigenvalues are $\lambda_{p/2}^{-1}\ge \cdots \ge \lambda_2^{-1} \ge \lambda_1^{-1}$.
-When $\lambda_1/\lambda_{p/2} = 1$, we have $M=\id_{p\times p}$ and there is no covariate shift.
-%while as As $\lambda$ increases, the severity of covariate shift increases.
-We claim the following dichotomy.
-\begin{enumerate}
-	\item If $n_1 \ge n_2$, then the variance limit is smallest when there is no covariate shift.
-	\item If $n_1 < n_2$, then the variance limit is largest when there is no covariate shift.
-\end{enumerate}
-We explain why the above dichotomy happens. We can write that variance limit as
-$$\ell_{\var}(M)=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2}\left( \frac{1}{\lambda_i^{2} a_1 + a_2} + \frac1{\lambda_i^{-2} a_1 + a_2} \right) .$$
-When $M=\id_{p\times p}$, by the first equation of \eqref{eq_a12extra}, we have
-$$\ell_{\var}(\id_{p\times p})=\frac{\sigma^2}{ n_1+n_2 }\sum_{i=1}^{p/2} \frac{2}{1-\gamma} , $$
-where we abbreviate $\gamma:=p/(n_1+n_2)$. Then using $a_1+a_2=1-\gamma$, through a direct calculation we find that %we can calculate that
-\begin{align*}
-\ell_{\var}(M) - \ell_{\var}(\id_{p\times p})%&= \frac{\sigma^2 \gamma}{2(1-\gamma)} (\lambda^2-1)a_1\cdot \bigbrace{  \frac{1}{ -a_1(\lambda^2-1)+(1-\gamma)\lambda^2 } - \frac{1}{a_1(\lambda^2-1) + (1-\gamma)}} \\
-&= \frac{\sigma^2 }{ n_1+n_2-p} \sum_{i=1}^{p/2} \frac{(\lambda_i^2-1)^2 a_1(M) \left[ a_1(M) - a_2(M)\right] }{[a_1(M)+\lambda_i^2 a_2(M)][\lambda_i^2 a_1(M)+a_2(M)]} .
-\end{align*}
-%in this example is equal to
-%$\frac{p}{2(n_1 + n_2)} f(\lambda)$, where
-%\[ f(\lambda) = {(\lambda^{-2} a_1 + a_2)^{-1} + (\lambda^2 a_1 + a_2)^{-1}}. \]
-%Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
-%where $g(\lambda, a_1) \ge 0$.
-%and can be derived from algebraic calculations (details omitted).
-We claim that $a_1(M) > a_2 (M)$ if and only if $n_1 > n_2$, which then explains the dichonomy.
-In fact, if $a_1>a_2$, then the first equation in \eqref{eq_a12extra} gives that $a_1> (1-\gamma)/2$, and the second equation in  \eqref{eq_a12extra} gives that
-\begin{align*}
- \frac{n_1}{n_1 + n_2} &> a_1 + \frac{1}{n_1+n_2} \sum_{i=1}^{p/2}\left(\frac{\lambda_i^2}{\lambda_i^2+1}+\frac{\lambda_i^{-2}}{\lambda_i^{-2}+1}\right) = \frac{1-\gamma}{2}+\frac{\gamma}{2}=\frac{1}{2}.
-\end{align*}
-%\begin{align*}
-% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-%\end{align*}
-This implies $n_1>n_2$.
-The other direction follows from a similar argument.
-% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
-\end{example}
-
-\iffalse
-%FY: Below was the word explanation. I still think the above simple proof is clearer.
-In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
-Hence, when $n_1 \ge n_2$, we have that $a_1 \ge a_2$, hence $a_1 \ge \frac{1}{2}(1 - \frac{p}{n_1 + n_2 - p}) = \frac{n_1 + n_2}{2 (n_1 + n_2 - p)}$.
-The other case when $n_1 < n_2$ is similar.
-A formal proof follows easily from the self-consistent equations \eqref{lem_cov_shift_eq} and we omit the details.
-Thus, we conclude that if $n_1 \ge n_2$, then $f(\lambda) > f(1)$.
-If $n_1< n_2$, then $f(\lambda)< f(1)$.
-\fi
-
-For the bias limit, we have the following proposition.
-
-\begin{proposition}\label{prop_main_RMT}
-%The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
-Under Assumption \ref{assm_big1}, for any small constant $c>0$ and large constant $C>0$, there exists a high probability event $\Xi$, on which the following estimate  holds for the bais term $L_{\bias}(a)$ in \eqref{Lbias}:
-			\begin{align}
-				& \bigabs{ L_{\bias}(a) -   (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   }  \nonumber\\
-				& \le \left[\left( 1+\sqrt{\frac{p}{n_1}}\right)^4 - 1 + n_1^{-1/2+2/\varphi + c}\right] \frac{n_1^2 \lambda_1^2 \left\|(\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2}{  [(\sqrt{n_1}-\sqrt{p})^2 \lambda_p^2+ (\sqrt{n_2}-\sqrt{p})^2]^2}  \nonumber\\
-				& + p^{-C} \left[\| \beta^{(1)}\|^2 + \| \beta^{(2)}\|^2 \right], \label{lem_cov_derv_eq}
-			\end{align}
-%			\begin{align}\label{lem_cov_derv_eq}
-%				\bigabs{ L_{\bias}(a) - \left\|\frac{n_1}{n_1+n_2}  \frac{\left[a_3 M(a)^\top M(a) + (a_4 + 1) \right]^{1/2}}{ a_1 M(a)^\top M(a) + a_2 } M(a)^\top (\Sigma^{(1)})^{1/2} \left(\beta^{(1)}- a\beta^{(2)}\right)\right\|^2   } \le  \frac{p^{-c_{\varphi}}}{(n_1+n_2)^2},
-%			\end{align}
-				uniformly in all $a\in \R$. Here $\Pi(a)$ is a $p\times p$ matrix defined as
-				$$\Pi(a):=\frac{n_1^2}{(n_1+n_2)^2}  M(a)  \frac{a_3 M(a)^\top M(a) + (a_4 + 1) }{[a_1 M(a)^\top M(a) + a_2 ]^2} M(a)^\top  ,$$
-				$\lambda_1$ and $\lambda_p$ are respectively the largest and smallest singular values of $M(a)$, and $(a_{3},a_4)$ is the solution of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
-		\be  \label{eq_a34extra}
-		\begin{split}
-				& a_3 + a_4 = \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2}, \\
-				& a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}},
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
-			\end{split}
-			\ee  
-			where recall that $(a_1,a_2)$ is the solution of \eqref{eq_a12extra}.
-\end{proposition}
-
-Note that the first error term on the right-hand side of \eqref{lem_cov_derv_eq} is typically smaller than the main term $ (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})  $ by a factor of $\OO(\sqrt{p/n_1} + n_1^{-1/2+2/\varphi + c})$.
-Hence \eqref{lem_cov_derv_eq} only gives an exact asymptotic limit in the regime $n_1\gg p$.
-Moreover, by equations \eqref{eq_a12extra} and \eqref{eq_a34extra} we have
-$$a_1 =\frac{n_1}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right), \quad a_3 =\frac{n_3}{n_1+n_2} + \OO\left( \frac{p}{n_1+n_2}\right),$$ 
-and
-$$a_3 =\OO\left( \frac{p}{n_1+n_2}\right),\quad a_4 =\OO\left( \frac{p}{n_1+n_2}\right).$$
-Using these estimates, it is easy to check that  
-\begin{align}
-& (\beta^{(1)}- a\beta^{(2)} )^\top (\Sigma^{(1)})^{1/2} \Pi(a)(\Sigma^{(1)})^{1/2} (\beta^{(1)}- a\beta^{(2)})   \nonumber \\
-&=\left\| (\Sigma^{(2)})^{1/2}\frac{1}{a^2\Sigma^{(1)}+\Sigma^{(2)}} a \Sigma^{(1)} \left(\beta^{(1)}- a\beta^{(2)}\right) \right\|^2 + \OO\left( \frac{p\left\|\beta^{(1)}- a\beta^{(2)}\right\|^2}{n_1+n_2}  \right)  .
-\label{bias_LLN}
-\end{align}
-Hence \eqref{lem_cov_derv_eq} is consistent with the result obtained by replacing $ (X^{(1)})^\top X^{(1)}$ and $ (X^{(2)})^\top X^{(2)}$ with $n_1\Sigma^{(1)}$ and $n_2\Sigma^{(2)}$, respectively, in $L_{\bias} (a) $ by the law of large numbers in the regime $n_1\gg p$.
-However, simulations show that our estimate \eqref{lem_cov_derv_eq} is more precise than the first term on the right-hand side of \eqref{bias_LLN}.
-
-\begin{remark}
-%First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-%Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-%This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
-%\begin{remark}
-The main error in Proposition \ref{prop_main_RMT} comes from approximating $(Z^{(1)})^\top Z^{(1)}$ by $n_1\id_{n_1\times n_2}$ using Corollary \ref{fact_minv} in the supplement \cite{MTL_suppl}.
-In order to improve this estimate and obtain an exact asymptotic result, one needs to study the singular value distribution of the  random matrix $\cal X + a^2$ for any fixed $a\in \R$, where $\cal X:=[(X^{(1)})^{\top}X^{(1)}]^{-1}(X^{(2)})^{\top}X^{(2)}$.
-We remark that the eigenvalues of $\cal X$ have been studied in the name of Fisher matrices \cite{Fmatrix}.
-However, since $\cal X$ is not symmetric, its singular values are different from its eigenvalues.
-To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still an open problem in random matrix theory, and the study of the singular values of $\cal X + a^2$ will be even harder.
-We leave this problem to future study.
-
-We also remark for the general case with covariate shift, the method in Section \ref{sec_sizeratio} for dealing with the bias term also fails, because we cannot reduce the problem into the study of the addition of two random matrices that are asymptotically freely independent.
-%\end{remark}
-\end{remark}
-
-\FY{add applications, simulations, and algorithm consequences of the results in this section}
-
-\section{Experiments}
+\section{Numerical Results}\label{sec_exp}
 
@@
 	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
-	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomena by fixing task two's sample size and increasing task one's sample size.
+	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
 	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
@@
 	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
-	Having covariate shift increases task two's prediction loss when task two's sample size is smaller than task one.
-Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
+	Having covariate shifts increases task two's prediction loss when task two's sample size is smaller than task one.
+Otherwise, having covariate shifts (surprisingly) decreases task two's prediction loss.}
 	\label{fig_model_shift_phasetrans}

### 2022-02-13 prior_versions/revision_journal/conclusions.tex
update

--- 2021-06-12 revision_journal/conclusions.tex
@@
 
-This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
-We provided sharp bias-variance tradeoffs of HPS in high-dimensional linear regression.
-Using these results, we analyzed how varying sample sizes and covariate shifts impact HPS, and rigorously explained several empirical phenomena such as negative transfer and covariate shift related to these dataset properties.
-We validated our theory and conducted further studies on text classification tasks.
-We describe several open questions for future work.
+Distribution shift is a fundamental challenge in applying transfer learning.
+This work formulated a theoretical setup in which questions related to the transfer effect can be formally analyzed.
+The setup can reproduce several interesting phenomena in the context of transfer learning.
+Precise asympotics for the risk of a two-layer linear neural network are shown under various kinds of distribution shift.
+Such analysis has led to a number of theoretical insights and practical implications for applying transfer learning to text classification tasks.
+
+%We describe several open questions for future work.
 %First, it would be interesting to tighten our estimate in Corollary \ref{cor_MTL_loss}, which would extend the observation in Figure \ref{fig_size} to small $n_1$.
 %Second, it would be interesting to extend our result to classification problems such as logistic regression.
-First, our result in Corollary \ref{cor_MTL_loss} involves an error term that scales down with $n_1$.
-Tightening this error bound requires showing the limit of $\normFro{({Z^{(1)}}^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)})^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two isotropic sample covariance matrices.
-This requires studying the asymptotic singular values distribution of the non-symmetric matrix $({Z^{(1)}}^{\top} Z^{(1)})^{-1}{Z^{(2)}}^{\top} Z^{(2)}+\id$, which is still an open problem in random matrix theory.
+It is a very interesting question to derive the asymptotic limit under general covariate and model shift.
+%This requires showing the limit of $\normFro{\big(({Z^{(1)}})^{\top} Z^{(1)} + {Z^{(2)}}^{\top} Z^{(2)}\big)^{-1} {Z^{(1)}}^{\top} Z^{(1)}}^2$ for two sample covariance matrices.
+We remark that likely such a result will require studying the asymptotic distribution of the singular values of asymmetric matrices, which is technically challenging.
 %FY: $+\id$ is very important and makes the problem very hard; otherwise the problem can be solved with current RMT methods.
-The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
+%The eigenvalue distribution of this matrix, which has been obtained in \cite{Fmatrix}, might be helpful towards resolving this problem.
 %but its singular values will follow a different distribution since the matrix is not symmetric.
  %might require new techniques beyond the current ones in random matrix theory .%\HZ{to add}.
-Second, it would be interesting to extend our results to classification problems.
-Several recent work have made remarkable progress for logistic regression in the high-dimensional setting, e.g. \cite{sur2019modern}.
-An interesting question is to study logistic regression in a multiple-sample setting.
+Another interesting question is to study the impact of distribution shift in other settings such as logistic regression \cite{sur2019modern}.
 

### 2022-02-13 prior_versions/revision_journal/manuscript_bk.tex
update

--- 2021-06-12 revision_journal/backup/03:06:2021/manuscript.tex
@@
 
-\title{High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression}
+\title{High-dimensional Asymptotics of Information Transfer for Linear Regression under Covariate Shifts}
 
-\runtitle{High-dimensional Asymptotics of Transferring from Different Domains}
+\runtitle{High-dimensional Asymptotics of Information Transfer}
 %\thankstext{T1}{A sample additional note to the title.}
@@
 
-\section{Main Results and Proof Techniques}\label{sec_HPS}
+\section{High-dimensional asymtotics of information transfer}\label{sec_HPS}
 In this section, we define our model for the setting of transfer learning, and introduce several transfer learning estimators that will be considered in this paper.
@@
 
-\subsection{The case of isotropic covariances} \label{sec_sizeratio}
+\subsection{A tight result for isotropic covariances} \label{sec_sizeratio}
 
@@
 
-\textbf{Variance asymptotic limit.}
+\paragraph{Variance asymptotic limit.}
 In Theorem \ref{main_cor}, we will show that for $z$ in a small neighborhood around $0$, when $p$ goes to infinity, $G(z)$ converges to the following limit
@@
 
-\textbf{Bias asymptotic limit.}
+\paragraph{Bias asymptotic limit.}
 For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
@@
 
-\textbf{Schur complement and self-consistent equations.}
+\paragraph{Schur complement and self-consistent equations.}
 First, we consider the special case where $Z^{(1)}$ and $Z^{(2)}$ are both multivariate Gaussian random matrices.
@@
 
-\section{Conclusions}\label{sec_conclude}
-
+\section{Discussions}\label{sec_conclude}
+\FY{Conclusions are not needed for AOS. If you want to have this section, please use it to give some additional remarks that are not discussed yet, and to discuss about possible futuer works.}
 This work studied generalization properties of a widely used hard parameter sharing approach for multi-task learning.
@@
 \begin{supplement}
-\textbf{Supplement to ``High-dimensional Asymptotics of Transferring from Different Domains in Linear Regression"}.
+\textbf{Supplement to ``High-dimensional Asymptotics of Information Transfer for Linear Regression under Covariate Shifts"}.
 In the Internet Appendix \cite{MTL_suppl}, we provide the proofs of the technical results in Sections \ref{sec_HPS}-\ref{sec_diff}, including Lemma \ref{lem_HPS_loss}, Theorem \ref{thm_many_tasks}, Theorem \ref{cor_MTL_loss}, Proposition \ref{lem_hat_v}, Theorem \ref{thm_main_RMT} and Proposition \ref{prop_main_RMT}.

### 2022-02-13 prior_versions/revision_journal/results.tex
update

--- 2021-07-23 revision_journal/results.tex
@@
 We show precise estimates of the bias and variance of HPS and almost sharp convergence rates.
-In Section \ref{sec3_cov}, we characterize the variance of HPS under covariate shift, which extends the classical result from Lemma \ref{fact_tr} to the sum of two sample covariance matrices.
-We provide a detailed analysis of the impact of covariate shift on the excess risk of HPS.
+In Section \ref{sec3_cov}, we characterize the variance of HPS under covariate shift, which extends the classical result from Lemma \ref{fact_tr} to the sum of two sample covariance matrices with covariate shift.
+Based on the characterization, We provide a detailed analysis of the impact of covariate shift on the excess risk of HPS.
 In Section \ref{sec_sizeratio}, we characterize the bias of HPS under model shift.
 Combined with the variance estimates, we describe three regimes of information transfer in the random-effect model, depending on the sample size $n_1$ and the model shift parameter $\mu$.
-Finally, Section \ref{sec3_combined} extends our results to settings with both covariate and model shift.
+Finally, Section \ref{sec3_combined} extends these results to settings under covariate and model shifts.
 %On the other hand, in case (ii), we will provide an estimate on the bias term, which becomes exact only when $n_1\gg p$.
@@
 
-\subsection{Covariate and model shift}\label{sec3_combined}
+\subsection{Covariate and model shifts}\label{sec3_combined}
+\todo{write down the formal statement}
 
@@
 	\end{subfigure}
-	\caption{We further show that our observations in Figures \ref{fig_sec31} and \ref{fig_sec3_model_shift} extend to settings with both covariate and model shift.
+	\caption{We further show that our observations in Figures \ref{fig_sec31} and \ref{fig_sec3_model_shift} extend to settings under covariate and model shifts.
 	Both simulation use $p = 100, n_2 = 300, \sigma = 1/2$.
@@
 
-\begin{theorem}[Bias estimates under covariate and model shift]\label{prop_main_RMT}
+\begin{theorem}[Bias estimates under covariate and model shifts]\label{prop_main_RMT}
 %The bias equation \eqref{Lbias} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
@@
 \end{theorem}
+\todo{consider changing $a_3, a_4$ to $\alpha_3, \alpha_4$ because of conflict with $a$}
 

### 2022-02-13 prior_versions/revision_journal/setup.tex
update

--- 2021-07-23 revision_journal/setup.tex
@@
 
-First, we assume the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)} \in \real^{p \times p}$. Equation \eqref{eq_rvm} implies that
+First, recall that the row vectors of $X^{(i)}$ are i.i.d. centered random vectors with  population covariance matrix $\Sigma^{(i)} \in \real^{p \times p}$:
 \be\label{XofZ}
-    X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p},
+    X^{(i)} = Z^{(i)} (\Sigma^{(i)})^{1/2} \in \real^{n_i\times p}.
 \ee
-recalling that $\Sigma^{(i)}$ is a deterministic positive definite symmetric matrices, $Z^{(i)}=(z^{(i)}_{j,k})$ is a $n_i\times p$ random matrix with real-valued independent entries having zero mean and unit variance.
+%recalling that $\Sigma^{(i)}$ is a deterministic positive definite symmetric matrices,
+where $Z^{(i)}=(z^{(i)}_{j,k})$ is a $n_i\times p$ random matrix with real-valued independent entries having zero mean and unit variance.
 %\begin{equation}\label{assm1}
@@
 
-\paragraph{Information transfer.} To be precise, we say that task one provides a \textit{positive transfer} to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
-Otherwise, we say that task one provides a \textit{negative transfer} to task two.
+%\paragraph{Information transfer.} To be precise, we say that task one provides a \textit{positive transfer} to task two, if the excess risk $L(\hat{\beta}_2^{\MTL})$ is smaller than $L(\hat{\beta}_2^{\STL})$.
+%Otherwise, we say that task one provides a \textit{negative transfer} to task two.
 
-\subsection{Bias and variance}
+\subsection{Bias and variance}\label{sec_bv}
 
@@
 \end{align*}
-Combining both comparisons, we conclude that HPS affects the excess risk in two ways: the bias always increases while the variance always decreases.
-Thus, whether or not task one provides a positive transfer to task two depends on which effect is more significant.
+Combining both comparisons, we conclude that the transfer effect of HPS is mixed: the bias always increases while the variance always decreases.
+Thus, whether or not the resulting information transfer is \textit{positive} depends on which effect is more significant.
 

### 2022-02-13 prior_versions/writeup/extension.tex
update

--- 2020-03-27 writeup/extension.tex
@@
 \section{Extensions to the Sparse Setting}
+
+\todo{Describe a straightforward extension of our results here through isometry.}
 One important case is the sparse case, where we assume that the $\beta_i$'s are sparse in the sense

### 2022-02-13 prior_versions/arxiv/diff_cov.tex
update

--- 2020-10-22 arxiv_full_version/diff_cov.tex
@@
 This section discusses how having different sample sizes and different covariance matrices impact hard parameter sharing.
-%The different covariates case differs from the same covariates case in two aspects.
-%First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
 The setting where covariates differ across tasks is often known as ``covariate shift''.
@@
 Hence the HPS estimator is equal to $B$.
-%Hence we can write down a closed form equation for any local minimizer of $f(A, B)$.
 By solving $B$ in equation \eqref{eq_mtl}, we obtain the estimator for task two as follows:
@@
 To derive the bias and variance equation, we consider the expected loss conditional on the covariates as follows (the empirical loss is close to this expectation as will be shown in equation \eqref{claim_largedev2}):
- %similar to Claim \ref{claim_pred_err}
 \begin{align}
@@
 However, capturing this intuition quantitatively turns out to be technically challenging.
-%The main technical challenge of our result deals with the ``covariate shift'' between tasks one and two.
 We introduce a critical quantity $M \define (\Sigma^{(1)})^{1/2}(\Sigma^{(2)})^{-1/2}$, and as we show below, the trace of $\hat{\Sigma}^{-1}$ has an intricate dependence on the spectrum of $M$.
-%Let $U\Lambda V^\top$ denote the SVD of $M$ and
 Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote $M$'s singular values in descending order.
@@
 
-\noindent(ii) The bias equation \eqref{eq_bias_2task} satisfies the following limit with high probability: Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$, for any unit vector $w\in S$,
+\noindent(ii) Let $S$ be an arbitrary subset of the unit sphere in dimension $p$ whose size is polynomial in $p$.
+The bias equation \eqref{eq_bias_2task} satisfies that for any unit vector $w\in S$, we have
 			\begin{align}\label{lem_cov_derv_eq}
@@
 			\end{align}
-				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations % with $b_k = \frac1{p}\sum_{i=1}^p \frac{\lambda_i^{2k}} {(\lambda_i^2 a_1 + a_2)^2}$, for $k = 0, 1, 2$:
+				where $a_{3}$ and $a_4$ are the solutions of the following self-consistent equations %
 			\begin{align}\label{eq_a34extra}
@@
 				a_3 + \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 (a_2 a_3-a_1 a_4 )}{(\lambda_i^2 a_1 + a_2)^2} = \frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^{2}}.
-%				\left(\frac{\rho_1}{a_1^{2}} -  b_2  \right)\cdot  a_3 -  b_1 \cdot  a_4 = b_1,\quad \left(\frac{\rho_2}{a_2^{2}}-  b_0\right)\cdot  a_4 - b_1 \cdot  a_3
-%				= b_0.
 			\end{align}
 \end{theorem}
-%Due to space limit, we defer the bias limit result to Appendix \eqref{appendix RMT}.
 Our result extends Fact \ref{fact_tr} to the inverse of the sum of two sample covariance matrices.
@@
 We defer a proof sketch of Theorem \ref{thm_main_RMT} until the end of the section.
-%This amounts to replacing $M$ with $\frac{A_1}{A_2}M$ in Theorem \ref{thm_main_RMT}.
 
@@
 	because $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$ by equation \eqref{eq_a12extra}.
-	%Similarly, for the bias limit, we solve the self-consistent equations \eqref{eq_a34extra} to get $a_3$ and $a_4$ after we have obtained $a_1, a_2$.
 	Similarly, we can calculate the bias limit.
@@
 	In the setting of Example \ref{ex_sample_ratio}, assume that
-	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
 	(i) both tasks sample sizes are at least $3p$;
 	(ii) noise variance is smaller than the shared signal variance: $\sigma^2 \lesssim  \kappa^2$;
-%	\be\label{choiceofpara0}
-%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
-	%\be\label{choiceofpara0}
-%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
-%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
 	(iii) task-specific variance is much smaller than the shared signal variance: $d^2 \le p^{-\e}{\kappa^2}$ for a small constant $c>0$.
@@
 	\begin{align}
-	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
 	   \left|L(\hat{\beta}_2^{\MTL}) - \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right|
 	\le \varepsilon \cdot \frac{2d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} +  \OO(p^{-c/2}).\label{cor_MTL_error}
-	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
-	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
 	 \end{align}
-%	 with high probability for any fixed $c\in(0, \min(\frac{1}{4}, \delta,\frac{\varphi-4}{2\varphi}))$.
-%	 {\color{red}[FY: the error also contains $p^{-1/2+2c}\kappa^2 +  p^{-1/4+c} (\sigma^2 +d^2) $, both of which cannot be omitted, because (i) there is no assumption on the upper bound of $\kappa^2$, and (ii) we do not necessarily have $c_\varphi<1/4$.
-We can decide how to present the result concisely (for instance we can impose an upper bound on $\kappa^2$ and that $c_\varphi<1/4$), but it needs to be correct.]}
 	 \end{corollary}
@@
 The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
-As a remark, %in equation \eqref{cor_MTL_error}, the predication loss $L(\hat{\beta}_2^{\MTL}) $ was obtained using the global minimizer $(\hat A,\hat B)$. B
+As a remark, %
 by combining the bias and variance limits, we can also obtain a bias-variance tradeoff for any local minimizer of $f(A, B)$.
@@
 We assume that $n_2$ is fixed for simplicity.
-%Now we illustrate an interesting phenomenon that adding task one's samples helps task two initially, but may hurt eventually.
 The variance limit in equation \eqref{cor_MTL_error} obviously decreases with $n_1$.
 It turns out that the bias term always increases with $n_1$, which can be verified by showing that the bias limit's derivative is always nonnegative.
-%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
-%We describe a sketch of the proof.
 By comparing the derivative of the bias and variance limits with respect to $n_1$ (details omitted), we obtain the following dichotomy.
@@
 \begin{example}[Covariate shift]\label{ex_covshift}
-%So far we have considered the isotropic model where $\Sigma_1 = \Sigma_2$.
-%This setting is relevant for settings where different tasks share the same input features such as multi-class image classification.
-%In general, the covariance matrices of the two tasks may be different such as in text classification.
 Our second example focuses on how varying covariate shifts impacts the \textit{variance} limit in equation \eqref{lem_cov_shift_eq}. For large enough $p$,
-%in the left hand side of equation \eqref{lem_cov_shift_eq}:
 \begin{align*}
@@
 \end{align*}
-%As we are going to show later, covariate shift is accurately captured by the spectrum of $\Sigma^{1/2}\Sigma^{-1/2}$.
-Hence the variance limit depends on the spectrum of $M$. % To be clear, for this example we assume that the bias is $0$.
+Hence the variance limit depends on the spectrum of $M$. %
 To illustrate the result, suppose that half of $M$'s singular values are equal to $\lambda > 1$ and the other half are equal to $\lambda^{-1}$.
@@
 Using the fact that $a_1 + a_2 = 1 - \frac{p}{n_1 + n_2}$, we can verify
-%\begin{align*}
-%	f(\lambda) - f(1) &= \left(\lambda^2 a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&+ \left(\lambda^{-2} a_1 + \frac{n_1 + n_2 - p}{n_1 + n_2} - a_1\right)^{-1} \\
-%	&- \frac{2(n_1 + n_2)}{n_1 + n_2 - p} \\
-%	&= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
-%\end{align*}
 \begin{align*}
-	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %\cdot (\lambda^2-1)^2
+	f(\lambda) - f(1) &= \left(2a_1 - \frac{n_1 + n_2-p} {n_1 + n_2 }\right)  g(\lambda, a_1), %
 \end{align*}
 where $g(\lambda, a_1) \ge 0$.
-%and can be derived from algebraic calculations (details omitted).
 We claim that $a_1 \ge \frac{n_1 + n_2-p}{2(n_1 + n_2 )}$ if and only if $n_1 \ge n_2$, which explains the dichonomy.
@@
 \end{align*}
-%\begin{align*}
-% \frac{n_1}{n_1 + n_2} &=a_1 + \frac1{n_1 + n_2}\cdot \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1}{\lambda_i^2 a_1 + a_2}} \\
-%	&> a_1 + \frac{p}{2(n_1+n_2)} \left(\frac{\lambda^2}{\lambda^2+1}+\frac{\lambda^{-2}}{\lambda^{-2}+1}\right) =\frac{1}{2}.
-%\end{align*}
-This implies $n_1>n_2$.
-The other direction follows from similar arguments.
-% Similarly, if $a_1<a_2$, equations  \eqref{eq_a12extra000} and  \eqref{eq_a12extra} give that $a_1 < \frac{n_1 + n_2-p}{2 (n_1 + n_2)}$ and $n_1<n_2$.
-%Thus, we conclude that $f(\lambda) \ge f(1)$ if and only if $n_1 \ge n_2$.
+This implies $n_1>n_2$. The other direction follows from similar arguments. %
 
 \iffalse
-%FY: Below was the word explanation. I still think the above simple proof is clearer.
 In fact, due to the fact that $M=M^{-1}$, $a_1$ and $a_2$ play symmetric roles in equations \eqref{eq_a12extra000} and \eqref{eq_a12extra}.
@@
 Thus, the Stieltjes transform method reduces the study of a probability measure $\mu$ to the study of a complex function $m_\mu(z)$.
-%To study the trace of $\hat{\Sigma}^{-1}$, we consider the Stieltjes transform of its empirical spectral distribution.
 
-%Recall that  $U\Lambda V^\top$ is the singular value decomposition of $M$, %$\Lambda$ consists of the singular values of $M$, $V$ is an orthonormal matrix,
-%It is not hard to verify that $(n_1 + n_2)\hat{\Sigma}^{-1}= (\Sigma^{(2)})^{-1/2} V W^{-1}V^\top (\Sigma^{(2)})^{-1/2}$ and .
 Let $\mu=p^{-1}\sum_{i} \delta_{\sigma_i}$ denote the empirical spectral distribution of $W$, where the $\sigma_i$'s are the eigenvalues of $W$ and $\delta_{\sigma_i}$ is the point mass measure at $\sigma_i$.
@@
 The above matrix $(W - z\id)^{-1}$ is known as $W$'s resolvent or Green's function.
-%When $p$ goes to infinity, it is well-known that $m_{\mu}(z)$ converges to a fixed distribution governed by a set of self-consistent equations.
-%These self-consistent equations give the asymptotic limit of the trace of $\hat{\Sigma}^{-1}$.
-%The above approach applies when $\Sigma^{(2)}$ is isotropic in Theorem \ref{thm_main_RMT}.
-%Since our goal is to show the limit of $\tr\left[ (Y - z\id)^{-1}V^{\top}{\Sigma^{(2)}}^{-1}V \right]$ as shown in equation \eqref{eigen2extra}, we study the  $(Y-z\id)^{-1}$.
-%Compared to the Stieltjes transform, the resolvent also applies to random matrices.
 We prove the convergence of $W$'s resolvent using the so-called ``local law'' with a sharp convergence rate \cite{isotropic,erdos2017dynamical,Anisotropic}.
-%Recent developments in the random matrix literature have shown the convergence of the resolvent matrix using the so-called ``local laws'' or ``deterministic equivalents'' (cf.
-\cite{Hachem2007deterministic,DS18}).
 
-%For our purpose, we use a convenient linearization trick in linear algebra, that is, the SVD of a rectangular matrix $A$ is equivalent to the study of the eigendecomposition of the symmetric block matrix
-%$$H(A):=\begin{pmatrix}0 & A \\ A^\top & 0\end{pmatrix},$$
-%which is linear in $A$. This trick has been used in many random matrix literatures, such as \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}.
 We say that $(W-z\id)^{-1}$ converges to a deterministic $p\times p$ matrix limit $R(z)$ if for any sequence of deterministic unit vectors $v\in \R^p$,
@@
 	\be\label{defn AF} \AF := (n_1+ n_2)^{-1/2} [\Lambda U^\top (Z^{(1)})^\top,V^\top (Z^{(2)})^\top]. \ee
-%}\HZ{what does this trick mean? use less technical words},
-%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein.
 Consider the following symmetric block matrix whose dimension is $p + n_1 + n_2$
-%which is a linear function of $(Z^{(1)})$ and $(Z^{(2)})$:
-%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
-%We define the $(n+N)\times (n+N)$ block matrix
  \begin{equation}\label{linearize_block}
@@
    \AF^{\top} & 0
-%   {Z^{(2)}V} & 0 & 0
    \end{array}} \right).
@@
 $$G(z) \define \left[H - \begin{pmatrix}z\id_{p\times p}&0\\ 0 & \id_{(n_1+n_2)\times (n_1+n_2)} \end{pmatrix}\right]^{-1},$$
-%as the resolvent of $H$,
 for any complex value $z\in \mathbb C$.
@@
       \AF^\top (W - z\id)^{-1} & z(\AF^\top \AF - z\id)^{-1}
-		\end{array}} \right).%\quad \cal G_R:=(W^\top W - z)^{-1} ,
+		\end{array}} \right).%
   \end{equation}
@@
 \begin{split}
-	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %\label{selfomega_a000} \\
+	&a_1(z) + a_2(z) = 1 - \frac{1}{n_1 + n_2} \bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z) + a_2(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}}, \\ %
 	&a_1(z) + \frac{1}{n_1 + n_2}\bigbrace{\sum_{i=1}^p \frac{\lambda_i^2 a_1(z)}{\lambda_i^2 a_1(z) + a_2(z) - z}} = \frac{n_1}{n_1 + n_2}.
-% \frac{\rho_1}{a_{1}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{\lambda_i^2}{ - z+\lambda_i^2 a_{1}(z) +a_{2} (z) } + (\rho_1+\rho_2),\  \frac{\rho_2}{a_{2}(z)} = \frac{1}{p}\sum_{i=1}^p \frac{1 }{  -z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }+ (\rho_1+\rho_2) .
 \end{split}
@@
 The existence and uniqueness of solutions to the above system are shown in Lemma \ref{lem_mbehaviorw}.
-%First, we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where
-%satisfying that $\im a_{1}(z)< 0$ and $\im a_{2}(z)<0$ for $z\in \C_+$ with $\im z$.
-%\be\label{ratios}
-% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
-%\ee
 Given this result, we now show that when $z = 0$, the matrix limit $\Gi(0)$ implies the variance limit shown in equation \eqref{lem_cov_shift_eq}.
@@
 Second, since $W^{-1}$ is the upper-left block matrix of $G(0)$, we have that $W^{-1}$ converges to $ (a_1\Lambda^2 + a_2\id)^{-1} $.
-Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, % the trace of $$ converges to
+Using the fact that $\tr[\Sigma^{(2)} \hat{\Sigma}^{-1}] = (n_1 + n_2)^{-1}\bigtr{W^{-1}} $, we get that when $p$ goes to infinity, %
 \begin{align*}
@@
   \end{align*}
-%\noindent{\bf Variance asymptotics.} Using definition \eqref{mainG}, we can write equation \eqref{eigen2extra} as
-%\be\label{rewrite X as R} [(X^{(1)})^\top X^{(1)}+(X^{(2)})^\top X^{(2)}]^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
-%When $z=0$, it is easy to check that , which means that we actually have $a_1(0)=a_1$ and $a_2(0)=a_2$.
-Hence the matrix limit of $\cal G(0)$ is given by $(a_{1}\Lambda^2 + a_{2}\id_p)^{-1}$.
-Then inserting this limit into equation \eqref{rewrite X as R}, we can write the left-hand side of equation \eqref{lem_cov_shift_eq} as
-%\begin{align}
-%&\bigtr{\left( (X^{(1)})^{\top}X^{(1)} + (X^{(2)})^{\top}X^{(2)}\right)^{-1} \Sigma}\approx n^{-1}\bigtr{\Sigma_2^{-1/2}V\cal (a_{1}\Lambda^2 + a_{2}\id_p)^{-1}V^\top\Sigma_2^{-1/2}\Sigma}  \nonumber\\
-%&=n^{-1}\bigtr{\Sigma_2^{-1/2}\cal (a_{1}\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_{2}\id_p)^{-1}\Sigma_2^{-1/2}\Sigma}  = n^{-1}\bigtr{\cal (a_{1} \Sigma_1  + a_{2}\Sigma_2)^{-1}\Sigma}  ,\label{Gi00}
-%\end{align}
 where we note that $M^\top M = (\Sigma^{(2)})^{-1/2} \Sigma^{(1)} (\Sigma^{(2)})^{-1/2}$ and its SVD is equal to $V^{\top}\Lambda^2 V$.
-%For the asymptotic limit, its concentration error is shown in Appendix \ref{appendix RMT}.
 
@@
  For the bias limit in equation \eqref{lem_cov_derv_eq}, we show that it is governed by the derivative of $(W - z\id)^2$ with respect to $z$ at $z = 0$.
-First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %$W$
+First, we can express the empirical bias term in equation \eqref{lem_cov_derv_eq} as %
 \begin{align}\label{calculate G'}
@@
 To find the derivatives of $a_1(z)$ and $a_2(z)$, we take the derivatives on both sides of the system of equations \eqref{selfomega_a}.
-%\begin{align*}
-%	\frac{\dd a_1(z)}{\dd z} + \frac{\dd a_2(z)}{\dd z} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{1}{\lambda_i^2 a_1 + a_2},
-%	\frac{\dd a_1(z)}{\dd z} + \frac{1}{n_1 + n_2}\sum_{i=1}^p \frac{\lambda_i^2 (a_1'(z) a_2 - a_2'(z) a_1)}{(\lambda_i^2 a_1 + a_2)^2} = -\frac{1}{n_1 + n_2} \sum_{i=1}^p \frac{\lambda_i^2 a_1}{(\lambda_i^2 a_1 + a_2)^2}
-%\end{align*}
 Let $a_3 = - \frac{\dd a_1(0)}{\dd z}$ and $a_4 = - \frac{\dd a_2(0)}{\dd z}$.
-%then taking implicit differentiation of equation \eqref{selfomega_a}
 One can verify that $a_3$ and $a_4$ satisfy the self-consistent equations in \eqref{eq_a34extra} (details omitted).
 Applying equation \eqref{cal G'0} to equation \eqref{calculate G'}, we obtain the bias limit.
-%\begin{align}
-%& n^2\bignorm{\Sigma_2^{1/2} \bigbrace{ (X^{(1)})^{\top}(X^{(1)}) + (X^{(2)})^{\top}(X^{(2)}) }^{-1} \Sigma_1^{1/2} w}^2 \nonumber\\
-%&\approx  w^\top \Sigma_1^{1/2}\Sigma_2^{-1/2}V\frac{a_3\Lambda^2 +(1+ a_4)\id_p}{(a_{1}\Lambda^2 + a_{2}\id)^2}V^\top \Sigma_2^{-1/2}\Sigma_1^{1/2}w= w^{\top} \Pi_\bias w, \label{calculatePibias}
-%\end{align}
-%where in the last step we used $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and $V \Lambda^2 V^\top=M^\top M$. This concludes equation \eqref{lem_cov_derv_eq}.
 
@@
 We prove an anisotropic local law using recent developments in random matrix theory \cite{erdos2017dynamical,Anisotropic}.
-The proof of Theorem \ref{thm_main_RMT} is shown in Appendix \ref{appendix RMT}. %Appendix \ref{appendix RMT}.
+The proof of Theorem \ref{thm_main_RMT} is shown in Appendix \ref{appendix RMT}. %

### 2022-02-13 prior_versions/arxiv/experiments.tex
update

--- 2022-02-13 prior_versions/arxiv_full_version/experiments.tex
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
+		\includegraphics[width=0.98\textwidth]{figures/same_covariates-eps-converted-to.pdf}
 		\caption{Example \ref{ex_same_cov}}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
+		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d-eps-converted-to.pdf}
 		\caption{Example \ref{ex_sample_ratio}}
@@
 		\centering
-		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
+		\includegraphics[width=0.98\textwidth]{figures/covariate_shift-eps-converted-to.pdf}
 		\caption{Example \ref{ex_covshift}}
@@
 	\end{subfigure}
-	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
+	\caption{%
 	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
@@
 	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
-%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
 	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
@@
 Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
-%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
 Indeed, we observe a crossover point between hard parameter sharing and STL.
-Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level.
-%\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at.
-For example, at the cross point, this ratio is 1.
-}
+Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level. %
 
@@
 Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
-%Again, our estimates are accurate compared to the empirical losses.
 We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
@@
 Intuitively, this is because bias increases less for smaller $d^2$.
-%Our result from Corollary \ref{cor_MTL_loss} explains this trend.
 
@@
 The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
-%Covariate shift: We set $\kappa = 1$ and $d = 0$.
-%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
-%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
-
-%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
-%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
-%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
-%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
-%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
-%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.
-
-%\begin{table}
-%	\begin{center}
-%		\begin{tabular}{c c c c c}
-%			\toprule
-%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
-%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
-%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
-%			\midrule
-%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
-%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
-			% {\bf CNN}  & 76\% & - & 32\% & -\\
-%			\bottomrule
-%		\end{tabular}
-%	\end{center}
-%	\caption{Taskonomy experiment.}
-%	\label{tab:taskonomy}
-%\end{table}
-%\begin{figure}[!t]
-%	\centering
-%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
-%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings.
-The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
-%	\label{fig_same_cov}
-%\end{figure}

### 2022-02-13 prior_versions/arxiv/proof_gaussian_case.tex
update

--- 2020-10-20 arxiv_full_version/proof_gaussian_case.tex
@@
 \section{Proof of Theorem \ref{thm_main_RMT}}\label{appendix RMT}
-%We first state the asymptotic limit for the bias equation \eqref{eq_bias_2task}.
-
-%\begin{theorem}\label{thm_main_RMT_app}
-%
-%	In the setting of Theorem \ref{thm_main_RMT},
-%\end{theorem}
-%For the rest of this section, we present the proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app}
-
-%\paragraph{Proof Overview (cont'd).}
-%We continue the proof overview of Theorem \ref{thm_main_RMT} and \ref{thm_main_RMT_app} from Section \ref{sec_diff}.
-%Since the full proof of Theorem \ref{thm_main_RMT} and Theorem \ref{thm_main_RMT_app} is rather technical, in this subsection we give a more detailed proof overview, which contains the main ideas of the proof.
-%Recall that $(W-z\id)^{-1}$ is the resolvent of matrix $W$.
 
@@
 $$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
-%We will consistently use the latin letters $i,j\in\sI_{0}$ and greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$.
-%Correspondingly, the indices of the matrices $Z^{(1)}$ and $Z^{(2)}$ are labelled as
-%	\be\label{labelZ}
-% Z^{(1)}= [Z^{(1)}_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1], \quad Z^{(2)}= [Z^{(2)}_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2].\ee
 We will study the following partial traces of the resolve $G(z)$:
@@
 
-%\be\label{approx m12 add}
-%(m_1,m_2) =\left(-\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),-\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)+\oo(1) \quad \text{with overwhelming probability. }
-%\ee
-
 Next, we apply standard concentration bounds to simplify the above results.
@@
 Hence by standard concentration inequalities, we have that the cross terms are approximately zero.
-%is approximately equal to the expectation over $\{Z^{(1)}_{\mu i}: \mu \in \cal I_1 \}\cup \{Z^{(2)}_{\nu i}: \nu \in \cal I_2\}$.
 As shown in Lemma \ref{lemm_selfcons_weak}, we have that with high probability the following holds
@@
 \end{align*}
-by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$. %with respect to the resolvent minor $G^{(i)}(z)$.
+by our definition of the partial traces $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$. %
 Since we have removed only one column and one row from $H(z)$, $m_1^{(i)}(z)$ and $m_2^{(i)}(z)$ should be approximately equal to $m_1(z)$ and $m_2(z)$.
@@
 \begin{align*}
-	G_{\mu\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1},\quad G_{\nu\nu}(z) = -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
+	G_{\mu\mu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m_0(z) + \oo(1)\right)^{-1},\\ 
+	G_{\nu\nu}(z) &= -\left(1+\frac{p}{n_1 + n_2} m(z) + \oo(1)\right)^{-1}.
 \end{align*}
@@
 \begin{align*}
-	m_1^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p \lambda_i^2 G_{ii}(z)+ \oo(1),\quad  m_2^{-1}(z) = -1- \frac{1}{n } \sum_{i=1}^p G_{ii}(z)  + \oo(1).
+	m_1^{-1}(z) &= -1- \frac{1}{n } \sum_{i=1}^p \lambda_i^2 G_{ii}(z)+ \oo(1),\\ 
+	 m_2^{-1}(z) &= -1- \frac{1}{n } \sum_{i=1}^p G_{ii}(z)  + \oo(1),
 \end{align*}
@@
 The other off-diagonal entries are bounded similarly.
-%The bound on the off-diagonal entries will be proved rigorously .
 
@@
 Let $\xi\equiv \xi^{(n)}$ and $\zeta\equiv \zeta^{(n)}$ be two $n$-dependent random variables.
-%\HZ{what is $n$-dependent rv?}[{\cor Most variables in our paper are $n$-dependent implicitly, such as resolvents.
-Furthermore, the random matrix entries can also depend on $n$ if we want.
-One important example is Bernoulli random variable with sparsity $p=n^{-\theta}$.
-Furthermore, this also includes the random variables that do not depend on $n$ as a special case.}]
 We say that $\xi$ is stochastically dominated by $\zeta$, denoted by $\xi\prec \zeta$ or $\xi=\OO_\prec(\zeta)$, if for any small constant $\e > 0$ and any large constant $D > 0$, there exists a function $n_0(\e, D)$ such that for all $n > n_0(\e, D)$,
 \[ \bbP\left(|\xi| >n^\e |\zeta|\right)\le n^{-D}. \]
-In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if % for any constants $\e, D>0$,
+In case $\xi(u)$ and $\zeta(u)$ is a function of $u$ supported in $\cal U$, then we say $\xi(u)$ is stochastically dominated by $\zeta(u)$ uniformly in $\cal U$ if %
 \[ \sup_{u\in \cal U}\bbP\left(|\xi(u)|>n^\e |\zeta(u)|\right)\le n^{-D}. \]
@@
 
-%For example, we say that $\xi$ is stochastically dominated by $\zeta$ with overwhelming probability if $\zeta$ is greater than $\xi$ up to a small power of $n^{\e}$.
 We make several remarks.
@@
 
-%In this section, we shall prove a more fundamental random matrix result in a little more general setting than the one in Section \todo{add reference}; see Theorem \ref{LEM_SMALL} below.
-%\ref{sec_prelim}.
-%Then Theorem \ref{thm_main_RMT} will follow from this result as immediate corollaries. We first state the exact assumptions needed for our purpose.
-
 Next, we introduce the bounded support assumption for a random matrix.
@@
 As shown in the example above, if the entries of $Z$ have finite moments up to any order, then $Z$ has bounded support $1$.
-More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that %\HZ{I don't fully get the equation below}
+More generally, if the entries of $Z$ have finite $\varphi$-th moment, then using Markov's inequality and a simple union bound we get that %
 \begin{align}
@@
 The following resolvent identities are important tools for our proof.
-Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{diagW}.
+Recall that the resolvent minors have been defined in Definition \ref{defn_Minor}, and matrix $\AF$ is given in equation \eqref{defn AF}.
+%
 \begin{lemma}\label{lemm_resolvent}
@@
 		\end{equation}
-%For $i\in \mathcal I_1$ and $\mu\in \mathcal I_2$, we have
-%\begin{equation}\label{resolvent6}
-%\begin{split}
-% G_{i\mu } =  -G_{ii}  \left( WG^{\left( {i} \right)} \right)_{i\mu}, \quad G_{\mu i}= -G_{\mu\mu}\left( W^\top G^{(\mu)}\right)_{\mu i}.
-%\left( { - Y_{i\mu }  +  {\left( {YG^{\left( {i\mu } \right)} Y} \right)_{i\mu } } } \right) .
-%, \ \  G_{\mu i}  = G_{\mu \mu } G_{ii}^{\left( \mu  \right)} \left( { - Y_{\mu i}^\top  + \left( {Y^\top  G^{\left( {\mu i} \right)} Y^\top  } \right)_{\mu i} } \right).
-%\end{split}
-%\end{equation}
  \item[(iii)] For $a \in \mathcal I$ and $a_1,a_2 \in \mathcal I \setminus \{a\}$, we have
@@
 			G_{a_1a_2}^{\left( a \right)}  = G_{a_1a_2}  - \frac{G_{a_1a} G_{aa_2}}{G_{aa}}.
-%, \quad  \frac{1}{{G_{{b}{b}} }} = \frac{1}{{G_{{b}{b}}^{({a})} }} - \frac{{G_{{b}{a}} G_{{a}{b}} }}{{G_{{b}{b}} G_{{b}{b}}^{({a})} G_{{a}{a}} }}.
 			\label{resolvent8}
 		\end{equation}
-%and
-%\begin{equation}
-%\frac{1}{{G_{ss} }} = \frac{1}{{G_{ss}^{(r)} }} - \frac{{G_{sr} G_{rs} }}{{G_{ss} G_{ss}^{(r)} G_{rr} }}.
-%\label{resolvent9}
-%\end{equation}
-% \item[(iv)]
-%All of the above identities hold for $G^{(\mathbb T)}$ instead of $G$ for $\mathbb T \subset \mathcal I$, and in the case where $A$ and $B$ are not diagonal.
 \end{itemize}
@@
 We recall that the stochastic domination ``$\prec$" has been defined in Definition \ref{stoch_domination}.
-%Besides the proof of Lemma \ref{prop_entry}, we also use it in several other places of this paper, including the proofs in Section \ref{sec_proof_general} and Section \ref{app_iso_cov}.
-%It constitutes the main difference between our proof and the one in \cite{KY2}, where the authors used a large deviation bound for random variables with arbitrarily high moments.
 \begin{lemma}[Lemma 3.8 of \cite{EKYY1} and Theorem B.1 of \cite{Delocal}]\label{largedeviation}
@@
 Suppose the entries $x_i$ and $y_j$ have variance at most $1$, and satisfy the bounded support condition (\ref{eq_support}) for a deterministic parameter $Q$.
-%with $q\le n^{-\phi}$ for a small constant $\phi>0$.
+%
 Then we have the following results:
-%for any fixed $\xi>0$, the following bounds hold with $\xi$-high probability:
 \begin{align}

### 2022-02-13 prior_versions/arxiv/proof_same_cov.tex
update

--- 2020-12-03 old/arxiv_full_version/proof_same_cov.tex
@@
 	Denote
-		%\[ \cE A^{\top} := {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \]
 \[\cE  :=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}],  \quad \text{ and } \quad \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{+}. \]
@@
 	We will divide $g(A)$ into three parts.
-	For simplicity, we will use matrix notations in the proof, %since they are more compact.
+	For simplicity, we will use matrix notations in the proof, %
 	that is, stacking $[H_j]_j$ gives matrix $B^{\star} A^{\top} (AA^{\top}) A - B^{\star}$,
@@
 	First, we have that $\ex{\|\cE\|_F^2} = \sigma^2 \cdot n \cdot t$.
-%	Conditional on $X$, we have that
-%	\begin{align*}
-%		\exarg{\cE}{\norm{E_j}^2}
-%		= \exarg{\cE}{\sum_{j=1}^t \bigbrace{\bignorm{\cW A_j}^2 - 2\inner{\cW A_j}{\varepsilon^{(j)}} }} + \sigma^2 \cdot n \cdot t.
-%	\end{align*}
-%	We consider both terms in the above equation one by one.
 	Second, we show that
-	%	\begin{align*}
-	%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
-	%	\end{align*}
-	%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
 	\begin{align*}
@@
 	For any $1\le i, j \le t$, let $\delta_{i, j} = 1$ if $i = j$, and $0$ otherwise.
-	%\begin{align}
-	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}.
-\label{eq_proof_same_cov_1}
-	%\end{align}
-	%We observe that
 	Because $\varepsilon^{(i)}$ and $\varepsilon^{(j)}$ are pairwise independent, we have that
@@
 	Hence, the second step is correct.
-	%Above, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
-	%Next, note that
-	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
-	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.
 
@@
 	Second, notice that
-	%\begin{align}
-	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}.
-\label{eq_proof_same_cov_1}
-	%\end{align}
-	%We observe that
 	\begin{align*}
@@
    because $X^\top X$ is a $p\times p$ matrix.	
-	%Next, note that
-	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
-	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.
 	Hence the proof is complete.
@@
 	\end{align}
-%	\begin{align}\label{eq_gA_err}
-%		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
-%	\end{align}
 	We consider the concentration error of each part of $g(A)$.
 
-	For equation \eqref{eq_gA_p1}, % $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
-%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
-%	note that $X H_j = Z \Sigma^{1/2} H_j \in \real^n$ is a random vector with i.i.d.
-entries of mean zero, variance $\|\Sigma^{1/2}H_j\|^2$, and finite $\varphi$-th moment by Assumption \eqref{assume_rm}.
-%	Hence by the law of large numbers, we have that with high probability	
+	For equation \eqref{eq_gA_p1}, %
 	applying Corollary \ref{cor_largedeviation} to $X H_j = Z \Sigma^{1/2} H_j$, we obtain that 
@@
 	For equation \eqref{eq_gA_p2}, 
-	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
 	using Corollary \ref{cor_calE}, we obtain the following with high probability:
@@
 		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} . \label{eq_gA_err2}
-%		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
 	\end{align}
@@
 	For equation \eqref{eq_gA_p3}, using Corollary \ref{cor_calE},
-	%Lemma \ref{largedeviation} and the fact that all moments of $\varepsilon_i$ exist, 
 	we obtain that with high probability,
@@
 		&\le \sqrt{r} \cdot n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F \nonumber \\
-		&\le \sqrt{r} \cdot n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err4} %  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
+		&\le \sqrt{r} \cdot n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err4} %
 	\end{align}
@@
 	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id_{t\times t}$ is at most one. 
-	%With \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows. 
 	Using equation \eqref{same_hA}, we can verify that
@@
 	\begin{proof}[Proof of Claim \ref{claim_pred_err}]
-	%We apply similar arguments from Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
 	The proof is similar to that of equation \eqref{eq_gA_err}.
@@
 	\end{align*}
-%	\begin{align*}
-%		\bigabs{\inner{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)}{\Sigma^{1/2}R_i}} &= \bigabs{\inner{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}{\cal E}} \\
-%		&\le n^{c}\sigma \cdot \bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)}\\
-%		&\le n^{c}\sigma \cdot\|\hat a_i\| \cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\| \cdot \| (Z^\top Z)^{-1} \|^{1/2} \\
-%		&\lesssim n^{-1/2+c}\sigma \cdot\|\hat a_i\| \cdot \bignorm{\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)} \\
-%		&\le n^{-1/2+c}\sigma^2  \cdot\|\hat a_i\|^2 + n^{-1/2+c} L(B^{\star} \hat{a}_i), 
-%	\end{align*}
 	In the first step, we plug in the definition of $R_i$ and re-arrange terms.
@@
 	\end{align*}
-%	\begin{align*}
-%	\bignormFro{\hat a_i^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i)} &=\|\hat a_i\|\cdot \left[ (B^{\star} \hat{a}_i - \beta_i)^\top \Sigma (X^\top X)^{-1}X^\top X(X^\top X)^{-1}\Sigma (B^{\star} \hat{a}_i - \beta_i) \right]^{1/2} \\
-%	&\le \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| \Sigma^{1/2}(X^\top X)^{-1}\Sigma ^{1/2} \right\|^{1/2} \\
-%	&= \|\hat a_i\|\cdot  \|\Sigma^{1/2}(B^{\star} \hat{a}_i - \beta_i)\|  \cdot \left\| (Z^\top Z)^{-1}\right\|^{1/2}
-%	\end{align*}
-	Above, we use $X=Z\Sigma^{1/2}$. In the last step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z^\top Z$ by $\OO(n^{-1})$. %, and apply the AM-GM inequality.
+	Above, we use $X=Z\Sigma^{1/2}$. In the last step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z^\top Z$ by $\OO(n^{-1})$. %
 	One can see that the concentration error from this part is upper bounded by the result in Claim \ref{claim_pred_err}.
@@
 	\end{align}	
-%	If $j\ne k$, using Corollary \ref{cor_calE} we obtain that 
-%	\begin{align}
-%	\left|{\epsilon^{(j)}}^\top X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} {\epsilon^{(k)}} \right| &\le \sigma^2 \cdot \bignormFro{X(X^{\top} X)^{-1}\Sigma (X^{\top} X)^{-1} X^{\top} } \nonumber\\
-%	& =\sigma^2 \cdot \bignormFro{\Sigma^{1/2}(X^{\top} X)^{-1}\Sigma^{1/2}} \nonumber\\
-%	&  \le \sigma^2 \cdot p^{1/2} \cdot \bignorm{(Z^{\top} Z)^{-1}} \lesssim \sigma^2 \cdot n^{-1/2+c} \label{jnek}
-%	\end{align}
-%	with high probability for any small constant $c>0$. On the other hand, if $j=k$, 
 	First, for any $1 \le j, k \le t$, the expectation is
@@
 	\end{align*}
-%	One can verify that the expectation of $\norm{\Sigma^{1/2} E_i}^2$ is equal to $\sigma^2 \norm{\hat{a}_i}^2 \cdot \tr[\Sigma (X^{\top} X)^{-1}]$.
-%	Next, we bound the concentration error.
-%	Let $A = X (X^{\top} X)^{-1} \Sigma (X^{\top} X)^{-1} X^{\top}$.
-%	We have that
-%	\begin{align*}
-%		\bigabs{\bignorm{\Sigma^{1/2} E_i}^2 - \exarg{\cE}{\bignorm{\Sigma^{1/2} E_i}^2}}
-%		&= \bigabs{\inner{A}{\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top} - \exarg{\cE}{\cE \hat{a}_i \hat{a}_i^{\top} \cE}}}.
-%	\end{align*}
-%	In the above equation, we note that the trace of $A$ is precisely the trace of $\Sigma (X^{\top} X)^{-1}$.
-%	On the other hand, the concentration error of the spectral norm of $\cE \hat{a}_i \hat{a}_i^{\top} \cE^{\top}$ is at most $\sigma^2 \e $.
 

### 2022-02-13 prior_versions/arxiv/setup.tex
update

--- 2020-10-22 arxiv_full_version/setup.tex
@@
 
-%We assume that there are multiple datasets that all follow (potentially different) linear models.
-%In each dataset, suppose the feature vector is $x = {\Sigma}^{1/2} z$, where $z \in \real^p$ has i.i.d entries with zero mean and unit variance, and the population covariance matrix $\Sigma \in\real^{p \times p}$ is deterministic and positive semidefinite.
 Suppose we have $t$ datasets.
@@
 See Figure \ref{fig_intro_arch} for an illustration.
-%The width of $B$, denoted by $r$, plays an important role in regularization.
-%As observed in Proposition 1 of \citet{WZR20}, if $r \ge t$, there is no regularization effect.
-%Hence, we assume that $r < t$ in our study.
-%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
 We study the following minimization problem:
-%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
-%	The size of each set is described below.
-%	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
-%\vspace{-0.1in}
 \begin{align}\label{eq_mtl}
@@
 \end{align}
-%\vspace{-0.05in}
 where $A = [A_1, A_2, \dots, A_t] \in \real^{r \times t}$.
@@
 This setting is tractable even though in general, $f(A, B)$ is non-convex in $A$ and $B$ (e.g. matrix completion is a special case for suitably designed $X^{(i)}, Y^{(i)}$).
-%We show that the prediction loss of HPS admits a clean bias-variance decomposition.
 Our result implies that when all tasks have the same features but different labels, for any task, HPS helps reduce the task's variance compared to single-task learning but increases bias.
@@
 
-%First, we develop tight bounds for the bias and variance of the multi-task estimator for two tasks by applying recent development in random matrix theory \cite{erdos2017dynamical,isotropic,Anisotropic}.
-%We observe that the variance of the multi-task estimator is \textit{always smaller} than single-task learning, because of added source task samples.
-%On the other hand, the bias of the multi-task estimator is \textit{always larger} than single-task learning, because of model distances.
-%Hence, the tradeoff between bias and variance determines whether the transfer is positive or negative.
-%We provide a sharp analysis of the \textit{variance} that scales with sample size and covariate shift.
-%We extend the analysis to the bias, which \textit{in addition} scales with {task similarity}.
-%Combining both, we analyze the bias-variance tradeoff for two tasks in Theorem \ref{thm_main_informal} and extend the analysis to many tasks with the same features in Theorem \ref{thm_many_tasks}.
-%For the setting of two tasks, we show how the variance of the multi-task estimator  scales with sample size and covariate shift in the following result.
-%\textit{Our first contribution} is to develop a concentration bound that arises naturally from the bias-variance tradeoff of $\hat{\beta}_t^{\MTL}$ for two tasks.
-%Let $\hat{\beta}_t^{\STL}$ denote the single-task estimator.
-%Without loss of generality, let the $t$-th task denote the target task.
-%Importantly, the target task's data size is a fixed constant times $p$ in the high-dimensional setting.
-%Hence adding more labeled data can help improve its test performance.
-%$B\in\real^{p\times r}$
-%$\set{W_i \in \real^{r}}_{i=1}^t$
-
-%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
-%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
-%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
-
-%We shall assume that each task data follows a linear model, i.e. $y_i = X_i \beta_i + \varepsilon_i$, $1\le i\le k$.
-%Here $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
-%Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed
-%distribution with covariance matrix $\Sigma_i$.
-
-%We extend our result to the transfer learning
-%in the setting of high-dimensional linear regression.
-%by pooling source task representations into the shared body of the hard parameter sharing architecture, following
-%setting of Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We prove that the bias of the transfer learning estimator is given by the projection of $\beta_t$ to the orthogonal subspace spanned by $\set{\beta_i}_{i=1}^{t-1}$.
-%These results are described more precisely in Section \ref{sec_main}.
-
-%Second, we explain the phenomena in Figure \ref{fig_model_shift_phasetrans} in isotropic and covariate shifted settings.
-%We observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
-%\textbf{Task similarity:}
-%\textbf{Data sizes:}
-%\textbf{Covariate shift:}
-%Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
-%\squishlist
-%	\item We provide conditions to predict the effect of transfer as a parameter of model distance $\norm{\beta_1-\beta_2}$ (Section \ref{sec_similarity}).
-%	As model distance increases, the bias becomes larger, resulting in negative transfer.
-%	Our result predicts most of the empirical observations in Figure \ref{fig_model_shift} correctly.
-%	It is crucial that the concentration result in Theorem \ref{lem_cov_shift_informal} is sufficiently precise so that we can explain the transition phenomena in Figure \ref{fig_model_shift} and \ref{fig_size}.
-%	The unexplained observations are caused by an error term from the bias.
-%	We discuss these in Section \ref{sec_insight}.
-%	\item We provide conditions to predict transfer as a parameter of sample ratio $\rho_1/\rho_2$ (Section \ref{sec_data_size}).
-%	Adding source task samples helps initially by reducing variance, but hurts eventually due to bias.
-	%namely adding more labeled data from the source task does not always improve performance (Proposition \ref{prop_data_size}).
-	%Theorem \ref{lem_cov_shift_informal} allows us to compare MTL performance under different covariate shifts.
-%	\item For a special case of $\beta_1=\beta_2$, we show that MTL performs best when the singular values of $\Sigma_1^{1/2}\Sigma_2^{-1/2}$ are all equal  (Section \ref{sec_covshift}).
-%	Otherwise, the variance reduces less with covariate shift.
-%	Our theoretical bound matches the empirical curve in Figure \ref{fig_covariate}.
-%\squishend
-%In Section \ref{sec_insight}, we consider three components including task similarity, data size and covariate shift for a simplified isotropic setting of two tasks.
-%We measure task similarity by how small is the distance between $\beta_1$ and $\beta_2$.
-%Using our tool, we explain a transition from positive to negative transfer as task similarity decreases.
-%		Furthermore, we show that negative transfer is more likely to occur when the source task labels are particularly noisy.
-%		In Section \ref{sec_validate}, we validate the observation on text and image classification tasks.
-%	In , we provide the trade-off between $\norm{\beta_1 - \beta_2}^2$ and a certain function $\Phi(\rho_1, \rho_2)$ to determine the type of transfer.
-%We show that increasing the data size of the source task does not always improve performance for the target task in multi-task learning.
-%Along the way, we analyze the benefit of MTL for reducing labeled data to achieve comparable performance to STL, which has been empirically observed in Taskonomy by Zamir et al. \cite{ZSSGM18}.
-%We show that covariate shift, measured by $\Sigma_1^{1/2}\Sigma_2^{-1/2}$, is another cause for suboptimal performance for $\hat{\beta}_t^{\MTL}$.
-%		We show that as $n_1 / n_2$ becomes large, having no covariate shift between the source and target tasks yields the optimal performance for the target task.
-%		On the other hand, when $n_1 / n_2$ is small, there are counter examples where having the same covariance matrix is not necessarily the optimal choice.
-
-%Our study also leads to several algorithmic consequences with practical interest.
-%First, we show that single-task learning results can help to predict positive or negative transfer for multi-task learning.
-%We validate this observation on ChestX-ray14 \cite{chexnet17} and sentiment analysis datasets \cite{LZWDA18}.
-
-%Third, we provide a fine-grained insight on a covariance alignment procedure proposed in \cite{WZR20}.
-%We show that the alignment procedure provides more significant improvement when the source/target sample ratio is large.
-%Finally, we validate our three theoretical findings on sentiment analysis tasks.
-
-% plus an identity matrix,  due to lack of freeness
-%\HZ{add why this is challenging}
-
 Finally, we discuss the practical implications of our work.
@@
 We use recently developed techniques from random matrix theory to show a sharp convergence rate.
-% to obtain a sharp estimate on the..., which is commonly referred to as the \emph{local law}.
-%\HZ{add several sentences on the technical insight}
 One limitation of our analysis is that in Example \ref{ex_sample_ratio}, there is an error term that can result in vacuous bounds for very small $n_1$ (cf. equation \eqref{cor_MTL_error}).
@@
 See Section \ref{sec_conclude} for more discussions of the technical challenge.
-
-%This part introduces a positive variance reduction effect from adding the source labels.
-%Hence, whether $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$ is determined precisely by the tradeoff between the negative effect of the bias term and the positive effect of the variance term!
-%(i) the negative effect from model shift bias.
-%(ii) the positive effect from variance reduction;
 
@@
 One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \citet{B00,MPR16}.
-Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
+Moreover, these techniques do not apply to the high-dimensional setting where the sample size is only a small constant factor of the dimension.
 
@@
 \citet{Anisotropic} later extended this result to arbitrary covariance matrices.
-%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
 These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
@@
 One closely related work is \citet{WZR20}, which studied hard parameter sharing for two linear regression tasks.
-However, their results only apply to sample size regimes at least logarithmic factors of dimension.
-%\citet{WZR20} (and an earlier work by \citet{KD12}) observed that the shared layer size $r$ in hard parameter sharing plays a critical role of regularization.
-%Linear models in multi-task learning have been studied in various settings, including online learning \cite{CCG10,DCSP18}, sparse regression \cite{LPTV09,LPVT11}, and representation learning \cite{BHKL19}.
-
-%Our setting is closely related to domain adaptation \cite{DM06,BB07,BC08,DH09,MMR09,CWB11,ZS13,NB17,ZD19}.
-%The important distinction is that we focus on predicting the target task using a hard parameter sharing model.
-%For such models, their output dimension plays an important role of regularization \cite{KD12}.
-%Below, we describe several lines of work that are most related to this work.
-
-%Some of the earliest works on multi-task learning are Baxter , Ben-David and Schuller \cite{BS03}.
-%Mauer \cite{M06} studies generalization bounds for linear separation settings of MTL.
-%The benefit of learning multi-task representations has been studied for learning certain half-spaces \cite{MPR16} and sparse regression \cite{LPTV09,LPVT11}.
-%Our work is closely related to Wu et al. \cite{WZR20}.
-%While Wu et al. provide generalization bounds to show that adding more labeled helps learn the target task more accurately, their techniques cannot be used to explain when MTL outperforms STL.
-%\todo{spell out the challenge more explicitly}
-
-%Ando and Zhang \cite{AZ05} introduces an alternating minimization framework for learning multiple tasks.
-%Argyriou et al. \cite{AEP08} present a convex algorithm which learns common sparse representations across a pool of related tasks.
-%Evgeniou et al. \cite{EMP05} develop a framework for multi-task learning in the context of kernel methods.
-%\cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
-%The multi-task learning model that we have focused on uses the idea of hard parameter sharing \cite{C93,KD12,R17}.
-%We believe that our theoretical framework can apply to other approaches to multi-task learning.
+However, their results only apply to sample size regimes at least logarithmic factors of the dimension.
 
@@
 \noindent\textbf{Notations.}
-%Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
-%We can also write $Y = XB^{\star} + \cE$.
-%Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
 For an $n\times p$ matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its largest singular value.
@@
 We say that an event $\Xi$ holds with high probability if the probability that $\Xi$ happens goes to $1$ as $p$ goes to infinity.
-We use the big-O notation $g(n) = \OO(f(n))$ if there exists a constant $C$ such that $g(n) \le C  f(n)$ for large enough $n$.
-%We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
+We use the big-O notation $g(n) = \OO(f(n))$ to denote that there exists a constant $C$ such that $g(n) \le C  f(n)$ for large enough $n$.
